### 2018-09-04 Manuscript/abstract.Rmd
initial commit

---
header-includes:
    - \usepackage{setspace}
    - \usepackage{amsmath}
output:
  word_document:
    fig_caption: yes
    fig_height: 3
    fig_width: 2
    toc: no
  pdf_document:
    toc: no
---

# Predictive modeling using epigenomic annotations

Spiro Stilianoudakis^1^ , Mikhail G. Dozmorov^1^

^1^ Dept. of Biostatistics, Virginia Commonwealth University, Richmond, VA, 23298, USA

**Background.** Chromosome conformation capture sequencing technologies have shown that the three-dimensional (3D) structure of the genome is folded into distinct compartments, known as topologically associated domains (TADs) - units of coordinated gene expression. The location of TAD boundaries is highly conserved, suggesting the presence of epigenomic marks aiding in TAD formation. The ability to predict which epigenomic features are most associated with the TAD boundaries will allow to better understand the regulatory role of the 3D structure of the genome.

Existing methods for predicting associations between genomic elements ignore key characteristics of the data. Specifically, the number of TAD boundaries is much less than the number of other genomic regions, leading to heavily imbalanced classes. Furthermore, most methods utilize direct overlap as a means to quantify the association, while distance, the measure of spatial relationships, remains unaccounted for. Consequently, distances on a genomic scale vary widely, leaving uncertainty how the heavily right-tailed distribution of distance measures will affect the model’s performance.

**Methods.** We propose a novel data pre-processing pipeline that addresses those shortcomings. It includes an elastic-net regularized classification model, where the mixing proportion, $\alpha$, and the penalization parameter, $\lambda$, are tuned for over a grid of values. A number of classifier performance metrics was assessed, including the F1 measure and Matthew Correlation Coefficient (MCC).

**Results.** Data preprocessing (log2-transformation and standardization) improves the performance of the models. The elastic-net model outperformed multiple logistic regression models, with and without LASSO-regularized coefficients. Likewise, the variable importance of the elastic-net yielded more stable and biologically meaningful results compared to the variables selected by the multiple logistic regression models.

**Conclusions.** Current methods used to model the epigenomic features associated with TAD boundaries are not robust to handle properties of genomic data. Models applied to unprocessed data can have poor predictive performances. Typical performance assessment metrics, such as AUROC, can mask poor performance of the models; thus, the use of more balanced metrics, such as F1 and MCC, is warranted. The elastic-net model, with its dual use of the $l_1$ and $l_2$ regularization terms allows for both the removal of uninformative predictors, while being able to handle multiple correlated epigenomic features. Our model results in better performances and more accurate identification of important features associated with the formation of TAD boundaries.

### 2018-09-04 Manuscript/manuscript.Rmd
initial commit

---
title: "Predictive modeling using genomic annotations"
subtitle: "Pitfalls and Recommendations"
author: "Spiro Stilianoudakis"
date: "August 9, 2018"
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage{amsmath}
output: 
  pdf_document:
    toc: yes
  word_document:
    fig_caption: yes
    fig_height: 3
    fig_width: 2
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# INTRODUCTION

The advent of various genome-wide technologies, such as high-throughput conformation capture (Hi-C), have revealed how the spatial organization of the human genome may affect several epigenetic functions (Aiden et al.). Analyses have shown that the genome is tightly compacted into distinct compartments.  There exist regions within these compartments that are highly conserved and self-interacting, and termed topologically associating domains (TADs) (Dixon et al.). Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD (Symmons et al.). This suggests that the boundaries of TADs may play a role in restricting the function of elements such as enhancers, thereby impacting the transcription of genes.

More recently, it has been discovered that insulators have a primary role in orchestrating the topological arrangement of higher-order chromatin architecture (Phillips-Cremins et al). Insulators are multi-faceted regulatory sequences that moderate a variety of genomic processes including activation, repression, and enhancer blocking. Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long range chromatin contacts (Zuin et al.). Likewise, it was found that DNase I-hypersensitive sites were enriched at the boundaries of domains and correlated with the CTCF signals (Hong et al) [??? They identify more]. On the other hand, it is unclear how other types of regulatory elements such as histone modifications, which are associated with transcriptional initiation and open chromatin structure, are related to TAD boundaries.

The distinct patterns of some of these different proteins and functional elements point toward the opportunity of computational approaches in predicting the development of TAD boundaries. However, due to the size of Hi-C data and the abundance of available genomic features, few methods have been developed to study the role of specific sets of these features on the folding of chromosomes. Furthermore, many widely used methods ignore key characteristics of the data that may hinder the performance of certain parametric models [??? Like what? It may be best to devote a paragraph clearly describing them. Then, describe the Mourad and other approaches]. One such group have proposed a multiple logistic (MLR) model used to identify the most influential proteins with regards to TAD boundaries (Mourad et al.). They also provide an MLR model with LASSO estimated coefficients that they believe is better suited for predictors that may be correlated. However, key aspects of the data were ignored with each of these models, such as the sparsity of domain borders throughout the genome. Likewise, data pre-processing techniques such as normalization, the elimination of low variance predictors, and variable selection techniques were not considered. Furthermore, due to the large number of genomic features that can be considered, accounting for the relationship among features with interaction effects becomes computationally infeasible.

Data pre-processing techniques such as normalization and the elimination of low variance predictors are an integral part of model fitting with regards to genomic data [??? Clarity. Define 1) the problem, and 2) ways to solve it, which is modeling. Then, for modeling, describe problems connecting genomics+machine learning terms]. Continuous predictors tend to be highly shewed. Therefore, a common practice is to perform a log base 2 transformation. It is also sometimes necessary to standardize continuous predictors, especially if they are on different scales. It is unclear, however, which combination of these two concepts improves prediction. Additionally, binary predictors may only be concordant with the outcome of interest in very rare cases. This contributes to predictors with near-zero variances. Eliminating these predictors prior to model fitting can reduce both the noise and the computational speed of the model. We use the nearZeroVar function provided in the caret package to determine which predictors have near-zero variance [??? This sentence is Methods].

TADs can be up to a million base pairs in length and therefore the boundaries are sparse throughout the genome. Sparse data can create heavily imbalanced classes and may affect prediction performance of classification algorithms. There are many techniques that can be used to more evenly balance such data. These include oversampling the minority class, under sampling the majority class, and some combination of both. One such technique is referred to as SMOTE, which stands for Synthetic Minority Over-sampling TEchnique. SMOTE is a function in the DmWR package in R and incorporates both under-sampling and over-sampling. It has been shown that SMOTE out performs simple under-sampling of the majority class for some machine learning algorithms (Nitesh et al). We instead propose a method of taking multiple bootstrap under-samples from the majority class and then aggregating performance metrics by taking the average across all iterations. We then compare this method to SMOTE.

Modeling genomic data often involves a large number of predictors as well. As a result, different machine learning models can benefit from variable selection techniques to reduce the feature space, and thereby improve computational speed. There are several known selection techniques in the field of machine learning including forward, backward, and stepwise selection. These are known as wrapper methods because they measure the usefulness of a subset of features by actually training a model on it. Additionally, we incorporate recursive feature elimination as a method of variable reduction and compare it to the rest.

Furthermore, the model proposed by Mourad et al. falls short of addressing issues such as cross-validation and variable importance, which can be handled more efficiently through ensemble models like random forests and gradient boosting machines.  Therefore, in addition to proposing a novel pipeline that addresses irregularities in the data mentioned above, we also apply a random forest model in order to find the key molecular drivers most associated with TAD boundaries. A random forest was chosen because of its ability to handle potentially correlated variables as well as its inability to overfit. We then compare the performance of the random forest model to the models proposed by Mourad et al.

# METHODS

## THE DATA

Publicly available topologically associating domain data was obtained from GEO with accession GSE53525 for the GM12878 and K562 cell lines.  The domain data was constructed from in situ Hi-C contact matrices at a 5kb and 10 kb resolution for the GM12878 and k562 cell lines respectively. The Arrowhead algorithm was used to identify TAD boundaries for a given contact matrix (Rao et. al). Identified TAD boundaries were represented by their genomic coordinates (hg19 human genome assembly), including chromosome, start and end coordinates. The start and end coordinates were concatenated, sorted, and unique coordinates representing unique TAD boundaries were obtained [??? Check for accuracy]. Next, the genome was binned into a series of 1kb intervals (flanked by 500 bases on either side of the boundary point) and an indicator vector Y was created based on whether there was a TAD boundary located in the 1kb interval (Y=1) or not (Y=0) [??? Should it be simplified - just consider boundaries to be flanked?].

## GENOMIC ANNOTATIONS

Annotation data was obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium [??? We need a table. Check Hong 2017 supplemental, there may be something else that I don't have in GenomeRunner database. Also, check iGD data http://big.databio.org/igd/].  These annotations consisted of genomic coordinates and were used to build the feature space, X = {X1, . . ., Xp}, of the subsequent models. The data consisted of genomic coordinates and chromosomal information. For each genomic feature, an indicator variable (1 for yes; 0 for no) was created based on whether the coordinates of the annotation overlapped with the coordinates representing a flanked TAD boundary. Likewise, a continuous variable representing the distance to the center of the nearest flanked TAD boundary was included [??? Measured in?]. Genomic features that were located inside of a flanked TAD boundary were given a distance of 0. Figure X presents an illustration for how the feature space was constructed.

## DATA PIPELINE

We developed a pipeline that systematically evaluates the problems associated with genomic data in predictive modeling settings. At each stage in the pipeline, Elastic-Net models were performed and performance metrics such as ROC curves and subsequent AUCs were evaluated. The Elastic-Net model was used here because of its ability to be tuned and its computational speed relative to other machine learning algorithms. For each elastic-net model the mixing parameter, alpha, was tuned on a grid of five values (0.1, 0.325, 0.550, 0.775, and 1.0). A sequence of values for the regularization parameter, lambda, was automatically provided by the CARET package in R. The algorithm then chose the optimal combination of alpha and lambda, and the model was evaluated. [??? Unclear, is it cross-validation tuning or what?]

Prior to initiating the pipeline, predictors with near-zero variance were removed. To identify said predictors, the nearZeroVar function in the CARET package was used. The function considers two metrics. First, the ratio of the most frequent value over the second most frequent value was calculated. Ideally, this ratio would be close to one for well-behaved predictors. Next, the number of unique values divided by the total number of samples multiplied by 100 was calculated. Here, if the frequency ratio was greater than 0.99 and the percentage of unique values was less than 0.001, the predictor was flagged as having near-zero variance and removed.

### CLASS IMBALANCE

To assess the class imbalance problem due to the sparcity of domains throughout the genome, two methods were used. The first consisted of incorporating the SMOTE command from the DmWR package in R. SMOTE stands for Synthetic Minority Over-sampling Technique. The SMOTE algorithm incorporates both under-sampling (percent under) of the majority class and over-sampling (percent over) of the minority class. The minority class is over-sampled by taking each minority class sample and introducing synthetic examples along the line segments joining any/all of the k minority class nearest neighbors (here, k=5). Then, the majority class is under sampled by taking a random sample that matches some pre-specified percentage of the updated minority class.  For example, consider a data set with 700 observations, where there are 35 minority classes and 665 majority classes. Now, when using SMOTE, consider a 200 percent over sample of the minority class and a 100 percent under sample of the majority class.  This means that two synthetic observations will be created for every minority class (35+70=105) and 1 majority class will be randomly chosen for every new minority class created (70), resulting in a classification of 70/105 (majority/minority). Now consider, a 200/200 combination. The new minority class is still 105 (70 new synthetic observations created), but now twice as many majority classes are randomly chosen (70*2=140), resulting in a 140/105 classification. It is important to note that using a combination of 100/200 will always result in perfectly balanced classes. A total of eight different combinations of percent over and undersampling were used which included: 100/200, 200/200, 300/200, 400/200, 100/300, 200/300, 300/300, 400/300. Here, the 100/200 combination creates a completely balanced dataset as mentioned before, while the others create an unbalanced dataset with the “No” class as the majority to reflect the original data. The second method involved iteratively taking 100 bootstrap samples of the majority class to match the number in the minority class. For each sample, an elastic-net model was tuned and evaluated. Then row wise means of the sensitivities, specificities, and AUCs of each of the 100 bootstrap samples were taken to evaluate the models as a whole. The SMOTE combination with the best performance was then compared to the bootstrap method. ROC curves were plotted and corresponding AUCs were presented in a table.

### NORMALIZATION

In order to correct for the skewness of the distances [??? Should be defined in the introduction], elastic-net models were evaluated based on a combination of log transformed and/or standardized predictors. A total of four elastic net models were performed including: with log transformation and standardization, without log transformation and with standardization, with log transformation and without standardization, and without log transformation and without standardization. One hundred bootstrap samples were taken from the majority class to create a balanced classification data. ROC curves were plotted and corresponding AUCs were presented in a table.  Likewise, we looked at the variable importance quality of the models.

### VARIABLE SELECTION

Due to the large number of genomic features included in the model, different variable selection techniques were evaluated in order to prevent overfitting, improve computational speed, and eliminate uninformative variables. There were three different wrapper methods that were used here, forward, backward, and stepwise selection. A null model consisting of just an intercept term and a full model, including all features, were specified for each selection technique. For all three, a logistic regression model was performed, and the AIC of the fitted model was used to establish which variables to include. That is, only a reduction in the model's AIC contributed to the inclusion of a feature in the model. Additionally, a recursive feature elimination (RFE) algorithm was performed. In RFE, a full model was created, a measure of variable importance was then computed that ranked the predictors from the most important to the least. Here, the importance of the model was based on the random forest importance criterion [??? Unclear how is it different from backward selection, compare and contrast]. Then, at each stage of the search, the least important predictors were iteratively eliminated prior to rebuilding the model. The process was continued for a pre-specified subset of predictors.

## FINAL MODEL

Once the pipeline produced the appropriate dataset, a random forest algorithm was used to assess which genomic features that were most predictive of the development of TAD boundaries. The algorithm was run iteratively over 100 bootstrap samples, each time producing sensitivities, specificities, AUCs, and variable importances. For each iteration, the model was tuned on the best number of predictors to subset as well as the optimal number of trees to use. At the end of the 100 iterations, row wise means were performed to aggregate the model performances. We then compared the random forest model to both the MLR model and the MLR model with LASSO estimated coefficients that was proposed by Mourad et al.

# RESULTS

There was a total of 247632 genomic bins that made up the response vector Y, 1629 (0.7%) of which contained TAD boundaries (Y=1). A total of 68 genomic features were included in the analysis. Two predictors were included for every feature (one binary, one continuous), making for a total of 136 predictors.  The list of predictors is provided in Table X. The feature space was reduced to 90 after all near-zero variance predictors were removed. The predictors that were removed are listed in Table X [??? Mark them in supplementary table of all features].

Figure X presents the model performance metrics of the eight different SMOTE combinations. The SMOTE combination utilizing percent over of 100 and percent under of 200 yielded the largest AUC (0.794). This was to be expected since this combination created perfectly balanced classes. However, looking at Figure X, the method using 100 bootstrap sample performed better than then model using SMOTE with an AUC of 0.809. Thus, it was concluded that using bootstrap samples would be more efficient moving forward.

The best normalization technique was found to be the model that included a log base 2 transform with no standardized predictors. The AUC was found to be 0.809 and presented in Figure X. We see that this value is only marginally greater than the model using a log base 2 transform and standardized predictors. However, from Figure X, we see that the variable importance plot associated with a log base 2 transform with no standardized predictors (top right) yielded more accurate results than all other combinations. Notably, the insulator, CTCF, and DNaseI features are located in the top 3 most important features for predicting TAD boundaries, as expected. This is in contrast to the other three combinations, which presented conflicting results. Thus, it was concluded that only performing a log base 2 transformation was necessary.

The best performing variable selection technique was found to be forward selection (AUC: 0.810) as shown in Figure X. All of the stepwise procedures performed better than the recursive feature elimination method, which not only performed worse, but also chose the most predictors. It should be noted that both forward and backward selection had the same AUC. However, the forward selection chose fewer predictors, 28 compared to 34 respectively. Thus, forward selection was chose as the most appropriate variable selection technique. Figure X presents the relationship between each variable selection technique. We see that there was significant agreement between forward and backward selections, with 26 predictors being shared by both. Likewise, there was a total of 12 predictors in common between all four techniques. Table X lists the common predictors between each comparison.

After the data was ran through our pipeline, the final dataset consisted of 28 log transformed predictors. Lastly, 100 bootstrap sampled random forest models were performed on said data. Figure X presents the results compared to the multiple logistic regression models proposed by Mourad et al. We see that the random forest model, using the pipeline processed data, preforms better compared to both models proposed by Mourad et al with an AUC of 0.805. Moreover, the variable importance plot in Figure X reiterates the strong predictive performance of the random forest model by indicating that the DNaseI, insulator, and CTCF genomic features are among the top 3 variables most predictive TAD boundaries. The MLR with LASSO estimation only marginally out performs the regular MLR model with AUCs of 0.750 and 0.747 respectively. Likewise, from Table X we can see that there is more similarity in the ranking of important features between the random forest model and the MLR with LASSO model. However, there is still a large disparity, with 12 variables recognized as important by the random forest that are missing from the MLR with LASSO model. Thus, we conclude that a random forest algorithm applied to a dataset ran through the proposed pipeline performs uniformly better than a multiple logistic regression model, regardless if LASSO estimation is used.

# DISCUSSION

### 2018-09-04 GM12878/Data_Pipeline/01model_filtering_gm12878.R

@@ -1,0 +1,952 @@
+#Model filtering
+
+#Loading Libraries
+
+library(GenomicRanges)
+library(caret)
+library(data.table)
+library(gbm)
+library(randomForest)
+library(glmnet)
+library(pROC)
+library(plyr)
+library(dplyr)
+library(ggplot2)
+library(DMwR)
+library(gridExtra)
+library(pROC)
+library(ROCR)
+library(leaps)
+
+# Creating Response Vector Y
+
+## Reading in TAD data
+
+domains <- read.table("/home/stilianoudakisc/TAD_data_analysis/GM12878/arrowhead_data.txt", header=T)
+domains <- domains[,1:3]
+head(domains)
+dim(domains) #9274    3
+
+#removing chrX from boundary data
+domains <- domains[-which(domains$Chromosome=="chrX"),]
+
+#creating granges object out of tad boundary data
+
+#concatenating boundary coordinates into one long vector
+coords <- domains
+colnames(coords)[2:3] <- c("coordinate", "coordinate")
+coords <- rbind.data.frame(coords[,c(1,2)],coords[,c(1,3)])
+coords$Chromosome <- as.character(coords$Chromosome)
+
+#sorting by chromosome and coordinate
+coords <- coords[order(as.numeric(substr(coords$Chromosome,4,5)), coords$coordinate, decreasing = FALSE),]
+
+#remove duplicates for coordinates that are conjoined
+coords <- coords[!duplicated(coords),]
+dim(coords) #16770     2
+
+coords$lagchrom <- lag(coords$Chromosome)
+coords$lagchrom[which(coords$Chromosome!=coords$lagchrom)] <- NA
+coords$lagcoord <- lag(coords$coordinate)
+coords$lagcoord[which(is.na(coords$lagchrom))] <- NA
+
+bounds <- GRanges(seqnames=coords$Chromosome, ranges=IRanges(start=coords$coordinate, width=1))
+bounds_f <- flank(bounds, width=5000, both=TRUE)
+
+#saving data
+saveRDS(bounds, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds.rds")
+saveRDS(bounds_f, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds_f.rds")
+
+
+## Reading in binned genome in the form of contact matrix at 10kb resolution
+
[…]

### 2018-09-04 GM12878/Data_Pipeline/02normalization_gm12878.R

@@ -1,0 +1,435 @@
+#Elastic net
+
+library(caret)
+#library(data.table)
+library(gbm)
+library(pROC)
+library(plyr)
+library(dplyr)
+#library(DMwR)
+library(gridExtra)
+library(ggplot2)
+
+setwd("/home/stilianoudakisc/TAD_data_analysis/comparing_normalization/")
+
+gm12878_10kb_f <- readRDS("gm12878_10kb_f.rds")
+
+
+#set number of bootstrap samples
+#1 = 5
+
+#set tuning parameters
+fitControl <- trainControl(method = "repeatedcv",
+                           number = 10,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           summaryFunction = twoClassSummary)
+
+#create a matrix of row ids that represent the zero class
+#the number of rows will match the one class
+#the number of columns match the number of bootstrap samples
+#sampids <- matrix(ncol=1, 
+#                  nrow=length(gm12878_10kb_f$y[which(gm12878_10kb_f$y=="Yes")]))
+
+
+#filling in the sample ids matrix
+#set.seed(123)
+#for(j in 1:1){
+#  sampids[,j] <- sample(which(gm12878_10kb_f$y=="No"),
+#                        length(which(gm12878_10kb_f$y=="Yes")),
+#                        replace = TRUE)
+#}
+
+
+#function for roc curves
+simple_roc <- function(labels, scores){
+  labels <- labels[order(scores, decreasing=TRUE)]
+  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
+}
+
+########################################################################################
+
+#With log transform and standardization
+
+#set length of list objects that will be filled in with specificities
+#and sensitivities and aucs and variable importance
+enetlst_ls <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb_f$y=="Yes"))*2)*.3), 
+                                 ncol=1),
+                   fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb_f$y=="Yes"))*2)*.3), 
+                                 ncol=1),
+                   varimp <- matrix(nrow=dim(gm12878_10kb_f)[2]-1,
[…]

### 2018-09-04 GM12878/Data_Pipeline/03class_imbalance_gm12878.R

@@ -1,0 +1,681 @@
+#Testing SMOTE combinations for Elastic Net
+
+
+library(caret)
+library(data.table)
+library(gbm)
+library(glmnet)
+library(pROC)
+library(plyr)
+library(dplyr)
+library(DMwR)
+library(gridExtra)
+
+
+setwd("/home/stilianoudakisc/TAD_data_analysis/evaluating_SMOTE/")
+
+gm12878_10kb_f <- readRDS("gm12878_10kb_f.rds")
+
+# Splitting the data
+set.seed(5228)
+inTrainingSet <- createDataPartition(gm12878_10kb_f$y,p=.7,list=FALSE)
+train <- gm12878_10kb_f[inTrainingSet,]
+test <- gm12878_10kb_f[-inTrainingSet,]
+
+# Establishing tuning/training parameters
+fitControl <- trainControl(method = "repeatedcv",
+                           number = 10,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           summaryFunction = twoClassSummary)
+
+#function for roc curves
+simple_roc <- function(labels, scores){
+  labels <- labels[order(scores, decreasing=TRUE)]
+  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
+}
+
+#Testing eight different combinations of perc.over/perc.under
+#100/200, 200/200, 300/200, 400/200, 
+#100/300, 200/300, 300/300, 400/300
+
+#########################################################################################
+
+
+#SMOTE
+
+#set length of list objects that will be filled in with specificities
+#and sensitivities and aucs and variable importance
+enetlst_sm <- list(tpr <- matrix(nrow=length(test$y), 
+                                 ncol=4),
+                   fpr <- matrix(nrow=length(test$y), 
+                                 ncol=4),
+                   varimp <- matrix(nrow=dim(gm12878_10kb_f)[2]-1,
+                                    ncol=4))
+rownames(enetlst_sm[[3]]) <- colnames(gm12878_10kb_f)[-1]
+
+enetperf_sm <- matrix(nrow = 17, ncol=4)
[…]

### 2018-09-04 GM12878/Data_Pipeline/04variable_reduction_rfe_gm12878.R

@@ -1,0 +1,196 @@
+library(GenomicRanges)
+library(caret)
+library(data.table)
+library(gbm)
+library(randomForest)
+library(glmnet)
+library(pROC)
+library(plyr)
+library(dplyr)
+library(ggplot2)
+library(DMwR)
+library(gridExtra)
+library(pROC)
+library(ROCR)
+library(leaps)
+
+setwd("/home/stilianoudakisc/TAD_data_analysis/evaluating_variable_reduction/")
+
+#### Forward Selection
+
+gm12878_10kb_f <- readRDS("gm12878_10kb_f.rds")
+
+####set number of bootstrap samples
+
+#bootsamps = 5
+
+#### function for roc curves
+
+simple_roc <- function(labels, scores){
+  labels <- labels[order(scores, decreasing=TRUE)]
+  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
+}
+
+
+#### Establishing tuning/training parameters
+
+fitControl <- trainControl(method = "repeatedcv",
+                           number = 10,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           summaryFunction = twoClassSummary)
+
+####create a matrix of row ids that represent the zero class
+
+#sampids <- matrix(ncol=bootsamps, 
+#                  nrow=length(gm12878_10kb_f$y[which(gm12878_10kb_f$y=="Yes")]))
+				  
+####filling in the sample ids matrix
+
+#set.seed(123)
+#for(j in 1:bootsamps){
+#  sampids[,j] <- sample(which(gm12878_10kb_f$y=="No"),
+#                        length(which(gm12878_10kb_f$y=="Yes")),
+#                        replace = TRUE)
+#}
+
+
+#### Recursive Feature Elimination
+
+
+#setting rfe parameters
+control <- rfeControl(functions=rfFuncs, method="cv", number=10, repeats=5)
+
+trainctrl <- trainControl(classProbs= TRUE,
+                          summaryFunction = twoClassSummary)
+
+#namesmat <- matrix(NA,nrow=dim(gm12878_10kb_f)[2]-1, ncol=bootsamps)
[…]

### 2018-09-04 GM12878/Full_Data_Modeling_Pipeline/full_data_model_pipeline.R

@@ -1,0 +1,4015 @@
+setwd("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb_bins/")
+
+#Loading Libraries
+
+library(GenomicRanges)
+library(caret)
+library(data.table)
+library(gbm)
+library(randomForest)
+library(glmnet)
+library(pROC)
+library(plyr)
+library(dplyr)
+library(ggplot2)
+library(DMwR)
+library(gridExtra)
+library(pROC)
+library(ROCR)
+library(leaps)
+
+# Creating Response Vector Y
+
+## Reading in TAD data
+
+domains <- read.table("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb_bins/arrowhead_data.txt", header=T)
+domains <- domains[,1:3]
+head(domains)
+dim(domains) #9274    3
+
+#removing chrX from boundary data
+domains <- domains[-which(domains$Chromosome=="chrX"),]
+
+#creating granges object out of tad boundary data
+
+#concatenating boundary coordinates into one long vector
+coords <- domains
+colnames(coords)[2:3] <- c("coordinate", "coordinate")
+coords <- rbind.data.frame(coords[,c(1,2)],coords[,c(1,3)])
+coords$Chromosome <- as.character(coords$Chromosome)
+
+#sorting by chromosome and coordinate
+coords <- coords[order(as.numeric(substr(coords$Chromosome,4,5)), coords$coordinate, decreasing = FALSE),]
+
+#remove duplicates for coordinates that are conjoined
+coords <- coords[!duplicated(coords),]
+dim(coords) #16770     2
+
+bounds <- GRanges(seqnames=coords$Chromosome, ranges=IRanges(start=coords$coordinate, width=1))
+
+#saving data
+saveRDS(bounds, "/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb_bins/bounds.rds")
+
+
+## Reading in binned genome in the form of contact matrix at 10kb resolution
+
+binslist10 <- read.table("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb_bins/binslist10.txt")
+
+dim(binslist10) #268498      2
+
+#ordering the bins according to left endpoint
+binslist10 <- binslist10[order(as.numeric(substr(binslist10$V1,4,5)), binslist10$V2, decreasing=FALSE),]
+
[…]

### 2018-09-04 GM12878/Measuring_Performances/measuring_performances.R

@@ -1,0 +1,852 @@
+# Measuring Performances and Providing Summaries
+
+# Loading Libraries
+
+library(GenomicRanges)
+library(caret)
+library(data.table)
+library(gbm)
+library(randomForest)
+library(glmnet)
+library(pROC)
+library(plyr)
+library(dplyr)
+library(ggplot2)
+library(DMwR)
+library(gridExtra)
+library(pROC)
+library(ROCR)
+library(leaps)
+library(limma)
+
+gm12878_10kb <- readRDS("/home/stilianoudakisc/TAD_data_analysis/measuring_performances/gm12878_10kb.rds")
+gm12878_10kb_f <- readRDS("/home/stilianoudakisc/TAD_data_analysis/measuring_performances/gm12878_10kb_f.rds")
+gm12878_10kb_reduced <- readRDS("/home/stilianoudakisc/TAD_data_analysis/final_models/gm12878_10kb_reduced.rds")
+
+
+distancetab <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/distancetab.rds")
+featdistdf2 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/featdistdf2.rds")
+
+bounds <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds.rds")
+grlist <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/grlist.rds")
+
+binslist10_center <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/binslist10_center.rds")
+
+#############################################################################
+
+#data exploration
+
+domains <- read.table("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb_bins/arrowhead_data.txt", header=T)
+domains <- domains[,1:3]
+
+#removing chrX from boundary data
+domains <- domains[-which(domains$Chromosome=="chrX"),]
+
+#adding distance variable
+domains$distance <- domains$End - domains$Start
+#log2 transform of distance
+domains$logdist <- log(domains$distance, base = 2)
+
+#distance of TADs
+
+tadlength <- ggplot() + geom_density(data=domains, aes(x=distance, group=Chromosome, color=Chromosome)) + 
+	xlab("Length of TADs") + 
+	xlim(0,1000000) + 
+	ylab("Density")+ 
[…]

### 2018-09-04 GM12878/Modeling/Mourad_Models/mourad_model_LASSOgm12878.R

@@ -1,0 +1,410 @@
+setwd("/home/stilianoudakisc/TAD_data_analysis/mourad_model/")
+
+library(GenomicRanges)
+library(caret)
+library(Matrix)
+library(glmnet)
+library(pROC)
+library(ROCR)
+
+averagePerBin <- function(x, binsize, mcolname)
+{
+ if(!is(x, "GenomicRanges")){stop("'x' must be a GenomicRanges object")}
+ if(any(is.na(seqlengths(x)))){stop("'seqlengths(x)' contains NAs")}
+
+ bins <- IRangesList(lapply(seqlengths(x),function(seqlen)IRanges(breakInChunks(seqlen, binsize))))
+
+ cvg <- coverage(x, weight=mcolname)
+
+ views_list <- RleViewsList(lapply(names(cvg),function(seqname)Views(cvg[[seqname]], bins[[seqname]])))
+
+ averageBin=NULL
+ for(i in 1:length(views_list)){
+  averageBin=c(averageBin,viewMeans(views_list)[[i]])
+ }
+
+ return(averageBin)
+}
+
+
+
+
+
+borderAnalysisFun<-function(genomicFeatureList.GR,GFDataType,annotNames,domains.GR,seqInfoChr,analysisMode,binSize=50,borderSize=1000,LRT=FALSE,interactionTerms="",testBorderType=FALSE,verbose=FALSE){
+
+
+# CHECK INPUT DATA ------------------------------------------------------------ 
+
+if(verbose){print("DATA CHECKING")}
+
+if(class(genomicFeatureList.GR)!="list"){print("genomicFeatureList.GR is not a list object!"); return(0)}
+for(i in 1:length(genomicFeatureList.GR)){
+ if(class(genomicFeatureList.GR[[i]])!="GRanges"){print("i-th object of genomicFeatureList.GR is not a GenomicRanges object!"); return(0)}
+}
+if(class(GFDataType)!="character"){print("GFDataType is not a character object!"); return(0)}
+if(class(annotNames)!="character"){print("annotNames is not a character object!"); return(0)}
+if(class(domains.GR)!="GRanges"){print("domains.GR is not a GenomicRanges object!"); return(0)}
[…]

### 2018-09-04 GM12878/Modeling/Mourad_Models/mourad_model_glm_gm12878.R

@@ -1,0 +1,394 @@
+setwd("/home/stilianoudakisc/TAD_data_analysis/mourad_model/")
+
+library(caret)
+library(GenomicRanges)
+library(Matrix)
+library(glmnet)
+library(pROC)
+library(ROCR)
+#library(zoo)
+#library(pracma)
+
+averagePerBin <- function(x, binsize, mcolname)
+{
+ if(!is(x, "GenomicRanges")){stop("'x' must be a GenomicRanges object")}
+ if(any(is.na(seqlengths(x)))){stop("'seqlengths(x)' contains NAs")}
+
+ bins <- IRangesList(lapply(seqlengths(x),function(seqlen)IRanges(breakInChunks(seqlen, binsize))))
+
+ cvg <- coverage(x, weight=mcolname)
+
+ views_list <- RleViewsList(lapply(names(cvg),function(seqname)Views(cvg[[seqname]], bins[[seqname]])))
+
+ averageBin=NULL
+ for(i in 1:length(views_list)){
+  averageBin=c(averageBin,viewMeans(views_list)[[i]])
+ }
+
+ return(averageBin)
+}
+
+simple_roc <- function(labels, scores){
+        labels <- labels[order(scores, decreasing=TRUE)]
+        data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
+      }
+
+
+
+borderAnalysisFun<-function(genomicFeatureList.GR,GFDataType,annotNames,domains.GR,seqInfoChr,analysisMode,binSize=50,borderSize=1000,LRT=FALSE,interactionTerms="",testBorderType=FALSE,verbose=FALSE){
+
+
+# CHECK INPUT DATA ------------------------------------------------------------ 
+
+if(verbose){print("DATA CHECKING")}
+
+if(class(genomicFeatureList.GR)!="list"){print("genomicFeatureList.GR is not a list object!"); return(0)}
+for(i in 1:length(genomicFeatureList.GR)){
+ if(class(genomicFeatureList.GR[[i]])!="GRanges"){print("i-th object of genomicFeatureList.GR is not a GenomicRanges object!"); return(0)}
+}
+if(class(GFDataType)!="character"){print("GFDataType is not a character object!"); return(0)}
[…]

### 2018-09-04 GM12878/Modeling/Our_Models/enet.R

@@ -1,0 +1,169 @@
+# Loading Libraries
+
+
+
+library(GenomicRanges)
+library(caret)
+library(data.table)
+library(gbm)
+library(randomForest)
+library(glmnet)
+library(pROC)
+library(plyr)
+library(dplyr)
+library(ggplot2)
+library(DMwR)
+library(gridExtra)
+library(pROC)
+library(ROCR)
+library(leaps)
+
+
+
+# Reading in data
+
+setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
+
+#chromosome 1 filtered/log transformed/no standardization/forward selection
+
+gm12878_10kb_reduced <- readRDS("gm12878_10kb_reduced.rds")
+
+### set number of bootstrap samples
+
+
+bootsamps = 5
+
+### set tuning parameters
+
+
+fitControl <- trainControl(method = "repeatedcv",
+                           number = 10,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           summaryFunction = twoClassSummary)
+						   
+#### function for roc curves
+
+simple_roc <- function(labels, scores){
+  labels <- labels[order(scores, decreasing=TRUE)]
+  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
+}
+						
+###create a matrix of row ids that represent the zero class
+
+##the number of rows will match the one class
+##the number of columns match the number of bootstrap samples
+
+sampids <- matrix(ncol=bootsamps, 
+                  nrow=length(gm12878_10kb_reduced$y[which(gm12878_10kb_reduced$y=="Yes")]))
+
+
+###filling in the sample ids matrix
+
+set.seed(123)
+for(j in 1:bootsamps){
+  sampids[,j] <- sample(which(gm12878_10kb_reduced$y=="No"),
+                        length(which(gm12878_10kb_reduced$y=="Yes")),
+                        replace = TRUE)
+}
+
+
+
+# Final Models:
+
+# Elastic Net
+
+#set length of list objects that will be filled in with specificities
+#and sensitivities and aucs and variable importance
[…]

### 2018-09-04 GM12878/Modeling/Our_Models/enet_unbalanced.R

@@ -1,0 +1,152 @@
+# Loading Libraries
+
+
+
+library(GenomicRanges)
+library(caret)
+library(data.table)
+library(gbm)
+library(randomForest)
+library(glmnet)
+library(pROC)
+library(plyr)
+library(dplyr)
+library(ggplot2)
+library(DMwR)
+library(gridExtra)
+library(pROC)
+library(ROCR)
+library(leaps)
+
+
+
+# Reading in data
+
+setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
+
+
+
+gm12878_10kb_reduced <- readRDS("gm12878_10kb_reduced.rds")
+
+
+
+# Final Models:
+
+## Elastic Net
+
+### set tuning parameters
+
+
+fitControl <- trainControl(method = "repeatedcv",
+                           number = 10,
+                           repeats = 5,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           summaryFunction = twoClassSummary)
+						   
+#### function for roc curves
+
+simple_roc <- function(labels, scores){
+  labels <- labels[order(scores, decreasing=TRUE)]
+  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
+}
+						
+
+###Performing model
+
+#set length of list objects that will be filled in with specificities
+#and sensitivities and aucs and variable importance
+enetlst <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb_reduced$y=="Yes"))*2)*.3), 
+                              ncol=1),
+                fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb_reduced$y=="Yes"))*2)*.3), 
+                              ncol=1),
+                varimp <- matrix(nrow=dim(gm12878_10kb_reduced)[2]-1,
+                                 ncol=1),
+				coefs <- matrix(nrow=dim(gm12878_10kb_reduced)[2]-1,
+									ncol=1))
+rownames(enetlst[[3]]) <- colnames(gm12878_10kb_reduced)[-1]
[…]

### 2018-09-04 GM12878/Modeling/Our_Models/full_enet.R

@@ -1,0 +1,130 @@
+#Elastic Net on Full Data
+
+library(GenomicRanges)
+library(caret)
+library(data.table)
+library(gbm)
+library(randomForest)
+library(glmnet)
+library(pROC)
+library(plyr)
+library(dplyr)
+library(ggplot2)
+library(DMwR)
+library(gridExtra)
+library(pROC)
+library(ROCR)
+library(leaps)
+
+
+setwd("/home/stilianoudakisc/TAD_data_analysis/full_data_model/")
+
+gm12878_10kb <- readRDS("gm12878_10kb.rds")
+
+gm12878_10kb$y <- factor(gm12878_10kb$y)
+
+levels(gm12878_10kb$y) <- c("No","Yes")
+
+#set tuning parameters
+fitControl <- trainControl(method = "repeatedcv",
+                           number = 10,
+                           repeats = 3,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           summaryFunction = twoClassSummary)
+
+#function for roc curves
+simple_roc <- function(labels, scores){
+  labels <- labels[order(scores, decreasing=TRUE)]
+  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
+}
+
+
+#splitting data
+inTrainingSet <- sample(length(gm12878_10kb$y),floor(length(gm12878_10kb$y)*.7))
+#inTrainingSet <- createDataPartition(data$y,p=.7,list=FALSE)
+train <- gm12878_10kb[inTrainingSet,]
+test <- gm12878_10kb[-inTrainingSet,]
+  
+  
+#set length of list objects that will be filled in with specificities
+#and sensitivities and aucs and variable importance
+enetlst_full <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
+                                 ncol=1),
+                   fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
+                                 ncol=1),
+                   varimp <- matrix(nrow=dim(gm12878_10kb)[2]-1,
+                                    ncol=1))
+rownames(enetlst_full[[3]]) <- colnames(gm12878_10kb)[-1]
+
+
+enetperf_full <- matrix(nrow = 17, ncol=1)
[…]

### 2018-09-04 GM12878/Modeling/Our_Models/full_rf.R

@@ -1,0 +1,162 @@
+#RF on Full Data
+
+library(GenomicRanges)
+library(caret)
+library(data.table)
+library(gbm)
+library(randomForest)
+library(glmnet)
+library(pROC)
+library(plyr)
+library(dplyr)
+library(ggplot2)
+library(DMwR)
+library(gridExtra)
+library(pROC)
+library(ROCR)
+library(leaps)
+
+
+setwd("/home/stilianoudakisc/TAD_data_analysis/full_data_model/")
+
+
+gm12878_10kb <- readRDS("gm12878_10kb.rds")
+
+gm12878_10kb$y <- factor(gm12878_10kb$y)
+
+levels(gm12878_10kb$y) <- c("No","Yes")
+
+#set tuning parameters
+fitControl <- trainControl(method = "repeatedcv",
+                           number = 10,
+                           repeats = 3,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           summaryFunction = twoClassSummary)
+
+#function for roc curves
+simple_roc <- function(labels, scores){
+  labels <- labels[order(scores, decreasing=TRUE)]
+  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
+}
+
+
+#set length of list objects that will be filled in with specificities
+#and sensitivities and aucs and variable importance
+rflst_full <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
+                                 ncol=1),
+                   fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
+                                 ncol=1),
+                   varimp <- matrix(nrow=dim(gm12878_10kb)[2]-1,
+                                    ncol=1))
+rownames(rflst_full[[3]]) <- colnames(gm12878_10kb)[-1]
+
+
+rfperf_full <- matrix(nrow = 17, ncol=1)
+rownames(rfperf_full) <- c("TN",
+                          "FN",
+                          "FP",
+                          "TP",
+                          "Total",
+                          "Sensitivity",
+                          "Specificity",
[…]

### 2018-09-04 GM12878/Modeling/Our_Models/lasso.R

@@ -1,0 +1,140 @@
+# Loading Libraries
+
+library(GenomicRanges)
+library(caret)
+library(data.table)
+library(gbm)
+library(randomForest)
+library(glmnet)
+library(pROC)
+library(plyr)
+library(dplyr)
+library(ggplot2)
+library(DMwR)
+library(gridExtra)
+library(pROC)
+library(ROCR)
+library(leaps)
+
+# Reading in data
+
+setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
+
+
+gm12878_10kb <- readRDS("gm12878_10kb.rds")
+
+#set tuning parameters
+fitControl <- trainControl(method = "repeatedcv",
+                           number = 10,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           summaryFunction = twoClassSummary)
+						   
+
+#function for roc curves
+simple_roc <- function(labels, scores){
+  labels <- labels[order(scores, decreasing=TRUE)]
+  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
+}
+
+
+#set length of list objects that will be filled in with specificities
+#and sensitivities and aucs and variable importance
+lassolst <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
+                              ncol=1),
+                fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
+                              ncol=1),
+                varimp <- matrix(nrow=dim(gm12878_10kb)[2]-1,
+                                 ncol=1),
+				coefs <- matrix(nrow=dim(gm12878_10kb)[2]-1,
+									ncol=1))
+rownames(lassolst[[3]]) <- colnames(gm12878_10kb)[-1]
+rownames(lassolst[[4]]) <- colnames(gm12878_10kb)[-1]				 
+								 
+lassoperf <- matrix(nrow = 17, ncol=1)
+rownames(lassoperf) <- c("TN",
+ 							"FN",
[…]

### 2018-09-04 GM12878/Modeling/Our_Models/mlr.R

@@ -1,0 +1,138 @@
+# Loading Libraries
+
+library(GenomicRanges)
+library(caret)
+library(data.table)
+library(gbm)
+library(randomForest)
+library(glmnet)
+library(pROC)
+library(plyr)
+library(dplyr)
+library(ggplot2)
+library(DMwR)
+library(gridExtra)
+library(pROC)
+library(ROCR)
+library(leaps)
+
+# Reading in data
+
+setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
+
+
+gm12878_10kb <- readRDS("gm12878_10kb.rds")
+
+#set tuning parameters
+fitControl <- trainControl(method = "repeatedcv",
+                           number = 10,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           summaryFunction = twoClassSummary)
+						   
+#function for roc curves
+simple_roc <- function(labels, scores){
+  labels <- labels[order(scores, decreasing=TRUE)]
+  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
+}
+
+
+						   
+#set length of list objects that will be filled in with specificities
+#and sensitivities and aucs and variable importance
+glmlst <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
+                              ncol=1),
+                fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
+                              ncol=1),
+                varimp <- matrix(nrow=dim(gm12878_10kb)[2]-1,
+                                 ncol=1),
+				coefs <- matrix(nrow=dim(gm12878_10kb)[2]-1,
+									ncol=1))
+rownames(glmlst[[3]]) <- colnames(gm12878_10kb)[-1]
+rownames(glmlst[[4]]) <- colnames(gm12878_10kb)[-1]				 
+								 
+glmperf <- matrix(nrow = 17, ncol=1)
+rownames(glmperf) <- c("TN",
+ 							"FN",
+ 							"FP",
[…]

### 2018-09-04 GM12878/Modeling/Our_Models/rf.R

@@ -1,0 +1,207 @@
+
+# Loading Libraries
+
+
+
+library(GenomicRanges)
+library(caret)
+library(data.table)
+library(gbm)
+library(randomForest)
+library(glmnet)
+library(pROC)
+library(plyr)
+library(dplyr)
+library(ggplot2)
+library(DMwR)
+library(gridExtra)
+library(pROC)
+library(ROCR)
+library(leaps)
+
+
+
+# Reading in data
+
+setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
+
+#chromosome 1 filtered/log transformed/no standardization/forward selection
+
+gm12878_10kb_reduced <- readRDS("gm12878_10kb_reduced.rds")
+
+
+
+# Final Models:
+
+## Random Forest
+
+### set number of bootstrap samples
+
+
+bootsamps = 5
+
+### set tuning parameters
+
+
+fitControl <- trainControl(method = "repeatedcv",
+                           number = 5,
+                           repeats = 3,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           summaryFunction = twoClassSummary)
+						   
+#### function for roc curves
+
+simple_roc <- function(labels, scores){
+  labels <- labels[order(scores, decreasing=TRUE)]
+  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
+}
+						
+###create a matrix of row ids that represent the zero class
+
+##the number of rows will match the one class
+##the number of columns match the number of bootstrap samples
+
+sampids <- matrix(ncol=bootsamps, 
+                  nrow=length(gm12878_10kb_reduced$y[which(gm12878_10kb_reduced$y=="Yes")]))
+
+
+###filling in the sample ids matrix
+
+set.seed(123)
+for(j in 1:bootsamps){
+  sampids[,j] <- sample(which(gm12878_10kb_reduced$y=="No"),
+                        length(which(gm12878_10kb_reduced$y=="Yes")),
+                        replace = TRUE)
+}
+
+
+###Performing model
+
[…]

### 2018-09-04 GM12878/Modeling/Our_Models/rf_unbalanced.R

@@ -1,0 +1,175 @@
+# Loading Libraries
+
+
+
+library(GenomicRanges)
+library(caret)
+library(data.table)
+library(gbm)
+library(randomForest)
+library(glmnet)
+library(pROC)
+library(plyr)
+library(dplyr)
+library(ggplot2)
+library(DMwR)
+library(gridExtra)
+library(pROC)
+library(ROCR)
+library(leaps)
+
+
+
+# Reading in data
+
+setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
+
+#chromosome 1 filtered/log transformed/no standardization/forward selection
+
+gm12878_10kb_reduced <- readRDS("gm12878_10kb_reduced.rds")
+
+
+
+# Final Models:
+
+## Random Forest
+
+### set tuning parameters
+
+
+fitControl <- trainControl(method = "repeatedcv",
+                           number = 10,
+                           repeats = 5,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           summaryFunction = twoClassSummary)
+						   
+#### function for roc curves
+
+simple_roc <- function(labels, scores){
+  labels <- labels[order(scores, decreasing=TRUE)]
+  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
+}
+						
+
+###Performing model
+
+#set length of list objects that will be filled in with specificities
+#and sensitivities and aucs and variable importance
+rflst <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb_reduced$y=="Yes"))*2)*.3), 
+                              ncol=1),
+                fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb_reduced$y=="Yes"))*2)*.3), 
+                              ncol=1),
+                varimp <- matrix(nrow=dim(gm12878_10kb_reduced)[2]-1,
+                                 ncol=1))
+rownames(rflst[[3]]) <- colnames(gm12878_10kb_reduced)[-1]
+
+rfperf <- matrix(nrow = 17, ncol=1)
+rownames(rfperf) <- c("TN",
[…]

### 2018-09-04 Manuscript/manuscript.Rmd
updates

@@
 ```
+
+# ABSTRACT
+
+###Background 
+Chromosome conformation capture sequencing technologies have shown that the three-dimensional (3D) structure of the genome is folded into distinct compartments, known as topologically associated domains (TADs) - units of coordinated gene expression.
+The location of TAD boundaries is highly conserved, suggesting the presence of epigenomic marks aiding in TAD formation.
+The ability to predict which epigenomic features are most associated with the TAD boundaries will allow to better understand the regulatory role of the 3D structure of the genome.
+
+Existing methods for predicting associations between genomic elements ignore key characteristics of the data.
+Specifically, the number of TAD boundaries is much less than the number of other genomic regions, leading to heavily imbalanced classes.
+Furthermore, most methods utilize direct overlap as a means to quantify the association, while distance, the measure of spatial relationships, remains unaccounted for.
+Consequently, distances on a genomic scale vary widely, leaving uncertainty how the heavily right-tailed distribution of distance measures will affect the model’s performance.
+
+###Methods 
+We propose a novel data pre-processing pipeline that addresses those shortcomings.
+It includes an elastic-net regularized classification model, where the mixing proportion, $\alpha$, and the penalization parameter, $\lambda$, are tuned for over a grid of values.
+A number of classifier performance metrics was assessed, including the F1 measure and Matthew Correlation Coefficient (MCC).
+
+###Results 
+Data preprocessing (log2-transformation and standardization) improves the performance of the models.
+The elastic-net model outperformed multiple logistic regression models, with and without LASSO-regularized coefficients.
+Likewise, the variable importance of the elastic-net yielded more stable and biologically meaningful results compared to the variables selected by the multiple logistic regression models.
+
+###Conclusions 
+Current methods used to model the epigenomic features associated with TAD boundaries are not robust to handle properties of genomic data.
+Models applied to unprocessed data can have poor predictive performances.
+Typical performance assessment metrics, such as AUROC, can mask poor performance of the models; thus, the use of more balanced metrics, such as F1 and MCC, is warranted.
+The elastic-net model, with its dual use of the $l_1$ and $l_2$ regularization terms allows for both the removal of uninformative predictors, while being able to handle multiple correlated epigenomic features.
+Our model results in better performances and more accurate identification of important features associated with the formation of TAD boundaries.
 

### 2018-09-05 ToDo.Rmd
initial commit

---
title: "To Do List"
author: "Spiro Stilianoudakis"
date: "September 4, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 09/04/18

* use width in base pairs as type of feature instead of counts of overlap
   - distance and width in base pairs of overlap as features
* finish methods

### 2018-09-10 Manuscript/manuscript.Rmd
updates

@@
 
-The advent of various genome-wide technologies, such as high-throughput conformation capture (Hi-C), have revealed how the spatial organization of the human genome may affect several epigenetic functions (Aiden et al.).
+The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect several epigenetic functions (Aiden et al.).
 Analyses have shown that the genome is tightly compacted into distinct compartments.
-There exist regions within these compartments that are highly conserved and self-interacting, and termed topologically associating domains (TADs) (Dixon et al.).
+There exist regions within these compartments that that have been shown to be highly conserved and self-interacting, and termed topologically associating domains (TADs) (Dixon et al.).
 Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD (Symmons et al.).
@@
 
-More recently, it has been discovered that insulators have a primary role in orchestrating the topological arrangement of higher-order chromatin architecture (Phillips-Cremins et al).
+More recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangement of higher-order chromatin architecture (Phillips-Cremins et al).
 Insulators are multi-faceted regulatory sequences that moderate a variety of genomic processes including activation, repression, and enhancer blocking.
 Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long range chromatin contacts (Zuin et al.).
-Likewise, it was found that DNase I-hypersensitive sites were enriched at the boundaries of domains and correlated with the CTCF signals (Hong et al) [???
-They identify more].
-On the other hand, it is unclear how other types of regulatory elements such as histone modifications, which are associated with transcriptional initiation and open chromatin structure, are related to TAD boundaries.
+Furthermore, other regulatory elements like DNase I hypersensitive sites, the H3K36 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions (Hong et al).
+Each of these associated with more open chromatin which alter the accessibility of genes for transcription.
+[???
+They identify more; !!!
+included mention of histone mods.
+and TFs].
+The distinct patterns of some of these different proteins and functional elements point toward the opportunity of computational approaches in predicting the development of TAD boundaries.
 
-The distinct patterns of some of these different proteins and functional elements point toward the opportunity of computational approaches in predicting the development of TAD boundaries.
-However, due to the size of Hi-C data and the abundance of available genomic features, few methods have been developed to study the role of specific sets of these features on the folding of chromosomes.
-Furthermore, many widely used methods ignore key characteristics of the data that may hinder the performance of certain parametric models [???
+Due to the size of Hi-C data and the abundance of available genomic features, few methods have been developed to study the role and interplay of different sets of these features on the folding of DNA.
+Furthermore, many accepted methods ignore key characteristics of the data that, when addressed, may improve predictive performances.
+One such pitfall is the issue of highly imbalanced classes.
+The commonality between most accepted methods for predicting TAD boundaries considers binning the genome and labeling the bins as either containing a TAD boundary or not.
+However, due to the sparcity of TADs throughout the genome, most bins will not contain a TAD boundary.
+This will contribute to highly imbalanced classes and will also introduce predictors with near-zero variance.
+It has been shown that imbalanced classes can result in poor predictive performances of classification algorithms and unless the class imbalance is mild, researchers should always use an appropriate method for dealing with this (Blagus et al).
+Another problem lies in identifying which positional characteristics of the genomic features will optimize prediction.
+It is unclear if distances or overlaps between genomic bins and regions of functional elements contain the most information.
+Lastly, given that some features tend to colocalize near TAD boundaries, most predictive models may be unable to identify the complete set of features most associated with boundary formation, and it is important that the proposed model is able to handle multiple correlated features.
+[???
 Like what?
 It may be best to devote a paragraph clearly describing them.
-Then, describe the Mourad and other approaches].
-One such group have proposed a multiple logistic (MLR) model used to identify the most influential proteins with regards to TAD boundaries (Mourad et al.).
-They also provide an MLR model with LASSO estimated coefficients that they believe is better suited for predictors that may be correlated.
-However, key aspects of the data were ignored with each of these models, such as the sparsity of domain borders throughout the genome.
-Likewise, data pre-processing techniques such as normalization, the elimination of low variance predictors, and variable selection techniques were not considered.
-Furthermore, due to the large number of genomic features that can be considered, accounting for the relationship among features with interaction effects becomes computationally infeasible.
+Then, describe the Mourad and other approaches; !!!
+stated the issues, now will discuss current methods].
 
-Data pre-processing techniques such as normalization and the elimination of low variance predictors are an integral part of model fitting with regards to genomic data [???
+In a previous study (Mourad et al) both a multiple logistic regression model and a LASSO regularized regression model were applied to a wide array of architectural proteins from the GM12878 cell line to predict TAD boundaries.
+The set of features consisted of whether or not the coordinates of a functional element overlaped with a particular genomic bin (yes or no).
+In the case of a partial overlap, a percentage of overlap was used.
+However, the class imbalance issue was not addressed.
+Additionally, neither model is suited to handle multiple correlated predictors.
+Furthermore, ROC curves and AUCs were used to evaluate model performance.
+This is problematic, especially for highly imbalaned classes because it dismisses how well the model is able to identify true positive cases.
+In another study (Huang et al), a more robust model in the form of a Bayesian Additive Regression Trees (BART) model was used.
+The set of features consisted of a score that averaged the number of sequence reads for each functional element over a particular bin for the GM12878 cell line.
+Here, the balanced classes were manually created by dividing the positive and negative classes into two equal subsets used for model training and testing.
+However, it is unclear what balancing technique was used.
+In addition to this, the model was only performed on a small set of histone marks while ignoring wider classes of epigenomic elements.
+Lastly, in a more recent study (Hong et al), a bayesian rigde regression model was iteratively used on a set of transcription factor binding sites, transcription start sites, and DNase I hypersensitive sites from the hESC cell line until the best combination of features led to the optimal prediction of TAD boundaries.
+Here, the features of the model consisted of the number of occurences of each genomic element within each genomic bin.
+Balanced classes were manually created by randomly sampling from the set of bins that did not contain a TAD boundary.
+Given the structure of the search algorithm proposed, though, it can be computationally inefficient to have to iterate through a large set of genomic features to find the particular set that contributes to the best prediction.
+Because of that, only a maximum set of 10 genomic features were considered at any given time.
+
+The types of models and the feature characteristics used in the aforementioned methods vary considerably.
+Additionally, a notable omission was the use of distances between regions of the functional elements and genomic bins.
+Because of the different cell lines available for analysis and the widening list of functional genomic elements, it can be quite useful to have a unified approach in predicting the formation of TAD boundaries.
+Therefore, in addition to proposing a novel data pre-processing pipeline that addresses irregularities in the data, we also apply an elastic-net model (and/or random forest?) using both distances and counts of overlaps between bins and features as predictors in our model.
+We aim to assess both the predictive performance of the model and the influence of genomic features on the borders that demarcate topological domains.[???
 Clarity.
 Define 1) the problem, and 2) ways to solve it, which is modeling.
-Then, for modeling, describe problems connecting genomics+machine learning terms].
-Continuous predictors tend to be highly shewed.
-Therefore, a common practice is to perform a log base 2 transformation.
-It is also sometimes necessary to standardize continuous predictors, especially if they are on different scales.
-It is unclear, however, which combination of these two concepts improves prediction.
-Additionally, binary predictors may only be concordant with the outcome of interest in very rare cases.
-This contributes to predictors with near-zero variances.
-Eliminating these predictors prior to model fitting can reduce both the noise and the computational speed of the model.
-We use the nearZeroVar function provided in the caret package to determine which predictors have near-zero variance [???
-This sentence is Methods].
-
-TADs can be up to a million base pairs in length and therefore the boundaries are sparse throughout the genome.
-Sparse data can create heavily imbalanced classes and may affect prediction performance of classification algorithms.
-There are many techniques that can be used to more evenly balance such data.
-These include oversampling the minority class, under sampling the majority class, and some combination of both.
-One such technique is referred to as SMOTE, which stands for Synthetic Minority Over-sampling TEchnique.
-SMOTE is a function in the DmWR package in R and incorporates both under-sampling and over-sampling.
-It has been shown that SMOTE out performs simple under-sampling of the majority class for some machine learning algorithms (Nitesh et al).
-We instead propose a method of taking multiple bootstrap under-samples from the majority class and then aggregating performance metrics by taking the average across all iterations.
-We then compare this method to SMOTE.
-
-Modeling genomic data often involves a large number of predictors as well.
-As a result, different machine learning models can benefit from variable selection techniques to reduce the feature space, and thereby improve computational speed.
-There are several known selection techniques in the field of machine learning including forward, backward, and stepwise selection.
-These are known as wrapper methods because they measure the usefulness of a subset of features by actually training a model on it.
-Additionally, we incorporate recursive feature elimination as a method of variable reduction and compare it to the rest.
-
-Furthermore, the model proposed by Mourad et al.
-falls short of addressing issues such as cross-validation and variable importance, which can be handled more efficiently through ensemble models like random forests and gradient boosting machines.
-Therefore, in addition to proposing a novel pipeline that addresses irregularities in the data mentioned above, we also apply a random forest model in order to find the key molecular drivers most associated with TAD boundaries.
-A random forest was chosen because of its ability to handle potentially correlated variables as well as its inability to overfit.
-We then compare the performance of the random forest model to the models proposed by Mourad et al.
+Then, for modeling, describe problems connecting genomics+machine learning terms; !!!identified problem and aim]
 

### 2018-09-10 Manuscript/manuscript.Rmd
updates

@@
 Lastly, given that some features tend to colocalize near TAD boundaries, most predictive models may be unable to identify the complete set of features most associated with boundary formation, and it is important that the proposed model is able to handle multiple correlated features.
-[???
-Like what?
-It may be best to devote a paragraph clearly describing them.
-Then, describe the Mourad and other approaches; !!!
-stated the issues, now will discuss current methods].
 
@@
 Define 1) the problem, and 2) ways to solve it, which is modeling.
-Then, for modeling, describe problems connecting genomics+machine learning terms; !!!identified problem and aim]
+Then, for modeling, describe problems connecting genomics+machine learning terms]
 
@@
 The start and end coordinates were concatenated, sorted, and unique coordinates representing unique TAD boundaries were obtained [???
-Check for accuracy].
-Next, the genome was binned into a series of 1kb intervals (flanked by 500 bases on either side of the boundary point) and an indicator vector Y was created based on whether there was a TAD boundary located in the 1kb interval (Y=1) or not (Y=0) [???
-Should it be simplified - just consider boundaries to be flanked?].
+Check for accuracy; !!!
+what do you mean by accuracy here?].
+The establishment of the data for modeling first consisted of binning the genome into equal sized intervals.
+This was performed at the same resolution as the respective cell line.
+That is, for GM12878, 5 kb genomic bins were used, while 10 kb intervals were used for K562.
+Next, for the domain data provided by each cell line, the boundary coordinates were flanked on either side by 5 kb [!!!
+use the same size flank for k562?
+(resolution was 10kb)].
+A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
+Otherwise, the bin was labeled as not containing an boundary (Y=0).[???
+Should it be simplified - just consider boundaries to be flanked?; !!!].
 
@@
 Check Hong 2017 supplemental, there may be something else that I don't have in GenomeRunner database.
-Also, check iGD data http://big.databio.org/igd/].
-These annotations consisted of genomic coordinates and were used to build the feature space, X = {X1, .
+Also, check iGD data http://big.databio.org/igd/; !!!
+table in supplementary file, Hong considers TFBS, should we also include?].
+These annotations consisted of genomic coordinates and were used to build the feature space, X = {$X_{1}$, .
 .
-., Xp}, of the subsequent models.
-The data consisted of genomic coordinates and chromosomal information.
-For each genomic feature, an indicator variable (1 for yes; 0 for no) was created based on whether the coordinates of the annotation overlapped with the coordinates representing a flanked TAD boundary.
-Likewise, a continuous variable representing the distance to the center of the nearest flanked TAD boundary was included [???
-Measured in?].
-Genomic features that were located inside of a flanked TAD boundary were given a distance of 0.
-Figure X presents an illustration for how the feature space was constructed.
+., $X_{p}$}, of the subsequent models.
+The full list of features is provided in [X].
+For each genomic feature, two predictors types were considered, a count variable and a distance variable.
+The count variable was based on the number of regions of each functional element that overlapped with a particular genomic bin.
+The distance variable consisted of the length (in base pairs) from the center of each genomic bin to the center of the nearest region of a functional element.
+If the center of the region given by a particular functional element was located within a genomic bin, then the distance was given to be 0.[???
+Measured in?; !!!].
+Figure X presents an illustration for how both the response vector and feature space were constructed.
 
@@
 We developed a pipeline that systematically evaluates the problems associated with genomic data in predictive modeling settings.
+
 At each stage in the pipeline, Elastic-Net models were performed and performance metrics such as ROC curves and subsequent AUCs were evaluated.
@@
 Next, the number of unique values divided by the total number of samples multiplied by 100 was calculated.
-Here, if the frequency ratio was greater than 0.99 and the percentage of unique values was less than 0.001, the predictor was flagged as having near-zero variance and removed.
+Here, if the frequency ratio was greater than 20 and the percentage of unique values was less than 10, the predictor was flagged as having near-zero variance and removed.
 

### 2018-09-10 ToDo.Rmd
updates

@@
 
-## 09/04/18
+## 09/07/18
 
-* use width in base pairs as type of feature instead of counts of overlap
+####To-Do
++ use width in base pairs as type of feature instead of counts of overlap
    - distance and width in base pairs of overlap as features
-* finish methods
++ finish introduction, start on methods
+
+## 09/10/18
+
+####Questions
+
+* Should we use elastic-net and RF as final models or just one or the other?
+* In results section should we compare between mourad models visually or verbally or none at all?
+* I've mentioned other methods in intro, it will be hard to compare to the others; how to handle this?
+* Hong et al uses TFBS should I also include them?
+
+####To-Do
+
+*Finish Methods
+*Finish running code applied to 100 iterations of undersampling
+*Apply pipeline to K562 cell line

### 2018-09-11 ToDo.Rmd
new todo

@@
 * In results section should we compare between mourad models visually or verbally or none at all?
+   + visually and verbally
+   + AUROCs, F1 and MCC
 * I've mentioned other methods in intro, it will be hard to compare to the others; how to handle this?
 * Hong et al uses TFBS should I also include them?
+   + use tfbs encode clustered (in separate model)
+* How to handle k562
+   +1 unit bin, 1unit flank (10 kb; 20kb)
 
@@
 
+*Make a bullet pointed list for manuscript
+*Apply RF, GBM, SVM (later), MLR using our features
 *Finish Methods

### 2018-09-12 Manuscript/manuscript.Rmd
updates

@@
 Analyses have shown that the genome is tightly compacted into distinct compartments.
-There exist regions within these compartments that that have been shown to be highly conserved and self-interacting, and termed topologically associating domains (TADs) (Dixon et al.).
+There exist regions within these compartments that have been shown to be highly conserved and self-interacting, and termed topologically associating domains (TADs) (Dixon et al.).
 Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD (Symmons et al.).
 This suggests that the boundaries of TADs may play a role in restricting the function of elements such as enhancers, thereby impacting the transcription of genes.
+Furthermore, changing the 3D structure of the DNA and distrupting these domains can lead to adverse outcomes and diseases like cancer.
+Therefore it is important to be able to identify the key molecular drivers of the formation of TADs in order to further our understanding of the human genome.
 
-More recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangement of higher-order chromatin architecture (Phillips-Cremins et al).
+The mechanisms underlying the formation of TADs are a complex and active area of research.
+Recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangement of higher-order chromatin architecture (Phillips-Cremins et al).
 Insulators are multi-faceted regulatory sequences that moderate a variety of genomic processes including activation, repression, and enhancer blocking.
 Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long range chromatin contacts (Zuin et al.).
-Furthermore, other regulatory elements like DNase I hypersensitive sites, the H3K36 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions (Hong et al).
-Each of these associated with more open chromatin which alter the accessibility of genes for transcription.
-[???
-They identify more; !!!
-included mention of histone mods.
-and TFs].
-The distinct patterns of some of these different proteins and functional elements point toward the opportunity of computational approaches in predicting the development of TAD boundaries.
+Other regulatory elements like DNase I hypersensitive sites, the H3K36 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions (Hong et al).
+These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
+The distinct patterns of some of these different proteins and functional elements point toward the opportunity of computational approaches in predicting the development of TAD boundaries, which, in genereal, will allow us to better understand what leads to their formation.
 
@@
 It has been shown that imbalanced classes can result in poor predictive performances of classification algorithms and unless the class imbalance is mild, researchers should always use an appropriate method for dealing with this (Blagus et al).
+Furthermore, the inclusion of predictors with near-zero variance can add unnecessary noise to the model and decrease computational efficiency of predictive algorithms.
 Another problem lies in identifying which positional characteristics of the genomic features will optimize prediction.
-It is unclear if distances or overlaps between genomic bins and regions of functional elements contain the most information.
-Lastly, given that some features tend to colocalize near TAD boundaries, most predictive models may be unable to identify the complete set of features most associated with boundary formation, and it is important that the proposed model is able to handle multiple correlated features.
+It is unclear if distances or overlaps between genomic bins and regions of functional elements contain the most information and will lead to better predictive performances.
+Lastly, given that some features tend to colocalize near TAD boundaries, most predictive models may be unable to identify the complete set of features most associated with boundary formation.
+This can lead to less informative results and restrict our knowledge of how these genomic elements correlate with eachother.
 
@@
 In the case of a partial overlap, a percentage of overlap was used.
-However, the class imbalance issue was not addressed.
-Additionally, neither model is suited to handle multiple correlated predictors.
-Furthermore, ROC curves and AUCs were used to evaluate model performance.
-This is problematic, especially for highly imbalaned classes because it dismisses how well the model is able to identify true positive cases.
+However, the class imbalance issue was not addressed and neither model used is suited to handle multiple correlated predictors.
+Additionally, ROC curves and AUCs were used to evaluate model performance, which is problematic, especially for highly imbalaned classes (Hanczar et al).
+A better indicator of predictive performance with classification algorithms is to consider the F1 score and Matthew's Correlation Coefficient (MCC).
 In another study (Huang et al), a more robust model in the form of a Bayesian Additive Regression Trees (BART) model was used.
 The set of features consisted of a score that averaged the number of sequence reads for each functional element over a particular bin for the GM12878 cell line.
-Here, the balanced classes were manually created by dividing the positive and negative classes into two equal subsets used for model training and testing.
+Here, the class proportion was manually created by dividing the positive and negative classes into two equal subsets used for model training and testing.
 However, it is unclear what balancing technique was used.
@@
 The types of models and the feature characteristics used in the aforementioned methods vary considerably.
-Additionally, a notable omission was the use of distances between regions of the functional elements and genomic bins.
 Because of the different cell lines available for analysis and the widening list of functional genomic elements, it can be quite useful to have a unified approach in predicting the formation of TAD boundaries.
-Therefore, in addition to proposing a novel data pre-processing pipeline that addresses irregularities in the data, we also apply an elastic-net model (and/or random forest?) using both distances and counts of overlaps between bins and features as predictors in our model.
-We aim to assess both the predictive performance of the model and the influence of genomic features on the borders that demarcate topological domains.[???
-Clarity.
-Define 1) the problem, and 2) ways to solve it, which is modeling.
-Then, for modeling, describe problems connecting genomics+machine learning terms]
+Therefore, in this study we have developed a novel data pre-processing pipeline that addresses the irregularities in the TAD boundary data provided by contact matrices at different resolutions.
+We then performed a variety of machine learning algorithms on the pre-processes data to identify the genomic elements that were most predictive of TAD boundaries.
+In our models we incorporated the distances from bin to region as features.
+We found that the models performed on our pre-processed data performed better than previously established methods.
+Additionally, we were able to confirm that the cis-regulatory elements like insulators and promotors were highly predictive of TAD boundaries.
+The specific transcriptional repressor, CCCTC-binding factor (CTCF) was found to be highly predictive of TAD boundaries.
+Other non-transcription factor sites like DNase I hypersensitive sites and certain histone modifications like H3K36me3 were also found to be better predictors.
+Our findings confirm that models with pre-processed data and distance-related genomic features not only perform better, but are also able to correctly identify a range of different functional genomic elements associated with the formation of TAD boundaries.
+This knowlege will allow us to gain better insight into the role that the spatial organisation of the human genome has on gene regulation.
 

### 2018-09-12 Manuscript/manuscript.Rmd
updates

@@
 Because of the different cell lines available for analysis and the widening list of functional genomic elements, it can be quite useful to have a unified approach in predicting the formation of TAD boundaries.
-Therefore, in this study we have developed a novel data pre-processing pipeline that addresses the irregularities in the TAD boundary data provided by contact matrices at different resolutions.
+Therefore, in this study we have developed a novel data pre-processing pipeline that addresses the irregularities in the TAD boundary data provided by contact matrices at different resolutions for two cell lines, GM12878 and K562.
 We then performed a variety of machine learning algorithms on the pre-processes data to identify the genomic elements that were most predictive of TAD boundaries.
@@
 what do you mean by accuracy here?].
+A depiction of the data is presented in Figure X.
+
 The establishment of the data for modeling first consisted of binning the genome into equal sized intervals.
 This was performed at the same resolution as the respective cell line.
-That is, for GM12878, 5 kb genomic bins were used, while 10 kb intervals were used for K562.
-Next, for the domain data provided by each cell line, the boundary coordinates were flanked on either side by 5 kb [!!!
-use the same size flank for k562?
-(resolution was 10kb)].
-A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
-Otherwise, the bin was labeled as not containing an boundary (Y=0).[???
-Should it be simplified - just consider boundaries to be flanked?; !!!].
+That is, for GM12878, 5 kb genomic bins were used, while 10 kb bins were used for K562.
+Next, for the domain data provided by GM12878, the boundary coordinates were flanked on either side by 5 kb.
+For the K562, the boundary coordinates were flanked by 10 kb.
+In either case, a genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
+Otherwise, the bin was labeled as not containing an boundary (Y=0) (Figure X).
 
@@
 
-Annotation data was obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium [???
-We need a table.
-Check Hong 2017 supplemental, there may be something else that I don't have in GenomeRunner database.
-Also, check iGD data http://big.databio.org/igd/; !!!
-table in supplementary file, Hong considers TFBS, should we also include?].
+Annotation data was obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium.
 These annotations consisted of genomic coordinates and were used to build the feature space, X = {$X_{1}$, .
@@
 ., $X_{p}$}, of the subsequent models.
-The full list of features is provided in [X].
-For each genomic feature, two predictors types were considered, a count variable and a distance variable.
-The count variable was based on the number of regions of each functional element that overlapped with a particular genomic bin.
-The distance variable consisted of the length (in base pairs) from the center of each genomic bin to the center of the nearest region of a functional element.
-If the center of the region given by a particular functional element was located within a genomic bin, then the distance was given to be 0.[???
-Measured in?; !!!].
-Figure X presents an illustration for how both the response vector and feature space were constructed.
+A full list of the genomic elements is provided in Table X.
+For each genomic element, the distance from the center of a genomic bin to the center of the nearest region (in base pairs) was calculated and included in the model.
+If the center of the region given by a particular functional element was located within a genomic bin, then the distance was given to be 0.
+Additionally, a variable denoting the number of overlaps between a genomic bin and region representing a genomic element was totaled and included in the model (Figure X).
 
@@
 
-We developed a pipeline that systematically evaluates the problems associated with genomic data in predictive modeling settings.
-
-At each stage in the pipeline, Elastic-Net models were performed and performance metrics such as ROC curves and subsequent AUCs were evaluated.
-The Elastic-Net model was used here because of its ability to be tuned and its computational speed relative to other machine learning algorithms.
-For each elastic-net model the mixing parameter, alpha, was tuned on a grid of five values (0.1, 0.325, 0.550, 0.775, and 1.0).
-A sequence of values for the regularization parameter, lambda, was automatically provided by the CARET package in R.
-The algorithm then chose the optimal combination of alpha and lambda, and the model was evaluated.
-[???
-Unclear, is it cross-validation tuning or what?]
-
+We developed a pipeline that systematically evaluates the problems associated with TAD boundary data in a predictive modeling setting (Figure X).
+The pipeline was used to address issues related to normalization of predictors, class imbalance, and variable reduction.
 Prior to initiating the pipeline, predictors with near-zero variance were removed.
@@
 
+At each subsequent stage in the pipeline, Elastic-Net models were performed and performance metrics such as F1 scores and MCCs were evaluated.
+The Elastic-Net model was used here because of its ability to be tuned and its computational speed relative to other machine learning algorithms.
+To avoid overfitting and more accurately assess performance, 10-fold cross validation was used for all models.
+For each elastic-net model the mixing parameter, alpha, was tuned over a grid of 10 evenly spaced values from 0 and 1.
+The penalty term, labmda, was tuned over a grid of 100 evenly spaced values from 0.01 to 100.
+
+### NORMALIZATION
+
+Distances on a genomic scale are frequently highly skewed.
+In order to correct for this, a log base 2 transformation was considered.
+Additionally, the predictors were standardized to have unit variance in order to be able to directly compare magnitudes of parameter coefficients.
+
 ### CLASS IMBALANCE
 
-To assess the class imbalance problem due to the sparcity of domains throughout the genome, two methods were used.
+When binning the genome, the sparcity of TAD boundaries through the genome contributed to heavily imbalanced classes.
+That is, proportionally, only a small number of genomic bins overlapped with a flanked TAD boundary.
+To assess this issue, two methods were used.
 The first consisted of incorporating the SMOTE command from the DmWR package in R.
@@
 Then, the majority class is under sampled by taking a random sample that matches some pre-specified percentage of the updated minority class.
-For example, consider a data set with 700 observations, where there are 35 minority classes and 665 majority classes.
-Now, when using SMOTE, consider a 200 percent over sample of the minority class and a 100 percent under sample of the majority class.
-This means that two synthetic observations will be created for every minority class (35+70=105) and 1 majority class will be randomly chosen for every new minority class created (70), resulting in a classification of 70/105 (majority/minority).
-Now consider, a 200/200 combination.
-The new minority class is still 105 (70 new synthetic observations created), but now twice as many majority classes are randomly chosen (70*2=140), resulting in a 140/105 classification.
-It is important to note that using a combination of 100/200 will always result in perfectly balanced classes.
-A total of eight different combinations of percent over and undersampling were used which included: 100/200, 200/200, 300/200, 400/200, 100/300, 200/300, 300/300, 400/300.
-Here, the 100/200 combination creates a completely balanced dataset as mentioned before, while the others create an unbalanced dataset with the “No” class as the majority to reflect the original data.
-The second method involved iteratively taking 100 bootstrap samples of the majority class to match the number in the minority class.
+It is important to note that using a combination of 100/200 (percent over/percent under-sample) will always result in perfectly balanced classes.
+A total of four different combinations of percent over and under-sampling were used which included: 100/200, 200/200, 300/200, and 400/200.
+As mentioned before, the 100/200 combination created balanced classes, while the others create an unbalanced dataset with the negative class as the majority to reflect the proportionality of the classes in the original data.
+The second method involved iteratively under-sampling 100 time from the majority class to match the number in the minority class.
 For each sample, an elastic-net model was tuned and evaluated.
-Then row wise means of the sensitivities, specificities, and AUCs of each of the 100 bootstrap samples were taken to evaluate the models as a whole.
-The SMOTE combination with the best performance was then compared to the bootstrap method.
-ROC curves were plotted and corresponding AUCs were presented in a table.
-
-### NORMALIZATION
-
-In order to correct for the skewness of the distances [???
-Should be defined in the introduction], elastic-net models were evaluated based on a combination of log transformed and/or standardized predictors.
-A total of four elastic net models were performed including: with log transformation and standardization, without log transformation and with standardization, with log transformation and without standardization, and without log transformation and without standardization.
-One hundred bootstrap samples were taken from the majority class to create a balanced classification data.
-ROC curves were plotted and corresponding AUCs were presented in a table.
-Likewise, we looked at the variable importance quality of the models.
+Then row-wise means of the performance metrics for each of the 100 interations were taken to evaluate the models (Figure X).
 
@@
 That is, only a reduction in the model's AIC contributed to the inclusion of a feature in the model.
-Additionally, a recursive feature elimination (RFE) algorithm was performed.
-In RFE, a full model was created, a measure of variable importance was then computed that ranked the predictors from the most important to the least.
-Here, the importance of the model was based on the random forest importance criterion [???
-Unclear how is it different from backward selection, compare and contrast].
-Then, at each stage of the search, the least important predictors were iteratively eliminated prior to rebuilding the model.
-The process was continued for a pre-specified subset of predictors.
+For each technique, prior to model selection, balanced classes were iteratively created 100 times by random under-sampling from teh majority class.
+At each iteration the variables selected from each technique were recorded.
+The final set of predictors selected for each technique were those that appeared over 90% of the time accross all iterations.
+The union of the three sets of features from each of the techniques was obtained and used as the final feature space of the data (Figure X)
 

### 2018-09-12 Manuscript/results_outline.Rmd
results outline

---
title: "Manuscript Outline"
author: "Spiro Stilianoudakis"
date: "September 11, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

   + Paragraph 1:
      - What are TADs and what role do they play in the human genome?
      - Why do we care about TADs?

   + Paragraph 2:
      - What is in the current literature?

   + Paragraph 3:
      - What are the issues?
      - Why are they issues?

   + Paragraph 4:
      - What are the current methods out there?
      - What drawbacks do they have?

   + Paragraph 5:
      - Defined the problem
      - What have we done?
      - Why have we done it?

# Methods

* The Data
   + Paragraph 1:
      - Where was the data obtained?
   + Paragraph 2:
      - How it was used?
      - How was the response vector created

* Genomic Annotations
   + Paragraph 1: 
      - Where was the annotation data obtained?
      - How were they used?

* Data Pipeline:
   + What was the pipeline used for?
   + Set up structure of pipeline
   + How were techniques evaluated?

* Normalization:
   + What techniques were used/compared?
   + How were they used/how do they worked?

* Class Imbalance:
   + What techniques were used/compared?
   + How were they used/how do they worked?

* Variable Selection:
   + What techniques were used/compared?
   + How were they used/how do they worked?

* Final Model:
   + What model(s) we used to evaluat the pipeline processed data
   + How the model(s) were performed
   + What we compared our models to

# Results

### 2018-09-12 Manuscript/manuscript.Rmd
updates

@@
 
-Due to the large number of genomic features included in the model, different variable selection techniques were evaluated in order to prevent overfitting, improve computational speed, and eliminate uninformative variables.
+Due to the large number of genomic features included in the model, different variable selection techniques were evaluated in order to improve computational speed and eliminate uninformative variables.
 There were three different wrapper methods that were used here, forward, backward, and stepwise selection.
@@
 
-Once the pipeline produced the appropriate dataset, a random forest algorithm was used to assess which genomic features that were most predictive of the development of TAD boundaries.
-The algorithm was run iteratively over 100 bootstrap samples, each time producing sensitivities, specificities, AUCs, and variable importances.
-For each iteration, the model was tuned on the best number of predictors to subset as well as the optimal number of trees to use.
-At the end of the 100 iterations, row wise means were performed to aggregate the model performances.
-We then compared the random forest model to both the MLR model and the MLR model with LASSO estimated coefficients that was proposed by Mourad et al.
+Once the pipeline produced the appropriate dataset, an elastic was used to assess which genomic features that were most predictive of the development of TAD boundaries.
+The algorithm was run iteratively over 100 random under-sampled majority classes to balance the data, each time producing performance metrics and variable importances.
+At the end of the 100 iterations, row-wise means were performed to aggregate the model information.
+We then compared the elastic-net model performed on the processed data to both a multiple logistic regression model and a LASSO regularized model with and without the use of distance predictors and with or without processed data.
+
+#####################
 

### 2018-09-13 ToDo.Rmd
updates

@@
 
-*Make a bullet pointed list for manuscript
-*Apply RF, GBM, SVM (later), MLR using our features
-*Finish Methods
-*Finish running code applied to 100 iterations of undersampling
-*Apply pipeline to K562 cell line
++ Make a bullet pointed list for manuscript
+* Apply RF, GBM, SVM (later), MLR using our features
++ Finish Methods
++ Finish running code applied to 100 iterations of undersampling
+* Apply pipeline to K562 cell line
+
+## 09/10/18
+
+####Questions
+
+* Should figures be placed in back of paper (in Appendix section)?
+* Line 60 of manuscript: Check for accuracy?
+
+####To-Do
+
+* in table with total features put (*) for removed then state why
+* Finish results outline
+* Finish results manuscript

### 2018-09-19 GM12878/Full_Data_Modeling_Pipeline/full_data_model_pipeline.R
deleted files

@@ -1,4015 +1,0 @@
-setwd("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb_bins/")
-
-#Loading Libraries
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-# Creating Response Vector Y
-
-## Reading in TAD data
-
-domains <- read.table("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb_bins/arrowhead_data.txt", header=T)
-domains <- domains[,1:3]
-head(domains)
-dim(domains) #9274    3
-
-#removing chrX from boundary data
-domains <- domains[-which(domains$Chromosome=="chrX"),]
-
-#creating granges object out of tad boundary data
-
-#concatenating boundary coordinates into one long vector
-coords <- domains
-colnames(coords)[2:3] <- c("coordinate", "coordinate")
-coords <- rbind.data.frame(coords[,c(1,2)],coords[,c(1,3)])
-coords$Chromosome <- as.character(coords$Chromosome)
-
-#sorting by chromosome and coordinate
-coords <- coords[order(as.numeric(substr(coords$Chromosome,4,5)), coords$coordinate, decreasing = FALSE),]
-
-#remove duplicates for coordinates that are conjoined
-coords <- coords[!duplicated(coords),]
-dim(coords) #16770     2
-
-bounds <- GRanges(seqnames=coords$Chromosome, ranges=IRanges(start=coords$coordinate, width=1))
-
-#saving data
-saveRDS(bounds, "/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb_bins/bounds.rds")
-
-
-## Reading in binned genome in the form of contact matrix at 10kb resolution
-
-binslist10 <- read.table("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb_bins/binslist10.txt")
-
-dim(binslist10) #268498      2
-
-#ordering the bins according to left endpoint
-binslist10 <- binslist10[order(as.numeric(substr(binslist10$V1,4,5)), binslist10$V2, decreasing=FALSE),]
-
[…]

### 2018-09-19 GM12878/Modeling/Our_Models/enet_unbalanced.R

@@ -1,152 +1,0 @@
-# Loading Libraries
-
-
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-
-
-# Reading in data
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
-
-
-
-gm12878_10kb_reduced <- readRDS("gm12878_10kb_reduced.rds")
-
-
-
-# Final Models:
-
-## Elastic Net
-
-### set tuning parameters
-
-
-fitControl <- trainControl(method = "repeatedcv",
-                           number = 10,
-                           repeats = 5,
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
-						   
-#### function for roc curves
-
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-						
-
-###Performing model
-
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
-enetlst <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb_reduced$y=="Yes"))*2)*.3), 
-                              ncol=1),
-                fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb_reduced$y=="Yes"))*2)*.3), 
-                              ncol=1),
-                varimp <- matrix(nrow=dim(gm12878_10kb_reduced)[2]-1,
-                                 ncol=1),
-				coefs <- matrix(nrow=dim(gm12878_10kb_reduced)[2]-1,
-									ncol=1))
-rownames(enetlst[[3]]) <- colnames(gm12878_10kb_reduced)[-1]
[…]

### 2018-09-19 GM12878/Modeling/Our_Models/full_enet.R

@@ -1,130 +1,0 @@
-#Elastic Net on Full Data
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/full_data_model/")
-
-gm12878_10kb <- readRDS("gm12878_10kb.rds")
-
-gm12878_10kb$y <- factor(gm12878_10kb$y)
-
-levels(gm12878_10kb$y) <- c("No","Yes")
-
-#set tuning parameters
-fitControl <- trainControl(method = "repeatedcv",
-                           number = 10,
-                           repeats = 3,
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
-
-#function for roc curves
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-
-
-#splitting data
-inTrainingSet <- sample(length(gm12878_10kb$y),floor(length(gm12878_10kb$y)*.7))
-#inTrainingSet <- createDataPartition(data$y,p=.7,list=FALSE)
-train <- gm12878_10kb[inTrainingSet,]
-test <- gm12878_10kb[-inTrainingSet,]
-  
-  
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
-enetlst_full <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
-                                 ncol=1),
-                   fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
-                                 ncol=1),
-                   varimp <- matrix(nrow=dim(gm12878_10kb)[2]-1,
-                                    ncol=1))
-rownames(enetlst_full[[3]]) <- colnames(gm12878_10kb)[-1]
-
-
-enetperf_full <- matrix(nrow = 17, ncol=1)
[…]

### 2018-09-19 GM12878/Modeling/Our_Models/full_rf.R

@@ -1,162 +1,0 @@
-#RF on Full Data
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/full_data_model/")
-
-
-gm12878_10kb <- readRDS("gm12878_10kb.rds")
-
-gm12878_10kb$y <- factor(gm12878_10kb$y)
-
-levels(gm12878_10kb$y) <- c("No","Yes")
-
-#set tuning parameters
-fitControl <- trainControl(method = "repeatedcv",
-                           number = 10,
-                           repeats = 3,
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
-
-#function for roc curves
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-
-
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
-rflst_full <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
-                                 ncol=1),
-                   fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
-                                 ncol=1),
-                   varimp <- matrix(nrow=dim(gm12878_10kb)[2]-1,
-                                    ncol=1))
-rownames(rflst_full[[3]]) <- colnames(gm12878_10kb)[-1]
-
-
-rfperf_full <- matrix(nrow = 17, ncol=1)
-rownames(rfperf_full) <- c("TN",
-                          "FN",
-                          "FP",
-                          "TP",
-                          "Total",
-                          "Sensitivity",
-                          "Specificity",
[…]

### 2018-09-19 GM12878/Modeling/Our_Models/lasso.R

@@ -1,140 +1,0 @@
-# Loading Libraries
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-# Reading in data
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
-
-
-gm12878_10kb <- readRDS("gm12878_10kb.rds")
-
-#set tuning parameters
-fitControl <- trainControl(method = "repeatedcv",
-                           number = 10,
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
-						   
-
-#function for roc curves
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-
-
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
-lassolst <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
-                              ncol=1),
-                fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
-                              ncol=1),
-                varimp <- matrix(nrow=dim(gm12878_10kb)[2]-1,
-                                 ncol=1),
-				coefs <- matrix(nrow=dim(gm12878_10kb)[2]-1,
-									ncol=1))
-rownames(lassolst[[3]]) <- colnames(gm12878_10kb)[-1]
-rownames(lassolst[[4]]) <- colnames(gm12878_10kb)[-1]				 
-								 
-lassoperf <- matrix(nrow = 17, ncol=1)
-rownames(lassoperf) <- c("TN",
- 							"FN",
[…]

### 2018-09-19 GM12878/Modeling/Our_Models/rf_unbalanced.R

@@ -1,175 +1,0 @@
-# Loading Libraries
-
-
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-
-
-# Reading in data
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
-
-#chromosome 1 filtered/log transformed/no standardization/forward selection
-
-gm12878_10kb_reduced <- readRDS("gm12878_10kb_reduced.rds")
-
-
-
-# Final Models:
-
-## Random Forest
-
-### set tuning parameters
-
-
-fitControl <- trainControl(method = "repeatedcv",
-                           number = 10,
-                           repeats = 5,
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
-						   
-#### function for roc curves
-
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-						
-
-###Performing model
-
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
-rflst <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb_reduced$y=="Yes"))*2)*.3), 
-                              ncol=1),
-                fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb_reduced$y=="Yes"))*2)*.3), 
-                              ncol=1),
-                varimp <- matrix(nrow=dim(gm12878_10kb_reduced)[2]-1,
-                                 ncol=1))
-rownames(rflst[[3]]) <- colnames(gm12878_10kb_reduced)[-1]
-
-rfperf <- matrix(nrow = 17, ncol=1)
-rownames(rfperf) <- c("TN",
[…]

### 2018-09-19 Manuscript/results_outline.Rmd
updated

@@
 # Results
+
+* GM12878 Resuts
+   + How many total genomic bins
+   + How many total TADs
+      - Summary stats for lengths of TADs
+   + Total number of features 
+      - Summary stats for both counts and distance features
+      - Which features were removed for near zero variance
+   + Normalization Techniques
+   + Class balancing techniques
+   + Variable selection techniques
+   + Final Models
+      - Mourad Models (MLR & LASSO)
+      - Models using distance/counts features with out pipeline (MLR & LASSO)
+      - Elastic-Net using processed data
+      - Comparisons
+* Validate results using K562 cell line
+* Validate results using TFBS cell line
+
+# Discussion
+
+* State the results that were interesting 
+   - Specific to each cell line/tfbs
+   - Then results all together
+* State how much better models using our pipeline performed compared to Mourad
+   - Was it due to the model choice or the use of distance features?
+* Limitations/Future
+   - Mention the need for HiC experiments using higher resolutions
+   - Experimenting with TAD data using other methods
+   - Exploring other cell lines

### 2018-09-19 ToDo.Rmd
updated

--- 2018-09-11 ToDo.Rmd
@@
 
-*Make a bullet pointed list for manuscript
-*Apply RF, GBM, SVM (later), MLR using our features
-*Finish Methods
-*Finish running code applied to 100 iterations of undersampling
-*Apply pipeline to K562 cell line
++ Make a bullet pointed list for manuscript
++ Apply RF, GBM, SVM (later), MLR using our features
++ Finish Methods
++ Finish running code applied to 100 iterations of undersampling
++ Apply pipeline to K562 cell line
+
+## 09/10/18
+
+####Questions
+
+* Should figures be placed in back of paper (in Appendix section)?
+* Line 60 of manuscript: Check for accuracy?
+
+####To-Do
+
++ in table with total features put (*) for removed then state why
++ order figures and create legends
+* Finish results outline
+* Finish results manuscript
+
+## 09/17/18
+
+####Questions
+
+* clustered vs cell type specific tfbs
+   +/home/sequencing/data/ExtData/db_5.00_07-22-2015/grsnp_db/hg19/ENCODE/
+
+####To-Do
+
+* Finish TFBS models
+* Include column for feature table for why a feature was excluded
+* Use tables instead of barplots for performance metrics
+* class imbalance barplot unnecessary, put in words
+* clean up class imbalance plot put bar underneath to categorize each technique; put x axis diagonally
+* put tad in boundary before tad not in boundary for class imbalance table
+* include venn diagram of selected features
+* create a heat map for AIC values from commonly selected features
+* look at chromosome specific models and compare
+* look at different resolutions (talk with john)
+* look at other type of transformation (inverse sine transformation)

### 2018-09-19 GM12878/Data_Pipeline/02.1normalizationlog_std.R

@@ -27,13 +27,13 @@ simple_roc <- function(labels, scores){
 
 #set length of list objects that will be filled in with specificities
 #and sensitivities and aucs and variable importance
-enetlst_lns <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_5kb_f$y=="Yes"))*2)*.3), 
+enetlst_ls <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_5kb_f$y=="Yes"))*2)*.3), 
                                  ncol=1),
                    fpr <- matrix(nrow=ceiling((length(which(gm12878_5kb_f$y=="Yes"))*2)*.3), 
                                  ncol=1),
                    varimp <- matrix(nrow=dim(gm12878_5kb_f)[2]-1,
                                     ncol=1))
-rownames(enetlst_lns[[3]]) <- colnames(gm12878_5kb_f)[-1]
+rownames(enetlst_ls[[3]]) <- colnames(gm12878_5kb_f)[-1]
 
 enetperf_ls <- matrix(nrow = 17, ncol=1)
 rownames(enetperf_ls) <- c("TN",
@@ -87,9 +87,9 @@ srchGrid <- expand.grid(.alpha=alpha.grid, .lambda=lambda.grid)
   pred.eNetModel <- as.vector(predict(eNetModel, 
                                       newdata=test, 
                                       type="prob")[,"Yes"])
-  enetlst_lns[[1]]<- simple_roc(ifelse(test$y=="Yes",1,0),pred.eNetModel)[,1]
-  enetlst_lns[[2]] <- simple_roc(ifelse(test$y=="Yes",1,0),pred.eNetModel)[,2]
-  enetlst_lns[[3]] <- varImp(eNetModel)$importance[,1]
+  enetlst_ls[[1]]<- simple_roc(ifelse(test$y=="Yes",1,0),pred.eNetModel)[,1]
+  enetlst_ls[[2]] <- simple_roc(ifelse(test$y=="Yes",1,0),pred.eNetModel)[,2]
+  enetlst_ls[[3]] <- varImp(eNetModel)$importance[,1]
   
 #Prediction vector for other performance metrics
   pred.enetModel2 <- predict(eNetModel,
@@ -120,7 +120,7 @@ srchGrid <- expand.grid(.alpha=alpha.grid, .lambda=lambda.grid)
   
 
 
[…]

### 2018-09-19 GM12878/Modeling/Our_Models/enet.R

@@ -24,26 +24,27 @@ library(leaps)
 
 setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
 
-#chromosome 1 filtered/log transformed/no standardization/forward selection
 
-gm12878_10kb_reduced <- readRDS("gm12878_10kb_reduced.rds")
+gm12878_5kb_reduced <- readRDS("gm12878_5kb_reduced.rds")
 
 ### set number of bootstrap samples
 
 
 bootsamps = 5
 
-### set tuning parameters
-
-
-fitControl <- trainControl(method = "repeatedcv",
-                           number = 10,
+#set tuning parameters
+fitControl <- trainControl(method = "cv",
                            ## Estimate class probabilities
                            classProbs = TRUE,
                            ## Evaluate performance using 
                            ## the following function
                            summaryFunction = twoClassSummary)
 						   
+#set up grid of alpha and lambda values
+lambda.grid = 10^seq(2,-2,length=100)
+alpha.grid = seq(0,1,length=10)
+srchGrid <- expand.grid(.alpha=alpha.grid, .lambda=lambda.grid)
+					   
 #### function for roc curves
 
 simple_roc <- function(labels, scores){
@@ -57,15 +58,15 @@ simple_roc <- function(labels, scores){
 ##the number of columns match the number of bootstrap samples
 
 sampids <- matrix(ncol=bootsamps, 
-                  nrow=length(gm12878_10kb_reduced$y[which(gm12878_10kb_reduced$y=="Yes")]))
+                  nrow=length(gm12878_5kb_reduced$y[which(gm12878_5kb_reduced$y=="Yes")]))
 
 
 ###filling in the sample ids matrix
 
 set.seed(123)
 for(j in 1:bootsamps){
-  sampids[,j] <- sample(which(gm12878_10kb_reduced$y=="No"),
-                        length(which(gm12878_10kb_reduced$y=="Yes")),
+  sampids[,j] <- sample(which(gm12878_5kb_reduced$y=="No"),
+                        length(which(gm12878_5kb_reduced$y=="Yes")),
                         replace = TRUE)
 }
 
@@ -77,16 +78,16 @@ for(j in 1:bootsamps){
 
 #set length of list objects that will be filled in with specificities
 #and sensitivities and aucs and variable importance
[…]

### 2018-09-19 GM12878/Modeling/Our_Models/mlr.R

@@ -21,16 +21,16 @@ library(leaps)
 setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
 
 
-gm12878_10kb <- readRDS("gm12878_10kb.rds")
+gm12878_5kb <- readRDS("gm12878_5kb.rds")
 
 #set tuning parameters
-fitControl <- trainControl(method = "repeatedcv",
-                           number = 10,
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
+#fitControl <- trainControl(method = "cv",
+#                           number = 10,
+#                           ## Estimate class probabilities
+#                           classProbs = TRUE,
+#                           ## Evaluate performance using 
+#                           ## the following function
+#                           summaryFunction = twoClassSummary)
 						   
 #function for roc curves
 simple_roc <- function(labels, scores){
@@ -42,16 +42,16 @@ simple_roc <- function(labels, scores){
 						   
 #set length of list objects that will be filled in with specificities
 #and sensitivities and aucs and variable importance
-glmlst <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
+glmlst <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_5kb$y=="Yes"))*2)*.3), 
                               ncol=1),
-                fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb$y=="Yes"))*2)*.3), 
+                fpr <- matrix(nrow=ceiling((length(which(gm12878_5kb$y=="Yes"))*2)*.3), 
                               ncol=1),
-                varimp <- matrix(nrow=dim(gm12878_10kb)[2]-1,
+                varimp <- matrix(nrow=dim(gm12878_5kb)[2]-1,
                                  ncol=1),
-				coefs <- matrix(nrow=dim(gm12878_10kb)[2]-1,
+				coefs <- matrix(nrow=dim(gm12878_5kb)[2]-1,
 									ncol=1))
-rownames(glmlst[[3]]) <- colnames(gm12878_10kb)[-1]
-rownames(glmlst[[4]]) <- colnames(gm12878_10kb)[-1]				 
[…]

### 2018-09-19 GM12878/Modeling/Our_Models/rf.R

@@ -25,9 +25,9 @@ library(leaps)
 
 setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
 
-#chromosome 1 filtered/log transformed/no standardization/forward selection
 
-gm12878_10kb_reduced <- readRDS("gm12878_10kb_reduced.rds")
+
+gm12878_5kb_reduced <- readRDS("gm12878_5kb_reduced.rds")
 
 
 
@@ -43,9 +43,8 @@ bootsamps = 5
 ### set tuning parameters
 
 
-fitControl <- trainControl(method = "repeatedcv",
-                           number = 5,
-                           repeats = 3,
+fitControl <- trainControl(method = "cv",
+                           number = 10,
                            ## Estimate class probabilities
                            classProbs = TRUE,
                            ## Evaluate performance using 
@@ -65,15 +64,15 @@ simple_roc <- function(labels, scores){
 ##the number of columns match the number of bootstrap samples
 
 sampids <- matrix(ncol=bootsamps, 
-                  nrow=length(gm12878_10kb_reduced$y[which(gm12878_10kb_reduced$y=="Yes")]))
+                  nrow=length(gm12878_5kb_reduced$y[which(gm12878_5kb_reduced$y=="Yes")]))
 
 
 ###filling in the sample ids matrix
 
 set.seed(123)
 for(j in 1:bootsamps){
-  sampids[,j] <- sample(which(gm12878_10kb_reduced$y=="No"),
-                        length(which(gm12878_10kb_reduced$y=="Yes")),
+  sampids[,j] <- sample(which(gm12878_5kb_reduced$y=="No"),
+                        length(which(gm12878_5kb_reduced$y=="Yes")),
                         replace = TRUE)
 }
 
@@ -82,13 +81,13 @@ for(j in 1:bootsamps){
 
 #set length of list objects that will be filled in with specificities
 #and sensitivities and aucs and variable importance
-rflst <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_10kb_reduced$y=="Yes"))*2)*.3), 
+rflst <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_5kb_reduced$y=="Yes"))*2)*.3), 
                               ncol=bootsamps),
-                fpr <- matrix(nrow=ceiling((length(which(gm12878_10kb_reduced$y=="Yes"))*2)*.3), 
[…]

### 2018-09-19 ToDo.Rmd
updates

@@
 * Finish TFBS models
-* Include column for feature table for why a feature was excluded
-* Use tables instead of barplots for performance metrics
-* class imbalance barplot unnecessary, put in words
++ Include column for feature table for why a feature was excluded
++ Use tables instead of barplots for performance metrics
++ class imbalance barplot unnecessary, put in words
 * clean up class imbalance plot put bar underneath to categorize each technique; put x axis diagonally
@@
 * create a heat map for AIC values from commonly selected features
-* look at chromosome specific models and compare
++ look at chromosome specific models and compare
 * look at different resolutions (talk with john)
-* look at other type of transformation (inverse sine transformation)
++ look at other type of transformation (inverse sine transformation)

### 2018-09-21 ToDo.Rmd
updates

@@
 * put tad in boundary before tad not in boundary for class imbalance table
-* include venn diagram of selected features
++ include venn diagram of selected features
 * create a heat map for AIC values from commonly selected features
@@
 + look at other type of transformation (inverse sine transformation)
+
+## 09/19/18
+
++ split feature list into distance then counts
+* run mlr/lasso without distances to compare with mourad
+* find out how to obtain consensus tree from random forest
++ do we need distance?
++ look at models with just counts vs just distance; compare

### 2018-09-24 ToDo.Rmd
added todo
completed tasks

@@
 + split feature list into distance then counts
-* run mlr/lasso without distances to compare with mourad
++ run mlr/lasso without distances to compare with mourad
 * find out how to obtain consensus tree from random forest
@@
 + look at models with just counts vs just distance; compare
+
+## 09/19/18
+
++ compare between mourad model and our pipeline at each step (full data vs balanced; distance vs no distance features)
+   - lasso to lasso
+   - mlr to mlr

### 2018-09-28 ToDo.Rmd
completed tasks

@@
    - mlr to mlr
+
+## 09/24/18
+
++ consider inverse normal distribution as another normalization technique
+   - understand conceptually what is happening
+
+## 09/24/18
+
++ disregard count overlaps and use binary overlap with percent overlap if partial
++ reformat table1 into asking question how bad in unbalanced data
+ + question 1 should be how severe is unbalanced data?
+    - distance not needed here
+* consider standardizing data prior to modeling
+* is scaling important
+ +just percent
+ +just dist
+ +both unscaled
+ +both scaled

### 2018-09-28 ToDo.Rmd
completed tasks

@@
     - distance not needed here
-* consider standardizing data prior to modeling
-* is scaling important
++ consider standardizing data prior to modeling
++ is scaling important
  +just percent

### 2018-10-01 Manuscript/manuscript.Rmd
updates
manuscript updates

@@
 We propose a novel data pre-processing pipeline that addresses those shortcomings.
-It includes an elastic-net regularized classification model, where the mixing proportion, $\alpha$, and the penalization parameter, $\lambda$, are tuned for over a grid of values.
-A number of classifier performance metrics was assessed, including the F1 measure and Matthew Correlation Coefficient (MCC).
+A number of classifier performance metrics were assessed, including the F1 measure and Matthew Correlation Coefficient (MCC), and area under the ROC curve (AUROC).
 
 ###Results 
-Data preprocessing (log2-transformation and standardization) improves the performance of the models.
-The elastic-net model outperformed multiple logistic regression models, with and without LASSO-regularized coefficients.
-Likewise, the variable importance of the elastic-net yielded more stable and biologically meaningful results compared to the variables selected by the multiple logistic regression models.
+Data preprocessing (log2-transformation and standardization) improves the performance of classification algorithms and allows for the ability to more accurately predict which genomic features are most associated with TAD boundaries.
 
@@
 Models applied to unprocessed data can have poor predictive performances.
-Typical performance assessment metrics, such as AUROC, can mask poor performance of the models; thus, the use of more balanced metrics, such as F1 and MCC, is warranted.
-The elastic-net model, with its dual use of the $l_1$ and $l_2$ regularization terms allows for both the removal of uninformative predictors, while being able to handle multiple correlated epigenomic features.
+Focusing solely on typical performance assessment metrics, such as AUROC, can mask poor performance of the models; thus, the use of more balanced metrics, such as F1 and MCC, is warranted.
 Our model results in better performances and more accurate identification of important features associated with the formation of TAD boundaries.
@@
 Another problem lies in identifying which positional characteristics of the genomic features will optimize prediction.
-It is unclear if distances or overlaps between genomic bins and regions of functional elements contain the most information and will lead to better predictive performances.
+The use of distances (in base pairs) from genomic bins to regions of functional elements has largely been ignored.
+However, these distance characteristics offer a more accurate spatial representation of which genomic features are associated with TAD boundaries and have the potential to improve predictive performance.
 Lastly, given that some features tend to colocalize near TAD boundaries, most predictive models may be unable to identify the complete set of features most associated with boundary formation.
@@
 Additionally, ROC curves and AUCs were used to evaluate model performance, which is problematic, especially for highly imbalaned classes (Hanczar et al).
-A better indicator of predictive performance with classification algorithms is to consider the F1 score and Matthew's Correlation Coefficient (MCC).
-In another study (Huang et al), a more robust model in the form of a Bayesian Additive Regression Trees (BART) model was used.
-The set of features consisted of a score that averaged the number of sequence reads for each functional element over a particular bin for the GM12878 cell line.
-Here, the class proportion was manually created by dividing the positive and negative classes into two equal subsets used for model training and testing.
-However, it is unclear what balancing technique was used.
-In addition to this, the model was only performed on a small set of histone marks while ignoring wider classes of epigenomic elements.
-Lastly, in a more recent study (Hong et al), a bayesian rigde regression model was iteratively used on a set of transcription factor binding sites, transcription start sites, and DNase I hypersensitive sites from the hESC cell line until the best combination of features led to the optimal prediction of TAD boundaries.
-Here, the features of the model consisted of the number of occurences of each genomic element within each genomic bin.
-Balanced classes were manually created by randomly sampling from the set of bins that did not contain a TAD boundary.
-Given the structure of the search algorithm proposed, though, it can be computationally inefficient to have to iterate through a large set of genomic features to find the particular set that contributes to the best prediction.
-Because of that, only a maximum set of 10 genomic features were considered at any given time.
+A better indicator of predictive performance with classification algorithms is to consider the F1 score and Matthew's Correlation Coefficient (MCC) as they involve all quadrants of a confusion matrix.
 
-The types of models and the feature characteristics used in the aforementioned methods vary considerably.
-Because of the different cell lines available for analysis and the widening list of functional genomic elements, it can be quite useful to have a unified approach in predicting the formation of TAD boundaries.
-Therefore, in this study we have developed a novel data pre-processing pipeline that addresses the irregularities in the TAD boundary data provided by contact matrices at different resolutions for two cell lines, GM12878 and K562.
-We then performed a variety of machine learning algorithms on the pre-processes data to identify the genomic elements that were most predictive of TAD boundaries.
-In our models we incorporated the distances from bin to region as features.
-We found that the models performed on our pre-processed data performed better than previously established methods.
-Additionally, we were able to confirm that the cis-regulatory elements like insulators and promotors were highly predictive of TAD boundaries.
-The specific transcriptional repressor, CCCTC-binding factor (CTCF) was found to be highly predictive of TAD boundaries.
-Other non-transcription factor sites like DNase I hypersensitive sites and certain histone modifications like H3K36me3 were also found to be better predictors.
+In this study we have developed a novel data pre-processing pipeline that addresses the irregularities in the TAD boundary data provided by contact matrices at different resolutions for two cell lines, GM12878 and K562.
+We then performed a variety of machine learning algorithms on the pre-processed data to identify the genomic elements that were most predictive of TAD boundaries.
+Firstly, we found that the models performed on balanced data out performed those on unbalanced data.
+Secondly, it was determined that multiple iterations of random under-sampling was the balancing technique that yielded the best results.
+Thirdly, the inclusion of distances as predictors was found to improve model performance.
+Lastly, it was found that performing an inverse normal transformation of the distance predictors further improved model performance.
+
+After applying (insert final model(s)) we were able to confirm that cis-regulatory elements like insulators and promotors were highly predictive of TAD boundaries.
+The specific transcriptional repressor, CCCTC-binding factor (CTCF), was also found to be highly associated with TAD boundaries.
+Other non-transcription factor sites like DNase I hypersensitive sites and certain histone modifications like H3K36me3 were also found to be better predictors of TAD boundaries.
 Our findings confirm that models with pre-processed data and distance-related genomic features not only perform better, but are also able to correctly identify a range of different functional genomic elements associated with the formation of TAD boundaries.
@@
 
-Publicly available topologically associating domain data was obtained from GEO with accession GSE53525 for the GM12878 and K562 cell lines.
+Publicly available topologically associating domain data was obtained from GEO with accession GSE53525 for the GM12878 and K562 cell lines (Rao et.
+al).
 The domain data was constructed from in situ Hi-C contact matrices at a 5kb and 10 kb resolution for the GM12878 and k562 cell lines respectively.
-The Arrowhead algorithm was used to identify TAD boundaries for a given contact matrix (Rao et.
-al).
 Identified TAD boundaries were represented by their genomic coordinates (hg19 human genome assembly), including chromosome, start and end coordinates.
-The start and end coordinates were concatenated, sorted, and unique coordinates representing unique TAD boundaries were obtained [???
-Check for accuracy; !!!
-what do you mean by accuracy here?].
-A depiction of the data is presented in Figure X.
+The start and end coordinates were concatenated, sorted, and unique coordinates representing the borders demarcating TADs were obtained.
 
@@
 In either case, a genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
-Otherwise, the bin was labeled as not containing an boundary (Y=0) (Figure X).
+Otherwise, the bin was labeled as not containing an boundary (Y=0).
+An illustration of the data is presented in Figure X.
 
@@
 
-Annotation data was obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium.
-These annotations consisted of genomic coordinates and were used to build the feature space, X = {$X_{1}$, .
-.
-., $X_{p}$}, of the subsequent models.
-A full list of the genomic elements is provided in Table X.
-For each genomic element, the distance from the center of a genomic bin to the center of the nearest region (in base pairs) was calculated and included in the model.
-If the center of the region given by a particular functional element was located within a genomic bin, then the distance was given to be 0.
-Additionally, a variable denoting the number of overlaps between a genomic bin and region representing a genomic element was totaled and included in the model (Figure X).
+Annotation data, in the form of functional genomic coordinates, from ChIP-seq experiments was obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium.
+Similar to Mourad et al.
+we considered overlaps between bins and regions defined by functional genomic elements when creating the predictor space of our models.
+If a elemental region was located completely within a bin then the predictor ($X_{i}$) was labeled as 1.
+If a bin did not overlap with any region then it was labeled as 0.
+In the case of partial overlaps, a fraction denoting the percent overlap from region to bin was used.
+In the event of multiple regions within the same bin.
+The sum total of fractions or instances of regions was used as in Figure X.
 
@@
 We developed a pipeline that systematically evaluates the problems associated with TAD boundary data in a predictive modeling setting (Figure X).
-The pipeline was used to address issues related to normalization of predictors, class imbalance, and variable reduction.
-Prior to initiating the pipeline, predictors with near-zero variance were removed.
+The pipeline addresses X key questions in aiming to improve predictive performances and accurately identify which functional genomic elements are most predictive of TAD boundaries.
+Prior to initiating the pipeline, predictors with near-zero variances were removed.
 To identify said predictors, the nearZeroVar function in the CARET package was used.
@@
 
-At each subsequent stage in the pipeline, Elastic-Net models were performed and performance metrics such as F1 scores and MCCs were evaluated.
-The Elastic-Net model was used here because of its ability to be tuned and its computational speed relative to other machine learning algorithms.
-To avoid overfitting and more accurately assess performance, 10-fold cross validation was used for all models.
-For each elastic-net model the mixing parameter, alpha, was tuned over a grid of 10 evenly spaced values from 0 and 1.
-The penalty term, labmda, was tuned over a grid of 100 evenly spaced values from 0.01 to 100.
+### Question 1: CLASS IMBALANCE
 
-### NORMALIZATION
+How severely unbalanced were the classes and what was the affect on model performance?
+When binning the genome, the sparcity of TAD boundaries contributed to heavily imbalanced classes.
+That is, proportionally, only a small number of genomic bins overlapped with a flanked TAD boundary.
+To assess this issue two multiple logistic regression models were performed.
+One with unbalanced classes and one with balanced classes created by random under-sampling from the majority class.
+It was found that the model with balanced classes out-performed the model with unbalanced classes.
+However, given the vast disparity between classes simply performing on iteration of random under-sampling is not sufficient in determining the best possible balancing technique.
 
-Distances on a genomic scale are frequently highly skewed.
-In order to correct for this, a log base 2 transformation was considered.
-Additionally, the predictors were standardized to have unit variance in order to be able to directly compare magnitudes of parameter coefficients.
+### Question 2: BALANCING TECHNIQUE
 
-### CLASS IMBALANCE
-
-When binning the genome, the sparcity of TAD boundaries through the genome contributed to heavily imbalanced classes.
-That is, proportionally, only a small number of genomic bins overlapped with a flanked TAD boundary.
-To assess this issue, two methods were used.
-The first consisted of incorporating the SMOTE command from the DmWR package in R.
+Which balancing technique performs best?
+To assess this issue, three methods were used.
+The first consisted of performing X iterations of over-sampling from the minority class to match the majority class.
+At each iteration, a multiple logistic regression model was used and performance metrics were recorded.
+At the end of the X iterations, the performance metrics were aggregated by taking the average.
+The second method consisted of random under-sampling.
+Similar to over-sampling, the majority class was randomly under-sampled over X iterations to create balanced classes.
+Again, at each step a multiple logistic regression model was performed and the results were aggregated using the average.
+The last method incorporated the SMOTE command from the DmWR package in R.
 SMOTE stands for Synthetic Minority Over-sampling Technique.
@@
 Then, the majority class is under sampled by taking a random sample that matches some pre-specified percentage of the updated minority class.
+A total of four different combinations of percent over and under-sampling were used which included: 100/200, 200/200, 300/200, and 400/200.
 It is important to note that using a combination of 100/200 (percent over/percent under-sample) will always result in perfectly balanced classes.
-A total of four different combinations of percent over and under-sampling were used which included: 100/200, 200/200, 300/200, and 400/200.
-As mentioned before, the 100/200 combination created balanced classes, while the others create an unbalanced dataset with the negative class as the majority to reflect the proportionality of the classes in the original data.
-The second method involved iteratively under-sampling 100 time from the majority class to match the number in the minority class.
-For each sample, an elastic-net model was tuned and evaluated.
-Then row-wise means of the performance metrics for each of the 100 interations were taken to evaluate the models (Figure X).
+The other combinations created unbalanced classes with the negative class as the majority to reflect the proportionality of the classes from the original data.
+Multiple logistic regression models were used and performance metrics were assessed and compared with each of the other techniques.
+It was determined that the model with data untilizing random under-sampling out-performed all other other balancing techniques.
+However, to this point we only considered overlaps between genomic bins and the regions that defined functional genomic elements.
+
+### Question 3: DISTANCE PREDICTORS
+
+What affect does the inclusion of distances from bin to region have on model performance?
+To this point we had only considered overlaps between genomic bins and the regions that defined functional genomic elements.
+Now we added another type of predictor created from each genomic element.
+This consisted of the distance from the center of each genomic bin to the center of the nearest region defining a genomic element as depicted in Figure X.
+To assess any improvement with the inclusion of these predictors we compared the performances of three multiple logistic regression models: one with only the overlap predictors, one with only the aforementioned distance predictors, and one with both.
+It was found that the inclusion of distance predictors improved model performance.
+Likewise, the model with both types of predictors futher improved model performance.
+As is common, with genomic data, the use of continuous predictors (especially with regards to distances) results in highly right skewed data with distances ranging from 0 to tens of thousands in base pairs.
+This can affect the convergence of likelihood maximization.
+
+### Question 4: NORMALIZATION
+
+What normalization technique best improves model performance?
 
@@
 
-Figure X presents the model performance metrics of the eight different SMOTE combinations.
-The SMOTE combination utilizing percent over of 100 and percent under of 200 yielded the largest AUC (0.794).
-This was to be expected since this combination created perfectly balanced classes.
-However, looking at Figure X, the method using 100 bootstrap sample performed better than then model using SMOTE with an AUC of 0.809.
-Thus, it was concluded that using bootstrap samples would be more efficient moving forward.
-
 The best normalization technique was found to be the model that included a log base 2 transform with no standardized predictors.
@@
 Thus, it was concluded that only performing a log base 2 transformation was necessary.
+
+Figure X presents the model performance metrics of the eight different SMOTE combinations.
+The SMOTE combination utilizing percent over of 100 and percent under of 200 yielded the largest AUC (0.794).
+This was to be expected since this combination created perfectly balanced classes.
+However, looking at Figure X, the method using 100 bootstrap sample performed better than then model using SMOTE with an AUC of 0.809.
+Thus, it was concluded that using bootstrap samples would be more efficient moving forward.
 

### 2018-10-01 Manuscript/manuscript.Rmd
edits

@@
 
-In this study we have developed a novel data pre-processing pipeline that addresses the irregularities in the TAD boundary data provided by contact matrices at different resolutions for two cell lines, GM12878 and K562.
+In this study we have developed a novel data pre-processing pipeline that addresses the irregularities in the TAD boundary data provided by contact matrices for the GM12878 cell line.
 We then performed a variety of machine learning algorithms on the pre-processed data to identify the genomic elements that were most predictive of TAD boundaries.
@@
 
-Publicly available topologically associating domain data was obtained from GEO with accession GSE53525 for the GM12878 and K562 cell lines (Rao et.
+Publicly available topologically associating domain data was obtained from GEO with accession GSE53525 for the GM12878 cell line (Rao et.
 al).
-The domain data was constructed from in situ Hi-C contact matrices at a 5kb and 10 kb resolution for the GM12878 and k562 cell lines respectively.
+The domain data was constructed from in situ Hi-C contact matrices at a 5kb resolution.
 Identified TAD boundaries were represented by their genomic coordinates (hg19 human genome assembly), including chromosome, start and end coordinates.
@@
 This was performed at the same resolution as the respective cell line.
-That is, for GM12878, 5 kb genomic bins were used, while 10 kb bins were used for K562.
-Next, for the domain data provided by GM12878, the boundary coordinates were flanked on either side by 5 kb.
-For the K562, the boundary coordinates were flanked by 10 kb.
-In either case, a genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
+That is, 5 kb genomic bins were used.
+Next, the boundary coordinates were flanked on either side by 5 kb.
+A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
 Otherwise, the bin was labeled as not containing an boundary (Y=0).
@@
 
-What normalization technique best improves model performance?
+What normalization technique performed on the distance predictors best improves model performance?
+Here, we considered three normalization techniques.
+The first was a simple $log_{2}$ transformation, in which one was added in the case of distances of 0.
+The second was an inverse hyperbolic sine tranformation given by $insert function here$ which has the benefit of handling values of 0.
+Lastly, an inverse normal tranformation was considered.
+The inverse normal transformation is a way of transforming the sample distribution of a continuous variable to make it appear more normally distributed by matching the normalized rank of the trait to a quantile in a normal distribution using the following formula $insert formula here$.
+Multiple logistic regression models were performed using data with each respective transformation and compared.
+It was found that the model with inverse normally transformed distance predictors not only out-performed the other transformation but also out-performed a model with no transformation at all.
+So far the only classification algorithm considered was a multiple logistic regression.
+However, given the large number possible functional genomic elements that can be considered, this model can be computationally inefficient.
 
-### VARIABLE SELECTION
+### Question 5: Classification
 
-Due to the large number of genomic features included in the model, different variable selection techniques were evaluated in order to improve computational speed and eliminate uninformative variables.
-There were three different wrapper methods that were used here, forward, backward, and stepwise selection.
-A null model consisting of just an intercept term and a full model, including all features, were specified for each selection technique.
-For all three, a logistic regression model was performed, and the AIC of the fitted model was used to establish which variables to include.
-That is, only a reduction in the model's AIC contributed to the inclusion of a feature in the model.
-For each technique, prior to model selection, balanced classes were iteratively created 100 times by random under-sampling from teh majority class.
-At each iteration the variables selected from each technique were recorded.
-The final set of predictors selected for each technique were those that appeared over 90% of the time accross all iterations.
-The union of the three sets of features from each of the techniques was obtained and used as the final feature space of the data (Figure X)
-
-## FINAL MODEL
-
-Once the pipeline produced the appropriate dataset, an elastic was used to assess which genomic features that were most predictive of the development of TAD boundaries.
-The algorithm was run iteratively over 100 random under-sampled majority classes to balance the data, each time producing performance metrics and variable importances.
-At the end of the 100 iterations, row-wise means were performed to aggregate the model information.
-We then compared the elastic-net model performed on the processed data to both a multiple logistic regression model and a LASSO regularized model with and without the use of distance predictors and with or without processed data.
-
-#####################
+Which classification algorithm most accurately and efficiently identifies the genomic elements associated with TAD boundaries?
 

### 2018-10-01 Manuscript/manuscript.Rmd
edits

@@
 output: 
-  pdf_document:
-    toc: yes
   word_document:
@@
     fig_width: 2
+    toc: yes
+  pdf_document:
     toc: yes
@@
 These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
-The distinct patterns of some of these different proteins and functional elements point toward the opportunity of computational approaches in predicting the development of TAD boundaries, which, in genereal, will allow us to better understand what leads to their formation.
+The distinct patterns of some of these different proteins and functional elements point toward the opportunity of computational approaches in predicting which epigenomic features are most predictive of the development of TAD boundaries.
+This will allow us to better understand what leads to their formation.
 
@@
 One such pitfall is the issue of highly imbalanced classes.
-The commonality between most accepted methods for predicting TAD boundaries considers binning the genome and labeling the bins as either containing a TAD boundary or not.
+The commonality between most accepted methods for predicting TAD boundaries considers performing a classification algorithm by binning the genome and labeling the bins as either containing a TAD boundary or not.
 However, due to the sparcity of TADs throughout the genome, most bins will not contain a TAD boundary.
-This will contribute to highly imbalanced classes and will also introduce predictors with near-zero variance.
-It has been shown that imbalanced classes can result in poor predictive performances of classification algorithms and unless the class imbalance is mild, researchers should always use an appropriate method for dealing with this (Blagus et al).
+This will contribute to highly imbalanced classes and has the potential to introduce predictors with near-zero variance.
+It has been shown that imbalanced classes can result in poor predictive performances of classification algorithms (Blagus et al).
 Furthermore, the inclusion of predictors with near-zero variance can add unnecessary noise to the model and decrease computational efficiency of predictive algorithms.
@@
 The use of distances (in base pairs) from genomic bins to regions of functional elements has largely been ignored.
-However, these distance characteristics offer a more accurate spatial representation of which genomic features are associated with TAD boundaries and have the potential to improve predictive performance.
+However, these distance characteristics offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
 Lastly, given that some features tend to colocalize near TAD boundaries, most predictive models may be unable to identify the complete set of features most associated with boundary formation.
@@
 However, the class imbalance issue was not addressed and neither model used is suited to handle multiple correlated predictors.
-Additionally, ROC curves and AUCs were used to evaluate model performance, which is problematic, especially for highly imbalaned classes (Hanczar et al).
+Likewise, it is unclear how the team handled the situation when multiple regions defined by the same genomic element are located within the same bin.
+The length of the genomic bins can be flexible and as the size increases, there is a greater chance for the occurance of multple regions to be located within the same bin.
+If a simple indicator (1 or 0) is used, instead of, say, the sum total of regions within that bin, it is possible that a significant amount of information is lost.
+Additionally, the team used ROC curves and AUCs to evaluate model performance, which is problematic, especially for highly imbalaned classes (Hanczar et al).
 A better indicator of predictive performance with classification algorithms is to consider the F1 score and Matthew's Correlation Coefficient (MCC) as they involve all quadrants of a confusion matrix.
@@
 Secondly, it was determined that multiple iterations of random under-sampling was the balancing technique that yielded the best results.
-Thirdly, the inclusion of distances as predictors was found to improve model performance.
+Thirdly, the inclusion of distances as predictors was found to improve model performance compared to a model with simple overlap predictors.
 Lastly, it was found that performing an inverse normal transformation of the distance predictors further improved model performance.
@@
 
-## THE DATA
+## DOMAIN DATA
 
@@
 The domain data was constructed from in situ Hi-C contact matrices at a 5kb resolution.
-Identified TAD boundaries were represented by their genomic coordinates (hg19 human genome assembly), including chromosome, start and end coordinates.
+Identified TAD boundaries were represented by their location in the genome (hg19 human genome assembly), including chromosome, start and end coordinates.
 The start and end coordinates were concatenated, sorted, and unique coordinates representing the borders demarcating TADs were obtained.
@@
 A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
-Otherwise, the bin was labeled as not containing an boundary (Y=0).
+Otherwise, the bin was labeled as not containing a boundary (Y=0).
 An illustration of the data is presented in Figure X.
@@
 In the case of partial overlaps, a fraction denoting the percent overlap from region to bin was used.
-In the event of multiple regions within the same bin.
-The sum total of fractions or instances of regions was used as in Figure X.
+However, in contrast to Mourad et al., in the event of multiple regions within the same bin, the sum total of fractions or instances of regions was used as in Figure X.
 
@@
 
-### Question 1: CLASS IMBALANCE
+### Question 1: How severely unbalanced were the classes and what was the affect on model performance?
 
-How severely unbalanced were the classes and what was the affect on model performance?
 When binning the genome, the sparcity of TAD boundaries contributed to heavily imbalanced classes.
@@
 It was found that the model with balanced classes out-performed the model with unbalanced classes.
-However, given the vast disparity between classes simply performing on iteration of random under-sampling is not sufficient in determining the best possible balancing technique.
+However, given the vast disparity between classes simply performing one iteration of random under-sampling was not sufficient in determining the best possible balancing technique.
 
-### Question 2: BALANCING TECHNIQUE
+### Question 2: Which balancing technique performs best?
 
-Which balancing technique performs best?
-To assess this issue, three methods were used.
+Three methods were used to evaluate class balance.
 The first consisted of performing X iterations of over-sampling from the minority class to match the majority class.
@@
 
-### Question 3: DISTANCE PREDICTORS
+### Question 3: What affect does the inclusion of distances from bin to region have on model performance?
 
-What affect does the inclusion of distances from bin to region have on model performance?
 To this point we had only considered overlaps between genomic bins and the regions that defined functional genomic elements.
@@
 
-### Question 4: NORMALIZATION
+### Question 4: What normalization technique performed on the distance predictors best improves model performance?
 
-What normalization technique performed on the distance predictors best improves model performance?
 Here, we considered three normalization techniques.
@@
 
-### Question 5: Classification
+### Question 5: Which classification algorithm most accurately and efficiently identifies the genomic elements associated with TAD boundaries?
 
-Which classification algorithm most accurately and efficiently identifies the genomic elements associated with TAD boundaries?
+We compared the results from a multiple logistic regression model to that of a multiple logistic regression model with both LASSO and Elastic-Net regularization.
+Prior to model fitting, the predictors were standardized in order to compare magnitudes of the subsequent beta coefficients as a measure of variable importance.
+For the models with regularization, 10-fold cross validation was used to tune the penalization terms ($\lambda$ for LASSO and both $\lambda$ and $\alpha$ for Elastic-Net).
+Model performance was compared using F1-scores, MCCs, and AUROCs.
+The alpha level of significance was set at 0.05.
+All statistical analyses was performed in R version 3.4.2.
 

### 2018-10-03 ToDo.Rmd
completed tasks

@@
  +both scaled
+
+## 09/24/18
+
++ add standardization part to question 4 table
++ question 6: which variable selection technique?
++ perform scaling with transformation
+
+## 10/01/18
+
+* read up on random forest 
+   - investigate how to get final decision tree
+   - how variable importance is calculated
++ write about answers not questions; make headers as answers not questions
++ investigate how many iterations are necessary for under sampling
+   - plot it
+* investigate svm & neural networks & naiive bayes

### 2018-10-03 Manuscript/manuscript.Rmd
edits

@@
 output: 
+  pdf_document:
+    toc: yes
   word_document:
@@
     fig_width: 2
-    toc: yes
-  pdf_document:
     toc: yes
@@
 The domain data was constructed from in situ Hi-C contact matrices at a 5kb resolution.
-Identified TAD boundaries were represented by their location in the genome (hg19 human genome assembly), including chromosome, start and end coordinates.
+Identified TAD boundaries were represented by their location in the genome (hg19 human genome assembly), including chromosome, start and end coordinates for chromosomes 1 through 22.
 The start and end coordinates were concatenated, sorted, and unique coordinates representing the borders demarcating TADs were obtained.
@@
 
-### Question 1: How severely unbalanced were the classes and what was the affect on model performance?
+### Class Imbalance
 
@@
 That is, proportionally, only a small number of genomic bins overlapped with a flanked TAD boundary.
-To assess this issue two multiple logistic regression models were performed.
-One with unbalanced classes and one with balanced classes created by random under-sampling from the majority class.
-It was found that the model with balanced classes out-performed the model with unbalanced classes.
-However, given the vast disparity between classes simply performing one iteration of random under-sampling was not sufficient in determining the best possible balancing technique.
-
-### Question 2: Which balancing technique performs best?
-
-Three methods were used to evaluate class balance.
-The first consisted of performing X iterations of over-sampling from the minority class to match the majority class.
-At each iteration, a multiple logistic regression model was used and performance metrics were recorded.
-At the end of the X iterations, the performance metrics were aggregated by taking the average.
-The second method consisted of random under-sampling.
-Similar to over-sampling, the majority class was randomly under-sampled over X iterations to create balanced classes.
-Again, at each step a multiple logistic regression model was performed and the results were aggregated using the average.
-The last method incorporated the SMOTE command from the DmWR package in R.
-SMOTE stands for Synthetic Minority Over-sampling Technique.
-The SMOTE algorithm incorporates both under-sampling (percent under) of the majority class and over-sampling (percent over) of the minority class.
-The minority class is over-sampled by taking each minority class sample and introducing synthetic examples along the line segments joining any/all of the k minority class nearest neighbors (here, k=5).
-Then, the majority class is under sampled by taking a random sample that matches some pre-specified percentage of the updated minority class.
-A total of four different combinations of percent over and under-sampling were used which included: 100/200, 200/200, 300/200, and 400/200.
-It is important to note that using a combination of 100/200 (percent over/percent under-sample) will always result in perfectly balanced classes.
-The other combinations created unbalanced classes with the negative class as the majority to reflect the proportionality of the classes from the original data.
-Multiple logistic regression models were used and performance metrics were assessed and compared with each of the other techniques.
+To assess this issue a series of multiple logistic regression models were performed.
+First, a multiple logistic regression model using the full data with unbalanced classes was assessed.
+We then compared this to a multiple logistic regression model with balanced classes created by random over-sampling, random under-sampling, and four other multiple logistic regression models with balanced classes created by the SMOTE (Synthetic Minority Over-sampling Technique) function in the DmWR package in R.
+For each of the random over- and under-sampling methods, multiple iterations were considered up until the difference in the cumulative means reached below a threshold of $5 \times 10^{-5}$.
+Performances were then aggregated by taking the average across all iterations.
 It was determined that the model with data untilizing random under-sampling out-performed all other other balancing techniques.
@@
 
-### Question 3: What affect does the inclusion of distances from bin to region have on model performance?
+### Incorporating Distances
 
-To this point we had only considered overlaps between genomic bins and the regions that defined functional genomic elements.
-Now we added another type of predictor created from each genomic element.
+To gain further insight into the spatial relationship between these chromatin factors and the genome, we introduced distance predictors into the model.
 This consisted of the distance from the center of each genomic bin to the center of the nearest region defining a genomic element as depicted in Figure X.
@@
 Likewise, the model with both types of predictors futher improved model performance.
-As is common, with genomic data, the use of continuous predictors (especially with regards to distances) results in highly right skewed data with distances ranging from 0 to tens of thousands in base pairs.
-This can affect the convergence of likelihood maximization.
+As is common, with genomic data, the use of the distance predictors resulted in highly right skewed data with distances ranging from 0 to tens of thousands in base pairs.
 
-### Question 4: What normalization technique performed on the distance predictors best improves model performance?
-
-Here, we considered three normalization techniques.
+To better improve computational efficiency with regards to the convergence of likelihood maximization, we considered three normalization techniques.
 The first was a simple $log_{2}$ transformation, in which one was added in the case of distances of 0.
@@
 It was found that the model with inverse normally transformed distance predictors not only out-performed the other transformation but also out-performed a model with no transformation at all.
-So far the only classification algorithm considered was a multiple logistic regression.
-However, given the large number possible functional genomic elements that can be considered, this model can be computationally inefficient.
 
-### Question 5: Which classification algorithm most accurately and efficiently identifies the genomic elements associated with TAD boundaries?
+### Classification Models
 
-We compared the results from a multiple logistic regression model to that of a multiple logistic regression model with both LASSO and Elastic-Net regularization.
-Prior to model fitting, the predictors were standardized in order to compare magnitudes of the subsequent beta coefficients as a measure of variable importance.
-For the models with regularization, 10-fold cross validation was used to tune the penalization terms ($\lambda$ for LASSO and both $\lambda$ and $\alpha$ for Elastic-Net).
+Therefore, the final data used for quantifying the association between each functional genomic element and TAD boundary formation was one that had been balanced using multiple iterations of random under-sampling, incorporated both overlapped and distance predictors, and normalized using an inverse normal transformation.
+Likewise, prior to model fitting, the predictors were standardized in order to compare magnitudes of the subsequent beta coefficients as a measure of variable importance.
+We then performed a wide variety of classification algorithms to determine which genomic elements were most predictive of TAD boundaries.
+The models included a multiple logistic regression, a multiple logistic regression with both LASSO and Elastic-Net regularization, a random forest, a gradient boosting machine, a support vector machine, and a naiive bayes model.
+For each model, 10-fold cross validation was performed to tune for any neccessary paramenters.
 Model performance was compared using F1-scores, MCCs, and AUROCs.
@@
 
-There was a total of 247632 genomic bins that made up the response vector Y, 1629 (0.7%) of which contained TAD boundaries (Y=1).
-A total of 68 genomic features were included in the analysis.
-Two predictors were included for every feature (one binary, one continuous), making for a total of 136 predictors.
-The list of predictors is provided in Table X.
-The feature space was reduced to 90 after all near-zero variance predictors were removed.
-The predictors that were removed are listed in Table X [???
-Mark them in supplementary table of all features].
+A total of 9048 topologically associating domains and their genomic locations were obtained for the GM12878 cell line for chromosomes 1 through 22.
+The median width of TADs was found to be 18.5 kb (IQR: 11.5kb - 33.0kb).
+The start and end coordiantes of the TADs were translated into a vector of boundary points.
+There were 1454 (16%) TADs that shared at least one coordinate (start, end, or both) with another TAD.
+In this case the unique boundary point demarcating two adjacent TADs was considered.
+The genome was binned at 10 kb interval, resulting in a total of 536396 bins.
+A total of 536396 genomic bins of 10 kb width were created.
+After flanking the TAD boundary points on either side by 5 kb, it was found that 31820 (5.9%) bins contained a flanked TAD boundary.
+We investigated a total of 68 genomic features, 12 (18%) of which were removed because they were assessed as having near-zero variance.
+Table X presents a full list of the genomic features in addition to the metrics and indicator corresponding to whether or not the feature was to be removed.
 
-The best normalization technique was found to be the model that included a log base 2 transform with no standardized predictors.
-The AUC was found to be 0.809 and presented in Figure X.
-We see that this value is only marginally greater than the model using a log base 2 transform and standardized predictors.
-However, from Figure X, we see that the variable importance plot associated with a log base 2 transform with no standardized predictors (top right) yielded more accurate results than all other combinations.
-Notably, the insulator, CTCF, and DNaseI features are located in the top 3 most important features for predicting TAD boundaries, as expected.
-This is in contrast to the other three combinations, which presented conflicting results.
-Thus, it was concluded that only performing a log base 2 transformation was necessary.
+## Balancing Classes Improves Performance
 
-Figure X presents the model performance metrics of the eight different SMOTE combinations.
-The SMOTE combination utilizing percent over of 100 and percent under of 200 yielded the largest AUC (0.794).
-This was to be expected since this combination created perfectly balanced classes.
-However, looking at Figure X, the method using 100 bootstrap sample performed better than then model using SMOTE with an AUC of 0.809.
-Thus, it was concluded that using bootstrap samples would be more efficient moving forward.
+It was found that the multiple logistic regression models utilizing random over and under-sampling out-performed the other techniques and were comparatively similar with F1 scores of 0.636 and 0.637 respectively.
+The under-technique was evaluated over 13 iterations, while the over-sampling technique took far more iterations for the cumulative mean F1 score to converge, X to be exact.
+Given that and the fact that the under-sampling technique uses significantly less data than the over-sampling, while still performing at the same level, it was concluded that this was the best balancing technique and used in further analyses.
 
-The best performing variable selection technique was found to be forward selection (AUC: 0.810) as shown in Figure X.
-All of the stepwise procedures performed better than the recursive feature elimination method, which not only performed worse, but also chose the most predictors.
-It should be noted that both forward and backward selection had the same AUC.
-However, the forward selection chose fewer predictors, 28 compared to 34 respectively.
-Thus, forward selection was chose as the most appropriate variable selection technique.
-Figure X presents the relationship between each variable selection technique.
-We see that there was significant agreement between forward and backward selections, with 26 predictors being shared by both.
-Likewise, there was a total of 12 predictors in common between all four techniques.
-Table X lists the common predictors between each comparison.
+## Incorporating Distance Predictors Improves Performance
 
-After the data was ran through our pipeline, the final dataset consisted of 28 log transformed predictors.
-Lastly, 100 bootstrap sampled random forest models were performed on said data.
-Figure X presents the results compared to the multiple logistic regression models proposed by Mourad et al.
-We see that the random forest model, using the pipeline processed data, preforms better compared to both models proposed by Mourad et al with an AUC of 0.805.
-Moreover, the variable importance plot in Figure X reiterates the strong predictive performance of the random forest model by indicating that the DNaseI, insulator, and CTCF genomic features are among the top 3 variables most predictive TAD boundaries.
-The MLR with LASSO estimation only marginally out performs the regular MLR model with AUCs of 0.750 and 0.747 respectively.
-Likewise, from Table X we can see that there is more similarity in the ranking of important features between the random forest model and the MLR with LASSO model.
-However, there is still a large disparity, with 12 variables recognized as important by the random forest that are missing from the MLR with LASSO model.
-Thus, we conclude that a random forest algorithm applied to a dataset ran through the proposed pipeline performs uniformly better than a multiple logistic regression model, regardless if LASSO estimation is used.
+The multiple logistic regression model with only distance predictors, evaluated on multiple iterations of random under-sampling was found to improve model performance from 0.637 (using only overlap predictors) to 0.747.
+Furthermore, the multiple logistic regression model with both types of predictors further improved model performance by raising the F1 score to 0.753.
+This suggested that the distance predictors were more representative of the association between the genomic elements and TAD boundaries.
+However, on a genomic scale, distances from the bins to the nearest region defined by a respective genomic element were highly right skewed.
+We evaluated three tranformations in order to normalize the distance predictors and improve model performance.
+Out of the three normalization techniques, the multiple logistic regression model with an inverse normal transformation on the distance predictors was found to perform the best with an F1 score of 0.747.
+
+##
 

### 2018-10-03 Manuscript/results_outline.Rmd
edits

--- 2018-09-12 Manuscript/results_outline.Rmd
@@
 # Results
+
+* Summary of data
+   + How many TADs
+   + How many genomic bins
+   + What genomic elements were used
+
+* Results of class imbalance
+   + which technique performed best?
+
+* Results for including distance predictors?
+   + results for model with just distance
+   + results for model with both types
+   + compare 
+   + results from normalization techniques
+
+* Results from classification algorithms
+   + MLR
+   + LASSO
+   + ENET
+   + RF
+   + GBM
+   + SVM 
+   + Naiive Bayes
+   + Compare
+
+# Discussion
+
+* State the results that were interesting 
+   - Specific to each cell line/tfbs
+   - Then results all together
+* State how much better models using our pipeline performed compared to Mourad
+   - Was it due to the model choice or the use of distance features?
+* Limitations/Future
+   - Mention the need for HiC experiments using higher resolutions
+   - Experimenting with TAD data using other methods
+   - Exploring other cell lines

### 2018-10-03 Manuscript/manuscript.Rmd
updates

@@
 It was found that the multiple logistic regression models utilizing random over and under-sampling out-performed the other techniques and were comparatively similar with F1 scores of 0.636 and 0.637 respectively.
-The under-technique was evaluated over 13 iterations, while the over-sampling technique took far more iterations for the cumulative mean F1 score to converge, X to be exact.
+The under- sampling technique was evaluated over 13 iterations, while the over-sampling technique took far more iterations for the cumulative mean F1 score to converge, 26 to be exact.
 Given that and the fact that the under-sampling technique uses significantly less data than the over-sampling, while still performing at the same level, it was concluded that this was the best balancing technique and used in further analyses.
@@
 
-##
+## X Classification Algorithm Provides Best Performance
 

### 2018-11-02 Manuscript/manuscript.Rmd
edits

--- 2018-10-03 Manuscript/manuscript.Rmd
@@
 Furthermore, changing the 3D structure of the DNA and distrupting these domains can lead to adverse outcomes and diseases like cancer.
-Therefore it is important to be able to identify the key molecular drivers of the formation of TADs in order to further our understanding of the human genome.
+Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.
 
@@
 Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long range chromatin contacts (Zuin et al.).
-Other regulatory elements like DNase I hypersensitive sites, the H3K36 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions (Hong et al).
+Other regulatory elements like DNase I hypersensitive sites, particular histone modifications, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions (Hong et al).
 These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
@@
 
-Due to the size of Hi-C data and the abundance of available genomic features, few methods have been developed to study the role and interplay of different sets of these features on the folding of DNA.
-Furthermore, many accepted methods ignore key characteristics of the data that, when addressed, may improve predictive performances.
-One such pitfall is the issue of highly imbalanced classes.
-The commonality between most accepted methods for predicting TAD boundaries considers performing a classification algorithm by binning the genome and labeling the bins as either containing a TAD boundary or not.
-However, due to the sparcity of TADs throughout the genome, most bins will not contain a TAD boundary.
-This will contribute to highly imbalanced classes and has the potential to introduce predictors with near-zero variance.
-It has been shown that imbalanced classes can result in poor predictive performances of classification algorithms (Blagus et al).
-Furthermore, the inclusion of predictors with near-zero variance can add unnecessary noise to the model and decrease computational efficiency of predictive algorithms.
-Another problem lies in identifying which positional characteristics of the genomic features will optimize prediction.
-The use of distances (in base pairs) from genomic bins to regions of functional elements has largely been ignored.
+Most accepted methods for predicting TAD boundaries consider performing a classification algorithm by binning the genome and labeling the bins as either containing a TAD boundary or not.
+However, a pervasive issue becomes the introduction of highly imbalanced classes.
+Due to the sparcity of TADs throughout the genome, most bins will not contain a TAD boundary.
+Therefore, the minority class of genomic bins with TAD boundaries in them becomes proportionally smaller than that of the majority class of genomic bins with no TAD boundaries.
+It is commonly agreed that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate (Estabrooks et al).
+Furthermore, it is unclear what sized bins best improves predictive performance or even if the results are stable across differently sized genomic bins.
+
+Another problem lies in identifying the feature space of subsequent classification algorithms.
+A variety of positional characteristics of the genomic features can be used to describes the relationship between TAD boundaries and genomic elements, but it is unclear which is best.
+The use of distances (in base pairs) from genomic bins to regions of functional genomic elements has largely been ignored.
 However, these distance characteristics offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
-Lastly, given that some features tend to colocalize near TAD boundaries, most predictive models may be unable to identify the complete set of features most associated with boundary formation.
-This can lead to less informative results and restrict our knowledge of how these genomic elements correlate with eachother.
 
-In a previous study (Mourad et al) both a multiple logistic regression model and a LASSO regularized regression model were applied to a wide array of architectural proteins from the GM12878 cell line to predict TAD boundaries.
-The set of features consisted of whether or not the coordinates of a functional element overlaped with a particular genomic bin (yes or no).
-In the case of a partial overlap, a percentage of overlap was used.
-However, the class imbalance issue was not addressed and neither model used is suited to handle multiple correlated predictors.
-Likewise, it is unclear how the team handled the situation when multiple regions defined by the same genomic element are located within the same bin.
-The length of the genomic bins can be flexible and as the size increases, there is a greater chance for the occurance of multple regions to be located within the same bin.
-If a simple indicator (1 or 0) is used, instead of, say, the sum total of regions within that bin, it is possible that a significant amount of information is lost.
-Additionally, the team used ROC curves and AUCs to evaluate model performance, which is problematic, especially for highly imbalaned classes (Hanczar et al).
-A better indicator of predictive performance with classification algorithms is to consider the F1 score and Matthew's Correlation Coefficient (MCC) as they involve all quadrants of a confusion matrix.
+In this study we have developed an ensemble framework that aims to address and compare a variety of data irregularities and characteristics that are associated with the prediction of TAD boundaries.
+We examined the inclusion of three different predictor types as the feature space for predictive modelling.
+We also examined four resampling techniques aimed at improving class imbalance.
+Lastly, we examined the effect of three separate variable reduction techniques on model performance.
+Random forest classification algorithms were performed to investigate which functional genomic features were most associated with the formaton of TAD boundaries.
+Model performance was evaluated based on a total of four metrics which included test accuracy, area under the ROC curve (AUC), F1 score, and Matthew's Correlation Coefficient (MCC).
 
-In this study we have developed a novel data pre-processing pipeline that addresses the irregularities in the TAD boundary data provided by contact matrices for the GM12878 cell line.
-We then performed a variety of machine learning algorithms on the pre-processed data to identify the genomic elements that were most predictive of TAD boundaries.
-Firstly, we found that the models performed on balanced data out performed those on unbalanced data.
-Secondly, it was determined that multiple iterations of random under-sampling was the balancing technique that yielded the best results.
-Thirdly, the inclusion of distances as predictors was found to improve model performance compared to a model with simple overlap predictors.
-Lastly, it was found that performing an inverse normal transformation of the distance predictors further improved model performance.
-
-After applying (insert final model(s)) we were able to confirm that cis-regulatory elements like insulators and promotors were highly predictive of TAD boundaries.
-The specific transcriptional repressor, CCCTC-binding factor (CTCF), was also found to be highly associated with TAD boundaries.
-Other non-transcription factor sites like DNase I hypersensitive sites and certain histone modifications like H3K36me3 were also found to be better predictors of TAD boundaries.
-Our findings confirm that models with pre-processed data and distance-related genomic features not only perform better, but are also able to correctly identify a range of different functional genomic elements associated with the formation of TAD boundaries.
-This knowlege will allow us to gain better insight into the role that the spatial organisation of the human genome has on gene regulation.
+[Insert last paragram for introduction]
 
@@
 al).
-The domain data was constructed from in situ Hi-C contact matrices at a 5kb resolution.
+The domain data was constructed from in situ Hi-C contact matrices at 5kb, 25kb, 50kb, and 100kb resolutions.
 Identified TAD boundaries were represented by their location in the genome (hg19 human genome assembly), including chromosome, start and end coordinates for chromosomes 1 through 22.
@@
 
-The establishment of the data for modeling first consisted of binning the genome into equal sized intervals.
-This was performed at the same resolution as the respective cell line.
-That is, 5 kb genomic bins were used.
-Next, the boundary coordinates were flanked on either side by 5 kb.
+Figure 1 presents a diagram of how the data was established for modeling purposes.
+First, the genome was binned into equally sized intervals.
+This was performed at the same resolution of the contact matrix that the domain data was obtained from.
+For example, for the domain data obtained from a 5kb resolution contact matrix, the genome was subsequently binned into 5kb intervals.
+The same processes was repeated for each of the other three resolutions.
+Next, the boundary coordinates were flanked on either side by a unit corresponding to the resolution of the particular domain data.
+Again siting the domain data obtained from a 5kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 5kb.
+Again, the same process was repeated for the other three resolutions.
 A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
 Otherwise, the bin was labeled as not containing a boundary (Y=0).
-An illustration of the data is presented in Figure X.
 
@@
 
-Annotation data, in the form of functional genomic coordinates, from ChIP-seq experiments was obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium.
-Similar to Mourad et al.
-we considered overlaps between bins and regions defined by functional genomic elements when creating the predictor space of our models.
-If a elemental region was located completely within a bin then the predictor ($X_{i}$) was labeled as 1.
-If a bin did not overlap with any region then it was labeled as 0.
-In the case of partial overlaps, a fraction denoting the percent overlap from region to bin was used.
-However, in contrast to Mourad et al., in the event of multiple regions within the same bin, the sum total of fractions or instances of regions was used as in Figure X.
+Annotation data, in the form of functional genomic element, from ChIP-seq experiments was obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium.
+The annotations consisted of a variety of different chromatin states using hidden markov models, histone marks, and DNase I hypersensitive sites.
+Each annotation is represented by their location throughout the genome via chromosomal coordinates.
+Using each genomic element we created three types of predictors that were used as features in downstream modelling.
 
-## DATA PIPELINE
+## Ensemble Framework
 
-We developed a pipeline that systematically evaluates the problems associated with TAD boundary data in a predictive modeling setting (Figure X).
-The pipeline addresses X key questions in aiming to improve predictive performances and accurately identify which functional genomic elements are most predictive of TAD boundaries.
-Prior to initiating the pipeline, predictors with near-zero variances were removed.
-To identify said predictors, the nearZeroVar function in the CARET package was used.
-The function considers two metrics.
-First, the ratio of the most frequent value over the second most frequent value was calculated.
-Ideally, this ratio would be close to one for well-behaved predictors.
-Next, the number of unique values divided by the total number of samples multiplied by 100 was calculated.
-Here, if the frequency ratio was greater than 20 and the percentage of unique values was less than 10, the predictor was flagged as having near-zero variance and removed.
+Figure 2 details the ensemble system proposed and evaluated in this study.
+For each predictor type chosen, the data, composed of majority and minority classes, was split into a 7:3 ratio of training to testing sets.
+For the trainig set, a variable reduction technique was performed.
+The feature space was reduced and a resampling technique was performed.
+A classification algorithm in the form of a random forest was performed and validated using the test set.
 
-### Class Imbalance
+A total of three increasingly refined predictor types where used to describe the relationship between TAD boundaries and each function genomic element of interest.
+Two different overlap types and a distance type were considered.
+Figure 3 presents an illustration of each type and is detailed below:
 
-When binning the genome, the sparcity of TAD boundaries contributed to heavily imbalanced classes.
-That is, proportionally, only a small number of genomic bins overlapped with a flanked TAD boundary.
-To assess this issue a series of multiple logistic regression models were performed.
-First, a multiple logistic regression model using the full data with unbalanced classes was assessed.
-We then compared this to a multiple logistic regression model with balanced classes created by random over-sampling, random under-sampling, and four other multiple logistic regression models with balanced classes created by the SMOTE (Synthetic Minority Over-sampling Technique) function in the DmWR package in R.
-For each of the random over- and under-sampling methods, multiple iterations were considered up until the difference in the cumulative means reached below a threshold of $5 \times 10^{-5}$.
-Performances were then aggregated by taking the average across all iterations.
-It was determined that the model with data untilizing random under-sampling out-performed all other other balancing techniques.
-However, to this point we only considered overlaps between genomic bins and the regions that defined functional genomic elements.
+1.
+Overlap Counts (OC): For each genomic bin, a total count of each overlapped region, defined by a functional genomic element, with a bin was calculated.
+If no regions overlapped with a bin, then the predictor was assigned as 0.
 
-### Incorporating Distances
+2.
+Overlap Percent (OP): For each genomic bin, the percent of overlap between a bin and a region was calculated as the ratio of feature width (in base pairs) and the total width of each bin.
+Here, the feature width was defined as the number of base pairs that overlapped between a bin and an elemental region.
+Note, that the denominator of this ratio was given to be that same for each respective domain data used.
+That is, for the 5kb resolution domain data, the total width of each bin was 5kb.
 
-To gain further insight into the spatial relationship between these chromatin factors and the genome, we introduced distance predictors into the model.
-This consisted of the distance from the center of each genomic bin to the center of the nearest region defining a genomic element as depicted in Figure X.
-To assess any improvement with the inclusion of these predictors we compared the performances of three multiple logistic regression models: one with only the overlap predictors, one with only the aforementioned distance predictors, and one with both.
-It was found that the inclusion of distance predictors improved model performance.
-Likewise, the model with both types of predictors futher improved model performance.
-As is common, with genomic data, the use of the distance predictors resulted in highly right skewed data with distances ranging from 0 to tens of thousands in base pairs.
+3. Distance: For each genomic bin, the distance (in base pairs) from the center of the bin to the center of the nearest region of a respective functional genomic elemnt was calculated.
 
-To better improve computational efficiency with regards to the convergence of likelihood maximization, we considered three normalization techniques.
-The first was a simple $log_{2}$ transformation, in which one was added in the case of distances of 0.
-The second was an inverse hyperbolic sine tranformation given by $insert function here$ which has the benefit of handling values of 0.
-Lastly, an inverse normal tranformation was considered.
-The inverse normal transformation is a way of transforming the sample distribution of a continuous variable to make it appear more normally distributed by matching the normalized rank of the trait to a quantile in a normal distribution using the following formula $insert formula here$.
-Multiple logistic regression models were performed using data with each respective transformation and compared.
-It was found that the model with inverse normally transformed distance predictors not only out-performed the other transformation but also out-performed a model with no transformation at all.
+Variable reduction techniques generally fall into one of three main categories: filter methods, wrapper methods, or embedded methods.
+Filter methods are generally used as a preprocessing step.
+The selection of features is independent of any machine learning algorithms.
+Instead, features are selected on the basis of their scores in various statistical tests for their correlation with the outcome variable.
+In wrapper methods, we try to use a subset of features and train a model using them.
+Based on the inferences drawn from the previous model, we decide to add or remove features.
+Embedded methods combine the qualities of filter and wrapper methods by implementing algorithms that have their own built-in feature selection methods.
 
-### Classification Models
+In this paper, we considered one technique from each group.
+For a filter method, we performed nonparametric two-sample Kolmogorov–Smirnov tests to assess how different the underlying distributions of a respective genomic element, for each predictor type, were between bins with and with a TAD boundary located inside it.
+The predictors were sorted according the p-value provided from the test.
+To determine the suitable number of features to reduce to, we plotted the performance of random forest models when iteratively including a new feature (up to the first 20).
+For a wrapper method, we performed forward selection.
+Forward selection is an iterative procedure in which began with an intercept only logistic regression model.
+At each step a feature is added, defined by a particular predictor type, and the AIC of the model is recorded.
+The method continues as long as there is a suitable reduction in AIC.
+Lastly, for an embedded method, we performed LASSO regularized regression.
+The LASSO regression is a penalization technique that uses L1-norm regularization in logistic regression.
+Here, the coefficients of irrelevant features are reduced to 0.
+The subsequent features are chosen for downstream modelling.
 
-Therefore, the final data used for quantifying the association between each functional genomic element and TAD boundary formation was one that had been balanced using multiple iterations of random under-sampling, incorporated both overlapped and distance predictors, and normalized using an inverse normal transformation.
-Likewise, prior to model fitting, the predictors were standardized in order to compare magnitudes of the subsequent beta coefficients as a measure of variable importance.
-We then performed a wide variety of classification algorithms to determine which genomic elements were most predictive of TAD boundaries.
-The models included a multiple logistic regression, a multiple logistic regression with both LASSO and Elastic-Net regularization, a random forest, a gradient boosting machine, a support vector machine, and a naiive bayes model.
-For each model, 10-fold cross validation was performed to tune for any neccessary paramenters.
-Model performance was compared using F1-scores, MCCs, and AUROCs.
-The alpha level of significance was set at 0.05.
-All statistical analyses was performed in R version 3.4.2.
+To address the class imbalance problem we evaluated four different resampling techniques (in addition to no sampling).
+For each resampling technique, the majority class is defined as the set of genomic bins that did not include a TAD boundary, while the minority class is defined as the set of bins that included a TAD boundary.
+The techniques included no sampling, random under-sampling, random over-sampling, SMOTE, and K-Medoids and are disussed in detail below:
+
+1. No Sampling: The full dimension of the training set was used.
+
+2.
+Random Under-Sampling (RUS): All data points (bins) from the minority class (bins with TAD boundaries) of the training set were used.
+Data from the majority class (bins without TAD boundaries) are randomly sampled to match the number of minority class instances.
+We considered 50 interations, each time randomly sampling from the majority class (without replacement) and performed a separate model.
+Performance metrics were aggregated by taking the average across all iterations.
+
+3.
+Random Over-Sampling (ROS): All data points from the majority class of the training set were used.
+Data from the minority class was randomly sampled (with replacement) to match the size of the majority class instances.
+Similar to the random under-sampling, we considered 50 iterations and aggregated the results by taking the average.
+
+4.
+SMOTE (Synthetic Minority Over-Sampling Technique): The method combines both random under-sampling and random over-sampling by creating synthetic observations.
+The SMOTE algorithm was implemented in R through the DmWR package.
+The user is able to specify the parameters that control the percent under- and over-sampling.
+Specific details of the SMOTE algorithm can be found in Chawla et al.
+For the purposes of this study, the parameters of the algorithm were chosen to create perfectly balanced classes.
+
+5.
+K-Medoids: This is an unsupervised clustering algorithm.
+The set of majority classes is isolated and the clustering algorthm is performed.
+The cluster centers are represented by actual data points.
+The set of cluster centers are chosen to match the set of minority classes.
+The final resampled training set is composed of the set of minority classes and the set of cluster centers from the majority classes.
+
+The graphical display of the disparity in classes across the different class-balancing techniques is provided is Figure X.
+Using set notation the formulation of the ensemble framework can be defined as follows:
+
+Set of Predictor Types:
+
+P = {OC, OP, Distance}
+
+Set of Variable Reduction Techniques:
+
+V = {KS-Test, Forward Selection (AIC), LASSO}
+
+Set of Class-Balancing Methods:
+
+C = {None, RUS, ROS, SMOTE, K-Medoids}
+
+Therefore, given domain data at a specific resolution, a system produced from the ensemble framework is defined as follows:
+
+E = {p, v, c}, where $p \in P$, $v \in V$, and $c \in C$
+
+Once a system was defined, a random forest algorithm was performed using 10-fold cross-validation to reduce bias.
+Letting $|X|$ denote the cardinality of each set, then for each domain data, we evaluated $|P| \times |V| \times |C|$ different ensemble systems in this paper.
 
@@
 
-A total of 9048 topologically associating domains and their genomic locations were obtained for the GM12878 cell line for chromosomes 1 through 22.
-The median width of TADs was found to be 18.5 kb (IQR: 11.5kb - 33.0kb).
-The start and end coordiantes of the TADs were translated into a vector of boundary points.
-There were 1454 (16%) TADs that shared at least one coordinate (start, end, or both) with another TAD.
-In this case the unique boundary point demarcating two adjacent TADs was considered.
-The genome was binned at 10 kb interval, resulting in a total of 536396 bins.
-A total of 536396 genomic bins of 10 kb width were created.
-After flanking the TAD boundary points on either side by 5 kb, it was found that 31820 (5.9%) bins contained a flanked TAD boundary.
-We investigated a total of 68 genomic features, 12 (18%) of which were removed because they were assessed as having near-zero variance.
-Table X presents a full list of the genomic features in addition to the metrics and indicator corresponding to whether or not the feature was to be removed.
+In this section we provide the details of the comprehensive experiments performed in order to assess each ensemble system.
+For the task of predicting TAD boundaries using functional genomic elements, we used 5 class balancing techniques, and for each balancing technique we used 3 predictor types and 3 variable reduction techniques.
+We evaluated each ensemble system using 10-fold cross-validated random forest models.
+Thus, we generated 45 (=5x3x3) separate models.
 
-## Balancing Classes Improves Performance
+After binning the genome at 5kb, [[25kb, 50kb, and 100kb]] there were a total of X [[, X, X, and X]] genomic bins respectively.
+Table X provides the data distributions of the different classes across each of the balancing techniques.
+We see that each class balancing technique considered resulted in perfectly balanced classes.
 
-It was found that the multiple logistic regression models utilizing random over and under-sampling out-performed the other techniques and were comparatively similar with F1 scores of 0.636 and 0.637 respectively.
-The under-technique was evaluated over 13 iterations, while the over-sampling technique took far more iterations for the cumulative mean F1 score to converge, X to be exact.
-Given that and the fact that the under-sampling technique uses significantly less data than the over-sampling, while still performing at the same level, it was concluded that this was the best balancing technique and used in further analyses.
+We implemented 3 types of variable reduction techniques that fell into 1 of 3 categories: filter methods, wrapper methods, or embedded methods.
+For the filter method, we performed nonparametric KS-tests for each predictor in the feature space.
+P-values of the tests were sorted into increasing order.
+Figure X presents AUCs and F1 scores results by iteratively adding 1 predictor at a time according to the sorted p-values across each resampling technique.
+We see that the performances begin to stabilize after the inclusion of the top 15 most significant features.
+Thus, the top 15 features were selected when applying this filter method for all downstream analyses.
 
-## Incorporating Distance Predictors Improves Performance
+Table X presents the complete results comparing each ensemble system in terms of accuracy, AUC, F1 score, and MCC.
+We see that the inclusion of distance type predictors significantly improved model performance compared to the other two overlap types.
+This improvement was apparant across all class balancing techniques.
+Furthermore, the improvement was irrespective of which variable reduction technique was chosen.
+Performance metrics remained relatively constant within each model with a specific predictor type and resampling technique, regardless of the variable reduction technique chosen.
+With respect to the class balancing technique, when isolated to models using distance type predictors, it was found that X preformed best.
 
-The multiple logistic regression model with only distance predictors, evaluated on multiple iterations of random under-sampling was found to improve model performance from 0.637 (using only overlap predictors) to 0.747.
-Furthermore, the multiple logistic regression model with both types of predictors further improved model performance by raising the F1 score to 0.753.
-This suggested that the distance predictors were more representative of the association between the genomic elements and TAD boundaries.
-However, on a genomic scale, distances from the bins to the nearest region defined by a respective genomic element were highly right skewed.
-We evaluated three tranformations in order to normalize the distance predictors and improve model performance.
-Out of the three normalization techniques, the multiple logistic regression model with an inverse normal transformation on the distance predictors was found to perform the best with an F1 score of 0.747.
-
-##
+Figure X presents the variable importance plot including the top X most predictive functional genomic elements associated with the formation of TAD boundaries. At the top we see X, X, and X
+.
+.
+.
 

### 2018-11-14 ToDo.Rmd
updates

@@
 * investigate svm & neural networks & naiive bayes
+
+## 10/03/18
+
+* pose additional question, does doing multiple iterations of sampling improve model performance
+* can we prove that the performance (f1 score & variables selected) is stable over multiple iterations
+
+## 10/05/18
+
+* does random forest sufffer on imbalanced data?
+* use maximum instead of mean when determining cutoff of iterations
+* find out if there is a convergence algorthim to decide point of convergence
+   + look at 0.001 or 0.0001 for now
+* look at AIC/BIC for potential cutoff
+* run anova test to determine if two models are different at different iterations
+* look into using c-index as performance metric
+* create heatmap of variable importance from different models
+
+## 11/09/18
+
+*stick with elastic net (compare with all others)
+*look at correlations

### 2018-11-14 Manuscript/manuscript.Rmd
updated manuscript

@@
 
-# INTRODUCTION
+#INTRODUCTION
 
@@
 Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD (Symmons et al.).
-This suggests that the boundaries of TADs may play a role in restricting the function of elements such as enhancers, thereby impacting the transcription of genes.
-Furthermore, changing the 3D structure of the DNA and distrupting these domains can lead to adverse outcomes and diseases like cancer.
+This suggests that the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
+Furthermore, changing the 3D structure of the DNA, causing disruptions in these domains can lead to adverse outcomes and diseases like cancer.
 Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.
@@
 The mechanisms underlying the formation of TADs are a complex and active area of research.
-Recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangement of higher-order chromatin architecture (Phillips-Cremins et al).
+Recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangements of higher-order chromatin architecture (Phillips-Cremins et al).
 Insulators are multi-faceted regulatory sequences that moderate a variety of genomic processes including activation, repression, and enhancer blocking.
-Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long range chromatin contacts (Zuin et al.).
-Other regulatory elements like DNase I hypersensitive sites, particular histone modifications, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions (Hong et al).
+Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long-range chromatin contacts (Zuin et al.).
+Other regulatory elements like DNase I hypersensitive sites, particular histone modifications [mention more specifically; include reference], and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions (Hong et al).
 These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
-The distinct patterns of some of these different proteins and functional elements point toward the opportunity of computational approaches in predicting which epigenomic features are most predictive of the development of TAD boundaries.
+The distinct patterns of some of these different proteins and functional elements point toward the opportunity of using computational approaches in identifying which epigenomic features are most predictive of the development of TAD boundaries.
 This will allow us to better understand what leads to their formation.
 
-Most accepted methods for predicting TAD boundaries consider performing a classification algorithm by binning the genome and labeling the bins as either containing a TAD boundary or not.
+Most accepted methods for predicting TAD boundaries consider performing a classification algorithm by binning the genome into equal-sized bins and labeling them as either containing a TAD boundary or not.
 However, a pervasive issue becomes the introduction of highly imbalanced classes.
@@
 Therefore, the minority class of genomic bins with TAD boundaries in them becomes proportionally smaller than that of the majority class of genomic bins with no TAD boundaries.
-It is commonly agreed that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate (Estabrooks et al).
-Furthermore, it is unclear what sized bins best improves predictive performance or even if the results are stable across differently sized genomic bins.
+It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate (Estabrooks et al).
+However, a clear method for creating balanced classes remains evasive and largely dependent on the problem at hand.
+For that reason we evaluated 3 widely accepted class balancing techniques, in addition to no balancing.
+They included random under-sampling, random over-sampling, and synthetic minority over-sampling technique (SMOTE).
+
+Model performance is also contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
+This will also affect the size of the genomic bins used in model construction.
+A larger resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
+This will contribute to smaller sample sizes and could effect predictive performances.
 
@@
 However, these distance characteristics offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
+In this paper we considered two types of variable reduction techniques, an L1 norm penalized regularization (LASSO) and a combination of both an L1 and L2 norm penalized regularizations (Elastic-Net).
+Due to the increasingly large amounts of functional genomic elements to consider, it is a popular approach in genomic studies to use variable reduction techniques to reduce the noise induced by noninformative predictors and increase computational efficiency.
+While both regularization techniques have merit, LASSO’s inability to handle correlated predictors poses a problem when identifying which element are most predictive of TAD boundaries.
+The elastic-net, however, is better suited in a situation where multiple genomic elements colocalize around the same TAD boundaries, and could be better suited for this type of alaysis.
 
 In this study we have developed an ensemble framework that aims to address and compare a variety of data irregularities and characteristics that are associated with the prediction of TAD boundaries.
-We examined the inclusion of three different predictor types as the feature space for predictive modelling.
-We also examined four resampling techniques aimed at improving class imbalance.
-Lastly, we examined the effect of three separate variable reduction techniques on model performance.
-Random forest classification algorithms were performed to investigate which functional genomic features were most associated with the formaton of TAD boundaries.
+We evaluated domain data obtained from four different resolution contact matrices for the GM12878 cell line including 5kb, 25kb, 50kb, and 100kb.
+For each resolution, we examined the inclusion of three different predictor types as the feature space for downstream modelling.
+We coupled each predictor type with two separate variable reduction techniques.
+Lastly, we performed a series of three different re-sampling techniques aimed at created balanced classes.
+Random forest classification algorithms were performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the formation of TAD boundaries.
 Model performance was evaluated based on a total of four metrics which included test accuracy, area under the ROC curve (AUC), F1 score, and Matthew's Correlation Coefficient (MCC).
 
-[Insert last paragram for introduction]
+#METHODS
 
-# METHODS
+##DOMAIN DATA
 
-## DOMAIN DATA
-
-Publicly available topologically associating domain data was obtained from GEO with accession GSE53525 for the GM12878 cell line (Rao et.
+Publicly available topologically associating domain data for the GM12878 cell line was obtained using the arrowhead algorithm from the Juicer toolbox (Rao et.
 al).
@@
 Next, the boundary coordinates were flanked on either side by a unit corresponding to the resolution of the particular domain data.
-Again siting the domain data obtained from a 5kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 5kb.
-Again, the same process was repeated for the other three resolutions.
+Again, siting the domain data obtained from a 5kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 5kb for a total width around each boundary point of 10kb.
+The same process was repeated for the other three resolutions.
 A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
@@
 
-## GENOMIC ANNOTATIONS
+##GENOMIC ANNOTATIONS
 
-Annotation data, in the form of functional genomic element, from ChIP-seq experiments was obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium.
-The annotations consisted of a variety of different chromatin states using hidden markov models, histone marks, and DNase I hypersensitive sites.
-Each annotation is represented by their location throughout the genome via chromosomal coordinates.
-Using each genomic element we created three types of predictors that were used as features in downstream modelling.
+Annotation data, in the form of functional genomic elements from ChIP-seq experiments were obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium.
+The annotations consisted of a variety of different chromatin states, histone marks, and DNase I hypersensitive sites.
+Each annotation was represented by their location throughout the genome via chromosomal coordinates.
+An example of a specific annotation, which is labeled as a functional genomic element, is presented in Figure 1.
+It is represented by the green segments that overlap with the genomic bins.
 
-## Ensemble Framework
+Using each genomic element, and their relationship with the genomic bins, we created three types of predictors that were used as features in downstream modelling.
+Figure 2 presents an illustration of each type of predictor that was considered.
+The predictors consisted of two different types of overlaps, and a distance type and are described in detail below:
 
-Figure 2 details the ensemble system proposed and evaluated in this study.
-For each predictor type chosen, the data, composed of majority and minority classes, was split into a 7:3 ratio of training to testing sets.
-For the trainig set, a variable reduction technique was performed.
-The feature space was reduced and a resampling technique was performed.
+   1.	Overlap Counts (OC): For each genomic bin, the total number of overlapped regions between a functional genomic element and a bin was calculated.
+This was defined as the overlap counts (OC) and is illustrated in the left part of Figure 2.
+From the first bin, in the highlighted region, we see that there are two regions defined by the particular functional genomic element that overlap within the same bin.
+Therefore the OC for that bin, given that feature, was determined to be 2.
+Bins that did not overlap with a feature were assigned a value of zero.
+
+   2.	Overlap Percent (OP): For each genomic bin, the percent overlap between regions defined by a particular functional element and a bin was calculated.
+From the middle region of Figure 2, the feature width was defined as the number of base pairs that overlapped with the genomic bin.
+The percent was then calculated by dividing the feature width with the bin width.
+If multiple overlaps existed, the feature width was defined as the sum of the total number of base pairs that overlapped with a particular bin.
+Note that the bin width remained constant for a given resolution (either 5kb, 25kb, 50kb, or 100kb).
+Similar to the OC predictor type, bins with no overlaps were given to be zero.
+
+   3.	Distance: For each genomic bin, the distance (in base pairs) from the center of the bin to the center of the nearest region of a respective functional element was calculated.
+The distance predictors were then normalized using a log base 2 transformation prior to modelling.
+
+##ENSEMBLE FRAMEWORK
+
+After choosing one of the aforementioned data resolutions, predictor types, and variable reduction techniques, we then evaluated three re-sampling techniques used to create balanced classes.
+For each resampling technique, the majority class is defined as the set of genomic bins that did not include a TAD boundary, while the minority class is defined as the set of bins that included a TAD boundary.
+The following details the re-sampling techniques considered in this paper:
+
+   1.	No Sampling: All of the data points from the majority and minority class of the training set were used.
+
+   2.	Random Under-Sampling: All of the minority classes from the training set were used.
+A random set without replacement from the majority classes of the training set were used to match the number of minority samples.
+In this paper we performed 50 iterations of random under-sampling.
+At each iteration a random forest classification algorithm was performed.
+Performance metrics were aggregated by taking the average across all of the iterations.
+
+   3.	Random Over-Sampling: All of the majority classes from the training set were used.
+A random set with replacement from the minority classes of the training set were used to match the number of majority samples.
+Similar to the under-sampling technique, 50 iterations were performed and results were aggregated by taking the average across iterations.
+
+   4.	SMOTE (Synthetic Minority Over-Sampling Technique): This method incorporated both random under- and over-sampling.
+Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class.
+The SMOTE algorithm was devised by Chawla et al and stored in the DMwR package, available in R.
+The user is able to specify the parameters denoting the percent of over- and under-sampling from the two classes.
+This allows the user to control the proportion of disbalance in the data.
+For the purposes of this paper, we used SMOTE to create perfectly balanced data.
+However further research would be needed to see if varying the proportion of class disbalance could improve predictive performance.
+
+Figure 3 details the ensemble framework proposed and evaluated in this study.
+For each resolution and predictor type chosen, the data, composed of majority and minority classes, was split into a 7:3 ratio of training to testing sets.
+For the training set, a variable reduction technique was performed.
+The feature space was reduced and a resampling technique was applied.
 A classification algorithm in the form of a random forest was performed and validated using the test set.
+10-fold cross validation was used such that each sub-training set was partitioned into a fixed 9:1 ratio.
+The model was performed and assessed using the holdout set to get more stable performance metrics and reduce bias.
 
-A total of three increasingly refined predictor types where used to describe the relationship between TAD boundaries and each function genomic element of interest.
-Two different overlap types and a distance type were considered.
-Figure 3 presents an illustration of each type and is detailed below:
+Using set notation the formulation of the ensemble framework can be defined as follows:
 
-1.
-Overlap Counts (OC): For each genomic bin, a total count of each overlapped region, defined by a functional genomic element, with a bin was calculated.
-If no regions overlapped with a bin, then the predictor was assigned as 0.
+Set of different resolutions:
 
-2.
-Overlap Percent (OP): For each genomic bin, the percent of overlap between a bin and a region was calculated as the ratio of feature width (in base pairs) and the total width of each bin.
-Here, the feature width was defined as the number of base pairs that overlapped between a bin and an elemental region.
-Note, that the denominator of this ratio was given to be that same for each respective domain data used.
-That is, for the 5kb resolution domain data, the total width of each bin was 5kb.
-
-3. Distance: For each genomic bin, the distance (in base pairs) from the center of the bin to the center of the nearest region of a respective functional genomic elemnt was calculated.
-
-Variable reduction techniques generally fall into one of three main categories: filter methods, wrapper methods, or embedded methods.
-Filter methods are generally used as a preprocessing step.
-The selection of features is independent of any machine learning algorithms.
-Instead, features are selected on the basis of their scores in various statistical tests for their correlation with the outcome variable.
-In wrapper methods, we try to use a subset of features and train a model using them.
-Based on the inferences drawn from the previous model, we decide to add or remove features.
-Embedded methods combine the qualities of filter and wrapper methods by implementing algorithms that have their own built-in feature selection methods.
-
-In this paper, we considered one technique from each group.
-For a filter method, we performed nonparametric two-sample Kolmogorov–Smirnov tests to assess how different the underlying distributions of a respective genomic element, for each predictor type, were between bins with and with a TAD boundary located inside it.
-The predictors were sorted according the p-value provided from the test.
-To determine the suitable number of features to reduce to, we plotted the performance of random forest models when iteratively including a new feature (up to the first 20).
-For a wrapper method, we performed forward selection.
-Forward selection is an iterative procedure in which began with an intercept only logistic regression model.
-At each step a feature is added, defined by a particular predictor type, and the AIC of the model is recorded.
-The method continues as long as there is a suitable reduction in AIC.
-Lastly, for an embedded method, we performed LASSO regularized regression.
-The LASSO regression is a penalization technique that uses L1-norm regularization in logistic regression.
-Here, the coefficients of irrelevant features are reduced to 0.
-The subsequent features are chosen for downstream modelling.
-
-To address the class imbalance problem we evaluated four different resampling techniques (in addition to no sampling).
-For each resampling technique, the majority class is defined as the set of genomic bins that did not include a TAD boundary, while the minority class is defined as the set of bins that included a TAD boundary.
-The techniques included no sampling, random under-sampling, random over-sampling, SMOTE, and K-Medoids and are disussed in detail below:
-
-1. No Sampling: The full dimension of the training set was used.
-
-2.
-Random Under-Sampling (RUS): All data points (bins) from the minority class (bins with TAD boundaries) of the training set were used.
-Data from the majority class (bins without TAD boundaries) are randomly sampled to match the number of minority class instances.
-We considered 50 interations, each time randomly sampling from the majority class (without replacement) and performed a separate model.
-Performance metrics were aggregated by taking the average across all iterations.
-
-3.
-Random Over-Sampling (ROS): All data points from the majority class of the training set were used.
-Data from the minority class was randomly sampled (with replacement) to match the size of the majority class instances.
-Similar to the random under-sampling, we considered 50 iterations and aggregated the results by taking the average.
-
-4.
-SMOTE (Synthetic Minority Over-Sampling Technique): The method combines both random under-sampling and random over-sampling by creating synthetic observations.
-The SMOTE algorithm was implemented in R through the DmWR package.
-The user is able to specify the parameters that control the percent under- and over-sampling.
-Specific details of the SMOTE algorithm can be found in Chawla et al.
-For the purposes of this study, the parameters of the algorithm were chosen to create perfectly balanced classes.
-
-5.
-K-Medoids: This is an unsupervised clustering algorithm.
-The set of majority classes is isolated and the clustering algorthm is performed.
-The cluster centers are represented by actual data points.
-The set of cluster centers are chosen to match the set of minority classes.
-The final resampled training set is composed of the set of minority classes and the set of cluster centers from the majority classes.
-
-The graphical display of the disparity in classes across the different class-balancing techniques is provided is Figure X.
-Using set notation the formulation of the ensemble framework can be defined as follows:
+R = {5kb, 25kb, 50kb, 100kb}
 
@@
 
-V = {KS-Test, Forward Selection (AIC), LASSO}
+V = {LASSO, Elastic-Net}
 
@@
 
-C = {None, RUS, ROS, SMOTE, K-Medoids}
+C = {None, RUS, ROS, SMOTE}
 
-Therefore, given domain data at a specific resolution, a system produced from the ensemble framework is defined as follows:
+Therefore, a system produced from the ensemble framework is defined as follows:
 
-E = {p, v, c}, where $p \in P$, $v \in V$, and $c \in C$
+E = {r, p, v, c}, where r in R, p in P, v in V, and c in C.
 
-Once a system was defined, a random forest algorithm was performed using 10-fold cross-validation to reduce bias.
-Letting $|X|$ denote the cardinality of each set, then for each domain data, we evaluated $|P| \times |V| \times |C|$ different ensemble systems in this paper.
+Once a system was defined, a random forest algorithm was performed. Letting |X| denote the cardinality of each set, then we evaluated |R| x |P| x |V| x |C| different ensemble systems in this paper.
 
-# RESULTS
+#RESULTS
 
 In this section we provide the details of the comprehensive experiments performed in order to assess each ensemble system.
-For the task of predicting TAD boundaries using functional genomic elements, we used 5 class balancing techniques, and for each balancing technique we used 3 predictor types and 3 variable reduction techniques.
+For the task of predicting TAD boundaries using functional genomic elements, we evaluated 4 domain data sets obtained using the arrowhead algorithm for the Juicer toolbox developed by Rao et al, 3 predictor types, 2 variable reduction techniques, and 4 class balancing techniques.
 We evaluated each ensemble system using 10-fold cross-validated random forest models.
-Thus, we generated 45 (=5x3x3) separate models.
+Thus, we generated 96 (=4x3x2x4) separate models.
 
-After binning the genome at 5kb, [[25kb, 50kb, and 100kb]] there were a total of X [[, X, X, and X]] genomic bins respectively.
-Table X provides the data distributions of the different classes across each of the balancing techniques.
-We see that each class balancing technique considered resulted in perfectly balanced classes.
+After binning the genome at 5kb, 25kb, 50kb, and 10kb intervals there were a total of 44948, 9042, 4541, and 2279 genomic bins created respectively.
+Figure 4 illustrates the class imbalance problem present in each data resolution.
+Likewise, we see the apparent decrease in data points (bins) as resolution increases.
+Furthermore, Table 1 shows that for each class balancing technique, perfectly balanced classes were created.
 
-We implemented 3 types of variable reduction techniques that fell into 1 of 3 categories: filter methods, wrapper methods, or embedded methods.
-For the filter method, we performed nonparametric KS-tests for each predictor in the feature space.
-P-values of the tests were sorted into increasing order.
-Figure X presents AUCs and F1 scores results by iteratively adding 1 predictor at a time according to the sorted p-values across each resampling technique.
-We see that the performances begin to stabilize after the inclusion of the top 15 most significant features.
-Thus, the top 15 features were selected when applying this filter method for all downstream analyses.
-
-Table X presents the complete results comparing each ensemble system in terms of accuracy, AUC, F1 score, and MCC.
-We see that the inclusion of distance type predictors significantly improved model performance compared to the other two overlap types.
-This improvement was apparant across all class balancing techniques.
-Furthermore, the improvement was irrespective of which variable reduction technique was chosen.
-Performance metrics remained relatively constant within each model with a specific predictor type and resampling technique, regardless of the variable reduction technique chosen.
-With respect to the class balancing technique, when isolated to models using distance type predictors, it was found that X preformed best.
-
-Figure X presents the variable importance plot including the top X most predictive functional genomic elements associated with the formation of TAD boundaries. At the top we see X, X, and X
-.
-.
-.
-
-# DISCUSSION
+##ENSEMBLE COMPARISONS

### 2018-11-14 Manuscript/manuscript.Rmd
updated manuscript

@@
 Model performance was evaluated based on a total of four metrics which included test accuracy, area under the ROC curve (AUC), F1 score, and Matthew's Correlation Coefficient (MCC).
+[mention reasons for including 4 metrics]
 
@@
 ##ENSEMBLE COMPARISONS
+
+###DISTANCE PREDICTORS IMPROVE MODEL PERFORMANCE IN ALL RESOLUTIONS
+
+Figures 4-7 present the results across all of the ensemble systems for each resolution of domain data.
+Focusing on the top row in each of Figure 4-7, indicating no balancing, we see that the model using distance predictors, represented by the blue bars, outperformed models using the other two predictor types.
+However, the disparity become less evident as the resolution increased.
+In each of the 4 figures we see that the F1-score and MCC metrics were noticeably lower than the accuracy and AUC.
+This highlights the problems associated with applying predictive models to unbalanced data.
+
+###CLASS BALANCING IMPROVES MODEL PERFORMANCE IN ALL RESOLUTIONS
+
+Moving down the rows in each of Figures 4-7 we see that model performance was markedly improved among the F1-scores and MCCs after creating balanced classes compared to the results using no re-sampling.
+For each of the resolutions, we see that random under-sampling and SMOTE re-sampling techniques performed very similarly, while random over-sampling performed poorly in comparison.
+Furthermore, we see that the elastic-net reduction technique outperformed the LASSO.
+Although, the disparity became less evident as the resolution increased.
+
+###PERFORMANCES BECOME INVARIANT AS RESOLUTION INCREASES

### 2018-11-14 Manuscript/manuscript.Rmd
updated manuscript

@@
 
+##ENSEMBLE COMPARISONS
+
 In this section we provide the details of the comprehensive experiments performed in order to assess each ensemble system.
@@
 Furthermore, Table 1 shows that for each class balancing technique, perfectly balanced classes were created.
-
-##ENSEMBLE COMPARISONS
 
@@
 Although, the disparity became less evident as the resolution increased.
+Specific ensemble results can be found in Supplement Tables X-X.
 
 ###PERFORMANCES BECOME INVARIANT AS RESOLUTION INCREASES
+
+Figure 8 compares the results of random forest models using distance-type predictors, with elastic-net regularization, over 50 iterations of random under-sampling, across each domain data resolution.
+We see that the results for F1-scores are relatively stable between 5kb, 25kb, and 50kb resolutions with a sharp decrease for the 100kb resolution.
+Furthermore, the decrease in performance is more evident and steady across accuracy, AUC, and MCC metrics.
+
+To identify the functional genomic elements that were most predictive of TAD boundaries, we analyzed the variable importance produced by each random forest algorithm.
+Figure 9 presents the scaled importance plots of the top 15 most predictive genomic elements for each resolution.
+We see that for the 5kb resolution, the most predictive elements include insulator proteins, DNase hypersensitive sites, the transcription factor CTCF, as well as histone modifications H3k9ac, H2az, and H3k4me2.
+These results align with what is seen in the literature.
+Although, the insulator protein is featured as a top predictor in 2 of the other 3 resolutions, the rest of the predictors are less consistent among each other and less in agreement with the literature.
+The results from Figure 8 and 9 confirm that the model results appear to degrade as resolution increases with respect to both prediction and the identification of genomic elements associated with TAD boundaries.

### 2018-11-19 GM12878/Counts_vs_Widths/broad.R
removed code

@@ -1,197 +1,0 @@
-#Model filtering
-
-#Loading Libraries
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-# Creating Response Vector Y
-
-## Reading in TAD data
-
-domains <- read.table("/home/stilianoudakisc/TAD_data_analysis/GM12878/arrowhead_data.txt", header=T)
-domains <- domains[,1:3]
-head(domains)
-dim(domains) #9274    3
-
-#removing chrX from boundary data
-domains <- domains[-which(domains$Chromosome=="chrX"),]
-
-#creating granges object out of tad boundary data
-
-#concatenating boundary coordinates into one long vector
-coords <- domains
-colnames(coords)[2:3] <- c("coordinate", "coordinate")
-coords <- rbind.data.frame(coords[,c(1,2)],coords[,c(1,3)])
-coords$Chromosome <- as.character(coords$Chromosome)
-
-#sorting by chromosome and coordinate
-coords <- coords[order(as.numeric(substr(coords$Chromosome,4,5)), coords$coordinate, decreasing = FALSE),]
-
-#remove duplicates for coordinates that are conjoined
-coords <- coords[!duplicated(coords),]
-dim(coords) #16770     2
-
-coords$lagchrom <- lag(coords$Chromosome)
-coords$lagchrom[which(coords$Chromosome!=coords$lagchrom)] <- NA
-coords$lagcoord <- lag(coords$coordinate)
-coords$lagcoord[which(is.na(coords$lagchrom))] <- NA
-
-bounds <- GRanges(seqnames=coords$Chromosome, ranges=IRanges(start=coords$coordinate, width=1))
-bounds_f <- flank(bounds, width=5000, both=TRUE)
-
-#saving data
-#saveRDS(bounds, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds.rds")
-#saveRDS(bounds_f, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds_f.rds")
-
-
-## Reading in binned genome in the form of contact matrix at 10kb resolution
-
[…]

### 2018-11-19 GM12878/Counts_vs_Widths/combined.R

@@ -1,198 +1,0 @@
-#Model filtering
-
-#Loading Libraries
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-# Creating Response Vector Y
-
-## Reading in TAD data
-
-domains <- read.table("/home/stilianoudakisc/TAD_data_analysis/GM12878/arrowhead_data.txt", header=T)
-domains <- domains[,1:3]
-head(domains)
-dim(domains) #9274    3
-
-#removing chrX from boundary data
-domains <- domains[-which(domains$Chromosome=="chrX"),]
-
-#creating granges object out of tad boundary data
-
-#concatenating boundary coordinates into one long vector
-coords <- domains
-colnames(coords)[2:3] <- c("coordinate", "coordinate")
-coords <- rbind.data.frame(coords[,c(1,2)],coords[,c(1,3)])
-coords$Chromosome <- as.character(coords$Chromosome)
-
-#sorting by chromosome and coordinate
-coords <- coords[order(as.numeric(substr(coords$Chromosome,4,5)), coords$coordinate, decreasing = FALSE),]
-
-#remove duplicates for coordinates that are conjoined
-coords <- coords[!duplicated(coords),]
-dim(coords) #16770     2
-
-coords$lagchrom <- lag(coords$Chromosome)
-coords$lagchrom[which(coords$Chromosome!=coords$lagchrom)] <- NA
-coords$lagcoord <- lag(coords$coordinate)
-coords$lagcoord[which(is.na(coords$lagchrom))] <- NA
-
-bounds <- GRanges(seqnames=coords$Chromosome, ranges=IRanges(start=coords$coordinate, width=1))
-bounds_f <- flank(bounds, width=5000, both=TRUE)
-
-#saving data
-#saveRDS(bounds, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds.rds")
-#saveRDS(bounds_f, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds_f.rds")
-
-
-## Reading in binned genome in the form of contact matrix at 10kb resolution
-
[…]

### 2018-11-19 GM12878/Counts_vs_Widths/correlations.R

@@ -1,83 +1,0 @@
-ab <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/count_vs_width/ab.rds")
-dgv <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/count_vs_width/dgv.rds")
-gerp <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/count_vs_width/gerp.rds")
-vmr <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/count_vs_width/vmr.rds")
-se <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/count_vs_width/se.rds")
-broad <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/count_vs_width/broad.rds")
-combined <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/count_vs_width/combined.rds")
-dnase <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/count_vs_width/dnase.rds")
-histone <- readRDS("/home/stilianoudakisc/TAD_data_analysis/model_filtering/count_vs_width/histone.rds")
-
-gm12878_5kb <- cbind.data.frame(ab,
-								dgv[,-1],
-								gerp[,-1],
-								vmr[,-1],
-								se[,-1],
-								broad[,-1],
-								combined[,-1],
-								dnase[,-1],
-								histone[,-1])
-								
-dim(gm12878_5kb)
-
-saveRDS(gm12878_5kb, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/count_vs_width/gm12878_5kb.rds")
-
-
-toMatch <- c("dist", "count")
-
-matches <- unique (grep(paste(toMatch,collapse="|"), 
-                        names(gm12878_5kb), value=TRUE))
-matches <- c("y",matches)
-
-
-
-#Calculating correlations between width and count overlap variables
-cordf <- data.frame(Feature = names(gm12878_5kb[,-which(names(gm12878_5kb) %in% matches)]),
[…]

### 2018-11-19 GM12878/Counts_vs_Widths/gerp.R

@@ -1,198 +1,0 @@
-#Model filtering
-
-#Loading Libraries
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-# Creating Response Vector Y
-
-## Reading in TAD data
-
-domains <- read.table("/home/stilianoudakisc/TAD_data_analysis/GM12878/arrowhead_data.txt", header=T)
-domains <- domains[,1:3]
-head(domains)
-dim(domains) #9274    3
-
-#removing chrX from boundary data
-domains <- domains[-which(domains$Chromosome=="chrX"),]
-
-#creating granges object out of tad boundary data
-
-#concatenating boundary coordinates into one long vector
-coords <- domains
-colnames(coords)[2:3] <- c("coordinate", "coordinate")
-coords <- rbind.data.frame(coords[,c(1,2)],coords[,c(1,3)])
-coords$Chromosome <- as.character(coords$Chromosome)
-
-#sorting by chromosome and coordinate
-coords <- coords[order(as.numeric(substr(coords$Chromosome,4,5)), coords$coordinate, decreasing = FALSE),]
-
-#remove duplicates for coordinates that are conjoined
-coords <- coords[!duplicated(coords),]
-dim(coords) #16770     2
-
-coords$lagchrom <- lag(coords$Chromosome)
-coords$lagchrom[which(coords$Chromosome!=coords$lagchrom)] <- NA
-coords$lagcoord <- lag(coords$coordinate)
-coords$lagcoord[which(is.na(coords$lagchrom))] <- NA
-
-bounds <- GRanges(seqnames=coords$Chromosome, ranges=IRanges(start=coords$coordinate, width=1))
-bounds_f <- flank(bounds, width=5000, both=TRUE)
-
-#saving data
-#saveRDS(bounds, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds.rds")
-#saveRDS(bounds_f, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds_f.rds")
-
-
-## Reading in binned genome in the form of contact matrix at 10kb resolution
-
[…]

### 2018-11-19 GM12878/Counts_vs_Widths/histone.R

@@ -1,197 +1,0 @@
-#Model filtering
-
-#Loading Libraries
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-# Creating Response Vector Y
-
-## Reading in TAD data
-
-domains <- read.table("/home/stilianoudakisc/TAD_data_analysis/GM12878/arrowhead_data.txt", header=T)
-domains <- domains[,1:3]
-head(domains)
-dim(domains) #9274    3
-
-#removing chrX from boundary data
-domains <- domains[-which(domains$Chromosome=="chrX"),]
-
-#creating granges object out of tad boundary data
-
-#concatenating boundary coordinates into one long vector
-coords <- domains
-colnames(coords)[2:3] <- c("coordinate", "coordinate")
-coords <- rbind.data.frame(coords[,c(1,2)],coords[,c(1,3)])
-coords$Chromosome <- as.character(coords$Chromosome)
-
-#sorting by chromosome and coordinate
-coords <- coords[order(as.numeric(substr(coords$Chromosome,4,5)), coords$coordinate, decreasing = FALSE),]
-
-#remove duplicates for coordinates that are conjoined
-coords <- coords[!duplicated(coords),]
-dim(coords) #16770     2
-
-coords$lagchrom <- lag(coords$Chromosome)
-coords$lagchrom[which(coords$Chromosome!=coords$lagchrom)] <- NA
-coords$lagcoord <- lag(coords$coordinate)
-coords$lagcoord[which(is.na(coords$lagchrom))] <- NA
-
-bounds <- GRanges(seqnames=coords$Chromosome, ranges=IRanges(start=coords$coordinate, width=1))
-bounds_f <- flank(bounds, width=5000, both=TRUE)
-
-#saving data
-#saveRDS(bounds, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds.rds")
-#saveRDS(bounds_f, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds_f.rds")
-
-
-## Reading in binned genome in the form of contact matrix at 10kb resolution
-
[…]

### 2018-11-19 GM12878/Counts_vs_Widths/se.R

@@ -1,198 +1,0 @@
-#Model filtering
-
-#Loading Libraries
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-# Creating Response Vector Y
-
-## Reading in TAD data
-
-domains <- read.table("/home/stilianoudakisc/TAD_data_analysis/GM12878/arrowhead_data.txt", header=T)
-domains <- domains[,1:3]
-head(domains)
-dim(domains) #9274    3
-
-#removing chrX from boundary data
-domains <- domains[-which(domains$Chromosome=="chrX"),]
-
-#creating granges object out of tad boundary data
-
-#concatenating boundary coordinates into one long vector
-coords <- domains
-colnames(coords)[2:3] <- c("coordinate", "coordinate")
-coords <- rbind.data.frame(coords[,c(1,2)],coords[,c(1,3)])
-coords$Chromosome <- as.character(coords$Chromosome)
-
-#sorting by chromosome and coordinate
-coords <- coords[order(as.numeric(substr(coords$Chromosome,4,5)), coords$coordinate, decreasing = FALSE),]
-
-#remove duplicates for coordinates that are conjoined
-coords <- coords[!duplicated(coords),]
-dim(coords) #16770     2
-
-coords$lagchrom <- lag(coords$Chromosome)
-coords$lagchrom[which(coords$Chromosome!=coords$lagchrom)] <- NA
-coords$lagcoord <- lag(coords$coordinate)
-coords$lagcoord[which(is.na(coords$lagchrom))] <- NA
-
-bounds <- GRanges(seqnames=coords$Chromosome, ranges=IRanges(start=coords$coordinate, width=1))
-bounds_f <- flank(bounds, width=5000, both=TRUE)
-
-#saving data
-#saveRDS(bounds, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds.rds")
-#saveRDS(bounds_f, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds_f.rds")
-
-
-## Reading in binned genome in the form of contact matrix at 10kb resolution
-
[…]

### 2018-11-19 GM12878/Data_Pipeline/01model_filtering_gm12878.R

@@ -1,551 +1,0 @@
-#Model filtering
-
-#Loading Libraries
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-# Creating Response Vector Y
-
-## Reading in TAD data
-
-domains <- read.table("/home/stilianoudakisc/TAD_data_analysis/GM12878/arrowhead_data.txt", header=T)
-domains <- domains[,1:3]
-head(domains)
-dim(domains) #9274    3
-
-#removing chrX from boundary data
-domains <- domains[-which(domains$Chromosome=="chrX"),]
-
-#creating granges object out of tad boundary data
-
-#concatenating boundary coordinates into one long vector
-coords <- domains
-colnames(coords)[2:3] <- c("coordinate", "coordinate")
-coords <- rbind.data.frame(coords[,c(1,2)],coords[,c(1,3)])
-coords$Chromosome <- as.character(coords$Chromosome)
-
-#sorting by chromosome and coordinate
-coords <- coords[order(as.numeric(substr(coords$Chromosome,4,5)), coords$coordinate, decreasing = FALSE),]
-
-#remove duplicates for coordinates that are conjoined
-coords <- coords[!duplicated(coords),]
-dim(coords) #16770     2
-
-coords$lagchrom <- lag(coords$Chromosome)
-coords$lagchrom[which(coords$Chromosome!=coords$lagchrom)] <- NA
-coords$lagcoord <- lag(coords$coordinate)
-coords$lagcoord[which(is.na(coords$lagchrom))] <- NA
-
-bounds <- GRanges(seqnames=coords$Chromosome, ranges=IRanges(start=coords$coordinate, width=1))
-bounds_f <- flank(bounds, width=5000, both=TRUE)
-
-#saving data
-saveRDS(bounds, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds.rds")
-saveRDS(bounds_f, "/home/stilianoudakisc/TAD_data_analysis/model_filtering/bounds_f.rds")
-
-
[…]

### 2018-11-19 GM12878/Data_Pipeline/02.2normalization_log_nostd.R

@@ -1,131 +1,0 @@
-library(caret)
-#library(data.table)
-library(gbm)
-library(pROC)
-library(plyr)
-library(dplyr)
-#library(DMwR)
-library(gridExtra)
-library(ggplot2)
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/comparing_normalization/")
-
-gm12878_5kb_f <- readRDS("gm12878_5kb_f.rds")
-
-						   
-#function for roc curves
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-
-
-########################################################################################
-
-
-#With No log transform and standardization
-
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
-enetlst_lns <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_5kb_f$y=="Yes"))*2)*.3), 
-                                 ncol=1),
-                   fpr <- matrix(nrow=ceiling((length(which(gm12878_5kb_f$y=="Yes"))*2)*.3), 
-                                 ncol=1),
-                   varimp <- matrix(nrow=dim(gm12878_5kb_f)[2]-1,
-                                    ncol=1))
-rownames(enetlst_lns[[3]]) <- colnames(gm12878_5kb_f)[-1]
-
-enetperf_lns <- matrix(nrow = 17, ncol=1)
-rownames(enetperf_lns) <- c("TN",
-                           "FN",
-                           "FP",
-                           "TP",
-                           "Total",
-                           "Sensitivity",
-                           "Specificity",
-                           "Kappa",
-                           "Accuracy",
-                           "Precision",
-                           "FPR",
-                           "FNR",
-                           "FOR",
-                           "NPV",
-                           "MCC",
-                           "F1",
-                           "AUC")
-						   
-data <- gm12878_5kb_f
-
-#split data
-inTrainingSet <- sample(length(data$y),floor(length(data$y)*.7))
-train <- data[inTrainingSet,]
[…]

### 2018-11-19 GM12878/Data_Pipeline/02.4normalization_nolog_nostd.R

@@ -1,132 +1,0 @@
-library(caret)
-#library(data.table)
-library(gbm)
-library(pROC)
-library(plyr)
-library(dplyr)
-#library(DMwR)
-library(gridExtra)
-library(ggplot2)
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/comparing_normalization/")
-
-gm12878_5kb_f <- readRDS("gm12878_5kb_f.rds")
-
-gm12878_5kb_f_nl <- gm12878_5kb_f
-
-cols <- c(grep("dist",colnames(gm12878_5kb_f_nl)))
-gm12878_5kb_f_nl[,cols] <- apply(gm12878_5kb_f_nl[,cols], 2, function(x){2^x})
-
-
-#function for roc curves
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-
-########################################################################################
-
-
-#With No log transform and No standardization
-
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
-enetlst_nlns <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_5kb_f_nl$y=="Yes"))*2)*.3), 
-                                 ncol=1),
-                   fpr <- matrix(nrow=ceiling((length(which(gm12878_5kb_f_nl$y=="Yes"))*2)*.3), 
-                                 ncol=1),
-                   varimp <- matrix(nrow=dim(gm12878_5kb_f_nl)[2]-1,
-                                    ncol=1))
-rownames(enetlst_nlns[[3]]) <- colnames(gm12878_5kb_f_nl)[-1]
-
-enetperf_nlns <- matrix(nrow = 17, ncol=1)
-rownames(enetperf_nlns) <- c("TN",
-                           "FN",
-                           "FP",
-                           "TP",
-                           "Total",
-                           "Sensitivity",
-                           "Specificity",
-                           "Kappa",
-                           "Accuracy",
-                           "Precision",
-                           "FPR",
-                           "FNR",
-                           "FOR",
-                           "NPV",
-                           "MCC",
[…]

### 2018-11-19 GM12878/Data_Pipeline/03.1SMOTE.R

@@ -1,137 +1,0 @@
-#Testing SMOTE combinations with Elastic Net
-
-library(caret)
-library(data.table)
-library(gbm)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(DMwR)
-library(gridExtra)
-
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/evaluating_SMOTE/")
-
-gm12878_5kb_f <- readRDS("gm12878_5kb_f.rds")
-
-# Splitting the data
-set.seed(5228)
-inTrainingSet <- createDataPartition(gm12878_5kb_f$y,p=.7,list=FALSE)
-train <- gm12878_5kb_f[inTrainingSet,]
-test <- gm12878_5kb_f[-inTrainingSet,]
-
-#function for roc curves
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-
-# Establishing tuning/training parameters
-fitControl <- trainControl(method = "cv",
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
-
-#set up grid of alpha and lambda values
-lambda.grid = 10^seq(2,-2,length=100)
-alpha.grid = seq(0,1,length=10)
-srchGrid <- expand.grid(.alpha=alpha.grid, .lambda=lambda.grid)
-
-
-#########################################################################################
-
-
-#SMOTE
-
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
-enetlst_sm <- list(tpr <- matrix(nrow=length(test$y), 
-                                 ncol=4),
-                   fpr <- matrix(nrow=length(test$y), 
-                                 ncol=4),
-                   varimp <- matrix(nrow=dim(gm12878_5kb_f)[2]-1,
-                                    ncol=4))
-rownames(enetlst_sm[[3]]) <- colnames(gm12878_5kb_f)[-1]
-
-enetperf_sm <- matrix(nrow = 17, ncol=4)
-rownames(enetperf_sm) <- c("TN",
-                           "FN",
[…]

### 2018-11-19 GM12878/Data_Pipeline/04.1forward.R

@@ -1,104 +1,0 @@
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/evaluating_variable_reduction/")
-
-gm12878_5kb_f <- readRDS("gm12878_5kb_f.rds")
-
-
-####set number of bootstrap samples
-
-bootsamps = 10
-
-#### function for roc curves
-
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-
-
-#### Establishing tuning/training parameters
-
-fitControl <- trainControl(method = "cv",
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
-						   
-#set up grid of alpha and lambda values
-lambda.grid = 10^seq(2,-2,length=100)
-alpha.grid = seq(0,1,length=10)
-srchGrid <- expand.grid(.alpha=alpha.grid, .lambda=lambda.grid)
-
-
-####create a matrix of row ids that represent the zero class
-
-sampids <- matrix(ncol=bootsamps, 
-                  nrow=length(gm12878_5kb_f$y[which(gm12878_5kb_f$y=="Yes")]))
-				  
-####filling in the sample ids matrix
-
-set.seed(123)
-for(j in 1:bootsamps){
-  sampids[,j] <- sample(which(gm12878_5kb_f$y=="No"),
-                        length(which(gm12878_5kb_f$y=="Yes")),
-                        replace = FALSE)
-}
-
-## Forward
-
-namesmat <- matrix(NA,nrow=dim(gm12878_5kb_f)[2]-1, ncol=bootsamps)
-rownames(namesmat) <- sort(names(gm12878_5kb_f)[-which(names(gm12878_5kb_f)=="y")])
-
-for(i in 1:bootsamps){
-  set.seed(7215)
[…]

### 2018-11-19 GM12878/Data_Pipeline/04.3both.R

@@ -1,105 +1,0 @@
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/evaluating_variable_reduction/")
-
-gm12878_5kb_f <- readRDS("gm12878_5kb_f.rds")
-
-
-####set number of bootstrap samples
-
-bootsamps = 10
-
-#### function for roc curves
-
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-
-
-#### Establishing tuning/training parameters
-
-fitControl <- trainControl(method = "cv",
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
-						   
-#set up grid of alpha and lambda values
-lambda.grid = 10^seq(2,-2,length=100)
-alpha.grid = seq(0,1,length=10)
-srchGrid <- expand.grid(.alpha=alpha.grid, .lambda=lambda.grid)
-
-
-####create a matrix of row ids that represent the zero class
-
-sampids <- matrix(ncol=bootsamps, 
-                  nrow=length(gm12878_5kb_f$y[which(gm12878_5kb_f$y=="Yes")]))
-				  
-####filling in the sample ids matrix
-
-set.seed(123)
-for(j in 1:bootsamps){
-  sampids[,j] <- sample(which(gm12878_5kb_f$y=="No"),
-                        length(which(gm12878_5kb_f$y=="Yes")),
-                        replace = TRUE)
-}
-
-## Stepwise (Both) Selection
-
-namesmat <- matrix(NA,nrow=dim(gm12878_5kb_f)[2]-1, ncol=bootsamps)
-rownames(namesmat) <- sort(names(gm12878_5kb_f)[-which(names(gm12878_5kb_f)=="y")])
-
-for(i in 1:bootsamps){
-  set.seed(7215)
[…]

### 2018-11-19 GM12878/Modeling/Our_Models/enet.R

@@ -1,170 +1,0 @@
-# Loading Libraries
-
-
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-
-
-# Reading in data
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
-
-
-gm12878_5kb_reduced <- readRDS("gm12878_5kb_reduced.rds")
-
-### set number of bootstrap samples
-
-
-bootsamps = 5
-
-#set tuning parameters
-fitControl <- trainControl(method = "cv",
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
-						   
-#set up grid of alpha and lambda values
-lambda.grid = 10^seq(2,-2,length=100)
-alpha.grid = seq(0,1,length=10)
-srchGrid <- expand.grid(.alpha=alpha.grid, .lambda=lambda.grid)
-					   
-#### function for roc curves
-
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-						
-###create a matrix of row ids that represent the zero class
-
-##the number of rows will match the one class
-##the number of columns match the number of bootstrap samples
-
-sampids <- matrix(ncol=bootsamps, 
-                  nrow=length(gm12878_5kb_reduced$y[which(gm12878_5kb_reduced$y=="Yes")]))
-
-
-###filling in the sample ids matrix
-
-set.seed(123)
-for(j in 1:bootsamps){
-  sampids[,j] <- sample(which(gm12878_5kb_reduced$y=="No"),
-                        length(which(gm12878_5kb_reduced$y=="Yes")),
-                        replace = TRUE)
-}
-
-
-
-# Final Models:
-
-# Elastic Net
-
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
[…]

### 2018-11-19 GM12878/Modeling/Our_Models/mlrlasso.R

@@ -1,143 +1,0 @@
-# Loading Libraries
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-# Reading in data
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
-
-
-gm12878_5kb <- readRDS("gm12878_5kb.rds")
-
-#set tuning parameters
-fitControl <- trainControl(method = "cv",
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
-						   
-#set up grid of alpha and lambda values
-lambda.grid = 10^seq(2,-2,length=100)
-alpha.grid = 1
-srchGrid <- expand.grid(.alpha=alpha.grid, .lambda=lambda.grid)					   
-
-#function for roc curves
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-
-
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
-lassolst <- list(tpr <- matrix(nrow=ceiling((length(which(gm12878_5kb$y=="Yes"))*2)*.3), 
-                              ncol=1),
-                fpr <- matrix(nrow=ceiling((length(which(gm12878_5kb$y=="Yes"))*2)*.3), 
-                              ncol=1),
-                varimp <- matrix(nrow=dim(gm12878_5kb)[2]-1,
-                                 ncol=1),
-				coefs <- matrix(nrow=dim(gm12878_5kb)[2]-1,
-									ncol=1))
-rownames(lassolst[[3]]) <- colnames(gm12878_5kb)[-1]
[…]

### 2018-11-19 GM12878/Modeling/Our_Models/rf.R

@@ -1,206 +1,0 @@
-
-# Loading Libraries
-
-
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-
-
-# Reading in data
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/final_models/")
-
-
-
-gm12878_5kb_reduced <- readRDS("gm12878_5kb_reduced.rds")
-
-
-
-# Final Models:
-
-## Random Forest
-
-### set number of bootstrap samples
-
-
-bootsamps = 5
-
-### set tuning parameters
-
-
-fitControl <- trainControl(method = "cv",
-                           number = 10,
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
-						   
-#### function for roc curves
-
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-						
-###create a matrix of row ids that represent the zero class
-
-##the number of rows will match the one class
-##the number of columns match the number of bootstrap samples
-
-sampids <- matrix(ncol=bootsamps, 
-                  nrow=length(gm12878_5kb_reduced$y[which(gm12878_5kb_reduced$y=="Yes")]))
-
-
-###filling in the sample ids matrix
-
-set.seed(123)
-for(j in 1:bootsamps){
-  sampids[,j] <- sample(which(gm12878_5kb_reduced$y=="No"),
-                        length(which(gm12878_5kb_reduced$y=="Yes")),
-                        replace = TRUE)
-}
-
-
-###Performing model
-
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
[…]

### 2018-11-19 K562/Data_Pipeline/01model_filtering_k562.R

@@ -1,527 +1,0 @@
-#Model filtering
-
-#Loading Libraries
-
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-# Creating Response Vector Y
-
-## Reading in TAD data
-
-domains <- read.table("/home/stilianoudakisc/TAD_data_analysis/K562/arrowhead_k562_data.txt", header=T)
-head(domains)
-dim(domains) # 5975    3
-
-#removing chrX from boundary data
-domains <- domains[-which(domains$Chromosome=="chrX"),]
-
-#creating granges object out of tad boundary data
-
-#concatenating boundary coordinates into one long vector
-coords <- domains
-colnames(coords)[2:3] <- c("coordinate", "coordinate")
-coords <- rbind.data.frame(coords[,c(1,2)],coords[,c(1,3)])
-coords$Chromosome <- as.character(coords$Chromosome)
-
-#sorting by chromosome and coordinate
-coords <- coords[order(as.numeric(substr(coords$Chromosome,4,5)), coords$coordinate, decreasing = FALSE),]
-
-#remove duplicates for coordinates that are conjoined
-coords <- coords[!duplicated(coords),]
-dim(coords) #10293     2
-
-coords$lagchrom <- lag(coords$Chromosome)
-coords$lagchrom[which(coords$Chromosome!=coords$lagchrom)] <- NA
-coords$lagcoord <- lag(coords$coordinate)
-coords$lagcoord[which(is.na(coords$lagchrom))] <- NA
-
-bounds <- GRanges(seqnames=coords$Chromosome, ranges=IRanges(start=coords$coordinate, width=1))
-bounds_f <- flank(bounds, width=10000, both=TRUE)
-
-#saving data
-saveRDS(bounds, "/home/stilianoudakisc/TAD_data_analysis/K562/model_filtering/bounds.rds")
-saveRDS(bounds_f, "/home/stilianoudakisc/TAD_data_analysis/K562/model_filtering/bounds_f.rds")
-
-
[…]

### 2018-11-19 K562/Data_Pipeline/02.2log_nostd.R

@@ -1,128 +1,0 @@
-library(caret)
-#library(data.table)
-library(gbm)
-library(pROC)
-library(plyr)
-library(dplyr)
-#library(DMwR)
-library(gridExtra)
-library(ggplot2)
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/K562/comparing_normalization/")
-
-k562_10kb_f <- readRDS("k562_10kb_f.rds")
-
-						   
-#function for roc curves
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-
-
-########################################################################################
-
-
-#With No log transform and standardization
-
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
-enetlst_lns <- list(tpr <- matrix(nrow=ceiling((length(which(k562_10kb_f$y=="Yes"))*2)*.3), 
-                                 ncol=1),
-                   fpr <- matrix(nrow=ceiling((length(which(k562_10kb_f$y=="Yes"))*2)*.3), 
-                                 ncol=1),
-                   varimp <- matrix(nrow=dim(k562_10kb_f)[2]-1,
-                                    ncol=1))
-rownames(enetlst_lns[[3]]) <- colnames(k562_10kb_f)[-1]
-
-enetperf_lns <- matrix(nrow = 17, ncol=1)
-rownames(enetperf_lns) <- c("TN",
-                           "FN",
-                           "FP",
-                           "TP",
-                           "Total",
-                           "Sensitivity",
-                           "Specificity",
-                           "Kappa",
-                           "Accuracy",
-                           "Precision",
-                           "FPR",
-                           "FNR",
-                           "FOR",
-                           "NPV",
-                           "MCC",
-                           "F1",
-                           "AUC")
-						   
-data <- k562_10kb_f
-
-#split data
-inTrainingSet <- sample(length(data$y),floor(length(data$y)*.7))
-train <- data[inTrainingSet,]
-test <- data[-inTrainingSet,]
-
[…]

### 2018-11-19 K562/Data_Pipeline/02.3nolog_std.R

@@ -1,134 +1,0 @@
-library(caret)
-#library(data.table)
-library(gbm)
-library(pROC)
-library(plyr)
-library(dplyr)
-#library(DMwR)
-library(gridExtra)
-library(ggplot2)
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/K562/comparing_normalization/")
-
-k562_10kb_f <- readRDS("k562_10kb_f.rds")
-
-k562_10kb_f_nl <- k562_10kb_f
-
-cols <- c(grep("dist",colnames(k562_10kb_f_nl)))
-k562_10kb_f_nl[,cols] <- apply(k562_10kb_f_nl[,cols], 2, function(x){2^x})
-
-						   
-#function for roc curves
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-
-
-########################################################################################
-
-
-#With No log transform and standardization
-
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
-enetlst_nls <- list(tpr <- matrix(nrow=ceiling((length(which(k562_10kb_f_nl$y=="Yes"))*2)*.3), 
-                                 ncol=1),
-                   fpr <- matrix(nrow=ceiling((length(which(k562_10kb_f_nl$y=="Yes"))*2)*.3), 
-                                 ncol=1),
-                   varimp <- matrix(nrow=dim(k562_10kb_f_nl)[2]-1,
-                                    ncol=1))
-rownames(enetlst_nls[[3]]) <- colnames(k562_10kb_f_nl)[-1]
-
-enetperf_nls <- matrix(nrow = 17, ncol=1)
-rownames(enetperf_nls) <- c("TN",
-                           "FN",
-                           "FP",
-                           "TP",
-                           "Total",
-                           "Sensitivity",
-                           "Specificity",
-                           "Kappa",
-                           "Accuracy",
-                           "Precision",
-                           "FPR",
-                           "FNR",
-                           "FOR",
-                           "NPV",
-                           "MCC",
-                           "F1",
[…]

### 2018-11-19 K562/Data_Pipeline/03.1SMOTE.R

@@ -1,137 +1,0 @@
-#Testing SMOTE combinations with Elastic Net
-
-library(caret)
-library(data.table)
-library(gbm)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(DMwR)
-library(gridExtra)
-
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/K562/evaluating_class_imbalance/")
-
-k562_10kb_f <- readRDS("k562_10kb_f.rds")
-
-# Splitting the data
-set.seed(5228)
-inTrainingSet <- createDataPartition(k562_10kb_f$y,p=.7,list=FALSE)
-train <- k562_10kb_f[inTrainingSet,]
-test <- k562_10kb_f[-inTrainingSet,]
-
-#function for roc curves
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-
-# Establishing tuning/training parameters
-fitControl <- trainControl(method = "cv",
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
-
-#set up grid of alpha and lambda values
-lambda.grid = 10^seq(2,-2,length=100)
-alpha.grid = seq(0,1,length=10)
-srchGrid <- expand.grid(.alpha=alpha.grid, .lambda=lambda.grid)
-
-
-#########################################################################################
-
-
-#SMOTE
-
-#set length of list objects that will be filled in with specificities
-#and sensitivities and aucs and variable importance
-enetlst_sm <- list(tpr <- matrix(nrow=length(test$y), 
-                                 ncol=4),
-                   fpr <- matrix(nrow=length(test$y), 
-                                 ncol=4),
-                   varimp <- matrix(nrow=dim(k562_10kb_f)[2]-1,
-                                    ncol=4))
-rownames(enetlst_sm[[3]]) <- colnames(k562_10kb_f)[-1]
-
-enetperf_sm <- matrix(nrow = 17, ncol=4)
-rownames(enetperf_sm) <- c("TN",
-                           "FN",
-                           "FP",
[…]

### 2018-11-19 K562/Data_Pipeline/04.2backward.R

@@ -1,103 +1,0 @@
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-library(leaps)
-
-setwd("/home/stilianoudakisc/TAD_data_analysis/K562/evaluating_variable_reduction/")
-
-k562_10kb_f <- readRDS("k562_10kb_f.rds")
-
-
-####set number of bootstrap samples
-
-bootsamps = 10
-
-#### function for roc curves
-
-simple_roc <- function(labels, scores){
-  labels <- labels[order(scores, decreasing=TRUE)]
-  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
-}
-
-
-#### Establishing tuning/training parameters
-
-fitControl <- trainControl(method = "cv",
-                           ## Estimate class probabilities
-                           classProbs = TRUE,
-                           ## Evaluate performance using 
-                           ## the following function
-                           summaryFunction = twoClassSummary)
-						   
-#set up grid of alpha and lambda values
-lambda.grid = 10^seq(2,-2,length=100)
-alpha.grid = seq(0,1,length=10)
-srchGrid <- expand.grid(.alpha=alpha.grid, .lambda=lambda.grid)
-
-
-####create a matrix of row ids that represent the zero class
-
-sampids <- matrix(ncol=bootsamps, 
-                  nrow=length(k562_10kb_f$y[which(k562_10kb_f$y=="Yes")]))
-				  
-####filling in the sample ids matrix
-
-set.seed(123)
-for(j in 1:bootsamps){
-  sampids[,j] <- sample(which(k562_10kb_f$y=="No"),
-                        length(which(k562_10kb_f$y=="Yes")),
-                        replace = TRUE)
-}
-
-## Backward
-
-namesmat <- matrix(NA,nrow=dim(k562_10kb_f)[2]-1, ncol=bootsamps)
-rownames(namesmat) <- sort(names(k562_10kb_f)[-which(names(k562_10kb_f)=="y")])
-
-for(i in 1:bootsamps){
-  set.seed(7215)
-  #combining the two classes to create balanced data
[…]

### 2018-11-19 Manuscript/manuscript.Rmd
Update abstract

@@
 
-###Background 
-Chromosome conformation capture sequencing technologies have shown that the three-dimensional (3D) structure of the genome is folded into distinct compartments, known as topologically associated domains (TADs) - units of coordinated gene expression.
+**Background.** Chromosome conformation capture sequencing technologies have shown that the three-dimensional (3D) structure of the genome is folded into distinct compartments, known as topologically associated domains (TADs) - units of coordinated gene expression.
 The location of TAD boundaries is highly conserved, suggesting the presence of epigenomic marks aiding in TAD formation.
@@
 
-Existing methods for predicting associations between genomic elements ignore key characteristics of the data.
+Existing methods for predicting associations between genomic elements tend to ignore key characteristics of the genomic data.
 Specifically, the number of TAD boundaries is much less than the number of other genomic regions, leading to heavily imbalanced classes.
@@
 
-###Methods 
-We propose a novel data pre-processing pipeline that addresses those shortcomings.
+**Methods.** We propose a novel data pre-processing pipeline that addresses those shortcomings.
 A number of classifier performance metrics were assessed, including the F1 measure and Matthew Correlation Coefficient (MCC), and area under the ROC curve (AUROC).
 
-###Results 
-Data preprocessing (log2-transformation and standardization) improves the performance of classification algorithms and allows for the ability to more accurately predict which genomic features are most associated with TAD boundaries.
+**Results.** Data preprocessing (log2-transformation and standardization) improves the performance of classification algorithms and allows for the ability to more accurately predict which genomic features are most associated with TAD boundaries.
 
-###Conclusions 
-Current methods used to model the epigenomic features associated with TAD boundaries are not robust to handle properties of genomic data.
+**Conclusions.** Current methods used to model the epigenomic features associated with TAD boundaries are insufficiently robust to handle properties of genomic data.
 Models applied to unprocessed data can have poor predictive performances.
@@
 
-#INTRODUCTION
+# INTRODUCTION
 

### 2018-11-19 Manuscript/Figures/figure_legends.Rmd
added figure and table legends

---
title: "Legends for Figures"
author: "Spiro Stilianoudakis"
date: "November 19, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Figure 1: Model Construction

Diagram of the model construction used for downstream analysis. The linear genome was binned according to the resolution of the respective HiC experiment (either 5kb, 25kb, 50kb, or 100kb intervals). TAD boundaries were then flanked by 1-unit on either side of the boundary point. The unit flanking was indicative of the resolution that the domain data was obtained from (i.e. for 5kb resolution, 1 unit represents 5kb for a total flanking region of 10kb). The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region. The positional coordinates of each functional genomic element, obtained from ENCODE, were then used to define the feature space of the models.

# Figure 2: Predictor Types

Diagram of the 3 predictor types considered when assessing the relationship between TAD boundaries and functional genomic elements. Each predictor type was used as the feature space in downstream analyses for predicting which functional genomic elements were associated with the formation of TAD boundaries. Featured above are bin-specific examples of the construction of each predictor type. (Left) The overlap count (OC) predictors were calculated by considering the total number of elemental regions that overlapped with each genomic bin. (Middle) The overlap percent (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin and dividing by the total bin width (either 5, 25, 50, or 100 kilobases given resolution of boundary data). (Right) The distance predictors were calculated by measuring the distance (in base pairs) from the center of each genomic bin to the center of the nearest elemental region of interest. The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective functional genomic element.

### 2018-11-19 Manuscript/Tables/table_legends.Rmd
added figure and table legends

---
title: "Legends for Tables"
author: "Spiro Stilianoudakis"
date: "November 19, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Table 1: List of Genomic Annoations.

The full list of genomic annotations used in downstream analyses. These annotations were the functional genomic elements used to predict the formation of TAD boundaries. They were obtained via ChIP-Seq experiments, mapped to human genome assembly hg19, and made available by the ENCODE Consortium.

# Table 2: 5kb Class Distributions

The class distributions for different re-sampling techniques from domain data obtained from 5kb resolution contact matrices.

# Table 3: 25kb Class Distributions

The class distributions for different re-sampling techniques from domain data obtained from 25kb resolution contact matrices.

# Table 4: 50kb Class Distributions

The class distributions for different re-sampling techniques from domain data obtained from 50kb resolution contact matrices.

# Table 5: 100kb Class Distributions

The class distributions for different re-sampling techniques from domain data obtained from 100kb resolution contact matrices.

### 2018-11-25 Manuscript/Figures/figure_legends.Rmd
added file for legends of figures/tables

@@
 The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective functional genomic element.
+
+# Figure 3: Ensemble Framework/Model Building Pipeline
+
+A diagram of the model building pipeline given an a combination of inputs from the ensemble framework.
+The data was split into a 7:3 training set to testing set ratio, the variable reduction technique of choice was implemented, and a random forest classification algorithm was performed.
+Each model was then validated on the same testing set.
+
+# Figure 4: Class Imbalance
+
+Barplots illustrating the class imbalance problem featured across each of the four different resolutions that were analyzed.
+Minority classes represent the number of genomic bins that contain a TAD boundary, while the majority classes represent the number of genomic bins that do not contain a TAD boundary.
+
+# Figure 5: 5kb Model Performances
+
+Comparing model performances for TAD boundary data at 5kb resolution across each re-sampling technique.
+Each square plot represents a random forest classifier performed on 5kb resolution binned boundary data using a particular predictor type, variable reduction algorithm, and re-sampling technique evaluated across 4 different performance metrics.
+
+# Figure 6: 25kb Model Performances
+
+Comparing model performances for TAD boundary data at 25kb resolution across each re-sampling technique.
+Each square plot represents a random forest classifier performed on 25kb resolution binned boundary data using a particular predictor type, variable reduction algorithm, and re-sampling technique evaluated across 4 different performance metrics.
+
+# Figure 7: 50kb Model Performances
+
+Comparing model performances for TAD boundary data at 50kb resolution across each re-sampling technique.
+Each square plot represents a random forest classifier performed on 50kb resolution binned boundary data using a particular predictor type, variable reduction algorithm, and re-sampling technique evaluated across 4 different performance metrics.
+
+# Figure 8: 100kb Model Performances
+
+Comparing model performances for TAD boundary data at 100kb resolution across each re-sampling technique. Each square plot represents a random forest classifier performed on 10
++0kb resolution binned boundary data using a particular predictor type, variable reduction algorithm, and re-sampling technique evaluated across 4 different performance metrics.
+
+# Figure 9: Comparing Performances
+
+Comparing performances of random forest classification algorithms, across TAD boundary data at each resolution for models using distance-type predictors, with elastic-net regularization and random under-sampling.
+Performances were aggregated by taking the average of each metric across 50 iterations of random under-sampling.
+
+# Figure 10: Comparing Variable Importance
+
+Comparing variable importance for the top 15 most predictive functional genomic elements for each of the 4 different resolutions.
+The x-axis represents the standardized difference between the out-of-bag prediction accuracy after permuting each predictor variable, averaged across all trees.
+The greater the mean standardized difference, the more importance the predictor is to the model.

### 2018-11-25 Manuscript/Tables/table_legends.Rmd
added file for legends of figures/tables

@@
 
-# Table 2: 5kb Class Distributions
+# Table 2: Class Distributions
 
-The class distributions for different re-sampling techniques from domain data obtained from 5kb resolution contact matrices.
+Summary of the class distributions for each re-sampling technique, across each resolution.
+All re-sampling techniques yielded completely balanced classes.
+That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.
 
-# Table 3: 25kb Class Distributions
+# Table 3: 5kb Model Performances
 
-The class distributions for different re-sampling techniques from domain data obtained from 25kb resolution contact matrices.
+Performance metrics comparing models using different sampling approaches for the 5kb resolution TAD boundary data.
+The best value in each column for each performance metric is underlined to compare different sampling approaches, while the highest value in each row is highlighted in bold to compare different predictor types.
 
-# Table 4: 50kb Class Distributions
+# Table 4: 25kb Model Performances
 
-The class distributions for different re-sampling techniques from domain data obtained from 50kb resolution contact matrices.
+Performance metrics comparing models using different sampling approaches for the 25kb resolution TAD boundary data.
+The best value in each column for each performance metric is underlined to compare different sampling approaches, while the highest value in each row is highlighted in bold to compare different predictor types.
 
-# Table 5: 100kb Class Distributions
+# Table 5: 50kb Model Performances
 
-The class distributions for different re-sampling techniques from domain data obtained from 100kb resolution contact matrices.
+Performance metrics comparing models using different sampling approaches for the 50kb resolution TAD boundary data.
+The best value in each column for each performance metric is underlined to compare different sampling approaches, while the highest value in each row is highlighted in bold to compare different predictor types.
+
+# Table 6: 100kb Model Performances
+
+Performance metrics comparing models using different sampling approaches for the 100kb resolution TAD boundary data.
+The best value in each column for each performance metric is underlined to compare different sampling approaches, while the highest value in each row is highlighted in bold to compare different predictor types.

### 2018-11-25 Manuscript/manuscript.Rmd
fixed references in manuscript

@@
     toc: yes
+bibliography: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/References
 ---
@@
 
-The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect several epigenetic functions (Aiden et al.).
+The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect several epigenetic functions [-@lieberman2009comprehensive].
 Analyses have shown that the genome is tightly compacted into distinct compartments.
-There exist regions within these compartments that have been shown to be highly conserved and self-interacting, and termed topologically associating domains (TADs) (Dixon et al.).
-Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD (Symmons et al.).
+There exist regions within these compartments that have been shown to be highly conserved and self-interacting, and termed topologically associating domains (TADs) [-@dixon2012topological].
+Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD [-@symmons2014functional].
 This suggests that the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
@@
 The mechanisms underlying the formation of TADs are a complex and active area of research.
-Recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangements of higher-order chromatin architecture (Phillips-Cremins et al).
+Recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangements of higher-order chromatin architecture [-@phillips2013chromatin].
 Insulators are multi-faceted regulatory sequences that moderate a variety of genomic processes including activation, repression, and enhancer blocking.
-Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long-range chromatin contacts (Zuin et al.).
-Other regulatory elements like DNase I hypersensitive sites, particular histone modifications [mention more specifically; include reference], and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions (Hong et al).
+Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long-range chromatin contacts [-@zuin2014cohesin].
+Other regulatory elements like DNase I hypersensitive sites, particular histone modifications such as H3k36 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [-@hong2017computational].
 These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
@@
 Therefore, the minority class of genomic bins with TAD boundaries in them becomes proportionally smaller than that of the majority class of genomic bins with no TAD boundaries.
-It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate (Estabrooks et al).
+It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [-@estabrooks2004multiple].
 However, a clear method for creating balanced classes remains evasive and largely dependent on the problem at hand.
@@
 However, these distance characteristics offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
+
 In this paper we considered two types of variable reduction techniques, an L1 norm penalized regularization (LASSO) and a combination of both an L1 and L2 norm penalized regularizations (Elastic-Net).
@@
 While both regularization techniques have merit, LASSO’s inability to handle correlated predictors poses a problem when identifying which element are most predictive of TAD boundaries.
-The elastic-net, however, is better suited in a situation where multiple genomic elements colocalize around the same TAD boundaries, and could be better suited for this type of alaysis.
+The elastic-net, however, is better suited in a situation where multiple genomic elements colocalize around the same TAD boundaries, and could be better suited for this type of alaysis [-@zou2005regularization].
+
+In a previous study, investigators
 
@@
 We evaluated domain data obtained from four different resolution contact matrices for the GM12878 cell line including 5kb, 25kb, 50kb, and 100kb.
-For each resolution, we examined the inclusion of three different predictor types as the feature space for downstream modelling.
+For each resolution, we examined the inclusion of three different predictor types as the feature space for downstream modeling.
 We coupled each predictor type with two separate variable reduction techniques.

### 2018-11-25 Manuscript/manuscript.Rmd
edits to manuscript

@@
 Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long-range chromatin contacts [-@zuin2014cohesin].
-Other regulatory elements like DNase I hypersensitive sites, particular histone modifications such as H3k36 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [-@hong2017computational].
+Other regulatory elements like particular histone modifications such as H3k36 and H3K27 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [-@rao20143d].
 These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
@@
 
-In this paper we considered two types of variable reduction techniques, an L1 norm penalized regularization (LASSO) and a combination of both an L1 and L2 norm penalized regularizations (Elastic-Net).
 Due to the increasingly large amounts of functional genomic elements to consider, it is a popular approach in genomic studies to use variable reduction techniques to reduce the noise induced by noninformative predictors and increase computational efficiency.
+Two popular approaches use the $l_{1}$ norm (LASSO) and a combination of the $l_{1}$ and $l_{2}$ norms together (Elastic-Net).
 While both regularization techniques have merit, LASSO’s inability to handle correlated predictors poses a problem when identifying which element are most predictive of TAD boundaries.
@@
 
-In a previous study, investigators
+Careful consideration must also be taken when deciding which performance metric(s) to present when evaluating predictive models.
+A common metric to consider is the the area under the ROC curve (AUC), as well as others including accuracy, sensitivity, and specificity.
+The main argument in favour of ROC curves is that they do not depend on a threshold, whose selection is thought to be subjective.
+However, when the prevalence of an event is low--that is, a genomic bin containing a TAD boundary)--mean probabilities are biased towards the most common event (Jorge M.
+Lobo).
+Likewise, metrics like accuracy and sensitivity and specificity do not incorporate the entirety of the confusion matrix created when validating predictive models on a test data set.
+Therefore, each of these metrics are likely to be inflated when evaluating model performance on imbalanced data.
+More robust metrics like the F1-score and Matthew's Correlation Coefficient are more suitable for this type of analysis and can highlight problems associated with applying predictive models on imbalanced data.
 

### 2018-11-26 Manuscript/manuscript.Rmd
manuscript edits

@@
 
+[Mention Feature Engineering]
+
 Another problem lies in identifying the feature space of subsequent classification algorithms.
@@
 A common metric to consider is the the area under the ROC curve (AUC), as well as others including accuracy, sensitivity, and specificity.
-The main argument in favour of ROC curves is that they do not depend on a threshold, whose selection is thought to be subjective.
-However, when the prevalence of an event is low--that is, a genomic bin containing a TAD boundary)--mean probabilities are biased towards the most common event (Jorge M.
-Lobo).
+
+The popularity surrounding the use of ROC curves is that they do not depend on a threshold.
+However, when the prevalence of an event is low--that is, a genomic bin containing a TAD boundary--mean probabilities are biased towards the majority class.
 Likewise, metrics like accuracy and sensitivity and specificity do not incorporate the entirety of the confusion matrix created when validating predictive models on a test data set.
@@
 More robust metrics like the F1-score and Matthew's Correlation Coefficient are more suitable for this type of analysis and can highlight problems associated with applying predictive models on imbalanced data.
+
+[Mention Previous Methods]
 
@@
 
-Publicly available topologically associating domain data for the GM12878 cell line was obtained using the arrowhead algorithm from the Juicer toolbox (Rao et.
-al).
-The domain data was constructed from in situ Hi-C contact matrices at 5kb, 25kb, 50kb, and 100kb resolutions.
+Topologically associating domain data for the GM12878 cell line was obtained using the arrowhead algorithm from the Juicer toolbox (https://github.com/aidenlab/juicer).
+Publically available domain data was obtained from in situ Hi-C contact matrices at 5kb resolution [-@rao20143d].
+Additional domain data was obtained from Dali et al.
+at 25kb, 50kb, and 100kb resolutions [-@dali2017critical].
+
 Identified TAD boundaries were represented by their location in the genome (hg19 human genome assembly), including chromosome, start and end coordinates for chromosomes 1 through 22.
@@
 The annotations consisted of a variety of different chromatin states, histone marks, and DNase I hypersensitive sites.
+Table 1 presents the total list of genomic  annotations considered in this study and the sources of downloadable files.
 Each annotation was represented by their location throughout the genome via chromosomal coordinates.
@@
 
-Using each genomic element, and their relationship with the genomic bins, we created three types of predictors that were used as features in downstream modelling.
+##Feature Engineering
+
+Using each genomic element, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries in downstream modelling.
 Figure 2 presents an illustration of each type of predictor that was considered.
-The predictors consisted of two different types of overlaps, and a distance type and are described in detail below:
+The predictors consisted of two different types of overlaps, and a distance type.
+They are described in detail below:
 
@@
 This was defined as the overlap counts (OC) and is illustrated in the left part of Figure 2.
-From the first bin, in the highlighted region, we see that there are two regions defined by the particular functional genomic element that overlap within the same bin.
-Therefore the OC for that bin, given that feature, was determined to be 2.
-Bins that did not overlap with a feature were assigned a value of zero.
+Within each bin (marked by the blue dashed lines), the total number of overlapped regions of the genomic element (represented by the horizontal green segments) are tallied and marked below.
+In the case of no overlaps the value is given as 0.
 
    2.	Overlap Percent (OP): For each genomic bin, the percent overlap between regions defined by a particular functional element and a bin was calculated.
-From the middle region of Figure 2, the feature width was defined as the number of base pairs that overlapped with the genomic bin.
+From the middle diagram of Figure 2, the feature width was defined as the number of base pairs that overlapped with the genomic bin.
 The percent was then calculated by dividing the feature width with the bin width.
@@
 Note that the bin width remained constant for a given resolution (either 5kb, 25kb, 50kb, or 100kb).
-Similar to the OC predictor type, bins with no overlaps were given to be zero.
+Similar to the OC predictor type, bins with no overlaps were given to be 0.
 
    3.	Distance: For each genomic bin, the distance (in base pairs) from the center of the bin to the center of the nearest region of a respective functional element was calculated.
-The distance predictors were then normalized using a log base 2 transformation prior to modelling.
+The right most diagram of Figure 2 depicts an example of how distance was calculated.
+The vertical green segments represent the centers of the respective genomic element.
+Each distance, $D_{i}$, represented by the blue brackets are the number of base pairs from the center of the bins to the center of the nearest genomic elemental region.
+
+[Mention transformations used]
+
+##Variable Reduction
+
+We evaluated the use of two variable reduction algorithms, the LASSO and Elastic-Net regularizations.
+Each algorithm was performed prior to re-sampling.
+For the LASSO, the $\lambda$ penalization term was tuned over a grid of 10 values on an exponential scale ranging from 0.01 to 10.
+The additional $\alpha$ term for the Elastic-Net was tuned
 
@@
 
-After choosing one of the aforementioned data resolutions, predictor types, and variable reduction techniques, we then evaluated three re-sampling techniques used to create balanced classes.
+Figure 3 details the ensemble framework proposed and evaluated in this study.
+For each resolution and predictor type chosen, the data, composed of majority and minority classes, was split into a 7:3 ratio of training to testing sets.
+For the training set, a variable reduction technique was performed.
+The feature space was reduced and a resampling technique was applied.
+A classification algorithm in the form of a random forest was performed and validated using the test set.
+Details of each step in the framework are provided below.
+
+###Training and Testing Sets
+
+###Variable Reduction
+
+###Re-Sampling Techniques
+
+After choosing one of the aforementioned data resolutions, predictor types, and variable reduction algorithms, we then evaluated three re-sampling techniques used to create balanced classes.
 For each resampling technique, the majority class is defined as the set of genomic bins that did not include a TAD boundary, while the minority class is defined as the set of bins that included a TAD boundary.

### 2018-11-26 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-##Variable Reduction
+##ENSEMBLE FRAMEWORK
+
+Figure 3 details the ensemble framework proposed and evaluated in this study.
+For each resolution and predictor type chosen, the data was split into training to testing sets.
+A variable reduction technique was then performed.
+The feature space was reduced and a resampling technique was applied.
+Lastly, a classification algorithm in the form of a random forest was performed and validated.
+Details of each step in the framework are provided below.
+
+###Training and Testing Sets
+
+Given a particular resolution, the full data set was composed of genomic bins that either overlapped with a flanked TAD boundary (minority set) or did not (majority set).
+Figure 3 highlights the severe class imbalance present in both the full data set.
+The data was then split into a 7:3 ratio of training to testing sets.
+Each training and testing set was composed of a similar majority to minority class ratio as the full data set, which is represented by the segmented regions in Figure 3.
+The training set was then used to perform all downstream modeling.
+The same test set was held separate and used to validate all models.
+
+###Variable Reduction
 
@@
 For the LASSO, the $\lambda$ penalization term was tuned over a grid of 10 values on an exponential scale ranging from 0.01 to 10.
-The additional $\alpha$ term for the Elastic-Net was tuned
-
-##ENSEMBLE FRAMEWORK
-
-Figure 3 details the ensemble framework proposed and evaluated in this study.
-For each resolution and predictor type chosen, the data, composed of majority and minority classes, was split into a 7:3 ratio of training to testing sets.
-For the training set, a variable reduction technique was performed.
-The feature space was reduced and a resampling technique was applied.
-A classification algorithm in the form of a random forest was performed and validated using the test set.
-Details of each step in the framework are provided below.
-
-###Training and Testing Sets
-
-###Variable Reduction
+The additional $\alpha$ term for the Elastic-Net was tuned over 10 equa-distant values from 0 to 1.
 
@@
 Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class.
-The SMOTE algorithm was devised by Chawla et al and stored in the DMwR package, available in R.
+The SMOTE algorithm was devised by Chawla et al.
+[-@chawla2002smote] and stored in the DMwR package, available in R.
 The user is able to specify the parameters denoting the percent of over- and under-sampling from the two classes.
@@
 
-Figure 3 details the ensemble framework proposed and evaluated in this study.
-For each resolution and predictor type chosen, the data, composed of majority and minority classes, was split into a 7:3 ratio of training to testing sets.
-For the training set, a variable reduction technique was performed.
-The feature space was reduced and a resampling technique was applied.
+###Classification
+
 A classification algorithm in the form of a random forest was performed and validated using the test set.
-10-fold cross validation was used such that each sub-training set was partitioned into a fixed 9:1 ratio.
-The model was performed and assessed using the holdout set to get more stable performance metrics and reduce bias.
+10-fold cross validation was used to reduced bias due to random dataset generation.
+The default number of features to consider at each node of the random forest algorithm was set as the square root of the number of features in the model.
+Likewise, the number of ensemble trees to aggregate was set at 500.
+Once the model was implemented, it was assessed using the test set, and performance metrics were then recorded.
 
@@
 Once a system was defined, a random forest algorithm was performed. Letting |X| denote the cardinality of each set, then we evaluated |R| x |P| x |V| x |C| different ensemble systems in this paper.
+
+###Model Evaluation
+
+The efficacy of different ensemble systems was compared using various performance metrics including accuracy, AUC, F1-score, and MCC. These metrics are defined as follows:
+
+$$
+\begin{equation}
+\begin{aligned}
+Accuracy &= \dfrac{TP + TN}{TP + TN + FP + FN} \\
+F1 - Score &= \dfrac{2TP}{2TP + FP + FN} \\
+MCC &= \dfrac{TP \times TN - FP \times FN}{\sqrt{ (TP + FP)(TP+FN)(TN+FP)(TN+FN) }}
+\end{aligned}
+\end{equation}
+$$
+Here, TP refers to the number of bins correctly identified as containing a TAD boundary (true positives), FP refers to the number of bins incorrectly identified as containing a TAD boundary (false positives), TN refers to the number of bins correctly identified as not containing a TAD boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a TAD boundary.
+Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
+Accuracy measures the percentage of correct classifications by the model.
+However, in the case of heavily imbalanced class, as can be seen by the numerator, the metric is biased toward correcly identified majority classes.
+The F1-score and MCC are more balanced measures.
+We also considered the AUC for each model, by computing the average trapezoidal approximations for the curve created by the true positive rates (TPR) and false positive rates (FPR)
 

### 2018-11-26 Manuscript/Figures/figure_legends.Rmd
manuscript and legends updates

@@
 The greater the mean standardized difference, the more importance the predictor is to the model.
+
+# Figure 11: Model Performances for all Resolutions
+
+Comparing model performances for TAD boundary data for all 4 resolutions.
+The four regions represent (from left to right; top to bottom) data at 5kb, 25kb, 50kb, and 100kb resolutions.
+Within each region, the rows represent the set of re-sampling techniques, while the columns represent the set of performance metrics that the models were evaluated on.
+Each plot compares 2 sets of models; one using LASSO regularization and one using Elastic-Net regularization.
+Within each set, each bar represents the performance of a model with a specific predictor type; either overlap counts (OC) in red, overlap percent (OP) in green, or distance in blue.

### 2018-11-26 Manuscript/Tables/table_legends.Rmd
manuscript and legends updates

@@
 The best value in each column for each performance metric is underlined to compare different sampling approaches, while the highest value in each row is highlighted in bold to compare different predictor types.
+
+# Table 7: Model Performances at all Resolutions
+
+Performance metrics comparing models using different sampling approaches for each of the 4 resolutions.
+Withing each resolution, the best value in each column for each performance metric is underlined to compare different sampling approaches, while the highest value in each row is highlighted in bold to compare different predictor types.

### 2018-11-26 Manuscript/manuscript.Rmd
manuscript and legends updates

@@
 In this section we provide the details of the comprehensive experiments performed in order to assess each ensemble system.
-For the task of predicting TAD boundaries using functional genomic elements, we evaluated 4 domain data sets obtained using the arrowhead algorithm for the Juicer toolbox developed by Rao et al, 3 predictor types, 2 variable reduction techniques, and 4 class balancing techniques.
+For the task of predicting TAD boundaries using functional genomic elements, we evaluated 4 domain data sets, 3 predictor types, 2 variable reduction techniques, and 4 class balancing techniques.
 We evaluated each ensemble system using 10-fold cross-validated random forest models.
 Thus, we generated 96 (=4x3x2x4) separate models.
+
+###CLASS DISTRIBUTIONS ACROSS RESOLUTIONS
 
@@
 Likewise, we see the apparent decrease in data points (bins) as resolution increases.
-Furthermore, Table 1 shows that for each class balancing technique, perfectly balanced classes were created.
+Furthermore, Table 1 specifically shows the class distribution for each resolution.
+The overall average perentage of minority classes across all data resolutions was 13.2%, with the most severe case present in the 5kb resolution (6.9%).
 
-###DISTANCE PREDICTORS IMPROVE MODEL PERFORMANCE IN ALL RESOLUTIONS
+###CLASS IMBALANCE HINDERS PERFORMANCE ACROSS RESOLUTIONS
 
-Figures 4-7 present the results across all of the ensemble systems for each resolution of domain data.
-Focusing on the top row in each of Figure 4-7, indicating no balancing, we see that the model using distance predictors, represented by the blue bars, outperformed models using the other two predictor types.
-However, the disparity become less evident as the resolution increased.
-In each of the 4 figures we see that the F1-score and MCC metrics were noticeably lower than the accuracy and AUC.
-This highlights the problems associated with applying predictive models to unbalanced data.
+Figure 11 present the results across all of the ensemble systems for each resolution of domain data.
+The first row in each of the 4 regions shows the performances for models without resampling.
+The average accuracy and AUC were marginally high across each of the resolutions with values of W%, X%, Y%, and Z% respectively.
+However, the severity of the model performances were much more apparant when comparing F1-scores and MCCs.
+The average F1-scores across resolutions for models without resampling were found to be W%, X%, Y%, and Z% respectively, while the MCCs were W%, X%, Y%, and Z% (Supplementary Table 6).
+We thus see the necessity for implementing a class balancing technique prior to modeling.
 
@@
 
-Moving down the rows in each of Figures 4-7 we see that model performance was markedly improved among the F1-scores and MCCs after creating balanced classes compared to the results using no re-sampling.
-For each of the resolutions, we see that random under-sampling and SMOTE re-sampling techniques performed very similarly, while random over-sampling performed poorly in comparison.
+Moving down the rows in each of the 4 regions of Figure 11 we see that model performance was markedly improved among the F1-scores and MCCs after creating balanced classes compared to the results using no re-sampling.
+For each of the resolutions, we see that random under-sampling out performed the other class balancing techniques.
+While SMOTE performed very similarly to RUS, ROS performed poorly in comparison, especially as the resolution of the data increased.
 Furthermore, we see that the elastic-net reduction technique outperformed the LASSO.
 Although, the disparity became less evident as the resolution increased.
-Specific ensemble results can be found in Supplement Tables X-X.
 
-###PERFORMANCES BECOME INVARIANT AS RESOLUTION INCREASES
+###DISTANCE TYPE PREDICTORS OUT-PERFORM OTHER PREDICTOR TYPES
 
-Figure 8 compares the results of random forest models using distance-type predictors, with elastic-net regularization, over 50 iterations of random under-sampling, across each domain data resolution.
+Again referencing Figure 11, focusing on the rows corresponding to models using randomly under-sampled data, it was found that models with distance type predictors out performed models with the two other overlap types (counts and percents).
+The disparity between predictor types was steady across resolutions (Supplementary Table 6).
+The greatest difference was seen in the 5kb data.
+For models with Elastic-Net regularization, the F1-scores were X, Y, and Z, while the MCCs were X, Y, and Z for each predictor type respectively.
+
+###PERFORMANCES WORSEN AS RESOLUTION INCREASES
+
+Figure 9 compares the results of random forest models using distance-type predictors, with elastic-net regularization, and random under-sampling, across each domain data resolution.
 We see that the results for F1-scores are relatively stable between 5kb, 25kb, and 50kb resolutions with a sharp decrease for the 100kb resolution.
@@
 
+###5kb RESOULTION DATA PROVIDES MOST ACCURATE ACCURATE RESULTS
+
 To identify the functional genomic elements that were most predictive of TAD boundaries, we analyzed the variable importance produced by each random forest algorithm.
-Figure 9 presents the scaled importance plots of the top 15 most predictive genomic elements for each resolution.
+Figure 10 presents the subsequent scaled importance plots of the top 15 most predictive genomic elements for each model presented in Figure 9.
 We see that for the 5kb resolution, the most predictive elements include insulator proteins, DNase hypersensitive sites, the transcription factor CTCF, as well as histone modifications H3k9ac, H2az, and H3k4me2.
@@
 Although, the insulator protein is featured as a top predictor in 2 of the other 3 resolutions, the rest of the predictors are less consistent among each other and less in agreement with the literature.
-The results from Figure 8 and 9 confirm that the model results appear to degrade as resolution increases with respect to both prediction and the identification of genomic elements associated with TAD boundaries.
+The results from Figure 9 and 10 confirm that the model results appear to degrade as resolution increases with respect to both prediction and the identification of genomic elements associated with TAD boundaries.
+
+#Discussion
+
+# Abbreviations
+
+# Acknowledgements
+
+_Conflict of Interest._ None.
+
+# Funding
+
+# Tables
+
+# Figures
+
+# Table Legends
+
+# Figure legends
+
+# Supplementary material
+
+# References

### 2018-11-26 Manuscript/manuscript.Rmd
updated manuscript

@@
     toc: yes
-bibliography: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/References
+  pdf_document:
+    toc: yes
+bibliography: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/References/references.bib
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+
 ```
@@
 
-The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect several epigenetic functions [-@lieberman2009comprehensive].
+The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect several epigenetic functions [@lieberman2009comprehensive].
 Analyses have shown that the genome is tightly compacted into distinct compartments.
-There exist regions within these compartments that have been shown to be highly conserved and self-interacting, and termed topologically associating domains (TADs) [-@dixon2012topological].
-Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD [-@symmons2014functional].
+There exist regions within these compartments that have been shown to be highly conserved and self-interacting, and termed topologically associating domains (TADs) [@dixon2012topological].
+Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD [@symmons2014functional].
 This suggests that the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
@@
 The mechanisms underlying the formation of TADs are a complex and active area of research.
-Recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangements of higher-order chromatin architecture [-@phillips2013chromatin].
+Recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangements of higher-order chromatin architecture [@phillips2013chromatin].
 Insulators are multi-faceted regulatory sequences that moderate a variety of genomic processes including activation, repression, and enhancer blocking.
-Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long-range chromatin contacts [-@zuin2014cohesin].
-Other regulatory elements like particular histone modifications such as H3k36 and H3K27 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [-@rao20143d].
+Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long-range chromatin contacts [@zuin2014cohesin].
+Other regulatory elements like particular histone modifications such as H3k36 and H3K27 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [@rao20143d].
 These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
@@
 Therefore, the minority class of genomic bins with TAD boundaries in them becomes proportionally smaller than that of the majority class of genomic bins with no TAD boundaries.
-It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [-@estabrooks2004multiple].
+It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@estabrooks2004multiple].
 However, a clear method for creating balanced classes remains evasive and largely dependent on the problem at hand.
@@
 
-[Mention Feature Engineering]
-
 Another problem lies in identifying the feature space of subsequent classification algorithms.
@@
 While both regularization techniques have merit, LASSO’s inability to handle correlated predictors poses a problem when identifying which element are most predictive of TAD boundaries.
-The elastic-net, however, is better suited in a situation where multiple genomic elements colocalize around the same TAD boundaries, and could be better suited for this type of alaysis [-@zou2005regularization].
+The elastic-net, however, is better suited in a situation where multiple genomic elements colocalize around the same TAD boundaries, and could be better suited for this type of alaysis [@zou2005regularization].
 
@@
 Model performance was evaluated based on a total of four metrics which included test accuracy, area under the ROC curve (AUC), F1 score, and Matthew's Correlation Coefficient (MCC).
-[mention reasons for including 4 metrics]
 
@@
 Topologically associating domain data for the GM12878 cell line was obtained using the arrowhead algorithm from the Juicer toolbox (https://github.com/aidenlab/juicer).
-Publically available domain data was obtained from in situ Hi-C contact matrices at 5kb resolution [-@rao20143d].
+Publically available domain data was obtained from in situ Hi-C contact matrices at 5kb resolution [@rao20143d].
 Additional domain data was obtained from Dali et al.
-at 25kb, 50kb, and 100kb resolutions [-@dali2017critical].
+at 25kb, 50kb, and 100kb resolutions [@dali2017critical].
 
@@
 Each annotation was represented by their location throughout the genome via chromosomal coordinates.
-An example of a specific annotation, which is labeled as a functional genomic element, is presented in Figure 1.
+An example of a specific annotation, which is labeled as a functional genomic element, is presented in Figure 2.
 It is represented by the green segments that overlap with the genomic bins.
@@
 Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class.
-The SMOTE algorithm was devised by Chawla et al.
-[-@chawla2002smote] and stored in the DMwR package, available in R.
+The SMOTE algorithm is stored in the DMwR package, available in R [@chawla2002smote].
 The user is able to specify the parameters denoting the percent of over- and under-sampling from the two classes.
@@
 
-E = {r, p, v, c}, where r in R, p in P, v in V, and c in C.
+E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.
 
@@
 
+Table 2 presents the class distributions across each resolution.
 After binning the genome at 5kb, 25kb, 50kb, and 10kb intervals there were a total of 44948, 9042, 4541, and 2279 genomic bins created respectively.
@@
 However, the severity of the model performances were much more apparant when comparing F1-scores and MCCs.
-The average F1-scores across resolutions for models without resampling were found to be W%, X%, Y%, and Z% respectively, while the MCCs were W%, X%, Y%, and Z% (Supplementary Table 6).
+The average F1-scores across resolutions for models without resampling were found to be W%, X%, Y%, and Z% respectively, while the MCCs were W%, X%, Y%, and Z% (Table 7).
 We thus see the necessity for implementing a class balancing technique prior to modeling.
@@
 Again referencing Figure 11, focusing on the rows corresponding to models using randomly under-sampled data, it was found that models with distance type predictors out performed models with the two other overlap types (counts and percents).
-The disparity between predictor types was steady across resolutions (Supplementary Table 6).
+The disparity between predictor types was steady across resolutions (Table 7).
 The greatest difference was seen in the 5kb data.
@@
 
+## Table 1.
+
+## Table 2.
+
+## Table 7.
+
 # Figures
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure1_model_construction.png)      |
+| **Figure 1.**     |
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure2_predictor_types.png)      |
+| **Figure 2.**     |
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure3_ensemble_framework.png)      |
+| **Figure 3.**     |
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure4_class_imbalance_plots.png)      |
+| **Figure 4.**     |
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure11_allresolutions_performances.png)      |
+| **Figure 11.**     |
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure9_comparing_resolutions_barplot.png)      |
+| **Figure 9.**     |
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure10_allresolutions_varimps.png)      |
+| **Figure 10.**     |
++-------+
 
@@
 
+## Table 1: List of Genomic Annoations.
+
+The full list of genomic annotations used in downstream analyses.
+These annotations were the functional genomic elements used to predict the formation of TAD boundaries.
+They were obtained via ChIP-Seq experiments, mapped to human genome assembly hg19, and made available by the ENCODE Consortium.
+
+## Table 2: Class Distributions
+
+Summary of the class distributions for each re-sampling technique, across each resolution.
+All re-sampling techniques yielded completely balanced classes.
+That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.
+
+## Table 7: Model Performances at all Resolutions
+
+Performance metrics comparing models using different sampling approaches for each of the 4 resolutions.
+Withing each resolution, the best value in each column for each performance metric is underlined to compare different sampling approaches, while the highest value in each row is highlighted in bold to compare different predictor types.
+
 # Figure legends
 
-# Supplementary material
+## Figure 1: Model Construction
+
+Diagram of the model construction used for downstream analysis.
+The linear genome was binned according to the resolution of the respective HiC experiment (either 5kb, 25kb, 50kb, or 100kb intervals).
+TAD boundaries were then flanked by 1-unit on either side of the boundary point.
+The unit flanking was indicative of the resolution that the domain data was obtained from (i.e.
+for 5kb resolution, 1 unit represents 5kb for a total flanking region of 10kb).
+The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region.
+The positional coordinates of each functional genomic element, obtained from ENCODE, were then used to define the feature space of the models.
+
+## Figure 2: Predictor Types
+
+Diagram of the 3 predictor types considered when assessing the relationship between TAD boundaries and functional genomic elements.
+Each predictor type was used as the feature space in downstream analyses for predicting which functional genomic elements were associated with the formation of TAD boundaries.
+Featured above are bin-specific examples of the construction of each predictor type.
+(Left) The overlap count (OC) predictors were calculated by considering the total number of elemental regions that overlapped with each genomic bin.
+(Middle) The overlap percent (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin and dividing by the total bin width (either 5, 25, 50, or 100 kilobases given resolution of boundary data).
+(Right) The distance predictors were calculated by measuring the distance (in base pairs) from the center of each genomic bin to the center of the nearest elemental region of interest.
+The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective functional genomic element.
+
+## Figure 3: Ensemble Framework/Model Building Pipeline
+
+A diagram of the model building pipeline given an a combination of inputs from the ensemble framework.
+The data was split into a 7:3 training set to testing set ratio, the variable reduction technique of choice was implemented, and a random forest classification algorithm was performed.
+Each model was then validated on the same testing set.
+
+## Figure 4: Class Imbalance
+
+Barplots illustrating the class imbalance problem featured across each of the four different resolutions that were analyzed.
+Minority classes represent the number of genomic bins that contain a TAD boundary, while the majority classes represent the number of genomic bins that do not contain a TAD boundary.
+
+## Figure 11: Model Performances for all Resolutions
+
+Comparing model performances for TAD boundary data for all 4 resolutions.
+The four regions represent (from left to right; top to bottom) data at 5kb, 25kb, 50kb, and 100kb resolutions.
+Within each region, the rows represent the set of re-sampling techniques, while the columns represent the set of performance metrics that the models were evaluated on.
+Each plot compares 2 sets of models; one using LASSO regularization and one using Elastic-Net regularization.
+Within each set, each bar represents the performance of a model with a specific predictor type; either overlap counts (OC) in red, overlap percent (OP) in green, or distance in blue.
+
+# Figure 9: Comparing Performances
+
+Comparing performances of random forest classification algorithms, across TAD boundary data at each resolution for models using distance-type predictors, with elastic-net regularization and random under-sampling.
+Performances were aggregated by taking the average of each metric across 50 iterations of random under-sampling.
+
+# Figure 10: Comparing Variable Importances
+
+Variable importance plots for the top 15 most predictive functional genomic elements for each of the 4 different resolutions.
+The x-axis represents the standardized difference between the out-of-bag prediction accuracy after permuting each predictor variable, averaged across all trees.
+The greater the mean standardized difference, the more importance the predictor is to the model.
+
+# Supplementary Tables and Figures
+
+# Supplementary Legends
 

### 2018-11-27 Manuscript/manuscript.Rmd

@@
 
-+-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure1_model_construction.png)      |
-| **Figure 1.**     |
-+-------+
-
-+-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure2_predictor_types.png)      |
-| **Figure 2.**     |
-+-------+
-
-+-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure3_ensemble_framework.png)      |
-| **Figure 3.**     |
-+-------+
-
-+-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure4_class_imbalance_plots.png)      |
-| **Figure 4.**     |
-+-------+
-
-+-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure11_allresolutions_performances.png)      |
-| **Figure 11.**     |
-+-------+
-
-+-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure9_comparing_resolutions_barplot.png)      |
-| **Figure 9.**     |
-+-------+
-
-+-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure10_allresolutions_varimps.png)      |
-| **Figure 10.**     |
-+-------+
-
 # Table Legends

### 2018-11-28 Manuscript/manuscript.Rmd
fixed header

@@
 ---
-title: "Predictive modeling using genomic annotations"
-subtitle: "Pitfalls and Recommendations"
-author: "Spiro Stilianoudakis"
-date: "August 9, 2018"
-header-includes:
-    - \usepackage{setspace}\doublespacing
-    - \usepackage{amsmath}
+title: "Manuscript title"
+csl: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.ref/genomebiology.csl
 output: 
   word_document:
-    fig_caption: yes
-    fig_height: 3
-    fig_width: 2
-    toc: yes
-  pdf_document:
-    toc: yes
+    reference_docx: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.doc/NIH_grant_style.docx
 bibliography: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/References/references.bib
 ---
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-
-```
 
@@
 
+[???provide urls to download domain data]
 Topologically associating domain data for the GM12878 cell line was obtained using the arrowhead algorithm from the Juicer toolbox (https://github.com/aidenlab/juicer).
@@
 
+[??? Don't explicitly descript figure in paper; only results]
 Figure 1 presents a diagram of how the data was established for modeling purposes.
@@
 
-## Table 1.
-
-## Table 2.
-
-## Table 7.
-
 # Figures
@@
 
-# Figure 9: Comparing Performances
+## Figure 9: Comparing Performances
 
@@
 
-# Figure 10: Comparing Variable Importances
+## Figure 10: Comparing Variable Importances
 

### 2018-12-02 Manuscript/manuscript.Rmd
manuscript edits

@@
 title: "Manuscript title"
-csl: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.ref/genomebiology.csl
+#csl: styles.ref/genomebiology.csl
 output: 
   word_document:
-    reference_docx: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.doc/NIH_grant_style.docx
+    #reference_docx: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.doc/NIH_grant_style.docx
 bibliography: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/References/references.bib
@@
 We evaluated each ensemble system using 10-fold cross-validated random forest models.
-Thus, we generated 96 (=4x3x2x4) separate models.
+Thus, we generated 96 (=4 $\times$ 3 $\times$ 2 $\times$ 4) separate models.
 
@@
 
-Table 2 presents the class distributions across each resolution.
-After binning the genome at 5kb, 25kb, 50kb, and 10kb intervals there were a total of 44948, 9042, 4541, and 2279 genomic bins created respectively.
-Figure 4 illustrates the class imbalance problem present in each data resolution.
-Likewise, we see the apparent decrease in data points (bins) as resolution increases.
-Furthermore, Table 1 specifically shows the class distribution for each resolution.
-The overall average perentage of minority classes across all data resolutions was 13.2%, with the most severe case present in the 5kb resolution (6.9%).
+The coordinates of the corresponding 5kb resolution contact maps resulted in a total of 44948 genomic bins (Table 2).
+There were only 3083 bins that overlapped with a flanked TAD boundary (6.9%).
+An increase in resolution resulted in less genomic bins and a slighly less degree of class imbalance (Supplementaty Table 8).
+The overall average perentage of class imbalance across all data resolutions was 13.2%.
+After applying each resampling technique to the training sets for each data resolution, we obtained perfectly balanced classes (Figure 4).
+That is, the ratio of bins that overlapped with flanked TAD boundaries to bins that did not was 1:1.
 

### 2018-12-03 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-###CLASS IMBALANCE HINDERS PERFORMANCE ACROSS RESOLUTIONS
+###CLASS IMBALANCE HINDERS PERFORMANCE
 
-Figure 11 present the results across all of the ensemble systems for each resolution of domain data.
-The first row in each of the 4 regions shows the performances for models without resampling.
-The average accuracy and AUC were marginally high across each of the resolutions with values of W%, X%, Y%, and Z% respectively.
-However, the severity of the model performances were much more apparant when comparing F1-scores and MCCs.
-The average F1-scores across resolutions for models without resampling were found to be W%, X%, Y%, and Z% respectively, while the MCCs were W%, X%, Y%, and Z% (Table 7).
-We thus see the necessity for implementing a class balancing technique prior to modeling.
+We first compared models with either overlap counts or overlap percent predictor types, from the 5kb resolution data (Figure 12).
+These results were from random forest models fit to data without any re-sampling, using either LASSO or Elastic-Net regulariations.
+We found that differences in performances across variable reduction technique were marginal.
+However, when evaluating model performance using accuracy or AUC, the model appeared to perform relatively well.
+At second glance, though, when considering both the F1-score and MCC of the model, we were able to assess just how poorly the model was indeed performing (Supplementary Table 9).
+The low, and sometimes missing, values indicate that the model is unable to identify many, if any, true positive outcomes.
+That is, given an imbalanced data, the model is unable to predict which genomic bins truly contain a flanked TAD boundary.
+The performance results were found to be consistently poor for models with no re-sampling across the other resolutions (Supplementary Figure 13).
 
-###CLASS BALANCING IMPROVES MODEL PERFORMANCE IN ALL RESOLUTIONS
+###Random UNDER-SAMPLING IMPROVES MODEL PERFORMANCE IN ALL RESOLUTIONS
 

### 2018-12-03 Manuscript/manuscript.Rmd
Add to Abstract-results section

--- 2018-11-28 Manuscript/manuscript.Rmd
@@
 **Methods.** We propose a novel data pre-processing pipeline that addresses those shortcomings.
+Lasso and Elastic Net were used for feature selection, coupled with five classifier methods.
 A number of classifier performance metrics were assessed, including the F1 measure and Matthew Correlation Coefficient (MCC), and area under the ROC curve (AUROC).
@@
 **Results.** Data preprocessing (log2-transformation and standardization) improves the performance of classification algorithms and allows for the ability to more accurately predict which genomic features are most associated with TAD boundaries.
+In contrast to overlap-based association measures, distance between genomic elements appears to be the most predictive measure.
+Random undersampling strategy addresses the class imbalance problem the most effectively in nearly all settings.
 

### 2018-12-03 Manuscript/manuscript.Rmd
Edit title, fine tuning abstract

@@
 ---
-title: "Manuscript title"
+title: "Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings"
 csl: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.ref/genomebiology.csl
@@
 ---
+
+Spiro C. Stilianoudakis^1^ (stilianoudasc@mymail.vcu.edu), Mikhail G. Dozmorov^1\*^ (mikhail.dozmorov@vcuhealth.org)
+
+^1^ Dept. of Biostatistics, Virginia Commonwealth University, Richmond, VA, 23298, USA  
+^\*^ To whom correspondence should be addressed: Virginia Commonwealth University, Richmond, VA, 23298, 804-827-2055, mikhail.dozmorov@vcuhealth.org
 
@@
 **Results.** Data preprocessing (log2-transformation and standardization) improves the performance of classification algorithms and allows for the ability to more accurately predict which genomic features are most associated with TAD boundaries.
-In contrast to overlap-based association measures, distance between genomic elements appears to be the most predictive measure.
-Random undersampling strategy addresses the class imbalance problem the most effectively in nearly all settings.
+In contrast to overlap-based association measures, the distance between genomic elements was the most predictive measure.
+The random undersampling strategy addresses the class imbalance problem the most effectively in nearly all settings.
 
@@
 Models applied to unprocessed data can have poor predictive performances.
-Focusing solely on typical performance assessment metrics, such as AUROC, can mask poor performance of the models; thus, the use of more balanced metrics, such as F1 and MCC, is warranted.
+Focusing solely on standard performance assessment metrics, such as AUROC, can mask poor performance of the models; thus, the use of more balanced metrics, such as F1 and MCC, is warranted.
 Our model results in better performances and more accurate identification of important features associated with the formation of TAD boundaries.

### 2018-12-03 Manuscript/manuscript.Rmd

--- 2018-12-03 Manuscript/manuscript.Rmd
@@
 ---
-title: "Manuscript title"
-#csl: styles.ref/genomebiology.csl
+title: "Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings"
+csl: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.ref/genomebiology.csl
 output: 
@@
 **Results.** Data preprocessing (log2-transformation and standardization) improves the performance of classification algorithms and allows for the ability to more accurately predict which genomic features are most associated with TAD boundaries.
+In contrast to overlap-based association measures, the distance between genomic elements was the most predictive measure.
+The random undersampling strategy addresses the class imbalance problem the most effectively in nearly all settings.
 

### 2018-12-03 Manuscript/manuscript.Rmd
manuscript edits

@@
 ---
-title: "Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings"
-csl: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.ref/genomebiology.csl
+title: "Manuscript title"
+#csl: styles.ref/genomebiology.csl
 output: 
@@
 ---
-
-Spiro C. Stilianoudakis^1^ (stilianoudasc@mymail.vcu.edu), Mikhail G. Dozmorov^1\*^ (mikhail.dozmorov@vcuhealth.org)
-
-^1^ Dept. of Biostatistics, Virginia Commonwealth University, Richmond, VA, 23298, USA  
-^\*^ To whom correspondence should be addressed: Virginia Commonwealth University, Richmond, VA, 23298, 804-827-2055, mikhail.dozmorov@vcuhealth.org
 
@@
 **Methods.** We propose a novel data pre-processing pipeline that addresses those shortcomings.
-Lasso and Elastic Net were used for feature selection, coupled with five classifier methods.
 A number of classifier performance metrics were assessed, including the F1 measure and Matthew Correlation Coefficient (MCC), and area under the ROC curve (AUROC).
@@
 **Results.** Data preprocessing (log2-transformation and standardization) improves the performance of classification algorithms and allows for the ability to more accurately predict which genomic features are most associated with TAD boundaries.
-In contrast to overlap-based association measures, the distance between genomic elements was the most predictive measure.
-The random undersampling strategy addresses the class imbalance problem the most effectively in nearly all settings.
 
@@
 Models applied to unprocessed data can have poor predictive performances.
-Focusing solely on standard performance assessment metrics, such as AUROC, can mask poor performance of the models; thus, the use of more balanced metrics, such as F1 and MCC, is warranted.
+Focusing solely on typical performance assessment metrics, such as AUROC, can mask poor performance of the models; thus, the use of more balanced metrics, such as F1 and MCC, is warranted.
 Our model results in better performances and more accurate identification of important features associated with the formation of TAD boundaries.
@@
 These results were from random forest models fit to data without any re-sampling, using either LASSO or Elastic-Net regulariations.
-We found that differences in performances across variable reduction technique were marginal.
-However, when evaluating model performance using accuracy or AUC, the model appeared to perform relatively well.
-At second glance, though, when considering both the F1-score and MCC of the model, we were able to assess just how poorly the model was indeed performing (Supplementary Table 9).
+We found that differences in performances across variable reduction techniques were marginal.
+More importantly, when evaluating model performance using accuracy or AUC, the model appeared to perform relatively well.
+At second glance, however, when considering both the F1-score and MCC, we were able to assess just how poorly the model was performing (Supplementary Table 9).
+
+The performances were found to be consistently poor for models with no re-sampling across the other resolutions (Supplementary Figure 13; Supplementary Table 10).
 The low, and sometimes missing, values indicate that the model is unable to identify many, if any, true positive outcomes.
-That is, given an imbalanced data, the model is unable to predict which genomic bins truly contain a flanked TAD boundary.
-The performance results were found to be consistently poor for models with no re-sampling across the other resolutions (Supplementary Figure 13).
+That is, given imbalanced data, the model was unable to predict which genomic bins truly contain a flanked TAD boundary.
 
-###Random UNDER-SAMPLING IMPROVES MODEL PERFORMANCE IN ALL RESOLUTIONS
+###RANDOM UNDER-SAMPLING IMPROVES MODEL PERFORMANCE
 
-Moving down the rows in each of the 4 regions of Figure 11 we see that model performance was markedly improved among the F1-scores and MCCs after creating balanced classes compared to the results using no re-sampling.
-For each of the resolutions, we see that random under-sampling out performed the other class balancing techniques.
-While SMOTE performed very similarly to RUS, ROS performed poorly in comparison, especially as the resolution of the data increased.
-Furthermore, we see that the elastic-net reduction technique outperformed the LASSO.
-Although, the disparity became less evident as the resolution increased.
+When evaluatating the 5kb resolution data for a randomly under-sampled training set, it was found that models obtained better classification performance for F1 and MCC metrics (Figure 14).
+The increase in performance was present across both overlap predictor types.
+Models also featured a decrease in both accuracy and AUC, which was attributed to less inflated false negative rates (Supplementary Table 11).
+Differences in performances were again marginal across the two variable reduction techniques.
+Performances were also improved among the models using the other data resolutions.
+However, model improvement dissipated as resolution increased (Supplementary Figure 15; Supplementary Table 12).
 

### 2018-12-03 Manuscript/manuscript.Rmd
manuscript edits

@@
 The F1-score and MCC are more balanced measures.
-We also considered the AUC for each model, by computing the average trapezoidal approximations for the curve created by the true positive rates (TPR) and false positive rates (FPR)
+We also considered the AUC for each model, by computing the average trapezoidal approximations for the curve created by the true positive rates (TPR) and false positive rates (FPR).
 
@@
 Thus, we generated 96 (=4 $\times$ 3 $\times$ 2 $\times$ 4) separate models.
+For simplicity, we have only presented the most significant results.
+Results of the complete ensemble are available in the Supplementary Materials.
 
@@
 Models also featured a decrease in both accuracy and AUC, which was attributed to less inflated false negative rates (Supplementary Table 11).
-Differences in performances were again marginal across the two variable reduction techniques.
-Performances were also improved among the models using the other data resolutions.
+Variable reduction was found not to have an affect on resampling, and subsequent performance as any differences were again marginal.
+Performances were also improved among the models using the other data resolutions as well.
 However, model improvement dissipated as resolution increased (Supplementary Figure 15; Supplementary Table 12).
@@
 ###DISTANCE TYPE PREDICTORS OUT-PERFORM OTHER PREDICTOR TYPES
+
+Lastly, we evaluated models when using distance type predictors for the feature space.
+For the 5kb resolution data, tt was found that models with distance type predictors out performed models with count overlaps types across resolutions (Figure ).
+
+This result was also observed when compared to models with percent overlap type predictors, regardless of the variable reduction technique used (Supplementary Table).
+The differences in performances was found to be most severe when looking at the F1-score and MCC (Supplementary Table).
 

### 2018-12-03 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-Lastly, we evaluated models when using distance type predictors for the feature space.
-For the 5kb resolution data, tt was found that models with distance type predictors out performed models with count overlaps types across resolutions (Figure ).
+We then used the ensemble to compare models with distance type predictors for the feature space.
+For the 5kb resolution data, it was found that models with distance type predictors out performed models with either of the two overlap types (Figure 16).
+The improvement was observed across all 4 performance metrics that were considered (Supplementary Table 13).
+Likewise, improved performances were seen in the other 3 resolutions as well.
+Although overall performance decreased as resolution increased, models with distance type predictors still were able to maintain a profound improvement (Supplementary Figure 14;Supplementary Table 14).
 
-This result was also observed when compared to models with percent overlap type predictors, regardless of the variable reduction technique used (Supplementary Table).
-The differences in performances was found to be most severe when looking at the F1-score and MCC (Supplementary Table).
+###PERFORMANCES DEGRADE AS RESOLUTION INCREASES
 
-Again referencing Figure 11, focusing on the rows corresponding to models using randomly under-sampled data, it was found that models with distance type predictors out performed models with the two other overlap types (counts and percents).
-The disparity between predictor types was steady across resolutions (Table 7).
-The greatest difference was seen in the 5kb data.
-For models with Elastic-Net regularization, the F1-scores were X, Y, and Z, while the MCCs were X, Y, and Z for each predictor type respectively.
+Finally, we directly compared the performances of models across the different resolutions.
+The comparisons consisted of random forest models using distance type predictors, elastic-net regularization, and 50 iterations of random under-sampling.
+The model using 5kb resolution domain data was found to perform slightly better compared to the 25kb and 50kb resolutions (Figure 9).
+A sharp decrease in performance was seen in the 100kb resolution.
 
-###PERFORMANCES WORSEN AS RESOLUTION INCREASES
-
-Figure 9 compares the results of random forest models using distance-type predictors, with elastic-net regularization, and random under-sampling, across each domain data resolution.
-We see that the results for F1-scores are relatively stable between 5kb, 25kb, and 50kb resolutions with a sharp decrease for the 100kb resolution.
-Furthermore, the decrease in performance is more evident and steady across accuracy, AUC, and MCC metrics.
-
-###5kb RESOULTION DATA PROVIDES MOST ACCURATE ACCURATE RESULTS
-
-To identify the functional genomic elements that were most predictive of TAD boundaries, we analyzed the variable importance produced by each random forest algorithm.
-Figure 10 presents the subsequent scaled importance plots of the top 15 most predictive genomic elements for each model presented in Figure 9.
-We see that for the 5kb resolution, the most predictive elements include insulator proteins, DNase hypersensitive sites, the transcription factor CTCF, as well as histone modifications H3k9ac, H2az, and H3k4me2.
-These results align with what is seen in the literature.
-Although, the insulator protein is featured as a top predictor in 2 of the other 3 resolutions, the rest of the predictors are less consistent among each other and less in agreement with the literature.
-The results from Figure 9 and 10 confirm that the model results appear to degrade as resolution increases with respect to both prediction and the identification of genomic elements associated with TAD boundaries.
+The differences in performances was most evident when analyzing the variable importance plots for each model using the 4 resolutions.
+We found that when we analyzed the variable importance produced by each random forest algorithm.
+We found that for the 5kb resolution, the most predictive elements include insulator proteins, DNase hypersensitive sites, the transcription factor CTCF, as well as histone modifications H3k9ac, H2az, and H3k4me2 (Figure 10 A).
+Although, the insulator protein is featured as a top predictor in 2 of the other 3 resolutions, the rest of the predictors are less consistent among each other and less in agreement with the literature (Figure 10 B-D).
+The results from Figures 9 and 10 confirm that the model results appear to degrade as resolution increases with respect to both prediction and the identification of genomic elements associated with TAD boundaries.
 

### 2018-12-03 Presentation/Abstract_MSU.Rmd

--- 2018-12-03 Manuscript/manuscript.Rmd
@@
 ---
-title: "Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings"
+title: Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance
+  Settings
+output:
+  pdf_document: default
+  word_document: default
 csl: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.ref/genomebiology.csl
-output: 
-  word_document:
-    #reference_docx: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.doc/NIH_grant_style.docx
-bibliography: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/References/references.bib
 ---
@@
 ^1^ Dept. of Biostatistics, Virginia Commonwealth University, Richmond, VA, 23298, USA
-^\*^ To whom correspondence should be addressed: Virginia Commonwealth University, Richmond, VA, 23298, 804-827-2055, mikhail.dozmorov@vcuhealth.org
 
@@
 Our model results in better performances and more accurate identification of important features associated with the formation of TAD boundaries.
-
-# INTRODUCTION
-
-The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect several epigenetic functions [@lieberman2009comprehensive].
-Analyses have shown that the genome is tightly compacted into distinct compartments.
-There exist regions within these compartments that have been shown to be highly conserved and self-interacting, and termed topologically associating domains (TADs) [@dixon2012topological].
-Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD [@symmons2014functional].
-This suggests that the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
-Furthermore, changing the 3D structure of the DNA, causing disruptions in these domains can lead to adverse outcomes and diseases like cancer.
-Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.
-
-The mechanisms underlying the formation of TADs are a complex and active area of research.
-Recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangements of higher-order chromatin architecture [@phillips2013chromatin].
-Insulators are multi-faceted regulatory sequences that moderate a variety of genomic processes including activation, repression, and enhancer blocking.
-Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long-range chromatin contacts [@zuin2014cohesin].
-Other regulatory elements like particular histone modifications such as H3k36 and H3K27 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [@rao20143d].
-These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
-The distinct patterns of some of these different proteins and functional elements point toward the opportunity of using computational approaches in identifying which epigenomic features are most predictive of the development of TAD boundaries.
-This will allow us to better understand what leads to their formation.
-
-Most accepted methods for predicting TAD boundaries consider performing a classification algorithm by binning the genome into equal-sized bins and labeling them as either containing a TAD boundary or not.
-However, a pervasive issue becomes the introduction of highly imbalanced classes.
-Due to the sparcity of TADs throughout the genome, most bins will not contain a TAD boundary.
-Therefore, the minority class of genomic bins with TAD boundaries in them becomes proportionally smaller than that of the majority class of genomic bins with no TAD boundaries.
-It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@estabrooks2004multiple].
-However, a clear method for creating balanced classes remains evasive and largely dependent on the problem at hand.
-For that reason we evaluated 3 widely accepted class balancing techniques, in addition to no balancing.
-They included random under-sampling, random over-sampling, and synthetic minority over-sampling technique (SMOTE).
-
-Model performance is also contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
-This will also affect the size of the genomic bins used in model construction.
-A larger resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
-This will contribute to smaller sample sizes and could effect predictive performances.
-
-Another problem lies in identifying the feature space of subsequent classification algorithms.
-A variety of positional characteristics of the genomic features can be used to describes the relationship between TAD boundaries and genomic elements, but it is unclear which is best.
-The use of distances (in base pairs) from genomic bins to regions of functional genomic elements has largely been ignored.
-However, these distance characteristics offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
-
-Due to the increasingly large amounts of functional genomic elements to consider, it is a popular approach in genomic studies to use variable reduction techniques to reduce the noise induced by noninformative predictors and increase computational efficiency.
-Two popular approaches use the $l_{1}$ norm (LASSO) and a combination of the $l_{1}$ and $l_{2}$ norms together (Elastic-Net).
-While both regularization techniques have merit, LASSO’s inability to handle correlated predictors poses a problem when identifying which element are most predictive of TAD boundaries.
-The elastic-net, however, is better suited in a situation where multiple genomic elements colocalize around the same TAD boundaries, and could be better suited for this type of alaysis [@zou2005regularization].
-
-Careful consideration must also be taken when deciding which performance metric(s) to present when evaluating predictive models.
-A common metric to consider is the the area under the ROC curve (AUC), as well as others including accuracy, sensitivity, and specificity.
-
-The popularity surrounding the use of ROC curves is that they do not depend on a threshold.
-However, when the prevalence of an event is low--that is, a genomic bin containing a TAD boundary--mean probabilities are biased towards the majority class.
-Likewise, metrics like accuracy and sensitivity and specificity do not incorporate the entirety of the confusion matrix created when validating predictive models on a test data set.
-Therefore, each of these metrics are likely to be inflated when evaluating model performance on imbalanced data.
-More robust metrics like the F1-score and Matthew's Correlation Coefficient are more suitable for this type of analysis and can highlight problems associated with applying predictive models on imbalanced data.
-
-[Mention Previous Methods]
-
-In this study we have developed an ensemble framework that aims to address and compare a variety of data irregularities and characteristics that are associated with the prediction of TAD boundaries.
-We evaluated domain data obtained from four different resolution contact matrices for the GM12878 cell line including 5kb, 25kb, 50kb, and 100kb.
-For each resolution, we examined the inclusion of three different predictor types as the feature space for downstream modeling.
-We coupled each predictor type with two separate variable reduction techniques.
-Lastly, we performed a series of three different re-sampling techniques aimed at created balanced classes.
-Random forest classification algorithms were performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the formation of TAD boundaries.
-Model performance was evaluated based on a total of four metrics which included test accuracy, area under the ROC curve (AUC), F1 score, and Matthew's Correlation Coefficient (MCC).
-
-#METHODS
-
-##DOMAIN DATA
-
-[???provide urls to download domain data]
-Topologically associating domain data for the GM12878 cell line was obtained using the arrowhead algorithm from the Juicer toolbox (https://github.com/aidenlab/juicer).
-Publically available domain data was obtained from in situ Hi-C contact matrices at 5kb resolution [@rao20143d].
-Additional domain data was obtained from Dali et al.
-at 25kb, 50kb, and 100kb resolutions [@dali2017critical].
-
-Identified TAD boundaries were represented by their location in the genome (hg19 human genome assembly), including chromosome, start and end coordinates for chromosomes 1 through 22.
-The start and end coordinates were concatenated, sorted, and unique coordinates representing the borders demarcating TADs were obtained.
-
-[??? Don't explicitly descript figure in paper; only results]
-Figure 1 presents a diagram of how the data was established for modeling purposes.
-First, the genome was binned into equally sized intervals.
-This was performed at the same resolution of the contact matrix that the domain data was obtained from.
-For example, for the domain data obtained from a 5kb resolution contact matrix, the genome was subsequently binned into 5kb intervals.
-The same processes was repeated for each of the other three resolutions.
-Next, the boundary coordinates were flanked on either side by a unit corresponding to the resolution of the particular domain data.
-Again, siting the domain data obtained from a 5kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 5kb for a total width around each boundary point of 10kb.
-The same process was repeated for the other three resolutions.
-A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
-Otherwise, the bin was labeled as not containing a boundary (Y=0).
-
-##GENOMIC ANNOTATIONS
-
-Annotation data, in the form of functional genomic elements from ChIP-seq experiments were obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium.
-The annotations consisted of a variety of different chromatin states, histone marks, and DNase I hypersensitive sites.
-Table 1 presents the total list of genomic  annotations considered in this study and the sources of downloadable files.
-Each annotation was represented by their location throughout the genome via chromosomal coordinates.
-An example of a specific annotation, which is labeled as a functional genomic element, is presented in Figure 2.
-It is represented by the green segments that overlap with the genomic bins.
-
-##Feature Engineering
-
-Using each genomic element, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries in downstream modelling.
-Figure 2 presents an illustration of each type of predictor that was considered.
-The predictors consisted of two different types of overlaps, and a distance type.
-They are described in detail below:
-
-   1.	Overlap Counts (OC): For each genomic bin, the total number of overlapped regions between a functional genomic element and a bin was calculated.
-This was defined as the overlap counts (OC) and is illustrated in the left part of Figure 2.
-Within each bin (marked by the blue dashed lines), the total number of overlapped regions of the genomic element (represented by the horizontal green segments) are tallied and marked below.
-In the case of no overlaps the value is given as 0.
-
-   2.	Overlap Percent (OP): For each genomic bin, the percent overlap between regions defined by a particular functional element and a bin was calculated.
-From the middle diagram of Figure 2, the feature width was defined as the number of base pairs that overlapped with the genomic bin.
-The percent was then calculated by dividing the feature width with the bin width.
-If multiple overlaps existed, the feature width was defined as the sum of the total number of base pairs that overlapped with a particular bin.
-Note that the bin width remained constant for a given resolution (either 5kb, 25kb, 50kb, or 100kb).
-Similar to the OC predictor type, bins with no overlaps were given to be 0.
-
-   3.	Distance: For each genomic bin, the distance (in base pairs) from the center of the bin to the center of the nearest region of a respective functional element was calculated.
-The right most diagram of Figure 2 depicts an example of how distance was calculated.
-The vertical green segments represent the centers of the respective genomic element.
-Each distance, $D_{i}$, represented by the blue brackets are the number of base pairs from the center of the bins to the center of the nearest genomic elemental region.
-
-[Mention transformations used]
-
-##ENSEMBLE FRAMEWORK
-
-Figure 3 details the ensemble framework proposed and evaluated in this study.
-For each resolution and predictor type chosen, the data was split into training to testing sets.
-A variable reduction technique was then performed.
-The feature space was reduced and a resampling technique was applied.
-Lastly, a classification algorithm in the form of a random forest was performed and validated.
-Details of each step in the framework are provided below.
-
-###Training and Testing Sets
-
-Given a particular resolution, the full data set was composed of genomic bins that either overlapped with a flanked TAD boundary (minority set) or did not (majority set).
-Figure 3 highlights the severe class imbalance present in both the full data set.
-The data was then split into a 7:3 ratio of training to testing sets.
-Each training and testing set was composed of a similar majority to minority class ratio as the full data set, which is represented by the segmented regions in Figure 3.
-The training set was then used to perform all downstream modeling.
-The same test set was held separate and used to validate all models.
-
-###Variable Reduction
-
-We evaluated the use of two variable reduction algorithms, the LASSO and Elastic-Net regularizations.
-Each algorithm was performed prior to re-sampling.
-For the LASSO, the $\lambda$ penalization term was tuned over a grid of 10 values on an exponential scale ranging from 0.01 to 10.
-The additional $\alpha$ term for the Elastic-Net was tuned over 10 equa-distant values from 0 to 1.
-
-###Re-Sampling Techniques
-
-After choosing one of the aforementioned data resolutions, predictor types, and variable reduction algorithms, we then evaluated three re-sampling techniques used to create balanced classes.
-For each resampling technique, the majority class is defined as the set of genomic bins that did not include a TAD boundary, while the minority class is defined as the set of bins that included a TAD boundary.
-The following details the re-sampling techniques considered in this paper:
-
-   1.	No Sampling: All of the data points from the majority and minority class of the training set were used.
-
-   2.	Random Under-Sampling: All of the minority classes from the training set were used.
-A random set without replacement from the majority classes of the training set were used to match the number of minority samples.
-In this paper we performed 50 iterations of random under-sampling.
-At each iteration a random forest classification algorithm was performed.
-Performance metrics were aggregated by taking the average across all of the iterations.
-
-   3.	Random Over-Sampling: All of the majority classes from the training set were used.
-A random set with replacement from the minority classes of the training set were used to match the number of majority samples.
-Similar to the under-sampling technique, 50 iterations were performed and results were aggregated by taking the average across iterations.
-
-   4.	SMOTE (Synthetic Minority Over-Sampling Technique): This method incorporated both random under- and over-sampling.
-Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class.
-The SMOTE algorithm is stored in the DMwR package, available in R [@chawla2002smote].
-The user is able to specify the parameters denoting the percent of over- and under-sampling from the two classes.
-This allows the user to control the proportion of disbalance in the data.
-For the purposes of this paper, we used SMOTE to create perfectly balanced data.
-However further research would be needed to see if varying the proportion of class disbalance could improve predictive performance.
-
-###Classification
-
-A classification algorithm in the form of a random forest was performed and validated using the test set.
-10-fold cross validation was used to reduced bias due to random dataset generation.
-The default number of features to consider at each node of the random forest algorithm was set as the square root of the number of features in the model.
-Likewise, the number of ensemble trees to aggregate was set at 500.
-Once the model was implemented, it was assessed using the test set, and performance metrics were then recorded.
-
-Using set notation the formulation of the ensemble framework can be defined as follows:
-
-Set of different resolutions:
-
-R = {5kb, 25kb, 50kb, 100kb}
-
-Set of Predictor Types:
-
-P = {OC, OP, Distance}
-
-Set of Variable Reduction Techniques:
-
-V = {LASSO, Elastic-Net}
-
-Set of Class-Balancing Methods:
-
-C = {None, RUS, ROS, SMOTE}
-
-Therefore, a system produced from the ensemble framework is defined as follows:
-
-E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.
-
-Once a system was defined, a random forest algorithm was performed. Letting |X| denote the cardinality of each set, then we evaluated |R| x |P| x |V| x |C| different ensemble systems in this paper.
-
-###Model Evaluation
-
-The efficacy of different ensemble systems was compared using various performance metrics including accuracy, AUC, F1-score, and MCC. These metrics are defined as follows:
-
-$$
-\begin{equation}
-\begin{aligned}
-Accuracy &= \dfrac{TP + TN}{TP + TN + FP + FN} \\
-F1 - Score &= \dfrac{2TP}{2TP + FP + FN} \\
-MCC &= \dfrac{TP \times TN - FP \times FN}{\sqrt{ (TP + FP)(TP+FN)(TN+FP)(TN+FN) }}
-\end{aligned}
-\end{equation}
-$$
-Here, TP refers to the number of bins correctly identified as containing a TAD boundary (true positives), FP refers to the number of bins incorrectly identified as containing a TAD boundary (false positives), TN refers to the number of bins correctly identified as not containing a TAD boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a TAD boundary.
-Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-Accuracy measures the percentage of correct classifications by the model.
-However, in the case of heavily imbalanced class, as can be seen by the numerator, the metric is biased toward correcly identified majority classes.
-The F1-score and MCC are more balanced measures.
-We also considered the AUC for each model, by computing the average trapezoidal approximations for the curve created by the true positive rates (TPR) and false positive rates (FPR).
-
-#RESULTS
-
-##ENSEMBLE COMPARISONS
-
-In this section we provide the details of the comprehensive experiments performed in order to assess each ensemble system.
-For the task of predicting TAD boundaries using functional genomic elements, we evaluated 4 domain data sets, 3 predictor types, 2 variable reduction techniques, and 4 class balancing techniques.
-We evaluated each ensemble system using 10-fold cross-validated random forest models.
-Thus, we generated 96 (=4 $\times$ 3 $\times$ 2 $\times$ 4) separate models.
-For simplicity, we have only presented the most significant results.
-Results of the complete ensemble are available in the Supplementary Materials.
-
-###CLASS DISTRIBUTIONS ACROSS RESOLUTIONS
-
-The coordinates of the corresponding 5kb resolution contact maps resulted in a total of 44948 genomic bins (Table 2).
-There were only 3083 bins that overlapped with a flanked TAD boundary (6.9%).
-An increase in resolution resulted in less genomic bins and a slighly less degree of class imbalance (Supplementaty Table 8).
-The overall average perentage of class imbalance across all data resolutions was 13.2%.
-After applying each resampling technique to the training sets for each data resolution, we obtained perfectly balanced classes (Figure 4).
-That is, the ratio of bins that overlapped with flanked TAD boundaries to bins that did not was 1:1.
-
-###CLASS IMBALANCE HINDERS PERFORMANCE
-
-We first compared models with either overlap counts or overlap percent predictor types, from the 5kb resolution data (Figure 12).
-These results were from random forest models fit to data without any re-sampling, using either LASSO or Elastic-Net regulariations.
-We found that differences in performances across variable reduction techniques were marginal.
-More importantly, when evaluating model performance using accuracy or AUC, the model appeared to perform relatively well.
-At second glance, however, when considering both the F1-score and MCC, we were able to assess just how poorly the model was performing (Supplementary Table 9).
-
-The performances were found to be consistently poor for models with no re-sampling across the other resolutions (Supplementary Figure 13; Supplementary Table 10).
-The low, and sometimes missing, values indicate that the model is unable to identify many, if any, true positive outcomes.
-That is, given imbalanced data, the model was unable to predict which genomic bins truly contain a flanked TAD boundary.
-
-###RANDOM UNDER-SAMPLING IMPROVES MODEL PERFORMANCE
-
-When evaluatating the 5kb resolution data for a randomly under-sampled training set, it was found that models obtained better classification performance for F1 and MCC metrics (Figure 14).
-The increase in performance was present across both overlap predictor types.
-Models also featured a decrease in both accuracy and AUC, which was attributed to less inflated false negative rates (Supplementary Table 11).
-Variable reduction was found not to have an affect on resampling, and subsequent performance as any differences were again marginal.
-Performances were also improved among the models using the other data resolutions as well.
-However, model improvement dissipated as resolution increased (Supplementary Figure 15; Supplementary Table 12).
-
-###DISTANCE TYPE PREDICTORS OUT-PERFORM OTHER PREDICTOR TYPES
-
-We then used the ensemble to compare models with distance type predictors for the feature space.
-For the 5kb resolution data, it was found that models with distance type predictors out performed models with either of the two overlap types (Figure 16).
-The improvement was observed across all 4 performance metrics that were considered (Supplementary Table 13).
-Likewise, improved performances were seen in the other 3 resolutions as well.
-Although overall performance decreased as resolution increased, models with distance type predictors still were able to maintain a profound improvement (Supplementary Figure 14;Supplementary Table 14).
-
-###PERFORMANCES DEGRADE AS RESOLUTION INCREASES
-
-Finally, we directly compared the performances of models across the different resolutions.
-The comparisons consisted of random forest models using distance type predictors, elastic-net regularization, and 50 iterations of random under-sampling.
-The model using 5kb resolution domain data was found to perform slightly better compared to the 25kb and 50kb resolutions (Figure 9).
-A sharp decrease in performance was seen in the 100kb resolution.
-
-The differences in performances was most evident when analyzing the variable importance plots for each model using the 4 resolutions.
-We found that when we analyzed the variable importance produced by each random forest algorithm.
-We found that for the 5kb resolution, the most predictive elements include insulator proteins, DNase hypersensitive sites, the transcription factor CTCF, as well as histone modifications H3k9ac, H2az, and H3k4me2 (Figure 10 A).
-Although, the insulator protein is featured as a top predictor in 2 of the other 3 resolutions, the rest of the predictors are less consistent among each other and less in agreement with the literature (Figure 10 B-D).
-The results from Figures 9 and 10 confirm that the model results appear to degrade as resolution increases with respect to both prediction and the identification of genomic elements associated with TAD boundaries.
-
-#Discussion
-
-# Abbreviations
-
-# Acknowledgements
-
-_Conflict of Interest._ None.
-
-# Funding
-
-# Tables
-
-# Figures
-
-# Table Legends
-
-## Table 1: List of Genomic Annoations.
-
-The full list of genomic annotations used in downstream analyses.
-These annotations were the functional genomic elements used to predict the formation of TAD boundaries.
-They were obtained via ChIP-Seq experiments, mapped to human genome assembly hg19, and made available by the ENCODE Consortium.
-
-## Table 2: Class Distributions
-
-Summary of the class distributions for each re-sampling technique, across each resolution.
-All re-sampling techniques yielded completely balanced classes.
-That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.
-
-## Table 7: Model Performances at all Resolutions
-
-Performance metrics comparing models using different sampling approaches for each of the 4 resolutions.
-Withing each resolution, the best value in each column for each performance metric is underlined to compare different sampling approaches, while the highest value in each row is highlighted in bold to compare different predictor types.
-
-# Figure legends
-
-## Figure 1: Model Construction
-
-Diagram of the model construction used for downstream analysis.
-The linear genome was binned according to the resolution of the respective HiC experiment (either 5kb, 25kb, 50kb, or 100kb intervals).
-TAD boundaries were then flanked by 1-unit on either side of the boundary point.
-The unit flanking was indicative of the resolution that the domain data was obtained from (i.e.
-for 5kb resolution, 1 unit represents 5kb for a total flanking region of 10kb).
-The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region.
-The positional coordinates of each functional genomic element, obtained from ENCODE, were then used to define the feature space of the models.
-
-## Figure 2: Predictor Types
-
-Diagram of the 3 predictor types considered when assessing the relationship between TAD boundaries and functional genomic elements.
-Each predictor type was used as the feature space in downstream analyses for predicting which functional genomic elements were associated with the formation of TAD boundaries.
-Featured above are bin-specific examples of the construction of each predictor type.
-(Left) The overlap count (OC) predictors were calculated by considering the total number of elemental regions that overlapped with each genomic bin.
-(Middle) The overlap percent (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin and dividing by the total bin width (either 5, 25, 50, or 100 kilobases given resolution of boundary data).
-(Right) The distance predictors were calculated by measuring the distance (in base pairs) from the center of each genomic bin to the center of the nearest elemental region of interest.
-The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective functional genomic element.
-
-## Figure 3: Ensemble Framework/Model Building Pipeline
-
-A diagram of the model building pipeline given an a combination of inputs from the ensemble framework.
-The data was split into a 7:3 training set to testing set ratio, the variable reduction technique of choice was implemented, and a random forest classification algorithm was performed.
-Each model was then validated on the same testing set.
-
-## Figure 4: Class Imbalance
-
-Barplots illustrating the class imbalance problem featured across each of the four different resolutions that were analyzed.
-Minority classes represent the number of genomic bins that contain a TAD boundary, while the majority classes represent the number of genomic bins that do not contain a TAD boundary.
-
-## Figure 11: Model Performances for all Resolutions
-
-Comparing model performances for TAD boundary data for all 4 resolutions.
-The four regions represent (from left to right; top to bottom) data at 5kb, 25kb, 50kb, and 100kb resolutions.
-Within each region, the rows represent the set of re-sampling techniques, while the columns represent the set of performance metrics that the models were evaluated on.
-Each plot compares 2 sets of models; one using LASSO regularization and one using Elastic-Net regularization.
-Within each set, each bar represents the performance of a model with a specific predictor type; either overlap counts (OC) in red, overlap percent (OP) in green, or distance in blue.
-
-## Figure 9: Comparing Performances
-
-Comparing performances of random forest classification algorithms, across TAD boundary data at each resolution for models using distance-type predictors, with elastic-net regularization and random under-sampling.
-Performances were aggregated by taking the average of each metric across 50 iterations of random under-sampling.
-
-## Figure 10: Comparing Variable Importances
-
-Variable importance plots for the top 15 most predictive functional genomic elements for each of the 4 different resolutions.
-The x-axis represents the standardized difference between the out-of-bag prediction accuracy after permuting each predictor variable, averaged across all trees.
-The greater the mean standardized difference, the more importance the predictor is to the model.
-
-# Supplementary Tables and Figures
-
-# Supplementary Legends
-
-# References

### 2018-12-03 Manuscript/manuscript.Rmd
manuscript edits

@@
 This suggests that the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
-Furthermore, changing the 3D structure of the DNA, causing disruptions in these domains can lead to adverse outcomes and diseases like cancer.
+Furthermore, changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer.
 Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.
@@
 
-Most accepted methods for predicting TAD boundaries consider performing a classification algorithm by binning the genome into equal-sized bins and labeling them as either containing a TAD boundary or not.
+Most accepted methods for predicting TAD boundaries consider performing a classification algorithm by binning the genome into equal-sized bins and labeling them as either overlapping with a flanked TAD boundary or not.
 However, a pervasive issue becomes the introduction of highly imbalanced classes.
@@
 They included random under-sampling, random over-sampling, and synthetic minority over-sampling technique (SMOTE).
-
-Model performance is also contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
-This will also affect the size of the genomic bins used in model construction.
-A larger resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
-This will contribute to smaller sample sizes and could effect predictive performances.
 
@@
 
+Model performance is also contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
+This will also affect the size of the genomic bins used in model construction.
+A larger resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
+This will contribute to smaller sample sizes and could effect predictive performances.
+
 Careful consideration must also be taken when deciding which performance metric(s) to present when evaluating predictive models.
@@
 More robust metrics like the F1-score and Matthew's Correlation Coefficient are more suitable for this type of analysis and can highlight problems associated with applying predictive models on imbalanced data.
-
-[Mention Previous Methods]
 
@@
 
-[???provide urls to download domain data]
 Topologically associating domain data for the GM12878 cell line was obtained using the arrowhead algorithm from the Juicer toolbox (https://github.com/aidenlab/juicer).
@@
 
-[??? Don't explicitly descript figure in paper; only results]
-Figure 1 presents a diagram of how the data was established for modeling purposes.
-First, the genome was binned into equally sized intervals.
+To establish the data for modeling, the genome was binned into equally sized intervals (Figure 1).
 This was performed at the same resolution of the contact matrix that the domain data was obtained from.

### 2018-12-04 Manuscript/manuscript.Rmd
manuscript edits

@@
 It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@estabrooks2004multiple].
-However, a clear method for creating balanced classes remains evasive and largely dependent on the problem at hand.
-For that reason we evaluated 3 widely accepted class balancing techniques, in addition to no balancing.
-They included random under-sampling, random over-sampling, and synthetic minority over-sampling technique (SMOTE).
+A clear method for creating balanced classes remains evasive and largely dependent on the problem at hand.
 
 Another problem lies in identifying the feature space of subsequent classification algorithms.
-A variety of positional characteristics of the genomic features can be used to describes the relationship between TAD boundaries and genomic elements, but it is unclear which is best.
+A variety of positional characteristics of the genomic features can be used to describe the relationship between TAD boundaries and genomic elements, but it is unclear which is best.
 The use of distances (in base pairs) from genomic bins to regions of functional genomic elements has largely been ignored.
@@
 The popularity surrounding the use of ROC curves is that they do not depend on a threshold.
-However, when the prevalence of an event is low--that is, a genomic bin containing a TAD boundary--mean probabilities are biased towards the majority class.
+However, when the prevalence of an event is low--that is, a genomic bin overlapping with a TAD boundary region--mean probabilities are biased towards the majority class.
 Likewise, metrics like accuracy and sensitivity and specificity do not incorporate the entirety of the confusion matrix created when validating predictive models on a test data set.
@@
 
-Topologically associating domain data for the GM12878 cell line was obtained using the arrowhead algorithm from the Juicer toolbox (https://github.com/aidenlab/juicer).
-Publically available domain data was obtained from in situ Hi-C contact matrices at 5kb resolution [@rao20143d].
-Additional domain data was obtained from Dali et al.
-at 25kb, 50kb, and 100kb resolutions [@dali2017critical].
+Replicate Hi-C data for the GM12878 cell line were downloaded from GEO GSE63525 (Experiments HIC001 to HIC029) [@rao20143d].
+The chromosomal coordinates of topologically associating domains throughout the genome were obtained using the arrowhead algorithm from the Juicer toolbox provided by the Aiden Laboratory (https://github.com/aidenlab/juicer) [@durand2016juicebox].
+Using the juicer toolbox, we were able to call TADs on 4 different contact matrix resolutions, which included 5 kb, 25 kb, 50 kb, and 100 kb.
+Identified TAD boundaries were represented by their location on the linear genome (hg19 human genome assembly), including start and end coordinates for chromosomes 1 through 22 (Figure 18 A).
+The start and end coordinates of all hierarchical TADs were concatenated, sorted, and unique boundary points representing the borders demarcating TADs were obtained (Figure 18 B).
 
-Identified TAD boundaries were represented by their location in the genome (hg19 human genome assembly), including chromosome, start and end coordinates for chromosomes 1 through 22.
-The start and end coordinates were concatenated, sorted, and unique coordinates representing the borders demarcating TADs were obtained.
+##MODEL CONSTRUCTION
 
-To establish the data for modeling, the genome was binned into equally sized intervals (Figure 1).
+To establish the data for modeling, the genome was binned into equally sized intervals (Figure 18 C).
 This was performed at the same resolution of the contact matrix that the domain data was obtained from.
@@
 Next, the boundary coordinates were flanked on either side by a unit corresponding to the resolution of the particular domain data.
-Again, siting the domain data obtained from a 5kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 5kb for a total width around each boundary point of 10kb.
+For example, for the domain data obtained from a 5kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 5kb for a total width around each boundary point of 10kb.
 The same process was repeated for the other three resolutions.
@@
 
-Annotation data, in the form of functional genomic elements from ChIP-seq experiments were obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium.
+Annotation data, in the form of functional genomic elements from ChIP-seq experiments were obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium (Table 1).
 The annotations consisted of a variety of different chromatin states, histone marks, and DNase I hypersensitive sites.
-Table 1 presents the total list of genomic  annotations considered in this study and the sources of downloadable files.
 Each annotation was represented by their location throughout the genome via chromosomal coordinates.
-An example of a specific annotation, which is labeled as a functional genomic element, is presented in Figure 2.
-It is represented by the green segments that overlap with the genomic bins.
 
-##Feature Engineering
+###FEATURE ENGINEERING USING GENOMIC ANNOTATIONS
 
-Using each genomic element, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries in downstream modelling.
-Figure 2 presents an illustration of each type of predictor that was considered.
+Using each genomic element, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries in downstream modelling (Figure 2).
 The predictors consisted of two different types of overlaps, and a distance type.
@@
 Each distance, $D_{i}$, represented by the blue brackets are the number of base pairs from the center of the bins to the center of the nearest genomic elemental region.
-
-[Mention transformations used]
 

### 2018-12-04 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-Using each genomic element, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries in downstream modelling (Figure 2).
+Using each genomic element, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries in downstream modelling.
 The predictors consisted of two different types of overlaps, and a distance type.
@@
 Within each bin (marked by the blue dashed lines), the total number of overlapped regions of the genomic element (represented by the horizontal green segments) are tallied and marked below.
-In the case of no overlaps the value is given as 0.
+In the case of no overlaps the value is given as 0 (Figure 2 A).
 
@@
 Note that the bin width remained constant for a given resolution (either 5kb, 25kb, 50kb, or 100kb).
-Similar to the OC predictor type, bins with no overlaps were given to be 0.
+Similar to the OC predictor type, bins with no overlaps were given to be 0 (Figure 2 B).
 
@@
 The vertical green segments represent the centers of the respective genomic element.
-Each distance, $D_{i}$, represented by the blue brackets are the number of base pairs from the center of the bins to the center of the nearest genomic elemental region.
+Each distance, $D_{i}$, represented by the blue brackets are the number of base pairs from the center of the bins to the center of the nearest genomic elemental region (Figure 2 C).
 
@@
 
-Figure 3 details the ensemble framework proposed and evaluated in this study.
-For each resolution and predictor type chosen, the data was split into training to testing sets.
-A variable reduction technique was then performed.
-The feature space was reduced and a resampling technique was applied.
-Lastly, a classification algorithm in the form of a random forest was performed and validated.
+An ensemble of models was established for the purposes of directly comparing the performances of different parameters in the framework.
+Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type as the feature space.
 Details of each step in the framework are provided below.
@@
 
-Given a particular resolution, the full data set was composed of genomic bins that either overlapped with a flanked TAD boundary (minority set) or did not (majority set).
-Figure 3 highlights the severe class imbalance present in both the full data set.
-The data was then split into a 7:3 ratio of training to testing sets.
-Each training and testing set was composed of a similar majority to minority class ratio as the full data set, which is represented by the segmented regions in Figure 3.
+The data set used for modeling was composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
+These two classes made up the majority and minority sets (Figure 3 A).
+The data was then split into a 7:3 ratio of training to testing sets (Figure 3 B).
+Each training and testing set was composed of a similar majority to minority class ratio as the full data set (Figure 3 C).
 The training set was then used to perform all downstream modeling.
-The same test set was held separate and used to validate all models.
 
@@
 
-We evaluated the use of two variable reduction algorithms, the LASSO and Elastic-Net regularizations.
+We evaluated the use of two variable reduction algorithms, the LASSO and Elastic-Net regularizations (Figure 3 D).
 Each algorithm was performed prior to re-sampling.
@@
 
-After choosing one of the aforementioned data resolutions, predictor types, and variable reduction algorithms, we then evaluated three re-sampling techniques used to create balanced classes.
-For each resampling technique, the majority class is defined as the set of genomic bins that did not include a TAD boundary, while the minority class is defined as the set of bins that included a TAD boundary.
-The following details the re-sampling techniques considered in this paper:
+We then evaluated three re-sampling techniques (in addition to no re-sampling) used to create balanced classes (Figure 3 E). They are detailed below:
 
@@
 
-A classification algorithm in the form of a random forest was performed and validated using the test set.
+A classification algorithm in the form of a random forest was performed and validated using the same test set for all models in the ensemble (Figure 3 F).
 10-fold cross validation was used to reduced bias due to random dataset generation.

### 2018-12-05 Manuscript/manuscript.Rmd
manuscript edits

@@
 title: "Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings"
-csl: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.ref/genomebiology.csl
+#csl: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.ref/genomebiology.csl
 output: 
@@
 These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
-The distinct patterns of some of these different proteins and functional elements point toward the opportunity of using computational approaches in identifying which epigenomic features are most predictive of the development of TAD boundaries.
-This will allow us to better understand what leads to their formation.
+The distinct patterns of different proteins and functional elements point toward the opportunity of using computational approaches in identifying which epigenomic features are most predictive of the development of TAD boundaries, allowing us to better understand what leads to their formation.
 
-Most accepted methods for predicting TAD boundaries consider performing a classification algorithm by binning the genome into equal-sized bins and labeling them as either overlapping with a flanked TAD boundary or not.
-However, a pervasive issue becomes the introduction of highly imbalanced classes.
-Due to the sparcity of TADs throughout the genome, most bins will not contain a TAD boundary.
-Therefore, the minority class of genomic bins with TAD boundaries in them becomes proportionally smaller than that of the majority class of genomic bins with no TAD boundaries.
+A study published by Mourad et al.
+used multiple logistic regression with LASSO regularization to predict TAD boundaries [@mourad2016computational].
+They considered binning the genome at both 50 base and 1kb intervals and flanking TAD boundaries by 1kb and 20kb regions.
+The outcome Y was determined by whether or not a genomic bin overlapped with a flanked boundary.
+The feature space was obtained by considering the percent overlap between a bin and coordinates defining ChIP-seq peak data.
+Models were then evaluated using AUROC.
+However, a pervasive issue here becomes the introduction of highly imbalanced classes.
+Due to the sparcity of TADs throughout the genome, most bins will not overlap with a flanked TAD boundary.
 It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@estabrooks2004multiple].
-A clear method for creating balanced classes remains evasive and largely dependent on the problem at hand.
-
-Another problem lies in identifying the feature space of subsequent classification algorithms.
-A variety of positional characteristics of the genomic features can be used to describe the relationship between TAD boundaries and genomic elements, but it is unclear which is best.
-The use of distances (in base pairs) from genomic bins to regions of functional genomic elements has largely been ignored.
-However, these distance characteristics offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
-
-Due to the increasingly large amounts of functional genomic elements to consider, it is a popular approach in genomic studies to use variable reduction techniques to reduce the noise induced by noninformative predictors and increase computational efficiency.
-Two popular approaches use the $l_{1}$ norm (LASSO) and a combination of the $l_{1}$ and $l_{2}$ norms together (Elastic-Net).
-While both regularization techniques have merit, LASSO’s inability to handle correlated predictors poses a problem when identifying which element are most predictive of TAD boundaries.
-The elastic-net, however, is better suited in a situation where multiple genomic elements colocalize around the same TAD boundaries, and could be better suited for this type of alaysis [@zou2005regularization].
-
-Model performance is also contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
-This will also affect the size of the genomic bins used in model construction.
-A larger resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
-This will contribute to smaller sample sizes and could effect predictive performances.
-
-Careful consideration must also be taken when deciding which performance metric(s) to present when evaluating predictive models.
-A common metric to consider is the the area under the ROC curve (AUC), as well as others including accuracy, sensitivity, and specificity.
-
+Similarly, careful consideration must also be taken when deciding which performance metric(s) to present when evaluating predictive models, especially in the case of imbalanced data.
 The popularity surrounding the use of ROC curves is that they do not depend on a threshold.
@@
 Likewise, metrics like accuracy and sensitivity and specificity do not incorporate the entirety of the confusion matrix created when validating predictive models on a test data set.
-Therefore, each of these metrics are likely to be inflated when evaluating model performance on imbalanced data.
-More robust metrics like the F1-score and Matthew's Correlation Coefficient are more suitable for this type of analysis and can highlight problems associated with applying predictive models on imbalanced data.
+Therefore, each of these metrics are likely to be inflated when evaluating model performance.
+
+In a similar study, Hong et al.
+used domain data from an hESC cell line to build a linear model and predict which genomic elements were associated with TAD boundaries [@hong2017computational].
+They defined boundary segments as genomic regions before and after 150 kilobases of the boundary.
+To solve the imbalance problem, they randomly sampled from regions outside of the 150kb flank.
+For their model, the feature space was determined by the number of counts of ChIP-seq peaks defining functional genomic elements that overlapped with the two segments.
+Individual models were then performed until the best model which included the concensus CTCF signal feature, followed by 10 additional elements was obtained.
+Here, however, it is likely that 1 iteration of random under-sampling will yield biased results, depending on how representative the under-sampled data is.
+Likewise, it is unclear how the performances of other balancing techniques compare (i.e.
+over-sampling or a combination of both under and over-sampling).
+
+Furthermore, there are other aspects of TAD boundary modelling that current methods have failed to consider.
+Most notably is the concept of distance.
+As a feature engineering step, the use of distances (in base pairs) from genomic bins to regions of functional genomic elements has largely been ignored.
+However, these distance characteristics have the potential to offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
+Additionally, model performance is heavily contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
+It is often unclear from authors of previous studies what resolution contact matrices were when retrieving TAD boundaries, and how other resolutions would affect their results.
+A larger resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
+This will contribute to smaller sample sizes and could effect predictive performances.
 
@@
 We coupled each predictor type with two separate variable reduction techniques.
-Lastly, we performed a series of three different re-sampling techniques aimed at created balanced classes.
+Lastly, we performed a series of three different re-sampling techniques aimed at creating balanced classes.
 Random forest classification algorithms were performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the formation of TAD boundaries.
@@
 To establish the data for modeling, the genome was binned into equally sized intervals (Figure 18 C).
-This was performed at the same resolution of the contact matrix that the domain data was obtained from.
+In order for a more systematic approach, the binning process was performed at the same resolution of the contact matrix that the domain data was obtained from.
 For example, for the domain data obtained from a 5kb resolution contact matrix, the genome was subsequently binned into 5kb intervals.
 The same processes was repeated for each of the other three resolutions.
-Next, the boundary coordinates were flanked on either side by a unit corresponding to the resolution of the particular domain data.
+Again, operating systematically, we flanked the boundary coordinates on either side by a unit corresponding to the resolution of the particular domain data.
 For example, for the domain data obtained from a 5kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 5kb for a total width around each boundary point of 10kb.
@@
 
-Using each genomic element, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries in downstream modelling.
+Using the genomic elements, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries in downstream modelling.
 The predictors consisted of two different types of overlaps, and a distance type.
@@
 
-   1.	Overlap Counts (OC): For each genomic bin, the total number of overlapped regions between a functional genomic element and a bin was calculated.
-This was defined as the overlap counts (OC) and is illustrated in the left part of Figure 2.
-Within each bin (marked by the blue dashed lines), the total number of overlapped regions of the genomic element (represented by the horizontal green segments) are tallied and marked below.
-In the case of no overlaps the value is given as 0 (Figure 2 A).
+   1.	Overlap Counts (OC): For each genomic bin, the total number of instances where a bin overlapped with regions representing a functional genomic element was calculated (Figure 2 A).
+In the case of no overlaps the value is given as 0.
 
-   2.	Overlap Percent (OP): For each genomic bin, the percent overlap between regions defined by a particular functional element and a bin was calculated.
-From the middle diagram of Figure 2, the feature width was defined as the number of base pairs that overlapped with the genomic bin.
-The percent was then calculated by dividing the feature width with the bin width.
+   2.	Overlap Percent (OP): For each genomic bin, the percent overlap between the feature width and the total width of the bin was calculated (Figure 2 B).
+We defined the feature width as the number of base pairs that overlapped with the genomic bin.
+The percent was then calculated by dividing the feature width by the bin width.
 If multiple overlaps existed, the feature width was defined as the sum of the total number of base pairs that overlapped with a particular bin.
 Note that the bin width remained constant for a given resolution (either 5kb, 25kb, 50kb, or 100kb).
-Similar to the OC predictor type, bins with no overlaps were given to be 0 (Figure 2 B).
+Bins with no overlaps were given to be 0.
 
-   3.	Distance: For each genomic bin, the distance (in base pairs) from the center of the bin to the center of the nearest region of a respective functional element was calculated.
-The right most diagram of Figure 2 depicts an example of how distance was calculated.
-The vertical green segments represent the centers of the respective genomic element.
-Each distance, $D_{i}$, represented by the blue brackets are the number of base pairs from the center of the bins to the center of the nearest genomic elemental region (Figure 2 C).
+   3.	Distance: For each genomic bin, the distance (in base pairs) from the center of the bin to the center of the nearest region of a respective functional element was calculated (Figure 2 C).
 
@@
 
-###Training and Testing Sets
+###TRAINING & TESTING SETS
 
@@
 
-###Variable Reduction
+###VARIABLE REDUCTION
 
@@
 
-###Re-Sampling Techniques
+###RE-SAMPLING TECHNIQUES
 
@@
 
-   2.	Random Under-Sampling: All of the minority classes from the training set were used.
+   2.	Random Under-Sampling (RUS): All of the minority classes from the training set were used.
 A random set without replacement from the majority classes of the training set were used to match the number of minority samples.
@@
 
-   3.	Random Over-Sampling: All of the majority classes from the training set were used.
+   3.	Random Over-Sampling (ROS): All of the majority classes from the training set were used.
 A random set with replacement from the minority classes of the training set were used to match the number of majority samples.
@@
 For the purposes of this paper, we used SMOTE to create perfectly balanced data.
-However further research would be needed to see if varying the proportion of class disbalance could improve predictive performance.
 
-###Classification
+###CLASSIFICATION
 
@@
 
-###Model Evaluation
+###MODEL EVALUATION & PREDICTION
 
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-Accuracy measures the percentage of correct classifications by the model.
-However, in the case of heavily imbalanced class, as can be seen by the numerator, the metric is biased toward correcly identified majority classes.
-The F1-score and MCC are more balanced measures.
-We also considered the AUC for each model, by computing the average trapezoidal approximations for the curve created by the true positive rates (TPR) and false positive rates (FPR).
+We also considered the AUC for each model by computing the average trapezoidal approximations for the curve created by the true positive rates (TPR) and false positive rates (FPR).
+
+For the task of identifying the functional genomic elements that were most predictive of the formation of TAD boundaries, we evaluated the variable importances associated with each predictor of the random forest model.
+For each tree, the prediction accuracy on the out-of-bag portion of the data is recorded.
+Then the same is done after permuting each predictor variable.
+The difference between the two accuracies are then averaged over all trees, and normalized by the standard error [@kuhn2012caret].
 
@@
 In this section we provide the details of the comprehensive experiments performed in order to assess each ensemble system.
-For the task of predicting TAD boundaries using functional genomic elements, we evaluated 4 domain data sets, 3 predictor types, 2 variable reduction techniques, and 4 class balancing techniques.
-We evaluated each ensemble system using 10-fold cross-validated random forest models.
+We evaluated and compared 4 domain data sets, 3 predictor types, 2 variable reduction techniques, and 4 class balancing techniques.
 Thus, we generated 96 (=4 $\times$ 3 $\times$ 2 $\times$ 4) separate models.

### 2018-12-05 Manuscript/manuscript.Rmd
manuscript edits

@@
 The performances were found to be consistently poor for models with no re-sampling across the other resolutions (Supplementary Figure 13; Supplementary Table 10).
-The low, and sometimes missing, values indicate that the model is unable to identify many, if any, true positive outcomes.
-That is, given imbalanced data, the model was unable to predict which genomic bins truly contain a flanked TAD boundary.
+The low, and sometimes missing, values indicated that the model was unable to identify many, if any, true positive outcomes.
+That is, given imbalanced data, the model was unable to predict which genomic bins truly overlapped with a flanked TAD boundary.
 
@@
 Models also featured a decrease in both accuracy and AUC, which was attributed to less inflated false negative rates (Supplementary Table 11).
-Variable reduction was found not to have an affect on resampling, and subsequent performance as any differences were again marginal.
+Variable reduction was found not to have an affect on resampling, and subsequent performances, as any differences were again marginal.
 Performances were also improved among the models using the other data resolutions as well.
-However, model improvement dissipated as resolution increased (Supplementary Figure 15; Supplementary Table 12).
+However, we found that model improvement dissipated as resolution increased (Supplementary Figure 15; Supplementary Table 12).
 
@@
 We then used the ensemble to compare models with distance type predictors for the feature space.
-For the 5kb resolution data, it was found that models with distance type predictors out performed models with either of the two overlap types (Figure 16).
+For the 5kb resolution data, it was found that models with distance type predictors out performed models with either of the two overlap types, regardless of the regularization technique performed (Figure 16).
 The improvement was observed across all 4 performance metrics that were considered (Supplementary Table 13).
 Likewise, improved performances were seen in the other 3 resolutions as well.
-Although overall performance decreased as resolution increased, models with distance type predictors still were able to maintain a profound improvement (Supplementary Figure 14;Supplementary Table 14).
+Although overall performance decreased as resolution increased, models with distance type predictors still were able to maintain a profound improvement (Supplementary Figure 14; Supplementary Table 14).
 
@@
 
-The differences in performances was most evident when analyzing the variable importance plots for each model using the 4 resolutions.
-We found that when we analyzed the variable importance produced by each random forest algorithm.
-We found that for the 5kb resolution, the most predictive elements include insulator proteins, DNase hypersensitive sites, the transcription factor CTCF, as well as histone modifications H3k9ac, H2az, and H3k4me2 (Figure 10 A).
-Although, the insulator protein is featured as a top predictor in 2 of the other 3 resolutions, the rest of the predictors are less consistent among each other and less in agreement with the literature (Figure 10 B-D).
+The differences in performances was most evident when comparing the variable importances across the 4 resolutions.
+We found that for the 5kb resolution, the most predictive elements included insulator proteins, DNase hypersensitive sites, the transcription factor CTCF, as well as histone modifications H3k9ac, H2az, and H3k4me2 (Figure 10 A).
+Although, the insulator protein is featured as a top predictor in 2 of the other 3 resolutions, the rest of the predictors were less consistent among each other and less in agreement with the literature (Figure 10 B-D).
 The results from Figures 9 and 10 confirm that the model results appear to degrade as resolution increases with respect to both prediction and the identification of genomic elements associated with TAD boundaries.

### 2018-12-11 Manuscript/manuscript.Rmd
edits

@@
 title: "Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings"
-#csl: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.ref/genomebiology.csl
+#csl: styles.ref/genomebiology.csl
 output: 
   word_document:
-    #reference_docx: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/styles.doc/NIH_grant_style.docx
-bibliography: C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/References/references.bib
+    #reference_docx: NIH_grant_style.docx
+bibliography: Manuscript/References/references.bib
 ---
@@
 
-## Table 1: List of Genomic Annoations.
-
-The full list of genomic annotations used in downstream analyses.
-These annotations were the functional genomic elements used to predict the formation of TAD boundaries.
-They were obtained via ChIP-Seq experiments, mapped to human genome assembly hg19, and made available by the ENCODE Consortium.
-
-## Table 2: Class Distributions
-
-Summary of the class distributions for each re-sampling technique, across each resolution.
-All re-sampling techniques yielded completely balanced classes.
-That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.
-
-## Table 7: Model Performances at all Resolutions
-
-Performance metrics comparing models using different sampling approaches for each of the 4 resolutions.
-Withing each resolution, the best value in each column for each performance metric is underlined to compare different sampling approaches, while the highest value in each row is highlighted in bold to compare different predictor types.
-
 # Figure legends
-
-## Figure 1: Model Construction
-
-Diagram of the model construction used for downstream analysis.
-The linear genome was binned according to the resolution of the respective HiC experiment (either 5kb, 25kb, 50kb, or 100kb intervals).
-TAD boundaries were then flanked by 1-unit on either side of the boundary point.
-The unit flanking was indicative of the resolution that the domain data was obtained from (i.e.
-for 5kb resolution, 1 unit represents 5kb for a total flanking region of 10kb).
-The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region.
-The positional coordinates of each functional genomic element, obtained from ENCODE, were then used to define the feature space of the models.
-
-## Figure 2: Predictor Types
-
-Diagram of the 3 predictor types considered when assessing the relationship between TAD boundaries and functional genomic elements.
-Each predictor type was used as the feature space in downstream analyses for predicting which functional genomic elements were associated with the formation of TAD boundaries.
-Featured above are bin-specific examples of the construction of each predictor type.
-(Left) The overlap count (OC) predictors were calculated by considering the total number of elemental regions that overlapped with each genomic bin.
-(Middle) The overlap percent (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin and dividing by the total bin width (either 5, 25, 50, or 100 kilobases given resolution of boundary data).
-(Right) The distance predictors were calculated by measuring the distance (in base pairs) from the center of each genomic bin to the center of the nearest elemental region of interest.
-The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective functional genomic element.
-
-## Figure 3: Ensemble Framework/Model Building Pipeline
-
-A diagram of the model building pipeline given an a combination of inputs from the ensemble framework.
-The data was split into a 7:3 training set to testing set ratio, the variable reduction technique of choice was implemented, and a random forest classification algorithm was performed.
-Each model was then validated on the same testing set.
-
-## Figure 4: Class Imbalance
-
-Barplots illustrating the class imbalance problem featured across each of the four different resolutions that were analyzed.
-Minority classes represent the number of genomic bins that contain a TAD boundary, while the majority classes represent the number of genomic bins that do not contain a TAD boundary.
-
-## Figure 11: Model Performances for all Resolutions
-
-Comparing model performances for TAD boundary data for all 4 resolutions.
-The four regions represent (from left to right; top to bottom) data at 5kb, 25kb, 50kb, and 100kb resolutions.
-Within each region, the rows represent the set of re-sampling techniques, while the columns represent the set of performance metrics that the models were evaluated on.
-Each plot compares 2 sets of models; one using LASSO regularization and one using Elastic-Net regularization.
-Within each set, each bar represents the performance of a model with a specific predictor type; either overlap counts (OC) in red, overlap percent (OP) in green, or distance in blue.
-
-## Figure 9: Comparing Performances
-
-Comparing performances of random forest classification algorithms, across TAD boundary data at each resolution for models using distance-type predictors, with elastic-net regularization and random under-sampling.
-Performances were aggregated by taking the average of each metric across 50 iterations of random under-sampling.
-
-## Figure 10: Comparing Variable Importances
-
-Variable importance plots for the top 15 most predictive functional genomic elements for each of the 4 different resolutions.
-The x-axis represents the standardized difference between the out-of-bag prediction accuracy after permuting each predictor variable, averaged across all trees.
-The greater the mean standardized difference, the more importance the predictor is to the model.
 

### 2018-12-13 Manuscript/manuscript.Rmd
edits

@@
 To establish the data for modeling, the genome was binned into equally sized intervals (Figure 18 C).
-In order for a more systematic approach, the binning process was performed at the same resolution of the contact matrix that the domain data was obtained from.
-For example, for the domain data obtained from a 5kb resolution contact matrix, the genome was subsequently binned into 5kb intervals.
+For a more systematic approach, the binning process was performed using the coordinates of the sparse contact matrix of the corresponding resolution.
+For example, for the domain data obtained from a 5kb resolution contact matrix, the genome was subsequently binned into 5kb intervals using the coordinates of a 5kb resolution contact matrix.
 The same processes was repeated for each of the other three resolutions.

### 2018-12-14 Manuscript/manuscript.Rmd
MD review 12-14-2018

--- 2018-12-11 Manuscript/manuscript.Rmd
@@
 Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long-range chromatin contacts [@zuin2014cohesin].
-Other regulatory elements like particular histone modifications such as H3k36 and H3K27 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [@rao20143d].
+Other regulatory elements like particular histone modifications such as H3K36 and H3K27 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [@rao20143d].
 These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
@@
 Therefore, each of these metrics are likely to be inflated when evaluating model performance.
+[???
+Make paragraphs contain one meaning.
+Split this paragraph into two, one describes the class imbalance problem, another is Mourad paper and how they didn't address it.]
 
@@
 
-#METHODS
+# METHODS
 
-##DOMAIN DATA
+## DOMAIN DATA
 
@@
 The chromosomal coordinates of topologically associating domains throughout the genome were obtained using the arrowhead algorithm from the Juicer toolbox provided by the Aiden Laboratory (https://github.com/aidenlab/juicer) [@durand2016juicebox].
-Using the juicer toolbox, we were able to call TADs on 4 different contact matrix resolutions, which included 5 kb, 25 kb, 50 kb, and 100 kb.
+Using the juicer toolbox, we were able to call TADs [???
+You called TADs yourself, correct?] on 4 different contact matrix resolutions, which included 5 kb, 25 kb, 50 kb, and 100 kb.
 Identified TAD boundaries were represented by their location on the linear genome (hg19 human genome assembly), including start and end coordinates for chromosomes 1 through 22 (Figure 18 A).
@@
 
-##MODEL CONSTRUCTION
+## MODEL CONSTRUCTION
 
-To establish the data for modeling, the genome was binned into equally sized intervals (Figure 18 C).
-In order for a more systematic approach, the binning process was performed at the same resolution of the contact matrix that the domain data was obtained from.
-For example, for the domain data obtained from a 5kb resolution contact matrix, the genome was subsequently binned into 5kb intervals.
+To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution (Figure 18 C).
+For example, for a 5kb resolution contact matrix, the genome was subsequently binned into 5kb intervals using the coordinates of a 5kb resolution contact matrix.
 The same processes was repeated for each of the other three resolutions.
-Again, operating systematically, we flanked the boundary coordinates on either side by a unit corresponding to the resolution of the particular domain data.
+To accommodate for the uncertainty in exact boundary location, the boundary coordinates were flanked on either side by a unit corresponding to the resolution of the corresponding contact matrix.
 For example, for the domain data obtained from a 5kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 5kb for a total width around each boundary point of 10kb.
@@
 
-##GENOMIC ANNOTATIONS
+## GENOMIC ANNOTATIONS
 
@@
 
-###FEATURE ENGINEERING USING GENOMIC ANNOTATIONS
+### FEATURE ENGINEERING USING GENOMIC ANNOTATIONS
 
@@
 
-##ENSEMBLE FRAMEWORK
+## ENSEMBLE FRAMEWORK
 
@@
 
-###TRAINING & TESTING SETS
+### TRAINING & TESTING SETS
 
@@
 
-###VARIABLE REDUCTION
+### VARIABLE REDUCTION [??? To be modified for using LASSO only]
 
@@
 
-###RE-SAMPLING TECHNIQUES
+### RE-SAMPLING TECHNIQUES
 
@@
 
-###CLASSIFICATION
+### CLASSIFICATION
 
@@
 
-Once a system was defined, a random forest algorithm was performed. Letting |X| denote the cardinality of each set, then we evaluated |R| x |P| x |V| x |C| different ensemble systems in this paper.
+Once a system was defined, a random forest algorithm was performed. Letting |X| denote the cardinality of each set, then we evaluated |R| x |P| x |V| x |C| different ensemble systems.
 
-###MODEL EVALUATION & PREDICTION
+### MODEL EVALUATION & PREDICTION
 
@@
 
-$$
-\begin{equation}
-\begin{aligned}
-Accuracy &= \dfrac{TP + TN}{TP + TN + FP + FN} \\
-F1 - Score &= \dfrac{2TP}{2TP + FP + FN} \\
-MCC &= \dfrac{TP \times TN - FP \times FN}{\sqrt{ (TP + FP)(TP+FN)(TN+FP)(TN+FN) }}
-\end{aligned}
-\end{equation}
-$$
+$$Accuracy = \frac{TP + TN}{TP + TN + FP + FN}$$
+$$F1 - Score = \frac{2TP}{2TP + FP + FN}$$
+$$MCC = \frac{TP \times TN - FP \times FN}{\sqrt{ (TP + FP)(TP+FN)(TN+FP)(TN+FN) }}$$
+
 Here, TP refers to the number of bins correctly identified as containing a TAD boundary (true positives), FP refers to the number of bins incorrectly identified as containing a TAD boundary (false positives), TN refers to the number of bins correctly identified as not containing a TAD boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a TAD boundary.
@@
 
-#RESULTS
+# RESULTS
 
-##ENSEMBLE COMPARISONS
+## ENSEMBLE COMPARISONS
 
@@
 
-###CLASS DISTRIBUTIONS ACROSS RESOLUTIONS
+### CLASS DISTRIBUTIONS ACROSS RESOLUTIONS
 
@@
 
-###CLASS IMBALANCE HINDERS PERFORMANCE
+### CLASS IMBALANCE HINDERS PERFORMANCE
 
@@
 
-###RANDOM UNDER-SAMPLING IMPROVES MODEL PERFORMANCE
+### RANDOM UNDER-SAMPLING IMPROVES MODEL PERFORMANCE
 
@@
 
-###DISTANCE TYPE PREDICTORS OUT-PERFORM OTHER PREDICTOR TYPES
+### DISTANCE TYPE PREDICTORS OUT-PERFORM OTHER PREDICTOR TYPES
 
@@
 
-###PERFORMANCES DEGRADE AS RESOLUTION INCREASES
+### PERFORMANCES DEGRADE AS RESOLUTION INCREASES [??? Terminology: 5kb - high resolution. 100kb - low resolution. Adjust the text]
 

### 2018-12-18 Manuscript/Figures/figure_legends.Rmd
WIP through the manuscript

@@
 
-# Figure 2: Predictor Types
+**Figure 2.
+Diagram of the three predictor types considered when assessing the relationship between TAD boundaries and genomic annotations.** The _overlap count_ (OC) predictors were calculated by considering the total number of elemental regions that overlapped with each genomic bin.
+The _overlap percent_ (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin and dividing by the total bin width.
+The _distance_ predictors were calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest elemental region of interest.
+The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective genomic annotations.
 
-Diagram of the 3 predictor types considered when assessing the relationship between TAD boundaries and functional genomic elements.
-Each predictor type was used as the feature space in downstream analyses for predicting which functional genomic elements were associated with the formation of TAD boundaries.
-Featured above are bin-specific examples of the construction of each predictor type.
-(Left) The overlap count (OC) predictors were calculated by considering the total number of elemental regions that overlapped with each genomic bin.
-(Middle) The overlap percent (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin and dividing by the total bin width (either 5, 25, 50, or 100 kilobases given resolution of boundary data).
-(Right) The distance predictors were calculated by measuring the distance (in base pairs) from the center of each genomic bin to the center of the nearest elemental region of interest.
-The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective functional genomic element.
-
-# Figure 3: Ensemble Framework/Model Building Pipeline
-
-A diagram of the model building pipeline given an a combination of inputs from the ensemble framework.
-The data was split into a 7:3 training set to testing set ratio, the variable reduction technique of choice was implemented, and a random forest classification algorithm was performed.
+**Figure 3: Ensemble Framework/Model Building Pipeline.** A diagram of the model building pipeline given an a combination of inputs from the ensemble framework.
+The data was split into a 7:3 training set to testing set ratio, the variable reduction technique of choice was used to minimize the number of uninformative predictors, and a random forest classification algorithm was performed.
 Each model was then validated on the same testing set.

### 2018-12-18 Manuscript/manuscript.Rmd
WIP through the manuscript

@@
 title: "Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings"
-#csl: styles.ref/genomebiology.csl
+csl: styles.ref/genomebiology.csl
 output:
   word_document:
-    #reference_docx: NIH_grant_style.docx
-bibliography: Manuscript/References/references.bib
+    reference_docx: styles.doc/NIH_grant_style.docx
+bibliography: References/references.bib
 ---
@@
 Using the juicer toolbox, we were able to call TADs [???
-You called TADs yourself, correct?] on 4 different contact matrix resolutions, which included 5 kb, 25 kb, 50 kb, and 100 kb.
-Identified TAD boundaries were represented by their location on the linear genome (hg19 human genome assembly), including start and end coordinates for chromosomes 1 through 22 (Figure 18 A).
-The start and end coordinates of all hierarchical TADs were concatenated, sorted, and unique boundary points representing the borders demarcating TADs were obtained (Figure 18 B).
+You called TADs yourself, correct?] on [???
+how many] contact matrices at 5 kb, 25 kb, 50 kb, and 100 kb resolutions.
+Identified TAD boundaries were represented by their location on the linear genome (GRCh37/hg19 human genome assembly), including start and end coordinates for chromosomes 1 through 22 (Figure 18 A).
+The start and end coordinates of all hierarchical TADs were concatenated, sorted, and unique TAD boundary points were obtained (Figure 18 B).
 
@@
 To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution (Figure 18 C).
-For example, for a 5kb resolution contact matrix, the genome was subsequently binned into 5kb intervals using the coordinates of a 5kb resolution contact matrix.
-The same processes was repeated for each of the other three resolutions.
-To accommodate for the uncertainty in exact boundary location, the boundary coordinates were flanked on either side by a unit corresponding to the resolution of the corresponding contact matrix.
+For example, for a 5kb resolution contact matrix, the genome was binned into 5kb intervals.
+To accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sized by regions of size of the resolution of the corresponding contact matrix.
 For example, for the domain data obtained from a 5kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 5kb for a total width around each boundary point of 10kb.
-The same process was repeated for the other three resolutions.
 A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
@@
 
-## GENOMIC ANNOTATIONS
+## GENOMIC ANNOTATION DATA
 
-Annotation data, in the form of functional genomic elements from ChIP-seq experiments were obtained from the Encyclopedia of DNA Elements (ENCODE) Consortium (Table 1).
+Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Table 1).
 The annotations consisted of a variety of different chromatin states, histone marks, and DNase I hypersensitive sites.
-Each annotation was represented by their location throughout the genome via chromosomal coordinates.
 
@@
 
-Using the genomic elements, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries in downstream modelling.
-The predictors consisted of two different types of overlaps, and a distance type.
-They are described in detail below:
+Each genomic annotation is typically represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological annotation.
+Using these sets of genomic annotations, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries (Figure 2):
 
-   1.	Overlap Counts (OC): For each genomic bin, the total number of instances where a bin overlapped with regions representing a functional genomic element was calculated (Figure 2 A).
-In the case of no overlaps the value is given as 0.
+1.
+**Overlap Counts (OC)**: For each genomic bin, the total number of instances where a bin overlapped with genomic annotation regions (features) was calculated.
+In the case of no overlaps the value is set as 0.
 
-   2.	Overlap Percent (OP): For each genomic bin, the percent overlap between the feature width and the total width of the bin was calculated (Figure 2 B).
-We defined the feature width as the number of base pairs that overlapped with the genomic bin.
+2.
+**Overlap Percent (OP)**: For each genomic bin, the percent overlap between the feature width and the total width of the bin was calculated.
+We defined the feature width as the number of bases that overlapped with the genomic bin.
 The percent was then calculated by dividing the feature width by the bin width.
-If multiple overlaps existed, the feature width was defined as the sum of the total number of base pairs that overlapped with a particular bin.
+If multiple overlaps existed, the feature width was defined as the sum of the total number of bases that overlapped with a particular bin.
 Note that the bin width remained constant for a given resolution (either 5kb, 25kb, 50kb, or 100kb).
-Bins with no overlaps were given to be 0.
+Values for bins with no overlaps were set to be 0.
 
-   3.	Distance: For each genomic bin, the distance (in base pairs) from the center of the bin to the center of the nearest region of a respective functional element was calculated (Figure 2 C).
+3. **Distance**: For each genomic bin, the distance (in bases) from the center of the bin to the center of the nearest region of a respective genomic annotation region was calculated.
 
@@
 
-An ensemble of models was established for the purposes of directly comparing the performances of different parameters in the framework.
-Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type as the feature space.
-Details of each step in the framework are provided below.
-
-### TRAINING & TESTING SETS
+An ensemble of models was established for the purposes of systematically comparing the performances of different parameters in the framework.
+Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type as the feature space, as follows.
 
 The data set used for modeling was composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
-These two classes made up the majority and minority sets (Figure 3 A).
-The data was then split into a 7:3 ratio of training to testing sets (Figure 3 B).
-Each training and testing set was composed of a similar majority to minority class ratio as the full data set (Figure 3 C).
-The training set was then used to perform all downstream modeling.
+These two classes made up the majority and minority sets.
+The data was then split into a 7:3 ratio of training to testing sets.
+Each training and testing set was composed of a similar majority to minority class ratio as the full data set.
+The training set was then used to perform all downstream modeling (Figure 3).
+[???
+Where is the resampling techniques come?]
 
@@
 
-We evaluated the use of two variable reduction algorithms, the LASSO and Elastic-Net regularizations (Figure 3 D).
+We evaluated the use of two variable reduction algorithms, the LASSO and Elastic-Net regularizations.
 Each algorithm was performed prior to re-sampling.
@@
 
-We then evaluated three re-sampling techniques (in addition to no re-sampling) used to create balanced classes (Figure 3 E). They are detailed below:
+We then evaluated three re-sampling techniques (in addition to no re-sampling) used to create balanced classes. They are detailed below:
 
-   1.	No Sampling: All of the data points from the majority and minority class of the training set were used.
+1. **No Sampling**: All of the data points from the majority and minority class of the training set were used.
 
-   2.	Random Under-Sampling (RUS): All of the minority classes from the training set were used.
-A random set without replacement from the majority classes of the training set were used to match the number of minority samples.
-In this paper we performed 50 iterations of random under-sampling.
+2.
+**Random Under-Sampling (RUS)**: All of the minority classes from the training set were used.
+Sampling without replacement was used to obtain the same number of the majority classes.
+We performed 50 iterations of random under-sampling.
 At each iteration a random forest classification algorithm was performed.
@@
 
-   3.	Random Over-Sampling (ROS): All of the majority classes from the training set were used.
-A random set with replacement from the minority classes of the training set were used to match the number of majority samples.
+3.
+**Random Over-Sampling (ROS)**: All of the majority classes from the training set were used.
+Sampling with replacement was used to obtain the same number of the minority classes.
 Similar to the under-sampling technique, 50 iterations were performed and results were aggregated by taking the average across iterations.
 
-   4.	SMOTE (Synthetic Minority Over-Sampling Technique): This method incorporated both random under- and over-sampling.
+4.
+**SMOTE** (Synthetic Minority Over-Sampling Technique) [@chawla2002smote]: This method incorporated both random under- and over-sampling.
 Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class.
-The SMOTE algorithm is stored in the DMwR package, available in R [@chawla2002smote].
 The user is able to specify the parameters denoting the percent of over- and under-sampling from the two classes.
-This allows the user to control the proportion of disbalance in the data.
-For the purposes of this paper, we used SMOTE to create perfectly balanced data.
+We used SMOTE to create perfectly balanced data.
+The `DMwR` R package v.
+[???
+Add version number] was used to perform SMOTE.
 
@@
 Thus, we generated 96 (=4 $\times$ 3 $\times$ 2 $\times$ 4) separate models.
-For simplicity, we have only presented the most significant results.
-Results of the complete ensemble are available in the Supplementary Materials.
+For simplicity, we present the most significant results, with the complete results available as Supplementary Tables.
 
@@
 
-The coordinates of the corresponding 5kb resolution contact maps resulted in a total of 44948 genomic bins (Table 2).
-There were only 3083 bins that overlapped with a flanked TAD boundary (6.9%).
-An increase in resolution resulted in less genomic bins and a slighly less degree of class imbalance (Supplementaty Table 8).
-The overall average perentage of class imbalance across all data resolutions was 13.2%.
+The coordinates of the corresponding 5kb resolution contact maps resulted in a total of 44948 genomic bins [???
+across all chromosomes?
+If I do 44948*5000, I get 224740000, which is 1 billion bases less than the size of the genome.
+What is going on?] (Table 2).
+There were only 3083 (6.9%) bins that overlapped with a flanked TAD boundary [???
+What is flanked TAD boundary?
+Why do we care?].
+An increase in resolution resulted in the overall less number of genomic bins and a slighly less degree of class imbalance [???
+Add exact numbers of class imbalance for each resolution] (Supplementaty Table 8).
+The overall average perentage of class imbalance across all data resolutions was 13.2% [???
+Do not understand.
+I understand the ratio of #minority/#majority, but what % tells?].
 After applying each resampling technique to the training sets for each data resolution, we obtained perfectly balanced classes (Figure 4).

### 2018-12-19 Manuscript/manuscript.Rmd
Merge ensemble comparison methods to the results

@@
 
-Using set notation the formulation of the ensemble framework can be defined as follows:
-
-Set of different resolutions:
-
-R = {5kb, 25kb, 50kb, 100kb}
-
-Set of Predictor Types:
-
-P = {OC, OP, Distance}
-
-Set of Variable Reduction Techniques:
-
-V = {LASSO, Elastic-Net}
-
-Set of Class-Balancing Methods:
-
-C = {None, RUS, ROS, SMOTE}
-
-Therefore, a system produced from the ensemble framework is defined as follows:
-
-E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.
-
-Once a system was defined, a random forest algorithm was performed. Letting |X| denote the cardinality of each set, then we evaluated |R| x |P| x |V| x |C| different ensemble systems.
-
 ### MODEL EVALUATION & PREDICTION
@@
 
-In this section we provide the details of the comprehensive experiments performed in order to assess each ensemble system.
-We evaluated and compared 4 domain data sets, 3 predictor types, 2 variable reduction techniques, and 4 class balancing techniques.
-Thus, we generated 96 (=4 $\times$ 3 $\times$ 2 $\times$ 4) separate models.
+We evaluated and compared Hi-C datasets at four different resolutions R = {5kb, 25kb, 50kb, 100kb}, used three predictor types P = {OC, OP, Distance}, two variable reduction techniques V = {LASSO, Elastic-Net}, and four class balancing techniques C = {None, RUS, ROS, SMOTE}.
+Therefore, a system produced from the ensemble framework is defined as: E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.
+Letting |X| denote the cardinality of each set, we evaluated |R| x |P| x |V| x |C| different ensemble systems, totaling 96 (=4 $\times$ 3 $\times$ 2 $\times$ 4) separate models.
 For simplicity, we present the most significant results, with the complete results available as Supplementary Tables.

### 2018-12-22 Manuscript/Figures/figure_legends.Rmd
WIP and issues on the current results

@@
 
-# Figure 4: Class Imbalance
-
-Barplots illustrating the class imbalance problem featured across each of the four different resolutions that were analyzed.
+**Figure 4: Techniques for addressing class imbalance.** Barplots illustrating the class imbalance problem featured across each of the four different resolutions that were analyzed.
 Minority classes represent the number of genomic bins that contain a TAD boundary, while the majority classes represent the number of genomic bins that do not contain a TAD boundary.
@@
 
-# Figure 9: Comparing Performances
+**Figure 9: Comparing Performances** Comparing performances of random forest classification algorithms, across TAD boundary data at each resolution for models using distance-type predictors, with elastic-net regularization and random under-sampling.
+Performances were aggregated by taking the average of each metric across 50 iterations of random under-sampling.
+[???
+Poor legend]
 
-Comparing performances of random forest classification algorithms, across TAD boundary data at each resolution for models using distance-type predictors, with elastic-net regularization and random under-sampling.
-Performances were aggregated by taking the average of each metric across 50 iterations of random under-sampling.
-
-# Figure 10: Comparing Variable Importance
-
-Comparing variable importance for the top 15 most predictive functional genomic elements for each of the 4 different resolutions.
-The x-axis represents the standardized difference between the out-of-bag prediction accuracy after permuting each predictor variable, averaged across all trees.
+**Figure 10: Comparing Variable Importance.** Comparing variable importance for the top 15 most predictive functional genomic elements for each of the 4 different resolutions.
+The x-axis represents the standardized difference between the out-of-bag prediction accuracy after permutting each predictor variable, averaged across all trees.
 The greater the mean standardized difference, the more importance the predictor is to the model.
+[???
+What are A/B/C/D panels?]
 

### 2018-12-22 Manuscript/manuscript.Rmd
WIP and issues on the current results

@@
 
-We first compared models with either overlap counts or overlap percent predictor types, from the 5kb resolution data (Figure 12).
+We first compared models with either overlap counts or overlap percent predictor types [???
+Why not distance?], from the 5kb resolution data (Figure 12).
 These results were from random forest models fit to data without any re-sampling, using either LASSO or Elastic-Net regulariations.
@@
 More importantly, when evaluating model performance using accuracy or AUC, the model appeared to perform relatively well.
-At second glance, however, when considering both the F1-score and MCC, we were able to assess just how poorly the model was performing (Supplementary Table 9).
+At second glance, however, when considering both the F1-score and MCC, we were able to assess just how poorly [???
+Describe, why is it so?] the model was performing (Supplementary Table 9).
 
@@
 
-When evaluatating the 5kb resolution data for a randomly under-sampled training set, it was found that models obtained better classification performance for F1 and MCC metrics (Figure 14).
-The increase in performance was present across both overlap predictor types.
+Random under-sampling substantially improved classification performance as quantified by F1 and MCC metrics (Figure 14).
+The increase in performance was present across both overlap count and overlap percent predictor types [???
+Again, where is distance?].
 Models also featured a decrease in both accuracy and AUC, which was attributed to less inflated false negative rates (Supplementary Table 11).
-Variable reduction was found not to have an affect on resampling, and subsequent performances, as any differences were again marginal.
-Performances were also improved among the models using the other data resolutions as well.
-However, we found that model improvement dissipated as resolution increased (Supplementary Figure 15; Supplementary Table 12).
+Variable reduction was found not to have an affect on resampling, and subsequent performances, as any differences were again marginal [???
+Where is the proof?].
+Notably, random under-sampling improved performance when using data at the other resolutions; however, at lower resolutions the performances were lower (Supplementary Figure 15; Supplementary Table 12).
+These results demonstrate that random under-sampling effectively alleviates class imbalance problem, especially for TAD boundaries detected from high-resolution Hi-C data.
 
 ### DISTANCE TYPE PREDICTORS OUT-PERFORM OTHER PREDICTOR TYPES
+
+[??? Why not using all predictors together? Combine it together with the previous steps, testing no sampling, RUS, and the effect of distance]
 
@@
 A sharp decrease in performance was seen in the 100kb resolution.
+[???
+This message is already evident from previous paragraphs and results.
+Not necessary to repeat it]
 
 The differences in performances was most evident when comparing the variable importances across the 4 resolutions.
-We found that for the 5kb resolution, the most predictive elements included insulator proteins, DNase hypersensitive sites, the transcription factor CTCF, as well as histone modifications H3k9ac, H2az, and H3k4me2 (Figure 10 A).
+[???
+You never said and justified that you use distance predictor.] We found that for the 5kb resolution, the most predictive elements included insulator proteins, DNase hypersensitive sites, the transcription factor CTCF, as well as histone modifications H3k9ac, H2az, and H3k4me2 (Figure 10 A).
 Although, the insulator protein is featured as a top predictor in 2 of the other 3 resolutions, the rest of the predictors were less consistent among each other and less in agreement with the literature (Figure 10 B-D).

### 2019-01-03 Manuscript/manuscript.Rmd
!!!separated paragraphs in intro

@@
 
+Current methods rely on the use of classification algorithms to identify which functional genomic elements are best able to discriminate between regions that include TAD boundaries and those that do not.
+Most methods differ on the techniques used to identify genomic regions that include TAD boundaries, as well as the models and tools used to evaluate the predictive capability of said models.
+In doing so, many methods ignore key characteristics of domain data that can impair and bias results.
+Most notably is the introduction of heavily imbalanced classes.
+Due to the sparcity of TADs throughout the genome, most defined regions will not contain a TAD boundary.
+It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@estabrooks2004multiple].
+Similarly, careful consideration must also be taken when deciding which performance metric(s) to present when evaluating predictive models, especially in the case of imbalanced data.
+The popularity surrounding the use of ROC curves is that they do not depend on a threshold.
+However, when the prevalence of an event is low--that is, a defined genomic region containing a TAD boundary--mean probabilities are biased towards the majority class.
+Likewise, metrics like accuracy and sensitivity and specificity do not incorporate the entirety of the confusion matrix created when validating predictive models on a test data set.
+Therefore, each of these metrics are likely to be inflated when evaluating model performance.
+
 A study published by Mourad et al.
@@
 Models were then evaluated using AUROC.
-However, a pervasive issue here becomes the introduction of highly imbalanced classes.
-Due to the sparcity of TADs throughout the genome, most bins will not overlap with a flanked TAD boundary.
-It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@estabrooks2004multiple].
-Similarly, careful consideration must also be taken when deciding which performance metric(s) to present when evaluating predictive models, especially in the case of imbalanced data.
-The popularity surrounding the use of ROC curves is that they do not depend on a threshold.
-However, when the prevalence of an event is low--that is, a genomic bin overlapping with a TAD boundary region--mean probabilities are biased towards the majority class.
-Likewise, metrics like accuracy and sensitivity and specificity do not incorporate the entirety of the confusion matrix created when validating predictive models on a test data set.
-Therefore, each of these metrics are likely to be inflated when evaluating model performance.
-[???
-Make paragraphs contain one meaning.
-Split this paragraph into two, one describes the class imbalance problem, another is Mourad paper and how they didn't address it.]
+Here, the authors ignored the effect of imbalanced classes as well as the use of potentially biased performance metrics.
+
+[!!! Separated paragraphs]
 
@@
 Additionally, model performance is heavily contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
-It is often unclear from authors of previous studies what resolution contact matrices were when retrieving TAD boundaries, and how other resolutions would affect their results.
+It is often unclear from authors of previous studies what resolution contact matrices were used when retrieving TAD boundaries, and how other resolutions would affect their results.
 A larger resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
@@
 
+## Figure 2: Predictor Types
+
+Diagram of the 3 predictor types considered when assessing the relationship between TAD boundaries and functional genomic elements.
+Each predictor type was used as the feature space in downstream analyses for predicting which functional genomic elements were associated with the formation of TAD boundaries.
+Featured above are bin-specific examples of the construction of each predictor type.
+(Left) The overlap count (OC) predictors were calculated by considering the total number of elemental regions that overlapped with each genomic bin.
+(Middle) The overlap percent (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin and dividing by the total bin width (either 5, 25, 50, or 100 kilobases given resolution of boundary data).
+(Right) The distance predictors were calculated by measuring the distance (in base pairs) from the center of each genomic bin to the center of the nearest elemental region of interest.
+The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective functional genomic element.
+
 # Supplementary Tables and Figures
@@
 
+## Table 1: List of Genomic Annoations.
+
+The full list of genomic annotations used in downstream analyses.
+These annotations were the functional genomic elements used to predict the formation of TAD boundaries.
+They were obtained via ChIP-Seq experiments, mapped to human genome assembly hg19, and made available by the ENCODE Consortium.
+Each element is denoted by its genomic class, and which cell type it is applied to.
+The elements that are invariant to a specific cell type are denoted by "Invariant".
+Additionally, a breif description and specific paths for downloads are also provided.
+
 # References

### 2019-01-03 Manuscript/manuscript.Rmd
!!! manuscript edits

@@
 Using the juicer toolbox, we were able to call TADs [???
-You called TADs yourself, correct?] on [???
-how many] contact matrices at 5 kb, 25 kb, 50 kb, and 100 kb resolutions.
-Identified TAD boundaries were represented by their location on the linear genome (GRCh37/hg19 human genome assembly), including start and end coordinates for chromosomes 1 through 22 (Figure 18 A).
-The start and end coordinates of all hierarchical TADs were concatenated, sorted, and unique TAD boundary points were obtained (Figure 18 B).
+You called TADs yourself, correct?
+!!!Yes, using the arrowhead algoirthm from the juicer toolbox] on [???
+how many; !!!
+the first 29 hic matrices (HIC001 to HIC029); should I provide more detail?] contact matrices at 5 kb, 25 kb, 50 kb, and 100 kb resolutions.
+Identified TAD boundaries were represented by their location on the linear genome (GRCh37/hg19 human genome assembly), including start and end coordinates for chromosomes 1 through 22.
+The start and end coordinates of all hierarchical TADs were concatenated, sorted, and unique TAD boundary points were obtained.
 
@@
 
-To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution (Figure 18 C).
+To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution (Figure 1).
 For example, for a 5kb resolution contact matrix, the genome was binned into 5kb intervals.
@@
 
-Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Table 1).
+Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
 The annotations consisted of a variety of different chromatin states, histone marks, and DNase I hypersensitive sites.
@@
 An ensemble of models was established for the purposes of systematically comparing the performances of different parameters in the framework.
-Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type as the feature space, as follows.
+Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type for the feature space (Figure 3).
 
-The data set used for modeling was composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
+The data sets used for modeling was composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
 These two classes made up the majority and minority sets.
@@
 Each training and testing set was composed of a similar majority to minority class ratio as the full data set.
-The training set was then used to perform all downstream modeling (Figure 3).
-[???
-Where is the resampling techniques come?]
+For each training set, an $l_{1}$ norm penalized regularization (LASSO) was performed.
+The $\lambda$ penalization term was tuned over a grid of 10 values on an exponential scale ranging from 0.01 to 10.
 
-### VARIABLE REDUCTION [??? To be modified for using LASSO only]
+[??? To be modified for using LASSO only; !!!removed variable reduction paragraph and combined it above]
 
-We evaluated the use of two variable reduction algorithms, the LASSO and Elastic-Net regularizations.
-Each algorithm was performed prior to re-sampling.
-For the LASSO, the $\lambda$ penalization term was tuned over a grid of 10 values on an exponential scale ranging from 0.01 to 10.
-The additional $\alpha$ term for the Elastic-Net was tuned over 10 equa-distant values from 0 to 1.
-
+[??? Where is the resampling techniques come?; !!!mentioned it below]
 ### RE-SAMPLING TECHNIQUES
 
-We then evaluated three re-sampling techniques (in addition to no re-sampling) used to create balanced classes. They are detailed below:
+We then evaluated three re-sampling techniques (in addition to no re-sampling) on the reduced training set, in order to evaluate the problem of imbalanced classes. They are detailed below:
 
@@
 
+## Figure 1: Model Construction
+
+Diagram of the model construction used for downstream analysis.
+The linear genome was binned according to the resolution of the respective HiC experiment (either 5kb, 25kb, 50kb, or 100kb intervals).
+TAD boundaries were then flanked by 1-unit on either side of the boundary point.
+The unit flanking was indicative of the resolution that the domain data was obtained from (i.e.
+for 5kb resolution, 1 unit represents 5kb for a total flanking region of 10kb).
+The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region.
+The positional coordinates of each functional genomic element, obtained from ENCODE, were then used to define the feature space of the models.
+
 ## Figure 2: Predictor Types

### 2019-01-03 Manuscript/manuscript.Rmd
!!!manuscript edits

@@
 We used SMOTE to create perfectly balanced data.
-The `DMwR` R package v.
-[???
-Add version number] was used to perform SMOTE.
+The `DMwR` R package (version 3.4.2) [???
+Add version number; !!!added version] was used to perform SMOTE.
 
@@
 If I do 44948*5000, I get 224740000, which is 1 billion bases less than the size of the genome.
-What is going on?] (Table 2).
+What is going on?; !!!This is only CHR1 for right now] (Table 2).
 There were only 3083 (6.9%) bins that overlapped with a flanked TAD boundary [???
@@
 Why do we care?].
-An increase in resolution resulted in the overall less number of genomic bins and a slighly less degree of class imbalance [???
-Add exact numbers of class imbalance for each resolution] (Supplementaty Table 8).
+An increase in resolution resulted in an overall decrease in the number of genomic bins, as well as a slighly less degree of class imbalance.
+The percentage of imbalance for each of the other resolutions were found to be  14.0%, 13.7%, and 12.2% for 25 kb, 50kb, and 100kb resolutions respectively.
+[???
+Add exact numbers of class imbalance for each resolution; !!!
+added exact numbers] (Supplementaty Table 8).
 The overall average perentage of class imbalance across all data resolutions was 13.2% [???
@@
 
+## Table 1: Class Distributions
+
+Summary of the class distributions for the 5 kb resolution domain data, across each re-sampling technique.
+All re-sampling techniques yielded completely balanced classes.
+That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.
+
 # Figure legends
@@
 
+## Table 2: Class Distributions for Other Resolutions
+
+Summary of the class distributions for each of the other resolution domain data sets (25 kb, 50 kb, and 100 kb), across each re-sampling technique.
+As with the 5 kb data, all re-sampling techniques yielded completely balanced classes.
+That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.
+
 # References

### 2019-01-06 Manuscript/manuscript.Rmd
updated manuscript

@@
 Add exact numbers of class imbalance for each resolution; !!!
-added exact numbers] (Supplementaty Table 8).
-The overall average perentage of class imbalance across all data resolutions was 13.2% [???
+added exact numbers] (Supplementaty Table 2).
+[???
 Do not understand.
-I understand the ratio of #minority/#majority, but what % tells?].
+I understand the ratio of #minority/#majority, but what % tells?; !!!was overally average of class imbalance for the 4 data resolutions; removed sentence; doesn't seem relevant].
 After applying each resampling technique to the training sets for each data resolution, we obtained perfectly balanced classes (Figure 4).

### 2019-01-06 Manuscript/manuscript.Rmd
updates

@@
 
-The data sets used for modeling was composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
+The data sets used for modeling were composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
 These two classes made up the majority and minority sets.
@@
 
-We first compared models with either overlap counts or overlap percent predictor types [???
-Why not distance?], from the 5kb resolution data (Figure 12).
-These results were from random forest models fit to data without any re-sampling, using either LASSO or Elastic-Net regulariations.
-We found that differences in performances across variable reduction techniques were marginal.
-More importantly, when evaluating model performance using accuracy or AUC, the model appeared to perform relatively well.
-At second glance, however, when considering both the F1-score and MCC, we were able to assess just how poorly [???
-Describe, why is it so?] the model was performing (Supplementary Table 9).
-
-The performances were found to be consistently poor for models with no re-sampling across the other resolutions (Supplementary Figure 13; Supplementary Table 10).
-The low, and sometimes missing, values indicated that the model was unable to identify many, if any, true positive outcomes.
-That is, given imbalanced data, the model was unable to predict which genomic bins truly overlapped with a flanked TAD boundary.
+We first assessed performances on random forest models built on fully unbalanced training sets across each resolution, for each predictor type (Figure 5) [???
+Why not distance?; !!!included a  more desciptive plot with distance].
+When looking at the the conventional metrics used for assessment (accuracy and AUC), models that were not corrected for class imbalance appeared to perform reasonably well.
+However, when we considered the F1-score and MCC, we observed a significant degredation in performance across both resolution and predictor type [???
+Describe, why is it so?; !!!described].
+This was due in part to each models' inability to correctly classify the genomic bins that overlapped with flanked TAD boundaries, as recognized by the small number of true positive cases (Supplementary Table 3).
+Even without correcting for the class imbalance, we found that, within predictor types, models with distance type predictors consistently outperformed the other two predictor types across all performance metrics.
 

### 2019-01-06 Manuscript/manuscript.Rmd
Checked !!!, cleanup, questions remain

@@
 
-[!!! Separated paragraphs]
-
 In a similar study, Hong et al.
@@
 Replicate Hi-C data for the GM12878 cell line were downloaded from GEO GSE63525 (Experiments HIC001 to HIC029) [@rao20143d].
-The chromosomal coordinates of topologically associating domains throughout the genome were obtained using the arrowhead algorithm from the Juicer toolbox provided by the Aiden Laboratory (https://github.com/aidenlab/juicer) [@durand2016juicebox].
-Using the juicer toolbox, we were able to call TADs [???
-You called TADs yourself, correct?
-!!!Yes, using the arrowhead algoirthm from the juicer toolbox] on [???
+The chromosomal coordinates of topologically associating domains throughout the genome were obtained using the Arrowhead algorithm from the Juicer toolbox provided by the Aiden Laboratory (https://github.com/aidenlab/juicer) [@durand2016juicebox].
+[???
 how many; !!!
-the first 29 hic matrices (HIC001 to HIC029); should I provide more detail?] contact matrices at 5 kb, 25 kb, 50 kb, and 100 kb resolutions.
+the first 29 hic matrices (HIC001 to HIC029); should I provide more detail?
+???
+TBD, why 29?] contact matrices at 5 kb, 25 kb, 50 kb, and 100 kb resolutions.
 Identified TAD boundaries were represented by their location on the linear genome (GRCh37/hg19 human genome assembly), including start and end coordinates for chromosomes 1 through 22.
@@
 Each training and testing set was composed of a similar majority to minority class ratio as the full data set.
-For each training set, an $l_{1}$ norm penalized regularization (LASSO) was performed.
+For each training set, an $l_{1}$ norm penalized regularization (LASSO) was performed [???
+what for?].
 The $\lambda$ penalization term was tuned over a grid of 10 values on an exponential scale ranging from 0.01 to 10.
 
-[??? To be modified for using LASSO only; !!!removed variable reduction paragraph and combined it above]
-
-[??? Where is the resampling techniques come?; !!!mentioned it below]
 ### RE-SAMPLING TECHNIQUES
@@
 We used SMOTE to create perfectly balanced data.
-The `DMwR` R package (version 3.4.2) [???
-Add version number; !!!added version] was used to perform SMOTE.
+The `DMwR` R package (version 3.4.2) was used to perform SMOTE.
 
@@
 The coordinates of the corresponding 5kb resolution contact maps resulted in a total of 44948 genomic bins [???
-across all chromosomes?
-If I do 44948*5000, I get 224740000, which is 1 billion bases less than the size of the genome.
-What is going on?; !!!This is only CHR1 for right now] (Table 2).
+To be modified for the whole genome] (Table 2).
 There were only 3083 (6.9%) bins that overlapped with a flanked TAD boundary [???
@@
 Do not understand.
-I understand the ratio of #minority/#majority, but what % tells?; !!!was overally average of class imbalance for the 4 data resolutions; removed sentence; doesn't seem relevant].
+I understand the ratio of #minority/#majority, but what % tells?; !!!was overally average of class imbalance for the 4 data resolutions; removed sentence; doesn't seem relevant ???
+We should rewrite using the ratio of #minority/#majority].
 After applying each resampling technique to the training sets for each data resolution, we obtained perfectly balanced classes (Figure 4).
@@
 We first assessed performances on random forest models built on fully unbalanced training sets across each resolution, for each predictor type (Figure 5) [???
-Why not distance?; !!!included a  more desciptive plot with distance].
+Why not distance?; !!!included a  more desciptive plot with distance ???
+Where?
+Don't see it on Figure 5, which exists in two versions (?)].
 When looking at the the conventional metrics used for assessment (accuracy and AUC), models that were not corrected for class imbalance appeared to perform reasonably well.
-However, when we considered the F1-score and MCC, we observed a significant degredation in performance across both resolution and predictor type [???
-Describe, why is it so?; !!!described].
-This was due in part to each models' inability to correctly classify the genomic bins that overlapped with flanked TAD boundaries, as recognized by the small number of true positive cases (Supplementary Table 3).
+However, when we considered the F1-score and MCC, we observed a significant degradation in performance across both resolution and predictor type.
+This was due in part to each models' inability to correctly classify the genomic bins that overlapped with flanked TAD boundaries (true positives, Supplementary Table 3).
 Even without correcting for the class imbalance, we found that, within predictor types, models with distance type predictors consistently outperformed the other two predictor types across all performance metrics.

### 2019-01-06 Manuscript/manuscript.Rmd
updates
Where? Don't see it on Figure 5, which exists in two versions (?); !!!figure5_v2_allnoneperfs, will delete other figures after meeting if deemed appropriate

@@
 Where?
-Don't see it on Figure 5, which exists in two versions (?)].
+Don't see it on Figure 5, which exists in two versions (?); !!!figure5_v2_allnoneperfs, will delete other figures after meeting if deemed appropriate].
 When looking at the the conventional metrics used for assessment (accuracy and AUC), models that were not corrected for class imbalance appeared to perform reasonably well.
@@
 
+## Table 3: Model Performances When Not Accounting for Class Imbalance
+
+A list of various metrics used to assess predictive performances for models that were built on fully imbalanced datasets.
+
 # References

### 2019-01-06 Manuscript/manuscript.Rmd
updates

@@
 
+When comparing re-sampling techniques it was found that performing 50 iterations of random under-sampling yielded significantly higher results for both F1-Scores and MCC metrics (Figure 6).
+
 Random under-sampling substantially improved classification performance as quantified by F1 and MCC metrics (Figure 14).
@@
 Models also featured a decrease in both accuracy and AUC, which was attributed to less inflated false negative rates (Supplementary Table 11).
+
 Variable reduction was found not to have an affect on resampling, and subsequent performances, as any differences were again marginal [???
@@
 
+## Figure 3: Ensemble Framework/Model Building Pipeline
+
+A diagram of the model building pipeline given a combination of inputs from the ensemble framework.
+The data was split into a 7:3 training set to testing set ratio, an $l_{1}$ norm regularization (LASSO) was implemented, and a random forest classification algorithm was performed.
+Each model was then validated on the same testing set.
+
+# Figure 4: Class Imbalance
+
+Barplots illustrating the class imbalance problem featured across each of the four different resolutions that were analyzed.
+Minority classes represent the number of genomic bins that contain a TAD boundary, while the majority classes represent the number of genomic bins that do not contain a TAD boundary.
+
+# Figure 5: Performances of Models with No Class-Balancing
+
+Barplots measuring the predictive performance of models built on imbalanced datasets.
+The performance metrics considered were accuracy, AUC, F1-Score, and MCC.
+Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).
+
 # Supplementary Tables and Figures

### 2019-01-07 Manuscript/manuscript.Rmd
updates

@@
 In this study we have developed an ensemble framework that aims to address and compare a variety of data irregularities and characteristics that are associated with the prediction of TAD boundaries.
-We evaluated domain data obtained from four different resolution contact matrices for the GM12878 cell line including 5kb, 25kb, 50kb, and 100kb.
+We evaluated domain data obtained from four different resolution contact matrices for the GM12878 cell line including 10 kb, 25 kb, 50 kb, and 100 kb.
 For each resolution, we examined the inclusion of three different predictor types as the feature space for downstream modeling.
@@
 To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution (Figure 1).
-For example, for a 5kb resolution contact matrix, the genome was binned into 5kb intervals.
+For example, for a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
 To accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sized by regions of size of the resolution of the corresponding contact matrix.
-For example, for the domain data obtained from a 5kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 5kb for a total width around each boundary point of 10kb.
+For example, for the domain data obtained from a 10 kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 10 kb for a total width around each boundary point of 20 kb.
 A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
@@
 If multiple overlaps existed, the feature width was defined as the sum of the total number of bases that overlapped with a particular bin.
-Note that the bin width remained constant for a given resolution (either 5kb, 25kb, 50kb, or 100kb).
+Note that the bin width remained constant for a given resolution (either 10 kb, 25 kb, 50 kb, or 100 kb).
 Values for bins with no overlaps were set to be 0.
@@
 Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class.
-The user is able to specify the parameters denoting the percent of over- and under-sampling from the two classes.
-We used SMOTE to create perfectly balanced data.
+To account for the bias introduced by the under-sampling, we performed 50-iterations of SMOTE The user is able to specify the parameters denoting the percent of over- and under-sampling from the two classes.
+We chose the parameters that would create perfectly balanced classes.
 The `DMwR` R package (version 3.4.2) was used to perform SMOTE.
@@
 
-We evaluated and compared Hi-C datasets at four different resolutions R = {5kb, 25kb, 50kb, 100kb}, used three predictor types P = {OC, OP, Distance}, two variable reduction techniques V = {LASSO, Elastic-Net}, and four class balancing techniques C = {None, RUS, ROS, SMOTE}.
+We evaluated and compared Hi-C datasets at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}, used three predictor types P = {OC, OP, Distance}, two variable reduction techniques V = {LASSO, Elastic-Net}, and four class balancing techniques C = {None, RUS, ROS, SMOTE}.
 Therefore, a system produced from the ensemble framework is defined as: E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.
@@
 
-The coordinates of the corresponding 5kb resolution contact maps resulted in a total of 44948 genomic bins [???
+The coordinates of the corresponding 10 kb resolution contact maps resulted in a total of 44948 genomic bins [???
 To be modified for the whole genome] (Table 2).
@@
 
-When comparing re-sampling techniques it was found that performing 50 iterations of random under-sampling yielded significantly higher results for both F1-Scores and MCC metrics (Figure 6).
-
-Random under-sampling substantially improved classification performance as quantified by F1 and MCC metrics (Figure 14).
-The increase in performance was present across both overlap count and overlap percent predictor types [???
-Again, where is distance?].
-Models also featured a decrease in both accuracy and AUC, which was attributed to less inflated false negative rates (Supplementary Table 11).
-
-Variable reduction was found not to have an affect on resampling, and subsequent performances, as any differences were again marginal [???
-Where is the proof?].
-Notably, random under-sampling improved performance when using data at the other resolutions; however, at lower resolutions the performances were lower (Supplementary Figure 15; Supplementary Table 12).
-These results demonstrate that random under-sampling effectively alleviates class imbalance problem, especially for TAD boundaries detected from high-resolution Hi-C data.
+When comparing re-sampling techniques it was found that performing 50 iterations of random under-sampling yielded the best performances for both F1-Scores and MCC metrics, across all resolutions and predictor types (Figure 6).
+Models using 50-iterations of the SMOTE algorithm performed comparitively similar to those using RUS, across all resolutions and predictor types (supplementary Figure 1A).
+However, it was observed that models using 50-iterations of random over-sampling performed substantially worse than both RUS and SMOTE (Supplementary Figure 1B).
+More importantly, there was a notable decrease in both accuracy and AUC metrics when performing random under-sampling compared to models with no class balancing.
+This was evidenced by the more balanced interplay between the componenets of the confusion matrices created when validating the models (Supplementary Table 4).
+That is, less weight was carried by the true negative cases.
+This feature was also observed for models using SMOTE and ROS (Supplementary Table 5).
+As was the case for models with no class-balancing, there was a clear improvement when performing RUS for models with distance-type predictors, across all resolutions.[???
+Again, where is distance?; !!!included]
 
@@
 Diagram of the model construction used for downstream analysis.
-The linear genome was binned according to the resolution of the respective HiC experiment (either 5kb, 25kb, 50kb, or 100kb intervals).
+The linear genome was binned according to the resolution of the respective HiC experiment (either 10 kb, 25 kb, 50 kb, or 100 kb intervals).
 TAD boundaries were then flanked by 1-unit on either side of the boundary point.
 The unit flanking was indicative of the resolution that the domain data was obtained from (i.e.
-for 5kb resolution, 1 unit represents 5kb for a total flanking region of 10kb).
+for 10 kb resolution, 1 unit represents 10 kb for a total flanking region of 20 kb).
 The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region.
@@
 
+# Figure 6:
+
 # Supplementary Tables and Figures

### 2019-01-07 Manuscript/manuscript.Rmd
updated manuscript

@@
 
-# Figure 4: Class Imbalance
+## Figure 4: Class Imbalance
 
@@
 
-# Figure 5: Performances of Models with No Class-Balancing
+## Figure 5: Performances of Models with No Class-Balancing
 
@@
 
-# Figure 6:
+## Figure 6: Performances of Models with Randomly Under-sampled Data.
+
+Barplots measuring the predictive performance of models built on datasets using 50 iterations of random under-sampling.
+The performance metrics considered were accuracy, AUC, F1-Score, and MCC.
+Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).
 
@@
 
-A list of various metrics used to assess predictive performances for models that were built on fully imbalanced datasets.
+Results of various metrics used to assess predictive performances for models that were built on fully imbalanced datasets.
+
+## Figure 1: Performances of Models with Both SMOTE-Balanced and Randomly Over-sampled Data.
+
+Barplots measuring the predictive performance of models built on datasets using 50 iterations of both the SMOTE algorithm (A) and random over-sampling (B).
+The performance metrics considered were accuracy, AUC, F1-Score, and MCC.
+Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).
+
+## Table 4:
+
+Results of various metrics used to assess predictive performances for models that were built on random under-sampled datasets.
+
+## Table 5:
+
+Results of various metrics used to assess predictive performances for models that were built on both SMOTE-balanced and random over-sampled datasets.
 

### 2019-01-07 Manuscript/manuscript.Rmd
manuscript updates

@@
 
-[??? Why not using all predictors together? Combine it together with the previous steps, testing no sampling, RUS, and the effect of distance]
+[??? Why not using all predictors together? Combine it together with the previous steps, testing no sampling, RUS, and the effect of distance; !!!running on cluster]
 
-We then used the ensemble to compare models with distance type predictors for the feature space.
-For the 5kb resolution data, it was found that models with distance type predictors out performed models with either of the two overlap types, regardless of the regularization technique performed (Figure 16).
-The improvement was observed across all 4 performance metrics that were considered (Supplementary Table 13).
-Likewise, improved performances were seen in the other 3 resolutions as well.
-Although overall performance decreased as resolution increased, models with distance type predictors still were able to maintain a profound improvement (Supplementary Figure 14; Supplementary Table 14).
+In order to more efficiently assess the impact of feature engineering on predictive performance, we directly compared models using each of the three predictor types, across all resolutions, while using 50 iterations of random under-sampling to account for the class imbalance.
+It was observed that the models built using distance-type features performed substanially better than the other two (Figure 7).
+This improvement in performance was observed across each of the 4 performance metrics considered.
+Interestingly, we found that models with overlap percent (OP) type predictors performed worse than those with simple overlap counts (OC), regardless of data resolution.
+This is notable because, OP predictors can be thought of as a more refined version of OC predictor.
+Likewise, there have been established methods from previous research that have used OP predictors when attempting to determine which genomic features are most predictive of TAD boundary formation [@mourad2016computational].
 

### 2019-01-07 Manuscript/manuscript.Rmd
review

@@
 
-We first assessed performances on random forest models built on fully unbalanced training sets across each resolution, for each predictor type (Figure 5) [???
-Why not distance?; !!!included a  more desciptive plot with distance ???
-Where?
-Don't see it on Figure 5, which exists in two versions (?); !!!figure5_v2_allnoneperfs, will delete other figures after meeting if deemed appropriate].
+We first assessed performances on random forest models built on fully unbalanced training sets across each resolution, for each predictor type (Figure 5).
 When looking at the the conventional metrics used for assessment (accuracy and AUC), models that were not corrected for class imbalance appeared to perform reasonably well.
@@
 This feature was also observed for models using SMOTE and ROS (Supplementary Table 5).
-As was the case for models with no class-balancing, there was a clear improvement when performing RUS for models with distance-type predictors, across all resolutions.[???
-Again, where is distance?; !!!included]
+As was the case for models with no class-balancing, there was a clear improvement when performing RUS for models with distance-type predictors, across all resolutions.
 

### 2019-01-16 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-Replicate Hi-C data for the GM12878 cell line were downloaded from GEO GSE63525 (Experiments HIC001 to HIC029) [@rao20143d].
+Replicate Hi-C data for the GM12878 cell line were downloaded from GEO GSE63525 (Experiments HIC001 to HIC018; produced using the MbolI restriction enzyme) [@rao20143d].
 The chromosomal coordinates of topologically associating domains throughout the genome were obtained using the Arrowhead algorithm from the Juicer toolbox provided by the Aiden Laboratory (https://github.com/aidenlab/juicer) [@durand2016juicebox].
-[???
-how many; !!!
-the first 29 hic matrices (HIC001 to HIC029); should I provide more detail?
-???
-TBD, why 29?] contact matrices at 5 kb, 25 kb, 50 kb, and 100 kb resolutions.
+Domain data was extracted at 4 different kilobase (kb) resolutions including 10 kb, 25 kb, 50 kb, and 100 kb.
 Identified TAD boundaries were represented by their location on the linear genome (GRCh37/hg19 human genome assembly), including start and end coordinates for chromosomes 1 through 22.
@@
 To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution (Figure 1).
-For example, for a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
-To accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sized by regions of size of the resolution of the corresponding contact matrix.
-For example, for the domain data obtained from a 10 kb resolution contact matrix, each uniquely identified TAD boundary was flanked on either side by 10 kb for a total width around each boundary point of 20 kb.
+For example, fordomain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
+To accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
+For example, returning to the 10 kb resolution example, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
 A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
@@
 Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
-The annotations consisted of a variety of different chromatin states, histone marks, and DNase I hypersensitive sites.
+The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments.
+Each genomic annotation was represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological significance.
+
+## ENSEMBLE FRAMEWORK
+
+An ensemble of models was established for the purposes of systematically comparing the performances of different parameters in the framework.
+Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type for the feature space (Figure 2).
+
+The data sets used for modeling were composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
+These two classes made up the minority and majority sets respectively.
+The data was then split into a 7:3 ratio of training to testing sets.
+Each training and testing set was composed of a similar majority to minority class ratio as the full data set.
+That is, for the task of prediction, the test set remained constant for all ensemble systems in order to account for a fair and unbiased comparison.
 
@@
 
-Each genomic annotation is typically represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological annotation.
-Using these sets of genomic annotations, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries (Figure 2):
+Using the sets of genomic annotations, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries (Figure 3):
 
@@
 
-3. **Distance**: For each genomic bin, the distance (in bases) from the center of the bin to the center of the nearest region of a respective genomic annotation region was calculated.
+3.
+**Log Distance**: For each genomic bin, the log of the distance (in bases) from the center of the bin to the center of the nearest region of a respective genomic annotation region was calculated.
+The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1)
 
-## ENSEMBLE FRAMEWORK
+To assess the predictive performance for each predictor type, we performed individual random forest models utilizing each specific predictor type, in addition to a model with all combined types.
+Precision-Recall (PR) Curves, and subsequent area under the PR curves (AUPRC), were used to evaluate which predictor type contributed to the best model performance.
 
-An ensemble of models was established for the purposes of systematically comparing the performances of different parameters in the framework.
-Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type for the feature space (Figure 3).
-
-The data sets used for modeling were composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
-These two classes made up the majority and minority sets.
-The data was then split into a 7:3 ratio of training to testing sets.
-Each training and testing set was composed of a similar majority to minority class ratio as the full data set.
-For each training set, an $l_{1}$ norm penalized regularization (LASSO) was performed [???
-what for?].
-The $\lambda$ penalization term was tuned over a grid of 10 values on an exponential scale ranging from 0.01 to 10.
+### VARIABLE REDUCTION
 
@@
 
-## Figure 2: Predictor Types
+## Figure 2: Ensemble Framework/Model Building Pipeline
+
+A diagram of the model building pipeline given a combination of inputs from the ensemble framework.
+The data was split into a 7:3 training set to testing set ratio, an $l_{1}$ norm regularization (LASSO) was implemented, and a random forest classification algorithm was performed.
+Each model was then validated on the same testing set.
+
+## Figure 3: Predictor Types
 
@@
 The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective functional genomic element.
-
-## Figure 3: Ensemble Framework/Model Building Pipeline
-
-A diagram of the model building pipeline given a combination of inputs from the ensemble framework.
-The data was split into a 7:3 training set to testing set ratio, an $l_{1}$ norm regularization (LASSO) was implemented, and a random forest classification algorithm was performed.
-Each model was then validated on the same testing set.
 

### 2019-01-17 Manuscript/manuscript.Rmd
manuscript edits

@@
 
+[???include explanation of why included metrics are better]
+
 A study published by Mourad et al.
@@
 Random forest classification algorithms were performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the formation of TAD boundaries.
-Model performance was evaluated based on a total of four metrics which included test accuracy, area under the ROC curve (AUC), F1 score, and Matthew's Correlation Coefficient (MCC).
+Model performance was evaluated based on a total of four metrics which included test accuracy, area under the precision-recall curve (AUPRC), F1 score, and Matthew's Correlation Coefficient (MCC).
 
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-We also considered the AUC for each model by computing the average trapezoidal approximations for the curve created by the true positive rates (TPR) and false positive rates (FPR).
+The evaluation metrics listed above are all considered single threshold measures.
+That is, they are defined for individual thresholds that separated class prediction.
+Thererfore they are unable to give an overview of the potential range of performance as thresholds vary.
+A full list of the single threshold measures used (including additional metrics not reported), along with their respective formulas, are provided in Supplementary Table 6.
+In order to evaluate the trade-off between precision and recall, we also considered a threshold free measure in form of the area under the precision recall curve (AUPRC).
 
@@
 For each tree, the prediction accuracy on the out-of-bag portion of the data is recorded.
-Then the same is done after permuting each predictor variable.
-The difference between the two accuracies are then averaged over all trees, and normalized by the standard error [@kuhn2012caret].
+Then the same was done after permuting each predictor variable.
+The difference between the two accuracies were then averaged over all trees, and normalized by the standard error [@kuhn2012caret].
 

### 2019-01-17 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-### FEATURE ENGINEERING USING GENOMIC ANNOTATIONS
+### FEATURE ENGINEERING AND REDUCTION USING GENOMIC ANNOTATIONS
 
@@
 
-To assess the predictive performance for each predictor type, we performed individual random forest models utilizing each specific predictor type, in addition to a model with all combined types.
+To assess the predictive performance for each predictor type, we performed individual random forest classification algorithms utilizing each set predictor types as the feature space, in addition to a model with all combined types.
 Precision-Recall (PR) Curves, and subsequent area under the PR curves (AUPRC), were used to evaluate which predictor type contributed to the best model performance.
-
-### VARIABLE REDUCTION
+Recursive feature elimination (RFE) was then used to determine the optimal number of features for models within each set of predictor types.
+Here, random forest models were used to assign weights to a set features of a given size.
+The optimal number of features was determined by the AUPRC of the corresponding model.
 
@@
 4.
-**SMOTE** (Synthetic Minority Over-Sampling Technique) [@chawla2002smote]: This method incorporated both random under- and over-sampling.
-Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class.
+**SMOTE** (Synthetic Minority Over-Sampling Technique): This method incorporates both random under- and over-sampling.
+Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class [@chawla2002smote].
 To account for the bias introduced by the under-sampling, we performed 50-iterations of SMOTE The user is able to specify the parameters denoting the percent of over- and under-sampling from the two classes.
 We chose the parameters that would create perfectly balanced classes.
-The `DMwR` R package (version 3.4.2) was used to perform SMOTE.
+The `DMwR` package in R (version 3.4.2) was used to perform SMOTE.
+
+5.
+**ROSE** (Random Over-Sampling Examples): Similar to SMOTE, ROSE combines combines techniques of over-sampling and under-sampling.
+However, contrary to SMOTE, all of the data generated by ROSE is synthetic.
+The data is created by sampling from one of the two classes, then generating a new example in its neighborhood using a smoothed bootstrap approach.
+The shape of the neighborhood is determined by the kernal density estimate of the two classes [@lunardon2013r].
+Another important distinction between ROSE and SMOTE is that, for ROSE, the creation of perfectly balanced classes is unlikely due to the randomness in sampling between the two classes.
+The `ROSE` package in R (version 3.4.2) was used to perform ROSE.
 
@@
 
-A classification algorithm in the form of a random forest was performed and validated using the same test set for all models in the ensemble (Figure 3 F).
-10-fold cross validation was used to reduced bias due to random dataset generation.
+A classification algorithm in the form of a random forest was performed and validated using the same test set for all models in the ensemble.
+To reduce bias due to random dataset generation, 10-fold cross validation was used.
 The default number of features to consider at each node of the random forest algorithm was set as the square root of the number of features in the model.
@@
 
-We evaluated and compared Hi-C datasets at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}, used three predictor types P = {OC, OP, Distance}, two variable reduction techniques V = {LASSO, Elastic-Net}, and four class balancing techniques C = {None, RUS, ROS, SMOTE}.
-Therefore, a system produced from the ensemble framework is defined as: E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.
-Letting |X| denote the cardinality of each set, we evaluated |R| x |P| x |V| x |C| different ensemble systems, totaling 96 (=4 $\times$ 3 $\times$ 2 $\times$ 4) separate models.
+We evaluated and compared Hi-C datasets at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}, used three predictor types P = {OC, OP, Distance}, two variable reduction techniques V = {LASSO, Elastic-Net}, and five class balancing techniques C = {None, RUS, ROS, SMOTE, ROSE}.
+A system produced from the ensemble framework was defined as: E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.
+Letting |X| denote the cardinality of each set, we evaluated |R| x |P| x |V| x |C| different ensemble systems, totaling 120 (=4 $\times$ 3 $\times$ 2 $\times$ 5) separate models.
 For simplicity, we present the most significant results, with the complete results available as Supplementary Tables.
@@
 
-The coordinates of the corresponding 10 kb resolution contact maps resulted in a total of 44948 genomic bins [???
-To be modified for the whole genome] (Table 2).
-There were only 3083 (6.9%) bins that overlapped with a flanked TAD boundary [???
-What is flanked TAD boundary?
-Why do we care?].
-An increase in resolution resulted in an overall decrease in the number of genomic bins, as well as a slighly less degree of class imbalance.
-The percentage of imbalance for each of the other resolutions were found to be  14.0%, 13.7%, and 12.2% for 25 kb, 50kb, and 100kb resolutions respectively.
-[???
-Add exact numbers of class imbalance for each resolution; !!!
-added exact numbers] (Supplementaty Table 2).
-[???
-Do not understand.
-I understand the ratio of #minority/#majority, but what % tells?; !!!was overally average of class imbalance for the 4 data resolutions; removed sentence; doesn't seem relevant ???
-We should rewrite using the ratio of #minority/#majority].
-After applying each resampling technique to the training sets for each data resolution, we obtained perfectly balanced classes (Figure 4).
-That is, the ratio of bins that overlapped with flanked TAD boundaries to bins that did not was 1:1.
+The coordinates of the corresponding 10 kb resolution contact maps resulted in a total of X genomic bins [???
+To be modified for the whole genome].
+There were only Y bins that overlapped with a flanked TAD boundary representing the minority class, for an imbalance ratio of (X-Y):Y.
+After applying each resampling technique to the training set, we obtained perfectly balanced classes for all except the ROSE technique (Figure 4).
 
-### CLASS IMBALANCE HINDERS PERFORMANCE
+An increase in resolution resulted in an overall decrease in the number of genomic bins, as well as a slight decrease in the imbalance ratio (Supplementary Figure 2).
+After performing the resampling techniques, the resulting imbalance ratios remained similar across the other 3 data resolutions (Supplementary Figure 2).
 
-We first assessed performances on random forest models built on fully unbalanced training sets across each resolution, for each predictor type (Figure 5).
-When looking at the the conventional metrics used for assessment (accuracy and AUC), models that were not corrected for class imbalance appeared to perform reasonably well.
-However, when we considered the F1-score and MCC, we observed a significant degradation in performance across both resolution and predictor type.
-This was due in part to each models' inability to correctly classify the genomic bins that overlapped with flanked TAD boundaries (true positives, Supplementary Table 3).
-Even without correcting for the class imbalance, we found that, within predictor types, models with distance type predictors consistently outperformed the other two predictor types across all performance metrics.
-
-### RANDOM UNDER-SAMPLING IMPROVES MODEL PERFORMANCE
-
-When comparing re-sampling techniques it was found that performing 50 iterations of random under-sampling yielded the best performances for both F1-Scores and MCC metrics, across all resolutions and predictor types (Figure 6).
-Models using 50-iterations of the SMOTE algorithm performed comparitively similar to those using RUS, across all resolutions and predictor types (supplementary Figure 1A).
-However, it was observed that models using 50-iterations of random over-sampling performed substantially worse than both RUS and SMOTE (Supplementary Figure 1B).
-More importantly, there was a notable decrease in both accuracy and AUC metrics when performing random under-sampling compared to models with no class balancing.
-This was evidenced by the more balanced interplay between the componenets of the confusion matrices created when validating the models (Supplementary Table 4).
-That is, less weight was carried by the true negative cases.
-This feature was also observed for models using SMOTE and ROS (Supplementary Table 5).
-As was the case for models with no class-balancing, there was a clear improvement when performing RUS for models with distance-type predictors, across all resolutions.
-
-### DISTANCE TYPE PREDICTORS OUT-PERFORM OTHER PREDICTOR TYPES
-
-[??? Why not using all predictors together? Combine it together with the previous steps, testing no sampling, RUS, and the effect of distance; !!!running on cluster]
-
-In order to more efficiently assess the impact of feature engineering on predictive performance, we directly compared models using each of the three predictor types, across all resolutions, while using 50 iterations of random under-sampling to account for the class imbalance.
-It was observed that the models built using distance-type features performed substanially better than the other two (Figure 7).
-This improvement in performance was observed across each of the 4 performance metrics considered.
-Interestingly, we found that models with overlap percent (OP) type predictors performed worse than those with simple overlap counts (OC), regardless of data resolution.
-This is notable because, OP predictors can be thought of as a more refined version of OC predictor.
-Likewise, there have been established methods from previous research that have used OP predictors when attempting to determine which genomic features are most predictive of TAD boundary formation [@mourad2016computational].
-
-### PERFORMANCES DEGRADE AS RESOLUTION INCREASES [??? Terminology: 5kb - high resolution. 100kb - low resolution. Adjust the text]
-
-Finally, we directly compared the performances of models across the different resolutions.
-The comparisons consisted of random forest models using distance type predictors, elastic-net regularization, and 50 iterations of random under-sampling.
-The model using 5kb resolution domain data was found to perform slightly better compared to the 25kb and 50kb resolutions (Figure 9).
-A sharp decrease in performance was seen in the 100kb resolution.
-[???
-This message is already evident from previous paragraphs and results.
-Not necessary to repeat it]
-
-The differences in performances was most evident when comparing the variable importances across the 4 resolutions.
-[???
-You never said and justified that you use distance predictor.] We found that for the 5kb resolution, the most predictive elements included insulator proteins, DNase hypersensitive sites, the transcription factor CTCF, as well as histone modifications H3k9ac, H2az, and H3k4me2 (Figure 10 A).
-Although, the insulator protein is featured as a top predictor in 2 of the other 3 resolutions, the rest of the predictors were less consistent among each other and less in agreement with the literature (Figure 10 B-D).
-The results from Figures 9 and 10 confirm that the model results appear to degrade as resolution increases with respect to both prediction and the identification of genomic elements associated with TAD boundaries.
+### DISTANCE-TYPE PREDICTORS PERFORM BEST
 

### 2019-01-17 Manuscript/manuscript.Rmd
editted intro

@@
 
-Current methods rely on the use of classification algorithms to identify which functional genomic elements are best able to discriminate between regions that include TAD boundaries and those that do not.
+Current methods rely on the use of classification algorithms to identify which functional genomic elements are best able to discriminate between regions that include TAD boundaries and those that do not [@mourad2016computational, @hong2017computational].
 Most methods differ on the techniques used to identify genomic regions that include TAD boundaries, as well as the models and tools used to evaluate the predictive capability of said models.
-In doing so, many methods ignore key characteristics of domain data that can impair and bias results.
+Moreover, many methods ignore key characteristics of domain data that can impair and bias results.
+
 Most notably is the introduction of heavily imbalanced classes.
 Due to the sparcity of TADs throughout the genome, most defined regions will not contain a TAD boundary.
-It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@estabrooks2004multiple].
+In a classification setting, when one is attempting to discriminate between regions with and without TAD boundaries, this will contribute to large imbalance ratios (defined as the ratio of majority to minority classes) [@Orriols-Puig2008].
+It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@estabrooks2004multiple, @chen2013influence].
 Similarly, careful consideration must also be taken when deciding which performance metric(s) to present when evaluating predictive models, especially in the case of imbalanced data.
+
+Commonly used measures of model performance for binary classifiers include the area under the receiver operating curve (AUROC).
 The popularity surrounding the use of ROC curves is that they do not depend on a threshold.
 However, when the prevalence of an event is low--that is, a defined genomic region containing a TAD boundary--mean probabilities are biased towards the majority class.
-Likewise, metrics like accuracy and sensitivity and specificity do not incorporate the entirety of the confusion matrix created when validating predictive models on a test data set.
+This results in the area of interest under an ROC curve to be compressed toward a small corner in the ROC space [@prati2011survey].
+While not directly affecting the value of the AUROC, this can have severe consequences on the interpretability of the model's performance.
+A better threshold-free measure to use when dealing with imbalanced data in the area under the precision-recall curve (AUPRC).
+It has been shown that the use of AUPRC with imbalanced datasets yields more accurate and intuitive interpretation of model performance when compared to AUROC [@saito2015precision].
+Likewise, metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data.
+In each case, the weight
+
+do not incorporate the entirety of the confusion matrix created when validating predictive models on a test data set.
 Therefore, each of these metrics are likely to be inflated when evaluating model performance.
+Better measures
 
@@
 
+?????????????????????????????????????????????????????????????????????????[include if we decide to directly compare these methods; otherwise referenced above]
 A study published by Mourad et al.
@@
 over-sampling or a combination of both under and over-sampling).
+?????????????????????????????????????????????????????????????????????????
 
@@
 To be modified for the whole genome].
-There were only Y bins that overlapped with a flanked TAD boundary representing the minority class, for an imbalance ratio of (X-Y):Y.
+There were only Y bins that overlapped with a flanked TAD boundary representing the minority class, for an imbalance ratio of (X-Y):Y [???
+To be modified for the whole genome].
 After applying each resampling technique to the training set, we obtained perfectly balanced classes for all except the ROSE technique (Figure 4).

### 2019-01-17 Manuscript/manuscript.Rmd
editted intro

@@
 Likewise, metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data.
-In each case, the weight
+In each case, the weight of the measure is carried primarily by the correct classification of the majority class.
+Better measures to consider are the F1-Score and Matthew's Correlation Coefficient (MCC) [@jeni2013facing].
+The F1-Score can be interpreted as a weighted average of the precision and recall values, while MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications.
+In either case, all 4 quadrants of the confusion matrix are used, making for more balanced measures in the case of imbalanced data [@chicco2017ten].
 
-do not incorporate the entirety of the confusion matrix created when validating predictive models on a test data set.
-Therefore, each of these metrics are likely to be inflated when evaluating model performance.
-Better measures
-
-[???include explanation of why included metrics are better]
+[???Now discuss sampling techniques to account for imbalanced data]
 

### 2019-01-19 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-Current methods rely on the use of classification algorithms to identify which functional genomic elements are best able to discriminate between regions that include TAD boundaries and those that do not [@mourad2016computational, @hong2017computational].
+Current methods rely on the use of classification algorithms to identify which functional genomic elements are best able to discriminate between regions that include TAD boundaries and those that do not [@mourad2016computational; @hong2017computational; @huang2015predicting].
 Most methods differ on the techniques used to identify genomic regions that include TAD boundaries, as well as the models and tools used to evaluate the predictive capability of said models.
@@
 Due to the sparcity of TADs throughout the genome, most defined regions will not contain a TAD boundary.
-In a classification setting, when one is attempting to discriminate between regions with and without TAD boundaries, this will contribute to large imbalance ratios (defined as the ratio of majority to minority classes) [@Orriols-Puig2008].
-It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@estabrooks2004multiple, @chen2013influence].
+In a classification setting, when one is attempting to discriminate between regions with and without TAD boundaries, this will contribute to small imbalance ratios (defined as the ratio of minority to majority classes) [@Orriols-Puig2008].
+It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class;@chen2013influence].
 Similarly, careful consideration must also be taken when deciding which performance metric(s) to present when evaluating predictive models, especially in the case of imbalanced data.
@@
 
-[???Now discuss sampling techniques to account for imbalanced data]
-
-?????????????????????????????????????????????????????????????????????????[include if we decide to directly compare these methods; otherwise referenced above]
-A study published by Mourad et al.
-used multiple logistic regression with LASSO regularization to predict TAD boundaries [@mourad2016computational].
-They considered binning the genome at both 50 base and 1kb intervals and flanking TAD boundaries by 1kb and 20kb regions.
-The outcome Y was determined by whether or not a genomic bin overlapped with a flanked boundary.
-The feature space was obtained by considering the percent overlap between a bin and coordinates defining ChIP-seq peak data.
-Models were then evaluated using AUROC.
-Here, the authors ignored the effect of imbalanced classes as well as the use of potentially biased performance metrics.
-
-In a similar study, Hong et al.
-used domain data from an hESC cell line to build a linear model and predict which genomic elements were associated with TAD boundaries [@hong2017computational].
-They defined boundary segments as genomic regions before and after 150 kilobases of the boundary.
-To solve the imbalance problem, they randomly sampled from regions outside of the 150kb flank.
-For their model, the feature space was determined by the number of counts of ChIP-seq peaks defining functional genomic elements that overlapped with the two segments.
-Individual models were then performed until the best model which included the concensus CTCF signal feature, followed by 10 additional elements was obtained.
-Here, however, it is likely that 1 iteration of random under-sampling will yield biased results, depending on how representative the under-sampled data is.
-Likewise, it is unclear how the performances of other balancing techniques compare (i.e.
-over-sampling or a combination of both under and over-sampling).
-?????????????????????????????????????????????????????????????????????????
+In addition to employing suitable metrics for evaluating models validated on imbalanced data, there also exist several external or data level solutions.
+These mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset.
+Many such solutions have been developed in a variety of fields related to machine learning [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical].
+Likewise, it has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis,].
 
@@
 
-In this study we have developed an ensemble framework that aims to address and compare a variety of data irregularities and characteristics that are associated with the prediction of TAD boundaries.
+In this study we have developed an ensemble framework that aims to address and compare a variety of data irregularities and characteristics that are associated with the prediction of TAD boundaries including class imbalance, feature engineering, and contact map resolution.
 We evaluated domain data obtained from four different resolution contact matrices for the GM12878 cell line including 10 kb, 25 kb, 50 kb, and 100 kb.
-For each resolution, we examined the inclusion of three different predictor types as the feature space for downstream modeling.
-We coupled each predictor type with two separate variable reduction techniques.
-Lastly, we performed a series of three different re-sampling techniques aimed at creating balanced classes.
+For each resolution, we examined the inclusion of 3 different predictor types as the feature space for downstream modeling.
+We then performed a series of 4 different re-sampling techniques aimed at creating balanced classes.
 Random forest classification algorithms were performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the formation of TAD boundaries.
 Model performance was evaluated based on a total of four metrics which included test accuracy, area under the precision-recall curve (AUPRC), F1 score, and Matthew's Correlation Coefficient (MCC).
+This process was then repeated for X additional cell lines including K562, ......
 

### 2019-01-19 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-In addition to employing suitable metrics for evaluating models validated on imbalanced data, there also exist several external or data level solutions.
-These mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset.
+In addition to employing suitable metrics for evaluating models validated on imbalanced data, there also exist several algorithmic or data level solutions.
+Algorithmic level solutions involve modifyng existing classifiers in order to curtail the bias induced by imbalanced classes.
 Many such solutions have been developed in a variety of fields related to machine learning [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical].
-Likewise, it has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis,].
+Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset.
+It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis,].
+For the purposes of this study we focus our attention toward data level solutions so that all results may be classifier independent, and thus, more easily comparable.
 

### 2019-01-19 Manuscript/manuscript.Rmd
edits and additions to manuscript/references

@@
 In a classification setting, when one is attempting to discriminate between regions with and without TAD boundaries, this will contribute to small imbalance ratios (defined as the ratio of minority to majority classes) [@Orriols-Puig2008].
-It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class;@chen2013influence].
+It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class;@chen2013influence;@jeni2013facing].
 Similarly, careful consideration must also be taken when deciding which performance metric(s) to present when evaluating predictive models, especially in the case of imbalanced data.
@@
 Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset.
-It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis,].
+It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
 For the purposes of this study we focus our attention toward data level solutions so that all results may be classifier independent, and thus, more easily comparable.

### 2019-01-20 Manuscript/manuscript.Rmd
Edits through introduction

@@
 
-Existing methods for predicting associations between genomic elements tend to ignore key characteristics of the genomic data.
+Existing methods for predicting associations between genomic elements tend to ignore key characteristics of genomic data.
 Specifically, the number of TAD boundaries is much less than the number of other genomic regions, leading to heavily imbalanced classes.
@@
 
-The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect several epigenetic functions [@lieberman2009comprehensive].
-Analyses have shown that the genome is tightly compacted into distinct compartments.
-There exist regions within these compartments that have been shown to be highly conserved and self-interacting, and termed topologically associating domains (TADs) [@dixon2012topological].
+The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect genomic regulation [@lieberman2009comprehensive].
+Analyses have shown that the genome is folded into distinct compartments termed topologically associating domains (TADs) [@dixon2012topological].
 Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD [@symmons2014functional].
-This suggests that the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
-Furthermore, changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer.
+Approximately 60-80% of TADs remain stable across cell types [@Schmitt:2016aa], suggestingthat the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
+Furthermore, changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [???
+REF].
 Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.
@@
 Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long-range chromatin contacts [@zuin2014cohesin].
-Other regulatory elements like particular histone modifications such as H3K36 and H3K27 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [@rao20143d].
+Other regulatory elements like particular histone modifications such as H3K36 and H3K27 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [???
+Better to mention those that came up in your analysis, otherwise, it is unnecessary information] [@rao20143d].
 These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
-The distinct patterns of different proteins and functional elements point toward the opportunity of using computational approaches in identifying which epigenomic features are most predictive of the development of TAD boundaries, allowing us to better understand what leads to their formation.
+The distinct patterns of different proteins and functional elements point toward the opportunity of using computational approaches in identifying which epigenomic features are most predictive of the TAD boundaries, allowing us to better understand what leads to their formation.
 
-Current methods rely on the use of classification algorithms to identify which functional genomic elements are best able to discriminate between regions that include TAD boundaries and those that do not [@mourad2016computational; @hong2017computational; @huang2015predicting].
+Current methods rely on the use of classification algorithms to identify which functional genomic elements are best able to discriminate between regions that include TAD boundaries and those that do not [@mourad2016computational; @hong2017computational; @huang2015predicting] [???
+Do not understand this sentence].
 Most methods differ on the techniques used to identify genomic regions that include TAD boundaries, as well as the models and tools used to evaluate the predictive capability of said models.
-Moreover, many methods ignore key characteristics of domain data that can impair and bias results.
-
-Most notably is the introduction of heavily imbalanced classes.
-Due to the sparcity of TADs throughout the genome, most defined regions will not contain a TAD boundary.
+Moreover, many methods ignore key characteristics of domain data, such as heavily imbalanced number ot boundaries vs.
+other regions.
 In a classification setting, when one is attempting to discriminate between regions with and without TAD boundaries, this will contribute to small imbalance ratios (defined as the ratio of minority to majority classes) [@Orriols-Puig2008].
 It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class;@chen2013influence;@jeni2013facing].
-Similarly, careful consideration must also be taken when deciding which performance metric(s) to present when evaluating predictive models, especially in the case of imbalanced data.
+Similarly, careful consideration must also be taken when deciding which performance metric(s) to use for evaluation of predictive models, especially in the case of imbalanced data.
 
@@
 It has been shown that the use of AUPRC with imbalanced datasets yields more accurate and intuitive interpretation of model performance when compared to AUROC [@saito2015precision].
-Likewise, metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data.
-In each case, the weight of the measure is carried primarily by the correct classification of the majority class.
+Likewise, metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
 Better measures to consider are the F1-Score and Matthew's Correlation Coefficient (MCC) [@jeni2013facing].
 The F1-Score can be interpreted as a weighted average of the precision and recall values, while MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications.
-In either case, all 4 quadrants of the confusion matrix are used, making for more balanced measures in the case of imbalanced data [@chicco2017ten].
+Both metrics use all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
 
 In addition to employing suitable metrics for evaluating models validated on imbalanced data, there also exist several algorithmic or data level solutions.
-Algorithmic level solutions involve modifyng existing classifiers in order to curtail the bias induced by imbalanced classes.
-Many such solutions have been developed in a variety of fields related to machine learning [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical].
-Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset.
+Algorithmic level solutions involve modifyng existing classifiers in order to curtail the bias induced by imbalanced classes [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical].
+Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset [???
+REFS].
 It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
@@
 Furthermore, there are other aspects of TAD boundary modelling that current methods have failed to consider.
-Most notably is the concept of distance.
-As a feature engineering step, the use of distances (in base pairs) from genomic bins to regions of functional genomic elements has largely been ignored.
+Most notably is the concept of genomic distance.
+As a feature engineering step, the use of distances (in base pairs) from TAD boundaries to regions of various genomic features has largely been ignored.
 However, these distance characteristics have the potential to offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
+
 Additionally, model performance is heavily contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
-It is often unclear from authors of previous studies what resolution contact matrices were used when retrieving TAD boundaries, and how other resolutions would affect their results.
+It is often unclear from previous studies what resolution contact matrices were used when retrieving TAD boundaries, and how other resolutions would affect their results.
 A larger resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
@@
 
-In this study we have developed an ensemble framework that aims to address and compare a variety of data irregularities and characteristics that are associated with the prediction of TAD boundaries including class imbalance, feature engineering, and contact map resolution.
-We evaluated domain data obtained from four different resolution contact matrices for the GM12878 cell line including 10 kb, 25 kb, 50 kb, and 100 kb.
-For each resolution, we examined the inclusion of 3 different predictor types as the feature space for downstream modeling.
-We then performed a series of 4 different re-sampling techniques aimed at creating balanced classes.
-Random forest classification algorithms were performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the formation of TAD boundaries.
-Model performance was evaluated based on a total of four metrics which included test accuracy, area under the precision-recall curve (AUPRC), F1 score, and Matthew's Correlation Coefficient (MCC).
+In this study we have developed an ensemble framework for predicting TAD boundaries that addresses class imbalance problem.
+We evaluated Hi-C data for the GM12878 cell line obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolution.
+For each resolution, we examined the inclusion of three different predictor types, including distance as the measure of association between genomic elements.
+We then tested four re-sampling techniques aimed at creating balanced classes.
+Random forest classification was performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the TAD boundaries.
+Model performance was evaluated using accuracy, area under the precision-recall curve (AUPRC), F1 score, and Matthew's Correlation Coefficient (MCC).
 This process was then repeated for X additional cell lines including K562, ......

### 2019-01-20 Manuscript/manuscript.Rmd
wip

@@
 Replicate Hi-C data for the GM12878 cell line were downloaded from GEO GSE63525 (Experiments HIC001 to HIC018; produced using the MbolI restriction enzyme) [@rao20143d].
-The chromosomal coordinates of topologically associating domains throughout the genome were obtained using the Arrowhead algorithm from the Juicer toolbox provided by the Aiden Laboratory (https://github.com/aidenlab/juicer) [@durand2016juicebox].
-Domain data was extracted at 4 different kilobase (kb) resolutions including 10 kb, 25 kb, 50 kb, and 100 kb.
-Identified TAD boundaries were represented by their location on the linear genome (GRCh37/hg19 human genome assembly), including start and end coordinates for chromosomes 1 through 22.
-The start and end coordinates of all hierarchical TADs were concatenated, sorted, and unique TAD boundary points were obtained.
+The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
+The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained.
 
@@
 
-To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution (Figure 1).
-For example, fordomain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
-To accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
+To accommodate for the uncertainty in the location of TAD boundary points, they were flanked on both sides by regions of the size of the resolution of the data (Figure 1).
 For example, returning to the 10 kb resolution example, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
-A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
-Otherwise, the bin was labeled as not containing a boundary (Y=0).
+
+The response vector $Y$ was formed by genomic regions defined by the resolution of the data.
+Genomic regions flanking TAD boundaries were labeled as $Y=1$; otherwise, the regions were labeled as not containing a boundary ($Y=0$).
 

### 2019-01-20 Manuscript/Figures/figure_legends.Rmd
Fig 1 legend done

@@
 
-# Figure 1: Model Construction
-
-Diagram of the model construction used for downstream analysis.
-The linear genome was binned according to the resolution of the respective HiC experiment (either 5kb, 25kb, 50kb, or 100kb intervals).
-TAD boundaries were then flanked by 1-unit on either side of the boundary point.
-The unit flanking was indicative of the resolution that the domain data was obtained from (i.e.
-for 5kb resolution, 1 unit represents 5kb for a total flanking region of 10kb).
-The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region.
+**Figure 1: Model Construction.** The linear genome was binned according to the resolution of the Hi-C data.
+TAD boundaries were then flanked by 1 resolution-unit on both sides of the boundary point.
+[???
+The following is unclear.
+Show Y on the figure.
+Are you talking about overlap only?] The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region.
 The positional coordinates of each functional genomic element, obtained from ENCODE, were then used to define the feature space of the models.

### 2019-01-20 Manuscript/Supplementary/supplementary_legends.Rmd
Move supplementary legends out

--- 2019-01-20 Manuscript/manuscript.Rmd
@@
 ---
-title: "Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings"
-csl: styles.ref/genomebiology.csl
-output:
-  word_document:
-    reference_docx: styles.doc/NIH_grant_style.docx
-bibliography: References/references.bib
+title: "Legends for supplementary material"
+output: pdf_document
 ---
-
-Spiro C. Stilianoudakis^1^ (stilianoudasc@mymail.vcu.edu), Mikhail G. Dozmorov^1\*^ (mikhail.dozmorov@vcuhealth.org)
-
-^1^ Dept. of Biostatistics, Virginia Commonwealth University, Richmond, VA, 23298, USA  
-^\*^ To whom correspondence should be addressed: Virginia Commonwealth University, Richmond, VA, 23298, 804-827-2055, mikhail.dozmorov@vcuhealth.org
-
-# ABSTRACT
-
-**Background.** Chromosome conformation capture sequencing technologies have shown that the three-dimensional (3D) structure of the genome is folded into distinct compartments, known as topologically associated domains (TADs) - units of coordinated gene expression.
-The location of TAD boundaries is highly conserved, suggesting the presence of epigenomic marks aiding in TAD formation.
-The ability to predict which epigenomic features are most associated with the TAD boundaries will allow to better understand the regulatory role of the 3D structure of the genome.
-
-Existing methods for predicting associations between genomic elements tend to ignore key characteristics of genomic data.
-Specifically, the number of TAD boundaries is much less than the number of other genomic regions, leading to heavily imbalanced classes.
-Furthermore, most methods utilize direct overlap as a means to quantify the association, while distance, the measure of spatial relationships, remains unaccounted for.
-Consequently, distances on a genomic scale vary widely, leaving uncertainty how the heavily right-tailed distribution of distance measures will affect the model’s performance.
-
-**Methods.** We propose a novel data pre-processing pipeline that addresses those shortcomings.
-Lasso and Elastic Net were used for feature selection, coupled with five classifier methods.
-A number of classifier performance metrics were assessed, including the F1 measure and Matthew Correlation Coefficient (MCC), and area under the ROC curve (AUROC).
-
-**Results.** Data preprocessing (log2-transformation and standardization) improves the performance of classification algorithms and allows for the ability to more accurately predict which genomic features are most associated with TAD boundaries.
-In contrast to overlap-based association measures, the distance between genomic elements was the most predictive measure.
-The random undersampling strategy addresses the class imbalance problem the most effectively in nearly all settings.
-
-**Conclusions.** Current methods used to model the epigenomic features associated with TAD boundaries are insufficiently robust to handle properties of genomic data.
-Models applied to unprocessed data can have poor predictive performances.
-Focusing solely on standard performance assessment metrics, such as AUROC, can mask poor performance of the models; thus, the use of more balanced metrics, such as F1 and MCC, is warranted.
-Our model results in better performances and more accurate identification of important features associated with the formation of TAD boundaries.
-
-# INTRODUCTION
-
-The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect genomic regulation [@lieberman2009comprehensive].
-Analyses have shown that the genome is folded into distinct compartments termed topologically associating domains (TADs) [@dixon2012topological].
-Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD [@symmons2014functional].
-Approximately 60-80% of TADs remain stable across cell types [@Schmitt:2016aa], suggestingthat the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
-Furthermore, changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [???
-REF].
-Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.
-
-The mechanisms underlying the formation of TADs are a complex and active area of research.
-Recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangements of higher-order chromatin architecture [@phillips2013chromatin].
-Insulators are multi-faceted regulatory sequences that moderate a variety of genomic processes including activation, repression, and enhancer blocking.
-Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long-range chromatin contacts [@zuin2014cohesin].
-Other regulatory elements like particular histone modifications such as H3K36 and H3K27 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [???
-Better to mention those that came up in your analysis, otherwise, it is unnecessary information] [@rao20143d].
-These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
-The distinct patterns of different proteins and functional elements point toward the opportunity of using computational approaches in identifying which epigenomic features are most predictive of the TAD boundaries, allowing us to better understand what leads to their formation.
-
-Current methods rely on the use of classification algorithms to identify which functional genomic elements are best able to discriminate between regions that include TAD boundaries and those that do not [@mourad2016computational; @hong2017computational; @huang2015predicting] [???
-Do not understand this sentence].
-Most methods differ on the techniques used to identify genomic regions that include TAD boundaries, as well as the models and tools used to evaluate the predictive capability of said models.
-Moreover, many methods ignore key characteristics of domain data, such as heavily imbalanced number ot boundaries vs.
-other regions.
-In a classification setting, when one is attempting to discriminate between regions with and without TAD boundaries, this will contribute to small imbalance ratios (defined as the ratio of minority to majority classes) [@Orriols-Puig2008].
-It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class;@chen2013influence;@jeni2013facing].
-Similarly, careful consideration must also be taken when deciding which performance metric(s) to use for evaluation of predictive models, especially in the case of imbalanced data.
-
-Commonly used measures of model performance for binary classifiers include the area under the receiver operating curve (AUROC).
-The popularity surrounding the use of ROC curves is that they do not depend on a threshold.
-However, when the prevalence of an event is low--that is, a defined genomic region containing a TAD boundary--mean probabilities are biased towards the majority class.
-This results in the area of interest under an ROC curve to be compressed toward a small corner in the ROC space [@prati2011survey].
-While not directly affecting the value of the AUROC, this can have severe consequences on the interpretability of the model's performance.
-A better threshold-free measure to use when dealing with imbalanced data in the area under the precision-recall curve (AUPRC).
-It has been shown that the use of AUPRC with imbalanced datasets yields more accurate and intuitive interpretation of model performance when compared to AUROC [@saito2015precision].
-Likewise, metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
-Better measures to consider are the F1-Score and Matthew's Correlation Coefficient (MCC) [@jeni2013facing].
-The F1-Score can be interpreted as a weighted average of the precision and recall values, while MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications.
-Both metrics use all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
-
-In addition to employing suitable metrics for evaluating models validated on imbalanced data, there also exist several algorithmic or data level solutions.
-Algorithmic level solutions involve modifyng existing classifiers in order to curtail the bias induced by imbalanced classes [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical].
-Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset [???
-REFS].
-It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
-For the purposes of this study we focus our attention toward data level solutions so that all results may be classifier independent, and thus, more easily comparable.
-
-Furthermore, there are other aspects of TAD boundary modelling that current methods have failed to consider.
-Most notably is the concept of genomic distance.
-As a feature engineering step, the use of distances (in base pairs) from TAD boundaries to regions of various genomic features has largely been ignored.
-However, these distance characteristics have the potential to offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
-
-Additionally, model performance is heavily contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
-It is often unclear from previous studies what resolution contact matrices were used when retrieving TAD boundaries, and how other resolutions would affect their results.
-A larger resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
-This will contribute to smaller sample sizes and could effect predictive performances.
-
-In this study we have developed an ensemble framework for predicting TAD boundaries that addresses class imbalance problem.
-We evaluated Hi-C data for the GM12878 cell line obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolution.
-For each resolution, we examined the inclusion of three different predictor types, including distance as the measure of association between genomic elements.
-We then tested four re-sampling techniques aimed at creating balanced classes.
-Random forest classification was performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the TAD boundaries.
-Model performance was evaluated using accuracy, area under the precision-recall curve (AUPRC), F1 score, and Matthew's Correlation Coefficient (MCC).
-This process was then repeated for X additional cell lines including K562, ......
-
-# METHODS
-
-## DOMAIN DATA
-
-Replicate Hi-C data for the GM12878 cell line were downloaded from GEO GSE63525 (Experiments HIC001 to HIC018; produced using the MbolI restriction enzyme) [@rao20143d].
-The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
-The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained.
-
-## MODEL CONSTRUCTION
-
-To accommodate for the uncertainty in the location of TAD boundary points, they were flanked on both sides by regions of the size of the resolution of the data (Figure 1).
-For example, returning to the 10 kb resolution example, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
-
-The response vector $Y$ was formed by genomic regions defined by the resolution of the data.
-Genomic regions flanking TAD boundaries were labeled as $Y=1$; otherwise, the regions were labeled as not containing a boundary ($Y=0$).
-
-## GENOMIC ANNOTATION DATA
-
-Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
-The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments.
-Each genomic annotation was represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological significance.
-
-## ENSEMBLE FRAMEWORK
-
-An ensemble of models was established for the purposes of systematically comparing the performances of different parameters in the framework.
-Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type for the feature space (Figure 2).
-
-The data sets used for modeling were composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
-These two classes made up the minority and majority sets respectively.
-The data was then split into a 7:3 ratio of training to testing sets.
-Each training and testing set was composed of a similar majority to minority class ratio as the full data set.
-That is, for the task of prediction, the test set remained constant for all ensemble systems in order to account for a fair and unbiased comparison.
-
-### FEATURE ENGINEERING AND REDUCTION USING GENOMIC ANNOTATIONS
-
-Using the sets of genomic annotations, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries (Figure 3):
-
-1.
-**Overlap Counts (OC)**: For each genomic bin, the total number of instances where a bin overlapped with genomic annotation regions (features) was calculated.
-In the case of no overlaps the value is set as 0.
-
-2.
-**Overlap Percent (OP)**: For each genomic bin, the percent overlap between the feature width and the total width of the bin was calculated.
-We defined the feature width as the number of bases that overlapped with the genomic bin.
-The percent was then calculated by dividing the feature width by the bin width.
-If multiple overlaps existed, the feature width was defined as the sum of the total number of bases that overlapped with a particular bin.
-Note that the bin width remained constant for a given resolution (either 10 kb, 25 kb, 50 kb, or 100 kb).
-Values for bins with no overlaps were set to be 0.
-
-3.
-**Log Distance**: For each genomic bin, the log of the distance (in bases) from the center of the bin to the center of the nearest region of a respective genomic annotation region was calculated.
-The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1)
-
-To assess the predictive performance for each predictor type, we performed individual random forest classification algorithms utilizing each set predictor types as the feature space, in addition to a model with all combined types.
-Precision-Recall (PR) Curves, and subsequent area under the PR curves (AUPRC), were used to evaluate which predictor type contributed to the best model performance.
-Recursive feature elimination (RFE) was then used to determine the optimal number of features for models within each set of predictor types.
-Here, random forest models were used to assign weights to a set features of a given size.
-The optimal number of features was determined by the AUPRC of the corresponding model.
-
-### RE-SAMPLING TECHNIQUES
-
-We then evaluated three re-sampling techniques (in addition to no re-sampling) on the reduced training set, in order to evaluate the problem of imbalanced classes. They are detailed below:
-
-1. **No Sampling**: All of the data points from the majority and minority class of the training set were used.
-
-2.
-**Random Under-Sampling (RUS)**: All of the minority classes from the training set were used.
-Sampling without replacement was used to obtain the same number of the majority classes.
-We performed 50 iterations of random under-sampling.
-At each iteration a random forest classification algorithm was performed.
-Performance metrics were aggregated by taking the average across all of the iterations.
-
-3.
-**Random Over-Sampling (ROS)**: All of the majority classes from the training set were used.
-Sampling with replacement was used to obtain the same number of the minority classes.
-Similar to the under-sampling technique, 50 iterations were performed and results were aggregated by taking the average across iterations.
-
-4.
-**SMOTE** (Synthetic Minority Over-Sampling Technique): This method incorporates both random under- and over-sampling.
-Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class [@chawla2002smote].
-To account for the bias introduced by the under-sampling, we performed 50-iterations of SMOTE The user is able to specify the parameters denoting the percent of over- and under-sampling from the two classes.
-We chose the parameters that would create perfectly balanced classes.
-The `DMwR` package in R (version 3.4.2) was used to perform SMOTE.
-
-5.
-**ROSE** (Random Over-Sampling Examples): Similar to SMOTE, ROSE combines combines techniques of over-sampling and under-sampling.
-However, contrary to SMOTE, all of the data generated by ROSE is synthetic.
-The data is created by sampling from one of the two classes, then generating a new example in its neighborhood using a smoothed bootstrap approach.
-The shape of the neighborhood is determined by the kernal density estimate of the two classes [@lunardon2013r].
-Another important distinction between ROSE and SMOTE is that, for ROSE, the creation of perfectly balanced classes is unlikely due to the randomness in sampling between the two classes.
-The `ROSE` package in R (version 3.4.2) was used to perform ROSE.
-
-### CLASSIFICATION
-
-A classification algorithm in the form of a random forest was performed and validated using the same test set for all models in the ensemble.
-To reduce bias due to random dataset generation, 10-fold cross validation was used.
-The default number of features to consider at each node of the random forest algorithm was set as the square root of the number of features in the model.
-Likewise, the number of ensemble trees to aggregate was set at 500.
-Once the model was implemented, it was assessed using the test set, and performance metrics were then recorded.
-
-### MODEL EVALUATION & PREDICTION
-
-The efficacy of different ensemble systems was compared using various performance metrics including accuracy, AUC, F1-score, and MCC. These metrics are defined as follows:
-
-$$Accuracy = \frac{TP + TN}{TP + TN + FP + FN}$$
-$$F1 - Score = \frac{2TP}{2TP + FP + FN}$$
-$$MCC = \frac{TP \times TN - FP \times FN}{\sqrt{ (TP + FP)(TP+FN)(TN+FP)(TN+FN) }}$$
-
-Here, TP refers to the number of bins correctly identified as containing a TAD boundary (true positives), FP refers to the number of bins incorrectly identified as containing a TAD boundary (false positives), TN refers to the number of bins correctly identified as not containing a TAD boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a TAD boundary.
-Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-The evaluation metrics listed above are all considered single threshold measures.
-That is, they are defined for individual thresholds that separated class prediction.
-Thererfore they are unable to give an overview of the potential range of performance as thresholds vary.
-A full list of the single threshold measures used (including additional metrics not reported), along with their respective formulas, are provided in Supplementary Table 6.
-In order to evaluate the trade-off between precision and recall, we also considered a threshold free measure in form of the area under the precision recall curve (AUPRC).
-
-For the task of identifying the functional genomic elements that were most predictive of the formation of TAD boundaries, we evaluated the variable importances associated with each predictor of the random forest model.
-For each tree, the prediction accuracy on the out-of-bag portion of the data is recorded.
-Then the same was done after permuting each predictor variable.
-The difference between the two accuracies were then averaged over all trees, and normalized by the standard error [@kuhn2012caret].
-
-# RESULTS
-
-## ENSEMBLE COMPARISONS
-
-We evaluated and compared Hi-C datasets at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}, used three predictor types P = {OC, OP, Distance}, two variable reduction techniques V = {LASSO, Elastic-Net}, and five class balancing techniques C = {None, RUS, ROS, SMOTE, ROSE}.
-A system produced from the ensemble framework was defined as: E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.
-Letting |X| denote the cardinality of each set, we evaluated |R| x |P| x |V| x |C| different ensemble systems, totaling 120 (=4 $\times$ 3 $\times$ 2 $\times$ 5) separate models.
-For simplicity, we present the most significant results, with the complete results available as Supplementary Tables.
-
-### CLASS DISTRIBUTIONS ACROSS RESOLUTIONS
-
-The coordinates of the corresponding 10 kb resolution contact maps resulted in a total of X genomic bins [???
-To be modified for the whole genome].
-There were only Y bins that overlapped with a flanked TAD boundary representing the minority class, for an imbalance ratio of (X-Y):Y [???
-To be modified for the whole genome].
-After applying each resampling technique to the training set, we obtained perfectly balanced classes for all except the ROSE technique (Figure 4).
-
-An increase in resolution resulted in an overall decrease in the number of genomic bins, as well as a slight decrease in the imbalance ratio (Supplementary Figure 2).
-After performing the resampling techniques, the resulting imbalance ratios remained similar across the other 3 data resolutions (Supplementary Figure 2).
-
-### DISTANCE-TYPE PREDICTORS PERFORM BEST
-
-#Discussion
-
-# Abbreviations
-
-# Acknowledgements
-
-_Conflict of Interest._ None.
-
-# Funding
-
-# Tables
-
-# Figures
-
-# Table Legends
-
-## Table 1: Class Distributions
-
-Summary of the class distributions for the 5 kb resolution domain data, across each re-sampling technique.
-All re-sampling techniques yielded completely balanced classes.
-That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.
-
-# Figure legends
-
-## Figure 1: Model Construction
-
-Diagram of the model construction used for downstream analysis.
-The linear genome was binned according to the resolution of the respective HiC experiment (either 10 kb, 25 kb, 50 kb, or 100 kb intervals).
-TAD boundaries were then flanked by 1-unit on either side of the boundary point.
-The unit flanking was indicative of the resolution that the domain data was obtained from (i.e.
-for 10 kb resolution, 1 unit represents 10 kb for a total flanking region of 20 kb).
-The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region.
-The positional coordinates of each functional genomic element, obtained from ENCODE, were then used to define the feature space of the models.
-
-## Figure 2: Ensemble Framework/Model Building Pipeline
-
-A diagram of the model building pipeline given a combination of inputs from the ensemble framework.
-The data was split into a 7:3 training set to testing set ratio, an $l_{1}$ norm regularization (LASSO) was implemented, and a random forest classification algorithm was performed.
-Each model was then validated on the same testing set.
-
-## Figure 3: Predictor Types
-
-Diagram of the 3 predictor types considered when assessing the relationship between TAD boundaries and functional genomic elements.
-Each predictor type was used as the feature space in downstream analyses for predicting which functional genomic elements were associated with the formation of TAD boundaries.
-Featured above are bin-specific examples of the construction of each predictor type.
-(Left) The overlap count (OC) predictors were calculated by considering the total number of elemental regions that overlapped with each genomic bin.
-(Middle) The overlap percent (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin and dividing by the total bin width (either 5, 25, 50, or 100 kilobases given resolution of boundary data).
-(Right) The distance predictors were calculated by measuring the distance (in base pairs) from the center of each genomic bin to the center of the nearest elemental region of interest.
-The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective functional genomic element.
-
-## Figure 4: Class Imbalance
-
-Barplots illustrating the class imbalance problem featured across each of the four different resolutions that were analyzed.
-Minority classes represent the number of genomic bins that contain a TAD boundary, while the majority classes represent the number of genomic bins that do not contain a TAD boundary.
-
-## Figure 5: Performances of Models with No Class-Balancing
-
-Barplots measuring the predictive performance of models built on imbalanced datasets.
-The performance metrics considered were accuracy, AUC, F1-Score, and MCC.
-Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).
-
-## Figure 6: Performances of Models with Randomly Under-sampled Data.
-
-Barplots measuring the predictive performance of models built on datasets using 50 iterations of random under-sampling.
-The performance metrics considered were accuracy, AUC, F1-Score, and MCC.
-Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).
-
-# Supplementary Tables and Figures
-
-# Supplementary Legends
 
@@
 Results of various metrics used to assess predictive performances for models that were built on both SMOTE-balanced and random over-sampled datasets.
-
-# References

### 2019-01-20 Manuscript/manuscript.Rmd
Move supplementary legends out

@@
 
-# Supplementary Tables and Figures
-
-# Supplementary Legends
-
-## Table 1: List of Genomic Annoations.
-
-The full list of genomic annotations used in downstream analyses.
-These annotations were the functional genomic elements used to predict the formation of TAD boundaries.
-They were obtained via ChIP-Seq experiments, mapped to human genome assembly hg19, and made available by the ENCODE Consortium.
-Each element is denoted by its genomic class, and which cell type it is applied to.
-The elements that are invariant to a specific cell type are denoted by "Invariant".
-Additionally, a breif description and specific paths for downloads are also provided.
-
-## Table 2: Class Distributions for Other Resolutions
-
-Summary of the class distributions for each of the other resolution domain data sets (25 kb, 50 kb, and 100 kb), across each re-sampling technique.
-As with the 5 kb data, all re-sampling techniques yielded completely balanced classes.
-That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.
-
-## Table 3: Model Performances When Not Accounting for Class Imbalance
-
-Results of various metrics used to assess predictive performances for models that were built on fully imbalanced datasets.
-
-## Figure 1: Performances of Models with Both SMOTE-Balanced and Randomly Over-sampled Data.
-
-Barplots measuring the predictive performance of models built on datasets using 50 iterations of both the SMOTE algorithm (A) and random over-sampling (B).
-The performance metrics considered were accuracy, AUC, F1-Score, and MCC.
-Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).
-
-## Table 4:
-
-Results of various metrics used to assess predictive performances for models that were built on random under-sampled datasets.
-
-## Table 5:
-
-Results of various metrics used to assess predictive performances for models that were built on both SMOTE-balanced and random over-sampled datasets.
-
 # References

### 2019-01-20 Manuscript/Figures/figure_legends.Rmd
Fix Figure 2 legend

@@
 **Figure 2.
-Diagram of the three predictor types considered when assessing the relationship between TAD boundaries and genomic annotations.** The _overlap count_ (OC) predictors were calculated by considering the total number of elemental regions that overlapped with each genomic bin.
-The _overlap percent_ (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin and dividing by the total bin width.
-The _distance_ predictors were calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest elemental region of interest.
-The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective genomic annotations.
+The three predictor types considered when quantifying the association between TAD boundaries and genomic annotations.** The _overlap count_ (OC) predictors consider the total number of genomic features that overlapped with each genomic bin.
+The _overlap percent_ (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin by the total bin width.
+The _distance_ predictors were calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest genomic feature.
 

### 2019-01-20 Manuscript/manuscript.Rmd
wip

@@
 The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained.
+Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table S1).
 
@@
 
-The response vector $Y$ was formed by genomic regions defined by the resolution of the data.
+The response vector $Y$ was formed by genomic regions (bins) defined by the resolution of the data.
 Genomic regions flanking TAD boundaries were labeled as $Y=1$; otherwise, the regions were labeled as not containing a boundary ($Y=0$).
 
-## GENOMIC ANNOTATION DATA
+Using the sets of genomic features, we created three types of predictors (Figure 2):
 
-Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
-The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments.
-Each genomic annotation was represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological significance.
+1. **Overlap Counts (OC)**: For each genomic bin, the total number of overlaps with genomic features was calculated. In the case of no overlaps the value is set as 0.
+
+2.
+**Overlap Percent (OP)**: For each genomic bin, the percent overlap was defined as the total width of features overlapping a bin divided by the bin width.
+Values for bins with no overlaps were set to be 0.
+
+3.
+**Distance**: For each genomic bin, the log [???
+didn't you test raw distance first?] [???
+log10?] of the distance (in bases) from the center of the bin to the center of the nearest genomic feature region was calculated.
+The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1)
+
+To assess the predictive performance for each predictor type, we performed individual random forest classification algorithms utilizing each set predictor types as the feature space, in addition to a model with all combined types.
+Precision-Recall (PR) Curves, and subsequent area under the PR curves (AUPRC), were used to evaluate which predictor type contributed to the best model performance.
+Recursive feature elimination (RFE) was then used to determine the optimal number of features for models within each set of predictor types.
+Here, random forest models were used to assign weights to a set features of a given size.
+The optimal number of features was determined by the AUPRC of the corresponding model.
 
@@
 That is, for the task of prediction, the test set remained constant for all ensemble systems in order to account for a fair and unbiased comparison.
-
-### FEATURE ENGINEERING AND REDUCTION USING GENOMIC ANNOTATIONS
-
-Using the sets of genomic annotations, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries (Figure 3):
-
-1.
-**Overlap Counts (OC)**: For each genomic bin, the total number of instances where a bin overlapped with genomic annotation regions (features) was calculated.
-In the case of no overlaps the value is set as 0.
-
-2.
-**Overlap Percent (OP)**: For each genomic bin, the percent overlap between the feature width and the total width of the bin was calculated.
-We defined the feature width as the number of bases that overlapped with the genomic bin.
-The percent was then calculated by dividing the feature width by the bin width.
-If multiple overlaps existed, the feature width was defined as the sum of the total number of bases that overlapped with a particular bin.
-Note that the bin width remained constant for a given resolution (either 10 kb, 25 kb, 50 kb, or 100 kb).
-Values for bins with no overlaps were set to be 0.
-
-3.
-**Log Distance**: For each genomic bin, the log of the distance (in bases) from the center of the bin to the center of the nearest region of a respective genomic annotation region was calculated.
-The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1)
-
-To assess the predictive performance for each predictor type, we performed individual random forest classification algorithms utilizing each set predictor types as the feature space, in addition to a model with all combined types.
-Precision-Recall (PR) Curves, and subsequent area under the PR curves (AUPRC), were used to evaluate which predictor type contributed to the best model performance.
-Recursive feature elimination (RFE) was then used to determine the optimal number of features for models within each set of predictor types.
-Here, random forest models were used to assign weights to a set features of a given size.
-The optimal number of features was determined by the AUPRC of the corresponding model.
 

### 2019-01-20 Manuscript/manuscript.Rmd
Methods reorganized and rewritten

@@
 log10?] of the distance (in bases) from the center of the bin to the center of the nearest genomic feature region was calculated.
-The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1)
-
-To assess the predictive performance for each predictor type, we performed individual random forest classification algorithms utilizing each set predictor types as the feature space, in addition to a model with all combined types.
-Precision-Recall (PR) Curves, and subsequent area under the PR curves (AUPRC), were used to evaluate which predictor type contributed to the best model performance.
-Recursive feature elimination (RFE) was then used to determine the optimal number of features for models within each set of predictor types.
-Here, random forest models were used to assign weights to a set features of a given size.
-The optimal number of features was determined by the AUPRC of the corresponding model.
-
-## ENSEMBLE FRAMEWORK
-
-An ensemble of models was established for the purposes of systematically comparing the performances of different parameters in the framework.
-Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type for the feature space (Figure 2).
+The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1).
 
@@
 
-We then evaluated three re-sampling techniques (in addition to no re-sampling) on the reduced training set, in order to evaluate the problem of imbalanced classes. They are detailed below:
+In order to evaluate the problem of imbalanced classes, we then evaluated three re-sampling techniques.
 
@@
 Sampling with replacement was used to obtain the same number of the minority classes.
-Similar to the under-sampling technique, 50 iterations were performed and results were aggregated by taking the average across iterations.
+Similar to the under-sampling technique, 50 iterations were performed and the results of a random forest classification were aggregated by taking the average across iterations.
 
@@
 Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class [@chawla2002smote].
-To account for the bias introduced by the under-sampling, we performed 50-iterations of SMOTE The user is able to specify the parameters denoting the percent of over- and under-sampling from the two classes.
+To account for the bias introduced by the under-sampling, we performed 50-iterations of SMOTE.
 We chose the parameters that would create perfectly balanced classes.
-The `DMwR` package in R (version 3.4.2) was used to perform SMOTE.
+The `DMwR` v.3.4.2 R package was used to perform SMOTE.
 
 5.
-**ROSE** (Random Over-Sampling Examples): Similar to SMOTE, ROSE combines combines techniques of over-sampling and under-sampling.
+**ROSE** (Random Over-Sampling Examples): Similar to SMOTE, ROSE combines techniques of over-sampling and under-sampling.
 However, contrary to SMOTE, all of the data generated by ROSE is synthetic.
 The data is created by sampling from one of the two classes, then generating a new example in its neighborhood using a smoothed bootstrap approach.
-The shape of the neighborhood is determined by the kernal density estimate of the two classes [@lunardon2013r].
+The shape of the neighborhood is determined by the kernel density estimate of the two classes [@lunardon2013r].
 Another important distinction between ROSE and SMOTE is that, for ROSE, the creation of perfectly balanced classes is unlikely due to the randomness in sampling between the two classes.
-The `ROSE` package in R (version 3.4.2) was used to perform ROSE.
+The `ROSE` v.3.4.2 [???
+Is it correct?
+Same version as DMwR?] R packagewas used to perform ROSE.
 
@@
 
-A classification algorithm in the form of a random forest was performed and validated using the same test set for all models in the ensemble.
+A classification algorithm in the form of a random forest was performed and validated using the same test [???
+Training?] set for all models in the ensemble.
 To reduce bias due to random dataset generation, 10-fold cross validation was used.
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-The evaluation metrics listed above are all considered single threshold measures.
+The evaluation metrics listed above are all considered to be single threshold measures.
 That is, they are defined for individual thresholds that separated class prediction.
-Thererfore they are unable to give an overview of the potential range of performance as thresholds vary.
-A full list of the single threshold measures used (including additional metrics not reported), along with their respective formulas, are provided in Supplementary Table 6.
-In order to evaluate the trade-off between precision and recall, we also considered a threshold free measure in form of the area under the precision recall curve (AUPRC).
+Thererfore, they are unable to give an overview of the potential range of performance as thresholds vary.
+In order to evaluate the trade-off between precision and recall, we also considered a threshold-free measure in form of the area under the precision recall curve (AUPRC).
 
@@
 The difference between the two accuracies were then averaged over all trees, and normalized by the standard error [@kuhn2012caret].
+Recursive feature elimination (RFE) was then used to determine the optimal number of features for models within each set of predictor types.
+Here, random forest models were used to assign weights to a set features of a given size.
+The optimal number of features was determined by the AUPRC of the corresponding model.
+[???
+Rewrite this paragraph as I put some disjoint sentences]
 
@@
 
-We evaluated and compared Hi-C datasets at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}, used three predictor types P = {OC, OP, Distance}, two variable reduction techniques V = {LASSO, Elastic-Net}, and five class balancing techniques C = {None, RUS, ROS, SMOTE, ROSE}.
+We created an ensemble framework to systematically evaluate the performance of of TAD boundary prediction under different conditions and resampling approaches (Figure 3).
+We evaluated and compared Hi-C datasets at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}, used three predictor types P = {OC, OP, Distance}, two variable reduction techniques V = {LASSO, Elastic-Net} [???
+Is that so?], and five class balancing techniques C = {None, RUS, ROS, SMOTE, ROSE}.
 A system produced from the ensemble framework was defined as: E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.

### 2019-01-20 Manuscript/manuscript.Rmd
Move old figure legends, groom results

@@
 We created an ensemble framework to systematically evaluate the performance of of TAD boundary prediction under different conditions and resampling approaches (Figure 3).
-We evaluated and compared Hi-C datasets at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}, used three predictor types P = {OC, OP, Distance}, two variable reduction techniques V = {LASSO, Elastic-Net} [???
-Is that so?], and five class balancing techniques C = {None, RUS, ROS, SMOTE, ROSE}.
-A system produced from the ensemble framework was defined as: E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.
-Letting |X| denote the cardinality of each set, we evaluated |R| x |P| x |V| x |C| different ensemble systems, totaling 120 (=4 $\times$ 3 $\times$ 2 $\times$ 5) separate models.
+Briefly, we used Hi-C datasets at four different resolutions $R = \{ 10 kb, 25 kb, 50 kb, 100 kb \}$, used three predictor types $P = \{ OC, OP, Distance \}$, two variable reduction techniques $V = \{ LASSO, Elastic-Net \}$ [???
+Is that so?], and five class balancing techniques $C = \{ None, RUS, ROS, SMOTE, ROSE \}$.
+A system produced from the ensemble framework was defined as: $E = \{ r, p, v, c \}$, where $r \in R$, $p \in P$, $v \in V$, and $c \in C$.
+Letting $|X|$ denote the cardinality of each set, we evaluated $|R| \times |P| \times |V| \times |C|$ different ensemble systems, totaling $120 (=4 \times 3 \times 2 \times 5)$ [???
+Check if you use Lasso only] separate models.
 For simplicity, we present the most significant results, with the complete results available as Supplementary Tables.
@@
 
-#Discussion
+# Discussion
 
@@
 
-# Tables
-
-# Figures
-
-# Table Legends
-
-## Table 1: Class Distributions
-
-Summary of the class distributions for the 5 kb resolution domain data, across each re-sampling technique.
-All re-sampling techniques yielded completely balanced classes.
-That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.
-
-# Figure legends
-
-## Figure 1: Model Construction
-
-Diagram of the model construction used for downstream analysis.
-The linear genome was binned according to the resolution of the respective HiC experiment (either 10 kb, 25 kb, 50 kb, or 100 kb intervals).
-TAD boundaries were then flanked by 1-unit on either side of the boundary point.
-The unit flanking was indicative of the resolution that the domain data was obtained from (i.e.
-for 10 kb resolution, 1 unit represents 10 kb for a total flanking region of 20 kb).
-The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region.
-The positional coordinates of each functional genomic element, obtained from ENCODE, were then used to define the feature space of the models.
-
-## Figure 2: Ensemble Framework/Model Building Pipeline
-
-A diagram of the model building pipeline given a combination of inputs from the ensemble framework.
-The data was split into a 7:3 training set to testing set ratio, an $l_{1}$ norm regularization (LASSO) was implemented, and a random forest classification algorithm was performed.
-Each model was then validated on the same testing set.
-
-## Figure 3: Predictor Types
-
-Diagram of the 3 predictor types considered when assessing the relationship between TAD boundaries and functional genomic elements.
-Each predictor type was used as the feature space in downstream analyses for predicting which functional genomic elements were associated with the formation of TAD boundaries.
-Featured above are bin-specific examples of the construction of each predictor type.
-(Left) The overlap count (OC) predictors were calculated by considering the total number of elemental regions that overlapped with each genomic bin.
-(Middle) The overlap percent (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin and dividing by the total bin width (either 5, 25, 50, or 100 kilobases given resolution of boundary data).
-(Right) The distance predictors were calculated by measuring the distance (in base pairs) from the center of each genomic bin to the center of the nearest elemental region of interest.
-The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective functional genomic element.
-
-## Figure 4: Class Imbalance
-
-Barplots illustrating the class imbalance problem featured across each of the four different resolutions that were analyzed.
-Minority classes represent the number of genomic bins that contain a TAD boundary, while the majority classes represent the number of genomic bins that do not contain a TAD boundary.
-
-## Figure 5: Performances of Models with No Class-Balancing
-
-Barplots measuring the predictive performance of models built on imbalanced datasets.
-The performance metrics considered were accuracy, AUC, F1-Score, and MCC.
-Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).
-
-## Figure 6: Performances of Models with Randomly Under-sampled Data.
-
-Barplots measuring the predictive performance of models built on datasets using 50 iterations of random under-sampling.
-The performance metrics considered were accuracy, AUC, F1-Score, and MCC.
-Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).
-
 # References

### 2019-01-20 Manuscript/Figures/figure_legends.Rmd
Move old legends here

@@
 **Figure 3: Ensemble Framework/Model Building Pipeline.** A diagram of the model building pipeline given an a combination of inputs from the ensemble framework.
-The data was split into a 7:3 training set to testing set ratio, the variable reduction technique of choice was used to minimize the number of uninformative predictors, and a random forest classification algorithm was performed.
+The data was split into a 7:3 training:testing set ratio, the variable reduction technique of choice [???
+Which one?] was used to minimize the number of uninformative predictors, and, following a resampling techinque, a random forest classification algorithm was performed on the training set.
 Each model was then validated on the same testing set.
@@
 Within each set, each bar represents the performance of a model with a specific predictor type; either overlap counts (OC) in red, overlap percent (OP) in green, or distance in blue.
+
+# OLD Figure legends
+
+## Figure 1: Model Construction
+
+Diagram of the model construction used for downstream analysis.
+The linear genome was binned according to the resolution of the respective HiC experiment (either 10 kb, 25 kb, 50 kb, or 100 kb intervals).
+TAD boundaries were then flanked by 1-unit on either side of the boundary point.
+The unit flanking was indicative of the resolution that the domain data was obtained from (i.e.
+for 10 kb resolution, 1 unit represents 10 kb for a total flanking region of 20 kb).
+The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region.
+The positional coordinates of each functional genomic element, obtained from ENCODE, were then used to define the feature space of the models.
+
+## Figure 2: Ensemble Framework/Model Building Pipeline
+
+A diagram of the model building pipeline given a combination of inputs from the ensemble framework.
+The data was split into a 7:3 training set to testing set ratio, an $l_{1}$ norm regularization (LASSO) was implemented, and a random forest classification algorithm was performed.
+Each model was then validated on the same testing set.
+
+## Figure 3: Predictor Types
+
+Diagram of the 3 predictor types considered when assessing the relationship between TAD boundaries and functional genomic elements.
+Each predictor type was used as the feature space in downstream analyses for predicting which functional genomic elements were associated with the formation of TAD boundaries.
+Featured above are bin-specific examples of the construction of each predictor type.
+(Left) The overlap count (OC) predictors were calculated by considering the total number of elemental regions that overlapped with each genomic bin.
+(Middle) The overlap percent (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin and dividing by the total bin width (either 5, 25, 50, or 100 kilobases given resolution of boundary data).
+(Right) The distance predictors were calculated by measuring the distance (in base pairs) from the center of each genomic bin to the center of the nearest elemental region of interest.
+The two green segments directly below the rightmost enlarged figure represent the center of the overlapping regions defining the respective functional genomic element.
+
+## Figure 4: Class Imbalance
+
+Barplots illustrating the class imbalance problem featured across each of the four different resolutions that were analyzed.
+Minority classes represent the number of genomic bins that contain a TAD boundary, while the majority classes represent the number of genomic bins that do not contain a TAD boundary.
+
+## Figure 5: Performances of Models with No Class-Balancing
+
+Barplots measuring the predictive performance of models built on imbalanced datasets.
+The performance metrics considered were accuracy, AUC, F1-Score, and MCC.
+Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).
+
+## Figure 6: Performances of Models with Randomly Under-sampled Data.
+
+Barplots measuring the predictive performance of models built on datasets using 50 iterations of random under-sampling.
+The performance metrics considered were accuracy, AUC, F1-Score, and MCC.
+Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).

### 2019-01-20 Manuscript/manuscript.Rmd
manuscript/todo edits

--- 2019-01-20 Manuscript/manuscript.Rmd
@@
 
-Existing methods for predicting associations between genomic elements tend to ignore key characteristics of genomic data.
+Existing methods for predicting associations between genomic elements tend to ignore key characteristics of the genomic data.
 Specifically, the number of TAD boundaries is much less than the number of other genomic regions, leading to heavily imbalanced classes.
@@
 
-The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect genomic regulation [@lieberman2009comprehensive].
-Analyses have shown that the genome is folded into distinct compartments termed topologically associating domains (TADs) [@dixon2012topological].
+The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect several epigenetic functions [@lieberman2009comprehensive].
+Analyses have shown that the genome is tightly compacted into distinct compartments.
+There exist regions within these compartments that have been shown to be highly conserved and self-interacting, and termed topologically associating domains (TADs) [@dixon2012topological].
 Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD [@symmons2014functional].
-Approximately 60-80% of TADs remain stable across cell types [@Schmitt:2016aa], suggestingthat the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
-Furthermore, changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [???
-REF].
+This suggests that the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
+Furthermore, changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer.
 Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.
@@
 Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long-range chromatin contacts [@zuin2014cohesin].
-Other regulatory elements like particular histone modifications such as H3K36 and H3K27 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [???
-Better to mention those that came up in your analysis, otherwise, it is unnecessary information] [@rao20143d].
+Other regulatory elements like particular histone modifications such as H3K36 and H3K27 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [@rao20143d].
 These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
-The distinct patterns of different proteins and functional elements point toward the opportunity of using computational approaches in identifying which epigenomic features are most predictive of the TAD boundaries, allowing us to better understand what leads to their formation.
+The distinct patterns of different proteins and functional elements point toward the opportunity of using computational approaches in identifying which epigenomic features are most predictive of the development of TAD boundaries, allowing us to better understand what leads to their formation.
 
-Current methods rely on the use of classification algorithms to identify which functional genomic elements are best able to discriminate between regions that include TAD boundaries and those that do not [@mourad2016computational; @hong2017computational; @huang2015predicting] [???
-Do not understand this sentence].
+Current methods rely on the use of classification algorithms to identify which functional genomic elements are best able to discriminate between regions that include TAD boundaries and those that do not [@mourad2016computational; @hong2017computational; @huang2015predicting].
 Most methods differ on the techniques used to identify genomic regions that include TAD boundaries, as well as the models and tools used to evaluate the predictive capability of said models.
-Moreover, many methods ignore key characteristics of domain data, such as heavily imbalanced number ot boundaries vs.
-other regions.
+Moreover, many methods ignore key characteristics of domain data that can impair and bias results.
+
+Most notably is the introduction of heavily imbalanced classes.
+Due to the sparcity of TADs throughout the genome, most defined regions will not contain a TAD boundary.
 In a classification setting, when one is attempting to discriminate between regions with and without TAD boundaries, this will contribute to small imbalance ratios (defined as the ratio of minority to majority classes) [@Orriols-Puig2008].
 It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class;@chen2013influence;@jeni2013facing].
-Similarly, careful consideration must also be taken when deciding which performance metric(s) to use for evaluation of predictive models, especially in the case of imbalanced data.
+Similarly, careful consideration must also be taken when deciding which performance metric(s) to present when evaluating predictive models, especially in the case of imbalanced data.
 
@@
 It has been shown that the use of AUPRC with imbalanced datasets yields more accurate and intuitive interpretation of model performance when compared to AUROC [@saito2015precision].
-Likewise, metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
+Likewise, metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data.
+In each case, the weight of the measure is carried primarily by the correct classification of the majority class.
 Better measures to consider are the F1-Score and Matthew's Correlation Coefficient (MCC) [@jeni2013facing].
 The F1-Score can be interpreted as a weighted average of the precision and recall values, while MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications.
-Both metrics use all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
+In either case, all 4 quadrants of the confusion matrix are used, making for more balanced measures in the case of imbalanced data [@chicco2017ten].
 
 In addition to employing suitable metrics for evaluating models validated on imbalanced data, there also exist several algorithmic or data level solutions.
-Algorithmic level solutions involve modifyng existing classifiers in order to curtail the bias induced by imbalanced classes [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical].
-Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset [???
-REFS].
+Algorithmic level solutions involve modifyng existing classifiers in order to curtail the bias induced by imbalanced classes.
+Many such solutions have been developed in a variety of fields related to machine learning [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical].
+Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset.
 It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
@@
 Furthermore, there are other aspects of TAD boundary modelling that current methods have failed to consider.
-Most notably is the concept of genomic distance.
-As a feature engineering step, the use of distances (in base pairs) from TAD boundaries to regions of various genomic features has largely been ignored.
+Most notably is the concept of distance.
+As a feature engineering step, the use of distances (in base pairs) from genomic bins to regions of functional genomic elements has largely been ignored.
 However, these distance characteristics have the potential to offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
-
 Additionally, model performance is heavily contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
-It is often unclear from previous studies what resolution contact matrices were used when retrieving TAD boundaries, and how other resolutions would affect their results.
+It is often unclear from authors of previous studies what resolution contact matrices were used when retrieving TAD boundaries, and how other resolutions would affect their results.
 A larger resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
@@
 
-In this study we have developed an ensemble framework for predicting TAD boundaries that addresses class imbalance problem.
-We evaluated Hi-C data for the GM12878 cell line obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolution.
-For each resolution, we examined the inclusion of three different predictor types, including distance as the measure of association between genomic elements.
-We then tested four re-sampling techniques aimed at creating balanced classes.
-Random forest classification was performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the TAD boundaries.
-Model performance was evaluated using accuracy, area under the precision-recall curve (AUPRC), F1 score, and Matthew's Correlation Coefficient (MCC).
+In this study we have developed an ensemble framework that aims to address and compare a variety of data irregularities and characteristics that are associated with the prediction of TAD boundaries including class imbalance, feature engineering, and contact map resolution.
+We evaluated domain data obtained from four different resolution contact matrices for the GM12878 cell line including 10 kb, 25 kb, 50 kb, and 100 kb.
+For each resolution, we examined the inclusion of 3 different predictor types as the feature space for downstream modeling.
+We then performed a series of 4 different re-sampling techniques aimed at creating balanced classes.
+Random forest classification algorithms were performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the formation of TAD boundaries.
+Model performance was evaluated based on a total of four metrics which included test accuracy, area under the precision-recall curve (AUPRC), F1 score, and Matthew's Correlation Coefficient (MCC).
 This process was then repeated for X additional cell lines including K562, ......
@@
 Replicate Hi-C data for the GM12878 cell line were downloaded from GEO GSE63525 (Experiments HIC001 to HIC018; produced using the MbolI restriction enzyme) [@rao20143d].
-The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
-The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained.
-Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table S1).
+The chromosomal coordinates of topologically associating domains throughout the genome were obtained using the Arrowhead algorithm from the Juicer toolbox provided by the Aiden Laboratory (https://github.com/aidenlab/juicer) [@durand2016juicebox].
+Domain data was extracted at 4 different kilobase (kb) resolutions including 10 kb, 25 kb, 50 kb, and 100 kb.
+Identified TAD boundaries were represented by their location on the linear genome (GRCh37/hg19 human genome assembly), including start and end coordinates for chromosomes 1 through 22.
+The start and end coordinates of all hierarchical TADs were concatenated, sorted, and unique TAD boundary points were obtained.
 
@@
 
-To accommodate for the uncertainty in the location of TAD boundary points, they were flanked on both sides by regions of the size of the resolution of the data (Figure 1).
-For example, returning to the 10 kb resolution example, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
+To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution (Figure 1).
+For example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
+To accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
+Returning to the 10 kb resolution example, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
+A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
+Otherwise, the bin was labeled as not containing a boundary (Y=0).
 
-The response vector $Y$ was formed by genomic regions (bins) defined by the resolution of the data.
-Genomic regions flanking TAD boundaries were labeled as $Y=1$; otherwise, the regions were labeled as not containing a boundary ($Y=0$).
+## GENOMIC ANNOTATION DATA
 
-Using the sets of genomic features, we created three types of predictors (Figure 2):
-
-1. **Overlap Counts (OC)**: For each genomic bin, the total number of overlaps with genomic features was calculated. In the case of no overlaps the value is set as 0.
-
-2.
-**Overlap Percent (OP)**: For each genomic bin, the percent overlap was defined as the total width of features overlapping a bin divided by the bin width.
-Values for bins with no overlaps were set to be 0.
-
-3.
-**Distance**: For each genomic bin, the log [???
-didn't you test raw distance first?] [???
-log10?] of the distance (in bases) from the center of the bin to the center of the nearest genomic feature region was calculated.
-The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1)
-
-To assess the predictive performance for each predictor type, we performed individual random forest classification algorithms utilizing each set predictor types as the feature space, in addition to a model with all combined types.
-Precision-Recall (PR) Curves, and subsequent area under the PR curves (AUPRC), were used to evaluate which predictor type contributed to the best model performance.
-Recursive feature elimination (RFE) was then used to determine the optimal number of features for models within each set of predictor types.
-Here, random forest models were used to assign weights to a set features of a given size.
-The optimal number of features was determined by the AUPRC of the corresponding model.
+Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
+The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments.
+Each genomic annotation was represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological significance.
 
@@
 That is, for the task of prediction, the test set remained constant for all ensemble systems in order to account for a fair and unbiased comparison.
+
+### FEATURE ENGINEERING AND REDUCTION USING GENOMIC ANNOTATIONS
+
+Using the sets of genomic annotations, we created three types of predictors that were used as features to analyze their relationships with TAD boundaries (Figure 3):
+
+1.
+**Overlap Counts (OC)**: For each genomic bin, the total number of instances where a bin overlapped with genomic annotation regions (features) was calculated.
+In the case of no overlaps the value is set as 0.
+
+2.
+**Overlap Percent (OP)**: For each genomic bin, the percent overlap between the feature width and the total width of the bin was calculated.
+We defined the feature width as the number of bases that overlapped with the genomic bin.
+The percent was then calculated by dividing the feature width by the bin width.
+If multiple overlaps existed, the feature width was defined as the sum of the total number of bases that overlapped with a particular bin.
+Note that the bin width remained constant for a given resolution (either 10 kb, 25 kb, 50 kb, or 100 kb).
+Values for bins with no overlaps were set to be 0.
+
+3.
+**Log Distance**: For each genomic bin, the log of the distance (in bases) from the center of the bin to the center of the nearest region of a respective genomic annotation region was calculated.
+The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1)
+
+To assess the predictive performance for each predictor type, we performed individual random forest classification algorithms utilizing each set predictor types as the feature space, in addition to a model with all combined types.
+Precision-Recall (PR) Curves, and subsequent area under the PR curves (AUPRC), were used to evaluate which predictor type contributed to the best model performance.
+Recursive feature elimination (RFE) was then used to determine the optimal number of features for models within each set of predictor types.
+Here, random forest models were used to assign weights to a set features of a given size.
+The optimal number of features was determined by the AUPRC of the corresponding model.
 
@@
 
-The efficacy of different ensemble systems was compared using various performance metrics including accuracy, AUC, F1-score, and MCC. These metrics are defined as follows:
+The efficacy of different ensemble systems was compared using various performance metrics including accuracy, F1-score, and MCC. These metrics are defined as follows:
 
@@
 Thererfore they are unable to give an overview of the potential range of performance as thresholds vary.
-A full list of the single threshold measures used (including additional metrics not reported), along with their respective formulas, are provided in Supplementary Table 6.
-In order to evaluate the trade-off between precision and recall, we also considered a threshold free measure in form of the area under the precision recall curve (AUPRC).
+A full list of the single threshold measures used (including additional metrics not reported), along with their respective formulas, are provided in Supplementary Table 2.
+In order to evaluate the trade-off between precision and recall, we also considered a threshold-free measure in form of the area under the precision recall curve (AUPRC).
 
@@
 
-We evaluated and compared Hi-C datasets at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}, used three predictor types P = {OC, OP, Distance}, two variable reduction techniques V = {LASSO, Elastic-Net}, and five class balancing techniques C = {None, RUS, ROS, SMOTE, ROSE}.
+We evaluated and compared multilpe random forest classification algorithms built of domain data extracted from Hi-C datasets at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}.
+For each classifier, we compared 3 predictor types P = {OC, OP, Distance} and 5 class balancing techniques C = {None, RUS, ROS, SMOTE, ROSE}.
 A system produced from the ensemble framework was defined as: E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.
 Letting |X| denote the cardinality of each set, we evaluated |R| x |P| x |V| x |C| different ensemble systems, totaling 120 (=4 $\times$ 3 $\times$ 2 $\times$ 5) separate models.
-For simplicity, we present the most significant results, with the complete results available as Supplementary Tables.
+For simplicity, we present the most significant results, with the complete results available as Supplementary Tables and Figures.
 
-### CLASS DISTRIBUTIONS ACROSS RESOLUTIONS
-
-The coordinates of the corresponding 10 kb resolution contact maps resulted in a total of X genomic bins [???
-To be modified for the whole genome].
-There were only Y bins that overlapped with a flanked TAD boundary representing the minority class, for an imbalance ratio of (X-Y):Y [???
-To be modified for the whole genome].
-After applying each resampling technique to the training set, we obtained perfectly balanced classes for all except the ROSE technique (Figure 4).
-
-An increase in resolution resulted in an overall decrease in the number of genomic bins, as well as a slight decrease in the imbalance ratio (Supplementary Figure 2).
-After performing the resampling techniques, the resulting imbalance ratios remained similar across the other 3 data resolutions (Supplementary Figure 2).
-
-### DISTANCE-TYPE PREDICTORS PERFORM BEST
+## IMBALANCE RATIOS ACROSS RESOLUTIONS & CELL LINES
 
@@
 
+# Supplementary Tables and Figures
+
+# Supplementary Legends
+
+## Table 1: List of Genomic Annoations.
+
+The full list of genomic annotations used in downstream analyses.
+These annotations were the functional genomic elements used to predict the formation of TAD boundaries.
+They were obtained via ChIP-Seq experiments, mapped to human genome assembly hg19, and made available by the ENCODE Consortium.
+Each element is denoted by its genomic class, and which cell type it is applied to.
+The elements that are invariant to a specific cell type are denoted by "Invariant".
+Additionally, a breif description and specific paths for downloads are also provided.
+
+## Table 2: Class Distributions for Other Resolutions
+
+Summary of the class distributions for each of the other resolution domain data sets (25 kb, 50 kb, and 100 kb), across each re-sampling technique.
+As with the 5 kb data, all re-sampling techniques yielded completely balanced classes.
+That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.
+
+## Table 3: Model Performances When Not Accounting for Class Imbalance
+
+Results of various metrics used to assess predictive performances for models that were built on fully imbalanced datasets.
+
+## Figure 1: Performances of Models with Both SMOTE-Balanced and Randomly Over-sampled Data.
+
+Barplots measuring the predictive performance of models built on datasets using 50 iterations of both the SMOTE algorithm (A) and random over-sampling (B).
+The performance metrics considered were accuracy, AUC, F1-Score, and MCC.
+Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).
+
+## Table 4:
+
+Results of various metrics used to assess predictive performances for models that were built on random under-sampled datasets.
+
+## Table 5:
+
+Results of various metrics used to assess predictive performances for models that were built on both SMOTE-balanced and random over-sampled datasets.
+
 # References

### 2019-01-20 Manuscript/manuscript.Rmd

--- 2019-01-20 Manuscript/manuscript.Rmd
@@
 
+To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution (Figure 1).
+For example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
+To accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
+Returning to the 10 kb resolution example, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
+A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
+Otherwise, the bin was labeled as not containing a boundary (Y=0).
+
 To accommodate for the uncertainty in the location of TAD boundary points, they were flanked on both sides by regions of the size of the resolution of the data (Figure 1).
@@
 $$MCC = \frac{TP \times TN - FP \times FN}{\sqrt{ (TP + FP)(TP+FN)(TN+FP)(TN+FN) }}$$
+
+Here, TP refers to the number of bins correctly identified as containing a TAD boundary (true positives), FP refers to the number of bins incorrectly identified as containing a TAD boundary (false positives), TN refers to the number of bins correctly identified as not containing a TAD boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a TAD boundary.
+Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
+The evaluation metrics listed above are all considered single threshold measures.
+That is, they are defined for individual thresholds that separated class prediction.
+Thererfore they are unable to give an overview of the potential range of performance as thresholds vary.
+A full list of the single threshold measures used (including additional metrics not reported), along with their respective formulas, are provided in Supplementary Table 2.
+In order to evaluate the trade-off between precision and recall, we also considered a threshold-free measure in form of the area under the precision recall curve (AUPRC).
 
@@
 
+We evaluated and compared multilpe random forest classification algorithms built of domain data extracted from Hi-C datasets at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}.
+For each classifier, we compared 3 predictor types P = {OC, OP, Distance} and 5 class balancing techniques C = {None, RUS, ROS, SMOTE, ROSE}.
+A system produced from the ensemble framework was defined as: E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.
+Letting |X| denote the cardinality of each set, we evaluated |R| x |P| x |V| x |C| different ensemble systems, totaling 120 (=4 $\times$ 3 $\times$ 2 $\times$ 5) separate models.
+For simplicity, we present the most significant results, with the complete results available as Supplementary Tables and Figures.
+
 We created an ensemble framework to systematically evaluate the performance of of TAD boundary prediction under different conditions and resampling approaches (Figure 3).
@@
 
-### CLASS DISTRIBUTIONS ACROSS RESOLUTIONS
-
-The coordinates of the corresponding 10 kb resolution contact maps resulted in a total of X genomic bins [???
-To be modified for the whole genome].
-There were only Y bins that overlapped with a flanked TAD boundary representing the minority class, for an imbalance ratio of (X-Y):Y [???
-To be modified for the whole genome].
-After applying each resampling technique to the training set, we obtained perfectly balanced classes for all except the ROSE technique (Figure 4).
-
-An increase in resolution resulted in an overall decrease in the number of genomic bins, as well as a slight decrease in the imbalance ratio (Supplementary Figure 2).
-After performing the resampling techniques, the resulting imbalance ratios remained similar across the other 3 data resolutions (Supplementary Figure 2).
-
-### DISTANCE-TYPE PREDICTORS PERFORM BEST
+## IMBALANCE RATIOS ACROSS RESOLUTIONS & CELL LINES
 

### 2019-01-20 Manuscript/Supplementary/supplementary_legends.Rmd
supplementary  legends

@@
 
-## Table 1: List of Genomic Annoations.
-
-The full list of genomic annotations used in downstream analyses.
-These annotations were the functional genomic elements used to predict the formation of TAD boundaries.
-They were obtained via ChIP-Seq experiments, mapped to human genome assembly hg19, and made available by the ENCODE Consortium.
-Each element is denoted by its genomic class, and which cell type it is applied to.
-The elements that are invariant to a specific cell type are denoted by "Invariant".
-Additionally, a breif description and specific paths for downloads are also provided.
+**Supplementary Table S1.
+List of Genomic Annotations.** The GRCh37/hg19 human genome assembly was used.
+"Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Cell Type" - cell type, "Source" - download URL.
+[???
+Did you use only features common to both cell lines?]
 

### 2019-01-20 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-We evaluated and compared multilpe random forest classification algorithms built of domain data extracted from Hi-C datasets at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}.
-For each classifier, we compared 3 predictor types P = {OC, OP, Distance} and 5 class balancing techniques C = {None, RUS, ROS, SMOTE, ROSE}.
-A system produced from the ensemble framework was defined as: E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C.
-Letting |X| denote the cardinality of each set, we evaluated |R| x |P| x |V| x |C| different ensemble systems, totaling 120 (=4 $\times$ 3 $\times$ 2 $\times$ 5) separate models.
+We evaluated and compared multilpe random forest classification algorithms built on domain data extracted from Hi-C datasets for X cell lines C = {GM12878, K562, ...}, at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}.
+For each classifier, we compared 3 predictor types P = {OC, OP, Distance} and 5 class balancing techniques B = {None, RUS, ROS, SMOTE, ROSE}.
+A system produced from the ensemble framework was defined as: E = {c, r, p, b}, where c $\in$ C, R $\in$ R, p $\in$ P, and b $\in$ B.
+Letting |X| denote the cardinality of each set, we evaluated |C| x |R| x |P| x |B| different ensemble systems, totaling X (=x $\times$ 4 $\times$ 3 $\times$ 5) separate models.
 For simplicity, we present the most significant results, with the complete results available as Supplementary Tables and Figures.
-
-We created an ensemble framework to systematically evaluate the performance of of TAD boundary prediction under different conditions and resampling approaches (Figure 3).
-Briefly, we used Hi-C datasets at four different resolutions $R = \{ 10 kb, 25 kb, 50 kb, 100 kb \}$, used three predictor types $P = \{ OC, OP, Distance \}$, two variable reduction techniques $V = \{ LASSO, Elastic-Net \}$ [???
-Is that so?], and five class balancing techniques $C = \{ None, RUS, ROS, SMOTE, ROSE \}$.
-A system produced from the ensemble framework was defined as: $E = \{ r, p, v, c \}$, where $r \in R$, $p \in P$, $v \in V$, and $c \in C$.
-Letting $|X|$ denote the cardinality of each set, we evaluated $|R| \times |P| \times |V| \times |C|$ different ensemble systems, totaling $120 (=4 \times 3 \times 2 \times 5)$ [???
-Check if you use Lasso only] separate models.
-For simplicity, we present the most significant results, with the complete results available as Supplementary Tables.
 

### 2019-01-21 Manuscript/manuscript.Rmd
manuscript edits

@@
 Approximately 60-80% of TADs remain stable across cell types [@Schmitt:2016aa], suggestingthat the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
-Furthermore, changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [???
-REF].
+Furthermore, studies have shown that changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @flavahan2016insulator] [???
+REF; !!!added references].
 Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.

### 2019-01-21 Manuscript/manuscript.Rmd
somehow a lot of my edits (mostly methods section) were overwritten, I have reincluded them

@@
 
-The mechanisms underlying the formation of TADs are a complex and active area of research.
-Recently, it has been discovered that insulator sequences have a primary role in orchestrating the topological arrangements of higher-order chromatin architecture [@phillips2013chromatin].
-Insulators are multi-faceted regulatory sequences that moderate a variety of genomic processes including activation, repression, and enhancer blocking.
-Specifically, the insulator binding protein CTCF has been found to be enriched at the boundary sequences of topologically associating domains in human cells and may therefore act as a mediator of long-range chromatin contacts [@zuin2014cohesin].
-Other regulatory elements like particular histone modifications such as H3K36 and H3K27 trimethylation, and transcription factors such as ZNF274 and YY1 have been more frequently observed at TAD boundaries than in other regions [???
-Better to mention those that came up in your analysis, otherwise, it is unnecessary information] [@rao20143d].
-These have been found to be associated with more open chromatin which alter the accessibility of genes for transcription.
-The distinct patterns of different proteins and functional elements point toward the opportunity of using computational approaches in identifying which epigenomic features are most predictive of the TAD boundaries, allowing us to better understand what leads to their formation.
-
-Current methods rely on the use of classification algorithms to identify which functional genomic elements are best able to discriminate between regions that include TAD boundaries and those that do not [@mourad2016computational; @hong2017computational; @huang2015predicting] [???
-Do not understand this sentence].
+Identifying the mechanisms underlying the formation of TADs are a complex and active area of research.
+The distinct patterns of different proteins and functional elements point toward the opportunity of using computational approaches in identifying which epigenomic features are most predictive of the TAD boundaries.
+[???
+Better to mention those that came up in your analysis, otherwise, it is unnecessary information; !!!editted paragraph] Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries [@mourad2016computational; @hong2017computational; @huang2015predicting] [???
+Do not understand this sentence; !!!editted sentence].
 Most methods differ on the techniques used to identify genomic regions that include TAD boundaries, as well as the models and tools used to evaluate the predictive capability of said models.
@@
 Algorithmic level solutions involve modifyng existing classifiers in order to curtail the bias induced by imbalanced classes [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical].
-Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset [???
-REFS].
+Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data] [???
+REFS; !!!added references].
 It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
@@
 
-Replicate Hi-C data for the GM12878 cell line were downloaded from GEO GSE63525 (Experiments HIC001 to HIC018; produced using the MbolI restriction enzyme) [@rao20143d].
+Replicate Hi-C data for the GM12878, K562, ...
+cell lines were downloaded from GEO GSE63525 (Experiments HIC001 to HIC018, HIC069 to HIC 074, ...
+respectively; produced using the MbolI restriction enzyme) [@rao20143d].
 The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
 The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained.
-Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table S1).
+Genomic annotation data consisting of various chromatin segmentation states, histone modifications, and transcription factor binding sites (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table S1).
 
@@
 
-To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution (Figure 1).
+To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution for the corresponding contact matrix (Figure 1).
 For example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
@@
 
-To accommodate for the uncertainty in the location of TAD boundary points, they were flanked on both sides by regions of the size of the resolution of the data (Figure 1).
-For example, returning to the 10 kb resolution example, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
+## GENOMIC ANNOTATION DATA
 
-The response vector $Y$ was formed by genomic regions (bins) defined by the resolution of the data.
-Genomic regions flanking TAD boundaries were labeled as $Y=1$; otherwise, the regions were labeled as not containing a boundary ($Y=0$).
+Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
+The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments.
+Each genomic annotation was represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological significance.
 
-Using the sets of genomic features, we created three types of predictors (Figure 2):
+## ENSEMBLE FRAMEWORK
 
-1. **Overlap Counts (OC)**: For each genomic bin, the total number of overlaps with genomic features was calculated. In the case of no overlaps the value is set as 0.
-
-2.
-**Overlap Percent (OP)**: For each genomic bin, the percent overlap was defined as the total width of features overlapping a bin divided by the bin width.
-Values for bins with no overlaps were set to be 0.
-
-3.
-**Distance**: For each genomic bin, the log [???
-didn't you test raw distance first?] [???
-log10?] of the distance (in bases) from the center of the bin to the center of the nearest genomic feature region was calculated.
-The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1).
+An ensemble of models was established for the purposes of systematically comparing the performances of different parameters in the framework.
+Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type for the feature space (Figure 2).
 
@@
 
+### FEATURE ENGINEERING AND REDUCTION USING GENOMIC ANNOTATIONS
+
+Using the sets of genomic annotations, we created three types of predictors that were used as features for subsequent models to analyze their respective spatial relationship with TAD boundaries (Figure 3):
+
+1.
+**Overlap Counts (OC)**: For each genomic bin, the total number of instances where a bin overlapped with genomic annotation regions (features) was calculated.
+In the case of no overlaps the value is set as 0.
+
+2.
+**Overlap Percent (OP)**: For each genomic bin, the percent overlap between the feature width and the total width of the bin was calculated.
+We defined the feature width as the number of bases that overlapped with the genomic bin.
+The percent was then calculated by dividing the feature width by the bin width.
+If multiple overlaps existed, the feature width was defined as the sum of the total number of bases that overlapped with a particular bin.
+Note that the bin width remained constant for a given resolution (either 10 kb, 25 kb, 50 kb, or 100 kb).
+Values for bins with no overlaps were set to be 0.
+
+3.
+**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance (in bases) from the center of the bin to the center of the nearest region of a respective genomic annotation region was calculated.
+The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1)
+
+To assess the predictive performance for each predictor type, we performed individual random forest classification algorithms utilizing each set predictor types as the feature space, in addition to a model with all combined types.
+Precision-Recall (PR) Curves, and subsequent area under the PR curves (AUPRC), were used to evaluate which predictor type contributed to the best model performance.
+Recursive feature elimination (RFE) was then used to determine the optimal number of features for models within each set of predictor types.
+In doing so, random forest models were used to assign weights to a set features of a given size.
+The optimal number of features was determined by the AUPRC of the corresponding model in order to reduce the feature space accordingly.
+
 ### RE-SAMPLING TECHNIQUES
 
-In order to evaluate the problem of imbalanced classes, we then evaluated three re-sampling techniques.
+In order to evaluate the problem of imbalanced classes, we then evaluated 4 re-sampling techniques (in addition to no re-sampling).
 
@@
 We chose the parameters that would create perfectly balanced classes.
-The `DMwR` v.3.4.2 R package was used to perform SMOTE.
+The `DMwR` package in R was used to perform SMOTE (version 0.4.1).
 
@@
 Another important distinction between ROSE and SMOTE is that, for ROSE, the creation of perfectly balanced classes is unlikely due to the randomness in sampling between the two classes.
-The `ROSE` v.3.4.2 [???
+The `ROSE` package [???
 Is it correct?
-Same version as DMwR?] R packagewas used to perform ROSE.
+Same version as DMwR?; !!!fixed] in R used to perform ROSE (version 0.0.3).
 
@@
 
-A classification algorithm in the form of a random forest was performed and validated using the same test [???
-Training?] set for all models in the ensemble.
+A classification algorithm in the form of a random forest was performed on the various resampled and reduced training sets and validated using the same test [???
+Training?; !!!clarified; different training sets due to the different resampling schemes, but validated using the same holdout set] set for all models in the ensemble.
 To reduce bias due to random dataset generation, 10-fold cross validation was used.
@@
 
-Here, TP refers to the number of bins correctly identified as containing a TAD boundary (true positives), FP refers to the number of bins incorrectly identified as containing a TAD boundary (false positives), TN refers to the number of bins correctly identified as not containing a TAD boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a TAD boundary.
-Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-The evaluation metrics listed above are all considered to be single threshold measures.
-That is, they are defined for individual thresholds that separated class prediction.
-Thererfore, they are unable to give an overview of the potential range of performance as thresholds vary.
-In order to evaluate the trade-off between precision and recall, we also considered a threshold-free measure in form of the area under the precision recall curve (AUPRC).
-
 For the task of identifying the functional genomic elements that were most predictive of the formation of TAD boundaries, we evaluated the variable importances associated with each predictor of the random forest model.
-For each tree, the prediction accuracy on the out-of-bag portion of the data is recorded.
+For each tree, the prediction accuracy on the out-of-bag portion of the data was recorded.
 Then the same was done after permuting each predictor variable.
-The difference between the two accuracies were then averaged over all trees, and normalized by the standard error [@kuhn2012caret].
-Recursive feature elimination (RFE) was then used to determine the optimal number of features for models within each set of predictor types.
-Here, random forest models were used to assign weights to a set features of a given size.
-The optimal number of features was determined by the AUPRC of the corresponding model.
-[???
-Rewrite this paragraph as I put some disjoint sentences]
+The difference between the two accuracies was then averaged over all trees, and normalized by the standard error [@kuhn2012caret].
 

### 2019-01-22 Manuscript/manuscript.Rmd
manuscript edits

@@
 The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained.
-Genomic annotation data consisting of various chromatin segmentation states, histone modifications, and transcription factor binding sites (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table S1).
+
+## GENOMIC ANNOTATION DATA
+
+Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
+The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments.
+Each genomic annotation was represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological significance.
 
@@
 
-## GENOMIC ANNOTATION DATA
-
-Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
-The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments.
-Each genomic annotation was represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological significance.
-
 ## ENSEMBLE FRAMEWORK
 
-An ensemble of models was established for the purposes of systematically comparing the performances of different parameters in the framework.
-Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type for the feature space (Figure 2).
+An ensemble of models was established for the purposes of systematically comparing the performances of different parameters in the framework (Figure 2).
+Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type for the feature space.
 
@@
 
+## DISTANCE TYPE PREDICTORS OUTPERFORM OTHER PREDICTOR-TYPES
+
+We first evaluated which predictor types were best able to discriminate between genomic bins that either flanked or did not flank TAD boundaries.
+To do so we performed a series of random forest classification algorithms on the full features space (all combined predictor types), as well as on type-specific feature spaces (overlap counts, overlap predictors, and log2 distances).
+It was found that models with distance type predictors had higher AUPRC values compared to other predictor types (Figure 4).
+This result was observed across both data resolution and cell line, with the largest AUPRC obtained from the 10 kb resolutions for all [gm12878, k562, ???update as more cell lines included] cell lines (0.431 and 0.456 respectively).
+There was a gradual decline in AUPRC values as resolution increased with models built on 100 kb resolution domain data having the lowest AUPRC curves, regardless of predictor type (Supplementary Table 3).
+
+Recursive feature elimination was used to establish the optimal number of distance-type features to include in downstream analyses.
+It was determined that performances according to AUPRC values were asymptotically similiar for random forest models with sets of predictors greater than 32 (Figure 5).
+Therefore, we reduced the feature space for subsequent models to the top 32 predictors, respective to resolution and cell line.
+The sets of top predictors chosen varied across resolution and cell line due to differences in the parameters provided in the TAD calling algorithm.
+
 ## IMBALANCE RATIOS ACROSS RESOLUTIONS & CELL LINES
+
+The low baseline AUPRC values, denoted by the dashed lines in the above PR curves, indicate the severity of
+
+After classifying each genomic bin as either being flanked by a TAD boundary or not, it was found that the subsequent imbalance ratios across resolutions and cell lines were extremely low.
+Ideally a manageable dataset will have an imbalance ratio hovering near 1.
+At their heights, the imbalance ratios were 0.179, 0.152, ...
+for cell lines GM12878, K562, ...
+respectively (Figure 4).
 

### 2019-01-22 Manuscript/manuscript.Rmd
cleanup

@@
 Approximately 60-80% of TADs remain stable across cell types [@Schmitt:2016aa], suggestingthat the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
-Furthermore, studies have shown that changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @flavahan2016insulator] [???
-REF; !!!added references].
+Furthermore, studies have shown that changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @flavahan2016insulator].
 Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.
@@
 Identifying the mechanisms underlying the formation of TADs are a complex and active area of research.
-The distinct patterns of different proteins and functional elements point toward the opportunity of using computational approaches in identifying which epigenomic features are most predictive of the TAD boundaries.
-[???
-Better to mention those that came up in your analysis, otherwise, it is unnecessary information; !!!editted paragraph] Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries [@mourad2016computational; @hong2017computational; @huang2015predicting] [???
-Do not understand this sentence; !!!editted sentence].
-Most methods differ on the techniques used to identify genomic regions that include TAD boundaries, as well as the models and tools used to evaluate the predictive capability of said models.
-Moreover, many methods ignore key characteristics of domain data, such as heavily imbalanced number ot boundaries vs.
+The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes [???
+REFs] prompt the use of computational approaches to identify which epigenomic features are most predictive of the TAD boundaries.
+Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries [@mourad2016computational; @hong2017computational; @huang2015predicting].
+Although several useful insights have been made, such as the convergent binding of CTCF [???
+Elaborate with refs.], many methods ignore key characteristics of domain data, such as heavily imbalanced number of boundaries vs.
 other regions.
-In a classification setting, when one is attempting to discriminate between regions with and without TAD boundaries, this will contribute to small imbalance ratios (defined as the ratio of minority to majority classes) [@Orriols-Puig2008].
+In a classification setting [???
+are we talking about classification or prediction?], when one is attempting to discriminate between regions with and without TAD boundaries, this will contribute to small imbalance ratios (defined as the ratio of minority to majority classes) [@Orriols-Puig2008].
 It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class;@chen2013influence;@jeni2013facing].
@@
 Algorithmic level solutions involve modifyng existing classifiers in order to curtail the bias induced by imbalanced classes [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical].
-Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data] [???
-REFS; !!!added references].
+Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
 It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
@@
 respectively; produced using the MbolI restriction enzyme) [@rao20143d].
-The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
+[???
+Need supplementary ref.] The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
 The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained.
@@
 3.
-**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance (in bases) from the center of the bin to the center of the nearest region of a respective genomic annotation region was calculated.
-The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1)
+**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance (in bases) from the center of the bin to the center of the nearest region of a respective genomic annotation region [???
+Decide whether to use "annotation" or "feature"] was calculated.
+The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1).
 
@@
 
-In order to evaluate the problem of imbalanced classes, we then evaluated 4 re-sampling techniques (in addition to no re-sampling).
+In order to evaluate the problem of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling).
 
@@
 We chose the parameters that would create perfectly balanced classes.
-The `DMwR` package in R was used to perform SMOTE (version 0.4.1).
+The `DMwR` R package was used to perform SMOTE (version 0.4.1).
 
@@
 Another important distinction between ROSE and SMOTE is that, for ROSE, the creation of perfectly balanced classes is unlikely due to the randomness in sampling between the two classes.
-The `ROSE` package [???
-Is it correct?
-Same version as DMwR?; !!!fixed] in R used to perform ROSE (version 0.0.3).
+The `ROSE` R package was used to perform ROSE (version 0.0.3).
 
@@
 
-A classification algorithm in the form of a random forest was performed on the various resampled and reduced training sets and validated using the same test [???
-Training?; !!!clarified; different training sets due to the different resampling schemes, but validated using the same holdout set] set for all models in the ensemble.
+A classification algorithm in the form of a random forest was performed on the various resampled and reduced training sets and validated using the same test set for all models in the ensemble.
 To reduce bias due to random dataset generation, 10-fold cross validation was used.

### 2019-01-22 Manuscript/manuscript.Rmd
manuscript/todo updates

--- 2019-01-22 Manuscript/manuscript.Rmd
@@
 
+## LOW IMBALANCE RATIOS ACROSS RESOLUTIONS & CELL LINES
+
+After classifying each genomic bin as either being flanked by a TAD boundary or not, it was found that the subsequent imbalance ratios across resolutions and cell lines were extremely low.
+Ideally a manageable dataset will have an imbalance ratio hovering near 1.
+At their heights, the imbalance ratios were 0.179, 0.152, ...
+for cell lines GM12878, K562, ...
+respectively (Figure 6).
+The imbalance ratio were lowest for the 10 kb resolution data for both GM12878 and K562.
+
 ## DISTANCE TYPE PREDICTORS OUTPERFORM OTHER PREDICTOR-TYPES
@@
 
-## IMBALANCE RATIOS ACROSS RESOLUTIONS & CELL LINES
-
-The low baseline AUPRC values, denoted by the dashed lines in the above PR curves, indicate the severity of
-
-After classifying each genomic bin as either being flanked by a TAD boundary or not, it was found that the subsequent imbalance ratios across resolutions and cell lines were extremely low.
-Ideally a manageable dataset will have an imbalance ratio hovering near 1.
-At their heights, the imbalance ratios were 0.179, 0.152, ...
-for cell lines GM12878, K562, ...
-respectively (Figure 4).
-
 # Discussion

### 2019-01-23 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-## LOW IMBALANCE RATIOS ACROSS RESOLUTIONS & CELL LINES
-
-After classifying each genomic bin as either being flanked by a TAD boundary or not, it was found that the subsequent imbalance ratios across resolutions and cell lines were extremely low.
-Ideally a manageable dataset will have an imbalance ratio hovering near 1.
-At their heights, the imbalance ratios were 0.179, 0.152, ...
-for cell lines GM12878, K562, ...
-respectively (Figure 6).
-The imbalance ratio were lowest for the 10 kb resolution data for both GM12878 and K562.
-
 ## DISTANCE TYPE PREDICTORS OUTPERFORM OTHER PREDICTOR-TYPES
 
-We first evaluated which predictor types were best able to discriminate between genomic bins that either flanked or did not flank TAD boundaries.
-To do so we performed a series of random forest classification algorithms on the full features space (all combined predictor types), as well as on type-specific feature spaces (overlap counts, overlap predictors, and log2 distances).
-It was found that models with distance type predictors had higher AUPRC values compared to other predictor types (Figure 4).
-This result was observed across both data resolution and cell line, with the largest AUPRC obtained from the 10 kb resolutions for all [gm12878, k562, ???update as more cell lines included] cell lines (0.431 and 0.456 respectively).
+Prior to resampling, we performed a series of random forest classification algorithms on the full features space (all combined predictor types), as well as on type-specific feature spaces (overlap counts, overlap predictors, and log2 distances) to evaluate which predictor types were best able to discriminate between genomic bins that either flanked or did not flank TAD boundaries.
+It was found that, for 10 kb resolution data, models with distance type predictors had higher AUPRC values compared to other predictor types for both GM12878 and K562 cell lines (Figure 4).
+This result was observed across all other data resolutions as well (Supplementary Figure 2).
 There was a gradual decline in AUPRC values as resolution increased with models built on 100 kb resolution domain data having the lowest AUPRC curves, regardless of predictor type (Supplementary Table 3).
@@
 Recursive feature elimination was used to establish the optimal number of distance-type features to include in downstream analyses.
-It was determined that performances according to AUPRC values were asymptotically similiar for random forest models with sets of predictors greater than 32 (Figure 5).
+It was determined that, for 10 kb resolution data, near optimal performance was obtained for models with only 32 predictors for each cell line (Figure 5).
+Results remained consistent across the other data resolutions (Supplementary Figure 4).
 Therefore, we reduced the feature space for subsequent models to the top 32 predictors, respective to resolution and cell line.
 The sets of top predictors chosen varied across resolution and cell line due to differences in the parameters provided in the TAD calling algorithm.
+For the 10 kb resolution data, the most important predictive features that were robust across cell lines were
+
+## DATA RESAMPLING IMPROVES MODEL PREDICTION
+
+The low baseline thresholds represented by the dashed line in the precision-recall curves (Figure 4 and Supplementary Figure2) indicate the wide disparity between majority and minority classes.
+Ideally a manageable dataset will have an imbalance ratio hovering near 1.
+However, in our study we found that there was an average imbalance ratio of 0.154 (SD=0.022) and 0.137 (SD=0.0181) for cell lines GM12878 and K562 respectively (Supplementary Figure 3).
+This highlights the need for suitable resampling techniques.
 

### 2019-01-23 Manuscript/manuscript.Rmd
manuscript updates

@@
 This result was observed across all other data resolutions as well (Supplementary Figure 2).
-There was a gradual decline in AUPRC values as resolution increased with models built on 100 kb resolution domain data having the lowest AUPRC curves, regardless of predictor type (Supplementary Table 3).
+There was a gradual decline in AUPRC values as resolution increased with models built on 100 kb resolution domain data having the lowest AUPRC curves, regardless of predictor type (Supplementary Table 2).
 
@@
 Therefore, we reduced the feature space for subsequent models to the top 32 predictors, respective to resolution and cell line.
-The sets of top predictors chosen varied across resolution and cell line due to differences in the parameters provided in the TAD calling algorithm.
-For the 10 kb resolution data, the most important predictive features that were robust across cell lines were
+The sets of top predictors chosen varied across resolution and cell line due to differences in the parameters provided in the TAD calling algorithm (Supplementary Table 3).
+For the 10 kb resolution data, the most important predictive features that were robust across cell lines were a mixture of transcription factor binding sites, chromatin states, and histone modifications including Smc3, Rad21, CTCF, and H3k9 trimethylation (Figure 6).
+Transcription factor binding sites Smc3, Rad21, and CTCF were also consitently featured as top predictors when comparing cell lines across the the 25 kb and 50 kb resolutions (Supplementary Figure 5).
+Results when cell lines were compared across the 100 kb resolutions were less consitent with current literature.
 

### 2019-01-23 Manuscript/manuscript.Rmd
renamed figures

@@
 It was determined that, for 10 kb resolution data, near optimal performance was obtained for models with only 32 predictors for each cell line (Figure 5).
-Results remained consistent across the other data resolutions (Supplementary Figure 4).
+Results remained consistent across the other data resolutions (Supplementary Figure 3).
 Therefore, we reduced the feature space for subsequent models to the top 32 predictors, respective to resolution and cell line.
@@
 For the 10 kb resolution data, the most important predictive features that were robust across cell lines were a mixture of transcription factor binding sites, chromatin states, and histone modifications including Smc3, Rad21, CTCF, and H3k9 trimethylation (Figure 6).
-Transcription factor binding sites Smc3, Rad21, and CTCF were also consitently featured as top predictors when comparing cell lines across the the 25 kb and 50 kb resolutions (Supplementary Figure 5).
+Transcription factor binding sites Smc3, Rad21, and CTCF were also consitently featured as top predictors when comparing cell lines across the the 25 kb and 50 kb resolutions (Supplementary Figure 4).
 Results when cell lines were compared across the 100 kb resolutions were less consitent with current literature.
@@
 Ideally a manageable dataset will have an imbalance ratio hovering near 1.
-However, in our study we found that there was an average imbalance ratio of 0.154 (SD=0.022) and 0.137 (SD=0.0181) for cell lines GM12878 and K562 respectively (Supplementary Figure 3).
+However, in our study we found that there was an average imbalance ratio of 0.154 (SD=0.022) and 0.137 (SD=0.0181) for cell lines GM12878 and K562 respectively (Supplementary Figure 5).
 This highlights the need for suitable resampling techniques.

### 2019-01-23 Manuscript/manuscript.Rmd
Review

@@
 Recursive feature elimination was used to establish the optimal number of distance-type features to include in downstream analyses.
-It was determined that, for 10 kb resolution data, near optimal performance was obtained for models with only 32 predictors for each cell line (Figure 5).
+It was determined that, for 10 kb resolution data, near optimal performance was obtained for models with only 32 predictors [???
+Distance-based only?] for each cell line (Figure 5).
 Results remained consistent across the other data resolutions (Supplementary Figure 3).
@@
 For the 10 kb resolution data, the most important predictive features that were robust across cell lines were a mixture of transcription factor binding sites, chromatin states, and histone modifications including Smc3, Rad21, CTCF, and H3k9 trimethylation (Figure 6).
-Transcription factor binding sites Smc3, Rad21, and CTCF were also consitently featured as top predictors when comparing cell lines across the the 25 kb and 50 kb resolutions (Supplementary Figure 4).
+[???
+We don't care - these are for unbalanced dataset] Transcription factor binding sites Smc3, Rad21, and CTCF were also consitently featured as top predictors when comparing cell lines across the the 25 kb and 50 kb resolutions (Supplementary Figure 4).
 Results when cell lines were compared across the 100 kb resolutions were less consitent with current literature.

### 2019-01-23 Manuscript/manuscript.Rmd
fixed mathjax

@@
 For each classifier, we compared 3 predictor types P = {OC, OP, Distance} and 5 class balancing techniques B = {None, RUS, ROS, SMOTE, ROSE}.
-A system produced from the ensemble framework was defined as: E = {c, r, p, b}, where c $\in$ C, R $\in$ R, p $\in$ P, and b $\in$ B.
-Letting |X| denote the cardinality of each set, we evaluated |C| x |R| x |P| x |B| different ensemble systems, totaling X (=x $\times$ 4 $\times$ 3 $\times$ 5) separate models.
+A system produced from the ensemble framework was defined as: E = {c, r, p, b}, where $c \in C, \quad R \in R, \quad p \in P,$ and $b \in$ B.
+Letting |X| denote the cardinality of each set, we evaluated $|C| \times |R| \times |P| \times |B|$ different ensemble systems, totaling X (=$x \times 4 \times 3 \times 5$) separate models.
 For simplicity, we present the most significant results, with the complete results available as Supplementary Tables and Figures.
@@
 
-The low baseline thresholds represented by the dashed line in the precision-recall curves (Figure 4 and Supplementary Figure2) indicate the wide disparity between majority and minority classes.
+The low baseline thresholds represented by the dashed line in the precision-recall curves (Figure 4 and Supplementary Figure 2) indicate the wide disparity between majority and minority classes.
 Ideally a manageable dataset will have an imbalance ratio hovering near 1.

### 2019-01-24 Manuscript/Figures/figure_legends.Rmd
updated legends

--- 2019-01-20 Manuscript/Figures/figure_legends.Rmd
@@
 
-**Figure 1: Model Construction.** The linear genome was binned according to the resolution of the Hi-C data.
-TAD boundaries were then flanked by 1 resolution-unit on both sides of the boundary point.
-[???
-The following is unclear.
-Show Y on the figure.
-Are you talking about overlap only?] The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region.
-The positional coordinates of each functional genomic element, obtained from ENCODE, were then used to define the feature space of the models.
+**Figure 1: Model Construction.** Cell line specific Hi-C matices were obtained from [@rao20143d].
+The linear genome was then binned according to the intervals of the square-symmetric contact matrices at given resolutions (10 kb, 25 kb, 50 kb, and 100 kb).
+The coordinates of subsequent topologically associating domains were identified using the Arrowhead TAD-calling algorithm [@durand2016juicebox].
+Each TAD coordinate was then flanked by a unit-specific amount (in basepairs) respective to the resolution of the corresponding contact matrix.
+The response vector Y used for classification was determined by whether a genomic bin overlapped with a flanked boundary region (Y=1) or not (Y=0).
+The spatial relationship between positional coordinates of various functional genomic elements, obtained from ENCODE, and the genomic bins were then used to define the feature space of the models.
 
-**Figure 2.
+**Figure 2: Ensemble Framework/Model Building Pipeline.** A diagram of the model building pipeline given a combination of inputs from the ensemble framework.
+For a particular cell line, contact matrix resolution, and set of features, the data was split into a 7:3 training:testing set ratio.
+For the training set, recursive feature elimination was used to reduce the feature space and minimize the influence of uninformative predictors.
+A particular resampling technique was applied to the reduced training set to create balanced classes.
+A random forest classification algorithm was then performed and validated using the testing set.
+
+**Figure 3.
 The three predictor types considered when quantifying the association between TAD boundaries and genomic annotations.** The _overlap count_ (OC) predictors consider the total number of genomic features that overlapped with each genomic bin.
@@
 
-**Figure 3: Ensemble Framework/Model Building Pipeline.** A diagram of the model building pipeline given an a combination of inputs from the ensemble framework.
-The data was split into a 7:3 training set to testing set ratio, the variable reduction technique of choice was used to minimize the number of uninformative predictors, and a random forest classification algorithm was performed.
-Each model was then validated on the same testing set.
+**Figure 4.
+Precision-Recall curves for unbalanced 10 kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on unbalanced data at 10 kb resolution.
+GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red).
+For both cell lines, random forest models with log distance-type predictors were found to have higher AUPRC values.
 
-**Figure 4: Techniques for addressing class imbalance.** Barplots illustrating the class imbalance problem featured across each of the four different resolutions that were analyzed.
-Minority classes represent the number of genomic bins that contain a TAD boundary, while the majority classes represent the number of genomic bins that do not contain a TAD boundary.
+**Figure 5.
+Model Performances on 10kb data using distance-type predictors for different number of features** Using RFE, performances of a series of random forest models with different numbers of the most predictive features for each cell line was compared using AUPRC.
+For convenience and computational efficiency, only specific subsets of features were considered (increasing powers of 2).
+For the 10 kb data, near optimal performance was achieved for both the GM12878 (red) and K562 cell lines (blue).
 
-# Figure 5: 5kb Model Performances
-
-Comparing model performances for TAD boundary data at 5kb resolution across each re-sampling technique.
-Each square plot represents a random forest classifier performed on 5kb resolution binned boundary data using a particular predictor type, variable reduction algorithm, and re-sampling technique evaluated across 4 different performance metrics.
-
-# Figure 6: 25kb Model Performances
-
-Comparing model performances for TAD boundary data at 25kb resolution across each re-sampling technique.
-Each square plot represents a random forest classifier performed on 25kb resolution binned boundary data using a particular predictor type, variable reduction algorithm, and re-sampling technique evaluated across 4 different performance metrics.
-
-# Figure 7: 50kb Model Performances
-
-Comparing model performances for TAD boundary data at 50kb resolution across each re-sampling technique.
-Each square plot represents a random forest classifier performed on 50kb resolution binned boundary data using a particular predictor type, variable reduction algorithm, and re-sampling technique evaluated across 4 different performance metrics.
-
-# Figure 8: 100kb Model Performances
-
-Comparing model performances for TAD boundary data at 100kb resolution across each re-sampling technique. Each square plot represents a random forest classifier performed on 10
-+0kb resolution binned boundary data using a particular predictor type, variable reduction algorithm, and re-sampling technique evaluated across 4 different performance metrics.
-
-**Figure 9: Comparing Performances** Comparing performances of random forest classification algorithms, across TAD boundary data at each resolution for models using distance-type predictors, with elastic-net regularization and random under-sampling.
-Performances were aggregated by taking the average of each metric across 50 iterations of random under-sampling.
-[???
-Poor legend]
-
-**Figure 10: Comparing Variable Importance.** Comparing variable importance for the top 15 most predictive functional genomic elements for each of the 4 different resolutions.
-The x-axis represents the standardized difference between the out-of-bag prediction accuracy after permutting each predictor variable, averaged across all trees.
-The greater the mean standardized difference, the more importance the predictor is to the model.
-[???
-What are A/B/C/D panels?]
-
-# Figure 11: Model Performances for all Resolutions
-
-Comparing model performances for TAD boundary data for all 4 resolutions.
-The four regions represent (from left to right; top to bottom) data at 5kb, 25kb, 50kb, and 100kb resolutions.
-Within each region, the rows represent the set of re-sampling techniques, while the columns represent the set of performance metrics that the models were evaluated on.
-Each plot compares 2 sets of models; one using LASSO regularization and one using Elastic-Net regularization.
-Within each set, each bar represents the performance of a model with a specific predictor type; either overlap counts (OC) in red, overlap percent (OP) in green, or distance in blue.
+**Figure 6.
+Variable importance heatmap for 10 kb data across cell lines.** Predictive importance of the top 32 genomic features across cell lines for 10 kb data.
+Importance was discretized into quantiles, with features that were not congruent between cell lines filled in grey.

### 2019-01-24 Manuscript/Supplementary/supplementary_legends.Rmd
updated legends

@@
 ---
+
+**Figure 1. Distance Densities across cell lines and resolutions**
+Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for GM12878 (left column) and K562 (right column) cell lines.
+The untransformed distances (red) are highly right skewed.
+After performing a $log_{2}$ tranformation (blue), the distances exhibit more normalized densities.
+The normalized distances were exhibited across all data resolution (rows).
+
+**Figure 2.
+Precision-Recall curves for unbalanced 25 kb, 50kb, and 100kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on unbalanced data at 25 kb, 50kb, and 100kb resolution.
+GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red).
+For both cell lines, and among all resolutions, random forest models with log distance-type predictors were found to have higher AUPRC values.
+
+**Figure 3.
+Model Performances on 25 kb, 50kb, and 100kb data using distance-type predictors for different number of features** Using RFE, performances of a series of random forest models with different numbers of the most predictive features for each cell line was compared using AUPRC.
+For convenience and computational efficiency, only specific subsets of features were considered (increasing powers of 2).
+For each resolution, near optimal performance was achieved for both the GM12878 (red) and K562 cell lines (blue).
+
+**Figure 4.
+Variable importance heatmap for 25 kb, 50kb, and 100kb data across cell lines.** Predictive importance of the top 32 genomic features across cell lines for 25 kb, 50kb, and 100kb resolutions.
+Importance was discretized into quantiles, with features that were not congruent between cell lines filled in grey.
+
+**Figure 5: Imbalance ratios across resolutions and cell lines.** Imbalance ratios, defined as the ratio of minority class samples to majority class samples, were plotted across resolutions for cell lines GM12878 (red) and K562 (blue).
+The mean imbalance ratios across resolutions were found to be X1 (SD=Y2) and X2 (SD=Y2) for the GM12878 and K562 cell lines respectively.
 
@@
 Did you use only features common to both cell lines?]
-
-## Table 2: Class Distributions for Other Resolutions
-
-Summary of the class distributions for each of the other resolution domain data sets (25 kb, 50 kb, and 100 kb), across each re-sampling technique.
-As with the 5 kb data, all re-sampling techniques yielded completely balanced classes.
-That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.
-
-## Table 3: Model Performances When Not Accounting for Class Imbalance
-
-Results of various metrics used to assess predictive performances for models that were built on fully imbalanced datasets.
-
-## Figure 1: Performances of Models with Both SMOTE-Balanced and Randomly Over-sampled Data.
-
-Barplots measuring the predictive performance of models built on datasets using 50 iterations of both the SMOTE algorithm (A) and random over-sampling (B).
-The performance metrics considered were accuracy, AUC, F1-Score, and MCC.
-Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).
-
-## Table 4:
-
-Results of various metrics used to assess predictive performances for models that were built on random under-sampled datasets.
-
-## Table 5:
-
-Results of various metrics used to assess predictive performances for models that were built on both SMOTE-balanced and random over-sampled datasets.

### 2019-01-24 Manuscript/Tables/table_legends.Rmd
WIP through the manuscript
updated legends

--- 2018-11-19 Manuscript/Tables/table_legends.Rmd
@@
 ```
-
-# Table 1: List of Genomic Annoations.
-
-The full list of genomic annotations used in downstream analyses.
-These annotations were the functional genomic elements used to predict the formation of TAD boundaries.
-They were obtained via ChIP-Seq experiments, mapped to human genome assembly hg19, and made available by the ENCODE Consortium.
-
-# Table 2: 5kb Class Distributions
-
-The class distributions for different re-sampling techniques from domain data obtained from 5kb resolution contact matrices.
-
-# Table 3: 25kb Class Distributions
-
-The class distributions for different re-sampling techniques from domain data obtained from 25kb resolution contact matrices.
-
-# Table 4: 50kb Class Distributions
-
-The class distributions for different re-sampling techniques from domain data obtained from 50kb resolution contact matrices.
-
-# Table 5: 100kb Class Distributions
-
-The class distributions for different re-sampling techniques from domain data obtained from 100kb resolution contact matrices.

### 2019-01-25 Scripts/performances.rmd
added scripts folder used to create figures for results

---
title: "Performances Code"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)

```

# Evaluating Distance Densities
##GM12878
###10kb

```{r}
gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")

gm12878_10kb_ld <- gm12878_10kb[,c(1,grep("_dist", names(gm12878_10kb)))]

###############
#gm12878_10kb_ld <- gm12878_10kb_ld[,c(1:5)]
###############

gm12878_10kb_d <- gm12878_10kb_ld
gm12878_10kb_d[,-1] <- exp(gm12878_10kb_ld[,-1]) - 1
gm12878_10kb_d$Average_dist <- rowMeans(gm12878_10kb_d[,-1])

gm12878_10kb_ld$Average_dist <- rowMeans(gm12878_10kb_ld[,-1])
names(gm12878_10kb_ld)[-1] <- paste(substr(names(gm12878_10kb_ld)[-1],
                                           1, 
                                           nchar(names(gm12878_10kb_ld)[-1])-4), 
                                    "logdist", 
                                    sep="")

gm12878_10kb_alldist <- cbind.data.frame(gm12878_10kb_d[,-1], gm12878_10kb_ld[,-1])

long10kb <- melt(gm12878_10kb_alldist)
long10kb$variable <- as.character(long10kb$variable)
long10kb$Transformation <- NA
long10kb$Transformation[grep("_logdist", long10kb$variable)] <- rep("Log Distance", length(long10kb$variable[grep("_logdist", long10kb$variable)]))
long10kb$Transformation[grep("_logdist", long10kb$variable, invert = TRUE)] <- rep("Distance", length(long10kb$variable[grep("_logdist", long10kb$variable, invert = TRUE)]))

table(long10kb$Transformation)

distdensity10kb <- ggplot() + 
  geom_density(data=long10kb[intersect(grep("_dist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long10kb[grep("Average_dist", long10kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,2.5e+07) + 
	ylab("")+ 
  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
	scale_fill_manual(values="red")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

logdistdensity10kb <- ggplot() + 
  geom_density(data=long10kb[intersect(grep("logdist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long10kb[grep("Average_logdist", long10kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	ylab("")+ 
	scale_fill_manual(values="blue")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

#rescaling nontransformed and combining two plots
long10kb$value[long10kb$Transformation=="Distance"] <- long10kb$value[long10kb$Transformation=="Distance"]/1000000
long10kb <- long10kb[grep("Average", long10kb$variable, invert = TRUE),]
long10kb$variable <- factor(long10kb$variable)
long10kb$Transformation <- factor(long10kb$Transformation)

alldensity10kb <- ggplot(long10kb, aes(x=value, group=variable, fill=Transformation)) + 
  geom_density(alpha=0.01) +
  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
  guides(fill = guide_legend(override.aes = list(alpha=1)))+
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	ylab("10 kb")+ 
  ylim(0,.8)+
  ggtitle("GM12878") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

```

###25kb

```{r}
gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")

gm12878_25kb_ld <- gm12878_25kb[,c(1,grep("_dist", names(gm12878_25kb)))]

###############
#gm12878_25kb_ld <- gm12878_25kb_ld[,c(1:5)]
###############

gm12878_25kb_d <- gm12878_25kb_ld
gm12878_25kb_d[,-1] <- exp(gm12878_25kb_ld[,-1]) - 1
gm12878_25kb_d$Average_dist <- rowMeans(gm12878_25kb_d[,-1])

gm12878_25kb_ld$Average_dist <- rowMeans(gm12878_25kb_ld[,-1])
names(gm12878_25kb_ld)[-1] <- paste(substr(names(gm12878_25kb_ld)[-1],
                                           1, 
                                           nchar(names(gm12878_25kb_ld)[-1])-4), 
                                    "logdist", 
                                    sep="")

gm12878_25kb_alldist <- cbind.data.frame(gm12878_25kb_d[,-1], gm12878_25kb_ld[,-1])

long25kb <- melt(gm12878_25kb_alldist)
long25kb$variable <- as.character(long25kb$variable)
long25kb$Transformation <- NA
long25kb$Transformation[grep("_logdist", long25kb$variable)] <- rep("Log Distance", length(long25kb$variable[grep("_logdist", long25kb$variable)]))
long25kb$Transformation[grep("_logdist", long25kb$variable, invert = TRUE)] <- rep("Distance", length(long25kb$variable[grep("_logdist", long25kb$variable, invert = TRUE)]))

table(long25kb$Transformation)

distdensity25kb <- ggplot() + 
  geom_density(data=long25kb[intersect(grep("_dist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long25kb[grep("Average_dist", long25kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,2.5e+07) + 
	ylab("")+ 
  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
	scale_fill_manual(values="red")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

logdistdensity25kb <- ggplot() + 
  geom_density(data=long25kb[intersect(grep("logdist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long25kb[grep("Average_logdist", long25kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) +  
	ylab("")+ 
	scale_fill_manual(values="blue")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

#rescaling nontransformed and combining two plots
long25kb$value[long25kb$Transformation=="Distance"] <- long25kb$value[long25kb$Transformation=="Distance"]/1000000
long25kb <- long25kb[grep("Average", long25kb$variable, invert = TRUE),]
long25kb$variable <- factor(long25kb$variable)
long25kb$Transformation <- factor(long25kb$Transformation)

alldensity25kb <- ggplot(long25kb, aes(x=value, group=variable, fill=Transformation)) + 
  geom_density(alpha=0.01) +
  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
  guides(fill = guide_legend(override.aes = list(alpha=1)))+
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	ylab("25 kb")+ 
  ylim(0,.8)+
  #ggtitle("GM12878") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

```

###50kb

```{r}
gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")

gm12878_50kb_ld <- gm12878_50kb[,c(1,grep("_dist", names(gm12878_50kb)))]

###############
#gm12878_50kb_ld <- gm12878_50kb_ld[,c(1:5)]
###############

gm12878_50kb_d <- gm12878_50kb_ld
gm12878_50kb_d[,-1] <- exp(gm12878_50kb_ld[,-1]) - 1
gm12878_50kb_d$Average_dist <- rowMeans(gm12878_50kb_d[,-1])

gm12878_50kb_ld$Average_dist <- rowMeans(gm12878_50kb_ld[,-1])
names(gm12878_50kb_ld)[-1] <- paste(substr(names(gm12878_50kb_ld)[-1],
                                           1, 
                                           nchar(names(gm12878_50kb_ld)[-1])-4), 
                                    "logdist", 
                                    sep="")

gm12878_50kb_alldist <- cbind.data.frame(gm12878_50kb_d[,-1], gm12878_50kb_ld[,-1])

long50kb <- melt(gm12878_50kb_alldist)
long50kb$variable <- as.character(long50kb$variable)
long50kb$Transformation <- NA
long50kb$Transformation[grep("_logdist", long50kb$variable)] <- rep("Log Distance", length(long50kb$variable[grep("_logdist", long50kb$variable)]))
long50kb$Transformation[grep("_logdist", long50kb$variable, invert = TRUE)] <- rep("Distance", length(long50kb$variable[grep("_logdist", long50kb$variable, invert = TRUE)]))

table(long50kb$Transformation)

distdensity50kb <- ggplot() + 
  geom_density(data=long50kb[intersect(grep("_dist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long50kb[grep("Average_dist", long50kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,2.5e+07) + 
	ylab("")+ 
  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
	scale_fill_manual(values="red")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

logdistdensity50kb <- ggplot() + 
  geom_density(data=long50kb[intersect(grep("logdist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long50kb[grep("Average_logdist", long50kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	ylab("")+ 
	scale_fill_manual(values="blue")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

#rescaling nontransformed and combining two plots
long50kb$value[long50kb$Transformation=="Distance"] <- long50kb$value[long50kb$Transformation=="Distance"]/1000000
long50kb <- long50kb[grep("Average", long50kb$variable, invert = TRUE),]
long50kb$variable <- factor(long50kb$variable)
long50kb$Transformation <- factor(long50kb$Transformation)

alldensity50kb <- ggplot(long50kb, aes(x=value, group=variable, fill=Transformation)) + 
  geom_density(alpha=0.01) +
  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
  guides(fill = guide_legend(override.aes = list(alpha=1)))+
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	ylab("50 kb")+ 
  ylim(0,.8)+
  #ggtitle("GM12878") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

```

###100kb

```{r}
gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")

gm12878_100kb_ld <- gm12878_100kb[,c(1,grep("_dist", names(gm12878_100kb)))]

###############
#gm12878_100kb_ld <- gm12878_100kb_ld[,c(1:5)]
###############

gm12878_100kb_d <- gm12878_100kb_ld
gm12878_100kb_d[,-1] <- exp(gm12878_100kb_ld[,-1]) - 1
gm12878_100kb_d$Average_dist <- rowMeans(gm12878_100kb_d[,-1])

gm12878_100kb_ld$Average_dist <- rowMeans(gm12878_100kb_ld[,-1])
names(gm12878_100kb_ld)[-1] <- paste(substr(names(gm12878_100kb_ld)[-1],
                                           1, 
                                           nchar(names(gm12878_100kb_ld)[-1])-4), 
                                    "logdist", 
                                    sep="")

gm12878_100kb_alldist <- cbind.data.frame(gm12878_100kb_d[,-1], gm12878_100kb_ld[,-1])

long100kb <- melt(gm12878_100kb_alldist)
long100kb$variable <- as.character(long100kb$variable)
long100kb$Transformation <- NA
long100kb$Transformation[grep("_logdist", long100kb$variable)] <- rep("Log Distance", length(long100kb$variable[grep("_logdist", long100kb$variable)]))
long100kb$Transformation[grep("_logdist", long100kb$variable, invert = TRUE)] <- rep("Distance", length(long100kb$variable[grep("_logdist", long100kb$variable, invert = TRUE)]))

table(long100kb$Transformation)

distdensity100kb <- ggplot() + 
  geom_density(data=long100kb[intersect(grep("_dist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long100kb[grep("Average_dist", long100kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("No Transformation") + 
	xlim(0,2.5e+07) + 
	ylab("")+ 
  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
	scale_fill_manual(values="red")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

logdistdensity100kb <- ggplot() + 
  geom_density(data=long100kb[intersect(grep("logdist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long100kb[grep("Average_logdist", long100kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("Log Tranformation") + 
	xlim(0,25) + 
	ylab("")+ 
	scale_fill_manual(values="blue")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

#rescaling nontransformed and combining two plots
long100kb$value[long100kb$Transformation=="Distance"] <- long100kb$value[long100kb$Transformation=="Distance"]/1000000
long100kb <- long100kb[grep("Average", long100kb$variable, invert = TRUE),]
long100kb$variable <- factor(long100kb$variable)
long100kb$Transformation <- factor(long100kb$Transformation)

alldensity100kb <- ggplot(long100kb, aes(x=value, group=variable, fill=Transformation)) + 
  geom_density(alpha=0.01) +
  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
  guides(fill = guide_legend(override.aes = list(alpha=1)))+
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	ylab("100 kb")+ 
  ylim(0,.8)+
  #ggtitle("GM12878") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

```

##K562
###10kb

```{r}
K562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")

K562_10kb_ld <- K562_10kb[,c(1,grep("_dist", names(K562_10kb)))]

###############
#K562_10kb_ld <- K562_10kb_ld[,c(1:5)]
###############

K562_10kb_d <- K562_10kb_ld
K562_10kb_d[,-1] <- exp(K562_10kb_ld[,-1]) - 1
K562_10kb_d$Average_dist <- rowMeans(K562_10kb_d[,-1])

K562_10kb_ld$Average_dist <- rowMeans(K562_10kb_ld[,-1])
names(K562_10kb_ld)[-1] <- paste(substr(names(K562_10kb_ld)[-1],
                                           1, 
                                           nchar(names(K562_10kb_ld)[-1])-4), 
                                    "logdist", 
                                    sep="")

K562_10kb_alldist <- cbind.data.frame(K562_10kb_d[,-1], K562_10kb_ld[,-1])

long10kb <- melt(K562_10kb_alldist)
long10kb$variable <- as.character(long10kb$variable)
long10kb$Transformation <- NA
long10kb$Transformation[grep("_logdist", long10kb$variable)] <- rep("Log Distance", length(long10kb$variable[grep("_logdist", long10kb$variable)]))
long10kb$Transformation[grep("_logdist", long10kb$variable, invert = TRUE)] <- rep("Distance", length(long10kb$variable[grep("_logdist", long10kb$variable, invert = TRUE)]))

table(long10kb$Transformation)

distdensity10kb <- ggplot() + 
  geom_density(data=long10kb[intersect(grep("_dist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long10kb[grep("Average_dist", long10kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,2.5e+07) + 
	ylab("")+ 
  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
	scale_fill_manual(values="red")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

logdistdensity10kb <- ggplot() + 
  geom_density(data=long10kb[intersect(grep("logdist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long10kb[grep("Average_logdist", long10kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	ylab("")+ 
	scale_fill_manual(values="blue")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

#rescaling nontransformed and combining two plots
long10kb$value[long10kb$Transformation=="Distance"] <- long10kb$value[long10kb$Transformation=="Distance"]/1000000
long10kb <- long10kb[grep("Average", long10kb$variable, invert = TRUE),]
long10kb$variable <- factor(long10kb$variable)
long10kb$Transformation <- factor(long10kb$Transformation)

alldensity10kb_k562 <- ggplot(long10kb, aes(x=value, group=variable, fill=Transformation)) + 
  geom_density(alpha=0.01) +
  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
  guides(fill = guide_legend(override.aes = list(alpha=1)))+
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	#ylab("10 kb")+ 
  ylim(0,.8)+
  ggtitle("K562") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

```

###25kb

```{r}
K562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")

K562_25kb_ld <- K562_25kb[,c(1,grep("_dist", names(K562_25kb)))]

###############
#K562_25kb_ld <- K562_25kb_ld[,c(1:5)]
###############

K562_25kb_d <- K562_25kb_ld
K562_25kb_d[,-1] <- exp(K562_25kb_ld[,-1]) - 1
K562_25kb_d$Average_dist <- rowMeans(K562_25kb_d[,-1])

K562_25kb_ld$Average_dist <- rowMeans(K562_25kb_ld[,-1])
names(K562_25kb_ld)[-1] <- paste(substr(names(K562_25kb_ld)[-1],
                                           1, 
                                           nchar(names(K562_25kb_ld)[-1])-4), 
                                    "logdist", 
                                    sep="")

K562_25kb_alldist <- cbind.data.frame(K562_25kb_d[,-1], K562_25kb_ld[,-1])

long25kb <- melt(K562_25kb_alldist)
long25kb$variable <- as.character(long25kb$variable)
long25kb$Transformation <- NA
long25kb$Transformation[grep("_logdist", long25kb$variable)] <- rep("Log Distance", length(long25kb$variable[grep("_logdist", long25kb$variable)]))
long25kb$Transformation[grep("_logdist", long25kb$variable, invert = TRUE)] <- rep("Distance", length(long25kb$variable[grep("_logdist", long25kb$variable, invert = TRUE)]))

table(long25kb$Transformation)

distdensity25kb <- ggplot() + 
  geom_density(data=long25kb[intersect(grep("_dist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long25kb[grep("Average_dist", long25kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,2.5e+07) + 
	ylab("")+ 
  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
	scale_fill_manual(values="red")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

logdistdensity25kb <- ggplot() + 
  geom_density(data=long25kb[intersect(grep("logdist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long25kb[grep("Average_logdist", long25kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	ylab("")+ 
	scale_fill_manual(values="blue")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

#rescaling nontransformed and combining two plots
long25kb$value[long25kb$Transformation=="Distance"] <- long25kb$value[long25kb$Transformation=="Distance"]/1000000
long25kb <- long25kb[grep("Average", long25kb$variable, invert = TRUE),]
long25kb$variable <- factor(long25kb$variable)
long25kb$Transformation <- factor(long25kb$Transformation)

alldensity25kb_k562 <- ggplot(long25kb, aes(x=value, group=variable, fill=Transformation)) + 
  geom_density(alpha=0.01) +
  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
  guides(fill = guide_legend(override.aes = list(alpha=1)))+
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	#ylab("25 kb")+ 
  ylim(0,.8)+
  #ggtitle("K562") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

```

###50kb

```{r}
K562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")

K562_50kb_ld <- K562_50kb[,c(1,grep("_dist", names(K562_50kb)))]

###############
#K562_50kb_ld <- K562_50kb_ld[,c(1:5)]
###############

K562_50kb_d <- K562_50kb_ld
K562_50kb_d[,-1] <- exp(K562_50kb_ld[,-1]) - 1
K562_50kb_d$Average_dist <- rowMeans(K562_50kb_d[,-1])

K562_50kb_ld$Average_dist <- rowMeans(K562_50kb_ld[,-1])
names(K562_50kb_ld)[-1] <- paste(substr(names(K562_50kb_ld)[-1],
                                           1, 
                                           nchar(names(K562_50kb_ld)[-1])-4), 
                                    "logdist", 
                                    sep="")

K562_50kb_alldist <- cbind.data.frame(K562_50kb_d[,-1], K562_50kb_ld[,-1])

long50kb <- melt(K562_50kb_alldist)
long50kb$variable <- as.character(long50kb$variable)
long50kb$Transformation <- NA
long50kb$Transformation[grep("_logdist", long50kb$variable)] <- rep("Log Distance", length(long50kb$variable[grep("_logdist", long50kb$variable)]))
long50kb$Transformation[grep("_logdist", long50kb$variable, invert = TRUE)] <- rep("Distance", length(long50kb$variable[grep("_logdist", long50kb$variable, invert = TRUE)]))

table(long50kb$Transformation)

distdensity50kb <- ggplot() + 
  geom_density(data=long50kb[intersect(grep("_dist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long50kb[grep("Average_dist", long50kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,2.5e+07) + 
	ylab("")+ 
  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
	scale_fill_manual(values="red")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

logdistdensity50kb <- ggplot() + 
  geom_density(data=long50kb[intersect(grep("logdist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long50kb[grep("Average_logdist", long50kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	ylab("")+ 
	scale_fill_manual(values="blue")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

#rescaling nontransformed and combining two plots
long50kb$value[long50kb$Transformation=="Distance"] <- long50kb$value[long50kb$Transformation=="Distance"]/1000000
long50kb <- long50kb[grep("Average", long50kb$variable, invert = TRUE),]
long50kb$variable <- factor(long50kb$variable)
long50kb$Transformation <- factor(long50kb$Transformation)

alldensity50kb_k562 <- ggplot(long50kb, aes(x=value, group=variable, fill=Transformation)) + 
  geom_density(alpha=0.01) +
  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
  guides(fill = guide_legend(override.aes = list(alpha=1)))+
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	#ylab("50 kb")+ 
  ylim(0,.8)+
  #ggtitle("K562") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

```

###100kb

```{r}
K562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")

K562_100kb_ld <- K562_100kb[,c(1,grep("_dist", names(K562_100kb)))]

###############
#K562_100kb_ld <- K562_100kb_ld[,c(1:5)]
###############

K562_100kb_d <- K562_100kb_ld
K562_100kb_d[,-1] <- exp(K562_100kb_ld[,-1]) - 1
K562_100kb_d$Average_dist <- rowMeans(K562_100kb_d[,-1])

K562_100kb_ld$Average_dist <- rowMeans(K562_100kb_ld[,-1])
names(K562_100kb_ld)[-1] <- paste(substr(names(K562_100kb_ld)[-1],
                                           1, 
                                           nchar(names(K562_100kb_ld)[-1])-4), 
                                    "logdist", 
                                    sep="")

K562_100kb_alldist <- cbind.data.frame(K562_100kb_d[,-1], K562_100kb_ld[,-1])

long100kb <- melt(K562_100kb_alldist)
long100kb$variable <- as.character(long100kb$variable)
long100kb$Transformation <- NA
long100kb$Transformation[grep("_logdist", long100kb$variable)] <- rep("Log Distance", length(long100kb$variable[grep("_logdist", long100kb$variable)]))
long100kb$Transformation[grep("_logdist", long100kb$variable, invert = TRUE)] <- rep("Distance", length(long100kb$variable[grep("_logdist", long100kb$variable, invert = TRUE)]))

table(long100kb$Transformation)

distdensity100kb <- ggplot() + 
  geom_density(data=long100kb[intersect(grep("_dist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long100kb[grep("Average_dist", long100kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,2.5e+07) + 
	ylab("")+ 
  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
	scale_fill_manual(values="red")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

logdistdensity100kb <- ggplot() + 
  geom_density(data=long100kb[intersect(grep("logdist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
               ,aes(x=value, 
                    group=variable, 
                    fill=Transformation), alpha=0.01, size=0.5) +
  #geom_density(data=long100kb[grep("Average_logdist", long100kb$variable),]
  #             ,aes(x=value), size = 1) +
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	ylab("")+ 
	scale_fill_manual(values="blue")+
		#labels=as.character(
		#		unique(
		#			sort(
		#				as.numeric(
		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
		#values=rainbow(22)) +
	theme_minimal() +
  guides(fill=FALSE)+
  theme(axis.text.y = element_blank())
  #theme(axis.line = element_line(color="black", size = .5))

#rescaling nontransformed and combining two plots
long100kb$value[long100kb$Transformation=="Distance"] <- long100kb$value[long100kb$Transformation=="Distance"]/1000000
long100kb <- long100kb[grep("Average", long100kb$variable, invert = TRUE),]
long100kb$variable <- factor(long100kb$variable)
long100kb$Transformation <- factor(long100kb$Transformation)

alldensity100kb_k562 <- ggplot(long100kb, aes(x=value, group=variable, fill=Transformation)) + 
  geom_density(alpha=0.01) +
  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
  guides(fill = guide_legend(override.aes = list(alpha=1)))+
  geom_vline(xintercept=0, size=1)+
  geom_hline(yintercept=0, size=1)+
	xlab("") + 
	xlim(0,25) + 
	#ylab("100 kb")+ 
  ylim(0,.8)+
  #ggtitle("K562") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

```

##Combined

```{r}
#alldistplots <- grid.arrange(distdensity10kb, logdistdensity10kb,
#             distdensity25kb, logdistdensity25kb,
#             distdensity50kb, logdistdensity50kb,
#             distdensity100kb, logdistdensity100kb, ncol=2, nrow=4)

alldistplots <- ggarrange(alldensity10kb,
                          alldensity10kb_k562,
                          alldensity25kb,
                          alldensity25kb_k562,
                          alldensity50kb,
                          alldensity50kb_k562,
                          alldensity100kb,
                          alldensity100kb_k562, 
          ncol=2, 
          nrow=4,
          #labels = c("A","", "B","", "C","", "D",""),
          legend = "top",
          common.legend = TRUE)

annotate_figure(alldistplots,
                bottom = text_grob("Distance to Nearest TAD Boundary \n (in millions of basepairs)", 
                                color = "black", 
                                face = "bold", 
                                size = 15),
                left = text_grob("Density", 
                                 color = "black",
                                 size = 15,
                                 rot = 90))
```

#Evaluating Imbalance Ratios
##GM12878
###10kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x10 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p10kb <- ggplot(x10, aes(y=IR, x=factor(CB, levels = unique(x10$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

```

###25kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x25 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p25kb <- ggplot(x25, aes(y=IR, x=factor(CB, levels = unique(x25$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

```

###50kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x50 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p50kb <- ggplot(x50, aes(y=IR, x=factor(CB, levels = unique(x50$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

```

###100kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x100 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p100kb <- ggplot(x100, aes(y=IR, x=factor(CB, levels = unique(x100$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

```

##K562
###10kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x10_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p10kb_k562 <- ggplot(x10_k562, aes(y=IR, x=factor(CB, levels = unique(x10_k562$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

```

###25kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x25_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p25kb_k562 <- ggplot(x25_k562, aes(y=IR, x=factor(CB, levels = unique(x25_k562$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

```

###50kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x50_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p50kb_k562 <- ggplot(x50_k562, aes(y=IR, x=factor(CB, levels = unique(x50_k562$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

```

###100kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x100_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p100kb_k562 <- ggplot(x100_k562, aes(y=IR, x=factor(CB, levels = unique(x100_k562$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

```

##Combined
```{r}

IR=c(x10$IR[x10$CB=="Complete"],
                              x25$IR[x25$CB=="Complete"],
                              x50$IR[x50$CB=="Complete"],
                              x100$IR[x100$CB=="Complete"],
                              x10_k562$IR[x10_k562$CB=="Complete"], 
                              x25_k562$IR[x25_k562$CB=="Complete"],
                              x50_k562$IR[x50_k562$CB=="Complete"],
                              x100_k562$IR[x100_k562$CB=="Complete"])
CL <- c(rep("GM12878", 4), 
                  rep("K562", 4))
Resolution <- c(rep(c("10 kb", "25 kb", "50 kb", "100 kb"), 2))

allirdata <- cbind.data.frame(IR, CL, Resolution)
allirdata$CL <- factor(allirdata$CL, levels=c("GM12878", "K562"))
allirdata$Resolution <- factor(allirdata$Resolution, c("10 kb", "25 kb", "50 kb", "100 kb"))

allirplots <- ggplot(allirdata, aes(x = Resolution, y = IR,fill = CL)) + 
  geom_bar(position = "dodge", stat="identity") + 
  ylab("Imbalance Ratio") +
  xlab("Resolution") +
  #scale_fill_manual(name="Cell Line", values=c("red", "blue"))+
  labs(fill="Cell Line")+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

```

#Evaluating Feature Engineering

## PR Curves

###GM12878

####10kb

```{r}

prall <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")

#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)

test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)

#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)

```

####25kb

```{r}

prall <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")

#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)

test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)

#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)

```

####50kb

```{r}

prall <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/op/RFE/prcurve.rds")

#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)

test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)

#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)

```

####100kb

```{r}

prall <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/op/RFE/prcurve.rds")

#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)

test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)

#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)

```

###K562

####10kb

```{r}
prall <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")

#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)

test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)

#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: )","All (AUPRC: )", "Percents (AUPRC: )", "Counts (AUPRC: )", "Baseline"),
#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)

```

####25kb

```{r}
prall <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")

#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)

test <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/test.rds")
abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)

#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: )","All (AUPRC: )","Percents (AUPRC: )", "Counts (AUPRC: )", "Baseline"),
#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)

```

####50kb

```{r}
prall <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/op/RFE/prcurve.rds")

#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)

test <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/test.rds")
abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)

#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: )","All (AUPRC: )","Percents (AUPRC: )", "Counts (AUPRC: )", "Baseline"),
#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)

```

####100kb

```{r}
prall <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/op/RFE/prcurve.rds")

#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)

test <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/test.rds")
abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)

#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: )","All (AUPRC: )", "Percents (AUPRC: )", "Counts (AUPRC: )", "Baseline"),
#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)

```

###Combined

```{r}
#10kb
prall <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")

prall_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
prdist_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
prop_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")

prdata_10kb <- rbind.data.frame(prall$curve,
                                prdist$curve,
                                prop$curve,
                                proc$curve,
                                prall_k562$curve,
                                prdist_k562$curve,
                                prop_k562$curve,
                                proc_k562$curve)
names(prdata_10kb) <- c("Recall", "Precision", "Threshold")
prdata_10kb$Predictor <- c(rep("All", dim(prall$curve)[1]),
                           rep("Distance", dim(prdist$curve)[1]),
                           rep("OP", dim(prop$curve)[1]),
                           rep("OC", dim(proc$curve)[1]),
                           rep("All", dim(prall_k562$curve)[1]),
                           rep("Distance", dim(prdist_k562$curve)[1]),
                           rep("OP", dim(prop_k562$curve)[1]),
                           rep("OC", dim(proc_k562$curve)[1]))
prdata_10kb$CL <- c(rep("GM12878", (dim(prall$curve)[1]+
                                      dim(prdist$curve)[1]+
                                      dim(prop$curve)[1]+
                                      dim(proc$curve)[1])),
                    rep("K562", (dim(prall_k562$curve)[1]+
                                      dim(prdist_k562$curve)[1]+
                                      dim(prop_k562$curve)[1]+
                                      dim(proc_k562$curve)[1])))
prdata_10kb$Predictor <- factor(prdata_10kb$Predictor)
prdata_10kb$CL <- factor(prdata_10kb$CL)

prplot_10kb <- ggplot(prdata_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

#25kb
prall <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")

prall_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
prdist_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
prop_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")

prdata_25kb <- rbind.data.frame(prall$curve,
                                prdist$curve,
                                prop$curve,
                                proc$curve,
                                prall_k562$curve,
                                prdist_k562$curve,
                                prop_k562$curve,
                                proc_k562$curve)
names(prdata_25kb) <- c("Recall", "Precision", "Threshold")
prdata_25kb$Predictor <- c(rep("All", dim(prall$curve)[1]),
                           rep("Distance", dim(prdist$curve)[1]),
                           rep("OP", dim(prop$curve)[1]),
                           rep("OC", dim(proc$curve)[1]),
                           rep("All", dim(prall_k562$curve)[1]),
                           rep("Distance", dim(prdist_k562$curve)[1]),
                           rep("OP", dim(prop_k562$curve)[1]),
                           rep("OC", dim(proc_k562$curve)[1]))
prdata_25kb$CL <- c(rep("GM12878", (dim(prall$curve)[1]+
                                      dim(prdist$curve)[1]+
                                      dim(prop$curve)[1]+
                                      dim(proc$curve)[1])),
                    rep("K562", (dim(prall_k562$curve)[1]+
                                      dim(prdist_k562$curve)[1]+
                                      dim(prop_k562$curve)[1]+
                                      dim(proc_k562$curve)[1])))
prdata_25kb$Predictor <- factor(prdata_25kb$Predictor)
prdata_25kb$CL <- factor(prdata_25kb$CL)

prplot_25kb <- ggplot(prdata_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

#50kb
prall <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/op/RFE/prcurve.rds")

prall_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")
prdist_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/oc/RFE/prcurve.rds")
prop_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/op/RFE/prcurve.rds")

prdata_50kb <- rbind.data.frame(prall$curve,
                                prdist$curve,
                                prop$curve,
                                proc$curve,
                                prall_k562$curve,
                                prdist_k562$curve,
                                prop_k562$curve,
                                proc_k562$curve)
names(prdata_50kb) <- c("Recall", "Precision", "Threshold")
prdata_50kb$Predictor <- c(rep("All", dim(prall$curve)[1]),
                           rep("Distance", dim(prdist$curve)[1]),
                           rep("OP", dim(prop$curve)[1]),
                           rep("OC", dim(proc$curve)[1]),
                           rep("All", dim(prall_k562$curve)[1]),
                           rep("Distance", dim(prdist_k562$curve)[1]),
                           rep("OP", dim(prop_k562$curve)[1]),
                           rep("OC", dim(proc_k562$curve)[1]))
prdata_50kb$CL <- c(rep("GM12878", (dim(prall$curve)[1]+
                                      dim(prdist$curve)[1]+
                                      dim(prop$curve)[1]+
                                      dim(proc$curve)[1])),
                    rep("K562", (dim(prall_k562$curve)[1]+
                                      dim(prdist_k562$curve)[1]+
                                      dim(prop_k562$curve)[1]+
                                      dim(proc_k562$curve)[1])))
prdata_50kb$Predictor <- factor(prdata_50kb$Predictor)
prdata_50kb$CL <- factor(prdata_50kb$CL)

prplot_50kb <- ggplot(prdata_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

#100kb
prall <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/op/RFE/prcurve.rds")

prall_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")
prdist_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/oc/RFE/prcurve.rds")
prop_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/op/RFE/prcurve.rds")

prdata_100kb <- rbind.data.frame(prall$curve,
                                prdist$curve,
                                prop$curve,
                                proc$curve,
                                prall_k562$curve,
                                prdist_k562$curve,
                                prop_k562$curve,
                                proc_k562$curve)
names(prdata_100kb) <- c("Recall", "Precision", "Threshold")
prdata_100kb$Predictor <- c(rep("All", dim(prall$curve)[1]),
                           rep("Distance", dim(prdist$curve)[1]),
                           rep("OP", dim(prop$curve)[1]),
                           rep("OC", dim(proc$curve)[1]),
                           rep("All", dim(prall_k562$curve)[1]),
                           rep("Distance", dim(prdist_k562$curve)[1]),
                           rep("OP", dim(prop_k562$curve)[1]),
                           rep("OC", dim(proc_k562$curve)[1]))
prdata_100kb$CL <- c(rep("GM12878", (dim(prall$curve)[1]+
                                      dim(prdist$curve)[1]+
                                      dim(prop$curve)[1]+
                                      dim(proc$curve)[1])),
                    rep("K562", (dim(prall_k562$curve)[1]+
                                      dim(prdist_k562$curve)[1]+
                                      dim(prop_k562$curve)[1]+
                                      dim(proc_k562$curve)[1])))
prdata_100kb$Predictor <- factor(prdata_100kb$Predictor)
prdata_100kb$CL <- factor(prdata_100kb$CL)

prplot_100kb <- ggplot(prdata_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

ggarrange(prplot_25kb, prplot_50kb, prplot_100kb,
          nrow=2,ncol=2,
          common.legend = TRUE, legend = "right")
```

## RFE

###GM12878

####10kb

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
#                                 rep("Distance", nrow(rfeModel_dist$results)),
#                                 rep("OC", nrow(rfeModel_oc$results)),
#                                 rep("OP", nrow(rfeModel_op$results)))

#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)

resampdata_10kb <- rfeModel_dist$results[1:6,]

pt10kb <- ggplot(resampdata_10kb, aes(x=Variables, y=AUPRC)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  theme_minimal()+
  ylim(0,.5)

```

####25kb

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
#                                 rep("Distance", nrow(rfeModel_dist$results)),
#                                 rep("OC", nrow(rfeModel_oc$results)),
#                                 rep("OP", nrow(rfeModel_op$results)))

#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)

resampdata_25kb <- rfeModel_dist$results[1:6,]

pt25kb <- ggplot(resampdata_25kb, aes(x=Variables, y=AUPRC)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  theme_minimal()+
  ylim(0,.5)

```

####50kb

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
#                                 rep("Distance", nrow(rfeModel_dist$results)),
#                                 rep("OC", nrow(rfeModel_oc$results)),
#                                 rep("OP", nrow(rfeModel_op$results)))

#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)

resampdata_50kb <- rfeModel_dist$results[1:6,]

pt50kb <- ggplot(resampdata_50kb, aes(x=Variables, y=AUPRC)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  theme_minimal()+
  ylim(0,.5)

```

####100kb

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
#                                 rep("Distance", nrow(rfeModel_dist$results)),
#                                 rep("OC", nrow(rfeModel_oc$results)),
#                                 rep("OP", nrow(rfeModel_op$results)))

#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)

resampdata_100kb <- rfeModel_dist$results[1:6,]

pt100kb <- ggplot(resampdata_100kb, aes(x=Variables, y=AUPRC)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  theme_minimal()+
  ylim(0,.5)

```

###K562

####10kb

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
#                                 rep("Distance", nrow(rfeModel_dist$results)),
#                                 rep("OC", nrow(rfeModel_oc$results)),
#                                 rep("OP", nrow(rfeModel_op$results)))

#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)

resampdata_10kb_k562 <- rfeModel_dist$results[1:6,]

pt10kb_k562 <- ggplot(resampdata_10kb_k562, aes(x=Variables, y=AUPRC)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  theme_minimal()+
  ylim(0,.5)

```

####25kb

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
#                                 rep("Distance", nrow(rfeModel_dist$results)),
#                                 rep("OC", nrow(rfeModel_oc$results)),
#                                 rep("OP", nrow(rfeModel_op$results)))

#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)

resampdata_25kb_k562 <- rfeModel_dist$results[1:6,]

pt25kb <- ggplot(resampdata_25kb_k562, aes(x=Variables, y=AUPRC)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  theme_minimal()+
  ylim(0,.5)

```

####50kb

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
#                                 rep("Distance", nrow(rfeModel_dist$results)),
#                                 rep("OC", nrow(rfeModel_oc$results)),
#                                 rep("OP", nrow(rfeModel_op$results)))

#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)

resampdata_50kb_k562 <- rfeModel_dist$results[1:6,]

pt50kb <- ggplot(resampdata_50kb_k562, aes(x=Variables, y=AUPRC)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  theme_minimal()+
  ylim(0,.5)

```

####100kb

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
#                                 rep("Distance", nrow(rfeModel_dist$results)),
#                                 rep("OC", nrow(rfeModel_oc$results)),
#                                 rep("OP", nrow(rfeModel_op$results)))

#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)

resampdata_100kb_k562 <- rfeModel_dist$results[1:6,]

pt100kb <- ggplot(resampdata_100kb_k562, aes(x=Variables, y=AUPRC)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  theme_minimal()+
  ylim(0,.5)

```

### Combined

```{r}

allrfe10kb <- rbind.data.frame(resampdata_10kb, resampdata_10kb_k562)
allrfe10kb$CL <- c(rep("GM12878", 6),rep("K562", 6))
allrfe10kb$CL <- factor(allrfe10kb$CL)

rfe10kbplot <- ggplot(data=allrfe10kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  scale_color_discrete(name="Cell Line")+
  theme_bw()+
  #ggtitle("10 kb") +
  ylim(0,.5)+
  theme(plot.title = element_text(hjust = 0.5))

allrfe25kb <- rbind.data.frame(resampdata_25kb, resampdata_25kb_k562)
allrfe25kb$CL <- c(rep("GM12878", 6),rep("K562", 6))
allrfe25kb$CL <- factor(allrfe25kb$CL)

rfe25kbplot <- ggplot(data=allrfe25kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  scale_color_discrete(name="Cell Line")+
  theme_bw()+
  #ggtitle("25 kb") +
  ylim(0,.5)+
  theme(plot.title = element_text(hjust = 0.5))

allrfe50kb <- rbind.data.frame(resampdata_50kb, resampdata_50kb_k562)
allrfe50kb$CL <- c(rep("GM12878", 6),rep("K562", 6))
allrfe50kb$CL <- factor(allrfe50kb$CL)

rfe50kbplot <- ggplot(data=allrfe50kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  scale_color_discrete(name="Cell Line")+
  theme_bw()+
  #ggtitle("50 kb") +
  ylim(0,.5)+
  theme(plot.title = element_text(hjust = 0.5))

allrfe100kb <- rbind.data.frame(resampdata_100kb, resampdata_100kb_k562)
allrfe100kb$CL <- c(rep("GM12878", 6),rep("K562", 6))
allrfe100kb$CL <- factor(allrfe100kb$CL)

rfe100kbplot <- ggplot(data=allrfe100kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  scale_color_discrete(name="Cell Line")+
  theme_minimal()+
  theme_bw()+
  #ggtitle("100 kb") +
  ylim(0,.5)+
  theme(plot.title = element_text(hjust = 0.5))

ggarrange(rfe25kbplot, rfe50kbplot, rfe100kbplot,
          nrow=2,ncol=2,
          common.legend = TRUE, legend = "right")

#comparing top predictors across resolution and cell line
rfeModel_dist_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe10kbvars <- rfeModel_dist_10kb$optVariables[1:32]

rfeModel_dist_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe25kbvars <- rfeModel_dist_25kb$optVariables[1:32]

rfeModel_dist_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe50kbvars <- rfeModel_dist_50kb$optVariables[1:32]

rfeModel_dist_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe100kbvars <- rfeModel_dist_100kb$optVariables[1:32]

rfeModel_dist_10kb_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe10kbvars_k562 <- rfeModel_dist_10kb_k562$optVariables[1:32]

rfeModel_dist_25kb_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe25kbvars_k562 <- rfeModel_dist_25kb_k562$optVariables[1:32]

rfeModel_dist_50kb_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe50kbvars_k562 <- rfeModel_dist_50kb_k562$optVariables[1:32]

rfeModel_dist_100kb_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe100kbvars_k562 <- rfeModel_dist_100kb_k562$variables$var[rfeModel_dist_100kb_k562$variables$Variables==32 & rfeModel_dist_100kb_k562$variables$Resample=="Fold1.Rep1"]

rfe10kbvars <- gsub(paste(c("Gm12878-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe10kbvars)
rfe25kbvars <- gsub(paste(c("Gm12878-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe25kbvars)
rfe50kbvars <- gsub(paste(c("Gm12878-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe50kbvars)
rfe100kbvars <- gsub(paste(c("Gm12878-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe100kbvars)

rfe10kbvars_k562 <- gsub(paste(c("K562-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe10kbvars_k562)
rfe25kbvars_k562 <- gsub(paste(c("K562-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe25kbvars_k562)
rfe50kbvars_k562 <- gsub(paste(c("K562-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe50kbvars_k562)
rfe100kbvars_k562 <- gsub(paste(c("K562-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe100kbvars_k562)

alltopvars <- data.frame(rfe10kbvars,
                         rfe10kbvars_k562,
                         rfe25kbvars,
                         rfe25kbvars_k562,
                         rfe50kbvars,
                         rfe50kbvars_k562,
                         rfe100kbvars,
                         rfe100kbvars_k562)

rfe10kbvars_o <- sort(rfe10kbvars)
rfe25kbvars_o <- sort(rfe25kbvars)
rfe50kbvars_o <- sort(rfe50kbvars)
rfe100kbvars_o <- sort(rfe100kbvars)
rfe10kbvars_k562_o <- sort(rfe10kbvars_k562)
rfe25kbvars_k562_o <- sort(rfe25kbvars_k562)
rfe50kbvars_k562_o <- sort(rfe50kbvars_k562)
rfe100kbvars_k562_o <- sort(rfe100kbvars_k562)
alltopvars_o <- data.frame(rfe10kbvars_o,rfe25kbvars_o,rfe50kbvars_o,rfe100kbvars_o,
                         rfe10kbvars_k562_o,rfe25kbvars_k562_o,rfe50kbvars_k562_o,rfe100kbvars_k562_o)

grid.newpage()
venn.plot <- draw.quad.venn(
	area1 = length(rfe10kbvars), #The size of the first set
	area2 = length(rfe25kbvars), #The size of the second set
	area3 = length(rfe50kbvars), #The size of the third set
	area4 = length(rfe100kbvars), #The size of the fourth set
	n12 = length(intersect(rfe10kbvars,rfe25kbvars)), #The size of the intersection between the first and the second set
	n13 = length(intersect(rfe10kbvars,rfe50kbvars)), #The size of the intersection between the first and the third set
	n14 = length(intersect(rfe10kbvars,rfe100kbvars)), #The size of the intersection between the first and the fourth set
	n23 = length(intersect(rfe25kbvars,rfe50kbvars)), #The size of the intersection between the second and the third set
	n24 = length(intersect(rfe25kbvars,rfe100kbvars)), #The size of the intersection between the second and the fourth set
	n34 = length(intersect(rfe50kbvars,rfe100kbvars)), #The size of the intersection between the third and the fourth set
	n123 = length(Reduce(intersect, list(rfe10kbvars,rfe25kbvars,rfe50kbvars))), #The size of the intersection between the first, second and third sets
	n124 = length(Reduce(intersect, list(rfe10kbvars,rfe25kbvars,rfe100kbvars))), #The size of the intersection between the first, second and fourth sets
	n134 = length(Reduce(intersect, list(rfe10kbvars,rfe50kbvars,rfe100kbvars))), #The size of the intersection between the first, third and fourth sets
	n234 = length(Reduce(intersect, list(rfe25kbvars,rfe50kbvars,rfe100kbvars))), #The size of the intersection between the second, third and fourth sets
	n1234 = length(Reduce(intersect, list(rfe10kbvars,rfe25kbvars,rfe50kbvars,rfe100kbvars))), #The size of the intersection between all four sets
	category = c("10 kb", "25 kb", "50 kb", "100 kb"),
	fill = c("orange", "red", "green", "blue"),
	lty = "dashed",
	cex = 2,
	cat.cex = 2,
	cat.col = c("orange", "red", "green", "blue")
	);

grid.newpage()
venn.plot.k562 <- draw.quad.venn(
	area1 = length(rfe10kbvars_k562), #The size of the first set
	area2 = length(rfe25kbvars_k562), #The size of the second set
	area3 = length(rfe50kbvars_k562), #The size of the third set
	area4 = length(rfe100kbvars_k562), #The size of the fourth set
	n12 = length(intersect(rfe10kbvars_k562,rfe25kbvars_k562)), #The size of the intersection between the first and the second set
	n13 = length(intersect(rfe10kbvars_k562,rfe50kbvars_k562)), #The size of the intersection between the first and the third set
	n14 = length(intersect(rfe10kbvars_k562,rfe100kbvars_k562)), #The size of the intersection between the first and the fourth set
	n23 = length(intersect(rfe25kbvars_k562,rfe50kbvars_k562)), #The size of the intersection between the second and the third set
	n24 = length(intersect(rfe25kbvars_k562,rfe100kbvars_k562)), #The size of the intersection between the second and the fourth set
	n34 = length(intersect(rfe50kbvars_k562,rfe100kbvars_k562)), #The size of the intersection between the third and the fourth set
	n123 = length(Reduce(intersect, list(rfe10kbvars_k562,rfe25kbvars_k562,rfe50kbvars_k562))), #The size of the intersection between the first, second and third sets
	n124 = length(Reduce(intersect, list(rfe10kbvars_k562,rfe25kbvars_k562,rfe100kbvars_k562))), #The size of the intersection between the first, second and fourth sets
	n134 = length(Reduce(intersect, list(rfe10kbvars_k562,rfe50kbvars_k562,rfe100kbvars_k562))), #The size of the intersection between the first, third and fourth sets
	n234 = length(Reduce(intersect, list(rfe25kbvars_k562,rfe50kbvars_k562,rfe100kbvars_k562))), #The size of the intersection between the second, third and fourth sets
	n1234 = length(Reduce(intersect, list(rfe10kbvars_k562,rfe25kbvars_k562,rfe50kbvars_k562,rfe100kbvars_k562))), #The size of the intersection between all four sets
	category = c("10 kb", "25 kb", "50 kb", "100 kb"),
	fill = c("orange", "red", "green", "blue"),
	lty = "dashed",
	cex = 2,
	cat.cex = 2,
	cat.col = c("orange", "red", "green", "blue")
	);

grid.newpage()
venn.plot.10kb <- draw.pairwise.venn(
	area1 = length(rfe10kbvars),
	area2 = length(rfe10kbvars_k562),
	cross.area = length(intersect(rfe10kbvars,rfe10kbvars_k562)),
	category = c("GM12878", "K562"),
	fill = c("blue", "red"),
	lty = "blank",
	cex = 2,
	cat.cex = 2,
	cat.just = list(c(-.5, -3), c(2, -3)))

grid.newpage()
venn.plot.25kb <- draw.pairwise.venn(
	area1 = length(rfe25kbvars),
	area2 = length(rfe25kbvars_k562),
	cross.area = length(intersect(rfe25kbvars,rfe25kbvars_k562)),
	category = c("GM12878", "K562"),
	fill = c("blue", "red"),
	lty = "blank",
	cex = 2,
	cat.cex = 2,
	cat.just = list(c(-.5, -3), c(2, -3)))

grid.newpage()
venn.plot.50kb <- draw.pairwise.venn(
	area1 = length(rfe50kbvars),
	area2 = length(rfe50kbvars_k562),
	cross.area = length(intersect(rfe50kbvars,rfe50kbvars_k562)),
	category = c("GM12878", "K562"),
	fill = c("blue", "red"),
	lty = "blank",
	cex = 2,
	cat.cex = 2,
	cat.just = list(c(-.5, -3), c(2, -3)))

grid.newpage()
venn.plot.100kb <- draw.pairwise.venn(
	area1 = length(rfe100kbvars),
	area2 = length(rfe100kbvars_k562),
	cross.area = length(intersect(rfe100kbvars,rfe100kbvars_k562)),
	category = c("GM12878", "K562"),
	fill = c("blue", "red"),
	lty = "blank",
	cex = 2,
	cat.cex = 2,
	cat.just = list(c(-.5, -3), c(2, -3)))

```

##Heatmaps of top predictors

###10 kb

```{r}
topvars10kbgm12878 <- cbind.data.frame(names(rfeModel_dist_10kb$fit$importance[,1]), rfeModel_dist_10kb$fit$importance)
topvars10kbgm12878 <- topvars10kbgm12878[1:32,]
rownames(topvars10kbgm12878) <- NULL
names(topvars10kbgm12878) <- c("Feature", "Importance")
topvars10kbgm12878$Feature <- gsub(paste(c("Gm12878-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars10kbgm12878$Feature)

topvars10kbk562 <- cbind.data.frame(names(rfeModel_dist_10kb_k562$fit$importance[,1]), rfeModel_dist_10kb_k562$fit$importance[,4])
topvars10kbk562 <- topvars10kbk562[1:32,]
rownames(topvars10kbk562) <- NULL
names(topvars10kbk562) <- c("Feature", "Importance")
topvars10kbk562$Feature <- gsub(paste(c("K562-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars10kbk562$Feature)

impdata_10kb <- data.frame(Feature = Reduce(union, 
                                            list(topvars10kbgm12878$Feature,
                                                 topvars10kbk562$Feature)))
impdata_10kb$gm12878_10kb <- NA
impdata_10kb$k562_10kb <- NA

impdata_10kb$gm12878_10kb[which(impdata_10kb$Feature %in% topvars10kbgm12878$Feature)] <- topvars10kbgm12878$Importance
impdata_10kb$k562_10kb[which(impdata_10kb$Feature %in% topvars10kbk562$Feature)] <- topvars10kbk562$Importance

impdata_10kb <- impdata_10kb[order(impdata_10kb$Feature),]

#preObj <- preProcess(impdata_10kb, method=c("center", "scale"))
#impdata_10kb <- predict(preObj, impdata_10kb)

impdata_10kb_long <- melt(impdata_10kb)
impdata_10kb_long <- ddply(impdata_10kb_long, .(variable), transform,   
                           rescale = rescale(value))

topvars10kbplot <- ggplot(impdata_10kb_long, aes(variable, Feature)) + 
    geom_tile(aes(fill = rescale),
              colour = "white") + scale_fill_gradient2(low = "white", 
                                                      #mid = "white",
                                                      high = muted("red"), 
                                                      #midpoint = 0, 
                                                      space = "Lab",
                                                      na.value = "grey50", 
                                                      guide = "legend", 
                                                      aesthetics = "fill",
                                                      name="Importance",
                                                      labels=c("Very Low",
                                                               "Low",
                                                               "Medium",
                                                               "High",
                                                               "Very High"))+
  scale_x_discrete(name="Cell Line", labels=c("GM12878", "K562"))+
  theme_bw()+
  theme_minimal()
```

###25 kb

```{r}
topvars25kbgm12878 <- cbind.data.frame(names(rfeModel_dist_25kb$fit$importance[,1]), rfeModel_dist_25kb$fit$importance)
topvars25kbgm12878 <- topvars25kbgm12878[1:32,]
rownames(topvars25kbgm12878) <- NULL
names(topvars25kbgm12878) <- c("Feature", "Importance")
topvars25kbgm12878$Feature <- gsub(paste(c("Gm12878-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars25kbgm12878$Feature)

topvars25kbk562 <- cbind.data.frame(names(rfeModel_dist_25kb_k562$fit$importance[,1]), rfeModel_dist_25kb_k562$fit$importance[,1])
topvars25kbk562 <- topvars25kbk562[1:32,]
rownames(topvars25kbk562) <- NULL
names(topvars25kbk562) <- c("Feature", "Importance")
topvars25kbk562$Feature <- gsub(paste(c("K562-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars25kbk562$Feature)

impdata_25kb <- data.frame(Feature = Reduce(union, 
                                            list(topvars25kbgm12878$Feature,
                                                 topvars25kbk562$Feature)))
impdata_25kb$gm12878_25kb <- NA
impdata_25kb$k562_25kb <- NA

impdata_25kb$gm12878_25kb[which(impdata_25kb$Feature %in% topvars25kbgm12878$Feature)] <- topvars25kbgm12878$Importance
impdata_25kb$k562_25kb[which(impdata_25kb$Feature %in% topvars25kbk562$Feature)] <- topvars25kbk562$Importance

impdata_25kb <- impdata_25kb[order(impdata_25kb$Feature),]

#preObj <- preProcess(impdata_25kb, method=c("center", "scale"))
#impdata_25kb <- predict(preObj, impdata_25kb)

impdata_25kb_long <- melt(impdata_25kb)
impdata_25kb_long <- ddply(impdata_25kb_long, .(variable), transform,   
                           rescale = rescale(value))

topvars25kbplot <- ggplot(impdata_25kb_long, aes(variable, Feature)) + 
    geom_tile(aes(fill = rescale),
              colour = "white") + scale_fill_gradient2(low = "white", 
                                                      #mid = "white",
                                                      high = muted("red"), 
                                                      #midpoint = 0, 
                                                      space = "Lab",
                                                      na.value = "grey50", 
                                                      guide = "legend", 
                                                      aesthetics = "fill",
                                                      name="Importance",
                                                      labels=c("Very Low",
                                                               "Low",
                                                               "Medium",
                                                               "High",
                                                               "Very High"))+
  scale_x_discrete(name="Cell Line", labels=c("GM12878", "K562"))+
  theme_bw()+
  theme_minimal()
```

###50kb

```{r}
topvars50kbgm12878 <- cbind.data.frame(names(rfeModel_dist_50kb$fit$importance[,1]), rfeModel_dist_50kb$fit$importance)
topvars50kbgm12878 <- topvars50kbgm12878[1:32,]
rownames(topvars50kbgm12878) <- NULL
names(topvars50kbgm12878) <- c("Feature", "Importance")
topvars50kbgm12878$Feature <- gsub(paste(c("Gm12878-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars50kbgm12878$Feature)

topvars50kbk562 <- cbind.data.frame(names(rfeModel_dist_50kb_k562$fit$importance[,1]), rfeModel_dist_50kb_k562$fit$importance[,1])
topvars50kbk562 <- topvars50kbk562[1:32,]
rownames(topvars50kbk562) <- NULL
names(topvars50kbk562) <- c("Feature", "Importance")
topvars50kbk562$Feature <- gsub(paste(c("K562-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars50kbk562$Feature)

impdata_50kb <- data.frame(Feature = Reduce(union, 
                                            list(topvars50kbgm12878$Feature,
                                                 topvars50kbk562$Feature)))
impdata_50kb$gm12878_50kb <- NA
impdata_50kb$k562_50kb <- NA

impdata_50kb$gm12878_50kb[which(impdata_50kb$Feature %in% topvars50kbgm12878$Feature)] <- topvars50kbgm12878$Importance
impdata_50kb$k562_50kb[which(impdata_50kb$Feature %in% topvars50kbk562$Feature)] <- topvars50kbk562$Importance

impdata_50kb <- impdata_50kb[order(impdata_50kb$Feature),]

#preObj <- preProcess(impdata_50kb, method=c("center", "scale"))
#impdata_50kb <- predict(preObj, impdata_50kb)

impdata_50kb_long <- melt(impdata_50kb)
impdata_50kb_long <- ddply(impdata_50kb_long, .(variable), transform,   
                           rescale = rescale(value))

topvars50kbplot <- ggplot(impdata_50kb_long, aes(variable, Feature)) + 
    geom_tile(aes(fill = rescale),
              colour = "white") + scale_fill_gradient2(low = "white", 
                                                      #mid = "white",
                                                      high = muted("red"), 
                                                      #midpoint = 0, 
                                                      space = "Lab",
                                                      na.value = "grey50", 
                                                      guide = "legend", 
                                                      aesthetics = "fill",
                                                      name="Importance",
                                                      labels=c("Very Low",
                                                               "Low",
                                                               "Medium",
                                                               "High",
                                                               "Very High"))+
  scale_x_discrete(name="Cell Line", labels=c("GM12878", "K562"))+
  theme_bw()+
  theme_minimal()
```

###100kb

```{r}
topvars100kbgm12878 <- cbind.data.frame(names(rfeModel_dist_100kb$fit$importance[,1]), rfeModel_dist_100kb$fit$importance)
topvars100kbgm12878 <- topvars100kbgm12878[1:32,]
rownames(topvars100kbgm12878) <- NULL
names(topvars100kbgm12878) <- c("Feature", "Importance")
topvars100kbgm12878$Feature <- gsub(paste(c("Gm12878-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars100kbgm12878$Feature)

topvars100kbk562 <- cbind.data.frame(rfeModel_dist_100kb_k562$variables$var[1:32], rfeModel_dist_100kb_k562$variables$Overall[1:32])
topvars100kbk562 <- topvars100kbk562[1:32,]
rownames(topvars100kbk562) <- NULL
names(topvars100kbk562) <- c("Feature", "Importance")
topvars100kbk562$Feature <- gsub(paste(c("K562-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars100kbk562$Feature)

impdata_100kb <- data.frame(Feature = Reduce(union, 
                                            list(topvars100kbgm12878$Feature,
                                                 topvars100kbk562$Feature)))
impdata_100kb$gm12878_100kb <- NA
impdata_100kb$k562_100kb <- NA

impdata_100kb$gm12878_100kb[which(impdata_100kb$Feature %in% topvars100kbgm12878$Feature)] <- topvars100kbgm12878$Importance
impdata_100kb$k562_100kb[which(impdata_100kb$Feature %in% topvars100kbk562$Feature)] <- topvars100kbk562$Importance

impdata_100kb <- impdata_100kb[order(impdata_100kb$Feature),]

#preObj <- preProcess(impdata_100kb, method=c("center", "scale"))
#impdata_100kb <- predict(preObj, impdata_100kb)

impdata_100kb_long <- melt(impdata_100kb)
impdata_100kb_long <- ddply(impdata_100kb_long, .(variable), transform,   
                           rescale = rescale(value))

topvars100kbplot <- ggplot(impdata_100kb_long, aes(variable, Feature)) + 
    geom_tile(aes(fill = rescale),
              colour = "white") + scale_fill_gradient2(low = "white", 
                                                      #mid = "white",
                                                      high = muted("red"), 
                                                      #midpoint = 0, 
                                                      space = "Lab",
                                                      na.value = "grey50", 
                                                      guide = "legend", 
                                                      aesthetics = "fill",
                                                      name="Importance",
                                                      labels=c("Very Low",
                                                               "Low",
                                                               "Medium",
                                                               "High",
                                                               "Very High"))+
  scale_x_discrete(name="Cell Line", labels=c("GM12878", "K562"))+
  theme_bw()+
  theme_minimal()
```

###Combined

```{r}
ggarrange(topvars25kbplot,
          topvars50kbplot,
          topvars100kbplot,
          ncol=3,
          nrow=1,
          common.legend = TRUE,
          legend = "right")
```

#Barplots of performance metrics

##Comparing results for no class balancing

###10kb

```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")

none.10 <- data.frame(Performance = c(rfperf1[9,2],
								rfperf2[9,2],
								rfperf3[9,2],
								rfperf1[17,2],
								rfperf2[17,2],
								rfperf3[17,2],
								rfperf1[16,2],
								rfperf2[16,2],
								rfperf3[16,2],
								rfperf1[15,2],
								rfperf2[15,2],
								rfperf3[15,2]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
none.10$Predictor <- factor(none.10$Predictor, levels=c("OC", "OP", "Distance"))
none.10$Metric <- factor(none.10$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###25kb
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")

none.25 <- data.frame(Performance = c(rfperf1[9,2],
								rfperf2[9,2],
								rfperf3[9,2],
								rfperf1[17,2],
								rfperf2[17,2],
								rfperf3[17,2],
								rfperf1[16,2],
								rfperf2[16,2],
								rfperf3[16,2],
								rfperf1[15,2],
								rfperf2[15,2],
								rfperf3[15,2]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
none.25$Predictor <- factor(none.25$Predictor, levels=c("OC", "OP", "Distance"))
none.25$Metric <- factor(none.25$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###50kb
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")

none.50 <- data.frame(Performance = c(rfperf1[9,2],
								rfperf2[9,2],
								rfperf3[9,2],
								rfperf1[17,2],
								rfperf2[17,2],
								rfperf3[17,2],
								rfperf1[16,2],
								rfperf2[16,2],
								rfperf3[16,2],
								rfperf1[15,2],
								rfperf2[15,2],
								rfperf3[15,2]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
none.50$Predictor <- factor(none.50$Predictor, levels=c("OC", "OP", "Distance"))
none.50$Metric <- factor(none.50$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###100kb
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")

none.100 <- data.frame(Performance = c(rfperf1[9,2],
								rfperf2[9,2],
								rfperf3[9,2],
								rfperf1[17,2],
								rfperf2[17,2],
								rfperf3[17,2],
								rfperf1[16,2],
								rfperf2[16,2],
								rfperf3[16,2],
								rfperf1[15,2],
								rfperf2[15,2],
								rfperf3[15,2]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
none.100$Predictor <- factor(none.100$Predictor, levels=c("OC", "OP", "Distance"))
none.100$Metric <- factor(none.100$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###Plots
```{r}
none.data <- rbind.data.frame(none.10,none.25,none.50,none.100) 
none.data$Resolution <- c(rep("10 kb", 12), rep("25 kb", 12), rep("50 kb", 12), rep("100 kb", 12))
none.data$Resolution <- factor(none.data$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))

allnoneplots <- ggplot(none.data, aes(fill=Resolution, y=Performance, x=Resolution)) +
	geom_bar( stat="identity", position="dodge") +
	facet_grid(Predictor ~ Metric) +
	ylab("Performance")+
	xlab("Resolution")+
	theme_bw() +
  guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
		legend.position="bottom")

```

###Tables

```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")

rfperf4 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
rfperf5 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
rfperf6 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")

rfperf7 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
rfperf8 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
rfperf9 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")

rfperf10 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
rfperf11 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
rfperf12 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")

nonetab <- cbind.data.frame(rfperf1$Metric,
                            rfperf1$Performance,
                            rfperf2$Performance,
                            rfperf3$Performance,
                            rfperf4$Performance,
                            rfperf5$Performance,
                            rfperf6$Performance,
                            rfperf7$Performance,
                            rfperf8$Performance,
                            rfperf9$Performance,
                            rfperf10$Performance,
                            rfperf11$Performance,
                            rfperf12$Performance)
nonetab[,-1] <- round(nonetab[,-1], 3)
datatable(nonetab)
```

##Comparing results for RUS

###10kb

```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

RUS.10 <- data.frame(Performance = c(rfperf1[9],
								rfperf2[9],
								rfperf3[9],
								rfperf1[17],
								rfperf2[17],
								rfperf3[17],
								rfperf1[16],
								rfperf2[16],
								rfperf3[16],
								rfperf1[15],
								rfperf2[15],
								rfperf3[15]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
RUS.10$Predictor <- factor(RUS.10$Predictor, levels=c("OC", "OP", "Distance"))
RUS.10$Metric <- factor(RUS.10$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###25kb
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

RUS.25 <- data.frame(Performance = c(rfperf1[9],
								rfperf2[9],
								rfperf3[9],
								rfperf1[17],
								rfperf2[17],
								rfperf3[17],
								rfperf1[16],
								rfperf2[16],
								rfperf3[16],
								rfperf1[15],
								rfperf2[15],
								rfperf3[15]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
RUS.25$Predictor <- factor(RUS.25$Predictor, levels=c("OC", "OP", "Distance"))
RUS.25$Metric <- factor(RUS.25$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###50kb
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

RUS.50 <- data.frame(Performance = c(rfperf1[9],
								rfperf2[9],
								rfperf3[9],
								rfperf1[17],
								rfperf2[17],
								rfperf3[17],
								rfperf1[16],
								rfperf2[16],
								rfperf3[16],
								rfperf1[15],
								rfperf2[15],
								rfperf3[15]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
RUS.50$Predictor <- factor(RUS.50$Predictor, levels=c("OC", "OP", "Distance"))
RUS.50$Metric <- factor(RUS.50$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###100kb
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

RUS.100 <- data.frame(Performance = c(rfperf1[9],
								rfperf2[9],
								rfperf3[9],
								rfperf1[17],
								rfperf2[17],
								rfperf3[17],
								rfperf1[16],
								rfperf2[16],
								rfperf3[16],
								rfperf1[15],
								rfperf2[15],
								rfperf3[15]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
RUS.100$Predictor <- factor(RUS.100$Predictor, levels=c("OC", "OP", "Distance"))
RUS.100$Metric <- factor(RUS.100$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###Plots
```{r}
RUS.data <- rbind.data.frame(RUS.10,RUS.25,RUS.50,RUS.100) 
RUS.data$Resolution <- c(rep("10 kb", 12), rep("25 kb", 12), rep("50 kb", 12), rep("100 kb", 12))
RUS.data$Resolution <- factor(RUS.data$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))

allRUSplots <- ggplot(RUS.data, aes(fill=Resolution, y=Performance, x=Resolution)) +
	geom_bar( stat="identity", position="dodge") +
	facet_grid(Predictor ~ Metric) +
	ylab("Performance")+
	xlab("Resolution")+
	theme_bw() +
  guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
		legend.position="bottom")

```

###Tables
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

rfperf4 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
rfperf4 <- rowMeans(rfperf4)
rfperf5 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
rfperf5 <- rowMeans(rfperf5)
rfperf6 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
rfperf6 <- rowMeans(rfperf6)

rfperf7 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
rfperf7 <- rowMeans(rfperf7)
rfperf8 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
rfperf8 <- rowMeans(rfperf8)
rfperf9 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
rfperf9 <- rowMeans(rfperf9)

rfperf10 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
rfperf10 <- rowMeans(rfperf10)
rfperf11 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
rfperf11 <- rowMeans(rfperf11)
rfperf12 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
rfperf12 <- rowMeans(rfperf12)

RUStab <- cbind.data.frame(names(rfperf1),
                            rfperf1,
                            rfperf2,
                            rfperf3,
                            rfperf4,
                            rfperf5,
                            rfperf6,
                            rfperf7,
                            rfperf8,
                            rfperf9,
                            rfperf10,
                            rfperf11,
                            rfperf12)
RUStab[,-1] <- round(RUStab[,-1], 3)
datatable(RUStab)
```

##Comparing results for SMOTE

###10kb

```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

SMOTE.10 <- data.frame(Performance = c(rfperf1[9],
								rfperf2[9],
								rfperf3[9],
								rfperf1[17],
								rfperf2[17],
								rfperf3[17],
								rfperf1[16],
								rfperf2[16],
								rfperf3[16],
								rfperf1[15],
								rfperf2[15],
								rfperf3[15]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
SMOTE.10$Predictor <- factor(SMOTE.10$Predictor, levels=c("OC", "OP", "Distance"))
SMOTE.10$Metric <- factor(SMOTE.10$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###25kb
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

SMOTE.25 <- data.frame(Performance = c(rfperf1[9],
								rfperf2[9],
								rfperf3[9],
								rfperf1[17],
								rfperf2[17],
								rfperf3[17],
								rfperf1[16],
								rfperf2[16],
								rfperf3[16],
								rfperf1[15],
								rfperf2[15],
								rfperf3[15]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
SMOTE.25$Predictor <- factor(SMOTE.25$Predictor, levels=c("OC", "OP", "Distance"))
SMOTE.25$Metric <- factor(SMOTE.25$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###50kb
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

SMOTE.50 <- data.frame(Performance = c(rfperf1[9],
								rfperf2[9],
								rfperf3[9],
								rfperf1[17],
								rfperf2[17],
								rfperf3[17],
								rfperf1[16],
								rfperf2[16],
								rfperf3[16],
								rfperf1[15],
								rfperf2[15],
								rfperf3[15]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
SMOTE.50$Predictor <- factor(SMOTE.50$Predictor, levels=c("OC", "OP", "Distance"))
SMOTE.50$Metric <- factor(SMOTE.50$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###100kb
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

SMOTE.100 <- data.frame(Performance = c(rfperf1[9],
								NA,#rfperf2[9],
								rfperf3[9],
								rfperf1[17],
								NA,#rfperf2[17],
								rfperf3[17],
								rfperf1[16],
								NA,#rfperf2[16],
								rfperf3[16],
								rfperf1[15],
								NA,#rfperf2[15],
								rfperf3[15]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
SMOTE.100$Predictor <- factor(SMOTE.100$Predictor, levels=c("OC", "OP", "Distance"))
SMOTE.100$Metric <- factor(SMOTE.100$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###Plots
```{r}
SMOTE.data <- rbind.data.frame(SMOTE.10,SMOTE.25,SMOTE.50,SMOTE.100) 
SMOTE.data$Resolution <- c(rep("10 kb", 12), rep("25 kb", 12), rep("50 kb", 12), rep("100 kb", 12))
SMOTE.data$Resolution <- factor(SMOTE.data$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))

allSMOTEplots <- ggplot(SMOTE.data, aes(fill=Resolution, y=Performance, x=Resolution)) +
	geom_bar( stat="identity", position="dodge") +
	facet_grid(Predictor ~ Metric) +
	ylab("Performance")+
	xlab("Resolution")+
	theme_bw() +
  guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
		legend.position="bottom")

```

###Tables
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

rfperf4 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
rfperf4 <- rowMeans(rfperf4)
rfperf5 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
rfperf5 <- rowMeans(rfperf5)
rfperf6 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
rfperf6 <- rowMeans(rfperf6)

rfperf7 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
rfperf7 <- rowMeans(rfperf7)
rfperf8 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
rfperf8 <- rowMeans(rfperf8)
rfperf9 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
rfperf9 <- rowMeans(rfperf9)

rfperf10 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
rfperf10 <- rowMeans(rfperf10)
rfperf11 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
rfperf11 <- rowMeans(rfperf11)
rfperf12 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
rfperf12 <- rowMeans(rfperf12)

SMOTEtab <- cbind.data.frame(names(rfperf1),
                            rfperf1,
                            rfperf2,
                            rfperf3,
                            rfperf4,
                            rfperf5,
                            rfperf6,
                            rfperf7,
                            rfperf8,
                            rfperf9,
                            rfperf10,
                            rep(NA,18),#rfperf11,
                            rfperf12)
SMOTEtab[,-c(1)] <- round(SMOTEtab[,-c(1)], 3)
SMOTEtab[,-c(1,12)] <- round(SMOTEtab[,-c(1,12)], 3)
datatable(SMOTEtab)
```

##Comparing results for SMOTE

###10kb

```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

ROS.10 <- data.frame(Performance = c(rfperf1[9],
								rfperf2[9],
								rfperf3[9],
								rfperf1[17],
								rfperf2[17],
								rfperf3[17],
								rfperf1[16],
								rfperf2[16],
								rfperf3[16],
								rfperf1[15],
								rfperf2[15],
								rfperf3[15]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
ROS.10$Predictor <- factor(ROS.10$Predictor, levels=c("OC", "OP", "Distance"))
ROS.10$Metric <- factor(ROS.10$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###25kb
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

ROS.25 <- data.frame(Performance = c(rfperf1[9],
								rfperf2[9],
								rfperf3[9],
								rfperf1[17],
								rfperf2[17],
								rfperf3[17],
								rfperf1[16],
								rfperf2[16],
								rfperf3[16],
								rfperf1[15],
								rfperf2[15],
								rfperf3[15]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
ROS.25$Predictor <- factor(ROS.25$Predictor, levels=c("OC", "OP", "Distance"))
ROS.25$Metric <- factor(ROS.25$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###50kb
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

ROS.50 <- data.frame(Performance = c(rfperf1[9],
								rfperf2[9],
								rfperf3[9],
								rfperf1[17],
								rfperf2[17],
								rfperf3[17],
								rfperf1[16],
								rfperf2[16],
								rfperf3[16],
								rfperf1[15],
								rfperf2[15],
								rfperf3[15]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
ROS.50$Predictor <- factor(ROS.50$Predictor, levels=c("OC", "OP", "Distance"))
ROS.50$Metric <- factor(ROS.50$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###100kb
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

ROS.100 <- data.frame(Performance = c(rfperf1[9],
								rfperf2[9],
								rfperf3[9],
								rfperf1[17],
								rfperf2[17],
								rfperf3[17],
								rfperf1[16],
								rfperf2[16],
								rfperf3[16],
								rfperf1[15],
								rfperf2[15],
								rfperf3[15]),
				Predictor = rep(c("OC", "OP", "Distance"), 4),
				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
ROS.100$Predictor <- factor(ROS.100$Predictor, levels=c("OC", "OP", "Distance"))
ROS.100$Metric <- factor(ROS.100$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
```

###Plots
```{r}
ROS.data <- rbind.data.frame(ROS.10,ROS.25,ROS.50,ROS.100) 
ROS.data$Resolution <- c(rep("10 kb", 12), rep("25 kb", 12), rep("50 kb", 12), rep("100 kb", 12))
ROS.data$Resolution <- factor(ROS.data$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))

allROSplots <- ggplot(ROS.data, aes(fill=Resolution, y=Performance, x=Resolution)) +
	geom_bar( stat="identity", position="dodge") +
	facet_grid(Predictor ~ Metric) +
	ylab("Performance")+
	xlab("Resolution")+
	theme_bw() +
  guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
		legend.position="bottom")

```

###Tables
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
rfperf1 <- rowMeans(rfperf1)
rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
rfperf2 <- rowMeans(rfperf2)
rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- rowMeans(rfperf3)

rfperf4 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
rfperf4 <- rowMeans(rfperf4)
rfperf5 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
rfperf5 <- rowMeans(rfperf5)
rfperf6 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
rfperf6 <- rowMeans(rfperf6)

rfperf7 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
rfperf7 <- rowMeans(rfperf7)
rfperf8 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
rfperf8 <- rowMeans(rfperf8)
rfperf9 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
rfperf9 <- rowMeans(rfperf9)

rfperf10 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
rfperf10 <- rowMeans(rfperf10)
rfperf11 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
rfperf11 <- rowMeans(rfperf11)
rfperf12 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
rfperf12 <- rowMeans(rfperf12)

ROStab <- cbind.data.frame(names(rfperf1),
                            rfperf1,
                            rfperf2,
                            rfperf3,
                            rfperf4,
                            rfperf5,
                            rfperf6,
                            rfperf7,
                            rfperf8,
                            rfperf9,
                            rfperf10,
                            rfperf11,
                            rfperf12)
ROStab[,-1] <- round(ROStab[,-1], 3)
datatable(ROStab)
```

#Comparing performance for distance predictors using RUS 
##10kb
```{r}
rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
rfperf1 <- cbind.data.frame(rownames(rfperf1),round(rowMeans(rfperf1),3))

rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
rfperf2 <- cbind.data.frame(rownames(rfperf2),round(rowMeans(rfperf2),3))

rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
rfperf3 <- cbind.data.frame(rownames(rfperf3),round(rowMeans(rfperf3),3))

```
##25kb
```{r}
rfperf4 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
rfperf4 <- cbind.data.frame(rownames(rfperf4),round(rowMeans(rfperf4),3))

rfperf5 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
rfperf5 <- cbind.data.frame(rownames(rfperf5),round(rowMeans(rfperf5),3))

rfperf6 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
rfperf6 <- cbind.data.frame(rownames(rfperf6),round(rowMeans(rfperf6),3))
```
##50kb
```{r}
rfperf7 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
rfperf7 <- cbind.data.frame(rownames(rfperf7),round(rowMeans(rfperf7),3))

rfperf8 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
rfperf8 <- cbind.data.frame(rownames(rfperf8),round(rowMeans(rfperf8),3))

rfperf9 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
rfperf9 <- cbind.data.frame(rownames(rfperf9),round(rowMeans(rfperf9),3))

```
##100kb
```{r}
rfperf10 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
rfperf10 <- cbind.data.frame(rownames(rfperf10),round(rowMeans(rfperf10),3))

rfperf11 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
rfperf11 <- cbind.data.frame(rownames(rfperf11),round(rowMeans(rfperf11),3))

rfperf12 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
rfperf12 <- cbind.data.frame(rownames(rfperf12),round(rowMeans(rfperf12),3))

```

##Plots
```{r}
distperftab <- data.frame(Performance =
                    c(rfperf1[9,2],
											rfperf1[17,2],
											rfperf1[16,2],
											rfperf1[15,2],
											rfperf2[9,2],
											rfperf2[17,2],
											rfperf2[16,2],
											rfperf2[15,2],
											rfperf3[9,2],
											rfperf3[17,2],
											rfperf3[16,2],
											rfperf3[15,2],
											rfperf4[9,2],
											rfperf4[17,2],
											rfperf4[16,2],
											rfperf4[15,2],
											rfperf5[9,2],
											rfperf5[17,2],
											rfperf5[16,2],
											rfperf5[15,2],
											rfperf6[9,2],
											rfperf6[17,2],
											rfperf6[16,2],
											rfperf6[15,2],
											rfperf7[9,2],
											rfperf7[17,2],
											rfperf7[16,2],
											rfperf7[15,2],
											rfperf8[9,2],
											rfperf8[17,2],
											rfperf8[16,2],
											rfperf8[15,2],
											rfperf9[9,2],
											rfperf9[17,2],
											rfperf9[16,2],
											rfperf9[15,2],
											rfperf10[9,2],
											rfperf10[17,2],
											rfperf10[16,2],
											rfperf10[15,2],
											rfperf11[9,2],
											rfperf11[17,2],
											rfperf11[16,2],
											rfperf11[15,2],
											rfperf12[9,2],
											rfperf12[17,2],
											rfperf12[16,2],
											rfperf12[15,2]),
							Metric = rep(c("Accuracy", "AUC", "F1-Score", "MCC"), 12),
							Resolution = c(rep("10kb", 12), rep("25kb", 12), rep("50kb", 12), rep("100kb", 12)),
							Predictor = rep(c(rep("OC", 4), rep("OP", 4), rep("Distance", 4)), 4))
distperftab$Metric <- factor(distperftab$Metric, levels = c("Accuracy", "AUC", "F1-Score", "MCC"))
distperftab$Resolution <- factor(distperftab$Resolution, levels = c("10kb","25kb","50kb","100kb"))
distperftab$Predictor <- factor(distperftab$Predictor, levels = c("OC", "OP", "Distance"))

p.distperfsbar <- ggplot(distperftab, aes(fill=Predictor, y=Performance, x=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
	facet_grid(Resolution ~ Metric) +
  ylab("Performance")+
	xlab("Predictor Type")+
  theme_bw() +
  guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
		legend.position="bottom")

#ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/p.distperfsbarline.png")
```

#Comparing performances across resolutions for RUS and distance

#Variable Importance Plots for distance predictors with ENET reduction

##5kb
###Random Under-Sampling
```{r}
rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/5kb/CHR1/rus/distance/enet/rfimpvars.rds")

rf5kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
					Importance = rowMeans(rfimpvars))
rf5kb <- rf5kb[order(rf5kb$Importance, decreasing=TRUE),]
rownames(rf) <- NULL

varimp.rf <- rf5kb$Importance
Labels <- as.character(rf5kb$Feature)
Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
varimp.rf.df.5kb <- cbind.data.frame(Feature=as.character(Labels),
                                 Importance=varimp.rf)
varimp.rf.df.5kb$Feature <- as.character(varimp.rf.df.5kb$Feature)							 
varimp.rf.df.5kb <-varimp.rf.df.5kb[order(varimp.rf.df.5kb$Importance),]
varimp.rf.df.5kb <- varimp.rf.df.5kb[(dim(varimp.rf.df.5kb)[1]-14):dim(varimp.rf.df.5kb)[1],]
varimp.rf.df.5kb$Feature <- factor(varimp.rf.df.5kb$Feature,
                                     levels=as.character(varimp.rf.df.5kb$Feature))

p.rf.5kb <- ggplot(varimp.rf.df.5kb, aes(x=Feature, y=Importance)) +
  xlab("Predictors") +
  ylab("Importance") +
  ggtitle("(A)") +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge",
           fill="red") +
  theme_minimal() +
  theme(axis.text=element_text(size=15),
        axis.title=element_text(size=20,face="bold")) +
  coord_flip()

  ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/5kb/p.rf.5kb.png")
```
##25kb
###Random Under-Sampling
```{r}
  rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/25kb/CHR1/rus/distance/enet/rfimpvars.rds")

rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
					Importance = rowMeans(rfimpvars))
rf <- rf[order(rf$Importance, decreasing=TRUE),]
rownames(rf) <- NULL

varimp.rf <- rf$Importance
Labels <- as.character(rf$Feature)
Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
varimp.rf.df.25kb <- cbind.data.frame(Feature=as.character(Labels),
                                 Importance=varimp.rf)
varimp.rf.df.25kb$Feature <- as.character(varimp.rf.df.25kb$Feature)							 
varimp.rf.df.25kb <-varimp.rf.df.25kb[order(varimp.rf.df.25kb$Importance),]
varimp.rf.df.25kb <- varimp.rf.df.25kb[(dim(varimp.rf.df.25kb)[1]-14):dim(varimp.rf.df.25kb)[1],]
varimp.rf.df.25kb$Feature <- factor(varimp.rf.df.25kb$Feature,
                                     levels=as.character(varimp.rf.df.25kb$Feature))

p.rf.25kb <- ggplot(varimp.rf.df.25kb, aes(x=Feature, y=Importance)) +
  xlab("Predictors") +
  ylab("Importance") +
  ggtitle("(B)") +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge",
           fill="blue") +
  theme_minimal() +
  theme(axis.text=element_text(size=15),
        axis.title=element_text(size=20,face="bold")) +
  coord_flip()

   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/25kb/p.rf.25kb.png")
```
##50kb
###Random Under-Sampling
```{r}
rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/50kb/CHR1/rus/distance/enet/rfimpvars.rds")

rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
					Importance = rowMeans(rfimpvars))
rf <- rf[order(rf$Importance, decreasing=TRUE),]
rownames(rf) <- NULL

varimp.rf <- rf$Importance
Labels <- as.character(rf$Feature)
Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
varimp.rf.df.50kb <- cbind.data.frame(Feature=as.character(Labels),
                                 Importance=varimp.rf)
varimp.rf.df.50kb$Feature <- as.character(varimp.rf.df.50kb$Feature)							 
varimp.rf.df.50kb <-varimp.rf.df.50kb[order(varimp.rf.df.50kb$Importance),]
varimp.rf.df.50kb <- varimp.rf.df.50kb[(dim(varimp.rf.df.50kb)[1]-14):dim(varimp.rf.df.50kb)[1],]
varimp.rf.df.50kb$Feature <- factor(varimp.rf.df.50kb$Feature,
                                     levels=as.character(varimp.rf.df.50kb$Feature))

p.rf.50kb <- ggplot(varimp.rf.df.50kb, aes(x=Feature, y=Importance)) +
  xlab("Predictors") +
  ylab("Importance") +
  ggtitle("(C)") +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge",
           fill="green") +
  theme_minimal() +
  theme(axis.text=element_text(size=15),
        axis.title=element_text(size=20,face="bold")) +
  coord_flip()

   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/50kb/p.rf.50kb.png")
```
##100kb
###Random Under-Sampling
```{r}
rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/100kb/CHR1/rus/distance/enet/rfimpvars.rds")

rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
					Importance = rowMeans(rfimpvars))
rf <- rf[order(rf$Importance, decreasing=TRUE),]
rownames(rf) <- NULL

varimp.rf <- rf$Importance
Labels <- as.character(rf$Feature)
Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
varimp.rf.df.100kb <- cbind.data.frame(Feature=as.character(Labels),
                                 Importance=varimp.rf)
varimp.rf.df.100kb$Feature <- as.character(varimp.rf.df.100kb$Feature)							 
varimp.rf.df.100kb <-varimp.rf.df.100kb[order(varimp.rf.df.100kb$Importance),]
#varimp.rf.df.100kb <- varimp.rf.df.100kb[(dim(varimp.rf.df.100kb)[1]-14):dim(varimp.rf.df.100kb)[1],]
varimp.rf.df.100kb$Feature <- factor(varimp.rf.df.100kb$Feature,
                                     levels=as.character(varimp.rf.df.100kb$Feature))

p.rf.100kb <- ggplot(varimp.rf.df.100kb, aes(x=Feature, y=Importance)) +
  xlab("Predictors") +
  ylab("Importance") +
  ggtitle("(D)") +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge",
           fill="orange") +
  theme_minimal() +
  theme(axis.text=element_text(size=15),
        axis.title=element_text(size=20,face="bold")) +
  coord_flip()

   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/100kb/p.rf.100kb.png")

allvarimps <- ggarrange(p.rf.5kb,p.rf.25kb,p.rf.50kb,p.rf.100kb, ncol=2, nrow=2)

ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/allvarimps.png")
```

#Network Analysis

```{r}
##venn diagram of top predictors 
#grid.newpage()
##vennp <- draw.triple.venn(area1 = 10, area2 = 10, area3 = 10, n12 = length(intersect(us,sm)), n23 = length(intersect(sm,km)), n13 = length(intersect(km,us)), 
##                 n123 = length(intersect(us,intersect(sm,km))), category = c("Under- \n Sampling", "SMOTE", "K-Medoids"), lty = "blank", 
##                 fill = c("red", "green", "blue"),cex=3,cat.cex = 3)
#
#vennp <- draw.pairwise.venn(length(varimp.rf.df.gm12878$Feature),
#						  length(varimp.rf.df.k562$Feature),
#						  length(intersect(varimp.rf.df.gm12878$Feature, varimp.rf.df.k562$Feature)),
#						  category = c("GM12878", "K562"),
#						  lty = "blank", 
#                          fill = c("red", "blue"),
#						  cex=3,
#						  cat.cex = 3,
#						  cat.pos = c(0,0),
#						  scaled = FALSE)

##Network Visualization between resolutions
rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/5kb/CHR1/rus/distance/enet/rfimpvars.rds")

rf5kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
					Importance = rowMeans(rfimpvars))
rownames(rf5kb) <- NULL
rf5kb$Feature <- as.character(rf5kb$Feature)
rf5kb$Feature[grep("Gm12878-", rf5kb$Feature)] <- gsub("Gm12878-","",rf5kb$Feature[grep("Gm12878-", rf5kb$Feature)])
rf5kb$Feature[grep("_dist", rf5kb$Feature)] <- gsub("_dist","",rf5kb$Feature[grep("_dist", rf5kb$Feature)])
rf5kb$Importance <- rf5kb$Importance/sum(rf5kb$Importance)

rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/25kb/CHR1/rus/distance/enet/rfimpvars.rds")

rf25kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
					Importance = rowMeans(rfimpvars))
rownames(rf25kb) <- NULL
rf25kb$Feature <- as.character(rf25kb$Feature)
rf25kb$Feature[grep("Gm12878-", rf25kb$Feature)] <- gsub("Gm12878-","",rf25kb$Feature[grep("Gm12878-", rf25kb$Feature)])
rf25kb$Feature[grep("_dist", rf25kb$Feature)] <- gsub("_dist","",rf25kb$Feature[grep("_dist", rf25kb$Feature)])
rf25kb$Importance <- rf25kb$Importance/sum(rf25kb$Importance)

rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/50kb/CHR1/rus/distance/enet/rfimpvars.rds")

rf50kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
					Importance = rowMeans(rfimpvars))
rownames(rf50kb) <- NULL
rf50kb$Feature <- as.character(rf50kb$Feature)
rf50kb$Feature[grep("Gm12878-", rf50kb$Feature)] <- gsub("Gm12878-","",rf50kb$Feature[grep("Gm12878-", rf50kb$Feature)])
rf50kb$Feature[grep("_dist", rf50kb$Feature)] <- gsub("_dist","",rf50kb$Feature[grep("_dist", rf50kb$Feature)])
rf50kb$Importance <- rf50kb$Importance/sum(rf50kb$Importance)

rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/100kb/CHR1/rus/distance/enet/rfimpvars.rds")

rf100kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
					Importance = rowMeans(rfimpvars))
rownames(rf100kb) <- NULL
rf100kb$Feature <- as.character(rf100kb$Feature)
rf100kb$Feature[grep("Gm12878-", rf100kb$Feature)] <- gsub("Gm12878-","",rf100kb$Feature[grep("Gm12878-", rf100kb$Feature)])
rf100kb$Feature[grep("_dist", rf100kb$Feature)] <- gsub("_dist","",rf100kb$Feature[grep("_dist", rf100kb$Feature)])
rf100kb$Importance <- rf100kb$Importance/sum(rf100kb$Importance)

commonannots <- union(rf5kb$Feature,union(rf25kb$Feature,union(rf50kb$Feature,rf100kb$Feature)))

networkmat <- matrix(ncol=4, nrow=length(commonannots), dimnames=list(commonannots, c("5kb", "25kb", "50kb", "100kb")))

networkmat[which(rownames(networkmat) %in% rf5kb$Feature),1] <- rf5kb$Importance
networkmat[which(rownames(networkmat) %in% rf25kb$Feature),2] <- rf25kb$Importance
networkmat[which(rownames(networkmat) %in% rf50kb$Feature),3] <- rf50kb$Importance
networkmat[which(rownames(networkmat) %in% rf100kb$Feature),4] <- rf100kb$Importance

networkmat[is.na(networkmat)] <- 0
networkmat <- networkmat*10

networkdf <- as.data.frame(networkmat)

net = network(networkdf,
              matrix.type = "bipartite",
              ignore.eval = FALSE,
              names.eval = "weights")

col = c("actor" = "green", "event" = "blue")

networkplot <- ggnet2(net, color = "mode", palette = col, edge.size = "weights", label=TRUE)

ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/networkplot.png")

networkdf <- as.data.frame(t(networkdf))

net = network(networkdf,
              matrix.type = "bipartite",
              ignore.eval = FALSE,
              names.eval = "weights")

col = c("actor" = "blue", "event" = "green")

networkplot2 <- ggnet2(net, color = "mode", palette = col, edge.size = "weights", label=TRUE)

ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/networkplot2.png")

```

### 2019-01-25 Scripts/changing_summary_in_caret.R

@@ -1,0 +1,78 @@
+library(caret)
+library(mlbench)
+library(Hmisc)
+library(randomForest)
+library(MLmetrics)
+
+
+#n <- 100
+#p <- 40
+#sigma <- 1
+#set.seed(1)
+#sim <- mlbench.friedman1(n, sd = sigma)
+#colnames(sim$x) <- c(paste("real", 1:5, sep = ""),
+#                     paste("bogus", 1:5, sep = ""))
+#bogus <- matrix(rnorm(n * p), nrow = n)
+#colnames(bogus) <- paste("bogus", 5+(1:ncol(bogus)), sep = "")
+#x <- cbind(sim$x, bogus)
+#y <- sim$y
+#normalization <- preProcess(x)
+#x <- predict(normalization, x)
+#x <- as.data.frame(x)
+#subsets <- c(1:5, 10, 15, 20, 25)
+
+#set.seed(10)
+
+#ctrl <- rfeControl(functions = lmFuncs,
+#                   method = "repeatedcv",
+#                   repeats = 5,
+#                   verbose = FALSE)
+
+#lmProfile <- rfe(x, y,
+#                 sizes = subsets,
+#                 rfeControl = ctrl)
+
+#lmProfile
+
+set.seed(346)
+dat <- twoClassSim(200, noiseVars = 5)
+
+f1 <- function(data, lev = NULL, model = NULL) {
+  f1_val <- F1_Score(y_pred = data$pred, y_true = data$obs, positive = lev[1])
+  c(F1 = f1_val)
+}
+
+rfRFE <-  list(summary = twoClassSummary,
+               #summary = f1,
+               fit = function(x, y, first, last, ...){
+                 library(randomForest)
+                 randomForest(x, y, importance = first, ntree=1000, mtry=sqrt(ncol(x)))
+               },
+               pred = function(object, x)  predict(object, x),
+               rank = function(object, x, y) {
+                 vimp <- varImp(object)
+                 vimp <- vimp[order(vimp$Overall,decreasing = TRUE),,drop = FALSE]
+                 vimp$var <- rownames(vimp)                  
+                 vimp
+               },
+               selectSize = pickSizeBest,
+               selectVar = pickVars)
+
+#rfRFE$summary <- f1
+
+ctrl <- rfeControl(functions = rfRFE,
+                   method = "repeatedcv",
+                   repeats = 5,
[…]

### 2019-01-26 Scripts/performances.rmd
collecting results for pr curves after rearranging flowchart

@@
 
-```{r}
-
-prall <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")
+#####None
+
+```{r}
+
+prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")
 
 #plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
 
@@
 
-####25kb
-
-```{r}
-
-prall <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")
+#####RUS
+
+```{r}
+prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
 
 #plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
 
@@
 
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROS
+
+```{r}
+prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####SMOTE
+
+```{r}
+prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROSE
+
+```{r}
+prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+####25kb
+
+#####None
+
+```{r}
+
+prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
 #legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
@@
 
-####50kb
-
-```{r}
-
-prall <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/op/RFE/prcurve.rds")
+#####RUS
+
+```{r}
+prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
 
 #plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
 
@@
 
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROS
+
+```{r}
+prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####SMOTE
+
+```{r}
+prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROSE
+
+```{r}
+prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+####50kb
+
+#####None
+
+```{r}
+
+prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
 #legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
@@
 
-####100kb
-
-```{r}
-
-prall <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/op/RFE/prcurve.rds")
+#####RUS
+
+```{r}
+prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
 
 #plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
 
@@
 
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROS
+
+```{r}
+prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####SMOTE
+
+```{r}
+prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROSE
+
+```{r}
+prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+####100kb
+
+#####None
+
+```{r}
+
+prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
 #legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
@@
 
+#####RUS
+
+```{r}
+prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROS
+
+```{r}
+prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####SMOTE
+
+```{r}
+prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROSE
+
+```{r}
+prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
 ###K562
@@
 
-```{r}
-prall <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")
+#####None
+
+```{r}
+
+prall_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")
 
 #plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
 
@@
 
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: )","All (AUPRC: )", "Percents (AUPRC: )", "Counts (AUPRC: )", "Baseline"),
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####RUS
+
+```{r}
+prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROS
+
+```{r}
+prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####SMOTE
+
+```{r}
+prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROSE
+
+```{r}
+prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+####25kb
+
+#####None
+
+```{r}
+
+prall_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
 #       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
@@
 
-####25kb
-
-```{r}
-prall <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")
+#####RUS
+
+```{r}
+prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
 
 #plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/test.rds")
+plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
 abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
 
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: )","All (AUPRC: )","Percents (AUPRC: )", "Counts (AUPRC: )", "Baseline"),
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
 #       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
@@
 
+#####ROS
+
+```{r}
+prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####SMOTE
+
+```{r}
+prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROSE
+
+```{r}
+prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
 ####50kb
 
-```{r}
-prall <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/op/RFE/prcurve.rds")
+#####None
+
+```{r}
+
+prall_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/op/RFE/prcurve.rds")
 
 #plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/test.rds")
+plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
 abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
 
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: )","All (AUPRC: )","Percents (AUPRC: )", "Counts (AUPRC: )", "Baseline"),
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
 #       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
@@
 
+#####RUS
+
+```{r}
+prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROS
+
+```{r}
+prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####SMOTE
+
+```{r}
+prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROSE
+
+```{r}
+prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
+#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
 ####100kb
 
-```{r}
-prall <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/op/RFE/prcurve.rds")
+#####None
+
+```{r}
+
+prall_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/op/RFE/prcurve.rds")
 
 #plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/test.rds")
+plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
 abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
 
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: )","All (AUPRC: )", "Percents (AUPRC: )", "Counts (AUPRC: )", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####RUS
+
+```{r}
+prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROS
+
+```{r}
+prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####SMOTE
+
+```{r}
+prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
+
+```
+
+#####ROSE
+
+```{r}
+prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
+plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
+lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
+lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
+lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
+
+test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
+
+#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
+#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
 

### 2019-01-29 Scripts/performances.rmd
aggregated results from prcurves for all balancing techniques

@@
 #10kb
-prall <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_10kb <- rbind.data.frame(prall$curve,
-                                prdist$curve,
-                                prop$curve,
-                                proc$curve,
-                                prall_k562$curve,
-                                prdist_k562$curve,
-                                prop_k562$curve,
-                                proc_k562$curve)
-names(prdata_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_10kb$Predictor <- c(rep("All", dim(prall$curve)[1]),
-                           rep("Distance", dim(prdist$curve)[1]),
-                           rep("OP", dim(prop$curve)[1]),
-                           rep("OC", dim(proc$curve)[1]),
-                           rep("All", dim(prall_k562$curve)[1]),
-                           rep("Distance", dim(prdist_k562$curve)[1]),
-                           rep("OP", dim(prop_k562$curve)[1]),
-                           rep("OC", dim(proc_k562$curve)[1]))
-prdata_10kb$CL <- c(rep("GM12878", (dim(prall$curve)[1]+
-                                      dim(prdist$curve)[1]+
-                                      dim(prop$curve)[1]+
-                                      dim(proc$curve)[1])),
-                    rep("K562", (dim(prall_k562$curve)[1]+
-                                      dim(prdist_k562$curve)[1]+
-                                      dim(prop_k562$curve)[1]+
-                                      dim(proc_k562$curve)[1])))
-prdata_10kb$Predictor <- factor(prdata_10kb$Predictor)
-prdata_10kb$CL <- factor(prdata_10kb$CL)
-
-prplot_10kb <- ggplot(prdata_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+##None
+prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")
+
+prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")
+
+prdata_None_10kb <- rbind.data.frame(prall_None$curve,
+                                prdist_None$curve,
+                                prop_None$curve,
+                                proc_None$curve,
+                                prall_None_k562$curve,
+                                prdist_None_k562$curve,
+                                prop_None_k562$curve,
+                                proc_None_k562$curve)
+names(prdata_None_10kb) <- c("Recall", "Precision", "Threshold")
+prdata_None_10kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
+                           rep("Distance", dim(prdist_None$curve)[1]),
+                           rep("OP", dim(prop_None$curve)[1]),
+                           rep("OC", dim(proc_None$curve)[1]),
+                           rep("All", dim(prall_None_k562$curve)[1]),
+                           rep("Distance", dim(prdist_None_k562$curve)[1]),
+                           rep("OP", dim(prop_None_k562$curve)[1]),
+                           rep("OC", dim(proc_None_k562$curve)[1]))
+prdata_None_10kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
+                                      dim(prdist_None$curve)[1]+
+                                      dim(prop_None$curve)[1]+
+                                      dim(proc_None$curve)[1])),
+                    rep("K562", (dim(prall_None_k562$curve)[1]+
+                                      dim(prdist_None_k562$curve)[1]+
+                                      dim(prop_None_k562$curve)[1]+
+                                      dim(proc_None_k562$curve)[1])))
+prdata_None_10kb$Predictor <- factor(prdata_None_10kb$Predictor)
+prdata_None_10kb$CL <- factor(prdata_None_10kb$CL)
+
+prplot_None_10kb <- ggplot(prdata_None_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
   geom_line(size=.75)+
@@
 
-#25kb
-prall <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_25kb <- rbind.data.frame(prall$curve,
-                                prdist$curve,
-                                prop$curve,
-                                proc$curve,
-                                prall_k562$curve,
-                                prdist_k562$curve,
-                                prop_k562$curve,
-                                proc_k562$curve)
-names(prdata_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_25kb$Predictor <- c(rep("All", dim(prall$curve)[1]),
-                           rep("Distance", dim(prdist$curve)[1]),
-                           rep("OP", dim(prop$curve)[1]),
-                           rep("OC", dim(proc$curve)[1]),
-                           rep("All", dim(prall_k562$curve)[1]),
-                           rep("Distance", dim(prdist_k562$curve)[1]),
-                           rep("OP", dim(prop_k562$curve)[1]),
-                           rep("OC", dim(proc_k562$curve)[1]))
-prdata_25kb$CL <- c(rep("GM12878", (dim(prall$curve)[1]+
-                                      dim(prdist$curve)[1]+
-                                      dim(prop$curve)[1]+
-                                      dim(proc$curve)[1])),
-                    rep("K562", (dim(prall_k562$curve)[1]+
-                                      dim(prdist_k562$curve)[1]+
-                                      dim(prop_k562$curve)[1]+
-                                      dim(proc_k562$curve)[1])))
-prdata_25kb$Predictor <- factor(prdata_25kb$Predictor)
-prdata_25kb$CL <- factor(prdata_25kb$CL)
-
-prplot_25kb <- ggplot(prdata_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+##RUS
+prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
+
+prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
+
+prdata_RUS_10kb <- rbind.data.frame(prall_RUS$curve,
+                                prdist_RUS$curve,
+                                prop_RUS$curve,
+                                proc_RUS$curve,
+                                prall_RUS_k562$curve,
+                                prdist_RUS_k562$curve,
+                                prop_RUS_k562$curve,
+                                proc_RUS_k562$curve)
+names(prdata_RUS_10kb) <- c("Recall", "Precision", "Threshold")
+prdata_RUS_10kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
+                           rep("Distance", dim(prdist_RUS$curve)[1]),
+                           rep("OP", dim(prop_RUS$curve)[1]),
+                           rep("OC", dim(proc_RUS$curve)[1]),
+                           rep("All", dim(prall_RUS_k562$curve)[1]),
+                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
+                           rep("OP", dim(prop_RUS_k562$curve)[1]),
+                           rep("OC", dim(proc_RUS_k562$curve)[1]))
+prdata_RUS_10kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
+                                      dim(prdist_RUS$curve)[1]+
+                                      dim(prop_RUS$curve)[1]+
+                                      dim(proc_RUS$curve)[1])),
+                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
+                                      dim(prdist_RUS_k562$curve)[1]+
+                                      dim(prop_RUS_k562$curve)[1]+
+                                      dim(proc_RUS_k562$curve)[1])))
+prdata_RUS_10kb$Predictor <- factor(prdata_RUS_10kb$Predictor)
+prdata_RUS_10kb$CL <- factor(prdata_RUS_10kb$CL)
+
+prplot_RUS_10kb <- ggplot(prdata_RUS_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
   geom_line(size=.75)+
@@
 
-#50kb
-prall <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_50kb <- rbind.data.frame(prall$curve,
-                                prdist$curve,
-                                prop$curve,
-                                proc$curve,
-                                prall_k562$curve,
-                                prdist_k562$curve,
-                                prop_k562$curve,
-                                proc_k562$curve)
-names(prdata_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_50kb$Predictor <- c(rep("All", dim(prall$curve)[1]),
-                           rep("Distance", dim(prdist$curve)[1]),
-                           rep("OP", dim(prop$curve)[1]),
-                           rep("OC", dim(proc$curve)[1]),
-                           rep("All", dim(prall_k562$curve)[1]),
-                           rep("Distance", dim(prdist_k562$curve)[1]),
-                           rep("OP", dim(prop_k562$curve)[1]),
-                           rep("OC", dim(proc_k562$curve)[1]))
-prdata_50kb$CL <- c(rep("GM12878", (dim(prall$curve)[1]+
-                                      dim(prdist$curve)[1]+
-                                      dim(prop$curve)[1]+
-                                      dim(proc$curve)[1])),
-                    rep("K562", (dim(prall_k562$curve)[1]+
-                                      dim(prdist_k562$curve)[1]+
-                                      dim(prop_k562$curve)[1]+
-                                      dim(proc_k562$curve)[1])))
-prdata_50kb$Predictor <- factor(prdata_50kb$Predictor)
-prdata_50kb$CL <- factor(prdata_50kb$CL)
-
-prplot_50kb <- ggplot(prdata_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+##ROS
+prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+prdata_ROS_10kb <- rbind.data.frame(prall_ROS$curve,
+                                prdist_ROS$curve,
+                                prop_ROS$curve,
+                                proc_ROS$curve,
+                                prall_ROS_k562$curve,
+                                prdist_ROS_k562$curve,
+                                prop_ROS_k562$curve,
+                                proc_ROS_k562$curve)
+names(prdata_ROS_10kb) <- c("Recall", "Precision", "Threshold")
+prdata_ROS_10kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
+                           rep("Distance", dim(prdist_ROS$curve)[1]),
+                           rep("OP", dim(prop_ROS$curve)[1]),
+                           rep("OC", dim(proc_ROS$curve)[1]),
+                           rep("All", dim(prall_ROS_k562$curve)[1]),
+                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
+                           rep("OP", dim(prop_ROS_k562$curve)[1]),
+                           rep("OC", dim(proc_ROS_k562$curve)[1]))
+prdata_ROS_10kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
+                                      dim(prdist_ROS$curve)[1]+
+                                      dim(prop_ROS$curve)[1]+
+                                      dim(proc_ROS$curve)[1])),
+                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
+                                      dim(prdist_ROS_k562$curve)[1]+
+                                      dim(prop_ROS_k562$curve)[1]+
+                                      dim(proc_ROS_k562$curve)[1])))
+prdata_ROS_10kb$Predictor <- factor(prdata_ROS_10kb$Predictor)
+prdata_ROS_10kb$CL <- factor(prdata_ROS_10kb$CL)
+
+prplot_ROS_10kb <- ggplot(prdata_ROS_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
   geom_line(size=.75)+
@@
 
-#100kb
-prall <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_100kb <- rbind.data.frame(prall$curve,
-                                prdist$curve,
-                                prop$curve,
-                                proc$curve,
-                                prall_k562$curve,
-                                prdist_k562$curve,
-                                prop_k562$curve,
-                                proc_k562$curve)
-names(prdata_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_100kb$Predictor <- c(rep("All", dim(prall$curve)[1]),
-                           rep("Distance", dim(prdist$curve)[1]),
-                           rep("OP", dim(prop$curve)[1]),
-                           rep("OC", dim(proc$curve)[1]),
-                           rep("All", dim(prall_k562$curve)[1]),
-                           rep("Distance", dim(prdist_k562$curve)[1]),
-                           rep("OP", dim(prop_k562$curve)[1]),
-                           rep("OC", dim(proc_k562$curve)[1]))
-prdata_100kb$CL <- c(rep("GM12878", (dim(prall$curve)[1]+
-                                      dim(prdist$curve)[1]+
-                                      dim(prop$curve)[1]+
-                                      dim(proc$curve)[1])),
-                    rep("K562", (dim(prall_k562$curve)[1]+
-                                      dim(prdist_k562$curve)[1]+
-                                      dim(prop_k562$curve)[1]+
-                                      dim(proc_k562$curve)[1])))
-prdata_100kb$Predictor <- factor(prdata_100kb$Predictor)
-prdata_100kb$CL <- factor(prdata_100kb$CL)
-
-prplot_100kb <- ggplot(prdata_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+##SMOTE
+prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+prdata_SMOTE_10kb <- rbind.data.frame(prall_SMOTE$curve,
+                                prdist_SMOTE$curve,
+                                prop_SMOTE$curve,
+                                proc_SMOTE$curve,
+                                prall_SMOTE_k562$curve,
+                                prdist_SMOTE_k562$curve,
+                                prop_SMOTE_k562$curve,
+                                proc_SMOTE_k562$curve)
+names(prdata_SMOTE_10kb) <- c("Recall", "Precision", "Threshold")
+prdata_SMOTE_10kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
+                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
+                           rep("OP", dim(prop_SMOTE$curve)[1]),
+                           rep("OC", dim(proc_SMOTE$curve)[1]),
+                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
+                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
+                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
+                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
+prdata_SMOTE_10kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
+                                      dim(prdist_SMOTE$curve)[1]+
+                                      dim(prop_SMOTE$curve)[1]+
+                                      dim(proc_SMOTE$curve)[1])),
+                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
+                                      dim(prdist_SMOTE_k562$curve)[1]+
+                                      dim(prop_SMOTE_k562$curve)[1]+
+                                      dim(proc_SMOTE_k562$curve)[1])))
+prdata_SMOTE_10kb$Predictor <- factor(prdata_SMOTE_10kb$Predictor)
+prdata_SMOTE_10kb$CL <- factor(prdata_SMOTE_10kb$CL)
+
+prplot_SMOTE_10kb <- ggplot(prdata_SMOTE_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
   geom_line(size=.75)+
@@
 
-ggarrange(prplot_25kb, prplot_50kb, prplot_100kb,
-          nrow=2,ncol=2,
+##ROSE
+prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+prdata_ROSE_10kb <- rbind.data.frame(prall_ROSE$curve,
+                                prdist_ROSE$curve,
+                                prop_ROSE$curve,
+                                proc_ROSE$curve,
+                                prall_ROSE_k562$curve,
+                                prdist_ROSE_k562$curve,
+                                prop_ROSE_k562$curve,
+                                proc_ROSE_k562$curve)
+names(prdata_ROSE_10kb) <- c("Recall", "Precision", "Threshold")
+prdata_ROSE_10kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
+                           rep("Distance", dim(prdist_ROSE$curve)[1]),
+                           rep("OP", dim(prop_ROSE$curve)[1]),
+                           rep("OC", dim(proc_ROSE$curve)[1]),
+                           rep("All", dim(prall_ROSE_k562$curve)[1]),
+                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
+                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
+                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
+prdata_ROSE_10kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
+                                      dim(prdist_ROSE$curve)[1]+
+                                      dim(prop_ROSE$curve)[1]+
+                                      dim(proc_ROSE$curve)[1])),
+                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
+                                      dim(prdist_ROSE_k562$curve)[1]+
+                                      dim(prop_ROSE_k562$curve)[1]+
+                                      dim(proc_ROSE_k562$curve)[1])))
+prdata_ROSE_10kb$Predictor <- factor(prdata_ROSE_10kb$Predictor)
+prdata_ROSE_10kb$CL <- factor(prdata_ROSE_10kb$CL)
+
+prplot_ROSE_10kb <- ggplot(prdata_ROSE_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+##Collecting 10kb plots
+ggarrange(prplot_None_10kb,
+          prplot_RUS_10kb,
+          prplot_ROS_10kb,
+          prplot_SMOTE_10kb,
+          prplot_ROSE_10kb,
+          nrow=3,ncol=2,
           common.legend = TRUE, legend = "right")
+
+#######################################################################################
+
+#25kb
+##None
+prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")
+
+prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")
+
+prdata_None_25kb <- rbind.data.frame(prall_None$curve,
+                                prdist_None$curve,
+                                prop_None$curve,
+                                proc_None$curve,
+                                prall_None_k562$curve,
+                                prdist_None_k562$curve,
+                                prop_None_k562$curve,
+                                proc_None_k562$curve)
+names(prdata_None_25kb) <- c("Recall", "Precision", "Threshold")
+prdata_None_25kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
+                           rep("Distance", dim(prdist_None$curve)[1]),
+                           rep("OP", dim(prop_None$curve)[1]),
+                           rep("OC", dim(proc_None$curve)[1]),
+                           rep("All", dim(prall_None_k562$curve)[1]),
+                           rep("Distance", dim(prdist_None_k562$curve)[1]),
+                           rep("OP", dim(prop_None_k562$curve)[1]),
+                           rep("OC", dim(proc_None_k562$curve)[1]))
+prdata_None_25kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
+                                      dim(prdist_None$curve)[1]+
+                                      dim(prop_None$curve)[1]+
+                                      dim(proc_None$curve)[1])),
+                    rep("K562", (dim(prall_None_k562$curve)[1]+
+                                      dim(prdist_None_k562$curve)[1]+
+                                      dim(prop_None_k562$curve)[1]+
+                                      dim(proc_None_k562$curve)[1])))
+prdata_None_25kb$Predictor <- factor(prdata_None_25kb$Predictor)
+prdata_None_25kb$CL <- factor(prdata_None_25kb$CL)
+
+prplot_None_25kb <- ggplot(prdata_None_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+##RUS
+prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
+
+prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
+
+prdata_RUS_25kb <- rbind.data.frame(prall_RUS$curve,
+                                prdist_RUS$curve,
+                                prop_RUS$curve,
+                                proc_RUS$curve,
+                                prall_RUS_k562$curve,
+                                prdist_RUS_k562$curve,
+                                prop_RUS_k562$curve,
+                                proc_RUS_k562$curve)
+names(prdata_RUS_25kb) <- c("Recall", "Precision", "Threshold")
+prdata_RUS_25kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
+                           rep("Distance", dim(prdist_RUS$curve)[1]),
+                           rep("OP", dim(prop_RUS$curve)[1]),
+                           rep("OC", dim(proc_RUS$curve)[1]),
+                           rep("All", dim(prall_RUS_k562$curve)[1]),
+                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
+                           rep("OP", dim(prop_RUS_k562$curve)[1]),
+                           rep("OC", dim(proc_RUS_k562$curve)[1]))
+prdata_RUS_25kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
+                                      dim(prdist_RUS$curve)[1]+
+                                      dim(prop_RUS$curve)[1]+
+                                      dim(proc_RUS$curve)[1])),
+                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
+                                      dim(prdist_RUS_k562$curve)[1]+
+                                      dim(prop_RUS_k562$curve)[1]+
+                                      dim(proc_RUS_k562$curve)[1])))
+prdata_RUS_25kb$Predictor <- factor(prdata_RUS_25kb$Predictor)
+prdata_RUS_25kb$CL <- factor(prdata_RUS_25kb$CL)
+
+prplot_RUS_25kb <- ggplot(prdata_RUS_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+##ROS
+prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+prdata_ROS_25kb <- rbind.data.frame(prall_ROS$curve,
+                                prdist_ROS$curve,
+                                prop_ROS$curve,
+                                proc_ROS$curve,
+                                prall_ROS_k562$curve,
+                                prdist_ROS_k562$curve,
+                                prop_ROS_k562$curve,
+                                proc_ROS_k562$curve)
+names(prdata_ROS_25kb) <- c("Recall", "Precision", "Threshold")
+prdata_ROS_25kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
+                           rep("Distance", dim(prdist_ROS$curve)[1]),
+                           rep("OP", dim(prop_ROS$curve)[1]),
+                           rep("OC", dim(proc_ROS$curve)[1]),
+                           rep("All", dim(prall_ROS_k562$curve)[1]),
+                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
+                           rep("OP", dim(prop_ROS_k562$curve)[1]),
+                           rep("OC", dim(proc_ROS_k562$curve)[1]))
+prdata_ROS_25kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
+                                      dim(prdist_ROS$curve)[1]+
+                                      dim(prop_ROS$curve)[1]+
+                                      dim(proc_ROS$curve)[1])),
+                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
+                                      dim(prdist_ROS_k562$curve)[1]+
+                                      dim(prop_ROS_k562$curve)[1]+
+                                      dim(proc_ROS_k562$curve)[1])))
+prdata_ROS_25kb$Predictor <- factor(prdata_ROS_25kb$Predictor)
+prdata_ROS_25kb$CL <- factor(prdata_ROS_25kb$CL)
+
+prplot_ROS_25kb <- ggplot(prdata_ROS_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+##SMOTE
+prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+prdata_SMOTE_25kb <- rbind.data.frame(prall_SMOTE$curve,
+                                prdist_SMOTE$curve,
+                                prop_SMOTE$curve,
+                                proc_SMOTE$curve,
+                                prall_SMOTE_k562$curve,
+                                prdist_SMOTE_k562$curve,
+                                prop_SMOTE_k562$curve,
+                                proc_SMOTE_k562$curve)
+names(prdata_SMOTE_25kb) <- c("Recall", "Precision", "Threshold")
+prdata_SMOTE_25kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
+                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
+                           rep("OP", dim(prop_SMOTE$curve)[1]),
+                           rep("OC", dim(proc_SMOTE$curve)[1]),
+                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
+                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
+                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
+                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
+prdata_SMOTE_25kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
+                                      dim(prdist_SMOTE$curve)[1]+
+                                      dim(prop_SMOTE$curve)[1]+
+                                      dim(proc_SMOTE$curve)[1])),
+                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
+                                      dim(prdist_SMOTE_k562$curve)[1]+
+                                      dim(prop_SMOTE_k562$curve)[1]+
+                                      dim(proc_SMOTE_k562$curve)[1])))
+prdata_SMOTE_25kb$Predictor <- factor(prdata_SMOTE_25kb$Predictor)
+prdata_SMOTE_25kb$CL <- factor(prdata_SMOTE_25kb$CL)
+
+prplot_SMOTE_25kb <- ggplot(prdata_SMOTE_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+##ROSE
+prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+prdata_ROSE_25kb <- rbind.data.frame(prall_ROSE$curve,
+                                prdist_ROSE$curve,
+                                prop_ROSE$curve,
+                                proc_ROSE$curve,
+                                prall_ROSE_k562$curve,
+                                prdist_ROSE_k562$curve,
+                                prop_ROSE_k562$curve,
+                                proc_ROSE_k562$curve)
+names(prdata_ROSE_25kb) <- c("Recall", "Precision", "Threshold")
+prdata_ROSE_25kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
+                           rep("Distance", dim(prdist_ROSE$curve)[1]),
+                           rep("OP", dim(prop_ROSE$curve)[1]),
+                           rep("OC", dim(proc_ROSE$curve)[1]),
+                           rep("All", dim(prall_ROSE_k562$curve)[1]),
+                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
+                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
+                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
+prdata_ROSE_25kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
+                                      dim(prdist_ROSE$curve)[1]+
+                                      dim(prop_ROSE$curve)[1]+
+                                      dim(proc_ROSE$curve)[1])),
+                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
+                                      dim(prdist_ROSE_k562$curve)[1]+
+                                      dim(prop_ROSE_k562$curve)[1]+
+                                      dim(proc_ROSE_k562$curve)[1])))
+prdata_ROSE_25kb$Predictor <- factor(prdata_ROSE_25kb$Predictor)
+prdata_ROSE_25kb$CL <- factor(prdata_ROSE_25kb$CL)
+
+prplot_ROSE_25kb <- ggplot(prdata_ROSE_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+###############################################################################
+
+#50kb
+##None
+prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/op/RFE/prcurve.rds")
+
+prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/op/RFE/prcurve.rds")
+
+prdata_None_50kb <- rbind.data.frame(prall_None$curve,
+                                prdist_None$curve,
+                                prop_None$curve,
+                                proc_None$curve,
+                                prall_None_k562$curve,
+                                prdist_None_k562$curve,
+                                prop_None_k562$curve,
+                                proc_None_k562$curve)
+names(prdata_None_50kb) <- c("Recall", "Precision", "Threshold")
+prdata_None_50kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
+                           rep("Distance", dim(prdist_None$curve)[1]),
+                           rep("OP", dim(prop_None$curve)[1]),
+                           rep("OC", dim(proc_None$curve)[1]),
+                           rep("All", dim(prall_None_k562$curve)[1]),
+                           rep("Distance", dim(prdist_None_k562$curve)[1]),
+                           rep("OP", dim(prop_None_k562$curve)[1]),
+                           rep("OC", dim(proc_None_k562$curve)[1]))
+prdata_None_50kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
+                                      dim(prdist_None$curve)[1]+
+                                      dim(prop_None$curve)[1]+
+                                      dim(proc_None$curve)[1])),
+                    rep("K562", (dim(prall_None_k562$curve)[1]+
+                                      dim(prdist_None_k562$curve)[1]+
+                                      dim(prop_None_k562$curve)[1]+
+                                      dim(proc_None_k562$curve)[1])))
+prdata_None_50kb$Predictor <- factor(prdata_None_50kb$Predictor)
+prdata_None_50kb$CL <- factor(prdata_None_50kb$CL)
+
+prplot_None_50kb <- ggplot(prdata_None_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+##RUS
+prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
+
+prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
+
+prdata_RUS_50kb <- rbind.data.frame(prall_RUS$curve,
+                                prdist_RUS$curve,
+                                prop_RUS$curve,
+                                proc_RUS$curve,
+                                prall_RUS_k562$curve,
+                                prdist_RUS_k562$curve,
+                                prop_RUS_k562$curve,
+                                proc_RUS_k562$curve)
+names(prdata_RUS_50kb) <- c("Recall", "Precision", "Threshold")
+prdata_RUS_50kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
+                           rep("Distance", dim(prdist_RUS$curve)[1]),
+                           rep("OP", dim(prop_RUS$curve)[1]),
+                           rep("OC", dim(proc_RUS$curve)[1]),
+                           rep("All", dim(prall_RUS_k562$curve)[1]),
+                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
+                           rep("OP", dim(prop_RUS_k562$curve)[1]),
+                           rep("OC", dim(proc_RUS_k562$curve)[1]))
+prdata_RUS_50kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
+                                      dim(prdist_RUS$curve)[1]+
+                                      dim(prop_RUS$curve)[1]+
+                                      dim(proc_RUS$curve)[1])),
+                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
+                                      dim(prdist_RUS_k562$curve)[1]+
+                                      dim(prop_RUS_k562$curve)[1]+
+                                      dim(proc_RUS_k562$curve)[1])))
+prdata_RUS_50kb$Predictor <- factor(prdata_RUS_50kb$Predictor)
+prdata_RUS_50kb$CL <- factor(prdata_RUS_50kb$CL)
+
+prplot_RUS_50kb <- ggplot(prdata_RUS_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+##ROS
+prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+prdata_ROS_50kb <- rbind.data.frame(prall_ROS$curve,
+                                prdist_ROS$curve,
+                                prop_ROS$curve,
+                                proc_ROS$curve,
+                                prall_ROS_k562$curve,
+                                prdist_ROS_k562$curve,
+                                prop_ROS_k562$curve,
+                                proc_ROS_k562$curve)
+names(prdata_ROS_50kb) <- c("Recall", "Precision", "Threshold")
+prdata_ROS_50kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
+                           rep("Distance", dim(prdist_ROS$curve)[1]),
+                           rep("OP", dim(prop_ROS$curve)[1]),
+                           rep("OC", dim(proc_ROS$curve)[1]),
+                           rep("All", dim(prall_ROS_k562$curve)[1]),
+                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
+                           rep("OP", dim(prop_ROS_k562$curve)[1]),
+                           rep("OC", dim(proc_ROS_k562$curve)[1]))
+prdata_ROS_50kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
+                                      dim(prdist_ROS$curve)[1]+
+                                      dim(prop_ROS$curve)[1]+
+                                      dim(proc_ROS$curve)[1])),
+                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
+                                      dim(prdist_ROS_k562$curve)[1]+
+                                      dim(prop_ROS_k562$curve)[1]+
+                                      dim(proc_ROS_k562$curve)[1])))
+prdata_ROS_50kb$Predictor <- factor(prdata_ROS_50kb$Predictor)
+prdata_ROS_50kb$CL <- factor(prdata_ROS_50kb$CL)
+
+prplot_ROS_50kb <- ggplot(prdata_ROS_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+##SMOTE
+prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+prdata_SMOTE_50kb <- rbind.data.frame(prall_SMOTE$curve,
+                                prdist_SMOTE$curve,
+                                prop_SMOTE$curve,
+                                proc_SMOTE$curve,
+                                prall_SMOTE_k562$curve,
+                                prdist_SMOTE_k562$curve,
+                                prop_SMOTE_k562$curve,
+                                proc_SMOTE_k562$curve)
+names(prdata_SMOTE_50kb) <- c("Recall", "Precision", "Threshold")
+prdata_SMOTE_50kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
+                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
+                           rep("OP", dim(prop_SMOTE$curve)[1]),
+                           rep("OC", dim(proc_SMOTE$curve)[1]),
+                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
+                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
+                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
+                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
+prdata_SMOTE_50kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
+                                      dim(prdist_SMOTE$curve)[1]+
+                                      dim(prop_SMOTE$curve)[1]+
+                                      dim(proc_SMOTE$curve)[1])),
+                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
+                                      dim(prdist_SMOTE_k562$curve)[1]+
+                                      dim(prop_SMOTE_k562$curve)[1]+
+                                      dim(proc_SMOTE_k562$curve)[1])))
+prdata_SMOTE_50kb$Predictor <- factor(prdata_SMOTE_50kb$Predictor)
+prdata_SMOTE_50kb$CL <- factor(prdata_SMOTE_50kb$CL)
+
+prplot_SMOTE_50kb <- ggplot(prdata_SMOTE_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+##ROSE
+prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+prdata_ROSE_50kb <- rbind.data.frame(prall_ROSE$curve,
+                                prdist_ROSE$curve,
+                                prop_ROSE$curve,
+                                proc_ROSE$curve,
+                                prall_ROSE_k562$curve,
+                                prdist_ROSE_k562$curve,
+                                prop_ROSE_k562$curve,
+                                proc_ROSE_k562$curve)
+names(prdata_ROSE_50kb) <- c("Recall", "Precision", "Threshold")
+prdata_ROSE_50kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
+                           rep("Distance", dim(prdist_ROSE$curve)[1]),
+                           rep("OP", dim(prop_ROSE$curve)[1]),
+                           rep("OC", dim(proc_ROSE$curve)[1]),
+                           rep("All", dim(prall_ROSE_k562$curve)[1]),
+                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
+                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
+                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
+prdata_ROSE_50kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
+                                      dim(prdist_ROSE$curve)[1]+
+                                      dim(prop_ROSE$curve)[1]+
+                                      dim(proc_ROSE$curve)[1])),
+                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
+                                      dim(prdist_ROSE_k562$curve)[1]+
+                                      dim(prop_ROSE_k562$curve)[1]+
+                                      dim(proc_ROSE_k562$curve)[1])))
+prdata_ROSE_50kb$Predictor <- factor(prdata_ROSE_50kb$Predictor)
+prdata_ROSE_50kb$CL <- factor(prdata_ROSE_50kb$CL)
+
+prplot_ROSE_50kb <- ggplot(prdata_ROSE_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+###########################################################################
+
+#100kb
+##None
+prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/op/RFE/prcurve.rds")
+
+prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")
+prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
+proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/oc/RFE/prcurve.rds")
+prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/op/RFE/prcurve.rds")
+
+prdata_None_100kb <- rbind.data.frame(prall_None$curve,
+                                prdist_None$curve,
+                                prop_None$curve,
+                                proc_None$curve,
+                                prall_None_k562$curve,
+                                prdist_None_k562$curve,
+                                prop_None_k562$curve,
+                                proc_None_k562$curve)
+names(prdata_None_100kb) <- c("Recall", "Precision", "Threshold")
+prdata_None_100kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
+                           rep("Distance", dim(prdist_None$curve)[1]),
+                           rep("OP", dim(prop_None$curve)[1]),
+                           rep("OC", dim(proc_None$curve)[1]),
+                           rep("All", dim(prall_None_k562$curve)[1]),
+                           rep("Distance", dim(prdist_None_k562$curve)[1]),
+                           rep("OP", dim(prop_None_k562$curve)[1]),
+                           rep("OC", dim(proc_None_k562$curve)[1]))
+prdata_None_100kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
+                                      dim(prdist_None$curve)[1]+
+                                      dim(prop_None$curve)[1]+
+                                      dim(proc_None$curve)[1])),
+                    rep("K562", (dim(prall_None_k562$curve)[1]+
+                                      dim(prdist_None_k562$curve)[1]+
+                                      dim(prop_None_k562$curve)[1]+
+                                      dim(proc_None_k562$curve)[1])))
+prdata_None_100kb$Predictor <- factor(prdata_None_100kb$Predictor)
+prdata_None_100kb$CL <- factor(prdata_None_100kb$CL)
+
+prplot_None_100kb <- ggplot(prdata_None_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+##RUS
+prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
+
+prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
+prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
+proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
+prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
+
+prdata_RUS_100kb <- rbind.data.frame(prall_RUS$curve,
+                                prdist_RUS$curve,
+                                prop_RUS$curve,
+                                proc_RUS$curve,
+                                prall_RUS_k562$curve,
+                                prdist_RUS_k562$curve,
+                                prop_RUS_k562$curve,
+                                proc_RUS_k562$curve)
+names(prdata_RUS_100kb) <- c("Recall", "Precision", "Threshold")
+prdata_RUS_100kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
+                           rep("Distance", dim(prdist_RUS$curve)[1]),
+                           rep("OP", dim(prop_RUS$curve)[1]),
+                           rep("OC", dim(proc_RUS$curve)[1]),
+                           rep("All", dim(prall_RUS_k562$curve)[1]),
+                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
+                           rep("OP", dim(prop_RUS_k562$curve)[1]),
+                           rep("OC", dim(proc_RUS_k562$curve)[1]))
+prdata_RUS_100kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
+                                      dim(prdist_RUS$curve)[1]+
+                                      dim(prop_RUS$curve)[1]+
+                                      dim(proc_RUS$curve)[1])),
+                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
+                                      dim(prdist_RUS_k562$curve)[1]+
+                                      dim(prop_RUS_k562$curve)[1]+
+                                      dim(proc_RUS_k562$curve)[1])))
+prdata_RUS_100kb$Predictor <- factor(prdata_RUS_100kb$Predictor)
+prdata_RUS_100kb$CL <- factor(prdata_RUS_100kb$CL)
+
+prplot_RUS_100kb <- ggplot(prdata_RUS_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+##ROS
+prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
+prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
+proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
+prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
+
+prdata_ROS_100kb <- rbind.data.frame(prall_ROS$curve,
+                                prdist_ROS$curve,
+                                prop_ROS$curve,
+                                proc_ROS$curve,
+                                prall_ROS_k562$curve,
+                                prdist_ROS_k562$curve,
+                                prop_ROS_k562$curve,
+                                proc_ROS_k562$curve)
+names(prdata_ROS_100kb) <- c("Recall", "Precision", "Threshold")
+prdata_ROS_100kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
+                           rep("Distance", dim(prdist_ROS$curve)[1]),
+                           rep("OP", dim(prop_ROS$curve)[1]),
+                           rep("OC", dim(proc_ROS$curve)[1]),
+                           rep("All", dim(prall_ROS_k562$curve)[1]),
+                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
+                           rep("OP", dim(prop_ROS_k562$curve)[1]),
+                           rep("OC", dim(proc_ROS_k562$curve)[1]))
+prdata_ROS_100kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
+                                      dim(prdist_ROS$curve)[1]+
+                                      dim(prop_ROS$curve)[1]+
+                                      dim(proc_ROS$curve)[1])),
+                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
+                                      dim(prdist_ROS_k562$curve)[1]+
+                                      dim(prop_ROS_k562$curve)[1]+
+                                      dim(proc_ROS_k562$curve)[1])))
+prdata_ROS_100kb$Predictor <- factor(prdata_ROS_100kb$Predictor)
+prdata_ROS_100kb$CL <- factor(prdata_ROS_100kb$CL)
+
+prplot_ROS_100kb <- ggplot(prdata_ROS_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+##SMOTE
+prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
+prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
+proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
+prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
+
+prdata_SMOTE_100kb <- rbind.data.frame(prall_SMOTE$curve,
+                                prdist_SMOTE$curve,
+                                prop_SMOTE$curve,
+                                proc_SMOTE$curve,
+                                prall_SMOTE_k562$curve,
+                                prdist_SMOTE_k562$curve,
+                                prop_SMOTE_k562$curve,
+                                proc_SMOTE_k562$curve)
+names(prdata_SMOTE_100kb) <- c("Recall", "Precision", "Threshold")
+prdata_SMOTE_100kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
+                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
+                           rep("OP", dim(prop_SMOTE$curve)[1]),
+                           rep("OC", dim(proc_SMOTE$curve)[1]),
+                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
+                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
+                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
+                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
+prdata_SMOTE_100kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
+                                      dim(prdist_SMOTE$curve)[1]+
+                                      dim(prop_SMOTE$curve)[1]+
+                                      dim(proc_SMOTE$curve)[1])),
+                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
+                                      dim(prdist_SMOTE_k562$curve)[1]+
+                                      dim(prop_SMOTE_k562$curve)[1]+
+                                      dim(proc_SMOTE_k562$curve)[1])))
+prdata_SMOTE_100kb$Predictor <- factor(prdata_SMOTE_100kb$Predictor)
+prdata_SMOTE_100kb$CL <- factor(prdata_SMOTE_100kb$CL)
+
+prplot_SMOTE_100kb <- ggplot(prdata_SMOTE_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+##ROSE
+prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
+prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
+proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
+prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
+
+prdata_ROSE_100kb <- rbind.data.frame(prall_ROSE$curve,
+                                prdist_ROSE$curve,
+                                prop_ROSE$curve,
+                                proc_ROSE$curve,
+                                prall_ROSE_k562$curve,
+                                prdist_ROSE_k562$curve,
+                                prop_ROSE_k562$curve,
+                                proc_ROSE_k562$curve)
+names(prdata_ROSE_100kb) <- c("Recall", "Precision", "Threshold")
+prdata_ROSE_100kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
+                           rep("Distance", dim(prdist_ROSE$curve)[1]),
+                           rep("OP", dim(prop_ROSE$curve)[1]),
+                           rep("OC", dim(proc_ROSE$curve)[1]),
+                           rep("All", dim(prall_ROSE_k562$curve)[1]),
+                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
+                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
+                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
+prdata_ROSE_100kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
+                                      dim(prdist_ROSE$curve)[1]+
+                                      dim(prop_ROSE$curve)[1]+
+                                      dim(proc_ROSE$curve)[1])),
+                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
+                                      dim(prdist_ROSE_k562$curve)[1]+
+                                      dim(prop_ROSE_k562$curve)[1]+
+                                      dim(proc_ROSE_k562$curve)[1])))
+prdata_ROSE_100kb$Predictor <- factor(prdata_ROSE_100kb$Predictor)
+prdata_ROSE_100kb$CL <- factor(prdata_ROSE_100kb$CL)
+
+prplot_ROSE_100kb <- ggplot(prdata_ROSE_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
+  geom_line(size=.75)+
+  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
+  scale_color_discrete(name = "Predictor Type") +
+  theme_minimal()+
+  theme_bw()
+
+###############################################################
+
+##Collecting 25kb, 50kb, and 100kb plots
+
+ggarrange(prplot_None_25kb, prplot_None_50kb, prplot_None_100kb,
+          prplot_RUS_25kb, prplot_RUS_50kb, prplot_RUS_100kb,
+          prplot_ROS_25kb, prplot_ROS_50kb, prplot_ROS_100kb,
+          prplot_SMOTE_25kb, prplot_SMOTE_50kb, prplot_SMOTE_100kb,
+          prplot_ROSE_25kb, prplot_ROSE_50kb, prplot_ROSE_100kb,
+          ncol=3,
+          nrow=5,
+          common.legend = TRUE,
+          legend = "right")
 ```

### 2019-01-29 Scripts/performances.rmd
aggregating rfe plots from all balancing techniques

@@
 
+##Tables of AUPRC
+
 ## RFE
 
-###GM12878
-
-####10kb
-
-```{r}
-#rfeModel_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/rfeModel_all.rds")
-rfeModel_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
-#rfeModel_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/RFE/rfeModel_op.rds")
-
-#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)
-
-#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
-#                                 rep("Distance", nrow(rfeModel_dist$results)),
-#                                 rep("OC", nrow(rfeModel_oc$results)),
-#                                 rep("OP", nrow(rfeModel_op$results)))
-
-#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)
-
-resampdata_10kb <- rfeModel_dist$results[1:6,]
-
-pt10kb <- ggplot(resampdata_10kb, aes(x=Variables, y=AUPRC)) +
-  geom_point()+
+###10kb
+
+```{r}
+rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
+rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
+
+rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
+rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
+
+#None
+resampdata_None_10kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
+resampdata_None_10kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
+                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
+
+rfeplot_None_10kb <- ggplot(resampdata_None_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
   geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
   scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64"), 
-                   labels=c("2", "4", "8", "16", "32", "64"), 
-                   limits=as.character(c(1:64)))+
-  theme_minimal()+
-  ylim(0,.5)
-
-```
-
-####25kb
-
-```{r}
-#rfeModel_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/rfeModel_all.rds")
-rfeModel_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
-#rfeModel_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/RFE/rfeModel_op.rds")
-
-#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)
-
-#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
-#                                 rep("Distance", nrow(rfeModel_dist$results)),
-#                                 rep("OC", nrow(rfeModel_oc$results)),
-#                                 rep("OP", nrow(rfeModel_op$results)))
-
-#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)
-
-resampdata_25kb <- rfeModel_dist$results[1:6,]
-
-pt25kb <- ggplot(resampdata_25kb, aes(x=Variables, y=AUPRC)) +
-  geom_point()+
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,.5)
+
+#RUS
+resampdata_RUS_10kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
+resampdata_RUS_10kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
+                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
+
+rfeplot_RUS_10kb <- ggplot(resampdata_RUS_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
   geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
   scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64"), 
-                   labels=c("2", "4", "8", "16", "32", "64"), 
-                   limits=as.character(c(1:64)))+
-  theme_minimal()+
-  ylim(0,.5)
-
-```
-
-####50kb
-
-```{r}
-#rfeModel_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/rfeModel_all.rds")
-rfeModel_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
-#rfeModel_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/RFE/rfeModel_op.rds")
-
-#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)
-
-#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
-#                                 rep("Distance", nrow(rfeModel_dist$results)),
-#                                 rep("OC", nrow(rfeModel_oc$results)),
-#                                 rep("OP", nrow(rfeModel_op$results)))
-
-#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)
-
-resampdata_50kb <- rfeModel_dist$results[1:6,]
-
-pt50kb <- ggplot(resampdata_50kb, aes(x=Variables, y=AUPRC)) +
-  geom_point()+
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+#ROS
+resampdata_ROS_10kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
+resampdata_ROS_10kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
+                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
+
+rfeplot_ROS_10kb <- ggplot(resampdata_ROS_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
   geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
   scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64"), 
-                   labels=c("2", "4", "8", "16", "32", "64"), 
-                   limits=as.character(c(1:64)))+
-  theme_minimal()+
-  ylim(0,.5)
-
-```
-
-####100kb
-
-```{r}
-#rfeModel_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/rfeModel_all.rds")
-rfeModel_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
-#rfeModel_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/RFE/rfeModel_op.rds")
-
-#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)
-
-#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
-#                                 rep("Distance", nrow(rfeModel_dist$results)),
-#                                 rep("OC", nrow(rfeModel_oc$results)),
-#                                 rep("OP", nrow(rfeModel_op$results)))
-
-#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)
-
-resampdata_100kb <- rfeModel_dist$results[1:6,]
-
-pt100kb <- ggplot(resampdata_100kb, aes(x=Variables, y=AUPRC)) +
-  geom_point()+
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+#SMOTE
+resampdata_SMOTE_10kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
+resampdata_SMOTE_10kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
+                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
+
+rfeplot_SMOTE_10kb <- ggplot(resampdata_SMOTE_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
   geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
   scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64"), 
-                   labels=c("2", "4", "8", "16", "32", "64"), 
-                   limits=as.character(c(1:64)))+
-  theme_minimal()+
-  ylim(0,.5)
-
-```
-
-###K562
-
-####10kb
-
-```{r}
-#rfeModel_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/rfeModel_all.rds")
-rfeModel_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
-#rfeModel_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/RFE/rfeModel_op.rds")
-
-#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)
-
-#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
-#                                 rep("Distance", nrow(rfeModel_dist$results)),
-#                                 rep("OC", nrow(rfeModel_oc$results)),
-#                                 rep("OP", nrow(rfeModel_op$results)))
-
-#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)
-
-resampdata_10kb_k562 <- rfeModel_dist$results[1:6,]
-
-pt10kb_k562 <- ggplot(resampdata_10kb_k562, aes(x=Variables, y=AUPRC)) +
-  geom_point()+
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+#ROSE
+resampdata_ROSE_10kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
+resampdata_ROSE_10kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
+                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
+
+rfeplot_ROSE_10kb <- ggplot(resampdata_ROSE_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
   geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
   scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64"), 
-                   labels=c("2", "4", "8", "16", "32", "64"), 
-                   limits=as.character(c(1:64)))+
-  theme_minimal()+
-  ylim(0,.5)
-
-```
-
-####25kb
-
-```{r}
-#rfeModel_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/rfeModel_all.rds")
-rfeModel_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
-#rfeModel_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/RFE/rfeModel_op.rds")
-
-#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)
-
-#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
-#                                 rep("Distance", nrow(rfeModel_dist$results)),
-#                                 rep("OC", nrow(rfeModel_oc$results)),
-#                                 rep("OP", nrow(rfeModel_op$results)))
-
-#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)
-
-resampdata_25kb_k562 <- rfeModel_dist$results[1:6,]
-
-pt25kb <- ggplot(resampdata_25kb_k562, aes(x=Variables, y=AUPRC)) +
-  geom_point()+
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+#Combining 10 kb plots
+ggarrange(rfeplot_None_10kb,
+          rfeplot_RUS_10kb,
+          rfeplot_ROS_10kb,
+          rfeplot_SMOTE_10kb,
+          rfeplot_ROSE_10kb,
+          nrow = 3,
+          ncol = 2,
+          common.legend = TRUE,
+          legend = "right")
+
+```
+
+###25kb
+
+```{r}
+rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
+rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
+
+rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
+rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
+
+#None
+resampdata_None_25kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
+resampdata_None_25kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
+                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
+
+rfeplot_None_25kb <- ggplot(resampdata_None_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
   geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
   scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64"), 
-                   labels=c("2", "4", "8", "16", "32", "64"), 
-                   limits=as.character(c(1:64)))+
-  theme_minimal()+
-  ylim(0,.5)
-
-```
-
-####50kb
-
-```{r}
-#rfeModel_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/rfeModel_all.rds")
-rfeModel_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
-#rfeModel_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/RFE/rfeModel_op.rds")
-
-#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)
-
-#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
-#                                 rep("Distance", nrow(rfeModel_dist$results)),
-#                                 rep("OC", nrow(rfeModel_oc$results)),
-#                                 rep("OP", nrow(rfeModel_op$results)))
-
-#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)
-
-resampdata_50kb_k562 <- rfeModel_dist$results[1:6,]
-
-pt50kb <- ggplot(resampdata_50kb_k562, aes(x=Variables, y=AUPRC)) +
-  geom_point()+
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,.5)
+
+#RUS
+resampdata_RUS_25kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
+resampdata_RUS_25kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
+                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
+
+rfeplot_RUS_25kb <- ggplot(resampdata_RUS_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
   geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
   scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64"), 
-                   labels=c("2", "4", "8", "16", "32", "64"), 
-                   limits=as.character(c(1:64)))+
-  theme_minimal()+
-  ylim(0,.5)
-
-```
-
-####100kb
-
-```{r}
-#rfeModel_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/rfeModel_all.rds")
-rfeModel_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
-#rfeModel_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/RFE/rfeModel_op.rds")
-
-#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)
-
-#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
-#                                 rep("Distance", nrow(rfeModel_dist$results)),
-#                                 rep("OC", nrow(rfeModel_oc$results)),
-#                                 rep("OP", nrow(rfeModel_op$results)))
-
-#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)
-
-resampdata_100kb_k562 <- rfeModel_dist$results[1:6,]
-
-pt100kb <- ggplot(resampdata_100kb_k562, aes(x=Variables, y=AUPRC)) +
-  geom_point()+
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+#ROS
+resampdata_ROS_25kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
+resampdata_ROS_25kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
+                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
+
+rfeplot_ROS_25kb <- ggplot(resampdata_ROS_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
   geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
   scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64"), 
-                   labels=c("2", "4", "8", "16", "32", "64"), 
-                   limits=as.character(c(1:64)))+
-  theme_minimal()+
-  ylim(0,.5)
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+#SMOTE
+resampdata_SMOTE_25kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
+resampdata_SMOTE_25kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
+                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
+
+rfeplot_SMOTE_25kb <- ggplot(resampdata_SMOTE_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
+  geom_line() +
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
+  scale_x_discrete(name="Number of Features", 
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+#ROSE
+resampdata_ROSE_25kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
+resampdata_ROSE_25kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
+                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
+
+rfeplot_ROSE_25kb <- ggplot(resampdata_ROSE_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
+  geom_line() +
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
+  scale_x_discrete(name="Number of Features", 
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+```
+
+###50kb
+
+```{r}
+rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
+rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
+
+rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
+rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
+
+#None
+resampdata_None_50kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
+resampdata_None_50kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
+                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
+
+rfeplot_None_50kb <- ggplot(resampdata_None_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
+  geom_line() +
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
+  scale_x_discrete(name="Number of Features", 
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,.5)
+
+#RUS
+resampdata_RUS_50kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
+resampdata_RUS_50kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
+                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
+
+rfeplot_RUS_50kb <- ggplot(resampdata_RUS_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
+  geom_line() +
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
+  scale_x_discrete(name="Number of Features", 
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+#ROS
+resampdata_ROS_50kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
+resampdata_ROS_50kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
+                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
+
+rfeplot_ROS_50kb <- ggplot(resampdata_ROS_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
+  geom_line() +
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
+  scale_x_discrete(name="Number of Features", 
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+#SMOTE
+resampdata_SMOTE_50kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
+resampdata_SMOTE_50kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
+                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
+
+rfeplot_SMOTE_50kb <- ggplot(resampdata_SMOTE_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
+  geom_line() +
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
+  scale_x_discrete(name="Number of Features", 
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+#ROSE
+resampdata_ROSE_50kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
+resampdata_ROSE_50kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
+                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
+
+rfeplot_ROSE_50kb <- ggplot(resampdata_ROSE_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
+  geom_line() +
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
+  scale_x_discrete(name="Number of Features", 
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+```
+
+###100kb
+
+```{r}
+rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
+rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
+
+rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
+rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
+rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
+rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
+
+#None
+resampdata_None_100kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
+resampdata_None_100kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
+                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
+
+rfeplot_None_100kb <- ggplot(resampdata_None_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
+  geom_line() +
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
+  scale_x_discrete(name="Number of Features", 
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,.5)
+
+#RUS
+resampdata_RUS_100kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
+resampdata_RUS_100kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
+                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
+
+rfeplot_RUS_100kb <- ggplot(resampdata_RUS_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
+  geom_line() +
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
+  scale_x_discrete(name="Number of Features", 
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+#ROS
+resampdata_ROS_100kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
+resampdata_ROS_100kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
+                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
+
+rfeplot_ROS_100kb <- ggplot(resampdata_ROS_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
+  geom_line() +
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
+  scale_x_discrete(name="Number of Features", 
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+#SMOTE
+resampdata_SMOTE_100kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
+resampdata_SMOTE_100kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
+                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
+
+rfeplot_SMOTE_100kb <- ggplot(resampdata_SMOTE_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
+  geom_line() +
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
+  scale_x_discrete(name="Number of Features", 
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
+
+#ROSE
+resampdata_ROSE_100kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
+resampdata_ROSE_100kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
+                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
+
+rfeplot_ROSE_100kb <- ggplot(resampdata_ROSE_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
+  geom_point(position = position_dodge(width = 3))+
+  geom_line() +
+  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
+                width=5,
+                position = position_dodge(width = 3))+
+  scale_color_discrete(name="Cell Line")+
+  scale_x_discrete(name="Number of Features", 
+                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
+                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
+                   limits=as.character(c(1:138)))+
+  theme_minimal()#+
+  #ylim(0,1)
 
@@
 
-allrfe10kb <- rbind.data.frame(resampdata_10kb, resampdata_10kb_k562)
-allrfe10kb$CL <- c(rep("GM12878", 6),rep("K562", 6))
-allrfe10kb$CL <- factor(allrfe10kb$CL)
-
-rfe10kbplot <- ggplot(data=allrfe10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point()+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64"), 
-                   labels=c("2", "4", "8", "16", "32", "64"), 
-                   limits=as.character(c(1:64)))+
-  scale_color_discrete(name="Cell Line")+
-  theme_bw()+
-  #ggtitle("10 kb") +
-  ylim(0,.5)+
-  theme(plot.title = element_text(hjust = 0.5))
-
-allrfe25kb <- rbind.data.frame(resampdata_25kb, resampdata_25kb_k562)
-allrfe25kb$CL <- c(rep("GM12878", 6),rep("K562", 6))
-allrfe25kb$CL <- factor(allrfe25kb$CL)
-
-rfe25kbplot <- ggplot(data=allrfe25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point()+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64"), 
-                   labels=c("2", "4", "8", "16", "32", "64"), 
-                   limits=as.character(c(1:64)))+
-  scale_color_discrete(name="Cell Line")+
-  theme_bw()+
-  #ggtitle("25 kb") +
-  ylim(0,.5)+
-  theme(plot.title = element_text(hjust = 0.5))
-
-allrfe50kb <- rbind.data.frame(resampdata_50kb, resampdata_50kb_k562)
-allrfe50kb$CL <- c(rep("GM12878", 6),rep("K562", 6))
-allrfe50kb$CL <- factor(allrfe50kb$CL)
-
-rfe50kbplot <- ggplot(data=allrfe50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point()+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64"), 
-                   labels=c("2", "4", "8", "16", "32", "64"), 
-                   limits=as.character(c(1:64)))+
-  scale_color_discrete(name="Cell Line")+
-  theme_bw()+
-  #ggtitle("50 kb") +
-  ylim(0,.5)+
-  theme(plot.title = element_text(hjust = 0.5))
-
-allrfe100kb <- rbind.data.frame(resampdata_100kb, resampdata_100kb_k562)
-allrfe100kb$CL <- c(rep("GM12878", 6),rep("K562", 6))
-allrfe100kb$CL <- factor(allrfe100kb$CL)
-
-rfe100kbplot <- ggplot(data=allrfe100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point()+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64"), 
-                   labels=c("2", "4", "8", "16", "32", "64"), 
-                   limits=as.character(c(1:64)))+
-  scale_color_discrete(name="Cell Line")+
-  theme_minimal()+
-  theme_bw()+
-  #ggtitle("100 kb") +
-  ylim(0,.5)+
-  theme(plot.title = element_text(hjust = 0.5))
-
-ggarrange(rfe25kbplot, rfe50kbplot, rfe100kbplot,
-          nrow=2,ncol=2,
-          common.legend = TRUE, legend = "right")
+ggarrange(rfeplot_None_25kb, rfeplot_None_50kb, rfeplot_None_100kb,
+          rfeplot_RUS_25kb, rfeplot_RUS_50kb, rfeplot_RUS_100kb,
+          rfeplot_ROS_25kb, rfeplot_ROS_50kb, rfeplot_ROS_100kb,
+          rfeplot_SMOTE_25kb, rfeplot_SMOTE_50kb, rfeplot_SMOTE_100kb,
+          rfeplot_ROSE_25kb, rfeplot_ROSE_50kb, rfeplot_ROSE_100kb,
+          nrow = 5,
+          ncol = 3,
+          common.legend = TRUE,
+          legend = "right")
 

### 2019-01-29 Manuscript/manuscript.Rmd
manuscript edits

@@
 Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
-The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments.
+The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments for the GM12878, K562, ...
+cell lines.
 Each genomic annotation was represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological significance.
@@
 Each training and testing set was composed of a similar majority to minority class ratio as the full data set.
-That is, for the task of prediction, the test set remained constant for all ensemble systems in order to account for a fair and unbiased comparison.
+For the task of performance evaluation and prediction, the test set remained constant for all ensemble systems to account for a fair and unbiased comparison.
 
@@
 3.
-**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance (in bases) from the center of the bin to the center of the nearest region of a respective genomic annotation region [???
+**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance (refered to hereafter simply as $\textit{distance}$), in basepairs, from the center of the bin to the center of the nearest region of a respective genomic annotation region [???
 Decide whether to use "annotation" or "feature"] was calculated.
 The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1).
-
-To assess the predictive performance for each predictor type, we performed individual random forest classification algorithms utilizing each set predictor types as the feature space, in addition to a model with all combined types.
-Precision-Recall (PR) Curves, and subsequent area under the PR curves (AUPRC), were used to evaluate which predictor type contributed to the best model performance.
-Recursive feature elimination (RFE) was then used to determine the optimal number of features for models within each set of predictor types.
-In doing so, random forest models were used to assign weights to a set features of a given size.
-The optimal number of features was determined by the AUPRC of the corresponding model in order to reduce the feature space accordingly.
 
@@
 
-### CLASSIFICATION
+### CLASSIFICATION & CROSS VALIDATION
 
@@
 
-### MODEL EVALUATION & PREDICTION
+### PERFORMANCE METRICS
 
@@
 Thererfore they are unable to give an overview of the potential range of performance as thresholds vary.
-A full list of the single threshold measures used (including additional metrics not reported), along with their respective formulas, are provided in Supplementary Table 2.
 In order to evaluate the trade-off between precision and recall, we also considered a threshold-free measure in form of the area under the precision recall curve (AUPRC).
+
+###MODEL ASSESSMENT AND PREDICTION
+
+We first assessed predictor type performance using random forest classification algorithms by utilizing each set of predictor types as the feature space, in addition to a model with all combined types.
+Models were evaluated across each combination of resampling techniques applied to the training set, for each cell line.
+Performance was based on the AUPRC
+
+To assess the performance for each predictor type, we performed individual random forest classification algorithms utilizing each set of predictor types as the feature space, in addition to a model with all combined types,.
+Precision-Recall (PR) Curves, and subsequent area under the PR curves (AUPRC), were used to evaluate which predictor type contributed to the best model performance.
+Recursive feature elimination (RFE) was then used to determine the optimal number of features for models within each set of predictor types.
+In doing so, random forest models were used to assign weights to a set features of a given size.
+The optimal number of features was determined by the AUPRC of the corresponding model in order to reduce the feature space accordingly.
 

### 2019-01-29 Manuscript/manuscript.Rmd
editted methods

@@
 We first assessed predictor type performance using random forest classification algorithms by utilizing each set of predictor types as the feature space, in addition to a model with all combined types.
-Models were evaluated across each combination of resampling techniques applied to the training set, for each cell line.
-Performance was based on the AUPRC
+Models were evaluated across each combination of resampling technique applied to the training set, for each cell line.
+Performance was based on the AUPRC.
+Recursive feature elimination (RFE) was then used to determine the optimal number of features for models with the best performing predictor type, across resampling techniques and cell lines.
+In doing so, random forest models were again used to recursively assign weights to a set of features of a given size.
+For computational efficiency we evaluated feature subset sizes in descending order of powers of 2.
+The optimal number of features was determined by the AUPRC of the corresponding model.
+Optimal performance was assessed and the feature spaced was reduced accordingly.
 
-To assess the performance for each predictor type, we performed individual random forest classification algorithms utilizing each set of predictor types as the feature space, in addition to a model with all combined types,.
-Precision-Recall (PR) Curves, and subsequent area under the PR curves (AUPRC), were used to evaluate which predictor type contributed to the best model performance.
-Recursive feature elimination (RFE) was then used to determine the optimal number of features for models within each set of predictor types.
-In doing so, random forest models were used to assign weights to a set features of a given size.
-The optimal number of features was determined by the AUPRC of the corresponding model in order to reduce the feature space accordingly.
-
-For the task of identifying the functional genomic elements that were most predictive of the formation of TAD boundaries, we evaluated the variable importances associated with each predictor of the random forest model.
-For each tree, the prediction accuracy on the out-of-bag portion of the data was recorded.
+For the task of identifying the functional genomic elements that were most predictive of the formation of TAD boundaries, we evaluated the variable importances associated with each predictor of the random forest models associated with each resampling technique.
+For each model and within each tree, the prediction accuracy on the out-of-bag portion of the data was recorded.
 Then the same was done after permuting each predictor variable.
-The difference between the two accuracies was then averaged over all trees, and normalized by the standard error [@kuhn2012caret].
+The difference between the two accuracies was then averaged over all trees, and normalized by the standard error.
+All random forest algorithms were implemented in R using the `caret` package version 6.0 [@kuhn2012caret].
 

### 2019-01-30 Manuscript/manuscript.Rmd
manuscript edits

@@
 Decide whether to use "annotation" or "feature"] was calculated.
-The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figure 1).
+The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figures 1-8).
 
@@
 
-Prior to resampling, we performed a series of random forest classification algorithms on the full features space (all combined predictor types), as well as on type-specific feature spaces (overlap counts, overlap predictors, and log2 distances) to evaluate which predictor types were best able to discriminate between genomic bins that either flanked or did not flank TAD boundaries.
-It was found that, for 10 kb resolution data, models with distance type predictors had higher AUPRC values compared to other predictor types for both GM12878 and K562 cell lines (Figure 4).
-This result was observed across all other data resolutions as well (Supplementary Figure 2).
-There was a gradual decline in AUPRC values as resolution increased with models built on 100 kb resolution domain data having the lowest AUPRC curves, regardless of predictor type (Supplementary Table 2).
+For each cell line, we performed a series of random forest classification algorithms on the full features space (all combined predictor types), as well as on type-specific feature spaces (overlap counts, overlap predictors, and distances) across each resampling technique.
+It was found that, for 10 kb resolution data, models with distance type predictors had consistently higher AUPRC values compared to other predictor types for both GM12878 and K562 cell lines (Figure 4-8).
+This result was observed across all other data resolutions as well (Supplementary Figures 9-23).
 
 Recursive feature elimination was used to establish the optimal number of distance-type features to include in downstream analyses.
-It was determined that, for 10 kb resolution data, near optimal performance was obtained for models with only 32 predictors [???
-Distance-based only?] for each cell line (Figure 5).
-Results remained consistent across the other data resolutions (Supplementary Figure 3).
-Therefore, we reduced the feature space for subsequent models to the top 32 predictors, respective to resolution and cell line.
-The sets of top predictors chosen varied across resolution and cell line due to differences in the parameters provided in the TAD calling algorithm (Supplementary Table 3).
-For the 10 kb resolution data, the most important predictive features that were robust across cell lines were a mixture of transcription factor binding sites, chromatin states, and histone modifications including Smc3, Rad21, CTCF, and H3k9 trimethylation (Figure 6).
-[???
-We don't care - these are for unbalanced dataset] Transcription factor binding sites Smc3, Rad21, and CTCF were also consitently featured as top predictors when comparing cell lines across the the 25 kb and 50 kb resolutions (Supplementary Figure 4).
-Results when cell lines were compared across the 100 kb resolutions were less consitent with current literature.
+It was determined that, for 10 kb resolution data, near optimal performance was obtained for models with only 32 predictors, across each resampling technique and for each cell line (Figures 9-13).
+Results remained consistent across the other data resolutions (Supplementary Figures 24-38).
+Therefore, we reduced the feature space for subsequent models to the top 32 predictors, respective to cell line, resolution, and resampling technique.
 

### 2019-01-30 Scripts/performances.rmd
added to script collecting results

@@
 library(ROCR)
-library(leaps)
+#library(leaps)
 library(cluster)

### 2019-01-30 Manuscript/manuscript.Rmd
edits

@@
 Results remained consistent across the other data resolutions (Supplementary Figures 24-38).
-Therefore, we reduced the feature space for subsequent models to the top 32 predictors, respective to cell line, resolution, and resampling technique.
+Therefore, the feature space was reduced for subsequent models to the top 32 predictors, respective to cell line, resolution, and resampling technique.
 

### 2019-01-31 Manuscript/manuscript.Rmd
added refs to manuscript

@@
 Identifying the mechanisms underlying the formation of TADs are a complex and active area of research.
-The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes [???
-REFs] prompt the use of computational approaches to identify which epigenomic features are most predictive of the TAD boundaries.
+The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes [@xiao2012comparative; @milosavljevic2011emerging] [???
+REFs; !!!added refs] prompt the use of computational approaches to identify which epigenomic features are most predictive of the TAD boundaries.
 Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries [@mourad2016computational; @hong2017computational; @huang2015predicting].
-Although several useful insights have been made, such as the convergent binding of CTCF [???
-Elaborate with refs.], many methods ignore key characteristics of domain data, such as heavily imbalanced number of boundaries vs.
+Although several useful insights have been made, such as the convergent binding of CTCF [@ong2014ctcf; @ghirlando2016ctcf] [???
+Elaborate with refs.; !!!added refs], many methods ignore key characteristics of domain data, such as heavily imbalanced number of boundaries vs.
 other regions.
 In a classification setting [???
-are we talking about classification or prediction?], when one is attempting to discriminate between regions with and without TAD boundaries, this will contribute to small imbalance ratios (defined as the ratio of minority to majority classes) [@Orriols-Puig2008].
-It is commonly agreed upon in the machine learning community that imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class;@chen2013influence;@jeni2013facing].
+are we talking about classification or prediction?; !!!prediction is a byproduct of classification correct?; wait to discuss in meeting], when one is attempting to discriminate between regions with and without TAD boundaries, this will contribute to small imbalance ratios (defined as the ratio of minority to majority classes) [@Orriols-Puig2008].
+As has been reported in the machine learning community, imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class;@chen2013influence;@jeni2013facing].
 Similarly, careful consideration must also be taken when deciding which performance metric(s) to use for evaluation of predictive models, especially in the case of imbalanced data.
@@
 
-Replicate Hi-C data for the GM12878, K562, ...
-cell lines were downloaded from GEO GSE63525 (Experiments HIC001 to HIC018, HIC069 to HIC 074, ...
-respectively; produced using the MbolI restriction enzyme) [@rao20143d].
-[???
-Need supplementary ref.] The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
+Replicate Hi-C data for the GM12878 and K562 cell lines were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 4) [???
+Need supplementary ref.; !!!added supp table] The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
 The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained.

### 2019-02-01 Manuscript/Figures/figure_legends.Rmd
updated figure and legend

@@
 
-**Figure 1: Model Construction.** Cell line specific Hi-C matices were obtained from [@rao20143d].
-The linear genome was then binned according to the intervals of the square-symmetric contact matrices at given resolutions (10 kb, 25 kb, 50 kb, and 100 kb).
-The coordinates of subsequent topologically associating domains were identified using the Arrowhead TAD-calling algorithm [@durand2016juicebox].
+**Figure 1: Model Construction.** An illustration of the proposed model construction given cell line-specific Hi-C matrices obtained from [@rao20143d].
+The contact matrix above is a visualization of the interconnectivity of chromosome 14 (GM12878) on the intervals from 20 mb to 100 mb [@durand2016juicebox].
+The coordinates of subsequent topologically association domains were identified using the arrowhead algorithm from Juicer.
+The linear genome, represented by the diagonal of the contact matrix, was then binned according to prespecified interaction frequency resolutions (10 kb, 25 kb, 50 kb, and 100 kb).
 Each TAD coordinate was then flanked by a unit-specific amount (in basepairs) respective to the resolution of the corresponding contact matrix.
-The response vector Y used for classification was determined by whether a genomic bin overlapped with a flanked boundary region (Y=1) or not (Y=0).
-The spatial relationship between positional coordinates of various functional genomic elements, obtained from ENCODE, and the genomic bins were then used to define the feature space of the models.
+The response vector Y, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region (Y=1) or not (Y=0).
+The spatial relationship between positional coordinates of various functional genomic annotations, obtained from ENCODE, and the genomic bins were then used to define the feature space of the models.
 

### 2019-02-01 Manuscript/manuscript.Rmd
editted manuscript

@@
 3.
-**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance (refered to hereafter simply as $\textit{distance}$), in basepairs, from the center of the bin to the center of the nearest region of a respective genomic annotation region [???
-Decide whether to use "annotation" or "feature"] was calculated.
+**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance (refered to hereafter simply as $\textit{distance}$), in basepairs, from the center of the bin to the center of the nearest region defined by a specific genomic annotation [???
+Decide whether to use "annotation" or "feature"; !!!go with annotation] was calculated.
 The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figures 1-8).

### 2019-02-01 Manuscript/Figures/figure_legends.Rmd
editted legends

@@
 The _overlap percent_ (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin by the total bin width.
-The _distance_ predictors were calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest genomic feature.
+The _distance_ ($log_{2}$ transformed) predictors were calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest genomic feature.
 
-**Figure 4.
-Precision-Recall curves for unbalanced 10 kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on unbalanced data at 10 kb resolution.
+**Figures 4-8.
+Precision-Recall curves for 10 kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on 10 kb resolution data, across each resampling technique.
 GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red).
-For both cell lines, random forest models with log distance-type predictors were found to have higher AUPRC values.
 
-**Figure 5.
-Model Performances on 10kb data using distance-type predictors for different number of features** Using RFE, performances of a series of random forest models with different numbers of the most predictive features for each cell line was compared using AUPRC.
+**Figure 9-13.
+Recursive Feature Elimination for 10 kb data** Beginning with the full set of distance type predictors for each cell line, models were recursively evaluated at different subsets of feature size.
+For convenience and computational efficiency, feature size decreasing in powers of 2 was considered.
+For the 10 kb data, near optimal performance was achieved for both the GM12878 (red) and K562 cell lines (blue).
+The maximum size for feature subsets differed between cell line due the available annotations provided in Supplementary Table 1.
+
+Performances of a series of random forest models with different numbers of the most predictive features for each cell line was compared using AUPRC.
 For convenience and computational efficiency, only specific subsets of features were considered (increasing powers of 2).
+
+Additionally, models using the full feature space were also evaluated, hence the differing number of features between cell lines.
 For the 10 kb data, near optimal performance was achieved for both the GM12878 (red) and K562 cell lines (blue).

### 2019-02-01 Manuscript/Supplementary/supplementary_legends.Rmd
editted legends

@@
 
-**Figure 1. Distance Densities across cell lines and resolutions**
+**Supplementary Table 4. Hi-C Data.** A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains and where they can be downloaded.
+
+**Supplementary Table 1.
+Genomic Annotations.** A complete list of the genomic annotations used to build the feature space for all downstream models.
+The GRCh37/hg19 human genome assembly was used.
+"Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Available Cell Type" - the name of the cell type in which the annotation was available, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
+[???
+Did you use only features common to both cell lines?; !!!clarified, need to discuss further]
+
+**Supplementary Figure 1-8. Distance Densities across cell lines and resolutions.**
 Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for GM12878 (left column) and K562 (right column) cell lines.
 The untransformed distances (red) are highly right skewed.
-After performing a $log_{2}$ tranformation (blue), the distances exhibit more normalized densities.
-The normalized distances were exhibited across all data resolution (rows).
+After performing a $log_{2}$ tranformation (blue), the distances exhibited more normalized densities.
 
-**Figure 2.
-Precision-Recall curves for unbalanced 25 kb, 50kb, and 100kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on unbalanced data at 25 kb, 50kb, and 100kb resolution.
+**Supplementary Table 5.
+Data Summaries and Imbalance Ratios.** The total number of genomic bins included in the complete, training, and testing sets, as well as the subsequent imbalance ratios across resolutions and cell lines.
+Imbalance ratio is defined as the ratio of genomic bins that overlapped a flanked TAD boundary (minority class), divided by the number of genomic bins that did not overlap a flanked TAD boundary (majority class).
+
+**Supplementary Figures 9-23.
+Precision-Recall curves for unbalanced 25 kb, 50kb, and 100kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on 25 kb, 50kb, and 100kb resolution data, across each resampling technique.
 GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red).
-For both cell lines, and among all resolutions, random forest models with log distance-type predictors were found to have higher AUPRC values.
+The baseline threshold for each PR curve is defined as the ratio of genomic bins that overlapped with a flanked TAD boundary divided by the total number of genomic bins for the test set, respective to cell line and resolution.
+
+**Supplementary Table 2.
+Area under Precision-Recall Curves.** Comparison of models applied to different data resolutions, resampling techniques, and predictor types for each of the two cell lines in terms of AUPRC.
+The column labeled "All" denotes models with all 3 combined predictor types.
 
@@
 The mean imbalance ratios across resolutions were found to be X1 (SD=Y2) and X2 (SD=Y2) for the GM12878 and K562 cell lines respectively.
-
-**Supplementary Table S1.
-List of Genomic Annotations.** The GRCh37/hg19 human genome assembly was used.
-"Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Cell Type" - cell type, "Source" - download URL.
-[???
-Did you use only features common to both cell lines?]

### 2019-02-01 Scripts/performances.rmd
added script for results

@@
 
-#comparing top predictors across resolution and cell line
-rfeModel_dist_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfe10kbvars <- rfeModel_dist_10kb$optVariables[1:32]
-
-rfeModel_dist_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfe25kbvars <- rfeModel_dist_25kb$optVariables[1:32]
-
-rfeModel_dist_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfe50kbvars <- rfeModel_dist_50kb$optVariables[1:32]
-
-rfeModel_dist_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfe100kbvars <- rfeModel_dist_100kb$optVariables[1:32]
-
-rfeModel_dist_10kb_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfe10kbvars_k562 <- rfeModel_dist_10kb_k562$optVariables[1:32]
-
-rfeModel_dist_25kb_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfe25kbvars_k562 <- rfeModel_dist_25kb_k562$optVariables[1:32]
-
-rfeModel_dist_50kb_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfe50kbvars_k562 <- rfeModel_dist_50kb_k562$optVariables[1:32]
-
-rfeModel_dist_100kb_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfe100kbvars_k562 <- rfeModel_dist_100kb_k562$variables$var[rfeModel_dist_100kb_k562$variables$Variables==32 & rfeModel_dist_100kb_k562$variables$Resample=="Fold1.Rep1"]
-
-rfe10kbvars <- gsub(paste(c("Gm12878-", 
-                            "_dist", 
-                            "-Sydh", 
-                            "-Haib", 
-                            "-Broad",
-                            "-Uchicago",
-                            "-Uta",
-                            "-Uw"), collapse = "|"),"", rfe10kbvars)
-rfe25kbvars <- gsub(paste(c("Gm12878-", 
-                            "_dist", 
-                            "-Sydh", 
-                            "-Haib", 
-                            "-Broad",
-                            "-Uchicago",
-                            "-Uta",
-                            "-Uw"), collapse = "|"),"", rfe25kbvars)
-rfe50kbvars <- gsub(paste(c("Gm12878-", 
-                            "_dist", 
-                            "-Sydh", 
-                            "-Haib", 
-                            "-Broad",
-                            "-Uchicago",
-                            "-Uta",
-                            "-Uw"), collapse = "|"),"", rfe50kbvars)
-rfe100kbvars <- gsub(paste(c("Gm12878-", 
-                            "_dist", 
-                            "-Sydh", 
-                            "-Haib", 
-                            "-Broad",
-                            "-Uchicago",
-                            "-Uta",
-                            "-Uw"), collapse = "|"),"", rfe100kbvars)
-
-rfe10kbvars_k562 <- gsub(paste(c("K562-", 
-                            "_dist", 
-                            "-Sydh", 
-                            "-Haib", 
-                            "-Broad",
-                            "-Uchicago",
-                            "-Uta",
-                            "-Uw"), collapse = "|"),"", rfe10kbvars_k562)
-rfe25kbvars_k562 <- gsub(paste(c("K562-", 
-                            "_dist", 
-                            "-Sydh", 
-                            "-Haib", 
-                            "-Broad",
-                            "-Uchicago",
-                            "-Uta",
-                            "-Uw"), collapse = "|"),"", rfe25kbvars_k562)
-rfe50kbvars_k562 <- gsub(paste(c("K562-", 
-                            "_dist", 
-                            "-Sydh", 
-                            "-Haib", 
-                            "-Broad",
-                            "-Uchicago",
-                            "-Uta",
-                            "-Uw"), collapse = "|"),"", rfe50kbvars_k562)
-rfe100kbvars_k562 <- gsub(paste(c("K562-", 
-                            "_dist", 
-                            "-Sydh", 
-                            "-Haib", 
-                            "-Broad",
-                            "-Uchicago",
-                            "-Uta",
-                            "-Uw"), collapse = "|"),"", rfe100kbvars_k562)
-
-alltopvars <- data.frame(rfe10kbvars,
-                         rfe10kbvars_k562,
-                         rfe25kbvars,
-                         rfe25kbvars_k562,
-                         rfe50kbvars,
-                         rfe50kbvars_k562,
-                         rfe100kbvars,
-                         rfe100kbvars_k562)
-
-rfe10kbvars_o <- sort(rfe10kbvars)
-rfe25kbvars_o <- sort(rfe25kbvars)
-rfe50kbvars_o <- sort(rfe50kbvars)
-rfe100kbvars_o <- sort(rfe100kbvars)
-rfe10kbvars_k562_o <- sort(rfe10kbvars_k562)
-rfe25kbvars_k562_o <- sort(rfe25kbvars_k562)
-rfe50kbvars_k562_o <- sort(rfe50kbvars_k562)
-rfe100kbvars_k562_o <- sort(rfe100kbvars_k562)
-alltopvars_o <- data.frame(rfe10kbvars_o,rfe25kbvars_o,rfe50kbvars_o,rfe100kbvars_o,
-                         rfe10kbvars_k562_o,rfe25kbvars_k562_o,rfe50kbvars_k562_o,rfe100kbvars_k562_o)
-
-grid.newpage()
-venn.plot <- draw.quad.venn(
-	area1 = length(rfe10kbvars), #The size of the first set
-	area2 = length(rfe25kbvars), #The size of the second set
-	area3 = length(rfe50kbvars), #The size of the third set
-	area4 = length(rfe100kbvars), #The size of the fourth set
-	n12 = length(intersect(rfe10kbvars,rfe25kbvars)), #The size of the intersection between the first and the second set
-	n13 = length(intersect(rfe10kbvars,rfe50kbvars)), #The size of the intersection between the first and the third set
-	n14 = length(intersect(rfe10kbvars,rfe100kbvars)), #The size of the intersection between the first and the fourth set
-	n23 = length(intersect(rfe25kbvars,rfe50kbvars)), #The size of the intersection between the second and the third set
-	n24 = length(intersect(rfe25kbvars,rfe100kbvars)), #The size of the intersection between the second and the fourth set
-	n34 = length(intersect(rfe50kbvars,rfe100kbvars)), #The size of the intersection between the third and the fourth set
-	n123 = length(Reduce(intersect, list(rfe10kbvars,rfe25kbvars,rfe50kbvars))), #The size of the intersection between the first, second and third sets
-	n124 = length(Reduce(intersect, list(rfe10kbvars,rfe25kbvars,rfe100kbvars))), #The size of the intersection between the first, second and fourth sets
-	n134 = length(Reduce(intersect, list(rfe10kbvars,rfe50kbvars,rfe100kbvars))), #The size of the intersection between the first, third and fourth sets
-	n234 = length(Reduce(intersect, list(rfe25kbvars,rfe50kbvars,rfe100kbvars))), #The size of the intersection between the second, third and fourth sets
-	n1234 = length(Reduce(intersect, list(rfe10kbvars,rfe25kbvars,rfe50kbvars,rfe100kbvars))), #The size of the intersection between all four sets
-	category = c("10 kb", "25 kb", "50 kb", "100 kb"),
-	fill = c("orange", "red", "green", "blue"),
-	lty = "dashed",
-	cex = 2,
-	cat.cex = 2,
-	cat.col = c("orange", "red", "green", "blue")
-	);
-
-grid.newpage()
-venn.plot.k562 <- draw.quad.venn(
-	area1 = length(rfe10kbvars_k562), #The size of the first set
-	area2 = length(rfe25kbvars_k562), #The size of the second set
-	area3 = length(rfe50kbvars_k562), #The size of the third set
-	area4 = length(rfe100kbvars_k562), #The size of the fourth set
-	n12 = length(intersect(rfe10kbvars_k562,rfe25kbvars_k562)), #The size of the intersection between the first and the second set
-	n13 = length(intersect(rfe10kbvars_k562,rfe50kbvars_k562)), #The size of the intersection between the first and the third set
-	n14 = length(intersect(rfe10kbvars_k562,rfe100kbvars_k562)), #The size of the intersection between the first and the fourth set
-	n23 = length(intersect(rfe25kbvars_k562,rfe50kbvars_k562)), #The size of the intersection between the second and the third set
-	n24 = length(intersect(rfe25kbvars_k562,rfe100kbvars_k562)), #The size of the intersection between the second and the fourth set
-	n34 = length(intersect(rfe50kbvars_k562,rfe100kbvars_k562)), #The size of the intersection between the third and the fourth set
-	n123 = length(Reduce(intersect, list(rfe10kbvars_k562,rfe25kbvars_k562,rfe50kbvars_k562))), #The size of the intersection between the first, second and third sets
-	n124 = length(Reduce(intersect, list(rfe10kbvars_k562,rfe25kbvars_k562,rfe100kbvars_k562))), #The size of the intersection between the first, second and fourth sets
-	n134 = length(Reduce(intersect, list(rfe10kbvars_k562,rfe50kbvars_k562,rfe100kbvars_k562))), #The size of the intersection between the first, third and fourth sets
-	n234 = length(Reduce(intersect, list(rfe25kbvars_k562,rfe50kbvars_k562,rfe100kbvars_k562))), #The size of the intersection between the second, third and fourth sets
-	n1234 = length(Reduce(intersect, list(rfe10kbvars_k562,rfe25kbvars_k562,rfe50kbvars_k562,rfe100kbvars_k562))), #The size of the intersection between all four sets
-	category = c("10 kb", "25 kb", "50 kb", "100 kb"),
-	fill = c("orange", "red", "green", "blue"),
-	lty = "dashed",
-	cex = 2,
-	cat.cex = 2,
-	cat.col = c("orange", "red", "green", "blue")
-	);
-
-grid.newpage()
-venn.plot.10kb <- draw.pairwise.venn(
-	area1 = length(rfe10kbvars),
-	area2 = length(rfe10kbvars_k562),
-	cross.area = length(intersect(rfe10kbvars,rfe10kbvars_k562)),
-	category = c("GM12878", "K562"),
-	fill = c("blue", "red"),
-	lty = "blank",
-	cex = 2,
-	cat.cex = 2,
-	cat.just = list(c(-.5, -3), c(2, -3)))
-
-grid.newpage()
-venn.plot.25kb <- draw.pairwise.venn(
-	area1 = length(rfe25kbvars),
-	area2 = length(rfe25kbvars_k562),
-	cross.area = length(intersect(rfe25kbvars,rfe25kbvars_k562)),
-	category = c("GM12878", "K562"),
-	fill = c("blue", "red"),
-	lty = "blank",
-	cex = 2,
-	cat.cex = 2,
-	cat.just = list(c(-.5, -3), c(2, -3)))
-
-grid.newpage()
-venn.plot.50kb <- draw.pairwise.venn(
-	area1 = length(rfe50kbvars),
-	area2 = length(rfe50kbvars_k562),
-	cross.area = length(intersect(rfe50kbvars,rfe50kbvars_k562)),
-	category = c("GM12878", "K562"),
-	fill = c("blue", "red"),
-	lty = "blank",
-	cex = 2,
-	cat.cex = 2,
-	cat.just = list(c(-.5, -3), c(2, -3)))
-
-grid.newpage()
-venn.plot.100kb <- draw.pairwise.venn(
-	area1 = length(rfe100kbvars),
-	area2 = length(rfe100kbvars_k562),
-	cross.area = length(intersect(rfe100kbvars,rfe100kbvars_k562)),
-	category = c("GM12878", "K562"),
-	fill = c("blue", "red"),
-	lty = "blank",
-	cex = 2,
-	cat.cex = 2,
-	cat.just = list(c(-.5, -3), c(2, -3)))
-
-```
-
-##Heatmaps of top predictors
-
-###10 kb
-
-```{r}
-topvars10kbgm12878 <- cbind.data.frame(names(rfeModel_dist_10kb$fit$importance[,1]), rfeModel_dist_10kb$fit$importance)
-topvars10kbgm12878 <- topvars10kbgm12878[1:32,]
-rownames(topvars10kbgm12878) <- NULL
-names(topvars10kbgm12878) <- c("Feature", "Importance")
-topvars10kbgm12878$Feature <- gsub(paste(c("Gm12878-",
-                                           "_dist",
-                                           "-Haib", 
-                                           "-Sydh",
-                                           "-Uta",
-                                           "-Uw",
-                                           "-Broad",
-                                           "-Uchicago"), collapse = "|"),
-                                   "",
-                                   topvars10kbgm12878$Feature)
-
-topvars10kbk562 <- cbind.data.frame(names(rfeModel_dist_10kb_k562$fit$importance[,1]), rfeModel_dist_10kb_k562$fit$importance[,4])
-topvars10kbk562 <- topvars10kbk562[1:32,]
-rownames(topvars10kbk562) <- NULL
-names(topvars10kbk562) <- c("Feature", "Importance")
-topvars10kbk562$Feature <- gsub(paste(c("K562-",
-                                           "_dist",
-                                           "-Haib", 
-                                           "-Sydh",
-                                           "-Uta",
-                                           "-Uw",
-                                           "-Broad",
-                                           "-Uchicago"), collapse = "|"),
-                                   "",
-                                   topvars10kbk562$Feature)
-
-impdata_10kb <- data.frame(Feature = Reduce(union, 
-                                            list(topvars10kbgm12878$Feature,
-                                                 topvars10kbk562$Feature)))
-impdata_10kb$gm12878_10kb <- NA
-impdata_10kb$k562_10kb <- NA
-
-impdata_10kb$gm12878_10kb[which(impdata_10kb$Feature %in% topvars10kbgm12878$Feature)] <- topvars10kbgm12878$Importance
-impdata_10kb$k562_10kb[which(impdata_10kb$Feature %in% topvars10kbk562$Feature)] <- topvars10kbk562$Importance
-
-impdata_10kb <- impdata_10kb[order(impdata_10kb$Feature),]
-
-#preObj <- preProcess(impdata_10kb, method=c("center", "scale"))
-#impdata_10kb <- predict(preObj, impdata_10kb)
-
-impdata_10kb_long <- melt(impdata_10kb)
-impdata_10kb_long <- ddply(impdata_10kb_long, .(variable), transform,   
-                           rescale = rescale(value))
-
-topvars10kbplot <- ggplot(impdata_10kb_long, aes(variable, Feature)) + 
-    geom_tile(aes(fill = rescale),
-              colour = "white") + scale_fill_gradient2(low = "white", 
-                                                      #mid = "white",
-                                                      high = muted("red"), 
-                                                      #midpoint = 0, 
-                                                      space = "Lab",
-                                                      na.value = "grey50", 
-                                                      guide = "legend", 
-                                                      aesthetics = "fill",
-                                                      name="Importance",
-                                                      labels=c("Very Low",
-                                                               "Low",
-                                                               "Medium",
-                                                               "High",
-                                                               "Very High"))+
-  scale_x_discrete(name="Cell Line", labels=c("GM12878", "K562"))+
-  theme_bw()+
-  theme_minimal()
-```
-
-###25 kb
-
-```{r}
-topvars25kbgm12878 <- cbind.data.frame(names(rfeModel_dist_25kb$fit$importance[,1]), rfeModel_dist_25kb$fit$importance)
-topvars25kbgm12878 <- topvars25kbgm12878[1:32,]
-rownames(topvars25kbgm12878) <- NULL
-names(topvars25kbgm12878) <- c("Feature", "Importance")
-topvars25kbgm12878$Feature <- gsub(paste(c("Gm12878-",
-                                           "_dist",
-                                           "-Haib", 
-                                           "-Sydh",
-                                           "-Uta",
-                                           "-Uw",
-                                           "-Broad",
-                                           "-Uchicago"), collapse = "|"),
-                                   "",
-                                   topvars25kbgm12878$Feature)
-
-topvars25kbk562 <- cbind.data.frame(names(rfeModel_dist_25kb_k562$fit$importance[,1]), rfeModel_dist_25kb_k562$fit$importance[,1])
-topvars25kbk562 <- topvars25kbk562[1:32,]
-rownames(topvars25kbk562) <- NULL
-names(topvars25kbk562) <- c("Feature", "Importance")
-topvars25kbk562$Feature <- gsub(paste(c("K562-",
-                                           "_dist",
-                                           "-Haib", 
-                                           "-Sydh",
-                                           "-Uta",
-                                           "-Uw",
-                                           "-Broad",
-                                           "-Uchicago"), collapse = "|"),
-                                   "",
-                                   topvars25kbk562$Feature)
-
-impdata_25kb <- data.frame(Feature = Reduce(union, 
-                                            list(topvars25kbgm12878$Feature,
-                                                 topvars25kbk562$Feature)))
-impdata_25kb$gm12878_25kb <- NA
-impdata_25kb$k562_25kb <- NA
-
-impdata_25kb$gm12878_25kb[which(impdata_25kb$Feature %in% topvars25kbgm12878$Feature)] <- topvars25kbgm12878$Importance
-impdata_25kb$k562_25kb[which(impdata_25kb$Feature %in% topvars25kbk562$Feature)] <- topvars25kbk562$Importance
-
-impdata_25kb <- impdata_25kb[order(impdata_25kb$Feature),]
-
-#preObj <- preProcess(impdata_25kb, method=c("center", "scale"))
-#impdata_25kb <- predict(preObj, impdata_25kb)
-
-impdata_25kb_long <- melt(impdata_25kb)
-impdata_25kb_long <- ddply(impdata_25kb_long, .(variable), transform,   
-                           rescale = rescale(value))
-
-topvars25kbplot <- ggplot(impdata_25kb_long, aes(variable, Feature)) + 
-    geom_tile(aes(fill = rescale),
-              colour = "white") + scale_fill_gradient2(low = "white", 
-                                                      #mid = "white",
-                                                      high = muted("red"), 
-                                                      #midpoint = 0, 
-                                                      space = "Lab",
-                                                      na.value = "grey50", 
-                                                      guide = "legend", 
-                                                      aesthetics = "fill",
-                                                      name="Importance",
-                                                      labels=c("Very Low",
-                                                               "Low",
-                                                               "Medium",
-                                                               "High",
-                                                               "Very High"))+
-  scale_x_discrete(name="Cell Line", labels=c("GM12878", "K562"))+
-  theme_bw()+
-  theme_minimal()
-```
-
-###50kb
-
-```{r}
-topvars50kbgm12878 <- cbind.data.frame(names(rfeModel_dist_50kb$fit$importance[,1]), rfeModel_dist_50kb$fit$importance)
-topvars50kbgm12878 <- topvars50kbgm12878[1:32,]
-rownames(topvars50kbgm12878) <- NULL
-names(topvars50kbgm12878) <- c("Feature", "Importance")
-topvars50kbgm12878$Feature <- gsub(paste(c("Gm12878-",
-                                           "_dist",
-                                           "-Haib", 
-                                           "-Sydh",
-                                           "-Uta",
-                                           "-Uw",
-                                           "-Broad",
-                                           "-Uchicago"), collapse = "|"),
-                                   "",
-                                   topvars50kbgm12878$Feature)
-
-topvars50kbk562 <- cbind.data.frame(names(rfeModel_dist_50kb_k562$fit$importance[,1]), rfeModel_dist_50kb_k562$fit$importance[,1])
-topvars50kbk562 <- topvars50kbk562[1:32,]
-rownames(topvars50kbk562) <- NULL
-names(topvars50kbk562) <- c("Feature", "Importance")
-topvars50kbk562$Feature <- gsub(paste(c("K562-",
-                                           "_dist",
-                                           "-Haib", 
-                                           "-Sydh",
-                                           "-Uta",
-                                           "-Uw",
-                                           "-Broad",
-                                           "-Uchicago"), collapse = "|"),
-                                   "",
-                                   topvars50kbk562$Feature)
-
-impdata_50kb <- data.frame(Feature = Reduce(union, 
-                                            list(topvars50kbgm12878$Feature,
-                                                 topvars50kbk562$Feature)))
-impdata_50kb$gm12878_50kb <- NA
-impdata_50kb$k562_50kb <- NA
-
-impdata_50kb$gm12878_50kb[which(impdata_50kb$Feature %in% topvars50kbgm12878$Feature)] <- topvars50kbgm12878$Importance
-impdata_50kb$k562_50kb[which(impdata_50kb$Feature %in% topvars50kbk562$Feature)] <- topvars50kbk562$Importance
-
-impdata_50kb <- impdata_50kb[order(impdata_50kb$Feature),]
-
-#preObj <- preProcess(impdata_50kb, method=c("center", "scale"))
-#impdata_50kb <- predict(preObj, impdata_50kb)
-
-impdata_50kb_long <- melt(impdata_50kb)
-impdata_50kb_long <- ddply(impdata_50kb_long, .(variable), transform,   
-                           rescale = rescale(value))
-
-topvars50kbplot <- ggplot(impdata_50kb_long, aes(variable, Feature)) + 
-    geom_tile(aes(fill = rescale),
-              colour = "white") + scale_fill_gradient2(low = "white", 
-                                                      #mid = "white",
-                                                      high = muted("red"), 
-                                                      #midpoint = 0, 
-                                                      space = "Lab",
-                                                      na.value = "grey50", 
-                                                      guide = "legend", 
-                                                      aesthetics = "fill",
-                                                      name="Importance",
-                                                      labels=c("Very Low",
-                                                               "Low",
-                                                               "Medium",
-                                                               "High",
-                                                               "Very High"))+
-  scale_x_discrete(name="Cell Line", labels=c("GM12878", "K562"))+
-  theme_bw()+
-  theme_minimal()
-```
-
-###100kb
-
-```{r}
-topvars100kbgm12878 <- cbind.data.frame(names(rfeModel_dist_100kb$fit$importance[,1]), rfeModel_dist_100kb$fit$importance)
-topvars100kbgm12878 <- topvars100kbgm12878[1:32,]
-rownames(topvars100kbgm12878) <- NULL
-names(topvars100kbgm12878) <- c("Feature", "Importance")
-topvars100kbgm12878$Feature <- gsub(paste(c("Gm12878-",
-                                           "_dist",
-                                           "-Haib", 
-                                           "-Sydh",
-                                           "-Uta",
-                                           "-Uw",
-                                           "-Broad",
-                                           "-Uchicago"), collapse = "|"),
-                                   "",
-                                   topvars100kbgm12878$Feature)
-
-topvars100kbk562 <- cbind.data.frame(rfeModel_dist_100kb_k562$variables$var[1:32], rfeModel_dist_100kb_k562$variables$Overall[1:32])
-topvars100kbk562 <- topvars100kbk562[1:32,]
-rownames(topvars100kbk562) <- NULL
-names(topvars100kbk562) <- c("Feature", "Importance")
-topvars100kbk562$Feature <- gsub(paste(c("K562-",
-                                           "_dist",
-                                           "-Haib", 
-                                           "-Sydh",
-                                           "-Uta",
-                                           "-Uw",
-                                           "-Broad",
-                                           "-Uchicago"), collapse = "|"),
-                                   "",
-                                   topvars100kbk562$Feature)
-
-impdata_100kb <- data.frame(Feature = Reduce(union, 
-                                            list(topvars100kbgm12878$Feature,
-                                                 topvars100kbk562$Feature)))
-impdata_100kb$gm12878_100kb <- NA
-impdata_100kb$k562_100kb <- NA
-
-impdata_100kb$gm12878_100kb[which(impdata_100kb$Feature %in% topvars100kbgm12878$Feature)] <- topvars100kbgm12878$Importance
-impdata_100kb$k562_100kb[which(impdata_100kb$Feature %in% topvars100kbk562$Feature)] <- topvars100kbk562$Importance
-
-impdata_100kb <- impdata_100kb[order(impdata_100kb$Feature),]
-
-#preObj <- preProcess(impdata_100kb, method=c("center", "scale"))
-#impdata_100kb <- predict(preObj, impdata_100kb)
-
-impdata_100kb_long <- melt(impdata_100kb)
-impdata_100kb_long <- ddply(impdata_100kb_long, .(variable), transform,   
-                           rescale = rescale(value))
-
-topvars100kbplot <- ggplot(impdata_100kb_long, aes(variable, Feature)) + 
-    geom_tile(aes(fill = rescale),
-              colour = "white") + scale_fill_gradient2(low = "white", 
-                                                      #mid = "white",
-                                                      high = muted("red"), 
-                                                      #midpoint = 0, 
-                                                      space = "Lab",
-                                                      na.value = "grey50", 
-                                                      guide = "legend", 
-                                                      aesthetics = "fill",
-                                                      name="Importance",
-                                                      labels=c("Very Low",
-                                                               "Low",
-                                                               "Medium",
-                                                               "High",
-                                                               "Very High"))+
-  scale_x_discrete(name="Cell Line", labels=c("GM12878", "K562"))+
-  theme_bw()+
-  theme_minimal()
-```
-
-###Combined
-
-```{r}
-ggarrange(topvars25kbplot,
-          topvars50kbplot,
-          topvars100kbplot,
-          ncol=3,
-          nrow=1,
-          common.legend = TRUE,
-          legend = "right")
 ```
@@
 #Barplots of performance metrics
+
+##10kb
+
+```{r}
+#GM12878
+
+##Accuracy
+
+```
 

### 2019-02-01 Manuscript/Figures/figure_legends.Rmd
edits to legend and manuscript

@@
 **Figure 9-13.
-Recursive Feature Elimination for 10 kb data** Beginning with the full set of distance type predictors for each cell line, models were recursively evaluated at different subsets of feature size.
+Recursive Feature Elimination for 10 kb data** Beginning with the full set of distance type predictors for each cell line, models built on 10 kb resolution data were recursively evaluated at different subsets of feature size.
 For convenience and computational efficiency, feature size decreasing in powers of 2 was considered.
-For the 10 kb data, near optimal performance was achieved for both the GM12878 (red) and K562 cell lines (blue).
-The maximum size for feature subsets differed between cell line due the available annotations provided in Supplementary Table 1.
-
-Performances of a series of random forest models with different numbers of the most predictive features for each cell line was compared using AUPRC.
-For convenience and computational efficiency, only specific subsets of features were considered (increasing powers of 2).
-
-Additionally, models using the full feature space were also evaluated, hence the differing number of features between cell lines.
-For the 10 kb data, near optimal performance was achieved for both the GM12878 (red) and K562 cell lines (blue).
-
-**Figure 6.
-Variable importance heatmap for 10 kb data across cell lines.** Predictive importance of the top 32 genomic features across cell lines for 10 kb data.
-Importance was discretized into quantiles, with features that were not congruent between cell lines filled in grey.
+The maximum size for feature subsets differed between cell line due the available annotations that were considered and provided in Supplementary Table 1.
+Near optimal performance was achieved using the top 32 distance type predictors for both the GM12878 (red) and K562 cell lines (blue).

### 2019-02-01 Manuscript/Supplementary/supplementary_legends.Rmd
edits to legend and manuscript

@@
 **Supplementary Figures 9-23.
-Precision-Recall curves for unbalanced 25 kb, 50kb, and 100kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on 25 kb, 50kb, and 100kb resolution data, across each resampling technique.
+Precision-Recall curves for 25 kb, 50kb, and 100kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on 25 kb, 50kb, and 100kb resolution data, across each resampling technique.
 GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red).
-The baseline threshold for each PR curve is defined as the ratio of genomic bins that overlapped with a flanked TAD boundary divided by the total number of genomic bins for the test set, respective to cell line and resolution.
 
@@
 **Figure 3.
-Model Performances on 25 kb, 50kb, and 100kb data using distance-type predictors for different number of features** Using RFE, performances of a series of random forest models with different numbers of the most predictive features for each cell line was compared using AUPRC.
-For convenience and computational efficiency, only specific subsets of features were considered (increasing powers of 2).
-For each resolution, near optimal performance was achieved for both the GM12878 (red) and K562 cell lines (blue).
-
-**Figure 4.
-Variable importance heatmap for 25 kb, 50kb, and 100kb data across cell lines.** Predictive importance of the top 32 genomic features across cell lines for 25 kb, 50kb, and 100kb resolutions.
-Importance was discretized into quantiles, with features that were not congruent between cell lines filled in grey.
-
-**Figure 5: Imbalance ratios across resolutions and cell lines.** Imbalance ratios, defined as the ratio of minority class samples to majority class samples, were plotted across resolutions for cell lines GM12878 (red) and K562 (blue).
-The mean imbalance ratios across resolutions were found to be X1 (SD=Y2) and X2 (SD=Y2) for the GM12878 and K562 cell lines respectively.
+Recursive Feature Elimination for 25 kb, 50 kb, and 100 kb data** Beginning with the full set of distance type predictors for each cell line, models built on 25 kb, 50 kb, and 100 kb resolution data were recursively evaluated at different subsets of feature size.
+For convenience and computational efficiency, feature size decreasing in powers of 2 was considered.
+The maximum size for feature subsets differed between cell line due the available annotations that were considered and provided in Supplementary Table 1.
+Near optimal performance was achieved using the top 32 distance type predictors for both the GM12878 (red) and K562 cell lines (blue).

### 2019-02-01 Manuscript/manuscript.Rmd
edits to legend and manuscript

@@
 
-We evaluated and compared multilpe random forest classification algorithms built on domain data extracted from Hi-C datasets for X cell lines C = {GM12878, K562, ...}, at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}.
+We evaluated and compared multiple random forest classification algorithms built on domain data extracted from Hi-C datasets for 2 cell lines C = {GM12878, K562}, at 4 different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}.
 For each classifier, we compared 3 predictor types P = {OC, OP, Distance} and 5 class balancing techniques B = {None, RUS, ROS, SMOTE, ROSE}.
@@
 Letting |X| denote the cardinality of each set, we evaluated $|C| \times |R| \times |P| \times |B|$ different ensemble systems, totaling X (=$x \times 4 \times 3 \times 5$) separate models.
+For each model, we aimed to assess both performance and identify the genomic annotations that were most influential in correctly labeling the genomic bins that overlapped with flanked TAD boundaries.
 For simplicity, we present the most significant results, with the complete results available as Supplementary Tables and Figures.
+
+We first examined the class imbalance of the different data resolutions (Supplementary Table ).
+While the total number of genomic bins decreased as resolution increased, the imbalance ratios remained relatively stable.
+We found that there was an average imbalance ratio of 0.154 (SD=0.022) and 0.137 (SD=0.0181) for cell lines GM12878 and K562 respectively.
+The low imbalance ratios indicate a wide disparity between majority and minority classes, and therefore suitable resampling techniques are needed.
 
@@
 
-For each cell line, we performed a series of random forest classification algorithms on the full features space (all combined predictor types), as well as on type-specific feature spaces (overlap counts, overlap predictors, and distances) across each resampling technique.
-It was found that, for 10 kb resolution data, models with distance type predictors had consistently higher AUPRC values compared to other predictor types for both GM12878 and K562 cell lines (Figure 4-8).
-This result was observed across all other data resolutions as well (Supplementary Figures 9-23).
+For each cell line and resolution, we balanced the data using each resampling technique and performed a series of random forest classification algorithms on the full features space (all combined predictor types), as well as on type-specific feature spaces (overlap counts, overlap predictors, and distances).
+PR-curves were plotted and compared for 10 kb resolutions (Figures 4-8).
+For all curves, the baseline threshold used to assign a performance to a random model is defined as the ratio of genomic bins that overlapped with a flanked TAD boundary divided by the total number of genomic bins for the test set, respective to cell line and resolution.
+It was found that for the 10 kb resolution data, models with distance type predictors had consistently higher AUPRC values compared to other predictor types, across both cell line and resampling technique.
+This result was observed for the other resolutions as well (Supplementary Figuers 9-23l; Supplementary Table 2).
 
@@
 ## DATA RESAMPLING IMPROVES MODEL PREDICTION
-
-The low baseline thresholds represented by the dashed line in the precision-recall curves (Figure 4 and Supplementary Figure 2) indicate the wide disparity between majority and minority classes.
-Ideally a manageable dataset will have an imbalance ratio hovering near 1.
-However, in our study we found that there was an average imbalance ratio of 0.154 (SD=0.022) and 0.137 (SD=0.0181) for cell lines GM12878 and K562 respectively (Supplementary Figure 5).
-This highlights the need for suitable resampling techniques.
 

### 2019-02-01 Manuscript/manuscript.Rmd
manuscript edits

@@
 In this study we have developed an ensemble framework for predicting TAD boundaries that addresses class imbalance problem.
-We evaluated Hi-C data for the GM12878 cell line obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolution.
+We evaluated Hi-C data for both the GM12878 and K562 cell line obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolution.
 For each resolution, we examined the inclusion of three different predictor types, including distance as the measure of association between genomic elements.
@@
 Random forest classification was performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the TAD boundaries.
-Model performance was evaluated using accuracy, area under the precision-recall curve (AUPRC), F1 score, and Matthew's Correlation Coefficient (MCC).
-This process was then repeated for X additional cell lines including K562, ......
+Model performance was evaluated using area under the precision-recall curve (AUPRC), F1-Score, and MCC.
 
@@
 
-The efficacy of different ensemble systems was compared using various performance metrics including accuracy, F1-score, and MCC. These metrics are defined as follows:
+The efficacy of different ensemble systems was compared using the F1-score and MCC. These metrics are defined as follows:
 
-$$Accuracy = \frac{TP + TN}{TP + TN + FP + FN}$$
 $$F1 - Score = \frac{2TP}{2TP + FP + FN}$$
@@
 For the task of identifying the functional genomic elements that were most predictive of the formation of TAD boundaries, we evaluated the variable importances associated with each predictor of the random forest models associated with each resampling technique.
-For each model and within each tree, the prediction accuracy on the out-of-bag portion of the data was recorded.
+For each model and within each tree, the AUPRC on the out-of-bag portion of the data was recorded.
 Then the same was done after permuting each predictor variable.
-The difference between the two accuracies was then averaged over all trees, and normalized by the standard error.
+The difference between the two AUPRC values was then averaged over all trees, and normalized by the standard error.
 All random forest algorithms were implemented in R using the `caret` package version 6.0 [@kuhn2012caret].

### 2019-02-01 Scripts/performances.rmd
editted script of results

@@
 
+```{r}
+
+gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
+
+gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
+
+gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
+
+gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
+
+K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
+K562_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
+K562_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
+K562_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
+K562_10kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
+
+K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
+K562_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
+K562_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
+K562_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
+K562_25kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
+
+K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
+K562_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
+K562_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
+K562_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
+K562_50kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
+
+K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
+K562_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
+K562_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
+K562_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
+K562_100kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
+
+gm12878_10kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
+
+gm12878_25kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
+
+gm12878_50kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
+
+gm12878_100kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
+
+K562_10kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
+K562_10kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
+K562_10kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
+K562_10kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
+K562_10kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
+
+K562_25kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
+K562_25kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
+K562_25kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
+K562_25kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
+K562_25kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
+
+K562_50kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
+K562_50kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
+K562_50kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
+K562_50kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
+K562_50kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
+
+K562_100kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
+K562_100kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
+K562_100kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
+K562_100kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
+K562_100kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
+
+gm12878_10kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
+
+gm12878_25kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
+
+gm12878_50kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
+
+gm12878_100kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
+
+K562_10kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
+K562_10kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
+K562_10kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
+K562_10kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
+K562_10kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
+
+K562_25kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
+K562_25kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
+K562_25kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
+K562_25kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
+K562_25kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
+
+K562_50kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
+K562_50kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
+K562_50kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
+K562_50kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
+K562_50kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
+
+K562_100kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
+K562_100kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
+K562_100kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
+K562_100kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
+K562_100kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
+
+gm12878_10kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
+gm12878_10kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
+
+gm12878_25kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
+gm12878_25kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
+
+gm12878_50kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
+gm12878_50kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
+
+gm12878_100kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
+gm12878_100kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
+
+K562_10kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
+K562_10kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
+K562_10kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
+K562_10kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
+K562_10kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
+
+K562_25kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
+K562_25kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
+K562_25kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
+K562_25kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
+K562_25kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
+
+K562_50kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
+K562_50kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
+K562_50kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
+K562_50kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
+K562_50kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
+
+K562_100kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
+K562_100kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
+K562_100kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
+K562_100kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
+K562_100kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
+
+prcurvetable <- data.frame(CL=c(rep("GM12878", 20), rep("K562", 20)),
+                           Resolution=c(c(rep("10 kb", 5), 
+                                        rep("25 kb", 5),
+                                        rep("50 kb", 5),
+                                        rep("100 kb", 5)),
+                                        c(rep("10 kb", 5), 
+                                        rep("25 kb", 5),
+                                        rep("50 kb", 5),
+                                        rep("100 kb", 5))),
+                           ReSampling=rep(c("None",
+                                        "RUS",
+                                        "ROS",
+                                        "SMOTE",
+                                        "ROSE"),8))
+prcurvetable$OC <- c(gm12878_10kb_none_oc,
+gm12878_10kb_rus_oc,
+gm12878_10kb_ros_oc,
+gm12878_10kb_smote_oc,
+gm12878_10kb_rose_oc,
+gm12878_25kb_none_oc,
+gm12878_25kb_rus_oc,
+gm12878_25kb_ros_oc,
+gm12878_25kb_smote_oc,
+gm12878_25kb_rose_oc,
+gm12878_50kb_none_oc,
+gm12878_50kb_rus_oc,
+gm12878_50kb_ros_oc,
+gm12878_50kb_smote_oc,
+gm12878_50kb_rose_oc,
+gm12878_100kb_none_oc,
+gm12878_100kb_rus_oc,
+gm12878_100kb_ros_oc,
+gm12878_100kb_smote_oc,
+gm12878_100kb_rose_oc,
+K562_10kb_none_oc,
+K562_10kb_rus_oc,
+K562_10kb_ros_oc,
+K562_10kb_smote_oc,
+K562_10kb_rose_oc,
+K562_25kb_none_oc,
+K562_25kb_rus_oc,
+K562_25kb_ros_oc,
+K562_25kb_smote_oc,
+K562_25kb_rose_oc,
+K562_50kb_none_oc,
+K562_50kb_rus_oc,
+K562_50kb_ros_oc,
+K562_50kb_smote_oc,
+K562_50kb_rose_oc,
+K562_100kb_none_oc,
+K562_100kb_rus_oc,
+K562_100kb_ros_oc,
+K562_100kb_smote_oc,
+K562_100kb_rose_oc)
+
+prcurvetable$OP <- c(gm12878_10kb_none_OP,
+gm12878_10kb_rus_OP,
+gm12878_10kb_ros_OP,
+gm12878_10kb_smote_OP,
+gm12878_10kb_rose_OP,
+gm12878_25kb_none_OP,
+gm12878_25kb_rus_OP,
+gm12878_25kb_ros_OP,
+gm12878_25kb_smote_OP,
+gm12878_25kb_rose_OP,
+gm12878_50kb_none_OP,
+gm12878_50kb_rus_OP,
+gm12878_50kb_ros_OP,
+gm12878_50kb_smote_OP,
+gm12878_50kb_rose_OP,
+gm12878_100kb_none_OP,
+gm12878_100kb_rus_OP,
+gm12878_100kb_ros_OP,
+gm12878_100kb_smote_OP,
+gm12878_100kb_rose_OP,
+K562_10kb_none_OP,
+K562_10kb_rus_OP,
+K562_10kb_ros_OP,
+K562_10kb_smote_OP,
+K562_10kb_rose_OP,
+K562_25kb_none_OP,
+K562_25kb_rus_OP,
+K562_25kb_ros_OP,
+K562_25kb_smote_OP,
+K562_25kb_rose_OP,
+K562_50kb_none_OP,
+K562_50kb_rus_OP,
+K562_50kb_ros_OP,
+K562_50kb_smote_OP,
+K562_50kb_rose_OP,
+K562_100kb_none_OP,
+K562_100kb_rus_OP,
+K562_100kb_ros_OP,
+K562_100kb_smote_OP,
+K562_100kb_rose_OP)
+
+prcurvetable$Distance <- c(gm12878_10kb_none_Distance,
+gm12878_10kb_rus_Distance,
+gm12878_10kb_ros_Distance,
+gm12878_10kb_smote_Distance,
+gm12878_10kb_rose_Distance,
+gm12878_25kb_none_Distance,
+gm12878_25kb_rus_Distance,
+gm12878_25kb_ros_Distance,
+gm12878_25kb_smote_Distance,
+gm12878_25kb_rose_Distance,
+gm12878_50kb_none_Distance,
+gm12878_50kb_rus_Distance,
+gm12878_50kb_ros_Distance,
+gm12878_50kb_smote_Distance,
+gm12878_50kb_rose_Distance,
+gm12878_100kb_none_Distance,
+gm12878_100kb_rus_Distance,
+gm12878_100kb_ros_Distance,
+gm12878_100kb_smote_Distance,
+gm12878_100kb_rose_Distance,
+K562_10kb_none_Distance,
+K562_10kb_rus_Distance,
+K562_10kb_ros_Distance,
+K562_10kb_smote_Distance,
+K562_10kb_rose_Distance,
+K562_25kb_none_Distance,
+K562_25kb_rus_Distance,
+K562_25kb_ros_Distance,
+K562_25kb_smote_Distance,
+K562_25kb_rose_Distance,
+K562_50kb_none_Distance,
+K562_50kb_rus_Distance,
+K562_50kb_ros_Distance,
+K562_50kb_smote_Distance,
+K562_50kb_rose_Distance,
+K562_100kb_none_Distance,
+K562_100kb_rus_Distance,
+K562_100kb_ros_Distance,
+K562_100kb_smote_Distance,
+K562_100kb_rose_Distance)
+
+prcurvetable$All <- c(gm12878_10kb_none_all,
+gm12878_10kb_rus_all,
+gm12878_10kb_ros_all,
+gm12878_10kb_smote_all,
+gm12878_10kb_rose_all,
+gm12878_25kb_none_all,
+gm12878_25kb_rus_all,
+gm12878_25kb_ros_all,
+gm12878_25kb_smote_all,
+gm12878_25kb_rose_all,
+gm12878_50kb_none_all,
+gm12878_50kb_rus_all,
+gm12878_50kb_ros_all,
+gm12878_50kb_smote_all,
+gm12878_50kb_rose_all,
+gm12878_100kb_none_all,
+gm12878_100kb_rus_all,
+gm12878_100kb_ros_all,
+gm12878_100kb_smote_all,
+gm12878_100kb_rose_all,
+K562_10kb_none_all,
+K562_10kb_rus_all,
+K562_10kb_ros_all,
+K562_10kb_smote_all,
+K562_10kb_rose_all,
+K562_25kb_none_all,
+K562_25kb_rus_all,
+K562_25kb_ros_all,
+K562_25kb_smote_all,
+K562_25kb_rose_all,
+K562_50kb_none_all,
+K562_50kb_rus_all,
+K562_50kb_ros_all,
+K562_50kb_smote_all,
+K562_50kb_rose_all,
+K562_100kb_none_all,
+K562_100kb_rus_all,
+K562_100kb_ros_all,
+K562_100kb_smote_all,
+K562_100kb_rose_all)
+
+```
+
 ## RFE
@@
 
-#Barplots of performance metrics
+#Barplots of performance metrics for models with distance-type predictors
 
@@
 
-##Accuracy
-
-```
-
-##Comparing results for no class balancing
-
-###10kb
-
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")
-
-none.10 <- data.frame(Performance = c(rfperf1[9,2],
-								rfperf2[9,2],
-								rfperf3[9,2],
-								rfperf1[17,2],
-								rfperf2[17,2],
-								rfperf3[17,2],
-								rfperf1[16,2],
-								rfperf2[16,2],
-								rfperf3[16,2],
-								rfperf1[15,2],
-								rfperf2[15,2],
-								rfperf3[15,2]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-none.10$Predictor <- factor(none.10$Predictor, levels=c("OC", "OP", "Distance"))
-none.10$Metric <- factor(none.10$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###25kb
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")
-
-none.25 <- data.frame(Performance = c(rfperf1[9,2],
-								rfperf2[9,2],
-								rfperf3[9,2],
-								rfperf1[17,2],
-								rfperf2[17,2],
-								rfperf3[17,2],
-								rfperf1[16,2],
-								rfperf2[16,2],
-								rfperf3[16,2],
-								rfperf1[15,2],
-								rfperf2[15,2],
-								rfperf3[15,2]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-none.25$Predictor <- factor(none.25$Predictor, levels=c("OC", "OP", "Distance"))
-none.25$Metric <- factor(none.25$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###50kb
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")
-
-none.50 <- data.frame(Performance = c(rfperf1[9,2],
-								rfperf2[9,2],
-								rfperf3[9,2],
-								rfperf1[17,2],
-								rfperf2[17,2],
-								rfperf3[17,2],
-								rfperf1[16,2],
-								rfperf2[16,2],
-								rfperf3[16,2],
-								rfperf1[15,2],
-								rfperf2[15,2],
-								rfperf3[15,2]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-none.50$Predictor <- factor(none.50$Predictor, levels=c("OC", "OP", "Distance"))
-none.50$Metric <- factor(none.50$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###100kb
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")
-
-none.100 <- data.frame(Performance = c(rfperf1[9,2],
-								rfperf2[9,2],
-								rfperf3[9,2],
-								rfperf1[17,2],
-								rfperf2[17,2],
-								rfperf3[17,2],
-								rfperf1[16,2],
-								rfperf2[16,2],
-								rfperf3[16,2],
-								rfperf1[15,2],
-								rfperf2[15,2],
-								rfperf3[15,2]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-none.100$Predictor <- factor(none.100$Predictor, levels=c("OC", "OP", "Distance"))
-none.100$Metric <- factor(none.100$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###Plots
-```{r}
-none.data <- rbind.data.frame(none.10,none.25,none.50,none.100) 
-none.data$Resolution <- c(rep("10 kb", 12), rep("25 kb", 12), rep("50 kb", 12), rep("100 kb", 12))
-none.data$Resolution <- factor(none.data$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
-
-allnoneplots <- ggplot(none.data, aes(fill=Resolution, y=Performance, x=Resolution)) +
+##None
+rfperf_gm12878_10kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_10kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_10kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_10kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
+
+##ROSE
+rfperf_gm12878_10kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
+
+#K562
+
+##None
+rfperf_K562_10kb_none <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_10kb_rus <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_10kb_ros <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_10kb_smote <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
+
+##ROSE
+rfperf_K562_10kb_rose <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
+
+all10kbresults <- data.frame(Resampling=c(rep("None", 8),
+                                       rep("RUS", 8),
+                                       rep("ROS", 8),
+                                       rep("SMOTE", 8),
+                                       rep("ROSE", 8)),
+                          CL=rep(c(rep("GM12878",4),
+                               rep("K562", 4)),5),
+                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
+
+all10kbresults$Performance <- c(round(rfperf_gm12878_10kb_none[9,2],2),
+                                round(rfperf_gm12878_10kb_none[19,2],2),
+                                round(rfperf_gm12878_10kb_none[16,2],2),
+                                round(rfperf_gm12878_10kb_none[15,2],2),
+                                round(rfperf_K562_10kb_none[9,2],2),
+                                round(rfperf_K562_10kb_none[19,2],2),
+                                round(rfperf_K562_10kb_none[16,2],2),
+                                round(rfperf_K562_10kb_none[15,2],2),
+                                round(rfperf_gm12878_10kb_rus[9,2],2),
+                                round(rfperf_gm12878_10kb_rus[19,2],2),
+                                round(rfperf_gm12878_10kb_rus[16,2],2),
+                                round(rfperf_gm12878_10kb_rus[15,2],2),
+                                round(rfperf_K562_10kb_rus[9,2],2),
+                                round(rfperf_K562_10kb_rus[19,2],2),
+                                round(rfperf_K562_10kb_rus[16,2],2),
+                                round(rfperf_K562_10kb_rus[15,2],2),
+                                round(rfperf_gm12878_10kb_ros[9,2],2),
+                                round(rfperf_gm12878_10kb_ros[19,2],2),
+                                round(rfperf_gm12878_10kb_ros[16,2],2),
+                                round(rfperf_gm12878_10kb_ros[15,2],2),
+                                round(rfperf_K562_10kb_ros[9,2],2),
+                                round(rfperf_K562_10kb_ros[19,2],2),
+                                round(rfperf_K562_10kb_ros[16,2],2),
+                                round(rfperf_K562_10kb_ros[15,2],2),
+                                round(rfperf_gm12878_10kb_smote[9,2],2),
+                                round(rfperf_gm12878_10kb_smote[19,2],2),
+                                round(rfperf_gm12878_10kb_smote[16,2],2),
+                                round(rfperf_gm12878_10kb_smote[15,2],2),
+                                round(rfperf_K562_10kb_smote[9,2],2),
+                                round(rfperf_K562_10kb_smote[19,2],2),
+                                round(rfperf_K562_10kb_smote[16,2],2),
+                                round(rfperf_K562_10kb_smote[15,2],2),
+                                round(rfperf_gm12878_10kb_rose[9,2],2),
+                                round(rfperf_gm12878_10kb_rose[19,2],2),
+                                round(rfperf_gm12878_10kb_rose[16,2],2),
+                                round(rfperf_gm12878_10kb_rose[15,2],2),
+                                round(rfperf_K562_10kb_rose[9,2],2),
+                                round(rfperf_K562_10kb_rose[19,2],2),
+                                round(rfperf_K562_10kb_rose[16,2],2),
+                                round(rfperf_K562_10kb_rose[15,2],2))
+
+all10kbresults$Resampling <- factor(all10kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
+all10kbresults$CL <- factor(all10kbresults$CL, levels=c("GM12878", "K562"))
+all10kbresults$Metric <- factor(all10kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
+
+none10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="None"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
   geom_bar( stat="identity", position="dodge") +
-	facet_grid(Predictor ~ Metric) +
-	ylab("Performance")+
-	xlab("Resolution")+
+  xlab("Cell Line") +
+  ylim(0,1)+
   theme_bw() +
-  guides(fill=FALSE)+
+  theme_minimal() +
+  #guides(fill=FALSE)+
 	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
         axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
         legend.text=element_text(size=15),
-        legend.title=element_text(size=20),
-		legend.position="bottom")
-
-```
-
-###Tables
-
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")
-
-rfperf4 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
-rfperf5 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
-rfperf6 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")
-
-rfperf7 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
-rfperf8 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
-rfperf9 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")
-
-rfperf10 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/LASSO/RF/rfperf.rds")
-rfperf11 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/LASSO/RF/rfperf.rds")
-rfperf12 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/LASSO/RF/rfperf.rds")
-
-nonetab <- cbind.data.frame(rfperf1$Metric,
-                            rfperf1$Performance,
-                            rfperf2$Performance,
-                            rfperf3$Performance,
-                            rfperf4$Performance,
-                            rfperf5$Performance,
-                            rfperf6$Performance,
-                            rfperf7$Performance,
-                            rfperf8$Performance,
-                            rfperf9$Performance,
-                            rfperf10$Performance,
-                            rfperf11$Performance,
-                            rfperf12$Performance)
-nonetab[,-1] <- round(nonetab[,-1], 3)
-datatable(nonetab)
-```
-
-##Comparing results for RUS
-
-###10kb
-
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-RUS.10 <- data.frame(Performance = c(rfperf1[9],
-								rfperf2[9],
-								rfperf3[9],
-								rfperf1[17],
-								rfperf2[17],
-								rfperf3[17],
-								rfperf1[16],
-								rfperf2[16],
-								rfperf3[16],
-								rfperf1[15],
-								rfperf2[15],
-								rfperf3[15]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-RUS.10$Predictor <- factor(RUS.10$Predictor, levels=c("OC", "OP", "Distance"))
-RUS.10$Metric <- factor(RUS.10$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###25kb
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-RUS.25 <- data.frame(Performance = c(rfperf1[9],
-								rfperf2[9],
-								rfperf3[9],
-								rfperf1[17],
-								rfperf2[17],
-								rfperf3[17],
-								rfperf1[16],
-								rfperf2[16],
-								rfperf3[16],
-								rfperf1[15],
-								rfperf2[15],
-								rfperf3[15]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-RUS.25$Predictor <- factor(RUS.25$Predictor, levels=c("OC", "OP", "Distance"))
-RUS.25$Metric <- factor(RUS.25$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###50kb
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-RUS.50 <- data.frame(Performance = c(rfperf1[9],
-								rfperf2[9],
-								rfperf3[9],
-								rfperf1[17],
-								rfperf2[17],
-								rfperf3[17],
-								rfperf1[16],
-								rfperf2[16],
-								rfperf3[16],
-								rfperf1[15],
-								rfperf2[15],
-								rfperf3[15]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-RUS.50$Predictor <- factor(RUS.50$Predictor, levels=c("OC", "OP", "Distance"))
-RUS.50$Metric <- factor(RUS.50$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###100kb
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-RUS.100 <- data.frame(Performance = c(rfperf1[9],
-								rfperf2[9],
-								rfperf3[9],
-								rfperf1[17],
-								rfperf2[17],
-								rfperf3[17],
-								rfperf1[16],
-								rfperf2[16],
-								rfperf3[16],
-								rfperf1[15],
-								rfperf2[15],
-								rfperf3[15]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-RUS.100$Predictor <- factor(RUS.100$Predictor, levels=c("OC", "OP", "Distance"))
-RUS.100$Metric <- factor(RUS.100$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###Plots
-```{r}
-RUS.data <- rbind.data.frame(RUS.10,RUS.25,RUS.50,RUS.100) 
-RUS.data$Resolution <- c(rep("10 kb", 12), rep("25 kb", 12), rep("50 kb", 12), rep("100 kb", 12))
-RUS.data$Resolution <- factor(RUS.data$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
-
-allRUSplots <- ggplot(RUS.data, aes(fill=Resolution, y=Performance, x=Resolution)) +
+        legend.title=element_text(size=20))
+
+rus10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="RUS"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
   geom_bar( stat="identity", position="dodge") +
-	facet_grid(Predictor ~ Metric) +
-	ylab("Performance")+
-	xlab("Resolution")+
+  xlab("Cell Line") +
+  ylim(0,1)+
   theme_bw() +
-  guides(fill=FALSE)+
+  theme_minimal() +
+  #guides(fill=FALSE)+
 	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
         axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
         legend.text=element_text(size=15),
-        legend.title=element_text(size=20),
-		legend.position="bottom")
-
-```
-
-###Tables
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-rfperf4 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
-rfperf4 <- rowMeans(rfperf4)
-rfperf5 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
-rfperf5 <- rowMeans(rfperf5)
-rfperf6 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
-rfperf6 <- rowMeans(rfperf6)
-
-rfperf7 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
-rfperf7 <- rowMeans(rfperf7)
-rfperf8 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
-rfperf8 <- rowMeans(rfperf8)
-rfperf9 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
-rfperf9 <- rowMeans(rfperf9)
-
-rfperf10 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
-rfperf10 <- rowMeans(rfperf10)
-rfperf11 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
-rfperf11 <- rowMeans(rfperf11)
-rfperf12 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
-rfperf12 <- rowMeans(rfperf12)
-
-RUStab <- cbind.data.frame(names(rfperf1),
-                            rfperf1,
-                            rfperf2,
-                            rfperf3,
-                            rfperf4,
-                            rfperf5,
-                            rfperf6,
-                            rfperf7,
-                            rfperf8,
-                            rfperf9,
-                            rfperf10,
-                            rfperf11,
-                            rfperf12)
-RUStab[,-1] <- round(RUStab[,-1], 3)
-datatable(RUStab)
-```
-
-##Comparing results for SMOTE
-
-###10kb
-
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-SMOTE.10 <- data.frame(Performance = c(rfperf1[9],
-								rfperf2[9],
-								rfperf3[9],
-								rfperf1[17],
-								rfperf2[17],
-								rfperf3[17],
-								rfperf1[16],
-								rfperf2[16],
-								rfperf3[16],
-								rfperf1[15],
-								rfperf2[15],
-								rfperf3[15]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-SMOTE.10$Predictor <- factor(SMOTE.10$Predictor, levels=c("OC", "OP", "Distance"))
-SMOTE.10$Metric <- factor(SMOTE.10$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###25kb
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-SMOTE.25 <- data.frame(Performance = c(rfperf1[9],
-								rfperf2[9],
-								rfperf3[9],
-								rfperf1[17],
-								rfperf2[17],
-								rfperf3[17],
-								rfperf1[16],
-								rfperf2[16],
-								rfperf3[16],
-								rfperf1[15],
-								rfperf2[15],
-								rfperf3[15]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-SMOTE.25$Predictor <- factor(SMOTE.25$Predictor, levels=c("OC", "OP", "Distance"))
-SMOTE.25$Metric <- factor(SMOTE.25$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###50kb
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-SMOTE.50 <- data.frame(Performance = c(rfperf1[9],
-								rfperf2[9],
-								rfperf3[9],
-								rfperf1[17],
-								rfperf2[17],
-								rfperf3[17],
-								rfperf1[16],
-								rfperf2[16],
-								rfperf3[16],
-								rfperf1[15],
-								rfperf2[15],
-								rfperf3[15]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-SMOTE.50$Predictor <- factor(SMOTE.50$Predictor, levels=c("OC", "OP", "Distance"))
-SMOTE.50$Metric <- factor(SMOTE.50$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###100kb
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-SMOTE.100 <- data.frame(Performance = c(rfperf1[9],
-								NA,#rfperf2[9],
-								rfperf3[9],
-								rfperf1[17],
-								NA,#rfperf2[17],
-								rfperf3[17],
-								rfperf1[16],
-								NA,#rfperf2[16],
-								rfperf3[16],
-								rfperf1[15],
-								NA,#rfperf2[15],
-								rfperf3[15]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-SMOTE.100$Predictor <- factor(SMOTE.100$Predictor, levels=c("OC", "OP", "Distance"))
-SMOTE.100$Metric <- factor(SMOTE.100$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###Plots
-```{r}
-SMOTE.data <- rbind.data.frame(SMOTE.10,SMOTE.25,SMOTE.50,SMOTE.100) 
-SMOTE.data$Resolution <- c(rep("10 kb", 12), rep("25 kb", 12), rep("50 kb", 12), rep("100 kb", 12))
-SMOTE.data$Resolution <- factor(SMOTE.data$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
-
-allSMOTEplots <- ggplot(SMOTE.data, aes(fill=Resolution, y=Performance, x=Resolution)) +
+        legend.title=element_text(size=20))
+
+ros10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="ROS"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
   geom_bar( stat="identity", position="dodge") +
-	facet_grid(Predictor ~ Metric) +
-	ylab("Performance")+
-	xlab("Resolution")+
+  xlab("Cell Line") +
+  ylim(0,1)+
   theme_bw() +
-  guides(fill=FALSE)+
+  theme_minimal() +
+  #guides(fill=FALSE)+
 	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
         axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
         legend.text=element_text(size=15),
-        legend.title=element_text(size=20),
-		legend.position="bottom")
-
-```
-
-###Tables
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-rfperf4 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
-rfperf4 <- rowMeans(rfperf4)
-rfperf5 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
-rfperf5 <- rowMeans(rfperf5)
-rfperf6 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
-rfperf6 <- rowMeans(rfperf6)
-
-rfperf7 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
-rfperf7 <- rowMeans(rfperf7)
-rfperf8 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
-rfperf8 <- rowMeans(rfperf8)
-rfperf9 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
-rfperf9 <- rowMeans(rfperf9)
-
-rfperf10 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/LASSO/RF/rfperf.rds")
-rfperf10 <- rowMeans(rfperf10)
-rfperf11 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/LASSO/RF/rfperf.rds")
-rfperf11 <- rowMeans(rfperf11)
-rfperf12 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/LASSO/RF/rfperf.rds")
-rfperf12 <- rowMeans(rfperf12)
-
-SMOTEtab <- cbind.data.frame(names(rfperf1),
-                            rfperf1,
-                            rfperf2,
-                            rfperf3,
-                            rfperf4,
-                            rfperf5,
-                            rfperf6,
-                            rfperf7,
-                            rfperf8,
-                            rfperf9,
-                            rfperf10,
-                            rep(NA,18),#rfperf11,
-                            rfperf12)
-SMOTEtab[,-c(1)] <- round(SMOTEtab[,-c(1)], 3)
-SMOTEtab[,-c(1,12)] <- round(SMOTEtab[,-c(1,12)], 3)
-datatable(SMOTEtab)
-```
-
-##Comparing results for SMOTE
-
-###10kb
-
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-ROS.10 <- data.frame(Performance = c(rfperf1[9],
-								rfperf2[9],
-								rfperf3[9],
-								rfperf1[17],
-								rfperf2[17],
-								rfperf3[17],
-								rfperf1[16],
-								rfperf2[16],
-								rfperf3[16],
-								rfperf1[15],
-								rfperf2[15],
-								rfperf3[15]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-ROS.10$Predictor <- factor(ROS.10$Predictor, levels=c("OC", "OP", "Distance"))
-ROS.10$Metric <- factor(ROS.10$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###25kb
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-ROS.25 <- data.frame(Performance = c(rfperf1[9],
-								rfperf2[9],
-								rfperf3[9],
-								rfperf1[17],
-								rfperf2[17],
-								rfperf3[17],
-								rfperf1[16],
-								rfperf2[16],
-								rfperf3[16],
-								rfperf1[15],
-								rfperf2[15],
-								rfperf3[15]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-ROS.25$Predictor <- factor(ROS.25$Predictor, levels=c("OC", "OP", "Distance"))
-ROS.25$Metric <- factor(ROS.25$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###50kb
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-ROS.50 <- data.frame(Performance = c(rfperf1[9],
-								rfperf2[9],
-								rfperf3[9],
-								rfperf1[17],
-								rfperf2[17],
-								rfperf3[17],
-								rfperf1[16],
-								rfperf2[16],
-								rfperf3[16],
-								rfperf1[15],
-								rfperf2[15],
-								rfperf3[15]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-ROS.50$Predictor <- factor(ROS.50$Predictor, levels=c("OC", "OP", "Distance"))
-ROS.50$Metric <- factor(ROS.50$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###100kb
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-ROS.100 <- data.frame(Performance = c(rfperf1[9],
-								rfperf2[9],
-								rfperf3[9],
-								rfperf1[17],
-								rfperf2[17],
-								rfperf3[17],
-								rfperf1[16],
-								rfperf2[16],
-								rfperf3[16],
-								rfperf1[15],
-								rfperf2[15],
-								rfperf3[15]),
-				Predictor = rep(c("OC", "OP", "Distance"), 4),
-				Metric = c(rep("Accuracy", 3), rep("AUC", 3), rep("F1-Score", 3), rep("MCC", 3)))
-ROS.100$Predictor <- factor(ROS.100$Predictor, levels=c("OC", "OP", "Distance"))
-ROS.100$Metric <- factor(ROS.100$Metric, levels=c("Accuracy", "AUC", "F1-Score", "MCC"))
-```
-
-###Plots
-```{r}
-ROS.data <- rbind.data.frame(ROS.10,ROS.25,ROS.50,ROS.100) 
-ROS.data$Resolution <- c(rep("10 kb", 12), rep("25 kb", 12), rep("50 kb", 12), rep("100 kb", 12))
-ROS.data$Resolution <- factor(ROS.data$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
-
-allROSplots <- ggplot(ROS.data, aes(fill=Resolution, y=Performance, x=Resolution)) +
+        legend.title=element_text(size=20))
+
+smote10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="SMOTE"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
   geom_bar( stat="identity", position="dodge") +
-	facet_grid(Predictor ~ Metric) +
-	ylab("Performance")+
-	xlab("Resolution")+
+  xlab("Cell Line") +
+  ylim(0,1)+
   theme_bw() +
-  guides(fill=FALSE)+
+  theme_minimal() +
+  #guides(fill=FALSE)+
 	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
         axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
         legend.text=element_text(size=15),
-        legend.title=element_text(size=20),
-		legend.position="bottom")
-
-```
-
-###Tables
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- rowMeans(rfperf1)
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- rowMeans(rfperf2)
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- rowMeans(rfperf3)
-
-rfperf4 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
-rfperf4 <- rowMeans(rfperf4)
-rfperf5 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
-rfperf5 <- rowMeans(rfperf5)
-rfperf6 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
-rfperf6 <- rowMeans(rfperf6)
-
-rfperf7 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
-rfperf7 <- rowMeans(rfperf7)
-rfperf8 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
-rfperf8 <- rowMeans(rfperf8)
-rfperf9 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
-rfperf9 <- rowMeans(rfperf9)
-
-rfperf10 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/LASSO/RF/rfperf.rds")
-rfperf10 <- rowMeans(rfperf10)
-rfperf11 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/LASSO/RF/rfperf.rds")
-rfperf11 <- rowMeans(rfperf11)
-rfperf12 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/LASSO/RF/rfperf.rds")
-rfperf12 <- rowMeans(rfperf12)
-
-ROStab <- cbind.data.frame(names(rfperf1),
-                            rfperf1,
-                            rfperf2,
-                            rfperf3,
-                            rfperf4,
-                            rfperf5,
-                            rfperf6,
-                            rfperf7,
-                            rfperf8,
-                            rfperf9,
-                            rfperf10,
-                            rfperf11,
-                            rfperf12)
-ROStab[,-1] <- round(ROStab[,-1], 3)
-datatable(ROStab)
-```
-
-#Comparing performance for distance predictors using RUS 
-##10kb
-```{r}
-rfperf1 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
-rfperf1 <- cbind.data.frame(rownames(rfperf1),round(rowMeans(rfperf1),3))
-
-rfperf2 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
-rfperf2 <- cbind.data.frame(rownames(rfperf2),round(rowMeans(rfperf2),3))
-
-rfperf3 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
-rfperf3 <- cbind.data.frame(rownames(rfperf3),round(rowMeans(rfperf3),3))
-
-```
-##25kb
-```{r}
-rfperf4 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
-rfperf4 <- cbind.data.frame(rownames(rfperf4),round(rowMeans(rfperf4),3))
-
-rfperf5 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
-rfperf5 <- cbind.data.frame(rownames(rfperf5),round(rowMeans(rfperf5),3))
-
-rfperf6 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
-rfperf6 <- cbind.data.frame(rownames(rfperf6),round(rowMeans(rfperf6),3))
-```
-##50kb
-```{r}
-rfperf7 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
-rfperf7 <- cbind.data.frame(rownames(rfperf7),round(rowMeans(rfperf7),3))
-
-rfperf8 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
-rfperf8 <- cbind.data.frame(rownames(rfperf8),round(rowMeans(rfperf8),3))
-
-rfperf9 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
-rfperf9 <- cbind.data.frame(rownames(rfperf9),round(rowMeans(rfperf9),3))
-
-```
-##100kb
-```{r}
-rfperf10 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/LASSO/RF/rfperf.rds")
-rfperf10 <- cbind.data.frame(rownames(rfperf10),round(rowMeans(rfperf10),3))
-
-rfperf11 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/LASSO/RF/rfperf.rds")
-rfperf11 <- cbind.data.frame(rownames(rfperf11),round(rowMeans(rfperf11),3))
-
-rfperf12 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/LASSO/RF/rfperf.rds")
-rfperf12 <- cbind.data.frame(rownames(rfperf12),round(rowMeans(rfperf12),3))
-
-```
-
-##Plots
-```{r}
-distperftab <- data.frame(Performance =
-                    c(rfperf1[9,2],
-											rfperf1[17,2],
-											rfperf1[16,2],
-											rfperf1[15,2],
-											rfperf2[9,2],
-											rfperf2[17,2],
-											rfperf2[16,2],
-											rfperf2[15,2],
-											rfperf3[9,2],
-											rfperf3[17,2],
-											rfperf3[16,2],
-											rfperf3[15,2],
-											rfperf4[9,2],
-											rfperf4[17,2],
-											rfperf4[16,2],
-											rfperf4[15,2],
-											rfperf5[9,2],
-											rfperf5[17,2],
-											rfperf5[16,2],
-											rfperf5[15,2],
-											rfperf6[9,2],
-											rfperf6[17,2],
-											rfperf6[16,2],
-											rfperf6[15,2],
-											rfperf7[9,2],
-											rfperf7[17,2],
-											rfperf7[16,2],
-											rfperf7[15,2],
-											rfperf8[9,2],
-											rfperf8[17,2],
-											rfperf8[16,2],
-											rfperf8[15,2],
-											rfperf9[9,2],
-											rfperf9[17,2],
-											rfperf9[16,2],
-											rfperf9[15,2],
-											rfperf10[9,2],
-											rfperf10[17,2],
-											rfperf10[16,2],
-											rfperf10[15,2],
-											rfperf11[9,2],
-											rfperf11[17,2],
-											rfperf11[16,2],
-											rfperf11[15,2],
-											rfperf12[9,2],
-											rfperf12[17,2],
-											rfperf12[16,2],
-											rfperf12[15,2]),
-							Metric = rep(c("Accuracy", "AUC", "F1-Score", "MCC"), 12),
-							Resolution = c(rep("10kb", 12), rep("25kb", 12), rep("50kb", 12), rep("100kb", 12)),
-							Predictor = rep(c(rep("OC", 4), rep("OP", 4), rep("Distance", 4)), 4))
-distperftab$Metric <- factor(distperftab$Metric, levels = c("Accuracy", "AUC", "F1-Score", "MCC"))
-distperftab$Resolution <- factor(distperftab$Resolution, levels = c("10kb","25kb","50kb","100kb"))
-distperftab$Predictor <- factor(distperftab$Predictor, levels = c("OC", "OP", "Distance"))
-
-p.distperfsbar <- ggplot(distperftab, aes(fill=Predictor, y=Performance, x=Predictor)) +
+        legend.title=element_text(size=20))
+
+rose10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="ROSE"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
   geom_bar( stat="identity", position="dodge") +
-	facet_grid(Resolution ~ Metric) +
-  ylab("Performance")+
-	xlab("Predictor Type")+
+  xlab("Cell Line") +
+  ylim(0,1)+
   theme_bw() +
-  guides(fill=FALSE)+
+  theme_minimal() +
+  #guides(fill=FALSE)+
 	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
         axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
         legend.text=element_text(size=15),
-        legend.title=element_text(size=20),
-		legend.position="bottom")
-
-#ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/p.distperfsbarline.png")
-```
-
-#Comparing performances across resolutions for RUS and distance
+        legend.title=element_text(size=20))
+
+######################################################################
+
+#comparing only f1 and mcc
+
+f1mcc10kbplot <- ggplot(all10kbresults[which(all10kbresults$Metric=="F1-Score" |
+                                               all10kbresults$Metric=="MCC"),],
+                       aes(x=Resampling, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ CL) +
+  xlab("Resampling Technique") +
+  theme_minimal() +
+  theme_bw() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+```
+
+##25kb
+
+```{r}
+#GM12878
+
+##None
+rfperf_gm12878_25kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_25kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_25kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_25kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
+
+##ROSE
+rfperf_gm12878_25kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
+
+#K562
+
+##None
+rfperf_K562_25kb_none <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_25kb_rus <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_25kb_ros <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_25kb_smote <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
+
+##ROSE
+rfperf_K562_25kb_rose <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
+
+all25kbresults <- data.frame(Resampling=c(rep("None", 8),
+                                       rep("RUS", 8),
+                                       rep("ROS", 8),
+                                       rep("SMOTE", 8),
+                                       rep("ROSE", 8)),
+                          CL=rep(c(rep("GM12878",4),
+                               rep("K562", 4)),5),
+                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
+
+all25kbresults$Performance <- c(round(rfperf_gm12878_25kb_none[9,2],2),
+                                round(rfperf_gm12878_25kb_none[19,2],2),
+                                round(rfperf_gm12878_25kb_none[16,2],2),
+                                round(rfperf_gm12878_25kb_none[15,2],2),
+                                round(rfperf_K562_25kb_none[9,2],2),
+                                round(rfperf_K562_25kb_none[19,2],2),
+                                round(rfperf_K562_25kb_none[16,2],2),
+                                round(rfperf_K562_25kb_none[15,2],2),
+                                round(rfperf_gm12878_25kb_rus[9,2],2),
+                                round(rfperf_gm12878_25kb_rus[19,2],2),
+                                round(rfperf_gm12878_25kb_rus[16,2],2),
+                                round(rfperf_gm12878_25kb_rus[15,2],2),
+                                round(rfperf_K562_25kb_rus[9,2],2),
+                                round(rfperf_K562_25kb_rus[19,2],2),
+                                round(rfperf_K562_25kb_rus[16,2],2),
+                                round(rfperf_K562_25kb_rus[15,2],2),
+                                round(rfperf_gm12878_25kb_ros[9,2],2),
+                                round(rfperf_gm12878_25kb_ros[19,2],2),
+                                round(rfperf_gm12878_25kb_ros[16,2],2),
+                                round(rfperf_gm12878_25kb_ros[15,2],2),
+                                round(rfperf_K562_25kb_ros[9,2],2),
+                                round(rfperf_K562_25kb_ros[19,2],2),
+                                round(rfperf_K562_25kb_ros[16,2],2),
+                                round(rfperf_K562_25kb_ros[15,2],2),
+                                round(rfperf_gm12878_25kb_smote[9,2],2),
+                                round(rfperf_gm12878_25kb_smote[19,2],2),
+                                round(rfperf_gm12878_25kb_smote[16,2],2),
+                                round(rfperf_gm12878_25kb_smote[15,2],2),
+                                round(rfperf_K562_25kb_smote[9,2],2),
+                                round(rfperf_K562_25kb_smote[19,2],2),
+                                round(rfperf_K562_25kb_smote[16,2],2),
+                                round(rfperf_K562_25kb_smote[15,2],2),
+                                round(rfperf_gm12878_25kb_rose[9,2],2),
+                                round(rfperf_gm12878_25kb_rose[19,2],2),
+                                round(rfperf_gm12878_25kb_rose[16,2],2),
+                                round(rfperf_gm12878_25kb_rose[15,2],2),
+                                round(rfperf_K562_25kb_rose[9,2],2),
+                                round(rfperf_K562_25kb_rose[19,2],2),
+                                round(rfperf_K562_25kb_rose[16,2],2),
+                                round(rfperf_K562_25kb_rose[15,2],2))
+
+all25kbresults$Resampling <- factor(all25kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
+all25kbresults$CL <- factor(all25kbresults$CL, levels=c("GM12878", "K562"))
+all25kbresults$Metric <- factor(all25kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
+
+none25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="None"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+rus25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="RUS"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+ros25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="ROS"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+smote25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="SMOTE"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+rose25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="ROSE"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+######################################################################
+
+#comparing only f1 and mcc
+
+f1mcc25kbplot <- ggplot(all25kbresults[which(all25kbresults$Metric=="F1-Score" |
+                                               all25kbresults$Metric=="MCC"),],
+                       aes(x=Resampling, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ CL) +
+  xlab("Resampling Technique") +
+  theme_minimal() +
+  theme_bw() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+```
+
+##50kb
+
+```{r}
+#GM12878
+
+##None
+rfperf_gm12878_50kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_50kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_50kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_50kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
+
+##ROSE
+rfperf_gm12878_50kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
+
+#K562
+
+##None
+rfperf_K562_50kb_none <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_50kb_rus <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_50kb_ros <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_50kb_smote <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
+
+##ROSE
+rfperf_K562_50kb_rose <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
+
+all50kbresults <- data.frame(Resampling=c(rep("None", 8),
+                                       rep("RUS", 8),
+                                       rep("ROS", 8),
+                                       rep("SMOTE", 8),
+                                       rep("ROSE", 8)),
+                          CL=rep(c(rep("GM12878",4),
+                               rep("K562", 4)),5),
+                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
+
+all50kbresults$Performance <- c(round(rfperf_gm12878_50kb_none[9,2],2),
+                                round(rfperf_gm12878_50kb_none[19,2],2),
+                                round(rfperf_gm12878_50kb_none[16,2],2),
+                                round(rfperf_gm12878_50kb_none[15,2],2),
+                                round(rfperf_K562_50kb_none[9,2],2),
+                                round(rfperf_K562_50kb_none[19,2],2),
+                                round(rfperf_K562_50kb_none[16,2],2),
+                                round(rfperf_K562_50kb_none[15,2],2),
+                                round(rfperf_gm12878_50kb_rus[9,2],2),
+                                round(rfperf_gm12878_50kb_rus[19,2],2),
+                                round(rfperf_gm12878_50kb_rus[16,2],2),
+                                round(rfperf_gm12878_50kb_rus[15,2],2),
+                                round(rfperf_K562_50kb_rus[9,2],2),
+                                round(rfperf_K562_50kb_rus[19,2],2),
+                                round(rfperf_K562_50kb_rus[16,2],2),
+                                round(rfperf_K562_50kb_rus[15,2],2),
+                                round(rfperf_gm12878_50kb_ros[9,2],2),
+                                round(rfperf_gm12878_50kb_ros[19,2],2),
+                                round(rfperf_gm12878_50kb_ros[16,2],2),
+                                round(rfperf_gm12878_50kb_ros[15,2],2),
+                                round(rfperf_K562_50kb_ros[9,2],2),
+                                round(rfperf_K562_50kb_ros[19,2],2),
+                                round(rfperf_K562_50kb_ros[16,2],2),
+                                round(rfperf_K562_50kb_ros[15,2],2),
+                                round(rfperf_gm12878_50kb_smote[9,2],2),
+                                round(rfperf_gm12878_50kb_smote[19,2],2),
+                                round(rfperf_gm12878_50kb_smote[16,2],2),
+                                round(rfperf_gm12878_50kb_smote[15,2],2),
+                                round(rfperf_K562_50kb_smote[9,2],2),
+                                round(rfperf_K562_50kb_smote[19,2],2),
+                                round(rfperf_K562_50kb_smote[16,2],2),
+                                round(rfperf_K562_50kb_smote[15,2],2),
+                                round(rfperf_gm12878_50kb_rose[9,2],2),
+                                round(rfperf_gm12878_50kb_rose[19,2],2),
+                                round(rfperf_gm12878_50kb_rose[16,2],2),
+                                round(rfperf_gm12878_50kb_rose[15,2],2),
+                                round(rfperf_K562_50kb_rose[9,2],2),
+                                round(rfperf_K562_50kb_rose[19,2],2),
+                                round(rfperf_K562_50kb_rose[16,2],2),
+                                round(rfperf_K562_50kb_rose[15,2],2))
+
+all50kbresults$Resampling <- factor(all50kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
+all50kbresults$CL <- factor(all50kbresults$CL, levels=c("GM12878", "K562"))
+all50kbresults$Metric <- factor(all50kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
+
+none50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="None"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+rus50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="RUS"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+ros50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="ROS"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+smote50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="SMOTE"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+rose50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="ROSE"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+######################################################################
+
+#comparing only f1 and mcc
+
+f1mcc50kbplot <- ggplot(all50kbresults[which(all50kbresults$Metric=="F1-Score" |
+                                               all50kbresults$Metric=="MCC"),],
+                       aes(x=Resampling, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ CL) +
+  xlab("Resampling Technique") +
+  theme_minimal() +
+  theme_bw() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+```
+
+##100kb
+
+```{r}
+#GM12878
+
+##None
+rfperf_gm12878_100kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_100kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_100kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_100kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
+
+##ROSE
+rfperf_gm12878_100kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
+
+#K562
+
+##None
+rfperf_K562_100kb_none <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_100kb_rus <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_100kb_ros <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_100kb_smote <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
+
+##ROSE
+rfperf_K562_100kb_rose <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
+
+all100kbresults <- data.frame(Resampling=c(rep("None", 8),
+                                       rep("RUS", 8),
+                                       rep("ROS", 8),
+                                       rep("SMOTE", 8),
+                                       rep("ROSE", 8)),
+                          CL=rep(c(rep("GM12878",4),
+                               rep("K562", 4)),5),
+                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
+
+all100kbresults$Performance <- c(round(rfperf_gm12878_100kb_none[9,2],2),
+                                round(rfperf_gm12878_100kb_none[19,2],2),
+                                round(rfperf_gm12878_100kb_none[16,2],2),
+                                round(rfperf_gm12878_100kb_none[15,2],2),
+                                round(rfperf_K562_100kb_none[9,2],2),
+                                round(rfperf_K562_100kb_none[19,2],2),
+                                round(rfperf_K562_100kb_none[16,2],2),
+                                round(rfperf_K562_100kb_none[15,2],2),
+                                round(rfperf_gm12878_100kb_rus[9,2],2),
+                                round(rfperf_gm12878_100kb_rus[19,2],2),
+                                round(rfperf_gm12878_100kb_rus[16,2],2),
+                                round(rfperf_gm12878_100kb_rus[15,2],2),
+                                round(rfperf_K562_100kb_rus[9,2],2),
+                                round(rfperf_K562_100kb_rus[19,2],2),
+                                round(rfperf_K562_100kb_rus[16,2],2),
+                                round(rfperf_K562_100kb_rus[15,2],2),
+                                round(rfperf_gm12878_100kb_ros[9,2],2),
+                                round(rfperf_gm12878_100kb_ros[19,2],2),
+                                round(rfperf_gm12878_100kb_ros[16,2],2),
+                                round(rfperf_gm12878_100kb_ros[15,2],2),
+                                round(rfperf_K562_100kb_ros[9,2],2),
+                                round(rfperf_K562_100kb_ros[19,2],2),
+                                round(rfperf_K562_100kb_ros[16,2],2),
+                                round(rfperf_K562_100kb_ros[15,2],2),
+                                round(rfperf_gm12878_100kb_smote[9,2],2),
+                                round(rfperf_gm12878_100kb_smote[19,2],2),
+                                round(rfperf_gm12878_100kb_smote[16,2],2),
+                                round(rfperf_gm12878_100kb_smote[15,2],2),
+                                round(rfperf_K562_100kb_smote[9,2],2),
+                                round(rfperf_K562_100kb_smote[19,2],2),
+                                round(rfperf_K562_100kb_smote[16,2],2),
+                                round(rfperf_K562_100kb_smote[15,2],2),
+                                round(rfperf_gm12878_100kb_rose[9,2],2),
+                                round(rfperf_gm12878_100kb_rose[19,2],2),
+                                round(rfperf_gm12878_100kb_rose[16,2],2),
+                                round(rfperf_gm12878_100kb_rose[15,2],2),
+                                round(rfperf_K562_100kb_rose[9,2],2),
+                                round(rfperf_K562_100kb_rose[19,2],2),
+                                round(rfperf_K562_100kb_rose[16,2],2),
+                                round(rfperf_K562_100kb_rose[15,2],2))
+
+all100kbresults$Resampling <- factor(all100kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
+all100kbresults$CL <- factor(all100kbresults$CL, levels=c("GM12878", "K562"))
+all100kbresults$Metric <- factor(all100kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
+
+none100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="None"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+rus100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="RUS"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+ros100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="ROS"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+smote100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="SMOTE"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+rose100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="ROSE"),],
+                       aes(x=CL, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  xlab("Cell Line") +
+  ylim(0,1)+
+  theme_bw() +
+  theme_minimal() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+######################################################################
+
+#comparing only f1 and mcc
+
+f1mcc100kbplot <- ggplot(all100kbresults[which(all100kbresults$Metric=="F1-Score" |
+                                               all100kbresults$Metric=="MCC"),],
+                       aes(x=Resampling, y=Performance, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ CL) +
+  xlab("Resampling Technique") +
+  theme_minimal() +
+  theme_bw() +
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+```
+
+#Tables model performances
+
+##10kb
+
+```{r}
+
+```
 

### 2019-02-02 Manuscript/manuscript.Rmd
updated todo and manuscript

@@
 Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
-The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments for the GM12878, K562, ...
-cell lines.
+The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments for the GM12878 and K562 cell lines.
 Each genomic annotation was represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological significance.

### 2019-02-03 Manuscript/manuscript.Rmd
Proof-read through introduction

--- 2019-02-01 Manuscript/manuscript.Rmd
@@
 Existing methods for predicting associations between genomic elements tend to ignore key characteristics of genomic data.
-Specifically, the number of TAD boundaries is much less than the number of other genomic regions, leading to heavily imbalanced classes.
+Specifically, the number of TAD boundaries is much less than the number of other genomic regions, leading to heavily imbalanced classes [???
+and why this is the problem?
+Instead of classes, something like "leading to the model biased towards classifying the majority of the regions".
+Rewrite].
 Furthermore, most methods utilize direct overlap as a means to quantify the association, while distance, the measure of spatial relationships, remains unaccounted for.
@@
 
-**Methods.** We propose a novel data pre-processing pipeline that addresses those shortcomings.
-Lasso and Elastic Net were used for feature selection, coupled with five classifier methods.
+**Methods.** We propose a novel data pre-processing pipeline that systematically addresses those shortcomings.
+Lasso and Elastic Net [???
+Adjust methods to the current setup] were used for feature selection, coupled with five classifier methods.
 A number of classifier performance metrics were assessed, including the F1 measure and Matthew Correlation Coefficient (MCC), and area under the ROC curve (AUROC).
@@
 Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD [@symmons2014functional].
-Approximately 60-80% of TADs remain stable across cell types [@Schmitt:2016aa], suggestingthat the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
+Approximately 60-80% of TADs remain stable across cell types [@Schmitt:2016aa], suggesting that the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
 Furthermore, studies have shown that changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @flavahan2016insulator].
@@
 
-Identifying the mechanisms underlying the formation of TADs are a complex and active area of research.
-The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes [@xiao2012comparative; @milosavljevic2011emerging] [???
-REFs; !!!added refs] prompt the use of computational approaches to identify which epigenomic features are most predictive of the TAD boundaries.
+Identifying the mechanisms underlying the formation of TADs are a complex and active area of research [???
+Need all refs that prove it].
+The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of the TAD boundaries.
 Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries [@mourad2016computational; @hong2017computational; @huang2015predicting].
-Although several useful insights have been made, such as the convergent binding of CTCF [@ong2014ctcf; @ghirlando2016ctcf] [???
-Elaborate with refs.; !!!added refs], many methods ignore key characteristics of domain data, such as heavily imbalanced number of boundaries vs.
+Although several useful insights have been made, such as the convergent binding of CTCF [@ong2014ctcf; @ghirlando2016ctcf], many methods ignore key characteristics of domain data, such as heavily imbalanced number of boundaries vs.
 other regions.
-In a classification setting [???
-are we talking about classification or prediction?; !!!prediction is a byproduct of classification correct?; wait to discuss in meeting], when one is attempting to discriminate between regions with and without TAD boundaries, this will contribute to small imbalance ratios (defined as the ratio of minority to majority classes) [@Orriols-Puig2008].
-As has been reported in the machine learning community, imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class;@chen2013influence;@jeni2013facing].
-Similarly, careful consideration must also be taken when deciding which performance metric(s) to use for evaluation of predictive models, especially in the case of imbalanced data.
+In a classification setting, when one is attempting to discriminate between regions with and without TAD boundaries, the class imbalance issue will contribute to small imbalance ratios (defined as the ratio of minority to majority classes) [@Orriols-Puig2008].
+Such heavily imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class;@chen2013influence;@jeni2013facing].
+Consequently, careful consideration must be taken when deciding which performance metric(s) to use for evaluation of predictive models, especially in the case of imbalanced data.
 
@@
 It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
-For the purposes of this study we focus our attention toward data level solutions so that all results may be classifier independent, and thus, more easily comparable.
+For the purposes of this study, we focus our attention toward data level solutions so that all results may be classifier-independent, and, thus, more easily comparable.
 
-Furthermore, there are other aspects of TAD boundary modelling that current methods have failed to consider.
-Most notably is the concept of genomic distance.
-As a feature engineering step, the use of distances (in base pairs) from TAD boundaries to regions of various genomic features has largely been ignored.
+The other aspect of TAD boundary modelling not considered by the current methods is the concept of genomic distance.
+The typical approaches for modeling the association between TAD boundaries and epigenomic elements include overlap counts [???
+REFs], or percent counts [???
+Do we have refs for this?].
+The use of distances from TAD boundaries to regions of various genomic features, measured in the number of bases between them, has largely been ignored.
 However, these distance characteristics have the potential to offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
@@
 It is often unclear from previous studies what resolution contact matrices were used when retrieving TAD boundaries, and how other resolutions would affect their results.
-A larger resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
+A lower resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
 This will contribute to smaller sample sizes and could effect predictive performances.
 
-In this study we have developed an ensemble framework for predicting TAD boundaries that addresses class imbalance problem.
+In this study, we have developed an ensemble framework for predicting TAD boundaries that addresses class imbalance problem.
 We evaluated Hi-C data for both the GM12878 and K562 cell line obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolution.
@@
 We then tested four re-sampling techniques aimed at creating balanced classes.
-Random forest classification was performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the TAD boundaries.
+[???
+"Following feature reduction using LASSO," - should this be added?] Random forest classification was performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the TAD boundaries.
 Model performance was evaluated using area under the precision-recall curve (AUPRC), F1-Score, and MCC.

### 2019-02-03 Manuscript/manuscript.Rmd
Methods proof-reading

@@
 
-Replicate Hi-C data for the GM12878 and K562 cell lines were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 4) [???
-Need supplementary ref.; !!!added supp table] The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
+Replicate Hi-C data for the GM12878 and K562 cell lines were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 4).
+The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
 The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained.
@@
 
-Genomic annotation data (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
-The annotations consisted of a variety of different chromatin states, histone marks, and transcription factor binding sites using ChIP-seq peak experiments for the GM12878, K562, ...
-cell lines.
-Each genomic annotation was represented by a set of regions (their genomic coordinates) annotated as having a functional property or biological significance.
+Genomic annotation data (chromatin states, histone marks, and transcription factor binding sites, GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
 
@@
 To accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
-Returning to the 10 kb resolution example, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
+For example, for 10 kb data, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
 A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
-Otherwise, the bin was labeled as not containing a boundary (Y=0).
+Otherwise, the bin was labeled as not containing a boundary (Y=0) (Figure 1).
 
@@
 Each training and testing set was composed of a similar majority to minority class ratio as the full data set.
-For the task of performance evaluation and prediction, the test set remained constant for all ensemble systems to account for a fair and unbiased comparison.
+For the task of performance evaluation and prediction, the test set remained constant for all ensemble systems to account for an unbiased comparison.
 
@@
 3.
-**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance (refered to hereafter simply as $\textit{distance}$), in basepairs, from the center of the bin to the center of the nearest region defined by a specific genomic annotation [???
+**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter simply as $\textit{distance}$), from the center of the bin to the center of the nearest region defined by a specific genomic annotation [???
 Decide whether to use "annotation" or "feature"; !!!go with annotation] was calculated.
@@
 That is, they are defined for individual thresholds that separated class prediction.
-Thererfore they are unable to give an overview of the potential range of performance as thresholds vary.
+Thererfore, they are unable to give an overview of the potential range of performance as thresholds vary.
 In order to evaluate the trade-off between precision and recall, we also considered a threshold-free measure in form of the area under the precision recall curve (AUPRC).
+[???
+This seem to be a good place to describe it in more details]
 
-###MODEL ASSESSMENT AND PREDICTION
+### MODEL ASSESSMENT AND PREDICTION
 
-We first assessed predictor type performance using random forest classification algorithms by utilizing each set of predictor types as the feature space, in addition to a model with all combined types.
+We first assessed predictor type performance using random forest classification algorithms by utilizing each set of predictor types as the feature space, in addition to a model with all types combined.
 Models were evaluated across each combination of resampling technique applied to the training set, for each cell line.
@@
 Recursive feature elimination (RFE) was then used to determine the optimal number of features for models with the best performing predictor type, across resampling techniques and cell lines.
-In doing so, random forest models were again used to recursively assign weights to a set of features of a given size.
+[???
+Unclear at shich step this was done] In doing so, random forest models were again used to recursively assign weights to a set of features of a given size.
 For computational efficiency we evaluated feature subset sizes in descending order of powers of 2.
@@
 Then the same was done after permuting each predictor variable.
-The difference between the two AUPRC values was then averaged over all trees, and normalized by the standard error.
+The difference between the two AUPRC values was then averaged over all trees, and normalized by the standard error [???
+of what?].
 All random forest algorithms were implemented in R using the `caret` package version 6.0 [@kuhn2012caret].

### 2019-02-03 Manuscript/manuscript.Rmd
Results review

@@
 Letting |X| denote the cardinality of each set, we evaluated $|C| \times |R| \times |P| \times |B|$ different ensemble systems, totaling X (=$x \times 4 \times 3 \times 5$) separate models.
-For each model, we aimed to assess both performance and identify the genomic annotations that were most influential in correctly labeling the genomic bins that overlapped with flanked TAD boundaries.
-For simplicity, we present the most significant results, with the complete results available as Supplementary Tables and Figures.
+For each model, we aimed to assess both performance and identify the genomic annotations that were most important in correctly labeling the genomic bins that overlapped with flanked TAD boundaries.
 
 We first examined the class imbalance of the different data resolutions (Supplementary Table ).
-While the total number of genomic bins decreased as resolution increased, the imbalance ratios remained relatively stable.
+[???
+What table?] While the total number of genomic bins decreased as resolution increased, the imbalance ratios remained relatively stable.
 We found that there was an average imbalance ratio of 0.154 (SD=0.022) and 0.137 (SD=0.0181) for cell lines GM12878 and K562 respectively.
-The low imbalance ratios indicate a wide disparity between majority and minority classes, and therefore suitable resampling techniques are needed.
+[???
+At which resolution?] The low imbalance ratios indicate a wide disparity between majority and minority classes, and therefore suitable resampling techniques are needed.
 

### 2019-02-05 Scripts/performances.rmd
editted script for results

@@
                                 round(rfperf_K562_10kb_none[15,2],2),
-                                round(rfperf_gm12878_10kb_rus[9,2],2),
-                                round(rfperf_gm12878_10kb_rus[19,2],2),
-                                round(rfperf_gm12878_10kb_rus[16,2],2),
-                                round(rfperf_gm12878_10kb_rus[15,2],2),
-                                round(rfperf_K562_10kb_rus[9,2],2),
-                                round(rfperf_K562_10kb_rus[19,2],2),
-                                round(rfperf_K562_10kb_rus[16,2],2),
-                                round(rfperf_K562_10kb_rus[15,2],2),
-                                round(rfperf_gm12878_10kb_ros[9,2],2),
-                                round(rfperf_gm12878_10kb_ros[19,2],2),
-                                round(rfperf_gm12878_10kb_ros[16,2],2),
-                                round(rfperf_gm12878_10kb_ros[15,2],2),
-                                round(rfperf_K562_10kb_ros[9,2],2),
-                                round(rfperf_K562_10kb_ros[19,2],2),
-                                round(rfperf_K562_10kb_ros[16,2],2),
-                                round(rfperf_K562_10kb_ros[15,2],2),
-                                round(rfperf_gm12878_10kb_smote[9,2],2),
-                                round(rfperf_gm12878_10kb_smote[19,2],2),
-                                round(rfperf_gm12878_10kb_smote[16,2],2),
-                                round(rfperf_gm12878_10kb_smote[15,2],2),
-                                round(rfperf_K562_10kb_smote[9,2],2),
-                                round(rfperf_K562_10kb_smote[19,2],2),
-                                round(rfperf_K562_10kb_smote[16,2],2),
-                                round(rfperf_K562_10kb_smote[15,2],2),
-                                round(rfperf_gm12878_10kb_rose[9,2],2),
-                                round(rfperf_gm12878_10kb_rose[19,2],2),
-                                round(rfperf_gm12878_10kb_rose[16,2],2),
-                                round(rfperf_gm12878_10kb_rose[15,2],2),
-                                round(rfperf_K562_10kb_rose[9,2],2),
-                                round(rfperf_K562_10kb_rose[19,2],2),
-                                round(rfperf_K562_10kb_rose[16,2],2),
-                                round(rfperf_K562_10kb_rose[15,2],2))
+                                round(mean(rfperf_gm12878_10kb_rus[9,]),2),
+                                round(mean(rfperf_gm12878_10kb_rus[19,]),2),
+                                round(mean(rfperf_gm12878_10kb_rus[16,]),2),
+                                round(mean(rfperf_gm12878_10kb_rus[15,]),2),
+                                round(mean(rfperf_K562_10kb_rus[9,]),2),
+                                round(mean(rfperf_K562_10kb_rus[19,]),2),
+                                round(mean(rfperf_K562_10kb_rus[16,]),2),
+                                round(mean(rfperf_K562_10kb_rus[15,]),2),
+                                round(mean(rfperf_gm12878_10kb_ros[9,]),2),
+                                round(mean(rfperf_gm12878_10kb_ros[19,]),2),
+                                round(mean(rfperf_gm12878_10kb_ros[16,]),2),
+                                round(mean(rfperf_gm12878_10kb_ros[15,]),2),
+                                round(mean(rfperf_K562_10kb_ros[9,]),2),
+                                round(mean(rfperf_K562_10kb_ros[19,]),2),
+                                round(mean(rfperf_K562_10kb_ros[16,]),2),
+                                round(mean(rfperf_K562_10kb_ros[15,]),2),
+                                round(mean(rfperf_gm12878_10kb_smote[9,]),2),
+                                round(mean(rfperf_gm12878_10kb_smote[19,]),2),
+                                round(mean(rfperf_gm12878_10kb_smote[16,]),2),
+                                round(mean(rfperf_gm12878_10kb_smote[15,]),2),
+                                round(mean(rfperf_K562_10kb_smote[9,]),2),
+                                round(mean(rfperf_K562_10kb_smote[19,]),2),
+                                round(mean(rfperf_K562_10kb_smote[16,]),2),
+                                round(mean(rfperf_K562_10kb_smote[15,]),2),
+                                round(mean(rfperf_gm12878_10kb_rose[9,]),2),
+                                round(mean(rfperf_gm12878_10kb_rose[19,]),2),
+                                round(mean(rfperf_gm12878_10kb_rose[16,]),2),
+                                round(mean(rfperf_gm12878_10kb_rose[15,]),2),
+                                round(mean(rfperf_K562_10kb_rose[9,]),2),
+                                round(mean(rfperf_K562_10kb_rose[19,]),2),
+                                round(mean(rfperf_K562_10kb_rose[16,]),2),
+                                round(mean(rfperf_K562_10kb_rose[15,]),2))
 
@@
                                                all10kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=Metric)) +
+                       aes(x=Resampling, y=Performance, fill=CL)) +
   geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ CL) +
+  facet_grid(~ Metric) +
   xlab("Resampling Technique") +
@@
   theme_bw() +
+  scale_fill_discrete(name="Cell Line")+
   #guides(fill=FALSE)+
@@
                                 round(rfperf_K562_25kb_none[15,2],2),
-                                round(rfperf_gm12878_25kb_rus[9,2],2),
-                                round(rfperf_gm12878_25kb_rus[19,2],2),
-                                round(rfperf_gm12878_25kb_rus[16,2],2),
-                                round(rfperf_gm12878_25kb_rus[15,2],2),
-                                round(rfperf_K562_25kb_rus[9,2],2),
-                                round(rfperf_K562_25kb_rus[19,2],2),
-                                round(rfperf_K562_25kb_rus[16,2],2),
-                                round(rfperf_K562_25kb_rus[15,2],2),
-                                round(rfperf_gm12878_25kb_ros[9,2],2),
-                                round(rfperf_gm12878_25kb_ros[19,2],2),
-                                round(rfperf_gm12878_25kb_ros[16,2],2),
-                                round(rfperf_gm12878_25kb_ros[15,2],2),
-                                round(rfperf_K562_25kb_ros[9,2],2),
-                                round(rfperf_K562_25kb_ros[19,2],2),
-                                round(rfperf_K562_25kb_ros[16,2],2),
-                                round(rfperf_K562_25kb_ros[15,2],2),
-                                round(rfperf_gm12878_25kb_smote[9,2],2),
-                                round(rfperf_gm12878_25kb_smote[19,2],2),
-                                round(rfperf_gm12878_25kb_smote[16,2],2),
-                                round(rfperf_gm12878_25kb_smote[15,2],2),
-                                round(rfperf_K562_25kb_smote[9,2],2),
-                                round(rfperf_K562_25kb_smote[19,2],2),
-                                round(rfperf_K562_25kb_smote[16,2],2),
-                                round(rfperf_K562_25kb_smote[15,2],2),
-                                round(rfperf_gm12878_25kb_rose[9,2],2),
-                                round(rfperf_gm12878_25kb_rose[19,2],2),
-                                round(rfperf_gm12878_25kb_rose[16,2],2),
-                                round(rfperf_gm12878_25kb_rose[15,2],2),
-                                round(rfperf_K562_25kb_rose[9,2],2),
-                                round(rfperf_K562_25kb_rose[19,2],2),
-                                round(rfperf_K562_25kb_rose[16,2],2),
-                                round(rfperf_K562_25kb_rose[15,2],2))
+                                round(mean(rfperf_gm12878_25kb_rus[9,]),2),
+                                round(mean(rfperf_gm12878_25kb_rus[19,]),2),
+                                round(mean(rfperf_gm12878_25kb_rus[16,]),2),
+                                round(mean(rfperf_gm12878_25kb_rus[15,]),2),
+                                round(mean(rfperf_K562_25kb_rus[9,]),2),
+                                round(mean(rfperf_K562_25kb_rus[19,]),2),
+                                round(mean(rfperf_K562_25kb_rus[16,]),2),
+                                round(mean(rfperf_K562_25kb_rus[15,]),2),
+                                round(mean(rfperf_gm12878_25kb_ros[9,]),2),
+                                round(mean(rfperf_gm12878_25kb_ros[19,]),2),
+                                round(mean(rfperf_gm12878_25kb_ros[16,]),2),
+                                round(mean(rfperf_gm12878_25kb_ros[15,]),2),
+                                round(mean(rfperf_K562_25kb_ros[9,]),2),
+                                round(mean(rfperf_K562_25kb_ros[19,]),2),
+                                round(mean(rfperf_K562_25kb_ros[16,]),2),
+                                round(mean(rfperf_K562_25kb_ros[15,]),2),
+                                round(mean(rfperf_gm12878_25kb_smote[9,]),2),
+                                round(mean(rfperf_gm12878_25kb_smote[19,]),2),
+                                round(mean(rfperf_gm12878_25kb_smote[16,]),2),
+                                round(mean(rfperf_gm12878_25kb_smote[15,]),2),
+                                round(mean(rfperf_K562_25kb_smote[9,]),2),
+                                round(mean(rfperf_K562_25kb_smote[19,]),2),
+                                round(mean(rfperf_K562_25kb_smote[16,]),2),
+                                round(mean(rfperf_K562_25kb_smote[15,]),2),
+                                round(mean(rfperf_gm12878_25kb_rose[9,]),2),
+                                round(mean(rfperf_gm12878_25kb_rose[19,]),2),
+                                round(mean(rfperf_gm12878_25kb_rose[16,]),2),
+                                round(mean(rfperf_gm12878_25kb_rose[15,]),2),
+                                round(mean(rfperf_K562_25kb_rose[9,]),2),
+                                round(mean(rfperf_K562_25kb_rose[19,]),2),
+                                round(mean(rfperf_K562_25kb_rose[16,]),2),
+                                round(mean(rfperf_K562_25kb_rose[15,]),2))
 
@@
                                                all25kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=Metric)) +
+                       aes(x=Resampling, y=Performance, fill=CL)) +
   geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ CL) +
+  facet_grid(~ Metric) +
   xlab("Resampling Technique") +
@@
                                 round(rfperf_K562_50kb_none[15,2],2),
-                                round(rfperf_gm12878_50kb_rus[9,2],2),
-                                round(rfperf_gm12878_50kb_rus[19,2],2),
-                                round(rfperf_gm12878_50kb_rus[16,2],2),
-                                round(rfperf_gm12878_50kb_rus[15,2],2),
-                                round(rfperf_K562_50kb_rus[9,2],2),
-                                round(rfperf_K562_50kb_rus[19,2],2),
-                                round(rfperf_K562_50kb_rus[16,2],2),
-                                round(rfperf_K562_50kb_rus[15,2],2),
-                                round(rfperf_gm12878_50kb_ros[9,2],2),
-                                round(rfperf_gm12878_50kb_ros[19,2],2),
-                                round(rfperf_gm12878_50kb_ros[16,2],2),
-                                round(rfperf_gm12878_50kb_ros[15,2],2),
-                                round(rfperf_K562_50kb_ros[9,2],2),
-                                round(rfperf_K562_50kb_ros[19,2],2),
-                                round(rfperf_K562_50kb_ros[16,2],2),
-                                round(rfperf_K562_50kb_ros[15,2],2),
-                                round(rfperf_gm12878_50kb_smote[9,2],2),
-                                round(rfperf_gm12878_50kb_smote[19,2],2),
-                                round(rfperf_gm12878_50kb_smote[16,2],2),
-                                round(rfperf_gm12878_50kb_smote[15,2],2),
-                                round(rfperf_K562_50kb_smote[9,2],2),
-                                round(rfperf_K562_50kb_smote[19,2],2),
-                                round(rfperf_K562_50kb_smote[16,2],2),
-                                round(rfperf_K562_50kb_smote[15,2],2),
-                                round(rfperf_gm12878_50kb_rose[9,2],2),
-                                round(rfperf_gm12878_50kb_rose[19,2],2),
-                                round(rfperf_gm12878_50kb_rose[16,2],2),
-                                round(rfperf_gm12878_50kb_rose[15,2],2),
-                                round(rfperf_K562_50kb_rose[9,2],2),
-                                round(rfperf_K562_50kb_rose[19,2],2),
-                                round(rfperf_K562_50kb_rose[16,2],2),
-                                round(rfperf_K562_50kb_rose[15,2],2))
+                                round(mean(rfperf_gm12878_50kb_rus[9,]),2),
+                                round(mean(rfperf_gm12878_50kb_rus[19,]),2),
+                                round(mean(rfperf_gm12878_50kb_rus[16,]),2),
+                                round(mean(rfperf_gm12878_50kb_rus[15,]),2),
+                                round(mean(rfperf_K562_50kb_rus[9,]),2),
+                                round(mean(rfperf_K562_50kb_rus[19,]),2),
+                                round(mean(rfperf_K562_50kb_rus[16,]),2),
+                                round(mean(rfperf_K562_50kb_rus[15,]),2),
+                                round(mean(rfperf_gm12878_50kb_ros[9,]),2),
+                                round(mean(rfperf_gm12878_50kb_ros[19,]),2),
+                                round(mean(rfperf_gm12878_50kb_ros[16,]),2),
+                                round(mean(rfperf_gm12878_50kb_ros[15,]),2),
+                                round(mean(rfperf_K562_50kb_ros[9,]),2),
+                                round(mean(rfperf_K562_50kb_ros[19,]),2),
+                                round(mean(rfperf_K562_50kb_ros[16,]),2),
+                                round(mean(rfperf_K562_50kb_ros[15,]),2),
+                                round(mean(rfperf_gm12878_50kb_smote[9,]),2),
+                                round(mean(rfperf_gm12878_50kb_smote[19,]),2),
+                                round(mean(rfperf_gm12878_50kb_smote[16,]),2),
+                                round(mean(rfperf_gm12878_50kb_smote[15,]),2),
+                                round(mean(rfperf_K562_50kb_smote[9,]),2),
+                                round(mean(rfperf_K562_50kb_smote[19,]),2),
+                                round(mean(rfperf_K562_50kb_smote[16,]),2),
+                                round(mean(rfperf_K562_50kb_smote[15,]),2),
+                                round(mean(rfperf_gm12878_50kb_rose[9,]),2),
+                                round(mean(rfperf_gm12878_50kb_rose[19,]),2),
+                                round(mean(rfperf_gm12878_50kb_rose[16,]),2),
+                                round(mean(rfperf_gm12878_50kb_rose[15,]),2),
+                                round(mean(rfperf_K562_50kb_rose[9,]),2),
+                                round(mean(rfperf_K562_50kb_rose[19,]),2),
+                                round(mean(rfperf_K562_50kb_rose[16,]),2),
+                                round(mean(rfperf_K562_50kb_rose[15,]),2))
 
@@
                                                all50kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=Metric)) +
+                       aes(x=Resampling, y=Performance, fill=CL)) +
   geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ CL) +
+  facet_grid(~ Metric) +
   xlab("Resampling Technique") +
@@
                                 round(rfperf_K562_100kb_none[15,2],2),
-                                round(rfperf_gm12878_100kb_rus[9,2],2),
-                                round(rfperf_gm12878_100kb_rus[19,2],2),
-                                round(rfperf_gm12878_100kb_rus[16,2],2),
-                                round(rfperf_gm12878_100kb_rus[15,2],2),
-                                round(rfperf_K562_100kb_rus[9,2],2),
-                                round(rfperf_K562_100kb_rus[19,2],2),
-                                round(rfperf_K562_100kb_rus[16,2],2),
-                                round(rfperf_K562_100kb_rus[15,2],2),
-                                round(rfperf_gm12878_100kb_ros[9,2],2),
-                                round(rfperf_gm12878_100kb_ros[19,2],2),
-                                round(rfperf_gm12878_100kb_ros[16,2],2),
-                                round(rfperf_gm12878_100kb_ros[15,2],2),
-                                round(rfperf_K562_100kb_ros[9,2],2),
-                                round(rfperf_K562_100kb_ros[19,2],2),
-                                round(rfperf_K562_100kb_ros[16,2],2),
-                                round(rfperf_K562_100kb_ros[15,2],2),
-                                round(rfperf_gm12878_100kb_smote[9,2],2),
-                                round(rfperf_gm12878_100kb_smote[19,2],2),
-                                round(rfperf_gm12878_100kb_smote[16,2],2),
-                                round(rfperf_gm12878_100kb_smote[15,2],2),
-                                round(rfperf_K562_100kb_smote[9,2],2),
-                                round(rfperf_K562_100kb_smote[19,2],2),
-                                round(rfperf_K562_100kb_smote[16,2],2),
-                                round(rfperf_K562_100kb_smote[15,2],2),
-                                round(rfperf_gm12878_100kb_rose[9,2],2),
-                                round(rfperf_gm12878_100kb_rose[19,2],2),
-                                round(rfperf_gm12878_100kb_rose[16,2],2),
-                                round(rfperf_gm12878_100kb_rose[15,2],2),
-                                round(rfperf_K562_100kb_rose[9,2],2),
-                                round(rfperf_K562_100kb_rose[19,2],2),
-                                round(rfperf_K562_100kb_rose[16,2],2),
-                                round(rfperf_K562_100kb_rose[15,2],2))
+                                round(mean(rfperf_gm12878_100kb_rus[9,]),2),
+                                round(mean(rfperf_gm12878_100kb_rus[19,]),2),
+                                round(mean(rfperf_gm12878_100kb_rus[16,]),2),
+                                round(mean(rfperf_gm12878_100kb_rus[15,]),2),
+                                round(mean(rfperf_K562_100kb_rus[9,]),2),
+                                round(mean(rfperf_K562_100kb_rus[19,]),2),
+                                round(mean(rfperf_K562_100kb_rus[16,]),2),
+                                round(mean(rfperf_K562_100kb_rus[15,]),2),
+                                round(mean(rfperf_gm12878_100kb_ros[9,]),2),
+                                round(mean(rfperf_gm12878_100kb_ros[19,]),2),
+                                round(mean(rfperf_gm12878_100kb_ros[16,]),2),
+                                round(mean(rfperf_gm12878_100kb_ros[15,]),2),
+                                round(mean(rfperf_K562_100kb_ros[9,]),2),
+                                round(mean(rfperf_K562_100kb_ros[19,]),2),
+                                round(mean(rfperf_K562_100kb_ros[16,]),2),
+                                round(mean(rfperf_K562_100kb_ros[15,]),2),
+                                round(mean(rfperf_gm12878_100kb_smote[9,]),2),
+                                round(mean(rfperf_gm12878_100kb_smote[19,]),2),
+                                round(mean(rfperf_gm12878_100kb_smote[16,]),2),
+                                round(mean(rfperf_gm12878_100kb_smote[15,]),2),
+                                round(mean(rfperf_K562_100kb_smote[9,]),2),
+                                round(mean(rfperf_K562_100kb_smote[19,]),2),
+                                round(mean(rfperf_K562_100kb_smote[16,]),2),
+                                round(mean(rfperf_K562_100kb_smote[15,]),2),
+                                round(mean(rfperf_gm12878_100kb_rose[9,]),2),
+                                round(mean(rfperf_gm12878_100kb_rose[19,]),2),
+                                round(mean(rfperf_gm12878_100kb_rose[16,]),2),
+                                round(mean(rfperf_gm12878_100kb_rose[15,]),2),
+                                round(mean(rfperf_K562_100kb_rose[9,]),2),
+                                round(mean(rfperf_K562_100kb_rose[19,]),2),
+                                round(mean(rfperf_K562_100kb_rose[16,]),2),
+                                round(mean(rfperf_K562_100kb_rose[15,]),2))
 
@@
                                                all100kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=Metric)) +
+                       aes(x=Resampling, y=Performance, fill=CL)) +
   geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ CL) +
+  facet_grid(~ Metric) +
   xlab("Resampling Technique") +
@@
 
-#Tables model performances
-
-##10kb
-
-```{r}
-
+#Table of model performances
+
+```{r}
+
+performancetab <- data.frame(Performance = c(rep("F1-Score", 10),
+                                             rep("MCC", 10)),
+                             Resampling = rep(c("None",
+                                                "None",
+                                                "RUS",
+                                                "RUS",
+                                                "ROS",
+                                                "ROS",
+                                                "SMOTE",
+                                                "SMOTE",
+                                                "ROSE",
+                                                "ROSE"),2),
+                             CL = rep(c("GM12878", "K562"), 10)
+                             )
+
+performancetab$kb10 <- c(rfperf_gm12878_10kb_none[16,2],
+                         rfperf_K562_10kb_none[16,2],
+                         mean(rfperf_gm12878_10kb_rus[16,]),
+                         mean(rfperf_K562_10kb_rus[16,]),
+                         mean(rfperf_gm12878_10kb_ros[16,]),
+                         mean(rfperf_K562_10kb_ros[16,]),
+                         mean(rfperf_gm12878_10kb_smote[16,]),
+                         mean(rfperf_K562_10kb_smote[16,]),
+                         mean(rfperf_gm12878_10kb_rose[16,]),
+                         mean(rfperf_K562_10kb_rose[16,]),
+                         rfperf_gm12878_10kb_none[15,2],
+                         rfperf_K562_10kb_none[15,2],
+                         mean(rfperf_gm12878_10kb_rus[15,]),
+                         mean(rfperf_K562_10kb_rus[15,]),
+                         mean(rfperf_gm12878_10kb_ros[15,]),
+                         mean(rfperf_K562_10kb_ros[15,]),
+                         mean(rfperf_gm12878_10kb_smote[15,]),
+                         mean(rfperf_K562_10kb_smote[15,]),
+                         mean(rfperf_gm12878_10kb_rose[15,]),
+                         mean(rfperf_K562_10kb_rose[15,]))
+
+performancetab$kb25 <- c(rfperf_gm12878_25kb_none[16,2],
+                         rfperf_K562_25kb_none[16,2],
+                         mean(rfperf_gm12878_25kb_rus[16,]),
+                         mean(rfperf_K562_25kb_rus[16,]),
+                         mean(rfperf_gm12878_25kb_ros[16,]),
+                         mean(rfperf_K562_25kb_ros[16,]),
+                         mean(rfperf_gm12878_25kb_smote[16,]),
+                         mean(rfperf_K562_25kb_smote[16,]),
+                         mean(rfperf_gm12878_25kb_rose[16,]),
+                         mean(rfperf_K562_25kb_rose[16,]),
+                         rfperf_gm12878_25kb_none[15,2],
+                         rfperf_K562_25kb_none[15,2],
+                         mean(rfperf_gm12878_25kb_rus[15,]),
+                         mean(rfperf_K562_25kb_rus[15,]),
+                         mean(rfperf_gm12878_25kb_ros[15,]),
+                         mean(rfperf_K562_25kb_ros[15,]),
+                         mean(rfperf_gm12878_25kb_smote[15,]),
+                         mean(rfperf_K562_25kb_smote[15,]),
+                         mean(rfperf_gm12878_25kb_rose[15,]),
+                         mean(rfperf_K562_25kb_rose[15,]))
+
+performancetab$kb50 <- c(rfperf_gm12878_50kb_none[16,2],
+                         rfperf_K562_50kb_none[16,2],
+                         mean(rfperf_gm12878_50kb_rus[16,]),
+                         mean(rfperf_K562_50kb_rus[16,]),
+                         mean(rfperf_gm12878_50kb_ros[16,]),
+                         mean(rfperf_K562_50kb_ros[16,]),
+                         mean(rfperf_gm12878_50kb_smote[16,]),
+                         mean(rfperf_K562_50kb_smote[16,]),
+                         mean(rfperf_gm12878_50kb_rose[16,]),
+                         mean(rfperf_K562_50kb_rose[16,]),
+                         rfperf_gm12878_50kb_none[15,2],
+                         rfperf_K562_50kb_none[15,2],
+                         mean(rfperf_gm12878_50kb_rus[15,]),
+                         mean(rfperf_K562_50kb_rus[15,]),
+                         mean(rfperf_gm12878_50kb_ros[15,]),
+                         mean(rfperf_K562_50kb_ros[15,]),
+                         mean(rfperf_gm12878_50kb_smote[15,]),
+                         mean(rfperf_K562_50kb_smote[15,]),
+                         mean(rfperf_gm12878_50kb_rose[15,]),
+                         mean(rfperf_K562_50kb_rose[15,]))
+
+performancetab$kb100 <- c(rfperf_gm12878_100kb_none[16,2],
+                         rfperf_K562_100kb_none[16,2],
+                         mean(rfperf_gm12878_100kb_rus[16,]),
+                         mean(rfperf_K562_100kb_rus[16,]),
+                         mean(rfperf_gm12878_100kb_ros[16,]),
+                         mean(rfperf_K562_100kb_ros[16,]),
+                         mean(rfperf_gm12878_100kb_smote[16,]),
+                         mean(rfperf_K562_100kb_smote[16,]),
+                         mean(rfperf_gm12878_100kb_rose[16,]),
+                         mean(rfperf_K562_100kb_rose[16,]),
+                         rfperf_gm12878_100kb_none[15,2],
+                         rfperf_K562_100kb_none[15,2],
+                         mean(rfperf_gm12878_100kb_rus[15,]),
+                         mean(rfperf_K562_100kb_rus[15,]),
+                         mean(rfperf_gm12878_100kb_ros[15,]),
+                         mean(rfperf_K562_100kb_ros[15,]),
+                         mean(rfperf_gm12878_100kb_smote[15,]),
+                         mean(rfperf_K562_100kb_smote[15,]),
+                         mean(rfperf_gm12878_100kb_rose[15,]),
+                         mean(rfperf_K562_100kb_rose[15,]))
+
+performancetab[,4:7] <- round(performancetab[,4:7], 3)
 ```

### 2019-02-12 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-Identifying the mechanisms underlying the formation of TADs are a complex and active area of research [???
-Need all refs that prove it].
-The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of the TAD boundaries.
+The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries.
 Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries [@mourad2016computational; @hong2017computational; @huang2015predicting].
-Although several useful insights have been made, such as the convergent binding of CTCF [@ong2014ctcf; @ghirlando2016ctcf], many methods ignore key characteristics of domain data, such as heavily imbalanced number of boundaries vs.
+Although several useful insights have been made, such as the convergent binding of CTCF [@ong2014ctcf; @ghirlando2016ctcf], many methods ignore key characteristics of domain data, such as the impact of heavily imbalanced number of boundaries vs.
 other regions.
@@
 While not directly affecting the value of the AUROC, this can have severe consequences on the interpretability of the model's performance.
-A better threshold-free measure to use when dealing with imbalanced data in the area under the precision-recall curve (AUPRC).
+A better threshold-free measure to use when dealing with imbalanced data is the area under the precision-recall curve (AUPRC).
 It has been shown that the use of AUPRC with imbalanced datasets yields more accurate and intuitive interpretation of model performance when compared to AUROC [@saito2015precision].
 Likewise, metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
-Better measures to consider are the F1-Score and Matthew's Correlation Coefficient (MCC) [@jeni2013facing].
-The F1-Score can be interpreted as a weighted average of the precision and recall values, while MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications.
-Both metrics use all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
+Better measures to consider are the precision and recall themselves.
+Both the precision and recall of a model include the true positives in the numerator of their respective ratios, thereby yielding more appropriate measures of a model's ability to accurately classify positive classes.
+Therefore, certain composite metrics like the F1-Score, Youden's Index, and Matthew's Correlation Coefficient (MCC) offer better interpretation, especially in the instance of imbalanced classes [@jeni2013facing].
+The F1-Score can be interpreted as a weighted average of the precision and recall values, while Youden's index is interpreted as the arithmetic mean between sensitivity (recall) and specificity.
+MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications.
+Each metric uses all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
 

### 2019-02-12 Manuscript/manuscript.Rmd
manuscript edits

@@
 Algorithmic level solutions involve modifyng existing classifiers in order to curtail the bias induced by imbalanced classes [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical].
-Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
+Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or remove data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
 It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
@@
 The other aspect of TAD boundary modelling not considered by the current methods is the concept of genomic distance.
-The typical approaches for modeling the association between TAD boundaries and epigenomic elements include overlap counts [???
-REFs], or percent counts [???
-Do we have refs for this?].
+The typical approaches for modeling the association between TAD boundaries and epigenomic elements include overlap counts or percents [???
+Do we have refs for this?; !!!should I repeat past used references here?].
+Counts refer to the total number of instances where a genomic annotation overlaps with a genomic region of interest, while percents refers to the percent of overlap that occurred (usually in terms of base pairs).
 The use of distances from TAD boundaries to regions of various genomic features, measured in the number of bases between them, has largely been ignored.
@@
 
-In this study, we have developed an ensemble framework for predicting TAD boundaries that addresses class imbalance problem.
+In this study, we have developed an ensemble framework for predicting TAD boundaries in order to systematically compare many data driven solutions used to address the issues presented above.
 We evaluated Hi-C data for both the GM12878 and K562 cell line obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolution.
 For each resolution, we examined the inclusion of three different predictor types, including distance as the measure of association between genomic elements.
-We then tested four re-sampling techniques aimed at creating balanced classes.
-[???
-"Following feature reduction using LASSO," - should this be added?] Random forest classification was performed to both compare each combination of the above ensemble, and investigate which functional genomic features were most associated with the TAD boundaries.
-Model performance was evaluated using area under the precision-recall curve (AUPRC), F1-Score, and MCC.
+We then tested four different re-sampling techniques aimed at creating balanced classes.
+Noninformative features were removed using a variable reduction algorithm and random forest classifications were performed to assess model performance, and investigate which genomic annotations were most associated with the TAD boundaries for a given system from the complete ensemble.
+Model performance was evaluated using area under the precision-recall curve (AUPRC), F1-Score, Youden's index (YI), and Matthew's correlation coefficient (MCC).
 

### 2019-02-13 Manuscript/manuscript.Rmd
manuscript edits

@@
 A better threshold-free measure to use when dealing with imbalanced data is the area under the precision-recall curve (AUPRC).
-It has been shown that the use of AUPRC with imbalanced datasets yields more accurate and intuitive interpretation of model performance when compared to AUROC [@saito2015precision].
+The precision-recall curve uses as its axes the precision and recall of the model.
+Both the precision and recall of a model include the true positives in the numerator of their respective ratios, thereby yielding more appropriate measures of a model's ability to accurately classify positive classes.
+Because of this, tt has been shown that the use of AUPRC with imbalanced datasets yields more accurate and intuitive interpretation of model performance when compared to AUROC [@saito2015precision].
 Likewise, metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
 Better measures to consider are the precision and recall themselves.
-Both the precision and recall of a model include the true positives in the numerator of their respective ratios, thereby yielding more appropriate measures of a model's ability to accurately classify positive classes.
-Therefore, certain composite metrics like the F1-Score, Youden's Index, and Matthew's Correlation Coefficient (MCC) offer better interpretation, especially in the instance of imbalanced classes [@jeni2013facing].
+Therefore, composite metrics that involve precision and recall, like the F1-Score, Youden's Index (YI), and Matthew's Correlation Coefficient (MCC) offer better interpretation, especially in the instance of imbalanced classes [@jeni2013facing].
 The F1-Score can be interpreted as a weighted average of the precision and recall values, while Youden's index is interpreted as the arithmetic mean between sensitivity (recall) and specificity.
@@
 For example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
-To accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
+For the boundary data, in order to accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
 For example, for 10 kb data, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
 A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
-Otherwise, the bin was labeled as not containing a boundary (Y=0) (Figure 1).
+Otherwise, the bin was labeled as not containing a boundary (Y=0).
 
@@
 
-### FEATURE ENGINEERING AND REDUCTION USING GENOMIC ANNOTATIONS
+### FEATURE ENGINEERING AND RE-SAMPLING
 
@@
 
-### RE-SAMPLING TECHNIQUES
-
-In order to evaluate the problem of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling).
+In order to assess the influence of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling), composed of data from each predictor type.
+Each re-sampling technique is described in detail below.
 
@@
 
-2.
-**Random Under-Sampling (RUS)**: All of the minority classes from the training set were used.
-Sampling without replacement was used to obtain the same number of the majority classes.
-We performed 50 iterations of random under-sampling.
-At each iteration a random forest classification algorithm was performed.
-Performance metrics were aggregated by taking the average across all of the iterations.
+2. **Random Under-Sampling (RUS)**: All of the minority classes from the training set were used. Sampling without replacement was used to obtain the same number of the majority classes.
 
-3.
-**Random Over-Sampling (ROS)**: All of the majority classes from the training set were used.
-Sampling with replacement was used to obtain the same number of the minority classes.
-Similar to the under-sampling technique, 50 iterations were performed and the results of a random forest classification were aggregated by taking the average across iterations.
+3. **Random Over-Sampling (ROS)**: All of the majority classes from the training set were used. Sampling with replacement was used to obtain the same number of the minority classes.
 
@@
 Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class [@chawla2002smote].
-To account for the bias introduced by the under-sampling, we performed 50-iterations of SMOTE.
-We chose the parameters that would create perfectly balanced classes.
 The `DMwR` R package was used to perform SMOTE (version 0.4.1).
@@
 
-### CLASSIFICATION & CROSS VALIDATION
+To determine the best predictor type we performed separate random forest models on each set of predictor types and evaluated the precision-recall curves, as well as the subsequent AUPRC.
+To confirm the optimality of the feature engineering, this was performed for each combination of re-sampling technique, resolution, and cell line.
 
-A classification algorithm in the form of a random forest was performed on the various resampled and reduced training sets and validated using the same test set for all models in the ensemble.
+### FEATURE REDUCTION
+
+Recursive feature elimination (RFE) was then used to determine the optimal number of features for models with the best performing predictor type.
+For each set of predictor type, random forest models were performed recursively on subsets of the feature space.
+The specific subsets of features were chosen as powers of 2 for computational efficiency.
+Model performance for each subset was evaluated using AUPRC.
+The optimal set of featues to include in downstream analyses was determined to be the subset in which the AUPRC leveled off.
+Again, to confirm that results were consistent, the reduction process was repeated for each combination of re-sampling technique, resolution, and cell line.
+
+### FINAL MODEL ASSESSMENT AND PERFORMANCE
+
+Once the appropriate predictor type and set of features were determined, a final set of random forest classification models were performed to fully compare re-sampling techniques.
 To reduce bias due to random dataset generation, 10-fold cross validation was used.
@@
 Likewise, the number of ensemble trees to aggregate was set at 500.
+All random forest algorithms were implemented in R using the `caret` package version 6.0 [@kuhn2012caret].
 Once the model was implemented, it was assessed using the test set, and performance metrics were then recorded.
 
-### PERFORMANCE METRICS
-
-The efficacy of different ensemble systems was compared using the F1-score and MCC. These metrics are defined as follows:
+The efficacy of each re-sampling technique was compared using the F1-score, YI, and  MCC. These metrics are defined as follows:
 
 $$F1 - Score = \frac{2TP}{2TP + FP + FN}$$
+
+$$YI = \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} - 1$$
+
 $$MCC = \frac{TP \times TN - FP \times FN}{\sqrt{ (TP + FP)(TP+FN)(TN+FP)(TN+FN) }}$$
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-The evaluation metrics listed above are all considered single threshold measures.
-That is, they are defined for individual thresholds that separated class prediction.
-Thererfore, they are unable to give an overview of the potential range of performance as thresholds vary.
-In order to evaluate the trade-off between precision and recall, we also considered a threshold-free measure in form of the area under the precision recall curve (AUPRC).
-[???
-This seem to be a good place to describe it in more details]
 
-### MODEL ASSESSMENT AND PREDICTION
-
-We first assessed predictor type performance using random forest classification algorithms by utilizing each set of predictor types as the feature space, in addition to a model with all types combined.
-Models were evaluated across each combination of resampling technique applied to the training set, for each cell line.
-Performance was based on the AUPRC.
-Recursive feature elimination (RFE) was then used to determine the optimal number of features for models with the best performing predictor type, across resampling techniques and cell lines.
-[???
-Unclear at shich step this was done] In doing so, random forest models were again used to recursively assign weights to a set of features of a given size.
-For computational efficiency we evaluated feature subset sizes in descending order of powers of 2.
-The optimal number of features was determined by the AUPRC of the corresponding model.
-Optimal performance was assessed and the feature spaced was reduced accordingly.
-
-For the task of identifying the functional genomic elements that were most predictive of the formation of TAD boundaries, we evaluated the variable importances associated with each predictor of the random forest models associated with each resampling technique.
-For each model and within each tree, the AUPRC on the out-of-bag portion of the data was recorded.
+Lastly, for the task of identifying the genomic annotations that were most predictive of the formation of TAD boundaries, we evaluated the variable importances associated with each feature of the random forest model associated with the best combination of reduced predictor type and re-sampling technique, across each cell line.
+To calculate variable importances for each model, the AUPRC on the out-of-bag portion of the data within each tree was recorded.
 Then the same was done after permuting each predictor variable.
-The difference between the two AUPRC values was then averaged over all trees, and normalized by the standard error [???
-of what?].
-All random forest algorithms were implemented in R using the `caret` package version 6.0 [@kuhn2012caret].
+The difference between the two AUPRC values was then averaged over all trees, and normalized by the standard error of the differences.
+All measures of importances were then rescaled to have a maximum value of 100 for better interpretation.
 

### 2019-02-19 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-Commonly used measures of model performance for binary classifiers include the area under the receiver operating curve (AUROC).
-The popularity surrounding the use of ROC curves is that they do not depend on a threshold.
-However, when the prevalence of an event is low--that is, a defined genomic region containing a TAD boundary--mean probabilities are biased towards the majority class.
+Commonly used measures of model performance for binary classifiers include threshold-free metrics like the area under the receiver operating curve (AUROC), and other threshold-specific metrics like accuracy, sensitivity, and specificity.
+The ROC curve is created by plotting the true positive rate (TPR) against the false positive rate (FPR) at various threshold settings.
+The subsequent AUROC, measures how well the model is capable of distinguishing between the two classes [@park2004receiver].
+Accuracy is defined as the ratio of correctly identified cases (either from the positive or negative class) over the total number of cases.
+It measures the overall proportion of correctly classified instances.
+Sensitivity, also referred to as recall or TPR, is the ratio of true positives over the total number of positive classes.
+Specificity, on the other hand, also referred to as TNR, is the ratio of true negatives over the total number of negative classes.
+Each measures the proportion of correctly identified positive and negative classes respectively [@yerushalmy1947statistical].
+Problems arise when using such measures in the event of imbalanced classes.
+For AUROC, when the prevalence of an event is low--that is, a defined genomic region truly containing a TAD boundary--mean probabilities are biased towards the majority class.
 This results in the area of interest under an ROC curve to be compressed toward a small corner in the ROC space [@prati2011survey].
@@
 A better threshold-free measure to use when dealing with imbalanced data is the area under the precision-recall curve (AUPRC).
-The precision-recall curve uses as its axes the precision and recall of the model.
-Both the precision and recall of a model include the true positives in the numerator of their respective ratios, thereby yielding more appropriate measures of a model's ability to accurately classify positive classes.
-Because of this, tt has been shown that the use of AUPRC with imbalanced datasets yields more accurate and intuitive interpretation of model performance when compared to AUROC [@saito2015precision].
-Likewise, metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
-Better measures to consider are the precision and recall themselves.
-Therefore, composite metrics that involve precision and recall, like the F1-Score, Youden's Index (YI), and Matthew's Correlation Coefficient (MCC) offer better interpretation, especially in the instance of imbalanced classes [@jeni2013facing].
-The F1-Score can be interpreted as a weighted average of the precision and recall values, while Youden's index is interpreted as the arithmetic mean between sensitivity (recall) and specificity.
-MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications.
-Each metric uses all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
+Likewise, threshold-specific metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
+Certain composite threshold-specific metrics such as balanced accuracy and Youden's Index should be preferred because they soften the influence of a model's ability to correctly classify majority classes and yield more dependable and interpretable results [@jeni2013facing].
+Here, balanced accuracy measures the average accuracy obtained on either class [@brodersen2010balanced].
+Informedness, also referred to as Youden's Index, measures the probability of the model making an informed decision and corresponds to giving equal weight per class, rather than to each instance like Accuracy [@youden1950index;@powers2011evaluation].
 
@@
 3.
-**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter simply as $\textit{distance}$), from the center of the bin to the center of the nearest region defined by a specific genomic annotation [???
-Decide whether to use "annotation" or "feature"; !!!go with annotation] was calculated.
+**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter simply as $\textit{distance}$), from the center of the bin to the center of the nearest region defined by a specific genomic annotation was calculated.
 The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figures 1-8).
@@
 
-The efficacy of each re-sampling technique was compared using the F1-score, YI, and  MCC. These metrics are defined as follows:
+The efficacy of each re-sampling technique was compared using the F1-score, balanced accuracy, informedness, and  MCC. These metrics are defined as follows:
 
@@
 
-$$YI = \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} - 1$$
+$$Balanced \quad Accuracy = \dfrac{1}{2}\left( \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} \right)$$
+
+$$Informedness = \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} - 1$$
 
@@
 
-We first examined the class imbalance of the different data resolutions (Supplementary Table ).
+We first examined the class imbalance of the different data resolutions (Supplementary Table 5).
 [???
-What table?] While the total number of genomic bins decreased as resolution increased, the imbalance ratios remained relatively stable.
-We found that there was an average imbalance ratio of 0.154 (SD=0.022) and 0.137 (SD=0.0181) for cell lines GM12878 and K562 respectively.
+What table?; !!!fixed] While the total number of genomic bins decreased as resolution increased, the imbalance ratios remained relatively stable.
+We found that there was an average imbalance ratio of 0.154 (SD=0.022) and 0.137 (SD=0.0181) across resolutions for cell lines GM12878 and K562 respectively.
 [???
-At which resolution?] The low imbalance ratios indicate a wide disparity between majority and minority classes, and therefore suitable resampling techniques are needed.
+At which resolution?; !!!fixed] The low imbalance ratios indicate a wide disparity between majority and minority classes, and therefore suitable resampling techniques are needed.
 

### 2019-02-19 Scripts/performances.rmd
added to results script

@@
 
-all10kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all10kbresults$Performance <- c(round(rfperf_gm12878_10kb_none[9,2],2),
-                                round(rfperf_gm12878_10kb_none[19,2],2),
-                                round(rfperf_gm12878_10kb_none[16,2],2),
-                                round(rfperf_gm12878_10kb_none[15,2],2),
+all10kbresults <- data.frame(Resampling=c(rep("None", 12),
+                                       rep("RUS", 12),
+                                       rep("ROS", 12),
+                                       rep("SMOTE", 12),
+                                       rep("ROSE", 12)),
+                          CL=rep(c(rep("GM12878",6),
+                               rep("K562", 6)),5),
+                          Metric=rep(c("Accuracy", 
+                                       "AUPRC", 
+                                       "F1-Score", 
+                                       "MCC",
+                                       "Informedness",
+                                       "Balanced Acc"), 10))
+
+all10kbresults$Performance <- c(round(rfperf_gm12878_10kb_none[9,2],2), #accuracy
+                                round(rfperf_gm12878_10kb_none[19,2],2), #auprc
+                                round(rfperf_gm12878_10kb_none[16,2],2), #f1
+                                round(rfperf_gm12878_10kb_none[15,2],2), #mcc
+								round(rfperf_gm12878_10kb_none[18,2],2), #youden
+								(round(rfperf_gm12878_10kb_none[6,2],2) + round(rfperf_gm12878_10kb_none[7,2],2))/2, #balanced accuracy
+
                                 round(rfperf_K562_10kb_none[9,2],2),
@@
                                 round(rfperf_K562_10kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_10kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_rus[15,]),2),
-                                round(mean(rfperf_K562_10kb_rus[9,]),2),
-                                round(mean(rfperf_K562_10kb_rus[19,]),2),
-                                round(mean(rfperf_K562_10kb_rus[16,]),2),
-                                round(mean(rfperf_K562_10kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[15,]),2),
-                                round(mean(rfperf_K562_10kb_ros[9,]),2),
-                                round(mean(rfperf_K562_10kb_ros[19,]),2),
-                                round(mean(rfperf_K562_10kb_ros[16,]),2),
-                                round(mean(rfperf_K562_10kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[15,]),2),
-                                round(mean(rfperf_K562_10kb_smote[9,]),2),
-                                round(mean(rfperf_K562_10kb_smote[19,]),2),
-                                round(mean(rfperf_K562_10kb_smote[16,]),2),
-                                round(mean(rfperf_K562_10kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[15,]),2),
-                                round(mean(rfperf_K562_10kb_rose[9,]),2),
-                                round(mean(rfperf_K562_10kb_rose[19,]),2),
-                                round(mean(rfperf_K562_10kb_rose[16,]),2),
-                                round(mean(rfperf_K562_10kb_rose[15,]),2))
+								round(rfperf_K562_10kb_none[18,2],2),
+								(round(rfperf_K562_10kb_none[6,2],2) + round(rfperf_K562_10kb_none[7,2],2))/2,
+
+                                round(mean(rfperf_gm12878_10kb_rus[9,1]),2),
+                                round(mean(rfperf_gm12878_10kb_rus[19,1]),2),
+                                round(mean(rfperf_gm12878_10kb_rus[16,1]),2),
+                                round(mean(rfperf_gm12878_10kb_rus[15,1]),2),
+								round(mean(rfperf_gm12878_10kb_rus[18,1]),2),
+								(round(mean(rfperf_gm12878_10kb_rus[6,1]),2) + round(mean(rfperf_gm12878_10kb_rus[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_10kb_rus[9,1]),2),
+                                round(mean(rfperf_K562_10kb_rus[19,1]),2),
+                                round(mean(rfperf_K562_10kb_rus[16,1]),2),
+                                round(mean(rfperf_K562_10kb_rus[15,1]),2),
+								round(mean(rfperf_K562_10kb_rus[18,1]),2),
+								(round(mean(rfperf_K562_10kb_rus[6,1]),2) + round(mean(rfperf_K562_10kb_rus[7,1]),2))/2,
+
+                                round(mean(rfperf_gm12878_10kb_ros[9,1]),2),
+                                round(mean(rfperf_gm12878_10kb_ros[19,1]),2),
+                                round(mean(rfperf_gm12878_10kb_ros[16,1]),2),
+                                round(mean(rfperf_gm12878_10kb_ros[15,1]),2),
+								round(mean(rfperf_gm12878_10kb_ros[18,1]),2),
+								(round(mean(rfperf_gm12878_10kb_ros[6,1]),2) + round(mean(rfperf_gm12878_10kb_ros[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_10kb_ros[9,1]),2),
+                                round(mean(rfperf_K562_10kb_ros[19,1]),2),
+                                round(mean(rfperf_K562_10kb_ros[16,1]),2),
+                                round(mean(rfperf_K562_10kb_ros[15,1]),2),
+								round(mean(rfperf_K562_10kb_ros[18,1]),2),
+								(round(mean(rfperf_K562_10kb_ros[6,1]),2) + round(mean(rfperf_K562_10kb_ros[7,1]),2))/2,
+
+                                round(mean(rfperf_gm12878_10kb_smote[9,1]),2),
+                                round(mean(rfperf_gm12878_10kb_smote[19,1]),2),
+                                round(mean(rfperf_gm12878_10kb_smote[16,1]),2),
+                                round(mean(rfperf_gm12878_10kb_smote[15,1]),2),
+								round(mean(rfperf_gm12878_10kb_smote[18,1]),2),
+								(round(mean(rfperf_gm12878_10kb_smote[6,1]),2) + round(mean(rfperf_gm12878_10kb_smote[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_10kb_smote[9,1]),2),
+                                round(mean(rfperf_K562_10kb_smote[19,1]),2),
+                                round(mean(rfperf_K562_10kb_smote[16,1]),2),
+                                round(mean(rfperf_K562_10kb_smote[15,1]),2),
+								round(mean(rfperf_K562_10kb_smote[18,1]),2),
+								(round(mean(rfperf_K562_10kb_smote[6,1]),2) + round(mean(rfperf_K562_10kb_smote[7,1]),2))/2,
+
+                                round(mean(rfperf_gm12878_10kb_rose[9,1]),2),
+                                round(mean(rfperf_gm12878_10kb_rose[19,1]),2),
+                                round(mean(rfperf_gm12878_10kb_rose[16,1]),2),
+                                round(mean(rfperf_gm12878_10kb_rose[15,1]),2),
+								round(mean(rfperf_gm12878_10kb_rose[18,1]),2),
+								(round(mean(rfperf_gm12878_10kb_rose[6,1]),2) + round(mean(rfperf_gm12878_10kb_rose[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_10kb_rose[9,1]),2),
+                                round(mean(rfperf_K562_10kb_rose[19,1]),2),
+                                round(mean(rfperf_K562_10kb_rose[16,1]),2),
+                                round(mean(rfperf_K562_10kb_rose[15,1]),2),
+								round(mean(rfperf_K562_10kb_rose[18,1]),2),
+								(round(mean(rfperf_K562_10kb_rose[6,1]),2) + round(mean(rfperf_K562_10kb_rose[7,1]),2))/2)
 
@@
 
+#comparing only informedness and balanced accuracy
+informBA10kbplot <- ggplot(all10kbresults[which(all10kbresults$Metric=="Informedness" |
+                                               all10kbresults$Metric=="Balanced Acc"),],
+                       aes(x=Resampling, y=Performance, fill=CL)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Metric) +
+  ylim(0,.8)+
+  xlab("Resampling Technique") +
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Cell Line")+
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
 ```
@@
 
-all25kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all25kbresults$Performance <- c(round(rfperf_gm12878_25kb_none[9,2],2),
-                                round(rfperf_gm12878_25kb_none[19,2],2),
-                                round(rfperf_gm12878_25kb_none[16,2],2),
-                                round(rfperf_gm12878_25kb_none[15,2],2),
+all25kbresults <- data.frame(Resampling=c(rep("None", 12),
+                                       rep("RUS", 12),
+                                       rep("ROS", 12),
+                                       rep("SMOTE", 12),
+                                       rep("ROSE", 12)),
+                          CL=rep(c(rep("GM12878",6),
+                               rep("K562", 6)),5),
+                          Metric=rep(c("Accuracy", 
+                                       "AUPRC", 
+                                       "F1-Score", 
+                                       "MCC",
+                                       "Informedness",
+                                       "Balanced Acc"), 10))
+
+all25kbresults$Performance <- c(round(rfperf_gm12878_25kb_none[9,2],2), #accuracy
+                                round(rfperf_gm12878_25kb_none[19,2],2), #auprc
+                                round(rfperf_gm12878_25kb_none[16,2],2), #f1
+                                round(rfperf_gm12878_25kb_none[15,2],2), #mcc
+								round(rfperf_gm12878_25kb_none[18,2],2), #youden
+								(round(rfperf_gm12878_25kb_none[6,2],2) + round(rfperf_gm12878_25kb_none[7,2],2))/2, #balanced accuracy
+
                                 round(rfperf_K562_25kb_none[9,2],2),
@@
                                 round(rfperf_K562_25kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_25kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_rus[15,]),2),
-                                round(mean(rfperf_K562_25kb_rus[9,]),2),
-                                round(mean(rfperf_K562_25kb_rus[19,]),2),
-                                round(mean(rfperf_K562_25kb_rus[16,]),2),
-                                round(mean(rfperf_K562_25kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[15,]),2),
-                                round(mean(rfperf_K562_25kb_ros[9,]),2),
-                                round(mean(rfperf_K562_25kb_ros[19,]),2),
-                                round(mean(rfperf_K562_25kb_ros[16,]),2),
-                                round(mean(rfperf_K562_25kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[15,]),2),
-                                round(mean(rfperf_K562_25kb_smote[9,]),2),
-                                round(mean(rfperf_K562_25kb_smote[19,]),2),
-                                round(mean(rfperf_K562_25kb_smote[16,]),2),
-                                round(mean(rfperf_K562_25kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[15,]),2),
-                                round(mean(rfperf_K562_25kb_rose[9,]),2),
-                                round(mean(rfperf_K562_25kb_rose[19,]),2),
-                                round(mean(rfperf_K562_25kb_rose[16,]),2),
-                                round(mean(rfperf_K562_25kb_rose[15,]),2))
+								round(rfperf_K562_25kb_none[18,2],2),
+								(round(rfperf_K562_25kb_none[6,2],2) + round(rfperf_K562_25kb_none[7,2],2))/2,
+
+                                round(mean(rfperf_gm12878_25kb_rus[9,1]),2),
+                                round(mean(rfperf_gm12878_25kb_rus[19,1]),2),
+                                round(mean(rfperf_gm12878_25kb_rus[16,1]),2),
+                                round(mean(rfperf_gm12878_25kb_rus[15,1]),2),
+								round(mean(rfperf_gm12878_25kb_rus[18,1]),2),
+								(round(mean(rfperf_gm12878_25kb_rus[6,1]),2) + round(mean(rfperf_gm12878_25kb_rus[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_25kb_rus[9,1]),2),
+                                round(mean(rfperf_K562_25kb_rus[19,1]),2),
+                                round(mean(rfperf_K562_25kb_rus[16,1]),2),
+                                round(mean(rfperf_K562_25kb_rus[15,1]),2),
+								round(mean(rfperf_K562_25kb_rus[18,1]),2),
+								(round(mean(rfperf_K562_25kb_rus[6,1]),2) + round(mean(rfperf_K562_25kb_rus[7,1]),2))/2,
+
+                                round(mean(rfperf_gm12878_25kb_ros[9,1]),2),
+                                round(mean(rfperf_gm12878_25kb_ros[19,1]),2),
+                                round(mean(rfperf_gm12878_25kb_ros[16,1]),2),
+                                round(mean(rfperf_gm12878_25kb_ros[15,1]),2),
+								round(mean(rfperf_gm12878_25kb_ros[18,1]),2),
+								(round(mean(rfperf_gm12878_25kb_ros[6,1]),2) + round(mean(rfperf_gm12878_25kb_ros[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_25kb_ros[9,1]),2),
+                                round(mean(rfperf_K562_25kb_ros[19,1]),2),
+                                round(mean(rfperf_K562_25kb_ros[16,1]),2),
+                                round(mean(rfperf_K562_25kb_ros[15,1]),2),
+								round(mean(rfperf_K562_25kb_ros[18,1]),2),
+								(round(mean(rfperf_K562_25kb_ros[6,1]),2) + round(mean(rfperf_K562_25kb_ros[7,1]),2))/2,
+
+                                round(mean(rfperf_gm12878_25kb_smote[9,1]),2),
+                                round(mean(rfperf_gm12878_25kb_smote[19,1]),2),
+                                round(mean(rfperf_gm12878_25kb_smote[16,1]),2),
+                                round(mean(rfperf_gm12878_25kb_smote[15,1]),2),
+								round(mean(rfperf_gm12878_25kb_smote[18,1]),2),
+								(round(mean(rfperf_gm12878_25kb_smote[6,1]),2) + round(mean(rfperf_gm12878_25kb_smote[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_25kb_smote[9,1]),2),
+                                round(mean(rfperf_K562_25kb_smote[19,1]),2),
+                                round(mean(rfperf_K562_25kb_smote[16,1]),2),
+                                round(mean(rfperf_K562_25kb_smote[15,1]),2),
+								round(mean(rfperf_K562_25kb_smote[18,1]),2),
+								(round(mean(rfperf_K562_25kb_smote[6,1]),2) + round(mean(rfperf_K562_25kb_smote[7,1]),2))/2,
+
+                                round(mean(rfperf_gm12878_25kb_rose[9,1]),2),
+                                round(mean(rfperf_gm12878_25kb_rose[19,1]),2),
+                                round(mean(rfperf_gm12878_25kb_rose[16,1]),2),
+                                round(mean(rfperf_gm12878_25kb_rose[15,1]),2),
+								round(mean(rfperf_gm12878_25kb_rose[18,1]),2),
+								(round(mean(rfperf_gm12878_25kb_rose[6,1]),2) + round(mean(rfperf_gm12878_25kb_rose[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_25kb_rose[9,1]),2),
+                                round(mean(rfperf_K562_25kb_rose[19,1]),2),
+                                round(mean(rfperf_K562_25kb_rose[16,1]),2),
+                                round(mean(rfperf_K562_25kb_rose[15,1]),2),
+								round(mean(rfperf_K562_25kb_rose[18,1]),2),
+								(round(mean(rfperf_K562_25kb_rose[6,1]),2) + round(mean(rfperf_K562_25kb_rose[7,1]),2))/2)
 
@@
 
+#comparing only informedness and balanced accuracy
+informBA25kbplot <- ggplot(all25kbresults[which(all25kbresults$Metric=="Informedness" |
+                                               all25kbresults$Metric=="Balanced Acc"),],
+                       aes(x=Resampling, y=Performance, fill=CL)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Metric) +
+  xlab("Resampling Technique") +
+  ylim(0,.8)+
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Cell Line")+
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
 ```
@@
 
-all50kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all50kbresults$Performance <- c(round(rfperf_gm12878_50kb_none[9,2],2),
-                                round(rfperf_gm12878_50kb_none[19,2],2),
-                                round(rfperf_gm12878_50kb_none[16,2],2),
-                                round(rfperf_gm12878_50kb_none[15,2],2),
+all50kbresults <- data.frame(Resampling=c(rep("None", 12),
+                                       rep("RUS", 12),
+                                       rep("ROS", 12),
+                                       rep("SMOTE", 12),
+                                       rep("ROSE", 12)),
+                          CL=rep(c(rep("GM12878",6),
+                               rep("K562", 6)),5),
+                          Metric=rep(c("Accuracy", 
+                                       "AUPRC", 
+                                       "F1-Score", 
+                                       "MCC",
+                                       "Informedness",
+                                       "Balanced Acc"), 10))
+
+all50kbresults$Performance <- c(round(rfperf_gm12878_50kb_none[9,2],2), #accuracy
+                                round(rfperf_gm12878_50kb_none[19,2],2), #auprc
+                                round(rfperf_gm12878_50kb_none[16,2],2), #f1
+                                round(rfperf_gm12878_50kb_none[15,2],2), #mcc
+								round(rfperf_gm12878_50kb_none[18,2],2), #youden
+								(round(rfperf_gm12878_50kb_none[6,2],2) + round(rfperf_gm12878_50kb_none[7,2],2))/2, #balanced accuracy
+
                                 round(rfperf_K562_50kb_none[9,2],2),
@@
                                 round(rfperf_K562_50kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_50kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_rus[15,]),2),
-                                round(mean(rfperf_K562_50kb_rus[9,]),2),
-                                round(mean(rfperf_K562_50kb_rus[19,]),2),
-                                round(mean(rfperf_K562_50kb_rus[16,]),2),
-                                round(mean(rfperf_K562_50kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[15,]),2),
-                                round(mean(rfperf_K562_50kb_ros[9,]),2),
-                                round(mean(rfperf_K562_50kb_ros[19,]),2),
-                                round(mean(rfperf_K562_50kb_ros[16,]),2),
-                                round(mean(rfperf_K562_50kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[15,]),2),
-                                round(mean(rfperf_K562_50kb_smote[9,]),2),
-                                round(mean(rfperf_K562_50kb_smote[19,]),2),
-                                round(mean(rfperf_K562_50kb_smote[16,]),2),
-                                round(mean(rfperf_K562_50kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[15,]),2),
-                                round(mean(rfperf_K562_50kb_rose[9,]),2),
-                                round(mean(rfperf_K562_50kb_rose[19,]),2),
-                                round(mean(rfperf_K562_50kb_rose[16,]),2),
-                                round(mean(rfperf_K562_50kb_rose[15,]),2))
-
-all50kbresults$Resampling <- factor(all50kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all50kbresults$CL <- factor(all50kbresults$CL, levels=c("GM12878", "K562"))
-all50kbresults$Metric <- factor(all50kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
+								round(rfperf_K562_50kb_none[18,2],2),
+								(round(rfperf_K562_50kb_none[6,2],2) + round(rfperf_K562_50kb_none[7,2],2))/2,
+
+                                round(mean(rfperf_gm12878_50kb_rus[9,1]),2),
+                                round(mean(rfperf_gm12878_50kb_rus[19,1]),2),
+                                round(mean(rfperf_gm12878_50kb_rus[16,1]),2),
+                                round(mean(rfperf_gm12878_50kb_rus[15,1]),2),
+								round(mean(rfperf_gm12878_50kb_rus[18,1]),2),
+								(round(mean(rfperf_gm12878_50kb_rus[6,1]),2) + round(mean(rfperf_gm12878_50kb_rus[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_50kb_rus[9,1]),2),
+                                round(mean(rfperf_K562_50kb_rus[19,1]),2),
+                                round(mean(rfperf_K562_50kb_rus[16,1]),2),
+                                round(mean(rfperf_K562_50kb_rus[15,1]),2),
+								round(mean(rfperf_K562_50kb_rus[18,1]),2),
+								(round(mean(rfperf_K562_50kb_rus[6,1]),2) + round(mean(rfperf_K562_50kb_rus[7,1]),2))/2,
+
+                                round(mean(rfperf_gm12878_50kb_ros[9,1]),2),
+                                round(mean(rfperf_gm12878_50kb_ros[19,1]),2),
+                                round(mean(rfperf_gm12878_50kb_ros[16,1]),2),
+                                round(mean(rfperf_gm12878_50kb_ros[15,1]),2),
+								round(mean(rfperf_gm12878_50kb_ros[18,1]),2),
+								(round(mean(rfperf_gm12878_50kb_ros[6,1]),2) + round(mean(rfperf_gm12878_50kb_ros[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_50kb_ros[9,1]),2),
+                                round(mean(rfperf_K562_50kb_ros[19,1]),2),
+                                round(mean(rfperf_K562_50kb_ros[16,1]),2),
+                                round(mean(rfperf_K562_50kb_ros[15,1]),2),
+								round(mean(rfperf_K562_50kb_ros[18,1]),2),
+								(round(mean(rfperf_K562_50kb_ros[6,1]),2) + round(mean(rfperf_K562_50kb_ros[7,1]),2))/2,
+
+                                round(mean(rfperf_gm12878_50kb_smote[9,1]),2),
+                                round(mean(rfperf_gm12878_50kb_smote[19,1]),2),
+                                round(mean(rfperf_gm12878_50kb_smote[16,1]),2),
+                                round(mean(rfperf_gm12878_50kb_smote[15,1]),2),
+								round(mean(rfperf_gm12878_50kb_smote[18,1]),2),
+								(round(mean(rfperf_gm12878_50kb_smote[6,1]),2) + round(mean(rfperf_gm12878_50kb_smote[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_50kb_smote[9,1]),2),
+                                round(mean(rfperf_K562_50kb_smote[19,1]),2),
+                                round(mean(rfperf_K562_50kb_smote[16,1]),2),
+                                round(mean(rfperf_K562_50kb_smote[15,1]),2),
+								round(mean(rfperf_K562_50kb_smote[18,1]),2),
+								(round(mean(rfperf_K562_50kb_smote[6,1]),2) + round(mean(rfperf_K562_50kb_smote[7,1]),2))/2,
+
+                                round(mean(rfperf_gm12878_50kb_rose[9,1]),2),
+                                round(mean(rfperf_gm12878_50kb_rose[19,1]),2),
+                                round(mean(rfperf_gm12878_50kb_rose[16,1]),2),
+                                round(mean(rfperf_gm12878_50kb_rose[15,1]),2),
+								round(mean(rfperf_gm12878_50kb_rose[18,1]),2),
+								(round(mean(rfperf_gm12878_50kb_rose[6,1]),2) + round(mean(rfperf_gm12878_50kb_rose[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_50kb_rose[9,1]),2),
+                                round(mean(rfperf_K562_50kb_rose[19,1]),2),
+                                round(mean(rfperf_K562_50kb_rose[16,1]),2),
+                                round(mean(rfperf_K562_50kb_rose[15,1]),2),
+								round(mean(rfperf_K562_50kb_rose[18,1]),2),
+								(round(mean(rfperf_K562_50kb_rose[6,1]),2) + round(mean(rfperf_K562_50kb_rose[7,1]),2))/2)
+
+#all50kbresults$Resampling <- factor(all50kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
+#all50kbresults$CL <- factor(all50kbresults$CL, levels=c("GM12878", "K562"))
+#all50kbresults$Metric <- factor(all50kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
 
@@
 
+#comparing only informedness and balanced accuracy
+informBA50kbplot <- ggplot(all50kbresults[which(all50kbresults$Metric=="Informedness" |
+                                               all50kbresults$Metric=="Balanced Acc"),],
+                       aes(x=Resampling, y=Performance, fill=CL)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Metric) +
+  xlab("Resampling Technique") +
+  ylim(0,.8)+
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Cell Line")+
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
 ```
@@
 
-all100kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all100kbresults$Performance <- c(round(rfperf_gm12878_100kb_none[9,2],2),
-                                round(rfperf_gm12878_100kb_none[19,2],2),
-                                round(rfperf_gm12878_100kb_none[16,2],2),
-                                round(rfperf_gm12878_100kb_none[15,2],2),
+all100kbresults <- data.frame(Resampling=c(rep("None", 12),
+                                       rep("RUS", 12),
+                                       rep("ROS", 12),
+                                       rep("SMOTE", 12),
+                                       rep("ROSE", 12)),
+                          CL=rep(c(rep("GM12878", 6),
+                               rep("K562", 6)),5),
+                          Metric=rep(c("Accuracy", 
+                                       "AUPRC", 
+                                       "F1-Score", 
+                                       "MCC",
+                                       "Informedness",
+                                       "Balanced Acc"), 10))
+
+all100kbresults$Performance <- c(round(rfperf_gm12878_100kb_none[9,2],2), #accuracy
+                                round(rfperf_gm12878_100kb_none[19,2],2), #auprc
+                                round(rfperf_gm12878_100kb_none[16,2],2), #f1
+                                round(rfperf_gm12878_100kb_none[15,2],2), #mcc
+								round(rfperf_gm12878_100kb_none[18,2],2), #youden
+								(round(rfperf_gm12878_100kb_none[6,2],2) + round(rfperf_gm12878_100kb_none[7,2],2))/2, #balanced accuracy
+
                                 round(rfperf_K562_100kb_none[9,2],2),
@@
                                 round(rfperf_K562_100kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_100kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_rus[15,]),2),
-                                round(mean(rfperf_K562_100kb_rus[9,]),2),
-                                round(mean(rfperf_K562_100kb_rus[19,]),2),
-                                round(mean(rfperf_K562_100kb_rus[16,]),2),
-                                round(mean(rfperf_K562_100kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[15,]),2),
-                                round(mean(rfperf_K562_100kb_ros[9,]),2),
-                                round(mean(rfperf_K562_100kb_ros[19,]),2),
-                                round(mean(rfperf_K562_100kb_ros[16,]),2),
-                                round(mean(rfperf_K562_100kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[15,]),2),
-                                round(mean(rfperf_K562_100kb_smote[9,]),2),
-                                round(mean(rfperf_K562_100kb_smote[19,]),2),
-                                round(mean(rfperf_K562_100kb_smote[16,]),2),
-                                round(mean(rfperf_K562_100kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[15,]),2),
-                                round(mean(rfperf_K562_100kb_rose[9,]),2),
-                                round(mean(rfperf_K562_100kb_rose[19,]),2),
-                                round(mean(rfperf_K562_100kb_rose[16,]),2),
-                                round(mean(rfperf_K562_100kb_rose[15,]),2))
-
-all100kbresults$Resampling <- factor(all100kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all100kbresults$CL <- factor(all100kbresults$CL, levels=c("GM12878", "K562"))
-all100kbresults$Metric <- factor(all100kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
+								round(rfperf_K562_100kb_none[18,2],2),
+								(round(rfperf_K562_100kb_none[6,2],2) + round(rfperf_K562_100kb_none[7,2],2))/2,
+
+                                round(mean(rfperf_gm12878_100kb_rus[9,1]),2),
+                                round(mean(rfperf_gm12878_100kb_rus[19,1]),2),
+                                round(mean(rfperf_gm12878_100kb_rus[16,1]),2),
+                                round(mean(rfperf_gm12878_100kb_rus[15,1]),2),
+								round(mean(rfperf_gm12878_100kb_rus[18,1]),2),
+								(round(mean(rfperf_gm12878_100kb_rus[6,1]),2) + round(mean(rfperf_gm12878_100kb_rus[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_100kb_rus[9,1]),2),
+                                round(mean(rfperf_K562_100kb_rus[19,1]),2),
+                                round(mean(rfperf_K562_100kb_rus[16,1]),2),
+                                round(mean(rfperf_K562_100kb_rus[15,1]),2),
+								round(mean(rfperf_K562_100kb_rus[18,1]),2),
+								(round(mean(rfperf_K562_100kb_rus[6,1]),2) + round(mean(rfperf_K562_100kb_rus[7,1]),2))/2,
+
+                                round(mean(rfperf_gm12878_100kb_ros[9,1]),2),
+                                round(mean(rfperf_gm12878_100kb_ros[19,1]),2),
+                                round(mean(rfperf_gm12878_100kb_ros[16,1]),2),
+                                round(mean(rfperf_gm12878_100kb_ros[15,1]),2),
+								round(mean(rfperf_gm12878_100kb_ros[18,1]),2),
+								(round(mean(rfperf_gm12878_100kb_ros[6,1]),2) + round(mean(rfperf_gm12878_100kb_ros[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_100kb_ros[9,1]),2),
+                                round(mean(rfperf_K562_100kb_ros[19,1]),2),
+                                round(mean(rfperf_K562_100kb_ros[16,1]),2),
+                                round(mean(rfperf_K562_100kb_ros[15,1]),2),
+								round(mean(rfperf_K562_100kb_ros[18,1]),2),
+								(round(mean(rfperf_K562_100kb_ros[6,1]),2) + round(mean(rfperf_K562_100kb_ros[7,1]),2))/2,
+
+                                round(mean(rfperf_gm12878_100kb_smote[9,1]),2),
+                                round(mean(rfperf_gm12878_100kb_smote[19,1]),2),
+                                round(mean(rfperf_gm12878_100kb_smote[16,1]),2),
+                                round(mean(rfperf_gm12878_100kb_smote[15,1]),2),
+								round(mean(rfperf_gm12878_100kb_smote[18,1]),2),
+								(round(mean(rfperf_gm12878_100kb_smote[6,1]),2) + round(mean(rfperf_gm12878_100kb_smote[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_100kb_smote[9,1]),2),
+                                round(mean(rfperf_K562_100kb_smote[19,1]),2),
+                                round(mean(rfperf_K562_100kb_smote[16,1]),2),
+                                round(mean(rfperf_K562_100kb_smote[15,1]),2),
+								round(mean(rfperf_K562_100kb_smote[18,1]),2),
+								(round(mean(rfperf_K562_100kb_smote[6,1]),2) + round(mean(rfperf_K562_100kb_smote[7,1]),2))/2,
+
+                                round(mean(rfperf_gm12878_100kb_rose[9,1]),2),
+                                round(mean(rfperf_gm12878_100kb_rose[19,1]),2),
+                                round(mean(rfperf_gm12878_100kb_rose[16,1]),2),
+                                round(mean(rfperf_gm12878_100kb_rose[15,1]),2),
+								round(mean(rfperf_gm12878_100kb_rose[18,1]),2),
+								(round(mean(rfperf_gm12878_100kb_rose[6,1]),2) + round(mean(rfperf_gm12878_100kb_rose[7,1]),2))/2,
+
+                                round(mean(rfperf_K562_100kb_rose[9,1]),2),
+                                round(mean(rfperf_K562_100kb_rose[19,1]),2),
+                                round(mean(rfperf_K562_100kb_rose[16,1]),2),
+                                round(mean(rfperf_K562_100kb_rose[15,1]),2),
+								round(mean(rfperf_K562_100kb_rose[18,1]),2),
+								(round(mean(rfperf_K562_100kb_rose[6,1]),2) + round(mean(rfperf_K562_100kb_rose[7,1]),2))/2)
+
+#all100kbresults$Resampling <- factor(all100kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
+#all100kbresults$CL <- factor(all100kbresults$CL, levels=c("GM12878", "K562"))
+#all100kbresults$Metric <- factor(all100kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
 
@@
   xlab("Resampling Technique") +
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Cell Line")+
+  #guides(fill=FALSE)+
+	theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+#comparing only informedness and balanced accuracy
+informBA100kbplot <- ggplot(all100kbresults[which(all100kbresults$Metric=="Informedness" |
+                                               all100kbresults$Metric=="Balanced Acc"),],
+                       aes(x=Resampling, y=Performance, fill=CL)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Metric) +
+  xlab("Resampling Technique") +
+  ylim(0,.8)+
   theme_minimal() +

### 2019-02-27 Manuscript/manuscript.Rmd
added more info for AUPRC; commented out other metrics in case we decide to use them

@@
 A better threshold-free measure to use when dealing with imbalanced data is the area under the precision-recall curve (AUPRC).
+The interpretation of the AUPRC of a model is similar to that of the AUROC.
+However, where as the baseline model performance according to the AUROC is given by 0.50, the baseline model performance according to the AUPRC is given by the ratio of true positives over the total number of cases.
+This enables a more realistic benchmark to evaluate a model on as this ratio will be lower than 0.5 for a test data set with imbalanced classes.
 Likewise, threshold-specific metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
@@
 Informedness, also referred to as Youden's Index, measures the probability of the model making an informed decision and corresponds to giving equal weight per class, rather than to each instance like Accuracy [@youden1950index;@powers2011evaluation].
+
+<!--
+Better measures to consider are composite metrics involving both precision and recall together.
+Therefore, measures like the F1-Score, Youden's Index (YI), and Matthew's Correlation Coefficient (MCC) offer better interpretation, especially in the instance of imbalanced classes [@jeni2013facing].
+The F1-Score can be interpreted as a weighted average of the precision and recall values, while Youden's index is interpreted as the arithmetic mean between sensitivity (recall) and specificity.
+MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications.
+Each metric uses all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
+-->
 

### 2019-02-27 Scripts/performances.rmd
added results to performance script

@@
 library(ROSE)
+library(lattice)
 
@@
 
-#Evaluating Feature Engineering
+#Feature Engineering
+
+## Exploring Correlations
+
+###GM12878
+
+####10kb
+
+```{r}
+
+train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
+
+binswtad <- train[which(train$y=="Yes"),]
+binswtad <- binswtad[,grep("count", names(binswtad))]
+
+names(binswtad) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", names(binswtad))
+
+cormat <- cor(binswtad)
+
+get_upper_tri <- function(cormat){
+    cormat[lower.tri(cormat)]<- NA
+    return(cormat)
+}
+
+upper_tri <- get_upper_tri(cormat)
+
+melted_cormat <- melt(upper_tri, na.rm = TRUE)
+
+reorder_cormat <- function(cormat){
+# Use correlation between variables as distance
+dd <- as.dist((1-cormat)/2)
+hc <- hclust(dd)
+cormat <-cormat[hc$order, hc$order]
+}
+
+cormat_reorder <- reorder_cormat(cormat)
+
+upper_tri_reorder <- get_upper_tri(cormat_reorder)
+
+melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)
+
+corplot_gm12878_10kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
+ geom_tile(color = "white")+
+ scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
+   midpoint = 0, limit = c(-1,1), space = "Lab", 
+   name="Pearson\nCorrelation") +
+ ylab("") +
+ xlab("") +  
+ theme_minimal()+ 
+ theme(axis.text.x = element_text(angle = 45, vjust = 1, 
+    size = 10, hjust = 1),
+       axis.text.y = element_text(size = 10))
+ #coord_fixed()
+
+pvals <- rcorr(as.matrix(binswtad))$P
+upper_tri_pvals <- get_upper_tri(pvals) 
+melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
+melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
+melted_cormat2$pvals <- melted_pvals$value
+
+#find significant correlations
+sigcorrs_gm12878_10kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
+dim(sigcorrs_gm12878_10kb) #4595    4
+sigcorrs_gm12878_10kb[,3:4] <- round(sigcorrs_gm12878_10kb[,3:4], 4)
+sigcorrs_gm12878_10kb <- sigcorrs_gm12878_10kb[order(sigcorrs_gm12878_10kb$pvals, decreasing = FALSE),]
+
+highcorrs_gm12878_10kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
+dim(highcorrs_gm12878_10kb) #21  4
+highcorrs_gm12878_10kb[,3:4] <- round(highcorrs_gm12878_10kb[,3:4], 2)
+highcorrs_gm12878_10kb <- highcorrs_gm12878_10kb[order(abs(highcorrs_gm12878_10kb$value), decreasing = TRUE),]
+
+#clustered heatmap
+clustcorplot_gm12878_10kb <- heatmap.2(cormat,
+          #cellnote = cormat,  # same data set for cell labels
+          main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(12,9),     # widens margins around plot
+          #col=my_palette,       # use on color palette defined earlier
+          #breaks=col_breaks,    # enable color transition at specified limits
+          dendrogram="row",     # only draw a row dendrogram
+          keysize = 1) 
+```
+
+####25kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
+
+binswtad <- train[which(train$y=="Yes"),]
+binswtad <- binswtad[,grep("count", names(binswtad))]
+
+names(binswtad) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", names(binswtad))
+
+cormat <- cor(binswtad)
+
+get_upper_tri <- function(cormat){
+    cormat[lower.tri(cormat)]<- NA
+    return(cormat)
+}
+
+upper_tri <- get_upper_tri(cormat)
+
+melted_cormat <- melt(upper_tri, na.rm = TRUE)
+
+reorder_cormat <- function(cormat){
+# Use correlation between variables as distance
+dd <- as.dist((1-cormat)/2)
+hc <- hclust(dd)
+cormat <-cormat[hc$order, hc$order]
+}
+
+cormat_reorder <- reorder_cormat(cormat)
+
+upper_tri_reorder <- get_upper_tri(cormat_reorder)
+
+melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)
+
+corplot_gm12878_25kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
+ geom_tile(color = "white")+
+ scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
+   midpoint = 0, limit = c(-1,1), space = "Lab", 
+   name="Pearson\nCorrelation") +
+ ylab("") +
+ xlab("") +  
+ theme_minimal()+ 
+ theme(axis.text.x = element_text(angle = 45, vjust = 1, 
+    size = 10, hjust = 1),
+       axis.text.y = element_text(size = 10))
+ #coord_fixed()
+
+pvals <- rcorr(as.matrix(binswtad))$P
+upper_tri_pvals <- get_upper_tri(pvals) 
+melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
+melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
+melted_cormat2$pvals <- melted_pvals$value
+
+#find significant correlations
+sigcorrs_gm12878_25kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
+dim(sigcorrs_gm12878_25kb) #4683    4
+sigcorrs_gm12878_25kb[,3:4] <- round(sigcorrs_gm12878_25kb[,3:4], 4)
+sigcorrs_gm12878_25kb <- sigcorrs_gm12878_25kb[order(sigcorrs_gm12878_25kb$pvals, decreasing = FALSE),]
+
+highcorrs_gm12878_25kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
+dim(highcorrs_gm12878_25kb) #50  4
+highcorrs_gm12878_25kb[,3:4] <- round(highcorrs_gm12878_25kb[,3:4], 2)
+highcorrs_gm12878_25kb <- highcorrs_gm12878_25kb[order(abs(highcorrs_gm12878_25kb$value), decreasing = TRUE),]
+
+#clustered heatmap
+clustcorplot_gm12878_25kb <- heatmap.2(cormat,
+          #cellnote = cormat,  # same data set for cell labels
+          main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(6,6),     # widens margins around plot
+          #col=my_palette,       # use on color palette defined earlier
+          #breaks=col_breaks,    # enable color transition at specified limits
+          dendrogram="row",     # only draw a row dendrogram
+          keysize = 1) 
+```
+
+####50kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
+
+binswtad <- train[which(train$y=="Yes"),]
+binswtad <- binswtad[,grep("count", names(binswtad))]
+
+names(binswtad) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", names(binswtad))
+
+cormat <- cor(binswtad)
+
+get_upper_tri <- function(cormat){
+    cormat[lower.tri(cormat)]<- NA
+    return(cormat)
+}
+
+upper_tri <- get_upper_tri(cormat)
+
+melted_cormat <- melt(upper_tri, na.rm = TRUE)
+
+reorder_cormat <- function(cormat){
+# Use correlation between variables as distance
+dd <- as.dist((1-cormat)/2)
+hc <- hclust(dd)
+cormat <-cormat[hc$order, hc$order]
+}
+
+cormat_reorder <- reorder_cormat(cormat)
+
+upper_tri_reorder <- get_upper_tri(cormat_reorder)
+
+melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)
+
+corplot_gm12878_50kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
+ geom_tile(color = "white")+
+ scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
+   midpoint = 0, limit = c(-1,1), space = "Lab", 
+   name="Pearson\nCorrelation") +
+ ylab("") +
+ xlab("") +  
+ theme_minimal()+ 
+ theme(axis.text.x = element_text(angle = 45, vjust = 1, 
+    size = 10, hjust = 1),
+       axis.text.y = element_text(size = 10))
+ #coord_fixed()
+
+pvals <- rcorr(as.matrix(binswtad))$P
+upper_tri_pvals <- get_upper_tri(pvals) 
+melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
+melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
+melted_cormat2$pvals <- melted_pvals$value
+
+#find significant correlations
+sigcorrs_gm12878_50kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
+dim(sigcorrs_gm12878_50kb) #
+sigcorrs_gm12878_50kb[,3:4] <- round(sigcorrs_gm12878_50kb[,3:4], 4)
+sigcorrs_gm12878_50kb <- sigcorrs_gm12878_50kb[order(sigcorrs_gm12878_50kb$pvals, decreasing = FALSE),]
+
+highcorrs_gm12878_50kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
+dim(highcorrs_gm12878_50kb) #
+highcorrs_gm12878_50kb[,3:4] <- round(highcorrs_gm12878_50kb[,3:4], 2)
+highcorrs_gm12878_50kb <- highcorrs_gm12878_50kb[order(abs(highcorrs_gm12878_50kb$value), decreasing = TRUE),]
+
+#clustered heatmap
+clustcorplot_gm12878_50kb <- heatmap.2(cormat,
+          #cellnote = cormat,  # same data set for cell labels
+          main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(6,6),     # widens margins around plot
+          #col=my_palette,       # use on color palette defined earlier
+          #breaks=col_breaks,    # enable color transition at specified limits
+          dendrogram="row",     # only draw a row dendrogram
+          keysize = 1)
+```
+
+####100kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
+
+binswtad <- train[which(train$y=="Yes"),]
+binswtad <- binswtad[,grep("count", names(binswtad))]
+
+names(binswtad) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", names(binswtad))
+
+cormat <- cor(binswtad)
+
+get_upper_tri <- function(cormat){
+    cormat[lower.tri(cormat)]<- NA
+    return(cormat)
+}
+
+upper_tri <- get_upper_tri(cormat)
+
+melted_cormat <- melt(upper_tri, na.rm = TRUE)
+
+reorder_cormat <- function(cormat){
+# Use correlation between variables as distance
+dd <- as.dist((1-cormat)/2)
+hc <- hclust(dd)
+cormat <-cormat[hc$order, hc$order]
+}
+
+cormat_reorder <- reorder_cormat(cormat)
+
+upper_tri_reorder <- get_upper_tri(cormat_reorder)
+
+melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)
+
+corplot_gm12878_100kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
+ geom_tile(color = "white")+
+ scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
+   midpoint = 0, limit = c(-1,1), space = "Lab", 
+   name="Pearson\nCorrelation") +
+ ylab("") +
+ xlab("") +  
+ theme_minimal()+ 
+ theme(axis.text.x = element_text(angle = 45, vjust = 1, 
+    size = 10, hjust = 1),
+       axis.text.y = element_text(size = 10))
+ #coord_fixed()
+
+pvals <- rcorr(as.matrix(binswtad))$P
+upper_tri_pvals <- get_upper_tri(pvals) 
+melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
+melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
+melted_cormat2$pvals <- melted_pvals$value
+
+#find significant correlations
+sigcorrs_gm12878_100kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
+dim(sigcorrs_gm12878_100kb) #4373    4
+sigcorrs_gm12878_100kb[,3:4] <- round(sigcorrs_gm12878_100kb[,3:4], 4)
+sigcorrs_gm12878_100kb <- sigcorrs_gm12878_100kb[order(sigcorrs_gm12878_100kb$pvals, decreasing = FALSE),]
+
+highcorrs_gm12878_100kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
+dim(highcorrs_gm12878_100kb) #424   4
+highcorrs_gm12878_100kb[,3:4] <- round(highcorrs_gm12878_100kb[,3:4], 2)
+highcorrs_gm12878_100kb <- highcorrs_gm12878_100kb[order(abs(highcorrs_gm12878_100kb$value), decreasing = TRUE),]
+
+#clustered heatmap
+clustcorplot_gm12878_100kb <- heatmap.2(cormat,
+          #cellnote = cormat,  # same data set for cell labels
+          main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(6,6),     # widens margins around plot
+          #col=my_palette,       # use on color palette defined earlier
+          #breaks=col_breaks,    # enable color transition at specified limits
+          dendrogram="row",     # only draw a row dendrogram
+          keysize = 1)
+```
+
+###K562
 
@@
 
+## Evaluating Regularization
+
+### GM12878
+
+####10kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_10kb_gm12878, 
+                      enetcoefs_none_op_10kb_gm12878, 
+                      enetcoefs_none_dist_10kb_gm12878,
+                      enetcoefs_RUS_oc_10kb_gm12878, 
+                      enetcoefs_RUS_op_10kb_gm12878, 
+                      enetcoefs_RUS_dist_10kb_gm12878,
+                      enetcoefs_ROS_oc_10kb_gm12878, 
+                      enetcoefs_ROS_op_10kb_gm12878, 
+                      enetcoefs_ROS_dist_10kb_gm12878,
+                      enetcoefs_SMOTE_oc_10kb_gm12878, 
+                      enetcoefs_SMOTE_op_10kb_gm12878, 
+                      enetcoefs_SMOTE_dist_10kb_gm12878)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_10kb <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_10kb[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_10kb), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
+
+featuredf <- data.frame(featuremat_10kb)
+featuredf$Feature <- rownames(featuredf)
+rownames(featuredf) <- NULL
+featuredf <- featuredf[,c(13,1:12)]
+names(featuredf) <- c("Feature",
+                      "None.OC", "None.OP", "None.Distance",
+                      "RUS.OC", "RUS.OP", "RUS.Distance",
+                      "ROS.OC", "ROS.OP", "ROS.Distance",
+                      "SMOTE.OC", "SMOTE.OP", "SMOTE.Distance")
+
+x <- melt(featuredf, id.vars = 1)
+
+```
+
+####25kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_25kb_gm12878, 
+                      enetcoefs_none_op_25kb_gm12878, 
+                      enetcoefs_none_dist_25kb_gm12878,
+                      enetcoefs_RUS_oc_25kb_gm12878, 
+                      enetcoefs_RUS_op_25kb_gm12878, 
+                      enetcoefs_RUS_dist_25kb_gm12878,
+                      enetcoefs_ROS_oc_25kb_gm12878, 
+                      enetcoefs_ROS_op_25kb_gm12878, 
+                      enetcoefs_ROS_dist_25kb_gm12878,
+                      enetcoefs_SMOTE_oc_25kb_gm12878, 
+                      enetcoefs_SMOTE_op_25kb_gm12878, 
+                      enetcoefs_SMOTE_dist_25kb_gm12878)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_25kb <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_25kb[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_25kb), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
+
+featuredf <- data.frame(featuremat_25kb)
+featuredf$Feature <- rownames(featuredf)
+rownames(featuredf) <- NULL
+featuredf <- featuredf[,c(13,1:12)]
+names(featuredf) <- c("Feature",
+                      "None.OC", "None.OP", "None.Distance",
+                      "RUS.OC", "RUS.OP", "RUS.Distance",
+                      "ROS.OC", "ROS.OP", "ROS.Distance",
+                      "SMOTE.OC", "SMOTE.OP", "SMOTE.Distance")
+
+x <- melt(featuredf, id.vars = 1)
+
+```
+
+####50kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_50kb_gm12878, 
+                      enetcoefs_none_op_50kb_gm12878, 
+                      enetcoefs_none_dist_50kb_gm12878,
+                      enetcoefs_RUS_oc_50kb_gm12878, 
+                      enetcoefs_RUS_op_50kb_gm12878, 
+                      enetcoefs_RUS_dist_50kb_gm12878,
+                      enetcoefs_ROS_oc_50kb_gm12878, 
+                      enetcoefs_ROS_op_50kb_gm12878, 
+                      enetcoefs_ROS_dist_50kb_gm12878,
+                      enetcoefs_SMOTE_oc_50kb_gm12878, 
+                      enetcoefs_SMOTE_op_50kb_gm12878, 
+                      enetcoefs_SMOTE_dist_50kb_gm12878)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_50kb <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_50kb[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_50kb), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
+
+featuredf <- data.frame(featuremat_50kb)
+featuredf$Feature <- rownames(featuredf)
+rownames(featuredf) <- NULL
+featuredf <- featuredf[,c(13,1:12)]
+names(featuredf) <- c("Feature",
+                      "None.OC", "None.OP", "None.Distance",
+                      "RUS.OC", "RUS.OP", "RUS.Distance",
+                      "ROS.OC", "ROS.OP", "ROS.Distance",
+                      "SMOTE.OC", "SMOTE.OP", "SMOTE.Distance")
+
+x <- melt(featuredf, id.vars = 1)
+
+```
+
+####100kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_100kb_gm12878, 
+                      enetcoefs_none_op_100kb_gm12878, 
+                      enetcoefs_none_dist_100kb_gm12878,
+                      enetcoefs_RUS_oc_100kb_gm12878, 
+                      enetcoefs_RUS_op_100kb_gm12878, 
+                      enetcoefs_RUS_dist_100kb_gm12878,
+                      enetcoefs_ROS_oc_100kb_gm12878, 
+                      enetcoefs_ROS_op_100kb_gm12878, 
+                      enetcoefs_ROS_dist_100kb_gm12878,
+                      enetcoefs_SMOTE_oc_100kb_gm12878, 
+                      enetcoefs_SMOTE_op_100kb_gm12878, 
+                      enetcoefs_SMOTE_dist_100kb_gm12878)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_100kb <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_100kb[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_100kb), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
+
+featuredf <- data.frame(featuremat_100kb)
+featuredf$Feature <- rownames(featuredf)
+rownames(featuredf) <- NULL
+featuredf <- featuredf[,c(13,1:12)]
+names(featuredf) <- c("Feature",
+                      "None.OC", "None.OP", "None.Distance",
+                      "RUS.OC", "RUS.OP", "RUS.Distance",
+                      "ROS.OC", "ROS.OP", "ROS.Distance",
+                      "SMOTE.OC", "SMOTE.OP", "SMOTE.Distance")
+
+x <- melt(featuredf, id.vars = 1)
+
+```
+
+####Combined
+
+```{r}
+all_featuremat_gm12878 <- cbind(featuremat_10kb,featuremat_25kb,featuremat_50kb,featuremat_100kb)
+levelplot(t(all_featuremat_gm12878), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45, cex=.5),
+                      alternating=3,
+                      y=list(cex=.7)), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 1.5, lty = "dashed");
+            panel.abline(v = 2.5, lty = "dashed");
+            panel.abline(v = 3.5);
+            panel.abline(v = 4.5, lty = "dashed");
+            panel.abline(v = 5.5, lty = "dashed");
+            panel.abline(v = 6.5);
+            panel.abline(v = 7.5, lty = "dashed");
+            panel.abline(v = 8.5, lty = "dashed");
+            panel.abline(v = 9.5);
+            panel.abline(v = 10.5, lty = "dashed");
+            panel.abline(v = 11.5, lty = "dashed");
+            panel.abline(v = 12.5, col="yellow");
+            panel.abline(v = 13.5, lty = "dashed");
+            panel.abline(v = 14.5, lty = "dashed");
+            panel.abline(v = 15.5);
+            panel.abline(v = 16.5, lty = "dashed");
+            panel.abline(v = 17.5, lty = "dashed");
+            panel.abline(v = 18.5);
+            panel.abline(v = 19.5, lty = "dashed");
+            panel.abline(v = 20.5, lty = "dashed");
+            panel.abline(v = 21.5);
+            panel.abline(v = 22.5, lty = "dashed");
+            panel.abline(v = 23.5, lty = "dashed");
+            panel.abline(v = 24.5, col="yellow");
+            panel.abline(v = 25.5, lty = "dashed");
+            panel.abline(v = 26.5, lty = "dashed");
+            panel.abline(v = 27.5);
+            panel.abline(v = 28.5, lty = "dashed");
+            panel.abline(v = 29.5, lty = "dashed");
+            panel.abline(v = 30.5);
+            panel.abline(v = 31.5, lty = "dashed");
+            panel.abline(v = 32.5, lty = "dashed");
+            panel.abline(v = 33.5);
+            panel.abline(v = 34.5, lty = "dashed");
+            panel.abline(v = 35.5, lty = "dashed");
+            panel.abline(v = 36.5, col="yellow");
+            panel.abline(v = 37.5, lty = "dashed");
+            panel.abline(v = 38.5, lty = "dashed");
+            panel.abline(v = 39.5);
+            panel.abline(v = 40.5, lty = "dashed");
+            panel.abline(v = 41.5, lty = "dashed");
+            panel.abline(v = 42.5);
+            panel.abline(v = 43.5, lty = "dashed");
+            panel.abline(v = 44.5, lty = "dashed");
+            panel.abline(v = 45.5);
+            panel.abline(v = 46.5, lty = "dashed");
+            panel.abline(v = 47.5, lty = "dashed");
+          },
+          xlab="",
+          ylab="")
+```
+
+### K562
+
+####10kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_10kb_K562, 
+                      enetcoefs_none_op_10kb_K562, 
+                      enetcoefs_none_dist_10kb_K562,
+                      enetcoefs_RUS_oc_10kb_K562, 
+                      enetcoefs_RUS_op_10kb_K562, 
+                      enetcoefs_RUS_dist_10kb_K562,
+                      enetcoefs_ROS_oc_10kb_K562, 
+                      enetcoefs_ROS_op_10kb_K562, 
+                      enetcoefs_ROS_dist_10kb_K562,
+                      enetcoefs_SMOTE_oc_10kb_K562, 
+                      enetcoefs_SMOTE_op_10kb_K562, 
+                      enetcoefs_SMOTE_dist_10kb_K562)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_10kb <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_10kb[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_10kb), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
+
+featuredf <- data.frame(featuremat_10kb)
+featuredf$Feature <- rownames(featuredf)
+rownames(featuredf) <- NULL
+featuredf <- featuredf[,c(13,1:12)]
+names(featuredf) <- c("Feature",
+                      "None.OC", "None.OP", "None.Distance",
+                      "RUS.OC", "RUS.OP", "RUS.Distance",
+                      "ROS.OC", "ROS.OP", "ROS.Distance",
+                      "SMOTE.OC", "SMOTE.OP", "SMOTE.Distance")
+
+x <- melt(featuredf, id.vars = 1)
+
+```
+
+####25kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_25kb_K562, 
+                      enetcoefs_none_op_25kb_K562, 
+                      enetcoefs_none_dist_25kb_K562,
+                      enetcoefs_RUS_oc_25kb_K562, 
+                      enetcoefs_RUS_op_25kb_K562, 
+                      enetcoefs_RUS_dist_25kb_K562,
+                      enetcoefs_ROS_oc_25kb_K562, 
+                      enetcoefs_ROS_op_25kb_K562, 
+                      enetcoefs_ROS_dist_25kb_K562,
+                      enetcoefs_SMOTE_oc_25kb_K562, 
+                      enetcoefs_SMOTE_op_25kb_K562, 
+                      enetcoefs_SMOTE_dist_25kb_K562)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_25kb <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_25kb[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_25kb), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
+
+featuredf <- data.frame(featuremat_25kb)
+featuredf$Feature <- rownames(featuredf)
+rownames(featuredf) <- NULL
+featuredf <- featuredf[,c(13,1:12)]
+names(featuredf) <- c("Feature",
+                      "None.OC", "None.OP", "None.Distance",
+                      "RUS.OC", "RUS.OP", "RUS.Distance",
+                      "ROS.OC", "ROS.OP", "ROS.Distance",
+                      "SMOTE.OC", "SMOTE.OP", "SMOTE.Distance")
+
+x <- melt(featuredf, id.vars = 1)
+
+```
+
+####50kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_50kb_K562, 
+                      enetcoefs_none_op_50kb_K562, 
+                      enetcoefs_none_dist_50kb_K562,
+                      enetcoefs_RUS_oc_50kb_K562, 
+                      enetcoefs_RUS_op_50kb_K562, 
+                      enetcoefs_RUS_dist_50kb_K562,
+                      enetcoefs_ROS_oc_50kb_K562, 
+                      enetcoefs_ROS_op_50kb_K562, 
+                      enetcoefs_ROS_dist_50kb_K562,
+                      enetcoefs_SMOTE_oc_50kb_K562, 
+                      enetcoefs_SMOTE_op_50kb_K562, 
+                      enetcoefs_SMOTE_dist_50kb_K562)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_50kb <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_50kb[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_50kb), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
+
+featuredf <- data.frame(featuremat_50kb)
+featuredf$Feature <- rownames(featuredf)
+rownames(featuredf) <- NULL
+featuredf <- featuredf[,c(13,1:12)]
+names(featuredf) <- c("Feature",
+                      "None.OC", "None.OP", "None.Distance",
+                      "RUS.OC", "RUS.OP", "RUS.Distance",
+                      "ROS.OC", "ROS.OP", "ROS.Distance",
+                      "SMOTE.OC", "SMOTE.OP", "SMOTE.Distance")
+
+x <- melt(featuredf, id.vars = 1)
+
+```
+
+####100kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_100kb_K562, 
+                      enetcoefs_none_op_100kb_K562, 
+                      enetcoefs_none_dist_100kb_K562,
+                      enetcoefs_RUS_oc_100kb_K562, 
+                      enetcoefs_RUS_op_100kb_K562, 
+                      enetcoefs_RUS_dist_100kb_K562,
+                      enetcoefs_ROS_oc_100kb_K562, 
+                      enetcoefs_ROS_op_100kb_K562, 
+                      enetcoefs_ROS_dist_100kb_K562,
+                      enetcoefs_SMOTE_oc_100kb_K562, 
+                      enetcoefs_SMOTE_op_100kb_K562, 
+                      enetcoefs_SMOTE_dist_100kb_K562)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_100kb <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_100kb[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_100kb), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
+
+featuredf <- data.frame(featuremat_100kb)
+featuredf$Feature <- rownames(featuredf)
+rownames(featuredf) <- NULL
+featuredf <- featuredf[,c(13,1:12)]
+names(featuredf) <- c("Feature",
+                      "None.OC", "None.OP", "None.Distance",
+                      "RUS.OC", "RUS.OP", "RUS.Distance",
+                      "ROS.OC", "ROS.OP", "ROS.Distance",
+                      "SMOTE.OC", "SMOTE.OP", "SMOTE.Distance")
+
+x <- melt(featuredf, id.vars = 1)
+
+```
+
+####Combined
+
+```{r}
+all_featuremat_K562 <- cbind(featuremat_10kb,featuremat_25kb,featuremat_50kb,featuremat_100kb)
+levelplot(t(all_featuremat_K562), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45, cex=.5),
+                      alternating=3,
+                      y=list(cex=.7)), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 1.5, lty = "dashed");
+            panel.abline(v = 2.5, lty = "dashed");
+            panel.abline(v = 3.5);
+            panel.abline(v = 4.5, lty = "dashed");
+            panel.abline(v = 5.5, lty = "dashed");
+            panel.abline(v = 6.5);
+            panel.abline(v = 7.5, lty = "dashed");
+            panel.abline(v = 8.5, lty = "dashed");
+            panel.abline(v = 9.5);
+            panel.abline(v = 10.5, lty = "dashed");
+            panel.abline(v = 11.5, lty = "dashed");
+            panel.abline(v = 12.5, col="yellow");
+            panel.abline(v = 13.5, lty = "dashed");
+            panel.abline(v = 14.5, lty = "dashed");
+            panel.abline(v = 15.5);
+            panel.abline(v = 16.5, lty = "dashed");
+            panel.abline(v = 17.5, lty = "dashed");
+            panel.abline(v = 18.5);
+            panel.abline(v = 19.5, lty = "dashed");
+            panel.abline(v = 20.5, lty = "dashed");
+            panel.abline(v = 21.5);
+            panel.abline(v = 22.5, lty = "dashed");
+            panel.abline(v = 23.5, lty = "dashed");
+            panel.abline(v = 24.5, col="yellow");
+            panel.abline(v = 25.5, lty = "dashed");
+            panel.abline(v = 26.5, lty = "dashed");
+            panel.abline(v = 27.5);
+            panel.abline(v = 28.5, lty = "dashed");
+            panel.abline(v = 29.5, lty = "dashed");
+            panel.abline(v = 30.5);
+            panel.abline(v = 31.5, lty = "dashed");
+            panel.abline(v = 32.5, lty = "dashed");
+            panel.abline(v = 33.5);
+            panel.abline(v = 34.5, lty = "dashed");
+            panel.abline(v = 35.5, lty = "dashed");
+            panel.abline(v = 36.5, col="yellow");
+            panel.abline(v = 37.5, lty = "dashed");
+            panel.abline(v = 38.5, lty = "dashed");
+            panel.abline(v = 39.5);
+            panel.abline(v = 40.5, lty = "dashed");
+            panel.abline(v = 41.5, lty = "dashed");
+            panel.abline(v = 42.5);
+            panel.abline(v = 43.5, lty = "dashed");
+            panel.abline(v = 44.5, lty = "dashed");
+            panel.abline(v = 45.5);
+            panel.abline(v = 46.5, lty = "dashed");
+            panel.abline(v = 47.5, lty = "dashed");
+          },
+          xlab="",
+          ylab="")
+```
+
 #Barplots of performance metrics for models with distance-type predictors
@@
 
-performancetab <- data.frame(Performance = c(rep("F1-Score", 10),
-                                             rep("MCC", 10)),
-                             Resampling = rep(c("None",
-                                                "None",
-                                                "RUS",
-                                                "RUS",
-                                                "ROS",
-                                                "ROS",
-                                                "SMOTE",
-                                                "SMOTE",
-                                                "ROSE",
-                                                "ROSE"),2),
-                             CL = rep(c("GM12878", "K562"), 10)
-                             )
-
-performancetab$kb10 <- c(rfperf_gm12878_10kb_none[16,2],
-                         rfperf_K562_10kb_none[16,2],
-                         mean(rfperf_gm12878_10kb_rus[16,]),
-                         mean(rfperf_K562_10kb_rus[16,]),
-                         mean(rfperf_gm12878_10kb_ros[16,]),
-                         mean(rfperf_K562_10kb_ros[16,]),
-                         mean(rfperf_gm12878_10kb_smote[16,]),
-                         mean(rfperf_K562_10kb_smote[16,]),
-                         mean(rfperf_gm12878_10kb_rose[16,]),
-                         mean(rfperf_K562_10kb_rose[16,]),
-                         rfperf_gm12878_10kb_none[15,2],
-                         rfperf_K562_10kb_none[15,2],
-                         mean(rfperf_gm12878_10kb_rus[15,]),
-                         mean(rfperf_K562_10kb_rus[15,]),
-                         mean(rfperf_gm12878_10kb_ros[15,]),
-                         mean(rfperf_K562_10kb_ros[15,]),
-                         mean(rfperf_gm12878_10kb_smote[15,]),
-                         mean(rfperf_K562_10kb_smote[15,]),
-                         mean(rfperf_gm12878_10kb_rose[15,]),
-                         mean(rfperf_K562_10kb_rose[15,]))
-
-performancetab$kb25 <- c(rfperf_gm12878_25kb_none[16,2],
-                         rfperf_K562_25kb_none[16,2],
-                         mean(rfperf_gm12878_25kb_rus[16,]),
-                         mean(rfperf_K562_25kb_rus[16,]),
-                         mean(rfperf_gm12878_25kb_ros[16,]),
-                         mean(rfperf_K562_25kb_ros[16,]),
-                         mean(rfperf_gm12878_25kb_smote[16,]),
-                         mean(rfperf_K562_25kb_smote[16,]),
-                         mean(rfperf_gm12878_25kb_rose[16,]),
-                         mean(rfperf_K562_25kb_rose[16,]),
-                         rfperf_gm12878_25kb_none[15,2],
-                         rfperf_K562_25kb_none[15,2],
-                         mean(rfperf_gm12878_25kb_rus[15,]),
-                         mean(rfperf_K562_25kb_rus[15,]),
-                         mean(rfperf_gm12878_25kb_ros[15,]),
-                         mean(rfperf_K562_25kb_ros[15,]),
-                         mean(rfperf_gm12878_25kb_smote[15,]),
-                         mean(rfperf_K562_25kb_smote[15,]),
-                         mean(rfperf_gm12878_25kb_rose[15,]),
-                         mean(rfperf_K562_25kb_rose[15,]))
-
-performancetab$kb50 <- c(rfperf_gm12878_50kb_none[16,2],
-                         rfperf_K562_50kb_none[16,2],
-                         mean(rfperf_gm12878_50kb_rus[16,]),
-                         mean(rfperf_K562_50kb_rus[16,]),
-                         mean(rfperf_gm12878_50kb_ros[16,]),
-                         mean(rfperf_K562_50kb_ros[16,]),
-                         mean(rfperf_gm12878_50kb_smote[16,]),
-                         mean(rfperf_K562_50kb_smote[16,]),
-                         mean(rfperf_gm12878_50kb_rose[16,]),
-                         mean(rfperf_K562_50kb_rose[16,]),
-                         rfperf_gm12878_50kb_none[15,2],
-                         rfperf_K562_50kb_none[15,2],
-                         mean(rfperf_gm12878_50kb_rus[15,]),
-                         mean(rfperf_K562_50kb_rus[15,]),
-                         mean(rfperf_gm12878_50kb_ros[15,]),
-                         mean(rfperf_K562_50kb_ros[15,]),
-                         mean(rfperf_gm12878_50kb_smote[15,]),
-                         mean(rfperf_K562_50kb_smote[15,]),
-                         mean(rfperf_gm12878_50kb_rose[15,]),
-                         mean(rfperf_K562_50kb_rose[15,]))
-
-performancetab$kb100 <- c(rfperf_gm12878_100kb_none[16,2],
-                         rfperf_K562_100kb_none[16,2],
-                         mean(rfperf_gm12878_100kb_rus[16,]),
-                         mean(rfperf_K562_100kb_rus[16,]),
-                         mean(rfperf_gm12878_100kb_ros[16,]),
-                         mean(rfperf_K562_100kb_ros[16,]),
-                         mean(rfperf_gm12878_100kb_smote[16,]),
-                         mean(rfperf_K562_100kb_smote[16,]),
-                         mean(rfperf_gm12878_100kb_rose[16,]),
-                         mean(rfperf_K562_100kb_rose[16,]),
-                         rfperf_gm12878_100kb_none[15,2],
-                         rfperf_K562_100kb_none[15,2],
-                         mean(rfperf_gm12878_100kb_rus[15,]),
-                         mean(rfperf_K562_100kb_rus[15,]),
-                         mean(rfperf_gm12878_100kb_ros[15,]),
-                         mean(rfperf_K562_100kb_ros[15,]),
-                         mean(rfperf_gm12878_100kb_smote[15,]),
-                         mean(rfperf_K562_100kb_smote[15,]),
-                         mean(rfperf_gm12878_100kb_rose[15,]),
-                         mean(rfperf_K562_100kb_rose[15,]))
-
-performancetab[,4:7] <- round(performancetab[,4:7], 3)
-```
-
-#Variable Importance Plots for distance predictors with ENET reduction
-
-##5kb
-###Random Under-Sampling
-```{r}
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/5kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf5kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf5kb <- rf5kb[order(rf5kb$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf5kb$Importance
-Labels <- as.character(rf5kb$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.5kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.5kb$Feature <- as.character(varimp.rf.df.5kb$Feature)							 
-varimp.rf.df.5kb <-varimp.rf.df.5kb[order(varimp.rf.df.5kb$Importance),]
-varimp.rf.df.5kb <- varimp.rf.df.5kb[(dim(varimp.rf.df.5kb)[1]-14):dim(varimp.rf.df.5kb)[1],]
-varimp.rf.df.5kb$Feature <- factor(varimp.rf.df.5kb$Feature,
-                                     levels=as.character(varimp.rf.df.5kb$Feature))
-
-p.rf.5kb <- ggplot(varimp.rf.df.5kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(A)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="red") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-  ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/5kb/p.rf.5kb.png")
-```
+```
+
+#Variable Importance Plots
+
+##10kb
+
+###None
+
+```{r}
+rfimpvars_gm12878_10kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/RF/rfimpvars.rds")
+rfimpvars_gm12878_10kb_none <- rfimpvars_gm12878_10kb_none[1:20,]
+
+rfimpvars_gm12878_10kb_none$Feature <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", rfimpvars_gm12878_10kb_none$Feature)
+
+rfimpvars_gm12878_10kb_none$Feature <- factor(rfimpvars_gm12878_10kb_none$Feature, levels=rfimpvars_gm12878_10kb_none$Feature)
+
+ggplot(rfimpvars_gm12878_10kb_none, aes(x=Feature, y=Importance)) +
+  geom_bar(stat="identity") +
+  theme_minimal()+
+  theme_bw()+
+  theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20))
+```
+
+###ROS
+
+```{r}
+
+```
+
+###RUS
+
+###SMOTE
+
+###ROSE
+
 ##25kb
-###Random Under-Sampling
-```{r}
-  rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/25kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf <- rf[order(rf$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf$Importance
-Labels <- as.character(rf$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.25kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.25kb$Feature <- as.character(varimp.rf.df.25kb$Feature)							 
-varimp.rf.df.25kb <-varimp.rf.df.25kb[order(varimp.rf.df.25kb$Importance),]
-varimp.rf.df.25kb <- varimp.rf.df.25kb[(dim(varimp.rf.df.25kb)[1]-14):dim(varimp.rf.df.25kb)[1],]
-varimp.rf.df.25kb$Feature <- factor(varimp.rf.df.25kb$Feature,
-                                     levels=as.character(varimp.rf.df.25kb$Feature))
-
-p.rf.25kb <- ggplot(varimp.rf.df.25kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(B)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="blue") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/25kb/p.rf.25kb.png")
-```
+
+###None
+
+```{r}
+rfimpvars_gm12878_25kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/RF/rfimpvars.rds")
+rfimpvars_gm12878_25kb_none <- rfimpvars_gm12878_25kb_none[1:20,]
+
+rfimpvars_gm12878_25kb_none$Feature <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", rfimpvars_gm12878_25kb_none$Feature)
+
+rfimpvars_gm12878_25kb_none$Feature <- factor(rfimpvars_gm12878_25kb_none$Feature, levels=rfimpvars_gm12878_25kb_none$Feature)
+
+ggplot(rfimpvars_gm12878_25kb_none, aes(x=Feature, y=Importance)) +
+  geom_bar(stat="identity") +
+  theme_minimal()+
+  theme_bw()+
+  theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20))
+```
+
+###ROS
+
+###RUS
+
+###SMOTE
+
+###ROSE
+
 ##50kb
-###Random Under-Sampling
-```{r}
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/50kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf <- rf[order(rf$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf$Importance
-Labels <- as.character(rf$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.50kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.50kb$Feature <- as.character(varimp.rf.df.50kb$Feature)							 
-varimp.rf.df.50kb <-varimp.rf.df.50kb[order(varimp.rf.df.50kb$Importance),]
-varimp.rf.df.50kb <- varimp.rf.df.50kb[(dim(varimp.rf.df.50kb)[1]-14):dim(varimp.rf.df.50kb)[1],]
-varimp.rf.df.50kb$Feature <- factor(varimp.rf.df.50kb$Feature,
-                                     levels=as.character(varimp.rf.df.50kb$Feature))
-
-p.rf.50kb <- ggplot(varimp.rf.df.50kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(C)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="green") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/50kb/p.rf.50kb.png")
-```
+
+###None
+
+```{r}
+rfimpvars_gm12878_50kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/RF/rfimpvars.rds")
+rfimpvars_gm12878_50kb_none <- rfimpvars_gm12878_50kb_none[1:20,]
+
+rfimpvars_gm12878_50kb_none$Feature <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", rfimpvars_gm12878_50kb_none$Feature)
+
+rfimpvars_gm12878_50kb_none$Feature <- factor(rfimpvars_gm12878_50kb_none$Feature, levels=rfimpvars_gm12878_50kb_none$Feature)
+
+ggplot(rfimpvars_gm12878_50kb_none, aes(x=Feature, y=Importance)) +
+  geom_bar(stat="identity") +
+  theme_minimal()+
+  theme_bw()+
+  theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20))
+```
+
+###ROS
+
+###RUS
+
+###SMOTE
+
+###ROSE
+
 ##100kb
-###Random Under-Sampling
-```{r}
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/100kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf <- rf[order(rf$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf$Importance
-Labels <- as.character(rf$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.100kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.100kb$Feature <- as.character(varimp.rf.df.100kb$Feature)							 
-varimp.rf.df.100kb <-varimp.rf.df.100kb[order(varimp.rf.df.100kb$Importance),]
-#varimp.rf.df.100kb <- varimp.rf.df.100kb[(dim(varimp.rf.df.100kb)[1]-14):dim(varimp.rf.df.100kb)[1],]
-varimp.rf.df.100kb$Feature <- factor(varimp.rf.df.100kb$Feature,
-                                     levels=as.character(varimp.rf.df.100kb$Feature))
-
-p.rf.100kb <- ggplot(varimp.rf.df.100kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(D)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="orange") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/100kb/p.rf.100kb.png")
-
-allvarimps <- ggarrange(p.rf.5kb,p.rf.25kb,p.rf.50kb,p.rf.100kb, ncol=2, nrow=2)
-
-ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/allvarimps.png")
-```
+
+###None
+```{r}
+rfimpvars_gm12878_100kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/RF/rfimpvars.rds")
+rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[1:20,]
+
+rfimpvars_gm12878_100kb_none$Feature <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", rfimpvars_gm12878_100kb_none$Feature)
+
+rfimpvars_gm12878_100kb_none$Feature <- factor(rfimpvars_gm12878_100kb_none$Feature, levels=rfimpvars_gm12878_100kb_none$Feature)
+
+ggplot(rfimpvars_gm12878_100kb_none, aes(x=Feature, y=Importance)) +
+  geom_bar(stat="identity") +
+  theme_minimal()+
+  theme_bw()+
+  theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20))
+```
+
+###ROS
+
+###RUS
+
+###SMOTE
+
+###ROSE
 

### 2019-02-27 Manuscript/manuscript.Rmd
manuscript edits

@@
 The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries.
-Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries [@mourad2016computational; @hong2017computational; @huang2015predicting].
+Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries.
 Although several useful insights have been made, such as the convergent binding of CTCF [@ong2014ctcf; @ghirlando2016ctcf], many methods ignore key characteristics of domain data, such as the impact of heavily imbalanced number of boundaries vs.
@@
 Algorithmic level solutions involve modifyng existing classifiers in order to curtail the bias induced by imbalanced classes [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical].
-Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or remove data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
+Data level solutions, on the other hand, mostly constitute as resampling techniques, in which random sampling is used to either replicate or remove data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
 It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
@@
 
-The other aspect of TAD boundary modelling not considered by the current methods is the concept of genomic distance.
-The typical approaches for modeling the association between TAD boundaries and epigenomic elements include overlap counts or percents [???
-Do we have refs for this?; !!!should I repeat past used references here?].
+Another aspect of TAD boundary modelling not currently being explored are the various feature engineering methods used to build the feature space of models.
+Different techniques can be employed to measure the relationship between TAD boundaries and genomic annotations.
+Typical approaches for modeling the association between TAD boundaries and epigenomic elements include overlap counts or percents [@mourad2016computational; @hong2017computational; @huang2015predicting].
 Counts refer to the total number of instances where a genomic annotation overlaps with a genomic region of interest, while percents refers to the percent of overlap that occurred (usually in terms of base pairs).
@@
 However, these distance characteristics have the potential to offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
+Likewise, any direct comparisons of the different feature engineering techniques remain unresearched.
 
@@
 We then tested four different re-sampling techniques aimed at creating balanced classes.
-Noninformative features were removed using a variable reduction algorithm and random forest classifications were performed to assess model performance, and investigate which genomic annotations were most associated with the TAD boundaries for a given system from the complete ensemble.
+Noninformative features were removed using a feature reduction algorithm and random forest classifications were performed to assess model performance, and investigate which genomic annotations were most associated with the TAD boundaries for a given system from the complete ensemble.
 Model performance was evaluated using area under the precision-recall curve (AUPRC), F1-Score, Youden's index (YI), and Matthew's correlation coefficient (MCC).
@@
 1.
-**Overlap Counts (OC)**: For each genomic bin, the total number of instances where a bin overlapped with genomic annotation regions (features) was calculated.
+**Overlap Counts (OC)**: For each genomic bin, the total number of instances (bases) where a bin overlapped with genomic annotation regions (features) was calculated.
 In the case of no overlaps the value is set as 0.
@@
 
+<!--
 5.
@@
 The `ROSE` R package was used to perform ROSE (version 0.0.3).
-
-To determine the best predictor type we performed separate random forest models on each set of predictor types and evaluated the precision-recall curves, as well as the subsequent AUPRC.
-To confirm the optimality of the feature engineering, this was performed for each combination of re-sampling technique, resolution, and cell line.
+-->
 
@@
 
+A regularization technique using a combination of the $l_{1}$ and $l_{2}$ penalties, known as the elastic-net, was used to reduce the feature space.
+The elastic-net was chosen in order to suitably reduce the feature space while also maintaining the inclusion of multiple correlated predictors.
+For each elastic-net regularization, 10-fold cross-validation was used to tune the parameters that controlled the penalty terms.
+All elastic-net algorithms were implemented in R using the `caret` package version 6.0 [@kuhn2012caret].
+
+<!--
 Recursive feature elimination (RFE) was then used to determine the optimal number of features for models with the best performing predictor type.
@@
 Again, to confirm that results were consistent, the reduction process was repeated for each combination of re-sampling technique, resolution, and cell line.
+-->
 
@@
 Once the appropriate predictor type and set of features were determined, a final set of random forest classification models were performed to fully compare re-sampling techniques.
-To reduce bias due to random dataset generation, 10-fold cross validation was used.
-The default number of features to consider at each node of the random forest algorithm was set as the square root of the number of features in the model.
+To reduce bias due to random dataset generation, 10-fold cross validation was used <!--to tune the number of features to consider at each node and the number of ensemble trees to aggregate-->.The default number of features to consider at each node of the random forest algorithm was set as the square root of the number of features in the model.
 Likewise, the number of ensemble trees to aggregate was set at 500.
@@
 Letting |X| denote the cardinality of each set, we evaluated $|C| \times |R| \times |P| \times |B|$ different ensemble systems, totaling X (=$x \times 4 \times 3 \times 5$) separate models.
-For each model, we aimed to assess both performance and identify the genomic annotations that were most important in correctly labeling the genomic bins that overlapped with flanked TAD boundaries.
+For each model, we aimed to assess both model performance and identify the genomic annotations that were most important in correctly labeling the genomic bins that overlapped with flanked TAD boundaries.
 
-We first examined the class imbalance of the different data resolutions (Supplementary Table 5).
-[???
-What table?; !!!fixed] While the total number of genomic bins decreased as resolution increased, the imbalance ratios remained relatively stable.
-We found that there was an average imbalance ratio of 0.154 (SD=0.022) and 0.137 (SD=0.0181) across resolutions for cell lines GM12878 and K562 respectively.
-[???
-At which resolution?; !!!fixed] The low imbalance ratios indicate a wide disparity between majority and minority classes, and therefore suitable resampling techniques are needed.
+## IMBALANCE RATIOS REMAINED SEVERE AND CONSISTENT ACROSS RESOLUTIONS
 
+We first examined the class imbalance of the different data resolutions for each cell line (Supplementary Table 5).
+While the total number of genomic bins decreased as resolution increased, the imbalance ratios remained relatively stable.
+We found that there was an average imbalance ratio of 0.154 (SD=0.022) and 0.137 (SD=0.0181) across resolutions for the GM12878 and K562 cell lines respectively.
+The low imbalance ratios indicate a wide disparity between majority and minority classes, and therefore suitable resampling techniques were needed.
+
+## MANY GENOMIC ANNOTATIONS WERE HIGHLY CORRELATED
+
+When assessing the collinearity of the genomic annotations, it was found that the total number of bases that the number overlapped bases between genomic bins flanked by a TAD boundary were highly correlated between many genomic annotations ().
+That is, many genomic annotations tended to colocalize near eachother at the boarders of domains.
+This was present across both resolution and cell line.
+Specifically, we found that the CTCF, Rad21, Smc3ab, and Znf143 transcription factor binding sites were highly colocalized near TAD boundaries.
+Likewise, many histone modifications also tended to appear near TAD boundaries in conjunction with one another including H3K4me1, H3K4me2, H3K4me3, H3K9ac, and H3K27ac.
+Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly correlated with on another, yet inversely correlated with many transcription factor binding sites.
+The high correlations among many of the genomic annotations gives precedent for the use of an elastic-net regularization.
+
+<!--
 ## DISTANCE TYPE PREDICTORS OUTPERFORM OTHER PREDICTOR-TYPES
@@
 Therefore, the feature space was reduced for subsequent models to the top 32 predictors, respective to cell line, resolution, and resampling technique.
+-->
 

### 2019-02-27 Manuscript/Supplementary/supplementary_legends.Rmd
Results review
commented out legends
edditted legend

@@
 
-**Supplementary Table 4. Hi-C Data.** A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains and where they can be downloaded.
+**Supplementary Table 4. Hi-C Data.** A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains.
 
@@
 
-**Supplementary Figure 1-8. Distance Densities across cell lines and resolutions.**
-Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for GM12878 (left column) and K562 (right column) cell lines.
-The untransformed distances (red) are highly right skewed.
-After performing a $log_{2}$ tranformation (blue), the distances exhibited more normalized densities.
+**Supplementary Figure 1. Distance Densities across cell lines and resolutions.**
+Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for 10 kb (A), 25 kb (B), 50 kb (C), and 100 kb (D) data resolutions across the GM12878 (left column) and K562 (right column) cell lines.
+The untransformed distance densities are filled in red, while the $log_{2}$ tranformed distance densities are filled in blue.
 
@@
 
+<!--
 **Supplementary Figures 9-23.
@@
 GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red).
+-->
 
+<!--
 **Supplementary Table 2.
@@
 The column labeled "All" denotes models with all 3 combined predictor types.
+-->
 
+<!--
 **Figure 3.
@@
 Near optimal performance was achieved using the top 32 distance type predictors for both the GM12878 (red) and K562 cell lines (blue).
+-->

### 2019-02-27 Scripts/evaluating_dist_densities.Rmd
added script evaluating distance densities

--- 2019-02-05 Scripts/performances.rmd
@@
 ---
-title: "Performances Code"
+title: "Evaluating Distance Densities"
 output: html_document
@@
   guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("10 kb")+ 
+  #geom_vline(xintercept=0, size=1)+
+  #geom_hline(yintercept=0, size=1)+
+	xlab("") + 
+	xlim(0,25) + 
+	ylab("Density")+ 
   ylim(0,.8)+
-  ggtitle("GM12878") +
-  theme_minimal() +
+  #ggtitle("GM12878") +
+  theme_minimal() +
+  theme_bw()+
   theme(plot.title = element_text(hjust = 0.5))
@@
   guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("25 kb")+ 
+  #geom_vline(xintercept=0, size=1)+
+  #geom_hline(yintercept=0, size=1)+
+	xlab("") + 
+	xlim(0,25) + 
+	ylab("Density")+ 
   ylim(0,.8)+
@@
   theme_minimal() +
+  theme_bw()+
   theme(plot.title = element_text(hjust = 0.5))
@@
   guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("50 kb")+ 
+  #geom_vline(xintercept=0, size=1)+
+  #geom_hline(yintercept=0, size=1)+
+	xlab("") + 
+	xlim(0,25) + 
+	ylab("Density")+ 
   ylim(0,.8)+
@@
   guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("100 kb")+ 
+  #geom_vline(xintercept=0, size=1)+
+  #geom_hline(yintercept=0, size=1)+
+	xlab("") + 
+	xlim(0,25) + 
+	ylab("Density")+ 
   ylim(0,.8)+
@@
   guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	#ylab("10 kb")+ 
+  #geom_vline(xintercept=0, size=1)+
+  #geom_hline(yintercept=0, size=1)+
+	xlab("") + 
+	xlim(0,25) + 
+	ylab("Density")+ 
   ylim(0,.8)+
-  ggtitle("K562") +
-  theme_minimal() +
+  #ggtitle("GM12878") +
+  theme_minimal() +
+  theme_bw()+
   theme(plot.title = element_text(hjust = 0.5))
@@
   guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	#ylab("25 kb")+ 
+  #geom_vline(xintercept=0, size=1)+
+  #geom_hline(yintercept=0, size=1)+
+	xlab("") + 
+	xlim(0,25) + 
+	ylab("Density")+ 
   ylim(0,.8)+
-  #ggtitle("K562") +
-  theme_minimal() +
+  #ggtitle("GM12878") +
+  theme_minimal() +
+  theme_bw()+
   theme(plot.title = element_text(hjust = 0.5))
@@
   guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	#ylab("50 kb")+ 
+  #geom_vline(xintercept=0, size=1)+
+  #geom_hline(yintercept=0, size=1)+
+	xlab("") + 
+	xlim(0,25) + 
+	ylab("Density")+ 
   ylim(0,.8)+
-  #ggtitle("K562") +
-  theme_minimal() +
+  #ggtitle("GM12878") +
+  theme_minimal() +
+  theme_bw()+
   theme(plot.title = element_text(hjust = 0.5))
@@
   guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	#ylab("100 kb")+ 
+  #geom_vline(xintercept=0, size=1)+
+  #geom_hline(yintercept=0, size=1)+
+	xlab("") + 
+	xlim(0,25) + 
+	ylab("Density")+ 
   ylim(0,.8)+
-  #ggtitle("K562") +
-  theme_minimal() +
+  #ggtitle("GM12878") +
+  theme_minimal() +
+  theme_bw()+
   theme(plot.title = element_text(hjust = 0.5))
@@
           #labels = c("A","", "B","", "C","", "D",""),
-          legend = "top",
+          legend = "bottom",
           common.legend = TRUE)
@@
 ```
-
-#Evaluating Imbalance Ratios
-##GM12878
-###10kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x10 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p10kb <- ggplot(x10, aes(y=IR, x=factor(CB, levels = unique(x10$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
-
-```
-
-###25kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x25 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p25kb <- ggplot(x25, aes(y=IR, x=factor(CB, levels = unique(x25$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
-
-```
-
-###50kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x50 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p50kb <- ggplot(x50, aes(y=IR, x=factor(CB, levels = unique(x50$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
-
-```
-
-###100kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x100 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p100kb <- ggplot(x100, aes(y=IR, x=factor(CB, levels = unique(x100$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
-
-```
-
-##K562
-###10kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x10_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p10kb_k562 <- ggplot(x10_k562, aes(y=IR, x=factor(CB, levels = unique(x10_k562$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
-
-```
-
-###25kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x25_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p25kb_k562 <- ggplot(x25_k562, aes(y=IR, x=factor(CB, levels = unique(x25_k562$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
-
-```
-
-###50kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x50_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p50kb_k562 <- ggplot(x50_k562, aes(y=IR, x=factor(CB, levels = unique(x50_k562$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
-
-```
-
-###100kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x100_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p100kb_k562 <- ggplot(x100_k562, aes(y=IR, x=factor(CB, levels = unique(x100_k562$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
-
-```
-
-##Combined
-```{r}
-
-IR=c(x10$IR[x10$CB=="Complete"],
-                              x25$IR[x25$CB=="Complete"],
-                              x50$IR[x50$CB=="Complete"],
-                              x100$IR[x100$CB=="Complete"],
-                              x10_k562$IR[x10_k562$CB=="Complete"], 
-                              x25_k562$IR[x25_k562$CB=="Complete"],
-                              x50_k562$IR[x50_k562$CB=="Complete"],
-                              x100_k562$IR[x100_k562$CB=="Complete"])
-CL <- c(rep("GM12878", 4), 
-                  rep("K562", 4))
-Resolution <- c(rep(c("10 kb", "25 kb", "50 kb", "100 kb"), 2))
-
-allirdata <- cbind.data.frame(IR, CL, Resolution)
-allirdata$CL <- factor(allirdata$CL, levels=c("GM12878", "K562"))
-allirdata$Resolution <- factor(allirdata$Resolution, c("10 kb", "25 kb", "50 kb", "100 kb"))
-
-allirplots <- ggplot(allirdata, aes(x = Resolution, y = IR,fill = CL)) + 
-  geom_bar(position = "dodge", stat="identity") + 
-  ylab("Imbalance Ratio") +
-  xlab("Resolution") +
-  #scale_fill_manual(name="Cell Line", values=c("red", "blue"))+
-  labs(fill="Cell Line")+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=10),
-        axis.text.y = element_text(size = 10),
-        axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-#Evaluating Feature Engineering
-
-## PR Curves
-
-###GM12878
-
-####10kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####25kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####50kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####100kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-###K562
-
-####10kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####25kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####50kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####100kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-###Combined
-
-```{r}
-#10kb
-##None
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_None_10kb <- rbind.data.frame(prall_None$curve,
-                                prdist_None$curve,
-                                prop_None$curve,
-                                proc_None$curve,
-                                prall_None_k562$curve,
-                                prdist_None_k562$curve,
-                                prop_None_k562$curve,
-                                proc_None_k562$curve)
-names(prdata_None_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_None_10kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
-                           rep("Distance", dim(prdist_None$curve)[1]),
-                           rep("OP", dim(prop_None$curve)[1]),
-                           rep("OC", dim(proc_None$curve)[1]),
-                           rep("All", dim(prall_None_k562$curve)[1]),
-                           rep("Distance", dim(prdist_None_k562$curve)[1]),
-                           rep("OP", dim(prop_None_k562$curve)[1]),
-                           rep("OC", dim(proc_None_k562$curve)[1]))
-prdata_None_10kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
-                                      dim(prdist_None$curve)[1]+
-                                      dim(prop_None$curve)[1]+
-                                      dim(proc_None$curve)[1])),
-                    rep("K562", (dim(prall_None_k562$curve)[1]+
-                                      dim(prdist_None_k562$curve)[1]+
-                                      dim(prop_None_k562$curve)[1]+
-                                      dim(proc_None_k562$curve)[1])))
-prdata_None_10kb$Predictor <- factor(prdata_None_10kb$Predictor)
-prdata_None_10kb$CL <- factor(prdata_None_10kb$CL)
-
-prplot_None_10kb <- ggplot(prdata_None_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##RUS
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prdata_RUS_10kb <- rbind.data.frame(prall_RUS$curve,
-                                prdist_RUS$curve,
-                                prop_RUS$curve,
-                                proc_RUS$curve,
-                                prall_RUS_k562$curve,
-                                prdist_RUS_k562$curve,
-                                prop_RUS_k562$curve,
-                                proc_RUS_k562$curve)
-names(prdata_RUS_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_RUS_10kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
-                           rep("Distance", dim(prdist_RUS$curve)[1]),
-                           rep("OP", dim(prop_RUS$curve)[1]),
-                           rep("OC", dim(proc_RUS$curve)[1]),
-                           rep("All", dim(prall_RUS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
-                           rep("OP", dim(prop_RUS_k562$curve)[1]),
-                           rep("OC", dim(proc_RUS_k562$curve)[1]))
-prdata_RUS_10kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
-                                      dim(prdist_RUS$curve)[1]+
-                                      dim(prop_RUS$curve)[1]+
-                                      dim(proc_RUS$curve)[1])),
-                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
-                                      dim(prdist_RUS_k562$curve)[1]+
-                                      dim(prop_RUS_k562$curve)[1]+
-                                      dim(proc_RUS_k562$curve)[1])))
-prdata_RUS_10kb$Predictor <- factor(prdata_RUS_10kb$Predictor)
-prdata_RUS_10kb$CL <- factor(prdata_RUS_10kb$CL)
-
-prplot_RUS_10kb <- ggplot(prdata_RUS_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROS
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prdata_ROS_10kb <- rbind.data.frame(prall_ROS$curve,
-                                prdist_ROS$curve,
-                                prop_ROS$curve,
-                                proc_ROS$curve,
-                                prall_ROS_k562$curve,
-                                prdist_ROS_k562$curve,
-                                prop_ROS_k562$curve,
-                                proc_ROS_k562$curve)
-names(prdata_ROS_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROS_10kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
-                           rep("Distance", dim(prdist_ROS$curve)[1]),
-                           rep("OP", dim(prop_ROS$curve)[1]),
-                           rep("OC", dim(proc_ROS$curve)[1]),
-                           rep("All", dim(prall_ROS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
-                           rep("OP", dim(prop_ROS_k562$curve)[1]),
-                           rep("OC", dim(proc_ROS_k562$curve)[1]))
-prdata_ROS_10kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
-                                      dim(prdist_ROS$curve)[1]+
-                                      dim(prop_ROS$curve)[1]+
-                                      dim(proc_ROS$curve)[1])),
-                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
-                                      dim(prdist_ROS_k562$curve)[1]+
-                                      dim(prop_ROS_k562$curve)[1]+
-                                      dim(proc_ROS_k562$curve)[1])))
-prdata_ROS_10kb$Predictor <- factor(prdata_ROS_10kb$Predictor)
-prdata_ROS_10kb$CL <- factor(prdata_ROS_10kb$CL)
-
-prplot_ROS_10kb <- ggplot(prdata_ROS_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##SMOTE
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prdata_SMOTE_10kb <- rbind.data.frame(prall_SMOTE$curve,
-                                prdist_SMOTE$curve,
-                                prop_SMOTE$curve,
-                                proc_SMOTE$curve,
-                                prall_SMOTE_k562$curve,
-                                prdist_SMOTE_k562$curve,
-                                prop_SMOTE_k562$curve,
-                                proc_SMOTE_k562$curve)
-names(prdata_SMOTE_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_SMOTE_10kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
-                           rep("OP", dim(prop_SMOTE$curve)[1]),
-                           rep("OC", dim(proc_SMOTE$curve)[1]),
-                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
-                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
-                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
-prdata_SMOTE_10kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
-                                      dim(prdist_SMOTE$curve)[1]+
-                                      dim(prop_SMOTE$curve)[1]+
-                                      dim(proc_SMOTE$curve)[1])),
-                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
-                                      dim(prdist_SMOTE_k562$curve)[1]+
-                                      dim(prop_SMOTE_k562$curve)[1]+
-                                      dim(proc_SMOTE_k562$curve)[1])))
-prdata_SMOTE_10kb$Predictor <- factor(prdata_SMOTE_10kb$Predictor)
-prdata_SMOTE_10kb$CL <- factor(prdata_SMOTE_10kb$CL)
-
-prplot_SMOTE_10kb <- ggplot(prdata_SMOTE_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROSE
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prdata_ROSE_10kb <- rbind.data.frame(prall_ROSE$curve,
-                                prdist_ROSE$curve,
-                                prop_ROSE$curve,
-                                proc_ROSE$curve,
-                                prall_ROSE_k562$curve,
-                                prdist_ROSE_k562$curve,
-                                prop_ROSE_k562$curve,
-                                proc_ROSE_k562$curve)
-names(prdata_ROSE_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROSE_10kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE$curve)[1]),
-                           rep("OP", dim(prop_ROSE$curve)[1]),
-                           rep("OC", dim(proc_ROSE$curve)[1]),
-                           rep("All", dim(prall_ROSE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
-                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
-                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
-prdata_ROSE_10kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
-                                      dim(prdist_ROSE$curve)[1]+
-                                      dim(prop_ROSE$curve)[1]+
-                                      dim(proc_ROSE$curve)[1])),
-                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
-                                      dim(prdist_ROSE_k562$curve)[1]+
-                                      dim(prop_ROSE_k562$curve)[1]+
-                                      dim(proc_ROSE_k562$curve)[1])))
-prdata_ROSE_10kb$Predictor <- factor(prdata_ROSE_10kb$Predictor)
-prdata_ROSE_10kb$CL <- factor(prdata_ROSE_10kb$CL)
-
-prplot_ROSE_10kb <- ggplot(prdata_ROSE_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##Collecting 10kb plots
-ggarrange(prplot_None_10kb,
-          prplot_RUS_10kb,
-          prplot_ROS_10kb,
-          prplot_SMOTE_10kb,
-          prplot_ROSE_10kb,
-          nrow=3,ncol=2,
-          common.legend = TRUE, legend = "right")
-
-#######################################################################################
-
-#25kb
-##None
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_None_25kb <- rbind.data.frame(prall_None$curve,
-                                prdist_None$curve,
-                                prop_None$curve,
-                                proc_None$curve,
-                                prall_None_k562$curve,
-                                prdist_None_k562$curve,
-                                prop_None_k562$curve,
-                                proc_None_k562$curve)
-names(prdata_None_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_None_25kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
-                           rep("Distance", dim(prdist_None$curve)[1]),
-                           rep("OP", dim(prop_None$curve)[1]),
-                           rep("OC", dim(proc_None$curve)[1]),
-                           rep("All", dim(prall_None_k562$curve)[1]),
-                           rep("Distance", dim(prdist_None_k562$curve)[1]),
-                           rep("OP", dim(prop_None_k562$curve)[1]),
-                           rep("OC", dim(proc_None_k562$curve)[1]))
-prdata_None_25kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
-                                      dim(prdist_None$curve)[1]+
-                                      dim(prop_None$curve)[1]+
-                                      dim(proc_None$curve)[1])),
-                    rep("K562", (dim(prall_None_k562$curve)[1]+
-                                      dim(prdist_None_k562$curve)[1]+
-                                      dim(prop_None_k562$curve)[1]+
-                                      dim(proc_None_k562$curve)[1])))
-prdata_None_25kb$Predictor <- factor(prdata_None_25kb$Predictor)
-prdata_None_25kb$CL <- factor(prdata_None_25kb$CL)
-
-prplot_None_25kb <- ggplot(prdata_None_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##RUS
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prdata_RUS_25kb <- rbind.data.frame(prall_RUS$curve,
-                                prdist_RUS$curve,
-                                prop_RUS$curve,
-                                proc_RUS$curve,
-                                prall_RUS_k562$curve,
-                                prdist_RUS_k562$curve,
-                                prop_RUS_k562$curve,
-                                proc_RUS_k562$curve)
-names(prdata_RUS_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_RUS_25kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
-                           rep("Distance", dim(prdist_RUS$curve)[1]),
-                           rep("OP", dim(prop_RUS$curve)[1]),
-                           rep("OC", dim(proc_RUS$curve)[1]),
-                           rep("All", dim(prall_RUS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
-                           rep("OP", dim(prop_RUS_k562$curve)[1]),
-                           rep("OC", dim(proc_RUS_k562$curve)[1]))
-prdata_RUS_25kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
-                                      dim(prdist_RUS$curve)[1]+
-                                      dim(prop_RUS$curve)[1]+
-                                      dim(proc_RUS$curve)[1])),
-                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
-                                      dim(prdist_RUS_k562$curve)[1]+
-                                      dim(prop_RUS_k562$curve)[1]+
-                                      dim(proc_RUS_k562$curve)[1])))
-prdata_RUS_25kb$Predictor <- factor(prdata_RUS_25kb$Predictor)
-prdata_RUS_25kb$CL <- factor(prdata_RUS_25kb$CL)
-
-prplot_RUS_25kb <- ggplot(prdata_RUS_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROS
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prdata_ROS_25kb <- rbind.data.frame(prall_ROS$curve,
-                                prdist_ROS$curve,
-                                prop_ROS$curve,
-                                proc_ROS$curve,
-                                prall_ROS_k562$curve,
-                                prdist_ROS_k562$curve,
-                                prop_ROS_k562$curve,
-                                proc_ROS_k562$curve)
-names(prdata_ROS_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROS_25kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
-                           rep("Distance", dim(prdist_ROS$curve)[1]),
-                           rep("OP", dim(prop_ROS$curve)[1]),
-                           rep("OC", dim(proc_ROS$curve)[1]),
-                           rep("All", dim(prall_ROS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
-                           rep("OP", dim(prop_ROS_k562$curve)[1]),
-                           rep("OC", dim(proc_ROS_k562$curve)[1]))
-prdata_ROS_25kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
-                                      dim(prdist_ROS$curve)[1]+
-                                      dim(prop_ROS$curve)[1]+
-                                      dim(proc_ROS$curve)[1])),
-                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
-                                      dim(prdist_ROS_k562$curve)[1]+
-                                      dim(prop_ROS_k562$curve)[1]+
-                                      dim(proc_ROS_k562$curve)[1])))
-prdata_ROS_25kb$Predictor <- factor(prdata_ROS_25kb$Predictor)
-prdata_ROS_25kb$CL <- factor(prdata_ROS_25kb$CL)
-
-prplot_ROS_25kb <- ggplot(prdata_ROS_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##SMOTE
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prdata_SMOTE_25kb <- rbind.data.frame(prall_SMOTE$curve,
-                                prdist_SMOTE$curve,
-                                prop_SMOTE$curve,
-                                proc_SMOTE$curve,
-                                prall_SMOTE_k562$curve,
-                                prdist_SMOTE_k562$curve,
-                                prop_SMOTE_k562$curve,
-                                proc_SMOTE_k562$curve)
-names(prdata_SMOTE_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_SMOTE_25kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
-                           rep("OP", dim(prop_SMOTE$curve)[1]),
-                           rep("OC", dim(proc_SMOTE$curve)[1]),
-                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
-                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
-                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
-prdata_SMOTE_25kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
-                                      dim(prdist_SMOTE$curve)[1]+
-                                      dim(prop_SMOTE$curve)[1]+
-                                      dim(proc_SMOTE$curve)[1])),
-                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
-                                      dim(prdist_SMOTE_k562$curve)[1]+
-                                      dim(prop_SMOTE_k562$curve)[1]+
-                                      dim(proc_SMOTE_k562$curve)[1])))
-prdata_SMOTE_25kb$Predictor <- factor(prdata_SMOTE_25kb$Predictor)
-prdata_SMOTE_25kb$CL <- factor(prdata_SMOTE_25kb$CL)
-
-prplot_SMOTE_25kb <- ggplot(prdata_SMOTE_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROSE
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prdata_ROSE_25kb <- rbind.data.frame(prall_ROSE$curve,
-                                prdist_ROSE$curve,
-                                prop_ROSE$curve,
-                                proc_ROSE$curve,
-                                prall_ROSE_k562$curve,
-                                prdist_ROSE_k562$curve,
-                                prop_ROSE_k562$curve,
-                                proc_ROSE_k562$curve)
-names(prdata_ROSE_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROSE_25kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE$curve)[1]),
-                           rep("OP", dim(prop_ROSE$curve)[1]),
-                           rep("OC", dim(proc_ROSE$curve)[1]),
-                           rep("All", dim(prall_ROSE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
-                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
-                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
-prdata_ROSE_25kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
-                                      dim(prdist_ROSE$curve)[1]+
-                                      dim(prop_ROSE$curve)[1]+
-                                      dim(proc_ROSE$curve)[1])),
-                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
-                                      dim(prdist_ROSE_k562$curve)[1]+
-                                      dim(prop_ROSE_k562$curve)[1]+
-                                      dim(proc_ROSE_k562$curve)[1])))
-prdata_ROSE_25kb$Predictor <- factor(prdata_ROSE_25kb$Predictor)
-prdata_ROSE_25kb$CL <- factor(prdata_ROSE_25kb$CL)
-
-prplot_ROSE_25kb <- ggplot(prdata_ROSE_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-###############################################################################
-
-#50kb
-##None
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_None_50kb <- rbind.data.frame(prall_None$curve,
-                                prdist_None$curve,
-                                prop_None$curve,
-                                proc_None$curve,
-                                prall_None_k562$curve,
-                                prdist_None_k562$curve,
-                                prop_None_k562$curve,
-                                proc_None_k562$curve)
-names(prdata_None_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_None_50kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
-                           rep("Distance", dim(prdist_None$curve)[1]),
-                           rep("OP", dim(prop_None$curve)[1]),
-                           rep("OC", dim(proc_None$curve)[1]),
-                           rep("All", dim(prall_None_k562$curve)[1]),
-                           rep("Distance", dim(prdist_None_k562$curve)[1]),
-                           rep("OP", dim(prop_None_k562$curve)[1]),
-                           rep("OC", dim(proc_None_k562$curve)[1]))
-prdata_None_50kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
-                                      dim(prdist_None$curve)[1]+
-                                      dim(prop_None$curve)[1]+
-                                      dim(proc_None$curve)[1])),
-                    rep("K562", (dim(prall_None_k562$curve)[1]+
-                                      dim(prdist_None_k562$curve)[1]+
-                                      dim(prop_None_k562$curve)[1]+
-                                      dim(proc_None_k562$curve)[1])))
-prdata_None_50kb$Predictor <- factor(prdata_None_50kb$Predictor)
-prdata_None_50kb$CL <- factor(prdata_None_50kb$CL)
-
-prplot_None_50kb <- ggplot(prdata_None_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##RUS
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prdata_RUS_50kb <- rbind.data.frame(prall_RUS$curve,
-                                prdist_RUS$curve,
-                                prop_RUS$curve,
-                                proc_RUS$curve,
-                                prall_RUS_k562$curve,
-                                prdist_RUS_k562$curve,
-                                prop_RUS_k562$curve,
-                                proc_RUS_k562$curve)
-names(prdata_RUS_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_RUS_50kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
-                           rep("Distance", dim(prdist_RUS$curve)[1]),
-                           rep("OP", dim(prop_RUS$curve)[1]),
-                           rep("OC", dim(proc_RUS$curve)[1]),
-                           rep("All", dim(prall_RUS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
-                           rep("OP", dim(prop_RUS_k562$curve)[1]),
-                           rep("OC", dim(proc_RUS_k562$curve)[1]))
-prdata_RUS_50kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
-                                      dim(prdist_RUS$curve)[1]+
-                                      dim(prop_RUS$curve)[1]+
-                                      dim(proc_RUS$curve)[1])),
-                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
-                                      dim(prdist_RUS_k562$curve)[1]+
-                                      dim(prop_RUS_k562$curve)[1]+
-                                      dim(proc_RUS_k562$curve)[1])))
-prdata_RUS_50kb$Predictor <- factor(prdata_RUS_50kb$Predictor)
-prdata_RUS_50kb$CL <- factor(prdata_RUS_50kb$CL)
-
-prplot_RUS_50kb <- ggplot(prdata_RUS_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROS
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prdata_ROS_50kb <- rbind.data.frame(prall_ROS$curve,
-                                prdist_ROS$curve,
-                                prop_ROS$curve,
-                                proc_ROS$curve,
-                                prall_ROS_k562$curve,
-                                prdist_ROS_k562$curve,
-                                prop_ROS_k562$curve,
-                                proc_ROS_k562$curve)
-names(prdata_ROS_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROS_50kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
-                           rep("Distance", dim(prdist_ROS$curve)[1]),
-                           rep("OP", dim(prop_ROS$curve)[1]),
-                           rep("OC", dim(proc_ROS$curve)[1]),
-                           rep("All", dim(prall_ROS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
-                           rep("OP", dim(prop_ROS_k562$curve)[1]),
-                           rep("OC", dim(proc_ROS_k562$curve)[1]))
-prdata_ROS_50kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
-                                      dim(prdist_ROS$curve)[1]+
-                                      dim(prop_ROS$curve)[1]+
-                                      dim(proc_ROS$curve)[1])),
-                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
-                                      dim(prdist_ROS_k562$curve)[1]+
-                                      dim(prop_ROS_k562$curve)[1]+
-                                      dim(proc_ROS_k562$curve)[1])))
-prdata_ROS_50kb$Predictor <- factor(prdata_ROS_50kb$Predictor)
-prdata_ROS_50kb$CL <- factor(prdata_ROS_50kb$CL)
-
-prplot_ROS_50kb <- ggplot(prdata_ROS_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##SMOTE
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prdata_SMOTE_50kb <- rbind.data.frame(prall_SMOTE$curve,
-                                prdist_SMOTE$curve,
-                                prop_SMOTE$curve,
-                                proc_SMOTE$curve,
-                                prall_SMOTE_k562$curve,
-                                prdist_SMOTE_k562$curve,
-                                prop_SMOTE_k562$curve,
-                                proc_SMOTE_k562$curve)
-names(prdata_SMOTE_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_SMOTE_50kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
-                           rep("OP", dim(prop_SMOTE$curve)[1]),
-                           rep("OC", dim(proc_SMOTE$curve)[1]),
-                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
-                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
-                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
-prdata_SMOTE_50kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
-                                      dim(prdist_SMOTE$curve)[1]+
-                                      dim(prop_SMOTE$curve)[1]+
-                                      dim(proc_SMOTE$curve)[1])),
-                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
-                                      dim(prdist_SMOTE_k562$curve)[1]+
-                                      dim(prop_SMOTE_k562$curve)[1]+
-                                      dim(proc_SMOTE_k562$curve)[1])))
-prdata_SMOTE_50kb$Predictor <- factor(prdata_SMOTE_50kb$Predictor)
-prdata_SMOTE_50kb$CL <- factor(prdata_SMOTE_50kb$CL)
-
-prplot_SMOTE_50kb <- ggplot(prdata_SMOTE_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROSE
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prdata_ROSE_50kb <- rbind.data.frame(prall_ROSE$curve,
-                                prdist_ROSE$curve,
-                                prop_ROSE$curve,
-                                proc_ROSE$curve,
-                                prall_ROSE_k562$curve,
-                                prdist_ROSE_k562$curve,
-                                prop_ROSE_k562$curve,
-                                proc_ROSE_k562$curve)
-names(prdata_ROSE_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROSE_50kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE$curve)[1]),
-                           rep("OP", dim(prop_ROSE$curve)[1]),
-                           rep("OC", dim(proc_ROSE$curve)[1]),
-                           rep("All", dim(prall_ROSE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
-                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
-                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
-prdata_ROSE_50kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
-                                      dim(prdist_ROSE$curve)[1]+
-                                      dim(prop_ROSE$curve)[1]+
-                                      dim(proc_ROSE$curve)[1])),
-                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
-                                      dim(prdist_ROSE_k562$curve)[1]+
-                                      dim(prop_ROSE_k562$curve)[1]+
-                                      dim(proc_ROSE_k562$curve)[1])))
-prdata_ROSE_50kb$Predictor <- factor(prdata_ROSE_50kb$Predictor)
-prdata_ROSE_50kb$CL <- factor(prdata_ROSE_50kb$CL)
-
-prplot_ROSE_50kb <- ggplot(prdata_ROSE_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-###########################################################################
-
-#100kb
-##None
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_None_100kb <- rbind.data.frame(prall_None$curve,
-                                prdist_None$curve,
-                                prop_None$curve,
-                                proc_None$curve,
-                                prall_None_k562$curve,
-                                prdist_None_k562$curve,
-                                prop_None_k562$curve,
-                                proc_None_k562$curve)
-names(prdata_None_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_None_100kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
-                           rep("Distance", dim(prdist_None$curve)[1]),
-                           rep("OP", dim(prop_None$curve)[1]),
-                           rep("OC", dim(proc_None$curve)[1]),
-                           rep("All", dim(prall_None_k562$curve)[1]),
-                           rep("Distance", dim(prdist_None_k562$curve)[1]),
-                           rep("OP", dim(prop_None_k562$curve)[1]),
-                           rep("OC", dim(proc_None_k562$curve)[1]))
-prdata_None_100kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
-                                      dim(prdist_None$curve)[1]+
-                                      dim(prop_None$curve)[1]+
-                                      dim(proc_None$curve)[1])),
-                    rep("K562", (dim(prall_None_k562$curve)[1]+
-                                      dim(prdist_None_k562$curve)[1]+
-                                      dim(prop_None_k562$curve)[1]+
-                                      dim(proc_None_k562$curve)[1])))
-prdata_None_100kb$Predictor <- factor(prdata_None_100kb$Predictor)
-prdata_None_100kb$CL <- factor(prdata_None_100kb$CL)
-
-prplot_None_100kb <- ggplot(prdata_None_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##RUS
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prdata_RUS_100kb <- rbind.data.frame(prall_RUS$curve,
-                                prdist_RUS$curve,
-                                prop_RUS$curve,
-                                proc_RUS$curve,
-                                prall_RUS_k562$curve,
-                                prdist_RUS_k562$curve,
-                                prop_RUS_k562$curve,
-                                proc_RUS_k562$curve)
-names(prdata_RUS_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_RUS_100kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
-                           rep("Distance", dim(prdist_RUS$curve)[1]),
-                           rep("OP", dim(prop_RUS$curve)[1]),
-                           rep("OC", dim(proc_RUS$curve)[1]),
-                           rep("All", dim(prall_RUS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
-                           rep("OP", dim(prop_RUS_k562$curve)[1]),
-                           rep("OC", dim(proc_RUS_k562$curve)[1]))
-prdata_RUS_100kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
-                                      dim(prdist_RUS$curve)[1]+
-                                      dim(prop_RUS$curve)[1]+
-                                      dim(proc_RUS$curve)[1])),
-                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
-                                      dim(prdist_RUS_k562$curve)[1]+
-                                      dim(prop_RUS_k562$curve)[1]+
-                                      dim(proc_RUS_k562$curve)[1])))
-prdata_RUS_100kb$Predictor <- factor(prdata_RUS_100kb$Predictor)
-prdata_RUS_100kb$CL <- factor(prdata_RUS_100kb$CL)
-
-prplot_RUS_100kb <- ggplot(prdata_RUS_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROS
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prdata_ROS_100kb <- rbind.data.frame(prall_ROS$curve,
-                                prdist_ROS$curve,
-                                prop_ROS$curve,
-                                proc_ROS$curve,
-                                prall_ROS_k562$curve,
-                                prdist_ROS_k562$curve,
-                                prop_ROS_k562$curve,
-                                proc_ROS_k562$curve)
-names(prdata_ROS_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROS_100kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
-                           rep("Distance", dim(prdist_ROS$curve)[1]),
-                           rep("OP", dim(prop_ROS$curve)[1]),
-                           rep("OC", dim(proc_ROS$curve)[1]),
-                           rep("All", dim(prall_ROS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
-                           rep("OP", dim(prop_ROS_k562$curve)[1]),
-                           rep("OC", dim(proc_ROS_k562$curve)[1]))
-prdata_ROS_100kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
-                                      dim(prdist_ROS$curve)[1]+
-                                      dim(prop_ROS$curve)[1]+
-                                      dim(proc_ROS$curve)[1])),
-                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
-                                      dim(prdist_ROS_k562$curve)[1]+
-                                      dim(prop_ROS_k562$curve)[1]+
-                                      dim(proc_ROS_k562$curve)[1])))
-prdata_ROS_100kb$Predictor <- factor(prdata_ROS_100kb$Predictor)
-prdata_ROS_100kb$CL <- factor(prdata_ROS_100kb$CL)
-
-prplot_ROS_100kb <- ggplot(prdata_ROS_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##SMOTE
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prdata_SMOTE_100kb <- rbind.data.frame(prall_SMOTE$curve,
-                                prdist_SMOTE$curve,
-                                prop_SMOTE$curve,
-                                proc_SMOTE$curve,
-                                prall_SMOTE_k562$curve,
-                                prdist_SMOTE_k562$curve,
-                                prop_SMOTE_k562$curve,
-                                proc_SMOTE_k562$curve)
-names(prdata_SMOTE_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_SMOTE_100kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
-                           rep("OP", dim(prop_SMOTE$curve)[1]),
-                           rep("OC", dim(proc_SMOTE$curve)[1]),
-                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
-                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
-                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
-prdata_SMOTE_100kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
-                                      dim(prdist_SMOTE$curve)[1]+
-                                      dim(prop_SMOTE$curve)[1]+
-                                      dim(proc_SMOTE$curve)[1])),
-                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
-                                      dim(prdist_SMOTE_k562$curve)[1]+
-                                      dim(prop_SMOTE_k562$curve)[1]+
-                                      dim(proc_SMOTE_k562$curve)[1])))
-prdata_SMOTE_100kb$Predictor <- factor(prdata_SMOTE_100kb$Predictor)
-prdata_SMOTE_100kb$CL <- factor(prdata_SMOTE_100kb$CL)
-
-prplot_SMOTE_100kb <- ggplot(prdata_SMOTE_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROSE
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prdata_ROSE_100kb <- rbind.data.frame(prall_ROSE$curve,
-                                prdist_ROSE$curve,
-                                prop_ROSE$curve,
-                                proc_ROSE$curve,
-                                prall_ROSE_k562$curve,
-                                prdist_ROSE_k562$curve,
-                                prop_ROSE_k562$curve,
-                                proc_ROSE_k562$curve)
-names(prdata_ROSE_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROSE_100kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE$curve)[1]),
-                           rep("OP", dim(prop_ROSE$curve)[1]),
-                           rep("OC", dim(proc_ROSE$curve)[1]),
-                           rep("All", dim(prall_ROSE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
-                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
-                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
-prdata_ROSE_100kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
-                                      dim(prdist_ROSE$curve)[1]+
-                                      dim(prop_ROSE$curve)[1]+
-                                      dim(proc_ROSE$curve)[1])),
-                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
-                                      dim(prdist_ROSE_k562$curve)[1]+
-                                      dim(prop_ROSE_k562$curve)[1]+
-                                      dim(proc_ROSE_k562$curve)[1])))
-prdata_ROSE_100kb$Predictor <- factor(prdata_ROSE_100kb$Predictor)
-prdata_ROSE_100kb$CL <- factor(prdata_ROSE_100kb$CL)
-
-prplot_ROSE_100kb <- ggplot(prdata_ROSE_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-###############################################################
-
-##Collecting 25kb, 50kb, and 100kb plots
-
-ggarrange(prplot_None_25kb, prplot_None_50kb, prplot_None_100kb,
-          prplot_RUS_25kb, prplot_RUS_50kb, prplot_RUS_100kb,
-          prplot_ROS_25kb, prplot_ROS_50kb, prplot_ROS_100kb,
-          prplot_SMOTE_25kb, prplot_SMOTE_50kb, prplot_SMOTE_100kb,
-          prplot_ROSE_25kb, prplot_ROSE_50kb, prplot_ROSE_100kb,
-          ncol=3,
-          nrow=5,
-          common.legend = TRUE,
-          legend = "right")
-```
-
-##Tables of AUPRC
-
-```{r}
-
-gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-K562_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-K562_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-K562_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-K562_10kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-K562_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-K562_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-K562_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-K562_25kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-K562_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-K562_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-K562_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-K562_50kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-K562_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-K562_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-K562_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-K562_100kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-gm12878_10kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-gm12878_25kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-gm12878_50kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-gm12878_100kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-K562_10kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-K562_10kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-K562_10kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-K562_10kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-K562_10kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-K562_25kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-K562_25kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-K562_25kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-K562_25kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-K562_25kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-K562_50kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-K562_50kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-K562_50kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-K562_50kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-K562_50kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-K562_100kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-K562_100kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-K562_100kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-K562_100kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-K562_100kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-gm12878_10kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-gm12878_25kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-gm12878_50kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-gm12878_100kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-K562_10kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-K562_10kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-K562_10kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-K562_10kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-K562_10kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-K562_25kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-K562_25kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-K562_25kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-K562_25kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-K562_25kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-K562_50kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-K562_50kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-K562_50kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-K562_50kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-K562_50kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-K562_100kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-K562_100kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-K562_100kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-K562_100kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-K562_100kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-gm12878_10kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-gm12878_25kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-gm12878_50kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-gm12878_100kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-K562_10kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-K562_10kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-K562_10kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-K562_10kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-K562_10kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-K562_25kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-K562_25kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-K562_25kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-K562_25kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-K562_25kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-K562_50kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-K562_50kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-K562_50kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-K562_50kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-K562_50kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-K562_100kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-K562_100kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-K562_100kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-K562_100kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-K562_100kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-prcurvetable <- data.frame(CL=c(rep("GM12878", 20), rep("K562", 20)),
-                           Resolution=c(c(rep("10 kb", 5), 
-                                        rep("25 kb", 5),
-                                        rep("50 kb", 5),
-                                        rep("100 kb", 5)),
-                                        c(rep("10 kb", 5), 
-                                        rep("25 kb", 5),
-                                        rep("50 kb", 5),
-                                        rep("100 kb", 5))),
-                           ReSampling=rep(c("None",
-                                        "RUS",
-                                        "ROS",
-                                        "SMOTE",
-                                        "ROSE"),8))
-prcurvetable$OC <- c(gm12878_10kb_none_oc,
-gm12878_10kb_rus_oc,
-gm12878_10kb_ros_oc,
-gm12878_10kb_smote_oc,
-gm12878_10kb_rose_oc,
-gm12878_25kb_none_oc,
-gm12878_25kb_rus_oc,
-gm12878_25kb_ros_oc,
-gm12878_25kb_smote_oc,
-gm12878_25kb_rose_oc,
-gm12878_50kb_none_oc,
-gm12878_50kb_rus_oc,
-gm12878_50kb_ros_oc,
-gm12878_50kb_smote_oc,
-gm12878_50kb_rose_oc,
-gm12878_100kb_none_oc,
-gm12878_100kb_rus_oc,
-gm12878_100kb_ros_oc,
-gm12878_100kb_smote_oc,
-gm12878_100kb_rose_oc,
-K562_10kb_none_oc,
-K562_10kb_rus_oc,
-K562_10kb_ros_oc,
-K562_10kb_smote_oc,
-K562_10kb_rose_oc,
-K562_25kb_none_oc,
-K562_25kb_rus_oc,
-K562_25kb_ros_oc,
-K562_25kb_smote_oc,
-K562_25kb_rose_oc,
-K562_50kb_none_oc,
-K562_50kb_rus_oc,
-K562_50kb_ros_oc,
-K562_50kb_smote_oc,
-K562_50kb_rose_oc,
-K562_100kb_none_oc,
-K562_100kb_rus_oc,
-K562_100kb_ros_oc,
-K562_100kb_smote_oc,
-K562_100kb_rose_oc)
-
-prcurvetable$OP <- c(gm12878_10kb_none_OP,
-gm12878_10kb_rus_OP,
-gm12878_10kb_ros_OP,
-gm12878_10kb_smote_OP,
-gm12878_10kb_rose_OP,
-gm12878_25kb_none_OP,
-gm12878_25kb_rus_OP,
-gm12878_25kb_ros_OP,
-gm12878_25kb_smote_OP,
-gm12878_25kb_rose_OP,
-gm12878_50kb_none_OP,
-gm12878_50kb_rus_OP,
-gm12878_50kb_ros_OP,
-gm12878_50kb_smote_OP,
-gm12878_50kb_rose_OP,
-gm12878_100kb_none_OP,
-gm12878_100kb_rus_OP,
-gm12878_100kb_ros_OP,
-gm12878_100kb_smote_OP,
-gm12878_100kb_rose_OP,
-K562_10kb_none_OP,
-K562_10kb_rus_OP,
-K562_10kb_ros_OP,
-K562_10kb_smote_OP,
-K562_10kb_rose_OP,
-K562_25kb_none_OP,
-K562_25kb_rus_OP,
-K562_25kb_ros_OP,
-K562_25kb_smote_OP,
-K562_25kb_rose_OP,
-K562_50kb_none_OP,
-K562_50kb_rus_OP,
-K562_50kb_ros_OP,
-K562_50kb_smote_OP,
-K562_50kb_rose_OP,
-K562_100kb_none_OP,
-K562_100kb_rus_OP,
-K562_100kb_ros_OP,
-K562_100kb_smote_OP,
-K562_100kb_rose_OP)
-
-prcurvetable$Distance <- c(gm12878_10kb_none_Distance,
-gm12878_10kb_rus_Distance,
-gm12878_10kb_ros_Distance,
-gm12878_10kb_smote_Distance,
-gm12878_10kb_rose_Distance,
-gm12878_25kb_none_Distance,
-gm12878_25kb_rus_Distance,
-gm12878_25kb_ros_Distance,
-gm12878_25kb_smote_Distance,
-gm12878_25kb_rose_Distance,
-gm12878_50kb_none_Distance,
-gm12878_50kb_rus_Distance,
-gm12878_50kb_ros_Distance,
-gm12878_50kb_smote_Distance,
-gm12878_50kb_rose_Distance,
-gm12878_100kb_none_Distance,
-gm12878_100kb_rus_Distance,
-gm12878_100kb_ros_Distance,
-gm12878_100kb_smote_Distance,
-gm12878_100kb_rose_Distance,
-K562_10kb_none_Distance,
-K562_10kb_rus_Distance,
-K562_10kb_ros_Distance,
-K562_10kb_smote_Distance,
-K562_10kb_rose_Distance,
-K562_25kb_none_Distance,
-K562_25kb_rus_Distance,
-K562_25kb_ros_Distance,
-K562_25kb_smote_Distance,
-K562_25kb_rose_Distance,
-K562_50kb_none_Distance,
-K562_50kb_rus_Distance,
-K562_50kb_ros_Distance,
-K562_50kb_smote_Distance,
-K562_50kb_rose_Distance,
-K562_100kb_none_Distance,
-K562_100kb_rus_Distance,
-K562_100kb_ros_Distance,
-K562_100kb_smote_Distance,
-K562_100kb_rose_Distance)
-
-prcurvetable$All <- c(gm12878_10kb_none_all,
-gm12878_10kb_rus_all,
-gm12878_10kb_ros_all,
-gm12878_10kb_smote_all,
-gm12878_10kb_rose_all,
-gm12878_25kb_none_all,
-gm12878_25kb_rus_all,
-gm12878_25kb_ros_all,
-gm12878_25kb_smote_all,
-gm12878_25kb_rose_all,
-gm12878_50kb_none_all,
-gm12878_50kb_rus_all,
-gm12878_50kb_ros_all,
-gm12878_50kb_smote_all,
-gm12878_50kb_rose_all,
-gm12878_100kb_none_all,
-gm12878_100kb_rus_all,
-gm12878_100kb_ros_all,
-gm12878_100kb_smote_all,
-gm12878_100kb_rose_all,
-K562_10kb_none_all,
-K562_10kb_rus_all,
-K562_10kb_ros_all,
-K562_10kb_smote_all,
-K562_10kb_rose_all,
-K562_25kb_none_all,
-K562_25kb_rus_all,
-K562_25kb_ros_all,
-K562_25kb_smote_all,
-K562_25kb_rose_all,
-K562_50kb_none_all,
-K562_50kb_rus_all,
-K562_50kb_ros_all,
-K562_50kb_smote_all,
-K562_50kb_rose_all,
-K562_100kb_none_all,
-K562_100kb_rus_all,
-K562_100kb_ros_all,
-K562_100kb_smote_all,
-K562_100kb_rose_all)
-
-```
-
-## RFE
-
-###10kb
-
-```{r}
-rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-#None
-resampdata_None_10kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
-resampdata_None_10kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
-                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
-
-rfeplot_None_10kb <- ggplot(resampdata_None_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,.5)
-
-#RUS
-resampdata_RUS_10kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
-resampdata_RUS_10kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
-
-rfeplot_RUS_10kb <- ggplot(resampdata_RUS_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROS
-resampdata_ROS_10kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
-resampdata_ROS_10kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
-
-rfeplot_ROS_10kb <- ggplot(resampdata_ROS_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#SMOTE
-resampdata_SMOTE_10kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
-resampdata_SMOTE_10kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
-
-rfeplot_SMOTE_10kb <- ggplot(resampdata_SMOTE_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROSE
-resampdata_ROSE_10kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
-resampdata_ROSE_10kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
-
-rfeplot_ROSE_10kb <- ggplot(resampdata_ROSE_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#Combining 10 kb plots
-ggarrange(rfeplot_None_10kb,
-          rfeplot_RUS_10kb,
-          rfeplot_ROS_10kb,
-          rfeplot_SMOTE_10kb,
-          rfeplot_ROSE_10kb,
-          nrow = 3,
-          ncol = 2,
-          common.legend = TRUE,
-          legend = "right")
-
-```
-
-###25kb
-
-```{r}
-rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-#None
-resampdata_None_25kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
-resampdata_None_25kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
-                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
-
-rfeplot_None_25kb <- ggplot(resampdata_None_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,.5)
-
-#RUS
-resampdata_RUS_25kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
-resampdata_RUS_25kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
-
-rfeplot_RUS_25kb <- ggplot(resampdata_RUS_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROS
-resampdata_ROS_25kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
-resampdata_ROS_25kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
-
-rfeplot_ROS_25kb <- ggplot(resampdata_ROS_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#SMOTE
-resampdata_SMOTE_25kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
-resampdata_SMOTE_25kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
-
-rfeplot_SMOTE_25kb <- ggplot(resampdata_SMOTE_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROSE
-resampdata_ROSE_25kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
-resampdata_ROSE_25kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
-
-rfeplot_ROSE_25kb <- ggplot(resampdata_ROSE_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-```
-
-###50kb
-
-```{r}
-rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-#None
-resampdata_None_50kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
-resampdata_None_50kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
-                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
-
-rfeplot_None_50kb <- ggplot(resampdata_None_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,.5)
-
-#RUS
-resampdata_RUS_50kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
-resampdata_RUS_50kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
-
-rfeplot_RUS_50kb <- ggplot(resampdata_RUS_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROS
-resampdata_ROS_50kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
-resampdata_ROS_50kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
-
-rfeplot_ROS_50kb <- ggplot(resampdata_ROS_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#SMOTE
-resampdata_SMOTE_50kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
-resampdata_SMOTE_50kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
-
-rfeplot_SMOTE_50kb <- ggplot(resampdata_SMOTE_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROSE
-resampdata_ROSE_50kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
-resampdata_ROSE_50kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
-
-rfeplot_ROSE_50kb <- ggplot(resampdata_ROSE_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-```
-
-###100kb
-
-```{r}
-rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-#None
-resampdata_None_100kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
-resampdata_None_100kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
-                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
-
-rfeplot_None_100kb <- ggplot(resampdata_None_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,.5)
-
-#RUS
-resampdata_RUS_100kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
-resampdata_RUS_100kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
-
-rfeplot_RUS_100kb <- ggplot(resampdata_RUS_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROS
-resampdata_ROS_100kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
-resampdata_ROS_100kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
-
-rfeplot_ROS_100kb <- ggplot(resampdata_ROS_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#SMOTE
-resampdata_SMOTE_100kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
-resampdata_SMOTE_100kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
-
-rfeplot_SMOTE_100kb <- ggplot(resampdata_SMOTE_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROSE
-resampdata_ROSE_100kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
-resampdata_ROSE_100kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
-
-rfeplot_ROSE_100kb <- ggplot(resampdata_ROSE_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-```
-
-### Combined
-
-```{r}
-
-ggarrange(rfeplot_None_25kb, rfeplot_None_50kb, rfeplot_None_100kb,
-          rfeplot_RUS_25kb, rfeplot_RUS_50kb, rfeplot_RUS_100kb,
-          rfeplot_ROS_25kb, rfeplot_ROS_50kb, rfeplot_ROS_100kb,
-          rfeplot_SMOTE_25kb, rfeplot_SMOTE_50kb, rfeplot_SMOTE_100kb,
-          rfeplot_ROSE_25kb, rfeplot_ROSE_50kb, rfeplot_ROSE_100kb,
-          nrow = 5,
-          ncol = 3,
-          common.legend = TRUE,
-          legend = "right")
-
-```
-
-#Barplots of performance metrics for models with distance-type predictors
-
-##10kb
-
-```{r}
-#GM12878
-
-##None
-rfperf_gm12878_10kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_10kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_10kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_10kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_gm12878_10kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-#K562
-
-##None
-rfperf_K562_10kb_none <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_10kb_rus <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_10kb_ros <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_10kb_smote <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_K562_10kb_rose <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-all10kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all10kbresults$Performance <- c(round(rfperf_gm12878_10kb_none[9,2],2),
-                                round(rfperf_gm12878_10kb_none[19,2],2),
-                                round(rfperf_gm12878_10kb_none[16,2],2),
-                                round(rfperf_gm12878_10kb_none[15,2],2),
-                                round(rfperf_K562_10kb_none[9,2],2),
-                                round(rfperf_K562_10kb_none[19,2],2),
-                                round(rfperf_K562_10kb_none[16,2],2),
-                                round(rfperf_K562_10kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_10kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_rus[15,]),2),
-                                round(mean(rfperf_K562_10kb_rus[9,]),2),
-                                round(mean(rfperf_K562_10kb_rus[19,]),2),
-                                round(mean(rfperf_K562_10kb_rus[16,]),2),
-                                round(mean(rfperf_K562_10kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[15,]),2),
-                                round(mean(rfperf_K562_10kb_ros[9,]),2),
-                                round(mean(rfperf_K562_10kb_ros[19,]),2),
-                                round(mean(rfperf_K562_10kb_ros[16,]),2),
-                                round(mean(rfperf_K562_10kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[15,]),2),
-                                round(mean(rfperf_K562_10kb_smote[9,]),2),
-                                round(mean(rfperf_K562_10kb_smote[19,]),2),
-                                round(mean(rfperf_K562_10kb_smote[16,]),2),
-                                round(mean(rfperf_K562_10kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[15,]),2),
-                                round(mean(rfperf_K562_10kb_rose[9,]),2),
-                                round(mean(rfperf_K562_10kb_rose[19,]),2),
-                                round(mean(rfperf_K562_10kb_rose[16,]),2),
-                                round(mean(rfperf_K562_10kb_rose[15,]),2))
-
-all10kbresults$Resampling <- factor(all10kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all10kbresults$CL <- factor(all10kbresults$CL, levels=c("GM12878", "K562"))
-all10kbresults$Metric <- factor(all10kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
-
-none10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="None"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rus10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="RUS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-ros10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="ROS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-smote10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="SMOTE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rose10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="ROSE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-######################################################################
-
-#comparing only f1 and mcc
-
-f1mcc10kbplot <- ggplot(all10kbresults[which(all10kbresults$Metric=="F1-Score" |
-                                               all10kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=CL)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-##25kb
-
-```{r}
-#GM12878
-
-##None
-rfperf_gm12878_25kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_25kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_25kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_25kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_gm12878_25kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-#K562
-
-##None
-rfperf_K562_25kb_none <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_25kb_rus <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_25kb_ros <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_25kb_smote <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_K562_25kb_rose <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-all25kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all25kbresults$Performance <- c(round(rfperf_gm12878_25kb_none[9,2],2),
-                                round(rfperf_gm12878_25kb_none[19,2],2),
-                                round(rfperf_gm12878_25kb_none[16,2],2),
-                                round(rfperf_gm12878_25kb_none[15,2],2),
-                                round(rfperf_K562_25kb_none[9,2],2),
-                                round(rfperf_K562_25kb_none[19,2],2),
-                                round(rfperf_K562_25kb_none[16,2],2),
-                                round(rfperf_K562_25kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_25kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_rus[15,]),2),
-                                round(mean(rfperf_K562_25kb_rus[9,]),2),
-                                round(mean(rfperf_K562_25kb_rus[19,]),2),
-                                round(mean(rfperf_K562_25kb_rus[16,]),2),
-                                round(mean(rfperf_K562_25kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[15,]),2),
-                                round(mean(rfperf_K562_25kb_ros[9,]),2),
-                                round(mean(rfperf_K562_25kb_ros[19,]),2),
-                                round(mean(rfperf_K562_25kb_ros[16,]),2),
-                                round(mean(rfperf_K562_25kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[15,]),2),
-                                round(mean(rfperf_K562_25kb_smote[9,]),2),
-                                round(mean(rfperf_K562_25kb_smote[19,]),2),
-                                round(mean(rfperf_K562_25kb_smote[16,]),2),
-                                round(mean(rfperf_K562_25kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[15,]),2),
-                                round(mean(rfperf_K562_25kb_rose[9,]),2),
-                                round(mean(rfperf_K562_25kb_rose[19,]),2),
-                                round(mean(rfperf_K562_25kb_rose[16,]),2),
-                                round(mean(rfperf_K562_25kb_rose[15,]),2))
-
-all25kbresults$Resampling <- factor(all25kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all25kbresults$CL <- factor(all25kbresults$CL, levels=c("GM12878", "K562"))
-all25kbresults$Metric <- factor(all25kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
-
-none25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="None"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rus25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="RUS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-ros25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="ROS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-smote25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="SMOTE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rose25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="ROSE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-######################################################################
-
-#comparing only f1 and mcc
-
-f1mcc25kbplot <- ggplot(all25kbresults[which(all25kbresults$Metric=="F1-Score" |
-                                               all25kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=CL)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-##50kb
-
-```{r}
-#GM12878
-
-##None
-rfperf_gm12878_50kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_50kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_50kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_50kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_gm12878_50kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-#K562
-
-##None
-rfperf_K562_50kb_none <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_50kb_rus <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_50kb_ros <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_50kb_smote <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_K562_50kb_rose <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-all50kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all50kbresults$Performance <- c(round(rfperf_gm12878_50kb_none[9,2],2),
-                                round(rfperf_gm12878_50kb_none[19,2],2),
-                                round(rfperf_gm12878_50kb_none[16,2],2),
-                                round(rfperf_gm12878_50kb_none[15,2],2),
-                                round(rfperf_K562_50kb_none[9,2],2),
-                                round(rfperf_K562_50kb_none[19,2],2),
-                                round(rfperf_K562_50kb_none[16,2],2),
-                                round(rfperf_K562_50kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_50kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_rus[15,]),2),
-                                round(mean(rfperf_K562_50kb_rus[9,]),2),
-                                round(mean(rfperf_K562_50kb_rus[19,]),2),
-                                round(mean(rfperf_K562_50kb_rus[16,]),2),
-                                round(mean(rfperf_K562_50kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[15,]),2),
-                                round(mean(rfperf_K562_50kb_ros[9,]),2),
-                                round(mean(rfperf_K562_50kb_ros[19,]),2),
-                                round(mean(rfperf_K562_50kb_ros[16,]),2),
-                                round(mean(rfperf_K562_50kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[15,]),2),
-                                round(mean(rfperf_K562_50kb_smote[9,]),2),
-                                round(mean(rfperf_K562_50kb_smote[19,]),2),
-                                round(mean(rfperf_K562_50kb_smote[16,]),2),
-                                round(mean(rfperf_K562_50kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[15,]),2),
-                                round(mean(rfperf_K562_50kb_rose[9,]),2),
-                                round(mean(rfperf_K562_50kb_rose[19,]),2),
-                                round(mean(rfperf_K562_50kb_rose[16,]),2),
-                                round(mean(rfperf_K562_50kb_rose[15,]),2))
-
-all50kbresults$Resampling <- factor(all50kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all50kbresults$CL <- factor(all50kbresults$CL, levels=c("GM12878", "K562"))
-all50kbresults$Metric <- factor(all50kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
-
-none50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="None"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rus50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="RUS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-ros50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="ROS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-smote50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="SMOTE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rose50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="ROSE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-######################################################################
-
-#comparing only f1 and mcc
-
-f1mcc50kbplot <- ggplot(all50kbresults[which(all50kbresults$Metric=="F1-Score" |
-                                               all50kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=CL)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-##100kb
-
-```{r}
-#GM12878
-
-##None
-rfperf_gm12878_100kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_100kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_100kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_100kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_gm12878_100kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-#K562
-
-##None
-rfperf_K562_100kb_none <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_100kb_rus <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_100kb_ros <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_100kb_smote <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_K562_100kb_rose <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-all100kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all100kbresults$Performance <- c(round(rfperf_gm12878_100kb_none[9,2],2),
-                                round(rfperf_gm12878_100kb_none[19,2],2),
-                                round(rfperf_gm12878_100kb_none[16,2],2),
-                                round(rfperf_gm12878_100kb_none[15,2],2),
-                                round(rfperf_K562_100kb_none[9,2],2),
-                                round(rfperf_K562_100kb_none[19,2],2),
-                                round(rfperf_K562_100kb_none[16,2],2),
-                                round(rfperf_K562_100kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_100kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_rus[15,]),2),
-                                round(mean(rfperf_K562_100kb_rus[9,]),2),
-                                round(mean(rfperf_K562_100kb_rus[19,]),2),
-                                round(mean(rfperf_K562_100kb_rus[16,]),2),
-                                round(mean(rfperf_K562_100kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[15,]),2),
-                                round(mean(rfperf_K562_100kb_ros[9,]),2),
-                                round(mean(rfperf_K562_100kb_ros[19,]),2),
-                                round(mean(rfperf_K562_100kb_ros[16,]),2),
-                                round(mean(rfperf_K562_100kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[15,]),2),
-                                round(mean(rfperf_K562_100kb_smote[9,]),2),
-                                round(mean(rfperf_K562_100kb_smote[19,]),2),
-                                round(mean(rfperf_K562_100kb_smote[16,]),2),
-                                round(mean(rfperf_K562_100kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[15,]),2),
-                                round(mean(rfperf_K562_100kb_rose[9,]),2),
-                                round(mean(rfperf_K562_100kb_rose[19,]),2),
-                                round(mean(rfperf_K562_100kb_rose[16,]),2),
-                                round(mean(rfperf_K562_100kb_rose[15,]),2))
-
-all100kbresults$Resampling <- factor(all100kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all100kbresults$CL <- factor(all100kbresults$CL, levels=c("GM12878", "K562"))
-all100kbresults$Metric <- factor(all100kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
-
-none100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="None"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rus100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="RUS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-ros100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="ROS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-smote100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="SMOTE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rose100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="ROSE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-######################################################################
-
-#comparing only f1 and mcc
-
-f1mcc100kbplot <- ggplot(all100kbresults[which(all100kbresults$Metric=="F1-Score" |
-                                               all100kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=CL)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-#Table of model performances
-
-```{r}
-
-performancetab <- data.frame(Performance = c(rep("F1-Score", 10),
-                                             rep("MCC", 10)),
-                             Resampling = rep(c("None",
-                                                "None",
-                                                "RUS",
-                                                "RUS",
-                                                "ROS",
-                                                "ROS",
-                                                "SMOTE",
-                                                "SMOTE",
-                                                "ROSE",
-                                                "ROSE"),2),
-                             CL = rep(c("GM12878", "K562"), 10)
-                             )
-
-performancetab$kb10 <- c(rfperf_gm12878_10kb_none[16,2],
-                         rfperf_K562_10kb_none[16,2],
-                         mean(rfperf_gm12878_10kb_rus[16,]),
-                         mean(rfperf_K562_10kb_rus[16,]),
-                         mean(rfperf_gm12878_10kb_ros[16,]),
-                         mean(rfperf_K562_10kb_ros[16,]),
-                         mean(rfperf_gm12878_10kb_smote[16,]),
-                         mean(rfperf_K562_10kb_smote[16,]),
-                         mean(rfperf_gm12878_10kb_rose[16,]),
-                         mean(rfperf_K562_10kb_rose[16,]),
-                         rfperf_gm12878_10kb_none[15,2],
-                         rfperf_K562_10kb_none[15,2],
-                         mean(rfperf_gm12878_10kb_rus[15,]),
-                         mean(rfperf_K562_10kb_rus[15,]),
-                         mean(rfperf_gm12878_10kb_ros[15,]),
-                         mean(rfperf_K562_10kb_ros[15,]),
-                         mean(rfperf_gm12878_10kb_smote[15,]),
-                         mean(rfperf_K562_10kb_smote[15,]),
-                         mean(rfperf_gm12878_10kb_rose[15,]),
-                         mean(rfperf_K562_10kb_rose[15,]))
-
-performancetab$kb25 <- c(rfperf_gm12878_25kb_none[16,2],
-                         rfperf_K562_25kb_none[16,2],
-                         mean(rfperf_gm12878_25kb_rus[16,]),
-                         mean(rfperf_K562_25kb_rus[16,]),
-                         mean(rfperf_gm12878_25kb_ros[16,]),
-                         mean(rfperf_K562_25kb_ros[16,]),
-                         mean(rfperf_gm12878_25kb_smote[16,]),
-                         mean(rfperf_K562_25kb_smote[16,]),
-                         mean(rfperf_gm12878_25kb_rose[16,]),
-                         mean(rfperf_K562_25kb_rose[16,]),
-                         rfperf_gm12878_25kb_none[15,2],
-                         rfperf_K562_25kb_none[15,2],
-                         mean(rfperf_gm12878_25kb_rus[15,]),
-                         mean(rfperf_K562_25kb_rus[15,]),
-                         mean(rfperf_gm12878_25kb_ros[15,]),
-                         mean(rfperf_K562_25kb_ros[15,]),
-                         mean(rfperf_gm12878_25kb_smote[15,]),
-                         mean(rfperf_K562_25kb_smote[15,]),
-                         mean(rfperf_gm12878_25kb_rose[15,]),
-                         mean(rfperf_K562_25kb_rose[15,]))
-
-performancetab$kb50 <- c(rfperf_gm12878_50kb_none[16,2],
-                         rfperf_K562_50kb_none[16,2],
-                         mean(rfperf_gm12878_50kb_rus[16,]),
-                         mean(rfperf_K562_50kb_rus[16,]),
-                         mean(rfperf_gm12878_50kb_ros[16,]),
-                         mean(rfperf_K562_50kb_ros[16,]),
-                         mean(rfperf_gm12878_50kb_smote[16,]),
-                         mean(rfperf_K562_50kb_smote[16,]),
-                         mean(rfperf_gm12878_50kb_rose[16,]),
-                         mean(rfperf_K562_50kb_rose[16,]),
-                         rfperf_gm12878_50kb_none[15,2],
-                         rfperf_K562_50kb_none[15,2],
-                         mean(rfperf_gm12878_50kb_rus[15,]),
-                         mean(rfperf_K562_50kb_rus[15,]),
-                         mean(rfperf_gm12878_50kb_ros[15,]),
-                         mean(rfperf_K562_50kb_ros[15,]),
-                         mean(rfperf_gm12878_50kb_smote[15,]),
-                         mean(rfperf_K562_50kb_smote[15,]),
-                         mean(rfperf_gm12878_50kb_rose[15,]),
-                         mean(rfperf_K562_50kb_rose[15,]))
-
-performancetab$kb100 <- c(rfperf_gm12878_100kb_none[16,2],
-                         rfperf_K562_100kb_none[16,2],
-                         mean(rfperf_gm12878_100kb_rus[16,]),
-                         mean(rfperf_K562_100kb_rus[16,]),
-                         mean(rfperf_gm12878_100kb_ros[16,]),
-                         mean(rfperf_K562_100kb_ros[16,]),
-                         mean(rfperf_gm12878_100kb_smote[16,]),
-                         mean(rfperf_K562_100kb_smote[16,]),
-                         mean(rfperf_gm12878_100kb_rose[16,]),
-                         mean(rfperf_K562_100kb_rose[16,]),
-                         rfperf_gm12878_100kb_none[15,2],
-                         rfperf_K562_100kb_none[15,2],
-                         mean(rfperf_gm12878_100kb_rus[15,]),
-                         mean(rfperf_K562_100kb_rus[15,]),
-                         mean(rfperf_gm12878_100kb_ros[15,]),
-                         mean(rfperf_K562_100kb_ros[15,]),
-                         mean(rfperf_gm12878_100kb_smote[15,]),
-                         mean(rfperf_K562_100kb_smote[15,]),
-                         mean(rfperf_gm12878_100kb_rose[15,]),
-                         mean(rfperf_K562_100kb_rose[15,]))
-
-performancetab[,4:7] <- round(performancetab[,4:7], 3)
-```
-
-#Variable Importance Plots for distance predictors with ENET reduction
-
-##5kb
-###Random Under-Sampling
-```{r}
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/5kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf5kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf5kb <- rf5kb[order(rf5kb$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf5kb$Importance
-Labels <- as.character(rf5kb$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.5kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.5kb$Feature <- as.character(varimp.rf.df.5kb$Feature)							 
-varimp.rf.df.5kb <-varimp.rf.df.5kb[order(varimp.rf.df.5kb$Importance),]
-varimp.rf.df.5kb <- varimp.rf.df.5kb[(dim(varimp.rf.df.5kb)[1]-14):dim(varimp.rf.df.5kb)[1],]
-varimp.rf.df.5kb$Feature <- factor(varimp.rf.df.5kb$Feature,
-                                     levels=as.character(varimp.rf.df.5kb$Feature))
-
-p.rf.5kb <- ggplot(varimp.rf.df.5kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(A)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="red") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-  ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/5kb/p.rf.5kb.png")
-```
-##25kb
-###Random Under-Sampling
-```{r}
-  rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/25kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf <- rf[order(rf$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf$Importance
-Labels <- as.character(rf$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.25kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.25kb$Feature <- as.character(varimp.rf.df.25kb$Feature)							 
-varimp.rf.df.25kb <-varimp.rf.df.25kb[order(varimp.rf.df.25kb$Importance),]
-varimp.rf.df.25kb <- varimp.rf.df.25kb[(dim(varimp.rf.df.25kb)[1]-14):dim(varimp.rf.df.25kb)[1],]
-varimp.rf.df.25kb$Feature <- factor(varimp.rf.df.25kb$Feature,
-                                     levels=as.character(varimp.rf.df.25kb$Feature))
-
-p.rf.25kb <- ggplot(varimp.rf.df.25kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(B)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="blue") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/25kb/p.rf.25kb.png")
-```
-##50kb
-###Random Under-Sampling
-```{r}
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/50kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf <- rf[order(rf$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf$Importance
-Labels <- as.character(rf$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.50kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.50kb$Feature <- as.character(varimp.rf.df.50kb$Feature)							 
-varimp.rf.df.50kb <-varimp.rf.df.50kb[order(varimp.rf.df.50kb$Importance),]
-varimp.rf.df.50kb <- varimp.rf.df.50kb[(dim(varimp.rf.df.50kb)[1]-14):dim(varimp.rf.df.50kb)[1],]
-varimp.rf.df.50kb$Feature <- factor(varimp.rf.df.50kb$Feature,
-                                     levels=as.character(varimp.rf.df.50kb$Feature))
-
-p.rf.50kb <- ggplot(varimp.rf.df.50kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(C)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="green") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/50kb/p.rf.50kb.png")
-```
-##100kb
-###Random Under-Sampling
-```{r}
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/100kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf <- rf[order(rf$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf$Importance
-Labels <- as.character(rf$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.100kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.100kb$Feature <- as.character(varimp.rf.df.100kb$Feature)							 
-varimp.rf.df.100kb <-varimp.rf.df.100kb[order(varimp.rf.df.100kb$Importance),]
-#varimp.rf.df.100kb <- varimp.rf.df.100kb[(dim(varimp.rf.df.100kb)[1]-14):dim(varimp.rf.df.100kb)[1],]
-varimp.rf.df.100kb$Feature <- factor(varimp.rf.df.100kb$Feature,
-                                     levels=as.character(varimp.rf.df.100kb$Feature))
-
-p.rf.100kb <- ggplot(varimp.rf.df.100kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(D)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="orange") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/100kb/p.rf.100kb.png")
-
-allvarimps <- ggarrange(p.rf.5kb,p.rf.25kb,p.rf.50kb,p.rf.100kb, ncol=2, nrow=2)
-
-ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/allvarimps.png")
-```
-
-#Network Analysis
-
-```{r}
-##venn diagram of top predictors 
-#grid.newpage()
-##vennp <- draw.triple.venn(area1 = 10, area2 = 10, area3 = 10, n12 = length(intersect(us,sm)), n23 = length(intersect(sm,km)), n13 = length(intersect(km,us)), 
-##                 n123 = length(intersect(us,intersect(sm,km))), category = c("Under- \n Sampling", "SMOTE", "K-Medoids"), lty = "blank", 
-##                 fill = c("red", "green", "blue"),cex=3,cat.cex = 3)
-#
-#vennp <- draw.pairwise.venn(length(varimp.rf.df.gm12878$Feature),
-#						  length(varimp.rf.df.k562$Feature),
-#						  length(intersect(varimp.rf.df.gm12878$Feature, varimp.rf.df.k562$Feature)),
-#						  category = c("GM12878", "K562"),
-#						  lty = "blank", 
-#                          fill = c("red", "blue"),
-#						  cex=3,
-#						  cat.cex = 3,
-#						  cat.pos = c(0,0),
-#						  scaled = FALSE)
-
-##Network Visualization between resolutions
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/5kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf5kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rownames(rf5kb) <- NULL
-rf5kb$Feature <- as.character(rf5kb$Feature)
-rf5kb$Feature[grep("Gm12878-", rf5kb$Feature)] <- gsub("Gm12878-","",rf5kb$Feature[grep("Gm12878-", rf5kb$Feature)])
-rf5kb$Feature[grep("_dist", rf5kb$Feature)] <- gsub("_dist","",rf5kb$Feature[grep("_dist", rf5kb$Feature)])
-rf5kb$Importance <- rf5kb$Importance/sum(rf5kb$Importance)
-
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/25kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf25kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rownames(rf25kb) <- NULL
-rf25kb$Feature <- as.character(rf25kb$Feature)
-rf25kb$Feature[grep("Gm12878-", rf25kb$Feature)] <- gsub("Gm12878-","",rf25kb$Feature[grep("Gm12878-", rf25kb$Feature)])
-rf25kb$Feature[grep("_dist", rf25kb$Feature)] <- gsub("_dist","",rf25kb$Feature[grep("_dist", rf25kb$Feature)])
-rf25kb$Importance <- rf25kb$Importance/sum(rf25kb$Importance)
-
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/50kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf50kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rownames(rf50kb) <- NULL
-rf50kb$Feature <- as.character(rf50kb$Feature)
-rf50kb$Feature[grep("Gm12878-", rf50kb$Feature)] <- gsub("Gm12878-","",rf50kb$Feature[grep("Gm12878-", rf50kb$Feature)])
-rf50kb$Feature[grep("_dist", rf50kb$Feature)] <- gsub("_dist","",rf50kb$Feature[grep("_dist", rf50kb$Feature)])
-rf50kb$Importance <- rf50kb$Importance/sum(rf50kb$Importance)
-
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/100kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf100kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rownames(rf100kb) <- NULL
-rf100kb$Feature <- as.character(rf100kb$Feature)
-rf100kb$Feature[grep("Gm12878-", rf100kb$Feature)] <- gsub("Gm12878-","",rf100kb$Feature[grep("Gm12878-", rf100kb$Feature)])
-rf100kb$Feature[grep("_dist", rf100kb$Feature)] <- gsub("_dist","",rf100kb$Feature[grep("_dist", rf100kb$Feature)])
-rf100kb$Importance <- rf100kb$Importance/sum(rf100kb$Importance)
-
-commonannots <- union(rf5kb$Feature,union(rf25kb$Feature,union(rf50kb$Feature,rf100kb$Feature)))
-
-networkmat <- matrix(ncol=4, nrow=length(commonannots), dimnames=list(commonannots, c("5kb", "25kb", "50kb", "100kb")))
-
-networkmat[which(rownames(networkmat) %in% rf5kb$Feature),1] <- rf5kb$Importance
-networkmat[which(rownames(networkmat) %in% rf25kb$Feature),2] <- rf25kb$Importance
-networkmat[which(rownames(networkmat) %in% rf50kb$Feature),3] <- rf50kb$Importance
-networkmat[which(rownames(networkmat) %in% rf100kb$Feature),4] <- rf100kb$Importance
-
-networkmat[is.na(networkmat)] <- 0
-networkmat <- networkmat*10
-
-networkdf <- as.data.frame(networkmat)
-
-net = network(networkdf,
-              matrix.type = "bipartite",
-              ignore.eval = FALSE,
-              names.eval = "weights")
-
-col = c("actor" = "green", "event" = "blue")
-
-networkplot <- ggnet2(net, color = "mode", palette = col, edge.size = "weights", label=TRUE)
-
-ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/networkplot.png")
-
-networkdf <- as.data.frame(t(networkdf))
-
-net = network(networkdf,
-              matrix.type = "bipartite",
-              ignore.eval = FALSE,
-              names.eval = "weights")
-
-col = c("actor" = "blue", "event" = "green")
-
-networkplot2 <- ggnet2(net, color = "mode", palette = col, edge.size = "weights", label=TRUE)
-
-ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/networkplot2.png")
-
-```

### 2019-02-27 Scripts/evaluating_imbalance_ratios.Rmd
added script evaluating imbalance ratios

--- 2019-02-05 Scripts/performances.rmd
@@
 ---
-title: "Performances Code"
+title: "Evaluating Class Imbalance"
 output: html_document
@@
 library(ROSE)
-
-```
-
-# Evaluating Distance Densities
-##GM12878
-###10kb
-
-```{r}
-gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
-
-gm12878_10kb_ld <- gm12878_10kb[,c(1,grep("_dist", names(gm12878_10kb)))]
-
-###############
-#gm12878_10kb_ld <- gm12878_10kb_ld[,c(1:5)]
-###############
-
-gm12878_10kb_d <- gm12878_10kb_ld
-gm12878_10kb_d[,-1] <- exp(gm12878_10kb_ld[,-1]) - 1
-gm12878_10kb_d$Average_dist <- rowMeans(gm12878_10kb_d[,-1])
-
-gm12878_10kb_ld$Average_dist <- rowMeans(gm12878_10kb_ld[,-1])
-names(gm12878_10kb_ld)[-1] <- paste(substr(names(gm12878_10kb_ld)[-1],
-                                           1, 
-                                           nchar(names(gm12878_10kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-gm12878_10kb_alldist <- cbind.data.frame(gm12878_10kb_d[,-1], gm12878_10kb_ld[,-1])
-
-long10kb <- melt(gm12878_10kb_alldist)
-long10kb$variable <- as.character(long10kb$variable)
-long10kb$Transformation <- NA
-long10kb$Transformation[grep("_logdist", long10kb$variable)] <- rep("Log Distance", length(long10kb$variable[grep("_logdist", long10kb$variable)]))
-long10kb$Transformation[grep("_logdist", long10kb$variable, invert = TRUE)] <- rep("Distance", length(long10kb$variable[grep("_logdist", long10kb$variable, invert = TRUE)]))
-
-table(long10kb$Transformation)
-
-distdensity10kb <- ggplot() + 
-  geom_density(data=long10kb[intersect(grep("_dist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long10kb[grep("Average_dist", long10kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity10kb <- ggplot() + 
-  geom_density(data=long10kb[intersect(grep("logdist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long10kb[grep("Average_logdist", long10kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long10kb$value[long10kb$Transformation=="Distance"] <- long10kb$value[long10kb$Transformation=="Distance"]/1000000
-long10kb <- long10kb[grep("Average", long10kb$variable, invert = TRUE),]
-long10kb$variable <- factor(long10kb$variable)
-long10kb$Transformation <- factor(long10kb$Transformation)
-
-alldensity10kb <- ggplot(long10kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("10 kb")+ 
-  ylim(0,.8)+
-  ggtitle("GM12878") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-###25kb
-
-```{r}
-gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
-
-gm12878_25kb_ld <- gm12878_25kb[,c(1,grep("_dist", names(gm12878_25kb)))]
-
-###############
-#gm12878_25kb_ld <- gm12878_25kb_ld[,c(1:5)]
-###############
-
-gm12878_25kb_d <- gm12878_25kb_ld
-gm12878_25kb_d[,-1] <- exp(gm12878_25kb_ld[,-1]) - 1
-gm12878_25kb_d$Average_dist <- rowMeans(gm12878_25kb_d[,-1])
-
-gm12878_25kb_ld$Average_dist <- rowMeans(gm12878_25kb_ld[,-1])
-names(gm12878_25kb_ld)[-1] <- paste(substr(names(gm12878_25kb_ld)[-1],
-                                           1, 
-                                           nchar(names(gm12878_25kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-gm12878_25kb_alldist <- cbind.data.frame(gm12878_25kb_d[,-1], gm12878_25kb_ld[,-1])
-
-long25kb <- melt(gm12878_25kb_alldist)
-long25kb$variable <- as.character(long25kb$variable)
-long25kb$Transformation <- NA
-long25kb$Transformation[grep("_logdist", long25kb$variable)] <- rep("Log Distance", length(long25kb$variable[grep("_logdist", long25kb$variable)]))
-long25kb$Transformation[grep("_logdist", long25kb$variable, invert = TRUE)] <- rep("Distance", length(long25kb$variable[grep("_logdist", long25kb$variable, invert = TRUE)]))
-
-table(long25kb$Transformation)
-
-distdensity25kb <- ggplot() + 
-  geom_density(data=long25kb[intersect(grep("_dist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long25kb[grep("Average_dist", long25kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity25kb <- ggplot() + 
-  geom_density(data=long25kb[intersect(grep("logdist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long25kb[grep("Average_logdist", long25kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) +  
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long25kb$value[long25kb$Transformation=="Distance"] <- long25kb$value[long25kb$Transformation=="Distance"]/1000000
-long25kb <- long25kb[grep("Average", long25kb$variable, invert = TRUE),]
-long25kb$variable <- factor(long25kb$variable)
-long25kb$Transformation <- factor(long25kb$Transformation)
-
-alldensity25kb <- ggplot(long25kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("25 kb")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-###50kb
-
-```{r}
-gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
-
-gm12878_50kb_ld <- gm12878_50kb[,c(1,grep("_dist", names(gm12878_50kb)))]
-
-###############
-#gm12878_50kb_ld <- gm12878_50kb_ld[,c(1:5)]
-###############
-
-gm12878_50kb_d <- gm12878_50kb_ld
-gm12878_50kb_d[,-1] <- exp(gm12878_50kb_ld[,-1]) - 1
-gm12878_50kb_d$Average_dist <- rowMeans(gm12878_50kb_d[,-1])
-
-gm12878_50kb_ld$Average_dist <- rowMeans(gm12878_50kb_ld[,-1])
-names(gm12878_50kb_ld)[-1] <- paste(substr(names(gm12878_50kb_ld)[-1],
-                                           1, 
-                                           nchar(names(gm12878_50kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-gm12878_50kb_alldist <- cbind.data.frame(gm12878_50kb_d[,-1], gm12878_50kb_ld[,-1])
-
-long50kb <- melt(gm12878_50kb_alldist)
-long50kb$variable <- as.character(long50kb$variable)
-long50kb$Transformation <- NA
-long50kb$Transformation[grep("_logdist", long50kb$variable)] <- rep("Log Distance", length(long50kb$variable[grep("_logdist", long50kb$variable)]))
-long50kb$Transformation[grep("_logdist", long50kb$variable, invert = TRUE)] <- rep("Distance", length(long50kb$variable[grep("_logdist", long50kb$variable, invert = TRUE)]))
-
-table(long50kb$Transformation)
-
-distdensity50kb <- ggplot() + 
-  geom_density(data=long50kb[intersect(grep("_dist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long50kb[grep("Average_dist", long50kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity50kb <- ggplot() + 
-  geom_density(data=long50kb[intersect(grep("logdist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long50kb[grep("Average_logdist", long50kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long50kb$value[long50kb$Transformation=="Distance"] <- long50kb$value[long50kb$Transformation=="Distance"]/1000000
-long50kb <- long50kb[grep("Average", long50kb$variable, invert = TRUE),]
-long50kb$variable <- factor(long50kb$variable)
-long50kb$Transformation <- factor(long50kb$Transformation)
-
-alldensity50kb <- ggplot(long50kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("50 kb")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-###100kb
-
-```{r}
-gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
-
-gm12878_100kb_ld <- gm12878_100kb[,c(1,grep("_dist", names(gm12878_100kb)))]
-
-###############
-#gm12878_100kb_ld <- gm12878_100kb_ld[,c(1:5)]
-###############
-
-gm12878_100kb_d <- gm12878_100kb_ld
-gm12878_100kb_d[,-1] <- exp(gm12878_100kb_ld[,-1]) - 1
-gm12878_100kb_d$Average_dist <- rowMeans(gm12878_100kb_d[,-1])
-
-gm12878_100kb_ld$Average_dist <- rowMeans(gm12878_100kb_ld[,-1])
-names(gm12878_100kb_ld)[-1] <- paste(substr(names(gm12878_100kb_ld)[-1],
-                                           1, 
-                                           nchar(names(gm12878_100kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-gm12878_100kb_alldist <- cbind.data.frame(gm12878_100kb_d[,-1], gm12878_100kb_ld[,-1])
-
-long100kb <- melt(gm12878_100kb_alldist)
-long100kb$variable <- as.character(long100kb$variable)
-long100kb$Transformation <- NA
-long100kb$Transformation[grep("_logdist", long100kb$variable)] <- rep("Log Distance", length(long100kb$variable[grep("_logdist", long100kb$variable)]))
-long100kb$Transformation[grep("_logdist", long100kb$variable, invert = TRUE)] <- rep("Distance", length(long100kb$variable[grep("_logdist", long100kb$variable, invert = TRUE)]))
-
-table(long100kb$Transformation)
-
-distdensity100kb <- ggplot() + 
-  geom_density(data=long100kb[intersect(grep("_dist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long100kb[grep("Average_dist", long100kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("No Transformation") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity100kb <- ggplot() + 
-  geom_density(data=long100kb[intersect(grep("logdist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long100kb[grep("Average_logdist", long100kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("Log Tranformation") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long100kb$value[long100kb$Transformation=="Distance"] <- long100kb$value[long100kb$Transformation=="Distance"]/1000000
-long100kb <- long100kb[grep("Average", long100kb$variable, invert = TRUE),]
-long100kb$variable <- factor(long100kb$variable)
-long100kb$Transformation <- factor(long100kb$Transformation)
-
-alldensity100kb <- ggplot(long100kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("100 kb")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-##K562
-###10kb
-
-```{r}
-K562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
-
-K562_10kb_ld <- K562_10kb[,c(1,grep("_dist", names(K562_10kb)))]
-
-###############
-#K562_10kb_ld <- K562_10kb_ld[,c(1:5)]
-###############
-
-K562_10kb_d <- K562_10kb_ld
-K562_10kb_d[,-1] <- exp(K562_10kb_ld[,-1]) - 1
-K562_10kb_d$Average_dist <- rowMeans(K562_10kb_d[,-1])
-
-K562_10kb_ld$Average_dist <- rowMeans(K562_10kb_ld[,-1])
-names(K562_10kb_ld)[-1] <- paste(substr(names(K562_10kb_ld)[-1],
-                                           1, 
-                                           nchar(names(K562_10kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-K562_10kb_alldist <- cbind.data.frame(K562_10kb_d[,-1], K562_10kb_ld[,-1])
-
-long10kb <- melt(K562_10kb_alldist)
-long10kb$variable <- as.character(long10kb$variable)
-long10kb$Transformation <- NA
-long10kb$Transformation[grep("_logdist", long10kb$variable)] <- rep("Log Distance", length(long10kb$variable[grep("_logdist", long10kb$variable)]))
-long10kb$Transformation[grep("_logdist", long10kb$variable, invert = TRUE)] <- rep("Distance", length(long10kb$variable[grep("_logdist", long10kb$variable, invert = TRUE)]))
-
-table(long10kb$Transformation)
-
-distdensity10kb <- ggplot() + 
-  geom_density(data=long10kb[intersect(grep("_dist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long10kb[grep("Average_dist", long10kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity10kb <- ggplot() + 
-  geom_density(data=long10kb[intersect(grep("logdist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long10kb[grep("Average_logdist", long10kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long10kb$value[long10kb$Transformation=="Distance"] <- long10kb$value[long10kb$Transformation=="Distance"]/1000000
-long10kb <- long10kb[grep("Average", long10kb$variable, invert = TRUE),]
-long10kb$variable <- factor(long10kb$variable)
-long10kb$Transformation <- factor(long10kb$Transformation)
-
-alldensity10kb_k562 <- ggplot(long10kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	#ylab("10 kb")+ 
-  ylim(0,.8)+
-  ggtitle("K562") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-###25kb
-
-```{r}
-K562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
-
-K562_25kb_ld <- K562_25kb[,c(1,grep("_dist", names(K562_25kb)))]
-
-###############
-#K562_25kb_ld <- K562_25kb_ld[,c(1:5)]
-###############
-
-K562_25kb_d <- K562_25kb_ld
-K562_25kb_d[,-1] <- exp(K562_25kb_ld[,-1]) - 1
-K562_25kb_d$Average_dist <- rowMeans(K562_25kb_d[,-1])
-
-K562_25kb_ld$Average_dist <- rowMeans(K562_25kb_ld[,-1])
-names(K562_25kb_ld)[-1] <- paste(substr(names(K562_25kb_ld)[-1],
-                                           1, 
-                                           nchar(names(K562_25kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-K562_25kb_alldist <- cbind.data.frame(K562_25kb_d[,-1], K562_25kb_ld[,-1])
-
-long25kb <- melt(K562_25kb_alldist)
-long25kb$variable <- as.character(long25kb$variable)
-long25kb$Transformation <- NA
-long25kb$Transformation[grep("_logdist", long25kb$variable)] <- rep("Log Distance", length(long25kb$variable[grep("_logdist", long25kb$variable)]))
-long25kb$Transformation[grep("_logdist", long25kb$variable, invert = TRUE)] <- rep("Distance", length(long25kb$variable[grep("_logdist", long25kb$variable, invert = TRUE)]))
-
-table(long25kb$Transformation)
-
-distdensity25kb <- ggplot() + 
-  geom_density(data=long25kb[intersect(grep("_dist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long25kb[grep("Average_dist", long25kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity25kb <- ggplot() + 
-  geom_density(data=long25kb[intersect(grep("logdist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long25kb[grep("Average_logdist", long25kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long25kb$value[long25kb$Transformation=="Distance"] <- long25kb$value[long25kb$Transformation=="Distance"]/1000000
-long25kb <- long25kb[grep("Average", long25kb$variable, invert = TRUE),]
-long25kb$variable <- factor(long25kb$variable)
-long25kb$Transformation <- factor(long25kb$Transformation)
-
-alldensity25kb_k562 <- ggplot(long25kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	#ylab("25 kb")+ 
-  ylim(0,.8)+
-  #ggtitle("K562") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-###50kb
-
-```{r}
-K562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
-
-K562_50kb_ld <- K562_50kb[,c(1,grep("_dist", names(K562_50kb)))]
-
-###############
-#K562_50kb_ld <- K562_50kb_ld[,c(1:5)]
-###############
-
-K562_50kb_d <- K562_50kb_ld
-K562_50kb_d[,-1] <- exp(K562_50kb_ld[,-1]) - 1
-K562_50kb_d$Average_dist <- rowMeans(K562_50kb_d[,-1])
-
-K562_50kb_ld$Average_dist <- rowMeans(K562_50kb_ld[,-1])
-names(K562_50kb_ld)[-1] <- paste(substr(names(K562_50kb_ld)[-1],
-                                           1, 
-                                           nchar(names(K562_50kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-K562_50kb_alldist <- cbind.data.frame(K562_50kb_d[,-1], K562_50kb_ld[,-1])
-
-long50kb <- melt(K562_50kb_alldist)
-long50kb$variable <- as.character(long50kb$variable)
-long50kb$Transformation <- NA
-long50kb$Transformation[grep("_logdist", long50kb$variable)] <- rep("Log Distance", length(long50kb$variable[grep("_logdist", long50kb$variable)]))
-long50kb$Transformation[grep("_logdist", long50kb$variable, invert = TRUE)] <- rep("Distance", length(long50kb$variable[grep("_logdist", long50kb$variable, invert = TRUE)]))
-
-table(long50kb$Transformation)
-
-distdensity50kb <- ggplot() + 
-  geom_density(data=long50kb[intersect(grep("_dist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long50kb[grep("Average_dist", long50kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity50kb <- ggplot() + 
-  geom_density(data=long50kb[intersect(grep("logdist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long50kb[grep("Average_logdist", long50kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long50kb$value[long50kb$Transformation=="Distance"] <- long50kb$value[long50kb$Transformation=="Distance"]/1000000
-long50kb <- long50kb[grep("Average", long50kb$variable, invert = TRUE),]
-long50kb$variable <- factor(long50kb$variable)
-long50kb$Transformation <- factor(long50kb$Transformation)
-
-alldensity50kb_k562 <- ggplot(long50kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	#ylab("50 kb")+ 
-  ylim(0,.8)+
-  #ggtitle("K562") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-###100kb
-
-```{r}
-K562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
-
-K562_100kb_ld <- K562_100kb[,c(1,grep("_dist", names(K562_100kb)))]
-
-###############
-#K562_100kb_ld <- K562_100kb_ld[,c(1:5)]
-###############
-
-K562_100kb_d <- K562_100kb_ld
-K562_100kb_d[,-1] <- exp(K562_100kb_ld[,-1]) - 1
-K562_100kb_d$Average_dist <- rowMeans(K562_100kb_d[,-1])
-
-K562_100kb_ld$Average_dist <- rowMeans(K562_100kb_ld[,-1])
-names(K562_100kb_ld)[-1] <- paste(substr(names(K562_100kb_ld)[-1],
-                                           1, 
-                                           nchar(names(K562_100kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-K562_100kb_alldist <- cbind.data.frame(K562_100kb_d[,-1], K562_100kb_ld[,-1])
-
-long100kb <- melt(K562_100kb_alldist)
-long100kb$variable <- as.character(long100kb$variable)
-long100kb$Transformation <- NA
-long100kb$Transformation[grep("_logdist", long100kb$variable)] <- rep("Log Distance", length(long100kb$variable[grep("_logdist", long100kb$variable)]))
-long100kb$Transformation[grep("_logdist", long100kb$variable, invert = TRUE)] <- rep("Distance", length(long100kb$variable[grep("_logdist", long100kb$variable, invert = TRUE)]))
-
-table(long100kb$Transformation)
-
-distdensity100kb <- ggplot() + 
-  geom_density(data=long100kb[intersect(grep("_dist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long100kb[grep("Average_dist", long100kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity100kb <- ggplot() + 
-  geom_density(data=long100kb[intersect(grep("logdist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long100kb[grep("Average_logdist", long100kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long100kb$value[long100kb$Transformation=="Distance"] <- long100kb$value[long100kb$Transformation=="Distance"]/1000000
-long100kb <- long100kb[grep("Average", long100kb$variable, invert = TRUE),]
-long100kb$variable <- factor(long100kb$variable)
-long100kb$Transformation <- factor(long100kb$Transformation)
-
-alldensity100kb_k562 <- ggplot(long100kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	#ylab("100 kb")+ 
-  ylim(0,.8)+
-  #ggtitle("K562") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-##Combined
-
-```{r}
-#alldistplots <- grid.arrange(distdensity10kb, logdistdensity10kb,
-#             distdensity25kb, logdistdensity25kb,
-#             distdensity50kb, logdistdensity50kb,
-#             distdensity100kb, logdistdensity100kb, ncol=2, nrow=4)
-
-alldistplots <- ggarrange(alldensity10kb,
-                          alldensity10kb_k562,
-                          alldensity25kb,
-                          alldensity25kb_k562,
-                          alldensity50kb,
-                          alldensity50kb_k562,
-                          alldensity100kb,
-                          alldensity100kb_k562, 
-          ncol=2, 
-          nrow=4,
-          #labels = c("A","", "B","", "C","", "D",""),
-          legend = "top",
-          common.legend = TRUE)
-
-annotate_figure(alldistplots,
-                bottom = text_grob("Distance to Nearest TAD Boundary \n (in millions of basepairs)", 
-                                color = "black", 
-                                face = "bold", 
-                                size = 15),
-                left = text_grob("Density", 
-                                 color = "black",
-                                 size = 15,
-                                 rot = 90))
+library(lattice)
+
 ```
@@
 ```
-
-#Evaluating Feature Engineering
-
-## PR Curves
-
-###GM12878
-
-####10kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####25kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####50kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####100kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-###K562
-
-####10kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####25kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####50kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####100kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-###Combined
-
-```{r}
-#10kb
-##None
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_None_10kb <- rbind.data.frame(prall_None$curve,
-                                prdist_None$curve,
-                                prop_None$curve,
-                                proc_None$curve,
-                                prall_None_k562$curve,
-                                prdist_None_k562$curve,
-                                prop_None_k562$curve,
-                                proc_None_k562$curve)
-names(prdata_None_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_None_10kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
-                           rep("Distance", dim(prdist_None$curve)[1]),
-                           rep("OP", dim(prop_None$curve)[1]),
-                           rep("OC", dim(proc_None$curve)[1]),
-                           rep("All", dim(prall_None_k562$curve)[1]),
-                           rep("Distance", dim(prdist_None_k562$curve)[1]),
-                           rep("OP", dim(prop_None_k562$curve)[1]),
-                           rep("OC", dim(proc_None_k562$curve)[1]))
-prdata_None_10kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
-                                      dim(prdist_None$curve)[1]+
-                                      dim(prop_None$curve)[1]+
-                                      dim(proc_None$curve)[1])),
-                    rep("K562", (dim(prall_None_k562$curve)[1]+
-                                      dim(prdist_None_k562$curve)[1]+
-                                      dim(prop_None_k562$curve)[1]+
-                                      dim(proc_None_k562$curve)[1])))
-prdata_None_10kb$Predictor <- factor(prdata_None_10kb$Predictor)
-prdata_None_10kb$CL <- factor(prdata_None_10kb$CL)
-
-prplot_None_10kb <- ggplot(prdata_None_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##RUS
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prdata_RUS_10kb <- rbind.data.frame(prall_RUS$curve,
-                                prdist_RUS$curve,
-                                prop_RUS$curve,
-                                proc_RUS$curve,
-                                prall_RUS_k562$curve,
-                                prdist_RUS_k562$curve,
-                                prop_RUS_k562$curve,
-                                proc_RUS_k562$curve)
-names(prdata_RUS_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_RUS_10kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
-                           rep("Distance", dim(prdist_RUS$curve)[1]),
-                           rep("OP", dim(prop_RUS$curve)[1]),
-                           rep("OC", dim(proc_RUS$curve)[1]),
-                           rep("All", dim(prall_RUS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
-                           rep("OP", dim(prop_RUS_k562$curve)[1]),
-                           rep("OC", dim(proc_RUS_k562$curve)[1]))
-prdata_RUS_10kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
-                                      dim(prdist_RUS$curve)[1]+
-                                      dim(prop_RUS$curve)[1]+
-                                      dim(proc_RUS$curve)[1])),
-                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
-                                      dim(prdist_RUS_k562$curve)[1]+
-                                      dim(prop_RUS_k562$curve)[1]+
-                                      dim(proc_RUS_k562$curve)[1])))
-prdata_RUS_10kb$Predictor <- factor(prdata_RUS_10kb$Predictor)
-prdata_RUS_10kb$CL <- factor(prdata_RUS_10kb$CL)
-
-prplot_RUS_10kb <- ggplot(prdata_RUS_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROS
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prdata_ROS_10kb <- rbind.data.frame(prall_ROS$curve,
-                                prdist_ROS$curve,
-                                prop_ROS$curve,
-                                proc_ROS$curve,
-                                prall_ROS_k562$curve,
-                                prdist_ROS_k562$curve,
-                                prop_ROS_k562$curve,
-                                proc_ROS_k562$curve)
-names(prdata_ROS_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROS_10kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
-                           rep("Distance", dim(prdist_ROS$curve)[1]),
-                           rep("OP", dim(prop_ROS$curve)[1]),
-                           rep("OC", dim(proc_ROS$curve)[1]),
-                           rep("All", dim(prall_ROS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
-                           rep("OP", dim(prop_ROS_k562$curve)[1]),
-                           rep("OC", dim(proc_ROS_k562$curve)[1]))
-prdata_ROS_10kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
-                                      dim(prdist_ROS$curve)[1]+
-                                      dim(prop_ROS$curve)[1]+
-                                      dim(proc_ROS$curve)[1])),
-                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
-                                      dim(prdist_ROS_k562$curve)[1]+
-                                      dim(prop_ROS_k562$curve)[1]+
-                                      dim(proc_ROS_k562$curve)[1])))
-prdata_ROS_10kb$Predictor <- factor(prdata_ROS_10kb$Predictor)
-prdata_ROS_10kb$CL <- factor(prdata_ROS_10kb$CL)
-
-prplot_ROS_10kb <- ggplot(prdata_ROS_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##SMOTE
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prdata_SMOTE_10kb <- rbind.data.frame(prall_SMOTE$curve,
-                                prdist_SMOTE$curve,
-                                prop_SMOTE$curve,
-                                proc_SMOTE$curve,
-                                prall_SMOTE_k562$curve,
-                                prdist_SMOTE_k562$curve,
-                                prop_SMOTE_k562$curve,
-                                proc_SMOTE_k562$curve)
-names(prdata_SMOTE_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_SMOTE_10kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
-                           rep("OP", dim(prop_SMOTE$curve)[1]),
-                           rep("OC", dim(proc_SMOTE$curve)[1]),
-                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
-                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
-                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
-prdata_SMOTE_10kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
-                                      dim(prdist_SMOTE$curve)[1]+
-                                      dim(prop_SMOTE$curve)[1]+
-                                      dim(proc_SMOTE$curve)[1])),
-                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
-                                      dim(prdist_SMOTE_k562$curve)[1]+
-                                      dim(prop_SMOTE_k562$curve)[1]+
-                                      dim(proc_SMOTE_k562$curve)[1])))
-prdata_SMOTE_10kb$Predictor <- factor(prdata_SMOTE_10kb$Predictor)
-prdata_SMOTE_10kb$CL <- factor(prdata_SMOTE_10kb$CL)
-
-prplot_SMOTE_10kb <- ggplot(prdata_SMOTE_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROSE
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prdata_ROSE_10kb <- rbind.data.frame(prall_ROSE$curve,
-                                prdist_ROSE$curve,
-                                prop_ROSE$curve,
-                                proc_ROSE$curve,
-                                prall_ROSE_k562$curve,
-                                prdist_ROSE_k562$curve,
-                                prop_ROSE_k562$curve,
-                                proc_ROSE_k562$curve)
-names(prdata_ROSE_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROSE_10kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE$curve)[1]),
-                           rep("OP", dim(prop_ROSE$curve)[1]),
-                           rep("OC", dim(proc_ROSE$curve)[1]),
-                           rep("All", dim(prall_ROSE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
-                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
-                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
-prdata_ROSE_10kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
-                                      dim(prdist_ROSE$curve)[1]+
-                                      dim(prop_ROSE$curve)[1]+
-                                      dim(proc_ROSE$curve)[1])),
-                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
-                                      dim(prdist_ROSE_k562$curve)[1]+
-                                      dim(prop_ROSE_k562$curve)[1]+
-                                      dim(proc_ROSE_k562$curve)[1])))
-prdata_ROSE_10kb$Predictor <- factor(prdata_ROSE_10kb$Predictor)
-prdata_ROSE_10kb$CL <- factor(prdata_ROSE_10kb$CL)
-
-prplot_ROSE_10kb <- ggplot(prdata_ROSE_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##Collecting 10kb plots
-ggarrange(prplot_None_10kb,
-          prplot_RUS_10kb,
-          prplot_ROS_10kb,
-          prplot_SMOTE_10kb,
-          prplot_ROSE_10kb,
-          nrow=3,ncol=2,
-          common.legend = TRUE, legend = "right")
-
-#######################################################################################
-
-#25kb
-##None
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_None_25kb <- rbind.data.frame(prall_None$curve,
-                                prdist_None$curve,
-                                prop_None$curve,
-                                proc_None$curve,
-                                prall_None_k562$curve,
-                                prdist_None_k562$curve,
-                                prop_None_k562$curve,
-                                proc_None_k562$curve)
-names(prdata_None_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_None_25kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
-                           rep("Distance", dim(prdist_None$curve)[1]),
-                           rep("OP", dim(prop_None$curve)[1]),
-                           rep("OC", dim(proc_None$curve)[1]),
-                           rep("All", dim(prall_None_k562$curve)[1]),
-                           rep("Distance", dim(prdist_None_k562$curve)[1]),
-                           rep("OP", dim(prop_None_k562$curve)[1]),
-                           rep("OC", dim(proc_None_k562$curve)[1]))
-prdata_None_25kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
-                                      dim(prdist_None$curve)[1]+
-                                      dim(prop_None$curve)[1]+
-                                      dim(proc_None$curve)[1])),
-                    rep("K562", (dim(prall_None_k562$curve)[1]+
-                                      dim(prdist_None_k562$curve)[1]+
-                                      dim(prop_None_k562$curve)[1]+
-                                      dim(proc_None_k562$curve)[1])))
-prdata_None_25kb$Predictor <- factor(prdata_None_25kb$Predictor)
-prdata_None_25kb$CL <- factor(prdata_None_25kb$CL)
-
-prplot_None_25kb <- ggplot(prdata_None_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##RUS
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prdata_RUS_25kb <- rbind.data.frame(prall_RUS$curve,
-                                prdist_RUS$curve,
-                                prop_RUS$curve,
-                                proc_RUS$curve,
-                                prall_RUS_k562$curve,
-                                prdist_RUS_k562$curve,
-                                prop_RUS_k562$curve,
-                                proc_RUS_k562$curve)
-names(prdata_RUS_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_RUS_25kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
-                           rep("Distance", dim(prdist_RUS$curve)[1]),
-                           rep("OP", dim(prop_RUS$curve)[1]),
-                           rep("OC", dim(proc_RUS$curve)[1]),
-                           rep("All", dim(prall_RUS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
-                           rep("OP", dim(prop_RUS_k562$curve)[1]),
-                           rep("OC", dim(proc_RUS_k562$curve)[1]))
-prdata_RUS_25kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
-                                      dim(prdist_RUS$curve)[1]+
-                                      dim(prop_RUS$curve)[1]+
-                                      dim(proc_RUS$curve)[1])),
-                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
-                                      dim(prdist_RUS_k562$curve)[1]+
-                                      dim(prop_RUS_k562$curve)[1]+
-                                      dim(proc_RUS_k562$curve)[1])))
-prdata_RUS_25kb$Predictor <- factor(prdata_RUS_25kb$Predictor)
-prdata_RUS_25kb$CL <- factor(prdata_RUS_25kb$CL)
-
-prplot_RUS_25kb <- ggplot(prdata_RUS_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROS
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prdata_ROS_25kb <- rbind.data.frame(prall_ROS$curve,
-                                prdist_ROS$curve,
-                                prop_ROS$curve,
-                                proc_ROS$curve,
-                                prall_ROS_k562$curve,
-                                prdist_ROS_k562$curve,
-                                prop_ROS_k562$curve,
-                                proc_ROS_k562$curve)
-names(prdata_ROS_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROS_25kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
-                           rep("Distance", dim(prdist_ROS$curve)[1]),
-                           rep("OP", dim(prop_ROS$curve)[1]),
-                           rep("OC", dim(proc_ROS$curve)[1]),
-                           rep("All", dim(prall_ROS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
-                           rep("OP", dim(prop_ROS_k562$curve)[1]),
-                           rep("OC", dim(proc_ROS_k562$curve)[1]))
-prdata_ROS_25kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
-                                      dim(prdist_ROS$curve)[1]+
-                                      dim(prop_ROS$curve)[1]+
-                                      dim(proc_ROS$curve)[1])),
-                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
-                                      dim(prdist_ROS_k562$curve)[1]+
-                                      dim(prop_ROS_k562$curve)[1]+
-                                      dim(proc_ROS_k562$curve)[1])))
-prdata_ROS_25kb$Predictor <- factor(prdata_ROS_25kb$Predictor)
-prdata_ROS_25kb$CL <- factor(prdata_ROS_25kb$CL)
-
-prplot_ROS_25kb <- ggplot(prdata_ROS_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##SMOTE
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prdata_SMOTE_25kb <- rbind.data.frame(prall_SMOTE$curve,
-                                prdist_SMOTE$curve,
-                                prop_SMOTE$curve,
-                                proc_SMOTE$curve,
-                                prall_SMOTE_k562$curve,
-                                prdist_SMOTE_k562$curve,
-                                prop_SMOTE_k562$curve,
-                                proc_SMOTE_k562$curve)
-names(prdata_SMOTE_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_SMOTE_25kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
-                           rep("OP", dim(prop_SMOTE$curve)[1]),
-                           rep("OC", dim(proc_SMOTE$curve)[1]),
-                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
-                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
-                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
-prdata_SMOTE_25kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
-                                      dim(prdist_SMOTE$curve)[1]+
-                                      dim(prop_SMOTE$curve)[1]+
-                                      dim(proc_SMOTE$curve)[1])),
-                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
-                                      dim(prdist_SMOTE_k562$curve)[1]+
-                                      dim(prop_SMOTE_k562$curve)[1]+
-                                      dim(proc_SMOTE_k562$curve)[1])))
-prdata_SMOTE_25kb$Predictor <- factor(prdata_SMOTE_25kb$Predictor)
-prdata_SMOTE_25kb$CL <- factor(prdata_SMOTE_25kb$CL)
-
-prplot_SMOTE_25kb <- ggplot(prdata_SMOTE_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROSE
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prdata_ROSE_25kb <- rbind.data.frame(prall_ROSE$curve,
-                                prdist_ROSE$curve,
-                                prop_ROSE$curve,
-                                proc_ROSE$curve,
-                                prall_ROSE_k562$curve,
-                                prdist_ROSE_k562$curve,
-                                prop_ROSE_k562$curve,
-                                proc_ROSE_k562$curve)
-names(prdata_ROSE_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROSE_25kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE$curve)[1]),
-                           rep("OP", dim(prop_ROSE$curve)[1]),
-                           rep("OC", dim(proc_ROSE$curve)[1]),
-                           rep("All", dim(prall_ROSE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
-                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
-                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
-prdata_ROSE_25kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
-                                      dim(prdist_ROSE$curve)[1]+
-                                      dim(prop_ROSE$curve)[1]+
-                                      dim(proc_ROSE$curve)[1])),
-                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
-                                      dim(prdist_ROSE_k562$curve)[1]+
-                                      dim(prop_ROSE_k562$curve)[1]+
-                                      dim(proc_ROSE_k562$curve)[1])))
-prdata_ROSE_25kb$Predictor <- factor(prdata_ROSE_25kb$Predictor)
-prdata_ROSE_25kb$CL <- factor(prdata_ROSE_25kb$CL)
-
-prplot_ROSE_25kb <- ggplot(prdata_ROSE_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-###############################################################################
-
-#50kb
-##None
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_None_50kb <- rbind.data.frame(prall_None$curve,
-                                prdist_None$curve,
-                                prop_None$curve,
-                                proc_None$curve,
-                                prall_None_k562$curve,
-                                prdist_None_k562$curve,
-                                prop_None_k562$curve,
-                                proc_None_k562$curve)
-names(prdata_None_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_None_50kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
-                           rep("Distance", dim(prdist_None$curve)[1]),
-                           rep("OP", dim(prop_None$curve)[1]),
-                           rep("OC", dim(proc_None$curve)[1]),
-                           rep("All", dim(prall_None_k562$curve)[1]),
-                           rep("Distance", dim(prdist_None_k562$curve)[1]),
-                           rep("OP", dim(prop_None_k562$curve)[1]),
-                           rep("OC", dim(proc_None_k562$curve)[1]))
-prdata_None_50kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
-                                      dim(prdist_None$curve)[1]+
-                                      dim(prop_None$curve)[1]+
-                                      dim(proc_None$curve)[1])),
-                    rep("K562", (dim(prall_None_k562$curve)[1]+
-                                      dim(prdist_None_k562$curve)[1]+
-                                      dim(prop_None_k562$curve)[1]+
-                                      dim(proc_None_k562$curve)[1])))
-prdata_None_50kb$Predictor <- factor(prdata_None_50kb$Predictor)
-prdata_None_50kb$CL <- factor(prdata_None_50kb$CL)
-
-prplot_None_50kb <- ggplot(prdata_None_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##RUS
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prdata_RUS_50kb <- rbind.data.frame(prall_RUS$curve,
-                                prdist_RUS$curve,
-                                prop_RUS$curve,
-                                proc_RUS$curve,
-                                prall_RUS_k562$curve,
-                                prdist_RUS_k562$curve,
-                                prop_RUS_k562$curve,
-                                proc_RUS_k562$curve)
-names(prdata_RUS_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_RUS_50kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
-                           rep("Distance", dim(prdist_RUS$curve)[1]),
-                           rep("OP", dim(prop_RUS$curve)[1]),
-                           rep("OC", dim(proc_RUS$curve)[1]),
-                           rep("All", dim(prall_RUS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
-                           rep("OP", dim(prop_RUS_k562$curve)[1]),
-                           rep("OC", dim(proc_RUS_k562$curve)[1]))
-prdata_RUS_50kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
-                                      dim(prdist_RUS$curve)[1]+
-                                      dim(prop_RUS$curve)[1]+
-                                      dim(proc_RUS$curve)[1])),
-                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
-                                      dim(prdist_RUS_k562$curve)[1]+
-                                      dim(prop_RUS_k562$curve)[1]+
-                                      dim(proc_RUS_k562$curve)[1])))
-prdata_RUS_50kb$Predictor <- factor(prdata_RUS_50kb$Predictor)
-prdata_RUS_50kb$CL <- factor(prdata_RUS_50kb$CL)
-
-prplot_RUS_50kb <- ggplot(prdata_RUS_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROS
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prdata_ROS_50kb <- rbind.data.frame(prall_ROS$curve,
-                                prdist_ROS$curve,
-                                prop_ROS$curve,
-                                proc_ROS$curve,
-                                prall_ROS_k562$curve,
-                                prdist_ROS_k562$curve,
-                                prop_ROS_k562$curve,
-                                proc_ROS_k562$curve)
-names(prdata_ROS_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROS_50kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
-                           rep("Distance", dim(prdist_ROS$curve)[1]),
-                           rep("OP", dim(prop_ROS$curve)[1]),
-                           rep("OC", dim(proc_ROS$curve)[1]),
-                           rep("All", dim(prall_ROS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
-                           rep("OP", dim(prop_ROS_k562$curve)[1]),
-                           rep("OC", dim(proc_ROS_k562$curve)[1]))
-prdata_ROS_50kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
-                                      dim(prdist_ROS$curve)[1]+
-                                      dim(prop_ROS$curve)[1]+
-                                      dim(proc_ROS$curve)[1])),
-                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
-                                      dim(prdist_ROS_k562$curve)[1]+
-                                      dim(prop_ROS_k562$curve)[1]+
-                                      dim(proc_ROS_k562$curve)[1])))
-prdata_ROS_50kb$Predictor <- factor(prdata_ROS_50kb$Predictor)
-prdata_ROS_50kb$CL <- factor(prdata_ROS_50kb$CL)
-
-prplot_ROS_50kb <- ggplot(prdata_ROS_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##SMOTE
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prdata_SMOTE_50kb <- rbind.data.frame(prall_SMOTE$curve,
-                                prdist_SMOTE$curve,
-                                prop_SMOTE$curve,
-                                proc_SMOTE$curve,
-                                prall_SMOTE_k562$curve,
-                                prdist_SMOTE_k562$curve,
-                                prop_SMOTE_k562$curve,
-                                proc_SMOTE_k562$curve)
-names(prdata_SMOTE_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_SMOTE_50kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
-                           rep("OP", dim(prop_SMOTE$curve)[1]),
-                           rep("OC", dim(proc_SMOTE$curve)[1]),
-                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
-                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
-                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
-prdata_SMOTE_50kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
-                                      dim(prdist_SMOTE$curve)[1]+
-                                      dim(prop_SMOTE$curve)[1]+
-                                      dim(proc_SMOTE$curve)[1])),
-                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
-                                      dim(prdist_SMOTE_k562$curve)[1]+
-                                      dim(prop_SMOTE_k562$curve)[1]+
-                                      dim(proc_SMOTE_k562$curve)[1])))
-prdata_SMOTE_50kb$Predictor <- factor(prdata_SMOTE_50kb$Predictor)
-prdata_SMOTE_50kb$CL <- factor(prdata_SMOTE_50kb$CL)
-
-prplot_SMOTE_50kb <- ggplot(prdata_SMOTE_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROSE
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prdata_ROSE_50kb <- rbind.data.frame(prall_ROSE$curve,
-                                prdist_ROSE$curve,
-                                prop_ROSE$curve,
-                                proc_ROSE$curve,
-                                prall_ROSE_k562$curve,
-                                prdist_ROSE_k562$curve,
-                                prop_ROSE_k562$curve,
-                                proc_ROSE_k562$curve)
-names(prdata_ROSE_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROSE_50kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE$curve)[1]),
-                           rep("OP", dim(prop_ROSE$curve)[1]),
-                           rep("OC", dim(proc_ROSE$curve)[1]),
-                           rep("All", dim(prall_ROSE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
-                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
-                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
-prdata_ROSE_50kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
-                                      dim(prdist_ROSE$curve)[1]+
-                                      dim(prop_ROSE$curve)[1]+
-                                      dim(proc_ROSE$curve)[1])),
-                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
-                                      dim(prdist_ROSE_k562$curve)[1]+
-                                      dim(prop_ROSE_k562$curve)[1]+
-                                      dim(proc_ROSE_k562$curve)[1])))
-prdata_ROSE_50kb$Predictor <- factor(prdata_ROSE_50kb$Predictor)
-prdata_ROSE_50kb$CL <- factor(prdata_ROSE_50kb$CL)
-
-prplot_ROSE_50kb <- ggplot(prdata_ROSE_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-###########################################################################
-
-#100kb
-##None
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_None_100kb <- rbind.data.frame(prall_None$curve,
-                                prdist_None$curve,
-                                prop_None$curve,
-                                proc_None$curve,
-                                prall_None_k562$curve,
-                                prdist_None_k562$curve,
-                                prop_None_k562$curve,
-                                proc_None_k562$curve)
-names(prdata_None_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_None_100kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
-                           rep("Distance", dim(prdist_None$curve)[1]),
-                           rep("OP", dim(prop_None$curve)[1]),
-                           rep("OC", dim(proc_None$curve)[1]),
-                           rep("All", dim(prall_None_k562$curve)[1]),
-                           rep("Distance", dim(prdist_None_k562$curve)[1]),
-                           rep("OP", dim(prop_None_k562$curve)[1]),
-                           rep("OC", dim(proc_None_k562$curve)[1]))
-prdata_None_100kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
-                                      dim(prdist_None$curve)[1]+
-                                      dim(prop_None$curve)[1]+
-                                      dim(proc_None$curve)[1])),
-                    rep("K562", (dim(prall_None_k562$curve)[1]+
-                                      dim(prdist_None_k562$curve)[1]+
-                                      dim(prop_None_k562$curve)[1]+
-                                      dim(proc_None_k562$curve)[1])))
-prdata_None_100kb$Predictor <- factor(prdata_None_100kb$Predictor)
-prdata_None_100kb$CL <- factor(prdata_None_100kb$CL)
-
-prplot_None_100kb <- ggplot(prdata_None_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##RUS
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prdata_RUS_100kb <- rbind.data.frame(prall_RUS$curve,
-                                prdist_RUS$curve,
-                                prop_RUS$curve,
-                                proc_RUS$curve,
-                                prall_RUS_k562$curve,
-                                prdist_RUS_k562$curve,
-                                prop_RUS_k562$curve,
-                                proc_RUS_k562$curve)
-names(prdata_RUS_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_RUS_100kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
-                           rep("Distance", dim(prdist_RUS$curve)[1]),
-                           rep("OP", dim(prop_RUS$curve)[1]),
-                           rep("OC", dim(proc_RUS$curve)[1]),
-                           rep("All", dim(prall_RUS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
-                           rep("OP", dim(prop_RUS_k562$curve)[1]),
-                           rep("OC", dim(proc_RUS_k562$curve)[1]))
-prdata_RUS_100kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
-                                      dim(prdist_RUS$curve)[1]+
-                                      dim(prop_RUS$curve)[1]+
-                                      dim(proc_RUS$curve)[1])),
-                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
-                                      dim(prdist_RUS_k562$curve)[1]+
-                                      dim(prop_RUS_k562$curve)[1]+
-                                      dim(proc_RUS_k562$curve)[1])))
-prdata_RUS_100kb$Predictor <- factor(prdata_RUS_100kb$Predictor)
-prdata_RUS_100kb$CL <- factor(prdata_RUS_100kb$CL)
-
-prplot_RUS_100kb <- ggplot(prdata_RUS_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROS
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prdata_ROS_100kb <- rbind.data.frame(prall_ROS$curve,
-                                prdist_ROS$curve,
-                                prop_ROS$curve,
-                                proc_ROS$curve,
-                                prall_ROS_k562$curve,
-                                prdist_ROS_k562$curve,
-                                prop_ROS_k562$curve,
-                                proc_ROS_k562$curve)
-names(prdata_ROS_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROS_100kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
-                           rep("Distance", dim(prdist_ROS$curve)[1]),
-                           rep("OP", dim(prop_ROS$curve)[1]),
-                           rep("OC", dim(proc_ROS$curve)[1]),
-                           rep("All", dim(prall_ROS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
-                           rep("OP", dim(prop_ROS_k562$curve)[1]),
-                           rep("OC", dim(proc_ROS_k562$curve)[1]))
-prdata_ROS_100kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
-                                      dim(prdist_ROS$curve)[1]+
-                                      dim(prop_ROS$curve)[1]+
-                                      dim(proc_ROS$curve)[1])),
-                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
-                                      dim(prdist_ROS_k562$curve)[1]+
-                                      dim(prop_ROS_k562$curve)[1]+
-                                      dim(proc_ROS_k562$curve)[1])))
-prdata_ROS_100kb$Predictor <- factor(prdata_ROS_100kb$Predictor)
-prdata_ROS_100kb$CL <- factor(prdata_ROS_100kb$CL)
-
-prplot_ROS_100kb <- ggplot(prdata_ROS_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##SMOTE
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prdata_SMOTE_100kb <- rbind.data.frame(prall_SMOTE$curve,
-                                prdist_SMOTE$curve,
-                                prop_SMOTE$curve,
-                                proc_SMOTE$curve,
-                                prall_SMOTE_k562$curve,
-                                prdist_SMOTE_k562$curve,
-                                prop_SMOTE_k562$curve,
-                                proc_SMOTE_k562$curve)
-names(prdata_SMOTE_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_SMOTE_100kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
-                           rep("OP", dim(prop_SMOTE$curve)[1]),
-                           rep("OC", dim(proc_SMOTE$curve)[1]),
-                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
-                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
-                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
-prdata_SMOTE_100kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
-                                      dim(prdist_SMOTE$curve)[1]+
-                                      dim(prop_SMOTE$curve)[1]+
-                                      dim(proc_SMOTE$curve)[1])),
-                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
-                                      dim(prdist_SMOTE_k562$curve)[1]+
-                                      dim(prop_SMOTE_k562$curve)[1]+
-                                      dim(proc_SMOTE_k562$curve)[1])))
-prdata_SMOTE_100kb$Predictor <- factor(prdata_SMOTE_100kb$Predictor)
-prdata_SMOTE_100kb$CL <- factor(prdata_SMOTE_100kb$CL)
-
-prplot_SMOTE_100kb <- ggplot(prdata_SMOTE_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROSE
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prdata_ROSE_100kb <- rbind.data.frame(prall_ROSE$curve,
-                                prdist_ROSE$curve,
-                                prop_ROSE$curve,
-                                proc_ROSE$curve,
-                                prall_ROSE_k562$curve,
-                                prdist_ROSE_k562$curve,
-                                prop_ROSE_k562$curve,
-                                proc_ROSE_k562$curve)
-names(prdata_ROSE_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROSE_100kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE$curve)[1]),
-                           rep("OP", dim(prop_ROSE$curve)[1]),
-                           rep("OC", dim(proc_ROSE$curve)[1]),
-                           rep("All", dim(prall_ROSE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
-                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
-                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
-prdata_ROSE_100kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
-                                      dim(prdist_ROSE$curve)[1]+
-                                      dim(prop_ROSE$curve)[1]+
-                                      dim(proc_ROSE$curve)[1])),
-                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
-                                      dim(prdist_ROSE_k562$curve)[1]+
-                                      dim(prop_ROSE_k562$curve)[1]+
-                                      dim(proc_ROSE_k562$curve)[1])))
-prdata_ROSE_100kb$Predictor <- factor(prdata_ROSE_100kb$Predictor)
-prdata_ROSE_100kb$CL <- factor(prdata_ROSE_100kb$CL)
-
-prplot_ROSE_100kb <- ggplot(prdata_ROSE_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-###############################################################
-
-##Collecting 25kb, 50kb, and 100kb plots
-
-ggarrange(prplot_None_25kb, prplot_None_50kb, prplot_None_100kb,
-          prplot_RUS_25kb, prplot_RUS_50kb, prplot_RUS_100kb,
-          prplot_ROS_25kb, prplot_ROS_50kb, prplot_ROS_100kb,
-          prplot_SMOTE_25kb, prplot_SMOTE_50kb, prplot_SMOTE_100kb,
-          prplot_ROSE_25kb, prplot_ROSE_50kb, prplot_ROSE_100kb,
-          ncol=3,
-          nrow=5,
-          common.legend = TRUE,
-          legend = "right")
-```
-
-##Tables of AUPRC
-
-```{r}
-
-gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-K562_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-K562_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-K562_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-K562_10kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-K562_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-K562_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-K562_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-K562_25kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-K562_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-K562_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-K562_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-K562_50kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-K562_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-K562_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-K562_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-K562_100kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-gm12878_10kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-gm12878_25kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-gm12878_50kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-gm12878_100kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-K562_10kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-K562_10kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-K562_10kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-K562_10kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-K562_10kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-K562_25kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-K562_25kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-K562_25kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-K562_25kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-K562_25kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-K562_50kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-K562_50kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-K562_50kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-K562_50kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-K562_50kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-K562_100kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-K562_100kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-K562_100kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-K562_100kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-K562_100kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-gm12878_10kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-gm12878_25kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-gm12878_50kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-gm12878_100kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-K562_10kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-K562_10kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-K562_10kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-K562_10kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-K562_10kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-K562_25kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-K562_25kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-K562_25kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-K562_25kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-K562_25kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-K562_50kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-K562_50kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-K562_50kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-K562_50kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-K562_50kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-K562_100kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-K562_100kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-K562_100kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-K562_100kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-K562_100kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-gm12878_10kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-gm12878_25kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-gm12878_50kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-gm12878_100kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-K562_10kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-K562_10kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-K562_10kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-K562_10kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-K562_10kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-K562_25kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-K562_25kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-K562_25kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-K562_25kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-K562_25kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-K562_50kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-K562_50kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-K562_50kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-K562_50kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-K562_50kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-K562_100kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-K562_100kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-K562_100kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-K562_100kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-K562_100kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-prcurvetable <- data.frame(CL=c(rep("GM12878", 20), rep("K562", 20)),
-                           Resolution=c(c(rep("10 kb", 5), 
-                                        rep("25 kb", 5),
-                                        rep("50 kb", 5),
-                                        rep("100 kb", 5)),
-                                        c(rep("10 kb", 5), 
-                                        rep("25 kb", 5),
-                                        rep("50 kb", 5),
-                                        rep("100 kb", 5))),
-                           ReSampling=rep(c("None",
-                                        "RUS",
-                                        "ROS",
-                                        "SMOTE",
-                                        "ROSE"),8))
-prcurvetable$OC <- c(gm12878_10kb_none_oc,
-gm12878_10kb_rus_oc,
-gm12878_10kb_ros_oc,
-gm12878_10kb_smote_oc,
-gm12878_10kb_rose_oc,
-gm12878_25kb_none_oc,
-gm12878_25kb_rus_oc,
-gm12878_25kb_ros_oc,
-gm12878_25kb_smote_oc,
-gm12878_25kb_rose_oc,
-gm12878_50kb_none_oc,
-gm12878_50kb_rus_oc,
-gm12878_50kb_ros_oc,
-gm12878_50kb_smote_oc,
-gm12878_50kb_rose_oc,
-gm12878_100kb_none_oc,
-gm12878_100kb_rus_oc,
-gm12878_100kb_ros_oc,
-gm12878_100kb_smote_oc,
-gm12878_100kb_rose_oc,
-K562_10kb_none_oc,
-K562_10kb_rus_oc,
-K562_10kb_ros_oc,
-K562_10kb_smote_oc,
-K562_10kb_rose_oc,
-K562_25kb_none_oc,
-K562_25kb_rus_oc,
-K562_25kb_ros_oc,
-K562_25kb_smote_oc,
-K562_25kb_rose_oc,
-K562_50kb_none_oc,
-K562_50kb_rus_oc,
-K562_50kb_ros_oc,
-K562_50kb_smote_oc,
-K562_50kb_rose_oc,
-K562_100kb_none_oc,
-K562_100kb_rus_oc,
-K562_100kb_ros_oc,
-K562_100kb_smote_oc,
-K562_100kb_rose_oc)
-
-prcurvetable$OP <- c(gm12878_10kb_none_OP,
-gm12878_10kb_rus_OP,
-gm12878_10kb_ros_OP,
-gm12878_10kb_smote_OP,
-gm12878_10kb_rose_OP,
-gm12878_25kb_none_OP,
-gm12878_25kb_rus_OP,
-gm12878_25kb_ros_OP,
-gm12878_25kb_smote_OP,
-gm12878_25kb_rose_OP,
-gm12878_50kb_none_OP,
-gm12878_50kb_rus_OP,
-gm12878_50kb_ros_OP,
-gm12878_50kb_smote_OP,
-gm12878_50kb_rose_OP,
-gm12878_100kb_none_OP,
-gm12878_100kb_rus_OP,
-gm12878_100kb_ros_OP,
-gm12878_100kb_smote_OP,
-gm12878_100kb_rose_OP,
-K562_10kb_none_OP,
-K562_10kb_rus_OP,
-K562_10kb_ros_OP,
-K562_10kb_smote_OP,
-K562_10kb_rose_OP,
-K562_25kb_none_OP,
-K562_25kb_rus_OP,
-K562_25kb_ros_OP,
-K562_25kb_smote_OP,
-K562_25kb_rose_OP,
-K562_50kb_none_OP,
-K562_50kb_rus_OP,
-K562_50kb_ros_OP,
-K562_50kb_smote_OP,
-K562_50kb_rose_OP,
-K562_100kb_none_OP,
-K562_100kb_rus_OP,
-K562_100kb_ros_OP,
-K562_100kb_smote_OP,
-K562_100kb_rose_OP)
-
-prcurvetable$Distance <- c(gm12878_10kb_none_Distance,
-gm12878_10kb_rus_Distance,
-gm12878_10kb_ros_Distance,
-gm12878_10kb_smote_Distance,
-gm12878_10kb_rose_Distance,
-gm12878_25kb_none_Distance,
-gm12878_25kb_rus_Distance,
-gm12878_25kb_ros_Distance,
-gm12878_25kb_smote_Distance,
-gm12878_25kb_rose_Distance,
-gm12878_50kb_none_Distance,
-gm12878_50kb_rus_Distance,
-gm12878_50kb_ros_Distance,
-gm12878_50kb_smote_Distance,
-gm12878_50kb_rose_Distance,
-gm12878_100kb_none_Distance,
-gm12878_100kb_rus_Distance,
-gm12878_100kb_ros_Distance,
-gm12878_100kb_smote_Distance,
-gm12878_100kb_rose_Distance,
-K562_10kb_none_Distance,
-K562_10kb_rus_Distance,
-K562_10kb_ros_Distance,
-K562_10kb_smote_Distance,
-K562_10kb_rose_Distance,
-K562_25kb_none_Distance,
-K562_25kb_rus_Distance,
-K562_25kb_ros_Distance,
-K562_25kb_smote_Distance,
-K562_25kb_rose_Distance,
-K562_50kb_none_Distance,
-K562_50kb_rus_Distance,
-K562_50kb_ros_Distance,
-K562_50kb_smote_Distance,
-K562_50kb_rose_Distance,
-K562_100kb_none_Distance,
-K562_100kb_rus_Distance,
-K562_100kb_ros_Distance,
-K562_100kb_smote_Distance,
-K562_100kb_rose_Distance)
-
-prcurvetable$All <- c(gm12878_10kb_none_all,
-gm12878_10kb_rus_all,
-gm12878_10kb_ros_all,
-gm12878_10kb_smote_all,
-gm12878_10kb_rose_all,
-gm12878_25kb_none_all,
-gm12878_25kb_rus_all,
-gm12878_25kb_ros_all,
-gm12878_25kb_smote_all,
-gm12878_25kb_rose_all,
-gm12878_50kb_none_all,
-gm12878_50kb_rus_all,
-gm12878_50kb_ros_all,
-gm12878_50kb_smote_all,
-gm12878_50kb_rose_all,
-gm12878_100kb_none_all,
-gm12878_100kb_rus_all,
-gm12878_100kb_ros_all,
-gm12878_100kb_smote_all,
-gm12878_100kb_rose_all,
-K562_10kb_none_all,
-K562_10kb_rus_all,
-K562_10kb_ros_all,
-K562_10kb_smote_all,
-K562_10kb_rose_all,
-K562_25kb_none_all,
-K562_25kb_rus_all,
-K562_25kb_ros_all,
-K562_25kb_smote_all,
-K562_25kb_rose_all,
-K562_50kb_none_all,
-K562_50kb_rus_all,
-K562_50kb_ros_all,
-K562_50kb_smote_all,
-K562_50kb_rose_all,
-K562_100kb_none_all,
-K562_100kb_rus_all,
-K562_100kb_ros_all,
-K562_100kb_smote_all,
-K562_100kb_rose_all)
-
-```
-
-## RFE
-
-###10kb
-
-```{r}
-rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-#None
-resampdata_None_10kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
-resampdata_None_10kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
-                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
-
-rfeplot_None_10kb <- ggplot(resampdata_None_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,.5)
-
-#RUS
-resampdata_RUS_10kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
-resampdata_RUS_10kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
-
-rfeplot_RUS_10kb <- ggplot(resampdata_RUS_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROS
-resampdata_ROS_10kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
-resampdata_ROS_10kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
-
-rfeplot_ROS_10kb <- ggplot(resampdata_ROS_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#SMOTE
-resampdata_SMOTE_10kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
-resampdata_SMOTE_10kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
-
-rfeplot_SMOTE_10kb <- ggplot(resampdata_SMOTE_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROSE
-resampdata_ROSE_10kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
-resampdata_ROSE_10kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
-
-rfeplot_ROSE_10kb <- ggplot(resampdata_ROSE_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#Combining 10 kb plots
-ggarrange(rfeplot_None_10kb,
-          rfeplot_RUS_10kb,
-          rfeplot_ROS_10kb,
-          rfeplot_SMOTE_10kb,
-          rfeplot_ROSE_10kb,
-          nrow = 3,
-          ncol = 2,
-          common.legend = TRUE,
-          legend = "right")
-
-```
-
-###25kb
-
-```{r}
-rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-#None
-resampdata_None_25kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
-resampdata_None_25kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
-                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
-
-rfeplot_None_25kb <- ggplot(resampdata_None_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,.5)
-
-#RUS
-resampdata_RUS_25kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
-resampdata_RUS_25kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
-
-rfeplot_RUS_25kb <- ggplot(resampdata_RUS_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROS
-resampdata_ROS_25kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
-resampdata_ROS_25kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
-
-rfeplot_ROS_25kb <- ggplot(resampdata_ROS_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#SMOTE
-resampdata_SMOTE_25kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
-resampdata_SMOTE_25kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
-
-rfeplot_SMOTE_25kb <- ggplot(resampdata_SMOTE_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROSE
-resampdata_ROSE_25kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
-resampdata_ROSE_25kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
-
-rfeplot_ROSE_25kb <- ggplot(resampdata_ROSE_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-```
-
-###50kb
-
-```{r}
-rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-#None
-resampdata_None_50kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
-resampdata_None_50kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
-                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
-
-rfeplot_None_50kb <- ggplot(resampdata_None_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,.5)
-
-#RUS
-resampdata_RUS_50kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
-resampdata_RUS_50kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
-
-rfeplot_RUS_50kb <- ggplot(resampdata_RUS_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROS
-resampdata_ROS_50kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
-resampdata_ROS_50kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
-
-rfeplot_ROS_50kb <- ggplot(resampdata_ROS_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#SMOTE
-resampdata_SMOTE_50kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
-resampdata_SMOTE_50kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
-
-rfeplot_SMOTE_50kb <- ggplot(resampdata_SMOTE_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROSE
-resampdata_ROSE_50kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
-resampdata_ROSE_50kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
-
-rfeplot_ROSE_50kb <- ggplot(resampdata_ROSE_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-```
-
-###100kb
-
-```{r}
-rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-#None
-resampdata_None_100kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
-resampdata_None_100kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
-                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
-
-rfeplot_None_100kb <- ggplot(resampdata_None_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,.5)
-
-#RUS
-resampdata_RUS_100kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
-resampdata_RUS_100kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
-
-rfeplot_RUS_100kb <- ggplot(resampdata_RUS_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROS
-resampdata_ROS_100kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
-resampdata_ROS_100kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
-
-rfeplot_ROS_100kb <- ggplot(resampdata_ROS_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#SMOTE
-resampdata_SMOTE_100kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
-resampdata_SMOTE_100kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
-
-rfeplot_SMOTE_100kb <- ggplot(resampdata_SMOTE_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROSE
-resampdata_ROSE_100kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
-resampdata_ROSE_100kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
-
-rfeplot_ROSE_100kb <- ggplot(resampdata_ROSE_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-```
-
-### Combined
-
-```{r}
-
-ggarrange(rfeplot_None_25kb, rfeplot_None_50kb, rfeplot_None_100kb,
-          rfeplot_RUS_25kb, rfeplot_RUS_50kb, rfeplot_RUS_100kb,
-          rfeplot_ROS_25kb, rfeplot_ROS_50kb, rfeplot_ROS_100kb,
-          rfeplot_SMOTE_25kb, rfeplot_SMOTE_50kb, rfeplot_SMOTE_100kb,
-          rfeplot_ROSE_25kb, rfeplot_ROSE_50kb, rfeplot_ROSE_100kb,
-          nrow = 5,
-          ncol = 3,
-          common.legend = TRUE,
-          legend = "right")
-
-```
-
-#Barplots of performance metrics for models with distance-type predictors
-
-##10kb
-
-```{r}
-#GM12878
-
-##None
-rfperf_gm12878_10kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_10kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_10kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_10kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_gm12878_10kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-#K562
-
-##None
-rfperf_K562_10kb_none <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_10kb_rus <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_10kb_ros <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_10kb_smote <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_K562_10kb_rose <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-all10kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all10kbresults$Performance <- c(round(rfperf_gm12878_10kb_none[9,2],2),
-                                round(rfperf_gm12878_10kb_none[19,2],2),
-                                round(rfperf_gm12878_10kb_none[16,2],2),
-                                round(rfperf_gm12878_10kb_none[15,2],2),
-                                round(rfperf_K562_10kb_none[9,2],2),
-                                round(rfperf_K562_10kb_none[19,2],2),
-                                round(rfperf_K562_10kb_none[16,2],2),
-                                round(rfperf_K562_10kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_10kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_rus[15,]),2),
-                                round(mean(rfperf_K562_10kb_rus[9,]),2),
-                                round(mean(rfperf_K562_10kb_rus[19,]),2),
-                                round(mean(rfperf_K562_10kb_rus[16,]),2),
-                                round(mean(rfperf_K562_10kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[15,]),2),
-                                round(mean(rfperf_K562_10kb_ros[9,]),2),
-                                round(mean(rfperf_K562_10kb_ros[19,]),2),
-                                round(mean(rfperf_K562_10kb_ros[16,]),2),
-                                round(mean(rfperf_K562_10kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[15,]),2),
-                                round(mean(rfperf_K562_10kb_smote[9,]),2),
-                                round(mean(rfperf_K562_10kb_smote[19,]),2),
-                                round(mean(rfperf_K562_10kb_smote[16,]),2),
-                                round(mean(rfperf_K562_10kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[15,]),2),
-                                round(mean(rfperf_K562_10kb_rose[9,]),2),
-                                round(mean(rfperf_K562_10kb_rose[19,]),2),
-                                round(mean(rfperf_K562_10kb_rose[16,]),2),
-                                round(mean(rfperf_K562_10kb_rose[15,]),2))
-
-all10kbresults$Resampling <- factor(all10kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all10kbresults$CL <- factor(all10kbresults$CL, levels=c("GM12878", "K562"))
-all10kbresults$Metric <- factor(all10kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
-
-none10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="None"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rus10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="RUS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-ros10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="ROS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-smote10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="SMOTE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rose10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="ROSE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-######################################################################
-
-#comparing only f1 and mcc
-
-f1mcc10kbplot <- ggplot(all10kbresults[which(all10kbresults$Metric=="F1-Score" |
-                                               all10kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=CL)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-##25kb
-
-```{r}
-#GM12878
-
-##None
-rfperf_gm12878_25kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_25kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_25kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_25kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_gm12878_25kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-#K562
-
-##None
-rfperf_K562_25kb_none <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_25kb_rus <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_25kb_ros <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_25kb_smote <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_K562_25kb_rose <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-all25kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all25kbresults$Performance <- c(round(rfperf_gm12878_25kb_none[9,2],2),
-                                round(rfperf_gm12878_25kb_none[19,2],2),
-                                round(rfperf_gm12878_25kb_none[16,2],2),
-                                round(rfperf_gm12878_25kb_none[15,2],2),
-                                round(rfperf_K562_25kb_none[9,2],2),
-                                round(rfperf_K562_25kb_none[19,2],2),
-                                round(rfperf_K562_25kb_none[16,2],2),
-                                round(rfperf_K562_25kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_25kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_rus[15,]),2),
-                                round(mean(rfperf_K562_25kb_rus[9,]),2),
-                                round(mean(rfperf_K562_25kb_rus[19,]),2),
-                                round(mean(rfperf_K562_25kb_rus[16,]),2),
-                                round(mean(rfperf_K562_25kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[15,]),2),
-                                round(mean(rfperf_K562_25kb_ros[9,]),2),
-                                round(mean(rfperf_K562_25kb_ros[19,]),2),
-                                round(mean(rfperf_K562_25kb_ros[16,]),2),
-                                round(mean(rfperf_K562_25kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[15,]),2),
-                                round(mean(rfperf_K562_25kb_smote[9,]),2),
-                                round(mean(rfperf_K562_25kb_smote[19,]),2),
-                                round(mean(rfperf_K562_25kb_smote[16,]),2),
-                                round(mean(rfperf_K562_25kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[15,]),2),
-                                round(mean(rfperf_K562_25kb_rose[9,]),2),
-                                round(mean(rfperf_K562_25kb_rose[19,]),2),
-                                round(mean(rfperf_K562_25kb_rose[16,]),2),
-                                round(mean(rfperf_K562_25kb_rose[15,]),2))
-
-all25kbresults$Resampling <- factor(all25kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all25kbresults$CL <- factor(all25kbresults$CL, levels=c("GM12878", "K562"))
-all25kbresults$Metric <- factor(all25kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
-
-none25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="None"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rus25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="RUS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-ros25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="ROS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-smote25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="SMOTE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rose25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="ROSE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-######################################################################
-
-#comparing only f1 and mcc
-
-f1mcc25kbplot <- ggplot(all25kbresults[which(all25kbresults$Metric=="F1-Score" |
-                                               all25kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=CL)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-##50kb
-
-```{r}
-#GM12878
-
-##None
-rfperf_gm12878_50kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_50kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_50kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_50kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_gm12878_50kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-#K562
-
-##None
-rfperf_K562_50kb_none <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_50kb_rus <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_50kb_ros <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_50kb_smote <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_K562_50kb_rose <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-all50kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all50kbresults$Performance <- c(round(rfperf_gm12878_50kb_none[9,2],2),
-                                round(rfperf_gm12878_50kb_none[19,2],2),
-                                round(rfperf_gm12878_50kb_none[16,2],2),
-                                round(rfperf_gm12878_50kb_none[15,2],2),
-                                round(rfperf_K562_50kb_none[9,2],2),
-                                round(rfperf_K562_50kb_none[19,2],2),
-                                round(rfperf_K562_50kb_none[16,2],2),
-                                round(rfperf_K562_50kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_50kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_rus[15,]),2),
-                                round(mean(rfperf_K562_50kb_rus[9,]),2),
-                                round(mean(rfperf_K562_50kb_rus[19,]),2),
-                                round(mean(rfperf_K562_50kb_rus[16,]),2),
-                                round(mean(rfperf_K562_50kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[15,]),2),
-                                round(mean(rfperf_K562_50kb_ros[9,]),2),
-                                round(mean(rfperf_K562_50kb_ros[19,]),2),
-                                round(mean(rfperf_K562_50kb_ros[16,]),2),
-                                round(mean(rfperf_K562_50kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[15,]),2),
-                                round(mean(rfperf_K562_50kb_smote[9,]),2),
-                                round(mean(rfperf_K562_50kb_smote[19,]),2),
-                                round(mean(rfperf_K562_50kb_smote[16,]),2),
-                                round(mean(rfperf_K562_50kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[15,]),2),
-                                round(mean(rfperf_K562_50kb_rose[9,]),2),
-                                round(mean(rfperf_K562_50kb_rose[19,]),2),
-                                round(mean(rfperf_K562_50kb_rose[16,]),2),
-                                round(mean(rfperf_K562_50kb_rose[15,]),2))
-
-all50kbresults$Resampling <- factor(all50kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all50kbresults$CL <- factor(all50kbresults$CL, levels=c("GM12878", "K562"))
-all50kbresults$Metric <- factor(all50kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
-
-none50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="None"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rus50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="RUS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-ros50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="ROS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-smote50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="SMOTE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rose50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="ROSE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-######################################################################
-
-#comparing only f1 and mcc
-
-f1mcc50kbplot <- ggplot(all50kbresults[which(all50kbresults$Metric=="F1-Score" |
-                                               all50kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=CL)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-##100kb
-
-```{r}
-#GM12878
-
-##None
-rfperf_gm12878_100kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_100kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_100kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_100kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_gm12878_100kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-#K562
-
-##None
-rfperf_K562_100kb_none <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_100kb_rus <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_100kb_ros <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_100kb_smote <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_K562_100kb_rose <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-all100kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all100kbresults$Performance <- c(round(rfperf_gm12878_100kb_none[9,2],2),
-                                round(rfperf_gm12878_100kb_none[19,2],2),
-                                round(rfperf_gm12878_100kb_none[16,2],2),
-                                round(rfperf_gm12878_100kb_none[15,2],2),
-                                round(rfperf_K562_100kb_none[9,2],2),
-                                round(rfperf_K562_100kb_none[19,2],2),
-                                round(rfperf_K562_100kb_none[16,2],2),
-                                round(rfperf_K562_100kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_100kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_rus[15,]),2),
-                                round(mean(rfperf_K562_100kb_rus[9,]),2),
-                                round(mean(rfperf_K562_100kb_rus[19,]),2),
-                                round(mean(rfperf_K562_100kb_rus[16,]),2),
-                                round(mean(rfperf_K562_100kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[15,]),2),
-                                round(mean(rfperf_K562_100kb_ros[9,]),2),
-                                round(mean(rfperf_K562_100kb_ros[19,]),2),
-                                round(mean(rfperf_K562_100kb_ros[16,]),2),
-                                round(mean(rfperf_K562_100kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[15,]),2),
-                                round(mean(rfperf_K562_100kb_smote[9,]),2),
-                                round(mean(rfperf_K562_100kb_smote[19,]),2),
-                                round(mean(rfperf_K562_100kb_smote[16,]),2),
-                                round(mean(rfperf_K562_100kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[15,]),2),
-                                round(mean(rfperf_K562_100kb_rose[9,]),2),
-                                round(mean(rfperf_K562_100kb_rose[19,]),2),
-                                round(mean(rfperf_K562_100kb_rose[16,]),2),
-                                round(mean(rfperf_K562_100kb_rose[15,]),2))
-
-all100kbresults$Resampling <- factor(all100kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all100kbresults$CL <- factor(all100kbresults$CL, levels=c("GM12878", "K562"))
-all100kbresults$Metric <- factor(all100kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
-
-none100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="None"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rus100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="RUS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-ros100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="ROS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-smote100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="SMOTE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rose100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="ROSE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-######################################################################
-
-#comparing only f1 and mcc
-
-f1mcc100kbplot <- ggplot(all100kbresults[which(all100kbresults$Metric=="F1-Score" |
-                                               all100kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=CL)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-#Table of model performances
-
-```{r}
-
-performancetab <- data.frame(Performance = c(rep("F1-Score", 10),
-                                             rep("MCC", 10)),
-                             Resampling = rep(c("None",
-                                                "None",
-                                                "RUS",
-                                                "RUS",
-                                                "ROS",
-                                                "ROS",
-                                                "SMOTE",
-                                                "SMOTE",
-                                                "ROSE",
-                                                "ROSE"),2),
-                             CL = rep(c("GM12878", "K562"), 10)
-                             )
-
-performancetab$kb10 <- c(rfperf_gm12878_10kb_none[16,2],
-                         rfperf_K562_10kb_none[16,2],
-                         mean(rfperf_gm12878_10kb_rus[16,]),
-                         mean(rfperf_K562_10kb_rus[16,]),
-                         mean(rfperf_gm12878_10kb_ros[16,]),
-                         mean(rfperf_K562_10kb_ros[16,]),
-                         mean(rfperf_gm12878_10kb_smote[16,]),
-                         mean(rfperf_K562_10kb_smote[16,]),
-                         mean(rfperf_gm12878_10kb_rose[16,]),
-                         mean(rfperf_K562_10kb_rose[16,]),
-                         rfperf_gm12878_10kb_none[15,2],
-                         rfperf_K562_10kb_none[15,2],
-                         mean(rfperf_gm12878_10kb_rus[15,]),
-                         mean(rfperf_K562_10kb_rus[15,]),
-                         mean(rfperf_gm12878_10kb_ros[15,]),
-                         mean(rfperf_K562_10kb_ros[15,]),
-                         mean(rfperf_gm12878_10kb_smote[15,]),
-                         mean(rfperf_K562_10kb_smote[15,]),
-                         mean(rfperf_gm12878_10kb_rose[15,]),
-                         mean(rfperf_K562_10kb_rose[15,]))
-
-performancetab$kb25 <- c(rfperf_gm12878_25kb_none[16,2],
-                         rfperf_K562_25kb_none[16,2],
-                         mean(rfperf_gm12878_25kb_rus[16,]),
-                         mean(rfperf_K562_25kb_rus[16,]),
-                         mean(rfperf_gm12878_25kb_ros[16,]),
-                         mean(rfperf_K562_25kb_ros[16,]),
-                         mean(rfperf_gm12878_25kb_smote[16,]),
-                         mean(rfperf_K562_25kb_smote[16,]),
-                         mean(rfperf_gm12878_25kb_rose[16,]),
-                         mean(rfperf_K562_25kb_rose[16,]),
-                         rfperf_gm12878_25kb_none[15,2],
-                         rfperf_K562_25kb_none[15,2],
-                         mean(rfperf_gm12878_25kb_rus[15,]),
-                         mean(rfperf_K562_25kb_rus[15,]),
-                         mean(rfperf_gm12878_25kb_ros[15,]),
-                         mean(rfperf_K562_25kb_ros[15,]),
-                         mean(rfperf_gm12878_25kb_smote[15,]),
-                         mean(rfperf_K562_25kb_smote[15,]),
-                         mean(rfperf_gm12878_25kb_rose[15,]),
-                         mean(rfperf_K562_25kb_rose[15,]))
-
-performancetab$kb50 <- c(rfperf_gm12878_50kb_none[16,2],
-                         rfperf_K562_50kb_none[16,2],
-                         mean(rfperf_gm12878_50kb_rus[16,]),
-                         mean(rfperf_K562_50kb_rus[16,]),
-                         mean(rfperf_gm12878_50kb_ros[16,]),
-                         mean(rfperf_K562_50kb_ros[16,]),
-                         mean(rfperf_gm12878_50kb_smote[16,]),
-                         mean(rfperf_K562_50kb_smote[16,]),
-                         mean(rfperf_gm12878_50kb_rose[16,]),
-                         mean(rfperf_K562_50kb_rose[16,]),
-                         rfperf_gm12878_50kb_none[15,2],
-                         rfperf_K562_50kb_none[15,2],
-                         mean(rfperf_gm12878_50kb_rus[15,]),
-                         mean(rfperf_K562_50kb_rus[15,]),
-                         mean(rfperf_gm12878_50kb_ros[15,]),
-                         mean(rfperf_K562_50kb_ros[15,]),
-                         mean(rfperf_gm12878_50kb_smote[15,]),
-                         mean(rfperf_K562_50kb_smote[15,]),
-                         mean(rfperf_gm12878_50kb_rose[15,]),
-                         mean(rfperf_K562_50kb_rose[15,]))
-
-performancetab$kb100 <- c(rfperf_gm12878_100kb_none[16,2],
-                         rfperf_K562_100kb_none[16,2],
-                         mean(rfperf_gm12878_100kb_rus[16,]),
-                         mean(rfperf_K562_100kb_rus[16,]),
-                         mean(rfperf_gm12878_100kb_ros[16,]),
-                         mean(rfperf_K562_100kb_ros[16,]),
-                         mean(rfperf_gm12878_100kb_smote[16,]),
-                         mean(rfperf_K562_100kb_smote[16,]),
-                         mean(rfperf_gm12878_100kb_rose[16,]),
-                         mean(rfperf_K562_100kb_rose[16,]),
-                         rfperf_gm12878_100kb_none[15,2],
-                         rfperf_K562_100kb_none[15,2],
-                         mean(rfperf_gm12878_100kb_rus[15,]),
-                         mean(rfperf_K562_100kb_rus[15,]),
-                         mean(rfperf_gm12878_100kb_ros[15,]),
-                         mean(rfperf_K562_100kb_ros[15,]),
-                         mean(rfperf_gm12878_100kb_smote[15,]),
-                         mean(rfperf_K562_100kb_smote[15,]),
-                         mean(rfperf_gm12878_100kb_rose[15,]),
-                         mean(rfperf_K562_100kb_rose[15,]))
-
-performancetab[,4:7] <- round(performancetab[,4:7], 3)
-```
-
-#Variable Importance Plots for distance predictors with ENET reduction
-
-##5kb
-###Random Under-Sampling
-```{r}
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/5kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf5kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf5kb <- rf5kb[order(rf5kb$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf5kb$Importance
-Labels <- as.character(rf5kb$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.5kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.5kb$Feature <- as.character(varimp.rf.df.5kb$Feature)							 
-varimp.rf.df.5kb <-varimp.rf.df.5kb[order(varimp.rf.df.5kb$Importance),]
-varimp.rf.df.5kb <- varimp.rf.df.5kb[(dim(varimp.rf.df.5kb)[1]-14):dim(varimp.rf.df.5kb)[1],]
-varimp.rf.df.5kb$Feature <- factor(varimp.rf.df.5kb$Feature,
-                                     levels=as.character(varimp.rf.df.5kb$Feature))
-
-p.rf.5kb <- ggplot(varimp.rf.df.5kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(A)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="red") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-  ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/5kb/p.rf.5kb.png")
-```
-##25kb
-###Random Under-Sampling
-```{r}
-  rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/25kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf <- rf[order(rf$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf$Importance
-Labels <- as.character(rf$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.25kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.25kb$Feature <- as.character(varimp.rf.df.25kb$Feature)							 
-varimp.rf.df.25kb <-varimp.rf.df.25kb[order(varimp.rf.df.25kb$Importance),]
-varimp.rf.df.25kb <- varimp.rf.df.25kb[(dim(varimp.rf.df.25kb)[1]-14):dim(varimp.rf.df.25kb)[1],]
-varimp.rf.df.25kb$Feature <- factor(varimp.rf.df.25kb$Feature,
-                                     levels=as.character(varimp.rf.df.25kb$Feature))
-
-p.rf.25kb <- ggplot(varimp.rf.df.25kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(B)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="blue") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/25kb/p.rf.25kb.png")
-```
-##50kb
-###Random Under-Sampling
-```{r}
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/50kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf <- rf[order(rf$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf$Importance
-Labels <- as.character(rf$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.50kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.50kb$Feature <- as.character(varimp.rf.df.50kb$Feature)							 
-varimp.rf.df.50kb <-varimp.rf.df.50kb[order(varimp.rf.df.50kb$Importance),]
-varimp.rf.df.50kb <- varimp.rf.df.50kb[(dim(varimp.rf.df.50kb)[1]-14):dim(varimp.rf.df.50kb)[1],]
-varimp.rf.df.50kb$Feature <- factor(varimp.rf.df.50kb$Feature,
-                                     levels=as.character(varimp.rf.df.50kb$Feature))
-
-p.rf.50kb <- ggplot(varimp.rf.df.50kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(C)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="green") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/50kb/p.rf.50kb.png")
-```
-##100kb
-###Random Under-Sampling
-```{r}
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/100kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf <- rf[order(rf$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf$Importance
-Labels <- as.character(rf$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.100kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.100kb$Feature <- as.character(varimp.rf.df.100kb$Feature)							 
-varimp.rf.df.100kb <-varimp.rf.df.100kb[order(varimp.rf.df.100kb$Importance),]
-#varimp.rf.df.100kb <- varimp.rf.df.100kb[(dim(varimp.rf.df.100kb)[1]-14):dim(varimp.rf.df.100kb)[1],]
-varimp.rf.df.100kb$Feature <- factor(varimp.rf.df.100kb$Feature,
-                                     levels=as.character(varimp.rf.df.100kb$Feature))
-
-p.rf.100kb <- ggplot(varimp.rf.df.100kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(D)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="orange") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/100kb/p.rf.100kb.png")
-
-allvarimps <- ggarrange(p.rf.5kb,p.rf.25kb,p.rf.50kb,p.rf.100kb, ncol=2, nrow=2)
-
-ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/allvarimps.png")
-```
-
-#Network Analysis
-
-```{r}
-##venn diagram of top predictors 
-#grid.newpage()
-##vennp <- draw.triple.venn(area1 = 10, area2 = 10, area3 = 10, n12 = length(intersect(us,sm)), n23 = length(intersect(sm,km)), n13 = length(intersect(km,us)), 
-##                 n123 = length(intersect(us,intersect(sm,km))), category = c("Under- \n Sampling", "SMOTE", "K-Medoids"), lty = "blank", 
-##                 fill = c("red", "green", "blue"),cex=3,cat.cex = 3)
-#
-#vennp <- draw.pairwise.venn(length(varimp.rf.df.gm12878$Feature),
-#						  length(varimp.rf.df.k562$Feature),
-#						  length(intersect(varimp.rf.df.gm12878$Feature, varimp.rf.df.k562$Feature)),
-#						  category = c("GM12878", "K562"),
-#						  lty = "blank", 
-#                          fill = c("red", "blue"),
-#						  cex=3,
-#						  cat.cex = 3,
-#						  cat.pos = c(0,0),
-#						  scaled = FALSE)
-
-##Network Visualization between resolutions
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/5kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf5kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rownames(rf5kb) <- NULL
-rf5kb$Feature <- as.character(rf5kb$Feature)
-rf5kb$Feature[grep("Gm12878-", rf5kb$Feature)] <- gsub("Gm12878-","",rf5kb$Feature[grep("Gm12878-", rf5kb$Feature)])
-rf5kb$Feature[grep("_dist", rf5kb$Feature)] <- gsub("_dist","",rf5kb$Feature[grep("_dist", rf5kb$Feature)])
-rf5kb$Importance <- rf5kb$Importance/sum(rf5kb$Importance)
-
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/25kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf25kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rownames(rf25kb) <- NULL
-rf25kb$Feature <- as.character(rf25kb$Feature)
-rf25kb$Feature[grep("Gm12878-", rf25kb$Feature)] <- gsub("Gm12878-","",rf25kb$Feature[grep("Gm12878-", rf25kb$Feature)])
-rf25kb$Feature[grep("_dist", rf25kb$Feature)] <- gsub("_dist","",rf25kb$Feature[grep("_dist", rf25kb$Feature)])
-rf25kb$Importance <- rf25kb$Importance/sum(rf25kb$Importance)
-
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/50kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf50kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rownames(rf50kb) <- NULL
-rf50kb$Feature <- as.character(rf50kb$Feature)
-rf50kb$Feature[grep("Gm12878-", rf50kb$Feature)] <- gsub("Gm12878-","",rf50kb$Feature[grep("Gm12878-", rf50kb$Feature)])
-rf50kb$Feature[grep("_dist", rf50kb$Feature)] <- gsub("_dist","",rf50kb$Feature[grep("_dist", rf50kb$Feature)])
-rf50kb$Importance <- rf50kb$Importance/sum(rf50kb$Importance)
-
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/100kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf100kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rownames(rf100kb) <- NULL
-rf100kb$Feature <- as.character(rf100kb$Feature)
-rf100kb$Feature[grep("Gm12878-", rf100kb$Feature)] <- gsub("Gm12878-","",rf100kb$Feature[grep("Gm12878-", rf100kb$Feature)])
-rf100kb$Feature[grep("_dist", rf100kb$Feature)] <- gsub("_dist","",rf100kb$Feature[grep("_dist", rf100kb$Feature)])
-rf100kb$Importance <- rf100kb$Importance/sum(rf100kb$Importance)
-
-commonannots <- union(rf5kb$Feature,union(rf25kb$Feature,union(rf50kb$Feature,rf100kb$Feature)))
-
-networkmat <- matrix(ncol=4, nrow=length(commonannots), dimnames=list(commonannots, c("5kb", "25kb", "50kb", "100kb")))
-
-networkmat[which(rownames(networkmat) %in% rf5kb$Feature),1] <- rf5kb$Importance
-networkmat[which(rownames(networkmat) %in% rf25kb$Feature),2] <- rf25kb$Importance
-networkmat[which(rownames(networkmat) %in% rf50kb$Feature),3] <- rf50kb$Importance
-networkmat[which(rownames(networkmat) %in% rf100kb$Feature),4] <- rf100kb$Importance
-
-networkmat[is.na(networkmat)] <- 0
-networkmat <- networkmat*10
-
-networkdf <- as.data.frame(networkmat)
-
-net = network(networkdf,
-              matrix.type = "bipartite",
-              ignore.eval = FALSE,
-              names.eval = "weights")
-
-col = c("actor" = "green", "event" = "blue")
-
-networkplot <- ggnet2(net, color = "mode", palette = col, edge.size = "weights", label=TRUE)
-
-ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/networkplot.png")
-
-networkdf <- as.data.frame(t(networkdf))
-
-net = network(networkdf,
-              matrix.type = "bipartite",
-              ignore.eval = FALSE,
-              names.eval = "weights")
-
-col = c("actor" = "blue", "event" = "green")
-
-networkplot2 <- ggnet2(net, color = "mode", palette = col, edge.size = "weights", label=TRUE)
-
-ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/networkplot2.png")
-
-```

### 2019-02-28 Manuscript/Supplementary/supplementary_legends.Rmd
legends edits

@@
 
-**Supplementary Figure 1. Distance Densities across cell lines and resolutions.**
-Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for 10 kb (A), 25 kb (B), 50 kb (C), and 100 kb (D) data resolutions across the GM12878 (left column) and K562 (right column) cell lines.
+**Supplementary Figure 1.
+Distance Densities across cell lines and resolutions.** Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for 10 kb (A), 25 kb (B), 50 kb (C), and 100 kb (D) data resolutions across the GM12878 (left column) and K562 (right column) cell lines.
 The untransformed distance densities are filled in red, while the $log_{2}$ tranformed distance densities are filled in blue.
@@
 Imbalance ratio is defined as the ratio of genomic bins that overlapped a flanked TAD boundary (minority class), divided by the number of genomic bins that did not overlap a flanked TAD boundary (majority class).
+
+**Supplementary Figure 2.
+Correlations between genomic annotations across cell lines and resolutions.** Lower triangular correlation heatmaps between genomic annotations for 10 kb (A), 25 kb (B), 50 kb (C), and 100 kb (D) data resolutions across the GM12878 (left column) and K562 (right column) cell lines.
+The correlations were based on the total number of overlapped bases between flanked TAD boundaries and genomic annotations.
+High correlations (red) denote annotations that tended to occur colocally near TAD boundaries.
+Low correlations (blue) denote annotations that did not tend to occur near TAD boundaries together.
 

### 2019-02-28 Scripts/evaluating_correlations.Rmd
added script for evaluating correlations

---
title: "Exploring Feature Engineering"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)

```

#Feature Engineering

## Exploring Correlations

###GM12878

####10kb

```{r}

train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))

cormat <- cor(binswtad)

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_gm12878_10kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_gm12878_10kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_gm12878_10kb) #4595    4
sigcorrs_gm12878_10kb[,3:4] <- round(sigcorrs_gm12878_10kb[,3:4], 4)
sigcorrs_gm12878_10kb <- sigcorrs_gm12878_10kb[order(sigcorrs_gm12878_10kb$pvals, decreasing = FALSE),]

highcorrs_gm12878_10kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_gm12878_10kb) #21  4
highcorrs_gm12878_10kb[,3:4] <- round(highcorrs_gm12878_10kb[,3:4], 2)
highcorrs_gm12878_10kb <- highcorrs_gm12878_10kb[order(abs(highcorrs_gm12878_10kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_gm12878_10kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5) 
```

####25kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))

cormat <- cor(binswtad)

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_gm12878_25kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_gm12878_25kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_gm12878_25kb) #4683    4
sigcorrs_gm12878_25kb[,3:4] <- round(sigcorrs_gm12878_25kb[,3:4], 4)
sigcorrs_gm12878_25kb <- sigcorrs_gm12878_25kb[order(sigcorrs_gm12878_25kb$pvals, decreasing = FALSE),]

highcorrs_gm12878_25kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_gm12878_25kb) #50  4
highcorrs_gm12878_25kb[,3:4] <- round(highcorrs_gm12878_25kb[,3:4], 2)
highcorrs_gm12878_25kb <- highcorrs_gm12878_25kb[order(abs(highcorrs_gm12878_25kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_gm12878_25kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5) 
```

####50kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))

cormat <- cor(binswtad)

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_gm12878_50kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_gm12878_50kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_gm12878_50kb) #
sigcorrs_gm12878_50kb[,3:4] <- round(sigcorrs_gm12878_50kb[,3:4], 4)
sigcorrs_gm12878_50kb <- sigcorrs_gm12878_50kb[order(sigcorrs_gm12878_50kb$pvals, decreasing = FALSE),]

highcorrs_gm12878_50kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_gm12878_50kb) #
highcorrs_gm12878_50kb[,3:4] <- round(highcorrs_gm12878_50kb[,3:4], 2)
highcorrs_gm12878_50kb <- highcorrs_gm12878_50kb[order(abs(highcorrs_gm12878_50kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_gm12878_50kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5)
```

####100kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))

cormat <- cor(binswtad)

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_gm12878_100kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_gm12878_100kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_gm12878_100kb) #4373    4
sigcorrs_gm12878_100kb[,3:4] <- round(sigcorrs_gm12878_100kb[,3:4], 4)
sigcorrs_gm12878_100kb <- sigcorrs_gm12878_100kb[order(sigcorrs_gm12878_100kb$pvals, decreasing = FALSE),]

highcorrs_gm12878_100kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_gm12878_100kb) #424   4
highcorrs_gm12878_100kb[,3:4] <- round(highcorrs_gm12878_100kb[,3:4], 2)
highcorrs_gm12878_100kb <- highcorrs_gm12878_100kb[order(abs(highcorrs_gm12878_100kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_gm12878_100kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5)
```

###K562

####10kb

```{r}

train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("K562",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))

cormat <- cor(binswtad)
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_K562_10kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
pvals <- pvals[-which(rownames(pvals) == "Znf274"), -which(colnames(pvals) == "Znf274")]

upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.0000000000),] #remove main daigonal
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_K562_10kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_K562_10kb) #4595    4
sigcorrs_K562_10kb[,3:4] <- round(sigcorrs_K562_10kb[,3:4], 4)
sigcorrs_K562_10kb <- sigcorrs_K562_10kb[order(sigcorrs_K562_10kb$pvals, decreasing = FALSE),]

highcorrs_K562_10kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_K562_10kb) #21  4
highcorrs_K562_10kb[,3:4] <- round(highcorrs_K562_10kb[,3:4], 2)
highcorrs_K562_10kb <- highcorrs_K562_10kb[order(abs(highcorrs_K562_10kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_K562_10kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5) 
```

####25kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("K562",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))

cormat <- cor(binswtad)
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_K562_25kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
pvals <- pvals[-which(rownames(pvals) == "Znf274"), -which(colnames(pvals) == "Znf274")]

upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_K562_25kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_K562_25kb) #4683    4
sigcorrs_K562_25kb[,3:4] <- round(sigcorrs_K562_25kb[,3:4], 4)
sigcorrs_K562_25kb <- sigcorrs_K562_25kb[order(sigcorrs_K562_25kb$pvals, decreasing = FALSE),]

highcorrs_K562_25kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_K562_25kb) #50  4
highcorrs_K562_25kb[,3:4] <- round(highcorrs_K562_25kb[,3:4], 2)
highcorrs_K562_25kb <- highcorrs_K562_25kb[order(abs(highcorrs_K562_25kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_K562_25kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5) 
```

####50kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("K562",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))

cormat <- cor(binswtad)
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_K562_50kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
pvals <- pvals[-which(rownames(pvals) == "Znf274"), -which(colnames(pvals) == "Znf274")]

upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_K562_50kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_K562_50kb) #
sigcorrs_K562_50kb[,3:4] <- round(sigcorrs_K562_50kb[,3:4], 4)
sigcorrs_K562_50kb <- sigcorrs_K562_50kb[order(sigcorrs_K562_50kb$pvals, decreasing = FALSE),]

highcorrs_K562_50kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_K562_50kb) #
highcorrs_K562_50kb[,3:4] <- round(highcorrs_K562_50kb[,3:4], 2)
highcorrs_K562_50kb <- highcorrs_K562_50kb[order(abs(highcorrs_K562_50kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_K562_50kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5)
```

####100kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("K562",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))

cormat <- cor(binswtad)
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_K562_100kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
pvals <- pvals[-which(rownames(pvals) == "Znf274"), -which(colnames(pvals) == "Znf274")]

upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_K562_100kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_K562_100kb) #4373    4
sigcorrs_K562_100kb[,3:4] <- round(sigcorrs_K562_100kb[,3:4], 4)
sigcorrs_K562_100kb <- sigcorrs_K562_100kb[order(sigcorrs_K562_100kb$pvals, decreasing = FALSE),]

highcorrs_K562_100kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_K562_100kb) #424   4
highcorrs_K562_100kb[,3:4] <- round(highcorrs_K562_100kb[,3:4], 2)
highcorrs_K562_100kb <- highcorrs_K562_100kb[order(abs(highcorrs_K562_100kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_K562_100kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5)
```

### 2019-02-28 Manuscript/manuscript.Rmd
manuscript edits

@@
 **Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter simply as $\textit{distance}$), from the center of the bin to the center of the nearest region defined by a specific genomic annotation was calculated.
-The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figures 1-8).
+The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figures 1).
 
@@
 
-When assessing the collinearity of the genomic annotations, it was found that the total number of bases that the number overlapped bases between genomic bins flanked by a TAD boundary were highly correlated between many genomic annotations ().
+When assessing the collinearity of the genomic annotations, it was found that the total number of bases that the number overlapped bases between genomic bins flanked by a TAD boundary were highly correlated between many genomic annotations (Supplementary Figure 2).
 That is, many genomic annotations tended to colocalize near eachother at the boarders of domains.

### 2019-03-08 Scripts/evaluating_correlations.Rmd
added code for new correlation figures

@@
 library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
 
@@
 ```
+
+## Using corrplot function
+
+### GM12878
+
+#### 10kb
+
+```{r}
+
+train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
+
+binswtad <- train[which(train$y=="Yes"),]
+binswtad <- binswtad[,grep("count", names(binswtad))]
+
+names(binswtad) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", names(binswtad))
+
+cormat <- cor(binswtad, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+#### 25kb
+
+```{r}
+
+train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
+
+binswtad <- train[which(train$y=="Yes"),]
+binswtad <- binswtad[,grep("count", names(binswtad))]
+
+names(binswtad) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", names(binswtad))
+
+cormat <- cor(binswtad, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+#### 50kb
+
+```{r}
+
+train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
+
+binswtad <- train[which(train$y=="Yes"),]
+binswtad <- binswtad[,grep("count", names(binswtad))]
+
+names(binswtad) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", names(binswtad))
+
+cormat <- cor(binswtad, method = "spearman")
+
+corrplot(cormat, 
+         type="lower", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+#### 100kb
+
+```{r}
+
+train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
+
+binswtad <- train[which(train$y=="Yes"),]
+binswtad <- binswtad[,grep("count", names(binswtad))]
+
+names(binswtad) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", names(binswtad))
+
+cormat <- cor(binswtad, method = "spearman")
+
+corrplot(cormat, 
+         type="lower", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+### K562
+
+#### 10kb
+
+```{r}
+
+train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
+
+binswtad <- train[which(train$y=="Yes"),]
+binswtad <- binswtad[,grep("count", names(binswtad))]
+
+names(binswtad) <- gsub(paste(c("K562",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", names(binswtad))
+
+cormat <- cor(binswtad, method = "spearman")
+#remove Znf274 columns
+#(no counts in flanked tad regions)
+#therefore the corelation will be NA with all other features
+cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .3,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+#### 25kb
+
+```{r}
+
+train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
+
+binswtad <- train[which(train$y=="Yes"),]
+binswtad <- binswtad[,grep("count", names(binswtad))]
+
+names(binswtad) <- gsub(paste(c("K562",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", names(binswtad))
+
+cormat <- cor(binswtad, method = "spearman")
+#remove Znf274 columns
+#(no counts in flanked tad regions)
+#therefore the corelation will be NA with all other features
+cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .3,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+#### 50kb
+
+```{r}
+
+train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
+
+binswtad <- train[which(train$y=="Yes"),]
+binswtad <- binswtad[,grep("count", names(binswtad))]
+
+names(binswtad) <- gsub(paste(c("K562",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", names(binswtad))
+
+cormat <- cor(binswtad, method = "spearman")
+#remove Znf274 columns
+#(no counts in flanked tad regions)
+#therefore the corelation will be NA with all other features
+cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]
+
+corrplot(cormat, 
+         type="lower", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .3,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+#### 100kb
+
+```{r}
+
+train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
+
+binswtad <- train[which(train$y=="Yes"),]
+binswtad <- binswtad[,grep("count", names(binswtad))]
+
+names(binswtad) <- gsub(paste(c("K562",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", names(binswtad))
+
+cormat <- cor(binswtad, method = "spearman")
+#remove Znf274 columns
+#(no counts in flanked tad regions)
+#therefore the corelation will be NA with all other features
+cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]
+
+corrplot(cormat, 
+         type="lower", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .3,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```

### 2019-03-08 Manuscript/Supplementary/supplementary_legends.Rmd
updated legends
eddited legend for correlation figure

--- 2019-02-27 Manuscript/Supplementary/supplementary_legends.Rmd
@@
 "Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Available Cell Type" - the name of the cell type in which the annotation was available, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
-[???
-Did you use only features common to both cell lines?; !!!clarified, need to discuss further]
 
-**Supplementary Figure 1. Distance Densities across cell lines and resolutions.**
-Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for 10 kb (A), 25 kb (B), 50 kb (C), and 100 kb (D) data resolutions across the GM12878 (left column) and K562 (right column) cell lines.
+**Supplementary Figure 1.
+Distance Densities across cell lines and resolutions.** Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for 10 kb (A), 25 kb (B), 50 kb (C), and 100 kb (D) data resolutions across the GM12878 (left column) and K562 (right column) cell lines.
 The untransformed distance densities are filled in red, while the $log_{2}$ tranformed distance densities are filled in blue.
@@
 Imbalance ratio is defined as the ratio of genomic bins that overlapped a flanked TAD boundary (minority class), divided by the number of genomic bins that did not overlap a flanked TAD boundary (majority class).
+
+**Supplementary Figure 2.
+Correlations between genomic annotations across cell lines and resolutions.** Upper and lower correlation heatmaps between genomic annotations for the GM12878 (A-D) and K562 (E-H) cell lines, across the 10 kb, 25 kb, 50 kb, and 100 kb resolutions (A, B, C, D; and E, F, G, H respectively).
+The correlations were evaluated on the total number of overlapped bases between flanked TAD boundaries and genomic annotations.
+High correlations (red) denote annotations that tended to occur colocally near TAD boundaries.
+Low correlations (blue) denote annotations that did not tend to occur near TAD boundaries together.
 

### 2019-03-08 Scripts/evaluating_feature_reduction.Rmd
added script for creating variable reduction heatmap

--- 2019-02-05 Scripts/performances.rmd
@@
 ---
-title: "Performances Code"
+title: "Evaluating Regularization"
+author: "Spiro Stilianoudakis"
+date: "March 7, 2019"
 output: html_document
@@
 library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
 
@@
 
-# Evaluating Distance Densities
-##GM12878
-###10kb
-
-```{r}
-gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
-
-gm12878_10kb_ld <- gm12878_10kb[,c(1,grep("_dist", names(gm12878_10kb)))]
-
-###############
-#gm12878_10kb_ld <- gm12878_10kb_ld[,c(1:5)]
-###############
-
-gm12878_10kb_d <- gm12878_10kb_ld
-gm12878_10kb_d[,-1] <- exp(gm12878_10kb_ld[,-1]) - 1
-gm12878_10kb_d$Average_dist <- rowMeans(gm12878_10kb_d[,-1])
-
-gm12878_10kb_ld$Average_dist <- rowMeans(gm12878_10kb_ld[,-1])
-names(gm12878_10kb_ld)[-1] <- paste(substr(names(gm12878_10kb_ld)[-1],
-                                           1, 
-                                           nchar(names(gm12878_10kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-gm12878_10kb_alldist <- cbind.data.frame(gm12878_10kb_d[,-1], gm12878_10kb_ld[,-1])
-
-long10kb <- melt(gm12878_10kb_alldist)
-long10kb$variable <- as.character(long10kb$variable)
-long10kb$Transformation <- NA
-long10kb$Transformation[grep("_logdist", long10kb$variable)] <- rep("Log Distance", length(long10kb$variable[grep("_logdist", long10kb$variable)]))
-long10kb$Transformation[grep("_logdist", long10kb$variable, invert = TRUE)] <- rep("Distance", length(long10kb$variable[grep("_logdist", long10kb$variable, invert = TRUE)]))
-
-table(long10kb$Transformation)
-
-distdensity10kb <- ggplot() + 
-  geom_density(data=long10kb[intersect(grep("_dist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long10kb[grep("Average_dist", long10kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity10kb <- ggplot() + 
-  geom_density(data=long10kb[intersect(grep("logdist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long10kb[grep("Average_logdist", long10kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long10kb$value[long10kb$Transformation=="Distance"] <- long10kb$value[long10kb$Transformation=="Distance"]/1000000
-long10kb <- long10kb[grep("Average", long10kb$variable, invert = TRUE),]
-long10kb$variable <- factor(long10kb$variable)
-long10kb$Transformation <- factor(long10kb$Transformation)
-
-alldensity10kb <- ggplot(long10kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("10 kb")+ 
-  ylim(0,.8)+
-  ggtitle("GM12878") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-###25kb
-
-```{r}
-gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
-
-gm12878_25kb_ld <- gm12878_25kb[,c(1,grep("_dist", names(gm12878_25kb)))]
-
-###############
-#gm12878_25kb_ld <- gm12878_25kb_ld[,c(1:5)]
-###############
-
-gm12878_25kb_d <- gm12878_25kb_ld
-gm12878_25kb_d[,-1] <- exp(gm12878_25kb_ld[,-1]) - 1
-gm12878_25kb_d$Average_dist <- rowMeans(gm12878_25kb_d[,-1])
-
-gm12878_25kb_ld$Average_dist <- rowMeans(gm12878_25kb_ld[,-1])
-names(gm12878_25kb_ld)[-1] <- paste(substr(names(gm12878_25kb_ld)[-1],
-                                           1, 
-                                           nchar(names(gm12878_25kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-gm12878_25kb_alldist <- cbind.data.frame(gm12878_25kb_d[,-1], gm12878_25kb_ld[,-1])
-
-long25kb <- melt(gm12878_25kb_alldist)
-long25kb$variable <- as.character(long25kb$variable)
-long25kb$Transformation <- NA
-long25kb$Transformation[grep("_logdist", long25kb$variable)] <- rep("Log Distance", length(long25kb$variable[grep("_logdist", long25kb$variable)]))
-long25kb$Transformation[grep("_logdist", long25kb$variable, invert = TRUE)] <- rep("Distance", length(long25kb$variable[grep("_logdist", long25kb$variable, invert = TRUE)]))
-
-table(long25kb$Transformation)
-
-distdensity25kb <- ggplot() + 
-  geom_density(data=long25kb[intersect(grep("_dist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long25kb[grep("Average_dist", long25kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity25kb <- ggplot() + 
-  geom_density(data=long25kb[intersect(grep("logdist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long25kb[grep("Average_logdist", long25kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) +  
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long25kb$value[long25kb$Transformation=="Distance"] <- long25kb$value[long25kb$Transformation=="Distance"]/1000000
-long25kb <- long25kb[grep("Average", long25kb$variable, invert = TRUE),]
-long25kb$variable <- factor(long25kb$variable)
-long25kb$Transformation <- factor(long25kb$Transformation)
-
-alldensity25kb <- ggplot(long25kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("25 kb")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-###50kb
-
-```{r}
-gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
-
-gm12878_50kb_ld <- gm12878_50kb[,c(1,grep("_dist", names(gm12878_50kb)))]
-
-###############
-#gm12878_50kb_ld <- gm12878_50kb_ld[,c(1:5)]
-###############
-
-gm12878_50kb_d <- gm12878_50kb_ld
-gm12878_50kb_d[,-1] <- exp(gm12878_50kb_ld[,-1]) - 1
-gm12878_50kb_d$Average_dist <- rowMeans(gm12878_50kb_d[,-1])
-
-gm12878_50kb_ld$Average_dist <- rowMeans(gm12878_50kb_ld[,-1])
-names(gm12878_50kb_ld)[-1] <- paste(substr(names(gm12878_50kb_ld)[-1],
-                                           1, 
-                                           nchar(names(gm12878_50kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-gm12878_50kb_alldist <- cbind.data.frame(gm12878_50kb_d[,-1], gm12878_50kb_ld[,-1])
-
-long50kb <- melt(gm12878_50kb_alldist)
-long50kb$variable <- as.character(long50kb$variable)
-long50kb$Transformation <- NA
-long50kb$Transformation[grep("_logdist", long50kb$variable)] <- rep("Log Distance", length(long50kb$variable[grep("_logdist", long50kb$variable)]))
-long50kb$Transformation[grep("_logdist", long50kb$variable, invert = TRUE)] <- rep("Distance", length(long50kb$variable[grep("_logdist", long50kb$variable, invert = TRUE)]))
-
-table(long50kb$Transformation)
-
-distdensity50kb <- ggplot() + 
-  geom_density(data=long50kb[intersect(grep("_dist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long50kb[grep("Average_dist", long50kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity50kb <- ggplot() + 
-  geom_density(data=long50kb[intersect(grep("logdist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long50kb[grep("Average_logdist", long50kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long50kb$value[long50kb$Transformation=="Distance"] <- long50kb$value[long50kb$Transformation=="Distance"]/1000000
-long50kb <- long50kb[grep("Average", long50kb$variable, invert = TRUE),]
-long50kb$variable <- factor(long50kb$variable)
-long50kb$Transformation <- factor(long50kb$Transformation)
-
-alldensity50kb <- ggplot(long50kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("50 kb")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-###100kb
-
-```{r}
-gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
-
-gm12878_100kb_ld <- gm12878_100kb[,c(1,grep("_dist", names(gm12878_100kb)))]
-
-###############
-#gm12878_100kb_ld <- gm12878_100kb_ld[,c(1:5)]
-###############
-
-gm12878_100kb_d <- gm12878_100kb_ld
-gm12878_100kb_d[,-1] <- exp(gm12878_100kb_ld[,-1]) - 1
-gm12878_100kb_d$Average_dist <- rowMeans(gm12878_100kb_d[,-1])
-
-gm12878_100kb_ld$Average_dist <- rowMeans(gm12878_100kb_ld[,-1])
-names(gm12878_100kb_ld)[-1] <- paste(substr(names(gm12878_100kb_ld)[-1],
-                                           1, 
-                                           nchar(names(gm12878_100kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-gm12878_100kb_alldist <- cbind.data.frame(gm12878_100kb_d[,-1], gm12878_100kb_ld[,-1])
-
-long100kb <- melt(gm12878_100kb_alldist)
-long100kb$variable <- as.character(long100kb$variable)
-long100kb$Transformation <- NA
-long100kb$Transformation[grep("_logdist", long100kb$variable)] <- rep("Log Distance", length(long100kb$variable[grep("_logdist", long100kb$variable)]))
-long100kb$Transformation[grep("_logdist", long100kb$variable, invert = TRUE)] <- rep("Distance", length(long100kb$variable[grep("_logdist", long100kb$variable, invert = TRUE)]))
-
-table(long100kb$Transformation)
-
-distdensity100kb <- ggplot() + 
-  geom_density(data=long100kb[intersect(grep("_dist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long100kb[grep("Average_dist", long100kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("No Transformation") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity100kb <- ggplot() + 
-  geom_density(data=long100kb[intersect(grep("logdist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long100kb[grep("Average_logdist", long100kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("Log Tranformation") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long100kb$value[long100kb$Transformation=="Distance"] <- long100kb$value[long100kb$Transformation=="Distance"]/1000000
-long100kb <- long100kb[grep("Average", long100kb$variable, invert = TRUE),]
-long100kb$variable <- factor(long100kb$variable)
-long100kb$Transformation <- factor(long100kb$Transformation)
-
-alldensity100kb <- ggplot(long100kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("100 kb")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-##K562
-###10kb
-
-```{r}
-K562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
-
-K562_10kb_ld <- K562_10kb[,c(1,grep("_dist", names(K562_10kb)))]
-
-###############
-#K562_10kb_ld <- K562_10kb_ld[,c(1:5)]
-###############
-
-K562_10kb_d <- K562_10kb_ld
-K562_10kb_d[,-1] <- exp(K562_10kb_ld[,-1]) - 1
-K562_10kb_d$Average_dist <- rowMeans(K562_10kb_d[,-1])
-
-K562_10kb_ld$Average_dist <- rowMeans(K562_10kb_ld[,-1])
-names(K562_10kb_ld)[-1] <- paste(substr(names(K562_10kb_ld)[-1],
-                                           1, 
-                                           nchar(names(K562_10kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-K562_10kb_alldist <- cbind.data.frame(K562_10kb_d[,-1], K562_10kb_ld[,-1])
-
-long10kb <- melt(K562_10kb_alldist)
-long10kb$variable <- as.character(long10kb$variable)
-long10kb$Transformation <- NA
-long10kb$Transformation[grep("_logdist", long10kb$variable)] <- rep("Log Distance", length(long10kb$variable[grep("_logdist", long10kb$variable)]))
-long10kb$Transformation[grep("_logdist", long10kb$variable, invert = TRUE)] <- rep("Distance", length(long10kb$variable[grep("_logdist", long10kb$variable, invert = TRUE)]))
-
-table(long10kb$Transformation)
-
-distdensity10kb <- ggplot() + 
-  geom_density(data=long10kb[intersect(grep("_dist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long10kb[grep("Average_dist", long10kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity10kb <- ggplot() + 
-  geom_density(data=long10kb[intersect(grep("logdist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long10kb[grep("Average_logdist", long10kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long10kb$value[long10kb$Transformation=="Distance"] <- long10kb$value[long10kb$Transformation=="Distance"]/1000000
-long10kb <- long10kb[grep("Average", long10kb$variable, invert = TRUE),]
-long10kb$variable <- factor(long10kb$variable)
-long10kb$Transformation <- factor(long10kb$Transformation)
-
-alldensity10kb_k562 <- ggplot(long10kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	#ylab("10 kb")+ 
-  ylim(0,.8)+
-  ggtitle("K562") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-###25kb
-
-```{r}
-K562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
-
-K562_25kb_ld <- K562_25kb[,c(1,grep("_dist", names(K562_25kb)))]
-
-###############
-#K562_25kb_ld <- K562_25kb_ld[,c(1:5)]
-###############
-
-K562_25kb_d <- K562_25kb_ld
-K562_25kb_d[,-1] <- exp(K562_25kb_ld[,-1]) - 1
-K562_25kb_d$Average_dist <- rowMeans(K562_25kb_d[,-1])
-
-K562_25kb_ld$Average_dist <- rowMeans(K562_25kb_ld[,-1])
-names(K562_25kb_ld)[-1] <- paste(substr(names(K562_25kb_ld)[-1],
-                                           1, 
-                                           nchar(names(K562_25kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-K562_25kb_alldist <- cbind.data.frame(K562_25kb_d[,-1], K562_25kb_ld[,-1])
-
-long25kb <- melt(K562_25kb_alldist)
-long25kb$variable <- as.character(long25kb$variable)
-long25kb$Transformation <- NA
-long25kb$Transformation[grep("_logdist", long25kb$variable)] <- rep("Log Distance", length(long25kb$variable[grep("_logdist", long25kb$variable)]))
-long25kb$Transformation[grep("_logdist", long25kb$variable, invert = TRUE)] <- rep("Distance", length(long25kb$variable[grep("_logdist", long25kb$variable, invert = TRUE)]))
-
-table(long25kb$Transformation)
-
-distdensity25kb <- ggplot() + 
-  geom_density(data=long25kb[intersect(grep("_dist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long25kb[grep("Average_dist", long25kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity25kb <- ggplot() + 
-  geom_density(data=long25kb[intersect(grep("logdist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long25kb[grep("Average_logdist", long25kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long25kb$value[long25kb$Transformation=="Distance"] <- long25kb$value[long25kb$Transformation=="Distance"]/1000000
-long25kb <- long25kb[grep("Average", long25kb$variable, invert = TRUE),]
-long25kb$variable <- factor(long25kb$variable)
-long25kb$Transformation <- factor(long25kb$Transformation)
-
-alldensity25kb_k562 <- ggplot(long25kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	#ylab("25 kb")+ 
-  ylim(0,.8)+
-  #ggtitle("K562") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-###50kb
-
-```{r}
-K562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
-
-K562_50kb_ld <- K562_50kb[,c(1,grep("_dist", names(K562_50kb)))]
-
-###############
-#K562_50kb_ld <- K562_50kb_ld[,c(1:5)]
-###############
-
-K562_50kb_d <- K562_50kb_ld
-K562_50kb_d[,-1] <- exp(K562_50kb_ld[,-1]) - 1
-K562_50kb_d$Average_dist <- rowMeans(K562_50kb_d[,-1])
-
-K562_50kb_ld$Average_dist <- rowMeans(K562_50kb_ld[,-1])
-names(K562_50kb_ld)[-1] <- paste(substr(names(K562_50kb_ld)[-1],
-                                           1, 
-                                           nchar(names(K562_50kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-K562_50kb_alldist <- cbind.data.frame(K562_50kb_d[,-1], K562_50kb_ld[,-1])
-
-long50kb <- melt(K562_50kb_alldist)
-long50kb$variable <- as.character(long50kb$variable)
-long50kb$Transformation <- NA
-long50kb$Transformation[grep("_logdist", long50kb$variable)] <- rep("Log Distance", length(long50kb$variable[grep("_logdist", long50kb$variable)]))
-long50kb$Transformation[grep("_logdist", long50kb$variable, invert = TRUE)] <- rep("Distance", length(long50kb$variable[grep("_logdist", long50kb$variable, invert = TRUE)]))
-
-table(long50kb$Transformation)
-
-distdensity50kb <- ggplot() + 
-  geom_density(data=long50kb[intersect(grep("_dist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long50kb[grep("Average_dist", long50kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity50kb <- ggplot() + 
-  geom_density(data=long50kb[intersect(grep("logdist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long50kb[grep("Average_logdist", long50kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long50kb$value[long50kb$Transformation=="Distance"] <- long50kb$value[long50kb$Transformation=="Distance"]/1000000
-long50kb <- long50kb[grep("Average", long50kb$variable, invert = TRUE),]
-long50kb$variable <- factor(long50kb$variable)
-long50kb$Transformation <- factor(long50kb$Transformation)
-
-alldensity50kb_k562 <- ggplot(long50kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	#ylab("50 kb")+ 
-  ylim(0,.8)+
-  #ggtitle("K562") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-###100kb
-
-```{r}
-K562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
-
-K562_100kb_ld <- K562_100kb[,c(1,grep("_dist", names(K562_100kb)))]
-
-###############
-#K562_100kb_ld <- K562_100kb_ld[,c(1:5)]
-###############
-
-K562_100kb_d <- K562_100kb_ld
-K562_100kb_d[,-1] <- exp(K562_100kb_ld[,-1]) - 1
-K562_100kb_d$Average_dist <- rowMeans(K562_100kb_d[,-1])
-
-K562_100kb_ld$Average_dist <- rowMeans(K562_100kb_ld[,-1])
-names(K562_100kb_ld)[-1] <- paste(substr(names(K562_100kb_ld)[-1],
-                                           1, 
-                                           nchar(names(K562_100kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-K562_100kb_alldist <- cbind.data.frame(K562_100kb_d[,-1], K562_100kb_ld[,-1])
-
-long100kb <- melt(K562_100kb_alldist)
-long100kb$variable <- as.character(long100kb$variable)
-long100kb$Transformation <- NA
-long100kb$Transformation[grep("_logdist", long100kb$variable)] <- rep("Log Distance", length(long100kb$variable[grep("_logdist", long100kb$variable)]))
-long100kb$Transformation[grep("_logdist", long100kb$variable, invert = TRUE)] <- rep("Distance", length(long100kb$variable[grep("_logdist", long100kb$variable, invert = TRUE)]))
-
-table(long100kb$Transformation)
-
-distdensity100kb <- ggplot() + 
-  geom_density(data=long100kb[intersect(grep("_dist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long100kb[grep("Average_dist", long100kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity100kb <- ggplot() + 
-  geom_density(data=long100kb[intersect(grep("logdist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long100kb[grep("Average_logdist", long100kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long100kb$value[long100kb$Transformation=="Distance"] <- long100kb$value[long100kb$Transformation=="Distance"]/1000000
-long100kb <- long100kb[grep("Average", long100kb$variable, invert = TRUE),]
-long100kb$variable <- factor(long100kb$variable)
-long100kb$Transformation <- factor(long100kb$Transformation)
-
-alldensity100kb_k562 <- ggplot(long100kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	#ylab("100 kb")+ 
-  ylim(0,.8)+
-  #ggtitle("K562") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-##Combined
-
-```{r}
-#alldistplots <- grid.arrange(distdensity10kb, logdistdensity10kb,
-#             distdensity25kb, logdistdensity25kb,
-#             distdensity50kb, logdistdensity50kb,
-#             distdensity100kb, logdistdensity100kb, ncol=2, nrow=4)
-
-alldistplots <- ggarrange(alldensity10kb,
-                          alldensity10kb_k562,
-                          alldensity25kb,
-                          alldensity25kb_k562,
-                          alldensity50kb,
-                          alldensity50kb_k562,
-                          alldensity100kb,
-                          alldensity100kb_k562, 
-          ncol=2, 
-          nrow=4,
-          #labels = c("A","", "B","", "C","", "D",""),
-          legend = "top",
-          common.legend = TRUE)
-
-annotate_figure(alldistplots,
-                bottom = text_grob("Distance to Nearest TAD Boundary \n (in millions of basepairs)", 
-                                color = "black", 
-                                face = "bold", 
-                                size = 15),
-                left = text_grob("Density", 
-                                 color = "black",
-                                 size = 15,
-                                 rot = 90))
-```
-
-#Evaluating Imbalance Ratios
-##GM12878
-###10kb
+### GM12878
+
+####10kb
 
@@
 train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x10 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p10kb <- ggplot(x10, aes(y=IR, x=factor(CB, levels = unique(x10$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_10kb_gm12878, 
+                      enetcoefs_none_op_10kb_gm12878, 
+                      enetcoefs_none_dist_10kb_gm12878,
+                      enetcoefs_RUS_oc_10kb_gm12878, 
+                      enetcoefs_RUS_op_10kb_gm12878, 
+                      enetcoefs_RUS_dist_10kb_gm12878,
+                      enetcoefs_ROS_oc_10kb_gm12878, 
+                      enetcoefs_ROS_op_10kb_gm12878, 
+                      enetcoefs_ROS_dist_10kb_gm12878,
+                      enetcoefs_SMOTE_oc_10kb_gm12878, 
+                      enetcoefs_SMOTE_op_10kb_gm12878, 
+                      enetcoefs_SMOTE_dist_10kb_gm12878)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_10kb_gm12878 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_10kb_gm12878[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_10kb_gm12878), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
 
@@
 
-###25kb
+####25kb
 
@@
 train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x25 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p25kb <- ggplot(x25, aes(y=IR, x=factor(CB, levels = unique(x25$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_25kb_gm12878, 
+                      enetcoefs_none_op_25kb_gm12878, 
+                      enetcoefs_none_dist_25kb_gm12878,
+                      enetcoefs_RUS_oc_25kb_gm12878, 
+                      enetcoefs_RUS_op_25kb_gm12878, 
+                      enetcoefs_RUS_dist_25kb_gm12878,
+                      enetcoefs_ROS_oc_25kb_gm12878, 
+                      enetcoefs_ROS_op_25kb_gm12878, 
+                      enetcoefs_ROS_dist_25kb_gm12878,
+                      enetcoefs_SMOTE_oc_25kb_gm12878, 
+                      enetcoefs_SMOTE_op_25kb_gm12878, 
+                      enetcoefs_SMOTE_dist_25kb_gm12878)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_25kb_gm12878 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_25kb_gm12878[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_25kb_gm12878), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
 
@@
 
-###50kb
+####50kb
 
@@
 train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x50 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p50kb <- ggplot(x50, aes(y=IR, x=factor(CB, levels = unique(x50$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_50kb_gm12878, 
+                      enetcoefs_none_op_50kb_gm12878, 
+                      enetcoefs_none_dist_50kb_gm12878,
+                      enetcoefs_RUS_oc_50kb_gm12878, 
+                      enetcoefs_RUS_op_50kb_gm12878, 
+                      enetcoefs_RUS_dist_50kb_gm12878,
+                      enetcoefs_ROS_oc_50kb_gm12878, 
+                      enetcoefs_ROS_op_50kb_gm12878, 
+                      enetcoefs_ROS_dist_50kb_gm12878,
+                      enetcoefs_SMOTE_oc_50kb_gm12878, 
+                      enetcoefs_SMOTE_op_50kb_gm12878, 
+                      enetcoefs_SMOTE_dist_50kb_gm12878)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_50kb_gm12878 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_50kb_gm12878[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_50kb_gm12878), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
 
@@
 
-###100kb
+####100kb
 
@@
 train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x100 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p100kb <- ggplot(x100, aes(y=IR, x=factor(CB, levels = unique(x100$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_100kb_gm12878, 
+                      enetcoefs_none_op_100kb_gm12878, 
+                      enetcoefs_none_dist_100kb_gm12878,
+                      enetcoefs_RUS_oc_100kb_gm12878, 
+                      enetcoefs_RUS_op_100kb_gm12878, 
+                      enetcoefs_RUS_dist_100kb_gm12878,
+                      enetcoefs_ROS_oc_100kb_gm12878, 
+                      enetcoefs_ROS_op_100kb_gm12878, 
+                      enetcoefs_ROS_dist_100kb_gm12878,
+                      enetcoefs_SMOTE_oc_100kb_gm12878, 
+                      enetcoefs_SMOTE_op_100kb_gm12878, 
+                      enetcoefs_SMOTE_dist_100kb_gm12878)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_100kb_gm12878 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_100kb_gm12878[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_100kb_gm12878), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
 
@@
 
-##K562
-###10kb
+####Combined
+
+```{r}
+all_featuremat_gm12878 <- cbind(featuremat_10kb_gm12878,
+                                featuremat_25kb_gm12878,
+                                featuremat_50kb_gm12878,
+                                featuremat_100kb_gm12878)
+all_featuremat_gm12878 <- all_featuremat_gm12878[,c(seq(1,48,3),
+                                                    seq(2,48,3),
+                                                    seq(3,48,3))]
+colnames(all_featuremat_gm12878) <- rep(c("None", "RUS", "ROS", "SMOTE"), 12)
+
+levelplot(t(all_featuremat_gm12878), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45, cex=.5),
+                      #alternating=3,
+                      y=list(cex=.5)), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+			#horizontal lines
+			panel.abline(h = 1.5);
+			panel.abline(h = 2.5);
+			panel.abline(h = 3.5);
+			panel.abline(h = 4.5);
+			panel.abline(h = 5.5);
+			panel.abline(h = 6.5);
+			panel.abline(h = 7.5);
+			panel.abline(h = 8.5);
+			panel.abline(h = 9.5);
+			panel.abline(h = 10.5);
+			panel.abline(h = 11.5);
+			panel.abline(h = 12.5);
+			panel.abline(h = 13.5);
+			panel.abline(h = 14.5);
+			panel.abline(h = 15.5);
+			panel.abline(h = 16.5);
+			panel.abline(h = 17.5);
+			panel.abline(h = 18.5);
+			panel.abline(h = 19.5);
+			panel.abline(h = 20.5);
+			panel.abline(h = 21.5);
+			panel.abline(h = 22.5);
+			panel.abline(h = 23.5);
+			panel.abline(h = 24.5);
+			panel.abline(h = 25.5);
+			panel.abline(h = 26.5);
+			panel.abline(h = 27.5);
+			panel.abline(h = 28.5);
+			panel.abline(h = 29.5);
+			panel.abline(h = 30.5);
+			panel.abline(h = 31.5);
+			panel.abline(h = 32.5);
+			panel.abline(h = 33.5);
+			panel.abline(h = 34.5);
+			panel.abline(h = 35.5);
+			panel.abline(h = 36.5);
+			panel.abline(h = 37.5);
+			panel.abline(h = 38.5);
+			panel.abline(h = 39.5);
+			panel.abline(h = 40.5);
+			panel.abline(h = 41.5);
+			panel.abline(h = 42.5);
+			panel.abline(h = 43.5);
+			panel.abline(h = 44.5);
+			panel.abline(h = 45.5);
+			panel.abline(h = 46.5);
+			panel.abline(h = 47.5);
+			panel.abline(h = 48.5);
+			panel.abline(h = 49.5);
+			panel.abline(h = 50.5);
+			panel.abline(h = 50.5);
+			panel.abline(h = 51.5);
+			panel.abline(h = 52.5);
+			panel.abline(h = 53.5);
+			panel.abline(h = 54.5);
+			panel.abline(h = 55.5);
+			panel.abline(h = 56.5);
+			panel.abline(h = 57.5);
+			panel.abline(h = 58.5);
+			panel.abline(h = 59.5);
+			panel.abline(h = 60.5);
+			panel.abline(h = 61.5);
+			panel.abline(h = 62.5);
+			panel.abline(h = 63.5);
+			panel.abline(h = 64.5);
+			panel.abline(h = 65.5);
+			panel.abline(h = 66.5);
+			panel.abline(h = 67.5);
+			panel.abline(h = 68.5);
+			panel.abline(h = 69.5);
+			panel.abline(h = 70.5);
+			panel.abline(h = 71.5);
+			panel.abline(h = 72.5);
+			panel.abline(h = 73.5);
+			panel.abline(h = 74.5);
+			panel.abline(h = 75.5);
+			panel.abline(h = 76.5);
+			panel.abline(h = 77.5);
+			panel.abline(h = 78.5);
+			panel.abline(h = 79.5);
+			panel.abline(h = 80.5);
+			panel.abline(h = 81.5);
+			panel.abline(h = 82.5);
+			panel.abline(h = 83.5);
+			panel.abline(h = 84.5);
+			panel.abline(h = 85.5);
+			panel.abline(h = 86.5);
+			panel.abline(h = 87.5);
+			panel.abline(h = 88.5);
+			panel.abline(h = 89.5);
+			panel.abline(h = 90.5);
+			panel.abline(h = 91.5);
+			panel.abline(h = 92.5);
+			panel.abline(h = 93.5);
+			panel.abline(h = 94.5);
+			panel.abline(h = 95.5);
+			panel.abline(h = 96.5);
+			panel.abline(h = 97.5);
+			panel.abline(h = 98.5);
+			panel.abline(h = 99.5);
+			panel.abline(h = 100.5);
+			panel.abline(h = 101.5);
+			panel.abline(h = 102.5);
+			panel.abline(h = 103.5);
+
+			#vertical lines
+            panel.abline(v = 1.5);
+            panel.abline(v = 2.5);
+            panel.abline(v = 3.5);
+            panel.abline(v = 4.5);
+            panel.abline(v = 5.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 7.5);
+            panel.abline(v = 8.5);
+            panel.abline(v = 9.5);
+            panel.abline(v = 10.5);
+            panel.abline(v = 11.5);
+            panel.abline(v = 12.5);
+            panel.abline(v = 13.5);
+            panel.abline(v = 14.5);
+            panel.abline(v = 15.5);
+            panel.abline(v = 16.5, col="yellow");
+            panel.abline(v = 17.5);
+            panel.abline(v = 18.5);
+            panel.abline(v = 19.5);
+            panel.abline(v = 20.5);
+            panel.abline(v = 21.5);
+            panel.abline(v = 22.5);
+            panel.abline(v = 23.5);
+            panel.abline(v = 24.5);
+            panel.abline(v = 25.5);
+            panel.abline(v = 26.5);
+            panel.abline(v = 27.5);
+            panel.abline(v = 28.5);
+            panel.abline(v = 29.5);
+            panel.abline(v = 30.5);
+            panel.abline(v = 31.5);
+            panel.abline(v = 32.5, col="yellow");
+            panel.abline(v = 33.5);
+            panel.abline(v = 34.5);
+            panel.abline(v = 35.5);
+            panel.abline(v = 36.5);
+            panel.abline(v = 37.5);
+            panel.abline(v = 38.5);
+            panel.abline(v = 39.5);
+            panel.abline(v = 40.5);
+            panel.abline(v = 41.5);
+            panel.abline(v = 42.5);
+            panel.abline(v = 43.5);
+            panel.abline(v = 44.5);
+            panel.abline(v = 45.5);
+            panel.abline(v = 46.5);
+            panel.abline(v = 47.5);
+          },
+          xlab="",
+          ylab="")
+```
+
+### K562
+
+####10kb
 
@@
 train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x10_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p10kb_k562 <- ggplot(x10_k562, aes(y=IR, x=factor(CB, levels = unique(x10_k562$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_10kb_K562, 
+                      enetcoefs_none_op_10kb_K562, 
+                      enetcoefs_none_dist_10kb_K562,
+                      enetcoefs_RUS_oc_10kb_K562, 
+                      enetcoefs_RUS_op_10kb_K562, 
+                      enetcoefs_RUS_dist_10kb_K562,
+                      enetcoefs_ROS_oc_10kb_K562, 
+                      enetcoefs_ROS_op_10kb_K562, 
+                      enetcoefs_ROS_dist_10kb_K562,
+                      enetcoefs_SMOTE_oc_10kb_K562, 
+                      enetcoefs_SMOTE_op_10kb_K562, 
+                      enetcoefs_SMOTE_dist_10kb_K562)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_10kb_k562 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_10kb_k562[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_10kb_k562), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
 
@@
 train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x25_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p25kb_k562 <- ggplot(x25_k562, aes(y=IR, x=factor(CB, levels = unique(x25_k562$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_25kb_K562, 
+                      enetcoefs_none_op_25kb_K562, 
+                      enetcoefs_none_dist_25kb_K562,
+                      enetcoefs_RUS_oc_25kb_K562, 
+                      enetcoefs_RUS_op_25kb_K562, 
+                      enetcoefs_RUS_dist_25kb_K562,
+                      enetcoefs_ROS_oc_25kb_K562, 
+                      enetcoefs_ROS_op_25kb_K562, 
+                      enetcoefs_ROS_dist_25kb_K562,
+                      enetcoefs_SMOTE_oc_25kb_K562, 
+                      enetcoefs_SMOTE_op_25kb_K562, 
+                      enetcoefs_SMOTE_dist_25kb_K562)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_25kb_k562 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_25kb_k562[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_25kb_k562), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
 
@@
 train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x50_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p50kb_k562 <- ggplot(x50_k562, aes(y=IR, x=factor(CB, levels = unique(x50_k562$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_50kb_K562, 
+                      enetcoefs_none_op_50kb_K562, 
+                      enetcoefs_none_dist_50kb_K562,
+                      enetcoefs_RUS_oc_50kb_K562, 
+                      enetcoefs_RUS_op_50kb_K562, 
+                      enetcoefs_RUS_dist_50kb_K562,
+                      enetcoefs_ROS_oc_50kb_K562, 
+                      enetcoefs_ROS_op_50kb_K562, 
+                      enetcoefs_ROS_dist_50kb_K562,
+                      enetcoefs_SMOTE_oc_50kb_K562, 
+                      enetcoefs_SMOTE_op_50kb_K562, 
+                      enetcoefs_SMOTE_dist_50kb_K562)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_50kb_k562 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_50kb_k562[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_50kb_k562), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
 
@@
 train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/test.rds")
-
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
-
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
-
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x100_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p100kb_k562 <- ggplot(x100_k562, aes(y=IR, x=factor(CB, levels = unique(x100_k562$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_none_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_none_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+
+#RUS
+##OC
+enetcoefs_RUS_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_RUS_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_RUS_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+
+#ROS
+##OC
+enetcoefs_ROS_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_ROS_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_ROS_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
+##OP
+enetcoefs_SMOTE_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
+##Distance
+enetcoefs_SMOTE_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+
+enetcoefslist <- list(enetcoefs_none_oc_100kb_K562, 
+                      enetcoefs_none_op_100kb_K562, 
+                      enetcoefs_none_dist_100kb_K562,
+                      enetcoefs_RUS_oc_100kb_K562, 
+                      enetcoefs_RUS_op_100kb_K562, 
+                      enetcoefs_RUS_dist_100kb_K562,
+                      enetcoefs_ROS_oc_100kb_K562, 
+                      enetcoefs_ROS_op_100kb_K562, 
+                      enetcoefs_ROS_dist_100kb_K562,
+                      enetcoefs_SMOTE_oc_100kb_K562, 
+                      enetcoefs_SMOTE_op_100kb_K562, 
+                      enetcoefs_SMOTE_dist_100kb_K562)
+
+enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+
+featuremat_100kb_k562 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
+                                                                    "Predictor Type"=rep(c("OC",
+                                                                                         "OP", 
+                                                                                         "Distance"),4)))
+
+for(j in 1:length(enetcoefslist)){
+    featuremat_100kb_k562[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+}
+
+#using lattice
+levelplot(t(featuremat_100kb_k562), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45),
+                      alternating=3), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+            panel.abline(v = 3.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 9.5);
+          },
+          xlab="",
+          ylab="")
+grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
+grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
+grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
+grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
 
@@
 
-##Combined
+####Combined
+
 ```{r}
-
-IR=c(x10$IR[x10$CB=="Complete"],
-                              x25$IR[x25$CB=="Complete"],
-                              x50$IR[x50$CB=="Complete"],
-                              x100$IR[x100$CB=="Complete"],
-                              x10_k562$IR[x10_k562$CB=="Complete"], 
-                              x25_k562$IR[x25_k562$CB=="Complete"],
-                              x50_k562$IR[x50_k562$CB=="Complete"],
-                              x100_k562$IR[x100_k562$CB=="Complete"])
-CL <- c(rep("GM12878", 4), 
-                  rep("K562", 4))
-Resolution <- c(rep(c("10 kb", "25 kb", "50 kb", "100 kb"), 2))
-
-allirdata <- cbind.data.frame(IR, CL, Resolution)
-allirdata$CL <- factor(allirdata$CL, levels=c("GM12878", "K562"))
-allirdata$Resolution <- factor(allirdata$Resolution, c("10 kb", "25 kb", "50 kb", "100 kb"))
-
-allirplots <- ggplot(allirdata, aes(x = Resolution, y = IR,fill = CL)) + 
-  geom_bar(position = "dodge", stat="identity") + 
-  ylab("Imbalance Ratio") +
-  xlab("Resolution") +
-  #scale_fill_manual(name="Cell Line", values=c("red", "blue"))+
-  labs(fill="Cell Line")+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=10),
-        axis.text.y = element_text(size = 10),
-        axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
+all_featuremat_k562 <- cbind(featuremat_10kb_k562,
+                                featuremat_25kb_k562,
+                                featuremat_50kb_k562,
+                                featuremat_100kb_k562)
+all_featuremat_k562 <- all_featuremat_k562[,c(seq(1,48,3),
+                                                    seq(2,48,3),
+                                                    seq(3,48,3))]
+colnames(all_featuremat_k562) <- rep(c("None", "RUS", "ROS", "SMOTE"), 12)
+
+levelplot(t(all_featuremat_k562), 
+          colorkey=FALSE, 
+          scales=list(x=list(rot=45, cex=.5),
+                      #alternating=3,
+                      y=list(cex=.5)), 
+          col.regions=c("white", "red"),
+          aspect="fill",panel = function(...){
+            panel.levelplot(...)
+			#horizontal lines
+			panel.abline(h = 1.5);
+			panel.abline(h = 2.5);
+			panel.abline(h = 3.5);
+			panel.abline(h = 4.5);
+			panel.abline(h = 5.5);
+			panel.abline(h = 6.5);
+			panel.abline(h = 7.5);
+			panel.abline(h = 8.5);
+			panel.abline(h = 9.5);
+			panel.abline(h = 10.5);
+			panel.abline(h = 11.5);
+			panel.abline(h = 12.5);
+			panel.abline(h = 13.5);
+			panel.abline(h = 14.5);
+			panel.abline(h = 15.5);
+			panel.abline(h = 16.5);
+			panel.abline(h = 17.5);
+			panel.abline(h = 18.5);
+			panel.abline(h = 19.5);
+			panel.abline(h = 20.5);
+			panel.abline(h = 21.5);
+			panel.abline(h = 22.5);
+			panel.abline(h = 23.5);
+			panel.abline(h = 24.5);
+			panel.abline(h = 25.5);
+			panel.abline(h = 26.5);
+			panel.abline(h = 27.5);
+			panel.abline(h = 28.5);
+			panel.abline(h = 29.5);
+			panel.abline(h = 30.5);
+			panel.abline(h = 31.5);
+			panel.abline(h = 32.5);
+			panel.abline(h = 33.5);
+			panel.abline(h = 34.5);
+			panel.abline(h = 35.5);
+			panel.abline(h = 36.5);
+			panel.abline(h = 37.5);
+			panel.abline(h = 38.5);
+			panel.abline(h = 39.5);
+			panel.abline(h = 40.5);
+			panel.abline(h = 41.5);
+			panel.abline(h = 42.5);
+			panel.abline(h = 43.5);
+			panel.abline(h = 44.5);
+			panel.abline(h = 45.5);
+			panel.abline(h = 46.5);
+			panel.abline(h = 47.5);
+			panel.abline(h = 48.5);
+			panel.abline(h = 49.5);
+			panel.abline(h = 50.5);
+			panel.abline(h = 50.5);
+			panel.abline(h = 51.5);
+			panel.abline(h = 52.5);
+			panel.abline(h = 53.5);
+			panel.abline(h = 54.5);
+			panel.abline(h = 55.5);
+			panel.abline(h = 56.5);
+			panel.abline(h = 57.5);
+			panel.abline(h = 58.5);
+			panel.abline(h = 59.5);
+			panel.abline(h = 60.5);
+			panel.abline(h = 61.5);
+			panel.abline(h = 62.5);
+			panel.abline(h = 63.5);
+			panel.abline(h = 64.5);
+			panel.abline(h = 65.5);
+			panel.abline(h = 66.5);
+			panel.abline(h = 67.5);
+			panel.abline(h = 68.5);
+			panel.abline(h = 69.5);
+			panel.abline(h = 70.5);
+			panel.abline(h = 71.5);
+			panel.abline(h = 72.5);
+			panel.abline(h = 73.5);
+			panel.abline(h = 74.5);
+			panel.abline(h = 75.5);
+			panel.abline(h = 76.5);
+			panel.abline(h = 77.5);
+			panel.abline(h = 78.5);
+			panel.abline(h = 79.5);
+			panel.abline(h = 80.5);
+			panel.abline(h = 81.5);
+			panel.abline(h = 82.5);
+			panel.abline(h = 83.5);
+			panel.abline(h = 84.5);
+			panel.abline(h = 85.5);
+			panel.abline(h = 86.5);
+			panel.abline(h = 87.5);
+			panel.abline(h = 88.5);
+			panel.abline(h = 89.5);
+			panel.abline(h = 90.5);
+			panel.abline(h = 91.5);
+			panel.abline(h = 92.5);
+			panel.abline(h = 93.5);
+			panel.abline(h = 94.5);
+			panel.abline(h = 95.5);
+			panel.abline(h = 96.5);
+			panel.abline(h = 97.5);
+			panel.abline(h = 98.5);
+			panel.abline(h = 99.5);
+			panel.abline(h = 100.5);
+			panel.abline(h = 101.5);
+			panel.abline(h = 102.5);
+			panel.abline(h = 103.5);
+			panel.abline(h = 104.5);
+			panel.abline(h = 105.5);
+			panel.abline(h = 106.5);
+			panel.abline(h = 107.5);
+			panel.abline(h = 108.5);
+			panel.abline(h = 109.5);
+			panel.abline(h = 110.5);
+			panel.abline(h = 111.5);
+			panel.abline(h = 112.5);
+			panel.abline(h = 113.5);
+			panel.abline(h = 114.5);
+			panel.abline(h = 115.5);
+			panel.abline(h = 116.5);
+			panel.abline(h = 117.5);
+			panel.abline(h = 118.5);
+			panel.abline(h = 119.5);
+			panel.abline(h = 120.5);
+			panel.abline(h = 121.5);
+			panel.abline(h = 122.5);
+			panel.abline(h = 123.5);
+			panel.abline(h = 124.5);
+			panel.abline(h = 125.5);
+			panel.abline(h = 126.5);
+			panel.abline(h = 127.5);
+			panel.abline(h = 128.5);
+			panel.abline(h = 129.5);
+			panel.abline(h = 130.5);
+			panel.abline(h = 131.5);
+			panel.abline(h = 132.5);
+			panel.abline(h = 133.5);
+			panel.abline(h = 134.5);
+			panel.abline(h = 135.5);
+			panel.abline(h = 136.5);
+			panel.abline(h = 137.5);
+
+			#vertical lines
+            panel.abline(v = 1.5);
+            panel.abline(v = 2.5);
+            panel.abline(v = 3.5);
+            panel.abline(v = 4.5);
+            panel.abline(v = 5.5);
+            panel.abline(v = 6.5);
+            panel.abline(v = 7.5);
+            panel.abline(v = 8.5);
+            panel.abline(v = 9.5);
+            panel.abline(v = 10.5);
+            panel.abline(v = 11.5);
+            panel.abline(v = 12.5);
+            panel.abline(v = 13.5);
+            panel.abline(v = 14.5);
+            panel.abline(v = 15.5);
+            panel.abline(v = 16.5, col="yellow");
+            panel.abline(v = 17.5);
+            panel.abline(v = 18.5);
+            panel.abline(v = 19.5);
+            panel.abline(v = 20.5);
+            panel.abline(v = 21.5);
+            panel.abline(v = 22.5);
+            panel.abline(v = 23.5);
+            panel.abline(v = 24.5);
+            panel.abline(v = 25.5);
+            panel.abline(v = 26.5);
+            panel.abline(v = 27.5);
+            panel.abline(v = 28.5);
+            panel.abline(v = 29.5);
+            panel.abline(v = 30.5);
+            panel.abline(v = 31.5);
+            panel.abline(v = 32.5, col="yellow");
+            panel.abline(v = 33.5);
+            panel.abline(v = 34.5);
+            panel.abline(v = 35.5);
+            panel.abline(v = 36.5);
+            panel.abline(v = 37.5);
+            panel.abline(v = 38.5);
+            panel.abline(v = 39.5);
+            panel.abline(v = 40.5);
+            panel.abline(v = 41.5);
+            panel.abline(v = 42.5);
+            panel.abline(v = 43.5);
+            panel.abline(v = 44.5);
+            panel.abline(v = 45.5);
+            panel.abline(v = 46.5);
+            panel.abline(v = 47.5);
+          },
+          xlab="",
+          ylab="")
 ```
-
-#Evaluating Feature Engineering
-
-## PR Curves
-
-###GM12878
-
-####10kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####25kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####50kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####100kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-###K562
-
-####10kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.431)","All (AUPRC: 0.358)", "Counts (AUPRC: 0.209)","Percents (AUPRC: 0.202)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####25kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.436)","All (AUPRC: 0.380)", "Percents (AUPRC: 0.239)","Counts (AUPRC: 0.231)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####50kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.405)","All (AUPRC: 0.367)", "Percents (AUPRC: 0.218)","Counts (AUPRC: 0.212)", "Baseline"),
-#       col=c("red", "black", "green", "blue", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-####100kb
-
-#####None
-
-```{r}
-
-prall_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_None$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_None$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_None$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_None$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####RUS
-
-```{r}
-prall_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_RUS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_RUS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_RUS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_RUS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROS
-
-```{r}
-prall_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROS$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROS$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROS$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROS$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####SMOTE
-
-```{r}
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_SMOTE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-#####ROSE
-
-```{r}
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-#plot(prall, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, rand.plot = TRUE)
-plot(prall_ROSE$curve, auc.main= FALSE, legend=FALSE, col='black', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")
-lines(prdist_ROSE$curve, auc.main= FALSE, legend=FALSE, col='red', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, xlab="Recall", ylab="Precision")#, add=TRUE)
-lines(proc_ROSE$curve, auc.main= FALSE, legend=FALSE, col='blue', panel.first= grid(), cex.main = 1.5, type="l",lwd=2, add=TRUE)
-lines(prop_ROSE$curve, auc.main= FALSE, legend=FALSE, col='green', panel.first= grid(), cex.main = 1.5, type="l", ylim=c(0,1), lwd=2, add=TRUE)
-
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
-abline(h = sum(test$y=="Yes")/(sum(test$y=="Yes") + sum(test$y=="No")), col="black", lty=2)
-
-#legend("topright", title="Predictor Type", legend=c("Distance (AUPRC: 0.361)","All (AUPRC: 0.301)", "Counts (AUPRC: 0.175)", "Percents (AUPRC: 0.156)", "Baseline"),
-#       col=c("red", "black", "blue", "green", "black"), lty=c(1,1,1,1,2), lwd=c(3,3,3,3,1), cex=0.8)
-
-```
-
-###Combined
-
-```{r}
-#10kb
-##None
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_None_10kb <- rbind.data.frame(prall_None$curve,
-                                prdist_None$curve,
-                                prop_None$curve,
-                                proc_None$curve,
-                                prall_None_k562$curve,
-                                prdist_None_k562$curve,
-                                prop_None_k562$curve,
-                                proc_None_k562$curve)
-names(prdata_None_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_None_10kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
-                           rep("Distance", dim(prdist_None$curve)[1]),
-                           rep("OP", dim(prop_None$curve)[1]),
-                           rep("OC", dim(proc_None$curve)[1]),
-                           rep("All", dim(prall_None_k562$curve)[1]),
-                           rep("Distance", dim(prdist_None_k562$curve)[1]),
-                           rep("OP", dim(prop_None_k562$curve)[1]),
-                           rep("OC", dim(proc_None_k562$curve)[1]))
-prdata_None_10kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
-                                      dim(prdist_None$curve)[1]+
-                                      dim(prop_None$curve)[1]+
-                                      dim(proc_None$curve)[1])),
-                    rep("K562", (dim(prall_None_k562$curve)[1]+
-                                      dim(prdist_None_k562$curve)[1]+
-                                      dim(prop_None_k562$curve)[1]+
-                                      dim(proc_None_k562$curve)[1])))
-prdata_None_10kb$Predictor <- factor(prdata_None_10kb$Predictor)
-prdata_None_10kb$CL <- factor(prdata_None_10kb$CL)
-
-prplot_None_10kb <- ggplot(prdata_None_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##RUS
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prdata_RUS_10kb <- rbind.data.frame(prall_RUS$curve,
-                                prdist_RUS$curve,
-                                prop_RUS$curve,
-                                proc_RUS$curve,
-                                prall_RUS_k562$curve,
-                                prdist_RUS_k562$curve,
-                                prop_RUS_k562$curve,
-                                proc_RUS_k562$curve)
-names(prdata_RUS_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_RUS_10kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
-                           rep("Distance", dim(prdist_RUS$curve)[1]),
-                           rep("OP", dim(prop_RUS$curve)[1]),
-                           rep("OC", dim(proc_RUS$curve)[1]),
-                           rep("All", dim(prall_RUS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
-                           rep("OP", dim(prop_RUS_k562$curve)[1]),
-                           rep("OC", dim(proc_RUS_k562$curve)[1]))
-prdata_RUS_10kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
-                                      dim(prdist_RUS$curve)[1]+
-                                      dim(prop_RUS$curve)[1]+
-                                      dim(proc_RUS$curve)[1])),
-                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
-                                      dim(prdist_RUS_k562$curve)[1]+
-                                      dim(prop_RUS_k562$curve)[1]+
-                                      dim(proc_RUS_k562$curve)[1])))
-prdata_RUS_10kb$Predictor <- factor(prdata_RUS_10kb$Predictor)
-prdata_RUS_10kb$CL <- factor(prdata_RUS_10kb$CL)
-
-prplot_RUS_10kb <- ggplot(prdata_RUS_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROS
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prdata_ROS_10kb <- rbind.data.frame(prall_ROS$curve,
-                                prdist_ROS$curve,
-                                prop_ROS$curve,
-                                proc_ROS$curve,
-                                prall_ROS_k562$curve,
-                                prdist_ROS_k562$curve,
-                                prop_ROS_k562$curve,
-                                proc_ROS_k562$curve)
-names(prdata_ROS_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROS_10kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
-                           rep("Distance", dim(prdist_ROS$curve)[1]),
-                           rep("OP", dim(prop_ROS$curve)[1]),
-                           rep("OC", dim(proc_ROS$curve)[1]),
-                           rep("All", dim(prall_ROS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
-                           rep("OP", dim(prop_ROS_k562$curve)[1]),
-                           rep("OC", dim(proc_ROS_k562$curve)[1]))
-prdata_ROS_10kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
-                                      dim(prdist_ROS$curve)[1]+
-                                      dim(prop_ROS$curve)[1]+
-                                      dim(proc_ROS$curve)[1])),
-                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
-                                      dim(prdist_ROS_k562$curve)[1]+
-                                      dim(prop_ROS_k562$curve)[1]+
-                                      dim(proc_ROS_k562$curve)[1])))
-prdata_ROS_10kb$Predictor <- factor(prdata_ROS_10kb$Predictor)
-prdata_ROS_10kb$CL <- factor(prdata_ROS_10kb$CL)
-
-prplot_ROS_10kb <- ggplot(prdata_ROS_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##SMOTE
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prdata_SMOTE_10kb <- rbind.data.frame(prall_SMOTE$curve,
-                                prdist_SMOTE$curve,
-                                prop_SMOTE$curve,
-                                proc_SMOTE$curve,
-                                prall_SMOTE_k562$curve,
-                                prdist_SMOTE_k562$curve,
-                                prop_SMOTE_k562$curve,
-                                proc_SMOTE_k562$curve)
-names(prdata_SMOTE_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_SMOTE_10kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
-                           rep("OP", dim(prop_SMOTE$curve)[1]),
-                           rep("OC", dim(proc_SMOTE$curve)[1]),
-                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
-                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
-                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
-prdata_SMOTE_10kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
-                                      dim(prdist_SMOTE$curve)[1]+
-                                      dim(prop_SMOTE$curve)[1]+
-                                      dim(proc_SMOTE$curve)[1])),
-                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
-                                      dim(prdist_SMOTE_k562$curve)[1]+
-                                      dim(prop_SMOTE_k562$curve)[1]+
-                                      dim(proc_SMOTE_k562$curve)[1])))
-prdata_SMOTE_10kb$Predictor <- factor(prdata_SMOTE_10kb$Predictor)
-prdata_SMOTE_10kb$CL <- factor(prdata_SMOTE_10kb$CL)
-
-prplot_SMOTE_10kb <- ggplot(prdata_SMOTE_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROSE
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prdata_ROSE_10kb <- rbind.data.frame(prall_ROSE$curve,
-                                prdist_ROSE$curve,
-                                prop_ROSE$curve,
-                                proc_ROSE$curve,
-                                prall_ROSE_k562$curve,
-                                prdist_ROSE_k562$curve,
-                                prop_ROSE_k562$curve,
-                                proc_ROSE_k562$curve)
-names(prdata_ROSE_10kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROSE_10kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE$curve)[1]),
-                           rep("OP", dim(prop_ROSE$curve)[1]),
-                           rep("OC", dim(proc_ROSE$curve)[1]),
-                           rep("All", dim(prall_ROSE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
-                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
-                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
-prdata_ROSE_10kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
-                                      dim(prdist_ROSE$curve)[1]+
-                                      dim(prop_ROSE$curve)[1]+
-                                      dim(proc_ROSE$curve)[1])),
-                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
-                                      dim(prdist_ROSE_k562$curve)[1]+
-                                      dim(prop_ROSE_k562$curve)[1]+
-                                      dim(proc_ROSE_k562$curve)[1])))
-prdata_ROSE_10kb$Predictor <- factor(prdata_ROSE_10kb$Predictor)
-prdata_ROSE_10kb$CL <- factor(prdata_ROSE_10kb$CL)
-
-prplot_ROSE_10kb <- ggplot(prdata_ROSE_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##Collecting 10kb plots
-ggarrange(prplot_None_10kb,
-          prplot_RUS_10kb,
-          prplot_ROS_10kb,
-          prplot_SMOTE_10kb,
-          prplot_ROSE_10kb,
-          nrow=3,ncol=2,
-          common.legend = TRUE, legend = "right")
-
-#######################################################################################
-
-#25kb
-##None
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_None_25kb <- rbind.data.frame(prall_None$curve,
-                                prdist_None$curve,
-                                prop_None$curve,
-                                proc_None$curve,
-                                prall_None_k562$curve,
-                                prdist_None_k562$curve,
-                                prop_None_k562$curve,
-                                proc_None_k562$curve)
-names(prdata_None_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_None_25kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
-                           rep("Distance", dim(prdist_None$curve)[1]),
-                           rep("OP", dim(prop_None$curve)[1]),
-                           rep("OC", dim(proc_None$curve)[1]),
-                           rep("All", dim(prall_None_k562$curve)[1]),
-                           rep("Distance", dim(prdist_None_k562$curve)[1]),
-                           rep("OP", dim(prop_None_k562$curve)[1]),
-                           rep("OC", dim(proc_None_k562$curve)[1]))
-prdata_None_25kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
-                                      dim(prdist_None$curve)[1]+
-                                      dim(prop_None$curve)[1]+
-                                      dim(proc_None$curve)[1])),
-                    rep("K562", (dim(prall_None_k562$curve)[1]+
-                                      dim(prdist_None_k562$curve)[1]+
-                                      dim(prop_None_k562$curve)[1]+
-                                      dim(proc_None_k562$curve)[1])))
-prdata_None_25kb$Predictor <- factor(prdata_None_25kb$Predictor)
-prdata_None_25kb$CL <- factor(prdata_None_25kb$CL)
-
-prplot_None_25kb <- ggplot(prdata_None_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##RUS
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prdata_RUS_25kb <- rbind.data.frame(prall_RUS$curve,
-                                prdist_RUS$curve,
-                                prop_RUS$curve,
-                                proc_RUS$curve,
-                                prall_RUS_k562$curve,
-                                prdist_RUS_k562$curve,
-                                prop_RUS_k562$curve,
-                                proc_RUS_k562$curve)
-names(prdata_RUS_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_RUS_25kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
-                           rep("Distance", dim(prdist_RUS$curve)[1]),
-                           rep("OP", dim(prop_RUS$curve)[1]),
-                           rep("OC", dim(proc_RUS$curve)[1]),
-                           rep("All", dim(prall_RUS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
-                           rep("OP", dim(prop_RUS_k562$curve)[1]),
-                           rep("OC", dim(proc_RUS_k562$curve)[1]))
-prdata_RUS_25kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
-                                      dim(prdist_RUS$curve)[1]+
-                                      dim(prop_RUS$curve)[1]+
-                                      dim(proc_RUS$curve)[1])),
-                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
-                                      dim(prdist_RUS_k562$curve)[1]+
-                                      dim(prop_RUS_k562$curve)[1]+
-                                      dim(proc_RUS_k562$curve)[1])))
-prdata_RUS_25kb$Predictor <- factor(prdata_RUS_25kb$Predictor)
-prdata_RUS_25kb$CL <- factor(prdata_RUS_25kb$CL)
-
-prplot_RUS_25kb <- ggplot(prdata_RUS_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROS
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prdata_ROS_25kb <- rbind.data.frame(prall_ROS$curve,
-                                prdist_ROS$curve,
-                                prop_ROS$curve,
-                                proc_ROS$curve,
-                                prall_ROS_k562$curve,
-                                prdist_ROS_k562$curve,
-                                prop_ROS_k562$curve,
-                                proc_ROS_k562$curve)
-names(prdata_ROS_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROS_25kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
-                           rep("Distance", dim(prdist_ROS$curve)[1]),
-                           rep("OP", dim(prop_ROS$curve)[1]),
-                           rep("OC", dim(proc_ROS$curve)[1]),
-                           rep("All", dim(prall_ROS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
-                           rep("OP", dim(prop_ROS_k562$curve)[1]),
-                           rep("OC", dim(proc_ROS_k562$curve)[1]))
-prdata_ROS_25kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
-                                      dim(prdist_ROS$curve)[1]+
-                                      dim(prop_ROS$curve)[1]+
-                                      dim(proc_ROS$curve)[1])),
-                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
-                                      dim(prdist_ROS_k562$curve)[1]+
-                                      dim(prop_ROS_k562$curve)[1]+
-                                      dim(proc_ROS_k562$curve)[1])))
-prdata_ROS_25kb$Predictor <- factor(prdata_ROS_25kb$Predictor)
-prdata_ROS_25kb$CL <- factor(prdata_ROS_25kb$CL)
-
-prplot_ROS_25kb <- ggplot(prdata_ROS_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##SMOTE
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prdata_SMOTE_25kb <- rbind.data.frame(prall_SMOTE$curve,
-                                prdist_SMOTE$curve,
-                                prop_SMOTE$curve,
-                                proc_SMOTE$curve,
-                                prall_SMOTE_k562$curve,
-                                prdist_SMOTE_k562$curve,
-                                prop_SMOTE_k562$curve,
-                                proc_SMOTE_k562$curve)
-names(prdata_SMOTE_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_SMOTE_25kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
-                           rep("OP", dim(prop_SMOTE$curve)[1]),
-                           rep("OC", dim(proc_SMOTE$curve)[1]),
-                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
-                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
-                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
-prdata_SMOTE_25kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
-                                      dim(prdist_SMOTE$curve)[1]+
-                                      dim(prop_SMOTE$curve)[1]+
-                                      dim(proc_SMOTE$curve)[1])),
-                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
-                                      dim(prdist_SMOTE_k562$curve)[1]+
-                                      dim(prop_SMOTE_k562$curve)[1]+
-                                      dim(proc_SMOTE_k562$curve)[1])))
-prdata_SMOTE_25kb$Predictor <- factor(prdata_SMOTE_25kb$Predictor)
-prdata_SMOTE_25kb$CL <- factor(prdata_SMOTE_25kb$CL)
-
-prplot_SMOTE_25kb <- ggplot(prdata_SMOTE_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROSE
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prdata_ROSE_25kb <- rbind.data.frame(prall_ROSE$curve,
-                                prdist_ROSE$curve,
-                                prop_ROSE$curve,
-                                proc_ROSE$curve,
-                                prall_ROSE_k562$curve,
-                                prdist_ROSE_k562$curve,
-                                prop_ROSE_k562$curve,
-                                proc_ROSE_k562$curve)
-names(prdata_ROSE_25kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROSE_25kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE$curve)[1]),
-                           rep("OP", dim(prop_ROSE$curve)[1]),
-                           rep("OC", dim(proc_ROSE$curve)[1]),
-                           rep("All", dim(prall_ROSE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
-                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
-                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
-prdata_ROSE_25kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
-                                      dim(prdist_ROSE$curve)[1]+
-                                      dim(prop_ROSE$curve)[1]+
-                                      dim(proc_ROSE$curve)[1])),
-                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
-                                      dim(prdist_ROSE_k562$curve)[1]+
-                                      dim(prop_ROSE_k562$curve)[1]+
-                                      dim(proc_ROSE_k562$curve)[1])))
-prdata_ROSE_25kb$Predictor <- factor(prdata_ROSE_25kb$Predictor)
-prdata_ROSE_25kb$CL <- factor(prdata_ROSE_25kb$CL)
-
-prplot_ROSE_25kb <- ggplot(prdata_ROSE_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-###############################################################################
-
-#50kb
-##None
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_None_50kb <- rbind.data.frame(prall_None$curve,
-                                prdist_None$curve,
-                                prop_None$curve,
-                                proc_None$curve,
-                                prall_None_k562$curve,
-                                prdist_None_k562$curve,
-                                prop_None_k562$curve,
-                                proc_None_k562$curve)
-names(prdata_None_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_None_50kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
-                           rep("Distance", dim(prdist_None$curve)[1]),
-                           rep("OP", dim(prop_None$curve)[1]),
-                           rep("OC", dim(proc_None$curve)[1]),
-                           rep("All", dim(prall_None_k562$curve)[1]),
-                           rep("Distance", dim(prdist_None_k562$curve)[1]),
-                           rep("OP", dim(prop_None_k562$curve)[1]),
-                           rep("OC", dim(proc_None_k562$curve)[1]))
-prdata_None_50kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
-                                      dim(prdist_None$curve)[1]+
-                                      dim(prop_None$curve)[1]+
-                                      dim(proc_None$curve)[1])),
-                    rep("K562", (dim(prall_None_k562$curve)[1]+
-                                      dim(prdist_None_k562$curve)[1]+
-                                      dim(prop_None_k562$curve)[1]+
-                                      dim(proc_None_k562$curve)[1])))
-prdata_None_50kb$Predictor <- factor(prdata_None_50kb$Predictor)
-prdata_None_50kb$CL <- factor(prdata_None_50kb$CL)
-
-prplot_None_50kb <- ggplot(prdata_None_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##RUS
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prdata_RUS_50kb <- rbind.data.frame(prall_RUS$curve,
-                                prdist_RUS$curve,
-                                prop_RUS$curve,
-                                proc_RUS$curve,
-                                prall_RUS_k562$curve,
-                                prdist_RUS_k562$curve,
-                                prop_RUS_k562$curve,
-                                proc_RUS_k562$curve)
-names(prdata_RUS_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_RUS_50kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
-                           rep("Distance", dim(prdist_RUS$curve)[1]),
-                           rep("OP", dim(prop_RUS$curve)[1]),
-                           rep("OC", dim(proc_RUS$curve)[1]),
-                           rep("All", dim(prall_RUS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
-                           rep("OP", dim(prop_RUS_k562$curve)[1]),
-                           rep("OC", dim(proc_RUS_k562$curve)[1]))
-prdata_RUS_50kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
-                                      dim(prdist_RUS$curve)[1]+
-                                      dim(prop_RUS$curve)[1]+
-                                      dim(proc_RUS$curve)[1])),
-                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
-                                      dim(prdist_RUS_k562$curve)[1]+
-                                      dim(prop_RUS_k562$curve)[1]+
-                                      dim(proc_RUS_k562$curve)[1])))
-prdata_RUS_50kb$Predictor <- factor(prdata_RUS_50kb$Predictor)
-prdata_RUS_50kb$CL <- factor(prdata_RUS_50kb$CL)
-
-prplot_RUS_50kb <- ggplot(prdata_RUS_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROS
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prdata_ROS_50kb <- rbind.data.frame(prall_ROS$curve,
-                                prdist_ROS$curve,
-                                prop_ROS$curve,
-                                proc_ROS$curve,
-                                prall_ROS_k562$curve,
-                                prdist_ROS_k562$curve,
-                                prop_ROS_k562$curve,
-                                proc_ROS_k562$curve)
-names(prdata_ROS_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROS_50kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
-                           rep("Distance", dim(prdist_ROS$curve)[1]),
-                           rep("OP", dim(prop_ROS$curve)[1]),
-                           rep("OC", dim(proc_ROS$curve)[1]),
-                           rep("All", dim(prall_ROS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
-                           rep("OP", dim(prop_ROS_k562$curve)[1]),
-                           rep("OC", dim(proc_ROS_k562$curve)[1]))
-prdata_ROS_50kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
-                                      dim(prdist_ROS$curve)[1]+
-                                      dim(prop_ROS$curve)[1]+
-                                      dim(proc_ROS$curve)[1])),
-                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
-                                      dim(prdist_ROS_k562$curve)[1]+
-                                      dim(prop_ROS_k562$curve)[1]+
-                                      dim(proc_ROS_k562$curve)[1])))
-prdata_ROS_50kb$Predictor <- factor(prdata_ROS_50kb$Predictor)
-prdata_ROS_50kb$CL <- factor(prdata_ROS_50kb$CL)
-
-prplot_ROS_50kb <- ggplot(prdata_ROS_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##SMOTE
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prdata_SMOTE_50kb <- rbind.data.frame(prall_SMOTE$curve,
-                                prdist_SMOTE$curve,
-                                prop_SMOTE$curve,
-                                proc_SMOTE$curve,
-                                prall_SMOTE_k562$curve,
-                                prdist_SMOTE_k562$curve,
-                                prop_SMOTE_k562$curve,
-                                proc_SMOTE_k562$curve)
-names(prdata_SMOTE_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_SMOTE_50kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
-                           rep("OP", dim(prop_SMOTE$curve)[1]),
-                           rep("OC", dim(proc_SMOTE$curve)[1]),
-                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
-                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
-                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
-prdata_SMOTE_50kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
-                                      dim(prdist_SMOTE$curve)[1]+
-                                      dim(prop_SMOTE$curve)[1]+
-                                      dim(proc_SMOTE$curve)[1])),
-                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
-                                      dim(prdist_SMOTE_k562$curve)[1]+
-                                      dim(prop_SMOTE_k562$curve)[1]+
-                                      dim(proc_SMOTE_k562$curve)[1])))
-prdata_SMOTE_50kb$Predictor <- factor(prdata_SMOTE_50kb$Predictor)
-prdata_SMOTE_50kb$CL <- factor(prdata_SMOTE_50kb$CL)
-
-prplot_SMOTE_50kb <- ggplot(prdata_SMOTE_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROSE
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prdata_ROSE_50kb <- rbind.data.frame(prall_ROSE$curve,
-                                prdist_ROSE$curve,
-                                prop_ROSE$curve,
-                                proc_ROSE$curve,
-                                prall_ROSE_k562$curve,
-                                prdist_ROSE_k562$curve,
-                                prop_ROSE_k562$curve,
-                                proc_ROSE_k562$curve)
-names(prdata_ROSE_50kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROSE_50kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE$curve)[1]),
-                           rep("OP", dim(prop_ROSE$curve)[1]),
-                           rep("OC", dim(proc_ROSE$curve)[1]),
-                           rep("All", dim(prall_ROSE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
-                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
-                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
-prdata_ROSE_50kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
-                                      dim(prdist_ROSE$curve)[1]+
-                                      dim(prop_ROSE$curve)[1]+
-                                      dim(proc_ROSE$curve)[1])),
-                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
-                                      dim(prdist_ROSE_k562$curve)[1]+
-                                      dim(prop_ROSE_k562$curve)[1]+
-                                      dim(proc_ROSE_k562$curve)[1])))
-prdata_ROSE_50kb$Predictor <- factor(prdata_ROSE_50kb$Predictor)
-prdata_ROSE_50kb$CL <- factor(prdata_ROSE_50kb$CL)
-
-prplot_ROSE_50kb <- ggplot(prdata_ROSE_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-###########################################################################
-
-#100kb
-##None
-prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")
-prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
-proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/oc/RFE/prcurve.rds")
-prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/op/RFE/prcurve.rds")
-
-prdata_None_100kb <- rbind.data.frame(prall_None$curve,
-                                prdist_None$curve,
-                                prop_None$curve,
-                                proc_None$curve,
-                                prall_None_k562$curve,
-                                prdist_None_k562$curve,
-                                prop_None_k562$curve,
-                                proc_None_k562$curve)
-names(prdata_None_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_None_100kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
-                           rep("Distance", dim(prdist_None$curve)[1]),
-                           rep("OP", dim(prop_None$curve)[1]),
-                           rep("OC", dim(proc_None$curve)[1]),
-                           rep("All", dim(prall_None_k562$curve)[1]),
-                           rep("Distance", dim(prdist_None_k562$curve)[1]),
-                           rep("OP", dim(prop_None_k562$curve)[1]),
-                           rep("OC", dim(proc_None_k562$curve)[1]))
-prdata_None_100kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
-                                      dim(prdist_None$curve)[1]+
-                                      dim(prop_None$curve)[1]+
-                                      dim(proc_None$curve)[1])),
-                    rep("K562", (dim(prall_None_k562$curve)[1]+
-                                      dim(prdist_None_k562$curve)[1]+
-                                      dim(prop_None_k562$curve)[1]+
-                                      dim(proc_None_k562$curve)[1])))
-prdata_None_100kb$Predictor <- factor(prdata_None_100kb$Predictor)
-prdata_None_100kb$CL <- factor(prdata_None_100kb$CL)
-
-prplot_None_100kb <- ggplot(prdata_None_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##RUS
-prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/all/RFE/prcurve.rds")
-prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
-proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/oc/RFE/prcurve.rds")
-prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/op/RFE/prcurve.rds")
-
-prdata_RUS_100kb <- rbind.data.frame(prall_RUS$curve,
-                                prdist_RUS$curve,
-                                prop_RUS$curve,
-                                proc_RUS$curve,
-                                prall_RUS_k562$curve,
-                                prdist_RUS_k562$curve,
-                                prop_RUS_k562$curve,
-                                proc_RUS_k562$curve)
-names(prdata_RUS_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_RUS_100kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
-                           rep("Distance", dim(prdist_RUS$curve)[1]),
-                           rep("OP", dim(prop_RUS$curve)[1]),
-                           rep("OC", dim(proc_RUS$curve)[1]),
-                           rep("All", dim(prall_RUS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
-                           rep("OP", dim(prop_RUS_k562$curve)[1]),
-                           rep("OC", dim(proc_RUS_k562$curve)[1]))
-prdata_RUS_100kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
-                                      dim(prdist_RUS$curve)[1]+
-                                      dim(prop_RUS$curve)[1]+
-                                      dim(proc_RUS$curve)[1])),
-                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
-                                      dim(prdist_RUS_k562$curve)[1]+
-                                      dim(prop_RUS_k562$curve)[1]+
-                                      dim(proc_RUS_k562$curve)[1])))
-prdata_RUS_100kb$Predictor <- factor(prdata_RUS_100kb$Predictor)
-prdata_RUS_100kb$CL <- factor(prdata_RUS_100kb$CL)
-
-prplot_RUS_100kb <- ggplot(prdata_RUS_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROS
-prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/all/RFE/prcurve.rds")
-prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
-proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/oc/RFE/prcurve.rds")
-prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/op/RFE/prcurve.rds")
-
-prdata_ROS_100kb <- rbind.data.frame(prall_ROS$curve,
-                                prdist_ROS$curve,
-                                prop_ROS$curve,
-                                proc_ROS$curve,
-                                prall_ROS_k562$curve,
-                                prdist_ROS_k562$curve,
-                                prop_ROS_k562$curve,
-                                proc_ROS_k562$curve)
-names(prdata_ROS_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROS_100kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
-                           rep("Distance", dim(prdist_ROS$curve)[1]),
-                           rep("OP", dim(prop_ROS$curve)[1]),
-                           rep("OC", dim(proc_ROS$curve)[1]),
-                           rep("All", dim(prall_ROS_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
-                           rep("OP", dim(prop_ROS_k562$curve)[1]),
-                           rep("OC", dim(proc_ROS_k562$curve)[1]))
-prdata_ROS_100kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
-                                      dim(prdist_ROS$curve)[1]+
-                                      dim(prop_ROS$curve)[1]+
-                                      dim(proc_ROS$curve)[1])),
-                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
-                                      dim(prdist_ROS_k562$curve)[1]+
-                                      dim(prop_ROS_k562$curve)[1]+
-                                      dim(proc_ROS_k562$curve)[1])))
-prdata_ROS_100kb$Predictor <- factor(prdata_ROS_100kb$Predictor)
-prdata_ROS_100kb$CL <- factor(prdata_ROS_100kb$CL)
-
-prplot_ROS_100kb <- ggplot(prdata_ROS_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##SMOTE
-prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
-prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
-proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
-prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/op/RFE/prcurve.rds")
-
-prdata_SMOTE_100kb <- rbind.data.frame(prall_SMOTE$curve,
-                                prdist_SMOTE$curve,
-                                prop_SMOTE$curve,
-                                proc_SMOTE$curve,
-                                prall_SMOTE_k562$curve,
-                                prdist_SMOTE_k562$curve,
-                                prop_SMOTE_k562$curve,
-                                proc_SMOTE_k562$curve)
-names(prdata_SMOTE_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_SMOTE_100kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
-                           rep("OP", dim(prop_SMOTE$curve)[1]),
-                           rep("OC", dim(proc_SMOTE$curve)[1]),
-                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
-                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
-                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
-prdata_SMOTE_100kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
-                                      dim(prdist_SMOTE$curve)[1]+
-                                      dim(prop_SMOTE$curve)[1]+
-                                      dim(proc_SMOTE$curve)[1])),
-                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
-                                      dim(prdist_SMOTE_k562$curve)[1]+
-                                      dim(prop_SMOTE_k562$curve)[1]+
-                                      dim(proc_SMOTE_k562$curve)[1])))
-prdata_SMOTE_100kb$Predictor <- factor(prdata_SMOTE_100kb$Predictor)
-prdata_SMOTE_100kb$CL <- factor(prdata_SMOTE_100kb$CL)
-
-prplot_SMOTE_100kb <- ggplot(prdata_SMOTE_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-##ROSE
-prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")
-prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
-proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
-prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/op/RFE/prcurve.rds")
-
-prdata_ROSE_100kb <- rbind.data.frame(prall_ROSE$curve,
-                                prdist_ROSE$curve,
-                                prop_ROSE$curve,
-                                proc_ROSE$curve,
-                                prall_ROSE_k562$curve,
-                                prdist_ROSE_k562$curve,
-                                prop_ROSE_k562$curve,
-                                proc_ROSE_k562$curve)
-names(prdata_ROSE_100kb) <- c("Recall", "Precision", "Threshold")
-prdata_ROSE_100kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE$curve)[1]),
-                           rep("OP", dim(prop_ROSE$curve)[1]),
-                           rep("OC", dim(proc_ROSE$curve)[1]),
-                           rep("All", dim(prall_ROSE_k562$curve)[1]),
-                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
-                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
-                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
-prdata_ROSE_100kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
-                                      dim(prdist_ROSE$curve)[1]+
-                                      dim(prop_ROSE$curve)[1]+
-                                      dim(proc_ROSE$curve)[1])),
-                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
-                                      dim(prdist_ROSE_k562$curve)[1]+
-                                      dim(prop_ROSE_k562$curve)[1]+
-                                      dim(proc_ROSE_k562$curve)[1])))
-prdata_ROSE_100kb$Predictor <- factor(prdata_ROSE_100kb$Predictor)
-prdata_ROSE_100kb$CL <- factor(prdata_ROSE_100kb$CL)
-
-prplot_ROSE_100kb <- ggplot(prdata_ROSE_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
-  geom_line(size=.75)+
-  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
-  scale_color_discrete(name = "Predictor Type") +
-  theme_minimal()+
-  theme_bw()
-
-###############################################################
-
-##Collecting 25kb, 50kb, and 100kb plots
-
-ggarrange(prplot_None_25kb, prplot_None_50kb, prplot_None_100kb,
-          prplot_RUS_25kb, prplot_RUS_50kb, prplot_RUS_100kb,
-          prplot_ROS_25kb, prplot_ROS_50kb, prplot_ROS_100kb,
-          prplot_SMOTE_25kb, prplot_SMOTE_50kb, prplot_SMOTE_100kb,
-          prplot_ROSE_25kb, prplot_ROSE_50kb, prplot_ROSE_100kb,
-          ncol=3,
-          nrow=5,
-          common.legend = TRUE,
-          legend = "right")
-```
-
-##Tables of AUPRC
-
-```{r}
-
-gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-K562_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-K562_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-K562_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-K562_10kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-K562_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-K562_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-K562_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-K562_25kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-K562_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-K562_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-K562_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-K562_50kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
-K562_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
-K562_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
-K562_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
-K562_100kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral
-
-gm12878_10kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-gm12878_25kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-gm12878_50kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-gm12878_100kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-K562_10kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-K562_10kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-K562_10kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-K562_10kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-K562_10kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-K562_25kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-K562_25kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-K562_25kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-K562_25kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-K562_25kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-K562_50kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-K562_50kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-K562_50kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-K562_50kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-K562_50kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-K562_100kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
-K562_100kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
-K562_100kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
-K562_100kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
-K562_100kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral
-
-gm12878_10kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-gm12878_25kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-gm12878_50kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-gm12878_100kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-K562_10kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-K562_10kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-K562_10kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-K562_10kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-K562_10kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-K562_25kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-K562_25kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-K562_25kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-K562_25kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-K562_25kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-K562_50kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-K562_50kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-K562_50kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-K562_50kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-K562_50kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-K562_100kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
-K562_100kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
-K562_100kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
-K562_100kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
-K562_100kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral
-
-gm12878_10kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-gm12878_10kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-gm12878_25kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-gm12878_25kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-gm12878_50kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-gm12878_50kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-gm12878_100kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-gm12878_100kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-K562_10kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-K562_10kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-K562_10kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-K562_10kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-K562_10kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-K562_25kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-K562_25kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-K562_25kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-K562_25kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-K562_25kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-K562_50kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-K562_50kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-K562_50kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-K562_50kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-K562_50kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-K562_100kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
-K562_100kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
-K562_100kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
-K562_100kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
-K562_100kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral
-
-prcurvetable <- data.frame(CL=c(rep("GM12878", 20), rep("K562", 20)),
-                           Resolution=c(c(rep("10 kb", 5), 
-                                        rep("25 kb", 5),
-                                        rep("50 kb", 5),
-                                        rep("100 kb", 5)),
-                                        c(rep("10 kb", 5), 
-                                        rep("25 kb", 5),
-                                        rep("50 kb", 5),
-                                        rep("100 kb", 5))),
-                           ReSampling=rep(c("None",
-                                        "RUS",
-                                        "ROS",
-                                        "SMOTE",
-                                        "ROSE"),8))
-prcurvetable$OC <- c(gm12878_10kb_none_oc,
-gm12878_10kb_rus_oc,
-gm12878_10kb_ros_oc,
-gm12878_10kb_smote_oc,
-gm12878_10kb_rose_oc,
-gm12878_25kb_none_oc,
-gm12878_25kb_rus_oc,
-gm12878_25kb_ros_oc,
-gm12878_25kb_smote_oc,
-gm12878_25kb_rose_oc,
-gm12878_50kb_none_oc,
-gm12878_50kb_rus_oc,
-gm12878_50kb_ros_oc,
-gm12878_50kb_smote_oc,
-gm12878_50kb_rose_oc,
-gm12878_100kb_none_oc,
-gm12878_100kb_rus_oc,
-gm12878_100kb_ros_oc,
-gm12878_100kb_smote_oc,
-gm12878_100kb_rose_oc,
-K562_10kb_none_oc,
-K562_10kb_rus_oc,
-K562_10kb_ros_oc,
-K562_10kb_smote_oc,
-K562_10kb_rose_oc,
-K562_25kb_none_oc,
-K562_25kb_rus_oc,
-K562_25kb_ros_oc,
-K562_25kb_smote_oc,
-K562_25kb_rose_oc,
-K562_50kb_none_oc,
-K562_50kb_rus_oc,
-K562_50kb_ros_oc,
-K562_50kb_smote_oc,
-K562_50kb_rose_oc,
-K562_100kb_none_oc,
-K562_100kb_rus_oc,
-K562_100kb_ros_oc,
-K562_100kb_smote_oc,
-K562_100kb_rose_oc)
-
-prcurvetable$OP <- c(gm12878_10kb_none_OP,
-gm12878_10kb_rus_OP,
-gm12878_10kb_ros_OP,
-gm12878_10kb_smote_OP,
-gm12878_10kb_rose_OP,
-gm12878_25kb_none_OP,
-gm12878_25kb_rus_OP,
-gm12878_25kb_ros_OP,
-gm12878_25kb_smote_OP,
-gm12878_25kb_rose_OP,
-gm12878_50kb_none_OP,
-gm12878_50kb_rus_OP,
-gm12878_50kb_ros_OP,
-gm12878_50kb_smote_OP,
-gm12878_50kb_rose_OP,
-gm12878_100kb_none_OP,
-gm12878_100kb_rus_OP,
-gm12878_100kb_ros_OP,
-gm12878_100kb_smote_OP,
-gm12878_100kb_rose_OP,
-K562_10kb_none_OP,
-K562_10kb_rus_OP,
-K562_10kb_ros_OP,
-K562_10kb_smote_OP,
-K562_10kb_rose_OP,
-K562_25kb_none_OP,
-K562_25kb_rus_OP,
-K562_25kb_ros_OP,
-K562_25kb_smote_OP,
-K562_25kb_rose_OP,
-K562_50kb_none_OP,
-K562_50kb_rus_OP,
-K562_50kb_ros_OP,
-K562_50kb_smote_OP,
-K562_50kb_rose_OP,
-K562_100kb_none_OP,
-K562_100kb_rus_OP,
-K562_100kb_ros_OP,
-K562_100kb_smote_OP,
-K562_100kb_rose_OP)
-
-prcurvetable$Distance <- c(gm12878_10kb_none_Distance,
-gm12878_10kb_rus_Distance,
-gm12878_10kb_ros_Distance,
-gm12878_10kb_smote_Distance,
-gm12878_10kb_rose_Distance,
-gm12878_25kb_none_Distance,
-gm12878_25kb_rus_Distance,
-gm12878_25kb_ros_Distance,
-gm12878_25kb_smote_Distance,
-gm12878_25kb_rose_Distance,
-gm12878_50kb_none_Distance,
-gm12878_50kb_rus_Distance,
-gm12878_50kb_ros_Distance,
-gm12878_50kb_smote_Distance,
-gm12878_50kb_rose_Distance,
-gm12878_100kb_none_Distance,
-gm12878_100kb_rus_Distance,
-gm12878_100kb_ros_Distance,
-gm12878_100kb_smote_Distance,
-gm12878_100kb_rose_Distance,
-K562_10kb_none_Distance,
-K562_10kb_rus_Distance,
-K562_10kb_ros_Distance,
-K562_10kb_smote_Distance,
-K562_10kb_rose_Distance,
-K562_25kb_none_Distance,
-K562_25kb_rus_Distance,
-K562_25kb_ros_Distance,
-K562_25kb_smote_Distance,
-K562_25kb_rose_Distance,
-K562_50kb_none_Distance,
-K562_50kb_rus_Distance,
-K562_50kb_ros_Distance,
-K562_50kb_smote_Distance,
-K562_50kb_rose_Distance,
-K562_100kb_none_Distance,
-K562_100kb_rus_Distance,
-K562_100kb_ros_Distance,
-K562_100kb_smote_Distance,
-K562_100kb_rose_Distance)
-
-prcurvetable$All <- c(gm12878_10kb_none_all,
-gm12878_10kb_rus_all,
-gm12878_10kb_ros_all,
-gm12878_10kb_smote_all,
-gm12878_10kb_rose_all,
-gm12878_25kb_none_all,
-gm12878_25kb_rus_all,
-gm12878_25kb_ros_all,
-gm12878_25kb_smote_all,
-gm12878_25kb_rose_all,
-gm12878_50kb_none_all,
-gm12878_50kb_rus_all,
-gm12878_50kb_ros_all,
-gm12878_50kb_smote_all,
-gm12878_50kb_rose_all,
-gm12878_100kb_none_all,
-gm12878_100kb_rus_all,
-gm12878_100kb_ros_all,
-gm12878_100kb_smote_all,
-gm12878_100kb_rose_all,
-K562_10kb_none_all,
-K562_10kb_rus_all,
-K562_10kb_ros_all,
-K562_10kb_smote_all,
-K562_10kb_rose_all,
-K562_25kb_none_all,
-K562_25kb_rus_all,
-K562_25kb_ros_all,
-K562_25kb_smote_all,
-K562_25kb_rose_all,
-K562_50kb_none_all,
-K562_50kb_rus_all,
-K562_50kb_ros_all,
-K562_50kb_smote_all,
-K562_50kb_rose_all,
-K562_100kb_none_all,
-K562_100kb_rus_all,
-K562_100kb_ros_all,
-K562_100kb_smote_all,
-K562_100kb_rose_all)
-
-```
-
-## RFE
-
-###10kb
-
-```{r}
-rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-#None
-resampdata_None_10kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
-resampdata_None_10kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
-                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
-
-rfeplot_None_10kb <- ggplot(resampdata_None_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,.5)
-
-#RUS
-resampdata_RUS_10kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
-resampdata_RUS_10kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
-
-rfeplot_RUS_10kb <- ggplot(resampdata_RUS_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROS
-resampdata_ROS_10kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
-resampdata_ROS_10kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
-
-rfeplot_ROS_10kb <- ggplot(resampdata_ROS_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#SMOTE
-resampdata_SMOTE_10kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
-resampdata_SMOTE_10kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
-
-rfeplot_SMOTE_10kb <- ggplot(resampdata_SMOTE_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROSE
-resampdata_ROSE_10kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
-resampdata_ROSE_10kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
-
-rfeplot_ROSE_10kb <- ggplot(resampdata_ROSE_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#Combining 10 kb plots
-ggarrange(rfeplot_None_10kb,
-          rfeplot_RUS_10kb,
-          rfeplot_ROS_10kb,
-          rfeplot_SMOTE_10kb,
-          rfeplot_ROSE_10kb,
-          nrow = 3,
-          ncol = 2,
-          common.legend = TRUE,
-          legend = "right")
-
-```
-
-###25kb
-
-```{r}
-rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-#None
-resampdata_None_25kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
-resampdata_None_25kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
-                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
-
-rfeplot_None_25kb <- ggplot(resampdata_None_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,.5)
-
-#RUS
-resampdata_RUS_25kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
-resampdata_RUS_25kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
-
-rfeplot_RUS_25kb <- ggplot(resampdata_RUS_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROS
-resampdata_ROS_25kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
-resampdata_ROS_25kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
-
-rfeplot_ROS_25kb <- ggplot(resampdata_ROS_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#SMOTE
-resampdata_SMOTE_25kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
-resampdata_SMOTE_25kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
-
-rfeplot_SMOTE_25kb <- ggplot(resampdata_SMOTE_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROSE
-resampdata_ROSE_25kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
-resampdata_ROSE_25kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
-
-rfeplot_ROSE_25kb <- ggplot(resampdata_ROSE_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-```
-
-###50kb
-
-```{r}
-rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-#None
-resampdata_None_50kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
-resampdata_None_50kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
-                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
-
-rfeplot_None_50kb <- ggplot(resampdata_None_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,.5)
-
-#RUS
-resampdata_RUS_50kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
-resampdata_RUS_50kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
-
-rfeplot_RUS_50kb <- ggplot(resampdata_RUS_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROS
-resampdata_ROS_50kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
-resampdata_ROS_50kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
-
-rfeplot_ROS_50kb <- ggplot(resampdata_ROS_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#SMOTE
-resampdata_SMOTE_50kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
-resampdata_SMOTE_50kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
-
-rfeplot_SMOTE_50kb <- ggplot(resampdata_SMOTE_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROSE
-resampdata_ROSE_50kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
-resampdata_ROSE_50kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
-
-rfeplot_ROSE_50kb <- ggplot(resampdata_ROSE_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-```
-
-###100kb
-
-```{r}
-rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
-rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
-rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
-rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")
-
-#None
-resampdata_None_100kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
-resampdata_None_100kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
-                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))
-
-rfeplot_None_100kb <- ggplot(resampdata_None_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,.5)
-
-#RUS
-resampdata_RUS_100kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
-resampdata_RUS_100kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))
-
-rfeplot_RUS_100kb <- ggplot(resampdata_RUS_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROS
-resampdata_ROS_100kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
-resampdata_ROS_100kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
-
-rfeplot_ROS_100kb <- ggplot(resampdata_ROS_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#SMOTE
-resampdata_SMOTE_100kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
-resampdata_SMOTE_100kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))
-
-rfeplot_SMOTE_100kb <- ggplot(resampdata_SMOTE_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-#ROSE
-resampdata_ROSE_100kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
-resampdata_ROSE_100kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
-                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))
-
-rfeplot_ROSE_100kb <- ggplot(resampdata_ROSE_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
-  geom_point(position = position_dodge(width = 3))+
-  geom_line() +
-  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
-                width=5,
-                position = position_dodge(width = 3))+
-  scale_color_discrete(name="Cell Line")+
-  scale_x_discrete(name="Number of Features", 
-                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
-                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
-                   limits=as.character(c(1:138)))+
-  theme_minimal()#+
-  #ylim(0,1)
-
-```
-
-### Combined
-
-```{r}
-
-ggarrange(rfeplot_None_25kb, rfeplot_None_50kb, rfeplot_None_100kb,
-          rfeplot_RUS_25kb, rfeplot_RUS_50kb, rfeplot_RUS_100kb,
-          rfeplot_ROS_25kb, rfeplot_ROS_50kb, rfeplot_ROS_100kb,
-          rfeplot_SMOTE_25kb, rfeplot_SMOTE_50kb, rfeplot_SMOTE_100kb,
-          rfeplot_ROSE_25kb, rfeplot_ROSE_50kb, rfeplot_ROSE_100kb,
-          nrow = 5,
-          ncol = 3,
-          common.legend = TRUE,
-          legend = "right")
-
-```
-
-#Barplots of performance metrics for models with distance-type predictors
-
-##10kb
-
-```{r}
-#GM12878
-
-##None
-rfperf_gm12878_10kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_10kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_10kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_10kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_gm12878_10kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-#K562
-
-##None
-rfperf_K562_10kb_none <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_10kb_rus <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_10kb_ros <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_10kb_smote <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_K562_10kb_rose <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-all10kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all10kbresults$Performance <- c(round(rfperf_gm12878_10kb_none[9,2],2),
-                                round(rfperf_gm12878_10kb_none[19,2],2),
-                                round(rfperf_gm12878_10kb_none[16,2],2),
-                                round(rfperf_gm12878_10kb_none[15,2],2),
-                                round(rfperf_K562_10kb_none[9,2],2),
-                                round(rfperf_K562_10kb_none[19,2],2),
-                                round(rfperf_K562_10kb_none[16,2],2),
-                                round(rfperf_K562_10kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_10kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_rus[15,]),2),
-                                round(mean(rfperf_K562_10kb_rus[9,]),2),
-                                round(mean(rfperf_K562_10kb_rus[19,]),2),
-                                round(mean(rfperf_K562_10kb_rus[16,]),2),
-                                round(mean(rfperf_K562_10kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_ros[15,]),2),
-                                round(mean(rfperf_K562_10kb_ros[9,]),2),
-                                round(mean(rfperf_K562_10kb_ros[19,]),2),
-                                round(mean(rfperf_K562_10kb_ros[16,]),2),
-                                round(mean(rfperf_K562_10kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_smote[15,]),2),
-                                round(mean(rfperf_K562_10kb_smote[9,]),2),
-                                round(mean(rfperf_K562_10kb_smote[19,]),2),
-                                round(mean(rfperf_K562_10kb_smote[16,]),2),
-                                round(mean(rfperf_K562_10kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_10kb_rose[15,]),2),
-                                round(mean(rfperf_K562_10kb_rose[9,]),2),
-                                round(mean(rfperf_K562_10kb_rose[19,]),2),
-                                round(mean(rfperf_K562_10kb_rose[16,]),2),
-                                round(mean(rfperf_K562_10kb_rose[15,]),2))
-
-all10kbresults$Resampling <- factor(all10kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all10kbresults$CL <- factor(all10kbresults$CL, levels=c("GM12878", "K562"))
-all10kbresults$Metric <- factor(all10kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
-
-none10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="None"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rus10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="RUS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-ros10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="ROS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-smote10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="SMOTE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rose10kbplot <- ggplot(all10kbresults[which(all10kbresults$Resampling=="ROSE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-######################################################################
-
-#comparing only f1 and mcc
-
-f1mcc10kbplot <- ggplot(all10kbresults[which(all10kbresults$Metric=="F1-Score" |
-                                               all10kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=CL)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-##25kb
-
-```{r}
-#GM12878
-
-##None
-rfperf_gm12878_25kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_25kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_25kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_25kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_gm12878_25kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-#K562
-
-##None
-rfperf_K562_25kb_none <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_25kb_rus <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_25kb_ros <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_25kb_smote <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_K562_25kb_rose <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-all25kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all25kbresults$Performance <- c(round(rfperf_gm12878_25kb_none[9,2],2),
-                                round(rfperf_gm12878_25kb_none[19,2],2),
-                                round(rfperf_gm12878_25kb_none[16,2],2),
-                                round(rfperf_gm12878_25kb_none[15,2],2),
-                                round(rfperf_K562_25kb_none[9,2],2),
-                                round(rfperf_K562_25kb_none[19,2],2),
-                                round(rfperf_K562_25kb_none[16,2],2),
-                                round(rfperf_K562_25kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_25kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_rus[15,]),2),
-                                round(mean(rfperf_K562_25kb_rus[9,]),2),
-                                round(mean(rfperf_K562_25kb_rus[19,]),2),
-                                round(mean(rfperf_K562_25kb_rus[16,]),2),
-                                round(mean(rfperf_K562_25kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_ros[15,]),2),
-                                round(mean(rfperf_K562_25kb_ros[9,]),2),
-                                round(mean(rfperf_K562_25kb_ros[19,]),2),
-                                round(mean(rfperf_K562_25kb_ros[16,]),2),
-                                round(mean(rfperf_K562_25kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_smote[15,]),2),
-                                round(mean(rfperf_K562_25kb_smote[9,]),2),
-                                round(mean(rfperf_K562_25kb_smote[19,]),2),
-                                round(mean(rfperf_K562_25kb_smote[16,]),2),
-                                round(mean(rfperf_K562_25kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_25kb_rose[15,]),2),
-                                round(mean(rfperf_K562_25kb_rose[9,]),2),
-                                round(mean(rfperf_K562_25kb_rose[19,]),2),
-                                round(mean(rfperf_K562_25kb_rose[16,]),2),
-                                round(mean(rfperf_K562_25kb_rose[15,]),2))
-
-all25kbresults$Resampling <- factor(all25kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all25kbresults$CL <- factor(all25kbresults$CL, levels=c("GM12878", "K562"))
-all25kbresults$Metric <- factor(all25kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
-
-none25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="None"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rus25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="RUS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-ros25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="ROS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-smote25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="SMOTE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rose25kbplot <- ggplot(all25kbresults[which(all25kbresults$Resampling=="ROSE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-######################################################################
-
-#comparing only f1 and mcc
-
-f1mcc25kbplot <- ggplot(all25kbresults[which(all25kbresults$Metric=="F1-Score" |
-                                               all25kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=CL)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-##50kb
-
-```{r}
-#GM12878
-
-##None
-rfperf_gm12878_50kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_50kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_50kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_50kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_gm12878_50kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-#K562
-
-##None
-rfperf_K562_50kb_none <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_50kb_rus <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_50kb_ros <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_50kb_smote <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_K562_50kb_rose <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-all50kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all50kbresults$Performance <- c(round(rfperf_gm12878_50kb_none[9,2],2),
-                                round(rfperf_gm12878_50kb_none[19,2],2),
-                                round(rfperf_gm12878_50kb_none[16,2],2),
-                                round(rfperf_gm12878_50kb_none[15,2],2),
-                                round(rfperf_K562_50kb_none[9,2],2),
-                                round(rfperf_K562_50kb_none[19,2],2),
-                                round(rfperf_K562_50kb_none[16,2],2),
-                                round(rfperf_K562_50kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_50kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_rus[15,]),2),
-                                round(mean(rfperf_K562_50kb_rus[9,]),2),
-                                round(mean(rfperf_K562_50kb_rus[19,]),2),
-                                round(mean(rfperf_K562_50kb_rus[16,]),2),
-                                round(mean(rfperf_K562_50kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_ros[15,]),2),
-                                round(mean(rfperf_K562_50kb_ros[9,]),2),
-                                round(mean(rfperf_K562_50kb_ros[19,]),2),
-                                round(mean(rfperf_K562_50kb_ros[16,]),2),
-                                round(mean(rfperf_K562_50kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_smote[15,]),2),
-                                round(mean(rfperf_K562_50kb_smote[9,]),2),
-                                round(mean(rfperf_K562_50kb_smote[19,]),2),
-                                round(mean(rfperf_K562_50kb_smote[16,]),2),
-                                round(mean(rfperf_K562_50kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_50kb_rose[15,]),2),
-                                round(mean(rfperf_K562_50kb_rose[9,]),2),
-                                round(mean(rfperf_K562_50kb_rose[19,]),2),
-                                round(mean(rfperf_K562_50kb_rose[16,]),2),
-                                round(mean(rfperf_K562_50kb_rose[15,]),2))
-
-all50kbresults$Resampling <- factor(all50kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all50kbresults$CL <- factor(all50kbresults$CL, levels=c("GM12878", "K562"))
-all50kbresults$Metric <- factor(all50kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
-
-none50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="None"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rus50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="RUS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-ros50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="ROS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-smote50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="SMOTE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rose50kbplot <- ggplot(all50kbresults[which(all50kbresults$Resampling=="ROSE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-######################################################################
-
-#comparing only f1 and mcc
-
-f1mcc50kbplot <- ggplot(all50kbresults[which(all50kbresults$Metric=="F1-Score" |
-                                               all50kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=CL)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-##100kb
-
-```{r}
-#GM12878
-
-##None
-rfperf_gm12878_100kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_100kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_100kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_100kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_gm12878_100kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-#K562
-
-##None
-rfperf_K562_100kb_none <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_100kb_rus <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_100kb_ros <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_100kb_smote <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")
-
-##ROSE
-rfperf_K562_100kb_rose <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")
-
-all100kbresults <- data.frame(Resampling=c(rep("None", 8),
-                                       rep("RUS", 8),
-                                       rep("ROS", 8),
-                                       rep("SMOTE", 8),
-                                       rep("ROSE", 8)),
-                          CL=rep(c(rep("GM12878",4),
-                               rep("K562", 4)),5),
-                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))
-
-all100kbresults$Performance <- c(round(rfperf_gm12878_100kb_none[9,2],2),
-                                round(rfperf_gm12878_100kb_none[19,2],2),
-                                round(rfperf_gm12878_100kb_none[16,2],2),
-                                round(rfperf_gm12878_100kb_none[15,2],2),
-                                round(rfperf_K562_100kb_none[9,2],2),
-                                round(rfperf_K562_100kb_none[19,2],2),
-                                round(rfperf_K562_100kb_none[16,2],2),
-                                round(rfperf_K562_100kb_none[15,2],2),
-                                round(mean(rfperf_gm12878_100kb_rus[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_rus[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_rus[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_rus[15,]),2),
-                                round(mean(rfperf_K562_100kb_rus[9,]),2),
-                                round(mean(rfperf_K562_100kb_rus[19,]),2),
-                                round(mean(rfperf_K562_100kb_rus[16,]),2),
-                                round(mean(rfperf_K562_100kb_rus[15,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_ros[15,]),2),
-                                round(mean(rfperf_K562_100kb_ros[9,]),2),
-                                round(mean(rfperf_K562_100kb_ros[19,]),2),
-                                round(mean(rfperf_K562_100kb_ros[16,]),2),
-                                round(mean(rfperf_K562_100kb_ros[15,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_smote[15,]),2),
-                                round(mean(rfperf_K562_100kb_smote[9,]),2),
-                                round(mean(rfperf_K562_100kb_smote[19,]),2),
-                                round(mean(rfperf_K562_100kb_smote[16,]),2),
-                                round(mean(rfperf_K562_100kb_smote[15,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[9,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[19,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[16,]),2),
-                                round(mean(rfperf_gm12878_100kb_rose[15,]),2),
-                                round(mean(rfperf_K562_100kb_rose[9,]),2),
-                                round(mean(rfperf_K562_100kb_rose[19,]),2),
-                                round(mean(rfperf_K562_100kb_rose[16,]),2),
-                                round(mean(rfperf_K562_100kb_rose[15,]),2))
-
-all100kbresults$Resampling <- factor(all100kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
-all100kbresults$CL <- factor(all100kbresults$CL, levels=c("GM12878", "K562"))
-all100kbresults$Metric <- factor(all100kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))
-
-none100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="None"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rus100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="RUS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-ros100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="ROS"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-smote100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="SMOTE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-rose100kbplot <- ggplot(all100kbresults[which(all100kbresults$Resampling=="ROSE"),],
-                       aes(x=CL, y=Performance, fill=Metric)) +
-  geom_bar( stat="identity", position="dodge") +
-  xlab("Cell Line") +
-  ylim(0,1)+
-  theme_bw() +
-  theme_minimal() +
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15), #, angle = 45, margin = ggplot2::margin(t = 35)),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-######################################################################
-
-#comparing only f1 and mcc
-
-f1mcc100kbplot <- ggplot(all100kbresults[which(all100kbresults$Metric=="F1-Score" |
-                                               all100kbresults$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=CL)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-#Table of model performances
-
-```{r}
-
-performancetab <- data.frame(Performance = c(rep("F1-Score", 10),
-                                             rep("MCC", 10)),
-                             Resampling = rep(c("None",
-                                                "None",
-                                                "RUS",
-                                                "RUS",
-                                                "ROS",
-                                                "ROS",
-                                                "SMOTE",
-                                                "SMOTE",
-                                                "ROSE",
-                                                "ROSE"),2),
-                             CL = rep(c("GM12878", "K562"), 10)
-                             )
-
-performancetab$kb10 <- c(rfperf_gm12878_10kb_none[16,2],
-                         rfperf_K562_10kb_none[16,2],
-                         mean(rfperf_gm12878_10kb_rus[16,]),
-                         mean(rfperf_K562_10kb_rus[16,]),
-                         mean(rfperf_gm12878_10kb_ros[16,]),
-                         mean(rfperf_K562_10kb_ros[16,]),
-                         mean(rfperf_gm12878_10kb_smote[16,]),
-                         mean(rfperf_K562_10kb_smote[16,]),
-                         mean(rfperf_gm12878_10kb_rose[16,]),
-                         mean(rfperf_K562_10kb_rose[16,]),
-                         rfperf_gm12878_10kb_none[15,2],
-                         rfperf_K562_10kb_none[15,2],
-                         mean(rfperf_gm12878_10kb_rus[15,]),
-                         mean(rfperf_K562_10kb_rus[15,]),
-                         mean(rfperf_gm12878_10kb_ros[15,]),
-                         mean(rfperf_K562_10kb_ros[15,]),
-                         mean(rfperf_gm12878_10kb_smote[15,]),
-                         mean(rfperf_K562_10kb_smote[15,]),
-                         mean(rfperf_gm12878_10kb_rose[15,]),
-                         mean(rfperf_K562_10kb_rose[15,]))
-
-performancetab$kb25 <- c(rfperf_gm12878_25kb_none[16,2],
-                         rfperf_K562_25kb_none[16,2],
-                         mean(rfperf_gm12878_25kb_rus[16,]),
-                         mean(rfperf_K562_25kb_rus[16,]),
-                         mean(rfperf_gm12878_25kb_ros[16,]),
-                         mean(rfperf_K562_25kb_ros[16,]),
-                         mean(rfperf_gm12878_25kb_smote[16,]),
-                         mean(rfperf_K562_25kb_smote[16,]),
-                         mean(rfperf_gm12878_25kb_rose[16,]),
-                         mean(rfperf_K562_25kb_rose[16,]),
-                         rfperf_gm12878_25kb_none[15,2],
-                         rfperf_K562_25kb_none[15,2],
-                         mean(rfperf_gm12878_25kb_rus[15,]),
-                         mean(rfperf_K562_25kb_rus[15,]),
-                         mean(rfperf_gm12878_25kb_ros[15,]),
-                         mean(rfperf_K562_25kb_ros[15,]),
-                         mean(rfperf_gm12878_25kb_smote[15,]),
-                         mean(rfperf_K562_25kb_smote[15,]),
-                         mean(rfperf_gm12878_25kb_rose[15,]),
-                         mean(rfperf_K562_25kb_rose[15,]))
-
-performancetab$kb50 <- c(rfperf_gm12878_50kb_none[16,2],
-                         rfperf_K562_50kb_none[16,2],
-                         mean(rfperf_gm12878_50kb_rus[16,]),
-                         mean(rfperf_K562_50kb_rus[16,]),
-                         mean(rfperf_gm12878_50kb_ros[16,]),
-                         mean(rfperf_K562_50kb_ros[16,]),
-                         mean(rfperf_gm12878_50kb_smote[16,]),
-                         mean(rfperf_K562_50kb_smote[16,]),
-                         mean(rfperf_gm12878_50kb_rose[16,]),
-                         mean(rfperf_K562_50kb_rose[16,]),
-                         rfperf_gm12878_50kb_none[15,2],
-                         rfperf_K562_50kb_none[15,2],
-                         mean(rfperf_gm12878_50kb_rus[15,]),
-                         mean(rfperf_K562_50kb_rus[15,]),
-                         mean(rfperf_gm12878_50kb_ros[15,]),
-                         mean(rfperf_K562_50kb_ros[15,]),
-                         mean(rfperf_gm12878_50kb_smote[15,]),
-                         mean(rfperf_K562_50kb_smote[15,]),
-                         mean(rfperf_gm12878_50kb_rose[15,]),
-                         mean(rfperf_K562_50kb_rose[15,]))
-
-performancetab$kb100 <- c(rfperf_gm12878_100kb_none[16,2],
-                         rfperf_K562_100kb_none[16,2],
-                         mean(rfperf_gm12878_100kb_rus[16,]),
-                         mean(rfperf_K562_100kb_rus[16,]),
-                         mean(rfperf_gm12878_100kb_ros[16,]),
-                         mean(rfperf_K562_100kb_ros[16,]),
-                         mean(rfperf_gm12878_100kb_smote[16,]),
-                         mean(rfperf_K562_100kb_smote[16,]),
-                         mean(rfperf_gm12878_100kb_rose[16,]),
-                         mean(rfperf_K562_100kb_rose[16,]),
-                         rfperf_gm12878_100kb_none[15,2],
-                         rfperf_K562_100kb_none[15,2],
-                         mean(rfperf_gm12878_100kb_rus[15,]),
-                         mean(rfperf_K562_100kb_rus[15,]),
-                         mean(rfperf_gm12878_100kb_ros[15,]),
-                         mean(rfperf_K562_100kb_ros[15,]),
-                         mean(rfperf_gm12878_100kb_smote[15,]),
-                         mean(rfperf_K562_100kb_smote[15,]),
-                         mean(rfperf_gm12878_100kb_rose[15,]),
-                         mean(rfperf_K562_100kb_rose[15,]))
-
-performancetab[,4:7] <- round(performancetab[,4:7], 3)
-```
-
-#Variable Importance Plots for distance predictors with ENET reduction
-
-##5kb
-###Random Under-Sampling
-```{r}
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/5kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf5kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf5kb <- rf5kb[order(rf5kb$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf5kb$Importance
-Labels <- as.character(rf5kb$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.5kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.5kb$Feature <- as.character(varimp.rf.df.5kb$Feature)							 
-varimp.rf.df.5kb <-varimp.rf.df.5kb[order(varimp.rf.df.5kb$Importance),]
-varimp.rf.df.5kb <- varimp.rf.df.5kb[(dim(varimp.rf.df.5kb)[1]-14):dim(varimp.rf.df.5kb)[1],]
-varimp.rf.df.5kb$Feature <- factor(varimp.rf.df.5kb$Feature,
-                                     levels=as.character(varimp.rf.df.5kb$Feature))
-
-p.rf.5kb <- ggplot(varimp.rf.df.5kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(A)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="red") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-  ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/5kb/p.rf.5kb.png")
-```
-##25kb
-###Random Under-Sampling
-```{r}
-  rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/25kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf <- rf[order(rf$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf$Importance
-Labels <- as.character(rf$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.25kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.25kb$Feature <- as.character(varimp.rf.df.25kb$Feature)							 
-varimp.rf.df.25kb <-varimp.rf.df.25kb[order(varimp.rf.df.25kb$Importance),]
-varimp.rf.df.25kb <- varimp.rf.df.25kb[(dim(varimp.rf.df.25kb)[1]-14):dim(varimp.rf.df.25kb)[1],]
-varimp.rf.df.25kb$Feature <- factor(varimp.rf.df.25kb$Feature,
-                                     levels=as.character(varimp.rf.df.25kb$Feature))
-
-p.rf.25kb <- ggplot(varimp.rf.df.25kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(B)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="blue") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/25kb/p.rf.25kb.png")
-```
-##50kb
-###Random Under-Sampling
-```{r}
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/50kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf <- rf[order(rf$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf$Importance
-Labels <- as.character(rf$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.50kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.50kb$Feature <- as.character(varimp.rf.df.50kb$Feature)							 
-varimp.rf.df.50kb <-varimp.rf.df.50kb[order(varimp.rf.df.50kb$Importance),]
-varimp.rf.df.50kb <- varimp.rf.df.50kb[(dim(varimp.rf.df.50kb)[1]-14):dim(varimp.rf.df.50kb)[1],]
-varimp.rf.df.50kb$Feature <- factor(varimp.rf.df.50kb$Feature,
-                                     levels=as.character(varimp.rf.df.50kb$Feature))
-
-p.rf.50kb <- ggplot(varimp.rf.df.50kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(C)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="green") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/50kb/p.rf.50kb.png")
-```
-##100kb
-###Random Under-Sampling
-```{r}
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/100kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rf <- rf[order(rf$Importance, decreasing=TRUE),]
-rownames(rf) <- NULL
-
-varimp.rf <- rf$Importance
-Labels <- as.character(rf$Feature)
-Labels[grep("Gm12878-", Labels)] <- gsub("Gm12878-","",Labels[grep("Gm12878-", Labels)])
-Labels[grep("_dist", Labels)] <- gsub("_dist","",Labels[grep("_dist", Labels)])
-varimp.rf.df.100kb <- cbind.data.frame(Feature=as.character(Labels),
-                                 Importance=varimp.rf)
-varimp.rf.df.100kb$Feature <- as.character(varimp.rf.df.100kb$Feature)							 
-varimp.rf.df.100kb <-varimp.rf.df.100kb[order(varimp.rf.df.100kb$Importance),]
-#varimp.rf.df.100kb <- varimp.rf.df.100kb[(dim(varimp.rf.df.100kb)[1]-14):dim(varimp.rf.df.100kb)[1],]
-varimp.rf.df.100kb$Feature <- factor(varimp.rf.df.100kb$Feature,
-                                     levels=as.character(varimp.rf.df.100kb$Feature))
-
-p.rf.100kb <- ggplot(varimp.rf.df.100kb, aes(x=Feature, y=Importance)) +
-  xlab("Predictors") +
-  ylab("Importance") +
-  ggtitle("(D)") +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge",
-           fill="orange") +
-  theme_minimal() +
-  theme(axis.text=element_text(size=15),
-        axis.title=element_text(size=20,face="bold")) +
-  coord_flip()
-
-   ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/100kb/p.rf.100kb.png")
-
-allvarimps <- ggarrange(p.rf.5kb,p.rf.25kb,p.rf.50kb,p.rf.100kb, ncol=2, nrow=2)
-
-ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/allvarimps.png")
-```
-
-#Network Analysis
-
-```{r}
-##venn diagram of top predictors 
-#grid.newpage()
-##vennp <- draw.triple.venn(area1 = 10, area2 = 10, area3 = 10, n12 = length(intersect(us,sm)), n23 = length(intersect(sm,km)), n13 = length(intersect(km,us)), 
-##                 n123 = length(intersect(us,intersect(sm,km))), category = c("Under- \n Sampling", "SMOTE", "K-Medoids"), lty = "blank", 
-##                 fill = c("red", "green", "blue"),cex=3,cat.cex = 3)
-#
-#vennp <- draw.pairwise.venn(length(varimp.rf.df.gm12878$Feature),
-#						  length(varimp.rf.df.k562$Feature),
-#						  length(intersect(varimp.rf.df.gm12878$Feature, varimp.rf.df.k562$Feature)),
-#						  category = c("GM12878", "K562"),
-#						  lty = "blank", 
-#                          fill = c("red", "blue"),
-#						  cex=3,
-#						  cat.cex = 3,
-#						  cat.pos = c(0,0),
-#						  scaled = FALSE)
-
-##Network Visualization between resolutions
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/5kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf5kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rownames(rf5kb) <- NULL
-rf5kb$Feature <- as.character(rf5kb$Feature)
-rf5kb$Feature[grep("Gm12878-", rf5kb$Feature)] <- gsub("Gm12878-","",rf5kb$Feature[grep("Gm12878-", rf5kb$Feature)])
-rf5kb$Feature[grep("_dist", rf5kb$Feature)] <- gsub("_dist","",rf5kb$Feature[grep("_dist", rf5kb$Feature)])
-rf5kb$Importance <- rf5kb$Importance/sum(rf5kb$Importance)
-
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/25kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf25kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rownames(rf25kb) <- NULL
-rf25kb$Feature <- as.character(rf25kb$Feature)
-rf25kb$Feature[grep("Gm12878-", rf25kb$Feature)] <- gsub("Gm12878-","",rf25kb$Feature[grep("Gm12878-", rf25kb$Feature)])
-rf25kb$Feature[grep("_dist", rf25kb$Feature)] <- gsub("_dist","",rf25kb$Feature[grep("_dist", rf25kb$Feature)])
-rf25kb$Importance <- rf25kb$Importance/sum(rf25kb$Importance)
-
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/50kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf50kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rownames(rf50kb) <- NULL
-rf50kb$Feature <- as.character(rf50kb$Feature)
-rf50kb$Feature[grep("Gm12878-", rf50kb$Feature)] <- gsub("Gm12878-","",rf50kb$Feature[grep("Gm12878-", rf50kb$Feature)])
-rf50kb$Feature[grep("_dist", rf50kb$Feature)] <- gsub("_dist","",rf50kb$Feature[grep("_dist", rf50kb$Feature)])
-rf50kb$Importance <- rf50kb$Importance/sum(rf50kb$Importance)
-
-rfimpvars <- readRDS("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/RData/GM12878/100kb/CHR1/rus/distance/enet/rfimpvars.rds")
-
-rf100kb <- data.frame(Feature = as.character(rownames(rfimpvars)),
-					Importance = rowMeans(rfimpvars))
-rownames(rf100kb) <- NULL
-rf100kb$Feature <- as.character(rf100kb$Feature)
-rf100kb$Feature[grep("Gm12878-", rf100kb$Feature)] <- gsub("Gm12878-","",rf100kb$Feature[grep("Gm12878-", rf100kb$Feature)])
-rf100kb$Feature[grep("_dist", rf100kb$Feature)] <- gsub("_dist","",rf100kb$Feature[grep("_dist", rf100kb$Feature)])
-rf100kb$Importance <- rf100kb$Importance/sum(rf100kb$Importance)
-
-commonannots <- union(rf5kb$Feature,union(rf25kb$Feature,union(rf50kb$Feature,rf100kb$Feature)))
-
-networkmat <- matrix(ncol=4, nrow=length(commonannots), dimnames=list(commonannots, c("5kb", "25kb", "50kb", "100kb")))
-
-networkmat[which(rownames(networkmat) %in% rf5kb$Feature),1] <- rf5kb$Importance
-networkmat[which(rownames(networkmat) %in% rf25kb$Feature),2] <- rf25kb$Importance
-networkmat[which(rownames(networkmat) %in% rf50kb$Feature),3] <- rf50kb$Importance
-networkmat[which(rownames(networkmat) %in% rf100kb$Feature),4] <- rf100kb$Importance
-
-networkmat[is.na(networkmat)] <- 0
-networkmat <- networkmat*10
-
-networkdf <- as.data.frame(networkmat)
-
-net = network(networkdf,
-              matrix.type = "bipartite",
-              ignore.eval = FALSE,
-              names.eval = "weights")
-
-col = c("actor" = "green", "event" = "blue")
-
-networkplot <- ggnet2(net, color = "mode", palette = col, edge.size = "weights", label=TRUE)
-
-ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/networkplot.png")
-
-networkdf <- as.data.frame(t(networkdf))
-
-net = network(networkdf,
-              matrix.type = "bipartite",
-              ignore.eval = FALSE,
-              names.eval = "weights")
-
-col = c("actor" = "blue", "event" = "green")
-
-networkplot2 <- ggnet2(net, color = "mode", palette = col, edge.size = "weights", label=TRUE)
-
-ggsave("C:/Users/Spiro Stilianoudakis/Documents/TAD_data/results/GM12878/networkplot2.png")
-
-```

### 2019-03-08 Scripts/evaluating_model_performances.Rmd
script for extracting model performances

---
title: "Evaluating Model Performances"
author: "Spiro Stilianoudakis"
date: "March 8, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

#Barplots of performance metrics for models

## GM12878

###10kb

```{r}
#OC
##None
rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_10kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_10kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_10kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_10kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_10kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878_10kb <- data.frame(Resampling=c(rep("None", 18),
                                       rep("RUS", 18),
                                       rep("ROS", 18),
                                       rep("SMOTE", 18)),
                          Predictor=rep(c(rep("OC", 6),
                                      rep("OP", 6),
                                      rep("Distance", 6)),4),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 12))

all_rfperfs_gm12878_10kb$Performance <- c(round(rfperf_gm12878_10kb_none_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_none_oc[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_none_oc[16,2],2), #f1
                                round(rfperf_gm12878_10kb_none_oc[15,2],2), #mcc
								round(rfperf_gm12878_10kb_none_oc[18,2],2), #youden
								(round(rfperf_gm12878_10kb_none_oc[6,2],2) + round(rfperf_gm12878_10kb_none_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_10kb_none_op[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_none_op[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_none_op[16,2],2), #f1
                                round(rfperf_gm12878_10kb_none_op[15,2],2), #mcc
								round(rfperf_gm12878_10kb_none_op[18,2],2), #youden
								(round(rfperf_gm12878_10kb_none_op[6,2],2) + round(rfperf_gm12878_10kb_none_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_none_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_none_dist[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_none_dist[16,2],2), #f1
                                round(rfperf_gm12878_10kb_none_dist[15,2],2), #mcc
								round(rfperf_gm12878_10kb_none_dist[18,2],2), #youden
								(round(rfperf_gm12878_10kb_none_dist[6,2],2) + round(rfperf_gm12878_10kb_none_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_rus_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_rus_oc[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_rus_oc[16,2],2), #f1
                                round(rfperf_gm12878_10kb_rus_oc[15,2],2), #mcc
								round(rfperf_gm12878_10kb_rus_oc[18,2],2), #youden
								(round(rfperf_gm12878_10kb_rus_oc[6,2],2) + round(rfperf_gm12878_10kb_rus_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_10kb_rus_op[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_rus_op[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_rus_op[16,2],2), #f1
                                round(rfperf_gm12878_10kb_rus_op[15,2],2), #mcc
								round(rfperf_gm12878_10kb_rus_op[18,2],2), #youden
								(round(rfperf_gm12878_10kb_rus_op[6,2],2) + round(rfperf_gm12878_10kb_rus_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_rus_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_rus_dist[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_rus_dist[16,2],2), #f1
                                round(rfperf_gm12878_10kb_rus_dist[15,2],2), #mcc
								round(rfperf_gm12878_10kb_rus_dist[18,2],2), #youden
								(round(rfperf_gm12878_10kb_rus_dist[6,2],2) + round(rfperf_gm12878_10kb_rus_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_ros_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_ros_oc[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_ros_oc[16,2],2), #f1
                                round(rfperf_gm12878_10kb_ros_oc[15,2],2), #mcc
								round(rfperf_gm12878_10kb_ros_oc[18,2],2), #youden
								(round(rfperf_gm12878_10kb_ros_oc[6,2],2) + round(rfperf_gm12878_10kb_ros_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_10kb_ros_op[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_ros_op[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_ros_op[16,2],2), #f1
                                round(rfperf_gm12878_10kb_ros_op[15,2],2), #mcc
								round(rfperf_gm12878_10kb_ros_op[18,2],2), #youden
								(round(rfperf_gm12878_10kb_ros_op[6,2],2) + round(rfperf_gm12878_10kb_ros_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_ros_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_ros_dist[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_ros_dist[16,2],2), #f1
                                round(rfperf_gm12878_10kb_ros_dist[15,2],2), #mcc
								round(rfperf_gm12878_10kb_ros_dist[18,2],2), #youden
								(round(rfperf_gm12878_10kb_ros_dist[6,2],2) + round(rfperf_gm12878_10kb_ros_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_smote_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_smote_oc[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_smote_oc[16,2],2), #f1
                                round(rfperf_gm12878_10kb_smote_oc[15,2],2), #mcc
								round(rfperf_gm12878_10kb_smote_oc[18,2],2), #youden
								(round(rfperf_gm12878_10kb_smote_oc[6,2],2) + round(rfperf_gm12878_10kb_smote_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_10kb_smote_op[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_smote_op[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_smote_op[16,2],2), #f1
                                round(rfperf_gm12878_10kb_smote_op[15,2],2), #mcc
								round(rfperf_gm12878_10kb_smote_op[18,2],2), #youden
								(round(rfperf_gm12878_10kb_smote_op[6,2],2) + round(rfperf_gm12878_10kb_smote_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_smote_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_smote_dist[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_smote_dist[16,2],2), #f1
                                round(rfperf_gm12878_10kb_smote_dist[15,2],2), #mcc
								round(rfperf_gm12878_10kb_smote_dist[18,2],2), #youden
								(round(rfperf_gm12878_10kb_smote_dist[6,2],2) + round(rfperf_gm12878_10kb_smote_dist[7,2],2))/2 #balanced accuracy
								)
all_rfperfs_gm12878_10kb$Resampling <- factor(all_rfperfs_gm12878_10kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
all_rfperfs_gm12878_10kb$Predictor <- factor(all_rfperfs_gm12878_10kb$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_gm12878_10kb$Metric <- factor(all_rfperfs_gm12878_10kb$Metric, levels = c("Accuracy",
                                                                                      "AUPRC",
                                                                                      "F1-Score",
                                                                                      "MCC",
                                                                                      "Informedness",
                                                                                      "Balanced Acc"))

#comparing only f1 and mcc

ggplot(all_rfperfs_gm12878_10kb[which(all_rfperfs_gm12878_10kb$Metric=="F1-Score" |
                                               all_rfperfs_gm12878_10kb$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

#comparing only informedness and balanced acc

ggplot(all_rfperfs_gm12878_10kb[which(all_rfperfs_gm12878_10kb$Metric=="Informedness" |
                                               all_rfperfs_gm12878_10kb$Metric=="Balanced Acc"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

```

###25kb

```{r}
#OC
##None
rfperf_gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_25kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_25kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_25kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_25kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_25kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_25kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_25kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878_25kb <- data.frame(Resampling=c(rep("None", 18),
                                       rep("RUS", 18),
                                       rep("ROS", 18),
                                       rep("SMOTE", 18)),
                          Predictor=rep(c(rep("OC", 6),
                                      rep("OP", 6),
                                      rep("Distance", 6)),4),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 12))

all_rfperfs_gm12878_25kb$Performance <- c(round(rfperf_gm12878_25kb_none_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_none_oc[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_none_oc[16,2],2), #f1
                                round(rfperf_gm12878_25kb_none_oc[15,2],2), #mcc
								round(rfperf_gm12878_25kb_none_oc[18,2],2), #youden
								(round(rfperf_gm12878_25kb_none_oc[6,2],2) + round(rfperf_gm12878_25kb_none_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_25kb_none_op[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_none_op[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_none_op[16,2],2), #f1
                                round(rfperf_gm12878_25kb_none_op[15,2],2), #mcc
								round(rfperf_gm12878_25kb_none_op[18,2],2), #youden
								(round(rfperf_gm12878_25kb_none_op[6,2],2) + round(rfperf_gm12878_25kb_none_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_none_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_none_dist[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_none_dist[16,2],2), #f1
                                round(rfperf_gm12878_25kb_none_dist[15,2],2), #mcc
								round(rfperf_gm12878_25kb_none_dist[18,2],2), #youden
								(round(rfperf_gm12878_25kb_none_dist[6,2],2) + round(rfperf_gm12878_25kb_none_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_rus_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_rus_oc[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_rus_oc[16,2],2), #f1
                                round(rfperf_gm12878_25kb_rus_oc[15,2],2), #mcc
								round(rfperf_gm12878_25kb_rus_oc[18,2],2), #youden
								(round(rfperf_gm12878_25kb_rus_oc[6,2],2) + round(rfperf_gm12878_25kb_rus_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_25kb_rus_op[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_rus_op[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_rus_op[16,2],2), #f1
                                round(rfperf_gm12878_25kb_rus_op[15,2],2), #mcc
								round(rfperf_gm12878_25kb_rus_op[18,2],2), #youden
								(round(rfperf_gm12878_25kb_rus_op[6,2],2) + round(rfperf_gm12878_25kb_rus_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_rus_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_rus_dist[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_rus_dist[16,2],2), #f1
                                round(rfperf_gm12878_25kb_rus_dist[15,2],2), #mcc
								round(rfperf_gm12878_25kb_rus_dist[18,2],2), #youden
								(round(rfperf_gm12878_25kb_rus_dist[6,2],2) + round(rfperf_gm12878_25kb_rus_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_ros_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_ros_oc[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_ros_oc[16,2],2), #f1
                                round(rfperf_gm12878_25kb_ros_oc[15,2],2), #mcc
								round(rfperf_gm12878_25kb_ros_oc[18,2],2), #youden
								(round(rfperf_gm12878_25kb_ros_oc[6,2],2) + round(rfperf_gm12878_25kb_ros_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_25kb_ros_op[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_ros_op[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_ros_op[16,2],2), #f1
                                round(rfperf_gm12878_25kb_ros_op[15,2],2), #mcc
								round(rfperf_gm12878_25kb_ros_op[18,2],2), #youden
								(round(rfperf_gm12878_25kb_ros_op[6,2],2) + round(rfperf_gm12878_25kb_ros_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_ros_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_ros_dist[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_ros_dist[16,2],2), #f1
                                round(rfperf_gm12878_25kb_ros_dist[15,2],2), #mcc
								round(rfperf_gm12878_25kb_ros_dist[18,2],2), #youden
								(round(rfperf_gm12878_25kb_ros_dist[6,2],2) + round(rfperf_gm12878_25kb_ros_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_smote_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_smote_oc[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_smote_oc[16,2],2), #f1
                                round(rfperf_gm12878_25kb_smote_oc[15,2],2), #mcc
								round(rfperf_gm12878_25kb_smote_oc[18,2],2), #youden
								(round(rfperf_gm12878_25kb_smote_oc[6,2],2) + round(rfperf_gm12878_25kb_smote_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_25kb_smote_op[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_smote_op[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_smote_op[16,2],2), #f1
                                round(rfperf_gm12878_25kb_smote_op[15,2],2), #mcc
								round(rfperf_gm12878_25kb_smote_op[18,2],2), #youden
								(round(rfperf_gm12878_25kb_smote_op[6,2],2) + round(rfperf_gm12878_25kb_smote_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_smote_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_smote_dist[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_smote_dist[16,2],2), #f1
                                round(rfperf_gm12878_25kb_smote_dist[15,2],2), #mcc
								round(rfperf_gm12878_25kb_smote_dist[18,2],2), #youden
								(round(rfperf_gm12878_25kb_smote_dist[6,2],2) + round(rfperf_gm12878_25kb_smote_dist[7,2],2))/2 #balanced accuracy
								)
all_rfperfs_gm12878_25kb$Resampling <- factor(all_rfperfs_gm12878_25kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
all_rfperfs_gm12878_25kb$Predictor <- factor(all_rfperfs_gm12878_25kb$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_gm12878_25kb$Metric <- factor(all_rfperfs_gm12878_25kb$Metric, levels = c("Accuracy",
                                                                                      "AUPRC",
                                                                                      "F1-Score",
                                                                                      "MCC",
                                                                                      "Informedness",
                                                                                      "Balanced Acc"))

#comparing only f1 and mcc

ggplot(all_rfperfs_gm12878_25kb[which(all_rfperfs_gm12878_25kb$Metric=="F1-Score" |
                                               all_rfperfs_gm12878_25kb$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

#comparing only informedness and balanced acc

ggplot(all_rfperfs_gm12878_25kb[which(all_rfperfs_gm12878_25kb$Metric=="Informedness" |
                                               all_rfperfs_gm12878_25kb$Metric=="Balanced Acc"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

```

###50kb

```{r}
#OC
##None
rfperf_gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_50kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_50kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_50kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_50kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_50kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_50kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_50kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878_50kb <- data.frame(Resampling=c(rep("None", 18),
                                       rep("RUS", 18),
                                       rep("ROS", 18),
                                       rep("SMOTE", 18)),
                          Predictor=rep(c(rep("OC", 6),
                                      rep("OP", 6),
                                      rep("Distance", 6)),4),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 12))

all_rfperfs_gm12878_50kb$Performance <- c(round(rfperf_gm12878_50kb_none_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_none_oc[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_none_oc[16,2],2), #f1
                                round(rfperf_gm12878_50kb_none_oc[15,2],2), #mcc
								round(rfperf_gm12878_50kb_none_oc[18,2],2), #youden
								(round(rfperf_gm12878_50kb_none_oc[6,2],2) + round(rfperf_gm12878_50kb_none_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_50kb_none_op[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_none_op[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_none_op[16,2],2), #f1
                                round(rfperf_gm12878_50kb_none_op[15,2],2), #mcc
								round(rfperf_gm12878_50kb_none_op[18,2],2), #youden
								(round(rfperf_gm12878_50kb_none_op[6,2],2) + round(rfperf_gm12878_50kb_none_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_none_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_none_dist[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_none_dist[16,2],2), #f1
                                round(rfperf_gm12878_50kb_none_dist[15,2],2), #mcc
								round(rfperf_gm12878_50kb_none_dist[18,2],2), #youden
								(round(rfperf_gm12878_50kb_none_dist[6,2],2) + round(rfperf_gm12878_50kb_none_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_rus_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_rus_oc[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_rus_oc[16,2],2), #f1
                                round(rfperf_gm12878_50kb_rus_oc[15,2],2), #mcc
								round(rfperf_gm12878_50kb_rus_oc[18,2],2), #youden
								(round(rfperf_gm12878_50kb_rus_oc[6,2],2) + round(rfperf_gm12878_50kb_rus_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_50kb_rus_op[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_rus_op[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_rus_op[16,2],2), #f1
                                round(rfperf_gm12878_50kb_rus_op[15,2],2), #mcc
								round(rfperf_gm12878_50kb_rus_op[18,2],2), #youden
								(round(rfperf_gm12878_50kb_rus_op[6,2],2) + round(rfperf_gm12878_50kb_rus_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_rus_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_rus_dist[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_rus_dist[16,2],2), #f1
                                round(rfperf_gm12878_50kb_rus_dist[15,2],2), #mcc
								round(rfperf_gm12878_50kb_rus_dist[18,2],2), #youden
								(round(rfperf_gm12878_50kb_rus_dist[6,2],2) + round(rfperf_gm12878_50kb_rus_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_ros_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_ros_oc[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_ros_oc[16,2],2), #f1
                                round(rfperf_gm12878_50kb_ros_oc[15,2],2), #mcc
								round(rfperf_gm12878_50kb_ros_oc[18,2],2), #youden
								(round(rfperf_gm12878_50kb_ros_oc[6,2],2) + round(rfperf_gm12878_50kb_ros_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_50kb_ros_op[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_ros_op[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_ros_op[16,2],2), #f1
                                round(rfperf_gm12878_50kb_ros_op[15,2],2), #mcc
								round(rfperf_gm12878_50kb_ros_op[18,2],2), #youden
								(round(rfperf_gm12878_50kb_ros_op[6,2],2) + round(rfperf_gm12878_50kb_ros_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_ros_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_ros_dist[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_ros_dist[16,2],2), #f1
                                round(rfperf_gm12878_50kb_ros_dist[15,2],2), #mcc
								round(rfperf_gm12878_50kb_ros_dist[18,2],2), #youden
								(round(rfperf_gm12878_50kb_ros_dist[6,2],2) + round(rfperf_gm12878_50kb_ros_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_smote_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_smote_oc[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_smote_oc[16,2],2), #f1
                                round(rfperf_gm12878_50kb_smote_oc[15,2],2), #mcc
								round(rfperf_gm12878_50kb_smote_oc[18,2],2), #youden
								(round(rfperf_gm12878_50kb_smote_oc[6,2],2) + round(rfperf_gm12878_50kb_smote_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_50kb_smote_op[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_smote_op[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_smote_op[16,2],2), #f1
                                round(rfperf_gm12878_50kb_smote_op[15,2],2), #mcc
								round(rfperf_gm12878_50kb_smote_op[18,2],2), #youden
								(round(rfperf_gm12878_50kb_smote_op[6,2],2) + round(rfperf_gm12878_50kb_smote_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_smote_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_smote_dist[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_smote_dist[16,2],2), #f1
                                round(rfperf_gm12878_50kb_smote_dist[15,2],2), #mcc
								round(rfperf_gm12878_50kb_smote_dist[18,2],2), #youden
								(round(rfperf_gm12878_50kb_smote_dist[6,2],2) + round(rfperf_gm12878_50kb_smote_dist[7,2],2))/2 #balanced accuracy
								)
all_rfperfs_gm12878_50kb$Resampling <- factor(all_rfperfs_gm12878_50kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
all_rfperfs_gm12878_50kb$Predictor <- factor(all_rfperfs_gm12878_50kb$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_gm12878_50kb$Metric <- factor(all_rfperfs_gm12878_50kb$Metric, levels = c("Accuracy",
                                                                                      "AUPRC",
                                                                                      "F1-Score",
                                                                                      "MCC",
                                                                                      "Informedness",
                                                                                      "Balanced Acc"))

#comparing only f1 and mcc

ggplot(all_rfperfs_gm12878_50kb[which(all_rfperfs_gm12878_50kb$Metric=="F1-Score" |
                                               all_rfperfs_gm12878_50kb$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

#comparing only informedness and balanced acc

ggplot(all_rfperfs_gm12878_50kb[which(all_rfperfs_gm12878_50kb$Metric=="Informedness" |
                                               all_rfperfs_gm12878_50kb$Metric=="Balanced Acc"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

```

###100kb

```{r}
#OC
##None
rfperf_gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_100kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_100kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_100kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_100kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_100kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_100kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_100kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878_100kb <- data.frame(Resampling=c(rep("None", 18),
                                       rep("RUS", 18),
                                       rep("ROS", 18),
                                       rep("SMOTE", 18)),
                          Predictor=rep(c(rep("OC", 6),
                                      rep("OP", 6),
                                      rep("Distance", 6)),4),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 12))

all_rfperfs_gm12878_100kb$Performance <- c(round(rfperf_gm12878_100kb_none_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_100kb_none_oc[19,2],2), #auprc
                                round(rfperf_gm12878_100kb_none_oc[16,2],2), #f1
                                round(rfperf_gm12878_100kb_none_oc[15,2],2), #mcc
								round(rfperf_gm12878_100kb_none_oc[18,2],2), #youden
								(round(rfperf_gm12878_100kb_none_oc[6,2],2) + round(rfperf_gm12878_100kb_none_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_100kb_none_op[9,2],2), #accuracy
                                round(rfperf_gm12878_100kb_none_op[19,2],2), #auprc
                                round(rfperf_gm12878_100kb_none_op[16,2],2), #f1
                                round(rfperf_gm12878_100kb_none_op[15,2],2), #mcc
								round(rfperf_gm12878_100kb_none_op[18,2],2), #youden
								(round(rfperf_gm12878_100kb_none_op[6,2],2) + round(rfperf_gm12878_100kb_none_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_100kb_none_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_100kb_none_dist[19,2],2), #auprc
                                round(rfperf_gm12878_100kb_none_dist[16,2],2), #f1
                                round(rfperf_gm12878_100kb_none_dist[15,2],2), #mcc
								round(rfperf_gm12878_100kb_none_dist[18,2],2), #youden
								(round(rfperf_gm12878_100kb_none_dist[6,2],2) + round(rfperf_gm12878_100kb_none_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_100kb_rus_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_100kb_rus_oc[19,2],2), #auprc
                                round(rfperf_gm12878_100kb_rus_oc[16,2],2), #f1
                                round(rfperf_gm12878_100kb_rus_oc[15,2],2), #mcc
								round(rfperf_gm12878_100kb_rus_oc[18,2],2), #youden
								(round(rfperf_gm12878_100kb_rus_oc[6,2],2) + round(rfperf_gm12878_100kb_rus_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_100kb_rus_op[9,2],2), #accuracy
                                round(rfperf_gm12878_100kb_rus_op[19,2],2), #auprc
                                round(rfperf_gm12878_100kb_rus_op[16,2],2), #f1
                                round(rfperf_gm12878_100kb_rus_op[15,2],2), #mcc
								round(rfperf_gm12878_100kb_rus_op[18,2],2), #youden
								(round(rfperf_gm12878_100kb_rus_op[6,2],2) + round(rfperf_gm12878_100kb_rus_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_100kb_rus_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_100kb_rus_dist[19,2],2), #auprc
                                round(rfperf_gm12878_100kb_rus_dist[16,2],2), #f1
                                round(rfperf_gm12878_100kb_rus_dist[15,2],2), #mcc
								round(rfperf_gm12878_100kb_rus_dist[18,2],2), #youden
								(round(rfperf_gm12878_100kb_rus_dist[6,2],2) + round(rfperf_gm12878_100kb_rus_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_100kb_ros_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_100kb_ros_oc[19,2],2), #auprc
                                round(rfperf_gm12878_100kb_ros_oc[16,2],2), #f1
                                round(rfperf_gm12878_100kb_ros_oc[15,2],2), #mcc
								round(rfperf_gm12878_100kb_ros_oc[18,2],2), #youden
								(round(rfperf_gm12878_100kb_ros_oc[6,2],2) + round(rfperf_gm12878_100kb_ros_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_100kb_ros_op[9,2],2), #accuracy
                                round(rfperf_gm12878_100kb_ros_op[19,2],2), #auprc
                                round(rfperf_gm12878_100kb_ros_op[16,2],2), #f1
                                round(rfperf_gm12878_100kb_ros_op[15,2],2), #mcc
								round(rfperf_gm12878_100kb_ros_op[18,2],2), #youden
								(round(rfperf_gm12878_100kb_ros_op[6,2],2) + round(rfperf_gm12878_100kb_ros_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_100kb_ros_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_100kb_ros_dist[19,2],2), #auprc
                                round(rfperf_gm12878_100kb_ros_dist[16,2],2), #f1
                                round(rfperf_gm12878_100kb_ros_dist[15,2],2), #mcc
								round(rfperf_gm12878_100kb_ros_dist[18,2],2), #youden
								(round(rfperf_gm12878_100kb_ros_dist[6,2],2) + round(rfperf_gm12878_100kb_ros_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_100kb_smote_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_100kb_smote_oc[19,2],2), #auprc
                                round(rfperf_gm12878_100kb_smote_oc[16,2],2), #f1
                                round(rfperf_gm12878_100kb_smote_oc[15,2],2), #mcc
								round(rfperf_gm12878_100kb_smote_oc[18,2],2), #youden
								(round(rfperf_gm12878_100kb_smote_oc[6,2],2) + round(rfperf_gm12878_100kb_smote_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_100kb_smote_op[9,2],2), #accuracy
                                round(rfperf_gm12878_100kb_smote_op[19,2],2), #auprc
                                round(rfperf_gm12878_100kb_smote_op[16,2],2), #f1
                                round(rfperf_gm12878_100kb_smote_op[15,2],2), #mcc
								round(rfperf_gm12878_100kb_smote_op[18,2],2), #youden
								(round(rfperf_gm12878_100kb_smote_op[6,2],2) + round(rfperf_gm12878_100kb_smote_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_100kb_smote_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_100kb_smote_dist[19,2],2), #auprc
                                round(rfperf_gm12878_100kb_smote_dist[16,2],2), #f1
                                round(rfperf_gm12878_100kb_smote_dist[15,2],2), #mcc
								round(rfperf_gm12878_100kb_smote_dist[18,2],2), #youden
								(round(rfperf_gm12878_100kb_smote_dist[6,2],2) + round(rfperf_gm12878_100kb_smote_dist[7,2],2))/2 #balanced accuracy
								)
all_rfperfs_gm12878_100kb$Resampling <- factor(all_rfperfs_gm12878_100kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
all_rfperfs_gm12878_100kb$Predictor <- factor(all_rfperfs_gm12878_100kb$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_gm12878_100kb$Metric <- factor(all_rfperfs_gm12878_100kb$Metric, levels = c("Accuracy",
                                                                                      "AUPRC",
                                                                                      "F1-Score",
                                                                                      "MCC",
                                                                                      "Informedness",
                                                                                      "Balanced Acc"))

#comparing only f1 and mcc

ggplot(all_rfperfs_gm12878_100kb[which(all_rfperfs_gm12878_100kb$Metric=="F1-Score" |
                                               all_rfperfs_gm12878_100kb$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

#comparing only informedness and balanced acc

ggplot(all_rfperfs_gm12878_100kb[which(all_rfperfs_gm12878_100kb$Metric=="Informedness" |
                                               all_rfperfs_gm12878_100kb$Metric=="Balanced Acc"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

```

## K562

###10kb

```{r}
#OC
##None
rfperf_K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_K562_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##ROS
rfperf_K562_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_K562_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_K562_10kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_K562_10kb_rus_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##ROS
rfperf_K562_10kb_ros_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_K562_10kb_smote_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_K562_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_K562_10kb_rus_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##ROS
rfperf_K562_10kb_ros_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_K562_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_K562_10kb <- data.frame(Resampling=c(rep("None", 18),
                                       rep("RUS", 18),
                                       rep("ROS", 18),
                                       rep("SMOTE", 18)),
                          Predictor=rep(c(rep("OC", 6),
                                      rep("OP", 6),
                                      rep("Distance", 6)),4),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 12))

all_rfperfs_K562_10kb$Performance <- c(round(rfperf_K562_10kb_none_oc[9,2],2), #accuracy
                                round(rfperf_K562_10kb_none_oc[19,2],2), #auprc
                                round(rfperf_K562_10kb_none_oc[16,2],2), #f1
                                round(rfperf_K562_10kb_none_oc[15,2],2), #mcc
								round(rfperf_K562_10kb_none_oc[18,2],2), #youden
								(round(rfperf_K562_10kb_none_oc[6,2],2) + round(rfperf_K562_10kb_none_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_10kb_none_op[9,2],2), #accuracy
                                round(rfperf_K562_10kb_none_op[19,2],2), #auprc
                                round(rfperf_K562_10kb_none_op[16,2],2), #f1
                                round(rfperf_K562_10kb_none_op[15,2],2), #mcc
								round(rfperf_K562_10kb_none_op[18,2],2), #youden
								(round(rfperf_K562_10kb_none_op[6,2],2) + round(rfperf_K562_10kb_none_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_10kb_none_dist[9,2],2), #accuracy
                                round(rfperf_K562_10kb_none_dist[19,2],2), #auprc
                                round(rfperf_K562_10kb_none_dist[16,2],2), #f1
                                round(rfperf_K562_10kb_none_dist[15,2],2), #mcc
								round(rfperf_K562_10kb_none_dist[18,2],2), #youden
								(round(rfperf_K562_10kb_none_dist[6,2],2) + round(rfperf_K562_10kb_none_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_10kb_rus_oc[9,2],2), #accuracy
                                round(rfperf_K562_10kb_rus_oc[19,2],2), #auprc
                                round(rfperf_K562_10kb_rus_oc[16,2],2), #f1
                                round(rfperf_K562_10kb_rus_oc[15,2],2), #mcc
								round(rfperf_K562_10kb_rus_oc[18,2],2), #youden
								(round(rfperf_K562_10kb_rus_oc[6,2],2) + round(rfperf_K562_10kb_rus_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_10kb_rus_op[9,2],2), #accuracy
                                round(rfperf_K562_10kb_rus_op[19,2],2), #auprc
                                round(rfperf_K562_10kb_rus_op[16,2],2), #f1
                                round(rfperf_K562_10kb_rus_op[15,2],2), #mcc
								round(rfperf_K562_10kb_rus_op[18,2],2), #youden
								(round(rfperf_K562_10kb_rus_op[6,2],2) + round(rfperf_K562_10kb_rus_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_10kb_rus_dist[9,2],2), #accuracy
                                round(rfperf_K562_10kb_rus_dist[19,2],2), #auprc
                                round(rfperf_K562_10kb_rus_dist[16,2],2), #f1
                                round(rfperf_K562_10kb_rus_dist[15,2],2), #mcc
								round(rfperf_K562_10kb_rus_dist[18,2],2), #youden
								(round(rfperf_K562_10kb_rus_dist[6,2],2) + round(rfperf_K562_10kb_rus_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_10kb_ros_oc[9,2],2), #accuracy
                                round(rfperf_K562_10kb_ros_oc[19,2],2), #auprc
                                round(rfperf_K562_10kb_ros_oc[16,2],2), #f1
                                round(rfperf_K562_10kb_ros_oc[15,2],2), #mcc
								round(rfperf_K562_10kb_ros_oc[18,2],2), #youden
								(round(rfperf_K562_10kb_ros_oc[6,2],2) + round(rfperf_K562_10kb_ros_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_10kb_ros_op[9,2],2), #accuracy
                                round(rfperf_K562_10kb_ros_op[19,2],2), #auprc
                                round(rfperf_K562_10kb_ros_op[16,2],2), #f1
                                round(rfperf_K562_10kb_ros_op[15,2],2), #mcc
								round(rfperf_K562_10kb_ros_op[18,2],2), #youden
								(round(rfperf_K562_10kb_ros_op[6,2],2) + round(rfperf_K562_10kb_ros_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_10kb_ros_dist[9,2],2), #accuracy
                                round(rfperf_K562_10kb_ros_dist[19,2],2), #auprc
                                round(rfperf_K562_10kb_ros_dist[16,2],2), #f1
                                round(rfperf_K562_10kb_ros_dist[15,2],2), #mcc
								round(rfperf_K562_10kb_ros_dist[18,2],2), #youden
								(round(rfperf_K562_10kb_ros_dist[6,2],2) + round(rfperf_K562_10kb_ros_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_10kb_smote_oc[9,2],2), #accuracy
                                round(rfperf_K562_10kb_smote_oc[19,2],2), #auprc
                                round(rfperf_K562_10kb_smote_oc[16,2],2), #f1
                                round(rfperf_K562_10kb_smote_oc[15,2],2), #mcc
								round(rfperf_K562_10kb_smote_oc[18,2],2), #youden
								(round(rfperf_K562_10kb_smote_oc[6,2],2) + round(rfperf_K562_10kb_smote_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_10kb_smote_op[9,2],2), #accuracy
                                round(rfperf_K562_10kb_smote_op[19,2],2), #auprc
                                round(rfperf_K562_10kb_smote_op[16,2],2), #f1
                                round(rfperf_K562_10kb_smote_op[15,2],2), #mcc
								round(rfperf_K562_10kb_smote_op[18,2],2), #youden
								(round(rfperf_K562_10kb_smote_op[6,2],2) + round(rfperf_K562_10kb_smote_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_10kb_smote_dist[9,2],2), #accuracy
                                round(rfperf_K562_10kb_smote_dist[19,2],2), #auprc
                                round(rfperf_K562_10kb_smote_dist[16,2],2), #f1
                                round(rfperf_K562_10kb_smote_dist[15,2],2), #mcc
								round(rfperf_K562_10kb_smote_dist[18,2],2), #youden
								(round(rfperf_K562_10kb_smote_dist[6,2],2) + round(rfperf_K562_10kb_smote_dist[7,2],2))/2 #balanced accuracy
								)
all_rfperfs_K562_10kb$Resampling <- factor(all_rfperfs_K562_10kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
all_rfperfs_K562_10kb$Predictor <- factor(all_rfperfs_K562_10kb$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_K562_10kb$Metric <- factor(all_rfperfs_K562_10kb$Metric, levels = c("Accuracy",
                                                                                      "AUPRC",
                                                                                      "F1-Score",
                                                                                      "MCC",
                                                                                      "Informedness",
                                                                                      "Balanced Acc"))

#comparing only f1 and mcc

ggplot(all_rfperfs_K562_10kb[which(all_rfperfs_K562_10kb$Metric=="F1-Score" |
                                               all_rfperfs_K562_10kb$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

#comparing only informedness and balanced acc

ggplot(all_rfperfs_K562_10kb[which(all_rfperfs_K562_10kb$Metric=="Informedness" |
                                               all_rfperfs_K562_10kb$Metric=="Balanced Acc"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

```

###25kb

```{r}
#OC
##None
rfperf_K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_K562_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##ROS
rfperf_K562_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_K562_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_K562_25kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_K562_25kb_rus_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##ROS
rfperf_K562_25kb_ros_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_K562_25kb_smote_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_K562_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_K562_25kb_rus_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##ROS
rfperf_K562_25kb_ros_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_K562_25kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_K562_25kb <- data.frame(Resampling=c(rep("None", 18),
                                       rep("RUS", 18),
                                       rep("ROS", 18),
                                       rep("SMOTE", 18)),
                          Predictor=rep(c(rep("OC", 6),
                                      rep("OP", 6),
                                      rep("Distance", 6)),4),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 12))

all_rfperfs_K562_25kb$Performance <- c(round(rfperf_K562_25kb_none_oc[9,2],2), #accuracy
                                round(rfperf_K562_25kb_none_oc[19,2],2), #auprc
                                round(rfperf_K562_25kb_none_oc[16,2],2), #f1
                                round(rfperf_K562_25kb_none_oc[15,2],2), #mcc
								round(rfperf_K562_25kb_none_oc[18,2],2), #youden
								(round(rfperf_K562_25kb_none_oc[6,2],2) + round(rfperf_K562_25kb_none_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_25kb_none_op[9,2],2), #accuracy
                                round(rfperf_K562_25kb_none_op[19,2],2), #auprc
                                round(rfperf_K562_25kb_none_op[16,2],2), #f1
                                round(rfperf_K562_25kb_none_op[15,2],2), #mcc
								round(rfperf_K562_25kb_none_op[18,2],2), #youden
								(round(rfperf_K562_25kb_none_op[6,2],2) + round(rfperf_K562_25kb_none_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_25kb_none_dist[9,2],2), #accuracy
                                round(rfperf_K562_25kb_none_dist[19,2],2), #auprc
                                round(rfperf_K562_25kb_none_dist[16,2],2), #f1
                                round(rfperf_K562_25kb_none_dist[15,2],2), #mcc
								round(rfperf_K562_25kb_none_dist[18,2],2), #youden
								(round(rfperf_K562_25kb_none_dist[6,2],2) + round(rfperf_K562_25kb_none_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_25kb_rus_oc[9,2],2), #accuracy
                                round(rfperf_K562_25kb_rus_oc[19,2],2), #auprc
                                round(rfperf_K562_25kb_rus_oc[16,2],2), #f1
                                round(rfperf_K562_25kb_rus_oc[15,2],2), #mcc
								round(rfperf_K562_25kb_rus_oc[18,2],2), #youden
								(round(rfperf_K562_25kb_rus_oc[6,2],2) + round(rfperf_K562_25kb_rus_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_25kb_rus_op[9,2],2), #accuracy
                                round(rfperf_K562_25kb_rus_op[19,2],2), #auprc
                                round(rfperf_K562_25kb_rus_op[16,2],2), #f1
                                round(rfperf_K562_25kb_rus_op[15,2],2), #mcc
								round(rfperf_K562_25kb_rus_op[18,2],2), #youden
								(round(rfperf_K562_25kb_rus_op[6,2],2) + round(rfperf_K562_25kb_rus_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_25kb_rus_dist[9,2],2), #accuracy
                                round(rfperf_K562_25kb_rus_dist[19,2],2), #auprc
                                round(rfperf_K562_25kb_rus_dist[16,2],2), #f1
                                round(rfperf_K562_25kb_rus_dist[15,2],2), #mcc
								round(rfperf_K562_25kb_rus_dist[18,2],2), #youden
								(round(rfperf_K562_25kb_rus_dist[6,2],2) + round(rfperf_K562_25kb_rus_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_25kb_ros_oc[9,2],2), #accuracy
                                round(rfperf_K562_25kb_ros_oc[19,2],2), #auprc
                                round(rfperf_K562_25kb_ros_oc[16,2],2), #f1
                                round(rfperf_K562_25kb_ros_oc[15,2],2), #mcc
								round(rfperf_K562_25kb_ros_oc[18,2],2), #youden
								(round(rfperf_K562_25kb_ros_oc[6,2],2) + round(rfperf_K562_25kb_ros_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_25kb_ros_op[9,2],2), #accuracy
                                round(rfperf_K562_25kb_ros_op[19,2],2), #auprc
                                round(rfperf_K562_25kb_ros_op[16,2],2), #f1
                                round(rfperf_K562_25kb_ros_op[15,2],2), #mcc
								round(rfperf_K562_25kb_ros_op[18,2],2), #youden
								(round(rfperf_K562_25kb_ros_op[6,2],2) + round(rfperf_K562_25kb_ros_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_25kb_ros_dist[9,2],2), #accuracy
                                round(rfperf_K562_25kb_ros_dist[19,2],2), #auprc
                                round(rfperf_K562_25kb_ros_dist[16,2],2), #f1
                                round(rfperf_K562_25kb_ros_dist[15,2],2), #mcc
								round(rfperf_K562_25kb_ros_dist[18,2],2), #youden
								(round(rfperf_K562_25kb_ros_dist[6,2],2) + round(rfperf_K562_25kb_ros_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_25kb_smote_oc[9,2],2), #accuracy
                                round(rfperf_K562_25kb_smote_oc[19,2],2), #auprc
                                round(rfperf_K562_25kb_smote_oc[16,2],2), #f1
                                round(rfperf_K562_25kb_smote_oc[15,2],2), #mcc
								round(rfperf_K562_25kb_smote_oc[18,2],2), #youden
								(round(rfperf_K562_25kb_smote_oc[6,2],2) + round(rfperf_K562_25kb_smote_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_25kb_smote_op[9,2],2), #accuracy
                                round(rfperf_K562_25kb_smote_op[19,2],2), #auprc
                                round(rfperf_K562_25kb_smote_op[16,2],2), #f1
                                round(rfperf_K562_25kb_smote_op[15,2],2), #mcc
								round(rfperf_K562_25kb_smote_op[18,2],2), #youden
								(round(rfperf_K562_25kb_smote_op[6,2],2) + round(rfperf_K562_25kb_smote_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_25kb_smote_dist[9,2],2), #accuracy
                                round(rfperf_K562_25kb_smote_dist[19,2],2), #auprc
                                round(rfperf_K562_25kb_smote_dist[16,2],2), #f1
                                round(rfperf_K562_25kb_smote_dist[15,2],2), #mcc
								round(rfperf_K562_25kb_smote_dist[18,2],2), #youden
								(round(rfperf_K562_25kb_smote_dist[6,2],2) + round(rfperf_K562_25kb_smote_dist[7,2],2))/2 #balanced accuracy
								)
all_rfperfs_K562_25kb$Resampling <- factor(all_rfperfs_K562_25kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
all_rfperfs_K562_25kb$Predictor <- factor(all_rfperfs_K562_25kb$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_K562_25kb$Metric <- factor(all_rfperfs_K562_25kb$Metric, levels = c("Accuracy",
                                                                                      "AUPRC",
                                                                                      "F1-Score",
                                                                                      "MCC",
                                                                                      "Informedness",
                                                                                      "Balanced Acc"))

#comparing only f1 and mcc

ggplot(all_rfperfs_K562_25kb[which(all_rfperfs_K562_25kb$Metric=="F1-Score" |
                                               all_rfperfs_K562_25kb$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

#comparing only informedness and balanced acc

ggplot(all_rfperfs_K562_25kb[which(all_rfperfs_K562_25kb$Metric=="Informedness" |
                                               all_rfperfs_K562_25kb$Metric=="Balanced Acc"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

```

###50kb

```{r}
#OC
##None
rfperf_K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_K562_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##ROS
rfperf_K562_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_K562_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_K562_50kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_K562_50kb_rus_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##ROS
rfperf_K562_50kb_ros_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_K562_50kb_smote_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_K562_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_K562_50kb_rus_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##ROS
rfperf_K562_50kb_ros_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_K562_50kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_K562_50kb <- data.frame(Resampling=c(rep("None", 18),
                                       rep("RUS", 18),
                                       rep("ROS", 18),
                                       rep("SMOTE", 18)),
                          Predictor=rep(c(rep("OC", 6),
                                      rep("OP", 6),
                                      rep("Distance", 6)),4),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 12))

all_rfperfs_K562_50kb$Performance <- c(round(rfperf_K562_50kb_none_oc[9,2],2), #accuracy
                                round(rfperf_K562_50kb_none_oc[19,2],2), #auprc
                                round(rfperf_K562_50kb_none_oc[16,2],2), #f1
                                round(rfperf_K562_50kb_none_oc[15,2],2), #mcc
								round(rfperf_K562_50kb_none_oc[18,2],2), #youden
								(round(rfperf_K562_50kb_none_oc[6,2],2) + round(rfperf_K562_50kb_none_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_50kb_none_op[9,2],2), #accuracy
                                round(rfperf_K562_50kb_none_op[19,2],2), #auprc
                                round(rfperf_K562_50kb_none_op[16,2],2), #f1
                                round(rfperf_K562_50kb_none_op[15,2],2), #mcc
								round(rfperf_K562_50kb_none_op[18,2],2), #youden
								(round(rfperf_K562_50kb_none_op[6,2],2) + round(rfperf_K562_50kb_none_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_50kb_none_dist[9,2],2), #accuracy
                                round(rfperf_K562_50kb_none_dist[19,2],2), #auprc
                                round(rfperf_K562_50kb_none_dist[16,2],2), #f1
                                round(rfperf_K562_50kb_none_dist[15,2],2), #mcc
								round(rfperf_K562_50kb_none_dist[18,2],2), #youden
								(round(rfperf_K562_50kb_none_dist[6,2],2) + round(rfperf_K562_50kb_none_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_50kb_rus_oc[9,2],2), #accuracy
                                round(rfperf_K562_50kb_rus_oc[19,2],2), #auprc
                                round(rfperf_K562_50kb_rus_oc[16,2],2), #f1
                                round(rfperf_K562_50kb_rus_oc[15,2],2), #mcc
								round(rfperf_K562_50kb_rus_oc[18,2],2), #youden
								(round(rfperf_K562_50kb_rus_oc[6,2],2) + round(rfperf_K562_50kb_rus_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_50kb_rus_op[9,2],2), #accuracy
                                round(rfperf_K562_50kb_rus_op[19,2],2), #auprc
                                round(rfperf_K562_50kb_rus_op[16,2],2), #f1
                                round(rfperf_K562_50kb_rus_op[15,2],2), #mcc
								round(rfperf_K562_50kb_rus_op[18,2],2), #youden
								(round(rfperf_K562_50kb_rus_op[6,2],2) + round(rfperf_K562_50kb_rus_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_50kb_rus_dist[9,2],2), #accuracy
                                round(rfperf_K562_50kb_rus_dist[19,2],2), #auprc
                                round(rfperf_K562_50kb_rus_dist[16,2],2), #f1
                                round(rfperf_K562_50kb_rus_dist[15,2],2), #mcc
								round(rfperf_K562_50kb_rus_dist[18,2],2), #youden
								(round(rfperf_K562_50kb_rus_dist[6,2],2) + round(rfperf_K562_50kb_rus_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_50kb_ros_oc[9,2],2), #accuracy
                                round(rfperf_K562_50kb_ros_oc[19,2],2), #auprc
                                round(rfperf_K562_50kb_ros_oc[16,2],2), #f1
                                round(rfperf_K562_50kb_ros_oc[15,2],2), #mcc
								round(rfperf_K562_50kb_ros_oc[18,2],2), #youden
								(round(rfperf_K562_50kb_ros_oc[6,2],2) + round(rfperf_K562_50kb_ros_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_50kb_ros_op[9,2],2), #accuracy
                                round(rfperf_K562_50kb_ros_op[19,2],2), #auprc
                                round(rfperf_K562_50kb_ros_op[16,2],2), #f1
                                round(rfperf_K562_50kb_ros_op[15,2],2), #mcc
								round(rfperf_K562_50kb_ros_op[18,2],2), #youden
								(round(rfperf_K562_50kb_ros_op[6,2],2) + round(rfperf_K562_50kb_ros_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_50kb_ros_dist[9,2],2), #accuracy
                                round(rfperf_K562_50kb_ros_dist[19,2],2), #auprc
                                round(rfperf_K562_50kb_ros_dist[16,2],2), #f1
                                round(rfperf_K562_50kb_ros_dist[15,2],2), #mcc
								round(rfperf_K562_50kb_ros_dist[18,2],2), #youden
								(round(rfperf_K562_50kb_ros_dist[6,2],2) + round(rfperf_K562_50kb_ros_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_50kb_smote_oc[9,2],2), #accuracy
                                round(rfperf_K562_50kb_smote_oc[19,2],2), #auprc
                                round(rfperf_K562_50kb_smote_oc[16,2],2), #f1
                                round(rfperf_K562_50kb_smote_oc[15,2],2), #mcc
								round(rfperf_K562_50kb_smote_oc[18,2],2), #youden
								(round(rfperf_K562_50kb_smote_oc[6,2],2) + round(rfperf_K562_50kb_smote_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_50kb_smote_op[9,2],2), #accuracy
                                round(rfperf_K562_50kb_smote_op[19,2],2), #auprc
                                round(rfperf_K562_50kb_smote_op[16,2],2), #f1
                                round(rfperf_K562_50kb_smote_op[15,2],2), #mcc
								round(rfperf_K562_50kb_smote_op[18,2],2), #youden
								(round(rfperf_K562_50kb_smote_op[6,2],2) + round(rfperf_K562_50kb_smote_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_50kb_smote_dist[9,2],2), #accuracy
                                round(rfperf_K562_50kb_smote_dist[19,2],2), #auprc
                                round(rfperf_K562_50kb_smote_dist[16,2],2), #f1
                                round(rfperf_K562_50kb_smote_dist[15,2],2), #mcc
								round(rfperf_K562_50kb_smote_dist[18,2],2), #youden
								(round(rfperf_K562_50kb_smote_dist[6,2],2) + round(rfperf_K562_50kb_smote_dist[7,2],2))/2 #balanced accuracy
								)
all_rfperfs_K562_50kb$Resampling <- factor(all_rfperfs_K562_50kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
all_rfperfs_K562_50kb$Predictor <- factor(all_rfperfs_K562_50kb$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_K562_50kb$Metric <- factor(all_rfperfs_K562_50kb$Metric, levels = c("Accuracy",
                                                                                      "AUPRC",
                                                                                      "F1-Score",
                                                                                      "MCC",
                                                                                      "Informedness",
                                                                                      "Balanced Acc"))

#comparing only f1 and mcc

ggplot(all_rfperfs_K562_50kb[which(all_rfperfs_K562_50kb$Metric=="F1-Score" |
                                               all_rfperfs_K562_50kb$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

#comparing only informedness and balanced acc

ggplot(all_rfperfs_K562_50kb[which(all_rfperfs_K562_50kb$Metric=="Informedness" |
                                               all_rfperfs_K562_50kb$Metric=="Balanced Acc"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

```

###100kb

```{r}
#OC
##None
rfperf_K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_K562_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##ROS
rfperf_K562_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_K562_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_K562_100kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_K562_100kb_rus_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##ROS
rfperf_K562_100kb_ros_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_K562_100kb_smote_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_K562_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_K562_100kb_rus_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##ROS
rfperf_K562_100kb_ros_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_K562_100kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_K562_100kb <- data.frame(Resampling=c(rep("None", 18),
                                       rep("RUS", 18),
                                       rep("ROS", 18),
                                       rep("SMOTE", 18)),
                          Predictor=rep(c(rep("OC", 6),
                                      rep("OP", 6),
                                      rep("Distance", 6)),4),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 12))

all_rfperfs_K562_100kb$Performance <- c(round(rfperf_K562_100kb_none_oc[9,2],2), #accuracy
                                round(rfperf_K562_100kb_none_oc[19,2],2), #auprc
                                round(rfperf_K562_100kb_none_oc[16,2],2), #f1
                                round(rfperf_K562_100kb_none_oc[15,2],2), #mcc
								round(rfperf_K562_100kb_none_oc[18,2],2), #youden
								(round(rfperf_K562_100kb_none_oc[6,2],2) + round(rfperf_K562_100kb_none_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_100kb_none_op[9,2],2), #accuracy
                                round(rfperf_K562_100kb_none_op[19,2],2), #auprc
                                round(rfperf_K562_100kb_none_op[16,2],2), #f1
                                round(rfperf_K562_100kb_none_op[15,2],2), #mcc
								round(rfperf_K562_100kb_none_op[18,2],2), #youden
								(round(rfperf_K562_100kb_none_op[6,2],2) + round(rfperf_K562_100kb_none_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_100kb_none_dist[9,2],2), #accuracy
                                round(rfperf_K562_100kb_none_dist[19,2],2), #auprc
                                round(rfperf_K562_100kb_none_dist[16,2],2), #f1
                                round(rfperf_K562_100kb_none_dist[15,2],2), #mcc
								round(rfperf_K562_100kb_none_dist[18,2],2), #youden
								(round(rfperf_K562_100kb_none_dist[6,2],2) + round(rfperf_K562_100kb_none_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_100kb_rus_oc[9,2],2), #accuracy
                                round(rfperf_K562_100kb_rus_oc[19,2],2), #auprc
                                round(rfperf_K562_100kb_rus_oc[16,2],2), #f1
                                round(rfperf_K562_100kb_rus_oc[15,2],2), #mcc
								round(rfperf_K562_100kb_rus_oc[18,2],2), #youden
								(round(rfperf_K562_100kb_rus_oc[6,2],2) + round(rfperf_K562_100kb_rus_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_100kb_rus_op[9,2],2), #accuracy
                                round(rfperf_K562_100kb_rus_op[19,2],2), #auprc
                                round(rfperf_K562_100kb_rus_op[16,2],2), #f1
                                round(rfperf_K562_100kb_rus_op[15,2],2), #mcc
								round(rfperf_K562_100kb_rus_op[18,2],2), #youden
								(round(rfperf_K562_100kb_rus_op[6,2],2) + round(rfperf_K562_100kb_rus_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_100kb_rus_dist[9,2],2), #accuracy
                                round(rfperf_K562_100kb_rus_dist[19,2],2), #auprc
                                round(rfperf_K562_100kb_rus_dist[16,2],2), #f1
                                round(rfperf_K562_100kb_rus_dist[15,2],2), #mcc
								round(rfperf_K562_100kb_rus_dist[18,2],2), #youden
								(round(rfperf_K562_100kb_rus_dist[6,2],2) + round(rfperf_K562_100kb_rus_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_100kb_ros_oc[9,2],2), #accuracy
                                round(rfperf_K562_100kb_ros_oc[19,2],2), #auprc
                                round(rfperf_K562_100kb_ros_oc[16,2],2), #f1
                                round(rfperf_K562_100kb_ros_oc[15,2],2), #mcc
								round(rfperf_K562_100kb_ros_oc[18,2],2), #youden
								(round(rfperf_K562_100kb_ros_oc[6,2],2) + round(rfperf_K562_100kb_ros_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_100kb_ros_op[9,2],2), #accuracy
                                round(rfperf_K562_100kb_ros_op[19,2],2), #auprc
                                round(rfperf_K562_100kb_ros_op[16,2],2), #f1
                                round(rfperf_K562_100kb_ros_op[15,2],2), #mcc
								round(rfperf_K562_100kb_ros_op[18,2],2), #youden
								(round(rfperf_K562_100kb_ros_op[6,2],2) + round(rfperf_K562_100kb_ros_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_100kb_ros_dist[9,2],2), #accuracy
                                round(rfperf_K562_100kb_ros_dist[19,2],2), #auprc
                                round(rfperf_K562_100kb_ros_dist[16,2],2), #f1
                                round(rfperf_K562_100kb_ros_dist[15,2],2), #mcc
								round(rfperf_K562_100kb_ros_dist[18,2],2), #youden
								(round(rfperf_K562_100kb_ros_dist[6,2],2) + round(rfperf_K562_100kb_ros_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_100kb_smote_oc[9,2],2), #accuracy
                                round(rfperf_K562_100kb_smote_oc[19,2],2), #auprc
                                round(rfperf_K562_100kb_smote_oc[16,2],2), #f1
                                round(rfperf_K562_100kb_smote_oc[15,2],2), #mcc
								round(rfperf_K562_100kb_smote_oc[18,2],2), #youden
								(round(rfperf_K562_100kb_smote_oc[6,2],2) + round(rfperf_K562_100kb_smote_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_100kb_smote_op[9,2],2), #accuracy
                                round(rfperf_K562_100kb_smote_op[19,2],2), #auprc
                                round(rfperf_K562_100kb_smote_op[16,2],2), #f1
                                round(rfperf_K562_100kb_smote_op[15,2],2), #mcc
								round(rfperf_K562_100kb_smote_op[18,2],2), #youden
								(round(rfperf_K562_100kb_smote_op[6,2],2) + round(rfperf_K562_100kb_smote_op[7,2],2))/2, #balanced accuracy

								round(rfperf_K562_100kb_smote_dist[9,2],2), #accuracy
                                round(rfperf_K562_100kb_smote_dist[19,2],2), #auprc
                                round(rfperf_K562_100kb_smote_dist[16,2],2), #f1
                                round(rfperf_K562_100kb_smote_dist[15,2],2), #mcc
								round(rfperf_K562_100kb_smote_dist[18,2],2), #youden
								(round(rfperf_K562_100kb_smote_dist[6,2],2) + round(rfperf_K562_100kb_smote_dist[7,2],2))/2 #balanced accuracy
								)
all_rfperfs_K562_100kb$Resampling <- factor(all_rfperfs_K562_100kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
all_rfperfs_K562_100kb$Predictor <- factor(all_rfperfs_K562_100kb$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_K562_100kb$Metric <- factor(all_rfperfs_K562_100kb$Metric, levels = c("Accuracy",
                                                                                      "AUPRC",
                                                                                      "F1-Score",
                                                                                      "MCC",
                                                                                      "Informedness",
                                                                                      "Balanced Acc"))

#comparing only f1 and mcc

ggplot(all_rfperfs_K562_100kb[which(all_rfperfs_K562_100kb$Metric=="F1-Score" |
                                               all_rfperfs_K562_100kb$Metric=="MCC"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

#comparing only informedness and balanced acc

ggplot(all_rfperfs_K562_100kb[which(all_rfperfs_K562_100kb$Metric=="Informedness" |
                                               all_rfperfs_K562_100kb$Metric=="Balanced Acc"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

```

### 2019-03-08 Manuscript/Figures/figure_legends.Rmd
Results review
commented out legends
added legends

@@
 For the training set, recursive feature elimination was used to reduce the feature space and minimize the influence of uninformative predictors.
-A particular resampling technique was applied to the reduced training set to create balanced classes.
+[???
+Should this be moved?] A particular resampling technique was applied to the reduced training set to create balanced classes.
 A random forest classification algorithm was then performed and validated using the testing set.
@@
 
+**Figure 4.
+Barplots comparing model performance for each predictor type.** Model performances were evaluated using F1-score and MCC for each of the 4 resampling techniques, across both the GM12878 (A) and K562 (B) cell lines.
+The results presented are for models applied to 10 kb resolution data.
+
+<!--
 **Figures 4-8.
@@
 GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red).
+-->
 
+<!--
 **Figure 9-13.

### 2019-03-08 Manuscript/Supplementary/supplementary_legends.Rmd
added legends

@@
 
+**Supplementary Figure 3.
+Heatmaps illustrating the variable reduction.** An elastic-net algorithm was used to improve computational efficiency and reduce noise for both the GM12878 (A) and K562 (B) cell lines.
+Features that were regularized and subsequently removed from downstream modeling are denoted in white, while the features that were not regularized and kept for further analyses are denoted in red.
+Each vertical region is made up of a particular data resolution (10 kb, 25 kb, 50kb, and 100 kb), resampling technique (None, RUS, ROS, and SMOTE), and predictor type (OC, OP, and Distance).
+The yellow lines separate each of the three predictor types.
+
+**Supplementary Figrue 4.
+Barplots comparing model performance for each predictor type across 25 kb, 50 kb, and 100 kb data resolutions** Model performances were evaluated using F1-scores and MCCs for each of the 4 resampling techniques, across both the GM12878 (A-C) and K562 (D-F) cell lines.
+Missing bars indicate that the model was unable to correctly predict any genomic regions that overlapped with flanked TAD boundaries in the test data, resulting in zero true positives.
+Bars that appear in the opposite direction (for MCC) indicate a negative correlation between the observed and predicted binary classifications of flanked TAD boundaries.
+
 <!--

### 2019-03-08 Scripts/evaluating_model_performances.Rmd
script for results comparing smote performances with distance predictors

@@
 
-#comparing only f1 and mcc
+#comparing only f1 and mcc and balanced acc
 
 ggplot(all_rfperfs_gm12878_10kb[which(all_rfperfs_gm12878_10kb$Metric=="F1-Score" |
-                                               all_rfperfs_gm12878_10kb$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-#comparing only informedness and balanced acc
-
-ggplot(all_rfperfs_gm12878_10kb[which(all_rfperfs_gm12878_10kb$Metric=="Informedness" |
+                                               all_rfperfs_gm12878_10kb$Metric=="MCC" |
                                         all_rfperfs_gm12878_10kb$Metric=="Balanced Acc"),],
@@
 
-#comparing only f1 and mcc
+#comparing only f1 and mcc and balanced acc
 
 ggplot(all_rfperfs_gm12878_25kb[which(all_rfperfs_gm12878_25kb$Metric=="F1-Score" |
-                                               all_rfperfs_gm12878_25kb$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-#comparing only informedness and balanced acc
-
-ggplot(all_rfperfs_gm12878_25kb[which(all_rfperfs_gm12878_25kb$Metric=="Informedness" |
+                                               all_rfperfs_gm12878_25kb$Metric=="MCC" |
                                         all_rfperfs_gm12878_25kb$Metric=="Balanced Acc"),],
@@
 
-#comparing only f1 and mcc
+#comparing only f1 and mcc and balanced acc
 
 ggplot(all_rfperfs_gm12878_50kb[which(all_rfperfs_gm12878_50kb$Metric=="F1-Score" |
-                                               all_rfperfs_gm12878_50kb$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-#comparing only informedness and balanced acc
-
-ggplot(all_rfperfs_gm12878_50kb[which(all_rfperfs_gm12878_50kb$Metric=="Informedness" |
+                                               all_rfperfs_gm12878_50kb$Metric=="MCC" |
                                         all_rfperfs_gm12878_50kb$Metric=="Balanced Acc"),],
@@
 
-#comparing only f1 and mcc
+#comparing only f1 and mcc and balanced acc
 
 ggplot(all_rfperfs_gm12878_100kb[which(all_rfperfs_gm12878_100kb$Metric=="F1-Score" |
-                                               all_rfperfs_gm12878_100kb$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-#comparing only informedness and balanced acc
-
-ggplot(all_rfperfs_gm12878_100kb[which(all_rfperfs_gm12878_100kb$Metric=="Informedness" |
+                                               all_rfperfs_gm12878_100kb$Metric=="MCC" |
                                          all_rfperfs_gm12878_100kb$Metric=="Balanced Acc"),],
@@
 
-#comparing only f1 and mcc
+#comparing only f1 and mcc and balanced acc
 
 ggplot(all_rfperfs_K562_10kb[which(all_rfperfs_K562_10kb$Metric=="F1-Score" |
-                                               all_rfperfs_K562_10kb$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-#comparing only informedness and balanced acc
-
-ggplot(all_rfperfs_K562_10kb[which(all_rfperfs_K562_10kb$Metric=="Informedness" |
+                                               all_rfperfs_K562_10kb$Metric=="MCC" |
                                      all_rfperfs_K562_10kb$Metric=="Balanced Acc"),],
@@
 
-#comparing only f1 and mcc
+#comparing only f1 and mcc and balanced acc
 
 ggplot(all_rfperfs_K562_25kb[which(all_rfperfs_K562_25kb$Metric=="F1-Score" |
-                                               all_rfperfs_K562_25kb$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-#comparing only informedness and balanced acc
-
-ggplot(all_rfperfs_K562_25kb[which(all_rfperfs_K562_25kb$Metric=="Informedness" |
+                                               all_rfperfs_K562_25kb$Metric=="MCC" |
                                      all_rfperfs_K562_25kb$Metric=="Balanced Acc"),],
@@
 
-#comparing only f1 and mcc
+#comparing only f1 and mcc and balanced acc
 
 ggplot(all_rfperfs_K562_50kb[which(all_rfperfs_K562_50kb$Metric=="F1-Score" |
-                                               all_rfperfs_K562_50kb$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-#comparing only informedness and balanced acc
-
-ggplot(all_rfperfs_K562_50kb[which(all_rfperfs_K562_50kb$Metric=="Informedness" |
+                                               all_rfperfs_K562_50kb$Metric=="MCC" |
                                      all_rfperfs_K562_50kb$Metric=="Balanced Acc"),],
@@
 
-#comparing only f1 and mcc
+#comparing only f1 and mcc and balanced acc
 
 ggplot(all_rfperfs_K562_100kb[which(all_rfperfs_K562_100kb$Metric=="F1-Score" |
-                                               all_rfperfs_K562_100kb$Metric=="MCC"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-#comparing only informedness and balanced acc
-
-ggplot(all_rfperfs_K562_100kb[which(all_rfperfs_K562_100kb$Metric=="Informedness" |
+                                               all_rfperfs_K562_100kb$Metric=="MCC" |
                                       all_rfperfs_K562_100kb$Metric=="Balanced Acc"),],
@@
 ```
+
+```{r}
+
+ggarrange(p25, p25.2, p50, p50.2, p100, p100.2, 
+          ncol=2, nrow=3, 
+          common.legend = TRUE, 
+          legend = "bottom", 
+          labels = c("A", "D", "B", "E", "C", "F"), 
+          font.label = list(size=20))
+```

### 2019-03-08 Manuscript/Figures/figure_legends.Rmd
updated legends with balanced accuracy

@@
 **Figure 4.
-Barplots comparing model performance for each predictor type.** Model performances were evaluated using F1-score and MCC for each of the 4 resampling techniques, across both the GM12878 (A) and K562 (B) cell lines.
+Barplots comparing model performance for each predictor type.** Model performances were evaluated using F1-score, MCC, and balanced accuracy for each of the 4 resampling techniques, across both the GM12878 (A) and K562 (B) cell lines.
 The results presented are for models applied to 10 kb resolution data.

### 2019-03-08 Manuscript/Supplementary/supplementary_legends.Rmd
updated legends with balanced accuracy

@@
 **Supplementary Figrue 4.
-Barplots comparing model performance for each predictor type across 25 kb, 50 kb, and 100 kb data resolutions** Model performances were evaluated using F1-scores and MCCs for each of the 4 resampling techniques, across both the GM12878 (A-C) and K562 (D-F) cell lines.
+Barplots comparing model performance for each predictor type across 25 kb, 50 kb, and 100 kb data resolutions** Model performances were evaluated using F1-scores, MCCs, and balanced accuracies for each of the 4 resampling techniques, across both the GM12878 (A-C) and K562 (D-F) cell lines.
 Missing bars indicate that the model was unable to correctly predict any genomic regions that overlapped with flanked TAD boundaries in the test data, resulting in zero true positives.

### 2019-03-08 Manuscript/manuscript.Rmd
manuscript updates

@@
 Likewise, threshold-specific metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
+Better measures to consider are composite metrics involving both precision and recall together because they soften the influence of a model's ability to correctly classify majority classes and yield more dependable and interpretable results.
+Therefore, measures like the F1-Score, Matthew's Correlation Coefficient (MCC), and balanced accuracy offer better interpretation, especially in the instance of imbalanced classes [@jeni2013facing].
+The F1-Score can be interpreted as a weighted average of the precision and recall values, balanced accuracy measures the average accuracy obtained on either class, and MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
+Each metric uses all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
+
+<!--
 Certain composite threshold-specific metrics such as balanced accuracy and Youden's Index should be preferred because they soften the influence of a model's ability to correctly classify majority classes and yield more dependable and interpretable results [@jeni2013facing].
@@
 Informedness, also referred to as Youden's Index, measures the probability of the model making an informed decision and corresponds to giving equal weight per class, rather than to each instance like Accuracy [@youden1950index;@powers2011evaluation].
+-->
 
@@
 Noninformative features were removed using a feature reduction algorithm and random forest classifications were performed to assess model performance, and investigate which genomic annotations were most associated with the TAD boundaries for a given system from the complete ensemble.
-Model performance was evaluated using area under the precision-recall curve (AUPRC), F1-Score, Youden's index (YI), and Matthew's correlation coefficient (MCC).
+Model performance was evaluated using the F1-Score, MCC, and balanced accuracy.
 
@@
 
-The efficacy of each re-sampling technique was compared using the F1-score, balanced accuracy, informedness, and  MCC. These metrics are defined as follows:
+The efficacy of each re-sampling technique was compared using the F1-score, MCC, and balanced accuracy. These metrics are defined as follows:
 
@@
 
+$$MCC = \frac{TP \times TN - FP \times FN}{\sqrt{ (TP + FP)(TP+FN)(TN+FP)(TN+FN) }}$$
+
 $$Balanced \quad Accuracy = \dfrac{1}{2}\left( \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} \right)$$
 
+<!--
 $$Informedness = \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} - 1$$
-
-$$MCC = \frac{TP \times TN - FP \times FN}{\sqrt{ (TP + FP)(TP+FN)(TN+FP)(TN+FN) }}$$
+-->
 

### 2019-03-08 Scripts/evaluating_smote_performances.Rmd
script for comparing models with distance type predictors

---
title: "Comparing top performing models"
author: "Spiro Stilianoudakis"
date: "March 8, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

# Comparing models with distance type predictors

## SMOTE

### GM12878

```{r}

###10kb
rfperf_gm12878_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

###25kb
rfperf_gm12878_25kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

###50kb
rfperf_gm12878_50kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

###100kb
rfperf_gm12878_100kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

```

### K562

```{r}

###10kb
rfperf_k562_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

###25kb
rfperf_k562_25kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

###50kb
rfperf_k562_50kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

###100kb
rfperf_k562_100kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

```

### Combined F1 and MCC and balanced acc

```{r}
all_smote_perfs <- data.frame(Performance = c(rfperf_gm12878_10kb_smote_dist[16,2],
                                              rfperf_gm12878_10kb_smote_dist[15,2],
                                              (rfperf_gm12878_10kb_smote_dist[6,2] + rfperf_gm12878_10kb_smote_dist[7,2])/2,
                                              rfperf_gm12878_25kb_smote_dist[16,2],
                                              rfperf_gm12878_25kb_smote_dist[15,2],
                                              (rfperf_gm12878_25kb_smote_dist[6,2] + rfperf_gm12878_25kb_smote_dist[7,2])/2,
                                              rfperf_gm12878_50kb_smote_dist[16,2],
                                              rfperf_gm12878_50kb_smote_dist[15,2],
                                              (rfperf_gm12878_50kb_smote_dist[6,2] + rfperf_gm12878_50kb_smote_dist[7,2])/2,
                                              rfperf_gm12878_100kb_smote_dist[16,2],
                                              rfperf_gm12878_100kb_smote_dist[15,2],
                                              (rfperf_gm12878_100kb_smote_dist[6,2] + rfperf_gm12878_100kb_smote_dist[7,2])/2,
                                              rfperf_k562_10kb_smote_dist[16,2],
                                              rfperf_k562_10kb_smote_dist[15,2],
                                              (rfperf_k562_10kb_smote_dist[6,2] + rfperf_k562_10kb_smote_dist[7,2])/2,
                                              rfperf_k562_25kb_smote_dist[16,2],
                                              rfperf_k562_25kb_smote_dist[15,2],
                                              (rfperf_k562_25kb_smote_dist[6,2] + rfperf_k562_25kb_smote_dist[7,2])/2,
                                              rfperf_k562_50kb_smote_dist[16,2],
                                              rfperf_k562_50kb_smote_dist[15,2],
                                              (rfperf_k562_50kb_smote_dist[6,2] + rfperf_k562_50kb_smote_dist[7,2])/2,
                                              rfperf_k562_100kb_smote_dist[16,2],
                                              rfperf_k562_100kb_smote_dist[15,2],
                                              (rfperf_k562_100kb_smote_dist[6,2] + rfperf_k562_100kb_smote_dist[7,2])/2),
                              CL = c(rep("GM12878", 12),
                                     rep("K562", 12)),
                              Resolution = rep(c(rep("10 kb", 3),
                                             rep("25 kb", 3),
                                             rep("50 kb", 3),
                                             rep("100 kb", 3)), 2),
                              Metric = rep(c("F1-Score", "MCC", "Balanced Acc"), 8))

all_smote_perfs$CL <- factor(all_smote_perfs$CL, levels=c("GM12878", "K562"))
all_smote_perfs$Resolution <- factor(all_smote_perfs$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
all_smote_perfs$Metric <- factor(all_smote_perfs$Metric, levels=c("F1-Score", "MCC", "Balanced Acc"))

ggplot(all_smote_perfs, aes(x=Resolution, y=Performance, group=CL, color=CL)) +
  geom_line(aes(linetype=CL))+
  geom_point(aes(shape=CL))+
  facet_grid(~ Metric)+
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Cell Line")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15
	                                 #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
	                                 ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))
```

## None

### GM12878

```{r}

###10kb
rfperf_gm12878_10kb_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

###25kb
rfperf_gm12878_25kb_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

###50kb
rfperf_gm12878_50kb_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

###100kb
rfperf_gm12878_100kb_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

```

### K562

```{r}

###10kb
rfperf_k562_10kb_None_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

###25kb
rfperf_k562_25kb_None_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

###50kb
rfperf_k562_50kb_None_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

###100kb
rfperf_k562_100kb_None_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

```

### Combined F1 and MCC and balanced acc

```{r}
all_None_perfs <- data.frame(Performance = c(rfperf_gm12878_10kb_None_dist[16,2],
                                              rfperf_gm12878_10kb_None_dist[15,2],
                                              (rfperf_gm12878_10kb_None_dist[6,2] + rfperf_gm12878_10kb_None_dist[7,2])/2,
                                              rfperf_gm12878_25kb_None_dist[16,2],
                                              rfperf_gm12878_25kb_None_dist[15,2],
                                              (rfperf_gm12878_25kb_None_dist[6,2] + rfperf_gm12878_25kb_None_dist[7,2])/2,
                                              rfperf_gm12878_50kb_None_dist[16,2],
                                              rfperf_gm12878_50kb_None_dist[15,2],
                                              (rfperf_gm12878_50kb_None_dist[6,2] + rfperf_gm12878_50kb_None_dist[7,2])/2,
                                              rfperf_gm12878_100kb_None_dist[16,2],
                                              rfperf_gm12878_100kb_None_dist[15,2],
                                              (rfperf_gm12878_100kb_None_dist[6,2] + rfperf_gm12878_100kb_None_dist[7,2])/2,
                                              rfperf_k562_10kb_None_dist[16,2],
                                              rfperf_k562_10kb_None_dist[15,2],
                                              (rfperf_k562_10kb_None_dist[6,2] + rfperf_k562_10kb_None_dist[7,2])/2,
                                              rfperf_k562_25kb_None_dist[16,2],
                                              rfperf_k562_25kb_None_dist[15,2],
                                              (rfperf_k562_25kb_None_dist[6,2] + rfperf_k562_25kb_None_dist[7,2])/2,
                                              rfperf_k562_50kb_None_dist[16,2],
                                              rfperf_k562_50kb_None_dist[15,2],
                                              (rfperf_k562_50kb_None_dist[6,2] + rfperf_k562_50kb_None_dist[7,2])/2,
                                              rfperf_k562_100kb_None_dist[16,2],
                                              rfperf_k562_100kb_None_dist[15,2],
                                              (rfperf_k562_100kb_None_dist[6,2] + rfperf_k562_100kb_None_dist[7,2])/2),
                              CL = c(rep("GM12878", 12),
                                     rep("K562", 12)),
                              Resolution = rep(c(rep("10 kb", 3),
                                             rep("25 kb", 3),
                                             rep("50 kb", 3),
                                             rep("100 kb", 3)), 2),
                              Metric = rep(c("F1-Score", "MCC", "Balanced Acc"), 8))

all_None_perfs$CL <- factor(all_None_perfs$CL, levels=c("GM12878", "K562"))
all_None_perfs$Resolution <- factor(all_None_perfs$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
all_None_perfs$Metric <- factor(all_None_perfs$Metric, levels=c("F1-Score", "MCC", "Balanced Acc"))

ggplot(all_None_perfs, aes(x=Resolution, y=Performance, group=CL, color=CL)) +
  geom_line(aes(linetype=CL))+
  geom_point(aes(shape=CL))+
  facet_grid(~ Metric)+
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Cell Line")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15
	                                 #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
	                                 ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))
```

##ROS

### GM12878

```{r}

###10kb
rfperf_gm12878_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

###25kb
rfperf_gm12878_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

###50kb
rfperf_gm12878_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

###100kb
rfperf_gm12878_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

```

### K562

```{r}

###10kb
rfperf_k562_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

###25kb
rfperf_k562_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

###50kb
rfperf_k562_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

###100kb
rfperf_k562_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

```

### Combined F1 and MCC and balanced acc

```{r}
all_ROS_perfs <- data.frame(Performance = c(rfperf_gm12878_10kb_ROS_dist[16,2],
                                              rfperf_gm12878_10kb_ROS_dist[15,2],
                                              (rfperf_gm12878_10kb_ROS_dist[6,2] + rfperf_gm12878_10kb_ROS_dist[7,2])/2,
                                              rfperf_gm12878_25kb_ROS_dist[16,2],
                                              rfperf_gm12878_25kb_ROS_dist[15,2],
                                              (rfperf_gm12878_25kb_ROS_dist[6,2] + rfperf_gm12878_25kb_ROS_dist[7,2])/2,
                                              rfperf_gm12878_50kb_ROS_dist[16,2],
                                              rfperf_gm12878_50kb_ROS_dist[15,2],
                                              (rfperf_gm12878_50kb_ROS_dist[6,2] + rfperf_gm12878_50kb_ROS_dist[7,2])/2,
                                              rfperf_gm12878_100kb_ROS_dist[16,2],
                                              rfperf_gm12878_100kb_ROS_dist[15,2],
                                              (rfperf_gm12878_100kb_ROS_dist[6,2] + rfperf_gm12878_100kb_ROS_dist[7,2])/2,
                                              rfperf_k562_10kb_ROS_dist[16,2],
                                              rfperf_k562_10kb_ROS_dist[15,2],
                                              (rfperf_k562_10kb_ROS_dist[6,2] + rfperf_k562_10kb_ROS_dist[7,2])/2,
                                              rfperf_k562_25kb_ROS_dist[16,2],
                                              rfperf_k562_25kb_ROS_dist[15,2],
                                              (rfperf_k562_25kb_ROS_dist[6,2] + rfperf_k562_25kb_ROS_dist[7,2])/2,
                                              rfperf_k562_50kb_ROS_dist[16,2],
                                              rfperf_k562_50kb_ROS_dist[15,2],
                                              (rfperf_k562_50kb_ROS_dist[6,2] + rfperf_k562_50kb_ROS_dist[7,2])/2,
                                              rfperf_k562_100kb_ROS_dist[16,2],
                                              rfperf_k562_100kb_ROS_dist[15,2],
                                              (rfperf_k562_100kb_ROS_dist[6,2] + rfperf_k562_100kb_ROS_dist[7,2])/2),
                              CL = c(rep("GM12878", 12),
                                     rep("K562", 12)),
                              Resolution = rep(c(rep("10 kb", 3),
                                             rep("25 kb", 3),
                                             rep("50 kb", 3),
                                             rep("100 kb", 3)), 2),
                              Metric = rep(c("F1-Score", "MCC", "Balanced Acc"), 8))

all_ROS_perfs$CL <- factor(all_ROS_perfs$CL, levels=c("GM12878", "K562"))
all_ROS_perfs$Resolution <- factor(all_ROS_perfs$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
all_ROS_perfs$Metric <- factor(all_ROS_perfs$Metric, levels=c("F1-Score", "MCC", "Balanced Acc"))

ggplot(all_ROS_perfs, aes(x=Resolution, y=Performance, group=CL, color=CL)) +
  geom_line(aes(linetype=CL))+
  geom_point(aes(shape=CL))+
  facet_grid(~ Metric)+
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Cell Line")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15
	                                 #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
	                                 ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))
```

##RUS

### GM12878

```{r}

###10kb
rfperf_gm12878_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

###25kb
rfperf_gm12878_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

###50kb
rfperf_gm12878_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

###100kb
rfperf_gm12878_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

```

### K562

```{r}

###10kb
rfperf_k562_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

###25kb
rfperf_k562_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

###50kb
rfperf_k562_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

###100kb
rfperf_k562_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

```

### Combined F1 and MCC and balanced acc

```{r}
all_RUS_perfs <- data.frame(Performance = c(rfperf_gm12878_10kb_RUS_dist[16,2],
                                              rfperf_gm12878_10kb_RUS_dist[15,2],
                                              (rfperf_gm12878_10kb_RUS_dist[6,2] + rfperf_gm12878_10kb_RUS_dist[7,2])/2,
                                              rfperf_gm12878_25kb_RUS_dist[16,2],
                                              rfperf_gm12878_25kb_RUS_dist[15,2],
                                              (rfperf_gm12878_25kb_RUS_dist[6,2] + rfperf_gm12878_25kb_RUS_dist[7,2])/2,
                                              rfperf_gm12878_50kb_RUS_dist[16,2],
                                              rfperf_gm12878_50kb_RUS_dist[15,2],
                                              (rfperf_gm12878_50kb_RUS_dist[6,2] + rfperf_gm12878_50kb_RUS_dist[7,2])/2,
                                              rfperf_gm12878_100kb_RUS_dist[16,2],
                                              rfperf_gm12878_100kb_RUS_dist[15,2],
                                              (rfperf_gm12878_100kb_RUS_dist[6,2] + rfperf_gm12878_100kb_RUS_dist[7,2])/2,
                                              rfperf_k562_10kb_RUS_dist[16,2],
                                              rfperf_k562_10kb_RUS_dist[15,2],
                                              (rfperf_k562_10kb_RUS_dist[6,2] + rfperf_k562_10kb_RUS_dist[7,2])/2,
                                              rfperf_k562_25kb_RUS_dist[16,2],
                                              rfperf_k562_25kb_RUS_dist[15,2],
                                              (rfperf_k562_25kb_RUS_dist[6,2] + rfperf_k562_25kb_RUS_dist[7,2])/2,
                                              rfperf_k562_50kb_RUS_dist[16,2],
                                              rfperf_k562_50kb_RUS_dist[15,2],
                                              (rfperf_k562_50kb_RUS_dist[6,2] + rfperf_k562_50kb_RUS_dist[7,2])/2,
                                              rfperf_k562_100kb_RUS_dist[16,2],
                                              rfperf_k562_100kb_RUS_dist[15,2],
                                              (rfperf_k562_100kb_RUS_dist[6,2] + rfperf_k562_100kb_RUS_dist[7,2])/2),
                              CL = c(rep("GM12878", 12),
                                     rep("K562", 12)),
                              Resolution = rep(c(rep("10 kb", 3),
                                             rep("25 kb", 3),
                                             rep("50 kb", 3),
                                             rep("100 kb", 3)), 2),
                              Metric = rep(c("F1-Score", "MCC", "Balanced Acc"), 8))

all_RUS_perfs$CL <- factor(all_RUS_perfs$CL, levels=c("GM12878", "K562"))
all_RUS_perfs$Resolution <- factor(all_RUS_perfs$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
all_RUS_perfs$Metric <- factor(all_RUS_perfs$Metric, levels=c("F1-Score", "MCC", "Balanced Acc"))

ggplot(all_RUS_perfs, aes(x=Resolution, y=Performance, group=CL, color=CL)) +
  geom_line(aes(linetype=CL))+
  geom_point(aes(shape=CL))+
  facet_grid(~ Metric)+
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Cell Line")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15
	                                 #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
	                                 ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))
```

```{r}
ggarrange(p.none, p.ros, p.rus, 
          ncol=1, nrow=3, 
          common.legend = TRUE, 
          legend="bottom",
          labels="AUTO",
          font.label = list(size=20))
```

### 2019-03-08 Manuscript/Figures/figure_legends.Rmd
added legends

@@
 
+**Figure 5.
+Line plots comparing models using SMOTE resampling with distance-type predictors.** Model performances were evaluated using F1-score, MCC, and balanced accuracy for each of the 4 data resolutions, across both the GM12878 (red, solid line) and K562 (blue; dashed line) cell lines.
+For a given metric, each point represents a model applied to a particular resolution with distance type predictors for the feature space, after which the SMOTE algorithm was used to create balanced classes on the trianing set.
+
 <!--

### 2019-03-08 Manuscript/Supplementary/supplementary_legends.Rmd
added legends

@@
 
+**Figure 5.
+Line plots comparing models using the remaining resampling techniques with distance-type predictors.** Model performances were evaluated using F1-score, MCC, and balanced accuracy for each of the 4 data resolutions, across both the GM12878 (red, solid line) and K562 (blue; dashed line) cell lines.
+For a given metric, each point represents a model applied to a particular resolution with distance type predictors for the feature space, after which a particular resampling technique was used to create balanced classes on the trianing set, including none (A), random over-sampling (B), and random under-sampling (C).
+
 <!--

### 2019-03-10 Scripts/evaluating_variable_importances.Rmd
script for extracting variable importances

---
title: "Evaluating Variable Importances"
author: "Spiro Stilianoudakis"
date: "March 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

#Variable Importance Bar Plots for models with distance type predictors

##10kb

###None

```{r}
#GM12878
rfimpvars_gm12878_10kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_10kb_none <- rfimpvars_gm12878_10kb_none[1:10,]
#rfimpvars_gm12878_10kb_none <- rfimpvars_gm12878_10kb_none[10:1,]
rfimpvars_gm12878_10kb_none <- rfimpvars_gm12878_10kb_none[1:20,]
rfimpvars_gm12878_10kb_none <- rfimpvars_gm12878_10kb_none[20:1,]

rfimpvars_gm12878_10kb_none$Feature <- gsub("_dist","", rfimpvars_gm12878_10kb_none$Feature)

rfimpvars_gm12878_10kb_none$Feature <- factor(rfimpvars_gm12878_10kb_none$Feature, levels=rfimpvars_gm12878_10kb_none$Feature)

vip.gm12878.10kb.none <- ggplot(rfimpvars_gm12878_10kb_none, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_10kb_none <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_10kb_none <- rfimpvars_K562_10kb_none[1:10,]
#rfimpvars_K562_10kb_none <- rfimpvars_K562_10kb_none[10:1,]
rfimpvars_K562_10kb_none <- rfimpvars_K562_10kb_none[1:20,]
rfimpvars_K562_10kb_none <- rfimpvars_K562_10kb_none[20:1,]

rfimpvars_K562_10kb_none$Feature <- gsub("_dist","", rfimpvars_K562_10kb_none$Feature)

rfimpvars_K562_10kb_none$Feature <- factor(rfimpvars_K562_10kb_none$Feature, levels=rfimpvars_K562_10kb_none$Feature)

vip.K562.10kb.none <- ggplot(rfimpvars_K562_10kb_none, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

```

###ROS

```{r}
rfimpvars_gm12878_10kb_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_10kb_ROS <- rfimpvars_gm12878_10kb_ROS[1:10,]
#rfimpvars_gm12878_10kb_ROS <- rfimpvars_gm12878_10kb_ROS[10:1,]
rfimpvars_gm12878_10kb_ROS <- rfimpvars_gm12878_10kb_ROS[1:20,]
rfimpvars_gm12878_10kb_ROS <- rfimpvars_gm12878_10kb_ROS[20:1,]

rfimpvars_gm12878_10kb_ROS$Feature <- gsub("_dist","", rfimpvars_gm12878_10kb_ROS$Feature)

rfimpvars_gm12878_10kb_ROS$Feature <- factor(rfimpvars_gm12878_10kb_ROS$Feature, levels=rfimpvars_gm12878_10kb_ROS$Feature)

vip.gm12878.10kb.ROS <- ggplot(rfimpvars_gm12878_10kb_ROS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_10kb_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_10kb_ROS <- rfimpvars_K562_10kb_ROS[1:10,]
#rfimpvars_K562_10kb_ROS <- rfimpvars_K562_10kb_ROS[10:1,]
rfimpvars_K562_10kb_ROS <- rfimpvars_K562_10kb_ROS[1:20,]
rfimpvars_K562_10kb_ROS <- rfimpvars_K562_10kb_ROS[20:1,]

rfimpvars_K562_10kb_ROS$Feature <- gsub("_dist","", rfimpvars_K562_10kb_ROS$Feature)

rfimpvars_K562_10kb_ROS$Feature <- factor(rfimpvars_K562_10kb_ROS$Feature, levels=rfimpvars_K562_10kb_ROS$Feature)

vip.K562.10kb.ROS <- ggplot(rfimpvars_K562_10kb_ROS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

###RUS

```{r}
rfimpvars_gm12878_10kb_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_10kb_RUS <- rfimpvars_gm12878_10kb_RUS[1:10,]
#rfimpvars_gm12878_10kb_RUS <- rfimpvars_gm12878_10kb_RUS[10:1,]
rfimpvars_gm12878_10kb_RUS <- rfimpvars_gm12878_10kb_RUS[1:20,]
rfimpvars_gm12878_10kb_RUS <- rfimpvars_gm12878_10kb_RUS[20:1,]

rfimpvars_gm12878_10kb_RUS$Feature <- gsub("_dist","", rfimpvars_gm12878_10kb_RUS$Feature)

rfimpvars_gm12878_10kb_RUS$Feature <- factor(rfimpvars_gm12878_10kb_RUS$Feature, levels=rfimpvars_gm12878_10kb_RUS$Feature)

vip.gm12878.10kb.RUS <- ggplot(rfimpvars_gm12878_10kb_RUS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_10kb_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_10kb_RUS <- rfimpvars_K562_10kb_RUS[1:10,]
#rfimpvars_K562_10kb_RUS <- rfimpvars_K562_10kb_RUS[10:1,]
rfimpvars_K562_10kb_RUS <- rfimpvars_K562_10kb_RUS[1:20,]
rfimpvars_K562_10kb_RUS <- rfimpvars_K562_10kb_RUS[20:1,]

rfimpvars_K562_10kb_RUS$Feature <- gsub("_dist","", rfimpvars_K562_10kb_RUS$Feature)

rfimpvars_K562_10kb_RUS$Feature <- factor(rfimpvars_K562_10kb_RUS$Feature, levels=rfimpvars_K562_10kb_RUS$Feature)

vip.K562.10kb.RUS <- ggplot(rfimpvars_K562_10kb_RUS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

###SMOTE

```{r}
rfimpvars_gm12878_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_10kb_SMOTE <- rfimpvars_gm12878_10kb_SMOTE[1:10,]
#rfimpvars_gm12878_10kb_SMOTE <- rfimpvars_gm12878_10kb_SMOTE[10:1,]
rfimpvars_gm12878_10kb_SMOTE <- rfimpvars_gm12878_10kb_SMOTE[1:20,]
rfimpvars_gm12878_10kb_SMOTE <- rfimpvars_gm12878_10kb_SMOTE[20:1,]

rfimpvars_gm12878_10kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_gm12878_10kb_SMOTE$Feature)

rfimpvars_gm12878_10kb_SMOTE$Feature <- factor(rfimpvars_gm12878_10kb_SMOTE$Feature, levels=rfimpvars_gm12878_10kb_SMOTE$Feature)

vip.gm12878.10kb.SMOTE <- ggplot(rfimpvars_gm12878_10kb_SMOTE, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_10kb_SMOTE <- rfimpvars_K562_10kb_SMOTE[1:10,]
#rfimpvars_K562_10kb_SMOTE <- rfimpvars_K562_10kb_SMOTE[10:1,]
rfimpvars_K562_10kb_SMOTE <- rfimpvars_K562_10kb_SMOTE[1:20,]
rfimpvars_K562_10kb_SMOTE <- rfimpvars_K562_10kb_SMOTE[20:1,]

rfimpvars_K562_10kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_K562_10kb_SMOTE$Feature)

rfimpvars_K562_10kb_SMOTE$Feature <- factor(rfimpvars_K562_10kb_SMOTE$Feature, levels=rfimpvars_K562_10kb_SMOTE$Feature)

vip.K562.10kb.SMOTE <- ggplot(rfimpvars_K562_10kb_SMOTE, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

##25kb

###None

```{r}
#GM12878
rfimpvars_gm12878_25kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_25kb_none <- rfimpvars_gm12878_25kb_none[1:10,]
#rfimpvars_gm12878_25kb_none <- rfimpvars_gm12878_25kb_none[10:1,]
rfimpvars_gm12878_25kb_none <- rfimpvars_gm12878_25kb_none[1:20,]
rfimpvars_gm12878_25kb_none <- rfimpvars_gm12878_25kb_none[20:1,]

rfimpvars_gm12878_25kb_none$Feature <- gsub("_dist","", rfimpvars_gm12878_25kb_none$Feature)

rfimpvars_gm12878_25kb_none$Feature <- factor(rfimpvars_gm12878_25kb_none$Feature, levels=rfimpvars_gm12878_25kb_none$Feature)

vip.gm12878.25kb.none <- ggplot(rfimpvars_gm12878_25kb_none, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_25kb_none <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_25kb_none <- rfimpvars_K562_25kb_none[1:10,]
#rfimpvars_K562_25kb_none <- rfimpvars_K562_25kb_none[10:1,]
rfimpvars_K562_25kb_none <- rfimpvars_K562_25kb_none[1:20,]
rfimpvars_K562_25kb_none <- rfimpvars_K562_25kb_none[20:1,]

rfimpvars_K562_25kb_none$Feature <- gsub("_dist","", rfimpvars_K562_25kb_none$Feature)

rfimpvars_K562_25kb_none$Feature <- factor(rfimpvars_K562_25kb_none$Feature, levels=rfimpvars_K562_25kb_none$Feature)

vip.K562.25kb.none <- ggplot(rfimpvars_K562_25kb_none, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

```

###ROS

```{r}
rfimpvars_gm12878_25kb_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_25kb_ROS <- rfimpvars_gm12878_25kb_ROS[1:10,]
#rfimpvars_gm12878_25kb_ROS <- rfimpvars_gm12878_25kb_ROS[10:1,]
rfimpvars_gm12878_25kb_ROS <- rfimpvars_gm12878_25kb_ROS[1:20,]
rfimpvars_gm12878_25kb_ROS <- rfimpvars_gm12878_25kb_ROS[20:1,]

rfimpvars_gm12878_25kb_ROS$Feature <- gsub("_dist","", rfimpvars_gm12878_25kb_ROS$Feature)

rfimpvars_gm12878_25kb_ROS$Feature <- factor(rfimpvars_gm12878_25kb_ROS$Feature, levels=rfimpvars_gm12878_25kb_ROS$Feature)

vip.gm12878.25kb.ROS <- ggplot(rfimpvars_gm12878_25kb_ROS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_25kb_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_25kb_ROS <- rfimpvars_K562_25kb_ROS[1:10,]
#rfimpvars_K562_25kb_ROS <- rfimpvars_K562_25kb_ROS[10:1,]
rfimpvars_K562_25kb_ROS <- rfimpvars_K562_25kb_ROS[1:20,]
rfimpvars_K562_25kb_ROS <- rfimpvars_K562_25kb_ROS[20:1,]

rfimpvars_K562_25kb_ROS$Feature <- gsub("_dist","", rfimpvars_K562_25kb_ROS$Feature)

rfimpvars_K562_25kb_ROS$Feature <- factor(rfimpvars_K562_25kb_ROS$Feature, levels=rfimpvars_K562_25kb_ROS$Feature)

vip.K562.25kb.ROS <- ggplot(rfimpvars_K562_25kb_ROS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

###RUS

```{r}
rfimpvars_gm12878_25kb_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_25kb_RUS <- rfimpvars_gm12878_25kb_RUS[1:10,]
#rfimpvars_gm12878_25kb_RUS <- rfimpvars_gm12878_25kb_RUS[10:1,]
rfimpvars_gm12878_25kb_RUS <- rfimpvars_gm12878_25kb_RUS[1:20,]
rfimpvars_gm12878_25kb_RUS <- rfimpvars_gm12878_25kb_RUS[20:1,]

rfimpvars_gm12878_25kb_RUS$Feature <- gsub("_dist","", rfimpvars_gm12878_25kb_RUS$Feature)

rfimpvars_gm12878_25kb_RUS$Feature <- factor(rfimpvars_gm12878_25kb_RUS$Feature, levels=rfimpvars_gm12878_25kb_RUS$Feature)

vip.gm12878.25kb.RUS <- ggplot(rfimpvars_gm12878_25kb_RUS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_25kb_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_25kb_RUS <- rfimpvars_K562_25kb_RUS[1:10,]
#rfimpvars_K562_25kb_RUS <- rfimpvars_K562_25kb_RUS[10:1,]
rfimpvars_K562_25kb_RUS <- rfimpvars_K562_25kb_RUS[1:20,]
rfimpvars_K562_25kb_RUS <- rfimpvars_K562_25kb_RUS[20:1,]

rfimpvars_K562_25kb_RUS$Feature <- gsub("_dist","", rfimpvars_K562_25kb_RUS$Feature)

rfimpvars_K562_25kb_RUS$Feature <- factor(rfimpvars_K562_25kb_RUS$Feature, levels=rfimpvars_K562_25kb_RUS$Feature)

vip.K562.25kb.RUS <- ggplot(rfimpvars_K562_25kb_RUS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

###SMOTE

```{r}
rfimpvars_gm12878_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_25kb_SMOTE <- rfimpvars_gm12878_25kb_SMOTE[1:10,]
#rfimpvars_gm12878_25kb_SMOTE <- rfimpvars_gm12878_25kb_SMOTE[10:1,]
rfimpvars_gm12878_25kb_SMOTE <- rfimpvars_gm12878_25kb_SMOTE[1:20,]
rfimpvars_gm12878_25kb_SMOTE <- rfimpvars_gm12878_25kb_SMOTE[20:1,]

rfimpvars_gm12878_25kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_gm12878_25kb_SMOTE$Feature)

rfimpvars_gm12878_25kb_SMOTE$Feature <- factor(rfimpvars_gm12878_25kb_SMOTE$Feature, levels=rfimpvars_gm12878_25kb_SMOTE$Feature)

vip.gm12878.25kb.SMOTE <- ggplot(rfimpvars_gm12878_25kb_SMOTE, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_25kb_SMOTE <- rfimpvars_K562_25kb_SMOTE[1:10,]
#rfimpvars_K562_25kb_SMOTE <- rfimpvars_K562_25kb_SMOTE[10:1,]
rfimpvars_K562_25kb_SMOTE <- rfimpvars_K562_25kb_SMOTE[1:20,]
rfimpvars_K562_25kb_SMOTE <- rfimpvars_K562_25kb_SMOTE[20:1,]

rfimpvars_K562_25kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_K562_25kb_SMOTE$Feature)

rfimpvars_K562_25kb_SMOTE$Feature <- factor(rfimpvars_K562_25kb_SMOTE$Feature, levels=rfimpvars_K562_25kb_SMOTE$Feature)

vip.K562.25kb.SMOTE <- ggplot(rfimpvars_K562_25kb_SMOTE, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

##50kb

###None

```{r}
#GM12878
rfimpvars_gm12878_50kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_50kb_none <- rfimpvars_gm12878_50kb_none[1:10,]
#rfimpvars_gm12878_50kb_none <- rfimpvars_gm12878_50kb_none[10:1,]
rfimpvars_gm12878_50kb_none <- rfimpvars_gm12878_50kb_none[1:20,]
rfimpvars_gm12878_50kb_none <- rfimpvars_gm12878_50kb_none[20:1,]

rfimpvars_gm12878_50kb_none$Feature <- gsub("_dist","", rfimpvars_gm12878_50kb_none$Feature)

rfimpvars_gm12878_50kb_none$Feature <- factor(rfimpvars_gm12878_50kb_none$Feature, levels=rfimpvars_gm12878_50kb_none$Feature)

vip.gm12878.50kb.none <- ggplot(rfimpvars_gm12878_50kb_none, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_50kb_none <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_50kb_none <- rfimpvars_K562_50kb_none[1:10,]
#rfimpvars_K562_50kb_none <- rfimpvars_K562_50kb_none[10:1,]
rfimpvars_K562_50kb_none <- rfimpvars_K562_50kb_none[1:20,]
rfimpvars_K562_50kb_none <- rfimpvars_K562_50kb_none[20:1,]

rfimpvars_K562_50kb_none$Feature <- gsub("_dist","", rfimpvars_K562_50kb_none$Feature)

rfimpvars_K562_50kb_none$Feature <- factor(rfimpvars_K562_50kb_none$Feature, levels=rfimpvars_K562_50kb_none$Feature)

vip.K562.50kb.none <- ggplot(rfimpvars_K562_50kb_none, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

```

###ROS

```{r}
rfimpvars_gm12878_50kb_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_50kb_ROS <- rfimpvars_gm12878_50kb_ROS[1:10,]
#rfimpvars_gm12878_50kb_ROS <- rfimpvars_gm12878_50kb_ROS[10:1,]
rfimpvars_gm12878_50kb_ROS <- rfimpvars_gm12878_50kb_ROS[1:20,]
rfimpvars_gm12878_50kb_ROS <- rfimpvars_gm12878_50kb_ROS[20:1,]

rfimpvars_gm12878_50kb_ROS$Feature <- gsub("_dist","", rfimpvars_gm12878_50kb_ROS$Feature)

rfimpvars_gm12878_50kb_ROS$Feature <- factor(rfimpvars_gm12878_50kb_ROS$Feature, levels=rfimpvars_gm12878_50kb_ROS$Feature)

vip.gm12878.50kb.ROS <- ggplot(rfimpvars_gm12878_50kb_ROS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_50kb_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_50kb_ROS <- rfimpvars_K562_50kb_ROS[1:10,]
#rfimpvars_K562_50kb_ROS <- rfimpvars_K562_50kb_ROS[10:1,]
rfimpvars_K562_50kb_ROS <- rfimpvars_K562_50kb_ROS[1:20,]
rfimpvars_K562_50kb_ROS <- rfimpvars_K562_50kb_ROS[20:1,]

rfimpvars_K562_50kb_ROS$Feature <- gsub("_dist","", rfimpvars_K562_50kb_ROS$Feature)

rfimpvars_K562_50kb_ROS$Feature <- factor(rfimpvars_K562_50kb_ROS$Feature, levels=rfimpvars_K562_50kb_ROS$Feature)

vip.K562.50kb.ROS <- ggplot(rfimpvars_K562_50kb_ROS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

###RUS

```{r}
rfimpvars_gm12878_50kb_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_50kb_RUS <- rfimpvars_gm12878_50kb_RUS[1:10,]
#rfimpvars_gm12878_50kb_RUS <- rfimpvars_gm12878_50kb_RUS[10:1,]
rfimpvars_gm12878_50kb_RUS <- rfimpvars_gm12878_50kb_RUS[1:20,]
rfimpvars_gm12878_50kb_RUS <- rfimpvars_gm12878_50kb_RUS[20:1,]

rfimpvars_gm12878_50kb_RUS$Feature <- gsub("_dist","", rfimpvars_gm12878_50kb_RUS$Feature)

rfimpvars_gm12878_50kb_RUS$Feature <- factor(rfimpvars_gm12878_50kb_RUS$Feature, levels=rfimpvars_gm12878_50kb_RUS$Feature)

vip.gm12878.50kb.RUS <- ggplot(rfimpvars_gm12878_50kb_RUS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_50kb_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_50kb_RUS <- rfimpvars_K562_50kb_RUS[1:10,]
#rfimpvars_K562_50kb_RUS <- rfimpvars_K562_50kb_RUS[10:1,]
rfimpvars_K562_50kb_RUS <- rfimpvars_K562_50kb_RUS[1:20,]
rfimpvars_K562_50kb_RUS <- rfimpvars_K562_50kb_RUS[20:1,]

rfimpvars_K562_50kb_RUS$Feature <- gsub("_dist","", rfimpvars_K562_50kb_RUS$Feature)

rfimpvars_K562_50kb_RUS$Feature <- factor(rfimpvars_K562_50kb_RUS$Feature, levels=rfimpvars_K562_50kb_RUS$Feature)

vip.K562.50kb.RUS <- ggplot(rfimpvars_K562_50kb_RUS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

###SMOTE

```{r}
rfimpvars_gm12878_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_50kb_SMOTE <- rfimpvars_gm12878_50kb_SMOTE[1:10,]
#rfimpvars_gm12878_50kb_SMOTE <- rfimpvars_gm12878_50kb_SMOTE[10:1,]
rfimpvars_gm12878_50kb_SMOTE <- rfimpvars_gm12878_50kb_SMOTE[1:20,]
rfimpvars_gm12878_50kb_SMOTE <- rfimpvars_gm12878_50kb_SMOTE[20:1,]

rfimpvars_gm12878_50kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_gm12878_50kb_SMOTE$Feature)

rfimpvars_gm12878_50kb_SMOTE$Feature <- factor(rfimpvars_gm12878_50kb_SMOTE$Feature, levels=rfimpvars_gm12878_50kb_SMOTE$Feature)

vip.gm12878.50kb.SMOTE <- ggplot(rfimpvars_gm12878_50kb_SMOTE, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_50kb_SMOTE <- rfimpvars_K562_50kb_SMOTE[1:10,]
#rfimpvars_K562_50kb_SMOTE <- rfimpvars_K562_50kb_SMOTE[10:1,]
rfimpvars_K562_50kb_SMOTE <- rfimpvars_K562_50kb_SMOTE[1:20,]
rfimpvars_K562_50kb_SMOTE <- rfimpvars_K562_50kb_SMOTE[20:1,]

rfimpvars_K562_50kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_K562_50kb_SMOTE$Feature)

rfimpvars_K562_50kb_SMOTE$Feature <- factor(rfimpvars_K562_50kb_SMOTE$Feature, levels=rfimpvars_K562_50kb_SMOTE$Feature)

vip.K562.50kb.SMOTE <- ggplot(rfimpvars_K562_50kb_SMOTE, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

##100kb

###None

```{r}
#GM12878
rfimpvars_gm12878_100kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[1:10,]
#rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[10:1,]
rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[1:20,]
rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[20:1,]

rfimpvars_gm12878_100kb_none$Feature <- gsub("_dist","", rfimpvars_gm12878_100kb_none$Feature)

rfimpvars_gm12878_100kb_none$Feature <- factor(rfimpvars_gm12878_100kb_none$Feature, levels=rfimpvars_gm12878_100kb_none$Feature)

vip.gm12878.100kb.none <- ggplot(rfimpvars_gm12878_100kb_none, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_100kb_none <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_100kb_none <- rfimpvars_K562_100kb_none[1:10,]
#rfimpvars_K562_100kb_none <- rfimpvars_K562_100kb_none[10:1,]
rfimpvars_K562_100kb_none <- rfimpvars_K562_100kb_none[1:20,]
rfimpvars_K562_100kb_none <- rfimpvars_K562_100kb_none[20:1,]

rfimpvars_K562_100kb_none$Feature <- gsub("_dist","", rfimpvars_K562_100kb_none$Feature)

rfimpvars_K562_100kb_none$Feature <- factor(rfimpvars_K562_100kb_none$Feature, levels=rfimpvars_K562_100kb_none$Feature)

vip.K562.100kb.none <- ggplot(rfimpvars_K562_100kb_none, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

```

###ROS

```{r}
rfimpvars_gm12878_100kb_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_100kb_ROS <- rfimpvars_gm12878_100kb_ROS[1:10,]
#rfimpvars_gm12878_100kb_ROS <- rfimpvars_gm12878_100kb_ROS[10:1,]
rfimpvars_gm12878_100kb_ROS <- rfimpvars_gm12878_100kb_ROS[1:20,]
rfimpvars_gm12878_100kb_ROS <- rfimpvars_gm12878_100kb_ROS[20:1,]

rfimpvars_gm12878_100kb_ROS$Feature <- gsub("_dist","", rfimpvars_gm12878_100kb_ROS$Feature)

rfimpvars_gm12878_100kb_ROS$Feature <- factor(rfimpvars_gm12878_100kb_ROS$Feature, levels=rfimpvars_gm12878_100kb_ROS$Feature)

vip.gm12878.100kb.ROS <- ggplot(rfimpvars_gm12878_100kb_ROS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_100kb_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_100kb_ROS <- rfimpvars_K562_100kb_ROS[1:10,]
#rfimpvars_K562_100kb_ROS <- rfimpvars_K562_100kb_ROS[10:1,]
rfimpvars_K562_100kb_ROS <- rfimpvars_K562_100kb_ROS[1:20,]
rfimpvars_K562_100kb_ROS <- rfimpvars_K562_100kb_ROS[20:1,]

rfimpvars_K562_100kb_ROS$Feature <- gsub("_dist","", rfimpvars_K562_100kb_ROS$Feature)

rfimpvars_K562_100kb_ROS$Feature <- factor(rfimpvars_K562_100kb_ROS$Feature, levels=rfimpvars_K562_100kb_ROS$Feature)

vip.K562.100kb.ROS <- ggplot(rfimpvars_K562_100kb_ROS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

###RUS

```{r}
rfimpvars_gm12878_100kb_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_100kb_RUS <- rfimpvars_gm12878_100kb_RUS[1:10,]
#rfimpvars_gm12878_100kb_RUS <- rfimpvars_gm12878_100kb_RUS[10:1,]
rfimpvars_gm12878_100kb_RUS <- rfimpvars_gm12878_100kb_RUS[1:20,]
rfimpvars_gm12878_100kb_RUS <- rfimpvars_gm12878_100kb_RUS[20:1,]

rfimpvars_gm12878_100kb_RUS$Feature <- gsub("_dist","", rfimpvars_gm12878_100kb_RUS$Feature)

rfimpvars_gm12878_100kb_RUS$Feature <- factor(rfimpvars_gm12878_100kb_RUS$Feature, levels=rfimpvars_gm12878_100kb_RUS$Feature)

vip.gm12878.100kb.RUS <- ggplot(rfimpvars_gm12878_100kb_RUS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_100kb_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_100kb_RUS <- rfimpvars_K562_100kb_RUS[1:10,]
#rfimpvars_K562_100kb_RUS <- rfimpvars_K562_100kb_RUS[10:1,]
rfimpvars_K562_100kb_RUS <- rfimpvars_K562_100kb_RUS[1:20,]
rfimpvars_K562_100kb_RUS <- rfimpvars_K562_100kb_RUS[20:1,]

rfimpvars_K562_100kb_RUS$Feature <- gsub("_dist","", rfimpvars_K562_100kb_RUS$Feature)

rfimpvars_K562_100kb_RUS$Feature <- factor(rfimpvars_K562_100kb_RUS$Feature, levels=rfimpvars_K562_100kb_RUS$Feature)

vip.K562.100kb.RUS <- ggplot(rfimpvars_K562_100kb_RUS, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

###SMOTE

```{r}
rfimpvars_gm12878_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_100kb_SMOTE <- rfimpvars_gm12878_100kb_SMOTE[1:10,]
#rfimpvars_gm12878_100kb_SMOTE <- rfimpvars_gm12878_100kb_SMOTE[10:1,]
rfimpvars_gm12878_100kb_SMOTE <- rfimpvars_gm12878_100kb_SMOTE[1:20,]
rfimpvars_gm12878_100kb_SMOTE <- rfimpvars_gm12878_100kb_SMOTE[20:1,]

rfimpvars_gm12878_100kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_gm12878_100kb_SMOTE$Feature)

rfimpvars_gm12878_100kb_SMOTE$Feature <- factor(rfimpvars_gm12878_100kb_SMOTE$Feature, levels=rfimpvars_gm12878_100kb_SMOTE$Feature)

vip.gm12878.100kb.SMOTE <- ggplot(rfimpvars_gm12878_100kb_SMOTE, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))

#K562
rfimpvars_K562_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_K562_100kb_SMOTE <- rfimpvars_K562_100kb_SMOTE[1:10,]
#rfimpvars_K562_100kb_SMOTE <- rfimpvars_K562_100kb_SMOTE[10:1,]
rfimpvars_K562_100kb_SMOTE <- rfimpvars_K562_100kb_SMOTE[1:20,]
rfimpvars_K562_100kb_SMOTE <- rfimpvars_K562_100kb_SMOTE[20:1,]

rfimpvars_K562_100kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_K562_100kb_SMOTE$Feature)

rfimpvars_K562_100kb_SMOTE$Feature <- factor(rfimpvars_K562_100kb_SMOTE$Feature, levels=rfimpvars_K562_100kb_SMOTE$Feature)

vip.K562.100kb.SMOTE <- ggplot(rfimpvars_K562_100kb_SMOTE, aes(x=Feature, y=Importance)) +
  geom_bar(stat="identity", 
           width=.5, 
           position="dodge") +
  coord_flip() +
  theme_minimal()+
  theme_bw()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

## Combined

```{r}
ggarrange(vip.gm12878.10kb.SMOTE, vip.K562.10kb.SMOTE, ncol = 2, nrow = 1)
```

## Variable Importance Heatmaps for models with distance type predictors

###SMOTE

```{r}
####GM12878

rfimpvars_gm12878_10kb_SMOTE <- rfimpvars_gm12878_10kb_SMOTE[order(as.character(rfimpvars_gm12878_10kb_SMOTE$Feature)),]
rfimpvars_gm12878_25kb_SMOTE <- rfimpvars_gm12878_25kb_SMOTE[order(as.character(rfimpvars_gm12878_25kb_SMOTE$Feature)),]
rfimpvars_gm12878_50kb_SMOTE <- rfimpvars_gm12878_50kb_SMOTE[order(as.character(rfimpvars_gm12878_50kb_SMOTE$Feature)),]
rfimpvars_gm12878_100kb_SMOTE <- rfimpvars_gm12878_100kb_SMOTE[order(as.character(rfimpvars_gm12878_100kb_SMOTE$Feature)),]

unionannots <- union(rfimpvars_gm12878_10kb_SMOTE$Feature,
                      union(rfimpvars_gm12878_25kb_SMOTE$Feature,
                            union(rfimpvars_gm12878_50kb_SMOTE$Feature,rfimpvars_gm12878_100kb_SMOTE$Feature)))
unionannots <- sort(unionannots)

vim.gm12878.smote <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
vim.gm12878.smote[which(rownames(vim.gm12878.smote) %in% rfimpvars_gm12878_10kb_SMOTE$Feature), 1] <- rfimpvars_gm12878_10kb_SMOTE$Importance
vim.gm12878.smote[which(rownames(vim.gm12878.smote) %in% rfimpvars_gm12878_25kb_SMOTE$Feature), 2] <- rfimpvars_gm12878_25kb_SMOTE$Importance
vim.gm12878.smote[which(rownames(vim.gm12878.smote) %in% rfimpvars_gm12878_50kb_SMOTE$Feature), 3] <- rfimpvars_gm12878_50kb_SMOTE$Importance
vim.gm12878.smote[which(rownames(vim.gm12878.smote) %in% rfimpvars_gm12878_100kb_SMOTE$Feature), 4] <- rfimpvars_gm12878_100kb_SMOTE$Importance

vim.gm12878.smote <- vim.gm12878.smote[order(vim.gm12878.smote[,1], decreasing = TRUE),]

vim.gm12878.smote.m <- melt(vim.gm12878.smote)
vim.gm12878.smote.m$X1 <- factor(vim.gm12878.smote.m$X1, levels = rownames(vim.gm12878.smote))
vim.gm12878.smote.m$X2 <- factor(vim.gm12878.smote.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))

ggplot(vim.gm12878.smote.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient2(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Variable \n Importance",
                        limits = c(0,100),
                        breaks = c(0,25,50,75, 100),
                        labels = c("0", "25", "50", "75", "100")) +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation") +
    theme(#legend.position = c(.10, .10), 
        #legend.justification = c(.10, .10),
        #panel.border = element_rect(colour = "black", fill=NA),
        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20) #,
        #legend.background = element_rect(fill="white",
        #                                 size=0.5, 
        #                                 linetype="solid", 
        #                                 colour ="black")
        )

####K562

rfimpvars_K562_10kb_SMOTE <- rfimpvars_K562_10kb_SMOTE[order(as.character(rfimpvars_K562_10kb_SMOTE$Feature)),]
rfimpvars_K562_25kb_SMOTE <- rfimpvars_K562_25kb_SMOTE[order(as.character(rfimpvars_K562_25kb_SMOTE$Feature)),]
rfimpvars_K562_50kb_SMOTE <- rfimpvars_K562_50kb_SMOTE[order(as.character(rfimpvars_K562_50kb_SMOTE$Feature)),]
rfimpvars_K562_100kb_SMOTE <- rfimpvars_K562_100kb_SMOTE[order(as.character(rfimpvars_K562_100kb_SMOTE$Feature)),]

unionannots <- union(rfimpvars_K562_10kb_SMOTE$Feature,
                      union(rfimpvars_K562_25kb_SMOTE$Feature,
                            union(rfimpvars_K562_50kb_SMOTE$Feature,rfimpvars_K562_100kb_SMOTE$Feature)))
unionannots <- sort(unionannots)

vim.K562.smote <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
vim.K562.smote[which(rownames(vim.K562.smote) %in% rfimpvars_K562_10kb_SMOTE$Feature), 1] <- rfimpvars_K562_10kb_SMOTE$Importance
vim.K562.smote[which(rownames(vim.K562.smote) %in% rfimpvars_K562_25kb_SMOTE$Feature), 2] <- rfimpvars_K562_25kb_SMOTE$Importance
vim.K562.smote[which(rownames(vim.K562.smote) %in% rfimpvars_K562_50kb_SMOTE$Feature), 3] <- rfimpvars_K562_50kb_SMOTE$Importance
vim.K562.smote[which(rownames(vim.K562.smote) %in% rfimpvars_K562_100kb_SMOTE$Feature), 4] <- rfimpvars_K562_100kb_SMOTE$Importance

vim.K562.smote <- vim.K562.smote[order(vim.K562.smote[,1], decreasing = TRUE),]

vim.K562.smote.m <- melt(vim.K562.smote)
vim.K562.smote.m$X1 <- factor(vim.K562.smote.m$X1, levels = rownames(vim.K562.smote))
vim.K562.smote.m$X2 <- factor(vim.K562.smote.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))

ggplot(vim.K562.smote.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient2(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Variable \n Importance",
                        limits = c(0,100),
                        breaks = c(0,25,50,75, 100),
                        labels = c("0", "25", "50", "75", "100")) +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation") +
    theme(#legend.position = c(.10, .10), 
        #legend.justification = c(.10, .10),
        #panel.border = element_rect(colour = "black", fill=NA),
        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20) #,
        #legend.background = element_rect(fill="white",
        #                                 size=0.5, 
        #                                 linetype="solid", 
        #                                 colour ="black")
        )

```

###RUS

```{r}
####GM12878

rfimpvars_gm12878_10kb_RUS <- rfimpvars_gm12878_10kb_RUS[order(as.character(rfimpvars_gm12878_10kb_RUS$Feature)),]
rfimpvars_gm12878_25kb_RUS <- rfimpvars_gm12878_25kb_RUS[order(as.character(rfimpvars_gm12878_25kb_RUS$Feature)),]
rfimpvars_gm12878_50kb_RUS <- rfimpvars_gm12878_50kb_RUS[order(as.character(rfimpvars_gm12878_50kb_RUS$Feature)),]
rfimpvars_gm12878_100kb_RUS <- rfimpvars_gm12878_100kb_RUS[order(as.character(rfimpvars_gm12878_100kb_RUS$Feature)),]

unionannots <- union(rfimpvars_gm12878_10kb_RUS$Feature,
                      union(rfimpvars_gm12878_25kb_RUS$Feature,
                            union(rfimpvars_gm12878_50kb_RUS$Feature,rfimpvars_gm12878_100kb_RUS$Feature)))
unionannots <- sort(unionannots)

vim.gm12878.RUS <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
vim.gm12878.RUS[which(rownames(vim.gm12878.RUS) %in% rfimpvars_gm12878_10kb_RUS$Feature), 1] <- rfimpvars_gm12878_10kb_RUS$Importance
vim.gm12878.RUS[which(rownames(vim.gm12878.RUS) %in% rfimpvars_gm12878_25kb_RUS$Feature), 2] <- rfimpvars_gm12878_25kb_RUS$Importance
vim.gm12878.RUS[which(rownames(vim.gm12878.RUS) %in% rfimpvars_gm12878_50kb_RUS$Feature), 3] <- rfimpvars_gm12878_50kb_RUS$Importance
vim.gm12878.RUS[which(rownames(vim.gm12878.RUS) %in% rfimpvars_gm12878_100kb_RUS$Feature), 4] <- rfimpvars_gm12878_100kb_RUS$Importance

vim.gm12878.RUS <- vim.gm12878.RUS[order(vim.gm12878.RUS[,1], decreasing = TRUE),]

vim.gm12878.RUS.m <- melt(vim.gm12878.RUS)
vim.gm12878.RUS.m$X1 <- factor(vim.gm12878.RUS.m$X1, levels = rownames(vim.gm12878.RUS))
vim.gm12878.RUS.m$X2 <- factor(vim.gm12878.RUS.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))

ggplot(vim.gm12878.RUS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Importance") +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation")

####K562

rfimpvars_K562_10kb_RUS <- rfimpvars_K562_10kb_RUS[order(as.character(rfimpvars_K562_10kb_RUS$Feature)),]
rfimpvars_K562_25kb_RUS <- rfimpvars_K562_25kb_RUS[order(as.character(rfimpvars_K562_25kb_RUS$Feature)),]
rfimpvars_K562_50kb_RUS <- rfimpvars_K562_50kb_RUS[order(as.character(rfimpvars_K562_50kb_RUS$Feature)),]
rfimpvars_K562_100kb_RUS <- rfimpvars_K562_100kb_RUS[order(as.character(rfimpvars_K562_100kb_RUS$Feature)),]

unionannots <- union(rfimpvars_K562_10kb_RUS$Feature,
                      union(rfimpvars_K562_25kb_RUS$Feature,
                            union(rfimpvars_K562_50kb_RUS$Feature,rfimpvars_K562_100kb_RUS$Feature)))
unionannots <- sort(unionannots)

vim.K562.RUS <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
vim.K562.RUS[which(rownames(vim.K562.RUS) %in% rfimpvars_K562_10kb_RUS$Feature), 1] <- rfimpvars_K562_10kb_RUS$Importance
vim.K562.RUS[which(rownames(vim.K562.RUS) %in% rfimpvars_K562_25kb_RUS$Feature), 2] <- rfimpvars_K562_25kb_RUS$Importance
vim.K562.RUS[which(rownames(vim.K562.RUS) %in% rfimpvars_K562_50kb_RUS$Feature), 3] <- rfimpvars_K562_50kb_RUS$Importance
vim.K562.RUS[which(rownames(vim.K562.RUS) %in% rfimpvars_K562_100kb_RUS$Feature), 4] <- rfimpvars_K562_100kb_RUS$Importance

vim.K562.RUS <- vim.K562.RUS[order(vim.K562.RUS[,1], decreasing = TRUE),]

vim.K562.RUS.m <- melt(vim.K562.RUS)
vim.K562.RUS.m$X1 <- factor(vim.K562.RUS.m$X1, levels = rownames(vim.K562.RUS))
vim.K562.RUS.m$X2 <- factor(vim.K562.RUS.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))

ggplot(vim.K562.RUS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Importance") +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation")

```

###ROS

```{r}
####GM12878

rfimpvars_gm12878_10kb_ROS <- rfimpvars_gm12878_10kb_ROS[order(as.character(rfimpvars_gm12878_10kb_ROS$Feature)),]
rfimpvars_gm12878_25kb_ROS <- rfimpvars_gm12878_25kb_ROS[order(as.character(rfimpvars_gm12878_25kb_ROS$Feature)),]
rfimpvars_gm12878_50kb_ROS <- rfimpvars_gm12878_50kb_ROS[order(as.character(rfimpvars_gm12878_50kb_ROS$Feature)),]
rfimpvars_gm12878_100kb_ROS <- rfimpvars_gm12878_100kb_ROS[order(as.character(rfimpvars_gm12878_100kb_ROS$Feature)),]

unionannots <- union(rfimpvars_gm12878_10kb_ROS$Feature,
                      union(rfimpvars_gm12878_25kb_ROS$Feature,
                            union(rfimpvars_gm12878_50kb_ROS$Feature,rfimpvars_gm12878_100kb_ROS$Feature)))
unionannots <- sort(unionannots)

vim.gm12878.ROS <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
vim.gm12878.ROS[which(rownames(vim.gm12878.ROS) %in% rfimpvars_gm12878_10kb_ROS$Feature), 1] <- rfimpvars_gm12878_10kb_ROS$Importance
vim.gm12878.ROS[which(rownames(vim.gm12878.ROS) %in% rfimpvars_gm12878_25kb_ROS$Feature), 2] <- rfimpvars_gm12878_25kb_ROS$Importance
vim.gm12878.ROS[which(rownames(vim.gm12878.ROS) %in% rfimpvars_gm12878_50kb_ROS$Feature), 3] <- rfimpvars_gm12878_50kb_ROS$Importance
vim.gm12878.ROS[which(rownames(vim.gm12878.ROS) %in% rfimpvars_gm12878_100kb_ROS$Feature), 4] <- rfimpvars_gm12878_100kb_ROS$Importance

vim.gm12878.ROS <- vim.gm12878.ROS[order(vim.gm12878.ROS[,1], decreasing = TRUE),]

vim.gm12878.ROS.m <- melt(vim.gm12878.ROS)
vim.gm12878.ROS.m$X1 <- factor(vim.gm12878.ROS.m$X1, levels = rownames(vim.gm12878.ROS))
vim.gm12878.ROS.m$X2 <- factor(vim.gm12878.ROS.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))

ggplot(vim.gm12878.ROS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Importance") +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation")

####K562

rfimpvars_K562_10kb_ROS <- rfimpvars_K562_10kb_ROS[order(as.character(rfimpvars_K562_10kb_ROS$Feature)),]
rfimpvars_K562_25kb_ROS <- rfimpvars_K562_25kb_ROS[order(as.character(rfimpvars_K562_25kb_ROS$Feature)),]
rfimpvars_K562_50kb_ROS <- rfimpvars_K562_50kb_ROS[order(as.character(rfimpvars_K562_50kb_ROS$Feature)),]
rfimpvars_K562_100kb_ROS <- rfimpvars_K562_100kb_ROS[order(as.character(rfimpvars_K562_100kb_ROS$Feature)),]

unionannots <- union(rfimpvars_K562_10kb_ROS$Feature,
                      union(rfimpvars_K562_25kb_ROS$Feature,
                            union(rfimpvars_K562_50kb_ROS$Feature,rfimpvars_K562_100kb_ROS$Feature)))
unionannots <- sort(unionannots)

vim.K562.ROS <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
vim.K562.ROS[which(rownames(vim.K562.ROS) %in% rfimpvars_K562_10kb_ROS$Feature), 1] <- rfimpvars_K562_10kb_ROS$Importance
vim.K562.ROS[which(rownames(vim.K562.ROS) %in% rfimpvars_K562_25kb_ROS$Feature), 2] <- rfimpvars_K562_25kb_ROS$Importance
vim.K562.ROS[which(rownames(vim.K562.ROS) %in% rfimpvars_K562_50kb_ROS$Feature), 3] <- rfimpvars_K562_50kb_ROS$Importance
vim.K562.ROS[which(rownames(vim.K562.ROS) %in% rfimpvars_K562_100kb_ROS$Feature), 4] <- rfimpvars_K562_100kb_ROS$Importance

vim.K562.ROS <- vim.K562.ROS[order(vim.K562.ROS[,1], decreasing = TRUE),]

vim.K562.ROS.m <- melt(vim.K562.ROS)
vim.K562.ROS.m$X1 <- factor(vim.K562.ROS.m$X1, levels = rownames(vim.K562.ROS))
vim.K562.ROS.m$X2 <- factor(vim.K562.ROS.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))

ggplot(vim.K562.ROS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Importance") +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation")

```

###None

```{r}
####GM12878

rfimpvars_gm12878_10kb_none <- rfimpvars_gm12878_10kb_none[order(as.character(rfimpvars_gm12878_10kb_none$Feature)),]
rfimpvars_gm12878_25kb_none <- rfimpvars_gm12878_25kb_none[order(as.character(rfimpvars_gm12878_25kb_none$Feature)),]
rfimpvars_gm12878_50kb_none <- rfimpvars_gm12878_50kb_none[order(as.character(rfimpvars_gm12878_50kb_none$Feature)),]
#rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[-which(is.na(rfimpvars_gm12878_100kb_none$Importance)),]
rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[order(as.character(rfimpvars_gm12878_100kb_none$Feature)),]

unionannots <- union(rfimpvars_gm12878_10kb_none$Feature,
                      union(rfimpvars_gm12878_25kb_none$Feature,
                            union(rfimpvars_gm12878_50kb_none$Feature,rfimpvars_gm12878_100kb_none$Feature)))
unionannots <- sort(unionannots)

vim.gm12878.none <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
vim.gm12878.none[which(rownames(vim.gm12878.none) %in% rfimpvars_gm12878_10kb_none$Feature), 1] <- rfimpvars_gm12878_10kb_none$Importance
vim.gm12878.none[which(rownames(vim.gm12878.none) %in% rfimpvars_gm12878_25kb_none$Feature), 2] <- rfimpvars_gm12878_25kb_none$Importance
vim.gm12878.none[which(rownames(vim.gm12878.none) %in% rfimpvars_gm12878_50kb_none$Feature), 3] <- rfimpvars_gm12878_50kb_none$Importance
vim.gm12878.none[which(rownames(vim.gm12878.none) %in% rfimpvars_gm12878_100kb_none$Feature), 4] <- rfimpvars_gm12878_100kb_none$Importance

vim.gm12878.none <- vim.gm12878.none[order(vim.gm12878.none[,1], decreasing = TRUE),]

vim.gm12878.none.m <- melt(vim.gm12878.none)
vim.gm12878.none.m$X1 <- factor(vim.gm12878.none.m$X1, levels = rownames(vim.gm12878.none))
vim.gm12878.none.m$X2 <- factor(vim.gm12878.none.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))

ggplot(vim.gm12878.none.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Importance") +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation")

####K562

rfimpvars_K562_10kb_none <- rfimpvars_K562_10kb_none[order(as.character(rfimpvars_K562_10kb_none$Feature)),]
rfimpvars_K562_25kb_none <- rfimpvars_K562_25kb_none[order(as.character(rfimpvars_K562_25kb_none$Feature)),]
rfimpvars_K562_50kb_none <- rfimpvars_K562_50kb_none[order(as.character(rfimpvars_K562_50kb_none$Feature)),]
rfimpvars_K562_100kb_none <- rfimpvars_K562_100kb_none[order(as.character(rfimpvars_K562_100kb_none$Feature)),]

unionannots <- union(rfimpvars_K562_10kb_none$Feature,
                      union(rfimpvars_K562_25kb_none$Feature,
                            union(rfimpvars_K562_50kb_none$Feature,rfimpvars_K562_100kb_none$Feature)))
unionannots <- sort(unionannots)

vim.K562.none <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
vim.K562.none[which(rownames(vim.K562.none) %in% rfimpvars_K562_10kb_none$Feature), 1] <- rfimpvars_K562_10kb_none$Importance
vim.K562.none[which(rownames(vim.K562.none) %in% rfimpvars_K562_25kb_none$Feature), 2] <- rfimpvars_K562_25kb_none$Importance
vim.K562.none[which(rownames(vim.K562.none) %in% rfimpvars_K562_50kb_none$Feature), 3] <- rfimpvars_K562_50kb_none$Importance
vim.K562.none[which(rownames(vim.K562.none) %in% rfimpvars_K562_100kb_none$Feature), 4] <- rfimpvars_K562_100kb_none$Importance

vim.K562.none <- vim.K562.none[order(vim.K562.none[,1], decreasing = TRUE),]

vim.K562.none.m <- melt(vim.K562.none)
vim.K562.none.m$X1 <- factor(vim.K562.none.m$X1, levels = rownames(vim.K562.none))
vim.K562.none.m$X2 <- factor(vim.K562.none.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))

ggplot(vim.K562.none.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
    geom_tile(aes(fill = value), 
              colour = "white") + 
    scale_fill_gradient(low = "white", 
                        high = "steelblue",
                        na.value = "grey50",
                        name="Importance") +
    theme_bw() +
    theme_minimal() +
    xlab("Resolution") +
    ylab("Genomic Annotation")

```

### 2019-03-10 Scripts/evaluating_variable_importances.Rmd
editting script to fix axes

@@
               colour = "white") + 
-    scale_fill_gradient(low = "white", 
+    scale_fill_gradient2(low = "white", 
                         high = "steelblue",
                         na.value = "grey50",
-                        name="Importance") +
+                        name="Variable \n Importance",
+                        limits = c(0,100),
+                        breaks = c(0,25,50,75, 100),
+                        labels = c("0", "25", "50", "75", "100")) +
     theme_bw() +
@@
     xlab("Resolution") +
-    ylab("Genomic Annotation")
+    ylab("Genomic Annotation") +
+    theme(#legend.position = c(.10, .10), 
+        #legend.justification = c(.10, .10),
+        #panel.border = element_rect(colour = "black", fill=NA),
+        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20) #,
+        #legend.background = element_rect(fill="white",
+        #                                 size=0.5, 
+        #                                 linetype="solid", 
+        #                                 colour ="black")
+        )
 
@@
     xlab("Resolution") +
-    ylab("Genomic Annotation")
-
-```
+    ylab("Genomic Annotation") +
+    theme(#legend.position = c(.10, .10), 
+        #legend.justification = c(.10, .10),
+        #panel.border = element_rect(colour = "black", fill=NA),
+        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20) #,
+        #legend.background = element_rect(fill="white",
+        #                                 size=0.5, 
+        #                                 linetype="solid", 
+        #                                 colour ="black")
+        )
+
+```

### 2019-03-11 Manuscript/Figures/figure_legends.Rmd
added to figure legends

@@
 
+**Figure 6.
+Variable importance of the top 20 most predictive genomic annotations for models using SMOTE resampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
+Variable importance is assigned on a continuous scale (range: 0-100).
+Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model.
+The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using SMOTE resampling, for each cell line respectively.
+
 <!--

### 2019-03-11 Manuscript/Supplementary/supplementary_legends.Rmd
added to figure legends

@@
 
+**Figure 6.
+Variable importance of the top 20 most predictive genomic annotations for models using no resampling technique with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
+Variable importance is assigned on a continuous scale (range: 0-100).
+Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model.
+The genomic annotations are sorted by highest level of importance obtained from a random forest model with distance-type predictors at the 10 kb data resolution, while not performing a class balancing technique, for each cell line respectively.
+
+**Figure 7.
+Variable importance of the top 20 most predictive genomic annotations for models using random over-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
+Variable importance is assigned on a continuous scale (range: 0-100).
+Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model.
+The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using random over-sampling to create balanced classes, for each cell line respectively.
+
+**Figure 8.
+Variable importance of the top 20 most predictive genomic annotations for models using random under-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
+Variable importance is assigned on a continuous scale (range: 0-100).
+Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model.
+The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using random under-sampling to create balanced classes, for each cell line respectively.
+
 <!--

### 2019-03-11 Manuscript/Supplementary/supplementary_legends.Rmd
editted legend for clarity

@@
 **Supplementary Figure 3.
-Heatmaps illustrating the variable reduction.** An elastic-net algorithm was used to improve computational efficiency and reduce noise for both the GM12878 (A) and K562 (B) cell lines.
+Heatmaps illustrating which features were reduced using Elastic-Net regularization.** An elastic-net algorithm was used to improve computational efficiency and reduce noise for both the GM12878 (A) and K562 (B) cell lines.
 Features that were regularized and subsequently removed from downstream modeling are denoted in white, while the features that were not regularized and kept for further analyses are denoted in red.
 Each vertical region is made up of a particular data resolution (10 kb, 25 kb, 50kb, and 100 kb), resampling technique (None, RUS, ROS, and SMOTE), and predictor type (OC, OP, and Distance).
-The yellow lines separate each of the three predictor types.
+The yellow lines separate each of the three predictor types (overlap counts, overlap percents, and distance types respectively).
 

### 2019-03-11 Manuscript/manuscript.Rmd
manuscript edits

@@
 1.
-**Overlap Counts (OC)**: For each genomic bin, the total number of instances (bases) where a bin overlapped with genomic annotation regions (features) was calculated.
-In the case of no overlaps the value is set as 0.
+**Overlap Counts (OC)**: For each genomic bin, the total number of instances where a genomic bin overlapped with regions assigned to genomic annotations (features) was calculated.
+In the case of no overlaps, the value was set to 0.
 
 2.
-**Overlap Percent (OP)**: For each genomic bin, the percent overlap between the feature width and the total width of the bin was calculated.
-We defined the feature width as the number of bases that overlapped with the genomic bin.
+**Overlap Percent (OP)**: For each genomic bin, the percent of overlap between the width of the region assigned to a genomic annotation and the total width of the bin was calculated.
+We defined the feature width as the number of bases that overlapped with a particular genomic bin.
 The percent was then calculated by dividing the feature width by the bin width.
@@
 
-## MANY GENOMIC ANNOTATIONS WERE HIGHLY CORRELATED
+## HIGH CORRRELATIONS IMPLY COLOCALIZATION OF MANY ANNOTATIONS AROUND TAD BOUNDARIES
 
-When assessing the collinearity of the genomic annotations, it was found that the total number of bases that the number overlapped bases between genomic bins flanked by a TAD boundary were highly correlated between many genomic annotations (Supplementary Figure 2).
-That is, many genomic annotations tended to colocalize near eachother at the boarders of domains.
+We assessed the collinearity among the genomic annotations used for the feature space of subsequent models by isolating the genomic bins that overlapped with flanked TAD boundaries.
+We then vectorized the number of instances when a region defined by a genomic annotation overlapped with the isolated bins.
+It was found that the correlations among these vectors were very high for many genomic annotations.
+The correlations were visualized using correlograms for each data resolution and cell line (Supplementary Figure 2).
+The high correlations imply that many genomic annotations tended to colocalize near eachother at the boarders of domains.
 This was present across both resolution and cell line.
@@
 Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly correlated with on another, yet inversely correlated with many transcription factor binding sites.
-The high correlations among many of the genomic annotations gives precedent for the use of an elastic-net regularization.
+
+The high correlations among many of the genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.
+The regularization was performed after implementing each of the resampling techniques on all data resolutions within each cell line.
+Additionally, a unique predictor-type was included separately as the set of features.
+It was found that the elastic-net regularized the coefficients of far more distance-type predictors to 0 compared to datasets with overlap count and percent predictor types, regardless of cell line or data resolution (Supplementary Figure 3).
+Many elastic-net models using overlap count or percent predictors were reduced to ridge, or near-ridge regression models at higher data resolutions by having the $alpha$ penalization term tuned to 0 in the cross-validation step, thereby not reducing, or reducing very few of the feature space.
+The results of the variable reduction step imply that far more information relating annotions to TAD boundaries is encoded in the distance-type predictors.
+That is, the elastic-net algorithms were better able to separate noise and reduce the feature space when performed on distance-type predictors.
+Likewise, this reduction was most efficient at more refined levels of data resolution.
 

### 2019-03-11 Manuscript/manuscript.Rmd
manuscript edits

@@
 
+## MODELS WITH DISTANCE-TYPE PREDICTORS OUTPERFORM MODELS WITH OTHER PREDICTOR-TYPES
+
+After suitably reducing the feature space, we performed individual random forest classification models specific to cell line, data resolution, resampling technique, and predictor type.
+We assessed each models' ability to correctly identify the genomic bins that overlap with flanked TAD boundaries using F1-Score, MCC, and balanced accuracy.
+For 10 kb data resoltion, it was found that models with distance-type predictors performed better according to all metrics, across each cell line, regardless of resampling technique used (Figure 4).
+This result was consistent across each of the other data resolutions as well (Supplementary Figure 4).
+Notably, we saw marked improvements in performance for models implemented on resampled datasets when compared to no resampling.
+Of the, resampling techniques considered, it was found that SMOTE resampled datasets, at the 10 kb resoltion, yielded the highest model performances across each metric.
+This result was, for the most part, consistent for the other data resolutions.
+Performances of randomly under-sampled datasets were found to be comparable to, if not better than (at some isolated resolutions; see supplementary), SMOTE.
+The steap drop off in performance for randomly over-sampled and no resampled datasets was most evident when assessing F1-scores and balanced accuracies.
+Measures of MCC were found to increase more steadily toward models implemented on SMOTE resampled datasets.
+These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that incorporates both random under- and over-sampling, as SMOTE is known to do.
+
 <!--

### 2019-03-11 Manuscript/manuscript.Rmd
manuscript edits

@@
 Notably, we saw marked improvements in performance for models implemented on resampled datasets when compared to no resampling.
+
+## MODELS IMPLEMENTED ON SMOTE RESAMPLED DATA PERFORMED BEST
+
 Of the, resampling techniques considered, it was found that SMOTE resampled datasets, at the 10 kb resoltion, yielded the highest model performances across each metric.
@@
 
-<!--
-## DISTANCE TYPE PREDICTORS OUTPERFORM OTHER PREDICTOR-TYPES
-
-For each cell line and resolution, we balanced the data using each resampling technique and performed a series of random forest classification algorithms on the full features space (all combined predictor types), as well as on type-specific feature spaces (overlap counts, overlap predictors, and distances).
-PR-curves were plotted and compared for 10 kb resolutions (Figures 4-8).
-For all curves, the baseline threshold used to assign a performance to a random model is defined as the ratio of genomic bins that overlapped with a flanked TAD boundary divided by the total number of genomic bins for the test set, respective to cell line and resolution.
-It was found that for the 10 kb resolution data, models with distance type predictors had consistently higher AUPRC values compared to other predictor types, across both cell line and resampling technique.
-This result was observed for the other resolutions as well (Supplementary Figuers 9-23l; Supplementary Table 2).
-
-Recursive feature elimination was used to establish the optimal number of distance-type features to include in downstream analyses.
-It was determined that, for 10 kb resolution data, near optimal performance was obtained for models with only 32 predictors, across each resampling technique and for each cell line (Figures 9-13).
-Results remained consistent across the other data resolutions (Supplementary Figures 24-38).
-Therefore, the feature space was reduced for subsequent models to the top 32 predictors, respective to cell line, resolution, and resampling technique.
--->
+We then directly compared models using SMOTE resampled datasets across each data resolution to see how performances changed as resolution increased.
+For each cell line, we found that model performances tended to decline as data resolution increased.
+Random forest models implemented on 10 kb, SMOTE resampled, data resolutions, with distance-type predictors were found to perform best according to MCC and balanced accuracy (Figure 5).
+There was a slight improvement in F1-Score for the 25 kb resolution on the GM12878 cell line.
+Performances from the K562 cell line degraded much faster as resolution increased, while the worst performing models for the GM12878 cell line were at the 50 kb resolution, followed by a slight improvement in performance at the 100 kb resolution.
+To be comprehensive we evaluated the performances across resolutions of models with distance-type predictors for the other resampling techniques and found the results to be largely consistent (Supplementary Figure 5).
 

### 2019-03-12 Scripts/evaluating_feature_reduction.Rmd
updated script for created heatmaps for enet coefficients

@@
 ```
+
+# Evaluating Elastic-Net
+
+## Heatmaps of whether or not a variable was reduced
 
@@
 ```
+
+## Heatmaps using coefficients from elastic-net
+
+### G12878
+
+#### 10 kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/enetModel.rds")
+enetcoefs_none_oc_10kb_gm12878 <- coef(enetcoefs_none_oc_10kb_gm12878$finalModel, s=enetcoefs_none_oc_10kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_none_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/enetModel.rds")
+enetcoefs_none_op_10kb_gm12878 <- coef(enetcoefs_none_op_10kb_gm12878$finalModel, s=enetcoefs_none_op_10kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_none_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/enetModel.rds")
+enetcoefs_none_dist_10kb_gm12878 <- coef(enetcoefs_none_dist_10kb_gm12878$finalModel, s=enetcoefs_none_dist_10kb_gm12878$bestTune$lambda)
+
+#RUS
+##OC
+enetcoefs_RUS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/enetModel.rds")
+enetcoefs_RUS_oc_10kb_gm12878 <- coef(enetcoefs_RUS_oc_10kb_gm12878$finalModel, s=enetcoefs_RUS_oc_10kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_RUS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/enetModel.rds")
+enetcoefs_RUS_op_10kb_gm12878 <- coef(enetcoefs_RUS_op_10kb_gm12878$finalModel, s=enetcoefs_RUS_op_10kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_RUS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
+enetcoefs_RUS_dist_10kb_gm12878 <- coef(enetcoefs_RUS_dist_10kb_gm12878$finalModel, s=enetcoefs_RUS_dist_10kb_gm12878$bestTune$lambda)
+
+#ROS
+##OC
+enetcoefs_ROS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/enetModel.rds")
+enetcoefs_ROS_oc_10kb_gm12878 <- coef(enetcoefs_ROS_oc_10kb_gm12878$finalModel, s=enetcoefs_ROS_oc_10kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_ROS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/enetModel.rds")
+enetcoefs_ROS_op_10kb_gm12878 <- coef(enetcoefs_ROS_op_10kb_gm12878$finalModel, s=enetcoefs_ROS_op_10kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_ROS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
+enetcoefs_ROS_dist_10kb_gm12878 <- coef(enetcoefs_ROS_dist_10kb_gm12878$finalModel, s=enetcoefs_ROS_dist_10kb_gm12878$bestTune$lambda)
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
+enetcoefs_SMOTE_oc_10kb_gm12878 <- coef(enetcoefs_SMOTE_oc_10kb_gm12878$finalModel, s=enetcoefs_SMOTE_oc_10kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_SMOTE_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
+enetcoefs_SMOTE_op_10kb_gm12878 <- coef(enetcoefs_SMOTE_op_10kb_gm12878$finalModel, s=enetcoefs_SMOTE_op_10kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_SMOTE_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
+enetcoefs_SMOTE_dist_10kb_gm12878 <- coef(enetcoefs_SMOTE_dist_10kb_gm12878$finalModel, s=enetcoefs_SMOTE_dist_10kb_gm12878$bestTune$lambda)
+
+enetcoefsmat <- cbind(enetcoefs_none_oc_10kb_gm12878[-1,1], 
+                      enetcoefs_ROS_oc_10kb_gm12878[-1,1],
+                      enetcoefs_RUS_oc_10kb_gm12878[-1,1], 
+                      enetcoefs_SMOTE_oc_10kb_gm12878[-1,1],
+
+                      enetcoefs_none_op_10kb_gm12878[-1,1], 
+                      enetcoefs_ROS_op_10kb_gm12878[-1,1],
+                      enetcoefs_RUS_op_10kb_gm12878[-1,1], 
+                      enetcoefs_SMOTE_op_10kb_gm12878[-1,1],
+
+                      enetcoefs_none_dist_10kb_gm12878[-1,1],
+                      enetcoefs_ROS_dist_10kb_gm12878[-1,1],
+                      enetcoefs_RUS_dist_10kb_gm12878[-1,1],
+                      enetcoefs_SMOTE_dist_10kb_gm12878[-1,1])
+
+enetcoefsmat[enetcoefsmat == 0] <- NA
+
+#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
+colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
+rownames(enetcoefsmat) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))
+
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
+
+```
+
+##### Overlap Counts
+
+```{r}
+heatmap.2(enetcoefsmat[,1:4],
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          dendrogram="row",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=1:4,
+          rowsep=1:nrow(enetcoefsmat),
+          keysize = 1) 
+```
+
+#####Overlap Percents
+
+```{r}
+heatmap.2(enetcoefsmat[,5:8],
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          dendrogram="row",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=1:4,
+          rowsep=1:nrow(enetcoefsmat),
+          keysize = 1) 
+```
+
+##### Distances
+
+```{r}
+heatmap.2(enetcoefsmat[,9:12],
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          dendrogram="row",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=1:4,
+          rowsep=1:nrow(enetcoefsmat),
+          keysize = 1) 
+```
+
+#### 25kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/enetModel.rds")
+enetcoefs_none_oc_25kb_gm12878 <- coef(enetcoefs_none_oc_25kb_gm12878$finalModel, s=enetcoefs_none_oc_25kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_none_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/enetModel.rds")
+enetcoefs_none_op_25kb_gm12878 <- coef(enetcoefs_none_op_25kb_gm12878$finalModel, s=enetcoefs_none_op_25kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_none_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/enetModel.rds")
+enetcoefs_none_dist_25kb_gm12878 <- coef(enetcoefs_none_dist_25kb_gm12878$finalModel, s=enetcoefs_none_dist_25kb_gm12878$bestTune$lambda)
+
+#RUS
+##OC
+enetcoefs_RUS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/enetModel.rds")
+enetcoefs_RUS_oc_25kb_gm12878 <- coef(enetcoefs_RUS_oc_25kb_gm12878$finalModel, s=enetcoefs_RUS_oc_25kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_RUS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/enetModel.rds")
+enetcoefs_RUS_op_25kb_gm12878 <- coef(enetcoefs_RUS_op_25kb_gm12878$finalModel, s=enetcoefs_RUS_op_25kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_RUS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
+enetcoefs_RUS_dist_25kb_gm12878 <- coef(enetcoefs_RUS_dist_25kb_gm12878$finalModel, s=enetcoefs_RUS_dist_25kb_gm12878$bestTune$lambda)
+
+#ROS
+##OC
+enetcoefs_ROS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/enetModel.rds")
+enetcoefs_ROS_oc_25kb_gm12878 <- coef(enetcoefs_ROS_oc_25kb_gm12878$finalModel, s=enetcoefs_ROS_oc_25kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_ROS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/enetModel.rds")
+enetcoefs_ROS_op_25kb_gm12878 <- coef(enetcoefs_ROS_op_25kb_gm12878$finalModel, s=enetcoefs_ROS_op_25kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_ROS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
+enetcoefs_ROS_dist_25kb_gm12878 <- coef(enetcoefs_ROS_dist_25kb_gm12878$finalModel, s=enetcoefs_ROS_dist_25kb_gm12878$bestTune$lambda)
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
+enetcoefs_SMOTE_oc_25kb_gm12878 <- coef(enetcoefs_SMOTE_oc_25kb_gm12878$finalModel, s=enetcoefs_SMOTE_oc_25kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_SMOTE_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
+enetcoefs_SMOTE_op_25kb_gm12878 <- coef(enetcoefs_SMOTE_op_25kb_gm12878$finalModel, s=enetcoefs_SMOTE_op_25kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_SMOTE_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
+enetcoefs_SMOTE_dist_25kb_gm12878 <- coef(enetcoefs_SMOTE_dist_25kb_gm12878$finalModel, s=enetcoefs_SMOTE_dist_25kb_gm12878$bestTune$lambda)
+
+enetcoefsmat <- cbind(enetcoefs_none_oc_25kb_gm12878[-1,1], 
+                      enetcoefs_ROS_oc_25kb_gm12878[-1,1],
+                      enetcoefs_RUS_oc_25kb_gm12878[-1,1], 
+                      enetcoefs_SMOTE_oc_25kb_gm12878[-1,1],
+
+                      enetcoefs_none_op_25kb_gm12878[-1,1], 
+                      enetcoefs_ROS_op_25kb_gm12878[-1,1],
+                      enetcoefs_RUS_op_25kb_gm12878[-1,1], 
+                      enetcoefs_SMOTE_op_25kb_gm12878[-1,1],
+
+                      enetcoefs_none_dist_25kb_gm12878[-1,1],
+                      enetcoefs_ROS_dist_25kb_gm12878[-1,1],
+                      enetcoefs_RUS_dist_25kb_gm12878[-1,1],
+                      enetcoefs_SMOTE_dist_25kb_gm12878[-1,1])
+
+enetcoefsmat[enetcoefsmat == 0] <- NA
+
+#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
+colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
+rownames(enetcoefsmat) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))
+
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
+
+```
+
+##### Overlap Counts
+
+```{r}
+heatmap.2(enetcoefsmat[,1:4],
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          dendrogram="row",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=1:4,
+          rowsep=1:nrow(enetcoefsmat),
+          keysize = 1) 
+```
+
+#####Overlap Percents
+
+```{r}
+heatmap.2(enetcoefsmat[,5:8],
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          dendrogram="row",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=1:4,
+          rowsep=1:nrow(enetcoefsmat),
+          keysize = 1) 
+```
+
+##### Distances
+
+```{r}
+my_palette2 <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
+my_palette2 <- c(my_palette2[1:20], "gray", my_palette2[21:39])
+my_palette2 <- colorRampPalette(c("blue", "white", "red"))(n=100)
+
+color.palette  <- c(colorRampPalette(c("blue", "gray", "red"))(n=99)[1:49], 
+                    "#F8F8F8", 
+                    colorRampPalette(c("yellow", "orange", "red"))(n=99)[50:99])
+enetcoefsmat2 <- enetcoefsmat
+enetcoefsmat2[,9:12][is.na(enetcoefsmat2[,9:12])] <- 0
+
+col_breaks = c(seq(-.999,-.900,length=2),
+           seq(-.899,-.800,length=2),
+           seq(-.799,-.700,length=2),
+           seq(-.699,-.600,length=2),
+           seq(-.599,-.500,length=2),
+           seq(-.499,-.400,length=2),
+           seq(-.399,-.300,length=2),
+           seq(-.299,-.200,length=2),
+           seq(-.199,-.100,length=2),
+           seq(-.099,-.001,length=2),
+           seq(0,0.1,length=1),  # for gray
+           seq(.001,.099,length=2),
+           seq(.100,.199,length=2),
+           seq(.200,.299,length=2),
+           seq(.300,.399,length=2),
+           seq(.400,.499,length=2),
+           seq(.500,.599,length=2),
+           seq(.600,.699,length=2),
+           seq(.700,.799,length=2),
+           seq(.800,.899,length=2),
+           seq(.900,.999,length=2))
+
+col_breaks = c(seq(-1,-.7,length=20),
+           seq(-.699,-.001,length=20),
+           seq(0,0.001,length=1),  # for white
+           seq(.001,.699,length=20),
+           seq(.7,1,length=20))
+
+heatmap.2(enetcoefsmat2[,9:12],
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette2,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          dendrogram="row",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=1:4,
+          rowsep=1:nrow(enetcoefsmat),
+          keysize = 1) 
+```

### 2019-03-12 Papers.Rmd
Rename file

# Notes on TAD prediction and enrichment

## TAD predictions

- Xiong, Kyle, and Jian Ma. “Revealing Hi-C Subcompartments by Imputing High-Resolution Inter-Chromosomal Chromatin Interactions.” BioRxiv, January 1, 2018, 505503. https://doi.org/10.1101/505503. - SNIPER - 3D subcompartment (A1, A2, B1, B2, B3) identification from low-coverage Hi-C datasets. A neural network based on a denoising autoencoder (9 layers) and multi-layer perceptron. Sigmoidal activation of inputs, ReLU, softmax on outputs. Dropout, binary cross-entropy. exp(-1/C) transformation of Hi-C matrices. Applied to Gm12878 and 8 additional cell types to compare subcompartment changes. Compared with Rao2014 annotations, outperforms Gaussian HMM and MEGABASE. https://github.com/ma-compbio/SNIPER
- Di Pierro, Michele, Ryan R. Cheng, Erez Lieberman Aiden, Peter G. Wolynes, and José N. Onuchic. “De Novo Prediction of Human Chromosome Structures: Epigenetic Marking Patterns Encode Genome Architecture.” Proceedings of the National Academy of Sciences of the United States of America 114, no. 46 (14 2017): 12126–31. https://doi.org/10.1073/pnas.1714980114. - MEGABASE - prediction of A1, A2, B1, B2, B3, B4 subcompartments from epigenomic features using deep learning. 84+11 histone- and ChIP-seq. Gm12878. Then, modeling 3D structure.

- Schreiber, Jacob, Timothy J Durham, Jeffrey Bilmes, and William Stafford Noble. “Multi-Scale Deep Tensor Factorization Learns a Latent Representation of the Human Epigenome,” July 8, 2018. https://doi.org/10.1101/364976. - Avocado - cell type-specific epigenome representation using a deep neural network tensor factorization method. Predict gene expression, promoter-enhancer interactions, TAD boundaries, frequently interacting regions (FIREs), missing cell-specific epigenomic marks. Comparison with ChromImpute, PREDICTD. Improves PREDICTD by inserting a deep neural network to nonlinearly combine decomposed latent factors. Model, imputed marks can be downloaded at https://noble.gs.washington.edu/proj/avocado/. Data source: TAD boundaries and FIRE scores are from supplementary of A. D. Schmitt, M. Hu, I. Jung, Z. Xu, Y. Qiu, C. L. Tan, Y. Li, S. Lin, Y. Lin, C. L. Barr, and B. Ren. A compendium of chromatin contact maps reveals spatially active regions in the human genome. Cell Reports, 17:2042–2059, 2016. Promoter-enhancer interactions are from https://github.com/shwhalen/targetfinder/tree/master/paper/targetfinder/combined/output-epw

- Hong, Seungpyo, and Dongsup Kim. “Computational Characterization of Chromatin Domain Boundary-Associated Genomic Elements.” Nucleic Acids Research 45, no. 18 (October 13, 2017): 10403–14. https://doi.org/10.1093/nar/gkx738. - Feature selection for predicting TAD boundaries. In addition to CTCF, ZNF143, YY1, DNAse, H3K36me3, TSSs, RNA Pol II, SP1, ZNF274, SIX5. Linear model, similar to forward selection. Data from UCSC, in supplementary. Distinguishing boundaries and centers. Distinguishing cell type-specific and clustered TFBSs.

- Mourad, Raphaël, and Olivier Cuvier. “Computational Identification of Genomic Features That Influence 3D Chromatin Domain Formation.” Edited by Kai Tan. PLOS Computational Biology 12, no. 5 (May 20, 2016): e1004908. https://doi.org/10.1371/journal.pcbi.1004908. - Predicting TAD boundaries from transcription factor binding sites (TFBSs). Multiple logistic regression with lasso L1 penalization, allows for interactions, positive/negative effect. Outperforms enrichment test, random forest (https://github.com/aloysius-lim/bigrf). For humans, CTCF, Cohesin, ZNF134, Polycomb group proteins are positive predictors, P300, RXRA, BCL11A and ELK1 are negative predictors. Tested for the effect of SNPs in CTCF binding sites (SNPs destroy TAD boundaries), the effect of slightly imprecise boundaries. Hi-C bins are assigned 1/0 for overlapping/nonoverlapping TFBSs, or % overlap if it is partial. No mentioning class disbalance problem, no cross-validation, no explicit distance consideration, no histone marks. HiCfeat R package, https://sites.google.com/site/raphaelmouradeng/home/programs

- Sefer, Emre, and Carl Kingsford. “Semi-Nonparametric Modeling of Topological Domain Formation from Epigenetic Data.” In Algorithms in Bioinformatics, edited by Mihai Pop and Hélène Touzet, 9289:148–61. Berlin, Heidelberg: Springer Berlin Heidelberg, 2015. https://doi.org/10.1007/978-3-662-48221-6_11. - Non-parametric approach, called nTDP, based on Bernstein polynomials for modeling TADs from histone modifications. Intro about histone modifications enriched in TAD boundaries (H3K4me3 and H3K27ac). Math, statistics, assumptions, regularization. Parameters of the model should be estimated via training, Cross-validation to prevent overfitting. Hi-C data from Human IMR90, ES, mouse ES. Binning ChIP-seq and DNAse-seq data at 40kb resolution as log RPKMs, consensus TAD boundaries from Armatus. The sets of 4 and 6 modifications that were most informative are: {H3K36me3, H3K4me1, H3K4me3, H3K9me3} and {H3K4me3, H3K79me2, H3K27ac, H3K9me3, H3K36me3, H4K20me1}. chromatin states from Segway are not important. https://www.cs.cmu.edu/~ckingsf/research/ntdp/

- Bednarz, Paweł, and Bartek Wilczyński. “Supervised Learning Method for Predicting Chromatin Boundary Associated Insulator Elements.” Journal of Bioinformatics and Computational Biology 12, no. 06 (December 2014): 1442006. https://doi.org/10.1142/S0219720014420062. - Predicting TAD boundaries using training data, and making new predictions. Bayesian network (BNFinder method), random forest vs. basic k-means clustering, ChromHMM, cdBEST. Using sequence k-mers and ChIP-seq data from modENCODE for prediction - CTCF ChIP-seq performs best. Used Boruta package for feature selection. Bayesian network performs best. To read on their BNFinder method

- Huang, Jialiang, Eugenio Marco, Luca Pinello, and Guo-Cheng Yuan. “Predicting Chromatin Organization Using Histone Marks.” Genome Biology 16, no. 1 (December 2015). https://doi.org/10.1186/s13059-015-0740-z. - Predicting chromatin interaction hubs and TAD boundaries from Hi-C data and 9 histone marks using BART - Bayesian Additive Regression Trees. Rank chromatin interactions into high ("hubs"), median, low, non-significant. Hubs are enriched in GWAS SNPs. Hubs are enriched in and predicted by H3K4me1, H3K27ac (markers of enhancers) in the center. Conservation, GC content, distance  to TSS did NOT improve predictions. The model trained using one cell type data predicts hubs in another. TAD boundaries from IMR90 (Dixon) vs. non-boundary genomic loci with similar interaction frequency. CTCF, then negative H3K4me1, are the most predictive, but H3K4me3 is the second most enriched.

- Zhou, Jian, and Olga G. Troyanskaya. “Global Quantitative Modeling of Chromatin Factor Interactions.” Edited by Andrey Rzhetsky. PLoS Computational Biology 10, no. 3 (March 27, 2014): e1003525. https://doi.org/10.1371/journal.pcbi.1003525. - A novel maximum entropy-based modeling approach to quantitatively capture interactions between chromatin factors at the same genomic location. Choosing the most uniform/least structured, maximum entropy. Pairwise and triplet interactions. L1 regularization.

- Bednarz, Paweł, and Bartek Wilczyński. “Supervised Learning Method for Predicting Chromatin Boundary Associated Insulator Elements.” Journal of Bioinformatics and Computational Biology 12, no. 6 (December 2014): 1442006. https://doi.org/10.1142/S0219720014420062. - Prediction of TAD boundaries in Drosophila using modENCODE data (>30 ChIP-Chip and ChIP-seq tracks). Starting from k-means, then Hidden Markov Models, then use cdBEST and BMFinder previously published methods. ROC curves. Boruta package for feature prioritization. Prediction of new boundaries.

## TAD epigenomics

- Yan, Koon-Kiu, Shaoke Lou, and Mark Gerstein. “MrTADFinder: A Network Modularity Based Approach to Identify Topologically Associating Domains in Multiple Resolutions.” PLoS Computational Biology 13, no. 7 (July 2017): e1005647. https://doi.org/10.1371/journal.pcbi.1005647. - MrTADFinder - network modularity-based TAD finder, community detection. Adapted for multiple resolutions with parameter y. Distance-dependent model. Optimization framework, Louvain algorithm to optimize Q. Confirmed Dixon's observations of H3K4me3, H3K27ac enrichment at TAD boundaries, depletion of H3K9me3, H3K27me3 enriched across resolutions. Genes, especially, housekeeping, are enriched near TAD boundaries. High- and extreme occupancy target regions (TF binding) are also enriched. CTCF enrichment is general. Logistic regression to predict TAD boundaries from TFBSs, prioritize which TFs are most important, Refs 18 and 19 refer to similar work. https://github.com/gersteinlab/MrTADFinder

## Epigenomic predictions

Many other in my `Zotero/Genome/Sequencing/Epigenomics/machine learning` collection

- Zhang, Shilu, Deborah Chasman, Sara Knaack, and Sushmita Roy. “Prediction of High-Resolution Hi-C Interaction Matrices.” BioRxiv, September 1, 2018. https://doi.org/10.1101/406322. - HiC-Reg - predict contact counts from epigenomic reatures, across cell lines. Previous methods use binary classification framework. Random forest regression-based framework, counts for pairs of regions as outputs of a regression model from input one-dimensional regulatory signals. Three types of feature encoding, all include distance between pairs of regions. AUC to measure performance. Five-fold cross-validation. Out Of Bag variable importance for feature selection. Distance, together with CTCF and other features are the best predictive features. TAD detection using directionality index, comparison with Jaccard. https://github.com/Roy-lab/HiC-Reg

- Belokopytova, Polina, Evgeniy Mozheiko, Miroslav Nuriddinov, Daniil Fishman, and Veniamin Fishman. “Quantitative Prediction of Enhancer-Promoter Interactions.” BioRxiv, February 5, 2019. https://doi.org/10.1101/541011. - 3DPredictor - Prediction of enhnancer-promoter interactions from gene expression and CTCF binding. Also predict changes in 3D genome organization - genomic rearrangements. Previous prediction techniques. Benchmarking of TargetFinder, its performance is overestimated. Class balance slightly improves performance. Two random chromosomes for validation, the rest - for training. DISTANCE as predictor. Gradient boosting for prediction, significantly better than Random Forest. Other tools - EP2Vec, CTCF-MP, HiC-Reg. https://github.com/labdevgen/3DPredictor

- Singh, Shashank, Yang Yang, Barnabas Poczos, and Jian Ma. “Predicting Enhancer-Promoter Interaction from Genomic Sequence with Deep Neural Networks,” February 5, 2018. https://doi.org/10.1101/085241. - SPEID - predict enhancer-promoter interactions from sequence only using deep learning. Extends author's PEP work, compared with TargetFinder, not RIPPLE. Three layers, convolutional, recurrent, dense. AUROC, F1. Class imbalance is addressed by "data augmentation", similar to oversampling. Ro account for proximal features, enhancers are extended. Feature importance in different cell lines. https://github.com/ma-compbio/SPEID

- Yang, Yang, Ruochi Zhang, Shashank Singh, and Jian Ma. “Exploiting Sequence-Based Features for Predicting Enhancer-Promoter Interactions.” Bioinformatics (Oxford, England) 33, no. 14 (July 15, 2017): i252–60. https://doi.org/10.1093/bioinformatics/btx257. - Predicting enhancer-promoter interactions based on sequence only. Boosted tree ensemble model. Two ways: PEP-Motif (prediction from motifs detected in the sequences), and PEP-Word (word embedding model, achieved better performance). Compared with RIPPLE and TargetFinder. https://github.com/ma-compbio/PEP

- Cao, Qin, Christine Anyansi, Xihao Hu, Liangliang Xu, Lei Xiong, Wenshu Tang, Myth T. S. Mok, et al. “Reconstruction of Enhancer-Target Networks in 935 Samples of Human Primary Cells, Tissues and Cell Lines.” Nature Genetics 49, no. 10 (October 2017): 1428–36. https://doi.org/10.1038/ng.3950. - Enhancer-promoter prediction from cell-specific gene expression, methylation in windows around TSS, Roadmap, FANTOM5 CAGE, ENCODE DNAse, LASSO, Elastic Net, cross-validation. 935 cell lines, networks downloadable as cell-specific hg19 genomic coordinates-EnsemblIDs-confidence score (higher the better) (http://yiplab.cse.cuhk.edu.hk/jeme/). Activity of _multiple_ enhancers explains gene expression better. JEME method outperforms TargetFinder, PreSTIGE, Ripple, IM-PET, Ernst. Activity is confined within TADs. Depletion of CTCF between enhander-TSS pair. Closest enhancer is poor predictor of gene regulation, distance is the second best predictor, combined model is the best. JEME code https://github.com/yiplabcuhk/JEME

- Firpi, Hiram A., Duygu Ucar, and Kai Tan. “Discover Regulatory DNA Elements Using Chromatin Signatures and Artificial Neural Network.” Bioinformatics (Oxford, England) 26, no. 13 (July 1, 2010): 1579–86. https://doi.org/10.1093/bioinformatics/btq248.  -Predicting enhancers from histone marks using a time-delay neural network. Review of other prediction approaches. Genomic annotations are converted into two functions - mean and energy, used for predictions. Fisher discriminant analysis as a feature extraction/reduction technique (H3K4me1 is the most predictive, then H3K4me2, H3K4me3)

- He, Bing, Changya Chen, Li Teng, and Kai Tan. “Global View of Enhancer-Promoter Interactome in Human Cells.” Proceedings of the National Academy of Sciences of the United States of America 111, no. 21 (May 27, 2014): E2191-2199. https://doi.org/10.1073/pnas.1320308111. - IM-PET method. Enhancer-promoter interaction prediction from several features: enhancer-promoter activity profile correlation, TF-promoter correlation, enhancer-promoter coevolution, distance between enhancer and promoter. DISTANCE is the most important predictive feature, but helped by others. Random forest, SVM and logistic regression perform worse. Compared with four other methods (nearest promoter, PreSTIGE, Ernst, Thurman). Cross-validation, no overfitting. Enhancer-promoter interactions are more cell-type-specific than just enhancers.

- Schuster-Böckler, Benjamin, and Ben Lehner. “Chromatin Organization Is a Major Influence on Regional Mutation Rates in Human Cancer Cells.” Nature 488, no. 7412 (August 23, 2012): 504–7. https://doi.org/10.1038/nature11273. - Cancer SNP density correlates with H3K9me3. 46 features, including Hi-C PCs, were tested for pairwise Pearson correlations.

## Prediction, general

- Wallace, Byron C., Kevin Small, Carla E. Brodley, and Thomas A. Trikalinos. “Class Imbalance, Redux.” In 2011 IEEE 11th International Conference on Data Mining, 754–63. Vancouver, BC, Canada: IEEE, 2011. https://doi.org/10.1109/ICDM.2011.33. - Class imbalance is best addressed by bagging an ensemble of classifiers over balanced bootstrap training samples. Undersampling performs well, SMOTE and weighted SVM fail at high dimensions.

- Haibo He, and E.A. Garcia. “Learning from Imbalanced Data.” IEEE Transactions on Knowledge and Data Engineering 21, no. 9 (September 2009): 1263–84. https://doi.org/10.1109/TKDE.2008.239. - Class imbalance comprehensive review. Approaches (random under-/oversampling, SMOTE, others). Assessment metrics for imbalanced class learning. Disadvantages of ROC curves and advantages of PR curves (J. Davis, M. Goadrich, "The Relationship between Precision-Recall and ROC Curves", Proc. Int’l Conf. Machine Learning).

- When the data is unbalanced, standard machine learning algorithms tend to be overwhelmed by the majority class, http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.711.8214

- C. Drummond, R. Holte, et al. C4. 5, class imbalance, and cost sensitivity: why under-sampling beats over-sampling. In Workshop on Learning from Imbalanced Datasets II. Citeseer, 2003

- Dal Pozzolo, Andrea, Olivier Caelen, Serge Waterschoot, and Gianluca Bontempi. “Racing for Unbalanced Methods Selection.” In International Conference on Intelligent Data Engineering and Automated Learning, 24–31. Springer, 2013. - F-racing strategy to select best performing method to deal with class imbalance. Overview of class imbalance techniques, including SMOTE, Ensemble methods. The F-Racing approach tests in parallel a set of alternatives and uses Friedman test to determine if an alternative is significantly worse than others.Random Forest and SMOTEnsemble generally perform best. race R package to perform F-racing algorithm https://cran.r-project.org/web/packages/race/index.html

- https://shiring.github.io/machine_learning/2017/04/02/unbalanced - Dealing with unbalanced data in machine learning

- Blagus, Rok, and Lara Lusa. “Class Prediction for High-Dimensional Class-Imbalanced Data.” BMC Bioinformatics 11 (October 20, 2010): 523. https://doi.org/10.1186/1471-2105-11-523. - Class imbalance empirical testing. Variable selection introduces additional bias towards classification into the majority class. Undersampling helps, oversampling does not. Variable normalization (centering) can worsen the performance.

- Bekkar, Mohamed, Hassiba Kheliouane Djemaa, and Taklit Akrouf Alitouche. "Evaluation measures for models assessment over imbalanced datasets." Iournal Of Information Engineering and Applications 3.10 (2013).  - List of various prediction metrics to use for imbalanced data and descriptions of each

- Whalen, Sean, Rebecca M. Truty, and Katherine S. Pollard. “Enhancer-Promoter Interactions Are Encoded by Complex Genomic Signatures on Looping Chromatin.” Nature Genetics 48, no. 5 (May 2016): 488–96. https://doi.org/10.1038/ng.3539.  -TargetFinder - ensemble learning of enhancer-promoter interactions within TADs using epigenomic data (DNAse hypersensitive sites, methylation, gene expression, TFBSs, conservation). Multiple machine learning techniques, applied to multiple cell types to learn shared and unique characteristics, as well to the combined cell line data modeled by epigenomic data common to the combined cell lines. Methylation, elongation histone modifications, AP-1 binding are best predictive features, not genes or conservation. Near optimal performance using 16 features. Importance of proximal features (distance). Introduction and discussion about previous use of epigenomic machine learning. https://github.com/shwhalen/targetfinder
- Xi, Wang, and Michael A Beer. “Local Epigenomic State Cannot Discriminate Interacting and Non-Interacting Enhancer-Promoter Pairs with High Accuracy,” October 25, 2018. https://doi.org/10.1101/420372. - Overfitting in epigenomics machine learning due to class imbalance. TargetFinder reanalysis. Gradient boosting, but not SVM, achieved good performance.

- Lu, Wei, Zhe Li, and Jinghui Chu. “Adaptive Ensemble Undersampling-Boost: A Novel Learning Framework for Imbalanced Data.” Journal of Systems and Software 132 (October 2017): 272–82. https://doi.org/10.1016/j.jss.2017.07.006. - Class imbalance problem, proposed the Ensemble of Undersampling (EUS) technique in combination with Real (in contrast to Discrete) Adaboost, cost-sensitive weighting, and adaptive boundary decision strategy. Introduction to the problem, references to existing methods. Tested on 18 datasets from KEEL repository, performance measured using AUC and other metrics.

- Dubey, Rashmi, Jiayu Zhou, Yalin Wang, Paul M. Thompson, Jieping Ye, and Alzheimer’s Disease Neuroimaging Initiative. “Analysis of Sampling Techniques for Imbalanced Data: An n = 648 ADNI Study.” NeuroImage 87 (February 15, 2014): 220–41. https://doi.org/10.1016/j.neuroimage.2013.10.005. - Class imbalance testing. Various sampling techniques (over-/undersampling, SMOTE), six feature selection algorithms, ensemble feature selection using RF and SVM. K-medoids undersampling is optimal. Description of existing approaches. Systematic framework to evaluate various combinations of F (feature selections algorithms) x S (set of class-imbalance handling approaches) x C ( classifiers). k-fold cross-validation to avoid bias due to random sampling.

- Blagus, Rok, and Lara Lusa. “SMOTE for High-Dimensional Class-Imbalanced Data.” BMC Bioinformatics 14, no. 1 (2013): 106. https://doi.org/10.1186/1471-2105-14-106. - SMOTE theoretical and empirical benchmarking. Inferior for high-dimensional data than undersampling. Class imbalance is most problematic in high-dimensional data. Variable reduction is needed before classification (ref 37).

- Lunardon, Nicola, Giovanna Menardi, and Nicola Torelli. “ROSE: A Package for Binary Imbalanced Learning.” R Journal 6, no. 1 (2014). - ROSE - R package for over-/undersampling. Menardi and Torelli reference to read. https://cran.r-project.org/web/packages/ROSE/index.html

- Zhang, Ruochi, Yuchuan Wang, Yang Yang, Yang Zhang, and Jian Ma. “Predicting CTCF-Mediated Chromatin Loops Using CTCF-MP.” Bioinformatics 34, no. 13 (July 1, 2018): i133–41. https://doi.org/10.1093/bioinformatics/bty248. - CTCF-MP - boosted tree classifier for loop prediction from sequence-level features (word2vec, deep autoencoder to compress the 200-dimensional space to 32 dimensions, then tSNE mapping to 2D), CTCF ChIP-seq and DNAse-seq data. Convergent CTCF sites are important. Best prediction of common loops, little worse cell-type-specific. Imbalanced dataset performed well. https://github.com/ma-compbio/CTCF-MP

- Wong, Kin Yau, Cheng Fan, Maki Tanioka, Joe S. Parker, Andrew B. Nobel, Donglin Zeng, Dan-Yu Lin, and Charles M. Perou. “An Integrative Boosting Approach for Predicting Survival Time With Multiple Genomics Platforms,” June 4, 2018. https://doi.org/10.1101/338145. - Survival analysis using integrative approach - multiple data types (clinical, gene/protein expression, gene signatures) and methods (LASSO, elastic net, boosting using cross-validation and permutation). Good example of presenting comparison of methods on a biological problem.

- Mayr, A., H. Binder, O. Gefeller, and M. Schmid. “The Evolution of Boosting Algorithms. From Machine Learning to Statistical Modelling.” Methods of Information in Medicine 53, no. 6 (2014): 419–27. https://doi.org/10.3414/ME13-01-0122. - Boosting, part 1. AdaBoost, algorithm, overfitting and resistance to it, connection to generalized additive model (GAM). Likelihood-based boosting. Early stopping as a way to prevent overfitting. R packages mboost, gbm, GAMBoost, CoxBoost

- Haibo He, Yang Bai, Edwardo A. Garcia, and Shutao Li. “ADASYN: Adaptive Synthetic Sampling Approach for Imbalanced Learning,” 1322–28. IEEE, 2008. https://doi.org/10.1109/IJCNN.2008.4633969. - ADASYN - adaptive synthetic sampling approach. Overview of current methodologies - sampling strategies, synthetic data generation (SMOTE), others. Comparison with others. Open question - how much imbalance hurt learning? Important - categorical variables are excluded. https://cran.r-project.org/web/packages/smotefamily/

- Turki, Turki, and Zhi Wei. “Boosting Support Vector Machines for Cancer Discrimination Tasks.” Computers in Biology and Medicine 101 (October 1, 2018): 236–49. https://doi.org/10.1016/j.compbiomed.2018.08.006. - Boosting SVM outperforms regular SVM and xgboost. Three versions of the algorithm. Tested on cancer datasets. An example which metrics to use for classifier performance evaluation, and how to describe and present the results in tables (figures are bad).

- Drummond, Chris, Robert C Holte, and others. “C4. 5, Class Imbalance, and Cost Sensitivity: Why under-Sampling Beats over-Sampling.” In Workshop on Learning from Imbalanced Datasets II, 11:1–8, 2003. - a reference demonstrating that undersampling is better than oversampling in class imbalance problem

- Bekkar, Mohamed, Hassiba Kheliouane Djemaa, and Taklit Akrouf Alitouche. “Evaluation Measures for Models Assessment over Imbalanced Datasets.” Iournal Of Information Engineering and Applications 3, no. 10 (2013). - Classifier performance metrics (G-means, likelihood ratios, Discriminant power, F-measure, Youden index, MCC, ROC, (P/W)AUC and more), and their behavior in class imbalance settings. MCC is considered the best metric for imbalanced data learning.

- Galar, M., A. Fernandez, E. Barrenechea, H. Bustince, and F. Herrera. “A Review on Ensembles for the Class Imbalance Problem: Bagging-, Boosting-, and Hybrid-Based Approaches.” IEEE Transactions on Systems, Man, and Cybernetics, Part C (Applications and Reviews) 42, no. 4 (July 2012): 463–84. https://doi.org/10.1109/TSMCC.2011.2161285. - Ensemble learning in class imbalance. Classifier metrics, from accuracy to AUROC. Three groups of approaches: algorithm-level (bias learning towards the minority class), data-level (resampling), cost-sensitive (mix). Resampling techniques also into three categories: RUS, ROS, SMOTE and variants, SPIDER. Overview of ensemble algorithms (Bagging, Boosting), classification of them to address class imbalance problem (Figure 3), description of each. Systematic experimental testing against C4.5 baseline using 44 KEEL datasets. SMOTEBagging, RUSBoost, UnderBagging are best.

- Lemaître, Guillaume, Fernando Nogueira, and Christos K. Aridas. “Imbalanced-Learn: A Python Toolbox to Tackle the Curse of Imbalanced Datasets in Machine Learning.” Journal of Machine Learning Research 18, no. 17 (2017): 1–5. http://jmlr.org/papers/v18/16-365. - imbalanced-learning Python package. 18 techniques, Table. The class imbalance problem has been encountered in multiple areas such as telecommu- nication managements, bioinformatics, fraud detection, and medical diagnosis, and has been considered one of the top 10 problems in data mining and pattern recognition (Yang and Wu, 2006; Rastgoo et al., 2016). https://github.com/scikit-learn-contrib/imbalanced-learn

- Wei, Qiong, and Roland L. Dunbrack. “The Role of Balanced Training and Testing Data Sets for Binary Classifiers in Bioinformatics.” Edited by Iddo Friedberg. PLoS ONE 8, no. 7 (July 9, 2013): e67863. https://doi.org/10.1371/journal.pone.0067863. - Training set should be balanced, tested set stays as-is, unbalanced.

## Misc

- Idea that TAD boundaries may not be created equal. Huang, Jialiang, Kailong Li, Wenqing Cai, Xin Liu, Yuannyu Zhang, Stuart H. Orkin, Jian Xu, and Guo-Cheng Yuan. “Dissecting Super-Enhancer Hierarchy Based on Chromatin Interactions.” Nature Communications 9, no. 1 (05 2018): 943. https://doi.org/10.1038/s41467-018-03279-9. - Enhancers can be separated into super- (SE) and regular (RE) enhancers, SE further classified into hub and nonhub based on Hi-C interaction frequency. ROSE to identify enhancers from H3K27ac peaks. Characterization of SEs  - broader. Characterization of hubs - enriched in CTCF, cohesin, disease-associated variants,

### 2019-03-12 Manuscript/Figures/figure_legends.Rmd
current

@@
 
-**Figure 1: Model Construction.** An illustration of the proposed model construction given cell line-specific Hi-C matrices obtained from [@rao20143d].
-The contact matrix above is a visualization of the interconnectivity of chromosome 14 (GM12878) on the intervals from 20 mb to 100 mb [@durand2016juicebox].
-The coordinates of subsequent topologically association domains were identified using the arrowhead algorithm from Juicer.
-The linear genome, represented by the diagonal of the contact matrix, was then binned according to prespecified interaction frequency resolutions (10 kb, 25 kb, 50 kb, and 100 kb).
-Each TAD coordinate was then flanked by a unit-specific amount (in basepairs) respective to the resolution of the corresponding contact matrix.
-The response vector Y, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region (Y=1) or not (Y=0).
+**Figure 1: Model Construction.** An illustration of the proposed model construction given cell line-specific Hi-C matrices.
+The contact matrix above is a visualization of the interconnectivity of chromosome 14 (GM12878 cell line, [???] resolution) on the intervals from 20 mb to 100 mb.
+The boundary coordinates of topologically association domains (TADs) were identified using the Arrowhead algorithm.
+To account for the uncertainty in TAD boundary detection, each boundary point was flanked on both sides by resolution-specific genomic regions (bins).
+The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region (Y=1) or not (Y=0).
 The spatial relationship between positional coordinates of various functional genomic annotations, obtained from ENCODE, and the genomic bins were then used to define the feature space of the models.

### 2019-03-12 Manuscript/manuscript.Rmd
current

@@
 All random forest algorithms were implemented in R using the `caret` package version 6.0 [@kuhn2012caret].
-Once the model was implemented, it was assessed using the test set, and performance metrics were then recorded.
+Once the model was implemented, it was assessed using the test set, and performance metrics were recorded.
 
@@
 
-We evaluated and compared multiple random forest classification algorithms built on domain data extracted from Hi-C datasets for 2 cell lines C = {GM12878, K562}, at 4 different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}.
-For each classifier, we compared 3 predictor types P = {OC, OP, Distance} and 5 class balancing techniques B = {None, RUS, ROS, SMOTE, ROSE}.
-A system produced from the ensemble framework was defined as: E = {c, r, p, b}, where $c \in C, \quad R \in R, \quad p \in P,$ and $b \in$ B.
-Letting |X| denote the cardinality of each set, we evaluated $|C| \times |R| \times |P| \times |B|$ different ensemble systems, totaling X (=$x \times 4 \times 3 \times 5$) separate models.
+We evaluated and compared multiple random forest classification algorithms built on domain data extracted from Hi-C datasets for 2 cell lines $C = {GM12878, K562}$, at four different resolutions $R = {10 kb, 25 kb, 50 kb, 100 kb}$.
+For each classifier, we compared three predictor types $P = {OC, OP, Distance}$ and five class balancing techniques $B = {None, RUS, ROS, SMOTE, ROSE}$.
+A system produced from the ensemble framework was defined as: $ = {c, r, p, b}$, where $c \in C, \quad R \in R, \quad p \in P,$ and $b \in B$.
+Letting $|X|$ denote the cardinality of each set, we evaluated $|C| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $X (= x \times 4 \times 3 \times 5)$ separate models.
 For each model, we aimed to assess both model performance and identify the genomic annotations that were most important in correctly labeling the genomic bins that overlapped with flanked TAD boundaries.
@@
 The correlations were visualized using correlograms for each data resolution and cell line (Supplementary Figure 2).
-The high correlations imply that many genomic annotations tended to colocalize near eachother at the boarders of domains.
+The high correlations imply that many genomic annotations tended to colocalize near each other at the boarders of domains.
 This was present across both resolution and cell line.
 Specifically, we found that the CTCF, Rad21, Smc3ab, and Znf143 transcription factor binding sites were highly colocalized near TAD boundaries.
-Likewise, many histone modifications also tended to appear near TAD boundaries in conjunction with one another including H3K4me1, H3K4me2, H3K4me3, H3K9ac, and H3K27ac.
-Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly correlated with on another, yet inversely correlated with many transcription factor binding sites.
+[???
+We need to quantify and show this, and the following colocalizations] Likewise, many histone modifications also tended to appear near TAD boundaries in conjunction with one another including H3K4me1, H3K4me2, H3K4me3, H3K9ac, and H3K27ac.
+Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly correlated, yet inversely correlated with many transcription factor binding sites.
 
@@
 Additionally, a unique predictor-type was included separately as the set of features.
-It was found that the elastic-net regularized the coefficients of far more distance-type predictors to 0 compared to datasets with overlap count and percent predictor types, regardless of cell line or data resolution (Supplementary Figure 3).
+It was found that the elastic-net regularized the coefficients of far more [???
+quantify] distance-type predictors to 0 compared to datasets with overlap count and percent predictor types, regardless of cell line or data resolution (Supplementary Figure 3).
 Many elastic-net models using overlap count or percent predictors were reduced to ridge, or near-ridge regression models at higher data resolutions by having the $alpha$ penalization term tuned to 0 in the cross-validation step, thereby not reducing, or reducing very few of the feature space.

### 2019-03-14 Scripts/evaluating_pca.Rmd
script for evaluating pca results

---
title: "Performing Cluster Analysis on TAD boundaries & Annotations"
author: "Spiro Stilianoudakis"
date: "March 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(factoextra)
library(FactoMineR)

```

# Boundaries as rows; Annotations as columns; clustering annotations

## GM12878

### 10kb

#### Overlap counts data

```{r}
pcadat_gm12878_10kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_count.rds")

#filtering low variance predictors
nzv <- nearZeroVar(pcadat_gm12878_10kb_count , saveMetrics= TRUE)
nzvar <- rownames(nzv[nzv$nzv,])
nzvar

pcadat_gm12878_10kb_count_f <- pcadat_gm12878_10kb_count[, -which(colnames(pcadat_gm12878_10kb_count) %in% nzvar)]

dim(pcadat_gm12878_10kb_count) 
dim(pcadat_gm12878_10kb_count_f) 
```

#### Distance data

```{r}
pcadat_gm12878_10kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_dist.rds")
```

### 2019-03-15 Scripts/evaluating_pca.Rmd
added script for results for counts and distances

@@
 
-# Boundaries as rows; Annotations as columns; clustering annotations
+# Clustering Annotations
 
@@
 pcadat_gm12878_10kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_count.rds")
+dim(pcadat_gm12878_10kb_count)
 
@@
 dim(pcadat_gm12878_10kb_count_f)
+
+colnames(pcadat_gm12878_10kb_count_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_count_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_gm12878_10kb_count_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_gm12878_10kb_count_f),
+          #rowsep=1:nrow(pcadat_gm12878_10kb_count_f),
+          keysize = 1)
+
+#PCA
+pca_gm12878_10kb_count <- prcomp(pcadat_gm12878_10kb_count_f, 
+                  scale = FALSE)
+
+##looking at the loadings
+pca_gm12878_10kb_count$rotation[1:5,1:5]
+
+##looking at the score vectors
+pca_gm12878_10kb_count$x[1:5,1:5]
+
+##screeplot
+###full
+std_dev <- pca_gm12878_10kb_count$sdev
+pr_var <- std_dev^2
+prop_varex <- pr_var/sum(pr_var)
+plot(prop_varex, xlab = "Principal Component",
+             ylab = "Proportion of Variance Explained",
+             type = "b")
+###top 10
+fviz_eig(pca_gm12878_10kb_count, addlabels = TRUE)
+
+##cumulative variance explained
+plot(cumsum(prop_varex), xlab = "Principal Component",
+     ylab = "Cumulative Proportion of Variance Explained",
+     ylim = c(0, 1), type = "b")
+
+##biplot
+biplot(pca_gm12878_10kb_count, scale = 0)
+
+##graph of the variables
+fviz_pca_var(pca_gm12878_10kb_count,
+             col.var = "contrib", # Color by contributions to the PC
+             gradient.cols = c("red", "white", "blue"),
+             repel = TRUE     # Avoid text overlapping
+             )
+
 ```
@@
 pcadat_gm12878_10kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_dist.rds")
+dim(pcadat_gm12878_10kb_dist)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_gm12878_10kb_dist , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_gm12878_10kb_dist_f <- pcadat_gm12878_10kb_dist[, -which(colnames(pcadat_gm12878_10kb_dist) %in% nzvar)]
+
+dim(pcadat_gm12878_10kb_dist) 
+dim(pcadat_gm12878_10kb_dist_f)
+
+colnames(pcadat_gm12878_10kb_dist_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_dist_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_gm12878_10kb_dist_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_gm12878_10kb_dist_f),
+          #rowsep=1:nrow(pcadat_gm12878_10kb_dist_f),
+          keysize = 1)
+
+#PCA
+pca_gm12878_10kb_dist <- prcomp(pcadat_gm12878_10kb_dist_f, 
+                  scale = FALSE)
+
+##looking at the loadings
+pca_gm12878_10kb_dist$rotation[1:5,1:5]
+
+##looking at the score vectors
+pca_gm12878_10kb_dist$x[1:5,1:5]
+
+##screeplot
+###full
+std_dev <- pca_gm12878_10kb_dist$sdev
+pr_var <- std_dev^2
+prop_varex <- pr_var/sum(pr_var)
+plot(prop_varex, xlab = "Principal Component",
+             ylab = "Proportion of Variance Explained",
+             type = "b")
+###top 10
+fviz_eig(pca_gm12878_10kb_dist, addlabels = TRUE)
+
+##cumulative variance explained
+plot(cumsum(prop_varex), xlab = "Principal Component",
+     ylab = "Cumulative Proportion of Variance Explained",
+     ylim = c(0, 1), type = "b")
+
+##biplot
+biplot(pca_gm12878_10kb_dist, scale = 0)
+
+##graph of the variables
+fviz_pca_var(pca_gm12878_10kb_dist,
+             col.var = "contrib", # Color by contributions to the PC
+             gradient.cols = c("red", "white", "blue"),
+             repel = TRUE     # Avoid text overlapping
+             )
+
 ```

### 2019-03-15 Scripts/evaluating_pca.Rmd
added to pca script

@@
 #PCA
-pca_gm12878_10kb_count <- prcomp(pcadat_gm12878_10kb_count_f, 
-                  scale = FALSE)
-
-##looking at the loadings
-pca_gm12878_10kb_count$rotation[1:5,1:5]
-
-##looking at the score vectors
-pca_gm12878_10kb_count$x[1:5,1:5]
-
-##screeplot
-###full
-std_dev <- pca_gm12878_10kb_count$sdev
-pr_var <- std_dev^2
-prop_varex <- pr_var/sum(pr_var)
-plot(prop_varex, xlab = "Principal Component",
-             ylab = "Proportion of Variance Explained",
-             type = "b")
-###top 10
-fviz_eig(pca_gm12878_10kb_count, addlabels = TRUE)
-
-##cumulative variance explained
-plot(cumsum(prop_varex), xlab = "Principal Component",
-     ylab = "Cumulative Proportion of Variance Explained",
-     ylim = c(0, 1), type = "b")
-
-##biplot
-biplot(pca_gm12878_10kb_count, scale = 0)
-
-##graph of the variables
-fviz_pca_var(pca_gm12878_10kb_count,
-             col.var = "contrib", # Color by contributions to the PC
-             gradient.cols = c("red", "white", "blue"),
-             repel = TRUE     # Avoid text overlapping
-             )
+pcadat_gm12878_10kb_count_f <- t(pcadat_gm12878_10kb_count_f)
+##with loadings
+autoplot(prcomp(pcadat_gm12878_10kb_count_f),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_10kb_count_f),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_10kb_count_f, 4),
+         data=pcadat_gm12878_10kb_count_f,
+         frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T) + 
+  theme_bw()
 
@@
 
+#performing log2 transformation
+pcadat_gm12878_10kb_dist <- apply(pcadat_gm12878_10kb_dist,2,function(x){log(x + 1, base=2)})
+
 #filtering low variance predictors
-nzv <- nearZeroVar(pcadat_gm12878_10kb_dist , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
+#nzv <- nearZeroVar(pcadat_gm12878_10kb_dist , saveMetrics= TRUE)
+#nzvar <- rownames(nzv[nzv$nzv,])
+#nzvar
+#no near zero variance predictors
 
 pcadat_gm12878_10kb_dist_f <- pcadat_gm12878_10kb_dist[, -which(colnames(pcadat_gm12878_10kb_dist) %in% nzvar)]
+pcadat_gm12878_10kb_dist_f <- pcadat_gm12878_10kb_dist
 
@@
 #PCA
-pca_gm12878_10kb_dist <- prcomp(pcadat_gm12878_10kb_dist_f, 
-                  scale = FALSE)
+pcadat_gm12878_10kb_dist_f <- t(pcadat_gm12878_10kb_dist_f)
+##with loadings
+autoplot(prcomp(pcadat_gm12878_10kb_dist_f),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_10kb_dist_f),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_10kb_dist_f, 5),
+         data=pcadat_gm12878_10kb_dist_f,
+         frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T) + 
+  theme_bw()
+```
 
-##looking at the loadings
-pca_gm12878_10kb_dist$rotation[1:5,1:5]
+## K562
 
-##looking at the score vectors
-pca_gm12878_10kb_dist$x[1:5,1:5]
+### 10kb
 
-##screeplot
-###full
-std_dev <- pca_gm12878_10kb_dist$sdev
-pr_var <- std_dev^2
-prop_varex <- pr_var/sum(pr_var)
-plot(prop_varex, xlab = "Principal Component",
-             ylab = "Proportion of Variance Explained",
-             type = "b")
-###top 10
-fviz_eig(pca_gm12878_10kb_dist, addlabels = TRUE)
+#### Overlap counts data
 
-##cumulative variance explained
-plot(cumsum(prop_varex), xlab = "Principal Component",
-     ylab = "Cumulative Proportion of Variance Explained",
-     ylim = c(0, 1), type = "b")
+```{r}
+pcadat_K562_10kb_count <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_K562_10kb_count.rds")
+dim(pcadat_K562_10kb_count)
 
-##biplot
-biplot(pca_gm12878_10kb_dist, scale = 0)
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_K562_10kb_count , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
 
-##graph of the variables
-fviz_pca_var(pca_gm12878_10kb_dist,
-             col.var = "contrib", # Color by contributions to the PC
-             gradient.cols = c("red", "white", "blue"),
-             repel = TRUE     # Avoid text overlapping
-             )
+pcadat_K562_10kb_count_f <- pcadat_K562_10kb_count[, -which(colnames(pcadat_K562_10kb_count) %in% nzvar)]
+
+dim(pcadat_K562_10kb_count) 
+dim(pcadat_K562_10kb_count_f)
+
+colnames(pcadat_K562_10kb_count_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_10kb_count_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_K562_10kb_count_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_K562_10kb_count_f),
+          #rowsep=1:nrow(pcadat_K562_10kb_count_f),
+          keysize = 1)
+
+#PCA
+pcadat_K562_10kb_count_f <- t(pcadat_K562_10kb_count_f)
+##with loadings
+autoplot(prcomp(pcadat_K562_10kb_count_f),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_10kb_count_f),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_K562_10kb_count_f, 4),
+         data=pcadat_K562_10kb_count_f,
+         frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T) + 
+  theme_bw()
 
 ```
+
+#### Distance data
+
+```{r}
+pcadat_K562_10kb_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_K562_10kb_dist.rds")
+dim(pcadat_K562_10kb_dist)
+
+#performing log2 transformation
+pcadat_K562_10kb_dist <- apply(pcadat_K562_10kb_dist,2,function(x){log(x + 1, base=2)})
+
+#filtering low variance predictors
+#nzv <- nearZeroVar(pcadat_K562_10kb_dist , saveMetrics= TRUE)
+#nzvar <- rownames(nzv[nzv$nzv,])
+#nzvar
+#no near zero variance predictors
+
+pcadat_K562_10kb_dist_f <- pcadat_K562_10kb_dist[, -which(colnames(pcadat_K562_10kb_dist) %in% nzvar)]
+pcadat_K562_10kb_dist_f <- pcadat_K562_10kb_dist
+
+dim(pcadat_K562_10kb_dist) 
+dim(pcadat_K562_10kb_dist_f)
+
+colnames(pcadat_K562_10kb_dist_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_10kb_dist_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_K562_10kb_dist_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_K562_10kb_dist_f),
+          #rowsep=1:nrow(pcadat_K562_10kb_dist_f),
+          keysize = 1)
+
+#PCA
+pcadat_K562_10kb_dist_f <- t(pcadat_K562_10kb_dist_f)
+##with loadings
+autoplot(prcomp(pcadat_K562_10kb_dist_f),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_10kb_dist_f),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_K562_10kb_dist_f, 4),
+         data=pcadat_K562_10kb_dist_f,
+         frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T) + 
+  theme_bw()
+```

### 2019-03-15 Scripts/evaluating_pca.Rmd
color coded pca plots by annotation group

@@
 
+##create annotation groups
+cs <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
+                 sep = "",
+                 collapse = "|"),
+           "", 
+           list.files("Z:/TAD_data_analysis/annotations/BroadHMM")))
+hm <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
+                 sep = "",
+                 collapse = "|"),
+           "", 
+           list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")))
+
 #PCA
 pcadat_gm12878_10kb_count_f <- t(pcadat_gm12878_10kb_count_f)
+
+Group <- ifelse(rownames(pcadat_gm12878_10kb_count_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_gm12878_10kb_count_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_gm12878_10kb_count_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_gm12878_10kb_count_f <- cbind.data.frame(pcadat_gm12878_10kb_count_f, Group)
 ##with loadings
-autoplot(prcomp(pcadat_gm12878_10kb_count_f),
+autoplot(prcomp(pcadat_gm12878_10kb_count_f[,-(dim(pcadat_gm12878_10kb_count_f2)[2])]),
          loadings = TRUE,
@@
          label.size = 3,
-         label.repel=T) +
+         label.repel=T,
+         data=pcadat_gm12878_10kb_count_f,
+         colour='Group') +
   theme_bw()
 ##without loadings
-autoplot(prcomp(pcadat_gm12878_10kb_count_f),
+autoplot(prcomp(pcadat_gm12878_10kb_count_f[,-(dim(pcadat_gm12878_10kb_count_f)[2])]),
          #loadings = TRUE,
@@
          label.size = 3,
-         label.repel=T) +
+         label.repel=T,
+         data=pcadat_gm12878_10kb_count_f,
+         colour='Group') +
   theme_bw()
@@
 set.seed(1)
-autoplot(kmeans(pcadat_gm12878_10kb_count_f, 4),
+autoplot(kmeans(pcadat_gm12878_10kb_count_f[,-(dim(pcadat_gm12878_10kb_count_f2)[2])], 4),
          data=pcadat_gm12878_10kb_count_f,
          frame = TRUE,
-         #frame.type = 'norm',
+         frame.type = 'norm',
          label = TRUE, 
          label.size = 3, 
+         #colour='Group',
          label.repel=T) + 
@@
 
+```
+
+#### Overlap percent data
+
+```{r}
+pcadat_gm12878_10kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_perc.rds")
+dim(pcadat_gm12878_10kb_perc)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_gm12878_10kb_perc , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_gm12878_10kb_perc_f <- pcadat_gm12878_10kb_perc[, -which(colnames(pcadat_gm12878_10kb_perc) %in% nzvar)]
+
+dim(pcadat_gm12878_10kb_perc) 
+dim(pcadat_gm12878_10kb_perc_f)
+
+colnames(pcadat_gm12878_10kb_perc_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "perc",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_perc_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_gm12878_10kb_perc_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_gm12878_10kb_perc_f),
+          #rowsep=1:nrow(pcadat_gm12878_10kb_perc_f),
+          keysize = 1)
+
+#PCA
+pcadat_gm12878_10kb_perc_f <- t(pcadat_gm12878_10kb_perc_f)
+
+Group <- ifelse(rownames(pcadat_gm12878_10kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_gm12878_10kb_perc_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_gm12878_10kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_gm12878_10kb_perc_f <- cbind.data.frame(pcadat_gm12878_10kb_perc_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_gm12878_10kb_perc_f[,-(dim(pcadat_gm12878_10kb_perc_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_10kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_10kb_perc_f[,-(dim(pcadat_gm12878_10kb_perc_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_10kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_10kb_perc_f[,-(dim(pcadat_gm12878_10kb_perc_f2)[2])], 4),
+         data=pcadat_gm12878_10kb_perc_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
 ```
@@
 pcadat_gm12878_10kb_dist_f <- t(pcadat_gm12878_10kb_dist_f)
+
+Group <- ifelse(rownames(pcadat_gm12878_10kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_gm12878_10kb_dist_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_gm12878_10kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_gm12878_10kb_dist_f <- cbind.data.frame(pcadat_gm12878_10kb_dist_f, Group)
 ##with loadings
-autoplot(prcomp(pcadat_gm12878_10kb_dist_f),
+autoplot(prcomp(pcadat_gm12878_10kb_dist_f[,-(dim(pcadat_gm12878_10kb_dist_f)[2])]),
          loadings = TRUE,
@@
          label.size = 3,
-         label.repel=T) +
+         label.repel=T,
+         data=pcadat_gm12878_10kb_dist_f,
+         colour='Group') +
   theme_bw()
 ##without loadings
-autoplot(prcomp(pcadat_gm12878_10kb_dist_f),
+autoplot(prcomp(pcadat_gm12878_10kb_dist_f[,-(dim(pcadat_gm12878_10kb_dist_f)[2])]),
          #loadings = TRUE,
@@
          label.size = 3,
-         label.repel=T) +
+         label.repel=T,
+         data=pcadat_gm12878_10kb_dist_f,
+         colour='Group') +
   theme_bw()
@@
 set.seed(1)
-autoplot(kmeans(pcadat_gm12878_10kb_dist_f, 5),
+autoplot(kmeans(pcadat_gm12878_10kb_dist_f[,-(dim(pcadat_gm12878_10kb_dist_f2)[2])], 4),
          data=pcadat_gm12878_10kb_dist_f,
          frame = TRUE,
-         #frame.type = 'norm',
+         frame.type = 'norm',
          label = TRUE, 
          label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+
+```
+
+### 25kb
+
+#### Overlap counts data
+
+```{r}
+pcadat_gm12878_25kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_count.rds")
+dim(pcadat_gm12878_25kb_count)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_gm12878_25kb_count , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_gm12878_25kb_count_f <- pcadat_gm12878_25kb_count[, -which(colnames(pcadat_gm12878_25kb_count) %in% nzvar)]
+
+dim(pcadat_gm12878_25kb_count) 
+dim(pcadat_gm12878_25kb_count_f)
+
+colnames(pcadat_gm12878_25kb_count_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_count_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_gm12878_25kb_count_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_gm12878_25kb_count_f),
+          #rowsep=1:nrow(pcadat_gm12878_25kb_count_f),
+          keysize = 1)
+
+#PCA
+pcadat_gm12878_25kb_count_f <- t(pcadat_gm12878_25kb_count_f)
+
+Group <- ifelse(rownames(pcadat_gm12878_25kb_count_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_gm12878_25kb_count_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_gm12878_25kb_count_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_gm12878_25kb_count_f <- cbind.data.frame(pcadat_gm12878_25kb_count_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_gm12878_25kb_count_f[,-(dim(pcadat_gm12878_25kb_count_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_25kb_count_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_25kb_count_f[,-(dim(pcadat_gm12878_25kb_count_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_25kb_count_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_25kb_count_f[,-(dim(pcadat_gm12878_25kb_count_f2)[2])], 4),
+         data=pcadat_gm12878_25kb_count_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+
+```
+
+#### Overlap percent data
+
+```{r}
+pcadat_gm12878_25kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_perc.rds")
+dim(pcadat_gm12878_25kb_perc)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_gm12878_25kb_perc , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_gm12878_25kb_perc_f <- pcadat_gm12878_25kb_perc[, -which(colnames(pcadat_gm12878_25kb_perc) %in% nzvar)]
+
+dim(pcadat_gm12878_25kb_perc) 
+dim(pcadat_gm12878_25kb_perc_f)
+
+colnames(pcadat_gm12878_25kb_perc_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "perc",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_perc_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_gm12878_25kb_perc_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_gm12878_25kb_perc_f),
+          #rowsep=1:nrow(pcadat_gm12878_25kb_perc_f),
+          keysize = 1)
+
+#PCA
+pcadat_gm12878_25kb_perc_f <- t(pcadat_gm12878_25kb_perc_f)
+
+Group <- ifelse(rownames(pcadat_gm12878_25kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_gm12878_25kb_perc_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_gm12878_25kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_gm12878_25kb_perc_f <- cbind.data.frame(pcadat_gm12878_25kb_perc_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_gm12878_25kb_perc_f[,-(dim(pcadat_gm12878_25kb_perc_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_25kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_25kb_perc_f[,-(dim(pcadat_gm12878_25kb_perc_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_25kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_25kb_perc_f[,-(dim(pcadat_gm12878_25kb_perc_f2)[2])], 4),
+         data=pcadat_gm12878_25kb_perc_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+
+```
+
+#### Distance data
+
+```{r}
+pcadat_gm12878_25kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_dist.rds")
+dim(pcadat_gm12878_25kb_dist)
+
+#performing log2 transformation
+pcadat_gm12878_25kb_dist <- apply(pcadat_gm12878_25kb_dist,2,function(x){log(x + 1, base=2)})
+
+#filtering low variance predictors
+#nzv <- nearZeroVar(pcadat_gm12878_25kb_dist , saveMetrics= TRUE)
+#nzvar <- rownames(nzv[nzv$nzv,])
+#nzvar
+#no near zero variance predictors
+
+pcadat_gm12878_25kb_dist_f <- pcadat_gm12878_25kb_dist[, -which(colnames(pcadat_gm12878_25kb_dist) %in% nzvar)]
+pcadat_gm12878_25kb_dist_f <- pcadat_gm12878_25kb_dist
+
+dim(pcadat_gm12878_25kb_dist) 
+dim(pcadat_gm12878_25kb_dist_f)
+
+colnames(pcadat_gm12878_25kb_dist_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_dist_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_gm12878_25kb_dist_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_gm12878_25kb_dist_f),
+          #rowsep=1:nrow(pcadat_gm12878_25kb_dist_f),
+          keysize = 1)
+
+#PCA
+pcadat_gm12878_25kb_dist_f <- t(pcadat_gm12878_25kb_dist_f)
+
+Group <- ifelse(rownames(pcadat_gm12878_25kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_gm12878_25kb_dist_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_gm12878_25kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_gm12878_25kb_dist_f <- cbind.data.frame(pcadat_gm12878_25kb_dist_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_gm12878_25kb_dist_f[,-(dim(pcadat_gm12878_25kb_dist_f)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_25kb_dist_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_25kb_dist_f[,-(dim(pcadat_gm12878_25kb_dist_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_25kb_dist_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_25kb_dist_f[,-(dim(pcadat_gm12878_25kb_dist_f2)[2])], 4),
+         data=pcadat_gm12878_25kb_dist_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+```
+
+### 50kb
+
+#### Overlap counts data
+
+```{r}
+pcadat_gm12878_50kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_count.rds")
+dim(pcadat_gm12878_50kb_count)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_gm12878_50kb_count , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_gm12878_50kb_count_f <- pcadat_gm12878_50kb_count[, -which(colnames(pcadat_gm12878_50kb_count) %in% nzvar)]
+
+dim(pcadat_gm12878_50kb_count) 
+dim(pcadat_gm12878_50kb_count_f)
+
+colnames(pcadat_gm12878_50kb_count_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_count_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_gm12878_50kb_count_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_gm12878_50kb_count_f),
+          #rowsep=1:nrow(pcadat_gm12878_50kb_count_f),
+          keysize = 1)
+
+#PCA
+pcadat_gm12878_50kb_count_f <- t(pcadat_gm12878_50kb_count_f)
+
+Group <- ifelse(rownames(pcadat_gm12878_50kb_count_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_gm12878_50kb_count_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_gm12878_50kb_count_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_gm12878_50kb_count_f <- cbind.data.frame(pcadat_gm12878_50kb_count_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_gm12878_50kb_count_f[,-(dim(pcadat_gm12878_50kb_count_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_50kb_count_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_50kb_count_f[,-(dim(pcadat_gm12878_50kb_count_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_50kb_count_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_50kb_count_f[,-(dim(pcadat_gm12878_50kb_count_f2)[2])], 4),
+         data=pcadat_gm12878_50kb_count_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+
+```
+
+#### Overlap percent data
+
+```{r}
+pcadat_gm12878_50kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_perc.rds")
+dim(pcadat_gm12878_50kb_perc)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_gm12878_50kb_perc , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_gm12878_50kb_perc_f <- pcadat_gm12878_50kb_perc[, -which(colnames(pcadat_gm12878_50kb_perc) %in% nzvar)]
+
+dim(pcadat_gm12878_50kb_perc) 
+dim(pcadat_gm12878_50kb_perc_f)
+
+colnames(pcadat_gm12878_50kb_perc_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "perc",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_perc_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_gm12878_50kb_perc_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_gm12878_50kb_perc_f),
+          #rowsep=1:nrow(pcadat_gm12878_50kb_perc_f),
+          keysize = 1)
+
+#PCA
+pcadat_gm12878_50kb_perc_f <- t(pcadat_gm12878_50kb_perc_f)
+
+Group <- ifelse(rownames(pcadat_gm12878_50kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_gm12878_50kb_perc_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_gm12878_50kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_gm12878_50kb_perc_f <- cbind.data.frame(pcadat_gm12878_50kb_perc_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_gm12878_50kb_perc_f[,-(dim(pcadat_gm12878_50kb_perc_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_50kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_50kb_perc_f[,-(dim(pcadat_gm12878_50kb_perc_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_50kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_50kb_perc_f[,-(dim(pcadat_gm12878_50kb_perc_f2)[2])], 4),
+         data=pcadat_gm12878_50kb_perc_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+```
+
+#### Distance data
+
+```{r}
+pcadat_gm12878_50kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_dist.rds")
+dim(pcadat_gm12878_50kb_dist)
+
+#performing log2 transformation
+pcadat_gm12878_50kb_dist <- apply(pcadat_gm12878_50kb_dist,2,function(x){log(x + 1, base=2)})
+
+#filtering low variance predictors
+#nzv <- nearZeroVar(pcadat_gm12878_50kb_dist , saveMetrics= TRUE)
+#nzvar <- rownames(nzv[nzv$nzv,])
+#nzvar
+#no near zero variance predictors
+
+pcadat_gm12878_50kb_dist_f <- pcadat_gm12878_50kb_dist[, -which(colnames(pcadat_gm12878_50kb_dist) %in% nzvar)]
+pcadat_gm12878_50kb_dist_f <- pcadat_gm12878_50kb_dist
+
+dim(pcadat_gm12878_50kb_dist) 
+dim(pcadat_gm12878_50kb_dist_f)
+
+colnames(pcadat_gm12878_50kb_dist_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_dist_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_gm12878_50kb_dist_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_gm12878_50kb_dist_f),
+          #rowsep=1:nrow(pcadat_gm12878_50kb_dist_f),
+          keysize = 1)
+
+#PCA
+pcadat_gm12878_50kb_dist_f <- t(pcadat_gm12878_50kb_dist_f)
+
+Group <- ifelse(rownames(pcadat_gm12878_50kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_gm12878_50kb_dist_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_gm12878_50kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_gm12878_50kb_dist_f <- cbind.data.frame(pcadat_gm12878_50kb_dist_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_gm12878_50kb_dist_f[,-(dim(pcadat_gm12878_50kb_dist_f)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_50kb_dist_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_50kb_dist_f[,-(dim(pcadat_gm12878_50kb_dist_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_50kb_dist_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_50kb_dist_f[,-(dim(pcadat_gm12878_50kb_dist_f2)[2])], 4),
+         data=pcadat_gm12878_50kb_dist_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+```
+
+### 100kb
+
+#### Overlap counts data
+
+```{r}
+pcadat_gm12878_100kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_count.rds")
+dim(pcadat_gm12878_100kb_count)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_gm12878_100kb_count , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_gm12878_100kb_count_f <- pcadat_gm12878_100kb_count[, -which(colnames(pcadat_gm12878_100kb_count) %in% nzvar)]
+
+dim(pcadat_gm12878_100kb_count) 
+dim(pcadat_gm12878_100kb_count_f)
+
+colnames(pcadat_gm12878_100kb_count_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_count_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_gm12878_100kb_count_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_gm12878_100kb_count_f),
+          #rowsep=1:nrow(pcadat_gm12878_100kb_count_f),
+          keysize = 1)
+
+#PCA
+pcadat_gm12878_100kb_count_f <- t(pcadat_gm12878_100kb_count_f)
+
+Group <- ifelse(rownames(pcadat_gm12878_100kb_count_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_gm12878_100kb_count_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_gm12878_100kb_count_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_gm12878_100kb_count_f <- cbind.data.frame(pcadat_gm12878_100kb_count_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_gm12878_100kb_count_f[,-(dim(pcadat_gm12878_100kb_count_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_100kb_count_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_100kb_count_f[,-(dim(pcadat_gm12878_100kb_count_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_100kb_count_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_100kb_count_f[,-(dim(pcadat_gm12878_100kb_count_f2)[2])], 4),
+         data=pcadat_gm12878_100kb_count_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+
+```
+
+#### Overlap percent data
+
+```{r}
+pcadat_gm12878_100kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_perc.rds")
+dim(pcadat_gm12878_100kb_perc)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_gm12878_100kb_perc , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_gm12878_100kb_perc_f <- pcadat_gm12878_100kb_perc[, -which(colnames(pcadat_gm12878_100kb_perc) %in% nzvar)]
+
+dim(pcadat_gm12878_100kb_perc) 
+dim(pcadat_gm12878_100kb_perc_f)
+
+colnames(pcadat_gm12878_100kb_perc_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "perc",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_perc_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_gm12878_100kb_perc_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_gm12878_100kb_perc_f),
+          #rowsep=1:nrow(pcadat_gm12878_100kb_perc_f),
+          keysize = 1)
+
+#PCA
+pcadat_gm12878_100kb_perc_f <- t(pcadat_gm12878_100kb_perc_f)
+
+Group <- ifelse(rownames(pcadat_gm12878_100kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_gm12878_100kb_perc_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_gm12878_100kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_gm12878_100kb_perc_f <- cbind.data.frame(pcadat_gm12878_100kb_perc_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_gm12878_100kb_perc_f[,-(dim(pcadat_gm12878_100kb_perc_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_100kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_100kb_perc_f[,-(dim(pcadat_gm12878_100kb_perc_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_100kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_100kb_perc_f[,-(dim(pcadat_gm12878_100kb_perc_f2)[2])], 4),
+         data=pcadat_gm12878_100kb_perc_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+
+```
+
+#### Distance data
+
+```{r}
+pcadat_gm12878_100kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_dist.rds")
+dim(pcadat_gm12878_100kb_dist)
+
+#performing log2 transformation
+pcadat_gm12878_100kb_dist <- apply(pcadat_gm12878_100kb_dist,2,function(x){log(x + 1, base=2)})
+
+#filtering low variance predictors
+#nzv <- nearZeroVar(pcadat_gm12878_100kb_dist , saveMetrics= TRUE)
+#nzvar <- rownames(nzv[nzv$nzv,])
+#nzvar
+#no near zero variance predictors
+
+pcadat_gm12878_100kb_dist_f <- pcadat_gm12878_100kb_dist[, -which(colnames(pcadat_gm12878_100kb_dist) %in% nzvar)]
+pcadat_gm12878_100kb_dist_f <- pcadat_gm12878_100kb_dist
+
+dim(pcadat_gm12878_100kb_dist) 
+dim(pcadat_gm12878_100kb_dist_f)
+
+colnames(pcadat_gm12878_100kb_dist_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_dist_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_gm12878_100kb_dist_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_gm12878_100kb_dist_f),
+          #rowsep=1:nrow(pcadat_gm12878_100kb_dist_f),
+          keysize = 1)
+
+#PCA
+pcadat_gm12878_100kb_dist_f <- t(pcadat_gm12878_100kb_dist_f)
+
+Group <- ifelse(rownames(pcadat_gm12878_100kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_gm12878_100kb_dist_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_gm12878_100kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_gm12878_100kb_dist_f <- cbind.data.frame(pcadat_gm12878_100kb_dist_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_gm12878_100kb_dist_f[,-(dim(pcadat_gm12878_100kb_dist_f)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_100kb_dist_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_100kb_dist_f[,-(dim(pcadat_gm12878_100kb_dist_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_gm12878_100kb_dist_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_100kb_dist_f[,-(dim(pcadat_gm12878_100kb_dist_f2)[2])], 4),
+         data=pcadat_gm12878_100kb_dist_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
          label.repel=T) + 
@@
 
+##create annotation groups
+cs <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
+                 sep = "",
+                 collapse = "|"),
+           "", 
+           list.files("Z:/TAD_data_analysis/annotations/BroadHMM")))
+hm <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
+                 sep = "",
+                 collapse = "|"),
+           "", 
+           list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")))
+
 #PCA
 pcadat_K562_10kb_count_f <- t(pcadat_K562_10kb_count_f)
+
+Group <- ifelse(rownames(pcadat_K562_10kb_count_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_K562_10kb_count_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_K562_10kb_count_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_K562_10kb_count_f <- cbind.data.frame(pcadat_K562_10kb_count_f, Group)
 ##with loadings
-autoplot(prcomp(pcadat_K562_10kb_count_f),
+autoplot(prcomp(pcadat_K562_10kb_count_f[,-(dim(pcadat_K562_10kb_count_f2)[2])]),
          loadings = TRUE,
@@
          label.size = 3,
-         label.repel=T) +
+         label.repel=T,
+         data=pcadat_K562_10kb_count_f,
+         colour='Group') +
   theme_bw()
 ##without loadings
-autoplot(prcomp(pcadat_K562_10kb_count_f),
+autoplot(prcomp(pcadat_K562_10kb_count_f[,-(dim(pcadat_K562_10kb_count_f)[2])]),
          #loadings = TRUE,
@@
          label.size = 3,
-         label.repel=T) +
+         label.repel=T,
+         data=pcadat_K562_10kb_count_f,
+         colour='Group') +
   theme_bw()
@@
 set.seed(1)
-autoplot(kmeans(pcadat_K562_10kb_count_f, 4),
+autoplot(kmeans(pcadat_K562_10kb_count_f[,-(dim(pcadat_K562_10kb_count_f2)[2])], 4),
          data=pcadat_K562_10kb_count_f,
          frame = TRUE,
-         #frame.type = 'norm',
+         frame.type = 'norm',
          label = TRUE, 
          label.size = 3, 
+         #colour='Group',
          label.repel=T) + 
@@
 
+```
+
+#### Overlap percent data
+
+```{r}
+pcadat_K562_10kb_perc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_K562_10kb_perc.rds")
+dim(pcadat_K562_10kb_perc)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_K562_10kb_perc , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_K562_10kb_perc_f <- pcadat_K562_10kb_perc[, -which(colnames(pcadat_K562_10kb_perc) %in% nzvar)]
+
+dim(pcadat_K562_10kb_perc) 
+dim(pcadat_K562_10kb_perc_f)
+
+colnames(pcadat_K562_10kb_perc_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "perc",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_10kb_perc_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_K562_10kb_perc_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_K562_10kb_perc_f),
+          #rowsep=1:nrow(pcadat_K562_10kb_perc_f),
+          keysize = 1)
+
+#PCA
+pcadat_K562_10kb_perc_f <- t(pcadat_K562_10kb_perc_f)
+
+Group <- ifelse(rownames(pcadat_K562_10kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_K562_10kb_perc_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_K562_10kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_K562_10kb_perc_f <- cbind.data.frame(pcadat_K562_10kb_perc_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_K562_10kb_perc_f[,-(dim(pcadat_K562_10kb_perc_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_10kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_10kb_perc_f[,-(dim(pcadat_K562_10kb_perc_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_10kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_K562_10kb_perc_f[,-(dim(pcadat_K562_10kb_perc_f2)[2])], 4),
+         data=pcadat_K562_10kb_perc_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
 ```
@@
 pcadat_K562_10kb_dist_f <- t(pcadat_K562_10kb_dist_f)
+
+Group <- ifelse(rownames(pcadat_K562_10kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_K562_10kb_dist_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_K562_10kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_K562_10kb_dist_f <- cbind.data.frame(pcadat_K562_10kb_dist_f, Group)
 ##with loadings
-autoplot(prcomp(pcadat_K562_10kb_dist_f),
+autoplot(prcomp(pcadat_K562_10kb_dist_f[,-(dim(pcadat_K562_10kb_dist_f)[2])]),
          loadings = TRUE,
@@
          label.size = 3,
-         label.repel=T) +
+         label.repel=T,
+         data=pcadat_K562_10kb_dist_f,
+         colour='Group') +
   theme_bw()
 ##without loadings
-autoplot(prcomp(pcadat_K562_10kb_dist_f),
+autoplot(prcomp(pcadat_K562_10kb_dist_f[,-(dim(pcadat_K562_10kb_dist_f)[2])]),
          #loadings = TRUE,
@@
          label.size = 3,
-         label.repel=T) +
+         label.repel=T,
+         data=pcadat_K562_10kb_dist_f,
+         colour='Group') +
   theme_bw()
@@
 set.seed(1)
-autoplot(kmeans(pcadat_K562_10kb_dist_f, 4),
+autoplot(kmeans(pcadat_K562_10kb_dist_f[,-(dim(pcadat_K562_10kb_dist_f2)[2])], 4),
          data=pcadat_K562_10kb_dist_f,
          frame = TRUE,
-         #frame.type = 'norm',
+         frame.type = 'norm',
          label = TRUE, 
          label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+
+```
+
+### 25kb
+
+#### Overlap counts data
+
+```{r}
+pcadat_K562_25kb_count <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/PCA/pcadat_K562_25kb_count.rds")
+dim(pcadat_K562_25kb_count)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_K562_25kb_count , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_K562_25kb_count_f <- pcadat_K562_25kb_count[, -which(colnames(pcadat_K562_25kb_count) %in% nzvar)]
+
+dim(pcadat_K562_25kb_count) 
+dim(pcadat_K562_25kb_count_f)
+
+colnames(pcadat_K562_25kb_count_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_25kb_count_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_K562_25kb_count_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_K562_25kb_count_f),
+          #rowsep=1:nrow(pcadat_K562_25kb_count_f),
+          keysize = 1)
+
+#PCA
+pcadat_K562_25kb_count_f <- t(pcadat_K562_25kb_count_f)
+
+Group <- ifelse(rownames(pcadat_K562_25kb_count_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_K562_25kb_count_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_K562_25kb_count_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_K562_25kb_count_f <- cbind.data.frame(pcadat_K562_25kb_count_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_K562_25kb_count_f[,-(dim(pcadat_K562_25kb_count_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_25kb_count_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_25kb_count_f[,-(dim(pcadat_K562_25kb_count_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_25kb_count_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_K562_25kb_count_f[,-(dim(pcadat_K562_25kb_count_f2)[2])], 4),
+         data=pcadat_K562_25kb_count_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+
+```
+
+#### Overlap percent data
+
+```{r}
+pcadat_K562_25kb_perc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/PCA/pcadat_K562_25kb_perc.rds")
+dim(pcadat_K562_25kb_perc)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_K562_25kb_perc , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_K562_25kb_perc_f <- pcadat_K562_25kb_perc[, -which(colnames(pcadat_K562_25kb_perc) %in% nzvar)]
+
+dim(pcadat_K562_25kb_perc) 
+dim(pcadat_K562_25kb_perc_f)
+
+colnames(pcadat_K562_25kb_perc_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "perc",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_25kb_perc_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_K562_25kb_perc_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_K562_25kb_perc_f),
+          #rowsep=1:nrow(pcadat_K562_25kb_perc_f),
+          keysize = 1)
+
+#PCA
+pcadat_K562_25kb_perc_f <- t(pcadat_K562_25kb_perc_f)
+
+Group <- ifelse(rownames(pcadat_K562_25kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_K562_25kb_perc_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_K562_25kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_K562_25kb_perc_f <- cbind.data.frame(pcadat_K562_25kb_perc_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_K562_25kb_perc_f[,-(dim(pcadat_K562_25kb_perc_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_25kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_25kb_perc_f[,-(dim(pcadat_K562_25kb_perc_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_25kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_K562_25kb_perc_f[,-(dim(pcadat_K562_25kb_perc_f2)[2])], 4),
+         data=pcadat_K562_25kb_perc_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+
+```
+
+#### Distance data
+
+```{r}
+pcadat_K562_25kb_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/PCA/pcadat_K562_25kb_dist.rds")
+dim(pcadat_K562_25kb_dist)
+
+#performing log2 transformation
+pcadat_K562_25kb_dist <- apply(pcadat_K562_25kb_dist,2,function(x){log(x + 1, base=2)})
+
+#filtering low variance predictors
+#nzv <- nearZeroVar(pcadat_K562_25kb_dist , saveMetrics= TRUE)
+#nzvar <- rownames(nzv[nzv$nzv,])
+#nzvar
+#no near zero variance predictors
+
+pcadat_K562_25kb_dist_f <- pcadat_K562_25kb_dist[, -which(colnames(pcadat_K562_25kb_dist) %in% nzvar)]
+pcadat_K562_25kb_dist_f <- pcadat_K562_25kb_dist
+
+dim(pcadat_K562_25kb_dist) 
+dim(pcadat_K562_25kb_dist_f)
+
+colnames(pcadat_K562_25kb_dist_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_25kb_dist_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_K562_25kb_dist_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_K562_25kb_dist_f),
+          #rowsep=1:nrow(pcadat_K562_25kb_dist_f),
+          keysize = 1)
+
+#PCA
+pcadat_K562_25kb_dist_f <- t(pcadat_K562_25kb_dist_f)
+
+Group <- ifelse(rownames(pcadat_K562_25kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_K562_25kb_dist_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_K562_25kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_K562_25kb_dist_f <- cbind.data.frame(pcadat_K562_25kb_dist_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_K562_25kb_dist_f[,-(dim(pcadat_K562_25kb_dist_f)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_25kb_dist_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_25kb_dist_f[,-(dim(pcadat_K562_25kb_dist_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_25kb_dist_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_K562_25kb_dist_f[,-(dim(pcadat_K562_25kb_dist_f2)[2])], 4),
+         data=pcadat_K562_25kb_dist_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
          label.repel=T) + 
@@
 ```
+
+### 50kb
+
+#### Overlap counts data
+
+```{r}
+pcadat_K562_50kb_count <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/PCA/pcadat_K562_50kb_count.rds")
+dim(pcadat_K562_50kb_count)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_K562_50kb_count , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_K562_50kb_count_f <- pcadat_K562_50kb_count[, -which(colnames(pcadat_K562_50kb_count) %in% nzvar)]
+
+dim(pcadat_K562_50kb_count) 
+dim(pcadat_K562_50kb_count_f)
+
+colnames(pcadat_K562_50kb_count_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_50kb_count_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_K562_50kb_count_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_K562_50kb_count_f),
+          #rowsep=1:nrow(pcadat_K562_50kb_count_f),
+          keysize = 1)
+
+#PCA
+pcadat_K562_50kb_count_f <- t(pcadat_K562_50kb_count_f)
+
+Group <- ifelse(rownames(pcadat_K562_50kb_count_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_K562_50kb_count_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_K562_50kb_count_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_K562_50kb_count_f <- cbind.data.frame(pcadat_K562_50kb_count_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_K562_50kb_count_f[,-(dim(pcadat_K562_50kb_count_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_50kb_count_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_50kb_count_f[,-(dim(pcadat_K562_50kb_count_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_50kb_count_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_K562_50kb_count_f[,-(dim(pcadat_K562_50kb_count_f2)[2])], 4),
+         data=pcadat_K562_50kb_count_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+
+```
+
+#### Overlap percent data
+
+```{r}
+pcadat_K562_50kb_perc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/PCA/pcadat_K562_50kb_perc.rds")
+dim(pcadat_K562_50kb_perc)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_K562_50kb_perc , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_K562_50kb_perc_f <- pcadat_K562_50kb_perc[, -which(colnames(pcadat_K562_50kb_perc) %in% nzvar)]
+
+dim(pcadat_K562_50kb_perc) 
+dim(pcadat_K562_50kb_perc_f)
+
+colnames(pcadat_K562_50kb_perc_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "perc",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_50kb_perc_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_K562_50kb_perc_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_K562_50kb_perc_f),
+          #rowsep=1:nrow(pcadat_K562_50kb_perc_f),
+          keysize = 1)
+
+#PCA
+pcadat_K562_50kb_perc_f <- t(pcadat_K562_50kb_perc_f)
+
+Group <- ifelse(rownames(pcadat_K562_50kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_K562_50kb_perc_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_K562_50kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_K562_50kb_perc_f <- cbind.data.frame(pcadat_K562_50kb_perc_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_K562_50kb_perc_f[,-(dim(pcadat_K562_50kb_perc_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_50kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_50kb_perc_f[,-(dim(pcadat_K562_50kb_perc_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_50kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_K562_50kb_perc_f[,-(dim(pcadat_K562_50kb_perc_f2)[2])], 4),
+         data=pcadat_K562_50kb_perc_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+```
+
+#### Distance data
+
+```{r}
+pcadat_K562_50kb_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/PCA/pcadat_K562_50kb_dist.rds")
+dim(pcadat_K562_50kb_dist)
+
+#performing log2 transformation
+pcadat_K562_50kb_dist <- apply(pcadat_K562_50kb_dist,2,function(x){log(x + 1, base=2)})
+
+#filtering low variance predictors
+#nzv <- nearZeroVar(pcadat_K562_50kb_dist , saveMetrics= TRUE)
+#nzvar <- rownames(nzv[nzv$nzv,])
+#nzvar
+#no near zero variance predictors
+
+pcadat_K562_50kb_dist_f <- pcadat_K562_50kb_dist[, -which(colnames(pcadat_K562_50kb_dist) %in% nzvar)]
+pcadat_K562_50kb_dist_f <- pcadat_K562_50kb_dist
+
+dim(pcadat_K562_50kb_dist) 
+dim(pcadat_K562_50kb_dist_f)
+
+colnames(pcadat_K562_50kb_dist_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_50kb_dist_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_K562_50kb_dist_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_K562_50kb_dist_f),
+          #rowsep=1:nrow(pcadat_K562_50kb_dist_f),
+          keysize = 1)
+
+#PCA
+pcadat_K562_50kb_dist_f <- t(pcadat_K562_50kb_dist_f)
+
+Group <- ifelse(rownames(pcadat_K562_50kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_K562_50kb_dist_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_K562_50kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_K562_50kb_dist_f <- cbind.data.frame(pcadat_K562_50kb_dist_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_K562_50kb_dist_f[,-(dim(pcadat_K562_50kb_dist_f)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_50kb_dist_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_50kb_dist_f[,-(dim(pcadat_K562_50kb_dist_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_50kb_dist_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_K562_50kb_dist_f[,-(dim(pcadat_K562_50kb_dist_f2)[2])], 4),
+         data=pcadat_K562_50kb_dist_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+```
+
+### 100kb
+
+#### Overlap counts data
+
+```{r}
+pcadat_K562_100kb_count <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/PCA/pcadat_K562_100kb_count.rds")
+dim(pcadat_K562_100kb_count)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_K562_100kb_count , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_K562_100kb_count_f <- pcadat_K562_100kb_count[, -which(colnames(pcadat_K562_100kb_count) %in% nzvar)]
+
+dim(pcadat_K562_100kb_count) 
+dim(pcadat_K562_100kb_count_f)
+
+colnames(pcadat_K562_100kb_count_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_100kb_count_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_K562_100kb_count_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_K562_100kb_count_f),
+          #rowsep=1:nrow(pcadat_K562_100kb_count_f),
+          keysize = 1)
+
+#PCA
+pcadat_K562_100kb_count_f <- t(pcadat_K562_100kb_count_f)
+
+Group <- ifelse(rownames(pcadat_K562_100kb_count_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_K562_100kb_count_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_K562_100kb_count_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_K562_100kb_count_f <- cbind.data.frame(pcadat_K562_100kb_count_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_K562_100kb_count_f[,-(dim(pcadat_K562_100kb_count_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_100kb_count_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_100kb_count_f[,-(dim(pcadat_K562_100kb_count_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_100kb_count_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_K562_100kb_count_f[,-(dim(pcadat_K562_100kb_count_f2)[2])], 4),
+         data=pcadat_K562_100kb_count_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+
+```
+
+#### Overlap percent data
+
+```{r}
+pcadat_K562_100kb_perc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/PCA/pcadat_K562_100kb_perc.rds")
+dim(pcadat_K562_100kb_perc)
+
+#filtering low variance predictors
+nzv <- nearZeroVar(pcadat_K562_100kb_perc , saveMetrics= TRUE)
+nzvar <- rownames(nzv[nzv$nzv,])
+nzvar
+
+pcadat_K562_100kb_perc_f <- pcadat_K562_100kb_perc[, -which(colnames(pcadat_K562_100kb_perc) %in% nzvar)]
+
+dim(pcadat_K562_100kb_perc) 
+dim(pcadat_K562_100kb_perc_f)
+
+colnames(pcadat_K562_100kb_perc_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "perc",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_100kb_perc_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_K562_100kb_perc_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_K562_100kb_perc_f),
+          #rowsep=1:nrow(pcadat_K562_100kb_perc_f),
+          keysize = 1)
+
+#PCA
+pcadat_K562_100kb_perc_f <- t(pcadat_K562_100kb_perc_f)
+
+Group <- ifelse(rownames(pcadat_K562_100kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_K562_100kb_perc_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_K562_100kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_K562_100kb_perc_f <- cbind.data.frame(pcadat_K562_100kb_perc_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_K562_100kb_perc_f[,-(dim(pcadat_K562_100kb_perc_f2)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_100kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_100kb_perc_f[,-(dim(pcadat_K562_100kb_perc_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_100kb_perc_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_K562_100kb_perc_f[,-(dim(pcadat_K562_100kb_perc_f2)[2])], 4),
+         data=pcadat_K562_100kb_perc_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+
+```
+
+#### Distance data
+
+```{r}
+pcadat_K562_100kb_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/PCA/pcadat_K562_100kb_dist.rds")
+dim(pcadat_K562_100kb_dist)
+
+#performing log2 transformation
+pcadat_K562_100kb_dist <- apply(pcadat_K562_100kb_dist,2,function(x){log(x + 1, base=2)})
+
+#filtering low variance predictors
+#nzv <- nearZeroVar(pcadat_K562_100kb_dist , saveMetrics= TRUE)
+#nzvar <- rownames(nzv[nzv$nzv,])
+#nzvar
+#no near zero variance predictors
+
+pcadat_K562_100kb_dist_f <- pcadat_K562_100kb_dist[, -which(colnames(pcadat_K562_100kb_dist) %in% nzvar)]
+pcadat_K562_100kb_dist_f <- pcadat_K562_100kb_dist
+
+dim(pcadat_K562_100kb_dist) 
+dim(pcadat_K562_100kb_dist_f)
+
+colnames(pcadat_K562_100kb_dist_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_100kb_dist_f))
+
+#heatmap 
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+heatmap.2(pcadat_K562_100kb_dist_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadat_K562_100kb_dist_f),
+          #rowsep=1:nrow(pcadat_K562_100kb_dist_f),
+          keysize = 1)
+
+#PCA
+pcadat_K562_100kb_dist_f <- t(pcadat_K562_100kb_dist_f)
+
+Group <- ifelse(rownames(pcadat_K562_100kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadat_K562_100kb_dist_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadat_K562_100kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+
+pcadat_K562_100kb_dist_f <- cbind.data.frame(pcadat_K562_100kb_dist_f, Group)
+##with loadings
+autoplot(prcomp(pcadat_K562_100kb_dist_f[,-(dim(pcadat_K562_100kb_dist_f)[2])]),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_100kb_dist_f,
+         colour='Group') +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_100kb_dist_f[,-(dim(pcadat_K562_100kb_dist_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadat_K562_100kb_dist_f,
+         colour='Group') +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+set.seed(1)
+autoplot(kmeans(pcadat_K562_100kb_dist_f[,-(dim(pcadat_K562_100kb_dist_f2)[2])], 4),
+         data=pcadat_K562_100kb_dist_f,
+         frame = TRUE,
+         frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         #colour='Group',
+         label.repel=T) + 
+  theme_bw()
+```
+
+## Saving plots
+
+```{r}
+
+```

### 2019-03-15 Scripts/evaluating_pca.Rmd
added loop to save plots

@@
 ```{r}
-
-```
+fileslst <- c(paste("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_GM12878_", 
+                    c("10kb", "25kb", "50kb", "100kb"), 
+                    "_count.rds",sep=""),
+              paste("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_GM12878_", 
+                    c("10kb", "25kb", "50kb", "100kb"), 
+                    "_perc.rds",sep=""),
+              paste("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_GM12878_", 
+                    c("10kb", "25kb", "50kb", "100kb"), 
+                    "_dist.rds",sep=""),
+              paste("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_GM12878_", 
+                    c("10kb", "25kb", "50kb", "100kb"), 
+                    "_count.rds",sep=""),
+              paste("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_GM12878_", 
+                    c("10kb", "25kb", "50kb", "100kb"), 
+                    "_perc.rds",sep=""),
+              paste("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_GM12878_", 
+                    c("10kb", "25kb", "50kb", "100kb"), 
+                    "_dist.rds",sep=""))
+
+#file names for heatmaps
+heatnames <- c(paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_heatmap.png", sep=""),
+               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_heatmap.png", sep=""),
+               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_heatmap.png", sep=""),
+               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_heatmap.png", sep=""),
+               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_heatmap.png", sep=""),
+               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_heatmap.png", sep=""))
+
+#file names for pca plots
+scorepnames <- c(paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_scoreplots.png", sep=""),
+               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_scoreplots.png", sep=""),
+               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_scoreplots.png", sep=""),
+               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_scoreplots.png", sep=""),
+               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_scoreplots.png", sep=""),
+               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_scoreplots.png", sep=""))
+
+##create annotation groups
+cs <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
+                 sep = "",
+                 collapse = "|"),
+           "", 
+           list.files("Z:/TAD_data_analysis/annotations/BroadHMM")))
+hm <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
+                 sep = "",
+                 collapse = "|"),
+           "", 
+           list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")))
+
+for(i in 1:length(fileslst)){
+  pcadata <- readRDS(fileslst[i])
+
+  #performing log2 transformation only for distance predictor types
+  if(grepl("_dist", colnames(pcadata)[1])){
+    pcadata <- apply(pcadata,2,function(x){log(x + 1, base=2)})
+  }
+
+  #filtering low variance predictors
+  nzv <- nearZeroVar(pcadata, saveMetrics= TRUE)
+  nzvar <- rownames(nzv[nzv$nzv,])
+  if(length(nzvar) > 0){ 
+    pcadata_f <- pcadata[, -which(colnames(pcadata) %in% nzvar)]
+    }
+
+  #cleaning column names
+  colnames(pcadata_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadata_f))
+
+  #heatmap 
+  #my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+  #png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", heatnames[i], sep=""),
+  #    width=11, height=8, units="in")
+  #heatmap.2(pcadata_f,
+  #        #cellnote = ,  # same data set for cell labels
+  #        #main = "", # heat map title
+  #        notecol="black",      # change font color of cell labels to black
+  #        density.info="none",  # turns off density plot inside color legend
+  #        trace="none",         # turns off trace lines inside the heat map
+  #        #margins =c(5,5),     # widens margins around plot
+  #        col=my_palette,       # use on color palette defined earlier
+  #        #na.color = "gray",
+  #        #breaks=col_breaks,    # enable color transition at specified limits
+  #        key=TRUE,
+  #        dendrogram="column",     # only draw a row dendrogram
+  #        cexRow=0.5,
+  #        cexCol=0.5,
+  #        labRow = FALSE,
+  #        #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+  #        #lhei=c(.5,6,0),
+  #        #sepwidth=c(0.001,0.001),
+  #        #sepcolor="black",
+  #        #colsep=1:ncol(pcadata_f),
+  #        #rowsep=1:nrow(pcadata_f),
+  #        keysize = 1) 
+  #dev.off()
+
+  #PCA
+  pcadata_f <- t(pcadata_f)
+  Group <- ifelse(rownames(pcadata_f) %in% cs, "Chromatin State", ###chromatin states
+                                            ifelse(rownames(pcadata_f)=="DNase", "DNase I", ###dnase
+                                                   ifelse(rownames(pcadata_f) %in% hm, "Histone Modification", ###histone modifications
+                                                          "TFBS"))) ###transcription factor binding sites
+  pcadata_f <- cbind.data.frame(pcadata_f, Group)
+
+  ##Plots without loadings
+  p <- autoplot(prcomp(pcadata_f[,-(dim(pcadata_f)[2])]),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T,
+         data=pcadata_f,
+         colour='Group') +
+  theme_bw()
+
+  ggsave(p, filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", 
+                             scorepnames[i], sep=""),
+         width=8, height=11, units="in", dpi=300)
+
+}
+
+```

### 2019-03-15 Scripts/evaluating_pca.Rmd
fixed code to save plots in loop

@@
 ```{r}
-fileslst <- c(paste("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_GM12878_", 
+fileslst <- c(paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"), "/Ensemble/PCA/pcadat_GM12878_", 
                     c("10kb", "25kb", "50kb", "100kb"), 
                     "_count.rds",sep=""),
-              paste("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_GM12878_", 
+              paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
                     c("10kb", "25kb", "50kb", "100kb"), 
                     "_perc.rds",sep=""),
-              paste("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_GM12878_", 
+              paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
                     c("10kb", "25kb", "50kb", "100kb"), 
                     "_dist.rds",sep=""),
-              paste("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_GM12878_", 
+              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
                     c("10kb", "25kb", "50kb", "100kb"), 
                     "_count.rds",sep=""),
-              paste("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_GM12878_", 
+              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
                     c("10kb", "25kb", "50kb", "100kb"), 
                     "_perc.rds",sep=""),
-              paste("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_GM12878_", 
+              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
                     c("10kb", "25kb", "50kb", "100kb"), 
@@
 for(i in 1:length(fileslst)){
+  print(i)
   pcadata <- readRDS(fileslst[i])
@@
     pcadata_f <- pcadata[, -which(colnames(pcadata) %in% nzvar)]
-    }
+    }else{pcadata_f <- pcadata}
 
@@
          data=pcadata_f,
-         colour='Group') +
+         colour='Group',
+         label.show.legend = FALSE) +
   theme_bw()

### 2019-03-15 Scripts/evaluating_pca.Rmd
saved heatmaps

--- 2019-03-15 Scripts/evaluating_pca.Rmd
@@
 ```{r}
-
-```
+fileslst <- c(paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"), "/Ensemble/PCA/pcadat_GM12878_", 
+                    c("10kb", "25kb", "50kb", "100kb"), 
+                    "_count.rds",sep=""),
+              paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
+                    c("10kb", "25kb", "50kb", "100kb"), 
+                    "_perc.rds",sep=""),
+              paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
+                    c("10kb", "25kb", "50kb", "100kb"), 
+                    "_dist.rds",sep=""),
+              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_K562_", 
+                    c("10kb", "25kb", "50kb", "100kb"), 
+                    "_count.rds",sep=""),
+              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_K562_", 
+                    c("10kb", "25kb", "50kb", "100kb"), 
+                    "_perc.rds",sep=""),
+              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_K562_", 
+                    c("10kb", "25kb", "50kb", "100kb"), 
+                    "_dist.rds",sep=""))
+
+#file names for heatmaps
+heatnames <- c(paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_heatmap.png", sep=""),
+               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_heatmap.png", sep=""),
+               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_heatmap.png", sep=""),
+               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_heatmap.png", sep=""),
+               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_heatmap.png", sep=""),
+               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_heatmap.png", sep=""))
+
+#file names for pca plots
+scorepnames <- c(paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_scoreplots.png", sep=""),
+               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_scoreplots.png", sep=""),
+               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_scoreplots.png", sep=""),
+               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_scoreplots.png", sep=""),
+               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_scoreplots.png", sep=""),
+               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_scoreplots.png", sep=""))
+
+##create annotation groups
+cs <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
+                 sep = "",
+                 collapse = "|"),
+           "", 
+           list.files("Z:/TAD_data_analysis/annotations/BroadHMM")))
+hm <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
+                 sep = "",
+                 collapse = "|"),
+           "", 
+           list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")))
+
+for(i in 1:length(fileslst)){
+  print(i)
+  pcadata <- readRDS(fileslst[i])
+
+  #performing log2 transformation only for distance predictor types
+  if(grepl("_dist", colnames(pcadata)[1])){
+    pcadata <- apply(pcadata,2,function(x){log(x + 1, base=2)})
+  }
+
+  #filtering low variance predictors
+  nzv <- nearZeroVar(pcadata, saveMetrics= TRUE)
+  nzvar <- rownames(nzv[nzv$nzv,])
+  if(length(nzvar) > 0){ 
+    pcadata_f <- pcadata[, -which(colnames(pcadata) %in% nzvar)]
+    }else{pcadata_f <- pcadata}
+
+  #cleaning column names
+  colnames(pcadata_f) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", colnames(pcadata_f))
+
+  #heatmap 
+  my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
+  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", heatnames[i], sep=""),
+      width=11, height=8, units="in", res = 300)
+  heatmap.2(pcadata_f,
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          #na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=TRUE,
+          dendrogram="column",     # only draw a row dendrogram
+          cexRow=0.5,
+          cexCol=0.5,
+          labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #sepwidth=c(0.001,0.001),
+          #sepcolor="black",
+          #colsep=1:ncol(pcadata_f),
+          #rowsep=1:nrow(pcadata_f),
+          keysize = 1) 
+  dev.off()
+
+  #PCA
+  #pcadata_f <- t(pcadata_f)
+  #Group <- ifelse(rownames(pcadata_f) %in% cs, "Chromatin State", ###chromatin states
+  #                                          ifelse(rownames(pcadata_f)=="DNase", "DNase I", ###dnase
+  #                                                 ifelse(rownames(pcadata_f) %in% hm, "Histone Modification", ###histone modifications
+  #                                                        "TFBS"))) ###transcription factor binding sites
+  #pcadata_f <- cbind.data.frame(pcadata_f, Group)
+  #
+  ###Plots without loadings
+  #p <- autoplot(prcomp(pcadata_f[,-(dim(pcadata_f)[2])]),
+  #       #loadings = TRUE,
+  #       label = TRUE, 
+  #       label.size = 3,
+  #       label.repel=T,
+  #       data=pcadata_f,
+  #       colour='Group',
+  #       label.show.legend = FALSE) +
+  #theme_bw()
+
+  #ggsave(p, filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", 
+  #                           scorepnames[i], sep=""),
+  #       width=8, height=11, units="in", dpi=300)
+
+}
+
+```

### 2019-03-22 Scripts/evaluating_pca.Rmd
editted script for pca

@@
 library(FactoMineR)
-
+library(ggfortify)
 ```
@@
 
-#### Overlap counts data
-
 ```{r}
 pcadat_gm12878_10kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_count.rds")
-dim(pcadat_gm12878_10kb_count)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_gm12878_10kb_count , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_gm12878_10kb_count_f <- pcadat_gm12878_10kb_count[, -which(colnames(pcadat_gm12878_10kb_count) %in% nzvar)]
-
-dim(pcadat_gm12878_10kb_count) 
-dim(pcadat_gm12878_10kb_count_f)
-
-colnames(pcadat_gm12878_10kb_count_f) <- gsub(paste(c("`", 
+pcadat_gm12878_10kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_perc.rds")
+pcadat_gm12878_10kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_dist.rds")
+
+#performing log2 transformation on distances
+pcadat_gm12878_10kb_dist <- apply(pcadat_gm12878_10kb_dist,2,function(x){log(x + 1, base=2)})
+
+cleancolnames <- function(x){gsub(paste(c("`", 
                                           "_",
-                                                    "-",
-                                                    "Gm12878", 
+                                          #"-",
+                                          #"Gm12878", 
+                                          #"Haib", 
+                                          #"Sydh",
+                                          #"Uta",
+                                          #"Uw",
+                                          #"Broad",
+                                          #"Uchicago",
                                           "dist",
                                           "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_count_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_gm12878_10kb_count_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_gm12878_10kb_count_f),
-          #rowsep=1:nrow(pcadat_gm12878_10kb_count_f),
-          keysize = 1)
-
-##create annotation groups
-cs <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
-                 sep = "",
-                 collapse = "|"),
-           "", 
-           list.files("Z:/TAD_data_analysis/annotations/BroadHMM")))
-hm <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
-                 sep = "",
-                 collapse = "|"),
-           "", 
-           list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")))
-
-#PCA
-pcadat_gm12878_10kb_count_f <- t(pcadat_gm12878_10kb_count_f)
-
-Group <- ifelse(rownames(pcadat_gm12878_10kb_count_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_gm12878_10kb_count_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_gm12878_10kb_count_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_gm12878_10kb_count_f <- cbind.data.frame(pcadat_gm12878_10kb_count_f, Group)
+                                          "perc"), collapse = "|"),"", 
+                                  colnames(x))}
+
+colnames(pcadat_gm12878_10kb_count) <- cleancolnames(pcadat_gm12878_10kb_count)
+colnames(pcadat_gm12878_10kb_perc) <- cleancolnames(pcadat_gm12878_10kb_perc)
+colnames(pcadat_gm12878_10kb_dist) <- cleancolnames(pcadat_gm12878_10kb_dist)
+
+pcadat_gm12878_10kb_count <- t(pcadat_gm12878_10kb_count)
+pcadat_gm12878_10kb_perc <- t(pcadat_gm12878_10kb_perc)
+pcadat_gm12878_10kb_dist <- t(pcadat_gm12878_10kb_dist)
+
+#pcadat_gm12878_10kb_count <- data.frame(pcadat_gm12878_10kb_count)
+#pcadat_gm12878_10kb_perc <- data.frame(pcadat_gm12878_10kb_perc)
+#pcadat_gm12878_10kb_dist <- data.frame(pcadat_gm12878_10kb_dist)
+
+#pcadat_gm12878_10kb_count$Type <- "Counts"
+#pcadat_gm12878_10kb_perc$Type <- "Percent"
+#pcadat_gm12878_10kb_dist$Type <- "Distance"
+
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+
+```
+
+#### Chromatin States
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_gm12878_10kb_count <- pcadat_gm12878_10kb_count[which(rownames(pcadat_gm12878_10kb_count) %in% chromstatevars),]
+
 ##with loadings
-autoplot(prcomp(pcadat_gm12878_10kb_count_f[,-(dim(pcadat_gm12878_10kb_count_f2)[2])]),
+autoplot(prcomp(pcadat_gm12878_10kb_count),
          loadings = TRUE,
@@
          label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_10kb_count_f,
-         colour='Group') +
+         label.repel=T) +
   theme_bw()
 ##without loadings
-autoplot(prcomp(pcadat_gm12878_10kb_count_f[,-(dim(pcadat_gm12878_10kb_count_f)[2])]),
+autoplot(prcomp(pcadat_gm12878_10kb_count),
          #loadings = TRUE,
@@
          label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_10kb_count_f,
-         colour='Group') +
+         label.repel=T) +
   theme_bw()
 ##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_10kb_count)-1)*sum(apply(pcadat_gm12878_10kb_count,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_count,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
 set.seed(1)
-autoplot(kmeans(pcadat_gm12878_10kb_count_f[,-(dim(pcadat_gm12878_10kb_count_f2)[2])], 4),
-         data=pcadat_gm12878_10kb_count_f,
+autoplot(kmeans(pcadat_gm12878_10kb_count, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_10kb_count,
          frame = TRUE,
@@
          label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
   theme_bw()

### 2019-03-22 Scripts/evaluating_pca.Rmd
editted pca script

@@
 
-histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
 tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
@@
 ```{r}
-pcadat_gm12878_10kb_count <- pcadat_gm12878_10kb_count[which(rownames(pcadat_gm12878_10kb_count) %in% chromstatevars),]
-
-##with loadings
-autoplot(prcomp(pcadat_gm12878_10kb_count),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T) +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_gm12878_10kb_count),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T) +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-wss <- (nrow(pcadat_gm12878_10kb_count)-1)*sum(apply(pcadat_gm12878_10kb_count,2,var))
-  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_count,
+pcadat_gm12878_10kb_count_chromstates <- pcadat_gm12878_10kb_count[which(rownames(pcadat_gm12878_10kb_count) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_10kb_count_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_10kb_count_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_10kb_count_chromstates)-1)*sum(apply(pcadat_gm12878_10kb_count_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_count_chromstates,
                                        centers=i, nstart=25, iter.max = 1000)$withinss)
@@
 set.seed(1)
-autoplot(kmeans(pcadat_gm12878_10kb_count, 3, nstart=25, iter.max = 1000),
-         data=pcadat_gm12878_10kb_count,
-         frame = TRUE,
-         frame.type = 'norm',
+autoplot(kmeans(pcadat_gm12878_10kb_count_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_10kb_count_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
          label = TRUE, 
@@
 
-#### Overlap percent data
-
-```{r}
-pcadat_gm12878_10kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_perc.rds")
-dim(pcadat_gm12878_10kb_perc)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_gm12878_10kb_perc , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_gm12878_10kb_perc_f <- pcadat_gm12878_10kb_perc[, -which(colnames(pcadat_gm12878_10kb_perc) %in% nzvar)]
-
-dim(pcadat_gm12878_10kb_perc) 
-dim(pcadat_gm12878_10kb_perc_f)
-
-colnames(pcadat_gm12878_10kb_perc_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "perc",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_perc_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_gm12878_10kb_perc_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_gm12878_10kb_perc_f),
-          #rowsep=1:nrow(pcadat_gm12878_10kb_perc_f),
-          keysize = 1)
-
-#PCA
-pcadat_gm12878_10kb_perc_f <- t(pcadat_gm12878_10kb_perc_f)
-
-Group <- ifelse(rownames(pcadat_gm12878_10kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_gm12878_10kb_perc_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_gm12878_10kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_gm12878_10kb_perc_f <- cbind.data.frame(pcadat_gm12878_10kb_perc_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_gm12878_10kb_perc_f[,-(dim(pcadat_gm12878_10kb_perc_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_10kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_gm12878_10kb_perc_f[,-(dim(pcadat_gm12878_10kb_perc_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_10kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_gm12878_10kb_perc_f[,-(dim(pcadat_gm12878_10kb_perc_f2)[2])], 4),
-         data=pcadat_gm12878_10kb_perc_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-```
-
-#### Distance data
-
-```{r}
-pcadat_gm12878_10kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_dist.rds")
-dim(pcadat_gm12878_10kb_dist)
-
-#performing log2 transformation
-pcadat_gm12878_10kb_dist <- apply(pcadat_gm12878_10kb_dist,2,function(x){log(x + 1, base=2)})
-
-#filtering low variance predictors
-#nzv <- nearZeroVar(pcadat_gm12878_10kb_dist , saveMetrics= TRUE)
-#nzvar <- rownames(nzv[nzv$nzv,])
-#nzvar
-#no near zero variance predictors
-
-pcadat_gm12878_10kb_dist_f <- pcadat_gm12878_10kb_dist[, -which(colnames(pcadat_gm12878_10kb_dist) %in% nzvar)]
-pcadat_gm12878_10kb_dist_f <- pcadat_gm12878_10kb_dist
-
-dim(pcadat_gm12878_10kb_dist) 
-dim(pcadat_gm12878_10kb_dist_f)
-
-colnames(pcadat_gm12878_10kb_dist_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_dist_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_gm12878_10kb_dist_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_gm12878_10kb_dist_f),
-          #rowsep=1:nrow(pcadat_gm12878_10kb_dist_f),
-          keysize = 1)
-
-#PCA
-pcadat_gm12878_10kb_dist_f <- t(pcadat_gm12878_10kb_dist_f)
-
-Group <- ifelse(rownames(pcadat_gm12878_10kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_gm12878_10kb_dist_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_gm12878_10kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_gm12878_10kb_dist_f <- cbind.data.frame(pcadat_gm12878_10kb_dist_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_gm12878_10kb_dist_f[,-(dim(pcadat_gm12878_10kb_dist_f)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_10kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_gm12878_10kb_dist_f[,-(dim(pcadat_gm12878_10kb_dist_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_10kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_gm12878_10kb_dist_f[,-(dim(pcadat_gm12878_10kb_dist_f2)[2])], 4),
-         data=pcadat_gm12878_10kb_dist_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-
-```
-
-### 25kb
-
-#### Overlap counts data
-
-```{r}
-pcadat_gm12878_25kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_count.rds")
-dim(pcadat_gm12878_25kb_count)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_gm12878_25kb_count , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_gm12878_25kb_count_f <- pcadat_gm12878_25kb_count[, -which(colnames(pcadat_gm12878_25kb_count) %in% nzvar)]
-
-dim(pcadat_gm12878_25kb_count) 
-dim(pcadat_gm12878_25kb_count_f)
-
-colnames(pcadat_gm12878_25kb_count_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_count_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_gm12878_25kb_count_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_gm12878_25kb_count_f),
-          #rowsep=1:nrow(pcadat_gm12878_25kb_count_f),
-          keysize = 1)
-
-#PCA
-pcadat_gm12878_25kb_count_f <- t(pcadat_gm12878_25kb_count_f)
-
-Group <- ifelse(rownames(pcadat_gm12878_25kb_count_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_gm12878_25kb_count_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_gm12878_25kb_count_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_gm12878_25kb_count_f <- cbind.data.frame(pcadat_gm12878_25kb_count_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_gm12878_25kb_count_f[,-(dim(pcadat_gm12878_25kb_count_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_25kb_count_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_gm12878_25kb_count_f[,-(dim(pcadat_gm12878_25kb_count_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_25kb_count_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_gm12878_25kb_count_f[,-(dim(pcadat_gm12878_25kb_count_f2)[2])], 4),
-         data=pcadat_gm12878_25kb_count_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-
-```
-
-#### Overlap percent data
-
-```{r}
-pcadat_gm12878_25kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_perc.rds")
-dim(pcadat_gm12878_25kb_perc)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_gm12878_25kb_perc , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_gm12878_25kb_perc_f <- pcadat_gm12878_25kb_perc[, -which(colnames(pcadat_gm12878_25kb_perc) %in% nzvar)]
-
-dim(pcadat_gm12878_25kb_perc) 
-dim(pcadat_gm12878_25kb_perc_f)
-
-colnames(pcadat_gm12878_25kb_perc_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "perc",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_perc_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_gm12878_25kb_perc_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_gm12878_25kb_perc_f),
-          #rowsep=1:nrow(pcadat_gm12878_25kb_perc_f),
-          keysize = 1)
-
-#PCA
-pcadat_gm12878_25kb_perc_f <- t(pcadat_gm12878_25kb_perc_f)
-
-Group <- ifelse(rownames(pcadat_gm12878_25kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_gm12878_25kb_perc_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_gm12878_25kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_gm12878_25kb_perc_f <- cbind.data.frame(pcadat_gm12878_25kb_perc_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_gm12878_25kb_perc_f[,-(dim(pcadat_gm12878_25kb_perc_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_25kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_gm12878_25kb_perc_f[,-(dim(pcadat_gm12878_25kb_perc_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_25kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_gm12878_25kb_perc_f[,-(dim(pcadat_gm12878_25kb_perc_f2)[2])], 4),
-         data=pcadat_gm12878_25kb_perc_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-
-```
-
-#### Distance data
-
-```{r}
-pcadat_gm12878_25kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_dist.rds")
-dim(pcadat_gm12878_25kb_dist)
-
-#performing log2 transformation
-pcadat_gm12878_25kb_dist <- apply(pcadat_gm12878_25kb_dist,2,function(x){log(x + 1, base=2)})
-
-#filtering low variance predictors
-#nzv <- nearZeroVar(pcadat_gm12878_25kb_dist , saveMetrics= TRUE)
-#nzvar <- rownames(nzv[nzv$nzv,])
-#nzvar
-#no near zero variance predictors
-
-pcadat_gm12878_25kb_dist_f <- pcadat_gm12878_25kb_dist[, -which(colnames(pcadat_gm12878_25kb_dist) %in% nzvar)]
-pcadat_gm12878_25kb_dist_f <- pcadat_gm12878_25kb_dist
-
-dim(pcadat_gm12878_25kb_dist) 
-dim(pcadat_gm12878_25kb_dist_f)
-
-colnames(pcadat_gm12878_25kb_dist_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_dist_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_gm12878_25kb_dist_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_gm12878_25kb_dist_f),
-          #rowsep=1:nrow(pcadat_gm12878_25kb_dist_f),
-          keysize = 1)
-
-#PCA
-pcadat_gm12878_25kb_dist_f <- t(pcadat_gm12878_25kb_dist_f)
-
-Group <- ifelse(rownames(pcadat_gm12878_25kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_gm12878_25kb_dist_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_gm12878_25kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_gm12878_25kb_dist_f <- cbind.data.frame(pcadat_gm12878_25kb_dist_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_gm12878_25kb_dist_f[,-(dim(pcadat_gm12878_25kb_dist_f)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_25kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_gm12878_25kb_dist_f[,-(dim(pcadat_gm12878_25kb_dist_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_25kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_gm12878_25kb_dist_f[,-(dim(pcadat_gm12878_25kb_dist_f2)[2])], 4),
-         data=pcadat_gm12878_25kb_dist_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-```
-
-### 50kb
-
-#### Overlap counts data
-
-```{r}
-pcadat_gm12878_50kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_count.rds")
-dim(pcadat_gm12878_50kb_count)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_gm12878_50kb_count , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_gm12878_50kb_count_f <- pcadat_gm12878_50kb_count[, -which(colnames(pcadat_gm12878_50kb_count) %in% nzvar)]
-
-dim(pcadat_gm12878_50kb_count) 
-dim(pcadat_gm12878_50kb_count_f)
-
-colnames(pcadat_gm12878_50kb_count_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_count_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_gm12878_50kb_count_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_gm12878_50kb_count_f),
-          #rowsep=1:nrow(pcadat_gm12878_50kb_count_f),
-          keysize = 1)
-
-#PCA
-pcadat_gm12878_50kb_count_f <- t(pcadat_gm12878_50kb_count_f)
-
-Group <- ifelse(rownames(pcadat_gm12878_50kb_count_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_gm12878_50kb_count_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_gm12878_50kb_count_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_gm12878_50kb_count_f <- cbind.data.frame(pcadat_gm12878_50kb_count_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_gm12878_50kb_count_f[,-(dim(pcadat_gm12878_50kb_count_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_50kb_count_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_gm12878_50kb_count_f[,-(dim(pcadat_gm12878_50kb_count_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_50kb_count_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_gm12878_50kb_count_f[,-(dim(pcadat_gm12878_50kb_count_f2)[2])], 4),
-         data=pcadat_gm12878_50kb_count_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-
-```
-
-#### Overlap percent data
-
-```{r}
-pcadat_gm12878_50kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_perc.rds")
-dim(pcadat_gm12878_50kb_perc)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_gm12878_50kb_perc , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_gm12878_50kb_perc_f <- pcadat_gm12878_50kb_perc[, -which(colnames(pcadat_gm12878_50kb_perc) %in% nzvar)]
-
-dim(pcadat_gm12878_50kb_perc) 
-dim(pcadat_gm12878_50kb_perc_f)
-
-colnames(pcadat_gm12878_50kb_perc_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "perc",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_perc_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_gm12878_50kb_perc_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_gm12878_50kb_perc_f),
-          #rowsep=1:nrow(pcadat_gm12878_50kb_perc_f),
-          keysize = 1)
-
-#PCA
-pcadat_gm12878_50kb_perc_f <- t(pcadat_gm12878_50kb_perc_f)
-
-Group <- ifelse(rownames(pcadat_gm12878_50kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_gm12878_50kb_perc_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_gm12878_50kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_gm12878_50kb_perc_f <- cbind.data.frame(pcadat_gm12878_50kb_perc_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_gm12878_50kb_perc_f[,-(dim(pcadat_gm12878_50kb_perc_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_50kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_gm12878_50kb_perc_f[,-(dim(pcadat_gm12878_50kb_perc_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_50kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_gm12878_50kb_perc_f[,-(dim(pcadat_gm12878_50kb_perc_f2)[2])], 4),
-         data=pcadat_gm12878_50kb_perc_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-```
-
-#### Distance data
-
-```{r}
-pcadat_gm12878_50kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_dist.rds")
-dim(pcadat_gm12878_50kb_dist)
-
-#performing log2 transformation
-pcadat_gm12878_50kb_dist <- apply(pcadat_gm12878_50kb_dist,2,function(x){log(x + 1, base=2)})
-
-#filtering low variance predictors
-#nzv <- nearZeroVar(pcadat_gm12878_50kb_dist , saveMetrics= TRUE)
-#nzvar <- rownames(nzv[nzv$nzv,])
-#nzvar
-#no near zero variance predictors
-
-pcadat_gm12878_50kb_dist_f <- pcadat_gm12878_50kb_dist[, -which(colnames(pcadat_gm12878_50kb_dist) %in% nzvar)]
-pcadat_gm12878_50kb_dist_f <- pcadat_gm12878_50kb_dist
-
-dim(pcadat_gm12878_50kb_dist) 
-dim(pcadat_gm12878_50kb_dist_f)
-
-colnames(pcadat_gm12878_50kb_dist_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_dist_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_gm12878_50kb_dist_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_gm12878_50kb_dist_f),
-          #rowsep=1:nrow(pcadat_gm12878_50kb_dist_f),
-          keysize = 1)
-
-#PCA
-pcadat_gm12878_50kb_dist_f <- t(pcadat_gm12878_50kb_dist_f)
-
-Group <- ifelse(rownames(pcadat_gm12878_50kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_gm12878_50kb_dist_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_gm12878_50kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_gm12878_50kb_dist_f <- cbind.data.frame(pcadat_gm12878_50kb_dist_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_gm12878_50kb_dist_f[,-(dim(pcadat_gm12878_50kb_dist_f)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_50kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_gm12878_50kb_dist_f[,-(dim(pcadat_gm12878_50kb_dist_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_50kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_gm12878_50kb_dist_f[,-(dim(pcadat_gm12878_50kb_dist_f2)[2])], 4),
-         data=pcadat_gm12878_50kb_dist_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-```
-
-### 100kb
-
-#### Overlap counts data
-
-```{r}
-pcadat_gm12878_100kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_count.rds")
-dim(pcadat_gm12878_100kb_count)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_gm12878_100kb_count , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_gm12878_100kb_count_f <- pcadat_gm12878_100kb_count[, -which(colnames(pcadat_gm12878_100kb_count) %in% nzvar)]
-
-dim(pcadat_gm12878_100kb_count) 
-dim(pcadat_gm12878_100kb_count_f)
-
-colnames(pcadat_gm12878_100kb_count_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_count_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_gm12878_100kb_count_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_gm12878_100kb_count_f),
-          #rowsep=1:nrow(pcadat_gm12878_100kb_count_f),
-          keysize = 1)
-
-#PCA
-pcadat_gm12878_100kb_count_f <- t(pcadat_gm12878_100kb_count_f)
-
-Group <- ifelse(rownames(pcadat_gm12878_100kb_count_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_gm12878_100kb_count_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_gm12878_100kb_count_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_gm12878_100kb_count_f <- cbind.data.frame(pcadat_gm12878_100kb_count_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_gm12878_100kb_count_f[,-(dim(pcadat_gm12878_100kb_count_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_100kb_count_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_gm12878_100kb_count_f[,-(dim(pcadat_gm12878_100kb_count_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_100kb_count_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_gm12878_100kb_count_f[,-(dim(pcadat_gm12878_100kb_count_f2)[2])], 4),
-         data=pcadat_gm12878_100kb_count_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-
-```
-
-#### Overlap percent data
-
-```{r}
-pcadat_gm12878_100kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_perc.rds")
-dim(pcadat_gm12878_100kb_perc)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_gm12878_100kb_perc , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_gm12878_100kb_perc_f <- pcadat_gm12878_100kb_perc[, -which(colnames(pcadat_gm12878_100kb_perc) %in% nzvar)]
-
-dim(pcadat_gm12878_100kb_perc) 
-dim(pcadat_gm12878_100kb_perc_f)
-
-colnames(pcadat_gm12878_100kb_perc_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "perc",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_perc_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_gm12878_100kb_perc_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_gm12878_100kb_perc_f),
-          #rowsep=1:nrow(pcadat_gm12878_100kb_perc_f),
-          keysize = 1)
-
-#PCA
-pcadat_gm12878_100kb_perc_f <- t(pcadat_gm12878_100kb_perc_f)
-
-Group <- ifelse(rownames(pcadat_gm12878_100kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_gm12878_100kb_perc_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_gm12878_100kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_gm12878_100kb_perc_f <- cbind.data.frame(pcadat_gm12878_100kb_perc_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_gm12878_100kb_perc_f[,-(dim(pcadat_gm12878_100kb_perc_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_100kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_gm12878_100kb_perc_f[,-(dim(pcadat_gm12878_100kb_perc_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_100kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_gm12878_100kb_perc_f[,-(dim(pcadat_gm12878_100kb_perc_f2)[2])], 4),
-         data=pcadat_gm12878_100kb_perc_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-
-```
-
-#### Distance data
-
-```{r}
-pcadat_gm12878_100kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_dist.rds")
-dim(pcadat_gm12878_100kb_dist)
-
-#performing log2 transformation
-pcadat_gm12878_100kb_dist <- apply(pcadat_gm12878_100kb_dist,2,function(x){log(x + 1, base=2)})
-
-#filtering low variance predictors
-#nzv <- nearZeroVar(pcadat_gm12878_100kb_dist , saveMetrics= TRUE)
-#nzvar <- rownames(nzv[nzv$nzv,])
-#nzvar
-#no near zero variance predictors
-
-pcadat_gm12878_100kb_dist_f <- pcadat_gm12878_100kb_dist[, -which(colnames(pcadat_gm12878_100kb_dist) %in% nzvar)]
-pcadat_gm12878_100kb_dist_f <- pcadat_gm12878_100kb_dist
-
-dim(pcadat_gm12878_100kb_dist) 
-dim(pcadat_gm12878_100kb_dist_f)
-
-colnames(pcadat_gm12878_100kb_dist_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_dist_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_gm12878_100kb_dist_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_gm12878_100kb_dist_f),
-          #rowsep=1:nrow(pcadat_gm12878_100kb_dist_f),
-          keysize = 1)
-
-#PCA
-pcadat_gm12878_100kb_dist_f <- t(pcadat_gm12878_100kb_dist_f)
-
-Group <- ifelse(rownames(pcadat_gm12878_100kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_gm12878_100kb_dist_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_gm12878_100kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_gm12878_100kb_dist_f <- cbind.data.frame(pcadat_gm12878_100kb_dist_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_gm12878_100kb_dist_f[,-(dim(pcadat_gm12878_100kb_dist_f)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_100kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_gm12878_100kb_dist_f[,-(dim(pcadat_gm12878_100kb_dist_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_gm12878_100kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_gm12878_100kb_dist_f[,-(dim(pcadat_gm12878_100kb_dist_f2)[2])], 4),
-         data=pcadat_gm12878_100kb_dist_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
+##### Overlap Percents
+
+```{r}
+pcadat_gm12878_10kb_perc_chromstates <- pcadat_gm12878_10kb_perc[which(rownames(pcadat_gm12878_10kb_perc) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_10kb_perc_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_10kb_perc_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_10kb_perc_chromstates)-1)*sum(apply(pcadat_gm12878_10kb_perc_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_perc_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_10kb_perc_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_10kb_perc_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_gm12878_10kb_dist_chromstates <- pcadat_gm12878_10kb_dist[which(rownames(pcadat_gm12878_10kb_dist) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_10kb_dist_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_10kb_dist_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_10kb_dist_chromstates)-1)*sum(apply(pcadat_gm12878_10kb_dist_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_dist_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_10kb_dist_chromstates, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_10kb_dist_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### Histone Modifications
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_gm12878_10kb_count_histones <- pcadat_gm12878_10kb_count[which(rownames(pcadat_gm12878_10kb_count) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_10kb_count_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_10kb_count_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_10kb_count_histones)-1)*sum(apply(pcadat_gm12878_10kb_count_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_count_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_10kb_count_histones, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_10kb_count_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_gm12878_10kb_perc_histones <- pcadat_gm12878_10kb_perc[which(rownames(pcadat_gm12878_10kb_perc) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_10kb_perc_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_10kb_perc_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_10kb_perc_histones)-1)*sum(apply(pcadat_gm12878_10kb_perc_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_perc_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_10kb_perc_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_10kb_perc_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_gm12878_10kb_dist_histones <- pcadat_gm12878_10kb_dist[which(rownames(pcadat_gm12878_10kb_dist) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_10kb_dist_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_10kb_dist_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_10kb_dist_histones)-1)*sum(apply(pcadat_gm12878_10kb_dist_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_dist_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_10kb_dist_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_10kb_dist_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_gm12878_10kb_count_tfbs <- pcadat_gm12878_10kb_count[which(rownames(pcadat_gm12878_10kb_count) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_10kb_count_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_10kb_count_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_10kb_count_tfbs)-1)*sum(apply(pcadat_gm12878_10kb_count_tfbs,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_count_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_10kb_count_tfbs, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_10kb_count_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_gm12878_10kb_perc_tfbs <- pcadat_gm12878_10kb_perc[which(rownames(pcadat_gm12878_10kb_perc) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_10kb_perc_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_10kb_perc_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_10kb_perc_tfbs)-1)*sum(apply(pcadat_gm12878_10kb_perc_tfbs,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_perc_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_10kb_perc_tfbs, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_10kb_perc_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_gm12878_10kb_dist_tfbs <- pcadat_gm12878_10kb_dist[which(rownames(pcadat_gm12878_10kb_dist) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_10kb_dist_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_10kb_dist_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_10kb_dist_tfbs)-1)*sum(apply(pcadat_gm12878_10kb_dist_tfbs,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_dist_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_10kb_dist_tfbs, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_10kb_dist_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
 ```

### 2019-03-22 Scripts/evaluating_pca.Rmd
editted pca script

@@
 
-tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
-
 ```
@@
 wss <- (nrow(pcadat_gm12878_10kb_count_tfbs)-1)*sum(apply(pcadat_gm12878_10kb_count_tfbs,2,var))
-  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_count_tfbs,
-                                       centers=i, nstart=25, iter.max = 1000)$withinss)
-plot(1:5, wss, type="b", xlab="Number of Clusters",
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_count_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
      ylab="Within groups sum of squares")
@@
 wss <- (nrow(pcadat_gm12878_10kb_perc_tfbs)-1)*sum(apply(pcadat_gm12878_10kb_perc_tfbs,2,var))
-  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_perc_tfbs,
-                                       centers=i, nstart=25, iter.max = 1000)$withinss)
-plot(1:5, wss, type="b", xlab="Number of Clusters",
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_perc_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
      ylab="Within groups sum of squares")
@@
 wss <- (nrow(pcadat_gm12878_10kb_dist_tfbs)-1)*sum(apply(pcadat_gm12878_10kb_dist_tfbs,2,var))
-  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_dist_tfbs,
-                                       centers=i, nstart=25, iter.max = 1000)$withinss)
-plot(1:5, wss, type="b", xlab="Number of Clusters",
-     ylab="Within groups sum of squares")
-
-set.seed(1)
-autoplot(kmeans(pcadat_gm12878_10kb_dist_tfbs, 4, nstart=25, iter.max = 1000),
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_gm12878_10kb_dist_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_10kb_dist_tfbs, 5, nstart=25, iter.max = 1000),
          data=pcadat_gm12878_10kb_dist_tfbs,
@@
 
-## K562
-
-### 10kb
-
-#### Overlap counts data
-
-```{r}
-pcadat_K562_10kb_count <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_K562_10kb_count.rds")
-dim(pcadat_K562_10kb_count)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_K562_10kb_count , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_K562_10kb_count_f <- pcadat_K562_10kb_count[, -which(colnames(pcadat_K562_10kb_count) %in% nzvar)]
-
-dim(pcadat_K562_10kb_count) 
-dim(pcadat_K562_10kb_count_f)
-
-colnames(pcadat_K562_10kb_count_f) <- gsub(paste(c("`", 
+### 25kb
+
+```{r}
+pcadat_gm12878_25kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_count.rds")
+pcadat_gm12878_25kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_perc.rds")
+pcadat_gm12878_25kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_dist.rds")
+
+#performing log2 transformation on distances
+pcadat_gm12878_25kb_dist <- apply(pcadat_gm12878_25kb_dist,2,function(x){log(x + 1, base=2)})
+
+cleancolnames <- function(x){gsub(paste(c("`", 
                                           "_",
-                                                    "-",
-                                                    "K562", 
+                                          #"-",
+                                          #"Gm12878", 
+                                          #"Haib", 
+                                          #"Sydh",
+                                          #"Uta",
+                                          #"Uw",
+                                          #"Broad",
+                                          #"Uchicago",
                                           "dist",
                                           "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_10kb_count_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_K562_10kb_count_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_K562_10kb_count_f),
-          #rowsep=1:nrow(pcadat_K562_10kb_count_f),
-          keysize = 1)
-
-##create annotation groups
-cs <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
-                 sep = "",
-                 collapse = "|"),
-           "", 
-           list.files("Z:/TAD_data_analysis/annotations/BroadHMM")))
-hm <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
-                 sep = "",
-                 collapse = "|"),
-           "", 
-           list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")))
-
-#PCA
-pcadat_K562_10kb_count_f <- t(pcadat_K562_10kb_count_f)
-
-Group <- ifelse(rownames(pcadat_K562_10kb_count_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_K562_10kb_count_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_K562_10kb_count_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_K562_10kb_count_f <- cbind.data.frame(pcadat_K562_10kb_count_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_K562_10kb_count_f[,-(dim(pcadat_K562_10kb_count_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_10kb_count_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_K562_10kb_count_f[,-(dim(pcadat_K562_10kb_count_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_10kb_count_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_K562_10kb_count_f[,-(dim(pcadat_K562_10kb_count_f2)[2])], 4),
-         data=pcadat_K562_10kb_count_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-
-```
-
-#### Overlap percent data
-
-```{r}
-pcadat_K562_10kb_perc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_K562_10kb_perc.rds")
-dim(pcadat_K562_10kb_perc)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_K562_10kb_perc , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_K562_10kb_perc_f <- pcadat_K562_10kb_perc[, -which(colnames(pcadat_K562_10kb_perc) %in% nzvar)]
-
-dim(pcadat_K562_10kb_perc) 
-dim(pcadat_K562_10kb_perc_f)
-
-colnames(pcadat_K562_10kb_perc_f) <- gsub(paste(c("`", 
+                                          "perc"), collapse = "|"),"", 
+                                  colnames(x))}
+
+colnames(pcadat_gm12878_25kb_count) <- cleancolnames(pcadat_gm12878_25kb_count)
+colnames(pcadat_gm12878_25kb_perc) <- cleancolnames(pcadat_gm12878_25kb_perc)
+colnames(pcadat_gm12878_25kb_dist) <- cleancolnames(pcadat_gm12878_25kb_dist)
+
+pcadat_gm12878_25kb_count <- t(pcadat_gm12878_25kb_count)
+pcadat_gm12878_25kb_perc <- t(pcadat_gm12878_25kb_perc)
+pcadat_gm12878_25kb_dist <- t(pcadat_gm12878_25kb_dist)
+
+#pcadat_gm12878_25kb_count <- data.frame(pcadat_gm12878_25kb_count)
+#pcadat_gm12878_25kb_perc <- data.frame(pcadat_gm12878_25kb_perc)
+#pcadat_gm12878_25kb_dist <- data.frame(pcadat_gm12878_25kb_dist)
+
+#pcadat_gm12878_25kb_count$Type <- "Counts"
+#pcadat_gm12878_25kb_perc$Type <- "Percent"
+#pcadat_gm12878_25kb_dist$Type <- "Distance"
+
+```
+
+#### Chromatin States
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_gm12878_25kb_count_chromstates <- pcadat_gm12878_25kb_count[which(rownames(pcadat_gm12878_25kb_count) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_25kb_count_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_25kb_count_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_25kb_count_chromstates)-1)*sum(apply(pcadat_gm12878_25kb_count_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_25kb_count_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_25kb_count_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_25kb_count_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_gm12878_25kb_perc_chromstates <- pcadat_gm12878_25kb_perc[which(rownames(pcadat_gm12878_25kb_perc) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_25kb_perc_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_25kb_perc_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_25kb_perc_chromstates)-1)*sum(apply(pcadat_gm12878_25kb_perc_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_25kb_perc_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_25kb_perc_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_25kb_perc_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_gm12878_25kb_dist_chromstates <- pcadat_gm12878_25kb_dist[which(rownames(pcadat_gm12878_25kb_dist) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_25kb_dist_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_25kb_dist_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_25kb_dist_chromstates)-1)*sum(apply(pcadat_gm12878_25kb_dist_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_25kb_dist_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_25kb_dist_chromstates, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_25kb_dist_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### Histone Modifications
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_gm12878_25kb_count_histones <- pcadat_gm12878_25kb_count[which(rownames(pcadat_gm12878_25kb_count) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_25kb_count_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_25kb_count_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_25kb_count_histones)-1)*sum(apply(pcadat_gm12878_25kb_count_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_25kb_count_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_25kb_count_histones, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_25kb_count_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_gm12878_25kb_perc_histones <- pcadat_gm12878_25kb_perc[which(rownames(pcadat_gm12878_25kb_perc) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_25kb_perc_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_25kb_perc_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_25kb_perc_histones)-1)*sum(apply(pcadat_gm12878_25kb_perc_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_25kb_perc_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_25kb_perc_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_25kb_perc_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_gm12878_25kb_dist_histones <- pcadat_gm12878_25kb_dist[which(rownames(pcadat_gm12878_25kb_dist) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_25kb_dist_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_25kb_dist_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_25kb_dist_histones)-1)*sum(apply(pcadat_gm12878_25kb_dist_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_25kb_dist_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_25kb_dist_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_25kb_dist_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_gm12878_25kb_count_tfbs <- pcadat_gm12878_25kb_count[which(rownames(pcadat_gm12878_25kb_count) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_25kb_count_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_25kb_count_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_25kb_count_tfbs)-1)*sum(apply(pcadat_gm12878_25kb_count_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_gm12878_25kb_count_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_25kb_count_tfbs, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_25kb_count_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_gm12878_25kb_perc_tfbs <- pcadat_gm12878_25kb_perc[which(rownames(pcadat_gm12878_25kb_perc) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_25kb_perc_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_25kb_perc_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_25kb_perc_tfbs)-1)*sum(apply(pcadat_gm12878_25kb_perc_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_gm12878_25kb_perc_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_25kb_perc_tfbs, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_25kb_perc_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_gm12878_25kb_dist_tfbs <- pcadat_gm12878_25kb_dist[which(rownames(pcadat_gm12878_25kb_dist) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_25kb_dist_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_25kb_dist_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_25kb_dist_tfbs)-1)*sum(apply(pcadat_gm12878_25kb_dist_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_gm12878_25kb_dist_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_25kb_dist_tfbs, 5, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_25kb_dist_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+### 50kb
+
+```{r}
+pcadat_gm12878_50kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_count.rds")
+pcadat_gm12878_50kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_perc.rds")
+pcadat_gm12878_50kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_dist.rds")
+
+#performing log2 transformation on distances
+pcadat_gm12878_50kb_dist <- apply(pcadat_gm12878_50kb_dist,2,function(x){log(x + 1, base=2)})
+
+cleancolnames <- function(x){gsub(paste(c("`", 
                                           "_",
-                                                    "-",
-                                                    "K562", 
-                                                    "dist",
-                                                    "perc",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_10kb_perc_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_K562_10kb_perc_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_K562_10kb_perc_f),
-          #rowsep=1:nrow(pcadat_K562_10kb_perc_f),
-          keysize = 1)
-
-#PCA
-pcadat_K562_10kb_perc_f <- t(pcadat_K562_10kb_perc_f)
-
-Group <- ifelse(rownames(pcadat_K562_10kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_K562_10kb_perc_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_K562_10kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_K562_10kb_perc_f <- cbind.data.frame(pcadat_K562_10kb_perc_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_K562_10kb_perc_f[,-(dim(pcadat_K562_10kb_perc_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_10kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_K562_10kb_perc_f[,-(dim(pcadat_K562_10kb_perc_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_10kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_K562_10kb_perc_f[,-(dim(pcadat_K562_10kb_perc_f2)[2])], 4),
-         data=pcadat_K562_10kb_perc_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-```
-
-#### Distance data
-
-```{r}
-pcadat_K562_10kb_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_K562_10kb_dist.rds")
-dim(pcadat_K562_10kb_dist)
-
-#performing log2 transformation
-pcadat_K562_10kb_dist <- apply(pcadat_K562_10kb_dist,2,function(x){log(x + 1, base=2)})
-
-#filtering low variance predictors
-#nzv <- nearZeroVar(pcadat_K562_10kb_dist , saveMetrics= TRUE)
-#nzvar <- rownames(nzv[nzv$nzv,])
-#nzvar
-#no near zero variance predictors
-
-pcadat_K562_10kb_dist_f <- pcadat_K562_10kb_dist[, -which(colnames(pcadat_K562_10kb_dist) %in% nzvar)]
-pcadat_K562_10kb_dist_f <- pcadat_K562_10kb_dist
-
-dim(pcadat_K562_10kb_dist) 
-dim(pcadat_K562_10kb_dist_f)
-
-colnames(pcadat_K562_10kb_dist_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "K562", 
+                                          #"-",
+                                          #"Gm12878", 
+                                          #"Haib", 
+                                          #"Sydh",
+                                          #"Uta",
+                                          #"Uw",
+                                          #"Broad",
+                                          #"Uchicago",
                                           "dist",
                                           "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_10kb_dist_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_K562_10kb_dist_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_K562_10kb_dist_f),
-          #rowsep=1:nrow(pcadat_K562_10kb_dist_f),
-          keysize = 1)
-
-#PCA
-pcadat_K562_10kb_dist_f <- t(pcadat_K562_10kb_dist_f)
-
-Group <- ifelse(rownames(pcadat_K562_10kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_K562_10kb_dist_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_K562_10kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_K562_10kb_dist_f <- cbind.data.frame(pcadat_K562_10kb_dist_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_K562_10kb_dist_f[,-(dim(pcadat_K562_10kb_dist_f)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_10kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_K562_10kb_dist_f[,-(dim(pcadat_K562_10kb_dist_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_10kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_K562_10kb_dist_f[,-(dim(pcadat_K562_10kb_dist_f2)[2])], 4),
-         data=pcadat_K562_10kb_dist_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-
-```
-
-### 25kb
-
-#### Overlap counts data
-
-```{r}
-pcadat_K562_25kb_count <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/PCA/pcadat_K562_25kb_count.rds")
-dim(pcadat_K562_25kb_count)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_K562_25kb_count , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_K562_25kb_count_f <- pcadat_K562_25kb_count[, -which(colnames(pcadat_K562_25kb_count) %in% nzvar)]
-
-dim(pcadat_K562_25kb_count) 
-dim(pcadat_K562_25kb_count_f)
-
-colnames(pcadat_K562_25kb_count_f) <- gsub(paste(c("`", 
+                                          "perc"), collapse = "|"),"", 
+                                  colnames(x))}
+
+colnames(pcadat_gm12878_50kb_count) <- cleancolnames(pcadat_gm12878_50kb_count)
+colnames(pcadat_gm12878_50kb_perc) <- cleancolnames(pcadat_gm12878_50kb_perc)
+colnames(pcadat_gm12878_50kb_dist) <- cleancolnames(pcadat_gm12878_50kb_dist)
+
+pcadat_gm12878_50kb_count <- t(pcadat_gm12878_50kb_count)
+pcadat_gm12878_50kb_perc <- t(pcadat_gm12878_50kb_perc)
+pcadat_gm12878_50kb_dist <- t(pcadat_gm12878_50kb_dist)
+
+#pcadat_gm12878_50kb_count <- data.frame(pcadat_gm12878_50kb_count)
+#pcadat_gm12878_50kb_perc <- data.frame(pcadat_gm12878_50kb_perc)
+#pcadat_gm12878_50kb_dist <- data.frame(pcadat_gm12878_50kb_dist)
+
+#pcadat_gm12878_50kb_count$Type <- "Counts"
+#pcadat_gm12878_50kb_perc$Type <- "Percent"
+#pcadat_gm12878_50kb_dist$Type <- "Distance"
+
+```
+
+#### Chromatin States
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_gm12878_50kb_count_chromstates <- pcadat_gm12878_50kb_count[which(rownames(pcadat_gm12878_50kb_count) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_50kb_count_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_50kb_count_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_50kb_count_chromstates)-1)*sum(apply(pcadat_gm12878_50kb_count_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_50kb_count_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_50kb_count_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_50kb_count_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_gm12878_50kb_perc_chromstates <- pcadat_gm12878_50kb_perc[which(rownames(pcadat_gm12878_50kb_perc) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_50kb_perc_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_50kb_perc_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_50kb_perc_chromstates)-1)*sum(apply(pcadat_gm12878_50kb_perc_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_50kb_perc_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_50kb_perc_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_50kb_perc_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_gm12878_50kb_dist_chromstates <- pcadat_gm12878_50kb_dist[which(rownames(pcadat_gm12878_50kb_dist) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_50kb_dist_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_50kb_dist_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_50kb_dist_chromstates)-1)*sum(apply(pcadat_gm12878_50kb_dist_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_50kb_dist_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_50kb_dist_chromstates, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_50kb_dist_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### Histone Modifications
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_gm12878_50kb_count_histones <- pcadat_gm12878_50kb_count[which(rownames(pcadat_gm12878_50kb_count) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_50kb_count_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_50kb_count_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_50kb_count_histones)-1)*sum(apply(pcadat_gm12878_50kb_count_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_50kb_count_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_50kb_count_histones, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_50kb_count_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_gm12878_50kb_perc_histones <- pcadat_gm12878_50kb_perc[which(rownames(pcadat_gm12878_50kb_perc) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_50kb_perc_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_50kb_perc_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_50kb_perc_histones)-1)*sum(apply(pcadat_gm12878_50kb_perc_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_50kb_perc_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_50kb_perc_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_50kb_perc_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_gm12878_50kb_dist_histones <- pcadat_gm12878_50kb_dist[which(rownames(pcadat_gm12878_50kb_dist) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_50kb_dist_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_50kb_dist_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_50kb_dist_histones)-1)*sum(apply(pcadat_gm12878_50kb_dist_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_50kb_dist_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_50kb_dist_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_50kb_dist_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_gm12878_50kb_count_tfbs <- pcadat_gm12878_50kb_count[which(rownames(pcadat_gm12878_50kb_count) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_50kb_count_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_50kb_count_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_50kb_count_tfbs)-1)*sum(apply(pcadat_gm12878_50kb_count_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_gm12878_50kb_count_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_50kb_count_tfbs, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_50kb_count_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_gm12878_50kb_perc_tfbs <- pcadat_gm12878_50kb_perc[which(rownames(pcadat_gm12878_50kb_perc) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_50kb_perc_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_50kb_perc_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_50kb_perc_tfbs)-1)*sum(apply(pcadat_gm12878_50kb_perc_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_gm12878_50kb_perc_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_50kb_perc_tfbs, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_50kb_perc_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_gm12878_50kb_dist_tfbs <- pcadat_gm12878_50kb_dist[which(rownames(pcadat_gm12878_50kb_dist) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_50kb_dist_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_50kb_dist_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_50kb_dist_tfbs)-1)*sum(apply(pcadat_gm12878_50kb_dist_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_gm12878_50kb_dist_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_50kb_dist_tfbs, 5, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_50kb_dist_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+### 100kb
+
+```{r}
+pcadat_gm12878_100kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_count.rds")
+pcadat_gm12878_100kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_perc.rds")
+pcadat_gm12878_100kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_dist.rds")
+
+#performing log2 transformation on distances
+pcadat_gm12878_100kb_dist <- apply(pcadat_gm12878_100kb_dist,2,function(x){log(x + 1, base=2)})
+
+cleancolnames <- function(x){gsub(paste(c("`", 
                                           "_",
-                                                    "-",
-                                                    "K562", 
+                                          #"-",
+                                          #"Gm12878", 
+                                          #"Haib", 
+                                          #"Sydh",
+                                          #"Uta",
+                                          #"Uw",
+                                          #"Broad",
+                                          #"Uchicago",
                                           "dist",
                                           "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_25kb_count_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_K562_25kb_count_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_K562_25kb_count_f),
-          #rowsep=1:nrow(pcadat_K562_25kb_count_f),
-          keysize = 1)
-
-#PCA
-pcadat_K562_25kb_count_f <- t(pcadat_K562_25kb_count_f)
-
-Group <- ifelse(rownames(pcadat_K562_25kb_count_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_K562_25kb_count_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_K562_25kb_count_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_K562_25kb_count_f <- cbind.data.frame(pcadat_K562_25kb_count_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_K562_25kb_count_f[,-(dim(pcadat_K562_25kb_count_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_25kb_count_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_K562_25kb_count_f[,-(dim(pcadat_K562_25kb_count_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_25kb_count_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_K562_25kb_count_f[,-(dim(pcadat_K562_25kb_count_f2)[2])], 4),
-         data=pcadat_K562_25kb_count_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-
-```
-
-#### Overlap percent data
-
-```{r}
-pcadat_K562_25kb_perc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/PCA/pcadat_K562_25kb_perc.rds")
-dim(pcadat_K562_25kb_perc)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_K562_25kb_perc , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_K562_25kb_perc_f <- pcadat_K562_25kb_perc[, -which(colnames(pcadat_K562_25kb_perc) %in% nzvar)]
-
-dim(pcadat_K562_25kb_perc) 
-dim(pcadat_K562_25kb_perc_f)
-
-colnames(pcadat_K562_25kb_perc_f) <- gsub(paste(c("`", 
+                                          "perc"), collapse = "|"),"", 
+                                  colnames(x))}
+
+colnames(pcadat_gm12878_100kb_count) <- cleancolnames(pcadat_gm12878_100kb_count)
+colnames(pcadat_gm12878_100kb_perc) <- cleancolnames(pcadat_gm12878_100kb_perc)
+colnames(pcadat_gm12878_100kb_dist) <- cleancolnames(pcadat_gm12878_100kb_dist)
+
+pcadat_gm12878_100kb_count <- t(pcadat_gm12878_100kb_count)
+pcadat_gm12878_100kb_perc <- t(pcadat_gm12878_100kb_perc)
+pcadat_gm12878_100kb_dist <- t(pcadat_gm12878_100kb_dist)
+
+#pcadat_gm12878_100kb_count <- data.frame(pcadat_gm12878_100kb_count)
+#pcadat_gm12878_100kb_perc <- data.frame(pcadat_gm12878_100kb_perc)
+#pcadat_gm12878_100kb_dist <- data.frame(pcadat_gm12878_100kb_dist)
+
+#pcadat_gm12878_100kb_count$Type <- "Counts"
+#pcadat_gm12878_100kb_perc$Type <- "Percent"
+#pcadat_gm12878_100kb_dist$Type <- "Distance"
+
+```
+
+#### Chromatin States
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_gm12878_100kb_count_chromstates <- pcadat_gm12878_100kb_count[which(rownames(pcadat_gm12878_100kb_count) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_100kb_count_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_100kb_count_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_100kb_count_chromstates)-1)*sum(apply(pcadat_gm12878_100kb_count_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_100kb_count_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_100kb_count_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_100kb_count_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_gm12878_100kb_perc_chromstates <- pcadat_gm12878_100kb_perc[which(rownames(pcadat_gm12878_100kb_perc) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_100kb_perc_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_100kb_perc_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_100kb_perc_chromstates)-1)*sum(apply(pcadat_gm12878_100kb_perc_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_100kb_perc_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_100kb_perc_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_100kb_perc_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_gm12878_100kb_dist_chromstates <- pcadat_gm12878_100kb_dist[which(rownames(pcadat_gm12878_100kb_dist) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_100kb_dist_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_100kb_dist_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_100kb_dist_chromstates)-1)*sum(apply(pcadat_gm12878_100kb_dist_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_100kb_dist_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_100kb_dist_chromstates, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_100kb_dist_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### Histone Modifications
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_gm12878_100kb_count_histones <- pcadat_gm12878_100kb_count[which(rownames(pcadat_gm12878_100kb_count) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_100kb_count_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_100kb_count_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_100kb_count_histones)-1)*sum(apply(pcadat_gm12878_100kb_count_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_100kb_count_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_100kb_count_histones, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_100kb_count_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_gm12878_100kb_perc_histones <- pcadat_gm12878_100kb_perc[which(rownames(pcadat_gm12878_100kb_perc) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_100kb_perc_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_100kb_perc_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_100kb_perc_histones)-1)*sum(apply(pcadat_gm12878_100kb_perc_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_100kb_perc_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_100kb_perc_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_100kb_perc_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_gm12878_100kb_dist_histones <- pcadat_gm12878_100kb_dist[which(rownames(pcadat_gm12878_100kb_dist) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_100kb_dist_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_100kb_dist_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_100kb_dist_histones)-1)*sum(apply(pcadat_gm12878_100kb_dist_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_gm12878_100kb_dist_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_100kb_dist_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_100kb_dist_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_gm12878_100kb_count_tfbs <- pcadat_gm12878_100kb_count[which(rownames(pcadat_gm12878_100kb_count) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_100kb_count_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_100kb_count_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_100kb_count_tfbs)-1)*sum(apply(pcadat_gm12878_100kb_count_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_gm12878_100kb_count_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_100kb_count_tfbs, 3, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_100kb_count_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_gm12878_100kb_perc_tfbs <- pcadat_gm12878_100kb_perc[which(rownames(pcadat_gm12878_100kb_perc) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_100kb_perc_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_100kb_perc_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_100kb_perc_tfbs)-1)*sum(apply(pcadat_gm12878_100kb_perc_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_gm12878_100kb_perc_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_100kb_perc_tfbs, 4, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_100kb_perc_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_gm12878_100kb_dist_tfbs <- pcadat_gm12878_100kb_dist[which(rownames(pcadat_gm12878_100kb_dist) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_gm12878_100kb_dist_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_gm12878_100kb_dist_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_gm12878_100kb_dist_tfbs)-1)*sum(apply(pcadat_gm12878_100kb_dist_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_gm12878_100kb_dist_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_gm12878_100kb_dist_tfbs, 5, nstart=25, iter.max = 1000),
+         data=pcadat_gm12878_100kb_dist_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+## K562
+
+### 10kb
+
+```{r}
+pcadat_K562_10kb_count <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_K562_10kb_count.rds")
+pcadat_K562_10kb_perc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_K562_10kb_perc.rds")
+pcadat_K562_10kb_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_K562_10kb_dist.rds")
+
+#performing log2 transformation on distances
+pcadat_K562_10kb_dist <- apply(pcadat_K562_10kb_dist,2,function(x){log(x + 1, base=2)})
+
+cleancolnames <- function(x){gsub(paste(c("`", 
                                           "_",
-                                                    "-",
-                                                    "K562", 
-                                                    "dist",
-                                                    "perc",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_25kb_perc_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_K562_25kb_perc_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_K562_25kb_perc_f),
-          #rowsep=1:nrow(pcadat_K562_25kb_perc_f),
-          keysize = 1)
-
-#PCA
-pcadat_K562_25kb_perc_f <- t(pcadat_K562_25kb_perc_f)
-
-Group <- ifelse(rownames(pcadat_K562_25kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_K562_25kb_perc_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_K562_25kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_K562_25kb_perc_f <- cbind.data.frame(pcadat_K562_25kb_perc_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_K562_25kb_perc_f[,-(dim(pcadat_K562_25kb_perc_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_25kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_K562_25kb_perc_f[,-(dim(pcadat_K562_25kb_perc_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_25kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_K562_25kb_perc_f[,-(dim(pcadat_K562_25kb_perc_f2)[2])], 4),
-         data=pcadat_K562_25kb_perc_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-
-```
-
-#### Distance data
-
-```{r}
-pcadat_K562_25kb_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/PCA/pcadat_K562_25kb_dist.rds")
-dim(pcadat_K562_25kb_dist)
-
-#performing log2 transformation
-pcadat_K562_25kb_dist <- apply(pcadat_K562_25kb_dist,2,function(x){log(x + 1, base=2)})
-
-#filtering low variance predictors
-#nzv <- nearZeroVar(pcadat_K562_25kb_dist , saveMetrics= TRUE)
-#nzvar <- rownames(nzv[nzv$nzv,])
-#nzvar
-#no near zero variance predictors
-
-pcadat_K562_25kb_dist_f <- pcadat_K562_25kb_dist[, -which(colnames(pcadat_K562_25kb_dist) %in% nzvar)]
-pcadat_K562_25kb_dist_f <- pcadat_K562_25kb_dist
-
-dim(pcadat_K562_25kb_dist) 
-dim(pcadat_K562_25kb_dist_f)
-
-colnames(pcadat_K562_25kb_dist_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "K562", 
+                                          #"-",
+                                          #"K562", 
+                                          #"Haib", 
+                                          #"Sydh",
+                                          #"Uta",
+                                          #"Uw",
+                                          #"Broad",
+                                          #"Uchicago",
                                           "dist",
                                           "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_25kb_dist_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_K562_25kb_dist_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_K562_25kb_dist_f),
-          #rowsep=1:nrow(pcadat_K562_25kb_dist_f),
-          keysize = 1)
-
-#PCA
-pcadat_K562_25kb_dist_f <- t(pcadat_K562_25kb_dist_f)
-
-Group <- ifelse(rownames(pcadat_K562_25kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_K562_25kb_dist_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_K562_25kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_K562_25kb_dist_f <- cbind.data.frame(pcadat_K562_25kb_dist_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_K562_25kb_dist_f[,-(dim(pcadat_K562_25kb_dist_f)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_25kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_K562_25kb_dist_f[,-(dim(pcadat_K562_25kb_dist_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_25kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_K562_25kb_dist_f[,-(dim(pcadat_K562_25kb_dist_f2)[2])], 4),
-         data=pcadat_K562_25kb_dist_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-```
-
-### 50kb
-
-#### Overlap counts data
-
-```{r}
-pcadat_K562_50kb_count <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/PCA/pcadat_K562_50kb_count.rds")
-dim(pcadat_K562_50kb_count)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_K562_50kb_count , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_K562_50kb_count_f <- pcadat_K562_50kb_count[, -which(colnames(pcadat_K562_50kb_count) %in% nzvar)]
-
-dim(pcadat_K562_50kb_count) 
-dim(pcadat_K562_50kb_count_f)
-
-colnames(pcadat_K562_50kb_count_f) <- gsub(paste(c("`", 
+                                          "perc"), collapse = "|"),"", 
+                                  colnames(x))}
+
+colnames(pcadat_K562_10kb_count) <- cleancolnames(pcadat_K562_10kb_count)
+colnames(pcadat_K562_10kb_perc) <- cleancolnames(pcadat_K562_10kb_perc)
+colnames(pcadat_K562_10kb_dist) <- cleancolnames(pcadat_K562_10kb_dist)
+
+pcadat_K562_10kb_count <- t(pcadat_K562_10kb_count)
+pcadat_K562_10kb_perc <- t(pcadat_K562_10kb_perc)
+pcadat_K562_10kb_dist <- t(pcadat_K562_10kb_dist)
+
+#pcadat_K562_10kb_count <- data.frame(pcadat_K562_10kb_count)
+#pcadat_K562_10kb_perc <- data.frame(pcadat_K562_10kb_perc)
+#pcadat_K562_10kb_dist <- data.frame(pcadat_K562_10kb_dist)
+
+#pcadat_K562_10kb_count$Type <- "Counts"
+#pcadat_K562_10kb_perc$Type <- "Percent"
+#pcadat_K562_10kb_dist$Type <- "Distance"
+
+```
+
+#### Chromatin States
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_K562_10kb_count_chromstates <- pcadat_K562_10kb_count[which(rownames(pcadat_K562_10kb_count) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_10kb_count_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_10kb_count_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_10kb_count_chromstates)-1)*sum(apply(pcadat_K562_10kb_count_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_10kb_count_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_10kb_count_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_10kb_count_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_K562_10kb_perc_chromstates <- pcadat_K562_10kb_perc[which(rownames(pcadat_K562_10kb_perc) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_10kb_perc_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_10kb_perc_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_10kb_perc_chromstates)-1)*sum(apply(pcadat_K562_10kb_perc_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_10kb_perc_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_10kb_perc_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_10kb_perc_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_K562_10kb_dist_chromstates <- pcadat_K562_10kb_dist[which(rownames(pcadat_K562_10kb_dist) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_10kb_dist_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_10kb_dist_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_10kb_dist_chromstates)-1)*sum(apply(pcadat_K562_10kb_dist_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_10kb_dist_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_10kb_dist_chromstates, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_10kb_dist_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### Histone Modifications
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_K562_10kb_count_histones <- pcadat_K562_10kb_count[which(rownames(pcadat_K562_10kb_count) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_10kb_count_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_10kb_count_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_10kb_count_histones)-1)*sum(apply(pcadat_K562_10kb_count_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_10kb_count_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_10kb_count_histones, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_10kb_count_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_K562_10kb_perc_histones <- pcadat_K562_10kb_perc[which(rownames(pcadat_K562_10kb_perc) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_10kb_perc_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_10kb_perc_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_10kb_perc_histones)-1)*sum(apply(pcadat_K562_10kb_perc_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_10kb_perc_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_10kb_perc_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_10kb_perc_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_K562_10kb_dist_histones <- pcadat_K562_10kb_dist[which(rownames(pcadat_K562_10kb_dist) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_10kb_dist_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_10kb_dist_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_10kb_dist_histones)-1)*sum(apply(pcadat_K562_10kb_dist_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_10kb_dist_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_10kb_dist_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_10kb_dist_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/K562"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_K562_10kb_count_tfbs <- pcadat_K562_10kb_count[which(rownames(pcadat_K562_10kb_count) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_10kb_count_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_10kb_count_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_10kb_count_tfbs)-1)*sum(apply(pcadat_K562_10kb_count_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_K562_10kb_count_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_10kb_count_tfbs, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_10kb_count_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_K562_10kb_perc_tfbs <- pcadat_K562_10kb_perc[which(rownames(pcadat_K562_10kb_perc) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_10kb_perc_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_10kb_perc_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_10kb_perc_tfbs)-1)*sum(apply(pcadat_K562_10kb_perc_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_K562_10kb_perc_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_10kb_perc_tfbs, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_10kb_perc_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_K562_10kb_dist_tfbs <- pcadat_K562_10kb_dist[which(rownames(pcadat_K562_10kb_dist) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_10kb_dist_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_10kb_dist_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_10kb_dist_tfbs)-1)*sum(apply(pcadat_K562_10kb_dist_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_K562_10kb_dist_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_10kb_dist_tfbs, 5, nstart=25, iter.max = 1000),
+         data=pcadat_K562_10kb_dist_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+### 25kb
+
+```{r}
+pcadat_K562_25kb_count <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/PCA/pcadat_K562_25kb_count.rds")
+pcadat_K562_25kb_perc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/PCA/pcadat_K562_25kb_perc.rds")
+pcadat_K562_25kb_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/PCA/pcadat_K562_25kb_dist.rds")
+
+#performing log2 transformation on distances
+pcadat_K562_25kb_dist <- apply(pcadat_K562_25kb_dist,2,function(x){log(x + 1, base=2)})
+
+cleancolnames <- function(x){gsub(paste(c("`", 
                                           "_",
-                                                    "-",
-                                                    "K562", 
+                                          #"-",
+                                          #"K562", 
+                                          #"Haib", 
+                                          #"Sydh",
+                                          #"Uta",
+                                          #"Uw",
+                                          #"Broad",
+                                          #"Uchicago",
                                           "dist",
                                           "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_50kb_count_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_K562_50kb_count_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_K562_50kb_count_f),
-          #rowsep=1:nrow(pcadat_K562_50kb_count_f),
-          keysize = 1)
-
-#PCA
-pcadat_K562_50kb_count_f <- t(pcadat_K562_50kb_count_f)
-
-Group <- ifelse(rownames(pcadat_K562_50kb_count_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_K562_50kb_count_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_K562_50kb_count_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_K562_50kb_count_f <- cbind.data.frame(pcadat_K562_50kb_count_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_K562_50kb_count_f[,-(dim(pcadat_K562_50kb_count_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_50kb_count_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_K562_50kb_count_f[,-(dim(pcadat_K562_50kb_count_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_50kb_count_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_K562_50kb_count_f[,-(dim(pcadat_K562_50kb_count_f2)[2])], 4),
-         data=pcadat_K562_50kb_count_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-
-```
-
-#### Overlap percent data
-
-```{r}
+                                          "perc"), collapse = "|"),"", 
+                                  colnames(x))}
+
+colnames(pcadat_K562_25kb_count) <- cleancolnames(pcadat_K562_25kb_count)
+colnames(pcadat_K562_25kb_perc) <- cleancolnames(pcadat_K562_25kb_perc)
+colnames(pcadat_K562_25kb_dist) <- cleancolnames(pcadat_K562_25kb_dist)
+
+pcadat_K562_25kb_count <- t(pcadat_K562_25kb_count)
+pcadat_K562_25kb_perc <- t(pcadat_K562_25kb_perc)
+pcadat_K562_25kb_dist <- t(pcadat_K562_25kb_dist)
+
+#pcadat_K562_25kb_count <- data.frame(pcadat_K562_25kb_count)
+#pcadat_K562_25kb_perc <- data.frame(pcadat_K562_25kb_perc)
+#pcadat_K562_25kb_dist <- data.frame(pcadat_K562_25kb_dist)
+
+#pcadat_K562_25kb_count$Type <- "Counts"
+#pcadat_K562_25kb_perc$Type <- "Percent"
+#pcadat_K562_25kb_dist$Type <- "Distance"
+
+```
+
+#### Chromatin States
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_K562_25kb_count_chromstates <- pcadat_K562_25kb_count[which(rownames(pcadat_K562_25kb_count) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_25kb_count_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_25kb_count_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_25kb_count_chromstates)-1)*sum(apply(pcadat_K562_25kb_count_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_25kb_count_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_25kb_count_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_25kb_count_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_K562_25kb_perc_chromstates <- pcadat_K562_25kb_perc[which(rownames(pcadat_K562_25kb_perc) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_25kb_perc_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_25kb_perc_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_25kb_perc_chromstates)-1)*sum(apply(pcadat_K562_25kb_perc_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_25kb_perc_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_25kb_perc_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_25kb_perc_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_K562_25kb_dist_chromstates <- pcadat_K562_25kb_dist[which(rownames(pcadat_K562_25kb_dist) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_25kb_dist_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_25kb_dist_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_25kb_dist_chromstates)-1)*sum(apply(pcadat_K562_25kb_dist_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_25kb_dist_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_25kb_dist_chromstates, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_25kb_dist_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### Histone Modifications
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_K562_25kb_count_histones <- pcadat_K562_25kb_count[which(rownames(pcadat_K562_25kb_count) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_25kb_count_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_25kb_count_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_25kb_count_histones)-1)*sum(apply(pcadat_K562_25kb_count_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_25kb_count_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_25kb_count_histones, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_25kb_count_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_K562_25kb_perc_histones <- pcadat_K562_25kb_perc[which(rownames(pcadat_K562_25kb_perc) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_25kb_perc_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_25kb_perc_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_25kb_perc_histones)-1)*sum(apply(pcadat_K562_25kb_perc_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_25kb_perc_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_25kb_perc_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_25kb_perc_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_K562_25kb_dist_histones <- pcadat_K562_25kb_dist[which(rownames(pcadat_K562_25kb_dist) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_25kb_dist_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_25kb_dist_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_25kb_dist_histones)-1)*sum(apply(pcadat_K562_25kb_dist_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_25kb_dist_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_25kb_dist_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_25kb_dist_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/K562"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_K562_25kb_count_tfbs <- pcadat_K562_25kb_count[which(rownames(pcadat_K562_25kb_count) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_25kb_count_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_25kb_count_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_25kb_count_tfbs)-1)*sum(apply(pcadat_K562_25kb_count_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_K562_25kb_count_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_25kb_count_tfbs, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_25kb_count_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_K562_25kb_perc_tfbs <- pcadat_K562_25kb_perc[which(rownames(pcadat_K562_25kb_perc) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_25kb_perc_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_25kb_perc_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_25kb_perc_tfbs)-1)*sum(apply(pcadat_K562_25kb_perc_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_K562_25kb_perc_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_25kb_perc_tfbs, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_25kb_perc_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_K562_25kb_dist_tfbs <- pcadat_K562_25kb_dist[which(rownames(pcadat_K562_25kb_dist) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_25kb_dist_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_25kb_dist_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_25kb_dist_tfbs)-1)*sum(apply(pcadat_K562_25kb_dist_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_K562_25kb_dist_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_25kb_dist_tfbs, 5, nstart=25, iter.max = 1000),
+         data=pcadat_K562_25kb_dist_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+### 50kb
+
+```{r}
+pcadat_K562_50kb_count <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/PCA/pcadat_K562_50kb_count.rds")
 pcadat_K562_50kb_perc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/PCA/pcadat_K562_50kb_perc.rds")
-dim(pcadat_K562_50kb_perc)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_K562_50kb_perc , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_K562_50kb_perc_f <- pcadat_K562_50kb_perc[, -which(colnames(pcadat_K562_50kb_perc) %in% nzvar)]
-
-dim(pcadat_K562_50kb_perc) 
-dim(pcadat_K562_50kb_perc_f)
-
-colnames(pcadat_K562_50kb_perc_f) <- gsub(paste(c("`", 
+pcadat_K562_50kb_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/PCA/pcadat_K562_50kb_dist.rds")
+
+#performing log2 transformation on distances
+pcadat_K562_50kb_dist <- apply(pcadat_K562_50kb_dist,2,function(x){log(x + 1, base=2)})
+
+cleancolnames <- function(x){gsub(paste(c("`", 
                                           "_",
-                                                    "-",
-                                                    "K562", 
-                                                    "dist",
-                                                    "perc",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_50kb_perc_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_K562_50kb_perc_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_K562_50kb_perc_f),
-          #rowsep=1:nrow(pcadat_K562_50kb_perc_f),
-          keysize = 1)
-
-#PCA
-pcadat_K562_50kb_perc_f <- t(pcadat_K562_50kb_perc_f)
-
-Group <- ifelse(rownames(pcadat_K562_50kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_K562_50kb_perc_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_K562_50kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_K562_50kb_perc_f <- cbind.data.frame(pcadat_K562_50kb_perc_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_K562_50kb_perc_f[,-(dim(pcadat_K562_50kb_perc_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_50kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_K562_50kb_perc_f[,-(dim(pcadat_K562_50kb_perc_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_50kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_K562_50kb_perc_f[,-(dim(pcadat_K562_50kb_perc_f2)[2])], 4),
-         data=pcadat_K562_50kb_perc_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-```
-
-#### Distance data
-
-```{r}
-pcadat_K562_50kb_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/PCA/pcadat_K562_50kb_dist.rds")
-dim(pcadat_K562_50kb_dist)
-
-#performing log2 transformation
-pcadat_K562_50kb_dist <- apply(pcadat_K562_50kb_dist,2,function(x){log(x + 1, base=2)})
-
-#filtering low variance predictors
-#nzv <- nearZeroVar(pcadat_K562_50kb_dist , saveMetrics= TRUE)
-#nzvar <- rownames(nzv[nzv$nzv,])
-#nzvar
-#no near zero variance predictors
-
-pcadat_K562_50kb_dist_f <- pcadat_K562_50kb_dist[, -which(colnames(pcadat_K562_50kb_dist) %in% nzvar)]
-pcadat_K562_50kb_dist_f <- pcadat_K562_50kb_dist
-
-dim(pcadat_K562_50kb_dist) 
-dim(pcadat_K562_50kb_dist_f)
-
-colnames(pcadat_K562_50kb_dist_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "K562", 
+                                          #"-",
+                                          #"K562", 
+                                          #"Haib", 
+                                          #"Sydh",
+                                          #"Uta",
+                                          #"Uw",
+                                          #"Broad",
+                                          #"Uchicago",
                                           "dist",
                                           "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_50kb_dist_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_K562_50kb_dist_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_K562_50kb_dist_f),
-          #rowsep=1:nrow(pcadat_K562_50kb_dist_f),
-          keysize = 1)
-
-#PCA
-pcadat_K562_50kb_dist_f <- t(pcadat_K562_50kb_dist_f)
-
-Group <- ifelse(rownames(pcadat_K562_50kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_K562_50kb_dist_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_K562_50kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_K562_50kb_dist_f <- cbind.data.frame(pcadat_K562_50kb_dist_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_K562_50kb_dist_f[,-(dim(pcadat_K562_50kb_dist_f)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_50kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_K562_50kb_dist_f[,-(dim(pcadat_K562_50kb_dist_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_50kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_K562_50kb_dist_f[,-(dim(pcadat_K562_50kb_dist_f2)[2])], 4),
-         data=pcadat_K562_50kb_dist_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
+                                          "perc"), collapse = "|"),"", 
+                                  colnames(x))}
+
+colnames(pcadat_K562_50kb_count) <- cleancolnames(pcadat_K562_50kb_count)
+colnames(pcadat_K562_50kb_perc) <- cleancolnames(pcadat_K562_50kb_perc)
+colnames(pcadat_K562_50kb_dist) <- cleancolnames(pcadat_K562_50kb_dist)
+
+pcadat_K562_50kb_count <- t(pcadat_K562_50kb_count)
+pcadat_K562_50kb_perc <- t(pcadat_K562_50kb_perc)
+pcadat_K562_50kb_dist <- t(pcadat_K562_50kb_dist)
+
+#pcadat_K562_50kb_count <- data.frame(pcadat_K562_50kb_count)
+#pcadat_K562_50kb_perc <- data.frame(pcadat_K562_50kb_perc)
+#pcadat_K562_50kb_dist <- data.frame(pcadat_K562_50kb_dist)
+
+#pcadat_K562_50kb_count$Type <- "Counts"
+#pcadat_K562_50kb_perc$Type <- "Percent"
+#pcadat_K562_50kb_dist$Type <- "Distance"
+
+```
+
+#### Chromatin States
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_K562_50kb_count_chromstates <- pcadat_K562_50kb_count[which(rownames(pcadat_K562_50kb_count) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_50kb_count_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_50kb_count_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_50kb_count_chromstates)-1)*sum(apply(pcadat_K562_50kb_count_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_50kb_count_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_50kb_count_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_50kb_count_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_K562_50kb_perc_chromstates <- pcadat_K562_50kb_perc[which(rownames(pcadat_K562_50kb_perc) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_50kb_perc_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_50kb_perc_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_50kb_perc_chromstates)-1)*sum(apply(pcadat_K562_50kb_perc_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_50kb_perc_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_50kb_perc_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_50kb_perc_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_K562_50kb_dist_chromstates <- pcadat_K562_50kb_dist[which(rownames(pcadat_K562_50kb_dist) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_50kb_dist_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_50kb_dist_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_50kb_dist_chromstates)-1)*sum(apply(pcadat_K562_50kb_dist_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_50kb_dist_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_50kb_dist_chromstates, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_50kb_dist_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### Histone Modifications
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_K562_50kb_count_histones <- pcadat_K562_50kb_count[which(rownames(pcadat_K562_50kb_count) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_50kb_count_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_50kb_count_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_50kb_count_histones)-1)*sum(apply(pcadat_K562_50kb_count_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_50kb_count_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_50kb_count_histones, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_50kb_count_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_K562_50kb_perc_histones <- pcadat_K562_50kb_perc[which(rownames(pcadat_K562_50kb_perc) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_50kb_perc_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_50kb_perc_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_50kb_perc_histones)-1)*sum(apply(pcadat_K562_50kb_perc_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_50kb_perc_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_50kb_perc_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_50kb_perc_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_K562_50kb_dist_histones <- pcadat_K562_50kb_dist[which(rownames(pcadat_K562_50kb_dist) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_50kb_dist_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_50kb_dist_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_50kb_dist_histones)-1)*sum(apply(pcadat_K562_50kb_dist_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_50kb_dist_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_50kb_dist_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_50kb_dist_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/K562"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_K562_50kb_count_tfbs <- pcadat_K562_50kb_count[which(rownames(pcadat_K562_50kb_count) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_50kb_count_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_50kb_count_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_50kb_count_tfbs)-1)*sum(apply(pcadat_K562_50kb_count_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_K562_50kb_count_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_50kb_count_tfbs, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_50kb_count_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_K562_50kb_perc_tfbs <- pcadat_K562_50kb_perc[which(rownames(pcadat_K562_50kb_perc) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_50kb_perc_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_50kb_perc_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_50kb_perc_tfbs)-1)*sum(apply(pcadat_K562_50kb_perc_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_K562_50kb_perc_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_50kb_perc_tfbs, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_50kb_perc_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_K562_50kb_dist_tfbs <- pcadat_K562_50kb_dist[which(rownames(pcadat_K562_50kb_dist) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_50kb_dist_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_50kb_dist_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_50kb_dist_tfbs)-1)*sum(apply(pcadat_K562_50kb_dist_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_K562_50kb_dist_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_50kb_dist_tfbs, 5, nstart=25, iter.max = 1000),
+         data=pcadat_K562_50kb_dist_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
 ```
@@
 
-#### Overlap counts data
-
 ```{r}
 pcadat_K562_100kb_count <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/PCA/pcadat_K562_100kb_count.rds")
-dim(pcadat_K562_100kb_count)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_K562_100kb_count , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_K562_100kb_count_f <- pcadat_K562_100kb_count[, -which(colnames(pcadat_K562_100kb_count) %in% nzvar)]
-
-dim(pcadat_K562_100kb_count) 
-dim(pcadat_K562_100kb_count_f)
-
-colnames(pcadat_K562_100kb_count_f) <- gsub(paste(c("`", 
+pcadat_K562_100kb_perc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/PCA/pcadat_K562_100kb_perc.rds")
+pcadat_K562_100kb_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/PCA/pcadat_K562_100kb_dist.rds")
+
+#performing log2 transformation on distances
+pcadat_K562_100kb_dist <- apply(pcadat_K562_100kb_dist,2,function(x){log(x + 1, base=2)})
+
+cleancolnames <- function(x){gsub(paste(c("`", 
                                           "_",
-                                                    "-",
-                                                    "K562", 
+                                          #"-",
+                                          #"K562", 
+                                          #"Haib", 
+                                          #"Sydh",
+                                          #"Uta",
+                                          #"Uw",
+                                          #"Broad",
+                                          #"Uchicago",
                                           "dist",
                                           "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_100kb_count_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_K562_100kb_count_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_K562_100kb_count_f),
-          #rowsep=1:nrow(pcadat_K562_100kb_count_f),
-          keysize = 1)
-
-#PCA
-pcadat_K562_100kb_count_f <- t(pcadat_K562_100kb_count_f)
-
-Group <- ifelse(rownames(pcadat_K562_100kb_count_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_K562_100kb_count_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_K562_100kb_count_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_K562_100kb_count_f <- cbind.data.frame(pcadat_K562_100kb_count_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_K562_100kb_count_f[,-(dim(pcadat_K562_100kb_count_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_100kb_count_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_K562_100kb_count_f[,-(dim(pcadat_K562_100kb_count_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_100kb_count_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_K562_100kb_count_f[,-(dim(pcadat_K562_100kb_count_f2)[2])], 4),
-         data=pcadat_K562_100kb_count_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-
-```
-
-#### Overlap percent data
-
-```{r}
-pcadat_K562_100kb_perc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/PCA/pcadat_K562_100kb_perc.rds")
-dim(pcadat_K562_100kb_perc)
-
-#filtering low variance predictors
-nzv <- nearZeroVar(pcadat_K562_100kb_perc , saveMetrics= TRUE)
-nzvar <- rownames(nzv[nzv$nzv,])
-nzvar
-
-pcadat_K562_100kb_perc_f <- pcadat_K562_100kb_perc[, -which(colnames(pcadat_K562_100kb_perc) %in% nzvar)]
-
-dim(pcadat_K562_100kb_perc) 
-dim(pcadat_K562_100kb_perc_f)
-
-colnames(pcadat_K562_100kb_perc_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "K562", 
-                                                    "dist",
-                                                    "perc",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_100kb_perc_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_K562_100kb_perc_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_K562_100kb_perc_f),
-          #rowsep=1:nrow(pcadat_K562_100kb_perc_f),
-          keysize = 1)
-
-#PCA
-pcadat_K562_100kb_perc_f <- t(pcadat_K562_100kb_perc_f)
-
-Group <- ifelse(rownames(pcadat_K562_100kb_perc_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_K562_100kb_perc_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_K562_100kb_perc_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_K562_100kb_perc_f <- cbind.data.frame(pcadat_K562_100kb_perc_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_K562_100kb_perc_f[,-(dim(pcadat_K562_100kb_perc_f2)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_100kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_K562_100kb_perc_f[,-(dim(pcadat_K562_100kb_perc_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_100kb_perc_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_K562_100kb_perc_f[,-(dim(pcadat_K562_100kb_perc_f2)[2])], 4),
-         data=pcadat_K562_100kb_perc_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-
-```
-
-#### Distance data
-
-```{r}
-pcadat_K562_100kb_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/PCA/pcadat_K562_100kb_dist.rds")
-dim(pcadat_K562_100kb_dist)
-
-#performing log2 transformation
-pcadat_K562_100kb_dist <- apply(pcadat_K562_100kb_dist,2,function(x){log(x + 1, base=2)})
-
-#filtering low variance predictors
-#nzv <- nearZeroVar(pcadat_K562_100kb_dist , saveMetrics= TRUE)
-#nzvar <- rownames(nzv[nzv$nzv,])
-#nzvar
-#no near zero variance predictors
-
-pcadat_K562_100kb_dist_f <- pcadat_K562_100kb_dist[, -which(colnames(pcadat_K562_100kb_dist) %in% nzvar)]
-pcadat_K562_100kb_dist_f <- pcadat_K562_100kb_dist
-
-dim(pcadat_K562_100kb_dist) 
-dim(pcadat_K562_100kb_dist_f)
-
-colnames(pcadat_K562_100kb_dist_f) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "K562", 
-                                                    "dist",
-                                                    "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadat_K562_100kb_dist_f))
-
-#heatmap 
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-heatmap.2(pcadat_K562_100kb_dist_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadat_K562_100kb_dist_f),
-          #rowsep=1:nrow(pcadat_K562_100kb_dist_f),
-          keysize = 1)
-
-#PCA
-pcadat_K562_100kb_dist_f <- t(pcadat_K562_100kb_dist_f)
-
-Group <- ifelse(rownames(pcadat_K562_100kb_dist_f) %in% cs, "Chromatin State", ###chromatin states
-                                            ifelse(rownames(pcadat_K562_100kb_dist_f)=="DNase", "DNase I", ###dnase
-                                                   ifelse(rownames(pcadat_K562_100kb_dist_f) %in% hm, "Histone Modification", ###histone modifications
-                                                          "TFBS"))) ###transcription factor binding sites
-
-pcadat_K562_100kb_dist_f <- cbind.data.frame(pcadat_K562_100kb_dist_f, Group)
-##with loadings
-autoplot(prcomp(pcadat_K562_100kb_dist_f[,-(dim(pcadat_K562_100kb_dist_f)[2])]),
-         loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_100kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##without loadings
-autoplot(prcomp(pcadat_K562_100kb_dist_f[,-(dim(pcadat_K562_100kb_dist_f)[2])]),
-         #loadings = TRUE,
-         label = TRUE, 
-         label.size = 3,
-         label.repel=T,
-         data=pcadat_K562_100kb_dist_f,
-         colour='Group') +
-  theme_bw()
-##kmeans clustering algorithm to group annotations
-set.seed(1)
-autoplot(kmeans(pcadat_K562_100kb_dist_f[,-(dim(pcadat_K562_100kb_dist_f2)[2])], 4),
-         data=pcadat_K562_100kb_dist_f,
-         frame = TRUE,
-         frame.type = 'norm',
-         label = TRUE, 
-         label.size = 3, 
-         #colour='Group',
-         label.repel=T) + 
-  theme_bw()
-```
-
-## Saving plots
+                                          "perc"), collapse = "|"),"", 
+                                  colnames(x))}
+
+colnames(pcadat_K562_100kb_count) <- cleancolnames(pcadat_K562_100kb_count)
+colnames(pcadat_K562_100kb_perc) <- cleancolnames(pcadat_K562_100kb_perc)
+colnames(pcadat_K562_100kb_dist) <- cleancolnames(pcadat_K562_100kb_dist)
+
+pcadat_K562_100kb_count <- t(pcadat_K562_100kb_count)
+pcadat_K562_100kb_perc <- t(pcadat_K562_100kb_perc)
+pcadat_K562_100kb_dist <- t(pcadat_K562_100kb_dist)
+
+#pcadat_K562_100kb_count <- data.frame(pcadat_K562_100kb_count)
+#pcadat_K562_100kb_perc <- data.frame(pcadat_K562_100kb_perc)
+#pcadat_K562_100kb_dist <- data.frame(pcadat_K562_100kb_dist)
+
+#pcadat_K562_100kb_count$Type <- "Counts"
+#pcadat_K562_100kb_perc$Type <- "Percent"
+#pcadat_K562_100kb_dist$Type <- "Distance"
+
+```
+
+#### Chromatin States
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_K562_100kb_count_chromstates <- pcadat_K562_100kb_count[which(rownames(pcadat_K562_100kb_count) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_100kb_count_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_100kb_count_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_100kb_count_chromstates)-1)*sum(apply(pcadat_K562_100kb_count_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_100kb_count_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_100kb_count_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_100kb_count_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_K562_100kb_perc_chromstates <- pcadat_K562_100kb_perc[which(rownames(pcadat_K562_100kb_perc) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_100kb_perc_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_100kb_perc_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_100kb_perc_chromstates)-1)*sum(apply(pcadat_K562_100kb_perc_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_100kb_perc_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_100kb_perc_chromstates, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_100kb_perc_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_K562_100kb_dist_chromstates <- pcadat_K562_100kb_dist[which(rownames(pcadat_K562_100kb_dist) %in% chromstatevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_100kb_dist_chromstates),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_100kb_dist_chromstates),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_100kb_dist_chromstates)-1)*sum(apply(pcadat_K562_100kb_dist_chromstates,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_100kb_dist_chromstates,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_100kb_dist_chromstates, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_100kb_dist_chromstates,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### Histone Modifications
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_K562_100kb_count_histones <- pcadat_K562_100kb_count[which(rownames(pcadat_K562_100kb_count) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_100kb_count_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_100kb_count_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_100kb_count_histones)-1)*sum(apply(pcadat_K562_100kb_count_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_100kb_count_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_100kb_count_histones, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_100kb_count_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_K562_100kb_perc_histones <- pcadat_K562_100kb_perc[which(rownames(pcadat_K562_100kb_perc) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_100kb_perc_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_100kb_perc_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_100kb_perc_histones)-1)*sum(apply(pcadat_K562_100kb_perc_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_100kb_perc_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_100kb_perc_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_100kb_perc_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_K562_100kb_dist_histones <- pcadat_K562_100kb_dist[which(rownames(pcadat_K562_100kb_dist) %in% histonevars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_100kb_dist_histones),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_100kb_dist_histones),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_100kb_dist_histones)-1)*sum(apply(pcadat_K562_100kb_dist_histones,2,var))
+  for (i in 2:5) wss[i] <- sum(kmeans(pcadat_K562_100kb_dist_histones,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:5, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_100kb_dist_histones, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_100kb_dist_histones,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/K562"))
+```
+
+##### Overlap Counts
+
+```{r}
+pcadat_K562_100kb_count_tfbs <- pcadat_K562_100kb_count[which(rownames(pcadat_K562_100kb_count) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_100kb_count_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_100kb_count_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_100kb_count_tfbs)-1)*sum(apply(pcadat_K562_100kb_count_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_K562_100kb_count_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_100kb_count_tfbs, 3, nstart=25, iter.max = 1000),
+         data=pcadat_K562_100kb_count_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+##### Overlap Percents
+
+```{r}
+pcadat_K562_100kb_perc_tfbs <- pcadat_K562_100kb_perc[which(rownames(pcadat_K562_100kb_perc) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_100kb_perc_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_100kb_perc_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_100kb_perc_tfbs)-1)*sum(apply(pcadat_K562_100kb_perc_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_K562_100kb_perc_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_100kb_perc_tfbs, 4, nstart=25, iter.max = 1000),
+         data=pcadat_K562_100kb_perc_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+#####Distance
+
+```{r}
+pcadat_K562_100kb_dist_tfbs <- pcadat_K562_100kb_dist[which(rownames(pcadat_K562_100kb_dist) %in% tfbsvars),]
+
+##with loadings
+autoplot(prcomp(pcadat_K562_100kb_dist_tfbs),
+         loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##without loadings
+autoplot(prcomp(pcadat_K562_100kb_dist_tfbs),
+         #loadings = TRUE,
+         label = TRUE, 
+         label.size = 3,
+         label.repel=T) +
+  theme_bw()
+##kmeans clustering algorithm to group annotations
+wss <- (nrow(pcadat_K562_100kb_dist_tfbs)-1)*sum(apply(pcadat_K562_100kb_dist_tfbs,2,var))
+  for (i in 2:50) wss[i] <- sum(kmeans(pcadat_K562_100kb_dist_tfbs,
+                                       centers=i, nstart=25, iter.max = 1000)$withinss)
+plot(1:50, wss, type="b", xlab="Number of Clusters",
+     ylab="Within groups sum of squares")
+
+set.seed(1)
+autoplot(kmeans(pcadat_K562_100kb_dist_tfbs, 5, nstart=25, iter.max = 1000),
+         data=pcadat_K562_100kb_dist_tfbs,
+         #frame = TRUE,
+         #frame.type = 'norm',
+         label = TRUE, 
+         label.size = 3, 
+         label.repel=T,
+         label.show.legend = FALSE) + 
+  #guides(fill=FALSE) +
+  theme_bw()
+
+```
+
+## Saving plots clustered annotation plots
 
@@
 ```
+
+# Clustering TADs

### 2019-03-22 Scripts/evaluating_correlations.Rmd
editted correlation script

@@
 ```
+
+## Stratifying by annotation group (using pca data--flanked TAD boundaries)
+
+###GM12878
+
+####10kb
+
+##### Counts
+
+```{r}
+pcadat_gm12878_10kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_count.rds")
+
+colnames(pcadat_gm12878_10kb_count) <- gsub("_count","",colnames(pcadat_gm12878_10kb_count))
+```
+
+######Chromstates
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+
+pcadat_gm12878_10kb_count_chromstates <- pcadat_gm12878_10kb_count[,which(colnames(pcadat_gm12878_10kb_count) %in% chromstatevars)]
+
+colnames(pcadat_gm12878_10kb_count_chromstates) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_count_chromstates))
+
+cormat <- cor(pcadat_gm12878_10kb_count_chromstates, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+######Histones
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+
+pcadat_gm12878_10kb_count_histones <- pcadat_gm12878_10kb_count[,which(colnames(pcadat_gm12878_10kb_count) %in% histonevars)]
+
+colnames(pcadat_gm12878_10kb_count_histones) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_count_histones))
+
+cormat <- cor(pcadat_gm12878_10kb_count_histones, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+
+pcadat_gm12878_10kb_count_tfbs <- pcadat_gm12878_10kb_count[,which(colnames(pcadat_gm12878_10kb_count) %in% tfbsvars)]
+
+colnames(pcadat_gm12878_10kb_count_tfbs) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_count_tfbs))
+
+cormat <- cor(pcadat_gm12878_10kb_count_tfbs, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .5,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### Percents
+
+```{r}
+pcadat_gm12878_10kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_perc.rds")
+
+colnames(pcadat_gm12878_10kb_perc) <- gsub("_perc","",colnames(pcadat_gm12878_10kb_perc))
+```
+
+######Chromstates
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+
+pcadat_gm12878_10kb_perc_chromstates <- pcadat_gm12878_10kb_perc[,which(colnames(pcadat_gm12878_10kb_perc) %in% chromstatevars)]
+
+colnames(pcadat_gm12878_10kb_perc_chromstates) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_perc_chromstates))
+
+cormat <- cor(pcadat_gm12878_10kb_perc_chromstates, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+######Histones
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+
+pcadat_gm12878_10kb_perc_histones <- pcadat_gm12878_10kb_perc[,which(colnames(pcadat_gm12878_10kb_perc) %in% histonevars)]
+
+colnames(pcadat_gm12878_10kb_perc_histones) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_perc_histones))
+
+cormat <- cor(pcadat_gm12878_10kb_perc_histones, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+
+pcadat_gm12878_10kb_perc_tfbs <- pcadat_gm12878_10kb_perc[,which(colnames(pcadat_gm12878_10kb_perc) %in% tfbsvars)]
+
+colnames(pcadat_gm12878_10kb_perc_tfbs) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_perc_tfbs))
+
+cormat <- cor(pcadat_gm12878_10kb_perc_tfbs, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .5,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+####Distances
+
+```{r}
+pcadat_gm12878_10kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_dist.rds")
+
+colnames(pcadat_gm12878_10kb_dist) <- gsub("_dist","",colnames(pcadat_gm12878_10kb_dist))
+```
+
+######Chromstates
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+
+pcadat_gm12878_10kb_dist_chromstates <- pcadat_gm12878_10kb_dist[,which(colnames(pcadat_gm12878_10kb_dist) %in% chromstatevars)]
+
+colnames(pcadat_gm12878_10kb_dist_chromstates) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_dist_chromstates))
+
+cormat <- cor(pcadat_gm12878_10kb_dist_chromstates, method = "pearson")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+######Histones
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+
+pcadat_gm12878_10kb_dist_histones <- pcadat_gm12878_10kb_dist[,which(colnames(pcadat_gm12878_10kb_dist) %in% histonevars)]
+
+colnames(pcadat_gm12878_10kb_dist_histones) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_dist_histones))
+
+cormat <- cor(pcadat_gm12878_10kb_dist_histones, method = "pearson")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+
+pcadat_gm12878_10kb_dist_tfbs <- pcadat_gm12878_10kb_dist[,which(colnames(pcadat_gm12878_10kb_dist) %in% tfbsvars)]
+
+colnames(pcadat_gm12878_10kb_dist_tfbs) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_dist_tfbs))
+
+cormat <- cor(pcadat_gm12878_10kb_dist_tfbs, method = "pearson")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .5,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+####25kb
+
+##### Counts
+
+```{r}
+pcadat_gm12878_25kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_count.rds")
+
+colnames(pcadat_gm12878_25kb_count) <- gsub("_count","",colnames(pcadat_gm12878_25kb_count))
+```
+
+######Chromstates
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+
+pcadat_gm12878_25kb_count_chromstates <- pcadat_gm12878_25kb_count[,which(colnames(pcadat_gm12878_25kb_count) %in% chromstatevars)]
+
+colnames(pcadat_gm12878_25kb_count_chromstates) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_count_chromstates))
+
+cormat <- cor(pcadat_gm12878_25kb_count_chromstates, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+######Histones
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+
+pcadat_gm12878_25kb_count_histones <- pcadat_gm12878_25kb_count[,which(colnames(pcadat_gm12878_25kb_count) %in% histonevars)]
+
+colnames(pcadat_gm12878_25kb_count_histones) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_count_histones))
+
+cormat <- cor(pcadat_gm12878_25kb_count_histones, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+
+pcadat_gm12878_25kb_count_tfbs <- pcadat_gm12878_25kb_count[,which(colnames(pcadat_gm12878_25kb_count) %in% tfbsvars)]
+
+colnames(pcadat_gm12878_25kb_count_tfbs) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_count_tfbs))
+
+cormat <- cor(pcadat_gm12878_25kb_count_tfbs, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .5,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### Percents
+
+```{r}
+pcadat_gm12878_25kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_perc.rds")
+
+colnames(pcadat_gm12878_25kb_perc) <- gsub("_perc","",colnames(pcadat_gm12878_25kb_perc))
+```
+
+######Chromstates
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+
+pcadat_gm12878_25kb_perc_chromstates <- pcadat_gm12878_25kb_perc[,which(colnames(pcadat_gm12878_25kb_perc) %in% chromstatevars)]
+
+colnames(pcadat_gm12878_25kb_perc_chromstates) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_perc_chromstates))
+
+cormat <- cor(pcadat_gm12878_25kb_perc_chromstates, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+######Histones
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+
+pcadat_gm12878_25kb_perc_histones <- pcadat_gm12878_25kb_perc[,which(colnames(pcadat_gm12878_25kb_perc) %in% histonevars)]
+
+colnames(pcadat_gm12878_25kb_perc_histones) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_perc_histones))
+
+cormat <- cor(pcadat_gm12878_25kb_perc_histones, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+
+pcadat_gm12878_25kb_perc_tfbs <- pcadat_gm12878_25kb_perc[,which(colnames(pcadat_gm12878_25kb_perc) %in% tfbsvars)]
+
+colnames(pcadat_gm12878_25kb_perc_tfbs) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_perc_tfbs))
+
+cormat <- cor(pcadat_gm12878_25kb_perc_tfbs, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .5,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+####Distances
+
+```{r}
+pcadat_gm12878_25kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_dist.rds")
+
+colnames(pcadat_gm12878_25kb_dist) <- gsub("_dist","",colnames(pcadat_gm12878_25kb_dist))
+```
+
+######Chromstates
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+
+pcadat_gm12878_25kb_dist_chromstates <- pcadat_gm12878_25kb_dist[,which(colnames(pcadat_gm12878_25kb_dist) %in% chromstatevars)]
+
+colnames(pcadat_gm12878_25kb_dist_chromstates) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_dist_chromstates))
+
+cormat <- cor(pcadat_gm12878_25kb_dist_chromstates, method = "pearson")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+######Histones
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+
+pcadat_gm12878_25kb_dist_histones <- pcadat_gm12878_25kb_dist[,which(colnames(pcadat_gm12878_25kb_dist) %in% histonevars)]
+
+colnames(pcadat_gm12878_25kb_dist_histones) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_dist_histones))
+
+cormat <- cor(pcadat_gm12878_25kb_dist_histones, method = "pearson")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+
+pcadat_gm12878_25kb_dist_tfbs <- pcadat_gm12878_25kb_dist[,which(colnames(pcadat_gm12878_25kb_dist) %in% tfbsvars)]
+
+colnames(pcadat_gm12878_25kb_dist_tfbs) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_dist_tfbs))
+
+cormat <- cor(pcadat_gm12878_25kb_dist_tfbs, method = "pearson")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .5,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+####50kb
+
+##### Counts
+
+```{r}
+pcadat_gm12878_50kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_count.rds")
+
+colnames(pcadat_gm12878_50kb_count) <- gsub("_count","",colnames(pcadat_gm12878_50kb_count))
+```
+
+######Chromstates
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+
+pcadat_gm12878_50kb_count_chromstates <- pcadat_gm12878_50kb_count[,which(colnames(pcadat_gm12878_50kb_count) %in% chromstatevars)]
+
+colnames(pcadat_gm12878_50kb_count_chromstates) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_count_chromstates))
+
+cormat <- cor(pcadat_gm12878_50kb_count_chromstates, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+######Histones
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+
+pcadat_gm12878_50kb_count_histones <- pcadat_gm12878_50kb_count[,which(colnames(pcadat_gm12878_50kb_count) %in% histonevars)]
+
+colnames(pcadat_gm12878_50kb_count_histones) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_count_histones))
+
+cormat <- cor(pcadat_gm12878_50kb_count_histones, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+
+pcadat_gm12878_50kb_count_tfbs <- pcadat_gm12878_50kb_count[,which(colnames(pcadat_gm12878_50kb_count) %in% tfbsvars)]
+
+colnames(pcadat_gm12878_50kb_count_tfbs) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_count_tfbs))
+
+cormat <- cor(pcadat_gm12878_50kb_count_tfbs, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .5,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### Percents
+
+```{r}
+pcadat_gm12878_50kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_perc.rds")
+
+colnames(pcadat_gm12878_50kb_perc) <- gsub("_perc","",colnames(pcadat_gm12878_50kb_perc))
+```
+
+######Chromstates
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+
+pcadat_gm12878_50kb_perc_chromstates <- pcadat_gm12878_50kb_perc[,which(colnames(pcadat_gm12878_50kb_perc) %in% chromstatevars)]
+
+colnames(pcadat_gm12878_50kb_perc_chromstates) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_perc_chromstates))
+
+cormat <- cor(pcadat_gm12878_50kb_perc_chromstates, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+######Histones
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+
+pcadat_gm12878_50kb_perc_histones <- pcadat_gm12878_50kb_perc[,which(colnames(pcadat_gm12878_50kb_perc) %in% histonevars)]
+
+colnames(pcadat_gm12878_50kb_perc_histones) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_perc_histones))
+
+cormat <- cor(pcadat_gm12878_50kb_perc_histones, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+
+pcadat_gm12878_50kb_perc_tfbs <- pcadat_gm12878_50kb_perc[,which(colnames(pcadat_gm12878_50kb_perc) %in% tfbsvars)]
+
+colnames(pcadat_gm12878_50kb_perc_tfbs) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_perc_tfbs))
+
+cormat <- cor(pcadat_gm12878_50kb_perc_tfbs, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .5,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+####Distances
+
+```{r}
+pcadat_gm12878_50kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_dist.rds")
+
+colnames(pcadat_gm12878_50kb_dist) <- gsub("_dist","",colnames(pcadat_gm12878_50kb_dist))
+```
+
+######Chromstates
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+
+pcadat_gm12878_50kb_dist_chromstates <- pcadat_gm12878_50kb_dist[,which(colnames(pcadat_gm12878_50kb_dist) %in% chromstatevars)]
+
+colnames(pcadat_gm12878_50kb_dist_chromstates) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_dist_chromstates))
+
+cormat <- cor(pcadat_gm12878_50kb_dist_chromstates, method = "pearson")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+######Histones
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+
+pcadat_gm12878_50kb_dist_histones <- pcadat_gm12878_50kb_dist[,which(colnames(pcadat_gm12878_50kb_dist) %in% histonevars)]
+
+colnames(pcadat_gm12878_50kb_dist_histones) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_dist_histones))
+
+cormat <- cor(pcadat_gm12878_50kb_dist_histones, method = "pearson")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+
+pcadat_gm12878_50kb_dist_tfbs <- pcadat_gm12878_50kb_dist[,which(colnames(pcadat_gm12878_50kb_dist) %in% tfbsvars)]
+
+colnames(pcadat_gm12878_50kb_dist_tfbs) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_dist_tfbs))
+
+cormat <- cor(pcadat_gm12878_50kb_dist_tfbs, method = "pearson")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .5,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+####100kb
+
+##### Counts
+
+```{r}
+pcadat_gm12878_100kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_count.rds")
+
+colnames(pcadat_gm12878_100kb_count) <- gsub("_count","",colnames(pcadat_gm12878_100kb_count))
+```
+
+######Chromstates
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+
+pcadat_gm12878_100kb_count_chromstates <- pcadat_gm12878_100kb_count[,which(colnames(pcadat_gm12878_100kb_count) %in% chromstatevars)]
+
+colnames(pcadat_gm12878_100kb_count_chromstates) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_count_chromstates))
+
+cormat <- cor(pcadat_gm12878_100kb_count_chromstates, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+######Histones
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+
+pcadat_gm12878_100kb_count_histones <- pcadat_gm12878_100kb_count[,which(colnames(pcadat_gm12878_100kb_count) %in% histonevars)]
+
+colnames(pcadat_gm12878_100kb_count_histones) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_count_histones))
+
+cormat <- cor(pcadat_gm12878_100kb_count_histones, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+
+pcadat_gm12878_100kb_count_tfbs <- pcadat_gm12878_100kb_count[,which(colnames(pcadat_gm12878_100kb_count) %in% tfbsvars)]
+
+colnames(pcadat_gm12878_100kb_count_tfbs) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_count_tfbs))
+
+cormat <- cor(pcadat_gm12878_100kb_count_tfbs, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .5,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### Percents
+
+```{r}
+pcadat_gm12878_100kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_perc.rds")
+
+colnames(pcadat_gm12878_100kb_perc) <- gsub("_perc","",colnames(pcadat_gm12878_100kb_perc))
+```
+
+######Chromstates
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+
+pcadat_gm12878_100kb_perc_chromstates <- pcadat_gm12878_100kb_perc[,which(colnames(pcadat_gm12878_100kb_perc) %in% chromstatevars)]
+
+colnames(pcadat_gm12878_100kb_perc_chromstates) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_perc_chromstates))
+
+cormat <- cor(pcadat_gm12878_100kb_perc_chromstates, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+######Histones
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+
+pcadat_gm12878_100kb_perc_histones <- pcadat_gm12878_100kb_perc[,which(colnames(pcadat_gm12878_100kb_perc) %in% histonevars)]
+
+colnames(pcadat_gm12878_100kb_perc_histones) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_perc_histones))
+
+cormat <- cor(pcadat_gm12878_100kb_perc_histones, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+
+pcadat_gm12878_100kb_perc_tfbs <- pcadat_gm12878_100kb_perc[,which(colnames(pcadat_gm12878_100kb_perc) %in% tfbsvars)]
+
+colnames(pcadat_gm12878_100kb_perc_tfbs) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_perc_tfbs))
+
+cormat <- cor(pcadat_gm12878_100kb_perc_tfbs, method = "spearman")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .5,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+####Distances
+
+```{r}
+pcadat_gm12878_100kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_dist.rds")
+
+colnames(pcadat_gm12878_100kb_dist) <- gsub("_dist","",colnames(pcadat_gm12878_100kb_dist))
+```
+
+######Chromstates
+
+```{r}
+chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+
+pcadat_gm12878_100kb_dist_chromstates <- pcadat_gm12878_100kb_dist[,which(colnames(pcadat_gm12878_100kb_dist) %in% chromstatevars)]
+
+colnames(pcadat_gm12878_100kb_dist_chromstates) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_dist_chromstates))
+
+cormat <- cor(pcadat_gm12878_100kb_dist_chromstates, method = "pearson")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+######Histones
+
+```{r}
+histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+
+pcadat_gm12878_100kb_dist_histones <- pcadat_gm12878_100kb_dist[,which(colnames(pcadat_gm12878_100kb_dist) %in% histonevars)]
+
+colnames(pcadat_gm12878_100kb_dist_histones) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_dist_histones))
+
+cormat <- cor(pcadat_gm12878_100kb_dist_histones, method = "pearson")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+##### TFBS
+
+```{r}
+tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+
+pcadat_gm12878_100kb_dist_tfbs <- pcadat_gm12878_100kb_dist[,which(colnames(pcadat_gm12878_100kb_dist) %in% tfbsvars)]
+
+colnames(pcadat_gm12878_100kb_dist_tfbs) <- gsub(paste(c("Gm12878",
+                          "-",
+                          "_",
+                          "count",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_dist_tfbs))
+
+cormat <- cor(pcadat_gm12878_100kb_dist_tfbs, method = "pearson")
+
+corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .5,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+```
+
+#### Saving GM12878 Correlation Plots
+
+```{r}
+
+corfunction <- function(resolution, predictortype, annotation){
+
+}
+
+```

### 2019-03-22 Scripts/evaluating_correlations.Rmd
saving gm12878 and k562 corr plots

@@
 
-corfunction <- function(resolution, predictortype, annotation){
-
+corfunction <- function(cl, resolution, predictortype, annotation){
+  #set up variable names to subset
+  chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+  histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+  if(cl=="GM12878"){
+    tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+  } else {
+    tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/k562"))
   }
 
-```
+  if(cl=="GM12878"){
+    datadir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA", 
+                    "/pcadat_gm12878_", resolution, "_", predictortype, ".rds",
+                    sep="")
+  }else{datadir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA", 
+                    "/pcadat_", cl, "_", resolution, "_", predictortype, ".rds",
+                    sep="")}
+
+  data <- readRDS(datadir)
+  colnames(data) <- gsub(paste("_", predictortype, sep=""),"",colnames(data))
+
+  if(annotation=="chromstates"){
+    data <- data[,which(colnames(data) %in% chromstatevars)];
+    colnames(data) <- gsub(paste(c("Gm12878", "K562",
+                          "-",
+                          "_",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(data))
+  } else if(annotation=="histones"){
+    data <- data[,which(colnames(data) %in% histonevars)];
+    colnames(data) <- gsub(paste(c("Gm12878", "K562",
+                          "-",
+                          "_",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(data))
+  } else if(annotation=="tfbs"){
+    data <- data[,which(colnames(data) %in% tfbsvars)];
+    colnames(data) <- gsub(paste(c("Gm12878", "K562",
+                          "-",
+                          "_",
+                          "Haib",
+                          "Sydh",
+                          "Uta",
+                          "Uw",
+                          "Broad",
+                          "Uchicago"), collapse = "|"),"", colnames(data))
+  }
+
+  if(predictortype=="count" | predictortype=="perc"){
+    cormat <- cor(data, method = "spearman")
+  } else {
+    cormat <- cor(data, method = "pearson")
+  }
+
+  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/correlation_plots/", 
+                       cl, resolution, predictortype, annotation,
+                       ".png", sep=""),
+      width=11, height=8, units="in", res = 300)
+  corrplot(cormat, 
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .5,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+  dev.off()
+
+}
+
+corfunction(cl = "GM12878", resolution = "10kb", predictortype = "count", annotation = "chromstates")
+corfunction(cl = "GM12878", resolution = "10kb", predictortype = "count", annotation = "histones")
+corfunction(cl = "GM12878", resolution = "10kb", predictortype = "count", annotation = "tfbs")
+
+corfunction(cl = "GM12878", resolution = "10kb", predictortype = "perc", annotation = "chromstates")
+corfunction(cl = "GM12878", resolution = "10kb", predictortype = "perc", annotation = "histones")
+corfunction(cl = "GM12878", resolution = "10kb", predictortype = "perc", annotation = "tfbs")
+
+corfunction(cl = "GM12878", resolution = "10kb", predictortype = "dist", annotation = "chromstates")
+corfunction(cl = "GM12878", resolution = "10kb", predictortype = "dist", annotation = "histones")
+corfunction(cl = "GM12878", resolution = "10kb", predictortype = "dist", annotation = "tfbs")
+
+corfunction(cl = "GM12878", resolution = "25kb", predictortype = "count", annotation = "chromstates")
+corfunction(cl = "GM12878", resolution = "25kb", predictortype = "count", annotation = "histones")
+corfunction(cl = "GM12878", resolution = "25kb", predictortype = "count", annotation = "tfbs")
+
+corfunction(cl = "GM12878", resolution = "25kb", predictortype = "perc", annotation = "chromstates")
+corfunction(cl = "GM12878", resolution = "25kb", predictortype = "perc", annotation = "histones")
+corfunction(cl = "GM12878", resolution = "25kb", predictortype = "perc", annotation = "tfbs")
+
+corfunction(cl = "GM12878", resolution = "25kb", predictortype = "dist", annotation = "chromstates")
+corfunction(cl = "GM12878", resolution = "25kb", predictortype = "dist", annotation = "histones")
+corfunction(cl = "GM12878", resolution = "25kb", predictortype = "dist", annotation = "tfbs")
+
+corfunction(cl = "GM12878", resolution = "50kb", predictortype = "count", annotation = "chromstates")
+corfunction(cl = "GM12878", resolution = "50kb", predictortype = "count", annotation = "histones")
+corfunction(cl = "GM12878", resolution = "50kb", predictortype = "count", annotation = "tfbs")
+
+corfunction(cl = "GM12878", resolution = "50kb", predictortype = "perc", annotation = "chromstates")
+corfunction(cl = "GM12878", resolution = "50kb", predictortype = "perc", annotation = "histones")
+corfunction(cl = "GM12878", resolution = "50kb", predictortype = "perc", annotation = "tfbs")
+
+corfunction(cl = "GM12878", resolution = "50kb", predictortype = "dist", annotation = "chromstates")
+corfunction(cl = "GM12878", resolution = "50kb", predictortype = "dist", annotation = "histones")
+corfunction(cl = "GM12878", resolution = "50kb", predictortype = "dist", annotation = "tfbs")
+
+corfunction(cl = "GM12878", resolution = "100kb", predictortype = "count", annotation = "chromstates")
+corfunction(cl = "GM12878", resolution = "100kb", predictortype = "count", annotation = "histones")
+corfunction(cl = "GM12878", resolution = "100kb", predictortype = "count", annotation = "tfbs")
+
+corfunction(cl = "GM12878", resolution = "100kb", predictortype = "perc", annotation = "chromstates")
+corfunction(cl = "GM12878", resolution = "100kb", predictortype = "perc", annotation = "histones")
+corfunction(cl = "GM12878", resolution = "100kb", predictortype = "perc", annotation = "tfbs")
+
+corfunction(cl = "GM12878", resolution = "100kb", predictortype = "dist", annotation = "chromstates")
+corfunction(cl = "GM12878", resolution = "100kb", predictortype = "dist", annotation = "histones")
+corfunction(cl = "GM12878", resolution = "100kb", predictortype = "dist", annotation = "tfbs")
+
+```
+
+#### Saving K562 Correlation Plots
+
+```{r}
+corfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "chromstates")
+corfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "histones")
+corfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "tfbs")
+
+corfunction(cl = "K562", resolution = "25kb", predictortype = "perc", annotation = "chromstates")
+corfunction(cl = "K562", resolution = "25kb", predictortype = "perc", annotation = "histones")
+corfunction(cl = "K562", resolution = "25kb", predictortype = "perc", annotation = "tfbs")
+
+corfunction(cl = "K562", resolution = "25kb", predictortype = "dist", annotation = "chromstates")
+corfunction(cl = "K562", resolution = "25kb", predictortype = "dist", annotation = "histones")
+corfunction(cl = "K562", resolution = "25kb", predictortype = "dist", annotation = "tfbs")
+
+corfunction(cl = "K562", resolution = "50kb", predictortype = "count", annotation = "chromstates")
+corfunction(cl = "K562", resolution = "50kb", predictortype = "count", annotation = "histones")
+corfunction(cl = "K562", resolution = "50kb", predictortype = "count", annotation = "tfbs")
+
+corfunction(cl = "K562", resolution = "50kb", predictortype = "perc", annotation = "chromstates")
+corfunction(cl = "K562", resolution = "50kb", predictortype = "perc", annotation = "histones")
+corfunction(cl = "K562", resolution = "50kb", predictortype = "perc", annotation = "tfbs")
+
+corfunction(cl = "K562", resolution = "50kb", predictortype = "dist", annotation = "chromstates")
+corfunction(cl = "K562", resolution = "50kb", predictortype = "dist", annotation = "histones")
+corfunction(cl = "K562", resolution = "50kb", predictortype = "dist", annotation = "tfbs")
+
+corfunction(cl = "K562", resolution = "100kb", predictortype = "count", annotation = "chromstates")
+corfunction(cl = "K562", resolution = "100kb", predictortype = "count", annotation = "histones")
+corfunction(cl = "K562", resolution = "100kb", predictortype = "count", annotation = "tfbs")
+
+corfunction(cl = "K562", resolution = "100kb", predictortype = "perc", annotation = "chromstates")
+corfunction(cl = "K562", resolution = "100kb", predictortype = "perc", annotation = "histones")
+corfunction(cl = "K562", resolution = "100kb", predictortype = "perc", annotation = "tfbs")
+
+corfunction(cl = "K562", resolution = "100kb", predictortype = "dist", annotation = "chromstates")
+corfunction(cl = "K562", resolution = "100kb", predictortype = "dist", annotation = "histones")
+corfunction(cl = "K562", resolution = "100kb", predictortype = "dist", annotation = "tfbs")
+
+```

### 2019-03-22 Scripts/evaluating_pca.Rmd
including grouping by kmedoid clustering in pca plots

@@
 library(ggfortify)
+library(fpc)
 ```
@@
 ```{r}
-fileslst <- c(paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"), "/Ensemble/PCA/pcadat_GM12878_", 
-                    c("10kb", "25kb", "50kb", "100kb"), 
-                    "_count.rds",sep=""),
-              paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
-                    c("10kb", "25kb", "50kb", "100kb"), 
-                    "_perc.rds",sep=""),
-              paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
-                    c("10kb", "25kb", "50kb", "100kb"), 
-                    "_dist.rds",sep=""),
-              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_K562_", 
-                    c("10kb", "25kb", "50kb", "100kb"), 
-                    "_count.rds",sep=""),
-              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_K562_", 
-                    c("10kb", "25kb", "50kb", "100kb"), 
-                    "_perc.rds",sep=""),
-              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_K562_", 
-                    c("10kb", "25kb", "50kb", "100kb"), 
-                    "_dist.rds",sep=""))
-
-#file names for heatmaps
-heatnames <- c(paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_heatmap.png", sep=""),
-               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_heatmap.png", sep=""),
-               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_heatmap.png", sep=""),
-               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_heatmap.png", sep=""),
-               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_heatmap.png", sep=""),
-               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_heatmap.png", sep=""))
-
-#file names for pca plots
-scorepnames <- c(paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_scoreplots.png", sep=""),
-               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_scoreplots.png", sep=""),
-               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_scoreplots.png", sep=""),
-               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_scoreplots.png", sep=""),
-               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_scoreplots.png", sep=""),
-               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_scoreplots.png", sep=""))
-
-##create annotation groups
-cs <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
-                 sep = "",
-                 collapse = "|"),
-           "", 
-           list.files("Z:/TAD_data_analysis/annotations/BroadHMM")))
-hm <- unique(gsub(paste(c("Gm12878-", "K562-", ".bed"), 
-                 sep = "",
-                 collapse = "|"),
-           "", 
-           list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")))
-
-for(i in 1:length(fileslst)){
-  print(i)
-  pcadata <- readRDS(fileslst[i])
-
-  #performing log2 transformation only for distance predictor types
-  if(grepl("_dist", colnames(pcadata)[1])){
-    pcadata <- apply(pcadata,2,function(x){log(x + 1, base=2)})
+pcaplotfunction <- function(cl, resolution, predictortype, annotation){
+
+  #set up variable names to subset
+  chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))
+  histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))
+  if(cl=="GM12878"){
+    tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))
+  } else {
+    tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/k562"))
   }
 
-  #filtering low variance predictors
-  nzv <- nearZeroVar(pcadata, saveMetrics= TRUE)
-  nzvar <- rownames(nzv[nzv$nzv,])
-  if(length(nzvar) > 0){ 
-    pcadata_f <- pcadata[, -which(colnames(pcadata) %in% nzvar)]
-    }else{pcadata_f <- pcadata}
-
-  #cleaning column names
-  colnames(pcadata_f) <- gsub(paste(c("`", 
+  if(cl=="GM12878"){
+    datadir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA", 
+                    "/pcadat_gm12878_", resolution, "_", predictortype, ".rds",
+                    sep="")
+  }else{datadir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA", 
+                        "/pcadat_", cl, "_", resolution, "_", predictortype, ".rds",
+                        sep="")}
+
+  data <- readRDS(datadir)
+
+  if(predictortype=="dist"){
+    #performing log2 transformation on distances
+    data <- apply(data,2,function(x){log(x + 1, base=2)})
+  }
+
+  colnames(data) <- gsub(paste("_", predictortype, sep=""),"",colnames(data))
+
+  data <- t(data)
+
+  if(annotation=="chromstates"){
+    data <- data[which(rownames(data) %in% chromstatevars),];
+    rownames(data) <- gsub(paste(c("Gm12878", "K562",
+                                   "-",
                                    "_",
-                                                    "-",
-                                                    "Gm12878",
-                                                    "K562", 
-                                                    "dist",
-                                                    "count",
-                                                    "perc",
                                    "Haib",
@@
                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", colnames(pcadata_f))
-
-  #heatmap 
-  my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
-  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", heatnames[i], sep=""),
+                                   "Uchicago"), collapse = "|"),"", rownames(data))
+  } else if(annotation=="histones"){
+    data <- data[which(rownames(data) %in% histonevars),];
+    rownames(data) <- gsub(paste(c("Gm12878", "K562",
+                                   "-",
+                                   "_",
+                                   "Haib",
+                                   "Sydh",
+                                   "Uta",
+                                   "Uw",
+                                   "Broad",
+                                   "Uchicago"), collapse = "|"),"", rownames(data))
+  } else if(annotation=="tfbs"){
+    data <- data[which(rownames(data) %in% tfbsvars),];
+    rownames(data) <- gsub(paste(c("Gm12878", "K562",
+                                   "-",
+                                   "_",
+                                   "Haib",
+                                   "Sydh",
+                                   "Uta",
+                                   "Uw",
+                                   "Broad",
+                                   "Uchicago"), collapse = "|"),"", rownames(data))
+  }
+
+  #determine optimal number of clusters
+  pamk.best <- pamk(data)
+
+  #perform PAM clustering
+  pam.med <- pam(data, k = pamk.best$nc, diss = FALSE,
+                 metric = "manhattan", 
+                 #medoids = NULL, 
+                 #stand = FALSE, 
+                 cluster.only = FALSE,
+                 do.swap = TRUE,
+                 keep.diss = FALSE,
+                 keep.data = FALSE,
+                 pamonce = FALSE, 
+                 trace.lev = 0)
+
+  data <- data.frame(data)
+  data$Cluster <- factor(pam.med$clustering)
+  data$Medoid <- factor(ifelse(rownames(data) %in% rownames(pam.med$medoids), "Center", "Other"),
+                        levels=c("Other", "Center"))
+
+  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", 
+                       cl, resolution, predictortype, annotation,
+                       ".png", sep=""),
       width=11, height=8, units="in", res = 300)
-  heatmap.2(pcadata_f,
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=TRUE,
-          dendrogram="column",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.5,
-          labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #sepwidth=c(0.001,0.001),
-          #sepcolor="black",
-          #colsep=1:ncol(pcadata_f),
-          #rowsep=1:nrow(pcadata_f),
-          keysize = 1) 
+  autoplot(prcomp(data[,-c(dim(data)[2]-1,dim(data)[2])]),
+           data=data,
+           #loadings = TRUE,
+           label = TRUE, 
+           label.size = 3,
+           label.repel=T, 
+           colour="Cluster",
+           shape="Medoid",
+           label.show.legend = FALSE) +
+    theme_bw()
   dev.off()
 
-  #PCA
-  #pcadata_f <- t(pcadata_f)
-  #Group <- ifelse(rownames(pcadata_f) %in% cs, "Chromatin State", ###chromatin states
-  #                                          ifelse(rownames(pcadata_f)=="DNase", "DNase I", ###dnase
-  #                                                 ifelse(rownames(pcadata_f) %in% hm, "Histone Modification", ###histone modifications
-  #                                                        "TFBS"))) ###transcription factor binding sites
-  #pcadata_f <- cbind.data.frame(pcadata_f, Group)
-  #
-  ###Plots without loadings
-  #p <- autoplot(prcomp(pcadata_f[,-(dim(pcadata_f)[2])]),
-  #       #loadings = TRUE,
-  #       label = TRUE, 
-  #       label.size = 3,
-  #       label.repel=T,
-  #       data=pcadata_f,
-  #       colour='Group',
-  #       label.show.legend = FALSE) +
-  #theme_bw()
-
-  #ggsave(p, filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", 
-  #                           scorepnames[i], sep=""),
-  #       width=8, height=11, units="in", dpi=300)
-
 }
@@
 
+###GM12878
+
+```{r}
+pcaplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "count", annotation = "chromstates")
+pcaplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "count", annotation = "histones")
+pcaplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "count", annotation = "tfbs")
+
+pcaplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "perc", annotation = "chromstates")
+pcaplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "perc", annotation = "histones")
+pcaplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "perc", annotation = "tfbs")
+
+pcaplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "dist", annotation = "chromstates")
+pcaplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "dist", annotation = "histones")
+pcaplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "dist", annotation = "tfbs")
+
+pcaplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "count", annotation = "chromstates")
+pcaplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "count", annotation = "histones")
+pcaplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "count", annotation = "tfbs")
+
+pcaplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "perc", annotation = "chromstates")
+pcaplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "perc", annotation = "histones")
+pcaplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "perc", annotation = "tfbs")
+
+pcaplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "dist", annotation = "chromstates")
+pcaplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "dist", annotation = "histones")
+pcaplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "dist", annotation = "tfbs")
+
+pcaplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "count", annotation = "chromstates")
+pcaplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "count", annotation = "histones")
+pcaplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "count", annotation = "tfbs")
+
+pcaplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "perc", annotation = "chromstates")
+pcaplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "perc", annotation = "histones")
+pcaplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "perc", annotation = "tfbs")
+
+pcaplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "dist", annotation = "chromstates")
+pcaplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "dist", annotation = "histones")
+pcaplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "dist", annotation = "tfbs")
+
+pcaplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "count", annotation = "chromstates")
+pcaplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "count", annotation = "histones")
+pcaplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "count", annotation = "tfbs")
+
+pcaplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "perc", annotation = "chromstates")
+pcaplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "perc", annotation = "histones")
+pcaplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "perc", annotation = "tfbs")
+
+pcaplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "dist", annotation = "chromstates")
+pcaplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "dist", annotation = "histones")
+pcaplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "dist", annotation = "tfbs")
+
+```
+
+###K562
+
+```{r}
+
+```
+
 # Clustering TADs

### 2019-03-22 Scripts/evaluating_correlations.Rmd
editted correlation script

@@
   data <- readRDS(datadir)
+
+  if(predictortype=="dist"){
+    #performing log2 transformation on distances
+    data <- apply(data,2,function(x){log(x + 1, base=2)})
+  }
+
   colnames(data) <- gsub(paste("_", predictortype, sep=""),"",colnames(data))
@@
 ```{r}
+corfunction(cl = "K562", resolution = "10kb", predictortype = "count", annotation = "chromstates")
+corfunction(cl = "K562", resolution = "10kb", predictortype = "count", annotation = "histones")
+corfunction(cl = "K562", resolution = "10kb", predictortype = "count", annotation = "tfbs")
+
+corfunction(cl = "K562", resolution = "10kb", predictortype = "perc", annotation = "chromstates")
+corfunction(cl = "K562", resolution = "10kb", predictortype = "perc", annotation = "histones")
+corfunction(cl = "K562", resolution = "10kb", predictortype = "perc", annotation = "tfbs")
+
+corfunction(cl = "K562", resolution = "10kb", predictortype = "dist", annotation = "chromstates")
+corfunction(cl = "K562", resolution = "10kb", predictortype = "dist", annotation = "histones")
+corfunction(cl = "K562", resolution = "10kb", predictortype = "dist", annotation = "tfbs")
+
 corfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "chromstates")

### 2019-03-22 Scripts/evaluating_pca.Rmd
editted pca script

@@
       width=11, height=8, units="in", res = 300)
+  print({
     autoplot(prcomp(data[,-c(dim(data)[2]-1,dim(data)[2])]),
@@
     theme_bw()
+  })
   dev.off()
@@
 ```{r}
+pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "count", annotation = "chromstates")
+pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "count", annotation = "histones")
+pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "count", annotation = "tfbs")
+
+pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "perc", annotation = "chromstates")
+pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "perc", annotation = "histones")
+pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "perc", annotation = "tfbs")
+
+pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "dist", annotation = "chromstates")
+pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "dist", annotation = "histones")
+pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "dist", annotation = "tfbs")
+
+pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "chromstates")
+pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "histones")
+pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "tfbs")
+
+pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "perc", annotation = "chromstates")
+pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "perc", annotation = "histones")
+pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "perc", annotation = "tfbs")
+
+pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "dist", annotation = "chromstates")
+pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "dist", annotation = "histones")
+pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "dist", annotation = "tfbs")
+
+pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "count", annotation = "chromstates")
+pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "count", annotation = "histones")
+pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "count", annotation = "tfbs")
+
+pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "perc", annotation = "chromstates")
+pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "perc", annotation = "histones")
+pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "perc", annotation = "tfbs")
+
+pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "dist", annotation = "chromstates")
+pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "dist", annotation = "histones")
+pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "dist", annotation = "tfbs")
+
+pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "count", annotation = "chromstates")
+pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "count", annotation = "histones")
+pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "count", annotation = "tfbs")
+
+pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "perc", annotation = "chromstates")
+pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "perc", annotation = "histones")
+pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "perc", annotation = "tfbs")
+
+pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "dist", annotation = "chromstates")
+pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "dist", annotation = "histones")
+pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "dist", annotation = "tfbs")
 

### 2019-03-24 Scripts/evaluating_pca.Rmd
add clustering by tad

@@
 
-  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", 
+  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/cluster_by_annotation/", 
                        cl, resolution, predictortype, annotation,
@@
 # Clustering TADs
+
+```{r}
+tadclusterplotfunction <- function(cl, resolution, predictortype, cluster){
+
+  if(cl=="GM12878"){
+    datadir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA", 
+                    "/pcadat_gm12878_", resolution, "_", predictortype, ".rds",
+                    sep="")
+  }else{datadir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA", 
+                        "/pcadat_", cl, "_", resolution, "_", predictortype, ".rds",
+                        sep="")}
+
+  data <- readRDS(datadir)
+
+  if(predictortype=="dist"){
+    #performing log2 transformation on distances
+    data <- apply(data,2,function(x){log(x + 1, base=2)})
+  }
+
+  colnames(data) <- gsub(paste("_", predictortype, sep=""),"",colnames(data))
+
+  #determine optimal number of clusters
+  pamk.best <- pamk(data)
+
+  if(cluster=="kmedoids"){
+    #perform PAM clustering
+    clusters <- pam(data, k = pamk.best$nc, diss = FALSE,
+                   metric = "manhattan", 
+                   #medoids = NULL, 
+                   #stand = FALSE, 
+                   cluster.only = FALSE,
+                   do.swap = TRUE,
+                   keep.diss = FALSE,
+                   keep.data = FALSE,
+                   pamonce = FALSE, 
+                   trace.lev = 0)
+
+    data <- data.frame(data)
+    data$Cluster <- factor(clusters$clustering)
+    data$Medoid <- factor(ifelse(rownames(data) %in% rownames(clusters$medoids), "Center", "Other"),
+                          levels=c("Other", "Center"))
+  }else{
+    clusters <- kmeans(data, centers = pamk.best$nc, nstart = 25, iter.max = 1000)
+
+    data <- data.frame(data)
+    data$Cluster <- factor(clusters$cluster)
+    data$Medoid <- NA
+  }
+
+  data <- data.frame(data)
+
+  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/cluster_by_tad/", 
+                       cl, resolution, predictortype, annotation,
+                       ".png", sep=""),
+      width=11, height=8, units="in", res = 300)
+  print({
+    autoplot(prcomp(data[,-c(dim(data)[2]-1,dim(data)[2])]),
+             data=data,
+             #loadings = TRUE,
+             label = FALSE, 
+             #label.size = 3,
+             #label.repel=T, 
+             colour="Cluster",
+             #shape="Medoid",
+             size=3,
+             frame = TRUE, 
+             frame.type = 'norm',
+             label.show.legend = FALSE) +
+      theme_bw()
+  })
+  dev.off()
+
+}
+
+```

### 2019-03-24 Scripts/evaluating_pca.Rmd
saving plots

@@
 
-## Saving plots clustered annotation plots
+## Saving clustered annotation plots
 
@@
 
-  data <- data.frame(data)
-
   png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/cluster_by_tad/", 
-                       cl, resolution, predictortype, annotation,
+                       cl, resolution, predictortype, cluster,
                        ".png", sep=""),
@@
              #shape="Medoid",
-             size=3,
-             frame = TRUE, 
-             frame.type = 'norm',
+             #size=3,
+             #frame = TRUE, 
+             #frame.type = 'norm',
              label.show.legend = FALSE) +
@@
 ```
+
+### Saving clustered tad plots
+
+####GM12878
+
+```{r}
+tadclusterplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "count", cluster = "kmedoids")
+tadclusterplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "count", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "perc", cluster = "kmedoids")
+tadclusterplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "perc", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "dist", cluster = "kmedoids")
+tadclusterplotfunction(cl = "GM12878", resolution = "10kb", predictortype = "dist", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "count", cluster = "kmedoids")
+tadclusterplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "count", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "perc", cluster = "kmedoids")
+tadclusterplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "perc", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "dist", cluster = "kmedoids")
+tadclusterplotfunction(cl = "GM12878", resolution = "25kb", predictortype = "dist", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "count", cluster = "kmedoids")
+tadclusterplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "count", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "perc", cluster = "kmedoids")
+tadclusterplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "perc", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "dist", cluster = "kmedoids")
+tadclusterplotfunction(cl = "GM12878", resolution = "50kb", predictortype = "dist", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "count", cluster = "kmedoids")
+tadclusterplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "count", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "perc", cluster = "kmedoids")
+tadclusterplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "perc", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "dist", cluster = "kmedoids")
+tadclusterplotfunction(cl = "GM12878", resolution = "100kb", predictortype = "dist", cluster = "kmeans")
+
+```
+
+#### K562
+
+```{r}
+tadclusterplotfunction(cl = "K562", resolution = "10kb", predictortype = "count", cluster = "kmedoids")
+tadclusterplotfunction(cl = "K562", resolution = "10kb", predictortype = "count", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "K562", resolution = "10kb", predictortype = "perc", cluster = "kmedoids")
+tadclusterplotfunction(cl = "K562", resolution = "10kb", predictortype = "perc", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "K562", resolution = "10kb", predictortype = "dist", cluster = "kmedoids")
+tadclusterplotfunction(cl = "K562", resolution = "10kb", predictortype = "dist", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "K562", resolution = "25kb", predictortype = "count", cluster = "kmedoids")
+tadclusterplotfunction(cl = "K562", resolution = "25kb", predictortype = "count", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "K562", resolution = "25kb", predictortype = "perc", cluster = "kmedoids")
+tadclusterplotfunction(cl = "K562", resolution = "25kb", predictortype = "perc", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "K562", resolution = "25kb", predictortype = "dist", cluster = "kmedoids")
+tadclusterplotfunction(cl = "K562", resolution = "25kb", predictortype = "dist", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "K562", resolution = "50kb", predictortype = "count", cluster = "kmedoids")
+tadclusterplotfunction(cl = "K562", resolution = "50kb", predictortype = "count", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "K562", resolution = "50kb", predictortype = "perc", cluster = "kmedoids")
+tadclusterplotfunction(cl = "K562", resolution = "50kb", predictortype = "perc", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "K562", resolution = "50kb", predictortype = "dist", cluster = "kmedoids")
+tadclusterplotfunction(cl = "K562", resolution = "50kb", predictortype = "dist", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "K562", resolution = "100kb", predictortype = "count", cluster = "kmedoids")
+tadclusterplotfunction(cl = "K562", resolution = "100kb", predictortype = "count", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "K562", resolution = "100kb", predictortype = "perc", cluster = "kmedoids")
+tadclusterplotfunction(cl = "K562", resolution = "100kb", predictortype = "perc", cluster = "kmeans")
+
+tadclusterplotfunction(cl = "K562", resolution = "100kb", predictortype = "dist", cluster = "kmedoids")
+tadclusterplotfunction(cl = "K562", resolution = "100kb", predictortype = "dist", cluster = "kmeans")
+
+```

### 2019-03-28 Manuscript/Supplementary/supplementary_legends.Rmd
editted supp legends

--- 2019-03-11 Manuscript/Supplementary/supplementary_legends.Rmd
@@
 
-**Supplementary Figure 3.
-Heatmaps illustrating the variable reduction.** An elastic-net algorithm was used to improve computational efficiency and reduce noise for both the GM12878 (A) and K562 (B) cell lines.
-Features that were regularized and subsequently removed from downstream modeling are denoted in white, while the features that were not regularized and kept for further analyses are denoted in red.
-Each vertical region is made up of a particular data resolution (10 kb, 25 kb, 50kb, and 100 kb), resampling technique (None, RUS, ROS, and SMOTE), and predictor type (OC, OP, and Distance).
-The yellow lines separate each of the three predictor types.
+**Supplementary Figure 2A. Correlograms separated by genomic annotation category for overlap count predictor types, using 10 kb resolution data, on the GM12878 cell line**
 
-**Supplementary Figrue 4.
+**Supplementary Figure 2B. Correlograms separated by genomic annotation category for overlap percent predictor types, using 10 kb resolution data, on the GM12878 cell line**
+
+**Supplementary Figure 2C. Correlograms separated by genomic annotation category for $log_{2}$ distance predictor types, using 10 kb resolution data, on the GM12878 cell line**
+
+**Supplementary Figure 3A. Correlograms separated by genomic annotation category for overlap count predictor types, using 25 kb resolution data, on the GM12878 cell line**
+
+**Supplementary Figure 3B. Correlograms separated by genomic annotation category for overlap percent predictor types, using 25 kb resolution data, on the GM12878 cell line**
+
+**Supplementary Figure 3C. Correlograms separated by genomic annotation category for $log_{2}$ distance predictor types, using 25 kb resolution data, on the GM12878 cell line**
+
+**Supplementary Figure 4A. Correlograms separated by genomic annotation category for overlap count predictor types, using 50 kb resolution data, on the GM12878 cell line**
+
+**Supplementary Figure 4B. Correlograms separated by genomic annotation category for overlap percent predictor types, using 50 kb resolution data, on the GM12878 cell line**
+
+**Supplementary Figure 4C. Correlograms separated by genomic annotation category for $log_{2}$ distance predictor types, using 50 kb resolution data, on the GM12878 cell line**
+
+**Supplementary Figure 5A. Correlograms separated by genomic annotation category for overlap count predictor types, using 100 kb resolution data, on the GM12878 cell line**
+
+**Supplementary Figure 5B. Correlograms separated by genomic annotation category for overlap percent predictor types, using 100 kb resolution data, on the GM12878 cell line**
+
+**Supplementary Figure 5C. Correlograms separated by genomic annotation category for $log_{2}$ distance predictor types, using 100 kb resolution data, on the GM12878 cell line**
+
+**Supplementary Figure 6A. Correlograms separated by genomic annotation category for overlap count predictor types, using 10 kb resolution data, on the K562 cell line**
+
+**Supplementary Figure 6B. Correlograms separated by genomic annotation category for overlap percent predictor types, using 10 kb resolution data, on the K562 cell line**
+
+**Supplementary Figure 6C. Correlograms separated by genomic annotation category for $log_{2}$ distance predictor types, using 10 kb resolution data, on the K562 cell line**
+
+**Supplementary Figure 7A. Correlograms separated by genomic annotation category for overlap count predictor types, using 25 kb resolution data, on the K562 cell line**
+
+**Supplementary Figure 7B. Correlograms separated by genomic annotation category for overlap percent predictor types, using 25 kb resolution data, on the K562 cell line**
+
+**Supplementary Figure 7C. Correlograms separated by genomic annotation category for $log_{2}$ distance predictor types, using 25 kb resolution data, on the K562 cell line**
+
+**Supplementary Figure 8A. Correlograms separated by genomic annotation category for overlap count predictor types, using 50 kb resolution data, on the K562 cell line**
+
+**Supplementary Figure 8B. Correlograms separated by genomic annotation category for overlap percent predictor types, using 50 kb resolution data, on the K562 cell line**
+
+**Supplementary Figure 8C. Correlograms separated by genomic annotation category for $log_{2}$ distance predictor types, using 50 kb resolution data, on the K562 cell line**
+
+**Supplementary Figure 9A. Correlograms separated by genomic annotation category for overlap count predictor types, using 100 kb resolution data, on the K562 cell line**
+
+**Supplementary Figure 9B. Correlograms separated by genomic annotation category for overlap percent predictor types, using 100 kb resolution data, on the K562 cell line**
+
+**Supplementary Figure 9C. Correlograms separated by genomic annotation category for $log_{2}$ distance predictor types, using 100 kb resolution data, on the K562 cell line**
+
+**Supplementary Figure 10A. Heatmap illustrating which features were regularized using Elastic-Net for 10 kb resolution data applied to the GM12878 cell line.**
+
+**Supplementary Figure 10B. Heatmap illustrating which features were regularized using Elastic-Net for 25 kb resolution data applied to the GM12878 cell line.**
+
+**Supplementary Figure 10C. Heatmap illustrating which features were regularized using Elastic-Net for 50 kb resolution data applied to the GM12878 cell line.**
+
+**Supplementary Figure 10D. Heatmap illustrating which features were regularized using Elastic-Net for 100 kb resolution data applied to the GM12878 cell line.**
+
+**Supplementary Figure 11A. Heatmap illustrating which features were regularized using Elastic-Net for 10 kb resolution data applied to the GM12878 cell line.**
+
+**Supplementary Figure 11B. Heatmap illustrating which features were regularized using Elastic-Net for 25 kb resolution data applied to the GM12878 cell line.**
+
+**Supplementary Figure 11C. Heatmap illustrating which features were regularized using Elastic-Net for 50 kb resolution data applied to the GM12878 cell line.**
+
+**Supplementary Figure 11D. Heatmap illustrating which features were regularized using Elastic-Net for 100 kb resolution data applied to the GM12878 cell line.**
+
+**Supplementary Figrue 12.
 Barplots comparing model performance for each predictor type across 25 kb, 50 kb, and 100 kb data resolutions** Model performances were evaluated using F1-scores, MCCs, and balanced accuracies for each of the 4 resampling techniques, across both the GM12878 (A-C) and K562 (D-F) cell lines.
@@
 
-**Figure 5.
+**Supplementary Figure 13.
 Line plots comparing models using the remaining resampling techniques with distance-type predictors.** Model performances were evaluated using F1-score, MCC, and balanced accuracy for each of the 4 data resolutions, across both the GM12878 (red, solid line) and K562 (blue; dashed line) cell lines.
@@
 
-**Figure 6.
+**Supplementary Figure 14.
 Variable importance of the top 20 most predictive genomic annotations for models using no resampling technique with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
@@
 
-**Figure 7.
+**Supplementary Figure 15.
 Variable importance of the top 20 most predictive genomic annotations for models using random over-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
@@
 
-**Figure 8.
+**Supplementary Figure 16.
 Variable importance of the top 20 most predictive genomic annotations for models using random under-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.

### 2019-03-28 Scripts/evaluating_feature_reduction.Rmd
editted script for evaluating elastic net

@@
 
-### G12878
+### GM12878
 
@@
                       enetcoefs_SMOTE_dist_10kb_gm12878[-1,1])
+
+enetcoefsmat[enetcoefsmat == 0] <- NA
+
+#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
+colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
+rownames(enetcoefsmat) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))
+
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
+
+```
+
+##### Overlap Counts
+
+```{r}
+heatmap.2(enetcoefsmat[,1:4],
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 1.5,
+          dendrogram="none",     # only draw a row dendrogram,
+          Rowv = FALSE,
+          Colv = FALSE,
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=1:4,
+          rowsep=0:nrow(enetcoefsmat)) 
+```
+
+#####Overlap Percents
+
+```{r}
+heatmap.2(enetcoefsmat[,5:8],
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 1.5,
+          dendrogram="row",     # only draw a row dendrogram,
+          #Rowv = FALSE,
+          #Colv = FALSE,
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=1:4,
+          rowsep=1:nrow(enetcoefsmat)) 
+```
+
+##### Distances
+
+```{r}
+heatmap.2(enetcoefsmat[,9:12],
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 1.5,
+          dendrogram="row",     # only draw a row dendrogram,
+          #Rowv = FALSE,
+          #Colv = FALSE,
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=1:4,
+          rowsep=1:nrow(enetcoefsmat)) 
+```
+
+#####All
+
+```{r}
+heatmap.2(enetcoefsmat,
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 1.5,
+          dendrogram="row",     # only draw a row dendrogram,
+          Rowv = TRUE,
+          Colv = FALSE,
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=0:12,
+          rowsep=0:nrow(enetcoefsmat)) 
+```
+
+#### 25kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/enetModel.rds")
+enetcoefs_none_oc_25kb_gm12878 <- coef(enetcoefs_none_oc_25kb_gm12878$finalModel, s=enetcoefs_none_oc_25kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_none_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/enetModel.rds")
+enetcoefs_none_op_25kb_gm12878 <- coef(enetcoefs_none_op_25kb_gm12878$finalModel, s=enetcoefs_none_op_25kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_none_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/enetModel.rds")
+enetcoefs_none_dist_25kb_gm12878 <- coef(enetcoefs_none_dist_25kb_gm12878$finalModel, s=enetcoefs_none_dist_25kb_gm12878$bestTune$lambda)
+
+#RUS
+##OC
+enetcoefs_RUS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/enetModel.rds")
+enetcoefs_RUS_oc_25kb_gm12878 <- coef(enetcoefs_RUS_oc_25kb_gm12878$finalModel, s=enetcoefs_RUS_oc_25kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_RUS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/enetModel.rds")
+enetcoefs_RUS_op_25kb_gm12878 <- coef(enetcoefs_RUS_op_25kb_gm12878$finalModel, s=enetcoefs_RUS_op_25kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_RUS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
+enetcoefs_RUS_dist_25kb_gm12878 <- coef(enetcoefs_RUS_dist_25kb_gm12878$finalModel, s=enetcoefs_RUS_dist_25kb_gm12878$bestTune$lambda)
+
+#ROS
+##OC
+enetcoefs_ROS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/enetModel.rds")
+enetcoefs_ROS_oc_25kb_gm12878 <- coef(enetcoefs_ROS_oc_25kb_gm12878$finalModel, s=enetcoefs_ROS_oc_25kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_ROS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/enetModel.rds")
+enetcoefs_ROS_op_25kb_gm12878 <- coef(enetcoefs_ROS_op_25kb_gm12878$finalModel, s=enetcoefs_ROS_op_25kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_ROS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
+enetcoefs_ROS_dist_25kb_gm12878 <- coef(enetcoefs_ROS_dist_25kb_gm12878$finalModel, s=enetcoefs_ROS_dist_25kb_gm12878$bestTune$lambda)
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
+enetcoefs_SMOTE_oc_25kb_gm12878 <- coef(enetcoefs_SMOTE_oc_25kb_gm12878$finalModel, s=enetcoefs_SMOTE_oc_25kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_SMOTE_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
+enetcoefs_SMOTE_op_25kb_gm12878 <- coef(enetcoefs_SMOTE_op_25kb_gm12878$finalModel, s=enetcoefs_SMOTE_op_25kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_SMOTE_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
+enetcoefs_SMOTE_dist_25kb_gm12878 <- coef(enetcoefs_SMOTE_dist_25kb_gm12878$finalModel, s=enetcoefs_SMOTE_dist_25kb_gm12878$bestTune$lambda)
+
+enetcoefsmat <- cbind(enetcoefs_none_oc_25kb_gm12878[-1,1], 
+                      enetcoefs_ROS_oc_25kb_gm12878[-1,1],
+                      enetcoefs_RUS_oc_25kb_gm12878[-1,1], 
+                      enetcoefs_SMOTE_oc_25kb_gm12878[-1,1],
+
+                      enetcoefs_none_op_25kb_gm12878[-1,1], 
+                      enetcoefs_ROS_op_25kb_gm12878[-1,1],
+                      enetcoefs_RUS_op_25kb_gm12878[-1,1], 
+                      enetcoefs_SMOTE_op_25kb_gm12878[-1,1],
+
+                      enetcoefs_none_dist_25kb_gm12878[-1,1],
+                      enetcoefs_ROS_dist_25kb_gm12878[-1,1],
+                      enetcoefs_RUS_dist_25kb_gm12878[-1,1],
+                      enetcoefs_SMOTE_dist_25kb_gm12878[-1,1])
 
@@
 ```{r}
-heatmap.2(enetcoefsmat[,9:12],
-          #cellnote = cormat,  # same data set for cell labels
-          #main = "Correlation", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          dendrogram="row",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.75,
-          #labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          sepwidth=c(0.001,0.001),
-          sepcolor="black",
-          colsep=1:4,
-          rowsep=1:nrow(enetcoefsmat),
-          keysize = 1) 
-```
-
-#### 25kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
-
-features <- names(train)[-1]
-features <- features[grep("dist", features)]
-features <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist", 
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", features)
-
-#None
-##OC
-enetcoefs_none_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/enetModel.rds")
-enetcoefs_none_oc_25kb_gm12878 <- coef(enetcoefs_none_oc_25kb_gm12878$finalModel, s=enetcoefs_none_oc_25kb_gm12878$bestTune$lambda)
-##OP
-enetcoefs_none_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/enetModel.rds")
-enetcoefs_none_op_25kb_gm12878 <- coef(enetcoefs_none_op_25kb_gm12878$finalModel, s=enetcoefs_none_op_25kb_gm12878$bestTune$lambda)
-##Distance
-enetcoefs_none_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/enetModel.rds")
-enetcoefs_none_dist_25kb_gm12878 <- coef(enetcoefs_none_dist_25kb_gm12878$finalModel, s=enetcoefs_none_dist_25kb_gm12878$bestTune$lambda)
-
-#RUS
-##OC
-enetcoefs_RUS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/enetModel.rds")
-enetcoefs_RUS_oc_25kb_gm12878 <- coef(enetcoefs_RUS_oc_25kb_gm12878$finalModel, s=enetcoefs_RUS_oc_25kb_gm12878$bestTune$lambda)
-##OP
-enetcoefs_RUS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/enetModel.rds")
-enetcoefs_RUS_op_25kb_gm12878 <- coef(enetcoefs_RUS_op_25kb_gm12878$finalModel, s=enetcoefs_RUS_op_25kb_gm12878$bestTune$lambda)
-##Distance
-enetcoefs_RUS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
-enetcoefs_RUS_dist_25kb_gm12878 <- coef(enetcoefs_RUS_dist_25kb_gm12878$finalModel, s=enetcoefs_RUS_dist_25kb_gm12878$bestTune$lambda)
-
-#ROS
-##OC
-enetcoefs_ROS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/enetModel.rds")
-enetcoefs_ROS_oc_25kb_gm12878 <- coef(enetcoefs_ROS_oc_25kb_gm12878$finalModel, s=enetcoefs_ROS_oc_25kb_gm12878$bestTune$lambda)
-##OP
-enetcoefs_ROS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/enetModel.rds")
-enetcoefs_ROS_op_25kb_gm12878 <- coef(enetcoefs_ROS_op_25kb_gm12878$finalModel, s=enetcoefs_ROS_op_25kb_gm12878$bestTune$lambda)
-##Distance
-enetcoefs_ROS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
-enetcoefs_ROS_dist_25kb_gm12878 <- coef(enetcoefs_ROS_dist_25kb_gm12878$finalModel, s=enetcoefs_ROS_dist_25kb_gm12878$bestTune$lambda)
-
-#SMOTE
-##OC
-enetcoefs_SMOTE_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
-enetcoefs_SMOTE_oc_25kb_gm12878 <- coef(enetcoefs_SMOTE_oc_25kb_gm12878$finalModel, s=enetcoefs_SMOTE_oc_25kb_gm12878$bestTune$lambda)
-##OP
-enetcoefs_SMOTE_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
-enetcoefs_SMOTE_op_25kb_gm12878 <- coef(enetcoefs_SMOTE_op_25kb_gm12878$finalModel, s=enetcoefs_SMOTE_op_25kb_gm12878$bestTune$lambda)
-##Distance
-enetcoefs_SMOTE_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
-enetcoefs_SMOTE_dist_25kb_gm12878 <- coef(enetcoefs_SMOTE_dist_25kb_gm12878$finalModel, s=enetcoefs_SMOTE_dist_25kb_gm12878$bestTune$lambda)
-
-enetcoefsmat <- cbind(enetcoefs_none_oc_25kb_gm12878[-1,1], 
-                      enetcoefs_ROS_oc_25kb_gm12878[-1,1],
-                      enetcoefs_RUS_oc_25kb_gm12878[-1,1], 
-                      enetcoefs_SMOTE_oc_25kb_gm12878[-1,1],
-
-                      enetcoefs_none_op_25kb_gm12878[-1,1], 
-                      enetcoefs_ROS_op_25kb_gm12878[-1,1],
-                      enetcoefs_RUS_op_25kb_gm12878[-1,1], 
-                      enetcoefs_SMOTE_op_25kb_gm12878[-1,1],
-
-                      enetcoefs_none_dist_25kb_gm12878[-1,1],
-                      enetcoefs_ROS_dist_25kb_gm12878[-1,1],
-                      enetcoefs_RUS_dist_25kb_gm12878[-1,1],
-                      enetcoefs_SMOTE_dist_25kb_gm12878[-1,1])
-
-enetcoefsmat[enetcoefsmat == 0] <- NA
-
-#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
-#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
-#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
-#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
-colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
-rownames(enetcoefsmat) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))
-
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
-
-```
-
-##### Overlap Counts
-
-```{r}
-heatmap.2(enetcoefsmat[,1:4],
-          #cellnote = cormat,  # same data set for cell labels
-          #main = "Correlation", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          dendrogram="row",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.75,
-          #labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          sepwidth=c(0.001,0.001),
-          sepcolor="black",
-          colsep=1:4,
-          rowsep=1:nrow(enetcoefsmat),
-          keysize = 1) 
-```
-
-#####Overlap Percents
-
-```{r}
-heatmap.2(enetcoefsmat[,5:8],
-          #cellnote = cormat,  # same data set for cell labels
-          #main = "Correlation", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          dendrogram="row",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.75,
-          #labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          sepwidth=c(0.001,0.001),
-          sepcolor="black",
-          colsep=1:4,
-          rowsep=1:nrow(enetcoefsmat),
-          keysize = 1) 
-```
-
-##### Distances
-
-```{r}
 my_palette2 <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
@@
 ```
+
+#####All
+
+```{r}
+heatmap.2(enetcoefsmat,
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 1.5,
+          dendrogram="row",     # only draw a row dendrogram,
+          Rowv = TRUE,
+          Colv = FALSE,
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=0:12,
+          rowsep=0:nrow(enetcoefsmat)) 
+```
+
+#### 50kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/enetModel.rds")
+enetcoefs_none_oc_50kb_gm12878 <- coef(enetcoefs_none_oc_50kb_gm12878$finalModel, s=enetcoefs_none_oc_50kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_none_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/enetModel.rds")
+enetcoefs_none_op_50kb_gm12878 <- coef(enetcoefs_none_op_50kb_gm12878$finalModel, s=enetcoefs_none_op_50kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_none_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/enetModel.rds")
+enetcoefs_none_dist_50kb_gm12878 <- coef(enetcoefs_none_dist_50kb_gm12878$finalModel, s=enetcoefs_none_dist_50kb_gm12878$bestTune$lambda)
+
+#RUS
+##OC
+enetcoefs_RUS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/enetModel.rds")
+enetcoefs_RUS_oc_50kb_gm12878 <- coef(enetcoefs_RUS_oc_50kb_gm12878$finalModel, s=enetcoefs_RUS_oc_50kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_RUS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/enetModel.rds")
+enetcoefs_RUS_op_50kb_gm12878 <- coef(enetcoefs_RUS_op_50kb_gm12878$finalModel, s=enetcoefs_RUS_op_50kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_RUS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
+enetcoefs_RUS_dist_50kb_gm12878 <- coef(enetcoefs_RUS_dist_50kb_gm12878$finalModel, s=enetcoefs_RUS_dist_50kb_gm12878$bestTune$lambda)
+
+#ROS
+##OC
+enetcoefs_ROS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/enetModel.rds")
+enetcoefs_ROS_oc_50kb_gm12878 <- coef(enetcoefs_ROS_oc_50kb_gm12878$finalModel, s=enetcoefs_ROS_oc_50kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_ROS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/enetModel.rds")
+enetcoefs_ROS_op_50kb_gm12878 <- coef(enetcoefs_ROS_op_50kb_gm12878$finalModel, s=enetcoefs_ROS_op_50kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_ROS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
+enetcoefs_ROS_dist_50kb_gm12878 <- coef(enetcoefs_ROS_dist_50kb_gm12878$finalModel, s=enetcoefs_ROS_dist_50kb_gm12878$bestTune$lambda)
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
+enetcoefs_SMOTE_oc_50kb_gm12878 <- coef(enetcoefs_SMOTE_oc_50kb_gm12878$finalModel, s=enetcoefs_SMOTE_oc_50kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_SMOTE_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
+enetcoefs_SMOTE_op_50kb_gm12878 <- coef(enetcoefs_SMOTE_op_50kb_gm12878$finalModel, s=enetcoefs_SMOTE_op_50kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_SMOTE_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
+enetcoefs_SMOTE_dist_50kb_gm12878 <- coef(enetcoefs_SMOTE_dist_50kb_gm12878$finalModel, s=enetcoefs_SMOTE_dist_50kb_gm12878$bestTune$lambda)
+
+enetcoefsmat <- cbind(enetcoefs_none_oc_50kb_gm12878[-1,1], 
+                      enetcoefs_ROS_oc_50kb_gm12878[-1,1],
+                      enetcoefs_RUS_oc_50kb_gm12878[-1,1], 
+                      enetcoefs_SMOTE_oc_50kb_gm12878[-1,1],
+
+                      enetcoefs_none_op_50kb_gm12878[-1,1], 
+                      enetcoefs_ROS_op_50kb_gm12878[-1,1],
+                      enetcoefs_RUS_op_50kb_gm12878[-1,1], 
+                      enetcoefs_SMOTE_op_50kb_gm12878[-1,1],
+
+                      enetcoefs_none_dist_50kb_gm12878[-1,1],
+                      enetcoefs_ROS_dist_50kb_gm12878[-1,1],
+                      enetcoefs_RUS_dist_50kb_gm12878[-1,1],
+                      enetcoefs_SMOTE_dist_50kb_gm12878[-1,1])
+
+enetcoefsmat[enetcoefsmat == 0] <- NA
+
+#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
+colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
+rownames(enetcoefsmat) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))
+
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
+
+```
+
+#####All
+
+```{r}
+heatmap.2(enetcoefsmat,
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 1.5,
+          dendrogram="row",     # only draw a row dendrogram,
+          Rowv = TRUE,
+          Colv = FALSE,
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=0:12,
+          rowsep=0:nrow(enetcoefsmat)) 
+```
+
+#### 100kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/enetModel.rds")
+enetcoefs_none_oc_100kb_gm12878 <- coef(enetcoefs_none_oc_100kb_gm12878$finalModel, s=enetcoefs_none_oc_100kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_none_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/enetModel.rds")
+enetcoefs_none_op_100kb_gm12878 <- coef(enetcoefs_none_op_100kb_gm12878$finalModel, s=enetcoefs_none_op_100kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_none_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/enetModel.rds")
+enetcoefs_none_dist_100kb_gm12878 <- coef(enetcoefs_none_dist_100kb_gm12878$finalModel, s=enetcoefs_none_dist_100kb_gm12878$bestTune$lambda)
+
+#RUS
+##OC
+enetcoefs_RUS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/enetModel.rds")
+enetcoefs_RUS_oc_100kb_gm12878 <- coef(enetcoefs_RUS_oc_100kb_gm12878$finalModel, s=enetcoefs_RUS_oc_100kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_RUS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/enetModel.rds")
+enetcoefs_RUS_op_100kb_gm12878 <- coef(enetcoefs_RUS_op_100kb_gm12878$finalModel, s=enetcoefs_RUS_op_100kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_RUS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
+enetcoefs_RUS_dist_100kb_gm12878 <- coef(enetcoefs_RUS_dist_100kb_gm12878$finalModel, s=enetcoefs_RUS_dist_100kb_gm12878$bestTune$lambda)
+
+#ROS
+##OC
+enetcoefs_ROS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/enetModel.rds")
+enetcoefs_ROS_oc_100kb_gm12878 <- coef(enetcoefs_ROS_oc_100kb_gm12878$finalModel, s=enetcoefs_ROS_oc_100kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_ROS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/enetModel.rds")
+enetcoefs_ROS_op_100kb_gm12878 <- coef(enetcoefs_ROS_op_100kb_gm12878$finalModel, s=enetcoefs_ROS_op_100kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_ROS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
+enetcoefs_ROS_dist_100kb_gm12878 <- coef(enetcoefs_ROS_dist_100kb_gm12878$finalModel, s=enetcoefs_ROS_dist_100kb_gm12878$bestTune$lambda)
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
+enetcoefs_SMOTE_oc_100kb_gm12878 <- coef(enetcoefs_SMOTE_oc_100kb_gm12878$finalModel, s=enetcoefs_SMOTE_oc_100kb_gm12878$bestTune$lambda)
+##OP
+enetcoefs_SMOTE_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
+enetcoefs_SMOTE_op_100kb_gm12878 <- coef(enetcoefs_SMOTE_op_100kb_gm12878$finalModel, s=enetcoefs_SMOTE_op_100kb_gm12878$bestTune$lambda)
+##Distance
+enetcoefs_SMOTE_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
+enetcoefs_SMOTE_dist_100kb_gm12878 <- coef(enetcoefs_SMOTE_dist_100kb_gm12878$finalModel, s=enetcoefs_SMOTE_dist_100kb_gm12878$bestTune$lambda)
+
+enetcoefsmat <- cbind(enetcoefs_none_oc_100kb_gm12878[-1,1], 
+                      enetcoefs_ROS_oc_100kb_gm12878[-1,1],
+                      enetcoefs_RUS_oc_100kb_gm12878[-1,1], 
+                      enetcoefs_SMOTE_oc_100kb_gm12878[-1,1],
+
+                      enetcoefs_none_op_100kb_gm12878[-1,1], 
+                      enetcoefs_ROS_op_100kb_gm12878[-1,1],
+                      enetcoefs_RUS_op_100kb_gm12878[-1,1], 
+                      enetcoefs_SMOTE_op_100kb_gm12878[-1,1],
+
+                      enetcoefs_none_dist_100kb_gm12878[-1,1],
+                      enetcoefs_ROS_dist_100kb_gm12878[-1,1],
+                      enetcoefs_RUS_dist_100kb_gm12878[-1,1],
+                      enetcoefs_SMOTE_dist_100kb_gm12878[-1,1])
+
+enetcoefsmat[enetcoefsmat == 0] <- NA
+
+#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
+colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
+rownames(enetcoefsmat) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "Gm12878", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))
+
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
+
+```
+
+#####All
+
+```{r}
+heatmap.2(enetcoefsmat,
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 1.5,
+          dendrogram="row",     # only draw a row dendrogram,
+          Rowv = TRUE,
+          Colv = FALSE,
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=0:12,
+          rowsep=0:nrow(enetcoefsmat)) 
+```

### 2019-03-28 Scripts/evaluating_feature_reduction.Rmd
added enet results for k562

@@
 ```
+
+### K562
+
+#### 10 kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/enetModel.rds")
+enetcoefs_none_oc_10kb_K562 <- coef(enetcoefs_none_oc_10kb_K562$finalModel, s=enetcoefs_none_oc_10kb_K562$bestTune$lambda)
+##OP
+enetcoefs_none_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/enetModel.rds")
+enetcoefs_none_op_10kb_K562 <- coef(enetcoefs_none_op_10kb_K562$finalModel, s=enetcoefs_none_op_10kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_none_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/enetModel.rds")
+enetcoefs_none_dist_10kb_K562 <- coef(enetcoefs_none_dist_10kb_K562$finalModel, s=enetcoefs_none_dist_10kb_K562$bestTune$lambda)
+
+#RUS
+##OC
+enetcoefs_RUS_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/enetModel.rds")
+enetcoefs_RUS_oc_10kb_K562 <- coef(enetcoefs_RUS_oc_10kb_K562$finalModel, s=enetcoefs_RUS_oc_10kb_K562$bestTune$lambda)
+##OP
+enetcoefs_RUS_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/enetModel.rds")
+enetcoefs_RUS_op_10kb_K562 <- coef(enetcoefs_RUS_op_10kb_K562$finalModel, s=enetcoefs_RUS_op_10kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_RUS_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
+enetcoefs_RUS_dist_10kb_K562 <- coef(enetcoefs_RUS_dist_10kb_K562$finalModel, s=enetcoefs_RUS_dist_10kb_K562$bestTune$lambda)
+
+#ROS
+##OC
+enetcoefs_ROS_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/enetModel.rds")
+enetcoefs_ROS_oc_10kb_K562 <- coef(enetcoefs_ROS_oc_10kb_K562$finalModel, s=enetcoefs_ROS_oc_10kb_K562$bestTune$lambda)
+##OP
+enetcoefs_ROS_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/enetModel.rds")
+enetcoefs_ROS_op_10kb_K562 <- coef(enetcoefs_ROS_op_10kb_K562$finalModel, s=enetcoefs_ROS_op_10kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_ROS_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
+enetcoefs_ROS_dist_10kb_K562 <- coef(enetcoefs_ROS_dist_10kb_K562$finalModel, s=enetcoefs_ROS_dist_10kb_K562$bestTune$lambda)
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
+enetcoefs_SMOTE_oc_10kb_K562 <- coef(enetcoefs_SMOTE_oc_10kb_K562$finalModel, s=enetcoefs_SMOTE_oc_10kb_K562$bestTune$lambda)
+##OP
+enetcoefs_SMOTE_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
+enetcoefs_SMOTE_op_10kb_K562 <- coef(enetcoefs_SMOTE_op_10kb_K562$finalModel, s=enetcoefs_SMOTE_op_10kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_SMOTE_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
+enetcoefs_SMOTE_dist_10kb_K562 <- coef(enetcoefs_SMOTE_dist_10kb_K562$finalModel, s=enetcoefs_SMOTE_dist_10kb_K562$bestTune$lambda)
+
+enetcoefsmat <- cbind(enetcoefs_none_oc_10kb_K562[-1,1], 
+                      enetcoefs_ROS_oc_10kb_K562[-1,1],
+                      enetcoefs_RUS_oc_10kb_K562[-1,1], 
+                      enetcoefs_SMOTE_oc_10kb_K562[-1,1],
+
+                      enetcoefs_none_op_10kb_K562[-1,1], 
+                      enetcoefs_ROS_op_10kb_K562[-1,1],
+                      enetcoefs_RUS_op_10kb_K562[-1,1], 
+                      enetcoefs_SMOTE_op_10kb_K562[-1,1],
+
+                      enetcoefs_none_dist_10kb_K562[-1,1],
+                      enetcoefs_ROS_dist_10kb_K562[-1,1],
+                      enetcoefs_RUS_dist_10kb_K562[-1,1],
+                      enetcoefs_SMOTE_dist_10kb_K562[-1,1])
+
+enetcoefsmat[enetcoefsmat == 0] <- NA
+
+#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
+colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
+rownames(enetcoefsmat) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))
+
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
+
+```
+
+#####All
+
+```{r}
+heatmap.2(enetcoefsmat,
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 1.5,
+          dendrogram="row",     # only draw a row dendrogram,
+          Rowv = TRUE,
+          Colv = FALSE,
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=0:12,
+          rowsep=0:nrow(enetcoefsmat)) 
+```
+
+#### 25kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/enetModel.rds")
+enetcoefs_none_oc_25kb_K562 <- coef(enetcoefs_none_oc_25kb_K562$finalModel, s=enetcoefs_none_oc_25kb_K562$bestTune$lambda)
+##OP
+enetcoefs_none_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/enetModel.rds")
+enetcoefs_none_op_25kb_K562 <- coef(enetcoefs_none_op_25kb_K562$finalModel, s=enetcoefs_none_op_25kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_none_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/enetModel.rds")
+enetcoefs_none_dist_25kb_K562 <- coef(enetcoefs_none_dist_25kb_K562$finalModel, s=enetcoefs_none_dist_25kb_K562$bestTune$lambda)
+
+#RUS
+##OC
+enetcoefs_RUS_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/enetModel.rds")
+enetcoefs_RUS_oc_25kb_K562 <- coef(enetcoefs_RUS_oc_25kb_K562$finalModel, s=enetcoefs_RUS_oc_25kb_K562$bestTune$lambda)
+##OP
+enetcoefs_RUS_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/enetModel.rds")
+enetcoefs_RUS_op_25kb_K562 <- coef(enetcoefs_RUS_op_25kb_K562$finalModel, s=enetcoefs_RUS_op_25kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_RUS_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
+enetcoefs_RUS_dist_25kb_K562 <- coef(enetcoefs_RUS_dist_25kb_K562$finalModel, s=enetcoefs_RUS_dist_25kb_K562$bestTune$lambda)
+
+#ROS
+##OC
+enetcoefs_ROS_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/enetModel.rds")
+enetcoefs_ROS_oc_25kb_K562 <- coef(enetcoefs_ROS_oc_25kb_K562$finalModel, s=enetcoefs_ROS_oc_25kb_K562$bestTune$lambda)
+##OP
+enetcoefs_ROS_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/enetModel.rds")
+enetcoefs_ROS_op_25kb_K562 <- coef(enetcoefs_ROS_op_25kb_K562$finalModel, s=enetcoefs_ROS_op_25kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_ROS_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
+enetcoefs_ROS_dist_25kb_K562 <- coef(enetcoefs_ROS_dist_25kb_K562$finalModel, s=enetcoefs_ROS_dist_25kb_K562$bestTune$lambda)
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
+enetcoefs_SMOTE_oc_25kb_K562 <- coef(enetcoefs_SMOTE_oc_25kb_K562$finalModel, s=enetcoefs_SMOTE_oc_25kb_K562$bestTune$lambda)
+##OP
+enetcoefs_SMOTE_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
+enetcoefs_SMOTE_op_25kb_K562 <- coef(enetcoefs_SMOTE_op_25kb_K562$finalModel, s=enetcoefs_SMOTE_op_25kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_SMOTE_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
+enetcoefs_SMOTE_dist_25kb_K562 <- coef(enetcoefs_SMOTE_dist_25kb_K562$finalModel, s=enetcoefs_SMOTE_dist_25kb_K562$bestTune$lambda)
+
+enetcoefsmat <- cbind(enetcoefs_none_oc_25kb_K562[-1,1], 
+                      enetcoefs_ROS_oc_25kb_K562[-1,1],
+                      enetcoefs_RUS_oc_25kb_K562[-1,1], 
+                      enetcoefs_SMOTE_oc_25kb_K562[-1,1],
+
+                      enetcoefs_none_op_25kb_K562[-1,1], 
+                      enetcoefs_ROS_op_25kb_K562[-1,1],
+                      enetcoefs_RUS_op_25kb_K562[-1,1], 
+                      enetcoefs_SMOTE_op_25kb_K562[-1,1],
+
+                      enetcoefs_none_dist_25kb_K562[-1,1],
+                      enetcoefs_ROS_dist_25kb_K562[-1,1],
+                      enetcoefs_RUS_dist_25kb_K562[-1,1],
+                      enetcoefs_SMOTE_dist_25kb_K562[-1,1])
+
+enetcoefsmat[enetcoefsmat == 0] <- NA
+
+#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
+colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
+rownames(enetcoefsmat) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))
+
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
+
+```
+
+#####All
+
+```{r}
+heatmap.2(enetcoefsmat,
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 1.5,
+          dendrogram="row",     # only draw a row dendrogram,
+          Rowv = TRUE,
+          Colv = FALSE,
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=0:12,
+          rowsep=0:nrow(enetcoefsmat)) 
+```
+
+#### 50kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/enetModel.rds")
+enetcoefs_none_oc_50kb_K562 <- coef(enetcoefs_none_oc_50kb_K562$finalModel, s=enetcoefs_none_oc_50kb_K562$bestTune$lambda)
+##OP
+enetcoefs_none_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/enetModel.rds")
+enetcoefs_none_op_50kb_K562 <- coef(enetcoefs_none_op_50kb_K562$finalModel, s=enetcoefs_none_op_50kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_none_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/enetModel.rds")
+enetcoefs_none_dist_50kb_K562 <- coef(enetcoefs_none_dist_50kb_K562$finalModel, s=enetcoefs_none_dist_50kb_K562$bestTune$lambda)
+
+#RUS
+##OC
+enetcoefs_RUS_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/enetModel.rds")
+enetcoefs_RUS_oc_50kb_K562 <- coef(enetcoefs_RUS_oc_50kb_K562$finalModel, s=enetcoefs_RUS_oc_50kb_K562$bestTune$lambda)
+##OP
+enetcoefs_RUS_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/enetModel.rds")
+enetcoefs_RUS_op_50kb_K562 <- coef(enetcoefs_RUS_op_50kb_K562$finalModel, s=enetcoefs_RUS_op_50kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_RUS_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
+enetcoefs_RUS_dist_50kb_K562 <- coef(enetcoefs_RUS_dist_50kb_K562$finalModel, s=enetcoefs_RUS_dist_50kb_K562$bestTune$lambda)
+
+#ROS
+##OC
+enetcoefs_ROS_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/enetModel.rds")
+enetcoefs_ROS_oc_50kb_K562 <- coef(enetcoefs_ROS_oc_50kb_K562$finalModel, s=enetcoefs_ROS_oc_50kb_K562$bestTune$lambda)
+##OP
+enetcoefs_ROS_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/enetModel.rds")
+enetcoefs_ROS_op_50kb_K562 <- coef(enetcoefs_ROS_op_50kb_K562$finalModel, s=enetcoefs_ROS_op_50kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_ROS_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
+enetcoefs_ROS_dist_50kb_K562 <- coef(enetcoefs_ROS_dist_50kb_K562$finalModel, s=enetcoefs_ROS_dist_50kb_K562$bestTune$lambda)
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
+enetcoefs_SMOTE_oc_50kb_K562 <- coef(enetcoefs_SMOTE_oc_50kb_K562$finalModel, s=enetcoefs_SMOTE_oc_50kb_K562$bestTune$lambda)
+##OP
+enetcoefs_SMOTE_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
+enetcoefs_SMOTE_op_50kb_K562 <- coef(enetcoefs_SMOTE_op_50kb_K562$finalModel, s=enetcoefs_SMOTE_op_50kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_SMOTE_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
+enetcoefs_SMOTE_dist_50kb_K562 <- coef(enetcoefs_SMOTE_dist_50kb_K562$finalModel, s=enetcoefs_SMOTE_dist_50kb_K562$bestTune$lambda)
+
+enetcoefsmat <- cbind(enetcoefs_none_oc_50kb_K562[-1,1], 
+                      enetcoefs_ROS_oc_50kb_K562[-1,1],
+                      enetcoefs_RUS_oc_50kb_K562[-1,1], 
+                      enetcoefs_SMOTE_oc_50kb_K562[-1,1],
+
+                      enetcoefs_none_op_50kb_K562[-1,1], 
+                      enetcoefs_ROS_op_50kb_K562[-1,1],
+                      enetcoefs_RUS_op_50kb_K562[-1,1], 
+                      enetcoefs_SMOTE_op_50kb_K562[-1,1],
+
+                      enetcoefs_none_dist_50kb_K562[-1,1],
+                      enetcoefs_ROS_dist_50kb_K562[-1,1],
+                      enetcoefs_RUS_dist_50kb_K562[-1,1],
+                      enetcoefs_SMOTE_dist_50kb_K562[-1,1])
+
+enetcoefsmat[enetcoefsmat == 0] <- NA
+
+#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
+colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
+rownames(enetcoefsmat) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))
+
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
+
+```
+
+#####All
+
+```{r}
+heatmap.2(enetcoefsmat,
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 1.5,
+          dendrogram="row",     # only draw a row dendrogram,
+          Rowv = TRUE,
+          Colv = FALSE,
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=0:12,
+          rowsep=0:nrow(enetcoefsmat)) 
+```
+
+#### 100kb
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
+
+features <- names(train)[-1]
+features <- features[grep("dist", features)]
+features <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist", 
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", features)
+
+#None
+##OC
+enetcoefs_none_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/enetModel.rds")
+enetcoefs_none_oc_100kb_K562 <- coef(enetcoefs_none_oc_100kb_K562$finalModel, s=enetcoefs_none_oc_100kb_K562$bestTune$lambda)
+##OP
+enetcoefs_none_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/enetModel.rds")
+enetcoefs_none_op_100kb_K562 <- coef(enetcoefs_none_op_100kb_K562$finalModel, s=enetcoefs_none_op_100kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_none_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/enetModel.rds")
+enetcoefs_none_dist_100kb_K562 <- coef(enetcoefs_none_dist_100kb_K562$finalModel, s=enetcoefs_none_dist_100kb_K562$bestTune$lambda)
+
+#RUS
+##OC
+enetcoefs_RUS_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/enetModel.rds")
+enetcoefs_RUS_oc_100kb_K562 <- coef(enetcoefs_RUS_oc_100kb_K562$finalModel, s=enetcoefs_RUS_oc_100kb_K562$bestTune$lambda)
+##OP
+enetcoefs_RUS_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/enetModel.rds")
+enetcoefs_RUS_op_100kb_K562 <- coef(enetcoefs_RUS_op_100kb_K562$finalModel, s=enetcoefs_RUS_op_100kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_RUS_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
+enetcoefs_RUS_dist_100kb_K562 <- coef(enetcoefs_RUS_dist_100kb_K562$finalModel, s=enetcoefs_RUS_dist_100kb_K562$bestTune$lambda)
+
+#ROS
+##OC
+enetcoefs_ROS_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/enetModel.rds")
+enetcoefs_ROS_oc_100kb_K562 <- coef(enetcoefs_ROS_oc_100kb_K562$finalModel, s=enetcoefs_ROS_oc_100kb_K562$bestTune$lambda)
+##OP
+enetcoefs_ROS_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/enetModel.rds")
+enetcoefs_ROS_op_100kb_K562 <- coef(enetcoefs_ROS_op_100kb_K562$finalModel, s=enetcoefs_ROS_op_100kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_ROS_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
+enetcoefs_ROS_dist_100kb_K562 <- coef(enetcoefs_ROS_dist_100kb_K562$finalModel, s=enetcoefs_ROS_dist_100kb_K562$bestTune$lambda)
+
+#SMOTE
+##OC
+enetcoefs_SMOTE_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
+enetcoefs_SMOTE_oc_100kb_K562 <- coef(enetcoefs_SMOTE_oc_100kb_K562$finalModel, s=enetcoefs_SMOTE_oc_100kb_K562$bestTune$lambda)
+##OP
+enetcoefs_SMOTE_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
+enetcoefs_SMOTE_op_100kb_K562 <- coef(enetcoefs_SMOTE_op_100kb_K562$finalModel, s=enetcoefs_SMOTE_op_100kb_K562$bestTune$lambda)
+##Distance
+enetcoefs_SMOTE_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
+enetcoefs_SMOTE_dist_100kb_K562 <- coef(enetcoefs_SMOTE_dist_100kb_K562$finalModel, s=enetcoefs_SMOTE_dist_100kb_K562$bestTune$lambda)
+
+enetcoefsmat <- cbind(enetcoefs_none_oc_100kb_K562[-1,1], 
+                      enetcoefs_ROS_oc_100kb_K562[-1,1],
+                      enetcoefs_RUS_oc_100kb_K562[-1,1], 
+                      enetcoefs_SMOTE_oc_100kb_K562[-1,1],
+
+                      enetcoefs_none_op_100kb_K562[-1,1], 
+                      enetcoefs_ROS_op_100kb_K562[-1,1],
+                      enetcoefs_RUS_op_100kb_K562[-1,1], 
+                      enetcoefs_SMOTE_op_100kb_K562[-1,1],
+
+                      enetcoefs_none_dist_100kb_K562[-1,1],
+                      enetcoefs_ROS_dist_100kb_K562[-1,1],
+                      enetcoefs_RUS_dist_100kb_K562[-1,1],
+                      enetcoefs_SMOTE_dist_100kb_K562[-1,1])
+
+enetcoefsmat[enetcoefsmat == 0] <- NA
+
+#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
+#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
+colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
+rownames(enetcoefsmat) <- gsub(paste(c("`", 
+                                                    "_",
+                                                    "-",
+                                                    "K562", 
+                                                    "dist",
+                                                    "count",
+                                                    "perc",
+                                                    "Haib", 
+                                                    "Sydh",
+                                                    "Uta",
+                                                    "Uw",
+                                                    "Broad",
+                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))
+
+my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
+
+```
+
+#####All
+
+```{r}
+heatmap.2(enetcoefsmat,
+          #cellnote = cormat,  # same data set for cell labels
+          #main = "Correlation", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 1.5,
+          dendrogram="row",     # only draw a row dendrogram,
+          Rowv = TRUE,
+          Colv = FALSE,
+          cexRow=0.5,
+          cexCol=0.75,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          colsep=0:12,
+          rowsep=0:nrow(enetcoefsmat)) 
+```

### 2019-03-28 Scripts/evaluating_model_performances.Rmd
edits to scripts

@@
 
+##Plots
+
 ```{r}
 
-ggarrange(p25, p25.2, p50, p50.2, p100, p100.2, 
+figure <- ggarrange(p1,p2,ncol = 2, nrow = 1, common.legend = TRUE, legend = "top")
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resampling Technique", color = "black", size = 20),
+    left = text_grob("Performance", color = "black", rot = 90, size=20)
+)
+
+figure <- ggarrange(p25, p25.2, p50, p50.2, p100, p100.2, 
           ncol=2, nrow=3, 
           common.legend = TRUE, 
-          legend = "bottom", 
+          legend = "top", 
           labels = c("A", "D", "B", "E", "C", "F"), 
           font.label = list(size=20))
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resampling Technique", color = "black", size = 20),
+    left = text_grob("Performance", color = "black", rot = 90, size=20)
+)
+
 ```

### 2019-03-28 Scripts/evaluating_models_with_dist_preds.Rmd
edits to scripts

--- 2019-03-08 Scripts/evaluating_smote_performances.Rmd
@@
 ```{r}
-ggarrange(p.none, p.ros, p.rus, 
+figure <- ggarrange(p.none, p.ros, p.rus, 
           ncol=1, nrow=3, 
           common.legend = TRUE, 
-          legend="bottom",
+          legend="top",
           labels="AUTO",
           font.label = list(size=20))
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resampling Technique", color = "black", size = 20),
+    left = text_grob("Performance", color = "black", rot = 90, size=20)
+)
+
 ```

### 2019-03-28 Scripts/evaluating_variable_importances.Rmd
edits to scripts

@@
 rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[20:1,]
+#rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[19:1,]
 
@@
 vim.gm12878.smote <- vim.gm12878.smote[order(vim.gm12878.smote[,1], decreasing = TRUE),]
+rownames(vim.gm12878.smote) <- gsub("`","",rownames(vim.gm12878.smote))
 
@@
 vim.K562.smote <- vim.K562.smote[order(vim.K562.smote[,1], decreasing = TRUE),]
+rownames(vim.K562.smote) <- gsub("`","",rownames(vim.K562.smote))
 
@@
 vim.gm12878.RUS <- vim.gm12878.RUS[order(vim.gm12878.RUS[,1], decreasing = TRUE),]
+rownames(vim.gm12878.RUS) <- gsub("`","",rownames(vim.gm12878.RUS))
 
@@
 vim.K562.RUS <- vim.K562.RUS[order(vim.K562.RUS[,1], decreasing = TRUE),]
+rownames(vim.K562.RUS) <- gsub("`","",rownames(vim.K562.RUS))
 
@@
 vim.gm12878.ROS <- vim.gm12878.ROS[order(vim.gm12878.ROS[,1], decreasing = TRUE),]
+rownames(vim.gm12878.ROS) <- gsub("`","",rownames(vim.gm12878.ROS))
 
@@
 vim.K562.ROS <- vim.K562.ROS[order(vim.K562.ROS[,1], decreasing = TRUE),]
+rownames(vim.K562.ROS) <- gsub("`","",rownames(vim.K562.ROS))
 
@@
 vim.gm12878.none <- vim.gm12878.none[order(vim.gm12878.none[,1], decreasing = TRUE),]
+rownames(vim.gm12878.none) <- gsub("`","",rownames(vim.gm12878.none))
 
@@
 vim.K562.none <- vim.K562.none[order(vim.K562.none[,1], decreasing = TRUE),]
+rownames(vim.K562.none) <- gsub("`","",rownames(vim.K562.none))
 
@@
 ```
+
+##Plots
+
+```{r}
+figure <- ggarrange(p1,p2,ncol=2,nrow=1,common.legend = TRUE, legend = "right", labels="AUTO")
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Genomic Annotation", color = "black", rot = 90, size=20)
+)
+
+figure <- ggarrange(p3,p4,ncol=2,nrow=1,common.legend = TRUE, legend = "right", labels="AUTO")
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Genomic Annotation", color = "black", rot = 90, size=20)
+)
+
+figure <- ggarrange(p5,p6,ncol=2,nrow=1,common.legend = TRUE, legend = "right", labels="AUTO")
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Genomic Annotation", color = "black", rot = 90, size=20)
+)
+
+figure <- ggarrange(p7,p8,ncol=2,nrow=1,common.legend = TRUE, legend = "right", labels="AUTO")
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Genomic Annotation", color = "black", rot = 90, size=20)
+)
+
+```

### 2019-03-28 Scripts/evaluating_pca.Rmd
created clustered tad plots after keeping only top 75% most variable columns

@@
 
+  ##Removing zero variance predictors
+  ###using caret
+  #nzv <- nearZeroVar(data, saveMetrics= TRUE)
+  #nzvar <- rownames(nzv[nzv$nzv,])
+  #if(length(nzvar) > 0){
+  #  data <- data[, -which(colnames(data) %in% nzvar)]
+  #}
+
+  ##keeping top 75th percentile variable
+  colvariance <- apply(data,2,var)
+  thirdquart <- as.numeric(summary(colvariance)[5])
+  data <- data[,which(colvariance >= thirdquart)]
+
   #determine optimal number of clusters

### 2019-03-31 Manuscript/manuscript.Rmd

@@
 
-Another aspect of TAD boundary modelling not currently being explored are the various feature engineering methods used to build the feature space of models.
-Different techniques can be employed to measure the relationship between TAD boundaries and genomic annotations.
-Typical approaches for modeling the association between TAD boundaries and epigenomic elements include overlap counts or percents [@mourad2016computational; @hong2017computational; @huang2015predicting].
-Counts refer to the total number of instances where a genomic annotation overlaps with a genomic region of interest, while percents refers to the percent of overlap that occurred (usually in terms of base pairs).
-The use of distances from TAD boundaries to regions of various genomic features, measured in the number of bases between them, has largely been ignored.
-However, these distance characteristics have the potential to offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
-Likewise, any direct comparisons of the different feature engineering techniques remain unresearched.
+Another underexplored aspect of modeling the association between TAD boundaries and genomic annotations is the various types of relationships between them.
+Typical approaches include overlap counts or percents [@mourad2016computational; @hong2017computational; @huang2015predicting].
+Counts refer to the number of times a genomic annotation directly overlaps with a TAD boundary region, e.g., a TAD boundary may overlap with several ChIP-seq peaks for a given transcription factor.
+Percents refers to the percent of overlap of a genomic annotation with a TAD boundary region, e.
+g., a 60% of a TAD boundary may overlap genomic region annotated as heterochromatin.
+
+While direct overlaps represent the most straightforward measure of functional associations, they do not account for indirect relationships shown to be one of the major driving force of genome regulation [???
+REFS].
+The most prominent example maybe the enhancer-promoter relationships, with enhancers are frequently located hundreths or thousands bases away from their target promoters [???
+REFS].
+The use of distances between TAD boundaries and genomic annotations has largely been ignored.
+However, these distance features have the potential to offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
 

### 2019-04-02 Scripts/evaluating_imbalance_ratios.Rmd
edits to results scripts

@@
   ylab("Imbalance Ratio") +
-  xlab("Resolution") +
+  xlab("") +
   #scale_fill_manual(name="Cell Line", values=c("red", "blue"))+
@@
   #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=10),
-        axis.text.y = element_text(size = 10),
-        axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15),
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
         legend.text=element_text(size=15),
@@
 ```
+
+# Evaluating number of bins
+
+```{r}
+binslist10 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")
+binslist10 <- length(binslist10)
+binslist25 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")
+binslist25 <- length(binslist25)
+binslist50 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")
+binslist50 <- length(binslist50)
+binslist100 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")
+binslist100 <- length(binslist100)
+
+binslist10k <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")
+binslist10k <- length(binslist10k)
+binslist25k <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")
+binslist25k <- length(binslist25k)
+binslist50k <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")
+binslist50k <- length(binslist50k)
+binslist100k <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")
+binslist100k <- length(binslist100k)
+
+Bins <- c(binslist10,binslist25,binslist50,binslist100,
+          binslist10k,binslist25k,binslist50k,binslist100k)
+CL <- c(rep("GM12878", 4), 
+                  rep("K562", 4))
+Resolution <- c(rep(c("10 kb", "25 kb", "50 kb", "100 kb"), 2))
+
+allbinsdata <- cbind.data.frame(Bins, CL, Resolution)
+allbinsdata$CL <- factor(allbinsdata$CL, levels=c("GM12878", "K562"))
+allbinsdata$Resolution <- factor(allbinsdata$Resolution, c("10 kb", "25 kb", "50 kb", "100 kb"))
+
+allbinsplots <- ggplot(allbinsdata, aes(x = Resolution, y = Bins,fill = CL)) + 
+  geom_bar(position = "dodge", stat="identity") + 
+  ylab("Total Number of Genomic Bins\n(in thousands of basepairs)") +
+  xlab("") +
+  #scale_fill_manual(name="Cell Line", values=c("red", "blue"))+
+  scale_y_continuous(limits=c(0,3e+05),
+                     breaks=c(0, 1e+05, 2e+05),
+                     labels = c("0", "100", "200")) +
+  labs(fill="Cell Line")+
+  theme_bw() +
+  #guides(fill=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+```
+
+```{r}
+figure <- ggarrange(allbinsplots, allirplots, ncol = 2, nrow = 1, common.legend = TRUE, legend = "top")
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20))
+```

### 2019-04-02 Scripts/evaluating_model_performances.Rmd
edits to results scripts

@@
 ```
+
+##gm12878
+
+###none
+
+```{r}
+
+#OC
+##None
+rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_gm12878_25kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_gm12878_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_gm12878_50kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_gm12878_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_gm12878_100kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_gm12878_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+all_rfperfs_gm12878_none <- data.frame(Resolution=rep(c(rep("10 kb", 3),
+                                                        rep("25 kb", 3),
+                                                        rep("50 kb", 3),
+                                                        rep("100 kb", 3)),4),
+                                       Predictor=rep(c("OC","OP","Distance"),16),
+                                       Metric=c(rep("AUC",12),
+                                                rep("F1-Score",12), 
+                                                rep("MCC",12),
+                                                rep("Balanced Acc", 12)))
+
+all_rfperfs_gm12878_none$Performance <- c(round(rfperf_gm12878_10kb_none_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_none_op[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_none_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_none_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_none_op[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_none_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_none_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_none_op[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_none_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_none_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_none_op[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_none_dist[17,2],2), #auc
+
+                                          round(rfperf_gm12878_10kb_none_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_none_op[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_none_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_none_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_none_op[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_none_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_none_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_none_op[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_none_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_none_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_none_op[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_none_dist[16,2],2), #f1
+
+                                          round(rfperf_gm12878_10kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_none_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_none_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_none_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_none_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_none_dist[15,2],2), #mcc
+
+                                          (round(rfperf_gm12878_10kb_none_oc[6,2],2) + round(rfperf_gm12878_10kb_none_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_10kb_none_op[6,2],2) + round(rfperf_gm12878_10kb_none_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_10kb_none_dist[6,2],2) + round(rfperf_gm12878_10kb_none_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_25kb_none_oc[6,2],2) + round(rfperf_gm12878_25kb_none_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_25kb_none_op[6,2],2) + round(rfperf_gm12878_25kb_none_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_25kb_none_dist[6,2],2) + round(rfperf_gm12878_25kb_none_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_50kb_none_oc[6,2],2) + round(rfperf_gm12878_50kb_none_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_50kb_none_op[6,2],2) + round(rfperf_gm12878_50kb_none_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_50kb_none_dist[6,2],2) + round(rfperf_gm12878_50kb_none_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_100kb_none_oc[6,2],2) + round(rfperf_gm12878_100kb_none_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_100kb_none_op[6,2],2) + round(rfperf_gm12878_100kb_none_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_100kb_none_dist[6,2],2) + round(rfperf_gm12878_100kb_none_dist[7,2],2))/2 #balanced accuracy
+)
+
+all_rfperfs_gm12878_none$Resolution <- factor(all_rfperfs_gm12878_none$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
+all_rfperfs_gm12878_none$Predictor <- factor(all_rfperfs_gm12878_none$Predictor, levels = c("OC", "OP", "Distance"))
+all_rfperfs_gm12878_none$Metric <- factor(all_rfperfs_gm12878_none$Metric, levels = c("AUC",
+                                                                                      "Balanced Acc",
+                                                                                      "F1-Score",
+                                                                                      "MCC"))
+
+p1 <- ggplot(all_rfperfs_gm12878_none,
+       aes(x=Resolution, y=Performance, fill=Predictor)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Metric) +
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Predictor Type")+
+  #guides(fill=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+```
+
+###ROS
+
+```{r}
+##ROS
+rfperf_gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_10kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_10kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_25kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_25kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_50kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_50kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_100kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_gm12878_100kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+all_rfperfs_gm12878_ros <- data.frame(Resolution=rep(c(rep("10 kb", 3),
+                                                        rep("25 kb", 3),
+                                                        rep("50 kb", 3),
+                                                        rep("100 kb", 3)),4),
+                                       Predictor=rep(c("OC","OP","Distance"),16),
+                                       Metric=c(rep("AUC",12),
+                                                rep("F1-Score",12), 
+                                                rep("MCC",12),
+                                                rep("Balanced Acc", 12)))
+
+all_rfperfs_gm12878_ros$Performance <- c(round(rfperf_gm12878_10kb_ros_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_ros_op[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_ros_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_ros_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_ros_op[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_ros_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_ros_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_ros_op[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_ros_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_ros_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_ros_op[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_ros_dist[17,2],2), #auc
+
+                                          round(rfperf_gm12878_10kb_ros_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_ros_op[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_ros_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_ros_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_ros_op[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_ros_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_ros_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_ros_op[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_ros_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_ros_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_ros_op[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_ros_dist[16,2],2), #f1
+
+                                          round(rfperf_gm12878_10kb_ros_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_ros_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_ros_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_ros_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_ros_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_ros_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_ros_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_ros_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_ros_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_ros_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_ros_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_ros_dist[15,2],2), #mcc
+
+                                          (round(rfperf_gm12878_10kb_ros_oc[6,2],2) + round(rfperf_gm12878_10kb_ros_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_10kb_ros_op[6,2],2) + round(rfperf_gm12878_10kb_ros_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_10kb_ros_dist[6,2],2) + round(rfperf_gm12878_10kb_ros_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_25kb_ros_oc[6,2],2) + round(rfperf_gm12878_25kb_ros_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_25kb_ros_op[6,2],2) + round(rfperf_gm12878_25kb_ros_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_25kb_ros_dist[6,2],2) + round(rfperf_gm12878_25kb_ros_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_50kb_ros_oc[6,2],2) + round(rfperf_gm12878_50kb_ros_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_50kb_ros_op[6,2],2) + round(rfperf_gm12878_50kb_ros_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_50kb_ros_dist[6,2],2) + round(rfperf_gm12878_50kb_ros_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_100kb_ros_oc[6,2],2) + round(rfperf_gm12878_100kb_ros_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_100kb_ros_op[6,2],2) + round(rfperf_gm12878_100kb_ros_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_100kb_ros_dist[6,2],2) + round(rfperf_gm12878_100kb_ros_dist[7,2],2))/2 #balanced accuracy
+)
+
+all_rfperfs_gm12878_ros$Resolution <- factor(all_rfperfs_gm12878_ros$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
+all_rfperfs_gm12878_ros$Predictor <- factor(all_rfperfs_gm12878_ros$Predictor, levels = c("OC", "OP", "Distance"))
+all_rfperfs_gm12878_ros$Metric <- factor(all_rfperfs_gm12878_ros$Metric, levels = c("AUC",
+                                                                                      "Balanced Acc",
+                                                                                      "F1-Score",
+                                                                                      "MCC"))
+
+ggplot(all_rfperfs_gm12878_ros,
+       aes(x=Resolution, y=Performance, fill=Predictor)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Metric) +
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Predictor Type")+
+  #guides(fill=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+```
+
+###RUS
+
+```{r}
+##RUS
+rfperf_gm12878_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_gm12878_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+all_rfperfs_gm12878_RUS <- data.frame(Resolution=rep(c(rep("10 kb", 3),
+                                                        rep("25 kb", 3),
+                                                        rep("50 kb", 3),
+                                                        rep("100 kb", 3)),4),
+                                       Predictor=rep(c("OC","OP","Distance"),16),
+                                       Metric=c(rep("AUC",12),
+                                                rep("F1-Score",12), 
+                                                rep("MCC",12),
+                                                rep("Balanced Acc", 12)))
+
+all_rfperfs_gm12878_RUS$Performance <- c(round(rfperf_gm12878_10kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_RUS_dist[17,2],2), #auc
+
+                                          round(rfperf_gm12878_10kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_RUS_dist[16,2],2), #f1
+
+                                          round(rfperf_gm12878_10kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_RUS_dist[15,2],2), #mcc
+
+                                          (round(rfperf_gm12878_10kb_RUS_oc[6,2],2) + round(rfperf_gm12878_10kb_RUS_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_10kb_RUS_op[6,2],2) + round(rfperf_gm12878_10kb_RUS_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_10kb_RUS_dist[6,2],2) + round(rfperf_gm12878_10kb_RUS_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_25kb_RUS_oc[6,2],2) + round(rfperf_gm12878_25kb_RUS_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_25kb_RUS_op[6,2],2) + round(rfperf_gm12878_25kb_RUS_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_25kb_RUS_dist[6,2],2) + round(rfperf_gm12878_25kb_RUS_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_50kb_RUS_oc[6,2],2) + round(rfperf_gm12878_50kb_RUS_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_50kb_RUS_op[6,2],2) + round(rfperf_gm12878_50kb_RUS_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_50kb_RUS_dist[6,2],2) + round(rfperf_gm12878_50kb_RUS_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_100kb_RUS_oc[6,2],2) + round(rfperf_gm12878_100kb_RUS_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_100kb_RUS_op[6,2],2) + round(rfperf_gm12878_100kb_RUS_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_100kb_RUS_dist[6,2],2) + round(rfperf_gm12878_100kb_RUS_dist[7,2],2))/2 #balanced accuracy
+)
+
+all_rfperfs_gm12878_RUS$Resolution <- factor(all_rfperfs_gm12878_RUS$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
+all_rfperfs_gm12878_RUS$Predictor <- factor(all_rfperfs_gm12878_RUS$Predictor, levels = c("OC", "OP", "Distance"))
+all_rfperfs_gm12878_RUS$Metric <- factor(all_rfperfs_gm12878_RUS$Metric, levels = c("AUC",
+                                                                                      "Balanced Acc",
+                                                                                      "F1-Score",
+                                                                                      "MCC"))
+
+ggplot(all_rfperfs_gm12878_RUS,
+       aes(x=Resolution, y=Performance, fill=Predictor)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Metric) +
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Predictor Type")+
+  #guides(fill=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+```
+
+###SMOTE
+
+```{r}
+##SMOTE
+rfperf_gm12878_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_gm12878_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+all_rfperfs_gm12878_SMOTE <- data.frame(Resolution=rep(c(rep("10 kb", 3),
+                                                        rep("25 kb", 3),
+                                                        rep("50 kb", 3),
+                                                        rep("100 kb", 3)),4),
+                                       Predictor=rep(c("OC","OP","Distance"),16),
+                                       Metric=c(rep("AUC",12),
+                                                rep("F1-Score",12), 
+                                                rep("MCC",12),
+                                                rep("Balanced Acc", 12)))
+
+all_rfperfs_gm12878_SMOTE$Performance <- c(round(rfperf_gm12878_10kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_SMOTE_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_SMOTE_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_SMOTE_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_SMOTE_dist[17,2],2), #auc
+
+                                          round(rfperf_gm12878_10kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_SMOTE_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_SMOTE_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_SMOTE_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_SMOTE_dist[16,2],2), #f1
+
+                                          round(rfperf_gm12878_10kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_SMOTE_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_SMOTE_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_SMOTE_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_SMOTE_dist[15,2],2), #mcc
+
+                                          (round(rfperf_gm12878_10kb_SMOTE_oc[6,2],2) + round(rfperf_gm12878_10kb_SMOTE_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_10kb_SMOTE_op[6,2],2) + round(rfperf_gm12878_10kb_SMOTE_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_10kb_SMOTE_dist[6,2],2) + round(rfperf_gm12878_10kb_SMOTE_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_25kb_SMOTE_oc[6,2],2) + round(rfperf_gm12878_25kb_SMOTE_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_25kb_SMOTE_op[6,2],2) + round(rfperf_gm12878_25kb_SMOTE_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_25kb_SMOTE_dist[6,2],2) + round(rfperf_gm12878_25kb_SMOTE_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_50kb_SMOTE_oc[6,2],2) + round(rfperf_gm12878_50kb_SMOTE_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_50kb_SMOTE_op[6,2],2) + round(rfperf_gm12878_50kb_SMOTE_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_50kb_SMOTE_dist[6,2],2) + round(rfperf_gm12878_50kb_SMOTE_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_100kb_SMOTE_oc[6,2],2) + round(rfperf_gm12878_100kb_SMOTE_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_100kb_SMOTE_op[6,2],2) + round(rfperf_gm12878_100kb_SMOTE_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_gm12878_100kb_SMOTE_dist[6,2],2) + round(rfperf_gm12878_100kb_SMOTE_dist[7,2],2))/2 #balanced accuracy
+)
+
+all_rfperfs_gm12878_SMOTE$Resolution <- factor(all_rfperfs_gm12878_SMOTE$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
+all_rfperfs_gm12878_SMOTE$Predictor <- factor(all_rfperfs_gm12878_SMOTE$Predictor, levels = c("OC", "OP", "Distance"))
+all_rfperfs_gm12878_SMOTE$Metric <- factor(all_rfperfs_gm12878_SMOTE$Metric, levels = c("AUC",
+                                                                                      "Balanced Acc",
+                                                                                      "F1-Score",
+                                                                                      "MCC"))
+
+ggplot(all_rfperfs_gm12878_SMOTE,
+       aes(x=Resolution, y=Performance, fill=Predictor)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Metric) +
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Predictor Type")+
+  #guides(fill=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+```
+
+##k562
+
+###none
+
+```{r}
+#OC
+##None
+rfperf_K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_K562_10kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_K562_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_K562_25kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_K562_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_K562_50kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_K562_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_K562_100kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_K562_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+all_rfperfs_K562_none <- data.frame(Resolution=rep(c(rep("10 kb", 3),
+                                                        rep("25 kb", 3),
+                                                        rep("50 kb", 3),
+                                                        rep("100 kb", 3)),4),
+                                       Predictor=rep(c("OC","OP","Distance"),16),
+                                       Metric=c(rep("AUC",12),
+                                                rep("F1-Score",12), 
+                                                rep("MCC",12),
+                                                rep("Balanced Acc", 12)))
+
+all_rfperfs_K562_none$Performance <- c(round(rfperf_K562_10kb_none_oc[17,2],2), #auc
+                                          round(rfperf_K562_10kb_none_op[17,2],2), #auc
+                                          round(rfperf_K562_10kb_none_dist[17,2],2), #auc
+                                          round(rfperf_K562_25kb_none_oc[17,2],2), #auc
+                                          round(rfperf_K562_25kb_none_op[17,2],2), #auc
+                                          round(rfperf_K562_25kb_none_dist[17,2],2), #auc
+                                          round(rfperf_K562_50kb_none_oc[17,2],2), #auc
+                                          round(rfperf_K562_50kb_none_op[17,2],2), #auc
+                                          round(rfperf_K562_50kb_none_dist[17,2],2), #auc
+                                          round(rfperf_K562_100kb_none_oc[17,2],2), #auc
+                                          round(rfperf_K562_100kb_none_op[17,2],2), #auc
+                                          round(rfperf_K562_100kb_none_dist[17,2],2), #auc
+
+                                          round(rfperf_K562_10kb_none_oc[16,2],2), #f1
+                                          round(rfperf_K562_10kb_none_op[16,2],2), #f1
+                                          round(rfperf_K562_10kb_none_dist[16,2],2), #f1
+                                          round(rfperf_K562_25kb_none_oc[16,2],2), #f1
+                                          round(rfperf_K562_25kb_none_op[16,2],2), #f1
+                                          round(rfperf_K562_25kb_none_dist[16,2],2), #f1
+                                          round(rfperf_K562_50kb_none_oc[16,2],2), #f1
+                                          round(rfperf_K562_50kb_none_op[16,2],2), #f1
+                                          round(rfperf_K562_50kb_none_dist[16,2],2), #f1
+                                          round(rfperf_K562_100kb_none_oc[16,2],2), #f1
+                                          round(rfperf_K562_100kb_none_op[16,2],2), #f1
+                                          round(rfperf_K562_100kb_none_dist[16,2],2), #f1
+
+                                          round(rfperf_K562_10kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_none_op[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_none_op[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_none_op[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_none_op[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_none_dist[15,2],2), #mcc
+
+                                          (round(rfperf_K562_10kb_none_oc[6,2],2) + round(rfperf_K562_10kb_none_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_10kb_none_op[6,2],2) + round(rfperf_K562_10kb_none_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_10kb_none_dist[6,2],2) + round(rfperf_K562_10kb_none_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_25kb_none_oc[6,2],2) + round(rfperf_K562_25kb_none_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_25kb_none_op[6,2],2) + round(rfperf_K562_25kb_none_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_25kb_none_dist[6,2],2) + round(rfperf_K562_25kb_none_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_50kb_none_oc[6,2],2) + round(rfperf_K562_50kb_none_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_50kb_none_op[6,2],2) + round(rfperf_K562_50kb_none_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_50kb_none_dist[6,2],2) + round(rfperf_K562_50kb_none_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_100kb_none_oc[6,2],2) + round(rfperf_K562_100kb_none_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_100kb_none_op[6,2],2) + round(rfperf_K562_100kb_none_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_100kb_none_dist[6,2],2) + round(rfperf_K562_100kb_none_dist[7,2],2))/2 #balanced accuracy
+)
+
+all_rfperfs_K562_none$Resolution <- factor(all_rfperfs_K562_none$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
+all_rfperfs_K562_none$Predictor <- factor(all_rfperfs_K562_none$Predictor, levels = c("OC", "OP", "Distance"))
+all_rfperfs_K562_none$Metric <- factor(all_rfperfs_K562_none$Metric, levels = c("AUC",
+                                                                                      "Balanced Acc",
+                                                                                      "F1-Score",
+                                                                                      "MCC"))
+
+p2 <- ggplot(all_rfperfs_K562_none,
+       aes(x=Resolution, y=Performance, fill=Predictor)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Metric) +
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Predictor Type")+
+  #guides(fill=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+```
+
+###ROS
+
+```{r}
+##ROS
+rfperf_K562_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_10kb_ros_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_10kb_ros_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_25kb_ros_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_25kb_ros_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_50kb_ros_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_50kb_ros_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_100kb_ros_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+##ROS
+rfperf_K562_100kb_ros_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+all_rfperfs_K562_ros <- data.frame(Resolution=rep(c(rep("10 kb", 3),
+                                                        rep("25 kb", 3),
+                                                        rep("50 kb", 3),
+                                                        rep("100 kb", 3)),4),
+                                       Predictor=rep(c("OC","OP","Distance"),16),
+                                       Metric=c(rep("AUC",12),
+                                                rep("F1-Score",12), 
+                                                rep("MCC",12),
+                                                rep("Balanced Acc", 12)))
+
+all_rfperfs_K562_ros$Performance <- c(round(rfperf_K562_10kb_ros_oc[17,2],2), #auc
+                                          round(rfperf_K562_10kb_ros_op[17,2],2), #auc
+                                          round(rfperf_K562_10kb_ros_dist[17,2],2), #auc
+                                          round(rfperf_K562_25kb_ros_oc[17,2],2), #auc
+                                          round(rfperf_K562_25kb_ros_op[17,2],2), #auc
+                                          round(rfperf_K562_25kb_ros_dist[17,2],2), #auc
+                                          round(rfperf_K562_50kb_ros_oc[17,2],2), #auc
+                                          round(rfperf_K562_50kb_ros_op[17,2],2), #auc
+                                          round(rfperf_K562_50kb_ros_dist[17,2],2), #auc
+                                          round(rfperf_K562_100kb_ros_oc[17,2],2), #auc
+                                          round(rfperf_K562_100kb_ros_op[17,2],2), #auc
+                                          round(rfperf_K562_100kb_ros_dist[17,2],2), #auc
+
+                                          round(rfperf_K562_10kb_ros_oc[16,2],2), #f1
+                                          round(rfperf_K562_10kb_ros_op[16,2],2), #f1
+                                          round(rfperf_K562_10kb_ros_dist[16,2],2), #f1
+                                          round(rfperf_K562_25kb_ros_oc[16,2],2), #f1
+                                          round(rfperf_K562_25kb_ros_op[16,2],2), #f1
+                                          round(rfperf_K562_25kb_ros_dist[16,2],2), #f1
+                                          round(rfperf_K562_50kb_ros_oc[16,2],2), #f1
+                                          round(rfperf_K562_50kb_ros_op[16,2],2), #f1
+                                          round(rfperf_K562_50kb_ros_dist[16,2],2), #f1
+                                          round(rfperf_K562_100kb_ros_oc[16,2],2), #f1
+                                          round(rfperf_K562_100kb_ros_op[16,2],2), #f1
+                                          round(rfperf_K562_100kb_ros_dist[16,2],2), #f1
+
+                                          round(rfperf_K562_10kb_ros_oc[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_ros_op[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_ros_dist[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_ros_oc[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_ros_op[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_ros_dist[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_ros_oc[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_ros_op[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_ros_dist[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_ros_oc[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_ros_op[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_ros_dist[15,2],2), #mcc
+
+                                          (round(rfperf_K562_10kb_ros_oc[6,2],2) + round(rfperf_K562_10kb_ros_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_10kb_ros_op[6,2],2) + round(rfperf_K562_10kb_ros_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_10kb_ros_dist[6,2],2) + round(rfperf_K562_10kb_ros_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_25kb_ros_oc[6,2],2) + round(rfperf_K562_25kb_ros_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_25kb_ros_op[6,2],2) + round(rfperf_K562_25kb_ros_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_25kb_ros_dist[6,2],2) + round(rfperf_K562_25kb_ros_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_50kb_ros_oc[6,2],2) + round(rfperf_K562_50kb_ros_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_50kb_ros_op[6,2],2) + round(rfperf_K562_50kb_ros_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_50kb_ros_dist[6,2],2) + round(rfperf_K562_50kb_ros_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_100kb_ros_oc[6,2],2) + round(rfperf_K562_100kb_ros_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_100kb_ros_op[6,2],2) + round(rfperf_K562_100kb_ros_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_100kb_ros_dist[6,2],2) + round(rfperf_K562_100kb_ros_dist[7,2],2))/2 #balanced accuracy
+)
+
+all_rfperfs_K562_ros$Resolution <- factor(all_rfperfs_K562_ros$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
+all_rfperfs_K562_ros$Predictor <- factor(all_rfperfs_K562_ros$Predictor, levels = c("OC", "OP", "Distance"))
+all_rfperfs_K562_ros$Metric <- factor(all_rfperfs_K562_ros$Metric, levels = c("AUC",
+                                                                                      "Balanced Acc",
+                                                                                      "F1-Score",
+                                                                                      "MCC"))
+
+ggplot(all_rfperfs_K562_ros,
+       aes(x=Resolution, y=Performance, fill=Predictor)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Metric) +
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Predictor Type")+
+  #guides(fill=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+```
+
+###RUS
+
+```{r}
+##RUS
+rfperf_K562_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+##RUS
+rfperf_K562_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+all_rfperfs_K562_RUS <- data.frame(Resolution=rep(c(rep("10 kb", 3),
+                                                        rep("25 kb", 3),
+                                                        rep("50 kb", 3),
+                                                        rep("100 kb", 3)),4),
+                                       Predictor=rep(c("OC","OP","Distance"),16),
+                                       Metric=c(rep("AUC",12),
+                                                rep("F1-Score",12), 
+                                                rep("MCC",12),
+                                                rep("Balanced Acc", 12)))
+
+all_rfperfs_K562_RUS$Performance <- c(round(rfperf_K562_10kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_K562_10kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_K562_10kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_K562_25kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_K562_25kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_K562_25kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_K562_50kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_K562_50kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_K562_50kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_K562_100kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_K562_100kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_K562_100kb_RUS_dist[17,2],2), #auc
+
+                                          round(rfperf_K562_10kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_K562_10kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_K562_10kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_K562_25kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_K562_25kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_K562_25kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_K562_50kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_K562_50kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_K562_50kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_K562_100kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_K562_100kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_K562_100kb_RUS_dist[16,2],2), #f1
+
+                                          round(rfperf_K562_10kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_RUS_dist[15,2],2), #mcc
+
+                                          (round(rfperf_K562_10kb_RUS_oc[6,2],2) + round(rfperf_K562_10kb_RUS_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_10kb_RUS_op[6,2],2) + round(rfperf_K562_10kb_RUS_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_10kb_RUS_dist[6,2],2) + round(rfperf_K562_10kb_RUS_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_25kb_RUS_oc[6,2],2) + round(rfperf_K562_25kb_RUS_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_25kb_RUS_op[6,2],2) + round(rfperf_K562_25kb_RUS_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_25kb_RUS_dist[6,2],2) + round(rfperf_K562_25kb_RUS_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_50kb_RUS_oc[6,2],2) + round(rfperf_K562_50kb_RUS_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_50kb_RUS_op[6,2],2) + round(rfperf_K562_50kb_RUS_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_50kb_RUS_dist[6,2],2) + round(rfperf_K562_50kb_RUS_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_100kb_RUS_oc[6,2],2) + round(rfperf_K562_100kb_RUS_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_100kb_RUS_op[6,2],2) + round(rfperf_K562_100kb_RUS_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_100kb_RUS_dist[6,2],2) + round(rfperf_K562_100kb_RUS_dist[7,2],2))/2 #balanced accuracy
+)
+
+all_rfperfs_K562_RUS$Resolution <- factor(all_rfperfs_K562_RUS$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
+all_rfperfs_K562_RUS$Predictor <- factor(all_rfperfs_K562_RUS$Predictor, levels = c("OC", "OP", "Distance"))
+all_rfperfs_K562_RUS$Metric <- factor(all_rfperfs_K562_RUS$Metric, levels = c("AUC",
+                                                                                      "Balanced Acc",
+                                                                                      "F1-Score",
+                                                                                      "MCC"))
+
+ggplot(all_rfperfs_K562_RUS,
+       aes(x=Resolution, y=Performance, fill=Predictor)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Metric) +
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Predictor Type")+
+  #guides(fill=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+```
+
+###SMOTE
+
+```{r}
+##SMOTE
+rfperf_K562_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+##SMOTE
+rfperf_K562_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+all_rfperfs_K562_SMOTE <- data.frame(Resolution=rep(c(rep("10 kb", 3),
+                                                        rep("25 kb", 3),
+                                                        rep("50 kb", 3),
+                                                        rep("100 kb", 3)),4),
+                                       Predictor=rep(c("OC","OP","Distance"),16),
+                                       Metric=c(rep("AUC",12),
+                                                rep("F1-Score",12), 
+                                                rep("MCC",12),
+                                                rep("Balanced Acc", 12)))
+
+all_rfperfs_K562_SMOTE$Performance <- c(round(rfperf_K562_10kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_K562_10kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_K562_10kb_SMOTE_dist[17,2],2), #auc
+                                          round(rfperf_K562_25kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_K562_25kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_K562_25kb_SMOTE_dist[17,2],2), #auc
+                                          round(rfperf_K562_50kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_K562_50kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_K562_50kb_SMOTE_dist[17,2],2), #auc
+                                          round(rfperf_K562_100kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_K562_100kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_K562_100kb_SMOTE_dist[17,2],2), #auc
+
+                                          round(rfperf_K562_10kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_K562_10kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_K562_10kb_SMOTE_dist[16,2],2), #f1
+                                          round(rfperf_K562_25kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_K562_25kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_K562_25kb_SMOTE_dist[16,2],2), #f1
+                                          round(rfperf_K562_50kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_K562_50kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_K562_50kb_SMOTE_dist[16,2],2), #f1
+                                          round(rfperf_K562_100kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_K562_100kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_K562_100kb_SMOTE_dist[16,2],2), #f1
+
+                                          round(rfperf_K562_10kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_SMOTE_dist[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_SMOTE_dist[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_SMOTE_dist[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_SMOTE_dist[15,2],2), #mcc
+
+                                          (round(rfperf_K562_10kb_SMOTE_oc[6,2],2) + round(rfperf_K562_10kb_SMOTE_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_10kb_SMOTE_op[6,2],2) + round(rfperf_K562_10kb_SMOTE_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_10kb_SMOTE_dist[6,2],2) + round(rfperf_K562_10kb_SMOTE_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_25kb_SMOTE_oc[6,2],2) + round(rfperf_K562_25kb_SMOTE_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_25kb_SMOTE_op[6,2],2) + round(rfperf_K562_25kb_SMOTE_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_25kb_SMOTE_dist[6,2],2) + round(rfperf_K562_25kb_SMOTE_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_50kb_SMOTE_oc[6,2],2) + round(rfperf_K562_50kb_SMOTE_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_50kb_SMOTE_op[6,2],2) + round(rfperf_K562_50kb_SMOTE_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_50kb_SMOTE_dist[6,2],2) + round(rfperf_K562_50kb_SMOTE_dist[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_100kb_SMOTE_oc[6,2],2) + round(rfperf_K562_100kb_SMOTE_oc[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_100kb_SMOTE_op[6,2],2) + round(rfperf_K562_100kb_SMOTE_op[7,2],2))/2, #balanced accuracy
+                                          (round(rfperf_K562_100kb_SMOTE_dist[6,2],2) + round(rfperf_K562_100kb_SMOTE_dist[7,2],2))/2 #balanced accuracy
+)
+
+all_rfperfs_K562_SMOTE$Resolution <- factor(all_rfperfs_K562_SMOTE$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
+all_rfperfs_K562_SMOTE$Predictor <- factor(all_rfperfs_K562_SMOTE$Predictor, levels = c("OC", "OP", "Distance"))
+all_rfperfs_K562_SMOTE$Metric <- factor(all_rfperfs_K562_SMOTE$Metric, levels = c("AUC",
+                                                                                      "Balanced Acc",
+                                                                                      "F1-Score",
+                                                                                      "MCC"))
+
+ggplot(all_rfperfs_K562_SMOTE,
+       aes(x=Resolution, y=Performance, fill=Predictor)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Metric) +
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Predictor Type")+
+  #guides(fill=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+```
+
+##Plots
+
+```{r}
+p.g.none <- p.g.none + ggtitle("None") + ylab("GM12878") + theme(plot.title = element_text(size=20)) #+ ylim(0,.85)
+p.g.ros <- p.g.ros + ggtitle("ROS") + theme(plot.title = element_text(size=20)) #+ ylim(0,.85)
+p.g.rus <- p.g.rus + ggtitle("RUS") + theme(plot.title = element_text(size=20)) #+ ylim(0,.85)
+p.g.smote <- p.g.smote + ggtitle("SMOTE") + theme(plot.title = element_text(size=20)) #+ ylim(0,.85)
+p.k.none <- p.k.none + ylab("K562") #+ ylim(0,.85)
+p.k.ros <- p.k.ros #+ ylim(0,.85)
+p.k.rus <- p.k.rus #+ ylim(0,.85)
+p.k.smote <- p.k.smote #+ ylim(0,.85)
+
+figure <- ggarrange(p.g.ros,p.g.rus,p.g.smote,
+                    p.k.ros,p.k.rus,p.k.smote,ncol = 3, nrow = 2, common.legend = TRUE, legend = "top")
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resampling Technique", color = "black", size = 20),
+    left = text_grob("Performance", color = "black", rot = 90, size=20)
+)
+
+figure <- ggarrange(p.g.none,p.g.ros,p.g.rus,p.g.smote,
+                    p.k.none,p.k.ros,p.k.rus,p.k.smote,
+          ncol=4, nrow=2, 
+          common.legend = TRUE, 
+          legend = "top") 
+          #, 
+          #labels = c("A", "D", "B", "E", "C", "F"), 
+          #font.label = list(size=20)
+          #)
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resampling Technique", color = "black", size = 20),
+    left = text_grob("Performance", color = "black", rot = 90, size=20)
+)
+
+```

### 2019-04-02 Scripts/evaluating_models_with_dist_preds.Rmd
edits to results scripts

@@
 ```
+
+```{r}
+all_perfs <- rbind.data.frame(all_None_perfs,
+                              all_ROS_perfs,
+                              all_RUS_perfs,
+                              all_smote_perfs)
+all_perfs$Resampling <- c(rep("None",24),
+                          rep("ROS",24),
+                          rep("RUS",24),
+                          rep("SMOTE",24))
+all_perfs$CL <- factor(all_perfs$CL, levels=c("GM12878","K562"))
+all_perfs$Resolution <- factor(all_perfs$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
+all_perfs$Metric <- factor(all_perfs$Metric, levels=c("Balanced Acc", "F1-Score", "MCC"))
+all_perfs$Resampling <- factor(all_perfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
+
+#gm12878
+p1 <- ggplot(all_perfs[which(all_perfs$CL=="GM12878"),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
+    geom_line(size=2)+
+    geom_point(size=5)+
+    facet_grid(~ Metric)+
+    theme_minimal() +
+    theme_bw()+
+    xlab("") + ylab("") +
+    ggtitle("GM12878") +
+  scale_color_discrete(name="Re-Sampling Technique")+
+	theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1
+	                                 ),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+	      plot.title = element_text(size=20))
+
+#k562
+p2 <- ggplot(all_perfs[which(all_perfs$CL=="K562"),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
+    geom_line(size=2)+
+    geom_point(size=5)+
+    facet_grid(~ Metric)+
+    theme_minimal() +
+    theme_bw()+
+    xlab("") + ylab("") +
+    ggtitle("K562") +
+  scale_color_discrete(name="Re-Sampling Technique")+
+	theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1
+	                                 ),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+	      plot.title = element_text(size=20))
+
+figure <- ggarrange(p1,p2,ncol = 2, nrow=1, common.legend = TRUE, legend = "top")
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Performance", color = "black", rot = 90, size=20)
+)
+
+```

### 2019-04-04 Manuscript/Supplementary/supplementary_legends.Rmd
editted legends
updated legend

@@
 
+<!--
 **Supplementary Table 5.
@@
 Imbalance ratio is defined as the ratio of genomic bins that overlapped a flanked TAD boundary (minority class), divided by the number of genomic bins that did not overlap a flanked TAD boundary (majority class).
+-->
+
+**Supplementary Figure 15.
+Data summaries in the form of barplots for the GM12878 (red) and K562 (blue) cell lines.** (A) The total number of genomic bins created by partitioning the linear genome into unit intervals corresponding to the resolution of the relevant domain data.
+(B) Subsequent imbalance ratios, defined as the ratio of the number of bins that overlapped with a flanked TAD boundary to the number of bins that did not overlap with a flanked TAD boundary.
 
@@
 
-**Supplementary Figure 14.
+**Supplementary Figure 14A.
 Variable importance of the top 20 most predictive genomic annotations for models using no resampling technique with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
@@
 
-**Supplementary Figure 15.
+**Supplementary Figure 14B.
 Variable importance of the top 20 most predictive genomic annotations for models using random over-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
@@
 
-**Supplementary Figure 16.
+**Supplementary Figure 14C.
 Variable importance of the top 20 most predictive genomic annotations for models using random under-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.

### 2019-04-04 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-We evaluated and compared multiple random forest classification algorithms built on domain data extracted from Hi-C datasets for 2 cell lines $C = {GM12878, K562}$, at four different resolutions $R = {10 kb, 25 kb, 50 kb, 100 kb}$.
-For each classifier, we compared three predictor types $P = {OC, OP, Distance}$ and five class balancing techniques $B = {None, RUS, ROS, SMOTE, ROSE}$.
-A system produced from the ensemble framework was defined as: $ = {c, r, p, b}$, where $c \in C, \quad R \in R, \quad p \in P,$ and $b \in B$.
-Letting $|X|$ denote the cardinality of each set, we evaluated $|C| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $X (= x \times 4 \times 3 \times 5)$ separate models.
-For each model, we aimed to assess both model performance and identify the genomic annotations that were most important in correctly labeling the genomic bins that overlapped with flanked TAD boundaries.
+Multiple random forest classification algorithms were built on domain data extracted from Hi-C data for 2 cell lines $C = \{GM12878, K562\}$, at four different resolutions $R = \{10 kb, 25 kb, 50 kb, 100 kb\}$.
+For each classifier, we compared three predictor types $P = \{\text{OC}, \text{OP}, \text{Distance}\}$ and 4 class balancing techniques $B = \{None, RUS, ROS, SMOTE}$.
+A system produced from the ensemble framework was defined as: $S = \{c, r, p, b\}$, where $c \in C, \quad R \in R, \quad p \in P,$ and $b \in B$.
+Letting $|X|$ denote the cardinality of each set, we evaluated $|C| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $96 (= 2 \times 4 \times 3 \times 4)$ separate models.
 
@@
 
-We first examined the class imbalance of the different data resolutions for each cell line (Supplementary Table 5).
-While the total number of genomic bins decreased as resolution increased, the imbalance ratios remained relatively stable.
-We found that there was an average imbalance ratio of 0.154 (SD=0.022) and 0.137 (SD=0.0181) across resolutions for the GM12878 and K562 cell lines respectively.
-The low imbalance ratios indicate a wide disparity between majority and minority classes, and therefore suitable resampling techniques were needed.
+We first examined the class imbalance of the different data resolutions for each cell line.
+As expected, the total number of genomic bins decreased as resolution decreased.
+That is, at lower resolutions, the linear genome was binned into larger units, thereby creating fewer bins (Supplementary Figure 15 (A)).
+The imbalance ratios, however, remained relatively stable (Supplementary Figure 15 (B)).
+We found that there was an average IR of 0.154 (SD=0.022) and 0.137 (SD=0.0181) across resolutions for the GM12878 and K562 cell lines respectively.
+Ideally, a balanced dataset will have an IR close to 0.50.
+Here, the low imbalance ratios indicated a wide disparity between majority and minority classes (i.e.
+a genomic bin was much more likely to not overlap with a flanked TAD boundary than it was to overlap with one).
+Therefore suitable resampling techniques were needed.
 
@@
 
-# Discussion
+# DISCUSSION
+
+We developed an ensemble framework to systematically compare model performances for different combinations of class balancing and feature engineering techniques aimed aimed at determining a consensus approach to predicting TAD boundary formation using genomic annotations
 

### 2019-04-05 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-We assessed the collinearity among the genomic annotations used for the feature space of subsequent models by isolating the genomic bins that overlapped with flanked TAD boundaries.
-We then vectorized the number of instances when a region defined by a genomic annotation overlapped with the isolated bins.
-It was found that the correlations among these vectors were very high for many genomic annotations.
-The correlations were visualized using correlograms for each data resolution and cell line (Supplementary Figure 2).
-The high correlations imply that many genomic annotations tended to colocalize near each other at the boarders of domains.
-This was present across both resolution and cell line.
-Specifically, we found that the CTCF, Rad21, Smc3ab, and Znf143 transcription factor binding sites were highly colocalized near TAD boundaries.
-[???
-We need to quantify and show this, and the following colocalizations] Likewise, many histone modifications also tended to appear near TAD boundaries in conjunction with one another including H3K4me1, H3K4me2, H3K4me3, H3K9ac, and H3K27ac.
+By isolating bins that overlapped with flanked TAD boundaries we were able to assess the correlations of genomic annotations and determine which annotations were enriched together at boundaries.
+To  get a hollisitic view of how some annotations tended to occur together at boundaries, we computed the pairwise correlations of the averages between count overlaps, count percents, and $log_{2}$ distances of each genomic annotation with bins that overlapped with flanked TAD boundaries.
+Clustered correlograms at the 10 kb resolution, for both cell lines, showed that distinct groups of transcription factors were highly correlated including CTCF, ZNF143, RAD21, and SMC3ab (Figure 7).
+Likewise, combinations of particular histone modifications and chromatin states were also shown to exhibit similar profiles near TAD boundaries including H3K4me1, H3K4me2, and H3K4me3, aswell as strong and weak enhancers.
 Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly correlated, yet inversely correlated with many transcription factor binding sites.
+Similar correlations were exhibited across the remainder of resolutions, for both cell lines (Supplementary Figure X).
+The high correlations among many of the genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.
+The regularization was performed predictor-type and resolution specific data after implementing each of the resampling techniques within each cell line.
 
-The high correlations among many of the genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.
-The regularization was performed after implementing each of the resampling techniques on all data resolutions within each cell line.
-Additionally, a unique predictor-type was included separately as the set of features.
-It was found that the elastic-net regularized the coefficients of far more [???
-quantify] distance-type predictors to 0 compared to datasets with overlap count and percent predictor types, regardless of cell line or data resolution (Supplementary Figure 3).
-Many elastic-net models using overlap count or percent predictors were reduced to ridge, or near-ridge regression models at higher data resolutions by having the $alpha$ penalization term tuned to 0 in the cross-validation step, thereby not reducing, or reducing very few of the feature space.
-The results of the variable reduction step imply that far more information relating annotions to TAD boundaries is encoded in the distance-type predictors.
-That is, the elastic-net algorithms were better able to separate noise and reduce the feature space when performed on distance-type predictors.
-Likewise, this reduction was most efficient at more refined levels of data resolution.
-
-## MODELS WITH DISTANCE-TYPE PREDICTORS OUTPERFORM MODELS WITH OTHER PREDICTOR-TYPES
+## CLASS IMBALANCE SEVERELY IMPACTS MODEL PERFORMANCE ACROSS RESOLUTIONS
 
@@
 
+# LIMITATIONS
+
+Many elastic-net models using overlap count or percent predictors were reduced to ridge, or near-ridge regression models at higher data resolutions by having the $alpha$ penalization term tuned to 0 in the cross-validation step, thereby not reducing, or reducing very few of the feature space.
+The results of the variable reduction step imply that far more information relating annotions to TAD boundaries is encoded in the distance-type predictors.
+That is, the elastic-net algorithms were better able to separate noise and reduce the feature space when performed on distance-type predictors.
+Likewise, this reduction was most efficient at more refined levels of data resolution.
+
 # Abbreviations

### 2019-04-05 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-We first examined the class imbalance of the different data resolutions for each cell line.
+We examined the class imbalance of the different data resolutions for each cell line.
 As expected, the total number of genomic bins decreased as resolution decreased.
@@
 
-After suitably reducing the feature space, we performed individual random forest classification models specific to cell line, data resolution, resampling technique, and predictor type.
-We assessed each models' ability to correctly identify the genomic bins that overlap with flanked TAD boundaries using F1-Score, MCC, and balanced accuracy.
-For 10 kb data resoltion, it was found that models with distance-type predictors performed better according to all metrics, across each cell line, regardless of resampling technique used (Figure 4).
-This result was consistent across each of the other data resolutions as well (Supplementary Figure 4).
-Notably, we saw marked improvements in performance for models implemented on resampled datasets when compared to no resampling.
+We first evaluated model performances using only the overlap counts predictor types without re-sampling as these characteristics represented models with the least granularity and could act as a baseline.
+We measured the performances across resolutions for each cell line (Figure 7 (A)).
+Some notable results became clear.
+First, we see that the conventional AUC value was unable to accurately portray the poor performance of the models when compared to the composite metrics F1-score, MCC, and, to a lesser extent, the balanced accuracy.
+Inspecting the F1-score and MCC more closely, we see that some models at lower resolutions (for either cell line) were unable to correctly predict any bins that overlap with flanked TAD boundaries in the test data, as indicated by the missing bars.
+
+## DATA RE-SAMPLING IMPROVES MODEL PERFORMANCE
+
+Comparisons of the effects of the various resampling techniques were then made across resolutions, for each cell line.
+Results showed that performances drastically improved among the composite metrics (Figure 7 (B-D)).
+Models implemented on randomly under-sampled and SMOTE-sampled data performed similarly, while performances on randomly over-sampled data lagged behind, yet still outperformed models with no data re-sampling.
+Overall, there appeared the be a downward trend in model performance as resolutions decreased, across both cell lines.
+
+## USING DISTANCE-TYPE PREDICTORS FURTHER IMPROVED MODEL PERFORMANCES
+
+After illustrating the improvement in model performance using re-sampled data for only the overlap counts predictor types, we then directly compared the performances of each re-sampling techniques on the other two predictor types (overlap percents and distances).
+Immediately, results showed that models with distance-type predictors outperformed models with other predictor types (Figure 8 (A-D)).
+This results was consistent across resolution and cell line.
+As before, we are able to gain much more insight into the performances of the models by using composite metrics as opposed to simply the AUC, in cases of class imbalance.
+Likewise, performances were shown to continue to degrade as resolutions decreased.
+
+## MODELS IMPLEMENTED ON SMOTE RE-SAMPLED DATA WITH DISTANCE-TYPE PREDICTORS PERFORMED BEST AMOUNG ALL ENSEMBLE SYSTEMS
+
+Of the re-sampling techniques considered, it was found that SMOTE re-sampled datasets, implemented on distance-type predictors, yielded the highest model performances across each of the 3 composite metrics (Figure 9).
+These results were consistent across resolution and cell line.
+Although RUS performed only marginally worse than SMOTE, there was a steap drop off in performances for ROS and no re-sampling, across both resolution and cell line.
+These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that incorporates both random under- and over-sampling, as SMOTE is known to do.
 
@@
 
-We then directly compared models using SMOTE resampled datasets across each data resolution to see how performances changed as resolution increased.
-For each cell line, we found that model performances tended to decline as data resolution increased.
-Random forest models implemented on 10 kb, SMOTE resampled, data resolutions, with distance-type predictors were found to perform best according to MCC and balanced accuracy (Figure 5).
+Furthermore, we found that model performances tended to decline as data resolution decreased.
+Random forest models implemented on 10 kb, SMOTE resampled, data resolutions, with distance-type predictors were found to perform best according to MCC and balanced accuracy.
 There was a slight improvement in F1-Score for the 25 kb resolution on the GM12878 cell line.
-Performances from the K562 cell line degraded much faster as resolution increased, while the worst performing models for the GM12878 cell line were at the 50 kb resolution, followed by a slight improvement in performance at the 100 kb resolution.
-To be comprehensive we evaluated the performances across resolutions of models with distance-type predictors for the other resampling techniques and found the results to be largely consistent (Supplementary Figure 5).
-
-## DATA RESAMPLING IMPROVES MODEL PREDICTION
+Performances from the K562 cell line degraded much faster as resolution decreased, while the worst performing models for the GM12878 cell line were at the 50 kb resolution, followed by a slight improvement in performance at the 100 kb resolution.
 

### 2019-04-05 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-## MODELS IMPLEMENTED ON SMOTE RESAMPLED DATA PERFORMED BEST
-
-Of the, resampling techniques considered, it was found that SMOTE resampled datasets, at the 10 kb resoltion, yielded the highest model performances across each metric.
-This result was, for the most part, consistent for the other data resolutions.
-Performances of randomly under-sampled datasets were found to be comparable to, if not better than (at some isolated resolutions; see supplementary), SMOTE.
-The steap drop off in performance for randomly over-sampled and no resampled datasets was most evident when assessing F1-scores and balanced accuracies.
-Measures of MCC were found to increase more steadily toward models implemented on SMOTE resampled datasets.
-These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that incorporates both random under- and over-sampling, as SMOTE is known to do.
-
 Furthermore, we found that model performances tended to decline as data resolution decreased.
@@
 
+## VARIABLE IMPORTANCES FROM TOP PERFORMING MODELS CONFIRMED BIOLOGICAL FUNCTIONALITY OF KNOWN GENOMIC ANNOTATIONS
+
+Lastly, we investigated which genomic annotations were most predictive of TAD boundary formation.
+Looking at heatmaps of variable importances provided by the random forest classifiers implemented on SMOTE re-sampled data, with distance-type predictors, we found that known transcription factors associated with the hypothesized loop extrusion model [???
+include refs] were give high predictive importance in the model (Figure 10).
+These tended to include the SMC3ab, ZNF143, CTCF, and RAD21 transcription factor binding sites and were found to be ranked consistly across resolution.
+Other annotations known to be associated with gene regulation and affect structural properties of chromatin, such as the YY1 and MAZ transcription factors, as well DNAse hypersensitive sites, regions of heterochromatin, and the H3k27 trimethylation and H3K4me1 modifications were less consistently ranked across resolutions for either cell line.
+
 # DISCUSSION
@@
 We developed an ensemble framework to systematically compare model performances for different combinations of class balancing and feature engineering techniques aimed aimed at determining a consensus approach to predicting TAD boundary formation using genomic annotations
+
+Although we were not able to draw direct comparisons between the GM12878 and K562 cell lines, given that they did not contain the same list of cell type specific annotations, we did find that there was relative agreement in rankings of the top 5-7 predictors.
+However, there were notable exclusions from each cell line, in addition to inconsistencies across resolutions
 

### 2019-04-05 Scripts/evaluating_pca.Rmd
editted pca script

@@
 
-## Saving clustered annotation plots
+## Clustering annotations
 
@@
 
-###GM12878
+###Saving clustering annotations plots
+
+####GM12878
 
@@
 
-###K562
+####K562
 
@@
 
-# Clustering TADs
+## Clustering annotations (unseparated)
+
+```{r}
+pcaplotfunction <- function(cl, resolution){
+
+  if(cl=="GM12878"){
+    countdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", resolution, "_count.rds",
+                    sep="")
+    percdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", resolution, "_perc.rds",
+                    sep="")
+    distdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", resolution, "_dist.rds",
+                    sep="")
+  }else{
+      countdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_count.rds",
+                    sep="")
+    percdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_perc.rds",
+                    sep="")
+    distdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_dist.rds",
+                    sep="")
+    }
+
+  countdata <- readRDS(countdir)
+  percdata <- readRDS(percdir)
+  distdata <- readRDS(distdir)
+
+  #performing log2 transformation on distances
+  distdata <- apply(distdata,2,function(x){log(x + 1, base=2)})
+
+  data <- (countdata + percdata + distdata)/3
+
+  colnames(data) <- gsub(paste(c("Gm12878", "K562",
+                                 "-",
+                                 "_",
+                                 "Haib",
+                                 "Sydh",
+                                 "Uta",
+                                 "Uw",
+                                 "Broad",
+                                 "Uchicago",
+                                 "count",
+                                 "perc",
+                                 "dist"), collapse = "|"),"", colnames(data))
+
+  data <- t(data)
+
+  #determine optimal number of clusters
+  pamk.best <- pamk(data)
+
+  #perform PAM clustering
+  pam.med <- pam(data, k = pamk.best$nc, diss = FALSE,
+                 metric = "manhattan", 
+                 #medoids = NULL, 
+                 #stand = FALSE, 
+                 cluster.only = FALSE,
+                 do.swap = TRUE,
+                 keep.diss = FALSE,
+                 keep.data = FALSE,
+                 pamonce = FALSE, 
+                 trace.lev = 0)
+
+  data <- data.frame(data)
+  data$Cluster <- factor(pam.med$clustering)
+  data$Medoid <- factor(ifelse(rownames(data) %in% rownames(pam.med$medoids), "Center", "Other"),
+                        levels=c("Other", "Center"))
+
+  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/cluster_by_annotation/", 
+                       cl, resolution, predictortype, annotation,
+                       ".png", sep=""),
+      width=11, height=8, units="in", res = 300)
+  print({
+    autoplot(prcomp(data[,-c(dim(data)[2]-1,dim(data)[2])]),
+           data=data,
+           #loadings = TRUE,
+           label = TRUE, 
+           label.size = 3,
+           label.repel=T, 
+           colour="Cluster",
+           shape="Medoid",
+           label.show.legend = FALSE) +
+    theme_bw()
+  })
+  dev.off()
+
+}
+
+```
+
+## Clustering TADs
 

### 2019-04-05 Manuscript/Supplementary/supplementary_legends.Rmd
editted supplementary legends

--- 2019-03-11 Manuscript/Supplementary/supplementary_legends.Rmd
@@
 Imbalance ratio is defined as the ratio of genomic bins that overlapped a flanked TAD boundary (minority class), divided by the number of genomic bins that did not overlap a flanked TAD boundary (majority class).
+-->
 
+**Supplementary Figure 15.
+Data summaries in the form of barplots for the GM12878 (red) and K562 (blue) cell lines.** (A) The total number of genomic bins created by partitioning the linear genome into unit intervals corresponding to the resolution of the relevant domain data.
+(B) Subsequent imbalance ratios, defined as the ratio of the number of bins that overlapped with a flanked TAD boundary to the number of bins that did not overlap with a flanked TAD boundary.
+
+<!--
 **Supplementary Figure 2.
@@
 
-**Supplementary Figure 3.
-Heatmaps illustrating which features were reduced using Elastic-Net regularization.** An elastic-net algorithm was used to improve computational efficiency and reduce noise for both the GM12878 (A) and K562 (B) cell lines.
-Features that were regularized and subsequently removed from downstream modeling are denoted in white, while the features that were not regularized and kept for further analyses are denoted in red.
-Each vertical region is made up of a particular data resolution (10 kb, 25 kb, 50kb, and 100 kb), resampling technique (None, RUS, ROS, and SMOTE), and predictor type (OC, OP, and Distance).
-The yellow lines separate each of the three predictor types (overlap counts, overlap percents, and distance types respectively).
+**Supplementary Figure 2A. Correlograms separated by genomic annotation category for overlap count predictor types, using 10 kb resolution data, on the GM12878 cell line** 
+-->
 
-**Supplementary Figrue 4.
+<!--
+**Supplementary Figrue 12.
 Barplots comparing model performance for each predictor type across 25 kb, 50 kb, and 100 kb data resolutions** Model performances were evaluated using F1-scores, MCCs, and balanced accuracies for each of the 4 resampling techniques, across both the GM12878 (A-C) and K562 (D-F) cell lines.
@@
 
-**Figure 6.
+**Supplementary Figure 14A.
 Variable importance of the top 20 most predictive genomic annotations for models using no resampling technique with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
@@
 
-**Figure 7.
+**Supplementary Figure 14B.
 Variable importance of the top 20 most predictive genomic annotations for models using random over-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
@@
 
-**Figure 8.
+**Supplementary Figure 14C.
 Variable importance of the top 20 most predictive genomic annotations for models using random under-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
@@
 The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using random under-sampling to create balanced classes, for each cell line respectively.
+-->
 

### 2019-04-05 Scripts/evaluating_correlations.Rmd
editted correlations and pca scripts

@@
 
-corfunction <- function(cl, resolution, predictortype, annotation){
+corfunction <- function(cl, resolution){
   #set up variable names to subset
@@
 
+#### Saving GM12878 Correlation Plots (unseparated)
+
+```{r}
+corfunction <- function(cl, resolution){
+
+  if(cl=="GM12878"){
+    countdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", 
+                     resolution, 
+                     "_count.rds",
+                    sep="")
+    percdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", 
+                    resolution,
+                    "_perc.rds",
+                    sep="")
+    distdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", 
+                    resolution, 
+                    "_dist.rds",
+                    sep="")
+  }else{
+    countdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_",
+                     resolution,
+                     "_count.rds",
+                    sep="")
+    percdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_",
+                    resolution,
+                    "_perc.rds",
+                    sep="")
+    distdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_",
+                    resolution,
+                    "_dist.rds",
+                    sep="")
+    }
+
+  countdata <- readRDS(countdir)
+  percdata <- readRDS(percdir)
+  distdata <- readRDS(distdir)
+
+  #performing log2 transformation on distances
+  distdata <- apply(distdata,2,function(x){log(x + 1, base=2)})
+
+  if(cl=="K562"){
+    countdata <- countdata[,-grep("Znf274", colnames(countdata))]
+    percdata <- percdata[,-grep("Znf274", colnames(percdata))]
+    distdata <- distdata[,-grep("Znf274", colnames(distdata))]
+  }
+
+  corrcount <- cor(countdata, method = "spearman")
+  corrperc <- cor(percdata, method = "spearman")
+  corrdist <- cor(distdata, method = "pearson")
+
+  corrdata <- (corrcount + corrperc + corrdist)/3
+
+  colnames(corrdata) <- rownames(corrdata) <- gsub(paste(c("Gm12878", "K562",
+                                 "-",
+                                 "_",
+                                 "Haib",
+                                 "Sydh",
+                                 "Uta",
+                                 "Uw",
+                                 "Broad",
+                                 "Uchicago",
+                                 "count",
+                                 "perc",
+                                 "dist"), collapse = "|"),"", colnames(corrdata))
+
+  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/correlation_plots_unseparated/", 
+                       cl, resolution,
+                       ".png", sep=""),
+      width=11, height=8, units="in", res = 300)
+  corrplot(corrdata,
+         method="color",
+         type="lower", 
+         order="hclust", 
+         tl.col="black", 
+         #tl.srt=90,
+         tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+  dev.off()
+
+}
+
+corfunction(cl = "GM12878", resolution = "10kb")
+
+corfunction(cl = "GM12878", resolution = "25kb")
+
+corfunction(cl = "GM12878", resolution = "50kb")
+
+corfunction(cl = "GM12878", resolution = "100kb")
+
+```
+
 #### Saving K562 Correlation Plots
@@
 ```
+
+#### Saving K562 Correlation Plots (unseparated)
+
+```{r}
+corfunction(cl = "K562", resolution = "10kb")
+
+corfunction(cl = "K562", resolution = "25kb")
+
+corfunction(cl = "K562", resolution = "50kb")
+
+corfunction(cl = "K562", resolution = "100kb")
+
+```

### 2019-04-05 Manuscript/manuscript.Rmd
editted manuscript

@@
 By isolating bins that overlapped with flanked TAD boundaries we were able to assess the correlations of genomic annotations and determine which annotations were enriched together at boundaries.
-To  get a hollisitic view of how some annotations tended to occur together at boundaries, we computed the pairwise correlations of the averages between count overlaps, count percents, and $log_{2}$ distances of each genomic annotation with bins that overlapped with flanked TAD boundaries.
+To  get a hollisitic view of how some annotations tended to occur together at boundaries, we computed the average pairwise correlations between count overlaps, count percents, and $log_{2}$ distances of each genomic annotation with bins that overlapped with flanked TAD boundaries.
 Clustered correlograms at the 10 kb resolution, for both cell lines, showed that distinct groups of transcription factors were highly correlated including CTCF, ZNF143, RAD21, and SMC3ab (Figure 7).
@@
 Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly correlated, yet inversely correlated with many transcription factor binding sites.
-Similar correlations were exhibited across the remainder of resolutions, for both cell lines (Supplementary Figure X).
+Similar correlations were exhibited across the remainder of resolutions, for both cell lines (Supplementary Figures 2-4).
 The high correlations among many of the genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.
@@
 Lastly, we investigated which genomic annotations were most predictive of TAD boundary formation.
-Looking at heatmaps of variable importances provided by the random forest classifiers implemented on SMOTE re-sampled data, with distance-type predictors, we found that known transcription factors associated with the hypothesized loop extrusion model [???
-include refs] were give high predictive importance in the model (Figure 10).
+Looking at heatmaps of variable importances provided by the random forest classifiers implemented on SMOTE re-sampled data, with distance-type predictors, we found that known transcription factors associated with the hypothesized loop extrusion model [@fudenberg2016formation; @alipour2012self] were give high predictive importance in the model (Figure 10).
 These tended to include the SMC3ab, ZNF143, CTCF, and RAD21 transcription factor binding sites and were found to be ranked consistly across resolution.
@@
 
-# LIMITATIONS
+## LIMITATIONS
 

### 2019-04-05 Scripts/evaluating_correlations.Rmd
added to correlation script

@@
 ```
+
+#### Specific correlations
+
+##### GM12878
+
+######10kb
+
+```{r}
+cl = "GM12878"; resolution = "10kb";
+
+vars1 <- c("02WeakPromoter", "06WeakEnhancer", "H2az", "H3k4me2", "H3k4me3", "H3k27ac", "H3k9ac", "DNase", "Runx3sc101553", "11WeakTxn", "07WeakEnhancer", "H3k4me1")
+
+vars2 <- c("08Insulator", "Ctcf", "Ctcfsc15914c20", "Rad21", "Smc3ab9263", "Yy1sc281", "Znf143166181ap")
+
+corrdata1 <- corrdata[which(rownames(corrdata) %in% vars1), which(colnames(corrdata) %in% vars1)]
+colnames(corrdata1) <- rownames(corrdata1) <- colnames(corrdata1)[c(1,2,11,10,8,3,6,12,4,5,7,9)]
+
+corrplot(corrdata1,
+         method="number",
+         type="upper", 
+         #order="hclust", 
+         tl.col="black", 
+         #tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+corrdata2 <- corrdata[which(rownames(corrdata) %in% vars2), which(colnames(corrdata) %in% vars2)]
+colnames(corrdata2) <- rownames(corrdata2) <- colnames(corrdata2)[c(1,2,3,4,5,6,7)]
+
+corrplot(corrdata2,
+         method="number",
+         type="upper", 
+         #order="hclust", 
+         tl.col="black", 
+         #tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+```
+
+##### K562
+
+######10kb
+
+```{r}
+cl = "K562"; resolution = "10kb";
+
+vars1 <- c("Ctcflsc98982", "Rad21", "Ctcfb", "Ctcf", "Ctcfc", "Smc3ab9263", "Znf143", "Cebpb")
+
+vars2 <- c("Corestsc30189", "Mazab85725", "DNase", "H3k4me1", "H3k4me2", "H3k4me3", "Egr1", "Elf1sc631", "Zbtb7asc34508", "E2f6", "Max", "H2az", "02WeakPromoter", "06WeakEnhancer")
+
+corrdata1 <- corrdata[which(rownames(corrdata) %in% vars1), which(colnames(corrdata) %in% vars1)]
+colnames(corrdata1) <- rownames(corrdata1) <- colnames(corrdata1)[c(4,7,3,6,2,8,1,5)]
+
+corrplot(corrdata1,
+         method="number",
+         type="lower", 
+         #order="hclust", 
+         tl.col="black", 
+         #tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+corrdata2 <- corrdata[which(rownames(corrdata) %in% vars2), which(colnames(corrdata) %in% vars2)]
+colnames(corrdata2) <- rownames(corrdata2) <- colnames(corrdata2)[c(3,13,4,9:11,6,7,14,5,12,8,1,2)]
+
+corrplot(corrdata2,
+         method="number",
+         type="lower", 
+         #order="hclust", 
+         tl.col="black", 
+         #tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("blue", "white", "red"))(20),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+```

### 2019-04-05 Manuscript/manuscript.Rmd
manuscript edits

@@
 Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly correlated, yet inversely correlated with many transcription factor binding sites.
-Similar correlations were exhibited across the remainder of resolutions, for both cell lines (Supplementary Figures 2-4).
+Similar correlations were exhibited across the remainder of resolutions, for both cell lines (Supplementary Figures X-Y).
 The high correlations among many of the genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.
@@
 We first evaluated model performances using only the overlap counts predictor types without re-sampling as these characteristics represented models with the least granularity and could act as a baseline.
-We measured the performances across resolutions for each cell line (Figure 7 (A)).
+We measured the performances across resolutions for each cell line (Figure 8 (A)).
 Some notable results became clear.
@@
 Comparisons of the effects of the various resampling techniques were then made across resolutions, for each cell line.
-Results showed that performances drastically improved among the composite metrics (Figure 7 (B-D)).
+Results showed that performances drastically improved among the composite metrics (Figure 8 (B-D)).
 Models implemented on randomly under-sampled and SMOTE-sampled data performed similarly, while performances on randomly over-sampled data lagged behind, yet still outperformed models with no data re-sampling.
@@
 
+<!-- IN PROGRESS
 # DISCUSSION
@@
 Likewise, this reduction was most efficient at more refined levels of data resolution.
+-->
 

### 2019-04-05 Scripts/evaluating_model_performances.Rmd
added to model performances script

@@
 
-figure <- ggarrange(p.g.ros,p.g.rus,p.g.smote,
-                    p.k.ros,p.k.rus,p.k.smote,ncol = 3, nrow = 2, common.legend = TRUE, legend = "top")
+figure <- ggarrange(p.g.none,p.g.none,
+                p.g.ros,p.k.ros,
+                p.g.rus,p.k.rus,
+                p.g.smote,p.k.smote,
+                ncol = 2, nrow = 4, 
+                common.legend = TRUE, 
+                legend = "top",
+                labels = c("A","",
+                           "B","",
+                           "C","",
+                           "D",""),
+                font.label = list(size=20))
 figure

### 2019-04-05 Manuscript/Figures/figure_legends.Rmd
added figures and editted legends
updating figures and legends

@@
 **Figure 1: Model Construction.** An illustration of the proposed model construction given cell line-specific Hi-C matrices.
-The contact matrix above is a visualization of the interconnectivity of chromosome 14 (GM12878 cell line, [???] resolution) on the intervals from 20 mb to 100 mb.
+The contact matrix above is a visualization of the interconnectivity of chromosome 14 at 100 kb resolution, for the GM12878 cell line, on the intervals from 20 mb to 100 mb.
 The boundary coordinates of topologically association domains (TADs) were identified using the Arrowhead algorithm.
@@
 **Figure 2: Ensemble Framework/Model Building Pipeline.** A diagram of the model building pipeline given a combination of inputs from the ensemble framework.
-For a particular cell line, contact matrix resolution, and set of features, the data was split into a 7:3 training:testing set ratio.
-For the training set, recursive feature elimination was used to reduce the feature space and minimize the influence of uninformative predictors.
-[???
-Should this be moved?] A particular resampling technique was applied to the reduced training set to create balanced classes.
-A random forest classification algorithm was then performed and validated using the testing set.
+A particular ensemble system included the total number of genomic bins, labeled as having been overlapped with a flanked TAD boundary or not, as well as a feature space composed of 1 of 3 different predictor-type specific annotations.
+The data was then split into a 7:3 training:testing set ratio.
+A re-sampling technique was applied to the training set, followed by an elastic-net regularization to reduce the feature space.
+Lastly, a random forest classification model was performed on the re-sampled and reduced training set and validated on the held out testing set common to all ensemble systems in the framework.
 
@@
 
+**Figure 4.
+Data summaries in the form of barplots for the GM12878 (red) and K562 (blue) cell lines.** (A) The total number of genomic bins created by partitioning the linear genome into unit intervals corresponding to the resolution of the relevant domain data.
+(B) Subsequent imbalance ratios, defined as the ratio of the number of bins that overlapped with a flanked TAD boundary to the number of bins that did not overlap with a flanked TAD boundary.
+
+**Figure 7. Evaluating effect of class imbalance on model performance.**
+
+<!--
 **Figure 4.
@@
 The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using SMOTE resampling, for each cell line respectively.
+-->
 

### 2019-04-05 Manuscript/Supplementary/supplementary_legends.Rmd
added figures and editted legends
updating figures and legends

@@
 -->
-
-**Supplementary Figure 15.
-Data summaries in the form of barplots for the GM12878 (red) and K562 (blue) cell lines.** (A) The total number of genomic bins created by partitioning the linear genome into unit intervals corresponding to the resolution of the relevant domain data.
-(B) Subsequent imbalance ratios, defined as the ratio of the number of bins that overlapped with a flanked TAD boundary to the number of bins that did not overlap with a flanked TAD boundary.
 

### 2019-04-05 Manuscript/Supplementary/supplementary_legends.Rmd
added figures to supplementary and updated legends

@@
 **Supplementary Figure 1.
-Distance Densities across cell lines and resolutions.** Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for 10 kb (A), 25 kb (B), 50 kb (C), and 100 kb (D) data resolutions across the GM12878 (left column) and K562 (right column) cell lines.
+Distance Densities Across Cell Lines and Resolutions.** Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for 10 kb (A), 25 kb (B), 50 kb (C), and 100 kb (D) data resolutions across the GM12878 (left column) and K562 (right column) cell lines.
 The untransformed distance densities are filled in red, while the $log_{2}$ tranformed distance densities are filled in blue.
+
+**Supplementary Figure 2.
+Clustered Correlogram for Genomic Annotations at the 10 kb Resolution for the GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 3.
+Clustered Correlogram for Genomic Annotations at the 10 kb Resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 4.
+Clustered Correlogram for Genomic Annotations at the 25 kb Resolution for GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 5.
+Clustered Correlogram for Genomic Annotations at the 25 kb Resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 6.
+Clustered Correlogram for Genomic Annotations at the 50 kb Resolution for GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 7.
+Clustered Correlogram for Genomic Annotations at the 50 kb Resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 8.
+Clustered Correlogram for Genomic Annotations at the 100 kb Resolution for GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 9.
+Clustered Correlogram for Genomic Annotations at the 100 kb Resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
 

### 2019-04-05 Manuscript/manuscript.Rmd
manuscript edits

@@
 The location of TAD boundaries is highly conserved, suggesting the presence of epigenomic marks aiding in TAD formation.
-The ability to predict which epigenomic features are most associated with the TAD boundaries will allow to better understand the regulatory role of the 3D structure of the genome.
+The ability to predict which epigenomic features are most associated with the TAD boundaries will allow for better understanding the regulatory role of the 3D structure of the genome.
 
-Existing methods for predicting associations between genomic elements tend to ignore key characteristics of genomic data.
-Specifically, the number of TAD boundaries is much less than the number of other genomic regions, leading to heavily imbalanced classes [???
-and why this is the problem?
-Instead of classes, something like "leading to the model biased towards classifying the majority of the regions".
-Rewrite].
-Furthermore, most methods utilize direct overlap as a means to quantify the association, while distance, the measure of spatial relationships, remains unaccounted for.
-Consequently, distances on a genomic scale vary widely, leaving uncertainty how the heavily right-tailed distribution of distance measures will affect the model’s performance.
+Existing methods for predicting associations between genomic annotations tend to ignore key characteristics of genomic data.
+Specifically, when constructing the model for classification, the number of genomic regions surrounding TAD boundaries is much less than the number of other regions.
+This leads to heavily imbalanced classes and can result in poor performances as a model's ability to assign a new sample to a given class is influenced by the prevalence of that class in the training set.
+Furthermore, most methods utilize direct overlap as a means to quantify this association, while distance, the measure of spatial relationships, remains unaccounted for.
 
-**Methods.** We propose a novel data pre-processing pipeline that systematically addresses those shortcomings.
-Lasso and Elastic Net [???
-Adjust methods to the current setup] were used for feature selection, coupled with five classifier methods.
-A number of classifier performance metrics were assessed, including the F1 measure and Matthew Correlation Coefficient (MCC), and area under the ROC curve (AUROC).
+**Methods.** We proposed a novel ensemble framework that systematically addresses those data irregularities and characteristics.
+Multiple random forest classification models, in combination with variations in cell line, data resolution, feature engineering, and re-sampling techniques were performed and compared.
+A number of performance metrics were assessed, including [???
+update when ready].
 
-**Results.** Data preprocessing (log2-transformation and standardization) improves the performance of classification algorithms and allows for the ability to more accurately predict which genomic features are most associated with TAD boundaries.
-In contrast to overlap-based association measures, the distance between genomic elements was the most predictive measure.
-The random undersampling strategy addresses the class imbalance problem the most effectively in nearly all settings.
+**Results.**
 
-**Conclusions.** Current methods used to model the epigenomic features associated with TAD boundaries are insufficiently robust to handle properties of genomic data.
-Models applied to unprocessed data can have poor predictive performances.
-Focusing solely on standard performance assessment metrics, such as AUROC, can mask poor performance of the models; thus, the use of more balanced metrics, such as F1 and MCC, is warranted.
-Our model results in better performances and more accurate identification of important features associated with the formation of TAD boundaries.
+**Conclusions.**
 
@@
 other regions.
-In a classification setting, when one is attempting to discriminate between regions with and without TAD boundaries, the class imbalance issue will contribute to small imbalance ratios (defined as the ratio of minority to majority classes) [@Orriols-Puig2008].
+In a classification setting, when one is attempting to discriminate between regions with and without TAD boundaries, the class imbalance issue will contribute to small imbalance ratios (defined as the ratio of minority to majority classes[@Orriols-Puig2008]).
 Such heavily imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class;@chen2013influence;@jeni2013facing].
@@
 Better measures to consider are composite metrics involving both precision and recall together because they soften the influence of a model's ability to correctly classify majority classes and yield more dependable and interpretable results.
-Therefore, measures like the F1-Score, Matthew's Correlation Coefficient (MCC), and balanced accuracy offer better interpretation, especially in the instance of imbalanced classes [@jeni2013facing].
+Therefore, measures like the F1-Score and Matthew's Correlation Coefficient (MCC) offer better interpretation, especially in the instance of imbalanced classes [@jeni2013facing].
+The F1-Score can be interpreted as a weighted average of the precision and recall values, while the MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
+Each metric uses all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
+
+<!--
+, and balanced accuracy offer better interpretation, especially in the instance of imbalanced classes [@jeni2013facing].
 The F1-Score can be interpreted as a weighted average of the precision and recall values, balanced accuracy measures the average accuracy obtained on either class, and MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
 Each metric uses all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
+-->
 
@@
 Noninformative features were removed using a feature reduction algorithm and random forest classifications were performed to assess model performance, and investigate which genomic annotations were most associated with the TAD boundaries for a given system from the complete ensemble.
-Model performance was evaluated using the F1-Score, MCC, and balanced accuracy.
+Model performance was evaluated using AUROC, AUPRC, F1-Score, and MCC.
 
@@
 
-Genomic annotation data (chromatin states, histone marks, and transcription factor binding sites, GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
+Genomic annotation data in the form of cell type specific chromatin states, histone marks, and transcription factor binding sites (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
 
@@
 
-The efficacy of each re-sampling technique was compared using the F1-score, MCC, and balanced accuracy. These metrics are defined as follows:
+The efficacy of each re-sampling technique was compared using composite metrics inclusing F1-score and MCC. These metrics are defined as follows:
 
@@
 $$MCC = \frac{TP \times TN - FP \times FN}{\sqrt{ (TP + FP)(TP+FN)(TN+FP)(TN+FN) }}$$
-
+<!--
 $$Balanced \quad Accuracy = \dfrac{1}{2}\left( \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} \right)$$
+-->
 
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
+Additional threshold-free metrics where also reported including the AUROC and AUPRC.
 
@@
 As expected, the total number of genomic bins decreased as resolution decreased.
-That is, at lower resolutions, the linear genome was binned into larger units, thereby creating fewer bins (Supplementary Figure 15 (A)).
-The imbalance ratios, however, remained relatively stable (Supplementary Figure 15 (B)).
+That is, at lower resolutions, the linear genome was binned into larger units, thereby creating fewer bins (Figure 4 (A)).
+The imbalance ratios, however, remained relatively stable (Figure 4 (B)).
 We found that there was an average IR of 0.154 (SD=0.022) and 0.137 (SD=0.0181) across resolutions for the GM12878 and K562 cell lines respectively.
@@
 
-By isolating bins that overlapped with flanked TAD boundaries we were able to assess the correlations of genomic annotations and determine which annotations were enriched together at boundaries.
-To  get a hollisitic view of how some annotations tended to occur together at boundaries, we computed the average pairwise correlations between count overlaps, count percents, and $log_{2}$ distances of each genomic annotation with bins that overlapped with flanked TAD boundaries.
-Clustered correlograms at the 10 kb resolution, for both cell lines, showed that distinct groups of transcription factors were highly correlated including CTCF, ZNF143, RAD21, and SMC3ab (Figure 7).
+By isolating bins that overlapped with flanked TAD boundaries and, in turn, counting the instances in which annotations overlapped with said bins (using the overlap counts discussed above) we were able to assess the correlations of genomic annotations and determine which annotations were enriched together at boundaries.
+
+Clustered correlograms for known colocalized annotations showed that distinct groups of transcription factors were highly correlated including CTCF, ZNF143, RAD21, and SMC3ab (Supplementary Figures 2-9).
 Likewise, combinations of particular histone modifications and chromatin states were also shown to exhibit similar profiles near TAD boundaries including H3K4me1, H3K4me2, and H3K4me3, aswell as strong and weak enhancers.
 Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly correlated, yet inversely correlated with many transcription factor binding sites.
-Similar correlations were exhibited across the remainder of resolutions, for both cell lines (Supplementary Figures X-Y).
+These results were consistent across resolution and cell line.
 The high correlations among many of the genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.
-The regularization was performed predictor-type and resolution specific data after implementing each of the resampling techniques within each cell line.
 

### 2019-04-06 Manuscript/manuscript.Rmd
Add references about distance

--- 2019-04-05 Manuscript/manuscript.Rmd
@@
 
-While direct overlaps represent the most straightforward measure of functional associations, they do not account for indirect relationships shown to be one of the major driving force of genome regulation [???
-REFS].
-The most prominent example maybe the enhancer-promoter relationships, with enhancers are frequently located hundreths or thousands bases away from their target promoters [???
-REFS].
+While direct overlaps represent the most straightforward measure of functional associations, they do not account for distant relationships shown to be one of the major driving force of genome regulation [12426570, 24243018].
+The most prominent example maybe the enhancer-promoter relationships, with enhancers are frequently located hundreths or thousands bases away from their target promoters [17086198, 24213634], or even on different chromosomes [15880101].
 The use of distances between TAD boundaries and genomic annotations has largely been ignored.

### 2019-04-06 Manuscript/manuscript.Rmd
manuscript edits

--- 2019-04-05 Manuscript/manuscript.Rmd
@@
 REFS].
-The most prominent example maybe the enhancer-promoter relationships, with enhancers are frequently located hundreths or thousands bases away from their target promoters [???
+The most prominent example being the enhancer-promoter relationships, where enhancers are frequently located hundreds or thousands of bases away from their target promoters [???
 REFS].
@@
 
-By isolating bins that overlapped with flanked TAD boundaries and, in turn, counting the instances in which annotations overlapped with said bins (using the overlap counts discussed above) we were able to assess the correlations of genomic annotations and determine which annotations were enriched together at boundaries.
+By isolating flanked TAD boundaries and, in turn, counting the instances in which annotations overlapped with boundary regions, we were able to assess the correlations of genomic annotations and determine which annotations were enriched together at boundaries.
 
-Clustered correlograms for known colocalized annotations showed that distinct groups of transcription factors were highly correlated including CTCF, ZNF143, RAD21, and SMC3ab (Supplementary Figures 2-9).
-Likewise, combinations of particular histone modifications and chromatin states were also shown to exhibit similar profiles near TAD boundaries including H3K4me1, H3K4me2, and H3K4me3, aswell as strong and weak enhancers.
-Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly correlated, yet inversely correlated with many transcription factor binding sites.
+Clustered correlograms for known colocalized annotations showed that distinct groups of transcription factors were highly positively correlated in both cell lines including CTCF, ZNF143, RAD21, and SMC3ab (Supplementary Figures 2-9).
+Likewise, combinations of particular histone modifications and chromatin states were also shown to exhibit similar profiles near TAD boundaries including H3K4me1, H3K4me2, and H3K4me3, as well as strong and weak enhancers.
+Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly positively inter-correlated, yet were negatively correlated with many transcription factor binding sites.
 These results were consistent across resolution and cell line.
+Notably, correlations amoung annotations were found to increase as resolutions decreased for both cell lines.
+This indicated that TAD bounardies called, and subsequently flanked, at lower resolutions tended to encapsulate more of these epigenomic marks and contribute to higher levels of enrichment.
+
 The high correlations among many of the genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.
 
-## CLASS IMBALANCE SEVERELY IMPACTS MODEL PERFORMANCE ACROSS RESOLUTIONS
+## CLASS IMBALANCE SEVERELY IMPACTS PERFORMANCE OF MODELS WITH OVERLAP COUNTS PREDICTOR TYPES
 
 We first evaluated model performances using only the overlap counts predictor types without re-sampling as these characteristics represented models with the least granularity and could act as a baseline.
-We measured the performances across resolutions for each cell line (Figure 8 (A)).
+We measured the performances across resolutions, for each cell line, and found that .
+
 Some notable results became clear.

### 2019-04-06 Manuscript/manuscript.Rmd
manuscript edits

@@
 As expected, the total number of genomic bins decreased as resolution decreased.
-That is, at lower resolutions, the linear genome was binned into larger units, thereby creating fewer bins (Figure 4 (A)).
-The imbalance ratios, however, remained relatively stable (Figure 4 (B)).
+That is, at lower resolutions, the linear genome was binned into larger units, thereby creating fewer bins (Figure 4A).
+The imbalance ratios, however, remained relatively stable (Figure 4B).
 We found that there was an average IR of 0.154 (SD=0.022) and 0.137 (SD=0.0181) across resolutions for the GM12878 and K562 cell lines respectively.
@@
 
-## CLASS IMBALANCE SEVERELY IMPACTS PERFORMANCE OF MODELS WITH OVERLAP COUNTS PREDICTOR TYPES
+## CLASS IMBALANCE SEVERELY IMPACTS PERFORMANCE AMONG MODELS WITH EITHER OVERLAP COUNTS OR PERCENTS PREDICTOR TYPES
 
-We first evaluated model performances using only the overlap counts predictor types without re-sampling as these characteristics represented models with the least granularity and could act as a baseline.
-We measured the performances across resolutions, for each cell line, and found that .
+We first evaluated model performances for the GM12878 cell line, using only the overlap counts predictor types, without re-sampling, as these characteristics represented models with the least granularity and could act as a baseline.
+We measured the performances across resolutions, and found that a conventional measure such as AUC artificially inflated model performances (Figure 5A (I)).
+In evaluating the composite metrics like F1-Score and MCC, we found more reasonable depictions of poor performance, given such high levels of class imbalance (Figure 5A (II-IV)).
+At the 50 kb and 100 kb resolution, for overlap counts, the F1-Score and MCC could not be determined given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data.
+When including overlap percents perdictor types in the models, we found that AUC values were comparable to OC models, across resolution.
+However, when considering both the F1-Score and MCC, we found that OP models performed worse than OC models.
+Similarly, at the 50 kb and 100 kb resolutions, models built on OP were unable produce F1-Scores or MCC values.
+Similar results were found for the K562 cell line (Supplementary Figure 10A (I-IV)).
 
-Some notable results became clear.
-First, we see that the conventional AUC value was unable to accurately portray the poor performance of the models when compared to the composite metrics F1-score, MCC, and, to a lesser extent, the balanced accuracy.
-Inspecting the F1-score and MCC more closely, we see that some models at lower resolutions (for either cell line) were unable to correctly predict any bins that overlap with flanked TAD boundaries in the test data, as indicated by the missing bars.
+## DATA RE-SAMPLING IMPROVES PERFORMANCE AMONG MODELS WITH OVERLAP COUNTS PREDICTOR TYPES
 
-## DATA RE-SAMPLING IMPROVES MODEL PERFORMANCE
+Comparisons of the effects of the various resampling techniques were then made for models using overlap counts predictor types, across resolutions.
+Simply considering AUC did not depict any notable improvement in performances, regardless of the re-sampling technique (Figure 5B-5D (I)).
+However, when considering the other composite metrics we found that there was a substantial increase in F1-Score and MCC in each of the 3 resampling techniques.
+For overlap counts predictors, both RUS and SMOTE resampled datasets were found to yield consistently better results than no resampling and ROS.
 
-Comparisons of the effects of the various resampling techniques were then made across resolutions, for each cell line.
 Results showed that performances drastically improved among the composite metrics (Figure 8 (B-D)).

### 2019-04-07 Manuscript/manuscript.Rmd
manuscript edits

--- 2019-04-06 Manuscript/manuscript.Rmd
@@
 ---
-title: "Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings"
+title: Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance
+  Settings
 csl: styles.ref/genomebiology.csl
@@
     reference_docx: styles.doc/NIH_grant_style.docx
+  pdf_document: default
 bibliography: References/references.bib
@@
 A number of performance metrics were assessed, including [???
-update when ready].
+will update when ready].
 
@@
 
-Multiple random forest classification algorithms were built on domain data extracted from Hi-C data for 2 cell lines $C = \{GM12878, K562\}$, at four different resolutions $R = \{10 kb, 25 kb, 50 kb, 100 kb\}$.
-For each classifier, we compared three predictor types $P = \{\text{OC}, \text{OP}, \text{Distance}\}$ and 4 class balancing techniques $B = \{None, RUS, ROS, SMOTE}$.
-A system produced from the ensemble framework was defined as: $S = \{c, r, p, b\}$, where $c \in C, \quad R \in R, \quad p \in P,$ and $b \in B$.
+Multiple random forest classification algorithms were built on domain data extracted from Hi-C data for 2 cell lines $C = \{GM12878, K562\}$, at four different resolutions $R = \{\text{10 kb}, \text{25 kb}, \text{50 kb}, \text{100 kb\}}$.
+For each classifier, we compared three predictor types $P = \{\text{OC}, \text{OP}, \text{Distance}\}$ and 4 class balancing techniques $B = \{None, RUS, ROS, SMOTE\}$.
+A system produced from the ensemble framework was defined as: $S = \{c, r, p, b\}$, where $c \in C$, $r \in R$, $p \in P$, and $b \in B$.
 Letting $|X|$ denote the cardinality of each set, we evaluated $|C| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $96 (= 2 \times 4 \times 3 \times 4)$ separate models.
@@
 We examined the class imbalance of the different data resolutions for each cell line.
-As expected, the total number of genomic bins decreased as resolution decreased.
-That is, at lower resolutions, the linear genome was binned into larger units, thereby creating fewer bins (Figure 4 (A)).
-The imbalance ratios, however, remained relatively stable (Figure 4 (B)).
+As expected, the total number of genomic bins decreased as resolution decreased (Figure 4A).
+That is, at lower resolutions, the linear genome was binned into larger units, thereby creating fewer bins.
+The imbalance ratios, however, remained relatively stable across resolutions (Figure 4B).
 We found that there was an average IR of 0.154 (SD=0.022) and 0.137 (SD=0.0181) across resolutions for the GM12878 and K562 cell lines respectively.
 Ideally, a balanced dataset will have an IR close to 0.50.
-Here, the low imbalance ratios indicated a wide disparity between majority and minority classes (i.e.
-a genomic bin was much more likely to not overlap with a flanked TAD boundary than it was to overlap with one).
-Therefore suitable resampling techniques were needed.
+Here, the low imbalance ratios indicated a wide disparity between majority and
 
@@
 By isolating flanked TAD boundaries and, in turn, counting the instances in which annotations overlapped with boundary regions, we were able to assess the correlations of genomic annotations and determine which annotations were enriched together at boundaries.
-
-Clustered correlograms for known colocalized annotations showed that distinct groups of transcription factors were highly positively correlated in both cell lines including CTCF, ZNF143, RAD21, and SMC3ab (Supplementary Figures 2-9).
+Clustered correlograms for known colocalized annotations showed that distinct groups of transcription factors were highly positively correlated in both cell lines, and across resolutions, including CTCF, ZNF143, RAD21, and SMC3ab (Supplementary Figures 2-9).
 Likewise, combinations of particular histone modifications and chromatin states were also shown to exhibit similar profiles near TAD boundaries including H3K4me1, H3K4me2, and H3K4me3, as well as strong and weak enhancers.
 Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly positively inter-correlated, yet were negatively correlated with many transcription factor binding sites.
-These results were consistent across resolution and cell line.
-Notably, correlations amoung annotations were found to increase as resolutions decreased for both cell lines.
+Notably, correlations among annotations were found to increase as resolutions decreased for both cell lines.
 This indicated that TAD bounardies called, and subsequently flanked, at lower resolutions tended to encapsulate more of these epigenomic marks and contribute to higher levels of enrichment.
 
+<!--
 The high correlations among many of the genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.
+-->
 
-## CLASS IMBALANCE SEVERELY IMPACTS PERFORMANCE OF MODELS WITH OVERLAP COUNTS PREDICTOR TYPES
+## CLASS IMBALANCE SEVERELY IMPACTS PERFORMANCE AMONG ALL CLASSES OF MODELS
 
-We first evaluated model performances using only the overlap counts predictor types without re-sampling as these characteristics represented models with the least granularity and could act as a baseline.
-We measured the performances across resolutions, for each cell line, and found that .
+We first evaluated performances for models implemented using overlap counts predictor types, without re-sampling (on the GM12878 cell line), as these characteristics represented models with the least granularity and could act as a baseline.
+In evaluating such composite metrics like F1-Score and MCC, we found that these models exhibited poor performances across resolutions (Figure 5A).
+Furthermore, at lower resolutions (50 kb and 100 kb specifically), the F1-Score and MCC could not be determined given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives, as can be seen by the missing red points.
+When including overlap percents perdictor types in the models, coupled with no resampling, we found that performances were worse than when using OC predictor types (Figure 5B).
+As with OC predictor types, these models were also not able to yield F1-Scores and MCCs at the 50 kb and 100 kb resolution.
+Models built on distance-type predictors, however, exhibited slightly better performances than the other two types, yet still yielded missing or low F1-Scores and MCC at lower resolutions (Figure 5C).
+This indicated that the key driver leading to poor performances was not feature engineering, but instead the severity in the class imbalance.
 
-Some notable results became clear.
-First, we see that the conventional AUC value was unable to accurately portray the poor performance of the models when compared to the composite metrics F1-score, MCC, and, to a lesser extent, the balanced accuracy.
-Inspecting the F1-score and MCC more closely, we see that some models at lower resolutions (for either cell line) were unable to correctly predict any bins that overlap with flanked TAD boundaries in the test data, as indicated by the missing bars.
+## DATA RE-SAMPLING IMPROVED PERFORMANCE AMONG ALL CLASSES OF MODELS
 
-## DATA RE-SAMPLING IMPROVES MODEL PERFORMANCE
-
-Comparisons of the effects of the various resampling techniques were then made across resolutions, for each cell line.
-Results showed that performances drastically improved among the composite metrics (Figure 8 (B-D)).
-Models implemented on randomly under-sampled and SMOTE-sampled data performed similarly, while performances on randomly over-sampled data lagged behind, yet still outperformed models with no data re-sampling.
-Overall, there appeared the be a downward trend in model performance as resolutions decreased, across both cell lines.
+Comparisons of the effects of the various resampling techniques were then made.
+We found that there was a substantial increase in F1-Score and MCC for models built on resampled data using any of the 3 techniques (Figure 5).
+After resampling, we were able to report performances at the lower resolutions which was not feasible for models built on fully imbalanced data.
+For all predictor types, implementation of either RUS or SMOTE resampling was found to yield consistently better results than no resampling and ROS.
 
@@
 
-After illustrating the improvement in model performance using re-sampled data for only the overlap counts predictor types, we then directly compared the performances of each re-sampling techniques on the other two predictor types (overlap percents and distances).
-Immediately, results showed that models with distance-type predictors outperformed models with other predictor types (Figure 8 (A-D)).
-This results was consistent across resolution and cell line.
-As before, we are able to gain much more insight into the performances of the models by using composite metrics as opposed to simply the AUC, in cases of class imbalance.
-Likewise, performances were shown to continue to degrade as resolutions decreased.
-
-## MODELS IMPLEMENTED ON SMOTE RE-SAMPLED DATA WITH DISTANCE-TYPE PREDICTORS PERFORMED BEST AMOUNG ALL ENSEMBLE SYSTEMS
-
-Of the re-sampling techniques considered, it was found that SMOTE re-sampled datasets, implemented on distance-type predictors, yielded the highest model performances across each of the 3 composite metrics (Figure 9).
+We then assessed the performances of models implemented on distance type predictors alone.
+Results showed that models with distance-type predictors outperformed models with other predictor types (Figure 5C).
+This result was consistent across both resampling technique and resolution.
+Directly comparing model performances using distance type predictors, we found that SMOTE resampled datasets yielded the highest model performances across each of the composite metrics.
 These results were consistent across resolution and cell line.
@@
 
-Furthermore, we found that model performances tended to decline as data resolution decreased.
-Random forest models implemented on 10 kb, SMOTE resampled, data resolutions, with distance-type predictors were found to perform best according to MCC and balanced accuracy.
-There was a slight improvement in F1-Score for the 25 kb resolution on the GM12878 cell line.
+Furthermore, we found that when using distance-type predictors, model performances tended to decline as data resolution decreased.
+There was a slight improvement in F1-Score for the 25 kb resolution on the GM12878 cell line, followed by a steep decline at 50 kb.
+Both F1-Scores and MCCs showed a momentary increase in performance at the lowest resolution considered in the study.
 Performances from the K562 cell line degraded much faster as resolution decreased, while the worst performing models for the GM12878 cell line were at the 50 kb resolution, followed by a slight improvement in performance at the 100 kb resolution.

### 2019-04-07 Scripts/evaluating_correlations.Rmd
editted results scripts

@@
                     sep="")
-    percdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", 
-                    resolution,
-                    "_perc.rds",
-                    sep="")
-    distdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", 
-                    resolution, 
-                    "_dist.rds",
-                    sep="")
+    #percdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", 
+    #                resolution,
+    #                "_perc.rds",
+    #                sep="")
+    #distdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", 
+    #                resolution, 
+    #                "_dist.rds",
+    #                sep="")
   }else{
@@
                     sep="")
-    percdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_",
-                    resolution,
-                    "_perc.rds",
-                    sep="")
-    distdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_",
-                    resolution,
-                    "_dist.rds",
-                    sep="")
+    #percdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_",
+    #                resolution,
+    #                "_perc.rds",
+    #                sep="")
+    #distdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_",
+    #                resolution,
+    #                "_dist.rds",
+    #                sep="")
     }
@@
   countdata <- readRDS(countdir)
-  percdata <- readRDS(percdir)
-  distdata <- readRDS(distdir)
+  #percdata <- readRDS(percdir)
+  #distdata <- readRDS(distdir)
 
   #performing log2 transformation on distances
-  distdata <- apply(distdata,2,function(x){log(x + 1, base=2)})
+  #distdata <- apply(distdata,2,function(x){log(x + 1, base=2)})
 
@@
     countdata <- countdata[,-grep("Znf274", colnames(countdata))]
-    percdata <- percdata[,-grep("Znf274", colnames(percdata))]
-    distdata <- distdata[,-grep("Znf274", colnames(distdata))]
+    #percdata <- percdata[,-grep("Znf274", colnames(percdata))]
+    #distdata <- distdata[,-grep("Znf274", colnames(distdata))]
   }
@@
   corrcount <- cor(countdata, method = "spearman")
-  corrperc <- cor(percdata, method = "spearman")
-  corrdist <- cor(distdata, method = "pearson")
-
-  corrdata <- (corrcount + corrperc + corrdist)/3
+  #corrperc <- cor(percdata, method = "spearman")
+  #corrdist <- cor(distdata, method = "pearson")
+
+  #corrdata <- (corrcount + corrperc + corrdist)/3
+  corrdata <- corrcount
 
@@
          method="color",
-         type="lower", 
+         type="upper", 
          order="hclust", 
@@
 
-#### Specific correlations
+#### Count overlap correlations
 

### 2019-04-07 Scripts/evaluating_model_performances.Rmd
editted results scripts

--- 2019-03-28 Scripts/evaluating_model_performances.Rmd
@@
 ```
+
+##gm12878
+
+```{r}
+#OC
+##None
+rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_gm12878_25kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_gm12878_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_gm12878_50kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_gm12878_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_gm12878_100kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_gm12878_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_gm12878_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_gm12878_10kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_gm12878_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_gm12878_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_gm12878_25kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_gm12878_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_gm12878_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_gm12878_50kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_gm12878_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_gm12878_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_gm12878_100kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_gm12878_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_gm12878_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_gm12878_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_gm12878_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_gm12878_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_gm12878_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_gm12878_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_gm12878_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_gm12878_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_gm12878_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_gm12878_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_gm12878_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_gm12878_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_gm12878_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_gm12878_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_gm12878_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_gm12878_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_gm12878_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_gm12878_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_gm12878_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_gm12878_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_gm12878_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_gm12878_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_gm12878_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_gm12878_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+all_rfperfs_gm12878 <- data.frame(Resolution=rep(c(rep("10 kb", 12),
+                                                        rep("25 kb", 12),
+                                                        rep("50 kb", 12),
+                                                        rep("100 kb", 12)),4),
+                                       Predictor=rep(c("OC","OP","Distance"),64),
+                                       Metric=c(rep("AUC",48),
+                                                rep("AUPRC",48),
+                                                rep("F1-Score",48), 
+                                                rep("MCC",48)),
+                                       Resampling=rep(c(rep("None",3),
+                                                    rep("ROS",3),
+                                                    rep("RUS",3),
+                                                    rep("SMOTE",3)),16))
+all_rfperfs_gm12878$Resolution <- factor(all_rfperfs_gm12878$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
+all_rfperfs_gm12878$Predictor <- factor(all_rfperfs_gm12878$Predictor, levels=c("OC", "OP", "Distance"))
+all_rfperfs_gm12878$Metric <- factor(all_rfperfs_gm12878$Metric, levels=c("AUC", "AUPRC", "F1-Score", "MCC"))
+all_rfperfs_gm12878$Resampling <- factor(all_rfperfs_gm12878$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))
+
+all_rfperfs_gm12878$Performance <- c(round(rfperf_gm12878_10kb_none_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_none_op[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_none_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_gm12878_25kb_none_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_none_op[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_none_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_gm12878_50kb_none_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_none_op[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_none_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_gm12878_100kb_none_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_none_op[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_none_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_gm12878_10kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_none_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_gm12878_25kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_none_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_gm12878_50kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_none_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_gm12878_100kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_none_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_gm12878_10kb_none_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_none_op[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_none_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_gm12878_25kb_none_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_none_op[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_none_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_gm12878_50kb_none_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_none_op[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_none_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_gm12878_100kb_none_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_none_op[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_none_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_gm12878_10kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_none_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_SMOTE_dist[15,2],2), #mcc
+
+                                     round(rfperf_gm12878_25kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_none_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_SMOTE_dist[15,2],2), #mcc
+
+                                     round(rfperf_gm12878_50kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_none_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_SMOTE_dist[15,2],2), #mcc
+
+                                     round(rfperf_gm12878_100kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_none_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_SMOTE_dist[15,2],2) #mcc
+)
+
+p1 <- ggplot(all_rfperfs_gm12878,
+       aes(x=Resolution, y=Performance, fill=Predictor)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(Metric ~ Resampling) +
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Predictor Type")+
+  #guides(fill=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+```
+
+##k562
+
+```{r}
+#OC
+##None
+rfperf_K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_K562_10kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_K562_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_K562_25kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_K562_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_K562_50kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_K562_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_K562_100kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_K562_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_K562_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_K562_10kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_K562_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_K562_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_K562_25kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_K562_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_K562_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_K562_50kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_K562_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_K562_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_K562_100kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_K562_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_K562_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_K562_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_K562_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_K562_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_K562_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_K562_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_K562_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_K562_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_K562_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_K562_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_K562_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_K562_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_K562_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_K562_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_K562_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_K562_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_K562_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_K562_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_K562_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_K562_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_K562_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_K562_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_K562_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_K562_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+all_rfperfs_K562 <- data.frame(Resolution=rep(c(rep("10 kb", 12),
+                                                        rep("25 kb", 12),
+                                                        rep("50 kb", 12),
+                                                        rep("100 kb", 12)),4),
+                                       Predictor=rep(c("OC","OP","Distance"),64),
+                                       Metric=c(rep("AUC",48),
+                                                rep("AUPRC",48),
+                                                rep("F1-Score",48), 
+                                                rep("MCC",48)),
+                                       Resampling=rep(c(rep("None",3),
+                                                    rep("ROS",3),
+                                                    rep("RUS",3),
+                                                    rep("SMOTE",3)),16))
+all_rfperfs_K562$Resolution <- factor(all_rfperfs_K562$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
+all_rfperfs_K562$Predictor <- factor(all_rfperfs_K562$Predictor, levels=c("OC", "OP", "Distance"))
+all_rfperfs_K562$Metric <- factor(all_rfperfs_K562$Metric, levels=c("AUC", "AUPRC", "F1-Score", "MCC"))
+all_rfperfs_K562$Resampling <- factor(all_rfperfs_K562$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))
+
+all_rfperfs_K562$Performance <- c(round(rfperf_K562_10kb_none_oc[17,2],2), #auc
+                                          round(rfperf_K562_10kb_none_op[17,2],2), #auc
+                                          round(rfperf_K562_10kb_none_dist[17,2],2), #auc
+                                          round(rfperf_K562_10kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_K562_10kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_K562_10kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_K562_10kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_K562_10kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_K562_10kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_K562_10kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_K562_10kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_K562_10kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_K562_25kb_none_oc[17,2],2), #auc
+                                          round(rfperf_K562_25kb_none_op[17,2],2), #auc
+                                          round(rfperf_K562_25kb_none_dist[17,2],2), #auc
+                                          round(rfperf_K562_25kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_K562_25kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_K562_25kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_K562_25kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_K562_25kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_K562_25kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_K562_25kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_K562_25kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_K562_25kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_K562_50kb_none_oc[17,2],2), #auc
+                                          round(rfperf_K562_50kb_none_op[17,2],2), #auc
+                                          round(rfperf_K562_50kb_none_dist[17,2],2), #auc
+                                          round(rfperf_K562_50kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_K562_50kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_K562_50kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_K562_50kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_K562_50kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_K562_50kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_K562_50kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_K562_50kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_K562_50kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_K562_100kb_none_oc[17,2],2), #auc
+                                          round(rfperf_K562_100kb_none_op[17,2],2), #auc
+                                          round(rfperf_K562_100kb_none_dist[17,2],2), #auc
+                                          round(rfperf_K562_100kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_K562_100kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_K562_100kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_K562_100kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_K562_100kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_K562_100kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_K562_100kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_K562_100kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_K562_100kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_K562_10kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_none_op[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_K562_25kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_none_op[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_K562_50kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_none_op[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_K562_100kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_none_op[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_K562_10kb_none_oc[16,2],2), #f1
+                                          round(rfperf_K562_10kb_none_op[16,2],2), #f1
+                                          round(rfperf_K562_10kb_none_dist[16,2],2), #f1
+                                          round(rfperf_K562_10kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_K562_10kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_K562_10kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_K562_10kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_K562_10kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_K562_10kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_K562_10kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_K562_10kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_K562_10kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_K562_25kb_none_oc[16,2],2), #f1
+                                          round(rfperf_K562_25kb_none_op[16,2],2), #f1
+                                          round(rfperf_K562_25kb_none_dist[16,2],2), #f1
+                                          round(rfperf_K562_25kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_K562_25kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_K562_25kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_K562_25kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_K562_25kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_K562_25kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_K562_25kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_K562_25kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_K562_25kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_K562_50kb_none_oc[16,2],2), #f1
+                                          round(rfperf_K562_50kb_none_op[16,2],2), #f1
+                                          round(rfperf_K562_50kb_none_dist[16,2],2), #f1
+                                          round(rfperf_K562_50kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_K562_50kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_K562_50kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_K562_50kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_K562_50kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_K562_50kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_K562_50kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_K562_50kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_K562_50kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_K562_100kb_none_oc[16,2],2), #f1
+                                          round(rfperf_K562_100kb_none_op[16,2],2), #f1
+                                          round(rfperf_K562_100kb_none_dist[16,2],2), #f1
+                                          round(rfperf_K562_100kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_K562_100kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_K562_100kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_K562_100kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_K562_100kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_K562_100kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_K562_100kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_K562_100kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_K562_100kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_K562_10kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_none_op[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_SMOTE_dist[15,2],2), #mcc
+
+                                     round(rfperf_K562_25kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_none_op[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_SMOTE_dist[15,2],2), #mcc
+
+                                     round(rfperf_K562_50kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_none_op[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_SMOTE_dist[15,2],2), #mcc
+
+                                     round(rfperf_K562_100kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_none_op[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_SMOTE_dist[15,2],2) #mcc
+)
+
+p2 <- ggplot(all_rfperfs_K562,
+       aes(x=Resolution, y=Performance, fill=Predictor)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(Metric ~ Resampling) +
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Predictor Type")+
+  #guides(fill=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+```
+
+##Plots
+
+```{r}
+p1 <- p1 + labs(title = "GM12878") + theme(plot.title = element_text(size=20))
+p2 <- p2 + labs(title = "K562") + theme(plot.title = element_text(size=20))
+
+figure <- ggarrange(p1,p2,
+                ncol = 2, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "top",
+                labels = "AUTO",
+                font.label = list(size=20))
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Performance", color = "black", rot = 90, size=20)
+)
+
+```
+
+##Plots
+
+```{r}
+c <- ggplot(all_rfperfs_gm12878[which(all_rfperfs_gm12878$Predictor=="OC" & (all_rfperfs_gm12878$Metric=="F1-Score" | all_rfperfs_gm12878$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
+    geom_line(size=2)+
+    geom_point(size=5)+
+    facet_grid(~ Metric)+
+    theme_minimal() +
+    theme_bw()+
+    xlab("") + ylab("") + ylim(-.02,.5) +
+    ggtitle("Overlap Counts") +
+    scale_color_discrete(name="Re-Sampling Technique")+
+    theme(axis.text.x = element_text(size=15,
+                                     angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20))
+
+p <- ggplot(all_rfperfs_gm12878[which(all_rfperfs_gm12878$Predictor=="OP" & (all_rfperfs_gm12878$Metric=="F1-Score" | all_rfperfs_gm12878$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
+    geom_line(size=2)+
+    geom_point(size=5)+
+    facet_grid(~ Metric)+
+    theme_minimal() +
+    theme_bw()+
+    xlab("") + ylab("") + ylim(-.02,.5) +
+    ggtitle("Overlap Percents") +
+    scale_color_discrete(name="Re-Sampling Technique")+
+    theme(axis.text.x = element_text(size=15,
+                                     angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20))
+
+d <- ggplot(all_rfperfs_gm12878[which(all_rfperfs_gm12878$Predictor=="Distance" & (all_rfperfs_gm12878$Metric=="F1-Score" | all_rfperfs_gm12878$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
+    geom_line(size=2)+
+    geom_point(size=5)+
+    facet_grid(~ Metric)+
+    theme_minimal() +
+    theme_bw()+
+    xlab("") + ylab("") + ylim(-.02,.5) +
+    ggtitle("Distance") +
+    scale_color_discrete(name="Re-Sampling Technique")+
+    theme(axis.text.x = element_text(size=15,
+                                     angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20))
+
+figure <- ggarrange(c,p,d,
+                ncol = 3, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "top",
+                labels = "AUTO",
+                font.label = list(size=20))
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Performance", color = "black", rot = 90, size=20)
+)
+
+```

### 2019-04-07 Scripts/evaluating_models_with_dist_preds.Rmd
editted results scripts

--- 2019-03-08 Scripts/evaluating_smote_performances.Rmd
@@
 
-## SMOTE
-
-### GM12878
+##gm12878
 
 ```{r}
+#OC
+##None
+rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
 
-###10kb
-rfperf_gm12878_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+#OP
+##None
+rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
 
-###25kb
-rfperf_gm12878_25kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+#Distance
+##None
+rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
 
-###50kb
-rfperf_gm12878_50kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+#OC
+##None
+rfperf_gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
 
-###100kb
-rfperf_gm12878_100kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+#OP
+##None
+rfperf_gm12878_25kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_gm12878_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_gm12878_50kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_gm12878_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##None
+rfperf_gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_gm12878_100kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_gm12878_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_gm12878_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_gm12878_10kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_gm12878_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_gm12878_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_gm12878_25kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_gm12878_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_gm12878_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_gm12878_50kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_gm12878_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_gm12878_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_gm12878_100kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_gm12878_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_gm12878_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_gm12878_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_gm12878_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_gm12878_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_gm12878_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_gm12878_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_gm12878_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_gm12878_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_gm12878_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_gm12878_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_gm12878_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_gm12878_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_gm12878_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_gm12878_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_gm12878_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_gm12878_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_gm12878_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_gm12878_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_gm12878_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_gm12878_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_gm12878_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_gm12878_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_gm12878_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_gm12878_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+all_rfperfs_gm12878 <- data.frame(Resolution=rep(c(rep("10 kb", 12),
+                                                        rep("25 kb", 12),
+                                                        rep("50 kb", 12),
+                                                        rep("100 kb", 12)),4),
+                                       Predictor=rep(c("OC","OP","Distance"),64),
+                                       Metric=c(rep("AUC",48),
+                                                rep("AUPRC",48),
+                                                rep("F1-Score",48), 
+                                                rep("MCC",48)),
+                                       Resampling=rep(c(rep("None",3),
+                                                    rep("ROS",3),
+                                                    rep("RUS",3),
+                                                    rep("SMOTE",3)),16))
+all_rfperfs_gm12878$Resolution <- factor(all_rfperfs_gm12878$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
+all_rfperfs_gm12878$Predictor <- factor(all_rfperfs_gm12878$Predictor, levels=c("OC", "OP", "Distance"))
+all_rfperfs_gm12878$Metric <- factor(all_rfperfs_gm12878$Metric, levels=c("AUC", "AUPRC", "F1-Score", "MCC"))
+all_rfperfs_gm12878$Resampling <- factor(all_rfperfs_gm12878$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))
+
+all_rfperfs_gm12878$Performance <- c(round(rfperf_gm12878_10kb_none_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_none_op[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_none_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_gm12878_10kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_gm12878_25kb_none_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_none_op[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_none_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_gm12878_25kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_gm12878_50kb_none_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_none_op[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_none_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_gm12878_50kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_gm12878_100kb_none_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_none_op[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_none_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_gm12878_100kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_gm12878_10kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_none_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_10kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_gm12878_25kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_none_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_25kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_gm12878_50kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_none_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_50kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_gm12878_100kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_none_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_gm12878_100kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_gm12878_10kb_none_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_none_op[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_none_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_gm12878_10kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_gm12878_25kb_none_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_none_op[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_none_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_gm12878_25kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_gm12878_50kb_none_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_none_op[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_none_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_gm12878_50kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_gm12878_100kb_none_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_none_op[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_none_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_gm12878_100kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_gm12878_10kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_none_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_10kb_SMOTE_dist[15,2],2), #mcc
+
+                                     round(rfperf_gm12878_25kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_none_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_25kb_SMOTE_dist[15,2],2), #mcc
+
+                                     round(rfperf_gm12878_50kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_none_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_50kb_SMOTE_dist[15,2],2), #mcc
+
+                                     round(rfperf_gm12878_100kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_none_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_gm12878_100kb_SMOTE_dist[15,2],2) #mcc
+)
+
+p1 <- ggplot(all_rfperfs_gm12878[which(all_rfperfs_gm12878$Predictor=="Distance"),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
+    geom_line(size=2)+
+    geom_point(size=5)+
+    facet_grid(~ Metric)+
+    theme_minimal() +
+    theme_bw()+
+    xlab("") + ylab("") +
+  scale_color_discrete(name="Re-Sampling Technique")+
+	theme(axis.text.x = element_text(size=15,
+	                                 angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1
+	                                 ),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+	      plot.title = element_text(size=20))
 
@@
 
-### K562
+##k562
 
 ```{r}
+#OC
+##None
+rfperf_K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
 
-###10kb
-rfperf_k562_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+#OP
+##None
+rfperf_K562_10kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
 
-###25kb
-rfperf_k562_25kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+#Distance
+##None
+rfperf_K562_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
 
-###50kb
-rfperf_k562_50kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+#OC
+##None
+rfperf_K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
 
-###100kb
-rfperf_k562_100kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+#OP
+##None
+rfperf_K562_25kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
 
-```
+#Distance
+##None
+rfperf_K562_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
 
-### Combined F1 and MCC and balanced acc
+#OC
+##None
+rfperf_K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
 
-```{r}
-all_smote_perfs <- data.frame(Performance = c(rfperf_gm12878_10kb_smote_dist[16,2],
-                                              rfperf_gm12878_10kb_smote_dist[15,2],
-                                              (rfperf_gm12878_10kb_smote_dist[6,2] + rfperf_gm12878_10kb_smote_dist[7,2])/2,
-                                              rfperf_gm12878_25kb_smote_dist[16,2],
-                                              rfperf_gm12878_25kb_smote_dist[15,2],
-                                              (rfperf_gm12878_25kb_smote_dist[6,2] + rfperf_gm12878_25kb_smote_dist[7,2])/2,
-                                              rfperf_gm12878_50kb_smote_dist[16,2],
-                                              rfperf_gm12878_50kb_smote_dist[15,2],
-                                              (rfperf_gm12878_50kb_smote_dist[6,2] + rfperf_gm12878_50kb_smote_dist[7,2])/2,
-                                              rfperf_gm12878_100kb_smote_dist[16,2],
-                                              rfperf_gm12878_100kb_smote_dist[15,2],
-                                              (rfperf_gm12878_100kb_smote_dist[6,2] + rfperf_gm12878_100kb_smote_dist[7,2])/2,
-                                              rfperf_k562_10kb_smote_dist[16,2],
-                                              rfperf_k562_10kb_smote_dist[15,2],
-                                              (rfperf_k562_10kb_smote_dist[6,2] + rfperf_k562_10kb_smote_dist[7,2])/2,
-                                              rfperf_k562_25kb_smote_dist[16,2],
-                                              rfperf_k562_25kb_smote_dist[15,2],
-                                              (rfperf_k562_25kb_smote_dist[6,2] + rfperf_k562_25kb_smote_dist[7,2])/2,
-                                              rfperf_k562_50kb_smote_dist[16,2],
-                                              rfperf_k562_50kb_smote_dist[15,2],
-                                              (rfperf_k562_50kb_smote_dist[6,2] + rfperf_k562_50kb_smote_dist[7,2])/2,
-                                              rfperf_k562_100kb_smote_dist[16,2],
-                                              rfperf_k562_100kb_smote_dist[15,2],
-                                              (rfperf_k562_100kb_smote_dist[6,2] + rfperf_k562_100kb_smote_dist[7,2])/2),
-                              CL = c(rep("GM12878", 12),
-                                     rep("K562", 12)),
-                              Resolution = rep(c(rep("10 kb", 3),
-                                             rep("25 kb", 3),
-                                             rep("50 kb", 3),
-                                             rep("100 kb", 3)), 2),
-                              Metric = rep(c("F1-Score", "MCC", "Balanced Acc"), 8))
+#OP
+##None
+rfperf_K562_50kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
 
-all_smote_perfs$CL <- factor(all_smote_perfs$CL, levels=c("GM12878", "K562"))
-all_smote_perfs$Resolution <- factor(all_smote_perfs$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
-all_smote_perfs$Metric <- factor(all_smote_perfs$Metric, levels=c("F1-Score", "MCC", "Balanced Acc"))
+#Distance
+##None
+rfperf_K562_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
 
-ggplot(all_smote_perfs, aes(x=Resolution, y=Performance, group=CL, color=CL)) +
-  geom_line(aes(linetype=CL))+
-  geom_point(aes(shape=CL))+
-  facet_grid(~ Metric)+
+#OC
+##None
+rfperf_K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+
+#OP
+##None
+rfperf_K562_100kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##None
+rfperf_K562_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_K562_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_K562_10kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_K562_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_K562_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_K562_25kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_K562_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_K562_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_K562_50kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_K562_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##ROS
+rfperf_K562_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##ROS
+rfperf_K562_100kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##ROS
+rfperf_K562_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_K562_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_K562_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_K562_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_K562_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_K562_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_K562_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_K562_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_K562_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_K562_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##RUS
+rfperf_K562_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+
+#OP
+##RUS
+rfperf_K562_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##RUS
+rfperf_K562_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_K562_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_K562_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_K562_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_K562_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_K562_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_K562_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_K562_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_K562_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_K562_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+#OC
+##SMOTE
+rfperf_K562_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+
+#OP
+##SMOTE
+rfperf_K562_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+
+#Distance
+##SMOTE
+rfperf_K562_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+all_rfperfs_K562 <- data.frame(Resolution=rep(c(rep("10 kb", 12),
+                                                        rep("25 kb", 12),
+                                                        rep("50 kb", 12),
+                                                        rep("100 kb", 12)),4),
+                                       Predictor=rep(c("OC","OP","Distance"),64),
+                                       Metric=c(rep("AUC",48),
+                                                rep("AUPRC",48),
+                                                rep("F1-Score",48), 
+                                                rep("MCC",48)),
+                                       Resampling=rep(c(rep("None",3),
+                                                    rep("ROS",3),
+                                                    rep("RUS",3),
+                                                    rep("SMOTE",3)),16))
+all_rfperfs_K562$Resolution <- factor(all_rfperfs_K562$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
+all_rfperfs_K562$Predictor <- factor(all_rfperfs_K562$Predictor, levels=c("OC", "OP", "Distance"))
+all_rfperfs_K562$Metric <- factor(all_rfperfs_K562$Metric, levels=c("AUC", "AUPRC", "F1-Score", "MCC"))
+all_rfperfs_K562$Resampling <- factor(all_rfperfs_K562$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))
+
+all_rfperfs_K562$Performance <- c(round(rfperf_K562_10kb_none_oc[17,2],2), #auc
+                                          round(rfperf_K562_10kb_none_op[17,2],2), #auc
+                                          round(rfperf_K562_10kb_none_dist[17,2],2), #auc
+                                          round(rfperf_K562_10kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_K562_10kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_K562_10kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_K562_10kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_K562_10kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_K562_10kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_K562_10kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_K562_10kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_K562_10kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_K562_25kb_none_oc[17,2],2), #auc
+                                          round(rfperf_K562_25kb_none_op[17,2],2), #auc
+                                          round(rfperf_K562_25kb_none_dist[17,2],2), #auc
+                                          round(rfperf_K562_25kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_K562_25kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_K562_25kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_K562_25kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_K562_25kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_K562_25kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_K562_25kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_K562_25kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_K562_25kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_K562_50kb_none_oc[17,2],2), #auc
+                                          round(rfperf_K562_50kb_none_op[17,2],2), #auc
+                                          round(rfperf_K562_50kb_none_dist[17,2],2), #auc
+                                          round(rfperf_K562_50kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_K562_50kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_K562_50kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_K562_50kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_K562_50kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_K562_50kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_K562_50kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_K562_50kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_K562_50kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_K562_100kb_none_oc[17,2],2), #auc
+                                          round(rfperf_K562_100kb_none_op[17,2],2), #auc
+                                          round(rfperf_K562_100kb_none_dist[17,2],2), #auc
+                                          round(rfperf_K562_100kb_ROS_oc[17,2],2), #auc
+                                          round(rfperf_K562_100kb_ROS_op[17,2],2), #auc
+                                          round(rfperf_K562_100kb_ROS_dist[17,2],2), #auc
+                                          round(rfperf_K562_100kb_RUS_oc[17,2],2), #auc
+                                          round(rfperf_K562_100kb_RUS_op[17,2],2), #auc
+                                          round(rfperf_K562_100kb_RUS_dist[17,2],2), #auc
+                                          round(rfperf_K562_100kb_SMOTE_oc[17,2],2), #auc
+                                          round(rfperf_K562_100kb_SMOTE_op[17,2],2), #auc
+                                          round(rfperf_K562_100kb_SMOTE_dist[17,2],2), #auc
+
+                                     round(rfperf_K562_10kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_none_op[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_K562_10kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_K562_25kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_none_op[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_K562_25kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_K562_50kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_none_op[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_K562_50kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_K562_100kb_none_oc[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_none_op[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_none_dist[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_ROS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_ROS_op[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_ROS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_RUS_oc[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_RUS_op[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_RUS_dist[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_SMOTE_oc[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_SMOTE_op[19,2],2), #auprc
+                                          round(rfperf_K562_100kb_SMOTE_dist[19,2],2), #auprc
+
+                                     round(rfperf_K562_10kb_none_oc[16,2],2), #f1
+                                          round(rfperf_K562_10kb_none_op[16,2],2), #f1
+                                          round(rfperf_K562_10kb_none_dist[16,2],2), #f1
+                                          round(rfperf_K562_10kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_K562_10kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_K562_10kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_K562_10kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_K562_10kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_K562_10kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_K562_10kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_K562_10kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_K562_10kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_K562_25kb_none_oc[16,2],2), #f1
+                                          round(rfperf_K562_25kb_none_op[16,2],2), #f1
+                                          round(rfperf_K562_25kb_none_dist[16,2],2), #f1
+                                          round(rfperf_K562_25kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_K562_25kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_K562_25kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_K562_25kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_K562_25kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_K562_25kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_K562_25kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_K562_25kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_K562_25kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_K562_50kb_none_oc[16,2],2), #f1
+                                          round(rfperf_K562_50kb_none_op[16,2],2), #f1
+                                          round(rfperf_K562_50kb_none_dist[16,2],2), #f1
+                                          round(rfperf_K562_50kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_K562_50kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_K562_50kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_K562_50kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_K562_50kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_K562_50kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_K562_50kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_K562_50kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_K562_50kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_K562_100kb_none_oc[16,2],2), #f1
+                                          round(rfperf_K562_100kb_none_op[16,2],2), #f1
+                                          round(rfperf_K562_100kb_none_dist[16,2],2), #f1
+                                          round(rfperf_K562_100kb_ROS_oc[16,2],2), #f1
+                                          round(rfperf_K562_100kb_ROS_op[16,2],2), #f1
+                                          round(rfperf_K562_100kb_ROS_dist[16,2],2), #f1
+                                          round(rfperf_K562_100kb_RUS_oc[16,2],2), #f1
+                                          round(rfperf_K562_100kb_RUS_op[16,2],2), #f1
+                                          round(rfperf_K562_100kb_RUS_dist[16,2],2), #f1
+                                          round(rfperf_K562_100kb_SMOTE_oc[16,2],2), #f1
+                                          round(rfperf_K562_100kb_SMOTE_op[16,2],2), #f1
+                                          round(rfperf_K562_100kb_SMOTE_dist[16,2],2), #f1
+
+                                     round(rfperf_K562_10kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_none_op[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_K562_10kb_SMOTE_dist[15,2],2), #mcc
+
+                                     round(rfperf_K562_25kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_none_op[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_K562_25kb_SMOTE_dist[15,2],2), #mcc
+
+                                     round(rfperf_K562_50kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_none_op[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_K562_50kb_SMOTE_dist[15,2],2), #mcc
+
+                                     round(rfperf_K562_100kb_none_oc[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_none_op[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_none_dist[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_ROS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_ROS_op[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_ROS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_RUS_oc[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_RUS_op[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_RUS_dist[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_SMOTE_oc[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_SMOTE_op[15,2],2), #mcc
+                                          round(rfperf_K562_100kb_SMOTE_dist[15,2],2) #mcc
+)
+
+p2 <- ggplot(all_rfperfs_K562,
+       aes(x=Resolution, y=Performance, fill=Predictor)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(Metric ~ Resampling) +
+  xlab("") + ylab("") +
   theme_minimal() +
   theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
+  scale_fill_discrete(name="Predictor Type")+
   #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15
-	                                 #angle = 45, 
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
                                    #margin = ggplot2::margin(t = 35),
-                                   #hjust = 1
-	                                 ),
+                                   hjust = 1),
         axis.text.y = element_text(size = 15),
@@
 
-## None
-
-### GM12878
+##Plots
 
 ```{r}
+p1 <- p1 + labs(title = "GM12878") + theme(plot.title = element_text(size=20))
+p2 <- p2 + labs(title = "K562") + theme(plot.title = element_text(size=20))
 
-###10kb
-rfperf_gm12878_10kb_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-###25kb
-rfperf_gm12878_25kb_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-###50kb
-rfperf_gm12878_50kb_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-###100kb
-rfperf_gm12878_100kb_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+figure <- ggarrange(p1,p2,
+                ncol = 2, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "top",
+                labels = "AUTO",
+                font.label = list(size=20))
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Performance", color = "black", rot = 90, size=20)
+)
 
 ```
-
-### K562
-
-```{r}
-
-###10kb
-rfperf_k562_10kb_None_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-###25kb
-rfperf_k562_25kb_None_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-###50kb
-rfperf_k562_50kb_None_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-###100kb
-rfperf_k562_100kb_None_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-```
-
-### Combined F1 and MCC and balanced acc
-
-```{r}
-all_None_perfs <- data.frame(Performance = c(rfperf_gm12878_10kb_None_dist[16,2],
-                                              rfperf_gm12878_10kb_None_dist[15,2],
-                                              (rfperf_gm12878_10kb_None_dist[6,2] + rfperf_gm12878_10kb_None_dist[7,2])/2,
-                                              rfperf_gm12878_25kb_None_dist[16,2],
-                                              rfperf_gm12878_25kb_None_dist[15,2],
-                                              (rfperf_gm12878_25kb_None_dist[6,2] + rfperf_gm12878_25kb_None_dist[7,2])/2,
-                                              rfperf_gm12878_50kb_None_dist[16,2],
-                                              rfperf_gm12878_50kb_None_dist[15,2],
-                                              (rfperf_gm12878_50kb_None_dist[6,2] + rfperf_gm12878_50kb_None_dist[7,2])/2,
-                                              rfperf_gm12878_100kb_None_dist[16,2],
-                                              rfperf_gm12878_100kb_None_dist[15,2],
-                                              (rfperf_gm12878_100kb_None_dist[6,2] + rfperf_gm12878_100kb_None_dist[7,2])/2,
-                                              rfperf_k562_10kb_None_dist[16,2],
-                                              rfperf_k562_10kb_None_dist[15,2],
-                                              (rfperf_k562_10kb_None_dist[6,2] + rfperf_k562_10kb_None_dist[7,2])/2,
-                                              rfperf_k562_25kb_None_dist[16,2],
-                                              rfperf_k562_25kb_None_dist[15,2],
-                                              (rfperf_k562_25kb_None_dist[6,2] + rfperf_k562_25kb_None_dist[7,2])/2,
-                                              rfperf_k562_50kb_None_dist[16,2],
-                                              rfperf_k562_50kb_None_dist[15,2],
-                                              (rfperf_k562_50kb_None_dist[6,2] + rfperf_k562_50kb_None_dist[7,2])/2,
-                                              rfperf_k562_100kb_None_dist[16,2],
-                                              rfperf_k562_100kb_None_dist[15,2],
-                                              (rfperf_k562_100kb_None_dist[6,2] + rfperf_k562_100kb_None_dist[7,2])/2),
-                              CL = c(rep("GM12878", 12),
-                                     rep("K562", 12)),
-                              Resolution = rep(c(rep("10 kb", 3),
-                                             rep("25 kb", 3),
-                                             rep("50 kb", 3),
-                                             rep("100 kb", 3)), 2),
-                              Metric = rep(c("F1-Score", "MCC", "Balanced Acc"), 8))
-
-all_None_perfs$CL <- factor(all_None_perfs$CL, levels=c("GM12878", "K562"))
-all_None_perfs$Resolution <- factor(all_None_perfs$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
-all_None_perfs$Metric <- factor(all_None_perfs$Metric, levels=c("F1-Score", "MCC", "Balanced Acc"))
-
-ggplot(all_None_perfs, aes(x=Resolution, y=Performance, group=CL, color=CL)) +
-  geom_line(aes(linetype=CL))+
-  geom_point(aes(shape=CL))+
-  facet_grid(~ Metric)+
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15
-	                                 #angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   #hjust = 1
-	                                 ),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-```
-
-##ROS
-
-### GM12878
-
-```{r}
-
-###10kb
-rfperf_gm12878_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-###25kb
-rfperf_gm12878_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-###50kb
-rfperf_gm12878_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-###100kb
-rfperf_gm12878_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-```
-
-### K562
-
-```{r}
-
-###10kb
-rfperf_k562_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-###25kb
-rfperf_k562_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-###50kb
-rfperf_k562_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-###100kb
-rfperf_k562_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-```
-
-### Combined F1 and MCC and balanced acc
-
-```{r}
-all_ROS_perfs <- data.frame(Performance = c(rfperf_gm12878_10kb_ROS_dist[16,2],
-                                              rfperf_gm12878_10kb_ROS_dist[15,2],
-                                              (rfperf_gm12878_10kb_ROS_dist[6,2] + rfperf_gm12878_10kb_ROS_dist[7,2])/2,
-                                              rfperf_gm12878_25kb_ROS_dist[16,2],
-                                              rfperf_gm12878_25kb_ROS_dist[15,2],
-                                              (rfperf_gm12878_25kb_ROS_dist[6,2] + rfperf_gm12878_25kb_ROS_dist[7,2])/2,
-                                              rfperf_gm12878_50kb_ROS_dist[16,2],
-                                              rfperf_gm12878_50kb_ROS_dist[15,2],
-                                              (rfperf_gm12878_50kb_ROS_dist[6,2] + rfperf_gm12878_50kb_ROS_dist[7,2])/2,
-                                              rfperf_gm12878_100kb_ROS_dist[16,2],
-                                              rfperf_gm12878_100kb_ROS_dist[15,2],
-                                              (rfperf_gm12878_100kb_ROS_dist[6,2] + rfperf_gm12878_100kb_ROS_dist[7,2])/2,
-                                              rfperf_k562_10kb_ROS_dist[16,2],
-                                              rfperf_k562_10kb_ROS_dist[15,2],
-                                              (rfperf_k562_10kb_ROS_dist[6,2] + rfperf_k562_10kb_ROS_dist[7,2])/2,
-                                              rfperf_k562_25kb_ROS_dist[16,2],
-                                              rfperf_k562_25kb_ROS_dist[15,2],
-                                              (rfperf_k562_25kb_ROS_dist[6,2] + rfperf_k562_25kb_ROS_dist[7,2])/2,
-                                              rfperf_k562_50kb_ROS_dist[16,2],
-                                              rfperf_k562_50kb_ROS_dist[15,2],
-                                              (rfperf_k562_50kb_ROS_dist[6,2] + rfperf_k562_50kb_ROS_dist[7,2])/2,
-                                              rfperf_k562_100kb_ROS_dist[16,2],
-                                              rfperf_k562_100kb_ROS_dist[15,2],
-                                              (rfperf_k562_100kb_ROS_dist[6,2] + rfperf_k562_100kb_ROS_dist[7,2])/2),
-                              CL = c(rep("GM12878", 12),
-                                     rep("K562", 12)),
-                              Resolution = rep(c(rep("10 kb", 3),
-                                             rep("25 kb", 3),
-                                             rep("50 kb", 3),
-                                             rep("100 kb", 3)), 2),
-                              Metric = rep(c("F1-Score", "MCC", "Balanced Acc"), 8))
-
-all_ROS_perfs$CL <- factor(all_ROS_perfs$CL, levels=c("GM12878", "K562"))
-all_ROS_perfs$Resolution <- factor(all_ROS_perfs$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
-all_ROS_perfs$Metric <- factor(all_ROS_perfs$Metric, levels=c("F1-Score", "MCC", "Balanced Acc"))
-
-ggplot(all_ROS_perfs, aes(x=Resolution, y=Performance, group=CL, color=CL)) +
-  geom_line(aes(linetype=CL))+
-  geom_point(aes(shape=CL))+
-  facet_grid(~ Metric)+
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15
-	                                 #angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   #hjust = 1
-	                                 ),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-```
-
-##RUS
-
-### GM12878
-
-```{r}
-
-###10kb
-rfperf_gm12878_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-###25kb
-rfperf_gm12878_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-###50kb
-rfperf_gm12878_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-###100kb
-rfperf_gm12878_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-```
-
-### K562
-
-```{r}
-
-###10kb
-rfperf_k562_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-###25kb
-rfperf_k562_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-###50kb
-rfperf_k562_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-###100kb
-rfperf_k562_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-```
-
-### Combined F1 and MCC and balanced acc
-
-```{r}
-all_RUS_perfs <- data.frame(Performance = c(rfperf_gm12878_10kb_RUS_dist[16,2],
-                                              rfperf_gm12878_10kb_RUS_dist[15,2],
-                                              (rfperf_gm12878_10kb_RUS_dist[6,2] + rfperf_gm12878_10kb_RUS_dist[7,2])/2,
-                                              rfperf_gm12878_25kb_RUS_dist[16,2],
-                                              rfperf_gm12878_25kb_RUS_dist[15,2],
-                                              (rfperf_gm12878_25kb_RUS_dist[6,2] + rfperf_gm12878_25kb_RUS_dist[7,2])/2,
-                                              rfperf_gm12878_50kb_RUS_dist[16,2],
-                                              rfperf_gm12878_50kb_RUS_dist[15,2],
-                                              (rfperf_gm12878_50kb_RUS_dist[6,2] + rfperf_gm12878_50kb_RUS_dist[7,2])/2,
-                                              rfperf_gm12878_100kb_RUS_dist[16,2],
-                                              rfperf_gm12878_100kb_RUS_dist[15,2],
-                                              (rfperf_gm12878_100kb_RUS_dist[6,2] + rfperf_gm12878_100kb_RUS_dist[7,2])/2,
-                                              rfperf_k562_10kb_RUS_dist[16,2],
-                                              rfperf_k562_10kb_RUS_dist[15,2],
-                                              (rfperf_k562_10kb_RUS_dist[6,2] + rfperf_k562_10kb_RUS_dist[7,2])/2,
-                                              rfperf_k562_25kb_RUS_dist[16,2],
-                                              rfperf_k562_25kb_RUS_dist[15,2],
-                                              (rfperf_k562_25kb_RUS_dist[6,2] + rfperf_k562_25kb_RUS_dist[7,2])/2,
-                                              rfperf_k562_50kb_RUS_dist[16,2],
-                                              rfperf_k562_50kb_RUS_dist[15,2],
-                                              (rfperf_k562_50kb_RUS_dist[6,2] + rfperf_k562_50kb_RUS_dist[7,2])/2,
-                                              rfperf_k562_100kb_RUS_dist[16,2],
-                                              rfperf_k562_100kb_RUS_dist[15,2],
-                                              (rfperf_k562_100kb_RUS_dist[6,2] + rfperf_k562_100kb_RUS_dist[7,2])/2),
-                              CL = c(rep("GM12878", 12),
-                                     rep("K562", 12)),
-                              Resolution = rep(c(rep("10 kb", 3),
-                                             rep("25 kb", 3),
-                                             rep("50 kb", 3),
-                                             rep("100 kb", 3)), 2),
-                              Metric = rep(c("F1-Score", "MCC", "Balanced Acc"), 8))
-
-all_RUS_perfs$CL <- factor(all_RUS_perfs$CL, levels=c("GM12878", "K562"))
-all_RUS_perfs$Resolution <- factor(all_RUS_perfs$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
-all_RUS_perfs$Metric <- factor(all_RUS_perfs$Metric, levels=c("F1-Score", "MCC", "Balanced Acc"))
-
-ggplot(all_RUS_perfs, aes(x=Resolution, y=Performance, group=CL, color=CL)) +
-  geom_line(aes(linetype=CL))+
-  geom_point(aes(shape=CL))+
-  facet_grid(~ Metric)+
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Cell Line")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15
-	                                 #angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   #hjust = 1
-	                                 ),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-```
-
-```{r}
-ggarrange(p.none, p.ros, p.rus, 
-          ncol=1, nrow=3, 
-          common.legend = TRUE, 
-          legend="bottom",
-          labels="AUTO",
-          font.label = list(size=20))
-```

### 2019-04-07 Manuscript/manuscript.Rmd
manuscript edits

@@
 Multiple random forest classification algorithms were built on domain data extracted from Hi-C data for 2 cell lines $C = \{GM12878, K562\}$, at four different resolutions $R = \{\text{10 kb}, \text{25 kb}, \text{50 kb}, \text{100 kb\}}$.
-For each classifier, we compared three predictor types $P = \{\text{OC}, \text{OP}, \text{Distance}\}$ and 4 class balancing techniques $B = \{None, RUS, ROS, SMOTE\}$.
+For each classifier, we compared model performances using 3 separate predictor types $P = \{\text{OC}, \text{OP}, \text{Distance}\}$ and 4 class balancing techniques $B = \{None, RUS, ROS, SMOTE\}$.
 A system produced from the ensemble framework was defined as: $S = \{c, r, p, b\}$, where $c \in C$, $r \in R$, $p \in P$, and $b \in B$.
@@
 As expected, the total number of genomic bins decreased as resolution decreased (Figure 4A).
-That is, at lower resolutions, the linear genome was binned into larger units, thereby creating fewer bins.
-The imbalance ratios, however, remained relatively stable across resolutions (Figure 4B).
+Specifically, at lower resolutions, the linear genome was binned into larger units, thereby creating fewer bins.
+The imbalance ratios, however, remained relatively stable and consistent across resolutions and cell line (Figure 4B).
 We found that there was an average IR of 0.154 (SD=0.022) and 0.137 (SD=0.0181) across resolutions for the GM12878 and K562 cell lines respectively.
-Ideally, a balanced dataset will have an IR close to 0.50.
-Here, the low imbalance ratios indicated a wide disparity between majority and
+Here, the low imbalance ratios indicated a wide disparity between the number of genomic bins that overlap with a flanked TAD boundary and the much larger number that did not.
 
@@
 
-We first evaluated performances for models implemented using overlap counts predictor types, without re-sampling (on the GM12878 cell line), as these characteristics represented models with the least granularity and could act as a baseline.
+We first evaluated performances for models implemented using OC predictor types, without re-sampling (on the GM12878 cell line), as these characteristics represented models with the least granularity and could act as a baseline.
 In evaluating such composite metrics like F1-Score and MCC, we found that these models exhibited poor performances across resolutions (Figure 5A).
-Furthermore, at lower resolutions (50 kb and 100 kb specifically), the F1-Score and MCC could not be determined given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives, as can be seen by the missing red points.
-When including overlap percents perdictor types in the models, coupled with no resampling, we found that performances were worse than when using OC predictor types (Figure 5B).
+Furthermore, at lower resolutions (50 kb and 100 kb specifically), the F1-Score and MCC could not be determined given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives <!--, as can be seen by the missing red points-->.
+When including OP perdictor types in the models, coupled with no resampling, we found that performances were worse than when using OC predictor types (Figure 5B).
 As with OC predictor types, these models were also not able to yield F1-Scores and MCCs at the 50 kb and 100 kb resolution.
 Models built on distance-type predictors, however, exhibited slightly better performances than the other two types, yet still yielded missing or low F1-Scores and MCC at lower resolutions (Figure 5C).
-This indicated that the key driver leading to poor performances was not feature engineering, but instead the severity in the class imbalance.
+Similar results were obtained on the K562 cell line, in which F1-Scores and MCCs were either low or missing across resolutions, with marginal improvement when considering distance types (Supplementary Figure 10 A-C).
+This indicated that the key driver leading to poor performances was not due to feature engineering, but instead the severity in the class imbalance.
 
@@
 Comparisons of the effects of the various resampling techniques were then made.
-We found that there was a substantial increase in F1-Score and MCC for models built on resampled data using any of the 3 techniques (Figure 5).
+On the GM12878 cell line, we found that there was a substantial increase in F1-Score and MCC for models built on resampled data using any of the 3 techniques (Figure 5).
 After resampling, we were able to report performances at the lower resolutions which was not feasible for models built on fully imbalanced data.
 For all predictor types, implementation of either RUS or SMOTE resampling was found to yield consistently better results than no resampling and ROS.
+These results were confirmed when evaluating the K562 cell line (Supplementary Figure 10 A-C).
 
@@
 
-We then assessed the performances of models implemented on distance type predictors alone.
-Results showed that models with distance-type predictors outperformed models with other predictor types (Figure 5C).
+On the GM12878 cell line, results showed that models with distance-type predictors outperformed models with other predictor types (Figure 5C).
 This result was consistent across both resampling technique and resolution.
 Directly comparing model performances using distance type predictors, we found that SMOTE resampled datasets yielded the highest model performances across each of the composite metrics.
-These results were consistent across resolution and cell line.
-Although RUS performed only marginally worse than SMOTE, there was a steap drop off in performances for ROS and no re-sampling, across both resolution and cell line.
+Although RUS performed only marginally worse than SMOTE, there was a steap drop off in performances for ROS and no re-sampling, across resolution.
+The same combination of resampling technique and predictor type was also found to result in the best performing model for the K562 cell line (Supplementary Figure 10C).
 These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that incorporates both random under- and over-sampling, as SMOTE is known to do.

### 2019-04-08 Scripts/evaluating_model_performances.Rmd
editted results script

@@
 
-all_rfperfs_gm12878$Performance <- c(round(rfperf_gm12878_10kb_none_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_none_op[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_none_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_gm12878_25kb_none_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_none_op[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_none_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_gm12878_50kb_none_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_none_op[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_none_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_gm12878_100kb_none_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_none_op[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_none_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_gm12878_10kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_none_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_gm12878_25kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_none_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_gm12878_50kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_none_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_gm12878_100kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_none_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_gm12878_10kb_none_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_none_op[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_none_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_gm12878_25kb_none_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_none_op[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_none_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_gm12878_50kb_none_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_none_op[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_none_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_gm12878_100kb_none_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_none_op[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_none_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_gm12878_10kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_none_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_SMOTE_dist[15,2],2), #mcc
-
-                                     round(rfperf_gm12878_25kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_none_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_SMOTE_dist[15,2],2), #mcc
-
-                                     round(rfperf_gm12878_50kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_none_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_SMOTE_dist[15,2],2), #mcc
-
-                                     round(rfperf_gm12878_100kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_none_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_SMOTE_dist[15,2],2) #mcc
+all_rfperfs_gm12878$Performance <- c(rfperf_gm12878_10kb_none_oc[17,2], #auc
+                                          rfperf_gm12878_10kb_none_op[17,2], #auc
+                                          rfperf_gm12878_10kb_none_dist[17,2], #auc
+                                          rfperf_gm12878_10kb_ROS_oc[17,2], #auc
+                                          rfperf_gm12878_10kb_ROS_op[17,2], #auc
+                                          rfperf_gm12878_10kb_ROS_dist[17,2], #auc
+                                          rfperf_gm12878_10kb_RUS_oc[17,2], #auc
+                                          rfperf_gm12878_10kb_RUS_op[17,2], #auc
+                                          rfperf_gm12878_10kb_RUS_dist[17,2], #auc
+                                          rfperf_gm12878_10kb_SMOTE_oc[17,2], #auc
+                                          rfperf_gm12878_10kb_SMOTE_op[17,2], #auc
+                                          rfperf_gm12878_10kb_SMOTE_dist[17,2], #auc
+
+                                     rfperf_gm12878_25kb_none_oc[17,2], #auc
+                                          rfperf_gm12878_25kb_none_op[17,2], #auc
+                                          rfperf_gm12878_25kb_none_dist[17,2], #auc
+                                          rfperf_gm12878_25kb_ROS_oc[17,2], #auc
+                                          rfperf_gm12878_25kb_ROS_op[17,2], #auc
+                                          rfperf_gm12878_25kb_ROS_dist[17,2], #auc
+                                          rfperf_gm12878_25kb_RUS_oc[17,2], #auc
+                                          rfperf_gm12878_25kb_RUS_op[17,2], #auc
+                                          rfperf_gm12878_25kb_RUS_dist[17,2], #auc
+                                          rfperf_gm12878_25kb_SMOTE_oc[17,2], #auc
+                                          rfperf_gm12878_25kb_SMOTE_op[17,2], #auc
+                                          rfperf_gm12878_25kb_SMOTE_dist[17,2], #auc
+
+                                     rfperf_gm12878_50kb_none_oc[17,2], #auc
+                                          rfperf_gm12878_50kb_none_op[17,2], #auc
+                                          rfperf_gm12878_50kb_none_dist[17,2], #auc
+                                          rfperf_gm12878_50kb_ROS_oc[17,2], #auc
+                                          rfperf_gm12878_50kb_ROS_op[17,2], #auc
+                                          rfperf_gm12878_50kb_ROS_dist[17,2], #auc
+                                          rfperf_gm12878_50kb_RUS_oc[17,2], #auc
+                                          rfperf_gm12878_50kb_RUS_op[17,2], #auc
+                                          rfperf_gm12878_50kb_RUS_dist[17,2], #auc
+                                          rfperf_gm12878_50kb_SMOTE_oc[17,2], #auc
+                                          rfperf_gm12878_50kb_SMOTE_op[17,2], #auc
+                                          rfperf_gm12878_50kb_SMOTE_dist[17,2], #auc
+
+                                     rfperf_gm12878_100kb_none_oc[17,2], #auc
+                                          rfperf_gm12878_100kb_none_op[17,2], #auc
+                                          rfperf_gm12878_100kb_none_dist[17,2], #auc
+                                          rfperf_gm12878_100kb_ROS_oc[17,2], #auc
+                                          rfperf_gm12878_100kb_ROS_op[17,2], #auc
+                                          rfperf_gm12878_100kb_ROS_dist[17,2], #auc
+                                          rfperf_gm12878_100kb_RUS_oc[17,2], #auc
+                                          rfperf_gm12878_100kb_RUS_op[17,2], #auc
+                                          rfperf_gm12878_100kb_RUS_dist[17,2], #auc
+                                          rfperf_gm12878_100kb_SMOTE_oc[17,2], #auc
+                                          rfperf_gm12878_100kb_SMOTE_op[17,2], #auc
+                                          rfperf_gm12878_100kb_SMOTE_dist[17,2], #auc
+
+                                     rfperf_gm12878_10kb_none_oc[19,2], #auprc
+                                          rfperf_gm12878_10kb_none_op[19,2], #auprc
+                                          rfperf_gm12878_10kb_none_dist[19,2], #auprc
+                                          rfperf_gm12878_10kb_ROS_oc[19,2], #auprc
+                                          rfperf_gm12878_10kb_ROS_op[19,2], #auprc
+                                          rfperf_gm12878_10kb_ROS_dist[19,2], #auprc
+                                          rfperf_gm12878_10kb_RUS_oc[19,2], #auprc
+                                          rfperf_gm12878_10kb_RUS_op[19,2], #auprc
+                                          rfperf_gm12878_10kb_RUS_dist[19,2], #auprc
+                                          rfperf_gm12878_10kb_SMOTE_oc[19,2], #auprc
+                                          rfperf_gm12878_10kb_SMOTE_op[19,2], #auprc
+                                          rfperf_gm12878_10kb_SMOTE_dist[19,2], #auprc
+
+                                     rfperf_gm12878_25kb_none_oc[19,2], #auprc
+                                          rfperf_gm12878_25kb_none_op[19,2], #auprc
+                                          rfperf_gm12878_25kb_none_dist[19,2], #auprc
+                                          rfperf_gm12878_25kb_ROS_oc[19,2], #auprc
+                                          rfperf_gm12878_25kb_ROS_op[19,2], #auprc
+                                          rfperf_gm12878_25kb_ROS_dist[19,2], #auprc
+                                          rfperf_gm12878_25kb_RUS_oc[19,2], #auprc
+                                          rfperf_gm12878_25kb_RUS_op[19,2], #auprc
+                                          rfperf_gm12878_25kb_RUS_dist[19,2], #auprc
+                                          rfperf_gm12878_25kb_SMOTE_oc[19,2], #auprc
+                                          rfperf_gm12878_25kb_SMOTE_op[19,2], #auprc
+                                          rfperf_gm12878_25kb_SMOTE_dist[19,2], #auprc
+
+                                     rfperf_gm12878_50kb_none_oc[19,2], #auprc
+                                          rfperf_gm12878_50kb_none_op[19,2], #auprc
+                                          rfperf_gm12878_50kb_none_dist[19,2], #auprc
+                                          rfperf_gm12878_50kb_ROS_oc[19,2], #auprc
+                                          rfperf_gm12878_50kb_ROS_op[19,2], #auprc
+                                          rfperf_gm12878_50kb_ROS_dist[19,2], #auprc
+                                          rfperf_gm12878_50kb_RUS_oc[19,2], #auprc
+                                          rfperf_gm12878_50kb_RUS_op[19,2], #auprc
+                                          rfperf_gm12878_50kb_RUS_dist[19,2], #auprc
+                                          rfperf_gm12878_50kb_SMOTE_oc[19,2], #auprc
+                                          rfperf_gm12878_50kb_SMOTE_op[19,2], #auprc
+                                          rfperf_gm12878_50kb_SMOTE_dist[19,2], #auprc
+
+                                     rfperf_gm12878_100kb_none_oc[19,2], #auprc
+                                          rfperf_gm12878_100kb_none_op[19,2], #auprc
+                                          rfperf_gm12878_100kb_none_dist[19,2], #auprc
+                                          rfperf_gm12878_100kb_ROS_oc[19,2], #auprc
+                                          rfperf_gm12878_100kb_ROS_op[19,2], #auprc
+                                          rfperf_gm12878_100kb_ROS_dist[19,2], #auprc
+                                          rfperf_gm12878_100kb_RUS_oc[19,2], #auprc
+                                          rfperf_gm12878_100kb_RUS_op[19,2], #auprc
+                                          rfperf_gm12878_100kb_RUS_dist[19,2], #auprc
+                                          rfperf_gm12878_100kb_SMOTE_oc[19,2], #auprc
+                                          rfperf_gm12878_100kb_SMOTE_op[19,2], #auprc
+                                          rfperf_gm12878_100kb_SMOTE_dist[19,2], #auprc
+
+                                     rfperf_gm12878_10kb_none_oc[16,2], #f1
+                                          rfperf_gm12878_10kb_none_op[16,2], #f1
+                                          rfperf_gm12878_10kb_none_dist[16,2], #f1
+                                          rfperf_gm12878_10kb_ROS_oc[16,2], #f1
+                                          rfperf_gm12878_10kb_ROS_op[16,2], #f1
+                                          rfperf_gm12878_10kb_ROS_dist[16,2], #f1
+                                          rfperf_gm12878_10kb_RUS_oc[16,2], #f1
+                                          rfperf_gm12878_10kb_RUS_op[16,2], #f1
+                                          rfperf_gm12878_10kb_RUS_dist[16,2], #f1
+                                          rfperf_gm12878_10kb_SMOTE_oc[16,2], #f1
+                                          rfperf_gm12878_10kb_SMOTE_op[16,2], #f1
+                                          rfperf_gm12878_10kb_SMOTE_dist[16,2], #f1
+
+                                     rfperf_gm12878_25kb_none_oc[16,2], #f1
+                                          rfperf_gm12878_25kb_none_op[16,2], #f1
+                                          rfperf_gm12878_25kb_none_dist[16,2], #f1
+                                          rfperf_gm12878_25kb_ROS_oc[16,2], #f1
+                                          rfperf_gm12878_25kb_ROS_op[16,2], #f1
+                                          rfperf_gm12878_25kb_ROS_dist[16,2], #f1
+                                          rfperf_gm12878_25kb_RUS_oc[16,2], #f1
+                                          rfperf_gm12878_25kb_RUS_op[16,2], #f1
+                                          rfperf_gm12878_25kb_RUS_dist[16,2], #f1
+                                          rfperf_gm12878_25kb_SMOTE_oc[16,2], #f1
+                                          rfperf_gm12878_25kb_SMOTE_op[16,2], #f1
+                                          rfperf_gm12878_25kb_SMOTE_dist[16,2], #f1
+
+                                     rfperf_gm12878_50kb_none_oc[16,2], #f1
+                                          rfperf_gm12878_50kb_none_op[16,2], #f1
+                                          rfperf_gm12878_50kb_none_dist[16,2], #f1
+                                          rfperf_gm12878_50kb_ROS_oc[16,2], #f1
+                                          rfperf_gm12878_50kb_ROS_op[16,2], #f1
+                                          rfperf_gm12878_50kb_ROS_dist[16,2], #f1
+                                          rfperf_gm12878_50kb_RUS_oc[16,2], #f1
+                                          rfperf_gm12878_50kb_RUS_op[16,2], #f1
+                                          rfperf_gm12878_50kb_RUS_dist[16,2], #f1
+                                          rfperf_gm12878_50kb_SMOTE_oc[16,2], #f1
+                                          rfperf_gm12878_50kb_SMOTE_op[16,2], #f1
+                                          rfperf_gm12878_50kb_SMOTE_dist[16,2], #f1
+
+                                     rfperf_gm12878_100kb_none_oc[16,2], #f1
+                                          rfperf_gm12878_100kb_none_op[16,2], #f1
+                                          rfperf_gm12878_100kb_none_dist[16,2], #f1
+                                          rfperf_gm12878_100kb_ROS_oc[16,2], #f1
+                                          rfperf_gm12878_100kb_ROS_op[16,2], #f1
+                                          rfperf_gm12878_100kb_ROS_dist[16,2], #f1
+                                          rfperf_gm12878_100kb_RUS_oc[16,2], #f1
+                                          rfperf_gm12878_100kb_RUS_op[16,2], #f1
+                                          rfperf_gm12878_100kb_RUS_dist[16,2], #f1
+                                          rfperf_gm12878_100kb_SMOTE_oc[16,2], #f1
+                                          rfperf_gm12878_100kb_SMOTE_op[16,2], #f1
+                                          rfperf_gm12878_100kb_SMOTE_dist[16,2], #f1
+
+                                     rfperf_gm12878_10kb_none_oc[15,2], #mcc
+                                          rfperf_gm12878_10kb_none_op[15,2], #mcc
+                                          rfperf_gm12878_10kb_none_dist[15,2], #mcc
+                                          rfperf_gm12878_10kb_ROS_oc[15,2], #mcc
+                                          rfperf_gm12878_10kb_ROS_op[15,2], #mcc
+                                          rfperf_gm12878_10kb_ROS_dist[15,2], #mcc
+                                          rfperf_gm12878_10kb_RUS_oc[15,2], #mcc
+                                          rfperf_gm12878_10kb_RUS_op[15,2], #mcc
+                                          rfperf_gm12878_10kb_RUS_dist[15,2], #mcc
+                                          rfperf_gm12878_10kb_SMOTE_oc[15,2], #mcc
+                                          rfperf_gm12878_10kb_SMOTE_op[15,2], #mcc
+                                          rfperf_gm12878_10kb_SMOTE_dist[15,2], #mcc
+
+                                     rfperf_gm12878_25kb_none_oc[15,2], #mcc
+                                          rfperf_gm12878_25kb_none_op[15,2], #mcc
+                                          rfperf_gm12878_25kb_none_dist[15,2], #mcc
+                                          rfperf_gm12878_25kb_ROS_oc[15,2], #mcc
+                                          rfperf_gm12878_25kb_ROS_op[15,2], #mcc
+                                          rfperf_gm12878_25kb_ROS_dist[15,2], #mcc
+                                          rfperf_gm12878_25kb_RUS_oc[15,2], #mcc
+                                          rfperf_gm12878_25kb_RUS_op[15,2], #mcc
+                                          rfperf_gm12878_25kb_RUS_dist[15,2], #mcc
+                                          rfperf_gm12878_25kb_SMOTE_oc[15,2], #mcc
+                                          rfperf_gm12878_25kb_SMOTE_op[15,2], #mcc
+                                          rfperf_gm12878_25kb_SMOTE_dist[15,2], #mcc
+
+                                     rfperf_gm12878_50kb_none_oc[15,2], #mcc
+                                          rfperf_gm12878_50kb_none_op[15,2], #mcc
+                                          rfperf_gm12878_50kb_none_dist[15,2], #mcc
+                                          rfperf_gm12878_50kb_ROS_oc[15,2], #mcc
+                                          rfperf_gm12878_50kb_ROS_op[15,2], #mcc
+                                          rfperf_gm12878_50kb_ROS_dist[15,2], #mcc
+                                          rfperf_gm12878_50kb_RUS_oc[15,2], #mcc
+                                          rfperf_gm12878_50kb_RUS_op[15,2], #mcc
+                                          rfperf_gm12878_50kb_RUS_dist[15,2], #mcc
+                                          rfperf_gm12878_50kb_SMOTE_oc[15,2], #mcc
+                                          rfperf_gm12878_50kb_SMOTE_op[15,2], #mcc
+                                          rfperf_gm12878_50kb_SMOTE_dist[15,2], #mcc
+
+                                     rfperf_gm12878_100kb_none_oc[15,2], #mcc
+                                          rfperf_gm12878_100kb_none_op[15,2], #mcc
+                                          rfperf_gm12878_100kb_none_dist[15,2], #mcc
+                                          rfperf_gm12878_100kb_ROS_oc[15,2], #mcc
+                                          rfperf_gm12878_100kb_ROS_op[15,2], #mcc
+                                          rfperf_gm12878_100kb_ROS_dist[15,2], #mcc
+                                          rfperf_gm12878_100kb_RUS_oc[15,2], #mcc
+                                          rfperf_gm12878_100kb_RUS_op[15,2], #mcc
+                                          rfperf_gm12878_100kb_RUS_dist[15,2], #mcc
+                                          rfperf_gm12878_100kb_SMOTE_oc[15,2], #mcc
+                                          rfperf_gm12878_100kb_SMOTE_op[15,2], #mcc
+                                          rfperf_gm12878_100kb_SMOTE_dist[15,2] #mcc
 )
@@
 
-all_rfperfs_K562$Performance <- c(round(rfperf_K562_10kb_none_oc[17,2],2), #auc
-                                          round(rfperf_K562_10kb_none_op[17,2],2), #auc
-                                          round(rfperf_K562_10kb_none_dist[17,2],2), #auc
-                                          round(rfperf_K562_10kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_K562_10kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_K562_10kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_K562_10kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_K562_10kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_K562_10kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_K562_10kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_K562_10kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_K562_10kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_K562_25kb_none_oc[17,2],2), #auc
-                                          round(rfperf_K562_25kb_none_op[17,2],2), #auc
-                                          round(rfperf_K562_25kb_none_dist[17,2],2), #auc
-                                          round(rfperf_K562_25kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_K562_25kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_K562_25kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_K562_25kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_K562_25kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_K562_25kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_K562_25kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_K562_25kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_K562_25kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_K562_50kb_none_oc[17,2],2), #auc
-                                          round(rfperf_K562_50kb_none_op[17,2],2), #auc
-                                          round(rfperf_K562_50kb_none_dist[17,2],2), #auc
-                                          round(rfperf_K562_50kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_K562_50kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_K562_50kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_K562_50kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_K562_50kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_K562_50kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_K562_50kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_K562_50kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_K562_50kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_K562_100kb_none_oc[17,2],2), #auc
-                                          round(rfperf_K562_100kb_none_op[17,2],2), #auc
-                                          round(rfperf_K562_100kb_none_dist[17,2],2), #auc
-                                          round(rfperf_K562_100kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_K562_100kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_K562_100kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_K562_100kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_K562_100kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_K562_100kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_K562_100kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_K562_100kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_K562_100kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_K562_10kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_none_op[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_K562_25kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_none_op[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_K562_50kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_none_op[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_K562_100kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_none_op[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_K562_10kb_none_oc[16,2],2), #f1
-                                          round(rfperf_K562_10kb_none_op[16,2],2), #f1
-                                          round(rfperf_K562_10kb_none_dist[16,2],2), #f1
-                                          round(rfperf_K562_10kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_K562_10kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_K562_10kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_K562_10kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_K562_10kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_K562_10kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_K562_10kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_K562_10kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_K562_10kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_K562_25kb_none_oc[16,2],2), #f1
-                                          round(rfperf_K562_25kb_none_op[16,2],2), #f1
-                                          round(rfperf_K562_25kb_none_dist[16,2],2), #f1
-                                          round(rfperf_K562_25kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_K562_25kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_K562_25kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_K562_25kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_K562_25kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_K562_25kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_K562_25kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_K562_25kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_K562_25kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_K562_50kb_none_oc[16,2],2), #f1
-                                          round(rfperf_K562_50kb_none_op[16,2],2), #f1
-                                          round(rfperf_K562_50kb_none_dist[16,2],2), #f1
-                                          round(rfperf_K562_50kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_K562_50kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_K562_50kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_K562_50kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_K562_50kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_K562_50kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_K562_50kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_K562_50kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_K562_50kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_K562_100kb_none_oc[16,2],2), #f1
-                                          round(rfperf_K562_100kb_none_op[16,2],2), #f1
-                                          round(rfperf_K562_100kb_none_dist[16,2],2), #f1
-                                          round(rfperf_K562_100kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_K562_100kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_K562_100kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_K562_100kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_K562_100kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_K562_100kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_K562_100kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_K562_100kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_K562_100kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_K562_10kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_none_op[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_SMOTE_dist[15,2],2), #mcc
-
-                                     round(rfperf_K562_25kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_none_op[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_SMOTE_dist[15,2],2), #mcc
-
-                                     round(rfperf_K562_50kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_none_op[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_SMOTE_dist[15,2],2), #mcc
-
-                                     round(rfperf_K562_100kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_none_op[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_SMOTE_dist[15,2],2) #mcc
+all_rfperfs_K562$Performance <- c(rfperf_K562_10kb_none_oc[17,2], #auc
+                                          rfperf_K562_10kb_none_op[17,2], #auc
+                                          rfperf_K562_10kb_none_dist[17,2], #auc
+                                          rfperf_K562_10kb_ROS_oc[17,2], #auc
+                                          rfperf_K562_10kb_ROS_op[17,2], #auc
+                                          rfperf_K562_10kb_ROS_dist[17,2], #auc
+                                          rfperf_K562_10kb_RUS_oc[17,2], #auc
+                                          rfperf_K562_10kb_RUS_op[17,2], #auc
+                                          rfperf_K562_10kb_RUS_dist[17,2], #auc
+                                          rfperf_K562_10kb_SMOTE_oc[17,2], #auc
+                                          rfperf_K562_10kb_SMOTE_op[17,2], #auc
+                                          rfperf_K562_10kb_SMOTE_dist[17,2], #auc
+
+                                     rfperf_K562_25kb_none_oc[17,2], #auc
+                                          rfperf_K562_25kb_none_op[17,2], #auc
+                                          rfperf_K562_25kb_none_dist[17,2], #auc
+                                          rfperf_K562_25kb_ROS_oc[17,2], #auc
+                                          rfperf_K562_25kb_ROS_op[17,2], #auc
+                                          rfperf_K562_25kb_ROS_dist[17,2], #auc
+                                          rfperf_K562_25kb_RUS_oc[17,2], #auc
+                                          rfperf_K562_25kb_RUS_op[17,2], #auc
+                                          rfperf_K562_25kb_RUS_dist[17,2], #auc
+                                          rfperf_K562_25kb_SMOTE_oc[17,2], #auc
+                                          rfperf_K562_25kb_SMOTE_op[17,2], #auc
+                                          rfperf_K562_25kb_SMOTE_dist[17,2], #auc
+
+                                     rfperf_K562_50kb_none_oc[17,2], #auc
+                                          rfperf_K562_50kb_none_op[17,2], #auc
+                                          rfperf_K562_50kb_none_dist[17,2], #auc
+                                          rfperf_K562_50kb_ROS_oc[17,2], #auc
+                                          rfperf_K562_50kb_ROS_op[17,2], #auc
+                                          rfperf_K562_50kb_ROS_dist[17,2], #auc
+                                          rfperf_K562_50kb_RUS_oc[17,2], #auc
+                                          rfperf_K562_50kb_RUS_op[17,2], #auc
+                                          rfperf_K562_50kb_RUS_dist[17,2], #auc
+                                          rfperf_K562_50kb_SMOTE_oc[17,2], #auc
+                                          rfperf_K562_50kb_SMOTE_op[17,2], #auc
+                                          rfperf_K562_50kb_SMOTE_dist[17,2], #auc
+
+                                     rfperf_K562_100kb_none_oc[17,2], #auc
+                                          rfperf_K562_100kb_none_op[17,2], #auc
+                                          rfperf_K562_100kb_none_dist[17,2], #auc
+                                          rfperf_K562_100kb_ROS_oc[17,2], #auc
+                                          rfperf_K562_100kb_ROS_op[17,2], #auc
+                                          rfperf_K562_100kb_ROS_dist[17,2], #auc
+                                          rfperf_K562_100kb_RUS_oc[17,2], #auc
+                                          rfperf_K562_100kb_RUS_op[17,2], #auc
+                                          rfperf_K562_100kb_RUS_dist[17,2], #auc
+                                          rfperf_K562_100kb_SMOTE_oc[17,2], #auc
+                                          rfperf_K562_100kb_SMOTE_op[17,2], #auc
+                                          rfperf_K562_100kb_SMOTE_dist[17,2], #auc
+
+                                     rfperf_K562_10kb_none_oc[19,2], #auprc
+                                          rfperf_K562_10kb_none_op[19,2], #auprc
+                                          rfperf_K562_10kb_none_dist[19,2], #auprc
+                                          rfperf_K562_10kb_ROS_oc[19,2], #auprc
+                                          rfperf_K562_10kb_ROS_op[19,2], #auprc
+                                          rfperf_K562_10kb_ROS_dist[19,2], #auprc
+                                          rfperf_K562_10kb_RUS_oc[19,2], #auprc
+                                          rfperf_K562_10kb_RUS_op[19,2], #auprc
+                                          rfperf_K562_10kb_RUS_dist[19,2], #auprc
+                                          rfperf_K562_10kb_SMOTE_oc[19,2], #auprc
+                                          rfperf_K562_10kb_SMOTE_op[19,2], #auprc
+                                          rfperf_K562_10kb_SMOTE_dist[19,2], #auprc
+
+                                     rfperf_K562_25kb_none_oc[19,2], #auprc
+                                          rfperf_K562_25kb_none_op[19,2], #auprc
+                                          rfperf_K562_25kb_none_dist[19,2], #auprc
+                                          rfperf_K562_25kb_ROS_oc[19,2], #auprc
+                                          rfperf_K562_25kb_ROS_op[19,2], #auprc
+                                          rfperf_K562_25kb_ROS_dist[19,2], #auprc
+                                          rfperf_K562_25kb_RUS_oc[19,2], #auprc
+                                          rfperf_K562_25kb_RUS_op[19,2], #auprc
+                                          rfperf_K562_25kb_RUS_dist[19,2], #auprc
+                                          rfperf_K562_25kb_SMOTE_oc[19,2], #auprc
+                                          rfperf_K562_25kb_SMOTE_op[19,2], #auprc
+                                          rfperf_K562_25kb_SMOTE_dist[19,2], #auprc
+
+                                     rfperf_K562_50kb_none_oc[19,2], #auprc
+                                          rfperf_K562_50kb_none_op[19,2], #auprc
+                                          rfperf_K562_50kb_none_dist[19,2], #auprc
+                                          rfperf_K562_50kb_ROS_oc[19,2], #auprc
+                                          rfperf_K562_50kb_ROS_op[19,2], #auprc
+                                          rfperf_K562_50kb_ROS_dist[19,2], #auprc
+                                          rfperf_K562_50kb_RUS_oc[19,2], #auprc
+                                          rfperf_K562_50kb_RUS_op[19,2], #auprc
+                                          rfperf_K562_50kb_RUS_dist[19,2], #auprc
+                                          rfperf_K562_50kb_SMOTE_oc[19,2], #auprc
+                                          rfperf_K562_50kb_SMOTE_op[19,2], #auprc
+                                          rfperf_K562_50kb_SMOTE_dist[19,2], #auprc
+
+                                     rfperf_K562_100kb_none_oc[19,2], #auprc
+                                          rfperf_K562_100kb_none_op[19,2], #auprc
+                                          rfperf_K562_100kb_none_dist[19,2], #auprc
+                                          rfperf_K562_100kb_ROS_oc[19,2], #auprc
+                                          rfperf_K562_100kb_ROS_op[19,2], #auprc
+                                          rfperf_K562_100kb_ROS_dist[19,2], #auprc
+                                          rfperf_K562_100kb_RUS_oc[19,2], #auprc
+                                          rfperf_K562_100kb_RUS_op[19,2], #auprc
+                                          rfperf_K562_100kb_RUS_dist[19,2], #auprc
+                                          rfperf_K562_100kb_SMOTE_oc[19,2], #auprc
+                                          rfperf_K562_100kb_SMOTE_op[19,2], #auprc
+                                          rfperf_K562_100kb_SMOTE_dist[19,2], #auprc
+
+                                     rfperf_K562_10kb_none_oc[16,2], #f1
+                                          rfperf_K562_10kb_none_op[16,2], #f1
+                                          rfperf_K562_10kb_none_dist[16,2], #f1
+                                          rfperf_K562_10kb_ROS_oc[16,2], #f1
+                                          rfperf_K562_10kb_ROS_op[16,2], #f1
+                                          rfperf_K562_10kb_ROS_dist[16,2], #f1
+                                          rfperf_K562_10kb_RUS_oc[16,2], #f1
+                                          rfperf_K562_10kb_RUS_op[16,2], #f1
+                                          rfperf_K562_10kb_RUS_dist[16,2], #f1
+                                          rfperf_K562_10kb_SMOTE_oc[16,2], #f1
+                                          rfperf_K562_10kb_SMOTE_op[16,2], #f1
+                                          rfperf_K562_10kb_SMOTE_dist[16,2], #f1
+
+                                     rfperf_K562_25kb_none_oc[16,2], #f1
+                                          rfperf_K562_25kb_none_op[16,2], #f1
+                                          rfperf_K562_25kb_none_dist[16,2], #f1
+                                          rfperf_K562_25kb_ROS_oc[16,2], #f1
+                                          rfperf_K562_25kb_ROS_op[16,2], #f1
+                                          rfperf_K562_25kb_ROS_dist[16,2], #f1
+                                          rfperf_K562_25kb_RUS_oc[16,2], #f1
+                                          rfperf_K562_25kb_RUS_op[16,2], #f1
+                                          rfperf_K562_25kb_RUS_dist[16,2], #f1
+                                          rfperf_K562_25kb_SMOTE_oc[16,2], #f1
+                                          rfperf_K562_25kb_SMOTE_op[16,2], #f1
+                                          rfperf_K562_25kb_SMOTE_dist[16,2], #f1
+
+                                     rfperf_K562_50kb_none_oc[16,2], #f1
+                                          rfperf_K562_50kb_none_op[16,2], #f1
+                                          rfperf_K562_50kb_none_dist[16,2], #f1
+                                          rfperf_K562_50kb_ROS_oc[16,2], #f1
+                                          rfperf_K562_50kb_ROS_op[16,2], #f1
+                                          rfperf_K562_50kb_ROS_dist[16,2], #f1
+                                          rfperf_K562_50kb_RUS_oc[16,2], #f1
+                                          rfperf_K562_50kb_RUS_op[16,2], #f1
+                                          rfperf_K562_50kb_RUS_dist[16,2], #f1
+                                          rfperf_K562_50kb_SMOTE_oc[16,2], #f1
+                                          rfperf_K562_50kb_SMOTE_op[16,2], #f1
+                                          rfperf_K562_50kb_SMOTE_dist[16,2], #f1
+
+                                     rfperf_K562_100kb_none_oc[16,2], #f1
+                                          rfperf_K562_100kb_none_op[16,2], #f1
+                                          rfperf_K562_100kb_none_dist[16,2], #f1
+                                          rfperf_K562_100kb_ROS_oc[16,2], #f1
+                                          rfperf_K562_100kb_ROS_op[16,2], #f1
+                                          rfperf_K562_100kb_ROS_dist[16,2], #f1
+                                          rfperf_K562_100kb_RUS_oc[16,2], #f1
+                                          rfperf_K562_100kb_RUS_op[16,2], #f1
+                                          rfperf_K562_100kb_RUS_dist[16,2], #f1
+                                          rfperf_K562_100kb_SMOTE_oc[16,2], #f1
+                                          rfperf_K562_100kb_SMOTE_op[16,2], #f1
+                                          rfperf_K562_100kb_SMOTE_dist[16,2], #f1
+
+                                     rfperf_K562_10kb_none_oc[15,2], #mcc
+                                          rfperf_K562_10kb_none_op[15,2], #mcc
+                                          rfperf_K562_10kb_none_dist[15,2], #mcc
+                                          rfperf_K562_10kb_ROS_oc[15,2], #mcc
+                                          rfperf_K562_10kb_ROS_op[15,2], #mcc
+                                          rfperf_K562_10kb_ROS_dist[15,2], #mcc
+                                          rfperf_K562_10kb_RUS_oc[15,2], #mcc
+                                          rfperf_K562_10kb_RUS_op[15,2], #mcc
+                                          rfperf_K562_10kb_RUS_dist[15,2], #mcc
+                                          rfperf_K562_10kb_SMOTE_oc[15,2], #mcc
+                                          rfperf_K562_10kb_SMOTE_op[15,2], #mcc
+                                          rfperf_K562_10kb_SMOTE_dist[15,2], #mcc
+
+                                     rfperf_K562_25kb_none_oc[15,2], #mcc
+                                          rfperf_K562_25kb_none_op[15,2], #mcc
+                                          rfperf_K562_25kb_none_dist[15,2], #mcc
+                                          rfperf_K562_25kb_ROS_oc[15,2], #mcc
+                                          rfperf_K562_25kb_ROS_op[15,2], #mcc
+                                          rfperf_K562_25kb_ROS_dist[15,2], #mcc
+                                          rfperf_K562_25kb_RUS_oc[15,2], #mcc
+                                          rfperf_K562_25kb_RUS_op[15,2], #mcc
+                                          rfperf_K562_25kb_RUS_dist[15,2], #mcc
+                                          rfperf_K562_25kb_SMOTE_oc[15,2], #mcc
+                                          rfperf_K562_25kb_SMOTE_op[15,2], #mcc
+                                          rfperf_K562_25kb_SMOTE_dist[15,2], #mcc
+
+                                     rfperf_K562_50kb_none_oc[15,2], #mcc
+                                          rfperf_K562_50kb_none_op[15,2], #mcc
+                                          rfperf_K562_50kb_none_dist[15,2], #mcc
+                                          rfperf_K562_50kb_ROS_oc[15,2], #mcc
+                                          rfperf_K562_50kb_ROS_op[15,2], #mcc
+                                          rfperf_K562_50kb_ROS_dist[15,2], #mcc
+                                          rfperf_K562_50kb_RUS_oc[15,2], #mcc
+                                          rfperf_K562_50kb_RUS_op[15,2], #mcc
+                                          rfperf_K562_50kb_RUS_dist[15,2], #mcc
+                                          rfperf_K562_50kb_SMOTE_oc[15,2], #mcc
+                                          rfperf_K562_50kb_SMOTE_op[15,2], #mcc
+                                          rfperf_K562_50kb_SMOTE_dist[15,2], #mcc
+
+                                     rfperf_K562_100kb_none_oc[15,2], #mcc
+                                          rfperf_K562_100kb_none_op[15,2], #mcc
+                                          rfperf_K562_100kb_none_dist[15,2], #mcc
+                                          rfperf_K562_100kb_ROS_oc[15,2], #mcc
+                                          rfperf_K562_100kb_ROS_op[15,2], #mcc
+                                          rfperf_K562_100kb_ROS_dist[15,2], #mcc
+                                          rfperf_K562_100kb_RUS_oc[15,2], #mcc
+                                          rfperf_K562_100kb_RUS_op[15,2], #mcc
+                                          rfperf_K562_100kb_RUS_dist[15,2], #mcc
+                                          rfperf_K562_100kb_SMOTE_oc[15,2], #mcc
+                                          rfperf_K562_100kb_SMOTE_op[15,2], #mcc
+                                          rfperf_K562_100kb_SMOTE_dist[15,2] #mcc
 )
@@
 ```
+
+##Plots
+
+```{r}
+all_rfperfs <- rbind.data.frame(all_rfperfs_gm12878, all_rfperfs_K562)
+all_rfperfs$CL <- c(rep("GM12878", dim(all_rfperfs_gm12878)[1]), rep("K562", dim(all_rfperfs_K562)[1]))
+
+c <- ggplot(all_rfperfs[which(all_rfperfs$Predictor=="OC" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=CL, group=CL, linetype=CL)) +
+     geom_line(size=1)+
+     geom_point(size=2)+
+     facet_grid(Resampling ~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.05,.5) +
+     ggtitle("Overlap Counts") +
+     scale_color_discrete(name="Cell Line")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=10,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 10),
+     axis.title.x = element_text(size = 15),
+     axis.title.y = element_text(size = 15),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=15),
+     plot.title = element_text(size=15))
+
+p <- ggplot(all_rfperfs[which(all_rfperfs$Predictor=="OP" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=CL, group=CL, linetype=CL)) +
+     geom_line(size=1)+
+     geom_point(size=2)+
+     facet_grid(Resampling ~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.05,.5) +
+     ggtitle("Overlap Percents") +
+     scale_color_discrete(name="Cell Line")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=10,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 10),
+     axis.title.x = element_text(size = 15),
+     axis.title.y = element_text(size = 15),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=15),
+     plot.title = element_text(size=15))
+
+d <- ggplot(all_rfperfs[which(all_rfperfs$Predictor=="Distance" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=CL, group=CL, linetype=CL)) +
+     geom_line(size=1)+
+     geom_point(size=2)+
+     facet_grid(Resampling ~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.05,.5) +
+     ggtitle("Distance") +
+     scale_color_discrete(name="Cell Line")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=10,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 10),
+     axis.title.x = element_text(size = 15),
+     axis.title.y = element_text(size = 15),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=15),
+     plot.title = element_text(size=15))
+
+figure <- ggarrange(c,p,d,
+                ncol = 3, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "top")
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Performance", color = "black", rot = 90, size=20)
+)
+
+```

### 2019-04-08 Scripts/evaluating_variable_importances.Rmd
edits to results scripts
editting script for variable importances
editted results script

@@
 ```
+
+## Variable Importance Heatmaps for models with distance type predictors (Ranks)
+
+### SMOTE
+
+```{r}
+#GM12878
+
+rfimpvars_gm12878_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+rfimpvars_gm12878_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+rfimpvars_gm12878_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+rfimpvars_gm12878_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+
+rfimpvars_gm12878_10kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_10kb_SMOTE$Feature)
+rfimpvars_gm12878_25kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_25kb_SMOTE$Feature)
+rfimpvars_gm12878_50kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_50kb_SMOTE$Feature)
+rfimpvars_gm12878_100kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_100kb_SMOTE$Feature)
+
+unionannots <- union(rfimpvars_gm12878_10kb_SMOTE$Feature,
+                      union(rfimpvars_gm12878_25kb_SMOTE$Feature,
+                            union(rfimpvars_gm12878_50kb_SMOTE$Feature,rfimpvars_gm12878_100kb_SMOTE$Feature)))
+unionannots <- sort(unionannots)
+
+vim.gm12878.smote <- data.frame(Feature=unionannots)
+
+vim.gm12878.smote <- left_join(left_join(left_join(left_join(vim.gm12878.smote,rfimpvars_gm12878_10kb_SMOTE, by="Feature"),
+								rfimpvars_gm12878_25kb_SMOTE, by="Feature"),
+								rfimpvars_gm12878_50kb_SMOTE, by="Feature"),
+								rfimpvars_gm12878_100kb_SMOTE, by="Feature")
+names(vim.gm12878.smote) <- c("Feature","Importance.10kb","Importance.25kb","Importance.50kb","Importance.100kb")
+
+vim.gm12878.smote.ranks <- data.frame(Feature=vim.gm12878.smote$Feature,
+									  Rank.10kb=rank(-vim.gm12878.smote$Importance.10kb, na.last = TRUE),
+									  Rank.25kb=rank(-vim.gm12878.smote$Importance.25kb, na.last = TRUE),
+									  Rank.50kb=rank(-vim.gm12878.smote$Importance.50kb, na.last = TRUE),
+									  Rank.100kb=rank(-vim.gm12878.smote$Importance.100kb, na.last = TRUE))
+
+rankdata <- cbind(vim.gm12878.smote.ranks$Rank.10kb,
+                  vim.gm12878.smote.ranks$Rank.25kb,
+				  vim.gm12878.smote.ranks$Rank.50kb,
+				  vim.gm12878.smote.ranks$Rank.100kb)
+rownames(rankdata) <- vim.gm12878.smote.ranks$Feature
+colnames(rankdata) <- c("10 kb", "25 kb", "50 kb", "100 kb")
+
+#my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100)) 
+my_palette <- colorRampPalette(c("red", "white"))(nrow(rankdata))
+heatmap.2(t(rankdata),
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 2,
+          dendrogram="both",     # only draw a row dendrogram,
+          Rowv = TRUE,
+          Colv = TRUE,
+          cexRow=1.5,
+          cexCol=0.5,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          rowsep=1:4,
+          colsep=0:nrow(rankdata))
+
+#K562
+
+rfimpvars_K562_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+rfimpvars_K562_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+rfimpvars_K562_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+rfimpvars_K562_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+
+rfimpvars_K562_10kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_10kb_SMOTE$Feature)
+rfimpvars_K562_25kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_25kb_SMOTE$Feature)
+rfimpvars_K562_50kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_50kb_SMOTE$Feature)
+rfimpvars_K562_100kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_100kb_SMOTE$Feature)
+
+unionannots <- union(rfimpvars_K562_10kb_SMOTE$Feature,
+                      union(rfimpvars_K562_25kb_SMOTE$Feature,
+                            union(rfimpvars_K562_50kb_SMOTE$Feature,rfimpvars_K562_100kb_SMOTE$Feature)))
+unionannots <- sort(unionannots)
+
+vim.K562.smote <- data.frame(Feature=unionannots)
+
+vim.K562.smote <- left_join(left_join(left_join(left_join(vim.K562.smote,rfimpvars_K562_10kb_SMOTE, by="Feature"),
+								rfimpvars_K562_25kb_SMOTE, by="Feature"),
+								rfimpvars_K562_50kb_SMOTE, by="Feature"),
+								rfimpvars_K562_100kb_SMOTE, by="Feature")
+names(vim.K562.smote) <- c("Feature","Importance.10kb","Importance.25kb","Importance.50kb","Importance.100kb")
+
+vim.K562.smote.ranks <- data.frame(Feature=vim.K562.smote$Feature,
+									  Rank.10kb=rank(-vim.K562.smote$Importance.10kb, na.last = TRUE),
+									  Rank.25kb=rank(-vim.K562.smote$Importance.25kb, na.last = TRUE),
+									  Rank.50kb=rank(-vim.K562.smote$Importance.50kb, na.last = TRUE),
+									  Rank.100kb=rank(-vim.K562.smote$Importance.100kb, na.last = TRUE))
+
+rankdata <- cbind(vim.K562.smote.ranks$Rank.10kb,
+                  vim.K562.smote.ranks$Rank.25kb,
+				  vim.K562.smote.ranks$Rank.50kb,
+				  vim.K562.smote.ranks$Rank.100kb)
+rownames(rankdata) <- vim.K562.smote.ranks$Feature
+colnames(rankdata) <- c("10 kb", "25 kb", "50 kb", "100 kb")
+
+#my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100)) 
+my_palette <- colorRampPalette(c("red", "white"))(nrow(rankdata))
+heatmap.2(t(rankdata),
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          #margins =c(5,5),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 2,
+          dendrogram="both",     # only draw a row dendrogram,
+          Rowv = TRUE,
+          Colv = TRUE,
+          cexRow=1.5,
+          cexCol=0.5,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          rowsep=1:4,
+          colsep=0:nrow(rankdata)) 
+```
+
+# ICC
+
+```{r}
+vim.gm12878.smote[is.na(vim.gm12878.smote)] <- 0
+icc(vim.gm12878.smote, model = "twoway", type = "agreement")
+
+```

### 2019-04-08 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-We first evaluated performances for models implemented using OC predictor types, without re-sampling (on the GM12878 cell line), as these characteristics represented models with the least granularity and could act as a baseline.
-In evaluating such composite metrics like F1-Score and MCC, we found that these models exhibited poor performances across resolutions (Figure 5A).
-Furthermore, at lower resolutions (50 kb and 100 kb specifically), the F1-Score and MCC could not be determined given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives <!--, as can be seen by the missing red points-->.
+We first evaluated performances for models implemented using OC predictor types, without re-sampling, as these characteristics represented models with the least granularity and could act as a baseline.
+In evaluating such composite metrics like F1-Score and MCC, we found that these models exhibited poor performances across resolutions, for both cell lines (Figure 5A).
+Furthermore, at some resolutions , the F1-Score and MCC could not be determined given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives <!--, as can be seen by the missing red points-->.
 When including OP perdictor types in the models, coupled with no resampling, we found that performances were worse than when using OC predictor types (Figure 5B).
-As with OC predictor types, these models were also not able to yield F1-Scores and MCCs at the 50 kb and 100 kb resolution.
+As with OC predictor types, these models were also not able to yield F1-Scores and MCCs at the 50 kb and 100 kb resolution for the GM12878 cell line or any resolution lower than 10 kb for the K562 cell line.
 Models built on distance-type predictors, however, exhibited slightly better performances than the other two types, yet still yielded missing or low F1-Scores and MCC at lower resolutions (Figure 5C).
-Similar results were obtained on the K562 cell line, in which F1-Scores and MCCs were either low or missing across resolutions, with marginal improvement when considering distance types (Supplementary Figure 10 A-C).
+Models built on 100 kb resolutions were not able to yeild F1-Scores for either cell line.
 This indicated that the key driver leading to poor performances was not due to feature engineering, but instead the severity in the class imbalance.
+<!--Mention AUC is not good metric using supplementary table-->
 
@@
 Comparisons of the effects of the various resampling techniques were then made.
-On the GM12878 cell line, we found that there was a substantial increase in F1-Score and MCC for models built on resampled data using any of the 3 techniques (Figure 5).
-After resampling, we were able to report performances at the lower resolutions which was not feasible for models built on fully imbalanced data.
-For all predictor types, implementation of either RUS or SMOTE resampling was found to yield consistently better results than no resampling and ROS.
-These results were confirmed when evaluating the K562 cell line (Supplementary Figure 10 A-C).
+When models were built on randomly oversampled data, we found a substantial increase in F1-Score and MCC for both cell lines (Figure 5 D-F).
+The biggest improvement in performance was seen at the 10 kb resolution, with a sharp downward trend as resolutions decreased.
+Although performances were low at lower resolutions, both F1-Scores and MCC values were able to be obtained, contrary to models built on completely unbalanced data as seen before.
+Distance-type predictors were found to offer the highest F1-Scores and MCCs for randomly oversampled data, across all resolutions and for both cell lines.
 
-## USING DISTANCE-TYPE PREDICTORS FURTHER IMPROVED MODEL PERFORMANCES
-
-On the GM12878 cell line, results showed that models with distance-type predictors outperformed models with other predictor types (Figure 5C).
-This result was consistent across both resampling technique and resolution.
-Directly comparing model performances using distance type predictors, we found that SMOTE resampled datasets yielded the highest model performances across each of the composite metrics.
-Although RUS performed only marginally worse than SMOTE, there was a steap drop off in performances for ROS and no re-sampling, across resolution.
-The same combination of resampling technique and predictor type was also found to result in the best performing model for the K562 cell line (Supplementary Figure 10C).
+Further improvement in performance was found when models were implemented on both randomly undersampled (Figure 5 G-H) and SMOTE resampled data (Figure 5 J-K).
+Although the differences in performance between the two techniques were marginal, SMOTE resampled data was found to yield the best F1-Scores and MCCs among all classes of models develeped and compared in the ensemble framework.
 These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that incorporates both random under- and over-sampling, as SMOTE is known to do.
 
-Furthermore, we found that when using distance-type predictors, model performances tended to decline as data resolution decreased.
-There was a slight improvement in F1-Score for the 25 kb resolution on the GM12878 cell line, followed by a steep decline at 50 kb.
-Both F1-Scores and MCCs showed a momentary increase in performance at the lowest resolution considered in the study.
-Performances from the K562 cell line degraded much faster as resolution decreased, while the worst performing models for the GM12878 cell line were at the 50 kb resolution, followed by a slight improvement in performance at the 100 kb resolution.
+## DISTANCE-TYPE PREDICTORS PROVIDED THE MOST INFORMATIVE SPATIAL REPRESENTATION OF EPIGENOMIC ANNOTATIONS ASSOCIATED WITH TAD BOUNDARIES
+
+Regardless, of resampling technique however, the inclusion of distance type predictors resulted in better F1-Scores and MCCs when compared to either OC or OP predictor types.
+This was consistent across all resolutions, for both cell lines.
+Furthermore, in the best overall model (SMOTE with distance-type predictors) we found that the degradation in model performance as resolution decreased was much more pronounced in the K562 cell line.
+on the GM12878 cell line, there was a slight improvement in F1-Score for the 25 kb resolution, followed by a steep decline at 50 kb.
+Then, both F1-Scores and MCCs showed a momentary increase in performance at the lowest resolution considered in the study.
+Performances from the K562 cell line degraded much faster as resolution decreased, the worse being at the 100 kb resolution.
 

### 2019-04-08 Manuscript/manuscript.Rmd
manuscript edits

@@
 While not directly affecting the value of the AUROC, this can have severe consequences on the interpretability of the model's performance.
-A better threshold-free measure to use when dealing with imbalanced data is the area under the precision-recall curve (AUPRC).
+<!--A better threshold-free measure to use when dealing with imbalanced data is the area under the precision-recall curve (AUPRC).
 The interpretation of the AUPRC of a model is similar to that of the AUROC.
 However, where as the baseline model performance according to the AUROC is given by 0.50, the baseline model performance according to the AUPRC is given by the ratio of true positives over the total number of cases.
-This enables a more realistic benchmark to evaluate a model on as this ratio will be lower than 0.5 for a test data set with imbalanced classes.
-Likewise, threshold-specific metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
+This enables a more realistic benchmark to evaluate a model on as this ratio will be lower than 0.5 for a test data set with imbalanced classes.--> Likewise, threshold-specific metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
 Better measures to consider are composite metrics involving both precision and recall together because they soften the influence of a model's ability to correctly classify majority classes and yield more dependable and interpretable results.
@@
 
-The efficacy of each re-sampling technique was compared using composite metrics inclusing F1-score and MCC. These metrics are defined as follows:
+The efficacy of each re-sampling technique was compared using composite metrics including F1-score and MCC. These metrics are defined as follows:
 
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-Additional threshold-free metrics where also reported including the AUROC and AUPRC.
-
-Lastly, for the task of identifying the genomic annotations that were most predictive of the formation of TAD boundaries, we evaluated the variable importances associated with each feature of the random forest model associated with the best combination of reduced predictor type and re-sampling technique, across each cell line.
-To calculate variable importances for each model, the AUPRC on the out-of-bag portion of the data within each tree was recorded.
+<!--Additional threshold-free metrics where also reported including the AUROC and AUPRC.--> Lastly, for the task of identifying the genomic annotations that were most predictive of the formation of TAD boundaries, we ranked the variable importances associated with each feature of the ensemble system-specific random forest model.
+<!--To calculate variable importances for each model, the F1-Score on the out-of-bag portion of the data within each tree was recorded.
 Then the same was done after permuting each predictor variable.
-The difference between the two AUPRC values was then averaged over all trees, and normalized by the standard error of the differences.
-All measures of importances were then rescaled to have a maximum value of 100 for better interpretation.
+The difference between the two AUPRC values was then averaged over all trees, and normalized by the standard error of the differences.--> Annotations with low rankings correspond to functional epigenomic features that are either positively or negatively enriched near TAD boundaries, and thus, better allow the model to discriminate between genomic bins that overlap with flanked TAD boundaries.
 
@@
 Lastly, we investigated which genomic annotations were most predictive of TAD boundary formation.
-Looking at heatmaps of variable importances provided by the random forest classifiers implemented on SMOTE re-sampled data, with distance-type predictors, we found that known transcription factors associated with the hypothesized loop extrusion model [@fudenberg2016formation; @alipour2012self] were give high predictive importance in the model (Figure 10).
+Looking at heatmaps of variable importances provided by the random forest classifiers implemented on SMOTE re-sampled data, with distance-type predictors, we found that known transcription factors associated with the hypothesized loop extrusion model [@fudenberg2016formation; @alipour2012self] were give high predictive importance in the model for both cell lines (Figure 6 A-B).
 These tended to include the SMC3ab, ZNF143, CTCF, and RAD21 transcription factor binding sites and were found to be ranked consistly across resolution.
 Other annotations known to be associated with gene regulation and affect structural properties of chromatin, such as the YY1 and MAZ transcription factors, as well DNAse hypersensitive sites, regions of heterochromatin, and the H3k27 trimethylation and H3K4me1 modifications were less consistently ranked across resolutions for either cell line.
+Moreover, the ranking profiles of genomic annotations were found to be more similar between the 10 kb and 25 kb resolutions, as well as between the 50 kb and 100 kb resoluions.
 

### 2019-04-08 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-Replicate Hi-C data for the GM12878 and K562 cell lines were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 4).
+Replicate Hi-C data for the GM12878 and K562 cell lines were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1).
 The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
@@
 
-Genomic annotation data in the form of cell type specific chromatin states, histone marks, and transcription factor binding sites (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 1).
+Genomic annotation data in the form of cell type specific chromatin states, histone marks, and transcription factor binding sites (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 2).
 

### 2019-04-09 Scripts/creating_supplementary_table_of_all_performances.Rmd
editted results scripts

--- 2019-04-07 Scripts/evaluating_models_with_dist_preds.Rmd
@@
 ---
-title: "Comparing top performing models"
+title: "Creating Supplementary Table of all Performances"
 author: "Spiro Stilianoudakis"
-date: "March 8, 2019"
+date: "April 8, 2019"
 output: html_document
@@
 
-# Loading Libraries
-
-```{r}
-library(GenomicRanges)
-library(caret)
-library(data.table)
-library(gbm)
-library(randomForest)
-library(glmnet)
-library(pROC)
-library(plyr)
-library(dplyr)
-library(ggplot2)
-library(DMwR)
-library(gridExtra)
-library(pROC)
-library(ROCR)
-#library(leaps)
-library(cluster)
-library(ggpubr)
-library(scales)
-library(GGally)
-library(VennDiagram)
-library(network)
-library(sna)
-library(gtable)
-library(grid)
-library(magrittr) 
-library(DT)
-library(tidyverse)
-library(reshape)
-library(ROSE)
-library(lattice)
-library(corrplot)
-library(cluster)
-library(RColorBrewer)
-
-```
-
-# Comparing models with distance type predictors
-
-##gm12878
+# Reading in all model results in the ensemble framework
 
@@
 
-all_rfperfs_gm12878 <- data.frame(Resolution=rep(c(rep("10 kb", 12),
-                                                        rep("25 kb", 12),
-                                                        rep("50 kb", 12),
-                                                        rep("100 kb", 12)),4),
-                                       Predictor=rep(c("OC","OP","Distance"),64),
-                                       Metric=c(rep("AUC",48),
-                                                rep("AUPRC",48),
-                                                rep("F1-Score",48), 
-                                                rep("MCC",48)),
-                                       Resampling=rep(c(rep("None",3),
-                                                    rep("ROS",3),
-                                                    rep("RUS",3),
-                                                    rep("SMOTE",3)),16))
-all_rfperfs_gm12878$Resolution <- factor(all_rfperfs_gm12878$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
-all_rfperfs_gm12878$Predictor <- factor(all_rfperfs_gm12878$Predictor, levels=c("OC", "OP", "Distance"))
-all_rfperfs_gm12878$Metric <- factor(all_rfperfs_gm12878$Metric, levels=c("AUC", "AUPRC", "F1-Score", "MCC"))
-all_rfperfs_gm12878$Resampling <- factor(all_rfperfs_gm12878$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))
-
-all_rfperfs_gm12878$Performance <- c(round(rfperf_gm12878_10kb_none_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_none_op[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_none_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_gm12878_10kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_gm12878_25kb_none_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_none_op[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_none_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_gm12878_25kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_gm12878_50kb_none_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_none_op[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_none_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_gm12878_50kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_gm12878_100kb_none_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_none_op[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_none_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_gm12878_100kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_gm12878_10kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_none_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_10kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_gm12878_25kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_none_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_25kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_gm12878_50kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_none_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_50kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_gm12878_100kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_none_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_gm12878_100kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_gm12878_10kb_none_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_none_op[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_none_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_gm12878_10kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_gm12878_25kb_none_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_none_op[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_none_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_gm12878_25kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_gm12878_50kb_none_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_none_op[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_none_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_gm12878_50kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_gm12878_100kb_none_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_none_op[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_none_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_gm12878_100kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_gm12878_10kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_none_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_10kb_SMOTE_dist[15,2],2), #mcc
-
-                                     round(rfperf_gm12878_25kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_none_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_25kb_SMOTE_dist[15,2],2), #mcc
-
-                                     round(rfperf_gm12878_50kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_none_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_50kb_SMOTE_dist[15,2],2), #mcc
-
-                                     round(rfperf_gm12878_100kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_none_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_gm12878_100kb_SMOTE_dist[15,2],2) #mcc
-)
-
-p1 <- ggplot(all_rfperfs_gm12878[which(all_rfperfs_gm12878$Predictor=="Distance"),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
-    geom_line(size=2)+
-    geom_point(size=5)+
-    facet_grid(~ Metric)+
-    theme_minimal() +
-    theme_bw()+
-    xlab("") + ylab("") +
-  scale_color_discrete(name="Re-Sampling Technique")+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1
-	                                 ),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20),
-	      plot.title = element_text(size=20))
-
-```
-
-##k562
-
-```{r}
 #OC
@@
 
-all_rfperfs_K562 <- data.frame(Resolution=rep(c(rep("10 kb", 12),
-                                                        rep("25 kb", 12),
-                                                        rep("50 kb", 12),
-                                                        rep("100 kb", 12)),4),
-                                       Predictor=rep(c("OC","OP","Distance"),64),
-                                       Metric=c(rep("AUC",48),
-                                                rep("AUPRC",48),
-                                                rep("F1-Score",48), 
-                                                rep("MCC",48)),
-                                       Resampling=rep(c(rep("None",3),
-                                                    rep("ROS",3),
-                                                    rep("RUS",3),
-                                                    rep("SMOTE",3)),16))
-all_rfperfs_K562$Resolution <- factor(all_rfperfs_K562$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
-all_rfperfs_K562$Predictor <- factor(all_rfperfs_K562$Predictor, levels=c("OC", "OP", "Distance"))
-all_rfperfs_K562$Metric <- factor(all_rfperfs_K562$Metric, levels=c("AUC", "AUPRC", "F1-Score", "MCC"))
-all_rfperfs_K562$Resampling <- factor(all_rfperfs_K562$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))
-
-all_rfperfs_K562$Performance <- c(round(rfperf_K562_10kb_none_oc[17,2],2), #auc
-                                          round(rfperf_K562_10kb_none_op[17,2],2), #auc
-                                          round(rfperf_K562_10kb_none_dist[17,2],2), #auc
-                                          round(rfperf_K562_10kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_K562_10kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_K562_10kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_K562_10kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_K562_10kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_K562_10kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_K562_10kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_K562_10kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_K562_10kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_K562_25kb_none_oc[17,2],2), #auc
-                                          round(rfperf_K562_25kb_none_op[17,2],2), #auc
-                                          round(rfperf_K562_25kb_none_dist[17,2],2), #auc
-                                          round(rfperf_K562_25kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_K562_25kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_K562_25kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_K562_25kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_K562_25kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_K562_25kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_K562_25kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_K562_25kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_K562_25kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_K562_50kb_none_oc[17,2],2), #auc
-                                          round(rfperf_K562_50kb_none_op[17,2],2), #auc
-                                          round(rfperf_K562_50kb_none_dist[17,2],2), #auc
-                                          round(rfperf_K562_50kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_K562_50kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_K562_50kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_K562_50kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_K562_50kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_K562_50kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_K562_50kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_K562_50kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_K562_50kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_K562_100kb_none_oc[17,2],2), #auc
-                                          round(rfperf_K562_100kb_none_op[17,2],2), #auc
-                                          round(rfperf_K562_100kb_none_dist[17,2],2), #auc
-                                          round(rfperf_K562_100kb_ROS_oc[17,2],2), #auc
-                                          round(rfperf_K562_100kb_ROS_op[17,2],2), #auc
-                                          round(rfperf_K562_100kb_ROS_dist[17,2],2), #auc
-                                          round(rfperf_K562_100kb_RUS_oc[17,2],2), #auc
-                                          round(rfperf_K562_100kb_RUS_op[17,2],2), #auc
-                                          round(rfperf_K562_100kb_RUS_dist[17,2],2), #auc
-                                          round(rfperf_K562_100kb_SMOTE_oc[17,2],2), #auc
-                                          round(rfperf_K562_100kb_SMOTE_op[17,2],2), #auc
-                                          round(rfperf_K562_100kb_SMOTE_dist[17,2],2), #auc
-
-                                     round(rfperf_K562_10kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_none_op[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_K562_10kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_K562_25kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_none_op[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_K562_25kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_K562_50kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_none_op[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_K562_50kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_K562_100kb_none_oc[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_none_op[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_none_dist[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_ROS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_ROS_op[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_ROS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_RUS_oc[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_RUS_op[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_RUS_dist[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_SMOTE_oc[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_SMOTE_op[19,2],2), #auprc
-                                          round(rfperf_K562_100kb_SMOTE_dist[19,2],2), #auprc
-
-                                     round(rfperf_K562_10kb_none_oc[16,2],2), #f1
-                                          round(rfperf_K562_10kb_none_op[16,2],2), #f1
-                                          round(rfperf_K562_10kb_none_dist[16,2],2), #f1
-                                          round(rfperf_K562_10kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_K562_10kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_K562_10kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_K562_10kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_K562_10kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_K562_10kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_K562_10kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_K562_10kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_K562_10kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_K562_25kb_none_oc[16,2],2), #f1
-                                          round(rfperf_K562_25kb_none_op[16,2],2), #f1
-                                          round(rfperf_K562_25kb_none_dist[16,2],2), #f1
-                                          round(rfperf_K562_25kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_K562_25kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_K562_25kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_K562_25kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_K562_25kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_K562_25kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_K562_25kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_K562_25kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_K562_25kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_K562_50kb_none_oc[16,2],2), #f1
-                                          round(rfperf_K562_50kb_none_op[16,2],2), #f1
-                                          round(rfperf_K562_50kb_none_dist[16,2],2), #f1
-                                          round(rfperf_K562_50kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_K562_50kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_K562_50kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_K562_50kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_K562_50kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_K562_50kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_K562_50kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_K562_50kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_K562_50kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_K562_100kb_none_oc[16,2],2), #f1
-                                          round(rfperf_K562_100kb_none_op[16,2],2), #f1
-                                          round(rfperf_K562_100kb_none_dist[16,2],2), #f1
-                                          round(rfperf_K562_100kb_ROS_oc[16,2],2), #f1
-                                          round(rfperf_K562_100kb_ROS_op[16,2],2), #f1
-                                          round(rfperf_K562_100kb_ROS_dist[16,2],2), #f1
-                                          round(rfperf_K562_100kb_RUS_oc[16,2],2), #f1
-                                          round(rfperf_K562_100kb_RUS_op[16,2],2), #f1
-                                          round(rfperf_K562_100kb_RUS_dist[16,2],2), #f1
-                                          round(rfperf_K562_100kb_SMOTE_oc[16,2],2), #f1
-                                          round(rfperf_K562_100kb_SMOTE_op[16,2],2), #f1
-                                          round(rfperf_K562_100kb_SMOTE_dist[16,2],2), #f1
-
-                                     round(rfperf_K562_10kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_none_op[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_K562_10kb_SMOTE_dist[15,2],2), #mcc
-
-                                     round(rfperf_K562_25kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_none_op[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_K562_25kb_SMOTE_dist[15,2],2), #mcc
-
-                                     round(rfperf_K562_50kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_none_op[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_K562_50kb_SMOTE_dist[15,2],2), #mcc
-
-                                     round(rfperf_K562_100kb_none_oc[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_none_op[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_none_dist[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_ROS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_ROS_op[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_ROS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_RUS_oc[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_RUS_op[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_RUS_dist[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_SMOTE_oc[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_SMOTE_op[15,2],2), #mcc
-                                          round(rfperf_K562_100kb_SMOTE_dist[15,2],2) #mcc
-)
-
-p2 <- ggplot(all_rfperfs_K562,
-       aes(x=Resolution, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(Metric ~ Resampling) +
-  xlab("") + ylab("") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15,
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
 ```
 
-##Plots
+# Creating and saving table with all results
 
 ```{r}
-p1 <- p1 + labs(title = "GM12878") + theme(plot.title = element_text(size=20))
-p2 <- p2 + labs(title = "K562") + theme(plot.title = element_text(size=20))
+all_rfperfs_df <- rbind.data.frame(rfperf_gm12878_10kb_none_oc,
+                                   rfperf_gm12878_10kb_none_op,
+                                   rfperf_gm12878_10kb_none_dist,
+                                   rfperf_gm12878_25kb_none_oc,
+                                   rfperf_gm12878_25kb_none_op,
+                                   rfperf_gm12878_25kb_none_dist,
+                                   rfperf_gm12878_50kb_none_oc,
+                                   rfperf_gm12878_50kb_none_op,
+                                   rfperf_gm12878_50kb_none_dist,
+                                   rfperf_gm12878_100kb_none_oc,
+                                   rfperf_gm12878_100kb_none_op,
+                                   rfperf_gm12878_100kb_none_dist,
 
-figure <- ggarrange(p1,p2,
-                ncol = 2, nrow = 1, 
-                common.legend = TRUE, 
-                legend = "top",
-                labels = "AUTO",
-                font.label = list(size=20))
-figure
-annotate_figure(figure,
-    bottom = text_grob("Resolution", color = "black", size = 20),
-    left = text_grob("Performance", color = "black", rot = 90, size=20)
-)
+                                   rfperf_gm12878_10kb_ROS_oc,
+                                   rfperf_gm12878_10kb_ROS_op,
+                                   rfperf_gm12878_10kb_ROS_dist,
+                                   rfperf_gm12878_25kb_ROS_oc,
+                                   rfperf_gm12878_25kb_ROS_op,
+                                   rfperf_gm12878_25kb_ROS_dist,
+                                   rfperf_gm12878_50kb_ROS_oc,
+                                   rfperf_gm12878_50kb_ROS_op,
+                                   rfperf_gm12878_50kb_ROS_dist,
+                                   rfperf_gm12878_100kb_ROS_oc,
+                                   rfperf_gm12878_100kb_ROS_op,
+                                   rfperf_gm12878_100kb_ROS_dist,
 
+                                   rfperf_gm12878_10kb_RUS_oc,
+                                   rfperf_gm12878_10kb_RUS_op,
+                                   rfperf_gm12878_10kb_RUS_dist,
+                                   rfperf_gm12878_25kb_RUS_oc,
+                                   rfperf_gm12878_25kb_RUS_op,
+                                   rfperf_gm12878_25kb_RUS_dist,
+                                   rfperf_gm12878_50kb_RUS_oc,
+                                   rfperf_gm12878_50kb_RUS_op,
+                                   rfperf_gm12878_50kb_RUS_dist,
+                                   rfperf_gm12878_100kb_RUS_oc,
+                                   rfperf_gm12878_100kb_RUS_op,
+                                   rfperf_gm12878_100kb_RUS_dist,
+
+                                   rfperf_gm12878_10kb_SMOTE_oc,
+                                   rfperf_gm12878_10kb_SMOTE_op,
+                                   rfperf_gm12878_10kb_SMOTE_dist,
+                                   rfperf_gm12878_25kb_SMOTE_oc,
+                                   rfperf_gm12878_25kb_SMOTE_op,
+                                   rfperf_gm12878_25kb_SMOTE_dist,
+                                   rfperf_gm12878_50kb_SMOTE_oc,
+                                   rfperf_gm12878_50kb_SMOTE_op,
+                                   rfperf_gm12878_50kb_SMOTE_dist,
+                                   rfperf_gm12878_100kb_SMOTE_oc,
+                                   rfperf_gm12878_100kb_SMOTE_op,
+                                   rfperf_gm12878_100kb_SMOTE_dist,
+
+                                   rfperf_K562_10kb_none_oc,
+                                   rfperf_K562_10kb_none_op,
+                                   rfperf_K562_10kb_none_dist,
+                                   rfperf_K562_25kb_none_oc,
+                                   rfperf_K562_25kb_none_op,
+                                   rfperf_K562_25kb_none_dist,
+                                   rfperf_K562_50kb_none_oc,
+                                   rfperf_K562_50kb_none_op,
+                                   rfperf_K562_50kb_none_dist,
+                                   rfperf_K562_100kb_none_oc,
+                                   rfperf_K562_100kb_none_op,
+                                   rfperf_K562_100kb_none_dist,
+
+                                   rfperf_K562_10kb_ROS_oc,
+                                   rfperf_K562_10kb_ROS_op,
+                                   rfperf_K562_10kb_ROS_dist,
+                                   rfperf_K562_25kb_ROS_oc,
+                                   rfperf_K562_25kb_ROS_op,
+                                   rfperf_K562_25kb_ROS_dist,
+                                   rfperf_K562_50kb_ROS_oc,
+                                   rfperf_K562_50kb_ROS_op,
+                                   rfperf_K562_50kb_ROS_dist,
+                                   rfperf_K562_100kb_ROS_oc,
+                                   rfperf_K562_100kb_ROS_op,
+                                   rfperf_K562_100kb_ROS_dist,
+
+                                   rfperf_K562_10kb_RUS_oc,
+                                   rfperf_K562_10kb_RUS_op,
+                                   rfperf_K562_10kb_RUS_dist,
+                                   rfperf_K562_25kb_RUS_oc,
+                                   rfperf_K562_25kb_RUS_op,
+                                   rfperf_K562_25kb_RUS_dist,
+                                   rfperf_K562_50kb_RUS_oc,
+                                   rfperf_K562_50kb_RUS_op,
+                                   rfperf_K562_50kb_RUS_dist,
+                                   rfperf_K562_100kb_RUS_oc,
+                                   rfperf_K562_100kb_RUS_op,
+                                   rfperf_K562_100kb_RUS_dist,
+
+                                   rfperf_K562_10kb_SMOTE_oc,
+                                   rfperf_K562_10kb_SMOTE_op,
+                                   rfperf_K562_10kb_SMOTE_dist,
+                                   rfperf_K562_25kb_SMOTE_oc,
+                                   rfperf_K562_25kb_SMOTE_op,
+                                   rfperf_K562_25kb_SMOTE_dist,
+                                   rfperf_K562_50kb_SMOTE_oc,
+                                   rfperf_K562_50kb_SMOTE_op,
+                                   rfperf_K562_50kb_SMOTE_dist,
+                                   rfperf_K562_100kb_SMOTE_oc,
+                                   rfperf_K562_100kb_SMOTE_op,
+                                   rfperf_K562_100kb_SMOTE_dist)
+
+all_rfperfs_df$CellLine <- c(rep("GM12878",19*48),rep("K562",19*48))
+all_rfperfs_df$Resolution <- rep(c(rep("10 kb", 19*3),rep("25 kb", 19*3),rep("50 kb", 19*3),rep("100 kb", 19*3)),8)
+all_rfperfs_df$Resampling <- rep(c(rep("None",19*12),rep("ROS",19*12),rep("RUS",19*12),rep("SMOTE",19*12)), 2)
+all_rfperfs_df$PredictorType <- rep(c("OC", "OP", "Distance"),19*32)
+
+all_rfperfs_df <- all_rfperfs_df[,c(3,4,5,6,1,2)]
+all_rfperfs_df$Performance <- round(all_rfperfs_df$Performance, 3)
+
+write.csv(all_rfperfs_df, "C:/Users/stili/Downloads/table3_all_model_performances.csv")
 ```

### 2019-04-09 Scripts/evaluating_model_performances.Rmd
editted results scripts

@@
 ```
+
+## Plots
+
+```{r}
+all_rfperfs <- rbind.data.frame(all_rfperfs_gm12878, all_rfperfs_K562)
+all_rfperfs$CL <- c(rep("GM12878", dim(all_rfperfs_gm12878)[1]), rep("K562", dim(all_rfperfs_K562)[1]))
+
+#GM12878
+c <- ggplot(all_rfperfs[which(all_rfperfs$CL=="GM12878" & all_rfperfs$Predictor=="OC" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
+     geom_line(size=2)+
+     geom_point(size=5)+
+     facet_grid(~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.05,.5) +
+     ggtitle("Overlap Counts") +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+p <- ggplot(all_rfperfs[which(all_rfperfs$CL=="GM12878" & all_rfperfs$Predictor=="OP" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
+     geom_line(size=2)+
+     geom_point(size=5)+
+     facet_grid(~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.05,.5) +
+     ggtitle("Overlap Percents") +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+d <- ggplot(all_rfperfs[which(all_rfperfs$CL=="GM12878" & all_rfperfs$Predictor=="Distance" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
+     geom_line(size=2)+
+     geom_point(size=5)+
+     facet_grid(~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.05,.5) +
+     ggtitle("Distance") +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+figure <- ggarrange(c,p,d,
+                ncol = 3, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "top",
+                labels = "AUTO",
+                font.label = list(size=20))
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Performance", color = "black", rot = 90, size=20)
+)
+
+#K562
+c2 <- ggplot(all_rfperfs[which(all_rfperfs$CL=="K562" & all_rfperfs$Predictor=="OC" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
+     geom_line(size=2)+
+     geom_point(size=5)+
+     facet_grid(~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.05,.5) +
+     ggtitle("Overlap Counts") +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+p2 <- ggplot(all_rfperfs[which(all_rfperfs$CL=="K562" & all_rfperfs$Predictor=="OP" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
+     geom_line(size=2)+
+     geom_point(size=5)+
+     facet_grid(~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.05,.5) +
+     ggtitle("Overlap Percents") +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+d2 <- ggplot(all_rfperfs[which(all_rfperfs$CL=="K562" & all_rfperfs$Predictor=="Distance" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
+     geom_line(size=2)+
+     geom_point(size=5)+
+     facet_grid(~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.05,.5) +
+     ggtitle("Distance") +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+figure <- ggarrange(c2,p2,d2,
+                ncol = 3, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "top",
+                labels = "AUTO",
+                font.label = list(size=20))
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Performance", color = "black", rot = 90, size=20)
+)
+
+figure <- ggarrange(c,p,d,c2,p2,d2,
+                ncol = 3, nrow = 2, 
+                common.legend = TRUE, 
+                legend = "top")
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Performance", color = "black", rot = 90, size=20)
+)
+
+```

### 2019-04-09 Scripts/evaluating_variable_importances.Rmd
editted results scripts

@@
 
-#Variable Importance Bar Plots for models with distance type predictors
-
-##10kb
-
-###None
-
-```{r}
-#GM12878
-rfimpvars_gm12878_10kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_10kb_none <- rfimpvars_gm12878_10kb_none[1:10,]
-#rfimpvars_gm12878_10kb_none <- rfimpvars_gm12878_10kb_none[10:1,]
-rfimpvars_gm12878_10kb_none <- rfimpvars_gm12878_10kb_none[1:20,]
-rfimpvars_gm12878_10kb_none <- rfimpvars_gm12878_10kb_none[20:1,]
-
-rfimpvars_gm12878_10kb_none$Feature <- gsub("_dist","", rfimpvars_gm12878_10kb_none$Feature)
-
-rfimpvars_gm12878_10kb_none$Feature <- factor(rfimpvars_gm12878_10kb_none$Feature, levels=rfimpvars_gm12878_10kb_none$Feature)
-
-vip.gm12878.10kb.none <- ggplot(rfimpvars_gm12878_10kb_none, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_10kb_none <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_10kb_none <- rfimpvars_K562_10kb_none[1:10,]
-#rfimpvars_K562_10kb_none <- rfimpvars_K562_10kb_none[10:1,]
-rfimpvars_K562_10kb_none <- rfimpvars_K562_10kb_none[1:20,]
-rfimpvars_K562_10kb_none <- rfimpvars_K562_10kb_none[20:1,]
-
-rfimpvars_K562_10kb_none$Feature <- gsub("_dist","", rfimpvars_K562_10kb_none$Feature)
-
-rfimpvars_K562_10kb_none$Feature <- factor(rfimpvars_K562_10kb_none$Feature, levels=rfimpvars_K562_10kb_none$Feature)
-
-vip.K562.10kb.none <- ggplot(rfimpvars_K562_10kb_none, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-```
-
-###ROS
-
-```{r}
-rfimpvars_gm12878_10kb_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_10kb_ROS <- rfimpvars_gm12878_10kb_ROS[1:10,]
-#rfimpvars_gm12878_10kb_ROS <- rfimpvars_gm12878_10kb_ROS[10:1,]
-rfimpvars_gm12878_10kb_ROS <- rfimpvars_gm12878_10kb_ROS[1:20,]
-rfimpvars_gm12878_10kb_ROS <- rfimpvars_gm12878_10kb_ROS[20:1,]
-
-rfimpvars_gm12878_10kb_ROS$Feature <- gsub("_dist","", rfimpvars_gm12878_10kb_ROS$Feature)
-
-rfimpvars_gm12878_10kb_ROS$Feature <- factor(rfimpvars_gm12878_10kb_ROS$Feature, levels=rfimpvars_gm12878_10kb_ROS$Feature)
-
-vip.gm12878.10kb.ROS <- ggplot(rfimpvars_gm12878_10kb_ROS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_10kb_ROS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_10kb_ROS <- rfimpvars_K562_10kb_ROS[1:10,]
-#rfimpvars_K562_10kb_ROS <- rfimpvars_K562_10kb_ROS[10:1,]
-rfimpvars_K562_10kb_ROS <- rfimpvars_K562_10kb_ROS[1:20,]
-rfimpvars_K562_10kb_ROS <- rfimpvars_K562_10kb_ROS[20:1,]
-
-rfimpvars_K562_10kb_ROS$Feature <- gsub("_dist","", rfimpvars_K562_10kb_ROS$Feature)
-
-rfimpvars_K562_10kb_ROS$Feature <- factor(rfimpvars_K562_10kb_ROS$Feature, levels=rfimpvars_K562_10kb_ROS$Feature)
-
-vip.K562.10kb.ROS <- ggplot(rfimpvars_K562_10kb_ROS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-```
-
-###RUS
-
-```{r}
-rfimpvars_gm12878_10kb_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_10kb_RUS <- rfimpvars_gm12878_10kb_RUS[1:10,]
-#rfimpvars_gm12878_10kb_RUS <- rfimpvars_gm12878_10kb_RUS[10:1,]
-rfimpvars_gm12878_10kb_RUS <- rfimpvars_gm12878_10kb_RUS[1:20,]
-rfimpvars_gm12878_10kb_RUS <- rfimpvars_gm12878_10kb_RUS[20:1,]
-
-rfimpvars_gm12878_10kb_RUS$Feature <- gsub("_dist","", rfimpvars_gm12878_10kb_RUS$Feature)
-
-rfimpvars_gm12878_10kb_RUS$Feature <- factor(rfimpvars_gm12878_10kb_RUS$Feature, levels=rfimpvars_gm12878_10kb_RUS$Feature)
-
-vip.gm12878.10kb.RUS <- ggplot(rfimpvars_gm12878_10kb_RUS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_10kb_RUS <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_10kb_RUS <- rfimpvars_K562_10kb_RUS[1:10,]
-#rfimpvars_K562_10kb_RUS <- rfimpvars_K562_10kb_RUS[10:1,]
-rfimpvars_K562_10kb_RUS <- rfimpvars_K562_10kb_RUS[1:20,]
-rfimpvars_K562_10kb_RUS <- rfimpvars_K562_10kb_RUS[20:1,]
-
-rfimpvars_K562_10kb_RUS$Feature <- gsub("_dist","", rfimpvars_K562_10kb_RUS$Feature)
-
-rfimpvars_K562_10kb_RUS$Feature <- factor(rfimpvars_K562_10kb_RUS$Feature, levels=rfimpvars_K562_10kb_RUS$Feature)
-
-vip.K562.10kb.RUS <- ggplot(rfimpvars_K562_10kb_RUS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-```
-
-###SMOTE
-
-```{r}
-rfimpvars_gm12878_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_10kb_SMOTE <- rfimpvars_gm12878_10kb_SMOTE[1:10,]
-#rfimpvars_gm12878_10kb_SMOTE <- rfimpvars_gm12878_10kb_SMOTE[10:1,]
-rfimpvars_gm12878_10kb_SMOTE <- rfimpvars_gm12878_10kb_SMOTE[1:20,]
-rfimpvars_gm12878_10kb_SMOTE <- rfimpvars_gm12878_10kb_SMOTE[20:1,]
-
-rfimpvars_gm12878_10kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_gm12878_10kb_SMOTE$Feature)
-
-rfimpvars_gm12878_10kb_SMOTE$Feature <- factor(rfimpvars_gm12878_10kb_SMOTE$Feature, levels=rfimpvars_gm12878_10kb_SMOTE$Feature)
-
-vip.gm12878.10kb.SMOTE <- ggplot(rfimpvars_gm12878_10kb_SMOTE, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_10kb_SMOTE <- rfimpvars_K562_10kb_SMOTE[1:10,]
-#rfimpvars_K562_10kb_SMOTE <- rfimpvars_K562_10kb_SMOTE[10:1,]
-rfimpvars_K562_10kb_SMOTE <- rfimpvars_K562_10kb_SMOTE[1:20,]
-rfimpvars_K562_10kb_SMOTE <- rfimpvars_K562_10kb_SMOTE[20:1,]
-
-rfimpvars_K562_10kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_K562_10kb_SMOTE$Feature)
-
-rfimpvars_K562_10kb_SMOTE$Feature <- factor(rfimpvars_K562_10kb_SMOTE$Feature, levels=rfimpvars_K562_10kb_SMOTE$Feature)
-
-vip.K562.10kb.SMOTE <- ggplot(rfimpvars_K562_10kb_SMOTE, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-```
-
-##25kb
-
-###None
-
-```{r}
-#GM12878
-rfimpvars_gm12878_25kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_25kb_none <- rfimpvars_gm12878_25kb_none[1:10,]
-#rfimpvars_gm12878_25kb_none <- rfimpvars_gm12878_25kb_none[10:1,]
-rfimpvars_gm12878_25kb_none <- rfimpvars_gm12878_25kb_none[1:20,]
-rfimpvars_gm12878_25kb_none <- rfimpvars_gm12878_25kb_none[20:1,]
-
-rfimpvars_gm12878_25kb_none$Feature <- gsub("_dist","", rfimpvars_gm12878_25kb_none$Feature)
-
-rfimpvars_gm12878_25kb_none$Feature <- factor(rfimpvars_gm12878_25kb_none$Feature, levels=rfimpvars_gm12878_25kb_none$Feature)
-
-vip.gm12878.25kb.none <- ggplot(rfimpvars_gm12878_25kb_none, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_25kb_none <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_25kb_none <- rfimpvars_K562_25kb_none[1:10,]
-#rfimpvars_K562_25kb_none <- rfimpvars_K562_25kb_none[10:1,]
-rfimpvars_K562_25kb_none <- rfimpvars_K562_25kb_none[1:20,]
-rfimpvars_K562_25kb_none <- rfimpvars_K562_25kb_none[20:1,]
-
-rfimpvars_K562_25kb_none$Feature <- gsub("_dist","", rfimpvars_K562_25kb_none$Feature)
-
-rfimpvars_K562_25kb_none$Feature <- factor(rfimpvars_K562_25kb_none$Feature, levels=rfimpvars_K562_25kb_none$Feature)
-
-vip.K562.25kb.none <- ggplot(rfimpvars_K562_25kb_none, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-```
-
-###ROS
-
-```{r}
-rfimpvars_gm12878_25kb_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_25kb_ROS <- rfimpvars_gm12878_25kb_ROS[1:10,]
-#rfimpvars_gm12878_25kb_ROS <- rfimpvars_gm12878_25kb_ROS[10:1,]
-rfimpvars_gm12878_25kb_ROS <- rfimpvars_gm12878_25kb_ROS[1:20,]
-rfimpvars_gm12878_25kb_ROS <- rfimpvars_gm12878_25kb_ROS[20:1,]
-
-rfimpvars_gm12878_25kb_ROS$Feature <- gsub("_dist","", rfimpvars_gm12878_25kb_ROS$Feature)
-
-rfimpvars_gm12878_25kb_ROS$Feature <- factor(rfimpvars_gm12878_25kb_ROS$Feature, levels=rfimpvars_gm12878_25kb_ROS$Feature)
-
-vip.gm12878.25kb.ROS <- ggplot(rfimpvars_gm12878_25kb_ROS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_25kb_ROS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_25kb_ROS <- rfimpvars_K562_25kb_ROS[1:10,]
-#rfimpvars_K562_25kb_ROS <- rfimpvars_K562_25kb_ROS[10:1,]
-rfimpvars_K562_25kb_ROS <- rfimpvars_K562_25kb_ROS[1:20,]
-rfimpvars_K562_25kb_ROS <- rfimpvars_K562_25kb_ROS[20:1,]
-
-rfimpvars_K562_25kb_ROS$Feature <- gsub("_dist","", rfimpvars_K562_25kb_ROS$Feature)
-
-rfimpvars_K562_25kb_ROS$Feature <- factor(rfimpvars_K562_25kb_ROS$Feature, levels=rfimpvars_K562_25kb_ROS$Feature)
-
-vip.K562.25kb.ROS <- ggplot(rfimpvars_K562_25kb_ROS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-```
-
-###RUS
-
-```{r}
-rfimpvars_gm12878_25kb_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_25kb_RUS <- rfimpvars_gm12878_25kb_RUS[1:10,]
-#rfimpvars_gm12878_25kb_RUS <- rfimpvars_gm12878_25kb_RUS[10:1,]
-rfimpvars_gm12878_25kb_RUS <- rfimpvars_gm12878_25kb_RUS[1:20,]
-rfimpvars_gm12878_25kb_RUS <- rfimpvars_gm12878_25kb_RUS[20:1,]
-
-rfimpvars_gm12878_25kb_RUS$Feature <- gsub("_dist","", rfimpvars_gm12878_25kb_RUS$Feature)
-
-rfimpvars_gm12878_25kb_RUS$Feature <- factor(rfimpvars_gm12878_25kb_RUS$Feature, levels=rfimpvars_gm12878_25kb_RUS$Feature)
-
-vip.gm12878.25kb.RUS <- ggplot(rfimpvars_gm12878_25kb_RUS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_25kb_RUS <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_25kb_RUS <- rfimpvars_K562_25kb_RUS[1:10,]
-#rfimpvars_K562_25kb_RUS <- rfimpvars_K562_25kb_RUS[10:1,]
-rfimpvars_K562_25kb_RUS <- rfimpvars_K562_25kb_RUS[1:20,]
-rfimpvars_K562_25kb_RUS <- rfimpvars_K562_25kb_RUS[20:1,]
-
-rfimpvars_K562_25kb_RUS$Feature <- gsub("_dist","", rfimpvars_K562_25kb_RUS$Feature)
-
-rfimpvars_K562_25kb_RUS$Feature <- factor(rfimpvars_K562_25kb_RUS$Feature, levels=rfimpvars_K562_25kb_RUS$Feature)
-
-vip.K562.25kb.RUS <- ggplot(rfimpvars_K562_25kb_RUS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-```
-
-###SMOTE
-
-```{r}
-rfimpvars_gm12878_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_25kb_SMOTE <- rfimpvars_gm12878_25kb_SMOTE[1:10,]
-#rfimpvars_gm12878_25kb_SMOTE <- rfimpvars_gm12878_25kb_SMOTE[10:1,]
-rfimpvars_gm12878_25kb_SMOTE <- rfimpvars_gm12878_25kb_SMOTE[1:20,]
-rfimpvars_gm12878_25kb_SMOTE <- rfimpvars_gm12878_25kb_SMOTE[20:1,]
-
-rfimpvars_gm12878_25kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_gm12878_25kb_SMOTE$Feature)
-
-rfimpvars_gm12878_25kb_SMOTE$Feature <- factor(rfimpvars_gm12878_25kb_SMOTE$Feature, levels=rfimpvars_gm12878_25kb_SMOTE$Feature)
-
-vip.gm12878.25kb.SMOTE <- ggplot(rfimpvars_gm12878_25kb_SMOTE, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_25kb_SMOTE <- rfimpvars_K562_25kb_SMOTE[1:10,]
-#rfimpvars_K562_25kb_SMOTE <- rfimpvars_K562_25kb_SMOTE[10:1,]
-rfimpvars_K562_25kb_SMOTE <- rfimpvars_K562_25kb_SMOTE[1:20,]
-rfimpvars_K562_25kb_SMOTE <- rfimpvars_K562_25kb_SMOTE[20:1,]
-
-rfimpvars_K562_25kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_K562_25kb_SMOTE$Feature)
-
-rfimpvars_K562_25kb_SMOTE$Feature <- factor(rfimpvars_K562_25kb_SMOTE$Feature, levels=rfimpvars_K562_25kb_SMOTE$Feature)
-
-vip.K562.25kb.SMOTE <- ggplot(rfimpvars_K562_25kb_SMOTE, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-```
-
-##50kb
-
-###None
-
-```{r}
-#GM12878
-rfimpvars_gm12878_50kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_50kb_none <- rfimpvars_gm12878_50kb_none[1:10,]
-#rfimpvars_gm12878_50kb_none <- rfimpvars_gm12878_50kb_none[10:1,]
-rfimpvars_gm12878_50kb_none <- rfimpvars_gm12878_50kb_none[1:20,]
-rfimpvars_gm12878_50kb_none <- rfimpvars_gm12878_50kb_none[20:1,]
-
-rfimpvars_gm12878_50kb_none$Feature <- gsub("_dist","", rfimpvars_gm12878_50kb_none$Feature)
-
-rfimpvars_gm12878_50kb_none$Feature <- factor(rfimpvars_gm12878_50kb_none$Feature, levels=rfimpvars_gm12878_50kb_none$Feature)
-
-vip.gm12878.50kb.none <- ggplot(rfimpvars_gm12878_50kb_none, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_50kb_none <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_50kb_none <- rfimpvars_K562_50kb_none[1:10,]
-#rfimpvars_K562_50kb_none <- rfimpvars_K562_50kb_none[10:1,]
-rfimpvars_K562_50kb_none <- rfimpvars_K562_50kb_none[1:20,]
-rfimpvars_K562_50kb_none <- rfimpvars_K562_50kb_none[20:1,]
-
-rfimpvars_K562_50kb_none$Feature <- gsub("_dist","", rfimpvars_K562_50kb_none$Feature)
-
-rfimpvars_K562_50kb_none$Feature <- factor(rfimpvars_K562_50kb_none$Feature, levels=rfimpvars_K562_50kb_none$Feature)
-
-vip.K562.50kb.none <- ggplot(rfimpvars_K562_50kb_none, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-```
-
-###ROS
-
-```{r}
-rfimpvars_gm12878_50kb_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_50kb_ROS <- rfimpvars_gm12878_50kb_ROS[1:10,]
-#rfimpvars_gm12878_50kb_ROS <- rfimpvars_gm12878_50kb_ROS[10:1,]
-rfimpvars_gm12878_50kb_ROS <- rfimpvars_gm12878_50kb_ROS[1:20,]
-rfimpvars_gm12878_50kb_ROS <- rfimpvars_gm12878_50kb_ROS[20:1,]
-
-rfimpvars_gm12878_50kb_ROS$Feature <- gsub("_dist","", rfimpvars_gm12878_50kb_ROS$Feature)
-
-rfimpvars_gm12878_50kb_ROS$Feature <- factor(rfimpvars_gm12878_50kb_ROS$Feature, levels=rfimpvars_gm12878_50kb_ROS$Feature)
-
-vip.gm12878.50kb.ROS <- ggplot(rfimpvars_gm12878_50kb_ROS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_50kb_ROS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_50kb_ROS <- rfimpvars_K562_50kb_ROS[1:10,]
-#rfimpvars_K562_50kb_ROS <- rfimpvars_K562_50kb_ROS[10:1,]
-rfimpvars_K562_50kb_ROS <- rfimpvars_K562_50kb_ROS[1:20,]
-rfimpvars_K562_50kb_ROS <- rfimpvars_K562_50kb_ROS[20:1,]
-
-rfimpvars_K562_50kb_ROS$Feature <- gsub("_dist","", rfimpvars_K562_50kb_ROS$Feature)
-
-rfimpvars_K562_50kb_ROS$Feature <- factor(rfimpvars_K562_50kb_ROS$Feature, levels=rfimpvars_K562_50kb_ROS$Feature)
-
-vip.K562.50kb.ROS <- ggplot(rfimpvars_K562_50kb_ROS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-```
-
-###RUS
-
-```{r}
-rfimpvars_gm12878_50kb_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_50kb_RUS <- rfimpvars_gm12878_50kb_RUS[1:10,]
-#rfimpvars_gm12878_50kb_RUS <- rfimpvars_gm12878_50kb_RUS[10:1,]
-rfimpvars_gm12878_50kb_RUS <- rfimpvars_gm12878_50kb_RUS[1:20,]
-rfimpvars_gm12878_50kb_RUS <- rfimpvars_gm12878_50kb_RUS[20:1,]
-
-rfimpvars_gm12878_50kb_RUS$Feature <- gsub("_dist","", rfimpvars_gm12878_50kb_RUS$Feature)
-
-rfimpvars_gm12878_50kb_RUS$Feature <- factor(rfimpvars_gm12878_50kb_RUS$Feature, levels=rfimpvars_gm12878_50kb_RUS$Feature)
-
-vip.gm12878.50kb.RUS <- ggplot(rfimpvars_gm12878_50kb_RUS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_50kb_RUS <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_50kb_RUS <- rfimpvars_K562_50kb_RUS[1:10,]
-#rfimpvars_K562_50kb_RUS <- rfimpvars_K562_50kb_RUS[10:1,]
-rfimpvars_K562_50kb_RUS <- rfimpvars_K562_50kb_RUS[1:20,]
-rfimpvars_K562_50kb_RUS <- rfimpvars_K562_50kb_RUS[20:1,]
-
-rfimpvars_K562_50kb_RUS$Feature <- gsub("_dist","", rfimpvars_K562_50kb_RUS$Feature)
-
-rfimpvars_K562_50kb_RUS$Feature <- factor(rfimpvars_K562_50kb_RUS$Feature, levels=rfimpvars_K562_50kb_RUS$Feature)
-
-vip.K562.50kb.RUS <- ggplot(rfimpvars_K562_50kb_RUS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-```
-
-###SMOTE
-
-```{r}
-rfimpvars_gm12878_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_50kb_SMOTE <- rfimpvars_gm12878_50kb_SMOTE[1:10,]
-#rfimpvars_gm12878_50kb_SMOTE <- rfimpvars_gm12878_50kb_SMOTE[10:1,]
-rfimpvars_gm12878_50kb_SMOTE <- rfimpvars_gm12878_50kb_SMOTE[1:20,]
-rfimpvars_gm12878_50kb_SMOTE <- rfimpvars_gm12878_50kb_SMOTE[20:1,]
-
-rfimpvars_gm12878_50kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_gm12878_50kb_SMOTE$Feature)
-
-rfimpvars_gm12878_50kb_SMOTE$Feature <- factor(rfimpvars_gm12878_50kb_SMOTE$Feature, levels=rfimpvars_gm12878_50kb_SMOTE$Feature)
-
-vip.gm12878.50kb.SMOTE <- ggplot(rfimpvars_gm12878_50kb_SMOTE, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_50kb_SMOTE <- rfimpvars_K562_50kb_SMOTE[1:10,]
-#rfimpvars_K562_50kb_SMOTE <- rfimpvars_K562_50kb_SMOTE[10:1,]
-rfimpvars_K562_50kb_SMOTE <- rfimpvars_K562_50kb_SMOTE[1:20,]
-rfimpvars_K562_50kb_SMOTE <- rfimpvars_K562_50kb_SMOTE[20:1,]
-
-rfimpvars_K562_50kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_K562_50kb_SMOTE$Feature)
-
-rfimpvars_K562_50kb_SMOTE$Feature <- factor(rfimpvars_K562_50kb_SMOTE$Feature, levels=rfimpvars_K562_50kb_SMOTE$Feature)
-
-vip.K562.50kb.SMOTE <- ggplot(rfimpvars_K562_50kb_SMOTE, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-```
-
-##100kb
-
-###None
-
-```{r}
-#GM12878
-rfimpvars_gm12878_100kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[1:10,]
-#rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[10:1,]
-rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[1:20,]
-rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[20:1,]
-#rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[19:1,]
-
-rfimpvars_gm12878_100kb_none$Feature <- gsub("_dist","", rfimpvars_gm12878_100kb_none$Feature)
-
-rfimpvars_gm12878_100kb_none$Feature <- factor(rfimpvars_gm12878_100kb_none$Feature, levels=rfimpvars_gm12878_100kb_none$Feature)
-
-vip.gm12878.100kb.none <- ggplot(rfimpvars_gm12878_100kb_none, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_100kb_none <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_100kb_none <- rfimpvars_K562_100kb_none[1:10,]
-#rfimpvars_K562_100kb_none <- rfimpvars_K562_100kb_none[10:1,]
-rfimpvars_K562_100kb_none <- rfimpvars_K562_100kb_none[1:20,]
-rfimpvars_K562_100kb_none <- rfimpvars_K562_100kb_none[20:1,]
-
-rfimpvars_K562_100kb_none$Feature <- gsub("_dist","", rfimpvars_K562_100kb_none$Feature)
-
-rfimpvars_K562_100kb_none$Feature <- factor(rfimpvars_K562_100kb_none$Feature, levels=rfimpvars_K562_100kb_none$Feature)
-
-vip.K562.100kb.none <- ggplot(rfimpvars_K562_100kb_none, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-```
-
-###ROS
-
-```{r}
-rfimpvars_gm12878_100kb_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_100kb_ROS <- rfimpvars_gm12878_100kb_ROS[1:10,]
-#rfimpvars_gm12878_100kb_ROS <- rfimpvars_gm12878_100kb_ROS[10:1,]
-rfimpvars_gm12878_100kb_ROS <- rfimpvars_gm12878_100kb_ROS[1:20,]
-rfimpvars_gm12878_100kb_ROS <- rfimpvars_gm12878_100kb_ROS[20:1,]
-
-rfimpvars_gm12878_100kb_ROS$Feature <- gsub("_dist","", rfimpvars_gm12878_100kb_ROS$Feature)
-
-rfimpvars_gm12878_100kb_ROS$Feature <- factor(rfimpvars_gm12878_100kb_ROS$Feature, levels=rfimpvars_gm12878_100kb_ROS$Feature)
-
-vip.gm12878.100kb.ROS <- ggplot(rfimpvars_gm12878_100kb_ROS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_100kb_ROS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_100kb_ROS <- rfimpvars_K562_100kb_ROS[1:10,]
-#rfimpvars_K562_100kb_ROS <- rfimpvars_K562_100kb_ROS[10:1,]
-rfimpvars_K562_100kb_ROS <- rfimpvars_K562_100kb_ROS[1:20,]
-rfimpvars_K562_100kb_ROS <- rfimpvars_K562_100kb_ROS[20:1,]
-
-rfimpvars_K562_100kb_ROS$Feature <- gsub("_dist","", rfimpvars_K562_100kb_ROS$Feature)
-
-rfimpvars_K562_100kb_ROS$Feature <- factor(rfimpvars_K562_100kb_ROS$Feature, levels=rfimpvars_K562_100kb_ROS$Feature)
-
-vip.K562.100kb.ROS <- ggplot(rfimpvars_K562_100kb_ROS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-```
-
-###RUS
-
-```{r}
-rfimpvars_gm12878_100kb_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_100kb_RUS <- rfimpvars_gm12878_100kb_RUS[1:10,]
-#rfimpvars_gm12878_100kb_RUS <- rfimpvars_gm12878_100kb_RUS[10:1,]
-rfimpvars_gm12878_100kb_RUS <- rfimpvars_gm12878_100kb_RUS[1:20,]
-rfimpvars_gm12878_100kb_RUS <- rfimpvars_gm12878_100kb_RUS[20:1,]
-
-rfimpvars_gm12878_100kb_RUS$Feature <- gsub("_dist","", rfimpvars_gm12878_100kb_RUS$Feature)
-
-rfimpvars_gm12878_100kb_RUS$Feature <- factor(rfimpvars_gm12878_100kb_RUS$Feature, levels=rfimpvars_gm12878_100kb_RUS$Feature)
-
-vip.gm12878.100kb.RUS <- ggplot(rfimpvars_gm12878_100kb_RUS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_100kb_RUS <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_100kb_RUS <- rfimpvars_K562_100kb_RUS[1:10,]
-#rfimpvars_K562_100kb_RUS <- rfimpvars_K562_100kb_RUS[10:1,]
-rfimpvars_K562_100kb_RUS <- rfimpvars_K562_100kb_RUS[1:20,]
-rfimpvars_K562_100kb_RUS <- rfimpvars_K562_100kb_RUS[20:1,]
-
-rfimpvars_K562_100kb_RUS$Feature <- gsub("_dist","", rfimpvars_K562_100kb_RUS$Feature)
-
-rfimpvars_K562_100kb_RUS$Feature <- factor(rfimpvars_K562_100kb_RUS$Feature, levels=rfimpvars_K562_100kb_RUS$Feature)
-
-vip.K562.100kb.RUS <- ggplot(rfimpvars_K562_100kb_RUS, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-```
-
-###SMOTE
-
-```{r}
-rfimpvars_gm12878_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_gm12878_100kb_SMOTE <- rfimpvars_gm12878_100kb_SMOTE[1:10,]
-#rfimpvars_gm12878_100kb_SMOTE <- rfimpvars_gm12878_100kb_SMOTE[10:1,]
-rfimpvars_gm12878_100kb_SMOTE <- rfimpvars_gm12878_100kb_SMOTE[1:20,]
-rfimpvars_gm12878_100kb_SMOTE <- rfimpvars_gm12878_100kb_SMOTE[20:1,]
-
-rfimpvars_gm12878_100kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_gm12878_100kb_SMOTE$Feature)
-
-rfimpvars_gm12878_100kb_SMOTE$Feature <- factor(rfimpvars_gm12878_100kb_SMOTE$Feature, levels=rfimpvars_gm12878_100kb_SMOTE$Feature)
-
-vip.gm12878.100kb.SMOTE <- ggplot(rfimpvars_gm12878_100kb_SMOTE, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-
-#K562
-rfimpvars_K562_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-#rfimpvars_K562_100kb_SMOTE <- rfimpvars_K562_100kb_SMOTE[1:10,]
-#rfimpvars_K562_100kb_SMOTE <- rfimpvars_K562_100kb_SMOTE[10:1,]
-rfimpvars_K562_100kb_SMOTE <- rfimpvars_K562_100kb_SMOTE[1:20,]
-rfimpvars_K562_100kb_SMOTE <- rfimpvars_K562_100kb_SMOTE[20:1,]
-
-rfimpvars_K562_100kb_SMOTE$Feature <- gsub("_dist","", rfimpvars_K562_100kb_SMOTE$Feature)
-
-rfimpvars_K562_100kb_SMOTE$Feature <- factor(rfimpvars_K562_100kb_SMOTE$Feature, levels=rfimpvars_K562_100kb_SMOTE$Feature)
-
-vip.K562.100kb.SMOTE <- ggplot(rfimpvars_K562_100kb_SMOTE, aes(x=Feature, y=Importance)) +
-  geom_bar(stat="identity", 
-           width=.5, 
-           position="dodge") +
-  coord_flip() +
-  theme_minimal()+
-  theme_bw()+
-  theme(axis.text.x = element_text(size=15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20))
-```
-
-## Combined
-
-```{r}
-ggarrange(vip.gm12878.10kb.SMOTE, vip.K562.10kb.SMOTE, ncol = 2, nrow = 1)
-```
-
-## Variable Importance Heatmaps for models with distance type predictors
-
-###SMOTE
-
-```{r}
-####GM12878
-
-rfimpvars_gm12878_10kb_SMOTE <- rfimpvars_gm12878_10kb_SMOTE[order(as.character(rfimpvars_gm12878_10kb_SMOTE$Feature)),]
-rfimpvars_gm12878_25kb_SMOTE <- rfimpvars_gm12878_25kb_SMOTE[order(as.character(rfimpvars_gm12878_25kb_SMOTE$Feature)),]
-rfimpvars_gm12878_50kb_SMOTE <- rfimpvars_gm12878_50kb_SMOTE[order(as.character(rfimpvars_gm12878_50kb_SMOTE$Feature)),]
-rfimpvars_gm12878_100kb_SMOTE <- rfimpvars_gm12878_100kb_SMOTE[order(as.character(rfimpvars_gm12878_100kb_SMOTE$Feature)),]
-
-unionannots <- union(rfimpvars_gm12878_10kb_SMOTE$Feature,
-                      union(rfimpvars_gm12878_25kb_SMOTE$Feature,
-                            union(rfimpvars_gm12878_50kb_SMOTE$Feature,rfimpvars_gm12878_100kb_SMOTE$Feature)))
-unionannots <- sort(unionannots)
-
-vim.gm12878.smote <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
-vim.gm12878.smote[which(rownames(vim.gm12878.smote) %in% rfimpvars_gm12878_10kb_SMOTE$Feature), 1] <- rfimpvars_gm12878_10kb_SMOTE$Importance
-vim.gm12878.smote[which(rownames(vim.gm12878.smote) %in% rfimpvars_gm12878_25kb_SMOTE$Feature), 2] <- rfimpvars_gm12878_25kb_SMOTE$Importance
-vim.gm12878.smote[which(rownames(vim.gm12878.smote) %in% rfimpvars_gm12878_50kb_SMOTE$Feature), 3] <- rfimpvars_gm12878_50kb_SMOTE$Importance
-vim.gm12878.smote[which(rownames(vim.gm12878.smote) %in% rfimpvars_gm12878_100kb_SMOTE$Feature), 4] <- rfimpvars_gm12878_100kb_SMOTE$Importance
-
-vim.gm12878.smote <- vim.gm12878.smote[order(vim.gm12878.smote[,1], decreasing = TRUE),]
-rownames(vim.gm12878.smote) <- gsub("`","",rownames(vim.gm12878.smote))
-
-vim.gm12878.smote.m <- melt(vim.gm12878.smote)
-vim.gm12878.smote.m$X1 <- factor(vim.gm12878.smote.m$X1, levels = rownames(vim.gm12878.smote))
-vim.gm12878.smote.m$X2 <- factor(vim.gm12878.smote.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
-
-ggplot(vim.gm12878.smote.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
-    geom_tile(aes(fill = value), 
-              colour = "white") + 
-    scale_fill_gradient2(low = "white", 
-                        high = "steelblue",
-                        na.value = "grey50",
-                        name="Variable \n Importance",
-                        limits = c(0,100),
-                        breaks = c(0,25,50,75, 100),
-                        labels = c("0", "25", "50", "75", "100")) +
-    theme_bw() +
-    theme_minimal() +
-    xlab("Resolution") +
-    ylab("Genomic Annotation") +
-    theme(#legend.position = c(.10, .10), 
-        #legend.justification = c(.10, .10),
-        #panel.border = element_rect(colour = "black", fill=NA),
-        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20) #,
-        #legend.background = element_rect(fill="white",
-        #                                 size=0.5, 
-        #                                 linetype="solid", 
-        #                                 colour ="black")
-        )
-
-####K562
-
-rfimpvars_K562_10kb_SMOTE <- rfimpvars_K562_10kb_SMOTE[order(as.character(rfimpvars_K562_10kb_SMOTE$Feature)),]
-rfimpvars_K562_25kb_SMOTE <- rfimpvars_K562_25kb_SMOTE[order(as.character(rfimpvars_K562_25kb_SMOTE$Feature)),]
-rfimpvars_K562_50kb_SMOTE <- rfimpvars_K562_50kb_SMOTE[order(as.character(rfimpvars_K562_50kb_SMOTE$Feature)),]
-rfimpvars_K562_100kb_SMOTE <- rfimpvars_K562_100kb_SMOTE[order(as.character(rfimpvars_K562_100kb_SMOTE$Feature)),]
-
-unionannots <- union(rfimpvars_K562_10kb_SMOTE$Feature,
-                      union(rfimpvars_K562_25kb_SMOTE$Feature,
-                            union(rfimpvars_K562_50kb_SMOTE$Feature,rfimpvars_K562_100kb_SMOTE$Feature)))
-unionannots <- sort(unionannots)
-
-vim.K562.smote <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
-vim.K562.smote[which(rownames(vim.K562.smote) %in% rfimpvars_K562_10kb_SMOTE$Feature), 1] <- rfimpvars_K562_10kb_SMOTE$Importance
-vim.K562.smote[which(rownames(vim.K562.smote) %in% rfimpvars_K562_25kb_SMOTE$Feature), 2] <- rfimpvars_K562_25kb_SMOTE$Importance
-vim.K562.smote[which(rownames(vim.K562.smote) %in% rfimpvars_K562_50kb_SMOTE$Feature), 3] <- rfimpvars_K562_50kb_SMOTE$Importance
-vim.K562.smote[which(rownames(vim.K562.smote) %in% rfimpvars_K562_100kb_SMOTE$Feature), 4] <- rfimpvars_K562_100kb_SMOTE$Importance
-
-vim.K562.smote <- vim.K562.smote[order(vim.K562.smote[,1], decreasing = TRUE),]
-rownames(vim.K562.smote) <- gsub("`","",rownames(vim.K562.smote))
-
-vim.K562.smote.m <- melt(vim.K562.smote)
-vim.K562.smote.m$X1 <- factor(vim.K562.smote.m$X1, levels = rownames(vim.K562.smote))
-vim.K562.smote.m$X2 <- factor(vim.K562.smote.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
-
-ggplot(vim.K562.smote.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
-    geom_tile(aes(fill = value), 
-              colour = "white") + 
-    scale_fill_gradient2(low = "white", 
-                        high = "steelblue",
-                        na.value = "grey50",
-                        name="Variable \n Importance",
-                        limits = c(0,100),
-                        breaks = c(0,25,50,75, 100),
-                        labels = c("0", "25", "50", "75", "100")) +
-    theme_bw() +
-    theme_minimal() +
-    xlab("Resolution") +
-    ylab("Genomic Annotation") +
-    theme(#legend.position = c(.10, .10), 
-        #legend.justification = c(.10, .10),
-        #panel.border = element_rect(colour = "black", fill=NA),
-        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20) #,
-        #legend.background = element_rect(fill="white",
-        #                                 size=0.5, 
-        #                                 linetype="solid", 
-        #                                 colour ="black")
-        )
-
-```
-
-###RUS
-
-```{r}
-####GM12878
-
-rfimpvars_gm12878_10kb_RUS <- rfimpvars_gm12878_10kb_RUS[order(as.character(rfimpvars_gm12878_10kb_RUS$Feature)),]
-rfimpvars_gm12878_25kb_RUS <- rfimpvars_gm12878_25kb_RUS[order(as.character(rfimpvars_gm12878_25kb_RUS$Feature)),]
-rfimpvars_gm12878_50kb_RUS <- rfimpvars_gm12878_50kb_RUS[order(as.character(rfimpvars_gm12878_50kb_RUS$Feature)),]
-rfimpvars_gm12878_100kb_RUS <- rfimpvars_gm12878_100kb_RUS[order(as.character(rfimpvars_gm12878_100kb_RUS$Feature)),]
-
-unionannots <- union(rfimpvars_gm12878_10kb_RUS$Feature,
-                      union(rfimpvars_gm12878_25kb_RUS$Feature,
-                            union(rfimpvars_gm12878_50kb_RUS$Feature,rfimpvars_gm12878_100kb_RUS$Feature)))
-unionannots <- sort(unionannots)
-
-vim.gm12878.RUS <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
-vim.gm12878.RUS[which(rownames(vim.gm12878.RUS) %in% rfimpvars_gm12878_10kb_RUS$Feature), 1] <- rfimpvars_gm12878_10kb_RUS$Importance
-vim.gm12878.RUS[which(rownames(vim.gm12878.RUS) %in% rfimpvars_gm12878_25kb_RUS$Feature), 2] <- rfimpvars_gm12878_25kb_RUS$Importance
-vim.gm12878.RUS[which(rownames(vim.gm12878.RUS) %in% rfimpvars_gm12878_50kb_RUS$Feature), 3] <- rfimpvars_gm12878_50kb_RUS$Importance
-vim.gm12878.RUS[which(rownames(vim.gm12878.RUS) %in% rfimpvars_gm12878_100kb_RUS$Feature), 4] <- rfimpvars_gm12878_100kb_RUS$Importance
-
-vim.gm12878.RUS <- vim.gm12878.RUS[order(vim.gm12878.RUS[,1], decreasing = TRUE),]
-rownames(vim.gm12878.RUS) <- gsub("`","",rownames(vim.gm12878.RUS))
-
-vim.gm12878.RUS.m <- melt(vim.gm12878.RUS)
-vim.gm12878.RUS.m$X1 <- factor(vim.gm12878.RUS.m$X1, levels = rownames(vim.gm12878.RUS))
-vim.gm12878.RUS.m$X2 <- factor(vim.gm12878.RUS.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
-
-ggplot(vim.gm12878.RUS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
-    geom_tile(aes(fill = value), 
-              colour = "white") + 
-    scale_fill_gradient2(low = "white", 
-                        high = "steelblue",
-                        na.value = "grey50",
-                        name="Variable \n Importance",
-                        limits = c(0,100),
-                        breaks = c(0,25,50,75, 100),
-                        labels = c("0", "25", "50", "75", "100")) +
-    theme_bw() +
-    theme_minimal() +
-    xlab("Resolution") +
-    ylab("Genomic Annotation") +
-    theme(#legend.position = c(.10, .10), 
-        #legend.justification = c(.10, .10),
-        #panel.border = element_rect(colour = "black", fill=NA),
-        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20) #,
-        #legend.background = element_rect(fill="white",
-        #                                 size=0.5, 
-        #                                 linetype="solid", 
-        #                                 colour ="black")
-        )
-
-####K562
-
-rfimpvars_K562_10kb_RUS <- rfimpvars_K562_10kb_RUS[order(as.character(rfimpvars_K562_10kb_RUS$Feature)),]
-rfimpvars_K562_25kb_RUS <- rfimpvars_K562_25kb_RUS[order(as.character(rfimpvars_K562_25kb_RUS$Feature)),]
-rfimpvars_K562_50kb_RUS <- rfimpvars_K562_50kb_RUS[order(as.character(rfimpvars_K562_50kb_RUS$Feature)),]
-rfimpvars_K562_100kb_RUS <- rfimpvars_K562_100kb_RUS[order(as.character(rfimpvars_K562_100kb_RUS$Feature)),]
-
-unionannots <- union(rfimpvars_K562_10kb_RUS$Feature,
-                      union(rfimpvars_K562_25kb_RUS$Feature,
-                            union(rfimpvars_K562_50kb_RUS$Feature,rfimpvars_K562_100kb_RUS$Feature)))
-unionannots <- sort(unionannots)
-
-vim.K562.RUS <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
-vim.K562.RUS[which(rownames(vim.K562.RUS) %in% rfimpvars_K562_10kb_RUS$Feature), 1] <- rfimpvars_K562_10kb_RUS$Importance
-vim.K562.RUS[which(rownames(vim.K562.RUS) %in% rfimpvars_K562_25kb_RUS$Feature), 2] <- rfimpvars_K562_25kb_RUS$Importance
-vim.K562.RUS[which(rownames(vim.K562.RUS) %in% rfimpvars_K562_50kb_RUS$Feature), 3] <- rfimpvars_K562_50kb_RUS$Importance
-vim.K562.RUS[which(rownames(vim.K562.RUS) %in% rfimpvars_K562_100kb_RUS$Feature), 4] <- rfimpvars_K562_100kb_RUS$Importance
-
-vim.K562.RUS <- vim.K562.RUS[order(vim.K562.RUS[,1], decreasing = TRUE),]
-rownames(vim.K562.RUS) <- gsub("`","",rownames(vim.K562.RUS))
-
-vim.K562.RUS.m <- melt(vim.K562.RUS)
-vim.K562.RUS.m$X1 <- factor(vim.K562.RUS.m$X1, levels = rownames(vim.K562.RUS))
-vim.K562.RUS.m$X2 <- factor(vim.K562.RUS.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
-
-ggplot(vim.K562.RUS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
-    geom_tile(aes(fill = value), 
-              colour = "white") + 
-    scale_fill_gradient2(low = "white", 
-                        high = "steelblue",
-                        na.value = "grey50",
-                        name="Variable \n Importance",
-                        limits = c(0,100),
-                        breaks = c(0,25,50,75, 100),
-                        labels = c("0", "25", "50", "75", "100")) +
-    theme_bw() +
-    theme_minimal() +
-    xlab("Resolution") +
-    ylab("Genomic Annotation") +
-    theme(#legend.position = c(.10, .10), 
-        #legend.justification = c(.10, .10),
-        #panel.border = element_rect(colour = "black", fill=NA),
-        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20) #,
-        #legend.background = element_rect(fill="white",
-        #                                 size=0.5, 
-        #                                 linetype="solid", 
-        #                                 colour ="black")
-        )
-
-```
-
-###ROS
-
-```{r}
-####GM12878
-
-rfimpvars_gm12878_10kb_ROS <- rfimpvars_gm12878_10kb_ROS[order(as.character(rfimpvars_gm12878_10kb_ROS$Feature)),]
-rfimpvars_gm12878_25kb_ROS <- rfimpvars_gm12878_25kb_ROS[order(as.character(rfimpvars_gm12878_25kb_ROS$Feature)),]
-rfimpvars_gm12878_50kb_ROS <- rfimpvars_gm12878_50kb_ROS[order(as.character(rfimpvars_gm12878_50kb_ROS$Feature)),]
-rfimpvars_gm12878_100kb_ROS <- rfimpvars_gm12878_100kb_ROS[order(as.character(rfimpvars_gm12878_100kb_ROS$Feature)),]
-
-unionannots <- union(rfimpvars_gm12878_10kb_ROS$Feature,
-                      union(rfimpvars_gm12878_25kb_ROS$Feature,
-                            union(rfimpvars_gm12878_50kb_ROS$Feature,rfimpvars_gm12878_100kb_ROS$Feature)))
-unionannots <- sort(unionannots)
-
-vim.gm12878.ROS <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
-vim.gm12878.ROS[which(rownames(vim.gm12878.ROS) %in% rfimpvars_gm12878_10kb_ROS$Feature), 1] <- rfimpvars_gm12878_10kb_ROS$Importance
-vim.gm12878.ROS[which(rownames(vim.gm12878.ROS) %in% rfimpvars_gm12878_25kb_ROS$Feature), 2] <- rfimpvars_gm12878_25kb_ROS$Importance
-vim.gm12878.ROS[which(rownames(vim.gm12878.ROS) %in% rfimpvars_gm12878_50kb_ROS$Feature), 3] <- rfimpvars_gm12878_50kb_ROS$Importance
-vim.gm12878.ROS[which(rownames(vim.gm12878.ROS) %in% rfimpvars_gm12878_100kb_ROS$Feature), 4] <- rfimpvars_gm12878_100kb_ROS$Importance
-
-vim.gm12878.ROS <- vim.gm12878.ROS[order(vim.gm12878.ROS[,1], decreasing = TRUE),]
-rownames(vim.gm12878.ROS) <- gsub("`","",rownames(vim.gm12878.ROS))
-
-vim.gm12878.ROS.m <- melt(vim.gm12878.ROS)
-vim.gm12878.ROS.m$X1 <- factor(vim.gm12878.ROS.m$X1, levels = rownames(vim.gm12878.ROS))
-vim.gm12878.ROS.m$X2 <- factor(vim.gm12878.ROS.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
-
-ggplot(vim.gm12878.ROS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
-    geom_tile(aes(fill = value), 
-              colour = "white") + 
-    scale_fill_gradient2(low = "white", 
-                        high = "steelblue",
-                        na.value = "grey50",
-                        name="Variable \n Importance",
-                        limits = c(0,100),
-                        breaks = c(0,25,50,75, 100),
-                        labels = c("0", "25", "50", "75", "100")) +
-    theme_bw() +
-    theme_minimal() +
-    xlab("Resolution") +
-    ylab("Genomic Annotation") +
-    theme(#legend.position = c(.10, .10), 
-        #legend.justification = c(.10, .10),
-        #panel.border = element_rect(colour = "black", fill=NA),
-        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20) #,
-        #legend.background = element_rect(fill="white",
-        #                                 size=0.5, 
-        #                                 linetype="solid", 
-        #                                 colour ="black")
-        )
-
-####K562
-
-rfimpvars_K562_10kb_ROS <- rfimpvars_K562_10kb_ROS[order(as.character(rfimpvars_K562_10kb_ROS$Feature)),]
-rfimpvars_K562_25kb_ROS <- rfimpvars_K562_25kb_ROS[order(as.character(rfimpvars_K562_25kb_ROS$Feature)),]
-rfimpvars_K562_50kb_ROS <- rfimpvars_K562_50kb_ROS[order(as.character(rfimpvars_K562_50kb_ROS$Feature)),]
-rfimpvars_K562_100kb_ROS <- rfimpvars_K562_100kb_ROS[order(as.character(rfimpvars_K562_100kb_ROS$Feature)),]
-
-unionannots <- union(rfimpvars_K562_10kb_ROS$Feature,
-                      union(rfimpvars_K562_25kb_ROS$Feature,
-                            union(rfimpvars_K562_50kb_ROS$Feature,rfimpvars_K562_100kb_ROS$Feature)))
-unionannots <- sort(unionannots)
-
-vim.K562.ROS <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
-vim.K562.ROS[which(rownames(vim.K562.ROS) %in% rfimpvars_K562_10kb_ROS$Feature), 1] <- rfimpvars_K562_10kb_ROS$Importance
-vim.K562.ROS[which(rownames(vim.K562.ROS) %in% rfimpvars_K562_25kb_ROS$Feature), 2] <- rfimpvars_K562_25kb_ROS$Importance
-vim.K562.ROS[which(rownames(vim.K562.ROS) %in% rfimpvars_K562_50kb_ROS$Feature), 3] <- rfimpvars_K562_50kb_ROS$Importance
-vim.K562.ROS[which(rownames(vim.K562.ROS) %in% rfimpvars_K562_100kb_ROS$Feature), 4] <- rfimpvars_K562_100kb_ROS$Importance
-
-vim.K562.ROS <- vim.K562.ROS[order(vim.K562.ROS[,1], decreasing = TRUE),]
-rownames(vim.K562.ROS) <- gsub("`","",rownames(vim.K562.ROS))
-
-vim.K562.ROS.m <- melt(vim.K562.ROS)
-vim.K562.ROS.m$X1 <- factor(vim.K562.ROS.m$X1, levels = rownames(vim.K562.ROS))
-vim.K562.ROS.m$X2 <- factor(vim.K562.ROS.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
-
-ggplot(vim.K562.ROS.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
-    geom_tile(aes(fill = value), 
-              colour = "white") + 
-    scale_fill_gradient2(low = "white", 
-                        high = "steelblue",
-                        na.value = "grey50",
-                        name="Variable \n Importance",
-                        limits = c(0,100),
-                        breaks = c(0,25,50,75, 100),
-                        labels = c("0", "25", "50", "75", "100")) +
-    theme_bw() +
-    theme_minimal() +
-    xlab("Resolution") +
-    ylab("Genomic Annotation") +
-    theme(#legend.position = c(.10, .10), 
-        #legend.justification = c(.10, .10),
-        #panel.border = element_rect(colour = "black", fill=NA),
-        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20) #,
-        #legend.background = element_rect(fill="white",
-        #                                 size=0.5, 
-        #                                 linetype="solid", 
-        #                                 colour ="black")
-        )
-
-```
-
-###None
-
-```{r}
-####GM12878
-
-rfimpvars_gm12878_10kb_none <- rfimpvars_gm12878_10kb_none[order(as.character(rfimpvars_gm12878_10kb_none$Feature)),]
-rfimpvars_gm12878_25kb_none <- rfimpvars_gm12878_25kb_none[order(as.character(rfimpvars_gm12878_25kb_none$Feature)),]
-rfimpvars_gm12878_50kb_none <- rfimpvars_gm12878_50kb_none[order(as.character(rfimpvars_gm12878_50kb_none$Feature)),]
-#rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[-which(is.na(rfimpvars_gm12878_100kb_none$Importance)),]
-rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[order(as.character(rfimpvars_gm12878_100kb_none$Feature)),]
-
-unionannots <- union(rfimpvars_gm12878_10kb_none$Feature,
-                      union(rfimpvars_gm12878_25kb_none$Feature,
-                            union(rfimpvars_gm12878_50kb_none$Feature,rfimpvars_gm12878_100kb_none$Feature)))
-unionannots <- sort(unionannots)
-
-vim.gm12878.none <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
-vim.gm12878.none[which(rownames(vim.gm12878.none) %in% rfimpvars_gm12878_10kb_none$Feature), 1] <- rfimpvars_gm12878_10kb_none$Importance
-vim.gm12878.none[which(rownames(vim.gm12878.none) %in% rfimpvars_gm12878_25kb_none$Feature), 2] <- rfimpvars_gm12878_25kb_none$Importance
-vim.gm12878.none[which(rownames(vim.gm12878.none) %in% rfimpvars_gm12878_50kb_none$Feature), 3] <- rfimpvars_gm12878_50kb_none$Importance
-vim.gm12878.none[which(rownames(vim.gm12878.none) %in% rfimpvars_gm12878_100kb_none$Feature), 4] <- rfimpvars_gm12878_100kb_none$Importance
-
-vim.gm12878.none <- vim.gm12878.none[order(vim.gm12878.none[,1], decreasing = TRUE),]
-rownames(vim.gm12878.none) <- gsub("`","",rownames(vim.gm12878.none))
-
-vim.gm12878.none.m <- melt(vim.gm12878.none)
-vim.gm12878.none.m$X1 <- factor(vim.gm12878.none.m$X1, levels = rownames(vim.gm12878.none))
-vim.gm12878.none.m$X2 <- factor(vim.gm12878.none.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
-
-ggplot(vim.gm12878.none.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
-    geom_tile(aes(fill = value), 
-              colour = "white") + 
-    scale_fill_gradient2(low = "white", 
-                        high = "steelblue",
-                        na.value = "grey50",
-                        name="Variable \n Importance",
-                        limits = c(0,100),
-                        breaks = c(0,25,50,75, 100),
-                        labels = c("0", "25", "50", "75", "100")) +
-    theme_bw() +
-    theme_minimal() +
-    xlab("Resolution") +
-    ylab("Genomic Annotation") +
-    theme(#legend.position = c(.10, .10), 
-        #legend.justification = c(.10, .10),
-        #panel.border = element_rect(colour = "black", fill=NA),
-        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20) #,
-        #legend.background = element_rect(fill="white",
-        #                                 size=0.5, 
-        #                                 linetype="solid", 
-        #                                 colour ="black")
-        )
-
-####K562
-
-rfimpvars_K562_10kb_none <- rfimpvars_K562_10kb_none[order(as.character(rfimpvars_K562_10kb_none$Feature)),]
-rfimpvars_K562_25kb_none <- rfimpvars_K562_25kb_none[order(as.character(rfimpvars_K562_25kb_none$Feature)),]
-rfimpvars_K562_50kb_none <- rfimpvars_K562_50kb_none[order(as.character(rfimpvars_K562_50kb_none$Feature)),]
-rfimpvars_K562_100kb_none <- rfimpvars_K562_100kb_none[order(as.character(rfimpvars_K562_100kb_none$Feature)),]
-
-unionannots <- union(rfimpvars_K562_10kb_none$Feature,
-                      union(rfimpvars_K562_25kb_none$Feature,
-                            union(rfimpvars_K562_50kb_none$Feature,rfimpvars_K562_100kb_none$Feature)))
-unionannots <- sort(unionannots)
-
-vim.K562.none <- matrix(ncol=4, nrow=length(unionannots), dimnames=list(unionannots, c("10 kb", "25 kb", "50 kb", "100 kb")))
-vim.K562.none[which(rownames(vim.K562.none) %in% rfimpvars_K562_10kb_none$Feature), 1] <- rfimpvars_K562_10kb_none$Importance
-vim.K562.none[which(rownames(vim.K562.none) %in% rfimpvars_K562_25kb_none$Feature), 2] <- rfimpvars_K562_25kb_none$Importance
-vim.K562.none[which(rownames(vim.K562.none) %in% rfimpvars_K562_50kb_none$Feature), 3] <- rfimpvars_K562_50kb_none$Importance
-vim.K562.none[which(rownames(vim.K562.none) %in% rfimpvars_K562_100kb_none$Feature), 4] <- rfimpvars_K562_100kb_none$Importance
-
-vim.K562.none <- vim.K562.none[order(vim.K562.none[,1], decreasing = TRUE),]
-rownames(vim.K562.none) <- gsub("`","",rownames(vim.K562.none))
-
-vim.K562.none.m <- melt(vim.K562.none)
-vim.K562.none.m$X1 <- factor(vim.K562.none.m$X1, levels = rownames(vim.K562.none))
-vim.K562.none.m$X2 <- factor(vim.K562.none.m$X2, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
-
-ggplot(vim.K562.none.m, aes(x=X2, y=ordered(X1, levels=rev(levels(X1))))) + 
-    geom_tile(aes(fill = value), 
-              colour = "white") + 
-    scale_fill_gradient2(low = "white", 
-                        high = "steelblue",
-                        na.value = "grey50",
-                        name="Variable \n Importance",
-                        limits = c(0,100),
-                        breaks = c(0,25,50,75, 100),
-                        labels = c("0", "25", "50", "75", "100")) +
-    theme_bw() +
-    theme_minimal() +
-    xlab("Resolution") +
-    ylab("Genomic Annotation") +
-    theme(#legend.position = c(.10, .10), 
-        #legend.justification = c(.10, .10),
-        #panel.border = element_rect(colour = "black", fill=NA),
-        axis.text.x = element_text(size=15, angle = 45, hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20) #,
-        #legend.background = element_rect(fill="white",
-        #                                 size=0.5, 
-        #                                 linetype="solid", 
-        #                                 colour ="black")
-        )
-
-```
-
-##Plots
-
-```{r}
-figure <- ggarrange(p1,p2,ncol=2,nrow=1,common.legend = TRUE, legend = "right", labels="AUTO")
-figure
-annotate_figure(figure,
-    bottom = text_grob("Resolution", color = "black", size = 20),
-    left = text_grob("Genomic Annotation", color = "black", rot = 90, size=20)
-)
-
-figure <- ggarrange(p3,p4,ncol=2,nrow=1,common.legend = TRUE, legend = "right", labels="AUTO")
-figure
-annotate_figure(figure,
-    bottom = text_grob("Resolution", color = "black", size = 20),
-    left = text_grob("Genomic Annotation", color = "black", rot = 90, size=20)
-)
-
-figure <- ggarrange(p5,p6,ncol=2,nrow=1,common.legend = TRUE, legend = "right", labels="AUTO")
-figure
-annotate_figure(figure,
-    bottom = text_grob("Resolution", color = "black", size = 20),
-    left = text_grob("Genomic Annotation", color = "black", rot = 90, size=20)
-)
-
-figure <- ggarrange(p7,p8,ncol=2,nrow=1,common.legend = TRUE, legend = "right", labels="AUTO")
-figure
-annotate_figure(figure,
-    bottom = text_grob("Resolution", color = "black", size = 20),
-    left = text_grob("Genomic Annotation", color = "black", rot = 90, size=20)
-)
-
-```
-
 ## Variable Importance Heatmaps for models with distance type predictors (Ranks)
@@
 colnames(rankdata) <- c("10 kb", "25 kb", "50 kb", "100 kb")	 			  
+rankdata <- rankdata[order(rankdata[,1], decreasing = FALSE),]
+rankdata <- rankdata[1:20,]
 
 #my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100)) 
-my_palette <- colorRampPalette(c("red", "white"))(nrow(rankdata))
+my_palette <- colorRampPalette(c("red", "pink", "white"))(nrow(rankdata))
 heatmap.2(t(rankdata),
@@
           trace="none",         # turns off trace lines inside the heat map
-          #margins =c(5,5),     # widens margins around plot
+          margins=c(12,8),     # widens margins around plot
           col=my_palette,       # use on color palette defined earlier
@@
           key=FALSE,
-          #key.title = "Elastic-Net\nCoefficient",
-          #keysize = 2,
-          dendrogram="both",     # only draw a row dendrogram,
-          Rowv = TRUE,
+          #keysize = 1.5,
+          #key.title = "Elastic-Net Coefficient",
+          dendrogram="column",     # only draw a row dendrogram,
+          Rowv = FALSE,
           Colv = TRUE,
           cexRow=1.5,
-          cexCol=0.5,
+          cexCol=1.5,
           #labRow = FALSE,
@@
 
-# ICC
+## Average Variable Importances Heatmaps for models with distance type predictors (Ranks)
+
+```{r}
+#gm12878 
+##average then rank
+vim.gm12878.smote[is.na(vim.gm12878.smote)] <- 0
+
+vim.gm12878.smote.ave.rank <- data.frame(Feature=vim.gm12878.smote$Feature,
+                                    AveImp=rowMeans(vim.gm12878.smote[,-1]))
+vim.gm12878.smote.ave.rank$Rank <- rank(-vim.gm12878.smote.ave.rank$AveImp, na.last = TRUE)
+vim.gm12878.smote.ave.rank <- vim.gm12878.smote.ave.rank[order(vim.gm12878.smote.ave.rank$Rank, decreasing = FALSE),]
+rankdata.a.r <- cbind(vim.gm12878.smote.ave.rank$Rank,vim.gm12878.smote.ave.rank$Rank)
+rankdata.a.r <- rankdata.a.r[1:20,]
+rownames(rankdata.a.r) <- vim.gm12878.smote.ave.rank$Feature[1:20]
+
+#my_palette <- colorRampPalette(c("red", "white"))(100)
+my_palette_rank <- colorRampPalette(c("red", "white"))(nrow(rankdata.a.r))
+heatmap.2(t(rankdata.a.r),
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          labRow = "",
+          labCol = rownames(rankdata.a.r),
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins=c(12,8),     # widens margins around plot
+          col=my_palette_rank,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 2,
+          dendrogram="none",     # only draw a row dendrogram,
+          Rowv = NA,
+          Colv = NA,
+          cexRow=1.5,
+          cexCol=1.5,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #lwid=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          rowsep=c(0,2),
+          colsep=0:nrow(rankdata.a.r)
+          )
+
+##rank then average
+vim.gm12878.smote.rank.ave <- cbind(Rank.10kb=rank(-vim.gm12878.smote$Importance.10kb, na.last = TRUE),
+                                    Rank.25kb=rank(-vim.gm12878.smote$Importance.25kb, na.last = TRUE),
+                                    Rank.50kb=rank(-vim.gm12878.smote$Importance.50kb, na.last = TRUE),
+                                    Rank.100kb=rank(-vim.gm12878.smote$Importance.100kb, na.last = TRUE))
+rownames(vim.gm12878.smote.rank.ave) <- vim.gm12878.smote$Feature
+rankdata.r.a <- rowMeans(vim.gm12878.smote.rank.ave)
+rankdata.r.a <- rankdata.r.a[order(rankdata.r.a, decreasing = FALSE)]
+rankdata.r.a <- rankdata.r.a[1:20]
+rankdata.r.a <- cbind(rankdata.r.a,rankdata.r.a)
+heatmap.2(t(rankdata.r.a),
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          labRow = "",
+          labCol = rownames(rankdata.r.a),
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins=c(12,8),     # widens margins around plot
+          col=my_palette_rank,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #key.title = "Elastic-Net\nCoefficient",
+          #keysize = 2,
+          dendrogram="none",     # only draw a row dendrogram,
+          Rowv = NA,
+          Colv = NA,
+          cexRow=1.5,
+          cexCol=1.5,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          #lwid=c(.5,6,0),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black",
+          rowsep=c(0,2),
+          colsep=0:nrow(rankdata.r.a)
+          )
+
+```
+
+## ICC
 

### 2019-04-11 Scripts/distribution_of_tads.Rmd
added script to plot distribution of tads and create table

---
title: "Distribution of TADs"
author: "Spiro Stilianoudakis"
date: "April 10, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

# GM12878

## 10kb

```{r}
tad_gm12878_10kb <- read.table("Z:/TAD_data_analysis/GM12878/10kb/GM12878_domain_data_10000.b.txt")
tad_gm12878_10kb <- tad_gm12878_10kb[,1:3]

tad_gm12878_10kb <- tad_gm12878_10kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)

tad_gm12878_10kb$V1 <- factor(tad_gm12878_10kb$V1, levels = c(1:22))

tad_data <- tad_gm12878_10kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

gm12878_10kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

gm12878_10kb_tabdist <- ggplot(tad_gm12878_10kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

## 25kb

```{r}
tad_gm12878_25kb <- read.table("Z:/TAD_data_analysis/GM12878/25kb/GM12878_domain_data_25000.b.txt")
tad_gm12878_25kb <- tad_gm12878_25kb[,1:3]

tad_gm12878_25kb <- tad_gm12878_25kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)

tad_gm12878_25kb$V1 <- factor(tad_gm12878_25kb$V1, levels = c(1:22))

tad_data <- tad_gm12878_25kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

gm12878_25kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

gm12878_25kb_tabdist <- ggplot(tad_gm12878_25kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

## 50kb

```{r}
tad_gm12878_50kb <- read.table("Z:/TAD_data_analysis/GM12878/50kb/GM12878_domain_data_50000.b.txt")
tad_gm12878_50kb <- tad_gm12878_50kb[,1:3]

tad_gm12878_50kb <- tad_gm12878_50kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)

tad_gm12878_50kb$V1 <- factor(tad_gm12878_50kb$V1, levels = c(1:22))

tad_data <- tad_gm12878_50kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

gm12878_50kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

gm12878_50kb_tabdist <- ggplot(tad_gm12878_50kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

## 100kb

```{r}
tad_gm12878_100kb <- read.table("Z:/TAD_data_analysis/GM12878/100kb/GM12878_domain_data_100000.b.txt")
tad_gm12878_100kb <- tad_gm12878_100kb[,1:3]

tad_gm12878_100kb <- tad_gm12878_100kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)

tad_gm12878_100kb$V1 <- factor(tad_gm12878_100kb$V1, levels = c(1:22))

tad_data <- tad_gm12878_100kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

gm12878_100kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

gm12878_100kb_tabdist <- ggplot(tad_gm12878_100kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

# K562

## 10kb

```{r}
tad_K562_10kb <- read.table("Z:/TAD_data_analysis/K562/10kb/K562_domain_data_10000.b.txt")
tad_K562_10kb <- tad_K562_10kb[,1:3]

tad_K562_10kb <- tad_K562_10kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)

tad_K562_10kb$V1 <- factor(tad_K562_10kb$V1, levels = c(1:22))

tad_data <- tad_K562_10kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

K562_10kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

K562_10kb_tabdist <- ggplot(tad_K562_10kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

## 25kb

```{r}
tad_K562_25kb <- read.table("Z:/TAD_data_analysis/K562/25kb/K562_domain_data_25000.b.txt")
tad_K562_25kb <- tad_K562_25kb[,1:3]

tad_K562_25kb <- tad_K562_25kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)

tad_K562_25kb$V1 <- factor(tad_K562_25kb$V1, levels = c(1:22))

tad_data <- tad_K562_25kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

K562_25kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

K562_25kb_tabdist <- ggplot(tad_K562_25kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

## 50kb

```{r}
tad_K562_50kb <- read.table("Z:/TAD_data_analysis/K562/50kb/K562_domain_data_50000.b.txt")
tad_K562_50kb <- tad_K562_50kb[,1:3]

tad_K562_50kb <- tad_K562_50kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)

tad_K562_50kb$V1 <- factor(tad_K562_50kb$V1, levels = c(1:22))

tad_data <- tad_K562_50kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

K562_50kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

K562_50kb_tabdist <- ggplot(tad_K562_50kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

## 100kb

```{r}
tad_K562_100kb <- read.table("Z:/TAD_data_analysis/K562/100kb/K562_domain_data_100000.b.txt")
tad_K562_100kb <- tad_K562_100kb[,1:3]

tad_K562_100kb <- tad_K562_100kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)

tad_K562_100kb$V1 <- factor(tad_K562_100kb$V1, levels = c(1:22))

tad_data <- tad_K562_100kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))

K562_100kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Chromosome") +
  guides(fill=FALSE) +
  ylab("Number of TADs") +
  xlab("Chromosome") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

K562_100kb_tabdist <- ggplot(tad_K562_100kb, aes(x=Length, color=V1)) +
  geom_density() +
  scale_color_discrete(name="Chromosome") +
  ylab("Count") +
  xlab("Length of TAD") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

# Plots

```{r}
figure <- ggarrange(gm12878_10kb_tabnum,gm12878_10kb_tabdist,
                    gm12878_25kb_tabnum,gm12878_25kb_tabdist,
                    gm12878_50kb_tabnum,gm12878_50kb_tabdist,
                    gm12878_100kb_tabnum,gm12878_100kb_tabdist,
                    ncol=2,nrow=4,
                    common.legend = TRUE,
                    legend="right",
                    labels = c("A", "","B", "","C", "","D", ""),
                    font.label = list(size=20))

figure <- ggarrange(K562_10kb_tabnum,K562_10kb_tabdist,
                    K562_25kb_tabnum,K562_25kb_tabdist,
                    K562_50kb_tabnum,K562_50kb_tabdist,
                    K562_100kb_tabnum,K562_100kb_tabdist,
                    ncol=2,nrow=4,
                    common.legend = TRUE,
                    legend="right",
                    labels = "AUTO",
                    font.label = list(size=20))
```

# Creating Table of Summaraies

```{r}
tad_gm12878_10kb$CL <- "GM12878"
tad_gm12878_25kb$CL <- "GM12878"
tad_gm12878_50kb$CL <- "GM12878"
tad_gm12878_100kb$CL <- "GM12878"
tad_K562_10kb$CL <- "K562"
tad_K562_25kb$CL <- "K562"
tad_K562_50kb$CL <- "K562"
tad_K562_100kb$CL <- "K562"

tad_data_summaries <- rbind.data.frame(aggregate(tad_gm12878_10kb$Length, by=list(tad_gm12878_10kb$V1), FUN=summary),
                 aggregate(tad_gm12878_25kb$Length, by=list(tad_gm12878_25kb$V1), FUN=summary),
                 aggregate(tad_gm12878_50kb$Length, by=list(tad_gm12878_50kb$V1), FUN=summary),
                 aggregate(tad_gm12878_100kb$Length, by=list(tad_gm12878_100kb$V1), FUN=summary),
                 aggregate(tad_K562_10kb$Length, by=list(tad_K562_10kb$V1), FUN=summary),
                 aggregate(tad_K562_25kb$Length, by=list(tad_K562_25kb$V1), FUN=summary),
                 aggregate(tad_K562_50kb$Length, by=list(tad_K562_50kb$V1), FUN=summary),
                 aggregate(tad_K562_100kb$Length, by=list(tad_K562_100kb$V1), FUN=summary))

#chr 9 for k562 at 10 kb has no tad boundaries

tad_data_summaries$CL <- c(rep("GM12878", 22*4), rep("K562", 22*4-1))
tad_data_summaries$Resolution <- c(rep("10 kb", 22),rep("25 kb", 22),rep("50 kb", 22),rep("100 kb", 22),
                                   rep("10 kb", 21),rep("25 kb", 22),rep("50 kb", 22),rep("100 kb", 22))

write.csv(tad_data_summaries, "C:/Users/stili/Downloads/tad_data_summaries.csv")
```

### 2019-04-12 Scripts/comparing_tfbs_specific_models_with_all_annotations.Rmd
script for comparing tfbs specific models with models containing all annotations (at 10 kb)

---
title: "Investigating TFBS Specific Model Performances"
author: "Spiro Stilianoudakis"
date: "April 11, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

# TFBS Specific Model Performances

## GM12878

### 10 kb

```{r}
#OC
##None
rfperf_gm12878_10kb_none_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/tfbs/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_10kb_none_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/tfbs/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_10kb_none_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/tfbs/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_gm12878_10kb_ros_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/tfbs/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_gm12878_10kb_ros_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/tfbs/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_gm12878_10kb_ros_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/tfbs/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_gm12878_10kb_rus_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/tfbs/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_gm12878_10kb_rus_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/tfbs/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_gm12878_10kb_rus_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/tfbs/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_gm12878_10kb_smote_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/tfbs/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_gm12878_10kb_smote_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/tfbs/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_gm12878_10kb_smote_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/tfbs/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878_tfbs <- data.frame(Resampling=rep(c(rep("None",3),
                                                    rep("ROS",3),
                                                    rep("RUS",3),
                                                    rep("SMOTE",3)),2),
                                       Predictor=rep(c("OC","OP","Distance"),8),
                                       Metric=c(rep("F1-Score",12), 
                                                rep("MCC",12)),
                                       Annotations=rep("TFBS Only",24)
                                       )

all_rfperfs_gm12878_tfbs$Predictor <- factor(all_rfperfs_gm12878_tfbs$Predictor, levels=c("OC", "OP", "Distance"))
all_rfperfs_gm12878_tfbs$Metric <- factor(all_rfperfs_gm12878_tfbs$Metric, levels=c("F1-Score", "MCC"))
all_rfperfs_gm12878_tfbs$Resampling <- factor(all_rfperfs_gm12878_tfbs$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))

all_rfperfs_gm12878_tfbs$Performance <- c(rfperf_gm12878_10kb_none_oc_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_none_op_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_none_dist_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_ros_oc_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_ros_op_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_ros_dist_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_rus_oc_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_rus_op_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_rus_dist_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_smote_oc_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_smote_op_tfbs[16,2], #f1
                                          rfperf_gm12878_10kb_smote_dist_tfbs[16,2], #f1

                                     rfperf_gm12878_10kb_none_oc_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_none_op_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_none_dist_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_ros_oc_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_ros_op_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_ros_dist_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_rus_oc_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_rus_op_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_rus_dist_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_smote_oc_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_smote_op_tfbs[15,2], #mcc
                                          rfperf_gm12878_10kb_smote_dist_tfbs[15,2] #mcc

                                     )

```

# All Annotations

## GM12878

### 10 kb

```{r}
#OC
##None
rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

#OC
##ROS
rfperf_gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

#OP
##ROS
rfperf_gm12878_10kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

#Distance
##ROS
rfperf_gm12878_10kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

#OC
##RUS
rfperf_gm12878_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

#OP
##RUS
rfperf_gm12878_10kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

#Distance
##RUS
rfperf_gm12878_10kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

#OC
##SMOTE
rfperf_gm12878_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##SMOTE
rfperf_gm12878_10kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##SMOTE
rfperf_gm12878_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878 <- data.frame(Resampling=rep(c(rep("None",3),
                                                    rep("ROS",3),
                                                    rep("RUS",3),
                                                    rep("SMOTE",3)),2),
                                       Predictor=rep(c("OC","OP","Distance"),8),
                                       Metric=c(rep("F1-Score",12), 
                                                rep("MCC",12)),
                                       Annotations=rep("ALL Types",24)
                                       )

all_rfperfs_gm12878$Predictor <- factor(all_rfperfs_gm12878$Predictor, levels=c("OC", "OP", "Distance"))
all_rfperfs_gm12878$Metric <- factor(all_rfperfs_gm12878$Metric, levels=c("F1-Score", "MCC"))
all_rfperfs_gm12878$Resampling <- factor(all_rfperfs_gm12878$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))

all_rfperfs_gm12878$Performance <- c(rfperf_gm12878_10kb_none_oc[16,2], #f1
                                          rfperf_gm12878_10kb_none_op[16,2], #f1
                                          rfperf_gm12878_10kb_none_dist[16,2], #f1
                                          rfperf_gm12878_10kb_ros_oc[16,2], #f1
                                          rfperf_gm12878_10kb_ros_op[16,2], #f1
                                          rfperf_gm12878_10kb_ros_dist[16,2], #f1
                                          rfperf_gm12878_10kb_rus_oc[16,2], #f1
                                          rfperf_gm12878_10kb_rus_op[16,2], #f1
                                          rfperf_gm12878_10kb_rus_dist[16,2], #f1
                                          rfperf_gm12878_10kb_smote_oc[16,2], #f1
                                          rfperf_gm12878_10kb_smote_op[16,2], #f1
                                          rfperf_gm12878_10kb_smote_dist[16,2], #f1

                                     rfperf_gm12878_10kb_none_oc[15,2], #mcc
                                          rfperf_gm12878_10kb_none_op[15,2], #mcc
                                          rfperf_gm12878_10kb_none_dist[15,2], #mcc
                                          rfperf_gm12878_10kb_ros_oc[15,2], #mcc
                                          rfperf_gm12878_10kb_ros_op[15,2], #mcc
                                          rfperf_gm12878_10kb_ros_dist[15,2], #mcc
                                          rfperf_gm12878_10kb_rus_oc[15,2], #mcc
                                          rfperf_gm12878_10kb_rus_op[15,2], #mcc
                                          rfperf_gm12878_10kb_rus_dist[15,2], #mcc
                                          rfperf_gm12878_10kb_smote_oc[15,2], #mcc
                                          rfperf_gm12878_10kb_smote_op[15,2], #mcc
                                          rfperf_gm12878_10kb_smote_dist[15,2] #mcc

                                     )

```

# Plots

## Comparing 10 kb

```{r}
all_rfperfs_gm12878_allvtfbs <- rbind.data.frame(all_rfperfs_gm12878,all_rfperfs_gm12878_tfbs)
all_rfperfs_gm12878_allvtfbs$Annotations <- factor(all_rfperfs_gm12878_allvtfbs$Annotations, levels=c("ALL Types", "TFBS Only"))

ggplot(all_rfperfs_gm12878_allvtfbs,
       aes(x=Resampling, y=Performance, fill=Annotations)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid( ~ Predictor + Metric) +
  #xlab("") + ylab("") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Feature Space")+
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))
```

### 2019-04-12 Scripts/investigating_misclassified_TADs.Rmd
script to investigate misclassified tads for best model

---
title: "Determining what makes some TADs unpredictable"
author: "Spiro Stilianoudakis"
date: "April 11, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

# Evaluating Missclassified TAD boundaries from best performing model

## SMOTE; distance-type predictors

### GM12878

####10kb

```{r}
#reading in test data and reducing
test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
names(test) <- gsub(paste(c("`", 
                            "Gm12878", 
                            "-", 
                            #"_", 
                            #"dist", "count", "perc",
                            "Haib", 
                            "Sydh",
                            "Uta",
                            "Uw",
                            "Broad",
                            "Uchicago"), collapse = "|"), "", names(test))
enetcoefs <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
test <- test[,c(1,which(names(test) %in% enetcoefs))]

#reading in model and making predictions
rfmodel_gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfModel.rds")
predictions <- predict(rfmodel_gm12878_10kb, newdata=test)
preddata <- cbind.data.frame(Prediction = predictions, True=test$y)

#subset the false negatives (bins that were predicted as not overlapping with flanked TAD boundary but really were)
FNdata <- test[which(preddata$Prediction=="No" & preddata$True=="Yes"),]
FNdatamelt <- melt(FNdata[,-1])
FNdatamelt$Prediction <- "False Negatives"

#subset the true positives (bins that were predicted as overlapping with flanked TAD boundary and truely were)
TPdata <- test[which(preddata$Prediction=="Yes" & preddata$True=="Yes"),]
TPdatamelt <- melt(TPdata[,-1])
TPdatamelt$Prediction <- "True Positives"

predictiondata_gm12878_10kb <- rbind.data.frame(FNdatamelt,TPdatamelt)
predictiondata_gm12878_10kb$Prediction <- factor(predictiondata_gm12878_10kb$Prediction, levels=c("False Negatives","True Positives"))

ggplot(predictiondata_gm12878_10kb, aes(x=value, color=Prediction)) +
  geom_density() +
  scale_color_discrete(name="Prediction Class") +
  ylab("Frequency") +
  xlab("Log2 Distance") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#looking at specific annotations
##Ctcf
ggplot(predictiondata_gm12878_10kb[grep("Ctcf_dist",predictiondata_gm12878_10kb$variable),], aes(x=value, color=Prediction)) +
  geom_density() +
  scale_color_discrete(name="Prediction Class") +
  ylab("Frequency") +
  xlab("Log2 Distance") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

##ZNF143
ggplot(predictiondata_gm12878_10kb[grep("Znf143166181ap_dist",predictiondata_gm12878_10kb$variable),], aes(x=value, color=Prediction)) +
  geom_density() +
  scale_color_discrete(name="Prediction Class") +
  ylab("Frequency") +
  xlab("Log2 Distance") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

##SMC3a
ggplot(predictiondata_gm12878_10kb[grep("Smc3ab9263_dist",predictiondata_gm12878_10kb$variable),], aes(x=value, color=Prediction)) +
  geom_density() +
  scale_color_discrete(name="Prediction Class") +
  ylab("Frequency") +
  xlab("Log2 Distance") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

##Rad21
ggplot(predictiondata_gm12878_10kb[grep("Rad21_dist",predictiondata_gm12878_10kb$variable),], aes(x=value, color=Prediction)) +
  geom_density() +
  scale_color_discrete(name="Prediction Class") +
  ylab("Frequency") +
  xlab("Log2 Distance") +
  #ylab("") +
  #xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

### 2019-04-12 Scripts/investigating_misclassified_TADs.Rmd
editted script for investigating misclassified tads

@@
 
+#Wilcoxon test on differences in distances between FN and TP
+FNdata <- FNdata[,-1]
+TPdata <- TPdata[,-1]
+wilcoxon.results <- numeric(length(colnames(FNdata)))
+for(i in 1:length(colnames(FNdata))){
+ wilcoxon.results[i] <- wilcox.test(FNdata[,i],TPdata[,i])$p.value
+}
+wilcox.table <- cbind.data.frame(Annotation=gsub("_dist","",colnames(FNdata)), Wilcoxon.PValue=wilcoxon.results)
+wilcox.table <- wilcox.table[order(wilcox.table$Wilcoxon.PValue, decreasing = FALSE),]
+wilcox.table$Wilcoxon.PValue <- round(wilcox.table$Wilcoxon.PValue,7)
+
 predictiondata_gm12878_10kb <- rbind.data.frame(FNdatamelt,TPdatamelt)
@@
 
+#Ploting densities
 ggplot(predictiondata_gm12878_10kb, aes(x=value, color=Prediction)) +

### 2019-04-16 Scripts/comparing_predictortypes_one_annot_at_a_time.Rmd
editted results scripts

---
title: "Comparing Predictor Types One Annotation At A Time"
author: "Spiro Stilianoudakis"
date: "April 15, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

# GM12878

##10kb

###One annotation at a time RF

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
train <- train[,-grep("_binary", names(train))]

set.seed(123)
train_smote <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

#Randomly shuffle the data
set.seed(123)
train_smote <- train_smote[sample(nrow(train_smote)),]

#Perform RF with 10 fold cross validation
tunegrid <- expand.grid(mtry=ceiling(sqrt(3)))
#modellist <- list()
#for (ntree in c(50,200,500,1000)) {
#  print(ntree)
#  set.seed(333)
#  fit <- train(y~., data=train_smote, 
#               method="rf", 
#               metric="Accuracy",
#               tuneGrid=tunegrid,  
#               ntree=ntree)
#  key <- toString(ntree)
#  modellist[[key]] <- fit
#}
# compare results
#results <- resamples(modellist)
#summary(results)
#dotplot(results)
#results <- data.frame(summary(results)[3]$statistics$Accuracy)
#results <- results[order(results$Mean, decreasing = TRUE),]

##defining function to extract AUPR curve
auprcSummary <- function(data, lev = NULL, model = NULL){
  lvls <- levels(data$obs) #take the probability of good class
  prob_good <- data[,lvls[2]] 
  the_curve <- pr.curve(scores.class0 = prob_good,
                        weights.class0 = as.numeric(data$obs)-1, #provide the class labels as 0/1
                        curve = FALSE)
  out <- the_curve$auc.integral
  names(out) <- "AUPRC"
  out
}

####set tuning parameters
####set seeds for each cross fols
set.seed(123)
#length is = (n_repeats*nresampling)+1
seeds <- vector(mode = "list", length = 11)
#(1 is the number of tuning parameter lambda
for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 1)
#for the last model
seeds[[11]]<-sample.int(1000, 1)

fitControl <- trainControl(seeds = seeds,
                           method = "cv",
                           number = 10,
                           ## Estimate class probabilities
                           classProbs = TRUE,
                           ## Evaluate performance using 
                           ## the following function
                           #summaryFunction = auprcSummary,
						   summaryFunction = twoClassSummary)

rfimpvarsmat_gm12878_10kb <- matrix(nrow=3, ncol=107,
				dimnames=list("Predictor Type"=c("OC",
												 "Distance",
												 "OP"),
							  "Annotation"=unique(gsub(paste0(c("Gm12878", 
																"_count", 
																"_perc", 
																"_dist",
																"-",
																"Haib", 
																"Sydh",
																"Uta",
																"Uw",
																"Broad",
																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))

for(i in 0:106){
  print(names(train_smote)[(i*3+2):(i*3+4)])
	rfModel <- train(y~., data=train_smote[,c(1, (i*3+2):(i*3+4))], 
                 method="rf", 
                 metric="ROC", 
                 tuneGrid=tunegrid, 
                 trControl=fitControl, 
                 ntree=500) #as.numeric(rownames(results)[1]))

	#rfimpvars <- data.frame(Feature=rownames(varImp(rfModel)$importance), Importance=varImp(rfModel)$importance[,1])
	#rfimpvars <- rfimpvars[order(rfimpvars$Importance, decreasing=TRUE),]

	rfimpvarsmat_gm12878_10kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
}

```

### 2019-04-16 Scripts/evaluating_variable_importances.Rmd
editted results scripts

@@
 colnames(rankdata) <- c("10 kb", "25 kb", "50 kb", "100 kb")
+rankdata <- rankdata[order(rankdata[,1], decreasing = FALSE),]
+rankdata <- rankdata[1:20,]
 

### 2019-04-16 Scripts/investigating_misclassified_TADs.Rmd
editted results scripts

@@
                             "Uchicago"), collapse = "|"), "", names(test))
-enetcoefs <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+enetcoefs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
 test <- test[,c(1,which(names(test) %in% enetcoefs))]

### 2019-04-16 Scripts/comparing_predictortypes_one_annot_at_a_time.Rmd
editted script

@@
 
+write.csv(t(rfimpvarsmat_gm12878_10kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_gm12878_10kb.csv")
+
 ```
+
+##25kb
+
+###One annotation at a time RF
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
+train <- train[,-grep("_binary", names(train))]
+
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+#Randomly shuffle the data
+set.seed(123)
+train_smote <- train_smote[sample(nrow(train_smote)),]
+
+#Perform RF with 10 fold cross validation
+tunegrid <- expand.grid(mtry=ceiling(sqrt(3)))
+#modellist <- list()
+#for (ntree in c(50,200,500,1000)) {
+#  print(ntree)
+#  set.seed(333)
+#  fit <- train(y~., data=train_smote, 
+#               method="rf", 
+#               metric="Accuracy",
+#               tuneGrid=tunegrid,  
+#               ntree=ntree)
+#  key <- toString(ntree)
+#  modellist[[key]] <- fit
+#}
+# compare results
+#results <- resamples(modellist)
+#summary(results)
+#dotplot(results)
+#results <- data.frame(summary(results)[3]$statistics$Accuracy)
+#results <- results[order(results$Mean, decreasing = TRUE),]
+
+##defining function to extract AUPR curve
+auprcSummary <- function(data, lev = NULL, model = NULL){
+  lvls <- levels(data$obs) #take the probability of good class
+  prob_good <- data[,lvls[2]] 
+  the_curve <- pr.curve(scores.class0 = prob_good,
+                        weights.class0 = as.numeric(data$obs)-1, #provide the class labels as 0/1
+                        curve = FALSE)
+  out <- the_curve$auc.integral
+  names(out) <- "AUPRC"
+  out
+}
+
+####set tuning parameters
+####set seeds for each cross fols
+set.seed(123)
+#length is = (n_repeats*nresampling)+1
+seeds <- vector(mode = "list", length = 11)
+#(1 is the number of tuning parameter lambda
+for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 1)
+#for the last model
+seeds[[11]]<-sample.int(1000, 1)
+
+fitControl <- trainControl(seeds = seeds,
+                           method = "cv",
+                           number = 10,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           #summaryFunction = auprcSummary,
+						   summaryFunction = twoClassSummary)
+
+rfimpvarsmat_gm12878_25kb <- matrix(nrow=3, ncol=107,
+				dimnames=list("Predictor Type"=c("OC",
+												 "Distance",
+												 "OP"),
+							  "Annotation"=unique(gsub(paste0(c("Gm12878", 
+																"_count", 
+																"_perc", 
+																"_dist",
+																"-",
+																"Haib", 
+																"Sydh",
+																"Uta",
+																"Uw",
+																"Broad",
+																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))
+
+for(i in 0:106){
+  print(names(train_smote)[(i*3+2):(i*3+4)])
+	rfModel <- train(y~., data=train_smote[,c(1, (i*3+2):(i*3+4))], 
+                 method="rf", 
+                 metric="ROC", 
+                 tuneGrid=tunegrid, 
+                 trControl=fitControl, 
+                 ntree=500) #as.numeric(rownames(results)[1]))
+
+	#rfimpvars <- data.frame(Feature=rownames(varImp(rfModel)$importance), Importance=varImp(rfModel)$importance[,1])
+	#rfimpvars <- rfimpvars[order(rfimpvars$Importance, decreasing=TRUE),]
+
+	rfimpvarsmat_gm12878_25kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
+}
+
+write.csv(t(rfimpvarsmat_gm12878_25kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_gm12878_25kb.csv")
+```
+
+##50kb
+
+###One annotation at a time RF
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
+train <- train[,-grep("_binary", names(train))]
+
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+#Randomly shuffle the data
+set.seed(123)
+train_smote <- train_smote[sample(nrow(train_smote)),]
+
+#Perform RF with 10 fold cross validation
+tunegrid <- expand.grid(mtry=ceiling(sqrt(3)))
+#modellist <- list()
+#for (ntree in c(50,200,500,1000)) {
+#  print(ntree)
+#  set.seed(333)
+#  fit <- train(y~., data=train_smote, 
+#               method="rf", 
+#               metric="Accuracy",
+#               tuneGrid=tunegrid,  
+#               ntree=ntree)
+#  key <- toString(ntree)
+#  modellist[[key]] <- fit
+#}
+# compare results
+#results <- resamples(modellist)
+#summary(results)
+#dotplot(results)
+#results <- data.frame(summary(results)[3]$statistics$Accuracy)
+#results <- results[order(results$Mean, decreasing = TRUE),]
+
+##defining function to extract AUPR curve
+auprcSummary <- function(data, lev = NULL, model = NULL){
+  lvls <- levels(data$obs) #take the probability of good class
+  prob_good <- data[,lvls[2]] 
+  the_curve <- pr.curve(scores.class0 = prob_good,
+                        weights.class0 = as.numeric(data$obs)-1, #provide the class labels as 0/1
+                        curve = FALSE)
+  out <- the_curve$auc.integral
+  names(out) <- "AUPRC"
+  out
+}
+
+####set tuning parameters
+####set seeds for each cross fols
+set.seed(123)
+#length is = (n_repeats*nresampling)+1
+seeds <- vector(mode = "list", length = 11)
+#(1 is the number of tuning parameter lambda
+for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 1)
+#for the last model
+seeds[[11]]<-sample.int(1000, 1)
+
+fitControl <- trainControl(seeds = seeds,
+                           method = "cv",
+                           number = 10,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           #summaryFunction = auprcSummary,
+						   summaryFunction = twoClassSummary)
+
+rfimpvarsmat_gm12878_50kb <- matrix(nrow=3, ncol=107,
+				dimnames=list("Predictor Type"=c("OC",
+												 "Distance",
+												 "OP"),
+							  "Annotation"=unique(gsub(paste0(c("Gm12878", 
+																"_count", 
+																"_perc", 
+																"_dist",
+																"-",
+																"Haib", 
+																"Sydh",
+																"Uta",
+																"Uw",
+																"Broad",
+																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))
+
+for(i in 0:106){
+  print(names(train_smote)[(i*3+2):(i*3+4)])
+	rfModel <- train(y~., data=train_smote[,c(1, (i*3+2):(i*3+4))], 
+                 method="rf", 
+                 metric="ROC", 
+                 tuneGrid=tunegrid, 
+                 trControl=fitControl, 
+                 ntree=500) #as.numeric(rownames(results)[1]))
+
+	#rfimpvars <- data.frame(Feature=rownames(varImp(rfModel)$importance), Importance=varImp(rfModel)$importance[,1])
+	#rfimpvars <- rfimpvars[order(rfimpvars$Importance, decreasing=TRUE),]
+
+	rfimpvarsmat_gm12878_50kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
+}
+
+write.csv(t(rfimpvarsmat_gm12878_50kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_gm12878_50kb.csv")
+```
+
+##100kb
+
+###One annotation at a time RF
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
+train <- train[,-grep("_binary", names(train))]
+
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+#Randomly shuffle the data
+set.seed(123)
+train_smote <- train_smote[sample(nrow(train_smote)),]
+
+#Perform RF with 10 fold cross validation
+tunegrid <- expand.grid(mtry=ceiling(sqrt(3)))
+#modellist <- list()
+#for (ntree in c(50,200,500,1000)) {
+#  print(ntree)
+#  set.seed(333)
+#  fit <- train(y~., data=train_smote, 
+#               method="rf", 
+#               metric="Accuracy",
+#               tuneGrid=tunegrid,  
+#               ntree=ntree)
+#  key <- toString(ntree)
+#  modellist[[key]] <- fit
+#}
+# compare results
+#results <- resamples(modellist)
+#summary(results)
+#dotplot(results)
+#results <- data.frame(summary(results)[3]$statistics$Accuracy)
+#results <- results[order(results$Mean, decreasing = TRUE),]
+
+##defining function to extract AUPR curve
+auprcSummary <- function(data, lev = NULL, model = NULL){
+  lvls <- levels(data$obs) #take the probability of good class
+  prob_good <- data[,lvls[2]] 
+  the_curve <- pr.curve(scores.class0 = prob_good,
+                        weights.class0 = as.numeric(data$obs)-1, #provide the class labels as 0/1
+                        curve = FALSE)
+  out <- the_curve$auc.integral
+  names(out) <- "AUPRC"
+  out
+}
+
+####set tuning parameters
+####set seeds for each cross fols
+set.seed(123)
+#length is = (n_repeats*nresampling)+1
+seeds <- vector(mode = "list", length = 11)
+#(1 is the number of tuning parameter lambda
+for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 1)
+#for the last model
+seeds[[11]]<-sample.int(1000, 1)
+
+fitControl <- trainControl(seeds = seeds,
+                           method = "cv",
+                           number = 10,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           #summaryFunction = auprcSummary,
+						   summaryFunction = twoClassSummary)
+
+rfimpvarsmat_gm12878_100kb <- matrix(nrow=3, ncol=107,
+				dimnames=list("Predictor Type"=c("OC",
+												 "Distance",
+												 "OP"),
+							  "Annotation"=unique(gsub(paste0(c("Gm12878", 
+																"_count", 
+																"_perc", 
+																"_dist",
+																"-",
+																"Haib", 
+																"Sydh",
+																"Uta",
+																"Uw",
+																"Broad",
+																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))
+
+for(i in 0:106){
+  print(names(train_smote)[(i*3+2):(i*3+4)])
+	rfModel <- train(y~., data=train_smote[,c(1, (i*3+2):(i*3+4))], 
+                 method="rf", 
+                 metric="ROC", 
+                 tuneGrid=tunegrid, 
+                 trControl=fitControl, 
+                 ntree=500) #as.numeric(rownames(results)[1]))
+
+	#rfimpvars <- data.frame(Feature=rownames(varImp(rfModel)$importance), Importance=varImp(rfModel)$importance[,1])
+	#rfimpvars <- rfimpvars[order(rfimpvars$Importance, decreasing=TRUE),]
+
+	rfimpvarsmat_gm12878_100kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
+}
+
+write.csv(t(rfimpvarsmat_gm12878_100kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_gm12878_100kb.csv")
+```
+
+# K562
+
+##10kb
+
+###One annotation at a time RF
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
+train <- train[,-grep("_binary", names(train))]
+
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+#Randomly shuffle the data
+set.seed(123)
+train_smote <- train_smote[sample(nrow(train_smote)),]
+
+#Perform RF with 10 fold cross validation
+tunegrid <- expand.grid(mtry=ceiling(sqrt(3)))
+#modellist <- list()
+#for (ntree in c(50,200,500,1000)) {
+#  print(ntree)
+#  set.seed(333)
+#  fit <- train(y~., data=train_smote, 
+#               method="rf", 
+#               metric="Accuracy",
+#               tuneGrid=tunegrid,  
+#               ntree=ntree)
+#  key <- toString(ntree)
+#  modellist[[key]] <- fit
+#}
+# compare results
+#results <- resamples(modellist)
+#summary(results)
+#dotplot(results)
+#results <- data.frame(summary(results)[3]$statistics$Accuracy)
+#results <- results[order(results$Mean, decreasing = TRUE),]
+
+##defining function to extract AUPR curve
+auprcSummary <- function(data, lev = NULL, model = NULL){
+  lvls <- levels(data$obs) #take the probability of good class
+  prob_good <- data[,lvls[2]] 
+  the_curve <- pr.curve(scores.class0 = prob_good,
+                        weights.class0 = as.numeric(data$obs)-1, #provide the class labels as 0/1
+                        curve = FALSE)
+  out <- the_curve$auc.integral
+  names(out) <- "AUPRC"
+  out
+}
+
+####set tuning parameters
+####set seeds for each cross fols
+set.seed(123)
+#length is = (n_repeats*nresampling)+1
+seeds <- vector(mode = "list", length = 11)
+#(1 is the number of tuning parameter lambda
+for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 1)
+#for the last model
+seeds[[11]]<-sample.int(1000, 1)
+
+fitControl <- trainControl(seeds = seeds,
+                           method = "cv",
+                           number = 10,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           #summaryFunction = auprcSummary,
+						   summaryFunction = twoClassSummary)
+
+rfimpvarsmat_K562_10kb <- matrix(nrow=3, ncol=141,
+				dimnames=list("Predictor Type"=c("OC",
+												 "Distance",
+												 "OP"),
+							  "Annotation"=unique(gsub(paste0(c("K562", 
+																"_count", 
+																"_perc", 
+																"_dist",
+																"-",
+																"Haib", 
+																"Sydh",
+																"Uta",
+																"Uw",
+																"Broad",
+																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))
+
+for(i in 0:140){
+  print(names(train_smote)[(i*3+2):(i*3+4)])
+	rfModel <- train(y~., data=train_smote[,c(1, (i*3+2):(i*3+4))], 
+                 method="rf", 
+                 metric="ROC", 
+                 tuneGrid=tunegrid, 
+                 trControl=fitControl, 
+                 ntree=500) #as.numeric(rownames(results)[1]))
+
+	#rfimpvars <- data.frame(Feature=rownames(varImp(rfModel)$importance), Importance=varImp(rfModel)$importance[,1])
+	#rfimpvars <- rfimpvars[order(rfimpvars$Importance, decreasing=TRUE),]
+
+	rfimpvarsmat_K562_10kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
+}
+
+write.csv(t(rfimpvarsmat_K562_10kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_K562_10kb.csv")
+
+```
+
+##25kb
+
+###One annotation at a time RF
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
+train <- train[,-grep("_binary", names(train))]
+
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+#Randomly shuffle the data
+set.seed(123)
+train_smote <- train_smote[sample(nrow(train_smote)),]
+
+#Perform RF with 10 fold cross validation
+tunegrid <- expand.grid(mtry=ceiling(sqrt(3)))
+#modellist <- list()
+#for (ntree in c(50,200,500,1000)) {
+#  print(ntree)
+#  set.seed(333)
+#  fit <- train(y~., data=train_smote, 
+#               method="rf", 
+#               metric="Accuracy",
+#               tuneGrid=tunegrid,  
+#               ntree=ntree)
+#  key <- toString(ntree)
+#  modellist[[key]] <- fit
+#}
+# compare results
+#results <- resamples(modellist)
+#summary(results)
+#dotplot(results)
+#results <- data.frame(summary(results)[3]$statistics$Accuracy)
+#results <- results[order(results$Mean, decreasing = TRUE),]
+
+##defining function to extract AUPR curve
+auprcSummary <- function(data, lev = NULL, model = NULL){
+  lvls <- levels(data$obs) #take the probability of good class
+  prob_good <- data[,lvls[2]] 
+  the_curve <- pr.curve(scores.class0 = prob_good,
+                        weights.class0 = as.numeric(data$obs)-1, #provide the class labels as 0/1
+                        curve = FALSE)
+  out <- the_curve$auc.integral
+  names(out) <- "AUPRC"
+  out
+}
+
+####set tuning parameters
+####set seeds for each cross fols
+set.seed(123)
+#length is = (n_repeats*nresampling)+1
+seeds <- vector(mode = "list", length = 11)
+#(1 is the number of tuning parameter lambda
+for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 1)
+#for the last model
+seeds[[11]]<-sample.int(1000, 1)
+
+fitControl <- trainControl(seeds = seeds,
+                           method = "cv",
+                           number = 10,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           #summaryFunction = auprcSummary,
+						   summaryFunction = twoClassSummary)
+
+rfimpvarsmat_K562_25kb <- matrix(nrow=3, ncol=141,
+				dimnames=list("Predictor Type"=c("OC",
+												 "Distance",
+												 "OP"),
+							  "Annotation"=unique(gsub(paste0(c("K562", 
+																"_count", 
+																"_perc", 
+																"_dist",
+																"-",
+																"Haib", 
+																"Sydh",
+																"Uta",
+																"Uw",
+																"Broad",
+																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))
+
+for(i in 0:140){
+  print(names(train_smote)[(i*3+2):(i*3+4)])
+	rfModel <- train(y~., data=train_smote[,c(1, (i*3+2):(i*3+4))], 
+                 method="rf", 
+                 metric="ROC", 
+                 tuneGrid=tunegrid, 
+                 trControl=fitControl, 
+                 ntree=500) #as.numeric(rownames(results)[1]))
+
+	#rfimpvars <- data.frame(Feature=rownames(varImp(rfModel)$importance), Importance=varImp(rfModel)$importance[,1])
+	#rfimpvars <- rfimpvars[order(rfimpvars$Importance, decreasing=TRUE),]
+
+	rfimpvarsmat_K562_25kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
+}
+
+write.csv(t(rfimpvarsmat_K562_25kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_K562_25kb.csv")
+```
+
+##50kb
+
+###One annotation at a time RF
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
+train <- train[,-grep("_binary", names(train))]
+
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+#Randomly shuffle the data
+set.seed(123)
+train_smote <- train_smote[sample(nrow(train_smote)),]
+
+#Perform RF with 10 fold cross validation
+tunegrid <- expand.grid(mtry=ceiling(sqrt(3)))
+#modellist <- list()
+#for (ntree in c(50,200,500,1000)) {
+#  print(ntree)
+#  set.seed(333)
+#  fit <- train(y~., data=train_smote, 
+#               method="rf", 
+#               metric="Accuracy",
+#               tuneGrid=tunegrid,  
+#               ntree=ntree)
+#  key <- toString(ntree)
+#  modellist[[key]] <- fit
+#}
+# compare results
+#results <- resamples(modellist)
+#summary(results)
+#dotplot(results)
+#results <- data.frame(summary(results)[3]$statistics$Accuracy)
+#results <- results[order(results$Mean, decreasing = TRUE),]
+
+##defining function to extract AUPR curve
+auprcSummary <- function(data, lev = NULL, model = NULL){
+  lvls <- levels(data$obs) #take the probability of good class
+  prob_good <- data[,lvls[2]] 
+  the_curve <- pr.curve(scores.class0 = prob_good,
+                        weights.class0 = as.numeric(data$obs)-1, #provide the class labels as 0/1
+                        curve = FALSE)
+  out <- the_curve$auc.integral
+  names(out) <- "AUPRC"
+  out
+}
+
+####set tuning parameters
+####set seeds for each cross fols
+set.seed(123)
+#length is = (n_repeats*nresampling)+1
+seeds <- vector(mode = "list", length = 11)
+#(1 is the number of tuning parameter lambda
+for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 1)
+#for the last model
+seeds[[11]]<-sample.int(1000, 1)
+
+fitControl <- trainControl(seeds = seeds,
+                           method = "cv",
+                           number = 10,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           #summaryFunction = auprcSummary,
+						   summaryFunction = twoClassSummary)
+
+rfimpvarsmat_K562_50kb <- matrix(nrow=3, ncol=141,
+				dimnames=list("Predictor Type"=c("OC",
+												 "Distance",
+												 "OP"),
+							  "Annotation"=unique(gsub(paste0(c("K562", 
+																"_count", 
+																"_perc", 
+																"_dist",
+																"-",
+																"Haib", 
+																"Sydh",
+																"Uta",
+																"Uw",
+																"Broad",
+																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))
+
+for(i in 0:140){
+  print(names(train_smote)[(i*3+2):(i*3+4)])
+	rfModel <- train(y~., data=train_smote[,c(1, (i*3+2):(i*3+4))], 
+                 method="rf", 
+                 metric="ROC", 
+                 tuneGrid=tunegrid, 
+                 trControl=fitControl, 
+                 ntree=500) #as.numeric(rownames(results)[1]))
+
+	#rfimpvars <- data.frame(Feature=rownames(varImp(rfModel)$importance), Importance=varImp(rfModel)$importance[,1])
+	#rfimpvars <- rfimpvars[order(rfimpvars$Importance, decreasing=TRUE),]
+
+	rfimpvarsmat_K562_50kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
+}
+
+write.csv(t(rfimpvarsmat_K562_50kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_K562_50kb.csv")
+```
+
+##100kb
+
+###One annotation at a time RF
+
+```{r}
+train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
+train <- train[,-grep("_binary", names(train))]
+
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+#Randomly shuffle the data
+set.seed(123)
+train_smote <- train_smote[sample(nrow(train_smote)),]
+
+#Perform RF with 10 fold cross validation
+tunegrid <- expand.grid(mtry=ceiling(sqrt(3)))
+#modellist <- list()
+#for (ntree in c(50,200,500,1000)) {
+#  print(ntree)
+#  set.seed(333)
+#  fit <- train(y~., data=train_smote, 
+#               method="rf", 
+#               metric="Accuracy",
+#               tuneGrid=tunegrid,  
+#               ntree=ntree)
+#  key <- toString(ntree)
+#  modellist[[key]] <- fit
+#}
+# compare results
+#results <- resamples(modellist)
+#summary(results)
+#dotplot(results)
+#results <- data.frame(summary(results)[3]$statistics$Accuracy)
+#results <- results[order(results$Mean, decreasing = TRUE),]
+
+##defining function to extract AUPR curve
+auprcSummary <- function(data, lev = NULL, model = NULL){
+  lvls <- levels(data$obs) #take the probability of good class
+  prob_good <- data[,lvls[2]] 
+  the_curve <- pr.curve(scores.class0 = prob_good,
+                        weights.class0 = as.numeric(data$obs)-1, #provide the class labels as 0/1
+                        curve = FALSE)
+  out <- the_curve$auc.integral
+  names(out) <- "AUPRC"
+  out
+}
+
+####set tuning parameters
+####set seeds for each cross fols
+set.seed(123)
+#length is = (n_repeats*nresampling)+1
+seeds <- vector(mode = "list", length = 11)
+#(1 is the number of tuning parameter lambda
+for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 1)
+#for the last model
+seeds[[11]]<-sample.int(1000, 1)
+
+fitControl <- trainControl(seeds = seeds,
+                           method = "cv",
+                           number = 10,
+                           ## Estimate class probabilities
+                           classProbs = TRUE,
+                           ## Evaluate performance using 
+                           ## the following function
+                           #summaryFunction = auprcSummary,
+						   summaryFunction = twoClassSummary)
+
+rfimpvarsmat_K562_100kb <- matrix(nrow=3, ncol=141,
+				dimnames=list("Predictor Type"=c("OC",
+												 "Distance",
+												 "OP"),
+							  "Annotation"=unique(gsub(paste0(c("K562", 
+																"_count", 
+																"_perc", 
+																"_dist",
+																"-",
+																"Haib", 
+																"Sydh",
+																"Uta",
+																"Uw",
+																"Broad",
+																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))
+
+for(i in 0:140){
+  print(names(train_smote)[(i*3+2):(i*3+4)])
+	rfModel <- train(y~., data=train_smote[,c(1, (i*3+2):(i*3+4))], 
+                 method="rf", 
+                 metric="ROC", 
+                 tuneGrid=tunegrid, 
+                 trControl=fitControl, 
+                 ntree=500) #as.numeric(rownames(results)[1]))
+
+	#rfimpvars <- data.frame(Feature=rownames(varImp(rfModel)$importance), Importance=varImp(rfModel)$importance[,1])
+	#rfimpvars <- rfimpvars[order(rfimpvars$Importance, decreasing=TRUE),]
+
+	rfimpvarsmat_K562_100kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
+}
+
+write.csv(t(rfimpvarsmat_K562_100kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_K562_100kb.csv")
+```

### 2019-04-17 Scripts/comparing_distance_densities_by_genomic_bin_class.Rmd
script for comparing distance densities between genomic bin class for top predictive annotations (gm12878)

---
title: "Comparing distance distributions for top predictive features between bins with and without TADs"
author: "Spiro Stilianoudakis"
date: "April 15, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(coin)
```

# GM12878

## Function for ploting distance densities between bins with and without TAD boundaries

```{r}
distplotsfunc <- function(cl, resolution, annotation){
  train <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/training_testing/train.rds"))
  data <- train[, c(1, which(names(train)==annotation))]

  set.seed(123)
  majorityids <- sample(x=which(data$y=="No"), size=length(which(data$y=="Yes")))
  annotdata <- rbind.data.frame(data[which(data$y=="Yes"),],
                                data[majorityids,])

  #ks.test(annotdata[which(annotdata$y=="No"),2], annotdata[which(annotdata$y=="Yes"),2], alternative = "two.sided")

  perm.pval <- pvalue(oneway_test(annotdata[,2] ~ annotdata[,1],
                     data=annotdata,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

  if(perm.pval==0){perm.pval="< 0.0001"}

  plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          annotation))

  p <- ggplot(annotdata, aes(x=annotdata[,2], color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("Frequency") +
    xlab("Log2 Distance") +
    ggtitle(paste(plottitle)) +
    annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20,
                               hjust=.5))

  ggsave(p, 
         filename = paste0("C:/Users/stili/Documents/TAD_miscellaneous/figures/comparing_distance_by_bin_class/", 
                           cl, 
                           "_", 
                           resolution, 
                           "_", 
                           plottitle, 
                           ".png"),
         width=10,
         height=10,
         units="in")
}

```

### 10kb

#### Top Annotations

```{r}
#### CTCF

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Ctcf-Broad_dist")

#### Smc3ab9263

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")

#### Znf143166181ap

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")

#### Rad21

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Rad21-Haib_dist")

#### 08Insulator

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-08Insulator_dist")

#### Yy1sc281

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Yy1sc281-Haib_dist")

#### DNase

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-DNase_dist")
```

### 25kb

#### Top Annotations

```{r}
#### CTCF

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Ctcf-Broad_dist")

#### Smc3ab9263

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")

#### Znf143166181ap

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")

#### Rad21

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Rad21-Haib_dist")

#### 08Insulator

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-08Insulator_dist")

#### Yy1sc281

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Yy1sc281-Haib_dist")

#### DNase

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-DNase_dist")
```

### 50kb

#### Top Annotations

```{r}
#### CTCF

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Ctcf-Broad_dist")

#### Smc3ab9263

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")

#### Znf143166181ap

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")

#### Rad21

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Rad21-Haib_dist")

#### 08Insulator

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-08Insulator_dist")

#### Yy1sc281

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Yy1sc281-Haib_dist")

#### DNase

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-DNase_dist")
```

### 100kb

#### Top Annotations

```{r}
#### CTCF

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Ctcf-Broad_dist")

#### Smc3ab9263

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")

#### Znf143166181ap

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")

#### Rad21

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Rad21-Haib_dist")

#### 08Insulator

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-08Insulator_dist")

#### Yy1sc281

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Yy1sc281-Haib_dist")

#### DNase

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-DNase_dist")
```

### 2019-04-17 Scripts/comparing_distance_densities_by_genomic_bin_class.Rmd
added to results scripts

@@
 
-## Function for ploting distance densities between bins with and without TAD boundaries
+## Function for ploting distance densities between bins with and without TAD boundaries from SMOTE resampled data
 
@@
   train <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/training_testing/train.rds"))
-  data <- train[, c(1, which(names(train)==annotation))]
+
+  enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))
+
+  names(train) <- gsub(paste(c("`", 
+                             "Gm12878", 
+                             "-", 
+                             #"_", 
+                             #"dist", "count", "perc",
+                             "Haib", 
+                             "Sydh",
+                             "Uta",
+                             "Uw",
+                             "Broad",
+                             "Uchicago"), collapse = "|"), "", names(train))
+  train <- train[,c(1,which(names(train) %in% enetcoefs))]
 
   set.seed(123)
-  majorityids <- sample(x=which(data$y=="No"), size=length(which(data$y=="Yes")))
-  annotdata <- rbind.data.frame(data[which(data$y=="Yes"),],
-                                data[majorityids,])
+  train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+  annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", annotation)
+
+  #data <- train[, c(1, which(names(train)==annotname))]
+  #
+  #set.seed(123)
+  #majorityids <- sample(x=which(data$y=="No"), size=length(which(data$y=="Yes")))
+  #annotdata <- rbind.data.frame(data[which(data$y=="Yes"),],
+  #                              data[majorityids,])
+
+  annotdata <- train_smote[, c(1, which(names(train_smote)==annotname))]
 
@@
 
-  if(perm.pval==0){perm.pval="< 0.0001"}
+  perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
 
@@
 
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-08Insulator_dist")
+#distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-08Insulator_dist")
 
@@
 
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-08Insulator_dist")
+#distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-08Insulator_dist")
 
@@
 
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-08Insulator_dist")
+#distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-08Insulator_dist")
 
@@
 
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-08Insulator_dist")
+#distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-08Insulator_dist")
 
@@
 ```
+
+# K562
+
+## Function for ploting distance densities between bins with and without TAD boundaries from SMOTE resampled data
+
+```{r}
+distplotsfunc <- function(cl, resolution, annotation){
+  train <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/training_testing/train.rds"))
+
+  enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))
+
+  names(train) <- gsub(paste(c("`", 
+                             "K562", 
+                             "-", 
+                             #"_", 
+                             #"dist", "count", "perc",
+                             "Haib", 
+                             "Sydh",
+                             "Uta",
+                             "Uw",
+                             "Broad",
+                             "Uchicago"), collapse = "|"), "", names(train))
+  train <- train[,c(1,which(names(train) %in% enetcoefs))]
+
+  set.seed(123)
+  train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+  annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", annotation)
+
+  #data <- train[, c(1, which(names(train)==annotname))]
+  #
+  #set.seed(123)
+  #majorityids <- sample(x=which(data$y=="No"), size=length(which(data$y=="Yes")))
+  #annotdata <- rbind.data.frame(data[which(data$y=="Yes"),],
+  #                              data[majorityids,])
+
+  annotdata <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+  #ks.test(annotdata[which(annotdata$y=="No"),2], annotdata[which(annotdata$y=="Yes"),2], alternative = "two.sided")
+
+  perm.pval <- pvalue(oneway_test(annotdata[,2] ~ annotdata[,1],
+                     data=annotdata,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+  perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+  plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          annotation))
+
+  p <- ggplot(annotdata, aes(x=annotdata[,2], color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("Frequency") +
+    xlab("Log2 Distance") +
+    ggtitle(paste(plottitle)) +
+    annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                      #angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      #hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20,
+                               hjust=.5))
+
+  ggsave(p, 
+         filename = paste0("C:/Users/stili/Documents/TAD_miscellaneous/figures/comparing_distance_by_bin_class/", 
+                           cl, 
+                           "_", 
+                           resolution, 
+                           "_", 
+                           plottitle, 
+                           ".png"),
+         width=10,
+         height=10,
+         units="in")
+}
+
+```
+
+### 10kb
+
+#### Top Annotations
+
+```{r}
+#### CTCF
+
+distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Ctcf-Broad_dist")
+
+#### Smc3ab9263
+
+distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Smc3ab9263-Sydh_dist")
+
+#### Znf143166181ap
+
+distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Znf143166181ap-Sydh_dist")
+
+#### Rad21
+
+distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Rad21-Haib_dist")
+
+#### 08Insulator
+
+#distplotsfunc(cl="K562", resolution="10kb", annotation="K562-08Insulator_dist")
+
+#### Yy1sc281
+
+distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Yy1sc281-Haib_dist")
+
+#### DNase
+
+distplotsfunc(cl="K562", resolution="10kb", annotation="K562-DNase_dist")
+```
+
+### 25kb
+
+#### Top Annotations
+
+```{r}
+#### CTCF
+
+distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Ctcf-Broad_dist")
+
+#### Smc3ab9263
+
+distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Smc3ab9263-Sydh_dist")
+
+#### Znf143166181ap
+
+distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Znf143166181ap-Sydh_dist")
+
+#### Rad21
+
+distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Rad21-Haib_dist")
+
+#### 08Insulator
+
+#distplotsfunc(cl="K562", resolution="25kb", annotation="K562-08Insulator_dist")
+
+#### Yy1sc281
+
+distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Yy1sc281-Haib_dist")
+
+#### DNase
+
+distplotsfunc(cl="K562", resolution="25kb", annotation="K562-DNase_dist")
+```
+
+### 50kb
+
+#### Top Annotations
+
+```{r}
+#### CTCF
+
+distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Ctcf-Broad_dist")
+
+#### Smc3ab9263
+
+distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Smc3ab9263-Sydh_dist")
+
+#### Znf143166181ap
+
+distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Znf143166181ap-Sydh_dist")
+
+#### Rad21
+
+distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Rad21-Haib_dist")
+
+#### 08Insulator
+
+#distplotsfunc(cl="K562", resolution="50kb", annotation="K562-08Insulator_dist")
+
+#### Yy1sc281
+
+distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Yy1sc281-Haib_dist")
+
+#### DNase
+
+distplotsfunc(cl="K562", resolution="50kb", annotation="K562-DNase_dist")
+```
+
+### 100kb
+
+#### Top Annotations
+
+```{r}
+#### CTCF
+
+distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Ctcf-Broad_dist")
+
+#### Smc3ab9263
+
+distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Smc3ab9263-Sydh_dist")
+
+#### Znf143166181ap
+
+distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Znf143166181ap-Sydh_dist")
+
+#### Rad21
+
+distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Rad21-Haib_dist")
+
+#### 08Insulator
+
+#distplotsfunc(cl="K562", resolution="100kb", annotation="K562-08Insulator_dist")
+
+#### Yy1sc281
+
+distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Yy1sc281-Haib_dist")
+
+#### DNase
+
+distplotsfunc(cl="K562", resolution="100kb", annotation="K562-DNase_dist")
+```

### 2019-04-17 Scripts/comparing_tfbs_specific_models_with_all_annotations.Rmd
added to results scripts

@@
 
-# TFBS Specific Model Performances
+# GM12878; smote; distance types
 
-## GM12878
-
-### 10 kb
+## 10kb
 
 ```{r}
-#OC
-##None
-rfperf_gm12878_10kb_none_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/tfbs/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_gm12878_10kb_none_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/tfbs/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_gm12878_10kb_none_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/tfbs/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_gm12878_10kb_ros_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/tfbs/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_gm12878_10kb_ros_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/tfbs/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_gm12878_10kb_ros_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/tfbs/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_gm12878_10kb_rus_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/tfbs/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_gm12878_10kb_rus_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/tfbs/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_gm12878_10kb_rus_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/tfbs/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_gm12878_10kb_smote_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/tfbs/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_gm12878_10kb_smote_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/tfbs/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
+### TFBS Specific Model Performances
+####SMOTE
+#####Distance
 rfperf_gm12878_10kb_smote_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/tfbs/Distance/ENET/RF/rfperf.rds")
 
-all_rfperfs_gm12878_tfbs <- data.frame(Resampling=rep(c(rep("None",3),
-                                                    rep("ROS",3),
-                                                    rep("RUS",3),
-                                                    rep("SMOTE",3)),2),
-                                       Predictor=rep(c("OC","OP","Distance"),8),
-                                       Metric=c(rep("F1-Score",12), 
-                                                rep("MCC",12)),
-                                       Annotations=rep("TFBS Only",24)
-                                       )
+### Chromstates Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_gm12878_10kb_smote_dist_chromstates <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/chromstates/Distance/ENET/RF/rfperf.rds")
 
-all_rfperfs_gm12878_tfbs$Predictor <- factor(all_rfperfs_gm12878_tfbs$Predictor, levels=c("OC", "OP", "Distance"))
-all_rfperfs_gm12878_tfbs$Metric <- factor(all_rfperfs_gm12878_tfbs$Metric, levels=c("F1-Score", "MCC"))
-all_rfperfs_gm12878_tfbs$Resampling <- factor(all_rfperfs_gm12878_tfbs$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))
+### Histones Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_gm12878_10kb_smote_dist_histones <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/histones/Distance/ENET/RF/rfperf.rds")
 
-all_rfperfs_gm12878_tfbs$Performance <- c(rfperf_gm12878_10kb_none_oc_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_none_op_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_none_dist_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_ros_oc_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_ros_op_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_ros_dist_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_rus_oc_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_rus_op_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_rus_dist_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_smote_oc_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_smote_op_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_smote_dist_tfbs[16,2], #f1
-
-                                     rfperf_gm12878_10kb_none_oc_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_none_op_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_none_dist_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_ros_oc_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_ros_op_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_ros_dist_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_rus_oc_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_rus_op_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_rus_dist_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_smote_oc_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_smote_op_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_smote_dist_tfbs[15,2] #mcc
-
-                                     )
+### All Annotations
+####SMOTE
+#####Distance
+rfperf_gm12878_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
 
@@
 
-# All Annotations
-
-## GM12878
-
-### 10 kb
+## 25kb
 
 ```{r}
-#OC
-##None
-rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+### TFBS Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_gm12878_25kb_smote_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/tfbs/Distance/ENET/RF/rfperf.rds")
 
-#OP
-##None
-rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+### Chromstates Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_gm12878_25kb_smote_dist_chromstates <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/chromstates/Distance/ENET/RF/rfperf.rds")
 
-#Distance
-##None
-rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+### Histones Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_gm12878_25kb_smote_dist_histones <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/histones/Distance/ENET/RF/rfperf.rds")
 
-#OC
-##ROS
-rfperf_gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+### All Annotations
+####SMOTE
+#####Distance
+rfperf_gm12878_25kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
 
-#OP
-##ROS
-rfperf_gm12878_10kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+```
 
-#Distance
-##ROS
-rfperf_gm12878_10kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+## 50kb
 
-#OC
-##RUS
-rfperf_gm12878_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+```{r}
+### TFBS Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_gm12878_50kb_smote_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/tfbs/Distance/ENET/RF/rfperf.rds")
 
-#OP
-##RUS
-rfperf_gm12878_10kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+### Chromstates Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_gm12878_50kb_smote_dist_chromstates <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/chromstates/Distance/ENET/RF/rfperf.rds")
 
-#Distance
-##RUS
-rfperf_gm12878_10kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+### Histones Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_gm12878_50kb_smote_dist_histones <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/histones/Distance/ENET/RF/rfperf.rds")
 
-#OC
-##SMOTE
-rfperf_gm12878_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+### All Annotations
+####SMOTE
+#####Distance
+rfperf_gm12878_50kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
 
-#OP
-##SMOTE
-rfperf_gm12878_10kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+```
 
-#Distance
-##SMOTE
-rfperf_gm12878_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+## 100kb
 
-all_rfperfs_gm12878 <- data.frame(Resampling=rep(c(rep("None",3),
-                                                    rep("ROS",3),
-                                                    rep("RUS",3),
-                                                    rep("SMOTE",3)),2),
-                                       Predictor=rep(c("OC","OP","Distance"),8),
-                                       Metric=c(rep("F1-Score",12), 
-                                                rep("MCC",12)),
-                                       Annotations=rep("ALL Types",24)
-                                       )
+```{r}
+### TFBS Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_gm12878_100kb_smote_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/tfbs/Distance/ENET/RF/rfperf.rds")
 
-all_rfperfs_gm12878$Predictor <- factor(all_rfperfs_gm12878$Predictor, levels=c("OC", "OP", "Distance"))
-all_rfperfs_gm12878$Metric <- factor(all_rfperfs_gm12878$Metric, levels=c("F1-Score", "MCC"))
-all_rfperfs_gm12878$Resampling <- factor(all_rfperfs_gm12878$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))
+### Chromstates Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_gm12878_100kb_smote_dist_chromstates <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/chromstates/Distance/ENET/RF/rfperf.rds")
 
-all_rfperfs_gm12878$Performance <- c(rfperf_gm12878_10kb_none_oc[16,2], #f1
-                                          rfperf_gm12878_10kb_none_op[16,2], #f1
-                                          rfperf_gm12878_10kb_none_dist[16,2], #f1
-                                          rfperf_gm12878_10kb_ros_oc[16,2], #f1
-                                          rfperf_gm12878_10kb_ros_op[16,2], #f1
-                                          rfperf_gm12878_10kb_ros_dist[16,2], #f1
-                                          rfperf_gm12878_10kb_rus_oc[16,2], #f1
-                                          rfperf_gm12878_10kb_rus_op[16,2], #f1
-                                          rfperf_gm12878_10kb_rus_dist[16,2], #f1
-                                          rfperf_gm12878_10kb_smote_oc[16,2], #f1
-                                          rfperf_gm12878_10kb_smote_op[16,2], #f1
-                                          rfperf_gm12878_10kb_smote_dist[16,2], #f1
+### Histones Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_gm12878_100kb_smote_dist_histones <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/histones/Distance/ENET/RF/rfperf.rds")
 
-                                     rfperf_gm12878_10kb_none_oc[15,2], #mcc
-                                          rfperf_gm12878_10kb_none_op[15,2], #mcc
-                                          rfperf_gm12878_10kb_none_dist[15,2], #mcc
-                                          rfperf_gm12878_10kb_ros_oc[15,2], #mcc
-                                          rfperf_gm12878_10kb_ros_op[15,2], #mcc
-                                          rfperf_gm12878_10kb_ros_dist[15,2], #mcc
-                                          rfperf_gm12878_10kb_rus_oc[15,2], #mcc
-                                          rfperf_gm12878_10kb_rus_op[15,2], #mcc
-                                          rfperf_gm12878_10kb_rus_dist[15,2], #mcc
-                                          rfperf_gm12878_10kb_smote_oc[15,2], #mcc
-                                          rfperf_gm12878_10kb_smote_op[15,2], #mcc
-                                          rfperf_gm12878_10kb_smote_dist[15,2] #mcc
-
-                                     )
+### All Annotations
+####SMOTE
+#####Distance
+rfperf_gm12878_100kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
 
@@
 
-## Comparing 10 kb
+```{r}
+all_rfperfs_gm12878 <- data.frame(Annotation=rep(c("TFBS", 
+                                               "Chromatin State Segmentations", 
+                                               "Histone Modifications", 
+                                               "All Combined"), 8),
+                                  Resolution=rep(c(rep("10 kb", 4),
+                                               rep("25 kb", 4),
+                                               rep("50 kb", 4),
+                                               rep("100 kb", 4)), 2),
+                                  Metric=c(rep("F1-Score", 16),
+                                           rep("MCC", 16))
+                                  )
+all_rfperfs_gm12878$Annotation <- factor(all_rfperfs_gm12878$Annotation, levels=c("Histone Modifications",
+                                                                                  "Chromatin State Segmentations",
+                                                                                  "TFBS",
+                                                                                  "All Combined"))
+all_rfperfs_gm12878$Resolution <- factor(all_rfperfs_gm12878$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
+all_rfperfs_gm12878$Metric <- factor(all_rfperfs_gm12878$Metric, levels=c("F1-Score", "MCC"))
 
-```{r}
-all_rfperfs_gm12878_allvtfbs <- rbind.data.frame(all_rfperfs_gm12878,all_rfperfs_gm12878_tfbs)
-all_rfperfs_gm12878_allvtfbs$Annotations <- factor(all_rfperfs_gm12878_allvtfbs$Annotations, levels=c("ALL Types", "TFBS Only"))
+all_rfperfs_gm12878$Performance <- c(rfperf_gm12878_10kb_smote_dist_tfbs[16,2], #f1
+                                     rfperf_gm12878_10kb_smote_dist_chromstates[16,2], #f1
+                                     rfperf_gm12878_10kb_smote_dist_histones[16,2], #f1
+                                     rfperf_gm12878_10kb_smote_dist[16,2], #f1
 
-ggplot(all_rfperfs_gm12878_allvtfbs,
-       aes(x=Resampling, y=Performance, fill=Annotations)) +
+                                     rfperf_gm12878_25kb_smote_dist_tfbs[16,2], #f1
+                                     rfperf_gm12878_25kb_smote_dist_chromstates[16,2], #f1
+                                     rfperf_gm12878_25kb_smote_dist_histones[16,2], #f1
+                                     rfperf_gm12878_25kb_smote_dist[16,2], #f1
+
+                                     rfperf_gm12878_50kb_smote_dist_tfbs[16,2], #f1
+                                     rfperf_gm12878_50kb_smote_dist_chromstates[16,2], #f1
+                                     rfperf_gm12878_50kb_smote_dist_histones[16,2], #f1
+                                     rfperf_gm12878_50kb_smote_dist[16,2], #f1
+
+                                     rfperf_gm12878_100kb_smote_dist_tfbs[16,2], #f1
+                                     rfperf_gm12878_100kb_smote_dist_chromstates[16,2], #f1
+                                     rfperf_gm12878_100kb_smote_dist_histones[16,2], #f1
+                                     rfperf_gm12878_100kb_smote_dist[16,2], #f1
+
+                                     rfperf_gm12878_10kb_smote_dist_tfbs[15,2], #mcc
+                                     rfperf_gm12878_10kb_smote_dist_chromstates[15,2], #mcc
+                                     rfperf_gm12878_10kb_smote_dist_histones[15,2], #mcc
+                                     rfperf_gm12878_10kb_smote_dist[15,2], #mcc
+
+                                     rfperf_gm12878_25kb_smote_dist_tfbs[15,2], #mcc
+                                     rfperf_gm12878_25kb_smote_dist_chromstates[15,2], #mcc
+                                     rfperf_gm12878_25kb_smote_dist_histones[15,2], #mcc
+                                     rfperf_gm12878_25kb_smote_dist[15,2], #mcc
+
+                                     rfperf_gm12878_50kb_smote_dist_tfbs[15,2], #mcc
+                                     rfperf_gm12878_50kb_smote_dist_chromstates[15,2], #mcc
+                                     rfperf_gm12878_50kb_smote_dist_histones[15,2], #mcc
+                                     rfperf_gm12878_50kb_smote_dist[15,2], #mcc
+
+                                     rfperf_gm12878_100kb_smote_dist_tfbs[15,2], #mcc
+                                     rfperf_gm12878_100kb_smote_dist_chromstates[15,2], #mcc
+                                     rfperf_gm12878_100kb_smote_dist_histones[15,2], #mcc
+                                     rfperf_gm12878_100kb_smote_dist[15,2] #mcc
+                                     )
+
+ggplot(all_rfperfs_gm12878,
+       aes(x=Resolution, y=Performance, fill=Annotation)) +
   geom_bar( stat="identity", position="dodge") +
-  facet_grid( ~ Predictor + Metric) +
+  facet_grid( ~ Metric) +
   #xlab("") + ylab("") +
@@
   theme_bw() +
-  scale_fill_discrete(name="Feature Space")+
+  scale_fill_discrete(name="Category of\nFeature Space",
+                      labels=c("Histone\nModifications",
+                               "Chromatin State\nSegmentations",
+                               "Transcription Factor\nBinding Sites",
+                               "All Combined"))+
   #guides(fill=FALSE)+
@@
 ```
+
+# K562; smote; distance types
+
+## 10kb
+
+```{r}
+### TFBS Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_K562_10kb_smote_dist_tfbs <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/tfbs/Distance/ENET/RF/rfperf.rds")
+
+### Chromstates Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_K562_10kb_smote_dist_chromstates <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/chromstates/Distance/ENET/RF/rfperf.rds")
+
+### Histones Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_K562_10kb_smote_dist_histones <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/histones/Distance/ENET/RF/rfperf.rds")
+
+### All Annotations
+####SMOTE
+#####Distance
+rfperf_K562_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+```
+
+## 25kb
+
+```{r}
+### TFBS Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_K562_25kb_smote_dist_tfbs <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/tfbs/Distance/ENET/RF/rfperf.rds")
+
+### Chromstates Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_K562_25kb_smote_dist_chromstates <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/chromstates/Distance/ENET/RF/rfperf.rds")
+
+### Histones Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_K562_25kb_smote_dist_histones <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/histones/Distance/ENET/RF/rfperf.rds")
+
+### All Annotations
+####SMOTE
+#####Distance
+rfperf_K562_25kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+```
+
+## 50kb
+
+```{r}
+### TFBS Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_K562_50kb_smote_dist_tfbs <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/tfbs/Distance/ENET/RF/rfperf.rds")
+
+### Chromstates Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_K562_50kb_smote_dist_chromstates <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/chromstates/Distance/ENET/RF/rfperf.rds")
+
+### Histones Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_K562_50kb_smote_dist_histones <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/histones/Distance/ENET/RF/rfperf.rds")
+
+### All Annotations
+####SMOTE
+#####Distance
+rfperf_K562_50kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+```
+
+## 100kb
+
+```{r}
+### TFBS Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_K562_100kb_smote_dist_tfbs <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/tfbs/Distance/ENET/RF/rfperf.rds")
+
+### Chromstates Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_K562_100kb_smote_dist_chromstates <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/chromstates/Distance/ENET/RF/rfperf.rds")
+
+### Histones Specific Model Performances
+####SMOTE
+#####Distance
+rfperf_K562_100kb_smote_dist_histones <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/histones/Distance/ENET/RF/rfperf.rds")
+
+### All Annotations
+####SMOTE
+#####Distance
+rfperf_K562_100kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+
+```
+
+# Plots
+
+```{r}
+all_rfperfs_K562 <- data.frame(Annotation=rep(c("TFBS", 
+                                               "Chromatin State Segmentations", 
+                                               "Histone Modifications", 
+                                               "All Combined"), 8),
+                                  Resolution=rep(c(rep("10 kb", 4),
+                                               rep("25 kb", 4),
+                                               rep("50 kb", 4),
+                                               rep("100 kb", 4)), 2),
+                                  Metric=c(rep("F1-Score", 16),
+                                           rep("MCC", 16))
+                                  )
+all_rfperfs_K562$Annotation <- factor(all_rfperfs_K562$Annotation, levels=c("Histone Modifications",
+                                                                                  "Chromatin State Segmentations",
+                                                                                  "TFBS",
+                                                                                  "All Combined"))
+all_rfperfs_K562$Resolution <- factor(all_rfperfs_K562$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
+all_rfperfs_K562$Metric <- factor(all_rfperfs_K562$Metric, levels=c("F1-Score", "MCC"))
+
+all_rfperfs_K562$Performance <- c(rfperf_K562_10kb_smote_dist_tfbs[16,2], #f1
+                                     rfperf_K562_10kb_smote_dist_chromstates[16,2], #f1
+                                     rfperf_K562_10kb_smote_dist_histones[16,2], #f1
+                                     rfperf_K562_10kb_smote_dist[16,2], #f1
+
+                                     rfperf_K562_25kb_smote_dist_tfbs[16,2], #f1
+                                     rfperf_K562_25kb_smote_dist_chromstates[16,2], #f1
+                                     rfperf_K562_25kb_smote_dist_histones[16,2], #f1
+                                     rfperf_K562_25kb_smote_dist[16,2], #f1
+
+                                     rfperf_K562_50kb_smote_dist_tfbs[16,2], #f1
+                                     rfperf_K562_50kb_smote_dist_chromstates[16,2], #f1
+                                     rfperf_K562_50kb_smote_dist_histones[16,2], #f1
+                                     rfperf_K562_50kb_smote_dist[16,2], #f1
+
+                                     rfperf_K562_100kb_smote_dist_tfbs[16,2], #f1
+                                     rfperf_K562_100kb_smote_dist_chromstates[16,2], #f1
+                                     rfperf_K562_100kb_smote_dist_histones[16,2], #f1
+                                     rfperf_K562_100kb_smote_dist[16,2], #f1
+
+                                     rfperf_K562_10kb_smote_dist_tfbs[15,2], #mcc
+                                     rfperf_K562_10kb_smote_dist_chromstates[15,2], #mcc
+                                     rfperf_K562_10kb_smote_dist_histones[15,2], #mcc
+                                     rfperf_K562_10kb_smote_dist[15,2], #mcc
+
+                                     rfperf_K562_25kb_smote_dist_tfbs[15,2], #mcc
+                                     rfperf_K562_25kb_smote_dist_chromstates[15,2], #mcc
+                                     rfperf_K562_25kb_smote_dist_histones[15,2], #mcc
+                                     rfperf_K562_25kb_smote_dist[15,2], #mcc
+
+                                     rfperf_K562_50kb_smote_dist_tfbs[15,2], #mcc
+                                     rfperf_K562_50kb_smote_dist_chromstates[15,2], #mcc
+                                     rfperf_K562_50kb_smote_dist_histones[15,2], #mcc
+                                     rfperf_K562_50kb_smote_dist[15,2], #mcc
+
+                                     rfperf_K562_100kb_smote_dist_tfbs[15,2], #mcc
+                                     rfperf_K562_100kb_smote_dist_chromstates[15,2], #mcc
+                                     rfperf_K562_100kb_smote_dist_histones[15,2], #mcc
+                                     rfperf_K562_100kb_smote_dist[15,2] #mcc
+                                     )
+
+ggplot(all_rfperfs_K562,
+       aes(x=Resolution, y=Performance, fill=Annotation)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid( ~ Metric) +
+  #xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  scale_fill_discrete(name="Category of\nFeature Space",
+                      labels=c("Histone\nModifications",
+                               "Chromatin State\nSegmentations",
+                               "Transcription Factor\nBinding Sites",
+                               "All Combined"))+
+  #guides(fill=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        strip.text.x = element_text(size = 15))
+```

### 2019-04-18 Scripts/creating_supplementary_table_of_all_performances.Rmd
editted script for supp table 3

@@
 all_rfperfs_df$Resampling <- rep(c(rep("None",19*12),rep("ROS",19*12),rep("RUS",19*12),rep("SMOTE",19*12)), 2)
-all_rfperfs_df$PredictorType <- rep(c("OC", "OP", "Distance"),19*32)
+all_rfperfs_df$PredictorType <- rep(c(rep("OC",19),
+                                      rep("OP", 19),
+                                      rep("Distance",19)),4*8)
 

### 2019-04-18 Scripts/validating_models_across_cell_lines_clustered_tfbs.Rmd
script to compare performances when validating models across cell lines for models built on clustered tfbs (smote; distance types)

---
title: "Training and validating models across cell lines using clustered TFBS"
author: "Spiro Stilianoudakis"
date: "April 17, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(PRROC)
```

# Reading in GM12878; smote; distance types

## Validating on GM12878

```{r}
#10kb
rfperf_gm12878_10kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#25kb
rfperf_gm12878_25kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#50kb
rfperf_gm12878_50kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#100kb
rfperf_gm12878_100kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

```

## Validating on K562

```{r}
#10kb
rfmodel_gm12878_10kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfModel.rds")
####reading in test data for K562
test <- readRDS("Z:/TAD_data_analysis/K562/10kb/clustered/training_testing/test.rds")
####reading in enetcoefs for K562
vars <- rfmodel_gm12878_10kb_clustered_smote_dist$finalModel$xNames
####reduce test data to match train data
names(test) <- gsub(paste(c("`", 
                          "Clustered", 
                          "-", 
                          #"_", 
                          #"dist", "count", "perc",
                          "TfbsV3"), collapse = "|"), "", names(test))
test <- test[,c(1,which(names(test) %in% vars))]
rfperf_K562_10kb_clustered_smote_dist <- data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)
pred.rfModel <- as.vector(predict(rfmodel_gm12878_10kb_clustered_smote_dist, 
                                  newdata=test, 
                                  type="prob")[,"Yes"])

fg <- pred.rfModel[test$y == "Yes"]
bg <- pred.rfModel[test$y == "No"]
pr <- pr.curve(scores.class0 = fg, scores.class1 = bg, curve = T)

pred.rfModel2 <- predict(rfmodel_gm12878_10kb_clustered_smote_dist,
                         newdata=test,
                         type="raw")

confMat <- confusionMatrix(data=pred.rfModel2, test$y, positive="Yes")
TN = as.numeric(confMat$table[1,1])
FN = as.numeric(confMat$table[1,2])
FP = as.numeric(confMat$table[2,1])
TP = as.numeric(confMat$table[2,2])
rfperf_K562_10kb_clustered_smote_dist[1,2] <- TN
rfperf_K562_10kb_clustered_smote_dist[2,2] <- FN
rfperf_K562_10kb_clustered_smote_dist[3,2] <- FP
rfperf_K562_10kb_clustered_smote_dist[4,2] <- TP
rfperf_K562_10kb_clustered_smote_dist[5,2] <- sum(confMat$table)
rfperf_K562_10kb_clustered_smote_dist[6,2] <- as.vector(confMat$byClass["Sensitivity"])
rfperf_K562_10kb_clustered_smote_dist[7,2] <- as.vector(confMat$byClass["Specificity"])
rfperf_K562_10kb_clustered_smote_dist[8,2] <- as.vector(confMat$overall["Kappa"])
rfperf_K562_10kb_clustered_smote_dist[9,2] <- as.vector(confMat$overall["Accuracy"])
rfperf_K562_10kb_clustered_smote_dist[10,2] <- TP/(TP+FP)
rfperf_K562_10kb_clustered_smote_dist[11,2] <- FP/(FP+TN)
rfperf_K562_10kb_clustered_smote_dist[12,2] <- FN/(FN+TN)
rfperf_K562_10kb_clustered_smote_dist[13,2] <- FN/(FN+TN)
rfperf_K562_10kb_clustered_smote_dist[14,2] <- TN/(TN+FN)
rfperf_K562_10kb_clustered_smote_dist[15,2] <- (TP*TN - FP*FN)/( sqrt( (TP+FP)*(TP+FN)*(TN+FP)*(TN+FN) ) )
rfperf_K562_10kb_clustered_smote_dist[16,2] <- (2*(TP/(TP+FN))*(TP/(TP+FP)))/((TP/(TP+FN)) + ((TP/(TP+FP))))
rfperf_K562_10kb_clustered_smote_dist[17,2] <- pROC::auc(pROC::roc(test$y, pred.rfModel))			
rfperf_K562_10kb_clustered_smote_dist[18,2] <- (TP/(TP + FN)) + (TN/(TN + FP)) - 1
rfperf_K562_10kb_clustered_smote_dist[19,2] <- pr$auc.integral

#25kb
rfmodel_gm12878_25kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfModel.rds")
####reading in test data for K562
test <- readRDS("Z:/TAD_data_analysis/K562/25kb/clustered/training_testing/test.rds")
####reading in enetcoefs for K562
vars <- rfmodel_gm12878_25kb_clustered_smote_dist$finalModel$xNames
####reduce test data to match train data
names(test) <- gsub(paste(c("`", 
                          "Clustered", 
                          "-", 
                          #"_", 
                          #"dist", "count", "perc",
                          "TfbsV3"), collapse = "|"), "", names(test))
test <- test[,c(1,which(names(test) %in% vars))]
rfperf_K562_25kb_clustered_smote_dist <- data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)
pred.rfModel <- as.vector(predict(rfmodel_gm12878_25kb_clustered_smote_dist, 
                                  newdata=test, 
                                  type="prob")[,"Yes"])

fg <- pred.rfModel[test$y == "Yes"]
bg <- pred.rfModel[test$y == "No"]
pr <- pr.curve(scores.class0 = fg, scores.class1 = bg, curve = T)

pred.rfModel2 <- predict(rfmodel_gm12878_25kb_clustered_smote_dist,
                         newdata=test,
                         type="raw")

confMat <- confusionMatrix(data=pred.rfModel2, test$y, positive="Yes")
TN = as.numeric(confMat$table[1,1])
FN = as.numeric(confMat$table[1,2])
FP = as.numeric(confMat$table[2,1])
TP = as.numeric(confMat$table[2,2])
rfperf_K562_25kb_clustered_smote_dist[1,2] <- TN
rfperf_K562_25kb_clustered_smote_dist[2,2] <- FN
rfperf_K562_25kb_clustered_smote_dist[3,2] <- FP
rfperf_K562_25kb_clustered_smote_dist[4,2] <- TP
rfperf_K562_25kb_clustered_smote_dist[5,2] <- sum(confMat$table)
rfperf_K562_25kb_clustered_smote_dist[6,2] <- as.vector(confMat$byClass["Sensitivity"])
rfperf_K562_25kb_clustered_smote_dist[7,2] <- as.vector(confMat$byClass["Specificity"])
rfperf_K562_25kb_clustered_smote_dist[8,2] <- as.vector(confMat$overall["Kappa"])
rfperf_K562_25kb_clustered_smote_dist[9,2] <- as.vector(confMat$overall["Accuracy"])
rfperf_K562_25kb_clustered_smote_dist[10,2] <- TP/(TP+FP)
rfperf_K562_25kb_clustered_smote_dist[11,2] <- FP/(FP+TN)
rfperf_K562_25kb_clustered_smote_dist[12,2] <- FN/(FN+TN)
rfperf_K562_25kb_clustered_smote_dist[13,2] <- FN/(FN+TN)
rfperf_K562_25kb_clustered_smote_dist[14,2] <- TN/(TN+FN)
rfperf_K562_25kb_clustered_smote_dist[15,2] <- (TP*TN - FP*FN)/( sqrt( (TP+FP)*(TP+FN)*(TN+FP)*(TN+FN) ) )
rfperf_K562_25kb_clustered_smote_dist[16,2] <- (2*(TP/(TP+FN))*(TP/(TP+FP)))/((TP/(TP+FN)) + ((TP/(TP+FP))))
rfperf_K562_25kb_clustered_smote_dist[17,2] <- pROC::auc(pROC::roc(test$y, pred.rfModel))			
rfperf_K562_25kb_clustered_smote_dist[18,2] <- (TP/(TP + FN)) + (TN/(TN + FP)) - 1
rfperf_K562_25kb_clustered_smote_dist[19,2] <- pr$auc.integral

#50kb
rfmodel_gm12878_50kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfModel.rds")
####reading in test data for K562
test <- readRDS("Z:/TAD_data_analysis/K562/50kb/clustered/training_testing/test.rds")
####reading in enetcoefs for K562
vars <- rfmodel_gm12878_50kb_clustered_smote_dist$finalModel$xNames
####reduce test data to match train data
names(test) <- gsub(paste(c("`", 
                          "Clustered", 
                          "-", 
                          #"_", 
                          #"dist", "count", "perc",
                          "TfbsV3"), collapse = "|"), "", names(test))
test <- test[,c(1,which(names(test) %in% vars))]
rfperf_K562_50kb_clustered_smote_dist <- data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)
pred.rfModel <- as.vector(predict(rfmodel_gm12878_50kb_clustered_smote_dist, 
                                  newdata=test, 
                                  type="prob")[,"Yes"])

fg <- pred.rfModel[test$y == "Yes"]
bg <- pred.rfModel[test$y == "No"]
pr <- pr.curve(scores.class0 = fg, scores.class1 = bg, curve = T)

pred.rfModel2 <- predict(rfmodel_gm12878_50kb_clustered_smote_dist,
                         newdata=test,
                         type="raw")

confMat <- confusionMatrix(data=pred.rfModel2, test$y, positive="Yes")
TN = as.numeric(confMat$table[1,1])
FN = as.numeric(confMat$table[1,2])
FP = as.numeric(confMat$table[2,1])
TP = as.numeric(confMat$table[2,2])
rfperf_K562_50kb_clustered_smote_dist[1,2] <- TN
rfperf_K562_50kb_clustered_smote_dist[2,2] <- FN
rfperf_K562_50kb_clustered_smote_dist[3,2] <- FP
rfperf_K562_50kb_clustered_smote_dist[4,2] <- TP
rfperf_K562_50kb_clustered_smote_dist[5,2] <- sum(confMat$table)
rfperf_K562_50kb_clustered_smote_dist[6,2] <- as.vector(confMat$byClass["Sensitivity"])
rfperf_K562_50kb_clustered_smote_dist[7,2] <- as.vector(confMat$byClass["Specificity"])
rfperf_K562_50kb_clustered_smote_dist[8,2] <- as.vector(confMat$overall["Kappa"])
rfperf_K562_50kb_clustered_smote_dist[9,2] <- as.vector(confMat$overall["Accuracy"])
rfperf_K562_50kb_clustered_smote_dist[10,2] <- TP/(TP+FP)
rfperf_K562_50kb_clustered_smote_dist[11,2] <- FP/(FP+TN)
rfperf_K562_50kb_clustered_smote_dist[12,2] <- FN/(FN+TN)
rfperf_K562_50kb_clustered_smote_dist[13,2] <- FN/(FN+TN)
rfperf_K562_50kb_clustered_smote_dist[14,2] <- TN/(TN+FN)
rfperf_K562_50kb_clustered_smote_dist[15,2] <- (TP*TN - FP*FN)/( sqrt( (TP+FP)*(TP+FN)*(TN+FP)*(TN+FN) ) )
rfperf_K562_50kb_clustered_smote_dist[16,2] <- (2*(TP/(TP+FN))*(TP/(TP+FP)))/((TP/(TP+FN)) + ((TP/(TP+FP))))
rfperf_K562_50kb_clustered_smote_dist[17,2] <- pROC::auc(pROC::roc(test$y, pred.rfModel))			
rfperf_K562_50kb_clustered_smote_dist[18,2] <- (TP/(TP + FN)) + (TN/(TN + FP)) - 1
rfperf_K562_50kb_clustered_smote_dist[19,2] <- pr$auc.integral

#100kb
rfmodel_gm12878_100kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfModel.rds")
####reading in test data for K562
test <- readRDS("Z:/TAD_data_analysis/K562/100kb/clustered/training_testing/test.rds")
####reading in enetcoefs for K562
vars <- rfmodel_gm12878_100kb_clustered_smote_dist$finalModel$xNames
####reduce test data to match train data
names(test) <- gsub(paste(c("`", 
                          "Clustered", 
                          "-", 
                          #"_", 
                          #"dist", "count", "perc",
                          "TfbsV3"), collapse = "|"), "", names(test))
test <- test[,c(1,which(names(test) %in% vars))]
rfperf_K562_100kb_clustered_smote_dist <- data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)
pred.rfModel <- as.vector(predict(rfmodel_gm12878_100kb_clustered_smote_dist, 
                                  newdata=test, 
                                  type="prob")[,"Yes"])

fg <- pred.rfModel[test$y == "Yes"]
bg <- pred.rfModel[test$y == "No"]
pr <- pr.curve(scores.class0 = fg, scores.class1 = bg, curve = T)

pred.rfModel2 <- predict(rfmodel_gm12878_100kb_clustered_smote_dist,
                         newdata=test,
                         type="raw")

confMat <- confusionMatrix(data=pred.rfModel2, test$y, positive="Yes")
TN = as.numeric(confMat$table[1,1])
FN = as.numeric(confMat$table[1,2])
FP = as.numeric(confMat$table[2,1])
TP = as.numeric(confMat$table[2,2])
rfperf_K562_100kb_clustered_smote_dist[1,2] <- TN
rfperf_K562_100kb_clustered_smote_dist[2,2] <- FN
rfperf_K562_100kb_clustered_smote_dist[3,2] <- FP
rfperf_K562_100kb_clustered_smote_dist[4,2] <- TP
rfperf_K562_100kb_clustered_smote_dist[5,2] <- sum(confMat$table)
rfperf_K562_100kb_clustered_smote_dist[6,2] <- as.vector(confMat$byClass["Sensitivity"])
rfperf_K562_100kb_clustered_smote_dist[7,2] <- as.vector(confMat$byClass["Specificity"])
rfperf_K562_100kb_clustered_smote_dist[8,2] <- as.vector(confMat$overall["Kappa"])
rfperf_K562_100kb_clustered_smote_dist[9,2] <- as.vector(confMat$overall["Accuracy"])
rfperf_K562_100kb_clustered_smote_dist[10,2] <- TP/(TP+FP)
rfperf_K562_100kb_clustered_smote_dist[11,2] <- FP/(FP+TN)
rfperf_K562_100kb_clustered_smote_dist[12,2] <- FN/(FN+TN)
rfperf_K562_100kb_clustered_smote_dist[13,2] <- FN/(FN+TN)
rfperf_K562_100kb_clustered_smote_dist[14,2] <- TN/(TN+FN)
rfperf_K562_100kb_clustered_smote_dist[15,2] <- (TP*TN - FP*FN)/( sqrt( (TP+FP)*(TP+FN)*(TN+FP)*(TN+FN) ) )
rfperf_K562_100kb_clustered_smote_dist[16,2] <- (2*(TP/(TP+FN))*(TP/(TP+FP)))/((TP/(TP+FN)) + ((TP/(TP+FP))))
rfperf_K562_100kb_clustered_smote_dist[17,2] <- pROC::auc(pROC::roc(test$y, pred.rfModel))			
rfperf_K562_100kb_clustered_smote_dist[18,2] <- (TP/(TP + FN)) + (TN/(TN + FP)) - 1
rfperf_K562_100kb_clustered_smote_dist[19,2] <- pr$auc.integral

```

##Plots

```{r}
rfperf_gm12878_validatedon_k562 <- data.frame(Model.Validation=rep(c("GM12878 validated on GM12878", "GM12878 validated on K562"), 8),
                                              Resolution=rep(c(rep("10 kb", 2),
                                                           rep("25 kb", 2),
                                                           rep("50 kb", 2),
                                                           rep("100 kb", 2)), 2),
                                              Metric=c(rep("F1-Score", 8),
                                                       rep("MCC", 8)))

rfperf_gm12878_validatedon_k562$Performance <- c(rfperf_gm12878_10kb_clustered_smote_dist[16,2], #f1
                                                 rfperf_K562_10kb_clustered_smote_dist[16,2], #f1

                                                 rfperf_gm12878_25kb_clustered_smote_dist[16,2], #f1
                                                 rfperf_K562_25kb_clustered_smote_dist[16,2], #f1

                                                 rfperf_gm12878_50kb_clustered_smote_dist[16,2], #f1
                                                 rfperf_K562_50kb_clustered_smote_dist[16,2], #f1

                                                 rfperf_gm12878_100kb_clustered_smote_dist[16,2], #f1
                                                 rfperf_K562_100kb_clustered_smote_dist[16,2], #f1

                                                 rfperf_gm12878_10kb_clustered_smote_dist[15,2], #mcc
                                                 rfperf_K562_10kb_clustered_smote_dist[15,2], #mcc

                                                 rfperf_gm12878_25kb_clustered_smote_dist[15,2], #mcc
                                                 rfperf_K562_25kb_clustered_smote_dist[15,2], #mcc

                                                 rfperf_gm12878_50kb_clustered_smote_dist[15,2], #mcc
                                                 rfperf_K562_50kb_clustered_smote_dist[15,2], #mcc

                                                 rfperf_gm12878_100kb_clustered_smote_dist[15,2], #mcc
                                                 rfperf_K562_100kb_clustered_smote_dist[15,2] #mcc
                                                 )

rfperf_gm12878_validatedon_k562$Resolution <- factor(rfperf_gm12878_validatedon_k562$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
rfperf_gm12878_validatedon_k562$Metric <- factor(rfperf_gm12878_validatedon_k562$Metric, levels=c("F1-Score", "MCC"))
rfperf_gm12878_validatedon_k562$Model.Validation <- factor(rfperf_gm12878_validatedon_k562$Model.Validation, levels=c("GM12878 validated on GM12878", "GM12878 validated on K562"))

ggplot(rfperf_gm12878_validatedon_k562,
       aes(x=Resolution, y=Performance, fill=Model.Validation)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid( ~ Metric) +
  #xlab("") + ylab("") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Model Validation")+
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))                                                 
```

# Reading in K562; smote; distance types

## Validating on K562

```{r}
#10kb
rfperf_K562_10kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#25kb
rfperf_K562_25kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#50kb
rfperf_K562_50kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

#100kb
rfperf_K562_100kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

```

## Validating on GM12878

```{r}
#10kb
rfmodel_K562_10kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfModel.rds")
####reading in test data for GM12878
test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/clustered/training_testing/test.rds")
####reading in enetcoefs for GM12878
vars <- rfmodel_K562_10kb_clustered_smote_dist$finalModel$xNames
####reduce test data to match train data
names(test) <- gsub(paste(c("`", 
                          "Clustered", 
                          "-", 
                          #"_", 
                          #"dist", "count", "perc",
                          "TfbsV3"), collapse = "|"), "", names(test))
test <- test[,c(1,which(names(test) %in% vars))]
rfperf_GM12878_10kb_clustered_smote_dist <- data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)
pred.rfModel <- as.vector(predict(rfmodel_K562_10kb_clustered_smote_dist, 
                                  newdata=test, 
                                  type="prob")[,"Yes"])

fg <- pred.rfModel[test$y == "Yes"]
bg <- pred.rfModel[test$y == "No"]
pr <- pr.curve(scores.class0 = fg, scores.class1 = bg, curve = T)

pred.rfModel2 <- predict(rfmodel_K562_10kb_clustered_smote_dist,
                         newdata=test,
                         type="raw")

confMat <- confusionMatrix(data=pred.rfModel2, test$y, positive="Yes")
TN = as.numeric(confMat$table[1,1])
FN = as.numeric(confMat$table[1,2])
FP = as.numeric(confMat$table[2,1])
TP = as.numeric(confMat$table[2,2])
rfperf_GM12878_10kb_clustered_smote_dist[1,2] <- TN
rfperf_GM12878_10kb_clustered_smote_dist[2,2] <- FN
rfperf_GM12878_10kb_clustered_smote_dist[3,2] <- FP
rfperf_GM12878_10kb_clustered_smote_dist[4,2] <- TP
rfperf_GM12878_10kb_clustered_smote_dist[5,2] <- sum(confMat$table)
rfperf_GM12878_10kb_clustered_smote_dist[6,2] <- as.vector(confMat$byClass["Sensitivity"])
rfperf_GM12878_10kb_clustered_smote_dist[7,2] <- as.vector(confMat$byClass["Specificity"])
rfperf_GM12878_10kb_clustered_smote_dist[8,2] <- as.vector(confMat$overall["Kappa"])
rfperf_GM12878_10kb_clustered_smote_dist[9,2] <- as.vector(confMat$overall["Accuracy"])
rfperf_GM12878_10kb_clustered_smote_dist[10,2] <- TP/(TP+FP)
rfperf_GM12878_10kb_clustered_smote_dist[11,2] <- FP/(FP+TN)
rfperf_GM12878_10kb_clustered_smote_dist[12,2] <- FN/(FN+TN)
rfperf_GM12878_10kb_clustered_smote_dist[13,2] <- FN/(FN+TN)
rfperf_GM12878_10kb_clustered_smote_dist[14,2] <- TN/(TN+FN)
rfperf_GM12878_10kb_clustered_smote_dist[15,2] <- (TP*TN - FP*FN)/( sqrt( (TP+FP)*(TP+FN)*(TN+FP)*(TN+FN) ) )
rfperf_GM12878_10kb_clustered_smote_dist[16,2] <- (2*(TP/(TP+FN))*(TP/(TP+FP)))/((TP/(TP+FN)) + ((TP/(TP+FP))))
rfperf_GM12878_10kb_clustered_smote_dist[17,2] <- pROC::auc(pROC::roc(test$y, pred.rfModel))			
rfperf_GM12878_10kb_clustered_smote_dist[18,2] <- (TP/(TP + FN)) + (TN/(TN + FP)) - 1
rfperf_GM12878_10kb_clustered_smote_dist[19,2] <- pr$auc.integral

#25kb
rfmodel_K562_25kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfModel.rds")
####reading in test data for GM12878
test <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/clustered/training_testing/test.rds")
####reading in enetcoefs for GM12878
vars <- rfmodel_K562_25kb_clustered_smote_dist$finalModel$xNames
####reduce test data to match train data
names(test) <- gsub(paste(c("`", 
                          "Clustered", 
                          "-", 
                          #"_", 
                          #"dist", "count", "perc",
                          "TfbsV3"), collapse = "|"), "", names(test))
test <- test[,c(1,which(names(test) %in% vars))]
rfperf_GM12878_25kb_clustered_smote_dist <- data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)
pred.rfModel <- as.vector(predict(rfmodel_K562_25kb_clustered_smote_dist, 
                                  newdata=test, 
                                  type="prob")[,"Yes"])

fg <- pred.rfModel[test$y == "Yes"]
bg <- pred.rfModel[test$y == "No"]
pr <- pr.curve(scores.class0 = fg, scores.class1 = bg, curve = T)

pred.rfModel2 <- predict(rfmodel_K562_25kb_clustered_smote_dist,
                         newdata=test,
                         type="raw")

confMat <- confusionMatrix(data=pred.rfModel2, test$y, positive="Yes")
TN = as.numeric(confMat$table[1,1])
FN = as.numeric(confMat$table[1,2])
FP = as.numeric(confMat$table[2,1])
TP = as.numeric(confMat$table[2,2])
rfperf_GM12878_25kb_clustered_smote_dist[1,2] <- TN
rfperf_GM12878_25kb_clustered_smote_dist[2,2] <- FN
rfperf_GM12878_25kb_clustered_smote_dist[3,2] <- FP
rfperf_GM12878_25kb_clustered_smote_dist[4,2] <- TP
rfperf_GM12878_25kb_clustered_smote_dist[5,2] <- sum(confMat$table)
rfperf_GM12878_25kb_clustered_smote_dist[6,2] <- as.vector(confMat$byClass["Sensitivity"])
rfperf_GM12878_25kb_clustered_smote_dist[7,2] <- as.vector(confMat$byClass["Specificity"])
rfperf_GM12878_25kb_clustered_smote_dist[8,2] <- as.vector(confMat$overall["Kappa"])
rfperf_GM12878_25kb_clustered_smote_dist[9,2] <- as.vector(confMat$overall["Accuracy"])
rfperf_GM12878_25kb_clustered_smote_dist[10,2] <- TP/(TP+FP)
rfperf_GM12878_25kb_clustered_smote_dist[11,2] <- FP/(FP+TN)
rfperf_GM12878_25kb_clustered_smote_dist[12,2] <- FN/(FN+TN)
rfperf_GM12878_25kb_clustered_smote_dist[13,2] <- FN/(FN+TN)
rfperf_GM12878_25kb_clustered_smote_dist[14,2] <- TN/(TN+FN)
rfperf_GM12878_25kb_clustered_smote_dist[15,2] <- (TP*TN - FP*FN)/( sqrt( (TP+FP)*(TP+FN)*(TN+FP)*(TN+FN) ) )
rfperf_GM12878_25kb_clustered_smote_dist[16,2] <- (2*(TP/(TP+FN))*(TP/(TP+FP)))/((TP/(TP+FN)) + ((TP/(TP+FP))))
rfperf_GM12878_25kb_clustered_smote_dist[17,2] <- pROC::auc(pROC::roc(test$y, pred.rfModel))			
rfperf_GM12878_25kb_clustered_smote_dist[18,2] <- (TP/(TP + FN)) + (TN/(TN + FP)) - 1
rfperf_GM12878_25kb_clustered_smote_dist[19,2] <- pr$auc.integral

#50kb
rfmodel_K562_50kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfModel.rds")
####reading in test data for GM12878
test <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/clustered/training_testing/test.rds")
####reading in enetcoefs for GM12878
vars <- rfmodel_K562_50kb_clustered_smote_dist$finalModel$xNames
####reduce test data to match train data
names(test) <- gsub(paste(c("`", 
                          "Clustered", 
                          "-", 
                          #"_", 
                          #"dist", "count", "perc",
                          "TfbsV3"), collapse = "|"), "", names(test))
test <- test[,c(1,which(names(test) %in% vars))]
rfperf_GM12878_50kb_clustered_smote_dist <- data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)
pred.rfModel <- as.vector(predict(rfmodel_K562_50kb_clustered_smote_dist, 
                                  newdata=test, 
                                  type="prob")[,"Yes"])

fg <- pred.rfModel[test$y == "Yes"]
bg <- pred.rfModel[test$y == "No"]
pr <- pr.curve(scores.class0 = fg, scores.class1 = bg, curve = T)

pred.rfModel2 <- predict(rfmodel_K562_50kb_clustered_smote_dist,
                         newdata=test,
                         type="raw")

confMat <- confusionMatrix(data=pred.rfModel2, test$y, positive="Yes")
TN = as.numeric(confMat$table[1,1])
FN = as.numeric(confMat$table[1,2])
FP = as.numeric(confMat$table[2,1])
TP = as.numeric(confMat$table[2,2])
rfperf_GM12878_50kb_clustered_smote_dist[1,2] <- TN
rfperf_GM12878_50kb_clustered_smote_dist[2,2] <- FN
rfperf_GM12878_50kb_clustered_smote_dist[3,2] <- FP
rfperf_GM12878_50kb_clustered_smote_dist[4,2] <- TP
rfperf_GM12878_50kb_clustered_smote_dist[5,2] <- sum(confMat$table)
rfperf_GM12878_50kb_clustered_smote_dist[6,2] <- as.vector(confMat$byClass["Sensitivity"])
rfperf_GM12878_50kb_clustered_smote_dist[7,2] <- as.vector(confMat$byClass["Specificity"])
rfperf_GM12878_50kb_clustered_smote_dist[8,2] <- as.vector(confMat$overall["Kappa"])
rfperf_GM12878_50kb_clustered_smote_dist[9,2] <- as.vector(confMat$overall["Accuracy"])
rfperf_GM12878_50kb_clustered_smote_dist[10,2] <- TP/(TP+FP)
rfperf_GM12878_50kb_clustered_smote_dist[11,2] <- FP/(FP+TN)
rfperf_GM12878_50kb_clustered_smote_dist[12,2] <- FN/(FN+TN)
rfperf_GM12878_50kb_clustered_smote_dist[13,2] <- FN/(FN+TN)
rfperf_GM12878_50kb_clustered_smote_dist[14,2] <- TN/(TN+FN)
rfperf_GM12878_50kb_clustered_smote_dist[15,2] <- (TP*TN - FP*FN)/( sqrt( (TP+FP)*(TP+FN)*(TN+FP)*(TN+FN) ) )
rfperf_GM12878_50kb_clustered_smote_dist[16,2] <- (2*(TP/(TP+FN))*(TP/(TP+FP)))/((TP/(TP+FN)) + ((TP/(TP+FP))))
rfperf_GM12878_50kb_clustered_smote_dist[17,2] <- pROC::auc(pROC::roc(test$y, pred.rfModel))			
rfperf_GM12878_50kb_clustered_smote_dist[18,2] <- (TP/(TP + FN)) + (TN/(TN + FP)) - 1
rfperf_GM12878_50kb_clustered_smote_dist[19,2] <- pr$auc.integral

#100kb
rfmodel_K562_100kb_clustered_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/clustered/Ensemble/SMOTE/Distance/ENET/RF/rfModel.rds")
####reading in test data for GM12878
test <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/clustered/training_testing/test.rds")
####reading in enetcoefs for GM12878
vars <- rfmodel_K562_100kb_clustered_smote_dist$finalModel$xNames
####reduce test data to match train data
names(test) <- gsub(paste(c("`", 
                          "Clustered", 
                          "-", 
                          #"_", 
                          #"dist", "count", "perc",
                          "TfbsV3"), collapse = "|"), "", names(test))
test <- test[,c(1,which(names(test) %in% vars))]
rfperf_GM12878_100kb_clustered_smote_dist <- data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)
pred.rfModel <- as.vector(predict(rfmodel_K562_100kb_clustered_smote_dist, 
                                  newdata=test, 
                                  type="prob")[,"Yes"])

fg <- pred.rfModel[test$y == "Yes"]
bg <- pred.rfModel[test$y == "No"]
pr <- pr.curve(scores.class0 = fg, scores.class1 = bg, curve = T)

pred.rfModel2 <- predict(rfmodel_K562_100kb_clustered_smote_dist,
                         newdata=test,
                         type="raw")

confMat <- confusionMatrix(data=pred.rfModel2, test$y, positive="Yes")
TN = as.numeric(confMat$table[1,1])
FN = as.numeric(confMat$table[1,2])
FP = as.numeric(confMat$table[2,1])
TP = as.numeric(confMat$table[2,2])
rfperf_GM12878_100kb_clustered_smote_dist[1,2] <- TN
rfperf_GM12878_100kb_clustered_smote_dist[2,2] <- FN
rfperf_GM12878_100kb_clustered_smote_dist[3,2] <- FP
rfperf_GM12878_100kb_clustered_smote_dist[4,2] <- TP
rfperf_GM12878_100kb_clustered_smote_dist[5,2] <- sum(confMat$table)
rfperf_GM12878_100kb_clustered_smote_dist[6,2] <- as.vector(confMat$byClass["Sensitivity"])
rfperf_GM12878_100kb_clustered_smote_dist[7,2] <- as.vector(confMat$byClass["Specificity"])
rfperf_GM12878_100kb_clustered_smote_dist[8,2] <- as.vector(confMat$overall["Kappa"])
rfperf_GM12878_100kb_clustered_smote_dist[9,2] <- as.vector(confMat$overall["Accuracy"])
rfperf_GM12878_100kb_clustered_smote_dist[10,2] <- TP/(TP+FP)
rfperf_GM12878_100kb_clustered_smote_dist[11,2] <- FP/(FP+TN)
rfperf_GM12878_100kb_clustered_smote_dist[12,2] <- FN/(FN+TN)
rfperf_GM12878_100kb_clustered_smote_dist[13,2] <- FN/(FN+TN)
rfperf_GM12878_100kb_clustered_smote_dist[14,2] <- TN/(TN+FN)
rfperf_GM12878_100kb_clustered_smote_dist[15,2] <- (TP*TN - FP*FN)/( sqrt( (TP+FP)*(TP+FN)*(TN+FP)*(TN+FN) ) )
rfperf_GM12878_100kb_clustered_smote_dist[16,2] <- (2*(TP/(TP+FN))*(TP/(TP+FP)))/((TP/(TP+FN)) + ((TP/(TP+FP))))
rfperf_GM12878_100kb_clustered_smote_dist[17,2] <- pROC::auc(pROC::roc(test$y, pred.rfModel))			
rfperf_GM12878_100kb_clustered_smote_dist[18,2] <- (TP/(TP + FN)) + (TN/(TN + FP)) - 1
rfperf_GM12878_100kb_clustered_smote_dist[19,2] <- pr$auc.integral

```

## Plots

```{r}
rfperf_k562_validatedon_gm12878 <- data.frame(Model.Validation=rep(c("K562 validated on K562", "K562 validated on GM12878"), 8),
                                              Resolution=rep(c(rep("10 kb", 2),
                                                           rep("25 kb", 2),
                                                           rep("50 kb", 2),
                                                           rep("100 kb", 2)), 2),
                                              Metric=c(rep("F1-Score", 8),
                                                       rep("MCC", 8)))

rfperf_k562_validatedon_gm12878$Performance <- c(rfperf_K562_10kb_clustered_smote_dist[16,2], #f1
                                                 rfperf_GM12878_10kb_clustered_smote_dist[16,2], #f1

                                                 rfperf_K562_25kb_clustered_smote_dist[16,2], #f1
                                                 rfperf_GM12878_25kb_clustered_smote_dist[16,2], #f1

                                                 rfperf_K562_50kb_clustered_smote_dist[16,2], #f1
                                                 rfperf_GM12878_50kb_clustered_smote_dist[16,2], #f1

                                                 rfperf_K562_100kb_clustered_smote_dist[16,2], #f1
                                                 rfperf_GM12878_100kb_clustered_smote_dist[16,2], #f1

                                                 rfperf_K562_10kb_clustered_smote_dist[15,2], #mcc
                                                 rfperf_GM12878_10kb_clustered_smote_dist[15,2], #mcc

                                                 rfperf_K562_25kb_clustered_smote_dist[15,2], #mcc
                                                 rfperf_GM12878_25kb_clustered_smote_dist[15,2], #mcc

                                                 rfperf_K562_50kb_clustered_smote_dist[15,2], #mcc
                                                 rfperf_GM12878_50kb_clustered_smote_dist[15,2], #mcc

                                                 rfperf_K562_100kb_clustered_smote_dist[15,2], #mcc
                                                 rfperf_GM12878_100kb_clustered_smote_dist[15,2] #mcc
                                                 )

rfperf_k562_validatedon_gm12878$Resolution <- factor(rfperf_k562_validatedon_gm12878$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
rfperf_k562_validatedon_gm12878$Metric <- factor(rfperf_k562_validatedon_gm12878$Metric, levels=c("F1-Score", "MCC"))
rfperf_k562_validatedon_gm12878$Model.Validation <- factor(rfperf_k562_validatedon_gm12878$Model.Validation, levels=c("K562 validated on K562", "K562 validated on GM12878"))

ggplot(rfperf_k562_validatedon_gm12878,
       aes(x=Resolution, y=Performance, fill=Model.Validation)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid( ~ Metric) +
  #xlab("") + ylab("") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Model Validation")+
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))   
```

### 2019-04-18 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-Multiple random forest classification algorithms were built on domain data extracted from Hi-C data for 2 cell lines $C = \{GM12878, K562\}$, at four different resolutions $R = \{\text{10 kb}, \text{25 kb}, \text{50 kb}, \text{100 kb\}}$.
-For each classifier, we compared model performances using 3 separate predictor types $P = \{\text{OC}, \text{OP}, \text{Distance}\}$ and 4 class balancing techniques $B = \{None, RUS, ROS, SMOTE\}$.
-A system produced from the ensemble framework was defined as: $S = \{c, r, p, b\}$, where $c \in C$, $r \in R$, $p \in P$, and $b \in B$.
+Multiple random forest classification algorithms were built on domain data extracted from Hi-C data for 2 cell lines $C = \{\textit{GM12878}, \textit{K562}\}$, at four different resolutions $R = \{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$.
+For each classifier, we compared model performances using 3 separate predictor types $P = \{\textit{OC}, \textit{OP}, \textit{Distance}\}$ and 4 class balancing techniques $B = \{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$.
+A system produced from the ensemble framework was defined as: $S = \{\textit{c}, \textit{r}, \textit{p}, \textit{b}\}$, where $c \in C$, $r \in R$, $p \in P$, and $b \in B$.
 Letting $|X|$ denote the cardinality of each set, we evaluated $|C| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $96 (= 2 \times 4 \times 3 \times 4)$ separate models.
@@
 We first evaluated performances for models implemented using OC predictor types, without re-sampling, as these characteristics represented models with the least granularity and could act as a baseline.
-In evaluating such composite metrics like F1-Score and MCC, we found that these models exhibited poor performances across resolutions, for both cell lines (Figure 5A).
-Furthermore, at some resolutions , the F1-Score and MCC could not be determined given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives <!--, as can be seen by the missing red points-->.
-When including OP perdictor types in the models, coupled with no resampling, we found that performances were worse than when using OC predictor types (Figure 5B).
-As with OC predictor types, these models were also not able to yield F1-Scores and MCCs at the 50 kb and 100 kb resolution for the GM12878 cell line or any resolution lower than 10 kb for the K562 cell line.
-Models built on distance-type predictors, however, exhibited slightly better performances than the other two types, yet still yielded missing or low F1-Scores and MCC at lower resolutions (Figure 5C).
-Models built on 100 kb resolutions were not able to yeild F1-Scores for either cell line.
-This indicated that the key driver leading to poor performances was not due to feature engineering, but instead the severity in the class imbalance.
-<!--Mention AUC is not good metric using supplementary table-->
+In evaluating such composite metrics like F1-Score and MCC, we found that these models exhibited poor performances across resolutions, for the GM12878 cell line (Figure 5A).
+The average F1-Score and MCC across resolution was found to be 0.04 and 0.07 respectively.
+When including OP perdictor types as the feature space, coupled with no resampling, we found that performances were worse than when using OC predictor types for the GM12878 cell line (Figure 5B).
+Here, the average F1-Score and MCC was found to be 0.01 and 0.03 respectively.
+Models built on distance-type predictors in conjuction with no resampling, however, were found to exhibit slightly better performances than the other two types, with average F1-Scores and MCCs of 0.08 and 0.10 respectively (Figure 5C).
+Importantly, when validating models built on fully imbalanced datasets, the F1-Score and MCC could not be determined at lower resolutions given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives.
+Furthermore, evaluating models using conventional metrics such as AUC or accuracy did not depict the true severity in performance.
+The average AUC across resolutions for the OC, OP, and distance type predictors was 0.65, 0.66, and 0.85 respectively, where as the average accuracies were 0.89, 0.89, and 0.90 respectively (Supplementary Table 3).
 

### 2019-04-18 Manuscript/manuscript.Rmd
manuscript edits

@@
 In evaluating such composite metrics like F1-Score and MCC, we found that these models exhibited poor performances across resolutions, for the GM12878 cell line (Figure 5A).
-The average F1-Score and MCC across resolution was found to be 0.04 and 0.07 respectively.
-When including OP perdictor types as the feature space, coupled with no resampling, we found that performances were worse than when using OC predictor types for the GM12878 cell line (Figure 5B).
-Here, the average F1-Score and MCC was found to be 0.01 and 0.03 respectively.
-Models built on distance-type predictors in conjuction with no resampling, however, were found to exhibit slightly better performances than the other two types, with average F1-Scores and MCCs of 0.08 and 0.10 respectively (Figure 5C).
+<!--The average F1-Score and MCC across resolution was found to be 0.04 and 0.07 respectively.--> When including OP perdictor types as the feature space, coupled with no resampling, we found that performances were worse than when using OC predictor types for the GM12878 cell line (Figure 5B).
+<!--Here, the average F1-Score and MCC was found to be 0.01 and 0.03 respectively.--> Models built on distance-type predictors in conjuction with no resampling, however, were found to exhibit slightly better performances than the other two types<!--, with average F1-Scores and MCCs of 0.08 and 0.10 respectively--> (Figure 5C).
 Importantly, when validating models built on fully imbalanced datasets, the F1-Score and MCC could not be determined at lower resolutions given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives.
-Furthermore, evaluating models using conventional metrics such as AUC or accuracy did not depict the true severity in performance.
-The average AUC across resolutions for the OC, OP, and distance type predictors was 0.65, 0.66, and 0.85 respectively, where as the average accuracies were 0.89, 0.89, and 0.90 respectively (Supplementary Table 3).
+Furthermore, evaluating models using conventional metrics such as AUC or accuracy did not depict the true severity in performance (Supplementary Table 3).
+<!--The average AUC across resolutions for the OC, OP, and distance type predictors was 0.65, 0.66, and 0.85 respectively, where as the average accuracies were 0.89, 0.89, and 0.90 respectively (Supplementary Table 3).--> Results were found to be consistently poor across resolutions for the K562 cell line (Supplementary Figure 10).
+Similarly, many of the performance metrics at higher resolutions were unable to be reported due to the models inability to produce any true positive cases.
 
-## DATA RE-SAMPLING IMPROVED PERFORMANCE AMONG ALL CLASSES OF MODELS
+## DATA RE-SAMPLING COUPLED WITH THE INCLUSION OF A DISTANCE-TYPE FEATURE SPACE IMPROVED PERFORMANCES AMONG ALL CLASSES OF MODELS
 
 Comparisons of the effects of the various resampling techniques were then made.
-When models were built on randomly oversampled data, we found a substantial increase in F1-Score and MCC for both cell lines (Figure 5 D-F).
-The biggest improvement in performance was seen at the 10 kb resolution, with a sharp downward trend as resolutions decreased.
+When models were built on randomly oversampled (ROS) data, we found a substantial increase in F1-Score and MCC for the GM12878 cell line (Figure 5).
+The biggest improvement in performance was seen at the 10 kb resolution, with a downward trend as resolutions decreased.
 Although performances were low at lower resolutions, both F1-Scores and MCC values were able to be obtained, contrary to models built on completely unbalanced data as seen before.
-Distance-type predictors were found to offer the highest F1-Scores and MCCs for randomly oversampled data, across all resolutions and for both cell lines.
+Distance-type predictors were found to offer the highest F1-Scores and MCCs for ROS data, across all resolutions.
+Similar results were obtained when applying ROS to the K562 cell line (Supplementary Figure 10).
+Here, a much sharper negative trend was featured for both F1-Score and MCC and resolution decreased, than in the GM12878 cell line.
 
-Further improvement in performance was found when models were implemented on both randomly undersampled (Figure 5 G-H) and SMOTE resampled data (Figure 5 J-K).
-Although the differences in performance between the two techniques were marginal, SMOTE resampled data was found to yield the best F1-Scores and MCCs among all classes of models develeped and compared in the ensemble framework.
+Further improvement in performance was found when models were implemented on both randomly undersampled (RUS) and SMOTE resampled data, for all 3 predictor types (Figure 5).
+Although the differences in performance between the two techniques were marginal, SMOTE resampled data was found to yield the best F1-Scores and MCCs among all classes of models developed and compared in the ensemble framework.
+As with ROS, distance type predictors yeilded the highest F1-Score and MCC values across resolutions, when applied to either RUS or SMOTE.
+SMOTE re-sampled data, with the inclusion of distance-type predictors was also found to be the best set of characteristics when applied to the K562 cell line (Supplementary Figure 10).
 These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that incorporates both random under- and over-sampling, as SMOTE is known to do.
+Likewise, it appears that distance-type predictors provided the most informative spatial representation of epigenomic annotations associated with TAD boundaries.
 
-## DISTANCE-TYPE PREDICTORS PROVIDED THE MOST INFORMATIVE SPATIAL REPRESENTATION OF EPIGENOMIC ANNOTATIONS ASSOCIATED WITH TAD BOUNDARIES
-
-Regardless, of resampling technique however, the inclusion of distance type predictors resulted in better F1-Scores and MCCs when compared to either OC or OP predictor types.
-This was consistent across all resolutions, for both cell lines.
-Furthermore, in the best overall model (SMOTE with distance-type predictors) we found that the degradation in model performance as resolution decreased was much more pronounced in the K562 cell line.
-on the GM12878 cell line, there was a slight improvement in F1-Score for the 25 kb resolution, followed by a steep decline at 50 kb.
-Then, both F1-Scores and MCCs showed a momentary increase in performance at the lowest resolution considered in the study.
-Performances from the K562 cell line degraded much faster as resolution decreased, the worse being at the 100 kb resolution.
+Moreover, we found that there was a degredation in model performance as data resolution decreased.
+This was much more pronounced in the K562 cell line.
+On the GM12878 cell line, there were only marginal differences in performance between 10 kb and 25 kb, followed by a steep decline at 50 kb.
+Then, both F1-Scores and MCCs showed a momentary increase in performance at 100 kb, the lowest resolution considered in the study.
+Performances from the K562 cell line degraded much faster as resolution decreased, starting with highest performance at 10 kb and ending with the worst performance at 100 kb.
 

### 2019-04-18 Manuscript/manuscript.Rmd
manuscript edits

@@
 SMOTE re-sampled data, with the inclusion of distance-type predictors was also found to be the best set of characteristics when applied to the K562 cell line (Supplementary Figure 10).
-These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that incorporates both random under- and over-sampling, as SMOTE is known to do.
-Likewise, it appears that distance-type predictors provided the most informative spatial representation of epigenomic annotations associated with TAD boundaries.
 
@@
 Performances from the K562 cell line degraded much faster as resolution decreased, starting with highest performance at 10 kb and ending with the worst performance at 100 kb.
+
+These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that incorporates both random under- and over-sampling, as SMOTE is known to do.
+Additionally, when we performed and evaluated the variable importances of random forest models built on one genomic annotation at a time (including the 3 predictor types each), we found that the distance-type consistently out-ranked the OC and OP type predictors in terms of predictive importance, for a majority of the cell line specific annotations, across resolution and cell line (Supplementary Tables 4 & 5).
+Therefore, it appears that distance-type predictors provided the most informative spatial representation of epigenomic annotations associated with TAD boundaries.
 

### 2019-04-18 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-Lastly, we investigated which genomic annotations were most predictive of TAD boundary formation.
-Looking at heatmaps of variable importances provided by the random forest classifiers implemented on SMOTE re-sampled data, with distance-type predictors, we found that known transcription factors associated with the hypothesized loop extrusion model [@fudenberg2016formation; @alipour2012self] were give high predictive importance in the model for both cell lines (Figure 6 A-B).
-These tended to include the SMC3ab, ZNF143, CTCF, and RAD21 transcription factor binding sites and were found to be ranked consistly across resolution.
-Other annotations known to be associated with gene regulation and affect structural properties of chromatin, such as the YY1 and MAZ transcription factors, as well DNAse hypersensitive sites, regions of heterochromatin, and the H3k27 trimethylation and H3K4me1 modifications were less consistently ranked across resolutions for either cell line.
-Moreover, the ranking profiles of genomic annotations were found to be more similar between the 10 kb and 25 kb resolutions, as well as between the 50 kb and 100 kb resoluions.
+We then investigated which genomic annotations were most predictive of TAD boundary formation, across resolution for random forest models with the best given set of data-level characteristics determined above (SMOTE re-sampled with distance type predictors).
+We found that specific transcription factor binding sites, including SMC3ab, ZNF143, CTCF, and RAD21, were given consistently high rankings of predictive importance in the models built on the GM12878 cell line (Table 1).
+These are known factors associated with the hypothesized loop extrusion model [@fudenberg2016formation; @alipour2012self] and were found to be ranked consistently high on the K562 cell line as well, with similar rankings across resolutions (Supplementary Table 6).
+Other annotations known to be associated with gene regulation and affect structural properties of chromatin, such as the YY1  transcription factor, as well DNAse hypersensitive sites, regions of heterochromatin, and the H3k27 trimethylation histone modifications were ranked high on the 10 kb resolution, but were less consistently ranked at lower resolutions for both cell lines.
+<!--Moreover, the ranking profiles of genomic annotations for both cell lines were found to be more similar between the 10 kb and 25 kb resolutions, as well as between the 50 kb and 100 kb resoluions (this is proved when looking at a clustered heatmap).-->
 

### 2019-04-19 Manuscript/manuscript.Rmd
manuscript edits

@@
 We then investigated which genomic annotations were most predictive of TAD boundary formation, across resolution for random forest models with the best given set of data-level characteristics determined above (SMOTE re-sampled with distance type predictors).
-We found that specific transcription factor binding sites, including SMC3ab, ZNF143, CTCF, and RAD21, were given consistently high rankings of predictive importance in the models built on the GM12878 cell line (Table 1).
+We found that specific transcription factor binding sites (TFBS), including SMC3ab, ZNF143, CTCF, and RAD21, were given consistently high rankings of predictive importance in the models built on the GM12878 cell line (Table 1).
 These are known factors associated with the hypothesized loop extrusion model [@fudenberg2016formation; @alipour2012self] and were found to be ranked consistently high on the K562 cell line as well, with similar rankings across resolutions (Supplementary Table 6).
@@
 <!--Moreover, the ranking profiles of genomic annotations for both cell lines were found to be more similar between the 10 kb and 25 kb resolutions, as well as between the 50 kb and 100 kb resoluions (this is proved when looking at a clustered heatmap).-->
+
+Given the prevalence of TFBS as the most consistently top ranked predictive features across resolution and cell line, we ventured to further compare performances of annotation specific models.
+After applying SMOTE re-sampling with distance type predictors, random forest models built on sets of histone modifications, chromatin state segmentations, and TFBS were compared to a model that included all three types together.
+For the GM12878 cell line, models built simply on TFBS were found to perform just as well as models that included all 3 sets of annotations according to F1-Score and MCC, consistently across resolution (Figure 6).
+Similar results were found when evaluating the K562 cell line (supplementary Figure 11).
 

### 2019-04-19 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-## VARIABLE IMPORTANCES FROM TOP PERFORMING MODELS CONFIRMED BIOLOGICAL FUNCTIONALITY OF KNOWN GENOMIC ANNOTATIONS
+## VARIABLE IMPORTANCES FROM TOP PERFORMING MODELS CONFIRMED BIOLOGICAL FUNCTIONALITY OF KNOWN TRANSCRIPTION FACTOR BINDING SITES
 
@@
 Similar results were found when evaluating the K562 cell line (supplementary Figure 11).
+For both resolutions, models built on only histone modifications were found to have the lowest F1-Scores and MCC, across resolutions, followed by models built on chromatin state segmentations.
+
+Distance profiles on a $log_{2}$ scale were found to exhibit significantly different densities between classes of genomic bins for TFBS with highly ranked predictive importances.
+Using permutation tests we found that the transcription factors SMC3a, ZNF143, CTCF, and RAD21 tended to have binding peaks that that were located closer to the centers of 10 kb sized genomic bins that overlapped with flanked TAD boundaries than to bins that did not overlap with flanked TAD boundaries across both cell lines (Figure 7 A-H).
+Similar distance profiles for the same TFBS were obtained when assessed at lower resolutions, across both cell lines (Supplementary Figures X-X)
 

### 2019-04-19 Scripts/comparing_distance_densities_by_genomic_bin_class.Rmd
editted results script

--- 2019-04-17 Scripts/comparing_distance_densities_by_genomic_bin_class.Rmd
@@
 
-## Function for ploting distance densities between bins with and without TAD boundaries
+## 10kb
 
 ```{r}
-distplotsfunc <- function(cl, resolution, annotation){
-  train <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/training_testing/train.rds"))
-  data <- train[, c(1, which(names(train)==annotation))]
+train <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds"))
+
+enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))
+
+names(train) <- gsub(paste(c("`", 
+                             "Gm12878", 
+                             "-", 
+                             #"_", 
+                             #"dist", "count", "perc",
+                             "Haib", 
+                             "Sydh",
+                             "Uta",
+                             "Uw",
+                             "Broad",
+                             "Uchicago"), collapse = "|"), "", names(train))
+train <- train[,c(1,which(names(train) %in% enetcoefs))]
 
 set.seed(123)
-  majorityids <- sample(x=which(data$y=="No"), size=length(which(data$y=="Yes")))
-  annotdata <- rbind.data.frame(data[which(data$y=="Yes"),],
-                                data[majorityids,])
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
 
-  #ks.test(annotdata[which(annotdata$y=="No"),2], annotdata[which(annotdata$y=="Yes"),2], alternative = "two.sided")
+```
 
-  perm.pval <- pvalue(oneway_test(annotdata[,2] ~ annotdata[,1],
-                     data=annotdata,
+### Top Annotations
+
+####SMC
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Smc3ab9263-Sydh_dist")
+
+annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
+                     data=annotdata.smc,
                      alternative="greater", 
@@
 
-  if(perm.pval==0){perm.pval="< 0.0001"}
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
 
@@
                           "",
-                          annotation))
+                          "Gm12878-Smc3ab9263-Sydh_dist"))
 
-  p <- ggplot(annotdata, aes(x=annotdata[,2], color=y)) +
+p.gm12878.10kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
     geom_density() +
@@
                          labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
-    ylab("Frequency") +
-    xlab("Log2 Distance") +
-    ggtitle(paste(plottitle)) +
-    annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    ylab("") +
+    xlab("") +
+    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
     theme_bw() +
@@
                               hjust=.5))
+```
 
-  ggsave(p, 
-         filename = paste0("C:/Users/stili/Documents/TAD_miscellaneous/figures/comparing_distance_by_bin_class/", 
-                           cl, 
-                           "_", 
-                           resolution, 
-                           "_", 
-                           plottitle, 
-                           ".png"),
-         width=10,
-         height=10,
-         units="in")
-}
+####ZNF143
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Znf143166181ap-Sydh_dist")
+
+annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
+                     data=annotdata.znf143,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Znf143166181ap-Sydh_dist"))
+
+p.gm12878.10kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143166181ap_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####CTCF
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Ctcf-Broad_dist")
+
+annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
+                     data=annotdata.ctcf,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Ctcf-Broad_dist"))
+
+p.gm12878.10kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####RAD21
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Rad21-Haib_dist")
+
+annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
+                     data=annotdata.rad21,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Rad21-Haib_dist"))
+
+p.gm12878.10kb.rad21 <- ggplot(annotdata.rad21, aes(x=Rad21_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("RAD21\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+## 25kb
+
+```{r}
+train <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds"))
+
+enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))
+
+names(train) <- gsub(paste(c("`", 
+                             "Gm12878", 
+                             "-", 
+                             #"_", 
+                             #"dist", "count", "perc",
+                             "Haib", 
+                             "Sydh",
+                             "Uta",
+                             "Uw",
+                             "Broad",
+                             "Uchicago"), collapse = "|"), "", names(train))
+train <- train[,c(1,which(names(train) %in% enetcoefs))]
+
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
 
@@
 
-### 10kb
+### Top Annotations
 
-#### Top Annotations
+####SMC
 
 ```{r}
-#### CTCF
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Smc3ab9263-Sydh_dist")
 
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Ctcf-Broad_dist")
+annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]
 
-#### Smc3ab9263
+#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")
 
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")
+perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
+                     data=annotdata.smc,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
 
-#### Znf143166181ap
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
 
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Smc3ab9263-Sydh_dist"))
 
-#### Rad21
-
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Rad21-Haib_dist")
-
-#### 08Insulator
-
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-08Insulator_dist")
-
-#### Yy1sc281
-
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Yy1sc281-Haib_dist")
-
-#### DNase
-
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-DNase_dist")
+p.gm12878.25kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
 ```
 
-### 25kb
-
-#### Top Annotations
+####ZNF143
 
 ```{r}
-#### CTCF
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Znf143166181ap-Sydh_dist")
 
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Ctcf-Broad_dist")
+annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]
 
-#### Smc3ab9263
+#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")
 
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")
+perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
+                     data=annotdata.znf143,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
 
-#### Znf143166181ap
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
 
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Znf143166181ap-Sydh_dist"))
 
-#### Rad21
-
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Rad21-Haib_dist")
-
-#### 08Insulator
-
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-08Insulator_dist")
-
-#### Yy1sc281
-
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Yy1sc281-Haib_dist")
-
-#### DNase
-
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-DNase_dist")
+p.gm12878.25kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143166181ap_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
 ```
 
-### 50kb
-
-#### Top Annotations
+####CTCF
 
 ```{r}
-#### CTCF
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Ctcf-Broad_dist")
 
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Ctcf-Broad_dist")
+annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]
 
-#### Smc3ab9263
+#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")
 
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")
+perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
+                     data=annotdata.ctcf,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
 
-#### Znf143166181ap
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
 
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Ctcf-Broad_dist"))
 
-#### Rad21
-
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Rad21-Haib_dist")
-
-#### 08Insulator
-
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-08Insulator_dist")
-
-#### Yy1sc281
-
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Yy1sc281-Haib_dist")
-
-#### DNase
-
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-DNase_dist")
+p.gm12878.25kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
 ```
 
-### 100kb
-
-#### Top Annotations
+####RAD21
 
 ```{r}
-#### CTCF
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Rad21-Haib_dist")
 
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Ctcf-Broad_dist")
+annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]
 
-#### Smc3ab9263
+#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")
 
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")
+perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
+                     data=annotdata.rad21,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
 
-#### Znf143166181ap
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
 
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Rad21-Haib_dist"))
 
-#### Rad21
+p.gm12878.25kb.rad21 <- ggplot(annotdata.rad21, aes(x=Rad21_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("RAD21\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
 
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Rad21-Haib_dist")
+## 50kb
 
-#### 08Insulator
+```{r}
+train <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds"))
 
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-08Insulator_dist")
+enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))
 
-#### Yy1sc281
+names(train) <- gsub(paste(c("`", 
+                             "Gm12878", 
+                             "-", 
+                             #"_", 
+                             #"dist", "count", "perc",
+                             "Haib", 
+                             "Sydh",
+                             "Uta",
+                             "Uw",
+                             "Broad",
+                             "Uchicago"), collapse = "|"), "", names(train))
+train <- train[,c(1,which(names(train) %in% enetcoefs))]
 
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Yy1sc281-Haib_dist")
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
 
-#### DNase
+```
 
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-DNase_dist")
+### Top Annotations
+
+####SMC
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Smc3ab9263-Sydh_dist")
+
+annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
+                     data=annotdata.smc,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Smc3ab9263-Sydh_dist"))
+
+p.gm12878.50kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
 ```
+
+####ZNF143
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Znf143166181ap-Sydh_dist")
+
+annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
+                     data=annotdata.znf143,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Znf143166181ap-Sydh_dist"))
+
+p.gm12878.50kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143166181ap_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####CTCF
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Ctcf-Broad_dist")
+
+annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
+                     data=annotdata.ctcf,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Ctcf-Broad_dist"))
+
+p.gm12878.50kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####RAD21
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Rad21-Haib_dist")
+
+annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
+                     data=annotdata.rad21,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Rad21-Haib_dist"))
+
+p.gm12878.50kb.rad21 <- ggplot(annotdata.rad21, aes(x=Rad21_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("RAD21\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+## 100kb
+
+```{r}
+train <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds"))
+
+enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))
+
+names(train) <- gsub(paste(c("`", 
+                             "Gm12878", 
+                             "-", 
+                             #"_", 
+                             #"dist", "count", "perc",
+                             "Haib", 
+                             "Sydh",
+                             "Uta",
+                             "Uw",
+                             "Broad",
+                             "Uchicago"), collapse = "|"), "", names(train))
+train <- train[,c(1,which(names(train) %in% enetcoefs))]
+
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+```
+
+### Top Annotations
+
+####SMC
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Smc3ab9263-Sydh_dist")
+
+annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
+                     data=annotdata.smc,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Smc3ab9263-Sydh_dist"))
+
+p.gm12878.100kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####ZNF143
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Znf143166181ap-Sydh_dist")
+
+annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
+                     data=annotdata.znf143,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Znf143166181ap-Sydh_dist"))
+
+p.gm12878.100kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143166181ap_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####CTCF
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Ctcf-Broad_dist")
+
+annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
+                     data=annotdata.ctcf,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Ctcf-Broad_dist"))
+
+p.gm12878.100kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####RAD21
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Rad21-Haib_dist")
+
+annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
+                     data=annotdata.rad21,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Rad21-Haib_dist"))
+
+p.gm12878.100kb.rad21 <- ggplot(annotdata.rad21, aes(x=Rad21_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("RAD21\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+# K562
+
+## 10kb
+
+```{r}
+train <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds"))
+
+enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))
+
+names(train) <- gsub(paste(c("`", 
+                             "K562", 
+                             "-", 
+                             #"_", 
+                             #"dist", "count", "perc",
+                             "Haib", 
+                             "Sydh",
+                             "Uta",
+                             "Uw",
+                             "Broad",
+                             "Uchicago"), collapse = "|"), "", names(train))
+train <- train[,c(1,which(names(train) %in% enetcoefs))]
+
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+```
+
+### Top Annotations
+
+####SMC
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Smc3ab9263-Sydh_dist")
+
+annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
+                     data=annotdata.smc,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Smc3ab9263-Sydh_dist"))
+
+p.K562.10kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####ZNF143
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Znf143-Sydh_dist")
+
+annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
+                     data=annotdata.znf143,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Znf143-Sydh_dist"))
+
+p.K562.10kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####CTCF
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Ctcf-Broad_dist")
+
+annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
+                     data=annotdata.ctcf,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Ctcf-Broad_dist"))
+
+p.K562.10kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####RAD21
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Rad21-Haib_dist")
+
+annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
+                     data=annotdata.rad21,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Rad21-Haib_dist"))
+
+p.K562.10kb.rad21 <- ggplot(annotdata.rad21, aes(x=Rad21_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("RAD21\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+## 25kb
+
+```{r}
+train <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds"))
+
+enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))
+
+names(train) <- gsub(paste(c("`", 
+                             "K562", 
+                             "-", 
+                             #"_", 
+                             #"dist", "count", "perc",
+                             "Haib", 
+                             "Sydh",
+                             "Uta",
+                             "Uw",
+                             "Broad",
+                             "Uchicago"), collapse = "|"), "", names(train))
+train <- train[,c(1,which(names(train) %in% enetcoefs))]
+
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+```
+
+### Top Annotations
+
+####SMC
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Smc3ab9263-Sydh_dist")
+
+annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
+                     data=annotdata.smc,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Smc3ab9263-Sydh_dist"))
+
+p.K562.25kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####ZNF143
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Znf143-Sydh_dist")
+
+annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
+                     data=annotdata.znf143,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Znf143-Sydh_dist"))
+
+p.K562.25kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####CTCF
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Ctcf-Broad_dist")
+
+annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
+                     data=annotdata.ctcf,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Ctcf-Broad_dist"))
+
+p.K562.25kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####RAD21
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Rad21-Haib_dist")
+
+annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
+                     data=annotdata.rad21,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Rad21-Haib_dist"))
+
+p.K562.25kb.rad21 <- ggplot(annotdata.rad21, aes(x=Rad21_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("RAD21\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+## 50kb
+
+```{r}
+train <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds"))
+
+enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))
+
+names(train) <- gsub(paste(c("`", 
+                             "K562", 
+                             "-", 
+                             #"_", 
+                             #"dist", "count", "perc",
+                             "Haib", 
+                             "Sydh",
+                             "Uta",
+                             "Uw",
+                             "Broad",
+                             "Uchicago"), collapse = "|"), "", names(train))
+train <- train[,c(1,which(names(train) %in% enetcoefs))]
+
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+```
+
+### Top Annotations
+
+####SMC
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Smc3ab9263-Sydh_dist")
+
+annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
+                     data=annotdata.smc,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Smc3ab9263-Sydh_dist"))
+
+p.K562.50kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####ZNF143
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Znf143-Sydh_dist")
+
+annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
+                     data=annotdata.znf143,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Znf143-Sydh_dist"))
+
+p.K562.50kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####CTCF
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Ctcf-Broad_dist")
+
+annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
+                     data=annotdata.ctcf,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Ctcf-Broad_dist"))
+
+p.K562.50kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####RAD21
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Rad21-Haib_dist")
+
+annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
+                     data=annotdata.rad21,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Rad21-Haib_dist"))
+
+p.K562.50kb.rad21 <- ggplot(annotdata.rad21, aes(x=Rad21_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("RAD21\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+## 100kb
+
+```{r}
+train <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds"))
+
+enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))
+
+names(train) <- gsub(paste(c("`", 
+                             "K562", 
+                             "-", 
+                             #"_", 
+                             #"dist", "count", "perc",
+                             "Haib", 
+                             "Sydh",
+                             "Uta",
+                             "Uw",
+                             "Broad",
+                             "Uchicago"), collapse = "|"), "", names(train))
+train <- train[,c(1,which(names(train) %in% enetcoefs))]
+
+set.seed(123)
+train_smote <- SMOTE(y ~ ., 
+                     data=train, 
+                     perc.over = 100, 
+                     perc.under = 200)
+
+```
+
+### Top Annotations
+
+####SMC
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Smc3ab9263-Sydh_dist")
+
+annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
+                     data=annotdata.smc,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Smc3ab9263-Sydh_dist"))
+
+p.K562.100kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####ZNF143
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Znf143-Sydh_dist")
+
+annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
+                     data=annotdata.znf143,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Znf143-Sydh_dist"))
+
+p.K562.100kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####CTCF
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Ctcf-Broad_dist")
+
+annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
+                     data=annotdata.ctcf,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Ctcf-Broad_dist"))
+
+p.K562.100kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```
+
+####RAD21
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "K562", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "K562-Rad21-Haib_dist")
+
+annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
+                     data=annotdata.rad21,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("K562",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "K562-Rad21-Haib_dist"))
+
+p.K562.100kb.rad21 <- ggplot(annotdata.rad21, aes(x=Rad21_dist, color=y)) +
+    geom_density() +
+    scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
+    ylab("") +
+    xlab("") +
+    ggtitle("RAD21\nPermutation P-Value: < 0.0001") +
+    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15 #,
+                                     #angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     #hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    plot.title = element_text(size=20,
+                              hjust=.5))
+```

### 2019-04-20 Papers.Rmd

@@
 Many other in my `Zotero/Genome/Sequencing/Epigenomics/machine learning` collection
+
+- Jaroszewicz, Artur, and Jason Ernst.
+“An Integrative Approach for Fine-Mapping Chromatin Interactions.” Preprint.
+Bioinformatics, April 11, 2019.
+https://doi.org/10.1101/605576.
+- X-SCNN - prediction of significant Hi-C interactions at highly improved resolution using TFBSs, histone marks, DNAse data (WIG format).
+A Siamese Convolutional Neural Network (SCNN) - two subnetworks with shared parameters predicting true interactions.
+HiCCUPS calls as true interactions, the same number of no interactions (balanced dataset).
+Keras with TensorFlow backend.https://github.com/ernstlab/X-SCNN.
+Describe this paper and the references from introduction about the use of epigenomic data for prediction.
 

### 2019-04-21 Scripts/distribution_of_tads.Rmd
editted results scripts

@@
 ```
+
+#Both cell lines together
+
+##10kb
+
+```{r}
+tad_gm12878_10kb <- read.table("Z:/TAD_data_analysis/GM12878/10kb/GM12878_domain_data_10000.b.txt")
+tad_gm12878_10kb <- tad_gm12878_10kb[,1:3]
+tad_gm12878_10kb <- tad_gm12878_10kb %>%
+  group_by(V1) %>%
+  mutate(Length = V3-V2)
+tad_gm12878_10kb$V1 <- factor(tad_gm12878_10kb$V1, levels = c(1:22))
+tad_data_gm12878_10kb <- tad_gm12878_10kb %>% 
+  group_by(V1) %>% 
+  summarise(Count = length(V1)) 
+tad_data_gm12878_10kb$CL <- "GM12878"
+
+tad_K562_10kb <- read.table("Z:/TAD_data_analysis/K562/10kb/K562_domain_data_10000.b.txt")
+tad_K562_10kb <- tad_K562_10kb[,1:3]
+tad_K562_10kb <- tad_K562_10kb %>%
+  group_by(V1) %>%
+  mutate(Length = V3-V2)
+tad_K562_10kb$V1 <- factor(tad_K562_10kb$V1, levels = c(1:22))
+tad_data_K562_10kb <- tad_K562_10kb %>% 
+  group_by(V1) %>% 
+  summarise(Count = length(V1))
+tad_data_K562_10kb$CL <- "K562"
+
+tad_data_10kb <- rbind.data.frame(tad_data_gm12878_10kb, tad_data_K562_10kb)
+tad_data_10kb$CL <- factor(tad_data_10kb$CL, levels=c("GM12878", "K562"))
+
+p_tadnum_10kb <- ggplot(tad_data_10kb, aes(x=V1, y=Count, fill=CL))+
+  geom_bar(stat="identity") +
+  scale_fill_discrete(name="Cell Line") +
+  #guides(fill=FALSE) +
+  #ylab("Number of TADs") +
+  #xlab("Chromosome") +
+  ylab("") +
+  xlab("") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15 #,
+                                      #angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      #hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+```
+
+##25kb
+
+```{r}
+tad_gm12878_25kb <- read.table("Z:/TAD_data_analysis/GM12878/25kb/GM12878_domain_data_25000.b.txt")
+tad_gm12878_25kb <- tad_gm12878_25kb[,1:3]
+tad_gm12878_25kb <- tad_gm12878_25kb %>%
+  group_by(V1) %>%
+  mutate(Length = V3-V2)
+tad_gm12878_25kb$V1 <- factor(tad_gm12878_25kb$V1, levels = c(1:22))
+tad_data_gm12878_25kb <- tad_gm12878_25kb %>% 
+  group_by(V1) %>% 
+  summarise(Count = length(V1)) 
+tad_data_gm12878_25kb$CL <- "GM12878"
+
+tad_K562_25kb <- read.table("Z:/TAD_data_analysis/K562/25kb/K562_domain_data_25000.b.txt")
+tad_K562_25kb <- tad_K562_25kb[,1:3]
+tad_K562_25kb <- tad_K562_25kb %>%
+  group_by(V1) %>%
+  mutate(Length = V3-V2)
+tad_K562_25kb$V1 <- factor(tad_K562_25kb$V1, levels = c(1:22))
+tad_data_K562_25kb <- tad_K562_25kb %>% 
+  group_by(V1) %>% 
+  summarise(Count = length(V1))
+tad_data_K562_25kb$CL <- "K562"
+
+tad_data_25kb <- rbind.data.frame(tad_data_gm12878_25kb, tad_data_K562_25kb)
+tad_data_25kb$CL <- factor(tad_data_25kb$CL, levels=c("GM12878", "K562"))
+
+p_tadnum_25kb <- ggplot(tad_data_25kb, aes(x=V1, y=Count, fill=CL))+
+  geom_bar(stat="identity") +
+  scale_fill_discrete(name="Cell Line") +
+  #guides(fill=FALSE) +
+  #ylab("Number of TADs") +
+  #xlab("Chromosome") +
+  ylab("") +
+  xlab("") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15 #,
+                                      #angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      #hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+```
+
+##50kb
+
+```{r}
+tad_gm12878_50kb <- read.table("Z:/TAD_data_analysis/GM12878/50kb/GM12878_domain_data_50000.b.txt")
+tad_gm12878_50kb <- tad_gm12878_50kb[,1:3]
+tad_gm12878_50kb <- tad_gm12878_50kb %>%
+  group_by(V1) %>%
+  mutate(Length = V3-V2)
+tad_gm12878_50kb$V1 <- factor(tad_gm12878_50kb$V1, levels = c(1:22))
+tad_data_gm12878_50kb <- tad_gm12878_50kb %>% 
+  group_by(V1) %>% 
+  summarise(Count = length(V1)) 
+tad_data_gm12878_50kb$CL <- "GM12878"
+
+tad_K562_50kb <- read.table("Z:/TAD_data_analysis/K562/50kb/K562_domain_data_50000.b.txt")
+tad_K562_50kb <- tad_K562_50kb[,1:3]
+tad_K562_50kb <- tad_K562_50kb %>%
+  group_by(V1) %>%
+  mutate(Length = V3-V2)
+tad_K562_50kb$V1 <- factor(tad_K562_50kb$V1, levels = c(1:22))
+tad_data_K562_50kb <- tad_K562_50kb %>% 
+  group_by(V1) %>% 
+  summarise(Count = length(V1))
+tad_data_K562_50kb$CL <- "K562"
+
+tad_data_50kb <- rbind.data.frame(tad_data_gm12878_50kb, tad_data_K562_50kb)
+tad_data_50kb$CL <- factor(tad_data_50kb$CL, levels=c("GM12878", "K562"))
+
+p_tadnum_50kb <- ggplot(tad_data_50kb, aes(x=V1, y=Count, fill=CL))+
+  geom_bar(stat="identity") +
+  scale_fill_discrete(name="Cell Line") +
+  #guides(fill=FALSE) +
+  #ylab("Number of TADs") +
+  #xlab("Chromosome") +
+  ylab("") +
+  xlab("") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15 #,
+                                      #angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      #hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+```
+
+##100kb
+
+```{r}
+tad_gm12878_100kb <- read.table("Z:/TAD_data_analysis/GM12878/100kb/GM12878_domain_data_100000.b.txt")
+tad_gm12878_100kb <- tad_gm12878_100kb[,1:3]
+tad_gm12878_100kb <- tad_gm12878_100kb %>%
+  group_by(V1) %>%
+  mutate(Length = V3-V2)
+tad_gm12878_100kb$V1 <- factor(tad_gm12878_100kb$V1, levels = c(1:22))
+tad_data_gm12878_100kb <- tad_gm12878_100kb %>% 
+  group_by(V1) %>% 
+  summarise(Count = length(V1)) 
+tad_data_gm12878_100kb$CL <- "GM12878"
+
+tad_K562_100kb <- read.table("Z:/TAD_data_analysis/K562/100kb/K562_domain_data_100000.b.txt")
+tad_K562_100kb <- tad_K562_100kb[,1:3]
+tad_K562_100kb <- tad_K562_100kb %>%
+  group_by(V1) %>%
+  mutate(Length = V3-V2)
+tad_K562_100kb$V1 <- factor(tad_K562_100kb$V1, levels = c(1:22))
+tad_data_K562_100kb <- tad_K562_100kb %>% 
+  group_by(V1) %>% 
+  summarise(Count = length(V1))
+tad_data_K562_100kb$CL <- "K562"
+
+tad_data_100kb <- rbind.data.frame(tad_data_gm12878_100kb, tad_data_K562_100kb)
+tad_data_100kb$CL <- factor(tad_data_100kb$CL, levels=c("GM12878", "K562"))
+
+p_tadnum_100kb <- ggplot(tad_data_100kb, aes(x=V1, y=Count, fill=CL))+
+  geom_bar(stat="identity") +
+  scale_fill_discrete(name="Cell Line") +
+  #guides(fill=FALSE) +
+  #ylab("Number of TADs") +
+  #xlab("Chromosome") +
+  ylab("") +
+  xlab("") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15 #,
+                                      #angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      #hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+```
+
+##Plots
+
+```{r}
+figure <- ggarrange(p_tadnum_10kb,
+                    p_tadnum_25kb,
+                    p_tadnum_50kb,
+                    p_tadnum_100kb,
+                    ncol=2,
+                    nrow=2,
+                    common.legend = TRUE,
+                    legend="top",
+                    labels = "AUTO",
+                    font.label = list(size=20))
+figure
+annotate_figure(figure,
+    bottom = text_grob("Chromosome", color = "black", size = 20),
+    left = text_grob("Number of TADs", color = "black", rot = 90, size=20)
+)
+
+```

### 2019-04-21 Scripts/evaluating_variable_importances.Rmd
editted results scripts

@@
 ```
+
+#Variable Importance Heatmaps (actual importance values)
+
+## SMOTE; distance types
+
+### GM12878
+
+```{r}
+rfimpvars_gm12878_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+rfimpvars_gm12878_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+rfimpvars_gm12878_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+rfimpvars_gm12878_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+
+rfimpvars_gm12878_10kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_10kb_SMOTE$Feature)
+rfimpvars_gm12878_25kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_25kb_SMOTE$Feature)
+rfimpvars_gm12878_50kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_50kb_SMOTE$Feature)
+rfimpvars_gm12878_100kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_100kb_SMOTE$Feature)
+
+unionannots <- union(rfimpvars_gm12878_10kb_SMOTE$Feature,
+                     union(rfimpvars_gm12878_25kb_SMOTE$Feature,
+                           union(rfimpvars_gm12878_50kb_SMOTE$Feature,rfimpvars_gm12878_100kb_SMOTE$Feature)))
+unionannots <- sort(unionannots)
+
+vim.gm12878.smote <- data.frame(Feature=unionannots)
+
+vim.gm12878.smote <- left_join(left_join(left_join(left_join(vim.gm12878.smote,rfimpvars_gm12878_10kb_SMOTE, by="Feature"),
+                                                   rfimpvars_gm12878_25kb_SMOTE, by="Feature"),
+                                         rfimpvars_gm12878_50kb_SMOTE, by="Feature"),
+                               rfimpvars_gm12878_100kb_SMOTE, by="Feature")
+names(vim.gm12878.smote) <- c("Feature","Importance.10kb","Importance.25kb","Importance.50kb","Importance.100kb")
+
+vim.gm12878.smote <- vim.gm12878.smote[order(vim.gm12878.smote$Importance.10kb, decreasing = TRUE),]
+
+vim.gm12878.smote.melt <- melt(vim.gm12878.smote)
+vim.gm12878.smote.melt$Feature <- factor(vim.gm12878.smote.melt$Feature, levels = vim.gm12878.smote$Feature)
+
+p.vim.gm12878 <- ggplot(vim.gm12878.smote.melt, aes(variable, 
+                                                    ordered(Feature, levels=rev(unique(Feature))))) + 
+  geom_tile(aes(fill = value), colour = "white") + 
+  xlab("Resolution") +
+  ylab("Genomic Annotation") +
+  scale_fill_gradient2(low = "white",
+                      mid = "pink",
+                      midpoint = 50,
+                      high = muted("red"),
+                      na.value = "grey50",
+                      name="Predictive\nImportance") +
+  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 5),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+```
+
+### K562
+
+```{r}
+rfimpvars_K562_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+rfimpvars_K562_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+rfimpvars_K562_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+rfimpvars_K562_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
+
+rfimpvars_K562_10kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_10kb_SMOTE$Feature)
+rfimpvars_K562_25kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_25kb_SMOTE$Feature)
+rfimpvars_K562_50kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_50kb_SMOTE$Feature)
+rfimpvars_K562_100kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_100kb_SMOTE$Feature)
+
+unionannots <- union(rfimpvars_K562_10kb_SMOTE$Feature,
+                     union(rfimpvars_K562_25kb_SMOTE$Feature,
+                           union(rfimpvars_K562_50kb_SMOTE$Feature,rfimpvars_K562_100kb_SMOTE$Feature)))
+unionannots <- sort(unionannots)
+
+vim.K562.smote <- data.frame(Feature=unionannots)
+
+vim.K562.smote <- left_join(left_join(left_join(left_join(vim.K562.smote,rfimpvars_K562_10kb_SMOTE, by="Feature"),
+                                                   rfimpvars_K562_25kb_SMOTE, by="Feature"),
+                                         rfimpvars_K562_50kb_SMOTE, by="Feature"),
+                               rfimpvars_K562_100kb_SMOTE, by="Feature")
+names(vim.K562.smote) <- c("Feature","Importance.10kb","Importance.25kb","Importance.50kb","Importance.100kb")
+
+vim.K562.smote <- vim.K562.smote[order(vim.K562.smote$Importance.10kb, decreasing = TRUE),]
+
+vim.K562.smote.melt <- melt(vim.K562.smote)
+vim.K562.smote.melt$Feature <- factor(vim.K562.smote.melt$Feature, levels = vim.K562.smote$Feature)
+
+p.vim.K562 <- ggplot(vim.K562.smote.melt, aes(variable, 
+                                                    ordered(Feature, levels=rev(unique(Feature))))) + 
+  geom_tile(aes(fill = value), colour = "white") + 
+  xlab("Resolution") +
+  ylab("Genomic Annotation") +
+  scale_fill_gradient2(low = "white",
+                      mid = "pink",
+                      midpoint = 50,
+                      high = muted("red"),
+                      na.value = "grey50",
+                      name="Predictive\nImportance") +
+  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 5),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+```

### 2019-04-21 Scripts/creating_supplementary_table_of_penalization_parameters.Rmd
script to extract alpha and lambda from all models

---
title: "Creating Tables of Elastic Net Parameters"
author: "Spiro Stilianoudakis"
date: "April 21, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Extracting alpha and lambda penalty parameters from elastic net

## GM12878

### 10kb

#### none

##### OC

```{r}
eNetModel_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/eNetModel.rds")
eNetModel_gm12878_10kb_none_oc_alpha <- as.numeric(eNetModel_gm12878_10kb_none_oc$bestTune[1])
eNetModel_gm12878_10kb_none_oc_lambda <- as.numeric(eNetModel_gm12878_10kb_none_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_10kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/eNetModel.rds")
eNetModel_gm12878_10kb_none_OP_alpha <- as.numeric(eNetModel_gm12878_10kb_none_OP$bestTune[1])
eNetModel_gm12878_10kb_none_OP_lambda <- as.numeric(eNetModel_gm12878_10kb_none_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_10kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_10kb_none_Distance_alpha <- as.numeric(eNetModel_gm12878_10kb_none_Distance$bestTune[1])
eNetModel_gm12878_10kb_none_Distance_lambda <- as.numeric(eNetModel_gm12878_10kb_none_Distance$bestTune[2])
```

#### ROS

##### OC

```{r}
eNetModel_gm12878_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/eNetModel.rds")
eNetModel_gm12878_10kb_ROS_oc_alpha <- as.numeric(eNetModel_gm12878_10kb_ROS_oc$bestTune[1])
eNetModel_gm12878_10kb_ROS_oc_lambda <- as.numeric(eNetModel_gm12878_10kb_ROS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_10kb_ROS_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/eNetModel.rds")
eNetModel_gm12878_10kb_ROS_OP_alpha <- as.numeric(eNetModel_gm12878_10kb_ROS_OP$bestTune[1])
eNetModel_gm12878_10kb_ROS_OP_lambda <- as.numeric(eNetModel_gm12878_10kb_ROS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_10kb_ROS_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_10kb_ROS_Distance_alpha <- as.numeric(eNetModel_gm12878_10kb_ROS_Distance$bestTune[1])
eNetModel_gm12878_10kb_ROS_Distance_lambda <- as.numeric(eNetModel_gm12878_10kb_ROS_Distance$bestTune[2])
```

#### RUS

##### OC

```{r}
eNetModel_gm12878_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/eNetModel.rds")
eNetModel_gm12878_10kb_RUS_oc_alpha <- as.numeric(eNetModel_gm12878_10kb_RUS_oc$bestTune[1])
eNetModel_gm12878_10kb_RUS_oc_lambda <- as.numeric(eNetModel_gm12878_10kb_RUS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_10kb_RUS_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/eNetModel.rds")
eNetModel_gm12878_10kb_RUS_OP_alpha <- as.numeric(eNetModel_gm12878_10kb_RUS_OP$bestTune[1])
eNetModel_gm12878_10kb_RUS_OP_lambda <- as.numeric(eNetModel_gm12878_10kb_RUS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_10kb_RUS_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_10kb_RUS_Distance_alpha <- as.numeric(eNetModel_gm12878_10kb_RUS_Distance$bestTune[1])
eNetModel_gm12878_10kb_RUS_Distance_lambda <- as.numeric(eNetModel_gm12878_10kb_RUS_Distance$bestTune[2])
```

#### SMOTE

##### OC

```{r}
eNetModel_gm12878_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/eNetModel.rds")
eNetModel_gm12878_10kb_SMOTE_oc_alpha <- as.numeric(eNetModel_gm12878_10kb_SMOTE_oc$bestTune[1])
eNetModel_gm12878_10kb_SMOTE_oc_lambda <- as.numeric(eNetModel_gm12878_10kb_SMOTE_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_10kb_SMOTE_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/eNetModel.rds")
eNetModel_gm12878_10kb_SMOTE_OP_alpha <- as.numeric(eNetModel_gm12878_10kb_SMOTE_OP$bestTune[1])
eNetModel_gm12878_10kb_SMOTE_OP_lambda <- as.numeric(eNetModel_gm12878_10kb_SMOTE_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_10kb_SMOTE_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_10kb_SMOTE_Distance_alpha <- as.numeric(eNetModel_gm12878_10kb_SMOTE_Distance$bestTune[1])
eNetModel_gm12878_10kb_SMOTE_Distance_lambda <- as.numeric(eNetModel_gm12878_10kb_SMOTE_Distance$bestTune[2])
```

### 25kb

#### none

##### OC

```{r}
eNetModel_gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/eNetModel.rds")
eNetModel_gm12878_25kb_none_oc_alpha <- as.numeric(eNetModel_gm12878_25kb_none_oc$bestTune[1])
eNetModel_gm12878_25kb_none_oc_lambda <- as.numeric(eNetModel_gm12878_25kb_none_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_25kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/eNetModel.rds")
eNetModel_gm12878_25kb_none_OP_alpha <- as.numeric(eNetModel_gm12878_25kb_none_OP$bestTune[1])
eNetModel_gm12878_25kb_none_OP_lambda <- as.numeric(eNetModel_gm12878_25kb_none_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_25kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_25kb_none_Distance_alpha <- as.numeric(eNetModel_gm12878_25kb_none_Distance$bestTune[1])
eNetModel_gm12878_25kb_none_Distance_lambda <- as.numeric(eNetModel_gm12878_25kb_none_Distance$bestTune[2])
```

#### ROS

##### OC

```{r}
eNetModel_gm12878_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/eNetModel.rds")
eNetModel_gm12878_25kb_ROS_oc_alpha <- as.numeric(eNetModel_gm12878_25kb_ROS_oc$bestTune[1])
eNetModel_gm12878_25kb_ROS_oc_lambda <- as.numeric(eNetModel_gm12878_25kb_ROS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_25kb_ROS_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/eNetModel.rds")
eNetModel_gm12878_25kb_ROS_OP_alpha <- as.numeric(eNetModel_gm12878_25kb_ROS_OP$bestTune[1])
eNetModel_gm12878_25kb_ROS_OP_lambda <- as.numeric(eNetModel_gm12878_25kb_ROS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_25kb_ROS_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_25kb_ROS_Distance_alpha <- as.numeric(eNetModel_gm12878_25kb_ROS_Distance$bestTune[1])
eNetModel_gm12878_25kb_ROS_Distance_lambda <- as.numeric(eNetModel_gm12878_25kb_ROS_Distance$bestTune[2])
```

#### RUS

##### OC

```{r}
eNetModel_gm12878_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/eNetModel.rds")
eNetModel_gm12878_25kb_RUS_oc_alpha <- as.numeric(eNetModel_gm12878_25kb_RUS_oc$bestTune[1])
eNetModel_gm12878_25kb_RUS_oc_lambda <- as.numeric(eNetModel_gm12878_25kb_RUS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_25kb_RUS_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/eNetModel.rds")
eNetModel_gm12878_25kb_RUS_OP_alpha <- as.numeric(eNetModel_gm12878_25kb_RUS_OP$bestTune[1])
eNetModel_gm12878_25kb_RUS_OP_lambda <- as.numeric(eNetModel_gm12878_25kb_RUS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_25kb_RUS_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_25kb_RUS_Distance_alpha <- as.numeric(eNetModel_gm12878_25kb_RUS_Distance$bestTune[1])
eNetModel_gm12878_25kb_RUS_Distance_lambda <- as.numeric(eNetModel_gm12878_25kb_RUS_Distance$bestTune[2])
```

#### SMOTE

##### OC

```{r}
eNetModel_gm12878_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/eNetModel.rds")
eNetModel_gm12878_25kb_SMOTE_oc_alpha <- as.numeric(eNetModel_gm12878_25kb_SMOTE_oc$bestTune[1])
eNetModel_gm12878_25kb_SMOTE_oc_lambda <- as.numeric(eNetModel_gm12878_25kb_SMOTE_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_25kb_SMOTE_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/eNetModel.rds")
eNetModel_gm12878_25kb_SMOTE_OP_alpha <- as.numeric(eNetModel_gm12878_25kb_SMOTE_OP$bestTune[1])
eNetModel_gm12878_25kb_SMOTE_OP_lambda <- as.numeric(eNetModel_gm12878_25kb_SMOTE_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_25kb_SMOTE_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_25kb_SMOTE_Distance_alpha <- as.numeric(eNetModel_gm12878_25kb_SMOTE_Distance$bestTune[1])
eNetModel_gm12878_25kb_SMOTE_Distance_lambda <- as.numeric(eNetModel_gm12878_25kb_SMOTE_Distance$bestTune[2])
```

### 50kb

#### none

##### OC

```{r}
eNetModel_gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/eNetModel.rds")
eNetModel_gm12878_50kb_none_oc_alpha <- as.numeric(eNetModel_gm12878_50kb_none_oc$bestTune[1])
eNetModel_gm12878_50kb_none_oc_lambda <- as.numeric(eNetModel_gm12878_50kb_none_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_50kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/eNetModel.rds")
eNetModel_gm12878_50kb_none_OP_alpha <- as.numeric(eNetModel_gm12878_50kb_none_OP$bestTune[1])
eNetModel_gm12878_50kb_none_OP_lambda <- as.numeric(eNetModel_gm12878_50kb_none_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_50kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_50kb_none_Distance_alpha <- as.numeric(eNetModel_gm12878_50kb_none_Distance$bestTune[1])
eNetModel_gm12878_50kb_none_Distance_lambda <- as.numeric(eNetModel_gm12878_50kb_none_Distance$bestTune[2])
```

#### ROS

##### OC

```{r}
eNetModel_gm12878_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/eNetModel.rds")
eNetModel_gm12878_50kb_ROS_oc_alpha <- as.numeric(eNetModel_gm12878_50kb_ROS_oc$bestTune[1])
eNetModel_gm12878_50kb_ROS_oc_lambda <- as.numeric(eNetModel_gm12878_50kb_ROS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_50kb_ROS_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/eNetModel.rds")
eNetModel_gm12878_50kb_ROS_OP_alpha <- as.numeric(eNetModel_gm12878_50kb_ROS_OP$bestTune[1])
eNetModel_gm12878_50kb_ROS_OP_lambda <- as.numeric(eNetModel_gm12878_50kb_ROS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_50kb_ROS_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_50kb_ROS_Distance_alpha <- as.numeric(eNetModel_gm12878_50kb_ROS_Distance$bestTune[1])
eNetModel_gm12878_50kb_ROS_Distance_lambda <- as.numeric(eNetModel_gm12878_50kb_ROS_Distance$bestTune[2])
```

#### RUS

##### OC

```{r}
eNetModel_gm12878_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/eNetModel.rds")
eNetModel_gm12878_50kb_RUS_oc_alpha <- as.numeric(eNetModel_gm12878_50kb_RUS_oc$bestTune[1])
eNetModel_gm12878_50kb_RUS_oc_lambda <- as.numeric(eNetModel_gm12878_50kb_RUS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_50kb_RUS_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/eNetModel.rds")
eNetModel_gm12878_50kb_RUS_OP_alpha <- as.numeric(eNetModel_gm12878_50kb_RUS_OP$bestTune[1])
eNetModel_gm12878_50kb_RUS_OP_lambda <- as.numeric(eNetModel_gm12878_50kb_RUS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_50kb_RUS_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_50kb_RUS_Distance_alpha <- as.numeric(eNetModel_gm12878_50kb_RUS_Distance$bestTune[1])
eNetModel_gm12878_50kb_RUS_Distance_lambda <- as.numeric(eNetModel_gm12878_50kb_RUS_Distance$bestTune[2])
```

#### SMOTE

##### OC

```{r}
eNetModel_gm12878_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/eNetModel.rds")
eNetModel_gm12878_50kb_SMOTE_oc_alpha <- as.numeric(eNetModel_gm12878_50kb_SMOTE_oc$bestTune[1])
eNetModel_gm12878_50kb_SMOTE_oc_lambda <- as.numeric(eNetModel_gm12878_50kb_SMOTE_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_50kb_SMOTE_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/eNetModel.rds")
eNetModel_gm12878_50kb_SMOTE_OP_alpha <- as.numeric(eNetModel_gm12878_50kb_SMOTE_OP$bestTune[1])
eNetModel_gm12878_50kb_SMOTE_OP_lambda <- as.numeric(eNetModel_gm12878_50kb_SMOTE_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_50kb_SMOTE_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_50kb_SMOTE_Distance_alpha <- as.numeric(eNetModel_gm12878_50kb_SMOTE_Distance$bestTune[1])
eNetModel_gm12878_50kb_SMOTE_Distance_lambda <- as.numeric(eNetModel_gm12878_50kb_SMOTE_Distance$bestTune[2])
```

### 100kb

#### none

##### OC

```{r}
eNetModel_gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/eNetModel.rds")
eNetModel_gm12878_100kb_none_oc_alpha <- as.numeric(eNetModel_gm12878_100kb_none_oc$bestTune[1])
eNetModel_gm12878_100kb_none_oc_lambda <- as.numeric(eNetModel_gm12878_100kb_none_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_100kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/eNetModel.rds")
eNetModel_gm12878_100kb_none_OP_alpha <- as.numeric(eNetModel_gm12878_100kb_none_OP$bestTune[1])
eNetModel_gm12878_100kb_none_OP_lambda <- as.numeric(eNetModel_gm12878_100kb_none_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_100kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_100kb_none_Distance_alpha <- as.numeric(eNetModel_gm12878_100kb_none_Distance$bestTune[1])
eNetModel_gm12878_100kb_none_Distance_lambda <- as.numeric(eNetModel_gm12878_100kb_none_Distance$bestTune[2])
```

#### ROS

##### OC

```{r}
eNetModel_gm12878_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/eNetModel.rds")
eNetModel_gm12878_100kb_ROS_oc_alpha <- as.numeric(eNetModel_gm12878_100kb_ROS_oc$bestTune[1])
eNetModel_gm12878_100kb_ROS_oc_lambda <- as.numeric(eNetModel_gm12878_100kb_ROS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_100kb_ROS_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/eNetModel.rds")
eNetModel_gm12878_100kb_ROS_OP_alpha <- as.numeric(eNetModel_gm12878_100kb_ROS_OP$bestTune[1])
eNetModel_gm12878_100kb_ROS_OP_lambda <- as.numeric(eNetModel_gm12878_100kb_ROS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_100kb_ROS_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_100kb_ROS_Distance_alpha <- as.numeric(eNetModel_gm12878_100kb_ROS_Distance$bestTune[1])
eNetModel_gm12878_100kb_ROS_Distance_lambda <- as.numeric(eNetModel_gm12878_100kb_ROS_Distance$bestTune[2])
```

#### RUS

##### OC

```{r}
eNetModel_gm12878_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/eNetModel.rds")
eNetModel_gm12878_100kb_RUS_oc_alpha <- as.numeric(eNetModel_gm12878_100kb_RUS_oc$bestTune[1])
eNetModel_gm12878_100kb_RUS_oc_lambda <- as.numeric(eNetModel_gm12878_100kb_RUS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_100kb_RUS_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/eNetModel.rds")
eNetModel_gm12878_100kb_RUS_OP_alpha <- as.numeric(eNetModel_gm12878_100kb_RUS_OP$bestTune[1])
eNetModel_gm12878_100kb_RUS_OP_lambda <- as.numeric(eNetModel_gm12878_100kb_RUS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_100kb_RUS_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_100kb_RUS_Distance_alpha <- as.numeric(eNetModel_gm12878_100kb_RUS_Distance$bestTune[1])
eNetModel_gm12878_100kb_RUS_Distance_lambda <- as.numeric(eNetModel_gm12878_100kb_RUS_Distance$bestTune[2])
```

#### SMOTE

##### OC

```{r}
eNetModel_gm12878_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/eNetModel.rds")
eNetModel_gm12878_100kb_SMOTE_oc_alpha <- as.numeric(eNetModel_gm12878_100kb_SMOTE_oc$bestTune[1])
eNetModel_gm12878_100kb_SMOTE_oc_lambda <- as.numeric(eNetModel_gm12878_100kb_SMOTE_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_gm12878_100kb_SMOTE_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/eNetModel.rds")
eNetModel_gm12878_100kb_SMOTE_OP_alpha <- as.numeric(eNetModel_gm12878_100kb_SMOTE_OP$bestTune[1])
eNetModel_gm12878_100kb_SMOTE_OP_lambda <- as.numeric(eNetModel_gm12878_100kb_SMOTE_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_gm12878_100kb_SMOTE_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/eNetModel.rds")
eNetModel_gm12878_100kb_SMOTE_Distance_alpha <- as.numeric(eNetModel_gm12878_100kb_SMOTE_Distance$bestTune[1])
eNetModel_gm12878_100kb_SMOTE_Distance_lambda <- as.numeric(eNetModel_gm12878_100kb_SMOTE_Distance$bestTune[2])
```

## Creating Table

```{r}
eNetModel_gm12878_parameter_tab <- data.frame(Alpha=c(eNetModel_gm12878_10kb_none_oc_alpha,
                                                      eNetModel_gm12878_10kb_none_OP_alpha,
                                                      eNetModel_gm12878_10kb_none_Distance_alpha,

                                                      eNetModel_gm12878_10kb_ROS_oc_alpha,
                                                      eNetModel_gm12878_10kb_ROS_OP_alpha,
                                                      eNetModel_gm12878_10kb_ROS_Distance_alpha,

                                                      eNetModel_gm12878_10kb_RUS_oc_alpha,
                                                      eNetModel_gm12878_10kb_RUS_OP_alpha,
                                                      eNetModel_gm12878_10kb_RUS_Distance_alpha,

                                                      eNetModel_gm12878_10kb_SMOTE_oc_alpha,
                                                      eNetModel_gm12878_10kb_SMOTE_OP_alpha,
                                                      eNetModel_gm12878_10kb_SMOTE_Distance_alpha,

                                                      eNetModel_gm12878_25kb_none_oc_alpha,
                                                      eNetModel_gm12878_25kb_none_OP_alpha,
                                                      eNetModel_gm12878_25kb_none_Distance_alpha,

                                                      eNetModel_gm12878_25kb_ROS_oc_alpha,
                                                      eNetModel_gm12878_25kb_ROS_OP_alpha,
                                                      eNetModel_gm12878_25kb_ROS_Distance_alpha,

                                                      eNetModel_gm12878_25kb_RUS_oc_alpha,
                                                      eNetModel_gm12878_25kb_RUS_OP_alpha,
                                                      eNetModel_gm12878_25kb_RUS_Distance_alpha,

                                                      eNetModel_gm12878_25kb_SMOTE_oc_alpha,
                                                      eNetModel_gm12878_25kb_SMOTE_OP_alpha,
                                                      eNetModel_gm12878_25kb_SMOTE_Distance_alpha,

                                                      eNetModel_gm12878_50kb_none_oc_alpha,
                                                      eNetModel_gm12878_50kb_none_OP_alpha,
                                                      eNetModel_gm12878_50kb_none_Distance_alpha,

                                                      eNetModel_gm12878_50kb_ROS_oc_alpha,
                                                      eNetModel_gm12878_50kb_ROS_OP_alpha,
                                                      eNetModel_gm12878_50kb_ROS_Distance_alpha,

                                                      eNetModel_gm12878_50kb_RUS_oc_alpha,
                                                      eNetModel_gm12878_50kb_RUS_OP_alpha,
                                                      eNetModel_gm12878_50kb_RUS_Distance_alpha,

                                                      eNetModel_gm12878_50kb_SMOTE_oc_alpha,
                                                      eNetModel_gm12878_50kb_SMOTE_OP_alpha,
                                                      eNetModel_gm12878_50kb_SMOTE_Distance_alpha,

                                                      eNetModel_gm12878_100kb_none_oc_alpha,
                                                      eNetModel_gm12878_100kb_none_OP_alpha,
                                                      eNetModel_gm12878_100kb_none_Distance_alpha,

                                                      eNetModel_gm12878_100kb_ROS_oc_alpha,
                                                      eNetModel_gm12878_100kb_ROS_OP_alpha,
                                                      eNetModel_gm12878_100kb_ROS_Distance_alpha,

                                                      eNetModel_gm12878_100kb_RUS_oc_alpha,
                                                      eNetModel_gm12878_100kb_RUS_OP_alpha,
                                                      eNetModel_gm12878_100kb_RUS_Distance_alpha,

                                                      eNetModel_gm12878_100kb_SMOTE_oc_alpha,
                                                      eNetModel_gm12878_100kb_SMOTE_OP_alpha,
                                                      eNetModel_gm12878_100kb_SMOTE_Distance_alpha),
                                              Lambda=c(eNetModel_gm12878_10kb_none_oc_lambda,
                                                      eNetModel_gm12878_10kb_none_OP_lambda,
                                                      eNetModel_gm12878_10kb_none_Distance_lambda,

                                                      eNetModel_gm12878_10kb_ROS_oc_lambda,
                                                      eNetModel_gm12878_10kb_ROS_OP_lambda,
                                                      eNetModel_gm12878_10kb_ROS_Distance_lambda,

                                                      eNetModel_gm12878_10kb_RUS_oc_lambda,
                                                      eNetModel_gm12878_10kb_RUS_OP_lambda,
                                                      eNetModel_gm12878_10kb_RUS_Distance_lambda,

                                                      eNetModel_gm12878_10kb_SMOTE_oc_lambda,
                                                      eNetModel_gm12878_10kb_SMOTE_OP_lambda,
                                                      eNetModel_gm12878_10kb_SMOTE_Distance_lambda,

                                                      eNetModel_gm12878_25kb_none_oc_lambda,
                                                      eNetModel_gm12878_25kb_none_OP_lambda,
                                                      eNetModel_gm12878_25kb_none_Distance_lambda,

                                                      eNetModel_gm12878_25kb_ROS_oc_lambda,
                                                      eNetModel_gm12878_25kb_ROS_OP_lambda,
                                                      eNetModel_gm12878_25kb_ROS_Distance_lambda,

                                                      eNetModel_gm12878_25kb_RUS_oc_lambda,
                                                      eNetModel_gm12878_25kb_RUS_OP_lambda,
                                                      eNetModel_gm12878_25kb_RUS_Distance_lambda,

                                                      eNetModel_gm12878_25kb_SMOTE_oc_lambda,
                                                      eNetModel_gm12878_25kb_SMOTE_OP_lambda,
                                                      eNetModel_gm12878_25kb_SMOTE_Distance_lambda,

                                                      eNetModel_gm12878_50kb_none_oc_lambda,
                                                      eNetModel_gm12878_50kb_none_OP_lambda,
                                                      eNetModel_gm12878_50kb_none_Distance_lambda,

                                                      eNetModel_gm12878_50kb_ROS_oc_lambda,
                                                      eNetModel_gm12878_50kb_ROS_OP_lambda,
                                                      eNetModel_gm12878_50kb_ROS_Distance_lambda,

                                                      eNetModel_gm12878_50kb_RUS_oc_lambda,
                                                      eNetModel_gm12878_50kb_RUS_OP_lambda,
                                                      eNetModel_gm12878_50kb_RUS_Distance_lambda,

                                                      eNetModel_gm12878_50kb_SMOTE_oc_lambda,
                                                      eNetModel_gm12878_50kb_SMOTE_OP_lambda,
                                                      eNetModel_gm12878_50kb_SMOTE_Distance_lambda,

                                                      eNetModel_gm12878_100kb_none_oc_lambda,
                                                      eNetModel_gm12878_100kb_none_OP_lambda,
                                                      eNetModel_gm12878_100kb_none_Distance_lambda,

                                                      eNetModel_gm12878_100kb_ROS_oc_lambda,
                                                      eNetModel_gm12878_100kb_ROS_OP_lambda,
                                                      eNetModel_gm12878_100kb_ROS_Distance_lambda,

                                                      eNetModel_gm12878_100kb_RUS_oc_lambda,
                                                      eNetModel_gm12878_100kb_RUS_OP_lambda,
                                                      eNetModel_gm12878_100kb_RUS_Distance_lambda,

                                                      eNetModel_gm12878_100kb_SMOTE_oc_lambda,
                                                      eNetModel_gm12878_100kb_SMOTE_OP_lambda,
                                                      eNetModel_gm12878_100kb_SMOTE_Distance_lambda))

eNetModel_gm12878_parameter_tab$CL <- "GM12878"
eNetModel_gm12878_parameter_tab$Resolution <- c(rep("10 kb", 12),
                                                rep("25 kb", 12),
                                                rep("50 kb", 12),
                                                rep("100 kb", 12))
eNetModel_gm12878_parameter_tab$PredictorType <- rep(c("OC","OP","Distance"),16)
eNetModel_gm12878_parameter_tab <- eNetModel_gm12878_parameter_tab[,c(3:5,1:2)]
```

## K562

### 10kb

#### none

##### OC

```{r}
eNetModel_K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/eNetModel.rds")
eNetModel_K562_10kb_none_oc_alpha <- as.numeric(eNetModel_K562_10kb_none_oc$bestTune[1])
eNetModel_K562_10kb_none_oc_lambda <- as.numeric(eNetModel_K562_10kb_none_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_10kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/eNetModel.rds")
eNetModel_K562_10kb_none_OP_alpha <- as.numeric(eNetModel_K562_10kb_none_OP$bestTune[1])
eNetModel_K562_10kb_none_OP_lambda <- as.numeric(eNetModel_K562_10kb_none_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_10kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/eNetModel.rds")
eNetModel_K562_10kb_none_Distance_alpha <- as.numeric(eNetModel_K562_10kb_none_Distance$bestTune[1])
eNetModel_K562_10kb_none_Distance_lambda <- as.numeric(eNetModel_K562_10kb_none_Distance$bestTune[2])
```

#### ROS

##### OC

```{r}
eNetModel_K562_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/eNetModel.rds")
eNetModel_K562_10kb_ROS_oc_alpha <- as.numeric(eNetModel_K562_10kb_ROS_oc$bestTune[1])
eNetModel_K562_10kb_ROS_oc_lambda <- as.numeric(eNetModel_K562_10kb_ROS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_10kb_ROS_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/eNetModel.rds")
eNetModel_K562_10kb_ROS_OP_alpha <- as.numeric(eNetModel_K562_10kb_ROS_OP$bestTune[1])
eNetModel_K562_10kb_ROS_OP_lambda <- as.numeric(eNetModel_K562_10kb_ROS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_10kb_ROS_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/eNetModel.rds")
eNetModel_K562_10kb_ROS_Distance_alpha <- as.numeric(eNetModel_K562_10kb_ROS_Distance$bestTune[1])
eNetModel_K562_10kb_ROS_Distance_lambda <- as.numeric(eNetModel_K562_10kb_ROS_Distance$bestTune[2])
```

#### RUS

##### OC

```{r}
eNetModel_K562_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/eNetModel.rds")
eNetModel_K562_10kb_RUS_oc_alpha <- as.numeric(eNetModel_K562_10kb_RUS_oc$bestTune[1])
eNetModel_K562_10kb_RUS_oc_lambda <- as.numeric(eNetModel_K562_10kb_RUS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_10kb_RUS_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/eNetModel.rds")
eNetModel_K562_10kb_RUS_OP_alpha <- as.numeric(eNetModel_K562_10kb_RUS_OP$bestTune[1])
eNetModel_K562_10kb_RUS_OP_lambda <- as.numeric(eNetModel_K562_10kb_RUS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_10kb_RUS_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/eNetModel.rds")
eNetModel_K562_10kb_RUS_Distance_alpha <- as.numeric(eNetModel_K562_10kb_RUS_Distance$bestTune[1])
eNetModel_K562_10kb_RUS_Distance_lambda <- as.numeric(eNetModel_K562_10kb_RUS_Distance$bestTune[2])
```

#### SMOTE

##### OC

```{r}
eNetModel_K562_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/eNetModel.rds")
eNetModel_K562_10kb_SMOTE_oc_alpha <- as.numeric(eNetModel_K562_10kb_SMOTE_oc$bestTune[1])
eNetModel_K562_10kb_SMOTE_oc_lambda <- as.numeric(eNetModel_K562_10kb_SMOTE_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_10kb_SMOTE_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/eNetModel.rds")
eNetModel_K562_10kb_SMOTE_OP_alpha <- as.numeric(eNetModel_K562_10kb_SMOTE_OP$bestTune[1])
eNetModel_K562_10kb_SMOTE_OP_lambda <- as.numeric(eNetModel_K562_10kb_SMOTE_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_10kb_SMOTE_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/eNetModel.rds")
eNetModel_K562_10kb_SMOTE_Distance_alpha <- as.numeric(eNetModel_K562_10kb_SMOTE_Distance$bestTune[1])
eNetModel_K562_10kb_SMOTE_Distance_lambda <- as.numeric(eNetModel_K562_10kb_SMOTE_Distance$bestTune[2])
```

### 25kb

#### none

##### OC

```{r}
eNetModel_K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/eNetModel.rds")
eNetModel_K562_25kb_none_oc_alpha <- as.numeric(eNetModel_K562_25kb_none_oc$bestTune[1])
eNetModel_K562_25kb_none_oc_lambda <- as.numeric(eNetModel_K562_25kb_none_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_25kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/eNetModel.rds")
eNetModel_K562_25kb_none_OP_alpha <- as.numeric(eNetModel_K562_25kb_none_OP$bestTune[1])
eNetModel_K562_25kb_none_OP_lambda <- as.numeric(eNetModel_K562_25kb_none_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_25kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/eNetModel.rds")
eNetModel_K562_25kb_none_Distance_alpha <- as.numeric(eNetModel_K562_25kb_none_Distance$bestTune[1])
eNetModel_K562_25kb_none_Distance_lambda <- as.numeric(eNetModel_K562_25kb_none_Distance$bestTune[2])
```

#### ROS

##### OC

```{r}
eNetModel_K562_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/eNetModel.rds")
eNetModel_K562_25kb_ROS_oc_alpha <- as.numeric(eNetModel_K562_25kb_ROS_oc$bestTune[1])
eNetModel_K562_25kb_ROS_oc_lambda <- as.numeric(eNetModel_K562_25kb_ROS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_25kb_ROS_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/eNetModel.rds")
eNetModel_K562_25kb_ROS_OP_alpha <- as.numeric(eNetModel_K562_25kb_ROS_OP$bestTune[1])
eNetModel_K562_25kb_ROS_OP_lambda <- as.numeric(eNetModel_K562_25kb_ROS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_25kb_ROS_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/eNetModel.rds")
eNetModel_K562_25kb_ROS_Distance_alpha <- as.numeric(eNetModel_K562_25kb_ROS_Distance$bestTune[1])
eNetModel_K562_25kb_ROS_Distance_lambda <- as.numeric(eNetModel_K562_25kb_ROS_Distance$bestTune[2])
```

#### RUS

##### OC

```{r}
eNetModel_K562_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/eNetModel.rds")
eNetModel_K562_25kb_RUS_oc_alpha <- as.numeric(eNetModel_K562_25kb_RUS_oc$bestTune[1])
eNetModel_K562_25kb_RUS_oc_lambda <- as.numeric(eNetModel_K562_25kb_RUS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_25kb_RUS_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/eNetModel.rds")
eNetModel_K562_25kb_RUS_OP_alpha <- as.numeric(eNetModel_K562_25kb_RUS_OP$bestTune[1])
eNetModel_K562_25kb_RUS_OP_lambda <- as.numeric(eNetModel_K562_25kb_RUS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_25kb_RUS_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/eNetModel.rds")
eNetModel_K562_25kb_RUS_Distance_alpha <- as.numeric(eNetModel_K562_25kb_RUS_Distance$bestTune[1])
eNetModel_K562_25kb_RUS_Distance_lambda <- as.numeric(eNetModel_K562_25kb_RUS_Distance$bestTune[2])
```

#### SMOTE

##### OC

```{r}
eNetModel_K562_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/eNetModel.rds")
eNetModel_K562_25kb_SMOTE_oc_alpha <- as.numeric(eNetModel_K562_25kb_SMOTE_oc$bestTune[1])
eNetModel_K562_25kb_SMOTE_oc_lambda <- as.numeric(eNetModel_K562_25kb_SMOTE_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_25kb_SMOTE_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/eNetModel.rds")
eNetModel_K562_25kb_SMOTE_OP_alpha <- as.numeric(eNetModel_K562_25kb_SMOTE_OP$bestTune[1])
eNetModel_K562_25kb_SMOTE_OP_lambda <- as.numeric(eNetModel_K562_25kb_SMOTE_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_25kb_SMOTE_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/eNetModel.rds")
eNetModel_K562_25kb_SMOTE_Distance_alpha <- as.numeric(eNetModel_K562_25kb_SMOTE_Distance$bestTune[1])
eNetModel_K562_25kb_SMOTE_Distance_lambda <- as.numeric(eNetModel_K562_25kb_SMOTE_Distance$bestTune[2])
```

### 50kb

#### none

##### OC

```{r}
eNetModel_K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/eNetModel.rds")
eNetModel_K562_50kb_none_oc_alpha <- as.numeric(eNetModel_K562_50kb_none_oc$bestTune[1])
eNetModel_K562_50kb_none_oc_lambda <- as.numeric(eNetModel_K562_50kb_none_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_50kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/eNetModel.rds")
eNetModel_K562_50kb_none_OP_alpha <- as.numeric(eNetModel_K562_50kb_none_OP$bestTune[1])
eNetModel_K562_50kb_none_OP_lambda <- as.numeric(eNetModel_K562_50kb_none_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_50kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/eNetModel.rds")
eNetModel_K562_50kb_none_Distance_alpha <- as.numeric(eNetModel_K562_50kb_none_Distance$bestTune[1])
eNetModel_K562_50kb_none_Distance_lambda <- as.numeric(eNetModel_K562_50kb_none_Distance$bestTune[2])
```

#### ROS

##### OC

```{r}
eNetModel_K562_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/eNetModel.rds")
eNetModel_K562_50kb_ROS_oc_alpha <- as.numeric(eNetModel_K562_50kb_ROS_oc$bestTune[1])
eNetModel_K562_50kb_ROS_oc_lambda <- as.numeric(eNetModel_K562_50kb_ROS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_50kb_ROS_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/eNetModel.rds")
eNetModel_K562_50kb_ROS_OP_alpha <- as.numeric(eNetModel_K562_50kb_ROS_OP$bestTune[1])
eNetModel_K562_50kb_ROS_OP_lambda <- as.numeric(eNetModel_K562_50kb_ROS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_50kb_ROS_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/eNetModel.rds")
eNetModel_K562_50kb_ROS_Distance_alpha <- as.numeric(eNetModel_K562_50kb_ROS_Distance$bestTune[1])
eNetModel_K562_50kb_ROS_Distance_lambda <- as.numeric(eNetModel_K562_50kb_ROS_Distance$bestTune[2])
```

#### RUS

##### OC

```{r}
eNetModel_K562_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/eNetModel.rds")
eNetModel_K562_50kb_RUS_oc_alpha <- as.numeric(eNetModel_K562_50kb_RUS_oc$bestTune[1])
eNetModel_K562_50kb_RUS_oc_lambda <- as.numeric(eNetModel_K562_50kb_RUS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_50kb_RUS_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/eNetModel.rds")
eNetModel_K562_50kb_RUS_OP_alpha <- as.numeric(eNetModel_K562_50kb_RUS_OP$bestTune[1])
eNetModel_K562_50kb_RUS_OP_lambda <- as.numeric(eNetModel_K562_50kb_RUS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_50kb_RUS_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/eNetModel.rds")
eNetModel_K562_50kb_RUS_Distance_alpha <- as.numeric(eNetModel_K562_50kb_RUS_Distance$bestTune[1])
eNetModel_K562_50kb_RUS_Distance_lambda <- as.numeric(eNetModel_K562_50kb_RUS_Distance$bestTune[2])
```

#### SMOTE

##### OC

```{r}
eNetModel_K562_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/eNetModel.rds")
eNetModel_K562_50kb_SMOTE_oc_alpha <- as.numeric(eNetModel_K562_50kb_SMOTE_oc$bestTune[1])
eNetModel_K562_50kb_SMOTE_oc_lambda <- as.numeric(eNetModel_K562_50kb_SMOTE_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_50kb_SMOTE_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/eNetModel.rds")
eNetModel_K562_50kb_SMOTE_OP_alpha <- as.numeric(eNetModel_K562_50kb_SMOTE_OP$bestTune[1])
eNetModel_K562_50kb_SMOTE_OP_lambda <- as.numeric(eNetModel_K562_50kb_SMOTE_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_50kb_SMOTE_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/eNetModel.rds")
eNetModel_K562_50kb_SMOTE_Distance_alpha <- as.numeric(eNetModel_K562_50kb_SMOTE_Distance$bestTune[1])
eNetModel_K562_50kb_SMOTE_Distance_lambda <- as.numeric(eNetModel_K562_50kb_SMOTE_Distance$bestTune[2])
```

### 100kb

#### none

##### OC

```{r}
eNetModel_K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/eNetModel.rds")
eNetModel_K562_100kb_none_oc_alpha <- as.numeric(eNetModel_K562_100kb_none_oc$bestTune[1])
eNetModel_K562_100kb_none_oc_lambda <- as.numeric(eNetModel_K562_100kb_none_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_100kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/eNetModel.rds")
eNetModel_K562_100kb_none_OP_alpha <- as.numeric(eNetModel_K562_100kb_none_OP$bestTune[1])
eNetModel_K562_100kb_none_OP_lambda <- as.numeric(eNetModel_K562_100kb_none_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_100kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/eNetModel.rds")
eNetModel_K562_100kb_none_Distance_alpha <- as.numeric(eNetModel_K562_100kb_none_Distance$bestTune[1])
eNetModel_K562_100kb_none_Distance_lambda <- as.numeric(eNetModel_K562_100kb_none_Distance$bestTune[2])
```

#### ROS

##### OC

```{r}
eNetModel_K562_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/eNetModel.rds")
eNetModel_K562_100kb_ROS_oc_alpha <- as.numeric(eNetModel_K562_100kb_ROS_oc$bestTune[1])
eNetModel_K562_100kb_ROS_oc_lambda <- as.numeric(eNetModel_K562_100kb_ROS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_100kb_ROS_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/eNetModel.rds")
eNetModel_K562_100kb_ROS_OP_alpha <- as.numeric(eNetModel_K562_100kb_ROS_OP$bestTune[1])
eNetModel_K562_100kb_ROS_OP_lambda <- as.numeric(eNetModel_K562_100kb_ROS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_100kb_ROS_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/eNetModel.rds")
eNetModel_K562_100kb_ROS_Distance_alpha <- as.numeric(eNetModel_K562_100kb_ROS_Distance$bestTune[1])
eNetModel_K562_100kb_ROS_Distance_lambda <- as.numeric(eNetModel_K562_100kb_ROS_Distance$bestTune[2])
```

#### RUS

##### OC

```{r}
eNetModel_K562_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/eNetModel.rds")
eNetModel_K562_100kb_RUS_oc_alpha <- as.numeric(eNetModel_K562_100kb_RUS_oc$bestTune[1])
eNetModel_K562_100kb_RUS_oc_lambda <- as.numeric(eNetModel_K562_100kb_RUS_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_100kb_RUS_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/eNetModel.rds")
eNetModel_K562_100kb_RUS_OP_alpha <- as.numeric(eNetModel_K562_100kb_RUS_OP$bestTune[1])
eNetModel_K562_100kb_RUS_OP_lambda <- as.numeric(eNetModel_K562_100kb_RUS_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_100kb_RUS_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/eNetModel.rds")
eNetModel_K562_100kb_RUS_Distance_alpha <- as.numeric(eNetModel_K562_100kb_RUS_Distance$bestTune[1])
eNetModel_K562_100kb_RUS_Distance_lambda <- as.numeric(eNetModel_K562_100kb_RUS_Distance$bestTune[2])
```

#### SMOTE

##### OC

```{r}
eNetModel_K562_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/eNetModel.rds")
eNetModel_K562_100kb_SMOTE_oc_alpha <- as.numeric(eNetModel_K562_100kb_SMOTE_oc$bestTune[1])
eNetModel_K562_100kb_SMOTE_oc_lambda <- as.numeric(eNetModel_K562_100kb_SMOTE_oc$bestTune[2])
```

##### OP

```{r}
eNetModel_K562_100kb_SMOTE_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/eNetModel.rds")
eNetModel_K562_100kb_SMOTE_OP_alpha <- as.numeric(eNetModel_K562_100kb_SMOTE_OP$bestTune[1])
eNetModel_K562_100kb_SMOTE_OP_lambda <- as.numeric(eNetModel_K562_100kb_SMOTE_OP$bestTune[2])
```

##### Distance

```{r}
eNetModel_K562_100kb_SMOTE_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/eNetModel.rds")
eNetModel_K562_100kb_SMOTE_Distance_alpha <- as.numeric(eNetModel_K562_100kb_SMOTE_Distance$bestTune[1])
eNetModel_K562_100kb_SMOTE_Distance_lambda <- as.numeric(eNetModel_K562_100kb_SMOTE_Distance$bestTune[2])
```

## Creating Table

```{r}
eNetModel_K562_parameter_tab <- data.frame(Alpha=c(eNetModel_K562_10kb_none_oc_alpha,
                                                      eNetModel_K562_10kb_none_OP_alpha,
                                                      eNetModel_K562_10kb_none_Distance_alpha,

                                                      eNetModel_K562_10kb_ROS_oc_alpha,
                                                      eNetModel_K562_10kb_ROS_OP_alpha,
                                                      eNetModel_K562_10kb_ROS_Distance_alpha,

                                                      eNetModel_K562_10kb_RUS_oc_alpha,
                                                      eNetModel_K562_10kb_RUS_OP_alpha,
                                                      eNetModel_K562_10kb_RUS_Distance_alpha,

                                                      eNetModel_K562_10kb_SMOTE_oc_alpha,
                                                      eNetModel_K562_10kb_SMOTE_OP_alpha,
                                                      eNetModel_K562_10kb_SMOTE_Distance_alpha,

                                                      eNetModel_K562_25kb_none_oc_alpha,
                                                      eNetModel_K562_25kb_none_OP_alpha,
                                                      eNetModel_K562_25kb_none_Distance_alpha,

                                                      eNetModel_K562_25kb_ROS_oc_alpha,
                                                      eNetModel_K562_25kb_ROS_OP_alpha,
                                                      eNetModel_K562_25kb_ROS_Distance_alpha,

                                                      eNetModel_K562_25kb_RUS_oc_alpha,
                                                      eNetModel_K562_25kb_RUS_OP_alpha,
                                                      eNetModel_K562_25kb_RUS_Distance_alpha,

                                                      eNetModel_K562_25kb_SMOTE_oc_alpha,
                                                      eNetModel_K562_25kb_SMOTE_OP_alpha,
                                                      eNetModel_K562_25kb_SMOTE_Distance_alpha,

                                                      eNetModel_K562_50kb_none_oc_alpha,
                                                      eNetModel_K562_50kb_none_OP_alpha,
                                                      eNetModel_K562_50kb_none_Distance_alpha,

                                                      eNetModel_K562_50kb_ROS_oc_alpha,
                                                      eNetModel_K562_50kb_ROS_OP_alpha,
                                                      eNetModel_K562_50kb_ROS_Distance_alpha,

                                                      eNetModel_K562_50kb_RUS_oc_alpha,
                                                      eNetModel_K562_50kb_RUS_OP_alpha,
                                                      eNetModel_K562_50kb_RUS_Distance_alpha,

                                                      eNetModel_K562_50kb_SMOTE_oc_alpha,
                                                      eNetModel_K562_50kb_SMOTE_OP_alpha,
                                                      eNetModel_K562_50kb_SMOTE_Distance_alpha,

                                                      eNetModel_K562_100kb_none_oc_alpha,
                                                      eNetModel_K562_100kb_none_OP_alpha,
                                                      eNetModel_K562_100kb_none_Distance_alpha,

                                                      eNetModel_K562_100kb_ROS_oc_alpha,
                                                      eNetModel_K562_100kb_ROS_OP_alpha,
                                                      eNetModel_K562_100kb_ROS_Distance_alpha,

                                                      eNetModel_K562_100kb_RUS_oc_alpha,
                                                      eNetModel_K562_100kb_RUS_OP_alpha,
                                                      eNetModel_K562_100kb_RUS_Distance_alpha,

                                                      eNetModel_K562_100kb_SMOTE_oc_alpha,
                                                      eNetModel_K562_100kb_SMOTE_OP_alpha,
                                                      eNetModel_K562_100kb_SMOTE_Distance_alpha),
                                              Lambda=c(eNetModel_K562_10kb_none_oc_lambda,
                                                      eNetModel_K562_10kb_none_OP_lambda,
                                                      eNetModel_K562_10kb_none_Distance_lambda,

                                                      eNetModel_K562_10kb_ROS_oc_lambda,
                                                      eNetModel_K562_10kb_ROS_OP_lambda,
                                                      eNetModel_K562_10kb_ROS_Distance_lambda,

                                                      eNetModel_K562_10kb_RUS_oc_lambda,
                                                      eNetModel_K562_10kb_RUS_OP_lambda,
                                                      eNetModel_K562_10kb_RUS_Distance_lambda,

                                                      eNetModel_K562_10kb_SMOTE_oc_lambda,
                                                      eNetModel_K562_10kb_SMOTE_OP_lambda,
                                                      eNetModel_K562_10kb_SMOTE_Distance_lambda,

                                                      eNetModel_K562_25kb_none_oc_lambda,
                                                      eNetModel_K562_25kb_none_OP_lambda,
                                                      eNetModel_K562_25kb_none_Distance_lambda,

                                                      eNetModel_K562_25kb_ROS_oc_lambda,
                                                      eNetModel_K562_25kb_ROS_OP_lambda,
                                                      eNetModel_K562_25kb_ROS_Distance_lambda,

                                                      eNetModel_K562_25kb_RUS_oc_lambda,
                                                      eNetModel_K562_25kb_RUS_OP_lambda,
                                                      eNetModel_K562_25kb_RUS_Distance_lambda,

                                                      eNetModel_K562_25kb_SMOTE_oc_lambda,
                                                      eNetModel_K562_25kb_SMOTE_OP_lambda,
                                                      eNetModel_K562_25kb_SMOTE_Distance_lambda,

                                                      eNetModel_K562_50kb_none_oc_lambda,
                                                      eNetModel_K562_50kb_none_OP_lambda,
                                                      eNetModel_K562_50kb_none_Distance_lambda,

                                                      eNetModel_K562_50kb_ROS_oc_lambda,
                                                      eNetModel_K562_50kb_ROS_OP_lambda,
                                                      eNetModel_K562_50kb_ROS_Distance_lambda,

                                                      eNetModel_K562_50kb_RUS_oc_lambda,
                                                      eNetModel_K562_50kb_RUS_OP_lambda,
                                                      eNetModel_K562_50kb_RUS_Distance_lambda,

                                                      eNetModel_K562_50kb_SMOTE_oc_lambda,
                                                      eNetModel_K562_50kb_SMOTE_OP_lambda,
                                                      eNetModel_K562_50kb_SMOTE_Distance_lambda,

                                                      eNetModel_K562_100kb_none_oc_lambda,
                                                      eNetModel_K562_100kb_none_OP_lambda,
                                                      eNetModel_K562_100kb_none_Distance_lambda,

                                                      eNetModel_K562_100kb_ROS_oc_lambda,
                                                      eNetModel_K562_100kb_ROS_OP_lambda,
                                                      eNetModel_K562_100kb_ROS_Distance_lambda,

                                                      eNetModel_K562_100kb_RUS_oc_lambda,
                                                      eNetModel_K562_100kb_RUS_OP_lambda,
                                                      eNetModel_K562_100kb_RUS_Distance_lambda,

                                                      eNetModel_K562_100kb_SMOTE_oc_lambda,
                                                      eNetModel_K562_100kb_SMOTE_OP_lambda,
                                                      eNetModel_K562_100kb_SMOTE_Distance_lambda))

eNetModel_K562_parameter_tab$CL <- "K562"
eNetModel_K562_parameter_tab$Resolution <- c(rep("10 kb", 12),
                                                rep("25 kb", 12),
                                                rep("50 kb", 12),
                                                rep("100 kb", 12))
eNetModel_K562_parameter_tab$PredictorType <- rep(c("OC","OP","Distance"),16)
eNetModel_K562_parameter_tab <- eNetModel_K562_parameter_tab[,c(3:5,1:2)]
```

#All cell lines

```{r}
eNetModel_parameters_table <- rbind.data.frame(eNetModel_gm12878_parameter_tab,
                                               eNetModel_K562_parameter_tab)

write.csv(eNetModel_parameters_table, "C:/Users/stili/Downloads/eNetModel_parameters_table.csv")
```

### 2019-04-21 Manuscript/manuscript.Rmd
editted manuscript
manuscript edits

@@
 The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
+For each of the 4 data resolutions, a total of 8008, 4869, 2449, and 1075 unique TADs were extracted from the GM12878 cell line, and a total of 5828, 4097, 2181, and 986 unique TADs were extracted from the K562 cell line.
+The TADs were distributed throughput the autosomal chromosomes, with larger chromosomes containing more TADs (Supplementary Figure 14; Supplementary Table 8).
 The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained.
@@
 For the boundary data, in order to accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
-For example, for 10 kb data, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
-A genomic bin was labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
+For example, for 10 kb resolution data, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
+A genomic bin was then labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
 Otherwise, the bin was labeled as not containing a boundary (Y=0).
+The process was repeat for each subsequent resolution.
 
@@
 
-### FEATURE ENGINEERING AND RE-SAMPLING
+### FEATURE ENGINEERING
 
@@
 **Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter simply as $\textit{distance}$), from the center of the bin to the center of the nearest region defined by a specific genomic annotation was calculated.
-The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figures 1).
+The log transformation was used as a normalization technique in order to account for the skewness present in the distance densities (Supplementary Figures 1).
+
+### DATA RE-SAMPLING
 
@@
 Once the appropriate predictor type and set of features were determined, a final set of random forest classification models were performed to fully compare re-sampling techniques.
-To reduce bias due to random dataset generation, 10-fold cross validation was used <!--to tune the number of features to consider at each node and the number of ensemble trees to aggregate-->.The default number of features to consider at each node of the random forest algorithm was set as the square root of the number of features in the model.
+To reduce bias due to random dataset generation, 10-fold cross validation was used <!--to tune the number of features to consider at each node and the number of ensemble trees to aggregate-->.
+The default number of features to consider at each node of the random forest algorithm was set as the square root of the number of features in the model.
 Likewise, the number of ensemble trees to aggregate was set at 500.
@@
 
-The efficacy of each re-sampling technique was compared using composite metrics including F1-score and MCC. These metrics are defined as follows:
+The efficacy of each ensemble system in the framework was compared using composite metrics including F1-score and MCC. These metrics are defined as follows:
 
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-<!--Additional threshold-free metrics where also reported including the AUROC and AUPRC.--> Lastly, for the task of identifying the genomic annotations that were most predictive of the formation of TAD boundaries, we ranked the variable importances associated with each feature of the ensemble system-specific random forest model.
-<!--To calculate variable importances for each model, the F1-Score on the out-of-bag portion of the data within each tree was recorded.
+Additional performance metrics were reported in the supplementary materials.
+
+<!--Additional threshold-free metrics where also reported including the AUROC and AUPRC.-->
+
+<!--
+Lastly, for the task of identifying the genomic annotations that were most predictive of the formation of TAD boundaries, we ranked the variable importances associated with each feature of the ensemble system-specific random forest model.
+To calculate variable importances for each model, the F1-Score on the out-of-bag portion of the data within each tree was recorded.
 Then the same was done after permuting each predictor variable.
-The difference between the two AUPRC values was then averaged over all trees, and normalized by the standard error of the differences.--> Annotations with low rankings correspond to functional epigenomic features that are either positively or negatively enriched near TAD boundaries, and thus, better allow the model to discriminate between genomic bins that overlap with flanked TAD boundaries.
+The difference between the two AUPRC values was then averaged over all trees, and normalized by the standard error of the differences.
+Annotations with low rankings correspond to functional epigenomic features that are either positively or negatively enriched near TAD boundaries, and thus, better allow the model to discriminate between genomic bins that overlap with flanked TAD boundaries.
+-->
 
@@
 
-We examined the class imbalance of the different data resolutions for each cell line.
+To assess the full severity of class imbalance present when constructing the models, we investigated the relationship between the total number of bins (sample observations) included at each resolution and the subsequent imbalance ratio (IR).
 As expected, the total number of genomic bins decreased as resolution decreased (Figure 4A).
 Specifically, at lower resolutions, the linear genome was binned into larger units, thereby creating fewer bins.
-The imbalance ratios, however, remained relatively stable and consistent across resolutions and cell line (Figure 4B).
+however, the IRs remained relatively stable and consistent across resolutions and cell lines (Figure 4B).
 We found that there was an average IR of 0.154 (SD=0.022) and 0.137 (SD=0.0181) across resolutions for the GM12878 and K562 cell lines respectively.
@@
 
-We first evaluated performances for models implemented using OC predictor types, without re-sampling, as these characteristics represented models with the least granularity and could act as a baseline.
-In evaluating such composite metrics like F1-Score and MCC, we found that these models exhibited poor performances across resolutions, for the GM12878 cell line (Figure 5A).
-<!--The average F1-Score and MCC across resolution was found to be 0.04 and 0.07 respectively.--> When including OP perdictor types as the feature space, coupled with no resampling, we found that performances were worse than when using OC predictor types for the GM12878 cell line (Figure 5B).
-<!--Here, the average F1-Score and MCC was found to be 0.01 and 0.03 respectively.--> Models built on distance-type predictors in conjuction with no resampling, however, were found to exhibit slightly better performances than the other two types<!--, with average F1-Scores and MCCs of 0.08 and 0.10 respectively--> (Figure 5C).
-Importantly, when validating models built on fully imbalanced datasets, the F1-Score and MCC could not be determined at lower resolutions given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives.
-Furthermore, evaluating models using conventional metrics such as AUC or accuracy did not depict the true severity in performance (Supplementary Table 3).
+In order to set a baseline in performance, we first evaluated the least granular model, that is one implemented using OC predictor types, without data re-sampling.
+In evaluating such composite metrics like F1-Score and MCC, we found that for the GM12878 cell line, these models exhibited poor performances across all resolutions (Figure 5A).
+<!--The average F1-Score and MCC across resolution was found to be 0.04 and 0.07 respectively.-->
+
+We then gradually increased the granularity in the characteristics of the model by assess the model built on OP predictor types, while still not performing any data resampling.
+Here we found that performances were worse than when using OC predictor types for the GM12878 cell line (Figure 5B).
+<!--Here, the average F1-Score and MCC was found to be 0.01 and 0.03 respectively.--> Finally, models built on distance-type predictors in conjuction with no resampling, however, were found to exhibit slightly better performances than the other two types<!--, with average F1-Scores and MCCs of 0.08 and 0.10 respectively--> (Figure 5C).
+
+Importantly, when validating these 3 models built on fully imbalanced datasets, the F1-Score and MCC could not be determined at lower resolutions given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives.
+Furthermore, we found that evaluating models using conventional metrics, such as AUC or accuracy, did not depict the true severity in performance (Supplementary Table 3).
 <!--The average AUC across resolutions for the OC, OP, and distance type predictors was 0.65, 0.66, and 0.85 respectively, where as the average accuracies were 0.89, 0.89, and 0.90 respectively (Supplementary Table 3).--> Results were found to be consistently poor across resolutions for the K562 cell line (Supplementary Figure 10).
-Similarly, many of the performance metrics at higher resolutions were unable to be reported due to the models inability to produce any true positive cases.
+Similarly, many of the performance metrics at higher resolutions were also unable to be reported due to the models inability to produce any true positive cases.
 
@@
 Using permutation tests we found that the transcription factors SMC3a, ZNF143, CTCF, and RAD21 tended to have binding peaks that that were located closer to the centers of 10 kb sized genomic bins that overlapped with flanked TAD boundaries than to bins that did not overlap with flanked TAD boundaries across both cell lines (Figure 7 A-H).
-Similar distance profiles for the same TFBS were obtained when assessed at lower resolutions, across both cell lines (Supplementary Figures X-X)
+Similar distance profiles for the same TFBS were obtained when assessed at lower resolutions, across both cell lines (Supplementary Figures 12 & 13 A-L).
 

### 2019-04-21 Manuscript/manuscript.Rmd
improving story

@@
 
-We then investigated which genomic annotations were most predictive of TAD boundary formation, across resolution for random forest models with the best given set of data-level characteristics determined above (SMOTE re-sampled with distance type predictors).
-We found that specific transcription factor binding sites (TFBS), including SMC3ab, ZNF143, CTCF, and RAD21, were given consistently high rankings of predictive importance in the models built on the GM12878 cell line (Table 1).
-These are known factors associated with the hypothesized loop extrusion model [@fudenberg2016formation; @alipour2012self] and were found to be ranked consistently high on the K562 cell line as well, with similar rankings across resolutions (Supplementary Table 6).
+In addition to adressing both the affect of class imbalance and the optimal spatial relationships used when predicting TAD boundaries, we also aimed at identifying the genomic annotations that were most predictive of TAD boundary formation.
+In doing so, we investigated which genomic annotations yielded the hight predictive importance values for random forest models implemented on the best given set of data-level characteristics determined above (SMOTE re-sampled with distance type predictors), across resolution and cell line.
+We found that specific transcription factor binding sites (TFBS), including SMC3ab, ZNF143, CTCF, and RAD21, were given consistently high predictive importance in the models built on the GM12878 cell line, across all resolutions (Figure 8).
+These are known factors associated with the hypothesized loop extrusion model [@fudenberg2016formation; @alipour2012self] and were found to yield consistently high predictive importance on the K562 cell line as well, with similar profiles across resolutions (Supplementary Figure 15).
 Other annotations known to be associated with gene regulation and affect structural properties of chromatin, such as the YY1  transcription factor, as well DNAse hypersensitive sites, regions of heterochromatin, and the H3k27 trimethylation histone modifications were ranked high on the 10 kb resolution, but were less consistently ranked at lower resolutions for both cell lines.

### 2019-04-22 Scripts/comparing_distance_profiles_using_density_plots.Rmd
added script for evaluating distance profiles using violin and shift plots

--- 2019-04-19 Scripts/comparing_distance_densities_by_genomic_bin_class.Rmd
@@
              "Broad",
-             "Uchicago"), collapse = "|"), "", "K562-Ctcf-Broad_dist")
+             "Uchicago"), collapse = "|"), "", "K562-Ctcfc-Broad_dist")
 
@@
                           "",
-                          "K562-Ctcf-Broad_dist"))
-
-p.K562.10kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
+                          "K562-Ctcfc-Broad_dist"))
+
+p.K562.10kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcfc_dist, color=y)) +
     geom_density() +
@@
                           "",
-                          "K562-Ctcf-Broad_dist"))
-
-p.K562.25kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
+                          "K562-Ctcfc-Broad_dist"))
+
+p.K562.25kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcfc_dist, color=y)) +
     geom_density() +
@@
                           "",
-                          "K562-Ctcf-Broad_dist"))
-
-p.K562.50kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
+                          "K562-Ctcfc-Broad_dist"))
+
+p.K562.50kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcfc_dist, color=y)) +
     geom_density() +
@@
                           "",
-                          "K562-Ctcf-Broad_dist"))
-
-p.K562.100kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
+                          "K562-Ctcfc-Broad_dist"))
+
+p.K562.100kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcfc_dist, color=y)) +
     geom_density() +

### 2019-04-22 Scripts/comparing_distance_profiles_using_violin_and_shift_plots.Rmd
added script for evaluating distance profiles using violin and shift plots

---
title: "Comparing Distance Profiles Using Violin Plots and Shift Function"
author: "Spiro Stilianoudakis"
date: "April 21, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(coin)
library(cowplot)
```

# Functions for shift function

```{r}
setwd("C:/Users/stili/Documents/TAD_miscellaneous/shift_function")

source("Rallfun-v30.txt")
source("wilcox_modified.txt")
source("rgar_visualisation.txt")
source("rgar_utils.txt")

```

# GM12878

## 10kb

```{r}
train <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds"))

enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))

names(train) <- gsub(paste(c("`", 
                             "Gm12878", 
                             "-", 
                             #"_", 
                             #"dist", "count", "perc",
                             "Haib", 
                             "Sydh",
                             "Uta",
                             "Uw",
                             "Broad",
                             "Uchicago"), collapse = "|"), "", names(train))
train <- train[,c(1,which(names(train) %in% enetcoefs))]

set.seed(123)
train_smote <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

```

### Top Annotations

####SMC

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Smc3ab9263-Sydh_dist")

annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
                     data=annotdata.smc,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Smc3ab9263-Sydh_dist"))

violin.gm12878.10kb.smc <- ggplot(annotdata.smc, aes(x=ordered(y, levels=rev(unique(y))), y=Smc3ab9263_dist, color=y)) + 
  geom_violin(trim=FALSE)+
  geom_boxplot(width=0.1, fill="white")+
  coord_flip() +
  scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Did not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary"))+
  xlab("Class of Genomic Bin") +
  ylab("Log2 Distance") +
  ggtitle("SMC3") +
  #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 15),
    axis.text.y = element_blank(),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))

out <- shifthd(annotdata.smc$Smc3ab9263_dist[which(annotdata.smc$y=="No")],
               annotdata.smc$Smc3ab9263_dist[which(annotdata.smc$y=="Yes")],
               nboot=200)

ylim <- max(max(abs(out$ci_upper)),max(abs(out$ci_lower)))
ylim <- c(-ylim,ylim)
xintercept <- as.numeric(out[5,1]) # get median of group 1
#xbreaks <- out[,1] # get deciles of group 1
xplot = names(out)[1]

shift.gm12878.10kb.smc <- ggplot(out, aes_string(x=xplot, y="difference")) +
  geom_hline(yintercept=0,linetype=2,alpha=0.5) + # x=0 reference line
  geom_vline(xintercept=xintercept,linetype=2,alpha=0.5) + # y=median reference line
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), colour="black", width=.15) +
  geom_line(colour="black", linetype="solid", size=1.5) +
  geom_point(colour="black", size=4, shape=21, fill="white") + #999999
  xlab("Quantiles for bins that\nOverlapped w/flanked TAD boundaries") +
  ylab("Quantile differences between bin class") +
  theme_bw() +
  theme(axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14),
        axis.title.x = element_text(size=16,face="bold"),
        axis.title.y = element_text(size=16,face="bold")) +
  scale_y_continuous(limits = ylim)

ggarrange(violin.gm12878.10kb.smc,
          shift.gm12878.10kb.smc,
          ncol=1,
          nrow=2,
          common.legend = TRUE,
          legend = "top")
```

### 2019-04-22 Scripts/comparing_distance_profiles_using_violin_and_shift_plots.Rmd
editted script

@@
                          labels=c("Did not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary"))+
-  xlab("Class of Genomic Bin") +
-  ylab("Log2 Distance") +
+  xlab("Class of genomic bin") +
+  ylab("Log2 distance") +
   ggtitle("SMC3") +
-  #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
   theme_bw() +
@@
     axis.text.y = element_blank(),
-    axis.title.x = element_text(size = 20),
-    axis.title.y = element_text(size = 20),
+    axis.title.x = element_text(size = 15),
+    axis.title.y = element_text(size = 15),
     legend.text=element_text(size=15),
-    legend.title=element_text(size=20),
+    legend.title=element_text(size=15),
+    legend.position="top",
     plot.title = element_text(size=20,
@@
   geom_vline(xintercept=xintercept,linetype=2,alpha=0.5) + # y=median reference line
-  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), colour="black", width=.15) +
+  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), colour="black", width=.10) +
   geom_line(colour="black", linetype="solid", size=1.5) +
   geom_point(colour="black", size=4, shape=21, fill="white") + #999999
-  xlab("Quantiles for bins that\nOverlapped w/flanked TAD boundaries") +
-  ylab("Quantile differences between bin class") +
+  xlab("Quantiles for bins that Overlapped\nw/flanked TAD boundaries") +
+  ylab("Quantile differences") +
   theme_bw() +
-  theme(axis.text.x = element_text(size=14),
-        axis.text.y = element_text(size=14),
-        axis.title.x = element_text(size=16,face="bold"),
-        axis.title.y = element_text(size=16,face="bold")) +
+  theme(axis.text.x = element_text(size=15),
+        axis.text.y = element_text(size=15),
+        axis.title.x = element_text(size=15),
+        axis.title.y = element_text(size=15)) +
   scale_y_continuous(limits = ylim)
 
-ggarrange(violin.gm12878.10kb.smc,
-          shift.gm12878.10kb.smc,
-          ncol=1,
+```
+
+####ZNF143
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Znf143166181ap-Sydh_dist")
+
+annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
+                     data=annotdata.znf143,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Znf143166181ap-Sydh_dist"))
+
+violin.gm12878.10kb.znf143 <- ggplot(annotdata.znf143, aes(x=ordered(y, levels=rev(unique(y))), y=Znf143166181ap_dist, color=y)) + 
+  geom_violin(trim=FALSE)+
+  geom_boxplot(width=0.1, fill="white")+
+  coord_flip() +
+  scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Did not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary"))+
+  xlab("Class of genomic bin") +
+  ylab("Log2 distance") +
+  ggtitle("ZNF143") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size = 15),
+    axis.text.y = element_blank(),
+    axis.title.x = element_text(size = 15),
+    axis.title.y = element_text(size = 15),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=15),
+    legend.position="top",
+    plot.title = element_text(size=20,
+                              hjust=.5))
+
+out <- shifthd(annotdata.znf143$Znf143166181ap_dist[which(annotdata.znf143$y=="No")],
+               annotdata.znf143$Znf143166181ap_dist[which(annotdata.znf143$y=="Yes")],
+               nboot=200)
+
+ylim <- max(max(abs(out$ci_upper)),max(abs(out$ci_lower)))
+ylim <- c(-ylim,ylim)
+xintercept <- as.numeric(out[5,1]) # get median of group 1
+#xbreaks <- out[,1] # get deciles of group 1
+xplot = names(out)[1]
+
+shift.gm12878.10kb.znf143 <- ggplot(out, aes_string(x=xplot, y="difference")) +
+  geom_hline(yintercept=0,linetype=2,alpha=0.5) + # x=0 reference line
+  geom_vline(xintercept=xintercept,linetype=2,alpha=0.5) + # y=median reference line
+  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), colour="black", width=.10) +
+  geom_line(colour="black", linetype="solid", size=1.5) +
+  geom_point(colour="black", size=4, shape=21, fill="white") + #999999
+  xlab("Quantiles for bins that Overlapped\nw/flanked TAD boundaries") +
+  ylab("Quantile differences") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+        axis.text.y = element_text(size=15),
+        axis.title.x = element_text(size=15),
+        axis.title.y = element_text(size=15)) +
+  scale_y_continuous(limits = ylim)
+
+```
+
+####CTCF
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Ctcf-Broad_dist")
+
+annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
+                     data=annotdata.ctcf,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Ctcf-Broad_dist"))
+
+violin.gm12878.10kb.ctcf <- ggplot(annotdata.ctcf, aes(x=ordered(y, levels=rev(unique(y))), y=Ctcf_dist, color=y)) + 
+  geom_violin(trim=FALSE)+
+  geom_boxplot(width=0.1, fill="white")+
+  coord_flip() +
+  scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Did not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary"))+
+  xlab("Class of genomic bin") +
+  ylab("Log2 distance") +
+  ggtitle("CTCF") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size = 15),
+    axis.text.y = element_blank(),
+    axis.title.x = element_text(size = 15),
+    axis.title.y = element_text(size = 15),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=15),
+    legend.position="top",
+    plot.title = element_text(size=20,
+                              hjust=.5))
+
+out <- shifthd(annotdata.ctcf$Ctcf_dist[which(annotdata.ctcf$y=="No")],
+               annotdata.ctcf$Ctcf_dist[which(annotdata.ctcf$y=="Yes")],
+               nboot=200)
+
+ylim <- max(max(abs(out$ci_upper)),max(abs(out$ci_lower)))
+ylim <- c(-ylim,ylim)
+xintercept <- as.numeric(out[5,1]) # get median of group 1
+#xbreaks <- out[,1] # get deciles of group 1
+xplot = names(out)[1]
+
+shift.gm12878.10kb.ctcf <- ggplot(out, aes_string(x=xplot, y="difference")) +
+  geom_hline(yintercept=0,linetype=2,alpha=0.5) + # x=0 reference line
+  geom_vline(xintercept=xintercept,linetype=2,alpha=0.5) + # y=median reference line
+  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), colour="black", width=.10) +
+  geom_line(colour="black", linetype="solid", size=1.5) +
+  geom_point(colour="black", size=4, shape=21, fill="white") + #999999
+  xlab("Quantiles for bins that Overlapped\nw/flanked TAD boundaries") +
+  ylab("Quantile differences") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+        axis.text.y = element_text(size=15),
+        axis.title.x = element_text(size=15),
+        axis.title.y = element_text(size=15)) +
+  scale_y_continuous(limits = ylim)
+
+```
+
+####RAD21
+
+```{r}
+annotname <- gsub(paste(c("`", 
+             "Gm12878", 
+             "-", 
+             #"_", 
+             #"dist", "count", "perc",
+             "Haib", 
+             "Sydh",
+             "Uta",
+             "Uw",
+             "Broad",
+             "Uchicago"), collapse = "|"), "", "Gm12878-Rad21-Haib_dist")
+
+annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]
+
+#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")
+
+perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
+                     data=annotdata.rad21,
+                     alternative="greater", 
+                     distribution=approximate(B=10000)))[1]
+
+perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+
+plottitle <- paste(gsub(paste(c("Gm12878",
+                                  "-","_",
+                                  "dist","perc","count",
+                                  "Haib",
+                                  "Sydh",
+                                  "Uta",
+                                  "Uw",
+                                  "Broad",
+                                  "Uchicago"), 
+                                collapse = "|"), 
+                          "",
+                          "Gm12878-Rad21-Haib_dist"))
+
+violin.gm12878.10kb.rad21 <- ggplot(annotdata.rad21, aes(x=ordered(y, levels=rev(unique(y))), y=Rad21_dist, color=y)) + 
+  geom_violin(trim=FALSE)+
+  geom_boxplot(width=0.1, fill="white")+
+  coord_flip() +
+  scale_color_discrete(name="Class of\nGenomic Bin",
+                         labels=c("Did not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary"))+
+  xlab("Class of genomic bin") +
+  ylab("Log2 distance") +
+  ggtitle("RAD21") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size = 15),
+    axis.text.y = element_blank(),
+    axis.title.x = element_text(size = 15),
+    axis.title.y = element_text(size = 15),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=15),
+    legend.position="top",
+    plot.title = element_text(size=20,
+                              hjust=.5))
+
+out <- shifthd(annotdata.rad21$Rad21_dist[which(annotdata.rad21$y=="No")],
+               annotdata.rad21$Rad21_dist[which(annotdata.rad21$y=="Yes")],
+               nboot=200)
+
+ylim <- max(max(abs(out$ci_upper)),max(abs(out$ci_lower)))
+ylim <- c(-ylim,ylim)
+xintercept <- as.numeric(out[5,1]) # get median of group 1
+#xbreaks <- out[,1] # get deciles of group 1
+xplot = names(out)[1]
+
+shift.gm12878.10kb.rad21 <- ggplot(out, aes_string(x=xplot, y="difference")) +
+  geom_hline(yintercept=0,linetype=2,alpha=0.5) + # x=0 reference line
+  geom_vline(xintercept=xintercept,linetype=2,alpha=0.5) + # y=median reference line
+  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), colour="black", width=.10) +
+  geom_line(colour="black", linetype="solid", size=1.5) +
+  geom_point(colour="black", size=4, shape=21, fill="white") + #999999
+  xlab("Quantiles for bins that Overlapped\nw/flanked TAD boundaries") +
+  ylab("Quantile differences") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+        axis.text.y = element_text(size=15),
+        axis.title.x = element_text(size=15),
+        axis.title.y = element_text(size=15)) +
+  scale_y_continuous(limits = ylim)
+
+```
+
+###Plots
+
+```{r}
+ggarrange(violin.gm12878.10kb.smc,violin.gm12878.10kb.znf143,violin.gm12878.10kb.ctcf,violin.gm12878.10kb.rad21,
+          shift.gm12878.10kb.smc,shift.gm12878.10kb.znf143,shift.gm12878.10kb.ctcf,shift.gm12878.10kb.rad21,
+          ncol=4,
           nrow=2,
           common.legend = TRUE,
-          legend = "top")
+          legend = "top",
+          labels = c("A","B","C","D","","","",""),
+          font.label = list(size=20))
+
 ```

### 2019-04-24 Manuscript/Figures/figure_legends.Rmd
editted legends
added figure/table legends

@@
 
-**Figure 1: Model Construction.** An illustration of the proposed model construction given cell line-specific Hi-C matrices.
+**Figure 1.
+Model Construction.** An illustration of the proposed model construction given cell line-specific Hi-C matrices.
 The contact matrix above is a visualization of the interconnectivity of chromosome 14 at 100 kb resolution, for the GM12878 cell line, on the intervals from 20 mb to 100 mb.
@@
 
-**Figure 2: Ensemble Framework/Model Building Pipeline.** A diagram of the model building pipeline given a combination of inputs from the ensemble framework.
-A particular ensemble system included the total number of genomic bins, labeled as having been overlapped with a flanked TAD boundary or not, as well as a feature space composed of 1 of 3 different predictor-type specific annotations.
+**Figure 2.
+Ensemble Framework.** A diagram of the ensemble framework detailing the various combination of inputs used in the model building pipeline.
+A given system within the ensemble framework included the total number of genomic bins, labeled as having been overlapped with a flanked TAD boundary or not, as well as a feature space composed of 1 of 3 different predictor-type specific annotations.
 The data was then split into a 7:3 training:testing set ratio.
@@
 **Figure 3.
-The three predictor types considered when quantifying the association between TAD boundaries and genomic annotations.** The _overlap count_ (OC) predictors consider the total number of genomic features that overlapped with each genomic bin.
+The three predictor types.** Three separate types of predictors were considered when quantifying the association between TAD boundaries and genomic annotations.
+Each predictor type was used to build the feature space of specific models in the ensemble framework.
+The _overlap count_ (OC) predictors consider the total number of genomic features that overlapped with each genomic bin.
 The _overlap percent_ (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin by the total bin width.
 The _distance_ ($log_{2}$ transformed) predictors were calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest genomic feature.
+[???should I include ABC here?]
 
 **Figure 4.
-Data summaries in the form of barplots for the GM12878 (red) and K562 (blue) cell lines.** (A) The total number of genomic bins created by partitioning the linear genome into unit intervals corresponding to the resolution of the relevant domain data.
-(B) Subsequent imbalance ratios, defined as the ratio of the number of bins that overlapped with a flanked TAD boundary to the number of bins that did not overlap with a flanked TAD boundary.
+Resolution-specific data summaries.** (A) The total number of genomic bins created by partitioning the linear genome into unit intervals corresponding to the resolution of the relevant domain data for the GM12878 (red) and K562 (blue) cell line.
+(B) Subsequent imbalance ratios created when labelling bin class, defined as the ratio of the number of bins that overlapped with a flanked TAD boundary to the number of bins that did not overlap with a flanked TAD boundary.
 
-**Figure 7. Evaluating effect of class imbalance on model performance.**
+**Figure 5.
+Comparing ensemble system specific model performances for GM12878.** Performances, separated by F1-Score and MCC, of random forest classification models built on each of the 3 predictor types: OC (A), OP (B), and Distance (C).
+Within each predictor type, and across resolution, F1-Scores and MCCs metrics were recorded for models subsequently implemented on re-sampled data using the 4 re-sampling techniques: None (red), ROS (green), RUS (blue), and SMOTE (purple).
+
+**Figure 8.
+Predictive importance of genomic annotations for random forest models implemented on SMOTE resampled data with distance-type predictors for GM12878.** Importance was rescaled to values between 0 and 100, and discretized.
+The importance was subsequently sorted according to the most predictive annotations associated with the 10 kb resolution.
+Annotations with higher values of predictive importance are denoted in dark red, while annotations that were regularized in the pipeline for specific resolutions are denoted in grey.
+
+**Figure 6.
+Comparing category-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for GM12878.** Performances, separated by F1-Score and MCC, were compared for models using specific categories of annotations as the feature space including: histone modifications (red), chromatin state segmentations (green), transcription factor binding sites, and a feature space containing all 3 types combined (purple).
+
+**Figure 7.
+Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 10 kb resolution, on GM12878.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
+For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
+That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
 

### 2019-04-24 Manuscript/Supplementary/supplementary_legends.Rmd
added figure/table legends

--- 2019-04-05 Manuscript/Supplementary/supplementary_legends.Rmd
@@
 
-**Supplementary Table 4. Hi-C Data.** A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains.
+**Supplementary Table 4. Hi-C data.** A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains.
 
-**Supplementary Table 1.
-Genomic Annotations.** A complete list of the genomic annotations used to build the feature space for all downstream models.
+**Supplementary Figure 14.
+Number of TADs called throughout the genome.** TADs were called throughout each of the 22 autosomal chromosomes for cell lines GM12878 (red) and K562 (blue) using the Arrowhead algorithm [@durand2016juicebox], across each data resolution including 10 kb, 25 kb, 50 kb, and 100 kb (A-D) respectively.
+
+**Supplementary Table 8.
+Summary statistics for TAD lengths.** The following summary statistics were recorded regarding lengths of TADs that were called and delineated into TAD boundaries including the minimum, 1st quartile, median, mean, 3rd quartile, and maximum TAD lengths (in basepairs).
+The summaries are provided for each cell line, resolution, and within each chromosome.
+[???should I leave space for 9th chromosome on k562 where no TADs were called?]
+
+**Supplementary Table 2.
+Genomic annotations.** A complete list of the genomic annotations used to build the feature space for all downstream models.
 The GRCh37/hg19 human genome assembly was used.
@@
 **Supplementary Figure 1.
-Distance Densities across cell lines and resolutions.** Density curves of distances (in millions of base pairs) from genomic bins to flanked TAD boundaries for 10 kb (A), 25 kb (B), 50 kb (C), and 100 kb (D) data resolutions across the GM12878 (left column) and K562 (right column) cell lines.
-The untransformed distance densities are filled in red, while the $log_{2}$ tranformed distance densities are filled in blue.
+Distance densities from centers of genomic bins to closest annotation.** Density curves of the distances (in millions of base pairs) from the center of genomic bins to the center of the nearest respective annotation for the GM12878 (left column) and K562 (right column) cell lines respectively.
+Each curve represents the raw (red) and $log_{2}$ transformed (blue) distance profiles for each annotation, across each of the 4 resolutions (A-D).
+
+**Supplementary Figure 2.
+Clustered correlogram for genomic annotations at the 10 kb resolution for the GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 3.
+Clustered correlogram for genomic annotations at the 10 kb resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 4.
+Clustered correlogram for genomic annotations at the 25 kb resolution for GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 5.
+Clustered correlogram for genomic annotations at the 25 kb resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 6.
+Clustered correlogram for genomic annotations at the 50 kb resolution for GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 7.
+Clustered correlogram for genomic annotations at the 50 kb resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 8.
+Clustered correlogram for genomic annotations at the 100 kb resolution for GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Figure 9.
+Clustered correlogram for genomic annotations at the 100 kb resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
+Positive correlations are denoted in red, while negative correlations are denoted in blue.
+The upper triangular matrix of correlations was clustered using Ward's method.
+Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+
+**Supplementary Table 7.
+Optimal alpha and lambda penalization parameters.** The tuned alpha and lambda penalization parameter terms after performing 10-fold cross validated elastic-net regularization specific to cell line, resolution, re-sampling technique, and predictor type.
+
+**Supplementary Figure 10.
+Comparing ensemble system specific model performances for K562.** Performances of random forest classification models built on each of the 3 predictor types: OC (A), OP (B), and Distance (C).
+Within each predictor type, and across resolution, F1-Scores and MCCs metrics were recorded for models subsequently implemented on re-sampled data using the 4 re-sampling techniques: None (red), ROS (green), RUS (blue), and SMOTE (purple).
+
+**Supplementary Table 4.
+Ranking predictive importance between predictor types for annotation-specific models for GM12878.** Annotation-specific random forest classification models were implemented on SMOTE resampled data, across resolution.
+Each model contained each of the 3 predictor types for one genomic annotation.
+Predictive importance was rescaled to values between 0 and 100.
+The predictor type with importance value of 100 indicates it was the most informative predictor type out of the 3.
+
+**Supplementary Table 5.
+Ranking predictive importance between predictor types for annotation-specific models for K562.** Annotation-specific random forest classification models were implemented on SMOTE resampled data, across resolution.
+Each model contained each of the 3 predictor types for one genomic annotation.
+Predictive importance was rescaled to values between 0 and 100.
+The predictor type with importance value of 100 indicates it was the most informative predictor type out of the 3.
+
+**Supplementary Figure 15.
+Predictive importance of genomic annotations for random forest models implemented on SMOTE resampled data with distance-type predictors for K562.** Importance was rescaled to values between 0 and 100, and discretized.
+The importance was subsequently sorted according to the most predictive annotations associated with the 10 kb resolution.
+Annotations with higher values of predictive importance are denoted in dark red, while annotations that were regularized in the pipeline for specific resolutions are denoted in grey.
+
+**Supplementary Figure 11.
+Comparing category-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for K562.** Performances, separated by F1-Score and MCC, were compared for models using specific categories of annotations as the feature space including: histone modifications (red), chromatin state segmentations (green), transcription factor binding sites, and a feature space containing all 3 types combined (purple).
+
+**Supplementary Figure 12.
+Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 25 kb resolution, on GM12878.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
+For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
+That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
+
+**Supplementary Figure 13.
+Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 50 kb resolution, on GM12878.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
+For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
+That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
+
+**Supplementary Figure 14.
+Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 100 kb resolution, on GM12878.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
+For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
+That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
+
+**Supplementary Figure 15.
+Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 10 kb resolution, on K562.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
+For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
+That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
+
+**Supplementary Figure 16.
+Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 25 kb resolution, on K562.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
+For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
+That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
+
+**Supplementary Figure 17.
+Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 50 kb resolution, on K562.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
+For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
+That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
+
+**Supplementary Figure 18.
+Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 100 kb resolution, on K562.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
+For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
+That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
 

### 2019-04-24 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-<!--
 The high correlations among many of the genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.
--->
+For each model created from the ensemble framework, the alpha and lambda were tuned over a grid of values using 10-fold cross validation (Supplementary Table 7).
 
@@
 
+## MODELS IMPLEMENTED ON TRANSCRIPTION FACTOR BINDING SITES OUTPERFORM OTHER ANNOTATION-SPECIFIC MODELS
+
 Given the prevalence of TFBS as the most consistently top ranked predictive features across resolution and cell line, we ventured to further compare performances of annotation specific models.
@@
 
-Distance profiles on a $log_{2}$ scale were found to exhibit significantly different densities between classes of genomic bins for TFBS with highly ranked predictive importances.
-Using permutation tests we found that the transcription factors SMC3a, ZNF143, CTCF, and RAD21 tended to have binding peaks that that were located closer to the centers of 10 kb sized genomic bins that overlapped with flanked TAD boundaries than to bins that did not overlap with flanked TAD boundaries across both cell lines (Figure 7 A-H).
-Similar distance profiles for the same TFBS were obtained when assessed at lower resolutions, across both cell lines (Supplementary Figures 12 & 13 A-L).
+## DISTANCE PROFILES HIGHLIGHT THE RELATIONSHIP BETWEEN KEY TFBS AND TAD BOUNDARIES
+
+When evaluating the 10 kb data resolution, on GM12878, the distance profiles (on a $log_{2}$ scale) were found to be smaller for top predictive TFBS annotations in relation to genomic bins that overlapped with flanked TAD boundaries, when compared to bins that did not overlap with a flanked TAD boundary (Figure 7).
+At the same resolution and cell line, direct comparisons of quantiles obtained from the distribution of distances for the transcription factors SMC3a, ZNF143, CTCF, and RAD21, led to the the conclusion that these TFBS were more often located near TAD boundaries on the linear genome, as can be seen from the shifted quantile differences (Figure 7).
+Similar distance profiles for the same TFBS were obtained when assessed at lower resolutions, across both cell lines (Supplementary Figures 12-17 A-D).
 

### 2019-04-24 Manuscript/Figures/figure_legends.Rmd

@@
 Model Construction.** An illustration of the proposed model construction given cell line-specific Hi-C matrices.
-The contact matrix above is a visualization of the interconnectivity of chromosome 14 at 100 kb resolution, for the GM12878 cell line, on the intervals from 20 mb to 100 mb.
+The contact matrix above is a visualization of the interconnectivity of chromosome 14 at 100 kb resolution, for the GM12878 cell line, on the intervals from 20 mb to 100 mb [@durand2016juicer].
 The boundary coordinates of topologically association domains (TADs) were identified using the Arrowhead algorithm.

### 2019-04-24 Manuscript/manuscript.Rmd

@@
 The location of TAD boundaries is highly conserved, suggesting the presence of epigenomic marks aiding in TAD formation.
-The ability to predict which epigenomic features are most associated with the TAD boundaries will allow for better understanding the regulatory role of the 3D structure of the genome.
+[The ability to predict which epigenomic features are most associated with the TAD boundaries will allow for better understanding the regulatory role of the 3D structure of the genome.
+- ???
+Weak]
 
@@
 Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries.
-Although several useful insights have been made, such as the convergent binding of CTCF [@ong2014ctcf; @ghirlando2016ctcf], many methods ignore key characteristics of domain data, such as the impact of heavily imbalanced number of boundaries vs.
+Although several useful insights have been made, such as the convergent binding of CTCF [@ong2014ctcf; @ghirlando2016ctcf], [???
+Describe other hallmarks of TAD boundaries, with references.
+And, most importantly, why you are doing your study?]
+
+many methods ignore key characteristics of domain data, such as the impact of heavily imbalanced number of boundaries vs.
 other regions.
@@
 
-Multiple random forest classification algorithms were built on domain data extracted from Hi-C data for 2 cell lines $C = \{\textit{GM12878}, \textit{K562}\}$, at four different resolutions $R = \{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$.
-For each classifier, we compared model performances using 3 separate predictor types $P = \{\textit{OC}, \textit{OP}, \textit{Distance}\}$ and 4 class balancing techniques $B = \{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$.
+Multiple random forest classification algorithms [???
+What you mean by multiple?
+Random forest already has multiplicity in it.] were built on domain data extracted from Hi-C data for 2 cell lines $C = \{\textit{GM12878}, \textit{K562}\}$, at four different resolutions $R = \{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$.
+[???
+Bad spacing, for the whole paragraph.
+Why you are not using plain and simple Markdown?] For each classifier, we compared model performances using 3 separate predictor types $P = \{\textit{OC}, \textit{OP}, \textit{Distance}\}$ and 4 class balancing techniques $B = \{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$.
 A system produced from the ensemble framework was defined as: $S = \{\textit{c}, \textit{r}, \textit{p}, \textit{b}\}$, where $c \in C$, $r \in R$, $p \in P$, and $b \in B$.
@@
 
-To assess the full severity of class imbalance present when constructing the models, we investigated the relationship between the total number of bins (sample observations) included at each resolution and the subsequent imbalance ratio (IR).
-As expected, the total number of genomic bins decreased as resolution decreased (Figure 4A).
+To assess the full [???] severity of class imbalance present when constructing the models, we investigated the relationship between the total number of bins (sample observations) included at each resolution [???
+That's mundane, supplemental at best] and the subsequent imbalance ratio (IR).
+[???
+Did you ever defined it?] As expected, the total number of genomic bins decreased as resolution decreased (Figure 4A).
 Specifically, at lower resolutions, the linear genome was binned into larger units, thereby creating fewer bins.

### 2019-04-25 Manuscript/manuscript.Rmd
wip

@@
 
-The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries.
+The distinct patterns of chromatin states, active or repressive histone marks, binding peaks of different factors associated with the 3D structures [@Naumova:2010aa; @Hou:2012aa] prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries.
 Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries.

### 2019-04-28 Manuscript/manuscript.Rmd
manuscript edits

--- 2019-04-24 Manuscript/manuscript.Rmd
@@
 
-Multiple random forest classification algorithms [???
-What you mean by multiple?
-Random forest already has multiplicity in it.] were built on domain data extracted from Hi-C data for 2 cell lines $C = \{\textit{GM12878}, \textit{K562}\}$, at four different resolutions $R = \{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$.
+We compared the performances of random forest classification models implemented on TAD boundaries called using the arrowhead algorithm [@durand2016juicebox] from Hi-C data for 2 cell lines $C = \{\textit{GM12878}, \textit{K562}\}$, at four different resolutions $R = \{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$.
 [???
 Bad spacing, for the whole paragraph.
-Why you are not using plain and simple Markdown?] For each classifier, we compared model performances using 3 separate predictor types $P = \{\textit{OC}, \textit{OP}, \textit{Distance}\}$ and 4 class balancing techniques $B = \{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$.
+Why you are not using plain and simple Markdown?] For each classifier, we considered 3 separate predictor types as the feature space including $P = \{\textit{OC}, \textit{OP}, \textit{Distance}\}$.
+To assess the severity of class imbalance 4 re-sampling techniques were implemented prior to modelling, including $B = \{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$.
 A system produced from the ensemble framework was defined as: $S = \{\textit{c}, \textit{r}, \textit{p}, \textit{b}\}$, where $c \in C$, $r \in R$, $p \in P$, and $b \in B$.
@@
 
-To assess the full [???] severity of class imbalance present when constructing the models, we investigated the relationship between the total number of bins (sample observations) included at each resolution [???
-That's mundane, supplemental at best] and the subsequent imbalance ratio (IR).
-[???
-Did you ever defined it?] As expected, the total number of genomic bins decreased as resolution decreased (Figure 4A).
-Specifically, at lower resolutions, the linear genome was binned into larger units, thereby creating fewer bins.
-however, the IRs remained relatively stable and consistent across resolutions and cell lines (Figure 4B).
-We found that there was an average IR of 0.154 (SD=0.022) and 0.137 (SD=0.0181) across resolutions for the GM12878 and K562 cell lines respectively.
-Here, the low imbalance ratios indicated a wide disparity between the number of genomic bins that overlap with a flanked TAD boundary and the much larger number that did not.
+Results showed that the imbalance ratios were well below acceptable thresholds for both cell lines, and across the 4 resolutions (Supplementary Table 9 ???SDs will come with more chromosomes).
+The low imbalance ratios indicated a wide disparity between the number of genomic bins that overlap with a flanked TAD boundary and the much larger number that did not.
+While resolution certainly played a role in determining the number of observations included in datasets used in downstream modeling, as it determines the width of genomic bins and larger widths (lower resolutions) created less bins, we found that there was very little variation in imbalance ratios across resolution, with ICC=X and Y for GM12878 and K562 respectively (Supplementary Figure 16 ???ICC values will come with more chromosomes).
 
+<!--
 ## HIGH CORRRELATIONS IMPLY COLOCALIZATION OF MANY ANNOTATIONS AROUND TAD BOUNDARIES
@@
 For each model created from the ensemble framework, the alpha and lambda were tuned over a grid of values using 10-fold cross validation (Supplementary Table 7).
+-->
 

### 2019-04-28 Manuscript/Supplementary/supplementary_legends.Rmd
cleaning up legends

@@
 
+<!--
 **Supplementary Figure 2.
@@
 Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
+-->
+
+**Supplementary Table 9.
+Imbalance ratios.** The mean (SD) imbalance ratios across the autosomal chromosomes for each resolution and cell line.
+Imbalance ratios are defined as the ratio of minority classes to majority classes are provided across resolution and cell line.
+The minority class is the set of genomic bins that overlap with flanked TAD boundaries, while the majority class is the set of genomic bins that do not overlap with any flanked TAD boundary.
+
+**Supplementary Figure 16. Imbalance ratios vs resolution.** Scatter plots illustrating the relationship between imbalance ratios and resolutions, for each cell line.
 
@@
 That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
-
-<!--
-**Supplementary Table 5.
-Data Summaries and Imbalance Ratios.** The total number of genomic bins included in the complete, training, and testing sets, as well as the subsequent imbalance ratios across resolutions and cell lines.
-Imbalance ratio is defined as the ratio of genomic bins that overlapped a flanked TAD boundary (minority class), divided by the number of genomic bins that did not overlap a flanked TAD boundary (majority class).
--->
-
-<!--
-**Supplementary Figure 2.
-Correlations between genomic annotations across cell lines and resolutions.** Upper and lower correlation heatmaps between genomic annotations for the GM12878 (A-D) and K562 (E-H) cell lines, across the 10 kb, 25 kb, 50 kb, and 100 kb resolutions (A, B, C, D; and E, F, G, H respectively).
-The correlations were evaluated on the total number of overlapped bases between flanked TAD boundaries and genomic annotations.
-High correlations (red) denote annotations that tended to occur colocally near TAD boundaries.
-Low correlations (blue) denote annotations that did not tend to occur near TAD boundaries together.
-
-**Supplementary Figure 2A. Correlograms separated by genomic annotation category for overlap count predictor types, using 10 kb resolution data, on the GM12878 cell line** 
--->
-
-<!--
-**Supplementary Figrue 12.
-Barplots comparing model performance for each predictor type across 25 kb, 50 kb, and 100 kb data resolutions** Model performances were evaluated using F1-scores, MCCs, and balanced accuracies for each of the 4 resampling techniques, across both the GM12878 (A-C) and K562 (D-F) cell lines.
-Missing bars indicate that the model was unable to correctly predict any genomic regions that overlapped with flanked TAD boundaries in the test data, resulting in zero true positives.
-Bars that appear in the opposite direction (for MCC) indicate a negative correlation between the observed and predicted binary classifications of flanked TAD boundaries.
-
-**Supplementary Figure 13.
-Line plots comparing models using the remaining resampling techniques with distance-type predictors.** Model performances were evaluated using F1-score, MCC, and balanced accuracy for each of the 4 data resolutions, across both the GM12878 (red, solid line) and K562 (blue; dashed line) cell lines.
-For a given metric, each point represents a model applied to a particular resolution with distance type predictors for the feature space, after which a particular resampling technique was used to create balanced classes on the trianing set, including none (A), random over-sampling (B), and random under-sampling (C).
-
-**Supplementary Figure 14A.
-Variable importance of the top 20 most predictive genomic annotations for models using no resampling technique with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
-Variable importance is assigned on a continuous scale (range: 0-100).
-Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model.
-The genomic annotations are sorted by highest level of importance obtained from a random forest model with distance-type predictors at the 10 kb data resolution, while not performing a class balancing technique, for each cell line respectively.
-
-**Supplementary Figure 14B.
-Variable importance of the top 20 most predictive genomic annotations for models using random over-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
-Variable importance is assigned on a continuous scale (range: 0-100).
-Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model.
-The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using random over-sampling to create balanced classes, for each cell line respectively.
-
-**Supplementary Figure 14C.
-Variable importance of the top 20 most predictive genomic annotations for models using random under-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
-Variable importance is assigned on a continuous scale (range: 0-100).
-Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model.
-The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using random under-sampling to create balanced classes, for each cell line respectively.
--->
-
-<!--
-**Supplementary Figures 9-23.
-Precision-Recall curves for 25 kb, 50kb, and 100kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on 25 kb, 50kb, and 100kb resolution data, across each resampling technique.
-GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red).
--->
-
-<!--
-**Supplementary Table 2.
-Area under Precision-Recall Curves.** Comparison of models applied to different data resolutions, resampling techniques, and predictor types for each of the two cell lines in terms of AUPRC.
-The column labeled "All" denotes models with all 3 combined predictor types.
--->
-
-<!--
-**Figure 3.
-Recursive Feature Elimination for 25 kb, 50 kb, and 100 kb data** Beginning with the full set of distance type predictors for each cell line, models built on 25 kb, 50 kb, and 100 kb resolution data were recursively evaluated at different subsets of feature size.
-For convenience and computational efficiency, feature size decreasing in powers of 2 was considered.
-The maximum size for feature subsets differed between cell line due the available annotations that were considered and provided in Supplementary Table 1.
-Near optimal performance was achieved using the top 32 distance type predictors for both the GM12878 (red) and K562 cell lines (blue).
--->

### 2019-05-04 Manuscript/manuscript.Rmd
manuscript edits

@@
 To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution for the corresponding contact matrix (Figure 1).
-For example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
+As an example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
 For the boundary data, in order to accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
-For example, for 10 kb resolution data, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
+That is, for 10 kb resolution data, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
 A genomic bin was then labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
 Otherwise, the bin was labeled as not containing a boundary (Y=0).
-The process was repeat for each subsequent resolution.
-
-## ENSEMBLE FRAMEWORK
-
-An ensemble of models was established for the purposes of systematically comparing the performances of different parameters in the framework (Figure 2).
-Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type for the feature space.
-
-The data sets used for modeling were composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
-These two classes made up the minority and majority sets respectively.
-The data was then split into a 7:3 ratio of training to testing sets.
-Each training and testing set was composed of a similar majority to minority class ratio as the full data set.
-For the task of performance evaluation and prediction, the test set remained constant for all ensemble systems to account for an unbiased comparison.
+The process was repeated for each subsequent resolution.
 
@@
 
-In order to assess the influence of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling), composed of data from each predictor type.
-Each re-sampling technique is described in detail below.
+In order to assess the influence of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling), composed of the genomic bin class and data from each predictor type.
+The re-sampling techniques considered are described in detail below.
 
@@
 For each elastic-net regularization, 10-fold cross-validation was used to tune the parameters that controlled the penalty terms.
+The parameters that maximized the mean AUPRC across each cross-fold was chosen.
 All elastic-net algorithms were implemented in R using the `caret` package version 6.0 [@kuhn2012caret].
@@
 
-Once the appropriate predictor type and set of features were determined, a final set of random forest classification models were performed to fully compare re-sampling techniques.
-To reduce bias due to random dataset generation, 10-fold cross validation was used <!--to tune the number of features to consider at each node and the number of ensemble trees to aggregate-->.
+Once the appropriate predictor type and set of features were determined, a final set of random forest classification models were performed to compare model performances between re-sampling techniques and predictor types.
+<!--To reduce bias due to random dataset generation, 10-fold cross validation was used to tune the number of features to consider at each node and the number of ensemble trees to aggregate-->.
 The default number of features to consider at each node of the random forest algorithm was set as the square root of the number of features in the model.
@@
 All random forest algorithms were implemented in R using the `caret` package version 6.0 [@kuhn2012caret].
-Once the model was implemented, it was assessed using the test set, and performance metrics were recorded.
+Once the model was implemented, it was validated on the test set.
 
-The efficacy of each ensemble system in the framework was compared using composite metrics including F1-score and MCC. These metrics are defined as follows:
+The performance of each ensemble system in the framework was compared using the composite metric, Matthew's Correlation Coefficient. The MCC is defined as follows:
 
+<!--
 $$F1 - Score = \frac{2TP}{2TP + FP + FN}$$
+-->
 
@@
 -->
+
+## ENSEMBLE FRAMEWORK
+
+An ensemble of models was established for the purposes of systematically comparing the performances of different parameters in the framework (Figure 2).
+Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type for the feature space.
+
+The data sets used for modeling were composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
+These two classes made up the minority and majority sets respectively.
+The data was then split into a 7:3 ratio of training to testing sets.
+Each training and testing set was composed of a similar majority to minority class ratio as the full data set.
+For the task of performance evaluation and prediction, the test set remained constant for all ensemble systems to account for an unbiased comparison.
 
@@
 
-## CLASS IMBALANCE SEVERELY IMPACTS PERFORMANCE AMONG ALL CLASSES OF MODELS
+## CLASS IMBALANCE SEVERELY IMPACTS MODEL PERFORMANCE
 
@@
 
-## DATA RE-SAMPLING COUPLED WITH THE INCLUSION OF A DISTANCE-TYPE FEATURE SPACE IMPROVED PERFORMANCES AMONG ALL CLASSES OF MODELS
+## DATA RE-SAMPLING COUPLED WITH THE INCLUSION OF A DISTANCE-TYPE FEATURE SPACE SUBSTANTIALLY IMPROVED MODEL PERFORMANCE
 

### 2019-05-04 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-An ensemble of models was established for the purposes of systematically comparing the performances of different parameters in the framework (Figure 2).
+An ensemble framework was established for the purposes of systematically creating a variety of models that each included different sets of parameters described above (Figure 2).
 Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type for the feature space.
-
 The data sets used for modeling were composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
@@
 For the task of performance evaluation and prediction, the test set remained constant for all ensemble systems to account for an unbiased comparison.
+Furthermore, this process was repeated, and performances were aggregated across each autosomal chromosome.
+Model results for Chromosome 9 was omitted from the analysis, for both cell lines, due to the sparcity of the contact matrix at the 10 kb resolution for the K562 cell line.
 
@@
 
-We compared the performances of random forest classification models implemented on TAD boundaries called using the arrowhead algorithm [@durand2016juicebox] from Hi-C data for 2 cell lines $C = \{\textit{GM12878}, \textit{K562}\}$, at four different resolutions $R = \{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$.
+We compared the performances of random forest classification models implemented on TAD boundaries called using the arrowhead algorithm [@durand2016juicebox] from Hi-C data for 2 cell lines $L = \{\textit{GM12878}, \textit{K562}\}$, at four different resolutions $R = \{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$.
 [???
@@
 To assess the severity of class imbalance 4 re-sampling techniques were implemented prior to modelling, including $B = \{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$.
-A system produced from the ensemble framework was defined as: $S = \{\textit{c}, \textit{r}, \textit{p}, \textit{b}\}$, where $c \in C$, $r \in R$, $p \in P$, and $b \in B$.
-Letting $|X|$ denote the cardinality of each set, we evaluated $|C| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $96 (= 2 \times 4 \times 3 \times 4)$ separate models.
+Each combination of the above parameters was repeated 21 times (number of autosomal chromosomes, excluding chromosome 9), $C = \{ 1, 2, ..., 22 \}$.
+A system produced from the ensemble framework was defined as: $S = \{\textit{c}, \textit{r}, \textit{p}, \textit{b}\}$, where $l \in L$, $r \in R$, $p \in P$, $b \in B$, and $c \in C$.
+Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2016 (= 2 \times 4 \times 3 \times 4 \times 21)$ separate models.
 

### 2019-05-05 Manuscript/manuscript.Rmd
editted manuscript

@@
 Analyses have shown that the genome is folded into distinct compartments termed topologically associating domains (TADs) [@dixon2012topological].
-Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD [@symmons2014functional].
 Approximately 60-80% of TADs remain stable across cell types [@Schmitt:2016aa], suggesting that the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
-Furthermore, studies have shown that changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @flavahan2016insulator].
+Furthermore, studies have shown that changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @flavahan2016insulator; @song2017ctcf].
 Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.
@@
 The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries.
+Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD [@symmons2014functional].
+Likewise, emerging research has shown that particular binding sites are enriched at TAD boundaries.
+It has been established that the zinc finger protein, CTCF, is associated with TAD boundaries and is an architectural protein responsible for the organization of the genome within the nucleus [@ghirlando2016ctcf; @ong2014ctcf].
+CTCF along with other transcription factors, including SMC1, SMC3, and RAD21 have been shown to colocalize together near TAD boundaries, leading to the recruitment of a cohesin ring [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+Together, these components are hypothesized to be what causes loops in the DNA, contributing to higher order chromatin organization.
+Other binding proteins have been shown to mediate enhancer-promoter interactions, including the transcription factors YY1 and ZNF143, thereby influencing the delineation of topological domains [@weintraub2017yy1; @gonzalez2017znf143; @heidari2014genome].
+Even more so, loci within a domain have been shown to interact more frequently with one another, exhibiting similar patterns of chromatin modifications, and long-range contact patterns [rao20143d].
+However, the growing number of annotated genomic features and the methods used to identify the ones assocaited with TAD boundaries still leaves much to be desired.
+
 Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries.
-Although several useful insights have been made, such as the convergent binding of CTCF [@ong2014ctcf; @ghirlando2016ctcf], [???
-Describe other hallmarks of TAD boundaries, with references.
-And, most importantly, why you are doing your study?]
+In doing so, many methods ignore key characteristics of domain data, such as the impact of heavily imbalanced number of boundaries vs.
+nonboundary regions.
+This is because, when constructing the data for modeling, a common methodology used to determine the class of the response variable is to bin the linear genome and then create a method used to determine if each bin "includes" a TAD boundary or not.
+Given the sparcity of TADs throughout the genome though, this will inevitably lead to severly imbalanced classes.
 
-many methods ignore key characteristics of domain data, such as the impact of heavily imbalanced number of boundaries vs.
-other regions.
-In a classification setting, when one is attempting to discriminate between regions with and without TAD boundaries, the class imbalance issue will contribute to small imbalance ratios (defined as the ratio of minority to majority classes[@Orriols-Puig2008]).
-Such heavily imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class;@chen2013influence;@jeni2013facing].
+In a classification setting, when one is attempting to discriminate between regions with (minority class) and without (majority class) TAD boundaries, the class imbalance issue will contribute to small imbalance ratios.
+The imbalance ratio is defined as the ratio of minority to majority classes [@Orriols-Puig2008].
+Such heavily imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class; @chen2013influence; @jeni2013facing].
 Consequently, careful consideration must be taken when deciding which performance metric(s) to use for evaluation of predictive models, especially in the case of imbalanced data.
@@
 While not directly affecting the value of the AUROC, this can have severe consequences on the interpretability of the model's performance.
-<!--A better threshold-free measure to use when dealing with imbalanced data is the area under the precision-recall curve (AUPRC).
+A better threshold-free measure to use when dealing with imbalanced data is the area under the precision-recall curve (AUPRC).
 The interpretation of the AUPRC of a model is similar to that of the AUROC.
 However, where as the baseline model performance according to the AUROC is given by 0.50, the baseline model performance according to the AUPRC is given by the ratio of true positives over the total number of cases.
-This enables a more realistic benchmark to evaluate a model on as this ratio will be lower than 0.5 for a test data set with imbalanced classes.--> Likewise, threshold-specific metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
-Better measures to consider are composite metrics involving both precision and recall together because they soften the influence of a model's ability to correctly classify majority classes and yield more dependable and interpretable results.
+This enables a more realistic benchmark to evaluate a model on as this ratio will be lower than 0.5 for a test data set with imbalanced classes.
+Likewise, threshold-specific metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
+A better measure to consider is a composite metric involving all quadrants of the confusion matirix, such as Matthew's Correlation Coefficient (MCC) [@jeni2013facing; @chicco2017ten].
+The MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
+A value of positive 1 represents a perfect prediction, while a value of negative 1 represents total disagreement between prediction and observation.
+A value of 0 indicates no better than random prediction.
+
+<!--
+precision and recall together because they soften the influence of a model's ability to correctly classify majority classes and yield more dependable and interpretable results.
 Therefore, measures like the F1-Score and Matthew's Correlation Coefficient (MCC) offer better interpretation, especially in the instance of imbalanced classes [@jeni2013facing].
@@
 Each metric uses all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
+-->
 
@@
 REFS].
-The most prominent example being the enhancer-promoter relationships, where enhancers are frequently located hundreds or thousands of bases away from their target promoters [???
-REFS].
+The most prominent example being the enhancer-promoter relationships, where enhancers are frequently located hundreds or thousands of bases away from their target promoters [@whalen2016enhancer].
 The use of distances between TAD boundaries and genomic annotations has largely been ignored.
@@
 ### DATA RE-SAMPLING
+
+Class imbalance was characterized by each dataset's imalance ratio, defined as the ratio of minority to majority classes given by the genomic bins.
+Minority classes were the set of genomic bins that overlapped with flanked TAD boundaries, while majority classes were the set of genomic bins that did not overlap with a flanked TAD boundary.
 
@@
 The low imbalance ratios indicated a wide disparity between the number of genomic bins that overlap with a flanked TAD boundary and the much larger number that did not.
-While resolution certainly played a role in determining the number of observations included in datasets used in downstream modeling, as it determines the width of genomic bins and larger widths (lower resolutions) created less bins, we found that there was very little variation in imbalance ratios across resolution, with ICC=X and Y for GM12878 and K562 respectively (Supplementary Figure 16 ???ICC values will come with more chromosomes).
+While resolution certainly played a role in determining the number of observations included in datasets used in downstream modeling, as it determines the width of genomic bins and larger widths (lower resolutions) created less bins, we found that there was very little variation in imbalance ratios across resolution (Supplementary Figure 16 ???variation will come with additional chrs).
 
@@
 In order to set a baseline in performance, we first evaluated the least granular model, that is one implemented using OC predictor types, without data re-sampling.
-In evaluating such composite metrics like F1-Score and MCC, we found that for the GM12878 cell line, these models exhibited poor performances across all resolutions (Figure 5A).
-<!--The average F1-Score and MCC across resolution was found to be 0.04 and 0.07 respectively.-->
-
-We then gradually increased the granularity in the characteristics of the model by assess the model built on OP predictor types, while still not performing any data resampling.
-Here we found that performances were worse than when using OC predictor types for the GM12878 cell line (Figure 5B).
-<!--Here, the average F1-Score and MCC was found to be 0.01 and 0.03 respectively.--> Finally, models built on distance-type predictors in conjuction with no resampling, however, were found to exhibit slightly better performances than the other two types<!--, with average F1-Scores and MCCs of 0.08 and 0.10 respectively--> (Figure 5C).
-
-Importantly, when validating these 3 models built on fully imbalanced datasets, the F1-Score and MCC could not be determined at lower resolutions given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives.
+We found that models built data with fully imbalanced classes exhibited poor MCC across all resolutions (Figure 5A).
+We then gradually increased the granularity by assessing models built on OP predictor types, while still not performing any data resampling.
+Interestingly, we found that MCCs were worse than when using OC predictor types for the GM12878 cell line (Figure 5B).
+When including distance-type predictors, models were found to exhibit slightly better MCCs than the other two types (Figure 5C).
+Importantly, when validating these 3 models built on fully imbalanced datasets, the MCC could not be determined at lower resolutions given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives.
 Furthermore, we found that evaluating models using conventional metrics, such as AUC or accuracy, did not depict the true severity in performance (Supplementary Table 3).
-<!--The average AUC across resolutions for the OC, OP, and distance type predictors was 0.65, 0.66, and 0.85 respectively, where as the average accuracies were 0.89, 0.89, and 0.90 respectively (Supplementary Table 3).--> Results were found to be consistently poor across resolutions for the K562 cell line (Supplementary Figure 10).
+Results were found to be consistently poor across resolutions for the K562 cell line (Supplementary Figure 10).
 Similarly, many of the performance metrics at higher resolutions were also unable to be reported due to the models inability to produce any true positive cases.
@@
 
-Comparisons of the effects of the various resampling techniques were then made.
-When models were built on randomly oversampled (ROS) data, we found a substantial increase in F1-Score and MCC for the GM12878 cell line (Figure 5).
-The biggest improvement in performance was seen at the 10 kb resolution, with a downward trend as resolutions decreased.
-Although performances were low at lower resolutions, both F1-Scores and MCC values were able to be obtained, contrary to models built on completely unbalanced data as seen before.
-Distance-type predictors were found to offer the highest F1-Scores and MCCs for ROS data, across all resolutions.
+When models were built on randomly oversampled (ROS) data, we found a substantial increase in MCC for the GM12878 cell line (Figure 5 A-C).
+The biggest improvement in performance was seen at the 10 kb resolution in each of the 3 predictor types, with a downward trend as resolutions decreased.
+Although performances were low at lower resolutions, MCC values were able to be obtained, contrary to models built on completely unbalanced data as seen before.
+Distance-type predictors were found to offer the highest MCCs for ROS data, across all resolutions.
 Similar results were obtained when applying ROS to the K562 cell line (Supplementary Figure 10).
-Here, a much sharper negative trend was featured for both F1-Score and MCC and resolution decreased, than in the GM12878 cell line.
+Here, a much sharper negative trend was featured for MCCs as resolution decreased, than in the GM12878 cell line.
 
 Further improvement in performance was found when models were implemented on both randomly undersampled (RUS) and SMOTE resampled data, for all 3 predictor types (Figure 5).
-Although the differences in performance between the two techniques were marginal, SMOTE resampled data was found to yield the best F1-Scores and MCCs among all classes of models developed and compared in the ensemble framework.
-As with ROS, distance type predictors yeilded the highest F1-Score and MCC values across resolutions, when applied to either RUS or SMOTE.
+Although the differences in performance between the two techniques were marginal, SMOTE resampled data was found to yield the best MCCs among all classes of models developed and compared in the ensemble framework.
+As with ROS, distance type predictors yielded the highest MCC values across resolutions, when applied to either RUS or SMOTE.
 SMOTE re-sampled data, with the inclusion of distance-type predictors was also found to be the best set of characteristics when applied to the K562 cell line (Supplementary Figure 10).
-
 Moreover, we found that there was a degredation in model performance as data resolution decreased.
@@
 On the GM12878 cell line, there were only marginal differences in performance between 10 kb and 25 kb, followed by a steep decline at 50 kb.
-Then, both F1-Scores and MCCs showed a momentary increase in performance at 100 kb, the lowest resolution considered in the study.
+Then, the MCCs showed a momentary increase in performance at 100 kb, the lowest resolution considered in the study.
 Performances from the K562 cell line degraded much faster as resolution decreased, starting with highest performance at 10 kb and ending with the worst performance at 100 kb.
+These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on distance-type predictors and incorporates both random under- and over-sampling.
 
-These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that incorporates both random under- and over-sampling, as SMOTE is known to do.
+<!--
 Additionally, when we performed and evaluated the variable importances of random forest models built on one genomic annotation at a time (including the 3 predictor types each), we found that the distance-type consistently out-ranked the OC and OP type predictors in terms of predictive importance, for a majority of the cell line specific annotations, across resolution and cell line (Supplementary Tables 4 & 5).
 Therefore, it appears that distance-type predictors provided the most informative spatial representation of epigenomic annotations associated with TAD boundaries.
+-->
 
-## VARIABLE IMPORTANCES FROM TOP PERFORMING MODELS CONFIRMED BIOLOGICAL FUNCTIONALITY OF KNOWN TRANSCRIPTION FACTOR BINDING SITES
+## MODELS IMPLEMENTED ON TRANSCRIPTION FACTOR BINDING SITES, USING OPTIMAL PARAMETERS, OUTPERFORM OTHER ANNOTATION-SPECIFIC MODELS
 
-In addition to adressing both the affect of class imbalance and the optimal spatial relationships used when predicting TAD boundaries, we also aimed at identifying the genomic annotations that were most predictive of TAD boundary formation.
-In doing so, we investigated which genomic annotations yielded the hight predictive importance values for random forest models implemented on the best given set of data-level characteristics determined above (SMOTE re-sampled with distance type predictors), across resolution and cell line.
+In order to assess the predictive capabilities of specific types of annotations, we further compared the performances of annotation-specific models.
+Using the optimal set of parameters, SMOTE re-sampling with distance-type predictors, random forest classifiers built on sets of histone modifications, chromatin state segmentations, and TFBS were compared to a model that included all three types together.
+For the GM12878 cell line, models built simply on TFBS were found to perform consistently just as well as models that included all 3 sets of annotations, across resolution (Figure 6).
+Similar results were found when evaluating the K562 cell line (supplementary Figure 11).
+For both resolutions, models built on only histone modifications were found to have the MCC, across resolutions, followed by models built on chromatin state segmentations.
+This suggests that TAD boundary formation is primarily carried out by transcription factor binding sites.
+
+## PREDICTIVE IMPORTANCES CONFIRMED BIOLOGICAL FUNCTIONALITY OF KNOWN TRANSCRIPTION FACTOR BINDING SITES
+
+As an external method of validation, we also investigated the predictive importance of the annotations that our top performing models were built on.
 We found that specific transcription factor binding sites (TFBS), including SMC3ab, ZNF143, CTCF, and RAD21, were given consistently high predictive importance in the models built on the GM12878 cell line, across all resolutions (Figure 8).
-These are known factors associated with the hypothesized loop extrusion model [@fudenberg2016formation; @alipour2012self] and were found to yield consistently high predictive importance on the K562 cell line as well, with similar profiles across resolutions (Supplementary Figure 15).
-Other annotations known to be associated with gene regulation and affect structural properties of chromatin, such as the YY1  transcription factor, as well DNAse hypersensitive sites, regions of heterochromatin, and the H3k27 trimethylation histone modifications were ranked high on the 10 kb resolution, but were less consistently ranked at lower resolutions for both cell lines.
-<!--Moreover, the ranking profiles of genomic annotations for both cell lines were found to be more similar between the 10 kb and 25 kb resolutions, as well as between the 50 kb and 100 kb resoluions (this is proved when looking at a clustered heatmap).-->
-
-## MODELS IMPLEMENTED ON TRANSCRIPTION FACTOR BINDING SITES OUTPERFORM OTHER ANNOTATION-SPECIFIC MODELS
-
-Given the prevalence of TFBS as the most consistently top ranked predictive features across resolution and cell line, we ventured to further compare performances of annotation specific models.
-After applying SMOTE re-sampling with distance type predictors, random forest models built on sets of histone modifications, chromatin state segmentations, and TFBS were compared to a model that included all three types together.
-For the GM12878 cell line, models built simply on TFBS were found to perform just as well as models that included all 3 sets of annotations according to F1-Score and MCC, consistently across resolution (Figure 6).
-Similar results were found when evaluating the K562 cell line (supplementary Figure 11).
-For both resolutions, models built on only histone modifications were found to have the lowest F1-Scores and MCC, across resolutions, followed by models built on chromatin state segmentations.
+These are known factors associated with the hypothesized loop extrusion model [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self] and were found to yield consistently high predictive importance on the K562 cell line as well, with similar profiles across resolutions (Supplementary Figure 15).
 
@@
 
-<!-- IN PROGRESS
 # DISCUSSION
 
-We developed an ensemble framework to systematically compare model performances for different combinations of class balancing and feature engineering techniques aimed aimed at determining a consensus approach to predicting TAD boundary formation using genomic annotations
+A typical problem facing machine learning approaches toward predicting TAD boundary formation is the introduction of highly imbalanced classes.
+This is because, when constructing the data for modeling, a common methodology used to determine the class of the response variable is to bin the linear genome and then create a method used to determine if each bin "includes" a TAD boundary or not.
+Given the sparcity of TADs throughout the genome though, this will inevitably lead to severly imbalanced classes.
+A workaround to this employed by [@huang2015predicting; @hong2017computational; @bednarz2014supervised] was to randomly sample from the majority class to create balanced classes in the training set.
+It is unclear how these studies handled
 
-Although we were not able to draw direct comparisons between the GM12878 and K562 cell lines, given that they did not contain the same list of cell type specific annotations, we did find that there was relative agreement in rankings of the top 5-7 predictors.
+We developed an ensemble framework to systematically compare model performances for different combinations of re-sampling and feature engineering techniques aimed at determining a consensus approach to predicting TAD boundary formation using genomic annotations.
+Additionally, this study provides direct comparisons of 4 different Hi-C data resolutions, and their effects on performances of downstream models.
+Furthermore, we go on to show the importance of using adequate metric when assessing model performance, especially in the case of highly imbalanced classes.
+
+When constructing the data for modeling, a common methodology used to determine the response variable is to bin the linear genome into equally sized intervals and then create a method used to determine if each bin "includes" a TAD boundary or not.
+Given the sparcity of TADs throughout the genome, this will inevitably lead to severly imbalanced classes.
+
+Although we were not able to draw direct comparisons between the GM12878 and K562 cell lines, given that they did not contain the same list of cell type specific annotations, we did find that there was relative agreement in rankings of the top predictive predictors.
 However, there were notable exclusions from each cell line, in addition to inconsistencies across resolutions
@@
 Likewise, this reduction was most efficient at more refined levels of data resolution.
--->
 

### 2019-05-05 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-**Background.** Chromosome conformation capture sequencing technologies have shown that the three-dimensional (3D) structure of the genome is folded into distinct compartments, known as topologically associated domains (TADs) - units of coordinated gene expression.
-The location of TAD boundaries is highly conserved, suggesting the presence of epigenomic marks aiding in TAD formation.
-[The ability to predict which epigenomic features are most associated with the TAD boundaries will allow for better understanding the regulatory role of the 3D structure of the genome.
-- ???
-Weak]
+**Background.** Chromosome conformation capture sequencing technologies have shown that the three-dimensional (3D) structure of the genome is folded into distinct compartments, known as topologically associated domains (TADs) -- units of coordinated gene expression.
+The location of TAD boundaries has been shown to be highly conserved.
+Additionally, the distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify the epigenomic features that are most predictive of TAD boundaries.
 
-Existing methods for predicting associations between genomic annotations tend to ignore key characteristics of genomic data.
-Specifically, when constructing the model for classification, the number of genomic regions surrounding TAD boundaries is much less than the number of other regions.
-This leads to heavily imbalanced classes and can result in poor performances as a model's ability to assign a new sample to a given class is influenced by the prevalence of that class in the training set.
-Furthermore, most methods utilize direct overlap as a means to quantify this association, while distance, the measure of spatial relationships, remains unaccounted for.
+Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries.
+However, many methods ignore key characteristics of domain data, such as the impact of heavily imbalanced classes of boundary vs.
+non-boundary regions and the use of distances ($log_{2}$ transformed) as the best representation of the association between TAD boundaries and genomic annotations.
 
-**Methods.** We proposed a novel ensemble framework that systematically addresses those data irregularities and characteristics.
-Multiple random forest classification models, in combination with variations in cell line, data resolution, feature engineering, and re-sampling techniques were performed and compared.
-A number of performance metrics were assessed, including [???
-will update when ready].
+**Methods.** Using replicate Hi-C data for the GM12878 and K562 cell lines, we proposed a novel ensemble framework that addresses these data irregularities and characteristics.
+Multiple random forest classification models built on regularized sets of genomic annotations, in combination with variations in data resolution, feature engineering, and re-sampling techniques.
+The composite metric Matthew's Correlation Coefficient (MCC) was used to compare models derived from the framework to determine a consensus approach to predicting TAD boundary formation.
 
-**Results.**
+**Results.** We discovered that models built on SMOTE re-sampled data out performed models built simply on  random under- and over-sampled data.
+Additionally, our results indicated that $log_{2}$ distances between annotations and TAD boundaries were more informative than other predictor-types used to build models.
+Furthermore, we found that performances tended to degrade as data resolution decreased.
+Lastly, the most predictive annotations in the best performing models included known architectural proteins such as CTCF, SMC3, RAD21, and ZNF143, as well as lesser known transcription factors including P300 and NFKB.
 
-**Conclusions.**
+**Conclusions.** The experiments derived from our ensemble framework provide a useful guide toward the exploration of chromatin organization, while highlighting the impact of both class imbalance and feature engineering in TAD boundary prediction.
 
@@
 
-In this study, we have developed an ensemble framework for predicting TAD boundaries in order to systematically compare many data driven solutions used to address the issues presented above.
+Therefore, in this study, we aimed to developed an ensemble framework used to build random forest classifiers composed of different combinations of data driven parameters used to address the issues presented above.
+We used our framework to systematically compare model performances using a composite performance metric, MCC.
+Our goal was to determine a suitable combination of data re-sampling and feature engineering techniques that both corrected the inherent imbalanced classes and provided the best spatial representation linking genomic annotations to TAD boundaries.
+Additionally, we used our framework to directly compare the influence of Hi-C contact matrix resolution on model performances.
 We evaluated Hi-C data for both the GM12878 and K562 cell line obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolution.
@@
 Noninformative features were removed using a feature reduction algorithm and random forest classifications were performed to assess model performance, and investigate which genomic annotations were most associated with the TAD boundaries for a given system from the complete ensemble.
-Model performance was evaluated using AUROC, AUPRC, F1-Score, and MCC.
 
@@
 
+We developed an ensemble framework to systematically compare model performances for different combinations of re-sampling and feature engineering techniques aimed at determining a consensus approach to predicting TAD boundary formation using genomic annotations.
+Additionally, this study provides direct comparisons of 4 different Hi-C data resolutions, and their effects on performances of downstream models.
+Furthermore, we go on to show the importance of using adequate metric when assessing model performance, especially in the case of highly imbalanced classes.
+
 A typical problem facing machine learning approaches toward predicting TAD boundary formation is the introduction of highly imbalanced classes.
@@
 It is unclear how these studies handled
-
-We developed an ensemble framework to systematically compare model performances for different combinations of re-sampling and feature engineering techniques aimed at determining a consensus approach to predicting TAD boundary formation using genomic annotations.
-Additionally, this study provides direct comparisons of 4 different Hi-C data resolutions, and their effects on performances of downstream models.
-Furthermore, we go on to show the importance of using adequate metric when assessing model performance, especially in the case of highly imbalanced classes.
 

### 2019-05-05 Manuscript/manuscript.Rmd
editted abstract

@@
 
-**Background.** Chromosome conformation capture sequencing technologies have shown that the three-dimensional (3D) structure of the genome is folded into distinct compartments, known as topologically associated domains (TADs) -- units of coordinated gene expression.
-The location of TAD boundaries has been shown to be highly conserved.
+**Background.** Chromosome conformation capture sequencing technologies have shown that the three-dimensional (3D) structure of the genome is folded into distinct compartments, known as topologically associated domains (TADs).
+The locations of TAD boundaries have been shown to be highly conserved.
 Additionally, the distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify the epigenomic features that are most predictive of TAD boundaries.
 
-Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries.
-However, many methods ignore key characteristics of domain data, such as the impact of heavily imbalanced classes of boundary vs.
+Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions on the linear genome that include TAD boundaries.
+However, many methods ignore key characteristics of domain data, such as the impact of heavily imbalanced classes distinguished by boundary vs.
 non-boundary regions and the use of distances ($log_{2}$ transformed) as the best representation of the association between TAD boundaries and genomic annotations.
@@
 **Methods.** Using replicate Hi-C data for the GM12878 and K562 cell lines, we proposed a novel ensemble framework that addresses these data irregularities and characteristics.
-Multiple random forest classification models built on regularized sets of genomic annotations, in combination with variations in data resolution, feature engineering, and re-sampling techniques.
-The composite metric Matthew's Correlation Coefficient (MCC) was used to compare models derived from the framework to determine a consensus approach to predicting TAD boundary formation.
+Multiple random forest classification models built on regularized sets of genomic annotations obtained from the UCSC genome browser database, in combination with variations in data resolution, feature engineering, and re-sampling techniques.
+The composite metric Matthew's Correlation Coefficient (MCC) was used to compare models derived from the framework to determine a consensus approach toward predicting TAD boundary formation.
 
-**Results.** We discovered that models built on SMOTE re-sampled data out performed models built simply on  random under- and over-sampled data.
-Additionally, our results indicated that $log_{2}$ distances between annotations and TAD boundaries were more informative than other predictor-types used to build models.
-Furthermore, we found that performances tended to degrade as data resolution decreased.
+**Results.** We discovered that models built on SMOTE (Synthetic Minority Over-sampling TEchnique) re-sampled data out performed models built simply on random under- and over-sampled data.
+Additionally, our results indicated that log2 distances between annotations and TAD boundaries were more informative than other predictor-types used to build models.
+Importantly, we also found that performances tended to degrade as data resolution decreased.
 Lastly, the most predictive annotations in the best performing models included known architectural proteins such as CTCF, SMC3, RAD21, and ZNF143, as well as lesser known transcription factors including P300 and NFKB.
@@
 Analyses have shown that the genome is folded into distinct compartments termed topologically associating domains (TADs) [@dixon2012topological].
-Approximately 60-80% of TADs remain stable across cell types [@Schmitt:2016aa], suggesting that the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
-Furthermore, studies have shown that changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @flavahan2016insulator; @song2017ctcf].
+Approximately 60-80% of TADs remain stable across cell types [@Schmitt2016aa], suggesting that the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
+Furthermore, studies have shown that changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @Flavahan2016; @song2017ctcf].
 Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.

### 2019-05-05 Manuscript/manuscript.Rmd
manuscript edits

@@
 Other binding proteins have been shown to mediate enhancer-promoter interactions, including the transcription factors YY1 and ZNF143, thereby influencing the delineation of topological domains [@weintraub2017yy1; @gonzalez2017znf143; @heidari2014genome].
-Even more so, loci within a domain have been shown to interact more frequently with one another, exhibiting similar patterns of chromatin modifications, and long-range contact patterns [rao20143d].
+Even more so, loci within a domain have been shown to interact more frequently with one another, exhibiting similar patterns of chromatin modifications, and long-range contact patterns [@rao20143d].
 However, the growing number of annotated genomic features and the methods used to identify the ones assocaited with TAD boundaries still leaves much to be desired.
 
-Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries.
+Current methods used to predict TAD boundaries rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries.
 In doing so, many methods ignore key characteristics of domain data, such as the impact of heavily imbalanced number of boundaries vs.
@@
 
-In addition to employing suitable metrics for evaluating models validated on imbalanced data, there also exist several algorithmic or data level solutions.
+In addition to employing suitable metrics for evaluating models validated on imbalanced data, there also exists several algorithmic or data level solutions.
 Algorithmic level solutions involve modifyng existing classifiers in order to curtail the bias induced by imbalanced classes [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical].
-Data level solutions, on the other hand, mostly constitute as resampling techniques, in which random sampling is used to either replicate or remove data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
+Data level solutions, on the other hand, mostly constitute as re-sampling techniques, in which random sampling is used to either replicate or remove data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
 It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
@@
 
-Another underexplored aspect of modeling the association between TAD boundaries and genomic annotations is the various types of relationships between them.
+Another underexplored aspect of modeling the association between TAD boundaries and genomic annotations is determining a suitable representation of the relationship between them.
 Typical approaches include overlap counts or percents [@mourad2016computational; @hong2017computational; @huang2015predicting].
 Counts refer to the number of times a genomic annotation directly overlaps with a TAD boundary region, e.g., a TAD boundary may overlap with several ChIP-seq peaks for a given transcription factor.
-Percents refers to the percent of overlap of a genomic annotation with a TAD boundary region, e.
-g., a 60% of a TAD boundary may overlap genomic region annotated as heterochromatin.
+Percents refers to the percent of overlap between a genomic annotation and a TAD boundary region, e.
+g., 60% of a TAD boundary region may overlap with a genomic region annotated as heterochromatin.
 
@@
 The most prominent example being the enhancer-promoter relationships, where enhancers are frequently located hundreds or thousands of bases away from their target promoters [@whalen2016enhancer].
-The use of distances between TAD boundaries and genomic annotations has largely been ignored.
+On the other hand, the use of distances between TAD boundaries and genomic annotations has largely been ignored.
 However, these distance features have the potential to offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
@@
 
-Therefore, in this study, we aimed to developed an ensemble framework used to build random forest classifiers composed of different combinations of data driven parameters used to address the issues presented above.
+Therefore, in this study, we aimed to develop an ensemble framework used to build random forest classifiers composed of different combinations of data driven parameters used to address the issues presented above.
 We used our framework to systematically compare model performances using a composite performance metric, MCC.
@@
 We then tested four different re-sampling techniques aimed at creating balanced classes.
-Noninformative features were removed using a feature reduction algorithm and random forest classifications were performed to assess model performance, and investigate which genomic annotations were most associated with the TAD boundaries for a given system from the complete ensemble.
+Noninformative features were removed using a feature reduction algorithm and random forest classifications were built to assess model performance, and investigate which genomic annotations were most predictive of TAD boundaries for a given system from the complete ensemble.
 
@@
 The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained.
+TAD boundaries called on Chromosome 9 were omitted from all downstream analysis, for both cell lines, due to the sparcity of the contact matrix at the 10 kb resolution for the K562 cell line.
 
@@
 
-Once the appropriate predictor type and set of features were determined, a final set of random forest classification models were performed to compare model performances between re-sampling techniques and predictor types.
-<!--To reduce bias due to random dataset generation, 10-fold cross validation was used to tune the number of features to consider at each node and the number of ensemble trees to aggregate-->.
-The default number of features to consider at each node of the random forest algorithm was set as the square root of the number of features in the model.
+Once the appropriate predictor type and set of features were determined, a final set of random forest classification models were built to compare model performances between re-sampling techniques and predictor types.
+<!--To reduce bias due to random dataset generation, 10-fold cross validation was used to tune the number of features to consider at each node and the number of ensemble trees to aggregate.--> The default number of features to consider at each node of the random forest algorithm was set as $\sqrt{p}$, where $p$ refers to the number of predictors included in the model.
 Likewise, the number of ensemble trees to aggregate was set at 500.
@@
 
-Here, TP refers to the number of bins correctly identified as containing a TAD boundary (true positives), FP refers to the number of bins incorrectly identified as containing a TAD boundary (false positives), TN refers to the number of bins correctly identified as not containing a TAD boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a TAD boundary.
+Here, TP refers to the number of bins correctly identified as containing a TAD boundary (true positives), FP refers to the number of bins incorrectly identified as containing a TAD boundary (false positives), TN refers to the number of bins correctly identified as not containing a TAD boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a TAD boundary (false negatives).
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
@@
 
-An ensemble framework was established for the purposes of systematically creating a variety of models that each included different sets of parameters described above (Figure 2).
-Each system in the framework is assumed to be composed of a model constructed from a particular data resolution, with a particular predictor type for the feature space.
+An ensemble framework was then established for the purposes of systematically creating a variety of models that each included different sets of parameters described above (Figure 2).
+Each system in the framework is assumed to be composed of a model constructed from a particular cell line and data resolution, with a particular predictor type for the feature space.
 The data sets used for modeling were composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
-These two classes made up the minority and majority sets respectively.
 The data was then split into a 7:3 ratio of training to testing sets.
-Each training and testing set was composed of a similar majority to minority class ratio as the full data set.
 For the task of performance evaluation and prediction, the test set remained constant for all ensemble systems to account for an unbiased comparison.
-Furthermore, this process was repeated, and performances were aggregated across each autosomal chromosome.
-Model results for Chromosome 9 was omitted from the analysis, for both cell lines, due to the sparcity of the contact matrix at the 10 kb resolution for the K562 cell line.
+Furthermore, this process was repeated, and performances were aggregated across each autosomal chromosome (omitting chromosome 9) using means and standard deviations.
 
@@
 
-We compared the performances of random forest classification models implemented on TAD boundaries called using the arrowhead algorithm [@durand2016juicebox] from Hi-C data for 2 cell lines $L = \{\textit{GM12878}, \textit{K562}\}$, at four different resolutions $R = \{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$.
+We compared the performances of random forest classification models implemented on TAD boundaries called using the arrowhead algorithm [@durand2016juicebox] from replicate Hi-C data for 2 cell lines $L = \{\textit{GM12878}, \textit{K562}\}$, at four different resolutions $R = \{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$.
 [???
@@
 Why you are not using plain and simple Markdown?] For each classifier, we considered 3 separate predictor types as the feature space including $P = \{\textit{OC}, \textit{OP}, \textit{Distance}\}$.
-To assess the severity of class imbalance 4 re-sampling techniques were implemented prior to modelling, including $B = \{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$.
+To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including $B = \{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$.
 Each combination of the above parameters was repeated 21 times (number of autosomal chromosomes, excluding chromosome 9), $C = \{ 1, 2, ..., 22 \}$.
@@
 Results showed that the imbalance ratios were well below acceptable thresholds for both cell lines, and across the 4 resolutions (Supplementary Table 9 ???SDs will come with more chromosomes).
-The low imbalance ratios indicated a wide disparity between the number of genomic bins that overlap with a flanked TAD boundary and the much larger number that did not.
+The low imbalance ratios indicated a wide disparity between the number of genomic bins that overlaped with a flanked TAD boundary and the much larger number that did not.
 While resolution certainly played a role in determining the number of observations included in datasets used in downstream modeling, as it determines the width of genomic bins and larger widths (lower resolutions) created less bins, we found that there was very little variation in imbalance ratios across resolution (Supplementary Figure 16 ???variation will come with additional chrs).
@@
 In order to set a baseline in performance, we first evaluated the least granular model, that is one implemented using OC predictor types, without data re-sampling.
-We found that models built data with fully imbalanced classes exhibited poor MCC across all resolutions (Figure 5A).
+We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 5A).
 We then gradually increased the granularity by assessing models built on OP predictor types, while still not performing any data resampling.
@@
 Similar results were obtained when applying ROS to the K562 cell line (Supplementary Figure 10).
-Here, a much sharper negative trend was featured for MCCs as resolution decreased, than in the GM12878 cell line.
+For K562, a much sharper negative trend was featured for MCCs as resolution decreased, than in the GM12878 cell line.
 
-Further improvement in performance was found when models were implemented on both randomly undersampled (RUS) and SMOTE resampled data, for all 3 predictor types (Figure 5).
-Although the differences in performance between the two techniques were marginal, SMOTE resampled data was found to yield the best MCCs among all classes of models developed and compared in the ensemble framework.
-As with ROS, distance type predictors yielded the highest MCC values across resolutions, when applied to either RUS or SMOTE.
+Further improvement in performance was found when models were implemented on both randomly undersampled (RUS) and SMOTE resampled data, for all 3 predictor types and across resolutions (Figure 5).
+SMOTE resampled data was found to yield the best MCCs among all classes of models developed and compared in the ensemble framework.
+Here, distance type predictors were found to again yield the highest MCC values across resolutions.
 SMOTE re-sampled data, with the inclusion of distance-type predictors was also found to be the best set of characteristics when applied to the K562 cell line (Supplementary Figure 10).
-Moreover, we found that there was a degredation in model performance as data resolution decreased.
+Moreover, for these sets of data characteristics, we again found that there was a degredation in model performance as data resolution decreased.
 This was much more pronounced in the K562 cell line.
@@
 These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on distance-type predictors and incorporates both random under- and over-sampling.
+Furthermore, models built on TAD boundaries called at higher resolutions exhibited better performances.
 
@@
 In order to assess the predictive capabilities of specific types of annotations, we further compared the performances of annotation-specific models.
-Using the optimal set of parameters, SMOTE re-sampling with distance-type predictors, random forest classifiers built on sets of histone modifications, chromatin state segmentations, and TFBS were compared to a model that included all three types together.
-For the GM12878 cell line, models built simply on TFBS were found to perform consistently just as well as models that included all 3 sets of annotations, across resolution (Figure 6).
+Using the optimal set of characteristics obtained above (SMOTE re-sampling with distance-type predictors), random forest classifiers built on sets of cell line specific histone modifications, chromatin state segmentations, and transcription factor binding sites (TFBS) were compared to a model that included all three types together.
+For GM12878, models built simply on TFBS were found to perform consistently just as well as models that included all 3 sets of annotations, across resolution (Figure 6).
 Similar results were found when evaluating the K562 cell line (supplementary Figure 11).
-For both resolutions, models built on only histone modifications were found to have the MCC, across resolutions, followed by models built on chromatin state segmentations.
+For both resolutions, models built on only histone modifications were found to have the lowest MCC, across resolutions, followed by models built on chromatin state segmentations.
 This suggests that TAD boundary formation is primarily carried out by transcription factor binding sites.
@@
 As an external method of validation, we also investigated the predictive importance of the annotations that our top performing models were built on.
-We found that specific transcription factor binding sites (TFBS), including SMC3ab, ZNF143, CTCF, and RAD21, were given consistently high predictive importance in the models built on the GM12878 cell line, across all resolutions (Figure 8).
+We found that specific TFBS, including SMC3ab, ZNF143, CTCF, and RAD21, were given consistently high predictive importance in the models built on the GM12878 cell line, across all resolutions (Figure 8).
 These are known factors associated with the hypothesized loop extrusion model [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self] and were found to yield consistently high predictive importance on the K562 cell line as well, with similar profiles across resolutions (Supplementary Figure 15).
+[???mention additional tfbs when full results ready]
 
@@
 
+<!--
 When evaluating the 10 kb data resolution, on GM12878, the distance profiles (on a $log_{2}$ scale) were found to be smaller for top predictive TFBS annotations in relation to genomic bins that overlapped with flanked TAD boundaries, when compared to bins that did not overlap with a flanked TAD boundary (Figure 7).
@@
 Similar distance profiles for the same TFBS were obtained when assessed at lower resolutions, across both cell lines (Supplementary Figures 12-17 A-D).
+-->
 

### 2019-05-06 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-**Background.** Chromosome conformation capture sequencing technologies have shown that the three-dimensional (3D) structure of the genome is folded into distinct compartments, known as topologically associated domains (TADs).
+**Background.** Chromosome conformation capture sequencing technologies have shown that the 3-dimensional structure of the genome is folded into distinct compartments, known as topologically associated domains (TADs).
 The locations of TAD boundaries have been shown to be highly conserved.
-Additionally, the distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify the epigenomic features that are most predictive of TAD boundaries.
+Additionally, the distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches toward identifying the epigenomic features most predictive of TAD boundaries.
 
@@
 For AUROC, when the prevalence of an event is low--that is, a defined genomic region truly containing a TAD boundary--mean probabilities are biased towards the majority class.
-This results in the area of interest under an ROC curve to be compressed toward a small corner in the ROC space [@prati2011survey].
+This results in the area of interest under an ROC curve to be compressed toward a small corner in the ROC space [@prati2011survey; @wei2013role].
 While not directly affecting the value of the AUROC, this can have severe consequences on the interpretability of the model's performance.
@@
 For both resolutions, models built on only histone modifications were found to have the lowest MCC, across resolutions, followed by models built on chromatin state segmentations.
-This suggests that TAD boundary formation is primarily carried out by transcription factor binding sites.
 
@@
 
-We developed an ensemble framework to systematically compare model performances for different combinations of re-sampling and feature engineering techniques aimed at determining a consensus approach to predicting TAD boundary formation using genomic annotations.
-Additionally, this study provides direct comparisons of 4 different Hi-C data resolutions, and their effects on performances of downstream models.
-Furthermore, we go on to show the importance of using adequate metric when assessing model performance, especially in the case of highly imbalanced classes.
+In this study we developed an ensemble framework to systematically compare model performances for different combinations of re-sampling and feature engineering techniques aimed at determining a consensus approach to predicting TAD boundary formation using genomic annotations.
+We provide direct comparisons of cell line specific random forest models built of a variety of different data dependent characteristics, including 4 contact matrix resolutions ($\{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$), 3 predictor-types ($\{\textit{OC}, \textit{OP}, \textit{Distance}\}$), and 4 re-sampling techniques ($\{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$), for the GM12878 and K562 cell lines.
 
-A typical problem facing machine learning approaches toward predicting TAD boundary formation is the introduction of highly imbalanced classes.
-This is because, when constructing the data for modeling, a common methodology used to determine the class of the response variable is to bin the linear genome and then create a method used to determine if each bin "includes" a TAD boundary or not.
-Given the sparcity of TADs throughout the genome though, this will inevitably lead to severly imbalanced classes.
-A workaround to this employed by [@huang2015predicting; @hong2017computational; @bednarz2014supervised] was to randomly sample from the majority class to create balanced classes in the training set.
-It is unclear how these studies handled
+The experiments derived from our ensemble framework provide a useful guide toward the exploration of chromatin organization, while highlighting the impact of both class imbalance and feature engineering in TAD boundary prediction.
+Using the framework we demonstrated that random forest models built on imbalanced data exhibited poor performance, regardless of cell line, resolution, or predictor type.
+In our framework, we opted to leave the test set as a completely untouched holdout set, only performing the re-sampling, and subsequent learning, on the training set.
+This was done so as to incur the least amount of bias and so that all conclusions could be made soley between model characteristics.
+As a result, we showed that Matthew's Correlation Coefficient was much more sensitive to the imbalance present in the test set, compared to more popular metrics like AUROC, which attain artificially high values by correctly predicting majority class samples.
+When comparing re-sampling techniques, we found that SMOTE re-sampling outperformed models built on both simple ROS or RUS, suggesting that, in fact, a combination of both random under-sampling and random over-sampling is preferred in TAD boundary prediction.
+Furthermore, the most improvement was seen when combining SMOTE resampling on distance-type features when building random forest classifiers.
+These two characteristics exhibited consistenly better performance results across both the GM12878 and K562 cell lines.
+This confirmed our hypothesis that the most granular and spatially informative representation of the relationship between TAD boundaries and annotations resulted in the best performing models.
 
-When constructing the data for modeling, a common methodology used to determine the response variable is to bin the linear genome into equally sized intervals and then create a method used to determine if each bin "includes" a TAD boundary or not.
-Given the sparcity of TADs throughout the genome, this will inevitably lead to severly imbalanced classes.
+When applying SMOTE re-sampling, with distance-type predictors, on transcription factor binding sites alone, we found that random forest classifiers performed better when compared to other annotation-specific models, including histone modifications and chromatin state segmentations.
+Likewise the performance of TFBS specific models was comparable to models with all annotations combined, across both cell line and resolution.
+This suggests that the majority of the key molecular drivers aiding in the formation of TAD boundaryies are transctiption factors, and that modifications at histone tails such as acetylation or methylation play less of a role.
 
-Although we were not able to draw direct comparisons between the GM12878 and K562 cell lines, given that they did not contain the same list of cell type specific annotations, we did find that there was relative agreement in rankings of the top predictive predictors.
-However, there were notable exclusions from each cell line, in addition to inconsistencies across resolutions
-
-## LIMITATIONS
-
-Many elastic-net models using overlap count or percent predictors were reduced to ridge, or near-ridge regression models at higher data resolutions by having the $alpha$ penalization term tuned to 0 in the cross-validation step, thereby not reducing, or reducing very few of the feature space.
-The results of the variable reduction step imply that far more information relating annotions to TAD boundaries is encoded in the distance-type predictors.
-That is, the elastic-net algorithms were better able to separate noise and reduce the feature space when performed on distance-type predictors.
-Likewise, this reduction was most efficient at more refined levels of data resolution.
+We also observed that, while the best set of data characteristics were consistent across resolutions, performances of classifiers built on said characteristics tended to decline as resolution decreased.
+For both cell lines, top performance was achieved at the 10 kb data resolution, while the worst performance was obtained at the 50 kb and 100 kb resolution for the GM12878 and K562 cell line respectively.
+This result can be attributed to one of two factors.
+First, at higher resolutions, by model construction genomic bins were smaller, Thereby resulting in more accurate profiles for the genomic annotations.
+Secondly, because we are mainly concerned with TAD boundaries, and not the heirarchical structure of domains as a whole, the sparcity of contact matrices at higher resolutions does not impair boundary prediction.
+Conversely, lower resolutions imply larger bin windows and lead to less specificity in boundary location on the linear genome, resulting in worse performances.
 

### 2019-05-06 Manuscript/manuscript.Rmd
manuscript edits

@@
 In this study we developed an ensemble framework to systematically compare model performances for different combinations of re-sampling and feature engineering techniques aimed at determining a consensus approach to predicting TAD boundary formation using genomic annotations.
-We provide direct comparisons of cell line specific random forest models built of a variety of different data dependent characteristics, including 4 contact matrix resolutions ($\{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$), 3 predictor-types ($\{\textit{OC}, \textit{OP}, \textit{Distance}\}$), and 4 re-sampling techniques ($\{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$), for the GM12878 and K562 cell lines.
+We provide direct comparisons of cell line specific random forest models built on a variety of different data dependent characteristics, including 4 contact matrix resolutions ($\{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$), 3 predictor-types ($\{\textit{OC}, \textit{OP}, \textit{Distance}\}$), and 4 re-sampling techniques ($\{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$), for both the GM12878 and K562 cell lines.
 
@@
 As a result, we showed that Matthew's Correlation Coefficient was much more sensitive to the imbalance present in the test set, compared to more popular metrics like AUROC, which attain artificially high values by correctly predicting majority class samples.
-When comparing re-sampling techniques, we found that SMOTE re-sampling outperformed models built on both simple ROS or RUS, suggesting that, in fact, a combination of both random under-sampling and random over-sampling is preferred in TAD boundary prediction.
+When comparing re-sampling techniques, we found that SMOTE re-sampling outperformed models built on both simple ROS or RUS, implying that, in fact, a combination of both random under-sampling and random over-sampling is preferred in TAD boundary prediction.
 Furthermore, the most improvement was seen when combining SMOTE resampling on distance-type features when building random forest classifiers.
 These two characteristics exhibited consistenly better performance results across both the GM12878 and K562 cell lines.
-This confirmed our hypothesis that the most granular and spatially informative representation of the relationship between TAD boundaries and annotations resulted in the best performing models.
+This confirmed our hypothesis that the most granular and spatially informative representation of the relationship between TAD boundaries and annotations resulted in the best performing model.
 
@@
 For both cell lines, top performance was achieved at the 10 kb data resolution, while the worst performance was obtained at the 50 kb and 100 kb resolution for the GM12878 and K562 cell line respectively.
-This result can be attributed to one of two factors.
-First, at higher resolutions, by model construction genomic bins were smaller, Thereby resulting in more accurate profiles for the genomic annotations.
+This suggests that TAD boundary prediction is intimately related to the resolution that boundaries are called on.
+This result can be attributed to one of two factors in the scheme of our framework.
+First, at higher resolutions, by model construction genomic bins were smaller, thereby resulting in more accurate profiles for the genomic annotations.
 Secondly, because we are mainly concerned with TAD boundaries, and not the heirarchical structure of domains as a whole, the sparcity of contact matrices at higher resolutions does not impair boundary prediction.
 Conversely, lower resolutions imply larger bin windows and lead to less specificity in boundary location on the linear genome, resulting in worse performances.
+Given the trend in performances across resolution, future research is necessary in determining the optimal resolution to use when predicting TAD boundaries.
+
+Given the formulation of our framework, we were not able to make direct comparisons between cell lines.
+This was due to the fact that we opted to use cell line specific annotations, and there existed some annotations that were available on the K562 cell line that were not available to GM12878, and vice versa.
+However, we were able to confirm that final models built on the optimal set of data characteristics identified consistent and well known proteins related to the 3D structure of chromatin, for both cell lines.
+Our results indicated that the zinc finger protein CTCF, as well components of the cohesin complex, SMC3 and RAD21, were found to be the key molecular drivers most predictive of TAD boundary formation, consistent across cell line and resolution.
+In addition, models derived from our framework recognized known mediaters of long range enhancer-promoter interactions, the ZNF143 and YY1 transcription factors, as being highly predictive of TAD boundaries.
+
+In summary, we have shown that TAD boundary prediction is a multi-faceted problem composed of many data irregularities and characteristics that previous model have failed to address.
+We have shown that our proposed framework suitably addresses each of these components, while also providing the optimal considerations to make in an effort to build consensus classifiers used to predict TAD boundary formation from functional genomic annotations.
+Given the stability of our results, this opens up the possibility of widening our framework to include a broader set of classifiers, cell lines, and Hi-C contact matix resolutions that will inevitably assist us in gaining a better understanding of the mechanisms associated with the architecture of the human genome.
 

### 2019-05-06 Manuscript/manuscript.Rmd
manuscript edits

@@
 Current methods used to predict TAD boundaries rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries.
-In doing so, many methods ignore key characteristics of domain data, such as the impact of heavily imbalanced number of boundaries vs.
+However, this is a multi-faceted probelem, and many methods ignore key characteristics of domain data when building models and reporting performances.
+We aim to address these characteristics in order to create a more unified approach toward identifyig the genomic annotations most predictive of TAD boundaries.
+
+A major ignored aspect of TAD boundary prediction is the introduction of heavily imbalanced classes resulting from the number of boundaries vs.
 nonboundary regions.
-This is because, when constructing the data for modeling, a common methodology used to determine the class of the response variable is to bin the linear genome and then create a method used to determine if each bin "includes" a TAD boundary or not.
-Given the sparcity of TADs throughout the genome though, this will inevitably lead to severly imbalanced classes.
-
 In a classification setting, when one is attempting to discriminate between regions with (minority class) and without (majority class) TAD boundaries, the class imbalance issue will contribute to small imbalance ratios.
@@
 Such heavily imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class; @chen2013influence; @jeni2013facing].
-Consequently, careful consideration must be taken when deciding which performance metric(s) to use for evaluation of predictive models, especially in the case of imbalanced data.
 
-Commonly used measures of model performance for binary classifiers include threshold-free metrics like the area under the receiver operating curve (AUROC), and other threshold-specific metrics like accuracy, sensitivity, and specificity.
-The ROC curve is created by plotting the true positive rate (TPR) against the false positive rate (FPR) at various threshold settings.
-The subsequent AUROC, measures how well the model is capable of distinguishing between the two classes [@park2004receiver].
-Accuracy is defined as the ratio of correctly identified cases (either from the positive or negative class) over the total number of cases.
-It measures the overall proportion of correctly classified instances.
-Sensitivity, also referred to as recall or TPR, is the ratio of true positives over the total number of positive classes.
-Specificity, on the other hand, also referred to as TNR, is the ratio of true negatives over the total number of negative classes.
-Each measures the proportion of correctly identified positive and negative classes respectively [@yerushalmy1947statistical].
-Problems arise when using such measures in the event of imbalanced classes.
-For AUROC, when the prevalence of an event is low--that is, a defined genomic region truly containing a TAD boundary--mean probabilities are biased towards the majority class.
+In a study published in 2016 [@mourad2016computational], an L1-regularized multiple logistic regression model was proposed using transcription factor binding sites on GM12878 to discriminate between regions with and without TADs, and to identify the most predictive factors associated with boundaries.
+However, the class imbalance issue was not addressed.
+Even worse, when performing cross-validation [@mourad2016computational], used the misclassification error rate of the model to establish the optimal L1-regularization lambda.
+They also reported ROC (receiver operating characteristic) curves and subsequent AUC (area under the curve) as measures of their model's performance.
+This is problematic in an imbalanced setting.
+Such heavily imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class; @chen2013influence; @jeni2013facing].
+For AUC, when the prevalence of an event is low--that is, a defined genomic region truly containing a TAD boundary--mean probabilities are biased towards the majority class.
 This results in the area of interest under an ROC curve to be compressed toward a small corner in the ROC space [@prati2011survey; @wei2013role].
 While not directly affecting the value of the AUROC, this can have severe consequences on the interpretability of the model's performance.
-A better threshold-free measure to use when dealing with imbalanced data is the area under the precision-recall curve (AUPRC).
-The interpretation of the AUPRC of a model is similar to that of the AUROC.
-However, where as the baseline model performance according to the AUROC is given by 0.50, the baseline model performance according to the AUPRC is given by the ratio of true positives over the total number of cases.
-This enables a more realistic benchmark to evaluate a model on as this ratio will be lower than 0.5 for a test data set with imbalanced classes.
-Likewise, threshold-specific metrics like accuracy and specificity are also problematic when evaluating model performance on imbalance data due to being highly influenced by the correct classification of the majority class.
+Consequently, careful consideration must be taken when deciding which performance metric(s) to use for evaluation of predictive models, especially in the case of imbalanced data.
 A better measure to consider is a composite metric involving all quadrants of the confusion matirix, such as Matthew's Correlation Coefficient (MCC) [@jeni2013facing; @chicco2017ten].
@@
 
-<!--
-precision and recall together because they soften the influence of a model's ability to correctly classify majority classes and yield more dependable and interpretable results.
-Therefore, measures like the F1-Score and Matthew's Correlation Coefficient (MCC) offer better interpretation, especially in the instance of imbalanced classes [@jeni2013facing].
-The F1-Score can be interpreted as a weighted average of the precision and recall values, while the MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
-Each metric uses all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
--->
+In addition to employing suitable metrics for evaluating models validated on imbalanced data, there also exists several data level solutions.
+Data level solutions mostly constitute as re-sampling techniques, in which random sampling is used to either replicate or remove data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
+It has been shown that quite simple re-sampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
 
-<!--
-, and balanced accuracy offer better interpretation, especially in the instance of imbalanced classes [@jeni2013facing].
-The F1-Score can be interpreted as a weighted average of the precision and recall values, balanced accuracy measures the average accuracy obtained on either class, and MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
-Each metric uses all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
--->
+Two studies published in 2015 and 2017 respectively [@huang2015predicting; @hong2017computational] used re-sampling techniques prior to modeling, and both implemented random under-sampling to balance classes.
+However, given the large disparity between the number of genomic regions labeled as containing a TAD boundary or not, performing random under-sampling alone is likely to be unstable and introduce bias.
+Also, it is unclear how other data level solution compare to simple random under-sampling, for instance random over-sampling or a weighted combination of both random under- and over-sampling together.
+Equally concerning is how the test set is treated in scenarios of re-sampling.
+It was found that [@huang2015predicting] performed re-sampling prior to splitting the data into training and testing.
+However, this is problematic because re-sampling prior to splitting can further introduce bias into the testing set, as it is no longer an accurate representation of real-world data [@wei2013role].
 
-<!--
-Certain composite threshold-specific metrics such as balanced accuracy and Youden's Index should be preferred because they soften the influence of a model's ability to correctly classify majority classes and yield more dependable and interpretable results [@jeni2013facing].
-Here, balanced accuracy measures the average accuracy obtained on either class [@brodersen2010balanced].
-Informedness, also referred to as Youden's Index, measures the probability of the model making an informed decision and corresponds to giving equal weight per class, rather than to each instance like Accuracy [@youden1950index;@powers2011evaluation].
--->
-
-<!--
-Better measures to consider are composite metrics involving both precision and recall together.
-Therefore, measures like the F1-Score, Youden's Index (YI), and Matthew's Correlation Coefficient (MCC) offer better interpretation, especially in the instance of imbalanced classes [@jeni2013facing].
-The F1-Score can be interpreted as a weighted average of the precision and recall values, while Youden's index is interpreted as the arithmetic mean between sensitivity (recall) and specificity.
-MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications.
-Each metric uses all 4 quadrants of the confusion matrix, thus providing more balanced measures in the case of imbalanced data [@chicco2017ten].
--->
-
-In addition to employing suitable metrics for evaluating models validated on imbalanced data, there also exists several algorithmic or data level solutions.
-Algorithmic level solutions involve modifyng existing classifiers in order to curtail the bias induced by imbalanced classes [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical].
-Data level solutions, on the other hand, mostly constitute as re-sampling techniques, in which random sampling is used to either replicate or remove data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
-It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
-For the purposes of this study, we focus our attention toward data level solutions so that all results may be classifier-independent, and, thus, more easily comparable.
-
-Another underexplored aspect of modeling the association between TAD boundaries and genomic annotations is determining a suitable representation of the relationship between them.
-Typical approaches include overlap counts or percents [@mourad2016computational; @hong2017computational; @huang2015predicting].
+Furthermore, determing the optimal representation of the relationship between features in the model and genomic regions, known as feature engineering, plays a significant role in TAD prediction.
+Typical approaches include overlap counts [@hong2017computational] or percents [@mourad2016computational; @huang2015predicting].
 Counts refer to the number of times a genomic annotation directly overlaps with a TAD boundary region, e.g., a TAD boundary may overlap with several ChIP-seq peaks for a given transcription factor.
@@
 g., 60% of a TAD boundary region may overlap with a genomic region annotated as heterochromatin.
-
 While direct overlaps represent the most straightforward measure of functional associations, they do not account for indirect relationships shown to be one of the major driving force of genome regulation [???
@@
 The most prominent example being the enhancer-promoter relationships, where enhancers are frequently located hundreds or thousands of bases away from their target promoters [@whalen2016enhancer].
+Using percents offers a more granular approach, but it is unclear how it performs when compared to counts.
 On the other hand, the use of distances between TAD boundaries and genomic annotations has largely been ignored.
-However, these distance features have the potential to offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
+However, these distance features have the potential to offer the most accurate spatial representation of which genomic features are associated with TAD boundaries.
 
@@
 This will contribute to smaller sample sizes and could effect predictive performances.
+To date, no study has compared the results of their predictive models built across multiple data resolutions.
 
-Therefore, in this study, we aimed to develop an ensemble framework used to build random forest classifiers composed of different combinations of data driven parameters used to address the issues presented above.
-We used our framework to systematically compare model performances using a composite performance metric, MCC.
+Therefore, in this study, we aimed to develop an ensemble framework composed of different combinations of data driven characteristics used to address the issues presented above.
+We used our framework to systematically compare performances of random forest classifiers using a composite performance metric, MCC.
 Our goal was to determine a suitable combination of data re-sampling and feature engineering techniques that both corrected the inherent imbalanced classes and provided the best spatial representation linking genomic annotations to TAD boundaries.

### 2019-05-06 Manuscript/manuscript.Rmd
manuscript edits

@@
 
+<!--
 ## DISTANCE PROFILES HIGHLIGHT THE RELATIONSHIP BETWEEN KEY TFBS AND TAD BOUNDARIES
 
-<!--
 When evaluating the 10 kb data resolution, on GM12878, the distance profiles (on a $log_{2}$ scale) were found to be smaller for top predictive TFBS annotations in relation to genomic bins that overlapped with flanked TAD boundaries, when compared to bins that did not overlap with a flanked TAD boundary (Figure 7).

### 2019-05-07 Manuscript/manuscript.Rmd
editted abstract

@@
 
-**Background.** Chromosome conformation capture sequencing technologies have shown that the 3-dimensional structure of the genome is folded into distinct compartments, known as topologically associated domains (TADs).
-The locations of TAD boundaries have been shown to be highly conserved.
-Additionally, the distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches toward identifying the epigenomic features most predictive of TAD boundaries.
+**Background.** Advances in chromosome conformation capture sequencing technologies have revealed the hierarchical structure of genome organization.
+Among this organization exists regions in the genome that are highly self-interacting, termed topologically associated domains (TADs).
+The locations of TADs throughout the linear genome has been studied extensively.
+However, the set of functional genomic annotations that are associated with the formation of TADs has not been systematically evaluated.
+By identifying the annotations that are enriched near regions that demarcate TADs, we can gain a better understanding of the mechanisms that lead to the 3D structure of the genome.
 
-Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions on the linear genome that include TAD boundaries.
-However, many methods ignore key characteristics of domain data, such as the impact of heavily imbalanced classes distinguished by boundary vs.
-non-boundary regions and the use of distances ($log_{2}$ transformed) as the best representation of the association between TAD boundaries and genomic annotations.
+This is a multi-faceted problem, and many current methods ignore key characteristics of domain data when building models and reporting performances.
+First, the sparsity of TAD boundaries throughout the linear genome leads to heavily imbalanced classes distinguished by boundary vs.
+non-boundary regions.
+Second, determining the most informative relationship between TAD boundaries and genomic annotations remains and open problem.
+We hypothesize that implementing re-sampling, in conjunction with distances (in basepairs) between annotations and pre-defined regions on the genome, will results in better learned models.
 
-**Methods.** Using replicate Hi-C data for the GM12878 and K562 cell lines, we proposed a novel ensemble framework that addresses these data irregularities and characteristics.
-Multiple random forest classification models built on regularized sets of genomic annotations obtained from the UCSC genome browser database, in combination with variations in data resolution, feature engineering, and re-sampling techniques.
-The composite metric Matthew's Correlation Coefficient (MCC) was used to compare models derived from the framework to determine a consensus approach toward predicting TAD boundary formation.
+**Methods.** We proposed a novel ensemble framework in order to systematically compare the performances of random forest classifiers implemented on combinations of different Hi-C contact matrix resolutions, feature engineering strategies, and re-sampling techniques.
 
-**Results.** We discovered that models built on SMOTE (Synthetic Minority Over-sampling TEchnique) re-sampled data out performed models built simply on random under- and over-sampled data.
-Additionally, our results indicated that log2 distances between annotations and TAD boundaries were more informative than other predictor-types used to build models.
+**Results.** Using the GM12878 and K562 cell lines, we show that models built on SMOTE (Synthetic Minority Over-sampling TEchnique) re-sampled data out performed models built simply on random under- and over-sampled data, across all resolutions.
+Additionally, our results indicated that distances between annotations and TAD boundaries were more informative than other predictor-types used to build models.
 Importantly, we also found that performances tended to degrade as data resolution decreased.
-Lastly, the most predictive annotations in the best performing models included known architectural proteins such as CTCF, SMC3, RAD21, and ZNF143, as well as lesser known transcription factors including P300 and NFKB.
+Lastly, the most predictive annotations in the best performing models were found to be consistent across both cell line and resolution.
+They included well-known marks of TAD boundaries such as CTCF, SMC3, RAD21, and ZNF143, as well as lesser known transcription factors including P300 and NFKB.
 
 **Conclusions.** The experiments derived from our ensemble framework provide a useful guide toward the exploration of chromatin organization, while highlighting the impact of both class imbalance and feature engineering in TAD boundary prediction.
+Our framework provides insight into the best set of parameter necessary for optimal performance.
 

### 2019-05-07 Manuscript/manuscript.Rmd
abstract edits

@@
 
-**Background.** Advances in chromosome conformation capture sequencing technologies have revealed the hierarchical structure of genome organization.
+**Background.** Advances in Hi-C sequencing technologies have revealed the hierarchical structure of genome organization.
 Among this organization exists regions in the genome that are highly self-interacting, termed topologically associated domains (TADs).
 The locations of TADs throughout the linear genome has been studied extensively.
-However, the set of functional genomic annotations that are associated with the formation of TADs has not been systematically evaluated.
+However, the set of functional genomic annotations that are associated with the formation of TADs has not yet been systematically evaluated.
 By identifying the annotations that are enriched near regions that demarcate TADs, we can gain a better understanding of the mechanisms that lead to the 3D structure of the genome.
 
-This is a multi-faceted problem, and many current methods ignore key characteristics of domain data when building models and reporting performances.
-First, the sparsity of TAD boundaries throughout the linear genome leads to heavily imbalanced classes distinguished by boundary vs.
+Current methods rely on the use of classification algorithms to predict influential annotations.
+However, key characteristics of domain data are typically ignored.
+Most importantly, the sparsity of TAD boundaries throughout the linear genome leads to heavily imbalanced classes that distinguish boundary vs.
 non-boundary regions.
-Second, determining the most informative relationship between TAD boundaries and genomic annotations remains and open problem.
-We hypothesize that implementing re-sampling, in conjunction with distances (in basepairs) between annotations and pre-defined regions on the genome, will results in better learned models.
-
-**Methods.** We proposed a novel ensemble framework in order to systematically compare the performances of random forest classifiers implemented on combinations of different Hi-C contact matrix resolutions, feature engineering strategies, and re-sampling techniques.
+In addition, determining the most informative relationship between TAD boundaries and genomic annotations remains an open problem.
+**Methods.** To address this, we proposed a novel ensemble framework in order to systematically compare the performances of random forest classifiers implemented on combinations of different Hi-C contact matrix resolutions, feature engineering strategies, and re-sampling techniques.
 
 **Results.** Using the GM12878 and K562 cell lines, we show that models built on SMOTE (Synthetic Minority Over-sampling TEchnique) re-sampled data out performed models built simply on random under- and over-sampled data, across all resolutions.
-Additionally, our results indicated that distances between annotations and TAD boundaries were more informative than other predictor-types used to build models.
-Importantly, we also found that performances tended to degrade as data resolution decreased.
+Additionally, our results indicated that distances between annotations and TAD boundaries were more informative than other predictor-types used to build the feature space of models.
+We also observed that performances tended to degrade as data resolution decreased.
 Lastly, the most predictive annotations in the best performing models were found to be consistent across both cell line and resolution.
@@
 **Conclusions.** The experiments derived from our ensemble framework provide a useful guide toward the exploration of chromatin organization, while highlighting the impact of both class imbalance and feature engineering in TAD boundary prediction.
-Our framework provides insight into the best set of parameter necessary for optimal performance.
+Our framework provides insight into the best set of parameters necessary for optimal performance.
 

### 2019-05-07 Manuscript/manuscript_structured.Rmd
Add structured version of the manuscript

---
title: "Untitled"
output: html_document
---

# Abstract

**Background.** Topologically Associated Domains (TADs) represent fundamental building blocks of the 3D genome organization and regulation. Several epigenomic marks, such as CTCF and the members of Cohesin complex, were found to be enriched at TAD boundaries, suggesting a strong epigenetic component in TAD formation. Several methods for predicting TAD boundaries using epigenomic data overlooked key characteristics of genome annotation data, such as indirect associations between an annotation and a boundary. Furthermore, the number of regions containing TAD boundaries is typically much smaller than the rest of the genome, creating a class imbalance problem.

**Methods.** To address this, we proposed a novel ensemble framework in order to systematically compare the performances of random forest classifiers implemented on combinations of different Hi-C contact matrix resolutions, feature engineering strategies, and re-sampling techniques.

**Results.** Using the GM12878 and K562 cell lines, we show that models built on SMOTE (Synthetic Minority Over-sampling TEchnique) re-sampled data out performed models built simply on random under- and over-sampled data, across all resolutions. Additionally, our results indicated that distances between annotations and TAD boundaries were more informative than other predictor-types used to build the feature space of models. We also observed that performances tended to degrade as data resolution decreased. Lastly, the most predictive annotations in the best performing models were found to be consistent across both cell line and resolution. They included well-known marks of TAD boundaries such as CTCF, SMC3, RAD21, and ZNF143, as well as lesser known transcription factors including P300 and NFKB.

**Conclusions.** The experiments derived from our ensemble framework provide a useful guide toward the exploration of chromatin organization, while highlighting the impact of both class imbalance and feature engineering in TAD boundary prediction. Our framework provides insight into the best set of parameters necessary for optimal performance.

# Introduction

## Importance

## Problems and limitations

### Hi-C data issues for TAD boundary identification

Although Hi-C data allows for identification of TADs genome-wide, it has limitations. First, Hi-C requires a large amount of sequencing (one Hi-C experiment requires >20X sequencing of a typical RNA-seq experiment). Consequently, the cost of obtaining Hi-C data remains high and the data availability for various cell lines and tissues remain highly uneven. Second, resolution of Hi-C data, or the size of interacting genomic regions, remains relatively coarse (on the order of kilobases) as compared with transcription factor binding motifs (tenths bases) or ChIP-seq peaks (hundredths bases), and inconsistent across cell lines and tissues. Third, Hi-C data suffers from technology- and DNA-driven biases, sparsity (high proportion of missing values), and limited sequencing depth, adding to inconsistency to cell- and tissue type-specific Hi-C data availability. These factors hinder the consistent TAD boundary identification across tissues and cell types.

### Genome annotation data opportunities

In contrast, 1D genome annotation tracks assembled by the ENCODE and Roadmap consortia provide a fine-grained look at the genome in various tissues and cell types. Although the original genome annotation data was highly uneven (rich annotations available for select cell types while remaining sparse for others), recent genome annotation imputation methods fill the cell type-specific sparsity of genome annotations. Consequently, using existing and imputed genome annotations for TAD boundary predictions represent a viable way to identify TAD boundaries in any cell or tissue type.

### Class imbalance

### Prediction types

## Previous works on solving problems

### Resampling approaches

### Models

### Evaluation metrics

## Pitfalls of previous works

### Distance not considered

## Our work on solving problems

### Consider distance

### 2019-05-08 Manuscript/manuscript.Rmd
manuscript edits

@@
 Consequently, careful consideration must be taken when deciding which performance metric(s) to use for evaluation of predictive models, especially in the case of imbalanced data.
-A better measure to consider is a composite metric involving all quadrants of the confusion matirix, such as Matthew's Correlation Coefficient (MCC) [@jeni2013facing; @chicco2017ten].
+
+A better threshold-free measure to use when dealing with imbalanced data is the area under the precision-recall curve (AUPRC).
+The interpretation of the AUPRC of a model is similar to that of the AUROC.
+However, where as the baseline model performance according to the AUROC is given by 0.50, the baseline model performance according to the AUPRC is given by the ratio of true positives over the total number of cases.
+This enables a more realistic benchmark to evaluate a model on as this ratio will be lower than 0.5 for a test data set with imbalanced classes [@saito2015precision].
+Another threshold-specific measure to consider is a composite metric involving all quadrants of the confusion matirix, such as Matthew's Correlation Coefficient (MCC) [@jeni2013facing; @chicco2017ten].
 The MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].

### 2019-05-08 Manuscript/Supplementary/supplementary_legends.Rmd
consolidated supp fig and table into one table

@@
 
-**Supplementary Figure 14.
-Number of TADs called throughout the genome.** TADs were called throughout each of the 22 autosomal chromosomes for cell lines GM12878 (red) and K562 (blue) using the Arrowhead algorithm [@durand2016juicebox], across each data resolution including 10 kb, 25 kb, 50 kb, and 100 kb (A-D) respectively.
-
 **Supplementary Table 8.
-Summary statistics for TAD lengths.** The following summary statistics were recorded regarding lengths of TADs that were called and delineated into TAD boundaries including the minimum, 1st quartile, median, mean, 3rd quartile, and maximum TAD lengths (in basepairs).
-The summaries are provided for each cell line, resolution, and within each chromosome.
-[???should I leave space for 9th chromosome on k562 where no TADs were called?]
+Summary statistics for called TADs.** The following summary statistics were recorded regarding the average number and length of TADs (along with standard deviations) that were called using the Arrowhead algorithm [@durand2016juicebox], across each of the autosomal chromosomes (excluding chromosome 9).
 

### 2019-05-08 Scripts/distribution_of_tads.Rmd
editted results script

--- 2019-04-11 Scripts/distribution_of_tads.Rmd
@@
 
-tad_data <- tad_gm12878_10kb %>% 
+tad_data_gm12878_10kb <- tad_gm12878_10kb %>% 
   group_by(V1) %>% 
-  summarise(Count = length(V1))
-
-gm12878_10kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
-  geom_bar(stat="identity") +
-  scale_fill_discrete(name="Chromosome") +
-  guides(fill=FALSE) +
-  ylab("Number of TADs") +
-  xlab("Chromosome") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
-
-gm12878_10kb_tabdist <- ggplot(tad_gm12878_10kb, aes(x=Length, color=V1)) +
-  geom_density() +
-  scale_color_discrete(name="Chromosome") +
-  ylab("Count") +
-  xlab("Length of TAD") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
+  summarise(Count = length(V1),
+            Length = mean(Length))
 
@@
 
-tad_data <- tad_gm12878_25kb %>% 
+tad_data_gm12878_25kb <- tad_gm12878_25kb %>% 
   group_by(V1) %>% 
-  summarise(Count = length(V1))
-
-gm12878_25kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
-  geom_bar(stat="identity") +
-  scale_fill_discrete(name="Chromosome") +
-  guides(fill=FALSE) +
-  ylab("Number of TADs") +
-  xlab("Chromosome") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
-
-gm12878_25kb_tabdist <- ggplot(tad_gm12878_25kb, aes(x=Length, color=V1)) +
-  geom_density() +
-  scale_color_discrete(name="Chromosome") +
-  ylab("Count") +
-  xlab("Length of TAD") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
+  summarise(Count = length(V1),
+            Length = mean(Length))
 
@@
 
-tad_data <- tad_gm12878_50kb %>% 
+tad_data_gm12878_50kb <- tad_gm12878_50kb %>% 
   group_by(V1) %>% 
-  summarise(Count = length(V1))
-
-gm12878_50kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
-  geom_bar(stat="identity") +
-  scale_fill_discrete(name="Chromosome") +
-  guides(fill=FALSE) +
-  ylab("Number of TADs") +
-  xlab("Chromosome") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
-
-gm12878_50kb_tabdist <- ggplot(tad_gm12878_50kb, aes(x=Length, color=V1)) +
-  geom_density() +
-  scale_color_discrete(name="Chromosome") +
-  ylab("Count") +
-  xlab("Length of TAD") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
+  summarise(Count = length(V1),
+            Length = mean(Length))
 
@@
 
-tad_data <- tad_gm12878_100kb %>% 
+tad_data_gm12878_100kb <- tad_gm12878_100kb %>% 
   group_by(V1) %>% 
-  summarise(Count = length(V1))
-
-gm12878_100kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
-  geom_bar(stat="identity") +
-  scale_fill_discrete(name="Chromosome") +
-  guides(fill=FALSE) +
-  ylab("Number of TADs") +
-  xlab("Chromosome") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
-
-gm12878_100kb_tabdist <- ggplot(tad_gm12878_100kb, aes(x=Length, color=V1)) +
-  geom_density() +
-  scale_color_discrete(name="Chromosome") +
-  ylab("Count") +
-  xlab("Length of TAD") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
+  summarise(Count = length(V1),
+            Length = mean(Length))
 
@@
 
-tad_data <- tad_K562_10kb %>% 
+tad_data_K562_10kb <- tad_K562_10kb %>% 
   group_by(V1) %>% 
-  summarise(Count = length(V1))
-
-K562_10kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
-  geom_bar(stat="identity") +
-  scale_fill_discrete(name="Chromosome") +
-  guides(fill=FALSE) +
-  ylab("Number of TADs") +
-  xlab("Chromosome") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
-
-K562_10kb_tabdist <- ggplot(tad_K562_10kb, aes(x=Length, color=V1)) +
-  geom_density() +
-  scale_color_discrete(name="Chromosome") +
-  ylab("Count") +
-  xlab("Length of TAD") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
+  summarise(Count = length(V1),
+            Length = mean(Length))
 
@@
 
-tad_data <- tad_K562_25kb %>% 
+tad_data_K562_25kb <- tad_K562_25kb %>% 
   group_by(V1) %>% 
-  summarise(Count = length(V1))
-
-K562_25kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
-  geom_bar(stat="identity") +
-  scale_fill_discrete(name="Chromosome") +
-  guides(fill=FALSE) +
-  ylab("Number of TADs") +
-  xlab("Chromosome") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
-
-K562_25kb_tabdist <- ggplot(tad_K562_25kb, aes(x=Length, color=V1)) +
-  geom_density() +
-  scale_color_discrete(name="Chromosome") +
-  ylab("Count") +
-  xlab("Length of TAD") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
+  summarise(Count = length(V1),
+            Length = mean(Length))
 
@@
 
-tad_data <- tad_K562_50kb %>% 
+tad_data_K562_50kb <- tad_K562_50kb %>% 
   group_by(V1) %>% 
-  summarise(Count = length(V1))
-
-K562_50kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
-  geom_bar(stat="identity") +
-  scale_fill_discrete(name="Chromosome") +
-  guides(fill=FALSE) +
-  ylab("Number of TADs") +
-  xlab("Chromosome") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
-
-K562_50kb_tabdist <- ggplot(tad_K562_50kb, aes(x=Length, color=V1)) +
-  geom_density() +
-  scale_color_discrete(name="Chromosome") +
-  ylab("Count") +
-  xlab("Length of TAD") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
+  summarise(Count = length(V1),
+            Length = mean(Length))
 
@@
 
-tad_data <- tad_K562_100kb %>% 
+tad_data_K562_100kb <- tad_K562_100kb %>% 
   group_by(V1) %>% 
-  summarise(Count = length(V1))
-
-K562_100kb_tabnum <- ggplot(tad_data, aes(x=V1, y=Count, fill=V1))+
-  geom_bar(stat="identity") +
-  scale_fill_discrete(name="Chromosome") +
-  guides(fill=FALSE) +
-  ylab("Number of TADs") +
-  xlab("Chromosome") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
-
-K562_100kb_tabdist <- ggplot(tad_K562_100kb, aes(x=Length, color=V1)) +
-  geom_density() +
-  scale_color_discrete(name="Chromosome") +
-  ylab("Count") +
-  xlab("Length of TAD") +
-  #ylab("") +
-  #xlab("") +
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
-     axis.text.y = element_text(size = 15),
-     axis.title.x = element_text(size = 20),
-     axis.title.y = element_text(size = 20),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=20),
-     plot.title = element_text(size=20))
+  summarise(Count = length(V1),
+            Length = mean(Length))
 
@@
 
-# Plots
+# Tables
 
 ```{r}
-figure <- ggarrange(gm12878_10kb_tabnum,gm12878_10kb_tabdist,
-                    gm12878_25kb_tabnum,gm12878_25kb_tabdist,
-                    gm12878_50kb_tabnum,gm12878_50kb_tabdist,
-                    gm12878_100kb_tabnum,gm12878_100kb_tabdist,
-                    ncol=2,nrow=4,
-                    common.legend = TRUE,
-                    legend="right",
-                    labels = c("A", "","B", "","C", "","D", ""),
-                    font.label = list(size=20))
+combined <- rbind.data.frame(tad_data_gm12878_10kb,
+                             tad_data_gm12878_25kb,
+                             tad_data_gm12878_50kb,
+                             tad_data_gm12878_100kb,
+                             tad_data_K562_10kb,
+                             tad_data_K562_25kb,
+                             tad_data_K562_50kb,
+                             tad_data_K562_100kb)
 
-figure <- ggarrange(K562_10kb_tabnum,K562_10kb_tabdist,
-                    K562_25kb_tabnum,K562_25kb_tabdist,
-                    K562_50kb_tabnum,K562_50kb_tabdist,
-                    K562_100kb_tabnum,K562_100kb_tabdist,
-                    ncol=2,nrow=4,
-                    common.legend = TRUE,
-                    legend="right",
-                    labels = "AUTO",
-                    font.label = list(size=20))
+combined <- combined[-which(combined$V1==9),]
+combined$V1 <- factor(combined$V1)
+
+combined$CL <- c(rep("GM12878", 84), rep("K562", 84))
+combined$Resolution <- c(rep("10 kb", 21),
+                         rep("25 kb", 21),
+                         rep("50 kb", 21),
+                         rep("100 kb", 21),
+                         rep("10 kb", 21),
+                         rep("25 kb", 21),
+                         rep("50 kb", 21),
+                         rep("100 kb", 21))
+combined$CL <- factor(combined$CL)
+combined$Resolution <- factor(combined$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
+
+summarytab <- combined %>% 
+  group_by(CL, Resolution) %>% 
+  summarise(AveNumber = mean(Count),
+            SDNumber = sd(Count),
+            AveLength = mean(Length),
+            SDLength = sd(Length))
+summarytab[,3:6] <- round(summarytab[,3:6], 1)
 ```
-
-# Creating Table of Summaraies
-
-```{r}
-tad_gm12878_10kb$CL <- "GM12878"
-tad_gm12878_25kb$CL <- "GM12878"
-tad_gm12878_50kb$CL <- "GM12878"
-tad_gm12878_100kb$CL <- "GM12878"
-tad_K562_10kb$CL <- "K562"
-tad_K562_25kb$CL <- "K562"
-tad_K562_50kb$CL <- "K562"
-tad_K562_100kb$CL <- "K562"
-
-tad_data_summaries <- rbind.data.frame(aggregate(tad_gm12878_10kb$Length, by=list(tad_gm12878_10kb$V1), FUN=summary),
-                 aggregate(tad_gm12878_25kb$Length, by=list(tad_gm12878_25kb$V1), FUN=summary),
-                 aggregate(tad_gm12878_50kb$Length, by=list(tad_gm12878_50kb$V1), FUN=summary),
-                 aggregate(tad_gm12878_100kb$Length, by=list(tad_gm12878_100kb$V1), FUN=summary),
-                 aggregate(tad_K562_10kb$Length, by=list(tad_K562_10kb$V1), FUN=summary),
-                 aggregate(tad_K562_25kb$Length, by=list(tad_K562_25kb$V1), FUN=summary),
-                 aggregate(tad_K562_50kb$Length, by=list(tad_K562_50kb$V1), FUN=summary),
-                 aggregate(tad_K562_100kb$Length, by=list(tad_K562_100kb$V1), FUN=summary))
-
-#chr 9 for k562 at 10 kb has no tad boundaries
-
-tad_data_summaries$CL <- c(rep("GM12878", 22*4), rep("K562", 22*4-1))
-tad_data_summaries$Resolution <- c(rep("10 kb", 22),rep("25 kb", 22),rep("50 kb", 22),rep("100 kb", 22),
-                                   rep("10 kb", 21),rep("25 kb", 22),rep("50 kb", 22),rep("100 kb", 22))
-
-write.csv(tad_data_summaries, "C:/Users/stili/Downloads/tad_data_summaries.csv")
-```

### 2019-05-08 Manuscript/Supplementary/supplementary_legends.Rmd
added imbalance ratio boxplot with all chromosomes; removed unnecessary tables plots

@@
 Each curve represents the raw (red) and $log_{2}$ transformed (blue) distance profiles for each annotation, across each of the 4 resolutions (A-D).
-
-<!--
-**Supplementary Figure 2.
-Clustered correlogram for genomic annotations at the 10 kb resolution for the GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
-Positive correlations are denoted in red, while negative correlations are denoted in blue.
-The upper triangular matrix of correlations was clustered using Ward's method.
-Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
-
-**Supplementary Figure 3.
-Clustered correlogram for genomic annotations at the 10 kb resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
-Positive correlations are denoted in red, while negative correlations are denoted in blue.
-The upper triangular matrix of correlations was clustered using Ward's method.
-Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
-
-**Supplementary Figure 4.
-Clustered correlogram for genomic annotations at the 25 kb resolution for GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
-Positive correlations are denoted in red, while negative correlations are denoted in blue.
-The upper triangular matrix of correlations was clustered using Ward's method.
-Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
-
-**Supplementary Figure 5.
-Clustered correlogram for genomic annotations at the 25 kb resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
-Positive correlations are denoted in red, while negative correlations are denoted in blue.
-The upper triangular matrix of correlations was clustered using Ward's method.
-Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
-
-**Supplementary Figure 6.
-Clustered correlogram for genomic annotations at the 50 kb resolution for GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
-Positive correlations are denoted in red, while negative correlations are denoted in blue.
-The upper triangular matrix of correlations was clustered using Ward's method.
-Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
-
-**Supplementary Figure 7.
-Clustered correlogram for genomic annotations at the 50 kb resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
-Positive correlations are denoted in red, while negative correlations are denoted in blue.
-The upper triangular matrix of correlations was clustered using Ward's method.
-Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
-
-**Supplementary Figure 8.
-Clustered correlogram for genomic annotations at the 100 kb resolution for GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
-Positive correlations are denoted in red, while negative correlations are denoted in blue.
-The upper triangular matrix of correlations was clustered using Ward's method.
-Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
-
-**Supplementary Figure 9.
-Clustered correlogram for genomic annotations at the 100 kb resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome.
-Positive correlations are denoted in red, while negative correlations are denoted in blue.
-The upper triangular matrix of correlations was clustered using Ward's method.
-Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
--->
-
-**Supplementary Table 9.
-Imbalance ratios.** The mean (SD) imbalance ratios across the autosomal chromosomes for each resolution and cell line.
-Imbalance ratios are defined as the ratio of minority classes to majority classes are provided across resolution and cell line.
-The minority class is the set of genomic bins that overlap with flanked TAD boundaries, while the majority class is the set of genomic bins that do not overlap with any flanked TAD boundary.
-
-**Supplementary Figure 16. Imbalance ratios vs resolution.** Scatter plots illustrating the relationship between imbalance ratios and resolutions, for each cell line.
 

### 2019-05-08 Scripts/evaluating_imbalance_ratios.Rmd
editted results script

--- 2019-02-27 Scripts/evaluating_imbalance_ratios.Rmd
@@
 ```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
+IR_gm12878_10kb <- numeric(22)
 
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
+#reading in whole genome data
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/gm12878_10kb.rds")
+#reading in bin data on the whole genome that contains chromosome information
+binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")
 
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
+for(i in 1:22){
+  #reducing the whole genome data to only specific chromosome
+	reduce_chr <- paste0("chr", i)
+	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]
 
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x10 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p10kb <- ggplot(x10, aes(y=IR, x=factor(CB, levels = unique(x10$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  IR_gm12878_10kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
+}
 
@@
 ```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/test.rds")
+IR_gm12878_25kb <- numeric(22)
 
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
+#reading in whole genome data
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/gm12878_25kb.rds")
+#reading in bin data on the whole genome that contains chromosome information
+binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")
 
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
+for(i in 1:22){
+  #reducing the whole genome data to only specific chromosome
+	reduce_chr <- paste0("chr", i)
+	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]
 
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x25 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p25kb <- ggplot(x25, aes(y=IR, x=factor(CB, levels = unique(x25$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  IR_gm12878_25kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
+}
 
@@
 ```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/test.rds")
+IR_gm12878_50kb <- numeric(22)
 
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
+#reading in whole genome data
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/gm12878_50kb.rds")
+#reading in bin data on the whole genome that contains chromosome information
+binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")
 
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
+for(i in 1:22){
+  #reducing the whole genome data to only specific chromosome
+	reduce_chr <- paste0("chr", i)
+	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]
 
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x50 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p50kb <- ggplot(x50, aes(y=IR, x=factor(CB, levels = unique(x50$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  IR_gm12878_50kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
+}
 
@@
 ```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/test.rds")
+IR_gm12878_100kb <- numeric(22)
 
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
+#reading in whole genome data
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/gm12878_100kb.rds")
+#reading in bin data on the whole genome that contains chromosome information
+binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")
 
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
+for(i in 1:22){
+  #reducing the whole genome data to only specific chromosome
+	reduce_chr <- paste0("chr", i)
+	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]
 
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x100 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p100kb <- ggplot(x100, aes(y=IR, x=factor(CB, levels = unique(x100$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  IR_gm12878_100kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
+}
 
@@
 ```{r}
-train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")
+IR_K562_10kb <- numeric(22)
 
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
+#reading in whole genome data
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/K562_10kb.rds")
+#reading in bin data on the whole genome that contains chromosome information
+binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")
 
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
+for(i in 1:22){
+  #reducing the whole genome data to only specific chromosome
+	reduce_chr <- paste0("chr", i)
+	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]
 
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x10_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p10kb_k562 <- ggplot(x10_k562, aes(y=IR, x=factor(CB, levels = unique(x10_k562$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  IR_K562_10kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
+}
 
@@
 ```{r}
-train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/test.rds")
+IR_K562_25kb <- numeric(22)
 
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
+#reading in whole genome data
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/K562_25kb.rds")
+#reading in bin data on the whole genome that contains chromosome information
+binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")
 
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
+for(i in 1:22){
+  #reducing the whole genome data to only specific chromosome
+	reduce_chr <- paste0("chr", i)
+	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]
 
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x25_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p25kb_k562 <- ggplot(x25_k562, aes(y=IR, x=factor(CB, levels = unique(x25_k562$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  IR_K562_25kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
+}
 
@@
 ```{r}
-train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/test.rds")
+IR_K562_50kb <- numeric(22)
 
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
+#reading in whole genome data
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/K562_50kb.rds")
+#reading in bin data on the whole genome that contains chromosome information
+binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")
 
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
+for(i in 1:22){
+  #reducing the whole genome data to only specific chromosome
+	reduce_chr <- paste0("chr", i)
+	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]
 
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
-
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
-
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
-
-x50_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
-
-p50kb_k562 <- ggplot(x50_k562, aes(y=IR, x=factor(CB, levels = unique(x50_k562$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15, 
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+  IR_K562_50kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
+}
 
@@
 ```{r}
-train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
-test <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/test.rds")
+IR_K562_100kb <- numeric(22)
 
-set.seed(123)
-sampids <- sample(which(train$y=="No"),
-                        length(which(train$y=="Yes")),
-                        replace = FALSE)
-data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
-                           train[sampids,])
+#reading in whole genome data
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/K562_100kb.rds")
+#reading in bin data on the whole genome that contains chromosome information
+binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")
 
-set.seed(123)		
-sampids <- sample(which(train$y=="Yes"),
-                        length(which(train$y=="No")),
-                        replace = TRUE)
-data.ros <- rbind.data.frame(train[which(train$y=="No"),],
-                           train[sampids,])
+for(i in 1:22){
+  #reducing the whole genome data to only specific chromosome
+	reduce_chr <- paste0("chr", i)
+	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]
 
-set.seed(123)
-data.sm <- SMOTE(y ~ ., 
-                     data=train, 
-                     perc.over = 100, 
-                     perc.under = 200)
+  IR_K562_100kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
+}
 
-names(train)[-1] <- gsub("-","_",names(train)[-1])
-data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data
+```
 
-#set.seed(123)
-#n <- 1000
-#nr <- nrow(train)
-#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
-#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
-#medoids <- list(as.numeric(),length(splitdat))
-#for(i in 1:length(splitdat)){
-#  print(i)
-#  data <- splitdat[[i]]
-#  majority <- data[which(data$y=="No"),-1]
-#  minnum <- length(which(data$y=="Yes"))
-# 
-#  pam.med <- pam(majority, k = minnum, diss = FALSE,
-#                 metric = "manhattan", 
-#                 #medoids = NULL, 
-#                 #stand = FALSE, 
-#                 cluster.only = FALSE,
-#                 do.swap = TRUE,
-#                 keep.diss = FALSE,
-#                 keep.data = FALSE,
-#                 pamonce = FALSE, trace.lev = 2)
-#  
-#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
-#  
-#}
-#medoids <- unlist(medoids)
-#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
-#                               train[which(train$y=="Yes"),])
+# Combined
 
-x100_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
-					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
-					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
-					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
-					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
-					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
-					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
-					  #length(data.km$y[which(data.km$y=="No")]), 
-					  #length(data.km$y[which(data.km$y=="Yes")])),
-			    CB = c("Complete",
-					   "Train",
-					   "Test",
-					   "Under-Sampling",
-					   "Over-Sampling",
-					   "SMOTE",
-					   "ROSE"))
+```{r}
+irtab <- data.frame(IR = c(IR_gm12878_10kb,
+                                 IR_gm12878_25kb,
+                                 IR_gm12878_50kb,
+                                 IR_gm12878_100kb,
+                                 IR_K562_10kb,
+                                 IR_K562_25kb,
+                                 IR_K562_50kb,
+                                 IR_K562_100kb),
+                          CL = c(rep("GM12878", 22*4), rep("K562", 22*4)),
+                          Resolution = rep(c("10 kb", "25 kb", "50 kb", "100 kb"), 2),
+                          Chromosome = rep(paste0("CHR",1:22),4)
+                          )
 
-p100kb_k562 <- ggplot(x100_k562, aes(y=IR, x=factor(CB, levels = unique(x100_k562$CB)))) + 
-  geom_bar( stat="identity") +
-  ylab("Imbalance Ratio")+
-  xlab("")+
-  #ylim(0, 30000)+
+irtab$CL <- factor(irtab$CL, levels=c("GM12878", "K562"))
+irtab$Resolution <- factor(irtab$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
+irtab$Chromosome <- factor(irtab$Chromosome, levels=paste0("CHR",1:22))
+
+irtab <- irtab[-which(irtab$Chromosome=="CHR9"),]
+
+ggplot(irtab, aes(x = Resolution, y = IR, fill = Resolution, color = Resolution)) +
+  geom_boxplot(#fill = fill, 
+               #colour = line,
+               outlier.colour = "black") +
+  facet_grid(~ CL) +
+  guides(fill=FALSE, color=FALSE) +
+  xlab("Resolution") +
+  ylab("Imbalance Ratio") +
+  theme_minimal() +
   theme_bw() +
-  #guides(fill=FALSE)+
   theme(axis.text.x = element_text(size=15,
@@
         axis.text.y = element_text(size = 15),
-        #axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15))
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        strip.text.x = element_text(size = 15))
 
 ```
-
-##Combined
-```{r}
-
-IR=c(x10$IR[x10$CB=="Complete"],
-                              x25$IR[x25$CB=="Complete"],
-                              x50$IR[x50$CB=="Complete"],
-                              x100$IR[x100$CB=="Complete"],
-                              x10_k562$IR[x10_k562$CB=="Complete"], 
-                              x25_k562$IR[x25_k562$CB=="Complete"],
-                              x50_k562$IR[x50_k562$CB=="Complete"],
-                              x100_k562$IR[x100_k562$CB=="Complete"])
-CL <- c(rep("GM12878", 4), 
-                  rep("K562", 4))
-Resolution <- c(rep(c("10 kb", "25 kb", "50 kb", "100 kb"), 2))
-
-allirdata <- cbind.data.frame(IR, CL, Resolution)
-allirdata$CL <- factor(allirdata$CL, levels=c("GM12878", "K562"))
-allirdata$Resolution <- factor(allirdata$Resolution, c("10 kb", "25 kb", "50 kb", "100 kb"))
-
-allirplots <- ggplot(allirdata, aes(x = Resolution, y = IR,fill = CL)) + 
-  geom_bar(position = "dodge", stat="identity") + 
-  ylab("Imbalance Ratio") +
-  xlab("Resolution") +
-  #scale_fill_manual(name="Cell Line", values=c("red", "blue"))+
-  labs(fill="Cell Line")+
-  theme_bw() +
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=10),
-        axis.text.y = element_text(size = 10),
-        axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```

### 2019-05-08 Manuscript/Figures/figure_legends.Rmd
cleaning up legends
editted figure legends

@@
 
-**Figure 4.
-Resolution-specific data summaries.** (A) The total number of genomic bins created by partitioning the linear genome into unit intervals corresponding to the resolution of the relevant domain data for the GM12878 (red) and K562 (blue) cell line.
-(B) Subsequent imbalance ratios created when labelling bin class, defined as the ratio of the number of bins that overlapped with a flanked TAD boundary to the number of bins that did not overlap with a flanked TAD boundary.
+**Imbalance Ratios.** Boxplots illustrating the variations in imbalance ratios (IR) across cell line and resolution.
+IR was calculated by dividing the number of chromosome-specific genomic bins that overlapped with flanked TAD boundaries by the number of chromosome-specific genomic bins that did not.
 
@@
 
+<!--
 **Figure 7.
@@
 That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
+-->
 

### 2019-05-08 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-Replicate Hi-C data for the GM12878 and K562 cell lines were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1).
+Biological replicate Hi-C data for the GM12878 and K562 cell lines were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1).
 The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
-For each of the 4 data resolutions, a total of 8008, 4869, 2449, and 1075 unique TADs were extracted from the GM12878 cell line, and a total of 5828, 4097, 2181, and 986 unique TADs were extracted from the K562 cell line.
-The TADs were distributed throughput the autosomal chromosomes, with larger chromosomes containing more TADs (Supplementary Figure 14; Supplementary Table 8).
-The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained.
-TAD boundaries called on Chromosome 9 were omitted from all downstream analysis, for both cell lines, due to the sparcity of the contact matrix at the 10 kb resolution for the K562 cell line.
+<!--For each of the 4 data resolutions, a total of 8008, 4869, 2449, and 1075 unique TADs were extracted from the GM12878 cell line, and a total of 5828, 4097, 2181, and 986 unique TADs were extracted from the K562 cell line.
+The TADs were distributed throughput the autosomal chromosomes, with larger chromosomes containing more TADs (Supplementary Figure 14; Supplementary Table 8).--> The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained throughput the autosomal chromosomes.
+TAD boundaries called on Chromosome 9 were omitted from all downstream analyses, for both cell lines, due to the sparcity of the contact matrix at the 10 kb resolution for the K562 cell line.
 
@@
 
-Results showed that the imbalance ratios were well below acceptable thresholds for both cell lines, and across the 4 resolutions (Supplementary Table 9 ???SDs will come with more chromosomes).
+Results showed that the imbalance ratios were well below acceptable thresholds for both cell lines, and across the 4 resolutions .
 The low imbalance ratios indicated a wide disparity between the number of genomic bins that overlaped with a flanked TAD boundary and the much larger number that did not.
-While resolution certainly played a role in determining the number of observations included in datasets used in downstream modeling, as it determines the width of genomic bins and larger widths (lower resolutions) created less bins, we found that there was very little variation in imbalance ratios across resolution (Supplementary Figure 16 ???variation will come with additional chrs).
+While resolution certainly played a role in determining the number of observations included in datasets used in downstream modeling, as it determines the width of genomic bins and larger widths (lower resolutions) created less bins, we found that there was very little variation in imbalance ratios across resolution.
 

### 2019-05-08 Manuscript/manuscript.Rmd
renamed figure, referenced in manuscript

@@
 
-Results showed that the imbalance ratios were well below acceptable thresholds for both cell lines, and across the 4 resolutions .
+Results showed that the imbalance ratios were well below acceptable thresholds for both cell lines, and across the 4 resolutions (Figure 4).
 The low imbalance ratios indicated a wide disparity between the number of genomic bins that overlaped with a flanked TAD boundary and the much larger number that did not.
-While resolution certainly played a role in determining the number of observations included in datasets used in downstream modeling, as it determines the width of genomic bins and larger widths (lower resolutions) created less bins, we found that there was very little variation in imbalance ratios across resolution.
+Likewise, there was very little variation in imbalance ratios across resolution.
+The low IR indicate a necessary re-sampling technique that will suitably balance the majority and minority classes.
 

### 2019-05-09 Manuscript/Figures/figure_legends.Rmd
renamed figure, referenced in manuscript
added model perfs figures with all chromosomes; editted legends

@@
 
-**Imbalance Ratios.** Boxplots illustrating the variations in imbalance ratios (IR) across cell line and resolution.
+**Figure 4.
+Imbalance Ratios.** Boxplots illustrating the variations in imbalance ratios (IR) across cell line and resolution.
 IR was calculated by dividing the number of chromosome-specific genomic bins that overlapped with flanked TAD boundaries by the number of chromosome-specific genomic bins that did not.
@@
 **Figure 5.
-Comparing ensemble system specific model performances for GM12878.** Performances, separated by F1-Score and MCC, of random forest classification models built on each of the 3 predictor types: OC (A), OP (B), and Distance (C).
-Within each predictor type, and across resolution, F1-Scores and MCCs metrics were recorded for models subsequently implemented on re-sampled data using the 4 re-sampling techniques: None (red), ROS (green), RUS (blue), and SMOTE (purple).
+Comparing ensemble system specific model performances for GM12878.** Performances of random forest classification models built on each of the 3 predictor types: OC (A), OP (B), and Distance (C).
+Within each predictor type, and across resolution, MCCs metrics were recorded for models subsequently implemented on re-sampled data using the 4 re-sampling techniques: None (red), ROS (green), RUS (blue), and SMOTE (purple).
+Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.
 

### 2019-05-09 Manuscript/Supplementary/supplementary_legends.Rmd
added model perfs figures with all chromosomes; editted legends

@@
 
-**Supplementary Table 7.
-Optimal alpha and lambda penalization parameters.** The tuned alpha and lambda penalization parameter terms after performing 10-fold cross validated elastic-net regularization specific to cell line, resolution, re-sampling technique, and predictor type.
-
 **Supplementary Figure 10.
 Comparing ensemble system specific model performances for K562.** Performances of random forest classification models built on each of the 3 predictor types: OC (A), OP (B), and Distance (C).
-Within each predictor type, and across resolution, F1-Scores and MCCs metrics were recorded for models subsequently implemented on re-sampled data using the 4 re-sampling techniques: None (red), ROS (green), RUS (blue), and SMOTE (purple).
+Within each predictor type, and across resolution, MCCs metrics were recorded for models subsequently implemented on re-sampled data using the 4 re-sampling techniques: None (red), ROS (green), RUS (blue), and SMOTE (purple).
+Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.
 

### 2019-05-09 Scripts/evaluating_model_performances.Rmd
editted results script

--- 2019-04-08 Scripts/evaluating_model_performances.Rmd
@@
 
-#Barplots of performance metrics for models
-
-## GM12878
-
-###10kb
-
-```{r}
-#OC
-##None
-rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_10kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_10kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_10kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_10kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_10kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-all_rfperfs_gm12878_10kb <- data.frame(Resampling=c(rep("None", 18),
-                                       rep("RUS", 18),
-                                       rep("ROS", 18),
-                                       rep("SMOTE", 18)),
-                          Predictor=rep(c(rep("OC", 6),
-                                      rep("OP", 6),
-                                      rep("Distance", 6)),4),
-                          Metric=rep(c("Accuracy", 
-                                       "AUPRC", 
-                                       "F1-Score", 
-                                       "MCC",
-                                       "Informedness",
-                                       "Balanced Acc"), 12))
-
-all_rfperfs_gm12878_10kb$Performance <- c(round(rfperf_gm12878_10kb_none_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_10kb_none_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_10kb_none_oc[16,2],2), #f1
-                                round(rfperf_gm12878_10kb_none_oc[15,2],2), #mcc
-								round(rfperf_gm12878_10kb_none_oc[18,2],2), #youden
-								(round(rfperf_gm12878_10kb_none_oc[6,2],2) + round(rfperf_gm12878_10kb_none_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_10kb_none_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_10kb_none_op[19,2],2), #auprc
-                                round(rfperf_gm12878_10kb_none_op[16,2],2), #f1
-                                round(rfperf_gm12878_10kb_none_op[15,2],2), #mcc
-								round(rfperf_gm12878_10kb_none_op[18,2],2), #youden
-								(round(rfperf_gm12878_10kb_none_op[6,2],2) + round(rfperf_gm12878_10kb_none_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_10kb_none_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_10kb_none_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_10kb_none_dist[16,2],2), #f1
-                                round(rfperf_gm12878_10kb_none_dist[15,2],2), #mcc
-								round(rfperf_gm12878_10kb_none_dist[18,2],2), #youden
-								(round(rfperf_gm12878_10kb_none_dist[6,2],2) + round(rfperf_gm12878_10kb_none_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_10kb_rus_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_10kb_rus_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_10kb_rus_oc[16,2],2), #f1
-                                round(rfperf_gm12878_10kb_rus_oc[15,2],2), #mcc
-								round(rfperf_gm12878_10kb_rus_oc[18,2],2), #youden
-								(round(rfperf_gm12878_10kb_rus_oc[6,2],2) + round(rfperf_gm12878_10kb_rus_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_10kb_rus_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_10kb_rus_op[19,2],2), #auprc
-                                round(rfperf_gm12878_10kb_rus_op[16,2],2), #f1
-                                round(rfperf_gm12878_10kb_rus_op[15,2],2), #mcc
-								round(rfperf_gm12878_10kb_rus_op[18,2],2), #youden
-								(round(rfperf_gm12878_10kb_rus_op[6,2],2) + round(rfperf_gm12878_10kb_rus_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_10kb_rus_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_10kb_rus_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_10kb_rus_dist[16,2],2), #f1
-                                round(rfperf_gm12878_10kb_rus_dist[15,2],2), #mcc
-								round(rfperf_gm12878_10kb_rus_dist[18,2],2), #youden
-								(round(rfperf_gm12878_10kb_rus_dist[6,2],2) + round(rfperf_gm12878_10kb_rus_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_10kb_ros_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_10kb_ros_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_10kb_ros_oc[16,2],2), #f1
-                                round(rfperf_gm12878_10kb_ros_oc[15,2],2), #mcc
-								round(rfperf_gm12878_10kb_ros_oc[18,2],2), #youden
-								(round(rfperf_gm12878_10kb_ros_oc[6,2],2) + round(rfperf_gm12878_10kb_ros_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_10kb_ros_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_10kb_ros_op[19,2],2), #auprc
-                                round(rfperf_gm12878_10kb_ros_op[16,2],2), #f1
-                                round(rfperf_gm12878_10kb_ros_op[15,2],2), #mcc
-								round(rfperf_gm12878_10kb_ros_op[18,2],2), #youden
-								(round(rfperf_gm12878_10kb_ros_op[6,2],2) + round(rfperf_gm12878_10kb_ros_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_10kb_ros_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_10kb_ros_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_10kb_ros_dist[16,2],2), #f1
-                                round(rfperf_gm12878_10kb_ros_dist[15,2],2), #mcc
-								round(rfperf_gm12878_10kb_ros_dist[18,2],2), #youden
-								(round(rfperf_gm12878_10kb_ros_dist[6,2],2) + round(rfperf_gm12878_10kb_ros_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_10kb_smote_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_10kb_smote_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_10kb_smote_oc[16,2],2), #f1
-                                round(rfperf_gm12878_10kb_smote_oc[15,2],2), #mcc
-								round(rfperf_gm12878_10kb_smote_oc[18,2],2), #youden
-								(round(rfperf_gm12878_10kb_smote_oc[6,2],2) + round(rfperf_gm12878_10kb_smote_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_10kb_smote_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_10kb_smote_op[19,2],2), #auprc
-                                round(rfperf_gm12878_10kb_smote_op[16,2],2), #f1
-                                round(rfperf_gm12878_10kb_smote_op[15,2],2), #mcc
-								round(rfperf_gm12878_10kb_smote_op[18,2],2), #youden
-								(round(rfperf_gm12878_10kb_smote_op[6,2],2) + round(rfperf_gm12878_10kb_smote_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_10kb_smote_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_10kb_smote_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_10kb_smote_dist[16,2],2), #f1
-                                round(rfperf_gm12878_10kb_smote_dist[15,2],2), #mcc
-								round(rfperf_gm12878_10kb_smote_dist[18,2],2), #youden
-								(round(rfperf_gm12878_10kb_smote_dist[6,2],2) + round(rfperf_gm12878_10kb_smote_dist[7,2],2))/2 #balanced accuracy
-								)
-all_rfperfs_gm12878_10kb$Resampling <- factor(all_rfperfs_gm12878_10kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
-all_rfperfs_gm12878_10kb$Predictor <- factor(all_rfperfs_gm12878_10kb$Predictor, levels = c("OC", "OP", "Distance"))
-all_rfperfs_gm12878_10kb$Metric <- factor(all_rfperfs_gm12878_10kb$Metric, levels = c("Accuracy",
-                                                                                      "AUPRC",
-                                                                                      "F1-Score",
-                                                                                      "MCC",
-                                                                                      "Informedness",
-                                                                                      "Balanced Acc"))
-
-#comparing only f1 and mcc and balanced acc
-
-ggplot(all_rfperfs_gm12878_10kb[which(all_rfperfs_gm12878_10kb$Metric=="F1-Score" |
-                                               all_rfperfs_gm12878_10kb$Metric=="MCC" |
-                                        all_rfperfs_gm12878_10kb$Metric=="Balanced Acc"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-###25kb
-
-```{r}
-#OC
-##None
-rfperf_gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_gm12878_25kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_25kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_25kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_25kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_gm12878_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_25kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_25kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_25kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-all_rfperfs_gm12878_25kb <- data.frame(Resampling=c(rep("None", 18),
-                                       rep("RUS", 18),
-                                       rep("ROS", 18),
-                                       rep("SMOTE", 18)),
-                          Predictor=rep(c(rep("OC", 6),
-                                      rep("OP", 6),
-                                      rep("Distance", 6)),4),
-                          Metric=rep(c("Accuracy", 
-                                       "AUPRC", 
-                                       "F1-Score", 
-                                       "MCC",
-                                       "Informedness",
-                                       "Balanced Acc"), 12))
-
-all_rfperfs_gm12878_25kb$Performance <- c(round(rfperf_gm12878_25kb_none_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_25kb_none_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_25kb_none_oc[16,2],2), #f1
-                                round(rfperf_gm12878_25kb_none_oc[15,2],2), #mcc
-								round(rfperf_gm12878_25kb_none_oc[18,2],2), #youden
-								(round(rfperf_gm12878_25kb_none_oc[6,2],2) + round(rfperf_gm12878_25kb_none_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_25kb_none_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_25kb_none_op[19,2],2), #auprc
-                                round(rfperf_gm12878_25kb_none_op[16,2],2), #f1
-                                round(rfperf_gm12878_25kb_none_op[15,2],2), #mcc
-								round(rfperf_gm12878_25kb_none_op[18,2],2), #youden
-								(round(rfperf_gm12878_25kb_none_op[6,2],2) + round(rfperf_gm12878_25kb_none_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_25kb_none_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_25kb_none_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_25kb_none_dist[16,2],2), #f1
-                                round(rfperf_gm12878_25kb_none_dist[15,2],2), #mcc
-								round(rfperf_gm12878_25kb_none_dist[18,2],2), #youden
-								(round(rfperf_gm12878_25kb_none_dist[6,2],2) + round(rfperf_gm12878_25kb_none_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_25kb_rus_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_25kb_rus_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_25kb_rus_oc[16,2],2), #f1
-                                round(rfperf_gm12878_25kb_rus_oc[15,2],2), #mcc
-								round(rfperf_gm12878_25kb_rus_oc[18,2],2), #youden
-								(round(rfperf_gm12878_25kb_rus_oc[6,2],2) + round(rfperf_gm12878_25kb_rus_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_25kb_rus_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_25kb_rus_op[19,2],2), #auprc
-                                round(rfperf_gm12878_25kb_rus_op[16,2],2), #f1
-                                round(rfperf_gm12878_25kb_rus_op[15,2],2), #mcc
-								round(rfperf_gm12878_25kb_rus_op[18,2],2), #youden
-								(round(rfperf_gm12878_25kb_rus_op[6,2],2) + round(rfperf_gm12878_25kb_rus_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_25kb_rus_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_25kb_rus_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_25kb_rus_dist[16,2],2), #f1
-                                round(rfperf_gm12878_25kb_rus_dist[15,2],2), #mcc
-								round(rfperf_gm12878_25kb_rus_dist[18,2],2), #youden
-								(round(rfperf_gm12878_25kb_rus_dist[6,2],2) + round(rfperf_gm12878_25kb_rus_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_25kb_ros_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_25kb_ros_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_25kb_ros_oc[16,2],2), #f1
-                                round(rfperf_gm12878_25kb_ros_oc[15,2],2), #mcc
-								round(rfperf_gm12878_25kb_ros_oc[18,2],2), #youden
-								(round(rfperf_gm12878_25kb_ros_oc[6,2],2) + round(rfperf_gm12878_25kb_ros_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_25kb_ros_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_25kb_ros_op[19,2],2), #auprc
-                                round(rfperf_gm12878_25kb_ros_op[16,2],2), #f1
-                                round(rfperf_gm12878_25kb_ros_op[15,2],2), #mcc
-								round(rfperf_gm12878_25kb_ros_op[18,2],2), #youden
-								(round(rfperf_gm12878_25kb_ros_op[6,2],2) + round(rfperf_gm12878_25kb_ros_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_25kb_ros_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_25kb_ros_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_25kb_ros_dist[16,2],2), #f1
-                                round(rfperf_gm12878_25kb_ros_dist[15,2],2), #mcc
-								round(rfperf_gm12878_25kb_ros_dist[18,2],2), #youden
-								(round(rfperf_gm12878_25kb_ros_dist[6,2],2) + round(rfperf_gm12878_25kb_ros_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_25kb_smote_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_25kb_smote_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_25kb_smote_oc[16,2],2), #f1
-                                round(rfperf_gm12878_25kb_smote_oc[15,2],2), #mcc
-								round(rfperf_gm12878_25kb_smote_oc[18,2],2), #youden
-								(round(rfperf_gm12878_25kb_smote_oc[6,2],2) + round(rfperf_gm12878_25kb_smote_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_25kb_smote_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_25kb_smote_op[19,2],2), #auprc
-                                round(rfperf_gm12878_25kb_smote_op[16,2],2), #f1
-                                round(rfperf_gm12878_25kb_smote_op[15,2],2), #mcc
-								round(rfperf_gm12878_25kb_smote_op[18,2],2), #youden
-								(round(rfperf_gm12878_25kb_smote_op[6,2],2) + round(rfperf_gm12878_25kb_smote_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_25kb_smote_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_25kb_smote_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_25kb_smote_dist[16,2],2), #f1
-                                round(rfperf_gm12878_25kb_smote_dist[15,2],2), #mcc
-								round(rfperf_gm12878_25kb_smote_dist[18,2],2), #youden
-								(round(rfperf_gm12878_25kb_smote_dist[6,2],2) + round(rfperf_gm12878_25kb_smote_dist[7,2],2))/2 #balanced accuracy
-								)
-all_rfperfs_gm12878_25kb$Resampling <- factor(all_rfperfs_gm12878_25kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
-all_rfperfs_gm12878_25kb$Predictor <- factor(all_rfperfs_gm12878_25kb$Predictor, levels = c("OC", "OP", "Distance"))
-all_rfperfs_gm12878_25kb$Metric <- factor(all_rfperfs_gm12878_25kb$Metric, levels = c("Accuracy",
-                                                                                      "AUPRC",
-                                                                                      "F1-Score",
-                                                                                      "MCC",
-                                                                                      "Informedness",
-                                                                                      "Balanced Acc"))
-
-#comparing only f1 and mcc and balanced acc
-
-ggplot(all_rfperfs_gm12878_25kb[which(all_rfperfs_gm12878_25kb$Metric=="F1-Score" |
-                                               all_rfperfs_gm12878_25kb$Metric=="MCC" |
-                                        all_rfperfs_gm12878_25kb$Metric=="Balanced Acc"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-###50kb
-
-```{r}
-#OC
-##None
-rfperf_gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_gm12878_50kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_50kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_50kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_50kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_gm12878_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_50kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_50kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_50kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-all_rfperfs_gm12878_50kb <- data.frame(Resampling=c(rep("None", 18),
-                                       rep("RUS", 18),
-                                       rep("ROS", 18),
-                                       rep("SMOTE", 18)),
-                          Predictor=rep(c(rep("OC", 6),
-                                      rep("OP", 6),
-                                      rep("Distance", 6)),4),
-                          Metric=rep(c("Accuracy", 
-                                       "AUPRC", 
-                                       "F1-Score", 
-                                       "MCC",
-                                       "Informedness",
-                                       "Balanced Acc"), 12))
-
-all_rfperfs_gm12878_50kb$Performance <- c(round(rfperf_gm12878_50kb_none_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_50kb_none_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_50kb_none_oc[16,2],2), #f1
-                                round(rfperf_gm12878_50kb_none_oc[15,2],2), #mcc
-								round(rfperf_gm12878_50kb_none_oc[18,2],2), #youden
-								(round(rfperf_gm12878_50kb_none_oc[6,2],2) + round(rfperf_gm12878_50kb_none_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_50kb_none_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_50kb_none_op[19,2],2), #auprc
-                                round(rfperf_gm12878_50kb_none_op[16,2],2), #f1
-                                round(rfperf_gm12878_50kb_none_op[15,2],2), #mcc
-								round(rfperf_gm12878_50kb_none_op[18,2],2), #youden
-								(round(rfperf_gm12878_50kb_none_op[6,2],2) + round(rfperf_gm12878_50kb_none_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_50kb_none_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_50kb_none_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_50kb_none_dist[16,2],2), #f1
-                                round(rfperf_gm12878_50kb_none_dist[15,2],2), #mcc
-								round(rfperf_gm12878_50kb_none_dist[18,2],2), #youden
-								(round(rfperf_gm12878_50kb_none_dist[6,2],2) + round(rfperf_gm12878_50kb_none_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_50kb_rus_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_50kb_rus_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_50kb_rus_oc[16,2],2), #f1
-                                round(rfperf_gm12878_50kb_rus_oc[15,2],2), #mcc
-								round(rfperf_gm12878_50kb_rus_oc[18,2],2), #youden
-								(round(rfperf_gm12878_50kb_rus_oc[6,2],2) + round(rfperf_gm12878_50kb_rus_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_50kb_rus_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_50kb_rus_op[19,2],2), #auprc
-                                round(rfperf_gm12878_50kb_rus_op[16,2],2), #f1
-                                round(rfperf_gm12878_50kb_rus_op[15,2],2), #mcc
-								round(rfperf_gm12878_50kb_rus_op[18,2],2), #youden
-								(round(rfperf_gm12878_50kb_rus_op[6,2],2) + round(rfperf_gm12878_50kb_rus_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_50kb_rus_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_50kb_rus_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_50kb_rus_dist[16,2],2), #f1
-                                round(rfperf_gm12878_50kb_rus_dist[15,2],2), #mcc
-								round(rfperf_gm12878_50kb_rus_dist[18,2],2), #youden
-								(round(rfperf_gm12878_50kb_rus_dist[6,2],2) + round(rfperf_gm12878_50kb_rus_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_50kb_ros_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_50kb_ros_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_50kb_ros_oc[16,2],2), #f1
-                                round(rfperf_gm12878_50kb_ros_oc[15,2],2), #mcc
-								round(rfperf_gm12878_50kb_ros_oc[18,2],2), #youden
-								(round(rfperf_gm12878_50kb_ros_oc[6,2],2) + round(rfperf_gm12878_50kb_ros_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_50kb_ros_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_50kb_ros_op[19,2],2), #auprc
-                                round(rfperf_gm12878_50kb_ros_op[16,2],2), #f1
-                                round(rfperf_gm12878_50kb_ros_op[15,2],2), #mcc
-								round(rfperf_gm12878_50kb_ros_op[18,2],2), #youden
-								(round(rfperf_gm12878_50kb_ros_op[6,2],2) + round(rfperf_gm12878_50kb_ros_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_50kb_ros_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_50kb_ros_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_50kb_ros_dist[16,2],2), #f1
-                                round(rfperf_gm12878_50kb_ros_dist[15,2],2), #mcc
-								round(rfperf_gm12878_50kb_ros_dist[18,2],2), #youden
-								(round(rfperf_gm12878_50kb_ros_dist[6,2],2) + round(rfperf_gm12878_50kb_ros_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_50kb_smote_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_50kb_smote_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_50kb_smote_oc[16,2],2), #f1
-                                round(rfperf_gm12878_50kb_smote_oc[15,2],2), #mcc
-								round(rfperf_gm12878_50kb_smote_oc[18,2],2), #youden
-								(round(rfperf_gm12878_50kb_smote_oc[6,2],2) + round(rfperf_gm12878_50kb_smote_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_50kb_smote_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_50kb_smote_op[19,2],2), #auprc
-                                round(rfperf_gm12878_50kb_smote_op[16,2],2), #f1
-                                round(rfperf_gm12878_50kb_smote_op[15,2],2), #mcc
-								round(rfperf_gm12878_50kb_smote_op[18,2],2), #youden
-								(round(rfperf_gm12878_50kb_smote_op[6,2],2) + round(rfperf_gm12878_50kb_smote_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_50kb_smote_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_50kb_smote_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_50kb_smote_dist[16,2],2), #f1
-                                round(rfperf_gm12878_50kb_smote_dist[15,2],2), #mcc
-								round(rfperf_gm12878_50kb_smote_dist[18,2],2), #youden
-								(round(rfperf_gm12878_50kb_smote_dist[6,2],2) + round(rfperf_gm12878_50kb_smote_dist[7,2],2))/2 #balanced accuracy
-								)
-all_rfperfs_gm12878_50kb$Resampling <- factor(all_rfperfs_gm12878_50kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
-all_rfperfs_gm12878_50kb$Predictor <- factor(all_rfperfs_gm12878_50kb$Predictor, levels = c("OC", "OP", "Distance"))
-all_rfperfs_gm12878_50kb$Metric <- factor(all_rfperfs_gm12878_50kb$Metric, levels = c("Accuracy",
-                                                                                      "AUPRC",
-                                                                                      "F1-Score",
-                                                                                      "MCC",
-                                                                                      "Informedness",
-                                                                                      "Balanced Acc"))
-
-#comparing only f1 and mcc and balanced acc
-
-ggplot(all_rfperfs_gm12878_50kb[which(all_rfperfs_gm12878_50kb$Metric=="F1-Score" |
-                                               all_rfperfs_gm12878_50kb$Metric=="MCC" |
-                                        all_rfperfs_gm12878_50kb$Metric=="Balanced Acc"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-###100kb
-
-```{r}
-#OC
-##None
-rfperf_gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_gm12878_100kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_100kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_100kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_100kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_gm12878_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_gm12878_100kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_gm12878_100kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_gm12878_100kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-all_rfperfs_gm12878_100kb <- data.frame(Resampling=c(rep("None", 18),
-                                       rep("RUS", 18),
-                                       rep("ROS", 18),
-                                       rep("SMOTE", 18)),
-                          Predictor=rep(c(rep("OC", 6),
-                                      rep("OP", 6),
-                                      rep("Distance", 6)),4),
-                          Metric=rep(c("Accuracy", 
-                                       "AUPRC", 
-                                       "F1-Score", 
-                                       "MCC",
-                                       "Informedness",
-                                       "Balanced Acc"), 12))
-
-all_rfperfs_gm12878_100kb$Performance <- c(round(rfperf_gm12878_100kb_none_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_100kb_none_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_100kb_none_oc[16,2],2), #f1
-                                round(rfperf_gm12878_100kb_none_oc[15,2],2), #mcc
-								round(rfperf_gm12878_100kb_none_oc[18,2],2), #youden
-								(round(rfperf_gm12878_100kb_none_oc[6,2],2) + round(rfperf_gm12878_100kb_none_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_100kb_none_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_100kb_none_op[19,2],2), #auprc
-                                round(rfperf_gm12878_100kb_none_op[16,2],2), #f1
-                                round(rfperf_gm12878_100kb_none_op[15,2],2), #mcc
-								round(rfperf_gm12878_100kb_none_op[18,2],2), #youden
-								(round(rfperf_gm12878_100kb_none_op[6,2],2) + round(rfperf_gm12878_100kb_none_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_100kb_none_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_100kb_none_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_100kb_none_dist[16,2],2), #f1
-                                round(rfperf_gm12878_100kb_none_dist[15,2],2), #mcc
-								round(rfperf_gm12878_100kb_none_dist[18,2],2), #youden
-								(round(rfperf_gm12878_100kb_none_dist[6,2],2) + round(rfperf_gm12878_100kb_none_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_100kb_rus_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_100kb_rus_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_100kb_rus_oc[16,2],2), #f1
-                                round(rfperf_gm12878_100kb_rus_oc[15,2],2), #mcc
-								round(rfperf_gm12878_100kb_rus_oc[18,2],2), #youden
-								(round(rfperf_gm12878_100kb_rus_oc[6,2],2) + round(rfperf_gm12878_100kb_rus_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_100kb_rus_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_100kb_rus_op[19,2],2), #auprc
-                                round(rfperf_gm12878_100kb_rus_op[16,2],2), #f1
-                                round(rfperf_gm12878_100kb_rus_op[15,2],2), #mcc
-								round(rfperf_gm12878_100kb_rus_op[18,2],2), #youden
-								(round(rfperf_gm12878_100kb_rus_op[6,2],2) + round(rfperf_gm12878_100kb_rus_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_100kb_rus_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_100kb_rus_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_100kb_rus_dist[16,2],2), #f1
-                                round(rfperf_gm12878_100kb_rus_dist[15,2],2), #mcc
-								round(rfperf_gm12878_100kb_rus_dist[18,2],2), #youden
-								(round(rfperf_gm12878_100kb_rus_dist[6,2],2) + round(rfperf_gm12878_100kb_rus_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_100kb_ros_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_100kb_ros_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_100kb_ros_oc[16,2],2), #f1
-                                round(rfperf_gm12878_100kb_ros_oc[15,2],2), #mcc
-								round(rfperf_gm12878_100kb_ros_oc[18,2],2), #youden
-								(round(rfperf_gm12878_100kb_ros_oc[6,2],2) + round(rfperf_gm12878_100kb_ros_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_100kb_ros_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_100kb_ros_op[19,2],2), #auprc
-                                round(rfperf_gm12878_100kb_ros_op[16,2],2), #f1
-                                round(rfperf_gm12878_100kb_ros_op[15,2],2), #mcc
-								round(rfperf_gm12878_100kb_ros_op[18,2],2), #youden
-								(round(rfperf_gm12878_100kb_ros_op[6,2],2) + round(rfperf_gm12878_100kb_ros_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_100kb_ros_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_100kb_ros_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_100kb_ros_dist[16,2],2), #f1
-                                round(rfperf_gm12878_100kb_ros_dist[15,2],2), #mcc
-								round(rfperf_gm12878_100kb_ros_dist[18,2],2), #youden
-								(round(rfperf_gm12878_100kb_ros_dist[6,2],2) + round(rfperf_gm12878_100kb_ros_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_100kb_smote_oc[9,2],2), #accuracy
-                                round(rfperf_gm12878_100kb_smote_oc[19,2],2), #auprc
-                                round(rfperf_gm12878_100kb_smote_oc[16,2],2), #f1
-                                round(rfperf_gm12878_100kb_smote_oc[15,2],2), #mcc
-								round(rfperf_gm12878_100kb_smote_oc[18,2],2), #youden
-								(round(rfperf_gm12878_100kb_smote_oc[6,2],2) + round(rfperf_gm12878_100kb_smote_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_gm12878_100kb_smote_op[9,2],2), #accuracy
-                                round(rfperf_gm12878_100kb_smote_op[19,2],2), #auprc
-                                round(rfperf_gm12878_100kb_smote_op[16,2],2), #f1
-                                round(rfperf_gm12878_100kb_smote_op[15,2],2), #mcc
-								round(rfperf_gm12878_100kb_smote_op[18,2],2), #youden
-								(round(rfperf_gm12878_100kb_smote_op[6,2],2) + round(rfperf_gm12878_100kb_smote_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_gm12878_100kb_smote_dist[9,2],2), #accuracy
-                                round(rfperf_gm12878_100kb_smote_dist[19,2],2), #auprc
-                                round(rfperf_gm12878_100kb_smote_dist[16,2],2), #f1
-                                round(rfperf_gm12878_100kb_smote_dist[15,2],2), #mcc
-								round(rfperf_gm12878_100kb_smote_dist[18,2],2), #youden
-								(round(rfperf_gm12878_100kb_smote_dist[6,2],2) + round(rfperf_gm12878_100kb_smote_dist[7,2],2))/2 #balanced accuracy
-								)
-all_rfperfs_gm12878_100kb$Resampling <- factor(all_rfperfs_gm12878_100kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
-all_rfperfs_gm12878_100kb$Predictor <- factor(all_rfperfs_gm12878_100kb$Predictor, levels = c("OC", "OP", "Distance"))
-all_rfperfs_gm12878_100kb$Metric <- factor(all_rfperfs_gm12878_100kb$Metric, levels = c("Accuracy",
-                                                                                      "AUPRC",
-                                                                                      "F1-Score",
-                                                                                      "MCC",
-                                                                                      "Informedness",
-                                                                                      "Balanced Acc"))
-
-#comparing only f1 and mcc and balanced acc
-
-ggplot(all_rfperfs_gm12878_100kb[which(all_rfperfs_gm12878_100kb$Metric=="F1-Score" |
-                                               all_rfperfs_gm12878_100kb$Metric=="MCC" |
-                                         all_rfperfs_gm12878_100kb$Metric=="Balanced Acc"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-## K562
-
-###10kb
-
-```{r}
-#OC
-##None
-rfperf_K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_K562_10kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_10kb_rus_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_10kb_ros_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_10kb_smote_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_K562_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_10kb_rus_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_10kb_ros_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-all_rfperfs_K562_10kb <- data.frame(Resampling=c(rep("None", 18),
-                                       rep("RUS", 18),
-                                       rep("ROS", 18),
-                                       rep("SMOTE", 18)),
-                          Predictor=rep(c(rep("OC", 6),
-                                      rep("OP", 6),
-                                      rep("Distance", 6)),4),
-                          Metric=rep(c("Accuracy", 
-                                       "AUPRC", 
-                                       "F1-Score", 
-                                       "MCC",
-                                       "Informedness",
-                                       "Balanced Acc"), 12))
-
-all_rfperfs_K562_10kb$Performance <- c(round(rfperf_K562_10kb_none_oc[9,2],2), #accuracy
-                                round(rfperf_K562_10kb_none_oc[19,2],2), #auprc
-                                round(rfperf_K562_10kb_none_oc[16,2],2), #f1
-                                round(rfperf_K562_10kb_none_oc[15,2],2), #mcc
-								round(rfperf_K562_10kb_none_oc[18,2],2), #youden
-								(round(rfperf_K562_10kb_none_oc[6,2],2) + round(rfperf_K562_10kb_none_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_10kb_none_op[9,2],2), #accuracy
-                                round(rfperf_K562_10kb_none_op[19,2],2), #auprc
-                                round(rfperf_K562_10kb_none_op[16,2],2), #f1
-                                round(rfperf_K562_10kb_none_op[15,2],2), #mcc
-								round(rfperf_K562_10kb_none_op[18,2],2), #youden
-								(round(rfperf_K562_10kb_none_op[6,2],2) + round(rfperf_K562_10kb_none_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_10kb_none_dist[9,2],2), #accuracy
-                                round(rfperf_K562_10kb_none_dist[19,2],2), #auprc
-                                round(rfperf_K562_10kb_none_dist[16,2],2), #f1
-                                round(rfperf_K562_10kb_none_dist[15,2],2), #mcc
-								round(rfperf_K562_10kb_none_dist[18,2],2), #youden
-								(round(rfperf_K562_10kb_none_dist[6,2],2) + round(rfperf_K562_10kb_none_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_10kb_rus_oc[9,2],2), #accuracy
-                                round(rfperf_K562_10kb_rus_oc[19,2],2), #auprc
-                                round(rfperf_K562_10kb_rus_oc[16,2],2), #f1
-                                round(rfperf_K562_10kb_rus_oc[15,2],2), #mcc
-								round(rfperf_K562_10kb_rus_oc[18,2],2), #youden
-								(round(rfperf_K562_10kb_rus_oc[6,2],2) + round(rfperf_K562_10kb_rus_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_10kb_rus_op[9,2],2), #accuracy
-                                round(rfperf_K562_10kb_rus_op[19,2],2), #auprc
-                                round(rfperf_K562_10kb_rus_op[16,2],2), #f1
-                                round(rfperf_K562_10kb_rus_op[15,2],2), #mcc
-								round(rfperf_K562_10kb_rus_op[18,2],2), #youden
-								(round(rfperf_K562_10kb_rus_op[6,2],2) + round(rfperf_K562_10kb_rus_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_10kb_rus_dist[9,2],2), #accuracy
-                                round(rfperf_K562_10kb_rus_dist[19,2],2), #auprc
-                                round(rfperf_K562_10kb_rus_dist[16,2],2), #f1
-                                round(rfperf_K562_10kb_rus_dist[15,2],2), #mcc
-								round(rfperf_K562_10kb_rus_dist[18,2],2), #youden
-								(round(rfperf_K562_10kb_rus_dist[6,2],2) + round(rfperf_K562_10kb_rus_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_10kb_ros_oc[9,2],2), #accuracy
-                                round(rfperf_K562_10kb_ros_oc[19,2],2), #auprc
-                                round(rfperf_K562_10kb_ros_oc[16,2],2), #f1
-                                round(rfperf_K562_10kb_ros_oc[15,2],2), #mcc
-								round(rfperf_K562_10kb_ros_oc[18,2],2), #youden
-								(round(rfperf_K562_10kb_ros_oc[6,2],2) + round(rfperf_K562_10kb_ros_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_10kb_ros_op[9,2],2), #accuracy
-                                round(rfperf_K562_10kb_ros_op[19,2],2), #auprc
-                                round(rfperf_K562_10kb_ros_op[16,2],2), #f1
-                                round(rfperf_K562_10kb_ros_op[15,2],2), #mcc
-								round(rfperf_K562_10kb_ros_op[18,2],2), #youden
-								(round(rfperf_K562_10kb_ros_op[6,2],2) + round(rfperf_K562_10kb_ros_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_10kb_ros_dist[9,2],2), #accuracy
-                                round(rfperf_K562_10kb_ros_dist[19,2],2), #auprc
-                                round(rfperf_K562_10kb_ros_dist[16,2],2), #f1
-                                round(rfperf_K562_10kb_ros_dist[15,2],2), #mcc
-								round(rfperf_K562_10kb_ros_dist[18,2],2), #youden
-								(round(rfperf_K562_10kb_ros_dist[6,2],2) + round(rfperf_K562_10kb_ros_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_10kb_smote_oc[9,2],2), #accuracy
-                                round(rfperf_K562_10kb_smote_oc[19,2],2), #auprc
-                                round(rfperf_K562_10kb_smote_oc[16,2],2), #f1
-                                round(rfperf_K562_10kb_smote_oc[15,2],2), #mcc
-								round(rfperf_K562_10kb_smote_oc[18,2],2), #youden
-								(round(rfperf_K562_10kb_smote_oc[6,2],2) + round(rfperf_K562_10kb_smote_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_10kb_smote_op[9,2],2), #accuracy
-                                round(rfperf_K562_10kb_smote_op[19,2],2), #auprc
-                                round(rfperf_K562_10kb_smote_op[16,2],2), #f1
-                                round(rfperf_K562_10kb_smote_op[15,2],2), #mcc
-								round(rfperf_K562_10kb_smote_op[18,2],2), #youden
-								(round(rfperf_K562_10kb_smote_op[6,2],2) + round(rfperf_K562_10kb_smote_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_10kb_smote_dist[9,2],2), #accuracy
-                                round(rfperf_K562_10kb_smote_dist[19,2],2), #auprc
-                                round(rfperf_K562_10kb_smote_dist[16,2],2), #f1
-                                round(rfperf_K562_10kb_smote_dist[15,2],2), #mcc
-								round(rfperf_K562_10kb_smote_dist[18,2],2), #youden
-								(round(rfperf_K562_10kb_smote_dist[6,2],2) + round(rfperf_K562_10kb_smote_dist[7,2],2))/2 #balanced accuracy
-								)
-all_rfperfs_K562_10kb$Resampling <- factor(all_rfperfs_K562_10kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
-all_rfperfs_K562_10kb$Predictor <- factor(all_rfperfs_K562_10kb$Predictor, levels = c("OC", "OP", "Distance"))
-all_rfperfs_K562_10kb$Metric <- factor(all_rfperfs_K562_10kb$Metric, levels = c("Accuracy",
-                                                                                      "AUPRC",
-                                                                                      "F1-Score",
-                                                                                      "MCC",
-                                                                                      "Informedness",
-                                                                                      "Balanced Acc"))
-
-#comparing only f1 and mcc and balanced acc
-
-ggplot(all_rfperfs_K562_10kb[which(all_rfperfs_K562_10kb$Metric=="F1-Score" |
-                                               all_rfperfs_K562_10kb$Metric=="MCC" |
-                                     all_rfperfs_K562_10kb$Metric=="Balanced Acc"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-###25kb
-
-```{r}
-#OC
-##None
-rfperf_K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_K562_25kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_25kb_rus_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_25kb_ros_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_25kb_smote_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_K562_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_25kb_rus_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_25kb_ros_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_25kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-all_rfperfs_K562_25kb <- data.frame(Resampling=c(rep("None", 18),
-                                       rep("RUS", 18),
-                                       rep("ROS", 18),
-                                       rep("SMOTE", 18)),
-                          Predictor=rep(c(rep("OC", 6),
-                                      rep("OP", 6),
-                                      rep("Distance", 6)),4),
-                          Metric=rep(c("Accuracy", 
-                                       "AUPRC", 
-                                       "F1-Score", 
-                                       "MCC",
-                                       "Informedness",
-                                       "Balanced Acc"), 12))
-
-all_rfperfs_K562_25kb$Performance <- c(round(rfperf_K562_25kb_none_oc[9,2],2), #accuracy
-                                round(rfperf_K562_25kb_none_oc[19,2],2), #auprc
-                                round(rfperf_K562_25kb_none_oc[16,2],2), #f1
-                                round(rfperf_K562_25kb_none_oc[15,2],2), #mcc
-								round(rfperf_K562_25kb_none_oc[18,2],2), #youden
-								(round(rfperf_K562_25kb_none_oc[6,2],2) + round(rfperf_K562_25kb_none_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_25kb_none_op[9,2],2), #accuracy
-                                round(rfperf_K562_25kb_none_op[19,2],2), #auprc
-                                round(rfperf_K562_25kb_none_op[16,2],2), #f1
-                                round(rfperf_K562_25kb_none_op[15,2],2), #mcc
-								round(rfperf_K562_25kb_none_op[18,2],2), #youden
-								(round(rfperf_K562_25kb_none_op[6,2],2) + round(rfperf_K562_25kb_none_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_25kb_none_dist[9,2],2), #accuracy
-                                round(rfperf_K562_25kb_none_dist[19,2],2), #auprc
-                                round(rfperf_K562_25kb_none_dist[16,2],2), #f1
-                                round(rfperf_K562_25kb_none_dist[15,2],2), #mcc
-								round(rfperf_K562_25kb_none_dist[18,2],2), #youden
-								(round(rfperf_K562_25kb_none_dist[6,2],2) + round(rfperf_K562_25kb_none_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_25kb_rus_oc[9,2],2), #accuracy
-                                round(rfperf_K562_25kb_rus_oc[19,2],2), #auprc
-                                round(rfperf_K562_25kb_rus_oc[16,2],2), #f1
-                                round(rfperf_K562_25kb_rus_oc[15,2],2), #mcc
-								round(rfperf_K562_25kb_rus_oc[18,2],2), #youden
-								(round(rfperf_K562_25kb_rus_oc[6,2],2) + round(rfperf_K562_25kb_rus_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_25kb_rus_op[9,2],2), #accuracy
-                                round(rfperf_K562_25kb_rus_op[19,2],2), #auprc
-                                round(rfperf_K562_25kb_rus_op[16,2],2), #f1
-                                round(rfperf_K562_25kb_rus_op[15,2],2), #mcc
-								round(rfperf_K562_25kb_rus_op[18,2],2), #youden
-								(round(rfperf_K562_25kb_rus_op[6,2],2) + round(rfperf_K562_25kb_rus_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_25kb_rus_dist[9,2],2), #accuracy
-                                round(rfperf_K562_25kb_rus_dist[19,2],2), #auprc
-                                round(rfperf_K562_25kb_rus_dist[16,2],2), #f1
-                                round(rfperf_K562_25kb_rus_dist[15,2],2), #mcc
-								round(rfperf_K562_25kb_rus_dist[18,2],2), #youden
-								(round(rfperf_K562_25kb_rus_dist[6,2],2) + round(rfperf_K562_25kb_rus_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_25kb_ros_oc[9,2],2), #accuracy
-                                round(rfperf_K562_25kb_ros_oc[19,2],2), #auprc
-                                round(rfperf_K562_25kb_ros_oc[16,2],2), #f1
-                                round(rfperf_K562_25kb_ros_oc[15,2],2), #mcc
-								round(rfperf_K562_25kb_ros_oc[18,2],2), #youden
-								(round(rfperf_K562_25kb_ros_oc[6,2],2) + round(rfperf_K562_25kb_ros_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_25kb_ros_op[9,2],2), #accuracy
-                                round(rfperf_K562_25kb_ros_op[19,2],2), #auprc
-                                round(rfperf_K562_25kb_ros_op[16,2],2), #f1
-                                round(rfperf_K562_25kb_ros_op[15,2],2), #mcc
-								round(rfperf_K562_25kb_ros_op[18,2],2), #youden
-								(round(rfperf_K562_25kb_ros_op[6,2],2) + round(rfperf_K562_25kb_ros_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_25kb_ros_dist[9,2],2), #accuracy
-                                round(rfperf_K562_25kb_ros_dist[19,2],2), #auprc
-                                round(rfperf_K562_25kb_ros_dist[16,2],2), #f1
-                                round(rfperf_K562_25kb_ros_dist[15,2],2), #mcc
-								round(rfperf_K562_25kb_ros_dist[18,2],2), #youden
-								(round(rfperf_K562_25kb_ros_dist[6,2],2) + round(rfperf_K562_25kb_ros_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_25kb_smote_oc[9,2],2), #accuracy
-                                round(rfperf_K562_25kb_smote_oc[19,2],2), #auprc
-                                round(rfperf_K562_25kb_smote_oc[16,2],2), #f1
-                                round(rfperf_K562_25kb_smote_oc[15,2],2), #mcc
-								round(rfperf_K562_25kb_smote_oc[18,2],2), #youden
-								(round(rfperf_K562_25kb_smote_oc[6,2],2) + round(rfperf_K562_25kb_smote_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_25kb_smote_op[9,2],2), #accuracy
-                                round(rfperf_K562_25kb_smote_op[19,2],2), #auprc
-                                round(rfperf_K562_25kb_smote_op[16,2],2), #f1
-                                round(rfperf_K562_25kb_smote_op[15,2],2), #mcc
-								round(rfperf_K562_25kb_smote_op[18,2],2), #youden
-								(round(rfperf_K562_25kb_smote_op[6,2],2) + round(rfperf_K562_25kb_smote_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_25kb_smote_dist[9,2],2), #accuracy
-                                round(rfperf_K562_25kb_smote_dist[19,2],2), #auprc
-                                round(rfperf_K562_25kb_smote_dist[16,2],2), #f1
-                                round(rfperf_K562_25kb_smote_dist[15,2],2), #mcc
-								round(rfperf_K562_25kb_smote_dist[18,2],2), #youden
-								(round(rfperf_K562_25kb_smote_dist[6,2],2) + round(rfperf_K562_25kb_smote_dist[7,2],2))/2 #balanced accuracy
-								)
-all_rfperfs_K562_25kb$Resampling <- factor(all_rfperfs_K562_25kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
-all_rfperfs_K562_25kb$Predictor <- factor(all_rfperfs_K562_25kb$Predictor, levels = c("OC", "OP", "Distance"))
-all_rfperfs_K562_25kb$Metric <- factor(all_rfperfs_K562_25kb$Metric, levels = c("Accuracy",
-                                                                                      "AUPRC",
-                                                                                      "F1-Score",
-                                                                                      "MCC",
-                                                                                      "Informedness",
-                                                                                      "Balanced Acc"))
-
-#comparing only f1 and mcc and balanced acc
-
-ggplot(all_rfperfs_K562_25kb[which(all_rfperfs_K562_25kb$Metric=="F1-Score" |
-                                               all_rfperfs_K562_25kb$Metric=="MCC" |
-                                     all_rfperfs_K562_25kb$Metric=="Balanced Acc"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-###50kb
-
-```{r}
-#OC
-##None
-rfperf_K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_K562_50kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_50kb_rus_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_50kb_ros_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_50kb_smote_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_K562_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_50kb_rus_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_50kb_ros_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_50kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-all_rfperfs_K562_50kb <- data.frame(Resampling=c(rep("None", 18),
-                                       rep("RUS", 18),
-                                       rep("ROS", 18),
-                                       rep("SMOTE", 18)),
-                          Predictor=rep(c(rep("OC", 6),
-                                      rep("OP", 6),
-                                      rep("Distance", 6)),4),
-                          Metric=rep(c("Accuracy", 
-                                       "AUPRC", 
-                                       "F1-Score", 
-                                       "MCC",
-                                       "Informedness",
-                                       "Balanced Acc"), 12))
-
-all_rfperfs_K562_50kb$Performance <- c(round(rfperf_K562_50kb_none_oc[9,2],2), #accuracy
-                                round(rfperf_K562_50kb_none_oc[19,2],2), #auprc
-                                round(rfperf_K562_50kb_none_oc[16,2],2), #f1
-                                round(rfperf_K562_50kb_none_oc[15,2],2), #mcc
-								round(rfperf_K562_50kb_none_oc[18,2],2), #youden
-								(round(rfperf_K562_50kb_none_oc[6,2],2) + round(rfperf_K562_50kb_none_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_50kb_none_op[9,2],2), #accuracy
-                                round(rfperf_K562_50kb_none_op[19,2],2), #auprc
-                                round(rfperf_K562_50kb_none_op[16,2],2), #f1
-                                round(rfperf_K562_50kb_none_op[15,2],2), #mcc
-								round(rfperf_K562_50kb_none_op[18,2],2), #youden
-								(round(rfperf_K562_50kb_none_op[6,2],2) + round(rfperf_K562_50kb_none_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_50kb_none_dist[9,2],2), #accuracy
-                                round(rfperf_K562_50kb_none_dist[19,2],2), #auprc
-                                round(rfperf_K562_50kb_none_dist[16,2],2), #f1
-                                round(rfperf_K562_50kb_none_dist[15,2],2), #mcc
-								round(rfperf_K562_50kb_none_dist[18,2],2), #youden
-								(round(rfperf_K562_50kb_none_dist[6,2],2) + round(rfperf_K562_50kb_none_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_50kb_rus_oc[9,2],2), #accuracy
-                                round(rfperf_K562_50kb_rus_oc[19,2],2), #auprc
-                                round(rfperf_K562_50kb_rus_oc[16,2],2), #f1
-                                round(rfperf_K562_50kb_rus_oc[15,2],2), #mcc
-								round(rfperf_K562_50kb_rus_oc[18,2],2), #youden
-								(round(rfperf_K562_50kb_rus_oc[6,2],2) + round(rfperf_K562_50kb_rus_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_50kb_rus_op[9,2],2), #accuracy
-                                round(rfperf_K562_50kb_rus_op[19,2],2), #auprc
-                                round(rfperf_K562_50kb_rus_op[16,2],2), #f1
-                                round(rfperf_K562_50kb_rus_op[15,2],2), #mcc
-								round(rfperf_K562_50kb_rus_op[18,2],2), #youden
-								(round(rfperf_K562_50kb_rus_op[6,2],2) + round(rfperf_K562_50kb_rus_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_50kb_rus_dist[9,2],2), #accuracy
-                                round(rfperf_K562_50kb_rus_dist[19,2],2), #auprc
-                                round(rfperf_K562_50kb_rus_dist[16,2],2), #f1
-                                round(rfperf_K562_50kb_rus_dist[15,2],2), #mcc
-								round(rfperf_K562_50kb_rus_dist[18,2],2), #youden
-								(round(rfperf_K562_50kb_rus_dist[6,2],2) + round(rfperf_K562_50kb_rus_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_50kb_ros_oc[9,2],2), #accuracy
-                                round(rfperf_K562_50kb_ros_oc[19,2],2), #auprc
-                                round(rfperf_K562_50kb_ros_oc[16,2],2), #f1
-                                round(rfperf_K562_50kb_ros_oc[15,2],2), #mcc
-								round(rfperf_K562_50kb_ros_oc[18,2],2), #youden
-								(round(rfperf_K562_50kb_ros_oc[6,2],2) + round(rfperf_K562_50kb_ros_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_50kb_ros_op[9,2],2), #accuracy
-                                round(rfperf_K562_50kb_ros_op[19,2],2), #auprc
-                                round(rfperf_K562_50kb_ros_op[16,2],2), #f1
-                                round(rfperf_K562_50kb_ros_op[15,2],2), #mcc
-								round(rfperf_K562_50kb_ros_op[18,2],2), #youden
-								(round(rfperf_K562_50kb_ros_op[6,2],2) + round(rfperf_K562_50kb_ros_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_50kb_ros_dist[9,2],2), #accuracy
-                                round(rfperf_K562_50kb_ros_dist[19,2],2), #auprc
-                                round(rfperf_K562_50kb_ros_dist[16,2],2), #f1
-                                round(rfperf_K562_50kb_ros_dist[15,2],2), #mcc
-								round(rfperf_K562_50kb_ros_dist[18,2],2), #youden
-								(round(rfperf_K562_50kb_ros_dist[6,2],2) + round(rfperf_K562_50kb_ros_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_50kb_smote_oc[9,2],2), #accuracy
-                                round(rfperf_K562_50kb_smote_oc[19,2],2), #auprc
-                                round(rfperf_K562_50kb_smote_oc[16,2],2), #f1
-                                round(rfperf_K562_50kb_smote_oc[15,2],2), #mcc
-								round(rfperf_K562_50kb_smote_oc[18,2],2), #youden
-								(round(rfperf_K562_50kb_smote_oc[6,2],2) + round(rfperf_K562_50kb_smote_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_50kb_smote_op[9,2],2), #accuracy
-                                round(rfperf_K562_50kb_smote_op[19,2],2), #auprc
-                                round(rfperf_K562_50kb_smote_op[16,2],2), #f1
-                                round(rfperf_K562_50kb_smote_op[15,2],2), #mcc
-								round(rfperf_K562_50kb_smote_op[18,2],2), #youden
-								(round(rfperf_K562_50kb_smote_op[6,2],2) + round(rfperf_K562_50kb_smote_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_50kb_smote_dist[9,2],2), #accuracy
-                                round(rfperf_K562_50kb_smote_dist[19,2],2), #auprc
-                                round(rfperf_K562_50kb_smote_dist[16,2],2), #f1
-                                round(rfperf_K562_50kb_smote_dist[15,2],2), #mcc
-								round(rfperf_K562_50kb_smote_dist[18,2],2), #youden
-								(round(rfperf_K562_50kb_smote_dist[6,2],2) + round(rfperf_K562_50kb_smote_dist[7,2],2))/2 #balanced accuracy
-								)
-all_rfperfs_K562_50kb$Resampling <- factor(all_rfperfs_K562_50kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
-all_rfperfs_K562_50kb$Predictor <- factor(all_rfperfs_K562_50kb$Predictor, levels = c("OC", "OP", "Distance"))
-all_rfperfs_K562_50kb$Metric <- factor(all_rfperfs_K562_50kb$Metric, levels = c("Accuracy",
-                                                                                      "AUPRC",
-                                                                                      "F1-Score",
-                                                                                      "MCC",
-                                                                                      "Informedness",
-                                                                                      "Balanced Acc"))
-
-#comparing only f1 and mcc and balanced acc
-
-ggplot(all_rfperfs_K562_50kb[which(all_rfperfs_K562_50kb$Metric=="F1-Score" |
-                                               all_rfperfs_K562_50kb$Metric=="MCC" |
-                                     all_rfperfs_K562_50kb$Metric=="Balanced Acc"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-###100kb
-
-```{r}
-#OC
-##None
-rfperf_K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_K562_100kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_100kb_rus_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_100kb_ros_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_100kb_smote_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_K562_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-##RUS
-rfperf_K562_100kb_rus_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-##ROS
-rfperf_K562_100kb_ros_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-##SMOTE
-rfperf_K562_100kb_smote_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-all_rfperfs_K562_100kb <- data.frame(Resampling=c(rep("None", 18),
-                                       rep("RUS", 18),
-                                       rep("ROS", 18),
-                                       rep("SMOTE", 18)),
-                          Predictor=rep(c(rep("OC", 6),
-                                      rep("OP", 6),
-                                      rep("Distance", 6)),4),
-                          Metric=rep(c("Accuracy", 
-                                       "AUPRC", 
-                                       "F1-Score", 
-                                       "MCC",
-                                       "Informedness",
-                                       "Balanced Acc"), 12))
-
-all_rfperfs_K562_100kb$Performance <- c(round(rfperf_K562_100kb_none_oc[9,2],2), #accuracy
-                                round(rfperf_K562_100kb_none_oc[19,2],2), #auprc
-                                round(rfperf_K562_100kb_none_oc[16,2],2), #f1
-                                round(rfperf_K562_100kb_none_oc[15,2],2), #mcc
-								round(rfperf_K562_100kb_none_oc[18,2],2), #youden
-								(round(rfperf_K562_100kb_none_oc[6,2],2) + round(rfperf_K562_100kb_none_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_100kb_none_op[9,2],2), #accuracy
-                                round(rfperf_K562_100kb_none_op[19,2],2), #auprc
-                                round(rfperf_K562_100kb_none_op[16,2],2), #f1
-                                round(rfperf_K562_100kb_none_op[15,2],2), #mcc
-								round(rfperf_K562_100kb_none_op[18,2],2), #youden
-								(round(rfperf_K562_100kb_none_op[6,2],2) + round(rfperf_K562_100kb_none_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_100kb_none_dist[9,2],2), #accuracy
-                                round(rfperf_K562_100kb_none_dist[19,2],2), #auprc
-                                round(rfperf_K562_100kb_none_dist[16,2],2), #f1
-                                round(rfperf_K562_100kb_none_dist[15,2],2), #mcc
-								round(rfperf_K562_100kb_none_dist[18,2],2), #youden
-								(round(rfperf_K562_100kb_none_dist[6,2],2) + round(rfperf_K562_100kb_none_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_100kb_rus_oc[9,2],2), #accuracy
-                                round(rfperf_K562_100kb_rus_oc[19,2],2), #auprc
-                                round(rfperf_K562_100kb_rus_oc[16,2],2), #f1
-                                round(rfperf_K562_100kb_rus_oc[15,2],2), #mcc
-								round(rfperf_K562_100kb_rus_oc[18,2],2), #youden
-								(round(rfperf_K562_100kb_rus_oc[6,2],2) + round(rfperf_K562_100kb_rus_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_100kb_rus_op[9,2],2), #accuracy
-                                round(rfperf_K562_100kb_rus_op[19,2],2), #auprc
-                                round(rfperf_K562_100kb_rus_op[16,2],2), #f1
-                                round(rfperf_K562_100kb_rus_op[15,2],2), #mcc
-								round(rfperf_K562_100kb_rus_op[18,2],2), #youden
-								(round(rfperf_K562_100kb_rus_op[6,2],2) + round(rfperf_K562_100kb_rus_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_100kb_rus_dist[9,2],2), #accuracy
-                                round(rfperf_K562_100kb_rus_dist[19,2],2), #auprc
-                                round(rfperf_K562_100kb_rus_dist[16,2],2), #f1
-                                round(rfperf_K562_100kb_rus_dist[15,2],2), #mcc
-								round(rfperf_K562_100kb_rus_dist[18,2],2), #youden
-								(round(rfperf_K562_100kb_rus_dist[6,2],2) + round(rfperf_K562_100kb_rus_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_100kb_ros_oc[9,2],2), #accuracy
-                                round(rfperf_K562_100kb_ros_oc[19,2],2), #auprc
-                                round(rfperf_K562_100kb_ros_oc[16,2],2), #f1
-                                round(rfperf_K562_100kb_ros_oc[15,2],2), #mcc
-								round(rfperf_K562_100kb_ros_oc[18,2],2), #youden
-								(round(rfperf_K562_100kb_ros_oc[6,2],2) + round(rfperf_K562_100kb_ros_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_100kb_ros_op[9,2],2), #accuracy
-                                round(rfperf_K562_100kb_ros_op[19,2],2), #auprc
-                                round(rfperf_K562_100kb_ros_op[16,2],2), #f1
-                                round(rfperf_K562_100kb_ros_op[15,2],2), #mcc
-								round(rfperf_K562_100kb_ros_op[18,2],2), #youden
-								(round(rfperf_K562_100kb_ros_op[6,2],2) + round(rfperf_K562_100kb_ros_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_100kb_ros_dist[9,2],2), #accuracy
-                                round(rfperf_K562_100kb_ros_dist[19,2],2), #auprc
-                                round(rfperf_K562_100kb_ros_dist[16,2],2), #f1
-                                round(rfperf_K562_100kb_ros_dist[15,2],2), #mcc
-								round(rfperf_K562_100kb_ros_dist[18,2],2), #youden
-								(round(rfperf_K562_100kb_ros_dist[6,2],2) + round(rfperf_K562_100kb_ros_dist[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_100kb_smote_oc[9,2],2), #accuracy
-                                round(rfperf_K562_100kb_smote_oc[19,2],2), #auprc
-                                round(rfperf_K562_100kb_smote_oc[16,2],2), #f1
-                                round(rfperf_K562_100kb_smote_oc[15,2],2), #mcc
-								round(rfperf_K562_100kb_smote_oc[18,2],2), #youden
-								(round(rfperf_K562_100kb_smote_oc[6,2],2) + round(rfperf_K562_100kb_smote_oc[7,2],2))/2, #balanced accuracy
-
-                                round(rfperf_K562_100kb_smote_op[9,2],2), #accuracy
-                                round(rfperf_K562_100kb_smote_op[19,2],2), #auprc
-                                round(rfperf_K562_100kb_smote_op[16,2],2), #f1
-                                round(rfperf_K562_100kb_smote_op[15,2],2), #mcc
-								round(rfperf_K562_100kb_smote_op[18,2],2), #youden
-								(round(rfperf_K562_100kb_smote_op[6,2],2) + round(rfperf_K562_100kb_smote_op[7,2],2))/2, #balanced accuracy
-
-								round(rfperf_K562_100kb_smote_dist[9,2],2), #accuracy
-                                round(rfperf_K562_100kb_smote_dist[19,2],2), #auprc
-                                round(rfperf_K562_100kb_smote_dist[16,2],2), #f1
-                                round(rfperf_K562_100kb_smote_dist[15,2],2), #mcc
-								round(rfperf_K562_100kb_smote_dist[18,2],2), #youden
-								(round(rfperf_K562_100kb_smote_dist[6,2],2) + round(rfperf_K562_100kb_smote_dist[7,2],2))/2 #balanced accuracy
-								)
-all_rfperfs_K562_100kb$Resampling <- factor(all_rfperfs_K562_100kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
-all_rfperfs_K562_100kb$Predictor <- factor(all_rfperfs_K562_100kb$Predictor, levels = c("OC", "OP", "Distance"))
-all_rfperfs_K562_100kb$Metric <- factor(all_rfperfs_K562_100kb$Metric, levels = c("Accuracy",
-                                                                                      "AUPRC",
-                                                                                      "F1-Score",
-                                                                                      "MCC",
-                                                                                      "Informedness",
-                                                                                      "Balanced Acc"))
-
-#comparing only f1 and mcc and balanced acc
-
-ggplot(all_rfperfs_K562_100kb[which(all_rfperfs_K562_100kb$Metric=="F1-Score" |
-                                               all_rfperfs_K562_100kb$Metric=="MCC" |
-                                      all_rfperfs_K562_100kb$Metric=="Balanced Acc"),],
-                       aes(x=Resampling, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(~ Metric) +
-  xlab("Resampling Technique") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-	theme(axis.text.x = element_text(size=15,
-	                                 angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-```
-
-##Plots
-
-```{r}
-
-figure <- ggarrange(p1,p2,ncol = 2, nrow = 1, common.legend = TRUE, legend = "top")
-figure
-annotate_figure(figure,
-    bottom = text_grob("Resampling Technique", color = "black", size = 20),
-    left = text_grob("Performance", color = "black", rot = 90, size=20)
-)
-
-figure <- ggarrange(p25, p25.2, p50, p50.2, p100, p100.2, 
-          ncol=2, nrow=3, 
-          common.legend = TRUE, 
-          legend = "top", 
-          labels = c("A", "D", "B", "E", "C", "F"), 
-          font.label = list(size=20))
-figure
-annotate_figure(figure,
-    bottom = text_grob("Resampling Technique", color = "black", size = 20),
-    left = text_grob("Performance", color = "black", rot = 90, size=20)
-)
-
-```
-
-##gm12878
-
-```{r}
-#OC
-##None
-rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##None
-rfperf_gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_gm12878_25kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_gm12878_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##None
-rfperf_gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_gm12878_50kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_gm12878_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##None
-rfperf_gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_gm12878_100kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_gm12878_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_gm12878_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_gm12878_10kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_gm12878_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_gm12878_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_gm12878_25kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_gm12878_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_gm12878_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_gm12878_50kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_gm12878_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_gm12878_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_gm12878_100kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_gm12878_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_gm12878_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_gm12878_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_gm12878_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_gm12878_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_gm12878_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_gm12878_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_gm12878_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_gm12878_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_gm12878_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_gm12878_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_gm12878_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_gm12878_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_gm12878_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_gm12878_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_gm12878_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_gm12878_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_gm12878_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_gm12878_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_gm12878_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_gm12878_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_gm12878_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_gm12878_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_gm12878_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_gm12878_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-all_rfperfs_gm12878 <- data.frame(Resolution=rep(c(rep("10 kb", 12),
-                                                        rep("25 kb", 12),
-                                                        rep("50 kb", 12),
-                                                        rep("100 kb", 12)),4),
-                                       Predictor=rep(c("OC","OP","Distance"),64),
-                                       Metric=c(rep("AUC",48),
-                                                rep("AUPRC",48),
-                                                rep("F1-Score",48), 
-                                                rep("MCC",48)),
-                                       Resampling=rep(c(rep("None",3),
-                                                    rep("ROS",3),
-                                                    rep("RUS",3),
-                                                    rep("SMOTE",3)),16))
-all_rfperfs_gm12878$Resolution <- factor(all_rfperfs_gm12878$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
-all_rfperfs_gm12878$Predictor <- factor(all_rfperfs_gm12878$Predictor, levels=c("OC", "OP", "Distance"))
-all_rfperfs_gm12878$Metric <- factor(all_rfperfs_gm12878$Metric, levels=c("AUC", "AUPRC", "F1-Score", "MCC"))
-all_rfperfs_gm12878$Resampling <- factor(all_rfperfs_gm12878$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))
-
-all_rfperfs_gm12878$Performance <- c(rfperf_gm12878_10kb_none_oc[17,2], #auc
-                                          rfperf_gm12878_10kb_none_op[17,2], #auc
-                                          rfperf_gm12878_10kb_none_dist[17,2], #auc
-                                          rfperf_gm12878_10kb_ROS_oc[17,2], #auc
-                                          rfperf_gm12878_10kb_ROS_op[17,2], #auc
-                                          rfperf_gm12878_10kb_ROS_dist[17,2], #auc
-                                          rfperf_gm12878_10kb_RUS_oc[17,2], #auc
-                                          rfperf_gm12878_10kb_RUS_op[17,2], #auc
-                                          rfperf_gm12878_10kb_RUS_dist[17,2], #auc
-                                          rfperf_gm12878_10kb_SMOTE_oc[17,2], #auc
-                                          rfperf_gm12878_10kb_SMOTE_op[17,2], #auc
-                                          rfperf_gm12878_10kb_SMOTE_dist[17,2], #auc
-
-                                     rfperf_gm12878_25kb_none_oc[17,2], #auc
-                                          rfperf_gm12878_25kb_none_op[17,2], #auc
-                                          rfperf_gm12878_25kb_none_dist[17,2], #auc
-                                          rfperf_gm12878_25kb_ROS_oc[17,2], #auc
-                                          rfperf_gm12878_25kb_ROS_op[17,2], #auc
-                                          rfperf_gm12878_25kb_ROS_dist[17,2], #auc
-                                          rfperf_gm12878_25kb_RUS_oc[17,2], #auc
-                                          rfperf_gm12878_25kb_RUS_op[17,2], #auc
-                                          rfperf_gm12878_25kb_RUS_dist[17,2], #auc
-                                          rfperf_gm12878_25kb_SMOTE_oc[17,2], #auc
-                                          rfperf_gm12878_25kb_SMOTE_op[17,2], #auc
-                                          rfperf_gm12878_25kb_SMOTE_dist[17,2], #auc
-
-                                     rfperf_gm12878_50kb_none_oc[17,2], #auc
-                                          rfperf_gm12878_50kb_none_op[17,2], #auc
-                                          rfperf_gm12878_50kb_none_dist[17,2], #auc
-                                          rfperf_gm12878_50kb_ROS_oc[17,2], #auc
-                                          rfperf_gm12878_50kb_ROS_op[17,2], #auc
-                                          rfperf_gm12878_50kb_ROS_dist[17,2], #auc
-                                          rfperf_gm12878_50kb_RUS_oc[17,2], #auc
-                                          rfperf_gm12878_50kb_RUS_op[17,2], #auc
-                                          rfperf_gm12878_50kb_RUS_dist[17,2], #auc
-                                          rfperf_gm12878_50kb_SMOTE_oc[17,2], #auc
-                                          rfperf_gm12878_50kb_SMOTE_op[17,2], #auc
-                                          rfperf_gm12878_50kb_SMOTE_dist[17,2], #auc
-
-                                     rfperf_gm12878_100kb_none_oc[17,2], #auc
-                                          rfperf_gm12878_100kb_none_op[17,2], #auc
-                                          rfperf_gm12878_100kb_none_dist[17,2], #auc
-                                          rfperf_gm12878_100kb_ROS_oc[17,2], #auc
-                                          rfperf_gm12878_100kb_ROS_op[17,2], #auc
-                                          rfperf_gm12878_100kb_ROS_dist[17,2], #auc
-                                          rfperf_gm12878_100kb_RUS_oc[17,2], #auc
-                                          rfperf_gm12878_100kb_RUS_op[17,2], #auc
-                                          rfperf_gm12878_100kb_RUS_dist[17,2], #auc
-                                          rfperf_gm12878_100kb_SMOTE_oc[17,2], #auc
-                                          rfperf_gm12878_100kb_SMOTE_op[17,2], #auc
-                                          rfperf_gm12878_100kb_SMOTE_dist[17,2], #auc
-
-                                     rfperf_gm12878_10kb_none_oc[19,2], #auprc
-                                          rfperf_gm12878_10kb_none_op[19,2], #auprc
-                                          rfperf_gm12878_10kb_none_dist[19,2], #auprc
-                                          rfperf_gm12878_10kb_ROS_oc[19,2], #auprc
-                                          rfperf_gm12878_10kb_ROS_op[19,2], #auprc
-                                          rfperf_gm12878_10kb_ROS_dist[19,2], #auprc
-                                          rfperf_gm12878_10kb_RUS_oc[19,2], #auprc
-                                          rfperf_gm12878_10kb_RUS_op[19,2], #auprc
-                                          rfperf_gm12878_10kb_RUS_dist[19,2], #auprc
-                                          rfperf_gm12878_10kb_SMOTE_oc[19,2], #auprc
-                                          rfperf_gm12878_10kb_SMOTE_op[19,2], #auprc
-                                          rfperf_gm12878_10kb_SMOTE_dist[19,2], #auprc
-
-                                     rfperf_gm12878_25kb_none_oc[19,2], #auprc
-                                          rfperf_gm12878_25kb_none_op[19,2], #auprc
-                                          rfperf_gm12878_25kb_none_dist[19,2], #auprc
-                                          rfperf_gm12878_25kb_ROS_oc[19,2], #auprc
-                                          rfperf_gm12878_25kb_ROS_op[19,2], #auprc
-                                          rfperf_gm12878_25kb_ROS_dist[19,2], #auprc
-                                          rfperf_gm12878_25kb_RUS_oc[19,2], #auprc
-                                          rfperf_gm12878_25kb_RUS_op[19,2], #auprc
-                                          rfperf_gm12878_25kb_RUS_dist[19,2], #auprc
-                                          rfperf_gm12878_25kb_SMOTE_oc[19,2], #auprc
-                                          rfperf_gm12878_25kb_SMOTE_op[19,2], #auprc
-                                          rfperf_gm12878_25kb_SMOTE_dist[19,2], #auprc
-
-                                     rfperf_gm12878_50kb_none_oc[19,2], #auprc
-                                          rfperf_gm12878_50kb_none_op[19,2], #auprc
-                                          rfperf_gm12878_50kb_none_dist[19,2], #auprc
-                                          rfperf_gm12878_50kb_ROS_oc[19,2], #auprc
-                                          rfperf_gm12878_50kb_ROS_op[19,2], #auprc
-                                          rfperf_gm12878_50kb_ROS_dist[19,2], #auprc
-                                          rfperf_gm12878_50kb_RUS_oc[19,2], #auprc
-                                          rfperf_gm12878_50kb_RUS_op[19,2], #auprc
-                                          rfperf_gm12878_50kb_RUS_dist[19,2], #auprc
-                                          rfperf_gm12878_50kb_SMOTE_oc[19,2], #auprc
-                                          rfperf_gm12878_50kb_SMOTE_op[19,2], #auprc
-                                          rfperf_gm12878_50kb_SMOTE_dist[19,2], #auprc
-
-                                     rfperf_gm12878_100kb_none_oc[19,2], #auprc
-                                          rfperf_gm12878_100kb_none_op[19,2], #auprc
-                                          rfperf_gm12878_100kb_none_dist[19,2], #auprc
-                                          rfperf_gm12878_100kb_ROS_oc[19,2], #auprc
-                                          rfperf_gm12878_100kb_ROS_op[19,2], #auprc
-                                          rfperf_gm12878_100kb_ROS_dist[19,2], #auprc
-                                          rfperf_gm12878_100kb_RUS_oc[19,2], #auprc
-                                          rfperf_gm12878_100kb_RUS_op[19,2], #auprc
-                                          rfperf_gm12878_100kb_RUS_dist[19,2], #auprc
-                                          rfperf_gm12878_100kb_SMOTE_oc[19,2], #auprc
-                                          rfperf_gm12878_100kb_SMOTE_op[19,2], #auprc
-                                          rfperf_gm12878_100kb_SMOTE_dist[19,2], #auprc
-
-                                     rfperf_gm12878_10kb_none_oc[16,2], #f1
-                                          rfperf_gm12878_10kb_none_op[16,2], #f1
-                                          rfperf_gm12878_10kb_none_dist[16,2], #f1
-                                          rfperf_gm12878_10kb_ROS_oc[16,2], #f1
-                                          rfperf_gm12878_10kb_ROS_op[16,2], #f1
-                                          rfperf_gm12878_10kb_ROS_dist[16,2], #f1
-                                          rfperf_gm12878_10kb_RUS_oc[16,2], #f1
-                                          rfperf_gm12878_10kb_RUS_op[16,2], #f1
-                                          rfperf_gm12878_10kb_RUS_dist[16,2], #f1
-                                          rfperf_gm12878_10kb_SMOTE_oc[16,2], #f1
-                                          rfperf_gm12878_10kb_SMOTE_op[16,2], #f1
-                                          rfperf_gm12878_10kb_SMOTE_dist[16,2], #f1
-
-                                     rfperf_gm12878_25kb_none_oc[16,2], #f1
-                                          rfperf_gm12878_25kb_none_op[16,2], #f1
-                                          rfperf_gm12878_25kb_none_dist[16,2], #f1
-                                          rfperf_gm12878_25kb_ROS_oc[16,2], #f1
-                                          rfperf_gm12878_25kb_ROS_op[16,2], #f1
-                                          rfperf_gm12878_25kb_ROS_dist[16,2], #f1
-                                          rfperf_gm12878_25kb_RUS_oc[16,2], #f1
-                                          rfperf_gm12878_25kb_RUS_op[16,2], #f1
-                                          rfperf_gm12878_25kb_RUS_dist[16,2], #f1
-                                          rfperf_gm12878_25kb_SMOTE_oc[16,2], #f1
-                                          rfperf_gm12878_25kb_SMOTE_op[16,2], #f1
-                                          rfperf_gm12878_25kb_SMOTE_dist[16,2], #f1
-
-                                     rfperf_gm12878_50kb_none_oc[16,2], #f1
-                                          rfperf_gm12878_50kb_none_op[16,2], #f1
-                                          rfperf_gm12878_50kb_none_dist[16,2], #f1
-                                          rfperf_gm12878_50kb_ROS_oc[16,2], #f1
-                                          rfperf_gm12878_50kb_ROS_op[16,2], #f1
-                                          rfperf_gm12878_50kb_ROS_dist[16,2], #f1
-                                          rfperf_gm12878_50kb_RUS_oc[16,2], #f1
-                                          rfperf_gm12878_50kb_RUS_op[16,2], #f1
-                                          rfperf_gm12878_50kb_RUS_dist[16,2], #f1
-                                          rfperf_gm12878_50kb_SMOTE_oc[16,2], #f1
-                                          rfperf_gm12878_50kb_SMOTE_op[16,2], #f1
-                                          rfperf_gm12878_50kb_SMOTE_dist[16,2], #f1
-
-                                     rfperf_gm12878_100kb_none_oc[16,2], #f1
-                                          rfperf_gm12878_100kb_none_op[16,2], #f1
-                                          rfperf_gm12878_100kb_none_dist[16,2], #f1
-                                          rfperf_gm12878_100kb_ROS_oc[16,2], #f1
-                                          rfperf_gm12878_100kb_ROS_op[16,2], #f1
-                                          rfperf_gm12878_100kb_ROS_dist[16,2], #f1
-                                          rfperf_gm12878_100kb_RUS_oc[16,2], #f1
-                                          rfperf_gm12878_100kb_RUS_op[16,2], #f1
-                                          rfperf_gm12878_100kb_RUS_dist[16,2], #f1
-                                          rfperf_gm12878_100kb_SMOTE_oc[16,2], #f1
-                                          rfperf_gm12878_100kb_SMOTE_op[16,2], #f1
-                                          rfperf_gm12878_100kb_SMOTE_dist[16,2], #f1
-
-                                     rfperf_gm12878_10kb_none_oc[15,2], #mcc
-                                          rfperf_gm12878_10kb_none_op[15,2], #mcc
-                                          rfperf_gm12878_10kb_none_dist[15,2], #mcc
-                                          rfperf_gm12878_10kb_ROS_oc[15,2], #mcc
-                                          rfperf_gm12878_10kb_ROS_op[15,2], #mcc
-                                          rfperf_gm12878_10kb_ROS_dist[15,2], #mcc
-                                          rfperf_gm12878_10kb_RUS_oc[15,2], #mcc
-                                          rfperf_gm12878_10kb_RUS_op[15,2], #mcc
-                                          rfperf_gm12878_10kb_RUS_dist[15,2], #mcc
-                                          rfperf_gm12878_10kb_SMOTE_oc[15,2], #mcc
-                                          rfperf_gm12878_10kb_SMOTE_op[15,2], #mcc
-                                          rfperf_gm12878_10kb_SMOTE_dist[15,2], #mcc
-
-                                     rfperf_gm12878_25kb_none_oc[15,2], #mcc
-                                          rfperf_gm12878_25kb_none_op[15,2], #mcc
-                                          rfperf_gm12878_25kb_none_dist[15,2], #mcc
-                                          rfperf_gm12878_25kb_ROS_oc[15,2], #mcc
-                                          rfperf_gm12878_25kb_ROS_op[15,2], #mcc
-                                          rfperf_gm12878_25kb_ROS_dist[15,2], #mcc
-                                          rfperf_gm12878_25kb_RUS_oc[15,2], #mcc
-                                          rfperf_gm12878_25kb_RUS_op[15,2], #mcc
-                                          rfperf_gm12878_25kb_RUS_dist[15,2], #mcc
-                                          rfperf_gm12878_25kb_SMOTE_oc[15,2], #mcc
-                                          rfperf_gm12878_25kb_SMOTE_op[15,2], #mcc
-                                          rfperf_gm12878_25kb_SMOTE_dist[15,2], #mcc
-
-                                     rfperf_gm12878_50kb_none_oc[15,2], #mcc
-                                          rfperf_gm12878_50kb_none_op[15,2], #mcc
-                                          rfperf_gm12878_50kb_none_dist[15,2], #mcc
-                                          rfperf_gm12878_50kb_ROS_oc[15,2], #mcc
-                                          rfperf_gm12878_50kb_ROS_op[15,2], #mcc
-                                          rfperf_gm12878_50kb_ROS_dist[15,2], #mcc
-                                          rfperf_gm12878_50kb_RUS_oc[15,2], #mcc
-                                          rfperf_gm12878_50kb_RUS_op[15,2], #mcc
-                                          rfperf_gm12878_50kb_RUS_dist[15,2], #mcc
-                                          rfperf_gm12878_50kb_SMOTE_oc[15,2], #mcc
-                                          rfperf_gm12878_50kb_SMOTE_op[15,2], #mcc
-                                          rfperf_gm12878_50kb_SMOTE_dist[15,2], #mcc
-
-                                     rfperf_gm12878_100kb_none_oc[15,2], #mcc
-                                          rfperf_gm12878_100kb_none_op[15,2], #mcc
-                                          rfperf_gm12878_100kb_none_dist[15,2], #mcc
-                                          rfperf_gm12878_100kb_ROS_oc[15,2], #mcc
-                                          rfperf_gm12878_100kb_ROS_op[15,2], #mcc
-                                          rfperf_gm12878_100kb_ROS_dist[15,2], #mcc
-                                          rfperf_gm12878_100kb_RUS_oc[15,2], #mcc
-                                          rfperf_gm12878_100kb_RUS_op[15,2], #mcc
-                                          rfperf_gm12878_100kb_RUS_dist[15,2], #mcc
-                                          rfperf_gm12878_100kb_SMOTE_oc[15,2], #mcc
-                                          rfperf_gm12878_100kb_SMOTE_op[15,2], #mcc
-                                          rfperf_gm12878_100kb_SMOTE_dist[15,2] #mcc
-)
-
-p1 <- ggplot(all_rfperfs_gm12878,
-       aes(x=Resolution, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(Metric ~ Resampling) +
-  xlab("") + ylab("") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15,
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-```
-
-##k562
-
-```{r}
-#OC
-##None
-rfperf_K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_K562_10kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_K562_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##None
-rfperf_K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_K562_25kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_K562_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##None
-rfperf_K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_K562_50kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_K562_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##None
-rfperf_K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_K562_100kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_K562_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_K562_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_K562_10kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_K562_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_K562_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_K562_25kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_K562_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_K562_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_K562_50kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_K562_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_K562_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_K562_100kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_K562_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_K562_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_K562_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_K562_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_K562_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_K562_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_K562_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_K562_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_K562_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_K562_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_K562_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_K562_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_K562_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_K562_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_K562_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_K562_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_K562_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_K562_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_K562_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_K562_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_K562_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_K562_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_K562_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_K562_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_K562_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-all_rfperfs_K562 <- data.frame(Resolution=rep(c(rep("10 kb", 12),
-                                                        rep("25 kb", 12),
-                                                        rep("50 kb", 12),
-                                                        rep("100 kb", 12)),4),
-                                       Predictor=rep(c("OC","OP","Distance"),64),
-                                       Metric=c(rep("AUC",48),
-                                                rep("AUPRC",48),
-                                                rep("F1-Score",48), 
-                                                rep("MCC",48)),
-                                       Resampling=rep(c(rep("None",3),
-                                                    rep("ROS",3),
-                                                    rep("RUS",3),
-                                                    rep("SMOTE",3)),16))
-all_rfperfs_K562$Resolution <- factor(all_rfperfs_K562$Resolution, levels=c("10 kb","25 kb","50 kb","100 kb"))
-all_rfperfs_K562$Predictor <- factor(all_rfperfs_K562$Predictor, levels=c("OC", "OP", "Distance"))
-all_rfperfs_K562$Metric <- factor(all_rfperfs_K562$Metric, levels=c("AUC", "AUPRC", "F1-Score", "MCC"))
-all_rfperfs_K562$Resampling <- factor(all_rfperfs_K562$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))
-
-all_rfperfs_K562$Performance <- c(rfperf_K562_10kb_none_oc[17,2], #auc
-                                          rfperf_K562_10kb_none_op[17,2], #auc
-                                          rfperf_K562_10kb_none_dist[17,2], #auc
-                                          rfperf_K562_10kb_ROS_oc[17,2], #auc
-                                          rfperf_K562_10kb_ROS_op[17,2], #auc
-                                          rfperf_K562_10kb_ROS_dist[17,2], #auc
-                                          rfperf_K562_10kb_RUS_oc[17,2], #auc
-                                          rfperf_K562_10kb_RUS_op[17,2], #auc
-                                          rfperf_K562_10kb_RUS_dist[17,2], #auc
-                                          rfperf_K562_10kb_SMOTE_oc[17,2], #auc
-                                          rfperf_K562_10kb_SMOTE_op[17,2], #auc
-                                          rfperf_K562_10kb_SMOTE_dist[17,2], #auc
-
-                                     rfperf_K562_25kb_none_oc[17,2], #auc
-                                          rfperf_K562_25kb_none_op[17,2], #auc
-                                          rfperf_K562_25kb_none_dist[17,2], #auc
-                                          rfperf_K562_25kb_ROS_oc[17,2], #auc
-                                          rfperf_K562_25kb_ROS_op[17,2], #auc
-                                          rfperf_K562_25kb_ROS_dist[17,2], #auc
-                                          rfperf_K562_25kb_RUS_oc[17,2], #auc
-                                          rfperf_K562_25kb_RUS_op[17,2], #auc
-                                          rfperf_K562_25kb_RUS_dist[17,2], #auc
-                                          rfperf_K562_25kb_SMOTE_oc[17,2], #auc
-                                          rfperf_K562_25kb_SMOTE_op[17,2], #auc
-                                          rfperf_K562_25kb_SMOTE_dist[17,2], #auc
-
-                                     rfperf_K562_50kb_none_oc[17,2], #auc
-                                          rfperf_K562_50kb_none_op[17,2], #auc
-                                          rfperf_K562_50kb_none_dist[17,2], #auc
-                                          rfperf_K562_50kb_ROS_oc[17,2], #auc
-                                          rfperf_K562_50kb_ROS_op[17,2], #auc
-                                          rfperf_K562_50kb_ROS_dist[17,2], #auc
-                                          rfperf_K562_50kb_RUS_oc[17,2], #auc
-                                          rfperf_K562_50kb_RUS_op[17,2], #auc
-                                          rfperf_K562_50kb_RUS_dist[17,2], #auc
-                                          rfperf_K562_50kb_SMOTE_oc[17,2], #auc
-                                          rfperf_K562_50kb_SMOTE_op[17,2], #auc
-                                          rfperf_K562_50kb_SMOTE_dist[17,2], #auc
-
-                                     rfperf_K562_100kb_none_oc[17,2], #auc
-                                          rfperf_K562_100kb_none_op[17,2], #auc
-                                          rfperf_K562_100kb_none_dist[17,2], #auc
-                                          rfperf_K562_100kb_ROS_oc[17,2], #auc
-                                          rfperf_K562_100kb_ROS_op[17,2], #auc
-                                          rfperf_K562_100kb_ROS_dist[17,2], #auc
-                                          rfperf_K562_100kb_RUS_oc[17,2], #auc
-                                          rfperf_K562_100kb_RUS_op[17,2], #auc
-                                          rfperf_K562_100kb_RUS_dist[17,2], #auc
-                                          rfperf_K562_100kb_SMOTE_oc[17,2], #auc
-                                          rfperf_K562_100kb_SMOTE_op[17,2], #auc
-                                          rfperf_K562_100kb_SMOTE_dist[17,2], #auc
-
-                                     rfperf_K562_10kb_none_oc[19,2], #auprc
-                                          rfperf_K562_10kb_none_op[19,2], #auprc
-                                          rfperf_K562_10kb_none_dist[19,2], #auprc
-                                          rfperf_K562_10kb_ROS_oc[19,2], #auprc
-                                          rfperf_K562_10kb_ROS_op[19,2], #auprc
-                                          rfperf_K562_10kb_ROS_dist[19,2], #auprc
-                                          rfperf_K562_10kb_RUS_oc[19,2], #auprc
-                                          rfperf_K562_10kb_RUS_op[19,2], #auprc
-                                          rfperf_K562_10kb_RUS_dist[19,2], #auprc
-                                          rfperf_K562_10kb_SMOTE_oc[19,2], #auprc
-                                          rfperf_K562_10kb_SMOTE_op[19,2], #auprc
-                                          rfperf_K562_10kb_SMOTE_dist[19,2], #auprc
-
-                                     rfperf_K562_25kb_none_oc[19,2], #auprc
-                                          rfperf_K562_25kb_none_op[19,2], #auprc
-                                          rfperf_K562_25kb_none_dist[19,2], #auprc
-                                          rfperf_K562_25kb_ROS_oc[19,2], #auprc
-                                          rfperf_K562_25kb_ROS_op[19,2], #auprc
-                                          rfperf_K562_25kb_ROS_dist[19,2], #auprc
-                                          rfperf_K562_25kb_RUS_oc[19,2], #auprc
-                                          rfperf_K562_25kb_RUS_op[19,2], #auprc
-                                          rfperf_K562_25kb_RUS_dist[19,2], #auprc
-                                          rfperf_K562_25kb_SMOTE_oc[19,2], #auprc
-                                          rfperf_K562_25kb_SMOTE_op[19,2], #auprc
-                                          rfperf_K562_25kb_SMOTE_dist[19,2], #auprc
-
-                                     rfperf_K562_50kb_none_oc[19,2], #auprc
-                                          rfperf_K562_50kb_none_op[19,2], #auprc
-                                          rfperf_K562_50kb_none_dist[19,2], #auprc
-                                          rfperf_K562_50kb_ROS_oc[19,2], #auprc
-                                          rfperf_K562_50kb_ROS_op[19,2], #auprc
-                                          rfperf_K562_50kb_ROS_dist[19,2], #auprc
-                                          rfperf_K562_50kb_RUS_oc[19,2], #auprc
-                                          rfperf_K562_50kb_RUS_op[19,2], #auprc
-                                          rfperf_K562_50kb_RUS_dist[19,2], #auprc
-                                          rfperf_K562_50kb_SMOTE_oc[19,2], #auprc
-                                          rfperf_K562_50kb_SMOTE_op[19,2], #auprc
-                                          rfperf_K562_50kb_SMOTE_dist[19,2], #auprc
-
-                                     rfperf_K562_100kb_none_oc[19,2], #auprc
-                                          rfperf_K562_100kb_none_op[19,2], #auprc
-                                          rfperf_K562_100kb_none_dist[19,2], #auprc
-                                          rfperf_K562_100kb_ROS_oc[19,2], #auprc
-                                          rfperf_K562_100kb_ROS_op[19,2], #auprc
-                                          rfperf_K562_100kb_ROS_dist[19,2], #auprc
-                                          rfperf_K562_100kb_RUS_oc[19,2], #auprc
-                                          rfperf_K562_100kb_RUS_op[19,2], #auprc
-                                          rfperf_K562_100kb_RUS_dist[19,2], #auprc
-                                          rfperf_K562_100kb_SMOTE_oc[19,2], #auprc
-                                          rfperf_K562_100kb_SMOTE_op[19,2], #auprc
-                                          rfperf_K562_100kb_SMOTE_dist[19,2], #auprc
-
-                                     rfperf_K562_10kb_none_oc[16,2], #f1
-                                          rfperf_K562_10kb_none_op[16,2], #f1
-                                          rfperf_K562_10kb_none_dist[16,2], #f1
-                                          rfperf_K562_10kb_ROS_oc[16,2], #f1
-                                          rfperf_K562_10kb_ROS_op[16,2], #f1
-                                          rfperf_K562_10kb_ROS_dist[16,2], #f1
-                                          rfperf_K562_10kb_RUS_oc[16,2], #f1
-                                          rfperf_K562_10kb_RUS_op[16,2], #f1
-                                          rfperf_K562_10kb_RUS_dist[16,2], #f1
-                                          rfperf_K562_10kb_SMOTE_oc[16,2], #f1
-                                          rfperf_K562_10kb_SMOTE_op[16,2], #f1
-                                          rfperf_K562_10kb_SMOTE_dist[16,2], #f1
-
-                                     rfperf_K562_25kb_none_oc[16,2], #f1
-                                          rfperf_K562_25kb_none_op[16,2], #f1
-                                          rfperf_K562_25kb_none_dist[16,2], #f1
-                                          rfperf_K562_25kb_ROS_oc[16,2], #f1
-                                          rfperf_K562_25kb_ROS_op[16,2], #f1
-                                          rfperf_K562_25kb_ROS_dist[16,2], #f1
-                                          rfperf_K562_25kb_RUS_oc[16,2], #f1
-                                          rfperf_K562_25kb_RUS_op[16,2], #f1
-                                          rfperf_K562_25kb_RUS_dist[16,2], #f1
-                                          rfperf_K562_25kb_SMOTE_oc[16,2], #f1
-                                          rfperf_K562_25kb_SMOTE_op[16,2], #f1
-                                          rfperf_K562_25kb_SMOTE_dist[16,2], #f1
-
-                                     rfperf_K562_50kb_none_oc[16,2], #f1
-                                          rfperf_K562_50kb_none_op[16,2], #f1
-                                          rfperf_K562_50kb_none_dist[16,2], #f1
-                                          rfperf_K562_50kb_ROS_oc[16,2], #f1
-                                          rfperf_K562_50kb_ROS_op[16,2], #f1
-                                          rfperf_K562_50kb_ROS_dist[16,2], #f1
-                                          rfperf_K562_50kb_RUS_oc[16,2], #f1
-                                          rfperf_K562_50kb_RUS_op[16,2], #f1
-                                          rfperf_K562_50kb_RUS_dist[16,2], #f1
-                                          rfperf_K562_50kb_SMOTE_oc[16,2], #f1
-                                          rfperf_K562_50kb_SMOTE_op[16,2], #f1
-                                          rfperf_K562_50kb_SMOTE_dist[16,2], #f1
-
-                                     rfperf_K562_100kb_none_oc[16,2], #f1
-                                          rfperf_K562_100kb_none_op[16,2], #f1
-                                          rfperf_K562_100kb_none_dist[16,2], #f1
-                                          rfperf_K562_100kb_ROS_oc[16,2], #f1
-                                          rfperf_K562_100kb_ROS_op[16,2], #f1
-                                          rfperf_K562_100kb_ROS_dist[16,2], #f1
-                                          rfperf_K562_100kb_RUS_oc[16,2], #f1
-                                          rfperf_K562_100kb_RUS_op[16,2], #f1
-                                          rfperf_K562_100kb_RUS_dist[16,2], #f1
-                                          rfperf_K562_100kb_SMOTE_oc[16,2], #f1
-                                          rfperf_K562_100kb_SMOTE_op[16,2], #f1
-                                          rfperf_K562_100kb_SMOTE_dist[16,2], #f1
-
-                                     rfperf_K562_10kb_none_oc[15,2], #mcc
-                                          rfperf_K562_10kb_none_op[15,2], #mcc
-                                          rfperf_K562_10kb_none_dist[15,2], #mcc
-                                          rfperf_K562_10kb_ROS_oc[15,2], #mcc
-                                          rfperf_K562_10kb_ROS_op[15,2], #mcc
-                                          rfperf_K562_10kb_ROS_dist[15,2], #mcc
-                                          rfperf_K562_10kb_RUS_oc[15,2], #mcc
-                                          rfperf_K562_10kb_RUS_op[15,2], #mcc
-                                          rfperf_K562_10kb_RUS_dist[15,2], #mcc
-                                          rfperf_K562_10kb_SMOTE_oc[15,2], #mcc
-                                          rfperf_K562_10kb_SMOTE_op[15,2], #mcc
-                                          rfperf_K562_10kb_SMOTE_dist[15,2], #mcc
-
-                                     rfperf_K562_25kb_none_oc[15,2], #mcc
-                                          rfperf_K562_25kb_none_op[15,2], #mcc
-                                          rfperf_K562_25kb_none_dist[15,2], #mcc
-                                          rfperf_K562_25kb_ROS_oc[15,2], #mcc
-                                          rfperf_K562_25kb_ROS_op[15,2], #mcc
-                                          rfperf_K562_25kb_ROS_dist[15,2], #mcc
-                                          rfperf_K562_25kb_RUS_oc[15,2], #mcc
-                                          rfperf_K562_25kb_RUS_op[15,2], #mcc
-                                          rfperf_K562_25kb_RUS_dist[15,2], #mcc
-                                          rfperf_K562_25kb_SMOTE_oc[15,2], #mcc
-                                          rfperf_K562_25kb_SMOTE_op[15,2], #mcc
-                                          rfperf_K562_25kb_SMOTE_dist[15,2], #mcc
-
-                                     rfperf_K562_50kb_none_oc[15,2], #mcc
-                                          rfperf_K562_50kb_none_op[15,2], #mcc
-                                          rfperf_K562_50kb_none_dist[15,2], #mcc
-                                          rfperf_K562_50kb_ROS_oc[15,2], #mcc
-                                          rfperf_K562_50kb_ROS_op[15,2], #mcc
-                                          rfperf_K562_50kb_ROS_dist[15,2], #mcc
-                                          rfperf_K562_50kb_RUS_oc[15,2], #mcc
-                                          rfperf_K562_50kb_RUS_op[15,2], #mcc
-                                          rfperf_K562_50kb_RUS_dist[15,2], #mcc
-                                          rfperf_K562_50kb_SMOTE_oc[15,2], #mcc
-                                          rfperf_K562_50kb_SMOTE_op[15,2], #mcc
-                                          rfperf_K562_50kb_SMOTE_dist[15,2], #mcc
-
-                                     rfperf_K562_100kb_none_oc[15,2], #mcc
-                                          rfperf_K562_100kb_none_op[15,2], #mcc
-                                          rfperf_K562_100kb_none_dist[15,2], #mcc
-                                          rfperf_K562_100kb_ROS_oc[15,2], #mcc
-                                          rfperf_K562_100kb_ROS_op[15,2], #mcc
-                                          rfperf_K562_100kb_ROS_dist[15,2], #mcc
-                                          rfperf_K562_100kb_RUS_oc[15,2], #mcc
-                                          rfperf_K562_100kb_RUS_op[15,2], #mcc
-                                          rfperf_K562_100kb_RUS_dist[15,2], #mcc
-                                          rfperf_K562_100kb_SMOTE_oc[15,2], #mcc
-                                          rfperf_K562_100kb_SMOTE_op[15,2], #mcc
-                                          rfperf_K562_100kb_SMOTE_dist[15,2] #mcc
-)
-
-p2 <- ggplot(all_rfperfs_K562,
-       aes(x=Resolution, y=Performance, fill=Predictor)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid(Metric ~ Resampling) +
-  xlab("") + ylab("") +
-  theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Predictor Type")+
-  #guides(fill=FALSE)+
-  theme(axis.text.x = element_text(size=15,
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-```
-
-##Plots
-
-```{r}
-p1 <- p1 + labs(title = "GM12878") + theme(plot.title = element_text(size=20))
-p2 <- p2 + labs(title = "K562") + theme(plot.title = element_text(size=20))
-
-figure <- ggarrange(p1,p2,
-                ncol = 2, nrow = 1, 
-                common.legend = TRUE, 
-                legend = "top",
-                labels = "AUTO",
-                font.label = list(size=20))
-figure
-annotate_figure(figure,
-    bottom = text_grob("Resolution", color = "black", size = 20),
-    left = text_grob("Performance", color = "black", rot = 90, size=20)
-)
-
-```
-
-##Plots
-
-```{r}
-c <- ggplot(all_rfperfs_gm12878[which(all_rfperfs_gm12878$Predictor=="OC" & (all_rfperfs_gm12878$Metric=="F1-Score" | all_rfperfs_gm12878$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
-    geom_line(size=2)+
-    geom_point(size=5)+
-    facet_grid(~ Metric)+
-    theme_minimal() +
-    theme_bw()+
-    xlab("") + ylab("") + ylim(-.02,.5) +
+# GM12878
+
+##10kb
+
+```{r}
+mccdata_gm12878_10kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/rfperf.rds"))
+
+			mccdata_gm12878_10kb <- rbind(mccdata_gm12878_10kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
+
+##25kb
+
+```{r}
+mccdata_gm12878_25kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/rfperf.rds"))
+
+			mccdata_gm12878_25kb <- rbind(mccdata_gm12878_25kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
+
+##50kb
+
+```{r}
+mccdata_gm12878_50kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/rfperf.rds"))
+
+			mccdata_gm12878_50kb <- rbind(mccdata_gm12878_50kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
+
+##100kb
+
+```{r}
+mccdata_gm12878_100kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/rfperf.rds"))
+
+			mccdata_gm12878_100kb <- rbind(mccdata_gm12878_100kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
+
+# K562
+
+##10kb
+
+```{r}
+mccdata_K562_10kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/rfperf.rds"))
+
+			mccdata_K562_10kb <- rbind(mccdata_K562_10kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
+
+##25kb
+
+```{r}
+mccdata_K562_25kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/rfperf.rds"))
+
+			mccdata_K562_25kb <- rbind(mccdata_K562_25kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
+
+##50kb
+
+```{r}
+mccdata_K562_50kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/rfperf.rds"))
+
+			mccdata_K562_50kb <- rbind(mccdata_K562_50kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
+
+##100kb
+
+```{r}
+mccdata_K562_100kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/rfperf.rds"))
+
+			mccdata_K562_100kb <- rbind(mccdata_K562_100kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
+
+## Plots
+
+```{r}
+all_rfperfs <- rbind.data.frame(mccdata_gm12878_10kb,
+                                mccdata_gm12878_25kb,
+                                mccdata_gm12878_50kb,
+                                mccdata_gm12878_100kb,
+                                mccdata_K562_10kb,
+                                mccdata_K562_25kb,
+                                mccdata_K562_50kb,
+                                mccdata_K562_100kb)
+all_rfperfs$CL <- c(rep("GM12878", length(mccdata_gm12878_10kb)*4), rep("K562", length(mccdata_K562_10kb)*4))
+all_rfperfs$Resolution <- rep(c(rep("10 kb", 252),
+                            rep("25 kb", 252),
+                            rep("50 kb", 252),
+                            rep("100 kb", 252)))
+all_rfperfs$Resampling <- rep(c(rep("None", 3),
+                            rep("ROS", 3),
+                            rep("RUS", 3),
+                            rep("SMOTE", 3)),168)
+all_rfperfs$Predictor <- rep(c("Distance", "OC", "OP"), 672)
+all_rfperfs$Chromosome <- c(rep("CHR1", 12),
+                            rep("CHR2", 12),
+                            rep("CHR3", 12),
+                            rep("CHR4", 12),
+                            rep("CHR5", 12),
+                            rep("CHR6", 12),
+                            rep("CHR7", 12),
+                            rep("CHR8", 12),
+                            rep("CHR10", 12),
+                            rep("CHR11", 12),
+                            rep("CHR12", 12),
+                            rep("CHR13", 12),
+                            rep("CHR14", 12),
+                            rep("CHR15", 12),
+                            rep("CHR16", 12),
+                            rep("CHR17", 12),
+                            rep("CHR18", 12),
+                            rep("CHR19", 12),
+                            rep("CHR20", 12),
+                            rep("CHR21", 12),
+                            rep("CHR22", 12))
+
+all_rfperfs$CL <- factor(all_rfperfs$CL, levels = c("GM12878", "K562"))
+all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
+all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
+all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("OC", "OP", "Distance"))
+all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))
+
+all_rfperfs_mcc <- all_rfperfs %>%
+  group_by(CL, Resolution, Resampling, Predictor) %>%
+  summarise(MCC = mean(V1, na.rm = TRUE),
+            MCCSD = sd(V1, na.rm = TRUE))
+
+#GM12878
+c <- ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="GM12878" & all_rfperfs_mcc$Predictor=="OC"),], aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     #facet_grid(~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.05,.5) +
      ggtitle("Overlap Counts") +
-    scale_color_discrete(name="Re-Sampling Technique")+
-    theme(axis.text.x = element_text(size=15,
-                                     angle = 45, 
-                                     #margin = ggplot2::margin(t = 35),
-                                     hjust = 1
-    ),
-    axis.text.y = element_text(size = 15),
-    axis.title.x = element_text(size = 20),
-    axis.title.y = element_text(size = 20),
-    legend.text=element_text(size=15),
-    legend.title=element_text(size=20),
-    plot.title = element_text(size=20))
-
-p <- ggplot(all_rfperfs_gm12878[which(all_rfperfs_gm12878$Predictor=="OP" & (all_rfperfs_gm12878$Metric=="F1-Score" | all_rfperfs_gm12878$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
-    geom_line(size=2)+
-    geom_point(size=5)+
-    facet_grid(~ Metric)+
-    theme_minimal() +
-    theme_bw()+
-    xlab("") + ylab("") + ylim(-.02,.5) +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+p <- ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="GM12878" & all_rfperfs_mcc$Predictor=="OP"),], aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     #facet_grid(~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.05,.5) +
      ggtitle("Overlap Percents") +
-    scale_color_discrete(name="Re-Sampling Technique")+
-    theme(axis.text.x = element_text(size=15,
-                                     angle = 45, 
-                                     #margin = ggplot2::margin(t = 35),
-                                     hjust = 1
-    ),
-    axis.text.y = element_text(size = 15),
-    axis.title.x = element_text(size = 20),
-    axis.title.y = element_text(size = 20),
-    legend.text=element_text(size=15),
-    legend.title=element_text(size=20),
-    plot.title = element_text(size=20))
-
-d <- ggplot(all_rfperfs_gm12878[which(all_rfperfs_gm12878$Predictor=="Distance" & (all_rfperfs_gm12878$Metric=="F1-Score" | all_rfperfs_gm12878$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
-    geom_line(size=2)+
-    geom_point(size=5)+
-    facet_grid(~ Metric)+
-    theme_minimal() +
-    theme_bw()+
-    xlab("") + ylab("") + ylim(-.02,.5) +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+d <- ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="GM12878" & all_rfperfs_mcc$Predictor=="Distance"),], aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     #facet_grid(~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.05,.5) +
      ggtitle("Distance") +
-    scale_color_discrete(name="Re-Sampling Technique")+
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
      theme(axis.text.x = element_text(size=15,
@@
     bottom = text_grob("Resolution", color = "black", size = 20),
-    left = text_grob("Performance", color = "black", rot = 90, size=20)
+    left = text_grob("MCC", color = "black", rot = 90, size=20)
 )
 
-```
-
-##Plots
-
-```{r}
-all_rfperfs <- rbind.data.frame(all_rfperfs_gm12878, all_rfperfs_K562)
-all_rfperfs$CL <- c(rep("GM12878", dim(all_rfperfs_gm12878)[1]), rep("K562", dim(all_rfperfs_K562)[1]))
-
-c <- ggplot(all_rfperfs[which(all_rfperfs$Predictor=="OC" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=CL, group=CL, linetype=CL)) +
-     geom_line(size=1)+
-     geom_point(size=2)+
-     facet_grid(Resampling ~ Metric)+
+#K562
+c2 <- ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="K562" & all_rfperfs_mcc$Predictor=="OC"),], aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     #facet_grid(~ Metric)+
      theme_minimal() +
@@
      ggtitle("Overlap Counts") +
-     scale_color_discrete(name="Cell Line")+
-     guides(shape=FALSE, linetype=FALSE)+
-     theme(axis.text.x = element_text(size=10,
-                                      angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      hjust = 1
-     ),
-     axis.text.y = element_text(size = 10),
-     axis.title.x = element_text(size = 15),
-     axis.title.y = element_text(size = 15),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=15),
-     plot.title = element_text(size=15))
-
-p <- ggplot(all_rfperfs[which(all_rfperfs$Predictor=="OP" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=CL, group=CL, linetype=CL)) +
-     geom_line(size=1)+
-     geom_point(size=2)+
-     facet_grid(Resampling ~ Metric)+
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+p2 <- ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="K562" & all_rfperfs_mcc$Predictor=="OP"),], aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     #facet_grid(~ Metric)+
      theme_minimal() +
@@
      ggtitle("Overlap Percents") +
-     scale_color_discrete(name="Cell Line")+
-     guides(shape=FALSE, linetype=FALSE)+
-     theme(axis.text.x = element_text(size=10,
-                                      angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      hjust = 1
-     ),
-     axis.text.y = element_text(size = 10),
-     axis.title.x = element_text(size = 15),
-     axis.title.y = element_text(size = 15),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=15),
-     plot.title = element_text(size=15))
-
-d <- ggplot(all_rfperfs[which(all_rfperfs$Predictor=="Distance" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=CL, group=CL, linetype=CL)) +
-     geom_line(size=1)+
-     geom_point(size=2)+
-     facet_grid(Resampling ~ Metric)+
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+d2 <- ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="K562" & all_rfperfs_mcc$Predictor=="Distance"),], aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     #facet_grid(~ Metric)+
      theme_minimal() +
@@
      ggtitle("Distance") +
-     scale_color_discrete(name="Cell Line")+
-     guides(shape=FALSE, linetype=FALSE)+
-     theme(axis.text.x = element_text(size=10,
-                                      angle = 45, 
-                                      #margin = ggplot2::margin(t = 35),
-                                      hjust = 1
-     ),
-     axis.text.y = element_text(size = 10),
-     axis.title.x = element_text(size = 15),
-     axis.title.y = element_text(size = 15),
-     legend.text=element_text(size=15),
-     legend.title=element_text(size=15),
-     plot.title = element_text(size=15))
-
-figure <- ggarrange(c,p,d,
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+figure2 <- ggarrange(c2,p2,d2,
                 ncol = 3, nrow = 1, 
                 common.legend = TRUE, 
-                legend = "top")
-figure
-annotate_figure(figure,
+                legend = "top",
+                labels = "AUTO",
+                font.label = list(size=20))
+figure2
+annotate_figure(figure2,
     bottom = text_grob("Resolution", color = "black", size = 20),
-    left = text_grob("Performance", color = "black", rot = 90, size=20)
+    left = text_grob("MCC", color = "black", rot = 90, size=20)
 )

### 2019-05-09 Manuscript/Supplementary/supplementary_legends.Rmd
editted legends

@@
 **Supplementary Figure 1.
-Distance densities from centers of genomic bins to closest annotation.** Density curves of the distances (in millions of base pairs) from the center of genomic bins to the center of the nearest respective annotation for the GM12878 (left column) and K562 (right column) cell lines respectively.
-Each curve represents the raw (red) and $log_{2}$ transformed (blue) distance profiles for each annotation, across each of the 4 resolutions (A-D).
+GM12878 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb.
+(E-H) $Log_{2}$ transformed distances for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb.
+
+**Supplementary Figure 2.
+K562 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb.
+(E-H) $Log_{2}$ transformed distances for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb.
 

### 2019-05-09 Scripts/evaluating_dist_densities.Rmd
editted results script

@@
 ##GM12878
-###10kb
 
 ```{r}
-gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
+NTdistance_list_gm12878 <- readRDS("Z:/TAD_data_analysis/NTdistance_list_gm12878.rds")
 
-gm12878_10kb_ld <- gm12878_10kb[,c(1,grep("_dist", names(gm12878_10kb)))]
-
-###############
-#gm12878_10kb_ld <- gm12878_10kb_ld[,c(1:5)]
-###############
-
-gm12878_10kb_d <- gm12878_10kb_ld
-gm12878_10kb_d[,-1] <- exp(gm12878_10kb_ld[,-1]) - 1
-gm12878_10kb_d$Average_dist <- rowMeans(gm12878_10kb_d[,-1])
-
-gm12878_10kb_ld$Average_dist <- rowMeans(gm12878_10kb_ld[,-1])
-names(gm12878_10kb_ld)[-1] <- paste(substr(names(gm12878_10kb_ld)[-1],
-                                           1, 
-                                           nchar(names(gm12878_10kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-gm12878_10kb_alldist <- cbind.data.frame(gm12878_10kb_d[,-1], gm12878_10kb_ld[,-1])
-
-long10kb <- melt(gm12878_10kb_alldist)
-long10kb$variable <- as.character(long10kb$variable)
-long10kb$Transformation <- NA
-long10kb$Transformation[grep("_logdist", long10kb$variable)] <- rep("Log Distance", length(long10kb$variable[grep("_logdist", long10kb$variable)]))
-long10kb$Transformation[grep("_logdist", long10kb$variable, invert = TRUE)] <- rep("Distance", length(long10kb$variable[grep("_logdist", long10kb$variable, invert = TRUE)]))
-
-table(long10kb$Transformation)
-
-distdensity10kb <- ggplot() + 
-  geom_density(data=long10kb[intersect(grep("_dist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long10kb[grep("Average_dist", long10kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity10kb <- ggplot() + 
-  geom_density(data=long10kb[intersect(grep("logdist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long10kb[grep("Average_logdist", long10kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long10kb$value[long10kb$Transformation=="Distance"] <- long10kb$value[long10kb$Transformation=="Distance"]/1000000
-long10kb <- long10kb[grep("Average", long10kb$variable, invert = TRUE),]
-long10kb$variable <- factor(long10kb$variable)
-long10kb$Transformation <- factor(long10kb$Transformation)
-
-alldensity10kb <- ggplot(long10kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  #geom_vline(xintercept=0, size=1)+
-  #geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("Density")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme_bw()+
-  theme(plot.title = element_text(hjust = 0.5))
+LTdistance_list_gm12878 <- readRDS("Z:/TAD_data_analysis/LTdistance_list_gm12878.rds")
 
@@
 
-###25kb
+### 10kb
+```{r}
+#no transformation
+ntplot10kb_gm12878 <- ggplot(NTdistance_list_gm12878[[1]], aes(x=value, group=variable, color="red")) + 
+  geom_density(alpha=.5) +
+  guides(color = FALSE)+ 
+	xlim(0,30000000) + 
+  xlab("") +
+	ylab("") + 
+  scale_x_continuous(limits = c(0,3e+7),
+                     breaks = c(0, 1e+07, 2e+07, 3e+07),
+                     labels = c(0,1,2,3))+
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
-```{r}
-gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
-
-gm12878_25kb_ld <- gm12878_25kb[,c(1,grep("_dist", names(gm12878_25kb)))]
-
-###############
-#gm12878_25kb_ld <- gm12878_25kb_ld[,c(1:5)]
-###############
-
-gm12878_25kb_d <- gm12878_25kb_ld
-gm12878_25kb_d[,-1] <- exp(gm12878_25kb_ld[,-1]) - 1
-gm12878_25kb_d$Average_dist <- rowMeans(gm12878_25kb_d[,-1])
-
-gm12878_25kb_ld$Average_dist <- rowMeans(gm12878_25kb_ld[,-1])
-names(gm12878_25kb_ld)[-1] <- paste(substr(names(gm12878_25kb_ld)[-1],
-                                           1, 
-                                           nchar(names(gm12878_25kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-gm12878_25kb_alldist <- cbind.data.frame(gm12878_25kb_d[,-1], gm12878_25kb_ld[,-1])
-
-long25kb <- melt(gm12878_25kb_alldist)
-long25kb$variable <- as.character(long25kb$variable)
-long25kb$Transformation <- NA
-long25kb$Transformation[grep("_logdist", long25kb$variable)] <- rep("Log Distance", length(long25kb$variable[grep("_logdist", long25kb$variable)]))
-long25kb$Transformation[grep("_logdist", long25kb$variable, invert = TRUE)] <- rep("Distance", length(long25kb$variable[grep("_logdist", long25kb$variable, invert = TRUE)]))
-
-table(long25kb$Transformation)
-
-distdensity25kb <- ggplot() + 
-  geom_density(data=long25kb[intersect(grep("_dist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long25kb[grep("Average_dist", long25kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
+#log transformation
+ltplot10kb_gm12878 <- ggplot(LTdistance_list_gm12878[[1]], aes(x=value, group=variable)) + 
+  geom_density(alpha=.5, color="blue") +
+  guides(color = FALSE)+ 
+	#xlim(0,30000000) + 
   xlab("") +
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
+	ylab("") + 
+  #scale_x_continuous(limits = c(0,3e+7),
+  #                   breaks = c(0, 1e+07, 2e+07, 3e+07),
+  #                   labels = c(0,1,2,3))+
   theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity25kb <- ggplot() + 
-  geom_density(data=long25kb[intersect(grep("logdist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long25kb[grep("Average_logdist", long25kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) +  
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long25kb$value[long25kb$Transformation=="Distance"] <- long25kb$value[long25kb$Transformation=="Distance"]/1000000
-long25kb <- long25kb[grep("Average", long25kb$variable, invert = TRUE),]
-long25kb$variable <- factor(long25kb$variable)
-long25kb$Transformation <- factor(long25kb$Transformation)
-
-alldensity25kb <- ggplot(long25kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  #geom_vline(xintercept=0, size=1)+
-  #geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("Density")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme_bw()+
-  theme(plot.title = element_text(hjust = 0.5))
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
@@
 
-###50kb
+### 25kb
+```{r}
+#no transformation
+ntplot25kb_gm12878 <- ggplot(NTdistance_list_gm12878[[2]], aes(x=value, group=variable, color="red")) + 
+  geom_density(alpha=.5) +
+  guides(color = FALSE)+ 
+	xlim(0,30000000) + 
+  xlab("") +
+	ylab("") + 
+  scale_x_continuous(limits = c(0,3e+7),
+                     breaks = c(0, 1e+07, 2e+07, 3e+07),
+                     labels = c(0,1,2,3))+
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
-```{r}
-gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
-
-gm12878_50kb_ld <- gm12878_50kb[,c(1,grep("_dist", names(gm12878_50kb)))]
-
-###############
-#gm12878_50kb_ld <- gm12878_50kb_ld[,c(1:5)]
-###############
-
-gm12878_50kb_d <- gm12878_50kb_ld
-gm12878_50kb_d[,-1] <- exp(gm12878_50kb_ld[,-1]) - 1
-gm12878_50kb_d$Average_dist <- rowMeans(gm12878_50kb_d[,-1])
-
-gm12878_50kb_ld$Average_dist <- rowMeans(gm12878_50kb_ld[,-1])
-names(gm12878_50kb_ld)[-1] <- paste(substr(names(gm12878_50kb_ld)[-1],
-                                           1, 
-                                           nchar(names(gm12878_50kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-gm12878_50kb_alldist <- cbind.data.frame(gm12878_50kb_d[,-1], gm12878_50kb_ld[,-1])
-
-long50kb <- melt(gm12878_50kb_alldist)
-long50kb$variable <- as.character(long50kb$variable)
-long50kb$Transformation <- NA
-long50kb$Transformation[grep("_logdist", long50kb$variable)] <- rep("Log Distance", length(long50kb$variable[grep("_logdist", long50kb$variable)]))
-long50kb$Transformation[grep("_logdist", long50kb$variable, invert = TRUE)] <- rep("Distance", length(long50kb$variable[grep("_logdist", long50kb$variable, invert = TRUE)]))
-
-table(long50kb$Transformation)
-
-distdensity50kb <- ggplot() + 
-  geom_density(data=long50kb[intersect(grep("_dist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long50kb[grep("Average_dist", long50kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
+#log transformation
+ltplot25kb_gm12878 <- ggplot(LTdistance_list_gm12878[[2]], aes(x=value, group=variable)) + 
+  geom_density(alpha=.5, color="blue") +
+  guides(color = FALSE)+ 
+	#xlim(0,30000000) + 
   xlab("") +
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
+	ylab("") + 
+  #scale_x_continuous(limits = c(0,3e+7),
+  #                   breaks = c(0, 1e+07, 2e+07, 3e+07),
+  #                   labels = c(0,1,2,3))+
   theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity50kb <- ggplot() + 
-  geom_density(data=long50kb[intersect(grep("logdist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long50kb[grep("Average_logdist", long50kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long50kb$value[long50kb$Transformation=="Distance"] <- long50kb$value[long50kb$Transformation=="Distance"]/1000000
-long50kb <- long50kb[grep("Average", long50kb$variable, invert = TRUE),]
-long50kb$variable <- factor(long50kb$variable)
-long50kb$Transformation <- factor(long50kb$Transformation)
-
-alldensity50kb <- ggplot(long50kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  #geom_vline(xintercept=0, size=1)+
-  #geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("Density")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme_bw()+
-  theme(plot.title = element_text(hjust = 0.5))
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
@@
 
-###100kb
+### 50kb
+```{r}
+#no transformation
+ntplot50kb_gm12878 <- ggplot(NTdistance_list_gm12878[[3]], aes(x=value, group=variable, color="red")) + 
+  geom_density(alpha=.5) +
+  guides(color = FALSE)+ 
+	xlim(0,30000000) + 
+  xlab("") +
+	ylab("") + 
+  scale_x_continuous(limits = c(0,3e+7),
+                     breaks = c(0, 1e+07, 2e+07, 3e+07),
+                     labels = c(0,1,2,3))+
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
+#log transformation
+ltplot50kb_gm12878 <- ggplot(LTdistance_list_gm12878[[3]], aes(x=value, group=variable)) + 
+  geom_density(alpha=.5, color="blue") +
+  guides(color = FALSE)+ 
+	#xlim(0,30000000) + 
+  xlab("") +
+	ylab("") + 
+  #scale_x_continuous(limits = c(0,3e+7),
+  #                   breaks = c(0, 1e+07, 2e+07, 3e+07),
+  #                   labels = c(0,1,2,3))+
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+```
+
+### 100kb
 ```{r}
-gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
+#no transformation
+ntplot100kb_gm12878 <- ggplot(NTdistance_list_gm12878[[4]], aes(x=value, group=variable, color="red")) + 
+  geom_density(alpha=.5) +
+  guides(color = FALSE)+ 
+	xlim(0,30000000) + 
+  xlab("") +
+	ylab("") + 
+  scale_x_continuous(limits = c(0,3e+7),
+                     breaks = c(0, 1e+07, 2e+07, 3e+07),
+                     labels = c(0,1,2,3))+
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
-gm12878_100kb_ld <- gm12878_100kb[,c(1,grep("_dist", names(gm12878_100kb)))]
-
-###############
-#gm12878_100kb_ld <- gm12878_100kb_ld[,c(1:5)]
-###############
-
-gm12878_100kb_d <- gm12878_100kb_ld
-gm12878_100kb_d[,-1] <- exp(gm12878_100kb_ld[,-1]) - 1
-gm12878_100kb_d$Average_dist <- rowMeans(gm12878_100kb_d[,-1])
-
-gm12878_100kb_ld$Average_dist <- rowMeans(gm12878_100kb_ld[,-1])
-names(gm12878_100kb_ld)[-1] <- paste(substr(names(gm12878_100kb_ld)[-1],
-                                           1, 
-                                           nchar(names(gm12878_100kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-gm12878_100kb_alldist <- cbind.data.frame(gm12878_100kb_d[,-1], gm12878_100kb_ld[,-1])
-
-long100kb <- melt(gm12878_100kb_alldist)
-long100kb$variable <- as.character(long100kb$variable)
-long100kb$Transformation <- NA
-long100kb$Transformation[grep("_logdist", long100kb$variable)] <- rep("Log Distance", length(long100kb$variable[grep("_logdist", long100kb$variable)]))
-long100kb$Transformation[grep("_logdist", long100kb$variable, invert = TRUE)] <- rep("Distance", length(long100kb$variable[grep("_logdist", long100kb$variable, invert = TRUE)]))
-
-table(long100kb$Transformation)
-
-distdensity100kb <- ggplot() + 
-  geom_density(data=long100kb[intersect(grep("_dist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long100kb[grep("Average_dist", long100kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("No Transformation") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
+#log transformation
+ltplot100kb_gm12878 <- ggplot(LTdistance_list_gm12878[[4]], aes(x=value, group=variable)) + 
+  geom_density(alpha=.5, color="blue") +
+  guides(color = FALSE)+ 
+	#xlim(0,30000000) + 
+  xlab("") +
+	ylab("") + 
+  #scale_x_continuous(limits = c(0,3e+7),
+  #                   breaks = c(0, 1e+07, 2e+07, 3e+07),
+  #                   labels = c(0,1,2,3))+
   theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity100kb <- ggplot() + 
-  geom_density(data=long100kb[intersect(grep("logdist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long100kb[grep("Average_logdist", long100kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("Log Tranformation") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long100kb$value[long100kb$Transformation=="Distance"] <- long100kb$value[long100kb$Transformation=="Distance"]/1000000
-long100kb <- long100kb[grep("Average", long100kb$variable, invert = TRUE),]
-long100kb$variable <- factor(long100kb$variable)
-long100kb$Transformation <- factor(long100kb$Transformation)
-
-alldensity100kb <- ggplot(long100kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  #geom_vline(xintercept=0, size=1)+
-  #geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("Density")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme_bw()+
-  theme(plot.title = element_text(hjust = 0.5))
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
@@
 ##K562
-###10kb
 
 ```{r}
-K562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
+NTdistance_list_K562 <- readRDS("Z:/TAD_data_analysis/NTdistance_list_K562.rds")
 
-K562_10kb_ld <- K562_10kb[,c(1,grep("_dist", names(K562_10kb)))]
-
-###############
-#K562_10kb_ld <- K562_10kb_ld[,c(1:5)]
-###############
-
-K562_10kb_d <- K562_10kb_ld
-K562_10kb_d[,-1] <- exp(K562_10kb_ld[,-1]) - 1
-K562_10kb_d$Average_dist <- rowMeans(K562_10kb_d[,-1])
-
-K562_10kb_ld$Average_dist <- rowMeans(K562_10kb_ld[,-1])
-names(K562_10kb_ld)[-1] <- paste(substr(names(K562_10kb_ld)[-1],
-                                           1, 
-                                           nchar(names(K562_10kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-K562_10kb_alldist <- cbind.data.frame(K562_10kb_d[,-1], K562_10kb_ld[,-1])
-
-long10kb <- melt(K562_10kb_alldist)
-long10kb$variable <- as.character(long10kb$variable)
-long10kb$Transformation <- NA
-long10kb$Transformation[grep("_logdist", long10kb$variable)] <- rep("Log Distance", length(long10kb$variable[grep("_logdist", long10kb$variable)]))
-long10kb$Transformation[grep("_logdist", long10kb$variable, invert = TRUE)] <- rep("Distance", length(long10kb$variable[grep("_logdist", long10kb$variable, invert = TRUE)]))
-
-table(long10kb$Transformation)
-
-distdensity10kb <- ggplot() + 
-  geom_density(data=long10kb[intersect(grep("_dist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long10kb[grep("Average_dist", long10kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity10kb <- ggplot() + 
-  geom_density(data=long10kb[intersect(grep("logdist", long10kb$variable), grep("Average", long10kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long10kb[grep("Average_logdist", long10kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long10kb$value[long10kb$Transformation=="Distance"] <- long10kb$value[long10kb$Transformation=="Distance"]/1000000
-long10kb <- long10kb[grep("Average", long10kb$variable, invert = TRUE),]
-long10kb$variable <- factor(long10kb$variable)
-long10kb$Transformation <- factor(long10kb$Transformation)
-
-alldensity10kb_k562 <- ggplot(long10kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  #geom_vline(xintercept=0, size=1)+
-  #geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("Density")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme_bw()+
-  theme(plot.title = element_text(hjust = 0.5))
+LTdistance_list_K562 <- readRDS("Z:/TAD_data_analysis/LTdistance_list_K562.rds")
 
@@
 
-###25kb
+### 10kb
+```{r}
+#no transformation
+ntplot10kb_K562 <- ggplot(NTdistance_list_K562[[1]], aes(x=value, group=variable, color="red")) + 
+  geom_density(alpha=.5) +
+  guides(color = FALSE)+ 
+	xlim(0,30000000) + 
+  xlab("") +
+	ylab("") + 
+  scale_x_continuous(limits = c(0,3e+7),
+                     breaks = c(0, 1e+07, 2e+07, 3e+07),
+                     labels = c(0,1,2,3))+
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
-```{r}
-K562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
-
-K562_25kb_ld <- K562_25kb[,c(1,grep("_dist", names(K562_25kb)))]
-
-###############
-#K562_25kb_ld <- K562_25kb_ld[,c(1:5)]
-###############
-
-K562_25kb_d <- K562_25kb_ld
-K562_25kb_d[,-1] <- exp(K562_25kb_ld[,-1]) - 1
-K562_25kb_d$Average_dist <- rowMeans(K562_25kb_d[,-1])
-
-K562_25kb_ld$Average_dist <- rowMeans(K562_25kb_ld[,-1])
-names(K562_25kb_ld)[-1] <- paste(substr(names(K562_25kb_ld)[-1],
-                                           1, 
-                                           nchar(names(K562_25kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-K562_25kb_alldist <- cbind.data.frame(K562_25kb_d[,-1], K562_25kb_ld[,-1])
-
-long25kb <- melt(K562_25kb_alldist)
-long25kb$variable <- as.character(long25kb$variable)
-long25kb$Transformation <- NA
-long25kb$Transformation[grep("_logdist", long25kb$variable)] <- rep("Log Distance", length(long25kb$variable[grep("_logdist", long25kb$variable)]))
-long25kb$Transformation[grep("_logdist", long25kb$variable, invert = TRUE)] <- rep("Distance", length(long25kb$variable[grep("_logdist", long25kb$variable, invert = TRUE)]))
-
-table(long25kb$Transformation)
-
-distdensity25kb <- ggplot() + 
-  geom_density(data=long25kb[intersect(grep("_dist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long25kb[grep("Average_dist", long25kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
+#log transformation
+ltplot10kb_K562 <- ggplot(LTdistance_list_K562[[1]], aes(x=value, group=variable)) + 
+  geom_density(alpha=.5, color="blue") +
+  guides(color = FALSE)+ 
+	#xlim(0,30000000) + 
   xlab("") +
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
+	ylab("") + 
+  #scale_x_continuous(limits = c(0,3e+7),
+  #                   breaks = c(0, 1e+07, 2e+07, 3e+07),
+  #                   labels = c(0,1,2,3))+
   theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity25kb <- ggplot() + 
-  geom_density(data=long25kb[intersect(grep("logdist", long25kb$variable), grep("Average", long25kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long25kb[grep("Average_logdist", long25kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long25kb$value[long25kb$Transformation=="Distance"] <- long25kb$value[long25kb$Transformation=="Distance"]/1000000
-long25kb <- long25kb[grep("Average", long25kb$variable, invert = TRUE),]
-long25kb$variable <- factor(long25kb$variable)
-long25kb$Transformation <- factor(long25kb$Transformation)
-
-alldensity25kb_k562 <- ggplot(long25kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  #geom_vline(xintercept=0, size=1)+
-  #geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("Density")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme_bw()+
-  theme(plot.title = element_text(hjust = 0.5))
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
@@
 
-###50kb
+### 25kb
+```{r}
+#no transformation
+ntplot25kb_K562 <- ggplot(NTdistance_list_K562[[2]], aes(x=value, group=variable, color="red")) + 
+  geom_density(alpha=.5) +
+  guides(color = FALSE)+ 
+	xlim(0,30000000) + 
+  xlab("") +
+	ylab("") + 
+  scale_x_continuous(limits = c(0,3e+7),
+                     breaks = c(0, 1e+07, 2e+07, 3e+07),
+                     labels = c(0,1,2,3))+
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
-```{r}
-K562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
-
-K562_50kb_ld <- K562_50kb[,c(1,grep("_dist", names(K562_50kb)))]
-
-###############
-#K562_50kb_ld <- K562_50kb_ld[,c(1:5)]
-###############
-
-K562_50kb_d <- K562_50kb_ld
-K562_50kb_d[,-1] <- exp(K562_50kb_ld[,-1]) - 1
-K562_50kb_d$Average_dist <- rowMeans(K562_50kb_d[,-1])
-
-K562_50kb_ld$Average_dist <- rowMeans(K562_50kb_ld[,-1])
-names(K562_50kb_ld)[-1] <- paste(substr(names(K562_50kb_ld)[-1],
-                                           1, 
-                                           nchar(names(K562_50kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-K562_50kb_alldist <- cbind.data.frame(K562_50kb_d[,-1], K562_50kb_ld[,-1])
-
-long50kb <- melt(K562_50kb_alldist)
-long50kb$variable <- as.character(long50kb$variable)
-long50kb$Transformation <- NA
-long50kb$Transformation[grep("_logdist", long50kb$variable)] <- rep("Log Distance", length(long50kb$variable[grep("_logdist", long50kb$variable)]))
-long50kb$Transformation[grep("_logdist", long50kb$variable, invert = TRUE)] <- rep("Distance", length(long50kb$variable[grep("_logdist", long50kb$variable, invert = TRUE)]))
-
-table(long50kb$Transformation)
-
-distdensity50kb <- ggplot() + 
-  geom_density(data=long50kb[intersect(grep("_dist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long50kb[grep("Average_dist", long50kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
+#log transformation
+ltplot25kb_K562 <- ggplot(LTdistance_list_K562[[2]], aes(x=value, group=variable)) + 
+  geom_density(alpha=.5, color="blue") +
+  guides(color = FALSE)+ 
+	#xlim(0,30000000) + 
   xlab("") +
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
+	ylab("") + 
+  #scale_x_continuous(limits = c(0,3e+7),
+  #                   breaks = c(0, 1e+07, 2e+07, 3e+07),
+  #                   labels = c(0,1,2,3))+
   theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity50kb <- ggplot() + 
-  geom_density(data=long50kb[intersect(grep("logdist", long50kb$variable), grep("Average", long50kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long50kb[grep("Average_logdist", long50kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long50kb$value[long50kb$Transformation=="Distance"] <- long50kb$value[long50kb$Transformation=="Distance"]/1000000
-long50kb <- long50kb[grep("Average", long50kb$variable, invert = TRUE),]
-long50kb$variable <- factor(long50kb$variable)
-long50kb$Transformation <- factor(long50kb$Transformation)
-
-alldensity50kb_k562 <- ggplot(long50kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  #geom_vline(xintercept=0, size=1)+
-  #geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("Density")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme_bw()+
-  theme(plot.title = element_text(hjust = 0.5))
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
@@
 
-###100kb
+### 50kb
+```{r}
+#no transformation
+ntplot50kb_K562 <- ggplot(NTdistance_list_K562[[3]], aes(x=value, group=variable, color="red")) + 
+  geom_density(alpha=.5) +
+  guides(color = FALSE)+ 
+	xlim(0,30000000) + 
+  xlab("") +
+	ylab("") + 
+  scale_x_continuous(limits = c(0,3e+7),
+                     breaks = c(0, 1e+07, 2e+07, 3e+07),
+                     labels = c(0,1,2,3))+
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
+#log transformation
+ltplot50kb_K562 <- ggplot(LTdistance_list_K562[[3]], aes(x=value, group=variable)) + 
+  geom_density(alpha=.5, color="blue") +
+  guides(color = FALSE)+ 
+	#xlim(0,30000000) + 
+  xlab("") +
+	ylab("") + 
+  #scale_x_continuous(limits = c(0,3e+7),
+  #                   breaks = c(0, 1e+07, 2e+07, 3e+07),
+  #                   labels = c(0,1,2,3))+
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+```
+
+### 100kb
 ```{r}
-K562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
+#no transformation
+ntplot100kb_K562 <- ggplot(NTdistance_list_K562[[4]], aes(x=value, group=variable, color="red")) + 
+  geom_density(alpha=.5) +
+  guides(color = FALSE)+ 
+	xlim(0,30000000) + 
+  xlab("") +
+	ylab("") + 
+  scale_x_continuous(limits = c(0,3e+7),
+                     breaks = c(0, 1e+07, 2e+07, 3e+07),
+                     labels = c(0,1,2,3))+
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
-K562_100kb_ld <- K562_100kb[,c(1,grep("_dist", names(K562_100kb)))]
-
-###############
-#K562_100kb_ld <- K562_100kb_ld[,c(1:5)]
-###############
-
-K562_100kb_d <- K562_100kb_ld
-K562_100kb_d[,-1] <- exp(K562_100kb_ld[,-1]) - 1
-K562_100kb_d$Average_dist <- rowMeans(K562_100kb_d[,-1])
-
-K562_100kb_ld$Average_dist <- rowMeans(K562_100kb_ld[,-1])
-names(K562_100kb_ld)[-1] <- paste(substr(names(K562_100kb_ld)[-1],
-                                           1, 
-                                           nchar(names(K562_100kb_ld)[-1])-4), 
-                                    "logdist", 
-                                    sep="")
-
-K562_100kb_alldist <- cbind.data.frame(K562_100kb_d[,-1], K562_100kb_ld[,-1])
-
-long100kb <- melt(K562_100kb_alldist)
-long100kb$variable <- as.character(long100kb$variable)
-long100kb$Transformation <- NA
-long100kb$Transformation[grep("_logdist", long100kb$variable)] <- rep("Log Distance", length(long100kb$variable[grep("_logdist", long100kb$variable)]))
-long100kb$Transformation[grep("_logdist", long100kb$variable, invert = TRUE)] <- rep("Distance", length(long100kb$variable[grep("_logdist", long100kb$variable, invert = TRUE)]))
-
-table(long100kb$Transformation)
-
-distdensity100kb <- ggplot() + 
-  geom_density(data=long100kb[intersect(grep("_dist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long100kb[grep("Average_dist", long100kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
+#log transformation
+ltplot100kb_K562 <- ggplot(LTdistance_list_K562[[4]], aes(x=value, group=variable)) + 
+  geom_density(alpha=.5, color="blue") +
+  guides(color = FALSE)+ 
+	#xlim(0,30000000) + 
   xlab("") +
-	xlim(0,2.5e+07) + 
-	ylab("")+ 
-  scale_x_continuous(limits = c(0,2.5e+07), labels = c("0.0e+00"="0", "5.0e+06"="5", "1e+07"="10", "1.5e+07"="15", "2.0e+07"="20", "2.0e+07"="25"))+
-	scale_fill_manual(values="red")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
+	ylab("") + 
+  #scale_x_continuous(limits = c(0,3e+7),
+  #                   breaks = c(0, 1e+07, 2e+07, 3e+07),
+  #                   labels = c(0,1,2,3))+
   theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-logdistdensity100kb <- ggplot() + 
-  geom_density(data=long100kb[intersect(grep("logdist", long100kb$variable), grep("Average", long100kb$variable, invert = TRUE)),]
-               ,aes(x=value, 
-                    group=variable, 
-                    fill=Transformation), alpha=0.01, size=0.5) +
-  #geom_density(data=long100kb[grep("Average_logdist", long100kb$variable),]
-  #             ,aes(x=value), size = 1) +
-  geom_vline(xintercept=0, size=1)+
-  geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("")+ 
-	scale_fill_manual(values="blue")+
-		#labels=as.character(
-		#		unique(
-		#			sort(
-		#				as.numeric(
-		#					substr(as.character(domains$Chromosome),4,nchar(as.character(domains$Chromosome))))))),
-		#values=rainbow(22)) +
-	theme_minimal() +
-  guides(fill=FALSE)+
-  theme(axis.text.y = element_blank())
-  #theme(axis.line = element_line(color="black", size = .5))
-
-#rescaling nontransformed and combining two plots
-long100kb$value[long100kb$Transformation=="Distance"] <- long100kb$value[long100kb$Transformation=="Distance"]/1000000
-long100kb <- long100kb[grep("Average", long100kb$variable, invert = TRUE),]
-long100kb$variable <- factor(long100kb$variable)
-long100kb$Transformation <- factor(long100kb$Transformation)
-
-alldensity100kb_k562 <- ggplot(long100kb, aes(x=value, group=variable, fill=Transformation)) + 
-  geom_density(alpha=0.01) +
-  scale_fill_manual(name = "", labels = c("Untransformed", "Log2"), values = c("red", "blue")) +
-  guides(fill = guide_legend(override.aes = list(alpha=1)))+
-  #geom_vline(xintercept=0, size=1)+
-  #geom_hline(yintercept=0, size=1)+
-	xlab("") + 
-	xlim(0,25) + 
-	ylab("Density")+ 
-  ylim(0,.8)+
-  #ggtitle("GM12878") +
-  theme_minimal() +
-  theme_bw()+
-  theme(plot.title = element_text(hjust = 0.5))
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 
@@
 
+###GM12878
 ```{r}
-#alldistplots <- grid.arrange(distdensity10kb, logdistdensity10kb,
-#             distdensity25kb, logdistdensity25kb,
-#             distdensity50kb, logdistdensity50kb,
-#             distdensity100kb, logdistdensity100kb, ncol=2, nrow=4)
-
-alldistplots <- ggarrange(alldensity10kb,
-                          alldensity10kb_k562,
-                          alldensity25kb,
-                          alldensity25kb_k562,
-                          alldensity50kb,
-                          alldensity50kb_k562,
-                          alldensity100kb,
-                          alldensity100kb_k562, 
-          ncol=2, 
-          nrow=4,
-          #labels = c("A","", "B","", "C","", "D",""),
-          legend = "bottom",
-          common.legend = TRUE)
-
-annotate_figure(alldistplots,
-                bottom = text_grob("Distance to Nearest TAD Boundary \n (in millions of basepairs)", 
+allplots_gm12878 <- ggarrange(ntplot10kb_gm12878,
+                          ntplot25kb_gm12878,
+                          ntplot50kb_gm12878,
+                          ntplot100kb_gm12878, 
+          ncol=4, 
+          nrow=1,
+          labels = c("A", "B", "C", "D"),
+          font.label = list(size=20))
+allplots_gm12878
+annotate_figure(allplots_gm12878,
+                bottom = text_grob("Distance (in millions of basepairs)", 
                                    color = "black", 
@@
                                  rot = 90))
+
+allplots_gm12878 <- ggarrange(ltplot10kb_gm12878,
+                          ltplot25kb_gm12878,
+                          ltplot50kb_gm12878,
+                          ltplot100kb_gm12878, 
+          ncol=4, 
+          nrow=1,
+          labels = c("E", "F", "G", "H"),
+          font.label = list(size=20))
+allplots_gm12878
+annotate_figure(allplots_gm12878,
+                bottom = text_grob("Log2 Transformed Distance", 
+                                   color = "black", 
+                                   face = "bold", 
+                                   size = 15),
+                left = text_grob("Density", 
+                                 color = "black",
+                                 size = 15,
+                                 rot = 90))
+
 ```
+
+###K562
+
+```{r}
+allplots_K562 <- ggarrange(ntplot10kb_K562,
+                          ntplot25kb_K562,
+                          ntplot50kb_K562,
+                          ntplot100kb_K562, 
+          ncol=4, 
+          nrow=1,
+          labels = c("A", "B", "C", "D"),
+          font.label = list(size=20))
+allplots_K562
+annotate_figure(allplots_K562,
+                bottom = text_grob("Distance (in millions of basepairs)", 
+                                   color = "black", 
+                                   face = "bold", 
+                                   size = 15),
+                left = text_grob("Density", 
+                                 color = "black",
+                                 size = 15,
+                                 rot = 90))
+
+allplots_K562 <- ggarrange(ltplot10kb_K562,
+                          ltplot25kb_K562,
+                          ltplot50kb_K562,
+                          ltplot100kb_K562, 
+          ncol=4, 
+          nrow=1,
+          labels = c("E", "F", "G", "H"),
+          font.label = list(size=20))
+allplots_K562
+annotate_figure(allplots_K562,
+                bottom = text_grob("Log2 Transformed Distance", 
+                                   color = "black", 
+                                   face = "bold", 
+                                   size = 15),
+                left = text_grob("Density", 
+                                 color = "black",
+                                 size = 15,
+                                 rot = 90))
+
+```

### 2019-05-09 Manuscript/manuscript.Rmd
editted manuscript and added to to do

@@
 The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
-<!--For each of the 4 data resolutions, a total of 8008, 4869, 2449, and 1075 unique TADs were extracted from the GM12878 cell line, and a total of 5828, 4097, 2181, and 986 unique TADs were extracted from the K562 cell line.
-The TADs were distributed throughput the autosomal chromosomes, with larger chromosomes containing more TADs (Supplementary Figure 14; Supplementary Table 8).--> The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained throughput the autosomal chromosomes.
+The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained throughput the autosomal chromosomes.
 TAD boundaries called on Chromosome 9 were omitted from all downstream analyses, for both cell lines, due to the sparcity of the contact matrix at the 10 kb resolution for the K562 cell line.

### 2019-05-11 Manuscript/manuscript.Rmd
fixed latex formatting

@@
 
-We compared the performances of random forest classification models implemented on TAD boundaries called using the arrowhead algorithm [@durand2016juicebox] from replicate Hi-C data for 2 cell lines $L = \{\textit{GM12878}, \textit{K562}\}$, at four different resolutions $R = \{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$.
-[???
-Bad spacing, for the whole paragraph.
-Why you are not using plain and simple Markdown?] For each classifier, we considered 3 separate predictor types as the feature space including $P = \{\textit{OC}, \textit{OP}, \textit{Distance}\}$.
-To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including $B = \{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$.
-Each combination of the above parameters was repeated 21 times (number of autosomal chromosomes, excluding chromosome 9), $C = \{ 1, 2, ..., 22 \}$.
-A system produced from the ensemble framework was defined as: $S = \{\textit{c}, \textit{r}, \textit{p}, \textit{b}\}$, where $l \in L$, $r \in R$, $p \in P$, $b \in B$, and $c \in C$.
-Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2016 (= 2 \times 4 \times 3 \times 4 \times 21)$ separate models.
+We compared the performances of random forest classification models implemented on TAD boundaries called using the arrowhead algorithm [@durand2016juicebox] from replicate Hi-C data for 2 cell lines *L* = { *GM12878*, *K562* }, at four different resolutions *R* = { *10 kb*, *25 kb*, *50 kb*, *100 kb* }.
+For each classifier, we considered 3 separate predictor types as the feature space including *P* = {*OC*, *OP*, *Distance* }.
+To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including *B* = {*None*, *RUS*, *ROS*, *SMOTE* }.
+Each combination of the above parameters was repeated 21 times (number of autosomal chromosomes, excluding chromosome 9), *C* = {*1*, *2*, ..., *22*}.
+A system produced from the ensemble framework was defined as: *S* = {*c*, *r*, *p*, *b*}, where *l* $\in$ *L*, *r* $\in$ *R*, *p* $\in$ *P*, *b* $\in$ *B*, and *c* $\in$ *C*.
+Letting *|X|* denote the cardinality of each set, we evaluated *|L|* $\times$ *|R|* $\times$ *|P|* $\times$ *|B|* different ensemble systems, totaling 2016 (= 2 $\times$ 4 $\times$ 3 $\times$ 4 $\times$ 21) separate models.
 

### 2019-05-12 Manuscript/Tables/table_legends.Rmd
consolidated figure 4 into a table with bin and ir summaries; updated legends

@@
 ```
+
+**Table 1.
+Data Summaries.** The average number of genomic bins and corresponding imbalance ratios, across each of the autosomal chromosomes (omitting chromosome 9), stratified by resolution and cell line.
+The resolution of the Hi-C contact matrix dictated the width of each genomic bin, with lower resolutions corresponding to wider genomic bins.

### 2019-05-12 Manuscript/Tables/table_legends.Rmd
added number of tads called to table1

--- 2019-01-24 Manuscript/Tables/table_legends.Rmd
@@
 ```
+
+**Table 1.
+Data Summaries.** The average number of genomic bins, TADs called, and the corresponding boundaries and imbalance ratios, across each of the autosomal chromosomes (omitting chromosome 9), stratified by resolution and cell line.
+The resolution of the Hi-C contact matrix dictated the width of each genomic bin, with lower resolutions corresponding to wider genomic bins.

### 2019-05-12 Scripts/evaluating_imbalance_ratios.Rmd
editted results script

@@
 
-# Combined
+# Combined Plots
 
@@
 ```
+
+# Combined Tables
+
+```{r}
+cl.per.chr <- character()
+res.per.chr <- character()
+chr.per.chr <- character()
+bins.per.chr <- numeric()
+bounds.per.chr <- numeric()
+ir.per.chr <- numeric()
+
+chrs <- paste0("chr", c(1:8,10:22))
+for(i in c("GM12878","K562")){
+  for(j in c("10kb", "25kb","50kb","100kb")){
+    for(k in 1:length(chrs)){
+      binslist_dat_center <- readRDS(paste0("Z:/TAD_data_analysis/",
+                                            i,
+                                            "/",
+                                            j,
+                                            "/training_testing/binslist",
+                                            gsub("kb","",j),
+                                            "_center.rds"))
+
+      cl.per.chr <- rbind(cl.per.chr, i)
+      res.per.chr <- rbind(res.per.chr, j)
+      chr.per.chr <- rbind(chr.per.chr, chrs[k])
+
+      bins.per.chr <- rbind(bins.per.chr, length(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]]))
+
+      bounds.per.chr <- rbind(bounds.per.chr, table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2])
+
+      ir.per.chr <- rbind(ir.per.chr, table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2]/table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[1])
+
+    }
+  }
+}
+
+irtab <- cbind.data.frame(cl.per.chr,
+                          res.per.chr,
+                          chr.per.chr,
+                          bins.per.chr,
+                          bounds.per.chr,
+                          ir.per.chr)
+colnames(irtab) <- c("cl","res","chr","bins","bounds","ir")
+
+irtab_summ <- irtab %>%
+  group_by(cl, res) %>%
+  summarise(AveBins = mean(bins, na.rm = TRUE),
+            AveBinsSD = sd(bins, na.rm = TRUE),
+            AveBounds = mean(bounds, na.rm = TRUE),
+            AveBoundsSD = sd(bounds, na.rm = TRUE),
+            AveIR = mean(ir, na.rm = TRUE),
+            AveIRSD = sd(ir, na.rm = TRUE))
+```

### 2019-05-12 Manuscript/Figures/figure_legends.Rmd
consolidated figure 4 into a table with bin and ir summaries; updated legends
updated legends

@@
 
-**Figure 4.
-Imbalance Ratios.** Boxplots illustrating the variations in imbalance ratios (IR) across cell line and resolution.
-IR was calculated by dividing the number of chromosome-specific genomic bins that overlapped with flanked TAD boundaries by the number of chromosome-specific genomic bins that did not.
-
 **Figure 5.
@@
 **Figure 6.
-Comparing category-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for GM12878.** Performances, separated by F1-Score and MCC, were compared for models using specific categories of annotations as the feature space including: histone modifications (red), chromatin state segmentations (green), transcription factor binding sites, and a feature space containing all 3 types combined (purple).
+Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for GM12878.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
+Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types.
+The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.
 

### 2019-05-12 Manuscript/Supplementary/supplementary_legends.Rmd
updated legends

@@
 
-**Supplementary Figure 11.
-Comparing category-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for K562.** Performances, separated by F1-Score and MCC, were compared for models using specific categories of annotations as the feature space including: histone modifications (red), chromatin state segmentations (green), transcription factor binding sites, and a feature space containing all 3 types combined (purple).
+**Supplementary Figure 11..
+Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for K562.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
+Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types.
+The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.
 

### 2019-05-12 Scripts/comparing_tfbs_specific_models_with_all_annotations.Rmd
editted results scripts

--- 2019-04-12 Scripts/comparing_tfbs_specific_models_with_all_annotations.Rmd
@@
 
-# TFBS Specific Model Performances
+# GM12878; smote; distance types
 
-## GM12878
-
-### 10 kb
+## 10kb
 
 ```{r}
-#OC
-##None
-rfperf_gm12878_10kb_none_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/tfbs/OC/ENET/RF/rfperf.rds")
+mccdata_gm12878_10kb <- numeric()
 
-#OP
-##None
-rfperf_gm12878_10kb_none_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/tfbs/OP/ENET/RF/rfperf.rds")
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("chromstates", "histones", "tfbs", "all")){
+	  if(j %in% c("chromstates", "histones", "tfbs")){
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_",
+									   j, 
+									   ".rds"))
+	  }else{
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf.rds"))
+	  }
 
-#Distance
-##None
-rfperf_gm12878_10kb_none_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/tfbs/Distance/ENET/RF/rfperf.rds")
+			mccdata_gm12878_10kb <- rbind(mccdata_gm12878_10kb,
+										  perfdata[15,2])
 
-#OC
-##ROS
-rfperf_gm12878_10kb_ros_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/tfbs/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_gm12878_10kb_ros_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/tfbs/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_gm12878_10kb_ros_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/tfbs/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_gm12878_10kb_rus_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/tfbs/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_gm12878_10kb_rus_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/tfbs/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_gm12878_10kb_rus_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/tfbs/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_gm12878_10kb_smote_oc_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/tfbs/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_gm12878_10kb_smote_op_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/tfbs/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_gm12878_10kb_smote_dist_tfbs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/tfbs/Distance/ENET/RF/rfperf.rds")
-
-all_rfperfs_gm12878_tfbs <- data.frame(Resampling=rep(c(rep("None",3),
-                                                    rep("ROS",3),
-                                                    rep("RUS",3),
-                                                    rep("SMOTE",3)),2),
-                                       Predictor=rep(c("OC","OP","Distance"),8),
-                                       Metric=c(rep("F1-Score",12), 
-                                                rep("MCC",12)),
-                                       Annotations=rep("TFBS Only",24)
-                                       )
-
-all_rfperfs_gm12878_tfbs$Predictor <- factor(all_rfperfs_gm12878_tfbs$Predictor, levels=c("OC", "OP", "Distance"))
-all_rfperfs_gm12878_tfbs$Metric <- factor(all_rfperfs_gm12878_tfbs$Metric, levels=c("F1-Score", "MCC"))
-all_rfperfs_gm12878_tfbs$Resampling <- factor(all_rfperfs_gm12878_tfbs$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))
-
-all_rfperfs_gm12878_tfbs$Performance <- c(rfperf_gm12878_10kb_none_oc_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_none_op_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_none_dist_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_ros_oc_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_ros_op_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_ros_dist_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_rus_oc_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_rus_op_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_rus_dist_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_smote_oc_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_smote_op_tfbs[16,2], #f1
-                                          rfperf_gm12878_10kb_smote_dist_tfbs[16,2], #f1
-
-                                     rfperf_gm12878_10kb_none_oc_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_none_op_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_none_dist_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_ros_oc_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_ros_op_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_ros_dist_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_rus_oc_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_rus_op_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_rus_dist_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_smote_oc_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_smote_op_tfbs[15,2], #mcc
-                                          rfperf_gm12878_10kb_smote_dist_tfbs[15,2] #mcc
-
-                                     )
+	}
+}
 
@@
 
-# All Annotations
-
-## GM12878
-
-### 10 kb
+## 25kb
 
 ```{r}
-#OC
-##None
-rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+mccdata_gm12878_25kb <- numeric()
 
-#OP
-##None
-rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("chromstates", "histones", "tfbs", "all")){
+	  if(j %in% c("chromstates", "histones", "tfbs")){
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_",
+									   j, 
+									   ".rds"))
+	  }else{
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf.rds"))
+	  }
 
-#Distance
-##None
-rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+			mccdata_gm12878_25kb <- rbind(mccdata_gm12878_25kb,
+										  perfdata[15,2])
 
-#OC
-##ROS
-rfperf_gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
+	}
+}
 
-#OP
-##ROS
-rfperf_gm12878_10kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
+```
 
-#Distance
-##ROS
-rfperf_gm12878_10kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
+## 50kb
 
-#OC
-##RUS
-rfperf_gm12878_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
+```{r}
+mccdata_gm12878_50kb <- numeric()
 
-#OP
-##RUS
-rfperf_gm12878_10kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("chromstates", "histones", "tfbs", "all")){
+	  if(j %in% c("chromstates", "histones", "tfbs")){
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_",
+									   j, 
+									   ".rds"))
+	  }else{
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf.rds"))
+	  }
 
-#Distance
-##RUS
-rfperf_gm12878_10kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
+			mccdata_gm12878_50kb <- rbind(mccdata_gm12878_50kb,
+										  perfdata[15,2])
 
-#OC
-##SMOTE
-rfperf_gm12878_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
+	}
+}
 
-#OP
-##SMOTE
-rfperf_gm12878_10kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
+```
 
-#Distance
-##SMOTE
-rfperf_gm12878_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+## 100kb
 
-all_rfperfs_gm12878 <- data.frame(Resampling=rep(c(rep("None",3),
-                                                    rep("ROS",3),
-                                                    rep("RUS",3),
-                                                    rep("SMOTE",3)),2),
-                                       Predictor=rep(c("OC","OP","Distance"),8),
-                                       Metric=c(rep("F1-Score",12), 
-                                                rep("MCC",12)),
-                                       Annotations=rep("ALL Types",24)
-                                       )
+```{r}
+mccdata_gm12878_100kb <- numeric()
 
-all_rfperfs_gm12878$Predictor <- factor(all_rfperfs_gm12878$Predictor, levels=c("OC", "OP", "Distance"))
-all_rfperfs_gm12878$Metric <- factor(all_rfperfs_gm12878$Metric, levels=c("F1-Score", "MCC"))
-all_rfperfs_gm12878$Resampling <- factor(all_rfperfs_gm12878$Resampling, levels=c("None", "ROS", "RUS", "SMOTE"))
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("chromstates", "histones", "tfbs", "all")){
+	  if(j %in% c("chromstates", "histones", "tfbs")){
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_",
+									   j, 
+									   ".rds"))
+	  }else{
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf.rds"))
+	  }
 
-all_rfperfs_gm12878$Performance <- c(rfperf_gm12878_10kb_none_oc[16,2], #f1
-                                          rfperf_gm12878_10kb_none_op[16,2], #f1
-                                          rfperf_gm12878_10kb_none_dist[16,2], #f1
-                                          rfperf_gm12878_10kb_ros_oc[16,2], #f1
-                                          rfperf_gm12878_10kb_ros_op[16,2], #f1
-                                          rfperf_gm12878_10kb_ros_dist[16,2], #f1
-                                          rfperf_gm12878_10kb_rus_oc[16,2], #f1
-                                          rfperf_gm12878_10kb_rus_op[16,2], #f1
-                                          rfperf_gm12878_10kb_rus_dist[16,2], #f1
-                                          rfperf_gm12878_10kb_smote_oc[16,2], #f1
-                                          rfperf_gm12878_10kb_smote_op[16,2], #f1
-                                          rfperf_gm12878_10kb_smote_dist[16,2], #f1
+			mccdata_gm12878_100kb <- rbind(mccdata_gm12878_100kb,
+										  perfdata[15,2])
 
-                                     rfperf_gm12878_10kb_none_oc[15,2], #mcc
-                                          rfperf_gm12878_10kb_none_op[15,2], #mcc
-                                          rfperf_gm12878_10kb_none_dist[15,2], #mcc
-                                          rfperf_gm12878_10kb_ros_oc[15,2], #mcc
-                                          rfperf_gm12878_10kb_ros_op[15,2], #mcc
-                                          rfperf_gm12878_10kb_ros_dist[15,2], #mcc
-                                          rfperf_gm12878_10kb_rus_oc[15,2], #mcc
-                                          rfperf_gm12878_10kb_rus_op[15,2], #mcc
-                                          rfperf_gm12878_10kb_rus_dist[15,2], #mcc
-                                          rfperf_gm12878_10kb_smote_oc[15,2], #mcc
-                                          rfperf_gm12878_10kb_smote_op[15,2], #mcc
-                                          rfperf_gm12878_10kb_smote_dist[15,2] #mcc
+	}
+}
 
-                                     )
+```
+
+# K562; smote; distance types
+
+## 10kb
+
+```{r}
+mccdata_K562_10kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("chromstates", "histones", "tfbs", "all")){
+	  if(j %in% c("chromstates", "histones", "tfbs")){
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_",
+									   j, 
+									   ".rds"))
+	  }else{
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf.rds"))
+	  }
+
+			mccdata_K562_10kb <- rbind(mccdata_K562_10kb,
+										  perfdata[15,2])
+
+	}
+}
+
+```
+
+## 25kb
+
+```{r}
+mccdata_K562_25kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("chromstates", "histones", "tfbs", "all")){
+	  if(j %in% c("chromstates", "histones", "tfbs")){
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_",
+									   j, 
+									   ".rds"))
+	  }else{
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf.rds"))
+	  }
+
+			mccdata_K562_25kb <- rbind(mccdata_K562_25kb,
+										  perfdata[15,2])
+
+	}
+}
+
+```
+
+## 50kb
+
+```{r}
+mccdata_K562_50kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("chromstates", "histones", "tfbs", "all")){
+	  if(j %in% c("chromstates", "histones", "tfbs")){
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_",
+									   j, 
+									   ".rds"))
+	  }else{
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf.rds"))
+	  }
+
+			mccdata_K562_50kb <- rbind(mccdata_K562_50kb,
+										  perfdata[15,2])
+
+	}
+}
+
+```
+
+## 100kb
+
+```{r}
+mccdata_K562_100kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("chromstates", "histones", "tfbs", "all")){
+	  if(j %in% c("chromstates", "histones", "tfbs")){
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_",
+									   j, 
+									   ".rds"))
+	  }else{
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf.rds"))
+	  }
+
+			mccdata_K562_100kb <- rbind(mccdata_K562_100kb,
+										  perfdata[15,2])
+
+	}
+}
 
@@
 
-## Comparing 10 kb
+```{r}
+all_rfperfs <- rbind.data.frame(mccdata_gm12878_10kb,
+                                mccdata_gm12878_25kb,
+                                mccdata_gm12878_50kb,
+                                mccdata_gm12878_100kb,
+                                mccdata_K562_10kb,
+                                mccdata_K562_25kb,
+                                mccdata_K562_50kb,
+                                mccdata_K562_100kb)
+all_rfperfs$CL <- c(rep("GM12878", length(mccdata_gm12878_10kb)*4), rep("K562", length(mccdata_K562_10kb)*4))
+all_rfperfs$Resolution <- rep(c(rep("10 kb", 84),
+                            rep("25 kb", 84),
+                            rep("50 kb", 84),
+                            rep("100 kb", 84)))
+all_rfperfs$Annotation <- rep(c("CSS","HM","TFBS","Combined"),168)
+all_rfperfs$Chromosome <- rep(c(rep("CHR1", 4),
+                            rep("CHR2", 4),
+                            rep("CHR3", 4),
+                            rep("CHR4", 4),
+                            rep("CHR5", 4),
+                            rep("CHR6", 4),
+                            rep("CHR7", 4),
+                            rep("CHR8", 4),
+                            rep("CHR10", 4),
+                            rep("CHR11", 4),
+                            rep("CHR12", 4),
+                            rep("CHR13", 4),
+                            rep("CHR14", 4),
+                            rep("CHR15", 4),
+                            rep("CHR16", 4),
+                            rep("CHR17", 4),
+                            rep("CHR18", 4),
+                            rep("CHR19", 4),
+                            rep("CHR20", 4),
+                            rep("CHR21", 4),
+                            rep("CHR22", 4)),8)
 
-```{r}
-all_rfperfs_gm12878_allvtfbs <- rbind.data.frame(all_rfperfs_gm12878,all_rfperfs_gm12878_tfbs)
-all_rfperfs_gm12878_allvtfbs$Annotations <- factor(all_rfperfs_gm12878_allvtfbs$Annotations, levels=c("ALL Types", "TFBS Only"))
+all_rfperfs$CL <- factor(all_rfperfs$CL, levels = c("GM12878", "K562"))
+all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
+all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "CSS", "TFBS", "Combined"))
+all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))
 
-ggplot(all_rfperfs_gm12878_allvtfbs,
-       aes(x=Resampling, y=Performance, fill=Annotations)) +
-  geom_bar( stat="identity", position="dodge") +
-  facet_grid( ~ Predictor + Metric) +
-  #xlab("") + ylab("") +
+all_rfperfs_mcc <- all_rfperfs %>%
+  dplyr::group_by(CL, Resolution, Annotation) %>%
+  dplyr::summarise(MCC = mean(V1, na.rm = TRUE),
+            MCCSD = sd(V1, na.rm = TRUE))
+
+#GM12878
+ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="GM12878"),], aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
+  geom_bar(stat="identity", position = position_dodge()) +
+  geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
+                 position=position_dodge(.9), alpha=0.75) +
   theme_minimal() +
-  theme_bw() +
-  scale_fill_discrete(name="Feature Space")+
-  #guides(fill=FALSE)+
+  theme_bw()+
+  #xlab("") + ylab("") + ylim(-.05,.5) +
+  scale_fill_discrete(name="Annotation\nGroup")+
+  guides(shape=FALSE, linetype=FALSE)+
   theme(axis.text.x = element_text(size=15,
@@
                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
+                                  hjust = 1
+  ),
   axis.text.y = element_text(size = 15),
@@
   legend.title=element_text(size=20),
-        strip.text.x = element_text(size = 15))
+  plot.title = element_text(size=20))
+
+#K562
+ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="K562"),], aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
+  geom_bar(stat="identity", position = position_dodge()) +
+  geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
+                 position=position_dodge(.9), alpha=0.75) +
+  theme_minimal() +
+  theme_bw()+
+  #xlab("") + ylab("") + ylim(-.05,.5) +
+  scale_fill_discrete(name="Annotation\nGroup")+
+  guides(shape=FALSE, linetype=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                  angle = 45, 
+                                  #margin = ggplot2::margin(t = 35),
+                                  hjust = 1
+  ),
+  axis.text.y = element_text(size = 15),
+  axis.title.x = element_text(size = 20),
+  axis.title.y = element_text(size = 20),
+  legend.text=element_text(size=15),
+  legend.title=element_text(size=20),
+  plot.title = element_text(size=20))
 ```

### 2019-05-12 Scripts/evaluating_model_performances.Rmd
editted results scripts

@@
 all_rfperfs_mcc <- all_rfperfs %>%
-  group_by(CL, Resolution, Resampling, Predictor) %>%
-  summarise(MCC = mean(V1, na.rm = TRUE),
+  dplyr::group_by(CL, Resolution, Resampling, Predictor) %>%
+  dplyr::summarise(MCC = mean(V1, na.rm = TRUE),
             MCCSD = sd(V1, na.rm = TRUE))

### 2019-05-12 Manuscript/Figures/figure_legends.Rmd
fixed figure 8 (fig 15 in supp); averaged over all chrs; updated legends

@@
 
-**Figure 8.
-Predictive importance of genomic annotations for random forest models implemented on SMOTE resampled data with distance-type predictors for GM12878.** Importance was rescaled to values between 0 and 100, and discretized.
-The importance was subsequently sorted according to the most predictive annotations associated with the 10 kb resolution.
-Annotations with higher values of predictive importance are denoted in dark red, while annotations that were regularized in the pipeline for specific resolutions are denoted in grey.
-
 **Figure 6.
@@
 The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.
+
+**Figure 8.
+Predictive importance** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for GM12878.
+Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100.
+Transcription factors with higher values of predictive importance are denoted in dark red.
 

### 2019-05-12 Manuscript/Supplementary/supplementary_legends.Rmd
fixed figure 8 (fig 15 in supp); averaged over all chrs; updated legends

@@
 
-**Supplementary Figure 15.
-Predictive importance of genomic annotations for random forest models implemented on SMOTE resampled data with distance-type predictors for K562.** Importance was rescaled to values between 0 and 100, and discretized.
-The importance was subsequently sorted according to the most predictive annotations associated with the 10 kb resolution.
-Annotations with higher values of predictive importance are denoted in dark red, while annotations that were regularized in the pipeline for specific resolutions are denoted in grey.
-
-**Supplementary Figure 11..
+**Supplementary Figure 11.
 Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for K562.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
@@
 The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.
+
+**Supplementary Figure 15.
+Predictive importance** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for K562.
+Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100.
+Transcription factors with higher values of predictive importance are denoted in dark red.
 

### 2019-05-12 Scripts/evaluating_variable_importances.Rmd
editted results script

--- 2019-04-09 Scripts/evaluating_variable_importances.Rmd
@@
 
-## Variable Importance Heatmaps for models with distance type predictors (Ranks)
+# Variable Importance Heatmaps for models with distance type predictors with SMOTE resampling
 
-### SMOTE
+##GM12878
+
+```{r}
+annots <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878")
+annots <- gsub(paste(c("Gm12878-", 
+                             "-Haib.bed", 
+                             "-Sydh.bed",
+                             "-Uta.bed",
+                             "-Uw.bed",
+                             "-Broad.bed",
+                             "-Uchicago.bed"), collapse = "|"), "", annots)
+annots <- annots[!duplicated(annots)]
+```
+
+###10kb
+
+```{r}
+varimp_gm12878_10kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_10kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+									   chrs[i], 
+									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
+	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_10kb <- data.frame(Feature = rownames(varimp_gm12878_10kb),
+                                  aveimp10kb = rowMeans(varimp_gm12878_10kb, na.rm = TRUE),
+                                  sdimp10kb = apply(varimp_gm12878_10kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_10kb) <- NULL
+```
+
+###25kb
+
+```{r}
+varimp_gm12878_25kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_25kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
+									   chrs[i], 
+									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
+	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_25kb <- data.frame(Feature = rownames(varimp_gm12878_25kb),
+                                  aveimp25kb = rowMeans(varimp_gm12878_25kb, na.rm = TRUE),
+                                  sdimp25kb = apply(varimp_gm12878_25kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_25kb) <- NULL
+```
+
+###50kb
+
+```{r}
+varimp_gm12878_50kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_50kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
+									   chrs[i], 
+									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
+	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_50kb <- data.frame(Feature = rownames(varimp_gm12878_50kb),
+                                  aveimp50kb = rowMeans(varimp_gm12878_50kb, na.rm = TRUE),
+                                  sdimp50kb = apply(varimp_gm12878_50kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_50kb) <- NULL
+```
+
+###100kb
+
+```{r}
+varimp_gm12878_100kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_100kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
+									   chrs[i], 
+									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
+	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_100kb <- data.frame(Feature = rownames(varimp_gm12878_100kb),
+                                  aveimp100kb = rowMeans(varimp_gm12878_100kb, na.rm = TRUE),
+                                  sdimp100kb = apply(varimp_gm12878_100kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_100kb) <- NULL
+```
+
+##K562
+
+```{r}
+annots <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/K562")
+annots <- gsub(paste(c("K562-", 
+                             "-Haib.bed", 
+                             "-Sydh.bed",
+                             "-Uta.bed",
+                             "-Uw.bed",
+                             "-Broad.bed",
+                             "-Uchicago.bed"), collapse = "|"), "", annots)
+annots <- annots[!duplicated(annots)]
+```
+
+###10kb
+
+```{r}
+varimp_K562_10kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_10kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+									   chrs[i], 
+									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
+	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_10kb <- data.frame(Feature = rownames(varimp_K562_10kb),
+                                  aveimp10kb = rowMeans(varimp_K562_10kb, na.rm = TRUE),
+                                  sdimp10kb = apply(varimp_K562_10kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_10kb) <- NULL
+```
+
+###25kb
+
+```{r}
+varimp_K562_25kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_25kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
+									   chrs[i], 
+									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
+	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_25kb <- data.frame(Feature = rownames(varimp_K562_25kb),
+                                  aveimp25kb = rowMeans(varimp_K562_25kb, na.rm = TRUE),
+                                  sdimp25kb = apply(varimp_K562_25kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_25kb) <- NULL
+```
+
+###50kb
+
+```{r}
+varimp_K562_50kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_50kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
+									   chrs[i], 
+									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
+	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_50kb <- data.frame(Feature = rownames(varimp_K562_50kb),
+                                  aveimp50kb = rowMeans(varimp_K562_50kb, na.rm = TRUE),
+                                  sdimp50kb = apply(varimp_K562_50kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_50kb) <- NULL
+```
+
+###100kb
+
+```{r}
+varimp_K562_100kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_100kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
+									   chrs[i], 
+									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
+	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_100kb <- data.frame(Feature = rownames(varimp_K562_100kb),
+                                  aveimp100kb = rowMeans(varimp_K562_100kb, na.rm = TRUE),
+                                  sdimp100kb = apply(varimp_K562_100kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_100kb) <- NULL
+```
+
+##Plots
 
@@
 #GM12878
+all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
+                                        varimp_gm12878_10kb$aveimp10kb,
+                                        varimp_gm12878_25kb$aveimp25kb,
+                                        varimp_gm12878_50kb$aveimp50kb,
+                                        varimp_gm12878_100kb$aveimp100kb)
+names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+all_varimps_gm12878 <- all_varimps_gm12878[order(all_varimps_gm12878$ave10kb, decreasing = TRUE),]
+all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
+all_varimps_gm12878 <- melt(all_varimps_gm12878)
 
-rfimpvars_gm12878_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-rfimpvars_gm12878_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-rfimpvars_gm12878_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-rfimpvars_gm12878_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-
-rfimpvars_gm12878_10kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_10kb_SMOTE$Feature)
-rfimpvars_gm12878_25kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_25kb_SMOTE$Feature)
-rfimpvars_gm12878_50kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_50kb_SMOTE$Feature)
-rfimpvars_gm12878_100kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_gm12878_100kb_SMOTE$Feature)
-
-unionannots <- union(rfimpvars_gm12878_10kb_SMOTE$Feature,
-                      union(rfimpvars_gm12878_25kb_SMOTE$Feature,
-                            union(rfimpvars_gm12878_50kb_SMOTE$Feature,rfimpvars_gm12878_100kb_SMOTE$Feature)))
-unionannots <- sort(unionannots)
-
-vim.gm12878.smote <- data.frame(Feature=unionannots)
-
-vim.gm12878.smote <- left_join(left_join(left_join(left_join(vim.gm12878.smote,rfimpvars_gm12878_10kb_SMOTE, by="Feature"),
-								rfimpvars_gm12878_25kb_SMOTE, by="Feature"),
-								rfimpvars_gm12878_50kb_SMOTE, by="Feature"),
-								rfimpvars_gm12878_100kb_SMOTE, by="Feature")
-names(vim.gm12878.smote) <- c("Feature","Importance.10kb","Importance.25kb","Importance.50kb","Importance.100kb")
-
-vim.gm12878.smote.ranks <- data.frame(Feature=vim.gm12878.smote$Feature,
-									  Rank.10kb=rank(-vim.gm12878.smote$Importance.10kb, na.last = TRUE),
-									  Rank.25kb=rank(-vim.gm12878.smote$Importance.25kb, na.last = TRUE),
-									  Rank.50kb=rank(-vim.gm12878.smote$Importance.50kb, na.last = TRUE),
-									  Rank.100kb=rank(-vim.gm12878.smote$Importance.100kb, na.last = TRUE))
-
-rankdata <- cbind(vim.gm12878.smote.ranks$Rank.10kb,
-                  vim.gm12878.smote.ranks$Rank.25kb,
-				  vim.gm12878.smote.ranks$Rank.50kb,
-				  vim.gm12878.smote.ranks$Rank.100kb)
-rownames(rankdata) <- vim.gm12878.smote.ranks$Feature
-colnames(rankdata) <- c("10 kb", "25 kb", "50 kb", "100 kb")	 			  
-rankdata <- rankdata[order(rankdata[,1], decreasing = FALSE),]
-rankdata <- rankdata[1:20,]
-
-#my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100)) 
-my_palette <- colorRampPalette(c("red", "pink", "white"))(nrow(rankdata))
-heatmap.2(t(rankdata),
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins=c(12,8),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          #keysize = 1.5,
-          #key.title = "Elastic-Net Coefficient",
-          dendrogram="column",     # only draw a row dendrogram,
-          Rowv = FALSE,
-          Colv = TRUE,
-          cexRow=1.5,
-          cexCol=1.5,
-          #labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          sepwidth=c(0.001,0.001),
-          sepcolor="black",
-          rowsep=1:4,
-          colsep=0:nrow(rankdata))
+ggplot(all_varimps_gm12878, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
+  geom_tile(aes(fill = value), colour = "white") + 
+  xlab("Resolution") +
+  ylab("Transcription Factor") +
+  scale_fill_gradient2(low = "white",
+                      mid = "pink",
+                      midpoint = 50,
+                      high = muted("red"),
+                      na.value = "grey50",
+                      name="Predictive\nImportance") +
+  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 10),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
 
 #K562
+all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
+                                        varimp_K562_10kb$aveimp10kb,
+                                        varimp_K562_25kb$aveimp25kb,
+                                        varimp_K562_50kb$aveimp50kb,
+                                        varimp_K562_100kb$aveimp100kb)
+names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+all_varimps_K562 <- all_varimps_K562[order(all_varimps_K562$ave10kb, decreasing = TRUE),]
+all_varimps_K562 <- all_varimps_K562[1:20,]
+all_varimps_K562 <- melt(all_varimps_K562)
 
-rfimpvars_K562_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-rfimpvars_K562_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-rfimpvars_K562_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-rfimpvars_K562_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
-
-rfimpvars_K562_10kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_10kb_SMOTE$Feature)
-rfimpvars_K562_25kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_25kb_SMOTE$Feature)
-rfimpvars_K562_50kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_50kb_SMOTE$Feature)
-rfimpvars_K562_100kb_SMOTE$Feature <- gsub(paste(c("`","_dist"),sep="", collapse="|"),"", rfimpvars_K562_100kb_SMOTE$Feature)
-
-unionannots <- union(rfimpvars_K562_10kb_SMOTE$Feature,
-                      union(rfimpvars_K562_25kb_SMOTE$Feature,
-                            union(rfimpvars_K562_50kb_SMOTE$Feature,rfimpvars_K562_100kb_SMOTE$Feature)))
-unionannots <- sort(unionannots)
-
-vim.K562.smote <- data.frame(Feature=unionannots)
-
-vim.K562.smote <- left_join(left_join(left_join(left_join(vim.K562.smote,rfimpvars_K562_10kb_SMOTE, by="Feature"),
-								rfimpvars_K562_25kb_SMOTE, by="Feature"),
-								rfimpvars_K562_50kb_SMOTE, by="Feature"),
-								rfimpvars_K562_100kb_SMOTE, by="Feature")
-names(vim.K562.smote) <- c("Feature","Importance.10kb","Importance.25kb","Importance.50kb","Importance.100kb")
-
-vim.K562.smote.ranks <- data.frame(Feature=vim.K562.smote$Feature,
-									  Rank.10kb=rank(-vim.K562.smote$Importance.10kb, na.last = TRUE),
-									  Rank.25kb=rank(-vim.K562.smote$Importance.25kb, na.last = TRUE),
-									  Rank.50kb=rank(-vim.K562.smote$Importance.50kb, na.last = TRUE),
-									  Rank.100kb=rank(-vim.K562.smote$Importance.100kb, na.last = TRUE))
-
-rankdata <- cbind(vim.K562.smote.ranks$Rank.10kb,
-                  vim.K562.smote.ranks$Rank.25kb,
-				  vim.K562.smote.ranks$Rank.50kb,
-				  vim.K562.smote.ranks$Rank.100kb)
-rownames(rankdata) <- vim.K562.smote.ranks$Feature
-colnames(rankdata) <- c("10 kb", "25 kb", "50 kb", "100 kb")
-
-#my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100)) 
-my_palette <- colorRampPalette(c("red", "white"))(nrow(rankdata))
-heatmap.2(t(rankdata),
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins=c(12,8),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          #key.title = "Elastic-Net\nCoefficient",
-          #keysize = 2,
-          dendrogram="both",     # only draw a row dendrogram,
-          Rowv = TRUE,
-          Colv = TRUE,
-          cexRow=1.5,
-          cexCol=0.5,
-          #labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          sepwidth=c(0.001,0.001),
-          sepcolor="black",
-          rowsep=1:4,
-          colsep=0:nrow(rankdata)) 
+ggplot(all_varimps_K562, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
+  geom_tile(aes(fill = value), colour = "white") + 
+  xlab("Resolution") +
+  ylab("Transcription Factor") +
+  scale_fill_gradient2(low = "white",
+                      mid = "pink",
+                      midpoint = 50,
+                      high = muted("red"),
+                      na.value = "grey50",
+                      name="Predictive\nImportance") +
+  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 10),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
 ```
-
-## Average Variable Importances Heatmaps for models with distance type predictors (Ranks)
-
-```{r}
-#gm12878 
-##average then rank
-vim.gm12878.smote[is.na(vim.gm12878.smote)] <- 0
-
-vim.gm12878.smote.ave.rank <- data.frame(Feature=vim.gm12878.smote$Feature,
-                                    AveImp=rowMeans(vim.gm12878.smote[,-1]))
-vim.gm12878.smote.ave.rank$Rank <- rank(-vim.gm12878.smote.ave.rank$AveImp, na.last = TRUE)
-vim.gm12878.smote.ave.rank <- vim.gm12878.smote.ave.rank[order(vim.gm12878.smote.ave.rank$Rank, decreasing = FALSE),]
-rankdata.a.r <- cbind(vim.gm12878.smote.ave.rank$Rank,vim.gm12878.smote.ave.rank$Rank)
-rankdata.a.r <- rankdata.a.r[1:20,]
-rownames(rankdata.a.r) <- vim.gm12878.smote.ave.rank$Feature[1:20]
-
-#my_palette <- colorRampPalette(c("red", "white"))(100)
-my_palette_rank <- colorRampPalette(c("red", "white"))(nrow(rankdata.a.r))
-heatmap.2(t(rankdata.a.r),
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          labRow = "",
-          labCol = rownames(rankdata.a.r),
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins=c(12,8),     # widens margins around plot
-          col=my_palette_rank,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          #key.title = "Elastic-Net\nCoefficient",
-          #keysize = 2,
-          dendrogram="none",     # only draw a row dendrogram,
-          Rowv = NA,
-          Colv = NA,
-          cexRow=1.5,
-          cexCol=1.5,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #lwid=c(.5,6,0),
-          sepwidth=c(0.001,0.001),
-          sepcolor="black",
-          rowsep=c(0,2),
-          colsep=0:nrow(rankdata.a.r)
-          )
-
-##rank then average
-vim.gm12878.smote.rank.ave <- cbind(Rank.10kb=rank(-vim.gm12878.smote$Importance.10kb, na.last = TRUE),
-                                    Rank.25kb=rank(-vim.gm12878.smote$Importance.25kb, na.last = TRUE),
-                                    Rank.50kb=rank(-vim.gm12878.smote$Importance.50kb, na.last = TRUE),
-                                    Rank.100kb=rank(-vim.gm12878.smote$Importance.100kb, na.last = TRUE))
-rownames(vim.gm12878.smote.rank.ave) <- vim.gm12878.smote$Feature
-rankdata.r.a <- rowMeans(vim.gm12878.smote.rank.ave)
-rankdata.r.a <- rankdata.r.a[order(rankdata.r.a, decreasing = FALSE)]
-rankdata.r.a <- rankdata.r.a[1:20]
-rankdata.r.a <- cbind(rankdata.r.a,rankdata.r.a)
-heatmap.2(t(rankdata.r.a),
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          labRow = "",
-          labCol = rownames(rankdata.r.a),
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins=c(12,8),     # widens margins around plot
-          col=my_palette_rank,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          #key.title = "Elastic-Net\nCoefficient",
-          #keysize = 2,
-          dendrogram="none",     # only draw a row dendrogram,
-          Rowv = NA,
-          Colv = NA,
-          cexRow=1.5,
-          cexCol=1.5,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          #lwid=c(.5,6,0),
-          sepwidth=c(0.001,0.001),
-          sepcolor="black",
-          rowsep=c(0,2),
-          colsep=0:nrow(rankdata.r.a)
-          )
-
-```
-
-## ICC
-
-```{r}
-vim.gm12878.smote[is.na(vim.gm12878.smote)] <- 0
-icc(vim.gm12878.smote, model = "twoway", type = "agreement")
-
-```

### 2019-05-13 Scripts/calculating_jaccard_index_between_annotations.Rmd
script for calculating jaccard index

---
title: "Evaluating Jaccard Index Between Annotations"
author: "Spiro Stilianoudakis"
date: "April 29, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(cotools)
library(HelloRanges)
```

# Function for calculating jaccard index between any two annotations

```{r}
#jaccard(A,B) = length of intersection between A and B (in base pairs)/(length of union between A and B - length of intersection between A and B)

jaccard_func <- function(A, B){
  #compute length of intersection between both annotations in base pairs (numerator)
  l.i <- sum(width(pintersect(findOverlapPairs(A, B))))

  #compute length of union between both annotations in base pairs
  l.u <- sum(width(A)) + sum(width(B))

  j <- l.i/(l.u-l.i)

  return(j)
}

```

# Iterate through all annotation and calculate paiwise jaccard index

## GM12878

```{r}
setwd("Z:/TAD_data_analysis/annotations/all_annotations/gm12878")
temp = list.files()

jaccard.mat <- matrix(nrow=length(temp), ncol=length(temp))
colnames(jaccard.mat) <- rownames(jaccard.mat) <- gsub(paste(c("Gm12878", "K562", ".bed",
                          "-",
                          "_",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", temp)

for(i in 27:length(temp)){
  for(j in 1:length(temp)){
    print(c(i,j))
    annotA <- read.table(temp[i],header = FALSE, sep="\t")
    annotA.gr <- GRanges(seqnames=annotA$V1,
                     IRanges(start=annotA$V2, 
                             end=annotA$V3))

    annotB <- read.table(temp[j],header = FALSE, sep="\t")
    annotB.gr <- GRanges(seqnames=annotB$V1,
                     IRanges(start=annotB$V2, 
                             end=annotB$V3))

    if(i==j){jaccard.mat[i,j] <- 1}else{
      code <- R_bedtools_jaccard(annotA.gr,annotB.gr)
      eval.code <- eval(code)
      jaccard.mat[i,j] <- eval.code@listData$jaccard
    }
  }
}
```

###Plots

####All
```{r}
jaccard.mat.gm12878 <- readRDS("Z:/TAD_data_analysis/jaccard/jaccard.mat.gm12878.rds")
jaccard.mat.gm12878 <- jaccard.mat.gm12878[!duplicated(rownames(jaccard.mat.gm12878)), !duplicated(colnames(jaccard.mat.gm12878))]

corrplot(jaccard.mat.gm12878, method = "square",
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("white", "red"))(100),
         cl.pos="n",
         mar = c(0, 0, 0, 0))
```

####Chomatin States

```{r}
css <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
css <- css[grep("Gm12878", css)]
css <- gsub(paste(c("Gm12878-", ".bed"), collapse = "|"), "", css)
jaccard.mat.gm12878.css <- jaccard.mat.gm12878[rownames(jaccard.mat.gm12878) %in% css, colnames(jaccard.mat.gm12878) %in% css]

corrplot(jaccard.mat.gm12878.css, method = "square",
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("white", "red"))(100),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

get_upper_tri <- function(cormat){
     cormat[lower.tri(cormat)]<- NA
     return(cormat)
}

upper_tri_css <- get_upper_tri(jaccard.mat.gm12878.css)
melted_css <- reshape2::melt(upper_tri_css, na.rm = TRUE)
melted_css <- melted_css[-which(melted_css$Var1==melted_css$Var2),]
summary(melted_css$value)
```

####Histone Modifications

```{r}
hm <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
hm <- hm[grep("Gm12878", hm)]
hm <- gsub(paste(c("Gm12878-", ".bed"), collapse = "|"), "", hm)
jaccard.mat.gm12878.hm <- jaccard.mat.gm12878[rownames(jaccard.mat.gm12878) %in% hm, colnames(jaccard.mat.gm12878) %in% hm]

corrplot(jaccard.mat.gm12878.hm, method = "square",
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("white", "red"))(100),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

get_upper_tri <- function(cormat){
     cormat[lower.tri(cormat)]<- NA
     return(cormat)
}

upper_tri_hm <- get_upper_tri(jaccard.mat.gm12878.hm)
melted_hm <- reshape2::melt(upper_tri_hm, na.rm = TRUE)
melted_hm <- melted_hm[-which(melted_hm$Var1==melted_hm$Var2),]
summary(melted_hm$value)
```

####TFBS

```{r}
tfbs <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878")
tfbs <- tfbs[grep("Gm12878", tfbs)]
tfbs <- gsub(paste(c("Gm12878-", ".bed","-Haib","-Sydh","-Uta","-Uw","-Broad","-Uchicago"), collapse = "|"), "", tfbs)
jaccard.mat.gm12878.tfbs <- jaccard.mat.gm12878[rownames(jaccard.mat.gm12878) %in% tfbs, colnames(jaccard.mat.gm12878) %in% tfbs]

corrplot(jaccard.mat.gm12878.tfbs, method = "square",
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .7,
         col=colorRampPalette(c("white", "red"))(100),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

get_upper_tri <- function(cormat){
     cormat[lower.tri(cormat)]<- NA
     return(cormat)
}

upper_tri_tfbs <- get_upper_tri(jaccard.mat.gm12878.tfbs)
melted_tfbs <- reshape2::melt(upper_tri_tfbs, na.rm = TRUE)
melted_tfbs <- melted_tfbs[-which(melted_tfbs$Var1==melted_tfbs$Var2),]
summary(melted_tfbs$value)
```

## K562

```{r}
setwd("Z:/TAD_data_analysis/annotations/all_annotations/k562")
temp = list.files()

jaccard.mat <- matrix(nrow=length(temp), ncol=length(temp))
colnames(jaccard.mat) <- rownames(jaccard.mat) <- gsub(paste(c("Gm12878", "K562", ".bed",
                          "-",
                          "_",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", temp)

for(i in 1:length(temp)){
  for(j in 1:length(temp)){
    print(c(i,j))
    annotA <- read.table(temp[i],header = FALSE, sep="\t")
    annotA.gr <- GRanges(seqnames=annotA$V1,
                     IRanges(start=annotA$V2, 
                             end=annotA$V3))

    annotB <- read.table(temp[j],header = FALSE, sep="\t")
    annotB.gr <- GRanges(seqnames=annotB$V1,
                     IRanges(start=annotB$V2, 
                             end=annotB$V3))

    if(i==j){jaccard.mat[i,j] <- 1}else{
      code <- R_bedtools_jaccard(annotA.gr,annotB.gr)
      eval.code <- eval(code)
      jaccard.mat[i,j] <- eval.code@listData$jaccard
    }
  }
}
```

### 2019-05-14 Manuscript/Tables/table_legends.Rmd
editted legends

@@
 The resolution of the Hi-C contact matrix dictated the width of each genomic bin, with lower resolutions corresponding to wider genomic bins.
+
+**Table 2.
+Jaccard Indices.** The median (range) Jaccard index illustrating the pairwise similarity between annotations within specific groups, including chromatin segmentation states, histone modifications, and transcription factor binding sites.
+The Jaccard Index measures the ratio of the number of intersecting base pairs between any two sets, to the number of base pairs in the union of the two sets.
+The number of cell line specific annotations included within each group is also provided.

### 2019-05-14 Scripts/calculating_jaccard_index_between_annotations.Rmd
editted results script

@@
 
-####All
 ```{r}
@@
 
-corrplot(jaccard.mat.gm12878, method = "square",
-         type="upper", 
-         order="hclust", 
-         tl.col="black", 
-         tl.srt=90,
-         tl.cex = .4,
-         col=colorRampPalette(c("white", "red"))(100),
-         cl.pos="n",
-         mar = c(0, 0, 0, 0))
 ```
@@
 
+####All
+
+```{r}
+corrplot(jaccard.mat.gm12878, method = "square",
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .4,
+         col=colorRampPalette(c("white", "red"))(100),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+all_melted_gm12878 <- rbind.data.frame(melted_css,
+                                       melted_hm,
+                                       melted_tfbs)
+all_melted_gm12878$annotation <- c(rep("CSS", length(melted_css$Var1)),
+                                   rep("HM", length(melted_hm$Var1)),
+                                   rep("TFBS", length(melted_tfbs$Var1)))
+all_melted_gm12878$annotation <- factor(all_melted_gm12878$annotation, levels=c("CSS", "HM", "TFBS"))
+
+ggplot(all_melted_gm12878[-which(all_melted_gm12878$annotation=="CSS"),], aes(x=value, group=annotation, color=annotation)) + 
+  geom_density(size=1) +
+  xlim(0,1) +
+  xlab("Jaccard Index") +
+  ylab("Density") +
+  scale_color_discrete(name="Annotation Group") +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_text(size=15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+```
+
 ## K562

### 2019-05-14 Manuscript/Figures/figure_legends.Rmd
reordering and relabeling figures and tables

@@
 
-**Figure 5.
+**Figure 4.
 Comparing ensemble system specific model performances for GM12878.** Performances of random forest classification models built on each of the 3 predictor types: OC (A), OP (B), and Distance (C).
@@
 
-**Figure 6.
+**Figure 5.
 Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for GM12878.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
@@
 
-**Figure 8.
+**Figure 6.
 Predictive importance** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for GM12878.
@@
 -->
-
-<!--
-**Figure 4.
-Barplots comparing model performance for each predictor type.** Model performances were evaluated using F1-score, MCC, and balanced accuracy for each of the 4 resampling techniques, across both the GM12878 (A) and K562 (B) cell lines.
-The results presented are for models applied to 10 kb resolution data.
-
-**Figure 5.
-Line plots comparing models using SMOTE resampling with distance-type predictors.** Model performances were evaluated using F1-score, MCC, and balanced accuracy for each of the 4 data resolutions, across both the GM12878 (red, solid line) and K562 (blue; dashed line) cell lines.
-For a given metric, each point represents a model applied to a particular resolution with distance type predictors for the feature space, after which the SMOTE algorithm was used to create balanced classes on the trianing set.
-
-**Figure 6.
-Variable importance of the top 20 most predictive genomic annotations for models using SMOTE resampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines.
-Variable importance is assigned on a continuous scale (range: 0-100).
-Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model.
-The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using SMOTE resampling, for each cell line respectively.
--->
-
-<!--
-**Figures 4-8.
-Precision-Recall curves for 10 kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on 10 kb resolution data, across each resampling technique.
-GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red).
--->
-
-<!--
-**Figure 9-13.
-Recursive Feature Elimination for 10 kb data** Beginning with the full set of distance type predictors for each cell line, models built on 10 kb resolution data were recursively evaluated at different subsets of feature size.
-For convenience and computational efficiency, feature size decreasing in powers of 2 was considered.
-The maximum size for feature subsets differed between cell line due the available annotations that were considered and provided in Supplementary Table 1.
-Near optimal performance was achieved using the top 32 distance type predictors for both the GM12878 (red) and K562 cell lines (blue).
--->

### 2019-05-14 Manuscript/Supplementary/supplementary_legends.Rmd
reordering and relabeling figures and tables

@@
 
-**Supplementary Table 4. Hi-C data.** A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains.
-
-**Supplementary Table 8.
-Summary statistics for called TADs.** The following summary statistics were recorded regarding the average number and length of TADs (along with standard deviations) that were called using the Arrowhead algorithm [@durand2016juicebox], across each of the autosomal chromosomes (excluding chromosome 9).
+**Supplementary Table 1. Hi-C data.** A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains.
 
@@
 
-**Supplementary Figure 10.
+**Supplementary Figure 3.
 Comparing ensemble system specific model performances for K562.** Performances of random forest classification models built on each of the 3 predictor types: OC (A), OP (B), and Distance (C).
@@
 
-**Supplementary Table 4.
-Ranking predictive importance between predictor types for annotation-specific models for GM12878.** Annotation-specific random forest classification models were implemented on SMOTE resampled data, across resolution.
-Each model contained each of the 3 predictor types for one genomic annotation.
-Predictive importance was rescaled to values between 0 and 100.
-The predictor type with importance value of 100 indicates it was the most informative predictor type out of the 3.
-
-**Supplementary Table 5.
-Ranking predictive importance between predictor types for annotation-specific models for K562.** Annotation-specific random forest classification models were implemented on SMOTE resampled data, across resolution.
-Each model contained each of the 3 predictor types for one genomic annotation.
-Predictive importance was rescaled to values between 0 and 100.
-The predictor type with importance value of 100 indicates it was the most informative predictor type out of the 3.
-
-**Supplementary Figure 11.
+**Supplementary Figure 4.
 Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for K562.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
@@
 
-**Supplementary Figure 15.
+**Supplementary Figure 5.
 Predictive importance** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for K562.
@@
 
+<!--
 **Supplementary Figure 12.
@@
 That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
-
-**Supplementary Figure 13.
-Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 50 kb resolution, on GM12878.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
-For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
-That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
-
-**Supplementary Figure 14.
-Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 100 kb resolution, on GM12878.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
-For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
-That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
-
-**Supplementary Figure 15.
-Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 10 kb resolution, on K562.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
-For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
-That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
-
-**Supplementary Figure 16.
-Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 25 kb resolution, on K562.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
-For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
-That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
-
-**Supplementary Figure 17.
-Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 50 kb resolution, on K562.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
-For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
-That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
-
-**Supplementary Figure 18.
-Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 100 kb resolution, on K562.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
-For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
-That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
+-->

### 2019-05-14 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution for the corresponding contact matrix (Figure 1).
+To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution for the corresponding contact matrix <!--(Figure 1)-->.
 As an example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
@@
 
-Using the sets of genomic annotations, we created three types of predictors that were used as features for subsequent models to analyze their respective spatial relationship with TAD boundaries (Figure 3):
+Using the sets of genomic annotations, we created three types of predictors that were used as features for subsequent models to analyze their respective spatial relationship with TAD boundaries <!--(Figure 3)-->:
 
@@
 **Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter simply as $\textit{distance}$), from the center of the bin to the center of the nearest region defined by a specific genomic annotation was calculated.
-The log transformation was used as a normalization technique in order to account for the skewness present in the distance densities (Supplementary Figures 1).
+The log transformation was used as a normalization technique in order to account for the skewness present in the distance densities <!--(Supplementary Figures 1)-->.
 
@@
 Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class [@chawla2002smote].
-The `DMwR` R package was used to perform SMOTE (version 0.4.1).
-
-<!--
-5.
-**ROSE** (Random Over-Sampling Examples): Similar to SMOTE, ROSE combines techniques of over-sampling and under-sampling.
-However, contrary to SMOTE, all of the data generated by ROSE is synthetic.
-The data is created by sampling from one of the two classes, then generating a new example in its neighborhood using a smoothed bootstrap approach.
-The shape of the neighborhood is determined by the kernel density estimate of the two classes [@lunardon2013r].
-Another important distinction between ROSE and SMOTE is that, for ROSE, the creation of perfectly balanced classes is unlikely due to the randomness in sampling between the two classes.
-The `ROSE` R package was used to perform ROSE (version 0.0.3).
--->
+The *DMwR* R package was used to perform SMOTE (version 0.4.1).
 
@@
 
-A regularization technique using a combination of the $l_{1}$ and $l_{2}$ penalties, known as the elastic-net, was used to reduce the feature space.
+A regularization technique using a combination of the *l_{1}* and *l_{2}* penalties, known as the elastic-net, was used to reduce the feature space.
 The elastic-net was chosen in order to suitably reduce the feature space while also maintaining the inclusion of multiple correlated predictors.
@@
 The parameters that maximized the mean AUPRC across each cross-fold was chosen.
-All elastic-net algorithms were implemented in R using the `caret` package version 6.0 [@kuhn2012caret].
-
-<!--
-Recursive feature elimination (RFE) was then used to determine the optimal number of features for models with the best performing predictor type.
-For each set of predictor type, random forest models were performed recursively on subsets of the feature space.
-The specific subsets of features were chosen as powers of 2 for computational efficiency.
-Model performance for each subset was evaluated using AUPRC.
-The optimal set of featues to include in downstream analyses was determined to be the subset in which the AUPRC leveled off.
-Again, to confirm that results were consistent, the reduction process was repeated for each combination of re-sampling technique, resolution, and cell line.
--->
+All elastic-net algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
 
@@
 Once the appropriate predictor type and set of features were determined, a final set of random forest classification models were built to compare model performances between re-sampling techniques and predictor types.
-<!--To reduce bias due to random dataset generation, 10-fold cross validation was used to tune the number of features to consider at each node and the number of ensemble trees to aggregate.--> The default number of features to consider at each node of the random forest algorithm was set as $\sqrt{p}$, where $p$ refers to the number of predictors included in the model.
+<!--To reduce bias due to random dataset generation, 10-fold cross validation was used to tune the number of features to consider at each node and the number of ensemble trees to aggregate.--> The default number of features to consider at each node of the random forest algorithm was set as $\sqrt{p}$, where *p* refers to the number of predictors included in the model.
 Likewise, the number of ensemble trees to aggregate was set at 500.
-All random forest algorithms were implemented in R using the `caret` package version 6.0 [@kuhn2012caret].
+All random forest algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
 Once the model was implemented, it was validated on the test set.
@@
 
-An ensemble framework was then established for the purposes of systematically creating a variety of models that each included different sets of parameters described above (Figure 2).
+An ensemble framework was then established for the purposes of systematically creating a variety of models that each included different sets of parameters described above <!--(Figure 2)-->.
 Each system in the framework is assumed to be composed of a model constructed from a particular cell line and data resolution, with a particular predictor type for the feature space.
@@
 # RESULTS
+
+## THE PROPOSED MODEL
+
+We illustrate a unified approach toward preparing TAD boundary data for predictive modelling purposes from different cell lines and data resolutions (Figure 1).
+To enable us to build a model that suitably discriminates between regions on the linear genome that are near TAD boundaries and regions that are not, we created a cell line- and resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary (Y=1), or not (Y=0).
+The unit width of each bin on the linear genome corresponded to the resolution of the contact matrix that domains were called on.
+Moreover, to account for uncertainty in boundary location, TAD boundaries were flanked on either side by the same unit length as the genomic bins.
+
+To investigate the relationship between functional genomic annotations and the development of TAD boundaries, we devised 3 different predictor-types that composed the feature space of downstream random forest classification models.
+These predictor-type specific annotations represented the data matrix, **X** = {$X_{1}$, $X_{2}$, ..., $X_{p}$}, where *p* the set of annotations.
+Overlap counts was the least granular predictor-type considered, simply defined by the number of annotation-specific regions located within each genomic bin (Figure 2A).
+Overlap percents was a more refined predictor-type, defined as the total percent overlap between each annotation-specific region and genomic bins (Figure 2B).
+Lastly, distances, the most granular predictor-type, described the spatial relationship between the center of each genomic bin to the center of the nearest annotation-specific region (Figure 2C).
+When measured in basepairs, distances were found to be highly skewed across all resolutions, for both the GM12878 and K562 cell lines (Supplementary Figures 1-2 A-D).
+As a normalization procedure, we performed a $log_{2}$ transformation on the distances (Supplementary Figures 1-2 E-H).
 
@@
 Furthermore, models built on TAD boundaries called at higher resolutions exhibited better performances.
-
-<!--
-Additionally, when we performed and evaluated the variable importances of random forest models built on one genomic annotation at a time (including the 3 predictor types each), we found that the distance-type consistently out-ranked the OC and OP type predictors in terms of predictive importance, for a majority of the cell line specific annotations, across resolution and cell line (Supplementary Tables 4 & 5).
-Therefore, it appears that distance-type predictors provided the most informative spatial representation of epigenomic annotations associated with TAD boundaries.
--->
 

### 2019-05-14 Manuscript/Supplementary/supplementary_legends.Rmd
editted legends

@@
 **Supplementary Figure 1.
-GM12878 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb.
-(E-H) $Log_{2}$ transformed distances for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb.
+GM12878 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths (resolutions) of 10 kb, 25 kb, 50 kb, and 100 kb.
+(E-H) $Log_{2}$ transformed distances for binwidths (resolutions) of 10 kb, 25 kb, 50 kb, and 100 kb.
 
 **Supplementary Figure 2.
-K562 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb.
-(E-H) $Log_{2}$ transformed distances for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb.
+K562 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths (resolutions) of 10 kb, 25 kb, 50 kb, and 100 kb.
+(E-H) $Log_{2}$ transformed distances for binwidths (resolutions) of 10 kb, 25 kb, 50 kb, and 100 kb.
 

### 2019-05-14 Manuscript/Figures/figure_legends.Rmd
reordered tables and figures and editted legends

@@
 **Figure 6.
-Predictive importance** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for GM12878.
+Predictive importance.** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for GM12878.
 Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100.

### 2019-05-14 Manuscript/Supplementary/supplementary_legends.Rmd
reordered tables and figures and editted legends

@@
 (E-H) $Log_{2}$ transformed distances for binwidths (resolutions) of 10 kb, 25 kb, 50 kb, and 100 kb.
+
+**Supplementary Table 3.
+Data Summaries and Imbalance Ratios.** For K562, average number of genomic bins, TADs called, and the corresponding boundaries and imbalance ratios, across each of the autosomal chromosomes (omitting chromosome 9), stratified by resolution.
+The resolution of the Hi-C contact matrix dictated the width of each genomic bin, with lower resolutions corresponding to wider genomic bins.
 

### 2019-05-14 Manuscript/Tables/table_legends.Rmd
reordered tables and figures and editted legends

@@
 **Table 1.
-Data Summaries.** The average number of genomic bins, TADs called, and the corresponding boundaries and imbalance ratios, across each of the autosomal chromosomes (omitting chromosome 9), stratified by resolution and cell line.
+Data Summaries and Imbalance Ratios.** For GM12878, average number of genomic bins, TADs called, and the corresponding boundaries and imbalance ratios, across each of the autosomal chromosomes (omitting chromosome 9), stratified by resolution.
 The resolution of the Hi-C contact matrix dictated the width of each genomic bin, with lower resolutions corresponding to wider genomic bins.

### 2019-05-14 Manuscript/manuscript.Rmd
manuscript edits

@@
 When measured in basepairs, distances were found to be highly skewed across all resolutions, for both the GM12878 and K562 cell lines (Supplementary Figures 1-2 A-D).
-As a normalization procedure, we performed a $log_{2}$ transformation on the distances (Supplementary Figures 1-2 E-H).
+As a normalization procedure, we performed a $log_{2}$ transformation, which resulted in much more gaussian-shaped distance densities (Supplementary Figures 1-2 E-H).
 
@@
 
-We compared the performances of random forest classification models implemented on TAD boundaries called using the arrowhead algorithm [@durand2016juicebox] from replicate Hi-C data for 2 cell lines *L* = { *GM12878*, *K562* }, at four different resolutions *R* = { *10 kb*, *25 kb*, *50 kb*, *100 kb* }.
-For each classifier, we considered 3 separate predictor types as the feature space including *P* = {*OC*, *OP*, *Distance* }.
-To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including *B* = {*None*, *RUS*, *ROS*, *SMOTE* }.
+We then developed an ensemble framework to systematically compare and establish the best set of data level characteristics for predicting TAD boundaries using random forest classifiers built on functional genomic annotations (Figure 3).
+TAD boundaries were called using the arrowhead algorithm [@durand2016juicebox] from replicate Hi-C data for 2 cell lines *L* = {*GM12878*, *K562*}, at four different resolutions *R* = {*10 kb*, *25 kb*, *50 kb*, *100 kb*}.
+For each classifier, we considered 3 separate predictor types as the feature space including *P* = {*OC*, *OP*, *Distance*}.
+To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including *B* = {*None*, *RUS*, *ROS*, *SMOTE*}.
 Each combination of the above parameters was repeated 21 times (number of autosomal chromosomes, excluding chromosome 9), *C* = {*1*, *2*, ..., *22*}.
@@
 Letting *|X|* denote the cardinality of each set, we evaluated *|L|* $\times$ *|R|* $\times$ *|P|* $\times$ *|B|* different ensemble systems, totaling 2016 (= 2 $\times$ 4 $\times$ 3 $\times$ 4 $\times$ 21) separate models.
+Performances were then aggregated across each of the 21 chromosomes (omitting chromosome 9; see Methods).
 
-## IMBALANCE RATIOS REMAINED SEVERE AND CONSISTENT ACROSS RESOLUTIONS
+## IMBALANCE RATIOS REMAINED SEVERE AND INVARIANT TOWARD RESOLUTION
 
-Results showed that the imbalance ratios were well below acceptable thresholds for both cell lines, and across the 4 resolutions (Figure 4).
-The low imbalance ratios indicated a wide disparity between the number of genomic bins that overlaped with a flanked TAD boundary and the much larger number that did not.
-Likewise, there was very little variation in imbalance ratios across resolution.
-The low IR indicate a necessary re-sampling technique that will suitably balance the majority and minority classes.
+[??? include icc for each component of table 1 with resolution]
+The total number of genomic bins, which defined the dimensions of the data for modelling, was contingent upon the resolution of the contact matrix that cell line specific TADs were called on.
+Higher resolutions resulted in smaller unit bin widths, which corresponded to larger numbers of genomic bins (Table 1).
+For GM12878, there was an average of 12,214.1, 4,892.7, 2,450.9, and 1,227.5 bins created across chromosomes, for each resolution respectively.
+Likewise, the average number of bins, respective to resolution, were found to be similar on the K562 cell line (Supplementary Table 3).
+
+As expected, the number of TADs called was related to resolution.
+Higher resolutions were found to result in a greater number of TADs called.
+For GM12878, an average of 365.5, 222.4, 111.9, and 49.1 TADs were called across chromosomes, for each respective resolution (Table 1).
+Average TADs called across chromosomes were found to be less on the K562 cell line at all resolutions (Supplementary Table 3).
+Although the downward trend was still present.
+As a result, a greater number of TADs corresponded to a greater number of TAD boundaries.
+For GM12878, the average number of TAD boundaries across chromosomes was found to be 1,254.6, 714.0, 364.4, and 165.3 for each resolution respectively (Table 1).
+Similar boundary profiles were exhibited on the K562 cell line (Supplementary Table 3).
+
+Furthermore, results showed that average imbalance ratios were consistently and severely low across resolutions, for both cell lines.
+For GM12878, the average imbalance ratios were found to be 0.12, 0.17, 0.17, and 0.15 for the 10 kb, 25 kb, 50 kb, and 100 kb resolutions respectively (Table 1).
+Slightly smaller resolution-specific and averaged imbalance ratios were featured on the K562 cell line, yet were still consistent and invariant to resolution.
+Such low imbalance ratios indicated a wide disparity between the number of genomic bins that overlaped with a flanked TAD boundary and the much larger number that did not.
 
@@
 Importantly, when validating these 3 models built on fully imbalanced datasets, the MCC could not be determined at lower resolutions given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives.
-Furthermore, we found that evaluating models using conventional metrics, such as AUC or accuracy, did not depict the true severity in performance (Supplementary Table 3).
 Results were found to be consistently poor across resolutions for the K562 cell line (Supplementary Figure 10).
 Similarly, many of the performance metrics at higher resolutions were also unable to be reported due to the models inability to produce any true positive cases.
+<!--Furthermore, we found that evaluating models using conventional metrics, such as AUC or accuracy, did not depict the true severity in performance (Supplementary Table 4).-->
 

### 2019-05-14 Manuscript/Supplementary/supplementary_legends.Rmd
added tables; updated legends

@@
 
+**Supplementary Table 4.
+Inter-Resolution ICCs.** For K562, two-way intraclass correlation coefficients between resolutions for the following quantities: Number of genomic bins, number of TADs called, number of unique TAD boundaries, and imbalance ratio.
+The ICC was computed across 21 of the autosomal chromosomes.
+All quatities, except for imbalance ratio, was correlated with data resolution.
+Instead, imbalance ratios remained consistent and low across resolutions.
+
+**Table 5.
+Jaccard Indices.** For K562, the median (range) Jaccard index illustrating the pairwise similarity between annotations within specific groups, including chromatin segmentation states, histone modifications, and transcription factor binding sites.
+The Jaccard Index measures the ratio of the number of intersecting base pairs between any two sets, to the number of base pairs in the union of the two sets.
+The number of cell line specific annotations included within each group is also provided.
+
 **Supplementary Figure 3.

### 2019-05-14 Manuscript/Tables/table_legends.Rmd
added tables; updated legends

@@
 **Table 2.
-Jaccard Indices.** The median (range) Jaccard index illustrating the pairwise similarity between annotations within specific groups, including chromatin segmentation states, histone modifications, and transcription factor binding sites.
+Inter-Resolution ICCs.** For GM12878, two-way intraclass correlation coefficients between resolutions for the following quantities: Number of genomic bins, number of TADs called, number of unique TAD boundaries, and imbalance ratio.
+The ICC was computed across 21 of the autosomal chromosomes.
+All quatities, except for imbalance ratio, was correlated with data resolution.
+Instead, imbalance ratios remained consistent and low across resolutions.
+
+**Table 3.
+Jaccard Indices.** For GM12878, the median (range) Jaccard index illustrating the pairwise similarity between annotations within specific groups, including chromatin segmentation states, histone modifications, and transcription factor binding sites.
 The Jaccard Index measures the ratio of the number of intersecting base pairs between any two sets, to the number of base pairs in the union of the two sets.

### 2019-05-14 Scripts/calculating_jaccard_index_between_annotations.Rmd
editted results scripts

@@
 ```
+
+###Plots
+
+```{r}
+jaccard.mat.k562 <- readRDS("Z:/TAD_data_analysis/jaccard/jaccard.mat.k562.rds")
+jaccard.mat.k562 <- jaccard.mat.k562[!duplicated(rownames(jaccard.mat.k562)), !duplicated(colnames(jaccard.mat.k562))]
+
+```
+
+####Chomatin States
+
+```{r}
+css <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
+css <- css[grep("K562", css)]
+css <- gsub(paste(c("K562-", ".bed"), collapse = "|"), "", css)
+jaccard.mat.k562.css <- jaccard.mat.k562[rownames(jaccard.mat.k562) %in% css, colnames(jaccard.mat.k562) %in% css]
+
+corrplot(jaccard.mat.k562.css, method = "square",
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("white", "red"))(100),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+get_upper_tri <- function(cormat){
+     cormat[lower.tri(cormat)]<- NA
+     return(cormat)
+}
+
+upper_tri_css <- get_upper_tri(jaccard.mat.k562.css)
+melted_css <- reshape2::melt(upper_tri_css, na.rm = TRUE)
+melted_css <- melted_css[-which(melted_css$Var1==melted_css$Var2),]
+summary(melted_css$value)
+```
+
+####Histone Modifications
+
+```{r}
+hm <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
+hm <- hm[grep("K562", hm)]
+hm <- gsub(paste(c("K562-", ".bed"), collapse = "|"), "", hm)
+jaccard.mat.k562.hm <- jaccard.mat.k562[rownames(jaccard.mat.k562) %in% hm, colnames(jaccard.mat.k562) %in% hm]
+
+corrplot(jaccard.mat.k562.hm, method = "square",
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         #tl.cex = .4,
+         col=colorRampPalette(c("white", "red"))(100),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+get_upper_tri <- function(cormat){
+     cormat[lower.tri(cormat)]<- NA
+     return(cormat)
+}
+
+upper_tri_hm <- get_upper_tri(jaccard.mat.k562.hm)
+melted_hm <- reshape2::melt(upper_tri_hm, na.rm = TRUE)
+melted_hm <- melted_hm[-which(melted_hm$Var1==melted_hm$Var2),]
+summary(melted_hm$value)
+```
+
+####TFBS
+
+```{r}
+tfbs <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/k562")
+tfbs <- tfbs[grep("K562", tfbs)]
+tfbs <- gsub(paste(c("K562-", ".bed","-Haib","-Sydh","-Uta","-Uw","-Broad","-Uchicago"), collapse = "|"), "", tfbs)
+jaccard.mat.k562.tfbs <- jaccard.mat.k562[rownames(jaccard.mat.k562) %in% tfbs, colnames(jaccard.mat.k562) %in% tfbs]
+
+corrplot(jaccard.mat.k562.tfbs, method = "square",
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .6,
+         col=colorRampPalette(c("white", "red"))(100),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+get_upper_tri <- function(cormat){
+     cormat[lower.tri(cormat)]<- NA
+     return(cormat)
+}
+
+upper_tri_tfbs <- get_upper_tri(jaccard.mat.k562.tfbs)
+melted_tfbs <- reshape2::melt(upper_tri_tfbs, na.rm = TRUE)
+melted_tfbs <- melted_tfbs[-which(melted_tfbs$Var1==melted_tfbs$Var2),]
+summary(melted_tfbs$value)
+```
+
+####All
+
+```{r}
+corrplot(jaccard.mat.k562, method = "square",
+         type="upper", 
+         order="hclust", 
+         tl.col="black", 
+         tl.srt=90,
+         tl.cex = .4,
+         col=colorRampPalette(c("white", "red"))(100),
+         cl.pos="n",
+         mar = c(0, 0, 0, 0))
+
+all_melted_k562 <- rbind.data.frame(melted_css,
+                                       melted_hm,
+                                       melted_tfbs)
+all_melted_k562$annotation <- c(rep("CSS", length(melted_css$Var1)),
+                                   rep("HM", length(melted_hm$Var1)),
+                                   rep("TFBS", length(melted_tfbs$Var1)))
+all_melted_k562$annotation <- factor(all_melted_k562$annotation, levels=c("CSS", "HM", "TFBS"))
+
+ggplot(all_melted_k562[-which(all_melted_k562$annotation=="CSS"),], aes(x=value, group=annotation, color=annotation)) + 
+  geom_density(size=1) +
+  xlim(0,1) +
+  xlab("Jaccard Index") +
+  ylab("Density") +
+  scale_color_discrete(name="Annotation Group") +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_text(size=15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+```

### 2019-05-14 Scripts/evaluating_imbalance_ratios.Rmd
editted results scripts

@@
 #Evaluating Imbalance Ratios
+
+<!--
 ##GM12878
@@
 ```		
+-->
 
+<!--	
 # Combined Plots
@@
 ```
+-->
 
@@
 ir.per.chr <- numeric()
+tads.per.chr <- numeric()
 
@@
 
+      tad_dat <- read.table(paste0("Z:/TAD_data_analysis/GSE63525_data/arrowhead_output/",
+                                            i,
+                                            "/",
+                                            paste0(i,"_domain_data_", gsub("kb", "000", j), ".b.txt")))
+
       cl.per.chr <- rbind(cl.per.chr, i)
@@
 
+      tads.per.chr <- rbind(tads.per.chr, dim(tad_dat[which(tad_dat$V1==k),])[1])
+
     }
@@
                           bins.per.chr,
+                          tads.per.chr,
                           bounds.per.chr,
                           ir.per.chr)
-colnames(irtab) <- c("cl","res","chr","bins","bounds","ir")
+colnames(irtab) <- c("cl","res","chr","bins","tads","bounds","ir")
+irtab$res <- factor(irtab$res, levels=c("10kb","25kb","50kb","100kb"))
 
@@
   group_by(cl, res) %>%
-  summarise(AveBins = mean(bins, na.rm = TRUE),
+  dplyr::summarise(AveBins = mean(bins, na.rm = TRUE),
             AveBinsSD = sd(bins, na.rm = TRUE),
+            AveTADs = mean(tads, na.rm = TRUE),
+            AveTADsSD = sd(tads, na.rm = TRUE),
             AveBounds = mean(bounds, na.rm = TRUE),
@@
 ```
+
+# ICC
+
+## GM12878
+
+### Number of genomic bins
+
+```{r}
+gbins <- reshape(irtab[which(irtab$cl=="GM12878"),c(2,3,4)], idvar = "chr", timevar = "res", direction = "wide")
+icc(gbins[,-1], model="twoway")
+```
+
+### Number of TADs
+
+```{r}
+tads <- reshape(irtab[which(irtab$cl=="GM12878"),c(2,3,5)], idvar = "chr", timevar = "res", direction = "wide")
+icc(tads[,-1], model="twoway")
+```
+
+### Number of boundaries
+
+```{r}
+bounds <- reshape(irtab[which(irtab$cl=="GM12878"),c(2,3,6)], idvar = "chr", timevar = "res", direction = "wide")
+icc(bounds[,-1], model="twoway")
+```
+
+### IR
+
+```{r}
+imbratio <- reshape(irtab[which(irtab$cl=="GM12878"),c(2,3,7)], idvar = "chr", timevar = "res", direction = "wide")
+icc(imbratio[,-1], model="twoway")
+```
+
+## K562
+
+### Number of genomic bins
+
+```{r}
+gbins <- reshape(irtab[which(irtab$cl=="K562"),c(2,3,4)], idvar = "chr", timevar = "res", direction = "wide")
+icc(gbins[,-1], model="twoway")
+```
+
+### Number of TADs
+
+```{r}
+tads <- reshape(irtab[which(irtab$cl=="K562"),c(2,3,5)], idvar = "chr", timevar = "res", direction = "wide")
+icc(tads[,-1], model="twoway")
+```
+
+### Number of boundaries
+
+```{r}
+bounds <- reshape(irtab[which(irtab$cl=="K562"),c(2,3,6)], idvar = "chr", timevar = "res", direction = "wide")
+icc(bounds[,-1], model="twoway")
+```
+
+### IR
+
+```{r}
+imbratio <- reshape(irtab[which(irtab$cl=="K562"),c(2,3,7)], idvar = "chr", timevar = "res", direction = "wide")
+icc(imbratio[,-1], model="twoway")
+```

### 2019-05-14 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-[??? include icc for each component of table 1 with resolution]
 The total number of genomic bins, which defined the dimensions of the data for modelling, was contingent upon the resolution of the contact matrix that cell line specific TADs were called on.
@@
 Higher resolutions were found to result in a greater number of TADs called.
-For GM12878, an average of 365.5, 222.4, 111.9, and 49.1 TADs were called across chromosomes, for each respective resolution (Table 1).
+For GM12878, an average of 375.0, 228.4, 115.1, and 50.6 TADs were called across chromosomes, for each respective resolution (Table 1).
 Average TADs called across chromosomes were found to be less on the K562 cell line at all resolutions (Supplementary Table 3).

### 2019-05-15 Manuscript/manuscript.Rmd
manuscript edits

@@
 To investigate the relationship between functional genomic annotations and the development of TAD boundaries, we devised 3 different predictor-types that composed the feature space of downstream random forest classification models.
-These predictor-type specific annotations represented the data matrix, **X** = {$X_{1}$, $X_{2}$, ..., $X_{p}$}, where *p* the set of annotations.
+These predictor-type specific annotations represented the data matrix, **X** = {$X_{1}$, $X_{2}$, ..., $X_{p}$}, where *p* is the complete set of functional annotations.
 Overlap counts was the least granular predictor-type considered, simply defined by the number of annotation-specific regions located within each genomic bin (Figure 2A).
@@
 
-We then developed an ensemble framework to systematically compare and establish the best set of data level characteristics for predicting TAD boundaries using random forest classifiers built on functional genomic annotations (Figure 3).
+We then developed an ensemble framework to systematically compare and establish the best set of data level characteristics for predicting TAD boundaries using random forest classifiers built on cell line specific functional genomic annotations (Figure 3).
 TAD boundaries were called using the arrowhead algorithm [@durand2016juicebox] from replicate Hi-C data for 2 cell lines *L* = {*GM12878*, *K562*}, at four different resolutions *R* = {*10 kb*, *25 kb*, *50 kb*, *100 kb*}.
@@
 To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including *B* = {*None*, *RUS*, *ROS*, *SMOTE*}.
-Each combination of the above parameters was repeated 21 times (number of autosomal chromosomes, excluding chromosome 9), *C* = {*1*, *2*, ..., *22*}.
+Each combination of the above parameters was implemented on chromosome specific sections of the linear genome, and thus, was repeated repeated 21 times (number of autosomal chromosomes, excluding chromosome 9), *C* = {*1*, *2*, ..., *22*}.
 A system produced from the ensemble framework was defined as: *S* = {*c*, *r*, *p*, *b*}, where *l* $\in$ *L*, *r* $\in$ *R*, *p* $\in$ *P*, *b* $\in$ *B*, and *c* $\in$ *C*.
@@
 Performances were then aggregated across each of the 21 chromosomes (omitting chromosome 9; see Methods).
+We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.
 
@@
 
-The total number of genomic bins, which defined the dimensions of the data for modelling, was contingent upon the resolution of the contact matrix that cell line specific TADs were called on.
-Higher resolutions resulted in smaller unit bin widths, which corresponded to larger numbers of genomic bins (Table 1).
-For GM12878, there was an average of 12,214.1, 4,892.7, 2,450.9, and 1,227.5 bins created across chromosomes, for each resolution respectively.
-Likewise, the average number of bins, respective to resolution, were found to be similar on the K562 cell line (Supplementary Table 3).
-
-As expected, the number of TADs called was related to resolution.
-Higher resolutions were found to result in a greater number of TADs called.
-For GM12878, an average of 375.0, 228.4, 115.1, and 50.6 TADs were called across chromosomes, for each respective resolution (Table 1).
-Average TADs called across chromosomes were found to be less on the K562 cell line at all resolutions (Supplementary Table 3).
-Although the downward trend was still present.
-As a result, a greater number of TADs corresponded to a greater number of TAD boundaries.
-For GM12878, the average number of TAD boundaries across chromosomes was found to be 1,254.6, 714.0, 364.4, and 165.3 for each resolution respectively (Table 1).
-Similar boundary profiles were exhibited on the K562 cell line (Supplementary Table 3).
-
-Furthermore, results showed that average imbalance ratios were consistently and severely low across resolutions, for both cell lines.
-For GM12878, the average imbalance ratios were found to be 0.12, 0.17, 0.17, and 0.15 for the 10 kb, 25 kb, 50 kb, and 100 kb resolutions respectively (Table 1).
-Slightly smaller resolution-specific and averaged imbalance ratios were featured on the K562 cell line, yet were still consistent and invariant to resolution.
+[???probably better to report medians here]
+For GM12878, the average number of genomic bins created across chromosomes was 12,214.1, 4,892.7, 2,450.9, and 1,227.5 for each resolution respectively (Table 1).
+Likewise, the average number chromosome specific TADs called on each resolution was found to be 375.0, 228.4, 115.1, and 50.6.
+These TADs resulted in an average of 1254.6, 714.0, 364.4, and 165.3 chromosome specific boundaries across each resolution.
+Each of these quantities was find to have a significantly large ICC, indicating that the number of genomic bins, TADs called, and corresponding unique boundaries were highly correlated between the different resolutions (Table 2).
+On the other hand, we found that the chromosome specific imbalance ratios remained consistenly severe across all resolution, with averages of 0.12, 0.17, 0.17, and 0.15 for each resolution respectively (ICC=0.114; p=0.109).
 Such low imbalance ratios indicated a wide disparity between the number of genomic bins that overlaped with a flanked TAD boundary and the much larger number that did not.
+The K562 cell line was found to exhibit similar profiles for the above quantities (Supplementary Tables 3-4)
 

### 2019-05-15 Manuscript/manuscript.Rmd
manuscript edits

@@
 We then tested four different re-sampling techniques aimed at creating balanced classes.
-Noninformative features were removed using a feature reduction algorithm and random forest classifications were built to assess model performance, and investigate which genomic annotations were most predictive of TAD boundaries for a given system from the complete ensemble.
+This process was performed on chromosome-specific regions on the linear genome.
+Noninformative features were removed using a feature reduction algorithm and classifiers were built to assess model performance, and investigate which genomic annotations were most predictive of TAD boundaries for a given system from the complete ensemble.
 
@@
 
-A regularization technique using a combination of the *l_{1}* and *l_{2}* penalties, known as the elastic-net, was used to reduce the feature space.
-The elastic-net was chosen in order to suitably reduce the feature space while also maintaining the inclusion of multiple correlated predictors.
+Architectural proteins tend to exhibit an extensive pattern of colocalization (correlation) [@van2014insulator].
+To measure the pairwise correlation of each cell line specific annotation, we used the Jaccard Index.
+The Jaccard Index measures the ratio of the number of intersecting base pairs between two sets to the number of base pairs in the union, subtracted by the intersection [@favorov2012exploring].
+The quantity ranges from 0.0 to 1.0, where 0.0 represents no overlap (no correlation) and 1.0 represent complete overlap (complete correlation).
+
+In order to suitably reduce the feature space while also maintaining the inclusion of possibly colocalized annotations, we implemented an elastic-net regularization technique prior to modelling.
+The technique using a combination of the *l_{1}* and *l_{2}* penalties.
 For each elastic-net regularization, 10-fold cross-validation was used to tune the parameters that controlled the penalty terms.
-The parameters that maximized the mean AUPRC across each cross-fold was chosen.
-All elastic-net algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
+<!--The parameters that maximized the mean AUPRC across each cross-fold was chosen.--> All elastic-net algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
 

### 2019-05-16 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-<!--
-## HIGH CORRRELATIONS IMPLY COLOCALIZATION OF MANY ANNOTATIONS AROUND TAD BOUNDARIES
+## HIGH JACCARD INDICES IMPLY COLOCALIZATION OF MANY GROUP-SPECIFC ANNOTATIONS
 
-By isolating flanked TAD boundaries and, in turn, counting the instances in which annotations overlapped with boundary regions, we were able to assess the correlations of genomic annotations and determine which annotations were enriched together at boundaries.
-Clustered correlograms for known colocalized annotations showed that distinct groups of transcription factors were highly positively correlated in both cell lines, and across resolutions, including CTCF, ZNF143, RAD21, and SMC3ab (Supplementary Figures 2-9).
-Likewise, combinations of particular histone modifications and chromatin states were also shown to exhibit similar profiles near TAD boundaries including H3K4me1, H3K4me2, and H3K4me3, as well as strong and weak enhancers.
-Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly positively inter-correlated, yet were negatively correlated with many transcription factor binding sites.
-Notably, correlations among annotations were found to increase as resolutions decreased for both cell lines.
-This indicated that TAD bounardies called, and subsequently flanked, at lower resolutions tended to encapsulate more of these epigenomic marks and contribute to higher levels of enrichment.
-
-The high correlations among many of the genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.
-For each model created from the ensemble framework, the alpha and lambda were tuned over a grid of values using 10-fold cross validation (Supplementary Table 7).
--->
+Using the jaccard index, we were able to determine which group-specific annotations were enriched together on the linear genome.
+As could be expected, for GM12878, the class of 14 annotations segmenting the chromation into different states exhibited very low pairwise correlations, with a jaccard index range of (0-0.001) (Table 1).
+However, specific sets of pairwise histone modifications and transcription factor binding sites (TFBS) were found to be highly enriched.
+The range of jaccard indices for the 10 histone modifications was found to be (0.022-0.539).
+Specifically, H3k27ac, H3k4me1, H3k4me2, and H3k4me3 were found to be highly correlated, high levels of which have been detected surrounding transcription start sites [@barski2007high].
+For the 79 TFBS, the range of jaccard indices was (<0.001-0.425).
+Here, known mediators of loop extrusion components were found to have high pairwise correlations including CTCF, RAD21, and SMC3 [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+Similar profiles of jaccard indices were exhibited across the sets of annotations for the K562 cell line (Supplementary Table 4).
+<!--The high jaccard indices among select sets of genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.-->
 
@@
 
+We then went on the evaluate the effect of class imbalance on model performance.
 In order to set a baseline in performance, we first evaluated the least granular model, that is one implemented using OC predictor types, without data re-sampling.

### 2019-05-16 Manuscript/Supplementary/supplementary_legends.Rmd
added two supplementary tables and updated legends

@@
 
+**Supplementary Table 6. Full list of aggregated performances for GM12878.** Performances were stratified by resolution, resampling technique, and predictor type, and then averaged across chromosomes.
+
+**Supplementary Table 7. Full list of aggregated performances for K562.** Performances were stratified by resolution, resampling technique, and predictor type, and then averaged across chromosomes.
+
 **Supplementary Figure 3.

### 2019-05-16 Scripts/creating_supplementary_table_of_all_performances.Rmd
editted results script

--- 2019-04-09 Scripts/creating_supplementary_table_of_all_performances.Rmd
@@
 
+## GM12878
+
 ```{r}
-#OC
-##None
-rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+rfperf_metric <- as.character()
+rfperf_chr <- as.character()
+rfperf_res <- as.character()
+rfperf_samp <- as.character()
+rfperf_pred <- as.character()
+rfperf_perf <- as.numeric()
 
-#OP
-##None
-rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+for(i in c("10kb", "25kb", "50kb", "100kb")){
+  for(j in paste0("CHR", c(1:8,10:22))){
+    for(k in c("none", "ros", "rus", "smote")){
+      for(l in c("oc","op","distance")){
+        perfdat <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/",
+                                 i,
+                                 "/results_by_chr/",
+                                 j,
+                                 "/",
+                                 k,
+                                 "/",
+                                 l,
+                                 "/enet/rfperf.rds"))
 
-#Distance
-##None
-rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+        rfperf_res <- c(rfperf_res, rep(i,8))
+        rfperf_chr <- c(rfperf_chr,rep(j,8))
+        rfperf_samp <- c(rfperf_samp,rep(k,8))
+        rfperf_pred <- c(rfperf_pred,rep(l,8))
+        rfperf_metric <- c(rfperf_metric, as.character(perfdat$Metric[c(6,7,9,10,15:17,19)]))
+        rfperf_perf <- c(rfperf_perf, perfdat$Performance[c(6,7,9,10,15:17,19)])
 
-#OC
-##None
-rfperf_gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+      }
+    }
+  }
+}
 
-#OP
-##None
-rfperf_gm12878_25kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
+gm12878_all_perfs <- cbind.data.frame(rfperf_res, rfperf_chr, rfperf_samp, rfperf_pred, rfperf_metric, rfperf_perf)
+colnames(gm12878_all_perfs) <- c("Resolution", "CHR", "Resampling", "Predictor", "Metric", "Performance")
 
-#Distance
-##None
-rfperf_gm12878_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
+gm12878_all_perfs$Resolution <- factor(gm12878_all_perfs$Resolution, levels=c("10kb","25kb","50kb","100kb"))
+gm12878_all_perfs$CHR <- factor(gm12878_all_perfs$CHR, levels=paste0("CHR", c(1:8,10:22)))
+gm12878_all_perfs$Resampling <- factor(gm12878_all_perfs$Resampling, levels=c("none", "ros", "rus", "smote"))
+gm12878_all_perfs$Predictor <- factor(gm12878_all_perfs$Predictor, levels=c("oc","op","distance"))
+gm12878_all_perfs$Metric <- factor(gm12878_all_perfs$Metric, levels=c("Sensitivity", "Specificity", "Accuracy", "Precision", "MCC", "F1", "AUC", "AUPRC"))
 
-#OC
-##None
-rfperf_gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
+gm12878_all_perfs_summ <- gm12878_all_perfs %>%
+  group_by(Resolution, Resampling, Predictor, Metric) %>%
+  dplyr::summarise(AvePerf = mean(Performance, na.rm = TRUE),
+            SDPerf = sd(Performance, na.rm = TRUE))
 
-#OP
-##None
-rfperf_gm12878_50kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_gm12878_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##None
-rfperf_gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_gm12878_100kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_gm12878_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_gm12878_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_gm12878_10kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_gm12878_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_gm12878_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_gm12878_25kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_gm12878_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_gm12878_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_gm12878_50kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_gm12878_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_gm12878_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_gm12878_100kb_ROS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_gm12878_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_gm12878_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_gm12878_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_gm12878_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_gm12878_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_gm12878_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_gm12878_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_gm12878_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_gm12878_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_gm12878_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_gm12878_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_gm12878_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_gm12878_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_gm12878_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_gm12878_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_gm12878_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_gm12878_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_gm12878_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_gm12878_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_gm12878_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_gm12878_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_gm12878_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_gm12878_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_gm12878_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_gm12878_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##None
-rfperf_K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_K562_10kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_K562_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##None
-rfperf_K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_K562_25kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_K562_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##None
-rfperf_K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_K562_50kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_K562_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##None
-rfperf_K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/RF/rfperf.rds")
-
-#OP
-##None
-rfperf_K562_100kb_none_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##None
-rfperf_K562_100kb_none_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_K562_10kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_K562_10kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_K562_10kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_K562_25kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_K562_25kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_K562_25kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_K562_50kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_K562_50kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_K562_50kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##ROS
-rfperf_K562_100kb_ROS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##ROS
-rfperf_K562_100kb_ROS_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##ROS
-rfperf_K562_100kb_ROS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_K562_10kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_K562_10kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_K562_10kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_K562_25kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_K562_25kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_K562_25kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_K562_50kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_K562_50kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_K562_50kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##RUS
-rfperf_K562_100kb_RUS_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")
-
-#OP
-##RUS
-rfperf_K562_100kb_RUS_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##RUS
-rfperf_K562_100kb_RUS_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_K562_10kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_K562_10kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_K562_10kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_K562_25kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_K562_25kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_K562_25kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_K562_50kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_K562_50kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_K562_50kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
-
-#OC
-##SMOTE
-rfperf_K562_100kb_SMOTE_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")
-
-#OP
-##SMOTE
-rfperf_K562_100kb_SMOTE_op <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")
-
-#Distance
-##SMOTE
-rfperf_K562_100kb_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")
+gm12878_all_perfs_summ$AvePerf <- round(gm12878_all_perfs_summ$AvePerf, 3)
+gm12878_all_perfs_summ$SDPerf <- round(gm12878_all_perfs_summ$SDPerf, 3)
 
@@
 
-# Creating and saving table with all results
+## K562
 
 ```{r}
-all_rfperfs_df <- rbind.data.frame(rfperf_gm12878_10kb_none_oc,
-                                   rfperf_gm12878_10kb_none_op,
-                                   rfperf_gm12878_10kb_none_dist,
-                                   rfperf_gm12878_25kb_none_oc,
-                                   rfperf_gm12878_25kb_none_op,
-                                   rfperf_gm12878_25kb_none_dist,
-                                   rfperf_gm12878_50kb_none_oc,
-                                   rfperf_gm12878_50kb_none_op,
-                                   rfperf_gm12878_50kb_none_dist,
-                                   rfperf_gm12878_100kb_none_oc,
-                                   rfperf_gm12878_100kb_none_op,
-                                   rfperf_gm12878_100kb_none_dist,
+rfperf_metric <- as.character()
+rfperf_chr <- as.character()
+rfperf_res <- as.character()
+rfperf_samp <- as.character()
+rfperf_pred <- as.character()
+rfperf_perf <- as.numeric()
 
-                                   rfperf_gm12878_10kb_ROS_oc,
-                                   rfperf_gm12878_10kb_ROS_op,
-                                   rfperf_gm12878_10kb_ROS_dist,
-                                   rfperf_gm12878_25kb_ROS_oc,
-                                   rfperf_gm12878_25kb_ROS_op,
-                                   rfperf_gm12878_25kb_ROS_dist,
-                                   rfperf_gm12878_50kb_ROS_oc,
-                                   rfperf_gm12878_50kb_ROS_op,
-                                   rfperf_gm12878_50kb_ROS_dist,
-                                   rfperf_gm12878_100kb_ROS_oc,
-                                   rfperf_gm12878_100kb_ROS_op,
-                                   rfperf_gm12878_100kb_ROS_dist,
+for(i in c("10kb", "25kb", "50kb", "100kb")){
+  for(j in paste0("CHR", c(1:8,10:22))){
+    for(k in c("none", "ros", "rus", "smote")){
+      for(l in c("oc","op","distance")){
+        perfdat <- readRDS(paste0("Z:/TAD_data_analysis/K562/",
+                                 i,
+                                 "/results_by_chr/",
+                                 j,
+                                 "/",
+                                 k,
+                                 "/",
+                                 l,
+                                 "/enet/rfperf.rds"))
 
-                                   rfperf_gm12878_10kb_RUS_oc,
-                                   rfperf_gm12878_10kb_RUS_op,
-                                   rfperf_gm12878_10kb_RUS_dist,
-                                   rfperf_gm12878_25kb_RUS_oc,
-                                   rfperf_gm12878_25kb_RUS_op,
-                                   rfperf_gm12878_25kb_RUS_dist,
-                                   rfperf_gm12878_50kb_RUS_oc,
-                                   rfperf_gm12878_50kb_RUS_op,
-                                   rfperf_gm12878_50kb_RUS_dist,
-                                   rfperf_gm12878_100kb_RUS_oc,
-                                   rfperf_gm12878_100kb_RUS_op,
-                                   rfperf_gm12878_100kb_RUS_dist,
+        rfperf_res <- c(rfperf_res, rep(i,8))
+        rfperf_chr <- c(rfperf_chr,rep(j,8))
+        rfperf_samp <- c(rfperf_samp,rep(k,8))
+        rfperf_pred <- c(rfperf_pred,rep(l,8))
+        rfperf_metric <- c(rfperf_metric, as.character(perfdat$Metric[c(6,7,9,10,15:17,19)]))
+        rfperf_perf <- c(rfperf_perf, perfdat$Performance[c(6,7,9,10,15:17,19)])
 
-                                   rfperf_gm12878_10kb_SMOTE_oc,
-                                   rfperf_gm12878_10kb_SMOTE_op,
-                                   rfperf_gm12878_10kb_SMOTE_dist,
-                                   rfperf_gm12878_25kb_SMOTE_oc,
-                                   rfperf_gm12878_25kb_SMOTE_op,
-                                   rfperf_gm12878_25kb_SMOTE_dist,
-                                   rfperf_gm12878_50kb_SMOTE_oc,
-                                   rfperf_gm12878_50kb_SMOTE_op,
-                                   rfperf_gm12878_50kb_SMOTE_dist,
-                                   rfperf_gm12878_100kb_SMOTE_oc,
-                                   rfperf_gm12878_100kb_SMOTE_op,
-                                   rfperf_gm12878_100kb_SMOTE_dist,
+      }
+    }
+  }
+}
 
-                                   rfperf_K562_10kb_none_oc,
-                                   rfperf_K562_10kb_none_op,
-                                   rfperf_K562_10kb_none_dist,
-                                   rfperf_K562_25kb_none_oc,
-                                   rfperf_K562_25kb_none_op,
-                                   rfperf_K562_25kb_none_dist,
-                                   rfperf_K562_50kb_none_oc,
-                                   rfperf_K562_50kb_none_op,
-                                   rfperf_K562_50kb_none_dist,
-                                   rfperf_K562_100kb_none_oc,
-                                   rfperf_K562_100kb_none_op,
-                                   rfperf_K562_100kb_none_dist,
+K562_all_perfs <- cbind.data.frame(rfperf_res, rfperf_chr, rfperf_samp, rfperf_pred, rfperf_metric, rfperf_perf)
+colnames(K562_all_perfs) <- c("Resolution", "CHR", "Resampling", "Predictor", "Metric", "Performance")
 
-                                   rfperf_K562_10kb_ROS_oc,
-                                   rfperf_K562_10kb_ROS_op,
-                                   rfperf_K562_10kb_ROS_dist,
-                                   rfperf_K562_25kb_ROS_oc,
-                                   rfperf_K562_25kb_ROS_op,
-                                   rfperf_K562_25kb_ROS_dist,
-                                   rfperf_K562_50kb_ROS_oc,
-                                   rfperf_K562_50kb_ROS_op,
-                                   rfperf_K562_50kb_ROS_dist,
-                                   rfperf_K562_100kb_ROS_oc,
-                                   rfperf_K562_100kb_ROS_op,
-                                   rfperf_K562_100kb_ROS_dist,
+K562_all_perfs$Resolution <- factor(K562_all_perfs$Resolution, levels=c("10kb","25kb","50kb","100kb"))
+K562_all_perfs$CHR <- factor(K562_all_perfs$CHR, levels=paste0("CHR", c(1:8,10:22)))
+K562_all_perfs$Resampling <- factor(K562_all_perfs$Resampling, levels=c("none", "ros", "rus", "smote"))
+K562_all_perfs$Predictor <- factor(K562_all_perfs$Predictor, levels=c("oc","op","distance"))
+K562_all_perfs$Metric <- factor(K562_all_perfs$Metric, levels=c("Sensitivity", "Specificity", "Accuracy", "Precision", "MCC", "F1", "AUC", "AUPRC"))
 
-                                   rfperf_K562_10kb_RUS_oc,
-                                   rfperf_K562_10kb_RUS_op,
-                                   rfperf_K562_10kb_RUS_dist,
-                                   rfperf_K562_25kb_RUS_oc,
-                                   rfperf_K562_25kb_RUS_op,
-                                   rfperf_K562_25kb_RUS_dist,
-                                   rfperf_K562_50kb_RUS_oc,
-                                   rfperf_K562_50kb_RUS_op,
-                                   rfperf_K562_50kb_RUS_dist,
-                                   rfperf_K562_100kb_RUS_oc,
-                                   rfperf_K562_100kb_RUS_op,
-                                   rfperf_K562_100kb_RUS_dist,
+K562_all_perfs_summ <- K562_all_perfs %>%
+  group_by(Resolution, Resampling, Predictor, Metric) %>%
+  dplyr::summarise(AvePerf = mean(Performance, na.rm = TRUE),
+            SDPerf = sd(Performance, na.rm = TRUE))
 
-                                   rfperf_K562_10kb_SMOTE_oc,
-                                   rfperf_K562_10kb_SMOTE_op,
-                                   rfperf_K562_10kb_SMOTE_dist,
-                                   rfperf_K562_25kb_SMOTE_oc,
-                                   rfperf_K562_25kb_SMOTE_op,
-                                   rfperf_K562_25kb_SMOTE_dist,
-                                   rfperf_K562_50kb_SMOTE_oc,
-                                   rfperf_K562_50kb_SMOTE_op,
-                                   rfperf_K562_50kb_SMOTE_dist,
-                                   rfperf_K562_100kb_SMOTE_oc,
-                                   rfperf_K562_100kb_SMOTE_op,
-                                   rfperf_K562_100kb_SMOTE_dist)
+K562_all_perfs_summ$AvePerf <- round(K562_all_perfs_summ$AvePerf, 3)
+K562_all_perfs_summ$SDPerf <- round(K562_all_perfs_summ$SDPerf, 3)
 
-all_rfperfs_df$CellLine <- c(rep("GM12878",19*48),rep("K562",19*48))
-all_rfperfs_df$Resolution <- rep(c(rep("10 kb", 19*3),rep("25 kb", 19*3),rep("50 kb", 19*3),rep("100 kb", 19*3)),8)
-all_rfperfs_df$Resampling <- rep(c(rep("None",19*12),rep("ROS",19*12),rep("RUS",19*12),rep("SMOTE",19*12)), 2)
-all_rfperfs_df$PredictorType <- rep(c("OC", "OP", "Distance"),19*32)
-
-all_rfperfs_df <- all_rfperfs_df[,c(3,4,5,6,1,2)]
-all_rfperfs_df$Performance <- round(all_rfperfs_df$Performance, 3)
-
-write.csv(all_rfperfs_df, "C:/Users/stili/Downloads/table3_all_model_performances.csv")
 ```

### 2019-05-16 Manuscript/manuscript.Rmd
manuscript edits

@@
 We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 5A).
-We then gradually increased the granularity by assessing models built on OP predictor types, while still not performing any data resampling.
-Interestingly, we found that MCCs were worse than when using OC predictor types for the GM12878 cell line (Figure 5B).
-When including distance-type predictors, models were found to exhibit slightly better MCCs than the other two types (Figure 5C).
-Importantly, when validating these 3 models built on fully imbalanced datasets, the MCC could not be determined at lower resolutions given by the model's complete inability to correctly classify any genomic bins that overlapped with flanked TAD boundaries in the test data, thereby resulting in 0 true positives.
-Results were found to be consistently poor across resolutions for the K562 cell line (Supplementary Figure 10).
-Similarly, many of the performance metrics at higher resolutions were also unable to be reported due to the models inability to produce any true positive cases.
-<!--Furthermore, we found that evaluating models using conventional metrics, such as AUC or accuracy, did not depict the true severity in performance (Supplementary Table 4).-->
+We gradually increased the granularity by assessing models built on OP predictor types, while still not performing any data resampling.
+Here, the results were similar to that of OC types (Figure 5B).
+However, when including distance-type predictors, models were found to exhibit a marked improvement in MCC compared to the other two types (Figure 5C).
+Results were found to be consistently poor across resolutions and predictor types, when implemented on the K562 cell line (Supplementary Figure 3).
+Furthermore, we found that conventional metrics of performance (i.e.
+accuracy, sensitivity and specificity, and AUC) were less sensitive for models built on imbalanced data, regardless of cell line, resolution, or predictor-type (Supplementary Tables 6-7).
 
@@
 
-When models were built on randomly oversampled (ROS) data, we found a substantial increase in MCC for the GM12878 cell line (Figure 5 A-C).
+When models were built on randomly oversampled (ROS) data for GM12878, we found an increase in MCC compared to no resampling, at higher resolutions.
 The biggest improvement in performance was seen at the 10 kb resolution in each of the 3 predictor types, with a downward trend as resolutions decreased.
-Although performances were low at lower resolutions, MCC values were able to be obtained, contrary to models built on completely unbalanced data as seen before.
-Distance-type predictors were found to offer the highest MCCs for ROS data, across all resolutions.
-Similar results were obtained when applying ROS to the K562 cell line (Supplementary Figure 10).
-For K562, a much sharper negative trend was featured for MCCs as resolution decreased, than in the GM12878 cell line.
+Again, distance-type predictors were found to offer the highest MCCs for ROS data, across all resolutions.
+Similar results were obtained when applying ROS to the K562 cell line (Supplementary Figure 3).
 
-Further improvement in performance was found when models were implemented on both randomly undersampled (RUS) and SMOTE resampled data, for all 3 predictor types and across resolutions (Figure 5).
-SMOTE resampled data was found to yield the best MCCs among all classes of models developed and compared in the ensemble framework.
+Further improvement in performance was found when models were implemented on both randomly undersampled (RUS) and SMOTE resampled data, especially between models with OC and OP predictor types.
+When using RUS or SMOTE, implemented on distance type predictors, we found a clear improvement compared to the other predictor types.
+However, there was less of a separation between ROS and RUS techniques within the ensemble of models using distance type predictors.
+
+Overall, SMOTE resampled data was found to yield the best MCCs among all classes of models developed and compared in the ensemble framework.
 Here, distance type predictors were found to again yield the highest MCC values across resolutions.
-SMOTE re-sampled data, with the inclusion of distance-type predictors was also found to be the best set of characteristics when applied to the K562 cell line (Supplementary Figure 10).
+It should be noted that, SMOTE re-sampled data, with the inclusion of distance-type predictors was also found to be the best set of characteristics when applied to the K562 cell line (Supplementary Figure 3).
 Moreover, for these sets of data characteristics, we again found that there was a degredation in model performance as data resolution decreased.
-This was much more pronounced in the K562 cell line.
-On the GM12878 cell line, there were only marginal differences in performance between 10 kb and 25 kb, followed by a steep decline at 50 kb.
-Then, the MCCs showed a momentary increase in performance at 100 kb, the lowest resolution considered in the study.
-Performances from the K562 cell line degraded much faster as resolution decreased, starting with highest performance at 10 kb and ending with the worst performance at 100 kb.
-These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on distance-type predictors and incorporates both random under- and over-sampling.
-Furthermore, models built on TAD boundaries called at higher resolutions exhibited better performances.
+Results indicated that performances exhibited much more variability when built on lower resolutions, specifically at the 100 kb level.
+These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
 

### 2019-05-16 Manuscript/Figures/figure_legends.Rmd
editted figure legends

@@
 **Figure 5.
+Predictive importance is outweighed by transcription factor binding sites.** Stacked barplots illustrating the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework, for each resolution on GM12878.
+Proportions are separated by the set of annotations included in the feature space including chromatin state segmentation, histone modification, and transcription factor binding sites.
+
+**Figure 6.
 Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for GM12878.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
@@
 
-**Figure 6.
+**Figure 7.
 Predictive importance.** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for GM12878.

### 2019-05-16 Manuscript/Supplementary/supplementary_legends.Rmd
editted figure legends

@@
 **Supplementary Figure 4.
+Predictive importance is outweighed by transcription factor binding sites.** Stacked barplots illustrating the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework, for each resolution on K562.
+Proportions are separated by the set of annotations included in the feature space including chromatin state segmentation, histone modification, and transcription factor binding sites.
+
+**Supplementary Figure 5.
 Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for K562.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
@@
 
-**Supplementary Figure 5.
+**Supplementary Figure 6.
 Predictive importance** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for K562.

### 2019-05-16 Scripts/evaluating_feature_reduction.Rmd
added results scripts

--- 2019-03-12 Scripts/evaluating_feature_reduction.Rmd
@@
 library(pROC)
-library(plyr)
 library(dplyr)
@@
 library(ROCR)
-#library(leaps)
 library(cluster)
@@
 
-## Heatmaps of whether or not a variable was reduced
-
-### GM12878
-
-####10kb
+##GM12878
 
 ```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
+chromstates <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
+chromstates <- chromstates[grep("Gm12878", chromstates)]
+chromstates <- gsub(paste0(c("Gm12878-", ".bed"), collapse = "|"),"",chromstates)
 
-features <- names(train)[-1]
-features <- features[grep("dist", features)]
-features <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist", 
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", features)
+histones <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
+histones <- histones[grep("Gm12878", histones)]
+histones <- gsub(paste0(c("Gm12878-", ".bed"), collapse = "|"),"",histones)
 
-#None
-##OC
-enetcoefs_none_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_none_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_none_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
+tfbs <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878")
+tfbs <- gsub(paste0(c("Gm12878-", ".bed", "-Haib", "-Sydh", "-Broad", "-Uw", "-Uta", "-Chicago"), collapse = "|"),"", tfbs)
+tfbs <- tfbs[!duplicated(tfbs)]
 
-#RUS
-##OC
-enetcoefs_RUS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_RUS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_RUS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
+ratio.per.chr <- as.numeric()
 
-#ROS
-##OC
-enetcoefs_ROS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_ROS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_ROS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
+for(i in c("10kb", "25kb", "50kb", "100kb")){
+  for(j in paste0("CHR", c(1:8,10:22))){
+    enetvars <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/",
+                                 i,
+                                 "/results_by_chr/",
+                                 j,
+                                 "/smote/distance/enet/enetcoefs.rds"))
 
-#SMOTE
-##OC
-enetcoefs_SMOTE_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_SMOTE_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_SMOTE_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
+    enetvars <- gsub("_dist", "", enetvars)
 
-enetcoefslist <- list(enetcoefs_none_oc_10kb_gm12878, 
-                      enetcoefs_none_op_10kb_gm12878, 
-                      enetcoefs_none_dist_10kb_gm12878,
-                      enetcoefs_RUS_oc_10kb_gm12878, 
-                      enetcoefs_RUS_op_10kb_gm12878, 
-                      enetcoefs_RUS_dist_10kb_gm12878,
-                      enetcoefs_ROS_oc_10kb_gm12878, 
-                      enetcoefs_ROS_op_10kb_gm12878, 
-                      enetcoefs_ROS_dist_10kb_gm12878,
-                      enetcoefs_SMOTE_oc_10kb_gm12878, 
-                      enetcoefs_SMOTE_op_10kb_gm12878, 
-                      enetcoefs_SMOTE_dist_10kb_gm12878)
+    cssratio <- length(intersect(enetvars, chromstates))/length(chromstates)
+    hmratio <- length(intersect(enetvars, histones))/length(histones)
+    tfbsratio <- length(intersect(enetvars, tfbs))/length(tfbs)
 
-enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
+    #res.per.chr <- c(res.per.chr, i)
+    #ann.per.chr <- c(ann.per.chr, j)
+    #chr.per.chr <- c(chr.per.chr, c("CSS", "HM", "TFBS"))
+    ratio.per.chr <- c(ratio.per.chr, c(cssratio,hmratio,tfbsratio))
 
-featuremat_10kb_gm12878 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
-                                                                    "Predictor Type"=rep(c("OC",
-                                                                                         "OP", 
-                                                                                         "Distance"),4)))
-
-for(j in 1:length(enetcoefslist)){
-    featuremat_10kb_gm12878[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
+  }
 }
 
-#using lattice
-levelplot(t(featuremat_10kb_gm12878), 
-          colorkey=FALSE, 
-          scales=list(x=list(rot=45),
-                      alternating=3), 
-          col.regions=c("white", "red"),
-          aspect="fill",panel = function(...){
-            panel.levelplot(...)
-            panel.abline(v = 3.5);
-            panel.abline(v = 6.5);
-            panel.abline(v = 9.5);
-          },
-          xlab="",
-          ylab="")
-grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
-grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
-grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
-grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
+enet_ratios_gm12878 <- cbind.data.frame(Ratio=ratio.per.chr,
+                                        Annotation=rep(c("CSS","HM","TFBS"), 84),
+                                        Chromosome=rep(c(rep("CHR1",3),
+                                                     rep("CHR2",3),
+                                                     rep("CHR3",3),
+                                                     rep("CHR4",3),
+                                                     rep("CHR5",3),
+                                                     rep("CHR6",3),
+                                                     rep("CHR7",3),
+                                                     rep("CHR8",3),
+                                                     rep("CHR10",3),
+                                                     rep("CHR11",3),
+                                                     rep("CHR12",3),
+                                                     rep("CHR13",3),
+                                                     rep("CHR14",3),
+                                                     rep("CHR15",3),
+                                                     rep("CHR16",3),
+                                                     rep("CHR17",3),
+                                                     rep("CHR18",3),
+                                                     rep("CHR19",3),
+                                                     rep("CHR20",3),
+                                                     rep("CHR21",3),
+                                                     rep("CHR22",3)),4),
+                                        Resolution=c(rep("10 kb", 21*3),
+                                                     rep("25 kb", 21*3),
+                                                     rep("50 kb", 21*3),
+                                                     rep("100 kb", 21*3)))
+
+enet_ratios_gm12878_summ <- enet_ratios_gm12878 %>%
+  group_by(Resolution, Annotation) %>%
+  dplyr::summarise(AveRatio = mean(Ratio, na.rm = TRUE),
+            AveRatioSD = sd(Ratio, na.rm = TRUE))
 
 ```
-
-####25kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
-
-features <- names(train)[-1]
-features <- features[grep("dist", features)]
-features <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist", 
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", features)
-
-#None
-##OC
-enetcoefs_none_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_none_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_none_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
-
-#RUS
-##OC
-enetcoefs_RUS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_RUS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_RUS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
-
-#ROS
-##OC
-enetcoefs_ROS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_ROS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_ROS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
-
-#SMOTE
-##OC
-enetcoefs_SMOTE_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_SMOTE_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_SMOTE_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
-
-enetcoefslist <- list(enetcoefs_none_oc_25kb_gm12878, 
-                      enetcoefs_none_op_25kb_gm12878, 
-                      enetcoefs_none_dist_25kb_gm12878,
-                      enetcoefs_RUS_oc_25kb_gm12878, 
-                      enetcoefs_RUS_op_25kb_gm12878, 
-                      enetcoefs_RUS_dist_25kb_gm12878,
-                      enetcoefs_ROS_oc_25kb_gm12878, 
-                      enetcoefs_ROS_op_25kb_gm12878, 
-                      enetcoefs_ROS_dist_25kb_gm12878,
-                      enetcoefs_SMOTE_oc_25kb_gm12878, 
-                      enetcoefs_SMOTE_op_25kb_gm12878, 
-                      enetcoefs_SMOTE_dist_25kb_gm12878)
-
-enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
-
-featuremat_25kb_gm12878 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
-                                                                    "Predictor Type"=rep(c("OC",
-                                                                                         "OP", 
-                                                                                         "Distance"),4)))
-
-for(j in 1:length(enetcoefslist)){
-    featuremat_25kb_gm12878[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
-}
-
-#using lattice
-levelplot(t(featuremat_25kb_gm12878), 
-          colorkey=FALSE, 
-          scales=list(x=list(rot=45),
-                      alternating=3), 
-          col.regions=c("white", "red"),
-          aspect="fill",panel = function(...){
-            panel.levelplot(...)
-            panel.abline(v = 3.5);
-            panel.abline(v = 6.5);
-            panel.abline(v = 9.5);
-          },
-          xlab="",
-          ylab="")
-grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
-grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
-grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
-grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
-
-```
-
-####50kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
-
-features <- names(train)[-1]
-features <- features[grep("dist", features)]
-features <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist", 
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", features)
-
-#None
-##OC
-enetcoefs_none_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_none_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_none_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
-
-#RUS
-##OC
-enetcoefs_RUS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_RUS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_RUS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
-
-#ROS
-##OC
-enetcoefs_ROS_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_ROS_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_ROS_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
-
-#SMOTE
-##OC
-enetcoefs_SMOTE_oc_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_SMOTE_op_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_SMOTE_dist_50kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
-
-enetcoefslist <- list(enetcoefs_none_oc_50kb_gm12878, 
-                      enetcoefs_none_op_50kb_gm12878, 
-                      enetcoefs_none_dist_50kb_gm12878,
-                      enetcoefs_RUS_oc_50kb_gm12878, 
-                      enetcoefs_RUS_op_50kb_gm12878, 
-                      enetcoefs_RUS_dist_50kb_gm12878,
-                      enetcoefs_ROS_oc_50kb_gm12878, 
-                      enetcoefs_ROS_op_50kb_gm12878, 
-                      enetcoefs_ROS_dist_50kb_gm12878,
-                      enetcoefs_SMOTE_oc_50kb_gm12878, 
-                      enetcoefs_SMOTE_op_50kb_gm12878, 
-                      enetcoefs_SMOTE_dist_50kb_gm12878)
-
-enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
-
-featuremat_50kb_gm12878 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
-                                                                    "Predictor Type"=rep(c("OC",
-                                                                                         "OP", 
-                                                                                         "Distance"),4)))
-
-for(j in 1:length(enetcoefslist)){
-    featuremat_50kb_gm12878[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
-}
-
-#using lattice
-levelplot(t(featuremat_50kb_gm12878), 
-          colorkey=FALSE, 
-          scales=list(x=list(rot=45),
-                      alternating=3), 
-          col.regions=c("white", "red"),
-          aspect="fill",panel = function(...){
-            panel.levelplot(...)
-            panel.abline(v = 3.5);
-            panel.abline(v = 6.5);
-            panel.abline(v = 9.5);
-          },
-          xlab="",
-          ylab="")
-grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
-grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
-grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
-grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
-
-```
-
-####100kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
-
-features <- names(train)[-1]
-features <- features[grep("dist", features)]
-features <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist", 
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", features)
-
-#None
-##OC
-enetcoefs_none_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_none_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_none_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
-
-#RUS
-##OC
-enetcoefs_RUS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_RUS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_RUS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
-
-#ROS
-##OC
-enetcoefs_ROS_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_ROS_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_ROS_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
-
-#SMOTE
-##OC
-enetcoefs_SMOTE_oc_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_SMOTE_op_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_SMOTE_dist_100kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
-
-enetcoefslist <- list(enetcoefs_none_oc_100kb_gm12878, 
-                      enetcoefs_none_op_100kb_gm12878, 
-                      enetcoefs_none_dist_100kb_gm12878,
-                      enetcoefs_RUS_oc_100kb_gm12878, 
-                      enetcoefs_RUS_op_100kb_gm12878, 
-                      enetcoefs_RUS_dist_100kb_gm12878,
-                      enetcoefs_ROS_oc_100kb_gm12878, 
-                      enetcoefs_ROS_op_100kb_gm12878, 
-                      enetcoefs_ROS_dist_100kb_gm12878,
-                      enetcoefs_SMOTE_oc_100kb_gm12878, 
-                      enetcoefs_SMOTE_op_100kb_gm12878, 
-                      enetcoefs_SMOTE_dist_100kb_gm12878)
-
-enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
-
-featuremat_100kb_gm12878 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
-                                                                    "Predictor Type"=rep(c("OC",
-                                                                                         "OP", 
-                                                                                         "Distance"),4)))
-
-for(j in 1:length(enetcoefslist)){
-    featuremat_100kb_gm12878[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
-}
-
-#using lattice
-levelplot(t(featuremat_100kb_gm12878), 
-          colorkey=FALSE, 
-          scales=list(x=list(rot=45),
-                      alternating=3), 
-          col.regions=c("white", "red"),
-          aspect="fill",panel = function(...){
-            panel.levelplot(...)
-            panel.abline(v = 3.5);
-            panel.abline(v = 6.5);
-            panel.abline(v = 9.5);
-          },
-          xlab="",
-          ylab="")
-grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
-grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
-grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
-grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
-
-```
-
-####Combined
-
-```{r}
-all_featuremat_gm12878 <- cbind(featuremat_10kb_gm12878,
-                                featuremat_25kb_gm12878,
-                                featuremat_50kb_gm12878,
-                                featuremat_100kb_gm12878)
-all_featuremat_gm12878 <- all_featuremat_gm12878[,c(seq(1,48,3),
-                                                    seq(2,48,3),
-                                                    seq(3,48,3))]
-colnames(all_featuremat_gm12878) <- rep(c("None", "RUS", "ROS", "SMOTE"), 12)
-
-levelplot(t(all_featuremat_gm12878), 
-          colorkey=FALSE, 
-          scales=list(x=list(rot=45, cex=.5),
-                      #alternating=3,
-                      y=list(cex=.5)), 
-          col.regions=c("white", "red"),
-          aspect="fill",panel = function(...){
-            panel.levelplot(...)
-			#horizontal lines
-			panel.abline(h = 1.5);
-			panel.abline(h = 2.5);
-			panel.abline(h = 3.5);
-			panel.abline(h = 4.5);
-			panel.abline(h = 5.5);
-			panel.abline(h = 6.5);
-			panel.abline(h = 7.5);
-			panel.abline(h = 8.5);
-			panel.abline(h = 9.5);
-			panel.abline(h = 10.5);
-			panel.abline(h = 11.5);
-			panel.abline(h = 12.5);
-			panel.abline(h = 13.5);
-			panel.abline(h = 14.5);
-			panel.abline(h = 15.5);
-			panel.abline(h = 16.5);
-			panel.abline(h = 17.5);
-			panel.abline(h = 18.5);
-			panel.abline(h = 19.5);
-			panel.abline(h = 20.5);
-			panel.abline(h = 21.5);
-			panel.abline(h = 22.5);
-			panel.abline(h = 23.5);
-			panel.abline(h = 24.5);
-			panel.abline(h = 25.5);
-			panel.abline(h = 26.5);
-			panel.abline(h = 27.5);
-			panel.abline(h = 28.5);
-			panel.abline(h = 29.5);
-			panel.abline(h = 30.5);
-			panel.abline(h = 31.5);
-			panel.abline(h = 32.5);
-			panel.abline(h = 33.5);
-			panel.abline(h = 34.5);
-			panel.abline(h = 35.5);
-			panel.abline(h = 36.5);
-			panel.abline(h = 37.5);
-			panel.abline(h = 38.5);
-			panel.abline(h = 39.5);
-			panel.abline(h = 40.5);
-			panel.abline(h = 41.5);
-			panel.abline(h = 42.5);
-			panel.abline(h = 43.5);
-			panel.abline(h = 44.5);
-			panel.abline(h = 45.5);
-			panel.abline(h = 46.5);
-			panel.abline(h = 47.5);
-			panel.abline(h = 48.5);
-			panel.abline(h = 49.5);
-			panel.abline(h = 50.5);
-			panel.abline(h = 50.5);
-			panel.abline(h = 51.5);
-			panel.abline(h = 52.5);
-			panel.abline(h = 53.5);
-			panel.abline(h = 54.5);
-			panel.abline(h = 55.5);
-			panel.abline(h = 56.5);
-			panel.abline(h = 57.5);
-			panel.abline(h = 58.5);
-			panel.abline(h = 59.5);
-			panel.abline(h = 60.5);
-			panel.abline(h = 61.5);
-			panel.abline(h = 62.5);
-			panel.abline(h = 63.5);
-			panel.abline(h = 64.5);
-			panel.abline(h = 65.5);
-			panel.abline(h = 66.5);
-			panel.abline(h = 67.5);
-			panel.abline(h = 68.5);
-			panel.abline(h = 69.5);
-			panel.abline(h = 70.5);
-			panel.abline(h = 71.5);
-			panel.abline(h = 72.5);
-			panel.abline(h = 73.5);
-			panel.abline(h = 74.5);
-			panel.abline(h = 75.5);
-			panel.abline(h = 76.5);
-			panel.abline(h = 77.5);
-			panel.abline(h = 78.5);
-			panel.abline(h = 79.5);
-			panel.abline(h = 80.5);
-			panel.abline(h = 81.5);
-			panel.abline(h = 82.5);
-			panel.abline(h = 83.5);
-			panel.abline(h = 84.5);
-			panel.abline(h = 85.5);
-			panel.abline(h = 86.5);
-			panel.abline(h = 87.5);
-			panel.abline(h = 88.5);
-			panel.abline(h = 89.5);
-			panel.abline(h = 90.5);
-			panel.abline(h = 91.5);
-			panel.abline(h = 92.5);
-			panel.abline(h = 93.5);
-			panel.abline(h = 94.5);
-			panel.abline(h = 95.5);
-			panel.abline(h = 96.5);
-			panel.abline(h = 97.5);
-			panel.abline(h = 98.5);
-			panel.abline(h = 99.5);
-			panel.abline(h = 100.5);
-			panel.abline(h = 101.5);
-			panel.abline(h = 102.5);
-			panel.abline(h = 103.5);
-
-			#vertical lines
-            panel.abline(v = 1.5);
-            panel.abline(v = 2.5);
-            panel.abline(v = 3.5);
-            panel.abline(v = 4.5);
-            panel.abline(v = 5.5);
-            panel.abline(v = 6.5);
-            panel.abline(v = 7.5);
-            panel.abline(v = 8.5);
-            panel.abline(v = 9.5);
-            panel.abline(v = 10.5);
-            panel.abline(v = 11.5);
-            panel.abline(v = 12.5);
-            panel.abline(v = 13.5);
-            panel.abline(v = 14.5);
-            panel.abline(v = 15.5);
-            panel.abline(v = 16.5, col="yellow");
-            panel.abline(v = 17.5);
-            panel.abline(v = 18.5);
-            panel.abline(v = 19.5);
-            panel.abline(v = 20.5);
-            panel.abline(v = 21.5);
-            panel.abline(v = 22.5);
-            panel.abline(v = 23.5);
-            panel.abline(v = 24.5);
-            panel.abline(v = 25.5);
-            panel.abline(v = 26.5);
-            panel.abline(v = 27.5);
-            panel.abline(v = 28.5);
-            panel.abline(v = 29.5);
-            panel.abline(v = 30.5);
-            panel.abline(v = 31.5);
-            panel.abline(v = 32.5, col="yellow");
-            panel.abline(v = 33.5);
-            panel.abline(v = 34.5);
-            panel.abline(v = 35.5);
-            panel.abline(v = 36.5);
-            panel.abline(v = 37.5);
-            panel.abline(v = 38.5);
-            panel.abline(v = 39.5);
-            panel.abline(v = 40.5);
-            panel.abline(v = 41.5);
-            panel.abline(v = 42.5);
-            panel.abline(v = 43.5);
-            panel.abline(v = 44.5);
-            panel.abline(v = 45.5);
-            panel.abline(v = 46.5);
-            panel.abline(v = 47.5);
-          },
-          xlab="",
-          ylab="")
-```
-
-### K562
-
-####10kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
-
-features <- names(train)[-1]
-features <- features[grep("dist", features)]
-features <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "K562", 
-                                                    "dist", 
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", features)
-
-#None
-##OC
-enetcoefs_none_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_none_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_none_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
-
-#RUS
-##OC
-enetcoefs_RUS_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_RUS_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_RUS_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
-
-#ROS
-##OC
-enetcoefs_ROS_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_ROS_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_ROS_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
-
-#SMOTE
-##OC
-enetcoefs_SMOTE_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_SMOTE_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_SMOTE_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
-
-enetcoefslist <- list(enetcoefs_none_oc_10kb_K562, 
-                      enetcoefs_none_op_10kb_K562, 
-                      enetcoefs_none_dist_10kb_K562,
-                      enetcoefs_RUS_oc_10kb_K562, 
-                      enetcoefs_RUS_op_10kb_K562, 
-                      enetcoefs_RUS_dist_10kb_K562,
-                      enetcoefs_ROS_oc_10kb_K562, 
-                      enetcoefs_ROS_op_10kb_K562, 
-                      enetcoefs_ROS_dist_10kb_K562,
-                      enetcoefs_SMOTE_oc_10kb_K562, 
-                      enetcoefs_SMOTE_op_10kb_K562, 
-                      enetcoefs_SMOTE_dist_10kb_K562)
-
-enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
-
-featuremat_10kb_k562 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
-                                                                    "Predictor Type"=rep(c("OC",
-                                                                                         "OP", 
-                                                                                         "Distance"),4)))
-
-for(j in 1:length(enetcoefslist)){
-    featuremat_10kb_k562[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
-}
-
-#using lattice
-levelplot(t(featuremat_10kb_k562), 
-          colorkey=FALSE, 
-          scales=list(x=list(rot=45),
-                      alternating=3), 
-          col.regions=c("white", "red"),
-          aspect="fill",panel = function(...){
-            panel.levelplot(...)
-            panel.abline(v = 3.5);
-            panel.abline(v = 6.5);
-            panel.abline(v = 9.5);
-          },
-          xlab="",
-          ylab="")
-grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
-grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
-grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
-grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
-
-```
-
-####25kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
-
-features <- names(train)[-1]
-features <- features[grep("dist", features)]
-features <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "K562", 
-                                                    "dist", 
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", features)
-
-#None
-##OC
-enetcoefs_none_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_none_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_none_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
-
-#RUS
-##OC
-enetcoefs_RUS_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_RUS_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_RUS_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
-
-#ROS
-##OC
-enetcoefs_ROS_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_ROS_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_ROS_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
-
-#SMOTE
-##OC
-enetcoefs_SMOTE_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_SMOTE_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_SMOTE_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
-
-enetcoefslist <- list(enetcoefs_none_oc_25kb_K562, 
-                      enetcoefs_none_op_25kb_K562, 
-                      enetcoefs_none_dist_25kb_K562,
-                      enetcoefs_RUS_oc_25kb_K562, 
-                      enetcoefs_RUS_op_25kb_K562, 
-                      enetcoefs_RUS_dist_25kb_K562,
-                      enetcoefs_ROS_oc_25kb_K562, 
-                      enetcoefs_ROS_op_25kb_K562, 
-                      enetcoefs_ROS_dist_25kb_K562,
-                      enetcoefs_SMOTE_oc_25kb_K562, 
-                      enetcoefs_SMOTE_op_25kb_K562, 
-                      enetcoefs_SMOTE_dist_25kb_K562)
-
-enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
-
-featuremat_25kb_k562 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
-                                                                    "Predictor Type"=rep(c("OC",
-                                                                                         "OP", 
-                                                                                         "Distance"),4)))
-
-for(j in 1:length(enetcoefslist)){
-    featuremat_25kb_k562[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
-}
-
-#using lattice
-levelplot(t(featuremat_25kb_k562), 
-          colorkey=FALSE, 
-          scales=list(x=list(rot=45),
-                      alternating=3), 
-          col.regions=c("white", "red"),
-          aspect="fill",panel = function(...){
-            panel.levelplot(...)
-            panel.abline(v = 3.5);
-            panel.abline(v = 6.5);
-            panel.abline(v = 9.5);
-          },
-          xlab="",
-          ylab="")
-grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
-grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
-grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
-grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
-
-```
-
-####50kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
-
-features <- names(train)[-1]
-features <- features[grep("dist", features)]
-features <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "K562", 
-                                                    "dist", 
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", features)
-
-#None
-##OC
-enetcoefs_none_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_none_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_none_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
-
-#RUS
-##OC
-enetcoefs_RUS_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_RUS_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_RUS_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
-
-#ROS
-##OC
-enetcoefs_ROS_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_ROS_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_ROS_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
-
-#SMOTE
-##OC
-enetcoefs_SMOTE_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_SMOTE_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_SMOTE_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
-
-enetcoefslist <- list(enetcoefs_none_oc_50kb_K562, 
-                      enetcoefs_none_op_50kb_K562, 
-                      enetcoefs_none_dist_50kb_K562,
-                      enetcoefs_RUS_oc_50kb_K562, 
-                      enetcoefs_RUS_op_50kb_K562, 
-                      enetcoefs_RUS_dist_50kb_K562,
-                      enetcoefs_ROS_oc_50kb_K562, 
-                      enetcoefs_ROS_op_50kb_K562, 
-                      enetcoefs_ROS_dist_50kb_K562,
-                      enetcoefs_SMOTE_oc_50kb_K562, 
-                      enetcoefs_SMOTE_op_50kb_K562, 
-                      enetcoefs_SMOTE_dist_50kb_K562)
-
-enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
-
-featuremat_50kb_k562 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
-                                                                    "Predictor Type"=rep(c("OC",
-                                                                                         "OP", 
-                                                                                         "Distance"),4)))
-
-for(j in 1:length(enetcoefslist)){
-    featuremat_50kb_k562[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
-}
-
-#using lattice
-levelplot(t(featuremat_50kb_k562), 
-          colorkey=FALSE, 
-          scales=list(x=list(rot=45),
-                      alternating=3), 
-          col.regions=c("white", "red"),
-          aspect="fill",panel = function(...){
-            panel.levelplot(...)
-            panel.abline(v = 3.5);
-            panel.abline(v = 6.5);
-            panel.abline(v = 9.5);
-          },
-          xlab="",
-          ylab="")
-grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
-grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
-grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
-grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
-
-```
-
-####100kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
-
-features <- names(train)[-1]
-features <- features[grep("dist", features)]
-features <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "K562", 
-                                                    "dist", 
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", features)
-
-#None
-##OC
-enetcoefs_none_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_none_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_none_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/enetcoefs.rds")
-
-#RUS
-##OC
-enetcoefs_RUS_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_RUS_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_RUS_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/enetcoefs.rds")
-
-#ROS
-##OC
-enetcoefs_ROS_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_ROS_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_ROS_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/enetcoefs.rds")
-
-#SMOTE
-##OC
-enetcoefs_SMOTE_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/enetcoefs.rds")
-##OP
-enetcoefs_SMOTE_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/enetcoefs.rds")
-##Distance
-enetcoefs_SMOTE_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
-
-enetcoefslist <- list(enetcoefs_none_oc_100kb_K562, 
-                      enetcoefs_none_op_100kb_K562, 
-                      enetcoefs_none_dist_100kb_K562,
-                      enetcoefs_RUS_oc_100kb_K562, 
-                      enetcoefs_RUS_op_100kb_K562, 
-                      enetcoefs_RUS_dist_100kb_K562,
-                      enetcoefs_ROS_oc_100kb_K562, 
-                      enetcoefs_ROS_op_100kb_K562, 
-                      enetcoefs_ROS_dist_100kb_K562,
-                      enetcoefs_SMOTE_oc_100kb_K562, 
-                      enetcoefs_SMOTE_op_100kb_K562, 
-                      enetcoefs_SMOTE_dist_100kb_K562)
-
-enetcoefslist <- lapply(enetcoefslist, function(x){gsub(paste(c("_dist", "_perc", "_count"), collapse = "|"), "", x)})
-
-featuremat_100kb_k562 <- array(NA, dim=c(length(features),12), dimnames = list("Features"=features,
-                                                                    "Predictor Type"=rep(c("OC",
-                                                                                         "OP", 
-                                                                                         "Distance"),4)))
-
-for(j in 1:length(enetcoefslist)){
-    featuremat_100kb_k562[,j] <- ifelse(features %in% enetcoefslist[[j]], 1, 0)
-}
-
-#using lattice
-levelplot(t(featuremat_100kb_k562), 
-          colorkey=FALSE, 
-          scales=list(x=list(rot=45),
-                      alternating=3), 
-          col.regions=c("white", "red"),
-          aspect="fill",panel = function(...){
-            panel.levelplot(...)
-            panel.abline(v = 3.5);
-            panel.abline(v = 6.5);
-            panel.abline(v = 9.5);
-          },
-          xlab="",
-          ylab="")
-grid.text("None",x=unit(.27,"npc"),y=unit(.95, "npc"))
-grid.text("RUS",x=unit(.43,"npc"),y=unit(.95, "npc"))
-grid.text("ROS",x=unit(.59,"npc"),y=unit(.95, "npc"))
-grid.text("SMOTE",x=unit(.75,"npc"),y=unit(.95, "npc"))
-
-```
-
-####Combined
-
-```{r}
-all_featuremat_k562 <- cbind(featuremat_10kb_k562,
-                                featuremat_25kb_k562,
-                                featuremat_50kb_k562,
-                                featuremat_100kb_k562)
-all_featuremat_k562 <- all_featuremat_k562[,c(seq(1,48,3),
-                                                    seq(2,48,3),
-                                                    seq(3,48,3))]
-colnames(all_featuremat_k562) <- rep(c("None", "RUS", "ROS", "SMOTE"), 12)
-
-levelplot(t(all_featuremat_k562), 
-          colorkey=FALSE, 
-          scales=list(x=list(rot=45, cex=.5),
-                      #alternating=3,
-                      y=list(cex=.5)), 
-          col.regions=c("white", "red"),
-          aspect="fill",panel = function(...){
-            panel.levelplot(...)
-			#horizontal lines
-			panel.abline(h = 1.5);
-			panel.abline(h = 2.5);
-			panel.abline(h = 3.5);
-			panel.abline(h = 4.5);
-			panel.abline(h = 5.5);
-			panel.abline(h = 6.5);
-			panel.abline(h = 7.5);
-			panel.abline(h = 8.5);
-			panel.abline(h = 9.5);
-			panel.abline(h = 10.5);
-			panel.abline(h = 11.5);
-			panel.abline(h = 12.5);
-			panel.abline(h = 13.5);
-			panel.abline(h = 14.5);
-			panel.abline(h = 15.5);
-			panel.abline(h = 16.5);
-			panel.abline(h = 17.5);
-			panel.abline(h = 18.5);
-			panel.abline(h = 19.5);
-			panel.abline(h = 20.5);
-			panel.abline(h = 21.5);
-			panel.abline(h = 22.5);
-			panel.abline(h = 23.5);
-			panel.abline(h = 24.5);
-			panel.abline(h = 25.5);
-			panel.abline(h = 26.5);
-			panel.abline(h = 27.5);
-			panel.abline(h = 28.5);
-			panel.abline(h = 29.5);
-			panel.abline(h = 30.5);
-			panel.abline(h = 31.5);
-			panel.abline(h = 32.5);
-			panel.abline(h = 33.5);
-			panel.abline(h = 34.5);
-			panel.abline(h = 35.5);
-			panel.abline(h = 36.5);
-			panel.abline(h = 37.5);
-			panel.abline(h = 38.5);
-			panel.abline(h = 39.5);
-			panel.abline(h = 40.5);
-			panel.abline(h = 41.5);
-			panel.abline(h = 42.5);
-			panel.abline(h = 43.5);
-			panel.abline(h = 44.5);
-			panel.abline(h = 45.5);
-			panel.abline(h = 46.5);
-			panel.abline(h = 47.5);
-			panel.abline(h = 48.5);
-			panel.abline(h = 49.5);
-			panel.abline(h = 50.5);
-			panel.abline(h = 50.5);
-			panel.abline(h = 51.5);
-			panel.abline(h = 52.5);
-			panel.abline(h = 53.5);
-			panel.abline(h = 54.5);
-			panel.abline(h = 55.5);
-			panel.abline(h = 56.5);
-			panel.abline(h = 57.5);
-			panel.abline(h = 58.5);
-			panel.abline(h = 59.5);
-			panel.abline(h = 60.5);
-			panel.abline(h = 61.5);
-			panel.abline(h = 62.5);
-			panel.abline(h = 63.5);
-			panel.abline(h = 64.5);
-			panel.abline(h = 65.5);
-			panel.abline(h = 66.5);
-			panel.abline(h = 67.5);
-			panel.abline(h = 68.5);
-			panel.abline(h = 69.5);
-			panel.abline(h = 70.5);
-			panel.abline(h = 71.5);
-			panel.abline(h = 72.5);
-			panel.abline(h = 73.5);
-			panel.abline(h = 74.5);
-			panel.abline(h = 75.5);
-			panel.abline(h = 76.5);
-			panel.abline(h = 77.5);
-			panel.abline(h = 78.5);
-			panel.abline(h = 79.5);
-			panel.abline(h = 80.5);
-			panel.abline(h = 81.5);
-			panel.abline(h = 82.5);
-			panel.abline(h = 83.5);
-			panel.abline(h = 84.5);
-			panel.abline(h = 85.5);
-			panel.abline(h = 86.5);
-			panel.abline(h = 87.5);
-			panel.abline(h = 88.5);
-			panel.abline(h = 89.5);
-			panel.abline(h = 90.5);
-			panel.abline(h = 91.5);
-			panel.abline(h = 92.5);
-			panel.abline(h = 93.5);
-			panel.abline(h = 94.5);
-			panel.abline(h = 95.5);
-			panel.abline(h = 96.5);
-			panel.abline(h = 97.5);
-			panel.abline(h = 98.5);
-			panel.abline(h = 99.5);
-			panel.abline(h = 100.5);
-			panel.abline(h = 101.5);
-			panel.abline(h = 102.5);
-			panel.abline(h = 103.5);
-			panel.abline(h = 104.5);
-			panel.abline(h = 105.5);
-			panel.abline(h = 106.5);
-			panel.abline(h = 107.5);
-			panel.abline(h = 108.5);
-			panel.abline(h = 109.5);
-			panel.abline(h = 110.5);
-			panel.abline(h = 111.5);
-			panel.abline(h = 112.5);
-			panel.abline(h = 113.5);
-			panel.abline(h = 114.5);
-			panel.abline(h = 115.5);
-			panel.abline(h = 116.5);
-			panel.abline(h = 117.5);
-			panel.abline(h = 118.5);
-			panel.abline(h = 119.5);
-			panel.abline(h = 120.5);
-			panel.abline(h = 121.5);
-			panel.abline(h = 122.5);
-			panel.abline(h = 123.5);
-			panel.abline(h = 124.5);
-			panel.abline(h = 125.5);
-			panel.abline(h = 126.5);
-			panel.abline(h = 127.5);
-			panel.abline(h = 128.5);
-			panel.abline(h = 129.5);
-			panel.abline(h = 130.5);
-			panel.abline(h = 131.5);
-			panel.abline(h = 132.5);
-			panel.abline(h = 133.5);
-			panel.abline(h = 134.5);
-			panel.abline(h = 135.5);
-			panel.abline(h = 136.5);
-			panel.abline(h = 137.5);
-
-			#vertical lines
-            panel.abline(v = 1.5);
-            panel.abline(v = 2.5);
-            panel.abline(v = 3.5);
-            panel.abline(v = 4.5);
-            panel.abline(v = 5.5);
-            panel.abline(v = 6.5);
-            panel.abline(v = 7.5);
-            panel.abline(v = 8.5);
-            panel.abline(v = 9.5);
-            panel.abline(v = 10.5);
-            panel.abline(v = 11.5);
-            panel.abline(v = 12.5);
-            panel.abline(v = 13.5);
-            panel.abline(v = 14.5);
-            panel.abline(v = 15.5);
-            panel.abline(v = 16.5, col="yellow");
-            panel.abline(v = 17.5);
-            panel.abline(v = 18.5);
-            panel.abline(v = 19.5);
-            panel.abline(v = 20.5);
-            panel.abline(v = 21.5);
-            panel.abline(v = 22.5);
-            panel.abline(v = 23.5);
-            panel.abline(v = 24.5);
-            panel.abline(v = 25.5);
-            panel.abline(v = 26.5);
-            panel.abline(v = 27.5);
-            panel.abline(v = 28.5);
-            panel.abline(v = 29.5);
-            panel.abline(v = 30.5);
-            panel.abline(v = 31.5);
-            panel.abline(v = 32.5, col="yellow");
-            panel.abline(v = 33.5);
-            panel.abline(v = 34.5);
-            panel.abline(v = 35.5);
-            panel.abline(v = 36.5);
-            panel.abline(v = 37.5);
-            panel.abline(v = 38.5);
-            panel.abline(v = 39.5);
-            panel.abline(v = 40.5);
-            panel.abline(v = 41.5);
-            panel.abline(v = 42.5);
-            panel.abline(v = 43.5);
-            panel.abline(v = 44.5);
-            panel.abline(v = 45.5);
-            panel.abline(v = 46.5);
-            panel.abline(v = 47.5);
-          },
-          xlab="",
-          ylab="")
-```
-
-## Heatmaps using coefficients from elastic-net
-
-### G12878
-
-#### 10 kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
-
-features <- names(train)[-1]
-features <- features[grep("dist", features)]
-features <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist", 
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", features)
-
-#None
-##OC
-enetcoefs_none_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/enetModel.rds")
-enetcoefs_none_oc_10kb_gm12878 <- coef(enetcoefs_none_oc_10kb_gm12878$finalModel, s=enetcoefs_none_oc_10kb_gm12878$bestTune$lambda)
-##OP
-enetcoefs_none_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/enetModel.rds")
-enetcoefs_none_op_10kb_gm12878 <- coef(enetcoefs_none_op_10kb_gm12878$finalModel, s=enetcoefs_none_op_10kb_gm12878$bestTune$lambda)
-##Distance
-enetcoefs_none_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/enetModel.rds")
-enetcoefs_none_dist_10kb_gm12878 <- coef(enetcoefs_none_dist_10kb_gm12878$finalModel, s=enetcoefs_none_dist_10kb_gm12878$bestTune$lambda)
-
-#RUS
-##OC
-enetcoefs_RUS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/enetModel.rds")
-enetcoefs_RUS_oc_10kb_gm12878 <- coef(enetcoefs_RUS_oc_10kb_gm12878$finalModel, s=enetcoefs_RUS_oc_10kb_gm12878$bestTune$lambda)
-##OP
-enetcoefs_RUS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/enetModel.rds")
-enetcoefs_RUS_op_10kb_gm12878 <- coef(enetcoefs_RUS_op_10kb_gm12878$finalModel, s=enetcoefs_RUS_op_10kb_gm12878$bestTune$lambda)
-##Distance
-enetcoefs_RUS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
-enetcoefs_RUS_dist_10kb_gm12878 <- coef(enetcoefs_RUS_dist_10kb_gm12878$finalModel, s=enetcoefs_RUS_dist_10kb_gm12878$bestTune$lambda)
-
-#ROS
-##OC
-enetcoefs_ROS_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/enetModel.rds")
-enetcoefs_ROS_oc_10kb_gm12878 <- coef(enetcoefs_ROS_oc_10kb_gm12878$finalModel, s=enetcoefs_ROS_oc_10kb_gm12878$bestTune$lambda)
-##OP
-enetcoefs_ROS_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/enetModel.rds")
-enetcoefs_ROS_op_10kb_gm12878 <- coef(enetcoefs_ROS_op_10kb_gm12878$finalModel, s=enetcoefs_ROS_op_10kb_gm12878$bestTune$lambda)
-##Distance
-enetcoefs_ROS_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
-enetcoefs_ROS_dist_10kb_gm12878 <- coef(enetcoefs_ROS_dist_10kb_gm12878$finalModel, s=enetcoefs_ROS_dist_10kb_gm12878$bestTune$lambda)
-
-#SMOTE
-##OC
-enetcoefs_SMOTE_oc_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
-enetcoefs_SMOTE_oc_10kb_gm12878 <- coef(enetcoefs_SMOTE_oc_10kb_gm12878$finalModel, s=enetcoefs_SMOTE_oc_10kb_gm12878$bestTune$lambda)
-##OP
-enetcoefs_SMOTE_op_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
-enetcoefs_SMOTE_op_10kb_gm12878 <- coef(enetcoefs_SMOTE_op_10kb_gm12878$finalModel, s=enetcoefs_SMOTE_op_10kb_gm12878$bestTune$lambda)
-##Distance
-enetcoefs_SMOTE_dist_10kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
-enetcoefs_SMOTE_dist_10kb_gm12878 <- coef(enetcoefs_SMOTE_dist_10kb_gm12878$finalModel, s=enetcoefs_SMOTE_dist_10kb_gm12878$bestTune$lambda)
-
-enetcoefsmat <- cbind(enetcoefs_none_oc_10kb_gm12878[-1,1], 
-                      enetcoefs_ROS_oc_10kb_gm12878[-1,1],
-                      enetcoefs_RUS_oc_10kb_gm12878[-1,1], 
-                      enetcoefs_SMOTE_oc_10kb_gm12878[-1,1],
-
-                      enetcoefs_none_op_10kb_gm12878[-1,1], 
-                      enetcoefs_ROS_op_10kb_gm12878[-1,1],
-                      enetcoefs_RUS_op_10kb_gm12878[-1,1], 
-                      enetcoefs_SMOTE_op_10kb_gm12878[-1,1],
-
-                      enetcoefs_none_dist_10kb_gm12878[-1,1],
-                      enetcoefs_ROS_dist_10kb_gm12878[-1,1],
-                      enetcoefs_RUS_dist_10kb_gm12878[-1,1],
-                      enetcoefs_SMOTE_dist_10kb_gm12878[-1,1])
-
-enetcoefsmat[enetcoefsmat == 0] <- NA
-
-#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
-#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
-#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
-#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
-colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
-rownames(enetcoefsmat) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))
-
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
-
-```
-
-##### Overlap Counts
-
-```{r}
-heatmap.2(enetcoefsmat[,1:4],
-          #cellnote = cormat,  # same data set for cell labels
-          #main = "Correlation", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          dendrogram="row",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.75,
-          #labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          sepwidth=c(0.001,0.001),
-          sepcolor="black",
-          colsep=1:4,
-          rowsep=1:nrow(enetcoefsmat),
-          keysize = 1) 
-```
-
-#####Overlap Percents
-
-```{r}
-heatmap.2(enetcoefsmat[,5:8],
-          #cellnote = cormat,  # same data set for cell labels
-          #main = "Correlation", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          dendrogram="row",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.75,
-          #labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          sepwidth=c(0.001,0.001),
-          sepcolor="black",
-          colsep=1:4,
-          rowsep=1:nrow(enetcoefsmat),
-          keysize = 1) 
-```
-
-##### Distances
-
-```{r}
-heatmap.2(enetcoefsmat[,9:12],
-          #cellnote = cormat,  # same data set for cell labels
-          #main = "Correlation", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          dendrogram="row",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.75,
-          #labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          sepwidth=c(0.001,0.001),
-          sepcolor="black",
-          colsep=1:4,
-          rowsep=1:nrow(enetcoefsmat),
-          keysize = 1) 
-```
-
-#### 25kb
-
-```{r}
-train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
-
-features <- names(train)[-1]
-features <- features[grep("dist", features)]
-features <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist", 
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", features)
-
-#None
-##OC
-enetcoefs_none_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/enetModel.rds")
-enetcoefs_none_oc_25kb_gm12878 <- coef(enetcoefs_none_oc_25kb_gm12878$finalModel, s=enetcoefs_none_oc_25kb_gm12878$bestTune$lambda)
-##OP
-enetcoefs_none_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/enetModel.rds")
-enetcoefs_none_op_25kb_gm12878 <- coef(enetcoefs_none_op_25kb_gm12878$finalModel, s=enetcoefs_none_op_25kb_gm12878$bestTune$lambda)
-##Distance
-enetcoefs_none_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/enetModel.rds")
-enetcoefs_none_dist_25kb_gm12878 <- coef(enetcoefs_none_dist_25kb_gm12878$finalModel, s=enetcoefs_none_dist_25kb_gm12878$bestTune$lambda)
-
-#RUS
-##OC
-enetcoefs_RUS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/enetModel.rds")
-enetcoefs_RUS_oc_25kb_gm12878 <- coef(enetcoefs_RUS_oc_25kb_gm12878$finalModel, s=enetcoefs_RUS_oc_25kb_gm12878$bestTune$lambda)
-##OP
-enetcoefs_RUS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/enetModel.rds")
-enetcoefs_RUS_op_25kb_gm12878 <- coef(enetcoefs_RUS_op_25kb_gm12878$finalModel, s=enetcoefs_RUS_op_25kb_gm12878$bestTune$lambda)
-##Distance
-enetcoefs_RUS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
-enetcoefs_RUS_dist_25kb_gm12878 <- coef(enetcoefs_RUS_dist_25kb_gm12878$finalModel, s=enetcoefs_RUS_dist_25kb_gm12878$bestTune$lambda)
-
-#ROS
-##OC
-enetcoefs_ROS_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/enetModel.rds")
-enetcoefs_ROS_oc_25kb_gm12878 <- coef(enetcoefs_ROS_oc_25kb_gm12878$finalModel, s=enetcoefs_ROS_oc_25kb_gm12878$bestTune$lambda)
-##OP
-enetcoefs_ROS_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/enetModel.rds")
-enetcoefs_ROS_op_25kb_gm12878 <- coef(enetcoefs_ROS_op_25kb_gm12878$finalModel, s=enetcoefs_ROS_op_25kb_gm12878$bestTune$lambda)
-##Distance
-enetcoefs_ROS_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
-enetcoefs_ROS_dist_25kb_gm12878 <- coef(enetcoefs_ROS_dist_25kb_gm12878$finalModel, s=enetcoefs_ROS_dist_25kb_gm12878$bestTune$lambda)
-
-#SMOTE
-##OC
-enetcoefs_SMOTE_oc_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
-enetcoefs_SMOTE_oc_25kb_gm12878 <- coef(enetcoefs_SMOTE_oc_25kb_gm12878$finalModel, s=enetcoefs_SMOTE_oc_25kb_gm12878$bestTune$lambda)
-##OP
-enetcoefs_SMOTE_op_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
-enetcoefs_SMOTE_op_25kb_gm12878 <- coef(enetcoefs_SMOTE_op_25kb_gm12878$finalModel, s=enetcoefs_SMOTE_op_25kb_gm12878$bestTune$lambda)
-##Distance
-enetcoefs_SMOTE_dist_25kb_gm12878 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
-enetcoefs_SMOTE_dist_25kb_gm12878 <- coef(enetcoefs_SMOTE_dist_25kb_gm12878$finalModel, s=enetcoefs_SMOTE_dist_25kb_gm12878$bestTune$lambda)
-
-enetcoefsmat <- cbind(enetcoefs_none_oc_25kb_gm12878[-1,1], 
-                      enetcoefs_ROS_oc_25kb_gm12878[-1,1],
-                      enetcoefs_RUS_oc_25kb_gm12878[-1,1], 
-                      enetcoefs_SMOTE_oc_25kb_gm12878[-1,1],
-
-                      enetcoefs_none_op_25kb_gm12878[-1,1], 
-                      enetcoefs_ROS_op_25kb_gm12878[-1,1],
-                      enetcoefs_RUS_op_25kb_gm12878[-1,1], 
-                      enetcoefs_SMOTE_op_25kb_gm12878[-1,1],
-
-                      enetcoefs_none_dist_25kb_gm12878[-1,1],
-                      enetcoefs_ROS_dist_25kb_gm12878[-1,1],
-                      enetcoefs_RUS_dist_25kb_gm12878[-1,1],
-                      enetcoefs_SMOTE_dist_25kb_gm12878[-1,1])
-
-enetcoefsmat[enetcoefsmat == 0] <- NA
-
-#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
-#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
-#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
-#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
-colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
-rownames(enetcoefsmat) <- gsub(paste(c("`", 
-                                                    "_",
-                                                    "-",
-                                                    "Gm12878", 
-                                                    "dist",
-                                                    "count",
-                                                    "perc",
-                                                    "Haib", 
-                                                    "Sydh",
-                                                    "Uta",
-                                                    "Uw",
-                                                    "Broad",
-                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))
-
-my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
-
-```
-
-##### Overlap Counts
-
-```{r}
-heatmap.2(enetcoefsmat[,1:4],
-          #cellnote = cormat,  # same data set for cell labels
-          #main = "Correlation", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          dendrogram="row",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.75,
-          #labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          sepwidth=c(0.001,0.001),
-          sepcolor="black",
-          colsep=1:4,
-          rowsep=1:nrow(enetcoefsmat),
-          keysize = 1) 
-```
-
-#####Overlap Percents
-
-```{r}
-heatmap.2(enetcoefsmat[,5:8],
-          #cellnote = cormat,  # same data set for cell labels
-          #main = "Correlation", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins =c(5,5),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          dendrogram="row",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.75,
-          #labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          sepwidth=c(0.001,0.001),
-          sepcolor="black",
-          colsep=1:4,
-          rowsep=1:nrow(enetcoefsmat),
-          keysize = 1) 
-```
-
-##### Distances
-
-```{r}
-my_palette2 <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(10))
-my_palette2 <- c(my_palette2[1:20], "gray", my_palette2[21:39])
-my_palette2 <- colorRampPalette(c("blue", "white", "red"))(n=100)
-
-color.palette  <- c(colorRampPalette(c("blue", "gray", "red"))(n=99)[1:49], 
-                    "#F8F8F8", 
-                    colorRampPalette(c("yellow", "orange", "red"))(n=99)[50:99])
-enetcoefsmat2 <- enetcoefsmat
-enetcoefsmat2[,9:12][is.na(enetcoefsmat2[,9:12])] <- 0
-
-col_breaks = c(seq(-.999,-.900,length=2),
-           seq(-.899,-.800,length=2),
-           seq(-.799,-.700,length=2),
-           seq(-.699,-.600,length=2),
-           seq(-.599,-.500,length=2),
-           seq(-.499,-.400,length=2),
-           seq(-.399,-.300,length=2),
-           seq(-.299,-.200,length=2),
-           seq(-.199,-.100,length=2),
-           seq(-.099,-.001,length=2),
-           seq(0,0.1,length=1),  # for gray
-           seq(.001,.099,length=2),
-           seq(.100,.199,length=2),
-           seq(.200,.299,length=2),
-           seq(.300,.399,length=2),
-           seq(.400,.499,length=2),
-           seq(.500,.599,length=2),
-           seq(.600,.699,length=2),
-           seq(.700,.799,length=2),
-           seq(.800,.899,length=2),
-           seq(.900,.999,length=2))
-
-col_breaks = c(seq(-1,-.7,length=20),
-           seq(-.699,-.001,length=20),
-           seq(0,0.001,length=1),  # for white
-           seq(.001,.699,length=20),
-           seq(.7,1,length=20))
-
-heatmap.2(enetcoefsmat2[,9:12],
-          #cellnote = cormat,  # same data set for cell labels
-          #main = "Correlation", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins =c(5,5),     # widens margins around plot
-          col=my_palette2,       # use on color palette defined earlier
-          #na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          dendrogram="row",     # only draw a row dendrogram
-          cexRow=0.5,
-          cexCol=0.75,
-          #labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          sepwidth=c(0.001,0.001),
-          sepcolor="black",
-          colsep=1:4,
-          rowsep=1:nrow(enetcoefsmat),
-          keysize = 1) 
-```

### 2019-05-16 Scripts/proportion_of_importance_per_annotation.Rmd
added results scripts

---
title: "proportion_of_importance_per_annotation"
author: "Spiro Stilianoudakis"
date: "May 16, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

#GM12878

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/all_annotations/gm12878")
annots <- gsub(paste(c("Gm12878-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", annots)
annots <- annots[!duplicated(annots)]

chromstates <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
chromstates <- chromstates[grep("Gm12878", chromstates)]
chromstates <- gsub(paste0(c("Gm12878-", ".bed"), collapse = "|"),"",chromstates)

histones <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
histones <- histones[grep("Gm12878", histones)]
histones <- gsub(paste0(c("Gm12878-", ".bed"), collapse = "|"),"",histones)

tfbs <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878")
tfbs <- gsub(paste0(c("Gm12878-", ".bed", "-Haib", "-Sydh", "-Broad", "-Uw", "-Uta", "-Chicago"), collapse = "|"),"", tfbs)
tfbs <- tfbs[!duplicated(tfbs)]

```

##10kb

```{r}
varimp_gm12878_10kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_gm12878_10kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_gm12878_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_gm12878_10kb <- data.frame(Feature = rownames(varimp_gm12878_10kb),
                                  aveimp10kb = rowMeans(varimp_gm12878_10kb, na.rm = TRUE),
                                  sdimp10kb = apply(varimp_gm12878_10kb,1, sd, na.rm = TRUE))
rownames(varimp_gm12878_10kb) <- NULL
```

##25kb

```{r}
varimp_gm12878_25kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_gm12878_25kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_gm12878_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_gm12878_25kb <- data.frame(Feature = rownames(varimp_gm12878_25kb),
                                  aveimp25kb = rowMeans(varimp_gm12878_25kb, na.rm = TRUE),
                                  sdimp25kb = apply(varimp_gm12878_25kb,1, sd, na.rm = TRUE))
rownames(varimp_gm12878_25kb) <- NULL
```

##50kb

```{r}
varimp_gm12878_50kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_gm12878_50kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_gm12878_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_gm12878_50kb <- data.frame(Feature = rownames(varimp_gm12878_50kb),
                                  aveimp50kb = rowMeans(varimp_gm12878_50kb, na.rm = TRUE),
                                  sdimp50kb = apply(varimp_gm12878_50kb,1, sd, na.rm = TRUE))
rownames(varimp_gm12878_50kb) <- NULL
```

##100kb

```{r}
varimp_gm12878_100kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_gm12878_100kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_gm12878_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_gm12878_100kb <- data.frame(Feature = rownames(varimp_gm12878_100kb),
                                  aveimp100kb = rowMeans(varimp_gm12878_100kb, na.rm = TRUE),
                                  sdimp100kb = apply(varimp_gm12878_100kb,1, sd, na.rm = TRUE))
rownames(varimp_gm12878_100kb) <- NULL
```

##Plots

```{r}
all_propimp_gm12878 <- data.frame(Importance=c(varimp_gm12878_10kb$aveimp10kb,
                                                   varimp_gm12878_25kb$aveimp25kb,
                                                   varimp_gm12878_50kb$aveimp50kb,
                                                   varimp_gm12878_100kb$aveimp100kb),
                                  Feature=c(as.character(varimp_gm12878_10kb$Feature),
                                            as.character(varimp_gm12878_10kb$Feature),
                                            as.character(varimp_gm12878_10kb$Feature),
                                            as.character(varimp_gm12878_10kb$Feature)),
                                  Resolution=c(rep("10 kb", 107),
                                               rep("25 kb", 107),
                                               rep("50 kb", 107),
                                               rep("100 kb", 107))
                                  )

all_propimp_gm12878$Annotation <- ifelse(all_propimp_gm12878$Feature %in% chromstates, "CSS",
                                         ifelse(all_propimp_gm12878$Feature %in% histones, "HM", "TFBS"))

all_propimp_gm12878_summ <- data.frame(Prop.VI = c(
                                                   #10kb
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb" & all_propimp_gm12878$Annotation=="CSS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb" & all_propimp_gm12878$Annotation=="HM")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb" & all_propimp_gm12878$Annotation=="TFBS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb")]),

                                                   #25kb
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="25 kb" & all_propimp_gm12878$Annotation=="CSS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="25 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="25 kb" & all_propimp_gm12878$Annotation=="HM")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="25 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="25 kb" & all_propimp_gm12878$Annotation=="TFBS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="25 kb")]),

                                                   #50kb
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="50 kb" & all_propimp_gm12878$Annotation=="CSS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="50 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="50 kb" & all_propimp_gm12878$Annotation=="HM")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="50 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="50 kb" & all_propimp_gm12878$Annotation=="TFBS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="50 kb")]),

                                                   #100kb
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb" & all_propimp_gm12878$Annotation=="CSS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb" & all_propimp_gm12878$Annotation=="HM")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb" & all_propimp_gm12878$Annotation=="TFBS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb")])),
                                       Resolution = c(rep("10 kb", 3),
                                                      rep("25 kb", 3),
                                                      rep("50 kb", 3),
                                                      rep("100 kb", 3)),
                                       Annotation = rep(c("CSS","HM","TFBS"), 4))

all_propimp_gm12878_summ$Resolution <- factor(all_propimp_gm12878_summ$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))

ggplot(all_propimp_gm12878_summ, aes(fill=Annotation, y=Prop.VI, x=Resolution)) + 
  geom_bar( stat="identity", position="fill") +
  xlab("Resolution") +
  ylab("Proportion of Importance") +
  scale_fill_discrete(name="Annotation\nGroup")+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

```

#K562

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/all_annotations/k562")
annots <- gsub(paste(c("K562-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", annots)
annots <- annots[!duplicated(annots)]

chromstates <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
chromstates <- chromstates[grep("K562", chromstates)]
chromstates <- gsub(paste0(c("K562-", ".bed"), collapse = "|"),"",chromstates)

histones <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
histones <- histones[grep("K562", histones)]
histones <- gsub(paste0(c("K562-", ".bed"), collapse = "|"),"",histones)

tfbs <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/K562")
tfbs <- gsub(paste0(c("K562-", ".bed", "-Haib", "-Sydh", "-Broad", "-Uw", "-Uta", "-Chicago"), collapse = "|"),"", tfbs)
tfbs <- tfbs[!duplicated(tfbs)]

```

##10kb

```{r}
varimp_K562_10kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_K562_10kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_K562_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_K562_10kb <- data.frame(Feature = rownames(varimp_K562_10kb),
                                  aveimp10kb = rowMeans(varimp_K562_10kb, na.rm = TRUE),
                                  sdimp10kb = apply(varimp_K562_10kb,1, sd, na.rm = TRUE))
rownames(varimp_K562_10kb) <- NULL
```

##25kb

```{r}
varimp_K562_25kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_K562_25kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_K562_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_K562_25kb <- data.frame(Feature = rownames(varimp_K562_25kb),
                                  aveimp25kb = rowMeans(varimp_K562_25kb, na.rm = TRUE),
                                  sdimp25kb = apply(varimp_K562_25kb,1, sd, na.rm = TRUE))
rownames(varimp_K562_25kb) <- NULL
```

##50kb

```{r}
varimp_K562_50kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_K562_50kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_K562_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_K562_50kb <- data.frame(Feature = rownames(varimp_K562_50kb),
                                  aveimp50kb = rowMeans(varimp_K562_50kb, na.rm = TRUE),
                                  sdimp50kb = apply(varimp_K562_50kb,1, sd, na.rm = TRUE))
rownames(varimp_K562_50kb) <- NULL
```

##100kb

```{r}
varimp_K562_100kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_K562_100kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_K562_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_K562_100kb <- data.frame(Feature = rownames(varimp_K562_100kb),
                                  aveimp100kb = rowMeans(varimp_K562_100kb, na.rm = TRUE),
                                  sdimp100kb = apply(varimp_K562_100kb,1, sd, na.rm = TRUE))
rownames(varimp_K562_100kb) <- NULL
```

##Plots

```{r}
all_propimp_K562 <- data.frame(Importance=c(varimp_K562_10kb$aveimp10kb,
                                                   varimp_K562_25kb$aveimp25kb,
                                                   varimp_K562_50kb$aveimp50kb,
                                                   varimp_K562_100kb$aveimp100kb),
                                  Feature=c(as.character(varimp_K562_10kb$Feature),
                                            as.character(varimp_K562_10kb$Feature),
                                            as.character(varimp_K562_10kb$Feature),
                                            as.character(varimp_K562_10kb$Feature)),
                                  Resolution=c(rep("10 kb", 141),
                                               rep("25 kb", 141),
                                               rep("50 kb", 141),
                                               rep("100 kb", 141))
                                  )

all_propimp_K562$Annotation <- ifelse(all_propimp_K562$Feature %in% chromstates, "CSS",
                                         ifelse(all_propimp_K562$Feature %in% histones, "HM", "TFBS"))

all_propimp_K562_summ <- data.frame(Prop.VI = c(
                                                   #10kb
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb" & all_propimp_K562$Annotation=="CSS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb" & all_propimp_K562$Annotation=="HM")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb" & all_propimp_K562$Annotation=="TFBS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb")]),

                                                   #25kb
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="25 kb" & all_propimp_K562$Annotation=="CSS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="25 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="25 kb" & all_propimp_K562$Annotation=="HM")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="25 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="25 kb" & all_propimp_K562$Annotation=="TFBS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="25 kb")]),

                                                   #50kb
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="50 kb" & all_propimp_K562$Annotation=="CSS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="50 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="50 kb" & all_propimp_K562$Annotation=="HM")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="50 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="50 kb" & all_propimp_K562$Annotation=="TFBS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="50 kb")]),

                                                   #100kb
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb" & all_propimp_K562$Annotation=="CSS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb" & all_propimp_K562$Annotation=="HM")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb" & all_propimp_K562$Annotation=="TFBS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb")])),
                                       Resolution = c(rep("10 kb", 3),
                                                      rep("25 kb", 3),
                                                      rep("50 kb", 3),
                                                      rep("100 kb", 3)),
                                       Annotation = rep(c("CSS","HM","TFBS"), 4))

all_propimp_K562_summ$Resolution <- factor(all_propimp_K562_summ$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))

ggplot(all_propimp_K562_summ, aes(fill=Annotation, y=Prop.VI, x=Resolution)) + 
  geom_bar( stat="identity", position="fill") +
  xlab("Resolution") +
  ylab("Proportion of Importance") +
  scale_fill_discrete(name="Annotation\nGroup")+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

```

### 2019-05-16 Manuscript/manuscript_structured.Rmd
manuscript and abstract edits

@@
 Several epigenomic marks, such as CTCF and the members of Cohesin complex, were found to be enriched at TAD boundaries, suggesting a strong epigenetic component in TAD formation.
-Several methods for predicting TAD boundaries using epigenomic data overlooked key characteristics of genome annotation data, such as indirect associations between an annotation and a boundary.
+Several methods for predicting TAD boundaries using epigenomic data have overlooked key characteristics of genome annotation data, such as indirect associations between an annotation and a boundary.
 Furthermore, the number of regions containing TAD boundaries is typically much smaller than the rest of the genome, creating a class imbalance problem.
+This can be further exacerbated by the particular resolution that TADs are called from.
+Higher resolution will typically result in more sparce data, but will likely capture the nuances between boundaries and annotation that could be missed at lower resolutions.
 

### 2019-05-16 Manuscript/manuscript_structured.Rmd
edits to abstract

@@
 Lastly, the most predictive annotations in the best performing models were found to be consistent across both cell line and resolution.
-They included well-known marks of TAD boundaries such as CTCF, SMC3, RAD21, and ZNF143, as well as lesser known transcription factors including P300 and NFKB.
+They included well-known marks of TAD boundaries such as CTCF, SMC3, RAD21, and ZNF143, as well as lesser known transcription factors including RUNX3, ELF1, and the Myc-associated zinc finger protein.
 

### 2019-05-17 Manuscript/manuscript.Rmd
manuscript and abstract edits
Trying to read

@@
 To investigate the relationship between functional genomic annotations and the development of TAD boundaries, we devised 3 different predictor-types that composed the feature space of downstream random forest classification models.
-These predictor-type specific annotations represented the data matrix, **X** = {$X_{1}$, $X_{2}$, ..., $X_{p}$}, where *p* is the complete set of functional annotations.
+These predictor-type specific annotations represented the data matrix, **X** = {$X_{1}$, $X_{2}$, ..., $X_{p}$}, where $p$ is the complete set of functional annotations.
 Overlap counts was the least granular predictor-type considered, simply defined by the number of annotation-specific regions located within each genomic bin (Figure 2A).
@@
 We then developed an ensemble framework to systematically compare and establish the best set of data level characteristics for predicting TAD boundaries using random forest classifiers built on cell line specific functional genomic annotations (Figure 3).
-TAD boundaries were called using the arrowhead algorithm [@durand2016juicebox] from replicate Hi-C data for 2 cell lines *L* = {*GM12878*, *K562*}, at four different resolutions *R* = {*10 kb*, *25 kb*, *50 kb*, *100 kb*}.
-For each classifier, we considered 3 separate predictor types as the feature space including *P* = {*OC*, *OP*, *Distance*}.
-To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including *B* = {*None*, *RUS*, *ROS*, *SMOTE*}.
-Each combination of the above parameters was implemented on chromosome specific sections of the linear genome, and thus, was repeated repeated 21 times (number of autosomal chromosomes, excluding chromosome 9), *C* = {*1*, *2*, ..., *22*}.
-A system produced from the ensemble framework was defined as: *S* = {*c*, *r*, *p*, *b*}, where *l* $\in$ *L*, *r* $\in$ *R*, *p* $\in$ *P*, *b* $\in$ *B*, and *c* $\in$ *C*.
-Letting *|X|* denote the cardinality of each set, we evaluated *|L|* $\times$ *|R|* $\times$ *|P|* $\times$ *|B|* different ensemble systems, totaling 2016 (= 2 $\times$ 4 $\times$ 3 $\times$ 4 $\times$ 21) separate models.
+TAD boundaries were called using the Arrowhead algorithm [@durand2016juicebox] from replicate Hi-C data for 2 cell lines $L = \{GM12878, K562\}$, at four different resolutions $R = \{10 kb, 25 kb, 50 kb, 100 kb\}$.
+For each classifier, we considered 3 separate predictor types as the feature space including $P = \{OC, OP, Distance\}$.
+To assess the severity of class imbalance, four re-sampling techniques were implemented prior to modelling, including $B = \{None, RUS, ROS, SMOTE\}$.
+Each combination of the above parameters was implemented on chromosome specific sections of the linear genome, and thus, was repeated repeated 21 times (number of autosomal chromosomes, excluding chromosome 9 [???
+In Methods, not here, you should explain why]), $C = \{1, 2, ..., 22\}$.
+A system produced from the ensemble framework was defined as: $S = \{c, r, p, b\}$, where $l \in L$, $r \in R$, $p \in P$, $b \in B$, and $c \in C$.
+Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling 2016 ($2 \times 4 \times 3 \times 4 \times 21$) separate models.
 Performances were then aggregated across each of the 21 chromosomes (omitting chromosome 9; see Methods).
 We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.
+[???
+Currently, Methods and the results are redundant.
+Look how others present their models in the results section, and how methods section is structured in such cases.
+Specifically, some key definitions, like OC, OP, Distance should be solidly introduced in the results section, while log2 status of distance and supplementary figure 1 description are for methods]
 
@@
 Such low imbalance ratios indicated a wide disparity between the number of genomic bins that overlaped with a flanked TAD boundary and the much larger number that did not.
-The K562 cell line was found to exhibit similar profiles for the above quantities (Supplementary Tables 3-4)
+The K562 cell line was found to exhibit similar profiles for the above quantities (Supplementary Tables 3-4) [???
+Very bad and boring.
+You should tell the STORY, not the report.
+E.g., "Expectedly, the average number of genomic bins, TADs, and TAD boundaries increased with the increased resolution of Hi-C data (Table 1).
+However, the imbalance ratio, defined as ..., remained severe (~XXX) at all resolutions (Table 1).
+In summary, the problem of class imbalance exists at all resolutions of Hi-C data."]
 
@@
 
-Using the jaccard index, we were able to determine which group-specific annotations were enriched together on the linear genome.
+Using the Jaccard [???
+Spell capital everywhere] index, we were able to determine which group-specific annotations were enriched together on the linear genome.
 As could be expected, for GM12878, the class of 14 annotations segmenting the chromation into different states exhibited very low pairwise correlations, with a jaccard index range of (0-0.001) (Table 1).
-However, specific sets of pairwise histone modifications and transcription factor binding sites (TFBS) were found to be highly enriched.
+[???
+Wrong table?] However, specific sets of pairwise histone modifications and transcription factor binding sites (TFBS) were found to be highly enriched.
 The range of jaccard indices for the 10 histone modifications was found to be (0.022-0.539).
@@
 accuracy, sensitivity and specificity, and AUC) were less sensitive for models built on imbalanced data, regardless of cell line, resolution, or predictor-type (Supplementary Tables 6-7).
+[???
+Need to know why PRCs give different results.]
 
@@
 ## MODELS IMPLEMENTED ON TRANSCRIPTION FACTOR BINDING SITES, USING OPTIMAL PARAMETERS, OUTPERFORM OTHER ANNOTATION-SPECIFIC MODELS
+
+After determining the optimal set of data level characteristics necessary for predicting TAD boundaries, we then aimed to identify the set of functional genomic elements that were most influential in predicting said boundaries.
 

### 2019-05-17 Manuscript/manuscript_structured.Rmd
abstract edits
Abstract complete

--- 2019-05-07 Manuscript/manuscript_structured.Rmd
@@
 ---
-title: "Untitled"
-output: html_document
+title: Computational Prediction of 3D Genomic Domains using 1D Genome Annotations
+  in Class Imbalance Settings
+output:
+  word_document: default
+  pdf_document:
+    fig_caption: no
+fontsize: 11pt
 ---
+
+Spiro Stilianoudakis^1,2^ (stilianoudasc@mymail.vcu.edu), Kellen G. Cresswell^1^ (cresswellkg@vcu.edu), Mikhail G. Dozmorov^1,2\*^ (mikhail.dozmorov@vcuhealth.org)
+
+^1^ Dept. of Biostatistics, Virginia Commonwealth University, Richmond, VA, 23298, USA  
+^2^ Equal contribution  
+^\*^ To whom correspondence should be addressed: Virginia Commonwealth University, Richmond, VA, 23298, 804-827-2055, mikhail.dozmorov@vcuhealth.org
 
@@
 
-**Background.** Topologically Associated Domains (TADs) represent fundamental building blocks of the 3D genome organization and regulation.
-Several epigenomic marks, such as CTCF and the members of Cohesin complex, were found to be enriched at TAD boundaries, suggesting a strong epigenetic component in TAD formation.
-Several methods for predicting TAD boundaries using epigenomic data overlooked key characteristics of genome annotation data, such as indirect associations between an annotation and a boundary.
-Furthermore, the number of regions containing TAD boundaries is typically much smaller than the rest of the genome, creating a class imbalance problem.
+**Background.** Topologically Associated Domains (TADs) represent fundamental building blocks of the three-dimensional (3D) genome organization and regulation.
+Several epigenetic marks, such as CTCF, are highly enriched at TAD boundaries, suggesting a strong epigenetic component of TAD boundary formation.
+Several methods have been developed to leverage the growing amount of (epi)genomic annotation data for predicting TAD boundaries; however, they overlooked key characteristics of the data, such as spatial associations between a genomic annotation and a boundary.
+Furthermore, the number of regions containing TAD boundaries is much smaller than the rest of the genome, creating a class imbalance problem.
 
-**Methods.** To address this, we proposed a novel ensemble framework in order to systematically compare the performances of random forest classifiers implemented on combinations of different Hi-C contact matrix resolutions, feature engineering strategies, and re-sampling techniques.
+**Methods.** To investigate the problem of spatial genomic relationships and class imbalance problem, we developed an ensemble framework for optimizing prediction of TAD boundaries.
+We utilized several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) coupled with various metrics for classifier performance evaluation (Area Under Receiver Operating Characteristics (AUCROC) curve, Precision-Recall curve (AUPRC), F1, Matthew Correlation Coefficient (MCC), among others) to select the best predictive model in class imbalance settings.
 
-**Results.** Using the GM12878 and K562 cell lines, we show that models built on SMOTE (Synthetic Minority Over-sampling TEchnique) re-sampled data out performed models built simply on random under- and over-sampled data, across all resolutions.
-Additionally, our results indicated that distances between annotations and TAD boundaries were more informative than other predictor-types used to build the feature space of models.
-We also observed that performances tended to degrade as data resolution decreased.
-Lastly, the most predictive annotations in the best performing models were found to be consistent across both cell line and resolution.
-They included well-known marks of TAD boundaries such as CTCF, SMC3, RAD21, and ZNF143, as well as lesser known transcription factors including P300 and NFKB.
+**Results.** Using different feature engineering and resampling strategies, coupled with elastic net-based feature selection, we systematically compared the performance of models predicting the location of TAD boundaries (Gm12878 and K562 Hi-C data at 10kb to 100kb resolutions).
+Precision-Recall curves were found to be best suited for evaluating model performance in class imbalance settings.
+Random undersampling and SMOTE-resampled data performed best for optimal parameter selection.
+Transcription Factor Binding Sites (TFBSs) were best type of genomic annotations for predicting TAD boundaries than histone modifications and chromatin states; we identified well-known CTCF, SMC3, RAD21, and several novel TFBSs as best predictors of TAD boundaries.
+Importantly, spatial relationships (distance between TAD boundaries and genomic annotations) were best predictors of TAD boundaries as compared with commonly used overlap counts or percent overlap measures.
 
-**Conclusions.** The experiments derived from our ensemble framework provide a useful guide toward the exploration of chromatin organization, while highlighting the impact of both class imbalance and feature engineering in TAD boundary prediction.
-Our framework provides insight into the best set of parameters necessary for optimal performance.
+**Conclusions.** Our results outline strategies for predictive modeling of 3D genomic domains using 1D genome annotation data.
+The accurate modeling of TAD boundaries will improve our understanding of how epigenetics shapes the 3D structure of the genome.
 
+<!--
 # Introduction
@@
 ### Consider distance
+-->

### 2019-05-17 submission.1/abstract.Rmd
Submitted abstract

--- 2019-05-17 Manuscript/manuscript_structured.Rmd
@@
 The accurate modeling of TAD boundaries will improve our understanding of how epigenetics shapes the 3D structure of the genome.
-
-<!--
-# Introduction
-
-## Importance
-
-## Problems and limitations
-
-### Hi-C data issues for TAD boundary identification
-
-Although Hi-C data allows for identification of TADs genome-wide, it has limitations.
-First, Hi-C requires a large amount of sequencing (one Hi-C experiment requires >20X sequencing of a typical RNA-seq experiment).
-Consequently, the cost of obtaining Hi-C data remains high and the data availability for various cell lines and tissues remain highly uneven.
-Second, resolution of Hi-C data, or the size of interacting genomic regions, remains relatively coarse (on the order of kilobases) as compared with transcription factor binding motifs (tenths bases) or ChIP-seq peaks (hundredths bases), and inconsistent across cell lines and tissues.
-Third, Hi-C data suffers from technology- and DNA-driven biases, sparsity (high proportion of missing values), and limited sequencing depth, adding to inconsistency to cell- and tissue type-specific Hi-C data availability.
-These factors hinder the consistent TAD boundary identification across tissues and cell types.
-
-### Genome annotation data opportunities
-
-In contrast, 1D genome annotation tracks assembled by the ENCODE and Roadmap consortia provide a fine-grained look at the genome in various tissues and cell types.
-Although the original genome annotation data was highly uneven (rich annotations available for select cell types while remaining sparse for others), recent genome annotation imputation methods fill the cell type-specific sparsity of genome annotations.
-Consequently, using existing and imputed genome annotations for TAD boundary predictions represent a viable way to identify TAD boundaries in any cell or tissue type.
-
-### Class imbalance
-
-### Prediction types
-
-## Previous works on solving problems
-
-### Resampling approaches
-
-### Models
-
-### Evaluation metrics
-
-## Pitfalls of previous works
-
-### Distance not considered
-
-## Our work on solving problems
-
-### Consider distance
--->

### 2019-05-18 Manuscript/manuscript.Rmd
manuscript edits

@@
 To enable us to build a model that suitably discriminates between regions on the linear genome that are near TAD boundaries and regions that are not, we created a cell line- and resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary (Y=1), or not (Y=0).
-The unit width of each bin on the linear genome corresponded to the resolution of the contact matrix that domains were called on.
+The unit width of each bin on the linear genome corresponded to the resolution of the contact matrix on which domains were called.
 Moreover, to account for uncertainty in boundary location, TAD boundaries were flanked on either side by the same unit length as the genomic bins.
@@
 Lastly, distances, the most granular predictor-type, described the spatial relationship between the center of each genomic bin to the center of the nearest annotation-specific region (Figure 2C).
-When measured in basepairs, distances were found to be highly skewed across all resolutions, for both the GM12878 and K562 cell lines (Supplementary Figures 1-2 A-D).
-As a normalization procedure, we performed a $log_{2}$ transformation, which resulted in much more gaussian-shaped distance densities (Supplementary Figures 1-2 E-H).
+<!--When measured in basepairs, distances were found to be highly skewed across all resolutions, for both the GM12878 and K562 cell lines (Supplementary Figures 1-2 A-D).--> As a normalization procedure, we performed a $log_{2}$ transformation on the distances prior to modelling (See Methods Section).
 
@@
 [???probably better to report medians here]
-For GM12878, the average number of genomic bins created across chromosomes was 12,214.1, 4,892.7, 2,450.9, and 1,227.5 for each resolution respectively (Table 1).
-Likewise, the average number chromosome specific TADs called on each resolution was found to be 375.0, 228.4, 115.1, and 50.6.
-These TADs resulted in an average of 1254.6, 714.0, 364.4, and 165.3 chromosome specific boundaries across each resolution.
-Each of these quantities was find to have a significantly large ICC, indicating that the number of genomic bins, TADs called, and corresponding unique boundaries were highly correlated between the different resolutions (Table 2).
-On the other hand, we found that the chromosome specific imbalance ratios remained consistenly severe across all resolution, with averages of 0.12, 0.17, 0.17, and 0.15 for each resolution respectively (ICC=0.114; p=0.109).
-Such low imbalance ratios indicated a wide disparity between the number of genomic bins that overlaped with a flanked TAD boundary and the much larger number that did not.
-The K562 cell line was found to exhibit similar profiles for the above quantities (Supplementary Tables 3-4) [???
+Expectedly, the average number of genomic bins, TADs called, and TAD boundaries increased with the increased resolution of cell-line specific Hi-C data (Table 1; Supplementary Tables 3).
+The correlation of each cell-line specific quantity with resolution was found to be significant, as evidenced by large intraclass correllation coefficients (ICC) (Table 2; Supplementary Tables 4).
+However, the class imbalance problem was found to be much more consistant across resolutions in both cell lines.
+Likewise, this relationship was not significantly correlated with resoltuion for either cell line, indicating that there exists a severe disparity between classes at all resolutions of Hi-C data.
+
+[???
 Very bad and boring.
@@
 However, the imbalance ratio, defined as ..., remained severe (~XXX) at all resolutions (Table 1).
-In summary, the problem of class imbalance exists at all resolutions of Hi-C data."]
+In summary, the problem of class imbalance exists at all resolutions of Hi-C data."; !!!
+editted]
 
@@
 
-Using the Jaccard [???
-Spell capital everywhere] index, we were able to determine which group-specific annotations were enriched together on the linear genome.
-As could be expected, for GM12878, the class of 14 annotations segmenting the chromation into different states exhibited very low pairwise correlations, with a jaccard index range of (0-0.001) (Table 1).
-[???
-Wrong table?] However, specific sets of pairwise histone modifications and transcription factor binding sites (TFBS) were found to be highly enriched.
-The range of jaccard indices for the 10 histone modifications was found to be (0.022-0.539).
+Using the Jaccard index, we were able to determine which group-specific annotations were enriched together on the linear genome.
+As could be expected, for GM12878, the class of 14 annotations segmenting the chromation into different states exhibited very low pairwise correlations, with a Jaccard index range of (0-0.001) (Table 3).
+However, specific sets of pairwise histone modifications and transcription factor binding sites (TFBS) were found to be highly enriched.
+The range of Jaccard indices for the 10 histone modifications was found to be (0.022-0.539).
 Specifically, H3k27ac, H3k4me1, H3k4me2, and H3k4me3 were found to be highly correlated, high levels of which have been detected surrounding transcription start sites [@barski2007high].
-For the 79 TFBS, the range of jaccard indices was (<0.001-0.425).
+For the 79 TFBS, the range of Jaccard indices was (<0.001-0.425).
 Here, known mediators of loop extrusion components were found to have high pairwise correlations including CTCF, RAD21, and SMC3 [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
-Similar profiles of jaccard indices were exhibited across the sets of annotations for the K562 cell line (Supplementary Table 4).
-<!--The high jaccard indices among select sets of genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.-->
+Similar profiles of Jaccard indices were exhibited across the sets of annotations for the K562 cell line (Supplementary Table 4).
+<!--The high Jaccard indices among select sets of genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.-->
 

### 2019-05-18 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-**Background.** Advances in Hi-C sequencing technologies have revealed the hierarchical structure of genome organization.
-Among this organization exists regions in the genome that are highly self-interacting, termed topologically associated domains (TADs).
-The locations of TADs throughout the linear genome has been studied extensively.
-However, the set of functional genomic annotations that are associated with the formation of TADs has not yet been systematically evaluated.
-By identifying the annotations that are enriched near regions that demarcate TADs, we can gain a better understanding of the mechanisms that lead to the 3D structure of the genome.
+**Background.** Topologically Associated Domains (TADs) represent fundamental building blocks of the three-dimensional (3D) genome organization and regulation.
+Several epigenetic marks, such as CTCF, are highly enriched at TAD boundaries, suggesting a strong epigenetic component of TAD boundary formation.
+Several methods have been developed to leverage the growing amount of (epi)genomic annotation data for predicting TAD boundaries; however, they overlooked key characteristics of the data, such as spatial associations between a genomic annotation and a boundary.
+Furthermore, the number of regions containing TAD boundaries is much smaller than the rest of the genome, creating a class imbalance problem.
 
-Current methods rely on the use of classification algorithms to predict influential annotations.
-However, key characteristics of domain data are typically ignored.
-Most importantly, the sparsity of TAD boundaries throughout the linear genome leads to heavily imbalanced classes that distinguish boundary vs.
-non-boundary regions.
-In addition, determining the most informative relationship between TAD boundaries and genomic annotations remains an open problem.
-**Methods.** To address this, we proposed a novel ensemble framework in order to systematically compare the performances of random forest classifiers implemented on combinations of different Hi-C contact matrix resolutions, feature engineering strategies, and re-sampling techniques.
+**Methods.** To investigate the problem of spatial genomic relationships and class imbalance problem, we developed an ensemble framework for optimizing prediction of TAD boundaries.
+We utilized several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) coupled with various metrics for classifier performance evaluation (Area Under Receiver Operating Characteristics (AUCROC) curve, Precision-Recall curve (AUPRC), F1, Matthew Correlation Coefficient (MCC), among others) to select the best predictive model in class imbalance settings.
 
-**Results.** Using the GM12878 and K562 cell lines, we show that models built on SMOTE (Synthetic Minority Over-sampling TEchnique) re-sampled data out performed models built simply on random under- and over-sampled data, across all resolutions.
-Additionally, our results indicated that distances between annotations and TAD boundaries were more informative than other predictor-types used to build the feature space of models.
-We also observed that performances tended to degrade as data resolution decreased.
-Lastly, the most predictive annotations in the best performing models were found to be consistent across both cell line and resolution.
-They included well-known marks of TAD boundaries such as CTCF, SMC3, RAD21, and ZNF143, as well as lesser known transcription factors including P300 and NFKB.
+**Results.** Using different feature engineering and resampling strategies, coupled with elastic net-based feature selection, we systematically compared the performance of models predicting the location of TAD boundaries (Gm12878 and K562 Hi-C data at 10kb to 100kb resolutions).
+Precision-Recall curves were found to be best suited for evaluating model performance in class imbalance settings.
+Random undersampling and SMOTE-resampled data performed best for optimal parameter selection.
+Transcription Factor Binding Sites (TFBSs) were best type of genomic annotations for predicting TAD boundaries than histone modifications and chromatin states; we identified well-known CTCF, SMC3, RAD21, and several novel TFBSs as best predictors of TAD boundaries.
+Importantly, spatial relationships (distance between TAD boundaries and genomic annotations) were best predictors of TAD boundaries as compared with commonly used overlap counts or percent overlap measures.
 
-**Conclusions.** The experiments derived from our ensemble framework provide a useful guide toward the exploration of chromatin organization, while highlighting the impact of both class imbalance and feature engineering in TAD boundary prediction.
-Our framework provides insight into the best set of parameters necessary for optimal performance.
+**Conclusions.** Our results outline strategies for predictive modeling of 3D genomic domains using 1D genome annotation data.
+The accurate modeling of TAD boundaries will improve our understanding of how epigenetics shapes the 3D structure of the genome.
 
@@
 
-After determining the optimal set of data level characteristics necessary for predicting TAD boundaries, we then aimed to identify the set of functional genomic elements that were most influential in predicting said boundaries.
+After determining the optimal set of data level characteristics, we then aimed to compare the performances of annotation-specifc models.
+In doing so, we inspected the proportion of predictive importance that was explained by each of the 3 groups of annotations (chromatin states, histone modifications, and transcription factor binding sites), across resolution.
+We found that for random forest models implemented on distance-type predictors, using SMOTE re-sampling, the majority of the proportional predictive importance was obtained by the cell-line specific transcription factor binding sites, and was consistent across resolutions (Figure 5; Supplementary Figure 4).
 
-In order to assess the predictive capabilities of specific types of annotations, we further compared the performances of annotation-specific models.
-Using the optimal set of characteristics obtained above (SMOTE re-sampling with distance-type predictors), random forest classifiers built on sets of cell line specific histone modifications, chromatin state segmentations, and transcription factor binding sites (TFBS) were compared to a model that included all three types together.
-For GM12878, models built simply on TFBS were found to perform consistently just as well as models that included all 3 sets of annotations, across resolution (Figure 6).
-Similar results were found when evaluating the K562 cell line (supplementary Figure 11).
-For both resolutions, models built on only histone modifications were found to have the lowest MCC, across resolutions, followed by models built on chromatin state segmentations.
+We further assessed the predictive capabilities of the specific sets of annotations by comparing the performances of annotation-specific random forest models implemented on the optimal set of characteristics.
+We found that models built simply on cell line specific TFBS out performed other cell line and annotation-specific models at all resolutions (Figure 6; Supplementary Figure 5).
+Additionally, when compared to the optimal model identified from the ensemble framework, one that included all 3 sets of annotations, the TFBS-specific models performed similarly at the 10 kb and 25 kb resolutions.
+Interestingly though, at the 50 kb and 100 kb resolutions, the TFBS-specific models out performed models built on the combined sets of annotations, indicating that, at lower resolution, the inclusion of other types of annotations contributed to additional noise rather than signal.
 
@@
 
-As an external method of validation, we also investigated the predictive importance of the annotations that our top performing models were built on.
-We found that specific TFBS, including SMC3ab, ZNF143, CTCF, and RAD21, were given consistently high predictive importance in the models built on the GM12878 cell line, across all resolutions (Figure 8).
-These are known factors associated with the hypothesized loop extrusion model [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self] and were found to yield consistently high predictive importance on the K562 cell line as well, with similar profiles across resolutions (Supplementary Figure 15).
-[???mention additional tfbs when full results ready]
+We then sought to determine which of the transcription factor binding sites were most influential in predicting TAD boundaries.
+We found that the cell line specific binding sites associated with SMC3, CTCF, RAD21, ZNF143, and YY1 were given consistently high predictive importance, across all resolutions (Figure 7; Supplementary Figure 6).
+The SMC3, CTCF, and RAD21 binding sites are known factors associated with the cohesin protein complex, which is hypothesized to be what creates loops in the DNA  [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+Likwise, ZNF143 and YY1 are known structural regulators of enhancer-promoter interactions that also contribute to looping of the linear genome [@weintraub2017yy1; @gonzalez2017znf143].
+With the identification of these factors known to be enriched at TAD boundaries, we are able to confirm the validity of our model building process.
+Additionally, we were also able to identify some lesser known cell line specific transcription factors as predictive of TAD boundaries including the MYC-associated zing-finger protein (MAZ), jun-D proto-oncogene (JUND), and ELF1.
+These transcription factor binding sites tended to be given higher predictive importance at lower resolution.
+In fact, at lower resolutions, the predictive importance was found to be much more evenly dispersed across the top transcription factor binding sites, than for higher resolutions.
+This is again suggestive of the fact that the spatial relationship between functional annotations, specifically transcription factor binding sites, and TAD boundaries changes at different Hi-C data resolutions.
 

### 2019-05-19 Scripts/investigating_auprc.Rmd
script for investigating auprc

---
title: "investigating_auprc"
author: "Spiro Stilianoudakis"
date: "May 18, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

# Investigating Area Under the Precision-Recall Curve

## GM12878

```{r}
auprcdata_gm12878 <- numeric()
pdata_gm12878 <- numeric()
rdata_gm12878 <- numeric()
f1data_gm12878 <- numeric()

for(i in c("10kb", "25kb","50kb","100kb")){
  for(j in paste0("CHR", c(1:8,10:22))){
	  for(k in c("none","ros","rus","smote")){
		  for(l in c("distance", "oc", "op")){
			  perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/",
			               i,
                     "/results_by_chr/",
									   j, 
									   "/",
									   k, 
									   "/", 
									   l, 
									   "/enet/rfperf.rds"))

			  auprcdata_gm12878 <- rbind(auprcdata_gm12878,
			                             perfdata[19,2])

			  pdata_gm12878 <- rbind(pdata_gm12878,
			                             perfdata[10,2])

			  rdata_gm12878 <- rbind(rdata_gm12878,
			                             perfdata[6,2])

			  f1data_gm12878 <- rbind(f1data_gm12878,
			                             perfdata[16,2])
		  }
	  }
  }
}

pr_results_gm12878 <- cbind.data.frame(AUPRC=auprcdata_gm12878,
                                       Precision=pdata_gm12878,
                                       Recall=rdata_gm12878,
                                       F1=f1data_gm12878,
                                       Predictor=rep(c("Distance", "OC", "OP"), 336),
                                       Resampling=rep(c(rep("None",3),
                                                    rep("ROS", 3),
                                                    rep("RUS", 3),
                                                    rep("SMOTE", 3)),84),
                                       Chromosome=rep(c(rep("CHR1",12),
                                                     rep("CHR2",12),
                                                     rep("CHR3",12),
                                                     rep("CHR4",12),
                                                     rep("CHR5",12),
                                                     rep("CHR6",12),
                                                     rep("CHR7",12),
                                                     rep("CHR8",12),
                                                     rep("CHR10",12),
                                                     rep("CHR11",12),
                                                     rep("CHR12",12),
                                                     rep("CHR13",12),
                                                     rep("CHR14",12),
                                                     rep("CHR15",12),
                                                     rep("CHR16",12),
                                                     rep("CHR17",12),
                                                     rep("CHR18",12),
                                                     rep("CHR19",12),
                                                     rep("CHR20",12),
                                                     rep("CHR21",12),
                                                     rep("CHR22",12)),4),
                                       Resolution=c(rep("10 kb", 21*12),
                                                     rep("25 kb", 21*12),
                                                     rep("50 kb", 21*12),
                                                     rep("100 kb", 21*12)))

pr_results_gm12878$Resolution <- factor(pr_results_gm12878$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
pr_results_gm12878$Predictor <- factor(pr_results_gm12878$Predictor, levels=c("OC","OP","Distance"))

pr_results_gm12878_summ <- pr_results_gm12878 %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(auprc = mean(AUPRC, na.rm = TRUE),
            auprcSD = sd(AUPRC, na.rm = TRUE),
            precision = mean(Precision, na.rm = TRUE),
            precisionSD = sd(Precision, na.rm = TRUE),
            recall = mean(Recall, na.rm = TRUE),
            recallSD = sd(Recall, na.rm = TRUE),
            f1 = mean(F1, na.rm = TRUE),
            f1SD = sd(F1, na.rm = TRUE))

#auprc
auprcplot <- ggplot(pr_results_gm12878_summ, aes(x=Resolution, y=auprc, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=auprc-auprcSD, ymax=auprc+auprcSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("AUPRC") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#precision
precisionplot <- ggplot(pr_results_gm12878_summ, aes(x=Resolution, y=precision, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=precision-precisionSD, ymax=precision+precisionSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("Precision") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#recall
recallplot <- ggplot(pr_results_gm12878_summ, aes(x=Resolution, y=recall, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=recall-recallSD, ymax=recall+recallSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("Recall") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#f1
f1plot <- ggplot(pr_results_gm12878_summ, aes(x=Resolution, y=f1, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=f1-f1SD, ymax=f1+f1SD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("F1") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

### 2019-05-19 Scripts/evaluating_feature_reduction.Rmd
editted results scripts

@@
 
+enet_ratios_gm12878_summ$Resolution <- factor(enet_ratios_gm12878_summ$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
+
+ggplot(enet_ratios_gm12878_summ, aes(fill=Annotation, y=AveRatio, x=Resolution)) + 
+    geom_bar(stat="identity", position = position_dodge()) +
+    geom_errorbar(aes(ymin=AveRatio-AveRatioSD, ymax=AveRatio+AveRatioSD), width=.5,
+                 position=position_dodge(.9), alpha=0.75) +
+    xlab("Resolution") +
+    ylab("Proportion of Features in Final Model") +
+    scale_fill_discrete(name="Annotation\nGroup")+
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15,
+                                     angle = 45,
+                                     hjust = 1),
+          axis.text.y = element_text(size = 10),
+          axis.title.x = element_text(size = 20),
+          axis.title.y = element_text(size = 20),
+          legend.text=element_text(size=15),
+          legend.title=element_text(size=20))
+
 ```

### 2019-05-19 Scripts/investigating_auprc.Rmd
editted results scripts

@@
 f1data_gm12878 <- numeric()
+tpdata_gm12878 <- numeric()
+fpdata_gm12878 <- numeric()
+tndata_gm12878 <- numeric()
+fndata_gm12878 <- numeric()
 
@@
 									   "/enet/rfperf.rds"))
+
+			  tndata_gm12878 <- rbind(tndata_gm12878, 
+			                          perfdata[1,2])
+
+			  fndata_gm12878 <- rbind(fndata_gm12878, 
+			                          perfdata[2,2])
+
+			  fpdata_gm12878 <- rbind(fpdata_gm12878, 
+			                          perfdata[3,2])
+
+			  tpdata_gm12878 <- rbind(tpdata_gm12878, 
+			                          perfdata[4,2])
 
@@
 
-pr_results_gm12878 <- cbind.data.frame(AUPRC=auprcdata_gm12878,
+pr_results_gm12878 <- cbind.data.frame(TN=tndata_gm12878,
+                                       FN=fndata_gm12878,
+                                       FP=fpdata_gm12878,
+                                       TP=tpdata_gm12878,
+                                       AUPRC=auprcdata_gm12878,
                                        Precision=pdata_gm12878,
@@
             f1 = mean(F1, na.rm = TRUE),
-            f1SD = sd(F1, na.rm = TRUE))
+            f1SD = sd(F1, na.rm = TRUE),
+            tn = mean(TN, na.rm = TRUE),
+            tnSD = sd(TN, na.rm = TRUE),
+            fn = mean(FN, na.rm = TRUE),
+            fnSD = sd(FN, na.rm = TRUE),
+            fp = mean(FP, na.rm = TRUE),
+            fpSD = sd(FP, na.rm = TRUE),
+            tp = mean(TP, na.rm = TRUE),
+            tpSD = sd(TP, na.rm = TRUE))
 
@@
 
+#TP
+tpplot <- ggplot(pr_results_gm12878_summ, aes(x=Resolution, y=tp, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=tp-tpSD, ymax=tp+tpSD), width=1,
+                 position=position_dodge(0.5)) +
+     facet_grid(~ Predictor)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("True Positives") + #ylim(-.05,.5) +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+#FP
+fpplot <- ggplot(pr_results_gm12878_summ, aes(x=Resolution, y=fp, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=fp-fpSD, ymax=fp+fpSD), width=1,
+                 position=position_dodge(0.5)) +
+     facet_grid(~ Predictor)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("False Positives") + #ylim(-.05,.5) +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+#TN
+tnplot <- ggplot(pr_results_gm12878_summ, aes(x=Resolution, y=tn, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=tn-tnSD, ymax=tn+tnSD), width=1,
+                 position=position_dodge(0.5)) +
+     facet_grid(~ Predictor)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("True Negatives") + #ylim(-.05,.5) +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+#FN
+fnplot <- ggplot(pr_results_gm12878_summ, aes(x=Resolution, y=fn, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=fn-fnSD, ymax=fn+fnSD), width=1,
+                 position=position_dodge(0.5)) +
+     facet_grid(~ Predictor)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("False Negatives") + #ylim(-.05,.5) +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
 ```

### 2019-05-20 Scripts/evaluating_variable_importances.Rmd
editted results script

@@
 
-# Variable Importance Heatmaps for models with distance type predictors with SMOTE resampling
+# TFBS with distance type predictors with SMOTE resampling
 
@@
   ylab("Transcription Factor") +
-  scale_fill_gradient2(low = "white",
+  scale_fill_gradient2(limits=c(0,100),
+                      low = "white",
                       mid = "pink",
@@
 ```
+
+# Chromstates with distance type predictors with SMOTE resampling
+
+##GM12878
+
+```{r}
+annots <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
+annots <- annots[grep("Gm12878", annots)]
+annots <- gsub(paste(c("Gm12878-",".bed"), collapse = "|"), "", annots)
+
+```
+
+###10kb
+
+```{r}
+varimp_gm12878_10kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_10kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_10kb <- data.frame(Feature = rownames(varimp_gm12878_10kb),
+                                  aveimp10kb = rowMeans(varimp_gm12878_10kb, na.rm = TRUE),
+                                  sdimp10kb = apply(varimp_gm12878_10kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_10kb) <- NULL
+
+```
+
+###25kb
+
+```{r}
+varimp_gm12878_25kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_25kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_25kb <- data.frame(Feature = rownames(varimp_gm12878_25kb),
+                                  aveimp25kb = rowMeans(varimp_gm12878_25kb, na.rm = TRUE),
+                                  sdimp25kb = apply(varimp_gm12878_25kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_25kb) <- NULL
+
+```
+
+###50kb
+
+```{r}
+varimp_gm12878_50kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_50kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_50kb <- data.frame(Feature = rownames(varimp_gm12878_50kb),
+                                  aveimp50kb = rowMeans(varimp_gm12878_50kb, na.rm = TRUE),
+                                  sdimp50kb = apply(varimp_gm12878_50kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_50kb) <- NULL
+
+```
+
+###100kb
+
+```{r}
+varimp_gm12878_100kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_100kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_100kb <- data.frame(Feature = rownames(varimp_gm12878_100kb),
+                                  aveimp100kb = rowMeans(varimp_gm12878_100kb, na.rm = TRUE),
+                                  sdimp100kb = apply(varimp_gm12878_100kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_100kb) <- NULL
+
+```
+
+##K562
+
+```{r}
+annots <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
+annots <- annots[grep("K562", annots)]
+annots <- gsub(paste(c("K562-",".bed"), collapse = "|"), "", annots)
+
+```
+
+###10kb
+
+```{r}
+varimp_K562_10kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_10kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_10kb <- data.frame(Feature = rownames(varimp_K562_10kb),
+                                  aveimp10kb = rowMeans(varimp_K562_10kb, na.rm = TRUE),
+                                  sdimp10kb = apply(varimp_K562_10kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_10kb) <- NULL
+
+```
+
+###25kb
+
+```{r}
+varimp_K562_25kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_25kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_25kb <- data.frame(Feature = rownames(varimp_K562_25kb),
+                                  aveimp25kb = rowMeans(varimp_K562_25kb, na.rm = TRUE),
+                                  sdimp25kb = apply(varimp_K562_25kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_25kb) <- NULL
+
+```
+
+###50kb
+
+```{r}
+varimp_K562_50kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_50kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_50kb <- data.frame(Feature = rownames(varimp_K562_50kb),
+                                  aveimp50kb = rowMeans(varimp_K562_50kb, na.rm = TRUE),
+                                  sdimp50kb = apply(varimp_K562_50kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_50kb) <- NULL
+
+```
+
+###100kb
+
+```{r}
+varimp_K562_100kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_100kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_100kb <- data.frame(Feature = rownames(varimp_K562_100kb),
+                                  aveimp100kb = rowMeans(varimp_K562_100kb, na.rm = TRUE),
+                                  sdimp100kb = apply(varimp_K562_100kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_100kb) <- NULL
+
+```
+
+##Plots
+
+```{r}
+#GM12878
+all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
+                                        varimp_gm12878_10kb$aveimp10kb,
+                                        varimp_gm12878_25kb$aveimp25kb,
+                                        varimp_gm12878_50kb$aveimp50kb,
+                                        varimp_gm12878_100kb$aveimp100kb)
+names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+all_varimps_gm12878 <- all_varimps_gm12878[order(all_varimps_gm12878$ave10kb, decreasing = TRUE),]
+#all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
+all_varimps_gm12878 <- melt(all_varimps_gm12878)
+
+chromstates_gm12878_plot <- ggplot(all_varimps_gm12878, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
+  geom_tile(aes(fill = value), colour = "white") + 
+  xlab("") +
+  ylab("") +
+  scale_fill_gradient2(limits=c(0,100),
+                      low = "white",
+                      mid = "pink",
+                      midpoint = 50,
+                      high = muted("red"),
+                      na.value = "grey50",
+                      name="Predictive\nImportance") +
+  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 10),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+#K562
+all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
+                                        varimp_K562_10kb$aveimp10kb,
+                                        varimp_K562_25kb$aveimp25kb,
+                                        varimp_K562_50kb$aveimp50kb,
+                                        varimp_K562_100kb$aveimp100kb)
+names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+all_varimps_K562 <- all_varimps_K562[order(all_varimps_K562$ave10kb, decreasing = TRUE),]
+#all_varimps_K562 <- all_varimps_K562[1:20,]
+all_varimps_K562 <- melt(all_varimps_K562)
+
+chromstates_K562_plot <- ggplot(all_varimps_K562, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
+  geom_tile(aes(fill = value), colour = "white") + 
+  xlab("") +
+  ylab("") +
+  scale_fill_gradient2(limits=c(0,100),
+                      low = "white",
+                      mid = "pink",
+                      midpoint = 50,
+                      high = muted("red"),
+                      na.value = "grey50",
+                      name="Predictive\nImportance") +
+  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 10),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+figure <- ggarrange(chromstates_gm12878_plot,
+                    chromstates_K562_plot,
+                ncol = 2, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "right",
+                labels = "AUTO",
+                font.label = list(size=20))
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Chromatin States", color = "black", rot = 90, size=20)
+)
+
+```
+
+# Histones with distance type predictors with SMOTE resampling
+
+##GM12878
+
+```{r}
+annots <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
+annots <- annots[grep("Gm12878", annots)]
+annots <- gsub(paste(c("Gm12878-",".bed"), collapse = "|"), "", annots)
+
+```
+
+###10kb
+
+```{r}
+varimp_gm12878_10kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_10kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_10kb <- data.frame(Feature = rownames(varimp_gm12878_10kb),
+                                  aveimp10kb = rowMeans(varimp_gm12878_10kb, na.rm = TRUE),
+                                  sdimp10kb = apply(varimp_gm12878_10kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_10kb) <- NULL
+
+```
+
+###25kb
+
+```{r}
+varimp_gm12878_25kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_25kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_25kb <- data.frame(Feature = rownames(varimp_gm12878_25kb),
+                                  aveimp25kb = rowMeans(varimp_gm12878_25kb, na.rm = TRUE),
+                                  sdimp25kb = apply(varimp_gm12878_25kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_25kb) <- NULL
+
+```
+
+###50kb
+
+```{r}
+varimp_gm12878_50kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_50kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_50kb <- data.frame(Feature = rownames(varimp_gm12878_50kb),
+                                  aveimp50kb = rowMeans(varimp_gm12878_50kb, na.rm = TRUE),
+                                  sdimp50kb = apply(varimp_gm12878_50kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_50kb) <- NULL
+
+```
+
+###100kb
+
+```{r}
+varimp_gm12878_100kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_100kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_100kb <- data.frame(Feature = rownames(varimp_gm12878_100kb),
+                                  aveimp100kb = rowMeans(varimp_gm12878_100kb, na.rm = TRUE),
+                                  sdimp100kb = apply(varimp_gm12878_100kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_100kb) <- NULL
+
+```
+
+##K562
+
+```{r}
+annots <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
+annots <- annots[grep("K562", annots)]
+annots <- gsub(paste(c("K562-",".bed"), collapse = "|"), "", annots)
+
+```
+
+###10kb
+
+```{r}
+varimp_K562_10kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_10kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_10kb <- data.frame(Feature = rownames(varimp_K562_10kb),
+                                  aveimp10kb = rowMeans(varimp_K562_10kb, na.rm = TRUE),
+                                  sdimp10kb = apply(varimp_K562_10kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_10kb) <- NULL
+
+```
+
+###25kb
+
+```{r}
+varimp_K562_25kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_25kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_25kb <- data.frame(Feature = rownames(varimp_K562_25kb),
+                                  aveimp25kb = rowMeans(varimp_K562_25kb, na.rm = TRUE),
+                                  sdimp25kb = apply(varimp_K562_25kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_25kb) <- NULL
+
+```
+
+###50kb
+
+```{r}
+varimp_K562_50kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_50kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_50kb <- data.frame(Feature = rownames(varimp_K562_50kb),
+                                  aveimp50kb = rowMeans(varimp_K562_50kb, na.rm = TRUE),
+                                  sdimp50kb = apply(varimp_K562_50kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_50kb) <- NULL
+
+```
+
+###100kb
+
+```{r}
+varimp_K562_100kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_100kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_100kb <- data.frame(Feature = rownames(varimp_K562_100kb),
+                                  aveimp100kb = rowMeans(varimp_K562_100kb, na.rm = TRUE),
+                                  sdimp100kb = apply(varimp_K562_100kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_100kb) <- NULL
+
+```
+
+##Plots
+
+```{r}
+#GM12878
+all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
+                                        varimp_gm12878_10kb$aveimp10kb,
+                                        varimp_gm12878_25kb$aveimp25kb,
+                                        varimp_gm12878_50kb$aveimp50kb,
+                                        varimp_gm12878_100kb$aveimp100kb)
+names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+all_varimps_gm12878 <- all_varimps_gm12878[order(all_varimps_gm12878$ave10kb, decreasing = TRUE),]
+#all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
+all_varimps_gm12878 <- melt(all_varimps_gm12878)
+
+histones_gm12878_plot <- ggplot(all_varimps_gm12878, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
+  geom_tile(aes(fill = value), colour = "white") + 
+  xlab("") +
+  ylab("") +
+  scale_fill_gradient2(limits=c(0,100),
+                      low = "white",
+                      mid = "pink",
+                      midpoint = 50,
+                      high = muted("red"),
+                      na.value = "grey50",
+                      name="Predictive\nImportance") +
+  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 10),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+#K562
+all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
+                                        varimp_K562_10kb$aveimp10kb,
+                                        varimp_K562_25kb$aveimp25kb,
+                                        varimp_K562_50kb$aveimp50kb,
+                                        varimp_K562_100kb$aveimp100kb)
+names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+all_varimps_K562 <- all_varimps_K562[order(all_varimps_K562$ave10kb, decreasing = TRUE),]
+#all_varimps_K562 <- all_varimps_K562[1:20,]
+all_varimps_K562 <- melt(all_varimps_K562)
+
+histones_K562_plot <- ggplot(all_varimps_K562, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
+  geom_tile(aes(fill = value), colour = "white") + 
+  xlab("") +
+  ylab("") +
+  scale_fill_gradient2(limits=c(0,100),
+                      low = "white",
+                      mid = "pink",
+                      midpoint = 50,
+                      high = muted("red"),
+                      na.value = "grey50",
+                      name="Predictive\nImportance") +
+  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 10),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20))
+
+figure <- ggarrange(histones_gm12878_plot,
+                    histones_K562_plot,
+                ncol = 2, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "right",
+                labels = "AUTO",
+                font.label = list(size=20))
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("Histone Modifications", color = "black", rot = 90, size=20)
+)
+
+```

### 2019-05-20 Scripts/comparing_distance_profiles_using_density_plots.Rmd
editted results script

--- 2019-04-17 Scripts/comparing_distance_densities_by_genomic_bin_class.Rmd
@@
 
-## Function for ploting distance densities between bins with and without TAD boundaries from SMOTE resampled data
+## Top annotations
 
 ```{r}
-distplotsfunc <- function(cl, resolution, annotation){
-  train <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/training_testing/train.rds"))
+annots <- c("Gm12878-Smc3ab9263-Sydh_dist",
+            "Gm12878-Ctcf-Broad_dist",
+            "Gm12878-Znf143166181ap-Sydh_dist",
+            "Gm12878-Yy1sc281-Haib_dist",
+            "Gm12878-Rad21-Haib_dist")
+```
 
-  enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))
+### 10kb
 
-  names(train) <- gsub(paste(c("`", 
-                             "Gm12878", 
-                             "-", 
-                             #"_", 
-                             #"dist", "count", "perc",
-                             "Haib", 
-                             "Sydh",
-                             "Uta",
-                             "Uw",
-                             "Broad",
-                             "Uchicago"), collapse = "|"), "", names(train))
-  train <- train[,c(1,which(names(train) %in% enetcoefs))]
+```{r}
+
+dist_list_gm12878_10kb <- list()
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/gm12878_10kb.rds")
+
+	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")
+
+	  reduce_chr <- tolower(chrs[i])
+	  chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),
+	                                       c(1, which(names(whole_genome_dat) %in% annots))]
 
 	  set.seed(123)
-  train_smote <- SMOTE(y ~ ., 
+	  inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
+    train <- chr_specific_dat[inTrainingSet,]
+
+    set.seed(123)
+	  train <- SMOTE(y ~ ., 
 	                 data=train, 
@@
                    perc.under = 200)
+	  train$CHR <- chrs[i]
+	  train$Resolution <- "10 kb"
 
-  annotname <- gsub(paste(c("`", 
-             "Gm12878", 
-             "-", 
-             #"_", 
-             #"dist", "count", "perc",
-             "Haib", 
-             "Sydh",
-             "Uta",
-             "Uw",
-             "Broad",
-             "Uchicago"), collapse = "|"), "", annotation)
+	  dist_list_gm12878_10kb[[i]] <- train
 
-  #data <- train[, c(1, which(names(train)==annotname))]
-  #
-  #set.seed(123)
-  #majorityids <- sample(x=which(data$y=="No"), size=length(which(data$y=="Yes")))
-  #annotdata <- rbind.data.frame(data[which(data$y=="Yes"),],
-  #                              data[majorityids,])
+}
 
-  annotdata <- train_smote[, c(1, which(names(train_smote)==annotname))]
+dist_gm12878_10kb <- do.call("rbind", dist_list_gm12878_10kb)
 
-  #ks.test(annotdata[which(annotdata$y=="No"),2], annotdata[which(annotdata$y=="Yes"),2], alternative = "two.sided")
+#dist_gm12878_10kb_summ <- dist_gm12878_10kb %>%
+#  dplyr::group_by(y,CHR) %>%
+#  dplyr::summarise(Ctcf = mean(`Gm12878-Ctcf-Broad_dist`, na.rm = TRUE),
+#                   Rad21 = mean(`Gm12878-Rad21-Haib_dist`, na.rm = TRUE),
+#                   Smc3ab9263 = mean(`Gm12878-Smc3ab9263-Sydh_dist`, na.rm = TRUE),
+#                   Yy1sc281 = mean(`Gm12878-Yy1sc281-Haib_dist`, na.rm = TRUE),
+#                   Znf143166181ap = mean(`Gm12878-Znf143166181ap-Sydh_dist`, na.rm = TRUE))
 
-  perm.pval <- pvalue(oneway_test(annotdata[,2] ~ annotdata[,1],
-                     data=annotdata,
-                     alternative="greater", 
-                     distribution=approximate(B=10000)))[1]
+```
 
-  perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+### 25kb
 
-  plottitle <- paste(gsub(paste(c("Gm12878",
-                                  "-","_",
-                                  "dist","perc","count",
-                                  "Haib",
-                                  "Sydh",
-                                  "Uta",
-                                  "Uw",
-                                  "Broad",
-                                  "Uchicago"), 
-                                collapse = "|"), 
-                          "",
-                          annotation))
+```{r}
 
-  p <- ggplot(annotdata, aes(x=annotdata[,2], color=y)) +
-    geom_density() +
-    scale_color_discrete(name="Class of\nGenomic Bin",
-                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
-    ylab("Frequency") +
-    xlab("Log2 Distance") +
-    ggtitle(paste(plottitle)) +
-    annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+dist_list_gm12878_25kb <- list()
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/gm12878_25kb.rds")
+
+	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")
+
+	  reduce_chr <- tolower(chrs[i])
+	  chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),
+	                                       c(1, which(names(whole_genome_dat) %in% annots))]
+
+	  set.seed(123)
+	  inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
+    train <- chr_specific_dat[inTrainingSet,]
+
+    set.seed(123)
+	  train <- SMOTE(y ~ ., 
+	                 data=train, 
+                   perc.over = 100, 
+                   perc.under = 200)
+	  train$CHR <- chrs[i]
+	  train$Resolution <- "25 kb"
+
+	  dist_list_gm12878_25kb[[i]] <- train
+
+}
+
+dist_gm12878_25kb <- do.call("rbind", dist_list_gm12878_25kb)
+
+#dist_gm12878_25kb_summ <- dist_gm12878_25kb %>%
+#  dplyr::group_by(y,CHR) %>%
+#  dplyr::summarise(Ctcf = mean(`Gm12878-Ctcf-Broad_dist`, na.rm = TRUE),
+#                   Rad21 = mean(`Gm12878-Rad21-Haib_dist`, na.rm = TRUE),
+#                   Smc3ab9263 = mean(`Gm12878-Smc3ab9263-Sydh_dist`, na.rm = TRUE),
+#                   Yy1sc281 = mean(`Gm12878-Yy1sc281-Haib_dist`, na.rm = TRUE),
+#                   Znf143166181ap = mean(`Gm12878-Znf143166181ap-Sydh_dist`, na.rm = TRUE))
+
+```
+
+### 50kb
+
+```{r}
+
+dist_list_gm12878_50kb <- list()
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/gm12878_50kb.rds")
+
+	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")
+
+	  reduce_chr <- tolower(chrs[i])
+	  chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),
+	                                       c(1, which(names(whole_genome_dat) %in% annots))]
+
+	  set.seed(123)
+	  inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
+    train <- chr_specific_dat[inTrainingSet,]
+
+    set.seed(123)
+	  train <- SMOTE(y ~ ., 
+	                 data=train, 
+                   perc.over = 100, 
+                   perc.under = 200)
+	  train$CHR <- chrs[i]
+	  train$Resolution <- "50 kb"
+
+	  dist_list_gm12878_50kb[[i]] <- train
+
+}
+
+dist_gm12878_50kb <- do.call("rbind", dist_list_gm12878_50kb)
+
+#dist_gm12878_50kb_summ <- dist_gm12878_50kb %>%
+#  dplyr::group_by(y,CHR) %>%
+#  dplyr::summarise(Ctcf = mean(`Gm12878-Ctcf-Broad_dist`, na.rm = TRUE),
+#                   Rad21 = mean(`Gm12878-Rad21-Haib_dist`, na.rm = TRUE),
+#                   Smc3ab9263 = mean(`Gm12878-Smc3ab9263-Sydh_dist`, na.rm = TRUE),
+#                   Yy1sc281 = mean(`Gm12878-Yy1sc281-Haib_dist`, na.rm = TRUE),
+#                   Znf143166181ap = mean(`Gm12878-Znf143166181ap-Sydh_dist`, na.rm = TRUE))
+
+```
+
+### 100kb
+
+```{r}
+
+dist_list_gm12878_100kb <- list()
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/gm12878_100kb.rds")
+
+	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")
+
+	  reduce_chr <- tolower(chrs[i])
+	  chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),
+	                                       c(1, which(names(whole_genome_dat) %in% annots))]
+
+	  set.seed(123)
+	  inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
+    train <- chr_specific_dat[inTrainingSet,]
+
+    set.seed(123)
+	  train <- SMOTE(y ~ ., 
+	                 data=train, 
+                   perc.over = 100, 
+                   perc.under = 200)
+	  train$CHR <- chrs[i]
+	  train$Resolution <- "100 kb"
+
+	  dist_list_gm12878_100kb[[i]] <- train
+
+}
+
+dist_gm12878_100kb <- do.call("rbind", dist_list_gm12878_100kb)
+
+#dist_gm12878_100kb_summ <- dist_gm12878_100kb %>%
+#  dplyr::group_by(y,CHR) %>%
+#  dplyr::summarise(Ctcf = mean(`Gm12878-Ctcf-Broad_dist`, na.rm = TRUE),
+#                   Rad21 = mean(`Gm12878-Rad21-Haib_dist`, na.rm = TRUE),
+#                   Smc3ab9263 = mean(`Gm12878-Smc3ab9263-Sydh_dist`, na.rm = TRUE),
+#                   Yy1sc281 = mean(`Gm12878-Yy1sc281-Haib_dist`, na.rm = TRUE),
+#                   Znf143166181ap = mean(`Gm12878-Znf143166181ap-Sydh_dist`, na.rm = TRUE))
+
+```
+
+## Plots
+
+```{r}
+all_dist_gm12878 <- rbind.data.frame(dist_gm12878_10kb,
+                                     dist_gm12878_25kb,
+                                     dist_gm12878_50kb,
+                                     dist_gm12878_100kb)
+
+names(all_dist_gm12878) <- c("y", "CTCF", "RAD21", "SMC3", "YY1sc281", "ZNF143", "CHR", "Resolution")
+
+all_dist_gm12878$Resolution <- factor(all_dist_gm12878$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
+
+all_dist_gm12878 <- melt(all_dist_gm12878)
+
+all_dist_gm12878$variable <- factor(all_dist_gm12878$variable, levels=c("SMC3", "CTCF", "RAD21", "ZNF143", "YY1sc281"))
+
+#SMC3
+ggplot(all_dist_gm12878, aes(x = Resolution, y = value, fill = y)) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot(#fill = fill, 
+               #colour = line,
+               outlier.shape = NA) +
+  facet_grid(~ variable) +
+  xlab("Resolution") +
+  ylab("Log2 Distances") +
+  ylim(5,25) +
+  scale_fill_discrete(name="Class of Genomic Bin",
+                      labels=c("Did not overlap\nw/ flanked TAD boundary",
+                               "Overlapped\nw/ flanked TAD boundary")) +
+  #guides(color=FALSE) +
+  theme_minimal() +
   theme_bw() +
-    theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
                                    #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
+                                   hjust = 1),
         axis.text.y = element_text(size = 15),
@@
         legend.title=element_text(size=20),
-     plot.title = element_text(size=20,
-                               hjust=.5))
+        strip.text.x = element_text(size = 15))
+```
 
-  ggsave(p, 
-         filename = paste0("C:/Users/stili/Documents/TAD_miscellaneous/figures/comparing_distance_by_bin_class/", 
-                           cl, 
-                           "_", 
-                           resolution, 
-                           "_", 
-                           plottitle, 
-                           ".png"),
-         width=10,
-         height=10,
-         units="in")
-}
+# K562
 
+## Top annotations
+
+```{r}
+annots <- c("K562-Smc3ab9263-Sydh_dist",
+            "K562-Ctcf-Broad_dist",
+            "K562-Znf143-Sydh_dist",
+            #"K562-Yy1sc281-Haib_dist",
+            "K562-Rad21-Haib_dist")
 ```
@@
 
-#### Top Annotations
+```{r}
 
-```{r}
-#### CTCF
+dist_list_K562_10kb <- list()
 
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Ctcf-Broad_dist")
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/K562_10kb.rds")
 
-#### Smc3ab9263
+	  binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")
 
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")
+	  reduce_chr <- tolower(chrs[i])
+	  chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),
+	                                       c(1, which(names(whole_genome_dat) %in% annots))]
 
-#### Znf143166181ap
+	  set.seed(123)
+	  inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
+    train <- chr_specific_dat[inTrainingSet,]
 
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")
+    set.seed(123)
+	  train <- SMOTE(y ~ ., 
+	                 data=train, 
+                   perc.over = 100, 
+                   perc.under = 200)
+	  train$CHR <- chrs[i]
+	  train$Resolution <- "10 kb"
 
-#### Rad21
+	  dist_list_K562_10kb[[i]] <- train
 
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Rad21-Haib_dist")
+}
 
-#### 08Insulator
+dist_K562_10kb <- do.call("rbind", dist_list_K562_10kb)
 
-#distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-08Insulator_dist")
+#dist_K562_10kb_summ <- dist_K562_10kb %>%
+#  dplyr::group_by(y,CHR) %>%
+#  dplyr::summarise(Ctcf = mean(`K562-Ctcf-Broad_dist`, na.rm = TRUE),
+#                   Rad21 = mean(`K562-Rad21-Haib_dist`, na.rm = TRUE),
+#                   Smc3ab9263 = mean(`K562-Smc3ab9263-Sydh_dist`, na.rm = TRUE),
+#                   Yy1sc281 = mean(`K562-Yy1sc281-Haib_dist`, na.rm = TRUE),
+#                   Znf143166181ap = mean(`K562-Znf143166181ap-Sydh_dist`, na.rm = TRUE))
 
-#### Yy1sc281
-
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Yy1sc281-Haib_dist")
-
-#### DNase
-
-distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-DNase_dist")
 ```
@@
 
-#### Top Annotations
+```{r}
 
-```{r}
-#### CTCF
+dist_list_K562_25kb <- list()
 
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Ctcf-Broad_dist")
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/K562_25kb.rds")
 
-#### Smc3ab9263
+	  binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")
 
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")
+	  reduce_chr <- tolower(chrs[i])
+	  chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),
+	                                       c(1, which(names(whole_genome_dat) %in% annots))]
 
-#### Znf143166181ap
+	  set.seed(123)
+	  inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
+    train <- chr_specific_dat[inTrainingSet,]
 
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")
+    set.seed(123)
+	  train <- SMOTE(y ~ ., 
+	                 data=train, 
+                   perc.over = 100, 
+                   perc.under = 200)
+	  train$CHR <- chrs[i]
+	  train$Resolution <- "25 kb"
 
-#### Rad21
+	  dist_list_K562_25kb[[i]] <- train
 
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Rad21-Haib_dist")
+}
 
-#### 08Insulator
+dist_K562_25kb <- do.call("rbind", dist_list_K562_25kb)
 
-#distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-08Insulator_dist")
+#dist_K562_25kb_summ <- dist_K562_25kb %>%
+#  dplyr::group_by(y,CHR) %>%
+#  dplyr::summarise(Ctcf = mean(`K562-Ctcf-Broad_dist`, na.rm = TRUE),
+#                   Rad21 = mean(`K562-Rad21-Haib_dist`, na.rm = TRUE),
+#                   Smc3ab9263 = mean(`K562-Smc3ab9263-Sydh_dist`, na.rm = TRUE),
+#                   Yy1sc281 = mean(`K562-Yy1sc281-Haib_dist`, na.rm = TRUE),
+#                   Znf143166181ap = mean(`K562-Znf143166181ap-Sydh_dist`, na.rm = TRUE))
 
-#### Yy1sc281
-
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Yy1sc281-Haib_dist")
-
-#### DNase
-
-distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-DNase_dist")
 ```
@@
 
-#### Top Annotations
+```{r}
 
-```{r}
-#### CTCF
+dist_list_K562_50kb <- list()
 
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Ctcf-Broad_dist")
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/K562_50kb.rds")
 
-#### Smc3ab9263
+	  binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")
 
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")
+	  reduce_chr <- tolower(chrs[i])
+	  chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),
+	                                       c(1, which(names(whole_genome_dat) %in% annots))]
 
-#### Znf143166181ap
+	  set.seed(123)
+	  inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
+    train <- chr_specific_dat[inTrainingSet,]
 
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")
+    set.seed(123)
+	  train <- SMOTE(y ~ ., 
+	                 data=train, 
+                   perc.over = 100, 
+                   perc.under = 200)
+	  train$CHR <- chrs[i]
+	  train$Resolution <- "50 kb"
 
-#### Rad21
+	  dist_list_K562_50kb[[i]] <- train
 
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Rad21-Haib_dist")
+}
 
-#### 08Insulator
+dist_K562_50kb <- do.call("rbind", dist_list_K562_50kb)
 
-#distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-08Insulator_dist")
+#dist_K562_50kb_summ <- dist_K562_50kb %>%
+#  dplyr::group_by(y,CHR) %>%
+#  dplyr::summarise(Ctcf = mean(`K562-Ctcf-Broad_dist`, na.rm = TRUE),
+#                   Rad21 = mean(`K562-Rad21-Haib_dist`, na.rm = TRUE),
+#                   Smc3ab9263 = mean(`K562-Smc3ab9263-Sydh_dist`, na.rm = TRUE),
+#                   Yy1sc281 = mean(`K562-Yy1sc281-Haib_dist`, na.rm = TRUE),
+#                   Znf143166181ap = mean(`K562-Znf143166181ap-Sydh_dist`, na.rm = TRUE))
 
-#### Yy1sc281
-
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Yy1sc281-Haib_dist")
-
-#### DNase
-
-distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-DNase_dist")
 ```
@@
 
-#### Top Annotations
+```{r}
 
-```{r}
-#### CTCF
+dist_list_K562_100kb <- list()
 
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Ctcf-Broad_dist")
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/K562_100kb.rds")
 
-#### Smc3ab9263
+	  binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")
 
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")
-
-#### Znf143166181ap
-
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")
-
-#### Rad21
-
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Rad21-Haib_dist")
-
-#### 08Insulator
-
-#distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-08Insulator_dist")
-
-#### Yy1sc281
-
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Yy1sc281-Haib_dist")
-
-#### DNase
-
-distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-DNase_dist")
-```
-
-# K562
-
-## Function for ploting distance densities between bins with and without TAD boundaries from SMOTE resampled data
-
-```{r}
-distplotsfunc <- function(cl, resolution, annotation){
-  train <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/training_testing/train.rds"))
-
-  enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))
-
-  names(train) <- gsub(paste(c("`", 
-                             "K562", 
-                             "-", 
-                             #"_", 
-                             #"dist", "count", "perc",
-                             "Haib", 
-                             "Sydh",
-                             "Uta",
-                             "Uw",
-                             "Broad",
-                             "Uchicago"), collapse = "|"), "", names(train))
-  train <- train[,c(1,which(names(train) %in% enetcoefs))]
+	  reduce_chr <- tolower(chrs[i])
+	  chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),
+	                                       c(1, which(names(whole_genome_dat) %in% annots))]
 
 	  set.seed(123)
-  train_smote <- SMOTE(y ~ ., 
+	  inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
+    train <- chr_specific_dat[inTrainingSet,]
+
+    set.seed(123)
+	  train <- SMOTE(y ~ ., 
 	                 data=train, 
@@
                    perc.under = 200)
+	  train$CHR <- chrs[i]
+	  train$Resolution <- "100 kb"
 
-  annotname <- gsub(paste(c("`", 
-             "K562", 
-             "-", 
-             #"_", 
-             #"dist", "count", "perc",
-             "Haib", 
-             "Sydh",
-             "Uta",
-             "Uw",
-             "Broad",
-             "Uchicago"), collapse = "|"), "", annotation)
+	  dist_list_K562_100kb[[i]] <- train
 
-  #data <- train[, c(1, which(names(train)==annotname))]
-  #
-  #set.seed(123)
-  #majorityids <- sample(x=which(data$y=="No"), size=length(which(data$y=="Yes")))
-  #annotdata <- rbind.data.frame(data[which(data$y=="Yes"),],
-  #                              data[majorityids,])
+}
 
-  annotdata <- train_smote[, c(1, which(names(train_smote)==annotname))]
+dist_K562_100kb <- do.call("rbind", dist_list_K562_100kb)
 
-  #ks.test(annotdata[which(annotdata$y=="No"),2], annotdata[which(annotdata$y=="Yes"),2], alternative = "two.sided")
+#dist_K562_100kb_summ <- dist_K562_100kb %>%
+#  dplyr::group_by(y,CHR) %>%
+#  dplyr::summarise(Ctcf = mean(`K562-Ctcf-Broad_dist`, na.rm = TRUE),
+#                   Rad21 = mean(`K562-Rad21-Haib_dist`, na.rm = TRUE),
+#                   Smc3ab9263 = mean(`K562-Smc3ab9263-Sydh_dist`, na.rm = TRUE),
+#                   Yy1sc281 = mean(`K562-Yy1sc281-Haib_dist`, na.rm = TRUE),
+#                   Znf143166181ap = mean(`K562-Znf143166181ap-Sydh_dist`, na.rm = TRUE))
 
-  perm.pval <- pvalue(oneway_test(annotdata[,2] ~ annotdata[,1],
-                     data=annotdata,
-                     alternative="greater", 
-                     distribution=approximate(B=10000)))[1]
+```
 
-  perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))
+## Plots
 
-  plottitle <- paste(gsub(paste(c("K562",
-                                  "-","_",
-                                  "dist","perc","count",
-                                  "Haib",
-                                  "Sydh",
-                                  "Uta",
-                                  "Uw",
-                                  "Broad",
-                                  "Uchicago"), 
-                                collapse = "|"), 
-                          "",
-                          annotation))
+```{r}
+all_dist_K562 <- rbind.data.frame(dist_K562_10kb,
+                                     dist_K562_25kb,
+                                     dist_K562_50kb,
+                                     dist_K562_100kb)
 
-  p <- ggplot(annotdata, aes(x=annotdata[,2], color=y)) +
-    geom_density() +
-    scale_color_discrete(name="Class of\nGenomic Bin",
-                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
-    ylab("Frequency") +
-    xlab("Log2 Distance") +
-    ggtitle(paste(plottitle)) +
-    annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
+names(all_dist_K562) <- c("y", "CTCF", "RAD21", "SMC3", "ZNF143", "CHR", "Resolution")
+
+all_dist_K562$Resolution <- factor(all_dist_K562$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
+
+all_dist_K562 <- melt(all_dist_K562)
+
+all_dist_K562$variable <- factor(all_dist_K562$variable, levels=c("SMC3", "CTCF", "RAD21", "ZNF143"))
+
+ggplot(all_dist_K562, aes(x = Resolution, y = value, fill = y)) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot(#fill = fill, 
+               #colour = line,
+               outlier.shape = NA) +
+  facet_grid(~ variable) +
+  xlab("Resolution") +
+  ylab("Log2 Distances") +
+  ylim(5,25) +
+  scale_fill_discrete(name="Class of Genomic Bin",
+                      labels=c("Did not overlap\nw/ flanked TAD boundary",
+                               "Overlapped\nw/ flanked TAD boundary")) +
+  #guides(color=FALSE) +
+  theme_minimal() +
   theme_bw() +
-    theme(axis.text.x = element_text(size=15 #,
-                                      #angle = 45, 
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
                                    #margin = ggplot2::margin(t = 35),
-                                      #hjust = 1
-     ),
+                                   hjust = 1),
         axis.text.y = element_text(size = 15),
@@
         legend.title=element_text(size=20),
-     plot.title = element_text(size=20,
-                               hjust=.5))
-
-  ggsave(p, 
-         filename = paste0("C:/Users/stili/Documents/TAD_miscellaneous/figures/comparing_distance_by_bin_class/", 
-                           cl, 
-                           "_", 
-                           resolution, 
-                           "_", 
-                           plottitle, 
-                           ".png"),
-         width=10,
-         height=10,
-         units="in")
-}
-
+        strip.text.x = element_text(size = 15))
 ```
-
-### 10kb
-
-#### Top Annotations
-
-```{r}
-#### CTCF
-
-distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Ctcf-Broad_dist")
-
-#### Smc3ab9263
-
-distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Smc3ab9263-Sydh_dist")
-
-#### Znf143166181ap
-
-distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Znf143166181ap-Sydh_dist")
-
-#### Rad21
-
-distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Rad21-Haib_dist")
-
-#### 08Insulator
-
-#distplotsfunc(cl="K562", resolution="10kb", annotation="K562-08Insulator_dist")
-
-#### Yy1sc281
-
-distplotsfunc(cl="K562", resolution="10kb", annotation="K562-Yy1sc281-Haib_dist")
-
-#### DNase
-
-distplotsfunc(cl="K562", resolution="10kb", annotation="K562-DNase_dist")
-```
-
-### 25kb
-
-#### Top Annotations
-
-```{r}
-#### CTCF
-
-distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Ctcf-Broad_dist")
-
-#### Smc3ab9263
-
-distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Smc3ab9263-Sydh_dist")
-
-#### Znf143166181ap
-
-distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Znf143166181ap-Sydh_dist")
-
-#### Rad21
-
-distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Rad21-Haib_dist")
-
-#### 08Insulator
-
-#distplotsfunc(cl="K562", resolution="25kb", annotation="K562-08Insulator_dist")
-
-#### Yy1sc281
-
-distplotsfunc(cl="K562", resolution="25kb", annotation="K562-Yy1sc281-Haib_dist")
-
-#### DNase
-
-distplotsfunc(cl="K562", resolution="25kb", annotation="K562-DNase_dist")
-```
-
-### 50kb
-
-#### Top Annotations
-
-```{r}
-#### CTCF
-
-distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Ctcf-Broad_dist")
-
-#### Smc3ab9263
-
-distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Smc3ab9263-Sydh_dist")
-
-#### Znf143166181ap
-
-distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Znf143166181ap-Sydh_dist")
-
-#### Rad21
-
-distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Rad21-Haib_dist")
-
-#### 08Insulator
-
-#distplotsfunc(cl="K562", resolution="50kb", annotation="K562-08Insulator_dist")
-
-#### Yy1sc281
-
-distplotsfunc(cl="K562", resolution="50kb", annotation="K562-Yy1sc281-Haib_dist")
-
-#### DNase
-
-distplotsfunc(cl="K562", resolution="50kb", annotation="K562-DNase_dist")
-```
-
-### 100kb
-
-#### Top Annotations
-
-```{r}
-#### CTCF
-
-distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Ctcf-Broad_dist")
-
-#### Smc3ab9263
-
-distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Smc3ab9263-Sydh_dist")
-
-#### Znf143166181ap
-
-distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Znf143166181ap-Sydh_dist")
-
-#### Rad21
-
-distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Rad21-Haib_dist")
-
-#### 08Insulator
-
-#distplotsfunc(cl="K562", resolution="100kb", annotation="K562-08Insulator_dist")
-
-#### Yy1sc281
-
-distplotsfunc(cl="K562", resolution="100kb", annotation="K562-Yy1sc281-Haib_dist")
-
-#### DNase
-
-distplotsfunc(cl="K562", resolution="100kb", annotation="K562-DNase_dist")
-```

### 2019-05-20 Manuscript/manuscript.Rmd
manuscript edits
small polishing

@@
 We illustrate a unified approach toward preparing TAD boundary data for predictive modelling purposes from different cell lines and data resolutions (Figure 1).
-To enable us to build a model that suitably discriminates between regions on the linear genome that are near TAD boundaries and regions that are not, we created a cell line- and resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary (Y=1), or not (Y=0).
+To enable us to build a model that suitably discriminates between regions on the linear genome that are near TAD boundaries and regions that are not, we created a cell line- and resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$).
 The unit width of each bin on the linear genome corresponded to the resolution of the contact matrix on which domains were called.
@@
 To investigate the relationship between functional genomic annotations and the development of TAD boundaries, we devised 3 different predictor-types that composed the feature space of downstream random forest classification models.
-These predictor-type specific annotations represented the data matrix, **X** = {$X_{1}$, $X_{2}$, ..., $X_{p}$}, where $p$ is the complete set of functional annotations.
+These predictor-type specific annotations represented the data matrix, $X = \{X_1, X_2, ..., X_p\}$, where $p$ is the complete set of functional annotations.
 Overlap counts was the least granular predictor-type considered, simply defined by the number of annotation-specific regions located within each genomic bin (Figure 2A).
@@
 <!--When measured in basepairs, distances were found to be highly skewed across all resolutions, for both the GM12878 and K562 cell lines (Supplementary Figures 1-2 A-D).--> As a normalization procedure, we performed a $log_{2}$ transformation on the distances prior to modelling (See Methods Section).
+[???
+Introduce all definitions in Results.
+Put all details in Methods.
+E.g., distance definition is crucial for understanding results, the fact of log2-transformation is Methods.]
 
@@
 
-We then developed an ensemble framework to systematically compare and establish the best set of data level characteristics for predicting TAD boundaries using random forest classifiers built on cell line specific functional genomic annotations (Figure 3).
+We then developed an ensemble framework to systematically compare and establish the best set of data level characteristics for predicting TAD boundaries using random forest classifiers [???
+Do we need RF?] built on cell line specific functional genomic annotations (Figure 3).
 TAD boundaries were called using the Arrowhead algorithm [@durand2016juicebox] from replicate Hi-C data for 2 cell lines $L = \{GM12878, K562\}$, at four different resolutions $R = \{10 kb, 25 kb, 50 kb, 100 kb\}$.
@@
 [???
+This is Methods.
+What is so compelling about those 'results' for the message you try to prove?] [???
 Currently, Methods and the results are redundant.
@@
 
-## IMBALANCE RATIOS REMAINED SEVERE AND INVARIANT TOWARD RESOLUTION
+## IMBALANCE RATIOS REMAINED SEVERE irrespectively of RESOLUTION of Hi-C data
 
@@
 Similar profiles of Jaccard indices were exhibited across the sets of annotations for the K562 cell line (Supplementary Table 4).
-<!--The high Jaccard indices among select sets of genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.-->
+[???
+So what?
+Why did you talk about it?] <!--The high Jaccard indices among select sets of genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.-->
 

### 2019-05-21 Scripts/AUPRC_simulation.Rmd
script for comparing enet results for different cross validation metrics

---
title: "AUPRC_simulation"
author: "Spiro Stilianoudakis"
date: "May 20, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(PRROC)
#library(MLmetrics)
```

# Initializing simulation

```{r}
# set of different levels of class imbalance
IR = seq(-20,-5,by=1)

##defining function to extract AUPR curve
auprcSummary <- function(data, lev = NULL, model = NULL){
  lvls <- levels(data$obs) #take the probability of good class
  prob_good <- data[,lvls[2]] 
  the_curve <- pr.curve(scores.class0 = prob_good,
                        weights.class0 = as.numeric(data$obs)-1, #provide the class labels as 0/1
                        curve = FALSE)
  out <- the_curve$auc.integral
  names(out) <- "AUPRC"
  out
}

#initializing
auprc <- numeric()
precision <- numeric()
recall <- numeric()
mcc <- numeric()
tp <- numeric()
fp <- numeric()
tn <- numeric()
fn <- numeric()
imbalance <- character()
iteration <- numeric()
resampling <- character()

for(i in 1:length(IR)){
#  for(j in 1:10){
j=1    
    #randomly generate data for classification
    set.seed(j)
    dat <- twoClassSim(n = 1000, #number of rows
                       linearVars = 10, #linearly important variables
                       noiseVars = 5, #uncorrelated irrelevant variables
                       corrVars = 5, #correlated irrelevant variables
                       mislabel = .05, #percentage possibly mislabeled
                       intercept = IR[i] #controls imbalance
                       )

    #recode the response variable
    dat$Class <- factor(ifelse(as.character(dat$Class)=="Class1", "No", "Yes"), levels=c("No", "Yes"))

    #split the data
    set.seed(j)
    index <- createDataPartition(y = dat$Class, p = .7, list = FALSE)
    train <- dat[index, ]
    test <- dat[-index, ]

    # set number of iterations
    samps = 50

    for(k in c("none", "ros", "rus", "smote")){
      print(paste(c(IR[i],j,k)))

      #perform resampling 
      if(k=="ros"){
        #assign sample indeces
        sampids <- matrix(ncol=samps, 
                          nrow=length(train$Class[which(train$Class=="No")]))

        #filling in the sample ids matrix
        set.seed(123)
        for(m in 1:samps){
          sampids[,m] <- sample(x = which(train$Class=="Yes"),
                                size = length(which(train$Class=="No")),
                                replace = TRUE)
        }
        train <- rbind.data.frame(train[which(train$Class=="No"),],
                                  train[sampids[,1],])
        #Randomly shuffle the data
        set.seed(321)
        train <- train[sample(nrow(train)),]
      }else if(k=="rus"){
        #assign sample indeces
        sampids <- matrix(ncol=samps, 
                          nrow=length(train$Class[which(train$Class=="Yes")]))

        #filling in the sample ids matrix
        set.seed(123)
        for(m in 1:samps){
          sampids[,m] <- sample(x = which(train$Class=="No"),
                                size = length(which(train$Class=="Yes")),
                                replace = FALSE)
        }
        train <- rbind.data.frame(train[which(train$Class=="Yes"),],
                                  train[sampids[,1],])

        #Randomly shuffle the data
        set.seed(321)
        train <- train[sample(nrow(train)),]
      }else if(k=="smote"){
        set.seed(123)
        train <- SMOTE(Class ~ ., 
                       data=train, 
                       perc.over = 100, 
                       perc.under = 200)

        #Randomly shuffle the data
        set.seed(123)
        train <- train[sample(nrow(train)),]
      }else{train=train}

      #set seeds for each cross folds
      set.seed(123)
      #length is = (n_repeats*nresampling)+1
      seeds <- vector(mode = "list", length = 11)
      #(1 is the number of tuning parameter lambda
      for(l in 1:10) seeds[[l]]<- sample.int(n=1000, 100)
      #for the last model
      seeds[[11]]<-sample.int(1000, 1)

      ##setting contols for elastic net
      fitControl <- trainControl(seeds = seeds,
                                 method = "cv",
                                 number = 5,
                                 ## Estimate class probabilities
                                 classProbs = TRUE,
                                 ## Evaluate performance using 
                                 ## the following function
                                 summaryFunction = auprcSummary)

      #set number of predictors to consider at each node
      tunegrid <- expand.grid(mtry=ceiling(sqrt(dim(train)[2] - 1)))

      #performing random forest
      rfModel <- train(Class~., data=train, 
                       method="rf", 
                       metric="AUPRC", 
                       tuneGrid=tunegrid, 
                       trControl=fitControl, 
                       ntree=500) #as.numeric(rownames(results)[1]))

      pred.rfModel <- predict(rfModel, 
                              newdata=test)

      confMat <- confusionMatrix(data=pred.rfModel, test$Class, positive="Yes")
      TN = as.numeric(confMat$table[1,1])
      FN = as.numeric(confMat$table[1,2])
      FP = as.numeric(confMat$table[2,1])
      TP = as.numeric(confMat$table[2,2])

      fg <- pred.rfModel[test$Class == "Yes"]
      bg <- pred.rfModel[test$Class == "No"]
      pr <- pr.curve(scores.class0 = fg, scores.class1 = bg, curve = F)

      #auprc <- pr$auc.integral
      #precision <- TP/(TP+FP)
      #recall <- TP/(TP+FN)
      #mcc <- (TP*TN - FP*FN)/( sqrt( (TP+FP)*(TP+FN)*(TN+FP)*(TN+FN) ) )

      auprc <- rbind(auprc, pr$auc.integral)
      precision <- rbind(precision, TP/(TP+FP))
      recall <- rbind(recall, TP/(TP+FN))
      mcc <- rbind(mcc, (TP*TN - FP*FN)/( sqrt( (TP+FP)*(TP+FN)*(TN+FP)*(TN+FN) ) ))
      tp <- rbind(tp, TP)
      fp <- rbind(fp, FP)
      tn <- rbind(tn, TN)
      fn <- rbind(fn, FN)
      #imbalance <- rbind(imbalance, IR[i])
      imbalance <- rbind(imbalance,as.numeric(table(test$Class)[2])/as.numeric(table(test$Class)[1]))
      iteration <- rbind(iteration, j)
      resampling <- rbind(resampling, k)

    }
#  }
}

performance_df <- cbind.data.frame(Imbalance = imbalance,
                                   Iteration = iteration,
                                   Resampling = resampling,
                                   AUPRC = auprc,
                                   Precision = precision,
                                   Recall = recall,
                                   MCC = mcc,
                                   TP = tp,
                                   FP = fp,
                                   TN = tn,
                                   FN = fn)

performance_df$Imbalance <- as.numeric(as.character(performance_df$Imbalance))

saveRDS(performance_df, "/home/stilianoudakisc/TAD_data_analysis/auprc_simulation/performance_df.rds")

```

# Plots

```{r}
ggplot(performance_df[which(performance_df$Resampling=="none"),], aes(x=Imbalance, y=AUPRC)) +
  geom_point(shape=1) +   
  geom_smooth(method=lm) +
  theme_minimal() +
  theme_bw()

ggplot(performance_df[which(performance_df$Resampling=="none"),], aes(x=Imbalance, y=Precision)) +
  geom_point(shape=1) +   
  geom_smooth(method=lm) +
  theme_minimal() +
  theme_bw()

ggplot(performance_df[which(performance_df$Resampling=="none"),], aes(x=Imbalance, y=Recall)) +
  geom_point(shape=1) +   
  geom_smooth(method=lm) +
  theme_minimal() +
  theme_bw()

ggplot(performance_df[which(performance_df$Resampling=="none"),], aes(x=Imbalance, y=MCC)) +
  geom_point(shape=1) +   
  geom_smooth(method=lm) +
  theme_minimal() +
  theme_bw()
```

### 2019-05-21 Scripts/evaluating_cv_metric_on_enet_penalization.Rmd
script for comparing enet results for different cross validation metrics

---
title: "evaluating_cv_metric_on_enet_penalization"
author: "Spiro Stilianoudakis"
date: "May 21, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(ggplot2, lib.loc = "/home/R/Rlib-3.4.1-rh6/")
library(caret, lib.loc = "/home/R/Rlib-3.4.1-rh6/")
library(DMwR)
#library(PRROC)
library(ModelMetrics, lib.loc = "/home/R/Rlib-3.4.1-rh6/")

```

# Defining summary metric for cross validation

```{r}
#defining function to extract AUPRC
#auprcSummary <- function(data, lev = NULL, model = NULL){
#  lvls <- levels(data$obs) #take the probability of good class
#  prob_good <- data[,lvls[2]] 
#  the_curve <- pr.curve(scores.class0 = prob_good,
#                        weights.class0 = as.numeric(data$obs)-1, #provide the class labels as 0/1
#                        curve = FALSE)
#  out <- the_curve$auc.integral
#  names(out) <- "AUPRC"
#  out
#}

#defining function to extract F1
#f1Summary <- function (data, lev = NULL, model = NULL) {
#  precision <- posPredValue(data$pred, data$obs, positive = "Yes")
#  recall  <- sensitivity(data$pred, data$obs, postive = "Yes")
#  f1_val <- (2 * precision * recall) / (precision + recall)
#  names(f1_val) <- c("F1")
#  f1_val
#}

#defining function to extract mcc
#mccSummary <- function (data, lev = NULL, model = NULL) 
#{
#  lvls <- levels(data$obs)
#  #if (length(lvls) > 2) 
#  #  stop(paste("Your outcome has", length(lvls), "levels. The twoClassSummary() function isn't appropriate."))
#  #requireNamespaceQuietStop("ModelMetrics")
#  #if (!all(levels(data[, "pred"]) == lvls)) 
#  #  stop("levels of observed and predicted data do not match")
#  mcc <- ModelMetrics::mcc(ifelse(data$obs == lev[2], 0, 
#                                  1), data[, lvls[1]], cutoff = .5)
#  out <- c(mcc)
#  names(out) <- c("MCC")
#  out
#}

#One summary function for roc,auprc,f1,and mcc
allSummary <- function (data, lev = NULL, model = NULL) {
  lvls <- levels(data$obs)

  #mcc
  mcc <- ModelMetrics::mcc(ifelse(data$obs == lev[2], 0, 1), data[, lvls[1]], cutoff = .5)

  #roc
  b1 <- twoClassSummary(data, lev, model)

  #auprc & f1
  c1 <- prSummary(data, lev, model)

  out <- c(mcc, b1, c1)
  names(out)[1] <- c("MCC")
  out
}

```

# GM12878 with distance type predictors

```{r}
sampling <- c("none", "ros", "rus", "smote")
resolution <- c("10kb", "25kb", "50kb", "100kb")
metric <- c("ROC", "AUC", "F", "MCC")

l=1
modelList <- list()

alpha_vals <- numeric()
lambda_vals <- numeric()
metric_vals <- character()
resample_vals <- character()
resolution_vals <- character()

for(i in 1:length(resolution)){

  #reading in whole genome data
  ##setting directory specific to cell line and resolution 
  wgd_directory <- paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/",
                          resolution[i],
                          "/training_testing/gm12878_",
                          resolution[i],
                          ".rds")
  whole_genome_dat <- readRDS(wgd_directory)

  #reading in bin data on the whole genome that contains chromosome information
  ##setting directory specific to cell line and resolution 
  bd_directory <- paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/",
                         resolution[i],
                         "/training_testing/binslist",
                         gsub("kb","",resolution[i]),
                         "_center.rds")
  binslist_dat <- readRDS(bd_directory)

  varstorm = c(names(whole_genome_dat)[grep("Ctcf-", names(whole_genome_dat))][-c(1:4)],
               names(whole_genome_dat)[grep("Ebf1sc137065-", names(whole_genome_dat))][-c(1:4)],
               names(whole_genome_dat)[grep("P300-", names(whole_genome_dat))][-c(1:4)],
               names(whole_genome_dat)[grep("Pol2-", names(whole_genome_dat))][-c(1:4)],
               names(whole_genome_dat)[grep("Rad21-", names(whole_genome_dat))][-c(1:4)])

  whole_genome_dat <- whole_genome_dat[,-which(names(whole_genome_dat) %in% varstorm)]

  #reducing the whole genome data to only specific chromosome
  reduce_chr <- "chr1"
  chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]

  #splitting into training and testing
  set.seed(123)
  inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
  train <- chr_specific_dat[inTrainingSet,]
  test <- chr_specific_dat[-inTrainingSet,]

  #reduce predictor space
  reduce_predictor = "_dist"
  train <- train[,c(1,grep(reduce_predictor, names(train)))]

  for(j in 1:length(sampling)){

    # set number of iterations
    samps = 50

    if(sampling[j]=="ros"){
      #assign sample indeces
      sampids <- matrix(ncol=samps, 
                        nrow=length(train$y[which(train$y=="No")]))

      #filling in the sample ids matrix
      set.seed(123)
      for(s in 1:samps){
        sampids[,s] <- sample(x = which(train$y=="Yes"),
                              size = length(which(train$y=="No")),
                              replace = TRUE)
      }
      train <- rbind.data.frame(train[which(train$y=="No"),],
                                train[sampids[,1],])
      #Randomly shuffle the data
      set.seed(321)
      train <- train[sample(nrow(train)),]
    }else if(sampling[j]=="rus"){
      #assign sample indeces
      sampids <- matrix(ncol=samps, 
                        nrow=length(train$y[which(train$y=="Yes")]))

      #filling in the sample ids matrix
      set.seed(123)
      for(s in 1:samps){
        sampids[,s] <- sample(x = which(train$y=="No"),
                              size = length(which(train$y=="Yes")),
                              replace = FALSE)
      }
      train <- rbind.data.frame(train[which(train$y=="Yes"),],
                                train[sampids[,1],])

      #Randomly shuffle the data
      set.seed(321)
      train <- train[sample(nrow(train)),]
    }else if(sampling[j]=="smote"){
      set.seed(123)
      train <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

      #Randomly shuffle the data
      set.seed(123)
      train <- train[sample(nrow(train)),]
    }else{train=train}

    for(k in 1:length(metric)){
      print(paste(i, j, k))

      #Feature Selection: ENET
      ##set up grid of alpha and lambda values
      lambda.grid = seq(0,10, length.out = 10)
      alpha.grid = seq(0,1,length=10)
      srchGrid <- expand.grid(.alpha=alpha.grid, .lambda=lambda.grid)

      ##set tuning parameters
      ##set seeds for each cross folds
      set.seed(123)
      #length is = (n_repeats*nresampling)+1
      seeds <- vector(mode = "list", length = 11)
      #(1 is the number of tuning parameter lambda
      for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 100)
      #for the last model
      seeds[[11]]<-sample.int(1000, 1)

      ##setting contols for elastic net
      fitControl <- trainControl(seeds = seeds,
                                 method = "cv",
                                 number = 10,
                                 ## Estimate class probabilities
                                 classProbs = TRUE,
                                 ## Evaluate performance using 
                                 ## the following function
                                 summaryFunction = allSummary)

      #running elastic net model
      eNetModel <- train(relevel(y, ref="Yes") ~ ., data=train, 
                         method = "glmnet", 
                         metric= metric[k], 
                         trControl = fitControl, 
                         family="binomial", 
                         tuneGrid=srchGrid,
                         standardize=FALSE)

      enetcoefs <- data.frame(Feature = gsub("`", "", rownames(coefficients(eNetModel$finalModel, s=eNetModel$bestTune$lambda))[-1]), 
                                                Coefficient = coefficients(eNetModel$finalModel, s=eNetModel$bestTune$lambda)[-1])

      #enetcoefs <- enetcoefs[-which(enetcoefs$Coefficient==0),]

      modelList[[l]] <- enetcoefs

      l <- l+1

      resolution_vals <- rbind(resolution_vals, resolution[i])
      resample_vals <- rbind(resample_vals, sampling[j])
      metric_vals <- rbind(metric_vals, metric[k])
      alpha_vals <- rbind(alpha_vals, as.numeric(eNetModel$bestTune[1])) 
      lambda_vals <- rbind(lambda_vals, as.numeric(eNetModel$bestTune[2])) 
    }
  }
}

saveRDS(modelList, "/home/stilianoudakisc/TAD_data_analysis/comparing_elastic_net_results/modelList.rds")

enet_df <- data.frame(Resolution = resolution_vals,
                      Resampling = resample_vals,
                      Metric = metric_vals,
                      Alpha = alpha_vals,
                      Lambda = lambda_vals)

saveRDS(enet_df, "/home/stilianoudakisc/TAD_data_analysis/comparing_elastic_net_results/enet_df.rds")
```

# Plots

### 2019-05-21 Manuscript/manuscript.Rmd
Add Spiro and MD abstracts side-by-side
An introductory paragraph on resolution gap - purpose of study

@@
 
-# ABSTRACT
+# ABSTRACT (Spiro version)
+
+**Background.** Topologically Associated Domains (TADs) represent fundamental building blocks of the three-dimensional (3D) genome organization and regulation.
+Several epigenetic marks, such as CTCF, are highly enriched at TAD boundaries, suggesting a strong epigenetic component of TAD boundary formation.
+Several methods have been developed to leverage the growing amount of (epi)genomic annotation data for predicting TAD boundaries; however, they overlooked key characteristics of the data, such as spatial associations between a genomic annotation and a boundary.
+Furthermore, the number of regions containing TAD boundaries is much smaller than the rest of the genome, creating a class imbalance problem.
+
+**Methods.** To investigate the problem of spatial genomic relationships and class imbalance problem, we developed an ensemble framework for optimizing prediction of TAD boundaries.
+We utilized several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) coupled with various metrics for classifier performance evaluation (Area Under Receiver Operating Characteristics (AUCROC) curve, Precision-Recall curve (AUPRC), F1, Matthew Correlation Coefficient (MCC), among others) to select the best predictive model in class imbalance settings.
+
+**Results.** Using different feature engineering and resampling strategies, coupled with elastic net-based feature selection, we systematically compared the performance of models predicting the location of TAD boundaries (Gm12878 and K562 Hi-C data at 10kb to 100kb resolutions).
+Precision-Recall curves were found to be best suited for evaluating model performance in class imbalance settings.
+Random undersampling and SMOTE-resampled data performed best for optimal parameter selection.
+Transcription Factor Binding Sites (TFBSs) were best type of genomic annotations for predicting TAD boundaries than histone modifications and chromatin states; we identified well-known CTCF, SMC3, RAD21, and several novel TFBSs as best predictors of TAD boundaries.
+Importantly, spatial relationships (distance between TAD boundaries and genomic annotations) were best predictors of TAD boundaries as compared with commonly used overlap counts or percent overlap measures.
+
+**Conclusions.** Our results outline strategies for predictive modeling of 3D genomic domains using 1D genome annotation data.
+The accurate modeling of TAD boundaries will improve our understanding of how epigenetics shapes the 3D structure of the genome.
+
+# ABSTRACT (MD version)
 
@@
 To date, no study has compared the results of their predictive models built across multiple data resolutions.
+
+[Paragraph about disconnect between Hi-C and epigenomic data] Despite the success of Hi-C technologies in revealing the high-order levels of genome organization (chromosome territories, A/B compartments, TADs, sub-TADs, chromatin loops), resolution of Hi-C data (~750kb [???
+REF, Bonev 2017?]) remains well below resolution of epigenomic assays (hundredths of bases for ChIP-seq).
+This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited out understanding of epigenomic regulation of gene expression and its potential link to chromatin architecture.
+One aim of this study is to predict the location of TAD boundaries on a scale comparable to epigenomic assays.
+For this, we developed a model trained on a relaticely coarse Hi-C data for predicting 3D features (TAD boundaries) from 1D data (epigenomic datasets).
 

### 2019-05-22 Scripts/comparing_distance_profiles_using_density_plots.Rmd
editted results scripts

@@
 
-#SMC3
 ggplot(all_dist_gm12878, aes(x = Resolution, y = value, fill = y)) +

### 2019-05-22 Scripts/evaluating_cv_metric_on_enet_penalization.Rmd
editted results scripts

@@
 # Plots
+
+```{r}
+enet_df <- readRDS("Z:/TAD_data_analysis/evaluating_cv_metric_on_enet_penalization/enet_df.rds")
+enet_df$Resolution <- c(rep("10 kb", 16),
+                        rep("25 kb", 16),
+                        rep("50 kb", 16),
+                        rep("100 kb", 16))
+enet_df$Resolution <- factor(enet_df$Resolution, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
+enet_df$Metric <- factor(enet_df$Metric, levels = c("ROC", "AUC", "F", "MCC"))
+
+#alpha
+all_enet_alpha <- ggplot(enet_df, aes(x=Resolution, y=Alpha, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Resampling) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        strip.text.x = element_text(size = 15))
+
+#lambda
+all_enet_lambda <- ggplot(enet_df, aes(x=Resolution, y=Lambda, fill=Metric)) +
+  geom_bar( stat="identity", position="dodge") +
+  facet_grid(~ Resampling) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        strip.text.x = element_text(size = 15))
+
+figure <- ggarrange(all_enet_alpha,
+                    all_enet_lambda,
+                    ncol=1,
+                    nrow=2,
+                    common.legend = TRUE,
+                    legend = "top")
+figure
+```

### 2019-05-22 Scripts/evaluating_enet_penalization_parameters.Rmd
editted results scripts

---
title: "evaluating_enet_penalization_parameters"
author: "Spiro Stilianoudakis"
date: "May 20, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Using AUPRC as CV metric

## Alpha: 0-1 length 100
## Lambda: 0-10 length 100

### GM12878

```{r}
alpha.per.chr <- numeric()
lambda.per.chr <- numeric()
chr.per.chr <- character()
res.per.chr <- character()
samp.per.chr <- character()
pred.per.chr <- character()

for(i in c("10kb", "25kb","50kb","100kb")){
  for(j in paste0("CHR", c(1:8,10:22))){
	  for(k in c("none","ros","rus","smote")){
		  for(l in c("distance", "oc", "op")){
		    print(paste(i, j, k, l))
			  enetmodel <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/",
			               i,
                     "/results_by_chr/",
									   j, 
									   "/",
									   k, 
									   "/", 
									   l, 
									   "/enet/eNetModel.rds"))

			  res.per.chr <- rbind(res.per.chr, i)
			  chr.per.chr <- rbind(chr.per.chr, j)
			  samp.per.chr <- rbind(samp.per.chr, k)
			  pred.per.chr <- rbind(pred.per.chr, l)

			  alpha.per.chr <- rbind(alpha.per.chr, as.numeric(enetmodel$bestTune[1])) 
        lambda.per.chr <- rbind(lambda.per.chr, as.numeric(enetmodel$bestTune[2])) 
		  }
	  }
  }
}

penal_params_gm12878 <- cbind.data.frame(Resolution = res.per.chr,
                                         CHR = chr.per.chr,
                                         Resampling = samp.per.chr,
                                         Predictor = pred.per.chr,
                                         Alpha = alpha.per.chr,
                                         Lambda = lambda.per.chr)

penal_params_gm12878$Resolution <- factor(penal_params_gm12878$Resolution, levels=c("10kb", "25kb", "50kb", "100kb"))
penal_params_gm12878$Predictor <- factor(penal_params_gm12878$Predictor, levels=c("oc","op","distance"))

penal_params_gm12878_summ <- penal_params_gm12878 %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(alpha = mean(Alpha, na.rm = TRUE),
            alphaSD = sd(Alpha, na.rm = TRUE),
            lambda = mean(Lambda, na.rm = TRUE),
            lambdaSD = sd(Lambda, na.rm = TRUE))

saveRDS(penal_params_gm12878_summ, "/home/stilianoudakisc/TAD_data_analysis/evaluating_alpha_and_lambda/penal_params_gm12878_summ.rds")	
```

### Plots

```{r}
penal_params_gm12878 <- readRDS("Z:/TAD_data_analysis/evaluating_alpha_and_lambda/penal_params_gm12878.rds")

penal_params_gm12878_summ <- penal_params_gm12878 %>%
  group_by(Resolution, Resampling, Predictor) %>%
  summarise(alpha = mean(Alpha, na.rm = TRUE),
            alphaSD = sd(Alpha, na.rm = TRUE),
            lambda = mean(Lambda, na.rm = TRUE),
            lambdaSD = sd(Lambda, na.rm = TRUE))

#alpha
ggplot(penal_params_gm12878_summ, aes(x=Resolution, y=alpha, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=alpha-alphaSD, ymax=alpha+alphaSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#lambda
ggplot(penal_params_gm12878_summ, aes(x=Resolution, y=lambda, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=lambda-lambdaSD, ymax=lambda+lambdaSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))
```

### K562

```{r}
alpha.per.chr <- numeric()
lambda.per.chr <- numeric()
chr.per.chr <- character()
res.per.chr <- character()
samp.per.chr <- character()
pred.per.chr <- character()

for(i in c("10kb", "25kb","50kb","100kb")){
  for(j in paste0("CHR", c(1:8,10:22))){
	  for(k in c("none","ros","rus","smote")){
		  for(l in c("distance", "oc", "op")){
		    print(paste(i, j, k, l))
			  enetmodel <- readRDS(paste0("Z:/TAD_data_analysis/K562/",
			               i,
                     "/results_by_chr/",
									   j, 
									   "/",
									   k, 
									   "/", 
									   l, 
									   "/enet/eNetModel.rds"))

			  res.per.chr <- rbind(res.per.chr, i)
			  chr.per.chr <- rbind(chr.per.chr, j)
			  samp.per.chr <- rbind(samp.per.chr, k)
			  pred.per.chr <- rbind(pred.per.chr, l)

			  alpha.per.chr <- rbind(alpha.per.chr, as.numeric(enetmodel$bestTune[1])) 
        lambda.per.chr <- rbind(lambda.per.chr, as.numeric(enetmodel$bestTune[2])) 
		  }
	  }
  }
}

penal_params_K562 <- cbind.data.frame(Resolution = res.per.chr,
                                         CHR = chr.per.chr,
                                         Resampling = samp.per.chr,
                                         Predictor = pred.per.chr,
                                         Alpha = alpha.per.chr,
                                         Lambda = lambda.per.chr)

penal_params_K562$Resolution <- factor(penal_params_K562$Resolution, levels=c("10kb", "25kb", "50kb", "100kb"))
penal_params_K562$Predictor <- factor(penal_params_K562$Predictor, levels=c("oc","op","distance"))

penal_params_K562_summ <- penal_params_K562 %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(alpha = mean(Alpha, na.rm = TRUE),
            alphaSD = sd(Alpha, na.rm = TRUE),
            lambda = mean(Lambda, na.rm = TRUE),
            lambdaSD = sd(Lambda, na.rm = TRUE))

saveRDS(penal_params_K562_summ, "/home/stilianoudakisc/TAD_data_analysis/evaluating_alpha_and_lambda/penal_params_K562_summ.rds")	
```

### Plots

```{r}
penal_params_K562 <- readRDS("Z:/TAD_data_analysis/evaluating_alpha_and_lambda/penal_params_K562.rds")

penal_params_K562_summ <- penal_params_K562 %>%
  group_by(Resolution, Resampling, Predictor) %>%
  summarise(alpha = mean(Alpha, na.rm = TRUE),
            alphaSD = sd(Alpha, na.rm = TRUE),
            lambda = mean(Lambda, na.rm = TRUE),
            lambdaSD = sd(Lambda, na.rm = TRUE))

#alpha
ggplot(penal_params_K562_summ, aes(x=Resolution, y=alpha, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=alpha-alphaSD, ymax=alpha+alphaSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#lambda
ggplot(penal_params_K562_summ, aes(x=Resolution, y=lambda, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=lambda-lambdaSD, ymax=lambda+lambdaSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))
```

### 2019-05-22 Manuscript/manuscript.Rmd
more wording

@@
 REF, Bonev 2017?]) remains well below resolution of epigenomic assays (hundredths of bases for ChIP-seq).
+One of the key missing pieces to connect 3D genome architecture to transcription has been the inability of Hi-C to attain the resolution necessary to discern gene-level features of chromatin.
 This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited out understanding of epigenomic regulation of gene expression and its potential link to chromatin architecture.
+Although computational [???
+REFS?] and technological [@Hsieh:2019aa] methods for enhancing resolution of Hi-C data started to appear, they [???
+remains to write about their pitfalls].
 One aim of this study is to predict the location of TAD boundaries on a scale comparable to epigenomic assays.

### 2019-05-22 Scripts/comparing_enet_and random_forest.Rmd
results scripts

---
title: "comparing_enet_and random_forest"
author: "Spiro Stilianoudakis"
date: "May 20, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Extracting chromosome specific elastic net model performances and variable importances

## GM12878

```{r}
m=1
performanceList <- list()
coefficientsList <- list()

for(i in c("10kb", "25kb","50kb","100kb")){
  for(j in paste0("CHR", c(1:8,10:22))){
	  for(k in c("none","ros","rus","smote")){
		  for(l in c("distance", "oc", "op")){
		    print(paste(i, j, k, l))

		    #read in elastic net model
		    enetmodel <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/",
			               i,
                     "/results_by_chr/",
									   j, 
									   "/",
									   k, 
									   "/", 
									   l, 
									   "/enet/eNetModel.rds"))

		    #establish training data to use to reduce test data features
		    train <- enetmodel$trainingData

		    #read in test data
		    test <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/",
                       i,
                       "/",
                       "training_testing/test.rds"))
		    test <- test[,c(1,which(names(test) %in% names(train)))]

		    #create matrix of performance metrics
	      enetperf <- data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)

	      pred.enetModel <- as.vector(predict(enetmodel, 
                                  newdata=test, 
                                  type="prob")[,"Yes"])

	      fg <- pred.enetModel[test$y == "Yes"]
	      bg <- pred.enetModel[test$y == "No"]
	      pr <- pr.curve(scores.class0 = fg, scores.class1 = bg, curve = T)

	      pred.enetModel2 <- predict(enetmodel,
                         newdata=test,
                         type="raw")

	      confMat <- confusionMatrix(data=pred.enetModel2, test$y, positive="Yes")
	      TN = as.numeric(confMat$table[1,1])
	      FN = as.numeric(confMat$table[1,2])
	      FP = as.numeric(confMat$table[2,1])
	      TP = as.numeric(confMat$table[2,2])
	      enetperf[1,2] <- TN
	      enetperf[2,2] <- FN
	      enetperf[3,2] <- FP
	      enetperf[4,2] <- TP
	      enetperf[5,2] <- sum(confMat$table)
	      enetperf[6,2] <- as.vector(confMat$byClass["Sensitivity"])
	      enetperf[7,2] <- as.vector(confMat$byClass["Specificity"])
	      enetperf[8,2] <- as.vector(confMat$overall["Kappa"])
	      enetperf[9,2] <- as.vector(confMat$overall["Accuracy"])
	      enetperf[10,2] <- TP/(TP+FP)
	      enetperf[11,2] <- FP/(FP+TN)
	      enetperf[12,2] <- FN/(FN+TN)
	      enetperf[13,2] <- FN/(FN+TN)
	      enetperf[14,2] <- TN/(TN+FN)
	      enetperf[15,2] <- (TP*TN - FP*FN)/( sqrt( (TP+FP)*(TP+FN)*(TN+FP)*(TN+FN) ) )
	      enetperf[16,2] <- (2*(TP/(TP+FN))*(TP/(TP+FP)))/((TP/(TP+FN)) + ((TP/(TP+FP))))
	      enetperf[17,2] <- pROC::auc(pROC::roc(test$y, pred.enetModel))			
	      enetperf[18,2] <- (TP/(TP + FN)) + (TN/(TN + FP)) - 1
	      enetperf[19,2] <- pr$auc.integral

	      performanceList[[m]] <- enetperf

	      enetcoefs <- data.frame(Feature = gsub("`", "", rownames(coefficients(enetmodel$finalModel,
	                                                                            s=enetmodel$bestTune$lambda))[-1]), 
                                                Coefficient = coefficients(enetmodel$finalModel,
                                                                           s=enetmodel$bestTune$lambda)[-1])

	      coefficientsList[[m]] <- enetcoefs

        m <- m+1

		  }
	  }
  }
}

saveRDS(performanceList, "/home/stilianoudakisc/TAD_data_analysis/comparing_enet_performances/performanceList_gm12878.rds")
saveRDS(coefficientsList, "/home/stilianoudakisc/TAD_data_analysis/comparing_enet_performances/coefficientsList_gm12878.rds")

```

### Model Performances

```{r}
performanceList_gm12878 <- readRDS("Z:/TAD_data_analysis/comparing_enet_performances/performanceList_gm12878.rds")

performanceList_gm12878 <- bind_rows(performanceList_gm12878)
performanceList_gm12878$CHR <- rep(c(rep("CHR1", 12*19),
                            rep("CHR2", 12*19),
                            rep("CHR3", 12*19),
                            rep("CHR4", 12*19),
                            rep("CHR5", 12*19),
                            rep("CHR6", 12*19),
                            rep("CHR7", 12*19),
                            rep("CHR8", 12*19),
                            rep("CHR10", 12*19),
                            rep("CHR11", 12*19),
                            rep("CHR12", 12*19),
                            rep("CHR13", 12*19),
                            rep("CHR14", 12*19),
                            rep("CHR15", 12*19),
                            rep("CHR16", 12*19),
                            rep("CHR17", 12*19),
                            rep("CHR18", 12*19),
                            rep("CHR19", 12*19),
                            rep("CHR20", 12*19),
                            rep("CHR21", 12*19),
                            rep("CHR22", 12*19)),4)
performanceList_gm12878$Resolution <- c(rep("10 kb", 4*3*21*19),
                                        rep("25 kb", 4*3*21*19),
                                        rep("50 kb", 4*3*21*19),
                                        rep("100 kb", 4*3*21*19))
performanceList_gm12878$Resampling <- rep(c(rep("None", 3*19),
                                        rep("ROS", 3*19),
                                        rep("RUS", 3*19),
                                        rep("SMOTE", 3*19)), 84)
performanceList_gm12878$Predictor <- rep(c(rep("Distance", 19),
                                       rep("OC", 19), 
                                       rep("OP", 19)), 336)

performanceList_gm12878$Resolution <- factor(performanceList_gm12878$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
performanceList_gm12878$Predictor <- factor(performanceList_gm12878$Predictor, levels=c("OC", "OP", "Distance"))

#MCC
all_enetperfs_mcc <- performanceList_gm12878[which(performanceList_gm12878$Metric=="MCC"),] %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(MCC = mean(Performance, na.rm = TRUE),
            MCCSD = sd(Performance, na.rm = TRUE))

ggplot(all_enetperfs_mcc, aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#F1
all_enetperfs_f1 <- performanceList_gm12878[which(performanceList_gm12878$Metric=="F1"),] %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(F1 = mean(Performance, na.rm = TRUE),
            F1SD = sd(Performance, na.rm = TRUE))

ggplot(all_enetperfs_f1, aes(x=Resolution, y=F1, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=F1-F1SD, ymax=F1+F1SD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#AUPRC
all_enetperfs_auprc <- performanceList_gm12878[which(performanceList_gm12878$Metric=="AUPRC"),] %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(AUPRC = mean(Performance, na.rm = TRUE),
            AUPRCSD = sd(Performance, na.rm = TRUE))

ggplot(all_enetperfs_auprc, aes(x=Resolution, y=AUPRC, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))
```

### Variable Importances

```{r}
coefficientsList_gm12878 <- readRDS("Z:/TAD_data_analysis/comparing_enet_performances/coefficientsList_gm12878.rds")

coefficientsList_gm12878 <- bind_rows(coefficientsList_gm12878)
coefficientsList_gm12878$CHR <- rep(c(rep("CHR1", 12*107),
                            rep("CHR2", 12*107),
                            rep("CHR3", 12*107),
                            rep("CHR4", 12*107),
                            rep("CHR5", 12*107),
                            rep("CHR6", 12*107),
                            rep("CHR7", 12*107),
                            rep("CHR8", 12*107),
                            rep("CHR10", 12*107),
                            rep("CHR11", 12*107),
                            rep("CHR12", 12*107),
                            rep("CHR13", 12*107),
                            rep("CHR14", 12*107),
                            rep("CHR15", 12*107),
                            rep("CHR16", 12*107),
                            rep("CHR17", 12*107),
                            rep("CHR18", 12*107),
                            rep("CHR19", 12*107),
                            rep("CHR20", 12*107),
                            rep("CHR21", 12*107),
                            rep("CHR22", 12*107)),4)
coefficientsList_gm12878$Resolution <- c(rep("10 kb", 4*3*21*107),
                                        rep("25 kb", 4*3*21*107),
                                        rep("50 kb", 4*3*21*107),
                                        rep("100 kb", 4*3*21*107))
coefficientsList_gm12878$Resampling <- rep(c(rep("None", 3*107),
                                        rep("ROS", 3*107),
                                        rep("RUS", 3*107),
                                        rep("SMOTE", 3*107)), 84)
coefficientsList_gm12878$Predictor <- rep(c(rep("Distance", 107),
                                       rep("OC", 107), 
                                       rep("OP", 107)), 336)

coefficientsList_gm12878$Resolution <- factor(coefficientsList_gm12878$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
coefficientsList_gm12878$Predictor <- factor(coefficientsList_gm12878$Predictor, levels=c("OC", "OP", "Distance"))

coefficientsList_gm12878_summ <- coefficientsList_gm12878 %>%
  dplyr::group_by(Resolution, Resampling, Predictor, Feature) %>%
  dplyr::summarise(Importance = mean(Coefficient, na.rm = TRUE),
            ImportanceSD = sd(Coefficient, na.rm = TRUE))

coefficientsList_gm12878_summ$Feature <- gsub(paste0(c("_perc", 
                                                     "_count", 
                                                     "_dist"),
                                                     collapse = "|"),
                                              "",
                                              coefficientsList_gm12878_summ$Feature)

#smote; distance types; tfbs
annots <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878")
annots <- gsub(".bed", "", annots)
coefficientsList_gm12878_summ <- coefficientsList_gm12878_summ[which(coefficientsList_gm12878_summ$Feature %in% annots), ]

coefficientsList_gm12878_summ$Feature <- gsub(paste0(c("Gm12878-",
                                                     "-Sydh",
                                                     "-Haib",
                                                     "-Broad"),
                                                     collapse = "|"),
                                              "",
                                              coefficientsList_gm12878_summ$Feature)

varimps_gm12878 <- coefficientsList_gm12878_summ[which(coefficientsList_gm12878_summ$Resampling=="SMOTE" & coefficientsList_gm12878_summ$Predictor=="Distance"),]
varimps_gm12878 <- varimps_gm12878[,c(1,4,5)]
varimps_gm12878 <- melt(varimps_gm12878)

varimps_gm12878_wide <- reshape(varimps_gm12878[,-3], idvar = "Feature", timevar = "Resolution", direction = "wide")

names(varimps_gm12878_wide) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
varimps_gm12878_wide[,-1] <- abs(varimps_gm12878_wide[,-1])
varimps_gm12878_wide <- varimps_gm12878_wide[order(varimps_gm12878_wide$ave10kb, decreasing = TRUE),]
varimps_gm12878_wide <- varimps_gm12878_wide[1:20,]
varimps_gm12878_melt <- melt(varimps_gm12878_wide)

ggplot(varimps_gm12878_melt, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("Resolution") +
  ylab("Transcription Factor") +
  scale_fill_gradient2(#limits=c(0,100),
                      low = "white",
                      mid = "pink",
                      #midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))
```

## K562

```{r}
m=1
performanceList <- list()
coefficientsList <- list()

for(i in c("10kb", "25kb","50kb","100kb")){
  for(j in paste0("CHR", c(1:8,10:22))){
	  for(k in c("none","ros","rus","smote")){
		  for(l in c("distance", "oc", "op")){
		    print(paste(i, j, k, l))

		    #read in elastic net model
		    enetmodel <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/",
			               i,
                     "/results_by_chr/",
									   j, 
									   "/",
									   k, 
									   "/", 
									   l, 
									   "/enet/eNetModel.rds"))

		    #establish training data to use to reduce test data features
		    train <- enetmodel$trainingData

		    #read in test data
		    test <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/",
                       i,
                       "/",
                       "training_testing/test.rds"))
		    test <- test[,c(1,which(names(test) %in% names(train)))]

		    #create matrix of performance metrics
			enetperf <- data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)

	      pred.enetModel <- as.vector(predict(enetmodel, 
                                  newdata=test, 
                                  type="prob")[,"Yes"])

	      fg <- pred.enetModel[test$y == "Yes"]
	      bg <- pred.enetModel[test$y == "No"]
	      pr <- pr.curve(scores.class0 = fg, scores.class1 = bg, curve = T)

	      pred.enetModel2 <- predict(enetmodel,
                         newdata=test,
                         type="raw")

	      confMat <- confusionMatrix(data=pred.enetModel2, test$y, positive="Yes")
	      TN = as.numeric(confMat$table[1,1])
	      FN = as.numeric(confMat$table[1,2])
	      FP = as.numeric(confMat$table[2,1])
	      TP = as.numeric(confMat$table[2,2])
	      enetperf[1,2] <- TN
	      enetperf[2,2] <- FN
	      enetperf[3,2] <- FP
	      enetperf[4,2] <- TP
	      enetperf[5,2] <- sum(confMat$table)
	      enetperf[6,2] <- as.vector(confMat$byClass["Sensitivity"])
	      enetperf[7,2] <- as.vector(confMat$byClass["Specificity"])
	      enetperf[8,2] <- as.vector(confMat$overall["Kappa"])
	      enetperf[9,2] <- as.vector(confMat$overall["Accuracy"])
	      enetperf[10,2] <- TP/(TP+FP)
	      enetperf[11,2] <- FP/(FP+TN)
	      enetperf[12,2] <- FN/(FN+TN)
	      enetperf[13,2] <- FN/(FN+TN)
	      enetperf[14,2] <- TN/(TN+FN)
	      enetperf[15,2] <- (TP*TN - FP*FN)/( sqrt( (TP+FP)*(TP+FN)*(TN+FP)*(TN+FN) ) )
	      enetperf[16,2] <- (2*(TP/(TP+FN))*(TP/(TP+FP)))/((TP/(TP+FN)) + ((TP/(TP+FP))))
	      enetperf[17,2] <- pROC::auc(pROC::roc(test$y, pred.enetModel))			
	      enetperf[18,2] <- (TP/(TP + FN)) + (TN/(TN + FP)) - 1
	      enetperf[19,2] <- pr$auc.integral

	      performanceList[[m]] <- enetperf

	      enetcoefs <- data.frame(Feature = gsub("`", "", rownames(coefficients(enetmodel$finalModel,
	                                                                            s=enetmodel$bestTune$lambda))[-1]), 
                                                Coefficient = coefficients(enetmodel$finalModel,
                                                                           s=enetmodel$bestTune$lambda)[-1])

	      coefficientsList[[m]] <- enetcoefs

        m <- m+1

		  }
	  }
  }
}

saveRDS(performanceList, "/home/stilianoudakisc/TAD_data_analysis/comparing_enet_performances/performanceList_K562.rds")
saveRDS(coefficientsList, "/home/stilianoudakisc/TAD_data_analysis/comparing_enet_performances/coefficientsList_K562.rds")
```

### 2019-05-22 Papers.Rmd
Add note that  CTCF is not at TAD boundaries, but nearby
Add Twitter tread on class imbalance

@@
 
+- Krietenstein, Nils, Sameer Abraham, Sergey Venev, Nezar Abdennur, Johan Gibcus, Tsung-Han Hsieh, Krishna Mohan Parsi, et al.
+“Ultrastructural Details of Mammalian Chromosome Architecture.” Preprint.
+Genomics, May 17, 2019.
+https://doi.org/10.1101/639922.
+- Micro-C (MNase digestion Hi-C) technology and basic analysis.
+human embryonic stem cells H1-ESC and differentiated human foreskin fibroblasts (HFFc6).
+Captures standard Hi-C features, with many additional interaction peaks ("dots").
+Enrichment of classical marks of TAD boundaries (Fig 3C) - RAD21, TAF1, PHF8, CTCF, TBP, POL2RA, YY1, and more.
+
 ## Epigenomic predictions
@@
 ## Prediction, general
+
+- Twitter tread on class imbalance, https://twitter.com/goodfellow_ian/status/1127994332416364549
 
@@
 Characterization of hubs - enriched in CTCF, cohesin, disease-associated variants,
+
+- CTCF is not at TAD boundaries, but nearby. "only 15% CTCF sites are at the TAD boundary while 85% CTCF sites are inside the TAD [@Ong:2014aa]."

### 2019-05-22 Papers.Rmd
Add Wei and Dunbrack paper on class imbalance

@@
 
+- Wei, Qiong, and Roland L.
+Dunbrack.
+“The Role of Balanced Training and Testing Data Sets for Binary Classifiers in Bioinformatics.” PloS One 8, no.
+7 (2013): e67863.
+https://doi.org/10.1371/journal.pone.0067863.
+- Class imbalance.
+Intro into the problem, methods for addressing class imbalance.
+Balanced _training_ set is crucial for the best classifier performance, balanced _test_set also helps to improve the results.
+AUROC is not sensitive to class imbalance, MCC is.
+Illustrated on predicting missense mutations.
+
 - Wallace, Byron C., Kevin Small, Carla E.

### 2019-05-22 Scripts/comparing_distance_profiles_using_density_plots.Rmd
results scripts

@@
 library(coin)
+library(ggsignif)
 ```
@@
 
-ggplot(all_dist_gm12878, aes(x = Resolution, y = value, fill = y)) +
+# 10 kb
+all_dist_gm12878_10kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="10 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
   stat_boxplot(geom = "errorbar") +
-  geom_boxplot(#fill = fill, 
-               #colour = line,
-               outlier.shape = NA) +
-  facet_grid(~ variable) +
-  xlab("Resolution") +
-  ylab("Log2 Distances") +
-  ylim(5,25) +
-  scale_fill_discrete(name="Class of Genomic Bin",
-                      labels=c("Did not overlap\nw/ flanked TAD boundary",
-                               "Overlapped\nw/ flanked TAD boundary")) +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("Transcription Factor\nBinding Site") +
+  ylab("Log2 Distance") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
   #guides(color=FALSE) +
@@
   theme_bw() +
-  theme(axis.text.x = element_text(size=15,
-                                   angle = 45, 
+  theme(axis.text.x = element_text(size=15#,
+                                   #angle = 45, 
                                    #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
+                                   #hjust = 1
+                                   ),
         axis.text.y = element_text(size = 15),
@@
         strip.text.x = element_text(size = 15))
+
+# 25 kb
+all_dist_gm12878_25kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="25 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
+  #guides(color=FALSE) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15#,
+                                   #angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   #hjust = 1
+                                   ),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        strip.text.x = element_text(size = 15))
+
+# 50 kb
+all_dist_gm12878_50kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="50 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
+  #guides(color=FALSE) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15#,
+                                   #angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   #hjust = 1
+                                   ),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        strip.text.x = element_text(size = 15))
+
+# 100 kb
+all_dist_gm12878_100kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="100 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
+  #guides(color=FALSE) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15#,
+                                   #angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   #hjust = 1
+                                   ),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        strip.text.x = element_text(size = 15))
+
+figure <- ggarrange(all_dist_gm12878_25kb,
+                    all_dist_gm12878_50kb,
+                    all_dist_gm12878_100kb,
+                    ncol = 1,
+                    nrow = 3,
+                    common.legend = TRUE,
+                    legend = "top",
+                    labels = "AUTO",
+                    font.label = list(size=20))
+figure 
+annotate_figure(figure, 
+                bottom = text_grob("Transcription Factor\nBinding Site", color = "black", size = 20),
+                left = text_grob("Log2 Distance", color = "black", size = 20, rot=90))
 ```
@@
 
-ggplot(all_dist_K562, aes(x = Resolution, y = value, fill = y)) +
+# 10 kb
+all_dist_K562_10kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="10 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
   stat_boxplot(geom = "errorbar") +
-  geom_boxplot(#fill = fill, 
-               #colour = line,
-               outlier.shape = NA) +
-  facet_grid(~ variable) +
-  xlab("Resolution") +
-  ylab("Log2 Distances") +
-  ylim(5,25) +
-  scale_fill_discrete(name="Class of Genomic Bin",
-                      labels=c("Did not overlap\nw/ flanked TAD boundary",
-                               "Overlapped\nw/ flanked TAD boundary")) +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
   #guides(color=FALSE) +
@@
         strip.text.x = element_text(size = 15))
+
+# 25 kb
+all_dist_K562_25kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="25 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
+  #guides(color=FALSE) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15#,
+                                   #angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   #hjust = 1
+                                   ),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        strip.text.x = element_text(size = 15))
+
+# 50 kb
+all_dist_K562_50kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="50 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
+  #guides(color=FALSE) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15#,
+                                   #angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   #hjust = 1
+                                   ),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        strip.text.x = element_text(size = 15))
+
+# 100 kb
+all_dist_K562_100kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="100 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
+  #guides(color=FALSE) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15#,
+                                   #angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   #hjust = 1
+                                   ),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        strip.text.x = element_text(size = 15))
+
+figure <- ggarrange(all_dist_K562_10kb,
+                    all_dist_K562_25kb,
+                    all_dist_K562_50kb,
+                    all_dist_K562_100kb,
+                    ncol = 2,
+                    nrow = 2,
+                    common.legend = TRUE,
+                    legend = "top",
+                    labels = "AUTO",
+                    font.label = list(size=20))
+figure 
+annotate_figure(figure, 
+                bottom = text_grob("Transcription Factor\nBinding Site", color = "black", size = 20),
+                left = text_grob("Log2 Distance", color = "black", size = 20, rot=90))
 ```

### 2019-05-22 Scripts/comparing_enet_and random_forest.Rmd
results scripts

@@
 
-ggplot(all_enetperfs_mcc, aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+mccplot <- ggplot(all_enetperfs_mcc, aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
      geom_line(size=2, position=position_dodge(0.5))+
@@
 
-ggplot(all_enetperfs_f1, aes(x=Resolution, y=F1, color=Resampling, group=Resampling)) +
+f1plot <- ggplot(all_enetperfs_f1, aes(x=Resolution, y=F1, color=Resampling, group=Resampling)) +
      geom_line(size=2, position=position_dodge(0.5))+
@@
 
-ggplot(all_enetperfs_auprc, aes(x=Resolution, y=AUPRC, color=Resampling, group=Resampling)) +
+auprcplot <- ggplot(all_enetperfs_auprc, aes(x=Resolution, y=AUPRC, color=Resampling, group=Resampling)) +
      geom_line(size=2, position=position_dodge(0.5))+
@@
      plot.title = element_text(size=20))
+
+figure <- ggarrange(mccplot,
+                    f1plot,
+                    auprcplot,
+                    ncol=1,
+                    nrow=3,
+                    common.legend = TRUE,
+                    legend = "top")
+figure
 ```

### 2019-05-22 Scripts/evaluating_enet_penalization_parameters.Rmd
results scripts

@@
 #alpha
-ggplot(penal_params_gm12878_summ, aes(x=Resolution, y=alpha, color=Resampling, group=Resampling)) +
+alphaplot <- ggplot(penal_params_gm12878_summ, aes(x=Resolution, y=alpha, color=Resampling, group=Resampling)) +
      geom_line(size=2, position=position_dodge(0.5))+
@@
      theme_bw()+
-     xlab("") + ylab("") + #ylim(-.05,.5) +
+     #xlab("") + ylab("") + #ylim(-.05,.5) +
      scale_color_discrete(name="Resampling Technique")+
@@
 #lambda
-ggplot(penal_params_gm12878_summ, aes(x=Resolution, y=lambda, color=Resampling, group=Resampling)) +
+lambdaplot <- ggplot(penal_params_gm12878_summ, aes(x=Resolution, y=lambda, color=Resampling, group=Resampling)) +
      geom_line(size=2, position=position_dodge(0.5))+
@@
      plot.title = element_text(size=20))
+
+figure <- ggarrange(alphaplot,
+                    lambdaplot,
+                    ncol = 1,
+                    nrow = 2,
+                    common.legend = TRUE,
+                    legend = "top")
+figure
 ```

### 2019-05-22 Scripts/evaluating_imbalance_ratios.Rmd
results script

@@
             AveIRSD = sd(ir, na.rm = TRUE))
+
+irtab_summ_med <- irtab %>%
+  group_by(cl, res) %>%
+  dplyr::summarise(MedBins = median(bins, na.rm = TRUE),
+            MedBinsIQR = IQR(bins, na.rm = TRUE),
+            MedTADs = median(tads, na.rm = TRUE),
+            MedTADsIQR = IQR(tads, na.rm = TRUE),
+            MedBounds = median(bounds, na.rm = TRUE),
+            MedBoundsIQR = IQR(bounds, na.rm = TRUE),
+            MedIR = median(ir, na.rm = TRUE),
+            MedIRIQR = IQR(ir, na.rm = TRUE))
 ```

### 2019-05-23 Manuscript/manuscript.Rmd
manuscrpt edits

@@
 
-<!--Additional threshold-free metrics where also reported including the AUROC and AUPRC.-->
+## ENSEMBLE FRAMEWORK & COMPARISONS
 
-<!--
-Lastly, for the task of identifying the genomic annotations that were most predictive of the formation of TAD boundaries, we ranked the variable importances associated with each feature of the ensemble system-specific random forest model.
-To calculate variable importances for each model, the F1-Score on the out-of-bag portion of the data within each tree was recorded.
-Then the same was done after permuting each predictor variable.
-The difference between the two AUPRC values was then averaged over all trees, and normalized by the standard error of the differences.
-Annotations with low rankings correspond to functional epigenomic features that are either positively or negatively enriched near TAD boundaries, and thus, better allow the model to discriminate between genomic bins that overlap with flanked TAD boundaries.
--->
-
-## ENSEMBLE FRAMEWORK
-
-An ensemble framework was then established for the purposes of systematically creating a variety of models that each included different sets of parameters described above <!--(Figure 2)-->.
-Each system in the framework is assumed to be composed of a model constructed from a particular cell line and data resolution, with a particular predictor type for the feature space.
-The data sets used for modeling were composed of the full set of genomic bins that either overlapped with a flanked TAD boundary or did not.
-The data was then split into a 7:3 ratio of training to testing sets.
-For the task of performance evaluation and prediction, the test set remained constant for all ensemble systems to account for an unbiased comparison.
-Furthermore, this process was repeated, and performances were aggregated across each autosomal chromosome (omitting chromosome 9) using means and standard deviations.
+To systematically summarize and compare our results, we created an ensemble framework.
+Each system in the framework was assumed to be composed of a model constructed from a particular cell line, $L = \{GM12878, K562\}$.
+Within each cell line we evaluated 4 data resolutions, $R = \{10 kb, 25 kb, 50 kb, 100 kb\}$.
+We then considered 3 separate predictor types as the feature space including $P = \{OC, OP, Distance\}$.
+The cell line- and resolution-specific data was then split into a 7:3 ratio of training to testing sets.
+Furthermore, for the task of performance evaluation and prediction, the test set remained constant for all ensemble systems to account for an unbiased comparison.
+To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including $B = \{None, RUS, ROS, SMOTE\}$.
+Each combination of the above parameters was implemented on chromosome specific sections of the linear genome, and thus, was repeated repeated 21 times (number of autosomal chromosomes, excluding chromosome 9).
+Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling 2016 ($2 \times 4 \times 3 \times 4 \times 21$) separate models.
+Performances were then aggregated across each of the 21 chromosomes (omitting chromosome 9; see Methods).
+We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.
 
@@
 
-## THE PROPOSED MODEL
+## IMBALANCE RATIOS REMAINED SEVERE irrespectively of RESOLUTION of Hi-C data
 
-We illustrate a unified approach toward preparing TAD boundary data for predictive modelling purposes from different cell lines and data resolutions (Figure 1).
-To enable us to build a model that suitably discriminates between regions on the linear genome that are near TAD boundaries and regions that are not, we created a cell line- and resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$).
-The unit width of each bin on the linear genome corresponded to the resolution of the contact matrix on which domains were called.
-Moreover, to account for uncertainty in boundary location, TAD boundaries were flanked on either side by the same unit length as the genomic bins.
+We analyzed publically available Hi-C data sets for the GM12878 and K562 cell lines provided by Rao et al.
+[@rao20143d].
+Topologically associating domains were then identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions, for each cell line respectively.
+We then established a unified approach toward preparing cell line specific TAD boundary data for predictive modelling purposes, irrespective of data resolutions (Figure 1).
+
+To enable us to build a model that suitably discriminated between regions on the linear genome that were near TAD boundaries and regions that were not, we created a  resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$).
+The unit width of each bin on the linear genome corresponded to the resolution of the cell line specific contact matrix on which domains were called.
+Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.
+
+Expectedly, the average number of genomic bins, TADs called, and TAD boundaries increased with the increased resolution of cell-line specific Hi-C data (Table 1; Supplementary Tables 3).
+This correlation with resolution was found to be significant, as evidenced by large intraclass correllation coefficients (ICC) (Table 2; Supplementary Tables 4).
+However, the class imbalance problem was found to be much more consistant across resolutions in both cell lines.
+The sparsity of TAD boundaries throughout the genome was found to contribute to heavily imbalanced classes.
+This imbalance was evidenced by low imbalance ratios, defined as the ratio of the number of genomic bins that overlapped with flanked TAD boundaries ($Y=1$), to the much larger number of genomic bins that did not ($Y=0$).
+This relationship was not significantly correlated with resoltuion for either cell line, indicating that there existed a severe disparity between classes at all resolutions of Hi-C data.
+[???
+Very bad and boring.
+You should tell the STORY, not the report.
+E.g., "Expectedly, the average number of genomic bins, TADs, and TAD boundaries increased with the increased resolution of Hi-C data (Table 1).
+However, the imbalance ratio, defined as ..., remained severe (~XXX) at all resolutions (Table 1).
+In summary, the problem of class imbalance exists at all resolutions of Hi-C data."; !!!
+editted]
 
@@
 E.g., distance definition is crucial for understanding results, the fact of log2-transformation is Methods.]
-
-## ENSEMBLE COMPARISONS
-
-We then developed an ensemble framework to systematically compare and establish the best set of data level characteristics for predicting TAD boundaries using random forest classifiers [???
-Do we need RF?] built on cell line specific functional genomic annotations (Figure 3).
-TAD boundaries were called using the Arrowhead algorithm [@durand2016juicebox] from replicate Hi-C data for 2 cell lines $L = \{GM12878, K562\}$, at four different resolutions $R = \{10 kb, 25 kb, 50 kb, 100 kb\}$.
-For each classifier, we considered 3 separate predictor types as the feature space including $P = \{OC, OP, Distance\}$.
-To assess the severity of class imbalance, four re-sampling techniques were implemented prior to modelling, including $B = \{None, RUS, ROS, SMOTE\}$.
-Each combination of the above parameters was implemented on chromosome specific sections of the linear genome, and thus, was repeated repeated 21 times (number of autosomal chromosomes, excluding chromosome 9 [???
-In Methods, not here, you should explain why]), $C = \{1, 2, ..., 22\}$.
-A system produced from the ensemble framework was defined as: $S = \{c, r, p, b\}$, where $l \in L$, $r \in R$, $p \in P$, $b \in B$, and $c \in C$.
-Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling 2016 ($2 \times 4 \times 3 \times 4 \times 21$) separate models.
-Performances were then aggregated across each of the 21 chromosomes (omitting chromosome 9; see Methods).
-We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.
-[???
-This is Methods.
-What is so compelling about those 'results' for the message you try to prove?] [???
-Currently, Methods and the results are redundant.
-Look how others present their models in the results section, and how methods section is structured in such cases.
-Specifically, some key definitions, like OC, OP, Distance should be solidly introduced in the results section, while log2 status of distance and supplementary figure 1 description are for methods]
-
-## IMBALANCE RATIOS REMAINED SEVERE irrespectively of RESOLUTION of Hi-C data
-
-[???probably better to report medians here]
-Expectedly, the average number of genomic bins, TADs called, and TAD boundaries increased with the increased resolution of cell-line specific Hi-C data (Table 1; Supplementary Tables 3).
-The correlation of each cell-line specific quantity with resolution was found to be significant, as evidenced by large intraclass correllation coefficients (ICC) (Table 2; Supplementary Tables 4).
-However, the class imbalance problem was found to be much more consistant across resolutions in both cell lines.
-Likewise, this relationship was not significantly correlated with resoltuion for either cell line, indicating that there exists a severe disparity between classes at all resolutions of Hi-C data.
-
-[???
-Very bad and boring.
-You should tell the STORY, not the report.
-E.g., "Expectedly, the average number of genomic bins, TADs, and TAD boundaries increased with the increased resolution of Hi-C data (Table 1).
-However, the imbalance ratio, defined as ..., remained severe (~XXX) at all resolutions (Table 1).
-In summary, the problem of class imbalance exists at all resolutions of Hi-C data."; !!!
-editted]
 

### 2019-05-23 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution for the corresponding contact matrix <!--(Figure 1)-->.
+To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution for the corresponding contact matrix.
 As an example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
@@
 
-Using the sets of genomic annotations, we created three types of predictors that were used as features for subsequent models to analyze their respective spatial relationship with TAD boundaries <!--(Figure 3)-->:
+Using the sets of genomic annotations, we created three types of predictors that were used as features for subsequent models to analyze their respective spatial relationship with TAD boundaries:
 
@@
 
-To systematically summarize and compare our results, we created an ensemble framework.
+To systematically summarize and compare our results of data driven random forest models, we created an ensemble framework (Figure 1).
 Each system in the framework was assumed to be composed of a model constructed from a particular cell line, $L = \{GM12878, K562\}$.
@@
 
-We analyzed publically available Hi-C data sets for the GM12878 and K562 cell lines provided by Rao et al.
+We analyzed publically available Hi-C data for the GM12878 and K562 cell lines provided by Rao et al.
 [@rao20143d].
 Topologically associating domains were then identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions, for each cell line respectively.
-We then established a unified approach toward preparing cell line specific TAD boundary data for predictive modelling purposes, irrespective of data resolutions (Figure 1).
+We then established a unified approach toward preparing cell line -specific TAD boundary data for predictive modelling purposes, irrespective of data resolutions (Figure 2).
 
@@
 
-Expectedly, the average number of genomic bins, TADs called, and TAD boundaries increased with the increased resolution of cell-line specific Hi-C data (Table 1; Supplementary Tables 3).
+Expectedly, the median number of genomic bins, TADs called, and TAD boundaries increased with the increased resolution of cell-line specific Hi-C data (Table 1; Supplementary Tables 3).
 This correlation with resolution was found to be significant, as evidenced by large intraclass correllation coefficients (ICC) (Table 2; Supplementary Tables 4).
@@
 
-To investigate the relationship between functional genomic annotations and the development of TAD boundaries, we devised 3 different predictor-types that composed the feature space of downstream random forest classification models.
-These predictor-type specific annotations represented the data matrix, $X = \{X_1, X_2, ..., X_p\}$, where $p$ is the complete set of functional annotations.
-Overlap counts was the least granular predictor-type considered, simply defined by the number of annotation-specific regions located within each genomic bin (Figure 2A).
-Overlap percents was a more refined predictor-type, defined as the total percent overlap between each annotation-specific region and genomic bins (Figure 2B).
-Lastly, distances, the most granular predictor-type, described the spatial relationship between the center of each genomic bin to the center of the nearest annotation-specific region (Figure 2C).
-<!--When measured in basepairs, distances were found to be highly skewed across all resolutions, for both the GM12878 and K562 cell lines (Supplementary Figures 1-2 A-D).--> As a normalization procedure, we performed a $log_{2}$ transformation on the distances prior to modelling (See Methods Section).
-[???
-Introduce all definitions in Results.
-Put all details in Methods.
-E.g., distance definition is crucial for understanding results, the fact of log2-transformation is Methods.]
-
 ## HIGH JACCARD INDICES IMPLY COLOCALIZATION OF MANY GROUP-SPECIFC ANNOTATIONS
 
-Using the Jaccard index, we were able to determine which group-specific annotations were enriched together on the linear genome.
-As could be expected, for GM12878, the class of 14 annotations segmenting the chromation into different states exhibited very low pairwise correlations, with a Jaccard index range of (0-0.001) (Table 3).
-However, specific sets of pairwise histone modifications and transcription factor binding sites (TFBS) were found to be highly enriched.
-The range of Jaccard indices for the 10 histone modifications was found to be (0.022-0.539).
+The influences of TAD boundaries were assessed using functional genomic annotations, derived by ChIP-seq peak algorithms.
+Specific groups of annotations were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] and included chromatin state segementations, histone modifications, and transcription factor binding sites (TFBS).
+
+Using the Jaccard index, we found that specific sets of these cell line-specific annotations were highly colocalized together on the linear genome (Table 3).
+For GM12878, the range of Jaccard indices for the 10 histone modifications was found to be (0.022-0.539).
 Specifically, H3k27ac, H3k4me1, H3k4me2, and H3k4me3 were found to be highly correlated, high levels of which have been detected surrounding transcription start sites [@barski2007high].
-For the 79 TFBS, the range of Jaccard indices was (<0.001-0.425).
+Likewise, for the 79 TFBS, the range of Jaccard indices was (<0.001-0.425).
 Here, known mediators of loop extrusion components were found to have high pairwise correlations including CTCF, RAD21, and SMC3 [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
@@
 So what?
-Why did you talk about it?] <!--The high Jaccard indices among select sets of genomic annotations gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space while retaining possibly correlated annotations that could be predictive of TAD boundary formation.-->
+Why did you talk about it?; !!!added implication].
+The high Jaccard indices among select sets of genomic annotations indicated the colocalization of annotations known to be enriched at TAD boundaries.
+This gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space of all annotations while retaining the possibly correlated annotations that could be predictive of TAD boundary formation.
+
+We then investigated the relationship between the functional genomic annotations and the development of TAD boundaries by devising 3 different predictor-types that composed the feature space of downstream random forest classification models.
+These predictor-type specific annotations represented the data matrix, $X = \{X_1, X_2, ..., X_p\}$, where $p$ is the complete set of functional annotations.
+Overlap counts was the least granular predictor-type considered, simply defined by the number of annotation-specific regions located within each genomic bin (Figure 3A).
+Overlap percents was a more refined predictor-type, defined as the total percent overlap between each annotation-specific region and genomic bins (Figure 3B).
+Lastly, distances, the most granular predictor-type, described the spatial relationship between the center of each genomic bin to the center of the nearest annotation-specific region (Figure 3C).
 

### 2019-05-23 Manuscript/manuscript.Rmd
manuscript edits

@@
 We then sought to determine which of the transcription factor binding sites were most influential in predicting TAD boundaries.
-We found that the cell line specific binding sites associated with SMC3, CTCF, RAD21, ZNF143, and YY1 were given consistently high predictive importance, across all resolutions (Figure 7; Supplementary Figure 6).
+We found that the cell line specific binding sites associated with SMC3, CTCF, RAD21, ZNF143, and YY1sc281 were given consistently high predictive importance, across all resolutions (Figure 7; Supplementary Figure 6).
 The SMC3, CTCF, and RAD21 binding sites are known factors associated with the cohesin protein complex, which is hypothesized to be what creates loops in the DNA  [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
@@
 
-<!--
-## DISTANCE PROFILES HIGHLIGHT THE RELATIONSHIP BETWEEN KEY TFBS AND TAD BOUNDARIES
+## INFLUENTIAL TFBS TENDED TO BE CLOSER TO BINS THAT OVERLAPPED WITH FLANKED TAD BOUNDARIES THAN THOSE THAT DID NOT
 
-When evaluating the 10 kb data resolution, on GM12878, the distance profiles (on a $log_{2}$ scale) were found to be smaller for top predictive TFBS annotations in relation to genomic bins that overlapped with flanked TAD boundaries, when compared to bins that did not overlap with a flanked TAD boundary (Figure 7).
-At the same resolution and cell line, direct comparisons of quantiles obtained from the distribution of distances for the transcription factors SMC3a, ZNF143, CTCF, and RAD21, led to the the conclusion that these TFBS were more often located near TAD boundaries on the linear genome, as can be seen from the shifted quantile differences (Figure 7).
-Similar distance profiles for the same TFBS were obtained when assessed at lower resolutions, across both cell lines (Supplementary Figures 12-17 A-D).
--->
-
+We then investigated the spatial patterns of the most predictive TFBS around TAD boudaries by characterizing the distance profiles between the classes of genomic bins.
+For GM12878, at 10 kb resolution, we found that SMC3, CTCF, RAD21, ZNF143, and YY1sc281 were all statistically significantly closer to bins that overlapped with flanked TAD boudaries than those that did not (Figure 8).
+Although still statistically significantly different, the distance profiles between genomic class were found to be much more similar at lower resolutions (Supplementary 9).
+For the K562 cell line, we reported the distance profiles of the same transcription factor binding sites, excluding the YY1sc281, due to its unavailability in the UCSC Genome Browser.
+These cell line specific distance profiles were again found to be significantly different between genomic class, at all resolutions (Supplementary 10).
 # DISCUSSION

### 2019-05-28 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-**Methods.** To investigate the problem of spatial genomic relationships and class imbalance problem, we developed an ensemble framework for optimizing prediction of TAD boundaries.
-We utilized several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) coupled with various metrics for classifier performance evaluation (Area Under Receiver Operating Characteristics (AUCROC) curve, Precision-Recall curve (AUPRC), F1, Matthew Correlation Coefficient (MCC), among others) to select the best predictive model in class imbalance settings.
+**Methods.** To investigate the problem of spatial genomic relationships and class imbalance, we developed an ensemble framework for optimizing prediction of TAD boundaries.
+We utilized several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) coupled with various metrics for classifier performance evaluation (Area Under Receiver Operating Characteristics (AUROC) curve, Precision-Recall curve (AUPRC), F1, Matthews Correlation Coefficient (MCC), among others) to select the best predictive model in class imbalance settings.
 
@@
 Random undersampling and SMOTE-resampled data performed best for optimal parameter selection.
-Transcription Factor Binding Sites (TFBSs) were best type of genomic annotations for predicting TAD boundaries than histone modifications and chromatin states; we identified well-known CTCF, SMC3, RAD21, and several novel TFBSs as best predictors of TAD boundaries.
+Transcription Factor Binding Sites (TFBSs) were the best type of genomic annotations for predicting TAD boundaries when directly compared with histone modifications and chromatin states; we identified well-known CTCF, SMC3, RAD21, and several novel TFBSs as best predictors of TAD boundaries.
 Importantly, spatial relationships (distance between TAD boundaries and genomic annotations) were best predictors of TAD boundaries as compared with commonly used overlap counts or percent overlap measures.
@@
 nonboundary regions.
-In a classification setting, when one is attempting to discriminate between regions with (minority class) and without (majority class) TAD boundaries, the class imbalance issue will contribute to small imbalance ratios.
+In a classification setting, when one is attempting to discriminate between minority (regions with TAD boundaries) and majority classes (regions without TAD boundaries), the class imbalance issue will contribute to small imbalance ratios.
 The imbalance ratio is defined as the ratio of minority to majority classes [@Orriols-Puig2008].
@@
 However, the class imbalance issue was not addressed.
-Even worse, when performing cross-validation [@mourad2016computational], used the misclassification error rate of the model to establish the optimal L1-regularization lambda.
+Even worse, when performing cross-validation, [@mourad2016computational] used the misclassification error rate of the model to establish the optimal L1-regularization lambda.
 They also reported ROC (receiver operating characteristic) curves and subsequent AUC (area under the curve) as measures of their model's performance.
@@
 However, given the large disparity between the number of genomic regions labeled as containing a TAD boundary or not, performing random under-sampling alone is likely to be unstable and introduce bias.
-Also, it is unclear how other data level solution compare to simple random under-sampling, for instance random over-sampling or a weighted combination of both random under- and over-sampling together.
+Also, it is unclear how other data level solutions compare to simple random under-sampling, for instance random over-sampling or a weighted combination of both random under- and over-sampling together.
 Equally concerning is how the test set is treated in scenarios of re-sampling.
@@
 g., 60% of a TAD boundary region may overlap with a genomic region annotated as heterochromatin.
-While direct overlaps represent the most straightforward measure of functional associations, they do not account for indirect relationships shown to be one of the major driving force of genome regulation [???
+Here, using percents offers a more granular approach, but it is unclear how it performs when compared to counts.
+On the other hand, the use of distances between TAD boundaries and genomic annotations has largely been ignored.
+Moreover, while direct overlaps represent the most straightforward measure of functional associations, they do not account for indirect relationships shown to be one of the major driving forces of genome regulation [???
 REFS].
+These relationships can be quantified using distances (in basepairs) from regions on the linear genome to regions that define functional genomic annotations.
 The most prominent example being the enhancer-promoter relationships, where enhancers are frequently located hundreds or thousands of bases away from their target promoters [@whalen2016enhancer].
-Using percents offers a more granular approach, but it is unclear how it performs when compared to counts.
-On the other hand, the use of distances between TAD boundaries and genomic annotations has largely been ignored.
-However, these distance features have the potential to offer the most accurate spatial representation of which genomic features are associated with TAD boundaries.
+The use of distances have largely been ignored, yet have the potential to offer the most accurate spatial representation of which genomic features are associated with TAD boundaries.
 
@@
 
+<!--
 [Paragraph about disconnect between Hi-C and epigenomic data] Despite the success of Hi-C technologies in revealing the high-order levels of genome organization (chromosome territories, A/B compartments, TADs, sub-TADs, chromatin loops), resolution of Hi-C data (~750kb [???
@@
 One of the key missing pieces to connect 3D genome architecture to transcription has been the inability of Hi-C to attain the resolution necessary to discern gene-level features of chromatin.
-This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited out understanding of epigenomic regulation of gene expression and its potential link to chromatin architecture.
+This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited our understanding of epigenomic regulation of gene expression and its potential link to chromatin architecture.
 Although computational [???
@@
 One aim of this study is to predict the location of TAD boundaries on a scale comparable to epigenomic assays.
-For this, we developed a model trained on a relaticely coarse Hi-C data for predicting 3D features (TAD boundaries) from 1D data (epigenomic datasets).
+For this, we developed a model trained on a relatively coarse Hi-C data for predicting 3D features (TAD boundaries) from 1D data (epigenomic datasets).
+-->
 
@@
 We evaluated Hi-C data for both the GM12878 and K562 cell line obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolution.
+
 For each resolution, we examined the inclusion of three different predictor types, including distance as the measure of association between genomic elements.
@@
 This process was performed on chromosome-specific regions on the linear genome.
-Noninformative features were removed using a feature reduction algorithm and classifiers were built to assess model performance, and investigate which genomic annotations were most predictive of TAD boundaries for a given system from the complete ensemble.
+Noninformative features were removed using a feature reduction algorithm.
+Lastly, random forest classifiers were built to assess model performance, and investigate which genomic annotations were most predictive of TAD boundaries for a given system from the complete ensemble.
 
@@
 The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
-The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained throughput the autosomal chromosomes.
+The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained for the autosomal chromosomes.
 TAD boundaries called on Chromosome 9 were omitted from all downstream analyses, for both cell lines, due to the sparcity of the contact matrix at the 10 kb resolution for the K562 cell line.
@@
 
-Using the sets of genomic annotations, we created three types of predictors that were used as features for subsequent models to analyze their respective spatial relationship with TAD boundaries:
+Using the sets of genomic annotations, we created three types of predictors that were used as features for subsequent models to analyze their respective spatial relationship with TAD boundaries.
+They are described in detail below:
 
 1.
-**Overlap Counts (OC)**: For each genomic bin, the total number of instances where a genomic bin overlapped with regions assigned to genomic annotations (features) was calculated.
+**Overlap Counts (OC)**: For each genomic bin, the total number of instances where a bin overlapped with regions assigned to genomic annotations (features) was calculated.
 In the case of no overlaps, the value was set to 0.
@@
 
+### TRAINING AND TESTING
+
+The cell line- and resolution-specific data was then split into a 7:3 ratio of training to testing sets.
+Furthermore, for the task of performance evaluation and prediction, the test set remained constant for all ensemble systems to account for an unbiased comparison.
+
 ### DATA RE-SAMPLING
@@
 Minority classes were the set of genomic bins that overlapped with flanked TAD boundaries, while majority classes were the set of genomic bins that did not overlap with a flanked TAD boundary.
+In order to assess the influence of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling).
+They are described in detail below.
 
-In order to assess the influence of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling), composed of the genomic bin class and data from each predictor type.
-The re-sampling techniques considered are described in detail below.
+1. **No Sampling**: All of the data points from the majority and minority classes of the training set were used.
 
-1. **No Sampling**: All of the data points from the majority and minority class of the training set were used.
+2.
+**Random Under-Sampling (RUS)**: All of the data points from the minority class of the training set were used.
+Sampling without replacement was used to obtain the same number of data points from the majority class.
 
-2. **Random Under-Sampling (RUS)**: All of the minority classes from the training set were used. Sampling without replacement was used to obtain the same number of the majority classes.
-
-3. **Random Over-Sampling (ROS)**: All of the majority classes from the training set were used. Sampling with replacement was used to obtain the same number of the minority classes.
+3.
+**Random Over-Sampling (ROS)**: All of the data points from the majority class of the training set were used.
+Sampling with replacement was used to obtain the same number of data points from the minority class.
 
 4.
-**SMOTE** (Synthetic Minority Over-Sampling Technique): This method incorporates both random under- and over-sampling.
-Under-sampling is performed without replacement from the majority class, while over-sampling is performed by creating new synthetic observations using the minority class [@chawla2002smote].
+**SMOTE** (Synthetic Minority Over-Sampling Technique): This method incorporates both random under- and over-sampling [@chawla2002smote].
+Under-sampling is performed without replacement from the majority class.
+On the other hand, over-sampling is performed by creating new synthetic observations using the minority class.
+The minority class is over-sampled by taking each minority class sample and introducing synthetic examples along the feature vectors joining any/all of the k=5 (default) minority class nearest neighbors.
+The SMOTE algorithm can have many variations is the percentage of over- and under-sampling.
+In this study we restricted the algorithm to 100% over-sampling and 200% under-sampling.
+That is, 1 new synthetic observation was to be created for each existing minority class data point, while 2 data points were simultaneously randomly selected from the majority class.
+This combination results in perfectly balanced classes.
 The *DMwR* R package was used to perform SMOTE (version 0.4.1).
@@
 We then considered 3 separate predictor types as the feature space including $P = \{OC, OP, Distance\}$.
-The cell line- and resolution-specific data was then split into a 7:3 ratio of training to testing sets.
-Furthermore, for the task of performance evaluation and prediction, the test set remained constant for all ensemble systems to account for an unbiased comparison.
 To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including $B = \{None, RUS, ROS, SMOTE\}$.
-Each combination of the above parameters was implemented on chromosome specific sections of the linear genome, and thus, was repeated repeated 21 times (number of autosomal chromosomes, excluding chromosome 9).
+Each combination of the above parameters was implemented on chromosome specific sections of the linear genome.
+Performances were then aggregated across each of the 21 chromosomes (omitting chromosome 9).
 Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling 2016 ($2 \times 4 \times 3 \times 4 \times 21$) separate models.
-Performances were then aggregated across each of the 21 chromosomes (omitting chromosome 9; see Methods).
 We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.
@@
 Topologically associating domains were then identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions, for each cell line respectively.
-We then established a unified approach toward preparing cell line -specific TAD boundary data for predictive modelling purposes, irrespective of data resolutions (Figure 2).
+We then established a unified approach toward preparing cell line specific TAD boundary data for predictive modelling purposes, irrespective of data resolutions (Figure 2).
 
@@
 This correlation with resolution was found to be significant, as evidenced by large intraclass correllation coefficients (ICC) (Table 2; Supplementary Tables 4).
-However, the class imbalance problem was found to be much more consistant across resolutions in both cell lines.
-The sparsity of TAD boundaries throughout the genome was found to contribute to heavily imbalanced classes.
-This imbalance was evidenced by low imbalance ratios, defined as the ratio of the number of genomic bins that overlapped with flanked TAD boundaries ($Y=1$), to the much larger number of genomic bins that did not ($Y=0$).
+However, the class imbalance problem, caused by the sparsity of TAD boundaries throughout the genome, was found to be much more consistant across resolutions in both cell lines.
+This imbalance was evidenced by low imbalance ratios, defined as the ratio of the number of genomic bins that overlapped with flanked TAD boundaries, to the much larger number of genomic bins that did not.
 This relationship was not significantly correlated with resoltuion for either cell line, indicating that there existed a severe disparity between classes at all resolutions of Hi-C data.
-[???
-Very bad and boring.
-You should tell the STORY, not the report.
-E.g., "Expectedly, the average number of genomic bins, TADs, and TAD boundaries increased with the increased resolution of Hi-C data (Table 1).
-However, the imbalance ratio, defined as ..., remained severe (~XXX) at all resolutions (Table 1).
-In summary, the problem of class imbalance exists at all resolutions of Hi-C data."; !!!
-editted]
 
@@
 
-We then investigated the relationship between the functional genomic annotations and the development of TAD boundaries by devising 3 different predictor-types that composed the feature space of downstream random forest classification models.
-These predictor-type specific annotations represented the data matrix, $X = \{X_1, X_2, ..., X_p\}$, where $p$ is the complete set of functional annotations.
+To establish said feature space for all downstream random forest models, we constructed 3 different predictor-types.
+These predictor-type specific annotations represented the data matrix, $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
 Overlap counts was the least granular predictor-type considered, simply defined by the number of annotation-specific regions located within each genomic bin (Figure 3A).
@@
 
-## DATA RE-SAMPLING COUPLED WITH THE INCLUSION OF A DISTANCE-TYPE FEATURE SPACE SUBSTANTIALLY IMPROVED MODEL PERFORMANCE
+## SMOTE RE-SAMPLING COUPLED WITH THE INCLUSION OF A DISTANCE-TYPE FEATURE SPACE SUBSTANTIALLY IMPROVED MODEL PERFORMANCE
 
+When assessing performances for models built on balanced data, we found that SMOTE re-sampling provided the optimal MCC consistently across both predictor type and resolution.
+Specifically, the most improvement in model performance was seen when combining SMOTE re-sampling with distance-type predictors.
+This was also the optimal combination for the K562 cell line (Supplementary Figure 3).
+These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
+Moreover, there was a clear degredation in model performance as data resolution decreased.
+Likewise, performances exhibited much more variability across chromosomes when built on lower resolutions.
+
+<!--
 When models were built on randomly oversampled (ROS) data for GM12878, we found an increase in MCC compared to no resampling, at higher resolutions.
@@
 These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
+-->
 
@@
 Additionally, we were also able to identify some lesser known cell line specific transcription factors as predictive of TAD boundaries including the MYC-associated zing-finger protein (MAZ), jun-D proto-oncogene (JUND), and ELF1.
-These transcription factor binding sites tended to be given higher predictive importance at lower resolution.
+These transcription factor binding sites tended to be given higher predictive importance at lower resolutions.
 In fact, at lower resolutions, the predictive importance was found to be much more evenly dispersed across the top transcription factor binding sites, than for higher resolutions.
@@
 These cell line specific distance profiles were again found to be significantly different between genomic class, at all resolutions (Supplementary 10).
+
 # DISCUSSION

### 2019-05-28 Manuscript/Figures/figure_legends.Rmd
rearranged figures
editted legends

@@
 **Figure 1.
-Model Construction.** An illustration of the proposed model construction given cell line-specific Hi-C matrices.
+Ensemble Framework.** A diagram of the cell line specific ensemble framework detailing the various combination of inputs used in the model building pipeline.
+The minoirty and majority classes were represented by the genomic bins that overlapped with flanked TAD boundaries or did not, respectively.
+Functional genomic annotations obtained from the UCSC Genome Browser Database composed the feature space.
+The data was split into a 7:3 training to testing set ratio.
+A feature engineering step was included to isolate the spatial relationship, of increasing granularity, between annotations and genomic bins.
+Data re-sampling and regularization was applied to the training data.
+Lastly, a random forest classification algorithm was implemeted and validated on the testing data.
+
+<!--
+A given system within the ensemble framework included the total number of genomic bins, labeled as having been overlapped with a flanked TAD boundary ($Y=1$) or not ($Y=0$).
+The data matrix that composed the feature space was composed of predictor-type specific annotations represented by $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
+The data was then split into a 7:3 training to testing set ratio.
+A re-sampling technique was applied to the training set, followed by an elastic-net regularization to reduce the feature space.
+Lastly, a random forest classification model was performed on the re-sampled and reduced training set and validated on the held out testing set common to all ensemble systems in the framework.
+-->
+
+**Figure 2.
+Model Construction.** An illustration of the proposed model construction given cell line specific Hi-C matrices.
 The contact matrix above is a visualization of the interconnectivity of chromosome 14 at 100 kb resolution, for the GM12878 cell line, on the intervals from 20 mb to 100 mb [@durand2016juicer].
@@
 To account for the uncertainty in TAD boundary detection, each boundary point was flanked on both sides by resolution-specific genomic regions (bins).
-The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region (Y=1) or not (Y=0).
-The spatial relationship between positional coordinates of various functional genomic annotations, obtained from ENCODE, and the genomic bins were then used to define the feature space of the models.
-
-**Figure 2.
-Ensemble Framework.** A diagram of the ensemble framework detailing the various combination of inputs used in the model building pipeline.
-A given system within the ensemble framework included the total number of genomic bins, labeled as having been overlapped with a flanked TAD boundary or not, as well as a feature space composed of 1 of 3 different predictor-type specific annotations.
-The data was then split into a 7:3 training:testing set ratio.
-A re-sampling technique was applied to the training set, followed by an elastic-net regularization to reduce the feature space.
-Lastly, a random forest classification model was performed on the re-sampled and reduced training set and validated on the held out testing set common to all ensemble systems in the framework.
+The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region ($Y=1$) or not ($Y=0$).
+The spatial relationship between positional coordinates of various functional genomic annotations, obtained from ENCODE, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
 
@@
 The _distance_ ($log_{2}$ transformed) predictors were calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest genomic feature.
-[???should I include ABC here?]
 
@@
 
+**Figure 8.
+Comparing $log_{2}$ distance profiles.** Boxplots illustrating the distribution of distances around 10 kb regions on the GM12878 genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
+P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [**** = p < 0.00001].
+
 <!--

### 2019-05-28 Manuscript/Supplementary/supplementary_legends.Rmd
editted legends

@@
 
+**Figure 9.
+Comparing $log_{2}$ distance profiles.** Boxplots illustrating the distribution of distances around (A) 25 kb, (B) 50 kb, and (C) 100 kb regions on the GM12878 genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
+P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [**** = p < 0.00001].
+
+**Figure 10.
+Comparing $log_{2}$ distance profiles.** Boxplots illustrating the distribution of distances around (A) 10 kb, (B) 25 kb, (C) 50 kb, (D) 100 kb regions on the GM12878 genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential TFBS including SMC3, CTCF, RAD21, and ZNF143.
+P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [**** = p < 0.00001].
+
 <!--

### 2019-05-29 Manuscript/Figures/figure_legends.Rmd
edits to figure legends

@@
 **Figure 2.
-Model Construction.** An illustration of the proposed model construction given cell line specific Hi-C matrices.
-The contact matrix above is a visualization of the interconnectivity of chromosome 14 at 100 kb resolution, for the GM12878 cell line, on the intervals from 20 mb to 100 mb [@durand2016juicer].
-The boundary coordinates of topologically association domains (TADs) were identified using the Arrowhead algorithm.
+Model Construction.** An illustration of the proposed model construction given cell line specific Hi-C data.
+Above is an example of a subsection of the contact matrix for chromosome 14 (at megabase scale) on GM12878 [@durand2016juicer].
+The contact matrix is a visualization of the interconnectivity of the linear genome at 100 kb resolution.
+The boundary coordinates of TADs were identified using the Arrowhead algorithm.
 To account for the uncertainty in TAD boundary detection, each boundary point was flanked on both sides by resolution-specific genomic regions (bins).
 The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region ($Y=1$) or not ($Y=0$).
-The spatial relationship between positional coordinates of various functional genomic annotations, obtained from ENCODE, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
+The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
 
 **Figure 3.
-The three predictor types.** Three separate types of predictors were considered when quantifying the association between TAD boundaries and genomic annotations.
+Predictor types.** Three separate types of predictors were considered when quantifying the association between TAD boundaries and genomic annotations.
 Each predictor type was used to build the feature space of specific models in the ensemble framework.
-The _overlap count_ (OC) predictors consider the total number of genomic features that overlapped with each genomic bin.
-The _overlap percent_ (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin by the total bin width.
-The _distance_ ($log_{2}$ transformed) predictors were calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest genomic feature.
+(A) _Overlap Counts_ (OC) consider the total number of genomic features that overlapped with each genomic bin.
+(B) _Overlap Percent_ (OP) was calculated by dividing the sum of all feature widths within each specific bin by the total bin width.
+(C) _Distance_ ($log_{2}$ transformed) was calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest region defining a genomic annotation.
 
 **Figure 4.
-Comparing ensemble system specific model performances for GM12878.** Performances of random forest classification models built on each of the 3 predictor types: OC (A), OP (B), and Distance (C).
-Within each predictor type, and across resolution, MCCs metrics were recorded for models subsequently implemented on re-sampled data using the 4 re-sampling techniques: None (red), ROS (green), RUS (blue), and SMOTE (purple).
+SMOTE re-sampled models built on distance-type predictors yielded optimal MCCs across resolutions for GM12878.** Performances of random forest classification models built on each of the 3 predictor types: (A) OC, (B) OP, and (C) Distance.
+Within each predictor type, and across resolution, training data was re-sampled using different techniques including: None (red), ROS (green), RUS (blue), and SMOTE (purple).
 Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.
@@
 **Figure 5.
-Predictive importance is outweighed by transcription factor binding sites.** Stacked barplots illustrating the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework, for each resolution on GM12878.
-Proportions are separated by the set of annotations included in the feature space including chromatin state segmentation, histone modification, and transcription factor binding sites.
+The proportional importance of optimally built predictive models was outweighed by transcription factor binding sites across resolutions for GM12878.** Stacked barplots illustrate the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework (SMOTE re-sampling; with distance-type predictors), for each resolution on GM12878.
+Proportions are grouped by the class of cell line specific annotations in the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).
 

### 2019-05-29 Manuscript/Supplementary/supplementary_legends.Rmd
edits to figure legends

@@
 **Supplementary Figure 1.
-GM12878 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths (resolutions) of 10 kb, 25 kb, 50 kb, and 100 kb.
-(E-H) $Log_{2}$ transformed distances for binwidths (resolutions) of 10 kb, 25 kb, 50 kb, and 100 kb.
+Performing $log_{2}$ transformations normalized skewed distance densities across resolution for GM12878.** When measured in basepairs, distances were highly right skewed for all resolutions: (A) 10 kb, (B) 25 kb, (C) 50 kb, and (D) 100 kb.
+After $log_{2}$ transforming the distances, densities became much more gaussian distributed for all resolutions: (E) 10 kb, (F) 25 kb, (G) 50 kb, and (H) 100 kb.
+Each density curve represents a cell line specific annotation, and its relationship with all resolution specific genomic bins.
 
 **Supplementary Figure 2.
-K562 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths (resolutions) of 10 kb, 25 kb, 50 kb, and 100 kb.
-(E-H) $Log_{2}$ transformed distances for binwidths (resolutions) of 10 kb, 25 kb, 50 kb, and 100 kb.
+Performing $log_{2}$ transformations normalized skewed distance densities across resolution for K562.** When measured in basepairs, distances were highly right skewed for all resolutions: (A) 10 kb, (B) 25 kb, (C) 50 kb, and (D) 100 kb.
+After $log_{2}$ transforming the distances, densities became much more gaussian distributed for all resolutions: (E) 10 kb, (F) 25 kb, (G) 50 kb, and (H) 100 kb.
+Each density curve represents a cell line specific annotation, and its relationship with all resolution specific genomic bins.
 
@@
 **Supplementary Figure 3.
-Comparing ensemble system specific model performances for K562.** Performances of random forest classification models built on each of the 3 predictor types: OC (A), OP (B), and Distance (C).
-Within each predictor type, and across resolution, MCCs metrics were recorded for models subsequently implemented on re-sampled data using the 4 re-sampling techniques: None (red), ROS (green), RUS (blue), and SMOTE (purple).
+SMOTE re-sampled models built on distance-type predictors yielded optimal MCCs across resolutions for K562.** Performances of random forest classification models built on each of the 3 predictor types: (A) OC, (B) OP, and (C) Distance.
+Within each predictor type, and across resolution, training data was re-sampled using different techniques including: None (red), ROS (green), RUS (blue), and SMOTE (purple).
 Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.
@@
 **Supplementary Figure 4.
-Predictive importance is outweighed by transcription factor binding sites.** Stacked barplots illustrating the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework, for each resolution on K562.
-Proportions are separated by the set of annotations included in the feature space including chromatin state segmentation, histone modification, and transcription factor binding sites.
+The proportional importance of optimally built predictive models was outweighed by transcription factor binding sites across resolutions for K562.** Stacked barplots illustrate the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework (SMOTE re-sampling; with distance-type predictors), for each resolution on GM12878.
+Proportions are grouped by the class of cell line specific annotations in the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).
 

### 2019-05-29 Manuscript/manuscript.Rmd
edits to figure legends

@@
 **Methods.** To investigate the problem of spatial genomic relationships and class imbalance problem, we developed an ensemble framework for optimizing prediction of TAD boundaries.
-We utilized several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) coupled with various metrics for classifier performance evaluation (Area Under Receiver Operating Characteristics (AUCROC) curve, Precision-Recall curve (AUPRC), F1, Matthew Correlation Coefficient (MCC), among others) to select the best predictive model in class imbalance settings.
+We utilized several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) coupled with various metrics for classifier performance evaluation (Area Under Receiver Operating Characteristics (AUCROC) curve, Precision-Recall curve (AUPRC), F1, Matthews Correlation Coefficient (MCC), among others) to select the best predictive model in class imbalance settings.
 
@@
 This enables a more realistic benchmark to evaluate a model on as this ratio will be lower than 0.5 for a test data set with imbalanced classes [@saito2015precision].
-Another threshold-specific measure to consider is a composite metric involving all quadrants of the confusion matirix, such as Matthew's Correlation Coefficient (MCC) [@jeni2013facing; @chicco2017ten].
+Another threshold-specific measure to consider is a composite metric involving all quadrants of the confusion matirix, such as Matthews Correlation Coefficient (MCC) [@jeni2013facing; @chicco2017ten].
 The MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
@@
 
-Using the sets of genomic annotations, we created three types of predictors that were used as features for subsequent models to analyze their respective spatial relationship with TAD boundaries.
+Using the sets of cell line specific genomic annotations, we created three types of predictors that were used as features for subsequent models to analyze their respective spatial relationship with TAD boundaries.
 They are described in detail below:
@@
 **Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter simply as $\textit{distance}$), from the center of the bin to the center of the nearest region defined by a specific genomic annotation was calculated.
-The log transformation was used as a normalization technique in order to account for the skewness present in the distance densities <!--(Supplementary Figures 1)-->.
+The log transformation was used as a normalization technique in order to account for the skewness present in the distance densities (Supplementary Figures 1-2).
 
@@
 
-The performance of each ensemble system in the framework was compared using the composite metric, Matthew's Correlation Coefficient. The MCC is defined as follows:
+The performance of each ensemble system in the framework was compared using the composite metric, Matthews Correlation Coefficient. The MCC is defined as follows:
 
@@
 In order to set a baseline in performance, we first evaluated the least granular model, that is one implemented using OC predictor types, without data re-sampling.
-We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 5A).
+We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 4A).
 We gradually increased the granularity by assessing models built on OP predictor types, while still not performing any data resampling.
-Here, the results were similar to that of OC types (Figure 5B).
-However, when including distance-type predictors, models were found to exhibit a marked improvement in MCC compared to the other two types (Figure 5C).
+Here, the results were similar to that of OC types (Figure 4B).
+However, when including distance-type predictors, models were found to exhibit a marked improvement in MCC compared to the other two types (Figure 4C).
 Results were found to be consistently poor across resolutions and predictor types, when implemented on the K562 cell line (Supplementary Figure 3).
@@
 
-When assessing performances for models built on balanced data, we found that SMOTE re-sampling provided the optimal MCC consistently across both predictor type and resolution.
+When assessing performances for models built on balanced data, we found that SMOTE re-sampling provided the optimal MCC consistently across both predictor type and resolution (Figure 4).
 Specifically, the most improvement in model performance was seen when combining SMOTE re-sampling with distance-type predictors.
@@
 This was done so as to incur the least amount of bias and so that all conclusions could be made soley between model characteristics.
-As a result, we showed that Matthew's Correlation Coefficient was much more sensitive to the imbalance present in the test set, compared to more popular metrics like AUROC, which attain artificially high values by correctly predicting majority class samples.
+As a result, we showed that Matthews Correlation Coefficient was much more sensitive to the imbalance present in the test set, compared to more popular metrics like AUROC, which attain artificially high values by correctly predicting majority class samples.
 When comparing re-sampling techniques, we found that SMOTE re-sampling outperformed models built on both simple ROS or RUS, implying that, in fact, a combination of both random under-sampling and random over-sampling is preferred in TAD boundary prediction.

### 2019-05-29 Manuscript/Figures/figure_legends.Rmd
editted manuscript and legends

@@
 **Figure 6.
-Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for GM12878.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
+Optimally built TFBS-specific models outperformed other annotation-specific models across resolution for GM12878** Performances were compared for random forest models built using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
 Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types.
@@
 **Figure 7.
-Predictive importance.** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for GM12878.
+Top 20 most predictive transcription factor binding sites sorted by 10 kb for GM12878.** A heatmap illustrating the importance of the key cell line specific transcription factors for optimally built random forest models across resolution.
 Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100.
@@
 **Figure 8.
-Comparing $log_{2}$ distance profiles.** Boxplots illustrating the distribution of distances around 10 kb regions on the GM12878 genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
-P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [**** = p < 0.00001].
-
-<!--
-**Figure 7.
-Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 10 kb resolution, on GM12878.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
-For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
-That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
--->
+Top predictive transcription factor binding sites were significantly closer to bins that overlapped with 10 kb flanked TAD boundaries on GM12878** Boxplots illustrating the distribution of distances (on $log_{2}$ scale) around 10 kb regions on the linear genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential cell line specific TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
+P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].

### 2019-05-29 Manuscript/Supplementary/supplementary_legends.Rmd
editted manuscript and legends

@@
 **Supplementary Figure 5.
-Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for K562.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
+Optimally built TFBS-specific models outperformed other annotation-specific models across resolution for K562** Performances were compared for random forest models built using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
 Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types.
@@
 **Supplementary Figure 6.
-Predictive importance** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for K562.
+Top 20 most predictive transcription factor binding sites sorted by 10 kb for K562.** A heatmap illustrating the importance of the key cell line specific transcription factors for optimally built random forest models across resolution.
 Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100.
@@
 
-**Figure 9.
-Comparing $log_{2}$ distance profiles.** Boxplots illustrating the distribution of distances around (A) 25 kb, (B) 50 kb, and (C) 100 kb regions on the GM12878 genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
-P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [**** = p < 0.00001].
+**Supplementary Figure 9.
+Top predictive transcription factor binding sites were significantly closer to bins that overlapped with varying units of flanked TAD boundaries on GM12878** Boxplots illustrating the distribution of distances (on $log_{2}$ scale) around (A) 25 kb, (B) 50 kb, and (C) 100 kb regions on the linear genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential cell line specific TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
+P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].
 
-**Figure 10.
-Comparing $log_{2}$ distance profiles.** Boxplots illustrating the distribution of distances around (A) 10 kb, (B) 25 kb, (C) 50 kb, (D) 100 kb regions on the GM12878 genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential TFBS including SMC3, CTCF, RAD21, and ZNF143.
-P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [**** = p < 0.00001].
+**Supplementary Figure 10.
+Top predictive transcription factor binding sites were significantly closer to bins that overlapped with varying units of flanked TAD boundaries on K562** Boxplots illustrating the distribution of distances (on $log_{2}$ scale) around (A) 10 kb, (B) 25 kb, (C) 50 kb, and (D) 100 kb regions on the linear genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential cell line specific TFBS including SMC3, CTCF, RAD21, and ZNF143.
+P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].
 

### 2019-05-29 Manuscript/manuscript.Rmd
editted manuscript and legends

@@
 For GM12878, at 10 kb resolution, we found that SMC3, CTCF, RAD21, ZNF143, and YY1sc281 were all statistically significantly closer to bins that overlapped with flanked TAD boudaries than those that did not (Figure 8).
-Although still statistically significantly different, the distance profiles between genomic class were found to be much more similar at lower resolutions (Supplementary 9).
+Although still statistically significantly different, the distance profiles between genomic class were found to be much more similar at lower resolutions (Supplementary Figure 9).
 For the K562 cell line, we reported the distance profiles of the same transcription factor binding sites, excluding the YY1sc281, due to its unavailability in the UCSC Genome Browser.
-These cell line specific distance profiles were again found to be significantly different between genomic class, at all resolutions (Supplementary 10).
+These cell line specific distance profiles were again found to be significantly different between genomic class, at all resolutions (Supplementary Figure 10).
 

### 2019-05-29 Presentation/ordered_list_of_figures.Rmd
added ordered list of figures .rmd file to presentation folder

--- 2019-05-29 Manuscript/Figures/figure_legends.Rmd
@@
 ---
-title: "Legends for Figures"
+title: "Ordered List of Figures"
 author: "Spiro Stilianoudakis"
-date: "November 19, 2018"
-output: pdf_document
+date: "May 28, 2019"
+output: word_document
 ---
@@
 
-**Figure 1.
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure1_dist_densities_gm12878.png) |
+| **Supplementary Figure 1.
+Performing $log_{2}$ transformations normalized skewed distance densities across resolution for GM12878.** When measured in basepairs, distances were highly right skewed for all resolutions: (A) 10 kb, (B) 25 kb, (C) 50 kb, and (D) 100 kb.
+After $log_{2}$ transforming the distances, densities became much more gaussian distributed for all resolutions: (E) 10 kb, (F) 25 kb, (G) 50 kb, and (H) 100 kb.
+Each density curve represents a cell line specific annotation, and its relationship with all resolution specific genomic bins.
+|
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure2_dist_densities_k562.png) |
+| **Supplementary Figure 2.
+Performing $log_{2}$ transformations normalized skewed distance densities across resolution for K562.** When measured in basepairs, distances were highly right skewed for all resolutions: (A) 10 kb, (B) 25 kb, (C) 50 kb, and (D) 100 kb.
+After $log_{2}$ transforming the distances, densities became much more gaussian distributed for all resolutions: (E) 10 kb, (F) 25 kb, (G) 50 kb, and (H) 100 kb.
+Each density curve represents a cell line specific annotation, and its relationship with all resolution specific genomic bins.
+|
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure1_ensemble_framework.png) |
+| **Figure 1.
 Ensemble Framework.** A diagram of the cell line specific ensemble framework detailing the various combination of inputs used in the model building pipeline.
@@
 Lastly, a random forest classification algorithm was implemeted and validated on the testing data.
+|
++-------+
 
-<!--
-A given system within the ensemble framework included the total number of genomic bins, labeled as having been overlapped with a flanked TAD boundary ($Y=1$) or not ($Y=0$).
-The data matrix that composed the feature space was composed of predictor-type specific annotations represented by $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
-The data was then split into a 7:3 training to testing set ratio.
-A re-sampling technique was applied to the training set, followed by an elastic-net regularization to reduce the feature space.
-Lastly, a random forest classification model was performed on the re-sampled and reduced training set and validated on the held out testing set common to all ensemble systems in the framework.
--->
-
-**Figure 2.
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure2_model_construction_V3.png) |
+| **Figure 2.
 Model Construction.** An illustration of the proposed model construction given cell line specific Hi-C data.
@@
 The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
+|
++-------+
 
-**Figure 3.
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure3_predictor_types.png) |
+| **Figure 3.
 Predictor types.** Three separate types of predictors were considered when quantifying the association between TAD boundaries and genomic annotations.
@@
 (C) _Distance_ ($log_{2}$ transformed) was calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest region defining a genomic annotation.
+|
++-------+
 
-**Figure 4.
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure4_gm12878_model_performances.png) |
+| **Figure 4.
 SMOTE re-sampled models built on distance-type predictors yielded optimal MCCs across resolutions for GM12878.** Performances of random forest classification models built on each of the 3 predictor types: (A) OC, (B) OP, and (C) Distance.
@@
 Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.
+|
++-------+
 
-**Figure 5.
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure3_k562_model_performances.png) |
+| **Supplementary Figure 3.
+SMOTE re-sampled models built on distance-type predictors yielded optimal MCCs across resolutions for K562.** Performances of random forest classification models built on each of the 3 predictor types: (A) OC, (B) OP, and (C) Distance.
+Within each predictor type, and across resolution, training data was re-sampled using different techniques including: None (red), ROS (green), RUS (blue), and SMOTE (purple).
+Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.
+|
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure4_gm12878_model_performances.png) |
+| **Figure 4.
+SMOTE re-sampled models built on distance-type predictors yielded optimal MCCs across resolutions for GM12878.** Performances of random forest classification models built on each of the 3 predictor types: (A) OC, (B) OP, and (C) Distance.
+Within each predictor type, and across resolution, training data was re-sampled using different techniques including: None (red), ROS (green), RUS (blue), and SMOTE (purple).
+Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.
+|
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure5_proportion_of_importances_gm12878.png) |
+| **Figure 5.
 The proportional importance of optimally built predictive models was outweighed by transcription factor binding sites across resolutions for GM12878.** Stacked barplots illustrate the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework (SMOTE re-sampling; with distance-type predictors), for each resolution on GM12878.
 Proportions are grouped by the class of cell line specific annotations in the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).
+|
++-------+
 
-**Figure 6.
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure4_proportion_of_importances_k562.png) |
+| **Supplementary Figure 4.
+The proportional importance of optimally built predictive models was outweighed by transcription factor binding sites across resolutions for K562.** Stacked barplots illustrate the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework (SMOTE re-sampling; with distance-type predictors), for each resolution on GM12878.
+Proportions are grouped by the class of cell line specific annotations in the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).
+|
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure6_comparing_sets_of_annotations_gm12878.png) |
+| **Figure 6.
 Optimally built TFBS-specific models outperformed other annotation-specific models across resolution for GM12878** Performances were compared for random forest models built using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
@@
 The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.
+|
++-------+
 
-**Figure 7.
-Top 20 most predictive transcription factor binding sites sorted by 10 kb for GM12878.** A heatmap illustrating the importance of the key cell line specific transcription factors for optimally built random forest models across resolution.
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure5_comparing_sets_of_annotations_k562.png) |
+| **Supplementary Figure 5.
+Optimally built TFBS-specific models outperformed other annotation-specific models across resolution for K562** Performances were compared for random forest models built using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
+Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types.
+The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.
+|
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure7_variable_importance_heatmaps_tfbs_gm12878.png) |
+| **Figure 7.
+Top 20 most predictive transcription factor binding sites sorted by 10 kb for GM12878.** A heatmap illustrating the importance of the key transcription factors for optimally built random forest models.
 Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100.
 Transcription factors with higher values of predictive importance are denoted in dark red.
+|
++-------+
 
-**Figure 8.
-Top predictive transcription factor binding sites were significantly closer to bins that overlapped with 10 kb flanked TAD boundaries on GM12878** Boxplots illustrating the distribution of distances (on $log_{2}$ scale) around 10 kb regions on the linear genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential cell line specific TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure6_variable_importance_heatmaps_tfbs_k562.png) |
+| **Supplementary Figure 6.
+Top 20 most predictive transcription factor binding sites sorted by 10 kb for K562.** A heatmap illustrating the importance of the key cell line specific transcription factors for optimally built random forest models across resolution.
+Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100.
+Transcription factors with higher values of predictive importance are denoted in dark red.
+|
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure8_distance_boxplots_key_tfbs_gm12878_10kb.png) |
+| **Figure 8.
+Top predictive transcription factor binding sites are significantly closer to bins that overlap with 10 kb flanked TAD boundaries on GM12878** Boxplots illustrating the distribution of distances (on $log_{2}$ scale) around 10 kb regions on the linear genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential cell line specific TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
 P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].
+|
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure9_distance_boxplots_key_tfbs_gm12878_other_res.png) |
+| **Supplementary Figure 9.
+Top predictive transcription factor binding sites were significantly closer to bins that overlapped with varying units of flanked TAD boundaries on GM12878** Boxplots illustrating the distribution of distances (on $log_{2}$ scale) around (A) 25 kb, (B) 50 kb, and (C) 100 kb regions on the linear genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential cell line specific TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
+P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].
+|
++-------+
+
++-------+
+| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure10_distance_boxplots_key_tfbs_K562_all_res.png) |
+| **Supplementary Figure 10.
+Top predictive transcription factor binding sites were significantly closer to bins that overlapped with varying units of flanked TAD boundaries on K562** Boxplots illustrating the distribution of distances (on $log_{2}$ scale) around (A) 10 kb, (B) 25 kb, (C) 50 kb, and (D) 100 kb regions on the linear genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential cell line specific TFBS including SMC3, CTCF, RAD21, and ZNF143.
+P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].
+|
++-------+

### 2019-05-29 Papers.Rmd
CTCF nearby TAD boundaries note

@@
 - CTCF is not at TAD boundaries, but nearby. "only 15% CTCF sites are at the TAD boundary while 85% CTCF sites are inside the TAD [@Ong:2014aa]."
+
+- CTCF showed a remarkable enrichment immediately outside of these boundaries, with sites on the plus strand sharply peaking at upstream TAD boundaries and those on the minus strand peaking at downstream boundaries.
+Similar enrich- ments at TAD boundaries are observed for RAD21, SMC3 (Cohesin complex), and ZNF143, consistent with previous reports [@Dixon:2012aa][@Zuin:2014aa][@Bailey2015].

### 2019-05-29 Manuscript/manuscript.Rmd
Relevant references for the prediction paragraph

@@
 Although computational [???
-REFS?] and technological [@Hsieh:2019aa] methods for enhancing resolution of Hi-C data started to appear, they [???
+REFS?](Zhang et al., “HiCPlus.”, Carron et al., “Boost-HiC.”) and technological [@Hsieh:2019aa][@Ma:1998aa][@Belaghzal2017] methods for enhancing resolution of Hi-C data started to appear, they [???
 remains to write about their pitfalls].

### 2019-05-29 Scripts/comparing_distance_profiles_using_boxplots.Rmd
edits to results script

--- 2019-05-22 Scripts/comparing_distance_profiles_using_density_plots.Rmd
@@
 
+all_dist_gm12878$y <- factor(all_dist_gm12878$y, levels=c("Yes","No"))
 all_dist_gm12878$Resolution <- factor(all_dist_gm12878$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
@@
 
-ggplot(all_dist_gm12878, aes(x = Resolution, y = value, fill = y)) +
+# 10 kb
+all_dist_gm12878_10kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="10 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
   stat_boxplot(geom = "errorbar") +
-  geom_boxplot(#fill = fill, 
-               #colour = line,
-               outlier.shape = NA) +
-  facet_grid(~ variable) +
-  xlab("Resolution") +
-  ylab("Log2 Distances") +
-  ylim(5,25) +
-  scale_fill_discrete(name="Class of Genomic Bin",
-                      labels=c("Did not overlap\nw/ flanked TAD boundary",
-                               "Overlapped\nw/ flanked TAD boundary")) +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("Transcription Factor Binding Site") +
+  ylab("Log2 Distance") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
   #guides(color=FALSE) +
@@
   theme_bw() +
-  theme(axis.text.x = element_text(size=15,
-                                   angle = 45, 
-                                   #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
+  theme(axis.text.x = element_blank(),
         axis.text.y = element_text(size = 15),
@@
         legend.title=element_text(size=20),
+        legend.position="bottom",
         strip.text.x = element_text(size = 15))
+
+# 25 kb
+all_dist_gm12878_25kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="25 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
+  #guides(color=FALSE) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        legend.position="bottom",
+        strip.text.x = element_text(size = 15))
+
+# 50 kb
+all_dist_gm12878_50kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="50 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
+  #guides(color=FALSE) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        legend.position="bottom",
+        strip.text.x = element_text(size = 15))
+
+# 100 kb
+all_dist_gm12878_100kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="100 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("Transcription Factor Binding Site") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
+  #guides(color=FALSE) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        legend.position="bottom",
+        strip.text.x = element_text(size = 15))
+
+figure <- ggarrange(all_dist_gm12878_25kb,
+                    all_dist_gm12878_50kb,
+                    all_dist_gm12878_100kb,
+                    ncol = 1,
+                    nrow = 3,
+                    common.legend = TRUE,
+                    legend = "bottom",
+                    labels = "AUTO",
+                    font.label = list(size=20))
+figure 
+annotate_figure(figure, 
+                #bottom = text_grob("Transcription Factor Binding Site", color = "black", size = 20),
+                left = text_grob("Log2 Distance", color = "black", size = 20, rot=90))
 ```
@@
 
+all_dist_K562$y <- factor(all_dist_K562$y, levels=c("Yes", "No"))
 all_dist_K562$Resolution <- factor(all_dist_K562$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
@@
 
-ggplot(all_dist_K562, aes(x = Resolution, y = value, fill = y)) +
+# 10 kb
+all_dist_K562_10kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="10 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
   stat_boxplot(geom = "errorbar") +
-  geom_boxplot(#fill = fill, 
-               #colour = line,
-               outlier.shape = NA) +
-  facet_grid(~ variable) +
-  xlab("Resolution") +
-  ylab("Log2 Distances") +
-  ylim(5,25) +
-  scale_fill_discrete(name="Class of Genomic Bin",
-                      labels=c("Did not overlap\nw/ flanked TAD boundary",
-                               "Overlapped\nw/ flanked TAD boundary")) +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
   #guides(color=FALSE) +
@@
         legend.title=element_text(size=20),
+        legend.position="bottom",
         strip.text.x = element_text(size = 15))
+
+# 25 kb
+all_dist_K562_25kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="25 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
+  #guides(color=FALSE) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        legend.position="bottom",
+        strip.text.x = element_text(size = 15))
+
+# 50 kb
+all_dist_K562_50kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="50 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("Transcription Factor Binding Site") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
+  #guides(color=FALSE) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        legend.position="bottom",
+        strip.text.x = element_text(size = 15))
+
+# 100 kb
+all_dist_K562_100kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="100 kb"),], aes(x = y, y = value, fill = y)) +
+  facet_grid(~ variable) +
+  stat_boxplot(geom = "errorbar") +
+  geom_boxplot() +
+  stat_compare_means(comparisons = list(c("No", "Yes")), 
+                     method = "wilcox.test", 
+                     label = "p.signif") +
+  #facet_grid(~ variable) +
+  xlab("Transcription Factor Binding Site") +
+  ylab("") +
+  #ylim(5,25) +
+  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
+  #guides(color=FALSE) +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        legend.position="bottom",
+        strip.text.x = element_text(size = 15))
+
+figure <- ggarrange(all_dist_K562_10kb,
+                    all_dist_K562_25kb,
+                    all_dist_K562_50kb,
+                    all_dist_K562_100kb,
+                    ncol = 2,
+                    nrow = 2,
+                    common.legend = TRUE,
+                    legend = "bottom",
+                    labels = "AUTO",
+                    font.label = list(size=20))
+figure 
+annotate_figure(figure, 
+                #bottom = text_grob("Transcription Factor Binding Site", color = "black", size = 20),
+                left = text_grob("Log2 Distance", color = "black", size = 20, rot=90))
 ```

### 2019-05-29 Presentation/ordered_list_of_figures.Rmd
fixed dimensions of supp fig 9

@@
 date: "May 28, 2019"
-output: word_document
+output:
+  word_document: default
 ---
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure1_dist_densities_gm12878.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure1_dist_densities_gm12878.png) |
 | **Supplementary Figure 1.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure2_dist_densities_k562.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure2_dist_densities_k562.png) |
 | **Supplementary Figure 2.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure1_ensemble_framework.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure1_ensemble_framework.png) |
 | **Figure 1.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure2_model_construction_V3.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure2_model_construction_V3.png) |
 | **Figure 2.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure3_predictor_types.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure3_predictor_types.png) |
 | **Figure 3.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure4_gm12878_model_performances.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure4_gm12878_model_performances.png) |
 | **Figure 4.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure3_k562_model_performances.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure3_k562_model_performances.png) |
 | **Supplementary Figure 3.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure5_proportion_of_importances_gm12878.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure5_proportion_of_importances_gm12878.png) |
 | **Figure 5.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure4_proportion_of_importances_k562.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure4_proportion_of_importances_k562.png) |
 | **Supplementary Figure 4.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure6_comparing_sets_of_annotations_gm12878.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure6_comparing_sets_of_annotations_gm12878.png) |
 | **Figure 6.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure5_comparing_sets_of_annotations_k562.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure5_comparing_sets_of_annotations_k562.png) |
 | **Supplementary Figure 5.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure7_variable_importance_heatmaps_tfbs_gm12878.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure7_variable_importance_heatmaps_tfbs_gm12878.png) |
 | **Figure 7.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure6_variable_importance_heatmaps_tfbs_k562.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure6_variable_importance_heatmaps_tfbs_k562.png) |
 | **Supplementary Figure 6.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Figures/figure8_distance_boxplots_key_tfbs_gm12878_10kb.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure8_distance_boxplots_key_tfbs_gm12878_10kb.png) |
 | **Figure 8.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure9_distance_boxplots_key_tfbs_gm12878_other_res.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure9_distance_boxplots_key_tfbs_gm12878_other_res.png) |
 | **Supplementary Figure 9.
@@
 +-------+
-| ![](C:/Users/Spiro Stilianoudakis/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure10_distance_boxplots_key_tfbs_K562_all_res.png) |
+| ![](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Supplementary/figure10_distance_boxplots_key_tfbs_K562_all_res.png) |
 | **Supplementary Figure 10.

### 2019-05-29 Scripts/comparing_distance_profiles_using_boxplots.Rmd
fixed dimensions of supp fig 9

@@
                     all_dist_gm12878_100kb,
-                    ncol = 1,
-                    nrow = 3,
+                    ncol = 2,
+                    nrow = 2,
                     common.legend = TRUE,

### 2019-05-30 Papers.Rmd
Add TADBoundaryDectector paper and notes

@@
 Prediction of new boundaries.
+
+- `TADBoundaryDectector` - TAD boundary prediction from sequence only using deep learning models.
+12 architectures tested, with three convolutional and an LSTM layer performed best.
+Methods, Implementation in Keras-TensorFlow.
+Model evaluation using different criteria, 96% accuracy reported.
+Deep learning outperform feature-based models, among which Boosted trees, Random Forest, elastic net logistic regression are best performers.
+Data augmentation (aka feature engineering) by randomly shifting TAD boundary regions by som base pairs of length (0-100).
+Tested on Drozophila data.
+https://github.com/lincshunter/TADBoundaryDectector
+    - Henderson, John, Vi Ly, Shawn Olichwier, Pranik Chainani, Yu Liu, and Benjamin Soibam.
+“Accurate Prediction of Boundaries of High Resolution Topologically Associated Domains (TADs) in Fruit Flies Using Deep Learning.” Nucleic Acids Research, May 3, 2019.
+https://doi.org/10.1093/nar/gkz315.
 

### 2019-05-31 Scripts/evaluating_model_performances_balanced_test.Rmd
added results scripts

---
title: "evaluating_model_performances_balanced_test"
author: "Spiro Stilianoudakis"
date: "May 30, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

# GM12878

##10kb

###MCC

####Balanced Test

```{r}
mccdata_gm12878_10kb_bt <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/rfperf_bt.rds"))

			mccdata_gm12878_10kb_bt <- rbind(mccdata_gm12878_10kb_bt,
										  perfdata[15,2])
		}
	}
}

```

####Unbalanced Test

```{r}
mccdata_gm12878_10kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/rfperf.rds"))

			mccdata_gm12878_10kb <- rbind(mccdata_gm12878_10kb,
										  perfdata[15,2])
		}
	}
}

```

###Plots

```{r}
all_rfperfs <- rbind.data.frame(mccdata_gm12878_10kb_bt,
                                mccdata_gm12878_10kb)

all_rfperfs$Testing <- c(rep("Balanced", length(mccdata_gm12878_10kb_bt)),
                                rep("Unbalanced", length(mccdata_gm12878_10kb)))
all_rfperfs$Predictor <- rep(c("Distance", "OC", "OP"), 168)
all_rfperfs$Resampling <- rep(c(rep("None", 3),
                            rep("ROS", 3),
                            rep("RUS", 3),
                            rep("SMOTE", 3)),42)
all_rfperfs$Chromosome <- rep(c(rep("CHR1", 12),
                            rep("CHR2", 12),
                            rep("CHR3", 12),
                            rep("CHR4", 12),
                            rep("CHR5", 12),
                            rep("CHR6", 12),
                            rep("CHR7", 12),
                            rep("CHR8", 12),
                            rep("CHR10", 12),
                            rep("CHR11", 12),
                            rep("CHR12", 12),
                            rep("CHR13", 12),
                            rep("CHR14", 12),
                            rep("CHR15", 12),
                            rep("CHR16", 12),
                            rep("CHR17", 12),
                            rep("CHR18", 12),
                            rep("CHR19", 12),
                            rep("CHR20", 12),
                            rep("CHR21", 12),
                            rep("CHR22", 12)), 2)

all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_mcc <- all_rfperfs %>%
  dplyr::group_by(Testing, Resampling, Predictor) %>%
  dplyr::summarise(MCC = mean(V1, na.rm = TRUE),
            MCCSD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_mcc, aes(x=Predictor, y=MCC, fill=Testing)) +
     #geom_line(size=2, position=position_dodge(0.5))+
     #geom_point(size=5, position=position_dodge(0.5))+
     #geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
     #             position=position_dodge(0.5)) +
     geom_bar(position=position_dodge(), stat="identity", colour='black') +
     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,position=position_dodge(.9)) +
     facet_grid(~ Resampling)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Predictor Type")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

###F1

####Balanced Test

```{r}
F1data_gm12878_10kb_bt <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/rfperf_bt.rds"))

			F1data_gm12878_10kb_bt <- rbind(F1data_gm12878_10kb_bt,
										  perfdata[16,2])
		}
	}
}

```

####Unbalanced Test

```{r}
F1data_gm12878_10kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/rfperf.rds"))

			F1data_gm12878_10kb <- rbind(F1data_gm12878_10kb,
										  perfdata[16,2])
		}
	}
}

```

###Plots

```{r}
all_rfperfs <- rbind.data.frame(F1data_gm12878_10kb_bt,
                                F1data_gm12878_10kb)

all_rfperfs$Testing <- c(rep("Balanced", length(F1data_gm12878_10kb_bt)),
                                rep("Unbalanced", length(F1data_gm12878_10kb)))
all_rfperfs$Predictor <- rep(c("Distance", "OC", "OP"), 168)
all_rfperfs$Resampling <- rep(c(rep("None", 3),
                            rep("ROS", 3),
                            rep("RUS", 3),
                            rep("SMOTE", 3)),42)
all_rfperfs$Chromosome <- rep(c(rep("CHR1", 12),
                            rep("CHR2", 12),
                            rep("CHR3", 12),
                            rep("CHR4", 12),
                            rep("CHR5", 12),
                            rep("CHR6", 12),
                            rep("CHR7", 12),
                            rep("CHR8", 12),
                            rep("CHR10", 12),
                            rep("CHR11", 12),
                            rep("CHR12", 12),
                            rep("CHR13", 12),
                            rep("CHR14", 12),
                            rep("CHR15", 12),
                            rep("CHR16", 12),
                            rep("CHR17", 12),
                            rep("CHR18", 12),
                            rep("CHR19", 12),
                            rep("CHR20", 12),
                            rep("CHR21", 12),
                            rep("CHR22", 12)), 2)

all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_F1 <- all_rfperfs %>%
  dplyr::group_by(Testing, Resampling, Predictor) %>%
  dplyr::summarise(F1 = mean(V1, na.rm = TRUE),
            F1SD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_F1, aes(x=Predictor, y=F1, fill=Testing)) +
     #geom_line(size=2, position=position_dodge(0.5))+
     #geom_point(size=5, position=position_dodge(0.5))+
     #geom_errorbar(aes(ymin=F1-F1SD, ymax=F1+F1SD), width=1,
     #             position=position_dodge(0.5)) +
     geom_bar(position=position_dodge(), stat="identity", colour='black') +
     geom_errorbar(aes(ymin=F1-F1SD, ymax=F1+F1SD), width=.5,position=position_dodge(.9)) +
     facet_grid(~ Resampling)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Predictor Type")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

### 2019-05-31 Scripts/evaluating_model_performances_noenet.Rmd
added results scripts

---
title: "evaluating_model_performances_noenet"
author: "Spiro Stilianoudakis"
date: "May 30, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

# GM12878

##10kb

###MCC

####No elastic-net

```{r}
mccdata_gm12878_10kb_noenet <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/rfperf_noenet.rds"))

			mccdata_gm12878_10kb_noenet <- rbind(mccdata_gm12878_10kb_noenet,
										  perfdata[15,2])
		}
	}
}

```

####With elastic-net

```{r}
mccdata_gm12878_10kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/rfperf.rds"))

			mccdata_gm12878_10kb <- rbind(mccdata_gm12878_10kb,
										  perfdata[15,2])
		}
	}
}

```

###Plots

```{r}
all_rfperfs <- rbind.data.frame(mccdata_gm12878_10kb_noenet,
                                mccdata_gm12878_10kb)

all_rfperfs$Regularization <- c(rep("No", length(mccdata_gm12878_10kb_noenet)),
                                rep("Yes", length(mccdata_gm12878_10kb)))
all_rfperfs$Predictor <- rep(c("Distance", "OC", "OP"), 168)
all_rfperfs$Resampling <- rep(c(rep("None", 3),
                            rep("ROS", 3),
                            rep("RUS", 3),
                            rep("SMOTE", 3)),42)
all_rfperfs$Chromosome <- rep(c(rep("CHR1", 12),
                            rep("CHR2", 12),
                            rep("CHR3", 12),
                            rep("CHR4", 12),
                            rep("CHR5", 12),
                            rep("CHR6", 12),
                            rep("CHR7", 12),
                            rep("CHR8", 12),
                            rep("CHR10", 12),
                            rep("CHR11", 12),
                            rep("CHR12", 12),
                            rep("CHR13", 12),
                            rep("CHR14", 12),
                            rep("CHR15", 12),
                            rep("CHR16", 12),
                            rep("CHR17", 12),
                            rep("CHR18", 12),
                            rep("CHR19", 12),
                            rep("CHR20", 12),
                            rep("CHR21", 12),
                            rep("CHR22", 12)), 2)

all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_mcc <- all_rfperfs %>%
  dplyr::group_by(Regularization, Resampling, Predictor) %>%
  dplyr::summarise(MCC = mean(V1, na.rm = TRUE),
            MCCSD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_mcc, aes(x=Predictor, y=MCC, fill=Regularization)) +
     #geom_line(size=2, position=position_dodge(0.5))+
     #geom_point(size=5, position=position_dodge(0.5))+
     #geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
     #             position=position_dodge(0.5)) +
     geom_bar(position=position_dodge(), stat="identity", colour='black') +
     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,position=position_dodge(.9)) +
     facet_grid(~ Resampling)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Predictor Type")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

###F1

####No elastic-net

```{r}
F1data_gm12878_10kb_noenet <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/rfperf_noenet.rds"))

			F1data_gm12878_10kb_noenet <- rbind(F1data_gm12878_10kb_noenet,
										  perfdata[16,2])
		}
	}
}

```

####With elastic-net

```{r}
F1data_gm12878_10kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/rfperf.rds"))

			F1data_gm12878_10kb <- rbind(F1data_gm12878_10kb,
										  perfdata[16,2])
		}
	}
}

```

###Plots

```{r}
all_rfperfs <- rbind.data.frame(F1data_gm12878_10kb_noenet,
                                F1data_gm12878_10kb)

all_rfperfs$Regularization <- c(rep("No", length(F1data_gm12878_10kb_noenet)),
                                rep("Yes", length(F1data_gm12878_10kb)))
all_rfperfs$Predictor <- rep(c("Distance", "OC", "OP"), 168)
all_rfperfs$Resampling <- rep(c(rep("None", 3),
                            rep("ROS", 3),
                            rep("RUS", 3),
                            rep("SMOTE", 3)),42)
all_rfperfs$Chromosome <- rep(c(rep("CHR1", 12),
                            rep("CHR2", 12),
                            rep("CHR3", 12),
                            rep("CHR4", 12),
                            rep("CHR5", 12),
                            rep("CHR6", 12),
                            rep("CHR7", 12),
                            rep("CHR8", 12),
                            rep("CHR10", 12),
                            rep("CHR11", 12),
                            rep("CHR12", 12),
                            rep("CHR13", 12),
                            rep("CHR14", 12),
                            rep("CHR15", 12),
                            rep("CHR16", 12),
                            rep("CHR17", 12),
                            rep("CHR18", 12),
                            rep("CHR19", 12),
                            rep("CHR20", 12),
                            rep("CHR21", 12),
                            rep("CHR22", 12)), 2)

all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_F1 <- all_rfperfs %>%
  dplyr::group_by(Regularization, Resampling, Predictor) %>%
  dplyr::summarise(F1 = mean(V1, na.rm = TRUE),
            F1SD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_F1, aes(x=Predictor, y=F1, fill=Regularization)) +
     #geom_line(size=2, position=position_dodge(0.5))+
     #geom_point(size=5, position=position_dodge(0.5))+
     #geom_errorbar(aes(ymin=F1-F1SD, ymax=F1+F1SD), width=1,
     #             position=position_dodge(0.5)) +
     geom_bar(position=position_dodge(), stat="identity", colour='black') +
     geom_errorbar(aes(ymin=F1-F1SD, ymax=F1+F1SD), width=.5,position=position_dodge(.9)) +
     facet_grid(~ Resampling)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Predictor Type")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

### 2019-05-31 Scripts/evaluating_model_performances_xgboost.Rmd
added results scripts

---
title: "evaluating_model_performances_xgboost"
author: "Spiro Stilianoudakis"
date: "May 30, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

# GM12878

##10kb

###MCC

####RF; No elastic-net

```{r}
mccdata_gm12878_10kb_rf <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/rfperf_noenet.rds"))

			mccdata_gm12878_10kb_rf <- rbind(mccdata_gm12878_10kb_rf,
										  perfdata[15,2])
		}
	}
}

```

####XGB; no elastic-net

```{r}
mccdata_gm12878_10kb_xgb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/gbmperf_noenet.rds"))

			mccdata_gm12878_10kb_xgb <- rbind(mccdata_gm12878_10kb_xgb,
										  perfdata[15,2])
		}
	}
}

```

###Plots

```{r}
all_rfperfs <- rbind.data.frame(mccdata_gm12878_10kb_rf,
                                mccdata_gm12878_10kb_xgb)

all_rfperfs$Model <- c(rep("RF", length(mccdata_gm12878_10kb_rf)),
                                rep("XGB", length(mccdata_gm12878_10kb_xgb)))
all_rfperfs$Predictor <- rep(c("Distance", "OC", "OP"), 168)
all_rfperfs$Resampling <- rep(c(rep("None", 3),
                            rep("ROS", 3),
                            rep("RUS", 3),
                            rep("SMOTE", 3)),42)
all_rfperfs$Chromosome <- rep(c(rep("CHR1", 12),
                            rep("CHR2", 12),
                            rep("CHR3", 12),
                            rep("CHR4", 12),
                            rep("CHR5", 12),
                            rep("CHR6", 12),
                            rep("CHR7", 12),
                            rep("CHR8", 12),
                            rep("CHR10", 12),
                            rep("CHR11", 12),
                            rep("CHR12", 12),
                            rep("CHR13", 12),
                            rep("CHR14", 12),
                            rep("CHR15", 12),
                            rep("CHR16", 12),
                            rep("CHR17", 12),
                            rep("CHR18", 12),
                            rep("CHR19", 12),
                            rep("CHR20", 12),
                            rep("CHR21", 12),
                            rep("CHR22", 12)), 2)

all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_mcc <- all_rfperfs %>%
  dplyr::group_by(Model, Resampling, Predictor) %>%
  dplyr::summarise(MCC = mean(V1, na.rm = TRUE),
            MCCSD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_mcc, aes(x=Predictor, y=MCC, fill=Model)) +
     #geom_line(size=2, position=position_dodge(0.5))+
     #geom_point(size=5, position=position_dodge(0.5))+
     #geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
     #             position=position_dodge(0.5)) +
     geom_bar(position=position_dodge(), stat="identity", colour='black') +
     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,position=position_dodge(.9)) +
     facet_grid(~ Resampling)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Predictor Type")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

###F1

####RF; No elastic-net

```{r}
F1data_gm12878_10kb_rf <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/rfperf_noenet.rds"))

			F1data_gm12878_10kb_rf <- rbind(F1data_gm12878_10kb_rf,
										  perfdata[16,2])
		}
	}
}

```

####XGB; no elastic-net

```{r}
F1data_gm12878_10kb_xgb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/gbmperf_noenet.rds"))

			F1data_gm12878_10kb_xgb <- rbind(F1data_gm12878_10kb_xgb,
										  perfdata[16,2])
		}
	}
}

```

###Plots

```{r}
all_rfperfs <- rbind.data.frame(F1data_gm12878_10kb_rf,
                                F1data_gm12878_10kb_xgb)

all_rfperfs$Model <- c(rep("RF", length(F1data_gm12878_10kb_rf)),
                                rep("XGB", length(F1data_gm12878_10kb_xgb)))
all_rfperfs$Predictor <- rep(c("Distance", "OC", "OP"), 168)
all_rfperfs$Resampling <- rep(c(rep("None", 3),
                            rep("ROS", 3),
                            rep("RUS", 3),
                            rep("SMOTE", 3)),42)
all_rfperfs$Chromosome <- rep(c(rep("CHR1", 12),
                            rep("CHR2", 12),
                            rep("CHR3", 12),
                            rep("CHR4", 12),
                            rep("CHR5", 12),
                            rep("CHR6", 12),
                            rep("CHR7", 12),
                            rep("CHR8", 12),
                            rep("CHR10", 12),
                            rep("CHR11", 12),
                            rep("CHR12", 12),
                            rep("CHR13", 12),
                            rep("CHR14", 12),
                            rep("CHR15", 12),
                            rep("CHR16", 12),
                            rep("CHR17", 12),
                            rep("CHR18", 12),
                            rep("CHR19", 12),
                            rep("CHR20", 12),
                            rep("CHR21", 12),
                            rep("CHR22", 12)), 2)

all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_F1 <- all_rfperfs %>%
  dplyr::group_by(Model, Resampling, Predictor) %>%
  dplyr::summarise(F1 = mean(V1, na.rm = TRUE),
            F1SD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_F1, aes(x=Predictor, y=F1, fill=Model)) +
     #geom_line(size=2, position=position_dodge(0.5))+
     #geom_point(size=5, position=position_dodge(0.5))+
     #geom_errorbar(aes(ymin=F1-F1SD, ymax=F1+F1SD), width=1,
     #             position=position_dodge(0.5)) +
     geom_bar(position=position_dodge(), stat="identity", colour='black') +
     geom_errorbar(aes(ymin=F1-F1SD, ymax=F1+F1SD), width=.5,position=position_dodge(.9)) +
     facet_grid(~ Resampling)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Predictor Type")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

```

### 2019-06-01 Papers.Rmd
Add DeepMILO paper

@@
 https://doi.org/10.1093/nar/gkz315.
+
+- Trieu, Tuan, and Ekta Khurana.
+“A Deep Learning Approach to Predict the Impact of Non-Coding Sequence Variants on 3D Chromatin Structure.” BioRxiv, January 1, 2019, 516849.
+https://doi.org/10.1101/516849.
+- DeepMILO - learn TAD boundaries and predict the effect of genomic variants on them.
+Convolutional and recurrent neural networks (CNN, RNN), distinguishes CTCF and cohesin vs.
+CTCF only.
+Trained on experimental CTCF peaks overlapping RAD21 peaks (Gm12878).
+CTCF orientation is important, Figure 2a, detected by FIMO tool. https://github.com/tuantrieu/DeepMILO
 

### 2019-06-03 Manuscript/manuscript.Rmd
manuscript edits; reordering figures

@@
 **Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter simply as $\textit{distance}$), from the center of the bin to the center of the nearest region defined by a specific genomic annotation was calculated.
-The log transformation was used as a normalization technique in order to account for the skewness present in the distance densities (Supplementary Figures 1-2).
 
@@
 
-## ENSEMBLE FRAMEWORK & COMPARISONS
-
-To systematically summarize and compare our results of data driven random forest models, we created an ensemble framework (Figure 1).
-Each system in the framework was assumed to be composed of a model constructed from a particular cell line, $L = \{GM12878, K562\}$.
-Within each cell line we evaluated 4 data resolutions, $R = \{10 kb, 25 kb, 50 kb, 100 kb\}$.
-We then considered 3 separate predictor types as the feature space including $P = \{OC, OP, Distance\}$.
-To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including $B = \{None, RUS, ROS, SMOTE\}$.
-Each combination of the above parameters was implemented on chromosome specific sections of the linear genome.
-Performances were then aggregated across each of the 21 chromosomes (omitting chromosome 9).
-Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling 2016 ($2 \times 4 \times 3 \times 4 \times 21$) separate models.
-We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.
-
 # RESULTS
 
-## IMBALANCE RATIOS REMAINED SEVERE irrespectively of RESOLUTION of Hi-C data
+## IMBALANCE RATIOS REMAINED SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION
 
@@
 [@rao20143d].
-Topologically associating domains were then identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions, for each cell line respectively.
-We then established a unified approach toward preparing cell line specific TAD boundary data for predictive modelling purposes, irrespective of data resolutions (Figure 2).
+Topologically associating domains were identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions, for each cell line respectively.
+We then established a unified approach toward preparing cell line specific TAD boundary data for predictive modelling purposes, irrespective of data resolutions (Figure 1).
 
@@
 
+<!--
 ## HIGH JACCARD INDICES IMPLY COLOCALIZATION OF MANY GROUP-SPECIFC ANNOTATIONS 
+-->
+
+## ESTABLISHING THE FEATURE SPACE USING INCREASINGLY GRANULAR RELATIONSHIPS BETWEEN FUNCTIONAL ANNOTATIONS AND GENOMIC BINS
 
@@
 
+<!--
 Using the Jaccard index, we found that specific sets of these cell line-specific annotations were highly colocalized together on the linear genome (Table 3).
@@
 This gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space of all annotations while retaining the possibly correlated annotations that could be predictive of TAD boundary formation.
+-->
 
-To establish said feature space for all downstream random forest models, we constructed 3 different predictor-types.
+To establish the feature space for all downstream models, we constructed 3 different predictor-types.
 These predictor-type specific annotations represented the data matrix, $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
-Overlap counts was the least granular predictor-type considered, simply defined by the number of annotation-specific regions located within each genomic bin (Figure 3A).
-Overlap percents was a more refined predictor-type, defined as the total percent overlap between each annotation-specific region and genomic bins (Figure 3B).
-Lastly, distances, the most granular predictor-type, described the spatial relationship between the center of each genomic bin to the center of the nearest annotation-specific region (Figure 3C).
+Overlap counts was the least granular predictor-type considered, simply defined by the number of annotation-specific regions located within each genomic bin (Figure 2A).
+Overlap percents was a more refined predictor-type, defined as the total percent overlap between each annotation-specific region and genomic bins (Figure 2B).
+Lastly, distances, the most granular predictor-type, described the spatial relationship between the center of each genomic bin to the center of the nearest annotation-specific region (Figure 2C).
+A $log_{2}}$ transformation was used as a normalization technique in order to account for the skewness present in the distance densities (Supplementary Figures 1-2).
+
+## ENSEMBLE FRAMEWORK & COMPARISONS
+
+To systematically summarize and compare our results of data driven random forest models, we created an ensemble framework (Figure 3).
+Each system in the framework was assumed to be composed of a model constructed from a particular cell line, $L = \{GM12878, K562\}$.
+Within each cell line we evaluated 4 data resolutions, $R = \{10 kb, 25 kb, 50 kb, 100 kb\}$.
+We then considered 3 separate predictor types as the feature space including $P = \{OC, OP, Distance\}$.
+To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including $B = \{None, RUS, ROS, SMOTE\}$.
+Each combination of the above parameters was implemented on chromosome specific sections of the linear genome.
+Performances were then aggregated across each of the 21 chromosomes (omitting chromosome 9).
+Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling 2016 ($2 \times 4 \times 3 \times 4 \times 21$) separate models.
+We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.
 

### 2019-06-03 Manuscript/Figures/figure_legends.Rmd
editted order and legend for figure 1

@@
 
-**Figure 1.
-Ensemble Framework.** A diagram of the cell line specific ensemble framework detailing the various combination of inputs used in the model building pipeline.
-The minoirty and majority classes were represented by the genomic bins that overlapped with flanked TAD boundaries or did not, respectively.
-Functional genomic annotations obtained from the UCSC Genome Browser Database composed the feature space.
-The data was split into a 7:3 training to testing set ratio.
-A feature engineering step was included to isolate the spatial relationship, of increasing granularity, between annotations and genomic bins.
-Data re-sampling and regularization was applied to the training data.
-Lastly, a random forest classification algorithm was implemeted and validated on the testing data.
-
 <!--
@@
 
-**Figure 2.
+**Figure 1.
 Model Construction.** An illustration of the proposed model construction given cell line specific Hi-C data.
@@
 
-**Figure 3.
+**Figure 2.
 Predictor types.** Three separate types of predictors were considered when quantifying the association between TAD boundaries and genomic annotations.
@@
 (C) _Distance_ ($log_{2}$ transformed) was calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest region defining a genomic annotation.
+
+**Figure 3.
+Ensemble Framework.** A diagram of the cell line specific ensemble framework detailing the combination of inputs used in the model building pipeline.
+The minoirty and majority classes were represented by the genomic bins that overlapped with flanked TAD boundaries or did not, respectively.
+Functional genomic annotations obtained from the UCSC Genome Browser Database composed the feature space ($X = \{X_1, X_2, ..., X_p\}$).
+A feature engineering step was included to isolate the predictor-type specific spatial relationship between annotations and genomic bins in increasing granularity, denoted by the red gradient.
+The data was split into a 7:3 training to testing set ratio.
+Data re-sampling was then applied to the training set.
+Lastly, a random forest classification algorithm was implemeted and validated on the testing data.
 

### 2019-06-04 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-## IMBALANCE RATIOS REMAINED SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION
+## Cell line and Data Resolution Specific Model Construction
 
@@
 Topologically associating domains were identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions, for each cell line respectively.
-We then established a unified approach toward preparing cell line specific TAD boundary data for predictive modelling purposes, irrespective of data resolutions (Figure 1).
-
+We then established a unified approach toward preparing cell line and resolution specific TAD boundary data for predictive modelling purposes (Figure 1).
 To enable us to build a model that suitably discriminated between regions on the linear genome that were near TAD boundaries and regions that were not, we created a  resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$).
@@
 Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.
+
+## IMBALANCE RATIOS REMAINED SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION
 

### 2019-06-04 Manuscript/manuscript.Rmd
specified tuning in methods

@@
 
+<!--
 ### FEATURE REDUCTION
@@
 <!--The parameters that maximized the mean AUPRC across each cross-fold was chosen.--> All elastic-net algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
+-->
 
@@
 Once the appropriate predictor type and set of features were determined, a final set of random forest classification models were built to compare model performances between re-sampling techniques and predictor types.
-<!--To reduce bias due to random dataset generation, 10-fold cross validation was used to tune the number of features to consider at each node and the number of ensemble trees to aggregate.--> The default number of features to consider at each node of the random forest algorithm was set as $\sqrt{p}$, where *p* refers to the number of predictors included in the model.
-Likewise, the number of ensemble trees to aggregate was set at 500.
+To reduce bias due to random dataset generation, 10-fold cross validation was used to tune the number of features, *p*, to consider at each node.
+The number of trees that were aggregated for each random forest model was set to the default, n=500.
 All random forest algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
@@
 
-To systematically summarize and compare our results of data driven random forest models, we created an ensemble framework (Figure 3).
-Each system in the framework was assumed to be composed of a model constructed from a particular cell line, $L = \{GM12878, K562\}$.
+We created an ensemble framework to systematically compare different data driven characteristics to identify the optimal set of parameters when predicting TAD boundaries using functional genomic annotations (Figure 3).
+Each system in the framework was assumed to be composed of a random forest model constructed from a particular cell line, $L = \{GM12878, K562\}$.
 Within each cell line we evaluated 4 data resolutions, $R = \{10 kb, 25 kb, 50 kb, 100 kb\}$.
@@
 
-We then went on the evaluate the effect of class imbalance on model performance.
-In order to set a baseline in performance, we first evaluated the least granular model, that is one implemented using OC predictor types, without data re-sampling.
+<!--We then went on the evaluate the effect of class imbalance on model performance.--> In order to set a baseline in performance, we first evaluated the least granular model, that is one implemented using OC predictor types, without data re-sampling.
 We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 4A).
@@
 Furthermore, we found that conventional metrics of performance (i.e.
-accuracy, sensitivity and specificity, and AUC) were less sensitive for models built on imbalanced data, regardless of cell line, resolution, or predictor-type (Supplementary Tables 6-7).
-[???
-Need to know why PRCs give different results.]
+accuracy, sensitivity and specificity, and AUC) were less sensitive to models built on imbalanced data, regardless of cell line, resolution, or predictor-type (Supplementary Tables 6-7).
 

### 2019-06-04 Manuscript/manuscript.Rmd
full edits

--- 2019-06-03 Manuscript/manuscript.Rmd
@@
 Even more so, loci within a domain have been shown to interact more frequently with one another, exhibiting similar patterns of chromatin modifications, and long-range contact patterns [@rao20143d].
-However, the growing number of annotated genomic features and the methods used to identify the ones assocaited with TAD boundaries still leaves much to be desired.
+However, the growing number of annotated genomic features and the methods used to identify the ones associated with TAD boundaries still leaves much to be desired.
 
 Current methods used to predict TAD boundaries rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries.
-However, this is a multi-faceted probelem, and many methods ignore key characteristics of domain data when building models and reporting performances.
-We aim to address these characteristics in order to create a more unified approach toward identifyig the genomic annotations most predictive of TAD boundaries.
+However, this is a multi-faceted probelem, and many methods ignore key characteristics [??
+which ones ??] of domain data when building models and reporting performances.
+We aim to address these characteristics in order to create a more unified approach toward identifying the genomic annotations most predictive of TAD boundaries.
 
@@
 The imbalance ratio is defined as the ratio of minority to majority classes [@Orriols-Puig2008].
-Such heavily imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class; @chen2013influence; @jeni2013facing].
+Such heavily imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class; @chen2013influence; @jeni2013facing] [??
+This sentence is very difficult to understand.
+Don't see connection between the bias and the error rate ??].
 
@@
 This is problematic in an imbalanced setting.
-Such heavily imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class; @chen2013influence; @jeni2013facing].
+Such heavily imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class; @chen2013influence; @jeni2013facing] [??
+This is the second mention of "biased towards the majority class to minimize the overall error rate" without strong explanation of what this means ??].
 For AUC, when the prevalence of an event is low--that is, a defined genomic region truly containing a TAD boundary--mean probabilities are biased towards the majority class.
 This results in the area of interest under an ROC curve to be compressed toward a small corner in the ROC space [@prati2011survey; @wei2013role].
-While not directly affecting the value of the AUROC, this can have severe consequences on the interpretability of the model's performance.
+While not directly affecting the value of the AUROC, this can have severe consequences on the interpretability of the model's performance [??
+How so?
+does it inflate it or deflate it or what ??].
 Consequently, careful consideration must be taken when deciding which performance metric(s) to use for evaluation of predictive models, especially in the case of imbalanced data.
@@
 The interpretation of the AUPRC of a model is similar to that of the AUROC.
-However, where as the baseline model performance according to the AUROC is given by 0.50, the baseline model performance according to the AUPRC is given by the ratio of true positives over the total number of cases.
+However, where as the baseline model performance according to the AUROC is given by 0.50, the baseline model performance according to the AUPRC is given by the ratio of true positives over the total number of cases [??
+Need to identify what you mean by "total number of cases." Is it just true positive divided by total number of possible boundaries ??].
 This enables a more realistic benchmark to evaluate a model on as this ratio will be lower than 0.5 for a test data set with imbalanced classes [@saito2015precision].
-Another threshold-specific measure to consider is a composite metric involving all quadrants of the confusion matirix, such as Matthews Correlation Coefficient (MCC) [@jeni2013facing; @chicco2017ten].
+Another threshold-specific measure to consider is a composite metric involving all quadrants of the confusion matrix, such as Matthews Correlation Coefficient (MCC) [@jeni2013facing; @chicco2017ten] [??
+MCC actually has all of the same components as AUC.
+AUC is a function of sensitivity and specificity which combined contain all quandrants ??].
 The MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
-A value of positive 1 represents a perfect prediction, while a value of negative 1 represents total disagreement between prediction and observation.
+A value of 1 represents a perfect prediction, while a value of -1 represents total disagreement between prediction and observation.
 A value of 0 indicates no better than random prediction.
 
-In addition to employing suitable metrics for evaluating models validated on imbalanced data, there also exists several data level solutions.
-Data level solutions mostly constitute as re-sampling techniques, in which random sampling is used to either replicate or remove data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
+We can account for imbalance at the data level in addition to at the evaluation level [??
+I rewrote this sentence.
+Was very wordy and difficult to follow ??].
+Data level solutions mostly constitute as [??
+I'd change "constiute as", unorthodox word choice ??] re-sampling techniques, in which random sampling is used to either replicate or remove data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
 It has been shown that quite simple re-sampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
+[??
+It feels like data level should come before evaluation level ??]
 
@@
 However, given the large disparity between the number of genomic regions labeled as containing a TAD boundary or not, performing random under-sampling alone is likely to be unstable and introduce bias.
-Also, it is unclear how other data level solutions compare to simple random under-sampling, for instance random over-sampling or a weighted combination of both random under- and over-sampling together.
+Also, it is unclear how other data level solutions compare to simple random under-sampling such as random over-sampling or a weighted combination of both random under- and over-sampling together.
 Equally concerning is how the test set is treated in scenarios of re-sampling.
@@
 
-Therefore, in this study, we aimed to develop an ensemble framework composed of different combinations of data driven characteristics used to address the issues presented above.
+In this study, we aimed to develop an ensemble framework composed of different combinations of data driven characteristics used to address the issues presented above.
 We used our framework to systematically compare performances of random forest classifiers using a composite performance metric, MCC.
-Our goal was to determine a suitable combination of data re-sampling and feature engineering techniques that both corrected the inherent imbalanced classes and provided the best spatial representation linking genomic annotations to TAD boundaries.
+Our goal was to determine a suitable combination of data re-sampling and feature engineering techniques that both corrected the inherent imbalanced classes and provided the best spatial representation [??
+Not sure what spatial representation means in this context ??] linking genomic annotations to TAD boundaries.
 Additionally, we used our framework to directly compare the influence of Hi-C contact matrix resolution on model performances.
 We evaluated Hi-C data for both the GM12878 and K562 cell line obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolution.
+[??
+It feels like some stronger statements need to be here.
+I would make a statement about predicting TAD regions using genomic annotations instead of using terms like "linking".
+It feels like the focus should be on this and not model selection which occurs in any analysis ??]
 
-For each resolution, we examined the inclusion of three different predictor types, including distance as the measure of association between genomic elements.
+For each resolution, we examined the inclusion of three different predictor types [??
+Maybe list all 3 (.e.g "For each resolution, we examined the inclusion of three different predictor types: counts, percentages and distances.") ??], including distance as the measure of association between genomic elements.
 We then tested four different re-sampling techniques aimed at creating balanced classes.
@@
 The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
-The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained for the autosomal chromosomes.
-TAD boundaries called on Chromosome 9 were omitted from all downstream analyses, for both cell lines, due to the sparcity of the contact matrix at the 10 kb resolution for the K562 cell line.
+The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained for the autosomal chromosomes [??
+Don't think sentence is necessary ??].
+TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for both cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
 
@@
 
-To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution for the corresponding contact matrix.
+To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution of the corresponding contact matrix.
 As an example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
@@
 Otherwise, the bin was labeled as not containing a boundary (Y=0).
-The process was repeated for each subsequent resolution.
+The process was repeated for each subsequent resolution [??
+Don't think this sentence is needed ??].
 
@@
 Values for bins with no overlaps were set to be 0.
+[??
+This entire section feels extremely wordy.
+Probably can reduce to a couple sentences ??]
 
@@
 The quantity ranges from 0.0 to 1.0, where 0.0 represents no overlap (no correlation) and 1.0 represent complete overlap (complete correlation).
+[??
+Jaccard is a distance measure, I would avoid using the term correlation here ??]
 
@@
 The technique using a combination of the *l_{1}* and *l_{2}* penalties.
-For each elastic-net regularization, 10-fold cross-validation was used to tune the parameters that controlled the penalty terms.
+For each elastic-net regularization [??
+It would help to describe why you used elastic-net and not ridge regression or lasso.
+Are you particularly concerned about bias/variance ??], 10-fold cross-validation was used to tune the parameters that controlled the penalty terms.
 <!--The parameters that maximized the mean AUPRC across each cross-fold was chosen.--> All elastic-net algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
@@
 Once the model was implemented, it was validated on the test set.
+[??
+Don't think this sentence is necessary.
+Its implied you will run the model ??]
 
@@
 
-$$MCC = \frac{TP \times TN - FP \times FN}{\sqrt{ (TP + FP)(TP+FN)(TN+FP)(TN+FN) }}$$
+$$
+MCC = \frac{TP \times TN - FP \times FN}{\sqrt{ (TP + FP)(TP+FN)(TN+FP)(TN+FN) }}
+$$
 <!--
@@
 
-To enable us to build a model that suitably discriminated between regions on the linear genome that were near TAD boundaries and regions that were not, we created a  resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$).
-The unit width of each bin on the linear genome corresponded to the resolution of the cell line specific contact matrix on which domains were called.
+To enable us to build a model that suitably discriminated between regions on the linear genome that were near TAD boundaries and regions that were not, we created a  resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$) [??
+extremely wordy sentence, can reduce ??].
+The unit width of each bin on the linear genome corresponded to the resolution of the contact matrix on which domains were called.
 Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.
@@
 Expectedly, the median number of genomic bins, TADs called, and TAD boundaries increased with the increased resolution of cell-line specific Hi-C data (Table 1; Supplementary Tables 3).
-This correlation with resolution was found to be significant, as evidenced by large intraclass correllation coefficients (ICC) (Table 2; Supplementary Tables 4).
+This correlation [??
+What correlation ??] with resolution was found to be significant, as evidenced by large intraclass correlation coefficients (ICC) (Table 2; Supplementary Tables 4).
 However, the class imbalance problem, caused by the sparsity of TAD boundaries throughout the genome, was found to be much more consistant across resolutions in both cell lines.
@@
 To establish the feature space for all downstream models, we constructed 3 different predictor-types.
-These predictor-type specific annotations represented the data matrix, $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
-Overlap counts was the least granular predictor-type considered, simply defined by the number of annotation-specific regions located within each genomic bin (Figure 2A).
-Overlap percents was a more refined predictor-type, defined as the total percent overlap between each annotation-specific region and genomic bins (Figure 2B).
+These predictor-type specific annotations represented the data matrix, $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations [??
+$p$ is actually the total number of functional annotations, $X_i$ is the functional annotation itself ??].
+Overlap counts was the least granular [??
+Maybe define granular ??] predictor-type considered, simply defined by the number of annotation-specific regions located within each genomic bin (Figure 2A).
+Overlap percents was a more refined [??
+what is refined in this context ??] predictor-type, defined as the total percent overlap between each annotation-specific region and genomic bins (Figure 2B).
 Lastly, distances, the most granular predictor-type, described the spatial relationship between the center of each genomic bin to the center of the nearest annotation-specific region (Figure 2C).
 A $log_{2}}$ transformation was used as a normalization technique in order to account for the skewness present in the distance densities (Supplementary Figures 1-2).
+[??
+Why would skewness matter, why not use raw data ??]
 
@@
 We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.
+[??
+Where does variable selection come into play here??]
 
@@
 We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 4A).
-We gradually increased the granularity by assessing models built on OP predictor types, while still not performing any data resampling.
+We gradually increased the granularity [??
+Really confused by the constant use of granularity.
+Why is it needed ??] by assessing models built on OP predictor types, while still not performing any data resampling.
 Here, the results were similar to that of OC types (Figure 4B).
@@
 When assessing performances for models built on balanced data, we found that SMOTE re-sampling provided the optimal MCC consistently across both predictor type and resolution (Figure 4).
-Specifically, the most improvement in model performance was seen when combining SMOTE re-sampling with distance-type predictors.
+Specifically, the most improvement in model performance [??
+Over what ??] was seen when combining SMOTE re-sampling with distance-type predictors.
 This was also the optimal combination for the K562 cell line (Supplementary Figure 3).
-These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
+These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries [??
+Is this what you are doing?
+Or are you identifying TAD boundaries themselves ??], is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
 Moreover, there was a clear degredation in model performance as data resolution decreased.
@@
 
-After determining the optimal set of data level characteristics, we then aimed to compare the performances of annotation-specifc models.
+After determining the optimal set of data level characteristics, we then aimed to compare the performances of annotation-specifc models [??
+In methods you say you do "feature selection" and then test model types.
+This implies the opposite ??].
 In doing so, we inspected the proportion of predictive importance that was explained by each of the 3 groups of annotations (chromatin states, histone modifications, and transcription factor binding sites), across resolution.
@@
 We then sought to determine which of the transcription factor binding sites were most influential in predicting TAD boundaries.
-We found that the cell line specific binding sites associated with SMC3, CTCF, RAD21, ZNF143, and YY1sc281 were given consistently high predictive importance, across all resolutions (Figure 7; Supplementary Figure 6).
+We found that the cell line specific binding sites associated with SMC3, CTCF, RAD21, ZNF143, and YY1sc281 were given consistently high predictive importance, across all resolutions [??
+Is this after elastic net?
+Elastic net distributes coefficients between correlated variables and it may affect variable importance ??] (Figure 7; Supplementary Figure 6).
 The SMC3, CTCF, and RAD21 binding sites are known factors associated with the cohesin protein complex, which is hypothesized to be what creates loops in the DNA  [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
-Likwise, ZNF143 and YY1 are known structural regulators of enhancer-promoter interactions that also contribute to looping of the linear genome [@weintraub2017yy1; @gonzalez2017znf143].
+Likewise, ZNF143 and YY1 are known structural regulators of enhancer-promoter interactions that also contribute to looping of the linear genome [@weintraub2017yy1; @gonzalez2017znf143].
 With the identification of these factors known to be enriched at TAD boundaries, we are able to confirm the validity of our model building process.
@@
 This was done so as to incur the least amount of bias and so that all conclusions could be made soley between model characteristics.
-As a result, we showed that Matthews Correlation Coefficient was much more sensitive to the imbalance present in the test set, compared to more popular metrics like AUROC, which attain artificially high values by correctly predicting majority class samples.
+As a result, we showed that Matthews Correlation Coefficient was much more sensitive to the imbalance present in the test set, compared to more popular metrics like AUROC, which attain artificially high values by correctly predicting majority class samples [??
+I may be mistaken but I don't see where this is proven ??].
 When comparing re-sampling techniques, we found that SMOTE re-sampling outperformed models built on both simple ROS or RUS, implying that, in fact, a combination of both random under-sampling and random over-sampling is preferred in TAD boundary prediction.
-Furthermore, the most improvement was seen when combining SMOTE resampling on distance-type features when building random forest classifiers.
-These two characteristics exhibited consistenly better performance results across both the GM12878 and K562 cell lines.
+Furthermore, the most improvement [??
+Over what ??] was seen when combining SMOTE resampling on distance-type features when building random forest classifiers.
+These two characteristics exhibited consistently better performance results across both the GM12878 and K562 cell lines.
 This confirmed our hypothesis that the most granular and spatially informative representation of the relationship between TAD boundaries and annotations resulted in the best performing model.
@@
 This result can be attributed to one of two factors in the scheme of our framework.
-First, at higher resolutions, by model construction genomic bins were smaller, thereby resulting in more accurate profiles for the genomic annotations.
-Secondly, because we are mainly concerned with TAD boundaries, and not the heirarchical structure of domains as a whole, the sparcity of contact matrices at higher resolutions does not impair boundary prediction.
+First, at higher resolutions, by model construction genomic bins were smaller, thereby resulting in more accurate profiles for the genomic annotations [??
+Don't understand this sentence ??].
+Secondly, because we are mainly concerned with TAD boundaries, and not the hierarchical structure of domains as a whole, the sparsity of contact matrices at higher resolutions does not impair boundary prediction [??
+Doesn't this contradict your results about low resolution causing worse boundary prediction ??].
 Conversely, lower resolutions imply larger bin windows and lead to less specificity in boundary location on the linear genome, resulting in worse performances.
-Given the trend in performances across resolution, future research is necessary in determining the optimal resolution to use when predicting TAD boundaries.
+Given the trend in performances across resolution, future research is necessary in determining the optimal resolution to use when predicting TAD boundaries [??
+Might want to qualify the statement in results about 10kb data being best by saying that it only applies to your data ??].
 
@@
 In summary, we have shown that TAD boundary prediction is a multi-faceted problem composed of many data irregularities and characteristics that previous model have failed to address.
-We have shown that our proposed framework suitably addresses each of these components, while also providing the optimal considerations to make in an effort to build consensus classifiers used to predict TAD boundary formation from functional genomic annotations.
+We have shown that our proposed framework suitably addresses each of these components, while also providing the optimal considerations to make in an effort to build consensus classifiers used to predict TAD boundary formation [??
+formation or location.
+Formation implies some temporal element ??] from functional genomic annotations.
 Given the stability of our results, this opens up the possibility of widening our framework to include a broader set of classifiers, cell lines, and Hi-C contact matix resolutions that will inevitably assist us in gaining a better understanding of the mechanisms associated with the architecture of the human genome.

### 2019-06-04 Manuscript/manuscript.Rmd

@@
 The technique using a combination of the *l_{1}* and *l_{2}* penalties.
-For each elastic-net regularization [??
-It would help to describe why you used elastic-net and not ridge regression or lasso.
-Are you particularly concerned about bias/variance ??], 10-fold cross-validation was used to tune the parameters that controlled the penalty terms.
+For each elastic-net regularization, 10-fold cross-validation was used to tune the parameters that controlled the penalty terms.
 <!--The parameters that maximized the mean AUPRC across each cross-fold was chosen.--> All elastic-net algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
+-->
 
@@
 All random forest algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
-Once the model was implemented, it was validated on the test set.
-[??
-Don't think this sentence is necessary.
-Its implied you will run the model ??]
 
@@
 Topologically associating domains were identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions, for each cell line respectively.
-We then established a unified approach toward preparing cell line specific TAD boundary data for predictive modelling purposes, irrespective of data resolutions (Figure 1).
+We then established a unified approach toward preparing cell line and resolution specific TAD boundary data for predictive modelling purposes (Figure 1).
+To enable us to build a model that suitably discriminated between regions on the linear genome that were near TAD boundaries and regions that were not, we created a  resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$).
+The unit width of each bin on the linear genome corresponded to the resolution of the cell line specific contact matrix on which domains were called.
+Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.
 
-To enable us to build a model that suitably discriminated between regions on the linear genome that were near TAD boundaries and regions that were not, we created a  resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$) [??
-extremely wordy sentence, can reduce ??].
+## IMBALANCE RATIOS REMAINED SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION
+
+We created a  resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$).
 The unit width of each bin on the linear genome corresponded to the resolution of the contact matrix on which domains were called.
 Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.
-
 Expectedly, the median number of genomic bins, TADs called, and TAD boundaries increased with the increased resolution of cell-line specific Hi-C data (Table 1; Supplementary Tables 3).
@@
 We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.
-[??
-Where does variable selection come into play here??]
+
+## CLASS IMBALANCE SEVERELY IMPACTS MODEL PERFORMANCE
+
+<!--We then went on the evaluate the effect of class imbalance on model performance.--> In order to set a baseline in performance, we first evaluated the least granular model, that is one implemented using OC predictor types, without data re-sampling.
+We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 4A).
+We gradually increased the granularity by assessing models built on OP predictor types, while still not performing any data resampling.
+Here, the results were similar to that of OC types (Figure 4B).
+However, when including distance-type predictors, models were found to exhibit a marked improvement in MCC compared to the other two types (Figure 4C).
+Results were found to be consistently poor across resolutions and predictor types, when implemented on the K562 cell line (Supplementary Figure 3).
+Furthermore, we found that conventional metrics of performance (i.e.
+accuracy, sensitivity and specificity, and AUC) were less sensitive to models built on imbalanced data, regardless of cell line, resolution, or predictor-type (Supplementary Tables 6-7).
 

### 2019-06-04 Manuscript/manuscript.Rmd
addressing kellen comments

@@
 The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
-The start and end coordinates of all TADs were concatenated, sorted, and unique TAD boundary points were obtained for the autosomal chromosomes [??
-Don't think sentence is necessary ??].
 TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for both cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
@@
 Genomic annotation data in the form of cell type specific chromatin states, histone marks, and transcription factor binding sites (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 2).
+Functional annotations were represented by chromosome-specific regions on the linear genome obtained by ChIP-seq peak calling algorithms.
 
@@
 Otherwise, the bin was labeled as not containing a boundary (Y=0).
-The process was repeated for each subsequent resolution [??
-Don't think this sentence is needed ??].
 
@@
 
-Using the sets of cell line specific genomic annotations, we created three types of predictors that were used as features for subsequent models to analyze their respective spatial relationship with TAD boundaries.
+Using the sets of cell line specific genomic annotations, we created three types of predictors that were used to describe the spatial relationship with genomic bins, $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
 They are described in detail below:
 
-1.
-**Overlap Counts (OC)**: For each genomic bin, the total number of instances where a bin overlapped with regions assigned to genomic annotations (features) was calculated.
-In the case of no overlaps, the value was set to 0.
+1. **Overlap Counts (OC)**: For each genomic bin, the total number of instances where a bin overlapped with regions assigned to genomic annotations (features) was calculated.
 
@@
 We defined the feature width as the number of bases that overlapped with a particular genomic bin.
-The percent was then calculated by dividing the feature width by the bin width.
 If multiple overlaps existed, the feature width was defined as the sum of the total number of bases that overlapped with a particular bin.
-Note that the bin width remained constant for a given resolution (either 10 kb, 25 kb, 50 kb, or 100 kb).
-Values for bins with no overlaps were set to be 0.
-[??
-This entire section feels extremely wordy.
-Probably can reduce to a couple sentences ??]
 
@@
 
-The cell line- and resolution-specific data was then split into a 7:3 ratio of training to testing sets.
+The cell line- and resolution-specific data, composed of the responsed vector and predictor-type specific data matrix  then split into a 7:3 ratio of training to testing sets.
 Furthermore, for the task of performance evaluation and prediction, the test set remained constant for all ensemble systems to account for an unbiased comparison.
@@
 
-## Cell line and Data Resolution Specific Model Construction
+## CELL LINE AND DATA RESOLUTION SPECIFIC MODEL CONSTRUCTION
 

### 2019-06-04 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-Using the sets of cell line specific genomic annotations, we created three types of predictors that were used to describe the spatial relationship with genomic bins, $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
+Using the sets of cell line specific genomic annotations, we created three types of predictors that were used to describe the spatial relationship with genomic bins, $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
 They are described in detail below:
@@
 
-The cell line- and resolution-specific data, composed of the responsed vector and predictor-type specific data matrix  then split into a 7:3 ratio of training to testing sets.
-Furthermore, for the task of performance evaluation and prediction, the test set remained constant for all ensemble systems to account for an unbiased comparison.
+The cell line- and resolution-specific data, composed of the response vector and predictor-type specific data matrix (**X**), was then split into a 7:3 ratio of training to testing sets.
+For the task of performance evaluation and prediction, the test set remained constant to account for an unbiased comparison between data level characteristics.
 
@@
 For each elastic-net regularization, 10-fold cross-validation was used to tune the parameters that controlled the penalty terms.
-<!--The parameters that maximized the mean AUPRC across each cross-fold was chosen.--> All elastic-net algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
+All elastic-net algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
 -->
@@
 
-Once the appropriate predictor type and set of features were determined, a final set of random forest classification models were built to compare model performances between re-sampling techniques and predictor types.
-<!--To reduce bias due to random dataset generation, 10-fold cross validation was used to tune the number of features to consider at each node and the number of ensemble trees to aggregate.--> The default number of features to consider at each node of the random forest algorithm was set as $\sqrt{p}$, where *p* refers to the number of predictors included in the model.
-Likewise, the number of ensemble trees to aggregate was set at 500.
+random forest classification models were built to compare model performances between re-sampling techniques and predictor types.
+To reduce bias due to random dataset generation, 10-fold cross validation was used to tune the number of annotations, *p*, to consider at each node.
+The number of trees that were aggregated for each random forest model was set to the default, n=500.
 All random forest algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
-
-The performance of each ensemble system in the framework was compared using the composite metric, Matthews Correlation Coefficient. The MCC is defined as follows:
+Once the model was implemented, it was validated on the test set.
+The performance of each ensemble system in the framework was compared using the composite metric, Matthews Correlation Coefficient (MCC), which is defined as follows:
 
@@
 To establish the feature space for all downstream models, we constructed 3 different predictor-types.
-These predictor-type specific annotations represented the data matrix, $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations [??
+These predictor-type specific annotations represented the data matrix, $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations [??
 $p$ is actually the total number of functional annotations, $X_i$ is the functional annotation itself ??].

### 2019-06-04 Manuscript/Figures/figure_legends.Rmd

@@
 The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region ($Y=1$) or not ($Y=0$).
-The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
+The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
 
@@
 The minoirty and majority classes were represented by the genomic bins that overlapped with flanked TAD boundaries or did not, respectively.
-Functional genomic annotations obtained from the UCSC Genome Browser Database composed the feature space ($X = \{X_1, X_2, ..., X_p\}$).
+Functional genomic annotations obtained from the UCSC Genome Browser Database composed the feature space ($\textbf{X} = \{X_1, X_2, ..., X_p\}$).
 A feature engineering step was included to isolate the predictor-type specific spatial relationship between annotations and genomic bins in increasing granularity, denoted by the red gradient.

### 2019-06-04 Manuscript/manuscript.Rmd

@@
 output:
+  pdf_document: default
   word_document:
     reference_docx: styles.doc/NIH_grant_style.docx
-  pdf_document: default
 bibliography: References/references.bib
@@
 
+![**Model Construction.** An illustration of the proposed model construction given cell line specific Hi-C data.
+Above is an example of a subsection of the contact matrix for chromosome 14 (at megabase scale) on GM12878 [@durand2016juicer].
+The contact matrix is a visualization of the interconnectivity of the linear genome at 100 kb resolution.
+The boundary coordinates of TADs were identified using the Arrowhead algorithm.
+To account for the uncertainty in TAD boundary detection, each boundary point was flanked on both sides by resolution-specific genomic regions (bins).
+The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region ($Y=1$) or not ($Y=0$).
+The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure1_model_construction_V3.png)
+
 ## IMBALANCE RATIOS REMAINED SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION
@@
 This relationship was not significantly correlated with resoltuion for either cell line, indicating that there existed a severe disparity between classes at all resolutions of Hi-C data.
+
+**Table 1.
+Domain Data Summaries and Imbalance Ratios.** For GM12878, average number of genomic bins, TADs called, and the corresponding boundaries and imbalance ratios, across each of the autosomal chromosomes (omitting chromosome 9), stratified by resolution.
+The resolution of the Hi-C contact matrix dictated the width of each genomic bin, with lower resolutions corresponding to wider genomic bins.
+
+| Resolution (Bin Width) | Median Number of Genomic Bins (IQR) | Median Number of TADs (IQR) | Median Number of TAD Boundaries (IQR) | Median Imbalance Ratio (IQR) |
+|------------------------|-------------------------------------|-----------------------------|---------------------------------------|------------------------------|
+| 10 kb                  | 13055 (8961)                        | 380 (203)                   | 1338 (832)                            | 0.11 (0.02)                  |
+| 25 kb                  | 5226 (3586)                         | 220 (155)                   | 737 (521)                             | 0.17 (0.02)                  |
+| 50 kb                  | 2616 (1794)                         | 110 (86)                    | 367 (294)                             | 0.17 (0.02)                  |
+| 100 kb                 | 1310 (897)                          | 53 (37)                     | 169 (136)                             | 0.15 (0.02)                  |
 
@@
 Lastly, distances, the most granular predictor-type, described the spatial relationship between the center of each genomic bin to the center of the nearest annotation-specific region (Figure 2C).
-A $log_{2}}$ transformation was used as a normalization technique in order to account for the skewness present in the distance densities (Supplementary Figures 1-2).
+A $log_{2}$ transformation was used as a normalization technique in order to account for the skewness present in the distance densities (Supplementary Figures 1-2).
 [??
 Why would skewness matter, why not use raw data ??]
+
+<!--![Caption for the picture.](/path/to/image.png)-->
 
@@
 We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.
+
+<!--![Caption for the picture.](/path/to/image.png)-->
 
@@
 
+<!--![Caption for the picture.](/path/to/image.png)-->
+
 <!--
@@
 
+<!--![Caption for the picture.](/path/to/image.png)-->
+
 We further assessed the predictive capabilities of the specific sets of annotations by comparing the performances of annotation-specific random forest models implemented on the optimal set of characteristics.
@@
 Interestingly though, at the 50 kb and 100 kb resolutions, the TFBS-specific models out performed models built on the combined sets of annotations, indicating that, at lower resolution, the inclusion of other types of annotations contributed to additional noise rather than signal.
+
+<!--![Caption for the picture.](/path/to/image.png)-->
 
@@
 
+<!--![Caption for the picture.](/path/to/image.png)-->
+
 ## INFLUENTIAL TFBS TENDED TO BE CLOSER TO BINS THAT OVERLAPPED WITH FLANKED TAD BOUNDARIES THAN THOSE THAT DID NOT
@@
 These cell line specific distance profiles were again found to be significantly different between genomic class, at all resolutions (Supplementary Figure 10).
+
+<!--![Caption for the picture.](/path/to/image.png)-->
 

### 2019-06-04 Manuscript/manuscript.Rmd
Remove hardcoded path

@@
 The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region ($Y=1$) or not ($Y=0$).
-The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure1_model_construction_V3.png)
+The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.](Figures/figure1_model_construction_V3.png)
 

### 2019-06-04 Manuscript/manuscript.Rmd
edits

--- 2019-06-04 Manuscript/manuscript.Rmd
@@
 
+**Table 2.
+Inter-Resolution ICCs.** For GM12878, two-way intraclass correlation coefficients between resolutions for the following quantities: Number of genomic bins, number of TADs called, number of unique TAD boundaries, and imbalance ratio.
+The ICC was computed across 21 of the autosomal chromosomes.
+P-values indicate the level of significance of the correlation between data resolution and each quantity.[???
+What is ICC?
+!!!editted]
+
+| Quantity                 | Inter-Resolution | 95% CI          | P-Value  |
+|--------------------------|------------------|-----------------|----------|
+| Number of Genomic Bins   | 0.464            | [0.244, 0.690]  | < 0.0001 |
+| Number of TADs Called    | 0.627            | [0.426, 0.802]  | < 0.0001 |
+| Number of TAD Boundaries | 0.611            | [0.407, 0.791]  | < 0.0001 |
+| Imbalanced Ratio         | 0.114            | [-0.058, 0.372] | 0.109    |
+
 <!--
@@
 
-<!--![Caption for the picture.](/path/to/image.png)-->
+![**Predictor types.** Three separate types of predictors were considered when quantifying the association between TAD boundaries and genomic annotations.
+Each predictor type was used to build the feature space of specific models in the ensemble framework.
+(A) _Overlap Counts_ (OC) consider the total number of genomic features that overlapped with each genomic bin.
+(B) _Overlap Percent_ (OP) was calculated by dividing the sum of all feature widths within each specific bin by the total bin width.
+(C) _Distance_ ($log_{2}$ transformed) was calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest region defining a genomic annotation.
+](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure2_predictor_types.png)
 
@@
 
-<!--![Caption for the picture.](/path/to/image.png)-->
+![**Figure 3.
+Ensemble Framework.** A diagram of the cell line specific ensemble framework detailing the combination of inputs used in the model building pipeline.
+The minoirty and majority classes were represented by the genomic bins that overlapped with flanked TAD boundaries or did not, respectively.
+Functional genomic annotations obtained from the UCSC Genome Browser Database composed the feature space ($\textbf{X} = \{X_1, X_2, ..., X_p\}$).
+A feature engineering step was included to isolate the predictor-type specific spatial relationship between annotations and genomic bins in increasing granularity, denoted by the red gradient.
+The data was split into a 7:3 training to testing set ratio.
+Data re-sampling was then applied to the training set.
+Lastly, a random forest classification algorithm was implemeted and validated on the testing data.](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure3_ensemble_framework.png)
 
@@
 <!--We then went on the evaluate the effect of class imbalance on model performance.--> In order to set a baseline in performance, we first evaluated the least granular model, that is one implemented using OC predictor types, without data re-sampling.
-We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 4A).
-We gradually increased the granularity by assessing models built on OP predictor types, while still not performing any data resampling.
-Here, the results were similar to that of OC types (Figure 4B).
-However, when including distance-type predictors, models were found to exhibit a marked improvement in MCC compared to the other two types (Figure 4C).
-Results were found to be consistently poor across resolutions and predictor types, when implemented on the K562 cell line (Supplementary Figure 3).
-Furthermore, we found that conventional metrics of performance (i.e.
-accuracy, sensitivity and specificity, and AUC) were less sensitive to models built on imbalanced data, regardless of cell line, resolution, or predictor-type (Supplementary Tables 6-7).
-
-## CLASS IMBALANCE SEVERELY IMPACTS MODEL PERFORMANCE
-
-We then went on the evaluate the effect of class imbalance on model performance.
-In order to set a baseline in performance, we first evaluated the least granular model, that is one implemented using OC predictor types, without data re-sampling.
 We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 4A).
@@
 
-<!--![Caption for the picture.](/path/to/image.png)-->
+![**Figure 4.
+SMOTE re-sampled models built on distance-type predictors yielded optimal MCCs across resolutions for GM12878.** Performances of random forest classification models built on each of the 3 predictor types: (A) OC, (B) OP, and (C) Distance.
+Within each predictor type, and across resolution, training data was re-sampled using different techniques including: None (red), ROS (green), RUS (blue), and SMOTE (purple).
+Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure4_gm12878_model_performances.png)
 
@@
 
-<!--![Caption for the picture.](/path/to/image.png)-->
+![**Figure 5.
+The proportional importance of optimally built predictive models was outweighed by transcription factor binding sites across resolutions for GM12878.** Stacked barplots illustrate the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework (SMOTE re-sampling; with distance-type predictors), for each resolution on GM12878.
+Proportions are grouped by the class of cell line specific annotations in the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure5_proportion_of_importances_gm12878.png)
 
@@
 
-<!--![Caption for the picture.](/path/to/image.png)-->
+![**Figure 6.
+Optimally built TFBS-specific models outperformed other annotation-specific models across resolution for GM12878** Performances were compared for random forest models built using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
+Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types.
+The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure6_comparing_sets_of_annotations_gm12878.png)
 
@@
 
-<!--![Caption for the picture.](/path/to/image.png)-->
+![**Figure 7.
+Top 20 most predictive transcription factor binding sites sorted by 10 kb for GM12878.** A heatmap illustrating the importance of the key cell line specific transcription factors for optimally built random forest models across resolution.
+Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100.
+Transcription factors with higher values of predictive importance are denoted in dark red.](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure7_variable_importance_heatmaps_tfbs_gm12878.png)
 
@@
 
-<!--![Caption for the picture.](/path/to/image.png)-->
+![**Figure 8.
+Top predictive transcription factor binding sites were significantly closer to bins that overlapped with 10 kb flanked TAD boundaries on GM12878** Boxplots illustrating the distribution of distances (on $log_{2}$ scale) around 10 kb regions on the linear genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential cell line specific TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
+P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure8_distance_boxplots_key_tfbs_gm12878_10kb.png)
 

### 2019-06-04 Manuscript/manuscript.Rmd
Paragraph 1 edits

--- 2019-06-04 Manuscript/manuscript.Rmd
@@
 
-## CELL LINE AND DATA RESOLUTION SPECIFIC MODEL CONSTRUCTION
+## CELL LINE AND DATA [??? What data?] RESOLUTION SPECIFIC MODEL [??? What model?] CONSTRUCTION [??? Why?]
 
-We analyzed publically available Hi-C data for the GM12878 and K562 cell lines provided by Rao et al.
+We analyzed [???
+Boring.
+What problem you are solving?] publically available Hi-C data for the GM12878 and K562 cell lines provided by Rao et al.
 [@rao20143d].
-Topologically associating domains were identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions, for each cell line respectively.
-We then established a unified approach toward preparing cell line and resolution specific TAD boundary data for predictive modelling purposes (Figure 1).
-To enable us to build a model that suitably discriminated between regions on the linear genome that were near TAD boundaries and regions that were not, we created a  resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$).
-The unit width of each bin on the linear genome corresponded to the resolution of the cell line specific contact matrix on which domains were called.
-Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.
+Topologically associating domains were identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions.
+We then established a unified approach toward preparing cell line and resolution specific TAD boundary data [???
+This is problem definition, should be done early on, not here] for predictive modelling purposes.
+Specifically, we created a response variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$, Figure 1).
+<!--The unit width of each bin on the linear genome corresponded to the resolution of the cell line specific contact matrix on which domains were called.
+Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.-->
 
-![**Model Construction.** An illustration of the proposed model construction given cell line specific Hi-C data.
-Above is an example of a subsection of the contact matrix for chromosome 14 (at megabase scale) on GM12878 [@durand2016juicer].
-The contact matrix is a visualization of the interconnectivity of the linear genome at 100 kb resolution.
-The boundary coordinates of TADs were identified using the Arrowhead algorithm.
-To account for the uncertainty in TAD boundary detection, each boundary point was flanked on both sides by resolution-specific genomic regions (bins).
-The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region ($Y=1$) or not ($Y=0$).
-The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.](Figures/figure1_model_construction_V3.png)
+![**Model Construction for TAD boundary classification.** A subsection of the contact matrix for chromosome 14 on GM12878 [@durand2016juicer] at 100kb resolution shows the appearance of TAD boundaries.
+To account for the uncertainty in TAD boundary location, each boundary point was flanked on both sides by resolution-specific genomic regions (bins).
+The response vector $Y$ was constructed by defining $Y=1$ if a bin flanks a TAD boundary, and $Y=0$ otherwise.
+<!--The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.-->](Figures/figure1_model_construction_V3.png)
 

### 2019-06-04 Manuscript/manuscript.Rmd
wip throuth figure 2

@@
 
-We created a resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$).
-The unit width of each bin on the linear genome corresponded to the resolution of the contact matrix on which domains were called.
-Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.
-Expectedly, the median number of genomic bins, TADs called, and TAD boundaries increased with the increased resolution of cell-line specific Hi-C data (Table 1; Supplementary Tables 3).
-This correlation [??
+To investigate class imbalance, defined as the ratio of TAD vs.
+non-TAD boundaries, we estimated the number of TAD boundaries ($Y=1$ in the response vector) and the rest of genomic bins ($Y=0$) at four resolutions of Hi-C data.
+Expectedly, the average number of TAD boundaries and the rest of genomic bins increased with the increased resolution of Hi-C data (Table 1) irrespectively of cell line (Supplementary Tables 3).
+<!--This correlation [??
 What correlation ??] with resolution was found to be significant, as evidenced by large intraclass correlation coefficients (ICC) (Table 2; Supplementary Tables 4).
@@
 This imbalance was evidenced by low imbalance ratios, defined as the ratio of the number of genomic bins that overlapped with flanked TAD boundaries, to the much larger number of genomic bins that did not.
-This relationship was not significantly correlated with resoltuion for either cell line, indicating that there existed a severe disparity between classes at all resolutions of Hi-C data.
+This relationship was not significantly correlated with resoltuion for either cell line, indicating that there existed a severe disparity between classes at all resolutions of Hi-C data.-->
 
-**Table 1.
-Domain Data Summaries and Imbalance Ratios.** For GM12878, average number of genomic bins, TADs called, and the corresponding boundaries and imbalance ratios, across each of the autosomal chromosomes (omitting chromosome 9), stratified by resolution.
-The resolution of the Hi-C contact matrix dictated the width of each genomic bin, with lower resolutions corresponding to wider genomic bins.
+**Table 1. TAD boundaries are the minority of the genome, creating high class imbalance ratio irrespectively of resolution.**
 
@@
 
-**Table 2.
+<!--**Table 2.
 Inter-Resolution ICCs.** For GM12878, two-way intraclass correlation coefficients between resolutions for the following quantities: Number of genomic bins, number of TADs called, number of unique TAD boundaries, and imbalance ratio.
@@
 | Imbalanced Ratio         | 0.114            | [-0.058, 0.372] | 0.109    |
-
+-->
 <!--
@@
 
-## ESTABLISHING THE FEATURE SPACE USING INCREASINGLY GRANULAR RELATIONSHIPS BETWEEN FUNCTIONAL ANNOTATIONS AND GENOMIC BINS
+## Three types of associations between TAD boundaries and epigenomic features
 
-The influences of TAD boundaries were assessed using functional genomic annotations, derived by ChIP-seq peak algorithms.
-Specific groups of annotations were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] and included chromatin state segementations, histone modifications, and transcription factor binding sites (TFBS).
+<!-- of TAD boundaries were assessed using functional genomic annotations, derived by ChIP-seq peak algorithms.
+Specific groups of annotations were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] and included chromatin state segementations, histone modifications, and transcription factor binding sites (TFBS).-->
 
@@
 
-To establish the feature space for all downstream models, we constructed 3 different predictor-types.
-These predictor-type specific annotations represented the data matrix, $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations [??
-$p$ is actually the total number of functional annotations, $X_i$ is the functional annotation itself ??].
-Overlap counts was the least granular [??
-Maybe define granular ??] predictor-type considered, simply defined by the number of annotation-specific regions located within each genomic bin (Figure 2A).
-Overlap percents was a more refined [??
-what is refined in this context ??] predictor-type, defined as the total percent overlap between each annotation-specific region and genomic bins (Figure 2B).
-Lastly, distances, the most granular predictor-type, described the spatial relationship between the center of each genomic bin to the center of the nearest annotation-specific region (Figure 2C).
-A $log_{2}$ transformation was used as a normalization technique in order to account for the skewness present in the distance densities (Supplementary Figures 1-2).
-[??
-Why would skewness matter, why not use raw data ??]
+To establish the feature space for classification modeling, we constructed three different predictor types.
+Counts of overlaps (**overlap count**, OC) is the most commonly used type of association between genomic elements (Figure 2A).
+**Overlap percent** (OP) represents a more precise measure of associations as it considers the proportion of a bin overlapped by a genomic annotation (Figure 2B).
+**Distance** between the centers of bins and genomic annotations quantifying the spatial relationship between genomic elements is the least common type of association (Figure 2C).
+Log2-transformation of distance was used as a normalization technique in order to account for the skewness present in the distributions of distances (Supplementary Figures 1-2).
+These types of genomic associations provide a granular way to investigate classification performance in class imbalance settings.
 
-![**Predictor types.** Three separate types of predictors were considered when quantifying the association between TAD boundaries and genomic annotations.
-Each predictor type was used to build the feature space of specific models in the ensemble framework.
-(A) _Overlap Counts_ (OC) consider the total number of genomic features that overlapped with each genomic bin.
+![**Three types of associations between TAD boundaries and genomic annotations.** (A) _Overlap Counts_ (OC) consider the total number of genomic features that overlapped with each genomic bin.
 (B) _Overlap Percent_ (OP) was calculated by dividing the sum of all feature widths within each specific bin by the total bin width.
 (C) _Distance_ ($log_{2}$ transformed) was calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest region defining a genomic annotation.
-](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure2_predictor_types.png)
+](Figures/figure2_predictor_types.png)
 
@@
 Data re-sampling was then applied to the training set.
-Lastly, a random forest classification algorithm was implemeted and validated on the testing data.](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure3_ensemble_framework.png)
+Lastly, a random forest classification algorithm was implemeted and validated on the testing data.](Figures/figure3_ensemble_framework.png)
 
@@
 Within each predictor type, and across resolution, training data was re-sampled using different techniques including: None (red), ROS (green), RUS (blue), and SMOTE (purple).
-Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure4_gm12878_model_performances.png)
+Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/figure4_gm12878_model_performances.png)
 
@@
 The proportional importance of optimally built predictive models was outweighed by transcription factor binding sites across resolutions for GM12878.** Stacked barplots illustrate the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework (SMOTE re-sampling; with distance-type predictors), for each resolution on GM12878.
-Proportions are grouped by the class of cell line specific annotations in the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure5_proportion_of_importances_gm12878.png)
+Proportions are grouped by the class of cell line specific annotations in the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).](Figures/figure5_proportion_of_importances_gm12878.png)
 
@@
 Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types.
-The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure6_comparing_sets_of_annotations_gm12878.png)
+The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.](Figures/figure6_comparing_sets_of_annotations_gm12878.png)
 
@@
 Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100.
-Transcription factors with higher values of predictive importance are denoted in dark red.](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure7_variable_importance_heatmaps_tfbs_gm12878.png)
+Transcription factors with higher values of predictive importance are denoted in dark red.](Figures/figure7_variable_importance_heatmaps_tfbs_gm12878.png)
 
@@
 Top predictive transcription factor binding sites were significantly closer to bins that overlapped with 10 kb flanked TAD boundaries on GM12878** Boxplots illustrating the distribution of distances (on $log_{2}$ scale) around 10 kb regions on the linear genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential cell line specific TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
-P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure8_distance_boxplots_key_tfbs_gm12878_10kb.png)
+P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].](Figures/figure8_distance_boxplots_key_tfbs_gm12878_10kb.png)
 

### 2019-06-04 Manuscript/manuscript.Rmd
edits

--- 2019-06-04 Manuscript/manuscript.Rmd
@@
 
-## CELL LINE AND DATA [??? What data?] RESOLUTION SPECIFIC MODEL [??? What model?] CONSTRUCTION [??? Why?]
+## CELL LINE AND DATA RESOLUTION SPECIFIC MODEL CONSTRUCTION
 
-We analyzed [???
-Boring.
-What problem you are solving?] publically available Hi-C data for the GM12878 and K562 cell lines provided by Rao et al.
+We analyzed publically available Hi-C data for the GM12878 and K562 cell lines provided by Rao et al.
 [@rao20143d].
-Topologically associating domains were identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions.
-We then established a unified approach toward preparing cell line and resolution specific TAD boundary data [???
-This is problem definition, should be done early on, not here] for predictive modelling purposes.
-Specifically, we created a response variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$, Figure 1).
-<!--The unit width of each bin on the linear genome corresponded to the resolution of the cell line specific contact matrix on which domains were called.
-Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.-->
+Topologically associating domains were identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions, for each cell line respectively.
+We then established a unified approach toward preparing cell line and resolution specific TAD boundary data for predictive modelling purposes (Figure 1).
+To enable us to build a model that suitably discriminated between regions on the linear genome that were near TAD boundaries and regions that were not, we created a  resolution-specific response variable that indicated whether a genomic bin of unit width overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$).
+The unit width of each bin on the linear genome corresponded to the resolution of the cell line specific contact matrix on which domains were called.
+Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.
 
-![**Model Construction for TAD boundary classification.** A subsection of the contact matrix for chromosome 14 on GM12878 [@durand2016juicer] at 100kb resolution shows the appearance of TAD boundaries.
-To account for the uncertainty in TAD boundary location, each boundary point was flanked on both sides by resolution-specific genomic regions (bins).
-The response vector $Y$ was constructed by defining $Y=1$ if a bin flanks a TAD boundary, and $Y=0$ otherwise.
-<!--The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.-->](Figures/figure1_model_construction_V3.png)
+![**Model Construction.** An illustration of the proposed model construction given cell line specific Hi-C data.
+Above is an example of a subsection of the contact matrix for chromosome 14 (at megabase scale) on GM12878 [@durand2016juicer].
+The contact matrix is a visualization of the interconnectivity of the linear genome at 100 kb resolution.
+The boundary coordinates of TADs were identified using the Arrowhead algorithm.
+To account for the uncertainty in TAD boundary detection, each boundary point was flanked on both sides by resolution-specific genomic regions (bins).
+The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region ($Y=1$) or not ($Y=0$).
+The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.](Figures/figure1_model_construction_V3.png)
 
@@
 (C) _Distance_ ($log_{2}$ transformed) was calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest region defining a genomic annotation.
-](C:/Users/stili/Documents/TAD_predictive_modeling/Manuscript/Figures/figure2_predictor_types.png)
+](Figures/figure2_predictor_types.png)
 

### 2019-06-05 Manuscript/manuscript.Rmd
editted table 1

--- 2019-06-04 Manuscript/manuscript.Rmd
@@
 
-**Table 1. TAD boundaries are the minority of the genome, creating high class imbalance ratio irrespectively of resolution.**
+**Table 1. Sparce TAD boundaries throughout the linear genome create high imbalance ratios irrespective of resolution.**
 
-| Resolution (Bin Width) | Median Number of Genomic Bins (IQR) | Median Number of TADs (IQR) | Median Number of TAD Boundaries (IQR) | Median Imbalance Ratio (IQR) |
-|------------------------|-------------------------------------|-----------------------------|---------------------------------------|------------------------------|
-| 10 kb                  | 13055 (8961)                        | 380 (203)                   | 1338 (832)                            | 0.11 (0.02)                  |
-| 25 kb                  | 5226 (3586)                         | 220 (155)                   | 737 (521)                             | 0.17 (0.02)                  |
-| 50 kb                  | 2616 (1794)                         | 110 (86)                    | 367 (294)                             | 0.17 (0.02)                  |
-| 100 kb                 | 1310 (897)                          | 53 (37)                     | 169 (136)                             | 0.15 (0.02)                  |
+| Resolution (Bin Width) | Average Number of Genomic Bins (SD) | Average Number of TAD Boundaries (SD) | Average Imbalance Ratio (SD) |
+|------------------------|-------------------------------------|---------------------------------------|------------------------------|
+| 10 kb                  | 12214.1 (6068.5)                    | 1254.6 (598.8)                        | 0.12 (0.02)                  |  
+| 25 kb                  | 4892.7 (2431.2)                     | 714.0 (358.4)                         | 0.17 (0.01)                  |
+| 50 kb	                 | 2450.9 (1217.6)                     | 364.4 (184.5)                         | 0.17 (0.01)                  |
+| 100 kb                 | 1227.5 (609.8)                      | 165.3 (90.9)                          | 0.15 (0.02)                  |
 

### 2019-06-05 Manuscript/manuscript.Rmd
edits

@@
 
-Current methods used to predict TAD boundaries rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries.
-However, this is a multi-faceted probelem, and many methods ignore key characteristics [??
-which ones ??] of domain data when building models and reporting performances.
-We aim to address these characteristics in order to create a more unified approach toward identifying the genomic annotations most predictive of TAD boundaries.
+Current methods used to predict TAD boundaries rely on the use of classification algorithms to draw associations between functional annotations and regions that include TAD boundaries.
+However, this is a multi-faceted probelem.
+Many methods ignore key characteristics [??
+which ones ??; !!!editted] of 3D genomic data including sparsity of TAD boundaries as well as suitably describing the spatial relationship between annotations and TAD boundaries.
 
@@
 This sentence is very difficult to understand.
-Don't see connection between the bias and the error rate ??].
+Don't see connection between the bias and the error rate ??; !!!].
 
+We can account for imbalance at the data level in addition to at the evaluation level [??
+I rewrote this sentence.
+Was very wordy and difficult to follow ??].
+Data level solutions mostly involve re-sampling techniques, in which random sampling is used to either replicate or remove data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
+It has been shown that quite simple re-sampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
+Evaluation level solutions include choosing suitable performance metrics for evaluating models.
+<!--These solutions are necessary given that the test set, used to validate re-sampled training sets, is itself imbalanced.--> It has been shown that common metrics such as accuracy and AUROC (area under the receiver operating characteristic curve) are insensitive to class imbalance [@prati2011survey; @wei2013role].
+A better measure to consider would be a composite metric involving all quadrants of the confusion matrix such as Matthews Correlation Coefficient (MCC).
+The suitability of MCC when evaluating models in imbalanced settings has researched previously [@boughorbel2017optimal; @brodersen2010balanced].
+Defined, the MCC is the correlation coefficient between the observed and predicted binary classifications.
+A value of 1 represents a perfect prediction, while a value of -1 represents total disagreement between prediction and observation.
+A value of 0 indicates no better than random prediction.
+
+<!--
 In a study published in 2016 [@mourad2016computational], an L1-regularized multiple logistic regression model was proposed using transcription factor binding sites on GM12878 to discriminate between regions with and without TADs, and to identify the most predictive factors associated with boundaries.
-However, the class imbalance issue was not addressed.
+The class imbalance issue was not addressed.
 Even worse, when performing cross-validation, [@mourad2016computational] used the misclassification error rate of the model to establish the optimal L1-regularization lambda.
 They also reported ROC (receiver operating characteristic) curves and subsequent AUC (area under the curve) as measures of their model's performance.
-This is problematic in an imbalanced setting.
-Such heavily imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class; @chen2013influence; @jeni2013facing] [??
-This is the second mention of "biased towards the majority class to minimize the overall error rate" without strong explanation of what this means ??].
-For AUC, when the prevalence of an event is low--that is, a defined genomic region truly containing a TAD boundary--mean probabilities are biased towards the majority class.
-This results in the area of interest under an ROC curve to be compressed toward a small corner in the ROC space [@prati2011survey; @wei2013role].
-While not directly affecting the value of the AUROC, this can have severe consequences on the interpretability of the model's performance [??
-How so?
-does it inflate it or deflate it or what ??].
-Consequently, careful consideration must be taken when deciding which performance metric(s) to use for evaluation of predictive models, especially in the case of imbalanced data.
+-->
 
+<!--
 A better threshold-free measure to use when dealing with imbalanced data is the area under the precision-recall curve (AUPRC).
@@
 A value of 0 indicates no better than random prediction.
+-->
 
-We can account for imbalance at the data level in addition to at the evaluation level [??
-I rewrote this sentence.
-Was very wordy and difficult to follow ??].
-Data level solutions mostly constitute as [??
-I'd change "constiute as", unorthodox word choice ??] re-sampling techniques, in which random sampling is used to either replicate or remove data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
-It has been shown that quite simple re-sampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
-[??
-It feels like data level should come before evaluation level ??]
-
+<!--
 Two studies published in 2015 and 2017 respectively [@huang2015predicting; @hong2017computational] used re-sampling techniques prior to modeling, and both implemented random under-sampling to balance classes.
@@
 However, this is problematic because re-sampling prior to splitting can further introduce bias into the testing set, as it is no longer an accurate representation of real-world data [@wei2013role].
+-->
 
@@
 This is problem definition, should be done early on, not here] for predictive modelling purposes.
-Specifically, we created a response variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$, Figure 1).
+Specifically, we created a response variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$) (Figure 1).
 <!--The unit width of each bin on the linear genome corresponded to the resolution of the cell line specific contact matrix on which domains were called.
@@
 
-## Three types of associations between TAD boundaries and epigenomic features
+## DEVELOPING THREE TYPES OF ASSOCIATIONS BETWEEN TAD BOUNDARIES AND EPIGENOMIC FEATURES
 
@@
 
-To establish the feature space for classification modeling, we constructed three different predictor types.
+To establish the feature space used for classification, we constructed three different predictor types.
 Counts of overlaps (**overlap count**, OC) is the most commonly used type of association between genomic elements (Figure 2A).
-**Overlap percent** (OP) represents a more precise measure of associations as it considers the proportion of a bin overlapped by a genomic annotation (Figure 2B).
+Percents of overlaps (**overlap percent**, OP) represents a more precise measure of association as it considers the proportion of a bin overlapped by a genomic annotation (Figure 2B).
 **Distance** between the centers of bins and genomic annotations quantifying the spatial relationship between genomic elements is the least common type of association (Figure 2C).

### 2019-06-05 Manuscript/manuscript.Rmd
edits

@@
 Many methods ignore key characteristics [??
-which ones ??; !!!editted] of 3D genomic data including sparsity of TAD boundaries as well as suitably describing the spatial relationship between annotations and TAD boundaries.
+which ones ??; !!!editted] of 3D genomic data.
+<!--including sparsity of TAD boundaries as well as suitably describing the spatial relationship between annotations and TAD boundaries.-->
 
-A major ignored aspect of TAD boundary prediction is the introduction of heavily imbalanced classes resulting from the number of boundaries vs.
-nonboundary regions.
-In a classification setting, when one is attempting to discriminate between minority (regions with TAD boundaries) and majority classes (regions without TAD boundaries), the class imbalance issue will contribute to small imbalance ratios.
-The imbalance ratio is defined as the ratio of minority to majority classes [@Orriols-Puig2008].
+Firstly, sparsity of TAD boundary regions throughout the linear genome contribute to heavily imbalanced classes.
+This imbalance results in small imbalance ratios.
+The imbalance ratio is defined as the ratio of minority classes (regions with TAD boundaries) to majority classes (regions without TAD boundaries) [@Orriols-Puig2008].
 Such heavily imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class; @chen2013influence; @jeni2013facing] [??
@@
 
-We can account for imbalance at the data level in addition to at the evaluation level [??
+We can account for this imbalance at the data level in addition to at the evaluation level [??
 I rewrote this sentence.
@@
 A better measure to consider would be a composite metric involving all quadrants of the confusion matrix such as Matthews Correlation Coefficient (MCC).
-The suitability of MCC when evaluating models in imbalanced settings has researched previously [@boughorbel2017optimal; @brodersen2010balanced].
+The suitability of MCC when evaluating models in imbalanced settings has been studied previously [@boughorbel2017optimal; @brodersen2010balanced].
 Defined, the MCC is the correlation coefficient between the observed and predicted binary classifications.
@@
 
-Furthermore, determing the optimal representation of the relationship between features in the model and genomic regions, known as feature engineering, plays a significant role in TAD prediction.
+Secondly, it is important to determine the optimal representation of the relationship between features in the model and genomic regions.
+This is known as feature engineering.
 Typical approaches include overlap counts [@hong2017computational] or percents [@mourad2016computational; @huang2015predicting].
 Counts refer to the number of times a genomic annotation directly overlaps with a TAD boundary region, e.g., a TAD boundary may overlap with several ChIP-seq peaks for a given transcription factor.
-Percents refers to the percent of overlap between a genomic annotation and a TAD boundary region, e.
-g., 60% of a TAD boundary region may overlap with a genomic region annotated as heterochromatin.
+Percents refers to the percent of overlap between a genomic annotation and a TAD boundary region, e.g., 60% of a TAD boundary region may overlap with a genomic region annotated as heterochromatin.
 Here, using percents offers a more granular approach, but it is unclear how it performs when compared to counts.
@@
 
-Additionally, model performance is heavily contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
+Lastly, model performance is heavily contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
 It is often unclear from previous studies what resolution contact matrices were used when retrieving TAD boundaries, and how other resolutions would affect their results.
@@
 
-In this study, we aimed to develop an ensemble framework composed of different combinations of data driven characteristics used to address the issues presented above.
-We used our framework to systematically compare performances of random forest classifiers using a composite performance metric, MCC.
-Our goal was to determine a suitable combination of data re-sampling and feature engineering techniques that both corrected the inherent imbalanced classes and provided the best spatial representation [??
-Not sure what spatial representation means in this context ??] linking genomic annotations to TAD boundaries.
-Additionally, we used our framework to directly compare the influence of Hi-C contact matrix resolution on model performances.
-We evaluated Hi-C data for both the GM12878 and K562 cell line obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolution.
-[??
-It feels like some stronger statements need to be here.
-I would make a statement about predicting TAD regions using genomic annotations instead of using terms like "linking".
-It feels like the focus should be on this and not model selection which occurs in any analysis ??]
+In this study, we developed a novel ensemble framework aimed at systematically comparing the performances of random forest classification models in order to determine the set of data level characteristics necessary for optimal prediction of TAD boundaries.
+We evaluated performances of Hi-C data for both the GM12878 and K562 cell line obtained at four different Hi-C resolutions including 10 kb, 25 kb, 50 kb, and 100 kb resolution.
+For each cell line and resolution, we compared three feature engineering techniques: counts, percents, and distances.
+Additionally, we compared three re-sampling techniques: random under-sampling, random-over-sampling, and a weighted combination of both referred to as Synthetic Minority Over-sampling Technique (SMOTE).
 
-For each resolution, we examined the inclusion of three different predictor types [??
-Maybe list all 3 (.e.g "For each resolution, we examined the inclusion of three different predictor types: counts, percentages and distances.") ??], including distance as the measure of association between genomic elements.
-We then tested four different re-sampling techniques aimed at creating balanced classes.
-This process was performed on chromosome-specific regions on the linear genome.
-Noninformative features were removed using a feature reduction algorithm.
-Lastly, random forest classifiers were built to assess model performance, and investigate which genomic annotations were most predictive of TAD boundaries for a given system from the complete ensemble.
+[???Include concluding paragraph]
 

### 2019-06-05 Manuscript/manuscript.Rmd
methods edits

@@
 The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
-TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for both cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
+TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all cell lines and resolutions, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
 
@@
 As an example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
-For the boundary data, in order to accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
+In order to accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
 That is, for 10 kb resolution data, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
@@
 
-Using the sets of cell line specific genomic annotations, we created three types of predictors that were used to describe the spatial relationship with genomic bins, $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
+Using the sets of cell line specific genomic annotations, we created three types of predictors that were used to describe the relationship between functional annotations and genomic bins<!--, $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations-->.
 They are described in detail below:
@@
 
-The cell line- and resolution-specific data, composed of the response vector and predictor-type specific data matrix (**X**), was then split into a 7:3 ratio of training to testing sets.
+The data set used for modeling was composed of the response vector **Y**, and the predictor-type specific data matrix, **X** = {X_1, X_2, ..., X_p}, where $p$ was the complete set of functional annotations.
+Each composed data set was specific to cell line and resolution.
+We then split the data into a 7:3 ratio of training to testing sets.
 For the task of performance evaluation and prediction, the test set remained constant to account for an unbiased comparison between data level characteristics.

### 2019-06-05 Manuscript/manuscript.Rmd
methods edits

@@
 
-Using the sets of cell line specific genomic annotations, we created three types of predictors that were used to describe the relationship between functional annotations and genomic bins<!--, $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations-->.
+Using the sets of cell line specific genomic annotations, we created three types of predictors that were used to describe the relationship between functional annotations and genomic bins.
 They are described in detail below:
@@
 
-The data set used for modeling was composed of the response vector **Y**, and the predictor-type specific data matrix, **X** = {X_1, X_2, ..., X_p}, where $p$ was the complete set of functional annotations.
+The data set used for modeling was composed of the response vector **Y**, and the predictor-type specific data matrix, **X** = {$X_1$, $X_2$, ..., $X_p$}, where $p$ was the complete set of functional annotations.
 Each composed data set was specific to cell line and resolution.
@@
 
-Class imbalance was characterized by each dataset's imalance ratio, defined as the ratio of minority to majority classes given by the genomic bins.
-Minority classes were the set of genomic bins that overlapped with flanked TAD boundaries, while majority classes were the set of genomic bins that did not overlap with a flanked TAD boundary.
+Class imbalance was characterized by each dataset's imalance ratio (IR), defined as the ratio of minority to majority sets given by the class of genomic bins:
+
+$$IR = \dfrac{C_{minority}}{C_{majority}}$$
+
+where $C_{minority}$ denotes the set of genomic bins that overlapped with flanked TAD boundaries and $C_{majority}$ denotes the set of genomic bins that did not overlap with a flanked TAD boundary.
 In order to assess the influence of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling).
@@
 The minority class is over-sampled by taking each minority class sample and introducing synthetic examples along the feature vectors joining any/all of the k=5 (default) minority class nearest neighbors.
-The SMOTE algorithm can have many variations is the percentage of over- and under-sampling.
+The SMOTE algorithm can have many variations in the weightinh of over- and under-sampling.
 In this study we restricted the algorithm to 100% over-sampling and 200% under-sampling.
@@
 
-random forest classification models were built to compare model performances between re-sampling techniques and predictor types.
+Random forest classification models were built to compare model performances between combinations of predictor types and re-sampling techniques.
 To reduce bias due to random dataset generation, 10-fold cross validation was used to tune the number of annotations, *p*, to consider at each node.
@@
 Once the model was implemented, it was validated on the test set.
-The performance of each ensemble system in the framework was compared using the composite metric, Matthews Correlation Coefficient (MCC), which is defined as follows:
+The performance of each model was compared using the composite metric, Matthews Correlation Coefficient (MCC), which is defined as follows:
 

### 2019-06-05 Manuscript/manuscript.Rmd
results edits

@@
 
-## MODEL CONSTRUCTION
+## CLASSIFICATION
 
-To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution of the corresponding contact matrix.
+To establish the data for classification, the genome was binned into equally sized intervals defined by the data resolution of the corresponding contact matrix.
 As an example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
@@
 
-## CELL LINE AND DATA [??? What data?] RESOLUTION SPECIFIC MODEL [??? What model?] CONSTRUCTION [??? Why?]
+## Data construction for unbiased comparisons between resolution specific random forest classifiers
+<!--## CELL LINE AND DATA [??? What data?] RESOLUTION SPECIFIC MODEL [??? What model?] CONSTRUCTION [??? Why?] !!!created new header-->
 
-We analyzed [???
+In total, we analyzed publically available Hi-C data for both the GM12878 and K562 cell lines, at four resolutions including 10 kb, 25 kb, 50 kb, and 100 kb.
+Given the varying levels of data resolution, we created a resolution-specific approach toward data constuction used for downstream modelling (Figure 1).
+This allowed us an unbiased way to compare performances of random forest classifiers between varying resolutions of Hi-C data.
+[???
 Boring.
-What problem you are solving?] publically available Hi-C data for the GM12878 and K562 cell lines provided by Rao et al.
-[@rao20143d].
-Topologically associating domains were identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions.
-We then established a unified approach toward preparing cell line and resolution specific TAD boundary data [???
-This is problem definition, should be done early on, not here] for predictive modelling purposes.
-Specifically, we created a response variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$) (Figure 1).
-<!--The unit width of each bin on the linear genome corresponded to the resolution of the cell line specific contact matrix on which domains were called.
-Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.-->
+What problem you are solving?;!!!editted]
 

### 2019-06-05 Manuscript/manuscript.Rmd
results edits

@@
 Under-sampling is performed without replacement from the majority class.
-On the other hand, over-sampling is performed by creating new synthetic observations using the minority class.
+Over-sampling is performed by creating new synthetic observations using the minority class.
 The minority class is over-sampled by taking each minority class sample and introducing synthetic examples along the feature vectors joining any/all of the k=5 (default) minority class nearest neighbors.
@@
 
-## Data construction for unbiased comparisons between resolution specific random forest classifiers
+## DATA CONSTRUCTION FOR UNBIASED COMPARISONS BETWEEN RESOLUTION-SPECIFIC RANDOM FOREST CLASSIFIERS
 <!--## CELL LINE AND DATA [??? What data?] RESOLUTION SPECIFIC MODEL [??? What model?] CONSTRUCTION [??? Why?] !!!created new header-->
@@
 To investigate class imbalance, defined as the ratio of TAD vs.
-non-TAD boundaries, we estimated the number of TAD boundaries ($Y=1$ in the response vector) and the rest of genomic bins ($Y=0$) at four resolutions of Hi-C data.
+non-TAD regions, we estimated the number of TAD boundaries ($Y=1$ in the response vector) and the rest of genomic bins ($Y=0$) at each of the four resolutions of Hi-C data.
 Expectedly, the average number of TAD boundaries and the rest of genomic bins increased with the increased resolution of Hi-C data (Table 1) irrespectively of cell line (Supplementary Tables 3).
-<!--This correlation [??
-What correlation ??] with resolution was found to be significant, as evidenced by large intraclass correlation coefficients (ICC) (Table 2; Supplementary Tables 4).
-However, the class imbalance problem, caused by the sparsity of TAD boundaries throughout the genome, was found to be much more consistant across resolutions in both cell lines.
-This imbalance was evidenced by low imbalance ratios, defined as the ratio of the number of genomic bins that overlapped with flanked TAD boundaries, to the much larger number of genomic bins that did not.
-This relationship was not significantly correlated with resoltuion for either cell line, indicating that there existed a severe disparity between classes at all resolutions of Hi-C data.-->
+However, imbalance ratios were found to be invariant to resolution, remaining consistently low with very little variability between chromosomes, regardless of cell line.
 
@@
 
-<!--We then went on the evaluate the effect of class imbalance on model performance.--> In order to set a baseline in performance, we first evaluated the least granular model, that is one implemented using OC predictor types, without data re-sampling.
+<!--We then went on the evaluate the effect of class imbalance on model performance.--> In order to set a baseline in performance, we first evaluated the least granular random forest classifier, that is one implemented using OC predictor types, without data re-sampling.
 We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 4A).
-We gradually increased the granularity [??
-Really confused by the constant use of granularity.
-Why is it needed ??] by assessing models built on OP predictor types, while still not performing any data resampling.
+We gradually increased the complexity in data level characteristics by assessing models built on OP predictor types, while still not performing any data resampling.
 Here, the results were similar to that of OC types (Figure 4B).
@@
 Furthermore, we found that conventional metrics of performance (i.e.
-accuracy, sensitivity and specificity, and AUC) were less sensitive to models built on imbalanced data, regardless of cell line, resolution, or predictor-type (Supplementary Tables 6-7).
+accuracy and AUC) were less sensitive to models built on imbalanced data, regardless of cell line, resolution, or predictor-type (Supplementary Tables 6-7).
 

### 2019-06-05 Manuscript/manuscript.Rmd
results edits

@@
 
-<!--We then went on the evaluate the effect of class imbalance on model performance.--> In order to set a baseline in performance, we first evaluated the least granular random forest classifier, that is one implemented using OC predictor types, without data re-sampling.
+In order to set a baseline in performance, we first evaluated the least granular random forest classifier, that is one implemented using OC predictor types, without data re-sampling.
 We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 4A).
@@
 
-When assessing performances for models built on balanced data, we found that SMOTE re-sampling provided the optimal MCC consistently across both predictor type and resolution (Figure 4).
-Specifically, the most improvement in model performance [??
-Over what ??] was seen when combining SMOTE re-sampling with distance-type predictors.
+When assessing performances for random forest classifiers built on balanced data, we found that SMOTE re-sampling provided the optimal MCC consistently outperforming models built on ROS or RUS, across both predictor type and resolution (Figure 4).
+Specifically, the most improvement in model performance was seen when combining SMOTE re-sampling with distance-type predictors.
 This was also the optimal combination for the K562 cell line (Supplementary Figure 3).
-These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries [??
-Is this what you are doing?
-Or are you identifying TAD boundaries themselves ??], is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
-Moreover, there was a clear degredation in model performance as data resolution decreased.
-Likewise, performances exhibited much more variability across chromosomes when built on lower resolutions.
+Interestingly, we found that there was a degredation in model performance as data resolution decreased.
+Chromosome specific models built on 10 kb data resolutions presented with the highest MCC values.
+Additionally, performances tended to be much more variable between chromosomes at lower resolutions.
+Moreover, this decreasing trend in performance was much more evident under the optimal combination of data level characteristics.
+These results imply that an optimally performing random forest classifier, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
 

### 2019-06-05 Manuscript/manuscript.Rmd
results edits

@@
 
-<!--
-When models were built on randomly oversampled (ROS) data for GM12878, we found an increase in MCC compared to no resampling, at higher resolutions.
-The biggest improvement in performance was seen at the 10 kb resolution in each of the 3 predictor types, with a downward trend as resolutions decreased.
-Again, distance-type predictors were found to offer the highest MCCs for ROS data, across all resolutions.
-Similar results were obtained when applying ROS to the K562 cell line (Supplementary Figure 3).
-
-Further improvement in performance was found when models were implemented on both randomly undersampled (RUS) and SMOTE resampled data, especially between models with OC and OP predictor types.
-When using RUS or SMOTE, implemented on distance type predictors, we found a clear improvement compared to the other predictor types.
-However, there was less of a separation between ROS and RUS techniques within the ensemble of models using distance type predictors.
-
-Overall, SMOTE resampled data was found to yield the best MCCs among all classes of models developed and compared in the ensemble framework.
-Here, distance type predictors were found to again yield the highest MCC values across resolutions.
-It should be noted that, SMOTE re-sampled data, with the inclusion of distance-type predictors was also found to be the best set of characteristics when applied to the K562 cell line (Supplementary Figure 3).
-Moreover, for these sets of data characteristics, we again found that there was a degredation in model performance as data resolution decreased.
-Results indicated that performances exhibited much more variability when built on lower resolutions, specifically at the 100 kb level.
-These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
--->
-
 ## MODELS IMPLEMENTED ON TRANSCRIPTION FACTOR BINDING SITES, USING OPTIMAL PARAMETERS, OUTPERFORM OTHER ANNOTATION-SPECIFIC MODELS

### 2019-06-05 Manuscript/manuscript.Rmd
wip on intro

--- 2019-06-05 Manuscript/manuscript.Rmd
@@
 
-The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries.
+The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries [???
+REFS?
+Carefully select from my paper notes].
 Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD [@symmons2014functional].
-Likewise, emerging research has shown that particular binding sites are enriched at TAD boundaries.
-It has been established that the zinc finger protein, CTCF, is associated with TAD boundaries and is an architectural protein responsible for the organization of the genome within the nucleus [@ghirlando2016ctcf; @ong2014ctcf].
-CTCF along with other transcription factors, including SMC1, SMC3, and RAD21 have been shown to colocalize together near TAD boundaries, leading to the recruitment of a cohesin ring [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+[???
+This sentence and reference belong to the previous paragraph, think and move] It has been established that the zinc finger protein, CTCF, is associated with TAD boundaries and is an architectural protein responsible for the organization of the genome within the nucleus [@ghirlando2016ctcf; @ong2014ctcf].
+CTCF along with other transcription factors, including SMC1, SMC3, and RAD21 <!--have been shown to -->colocalize <!--together [???
+Note removal of "water" words]-->near TAD boundaries, leading to the recruitment of a cohesin ring [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
 Together, these components are hypothesized to be what causes loops in the DNA, contributing to higher order chromatin organization.
@@
 Even more so, loci within a domain have been shown to interact more frequently with one another, exhibiting similar patterns of chromatin modifications, and long-range contact patterns [@rao20143d].
-However, the growing number of annotated genomic features and the methods used to identify the ones associated with TAD boundaries still leaves much to be desired.
+[???
+This sentence and reference belong to the previous paragraph, think and move] However, the growing number of annotated genomic features and the methods used to identify the ones associated with TAD boundaries still leaves much to be desired.
+[???
+This is very weak and undefined.
+You started with mentioning prediction - finish with unsolved problems with it.]
+
+[!!! This paragraph defines problems]
 
 Current methods used to predict TAD boundaries rely on the use of classification algorithms to draw associations between functional annotations and regions that include TAD boundaries.
-However, this is a multi-faceted probelem.
-Many methods ignore key characteristics [??
-which ones ??; !!!editted] of 3D genomic data.
-<!--including sparsity of TAD boundaries as well as suitably describing the spatial relationship between annotations and TAD boundaries.-->
+However, <!--this is a multi-faceted probelem.
+[???
+"WATER"!]-->many key characteristics of 3D genomic data remains unexplored, potentially limiting performance of predictive modeling.
+<!--including sparsity of TAD boundaries as well as suitably describing the spatial relationship between annotations and TAD boundaries.-->Specifically, the minority of TAD boundaries as compared with the rest of the genome creates heavily imbalanced ratio of positive/negative classes usef to train the models.
+The imbalance ratio is defined as the ratio of minority classes (regions with TAD boundaries) to majority classes (regions without TAD boundaries) [@Orriols-Puig2008].
+[???
+You confused me a lot with this] Such heavily imbalanced datasets <!--are known to [???
+WATER!] -->adversely impact the performance of the classifiers as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
+Furthermore, it remains unclear how the increased resolution of Hi-C data affect the performance of predictive modeling.
+Lastly, the use of different levels of association between TAD boundaries and genomic features (number, or proportion of overlaps, or distance) as predictors remain underexplored.
 
-Firstly, sparsity of TAD boundary regions throughout the linear genome contribute to heavily imbalanced classes.
-This imbalance results in small imbalance ratios.
-The imbalance ratio is defined as the ratio of minority classes (regions with TAD boundaries) to majority classes (regions without TAD boundaries) [@Orriols-Puig2008].
-Such heavily imbalanced datasets are known to adversely impact the performance of the classifiers as the learned model is biased towards the majority class to minimize the overall error rate [@lusa2010class; @chen2013influence; @jeni2013facing] [??
-This sentence is very difficult to understand.
-Don't see connection between the bias and the error rate ??; !!!].
+[!!! The following paragraph should review previous work and highlight pitfalls, creating motivation for yor study]
 
-We can account for this imbalance at the data level in addition to at the evaluation level [??
-I rewrote this sentence.
-Was very wordy and difficult to follow ??].
+<!--Secondly, it is important to determine the optimal representation of the relationship between features in the model and genomic regions.
+This is known as feature engineering.
+Typical approaches include overlap counts [@hong2017computational] or percents [@mourad2016computational; @huang2015predicting].
+Counts refer to the number of times a genomic annotation directly overlaps with a TAD boundary region, e.g., a TAD boundary may overlap with several ChIP-seq peaks for a given transcription factor.
+Percents refers to the percent of overlap between a genomic annotation and a TAD boundary region, e.g., 60% of a TAD boundary region may overlap with a genomic region annotated as heterochromatin.
+Here, using percents offers a more granular approach, but it is unclear how it performs when compared to counts.
+On the other hand, the use of distances between TAD boundaries and genomic annotations has largely been ignored.
+Moreover, while direct overlaps represent the most straightforward measure of functional associations, they do not account for indirect relationships shown to be one of the major driving forces of genome regulation [???
+REFS].
+These relationships can be quantified using distances (in basepairs) from regions on the linear genome to regions that define functional genomic annotations.
+The most prominent example being the enhancer-promoter relationships, where enhancers are frequently located hundreds or thousands of bases away from their target promoters [@whalen2016enhancer].
+The use of distances have largely been ignored, yet have the potential to offer the most accurate spatial representation of which genomic features are associated with TAD boundaries.-->
+
+Lastly, model performance is heavily contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
+It is often unclear from previous studies what resolution contact matrices were used when retrieving TAD boundaries, and how other resolutions would affect their results.
+A lower resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
+This will contribute to smaller sample sizes and could effect predictive performances.
+To date, no study has compared the results of their predictive models built across multiple data resolutions.
+
+Furthermore... [??? You never describe the other data property - various levels of relationships]
+
 Data level solutions mostly involve re-sampling techniques, in which random sampling is used to either replicate or remove data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
 It has been shown that quite simple re-sampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
+[???
+So, if the problem is solved, why do you bother with class imbalance at all?]
+
 Evaluation level solutions include choosing suitable performance metrics for evaluating models.
-<!--These solutions are necessary given that the test set, used to validate re-sampled training sets, is itself imbalanced.--> It has been shown that common metrics such as accuracy and AUROC (area under the receiver operating characteristic curve) are insensitive to class imbalance [@prati2011survey; @wei2013role].
+It has been shown that common metrics such as accuracy and AUROC (area under the receiver operating characteristic curve) are insensitive to class imbalance [@prati2011survey; @wei2013role].
 A better measure to consider would be a composite metric involving all quadrants of the confusion matrix such as Matthews Correlation Coefficient (MCC).
@@
 A value of 0 indicates no better than random prediction.
+[???
+So, if the problem is solved, why do you bother with it at all?]
 
-<!--
+[??? Carefully think on the "why" questions above. This paragraph answers it, connect it]
 In a study published in 2016 [@mourad2016computational], an L1-regularized multiple logistic regression model was proposed using transcription factor binding sites on GM12878 to discriminate between regions with and without TADs, and to identify the most predictive factors associated with boundaries.
@@
 They also reported ROC (receiver operating characteristic) curves and subsequent AUC (area under the curve) as measures of their model's performance.
--->
 
-<!--
+[??? Carefully think on the "why" questions above. This paragraph answers it, connect it]
 A better threshold-free measure to use when dealing with imbalanced data is the area under the precision-recall curve (AUPRC).
@@
 A value of 0 indicates no better than random prediction.
--->
 
-<!--
+<--
 Two studies published in 2015 and 2017 respectively [@huang2015predicting; @hong2017computational] used re-sampling techniques prior to modeling, and both implemented random under-sampling to balance classes.
@@
 
-Secondly, it is important to determine the optimal representation of the relationship between features in the model and genomic regions.
-This is known as feature engineering.
-Typical approaches include overlap counts [@hong2017computational] or percents [@mourad2016computational; @huang2015predicting].
-Counts refer to the number of times a genomic annotation directly overlaps with a TAD boundary region, e.g., a TAD boundary may overlap with several ChIP-seq peaks for a given transcription factor.
-Percents refers to the percent of overlap between a genomic annotation and a TAD boundary region, e.g., 60% of a TAD boundary region may overlap with a genomic region annotated as heterochromatin.
-Here, using percents offers a more granular approach, but it is unclear how it performs when compared to counts.
-On the other hand, the use of distances between TAD boundaries and genomic annotations has largely been ignored.
-Moreover, while direct overlaps represent the most straightforward measure of functional associations, they do not account for indirect relationships shown to be one of the major driving forces of genome regulation [???
-REFS].
-These relationships can be quantified using distances (in basepairs) from regions on the linear genome to regions that define functional genomic annotations.
-The most prominent example being the enhancer-promoter relationships, where enhancers are frequently located hundreds or thousands of bases away from their target promoters [@whalen2016enhancer].
-The use of distances have largely been ignored, yet have the potential to offer the most accurate spatial representation of which genomic features are associated with TAD boundaries.
-
-Lastly, model performance is heavily contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
-It is often unclear from previous studies what resolution contact matrices were used when retrieving TAD boundaries, and how other resolutions would affect their results.
-A lower resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
-This will contribute to smaller sample sizes and could effect predictive performances.
-To date, no study has compared the results of their predictive models built across multiple data resolutions.
-
-<!--
 [Paragraph about disconnect between Hi-C and epigenomic data] Despite the success of Hi-C technologies in revealing the high-order levels of genome organization (chromosome territories, A/B compartments, TADs, sub-TADs, chromatin loops), resolution of Hi-C data (~750kb [???
@@
 For this, we developed a model trained on a relatively coarse Hi-C data for predicting 3D features (TAD boundaries) from 1D data (epigenomic datasets).
--->
 
@@
 Under-sampling is performed without replacement from the majority class.
-Over-sampling is performed by creating new synthetic observations using the minority class.
+On the other hand, over-sampling is performed by creating new synthetic observations using the minority class.
 The minority class is over-sampled by taking each minority class sample and introducing synthetic examples along the feature vectors joining any/all of the k=5 (default) minority class nearest neighbors.
@@
 
-## DATA CONSTRUCTION FOR UNBIASED COMPARISONS BETWEEN RESOLUTION-SPECIFIC RANDOM FOREST CLASSIFIERS
+## Data construction for unbiased comparisons between resolution specific random forest classifiers
 <!--## CELL LINE AND DATA [??? What data?] RESOLUTION SPECIFIC MODEL [??? What model?] CONSTRUCTION [??? Why?] !!!created new header-->
 
-In total, we analyzed publically available Hi-C data for both the GM12878 and K562 cell lines, at four resolutions including 10 kb, 25 kb, 50 kb, and 100 kb.
-Given the varying levels of data resolution, we created a resolution-specific approach toward data constuction used for downstream modelling (Figure 1).
+In total, we analyzed [???
+Very boring] publically available Hi-C data for both the GM12878 and K562 cell lines, at four resolutions including 10 kb, 25 kb, 50 kb, and 100 kb.
+[???
+But why?
+Problem is not defined] Given the varying levels of data resolution, we created a resolution-specific approach toward data constuction used for downstream modelling (Figure 1).
 This allowed us an unbiased way to compare performances of random forest classifiers between varying resolutions of Hi-C data.
 [???
-Boring.
-What problem you are solving?;!!!editted]
+Problem is not defined]
 
@@
 To investigate class imbalance, defined as the ratio of TAD vs.
-non-TAD regions, we estimated the number of TAD boundaries ($Y=1$ in the response vector) and the rest of genomic bins ($Y=0$) at each of the four resolutions of Hi-C data.
+non-TAD boundaries, we estimated the number of TAD boundaries ($Y=1$ in the response vector) and the rest of genomic bins ($Y=0$) at four resolutions of Hi-C data.
 Expectedly, the average number of TAD boundaries and the rest of genomic bins increased with the increased resolution of Hi-C data (Table 1) irrespectively of cell line (Supplementary Tables 3).
-However, imbalance ratios were found to be invariant to resolution, remaining consistently low with very little variability between chromosomes, regardless of cell line.
+<!--This correlation [??
+What correlation ??] with resolution was found to be significant, as evidenced by large intraclass correlation coefficients (ICC) (Table 2; Supplementary Tables 4).
+However, the class imbalance problem, caused by the sparsity of TAD boundaries throughout the genome, was found to be much more consistant across resolutions in both cell lines.
+This imbalance was evidenced by low imbalance ratios, defined as the ratio of the number of genomic bins that overlapped with flanked TAD boundaries, to the much larger number of genomic bins that did not.
+This relationship was not significantly correlated with resoltuion for either cell line, indicating that there existed a severe disparity between classes at all resolutions of Hi-C data.-->
 
-**Table 1. Sparce TAD boundaries throughout the linear genome create high imbalance ratios irrespective of resolution.**
+**Table 1. Sparse TAD boundaries throughout the linear genome create high imbalance ratios irrespective of resolution.**
 
@@
 
-<!--We then went on the evaluate the effect of class imbalance on model performance.--> In order to set a baseline in performance, we first evaluated the least granular random forest classifier, that is one implemented using OC predictor types, without data re-sampling.
+<!--We then went on the evaluate the effect of class imbalance on model performance.--> In order to set a baseline in performance, we first evaluated the least granular model, that is one implemented using OC predictor types, without data re-sampling.
 We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 4A).
-We gradually increased the complexity in data level characteristics by assessing models built on OP predictor types, while still not performing any data resampling.
+We gradually increased the granularity [??
+Really confused by the constant use of granularity.
+Why is it needed ??] by assessing models built on OP predictor types, while still not performing any data resampling.
 Here, the results were similar to that of OC types (Figure 4B).
@@
 Furthermore, we found that conventional metrics of performance (i.e.
-accuracy and AUC) were less sensitive to models built on imbalanced data, regardless of cell line, resolution, or predictor-type (Supplementary Tables 6-7).
+accuracy, sensitivity and specificity, and AUC) were less sensitive to models built on imbalanced data, regardless of cell line, resolution, or predictor-type (Supplementary Tables 6-7).
 

### 2019-06-05 Manuscript/manuscript.Rmd

@@
 
-<!--We then went on the evaluate the effect of class imbalance on model performance.--> In order to set a baseline in performance, we first evaluated the least granular model, that is one implemented using OC predictor types, without data re-sampling.
+In order to set a baseline in performance, we first evaluated the least granular random forest classifier, that is one implemented using OC predictor types, without data re-sampling.
 We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 4A).
-We gradually increased the granularity [??
-Really confused by the constant use of granularity.
-Why is it needed ??] by assessing models built on OP predictor types, while still not performing any data resampling.
+We gradually increased the complexity in data level characteristics by assessing models built on OP predictor types, while still not performing any data resampling.
 Here, the results were similar to that of OC types (Figure 4B).
@@
 Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/figure4_gm12878_model_performances.png)
-
-<!--
-When models were built on randomly oversampled (ROS) data for GM12878, we found an increase in MCC compared to no resampling, at higher resolutions.
-The biggest improvement in performance was seen at the 10 kb resolution in each of the 3 predictor types, with a downward trend as resolutions decreased.
-Again, distance-type predictors were found to offer the highest MCCs for ROS data, across all resolutions.
-Similar results were obtained when applying ROS to the K562 cell line (Supplementary Figure 3).
-
-Further improvement in performance was found when models were implemented on both randomly undersampled (RUS) and SMOTE resampled data, especially between models with OC and OP predictor types.
-When using RUS or SMOTE, implemented on distance type predictors, we found a clear improvement compared to the other predictor types.
-However, there was less of a separation between ROS and RUS techniques within the ensemble of models using distance type predictors.
-
-Overall, SMOTE resampled data was found to yield the best MCCs among all classes of models developed and compared in the ensemble framework.
-Here, distance type predictors were found to again yield the highest MCC values across resolutions.
-It should be noted that, SMOTE re-sampled data, with the inclusion of distance-type predictors was also found to be the best set of characteristics when applied to the K562 cell line (Supplementary Figure 3).
-Moreover, for these sets of data characteristics, we again found that there was a degredation in model performance as data resolution decreased.
-Results indicated that performances exhibited much more variability when built on lower resolutions, specifically at the 100 kb level.
-These results imply that a best performing model, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
--->
 

### 2019-06-05 Scripts/evaluating_model_performances.Rmd
new results after tuning for mtry

@@
 title: "Evaluating Model Performances"
+subtitle: "RF; no enet"
 author: "Spiro Stilianoudakis"
@@
 		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("rfperf_noenet.rds" %in% files){
 		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
@@
 									   k, 
-									   "/enet/rfperf.rds"))
+									   "/enet/rfperf_noenet.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
 
@@
 		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("rfperf_noenet.rds" %in% files){
 		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
@@
 		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("rfperf_noenet.rds" %in% files){
 		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
@@
 		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("rfperf_noenet.rds" %in% files){
 		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
@@
 		for(k in c("distance", "oc", "op")){
+		  files <- list.files(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("rfperf_noenet.rds" %in% files){
 		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
@@
 										  perfdata[15,2])
+
 		}
@@
 		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("rfperf_noenet.rds" %in% files){
 		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
@@
 		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("rfperf_noenet.rds" %in% files){
 		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
@@
 		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("rfperf_noenet.rds" %in% files){
 		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
@@
      theme_bw()+
-     xlab("") + ylab("") + ylim(-.05,.5) +
+     xlab("") + ylab("") + ylim(-.1,.5) +
      ggtitle("Overlap Counts") +
@@
      theme_bw()+
-     xlab("") + ylab("") + ylim(-.05,.5) +
+     xlab("") + ylab("") + ylim(-.1,.5) +
      ggtitle("Overlap Percents") +
@@
      theme_bw()+
-     xlab("") + ylab("") + ylim(-.05,.5) +
+     xlab("") + ylab("") + ylim(-.1,.5) +
      ggtitle("Distance") +

### 2019-06-06 Scripts/comparing_distance_profiles_using_boxplots.Rmd
edits from tuning mtry

@@
 
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/gm12878_10kb.rds")
+binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")
+
 dist_list_gm12878_10kb <- list()
@@
 for(i in 1:length(chrs)){
-	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/gm12878_10kb.rds")
-
-	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")
 
@@
 ```{r}
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/gm12878_25kb.rds")
+binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")
 
@@
 for(i in 1:length(chrs)){
-	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/gm12878_25kb.rds")
-
-	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")
 
@@
 ```{r}
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/gm12878_50kb.rds")
+binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")
 
@@
 for(i in 1:length(chrs)){
-	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/gm12878_50kb.rds")
-
-	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")
 
@@
 ```{r}
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/gm12878_100kb.rds")
+binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")
 
@@
 for(i in 1:length(chrs)){
-	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/gm12878_100kb.rds")
-
-	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")
 
@@
 ```{r}
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/K562_10kb.rds")
+binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")
 
@@
 for(i in 1:length(chrs)){
-	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/K562_10kb.rds")
-
-	  binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")
 
@@
 ```{r}
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/K562_25kb.rds")
+binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")
 
@@
 for(i in 1:length(chrs)){
-	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/K562_25kb.rds")
-
-	  binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")
 
@@
 ```{r}
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/K562_50kb.rds")
+binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")
 
@@
 for(i in 1:length(chrs)){
-	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/K562_50kb.rds")
-
-	  binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")
 
@@
 ```{r}
+whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/K562_100kb.rds")
+binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")
 
@@
 for(i in 1:length(chrs)){
-	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/K562_100kb.rds")
-
-	  binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")
 

### 2019-06-06 Scripts/evaluating_dist_densities.Rmd
edits from tuning mtry

@@
 ```{r}
-NTdistance_list_gm12878 <- readRDS("Z:/TAD_data_analysis/NTdistance_list_gm12878.rds")
+NTdistance_list_gm12878 <- readRDS("Z:/TAD_data_analysis/distance_densities/NTdistance_list_gm12878.rds")
 
-LTdistance_list_gm12878 <- readRDS("Z:/TAD_data_analysis/LTdistance_list_gm12878.rds")
+LTdistance_list_gm12878 <- readRDS("Z:/TAD_data_analysis/distance_densities/LTdistance_list_gm12878.rds")
 
@@
 ```{r}
-NTdistance_list_K562 <- readRDS("Z:/TAD_data_analysis/NTdistance_list_K562.rds")
+NTdistance_list_K562 <- readRDS("Z:/TAD_data_analysis/distance_densities/NTdistance_list_K562.rds")
 
-LTdistance_list_K562 <- readRDS("Z:/TAD_data_analysis/LTdistance_list_K562.rds")
+LTdistance_list_K562 <- readRDS("Z:/TAD_data_analysis/distance_densities/LTdistance_list_K562.rds")
 
@@
 ```{r}
-allplots_gm12878 <- ggarrange(ntplot10kb_gm12878,
-                          ntplot25kb_gm12878,
-                          ntplot50kb_gm12878,
-                          ntplot100kb_gm12878, 
-          ncol=4, 
-          nrow=1,
-          labels = c("A", "B", "C", "D"),
+
+gm12878_nt_plot <- ggplot(gm12878_dist_densities[which(gm12878_dist_densities$Transformation=="Untransformed"),], aes(x=value, group=variable)) + 
+  facet_grid(Transformation ~ Resolution, scales="free") +
+  geom_density(alpha=.5, color="red") + 
+  xlim(0,30000000) +
+  scale_x_continuous(limits = c(0,3e+7),
+                     breaks = c(0, 1e+07, 2e+07, 3e+07),
+                     labels = c(0,1,2,3))+
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     strip.text.x = element_text(size = 15),
+     strip.text.y = element_text(size = 15),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+gm12878_lt_plot <- ggplot(gm12878_dist_densities[-which(gm12878_dist_densities$Transformation=="Untransformed"),], aes(x=value, group=variable)) + 
+  facet_grid(Transformation ~ Resolution, scales="free") +
+  geom_density(alpha=.5, color="blue") + 
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_blank(),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     strip.text.x = element_text(size = 15),
+     strip.text.y = element_text(size = 15),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+allplots_gm12878 <- ggarrange(gm12878_nt_plot,
+                          gm12878_lt_plot, 
+          ncol=1, 
+          nrow=2,
+          labels = "AUTO",
           font.label = list(size=20))
@@
 annotate_figure(allplots_gm12878,
-                bottom = text_grob("Distance (in millions of basepairs)", 
+                bottom = text_grob("Distance (mb)", 
                                    color = "black", 
@@
                                  rot = 90))
+```
 
-allplots_gm12878 <- ggarrange(ltplot10kb_gm12878,
-                          ltplot25kb_gm12878,
-                          ltplot50kb_gm12878,
-                          ltplot100kb_gm12878, 
-          ncol=4, 
-          nrow=1,
-          labels = c("E", "F", "G", "H"),
+###K562
+
+```{r}
+K562_dist_densities <- rbind.data.frame(NTdistance_list_K562[[1]],
+                                           NTdistance_list_K562[[2]],
+                                           NTdistance_list_K562[[3]],
+                                           NTdistance_list_K562[[4]],
+                                           LTdistance_list_K562[[1]],
+                                           LTdistance_list_K562[[2]],
+                                           LTdistance_list_K562[[3]],
+                                           LTdistance_list_K562[[4]])
+K562_dist_densities$Transformation <- c(rep("Untransformed", dim(NTdistance_list_K562[[1]])[1] + 
+                                                                dim(NTdistance_list_K562[[2]])[1] +
+                                                                dim(NTdistance_list_K562[[3]])[1] +
+                                                                dim(NTdistance_list_K562[[4]])[1]),
+                                           rep("Log2 Transformed", dim(LTdistance_list_K562[[1]])[1] + 
+                                                                dim(LTdistance_list_K562[[2]])[1] +
+                                                                dim(LTdistance_list_K562[[3]])[1] +
+                                                                dim(LTdistance_list_K562[[4]])[1]))
+K562_dist_densities$Resolution <- c(rep("10 kb", dim(NTdistance_list_K562[[1]])[1]),
+                                       rep("25 kb", dim(NTdistance_list_K562[[2]])[1]),
+                                       rep("50 kb", dim(NTdistance_list_K562[[3]])[1]),
+                                       rep("100 kb", dim(NTdistance_list_K562[[4]])[1]),
+                                       rep("10 kb", dim(LTdistance_list_K562[[1]])[1]),
+                                       rep("25 kb", dim(LTdistance_list_K562[[2]])[1]),
+                                       rep("50 kb", dim(LTdistance_list_K562[[3]])[1]),
+                                       rep("100 kb", dim(LTdistance_list_K562[[4]])[1]))
+K562_dist_densities$Transformation <- factor(K562_dist_densities$Transformation, levels=c("Untransformed", "Log2 Transformed"))
+K562_dist_densities$Resolution <- factor(K562_dist_densities$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
+
+K562_nt_plot <- ggplot(K562_dist_densities[which(K562_dist_densities$Transformation=="Untransformed"),], aes(x=value, group=variable)) + 
+  facet_grid(Transformation ~ Resolution, scales="free") +
+  geom_density(alpha=.5, color="red") + 
+  xlim(0,30000000) +
+  scale_x_continuous(limits = c(0,3e+7),
+                     breaks = c(0, 1e+07, 2e+07, 3e+07),
+                     labels = c(0,1,2,3))+
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+        axis.text.y = element_blank(),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        strip.text.x = element_text(size = 15),
+        strip.text.y = element_text(size = 15),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        plot.title = element_text(size=20))
+
+K562_lt_plot <- ggplot(K562_dist_densities[-which(K562_dist_densities$Transformation=="Untransformed"),], aes(x=value, group=variable)) + 
+  facet_grid(Transformation ~ Resolution, scales="free") +
+  geom_density(alpha=.5, color="blue") + 
+  xlab("") + ylab("") +
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+        axis.text.y = element_blank(),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        strip.text.x = element_text(size = 15),
+        strip.text.y = element_text(size = 15),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        plot.title = element_text(size=20))
+
+allplots_K562 <- ggarrange(K562_nt_plot,
+                              K562_lt_plot, 
+                              ncol=1, 
+                              nrow=2,
+                              labels = "AUTO",
                               font.label = list(size=20))
-allplots_gm12878
-annotate_figure(allplots_gm12878,
-                bottom = text_grob("Log2 Transformed Distance", 
+allplots_K562
+annotate_figure(allplots_K562,
+                bottom = text_grob("Distance (mb)", 
                                    color = "black", 
@@
                                  rot = 90))
-
 ```
-
-###K562
-
-```{r}
-allplots_K562 <- ggarrange(ntplot10kb_K562,
-                          ntplot25kb_K562,
-                          ntplot50kb_K562,
-                          ntplot100kb_K562, 
-          ncol=4, 
-          nrow=1,
-          labels = c("A", "B", "C", "D"),
-          font.label = list(size=20))
-allplots_K562
-annotate_figure(allplots_K562,
-                bottom = text_grob("Distance (in millions of basepairs)", 
-                                   color = "black", 
-                                   face = "bold", 
-                                   size = 15),
-                left = text_grob("Density", 
-                                 color = "black",
-                                 size = 15,
-                                 rot = 90))
-
-allplots_K562 <- ggarrange(ltplot10kb_K562,
-                          ltplot25kb_K562,
-                          ltplot50kb_K562,
-                          ltplot100kb_K562, 
-          ncol=4, 
-          nrow=1,
-          labels = c("E", "F", "G", "H"),
-          font.label = list(size=20))
-allplots_K562
-annotate_figure(allplots_K562,
-                bottom = text_grob("Log2 Transformed Distance", 
-                                   color = "black", 
-                                   face = "bold", 
-                                   size = 15),
-                left = text_grob("Density", 
-                                 color = "black",
-                                 size = 15,
-                                 rot = 90))
-
-```

### 2019-06-06 Scripts/evaluating_variable_importances.Rmd
edits from tuning mtry

@@
 									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
-	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
 	  varimps <- varimps[order(varimps$Feature),]
@@
 									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
-	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
 	  varimps <- varimps[order(varimps$Feature),]
@@
 									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
-	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
 	  varimps <- varimps[order(varimps$Feature),]
@@
 names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
-all_varimps_gm12878 <- all_varimps_gm12878[order(all_varimps_gm12878$ave10kb, decreasing = TRUE),]
+all_varimps_gm12878 <- all_varimps_gm12878[order(rowMeans(all_varimps_gm12878[,-1]), decreasing = TRUE),]
 all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
@@
 names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
-all_varimps_K562 <- all_varimps_K562[order(all_varimps_K562$ave10kb, decreasing = TRUE),]
+all_varimps_K562 <- all_varimps_K562[order(rowMeans(all_varimps_K562[,-1]), decreasing = TRUE),]
 all_varimps_K562 <- all_varimps_K562[1:20,]
@@
 									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
-	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
 	  varimps <- varimps[order(varimps$Feature),]
@@
 									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
-	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
 	  varimps <- varimps[order(varimps$Feature),]
@@
 									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
-	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
 	  varimps <- varimps[order(varimps$Feature),]
@@
 									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
-	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)		
 	  varimps <- varimps[order(varimps$Feature),]
@@
 names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
-all_varimps_gm12878 <- all_varimps_gm12878[order(all_varimps_gm12878$ave10kb, decreasing = TRUE),]
+all_varimps_gm12878 <- all_varimps_gm12878[order(rowMeans(all_varimps_gm12878[,-1]), decreasing = TRUE),]
 #all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
@@
 names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
-all_varimps_K562 <- all_varimps_K562[order(all_varimps_K562$ave10kb, decreasing = TRUE),]
+all_varimps_K562 <- all_varimps_K562[order(rowMeans(all_varimps_K562[,-1]), decreasing = TRUE),]
 #all_varimps_K562 <- all_varimps_K562[1:20,]
@@
 									            "/smote/distance/enet/rfimpvars_histones.rds"))
-	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)		
 	  varimps <- varimps[order(varimps$Feature),]
@@
 									            "/smote/distance/enet/rfimpvars_histones.rds"))
-	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
 	  varimps <- varimps[order(varimps$Feature),]
@@
 									            "/smote/distance/enet/rfimpvars_histones.rds"))
-	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
 	  varimps <- varimps[order(varimps$Feature),]
@@
 									            "/smote/distance/enet/rfimpvars_histones.rds"))
-	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
 	  varimps <- varimps[order(varimps$Feature),]

### 2019-06-06 Manuscript/manuscript.Rmd
intro edits

@@
 Analyses have shown that the genome is folded into distinct compartments termed topologically associating domains (TADs) [@dixon2012topological].
-Approximately 60-80% of TADs remain stable across cell types [@Schmitt2016aa], suggesting that the boundaries of TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes.
+Given the high degree of conservation between cell types and species, it has been proposed that TADs represent a fundamental unit of organization, giving the genome its architecture [@rocha2015breaking; @dixon2012topological].
+Likewise, Evidence suggests that the boundaries that delineate TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes [@symmons2014functional].
+Even more so, loci within a domain have been shown to interact more frequently with one another, exhibiting similar patterns of chromatin modifications, and long-range contact patterns [@rao20143d; @symmons2014functional] [???
+This sentence and reference belong to the previous paragraph, think and move; !!!combined and moved].
 Furthermore, studies have shown that changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @Flavahan2016; @song2017ctcf].
@@
 
-The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries [???
+The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries [dixon2015chromatin; @di2017novo] [???
 REFS?
-Carefully select from my paper notes].
-Evidence suggests that regulatory elements and genes tend to interact more frequently within the same TAD [@symmons2014functional].
-[???
-This sentence and reference belong to the previous paragraph, think and move] It has been established that the zinc finger protein, CTCF, is associated with TAD boundaries and is an architectural protein responsible for the organization of the genome within the nucleus [@ghirlando2016ctcf; @ong2014ctcf].
+Carefully select from my paper notes; !!!added refs].
+It has been established that the zinc finger protein, CTCF, is associated with TAD boundaries and is an architectural protein responsible for the organization of the genome within the nucleus [@ghirlando2016ctcf; @ong2014ctcf].
 CTCF along with other transcription factors, including SMC1, SMC3, and RAD21 <!--have been shown to -->colocalize <!--together [???
@@
 Other binding proteins have been shown to mediate enhancer-promoter interactions, including the transcription factors YY1 and ZNF143, thereby influencing the delineation of topological domains [@weintraub2017yy1; @gonzalez2017znf143; @heidari2014genome].
-Even more so, loci within a domain have been shown to interact more frequently with one another, exhibiting similar patterns of chromatin modifications, and long-range contact patterns [@rao20143d].
-[???
-This sentence and reference belong to the previous paragraph, think and move] However, the growing number of annotated genomic features and the methods used to identify the ones associated with TAD boundaries still leaves much to be desired.
+However, the growing number of annotated genomic features and the methods used to identify the ones associated with TAD boundaries still leaves much to be desired.
 [???

### 2019-06-06 Manuscript/manuscript.Rmd
intro edits

@@
 
-The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed how the spatial organization of the human genome may affect genomic regulation [@lieberman2009comprehensive].
+The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed the spatial organization of the human genome <!--may affect genomic regulation--> [@lieberman2009comprehensive].
 Analyses have shown that the genome is folded into distinct compartments termed topologically associating domains (TADs) [@dixon2012topological].
-Given the high degree of conservation between cell types and species, it has been proposed that TADs represent a fundamental unit of organization, giving the genome its architecture [@rocha2015breaking; @dixon2012topological].
-Likewise, Evidence suggests that the boundaries that delineate TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes [@symmons2014functional].
+Given their high degree of conservation between cell types and species, it has been proposed that TADs represent the fundamental building blocks of organization, giving the genome its 3D structure [@rocha2015breaking; @dixon2012topological].
+Likewise, evidence suggests that the boundaries that delineate TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes [@symmons2014functional].
 Even more so, loci within a domain have been shown to interact more frequently with one another, exhibiting similar patterns of chromatin modifications, and long-range contact patterns [@rao20143d; @symmons2014functional] [???
@@
 
-The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries [dixon2015chromatin; @di2017novo] [???
+Distinct patterns in epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries [@dixon2015chromatin; @di2017novo] [???
 REFS?
 Carefully select from my paper notes; !!!added refs].
-It has been established that the zinc finger protein, CTCF, is associated with TAD boundaries and is an architectural protein responsible for the organization of the genome within the nucleus [@ghirlando2016ctcf; @ong2014ctcf].
-CTCF along with other transcription factors, including SMC1, SMC3, and RAD21 <!--have been shown to -->colocalize <!--together [???
-Note removal of "water" words]-->near TAD boundaries, leading to the recruitment of a cohesin ring [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+Recent research has identified key functional genomic annotations enriched at boundaries.
+Namely, the zinc finger protein, CTCF, has been shown to be associated with TAD boundaries [@ghirlando2016ctcf].
+Other transcription factors including SMC1, SMC3, and RAD21 have been shown to colocalize near TAD boundaries [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
 Together, these components are hypothesized to be what causes loops in the DNA, contributing to higher order chromatin organization.
-Other binding proteins have been shown to mediate enhancer-promoter interactions, including the transcription factors YY1 and ZNF143, thereby influencing the delineation of topological domains [@weintraub2017yy1; @gonzalez2017znf143; @heidari2014genome].
-However, the growing number of annotated genomic features and the methods used to identify the ones associated with TAD boundaries still leaves much to be desired.
+Additional binding proteins, known to mediate enhancer-promoter interactions including YY1 and ZNF143, have been shown to influence the delineation of topological domains [@weintraub2017yy1; @gonzalez2017znf143; @heidari2014genome].
+<!--However, there is a growing number of publically available annotated genomic features, and it is unclear if current methods are robust enough to identify all of them.
 [???
 This is very weak and undefined.
-You started with mentioning prediction - finish with unsolved problems with it.]
+You started with mentioning prediction - finish with unsolved problems with it.
+!!!editted]-->
 
@@
 
-Current methods used to predict TAD boundaries rely on the use of classification algorithms to draw associations between functional annotations and regions that include TAD boundaries.
+Current methods used to predict TAD boundaries rely on the use of classification models to draw associations between functional annotations and regions that include TAD boundaries.
 However, <!--this is a multi-faceted probelem.
 [???
-"WATER"!]-->many key characteristics of 3D genomic data remains unexplored, potentially limiting performance of predictive modeling.
-<!--including sparsity of TAD boundaries as well as suitably describing the spatial relationship between annotations and TAD boundaries.-->Specifically, the minority of TAD boundaries as compared with the rest of the genome creates heavily imbalanced ratio of positive/negative classes usef to train the models.
+"WATER"!]-->many key characteristics of 3D genomic data remain unexplored, potentially limiting performance of predictive modeling.
+<!--including sparsity of TAD boundaries as well as suitably describing the spatial relationship between annotations and TAD boundaries.-->Specifically, the minority of TAD boundaries as compared with the rest of the genome creates heavily imbalanced classes, characterized by ratios of positive/negative classes used to train the models.
 The imbalance ratio is defined as the ratio of minority classes (regions with TAD boundaries) to majority classes (regions without TAD boundaries) [@Orriols-Puig2008].
@@
 WATER!] -->adversely impact the performance of the classifiers as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
-Furthermore, it remains unclear how the increased resolution of Hi-C data affect the performance of predictive modeling.
-Lastly, the use of different levels of association between TAD boundaries and genomic features (number, or proportion of overlaps, or distance) as predictors remain underexplored.
+Furthermore, the use of different levels of association between TAD boundaries and genomic features (number, or proportion of overlaps, or distance) as predictors remain underexplored.
+Lastly, it remains unclear how the increased resolution of Hi-C data affect the performance of predictive modeling.
 
@@
 
-<!--Secondly, it is important to determine the optimal representation of the relationship between features in the model and genomic regions.
-This is known as feature engineering.
-Typical approaches include overlap counts [@hong2017computational] or percents [@mourad2016computational; @huang2015predicting].
-Counts refer to the number of times a genomic annotation directly overlaps with a TAD boundary region, e.g., a TAD boundary may overlap with several ChIP-seq peaks for a given transcription factor.
-Percents refers to the percent of overlap between a genomic annotation and a TAD boundary region, e.g., 60% of a TAD boundary region may overlap with a genomic region annotated as heterochromatin.
-Here, using percents offers a more granular approach, but it is unclear how it performs when compared to counts.
-On the other hand, the use of distances between TAD boundaries and genomic annotations has largely been ignored.
-Moreover, while direct overlaps represent the most straightforward measure of functional associations, they do not account for indirect relationships shown to be one of the major driving forces of genome regulation [???
-REFS].
-These relationships can be quantified using distances (in basepairs) from regions on the linear genome to regions that define functional genomic annotations.
-The most prominent example being the enhancer-promoter relationships, where enhancers are frequently located hundreds or thousands of bases away from their target promoters [@whalen2016enhancer].
-The use of distances have largely been ignored, yet have the potential to offer the most accurate spatial representation of which genomic features are associated with TAD boundaries.-->
-
-Lastly, model performance is heavily contingent upon the resolution of the contact matrix used to identify the location of TADs throughout the genome.
-It is often unclear from previous studies what resolution contact matrices were used when retrieving TAD boundaries, and how other resolutions would affect their results.
-A lower resolution contact matrix will result in the identification of larger-sized TADs, and subsequently, less TAD boundary points.
-This will contribute to smaller sample sizes and could effect predictive performances.
-To date, no study has compared the results of their predictive models built across multiple data resolutions.
-
-Furthermore... [??? You never describe the other data property - various levels of relationships]
-
-Data level solutions mostly involve re-sampling techniques, in which random sampling is used to either replicate or remove data points in order to create a more balanced dataset [@chawla2004special; @chawla2009data].
-It has been shown that quite simple re-sampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis].
-[???
-So, if the problem is solved, why do you bother with class imbalance at all?]
-
-Evaluation level solutions include choosing suitable performance metrics for evaluating models.
-It has been shown that common metrics such as accuracy and AUROC (area under the receiver operating characteristic curve) are insensitive to class imbalance [@prati2011survey; @wei2013role].
-A better measure to consider would be a composite metric involving all quadrants of the confusion matrix such as Matthews Correlation Coefficient (MCC).
-The suitability of MCC when evaluating models in imbalanced settings has been studied previously [@boughorbel2017optimal; @brodersen2010balanced].
-Defined, the MCC is the correlation coefficient between the observed and predicted binary classifications.
-A value of 1 represents a perfect prediction, while a value of -1 represents total disagreement between prediction and observation.
-A value of 0 indicates no better than random prediction.
-[???
-So, if the problem is solved, why do you bother with it at all?]
-
-[??? Carefully think on the "why" questions above. This paragraph answers it, connect it]
-In a study published in 2016 [@mourad2016computational], an L1-regularized multiple logistic regression model was proposed using transcription factor binding sites on GM12878 to discriminate between regions with and without TADs, and to identify the most predictive factors associated with boundaries.
-The class imbalance issue was not addressed.
-Even worse, when performing cross-validation, [@mourad2016computational] used the misclassification error rate of the model to establish the optimal L1-regularization lambda.
-They also reported ROC (receiver operating characteristic) curves and subsequent AUC (area under the curve) as measures of their model's performance.
-
-[??? Carefully think on the "why" questions above. This paragraph answers it, connect it]
-A better threshold-free measure to use when dealing with imbalanced data is the area under the precision-recall curve (AUPRC).
-The interpretation of the AUPRC of a model is similar to that of the AUROC.
-However, where as the baseline model performance according to the AUROC is given by 0.50, the baseline model performance according to the AUPRC is given by the ratio of true positives over the total number of cases [??
-Need to identify what you mean by "total number of cases." Is it just true positive divided by total number of possible boundaries ??].
-This enables a more realistic benchmark to evaluate a model on as this ratio will be lower than 0.5 for a test data set with imbalanced classes [@saito2015precision].
-Another threshold-specific measure to consider is a composite metric involving all quadrants of the confusion matrix, such as Matthews Correlation Coefficient (MCC) [@jeni2013facing; @chicco2017ten] [??
-MCC actually has all of the same components as AUC.
-AUC is a function of sensitivity and specificity which combined contain all quandrants ??].
-The MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
-A value of 1 represents a perfect prediction, while a value of -1 represents total disagreement between prediction and observation.
-A value of 0 indicates no better than random prediction.
-
-<--
-Two studies published in 2015 and 2017 respectively [@huang2015predicting; @hong2017computational] used re-sampling techniques prior to modeling, and both implemented random under-sampling to balance classes.
-However, given the large disparity between the number of genomic regions labeled as containing a TAD boundary or not, performing random under-sampling alone is likely to be unstable and introduce bias.
-Also, it is unclear how other data level solutions compare to simple random under-sampling such as random over-sampling or a weighted combination of both random under- and over-sampling together.
-Equally concerning is how the test set is treated in scenarios of re-sampling.
-It was found that [@huang2015predicting] performed re-sampling prior to splitting the data into training and testing.
-However, this is problematic because re-sampling prior to splitting can further introduce bias into the testing set, as it is no longer an accurate representation of real-world data [@wei2013role].
--->
-
-[Paragraph about disconnect between Hi-C and epigenomic data] Despite the success of Hi-C technologies in revealing the high-order levels of genome organization (chromosome territories, A/B compartments, TADs, sub-TADs, chromatin loops), resolution of Hi-C data (~750kb [???
-REF, Bonev 2017?]) remains well below resolution of epigenomic assays (hundredths of bases for ChIP-seq).
-One of the key missing pieces to connect 3D genome architecture to transcription has been the inability of Hi-C to attain the resolution necessary to discern gene-level features of chromatin.
-This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited our understanding of epigenomic regulation of gene expression and its potential link to chromatin architecture.
-Although computational [???
-REFS?](Zhang et al., “HiCPlus.”, Carron et al., “Boost-HiC.”) and technological [@Hsieh:2019aa][@Ma:1998aa][@Belaghzal2017] methods for enhancing resolution of Hi-C data started to appear, they [???
-remains to write about their pitfalls].
-One aim of this study is to predict the location of TAD boundaries on a scale comparable to epigenomic assays.
-For this, we developed a model trained on a relatively coarse Hi-C data for predicting 3D features (TAD boundaries) from 1D data (epigenomic datasets).
-
-In this study, we developed a novel ensemble framework aimed at systematically comparing the performances of random forest classification models in order to determine the set of data level characteristics necessary for optimal prediction of TAD boundaries.
-We evaluated performances of Hi-C data for both the GM12878 and K562 cell line obtained at four different Hi-C resolutions including 10 kb, 25 kb, 50 kb, and 100 kb resolution.
-For each cell line and resolution, we compared three feature engineering techniques: counts, percents, and distances.
-Additionally, we compared three re-sampling techniques: random under-sampling, random-over-sampling, and a weighted combination of both referred to as Synthetic Minority Over-sampling Technique (SMOTE).
-
-[???Include concluding paragraph]
+Recently, an L1-regularized multiple logistic regression model was developed to predict TAD boundaries using transcription factor binding sites on GM12878 [@mourad2016computational].
+Based on a 1 kb binned genomic data matrix and 20 kb flanked TAD boundaries, the model was trained to identify the set of transcription factors most influential of TAD boundaries.
+Several problems exist with the study.
+First, the class imbalance issue was not addressed.
+Secondly, many transcription factors are known to colocalize, and therefore exhibit high correlations.
+If a group of predictors are highly correlated among themselves, L1-regularization tends to pick only one of them and will shrink the others to zero [@zou2005regularization].
+Thirdly, [@mourad2016computational] reported ROC (receiver operating characteristic) curves and subsequent AUC (area under the curve) as measures of their model's performance.
+It has been shown that AUC is insensitive to class imbalance, creating artificially inflated values inlfuenced by the majority class [@prati2011survey; @wei2013role].
 

### 2019-06-06 Manuscript/manuscript.Rmd
intro edits

@@
 Furthermore, the use of different levels of association between TAD boundaries and genomic features (number, or proportion of overlaps, or distance) as predictors remain underexplored.
-Lastly, it remains unclear how the increased resolution of Hi-C data affect the performance of predictive modeling.
+Lastly, it remains unclear how increased resolution of Hi-C data might affect the performance of predictive models.
 
@@
 
-Recently, an L1-regularized multiple logistic regression model was developed to predict TAD boundaries using transcription factor binding sites on GM12878 [@mourad2016computational].
-Based on a 1 kb binned genomic data matrix and 20 kb flanked TAD boundaries, the model was trained to identify the set of transcription factors most influential of TAD boundaries.
-Several problems exist with the study.
-First, the class imbalance issue was not addressed.
-Secondly, many transcription factors are known to colocalize, and therefore exhibit high correlations.
-If a group of predictors are highly correlated among themselves, L1-regularization tends to pick only one of them and will shrink the others to zero [@zou2005regularization].
-Thirdly, [@mourad2016computational] reported ROC (receiver operating characteristic) curves and subsequent AUC (area under the curve) as measures of their model's performance.
+Recently, an L1-regularized multiple logistic regression model, called *HiCfeat*, was developed to predict TAD boundaries using transcription factor binding sites on GM12878 [@mourad2016computational].
+Based on a 1 kb binned genomic data matrix and 20 kb flanked TAD boundaries, the model was trained using proportions of overlaps between ChiP-seq peak defined functional element coordinates and genomic bins.
+However, several problems exist with this study.
+First, many transcription factors are known to colocalize, and therefore exhibit high correlations.
+Given a group of features that are highly correlated, L1-regularization tends to pick only one of them, while shrinking the others to zero [@zou2005regularization].
+Here, ensemble learning techniques could offer a more robust method toward identifying  annotations associated with TAD boudaries.
+Likewise, it is unclear how other sets of epigenomic features affect prediction, including chromatin state segmentations and histone modifications.
+Secondly, the class imbalance issue was not addressed prior to modelling.
+Instead, model performance was evaluated using ROC (receiver operating characteristic) curves and subsequent AUC (area under the curve).
 It has been shown that AUC is insensitive to class imbalance, creating artificially inflated values inlfuenced by the majority class [@prati2011survey; @wei2013role].
+It is unclear how simple data level solutions to class imbalance, such random under-sampling and random over-sampling affect TAD boundary prediction.
+Likewise, a more composite metric such as Matthews Correlation Coefficient (MCC), might provide more sensitive assessment of model performance.
+Thirdly, the relationship between annotations and boundaries was quantified using proportions of overlaps.
+This type of predictor ignores distances, which offers a much more spatially descriptive feature space and could improve predictive performance.
+Lastly, it is unclear how *HiCfeat* would perform on other cell lines and Hi-C data resolutions, giving *HiCfeat* a limited application in TAD boundary prediction.
+
+<!--
+[Paragraph about disconnect between Hi-C and epigenomic data] Despite the success of Hi-C technologies in revealing the high-order levels of genome organization (chromosome territories, A/B compartments, TADs, sub-TADs, chromatin loops), resolution of Hi-C data (~750kb [???
+REF, Bonev 2017?]) remains well below resolution of epigenomic assays (hundredths of bases for ChIP-seq).
+One of the key missing pieces to connect 3D genome architecture to transcription has been the inability of Hi-C to attain the resolution necessary to discern gene-level features of chromatin.
+This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited our understanding of epigenomic regulation of gene expression and its potential link to chromatin architecture.
+Although computational [???
+REFS?](Zhang et al., “HiCPlus.”, Carron et al., “Boost-HiC.”) and technological [@Hsieh:2019aa][@Ma:1998aa][@Belaghzal2017] methods for enhancing resolution of Hi-C data started to appear, they [???
+remains to write about their pitfalls].
+One aim of this study is to predict the location of TAD boundaries on a scale comparable to epigenomic assays.
+For this, we developed a model trained on a relatively coarse Hi-C data for predicting 3D features (TAD boundaries) from 1D data (epigenomic datasets).
+-->
+
+In this study, we developed a computational framework aimed at determining the optimal set of data level characteristics necessary for optimal prediction of TAD boundaries and identification of influential genomic annotations.
+We utilize random forest classification models built on HiC-data from two cell lines, including GM12878 and K562, obtained at four different resolutions, including 10 kb, 25 kb, 50 kb, and 100 kb.
+For each cell line and resolution, we compared three feature engineering techniques, including counts, percents, and distances.
+Additionally, we compared three re-sampling techniques, including random under-sampling, random over-sampling, and a weighted combination of both referred to as Synthetic Minority Over-sampling Technique (SMOTE).
+Model performances were evaluated and compared using Matthews Correlation Coefficient (MCC).
+
+[???Include concluding paragraph]
 

### 2019-06-07 Manuscript/manuscript.Rmd
methods edits

@@
 Once the model was implemented, it was validated on the test set.
-The performance of each model was compared using the composite metric, Matthews Correlation Coefficient (MCC), which is defined as follows:
+The performance of each model was compared using the composite metric, Matthews Correlation Coefficient (MCC).
+The MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
+A value of 1 represents a perfect prediction, while a value of -1 represents total disagreement between prediction and observation.
+A value of 0 indicates no better than random prediction.
+The MCC is defined as
 
@@
 
-Here, TP refers to the number of bins correctly identified as containing a TAD boundary (true positives), FP refers to the number of bins incorrectly identified as containing a TAD boundary (false positives), TN refers to the number of bins correctly identified as not containing a TAD boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a TAD boundary (false negatives).
+where TP refers to the number of bins correctly identified as containing a TAD boundary (true positives), FP refers to the number of bins incorrectly identified as containing a TAD boundary (false positives), TN refers to the number of bins correctly identified as not containing a TAD boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a TAD boundary (false negatives).
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.

### 2019-06-07 Manuscript/manuscript.Rmd
results paragraph 1 edits

@@
 
-## DATA CONSTRUCTION FOR UNBIASED COMPARISONS BETWEEN RESOLUTION-SPECIFIC RANDOM FOREST CLASSIFIERS
+## DEVELOPING A RESOLUTION-SPECIFIC APPROACH FOR DATA CONSTRUCTION
 <!--## CELL LINE AND DATA [??? What data?] RESOLUTION SPECIFIC MODEL [??? What model?] CONSTRUCTION [??? Why?] !!!created new header-->
 
-In total, we analyzed [???
-Very boring] publically available Hi-C data for both the GM12878 and K562 cell lines, at four resolutions including 10 kb, 25 kb, 50 kb, and 100 kb.
-[???
-But why?
-Problem is not defined] Given the varying levels of data resolution, we created a resolution-specific approach toward data constuction used for downstream modelling (Figure 1).
-This allowed us an unbiased way to compare performances of random forest classifiers between varying resolutions of Hi-C data.
-[???
-Problem is not defined]
+We developed a resolution-specific approach toward constructing data necessary for TAD boundary prediction.
+We illustrate the proposed method of construction using the following example (Figure 1).
+Given in-situ Hi-C data sequenced at 100 kb resolution, we binned the linear genome into 100 kb intervals.
+Using the Arrowhead TAD calling algorithm [@durand2016juicer], unique TAD boundaries were identified and flanked on either side by the corresponding bin width, $b$, for a total flanking width of $2b$ (i.e.
+if $b$=100 kb, the total flanked width of each TAD would be 200 kb).
+We defined the response vector **Y** as a variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y=1$) or not ($Y=0$).
+In total, we applied our method of data construction for four resolutions including 10 kb, 25 kb, 50 kb, and 100 kb.
 
-![**Model Construction for TAD boundary classification.** A subsection of the contact matrix for chromosome 14 on GM12878 [@durand2016juicer] at 100kb resolution shows the appearance of TAD boundaries.
+![**An illustration of the proposed approach for resolution-specific data construction used for TAD boundary prediction.** <!--A subsection of the contact matrix for chromosome 14 on GM12878 [@durand2016juicer] at 100kb resolution shows the appearance of TAD boundaries.
 To account for the uncertainty in TAD boundary location, each boundary point was flanked on both sides by resolution-specific genomic regions (bins).
-The response vector $Y$ was constructed by defining $Y=1$ if a bin flanks a TAD boundary, and $Y=0$ otherwise.
-<!--The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $\textbf{X} = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.-->](Figures/figure1_model_construction_V3.png)
+The response vector $Y$ was constructed by defining $Y=1$ if a bin flanks a TAD boundary, and $Y=0$ otherwise.-->](Figures/figure1_model_construction_V3.png)
 
@@
 
-After determining the optimal set of data level characteristics, we then aimed to compare the performances of annotation-specifc models [??
-In methods you say you do "feature selection" and then test model types.
-This implies the opposite ??].
+After determining the optimal set of data level characteristics, we then aimed to compare the performances of annotation-specifc models.
 In doing so, we inspected the proportion of predictive importance that was explained by each of the 3 groups of annotations (chromatin states, histone modifications, and transcription factor binding sites), across resolution.
@@
 We then sought to determine which of the transcription factor binding sites were most influential in predicting TAD boundaries.
-We found that the cell line specific binding sites associated with SMC3, CTCF, RAD21, ZNF143, and YY1sc281 were given consistently high predictive importance, across all resolutions [??
-Is this after elastic net?
-Elastic net distributes coefficients between correlated variables and it may affect variable importance ??] (Figure 7; Supplementary Figure 6).
+We found that the cell line specific binding sites associated with SMC3, CTCF, RAD21, ZNF143, and YY1sc281 were given consistently high predictive importance, across all resolutions (Figure 7; Supplementary Figure 6).
 The SMC3, CTCF, and RAD21 binding sites are known factors associated with the cohesin protein complex, which is hypothesized to be what creates loops in the DNA  [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].

### 2019-06-09 Scripts/evaluating_model_performances_xgboost.Rmd
aggregating xgb results

@@
 ---
-title: "evaluating_model_performances_xgboost"
+title: "Evaluating Model Performances"
+subtitle: "XGBoost; no enet"
 author: "Spiro Stilianoudakis"
-date: "May 30, 2019"
+date: "March 8, 2019"
 output: html_document
@@
 
-###MCC
-
-####RF; No elastic-net
-
 ```{r}
-mccdata_gm12878_10kb_rf <- numeric()
+mccdata_gm12878_10kb <- numeric()
 
@@
 		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("gbmperf_noenet.rds" %in% files){
 		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
@@
 									   k, 
-									   "/enet/rfperf_noenet.rds"))
+									   "/enet/gbmperf_noenet.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
 
-			mccdata_gm12878_10kb_rf <- rbind(mccdata_gm12878_10kb_rf,
+			mccdata_gm12878_10kb <- rbind(mccdata_gm12878_10kb,
 										  perfdata[15,2])
@@
 
-####XGB; no elastic-net
+##25kb
 
 ```{r}
-mccdata_gm12878_10kb_xgb <- numeric()
+mccdata_gm12878_25kb <- numeric()
 
@@
 		for(k in c("distance", "oc", "op")){
-			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("gbmperf_noenet.rds" %in% files){
+		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
 									   i, 
@@
 									   "/enet/gbmperf_noenet.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
 
-			mccdata_gm12878_10kb_xgb <- rbind(mccdata_gm12878_10kb_xgb,
+			mccdata_gm12878_25kb <- rbind(mccdata_gm12878_25kb,
 										  perfdata[15,2])
@@
 
-###Plots
+##50kb
 
 ```{r}
-all_rfperfs <- rbind.data.frame(mccdata_gm12878_10kb_rf,
-                                mccdata_gm12878_10kb_xgb)
+mccdata_gm12878_50kb <- numeric()
 
-all_rfperfs$Model <- c(rep("RF", length(mccdata_gm12878_10kb_rf)),
-                                rep("XGB", length(mccdata_gm12878_10kb_xgb)))
-all_rfperfs$Predictor <- rep(c("Distance", "OC", "OP"), 168)
-all_rfperfs$Resampling <- rep(c(rep("None", 3),
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("gbmperf_noenet.rds" %in% files){
+		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/gbmperf_noenet.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
+
+			mccdata_gm12878_50kb <- rbind(mccdata_gm12878_50kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
+
+##100kb
+
+```{r}
+mccdata_gm12878_100kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("gbmperf_noenet.rds" %in% files){
+		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/gbmperf_noenet.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
+
+			mccdata_gm12878_100kb <- rbind(mccdata_gm12878_100kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
+
+# K562
+
+##10kb
+
+```{r}
+mccdata_K562_10kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+		  files <- list.files(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("gbmperf_noenet.rds" %in% files){
+		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/gbmperf_noenet.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
+
+		  mccdata_K562_10kb <- rbind(mccdata_K562_10kb,
+										  perfdata[15,2])
+
+		}
+	}
+}
+
+```
+
+##25kb
+
+```{r}
+mccdata_K562_25kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("gbmperf_noenet.rds" %in% files){
+		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/gbmperf_noenet.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
+
+			mccdata_K562_25kb <- rbind(mccdata_K562_25kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
+
+##50kb
+
+```{r}
+mccdata_K562_50kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("gbmperf_noenet.rds" %in% files){
+		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/gbmperf_noenet.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
+
+			mccdata_K562_50kb <- rbind(mccdata_K562_50kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
+
+##100kb
+
+```{r}
+mccdata_K562_100kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("gbmperf_noenet.rds" %in% files){
+		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/gbmperf_noenet.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
+
+			mccdata_K562_100kb <- rbind(mccdata_K562_100kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
+
+## Plots
+
+```{r}
+all_xgbperfs <- rbind.data.frame(mccdata_gm12878_10kb,
+                                mccdata_gm12878_25kb,
+                                mccdata_gm12878_50kb,
+                                mccdata_gm12878_100kb,
+                                mccdata_K562_10kb,
+                                mccdata_K562_25kb,
+                                mccdata_K562_50kb,
+                                mccdata_K562_100kb)
+all_xgbperfs$CL <- c(rep("GM12878", length(mccdata_gm12878_10kb)*4), rep("K562", length(mccdata_K562_10kb)*4))
+all_xgbperfs$Resolution <- rep(c(rep("10 kb", 252),
+                            rep("25 kb", 252),
+                            rep("50 kb", 252),
+                            rep("100 kb", 252)))
+all_xgbperfs$Resampling <- rep(c(rep("None", 3),
                             rep("ROS", 3),
                             rep("RUS", 3),
-                            rep("SMOTE", 3)),42)
-all_rfperfs$Chromosome <- rep(c(rep("CHR1", 12),
+                            rep("SMOTE", 3)),168)
+all_xgbperfs$Predictor <- rep(c("Distance", "OC", "OP"), 672)
+all_xgbperfs$Chromosome <- c(rep("CHR1", 12),
                             rep("CHR2", 12),
@@
                             rep("CHR21", 12),
-                            rep("CHR22", 12)), 2)
+                            rep("CHR22", 12))
 
-all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
-all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("OC", "OP", "Distance"))
-all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))
+all_xgbperfs$CL <- factor(all_xgbperfs$CL, levels = c("GM12878", "K562"))
+all_xgbperfs$Resolution <- factor(all_xgbperfs$Resolution, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
+all_xgbperfs$Resampling <- factor(all_xgbperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
+all_xgbperfs$Predictor <- factor(all_xgbperfs$Predictor, levels = c("OC", "OP", "Distance"))
+all_xgbperfs$Chromosome <- factor(all_xgbperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))
 
-all_rfperfs_mcc <- all_rfperfs %>%
-  dplyr::group_by(Model, Resampling, Predictor) %>%
+all_xgbperfs_mcc <- all_xgbperfs %>%
+  dplyr::group_by(CL, Resolution, Resampling, Predictor) %>%
   dplyr::summarise(MCC = mean(V1, na.rm = TRUE),
@@
 
-ggplot(all_rfperfs_mcc, aes(x=Predictor, y=MCC, fill=Model)) +
-     #geom_line(size=2, position=position_dodge(0.5))+
-     #geom_point(size=5, position=position_dodge(0.5))+
-     #geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
-     #             position=position_dodge(0.5)) +
-     geom_bar(position=position_dodge(), stat="identity", colour='black') +
-     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,position=position_dodge(.9)) +
-     facet_grid(~ Resampling)+
+#GM12878
+c <- ggplot(all_xgbperfs_mcc[which(all_xgbperfs_mcc$CL=="GM12878" & all_xgbperfs_mcc$Predictor=="OC"),], aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     #facet_grid(~ Metric)+
      theme_minimal() +
      theme_bw()+
-     #xlab("") + ylab("") + ylim(-.05,.5) +
-     scale_color_discrete(name="Predictor Type")+
+     xlab("") + ylab("") + ylim(-.1,.5) +
+     ggtitle("Overlap Counts") +
+     scale_color_discrete(name="Resampling Technique")+
      guides(shape=FALSE, linetype=FALSE)+
@@
 
-```
-
-###F1
-
-####RF; No elastic-net
-
-```{r}
-F1data_gm12878_10kb_rf <- numeric()
-
-for(i in paste0("CHR", c(1:8,10:22))){
-	for(j in c("none","ros","rus","smote")){
-		for(k in c("distance", "oc", "op")){
-			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
-									   i, 
-									   "/",
-									   j, 
-									   "/", 
-									   k, 
-									   "/enet/rfperf_noenet.rds"))
-
-			F1data_gm12878_10kb_rf <- rbind(F1data_gm12878_10kb_rf,
-										  perfdata[16,2])
-		}
-	}
-}
-
-```
-
-####XGB; no elastic-net
-
-```{r}
-F1data_gm12878_10kb_xgb <- numeric()
-
-for(i in paste0("CHR", c(1:8,10:22))){
-	for(j in c("none","ros","rus","smote")){
-		for(k in c("distance", "oc", "op")){
-			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
-									   i, 
-									   "/",
-									   j, 
-									   "/", 
-									   k, 
-									   "/enet/gbmperf_noenet.rds"))
-
-			F1data_gm12878_10kb_xgb <- rbind(F1data_gm12878_10kb_xgb,
-										  perfdata[16,2])
-		}
-	}
-}
-
-```
-
-###Plots
-
-```{r}
-all_rfperfs <- rbind.data.frame(F1data_gm12878_10kb_rf,
-                                F1data_gm12878_10kb_xgb)
-
-all_rfperfs$Model <- c(rep("RF", length(F1data_gm12878_10kb_rf)),
-                                rep("XGB", length(F1data_gm12878_10kb_xgb)))
-all_rfperfs$Predictor <- rep(c("Distance", "OC", "OP"), 168)
-all_rfperfs$Resampling <- rep(c(rep("None", 3),
-                            rep("ROS", 3),
-                            rep("RUS", 3),
-                            rep("SMOTE", 3)),42)
-all_rfperfs$Chromosome <- rep(c(rep("CHR1", 12),
-                            rep("CHR2", 12),
-                            rep("CHR3", 12),
-                            rep("CHR4", 12),
-                            rep("CHR5", 12),
-                            rep("CHR6", 12),
-                            rep("CHR7", 12),
-                            rep("CHR8", 12),
-                            rep("CHR10", 12),
-                            rep("CHR11", 12),
-                            rep("CHR12", 12),
-                            rep("CHR13", 12),
-                            rep("CHR14", 12),
-                            rep("CHR15", 12),
-                            rep("CHR16", 12),
-                            rep("CHR17", 12),
-                            rep("CHR18", 12),
-                            rep("CHR19", 12),
-                            rep("CHR20", 12),
-                            rep("CHR21", 12),
-                            rep("CHR22", 12)), 2)
-
-all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
-all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("OC", "OP", "Distance"))
-all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))
-
-all_rfperfs_F1 <- all_rfperfs %>%
-  dplyr::group_by(Model, Resampling, Predictor) %>%
-  dplyr::summarise(F1 = mean(V1, na.rm = TRUE),
-            F1SD = sd(V1, na.rm = TRUE))
-
-ggplot(all_rfperfs_F1, aes(x=Predictor, y=F1, fill=Model)) +
-     #geom_line(size=2, position=position_dodge(0.5))+
-     #geom_point(size=5, position=position_dodge(0.5))+
-     #geom_errorbar(aes(ymin=F1-F1SD, ymax=F1+F1SD), width=1,
-     #             position=position_dodge(0.5)) +
-     geom_bar(position=position_dodge(), stat="identity", colour='black') +
-     geom_errorbar(aes(ymin=F1-F1SD, ymax=F1+F1SD), width=.5,position=position_dodge(.9)) +
-     facet_grid(~ Resampling)+
+p <- ggplot(all_xgbperfs_mcc[which(all_xgbperfs_mcc$CL=="GM12878" & all_xgbperfs_mcc$Predictor=="OP"),], aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     #facet_grid(~ Metric)+
      theme_minimal() +
      theme_bw()+
-     #xlab("") + ylab("") + ylim(-.05,.5) +
-     scale_color_discrete(name="Predictor Type")+
+     xlab("") + ylab("") + ylim(-.1,.5) +
+     ggtitle("Overlap Percents") +
+     scale_color_discrete(name="Resampling Technique")+
      guides(shape=FALSE, linetype=FALSE)+
@@
 
+d <- ggplot(all_xgbperfs_mcc[which(all_xgbperfs_mcc$CL=="GM12878" & all_xgbperfs_mcc$Predictor=="Distance"),], aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     #facet_grid(~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.1,.5) +
+     ggtitle("Distance") +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+figure <- ggarrange(c,p,d,
+                ncol = 3, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "top",
+                labels = "AUTO",
+                font.label = list(size=20))
+figure
+annotate_figure(figure,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("MCC", color = "black", rot = 90, size=20)
+)
+
+#K562
+c2 <- ggplot(all_xgbperfs_mcc[which(all_xgbperfs_mcc$CL=="K562" & all_xgbperfs_mcc$Predictor=="OC"),], aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     #facet_grid(~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.1,.5) +
+     ggtitle("Overlap Counts") +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+p2 <- ggplot(all_xgbperfs_mcc[which(all_xgbperfs_mcc$CL=="K562" & all_xgbperfs_mcc$Predictor=="OP"),], aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     #facet_grid(~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.1,.5) +
+     ggtitle("Overlap Percents") +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+d2 <- ggplot(all_xgbperfs_mcc[which(all_xgbperfs_mcc$CL=="K562" & all_xgbperfs_mcc$Predictor=="Distance"),], aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     #facet_grid(~ Metric)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("") + ylab("") + ylim(-.1,.5) +
+     ggtitle("Distance") +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+figure2 <- ggarrange(c2,p2,d2,
+                ncol = 3, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "top",
+                labels = "AUTO",
+                font.label = list(size=20))
+figure2
+annotate_figure(figure2,
+    bottom = text_grob("Resolution", color = "black", size = 20),
+    left = text_grob("MCC", color = "black", rot = 90, size=20)
+)
+
 ```

### 2019-06-10 Scripts/investigating_misclassified_TADs.Rmd
script for predicting finer bins

@@
 
-### GM12878
+```{r}
+misclassified_func <- function(CL, resolution, sampling="smote", predictor="distance", chromosome){
+  #reading in whole genome data
+	##setting directory specific to cell line and resolution 
+	if(CL=="GM12878"){dataset = "gm12878"}else{dataset = "K562"}
+	wgd_directory <- paste0("Z:/TAD_data_analysis/",
+	                        CL,
+							"/",
+							resolution,
+							"/training_testing/",
+							dataset,
+							"_",
+							resolution,
+							".rds")
+	whole_genome_dat <- readRDS(wgd_directory)
 
-####10kb
+	#reading in bin data on the whole genome that contains chromosome information
+	##setting directory specific to cell line and resolution 
+	bd_directory <- paste0("Z:/TAD_data_analysis/",
+	                        CL,
+							"/",
+							resolution,
+							"/training_testing/binslist",
+							gsub("kb","",resolution),
+							"_center.rds")
+	binslist_dat <- readRDS(bd_directory)
+
+	#removing duplicate annotations
+	if(CL=="GM12878"){
+		varstorm = c(names(whole_genome_dat)[grep("Ctcf-", names(whole_genome_dat))][-c(1:4)],
+					 names(whole_genome_dat)[grep("Ebf1sc137065-", names(whole_genome_dat))][-c(1:4)],
+                     names(whole_genome_dat)[grep("P300-", names(whole_genome_dat))][-c(1:4)],
+                     names(whole_genome_dat)[grep("Pol2-", names(whole_genome_dat))][-c(1:4)],
+                     names(whole_genome_dat)[grep("Rad21-", names(whole_genome_dat))][-c(1:4)])} else {
+		varstorm = c(names(whole_genome_dat)[grep("Atf3-", names(whole_genome_dat))][-c(1:4)],
+                     names(whole_genome_dat)[grep("Cmyc-", names(whole_genome_dat))][-c(1:4)],
+                     names(whole_genome_dat)[grep("Ctcf-", names(whole_genome_dat))][-c(1:4)],
+                     names(whole_genome_dat)[grep("E2f6-", names(whole_genome_dat))][-c(1:4)],
+                     names(whole_genome_dat)[grep("Max-", names(whole_genome_dat))][-c(1:4)],
+                     names(whole_genome_dat)[grep("P300-", names(whole_genome_dat))][-c(1:4)],
+                     names(whole_genome_dat)[grep("Pol2-", names(whole_genome_dat))][-c(1:4)],
+                     names(whole_genome_dat)[grep("Rad21-", names(whole_genome_dat))][-c(1:4)],
+                     names(whole_genome_dat)[grep("Yy1-", names(whole_genome_dat))][-c(1:4)])
+					 }
+
+	whole_genome_dat <- whole_genome_dat[,-which(names(whole_genome_dat) %in% varstorm)]
+
+	#reducing the whole genome data to only specific chromosome
+	reduce_chr <- tolower(chromosome)
+	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]
+
+	#splitting into training and testing
+	set.seed(123)
+    inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
+    train <- chr_specific_dat[inTrainingSet,]
+    test <- chr_specific_dat[-inTrainingSet,]
+
+	#reduce predictor space
+	if(predictor=="distance"){reduce_predictor = "_dist"}else if(predictor=="oc"){reduce_predictor = "_count"}else{reduce_predictor = "_perc"}
+
+	train <- train[,c(1,grep(reduce_predictor, names(train)))]
+	test <- test[,c(1,grep(reduce_predictor, names(test)))]
+
+	#reading in model and making predictions
+	model_directory <- paste0("Z:/TAD_data_analysis/",
+	                        CL,
+							"/",
+							resolution,
+							"/results_by_chr/",
+							chromosome,
+							"/",
+							"smote/distance/enet/rfModel_noenet.rds")
+  rfModel <- readRDS(model_directory)
+
+  predictions <- predict(rfModel, newdata=test)
+  preddata <- cbind.data.frame(Prediction = predictions, True=test$y)
+
+  #subset the false negatives (bins that were predicted as not overlapping with flanked TAD boundary but really were)
+  FNdata <- test[which(preddata$Prediction=="No" & preddata$True=="Yes"),]
+  FNdatamelt <- melt(FNdata[,-1])
+  FNdatamelt$Prediction <- "False Negatives"
+
+  #subset the true positives (bins that were predicted as overlapping with flanked TAD boundary and truely were)
+  TPdata <- test[which(preddata$Prediction=="Yes" & preddata$True=="Yes"),]
+  TPdatamelt <- melt(TPdata[,-1])
+  TPdatamelt$Prediction <- "True Positives"
+
+  prediction_data <- list(FNdatamelt,TPdatamelt)
+  return(prediction_data)
+}
+```
+
+## Plots
+
+```{r}
+allpredictiondata <- rbind.data.frame(prediction_data[[1]],prediction_data[[2]])
+allpredictiondata$Prediction <- factor(allpredictiondata$Prediction, levels=c("False Negatives","True Positives"))
+
+#looking at specific annotations
+##Ctcf
+ggplot(allpredictiondata[grep("Ctcf-",allpredictiondata$variable),], aes(x=value, color=Prediction)) +
+  geom_density() +
+  scale_color_discrete(name="Prediction Class") +
+  ylab("Density") +
+  xlab("Log2 Distance") +
+  #ylab("") +
+  #xlab("") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15 #,
+                                      #angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      #hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+##Rad21
+ggplot(allpredictiondata[grep("Rad21-",allpredictiondata$variable),], aes(x=value, color=Prediction)) +
+  geom_density() +
+  scale_color_discrete(name="Prediction Class") +
+  ylab("Density") +
+  xlab("Log2 Distance") +
+  #ylab("") +
+  #xlab("") +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15 #,
+                                      #angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      #hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+```
 

### 2019-06-10 Scripts/predicting_finer_bins.Rmd
added result script

---
title: "Predicting Finer Bins"
author: "Spiro Stilianoudakis"
date: "June 10, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

# Predict finer bins

```{r}
finer_resolution_predict_func <- function(CL, resolution, sampling, predictor, chromosome){
	#reading in whole genome data
	##setting directory specific to cell line and resolution 
	if(CL=="GM12878"){dataset = "gm12878"}else{dataset = "K562"}
	wgd_directory <- paste0("Z:/TAD_data_analysis/",
	                        CL,
							"/",
							resolution,
							"/training_testing/",
							dataset,
							"_",
							resolution,
							".rds")
	whole_genome_dat <- readRDS(wgd_directory)

	#reading in bin data on the whole genome that contains chromosome information
	##setting directory specific to cell line and resolution 
	bd_directory <- paste0("Z:/TAD_data_analysis/",
	                        CL,
							"/",
							resolution,
							"/training_testing/binslist",
							gsub("kb","",resolution),
							"_center.rds")
	binslist_dat <- readRDS(bd_directory)

	#annotations to keep
	#############################################
	#!!!make this cell line specific; don't include yy1 for k562
	#############################################

	if(CL=="GM12878" & predictor=="distance"){
	  annots = c("Gm12878-Ctcf-Broad_dist",
				   "Gm12878-Znf143166181ap-Sydh_dist",
				   "Gm12878-Rad21-Haib_dist",
				   "Gm12878-Smc3ab9263-Sydh_dist",
				   "Gm12878-Yy1sc281-Haib_dist")
	}else if(CL=="GM12878" & predictor=="count"){
	  annots = c("Gm12878-Ctcf-Broad_count",
				   "Gm12878-Znf143166181ap-Sydh_count",
				   "Gm12878-Rad21-Haib_count",
				   "Gm12878-Smc3ab9263-Sydh_count",
				   "Gm12878-Yy1sc281-Haib_count")
	}else if(CL=="K562" & predictor=="distance"){
	  annots = c("K562-Ctcf-Broad_dist",
				   "K562-Znf143-Sydh_dist",
				   "K562-Rad21-Haib_dist",
				   "K562-Smc3ab9263-Sydh_dist")
	}else{
	   annots = c("K562-Ctcf-Broad_count",
				   "K562-Znf143-Sydh_count",
				   "K562-Rad21-Haib_count",
				   "K562-Smc3ab9263-Sydh_count") 
	  }

	whole_genome_dat <- whole_genome_dat[,c(1,which(names(whole_genome_dat) %in% annots))]

	#reducing the whole genome data to only specific chromosome
	reduce_chr <- tolower(chromosome)
	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]

	train <- chr_specific_dat

	# set number of iterations
	samps = 50

	if(sampling=="ros"){
	    #assign sample indeces
		sampids <- matrix(ncol=samps, 
                  nrow=length(train$y[which(train$y=="No")]))

		#filling in the sample ids matrix
		set.seed(123)
		for(j in 1:samps){
			sampids[,j] <- sample(x = which(train$y=="Yes"),
                        size = length(which(train$y=="No")),
                        replace = TRUE)
		}
		train <- rbind.data.frame(train[which(train$y=="No"),],
                          train[sampids[,1],])
		#Randomly shuffle the data
		set.seed(321)
		train <- train[sample(nrow(train)),]
        }else if(sampling=="rus"){
		    #assign sample indeces
			sampids <- matrix(ncol=samps, 
                  nrow=length(train$y[which(train$y=="Yes")]))

			#filling in the sample ids matrix
			set.seed(123)
			for(j in 1:samps){
				sampids[,j] <- sample(x = which(train$y=="No"),
                        size = length(which(train$y=="Yes")),
                        replace = FALSE)
			}
			train <- rbind.data.frame(train[which(train$y=="Yes"),],
                          train[sampids[,1],])

			#Randomly shuffle the data
			set.seed(321)
			train <- train[sample(nrow(train)),]
			}else if(sampling=="smote"){
				set.seed(123)
				train <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

				#Randomly shuffle the data
				set.seed(123)
				train <- train[sample(nrow(train)),]
				}else{train=train}

	##set tuning parameters
	##set seeds for each cross folds
	set.seed(123)
	#length is = (n_repeats*nresampling)+1
	seeds <- vector(mode = "list", length = 11)
	#(1 is the number of tuning parameter lambda
	for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 100)
	#for the last model
	seeds[[11]]<-sample.int(1000, 1)

	##defining one summary function for roc,auprc,f1,and mcc
	allSummary <- function (data, lev = NULL, model = NULL) {
		lvls <- levels(data$obs)

		#mcc
		mcc <- ModelMetrics::mcc(ifelse(data$obs == lev[2], 0, 1), data[, lvls[1]], cutoff = .5)

		#roc
		b1 <- twoClassSummary(data, lev, model)

		#auprc & f1
		c1 <- prSummary(data, lev, model)

		out <- c(mcc, b1, c1)
		names(out)[1] <- c("MCC")
		out
	}

	##setting contols for elastic net
	fitControl <- trainControl(#seeds = seeds,
                           method = "cv",
                           number = 5,
                           ## Estimate class probabilities
                           classProbs = TRUE,
                           ## Evaluate performance using 
                           ## the following function
                           summaryFunction = allSummary)

	#set number of predictors to consider at each node
	tunegrid <- expand.grid(mtry=ceiling(sqrt(dim(train)[2] - 1)))

	#performing random forest
	rfModel <- train(y~., data=train, 
                 method="rf", 
                 metric="AUC", 
                 #tuneGrid=tunegrid, 
				 tuneLength=4,
                 trControl=fitControl, 
                 ntree=500) #as.numeric(rownames(results)[1]))

	return(rfModel)

}

```

# Make finer bins

```{r}
#CL="GM12878"; resolution="10kb"; sampling="smote"; predictor="distance"; chromosome="CHR22"

make_finer_test <- function(CL, resolution, sampling, predictor, chromosome){
	#reading in bin data on the whole genome that contains chromosome information
	##setting directory specific to cell line and resolution 
	bd_directory <- paste0("Z:/TAD_data_analysis/",
	                        CL,
							"/",
							resolution,
							"/training_testing/binslist",
							gsub("kb","",resolution),
							"_center.rds")
	binslist_dat <- readRDS(bd_directory)

	#extracting the first and last chromosome specific genomic coordinate
	reduce_chr <- tolower(chromosome)
	chr_binslist_dat <- binslist_dat[which(as.character(seqnames(binslist_dat))==reduce_chr)]
	min_point <- start(chr_binslist_dat)[1]+1
	max_point <- end(chr_binslist_dat)[length(chr_binslist_dat)]+1

	#creating finer bins for new test data
	##100 bases 
	test_bins <- GRanges(seqnames=reduce_chr, 
						 ranges=IRanges(start=seq(from=min_point, to=max_point, by=100), 
						 width=100))

	#reading chromosome and resolution specific boundary data
	bounds_directory <- paste0("Z:/TAD_data_analysis/",
	                        CL,
							"/",
							resolution,
							"/training_testing/bounds.rds")
	bounds <- readRDS(bounds_directory)
	bounds_f <- flank(bounds, width=100, both=TRUE)
	bounds_f <- bounds_f[which(as.character(seqnames(bounds_f))==tolower(chromosome))]

	#Creating Response Vector Y (1 if tad boundary is in bin; 0 if not)
	y <- countOverlaps(test_bins, bounds_f)
	y <- ifelse(y>=1,1,0)

	test_data <- data.frame(y = y)

	#creating a granges object from the center of every range in the new binned test data
	#this will be used to calculate distances from genomic feature to center of genomic bin
	test_bins_center <- resize(test_bins, width = 1, fix = "center")

	#annotating test data 
	##Creating Feature Space
	###calculating distance
	distance_func <- function(binned_data_center_gr, annot_data_center_gr){
		#distance from center of genomic bin to nearest genomic region of interest
		dist <- mcols(distanceToNearest(binned_data_center_gr, annot_data_center_gr))$distance
		return(dist)
	}

	####calculating count overlaps
	count_func <- function(binned_data_gr, annot_data_gr){
		#Finding the total number of overlaps between genomic bins and the specific genomic annotation
		count_total <- countOverlaps(binned_data_gr, annot_data_gr)

		return(count_total)
	}

	setwd("Z:/TAD_data_analysis/annotations/all_annotations/gm12878/")
	temp = list.files()

	#isolate specific annotations
	#############################################
	#!!!make this cell line specific; don't include yy1 for k562
	#############################################
	annots <- c("Gm12878-Ctcf-Broad.bed",
				"Gm12878-Znf143166181ap-Sydh.bed",
				"Gm12878-Rad21-Haib.bed",
				"Gm12878-Smc3ab9263-Sydh.bed",
				"Gm12878-Yy1sc281-Haib.bed")
	temp <- temp[which(temp %in% annots)]

	for(i in 1:length(temp)){
		#print(temp[i])
		dat <- read.table(temp[i],header = FALSE, sep="\t")
		dat_gr <- GRanges(seqnames=dat$V1,
						IRanges(start=dat$V2, 
								end=dat$V3))
		dat_gr_center <- resize(dat_gr, width = 1, fix = "center")

		####calculating distance
		d <- distance_func(test_bins_center, dat_gr_center)
		test_data <- cbind.data.frame(test_data,d)
		names(test_data)[length(names(test_data))] <- paste(sub(".bed", "", temp[i]), "_dist", sep="")

		####calculating count overlaps
		#co <- count_func(test_bins_center, dat_gr)
		#test_data <- cbind.data.frame(test_data,co)
		#names(test_data)[length(names(test_data))] <- paste(sub(".bed", "", temp[i]), "_count", sep="")

	}

	##Taking log2 transform of distance variables
	cols <- grep("dist",colnames(test_data))
	test_data[,cols] <- apply(test_data[,cols],2,function(x){log(x + 1, base=2)})

	##Changing levels of response (y) to yes no
	test_data$y <- factor(test_data$y)
	levels(test_data$y) <- c("No", "Yes")

	return(list(test_data,test_bins,test_bins_center))

}

test_list <- make_finer_test(CL="GM12878", resolution="10kb", sampling="smote", predictor="distance", chromosome="CHR22")

test_bins <- test_list[[2]]
test_bins_center <- test_list[[3]]
test_data <- test_list[[1]]

```

# Plots

```{r}
pred.rfModel2 <- predict(rfModel,newdata=test_data[,-1],type="prob")[,"Yes"]

	test_data$PredProb <- pred.rfModel2

mcols(test_bins_center)$prediction <- pred.rfModel2

test_data[which(test_data$y=="Yes"),][1:100,c(1,7)]

x <- cbind.data.frame(bin=seq(51224999+1, 51234999, 100),
                      PredProb=test_data$PredProb)

ggplot(x, aes(x=bin, y=PredProb)) + 
    geom_point() +
    geom_smooth(method="loess",size=1)+
    theme_minimal() +
    theme_bw()

```

### 2019-06-11 Manuscript/manuscript.Rmd
changed def of IR

@@
 Recent research has identified key functional genomic annotations enriched at boundaries.
-Namely, the zinc finger protein, CTCF, has been shown to be associated with TAD boundaries [@ghirlando2016ctcf].
+Namely, the CCCTC-binding factor  (CTCF), has been shown to be associated with TAD boundaries [@ghirlando2016ctcf].
 Other transcription factors including SMC1, SMC3, and RAD21 have been shown to colocalize near TAD boundaries [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
@@
 
-[!!! This paragraph defines problems]
-
-Current methods used to predict TAD boundaries rely on the use of classification models to draw associations between functional annotations and regions that include TAD boundaries.
-However, <!--this is a multi-faceted probelem.
-[???
-"WATER"!]-->many key characteristics of 3D genomic data remain unexplored, potentially limiting performance of predictive modeling.
-<!--including sparsity of TAD boundaries as well as suitably describing the spatial relationship between annotations and TAD boundaries.-->Specifically, the minority of TAD boundaries as compared with the rest of the genome creates heavily imbalanced classes, characterized by ratios of positive/negative classes used to train the models.
-The imbalance ratio is defined as the ratio of minority classes (regions with TAD boundaries) to majority classes (regions without TAD boundaries) [@Orriols-Puig2008].
-[???
-You confused me a lot with this] Such heavily imbalanced datasets <!--are known to [???
-WATER!] -->adversely impact the performance of the classifiers as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
+Current methods used to predict TAD boundaries rely on the use of classification models to draw associations between functional annotations and genomic regions that include TAD boundaries.
+However, many key characteristics of 3D genomic data remain unexplored, potentially limiting performance of predictive modeling.
+Specifically, the minority of TAD boundaries as compared with the rest of the genome creates heavily imbalanced classes, characterized by ratios of positive/negative classes used to train the models.
+Here, the imbalance ratio is defined as the ratio of majority classes (regions not including TAD boundaries) to minority classes (regions including TAD boundaries) [@Orriols-Puig2008].
+Such heavily imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
 Furthermore, the use of different levels of association between TAD boundaries and genomic features (number, or proportion of overlaps, or distance) as predictors remain underexplored.
 Lastly, it remains unclear how increased resolution of Hi-C data might affect the performance of predictive models.
-
-[!!! The following paragraph should review previous work and highlight pitfalls, creating motivation for yor study]
 
@@
 
-Class imbalance was characterized by each dataset's imalance ratio (IR), defined as the ratio of minority to majority sets given by the class of genomic bins:
+Class imbalance was characterized by each dataset's imalance ratio (IR), defined as the ratio of majority to minority sets given by the class of genomic bins:
 
-$$IR = \dfrac{C_{minority}}{C_{majority}}$$
+$$IR = \dfrac{C_{majority}}{C_{minority}}$$
 
-where $C_{minority}$ denotes the set of genomic bins that overlapped with flanked TAD boundaries and $C_{majority}$ denotes the set of genomic bins that did not overlap with a flanked TAD boundary.
+where $C_{majority}$ denotes the set of genomic bins that did not overlap with a flanked TAD boundary and $C_{majority}$ denotes the complementary set of genomic bins that did overlap with a flanked TAD boundary.
 In order to assess the influence of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling).
@@
 Expectedly, the average number of TAD boundaries and the rest of genomic bins increased with the increased resolution of Hi-C data (Table 1) irrespectively of cell line (Supplementary Tables 3).
-However, imbalance ratios were found to be invariant to resolution, remaining consistently low with very little variability between chromosomes, regardless of cell line.
+However, imbalance ratios were found to be invariant to resolution, remaining consistently high with very little variability between chromosomes, regardless of cell line.
 
@@
 |------------------------|-------------------------------------|---------------------------------------|------------------------------|
-| 10 kb                  | 12214.1 (6068.5)                    | 1254.6 (598.8)                        | 0.12 (0.02)                  |  
-| 25 kb                  | 4892.7 (2431.2)                     | 714.0 (358.4)                         | 0.17 (0.01)                  |
-| 50 kb	                 | 2450.9 (1217.6)                     | 364.4 (184.5)                         | 0.17 (0.01)                  |
-| 100 kb                 | 1227.5 (609.8)                      | 165.3 (90.9)                          | 0.15 (0.02)                  |
+| 10 kb                  | 12214.1 (6068.5)                    | 1254.6 (598.8)                        | 8.7 (1.2)                    |  
+| 25 kb                  | 4892.7 (2431.2)                     | 714.0 (358.4)                         | 5.9 (0.5)                    |
+| 50 kb	                 | 2450.9 (1217.6)                     | 364.4 (184.5)                         | 5.8 (0.5)                    |
+| 100 kb                 | 1227.5 (609.8)                      | 165.3 (90.9)                          | 6.8 (1.1)                    |
 

### 2019-06-11 Manuscript/manuscript.Rmd
editted first paragraph results

@@
 ## DEVELOPING A RESOLUTION-SPECIFIC APPROACH FOR DATA CONSTRUCTION
-<!--## CELL LINE AND DATA [??? What data?] RESOLUTION SPECIFIC MODEL [??? What model?] CONSTRUCTION [??? Why?] !!!created new header-->
 
-We developed a resolution-specific approach toward constructing data necessary for TAD boundary prediction.
-We illustrate the proposed method of construction using the following example (Figure 1).
-Given in-situ Hi-C data sequenced at 100 kb resolution, we binned the linear genome into 100 kb intervals.
-Using the Arrowhead TAD calling algorithm [@durand2016juicer], unique TAD boundaries were identified and flanked on either side by the corresponding bin width, $b$, for a total flanking width of $2b$ (i.e.
-if $b$=100 kb, the total flanked width of each TAD would be 200 kb).
-We defined the response vector **Y** as a variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y=1$) or not ($Y=0$).
-In total, we applied our method of data construction for four resolutions including 10 kb, 25 kb, 50 kb, and 100 kb.
+We analyzed publically published replicate HiC data sets from two cell lines (Supplementary Table 1): GM12878 and K562.
+Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at four resolutions: 10 kb, 25 kb, 50 kb, and 100 kb.
+To account for the varying levels of data resolution, we developed a resolution-specific approach toward constructing TAD vs non TAD boundary regions on the linear genome (Figure 1).
 
-![**An illustration of the proposed approach for resolution-specific data construction used for TAD boundary prediction.** <!--A subsection of the contact matrix for chromosome 14 on GM12878 [@durand2016juicer] at 100kb resolution shows the appearance of TAD boundaries.
-To account for the uncertainty in TAD boundary location, each boundary point was flanked on both sides by resolution-specific genomic regions (bins).
-The response vector $Y$ was constructed by defining $Y=1$ if a bin flanks a TAD boundary, and $Y=0$ otherwise.-->](Figures/figure1_model_construction_V3.png)
+![**An illustration of the proposed approach for resolution-specific data construction used for TAD boundary prediction.** Depicted is a subsection of the contact matrix of GM12878 (chromosome 14; 100kb) as visualized by JUICERBOX [@durand2016juicer].
+Resolution-specific TADs were called and unique boundaries were identified.
+Boundaries were flanked on either side according to the resolution (i.e.
+100 kb resolution corresponded to a 100 kb flank for a total boundary region of 200 kb).
+The linear genome was subsequently binned into resolution-specific intervals.
+The response vector **Y** was defined as a variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y = 1$) or not ($Y = 0$).
+](Figures/figure1_model_construction_V3.png)
+
+## TAD boundary regions exhibit cell-line specificity
 

### 2019-06-12 Manuscript/manuscript.Rmd
editting results

@@
 
-We analyzed publically published replicate HiC data sets from two cell lines (Supplementary Table 1): GM12878 and K562.
+We analyzed publically available replicate HiC data sets from two cell lines (Supplementary Table 1): GM12878 and K562.
 Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at four resolutions: 10 kb, 25 kb, 50 kb, and 100 kb.
-To account for the varying levels of data resolution, we developed a resolution-specific approach toward constructing TAD vs non TAD boundary regions on the linear genome (Figure 1).
+To account for the varying levels of data resolution, we developed a resolution-specific approach toward constructing TAD vs non TAD boundary regions on the linear genome.
+TAD boundary regions were defined as regions on the linear genome marking the coordinates of flanked TAD boundaries (Figure 1 A).
+To account for the varying levels of data resolution, we developed a resolution-specific approach toward constructing TAD vs non TAD boundary regions on the linear genome (Figure 1 B).
 
-![**An illustration of the proposed approach for resolution-specific data construction used for TAD boundary prediction.** Depicted is a subsection of the contact matrix of GM12878 (chromosome 14; 100kb) as visualized by JUICERBOX [@durand2016juicer].
-Resolution-specific TADs were called and unique boundaries were identified.
-Boundaries were flanked on either side according to the resolution (i.e.
+![**An illustration of the proposed approach for resolution-specific data construction used for TAD boundary prediction.** (A) Resolution-specific TADs were called and unique boundaries were identified.
+Boundaries were flanked on either side according to the Hi-C data resolution (i.e.
 100 kb resolution corresponded to a 100 kb flank for a total boundary region of 200 kb).
-The linear genome was subsequently binned into resolution-specific intervals.
-The response vector **Y** was defined as a variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y = 1$) or not ($Y = 0$).
-](Figures/figure1_model_construction_V3.png)
+(B) The linear genome was subsequently binned into resolution-specific intervals.
+The response vector **Y** was defined as a variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y = 1$) or not ($Y = 0$).](Figures/figure1_model_construction_V5.png)
+
+## Number of TAD boundary regions decrease as Hi-C data resolution decrease
 
@@
 
+![**Cell-line specific boundary summaries.** (A) Barplots illustrating that the total number of TAD boundary regions decreases as Hi-C data resolution decreases.
+(B) Venn diagrams showing that TAD boundary regions exhibit cell-line specificity across resolution.
+(C) Boxplots indicating that imbalance ratios remain severe irrespective of resolution.](Figures/bounds_and_irs.png)
+
+## IMBALANCE RATIOS REMAINED SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION
+
+To investigate class imbalance, defined as the ratio of TAD vs.
+non-TAD regions, we estimated the number of TAD boundaries ($Y=1$ in the response vector) and the rest of genomic bins ($Y=0$) at each of the four resolutions of Hi-C data.
+Expectedly, the average number of TAD boundaries and the rest of genomic bins increased with the increased resolution of Hi-C data (Table 1) irrespectively of cell line (Supplementary Tables 3).
+However, imbalance ratios were found to be invariant to resolution, remaining consistently high with very little variability between chromosomes, regardless of cell line.
+
+<!--
 **Table 1. Sparse TAD boundaries throughout the linear genome create high imbalance ratios irrespective of resolution.**
@@
 | 100 kb                 | 1227.5 (609.8)                      | 165.3 (90.9)                          | 6.8 (1.1)                    |
+-->
 

### 2019-06-12 Scripts/evaluating_imbalance_ratios.Rmd
edits

@@
 
-      ir.per.chr <- rbind(ir.per.chr, table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2]/table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[1])
+      ir.per.chr <- rbind(ir.per.chr, table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[1]/table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2])
 

### 2019-06-16 Scripts/evaluating_imbalance_ratios.Rmd
edits

@@
             MedIRIQR = IQR(ir, na.rm = TRUE))
+
+bounds_df <-irtab %>%
+  group_by(cl, res) %>%
+  dplyr::summarise(TotBounds = sum(bounds, na.rm = TRUE))
 ```
@@
 ```
+
+##Bounds Plots
+
+```{r}
+a <- ggplot(bounds_df[which(bounds_df$res=="10kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+  geom_bar(stat="identity", position="dodge")+
+  theme_minimal() +
+  theme_bw()+
+  xlab("") + ylab("") + ylim(0,27000) +
+  scale_fill_discrete(name="Cell Line") +
+  ggtitle("10 kb") +
+  guides(fill=FALSE) +
+  theme(axis.text.x = element_text(size=10),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+b <- ggplot(bounds_df[which(bounds_df$res=="25kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+  geom_bar(stat="identity", position="dodge")+
+  theme_minimal() +
+  theme_bw()+
+  xlab("") + ylab("") + ylim(0,27000) +
+  scale_fill_discrete(name="Cell Line") +
+  ggtitle("25 kb") +
+  guides(fill=FALSE) +
+  theme(axis.text.x = element_text(size=10),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+c <- ggplot(bounds_df[which(bounds_df$res=="50kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+  geom_bar(stat="identity", position="dodge")+
+  theme_minimal() +
+  theme_bw()+
+  xlab("") + ylab("") + ylim(0,27000) +
+  scale_fill_discrete(name="Cell Line") +
+  ggtitle("50 kb") +
+  guides(fill=FALSE) +
+  theme(axis.text.x = element_text(size=10),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+d <- ggplot(bounds_df[which(bounds_df$res=="100kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+  geom_bar(stat="identity", position="dodge")+
+  theme_minimal() +
+  theme_bw()+
+  xlab("") + ylab("") + ylim(0,27000) +
+  scale_fill_discrete(name="Cell Line") +
+  ggtitle("100 kb") +
+  guides(fill=FALSE) +
+  theme(axis.text.x = element_text(size=10),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+figure <- ggarrange(a,b,c,d,
+                    ncol=4,
+                    nrow=1)
+figure
+annotate_figure(figure,
+    #bottom = text_grob("Cell Line", color = "black", size = 20),
+    left = text_grob("Number of TAD Boundary Regions", color = "black", rot = 90, size=20)
+)
+
+```
+
+## IR Plots
+
+```{r}
+a <- ggplot(irtab[which(irtab$res=="10kb"),], aes(x=cl, y = ir, fill=cl, color=cl))  + 
+ stat_boxplot(geom ='errorbar', width = 0.2) + 
+ geom_boxplot() +
+ theme_minimal() +
+ theme_bw()+
+ xlab("") + ylab("") + #ylim(5,21) +
+ ggtitle("10 kb") +
+ guides(fill=FALSE) +
+ guides(color=FALSE) +
+ theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+b <- ggplot(irtab[which(irtab$res=="25kb"),], aes(x=cl, y = ir, fill=cl, color=cl))  + 
+ stat_boxplot(geom ='errorbar', width = 0.2) + 
+ geom_boxplot() +
+ theme_minimal() +
+ theme_bw()+
+ xlab("") + ylab("") + #ylim(5,21) +
+ ggtitle("25 kb") +
+ guides(fill=FALSE) +
+ guides(color=FALSE) +
+ theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+c <- ggplot(irtab[which(irtab$res=="50kb"),], aes(x=cl, y = ir, fill=cl, color=cl))  + 
+ stat_boxplot(geom ='errorbar', width = 0.2) + 
+ geom_boxplot() +
+ theme_minimal() +
+ theme_bw()+
+ xlab("") + ylab("") + #ylim(5,21) +
+ ggtitle("50 kb") +
+ guides(fill=FALSE) +
+ guides(color=FALSE) +
+ theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+d <- ggplot(irtab[which(irtab$res=="100kb"),], aes(x=cl, y = ir, fill=cl, color=cl))  + 
+ stat_boxplot(geom ='errorbar', width = 0.2) + 
+ geom_boxplot() +
+ theme_minimal() +
+ theme_bw()+
+ xlab("") + ylab("") + #ylim(5,21) +
+ ggtitle("100 kb") +
+ guides(fill=FALSE) +
+ guides(color=FALSE) +
+ theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+figure <- ggarrange(a,b,c,d,
+                    ncol=4,
+                    nrow=1)
+figure
+annotate_figure(figure,
+    #bottom = text_grob("Cell Line", color = "black", size = 20),
+    left = text_grob("Imbalance Ratio", color = "black", rot = 90, size=20)
+)
+
+```

### 2019-06-25 Manuscript/manuscript.Rmd
editted first 4 paragraphs of results; changed imbalance ratio to proportional imbalance

@@
 However, many key characteristics of 3D genomic data remain unexplored, potentially limiting performance of predictive modeling.
-Specifically, the minority of TAD boundaries as compared with the rest of the genome creates heavily imbalanced classes, characterized by ratios of positive/negative classes used to train the models.
-Here, the imbalance ratio is defined as the ratio of majority classes (regions not including TAD boundaries) to minority classes (regions including TAD boundaries) [@Orriols-Puig2008].
-Such heavily imbalanced datasets adversely impact the performance of the classifiers as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
+Specifically, the minority of TAD boundaries as compared with the rest of the genome creates proportionally small TAD boundary regions versus non boundary regions.
+Here, the proportion of imbalance is defined as the ratio of the set of TAD boundary regions to the sum of both TAD and non-TAD boundary regions.<!--Specifically, the minority of TAD boundaries as compared with the rest of the genome creates heavily imbalanced classes, characterized by ratios of positive/negative classes used to train the models.
+Here, the imbalance ratio is defined as the ratio of majority classes (regions not including TAD boundaries) to minority classes (regions including TAD boundaries) [@Orriols-Puig2008].--> Such heavily imbalanced datasets are known to adversely impact the performance of classifiers as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
 Furthermore, the use of different levels of association between TAD boundaries and genomic features (number, or proportion of overlaps, or distance) as predictors remain underexplored.
@@
 
-We analyzed publically available replicate HiC data sets from two cell lines (Supplementary Table 1): GM12878 and K562.
+We analyzed publically available replicate Hi-C data sets from two cell lines including GM12878 and K562 (Supplementary Table 1).
 Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at four resolutions: 10 kb, 25 kb, 50 kb, and 100 kb.
-To account for the varying levels of data resolution, we developed a resolution-specific approach toward constructing TAD vs non TAD boundary regions on the linear genome.
-TAD boundary regions were defined as regions on the linear genome marking the coordinates of flanked TAD boundaries (Figure 1 A).
-To account for the varying levels of data resolution, we developed a resolution-specific approach toward constructing TAD vs non TAD boundary regions on the linear genome (Figure 1 B).
+To account for the varying levels of data resolution, we developed a resolution-specific approach toward constructing TAD versus non TAD boundary regions on the linear genome, labeled as a response vector **Y** (Figure 1).
+First we binned the linear genome according to the data resolution.
+We then flanked the boundaries on either side by the same number of basepairs as the previously constructed genomic bins.
+TAD boundary regions were defined as regions on the linear genome where a genomic bin overlapped with a flanked TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as the regions that did not overlap with a flanked TAD boundary ($Y = 0$).
 
-![**An illustration of the proposed approach for resolution-specific data construction used for TAD boundary prediction.** (A) Resolution-specific TADs were called and unique boundaries were identified.
-Boundaries were flanked on either side according to the Hi-C data resolution (i.e.
+![**An illustration of the proposed approach for resolution-specific data construction used for TAD boundary prediction.** Resolution-specific TADs were called and unique boundaries were identified, denoted by the blue dots.
+The yellow regions denote the flanked boundary regions according to the Hi-C data resolution (i.e.
 100 kb resolution corresponded to a 100 kb flank for a total boundary region of 200 kb).
-(B) The linear genome was subsequently binned into resolution-specific intervals.
-The response vector **Y** was defined as a variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y = 1$) or not ($Y = 0$).](Figures/figure1_model_construction_V5.png)
+The linear genome was subsequently binned into resolution-specific intervals.
+The response vector **Y** was defined as a variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y = 1$) or not ($Y = 0$).](Figures/figure1_model_construction_V7.png)
 
-## Number of TAD boundary regions decrease as Hi-C data resolution decrease
+## TOTAL NUMBER OF TAD BOUNDARY REGIONS DECREASE AS Hi-C DATA RESOLUTION DECREASES
 
-## TAD boundary regions exhibit cell-line specificity
+Expectedly, the total number of TAD boundary regions increased with the increased resolution of Hi-C data irrespectively of cell line (Figure 2 A).
+At higher resolutions, GM12878 was found to contain more TADs, and thus more TAD boundary regions compared to K562.
+This can largely be attributed to the increased sequencing depth of the GM12878 library.
+However, this difference was found to dissipate as resolution decreased, resulting in much more similar numbers of TAD boundary regions between the two cell lines at the 50 kb and 100 kb resolutions respectively.
 
+## TAD BOUNDARY REGIONS EXHIBIT CELL-LINE SPECIFICITY
+
+We then sought to compare the cell-line specificity of TAD boundary regions.
+Between the two cell lines, a significant number of TAD boundary regions were specific to one of the two cell lines (Figure 2 B).
+It was found that 45%, 38%, 37%, and 36% of TAD boundary regions were specific to the GM12878 cell line, across each resolution respectively.
+Similarly, for K562, it was found that 27%, 27%, 29%, and 33% of TAD boundary regions were cell line specific for each resolution specifically.
+
+## PROPORTIONAL IMBALANCE REMAINED SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION
+
+We then investigated the proportion of class imbalance, defined as the ratio of TAD boundary regions versus the sum of both TAD and non-TAD boundary regions.
+We compared the estimated the number of TAD boundary regions ($Y=1$ in the response vector) and the rest of genomic bins ($Y=0$) for each cell line, at each of the four resolutions of Hi-C data.
+The proportional imbalance was found to be invariant to resolution, remaining consistently low for both cell lines, with very little variability between chromosomes (Figure 3 C).
+
+![**Cell-line specific boundary summaries.** (A) Barplots illustrating that the total number of TAD boundary regions decreases as Hi-C data resolution decreases.
+(B) Venn diagrams showing that TAD boundary regions exhibit cell-line specificity across resolution.
+(C) Boxplots indicating that the proportion of class imbalance remained severe irrespective of resolution.](Figures/bounds_and_pis.png)
+
+<!--
 ## IMBALANCE RATIOS REMAINED SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION
@@
 However, imbalance ratios were found to be invariant to resolution, remaining consistently high with very little variability between chromosomes, regardless of cell line.
-
-![**Cell-line specific boundary summaries.** (A) Barplots illustrating that the total number of TAD boundary regions decreases as Hi-C data resolution decreases.
-(B) Venn diagrams showing that TAD boundary regions exhibit cell-line specificity across resolution.
-(C) Boxplots indicating that imbalance ratios remain severe irrespective of resolution.](Figures/bounds_and_irs.png)
-
-## IMBALANCE RATIOS REMAINED SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION
-
-To investigate class imbalance, defined as the ratio of TAD vs.
-non-TAD regions, we estimated the number of TAD boundaries ($Y=1$ in the response vector) and the rest of genomic bins ($Y=0$) at each of the four resolutions of Hi-C data.
-Expectedly, the average number of TAD boundaries and the rest of genomic bins increased with the increased resolution of Hi-C data (Table 1) irrespectively of cell line (Supplementary Tables 3).
-However, imbalance ratios were found to be invariant to resolution, remaining consistently high with very little variability between chromosomes, regardless of cell line.
+-->
 

### 2019-06-25 Scripts/evaluating_imbalance_ratios.Rmd
editted script

@@
 tads.per.chr <- numeric()
+pi.per.chr <- numeric()
 
@@
 
+      pi.per.chr <- rbind(pi.per.chr, table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2]/sum(table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)))
+
     }
@@
                           bounds.per.chr,
-                          ir.per.chr)
-colnames(irtab) <- c("cl","res","chr","bins","tads","bounds","ir")
+                          ir.per.chr,
+                          pi.per.chr)
+colnames(irtab) <- c("cl","res","chr","bins","tads","bounds","ir","pi")
 irtab$res <- factor(irtab$res, levels=c("10kb","25kb","50kb","100kb"))
@@
             AveIR = mean(ir, na.rm = TRUE),
-            AveIRSD = sd(ir, na.rm = TRUE))
+            AveIRSD = sd(ir, na.rm = TRUE),
+            AvePI = mean(pi, na.rm = TRUE),
+            AvePISD = sd(pi, na.rm = TRUE))
 
@@
             MedIR = median(ir, na.rm = TRUE),
-            MedIRIQR = IQR(ir, na.rm = TRUE))
+            MedIRIQR = IQR(ir, na.rm = TRUE),
+            MedPI = median(pi, na.rm = TRUE),
+            MedPIIQR = IQR(pi, na.rm = TRUE))
 
@@
   scale_fill_discrete(name="Cell Line") +
+  scale_y_continuous(limits = c(0,27000),
+                     breaks=c(0,10000,20000),
+                     labels=c("0"="0", "10000"="10", "20000"="20")) +
   ggtitle("10 kb") +
   guides(fill=FALSE) +
-  theme(axis.text.x = element_text(size=10),
+  theme(axis.text.x = element_text(size=15),
      axis.text.y = element_text(size = 15),
@@
   scale_fill_discrete(name="Cell Line") +
+  scale_y_continuous(limits = c(0,27000),
+                     breaks=c(0,10000,20000),
+                     labels=c("0"="0", "10000"="10", "20000"="20")) +
   ggtitle("25 kb") +
   guides(fill=FALSE) +
-  theme(axis.text.x = element_text(size=10),
+  theme(axis.text.x = element_text(size=15),
      axis.text.y = element_text(size = 15),
@@
   scale_fill_discrete(name="Cell Line") +
+  scale_y_continuous(limits = c(0,27000),
+                     breaks=c(0,10000,20000),
+                     labels=c("0"="0", "10000"="10", "20000"="20")) +
   ggtitle("50 kb") +
   guides(fill=FALSE) +
-  theme(axis.text.x = element_text(size=10),
+  theme(axis.text.x = element_text(size=15),
      axis.text.y = element_text(size = 15),
@@
   scale_fill_discrete(name="Cell Line") +
+  scale_y_continuous(limits = c(0,27000),
+                     breaks=c(0,10000,20000),
+                     labels=c("0"="0", "10000"="10", "20000"="20")) +
   ggtitle("100 kb") +
   guides(fill=FALSE) +
-  theme(axis.text.x = element_text(size=10),
+  theme(axis.text.x = element_text(size=15),
      axis.text.y = element_text(size = 15),
@@
     #bottom = text_grob("Cell Line", color = "black", size = 20),
-    left = text_grob("Number of TAD Boundary Regions", color = "black", rot = 90, size=20)
+    left = text_grob("Number of TAD Boundary\nRegions (thousands)", color = "black", rot = 90, size=20)
 )
@@
 ```
+
+## PI Plots
+
+```{r}
+a <- ggplot(irtab[which(irtab$res=="10kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
+ stat_boxplot(geom ='errorbar', width = 0.2) + 
+ geom_boxplot() +
+ theme_minimal() +
+ theme_bw()+
+ xlab("") + ylab("") + ylim(0,.2) +
+ ggtitle("10 kb") +
+ guides(fill=FALSE) +
+ guides(color=FALSE) +
+ theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+b <- ggplot(irtab[which(irtab$res=="25kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
+ stat_boxplot(geom ='errorbar', width = 0.2) + 
+ geom_boxplot() +
+ theme_minimal() +
+ theme_bw()+
+ xlab("") + ylab("") + ylim(0,.2) +
+ ggtitle("25 kb") +
+ guides(fill=FALSE) +
+ guides(color=FALSE) +
+ theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+c <- ggplot(irtab[which(irtab$res=="50kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
+ stat_boxplot(geom ='errorbar', width = 0.2) + 
+ geom_boxplot() +
+ theme_minimal() +
+ theme_bw()+
+ xlab("") + ylab("") + ylim(0,.2) +
+ ggtitle("50 kb") +
+ guides(fill=FALSE) +
+ guides(color=FALSE) +
+ theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+d <- ggplot(irtab[which(irtab$res=="100kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
+ stat_boxplot(geom ='errorbar', width = 0.2) + 
+ geom_boxplot() +
+ theme_minimal() +
+ theme_bw()+
+ xlab("") + ylab("") + ylim(0,.2) +
+ ggtitle("100 kb") +
+ guides(fill=FALSE) +
+ guides(color=FALSE) +
+ theme(axis.text.x = element_text(size=15),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+figure <- ggarrange(a,b,c,d,
+                    ncol=4,
+                    nrow=1)
+figure
+annotate_figure(figure,
+    #bottom = text_grob("Cell Line", color = "black", size = 20),
+    left = text_grob("Proportion of Imbalance", color = "black", rot = 90, size=20)
+)
+
+```

### 2019-06-25 Scripts/comparing_tad_regions_across_cl_using_vd.Rmd
intitial commit

---
title: "Untitled"
author: "Spiro Stilianoudakis"
date: "June 11, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(Vennerable)
library(ChIPpeakAnno)
```

# Comparing TAD regions across cell lines

## Venn diagrams

```{r}
venn_cnt2venn <- function(venn_cnt){
  n <- which(colnames(venn_cnt)=="Counts") - 1
  SetNames=colnames(venn_cnt)[1:n]
  Weight=venn_cnt[,"Counts"]
  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
  Venn(SetNames=SetNames, Weight=Weight)
}

```

### 10kb

```{r}
#bounds_f_gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/bounds_f.rds")
#bounds_f_K562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/bounds_f.rds")

#res <- makeVennDiagram(Peaks=list(bounds_f_gm12878_10kb, bounds_f_K562_10kb),
#                       NameOfPeaks=c("GM12878", "K562"))

#venn_10kb <- venn_cnt2venn(res$vennCounts)
#plot(venn_10kb)

binslist_gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")
binslist_gm12878_10kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10_center.rds")
mcols(binslist_gm12878_10kb)$y <- mcols(binslist_gm12878_10kb_center)$y
binslist_gm12878_10kb <- binslist_gm12878_10kb[mcols(binslist_gm12878_10kb)$y==1]

binslist_K562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")
binslist_K562_10kb_center <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10_center.rds")
mcols(binslist_K562_10kb)$y <- mcols(binslist_K562_10kb_center)$y
binslist_K562_10kb <- binslist_K562_10kb[mcols(binslist_K562_10kb)$y==1]

res <- makeVennDiagram(Peaks=list(binslist_gm12878_10kb, binslist_K562_10kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_10kb <- venn_cnt2venn(res$vennCounts)
venn_10kb <- compute.Venn(venn_10kb)
gp <- VennThemes(venn_10kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
#plot(venn_10kb)

```

### 25kb

```{r}
#bounds_f_gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/bounds_f.rds")
#bounds_f_K562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/bounds_f.rds")

#res <- makeVennDiagram(Peaks=list(bounds_f_gm12878_25kb, bounds_f_K562_25kb),
#                       NameOfPeaks=c("GM12878", "K562"))

#venn_25kb <- venn_cnt2venn(res$vennCounts)
#plot(venn_25kb)

binslist_gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")
binslist_gm12878_25kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25_center.rds")
mcols(binslist_gm12878_25kb)$y <- mcols(binslist_gm12878_25kb_center)$y
binslist_gm12878_25kb <- binslist_gm12878_25kb[mcols(binslist_gm12878_25kb)$y==1]

binslist_K562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")
binslist_K562_25kb_center <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25_center.rds")
mcols(binslist_K562_25kb)$y <- mcols(binslist_K562_25kb_center)$y
binslist_K562_25kb <- binslist_K562_25kb[mcols(binslist_K562_25kb)$y==1]

res <- makeVennDiagram(Peaks=list(binslist_gm12878_25kb, binslist_K562_25kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_25kb <- venn_cnt2venn(res$vennCounts)
venn_25kb <- compute.Venn(venn_25kb)
gp <- VennThemes(venn_25kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
#plot(venn_25kb)

```

### 50kb

```{r}
#bounds_f_gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/bounds_f.rds")
#bounds_f_K562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/bounds_f.rds")

#res <- makeVennDiagram(Peaks=list(bounds_f_gm12878_50kb, bounds_f_K562_50kb),
#                       NameOfPeaks=c("GM12878", "K562"))

#venn_50kb <- venn_cnt2venn(res$vennCounts)
#plot(venn_50kb)

binslist_gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")
binslist_gm12878_50kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50_center.rds")
mcols(binslist_gm12878_50kb)$y <- mcols(binslist_gm12878_50kb_center)$y
binslist_gm12878_50kb <- binslist_gm12878_50kb[mcols(binslist_gm12878_50kb)$y==1]

binslist_K562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")
binslist_K562_50kb_center <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50_center.rds")
mcols(binslist_K562_50kb)$y <- mcols(binslist_K562_50kb_center)$y
binslist_K562_50kb <- binslist_K562_50kb[mcols(binslist_K562_50kb)$y==1]

res <- makeVennDiagram(Peaks=list(binslist_gm12878_50kb, binslist_K562_50kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_50kb <- venn_cnt2venn(res$vennCounts)
venn_50kb <- compute.Venn(venn_50kb)
gp <- VennThemes(venn_50kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
#plot(venn_50kb)

```

### 100kb

```{r}
#bounds_f_gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/bounds_f.rds")
#bounds_f_K562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/bounds_f.rds")

#res <- makeVennDiagram(Peaks=list(bounds_f_gm12878_100kb, bounds_f_K562_100kb),
#                       NameOfPeaks=c("GM12878", "K562"))

#venn_100kb <- venn_cnt2venn(res$vennCounts)
#plot(venn_100kb)

binslist_gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")
binslist_gm12878_100kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100_center.rds")
mcols(binslist_gm12878_100kb)$y <- mcols(binslist_gm12878_100kb_center)$y
binslist_gm12878_100kb <- binslist_gm12878_100kb[mcols(binslist_gm12878_100kb)$y==1]

binslist_K562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")
binslist_K562_100kb_center <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100_center.rds")
mcols(binslist_K562_100kb)$y <- mcols(binslist_K562_100kb_center)$y
binslist_K562_100kb <- binslist_K562_100kb[mcols(binslist_K562_100kb)$y==1]

res <- makeVennDiagram(Peaks=list(binslist_gm12878_100kb, binslist_K562_100kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_100kb <- venn_cnt2venn(res$vennCounts)
venn_100kb <- compute.Venn(venn_100kb)
gp <- VennThemes(venn_100kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
#plot(venn_100kb)

```

### Plots

```{r}
#par(mfrow=c(1,4))

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_10kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("10 kb", gp=gpar(fontsize=20)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_25kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("25 kb", gp=gpar(fontsize=20)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_50kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("50 kb", gp=gpar(fontsize=20)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_100kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("100 kb", gp=gpar(fontsize=20)))
grid.newpage()

#par(mfrow=c(1,1))
```

### 2019-06-26 Manuscript/manuscript.Rmd
fixed methods; exchanged IR for PI

@@
 However, many key characteristics of 3D genomic data remain unexplored, potentially limiting performance of predictive modeling.
-Specifically, the minority of TAD boundaries as compared with the rest of the genome creates proportionally small TAD boundary regions versus non boundary regions.
-Here, the proportion of imbalance is defined as the ratio of the set of TAD boundary regions to the sum of both TAD and non-TAD boundary regions.<!--Specifically, the minority of TAD boundaries as compared with the rest of the genome creates heavily imbalanced classes, characterized by ratios of positive/negative classes used to train the models.
-Here, the imbalance ratio is defined as the ratio of majority classes (regions not including TAD boundaries) to minority classes (regions including TAD boundaries) [@Orriols-Puig2008].--> Such heavily imbalanced datasets are known to adversely impact the performance of classifiers as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
+Specifically, the minority of TAD boundaries as compared with the rest of the genome creates proportionally small TAD boundary regions versus non-TAD boundary regions.
+These TAD boundary regions make up the minority class, while the non-TAD boundary regions make up the remaining majority class.
+The large disparity is sizes between minority and majority classes creates imbalanced data, as can be characterized by the *proportion of imbalance* (PI).
+Here, PI is defined as the ratio of the set minority class observations to the sum of both sets of minority and majority class observations.
+A dataset is considered imbalanced if PI<0.5.
+<!--Specifically, the minority of TAD boundaries as compared with the rest of the genome creates heavily imbalanced classes, characterized by ratios of positive/negative classes used to train the models.
+Here, the imbalance ratio is defined as the ratio of majority classes (regions not including TAD boundaries) to minority classes (regions including TAD boundaries) [@Orriols-Puig2008].--> Classifiers implemented on heavily imbalanced datasets are known to exhibit poor performances as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
 Furthermore, the use of different levels of association between TAD boundaries and genomic features (number, or proportion of overlaps, or distance) as predictors remain underexplored.
@@
 
-Class imbalance was characterized by each dataset's imalance ratio (IR), defined as the ratio of majority to minority sets given by the class of genomic bins:
+Class imbalance was characterized by each dataset's *proportion of imbalance* (PI), defined as the ratio of minority class observations to the sum of minority and majority class observations:
 
-$$IR = \dfrac{C_{majority}}{C_{minority}}$$
+$$PI = \dfrac{C_{min}}{C_{min} + C_{maj}}$$
 
-where $C_{majority}$ denotes the set of genomic bins that did not overlap with a flanked TAD boundary and $C_{majority}$ denotes the complementary set of genomic bins that did overlap with a flanked TAD boundary.
+where $C_{min}$ denotes the complementary set of genomic bins that did overlap with a flanked TAD boundary and $C_{maj}$ denotes the set of genomic bins that did not overlap with a flanked TAD boundary.
 In order to assess the influence of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling).

### 2019-06-26 Manuscript/manuscript.Rmd
edits

@@
 
+<!--## TOTAL NUMBER OF TAD BOUNDARY REGIONS DECREASE AS Hi-C DATA RESOLUTION DECREASES-->
+Expectedly, the total number of TAD boundary regions increased with the increased resolution of Hi-C data irrespectively of cell line (Figure 2A).
+At higher resolutions, GM12878 was found to contain more TADs, and thus more TAD boundary regions compared to K562.
+This can largely be attributed to the increased sequencing depth of the GM12878 library.
+However, this difference was found to dissipate as resolution decreased, resulting in much more similar numbers of TAD boundary regions between the two cell lines at the 50 kb and 100 kb resolutions respectively.
+
 ![**An illustration of the proposed approach for resolution-specific data construction used for TAD boundary prediction.** Resolution-specific TADs were called and unique boundaries were identified, denoted by the blue dots.
@@
 
-## TOTAL NUMBER OF TAD BOUNDARY REGIONS DECREASE AS Hi-C DATA RESOLUTION DECREASES
-
-Expectedly, the total number of TAD boundary regions increased with the increased resolution of Hi-C data irrespectively of cell line (Figure 2 A).
-At higher resolutions, GM12878 was found to contain more TADs, and thus more TAD boundary regions compared to K562.
-This can largely be attributed to the increased sequencing depth of the GM12878 library.
-However, this difference was found to dissipate as resolution decreased, resulting in much more similar numbers of TAD boundary regions between the two cell lines at the 50 kb and 100 kb resolutions respectively.
-
 ## TAD BOUNDARY REGIONS EXHIBIT CELL-LINE SPECIFICITY
 
-We then sought to compare the cell-line specificity of TAD boundary regions.
-Between the two cell lines, a significant number of TAD boundary regions were specific to one of the two cell lines (Figure 2 B).
+We first sought to compare the cell-line specificity of TAD boundary regions.
+Between the two cell lines, a significant number of TAD boundary regions were specific to one of the two cell lines (Figure 2B).
 It was found that 45%, 38%, 37%, and 36% of TAD boundary regions were specific to the GM12878 cell line, across each resolution respectively.
@@
 We compared the estimated the number of TAD boundary regions ($Y=1$ in the response vector) and the rest of genomic bins ($Y=0$) for each cell line, at each of the four resolutions of Hi-C data.
-The proportional imbalance was found to be invariant to resolution, remaining consistently low for both cell lines, with very little variability between chromosomes (Figure 3 C).
+The proportional imbalance was found to be invariant to resolution, remaining consistently low for both cell lines, with very little variability between chromosomes (Figure 3C).
 
@@
 (C) Boxplots indicating that the proportion of class imbalance remained severe irrespective of resolution.](Figures/bounds_and_pis.png)
-
-<!--
-## IMBALANCE RATIOS REMAINED SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION
-
-To investigate class imbalance, defined as the ratio of TAD vs.
-non-TAD regions, we estimated the number of TAD boundaries ($Y=1$ in the response vector) and the rest of genomic bins ($Y=0$) at each of the four resolutions of Hi-C data.
-Expectedly, the average number of TAD boundaries and the rest of genomic bins increased with the increased resolution of Hi-C data (Table 1) irrespectively of cell line (Supplementary Tables 3).
-However, imbalance ratios were found to be invariant to resolution, remaining consistently high with very little variability between chromosomes, regardless of cell line.
--->
 
@@
 -->
-<!--
-## HIGH JACCARD INDICES IMPLY COLOCALIZATION OF MANY GROUP-SPECIFC ANNOTATIONS 
--->
 
-## DEVELOPING THREE TYPES OF ASSOCIATIONS BETWEEN TAD BOUNDARIES AND EPIGENOMIC FEATURES
-
-<!-- of TAD boundaries were assessed using functional genomic annotations, derived by ChIP-seq peak algorithms.
-Specific groups of annotations were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] and included chromatin state segementations, histone modifications, and transcription factor binding sites (TFBS).-->
-
-<!--
-Using the Jaccard index, we found that specific sets of these cell line-specific annotations were highly colocalized together on the linear genome (Table 3).
-For GM12878, the range of Jaccard indices for the 10 histone modifications was found to be (0.022-0.539).
-Specifically, H3k27ac, H3k4me1, H3k4me2, and H3k4me3 were found to be highly correlated, high levels of which have been detected surrounding transcription start sites [@barski2007high].
-Likewise, for the 79 TFBS, the range of Jaccard indices was (<0.001-0.425).
-Here, known mediators of loop extrusion components were found to have high pairwise correlations including CTCF, RAD21, and SMC3 [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
-Similar profiles of Jaccard indices were exhibited across the sets of annotations for the K562 cell line (Supplementary Table 4).
-[???
-So what?
-Why did you talk about it?; !!!added implication].
-The high Jaccard indices among select sets of genomic annotations indicated the colocalization of annotations known to be enriched at TAD boundaries.
-This gave precedent for the use of an elastic-net regularization algorithm in order to suitably reduce the feature space of all annotations while retaining the possibly correlated annotations that could be predictive of TAD boundary formation.
--->
+## DEVELOPING THREE TYPES OF PREDICTORS DESCRIBING THE ASSOCIATIONS BETWEEN TAD BOUNDARY REGIONS AND EPIGENOMIC FEATURES
 
 To establish the feature space used for classification, we constructed three different predictor types.
-Counts of overlaps (**overlap count**, OC) is the most commonly used type of association between genomic elements (Figure 2A).
-Percents of overlaps (**overlap percent**, OP) represents a more precise measure of association as it considers the proportion of a bin overlapped by a genomic annotation (Figure 2B).
-**Distance** between the centers of bins and genomic annotations quantifying the spatial relationship between genomic elements is the least common type of association (Figure 2C).
+Counts of overlaps (**overlap count**, OC) is the most commonly used type of association between genomic elements (Figure 3A).
+Percents of overlaps (**overlap percent**, OP) represents a more precise measure of association as it considers the proportion of a bin overlapped by a genomic annotation (Figure 3B).
+**Distance** between the centers of bins and genomic annotations quantifying the spatial relationship between genomic elements is currently unexplored (Figure 3C).
 Log2-transformation of distance was used as a normalization technique in order to account for the skewness present in the distributions of distances (Supplementary Figures 1-2).

### 2019-06-26 Manuscript/manuscript.Rmd
edits

@@
 The proportional imbalance was found to be invariant to resolution, remaining consistently low for both cell lines, with very little variability between chromosomes (Figure 3C).
+Such low proportions of imbalance gave precedence for the implementation of re-sampling prior to modeling.
 
@@
 
-We created an ensemble framework to systematically compare different data driven characteristics to identify the optimal set of parameters when predicting TAD boundaries using functional genomic annotations (Figure 3).
-Each system in the framework was assumed to be composed of a random forest model constructed from a particular cell line, $L = \{GM12878, K562\}$.
-Within each cell line we evaluated 4 data resolutions, $R = \{10 kb, 25 kb, 50 kb, 100 kb\}$.
-We then considered 3 separate predictor types as the feature space including $P = \{OC, OP, Distance\}$.
-To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including $B = \{None, RUS, ROS, SMOTE\}$.
+In order to identify the optimal set of parameters necessary for TAD boundary prediction, we created an ensemble framework to systematically compare performances of random forest classifiers built on different combinations of predictor types and re-sampling techniques (Figure 4).
+Each system in the framework was assumed to be composed of a random forest model constructed from a particular cell line ($L = \{GM12878, K562\}$).
+Within each cell line we evaluated 4 data resolutions ($R = \{10 kb, 25 kb, 50 kb, 100 kb\}$).
+We then considered 3 separate predictor types as the feature space ($P = \{OC, OP, Distance\}$.
+To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including $B = \{None, RUS, ROS, SMOTE\}$).
 Each combination of the above parameters was implemented on chromosome specific sections of the linear genome.
@@
 Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling 2016 ($2 \times 4 \times 3 \times 4 \times 21$) separate models.
-We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.
+<!--We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.-->
 
-![**Figure 3.
-Ensemble Framework.** A diagram of the cell line specific ensemble framework detailing the combination of inputs used in the model building pipeline.
-The minoirty and majority classes were represented by the genomic bins that overlapped with flanked TAD boundaries or did not, respectively.
-Functional genomic annotations obtained from the UCSC Genome Browser Database composed the feature space ($\textbf{X} = \{X_1, X_2, ..., X_p\}$).
-A feature engineering step was included to isolate the predictor-type specific spatial relationship between annotations and genomic bins in increasing granularity, denoted by the red gradient.
-The data was split into a 7:3 training to testing set ratio.
-Data re-sampling was then applied to the training set.
-Lastly, a random forest classification algorithm was implemeted and validated on the testing data.](Figures/figure3_ensemble_framework.png)
+![**Ensemble Framework.** A diagram of the ensemble framework detailing the combination of inputs used in the model building pipeline.
+TAD boundary data was extracted from a specific Hi-C resolution and a variety of functional genomic annotations were used to establish the feature space.
+Each subsequent cell line specific random forest classification model was built on an isolated predictor type in conjunction with a particular data re-sampling technique to account for class imbalance.
+The model was then validated on a testing set and performances were evaluated using MCC.](Figures/figure3_ensemble_framework_V2.png)
 

### 2019-06-29 Manuscript/manuscript.Rmd
edits

@@
 
-In order to set a baseline in performance, we first evaluated the least granular random forest classifier, that is one implemented using OC predictor types, without data re-sampling.
-We found that models built on data with fully imbalanced classes exhibited poor MCCs across all resolutions (Figure 4A).
-We gradually increased the complexity in data level characteristics by assessing models built on OP predictor types, while still not performing any data resampling.
-Here, the results were similar to that of OC types (Figure 4B).
-However, when including distance-type predictors, models were found to exhibit a marked improvement in MCC compared to the other two types (Figure 4C).
+We first evaluated the least granular random forest classifier, that was one implemented using OC predictor types, without data re-sampling.
+We found that these models exhibited poor MCCs across all resolutions (Figure 4A (red)).
+We then assessing models built on OP predictor types, while still not performing any data resampling.
+Performances were similar to that of OC types, with no clear improvement (Figure 4B (red)).
+This indicated that the added complexity of using overlap percents from the functional genomic annotations did not affect predictive performance.
+
+However, when implemented using distance-type predictors and no re-sampling, models were found to exhibit a marked improvement in MCC compared to the other two types (Figure 4C (red)).
+
+<!--Add K562 results in main paper-->
+
+<!--
 Results were found to be consistently poor across resolutions and predictor types, when implemented on the K562 cell line (Supplementary Figure 3).
@@
 accuracy and AUC) were less sensitive to models built on imbalanced data, regardless of cell line, resolution, or predictor-type (Supplementary Tables 6-7).
+-->
 
@@
 
-![**Figure 4.
-SMOTE re-sampled models built on distance-type predictors yielded optimal MCCs across resolutions for GM12878.** Performances of random forest classification models built on each of the 3 predictor types: (A) OC, (B) OP, and (C) Distance.
+![**SMOTE re-sampled models built on distance-type predictors yielded optimal MCCs across resolutions for GM12878.** Performances of random forest classification models built on each of the 3 predictor types: (A) OC, (B) OP, and (C) Distance.
 Within each predictor type, and across resolution, training data was re-sampled using different techniques including: None (red), ROS (green), RUS (blue), and SMOTE (purple).

### 2019-06-29 Manuscript/manuscript.Rmd
edits

@@
 We first sought to compare the cell-line specificity of TAD boundary regions.
-Between the two cell lines, a significant number of TAD boundary regions were specific to one of the two cell lines (Figure 2B).
+Between the two cell lines, a significant number of TAD boundary regions were found to be specific to one of the two cell lines (Figure 2B).
 It was found that 45%, 38%, 37%, and 36% of TAD boundary regions were specific to the GM12878 cell line, across each resolution respectively.
 Similarly, for K562, it was found that 27%, 27%, 29%, and 33% of TAD boundary regions were cell line specific for each resolution specifically.
+This indicates a necessity for computationally specific models in predicting TAD boundary formations.
 
@@
 
-We then investigated the proportion of class imbalance, defined as the ratio of TAD boundary regions versus the sum of both TAD and non-TAD boundary regions.
-We compared the estimated the number of TAD boundary regions ($Y=1$ in the response vector) and the rest of genomic bins ($Y=0$) for each cell line, at each of the four resolutions of Hi-C data.
+We then investigated the proportional class imbalance (PI) featured at each resolution and among each cell line.
+The PI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions.
 The proportional imbalance was found to be invariant to resolution, remaining consistently low for both cell lines, with very little variability between chromosomes (Figure 3C).
-Such low proportions of imbalance gave precedence for the implementation of re-sampling prior to modeling.
+Such low proportions of imbalance gave precedence for the implementation of re-sampling prior to classification.
 
@@
 
+[include number of cell type specific features and number of features in common]
+
 To establish the feature space used for classification, we constructed three different predictor types.
@@
 Log2-transformation of distance was used as a normalization technique in order to account for the skewness present in the distributions of distances (Supplementary Figures 1-2).
-These types of genomic associations provide a granular way to investigate classification performance in class imbalance settings.
+These types of genomic associations provide a granular way to investigate classifier performance in class imbalance settings.
 
@@
 
-In order to identify the optimal set of parameters necessary for TAD boundary prediction, we created an ensemble framework to systematically compare performances of random forest classifiers built on different combinations of predictor types and re-sampling techniques (Figure 4).
-Each system in the framework was assumed to be composed of a random forest model constructed from a particular cell line ($L = \{GM12878, K562\}$).
+In order to identify the optimal combination of data resolution, predictor type, and re-sampling technique necessary for TAD boundary prediction, we created an ensemble framework to systematically compare performances of different model inputs (Figure 4).
+Each system in the framework was assumed to be composed of a random forest classifier constructed from a particular cell line ($L = \{GM12878, K562\}$).
 Within each cell line we evaluated 4 data resolutions ($R = \{10 kb, 25 kb, 50 kb, 100 kb\}$).
-We then considered 3 separate predictor types as the feature space ($P = \{OC, OP, Distance\}$.
-To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including $B = \{None, RUS, ROS, SMOTE\}$).
-Each combination of the above parameters was implemented on chromosome specific sections of the linear genome.
-Performances were then aggregated across each of the 21 chromosomes (omitting chromosome 9).
+We then considered 3 separate predictor types as the feature space ($P = \{OC, OP, Distance\}$).
+To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling ($B = \{None, RUS, ROS, SMOTE\}$).
+Each combination of the above cell line specific parameters was implemented on chromosome specific sections of the linear genome (omitting chromosome 9).
 Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling 2016 ($2 \times 4 \times 3 \times 4 \times 21$) separate models.
+For each combination of inputs, we performed 10-fold cross-validation to tune for the number of features to consider at each node of the random forest classifier.
+Each optimally tuned model was then validated on the same separate testing set for unbiased comparisons.
+Performances were evaluated using MCCs and aggregated across each chromosome by averaging.
 <!--We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.-->

### 2019-06-29 Manuscript/manuscript.Rmd
edits

@@
 
-[include number of cell type specific features and number of features in common]
-
-To establish the feature space used for classification, we constructed three different predictor types.
+A total of 107 and 152 cell type specific functional genomic annotations derived from ChIP-Seq experiments (See Methods) for the GM12878 and K562 cell line respectively.
+To establish the feature space used for classification, we constructed three different predictor types for each functional genomic annotation.
 Counts of overlaps (**overlap count**, OC) is the most commonly used type of association between genomic elements (Figure 3A).
@@
 ![**Ensemble Framework.** A diagram of the ensemble framework detailing the combination of inputs used in the model building pipeline.
-TAD boundary data was extracted from a specific Hi-C resolution and a variety of functional genomic annotations were used to establish the feature space.
-Each subsequent cell line specific random forest classification model was built on an isolated predictor type in conjunction with a particular data re-sampling technique to account for class imbalance.
-The model was then validated on a testing set and performances were evaluated using MCC.](Figures/figure3_ensemble_framework_V2.png)
+Cell line specific TAD boundary data was extracted from a Hi-C produced contact matrix of a given resolution.
+A variety of functional genomic annotations were used to establish the feature space.
+Each subsequent random forest classification model was trained on an isolated predictor type in conjunction with a particular data re-sampling technique to account for class imbalance.
+Each model was then validated on a testing set and performances were evaluated using MCC.](Figures/figure3_ensemble_framework_V3.png)
 
-## CLASS IMBALANCE SEVERELY IMPACTS MODEL PERFORMANCE
+## CLASS IMBALANCE SEVERELY IMPACTS PERFORMANCE FOR CELL LINE SPECIFIC MODELS
 
-We first evaluated the least granular random forest classifier, that was one implemented using OC predictor types, without data re-sampling.
+We first evaluated the least granular cell line specific random forest classifiers, that was one implemented using OC predictor types, without data re-sampling.
 We found that these models exhibited poor MCCs across all resolutions (Figure 4A (red)).

### 2019-06-30 Manuscript/manuscript.Rmd
edits

@@
 
-We first evaluated the least granular cell line specific random forest classifiers, that was one implemented using OC predictor types, without data re-sampling.
+We first evaluated the least granular cell line specific random forest classifiers, those were ones implemented using OC predictor types, without data re-sampling.
 We found that these models exhibited poor MCCs across all resolutions (Figure 4A (red)).
@@
 
+[Put this section last]
+
 ## INFLUENTIAL TFBS TENDED TO BE CLOSER TO BINS THAT OVERLAPPED WITH FLANKED TAD BOUNDARIES THAN THOSE THAT DID NOT

### 2019-06-30 Manuscript/manuscript.Rmd
edits

@@
 Each subsequent random forest classification model was trained on an isolated predictor type in conjunction with a particular data re-sampling technique to account for class imbalance.
+Ten-fold cross validation was performed to tune for the number of predictor-type specific genomic features to consider at each node.
 Each model was then validated on a testing set and performances were evaluated using MCC.](Figures/figure3_ensemble_framework_V3.png)
 
-## CLASS IMBALANCE SEVERELY IMPACTS PERFORMANCE FOR CELL LINE SPECIFIC MODELS
+## SMOTE RE-SAMPLING COUPLED WITH A DISTANCE-TYPE FEATURE SPACE PROVIDED OPTIMAL CELL LINE SPECIFIC MODEL PERFORMANCE
+
+<!--## CLASS IMBALANCE SEVERELY IMPACTS PERFORMANCE FOR CELL LINE SPECIFIC MODELS-->
 
 We first evaluated the least granular cell line specific random forest classifiers, those were ones implemented using OC predictor types, without data re-sampling.
-We found that these models exhibited poor MCCs across all resolutions (Figure 4A (red)).
-We then assessing models built on OP predictor types, while still not performing any data resampling.
-Performances were similar to that of OC types, with no clear improvement (Figure 4B (red)).
-This indicated that the added complexity of using overlap percents from the functional genomic annotations did not affect predictive performance.
+We found that these models exhibited poor MCCs across all resolutions (Figure 5 A-B (red)).
+We then assessed models built on OP predictor types, while still not performing any data resampling.
+Performances were similar to that of OC types, with no clear improvement (Figure 5 C-D (red)).
+This indicated that the added complexity of using overlap percents from the functional genomic annotations did not affect predictive performance, regardless of cell line and resolution.
+However, when cell line specific classifiers were implemented using distance-type predictors and no re-sampling, we found that there was a significant improvement in MCC compared to the other two predictor types (Figure 5 E-F (red)).
 
-However, when implemented using distance-type predictors and no re-sampling, models were found to exhibit a marked improvement in MCC compared to the other two types (Figure 4C (red)).
+We then further explored the impact of data re-sampling on model performance, across cell line and resolution.
+For cell line specific random forest classifiers built on balanced data, we found that SMOTE re-sampling provided the optimal MCC, consistently outperforming models built on ROS or RUS, across both predictor type and resolution (Figure 5).
+Specifically, the most improvement was seen when combining SMOTE re-sampling with distance-type predictors for both the GM12878 and K562 cell lines.
 
-<!--Add K562 results in main paper-->
+## MODEL PERFORMANCE DECREASED AS Hi-C DATA RESOLUTION DECREASED
 
-<!--
-Results were found to be consistently poor across resolutions and predictor types, when implemented on the K562 cell line (Supplementary Figure 3).
-Furthermore, we found that conventional metrics of performance (i.e.
-accuracy and AUC) were less sensitive to models built on imbalanced data, regardless of cell line, resolution, or predictor-type (Supplementary Tables 6-7).
--->
-
-## SMOTE RE-SAMPLING COUPLED WITH THE INCLUSION OF A DISTANCE-TYPE FEATURE SPACE SUBSTANTIALLY IMPROVED MODEL PERFORMANCE
-
-When assessing performances for random forest classifiers built on balanced data, we found that SMOTE re-sampling provided the optimal MCC consistently outperforming models built on ROS or RUS, across both predictor type and resolution (Figure 4).
-Specifically, the most improvement in model performance was seen when combining SMOTE re-sampling with distance-type predictors.
-This was also the optimal combination for the K562 cell line (Supplementary Figure 3).
 Interestingly, we found that there was a degredation in model performance as data resolution decreased.
-Chromosome specific models built on 10 kb data resolutions presented with the highest MCC values.
+Chromosome specific models built on 10 kb data resolutions presented the highest MCC values (Figure 5).
 Additionally, performances tended to be much more variable between chromosomes at lower resolutions.
 Moreover, this decreasing trend in performance was much more evident under the optimal combination of data level characteristics.
-These results imply that an optimally performing random forest classifier, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
+These results imply that an optimally performing cell line specific random forest classifier <!--, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries,--> is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
 
-![**SMOTE re-sampled models built on distance-type predictors yielded optimal MCCs across resolutions for GM12878.** Performances of random forest classification models built on each of the 3 predictor types: (A) OC, (B) OP, and (C) Distance.
-Within each predictor type, and across resolution, training data was re-sampled using different techniques including: None (red), ROS (green), RUS (blue), and SMOTE (purple).
-Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/figure4_gm12878_model_performances.png)
+![**SMOTE re-sampling coupled with distance-type predictors yielded optimal MCCs across resolution for cell line specific models.** Performances of random forest classification models built on each of the 3 predictor types includeing (A-B) OC, (C-D) OP, and (E-F) Distance, and across both the GM12878 and K562 cell lines.
+Within each cell line, predictor type, and resolution, chromosome-specific training data was re-sampled using different techniques including no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and *Synthetic Minority Over Sampling TEchnique* (SMOTE; purple).
+Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/model_performances_v2.png)
 

### 2019-06-30 Scripts/evaluating_model_performances_rf.Rmd
added other version of plot

--- 2019-06-05 Scripts/evaluating_model_performances.Rmd
@@
 
-## Plots
+# Line Plots V1
 
@@
 ```
+
+# Line Plots V2
+
+```{r}
+x <- ggplot(all_rfperfs_mcc, aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     facet_grid(CL ~ Predictor)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("Resolution") + ylab("MCC") + ylim(-.1,.5) +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     strip.text.x = element_text(size = 15),
+     strip.text.y = element_text(size = 15),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20),
+     legend.position="bottom")
+
+#figure <- ggarrange(x,
+#                ncol = 1, nrow = 1, 
+#                common.legend = TRUE, 
+#                legend = "bottom")
+#figure
+#annotate_figure(figure,
+#    bottom = text_grob("Resolution", color = "black", size = 20),
+#    left = text_grob("MCC", color = "black", rot = 90, size=20)
+#)
+
+```

### 2019-06-30 Manuscript/manuscript.Rmd
edits

@@
 
-After determining the optimal set of data level characteristics, we then aimed to compare the performances of annotation-specifc models.
-In doing so, we inspected the proportion of predictive importance that was explained by each of the 3 groups of annotations (chromatin states, histone modifications, and transcription factor binding sites), across resolution.
-We found that for random forest models implemented on distance-type predictors, using SMOTE re-sampling, the majority of the proportional predictive importance was obtained by the cell-line specific transcription factor binding sites, and was consistent across resolutions (Figure 5; Supplementary Figure 4).
-
-![**Figure 5.
-The proportional importance of optimally built predictive models was outweighed by transcription factor binding sites across resolutions for GM12878.** Stacked barplots illustrate the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework (SMOTE re-sampling; with distance-type predictors), for each resolution on GM12878.
-Proportions are grouped by the class of cell line specific annotations in the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).](Figures/figure5_proportion_of_importances_gm12878.png)
+After determining the optimal set of data level characteristics, we then aimed to compare the performances of annotation-specifc models, within each cell line and across resolution.
+In doing so, we inspected the proportion of predictive importance that was explained by each of the 3 groups of annotations (chromatin states, histone modifications, and transcription factor binding sites).
+We found that for cell line specific random forest models implemented on distance-type predictors, using SMOTE re-sampling, the majority of the proportional predictive importance was obtained by the functional genomic annotations classified as transcription factor binding sites (TFBS) (Figure 6).
+This was consistent across resolutions, suggesting that TFBS were the primary drivers of TAD boundary formation in both the GM12878 and K562 cell lines.
 
 We further assessed the predictive capabilities of the specific sets of annotations by comparing the performances of annotation-specific random forest models implemented on the optimal set of characteristics.
-We found that models built simply on cell line specific TFBS out performed other cell line and annotation-specific models at all resolutions (Figure 6; Supplementary Figure 5).
-Additionally, when compared to the optimal model identified from the ensemble framework, one that included all 3 sets of annotations, the TFBS-specific models performed similarly at the 10 kb and 25 kb resolutions.
-Interestingly though, at the 50 kb and 100 kb resolutions, the TFBS-specific models out performed models built on the combined sets of annotations, indicating that, at lower resolution, the inclusion of other types of annotations contributed to additional noise rather than signal.
+We found that cell line specific models built simply on TFBS out performed other cell line and annotation-specific models at all resolutions (Figure 7).
+Additionally, when compared to models built on all 3 sets of functional genomic annotations, the TFBS-specific models performed similarly at the 10 kb and 25 kb resolutions.
+Interestingly though, at the 50 kb and 100 kb resolutions, the TFBS-specific models out performed models built on the combined sets of annotations for both cell lines.
+This indicated that, at lower resolutions, the inclusion of other types of annotations contributed to additional noise rather than signal.
 
-![**Figure 6.
-Optimally built TFBS-specific models outperformed other annotation-specific models across resolution for GM12878** Performances were compared for random forest models built using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
+![**The proportional importance of optimally built cell line specific models was outweighed by transcription factor binding sites across resolutions.** Stacked barplots illustrate the proportion of total predictive importance in cell line specific random forest classifiers for (A) GM12878 and (B) K562 respectively.
+Model inputs included the optimal data level characteristics determined by the ensemble framework (SMOTE re-sampling; with distance-type predictors).
+Predictive importance was averaged for models built on chromosome specific regions of the linear genome.
+Proportional importance was then calculated according to the annotation group of the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).](Figures/proportion_of_importances_v2.png)
+
+![**Optimally built TFBS-specific models outperformed other annotation-specific models across resolution for GM12878** Performances were compared for random forest models built using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
 Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types.
@@
 
-![**Figure 7.
-Top 20 most predictive transcription factor binding sites sorted by 10 kb for GM12878.** A heatmap illustrating the importance of the key cell line specific transcription factors for optimally built random forest models across resolution.
+![**Top 20 most predictive transcription factor binding sites sorted by 10 kb for GM12878.** A heatmap illustrating the importance of the key cell line specific transcription factors for optimally built random forest models across resolution.
 Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100.

### 2019-07-01 Manuscript/manuscript.Rmd
edits

@@
 
+<!--
 ![**The proportional importance of optimally built cell line specific models was outweighed by transcription factor binding sites across resolutions.** Stacked barplots illustrate the proportion of total predictive importance in cell line specific random forest classifiers for (A) GM12878 and (B) K562 respectively.
@@
 Proportional importance was then calculated according to the annotation group of the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).](Figures/proportion_of_importances_v2.png)
+-->
 
+<!--
 ![**Optimally built TFBS-specific models outperformed other annotation-specific models across resolution for GM12878** Performances were compared for random forest models built using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
 Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types.
-The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.](Figures/figure6_comparing_sets_of_annotations_gm12878.png)
+The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.](Figures/comparing_sets_of_annotations_v2.png)
+-->
 
@@
 
+<!--
 ![**Top 20 most predictive transcription factor binding sites sorted by 10 kb for GM12878.** A heatmap illustrating the importance of the key cell line specific transcription factors for optimally built random forest models across resolution.
@@
 Transcription factors with higher values of predictive importance are denoted in dark red.](Figures/figure7_variable_importance_heatmaps_tfbs_gm12878.png)
+-->
+
+![**Assessing optimally built cell line specific random forest classifiers for predicting TAD boundary formation.** (A) Comparing the proportion of total predictive importance carried by each group of functional genomic annotation across resolution.
+Predictive importance was averaged for models built on chromosome specific regions of the linear genome.
+Proportional importance was then calculated according to the annotation group of the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).
+(B) Comparing models using specific groups of functional genomic annotation as the feature space in addition to a model with a feature space containing all 3 types combined (combined; purple).
+Error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosomal section of the linear genome.
+(C) Heatmaps illustrating the importance of the top 20 cell line specific transcription factors across resolution.
+Importances were sorted according to the row-wise average across resolution and rescaled to values between 0 and 100.
+Transcription factors with higher values of predictive importance are denoted in dark red and dark blue for the GM12878 and K562 cell line respectively.](Figures/prop_imps_a_comparing_annots_b_var_imps_c.png)
 

### 2019-07-01 Scripts/comparing_tfbs_specific_models_with_all_annotations.Rmd
editted script for figure

@@
 #GM12878
-ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="GM12878"),], aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
+a <- ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="GM12878"),], aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
   geom_bar(stat="identity", position = position_dodge()) +
@@
   theme_bw()+
-  #xlab("") + ylab("") + ylim(-.05,.5) +
-  scale_fill_discrete(name="Annotation\nGroup")+
-  guides(shape=FALSE, linetype=FALSE)+
+  xlab("") + ylab("MCC") + 
+  scale_fill_discrete(name="Annotation Group")+
+  ggtitle("GM12878") +
   theme(axis.text.x = element_text(size=15,
@@
 #K562
-ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="K562"),], aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
+b <- ggplot(all_rfperfs_mcc[which(all_rfperfs_mcc$CL=="K562"),], aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
   geom_bar(stat="identity", position = position_dodge()) +
@@
   theme_bw()+
-  #xlab("") + ylab("") + ylim(-.05,.5) +
+  xlab("") + ylab("") +
   scale_fill_discrete(name="Annotation\nGroup")+
-  guides(shape=FALSE, linetype=FALSE)+
+  ggtitle("K562") +
   theme(axis.text.x = element_text(size=15,
@@
   plot.title = element_text(size=20))
+
+figure <- ggarrange(a,b,
+                ncol = 2, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "bottom")
+figure
 ```
+
+# Plots v2
+
+```{r}
+ggplot(all_rfperfs_mcc, aes(x=Resolution, y=MCC, group=Annotation, fill=Annotation)) +
+  geom_bar(stat="identity", position = position_dodge()) +
+  geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
+                 position=position_dodge(.9), alpha=0.75) +
+  facet_grid(~ CL) +
+  theme_minimal() +
+  theme_bw()+
+  #xlab("") + ylab("") + ylim(-.05,.5) +
+  scale_fill_discrete(name="Annotation Group")+
+  guides(shape=FALSE, linetype=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                  angle = 45, 
+                                  #margin = ggplot2::margin(t = 35),
+                                  hjust = 1
+  ),
+  axis.text.y = element_text(size = 15),
+  axis.title.x = element_text(size = 20),
+  axis.title.y = element_text(size = 20),
+  strip.text.x = element_text(size = 15),
+  panel.spacing = unit(2, "lines"),
+  legend.text=element_text(size=15),
+  legend.title=element_text(size=20),
+  plot.title = element_text(size=20),
+  legend.position = "bottom")
+```

### 2019-07-01 Scripts/evaluating_variable_importances.Rmd
editted script for figure

@@
 #GM12878
-all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
+all_varimps_gm12878_tfbs <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                         varimp_gm12878_10kb$aveimp10kb,
@@
                                         varimp_gm12878_100kb$aveimp100kb)
-names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
-all_varimps_gm12878 <- all_varimps_gm12878[order(rowMeans(all_varimps_gm12878[,-1]), decreasing = TRUE),]
-all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
-all_varimps_gm12878 <- melt(all_varimps_gm12878)
-
-ggplot(all_varimps_gm12878, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
+names(all_varimps_gm12878_tfbs) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[order(rowMeans(all_varimps_gm12878_tfbs[,-1]), decreasing = TRUE),]
+all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[1:20,]
+all_varimps_gm12878_tfbs <- melt(all_varimps_gm12878_tfbs)
+
+a <- ggplot(all_varimps_gm12878_tfbs, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
   geom_tile(aes(fill = value), colour = "white") + 
-  xlab("Resolution") +
+  xlab("") +
   ylab("Transcription Factor") +
+  ggtitle("GM12878") +
+  scale_fill_gradient2(limits=c(0,100),
+                      low = "white",
+                      mid = "pink",
+                      midpoint = 50,
+                      high = muted("red"),
+                      na.value = "grey50",
+                      name="Predictive\nImportance") +
+  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 12),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        plot.title = element_text(size = 20))
+
+#K562
+all_varimps_K562_tfbs <- cbind.data.frame(varimp_K562_10kb$Feature,
+                                        varimp_K562_10kb$aveimp10kb,
+                                        varimp_K562_25kb$aveimp25kb,
+                                        varimp_K562_50kb$aveimp50kb,
+                                        varimp_K562_100kb$aveimp100kb)
+names(all_varimps_K562_tfbs) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+all_varimps_K562_tfbs <- all_varimps_K562_tfbs[order(rowMeans(all_varimps_K562_tfbs[,-1]), decreasing = TRUE),]
+all_varimps_K562_tfbs <- all_varimps_K562_tfbs[1:20,]
+all_varimps_K562_tfbs <- melt(all_varimps_K562_tfbs)
+
+b <- ggplot(all_varimps_K562_tfbs, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
+  geom_tile(aes(fill = value), colour = "white") + 
+  xlab("") +
+  ylab("") +
+  ggtitle("K562") +
+  scale_fill_gradient2(limits=c(0,100),
+                      low = "white",
+                      mid = "lightblue",
+                      midpoint = 50,
+                      high = muted("blue"),
+                      na.value = "grey50",
+                      name="Predictive\nImportance") +
+  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 12),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        plot.title = element_text(size = 20))
+
+figure <- ggarrange(a,b,
+                ncol = 2, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "bottom")
+figure
+
+```
+
+# Chromstates with distance type predictors with SMOTE resampling
+
+##GM12878
+
+```{r}
+annots <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
+annots <- annots[grep("Gm12878", annots)]
+annots <- gsub(paste(c("Gm12878-",".bed"), collapse = "|"), "", annots)
+
+```
+
+###10kb
+
+```{r}
+varimp_gm12878_10kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_10kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_10kb <- data.frame(Feature = rownames(varimp_gm12878_10kb),
+                                  aveimp10kb = rowMeans(varimp_gm12878_10kb, na.rm = TRUE),
+                                  sdimp10kb = apply(varimp_gm12878_10kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_10kb) <- NULL
+
+```
+
+###25kb
+
+```{r}
+varimp_gm12878_25kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_25kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_25kb <- data.frame(Feature = rownames(varimp_gm12878_25kb),
+                                  aveimp25kb = rowMeans(varimp_gm12878_25kb, na.rm = TRUE),
+                                  sdimp25kb = apply(varimp_gm12878_25kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_25kb) <- NULL
+
+```
+
+###50kb
+
+```{r}
+varimp_gm12878_50kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_50kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_50kb <- data.frame(Feature = rownames(varimp_gm12878_50kb),
+                                  aveimp50kb = rowMeans(varimp_gm12878_50kb, na.rm = TRUE),
+                                  sdimp50kb = apply(varimp_gm12878_50kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_50kb) <- NULL
+
+```
+
+###100kb
+
+```{r}
+varimp_gm12878_100kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_100kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_100kb <- data.frame(Feature = rownames(varimp_gm12878_100kb),
+                                  aveimp100kb = rowMeans(varimp_gm12878_100kb, na.rm = TRUE),
+                                  sdimp100kb = apply(varimp_gm12878_100kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_100kb) <- NULL
+
+```
+
+##K562
+
+```{r}
+annots <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
+annots <- annots[grep("K562", annots)]
+annots <- gsub(paste(c("K562-",".bed"), collapse = "|"), "", annots)
+
+```
+
+###10kb
+
+```{r}
+varimp_K562_10kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_10kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_10kb <- data.frame(Feature = rownames(varimp_K562_10kb),
+                                  aveimp10kb = rowMeans(varimp_K562_10kb, na.rm = TRUE),
+                                  sdimp10kb = apply(varimp_K562_10kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_10kb) <- NULL
+
+```
+
+###25kb
+
+```{r}
+varimp_K562_25kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_25kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)		
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_25kb <- data.frame(Feature = rownames(varimp_K562_25kb),
+                                  aveimp25kb = rowMeans(varimp_K562_25kb, na.rm = TRUE),
+                                  sdimp25kb = apply(varimp_K562_25kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_25kb) <- NULL
+
+```
+
+###50kb
+
+```{r}
+varimp_K562_50kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_50kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_50kb <- data.frame(Feature = rownames(varimp_K562_50kb),
+                                  aveimp50kb = rowMeans(varimp_K562_50kb, na.rm = TRUE),
+                                  sdimp50kb = apply(varimp_K562_50kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_50kb) <- NULL
+
+```
+
+###100kb
+
+```{r}
+varimp_K562_100kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_100kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_100kb <- data.frame(Feature = rownames(varimp_K562_100kb),
+                                  aveimp100kb = rowMeans(varimp_K562_100kb, na.rm = TRUE),
+                                  sdimp100kb = apply(varimp_K562_100kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_100kb) <- NULL
+
+```
+
+##Plots
+
+```{r}
+#GM12878
+all_varimps_gm12878_chromstates <- cbind.data.frame(varimp_gm12878_10kb$Feature,
+                                        varimp_gm12878_10kb$aveimp10kb,
+                                        varimp_gm12878_25kb$aveimp25kb,
+                                        varimp_gm12878_50kb$aveimp50kb,
+                                        varimp_gm12878_100kb$aveimp100kb)
+names(all_varimps_gm12878_chromstates) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+all_varimps_gm12878_chromstates <- all_varimps_gm12878_chromstates[order(rowMeans(all_varimps_gm12878_chromstates[,-1]), decreasing = TRUE),]
+#all_varimps_gm12878_chromstates <- all_varimps_gm12878_chromstates[1:20,]
+all_varimps_gm12878_chromstates <- melt(all_varimps_gm12878_chromstates)
+
+a <- ggplot(all_varimps_gm12878_chromstates, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
+  geom_tile(aes(fill = value), colour = "white") + 
+  xlab("") +
+  ylab("Chromatin State") +
+  ggtitle("GM12878") +
   scale_fill_gradient2(limits=c(0,100),
@@
         legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
+        legend.title=element_text(size=20),
+        plot.title = element_text(size = 20))
 
 #K562
-all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
+all_varimps_K562_chromstates <- cbind.data.frame(varimp_K562_10kb$Feature,
                                         varimp_K562_10kb$aveimp10kb,
@@
                                         varimp_K562_100kb$aveimp100kb)
-names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
-all_varimps_K562 <- all_varimps_K562[order(rowMeans(all_varimps_K562[,-1]), decreasing = TRUE),]
-all_varimps_K562 <- all_varimps_K562[1:20,]
-all_varimps_K562 <- melt(all_varimps_K562)
-
-ggplot(all_varimps_K562, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
+names(all_varimps_K562_chromstates) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+all_varimps_K562_chromstates <- all_varimps_K562_chromstates[order(rowMeans(all_varimps_K562_chromstates[,-1]), decreasing = TRUE),]
+#all_varimps_K562_chromstates <- all_varimps_K562_chromstates[1:20,]
+all_varimps_K562_chromstates <- melt(all_varimps_K562_chromstates)
+
+b <- ggplot(all_varimps_K562_chromstates, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
   geom_tile(aes(fill = value), colour = "white") + 
-  xlab("Resolution") +
-  ylab("Transcription Factor") +
+  xlab("") +
+  ylab("") +
+  ggtitle("K562") +
+  scale_fill_gradient2(limits=c(0,100),
+                      low = "white",
+                      mid = "lightblue",
+                      midpoint = 50,
+                      high = muted("blue"),
+                      na.value = "grey50",
+                      name="Predictive\nImportance") +
+  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 10),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        plot.title = element_text(size = 20))
+
+figure <- ggarrange(a,b,
+                ncol = 2, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "bottom")
+figure
+```
+
+# Histones with distance type predictors with SMOTE resampling
+
+##GM12878
+
+```{r}
+annots <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
+annots <- annots[grep("Gm12878", annots)]
+annots <- gsub(paste(c("Gm12878-",".bed"), collapse = "|"), "", annots)
+
+```
+
+###10kb
+
+```{r}
+varimp_gm12878_10kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_10kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)		
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_10kb <- data.frame(Feature = rownames(varimp_gm12878_10kb),
+                                  aveimp10kb = rowMeans(varimp_gm12878_10kb, na.rm = TRUE),
+                                  sdimp10kb = apply(varimp_gm12878_10kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_10kb) <- NULL
+
+```
+
+###25kb
+
+```{r}
+varimp_gm12878_25kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_25kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_25kb <- data.frame(Feature = rownames(varimp_gm12878_25kb),
+                                  aveimp25kb = rowMeans(varimp_gm12878_25kb, na.rm = TRUE),
+                                  sdimp25kb = apply(varimp_gm12878_25kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_25kb) <- NULL
+
+```
+
+###50kb
+
+```{r}
+varimp_gm12878_50kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_50kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_50kb <- data.frame(Feature = rownames(varimp_gm12878_50kb),
+                                  aveimp50kb = rowMeans(varimp_gm12878_50kb, na.rm = TRUE),
+                                  sdimp50kb = apply(varimp_gm12878_50kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_50kb) <- NULL
+
+```
+
+###100kb
+
+```{r}
+varimp_gm12878_100kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_100kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_100kb <- data.frame(Feature = rownames(varimp_gm12878_100kb),
+                                  aveimp100kb = rowMeans(varimp_gm12878_100kb, na.rm = TRUE),
+                                  sdimp100kb = apply(varimp_gm12878_100kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_100kb) <- NULL
+
+```
+
+##K562
+
+```{r}
+annots <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
+annots <- annots[grep("K562", annots)]
+annots <- gsub(paste(c("K562-",".bed"), collapse = "|"), "", annots)
+
+```
+
+###10kb
+
+```{r}
+varimp_K562_10kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_10kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_10kb <- data.frame(Feature = rownames(varimp_K562_10kb),
+                                  aveimp10kb = rowMeans(varimp_K562_10kb, na.rm = TRUE),
+                                  sdimp10kb = apply(varimp_K562_10kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_10kb) <- NULL
+
+```
+
+###25kb
+
+```{r}
+varimp_K562_25kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_25kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_25kb <- data.frame(Feature = rownames(varimp_K562_25kb),
+                                  aveimp25kb = rowMeans(varimp_K562_25kb, na.rm = TRUE),
+                                  sdimp25kb = apply(varimp_K562_25kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_25kb) <- NULL
+
+```
+
+###50kb
+
+```{r}
+varimp_K562_50kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_50kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_50kb <- data.frame(Feature = rownames(varimp_K562_50kb),
+                                  aveimp50kb = rowMeans(varimp_K562_50kb, na.rm = TRUE),
+                                  sdimp50kb = apply(varimp_K562_50kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_50kb) <- NULL
+
+```
+
+###100kb
+
+```{r}
+varimp_K562_100kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_100kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_100kb <- data.frame(Feature = rownames(varimp_K562_100kb),
+                                  aveimp100kb = rowMeans(varimp_K562_100kb, na.rm = TRUE),
+                                  sdimp100kb = apply(varimp_K562_100kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_100kb) <- NULL
+
+```
+
+##Plots
+
+```{r}
+#GM12878
+all_varimps_gm12878_histones <- cbind.data.frame(varimp_gm12878_10kb$Feature,
+                                        varimp_gm12878_10kb$aveimp10kb,
+                                        varimp_gm12878_25kb$aveimp25kb,
+                                        varimp_gm12878_50kb$aveimp50kb,
+                                        varimp_gm12878_100kb$aveimp100kb)
+names(all_varimps_gm12878_histones) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+all_varimps_gm12878_histones <- all_varimps_gm12878_histones[order(rowMeans(all_varimps_gm12878_histones[,-1]), decreasing = TRUE),]
+#all_varimps_gm12878_histones <- all_varimps_gm12878_histones[1:20,]
+all_varimps_gm12878_histones <- melt(all_varimps_gm12878_histones)
+
+a2 <- ggplot(all_varimps_gm12878_histones, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
+  geom_tile(aes(fill = value), colour = "white") + 
+  xlab("") +
+  ylab("Histone Modification") +
+  ggtitle("GM12878") +
   scale_fill_gradient2(limits=c(0,100),
@@
         legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-```
-
-# Chromstates with distance type predictors with SMOTE resampling
-
-##GM12878
-
-```{r}
-annots <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
-annots <- annots[grep("Gm12878", annots)]
-annots <- gsub(paste(c("Gm12878-",".bed"), collapse = "|"), "", annots)
-
-```
-
-###10kb
-
-```{r}
-varimp_gm12878_10kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_gm12878_10kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "Gm12878-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_gm12878_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_gm12878_10kb <- data.frame(Feature = rownames(varimp_gm12878_10kb),
-                                  aveimp10kb = rowMeans(varimp_gm12878_10kb, na.rm = TRUE),
-                                  sdimp10kb = apply(varimp_gm12878_10kb,1, sd, na.rm = TRUE))
-rownames(varimp_gm12878_10kb) <- NULL
-
-```
-
-###25kb
-
-```{r}
-varimp_gm12878_25kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_gm12878_25kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "Gm12878-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_gm12878_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_gm12878_25kb <- data.frame(Feature = rownames(varimp_gm12878_25kb),
-                                  aveimp25kb = rowMeans(varimp_gm12878_25kb, na.rm = TRUE),
-                                  sdimp25kb = apply(varimp_gm12878_25kb,1, sd, na.rm = TRUE))
-rownames(varimp_gm12878_25kb) <- NULL
-
-```
-
-###50kb
-
-```{r}
-varimp_gm12878_50kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_gm12878_50kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "Gm12878-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_gm12878_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_gm12878_50kb <- data.frame(Feature = rownames(varimp_gm12878_50kb),
-                                  aveimp50kb = rowMeans(varimp_gm12878_50kb, na.rm = TRUE),
-                                  sdimp50kb = apply(varimp_gm12878_50kb,1, sd, na.rm = TRUE))
-rownames(varimp_gm12878_50kb) <- NULL
-
-```
-
-###100kb
-
-```{r}
-varimp_gm12878_100kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_gm12878_100kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "Gm12878-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_gm12878_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_gm12878_100kb <- data.frame(Feature = rownames(varimp_gm12878_100kb),
-                                  aveimp100kb = rowMeans(varimp_gm12878_100kb, na.rm = TRUE),
-                                  sdimp100kb = apply(varimp_gm12878_100kb,1, sd, na.rm = TRUE))
-rownames(varimp_gm12878_100kb) <- NULL
-
-```
-
-##K562
-
-```{r}
-annots <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
-annots <- annots[grep("K562", annots)]
-annots <- gsub(paste(c("K562-",".bed"), collapse = "|"), "", annots)
-
-```
-
-###10kb
-
-```{r}
-varimp_K562_10kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_K562_10kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "K562-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_K562_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_K562_10kb <- data.frame(Feature = rownames(varimp_K562_10kb),
-                                  aveimp10kb = rowMeans(varimp_K562_10kb, na.rm = TRUE),
-                                  sdimp10kb = apply(varimp_K562_10kb,1, sd, na.rm = TRUE))
-rownames(varimp_K562_10kb) <- NULL
-
-```
-
-###25kb
-
-```{r}
-varimp_K562_25kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_K562_25kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "K562-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)		
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_K562_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_K562_25kb <- data.frame(Feature = rownames(varimp_K562_25kb),
-                                  aveimp25kb = rowMeans(varimp_K562_25kb, na.rm = TRUE),
-                                  sdimp25kb = apply(varimp_K562_25kb,1, sd, na.rm = TRUE))
-rownames(varimp_K562_25kb) <- NULL
-
-```
-
-###50kb
-
-```{r}
-varimp_K562_50kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_K562_50kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "K562-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_K562_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_K562_50kb <- data.frame(Feature = rownames(varimp_K562_50kb),
-                                  aveimp50kb = rowMeans(varimp_K562_50kb, na.rm = TRUE),
-                                  sdimp50kb = apply(varimp_K562_50kb,1, sd, na.rm = TRUE))
-rownames(varimp_K562_50kb) <- NULL
-
-```
-
-###100kb
-
-```{r}
-varimp_K562_100kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_K562_100kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "K562-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_K562_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_K562_100kb <- data.frame(Feature = rownames(varimp_K562_100kb),
-                                  aveimp100kb = rowMeans(varimp_K562_100kb, na.rm = TRUE),
-                                  sdimp100kb = apply(varimp_K562_100kb,1, sd, na.rm = TRUE))
-rownames(varimp_K562_100kb) <- NULL
-
-```
-
-##Plots
-
-```{r}
-#GM12878
-all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
-                                        varimp_gm12878_10kb$aveimp10kb,
-                                        varimp_gm12878_25kb$aveimp25kb,
-                                        varimp_gm12878_50kb$aveimp50kb,
-                                        varimp_gm12878_100kb$aveimp100kb)
-names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
-all_varimps_gm12878 <- all_varimps_gm12878[order(rowMeans(all_varimps_gm12878[,-1]), decreasing = TRUE),]
-#all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
-all_varimps_gm12878 <- melt(all_varimps_gm12878)
-
-chromstates_gm12878_plot <- ggplot(all_varimps_gm12878, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
+        legend.title=element_text(size=20),
+        plot.title = element_text(size = 20))
+
+#K562
+all_varimps_K562_histones <- cbind.data.frame(varimp_K562_10kb$Feature,
+                                        varimp_K562_10kb$aveimp10kb,
+                                        varimp_K562_25kb$aveimp25kb,
+                                        varimp_K562_50kb$aveimp50kb,
+                                        varimp_K562_100kb$aveimp100kb)
+names(all_varimps_K562_histones) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+all_varimps_K562_histones <- all_varimps_K562_histones[order(rowMeans(all_varimps_K562_histones[,-1]), decreasing = TRUE),]
+#all_varimps_K562_histones <- all_varimps_K562_histones[1:20,]
+all_varimps_K562_histones <- melt(all_varimps_K562_histones)
+
+b2 <- ggplot(all_varimps_K562_histones, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
   geom_tile(aes(fill = value), colour = "white") + 
@@
   ylab("") +
+  ggtitle("K562") +
   scale_fill_gradient2(limits=c(0,100),
                       low = "white",
-                      mid = "pink",
+                      mid = "lightblue",
                       midpoint = 50,
-                      high = muted("red"),
+                      high = muted("blue"),
                       na.value = "grey50",
@@
         legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-#K562
-all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
-                                        varimp_K562_10kb$aveimp10kb,
-                                        varimp_K562_25kb$aveimp25kb,
-                                        varimp_K562_50kb$aveimp50kb,
-                                        varimp_K562_100kb$aveimp100kb)
-names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
-all_varimps_K562 <- all_varimps_K562[order(rowMeans(all_varimps_K562[,-1]), decreasing = TRUE),]
-#all_varimps_K562 <- all_varimps_K562[1:20,]
-all_varimps_K562 <- melt(all_varimps_K562)
-
-chromstates_K562_plot <- ggplot(all_varimps_K562, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
-  geom_tile(aes(fill = value), colour = "white") + 
-  xlab("") +
-  ylab("") +
-  scale_fill_gradient2(limits=c(0,100),
-                      low = "white",
-                      mid = "pink",
-                      midpoint = 50,
-                      high = muted("red"),
-                      na.value = "grey50",
-                      name="Predictive\nImportance") +
-  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15,
-                                   angle = 45,
-                                   hjust = 1),
-        axis.text.y = element_text(size = 10),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-figure <- ggarrange(chromstates_gm12878_plot,
-                    chromstates_K562_plot,
+        legend.title=element_text(size=20),
+        plot.title = element_text(size = 20))
+
+figure <- ggarrange(a,b,
                 ncol = 2, nrow = 1, 
                 common.legend = TRUE, 
-                legend = "right",
-                labels = "AUTO",
-                font.label = list(size=20))
+                legend = "bottom")
 figure
-annotate_figure(figure,
-    bottom = text_grob("Resolution", color = "black", size = 20),
-    left = text_grob("Chromatin States", color = "black", rot = 90, size=20)
-)
-
-```
-
-# Histones with distance type predictors with SMOTE resampling
-
-##GM12878
-
-```{r}
-annots <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
-annots <- annots[grep("Gm12878", annots)]
-annots <- gsub(paste(c("Gm12878-",".bed"), collapse = "|"), "", annots)
-
-```
-
-###10kb
-
-```{r}
-varimp_gm12878_10kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_gm12878_10kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_histones.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "Gm12878-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)		
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_gm12878_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_gm12878_10kb <- data.frame(Feature = rownames(varimp_gm12878_10kb),
-                                  aveimp10kb = rowMeans(varimp_gm12878_10kb, na.rm = TRUE),
-                                  sdimp10kb = apply(varimp_gm12878_10kb,1, sd, na.rm = TRUE))
-rownames(varimp_gm12878_10kb) <- NULL
-
-```
-
-###25kb
-
-```{r}
-varimp_gm12878_25kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_gm12878_25kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_histones.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "Gm12878-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_gm12878_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_gm12878_25kb <- data.frame(Feature = rownames(varimp_gm12878_25kb),
-                                  aveimp25kb = rowMeans(varimp_gm12878_25kb, na.rm = TRUE),
-                                  sdimp25kb = apply(varimp_gm12878_25kb,1, sd, na.rm = TRUE))
-rownames(varimp_gm12878_25kb) <- NULL
-
-```
-
-###50kb
-
-```{r}
-varimp_gm12878_50kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_gm12878_50kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_histones.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "Gm12878-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_gm12878_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_gm12878_50kb <- data.frame(Feature = rownames(varimp_gm12878_50kb),
-                                  aveimp50kb = rowMeans(varimp_gm12878_50kb, na.rm = TRUE),
-                                  sdimp50kb = apply(varimp_gm12878_50kb,1, sd, na.rm = TRUE))
-rownames(varimp_gm12878_50kb) <- NULL
-
-```
-
-###100kb
-
-```{r}
-varimp_gm12878_100kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_gm12878_100kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_histones.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "Gm12878-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_gm12878_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_gm12878_100kb <- data.frame(Feature = rownames(varimp_gm12878_100kb),
-                                  aveimp100kb = rowMeans(varimp_gm12878_100kb, na.rm = TRUE),
-                                  sdimp100kb = apply(varimp_gm12878_100kb,1, sd, na.rm = TRUE))
-rownames(varimp_gm12878_100kb) <- NULL
-
-```
-
-##K562
-
-```{r}
-annots <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
-annots <- annots[grep("K562", annots)]
-annots <- gsub(paste(c("K562-",".bed"), collapse = "|"), "", annots)
-
-```
-
-###10kb
-
-```{r}
-varimp_K562_10kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_K562_10kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_histones.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "K562-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_K562_10kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_K562_10kb <- data.frame(Feature = rownames(varimp_K562_10kb),
-                                  aveimp10kb = rowMeans(varimp_K562_10kb, na.rm = TRUE),
-                                  sdimp10kb = apply(varimp_K562_10kb,1, sd, na.rm = TRUE))
-rownames(varimp_K562_10kb) <- NULL
-
-```
-
-###25kb
-
-```{r}
-varimp_K562_25kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_K562_25kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_histones.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "K562-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_K562_25kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_K562_25kb <- data.frame(Feature = rownames(varimp_K562_25kb),
-                                  aveimp25kb = rowMeans(varimp_K562_25kb, na.rm = TRUE),
-                                  sdimp25kb = apply(varimp_K562_25kb,1, sd, na.rm = TRUE))
-rownames(varimp_K562_25kb) <- NULL
-
-```
-
-###50kb
-
-```{r}
-varimp_K562_50kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_K562_50kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_histones.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "K562-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_K562_50kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_K562_50kb <- data.frame(Feature = rownames(varimp_K562_50kb),
-                                  aveimp50kb = rowMeans(varimp_K562_50kb, na.rm = TRUE),
-                                  sdimp50kb = apply(varimp_K562_50kb,1, sd, na.rm = TRUE))
-rownames(varimp_K562_50kb) <- NULL
-
-```
-
-###100kb
-
-```{r}
-varimp_K562_100kb <- matrix(nrow=length(annots), ncol=21)
-rownames(varimp_K562_100kb) <- annots
-
-chrs <- paste0("CHR", c(1:8,10:22))
-for(i in 1:length(chrs)){
-	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
-                              chrs[i],
-									            "/smote/distance/enet/rfimpvars_histones.rds"))
-	  varimps$Feature <- gsub(paste0(c("`",
-	                                   "K562-",
-	                                   "_dist",
-	                                   "-Haib", 
-                                     "-Sydh",
-                                     "-Uta",
-                                     "-Uw",
-                                     "-Broad",
-                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
-	  varimps <- varimps[order(varimps$Feature),]
-
-		varimp_K562_100kb[match(varimps$Feature,annots),i] <- varimps$Importance
-}
-
-varimp_K562_100kb <- data.frame(Feature = rownames(varimp_K562_100kb),
-                                  aveimp100kb = rowMeans(varimp_K562_100kb, na.rm = TRUE),
-                                  sdimp100kb = apply(varimp_K562_100kb,1, sd, na.rm = TRUE))
-rownames(varimp_K562_100kb) <- NULL
-
-```
-
-##Plots
-
-```{r}
-#GM12878
-all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
-                                        varimp_gm12878_10kb$aveimp10kb,
-                                        varimp_gm12878_25kb$aveimp25kb,
-                                        varimp_gm12878_50kb$aveimp50kb,
-                                        varimp_gm12878_100kb$aveimp100kb)
-names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
-all_varimps_gm12878 <- all_varimps_gm12878[order(rowMeans(all_varimps_gm12878[,-1]), decreasing = TRUE),]
-#all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
-all_varimps_gm12878 <- melt(all_varimps_gm12878)
-
-histones_gm12878_plot <- ggplot(all_varimps_gm12878, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
-  geom_tile(aes(fill = value), colour = "white") + 
-  xlab("") +
-  ylab("") +
-  scale_fill_gradient2(limits=c(0,100),
-                      low = "white",
-                      mid = "pink",
-                      midpoint = 50,
-                      high = muted("red"),
-                      na.value = "grey50",
-                      name="Predictive\nImportance") +
-  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15,
-                                   angle = 45,
-                                   hjust = 1),
-        axis.text.y = element_text(size = 10),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-#K562
-all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
-                                        varimp_K562_10kb$aveimp10kb,
-                                        varimp_K562_25kb$aveimp25kb,
-                                        varimp_K562_50kb$aveimp50kb,
-                                        varimp_K562_100kb$aveimp100kb)
-names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
-all_varimps_K562 <- all_varimps_K562[order(rowMeans(all_varimps_K562[,-1]), decreasing = TRUE),]
-#all_varimps_K562 <- all_varimps_K562[1:20,]
-all_varimps_K562 <- melt(all_varimps_K562)
-
-histones_K562_plot <- ggplot(all_varimps_K562, aes(variable, ordered(Feature, levels=rev(unique(Feature))))) + 
-  geom_tile(aes(fill = value), colour = "white") + 
-  xlab("") +
-  ylab("") +
-  scale_fill_gradient2(limits=c(0,100),
-                      low = "white",
-                      mid = "pink",
-                      midpoint = 50,
-                      high = muted("red"),
-                      na.value = "grey50",
-                      name="Predictive\nImportance") +
-  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
-  theme_bw() +
-  theme(axis.text.x = element_text(size=15,
-                                   angle = 45,
-                                   hjust = 1),
-        axis.text.y = element_text(size = 10),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
-
-figure <- ggarrange(histones_gm12878_plot,
-                    histones_K562_plot,
-                ncol = 2, nrow = 1, 
+
+figure <- ggarrange(a,b,a2,b2,
+                ncol = 2, nrow = 2, 
                 common.legend = TRUE, 
-                legend = "right",
-                labels = "AUTO",
-                font.label = list(size=20))
+                legend = "bottom",
+                labels = c("A","","B",""),
+                font.label = list(size=25))
 figure
-annotate_figure(figure,
-    bottom = text_grob("Resolution", color = "black", size = 20),
-    left = text_grob("Histone Modifications", color = "black", rot = 90, size=20)
-)
-
-```
+```

### 2019-07-01 Scripts/proportion_of_importance_per_annotation.Rmd
editted script for figure

@@
 
-ggplot(all_propimp_gm12878_summ, aes(fill=Annotation, y=Prop.VI, x=Resolution)) + 
+a <- ggplot(all_propimp_gm12878_summ, aes(fill=Annotation, y=Prop.VI, x=Resolution)) + 
   geom_bar( stat="identity", position="fill") +
-  xlab("Resolution") +
+  xlab("") +
   ylab("Proportion of Importance") +
-  scale_fill_discrete(name="Annotation\nGroup")+
+  scale_fill_discrete(name="Annotation Group")+
+  ggtitle("GM12878") +
   theme_bw() +
@@
         legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
+        legend.title=element_text(size=20),
+        plot.title = element_text(size=20))
 
@@
 
-ggplot(all_propimp_K562_summ, aes(fill=Annotation, y=Prop.VI, x=Resolution)) + 
+b <- ggplot(all_propimp_K562_summ, aes(fill=Annotation, y=Prop.VI, x=Resolution)) + 
   geom_bar( stat="identity", position="fill") +
-  xlab("Resolution") +
-  ylab("Proportion of Importance") +
-  scale_fill_discrete(name="Annotation\nGroup")+
+  xlab("") +
+  ylab("") +
+  scale_fill_discrete(name="Annotation Group")+
+  ggtitle("K562") +
   theme_bw() +
@@
         legend.text=element_text(size=15),
-        legend.title=element_text(size=20))
+        legend.title=element_text(size=20),
+        plot.title = element_text(size=20))
 
 ```
+
+# Plots v2
+
+```{r}
+figure <- ggarrange(a,b,
+                ncol = 2, nrow = 1, 
+                common.legend = TRUE, 
+                legend = "bottom")
+figure
+
+all_propimp <- rbind(all_propimp_gm12878_summ, all_propimp_K562_summ)
+all_propimp$CL <- c(rep("GM12878", 12),
+                    rep("K562", 12))
+
+ggplot(all_propimp, aes(fill=Annotation, y=Prop.VI, x=Resolution)) + 
+  geom_bar( stat="identity", position="fill") +
+  facet_grid(~ CL) +
+  xlab("Resolution") +
+  ylab("Proportion of Importance") +
+  scale_fill_discrete(name="Annotation Group")+
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45,
+                                   hjust = 1),
+        axis.text.y = element_text(size = 10),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        strip.text.x = element_text(size = 15),
+        panel.spacing = unit(2, "lines"),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        legend.position = "bottom")
+
+```

### 2019-07-01 Manuscript/manuscript.Rmd
edits

@@
 In doing so, we inspected the proportion of predictive importance that was explained by each of the 3 groups of annotations (chromatin states, histone modifications, and transcription factor binding sites).
-We found that for cell line specific random forest models implemented on distance-type predictors, using SMOTE re-sampling, the majority of the proportional predictive importance was obtained by the functional genomic annotations classified as transcription factor binding sites (TFBS) (Figure 6).
+We found that for cell line specific random forest models implemented on distance-type predictors, using SMOTE re-sampling, the majority of the proportional predictive importance was obtained by the functional genomic annotations classified as transcription factor binding sites (TFBS) (Figure 6 A).
 This was consistent across resolutions, suggesting that TFBS were the primary drivers of TAD boundary formation in both the GM12878 and K562 cell lines.
@@
 We further assessed the predictive capabilities of the specific sets of annotations by comparing the performances of annotation-specific random forest models implemented on the optimal set of characteristics.
-We found that cell line specific models built simply on TFBS out performed other cell line and annotation-specific models at all resolutions (Figure 7).
+We found that cell line specific models built simply on TFBS out performed other cell line and annotation-specific models at all resolutions (Figure 6 B).
 Additionally, when compared to models built on all 3 sets of functional genomic annotations, the TFBS-specific models performed similarly at the 10 kb and 25 kb resolutions.
@@
 This indicated that, at lower resolutions, the inclusion of other types of annotations contributed to additional noise rather than signal.
+These results imply that restricting the feature space of downstream predictive models to transcription factor binding sites is less computationally intesive and does not necessarily sacrifice performance.
 
@@
 
-We then sought to determine which of the transcription factor binding sites were most influential in predicting TAD boundaries.
-We found that the cell line specific binding sites associated with SMC3, CTCF, RAD21, ZNF143, and YY1sc281 were given consistently high predictive importance, across all resolutions (Figure 7; Supplementary Figure 6).
+We then sought to determine which of the cell line specific transcription factor binding sites were most influential in predicting TAD boundaries.
+
+We found that the cell line specific binding sites associated with SMC3, CTCF, RAD21, ZNF143, and YY1sc281 were given consistently high predictive importance, across all resolutions (Figure 6 C).
 The SMC3, CTCF, and RAD21 binding sites are known factors associated with the cohesin protein complex, which is hypothesized to be what creates loops in the DNA  [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].

### 2019-07-06 Manuscript/manuscript.Rmd
Review

--- 2019-07-01 Manuscript/manuscript.Rmd
@@
 Likewise, evidence suggests that the boundaries that delineate TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes [@symmons2014functional].
-Even more so, loci within a domain have been shown to interact more frequently with one another, exhibiting similar patterns of chromatin modifications, and long-range contact patterns [@rao20143d; @symmons2014functional] [???
-This sentence and reference belong to the previous paragraph, think and move; !!!combined and moved].
+Even more so, loci within a domain have been shown to interact more frequently with one another, exhibiting similar patterns of chromatin modifications, and long-range contact patterns [@rao20143d; @symmons2014functional].
 Furthermore, studies have shown that changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @Flavahan2016; @song2017ctcf].
@@
 
-Distinct patterns in epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries [@dixon2015chromatin; @di2017novo] [???
-REFS?
-Carefully select from my paper notes; !!!added refs].
+Distinct patterns in epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries [@dixon2015chromatin; @di2017novo].
 Recent research has identified key functional genomic annotations enriched at boundaries.
@@
 You started with mentioning prediction - finish with unsolved problems with it.
-!!!editted]-->
+!!!editted]--> [???
+What's the summary/conclusion/problem?]
 
-Current methods used to predict TAD boundaries rely on the use of classification models to draw associations between functional annotations and genomic regions that include TAD boundaries.
+Current methods used to predict [???
+you never introduced prediction problem] TAD boundaries rely on the use of classification models to draw associations between functional annotations and genomic regions that include TAD boundaries.
 However, many key characteristics of 3D genomic data remain unexplored, potentially limiting performance of predictive modeling.
@@
 A dataset is considered imbalanced if PI<0.5.
-<!--Specifically, the minority of TAD boundaries as compared with the rest of the genome creates heavily imbalanced classes, characterized by ratios of positive/negative classes used to train the models.
+[???
+Not really.
+Poor metric choice.] <!--Specifically, the minority of TAD boundaries as compared with the rest of the genome creates heavily imbalanced classes, characterized by ratios of positive/negative classes used to train the models.
 Here, the imbalance ratio is defined as the ratio of majority classes (regions not including TAD boundaries) to minority classes (regions including TAD boundaries) [@Orriols-Puig2008].--> Classifiers implemented on heavily imbalanced datasets are known to exhibit poor performances as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
@@
 If multiple overlaps existed, the feature width was defined as the sum of the total number of bases that overlapped with a particular bin.
+[???
+Unclear.]
 
 3.
-**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter simply as $\textit{distance}$), from the center of the bin to the center of the nearest region defined by a specific genomic annotation was calculated.
+**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter as $\textit{distance}$) [???
+Learn Markdown!], from the center of the bin to the center of the nearest region defined by a specific genomic annotation was calculated.
 
@@
 
-Class imbalance was characterized by each dataset's *proportion of imbalance* (PI), defined as the ratio of minority class observations to the sum of minority and majority class observations:
+Class imbalance was characterized by each dataset's *proportion of imbalance* (PI), [???
+Why?
+It is bounded [0, 0.5], never seen it is used.] defined as the ratio of minority class observations to the sum of minority and majority class observations:
 
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-Additional performance metrics were reported in the supplementary materials.
+Additional performance metrics were [???
+are?] reported in the supplementary materials.
+[???
+Where is it?]
 
@@
 To account for the varying levels of data resolution, we developed a resolution-specific approach toward constructing TAD versus non TAD boundary regions on the linear genome, labeled as a response vector **Y** (Figure 1).
-First we binned the linear genome according to the data resolution.
+First, we binned the linear genome according to the data resolution.
 We then flanked the boundaries on either side by the same number of basepairs as the previously constructed genomic bins.
@@
 
-We first sought to compare the cell-line specificity of TAD boundary regions.
+We sought to compare the cell-line specificity of TAD boundary regions.
 Between the two cell lines, a significant number of TAD boundary regions were found to be specific to one of the two cell lines (Figure 2B).
-It was found that 45%, 38%, 37%, and 36% of TAD boundary regions were specific to the GM12878 cell line, across each resolution respectively.
+It was found that 45%, 38%, 37%, and 36% of TAD boundary regions were specific to the GM12878 cell line, across each resolution [???
+spell out resolutions exactly.] respectively.
 Similarly, for K562, it was found that 27%, 27%, 29%, and 33% of TAD boundary regions were cell line specific for each resolution specifically.
-This indicates a necessity for computationally specific models in predicting TAD boundary formations.
+This indicates a necessity for computationally specific models [???
+Do not understand] in predicting TAD boundary formations.
 
@@
 Such low proportions of imbalance gave precedence for the implementation of re-sampling prior to classification.
+[???
+It is low because the upper bound is 0.5.
+It is an unconventional measure.]
 
@@
 
-A total of 107 and 152 cell type specific functional genomic annotations derived from ChIP-Seq experiments (See Methods) for the GM12878 and K562 cell line respectively.
-To establish the feature space used for classification, we constructed three different predictor types for each functional genomic annotation.
+A total of 107 and 152 cell type specific functional genomic annotations derived from ChIP-Seq experiments (See Methods) for the GM12878 and K562 cell line, respectively.
+[???
+Is that so?
+How many are common?] To establish the feature space used for classification, we constructed three different predictor types for each functional genomic annotation.
 Counts of overlaps (**overlap count**, OC) is the most commonly used type of association between genomic elements (Figure 3A).
@@
 **Distance** between the centers of bins and genomic annotations quantifying the spatial relationship between genomic elements is currently unexplored (Figure 3C).
-Log2-transformation of distance was used as a normalization technique in order to account for the skewness present in the distributions of distances (Supplementary Figures 1-2).
+Log2-transformation of distance was used to account for the skewness present in the distributions of distances (Supplementary Figures 1-2).
 These types of genomic associations provide a granular way to investigate classifier performance in class imbalance settings.
@@
 Each combination of the above cell line specific parameters was implemented on chromosome specific sections of the linear genome (omitting chromosome 9).
-Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling 2016 ($2 \times 4 \times 3 \times 4 \times 21$) separate models.
+Letting $|X|$ denote the cardinality [???
+TBD] of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling 2016 ($2 \times 4 \times 3 \times 4 \times 21$) separate models.
 For each combination of inputs, we performed 10-fold cross-validation to tune for the number of features to consider at each node of the random forest classifier.
@@
 
-We first evaluated the least granular cell line specific random forest classifiers, those were ones implemented using OC predictor types, without data re-sampling.
+We first evaluated the least granular cell line specific random forest classifiers [???
+Unclear], those were ones implemented using OC predictor types, without data re-sampling.
 We found that these models exhibited poor MCCs across all resolutions (Figure 5 A-B (red)).
@@
 
-After determining the optimal set of data level characteristics, we then aimed to compare the performances of annotation-specifc models, within each cell line and across resolution.
+After determining the optimal set of data level characteristics, we then aimed to compare the performances of annotation-specifc models [???
+Never defined, what is this?], within each cell line and across resolution.
 In doing so, we inspected the proportion of predictive importance that was explained by each of the 3 groups of annotations (chromatin states, histone modifications, and transcription factor binding sites).
@@
 We further assessed the predictive capabilities of the specific sets of annotations by comparing the performances of annotation-specific random forest models implemented on the optimal set of characteristics.
-We found that cell line specific models built simply on TFBS out performed other cell line and annotation-specific models at all resolutions (Figure 7).
+We found that cell line specific models built simply on TFBS outperformed other cell line and annotation-specific models at all resolutions (Figure 7).
 Additionally, when compared to models built on all 3 sets of functional genomic annotations, the TFBS-specific models performed similarly at the 10 kb and 25 kb resolutions.
@@
 These transcription factor binding sites tended to be given higher predictive importance at lower resolutions.
-In fact, at lower resolutions, the predictive importance was found to be much more evenly dispersed across the top transcription factor binding sites, than for higher resolutions.
+[???
+Where do you show it?] In fact, at lower resolutions, the predictive importance was found to be much more evenly dispersed across the top transcription factor binding sites, than for higher resolutions.
 This is again suggestive of the fact that the spatial relationship between functional annotations, specifically transcription factor binding sites, and TAD boundaries changes at different Hi-C data resolutions.
@@
 
-[Put this section last]
-
 ## INFLUENTIAL TFBS TENDED TO BE CLOSER TO BINS THAT OVERLAPPED WITH FLANKED TAD BOUNDARIES THAN THOSE THAT DID NOT
@@
 For GM12878, at 10 kb resolution, we found that SMC3, CTCF, RAD21, ZNF143, and YY1sc281 were all statistically significantly closer to bins that overlapped with flanked TAD boudaries than those that did not (Figure 8).
-Although still statistically significantly different, the distance profiles between genomic class were found to be much more similar at lower resolutions (Supplementary Figure 9).
+[???
+not there] Although still statistically significantly different, the distance profiles between genomic class were found to be much more similar at lower resolutions (Supplementary Figure 9).
 For the K562 cell line, we reported the distance profiles of the same transcription factor binding sites, excluding the YY1sc281, due to its unavailability in the UCSC Genome Browser.
@@
 We provide direct comparisons of cell line specific random forest models built on a variety of different data dependent characteristics, including 4 contact matrix resolutions ($\{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$), 3 predictor-types ($\{\textit{OC}, \textit{OP}, \textit{Distance}\}$), and 4 re-sampling techniques ($\{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$), for both the GM12878 and K562 cell lines.
+[???
+Learn Markdown] [???
+What's the summary of your work?]
 
@@
 Using the framework we demonstrated that random forest models built on imbalanced data exhibited poor performance, regardless of cell line, resolution, or predictor type.
-In our framework, we opted to leave the test set as a completely untouched holdout set, only performing the re-sampling, and subsequent learning, on the training set.
+In our framework, [???
+Too much "framework" mentioning] we opted to leave the test set as a completely untouched holdout set, only performing the re-sampling, and subsequent learning, on the training set.
 This was done so as to incur the least amount of bias and so that all conclusions could be made soley between model characteristics.
-As a result, we showed that Matthews Correlation Coefficient was much more sensitive to the imbalance present in the test set, compared to more popular metrics like AUROC, which attain artificially high values by correctly predicting majority class samples [??
-I may be mistaken but I don't see where this is proven ??].
+As a result, we showed that Matthews Correlation Coefficient was much more sensitive to the imbalance present in the test set, compared to more popular metrics like AUROC, which attain artificially high values by correctly predicting majority class samples [???
+I don't see results for it].
 When comparing re-sampling techniques, we found that SMOTE re-sampling outperformed models built on both simple ROS or RUS, implying that, in fact, a combination of both random under-sampling and random over-sampling is preferred in TAD boundary prediction.
-Furthermore, the most improvement [??
-Over what ??] was seen when combining SMOTE resampling on distance-type features when building random forest classifiers.
+Furthermore, the most improvement [???
+In what?] was seen when combining SMOTE resampling on distance-type features when building random forest classifiers.
 These two characteristics exhibited consistently better performance results across both the GM12878 and K562 cell lines.
@@
 Might want to qualify the statement in results about 10kb data being best by saying that it only applies to your data ??].
+[???
+This paragraph is a mess]
 
@@
 This was due to the fact that we opted to use cell line specific annotations, and there existed some annotations that were available on the K562 cell line that were not available to GM12878, and vice versa.
-However, we were able to confirm that final models built on the optimal set of data characteristics identified consistent and well known proteins related to the 3D structure of chromatin, for both cell lines.
+[???
+Did they provide additional advantage?] However, we were able to confirm that final models built on the optimal set of data characteristics identified consistent and well known proteins related to the 3D structure of chromatin, for both cell lines.
 Our results indicated that the zinc finger protein CTCF, as well components of the cohesin complex, SMC3 and RAD21, were found to be the key molecular drivers most predictive of TAD boundary formation, consistent across cell line and resolution.

### 2019-07-08 Manuscript/manuscript.Rmd
resolved conflict
grammar edit

@@
 
-![**SMOTE re-sampling coupled with distance-type predictors yielded optimal MCCs across resolution for cell line specific models.** Performances of random forest classification models built on each of the 3 predictor types includeing (A-B) OC, (C-D) OP, and (E-F) Distance, and across both the GM12878 and K562 cell lines.
+![**SMOTE re-sampling coupled with distance-type predictors yielded optimal MCCs across resolution for cell line specific models.** Performances of random forest classification models built on each of the 3 predictor types including (A-B) OC, (C-D) OP, and (E-F) Distance, and across both the GM12878 and K562 cell lines.
 Within each cell line, predictor type, and resolution, chromosome-specific training data was re-sampled using different techniques including no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and *Synthetic Minority Over Sampling TEchnique* (SMOTE; purple).

### 2019-07-08 Papers.Rmd
Add Mourad's distance idea

@@
 
+- Mourad, Raphaël.
+“Studying 3D Genome Evolution Using Genomic Sequence.” Preprint.
+Bioinformatics, May 23, 2019.
+https://doi.org/10.1101/646851.
+- Distance idea - Ratio R of the median distances between convergent CTCF motifs.
+CTCF sites from ChIP-seq, predicted if not available.
+R depends on A/B compartments and subcompartments, replication timing, isochores.
+R can be used to study genome evolution.https://github.com/morphos30/PhyloCTCFLooping
+
 - Idea that TAD boundaries may not be created equal.

### 2019-07-09 Scripts/comparing_tad_regions_across_cl_using_vd.Rmd
added 5kb results

@@
 }
+
+```
+
+### 5kb
+
+```{r}
+#bounds_f_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/bounds_f.rds")
+#bounds_f_K562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/bounds_f.rds")
+
+#res <- makeVennDiagram(Peaks=list(bounds_f_gm12878_5kb, bounds_f_K562_5kb),
+#                       NameOfPeaks=c("GM12878", "K562"))
+
+#venn_5kb <- venn_cnt2venn(res$vennCounts)
+#plot(venn_5kb)
+
+binslist_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/binslist5.rds")
+binslist_gm12878_5kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/binslist5_center.rds")
+mcols(binslist_gm12878_5kb)$y <- mcols(binslist_gm12878_5kb_center)$y
+binslist_gm12878_5kb <- binslist_gm12878_5kb[mcols(binslist_gm12878_5kb)$y==1]
+
+binslist_K562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/binslist5.rds")
+binslist_K562_5kb_center <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/binslist5_center.rds")
+mcols(binslist_K562_5kb)$y <- mcols(binslist_K562_5kb_center)$y
+binslist_K562_5kb <- binslist_K562_5kb[mcols(binslist_K562_5kb)$y==1]
+
+res <- makeVennDiagram(Peaks=list(binslist_gm12878_5kb, binslist_K562_5kb),
+                       NameOfPeaks=c("GM12878", "K562"))
+
+venn_5kb <- venn_cnt2venn(res$vennCounts)
+venn_5kb <- compute.Venn(venn_5kb)
+gp <- VennThemes(venn_5kb)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+#plot(venn_5kb)
 
@@
 
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_5kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("5 kb", gp=gpar(fontsize=20)))
+grid.newpage()
 gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_10kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("10 kb", gp=gpar(fontsize=20)))

### 2019-07-09 Scripts/evaluating_imbalance_ratios.Rmd
added 5kb results

--- 2019-06-16 Scripts/evaluating_imbalance_ratios.Rmd
@@
 for(i in c("GM12878","K562")){
-  for(j in c("10kb", "25kb","50kb","100kb")){
+  for(j in c("5kb", "10kb", "25kb","50kb","100kb")){
     for(k in 1:length(chrs)){
@@
                           bounds.per.chr,
-                          ir.per.chr)
-colnames(irtab) <- c("cl","res","chr","bins","tads","bounds","ir")
-irtab$res <- factor(irtab$res, levels=c("10kb","25kb","50kb","100kb"))
+                          ir.per.chr,
+                          pi.per.chr)
+colnames(irtab) <- c("cl","res","chr","bins","tads","bounds","ir","pi")
+irtab$res <- factor(irtab$res, levels=c("5kb","10kb","25kb","50kb","100kb"))
 
@@
 ```{r}
-a <- ggplot(bounds_df[which(bounds_df$res=="10kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+a <- ggplot(bounds_df[which(bounds_df$res=="5kb"),], aes(x=cl, y=TotBounds, fill=cl))+
   geom_bar(stat="identity", position="dodge")+
@@
   theme_bw()+
-  xlab("") + ylab("") + ylim(0,27000) +
+  xlab("") + ylab("") + ylim(0,30000) +
   scale_fill_discrete(name="Cell Line") +
-  ggtitle("10 kb") +
+  scale_y_continuous(limits = c(0,30000),
+                     breaks=c(0,10000,20000,30000),
+                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
+  ggtitle("5 kb") +
   guides(fill=FALSE) +
-  theme(axis.text.x = element_text(size=10),
+  theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1),
      axis.text.y = element_text(size = 15),
@@
 
-b <- ggplot(bounds_df[which(bounds_df$res=="25kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+b <- ggplot(bounds_df[which(bounds_df$res=="10kb"),], aes(x=cl, y=TotBounds, fill=cl))+
   geom_bar(stat="identity", position="dodge")+
@@
   theme_bw()+
-  xlab("") + ylab("") + ylim(0,27000) +
+  xlab("") + ylab("") + ylim(0,30000) +
   scale_fill_discrete(name="Cell Line") +
-  ggtitle("25 kb") +
+  scale_y_continuous(limits = c(0,30000),
+                     breaks=c(0,10000,20000,30000),
+                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
+  ggtitle("10 kb") +
   guides(fill=FALSE) +
-  theme(axis.text.x = element_text(size=10),
+  theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1),
      axis.text.y = element_text(size = 15),
@@
 
-c <- ggplot(bounds_df[which(bounds_df$res=="50kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+c <- ggplot(bounds_df[which(bounds_df$res=="25kb"),], aes(x=cl, y=TotBounds, fill=cl))+
   geom_bar(stat="identity", position="dodge")+
@@
   theme_bw()+
-  xlab("") + ylab("") + ylim(0,27000) +
+  xlab("") + ylab("") + ylim(0,30000) +
   scale_fill_discrete(name="Cell Line") +
-  ggtitle("50 kb") +
+  scale_y_continuous(limits = c(0,30000),
+                     breaks=c(0,10000,20000,30000),
+                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
+  ggtitle("25 kb") +
   guides(fill=FALSE) +
-  theme(axis.text.x = element_text(size=10),
+  theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1),
      axis.text.y = element_text(size = 15),
@@
 
-d <- ggplot(bounds_df[which(bounds_df$res=="100kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+d <- ggplot(bounds_df[which(bounds_df$res=="50kb"),], aes(x=cl, y=TotBounds, fill=cl))+
   geom_bar(stat="identity", position="dodge")+
@@
   theme_bw()+
-  xlab("") + ylab("") + ylim(0,27000) +
+  xlab("") + ylab("") + ylim(0,30000) +
   scale_fill_discrete(name="Cell Line") +
-  ggtitle("100 kb") +
+  scale_y_continuous(limits = c(0,30000),
+                     breaks=c(0,10000,20000,30000),
+                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
+  ggtitle("50 kb") +
   guides(fill=FALSE) +
-  theme(axis.text.x = element_text(size=10),
+  theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1),
      axis.text.y = element_text(size = 15),
@@
 
-figure <- ggarrange(a,b,c,d,
-                    ncol=4,
+e <- ggplot(bounds_df[which(bounds_df$res=="100kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+  geom_bar(stat="identity", position="dodge")+
+  theme_minimal() +
+  theme_bw()+
+  xlab("") + ylab("") + ylim(0,30000) +
+  scale_fill_discrete(name="Cell Line") +
+  scale_y_continuous(limits = c(0,30000),
+                     breaks=c(0,10000,20000,30000),
+                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
+  ggtitle("100 kb") +
+  guides(fill=FALSE) +
+  theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+figure <- ggarrange(a,b,c,d,e,
+                    ncol=5,
                     nrow=1)
@@
 ```
+
+## PI Plots
+
+```{r}
+a <- ggplot(irtab[which(irtab$res=="5kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
+ stat_boxplot(geom ='errorbar', width = 0.2) + 
+ geom_boxplot() +
+ theme_minimal() +
+ theme_bw()+
+ xlab("") + ylab("") + ylim(0,.2) +
+ ggtitle("5 kb") +
+ guides(fill=FALSE) +
+ guides(color=FALSE) +
+ theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+b <- ggplot(irtab[which(irtab$res=="10kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
+ stat_boxplot(geom ='errorbar', width = 0.2) + 
+ geom_boxplot() +
+ theme_minimal() +
+ theme_bw()+
+ xlab("") + ylab("") + ylim(0,.2) +
+ ggtitle("10 kb") +
+ guides(fill=FALSE) +
+ guides(color=FALSE) +
+ theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+c <- ggplot(irtab[which(irtab$res=="25kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
+ stat_boxplot(geom ='errorbar', width = 0.2) + 
+ geom_boxplot() +
+ theme_minimal() +
+ theme_bw()+
+ xlab("") + ylab("") + ylim(0,.2) +
+ ggtitle("25 kb") +
+ guides(fill=FALSE) +
+ guides(color=FALSE) +
+ theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+d <- ggplot(irtab[which(irtab$res=="50kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
+ stat_boxplot(geom ='errorbar', width = 0.2) + 
+ geom_boxplot() +
+ theme_minimal() +
+ theme_bw()+
+ xlab("") + ylab("") + ylim(0,.2) +
+ ggtitle("50 kb") +
+ guides(fill=FALSE) +
+ guides(color=FALSE) +
+ theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+e <- ggplot(irtab[which(irtab$res=="100kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
+ stat_boxplot(geom ='errorbar', width = 0.2) + 
+ geom_boxplot() +
+ theme_minimal() +
+ theme_bw()+
+ xlab("") + ylab("") + ylim(0,.2) +
+ ggtitle("100 kb") +
+ guides(fill=FALSE) +
+ guides(color=FALSE) +
+ theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20))
+
+figure <- ggarrange(a,b,c,d,e,
+                    ncol=5,
+                    nrow=1)
+figure
+annotate_figure(figure,
+    #bottom = text_grob("Cell Line", color = "black", size = 20),
+    left = text_grob("Proportion of Imbalance", color = "black", rot = 90, size=20)
+)
+
+```

### 2019-07-09 Scripts/evaluating_cell_line_specific_validation_performances.Rmd
initial commit

---
title: "Cell Type Specific Validation"
author: "Spiro Stilianoudakis"
date: "July 8, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

# Building optimal models on one cell line and validating on another

## GM12878 on K562

### 10kb

```{r}
mccdata_gm12878_on_k562_10kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs_GM12878_on_K562.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs_GM12878_on_K562.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_gm12878_on_k562_10kb <- rbind(mccdata_gm12878_on_k562_10kb,
			                                      perfdata[15,2])
}

```

### 25kb

```{r}
mccdata_gm12878_on_k562_25kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs_GM12878_on_K562.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs_GM12878_on_K562.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_gm12878_on_k562_25kb <- rbind(mccdata_gm12878_on_k562_25kb,
			                                      perfdata[15,2])
}

```

### 50kb

```{r}
mccdata_gm12878_on_k562_50kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs_GM12878_on_K562.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs_GM12878_on_K562.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_gm12878_on_k562_50kb <- rbind(mccdata_gm12878_on_k562_50kb,
			                                      perfdata[15,2])
}

```

### 100kb

```{r}
mccdata_gm12878_on_k562_100kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs_GM12878_on_K562.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs_GM12878_on_K562.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_gm12878_on_k562_100kb <- rbind(mccdata_gm12878_on_k562_100kb,
			                                      perfdata[15,2])
}

```

## K562 on GM12878

### 10kb

```{r}
mccdata_k562_on_gm12878_10kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs_K562_on_GM12878.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs_K562_on_GM12878.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_k562_on_gm12878_10kb <- rbind(mccdata_k562_on_gm12878_10kb,
			                                      perfdata[15,2])
}

```

### 25kb

```{r}
mccdata_k562_on_gm12878_25kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs_K562_on_GM12878.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs_K562_on_GM12878.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_k562_on_gm12878_25kb <- rbind(mccdata_k562_on_gm12878_25kb,
			                                      perfdata[15,2])
}

```

### 50kb

```{r}
mccdata_k562_on_gm12878_50kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs_K562_on_GM12878.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs_K562_on_GM12878.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_k562_on_gm12878_50kb <- rbind(mccdata_k562_on_gm12878_50kb,
			                                      perfdata[15,2])
}

```

### 100kb

```{r}
mccdata_k562_on_gm12878_100kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs_K562_on_GM12878.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs_K562_on_GM12878.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_k562_on_gm12878_100kb <- rbind(mccdata_k562_on_gm12878_100kb,
			                                      perfdata[15,2])
}

```

## GM12878 on GM12878

### 10kb

```{r}
mccdata_gm12878_on_gm12878_10kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_gm12878_on_gm12878_10kb <- rbind(mccdata_gm12878_on_gm12878_10kb,
			                                      perfdata[15,2])
}

```

### 25kb

```{r}
mccdata_gm12878_on_gm12878_25kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_gm12878_on_gm12878_25kb <- rbind(mccdata_gm12878_on_gm12878_25kb,
			                                      perfdata[15,2])
}

```

### 50kb

```{r}
mccdata_gm12878_on_gm12878_50kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_gm12878_on_gm12878_50kb <- rbind(mccdata_gm12878_on_gm12878_50kb,
			                                      perfdata[15,2])
}

```

### 100kb

```{r}
mccdata_gm12878_on_gm12878_100kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_gm12878_on_gm12878_100kb <- rbind(mccdata_gm12878_on_gm12878_100kb,
			                                      perfdata[15,2])
}

```

## K562 on K562

### 10kb

```{r}
mccdata_k562_on_k562_10kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_k562_on_k562_10kb <- rbind(mccdata_k562_on_k562_10kb,
			                                      perfdata[15,2])
}

```

### 25kb

```{r}
mccdata_k562_on_k562_25kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_k562_on_k562_25kb <- rbind(mccdata_k562_on_k562_25kb,
			                                      perfdata[15,2])
}

```

### 50kb

```{r}
mccdata_k562_on_k562_50kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_k562_on_k562_50kb <- rbind(mccdata_k562_on_k562_50kb,
			                                      perfdata[15,2])
}

```

### 100kb

```{r}
mccdata_k562_on_k562_100kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
			files <- list.files(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/"))
		  if("rfperf_tfbs.rds" %in% files){
		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   i, 
									   "/smote/distance/enet/rfperf_tfbs.rds"))
		  }else{perfdata=data.frame(Metric = c("TN",
                                "FN",
                                "FP",
                                "TP",
                                "Total",
                                "Sensitivity",
                                "Specificity",
                                "Kappa",
                                "Accuracy",
                                "Precision",
                                "FPR",
                                "FNR",
                                "FOR",
                                "NPV",
                                "MCC",
                                "F1",
                                "AUC",
                                "Youden",
                                "AUPRC"), 
                     Performance=NA)}

			mccdata_k562_on_k562_100kb <- rbind(mccdata_k562_on_k562_100kb,
			                                      perfdata[15,2])
}

```

## Plots

```{r}
all_rfperfs_cl_specific_valid <- rbind.data.frame(mccdata_gm12878_on_k562_10kb,
                                                  mccdata_gm12878_on_k562_25kb,
                                                  mccdata_gm12878_on_k562_50kb,
                                                  mccdata_gm12878_on_k562_100kb,
                                                  mccdata_k562_on_gm12878_10kb,
                                                  mccdata_k562_on_gm12878_25kb,
                                                  mccdata_k562_on_gm12878_50kb,
                                                  mccdata_k562_on_gm12878_100kb,
                                                  mccdata_gm12878_on_gm12878_10kb,
                                                  mccdata_gm12878_on_gm12878_25kb,
                                                  mccdata_gm12878_on_gm12878_50kb,
                                                  mccdata_gm12878_on_gm12878_100kb,
                                                  mccdata_k562_on_k562_10kb,
                                                  mccdata_k562_on_k562_25kb,
                                                  mccdata_k562_on_k562_50kb,
                                                  mccdata_k562_on_k562_100kb)

all_rfperfs_cl_specific_valid$Chromosome <- rep(c("CHR1",
                                                  "CHR2",
                                                  "CHR3",
                                                  "CHR4",
                                                  "CHR5",
                                                  "CHR6",
                                                  "CHR7",
                                                  "CHR8",
                                                  "CHR10",
                                                  "CHR11",
                                                  "CHR12",
                                                  "CHR13",
                                                  "CHR14",
                                                  "CHR15",
                                                  "CHR16",
                                                  "CHR17",
                                                  "CHR18",
                                                  "CHR19",
                                                  "CHR20",
                                                  "CHR21",
                                                  "CHR22"),16)
all_rfperfs_cl_specific_valid$Resolution <- rep(c(rep("10 kb", 21),
                                              rep("25 kb", 21),
                                              rep("50 kb", 21),
                                              rep("100 kb", 21)), 4)
all_rfperfs_cl_specific_valid$Validation <- c(rep("GM12878 on K562", 21*4),
                                              rep("K562 on GM12878", 21*4),
                                              rep("GM12878 on GM12878", 21*4),
                                              rep("K562 on K562", 21*4))

all_rfperfs_cl_specific_valid$Validation <- factor(all_rfperfs_cl_specific_valid$Validation, levels = c("GM12878 on GM12878", "K562 on K562", "GM12878 on K562", "K562 on GM12878"))
all_rfperfs_cl_specific_valid$Resolution <- factor(all_rfperfs_cl_specific_valid$Resolution, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs_cl_specific_valid$Chromosome <- factor(all_rfperfs_cl_specific_valid$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_cl_specific_valid_mcc <- all_rfperfs_cl_specific_valid %>%
  dplyr::group_by(Validation, Resolution) %>%
  dplyr::summarise(MCC = mean(V1, na.rm = TRUE),
            MCCSD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_cl_specific_valid_mcc, aes(x=Resolution, y=MCC, group=Validation, fill=Validation)) +
  geom_bar(stat="identity", position = position_dodge()) +
  geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
  theme_minimal() +
  theme_bw()+
  #scale_fill_discrete(name="Cell Line\nSpecific\nValidation")+
  scale_fill_manual(name="Cell Line\nSpecific\nValidation", 
                    values = c("GM12878 on GM12878" = "red", 
                               "K562 on K562" = "blue", 
                               "GM12878 on K562" = "pink",
                               "K562 on GM12878" = "purple")) +
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                  angle = 45, 
                                  #margin = ggplot2::margin(t = 35),
                                  hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  strip.text.x = element_text(size = 15),
  panel.spacing = unit(2, "lines"),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20),
  legend.position = "bottom")
```

### 2019-07-10 Papers.Rmd

@@
 ## TAD predictions
+
+- Mourad, Raphaël, Lang Li, and Olivier Cuvier.
+“Uncovering Direct and Indirect Molecular Determinants of Chromatin Loops Using a Computational Integrative Approach.” Edited by Alexandre V Morozov.
+PLOS Computational Biology 13, no.
+5 (May 23, 2017): e1005538.
+https://doi.org/10.1371/journal.pcbi.1005538.
+- Generalized Linear Model with Interactions (GLMI) to assess TFBSs association with TAD boundaries.
+10 versions, each answers different biological question.
+Log-distance.
+Biases (fragment length, GC, mappability) are explicitly included.
+Comparison with enrichment test, correlation, random forest.
+Outperforms by AUROC.
+Collinearity and its impact, model with all interactions can account for that.
+Poisson lasso to regularize.
+CTCF, RAD21, SMC3, ZNF143, Polycomb proteins, EGR1, ELF1, FOXM1, MAZ, MXI1, NRF1, YY1.
+Repulsion testing, CTCF and EZH2 are repulsive.
+Drosophila and human data. https://cran.r-project.org/web/packages/HiCglmi/index.html
 

### 2019-07-10 Papers.Rmd
Add Mourad 2018 GLM paper addressing blurriness

@@
 ## TAD predictions
+
+- Mourad, Raphaël, and Olivier Cuvier.
+“TAD-Free Analysis of Architectural Proteins and Insulators.” Nucleic Acids Research 46, no.
+5 (March 16, 2018): e27–e27.
+https://doi.org/10.1093/nar/gkx1246.
+- GLM to investigate the association of TFBSs with TAD boundaries.
+Eliminates the blurriness effect of TAD boundaries.
+GLM includes distance between boundaries, interaction frequency, biases (fragment length, GC content, mappability). https://cran.r-project.org/web/packages/HiCblock/index.html
 
@@
 
+- TAD boundaries are blurry - Van Bortle K., Nichols M.H., Li L., Ong C.-T., Takenaka N., Qin Z.S., Corces V.G.
+Insulator function and topological domain border strength scale with architectural protein occupancy.
+
 - Mourad, Raphaël.

### 2019-07-11 Scripts/evaluating_variable_importances.Rmd
added 5kb

@@
 ```{r}
-annots <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878")
+annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/TFBS")
 annots <- gsub(paste(c("Gm12878-", 
@@
                              "-Uchicago.bed"), collapse = "|"), "", annots)
-annots <- annots[!duplicated(annots)]
 ```
@@
 ```{r}
-annots <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/K562")
+annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562/TFBS")
 annots <- gsub(paste(c("K562-", 
@@
 ```{r}
-annots <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
-annots <- annots[grep("Gm12878", annots)]
+annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/BroadHMM")
 annots <- gsub(paste(c("Gm12878-",".bed"), collapse = "|"), "", annots)
@@
 ```{r}
-annots <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
-annots <- annots[grep("K562", annots)]
+annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562/BroadHMM")
 annots <- gsub(paste(c("K562-",".bed"), collapse = "|"), "", annots)
@@
 ```{r}
-annots <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
-annots <- annots[grep("Gm12878", annots)]
+annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/HistoneModifications")
 annots <- gsub(paste(c("Gm12878-",".bed"), collapse = "|"), "", annots)
@@
 ```{r}
-annots <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
-annots <- annots[grep("K562", annots)]
+annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562/HistoneModifications")
 annots <- gsub(paste(c("K562-",".bed"), collapse = "|"), "", annots)

### 2019-07-11 Manuscript/manuscript.Rmd
methods edits
intro edits

@@
 
-The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed the spatial organization of the human genome <!--may affect genomic regulation--> [@lieberman2009comprehensive].
+The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed the spatial organization of the human genome  [@lieberman2009comprehensive].
 Analyses have shown that the genome is folded into distinct compartments termed topologically associating domains (TADs) [@dixon2012topological].
-Given their high degree of conservation between cell types and species, it has been proposed that TADs represent the fundamental building blocks of organization, giving the genome its 3D structure [@rocha2015breaking; @dixon2012topological].
-Likewise, evidence suggests that the boundaries that delineate TADs may play a role in restricting the function of certain genomic elements such as enhancers, thereby impacting the transcription of genes [@symmons2014functional].
-Even more so, loci within a domain have been shown to interact more frequently with one another, exhibiting similar patterns of chromatin modifications, and long-range contact patterns [@rao20143d; @symmons2014functional].
-Furthermore, studies have shown that changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @Flavahan2016; @song2017ctcf].
+Given their high degree of conservation between cell types and species, it has been proposed that TADs represent the fundamental building blocks of organization, giving the genome its 3D structure [@rocha2015breaking].
+Studies have shown that changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @Flavahan2016; @song2017ctcf].
 Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.
+It has been thought that the collection of particular functional genomic elements may contribute to the formation of TADs.
+Namely, the CCCTC-binding factor (CTCF) has been shown to be enriched at TAD boundaries [@ghirlando2016ctcf].
+Additional transcription factors including SMC1, SMC3, and RAD21 have also been shown to colocalize near TAD boundaries [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+Likewise, chromatin has been shown to exhibit certain modifications at TAD boundaries, evidenced by the frequent observation of the H3K36me3 histone mark [@dixon2012topological].
+However, the growing number of publically available annotated genomic elements and there collinearity pose a significant problem for determining the most important epigenomic factors that contribute to TAD boudandary formation.
+
+## PREVIOUS METHODS
 
 Distinct patterns in epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries [@dixon2015chromatin; @di2017novo].
+Currently, classification models have been used to draw associations between these functional annotations and genomic regions that include TAD boundaries.
+
+## PROBLEMS AND LIMITATIONS
+
+## OUR APPROACH
+
+##################
 Recent research has identified key functional genomic annotations enriched at boundaries.
 Namely, the CCCTC-binding factor  (CTCF), has been shown to be associated with TAD boundaries [@ghirlando2016ctcf].
-Other transcription factors including SMC1, SMC3, and RAD21 have been shown to colocalize near TAD boundaries [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+Other transcription factors including SMC1, SMC3, and RAD21 have also been shown to colocalize near TAD boundaries [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
 Together, these components are hypothesized to be what causes loops in the DNA, contributing to higher order chromatin organization.
@@
 
-Current methods used to predict [???
-you never introduced prediction problem] TAD boundaries rely on the use of classification models to draw associations between functional annotations and genomic regions that include TAD boundaries.
+Current methods used to predict TAD boundaries rely on the use of classification models to draw associations between functional annotations and genomic regions that include TAD boundaries.
 However, many key characteristics of 3D genomic data remain unexplored, potentially limiting performance of predictive modeling.
@@
 Lastly, it remains unclear how increased resolution of Hi-C data might affect the performance of predictive models.
+##################
 
@@
 
-<!--
-[Paragraph about disconnect between Hi-C and epigenomic data] Despite the success of Hi-C technologies in revealing the high-order levels of genome organization (chromosome territories, A/B compartments, TADs, sub-TADs, chromatin loops), resolution of Hi-C data (~750kb [???
+<!--[Paragraph about disconnect between Hi-C and epigenomic data]--> 
+Despite the success of Hi-C technologies in revealing the high-order levels of genome organization (chromosome territories, A/B compartments, TADs, sub-TADs, chromatin loops), resolution of Hi-C data (~750kb [???
 REF, Bonev 2017?]) remains well below resolution of epigenomic assays (hundredths of bases for ChIP-seq).
@@
 
-## CLASSIFICATION
+## DEVELOPING FRAMEWORK TO DETERMINE OPTIMAL DATA LEVEL CHARACTERISTICS FOR TAD BOUNDARY PREDICTION
+
+### CLASSIFICATION
 
@@
 Where is it?]
+
+## USING OPTIMALLY BUILD CLASSIFIER TO PREDICT BOUNDARIES AT FINER RESOLUTION
 

### 2019-07-11 Manuscript/manuscript.Rmd
intro edits

@@
 Likewise, chromatin has been shown to exhibit certain modifications at TAD boundaries, evidenced by the frequent observation of the H3K36me3 histone mark [@dixon2012topological].
-However, the growing number of publically available annotated genomic elements and there collinearity pose a significant problem for determining the most important epigenomic factors that contribute to TAD boudandary formation.
-
-## PREVIOUS METHODS
-
-Distinct patterns in epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries [@dixon2015chromatin; @di2017novo].
-Currently, classification models have been used to draw associations between these functional annotations and genomic regions that include TAD boundaries.
+However, the growing number of publically available annotated genomic elements and there collinearity pose a significant problem for establishing methods robust enough to determine the most important epigenomic factors that contribute to TAD boudandary formation.
 
@@
 
-## OUR APPROACH
+The distinct patterns in epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches toward TAD boundary prediction  <!--[@dixon2015chromatin; @di2017novo]-->.
+Currently, classification models have been used to draw associations between these functional annotations and genomic regions that include TAD boundaries.
+However, many key characteristics of 3D genomic data remain unexplored, potentially limiting the performance of predictive modeling.
 
-##################
-Recent research has identified key functional genomic annotations enriched at boundaries.
-Namely, the CCCTC-binding factor  (CTCF), has been shown to be associated with TAD boundaries [@ghirlando2016ctcf].
-Other transcription factors including SMC1, SMC3, and RAD21 have also been shown to colocalize near TAD boundaries [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
-Together, these components are hypothesized to be what causes loops in the DNA, contributing to higher order chromatin organization.
-Additional binding proteins, known to mediate enhancer-promoter interactions including YY1 and ZNF143, have been shown to influence the delineation of topological domains [@weintraub2017yy1; @gonzalez2017znf143; @heidari2014genome].
-<!--However, there is a growing number of publically available annotated genomic features, and it is unclear if current methods are robust enough to identify all of them.
-[???
-This is very weak and undefined.
-You started with mentioning prediction - finish with unsolved problems with it.
-!!!editted]--> [???
-What's the summary/conclusion/problem?]
+First, the use of different levels of association between TAD boundary regions and genomic features as predictors remain underexplored.
+Counts of overlaps (**overlap count**, OC) is the most commonly used type of association as it simply counts the total number of peaks defining a genomic annotation that are inside a given TAD boundary region.
+Percents of overlaps (**overlap percent**, OP) represents a more precise measure of association as it considers the proportion of overlap betwee a genomic annotation and a boundary region.
+However, the distance between boundary regions and genomic annotations are currently unexplored.
+This association allows for quantifying the spatial relationship between genomic elements and boundary regions.
+We hypothesize that the inclusion of this type of association will correspond with more accurate identification of functional genomic elements association with TAD boundary formation.
 
-Current methods used to predict TAD boundaries rely on the use of classification models to draw associations between functional annotations and genomic regions that include TAD boundaries.
-However, many key characteristics of 3D genomic data remain unexplored, potentially limiting performance of predictive modeling.
-Specifically, the minority of TAD boundaries as compared with the rest of the genome creates proportionally small TAD boundary regions versus non-TAD boundary regions.
-These TAD boundary regions make up the minority class, while the non-TAD boundary regions make up the remaining majority class.
+Second, the minority of TAD boundaries as compared with the rest of the genome creates proportionally small TAD boundary regions versus non-TAD boundary regions.
+These boundary regions make up the minority class, while the non-boundary regions make up the remaining majority class.
 The large disparity is sizes between minority and majority classes creates imbalanced data, as can be characterized by the *proportion of imbalance* (PI).
-Here, PI is defined as the ratio of the set minority class observations to the sum of both sets of minority and majority class observations.
-A dataset is considered imbalanced if PI<0.5.
-[???
-Not really.
-Poor metric choice.] <!--Specifically, the minority of TAD boundaries as compared with the rest of the genome creates heavily imbalanced classes, characterized by ratios of positive/negative classes used to train the models.
-Here, the imbalance ratio is defined as the ratio of majority classes (regions not including TAD boundaries) to minority classes (regions including TAD boundaries) [@Orriols-Puig2008].--> Classifiers implemented on heavily imbalanced datasets are known to exhibit poor performances as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
-Furthermore, the use of different levels of association between TAD boundaries and genomic features (number, or proportion of overlaps, or distance) as predictors remain underexplored.
-Lastly, it remains unclear how increased resolution of Hi-C data might affect the performance of predictive models.
-##################
+Here, PI is defined as twice the ratio of the set minority class observations to the sum of both sets of minority and majority class observations.
+That is, the PI is bounded by 0 and 1.
+A dataset is considered balanced if PI$\approx$1, and imbalanced if PI$<<$1.
+Classifiers implemented on heavily imbalanced datasets are known to exhibit poor performances as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
+We hypothesize that the implementation of novel data resampling techniques will significantly improve model performance.
+Futhermore, the choice of performance metric can mask the poor performance of models implemented on imbalanced data.
+It has been shown that conventional metrics such as AUC and accuracy are insensitive to class imbalance, creating artificially inflated values influenced by the majority class [@prati2011survey; @wei2013role].
+Therefore, we hypothesize that a more composite metric such as Matthews Correlation Coefficient (MCC), might provide more sensitive assessment of model performance, given that it penalizes for both false positives and false negatives.
 
-Recently, an L1-regularized multiple logistic regression model, called *HiCfeat*, was developed to predict TAD boundaries using transcription factor binding sites on GM12878 [@mourad2016computational].
-Based on a 1 kb binned genomic data matrix and 20 kb flanked TAD boundaries, the model was trained using proportions of overlaps between ChiP-seq peak defined functional element coordinates and genomic bins.
-However, several problems exist with this study.
-First, many transcription factors are known to colocalize, and therefore exhibit high correlations.
-Given a group of features that are highly correlated, L1-regularization tends to pick only one of them, while shrinking the others to zero [@zou2005regularization].
-Here, ensemble learning techniques could offer a more robust method toward identifying  annotations associated with TAD boudaries.
-Likewise, it is unclear how other sets of epigenomic features affect prediction, including chromatin state segmentations and histone modifications.
-Secondly, the class imbalance issue was not addressed prior to modelling.
-Instead, model performance was evaluated using ROC (receiver operating characteristic) curves and subsequent AUC (area under the curve).
-It has been shown that AUC is insensitive to class imbalance, creating artificially inflated values inlfuenced by the majority class [@prati2011survey; @wei2013role].
-It is unclear how simple data level solutions to class imbalance, such random under-sampling and random over-sampling affect TAD boundary prediction.
-Likewise, a more composite metric such as Matthews Correlation Coefficient (MCC), might provide more sensitive assessment of model performance.
-Thirdly, the relationship between annotations and boundaries was quantified using proportions of overlaps.
-This type of predictor ignores distances, which offers a much more spatially descriptive feature space and could improve predictive performance.
-Lastly, it is unclear how *HiCfeat* would perform on other cell lines and Hi-C data resolutions, giving *HiCfeat* a limited application in TAD boundary prediction.
-
-<!--[Paragraph about disconnect between Hi-C and epigenomic data]--> 
+Thirdly, TAD boundary location is known to be heavily influenced by the resolution of the subsequent Hi-C interaction matrix [@sexton2012three].
+Higher resolutions require a larger number of mapped reads, thereby creating larger data matrices, increasing computation time.
+However, the increased resolution available in newer datasets has highlighted the existence of a hierarchical structure of TADs inside other TADs [@pal2019hi].
+It is unclear how varying levels of resolution affect the association between functional genomic annotations and TAD boundary regions.
+<!--[link these two paragraphs]-->
+<!--[Paragraph about disconnect between Hi-C and epigenomic data] 
 Despite the success of Hi-C technologies in revealing the high-order levels of genome organization (chromosome territories, A/B compartments, TADs, sub-TADs, chromatin loops), resolution of Hi-C data (~750kb [???
@@
 One aim of this study is to predict the location of TAD boundaries on a scale comparable to epigenomic assays.
-For this, we developed a model trained on a relatively coarse Hi-C data for predicting 3D features (TAD boundaries) from 1D data (epigenomic datasets).
+For this, we developed a model trained on a relatively coarse Hi-C data for predicting 3D features (TAD boundaries) from 1D data (epigenomic datasets).-->
+
+## PREVIOUS METHODS
+
+Recently, an L1-regularized multiple logistic regression model, called *HiCfeat*, was developed to predict TAD boundary regions using a collection of 69 transcription factor binding sites on the GM12878 cell line [@mourad2016computational].
+
+Another method used an L2-based regularized linear model to discriminate between what was termed as "boundary-" and "TAD-segments" of the hESC cell line [@hong2017computational].
+
+A method devolped in 2015 used a tree based model to predict TAD boundary regions using 9 different cell line specific histone modifications, as well as consensus CTCF peaks, across 8 cell lines [@huang2015predicting].
+
+## OUR APPROACH
 

### 2019-07-12 Manuscript/manuscript.Rmd
intro edits

@@
 However, the growing number of publically available annotated genomic elements and there collinearity pose a significant problem for establishing methods robust enough to determine the most important epigenomic factors that contribute to TAD boudandary formation.
+Moreover, the plasticity of functional annotations make TAD boundary prediction a cell line specific problem [@wang2012widespread]
 
@@
 First, the use of different levels of association between TAD boundary regions and genomic features as predictors remain underexplored.
+These associations are termed predictor-types and make up the feature space of classifiers.
 Counts of overlaps (**overlap count**, OC) is the most commonly used type of association as it simply counts the total number of peaks defining a genomic annotation that are inside a given TAD boundary region.
@@
 
-Second, the minority of TAD boundaries as compared with the rest of the genome creates proportionally small TAD boundary regions versus non-TAD boundary regions.
+Secondly, the minority of TAD boundaries as compared with the rest of the genome creates proportionally small TAD boundary regions versus non-TAD boundary regions.
 These boundary regions make up the minority class, while the non-boundary regions make up the remaining majority class.
@@
 That is, the PI is bounded by 0 and 1.
-A dataset is considered balanced if PI$\approx$1, and imbalanced if PI$<<$1.
+A dataset is considered balanced if PI $\approx$ 1, and imbalanced if PI$<<$1.
 Classifiers implemented on heavily imbalanced datasets are known to exhibit poor performances as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
@@
 
+<!--[still revising]-->
 Recently, an L1-regularized multiple logistic regression model, called *HiCfeat*, was developed to predict TAD boundary regions using a collection of 69 transcription factor binding sites on the GM12878 cell line [@mourad2016computational].
@@
 
-In this study, we developed a computational framework aimed at determining the optimal set of data level characteristics necessary for optimal prediction of TAD boundaries and identification of influential genomic annotations.
-We utilize random forest classification models built on HiC-data from two cell lines, including GM12878 and K562, obtained at four different resolutions, including 10 kb, 25 kb, 50 kb, and 100 kb.
-For each cell line and resolution, we compared three feature engineering techniques, including counts, percents, and distances.
+In this study, we have developed a computational framework aimed at determining the optimal set of data level characteristics necessary for optimal prediction of TAD boundaries and identification of influential genomic annotations.
+These include the best combination of predictor type, resampling technique, and data resolution.
+We utilize random forest classification models built on Hi-C data from two cell lines, including GM12878 and K562, obtained at four different resolutions, including 10 kb, 25 kb, 50 kb, and 100 kb.
+For each cell line and resolution, we compared three predictor types, including counts, percents, and distances.
 Additionally, we compared three re-sampling techniques, including random under-sampling, random over-sampling, and a weighted combination of both referred to as Synthetic Minority Over-sampling Technique (SMOTE).
 Model performances were evaluated and compared using Matthews Correlation Coefficient (MCC).
-
-[???Include concluding paragraph]
+We performed 10-fold cross-validation for parameter tuning and to guard against over-fitting.
+We found that the optimally built cell line specific model is one implemented using distance type predictors, with SMOTE resampling, at the 10-kb data resolution.
+We also determined that simply including transcription factor binding sites was necessary for optimal performance.
+The inclusion of chromatin states and histone modifications was found to induce noise into the model.
+Specifically, we found that the transcription factors CTCF, ZNF143, RAD21, and SMC3 exhibited high predictive importances, confirming there involvement in TAD boundary formation.
+We then aimed to evaluate the cell line specificity of TAD boundaries by validating our optimally built models across cell lines.
+We found that models built and validated on the same cell line outperformed models that were validated across cell lines, confirming the cell line specific nature and plasticity of TAD boundaries and functional genomic annotations respectively.
+<!--[add conclusion from results of predicting finer bins]-->
 

### 2019-07-12 Manuscript/manuscript.Rmd
methods edits

@@
 
-Class imbalance was characterized by each dataset's *proportion of imbalance* (PI), [???
-Why?
-It is bounded [0, 0.5], never seen it is used.] defined as the ratio of minority class observations to the sum of minority and majority class observations:
+Class imbalance was characterized by each dataset's *proportion of imbalance* (PI) defined as the ratio of minority class observations to the sum of minority and majority class observations:
 
-$$PI = \dfrac{C_{min}}{C_{min} + C_{maj}}$$
+$$PI = 2\dfrac{C_{min}}{C_{min} + C_{maj}}$$
 
-where $C_{min}$ denotes the complementary set of genomic bins that did overlap with a flanked TAD boundary and $C_{maj}$ denotes the set of genomic bins that did not overlap with a flanked TAD boundary.
-In order to assess the influence of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling).
-They are described in detail below.
+where $C_{min}$ denotes the set of genomic bins that overlap with a flanked TAD boundary and $C_{maj}$ denotes the complementary set of genomic bins that did not overlap with a flanked TAD boundary.
+Here, PI is bounded by 0 and 1, with heavily imbalanced classes approaching 0.
+
+In order to assess the influence of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling). They are described in detail below.
 

### 2019-07-12 Manuscript/manuscript.Rmd
results edits

@@
 These include the best combination of predictor type, resampling technique, and data resolution.
-We utilize random forest classification models built on Hi-C data from two cell lines, including GM12878 and K562, obtained at four different resolutions, including 10 kb, 25 kb, 50 kb, and 100 kb.
+We utilize random forest classification models built on Hi-C data from two cell lines, including GM12878 and K562, obtained at four different resolutions, including 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
 For each cell line and resolution, we compared three predictor types, including counts, percents, and distances.
@@
 
-## USING OPTIMALLY BUILD CLASSIFIER TO PREDICT BOUNDARIES AT FINER RESOLUTION
+## USING OPTIMALLY BUILT CLASSIFIER TO PREDICT BOUNDARIES AT FINER RESOLUTION
 
@@
 We analyzed publically available replicate Hi-C data sets from two cell lines including GM12878 and K562 (Supplementary Table 1).
-Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at four resolutions: 10 kb, 25 kb, 50 kb, and 100 kb.
+Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at four resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
 To account for the varying levels of data resolution, we developed a resolution-specific approach toward constructing TAD versus non TAD boundary regions on the linear genome, labeled as a response vector **Y** (Figure 1).
@@
 Between the two cell lines, a significant number of TAD boundary regions were found to be specific to one of the two cell lines (Figure 2B).
-It was found that 45%, 38%, 37%, and 36% of TAD boundary regions were specific to the GM12878 cell line, across each resolution [???
-spell out resolutions exactly.] respectively.
-Similarly, for K562, it was found that 27%, 27%, 29%, and 33% of TAD boundary regions were cell line specific for each resolution specifically.
-This indicates a necessity for computationally specific models [???
-Do not understand] in predicting TAD boundary formations.
+It was found that X%, 45%, 38%, 37%, and 36% of TAD boundary regions were specific to the GM12878 cell line, while X%, 27%, 27%, 29%, and 33% of TAD boundary regions were specific to the K562 cell line across each of the 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions respectively.
+Given the plasticity in boundary location, we opted to build cell line specific models for predicting TAD boundary regions.
 
@@
 We then investigated the proportional class imbalance (PI) featured at each resolution and among each cell line.
-The PI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions.
+The PI was defined as twice the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions.
 The proportional imbalance was found to be invariant to resolution, remaining consistently low for both cell lines, with very little variability between chromosomes (Figure 3C).
 Such low proportions of imbalance gave precedence for the implementation of re-sampling prior to classification.
-[???
-It is low because the upper bound is 0.5.
-It is an unconventional measure.]
 
@@
 
-A total of 107 and 152 cell type specific functional genomic annotations derived from ChIP-Seq experiments (See Methods) for the GM12878 and K562 cell line, respectively.
-[???
-Is that so?
-How many are common?] To establish the feature space used for classification, we constructed three different predictor types for each functional genomic annotation.
-Counts of overlaps (**overlap count**, OC) is the most commonly used type of association between genomic elements (Figure 3A).
-Percents of overlaps (**overlap percent**, OP) represents a more precise measure of association as it considers the proportion of a bin overlapped by a genomic annotation (Figure 3B).
-**Distance** between the centers of bins and genomic annotations quantifying the spatial relationship between genomic elements is currently unexplored (Figure 3C).
-Log2-transformation of distance was used to account for the skewness present in the distributions of distances (Supplementary Figures 1-2).
-These types of genomic associations provide a granular way to investigate classifier performance in class imbalance settings.
+A total of 78 cell type specific functional genomic annotations derived from ChIP-Seq experiments (See Methods) for the GM12878 and K562 cell line were used to build the feature space of downstream predictive models.
+We constructed three different predictor types for each functional genomic annotation.
+Counts of overlaps (**overlap count**, OC) were defined as the total number of peak regions that overlapped within a given genomic bin (Figure 3A).
+Percents of overlaps (**overlap percent**, OP) were defined as the proportion of a bin overlapped by a peak region (Figure 3B).
+**Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations (Figure 3C).
+A log2-transformation of distance was used to account for the skewness present in the distributions of distances (Supplementary Figures 1-2).
+Each predictor type provides a granular way to draw associations between functional genomic annotations and the spatial structure of the genome.
 

### 2019-07-12 Scripts/evaluating_imbalance_ratios.Rmd
adding 5 kb results

@@
 
-      pi.per.chr <- rbind(pi.per.chr, table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2]/sum(table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)))
+      pi.per.chr <- rbind(pi.per.chr, 2*(table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2]/sum(table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y))))
 
@@
  theme_bw()+
- xlab("") + ylab("") + ylim(0,.2) +
+ xlab("") + ylab("") + ylim(0,1) +
  ggtitle("5 kb") +
@@
  theme_bw()+
- xlab("") + ylab("") + ylim(0,.2) +
+ xlab("") + ylab("") + ylim(0,1) +
  ggtitle("10 kb") +
@@
  theme_bw()+
- xlab("") + ylab("") + ylim(0,.2) +
+ xlab("") + ylab("") + ylim(0,1) +
  ggtitle("25 kb") +
@@
  theme_bw()+
- xlab("") + ylab("") + ylim(0,.2) +
+ xlab("") + ylab("") + ylim(0,1) +
  ggtitle("50 kb") +
@@
  theme_bw()+
- xlab("") + ylab("") + ylim(0,.2) +
+ xlab("") + ylab("") + ylim(0,1) +
  ggtitle("100 kb") +

### 2019-07-12 Scripts/evaluating_model_performances_rf.Rmd
adding 5 kb results

--- 2019-06-05 Scripts/evaluating_model_performances.Rmd
@@
 # GM12878
+
+##5kb
+
+```{r}
+mccdata_gm12878_5kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("rfperf_noenet.rds" %in% files){
+		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/rfperf_noenet.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
+
+			mccdata_gm12878_5kb <- rbind(mccdata_gm12878_5kb,
+										  perfdata[15,2])
+		}
+	}
+}
+
+```
 
@@
 
+##5kb
+
+```{r}
+mccdata_K562_5kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("none","ros","rus","smote")){
+		for(k in c("distance", "oc", "op")){
+		  files <- list.files(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet"))
+		  if("rfperf_noenet.rds" %in% files){
+		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+									   i, 
+									   "/",
+									   j, 
+									   "/", 
+									   k, 
+									   "/enet/rfperf_noenet.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
+
+		  mccdata_K562_5kb <- rbind(mccdata_K562_5kb,
+										  perfdata[15,2])
+
+		}
+	}
+}
+
+```
+
 ##10kb
@@
 
-## Plots
+# Line Plots V1
 
 ```{r}
-all_rfperfs <- rbind.data.frame(mccdata_gm12878_10kb,
+all_rfperfs <- rbind.data.frame(mccdata_gm12878_5kb,
+                                mccdata_gm12878_10kb,
                                 mccdata_gm12878_25kb,
@@
                                 mccdata_gm12878_100kb,
+                                mccdata_K562_5kb,
                                 mccdata_K562_10kb,
@@
                                 mccdata_K562_100kb)
-all_rfperfs$CL <- c(rep("GM12878", length(mccdata_gm12878_10kb)*4), rep("K562", length(mccdata_K562_10kb)*4))
-all_rfperfs$Resolution <- rep(c(rep("10 kb", 252),
-                            rep("25 kb", 252),
-                            rep("50 kb", 252),
-                            rep("100 kb", 252)))
+all_rfperfs$CL <- c(rep("GM12878", length(mccdata_gm12878_10kb)*5), rep("K562", length(mccdata_K562_10kb)*5))
+all_rfperfs$Resolution <- rep(c(rep("5 kb", length(mccdata_gm12878_5kb)),
+                            rep("10 kb", length(mccdata_gm12878_10kb)),
+                            rep("25 kb", length(mccdata_gm12878_25kb)),
+                            rep("50 kb", length(mccdata_gm12878_50kb)),
+                            rep("100 kb", length(mccdata_gm12878_100kb))), 2)
 all_rfperfs$Resampling <- rep(c(rep("None", 3),
@@
                             rep("RUS", 3),
-                            rep("SMOTE", 3)),168)
-all_rfperfs$Predictor <- rep(c("Distance", "OC", "OP"), 672)
+                            rep("SMOTE", 3)),210)
+all_rfperfs$Predictor <- rep(c("Distance", "OC", "OP"), 840)
 all_rfperfs$Chromosome <- c(rep("CHR1", 12),
@@
 all_rfperfs$CL <- factor(all_rfperfs$CL, levels = c("GM12878", "K562"))
-all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
+all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
 all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
@@
 ```
+
+# Line Plots V2
+
+```{r}
+x <- ggplot(all_rfperfs_mcc, aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
+     geom_line(size=2, position=position_dodge(0.5))+
+     geom_point(size=5, position=position_dodge(0.5))+
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+                 position=position_dodge(0.5)) +
+     facet_grid(CL ~ Predictor)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("Resolution") + ylab("MCC") + ylim(-.1,.5) +
+     scale_color_discrete(name="Resampling Technique")+
+     guides(shape=FALSE, linetype=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     strip.text.x = element_text(size = 15),
+     strip.text.y = element_text(size = 15),
+     panel.spacing = unit(2, "lines"),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20),
+     legend.position="bottom")
+
+#figure <- ggarrange(x,
+#                ncol = 1, nrow = 1, 
+#                common.legend = TRUE, 
+#                legend = "bottom")
+#figure
+#annotate_figure(figure,
+#    bottom = text_grob("Resolution", color = "black", size = 20),
+#    left = text_grob("MCC", color = "black", rot = 90, size=20)
+#)
+
+```

### 2019-07-12 Manuscript/manuscript.Rmd
results edits

@@
 (B) Venn diagrams showing that TAD boundary regions exhibit cell-line specificity across resolution.
-(C) Boxplots indicating that the proportion of class imbalance remained severe irrespective of resolution.](Figures/bounds_and_pis.png)
+(C) Boxplots indicating that the proportion of class imbalance remained severe irrespective of resolution.](Figures/bounds_and_pis_v2.png)
 
@@
 Each system in the framework was assumed to be composed of a random forest classifier constructed from a particular cell line ($L = \{GM12878, K562\}$).
-Within each cell line we evaluated 4 data resolutions ($R = \{10 kb, 25 kb, 50 kb, 100 kb\}$).
+Within each cell line we evaluated 5 data resolutions ($R = \{5 kb, 10 kb, 25 kb, 50 kb, 100 kb\}$).
 We then considered 3 separate predictor types as the feature space ($P = \{OC, OP, Distance\}$).
@@
 Letting $|X|$ denote the cardinality [???
-TBD] of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling 2016 ($2 \times 4 \times 3 \times 4 \times 21$) separate models.
+TBD] of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling 2520 ($2 \times 5 \times 3 \times 4 \times 21$) separate models.
 For each combination of inputs, we performed 10-fold cross-validation to tune for the number of features to consider at each node of the random forest classifier.
-Each optimally tuned model was then validated on the same separate testing set for unbiased comparisons.
+Each optimally tuned model was then validated on the same separate cell line specific testing set for unbiased comparisons.
 Performances were evaluated using MCCs and aggregated across each chromosome by averaging.
@@
 
-## MODEL PERFORMANCE DECREASED AS Hi-C DATA RESOLUTION DECREASED
+## MODEL PERFORMANCE PEAKED AT 10 KB AND DECREASED AS Hi-C DATA RESOLUTION DECREASED
 
@@
 Within each cell line, predictor type, and resolution, chromosome-specific training data was re-sampled using different techniques including no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and *Synthetic Minority Over Sampling TEchnique* (SMOTE; purple).
-Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/model_performances_v2.png)
+Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/model_performances_v3.png)
 
@@
 After determining the optimal set of data level characteristics, we then aimed to compare the performances of annotation-specifc models [???
-Never defined, what is this?], within each cell line and across resolution.
+Never defined, what is this?; !!!defined above; should i mention again?], within each cell line and across resolution.
 In doing so, we inspected the proportion of predictive importance that was explained by each of the 3 groups of annotations (chromatin states, histone modifications, and transcription factor binding sites).

### 2019-07-12 Scripts/comparing_tfbs_specific_models_with_all_annotations.Rmd
added 5kb results

@@
 
+## 5kb
+
+```{r}
+mccdata_gm12878_5kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("chromstates", "histones", "tfbs", "all")){
+	  if(j %in% c("chromstates", "histones", "tfbs")){
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_",
+									   j, 
+									   ".rds"))
+	  }else{
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_noenet.rds"))
+	  }
+
+			mccdata_gm12878_5kb <- rbind(mccdata_gm12878_5kb,
+										  perfdata[15,2])
+
+	}
+}
+
+```
+
 ## 10kb
@@
 									   i, 
-									   "/smote/distance/enet/rfperf.rds"))
+									   "/smote/distance/enet/rfperf_noenet.rds"))
 	  }
@@
 # K562; smote; distance types
+
+## 5kb
+
+```{r}
+mccdata_K562_5kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+	for(j in c("chromstates", "histones", "tfbs", "all")){
+	  if(j %in% c("chromstates", "histones", "tfbs")){
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_",
+									   j, 
+									   ".rds"))
+	  }else{
+	    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_noenet.rds"))
+	  }
+
+			mccdata_K562_5kb <- rbind(mccdata_K562_5kb,
+										  perfdata[15,2])
+
+	}
+}
+
+```
 
@@
 ```{r}
-all_rfperfs <- rbind.data.frame(mccdata_gm12878_10kb,
+all_rfperfs <- rbind.data.frame(mccdata_gm12878_5kb,
+                                mccdata_gm12878_10kb,
                                 mccdata_gm12878_25kb,
@@
                                 mccdata_K562_100kb)
-all_rfperfs$CL <- c(rep("GM12878", length(mccdata_gm12878_10kb)*4), rep("K562", length(mccdata_K562_10kb)*4))
-all_rfperfs$Resolution <- rep(c(rep("10 kb", 84),
-                            rep("25 kb", 84),
-                            rep("50 kb", 84),
-                            rep("100 kb", 84)))
-all_rfperfs$Annotation <- rep(c("CSS","HM","TFBS","Combined"),168)
+all_rfperfs$CL <- c(rep("GM12878", length(mccdata_gm12878_5kb)*5), rep("K562", length(mccdata_K562_5kb)*5))
+all_rfperfs$Resolution <- c(rep("5 kb", length(mccdata_gm12878_5kb)),
+                            rep("10 kb", length(mccdata_gm12878_10kb)),
+                            rep("25 kb", length(mccdata_gm12878_25kb)),
+                            rep("50 kb", length(mccdata_gm12878_50kb)),
+                            rep("100 kb", length(mccdata_gm12878_100kb)))
+all_rfperfs$Annotation <- rep(c("CSS","HM","TFBS","Combined"),210)
 all_rfperfs$Chromosome <- rep(c(rep("CHR1", 4),
@@
                             rep("CHR21", 4),
-                            rep("CHR22", 4)),8)
+                            rep("CHR22", 4)),10)
 
 all_rfperfs$CL <- factor(all_rfperfs$CL, levels = c("GM12878", "K562"))
-all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
+all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
 all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "CSS", "TFBS", "Combined"))

### 2019-07-12 Scripts/evaluating_cell_line_specific_validation_performances.Rmd
added 5kb results

@@
 ## GM12878 on K562
+
+### 5kb
+
+```{r}
+mccdata_gm12878_on_k562_5kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/"))
+		  if("rfperf_tfbs_GM12878_on_K562.rds" %in% files){
+		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_tfbs_GM12878_on_K562.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
+
+			mccdata_gm12878_on_k562_5kb <- rbind(mccdata_gm12878_on_k562_5kb,
+			                                      perfdata[15,2])
+}
+
+```
 
@@
 
+### 5kb
+
+```{r}
+mccdata_k562_on_gm12878_5kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+			files <- list.files(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/"))
+		  if("rfperf_tfbs_K562_on_GM12878.rds" %in% files){
+		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_tfbs_K562_on_GM12878.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
+
+			mccdata_k562_on_gm12878_5kb <- rbind(mccdata_k562_on_gm12878_5kb,
+			                                      perfdata[15,2])
+}
+
+```
+
 ### 10kb
@@
 
+### 5kb
+
+```{r}
+mccdata_gm12878_on_gm12878_5kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+			files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/"))
+		  if("rfperf_tfbs.rds" %in% files){
+		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_tfbs.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
+
+			mccdata_gm12878_on_gm12878_5kb <- rbind(mccdata_gm12878_on_gm12878_5kb,
+			                                      perfdata[15,2])
+}
+
+```
+
 ### 10kb
@@
 ## K562 on K562
+
+### 5kb
+
+```{r}
+mccdata_k562_on_k562_5kb <- numeric()
+
+for(i in paste0("CHR", c(1:8,10:22))){
+			files <- list.files(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/"))
+		  if("rfperf_tfbs.rds" %in% files){
+		    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+									   i, 
+									   "/smote/distance/enet/rfperf_tfbs.rds"))
+		  }else{perfdata=data.frame(Metric = c("TN",
+                                "FN",
+                                "FP",
+                                "TP",
+                                "Total",
+                                "Sensitivity",
+                                "Specificity",
+                                "Kappa",
+                                "Accuracy",
+                                "Precision",
+                                "FPR",
+                                "FNR",
+                                "FOR",
+                                "NPV",
+                                "MCC",
+                                "F1",
+                                "AUC",
+                                "Youden",
+                                "AUPRC"), 
+                     Performance=NA)}
+
+			mccdata_k562_on_k562_5kb <- rbind(mccdata_k562_on_k562_5kb,
+			                                      perfdata[15,2])
+}
+
+```
 
@@
 ```{r}
-all_rfperfs_cl_specific_valid <- rbind.data.frame(mccdata_gm12878_on_k562_10kb,
+all_rfperfs_cl_specific_valid <- rbind.data.frame(mccdata_gm12878_on_k562_5kb,
+                                                  mccdata_gm12878_on_k562_10kb,
                                                   mccdata_gm12878_on_k562_25kb,
@@
                                                   mccdata_gm12878_on_k562_100kb,
+                                                  mccdata_k562_on_gm12878_5kb,
                                                   mccdata_k562_on_gm12878_10kb,
@@
                                                   mccdata_k562_on_gm12878_100kb,
+                                                  mccdata_gm12878_on_gm12878_5kb,
                                                   mccdata_gm12878_on_gm12878_10kb,
@@
                                                   mccdata_gm12878_on_gm12878_100kb,
+                                                  mccdata_k562_on_k562_5kb,
                                                   mccdata_k562_on_k562_10kb,
@@
                                                   "CHR21",
-                                                  "CHR22"),16)
-all_rfperfs_cl_specific_valid$Resolution <- rep(c(rep("10 kb", 21),
+                                                  "CHR22"),20)
+all_rfperfs_cl_specific_valid$Resolution <- rep(c(rep("5 kb", 21),
+                                              rep("10 kb", 21),
                                               rep("25 kb", 21),
@@
                                               rep("100 kb", 21)), 4)
-all_rfperfs_cl_specific_valid$Validation <- c(rep("GM12878 on K562", 21*4),
-                                              rep("K562 on GM12878", 21*4),
-                                              rep("GM12878 on GM12878", 21*4),
-                                              rep("K562 on K562", 21*4))
+all_rfperfs_cl_specific_valid$Validation <- c(rep("GM12878 on K562", 21*5),
+                                              rep("K562 on GM12878", 21*5),
+                                              rep("GM12878 on GM12878", 21*5),
+                                              rep("K562 on K562", 21*5))
 
 all_rfperfs_cl_specific_valid$Validation <- factor(all_rfperfs_cl_specific_valid$Validation, levels = c("GM12878 on GM12878", "K562 on K562", "GM12878 on K562", "K562 on GM12878"))
-all_rfperfs_cl_specific_valid$Resolution <- factor(all_rfperfs_cl_specific_valid$Resolution, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
+all_rfperfs_cl_specific_valid$Resolution <- factor(all_rfperfs_cl_specific_valid$Resolution, levels = c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
 all_rfperfs_cl_specific_valid$Chromosome <- factor(all_rfperfs_cl_specific_valid$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

### 2019-07-12 Scripts/evaluating_variable_importances.Rmd
added 5kb results

@@
 
+###5kb
+
+```{r}
+varimp_gm12878_5kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_5kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+									   chrs[i], 
+									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_5kb <- data.frame(Feature = rownames(varimp_gm12878_5kb),
+                                  aveimp5kb = rowMeans(varimp_gm12878_5kb, na.rm = TRUE),
+                                  sdimp5kb = apply(varimp_gm12878_5kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_5kb) <- NULL
+```
+
 ###10kb
@@
 
+###5kb
+
+```{r}
+varimp_K562_5kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_5kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+									   chrs[i], 
+									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_5kb <- data.frame(Feature = rownames(varimp_K562_5kb),
+                                  aveimp5kb = rowMeans(varimp_K562_5kb, na.rm = TRUE),
+                                  sdimp5kb = apply(varimp_K562_5kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_5kb) <- NULL
+```
+
 ###10kb
@@
 #GM12878
-all_varimps_gm12878_tfbs <- cbind.data.frame(varimp_gm12878_10kb$Feature,
+all_varimps_gm12878_tfbs <- cbind.data.frame(varimp_gm12878_5kb$Feature,
+                                        varimp_gm12878_5kb$aveimp5kb,
                                         varimp_gm12878_10kb$aveimp10kb,
@@
                                         varimp_gm12878_100kb$aveimp100kb)
-names(all_varimps_gm12878_tfbs) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+names(all_varimps_gm12878_tfbs) <- c("Feature", "ave10kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
 all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[order(rowMeans(all_varimps_gm12878_tfbs[,-1]), decreasing = TRUE),]
@@
                       name="Predictive\nImportance") +
-  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
+  scale_x_discrete(labels=c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))+
   theme_bw() +
@@
 #K562
-all_varimps_K562_tfbs <- cbind.data.frame(varimp_K562_10kb$Feature,
+all_varimps_K562_tfbs <- cbind.data.frame(varimp_K562_5kb$Feature,
+                                        varimp_K562_5kb$aveimp5kb,
                                         varimp_K562_10kb$aveimp10kb,
@@
                                         varimp_K562_100kb$aveimp100kb)
-names(all_varimps_K562_tfbs) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+names(all_varimps_K562_tfbs) <- c("Feature", "ave5kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
 all_varimps_K562_tfbs <- all_varimps_K562_tfbs[order(rowMeans(all_varimps_K562_tfbs[,-1]), decreasing = TRUE),]
@@
 
+###5kb
+
+```{r}
+varimp_gm12878_5kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_5kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_5kb <- data.frame(Feature = rownames(varimp_gm12878_5kb),
+                                  aveimp5kb = rowMeans(varimp_gm12878_5kb, na.rm = TRUE),
+                                  sdimp5kb = apply(varimp_gm12878_5kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_5kb) <- NULL
+
+```
+
 ###10kb
@@
 
+###5kb
+
+```{r}
+varimp_K562_5kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_5kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_5kb <- data.frame(Feature = rownames(varimp_K562_5kb),
+                                  aveimp5kb = rowMeans(varimp_K562_5kb, na.rm = TRUE),
+                                  sdimp5kb = apply(varimp_K562_5kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_5kb) <- NULL
+
+```
+
 ###10kb
@@
 #GM12878
-all_varimps_gm12878_chromstates <- cbind.data.frame(varimp_gm12878_10kb$Feature,
+all_varimps_gm12878_chromstates <- cbind.data.frame(varimp_gm12878_5kb$Feature,
+                                        varimp_gm12878_5kb$aveimp5kb,            
                                         varimp_gm12878_10kb$aveimp10kb,
@@
                                         varimp_gm12878_100kb$aveimp100kb)
-names(all_varimps_gm12878_chromstates) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+names(all_varimps_gm12878_chromstates) <- c("Feature", "ave5kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
 all_varimps_gm12878_chromstates <- all_varimps_gm12878_chromstates[order(rowMeans(all_varimps_gm12878_chromstates[,-1]), decreasing = TRUE),]
@@
 #K562
-all_varimps_K562_chromstates <- cbind.data.frame(varimp_K562_10kb$Feature,
+all_varimps_K562_chromstates <- cbind.data.frame(varimp_K562_5kb$Feature,
+                                        varimp_K562_5kb$aveimp5kb,         
                                         varimp_K562_10kb$aveimp10kb,
@@
                                         varimp_K562_100kb$aveimp100kb)
-names(all_varimps_K562_chromstates) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+names(all_varimps_K562_chromstates) <- c("Feature", "ave5kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
 all_varimps_K562_chromstates <- all_varimps_K562_chromstates[order(rowMeans(all_varimps_K562_chromstates[,-1]), decreasing = TRUE),]
@@
 
+###5kb
+
+```{r}
+varimp_gm12878_5kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_5kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "Gm12878-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)		
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_5kb <- data.frame(Feature = rownames(varimp_gm12878_5kb),
+                                  aveimp5kb = rowMeans(varimp_gm12878_5kb, na.rm = TRUE),
+                                  sdimp5kb = apply(varimp_gm12878_5kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_5kb) <- NULL
+
+```
+
 ###10kb
@@
 
+###5kb
+
+```{r}
+varimp_K562_5kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_5kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+                              chrs[i],
+									            "/smote/distance/enet/rfimpvars_histones.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                                   "K562-",
+	                                   "_dist",
+	                                   "-Haib", 
+                                     "-Sydh",
+                                     "-Uta",
+                                     "-Uw",
+                                     "-Broad",
+                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_5kb <- data.frame(Feature = rownames(varimp_K562_5kb),
+                                  aveimp5kb = rowMeans(varimp_K562_5kb, na.rm = TRUE),
+                                  sdimp5kb = apply(varimp_K562_5kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_5kb) <- NULL
+
+```
+
 ###10kb
@@
 #GM12878
-all_varimps_gm12878_histones <- cbind.data.frame(varimp_gm12878_10kb$Feature,
+all_varimps_gm12878_histones <- cbind.data.frame(varimp_gm12878_5kb$Feature,
+                                        varimp_gm12878_5kb$aveimp5kb,
                                         varimp_gm12878_10kb$aveimp10kb,
@@
                                         varimp_gm12878_100kb$aveimp100kb)
-names(all_varimps_gm12878_histones) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+names(all_varimps_gm12878_histones) <- c("Feature", "ave5kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
 all_varimps_gm12878_histones <- all_varimps_gm12878_histones[order(rowMeans(all_varimps_gm12878_histones[,-1]), decreasing = TRUE),]
@@
 #K562
-all_varimps_K562_histones <- cbind.data.frame(varimp_K562_10kb$Feature,
+all_varimps_K562_histones <- cbind.data.frame(varimp_K562_5kb$Feature,
+                                        varimp_K562_5kb$aveimp5kb,
                                         varimp_K562_10kb$aveimp10kb,
@@
                                         varimp_K562_100kb$aveimp100kb)
-names(all_varimps_K562_histones) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+names(all_varimps_K562_histones) <- c("Feature", "ave5kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
 all_varimps_K562_histones <- all_varimps_K562_histones[order(rowMeans(all_varimps_K562_histones[,-1]), decreasing = TRUE),]

### 2019-07-12 Scripts/proportion_of_importance_per_annotation.Rmd
added 5kb results

@@
 ```{r}
-annots <- list.files("Z:/TAD_data_analysis/annotations/all_annotations/gm12878")
+annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878", pattern = "*.bed")
 annots <- gsub(paste(c("Gm12878-",".bed", 
@@
 
-chromstates <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
+chromstates <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/BroadHMM")
 chromstates <- chromstates[grep("Gm12878", chromstates)]
@@
 
-histones <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
+histones <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/HistoneModifications")
 histones <- histones[grep("Gm12878", histones)]
@@
 
-tfbs <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878")
+tfbs <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/TFBS")
 tfbs <- gsub(paste0(c("Gm12878-", ".bed", "-Haib", "-Sydh", "-Broad", "-Uw", "-Uta", "-Chicago"), collapse = "|"),"", tfbs)
@@
 
+```
+
+##5kb
+
+```{r}
+varimp_gm12878_5kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_gm12878_5kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+									   chrs[i], 
+									   "/smote/distance/enet/rfimpvars_noenet.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                           "_dist",
+	                           "Gm12878-",".bed", 
+                             "-Haib", 
+                             "-Sydh",
+                             "-Uta",
+                             "-Uw",
+                             "-Broad",
+                             "-Uchicago"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_gm12878_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_gm12878_5kb <- data.frame(Feature = rownames(varimp_gm12878_5kb),
+                                  aveimp5kb = rowMeans(varimp_gm12878_5kb, na.rm = TRUE),
+                                  sdimp5kb = apply(varimp_gm12878_5kb,1, sd, na.rm = TRUE))
+rownames(varimp_gm12878_5kb) <- NULL
 ```
@@
 									   chrs[i], 
-									   "/smote/distance/enet/rfimpvars.rds"))
-	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+									   "/smote/distance/enet/rfimpvars_noenet.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                           "_dist",
+	                           "Gm12878-",".bed", 
+                             "-Haib", 
+                             "-Sydh",
+                             "-Uta",
+                             "-Uw",
+                             "-Broad",
+                             "-Uchicago"), collapse = "|"), "", varimps$Feature)	
 	  varimps <- varimps[order(varimps$Feature),]
@@
 									   chrs[i], 
-									   "/smote/distance/enet/rfimpvars.rds"))
-	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+									   "/smote/distance/enet/rfimpvars_noenet.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                           "_dist",
+	                           "Gm12878-",".bed", 
+                             "-Haib", 
+                             "-Sydh",
+                             "-Uta",
+                             "-Uw",
+                             "-Broad",
+                             "-Uchicago"), collapse = "|"), "", varimps$Feature)
 	  varimps <- varimps[order(varimps$Feature),]
@@
 ```{r}
-all_propimp_gm12878 <- data.frame(Importance=c(varimp_gm12878_10kb$aveimp10kb,
+all_propimp_gm12878 <- data.frame(Importance=c(varimp_gm12878_5kb$aveimp5kb,
+                                                   varimp_gm12878_10kb$aveimp10kb,
                                                    varimp_gm12878_25kb$aveimp25kb,
@@
                                             as.character(varimp_gm12878_10kb$Feature),
+                                            as.character(varimp_gm12878_10kb$Feature),
                                             as.character(varimp_gm12878_10kb$Feature)),
-                                  Resolution=c(rep("10 kb", 107),
-                                               rep("25 kb", 107),
-                                               rep("50 kb", 107),
-                                               rep("100 kb", 107))
+                                  Resolution=c(rep("5 kb", 78),
+                                               rep("10 kb", 78),
+                                               rep("25 kb", 78),
+                                               rep("50 kb", 78),
+                                               rep("100 kb", 78))
                                   )
@@
 
-all_propimp_gm12878_summ <- data.frame(Prop.VI = c(
+all_propimp_gm12878_summ <- data.frame(Prop.VI = c(#5kb
+                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="5 kb" & all_propimp_gm12878$Annotation=="CSS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="5 kb")]),
+                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="5 kb" & all_propimp_gm12878$Annotation=="HM")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="5 kb")]),
+                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="5 kb" & all_propimp_gm12878$Annotation=="TFBS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="5 kb")]),
+
                                                    #10kb
@@
                                                    sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb" & all_propimp_gm12878$Annotation=="TFBS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb")])),
-                                       Resolution = c(rep("10 kb", 3),
+                                       Resolution = c(rep("5 kb", 3),
+                                                      rep("10 kb", 3),
                                                       rep("25 kb", 3),
@@
                                                       rep("100 kb", 3)),
-                                       Annotation = rep(c("CSS","HM","TFBS"), 4))
+                                       Annotation = rep(c("CSS","HM","TFBS"), 5))
 
-all_propimp_gm12878_summ$Resolution <- factor(all_propimp_gm12878_summ$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
+all_propimp_gm12878_summ$Resolution <- factor(all_propimp_gm12878_summ$Resolution, levels=c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
 
@@
 ```{r}
-annots <- list.files("Z:/TAD_data_analysis/annotations/all_annotations/k562")
+annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562", pattern = "*.bed")
 annots <- gsub(paste(c("K562-",".bed", 
@@
 
-chromstates <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
+chromstates <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562/BroadHMM")
 chromstates <- chromstates[grep("K562", chromstates)]
@@
 
-histones <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
+histones <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562/HistoneModifications")
 histones <- histones[grep("K562", histones)]
@@
 
-tfbs <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/K562")
+tfbs <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562/TFBS")
 tfbs <- gsub(paste0(c("K562-", ".bed", "-Haib", "-Sydh", "-Broad", "-Uw", "-Uta", "-Chicago"), collapse = "|"),"", tfbs)
@@
 
+```
+
+##5kb
+
+```{r}
+varimp_K562_5kb <- matrix(nrow=length(annots), ncol=21)
+rownames(varimp_K562_5kb) <- annots
+
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+									   chrs[i], 
+									   "/smote/distance/enet/rfimpvars_noenet.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                           "_dist",
+	                           "K562-",".bed", 
+                             "-Haib", 
+                             "-Sydh",
+                             "-Uta",
+                             "-Uw",
+                             "-Broad",
+                             "-Uchicago"), collapse = "|"), "", varimps$Feature)	
+	  varimps <- varimps[order(varimps$Feature),]
+
+		varimp_K562_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
+}
+
+varimp_K562_5kb <- data.frame(Feature = rownames(varimp_K562_5kb),
+                                  aveimp5kb = rowMeans(varimp_K562_5kb, na.rm = TRUE),
+                                  sdimp5kb = apply(varimp_K562_5kb,1, sd, na.rm = TRUE))
+rownames(varimp_K562_5kb) <- NULL
 ```
@@
 									   chrs[i], 
-									   "/smote/distance/enet/rfimpvars.rds"))
-	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+									   "/smote/distance/enet/rfimpvars_noenet.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                           "_dist",
+	                           "K562-",".bed", 
+                             "-Haib", 
+                             "-Sydh",
+                             "-Uta",
+                             "-Uw",
+                             "-Broad",
+                             "-Uchicago"), collapse = "|"), "", varimps$Feature)	
 	  varimps <- varimps[order(varimps$Feature),]
@@
 									   chrs[i], 
-									   "/smote/distance/enet/rfimpvars.rds"))
-	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
+									   "/smote/distance/enet/rfimpvars_noenet.rds"))
+	  varimps$Feature <- gsub(paste0(c("`",
+	                           "_dist",
+	                           "K562-",".bed", 
+                             "-Haib", 
+                             "-Sydh",
+                             "-Uta",
+                             "-Uw",
+                             "-Broad",
+                             "-Uchicago"), collapse = "|"), "", varimps$Feature)
 	  varimps <- varimps[order(varimps$Feature),]
@@
 ```{r}
-all_propimp_K562 <- data.frame(Importance=c(varimp_K562_10kb$aveimp10kb,
+all_propimp_K562 <- data.frame(Importance=c(varimp_K562_5kb$aveimp5kb,
+                                                  varimp_K562_10kb$aveimp10kb,
                                                    varimp_K562_25kb$aveimp25kb,
@@
                                             as.character(varimp_K562_10kb$Feature),
+                                            as.character(varimp_K562_10kb$Feature),
                                             as.character(varimp_K562_10kb$Feature)),
-                                  Resolution=c(rep("10 kb", 141),
-                                               rep("25 kb", 141),
-                                               rep("50 kb", 141),
-                                               rep("100 kb", 141))
+                                  Resolution=c(rep("5 kb", 78),
+                                               rep("10 kb", 78),
+                                               rep("25 kb", 78),
+                                               rep("50 kb", 78),
+                                               rep("100 kb", 78))
                                   )
@@
 
-all_propimp_K562_summ <- data.frame(Prop.VI = c(
+all_propimp_K562_summ <- data.frame(Prop.VI = c(#5kb
+                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="5 kb" & all_propimp_K562$Annotation=="CSS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="5 kb")]),
+                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="5 kb" & all_propimp_K562$Annotation=="HM")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="5 kb")]),
+                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="5 kb" & all_propimp_K562$Annotation=="TFBS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="5 kb")]),
+
                                                    #10kb
@@
                                                    sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb" & all_propimp_K562$Annotation=="TFBS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb")])),
-                                       Resolution = c(rep("10 kb", 3),
+                                       Resolution = c(rep("5 kb", 3),
+                                                      rep("10 kb", 3),
                                                       rep("25 kb", 3),
@@
                                                       rep("100 kb", 3)),
-                                       Annotation = rep(c("CSS","HM","TFBS"), 4))
+                                       Annotation = rep(c("CSS","HM","TFBS"), 5))
 
-all_propimp_K562_summ$Resolution <- factor(all_propimp_K562_summ$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))
+all_propimp_K562_summ$Resolution <- factor(all_propimp_K562_summ$Resolution, levels=c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
 

### 2019-07-12 Manuscript/manuscript.Rmd
results edits

@@
 To establish the data for classification, the genome was binned into equally sized intervals defined by the data resolution of the corresponding contact matrix.
-As an example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals.
+As an example, for domain data obtained from a 100 kb resolution contact matrix, the genome was binned into 100 kb intervals.
 In order to accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
-That is, for 10 kb resolution data, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb.
-A genomic bin was then labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary.
-Otherwise, the bin was labeled as not containing a boundary (Y=0).
+That is, for 100 kb resolution data, each uniquely identified TAD boundary was flanked on either side by 100 kilobases for a total width around each boundary point of 200 kb.
+A genomic bin was then labeled as having a TAD boundary within it ($Y = 1$) if it overlapped with a particular flanked boundary.
+Otherwise, the bin was labeled as not containing a boundary ($Y = 0$).
 
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-Additional performance metrics were [???
+<!--Additional performance metrics including AUROC, accuracy, sensitivity, and specificity were [???
 are?] reported in the supplementary materials.
 [???
-Where is it?]
+Where is it?]-->
 
 ## USING OPTIMALLY BUILT CLASSIFIER TO PREDICT BOUNDARIES AT FINER RESOLUTION
+
+[needs editting]
 
@@
 We analyzed publically available replicate Hi-C data sets from two cell lines including GM12878 and K562 (Supplementary Table 1).
-Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at four resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-To account for the varying levels of data resolution, we developed a resolution-specific approach toward constructing TAD versus non TAD boundary regions on the linear genome, labeled as a response vector **Y** (Figure 1).
-First, we binned the linear genome according to the data resolution.
-We then flanked the boundaries on either side by the same number of basepairs as the previously constructed genomic bins.
-TAD boundary regions were defined as regions on the linear genome where a genomic bin overlapped with a flanked TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as the regions that did not overlap with a flanked TAD boundary ($Y = 0$).
-
-<!--## TOTAL NUMBER OF TAD BOUNDARY REGIONS DECREASE AS Hi-C DATA RESOLUTION DECREASES-->
-Expectedly, the total number of TAD boundary regions increased with the increased resolution of Hi-C data irrespectively of cell line (Figure 2A).
-At higher resolutions, GM12878 was found to contain more TADs, and thus more TAD boundary regions compared to K562.
-This can largely be attributed to the increased sequencing depth of the GM12878 library.
-However, this difference was found to dissipate as resolution decreased, resulting in much more similar numbers of TAD boundary regions between the two cell lines at the 50 kb and 100 kb resolutions respectively.
+Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at 4 resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
+To account for the varying levels of data resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1).
+<!--First, we binned the linear genome according to the data resolution.
+We then flanked the boundaries on either side by the same number of basepairs as the previously constructed genomic bins.--> TAD boundary regions were defined as regions on the linear genome where a genomic bin overlapped with a flanked TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as the regions that did not overlap with a flanked TAD boundary ($Y = 0$).
 
@@
 ## TAD BOUNDARY REGIONS EXHIBIT CELL-LINE SPECIFICITY
+
+<!--## TOTAL NUMBER OF TAD BOUNDARY REGIONS DECREASE AS Hi-C DATA RESOLUTION DECREASES-->
+Expectedly, the total number of TAD boundary regions increased with the increased resolution of Hi-C data irrespectively of cell line (Figure 2A).
+At higher resolutions, GM12878 was found to contain more TADs, and thus more TAD boundary regions compared to K562.
+This can largely be attributed to the increased sequencing depth of the GM12878 library.
+However, this difference was found to dissipate as resolution decreased, resulting in much more similar numbers of TAD boundary regions between the two cell lines at the 50 kb and 100 kb resolutions respectively.
 
@@
 In order to identify the optimal combination of data resolution, predictor type, and re-sampling technique necessary for TAD boundary prediction, we created an ensemble framework to systematically compare performances of different model inputs (Figure 4).
-Each system in the framework was assumed to be composed of a random forest classifier constructed from a particular cell line ($L = \{GM12878, K562\}$).
-Within each cell line we evaluated 5 data resolutions ($R = \{5 kb, 10 kb, 25 kb, 50 kb, 100 kb\}$).
-We then considered 3 separate predictor types as the feature space ($P = \{OC, OP, Distance\}$).
-To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling ($B = \{None, RUS, ROS, SMOTE\}$).
+Each system in the framework was assumed to be composed of a random forest classifier constructed from a particular cell line (*L = {GM12878, K562}*).
+Within each cell line we evaluated 5 data resolutions (*R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*).
+We then considered 3 separate predictor types as the feature space (*P = {OC, OP, Distance}*).
+To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling (*B = {None, RUS, ROS, SMOTE}*).
 Each combination of the above cell line specific parameters was implemented on chromosome specific sections of the linear genome (omitting chromosome 9).
 Letting $|X|$ denote the cardinality [???
-TBD] of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling 2520 ($2 \times 5 \times 3 \times 4 \times 21$) separate models.
+TBD] of each set, we evaluated *|L|* $\times$ *|R|* $\times$ *|P|* $\times$ *|B|* different ensemble systems, totaling 2520 (*2* $\times$ *5* $\times$ *3* $\times$ *4* $\times$ *21*) separate models.
 For each combination of inputs, we performed 10-fold cross-validation to tune for the number of features to consider at each node of the random forest classifier.
@@
 We first evaluated the least granular cell line specific random forest classifiers [???
-Unclear], those were ones implemented using OC predictor types, without data re-sampling.
+Unclear; !!!discuss in meeting], those were ones implemented using OC predictor types, without data re-sampling.
 We found that these models exhibited poor MCCs across all resolutions (Figure 5 A-B (red)).
 We then assessed models built on OP predictor types, while still not performing any data resampling.
-Performances were similar to that of OC types, with no clear improvement (Figure 5 C-D (red)).
-This indicated that the added complexity of using overlap percents from the functional genomic annotations did not affect predictive performance, regardless of cell line and resolution.
+Performances were similar to that of OC types, with no visible improvement across resolution, for either cell line (Figure 5 C-D (red)).
+This indicated that the added complexity of using overlap percents from the functional genomic annotations did not affect predictive performance.
 However, when cell line specific classifiers were implemented using distance-type predictors and no re-sampling, we found that there was a significant improvement in MCC compared to the other two predictor types (Figure 5 E-F (red)).
-
 We then further explored the impact of data re-sampling on model performance, across cell line and resolution.
-For cell line specific random forest classifiers built on balanced data, we found that SMOTE re-sampling provided the optimal MCC, consistently outperforming models built on ROS or RUS, across both predictor type and resolution (Figure 5).
+For cell line specific random forest classifiers built on balanced data, we found that SMOTE re-sampling provided the optimal MCC, consistently outperforming models built on ROS or RUS respectively, across both predictor type and resolution (Figure 5).
 Specifically, the most improvement was seen when combining SMOTE re-sampling with distance-type predictors for both the GM12878 and K562 cell lines.
@@
 
-Interestingly, we found that there was a degredation in model performance as data resolution decreased.
-Chromosome specific models built on 10 kb data resolutions presented the highest MCC values (Figure 5).
+Interestingly, we found that performance peaked at 10 kb resolution and then degraded as data resolution decreased (Figure 5).
+The reason for the improved performance between 5 kb and 10 kb data resolutions can be attributed to the added sparcity in the interaction frequency matrices at finer resolutions.
+This sparcity corresponds to inaccurate TAD calling which leads to worse model performance.
+The difference in performance between 5 kb and 10 kb resolutions for K562 was found to be slightly steaper, indicating that this issue of sparcity was more severe at finer resolutions for K562.
 Additionally, performances tended to be much more variable between chromosomes at lower resolutions.
-Moreover, this decreasing trend in performance was much more evident under the optimal combination of data level characteristics.
-These results imply that an optimally performing cell line specific random forest classifier <!--, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries,--> is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
+Moreover, this decreasing trend in performance was much more evident under the optimal combination of data level characteristics (SMOTE resampling with distance type predictors).
+These results imply that there is an ideal resolution in TAD boundary prediction, and that that an optimally performing cell line specific random forest classifier <!--, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries,--> is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
 
@@
 We further assessed the predictive capabilities of the specific sets of annotations by comparing the performances of annotation-specific random forest models implemented on the optimal set of characteristics.
-We found that cell line specific models built simply on TFBS outperformed other cell line and annotation-specific models at all resolutions (Figure 7).
+We found that cell line specific models built simply on TFBS outperformed other cell line and annotation-specific models at all resolutions (Figure 6 B).
 Additionally, when compared to models built on all 3 sets of functional genomic annotations, the TFBS-specific models performed similarly at the 10 kb and 25 kb resolutions.
@@
 We then sought to determine which of the transcription factor binding sites were most influential in predicting TAD boundaries.
-We found that the cell line specific binding sites associated with SMC3, CTCF, RAD21, ZNF143, and YY1sc281 were given consistently high predictive importance, across all resolutions (Figure 7; Supplementary Figure 6).
+We found that the cell line specific binding sites associated with SMC3, CTCF, RAD21, and ZNF143 were given consistently high predictive importance, across all resolutions (Figure 6 C).
 The SMC3, CTCF, and RAD21 binding sites are known factors associated with the cohesin protein complex, which is hypothesized to be what creates loops in the DNA  [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
-Likewise, ZNF143 and YY1 are known structural regulators of enhancer-promoter interactions that also contribute to looping of the linear genome [@weintraub2017yy1; @gonzalez2017znf143].
+Likewise, ZNF143 is a known structural regulators of enhancer-promoter interactions that also contribute to looping of the linear genome [@weintraub2017yy1; @gonzalez2017znf143].
 With the identification of these factors known to be enriched at TAD boundaries, we are able to confirm the validity of our model building process.
@@
 Importances were sorted according to the row-wise average across resolution and rescaled to values between 0 and 100.
-Transcription factors with higher values of predictive importance are denoted in dark red and dark blue for the GM12878 and K562 cell line respectively.](Figures/prop_imps_a_comparing_annots_b_var_imps_c.png)
+Transcription factors with higher values of predictive importance are denoted in dark red and dark blue for the GM12878 and K562 cell line respectively.](Figures/prop_imps_a_comparing_annots_b_var_imps_c_v2.png)
 

### 2019-07-12 Scripts/evaluating_variable_importances.Rmd
edits for 5kb results

@@
 all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[order(rowMeans(all_varimps_gm12878_tfbs[,-1]), decreasing = TRUE),]
-all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[1:20,]
+#all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[1:20,]
 all_varimps_gm12878_tfbs <- melt(all_varimps_gm12878_tfbs)
@@
 all_varimps_K562_tfbs <- all_varimps_K562_tfbs[order(rowMeans(all_varimps_K562_tfbs[,-1]), decreasing = TRUE),]
-all_varimps_K562_tfbs <- all_varimps_K562_tfbs[1:20,]
+#all_varimps_K562_tfbs <- all_varimps_K562_tfbs[1:20,]
 all_varimps_K562_tfbs <- melt(all_varimps_K562_tfbs)

### 2019-07-22 Manuscript/manuscript_structured.Rmd
added prefered results for predicting boundaries at bp res

@@
 ### Consider distance
+
+## Predicting at bp resolution
+
+### Empirical way to determine boundary regions
+
+### Predicted TAD boundary regions vs Called TAD boundary regions
+
+#### Number of predicted regions compared to called regions
+#### Overlap between the two
+#### Summary statistics
+##### Distribution of distances 
+###### densities
+###### ECDF
+##### Jaccard indeces
+##### Enrichment
+
 -->

### 2019-07-22 Scripts/functions_for_R_package/all_functions.R
edits

@@ -1,8 +1,15 @@
+#Functions for R package
+
+#libraries
 library(GenomicRanges)
 library(ggplot2)
 library(caret)
 library(GenomeInfoDbData)
 library(GenomeInfoDb)
+library(GenometriCorr)
+library(BSgenome)
+
+###################################################################################
 
 #function to create grangeslist object from functional genomic annotation .bed files
 annots_to_granges_func <- function(filepath){
@@ -21,7 +28,7 @@ annots_to_granges_func <- function(filepath){
   return(annots_gr_list)
 }
 
-###############################################################################3333
+##################################################################################
 
 #Functions for calculating different types of predictors/overlaps
 ####calculating binary overlaps
@@ -399,8 +406,13 @@ predict_at_bp_resolution_func <- function(bounds.GR, resolution, chromosome, ann
   if(region==TRUE){
     finer_res_list <- list(trueBound_gr_region,predBound_gr_region)
   }else{finer_res_list <- list(trueBound_gr,predBound_gr)}
+  names(finer_res_list) <- c("Called", "Predicted")
   
   return(finer_res_list)
   
 }
+
+###################################################################################################
+
+#function to perform correlation tests
 

### 2019-07-22 Scripts/functions_for_R_package/predict_at_bp_resolution_func.r

@@ -107,6 +107,7 @@ predict_at_bp_resolution_func <- function(bounds.GR, resolution, chromosome, ann
   if(region==TRUE){
     finer_res_list <- list(trueBound_gr_region,predBound_gr_region)
   }else{finer_res_list <- list(trueBound_gr,predBound_gr)}
+  names(finer_res_list) <- c("Called", "Predicted")
   
   return(finer_res_list)
   

### 2019-07-23 Scripts/comparing_tad_regions_across_cl_using_vd.Rmd
updated with preprocessed tads

--- 2019-06-25 Scripts/comparing_tad_regions_across_cl_using_vd.Rmd
@@
 
+### 5kb
+
+```{r}
+#bounds_f_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/bounds_f.rds")
+#bounds_f_K562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/bounds_f.rds")
+
+#res <- makeVennDiagram(Peaks=list(bounds_f_gm12878_5kb, bounds_f_K562_5kb),
+#                       NameOfPeaks=c("GM12878", "K562"))
+
+#venn_5kb <- venn_cnt2venn(res$vennCounts)
+#plot(venn_5kb)
+
+#binslist_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/binslist5.rds")
+#binslist_gm12878_5kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/binslist5_center.rds")
+#mcols(binslist_gm12878_5kb)$y <- mcols(binslist_gm12878_5kb_center)$y
+#binslist_gm12878_5kb <- binslist_gm12878_5kb[mcols(binslist_gm12878_5kb)$y==1]
+
+#binslist_K562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/binslist5.rds")
+#binslist_K562_5kb_center <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/binslist5_center.rds")
+#mcols(binslist_K562_5kb)$y <- mcols(binslist_K562_5kb_center)$y
+#binslist_K562_5kb <- binslist_K562_5kb[mcols(binslist_K562_5kb)$y==1]
+
+bounds_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/bounds_f.rds")
+bounds_k562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/bounds_f.rds")
+
+res <- makeVennDiagram(Peaks=list(bounds_gm12878_5kb, bounds_k562_5kb),
+                       NameOfPeaks=c("GM12878", "K562"))
+
+venn_5kb <- venn_cnt2venn(res$vennCounts)
+venn_5kb <- compute.Venn(venn_5kb)
+gp <- VennThemes(venn_5kb)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+
+#plot(venn_5kb)
+
+```
+
 ### 10kb
@@
 
-binslist_gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")
-binslist_gm12878_10kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10_center.rds")
-mcols(binslist_gm12878_10kb)$y <- mcols(binslist_gm12878_10kb_center)$y
-binslist_gm12878_10kb <- binslist_gm12878_10kb[mcols(binslist_gm12878_10kb)$y==1]
+#binslist_gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")
+#binslist_gm12878_10kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10_center.rds")
+#mcols(binslist_gm12878_10kb)$y <- mcols(binslist_gm12878_10kb_center)$y
+#binslist_gm12878_10kb <- binslist_gm12878_10kb[mcols(binslist_gm12878_10kb)$y==1]
 
-binslist_K562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")
-binslist_K562_10kb_center <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10_center.rds")
-mcols(binslist_K562_10kb)$y <- mcols(binslist_K562_10kb_center)$y
-binslist_K562_10kb <- binslist_K562_10kb[mcols(binslist_K562_10kb)$y==1]
+#binslist_K562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")
+#binslist_K562_10kb_center <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10_center.rds")
+#mcols(binslist_K562_10kb)$y <- mcols(binslist_K562_10kb_center)$y
+#binslist_K562_10kb <- binslist_K562_10kb[mcols(binslist_K562_10kb)$y==1]
 
-res <- makeVennDiagram(Peaks=list(binslist_gm12878_10kb, binslist_K562_10kb),
+bounds_gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/bounds_f.rds")
+bounds_k562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/bounds_f.rds")
+
+res <- makeVennDiagram(Peaks=list(bounds_gm12878_10kb, bounds_k562_10kb),
                        NameOfPeaks=c("GM12878", "K562"))
@@
 gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
 #plot(venn_10kb)
@@
 
-binslist_gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")
-binslist_gm12878_25kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25_center.rds")
-mcols(binslist_gm12878_25kb)$y <- mcols(binslist_gm12878_25kb_center)$y
-binslist_gm12878_25kb <- binslist_gm12878_25kb[mcols(binslist_gm12878_25kb)$y==1]
+#binslist_gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")
+#binslist_gm12878_25kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25_center.rds")
+#mcols(binslist_gm12878_25kb)$y <- mcols(binslist_gm12878_25kb_center)$y
+#binslist_gm12878_25kb <- binslist_gm12878_25kb[mcols(binslist_gm12878_25kb)$y==1]
 
-binslist_K562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")
-binslist_K562_25kb_center <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25_center.rds")
-mcols(binslist_K562_25kb)$y <- mcols(binslist_K562_25kb_center)$y
-binslist_K562_25kb <- binslist_K562_25kb[mcols(binslist_K562_25kb)$y==1]
+#binslist_K562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")
+#binslist_K562_25kb_center <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25_center.rds")
+#mcols(binslist_K562_25kb)$y <- mcols(binslist_K562_25kb_center)$y
+#binslist_K562_25kb <- binslist_K562_25kb[mcols(binslist_K562_25kb)$y==1]
 
-res <- makeVennDiagram(Peaks=list(binslist_gm12878_25kb, binslist_K562_25kb),
+bounds_gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/bounds_f.rds")
+bounds_k562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/bounds_f.rds")
+
+res <- makeVennDiagram(Peaks=list(bounds_gm12878_25kb, bounds_k562_25kb),
                        NameOfPeaks=c("GM12878", "K562"))
@@
 gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
 #plot(venn_25kb)
@@
 
-binslist_gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")
-binslist_gm12878_50kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50_center.rds")
-mcols(binslist_gm12878_50kb)$y <- mcols(binslist_gm12878_50kb_center)$y
-binslist_gm12878_50kb <- binslist_gm12878_50kb[mcols(binslist_gm12878_50kb)$y==1]
+#binslist_gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")
+#binslist_gm12878_50kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50_center.rds")
+#mcols(binslist_gm12878_50kb)$y <- mcols(binslist_gm12878_50kb_center)$y
+#binslist_gm12878_50kb <- binslist_gm12878_50kb[mcols(binslist_gm12878_50kb)$y==1]
 
-binslist_K562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")
-binslist_K562_50kb_center <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50_center.rds")
-mcols(binslist_K562_50kb)$y <- mcols(binslist_K562_50kb_center)$y
-binslist_K562_50kb <- binslist_K562_50kb[mcols(binslist_K562_50kb)$y==1]
+#binslist_K562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")
+#binslist_K562_50kb_center <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50_center.rds")
+#mcols(binslist_K562_50kb)$y <- mcols(binslist_K562_50kb_center)$y
+#binslist_K562_50kb <- binslist_K562_50kb[mcols(binslist_K562_50kb)$y==1]
 
-res <- makeVennDiagram(Peaks=list(binslist_gm12878_50kb, binslist_K562_50kb),
+bounds_gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/bounds_f.rds")
+bounds_k562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/bounds_f.rds")
+
+res <- makeVennDiagram(Peaks=list(bounds_gm12878_50kb, bounds_k562_50kb),
                        NameOfPeaks=c("GM12878", "K562"))
@@
 gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
 #plot(venn_50kb)
@@
 
-binslist_gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")
-binslist_gm12878_100kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100_center.rds")
-mcols(binslist_gm12878_100kb)$y <- mcols(binslist_gm12878_100kb_center)$y
-binslist_gm12878_100kb <- binslist_gm12878_100kb[mcols(binslist_gm12878_100kb)$y==1]
+#binslist_gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")
+#binslist_gm12878_100kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100_center.rds")
+#mcols(binslist_gm12878_100kb)$y <- mcols(binslist_gm12878_100kb_center)$y
+#binslist_gm12878_100kb <- binslist_gm12878_100kb[mcols(binslist_gm12878_100kb)$y==1]
 
-binslist_K562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")
-binslist_K562_100kb_center <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100_center.rds")
-mcols(binslist_K562_100kb)$y <- mcols(binslist_K562_100kb_center)$y
-binslist_K562_100kb <- binslist_K562_100kb[mcols(binslist_K562_100kb)$y==1]
+#binslist_K562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")
+#binslist_K562_100kb_center <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100_center.rds")
+#mcols(binslist_K562_100kb)$y <- mcols(binslist_K562_100kb_center)$y
+#binslist_K562_100kb <- binslist_K562_100kb[mcols(binslist_K562_100kb)$y==1]
 
-res <- makeVennDiagram(Peaks=list(binslist_gm12878_100kb, binslist_K562_100kb),
+bounds_gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/bounds_f.rds")
+bounds_k562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/bounds_f.rds")
+
+res <- makeVennDiagram(Peaks=list(bounds_gm12878_100kb, bounds_k562_100kb),
                        NameOfPeaks=c("GM12878", "K562"))
@@
 gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
 #plot(venn_100kb)
@@
 
-gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_10kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("10 kb", gp=gpar(fontsize=20)))
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_5kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("5 kb", gp=gpar(fontsize=50)))
 grid.newpage()
-gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_25kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("25 kb", gp=gpar(fontsize=20)))
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_10kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("10 kb", gp=gpar(fontsize=50)))
 grid.newpage()
-gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_50kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("50 kb", gp=gpar(fontsize=20)))
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_25kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("25 kb", gp=gpar(fontsize=50)))
 grid.newpage()
-gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_100kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("100 kb", gp=gpar(fontsize=20)))
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_50kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("50 kb", gp=gpar(fontsize=50)))
+grid.newpage()
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_100kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("100 kb", gp=gpar(fontsize=50)))
 grid.newpage()

### 2019-07-23 Scripts/evaluating_imbalance_ratios.Rmd
updated with preprocessed tads

@@
 library(lattice)
+library(irr)
 
@@
 
-##Bounds Plots
+##Boundary regions Plots
 
 ```{r}
-a <- ggplot(bounds_df[which(bounds_df$res=="5kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+a <- ggplot(irtab_summ[which(irtab_summ$res=="5kb"),], aes(x=cl, y=AveBounds, fill=cl))+
   geom_bar(stat="identity", position="dodge")+
+  geom_errorbar(aes(ymin=AveBounds-AveBoundsSD, ymax=AveBounds+AveBoundsSD), width=.5,
+                 position=position_dodge(.9), alpha=0.75) +
   theme_minimal() +
   theme_bw()+
-  xlab("") + ylab("") + ylim(0,30000) +
+  xlab("") + ylab("") + ylim(0,2100) +
   scale_fill_discrete(name="Cell Line") +
-  scale_y_continuous(limits = c(0,30000),
-                     breaks=c(0,10000,20000,30000),
-                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
+  scale_y_continuous(limits = c(0,2100),
+                     breaks=c(0,500,1000,1500,2000),
+                     labels=c("0"="0", "500"="5", "1000"="10", "1500"="15", "2000"="20")) +
   ggtitle("5 kb") +
@@
 
-b <- ggplot(bounds_df[which(bounds_df$res=="10kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+b <- ggplot(irtab_summ[which(irtab_summ$res=="10kb"),], aes(x=cl, y=AveBounds, fill=cl))+
   geom_bar(stat="identity", position="dodge")+
+  geom_errorbar(aes(ymin=AveBounds-AveBoundsSD, ymax=AveBounds+AveBoundsSD), width=.5,
+                 position=position_dodge(.9), alpha=0.75) +
   theme_minimal() +
   theme_bw()+
-  xlab("") + ylab("") + ylim(0,30000) +
+  xlab("") + ylab("") + ylim(0,2100) +
   scale_fill_discrete(name="Cell Line") +
-  scale_y_continuous(limits = c(0,30000),
-                     breaks=c(0,10000,20000,30000),
-                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
+  scale_y_continuous(limits = c(0,2100),
+                     breaks=c(0,500,1000,1500,2000),
+                     labels=c("0"="0", "500"="5", "1000"="10", "1500"="15", "2000"="20")) +
   ggtitle("10 kb") +
@@
 
-c <- ggplot(bounds_df[which(bounds_df$res=="25kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+c <- ggplot(irtab_summ[which(irtab_summ$res=="25kb"),], aes(x=cl, y=AveBounds, fill=cl))+
   geom_bar(stat="identity", position="dodge")+
+  geom_errorbar(aes(ymin=AveBounds-AveBoundsSD, ymax=AveBounds+AveBoundsSD), width=.5,
+                 position=position_dodge(.9), alpha=0.75) +
   theme_minimal() +
   theme_bw()+
-  xlab("") + ylab("") + ylim(0,30000) +
+  xlab("") + ylab("") + ylim(0,2100) +
   scale_fill_discrete(name="Cell Line") +
-  scale_y_continuous(limits = c(0,30000),
-                     breaks=c(0,10000,20000,30000),
-                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
+  scale_y_continuous(limits = c(0,2100),
+                     breaks=c(0,500,1000,1500,2000),
+                     labels=c("0"="0", "500"="5", "1000"="10", "1500"="15", "2000"="20")) +
   ggtitle("25 kb") +
@@
 
-d <- ggplot(bounds_df[which(bounds_df$res=="50kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+d <- ggplot(irtab_summ[which(irtab_summ$res=="50kb"),], aes(x=cl, y=AveBounds, fill=cl))+
   geom_bar(stat="identity", position="dodge")+
+  geom_errorbar(aes(ymin=AveBounds-AveBoundsSD, ymax=AveBounds+AveBoundsSD), width=.5,
+                 position=position_dodge(.9), alpha=0.75) +
   theme_minimal() +
   theme_bw()+
-  xlab("") + ylab("") + ylim(0,30000) +
+  xlab("") + ylab("") + ylim(0,2100) +
   scale_fill_discrete(name="Cell Line") +
-  scale_y_continuous(limits = c(0,30000),
-                     breaks=c(0,10000,20000,30000),
-                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
+  scale_y_continuous(limits = c(0,2100),
+                     breaks=c(0,500,1000,1500,2000),
+                     labels=c("0"="0", "500"="5", "1000"="10", "1500"="15", "2000"="20")) +
   ggtitle("50 kb") +
@@
 
-e <- ggplot(bounds_df[which(bounds_df$res=="100kb"),], aes(x=cl, y=TotBounds, fill=cl))+
+e <- ggplot(irtab_summ[which(irtab_summ$res=="100kb"),], aes(x=cl, y=AveBounds, fill=cl))+
   geom_bar(stat="identity", position="dodge")+
+  geom_errorbar(aes(ymin=AveBounds-AveBoundsSD, ymax=AveBounds+AveBoundsSD), width=.5,
+                 position=position_dodge(.9), alpha=0.75) +
   theme_minimal() +
   theme_bw()+
-  xlab("") + ylab("") + ylim(0,30000) +
+  xlab("") + ylab("") + ylim(0,2100) +
   scale_fill_discrete(name="Cell Line") +
-  scale_y_continuous(limits = c(0,30000),
-                     breaks=c(0,10000,20000,30000),
-                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
+  scale_y_continuous(limits = c(0,2100),
+                     breaks=c(0,500,1000,1500,2000),
+                     labels=c("0"="0", "500"="5", "1000"="10", "1500"="15", "2000"="20")) +
   ggtitle("100 kb") +
@@
                 #bottom = text_grob("Cell Line", color = "black", size = 20),
-    left = text_grob("Number of TAD Boundary\nRegions (thousands)", color = "black", rot = 90, size=20)
+                left = text_grob("Average number of TBR across chromosomes\n(thousands)", color = "black", rot = 90, size=20)
 )

### 2019-07-23 Scripts/evaluating_preprocessed_tad_summaries.Rmd
intial commit

---
title: "Evaluating Preprocessed TAD Summaries"
author: "Spiro Stilianoudakis"
date: "July 23, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)

```

# GM12878

```{r}

num_domains <- numeric()
num_domains_lt_2mb <- numeric()
num_domains2 <- numeric()
num_domains_gt_res <- numeric()
num_domains3 <- numeric()
num_bounds <- numeric()

res <- c("5kb" ,"10kb", "25kb","50kb", "100kb")
for(i in 1:length(res)){
  domains <- read.table(paste0("Z:/TAD_data_analysis/GM12878/",
                               res[i],
                               "/GM12878_domain_data_",
                               as.integer(gsub("kb", "000", res[i])),
                               ".b.txt"), header=F)
  domains <- domains[,1:3]
  names(domains) <- c("Chromosome","Start","End")

  num_domains <- rbind(num_domains, nrow(domains))
  num_domains_lt_2mb <- rbind(num_domains_lt_2mb,length(which((domains$End - domains$Start)>=2000000)))

  domains2 <- domains[which((domains$End - domains$Start)<2000000),]

  num_domains2 <- rbind(num_domains2, nrow(domains2))
  num_domains_gt_res <- rbind(num_domains_gt_res, length(which((domains2$End - domains2$Start)<=(as.integer(gsub("kb", "000", res[i]))))))

  domains3 <- domains2[which((domains2$End - domains2$Start)>(as.integer(gsub("kb", "000", res[i])))),]

  num_domains3 <- rbind(num_domains3, nrow(domains3))

  bounds <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/",
                           res[i],
                           "/training_testing/bounds.rds"))

  num_bounds <- rbind(num_bounds, length(bounds))
}

tad_sum_df_gm12878 <- cbind(c("5kb" ,"10kb", "25kb","50kb", "100kb"),
                    num_domains,
                    num_domains_lt_2mb,
                    num_domains2,
                    num_domains_gt_res,
                    num_domains3,
                    num_bounds)

```

# K562

```{r}

num_domains <- numeric()
num_domains_lt_2mb <- numeric()
num_domains2 <- numeric()
num_domains_gt_res <- numeric()
num_domains3 <- numeric()
num_bounds <- numeric()

res <- c("5kb" ,"10kb", "25kb","50kb", "100kb")
for(i in 1:length(res)){
  domains <- read.table(paste0("Z:/TAD_data_analysis/K562/",
                               res[i],
                               "/K562_domain_data_",
                               as.integer(gsub("kb", "000", res[i])),
                               ".b.txt"), header=F)
  domains <- domains[,1:3]
  names(domains) <- c("Chromosome","Start","End")

  num_domains <- rbind(num_domains, nrow(domains))
  num_domains_lt_2mb <- rbind(num_domains_lt_2mb,length(which((domains$End - domains$Start)>=2000000)))

  domains2 <- domains[which((domains$End - domains$Start)<2000000),]

  num_domains2 <- rbind(num_domains2, nrow(domains2))
  num_domains_gt_res <- rbind(num_domains_gt_res, length(which((domains2$End - domains2$Start)<=(as.integer(gsub("kb", "000", res[i]))))))

  domains3 <- domains2[which((domains2$End - domains2$Start)>(as.integer(gsub("kb", "000", res[i])))),]

  num_domains3 <- rbind(num_domains3, nrow(domains3))

  bounds <- readRDS(paste0("Z:/TAD_data_analysis/K562/",
                           res[i],
                           "/training_testing/bounds.rds"))

  num_bounds <- rbind(num_bounds, length(bounds))
}

tad_sum_df_k562 <- cbind(c("5kb" ,"10kb", "25kb","50kb", "100kb"),
                    num_domains,
                    num_domains_lt_2mb,
                    num_domains2,
                    num_domains_gt_res,
                    num_domains3,
                    num_bounds)

```

### 2019-07-23 Scripts/evaluating_variable_importances.Rmd
updated with preprocessed tads

@@
                                         varimp_gm12878_100kb$aveimp100kb)
-names(all_varimps_gm12878_tfbs) <- c("Feature", "ave10kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
+names(all_varimps_gm12878_tfbs) <- c("Feature", "ave5kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
 all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[order(rowMeans(all_varimps_gm12878_tfbs[,-1]), decreasing = TRUE),]

### 2019-07-23 Manuscript/manuscript.Rmd
edits

@@
 ---
-title: Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance
-  Settings
+title: Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings
 csl: styles.ref/genomebiology.csl
@@
 Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at 4 resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
+We implemented a preprocessing step by removing TADs with lengths that exceeded 2 mb [???ref] (Supplementary Figure 1).
 To account for the varying levels of data resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1).
@@
 
+<!--
 ## INFLUENTIAL TFBS TENDED TO BE CLOSER TO BINS THAT OVERLAPPED WITH FLANKED TAD BOUNDARIES THAN THOSE THAT DID NOT
@@
 P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].](Figures/figure8_distance_boxplots_key_tfbs_gm12878_10kb.png)
+-->
 

### 2019-07-24 Scripts/functions_for_R_package/all_functions.R
included addition object to be returned

@@ -404,8 +404,8 @@ predict_at_bp_resolution_func <- function(bounds.GR, resolution, chromosome, ann
   predBound_gr_region <- do.call("c", predBound_gr_region)
   
   if(region==TRUE){
-    finer_res_list <- list(trueBound_gr_region,predBound_gr_region)
-  }else{finer_res_list <- list(trueBound_gr,predBound_gr)}
+    finer_res_list <- list(predprob_df, trueBound_gr_region,predBound_gr_region)
+  }else{finer_res_list <- list(predprob_df, trueBound_gr,predBound_gr)}
   names(finer_res_list) <- c("Called", "Predicted")
   
   return(finer_res_list)

### 2019-07-24 Scripts/functions_for_R_package/predict_at_bp_resolution_func.r

@@ -105,8 +105,8 @@ predict_at_bp_resolution_func <- function(bounds.GR, resolution, chromosome, ann
   predBound_gr_region <- do.call("c", predBound_gr_region)
   
   if(region==TRUE){
-    finer_res_list <- list(trueBound_gr_region,predBound_gr_region)
-  }else{finer_res_list <- list(trueBound_gr,predBound_gr)}
+    finer_res_list <- list(predprob_df,trueBound_gr_region,predBound_gr_region)
+  }else{finer_res_list <- list(predprob_df,trueBound_gr,predBound_gr)}
   names(finer_res_list) <- c("Called", "Predicted")
   
   return(finer_res_list)

### 2019-07-24 Manuscript/manuscript.Rmd
manuscript edits

@@
 
-Genomic annotation data in the form of cell type specific chromatin states, histone marks, and transcription factor binding sites (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 2).
+Genomic annotation data in the form of cell type specific chromatin states, histone marks, and transcription factor binding sites (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Tables 2-3).
 Functional annotations were represented by chromosome-specific regions on the linear genome obtained by ChIP-seq peak calling algorithms.
@@
 
-A total of 78 cell type specific functional genomic annotations derived from ChIP-Seq experiments (See Methods) for the GM12878 and K562 cell line were used to build the feature space of downstream predictive models.
+A total of 78 cell type specific functional genomic annotations derived from ChIP-Seq experiments (See Methods) for the GM12878 and K562 cell line were used to build the feature space of downstream predictive models (Supplementary Tables 2-3).
 We constructed three different predictor types for each functional genomic annotation.
@@
 **Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations (Figure 3C).
-A log2-transformation of distance was used to account for the skewness present in the distributions of distances (Supplementary Figures 1-2).
+A log2-transformation of distance was used to account for the skewness present in the distributions of distances <!--(Supplementary Figures 1-2)-->.
 Each predictor type provides a granular way to draw associations between functional genomic annotations and the spatial structure of the genome.
@@
 
-After determining the optimal set of data level characteristics, we then aimed to compare the performances of annotation-specifc models [???
-Never defined, what is this?; !!!defined above; should i mention again?], within each cell line and across resolution.
+After determining the optimal set of data level characteristics, we then aimed to compare the performances of annotation-specifc models, within each cell line and across resolution.
 In doing so, we inspected the proportion of predictive importance that was explained by each of the 3 groups of annotations (chromatin states, histone modifications, and transcription factor binding sites).
@@
 
+## Top TFBS were more enriched at predicted TAD boundaries at bp resolution than those provided by the TAD caller kb resolution
+
+We then shifted our focus toward developing a method to more accurately identify the location of TAD boundaries throughout the linear genome.
+Typical TAD callers are restricted to kilobase resolutions, which increase the variability in the actual location of a boundary.
+Instead, we aimed to predict the location of TAD boundaries at basepair resolution using optimally built cell line specific random forest classifiers.
+Each model was restricted to only include the most influential cell line specific TFBS, namely CTCF, RAD21, SMC3a, adn ZNF143.
+We then validated our models on cell line and chromosome specific regions of the genome, at base pair resolution.
+Predicted TAD boundary regions (PTBR) were identified as the collection of base pairs where the predicted probability vector was equal to 1, which denoted 100% accuracy in correctly identifying a basepair as a potential TAD boundary (Figure 7A).
+To allow for minor fluctuations in probability, any base pair given probability of 1 that was within a 10 bp window from another base pair also given probability of 1 were combined into one PTBR.
+PTBR were then compared to the called TAD boundary regions (CTBR), which here were defined by a 10 kb resolution flanking (See Methods).
+There were a total of 4663 identified PTBR compared to 237 CTBR.
+We found that approximately 59% (139 out of 237) of CTBR were overlapped by PTBR, indicating there are fluctuations in probabilities within the 20 kb regions defining CTBR (Figure 7B).
+We then compared distances between PTBRs and annotations versus CRBRs and annotations.
+We found that boundary regions predicted by our model at bp resolution experienced short distance profiles to known architectural proteins than did boundary regions called by Arrowhead.
+
+![**Comparing TAD boundaries regions predicted at bp resolution with those called at 10 kb resolution.** (A) A subset of the probabilitity vector for predicting TAD boundaries for chr22:17380000-chr22:18650000.
+The red dashed lines represent predicted TAD boundary regions, while the blue dashed lines represent called TAD boundaries identified by Arrowead at 10 kb.
+A called TAD boundary region is one flanked by 10 kb (B) Venn diagram illustrating the number of overlapped regions between predicted (red) and called (blue) TAD boundary regions.
+(C) Boxplots illustrating the distance profiles between each class of boundary regions (predicted-red; called-blue) and architechtural proteins known to be enriched at TAD boundaries.](Figures/pred_at_bp_res_plots.png)
+
 # DISCUSSION

### 2019-07-30 Scripts/comparing_predicted_vs_called_boundary_regions.Rmd
comparing predicted vs called boundary regions

---
title: "Comparing Predicted Boundaries vs Called Boundaries"
author: "Spiro Stilianoudakis"
date: "July 30, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(scales)
library(GGally)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggpubr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
```

# Testing what cutoff to use to determine predicted boundary regions

# Create granges from top tfbs

```{r}
source("C:/Users/stili/Documents/TAD_predictive_modeling/Scripts/functions_for_R_package/annots_to_granges_func.r")
#file_path="Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/chr22_tfbs_gm12878"
file_path="Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS"
annots.GR <- annots_to_granges_func(filepath=file_path)

```

## GM12878; chr22

### 10 pb cutoff

```{r}
toptfbs_10_gm12878_chr22 <- readRDS("Z:/TAD_data_analysis/GM12878/experiments/toptfbs_10.rds")

venn_cnt2venn <- function(venn_cnt){
  n <- which(colnames(venn_cnt)=="Counts") - 1
  SetNames=colnames(venn_cnt)[1:n]
  Weight=venn_cnt[,"Counts"]
  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
  Venn(SetNames=SetNames, Weight=Weight)
}

res <- makeVennDiagram(Peaks=list(toptfbs_10_gm12878_chr22[[3]], toptfbs_10_gm12878_chr22[[4]]),
                       NameOfPeaks=c("Called", "Predicted"),
                       connectedPeaks = "keepAll")
venn_gm12878_22 <- venn_cnt2venn(res$vennCounts)
venn_gm12878_22 <- compute.Venn(venn_gm12878_22)
gp <- VennThemes(venn_gm12878_22)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_5kb, 
                                                 gp = gp, 
                                                 show=list(Universe=FALSE))), 
                        top=textGrob("Boundary Region", 
                                     gp=gpar(fontsize=50)))

############################################################################################################

#PBNC

sh <- unique(subjectHits(findOverlaps(toptfbs_10_gm12878_chr22[[3]], toptfbs_10_gm12878_chr22[[4]])))
pbnc <- toptfbs_10_gm12878_chr22[[4]][-sh]

pbnc_to_ctcf <- GenometriCorrelation(pbnc,
                                     annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"], 
                                     chromosomes.length = max(end(pbnc),
                                                              end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

pbnc_to_rad21 <- GenometriCorrelation(pbnc,
                                      annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"], 
                                      chromosomes.length = max(end(pbnc),
                                                               end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

pbnc_to_smc3a <- GenometriCorrelation(pbnc,
                                      annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"], 
                                      chromosomes.length = max(end(pbnc),
                                                               end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

pbnc_to_znf143 <- GenometriCorrelation(pbnc,
                                       annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"], 
                                       chromosomes.length = max(end(pbnc),
                                                                end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"])),
                                       chromosomes.to.proceed = "chr22", 
                                       permut.number = 100,
                                       ecdf.area.permut.number = 100,
                                       mean.distance.permut.number = 100,
                                       jaccard.measure.permut.number = 100,
                                       keep.distributions = TRUE, 
                                       showProgressBar = TRUE)

############################################################################################################

#PAC
sh <- unique(subjectHits(findOverlaps(toptfbs_10_gm12878_chr22[[3]], toptfbs_10_gm12878_chr22[[4]])))
pac <- toptfbs_10_gm12878_chr22[[4]][sh]

pac_to_ctcf <- GenometriCorrelation(pac,
                                    annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"], 
                                    chromosomes.length = max(end(pac),
                                                             end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"])),
                                    chromosomes.to.proceed = "chr22", 
                                    permut.number = 100,
                                    ecdf.area.permut.number = 100,
                                    mean.distance.permut.number = 100,
                                    jaccard.measure.permut.number = 100,
                                    keep.distributions = TRUE, 
                                    showProgressBar = TRUE)

pac_to_rad21 <- GenometriCorrelation(pac,
                                     annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"], 
                                     chromosomes.length = max(end(pac),
                                                              end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

pac_to_smc3a <- GenometriCorrelation(pac,
                                     annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"], 
                                     chromosomes.length = max(end(pac),
                                                              end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

pac_to_znf143 <- GenometriCorrelation(pac,
                                      annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"], 
                                      chromosomes.length = max(end(pac),
                                                               end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

############################################################################################################

#CAP
qh <- unique(queryHits(findOverlaps(toptfbs_10_gm12878_chr22[[3]], toptfbs_10_gm12878_chr22[[4]])))
cap <- toptfbs_10_gm12878_chr22[[3]][qh]

cap_to_ctcf <- GenometriCorrelation(cap,
                                    annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"], 
                                    chromosomes.length = max(end(cap),
                                                             end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"])),
                                    chromosomes.to.proceed = "chr22", 
                                    permut.number = 100,
                                    ecdf.area.permut.number = 100,
                                    mean.distance.permut.number = 100,
                                    jaccard.measure.permut.number = 100,
                                    keep.distributions = TRUE, 
                                    showProgressBar = TRUE)

cap_to_rad21 <- GenometriCorrelation(cap,
                                     annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"], 
                                     chromosomes.length = max(end(cap),
                                                              end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

cap_to_smc3a <- GenometriCorrelation(cap,
                                     annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"], 
                                     chromosomes.length = max(end(cap),
                                                              end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

cap_to_znf143 <- GenometriCorrelation(cap,
                                      annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"], 
                                      chromosomes.length = max(end(cap),
                                                               end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

###########################################################################################################

#CBNP
qh <- unique(queryHits(findOverlaps(toptfbs_10_gm12878_chr22[[3]], toptfbs_10_gm12878_chr22[[4]])))
cbnp <- toptfbs_10_gm12878_chr22[[3]][-qh]

cbnp_to_ctcf <- GenometriCorrelation(cbnp,
                                     annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"], 
                                     chromosomes.length = max(end(cbnp),
                                                              end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

cbnp_to_rad21 <- GenometriCorrelation(cbnp,
                                      annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"], 
                                      chromosomes.length = max(end(cbnp),
                                                               end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

cbnp_to_smc3a <- GenometriCorrelation(cbnp,
                                      annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"], 
                                      chromosomes.length = max(end(cbnp),
                                                               end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

cbnp_to_znf143 <- GenometriCorrelation(cbnp,
                                       annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"], 
                                       chromosomes.length = max(end(cbnp),
                                                                end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"])),
                                       chromosomes.to.proceed = "chr22", 
                                       permut.number = 100,
                                       ecdf.area.permut.number = 100,
                                       mean.distance.permut.number = 100,
                                       jaccard.measure.permut.number = 100,
                                       keep.distributions = TRUE, 
                                       showProgressBar = TRUE)

############################################################################################################

pred_v_called_10_df <- data.frame(AbsoluteDist = c(#PBNC
  pbnc_to_ctcf@.Data[[1]]$absolute.min.distance.data,
  pbnc_to_rad21@.Data[[1]]$absolute.min.distance.data,
  pbnc_to_smc3a@.Data[[1]]$absolute.min.distance.data,
  pbnc_to_znf143@.Data[[1]]$absolute.min.distance.data,

  #PAC
  pac_to_ctcf@.Data[[1]]$absolute.min.distance.data,
  pac_to_rad21@.Data[[1]]$absolute.min.distance.data,
  pac_to_smc3a@.Data[[1]]$absolute.min.distance.data,
  pac_to_znf143@.Data[[1]]$absolute.min.distance.data,

  #CAP
  cap_to_ctcf@.Data[[1]]$absolute.min.distance.data,
  cap_to_rad21@.Data[[1]]$absolute.min.distance.data,
  cap_to_smc3a@.Data[[1]]$absolute.min.distance.data,
  cap_to_znf143@.Data[[1]]$absolute.min.distance.data,

  #CBNP
  cbnp_to_ctcf@.Data[[1]]$absolute.min.distance.data,
  cbnp_to_rad21@.Data[[1]]$absolute.min.distance.data,
  cbnp_to_smc3a@.Data[[1]]$absolute.min.distance.data,
  cbnp_to_znf143@.Data[[1]]$absolute.min.distance.data),
  Annotation = c(#PBNC
    rep("CTCF",length(pbnc_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("RAD21",length(pbnc_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("SMC3a",length(pbnc_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("ZNF143",length(pbnc_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #PAC
    rep("CTCF",length(pac_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("RAD21",length(pac_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("SMC3a",length(pac_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("ZNF143",length(pac_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #CAP
    rep("CTCF",length(cap_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("RAD21",length(cap_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("SMC3a",length(cap_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("ZNF143",length(cap_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #CBNP
    rep("CTCF",length(cbnp_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("RAD21",length(cbnp_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("SMC3a",length(cbnp_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("ZNF143",length(cbnp_to_znf143@.Data[[1]]$absolute.min.distance.data))),
  BoundReg = c(#PBNC
    rep("PBNC", length(pbnc_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("PBNC", length(pbnc_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("PBNC", length(pbnc_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("PBNC", length(pbnc_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #PAC
    rep("PAC", length(pac_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("PAC", length(pac_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("PAC", length(pac_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("PAC", length(pac_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #CAP
    rep("CAP", length(cap_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("CAP", length(cap_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("CAP", length(cap_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("CAP", length(cap_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #CBNP
    rep("CBNP", length(cbnp_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("CBNP", length(cbnp_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("CBNP", length(cbnp_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("CBNP", length(cbnp_to_znf143@.Data[[1]]$absolute.min.distance.data))))
pred_v_called_10_df$BoundReg <- factor(pred_v_called_10_df$BoundReg, levels=c("PBNC", "PAC", "CAP", "CBNP"))
pred_v_called_10_df$log2AbsoluteDist <- log(pred_v_called_10_df$AbsoluteDist + 1, base = 2)

ggplot(pred_v_called_10_df, aes(x=BoundReg, y = log2AbsoluteDist, fill=BoundReg))  + 
  facet_grid(~ Annotation) +    
  stat_boxplot(geom ='errorbar', width = 0.2) + 
  geom_boxplot(outlier.shape = NA) +
  #stat_compare_means(comparisons = list( c("PBNC", "PAC"), 
  #                                       c("PBNC", "CAP"), 
  #                                       c("PBNC", "CBNP"),
  #                                       c("PAC", "CAP"),
  #                                       c("PAC", "CBNP"),
  #                                       c("CAP", "CBNP")),
  #                   vjust = 0,
  #                   #textsize = 4,
  #                   #size = .5,
  #                   #step_increase = .08, 
  #                   method = "wilcox.test", 
  #                   label = "p.format") +
  geom_signif(test = "wilcox.test", 
              comparisons = list( c("PBNC", "PAC"), 
                                  c("PBNC", "CAP"), 
                                  c("PBNC", "CBNP"),
                                  c("PAC", "CAP"),
                                  c("PAC", "CBNP"),
                                  c("CAP", "CBNP")),
              vjust = 0,
              textsize = 4,
              size = .5,
              step_increase = .08) +
  theme_minimal()+
  theme_bw()+
  ylab("Log2 Distance to Annotation")+
  xlab("") +
  ggtitle("10 bp width cutoff")+
  scale_fill_discrete(name="Boundary Region")+
  scale_x_discrete(labels=c("PBNC"="Predicted but\nnot called",
                           "PAC"="Predicted\nand called",
                           "CAP"="Called and\npredicted",
                           "CBNP"="Called but not\npredicted"))+
  #guides(color=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

```

### Median length of adjacent 1bp cutoff

```{r}
toptfbs_median_gm12878_chr22 <- readRDS("Z:/TAD_data_analysis/GM12878/experiments/toptfbs_median.rds")

venn_cnt2venn <- function(venn_cnt){
  n <- which(colnames(venn_cnt)=="Counts") - 1
  SetNames=colnames(venn_cnt)[1:n]
  Weight=venn_cnt[,"Counts"]
  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
  Venn(SetNames=SetNames, Weight=Weight)
}

res <- makeVennDiagram(Peaks=list(toptfbs_median_gm12878_chr22[[3]], toptfbs_median_gm12878_chr22[[4]]),
                       NameOfPeaks=c("Called", "Predicted"),
                       connectedPeaks = "keepAll")
venn_gm12878_22 <- venn_cnt2venn(res$vennCounts)
venn_gm12878_22 <- compute.Venn(venn_gm12878_22)
gp <- VennThemes(venn_gm12878_22)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_5kb, 
                                                 gp = gp, 
                                                 show=list(Universe=FALSE))), 
                        top=textGrob("Boundary Region", 
                                     gp=gpar(fontsize=50)))

############################################################################################################

#PBNC

sh <- unique(subjectHits(findOverlaps(toptfbs_median_gm12878_chr22[[3]], toptfbs_median_gm12878_chr22[[4]])))
pbnc <- toptfbs_median_gm12878_chr22[[4]][-sh]

pbnc_to_ctcf <- GenometriCorrelation(pbnc,
                                     annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"], 
                                     chromosomes.length = max(end(pbnc),
                                                              end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

pbnc_to_rad21 <- GenometriCorrelation(pbnc,
                                      annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"], 
                                      chromosomes.length = max(end(pbnc),
                                                               end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

pbnc_to_smc3a <- GenometriCorrelation(pbnc,
                                      annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"], 
                                      chromosomes.length = max(end(pbnc),
                                                               end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

pbnc_to_znf143 <- GenometriCorrelation(pbnc,
                                       annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"], 
                                       chromosomes.length = max(end(pbnc),
                                                                end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"])),
                                       chromosomes.to.proceed = "chr22", 
                                       permut.number = 100,
                                       ecdf.area.permut.number = 100,
                                       mean.distance.permut.number = 100,
                                       jaccard.measure.permut.number = 100,
                                       keep.distributions = TRUE, 
                                       showProgressBar = TRUE)

############################################################################################################

#PAC
sh <- unique(subjectHits(findOverlaps(toptfbs_median_gm12878_chr22[[3]], toptfbs_median_gm12878_chr22[[4]])))
pac <- toptfbs_median_gm12878_chr22[[4]][sh]

pac_to_ctcf <- GenometriCorrelation(pac,
                                    annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"], 
                                    chromosomes.length = max(end(pac),
                                                             end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"])),
                                    chromosomes.to.proceed = "chr22", 
                                    permut.number = 100,
                                    ecdf.area.permut.number = 100,
                                    mean.distance.permut.number = 100,
                                    jaccard.measure.permut.number = 100,
                                    keep.distributions = TRUE, 
                                    showProgressBar = TRUE)

pac_to_rad21 <- GenometriCorrelation(pac,
                                     annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"], 
                                     chromosomes.length = max(end(pac),
                                                              end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

pac_to_smc3a <- GenometriCorrelation(pac,
                                     annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"], 
                                     chromosomes.length = max(end(pac),
                                                              end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

pac_to_znf143 <- GenometriCorrelation(pac,
                                      annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"], 
                                      chromosomes.length = max(end(pac),
                                                               end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

############################################################################################################

#CAP
qh <- unique(queryHits(findOverlaps(toptfbs_median_gm12878_chr22[[3]], toptfbs_median_gm12878_chr22[[4]])))
cap <- toptfbs_median_gm12878_chr22[[3]][qh]

cap_to_ctcf <- GenometriCorrelation(cap,
                                    annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"], 
                                    chromosomes.length = max(end(cap),
                                                             end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"])),
                                    chromosomes.to.proceed = "chr22", 
                                    permut.number = 100,
                                    ecdf.area.permut.number = 100,
                                    mean.distance.permut.number = 100,
                                    jaccard.measure.permut.number = 100,
                                    keep.distributions = TRUE, 
                                    showProgressBar = TRUE)

cap_to_rad21 <- GenometriCorrelation(cap,
                                     annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"], 
                                     chromosomes.length = max(end(cap),
                                                              end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

cap_to_smc3a <- GenometriCorrelation(cap,
                                     annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"], 
                                     chromosomes.length = max(end(cap),
                                                              end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

cap_to_znf143 <- GenometriCorrelation(cap,
                                      annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"], 
                                      chromosomes.length = max(end(cap),
                                                               end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

###########################################################################################################

#CBNP
qh <- unique(queryHits(findOverlaps(toptfbs_median_gm12878_chr22[[3]], toptfbs_median_gm12878_chr22[[4]])))
cbnp <- toptfbs_median_gm12878_chr22[[3]][-qh]

cbnp_to_ctcf <- GenometriCorrelation(cbnp,
                                     annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"], 
                                     chromosomes.length = max(end(cbnp),
                                                              end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

cbnp_to_rad21 <- GenometriCorrelation(cbnp,
                                      annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"], 
                                      chromosomes.length = max(end(cbnp),
                                                               end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

cbnp_to_smc3a <- GenometriCorrelation(cbnp,
                                      annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"], 
                                      chromosomes.length = max(end(cbnp),
                                                               end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

cbnp_to_znf143 <- GenometriCorrelation(cbnp,
                                       annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"], 
                                       chromosomes.length = max(end(cbnp),
                                                                end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"])),
                                       chromosomes.to.proceed = "chr22", 
                                       permut.number = 100,
                                       ecdf.area.permut.number = 100,
                                       mean.distance.permut.number = 100,
                                       jaccard.measure.permut.number = 100,
                                       keep.distributions = TRUE, 
                                       showProgressBar = TRUE)

############################################################################################################

pred_v_called_median_df <- data.frame(AbsoluteDist = c(#PBNC
  pbnc_to_ctcf@.Data[[1]]$absolute.min.distance.data,
  pbnc_to_rad21@.Data[[1]]$absolute.min.distance.data,
  pbnc_to_smc3a@.Data[[1]]$absolute.min.distance.data,
  pbnc_to_znf143@.Data[[1]]$absolute.min.distance.data,

  #PAC
  pac_to_ctcf@.Data[[1]]$absolute.min.distance.data,
  pac_to_rad21@.Data[[1]]$absolute.min.distance.data,
  pac_to_smc3a@.Data[[1]]$absolute.min.distance.data,
  pac_to_znf143@.Data[[1]]$absolute.min.distance.data,

  #CAP
  cap_to_ctcf@.Data[[1]]$absolute.min.distance.data,
  cap_to_rad21@.Data[[1]]$absolute.min.distance.data,
  cap_to_smc3a@.Data[[1]]$absolute.min.distance.data,
  cap_to_znf143@.Data[[1]]$absolute.min.distance.data,

  #CBNP
  cbnp_to_ctcf@.Data[[1]]$absolute.min.distance.data,
  cbnp_to_rad21@.Data[[1]]$absolute.min.distance.data,
  cbnp_to_smc3a@.Data[[1]]$absolute.min.distance.data,
  cbnp_to_znf143@.Data[[1]]$absolute.min.distance.data),
  Annotation = c(#PBNC
    rep("CTCF",length(pbnc_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("RAD21",length(pbnc_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("SMC3a",length(pbnc_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("ZNF143",length(pbnc_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #PAC
    rep("CTCF",length(pac_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("RAD21",length(pac_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("SMC3a",length(pac_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("ZNF143",length(pac_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #CAP
    rep("CTCF",length(cap_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("RAD21",length(cap_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("SMC3a",length(cap_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("ZNF143",length(cap_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #CBNP
    rep("CTCF",length(cbnp_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("RAD21",length(cbnp_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("SMC3a",length(cbnp_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("ZNF143",length(cbnp_to_znf143@.Data[[1]]$absolute.min.distance.data))),
  BoundReg = c(#PBNC
    rep("PBNC", length(pbnc_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("PBNC", length(pbnc_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("PBNC", length(pbnc_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("PBNC", length(pbnc_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #PAC
    rep("PAC", length(pac_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("PAC", length(pac_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("PAC", length(pac_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("PAC", length(pac_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #CAP
    rep("CAP", length(cap_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("CAP", length(cap_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("CAP", length(cap_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("CAP", length(cap_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #CBNP
    rep("CBNP", length(cbnp_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("CBNP", length(cbnp_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("CBNP", length(cbnp_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("CBNP", length(cbnp_to_znf143@.Data[[1]]$absolute.min.distance.data))))
pred_v_called_median_df$BoundReg <- factor(pred_v_called_median_df$BoundReg, levels=c("PBNC", "PAC", "CAP", "CBNP"))
pred_v_called_median_df$log2AbsoluteDist <- log(pred_v_called_median_df$AbsoluteDist + 1, base = 2)

ggplot(pred_v_called_median_df, aes(x=BoundReg, y = log2AbsoluteDist, fill=BoundReg))  + 
  facet_grid(~ Annotation) +    
  stat_boxplot(geom ='errorbar', width = 0.2) + 
  geom_boxplot(outlier.shape = NA) +
  #stat_compare_means(comparisons = list( c("PBNC", "PAC"), 
  #                                       c("PBNC", "CAP"), 
  #                                       c("PBNC", "CBNP"),
  #                                       c("PAC", "CAP"),
  #                                       c("PAC", "CBNP"),
  #                                       c("CAP", "CBNP")),
  #                   vjust = 0,
  #                   #textsize = 4,
  #                   #size = .5,
  #                   #step_increase = .08, 
  #                   method = "wilcox.test", 
  #                   label = "p.format") +
  geom_signif(test = "wilcox.test", 
            comparisons = list( c("PBNC", "PAC"), 
                                c("PBNC", "CAP"), 
                                c("PBNC", "CBNP"),
                                c("PAC", "CAP"),
                                c("PAC", "CBNP"),
                                c("CAP", "CBNP")),
            vjust = 0,
            textsize = 4,
            size = .5,
            step_increase = .08) +
  theme_minimal()+
  theme_bw()+
  ylab("Log2 Distance to Annotation")+
  xlab("") +
  ggtitle("Median width cutoff")+
  scale_fill_discrete(name="Boundary Region")+
  scale_x_discrete(labels=c("PBNC"="Predicted but\nnot called",
                            "PAC"="Predicted\nand called",
                            "CAP"="Called and\npredicted",
                            "CBNP"="Called but not\npredicted"))+
  #guides(color=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

```

### Mean length of adjacent 1bp cutoff

```{r}
toptfbs_mean_gm12878_chr22 <- readRDS("Z:/TAD_data_analysis/GM12878/experiments/toptfbs_mean.rds")

venn_cnt2venn <- function(venn_cnt){
  n <- which(colnames(venn_cnt)=="Counts") - 1
  SetNames=colnames(venn_cnt)[1:n]
  Weight=venn_cnt[,"Counts"]
  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
  Venn(SetNames=SetNames, Weight=Weight)
}

res <- makeVennDiagram(Peaks=list(toptfbs_mean_gm12878_chr22[[3]], toptfbs_mean_gm12878_chr22[[4]]),
                       NameOfPeaks=c("Called", "Predicted"),
                       connectedPeaks = "keepAll")
venn_gm12878_22 <- venn_cnt2venn(res$vennCounts)
venn_gm12878_22 <- compute.Venn(venn_gm12878_22)
gp <- VennThemes(venn_gm12878_22)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_5kb, 
                                                 gp = gp, 
                                                 show=list(Universe=FALSE))), 
                        top=textGrob("Boundary Region", 
                                     gp=gpar(fontsize=50)))

############################################################################################################

#PBNC

sh <- unique(subjectHits(findOverlaps(toptfbs_mean_gm12878_chr22[[3]], toptfbs_mean_gm12878_chr22[[4]])))
pbnc <- toptfbs_mean_gm12878_chr22[[4]][-sh]

pbnc_to_ctcf <- GenometriCorrelation(pbnc,
                                     annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"], 
                                     chromosomes.length = max(end(pbnc),
                                                              end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

pbnc_to_rad21 <- GenometriCorrelation(pbnc,
                                      annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"], 
                                      chromosomes.length = max(end(pbnc),
                                                               end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

pbnc_to_smc3a <- GenometriCorrelation(pbnc,
                                      annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"], 
                                      chromosomes.length = max(end(pbnc),
                                                               end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

pbnc_to_znf143 <- GenometriCorrelation(pbnc,
                                       annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"], 
                                       chromosomes.length = max(end(pbnc),
                                                                end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"])),
                                       chromosomes.to.proceed = "chr22", 
                                       permut.number = 100,
                                       ecdf.area.permut.number = 100,
                                       mean.distance.permut.number = 100,
                                       jaccard.measure.permut.number = 100,
                                       keep.distributions = TRUE, 
                                       showProgressBar = TRUE)

############################################################################################################

#PAC
sh <- unique(subjectHits(findOverlaps(toptfbs_mean_gm12878_chr22[[3]], toptfbs_mean_gm12878_chr22[[4]])))
pac <- toptfbs_mean_gm12878_chr22[[4]][sh]

pac_to_ctcf <- GenometriCorrelation(pac,
                                    annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"], 
                                    chromosomes.length = max(end(pac),
                                                             end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"])),
                                    chromosomes.to.proceed = "chr22", 
                                    permut.number = 100,
                                    ecdf.area.permut.number = 100,
                                    mean.distance.permut.number = 100,
                                    jaccard.measure.permut.number = 100,
                                    keep.distributions = TRUE, 
                                    showProgressBar = TRUE)

pac_to_rad21 <- GenometriCorrelation(pac,
                                     annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"], 
                                     chromosomes.length = max(end(pac),
                                                              end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

pac_to_smc3a <- GenometriCorrelation(pac,
                                     annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"], 
                                     chromosomes.length = max(end(pac),
                                                              end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

pac_to_znf143 <- GenometriCorrelation(pac,
                                      annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"], 
                                      chromosomes.length = max(end(pac),
                                                               end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

############################################################################################################

#CAP
qh <- unique(queryHits(findOverlaps(toptfbs_mean_gm12878_chr22[[3]], toptfbs_mean_gm12878_chr22[[4]])))
cap <- toptfbs_mean_gm12878_chr22[[3]][qh]

cap_to_ctcf <- GenometriCorrelation(cap,
                                    annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"], 
                                    chromosomes.length = max(end(cap),
                                                             end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"])),
                                    chromosomes.to.proceed = "chr22", 
                                    permut.number = 100,
                                    ecdf.area.permut.number = 100,
                                    mean.distance.permut.number = 100,
                                    jaccard.measure.permut.number = 100,
                                    keep.distributions = TRUE, 
                                    showProgressBar = TRUE)

cap_to_rad21 <- GenometriCorrelation(cap,
                                     annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"], 
                                     chromosomes.length = max(end(cap),
                                                              end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

cap_to_smc3a <- GenometriCorrelation(cap,
                                     annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"], 
                                     chromosomes.length = max(end(cap),
                                                              end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

cap_to_znf143 <- GenometriCorrelation(cap,
                                      annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"], 
                                      chromosomes.length = max(end(cap),
                                                               end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

###########################################################################################################

#CBNP
qh <- unique(queryHits(findOverlaps(toptfbs_mean_gm12878_chr22[[3]], toptfbs_mean_gm12878_chr22[[4]])))
cbnp <- toptfbs_mean_gm12878_chr22[[3]][-qh]

cbnp_to_ctcf <- GenometriCorrelation(cbnp,
                                     annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"], 
                                     chromosomes.length = max(end(cbnp),
                                                              end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr22"])),
                                     chromosomes.to.proceed = "chr22", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

cbnp_to_rad21 <- GenometriCorrelation(cbnp,
                                      annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"], 
                                      chromosomes.length = max(end(cbnp),
                                                               end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

cbnp_to_smc3a <- GenometriCorrelation(cbnp,
                                      annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"], 
                                      chromosomes.length = max(end(cbnp),
                                                               end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr22"])),
                                      chromosomes.to.proceed = "chr22", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

cbnp_to_znf143 <- GenometriCorrelation(cbnp,
                                       annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"], 
                                       chromosomes.length = max(end(cbnp),
                                                                end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr22"])),
                                       chromosomes.to.proceed = "chr22", 
                                       permut.number = 100,
                                       ecdf.area.permut.number = 100,
                                       mean.distance.permut.number = 100,
                                       jaccard.measure.permut.number = 100,
                                       keep.distributions = TRUE, 
                                       showProgressBar = TRUE)

############################################################################################################

pred_v_called_mean_df <- data.frame(AbsoluteDist = c(#PBNC
                                            pbnc_to_ctcf@.Data[[1]]$absolute.min.distance.data,
                                            pbnc_to_rad21@.Data[[1]]$absolute.min.distance.data,
                                            pbnc_to_smc3a@.Data[[1]]$absolute.min.distance.data,
                                            pbnc_to_znf143@.Data[[1]]$absolute.min.distance.data,

                                            #PAC
                                            pac_to_ctcf@.Data[[1]]$absolute.min.distance.data,
                                            pac_to_rad21@.Data[[1]]$absolute.min.distance.data,
                                            pac_to_smc3a@.Data[[1]]$absolute.min.distance.data,
                                            pac_to_znf143@.Data[[1]]$absolute.min.distance.data,

                                            #CAP
                                            cap_to_ctcf@.Data[[1]]$absolute.min.distance.data,
                                            cap_to_rad21@.Data[[1]]$absolute.min.distance.data,
                                            cap_to_smc3a@.Data[[1]]$absolute.min.distance.data,
                                            cap_to_znf143@.Data[[1]]$absolute.min.distance.data,

                                            #CBNP
                                            cbnp_to_ctcf@.Data[[1]]$absolute.min.distance.data,
                                            cbnp_to_rad21@.Data[[1]]$absolute.min.distance.data,
                                            cbnp_to_smc3a@.Data[[1]]$absolute.min.distance.data,
                                            cbnp_to_znf143@.Data[[1]]$absolute.min.distance.data),
                               Annotation = c(#PBNC
                                            rep("CTCF",length(pbnc_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
                                            rep("RAD21",length(pbnc_to_rad21@.Data[[1]]$absolute.min.distance.data)),
                                            rep("SMC3a",length(pbnc_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
                                            rep("ZNF143",length(pbnc_to_znf143@.Data[[1]]$absolute.min.distance.data)),

                                            #PAC
                                            rep("CTCF",length(pac_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
                                            rep("RAD21",length(pac_to_rad21@.Data[[1]]$absolute.min.distance.data)),
                                            rep("SMC3a",length(pac_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
                                            rep("ZNF143",length(pac_to_znf143@.Data[[1]]$absolute.min.distance.data)),

                                            #CAP
                                            rep("CTCF",length(cap_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
                                            rep("RAD21",length(cap_to_rad21@.Data[[1]]$absolute.min.distance.data)),
                                            rep("SMC3a",length(cap_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
                                            rep("ZNF143",length(cap_to_znf143@.Data[[1]]$absolute.min.distance.data)),

                                            #CBNP
                                            rep("CTCF",length(cbnp_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
                                            rep("RAD21",length(cbnp_to_rad21@.Data[[1]]$absolute.min.distance.data)),
                                            rep("SMC3a",length(cbnp_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
                                            rep("ZNF143",length(cbnp_to_znf143@.Data[[1]]$absolute.min.distance.data))),
                               BoundReg = c(#PBNC
                                            rep("PBNC", length(pbnc_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
                                            rep("PBNC", length(pbnc_to_rad21@.Data[[1]]$absolute.min.distance.data)),
                                            rep("PBNC", length(pbnc_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
                                            rep("PBNC", length(pbnc_to_znf143@.Data[[1]]$absolute.min.distance.data)),

                                            #PAC
                                            rep("PAC", length(pac_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
                                            rep("PAC", length(pac_to_rad21@.Data[[1]]$absolute.min.distance.data)),
                                            rep("PAC", length(pac_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
                                            rep("PAC", length(pac_to_znf143@.Data[[1]]$absolute.min.distance.data)),

                                            #CAP
                                            rep("CAP", length(cap_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
                                            rep("CAP", length(cap_to_rad21@.Data[[1]]$absolute.min.distance.data)),
                                            rep("CAP", length(cap_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
                                            rep("CAP", length(cap_to_znf143@.Data[[1]]$absolute.min.distance.data)),

                                            #CBNP
                                            rep("CBNP", length(cbnp_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
                                            rep("CBNP", length(cbnp_to_rad21@.Data[[1]]$absolute.min.distance.data)),
                                            rep("CBNP", length(cbnp_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
                                            rep("CBNP", length(cbnp_to_znf143@.Data[[1]]$absolute.min.distance.data))))
pred_v_called_mean_df$BoundReg <- factor(pred_v_called_mean_df$BoundReg, levels=c("PBNC", "PAC", "CAP", "CBNP"))
pred_v_called_mean_df$log2AbsoluteDist <- log(pred_v_called_mean_df$AbsoluteDist + 1, base = 2)

ggplot(pred_v_called_mean_df, aes(x=BoundReg, y = log2AbsoluteDist, fill=BoundReg))  + 
  facet_grid(~ Annotation) +    
  stat_boxplot(geom ='errorbar', width = 0.2) + 
  geom_boxplot(outlier.shape = NA) +
  #stat_compare_means(comparisons = list( c("PBNC", "PAC"), 
  #                                       c("PBNC", "CAP"), 
  #                                       c("PBNC", "CBNP"),
  #                                       c("PAC", "CAP"),
  #                                       c("PAC", "CBNP"),
  #                                       c("CAP", "CBNP")),
  #                   vjust = 0,
  #                   #textsize = 4,
  #                   #size = .5,
  #                   #step_increase = .08, 
  #                   method = "wilcox.test", 
  #                   label = "p.format") +
  geom_signif(test = "wilcox.test", 
            comparisons = list( c("PBNC", "PAC"), 
                                c("PBNC", "CAP"), 
                                c("PBNC", "CBNP"),
                                c("PAC", "CAP"),
                                c("PAC", "CBNP"),
                                c("CAP", "CBNP")),
            vjust = 0,
            textsize = 4,
            size = .5,
            step_increase = .08) +
  theme_minimal()+
  theme_bw()+
  ylab("Log2 Distance to Annotation")+
  xlab("") +
  ggtitle("Mean width cutoff")+
  scale_fill_discrete(name="Boundary Region")+
  scale_x_discrete(labels=c("PBNC"="Predicted but\nnot called",
                            "PAC"="Predicted\nand called",
                            "CAP"="Called and\npredicted",
                            "CBNP"="Called but not\npredicted"))+
  #guides(color=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

```

### 2019-07-30 Scripts/evaluating_rfe_across_chromosomes.Rmd
evaluating feature selection using rfe importances across chromosomes

---
title: "Evaluating RFE across chromosomes"
author: "Spiro Stilianoudakis"
date: "July 30, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(scales)
library(GGally)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggpubr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
```

# Optimal parameters: 10 kb, TFBS, distance type predictors, SMOTE resampling

## Determining number of annotations

### Line plot

```{r}

rfeperchr <- data.frame()

chrs <- paste0("chr", c(1:8,10:22))
for(i in c("GM12878","K562")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/smote/distance/enet/rfeModelResultsList.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,1:2]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

rfeperchr_summ <- rfeperchr %>%
  group_by(CL, Variables) %>%
  dplyr::summarise(AveMCC = mean(MCC, na.rm = TRUE),
            AveMCCSD = sd(MCC, na.rm = TRUE))

ggplot(rfeperchr_summ, aes(x=Variables, y=AveMCC, color=CL)) + 
    geom_errorbar(aes(ymin=AveMCC-AveMCCSD, ymax=AveMCC+AveMCCSD), 
                  width=2, 
                  position=position_dodge(2),
                  size=1) +
    geom_line(position=position_dodge(2), size=1) +
    geom_point(position=position_dodge(2), size=2) +
    xlab("Number of top ranked annotations") +
    ylab("Cross-Validated MCC") +
    #ylim(.3,.8)+
    scale_color_discrete(name="Cell line")+
    scale_x_continuous(breaks = c(2,4,8,16,32,52),
                     labels = c(2,4,8,16,32,52))+
    theme_minimal() +
    theme_bw()+
    theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")
```

### Importance heatmap

```{r}

rfeperchr <- data.frame()

set.size = 8
chrs <- paste0("chr", c(1:8,10:22))
for(i in c("GM12878","K562")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/smote/distance/enet/rfeModelResultsList.rds"))
    rfeModelResults <- rfeModelResultsList[[2]]
    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size,]
    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)[1:set.size]
    rfe.set <- rfe.set[rfe.order, ]
    rfe.set$CL <- i
    rfe.set$Chromosome <- chrs[k]

    rfeperchr <- rbind.data.frame(rfeperchr, rfe.set)
  }
}

rfeperchr$Group.1 <- gsub(paste0(c("Gm12878-", 
                                   "K562-", 
                                   "-Haib", 
                                   "-Sydh",
                                   "-Uta",
                                   "-Uw",
                                   "-Broad",
                                   "-Uchicago"), collapse = "|"), "", rfeperchr$Group.1)
names(rfeperchr)[1:2] <- c("Feature", "Importance")

rfeperchr_summ <- rfeperchr %>%
  group_by(CL, Feature) %>%
  dplyr::summarise(AveImp = mean(Importance, na.rm = TRUE),
            AveImpSD = sd(Importance, na.rm = TRUE)) %>%
  dplyr::arrange(CL, desc(AveImp))

rfegm12878 <- rfeperchr[which(rfeperchr$CL=="GM12878"),]
rfegm12878 <- reshape(rfegm12878[,c(1,2,4)], idvar = "Feature", timevar = "Chromosome", direction = "wide")
names(rfegm12878)[-1] <- paste0("CHR", c(1:8,10:22)) 
rfegm12878.mat <- as.matrix(rfegm12878[,-1])
rownames(rfegm12878.mat) <- rfegm12878$Feature
rfegm12878.mat[is.na(rfegm12878.mat)] <- 0
rfegm12878.mat <- apply(rfegm12878.mat,2,rev)

#using heatmap.2
distance.col = dist(rfegm12878.mat, method = "euclidean")
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "pink", "red"))(rcol(rfegm12878.mat))
heatmap.2(t(rfegm12878.mat),
          #labRow=rownames(rfegm12878.mat),
          #labCol=colnames(rfegm12878.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="column",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=1.5,
          cexCol=1.5,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          rowsep=0:nrow(t(rfegm12878.mat)),
          colsep=0:ncol(t(rfegm12878.mat)),
          sepwidth=c(0.001,0.001),
          sepcolor="black"
) 
```

### 2019-08-01 Papers.Rmd
Add 3DEpiLoop paper

@@
 Many other in my `Zotero/Genome/Sequencing/Epigenomics/machine learning` collection
+
+- Al Bkhetan, Ziad, and Dariusz Plewczynski.
+“Three-Dimensional Epigenome Statistical Model: Genome-Wide Chromatin Looping Prediction.” Scientific Reports 8, no.
+1 (December 2018).
+https://doi.org/10.1038/s41598-018-23276-8.
+- 3DEpiLoop - prediction of 3D interactions from 1D epigenomic profiles using Random Forest trained on CTCF peaks (histone modifications are the most important predictors, and TFBSs).
+https://bitbucket.org/4dnucleome/3depiloop
 

### 2019-08-01 Papers.Rmd
Add LSTM TAD prediction paper

@@
 CTCF orientation is important, Figure 2a, detected by FIMO tool. https://github.com/tuantrieu/DeepMILO
+
+- Rozenwald, Michal, Ekaterina Khrameeva, Grigory Sapunov, and Mikhail Gelfand.
+“Prediction of 3D Chromatin Structure Using Recurrent Neural Networks.” In 2018 IEEE International Conference on Bioinformatics and Biomedicine (BIBM), 2488–2488.
+IEEE, 2018.
+- Prediction of TAD boundaries using penalized regressions and RNNs.
+RNN with LSTM units captures the sequential ordering of the genome, distance.
+Drosophila data, Armatus for TAD calling.
+PyTorch and Keras implementation.
 

### 2019-08-01 Manuscript/manuscript.Rmd
editted abstract for BSRS

@@
 
-**Background.** Topologically Associated Domains (TADs) represent fundamental building blocks of the three-dimensional (3D) genome organization and regulation.
-Several epigenetic marks, such as CTCF, are highly enriched at TAD boundaries, suggesting a strong epigenetic component of TAD boundary formation.
-Several methods have been developed to leverage the growing amount of (epi)genomic annotation data for predicting TAD boundaries; however, they overlooked key characteristics of the data, such as spatial associations between a genomic annotation and a boundary.
-Furthermore, the number of regions containing TAD boundaries is much smaller than the rest of the genome, creating a class imbalance problem.
+**Background.** Topologically Associated Domains (TADs) represent fundamental building blocks that lead to the organization and regulation of the three-dimensional (3D) genome.
+The enrichment of several epigenetic marks at TAD boundaries suggests a strong epigenetic component of TAD boundary formation.
+Several methods have been developed to leverage the growing amount of (epi)genomic annotation data for predicting TAD boundaries; however, they overlooked key characteristics of the data including spatial associations between genomic annotations and boundaries, as well as the severe imbalance in TAD-boundary vs non-TAD boundary defined genomic regions.
+Furthermore, resolution of Hi-C data remains well below the resolution of epigenomic assays (hundredths of bases for ChIP-seq) affecting the ability of Hi-C sequencing in discerning gene-level features of chromatin.
+This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited our understanding of epigenomic regulation of gene expression and its potential link to chromatin architecture.
 
-**Methods.** To investigate the problem of spatial genomic relationships and class imbalance problem, we developed an ensemble framework for optimizing prediction of TAD boundaries.
-We utilized several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) coupled with various metrics for classifier performance evaluation (Area Under Receiver Operating Characteristics (AUCROC) curve, Precision-Recall curve (AUPRC), F1, Matthews Correlation Coefficient (MCC), among others) to select the best predictive model in class imbalance settings.
+**Methods.** We first developed an ensemble framework for optimizing data level characteristics necessary for TAD boundary prediction including combinations of 5 Hi-C data resolutions (5 kb to 100 kb), 3 spatially defined predictor types, and 4 re-sampling techniques, across the GM12878 and K562 cell lines.
+We then aimed to predict TAD boundary location on a 1D genomic map by validating optimally built cell line specific models at basepair resolution.
 
-**Results.** Using different feature engineering and resampling strategies, coupled with elastic net-based feature selection, we systematically compared the performance of models predicting the location of TAD boundaries (Gm12878 and K562 Hi-C data at 10kb to 100kb resolutions).
-Precision-Recall curves were found to be best suited for evaluating model performance in class imbalance settings.
-Random undersampling and SMOTE-resampled data performed best for optimal parameter selection.
-Transcription Factor Binding Sites (TFBSs) were best type of genomic annotations for predicting TAD boundaries than histone modifications and chromatin states; we identified well-known CTCF, SMC3, RAD21, and several novel TFBSs as best predictors of TAD boundaries.
-Importantly, spatial relationships (distance between TAD boundaries and genomic annotations) were best predictors of TAD boundaries as compared with commonly used overlap counts or percent overlap measures.
+**Results.** We demonstrate with our ensemble framework that cell line specific random forest classifiers built on 10 kb resolution Hi-C data, with distance-type predictors, using SMOTE (*Synthetic Minority Oversampling Technique*) re-sampling yield optimal predictive performances, and outperform existing methods.
+Cell specific transcription factor binding sites (TFBS) were the best type of genomic annotations for predicting TAD boundaries when directly compared with histone modifications and chromatin states; we identified the well-known CTCF, SMC3, RAD21, and ZNF143 TFBS known to be enriched at TAD boundaries.
+Additionally, TAD boundary regions predicted at basepair resolution using our optimally built cell line specific models were found to be significantly closer to known enriched epigenomic marks indicating more accurate identification of TAD boundaries than existing Hi-C sequencing technologies.
 

### 2019-08-02 Scripts/comparing_predicted_vs_called_boundary_regions.Rmd
edits

@@
 gp[["SetText"]][["Set2"]]$cex <- 2
-gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_5kb, 
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_gm12878_22, 
                                                  gp = gp, 

### 2019-08-09 Scripts/comparing_predicted_boundaries_vs_called_boundaries.Rmd
initial commit

---
title: "Comparing Predicted Boundaries vs Called Boundaries"
author: "Spiro Stilianoudakis"
date: "August 8, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(scales)
library(GGally)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggpubr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)
```

# GM12878

## Create granges from top tfbs

```{r}
source("C:/Users/stili/Documents/TAD_predictive_modeling/Scripts/functions_for_R_package/annots_to_granges_func.r")
#file_path="Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/chr22_tfbs_gm12878"
file_path="Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS"
annots.GR <- annots_to_granges_func(filepath=file_path)

```

## Overlap between Called Regions and Predicted Boundaroes

```{r}

pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/smote/distance/enet/called_and_pred_bound_regions.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[4]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

venn_cnt2venn <- function(venn_cnt){
  n <- which(colnames(venn_cnt)=="Counts") - 1
  SetNames=colnames(venn_cnt)[1:n]
  Weight=venn_cnt[,"Counts"]
  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
  Venn(SetNames=SetNames, Weight=Weight)
}

res <- makeVennDiagram(Peaks=list(all_true_bounds, all_pred_bounds),
                       NameOfPeaks=c("Called", "Predicted"),
                       connectedPeaks = "keepAll")
venn_gm12878 <- venn_cnt2venn(res$vennCounts)
venn_gm12878 <- compute.Venn(venn_gm12878)
gp <- VennThemes(venn_gm12878)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_gm12878, 
                                                 gp = gp, 
                                                 show=list(Universe=FALSE))), 
                        top=textGrob("Boundary Region", 
                                     gp=gpar(fontsize=50)))

```

## Enriched Heatmaps

```{r}
annots.GR.f <- lapply(annots.GR, function(x){x[which(as.character(seqnames(x)) %in% tolower(chrs))]})

all_true_bounds_r <- resize(all_true_bounds, width=1,fix = "center")

e = 10000
axis_names <- c("-10 kb", "Center", "10 kb")
```

### CTCF

#### Predicted

```{r}

mat = normalizeToMatrix(annots.GR.f[[1]], 
                         all_pred_bounds, 
                         value_column = "coverage", 
                         extend = e, 
                         mean_mode = "w0",
                         keep = c(0,.99))

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "CTCF"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

#### Called

```{r}

mat = normalizeToMatrix(annots.GR.f[[1]], 
                         all_true_bounds_r, 
                         value_column = "coverage", 
                         extend = e, 
                         mean_mode = "w0",
                         keep = c(0,.99))

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "CTCF"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "right")))
```

### RAD21

#### Predicted

```{r}

mat = normalizeToMatrix(annots.GR.f[[2]], 
                         all_pred_bounds, 
                         value_column = "coverage", 
                         extend = e, 
                         mean_mode = "w0",
                         keep = c(0,.99))

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "RAD21"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

#### Called

```{r}

mat = normalizeToMatrix(annots.GR.f[[2]], 
                         all_true_bounds_r, 
                         value_column = "coverage", 
                         extend = e, 
                         mean_mode = "w0",
                         keep = c(0,.99))

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "RAD21"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "right")))
```

### SMC3

#### Predicted

```{r}

mat = normalizeToMatrix(annots.GR.f[[3]], 
                         all_pred_bounds, 
                         value_column = "coverage", 
                         extend = e, 
                         mean_mode = "w0",
                         keep = c(0,.99))

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "SMC3"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

#### Called

```{r}

mat = normalizeToMatrix(annots.GR.f[[3]], 
                         all_true_bounds_r, 
                         value_column = "coverage", 
                         extend = e, 
                         mean_mode = "w0",
                         keep = c(0,.99))

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "SMC3"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "right")))
```

### ZNF143

#### Predicted

```{r}

mat = normalizeToMatrix(annots.GR.f[[4]], 
                         all_pred_bounds, 
                         value_column = "coverage", 
                         extend = e, 
                         mean_mode = "w0",
                         keep = c(0,.99))

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "ZNF143"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

#### Called

```{r}

mat = normalizeToMatrix(annots.GR.f[[4]], 
                         all_true_bounds_r, 
                         value_column = "coverage", 
                         extend = e, 
                         mean_mode = "w0",
                         keep = c(0,.99))

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "ZNF143"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "right")))
```

## Distance Plots

### Predicted

```{r}
chromslength <- numeric()
for(i in 1:length(chrs)){
  chromslength[i] <- max(end(all_pred_bounds[which(as.character(seqnames(all_pred_bounds))==tolower(chrs[i]))]),
                         end(annots.GR.f[[1]][which(as.character(seqnames(annots.GR.f[[1]]))==tolower(chrs[i]))]))
}
names(chromslength) <- tolower(chrs)

p_to_ctcf <- GenometriCorrelation(all_pred_bounds,
                                     annots.GR.f[[1]], 
                                     chromosomes.length = chromslength,
                                     chromosomes.to.proceed = tolower(chrs), 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

chromslength <- numeric()
for(i in 1:length(chrs)){
  chromslength[i] <- max(end(all_pred_bounds[which(as.character(seqnames(all_pred_bounds))==tolower(chrs[i]))]),
                         end(annots.GR.f[[2]][which(as.character(seqnames(annots.GR.f[[2]]))==tolower(chrs[i]))]))
}
names(chromslength) <- tolower(chrs)

p_to_rad21 <- GenometriCorrelation(all_pred_bounds,
                                      annots.GR.f[[2]], 
                                      chromosomes.length = chromslength,
                                      chromosomes.to.proceed = tolower(chrs),
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

chromslength <- numeric()
for(i in 1:length(chrs)){
  chromslength[i] <- max(end(all_pred_bounds[which(as.character(seqnames(all_pred_bounds))==tolower(chrs[i]))]),
                         end(annots.GR.f[[3]][which(as.character(seqnames(annots.GR.f[[3]]))==tolower(chrs[i]))]))
}
names(chromslength) <- tolower(chrs)

p_to_smc3a <- GenometriCorrelation(all_pred_bounds,
                                      annots.GR.f[[3]], 
                                      chromosomes.length = chromslength,
                                      chromosomes.to.proceed = tolower(chrs),
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

chromslength <- numeric()
for(i in 1:length(chrs)){
  chromslength[i] <- max(end(all_pred_bounds[which(as.character(seqnames(all_pred_bounds))==tolower(chrs[i]))]),
                         end(annots.GR.f[[4]][which(as.character(seqnames(annots.GR.f[[4]]))==tolower(chrs[i]))]))
}
names(chromslength) <- tolower(chrs)

p_to_znf143 <- GenometriCorrelation(all_pred_bounds,
                                       annots.GR.f[[4]], 
                                       chromosomes.length = chromslength,
                                       chromosomes.to.proceed = tolower(chrs), 
                                       permut.number = 100,
                                       ecdf.area.permut.number = 100,
                                       mean.distance.permut.number = 100,
                                       jaccard.measure.permut.number = 100,
                                       keep.distributions = TRUE, 
                                       showProgressBar = TRUE)

```

### Called

```{r}
chromslength <- numeric()
for(i in 1:length(chrs)){
  chromslength[i] <- max(end(all_true_bounds[which(as.character(seqnames(all_true_bounds))==tolower(chrs[i]))]),
                         end(annots.GR.f[[1]][which(as.character(seqnames(annots.GR.f[[1]]))==tolower(chrs[i]))]))
}
names(chromslength) <- tolower(chrs)

t_to_ctcf <- GenometriCorrelation(all_true_bounds,
                                     annots.GR.f[[1]], 
                                     chromosomes.length = chromslength,
                                     chromosomes.to.proceed = tolower(chrs), 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

chromslength <- numeric()
for(i in 1:length(chrs)){
  chromslength[i] <- max(end(all_true_bounds[which(as.character(seqnames(all_true_bounds))==tolower(chrs[i]))]),
                         end(annots.GR.f[[2]][which(as.character(seqnames(annots.GR.f[[2]]))==tolower(chrs[i]))]))
}
names(chromslength) <- tolower(chrs)

t_to_rad21 <- GenometriCorrelation(all_true_bounds,
                                      annots.GR.f[[2]], 
                                      chromosomes.length = chromslength,
                                      chromosomes.to.proceed = tolower(chrs),
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

chromslength <- numeric()
for(i in 1:length(chrs)){
  chromslength[i] <- max(end(all_true_bounds[which(as.character(seqnames(all_true_bounds))==tolower(chrs[i]))]),
                         end(annots.GR.f[[3]][which(as.character(seqnames(annots.GR.f[[3]]))==tolower(chrs[i]))]))
}
names(chromslength) <- tolower(chrs)

t_to_smc3a <- GenometriCorrelation(all_true_bounds,
                                      annots.GR.f[[3]], 
                                      chromosomes.length = chromslength,
                                      chromosomes.to.proceed = tolower(chrs),
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

chromslength <- numeric()
for(i in 1:length(chrs)){
  chromslength[i] <- max(end(all_true_bounds[which(as.character(seqnames(all_true_bounds))==tolower(chrs[i]))]),
                         end(annots.GR.f[[4]][which(as.character(seqnames(annots.GR.f[[4]]))==tolower(chrs[i]))]))
}
names(chromslength) <- tolower(chrs)

t_to_znf143 <- GenometriCorrelation(all_true_bounds,
                                       annots.GR.f[[4]], 
                                       chromosomes.length = chromslength,
                                       chromosomes.to.proceed = tolower(chrs), 
                                       permut.number = 100,
                                       ecdf.area.permut.number = 100,
                                       mean.distance.permut.number = 100,
                                       jaccard.measure.permut.number = 100,
                                       keep.distributions = TRUE, 
                                       showProgressBar = TRUE)

```

### Plots

```{r}
pred_v_called_10_df <- data.frame(AbsoluteDist = c(#Predicted
  p_to_ctcf@.Data[[1]]$absolute.min.distance.data,
  p_to_rad21@.Data[[1]]$absolute.min.distance.data,
  p_to_smc3a@.Data[[1]]$absolute.min.distance.data,
  p_to_znf143@.Data[[1]]$absolute.min.distance.data,

  #Called
  t_to_ctcf@.Data[[1]]$absolute.min.distance.data,
  t_to_rad21@.Data[[1]]$absolute.min.distance.data,
  t_to_smc3a@.Data[[1]]$absolute.min.distance.data,
  t_to_znf143@.Data[[1]]$absolute.min.distance.data
),
Annotation = c(#Predicted
    rep("CTCF",length(p_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("RAD21",length(p_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("SMC3a",length(p_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("ZNF143",length(p_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #Called
    rep("CTCF",length(t_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("RAD21",length(t_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("SMC3a",length(t_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("ZNF143",length(t_to_znf143@.Data[[1]]$absolute.min.distance.data))),
BoundReg = c(#Predicted
    rep("Predicted", length(p_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("Predicted", length(p_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("Predicted", length(p_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("Predicted", length(p_to_znf143@.Data[[1]]$absolute.min.distance.data)),

    #Called
    rep("Called", length(t_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
    rep("Called", length(t_to_rad21@.Data[[1]]$absolute.min.distance.data)),
    rep("Called", length(t_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
    rep("Called", length(t_to_znf143@.Data[[1]]$absolute.min.distance.data))))

pred_v_called_10_df$BoundReg <- factor(pred_v_called_10_df$BoundReg, levels=c("Predicted", "Called"))
pred_v_called_10_df$log2AbsoluteDist <- log(pred_v_called_10_df$AbsoluteDist + 1, base = 2)

ggplot(pred_v_called_10_df, aes(x=BoundReg, y = log2AbsoluteDist, fill=BoundReg))  + 
  facet_grid(~ Annotation) +    
  stat_boxplot(geom ='errorbar', width = 0.2) + 
  geom_boxplot(outlier.shape = NA) +
  geom_signif(test = "wilcox.test", 
              comparisons = list( c("Predicted", "Called")),
              vjust = 0,
              textsize = 4,
              size = .5,
              step_increase = .08) +
  theme_minimal()+
  theme_bw()+
  ylab("Log2 Distance to Annotation")+
  xlab("") +
  scale_fill_discrete(name="Boundary Region")+
  #guides(color=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

```

### 2019-08-09 Scripts/evaluating_thresholds_for_pred_bounds.Rmd
initial commit

--- 2019-08-02 Scripts/comparing_predicted_vs_called_boundary_regions.Rmd
@@
 ```
+
+## GM12878; chr21
+
+### Mean length of adjacent 1bp cutoff
+
+```{r}
+toptfbs_mean_gm12878_chr21 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR21/smote/distance/enet/called_and_pred_bound_regions.rds")
+
+venn_cnt2venn <- function(venn_cnt){
+  n <- which(colnames(venn_cnt)=="Counts") - 1
+  SetNames=colnames(venn_cnt)[1:n]
+  Weight=venn_cnt[,"Counts"]
+  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
+  Venn(SetNames=SetNames, Weight=Weight)
+}
+
+res <- makeVennDiagram(Peaks=list(toptfbs_mean_gm12878_chr21[[3]], toptfbs_mean_gm12878_chr21[[4]]),
+                       NameOfPeaks=c("Called", "Predicted"),
+                       connectedPeaks = "keepAll")
+venn_gm12878_22 <- venn_cnt2venn(res$vennCounts)
+venn_gm12878_22 <- compute.Venn(venn_gm12878_22)
+gp <- VennThemes(venn_gm12878_22)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_5kb, 
+                                                 gp = gp, 
+                                                 show=list(Universe=FALSE))), 
+                        top=textGrob("Boundary Region", 
+                                     gp=gpar(fontsize=50)))
+
+############################################################################################################
+
+#PBNC
+
+sh <- unique(subjectHits(findOverlaps(toptfbs_mean_gm12878_chr21[[3]], toptfbs_mean_gm12878_chr21[[4]])))
+pbnc <- toptfbs_mean_gm12878_chr21[[4]][-sh]
+
+pbnc_to_ctcf <- GenometriCorrelation(pbnc,
+                                     annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"], 
+                                     chromosomes.length = max(end(pbnc),
+                                                              end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"])),
+                                     chromosomes.to.proceed = "chr21", 
+                                     permut.number = 100,
+                                     ecdf.area.permut.number = 100,
+                                     mean.distance.permut.number = 100,
+                                     jaccard.measure.permut.number = 100,
+                                     keep.distributions = TRUE, 
+                                     showProgressBar = TRUE)
+
+pbnc_to_rad21 <- GenometriCorrelation(pbnc,
+                                      annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"], 
+                                      chromosomes.length = max(end(pbnc),
+                                                               end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"])),
+                                      chromosomes.to.proceed = "chr21", 
+                                      permut.number = 100,
+                                      ecdf.area.permut.number = 100,
+                                      mean.distance.permut.number = 100,
+                                      jaccard.measure.permut.number = 100,
+                                      keep.distributions = TRUE, 
+                                      showProgressBar = TRUE)
+
+pbnc_to_smc3a <- GenometriCorrelation(pbnc,
+                                      annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"], 
+                                      chromosomes.length = max(end(pbnc),
+                                                               end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"])),
+                                      chromosomes.to.proceed = "chr21", 
+                                      permut.number = 100,
+                                      ecdf.area.permut.number = 100,
+                                      mean.distance.permut.number = 100,
+                                      jaccard.measure.permut.number = 100,
+                                      keep.distributions = TRUE, 
+                                      showProgressBar = TRUE)
+
+pbnc_to_znf143 <- GenometriCorrelation(pbnc,
+                                       annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"], 
+                                       chromosomes.length = max(end(pbnc),
+                                                                end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"])),
+                                       chromosomes.to.proceed = "chr21", 
+                                       permut.number = 100,
+                                       ecdf.area.permut.number = 100,
+                                       mean.distance.permut.number = 100,
+                                       jaccard.measure.permut.number = 100,
+                                       keep.distributions = TRUE, 
+                                       showProgressBar = TRUE)
+
+############################################################################################################
+
+#PAC
+sh <- unique(subjectHits(findOverlaps(toptfbs_mean_gm12878_chr21[[3]], toptfbs_mean_gm12878_chr21[[4]])))
+pac <- toptfbs_mean_gm12878_chr21[[4]][sh]
+
+pac_to_ctcf <- GenometriCorrelation(pac,
+                                    annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"], 
+                                    chromosomes.length = max(end(pac),
+                                                             end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"])),
+                                    chromosomes.to.proceed = "chr21", 
+                                    permut.number = 100,
+                                    ecdf.area.permut.number = 100,
+                                    mean.distance.permut.number = 100,
+                                    jaccard.measure.permut.number = 100,
+                                    keep.distributions = TRUE, 
+                                    showProgressBar = TRUE)
+
+pac_to_rad21 <- GenometriCorrelation(pac,
+                                     annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"], 
+                                     chromosomes.length = max(end(pac),
+                                                              end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"])),
+                                     chromosomes.to.proceed = "chr21", 
+                                     permut.number = 100,
+                                     ecdf.area.permut.number = 100,
+                                     mean.distance.permut.number = 100,
+                                     jaccard.measure.permut.number = 100,
+                                     keep.distributions = TRUE, 
+                                     showProgressBar = TRUE)
+
+pac_to_smc3a <- GenometriCorrelation(pac,
+                                     annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"], 
+                                     chromosomes.length = max(end(pac),
+                                                              end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"])),
+                                     chromosomes.to.proceed = "chr21", 
+                                     permut.number = 100,
+                                     ecdf.area.permut.number = 100,
+                                     mean.distance.permut.number = 100,
+                                     jaccard.measure.permut.number = 100,
+                                     keep.distributions = TRUE, 
+                                     showProgressBar = TRUE)
+
+pac_to_znf143 <- GenometriCorrelation(pac,
+                                      annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"], 
+                                      chromosomes.length = max(end(pac),
+                                                               end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"])),
+                                      chromosomes.to.proceed = "chr21", 
+                                      permut.number = 100,
+                                      ecdf.area.permut.number = 100,
+                                      mean.distance.permut.number = 100,
+                                      jaccard.measure.permut.number = 100,
+                                      keep.distributions = TRUE, 
+                                      showProgressBar = TRUE)
+
+############################################################################################################
+
+#CAP
+qh <- unique(queryHits(findOverlaps(toptfbs_mean_gm12878_chr21[[3]], toptfbs_mean_gm12878_chr21[[4]])))
+cap <- toptfbs_mean_gm12878_chr21[[3]][qh]
+
+cap_to_ctcf <- GenometriCorrelation(cap,
+                                    annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"], 
+                                    chromosomes.length = max(end(cap),
+                                                             end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"])),
+                                    chromosomes.to.proceed = "chr21", 
+                                    permut.number = 100,
+                                    ecdf.area.permut.number = 100,
+                                    mean.distance.permut.number = 100,
+                                    jaccard.measure.permut.number = 100,
+                                    keep.distributions = TRUE, 
+                                    showProgressBar = TRUE)
+
+cap_to_rad21 <- GenometriCorrelation(cap,
+                                     annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"], 
+                                     chromosomes.length = max(end(cap),
+                                                              end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"])),
+                                     chromosomes.to.proceed = "chr21", 
+                                     permut.number = 100,
+                                     ecdf.area.permut.number = 100,
+                                     mean.distance.permut.number = 100,
+                                     jaccard.measure.permut.number = 100,
+                                     keep.distributions = TRUE, 
+                                     showProgressBar = TRUE)
+
+cap_to_smc3a <- GenometriCorrelation(cap,
+                                     annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"], 
+                                     chromosomes.length = max(end(cap),
+                                                              end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"])),
+                                     chromosomes.to.proceed = "chr21", 
+                                     permut.number = 100,
+                                     ecdf.area.permut.number = 100,
+                                     mean.distance.permut.number = 100,
+                                     jaccard.measure.permut.number = 100,
+                                     keep.distributions = TRUE, 
+                                     showProgressBar = TRUE)
+
+cap_to_znf143 <- GenometriCorrelation(cap,
+                                      annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"], 
+                                      chromosomes.length = max(end(cap),
+                                                               end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"])),
+                                      chromosomes.to.proceed = "chr21", 
+                                      permut.number = 100,
+                                      ecdf.area.permut.number = 100,
+                                      mean.distance.permut.number = 100,
+                                      jaccard.measure.permut.number = 100,
+                                      keep.distributions = TRUE, 
+                                      showProgressBar = TRUE)
+
+###########################################################################################################
+
+#CBNP
+qh <- unique(queryHits(findOverlaps(toptfbs_mean_gm12878_chr21[[3]], toptfbs_mean_gm12878_chr21[[4]])))
+cbnp <- toptfbs_mean_gm12878_chr21[[3]][-qh]
+
+cbnp_to_ctcf <- GenometriCorrelation(cbnp,
+                                     annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"], 
+                                     chromosomes.length = max(end(cbnp),
+                                                              end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"])),
+                                     chromosomes.to.proceed = "chr21", 
+                                     permut.number = 100,
+                                     ecdf.area.permut.number = 100,
+                                     mean.distance.permut.number = 100,
+                                     jaccard.measure.permut.number = 100,
+                                     keep.distributions = TRUE, 
+                                     showProgressBar = TRUE)
+
+cbnp_to_rad21 <- GenometriCorrelation(cbnp,
+                                      annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"], 
+                                      chromosomes.length = max(end(cbnp),
+                                                               end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"])),
+                                      chromosomes.to.proceed = "chr21", 
+                                      permut.number = 100,
+                                      ecdf.area.permut.number = 100,
+                                      mean.distance.permut.number = 100,
+                                      jaccard.measure.permut.number = 100,
+                                      keep.distributions = TRUE, 
+                                      showProgressBar = TRUE)
+
+cbnp_to_smc3a <- GenometriCorrelation(cbnp,
+                                      annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"], 
+                                      chromosomes.length = max(end(cbnp),
+                                                               end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"])),
+                                      chromosomes.to.proceed = "chr21", 
+                                      permut.number = 100,
+                                      ecdf.area.permut.number = 100,
+                                      mean.distance.permut.number = 100,
+                                      jaccard.measure.permut.number = 100,
+                                      keep.distributions = TRUE, 
+                                      showProgressBar = TRUE)
+
+cbnp_to_znf143 <- GenometriCorrelation(cbnp,
+                                       annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"], 
+                                       chromosomes.length = max(end(cbnp),
+                                                                end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"])),
+                                       chromosomes.to.proceed = "chr21", 
+                                       permut.number = 100,
+                                       ecdf.area.permut.number = 100,
+                                       mean.distance.permut.number = 100,
+                                       jaccard.measure.permut.number = 100,
+                                       keep.distributions = TRUE, 
+                                       showProgressBar = TRUE)
+
+############################################################################################################
+
+pred_v_called_mean_df <- data.frame(AbsoluteDist = c(#PBNC
+                                            pbnc_to_ctcf@.Data[[1]]$absolute.min.distance.data,
+                                            pbnc_to_rad21@.Data[[1]]$absolute.min.distance.data,
+                                            pbnc_to_smc3a@.Data[[1]]$absolute.min.distance.data,
+                                            pbnc_to_znf143@.Data[[1]]$absolute.min.distance.data,
+
+                                            #PAC
+                                            pac_to_ctcf@.Data[[1]]$absolute.min.distance.data,
+                                            pac_to_rad21@.Data[[1]]$absolute.min.distance.data,
+                                            pac_to_smc3a@.Data[[1]]$absolute.min.distance.data,
+                                            pac_to_znf143@.Data[[1]]$absolute.min.distance.data,
+
+                                            #CAP
+                                            cap_to_ctcf@.Data[[1]]$absolute.min.distance.data,
+                                            cap_to_rad21@.Data[[1]]$absolute.min.distance.data,
+                                            cap_to_smc3a@.Data[[1]]$absolute.min.distance.data,
+                                            cap_to_znf143@.Data[[1]]$absolute.min.distance.data,
+
+                                            #CBNP
+                                            cbnp_to_ctcf@.Data[[1]]$absolute.min.distance.data,
+                                            cbnp_to_rad21@.Data[[1]]$absolute.min.distance.data,
+                                            cbnp_to_smc3a@.Data[[1]]$absolute.min.distance.data,
+                                            cbnp_to_znf143@.Data[[1]]$absolute.min.distance.data),
+                               Annotation = c(#PBNC
+                                            rep("CTCF",length(pbnc_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("RAD21",length(pbnc_to_rad21@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("SMC3a",length(pbnc_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("ZNF143",length(pbnc_to_znf143@.Data[[1]]$absolute.min.distance.data)),
+
+                                            #PAC
+                                            rep("CTCF",length(pac_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("RAD21",length(pac_to_rad21@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("SMC3a",length(pac_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("ZNF143",length(pac_to_znf143@.Data[[1]]$absolute.min.distance.data)),
+
+                                            #CAP
+                                            rep("CTCF",length(cap_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("RAD21",length(cap_to_rad21@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("SMC3a",length(cap_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("ZNF143",length(cap_to_znf143@.Data[[1]]$absolute.min.distance.data)),
+
+                                            #CBNP
+                                            rep("CTCF",length(cbnp_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("RAD21",length(cbnp_to_rad21@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("SMC3a",length(cbnp_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("ZNF143",length(cbnp_to_znf143@.Data[[1]]$absolute.min.distance.data))),
+                               BoundReg = c(#PBNC
+                                            rep("PBNC", length(pbnc_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("PBNC", length(pbnc_to_rad21@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("PBNC", length(pbnc_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("PBNC", length(pbnc_to_znf143@.Data[[1]]$absolute.min.distance.data)),
+
+                                            #PAC
+                                            rep("PAC", length(pac_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("PAC", length(pac_to_rad21@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("PAC", length(pac_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("PAC", length(pac_to_znf143@.Data[[1]]$absolute.min.distance.data)),
+
+                                            #CAP
+                                            rep("CAP", length(cap_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("CAP", length(cap_to_rad21@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("CAP", length(cap_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("CAP", length(cap_to_znf143@.Data[[1]]$absolute.min.distance.data)),
+
+                                            #CBNP
+                                            rep("CBNP", length(cbnp_to_ctcf@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("CBNP", length(cbnp_to_rad21@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("CBNP", length(cbnp_to_smc3a@.Data[[1]]$absolute.min.distance.data)),
+                                            rep("CBNP", length(cbnp_to_znf143@.Data[[1]]$absolute.min.distance.data))))
+pred_v_called_mean_df$BoundReg <- factor(pred_v_called_mean_df$BoundReg, levels=c("PBNC", "PAC", "CAP", "CBNP"))
+pred_v_called_mean_df$log2AbsoluteDist <- log(pred_v_called_mean_df$AbsoluteDist + 1, base = 2)
+
+ggplot(pred_v_called_mean_df, aes(x=BoundReg, y = log2AbsoluteDist, fill=BoundReg))  + 
+  facet_grid(~ Annotation) +    
+  stat_boxplot(geom ='errorbar', width = 0.2) + 
+  geom_boxplot(outlier.shape = NA) +
+  #stat_compare_means(comparisons = list( c("PBNC", "PAC"), 
+  #                                       c("PBNC", "CAP"), 
+  #                                       c("PBNC", "CBNP"),
+  #                                       c("PAC", "CAP"),
+  #                                       c("PAC", "CBNP"),
+  #                                       c("CAP", "CBNP")),
+  #                   vjust = 0,
+  #                   #textsize = 4,
+  #                   #size = .5,
+  #                   #step_increase = .08, 
+  #                   method = "wilcox.test", 
+  #                   label = "p.format") +
+  geom_signif(test = "wilcox.test", 
+            comparisons = list( c("PBNC", "PAC"), 
+                                c("PBNC", "CAP"), 
+                                c("PBNC", "CBNP"),
+                                c("PAC", "CAP"),
+                                c("PAC", "CBNP"),
+                                c("CAP", "CBNP")),
+            vjust = 0,
+            textsize = 4,
+            size = .5,
+            step_increase = .08) +
+  theme_minimal()+
+  theme_bw()+
+  ylab("Log2 Distance to Annotation")+
+  xlab("") +
+  ggtitle("Mean width cutoff")+
+  scale_fill_discrete(name="Boundary Region")+
+  scale_x_discrete(labels=c("PBNC"="Predicted but\nnot called",
+                            "PAC"="Predicted\nand called",
+                            "CAP"="Called and\npredicted",
+                            "CBNP"="Called but not\npredicted"))+
+  #guides(color=FALSE, linetype=FALSE)+
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        strip.text.x = element_text(size = 15),
+        #panel.spacing = unit(2, "lines"),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        plot.title = element_text(size=20),
+        legend.position = "bottom")
+
+```

### 2019-08-09 Scripts/visualizing_example_predicted_tad_bounds.Rmd
initial commit

---
title: "Visualizing Example of Clustered Predicted TAD Boundary Regions"
author: "Spiro Stilianoudakis"
date: "August 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(scales)
library(GGally)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggpubr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)
library(factoextra)
```

# Steps
##1.	Build chromosome specific test data
###a.	Bin chromosome specific data at bp resolution (i.e. 1 row -> 1 bp)
###b.	Annotate data matrix with distances to top TFBS
##2.	Validate best performing model on test data
##3.	Extract probability vector
##4.	Determine threshold for identifying predicted TAD boundary
###a.	Consider the base pairs where the probability vector is given to be 1 
###b.	Consider the midpoints of all groups of base pairs with probability 1
###c.	Obtain distance matrix of all pairwise distances between midpoints
###d.	Perform PAM clustering on the distance matrix
###i.	Obtain optimal number of clusters using silhouette method
###e.	Assign predicted TAD boundary as the new midpoint (bp) of clustered distances

# GM12878

## CHR 22

###17390000-18640000

```{r}
called_and_pred_bound_regions <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR22/smote/distance/enet/called_and_pred_bound_regions.rds")

predprob_df_1 <- called_and_pred_bound_regions[[1]]
predprob_df <- called_and_pred_bound_regions[[2]]
trueBound_gr_region <- called_and_pred_bound_regions[[3]]
predBound_gr <- called_and_pred_bound_regions[[4]]

predprob_df$baseNum[which(predprob_df$trueBound=="Yes")][1:10]
#17390000 17540000 17550000 17650000 17820000 18010000 18030000 18210000 18280000 18640000

predprob_df_temp <- predprob_df[which(predprob_df$baseNum>=17390000 & predprob_df$baseNum<=18640000),]
table(predprob_df_temp$predBound)

ggplot(predprob_df_temp, aes(x=baseNum, y=PredProb)) +
     geom_line(size=.5)+
     #geom_smooth(method = "loess", size = 5, color="blue")
	   geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$PredProb==1)], 
	              color="red", 
	              #linetype="dashed", 
	              size=.5)+
     geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], 
	              color="yellow", 
	              #linetype="dashed", 
	              size=.5)+
     xlab("Base Pair") +
     ylab("Predicted Probability") +
     theme_minimal() +
     theme_bw() +
     theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

x <- dist(predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], method = "euclidean")

xlabels <- c("1", "2", "3", "9", "10", "4", "5", "8", "6", "7")
fviz_dist(x, gradient = list(low = "white", mid = "pink", high = muted("red")))+
  xlab("")+
  ylab("")+
  #scale_fill_continuous("Distance")+
  scale_fill_gradient2("Distance",
                       low = "white", 
                       mid = "pink",
                       midpoint = 450000,
                       high = muted("red"))+
  scale_x_discrete(labels=xlabels)+
  scale_y_discrete(labels=xlabels)+
  theme_minimal()+
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #panel.grid.major = element_blank(),
        #panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

hc1 <- hclust(x, method = "complete")
plot(hc1)

z <- sapply(2:(dim(as.matrix(x))[1]-1), function(i) { 
    mean(silhouette(cutree(hc1, i), dist=x)[,"sil_width"]) })
plot(2:(dim(as.matrix(x))[1]-1), z)

k = which.max(z)+1
p <- pam(x, diss=TRUE, k=k, cluster.only=TRUE, trace.lev = 0)
clustdf <- data.frame(mid=predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], clust=cutree(hc1, k=k))

plot(hc1, hang = -1)
rect.hclust(hc1, k = k)

prob1intervals <- unique(clustdf$clust)
  mid2 <- numeric()
  for(i in prob1intervals){
    dat <- clustdf[which(clustdf$clust==prob1intervals[i]),]
    n=dim(dat)[1]
    mid2[i] <- ceiling((dat$mid[1]+dat$mid[n])/2)
  }

  predprob_df_temp$predBound2 <- ifelse(predprob_df_temp$baseNum %in% mid2, "Yes", "No")

ggplot(predprob_df_temp, aes(x=baseNum, y=PredProb)) +
     geom_line(size=.5)+
     #geom_smooth(method = "loess", size = 5, color="blue")
	   geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$PredProb==1)], 
	              color="red", 
	              #linetype="dashed", 
	              size=.5)+
     geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$predBound2=="Yes")], 
	              color="yellow", 
	              #linetype="dashed", 
	              size=.5)+
     xlab("Base Pair") +
     ylab("Predicted Probability") +
     theme_minimal() +
     theme_bw() +
     theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

```

### 2019-08-09 Scripts/functions_for_R_package/all_functions.R
edits

@@ -17,16 +17,17 @@ annots_to_granges_func <- function(filepath){
   #if(grepl(paste0(names, collapse = "|"), list.files(filepath)))
   for(i in 1:length(list.files(filepath))){
     dat <- read.table(paste0(filepath,"/",list.files(filepath)[i]),
-                      header = FALSE, 
-                      sep="\t")
+                      header = FALSE)
     
     annots_gr_list[[i]] <- GRanges(seqnames=dat$V1,
                                    IRanges(start=dat$V2, 
                                            end=dat$V3))
+    mcols(annots_gr_list[[i]])$coverage <- dat[,4]
   }
   names(annots_gr_list) <- gsub(".bed", "", list.files(filepath))
   return(annots_gr_list)
 }
+
 
 ##################################################################################
 
@@ -335,7 +336,7 @@ predict_tad_bounds_func <- function(resolution, bounds.GR, datamatrix, chromosom
 ############################################################################################
 
 #function to predict TAD boundaries at bp resolution
-predict_at_bp_resolution_func <- function(bounds.GR, resolution, chromosome, seqList, annotationListGR, tadModel, predwindow, region=TRUE){
+predict_at_bp_resolution_func <- function(bounds.GR, resolution, chromosome, seqList, annotationListGR, tadModel){
   #creating chromosome specific test data at bp resolution
   
   #chromosome-specific test data is at basepair resolution
@@ -401,116 +402,43 @@ predict_at_bp_resolution_func <- function(bounds.GR, resolution, chromosome, seq
   predprob_df_1$lagbaseNum <- lagpad(predprob_df_1$baseNum, 1)
   predprob_df_1$predprob1length <- predprob_df_1$baseNum - predprob_df_1$lagbaseNum  
   
-  if(predwindow=="median"){
-    
-    predprob_df_1$retain <-  NA
-    predprob_df_1$retain[1] <- 1
-    x <- 1
-    #consider where groups of probabilities==1 are not adjacent
-    ##set the window as 1 base pair 
-    ###all basepairs within that window are considered a predicted TAD boundary region (PTBR)
[…]

### 2019-08-09 Scripts/functions_for_R_package/annots_to_granges_func.r

@@ -5,12 +5,12 @@ annots_to_granges_func <- function(filepath){
   #if(grepl(paste0(names, collapse = "|"), list.files(filepath)))
   for(i in 1:length(list.files(filepath))){
     dat <- read.table(paste0(filepath,"/",list.files(filepath)[i]),
-                      header = FALSE, 
-                      sep="\t")
+                      header = FALSE)
     
     annots_gr_list[[i]] <- GRanges(seqnames=dat$V1,
                                    IRanges(start=dat$V2, 
                                            end=dat$V3))
+    mcols(annots_gr_list[[i]])$coverage <- dat[,4]
   }
   names(annots_gr_list) <- gsub(".bed", "", list.files(filepath))
   return(annots_gr_list)

### 2019-08-09 Scripts/functions_for_R_package/predict_at_bp_resolution_func.r

@@ -1,5 +1,5 @@
 #function to predict TAD boundaries at bp resolution
-predict_at_bp_resolution_func <- function(bounds.GR, resolution, chromosome, seqList, annotationListGR, tadModel, predwindow, region=TRUE){
+predict_at_bp_resolution_func <- function(bounds.GR, resolution, chromosome, seqList, annotationListGR, tadModel){
   #creating chromosome specific test data at bp resolution
   
   #chromosome-specific test data is at basepair resolution
@@ -65,116 +65,43 @@ predict_at_bp_resolution_func <- function(bounds.GR, resolution, chromosome, seq
   predprob_df_1$lagbaseNum <- lagpad(predprob_df_1$baseNum, 1)
   predprob_df_1$predprob1length <- predprob_df_1$baseNum - predprob_df_1$lagbaseNum  
   
-  if(predwindow=="median"){
-    
-    predprob_df_1$retain <-  NA
-    predprob_df_1$retain[1] <- 1
-    x <- 1
-    #consider where groups of probabilities==1 are not adjacent
-    ##set the window as 1 base pair 
-    ###all basepairs within that window are considered a predicted TAD boundary region (PTBR)
-    for(i in 2:(dim(predprob_df_1)[1])){
-      if(predprob_df_1$predprob1length[i]<=1){predprob_df_1$retain[i] = x}else{x = x+1; predprob_df_1$retain[i] = x}
-    }
-    
-    #consider the middle of a PTR as a predicted TAD boundary point (PTBP)
-    prob1intervals <- unique(predprob_df_1$retain)
-    mid <- numeric()
-    for(i in prob1intervals){
-      dat <- predprob_df_1[which(predprob_df_1$retain==prob1intervals[i]),]
-      n=dim(dat)[1]
-      mid[i] <- ceiling((dat$baseNum[1]+dat$baseNum[n])/2)
-    }
-    
-    predprob_df_1$retain2 <-  NA
-    predprob_df_1$retain2[1] <- 1
-    x <- 1
-    #consider where groups of probabilities==1 are not adjacent
-    ##set the window as 1 base pair 
-    ###all basepairs within that window are considered a predicted TAD boundary region (PTBR)
-    pred.window = median(diff(mid))
-    for(i in 2:(dim(predprob_df_1)[1])){
[…]

### 2019-08-09 Scripts/visualizing_example_predicted_tad_bounds.Rmd
edits

@@
      geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], 
-	              color="yellow", 
+	              color="blue", 
 	              #linetype="dashed", 
@@
      geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$predBound2=="Yes")], 
-	              color="yellow", 
+	              color="blue", 
 	              #linetype="dashed", 
-	              size=.5)+
+	              size=1)+
      xlab("Base Pair") +

### 2019-08-17 Manuscript/manuscript_structured.Rmd

--- 2019-05-17 Manuscript/manuscript_structured.Rmd
@@
 ### Consider distance
+
+## Predicting at bp resolution
+
+### Empirical way to determine boundary regions
+
+####################################################################################
+
+# Results
+
+## Determining optimal data level characteristics for TAD boundary prediction
+## Identifying top predictive annotations of TAD boundaries
+## Predicting TAD boundaries at bp resolution
+### Comparing distance profiles of called TAD boundaries vs predicted TAD boundaries
+
 -->

### 2019-08-17 Scripts/comparing_predicted_boundaries_vs_called_boundaries.Rmd

@@
 
-all_true_bounds <- do.call("c", true_bound_list)
-all_pred_bounds <- do.call("c", pred_bound_list)
+called_and_pred_17 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR17/smote/distance/enet/called_and_pred_bound_regions.rds"))
+true_bound_17 <- called_and_pred_17[[3]]
+pred_bound_17 <- called_and_pred_17[[4]]
+rm(called_and_pred_17)
+
+called_and_pred_18 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR18/smote/distance/enet/called_and_pred_bound_regions.rds"))
+true_bound_18 <- called_and_pred_18[[3]]
+pred_bound_18 <- called_and_pred_18[[4]]
+rm(called_and_pred_18)
+
+called_and_pred_19 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR19/smote/distance/enet/called_and_pred_bound_regions.rds"))
+true_bound_19 <- called_and_pred_19[[3]]
+pred_bound_19 <- called_and_pred_19[[4]]
+rm(called_and_pred_19)
+
+called_and_pred_20 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR20/smote/distance/enet/called_and_pred_bound_regions.rds"))
+true_bound_20 <- called_and_pred_20[[3]]
+pred_bound_20 <- called_and_pred_20[[4]]
+rm(called_and_pred_20)
+
+called_and_pred_21 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR21/smote/distance/enet/called_and_pred_bound_regions.rds"))
+true_bound_21 <- called_and_pred_21[[3]]
+pred_bound_21 <- called_and_pred_21[[4]]
+rm(called_and_pred_21)
+
+called_and_pred_22 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR22/smote/distance/enet/called_and_pred_bound_regions.rds"))
+true_bound_22 <- called_and_pred_22[[3]]
+pred_bound_22 <- called_and_pred_22[[4]]
+rm(called_and_pred_22)
+
+all_true_bounds <- GRangesList(true_bound_17,
+                               true_bound_18,
+                               true_bound_19,
+                               true_bound_20,
+                               true_bound_21,
+                               true_bound_22)
+all_pred_bounds <- GRangesList(pred_bound_17,
+                               pred_bound_18,
+                               pred_bound_19,
+                               pred_bound_20,
+                               pred_bound_21,
+                               pred_bound_22)
+
+all_true_bounds <- do.call("c", all_true_bounds)
+all_pred_bounds <- do.call("c", all_pred_bounds)
 
@@
                 axis_name = axis_names,
-                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = muted("red"), 
+                                                                                   lwd = 2), 
                                                                          yaxis_side = "right", 
@@
 ```{r}
+all_true_bounds <- resize(all_true_bounds, width=1,fix = "center")
+
 chromslength <- numeric()
@@
 ```
+
+### Plots v2
+
+```{r}
+pred_v_called_10_df <- data.frame(LogDist = c(#Predicted
+    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1),
+    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[2]]))$distance+1),
+    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[3]]))$distance+1),
+    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[4]]))$distance+1),
+
+    #Called
+    log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1),
+    log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[2]]))$distance+1),
+    log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[3]]))$distance+1),
+    log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[4]]))$distance+1)
+),
+Annotation = c(#Predicted
+    rep("CTCF",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("RAD21",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("SMC3a",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("ZNF143",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+
+    #Called
+    rep("CTCF",length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("RAD21",length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("SMC3a",length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("ZNF143",length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1)))),
+BoundReg = c(#Predicted
+    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+
+    #Called
+    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1)))))
+
+pred_v_called_10_df$BoundReg <- factor(pred_v_called_10_df$BoundReg, levels=c("Predicted", "Called"))
+
+ggplot(pred_v_called_10_df, aes(x=BoundReg, y = LogDist, fill=BoundReg))  + 
+    facet_grid(~ Annotation) +    
+    stat_boxplot(geom ='errorbar', width = 0.2) + 
+    geom_boxplot(outlier.shape = NA) +
+    geom_signif(test = "wilcox.test", 
+                comparisons = list( c("Predicted", "Called")),
+                vjust = 0,
+                textsize = 4,
+                size = .5,
+                step_increase = .08) +
+    theme_minimal()+
+    theme_bw()+
+    ylab("Log2 Distance to Annotation")+
+    xlab("") +
+    scale_fill_discrete(name="Boundary Region")+
+    #guides(color=FALSE, linetype=FALSE)+
+    theme(axis.text.x = element_text(size=15,
+                                     angle = 45,
+                                     hjust = 1),
+          axis.text.y = element_text(size = 15),
+          axis.title.x = element_text(size = 20),
+          axis.title.y = element_text(size = 20),
+          strip.text.x = element_text(size = 15),
+          #panel.spacing = unit(2, "lines"),
+          legend.text=element_text(size=15),
+          legend.title=element_text(size=20),
+          plot.title = element_text(size=20),
+          legend.position = "bottom")
+```

### 2019-08-17 Scripts/comparing_tad_regions_across_cl_using_vd.Rmd

@@
 
+## Function to extract boundaries
+
+```{r}
+source("C:/Users/stili/Documents/TAD_predictive_modeling/Scripts/functions_for_R_package/extract_boundaries_func.r")
+```
+
 ## Venn diagrams
@@
 
-bounds_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/bounds_f.rds")
-bounds_k562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/bounds_f.rds")
+#bounds_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/bounds_f.rds")
+#bounds_k562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/bounds_f.rds")
+
+domains <- read.table("Z:/TAD_data_analysis/GM12878/5kb/GM12878_domain_data_5000.b.txt", header=F)
+bounds_gm12878_5kb <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=5000)
+  bounds_gm12878_5kb[[i]] <- bounds
+}
+bounds_gm12878_5kb <- do.call("c", bounds_gm12878_5kb)
+
+domains <- read.table("Z:/TAD_data_analysis/K562/5kb/K562_domain_data_5000.b.txt", header=F)
+bounds_k562_5kb <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=5000)
+  bounds_k562_5kb[[i]] <- bounds
+}
+bounds_k562_5kb <- do.call("c", bounds_k562_5kb)
 
@@
 
-bounds_gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/bounds_f.rds")
-bounds_k562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/bounds_f.rds")
+#bounds_gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/bounds_f.rds")
+#bounds_k562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/bounds_f.rds")
+
+domains <- read.table("Z:/TAD_data_analysis/GM12878/10kb/GM12878_domain_data_10000.b.txt", header=F)
+bounds_gm12878_10kb <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=10000)
+  bounds_gm12878_10kb[[i]] <- bounds
+}
+bounds_gm12878_10kb <- do.call("c", bounds_gm12878_10kb)
+
+domains <- read.table("Z:/TAD_data_analysis/K562/10kb/K562_domain_data_10000.b.txt", header=F)
+bounds_k562_10kb <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=10000)
+  bounds_k562_10kb[[i]] <- bounds
+}
+bounds_k562_10kb <- do.call("c", bounds_k562_10kb)
 
@@
 
-bounds_gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/bounds_f.rds")
-bounds_k562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/bounds_f.rds")
+#bounds_gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/bounds_f.rds")
+#bounds_k562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/bounds_f.rds")
+
+domains <- read.table("Z:/TAD_data_analysis/GM12878/25kb/GM12878_domain_data_25000.b.txt", header=F)
+bounds_gm12878_25kb <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=25000)
+  bounds_gm12878_25kb[[i]] <- bounds
+}
+bounds_gm12878_25kb <- do.call("c", bounds_gm12878_25kb)
+
+domains <- read.table("Z:/TAD_data_analysis/K562/25kb/K562_domain_data_25000.b.txt", header=F)
+bounds_k562_25kb <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=25000)
+  bounds_k562_25kb[[i]] <- bounds
+}
+bounds_k562_25kb <- do.call("c", bounds_k562_25kb)
 
@@
 
-bounds_gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/bounds_f.rds")
-bounds_k562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/bounds_f.rds")
+#bounds_gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/bounds_f.rds")
+#bounds_k562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/bounds_f.rds")
+
+domains <- read.table("Z:/TAD_data_analysis/GM12878/50kb/GM12878_domain_data_50000.b.txt", header=F)
+bounds_gm12878_50kb <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=50000)
+  bounds_gm12878_50kb[[i]] <- bounds
+}
+bounds_gm12878_50kb <- do.call("c", bounds_gm12878_50kb)
+
+domains <- read.table("Z:/TAD_data_analysis/K562/50kb/K562_domain_data_50000.b.txt", header=F)
+bounds_k562_50kb <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=50000)
+  bounds_k562_50kb[[i]] <- bounds
+}
+bounds_k562_50kb <- do.call("c", bounds_k562_50kb)
 
@@
 
-bounds_gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/bounds_f.rds")
-bounds_k562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/bounds_f.rds")
+#bounds_gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/bounds_f.rds")
+#bounds_k562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/bounds_f.rds")
+
+domains <- read.table("Z:/TAD_data_analysis/GM12878/100kb/GM12878_domain_data_100000.b.txt", header=F)
+bounds_gm12878_100kb <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=100000)
+  bounds_gm12878_100kb[[i]] <- bounds
+}
+bounds_gm12878_100kb <- do.call("c", bounds_gm12878_100kb)
+
+domains <- read.table("Z:/TAD_data_analysis/K562/100kb/K562_domain_data_100000.b.txt", header=F)
+bounds_k562_100kb <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=100000)
+  bounds_k562_100kb[[i]] <- bounds
+}
+bounds_k562_100kb <- do.call("c", bounds_k562_100kb)
 
@@
 gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_100kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("100 kb", gp=gpar(fontsize=50)))
-grid.newpage()
 

### 2019-08-17 Scripts/evaluating_rfe_across_chromosomes.Rmd

@@
         axis.title.y = element_text(size = 20),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
         #strip.text.x = element_text(size = 15),
@@
 
+#gm12878
 rfegm12878 <- rfeperchr[which(rfeperchr$CL=="GM12878"),]
@@
 cluster.col = hclust(distance.col, method = "average")
-my_palette <- colorRampPalette(c("white", "pink", "red"))(rcol(rfegm12878.mat))
+my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfegm12878.mat))
 heatmap.2(t(rfegm12878.mat),

### 2019-08-17 Scripts/visualizing_example_predicted_tad_bounds.Rmd

@@
 
-ggplot(predprob_df_temp, aes(x=baseNum, y=PredProb)) +
-     geom_line(size=.5)+
-     #geom_smooth(method = "loess", size = 5, color="blue")
-	   geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$PredProb==1)], 
-	              color="red", 
-	              #linetype="dashed", 
+dat1 <- predprob_df_temp[which(predprob_df_temp$PredProb==1),]
+
+ggplot() + 
+  geom_line(data=predprob_df_temp, aes(x=baseNum, y=PredProb), 
+              color='black',
               size=.5)+
-     geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], 
-	              color="blue", 
-	              #linetype="dashed", 
-	              size=.5)+
+  geom_vline(data=dat1, aes(xintercept=baseNum, 
+             color=as.factor(PredProb)),
+             size=.75,
+             show.legend = TRUE)+
   xlab("Base Pair") +
   ylab("Predicted Probability") +
+  scale_color_manual(name = '', 
+         values =c("red"),
+         labels = c('Predicted Region'))+
   theme_minimal() +
@@
 fviz_dist(x, gradient = list(low = "white", mid = "pink", high = muted("red")))+
-  xlab("")+
-  ylab("")+
+  xlab("Predicted Boundary Regions")+
+  ylab("Predicted Boundary Regions")+
   #scale_fill_continuous("Distance")+
-  scale_fill_gradient2("Distance",
+  scale_fill_gradient2("Distance\nBetween\nMidpoints",
                        low = "white", 
@@
 
-hc1 <- hclust(x, method = "complete")
+hc1 <- hclust(x, method = "complete", size=2)
 plot(hc1)
@@
 k = which.max(z)+1
-p <- pam(x, diss=TRUE, k=k, cluster.only=TRUE, trace.lev = 0)
-clustdf <- data.frame(mid=predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], clust=cutree(hc1, k=k))
+c <- clara(predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], k=k, metric = "euclidean",
+           stand = FALSE, 
+           trace = 2, medoids.x = TRUE)
+clustdf <- data.frame(mid=predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], clust=c$clustering, medoid=ifelse(predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")] %in% c$medoids, "Yes", "No"))
 
-plot(hc1, hang = -1)
+dend <- as.dendrogram(hc1)
+dend %>% set("labels_col", c("red","green","red","red","green","red","green","red","red","green")) %>% set("labels_cex", 2) %>% plot(main = "Clustered Distances")
 rect.hclust(hc1, k = k)
 
-prob1intervals <- unique(clustdf$clust)
-  mid2 <- numeric()
-  for(i in prob1intervals){
-    dat <- clustdf[which(clustdf$clust==prob1intervals[i]),]
-    n=dim(dat)[1]
-    mid2[i] <- ceiling((dat$mid[1]+dat$mid[n])/2)
-  }
+#prob1intervals <- unique(clustdf$clust)
+#  mid2 <- numeric()
+#  for(i in prob1intervals){
+#    dat <- clustdf[which(clustdf$clust==prob1intervals[i]),]
+#    n=dim(dat)[1]
+#    mid2[i] <- ceiling((dat$mid[1]+dat$mid[n])/2)
+#  }
 
-  predprob_df_temp$predBound2 <- ifelse(predprob_df_temp$baseNum %in% mid2, "Yes", "No")
+  predprob_df_temp$predBound2 <- ifelse(predprob_df_temp$baseNum %in% c$medoids, "Yes", "No")
+
+  dat2 <- predprob_df_temp[which(predprob_df_temp$predBound2=="Yes"),]
 
@@
      #geom_smooth(method = "loess", size = 5, color="blue")
-	   geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$PredProb==1)], 
-	              color="red", 
-	              #linetype="dashed", 
-	              size=.5)+
-     geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$predBound2=="Yes")], 
-	              color="blue", 
-	              #linetype="dashed", 
-	              size=1)+
+	   geom_vline(data=dat1, aes(xintercept=baseNum, 
+             color=as.factor(PredProb)),
+             size=.75,
+             show.legend = TRUE)+
+     geom_vline(data=dat2, aes(xintercept=baseNum, 
+             color=predBound2),
+             size=.75,
+             show.legend = TRUE)+
+     scale_color_manual(name = '', 
+         values =c("red", "green"),
+         labels = c('Predicted Region',
+                    'Predicted Boundary'))+
      xlab("Base Pair") +
@@
 
+#dat3 <- predprob_df_temp[which(predprob_df_temp$predBound2=="Yes"),]
+#dat3$predBound2 <- "T"
+
+#ggplot() + 
+#  geom_line(data=predprob_df_temp, aes(x=baseNum, y=PredProb), 
+#              color='black',
+#              size=.5)+
+#  geom_vline(data=dat1, aes(xintercept=baseNum, 
+#             color=as.factor(PredProb)),
+#             size=.75,
+#             show.legend = TRUE)+
+#  geom_vline(data=dat2, aes(xintercept=baseNum, 
+#             color=predBound),
+#             size=.75,
+#             show.legend = TRUE)+
+#  geom_vline(data=dat3, aes(xintercept=baseNum, 
+#             color=predBound2),
+#             size=.75,
+#             show.legend = TRUE)+
+#  xlab("Base Pair") +
+#  ylab("Predicted Probability") +
+#  scale_color_manual(name = '', 
+#         values =c("red", "blue", "green"),
+#         labels = c('Predicted Region',
+#                    'New Predicted Boundary',
+#                    'Midpoint'))+
+#  theme_minimal() +
+#  theme_bw() +
+#  theme(axis.text.x = element_text(size=15),
+#        axis.text.y = element_text(size = 15),
+#        axis.title.x = element_text(size = 20),
+#        axis.title.y = element_text(size = 20),
+#        #strip.text.x = element_text(size = 15),
+#        #panel.spacing = unit(2, "lines"),
+#        legend.text=element_text(size=15),
+#        legend.title=element_text(size=20),
+#        plot.title = element_text(size=20),
+#        legend.position = "bottom")
+
 ```

### 2019-08-23 Papers.Rmd
Add collinearity note
Add Peakachu paper

@@
 ## TAD predictions
+
+- Salameh, Tarik J, Xiaotao Wang, Fan Song, Bo Zhang, Sage M.
+Wright, Chachrit Khunsriraksakul, and Feng Yue.
+“A Supervised Learning Framework for Chromatin Loop Detection in Genome-Wide Contact Maps.” Preprint.
+Bioinformatics, August 20, 2019.
+https://doi.org/10.1101/739698.
+- Peakachu - loop prediction from Hi-C data using random forest.
+ChIA-PET and HiChIP provide positive training examples.
+H3K27ac HiChIP better predicts short-range interactions, CTCF ChIA-PET is better for longer interactions.
+Each pixel is characterized by 11x11 window, 10Kb resolution data, Gm12878 and K562 cell line.
+Excels for short-range interactions.
+Model trained using data from Hi-C performs well in other technologies, Micro-C, DNA SPRITE.
+Code athttps://github.com/tariks/peakachu, Predicted loops for 56 cell/tissue types are available athttp://promoter.bx.psu.edu/hi-c/publications.html
 
@@
 
+- Check your (Mixed) Model for Multicollinearity with ‘performance’, https://www.r-bloggers.com/check-your-mixed-model-for-multicollinearity-with-performance/
+
 - TAD boundaries are blurry - Van Bortle K., Nichols M.H., Li L., Ong C.-T., Takenaka N., Qin Z.S., Corces V.G.

### 2019-08-23 Scripts/comparing_predicted_boundaries_vs_called_boundaries.Rmd
edits

--- 2019-08-09 Scripts/comparing_predicted_boundaries_vs_called_boundaries.Rmd
@@
 true_bound_list <- GRangesList()
-chrs <- paste0("CHR", c(17:22))
+chrs <- paste0("CHR", c(1:8,10:22))
+chrs <- paste0("CHR", c(2:8,10:15,17:22))
 for(i in 1:length(chrs)){
@@
                                     chrs[i],
-                                    "/smote/distance/enet/called_and_pred_bound_regions.rds"))
+                                    "/smote/distance/enet/called_and_pred_bounds.rds"))
 
-  true_bound_list[[i]] <- called_and_pred[[3]]
-  pred_bound_list[[i]] <- called_and_pred[[4]]
+  true_bound_list[[i]] <- called_and_pred[[1]]
+  pred_bound_list[[i]] <- called_and_pred[[2]]
 
@@
 all_pred_bounds <- do.call("c", pred_bound_list)
+
+length(all_true_bounds) #12388
+length(all_pred_bounds) #7708
+
+all_pred_bounds_r <- flank(all_pred_bounds, width=10000, both=TRUE)
 
@@
 
-res <- makeVennDiagram(Peaks=list(all_true_bounds, all_pred_bounds),
+res <- makeVennDiagram(Peaks=list(all_true_bounds, all_pred_bounds_r),
                        NameOfPeaks=c("Called", "Predicted"),
@@
 e = 10000
-axis_names <- c("-10 kb", "Center", "10 kb")
+axis_names <- c("-10kb", "Center", "10kb")
 ```
@@
 
-mat = normalizeToMatrix(annots.GR.f[[1]], 
+mat_pred_ctcf = normalizeToMatrix(annots.GR.f[[1]], 
                          all_pred_bounds, 
@@
 
-EnrichedHeatmap(mat, 
-                col = c("white", muted("red")), 
-                heatmap_legend_param = list(title = "CTCF"),
-                row_title="Chromosomes",
+EnrichedHeatmap(mat_pred_ctcf, 
+                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
                 row_title_side="left", 
@@
                 axis_name = axis_names,
-                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col ="red", 
+                                                                                   lwd = 2), 
                                                                          yaxis_side = "right", 
@@
 
-mat = normalizeToMatrix(annots.GR.f[[1]], 
+mat_called_ctcf = normalizeToMatrix(annots.GR.f[[1]], 
                          all_true_bounds_r, 
@@
 
-EnrichedHeatmap(mat, 
-                col = c("white", muted("red")), 
-                heatmap_legend_param = list(title = "CTCF"),
-                row_title="Chromosomes",
+EnrichedHeatmap(mat_called_ctcf, 
+                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
                 row_title_side="left", 
@@
                 axis_name = axis_names,
-                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red", 
+                                                                                   lwd = 2,
+                                                                                   lty=3), 
                                                                          yaxis_side = "right", 
-                                                                         yaxis_facing = "right")))
+                                                                         yaxis_facing = "left")))
 ```
@@
 
-mat = normalizeToMatrix(annots.GR.f[[2]], 
+mat_pred_rad21 = normalizeToMatrix(annots.GR.f[[2]], 
                          all_pred_bounds, 
@@
 
-EnrichedHeatmap(mat, 
-                col = c("white", muted("red")), 
-                heatmap_legend_param = list(title = "RAD21"),
-                row_title="Chromosomes",
+EnrichedHeatmap(mat_pred_rad21, 
+                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
                 row_title_side="left", 
@@
                 axis_name = axis_names,
-                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red", 
+                                                                                   lwd = 2), 
                                                                          yaxis_side = "right", 
@@
 
-mat = normalizeToMatrix(annots.GR.f[[2]], 
+mat_called_rad21 = normalizeToMatrix(annots.GR.f[[2]], 
                          all_true_bounds_r, 
@@
 
-EnrichedHeatmap(mat, 
-                col = c("white", muted("red")), 
-                heatmap_legend_param = list(title = "RAD21"),
-                row_title="Chromosomes",
+EnrichedHeatmap(mat_called_rad21, 
+                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
                 row_title_side="left", 
@@
                 axis_name = axis_names,
-                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red", 
+                                                                                   lwd = 2,
+                                                                                   lty = 3), 
                                                                          yaxis_side = "right", 
-                                                                         yaxis_facing = "right")))
+                                                                         yaxis_facing = "left")))
 ```
@@
 
-mat = normalizeToMatrix(annots.GR.f[[3]], 
+mat_pred_smc3 = normalizeToMatrix(annots.GR.f[[3]], 
                          all_pred_bounds, 
@@
 
-EnrichedHeatmap(mat, 
-                col = c("white", muted("red")), 
-                heatmap_legend_param = list(title = "SMC3"),
-                row_title="Chromosomes",
+EnrichedHeatmap(mat_pred_smc3, 
+                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
                 row_title_side="left", 
@@
 
-mat = normalizeToMatrix(annots.GR.f[[3]], 
+mat_called_smc3 = normalizeToMatrix(annots.GR.f[[3]], 
                          all_true_bounds_r, 
@@
 
-EnrichedHeatmap(mat, 
-                col = c("white", muted("red")), 
-                heatmap_legend_param = list(title = "SMC3"),
-                row_title="Chromosomes",
+EnrichedHeatmap(mat_called_smc3, 
+                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
                 row_title_side="left", 
@@
 
-mat = normalizeToMatrix(annots.GR.f[[4]], 
+mat_pred_znf143 = normalizeToMatrix(annots.GR.f[[4]], 
                          all_pred_bounds, 
@@
 
-EnrichedHeatmap(mat, 
-                col = c("white", muted("red")), 
-                heatmap_legend_param = list(title = "ZNF143"),
-                row_title="Chromosomes",
+EnrichedHeatmap(mat_pred_znf143, 
+                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
                 row_title_side="left", 
@@
 
-mat = normalizeToMatrix(annots.GR.f[[4]], 
+mat_called_znf143 = normalizeToMatrix(annots.GR.f[[4]], 
                          all_true_bounds_r, 
@@
 
-EnrichedHeatmap(mat, 
-                col = c("white", muted("red")), 
-                heatmap_legend_param = list(title = "ZNF143"),
-                row_title="Chromosomes",
+EnrichedHeatmap(mat_called_znf143, 
+                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
                 row_title_side="left", 
@@
 
+<!--
 ### Predicted
@@
 ```
+-->
+
+### Plots v2
+
+```{r}
+
+pred_v_called_10_df <- data.frame(LogDist = c(#Predicted
+    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1),
+    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[2]]))$distance+1),
+    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[3]]))$distance+1),
+    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[4]]))$distance+1),
+
+    #Called
+    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1),
+    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[2]]))$distance+1),
+    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[3]]))$distance+1),
+    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[4]]))$distance+1)
+),
+Annotation = c(#Predicted
+    rep("CTCF",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("RAD21",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("SMC3",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("ZNF143",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+
+    #Called
+    rep("CTCF",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
+    rep("RAD21",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
+    rep("SMC3",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
+    rep("ZNF143",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1)))),
+BoundReg = c(#Predicted
+    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+
+    #Called
+    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
+    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
+    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
+    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1)))))
+
+pred_v_called_10_df$BoundReg <- factor(pred_v_called_10_df$BoundReg, levels=c("Predicted", "Called"))
+
+ggplot(pred_v_called_10_df, aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  + 
+    facet_grid(~ Annotation) +    
+    stat_boxplot(geom ='errorbar', width = 0.2) + 
+    geom_boxplot(outlier.shape = NA) +
+    geom_signif(test = "wilcox.test", 
+                comparisons = list( c("Predicted", "Called")),
+                vjust = 0,
+                textsize = 4,
+                size = .5,
+                step_increase = .08,
+                color="black") +
+    theme_minimal()+
+    theme_bw()+
+    ylab("Log2 Distance to Annotation")+
+    xlab("") +
+    scale_fill_manual(name="Boundary Region",
+                      values=c("red",
+                               "blue"))+
+    scale_color_manual(values=c("red",
+                                "blue")) +
+    guides(color=FALSE, linetype=FALSE)+
+    theme(axis.text.x = element_text(size=15,
+                                     angle = 45,
+                                     hjust = 1),
+          axis.text.y = element_text(size = 15),
+          axis.title.x = element_text(size = 20),
+          axis.title.y = element_text(size = 20),
+          strip.text.x = element_text(size = 15),
+          #panel.spacing = unit(2, "lines"),
+          legend.text=element_text(size=15),
+          legend.title=element_text(size=20),
+          plot.title = element_text(size=20),
+          legend.position = "bottom")
+```
+
+# K562
+
+## Create granges from top tfbs
+
+```{r}
+source("C:/Users/stili/Documents/TAD_predictive_modeling/Scripts/functions_for_R_package/annots_to_granges_func.r")
+#file_path="Z:/TAD_data_analysis/annotations/all_common_annotations/k562/chr22_tfbs_gm12878"
+file_path="Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS"
+annots.GR <- annots_to_granges_func(filepath=file_path)
+
+```
+
+## Overlap between Called Regions and Predicted Boundaroes
+
+```{r}
+
+pred_bound_list <- GRangesList()
+true_bound_list <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+chrs <- paste0("CHR", c(2:8,10:15,17:22))
+for(i in 1:length(chrs)){
+  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+                                    chrs[i],
+                                    "/smote/distance/enet/called_and_pred_bounds.rds"))
+
+  true_bound_list[[i]] <- called_and_pred[[1]]
+  pred_bound_list[[i]] <- called_and_pred[[2]]
+
+}
+
+all_true_bounds <- do.call("c", true_bound_list)
+all_pred_bounds <- do.call("c", pred_bound_list)
+
+length(all_true_bounds) #9301
+length(all_pred_bounds) #9656
+
+all_pred_bounds_r <- flank(all_pred_bounds, width=10000, both=TRUE)
+
+venn_cnt2venn <- function(venn_cnt){
+  n <- which(colnames(venn_cnt)=="Counts") - 1
+  SetNames=colnames(venn_cnt)[1:n]
+  Weight=venn_cnt[,"Counts"]
+  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
+  Venn(SetNames=SetNames, Weight=Weight)
+}
+
+res <- makeVennDiagram(Peaks=list(all_true_bounds, all_pred_bounds_r),
+                       NameOfPeaks=c("Called", "Predicted"),
+                       connectedPeaks = "keepAll")
+venn_k562 <- venn_cnt2venn(res$vennCounts)
+venn_k562 <- compute.Venn(venn_k562)
+gp <- VennThemes(venn_k562)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_k562, 
+                                                 gp = gp, 
+                                                 show=list(Universe=FALSE))), 
+                        top=textGrob("Boundary Region", 
+                                     gp=gpar(fontsize=50)))
+
+```
+
+## Enriched Heatmaps
+
+```{r}
+annots.GR.f <- lapply(annots.GR, function(x){x[which(as.character(seqnames(x)) %in% tolower(chrs))]})
+
+all_true_bounds_r <- resize(all_true_bounds, width=1,fix = "center")
+
+e = 10000
+axis_names <- c("-10kb", "Center", "10kb")
+```
+
+### CTCF
+
+#### Predicted
+
+```{r}
+
+mat_pred_ctcf = normalizeToMatrix(annots.GR.f[[1]], 
+                         all_pred_bounds, 
+                         value_column = "coverage", 
+                         extend = e, 
+                         mean_mode = "w0",
+                         keep = c(0,.99))
+
+EnrichedHeatmap(mat_pred_ctcf, 
+                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
+                row_title_side="left", 
+                column_title="Predicted", 
+                axis_name = axis_names,
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col ="blue", 
+                                                                                   lwd = 2), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+```
+
+#### Called
+
+```{r}
+
+mat_called_ctcf = normalizeToMatrix(annots.GR.f[[1]], 
+                         all_true_bounds_r, 
+                         value_column = "coverage", 
+                         extend = e, 
+                         mean_mode = "w0",
+                         keep = c(0,.99))
+
+EnrichedHeatmap(mat_called_ctcf, 
+                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
+                row_title_side="left", 
+                column_title="Called", 
+                axis_name = axis_names,
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
+                                                                                   lwd = 2,
+                                                                                   lty=3), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+```
+
+### RAD21
+
+#### Predicted
+
+```{r}
+
+mat_pred_rad21 = normalizeToMatrix(annots.GR.f[[2]], 
+                         all_pred_bounds, 
+                         value_column = "coverage", 
+                         extend = e, 
+                         mean_mode = "w0",
+                         keep = c(0,.99))
+
+EnrichedHeatmap(mat_pred_rad21, 
+                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
+                row_title_side="left", 
+                column_title="Predicted", 
+                axis_name = axis_names,
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
+                                                                                   lwd = 2), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+```
+
+#### Called
+
+```{r}
+
+mat_called_rad21 = normalizeToMatrix(annots.GR.f[[2]], 
+                         all_true_bounds_r, 
+                         value_column = "coverage", 
+                         extend = e, 
+                         mean_mode = "w0",
+                         keep = c(0,.99))
+
+EnrichedHeatmap(mat_called_rad21, 
+                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
+                row_title_side="left", 
+                column_title="Called", 
+                axis_name = axis_names,
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
+                                                                                   lwd = 2,
+                                                                                   lty = 3), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+```
+
+### SMC3
+
+#### Predicted
+
+```{r}
+
+mat_pred_smc3 = normalizeToMatrix(annots.GR.f[[3]], 
+                         all_pred_bounds, 
+                         value_column = "coverage", 
+                         extend = e, 
+                         mean_mode = "w0",
+                         keep = c(0,.99))
+
+EnrichedHeatmap(mat_pred_smc3, 
+                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
+                row_title_side="left", 
+                column_title="Predicted", 
+                axis_name = axis_names,
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
+                                                                                   lwd = 2), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+```
+
+#### Called
+
+```{r}
+
+mat_called_smc3 = normalizeToMatrix(annots.GR.f[[3]], 
+                         all_true_bounds_r, 
+                         value_column = "coverage", 
+                         extend = e, 
+                         mean_mode = "w0",
+                         keep = c(0,.99))
+
+EnrichedHeatmap(mat_called_smc3, 
+                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
+                row_title_side="left", 
+                column_title="Called", 
+                axis_name = axis_names,
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
+                                                                                   lwd = 2,
+                                                                                   lty = 3), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+```
+
+### ZNF143
+
+#### Predicted
+
+```{r}
+
+mat_pred_znf143 = normalizeToMatrix(annots.GR.f[[4]], 
+                         all_pred_bounds, 
+                         value_column = "coverage", 
+                         extend = e, 
+                         mean_mode = "w0",
+                         keep = c(0,.99))
+
+EnrichedHeatmap(mat_pred_znf143, 
+                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
+                row_title_side="left", 
+                column_title="Predicted", 
+                axis_name = axis_names,
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
+                                                                                   lwd = 2), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+```
+
+#### Called
+
+```{r}
+
+mat_called_znf143 = normalizeToMatrix(annots.GR.f[[4]], 
+                         all_true_bounds_r, 
+                         value_column = "coverage", 
+                         extend = e, 
+                         mean_mode = "w0",
+                         keep = c(0,.99))
+
+EnrichedHeatmap(mat_called_znf143, 
+                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
+                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
+                row_title="Chromosomes",show_heatmap_legend = FALSE,
+                row_title_side="left", 
+                column_title="Called", 
+                axis_name = axis_names,
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
+                                                                                   lwd = 2,
+                                                                                   lty = 3), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+```
+
+### Plots v2
+
+```{r}
+
+pred_v_called_10_df <- data.frame(LogDist = c(#Predicted
+    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1),
+    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[2]]))$distance+1),
+    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[3]]))$distance+1),
+    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[4]]))$distance+1),
+
+    #Called
+    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1),
+    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[2]]))$distance+1),
+    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[3]]))$distance+1),
+    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[4]]))$distance+1)
+),
+Annotation = c(#Predicted
+    rep("CTCF",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("RAD21",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("SMC3",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("ZNF143",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+
+    #Called
+    rep("CTCF",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
+    rep("RAD21",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
+    rep("SMC3",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
+    rep("ZNF143",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1)))),
+BoundReg = c(#Predicted
+    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
+
+    #Called
+    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
+    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
+    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
+    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1)))))
+
+pred_v_called_10_df$BoundReg <- factor(pred_v_called_10_df$BoundReg, levels=c("Predicted", "Called"))
+
+ggplot(pred_v_called_10_df, aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  + 
+    facet_grid(~ Annotation) +    
+    stat_boxplot(geom ='errorbar', width = 0.2) + 
+    geom_boxplot(outlier.shape = NA) +
+    geom_signif(test = "wilcox.test", 
+                comparisons = list( c("Predicted", "Called")),
+                vjust = 0,
+                textsize = 4,
+                size = .5,
+                step_increase = .08,
+                color="black") +
+    theme_minimal()+
+    theme_bw()+
+    ylab("Log2 Distance to Annotation")+
+    xlab("") +
+    scale_fill_manual(name="Boundary Region",
+                      values=c("red",
+                               "blue"))+
+    scale_color_manual(values=c("red",
+                                "blue")) +
+    guides(color=FALSE, linetype=FALSE)+
+    theme(axis.text.x = element_text(size=15,
+                                     angle = 45,
+                                     hjust = 1),
+          axis.text.y = element_text(size = 15),
+          axis.title.x = element_text(size = 20),
+          axis.title.y = element_text(size = 20),
+          strip.text.x = element_text(size = 15),
+          #panel.spacing = unit(2, "lines"),
+          legend.text=element_text(size=15),
+          legend.title=element_text(size=20),
+          plot.title = element_text(size=20),
+          legend.position = "bottom")
+```

### 2019-08-23 Scripts/evaluating_imbalance_ratios.Rmd
edits

@@
 
-      ir.per.chr <- rbind(ir.per.chr, table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[1]/table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2])
+      ir.per.chr <- rbind(ir.per.chr, table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2]/(table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[1]+table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2]))
 

### 2019-08-23 Scripts/evaluating_rfe_across_chromosomes.Rmd
edits

@@
 ```{r}
-
 rfeperchr <- data.frame()
@@
 
-#gm12878
+```
+
+#### GM12878
+
+```{r}
+
 rfegm12878 <- rfeperchr[which(rfeperchr$CL=="GM12878"),]
@@
           Colv = reorder(as.dendrogram(cluster.col), 37:1),
-          cexRow=1.5,
-          cexCol=1.5,
+          cexRow=.5,
+          cexCol=1,
           #labRow = FALSE,
@@
 ```
+
+#### K562
+
+```{r}
+rfek562 <- rfeperchr[which(rfeperchr$CL=="K562"),]
+rfek562 <- reshape(rfek562[,c(1,2,4)], idvar = "Feature", timevar = "Chromosome", direction = "wide")
+names(rfek562)[-1] <- paste0("CHR", c(1:8,10:22)) 
+rfek562.mat <- as.matrix(rfek562[,-1])
+rownames(rfek562.mat) <- rfek562$Feature
+rfek562.mat[is.na(rfek562.mat)] <- 0
+#rfek562.mat <- apply(rfek562.mat,2,rev)
+
+#using heatmap.2
+distance.col = dist(rfek562.mat, method = "euclidean")
+cluster.col = hclust(distance.col, method = "average")
+my_palette <- colorRampPalette(c("white", "lightblue", "blue"))(ncol(rfek562.mat))
+heatmap.2(t(rfek562.mat),
+          #labRow=rownames(rfek562.mat),
+          #labCol=colnames(rfek562.mat),
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins=c(12,8),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #keysize = 1.5,
+          #key.title = "Elastic-Net Coefficient",
+          dendrogram="column",     # only draw a row dendrogram,
+          Rowv = FALSE,
+          Colv = reorder(as.dendrogram(cluster.col), 37:1),
+          cexRow=.5,
+          cexCol=1,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          rowsep=0:nrow(t(rfek562.mat)),
+          colsep=0:ncol(t(rfek562.mat)),
+          sepwidth=c(0.001,0.001),
+          sepcolor="black"
+) 
+```

### 2019-08-23 Scripts/visualizing_example_predicted_tad_bounds.Rmd
edits

--- 2019-08-09 Scripts/visualizing_example_predicted_tad_bounds.Rmd
@@
 library(factoextra)
+library(dendextend)
 ```
@@
 
-###17390000-18640000
+###17380000-18650000 (first 10 called TAD boundaries)
 
 ```{r}
-called_and_pred_bound_regions <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR22/smote/distance/enet/called_and_pred_bound_regions.rds")
+#GM12878
+#CHR22
 
-predprob_df_1 <- called_and_pred_bound_regions[[1]]
-predprob_df <- called_and_pred_bound_regions[[2]]
-trueBound_gr_region <- called_and_pred_bound_regions[[3]]
-predBound_gr <- called_and_pred_bound_regions[[4]]
+#reading in probability vector
+pred.TADModel <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR22/smote/distance/enet/pred.TADModel.rds")
 
-predprob_df$baseNum[which(predprob_df$trueBound=="Yes")][1:10]
-#17390000 17540000 17550000 17650000 17820000 18010000 18030000 18210000 18280000 18640000
+#reading in called and predicted TAD boundary regions
+called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR22/smote/distance/enet/called_and_pred_bounds.rds"))
 
-predprob_df_temp <- predprob_df[which(predprob_df$baseNum>=17390000 & predprob_df$baseNum<=18640000),]
-table(predprob_df_temp$predBound)
+#assigning called tad boundaries
+called <- called_and_pred[[1]]
+called <- resize(called, width=1,fix = "center")
 
-ggplot(predprob_df_temp, aes(x=baseNum, y=PredProb)) +
-     geom_line(size=.5)+
-     #geom_smooth(method = "loess", size = 5, color="blue")
-	   geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$PredProb==1)], 
-	              color="red", 
-	              #linetype="dashed", 
+#assigning predicted tad boundaries
+predicted <- called_and_pred[[2]]
+
+#reading in base pair data for chromosome 22
+seqData <- readRDS("Z:/TAD_data_analysis/seq_data/seqData_CHR22.rds")
+
+#creating a dataframe with base pair coordinates, what the probability of each base pair being a TAD boundary, and which base pair corresponds to a called tad boundary
+predprobdata <- data.frame(basenum = seqData,
+                           prob = pred.TADModel,
+                           called = ifelse(seqData %in% start(called), "Yes", "No"))
+dim(predprobdata) #48284564        4
+
+rm(seqData)
+rm(pred.TADModel)
+rm(called_and_pred)
+
+start(called)[1:10]
+#17389999 17539999 17549999 17649999 17819999 18009999 18029999 18209999 18279999 18639999
+
+#creating a window from the first called tad boundary to the 10th called tad boundary (+- 10000 bp)
+s=start(called)[1:10][1]-10000+1
+e=start(called)[1:10][10]+10000+1
+
+predprobdata2 <- predprobdata[which(predprobdata$basenum>=s & predprobdata$basenum <= e), ]
+dim(predprobdata2) #1270001       3
+
+#datasets for plotting
+##only called boundaries
+calleddata <- predprobdata2[which(predprobdata2$called=="Yes"),]
+dim(calleddata) #10  3
+##only predicted tad regions (p=1)
+predicteddata <- predprobdata2[which(predprobdata2$prob==1),]
+dim(predicteddata) #20055     3
+
+#plot
+ggplot() + 
+  geom_line(data=predprobdata2, aes(x=basenum, y=prob), 
+            color='black',
             size=.5)+
-     geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], 
-	              color="blue", 
-	              #linetype="dashed", 
-	              size=.5)+
+  geom_vline(data=calleddata, aes(xintercept=basenum, 
+                            color="blue"),
+             size=.75,
+             show.legend = TRUE)+
+  geom_vline(data=predicteddata, aes(xintercept=basenum, 
+                                  color="red"),
+             size=.75,
+             show.legend = TRUE)+
   xlab("Base Pair") +
   ylab("Predicted Probability") +
+  scale_color_manual(name = '', 
+                     values =c("blue", "red"),
+                     labels = c("Called Boundary", 'Predicted Region'))+
   theme_minimal() +
@@
 
-x <- dist(predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], method = "euclidean")
+#determine midpoints of predicted tad regions
+prob1basenumdiff <- diff(predicteddata$basenum)
+retain <- numeric()
+x <- 1
+for(i in 1:length(prob1basenumdiff)){
+  if(prob1basenumdiff[i]<=1){retain[i] = x}else{x = x+1; retain[i] = x}
+}
+retain = c(1,retain)
+length(table(retain)) #95
 
-xlabels <- c("1", "2", "3", "9", "10", "4", "5", "8", "6", "7")
+mid <- numeric()
+for(i in unique(retain)){
+  #print(i)
+  bpdat <- predicteddata$basenum[which(retain==i)]
+  n=length(bpdat)
+  mid[i] <- ceiling((bpdat[1]+bpdat[n])/2)
+}
+
+#create distance matrix of all pairwise distances between midpoints
+x <- dist(mid, method = "euclidean")
+
+#visualize distance matrix
 fviz_dist(x, gradient = list(low = "white", mid = "pink", high = muted("red")))+
-  xlab("")+
-  ylab("")+
+  xlab("Predicted Boundary Regions")+
+  ylab("Predicted Boundary Regions")+
   #scale_fill_continuous("Distance")+
-  scale_fill_gradient2("Distance",
+  scale_fill_gradient2("Distance\nBetween\nMidpoints",
                        low = "white", 
                        mid = "pink",
-                       midpoint = 450000,
-                       high = muted("red"))+
-  scale_x_discrete(labels=xlabels)+
-  scale_y_discrete(labels=xlabels)+
+                       midpoint = 600000,
+                       high = muted("red"),
+                       limits=c(0,1200000),
+                       breaks=c(0,400000, 800000, 1200000),
+                       labels=c("0","400000", "800000", "1200000"))+
+  #scale_x_discrete(labels=xlabels)+
+  #scale_y_discrete(labels=xlabels)+
+  theme_minimal()+
+  theme(axis.text.x = element_text(size = 5),
+        axis.text.y = element_text(size = 5),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        #panel.grid.major = element_blank(),
+        #panel.grid.minor = element_blank(),
+        #strip.text.x = element_text(size = 15),
+        #panel.spacing = unit(2, "lines"),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        plot.title = element_text(size=20))
+
+#cluster distance matrix
+hc1 <- hclust(x, method = "complete")
+plot(hc1)
+
+#determine suitable number of clusters using the silhouette method
+z <- sapply(2:(length(mid)-1), function(i) { 
+  mean(silhouette(cutree(hc1, i), dist=x)[,"sil_width"]) })
+k=which.max(z)+1
+k #10
+
+#perform PAM clustering to determine cluster centers
+c <- clara(mid, 
+           k=k, 
+           samples=100,
+           metric = "euclidean",
+           stand = FALSE, 
+           trace = 2, 
+           medoids.x = TRUE)
+clustdf <- data.frame(mid=mid, 
+                      clust=c$clustering, 
+                      medoid=ifelse(mid %in% c$medoids, "Yes", "No"))
+
+dend <- as.dendrogram(hc1)
+dend %>% set("labels_colors", 
+             value=as.numeric(clustdf$medoid)+1) %>% 
+  set("labels_cex", value=1.5) %>% 
+  plot(main = "Clustered Distances", xlab="Predicted Boundary Regions")
+rect.hclust(hc1, k = k)
+
+#assign cluster centers as predicted TAD boundaries
+predprobdata2$predicted <- ifelse(predprobdata2$basenum %in% clustdf$mid[which(clustdf$medoid=="Yes")], "Yes", "No")
+
+predicteddata2 <- predprobdata2[which(predprobdata2$predicted=="Yes"),]
+
+ggplot() + 
+  geom_line(data=predprobdata2, aes(x=basenum, y=prob), 
+            color='black',
+            size=.5)+
+  geom_vline(data=calleddata, aes(xintercept=basenum, 
+                                  color="blue"),
+             size=.75,
+             show.legend = TRUE)+
+  geom_vline(data=predicteddata, aes(xintercept=basenum, 
+                                     color="red"),
+             size=.75,
+             show.legend = TRUE)+
+  geom_vline(data=predicteddata2, aes(xintercept=basenum, 
+                                     color="green"),
+             size=.75,
+             show.legend = TRUE)+
+  xlab("Base Pair") +
+  ylab("Predicted Probability") +
+  scale_color_manual(name = '', 
+                     values =c("blue", "green", "red"),
+                     labels = c("Called Boundary",
+                                "Predicted Boundary",
+                                "Predicted Region"))+
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        #strip.text.x = element_text(size = 15),
+        #panel.spacing = unit(2, "lines"),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        plot.title = element_text(size=20),
+        legend.position = "bottom")
+
+```
+
+# GM12878
+
+## CHR22
+
+### 17390000-18640000 (first called TAD on chr 22; 2 boundaries)
+
+```{r}
+domains <- read.table("Z:/TAD_data_analysis/GM12878/10kb/GM12878_domain_data_10000.b.txt", header=F)
+resolution=as.integer(10000)
+preprocess=TRUE
+domains.mat=domains
+domains.mat <- domains.mat[,1:3]
+domains.mat[,1] <- paste0("chr",domains.mat[,1])
+colnames(domains.mat) <- c("Chromosome", "Start", "End")
+if(preprocess==TRUE){
+  ##restricting domain data to TADs > 2*resolution and < 2,000,000
+  domains.mat <- domains.mat[which((domains.mat$End - domains.mat$Start)>(2*resolution) & (domains.mat$End - domains.mat$Start)<2000000),]
+}
+
+head(domains.mat[which(domains.mat$Chromosome=="chr22"),])
+d <- domains.mat[which(domains.mat$Chromosome=="chr22"),]
+head(d[order(d$Start, decreasing = FALSE),])
+d <- d[order(d$Start, decreasing = FALSE),]
+
+s=d$Start[1]-1000
+e=d$End[2]+1000
+predprobdata2 <- predprobdata[which(predprobdata$basenum>=s & predprobdata$basenum <= e), ]
+dim(predprobdata2) #152001      3
+
+calleddata <- predprobdata2[which(predprobdata2$called=="Yes"),]
+dim(calleddata) #2 3
+
+predicteddata <- predprobdata2[which(predprobdata2$prob==1),]
+dim(predicteddata) #3471    3
+
+ggplot() + 
+  geom_line(data=predprobdata2, aes(x=basenum, y=prob), 
+            color='black',
+            size=.5)+
+  geom_vline(data=calleddata, aes(xintercept=basenum, 
+                                  color="blue"),
+             size=.75,
+             show.legend = TRUE)+
+  geom_vline(data=predicteddata, aes(xintercept=basenum, 
+                                     color="red"),
+             size=.75,
+             show.legend = TRUE)+
+  xlab("Base Pair") +
+  ylab("Predicted Probability") +
+  scale_color_manual(name = '', 
+                     values =c("blue", "red"),
+                     labels = c("Called Boundary", 'Predicted Region'))+
+  theme_minimal() +
+  theme_bw() +
+  theme(axis.text.x = element_text(size=15),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        #strip.text.x = element_text(size = 15),
+        #panel.spacing = unit(2, "lines"),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        plot.title = element_text(size=20),
+        legend.position = "bottom")
+
+prob1basenumdiff <- diff(predicteddata$basenum)
+retain <- numeric()
+x <- 1
+for(i in 1:length(prob1basenumdiff)){
+  if(prob1basenumdiff[i]<=1){retain[i] = x}else{x = x+1; retain[i] = x}
+}
+retain = c(1,retain)
+length(table(retain)) #20
+
+mid <- numeric()
+for(i in unique(retain)){
+  #print(i)
+  bpdat <- predicteddata$basenum[which(retain==i)]
+  n=length(bpdat)
+  mid[i] <- ceiling((bpdat[1]+bpdat[n])/2)
+}
+
+x <- dist(mid, method = "euclidean")
+
+fviz_dist(x, gradient = list(low = "white", mid = "pink", high = muted("red")))+
+  xlab("Predicted Boundary Regions")+
+  ylab("Predicted Boundary Regions")+
+  #scale_fill_continuous("Distance")+
+  scale_fill_gradient2("Distance\nBetween\nMidpoints",
+                       low = "white", 
+                       mid = "pink",
+                       midpoint = 75000,
+                       high = muted("red"),
+                       limits=c(0,150000),
+                       breaks=c(0,50000,100000,150000),
+                       labels=c("0","50000", "100000", "150000"))+
+  #scale_x_discrete(labels=xlabels)+
+  #scale_y_discrete(labels=xlabels)+
   theme_minimal()+
@@
 plot(hc1)
+z <- sapply(2:(length(mid)-1), function(i) { 
+  mean(silhouette(cutree(hc1, i), dist=x)[,"sil_width"]) })
+k=which.max(z)+1
+k #2
 
-z <- sapply(2:(dim(as.matrix(x))[1]-1), function(i) { 
-    mean(silhouette(cutree(hc1, i), dist=x)[,"sil_width"]) })
-plot(2:(dim(as.matrix(x))[1]-1), z)
+c <- clara(mid, 
+           k=k, 
+           samples=100,
+           metric = "euclidean",
+           stand = FALSE, 
+           trace = 2, 
+           medoids.x = TRUE)
+clustdf <- data.frame(mid=mid, 
+                      clust=c$clustering, 
+                      medoid=ifelse(mid %in% c$medoids, "Yes", "No"))
 
-k = which.max(z)+1
-p <- pam(x, diss=TRUE, k=k, cluster.only=TRUE, trace.lev = 0)
-clustdf <- data.frame(mid=predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], clust=cutree(hc1, k=k))
-
-plot(hc1, hang = -1)
+dend <- as.dendrogram(hc1)
+dend %>% set("labels_colors", 
+             value=as.numeric(clustdf$medoid)+1) %>% 
+  set("labels_cex", value=1.5) %>% 
+  plot(main = "Clustered Distances", xlab="Predicted Boundary Regions")
 rect.hclust(hc1, k = k)
 
-prob1intervals <- unique(clustdf$clust)
-  mid2 <- numeric()
-  for(i in prob1intervals){
-    dat <- clustdf[which(clustdf$clust==prob1intervals[i]),]
-    n=dim(dat)[1]
-    mid2[i] <- ceiling((dat$mid[1]+dat$mid[n])/2)
-  }
+predprobdata2$predicted <- ifelse(predprobdata2$basenum %in% clustdf$mid[which(clustdf$medoid=="Yes")], "Yes", "No")
 
-  predprob_df_temp$predBound2 <- ifelse(predprob_df_temp$baseNum %in% mid2, "Yes", "No")
+predicteddata2 <- predprobdata2[which(predprobdata2$predicted=="Yes"),]
 
-ggplot(predprob_df_temp, aes(x=baseNum, y=PredProb)) +
-     geom_line(size=.5)+
-     #geom_smooth(method = "loess", size = 5, color="blue")
-	   geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$PredProb==1)], 
-	              color="red", 
-	              #linetype="dashed", 
+ggplot() + 
+  geom_line(data=predprobdata2, aes(x=basenum, y=prob), 
+            color='black',
             size=.5)+
-     geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$predBound2=="Yes")], 
-	              color="blue", 
-	              #linetype="dashed", 
-	              size=1)+
+  geom_vline(data=calleddata, aes(xintercept=basenum, 
+                                  color="blue"),
+             size=.75,
+             show.legend = TRUE)+
+  geom_vline(data=predicteddata, aes(xintercept=basenum, 
+                                     color="red"),
+             size=.75,
+             show.legend = TRUE)+
+  geom_vline(data=predicteddata2, aes(xintercept=basenum, 
+                                      color="green"),
+             size=.75,
+             show.legend = TRUE)+
   xlab("Base Pair") +
   ylab("Predicted Probability") +
+  scale_color_manual(name = '', 
+                     values =c("blue", "green", "red"),
+                     labels = c("Called Boundary",
+                                "Predicted Boundary",
+                                "Predicted Region"))+
   theme_minimal() +

### 2019-08-23 Scripts/functions_for_R_package/all_functions.R
edits

@@ -15,8 +15,8 @@ library(BSgenome)
 annots_to_granges_func <- function(filepath){
   annots_gr_list <- GRangesList() 
   #if(grepl(paste0(names, collapse = "|"), list.files(filepath)))
-  for(i in 1:length(list.files(filepath))){
-    dat <- read.table(paste0(filepath,"/",list.files(filepath)[i]),
+  for(i in 1:length(list.files(filepath, pattern = "*.bed"))){
+    dat <- read.table(paste0(filepath,"/",list.files(filepath, pattern = "*.bed")[i]),
                       header = FALSE)
     
     annots_gr_list[[i]] <- GRanges(seqnames=dat$V1,
@@ -24,7 +24,7 @@ annots_to_granges_func <- function(filepath){
                                            end=dat$V3))
     mcols(annots_gr_list[[i]])$coverage <- dat[,4]
   }
-  names(annots_gr_list) <- gsub(".bed", "", list.files(filepath))
+  names(annots_gr_list) <- gsub(".bed", "", list.files(filepath, pattern = "*.bed"))
   return(annots_gr_list)
 }
 

### 2019-08-23 Scripts/functions_for_R_package/annots_to_granges_func.r

@@ -3,8 +3,8 @@
 annots_to_granges_func <- function(filepath){
   annots_gr_list <- GRangesList() 
   #if(grepl(paste0(names, collapse = "|"), list.files(filepath)))
-  for(i in 1:length(list.files(filepath))){
-    dat <- read.table(paste0(filepath,"/",list.files(filepath)[i]),
+  for(i in 1:length(list.files(filepath, pattern = "*.bed"))){
+    dat <- read.table(paste0(filepath,"/",list.files(filepath, pattern = "*.bed")[i]),
                       header = FALSE)
     
     annots_gr_list[[i]] <- GRanges(seqnames=dat$V1,
@@ -12,6 +12,6 @@ annots_to_granges_func <- function(filepath){
                                            end=dat$V3))
     mcols(annots_gr_list[[i]])$coverage <- dat[,4]
   }
-  names(annots_gr_list) <- gsub(".bed", "", list.files(filepath))
+  names(annots_gr_list) <- gsub(".bed", "", list.files(filepath, pattern = "*.bed"))
   return(annots_gr_list)
 }

### 2019-08-25 Manuscript/manuscript.Rmd
edits

@@
 
-We analyzed publically available replicate Hi-C data sets from two cell lines including GM12878 and K562 (Supplementary Table 1).
-Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at 4 resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-We implemented a preprocessing step by removing TADs with lengths that exceeded 2 mb [???ref] (Supplementary Figure 1).
-To account for the varying levels of data resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1).
-<!--First, we binned the linear genome according to the data resolution.
-We then flanked the boundaries on either side by the same number of basepairs as the previously constructed genomic bins.--> TAD boundary regions were defined as regions on the linear genome where a genomic bin overlapped with a flanked TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as the regions that did not overlap with a flanked TAD boundary ($Y = 0$).
+We analyzed publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1).
+Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at 5 data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
+After removing TADs that exceeded 2 megabases in length, we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, and 9314, 10881, 6923, 3197, and 831 unique TAD boundaries for the K562 cell line across each of the 5 resolutions respectively (Supplementary Figure 1).
+To account for the variability in boundary location due to varying resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1).
+TAD boundary regions were defined as regions on the linear genome where a genomic bin overlapped with a flanked TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as the regions that did not overlap with a flanked TAD boundary ($Y = 0$).
+A significant number of TAD boundary regions were found to be specific to one of the two cell lines (Supplementary Figure 2).
+Given the plasticity in boundary location, we opted to build cell line specific models for predicting TAD boundary regions.
+The results presented are for the GM12878 cell line, with K562 results presented as supplementary.
 
-![**An illustration of the proposed approach for resolution-specific data construction used for TAD boundary prediction.** Resolution-specific TADs were called and unique boundaries were identified, denoted by the blue dots.
+![**An illustration of the proposed approach for resolution-specific data construction used for TAD boundary prediction.** Unique boundaries are denoted by the blue dots.
 The yellow regions denote the flanked boundary regions according to the Hi-C data resolution (i.e.
@@
 The response vector **Y** was defined as a variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y = 1$) or not ($Y = 0$).](Figures/figure1_model_construction_V7.png)
-
-## TAD BOUNDARY REGIONS EXHIBIT CELL-LINE SPECIFICITY
-
-<!--## TOTAL NUMBER OF TAD BOUNDARY REGIONS DECREASE AS Hi-C DATA RESOLUTION DECREASES-->
-Expectedly, the total number of TAD boundary regions increased with the increased resolution of Hi-C data irrespectively of cell line (Figure 2A).
-At higher resolutions, GM12878 was found to contain more TADs, and thus more TAD boundary regions compared to K562.
-This can largely be attributed to the increased sequencing depth of the GM12878 library.
-However, this difference was found to dissipate as resolution decreased, resulting in much more similar numbers of TAD boundary regions between the two cell lines at the 50 kb and 100 kb resolutions respectively.
-
-We sought to compare the cell-line specificity of TAD boundary regions.
-Between the two cell lines, a significant number of TAD boundary regions were found to be specific to one of the two cell lines (Figure 2B).
-It was found that X%, 45%, 38%, 37%, and 36% of TAD boundary regions were specific to the GM12878 cell line, while X%, 27%, 27%, 29%, and 33% of TAD boundary regions were specific to the K562 cell line across each of the 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions respectively.
-Given the plasticity in boundary location, we opted to build cell line specific models for predicting TAD boundary regions.
 
@@
 (C) Boxplots indicating that the proportion of class imbalance remained severe irrespective of resolution.](Figures/bounds_and_pis_v2.png)
-
-<!--
-**Table 1. Sparse TAD boundaries throughout the linear genome create high imbalance ratios irrespective of resolution.**
-
-| Resolution (Bin Width) | Average Number of Genomic Bins (SD) | Average Number of TAD Boundaries (SD) | Average Imbalance Ratio (SD) |
-|------------------------|-------------------------------------|---------------------------------------|------------------------------|
-| 10 kb                  | 12214.1 (6068.5)                    | 1254.6 (598.8)                        | 8.7 (1.2)                    |  
-| 25 kb                  | 4892.7 (2431.2)                     | 714.0 (358.4)                         | 5.9 (0.5)                    |
-| 50 kb	                 | 2450.9 (1217.6)                     | 364.4 (184.5)                         | 5.8 (0.5)                    |
-| 100 kb                 | 1227.5 (609.8)                      | 165.3 (90.9)                          | 6.8 (1.1)                    |
--->
-
-<!--**Table 2.
-Inter-Resolution ICCs.** For GM12878, two-way intraclass correlation coefficients between resolutions for the following quantities: Number of genomic bins, number of TADs called, number of unique TAD boundaries, and imbalance ratio.
-The ICC was computed across 21 of the autosomal chromosomes.
-P-values indicate the level of significance of the correlation between data resolution and each quantity.[???
-What is ICC?
-!!!editted]
-
-| Quantity                 | Inter-Resolution | 95% CI          | P-Value  |
-|--------------------------|------------------|-----------------|----------|
-| Number of Genomic Bins   | 0.464            | [0.244, 0.690]  | < 0.0001 |
-| Number of TADs Called    | 0.627            | [0.426, 0.802]  | < 0.0001 |
-| Number of TAD Boundaries | 0.611            | [0.407, 0.791]  | < 0.0001 |
-| Imbalanced Ratio         | 0.114            | [-0.058, 0.372] | 0.109    |
--->
 

### 2019-08-25 Scripts/evaluating_preprocessed_tad_summaries.Rmd
edits

@@
   names(domains) <- c("Chromosome","Start","End")
+  domains <- domains[-which(domains$Chromosome==9),]
 
@@
   names(domains) <- c("Chromosome","Start","End")
+  if("9" %in% names(table(domains$Chromosome))){domains <- domains[-which(domains$Chromosome==9),]}
 

### 2019-08-25 Manuscript/manuscript.Rmd
edits

@@
 After removing TADs that exceeded 2 megabases in length, we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, and 9314, 10881, 6923, 3197, and 831 unique TAD boundaries for the K562 cell line across each of the 5 resolutions respectively (Supplementary Figure 1).
-To account for the variability in boundary location due to varying resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1).
+To account for the variability in boundary location due to varying resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1A).
 TAD boundary regions were defined as regions on the linear genome where a genomic bin overlapped with a flanked TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as the regions that did not overlap with a flanked TAD boundary ($Y = 0$).
@@
 
-![**An illustration of the proposed approach for resolution-specific data construction used for TAD boundary prediction.** Unique boundaries are denoted by the blue dots.
+![**Illustrating the resolution-specific data construction and feature engineering used for downstream modelling.** (A) Unique boundaries are denoted by the blue dots.
 The yellow regions denote the flanked boundary regions according to the Hi-C data resolution (i.e.
@@
 The linear genome was subsequently binned into resolution-specific intervals.
-The response vector **Y** was defined as a variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y = 1$) or not ($Y = 0$).](Figures/figure1_model_construction_V7.png)
+The response vector **Y** was defined as a variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y = 1$) or not ($Y = 0$).
+(B) Three types of associations between TAD boundaries and genomic annotations including _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
+The green shapes denote regions defined by a specific functional genomic annotation used for feature engineering.
+](Figures/model_construction_and_predictor_types.png)
 
@@
 
-We then investigated the proportional class imbalance (PI) featured at each resolution and among each cell line.
-The PI was defined as twice the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions.
-The proportional imbalance was found to be invariant to resolution, remaining consistently low for both cell lines, with very little variability between chromosomes (Figure 3C).
-Such low proportions of imbalance gave precedence for the implementation of re-sampling prior to classification.
-
-![**Cell-line specific boundary summaries.** (A) Barplots illustrating that the total number of TAD boundary regions decreases as Hi-C data resolution decreases.
-(B) Venn diagrams showing that TAD boundary regions exhibit cell-line specificity across resolution.
-(C) Boxplots indicating that the proportion of class imbalance remained severe irrespective of resolution.](Figures/bounds_and_pis_v2.png)
+We then investigated the proportional class imbalance (PI) featured at each resolution.
+The PI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions for each chromosome specific sections of the linear genome and has a range from 0 to 0.5.
+The PI was found to be invariant to resolution, remaining consistently low, with an average of 0.06, 0.10, 0.14, 0.12, and 0.06 for the 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions respectively.
+The K562 cell line was found to have comparatively low proportional imbalances (Supplementary Figure 3).
+Such low proportions of imbalance gave precedence for the implementation of re-sampling prior to performing classification.
 
@@
 We constructed three different predictor types for each functional genomic annotation.
-Counts of overlaps (**overlap count**, OC) were defined as the total number of peak regions that overlapped within a given genomic bin (Figure 3A).
+Counts of overlaps (**overlap count**, OC) were defined as the total number of peak regions that overlapped within a given genomic bin (Figure 1B).
 Percents of overlaps (**overlap percent**, OP) were defined as the proportion of a bin overlapped by a peak region (Figure 3B).
@@
 Each predictor type provides a granular way to draw associations between functional genomic annotations and the spatial structure of the genome.
-
-![**Three types of associations between TAD boundaries and genomic annotations.** (A) _Overlap Counts_ (OC) consider the total number of genomic features that overlapped with each genomic bin.
-(B) _Overlap Percent_ (OP) was calculated by dividing the sum of all feature widths within each specific bin by the total bin width.
-(C) _Distance_ ($log_{2}$ transformed) was calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest region defining a genomic annotation.
-](Figures/figure2_predictor_types.png)
 

### 2019-08-25 Manuscript/manuscript.Rmd
edits

@@
 Given the plasticity in boundary location, we opted to build cell line specific models for predicting TAD boundary regions.
-The results presented are for the GM12878 cell line, with K562 results presented as supplementary.
+The results presented are for the GM12878 cell line, with K562 results presented in the supplementary materials.
 
-![**Illustrating the resolution-specific data construction and feature engineering used for downstream modelling.** (A) Unique boundaries are denoted by the blue dots.
+![**Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** (A) Unique boundaries are denoted by the blue dots.
 The yellow regions denote the flanked boundary regions according to the Hi-C data resolution (i.e.
@@
 The linear genome was subsequently binned into resolution-specific intervals.
-The response vector **Y** was defined as a variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y = 1$) or not ($Y = 0$).
-(B) Three types of associations between TAD boundaries and genomic annotations including _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
+The response vector **Y** was defined as a genomic bin that either overlapped with a flanked TAD boundary ($Y = 1$) or did not ($Y = 0$).
+(B) Three types of associations between TAD boundaries and genomic annotations were used to build the feature space including _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
 The green shapes denote regions defined by a specific functional genomic annotation used for feature engineering.
@@
 The K562 cell line was found to have comparatively low proportional imbalances (Supplementary Figure 3).
-Such low proportions of imbalance gave precedence for the implementation of re-sampling prior to performing classification.
+Such low PI gave precedence for the implementation of re-sampling prior to performing classification.
 
@@
 A total of 78 cell type specific functional genomic annotations derived from ChIP-Seq experiments (See Methods) for the GM12878 and K562 cell line were used to build the feature space of downstream predictive models (Supplementary Tables 2-3).
-We constructed three different predictor types for each functional genomic annotation.
-Counts of overlaps (**overlap count**, OC) were defined as the total number of peak regions that overlapped within a given genomic bin (Figure 1B).
-Percents of overlaps (**overlap percent**, OP) were defined as the proportion of a bin overlapped by a peak region (Figure 3B).
-**Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations (Figure 3C).
-A log2-transformation of distance was used to account for the skewness present in the distributions of distances <!--(Supplementary Figures 1-2)-->.
-Each predictor type provides a granular way to draw associations between functional genomic annotations and the spatial structure of the genome.
+The annotations could be broken down into 3 sets including histone modifications (HM), chromatin state segmentations (ChromHMM), and transcription factor binding sites (TFBS).
+We constructed three different predictor types for each functional genomic annotation (Figure 1B).
+Counts of overlaps (**overlap count**, OC) were defined as the total number of peak regions that overlapped within a given genomic bin.
+Percents of overlaps (**overlap percent**, OP) were defined as the proportion of a bin overlapped by a peak region.
+**Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations.
+A log2-transformation of distance was used to account for the skewness present in the distributions of distances (Supplementary Figures 4-5).
 
@@
 
-In order to identify the optimal combination of data resolution, predictor type, and re-sampling technique necessary for TAD boundary prediction, we created an ensemble framework to systematically compare performances of different model inputs (Figure 4).
+In order to identify the combination of data resolution, predictor type, and re-sampling technique necessary for optimal cell line specific TAD boundary prediction, we created an ensemble framework to systematically compare performances of different model inputs (Figure 2).
 Each system in the framework was assumed to be composed of a random forest classifier constructed from a particular cell line (*L = {GM12878, K562}*).
@@
 To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling (*B = {None, RUS, ROS, SMOTE}*).
-Each combination of the above cell line specific parameters was implemented on chromosome specific sections of the linear genome (omitting chromosome 9).
-Letting $|X|$ denote the cardinality [???
-TBD] of each set, we evaluated *|L|* $\times$ *|R|* $\times$ *|P|* $\times$ *|B|* different ensemble systems, totaling 2520 (*2* $\times$ *5* $\times$ *3* $\times$ *4* $\times$ *21*) separate models.
-For each combination of inputs, we performed 10-fold cross-validation to tune for the number of features to consider at each node of the random forest classifier.
-Each optimally tuned model was then validated on the same separate cell line specific testing set for unbiased comparisons.
-Performances were evaluated using MCCs and aggregated across each chromosome by averaging.
-<!--We report our main results for the GM12878 cell line and have included results from the K562 cell line in the supplementary materials.-->
+Once the model inputs were established a random forest classifier was trained on chromosome specific sections of the genome using 10-fold cross validation.
+The model was then validated on the same separate chromosome specific test set for unbiased comparisons and evaluated using Matthews Correlation Coefficient (MCC).
+Letting $|X|$ denote the cardinality of each set, we evaluated *|L|* $\times$ *|R|* $\times$ *|P|* $\times$ *|B|* different ensemble systems, totaling 2520 (*2* $\times$ *5* $\times$ *3* $\times$ *4* $\times$ *21*) separate models.
+Additional performance metrics are reported in the supplementary materials.
 

### 2019-08-25 Manuscript/manuscript.Rmd
edits

@@
 
-## SMOTE RE-SAMPLING COUPLED WITH A DISTANCE-TYPE FEATURE SPACE PROVIDED OPTIMAL CELL LINE SPECIFIC MODEL PERFORMANCE
+## RANDOM FOREST CLASSIFIERS BUILT USING A DISTANCE-TYPE FEATURE SPACE COMBINED WITH SMOTE RE-SAMPLING PROVIDED OPTIMAL MODEL PERFORMANCE
 
@@
 
-We first evaluated the least granular cell line specific random forest classifiers [???
-Unclear; !!!discuss in meeting], those were ones implemented using OC predictor types, without data re-sampling.
-We found that these models exhibited poor MCCs across all resolutions (Figure 5 A-B (red)).
-We then assessed models built on OP predictor types, while still not performing any data resampling.
-Performances were similar to that of OC types, with no visible improvement across resolution, for either cell line (Figure 5 C-D (red)).
-This indicated that the added complexity of using overlap percents from the functional genomic annotations did not affect predictive performance.
-However, when cell line specific classifiers were implemented using distance-type predictors and no re-sampling, we found that there was a significant improvement in MCC compared to the other two predictor types (Figure 5 E-F (red)).
-We then further explored the impact of data re-sampling on model performance, across cell line and resolution.
-For cell line specific random forest classifiers built on balanced data, we found that SMOTE re-sampling provided the optimal MCC, consistently outperforming models built on ROS or RUS respectively, across both predictor type and resolution (Figure 5).
-Specifically, the most improvement was seen when combining SMOTE re-sampling with distance-type predictors for both the GM12878 and K562 cell lines.
-
-## MODEL PERFORMANCE PEAKED AT 10 KB AND DECREASED AS Hi-C DATA RESOLUTION DECREASED
-
-Interestingly, we found that performance peaked at 10 kb resolution and then degraded as data resolution decreased (Figure 5).
-The reason for the improved performance between 5 kb and 10 kb data resolutions can be attributed to the added sparcity in the interaction frequency matrices at finer resolutions.
+When evaluating model performances, we found that regardless of resampling technique, random forest classifiers built using a distance-type feature space yielded consistently higher MCCs when compared to the other two predictor types (Figure 3).
+This indicated that models are better able to discriminate between TAD and non-TAD boundary regions when provided with spatially related associations.
+Delving further, we found that when combined with SMOTE re-sampling, random forest classifiers built using distance-type predictors out performed other re-sampling techniques across resolutions, suggesting that a combination of both random over- and under-sampling can improve TAD boundary prediction.
+Interestingly, given these parameters, we found that performances peaked at 10 kb resolution and then degraded as data resolution decreased.
+This reason for the improved performance between 5 kb and 10 kb data resolutions can be attributed to the added sparcity in the interaction frequency matrices at finer resolutions.
 This sparcity corresponds to inaccurate TAD calling which leads to worse model performance.
-The difference in performance between 5 kb and 10 kb resolutions for K562 was found to be slightly steaper, indicating that this issue of sparcity was more severe at finer resolutions for K562.
 Additionally, performances tended to be much more variable between chromosomes at lower resolutions.
 Moreover, this decreasing trend in performance was much more evident under the optimal combination of data level characteristics (SMOTE resampling with distance type predictors).
-These results imply that there is an ideal resolution in TAD boundary prediction, and that that an optimally performing cell line specific random forest classifier <!--, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries,--> is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
+<!--These results imply that there is an ideal resolution in TAD boundary prediction, and that that an optimally performing cell line specific random forest classifier, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.--> Models implemented on the K562 cell line were found to yield the same optimal data level characteristics (Supplementary Figure 6).
 
-![**SMOTE re-sampling coupled with distance-type predictors yielded optimal MCCs across resolution for cell line specific models.** Performances of random forest classification models built on each of the 3 predictor types including (A-B) OC, (C-D) OP, and (E-F) Distance, and across both the GM12878 and K562 cell lines.
-Within each cell line, predictor type, and resolution, chromosome-specific training data was re-sampled using different techniques including no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and *Synthetic Minority Over Sampling TEchnique* (SMOTE; purple).
-Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/model_performances_v3.png)
+![**Models built using distance-type functional genomic annotations combined with SMOTE re-sampling yielded optimal MCCs across resolution.** Barplots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
+Within each re-sampling technique (A-D), performances are compared for each type of feature space: OC (red), OP (green), and Distance (blue), across resolutions.
+Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/model_performances_v3_bars.png)
 

### 2019-08-25 Scripts/evaluating_model_performances_rf.Rmd
added other types of plotting

@@
 ```
+
+# Boxplots
+
+## GM12878
+
+```{r}
+ggplot(all_rfperfs[all_rfperfs$CL=="GM12878",], aes(x=Resolution, y=V1, color=Predictor, fill=Predictor)) +
+     #geom_line(size=2, position=position_dodge(0.5))+
+     #geom_point(size=5, position=position_dodge(0.5))+
+     #geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+     #             position=position_dodge(0.5)) +
+     #stat_boxplot(geom ='errorbar', width = 0.2) + 
+     geom_boxplot() +
+     facet_grid( ~ Resampling)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("Resolution") + ylab("MCC") + ylim(-.1,.5) +
+     scale_fill_discrete(name="Predictor Type")+
+     guides(color=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     strip.text.x = element_text(size = 15),
+     strip.text.y = element_text(size = 15),
+     panel.spacing = unit(2, "lines"),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20),
+     legend.position="bottom")
+
+```
+
+## K562
+
+```{r}
+ggplot(all_rfperfs[all_rfperfs$CL=="K562",], aes(x=Resolution, y=V1, color=Predictor, fill=Predictor)) +
+     #geom_line(size=2, position=position_dodge(0.5))+
+     #geom_point(size=5, position=position_dodge(0.5))+
+     #geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
+     #             position=position_dodge(0.5)) +
+     #stat_boxplot(geom ='errorbar', width = 0.2) + 
+     geom_boxplot() +
+     facet_grid( ~ Resampling)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("Resolution") + ylab("MCC") + ylim(-.1,.5) +
+     scale_fill_discrete(name="Predictor Type")+
+     guides(color=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     strip.text.x = element_text(size = 15),
+     strip.text.y = element_text(size = 15),
+     panel.spacing = unit(2, "lines"),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20),
+     legend.position="bottom")
+
+```
+
+# Barplots
+
+## GM12878
+
+```{r}
+ggplot(all_rfperfs_mcc[all_rfperfs_mcc$CL=="GM12878",], aes(x=Resolution, y=MCC, color=Predictor, fill=Predictor, group=Predictor)) +
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
+                 position=position_dodge(.9), alpha=0.75) +
+     geom_bar(stat="identity", position = position_dodge()) +
+     facet_grid(. ~ Resampling)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("Resolution") + ylab("MCC") + ylim(-.1,.5) +
+     scale_fill_discrete(name="Predictor Type")+
+     guides(color=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     strip.text.x = element_text(size = 15),
+     strip.text.y = element_text(size = 15),
+     panel.spacing = unit(2, "lines"),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20),
+     legend.position="bottom")
+
+```
+
+## K562
+
+```{r}
+ggplot(all_rfperfs_mcc[all_rfperfs_mcc$CL=="K562",], aes(x=Resolution, y=MCC, color=Predictor, fill=Predictor, group=Predictor)) +
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
+                 position=position_dodge(.9), alpha=0.75) +
+     geom_bar(stat="identity", position = position_dodge()) +
+     facet_grid(. ~ Resampling)+
+     theme_minimal() +
+     theme_bw()+
+     xlab("Resolution") + ylab("MCC") + #ylim(-.1,.5) +
+     scale_fill_discrete(name="Predictor Type")+
+     guides(color=FALSE)+
+     theme(axis.text.x = element_text(size=15,
+                                      angle = 45, 
+                                      #margin = ggplot2::margin(t = 35),
+                                      hjust = 1
+     ),
+     axis.text.y = element_text(size = 15),
+     axis.title.x = element_text(size = 20),
+     axis.title.y = element_text(size = 20),
+     strip.text.x = element_text(size = 15),
+     strip.text.y = element_text(size = 15),
+     panel.spacing = unit(2, "lines"),
+     legend.text=element_text(size=15),
+     legend.title=element_text(size=20),
+     plot.title = element_text(size=20),
+     legend.position="bottom")
+```

### 2019-08-25 Manuscript/manuscript.Rmd
edits

@@
 Moreover, this decreasing trend in performance was much more evident under the optimal combination of data level characteristics (SMOTE resampling with distance type predictors).
-<!--These results imply that there is an ideal resolution in TAD boundary prediction, and that that an optimally performing cell line specific random forest classifier, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.--> Models implemented on the K562 cell line were found to yield the same optimal data level characteristics (Supplementary Figure 6).
+These results imply that there is an ideal resolution in TAD boundary prediction, and that that an optimally performing cell line specific random forest classifier, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
+Models implemented on the K562 cell line were found to yield the same optimal data level characteristics (Supplementary Figure 6).
 
@@
 
-After determining the optimal set of data level characteristics, we then aimed to compare the performances of annotation-specifc models, within each cell line and across resolution.
-In doing so, we inspected the proportion of predictive importance that was explained by each of the 3 groups of annotations (chromatin states, histone modifications, and transcription factor binding sites).
-We found that for cell line specific random forest models implemented on distance-type predictors, using SMOTE re-sampling, the majority of the proportional predictive importance was obtained by the functional genomic annotations classified as transcription factor binding sites (TFBS) (Figure 6 A).
+We then aimed to compare the performances of annotation-specifc models.
+In doing so, we inspected the proportion of predictive importance that was explained by each of the 3 groups of annotations (HM, ChromHMM, and TFBS).
+For optimal random forest classifiers, we found that the majority of the proportional predictive importance was obtained by transcription factor binding sites (Supplementary Figure 7).
 This was consistent across resolutions, suggesting that TFBS were the primary drivers of TAD boundary formation in both the GM12878 and K562 cell lines.
@@
 We further assessed the predictive capabilities of the specific sets of annotations by comparing the performances of annotation-specific random forest models implemented on the optimal set of characteristics.
-We found that cell line specific models built simply on TFBS outperformed other cell line and annotation-specific models at all resolutions (Figure 6 B).
-Additionally, when compared to models built on all 3 sets of functional genomic annotations, the TFBS-specific models performed similarly at the 10 kb and 25 kb resolutions.
-Interestingly though, at the 50 kb and 100 kb resolutions, the TFBS-specific models out performed models built on the combined sets of annotations for both cell lines.
-This indicated that, at lower resolutions, the inclusion of other types of annotations contributed to additional noise rather than signal.
+We found that models built simply on TFBS outperformed other annotation-specific models at all resolutions (Figure 4A; Supplementary Figure 8A).
+Additionally, when compared to models built on all 3 sets of functional genomic annotations, the TFBS-specific models performed similarly at the 5 kb and 10 kb resolutions.
+Interestingly though, at the 25 kb, 50 kb, and 100 kb resolutions, the TFBS-specific models out performed models built on the combined sets of annotations.
+This indicated that, at lower resolutions, the inclusion of other types of annotations contributed to additional noise rather than signal in TAD boundary prediction.
+
+##PREDICTIVE IMPORTANCES CONFIRMED BIOLOGICAL FUNCTIONALITY OF KNOWN ENRICHED TRANSCRIPTION FACTOR BINDING SITES AT TAD BOUNDARIES
+
+Given that many TFBS are known to colocalize together on the linear genome and are therefore highly correlated, we sought to avoid the incidence of overfitting our optimally built classifier by performing recursive feature elimination (Supplementary Figure 9) to establish the necessary number of TFBS to include.
+We found that our cell line specific model was able to obtain near optimal performance using only ~8 TFBS (Figure 4B; Supplementary Figure 8B).
 
 <!--
-![**The proportional importance of optimally built cell line specific models was outweighed by transcription factor binding sites across resolutions.** Stacked barplots illustrate the proportion of total predictive importance in cell line specific random forest classifiers for (A) GM12878 and (B) K562 respectively.
-Model inputs included the optimal data level characteristics determined by the ensemble framework (SMOTE re-sampling; with distance-type predictors).
-Predictive importance was averaged for models built on chromosome specific regions of the linear genome.
-Proportional importance was then calculated according to the annotation group of the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).](Figures/proportion_of_importances_v2.png)
--->
-
-<!--
-![**Optimally built TFBS-specific models outperformed other annotation-specific models across resolution for GM12878** Performances were compared for random forest models built using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
-Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types.
-The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.](Figures/comparing_sets_of_annotations_v2.png)
--->
-
 ## PREDICTIVE IMPORTANCES CONFIRMED BIOLOGICAL FUNCTIONALITY OF KNOWN TRANSCRIPTION FACTOR BINDING SITES
@@
 
-<!--
-![**Top 20 most predictive transcription factor binding sites sorted by 10 kb for GM12878.** A heatmap illustrating the importance of the key cell line specific transcription factors for optimally built random forest models across resolution.
-Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100.
-Transcription factors with higher values of predictive importance are denoted in dark red.](Figures/figure7_variable_importance_heatmaps_tfbs_gm12878.png)
--->
-
 ![**Assessing optimally built cell line specific random forest classifiers for predicting TAD boundary formation.** (A) Comparing the proportion of total predictive importance carried by each group of functional genomic annotation across resolution.
@@
 
-<!--
-## INFLUENTIAL TFBS TENDED TO BE CLOSER TO BINS THAT OVERLAPPED WITH FLANKED TAD BOUNDARIES THAN THOSE THAT DID NOT
-
-We then investigated the spatial patterns of the most predictive TFBS around TAD boudaries by characterizing the distance profiles between the classes of genomic bins.
-For GM12878, at 10 kb resolution, we found that SMC3, CTCF, RAD21, ZNF143, and YY1sc281 were all statistically significantly closer to bins that overlapped with flanked TAD boudaries than those that did not (Figure 8).
-[???
-not there] Although still statistically significantly different, the distance profiles between genomic class were found to be much more similar at lower resolutions (Supplementary Figure 9).
-For the K562 cell line, we reported the distance profiles of the same transcription factor binding sites, excluding the YY1sc281, due to its unavailability in the UCSC Genome Browser.
-These cell line specific distance profiles were again found to be significantly different between genomic class, at all resolutions (Supplementary Figure 10).
-
-![**Figure 8.
-Top predictive transcription factor binding sites were significantly closer to bins that overlapped with 10 kb flanked TAD boundaries on GM12878** Boxplots illustrating the distribution of distances (on $log_{2}$ scale) around 10 kb regions on the linear genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential cell line specific TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
-P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].](Figures/figure8_distance_boxplots_key_tfbs_gm12878_10kb.png)
 -->

### 2019-08-25 Manuscript/manuscript.Rmd
edits

@@
 We found that our cell line specific model was able to obtain near optimal performance using only ~8 TFBS (Figure 4B; Supplementary Figure 8B).
+However, given that we are modeling on chromosome specific sections of the genome, these 8 annotations are not the same for all chromosomes.
+To determine the most common TFBS, we clustered the predictive importances across chromosomes (Figure 4C; Supplementary Figure 8C).
+We found that the following transcription factors were most important in predicting TAD boundary regions: SMC3, ZNF143, CTCF, and RAD21.
+These are known architectural proteins responsible for the 3D structure of the human genome.
+Namely, the SMC3, CTCF, and RAD21 binding sites are known factors associated with the cohesin protein complex, which is hypothesized to be what creates loops in the DNA  [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+Likewise, ZNF143 is a known structural regulators of enhancer-promoter interactions that also contribute to looping of the linear genome [@weintraub2017yy1; @gonzalez2017znf143].
 
-<!--
-## PREDICTIVE IMPORTANCES CONFIRMED BIOLOGICAL FUNCTIONALITY OF KNOWN TRANSCRIPTION FACTOR BINDING SITES
-
-We then sought to determine which of the transcription factor binding sites were most influential in predicting TAD boundaries.
-We found that the cell line specific binding sites associated with SMC3, CTCF, RAD21, and ZNF143 were given consistently high predictive importance, across all resolutions (Figure 6 C).
-The SMC3, CTCF, and RAD21 binding sites are known factors associated with the cohesin protein complex, which is hypothesized to be what creates loops in the DNA  [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
-Likewise, ZNF143 is a known structural regulators of enhancer-promoter interactions that also contribute to looping of the linear genome [@weintraub2017yy1; @gonzalez2017znf143].
-With the identification of these factors known to be enriched at TAD boundaries, we are able to confirm the validity of our model building process.
-Additionally, we were also able to identify some lesser known cell line specific transcription factors as predictive of TAD boundaries including the MYC-associated zing-finger protein (MAZ), jun-D proto-oncogene (JUND), and ELF1.
-These transcription factor binding sites tended to be given higher predictive importance at lower resolutions.
-[???
-Where do you show it?] In fact, at lower resolutions, the predictive importance was found to be much more evenly dispersed across the top transcription factor binding sites, than for higher resolutions.
-This is again suggestive of the fact that the spatial relationship between functional annotations, specifically transcription factor binding sites, and TAD boundaries changes at different Hi-C data resolutions.
-
-![**Assessing optimally built cell line specific random forest classifiers for predicting TAD boundary formation.** (A) Comparing the proportion of total predictive importance carried by each group of functional genomic annotation across resolution.
-Predictive importance was averaged for models built on chromosome specific regions of the linear genome.
-Proportional importance was then calculated according to the annotation group of the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).
-(B) Comparing models using specific groups of functional genomic annotation as the feature space in addition to a model with a feature space containing all 3 types combined (combined; purple).
-Error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosomal section of the linear genome.
-(C) Heatmaps illustrating the importance of the top 20 cell line specific transcription factors across resolution.
-Importances were sorted according to the row-wise average across resolution and rescaled to values between 0 and 100.
-Transcription factors with higher values of predictive importance are denoted in dark red and dark blue for the GM12878 and K562 cell line respectively.](Figures/prop_imps_a_comparing_annots_b_var_imps_c_v2.png)
-
--->
+![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) (B) (C)](Figures/annot_specific_rfe_varimps_heatmap.png)
 

### 2019-08-26 Manuscript/manuscript.Rmd
edits

@@
 
-![**Models built using distance-type functional genomic annotations combined with SMOTE re-sampling yielded optimal MCCs across resolution.** Barplots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
+![**Models built using distance-type predictors combined with SMOTE re-sampling yielded optimal MCCs across resolution.** Barplots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
 Within each re-sampling technique (A-D), performances are compared for each type of feature space: OC (red), OP (green), and Distance (blue), across resolutions.
@@
 
-![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) (B) (C)](Figures/annot_specific_rfe_varimps_heatmap.png)
+![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) Barplots comparing performances of models using specific groups of functional genomic annotation as the feature space including histone modifications (HM; red), chromatin states (ChromHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all 3 groups (Combined; purple).
+Error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosomal section of the linear genome.
+(B) Recursive feature elimimation analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
+Error bars represent 1 standard deviation away from the mean cross-validated MCC.
+(C) Clustered heatmap of variable importances for the union of the top 8 most predictive TFBS across chromosomes.](Figures/annot_specific_rfe_varimps_heatmap.png)
 
-## Top TFBS were more enriched at predicted TAD boundaries at bp resolution than those provided by the TAD caller kb resolution
+## LEVERAGING ChIP-seq PEAK REGIONS OF TOP PREDICTIVE TFBS PROVIDE MORE PRECISE LOCATION OF TAD BOUNDARIES
 

### 2019-08-26 Manuscript/manuscript.Rmd
edits

@@
 
-We then shifted our focus toward developing a method to more accurately identify the location of TAD boundaries throughout the linear genome.
-Typical TAD callers are restricted to kilobase resolutions, which increase the variability in the actual location of a boundary.
-Instead, we aimed to predict the location of TAD boundaries at basepair resolution using optimally built cell line specific random forest classifiers.
-Each model was restricted to only include the most influential cell line specific TFBS, namely CTCF, RAD21, SMC3a, adn ZNF143.
-We then validated our models on cell line and chromosome specific regions of the genome, at base pair resolution.
-Predicted TAD boundary regions (PTBR) were identified as the collection of base pairs where the predicted probability vector was equal to 1, which denoted 100% accuracy in correctly identifying a basepair as a potential TAD boundary (Figure 7A).
-To allow for minor fluctuations in probability, any base pair given probability of 1 that was within a 10 bp window from another base pair also given probability of 1 were combined into one PTBR.
-PTBR were then compared to the called TAD boundary regions (CTBR), which here were defined by a 10 kb resolution flanking (See Methods).
-There were a total of 4663 identified PTBR compared to 237 CTBR.
-We found that approximately 59% (139 out of 237) of CTBR were overlapped by PTBR, indicating there are fluctuations in probabilities within the 20 kb regions defining CTBR (Figure 7B).
-We then compared distances between PTBRs and annotations versus CRBRs and annotations.
-We found that boundary regions predicted by our model at bp resolution experienced short distance profiles to known architectural proteins than did boundary regions called by Arrowhead.
+After obtaining our optimally built random forest classifier, we aimed to leverage the ChIP-seq peak regions defined by the SMC3, ZNF143, CTCF, and RAD21 tanscription factors for precised TAD bounday prediction at base pair resolution.
+We found that when we validated our model against chromosome specific base pairs, we were able to identify clusters of regions where the model predicted the base pair to be a TAD boundary with probability equal to 1.
+By clustering the regions and performing medoid partitioning (See Methods), we were able to identify a comparative number of TAD boundaries as the ARROWHEAD TAD caller.
+However, only 24% and 29% of predicted and called (and 10 kb flanked) TAD boundaries overlapped for the GM12878 and K562 cell line respectively, suggesting differing locations in TAD boundaries throughout the linear genome (Supplementary Figure 10).
+To compare between predicted and called TAD boundaries we evaluated the signal strength of ChIP-seq peak regions around a 10 kb flank of each.
+We found that the peak signal strength for the SMC3, ZNF143, CTCF, and RAD21 TFBS were much closer, on average, to our predicted TAD boudaries the the called TAD boundaries obtained using the ARROWHEAD pipeline for 10 kb resolution Hi-C data (Figure 5; Supplementary Figure ).
+ChIP-seq assays offer much higher resolutions (often in the tens of bases) compared to Hi-C sequenced data, which can be in the hundreds of kilobases.
+This disparity in resolution can affect a TAD caller's ability to precisely locate TADs.
+Moreover, by building a model using annotations known to be enriched at TAD boundaries we were able to bridge this gap in resolution and more precisely locate TAD boundaries that corresponded to the highest concentration in signal strength for top ranked TFBS.
 
-![**Comparing TAD boundaries regions predicted at bp resolution with those called at 10 kb resolution.** (A) A subset of the probabilitity vector for predicting TAD boundaries for chr22:17380000-chr22:18650000.
-The red dashed lines represent predicted TAD boundary regions, while the blue dashed lines represent called TAD boundaries identified by Arrowead at 10 kb.
-A called TAD boundary region is one flanked by 10 kb (B) Venn diagram illustrating the number of overlapped regions between predicted (red) and called (blue) TAD boundary regions.
-(C) Boxplots illustrating the distance profiles between each class of boundary regions (predicted-red; called-blue) and architechtural proteins known to be enriched at TAD boundaries.](Figures/pred_at_bp_res_plots.png)
+![**Predicted TAD boundaries were centered closer to peak signal regions defined by known architectural transcription factors when compared to called TAD boundaries.** Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by (A) SMC3, (B) ZNF143, (C) CTCF, and (D) RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.](Figures/enrichment_heatmaps_gm12878.png)
 

### 2019-08-26 Manuscript/manuscript.Rmd
edits

@@
 
-After obtaining our optimally built random forest classifier, we aimed to leverage the ChIP-seq peak regions defined by the SMC3, ZNF143, CTCF, and RAD21 tanscription factors for precised TAD bounday prediction at base pair resolution.
+After obtaining our optimally built random forest classifier, we aimed to leverage the ChIP-seq peak regions defined by the SMC3, ZNF143, CTCF, and RAD21 tanscription factors for precise TAD bounday prediction at base pair resolution.
 We found that when we validated our model against chromosome specific base pairs, we were able to identify clusters of regions where the model predicted the base pair to be a TAD boundary with probability equal to 1.
-By clustering the regions and performing medoid partitioning (See Methods), we were able to identify a comparative number of TAD boundaries as the ARROWHEAD TAD caller.
+By clustering the regions and performing medoid partitioning (See Methods), we were able to predict a comparative number of TAD boundaries (base pairs) as called by the ARROWHEAD TAD caller.
 However, only 24% and 29% of predicted and called (and 10 kb flanked) TAD boundaries overlapped for the GM12878 and K562 cell line respectively, suggesting differing locations in TAD boundaries throughout the linear genome (Supplementary Figure 10).

### 2019-08-26 Manuscript/manuscript.Rmd
Results edits

--- 2019-08-26 Manuscript/manuscript.Rmd
@@
 
-## DEVELOPING A RESOLUTION-SPECIFIC APPROACH FOR DATA CONSTRUCTION
+## A RESOLUTION-SPECIFIC APPROACH FOR PREDICTING TAD BOUNDARIES
 
 We analyzed publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1).
-Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at 5 data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-After removing TADs that exceeded 2 megabases in length, we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, and 9314, 10881, 6923, 3197, and 831 unique TAD boundaries for the K562 cell line across each of the 5 resolutions respectively (Supplementary Figure 1).
+Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
+After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [???
+Add ref, see one in SpectralTAD]), we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, and 9314, 10881, 6923, 3197, and 831 unique TAD boundaries for the K562 cell line across each of the five resolutions respectively (Supplementary Figure 1).
 To account for the variability in boundary location due to varying resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1A).
 TAD boundary regions were defined as regions on the linear genome where a genomic bin overlapped with a flanked TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as the regions that did not overlap with a flanked TAD boundary ($Y = 0$).
-A significant number of TAD boundary regions were found to be specific to one of the two cell lines (Supplementary Figure 2).
-Given the plasticity in boundary location, we opted to build cell line specific models for predicting TAD boundary regions.
-The results presented are for the GM12878 cell line, with K562 results presented in the supplementary materials.
+A significant number [???
+Need to put exactly, e.g., $18.34 \pm 5.06 \%$] of TAD boundary regions were found to be specific to one of the two cell lines (Supplementary Figure 2).
+Given the cell type specificity of TAD boundaries, we opted to build cell line specific models for predicting TAD boundary regions.
+The results presented are for the GM12878 cell line, with K562 results presented in the Supplementary material.
+In summary, we developed a framework enabling resolution-specific prediction of TAD boundaries, with resolution-specific bins defining the response variable.
 
 ![**Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** (A) Unique boundaries are denoted by the blue dots.
-The yellow regions denote the flanked boundary regions according to the Hi-C data resolution (i.e.
-100 kb resolution corresponded to a 100 kb flank for a total boundary region of 200 kb).
+The yellow regions denote the flanked boundary regions according to the Hi-C data resolution (i.e., 100 kb resolution corresponded to a 100 kb flank for a total boundary region of 200 kb).
 The linear genome was subsequently binned into resolution-specific intervals.
 The response vector **Y** was defined as a genomic bin that either overlapped with a flanked TAD boundary ($Y = 1$) or did not ($Y = 0$).
-(B) Three types of associations between TAD boundaries and genomic annotations were used to build the feature space including _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
-The green shapes denote regions defined by a specific functional genomic annotation used for feature engineering.
+(B) Three types of associations between bins and genomic annotations (green shapes) used to build the feature space include _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
 ](Figures/model_construction_and_predictor_types.png)
 
-## PROPORTIONAL IMBALANCE REMAINED SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION
+## THREE TYPES OF PREDICTORS DEFINE THE ASSOCIATIONS BETWEEN TAD BOUNDARY REGIONS AND GENOMIC ANNOTATIONS
 
-We then investigated the proportional class imbalance (PI) featured at each resolution.
-The PI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions for each chromosome specific sections of the linear genome and has a range from 0 to 0.5.
-The PI was found to be invariant to resolution, remaining consistently low, with an average of 0.06, 0.10, 0.14, 0.12, and 0.06 for the 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions respectively.
-The K562 cell line was found to have comparatively low proportional imbalances (Supplementary Figure 3).
-Such low PI gave precedence for the implementation of re-sampling prior to performing classification.
-
-## DEVELOPING THREE TYPES OF PREDICTORS DESCRIBING THE ASSOCIATIONS BETWEEN TAD BOUNDARY REGIONS AND EPIGENOMIC FEATURES
-
-A total of 78 cell type specific functional genomic annotations derived from ChIP-Seq experiments (See Methods) for the GM12878 and K562 cell line were used to build the feature space of downstream predictive models (Supplementary Tables 2-3).
-The annotations could be broken down into 3 sets including histone modifications (HM), chromatin state segmentations (ChromHMM), and transcription factor binding sites (TFBS).
+A total of 78 cell type specific functional genomic annotations for the GM12878 and K562 cell line were used to build the feature space of downstream predictive models (Supplementary Tables 2-3).
+The annotations could be broken down into three sets including histone modifications (HM), chromatin state segmentations (ChromHMM), and transcription factor binding sites (TFBS).
 We constructed three different predictor types for each functional genomic annotation (Figure 1B).
-Counts of overlaps (**overlap count**, OC) were defined as the total number of peak regions that overlapped within a given genomic bin.
-Percents of overlaps (**overlap percent**, OP) were defined as the proportion of a bin overlapped by a peak region.
+Counts of overlaps (**overlap count**, OC) were defined as the total number of genomic annotation regions that overlapped within a given genomic bin.
+Percents of overlaps (**overlap percent**, OP) were defined as the proportion of a bin overlapped by an annotation region.
 **Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations.
 A log2-transformation of distance was used to account for the skewness present in the distributions of distances (Supplementary Figures 4-5).
+These feature engineering steps were performed to improve TAD boundary predictions by accounting for direct (OC), proportional (OP), and indirect (distance) relationships between TAD boundaries and genomic annotations.
 
-## ENSEMBLE FRAMEWORK & COMPARISONS
+## TAD VS. NON-TAD BOUNDARY CLASS IMBALANCE IS SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION
 
-In order to identify the combination of data resolution, predictor type, and re-sampling technique necessary for optimal cell line specific TAD boundary prediction, we created an ensemble framework to systematically compare performances of different model inputs (Figure 2).
-Each system in the framework was assumed to be composed of a random forest classifier constructed from a particular cell line (*L = {GM12878, K562}*).
-Within each cell line we evaluated 5 data resolutions (*R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*).
-We then considered 3 separate predictor types as the feature space (*P = {OC, OP, Distance}*).
-To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling (*B = {None, RUS, ROS, SMOTE}*).
-Once the model inputs were established a random forest classifier was trained on chromosome specific sections of the genome using 10-fold cross validation.
-The model was then validated on the same separate chromosome specific test set for unbiased comparisons and evaluated using Matthews Correlation Coefficient (MCC).
-Letting $|X|$ denote the cardinality of each set, we evaluated *|L|* $\times$ *|R|* $\times$ *|P|* $\times$ *|B|* different ensemble systems, totaling 2520 (*2* $\times$ *5* $\times$ *3* $\times$ *4* $\times$ *21*) separate models.
-Additional performance metrics are reported in the supplementary materials.
+Given that the number of bins annotated as TAD boundaries (TAD boundary regions) is much smaller than the number of non-TAD boundary bins, we investigated the class imbalance (CI) [???
+I changed PI to CI - change in supplementary accordingly] featured at each resolution.
+The CI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions.
+The CI was found to be invariant to resolution, remaining consistently low, with an average of 0.06, 0.10, 0.14, 0.12, and 0.06 [???
+Add exact numbers, like $18.34 \pm 5.06 \%$] for the Gm12878 data at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions, respectively, with similar results observed for the K562 cell line  (Supplementary Figure 3).
+The presence of class imbalance justifies the the need for using resampling techniques before predictive modeling.
 
-![**Ensemble Framework.** A diagram of the ensemble framework detailing the combination of inputs used in the model building pipeline.
-Cell line specific TAD boundary data was extracted from a Hi-C produced contact matrix of a given resolution.
-A variety of functional genomic annotations were used to establish the feature space.
-Each subsequent random forest classification model was trained on an isolated predictor type in conjunction with a particular data re-sampling technique to account for class imbalance.
-Ten-fold cross validation was performed to tune for the number of predictor-type specific genomic features to consider at each node.
-Each model was then validated on a testing set and performances were evaluated using MCC.](Figures/figure3_ensemble_framework_V3.png)
+[??? Very briefly introduce each technique, refer to Methods for details]
 
-## RANDOM FOREST CLASSIFIERS BUILT USING A DISTANCE-TYPE FEATURE SPACE COMBINED WITH SMOTE RE-SAMPLING PROVIDED OPTIMAL MODEL PERFORMANCE
+## ENSEMBLE FRAMEWORK FOR TAD BOUNDARY PREDICTION
 
-<!--## CLASS IMBALANCE SEVERELY IMPACTS PERFORMANCE FOR CELL LINE SPECIFIC MODELS-->
+To identify the combination of data resolution, predictor type, and re-sampling technique necessary for optimal cell line specific TAD boundary prediction, we created an ensemble framework to systematically compare performances of different model inputs (Figure 2).
+The framework uses data for a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, using one of the predictor type *P = {OC, OP, Distance}*, and the re-sampling technique *B = {None, RUS, ROS, SMOTE}*.
+Once the model inputs were established, a random forest classifier was trained on chromosome-specific datasets using 10-fold cross validation.
+The model was then validated on the same separate chromosome specific test set for unbiased comparisons [???
+Ugly sentence, rewrite] and evaluated using Matthews Correlation Coefficient (MCC).
+Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2 \times 5 \times 3 \times 4 \times 21 = 2520$) models.
+Additional performance metrics are reported in the Supplementary materials.
 
-When evaluating model performances, we found that regardless of resampling technique, random forest classifiers built using a distance-type feature space yielded consistently higher MCCs when compared to the other two predictor types (Figure 3).
+![**A diagram of the ensemble framework detailing the combination of inputs used in the model building pipeline.** [???
+Describe abbreviations on the figure, the figure itself is already described in text] ](Figures/figure3_ensemble_framework_V3.png)
+
+## SMOTE RESAMPLING, DISTANCE-BASED ASSOCIATIONS OF TAD BOUNDARIES AND GENOMIC ANNOTATIONS, AND 10KB RESOLUTION OF HI-C DATA PROVIDED OPTIMAL MODEL PERFORMANCE [???
+This paragraph was completely rewritten, check for logic flow]
+
+We investigated the effect of class imbalance on model performance using three re-sampling techniques.
+Expectedly, when using data as-is, that is, with class imbalance present, the models performed poorly.
+Using any of the resampling techniques improved the performance, with SMOTE-resampled data being the most optimal (Figure 3, Supplementary Figure 3).
+These results suggest that a combination of both random over- and under-sampling (SMOTE) can improve TAD boundary prediction.
+
+We found that, regardless of resampling technique, random forest classifiers built using a distance-type feature space yielded consistently higher MCCs when compared to the overlap count and overlap percent predictor types (Figure 3), and these results were consistent across resolutions and cell types (Supplementary Figure 6).
 This indicated that models are better able to discriminate between TAD and non-TAD boundary regions when provided with spatially related associations.
-Delving further, we found that when combined with SMOTE re-sampling, random forest classifiers built using distance-type predictors out performed other re-sampling techniques across resolutions, suggesting that a combination of both random over- and under-sampling can improve TAD boundary prediction.
-Interestingly, given these parameters, we found that performances peaked at 10 kb resolution and then degraded as data resolution decreased.
-This reason for the improved performance between 5 kb and 10 kb data resolutions can be attributed to the added sparcity in the interaction frequency matrices at finer resolutions.
-This sparcity corresponds to inaccurate TAD calling which leads to worse model performance.
+
+Interestingly, we found that performances peaked at 10 kb resolution and then degraded as data resolution decreased.
+The reason for the improved performance between 5 kb and 10 kb data resolutions can be due to the sparsity in the interaction frequency matrices at finer resolutions.
+[???
+Quantify sparsity, need to substantiate this statement] This sparsity may lead to inaccurate TAD calling and, subsequently, to worse model performance.
+These results suggest that finer resolution of Hi-C data is not always optimal for accurate TAD calling and prediction, and sparsity of the data needs to be considered.
+
 Additionally, performances tended to be much more variable between chromosomes at lower resolutions.
-Moreover, this decreasing trend in performance was much more evident under the optimal combination of data level characteristics (SMOTE resampling with distance type predictors).
-These results imply that there is an ideal resolution in TAD boundary prediction, and that that an optimally performing cell line specific random forest classifier, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling.
-Models implemented on the K562 cell line were found to yield the same optimal data level characteristics (Supplementary Figure 6).
+[???
+Where are the results?] Moreover, this decreasing trend in performance was much more evident under the optimal combination of data level characteristics (SMOTE resampling with distance type predictors).
+[???
+Where are the results?]
+
+In summary, our results imply that using random under- and oversampling, distance-type predictors, and the data at 10kb resolution results in an optimally performing cell line-specific random forest-based TAD boundary prediction model.
 
@@
 
-## MODELS IMPLEMENTED ON TRANSCRIPTION FACTOR BINDING SITES, USING OPTIMAL PARAMETERS, OUTPERFORM OTHER ANNOTATION-SPECIFIC MODELS
+## TRANSCRIPTION FACTOR BINDING SITES OUTPERFORM OTHER ANNOTATION-SPECIFIC MODELS
 
 We then aimed to compare the performances of annotation-specifc models.
-In doing so, we inspected the proportion of predictive importance that was explained by each of the 3 groups of annotations (HM, ChromHMM, and TFBS).
+In doing so, we inspected the proportion of predictive importance that was explained by each of the three groups of genomic annotations (histone modifications (HM), chromatin states (ChromHMM), and transcription factor binding sites (TFBS)).
 For optimal random forest classifiers, we found that the majority of the proportional predictive importance was obtained by transcription factor binding sites (Supplementary Figure 7).
-This was consistent across resolutions, suggesting that TFBS were the primary drivers of TAD boundary formation in both the GM12878 and K562 cell lines.
+Furthermore, models build solely on TFBSs outperformed other annotation-specific models at all resolutions (Figure 4A; Supplementary Figure 8A).
+Notably, the TFBS-specific models outperformed models built on the combined sets of annotations, and this effect was most pronounced at lower resolutions.
+This indicated that the inclusion of other types of annotations contributed to additional noise rather than signal in TAD boundary prediction.
+In summary, these results suggest that TFBS are the primary drivers of TAD boundary formation in both the GM12878 and K562 cell lines.
 
-We further assessed the predictive capabilities of the specific sets of annotations by comparing the performances of annotation-specific random forest models implemented on the optimal set of characteristics.
-We found that models built simply on TFBS outperformed other annotation-specific models at all resolutions (Figure 4A; Supplementary Figure 8A).
-Additionally, when compared to models built on all 3 sets of functional genomic annotations, the TFBS-specific models performed similarly at the 5 kb and 10 kb resolutions.
-Interestingly though, at the 25 kb, 50 kb, and 100 kb resolutions, the TFBS-specific models out performed models built on the combined sets of annotations.
-This indicated that, at lower resolutions, the inclusion of other types of annotations contributed to additional noise rather than signal in TAD boundary prediction.
+## PREDICTIVE IMPORTANCES CONFIRMED BIOLOGICAL FUNCTIONALITY OF CTCF, RAD21, SMC3, and ZNF143 AT TAD BOUNDARIES
 
-##PREDICTIVE IMPORTANCES CONFIRMED BIOLOGICAL FUNCTIONALITY OF KNOWN ENRICHED TRANSCRIPTION FACTOR BINDING SITES AT TAD BOUNDARIES
+Given that many TFBS are known to colocalize together on the linear genome and are therefore highly correlated (Supplementary Figure 9), we sought to avoid overfitting by performing recursive feature elimination.
+We found that our models were able to obtain near-optimal performance using approximately eight TFBSs (Figure 4B; Supplementary Figure 8B).
+However, given that we train our models on chromosome-specific data, the most significant annotations vary for each chromosome.
+To determine the most common TFBSs, we clustered the predictive importance values across chromosomes (Figure 4C; Supplementary Figure 8C).
+We found that, similar to other studies [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD boundary regions.
 
-Given that many TFBS are known to colocalize together on the linear genome and are therefore highly correlated, we sought to avoid the incidence of overfitting our optimally built classifier by performing recursive feature elimination (Supplementary Figure 9) to establish the necessary number of TFBS to include.
-We found that our cell line specific model was able to obtain near optimal performance using only ~8 TFBS (Figure 4B; Supplementary Figure 8B).
-However, given that we are modeling on chromosome specific sections of the genome, these 8 annotations are not the same for all chromosomes.
-To determine the most common TFBS, we clustered the predictive importances across chromosomes (Figure 4C; Supplementary Figure 8C).
-We found that the following transcription factors were most important in predicting TAD boundary regions: SMC3, ZNF143, CTCF, and RAD21.
-These are known architectural proteins responsible for the 3D structure of the human genome.
-Namely, the SMC3, CTCF, and RAD21 binding sites are known factors associated with the cohesin protein complex, which is hypothesized to be what creates loops in the DNA  [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
-Likewise, ZNF143 is a known structural regulators of enhancer-promoter interactions that also contribute to looping of the linear genome [@weintraub2017yy1; @gonzalez2017znf143].
+![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) Barplots comparing performances of models using specific groups of functional genomic annotation as the feature space including histone modifications (HM; red), chromatin states (ChromHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all three groups (Combined; purple).
+(B) Recursive feature elimimation analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
+(C) Clustered heatmap of variable importances for the union of the top 8 most predictive TFBS across chromosomes.
+Error bars represent standard deviation from the mean MCC across each chromosome.](Figures/annot_specific_rfe_varimps_heatmap.png)
 
-![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) Barplots comparing performances of models using specific groups of functional genomic annotation as the feature space including histone modifications (HM; red), chromatin states (ChromHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all 3 groups (Combined; purple).
-Error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosomal section of the linear genome.
-(B) Recursive feature elimimation analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
-Error bars represent 1 standard deviation away from the mean cross-validated MCC.
-(C) Clustered heatmap of variable importances for the union of the top 8 most predictive TFBS across chromosomes.](Figures/annot_specific_rfe_varimps_heatmap.png)
+## PREDICTIVE MODELING DEFINES PRECISE AND BIOLOGICALLY RELEVANT LOCATION OF TAD BOUNDARIES
 
-## LEVERAGING ChIP-seq PEAK REGIONS OF TOP PREDICTIVE TFBS PROVIDE MORE PRECISE LOCATION OF TAD BOUNDARIES
+After obtaining our optimally built random forest classifier, we investigated whether our predictive models can alleviate resolution limitations of Hi-C data by predicting TAD boundaries at base pair resolution.
+We were able to identify regions where the model predicted the base pair to be a TAD boundary with probability equal to 1.
+[???
+Where is this figure?
+It seemed important] By clustering the regions (see Methods), we were able to predict a comparable number of TAD boundary regions as called by the ARROWHEAD TAD caller.
+However, only 24% and 29% of predicted and called (and 10 kb flanked) TAD boundaries overlapped for the GM12878 and K562 cell line, respectively, suggesting differing locations in TAD boundaries throughout the linear genome (Supplementary Figure 10).
+[???
+Need further drill down, as we discussed]
 
-After obtaining our optimally built random forest classifier, we aimed to leverage the ChIP-seq peak regions defined by the SMC3, ZNF143, CTCF, and RAD21 tanscription factors for precised TAD bounday prediction at base pair resolution.
-We found that when we validated our model against chromosome specific base pairs, we were able to identify clusters of regions where the model predicted the base pair to be a TAD boundary with probability equal to 1.
-By clustering the regions and performing medoid partitioning (See Methods), we were able to identify a comparative number of TAD boundaries as the ARROWHEAD TAD caller.
-However, only 24% and 29% of predicted and called (and 10 kb flanked) TAD boundaries overlapped for the GM12878 and K562 cell line respectively, suggesting differing locations in TAD boundaries throughout the linear genome (Supplementary Figure 10).
-To compare between predicted and called TAD boundaries we evaluated the signal strength of ChIP-seq peak regions around a 10 kb flank of each.
-We found that the peak signal strength for the SMC3, ZNF143, CTCF, and RAD21 TFBS were much closer, on average, to our predicted TAD boudaries the the called TAD boundaries obtained using the ARROWHEAD pipeline for 10 kb resolution Hi-C data (Figure 5; Supplementary Figure ).
+For each predicted TAD boundary region, we were able to identify the summit locations of TAD boundary location by performing partitioning around medoids (see Methods).
+To compare the summit locations of predicted and called TAD boundaries, we evaluated the signal strength of ChIP-seq peak regions around a 10 kb flanking region.
+We found that the signal strength for the CTCF, RAD21, SMC3, and ZNF143 [???
+Make all in this order!] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5; Supplementary Figure [???]).
+Thus, our model is able to alleviate resolution limitations and precisely locate TAD boundaries that correspond to the highest signal strength of known TAD boundary-forming TFBSs.
+
 ChIP-seq assays offer much higher resolutions (often in the tens of bases) compared to Hi-C sequenced data, which can be in the hundreds of kilobases.
-This disparity in resolution can affect a TAD caller's ability to precisely locate TADs.
-Moreover, by building a model using annotations known to be enriched at TAD boundaries we were able to bridge this gap in resolution and more precisely locate TAD boundaries that corresponded to the highest concentration in signal strength for top ranked TFBS.
+This disparity in resolution can affect a TAD caller's ability to precisely locate TADs.[???
+This is for the introduction, justifying motives for your work]
 
-![**Predicted TAD boundaries were centered closer to peak signal regions defined by known architectural transcription factors when compared to called TAD boundaries.** Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by (A) SMC3, (B) ZNF143, (C) CTCF, and (D) RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.](Figures/enrichment_heatmaps_gm12878.png)
+![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by (A) SMC3, (B) ZNF143, (C) CTCF, and (D) RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.](Figures/enrichment_heatmaps_gm12878.png) [???
+Order]
 

### 2019-08-26 Scripts/evaluating_rfe_across_chromosomes.Rmd
heatmap formatting

@@
           colsep=0:ncol(t(rfegm12878.mat)),
-          sepwidth=c(0.001,0.001),
+          sepwidth=c(0.00001,0.00001),
           sepcolor="black"
@@
           colsep=0:ncol(t(rfek562.mat)),
-          sepwidth=c(0.001,0.001),
+          sepwidth=c(0.00001,0.00001),
           sepcolor="black"

### 2019-08-26 Scripts/proportion_of_importance_per_annotation.Rmd
edits for 5kb results
changed css to chromhmm; added a and b

@@
 all_propimp <- rbind(all_propimp_gm12878_summ, all_propimp_K562_summ)
-all_propimp$CL <- c(rep("GM12878", 12),
-                    rep("K562", 12))
+all_propimp$CL <- c(rep("GM12878", 15),
+                    rep("K562", 15))
+levels(all_propimp$Annotation) <- c("ChromHMM", "HM", "TFBS")
+all_propimp$Annotation <- factor(all_propimp$Annotation, levels=c("HM", "ChromHMM", "TFBS"))
 

### 2019-08-26 Manuscript/manuscript.Rmd
added supp legends at bottom

@@
 
-Genomic annotation data in the form of cell type specific chromatin states, histone marks, and transcription factor binding sites (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Tables 2-3).
+Genomic annotation data in the form of cell type specific chromatin states, histone marks, and transcription factor binding sites (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 2).
 Functional annotations were represented by chromosome-specific regions on the linear genome obtained by ChIP-seq peak calling algorithms.
@@
 
-A total of 78 cell type specific functional genomic annotations for the GM12878 and K562 cell line were used to build the feature space of downstream predictive models (Supplementary Tables 2-3).
+A total of 78 cell type specific functional genomic annotations for the GM12878 and K562 cell line were used to build the feature space of downstream predictive models (Supplementary Table 2).
 The annotations could be broken down into three sets including histone modifications (HM), chromatin state segmentations (ChromHMM), and transcription factor binding sites (TFBS).
@@
 **Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations.
-A log2-transformation of distance was used to account for the skewness present in the distributions of distances (Supplementary Figures 4-5).
+A log2-transformation of distance was used to account for the skewness present in the distributions of distances (Supplementary Figure 4).
 These feature engineering steps were performed to improve TAD boundary predictions by accounting for direct (OC), proportional (OP), and indirect (distance) relationships between TAD boundaries and genomic annotations.
@@
 
-We found that, regardless of resampling technique, random forest classifiers built using a distance-type feature space yielded consistently higher MCCs when compared to the overlap count and overlap percent predictor types (Figure 3), and these results were consistent across resolutions and cell types (Supplementary Figure 6).
+We found that, regardless of resampling technique, random forest classifiers built using a distance-type feature space yielded consistently higher MCCs when compared to the overlap count and overlap percent predictor types (Figure 3), and these results were consistent across resolutions and cell types (Supplementary Figure 5).
 This indicated that models are better able to discriminate between TAD and non-TAD boundary regions when provided with spatially related associations.
@@
 In doing so, we inspected the proportion of predictive importance that was explained by each of the three groups of genomic annotations (histone modifications (HM), chromatin states (ChromHMM), and transcription factor binding sites (TFBS)).
-For optimal random forest classifiers, we found that the majority of the proportional predictive importance was obtained by transcription factor binding sites (Supplementary Figure 7).
-Furthermore, models build solely on TFBSs outperformed other annotation-specific models at all resolutions (Figure 4A; Supplementary Figure 8A).
+For optimal random forest classifiers, we found that the majority of the proportional predictive importance was obtained by transcription factor binding sites (Supplementary Figure 6).
+Furthermore, models build solely on TFBSs outperformed other annotation-specific models at all resolutions (Figure 4A; Supplementary Figure 7A).
 Notably, the TFBS-specific models outperformed models built on the combined sets of annotations, and this effect was most pronounced at lower resolutions.
@@
 
-Given that many TFBS are known to colocalize together on the linear genome and are therefore highly correlated (Supplementary Figure 9), we sought to avoid overfitting by performing recursive feature elimination.
-We found that our models were able to obtain near-optimal performance using approximately eight TFBSs (Figure 4B; Supplementary Figure 8B).
+Given that many TFBS are known to colocalize together on the linear genome and are therefore highly correlated (Supplementary Figure 8), we sought to avoid overfitting by performing recursive feature elimination.
+We found that our models were able to obtain near-optimal performance using approximately eight TFBSs (Figure 4B; Supplementary Figure 7B).
 However, given that we train our models on chromosome-specific data, the most significant annotations vary for each chromosome.
-To determine the most common TFBSs, we clustered the predictive importance values across chromosomes (Figure 4C; Supplementary Figure 8C).
+To determine the most common TFBSs, we clustered the predictive importance values across chromosomes (Figure 4C; Supplementary Figure 7C).
 We found that, similar to other studies [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD boundary regions.
@@
 It seemed important] By clustering the regions (see Methods), we were able to predict a comparable number of TAD boundary regions as called by the ARROWHEAD TAD caller.
-However, only 24% and 29% of predicted and called (and 10 kb flanked) TAD boundaries overlapped for the GM12878 and K562 cell line, respectively, suggesting differing locations in TAD boundaries throughout the linear genome (Supplementary Figure 10).
+However, only 24% and 29% of predicted and called (and 10 kb flanked) TAD boundaries overlapped for the GM12878 and K562 cell line, respectively, suggesting differing locations in TAD boundaries throughout the linear genome (Supplementary Figure 9).
 [???
@@
 We found that the signal strength for the CTCF, RAD21, SMC3, and ZNF143 [???
-Make all in this order!] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5; Supplementary Figure [???]).
+Make all in this order!] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5; Supplementary Figure 10[???; !!!fixed]).
 Thus, our model is able to alleviate resolution limitations and precisely locate TAD boundaries that correspond to the highest signal strength of known TAD boundary-forming TFBSs.
@@
 
+# Supplementary Legends
+
+**Supplementary Table 1. Hi-C data.** A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains.
+
+**Supplementary Table 2.
+Genomic annotations.** A complete list of the cell line specific genomic annotations used to build the feature space for all downstream models.
+The GRCh37/hg19 human genome assembly was used.
+"Genomic Class" - broad category of genomic features, "Element" - names of genomic annotations, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
+
+**Supplementary Figure 1.
+Diagram of the number of called TADs and TAD boundaries.** TADs were called using the ARROWHEAD pipeline [@durand2016juicebox] at 5 resolutions: 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb, for both the GM12878 and K562 cell line, across each autosomal chromosome (excluding chromosome 9).
+A preprocessing step was included to filter the TADs that exceeded 2 mb in width.
+The coordinates of unique TAD boundaries were then extracted and enumerated at each resolution.
+
+**Supplementary Figure 2. Venn diagrams showing that TAD boundary regions exhibit cell-line specificity across resolution.**
+
+**Supplementary Figure 3.
+Boxplots illustrating that the cell line specific proportion of class imbalance remained severe irrespective of resolution.** Proportion of imbalance (PI) was defined as the ratio of TAD boundary regions to the sum of both TAD and non-TAD boundary regions.
+Balanced datasets have PI close to 0.50.
+
+**Supplementary Figure 4.
+Performing $log_{2}$ transformations normalizes skewed distance densities across resolution.** When measured in basepairs, distances were highly right skewed (red lines) across all resolutions for both the GM12878 (A) and K562 (B) cell lines.
+After $log_{2}$ transforming the distances (blue lines), densities became much more gaussian distributed for all resolutions.
+
+**Supplementary Figure 5.
+Models built using distance-type predictors combined with SMOTE re-sampling yielded optimal MCCs across resolution on K562.** Barplots comparing the performances of random forest classifiers built using different combinations of data level characteristics for K562.
+Within each re-sampling technique (A-D), performances are compared for each type of feature space: OC (red), OP (green), and Distance (blue), across resolutions.
+Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.
+
+**Supplementary Figure 6.
+The proportional importance of optimally built cell line specific models was outweighed by transcription factor binding sites across resolutions.** Stacked barplots illustrate the proportion of total predictive importance in cell line specific random forest classifiers for (A) GM12878 and (B) K562 respectively.
+Model inputs included the optimal data level characteristics determined by the ensemble framework (SMOTE re-sampling; with distance-type predictors).
+Predictive importance was averaged for models built on chromosome specific regions of the linear genome.
+Proportional importance was then calculated according to the annotation group of the feature space including histone modifications (HM), chromatin state segmentations (ChromHMM), and transcription factor binding sites (TFBS).
+
+**Supplementary Figure 7.
+Assessing top ranked transcription factors in TAD boundary prediction for K562.** (A) Barplots comparing performances of models using K562-specific groups of functional genomic annotation as the feature space including histone modifications (HM; red), chromatin states (ChromHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all 3 groups (Combined; purple).
+Error bars represent ± 1 standard deviation from the mean MCC across each chromosomal section of the linear genome.
+(B) Recursive feature elimimation analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
+Error bars represent 1 standard deviation away from the mean cross-validated MCC.
+(C) Clustered heatmap of variable importances for the union of the top 8 most predictive TFBS across chromosomes.
+
+**Supplementary Figure 8. Pairwise Jaccard Indices illustrate correlations between cell line specific transcription factor binding sites for GM12878 (A) and K562 (B).**
+
+**Supplementary Figure 9.
+Venn diagrams illustrating the amount of overlap between predicted and called TAD boundary regions.** For each of the GM12878 (A) and K562 (B), both predicted and called TAD boundaries were flanked other either side by 10 kb and the amount of overlap was enumerated.
+
+**Supplementary Figure 10.
+Predicted TAD boundaries were centered closer to peak signal regions defined by known architectural transcription factors when compared to called TAD boundaries for K562.** Enrichment
+heatmaps illustrate the average signal strength of K562-specific ChIP-seq peak regions defined by (A) SMC3, (B) ZNF143, (C) CTCF, and (D) RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.
+
 # Abbreviations

### 2019-08-27 Manuscript/manuscript.Rmd
methods edits

@@
 
-Biological replicate Hi-C data for the GM12878 and K562 cell lines were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1).
+Biological replicate Hi-C data were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1) for the GM12878 and K562 cell lines.
 The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
-TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all cell lines and resolutions, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
+TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all resolutions and cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
 
@@
 
-Genomic annotation data in the form of cell type specific chromatin states, histone marks, and transcription factor binding sites (GRCh37/hg19 human genome assembly) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 2).
-Functional annotations were represented by chromosome-specific regions on the linear genome obtained by ChIP-seq peak calling algorithms.
+Genomic annotation data in the form of cell type specific chromatin states (ChromHMM), histone modifications (HM), and transcription factor binding sites (TFBS) were obtained from the UCSC Genome Browser Database (GRCh37/hg19 human genome assembly) [@Tyner:2017aa] (Supplementary Table 2).
+Each functional annotation was represented by chromosome-specific coordinates on the linear genome obtained by ChIP-seq peak calling algorithms.
 
@@
 In order to accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
-That is, for 100 kb resolution data, each uniquely identified TAD boundary was flanked on either side by 100 kilobases for a total width around each boundary point of 200 kb.
-A genomic bin was then labeled as having a TAD boundary within it ($Y = 1$) if it overlapped with a particular flanked boundary.
-Otherwise, the bin was labeled as not containing a boundary ($Y = 0$).
+That is, for 100 kb resolution data, each uniquely identified TAD boundary was flanked on either side by 100 kb for a total width around each boundary point of 200,000 base pairs.
+A genomic bin was defined as a TAD boundary region ($Y = 1$) if it overlapped with at least one flanked TAD boundary.
+Otherwise, the bin was considered a non-TAD boundary region ($Y = 0$).
+Random forest classifiers were used to discriminate between TAD and non-TAD boundary regions on chromosome-specific sections of the linear genome.
 
@@
 
-Using the sets of cell line specific genomic annotations, we created three types of predictors that were used to describe the relationship between functional annotations and genomic bins.
+Cell line specific genomic annotations were used to built the feature space of our random forest models.
+Here, we created three types of predictors that were used to describe the relationship between functional annotations and genomic bins.
 They are described in detail below:
 
-1. **Overlap Counts (OC)**: For each genomic bin, the total number of instances where a bin overlapped with regions assigned to genomic annotations (features) was calculated.
+1. **Overlap Counts (OC)**: For each genomic bin, the total number of instances where a bin overlapped with regions assigned to genomic annotations (features).
 
 2.
-**Overlap Percent (OP)**: For each genomic bin, the percent of overlap between the width of the region assigned to a genomic annotation and the total width of the bin was calculated.
-We defined the feature width as the number of bases that overlapped with a particular genomic bin.
-If multiple overlaps existed, the feature width was defined as the sum of the total number of bases that overlapped with a particular bin.
-[???
-Unclear.]
+**Overlap Percent (OP)**: For each genomic bin, the percent of overlap between the bin and the region assigned to a genomic annotation, defined as the *feature width*.
+If multiple overlaps existed, the *feature width* was defined as the sum of the total number of bases that overlapped with a particular bin.
 
 3.
-**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter as $\textit{distance}$) [???
-Learn Markdown!], from the center of the bin to the center of the nearest region defined by a specific genomic annotation was calculated.
+**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter as *Distance*), from the center of the bin to the center of the nearest region defined by a specific genomic annotation.
 
@@
 
-The data set used for modeling was composed of the response vector **Y**, and the predictor-type specific data matrix, **X** = {$X_1$, $X_2$, ..., $X_p$}, where $p$ was the complete set of functional annotations.
-Each composed data set was specific to cell line and resolution.
+The data set used for modeling was composed of two components: the response vector **Y**, an indicator variable separating between TAD and non-TAD boundary regions, and the predictor-type specific data matrix, **X** = {$X_1$, $X_2$, ..., $X_p$}, where $p$ was the complete set of functional annotations.
+Each composed data set was specific to cell line, resolution, and chromosome.
 We then split the data into a 7:3 ratio of training to testing sets.
-For the task of performance evaluation and prediction, the test set remained constant to account for an unbiased comparison between data level characteristics.
+<!--For the task of performance evaluation and prediction, the test set remained untouched to account for an unbiased comparison between data level characteristics.-->
 
@@
 
-$$PI = 2\dfrac{C_{min}}{C_{min} + C_{maj}}$$
+$$PI = \dfrac{C_{min}}{C_{min} + C_{maj}}$$
 
-where $C_{min}$ denotes the set of genomic bins that overlap with a flanked TAD boundary and $C_{maj}$ denotes the complementary set of genomic bins that did not overlap with a flanked TAD boundary.
-Here, PI is bounded by 0 and 1, with heavily imbalanced classes approaching 0.
+where $C_{min}$ denotes the set of TAD boundary regions and $C_{maj}$ denotes the complementary set non-TAD boundary regions.
+Here, PI is bounded by 0 and 0.50.
+Heavily imbalanced classes tend to approach 0, while balanced classes approach 0.50.
 
-In order to assess the influence of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling). They are described in detail below.
+In order to assess the influence of imbalanced classes, we evaluated four re-sampling techniques (including to no re-sampling). They are described in detail below.
 
@@
 
-<!--
 ### FEATURE REDUCTION
@@
 The quantity ranges from 0.0 to 1.0, where 0.0 represents no overlap (no correlation) and 1.0 represent complete overlap (complete correlation).
-[??
-Jaccard is a distance measure, I would avoid using the term correlation here ??]
 
-In order to suitably reduce the feature space while also maintaining the inclusion of possibly colocalized annotations, we implemented an elastic-net regularization technique prior to modelling.
-The technique using a combination of the *l_{1}* and *l_{2}* penalties.
-For each elastic-net regularization, 10-fold cross-validation was used to tune the parameters that controlled the penalty terms.
-All elastic-net algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
--->
+In order to suitably reduce the feature space while also maintaining the inclusion of possibly colocalized annotations, we implemented recursive feature elimination to estimate the optimal number of necessary features to include in the model.
+The best performing subset was identified, ranging from 2 to the maximum number of features by powers of 2.
+Given that our approach is chromosome specific, we aggregated the predictive importance of the union of the optimal set of features across chromosome using the mean decrease in node impurity.
+We then performed hierarchical clustering to obtained the most common and top ranked annotations responsible for TAD boundary prediction.
 

### 2019-08-27 Manuscript/manuscript.Rmd
methods edits

@@
 
-### FEATURE REDUCTION
-
-Architectural proteins tend to exhibit an extensive pattern of colocalization (correlation) [@van2014insulator].
-To measure the pairwise correlation of each cell line specific annotation, we used the Jaccard Index.
-The Jaccard Index measures the ratio of the number of intersecting base pairs between two sets to the number of base pairs in the union, subtracted by the intersection [@favorov2012exploring].
-The quantity ranges from 0.0 to 1.0, where 0.0 represents no overlap (no correlation) and 1.0 represent complete overlap (complete correlation).
-
-In order to suitably reduce the feature space while also maintaining the inclusion of possibly colocalized annotations, we implemented recursive feature elimination to estimate the optimal number of necessary features to include in the model.
-The best performing subset was identified, ranging from 2 to the maximum number of features by powers of 2.
-Given that our approach is chromosome specific, we aggregated the predictive importance of the union of the optimal set of features across chromosome using the mean decrease in node impurity.
-We then performed hierarchical clustering to obtained the most common and top ranked annotations responsible for TAD boundary prediction.
-
 ### FINAL MODEL ASSESSMENT AND PERFORMANCE
 
-Random forest classification models were built to compare model performances between combinations of predictor types and re-sampling techniques.
+Random forest classification models were built to compare model performances between combinations of data resolutions, predictor types, and re-sampling techniques.
 To reduce bias due to random dataset generation, 10-fold cross validation was used to tune the number of annotations, *p*, to consider at each node.
@@
 All random forest algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
-Once the model was implemented, it was validated on the test set.
-The performance of each model was compared using the composite metric, Matthews Correlation Coefficient (MCC).
-The MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
+The performance of each model was compared using Matthews Correlation Coefficient (MCC), defined as <!--The MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
 A value of 1 represents a perfect prediction, while a value of -1 represents total disagreement between prediction and observation.
 A value of 0 indicates no better than random prediction.
-The MCC is defined as
+The MCC is defined as-->
 
@@
 
-## USING OPTIMALLY BUILT CLASSIFIER TO PREDICT BOUNDARIES AT FINER RESOLUTION
+### FEATURE REDUCTION
 
-[needs editting]
+Many genomic annotations, notably architectural proteins, tend to exhibit an extensive pattern of colocalization (correlation) [@van2014insulator].
+This can contribute to high collinearity which can result in overfitting a predictive model.
+To measure the pairwise correlation of each cell line specific annotation, we used the Jaccard Index.
+The Jaccard Index measures the ratio of the number of intersecting base pairs between two sets to the number of base pairs in the union, subtracted by the intersection [@favorov2012exploring].
+The quantity ranges from 0.0 to 1.0, where 0.0 represents no overlap (no correlation) and 1.0 represent complete overlap (complete correlation).
+
+In order to suitably reduce the feature space and prevent overfitting, we implemented recursive feature elimination to estimate the optimal number of necessary features to include in the model.
+The best performing subset was identified, ranging from 2 to the maximum number of features by powers of 2.
+Given that our approach is chromosome specific, we aggregated the predictive importance of the union of the optimal set of features across chromosome using the mean decrease in node impurity.
+We then performed hierarchical clustering to obtained the most common and top ranked annotations responsible for TAD boundary prediction.
+
+## USING OPTIMALLY BUILT RANDOM FOREST CLASSIFIERS FOR MORE PRECISE TAD BOUNDARY PREDICTION
+
+Once we established our optimally built and feature reduced random forest classifier, we aimed to leverage the enrichment of known annotations to predict TAD boundaries at base pair resolution.
+We established a *predicted TAD boundary region* as a collection of adjacent base pairs that were given a probability of 1 by our model in being a predicted TAD boundary.
+To guard against inflating the number of predicted TAD boundaries, we clustered the distances between the midpoints of the *predicted TAD boundary region*.
+We then performed partitioning around mediods (PAM) to determine the *predicted TAD boundary region* that was most representative of the cluster.
+Lastly, the midpoint, in this case a particular basepair, of the *predicted TAD boundary region* identified as the medoid was defined as a predicted TAD boundary.
 

### 2019-08-27 Manuscript/manuscript.Rmd
results edits

@@
 Counts of overlaps (**overlap count**, OC) is the most commonly used type of association as it simply counts the total number of peaks defining a genomic annotation that are inside a given TAD boundary region.
-Percents of overlaps (**overlap percent**, OP) represents a more precise measure of association as it considers the proportion of overlap betwee a genomic annotation and a boundary region.
+Percents of overlaps (**overlap percent**, OP) represents a more precise measure of association as it considers the proportion of overlap between a genomic annotation and a boundary region.
 However, the distance between boundary regions and genomic annotations are currently unexplored.
@@
 These boundary regions make up the minority class, while the non-boundary regions make up the remaining majority class.
-The large disparity is sizes between minority and majority classes creates imbalanced data, as can be characterized by the *proportion of imbalance* (PI).
-Here, PI is defined as twice the ratio of the set minority class observations to the sum of both sets of minority and majority class observations.
-That is, the PI is bounded by 0 and 1.
-A dataset is considered balanced if PI $\approx$ 1, and imbalanced if PI$<<$1.
+The large disparity is sizes between minority and majority classes creates imbalanced data, as can be characterized by the *class imbalance* (CI).
+Here, CI is defined as the ratio of the set minority class observations to the sum of both sets of minority and majority class observations.
+That is, CI is bounded by 0 and 0.50.
+A dataset is considered balanced if CI $\approx$ 0.50, and imbalanced as CI approaches 0.
 Classifiers implemented on heavily imbalanced datasets are known to exhibit poor performances as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
@@
 
-Class imbalance was characterized by each dataset's *proportion of imbalance* (PI) defined as the ratio of minority class observations to the sum of minority and majority class observations:
+Class imbalance was (CI) defined as the ratio of minority class observations to the sum of minority and majority class observations:
 
-$$PI = \dfrac{C_{min}}{C_{min} + C_{maj}}$$
+$$CI = \dfrac{C_{min}}{C_{min} + C_{maj}}$$
 
 where $C_{min}$ denotes the set of TAD boundary regions and $C_{maj}$ denotes the complementary set non-TAD boundary regions.
-Here, PI is bounded by 0 and 0.50.
+Here, CI is bounded by 0 and 0.50.
 Heavily imbalanced classes tend to approach 0, while balanced classes approach 0.50.
@@
 We then performed partitioning around mediods (PAM) to determine the *predicted TAD boundary region* that was most representative of the cluster.
-Lastly, the midpoint, in this case a particular basepair, of the *predicted TAD boundary region* identified as the medoid was defined as a predicted TAD boundary.
+Lastly, the midpoint, in this case a particular basepair, of the *predicted TAD boundary region* identified as the medoid was defined as a *predicted TAD boundary*.
 
@@
 Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [???
-Add ref, see one in SpectralTAD]), we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, and 9314, 10881, 6923, 3197, and 831 unique TAD boundaries for the K562 cell line across each of the five resolutions respectively (Supplementary Figure 1).
+After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [@dixon2012topological; @sofueva2013cohesin] [???
+Add ref, see one in SpectralTAD; !!!added]), we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, and 9314, 10881, 6923, 3197, and 831 unique TAD boundaries for the K562 cell line across each of the five resolutions respectively (Supplementary Figure 1).
 To account for the variability in boundary location due to varying resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1A).
 TAD boundary regions were defined as regions on the linear genome where a genomic bin overlapped with a flanked TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as the regions that did not overlap with a flanked TAD boundary ($Y = 0$).
-A significant number [???
-Need to put exactly, e.g., $18.34 \pm 5.06 \%$] of TAD boundary regions were found to be specific to one of the two cell lines (Supplementary Figure 2).
+On average, we found that only 18.0% (SD=4.6%) [???
+Need to put exactly, e.g., $18.34 \pm 5.06 \%$; !!!added] of TAD boundary regions overlapped between both cell lines (Supplementary Figure 2).
 Given the cell type specificity of TAD boundaries, we opted to build cell line specific models for predicting TAD boundary regions.
@@
 Given that the number of bins annotated as TAD boundaries (TAD boundary regions) is much smaller than the number of non-TAD boundary bins, we investigated the class imbalance (CI) [???
-I changed PI to CI - change in supplementary accordingly] featured at each resolution.
-The CI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions.
-The CI was found to be invariant to resolution, remaining consistently low, with an average of 0.06, 0.10, 0.14, 0.12, and 0.06 [???
+I changed PI to CI - change in supplementary accordingly; !!!fixed] featured at each resolution.
+The CI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions and ranging from 0 to 0.50.
+The CI was found to be invariant to resolution, remaining consistently low across chromosomes, with an average of 0.06, 0.10, 0.14, 0.12, and 0.06 [???
 Add exact numbers, like $18.34 \pm 5.06 \%$] for the Gm12878 data at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions, respectively, with similar results observed for the K562 cell line  (Supplementary Figure 3).
@@
 **Supplementary Figure 3.
-Boxplots illustrating that the cell line specific proportion of class imbalance remained severe irrespective of resolution.** Proportion of imbalance (PI) was defined as the ratio of TAD boundary regions to the sum of both TAD and non-TAD boundary regions.
-Balanced datasets have PI close to 0.50.
+Boxplots illustrating that the cell line specific class imbalance remained severe irrespective of resolution.** Class imbalance (CI) was defined as the ratio of TAD boundary regions to the sum of both TAD and non-TAD boundary regions.
+The boxplots provide summaries of CI across chromosomes across resolution, for the GM12878 (A) and K562 (B) cell lines.
 

### 2019-08-27 Manuscript/manuscript.Rmd
results edits

@@
 The CI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions and ranging from 0 to 0.50.
-The CI was found to be invariant to resolution, remaining consistently low across chromosomes, with an average of 0.06, 0.10, 0.14, 0.12, and 0.06 [???
-Add exact numbers, like $18.34 \pm 5.06 \%$] for the Gm12878 data at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions, respectively, with similar results observed for the K562 cell line  (Supplementary Figure 3).
+The CI was found to be invariant to resolution, remaining consistently low across chromosomes, with an average of 0.196 (SD=0.025) and 0.166 (SD=0.026) for the GM12878 and K562 cell lines, respectively [???
+Add exact numbers, like $18.34 \pm 5.06 \%$ !!!added] (Supplementary Figure 3).
 The presence of class imbalance justifies the the need for using resampling techniques before predictive modeling.

### 2019-08-27 Manuscript/manuscript.Rmd
results edits

@@
 Add exact numbers, like $18.34 \pm 5.06 \%$ !!!added] (Supplementary Figure 3).
-The presence of class imbalance justifies the the need for using resampling techniques before predictive modeling.
+To account for such imbalance we evaluated 4 re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries.
+**Random over-sampling** (ROS) was defined as sampling with replacement from TAD boundary regions.
+**Random under-sampling** (RUS) was defined as sampling with replacement from non-TAD boundary regions.
+Lastly, we considered **Synthetic minority over-sampling technique** (SMOTE), which is a combination of both random over- and under-sampling [@chawla2002smote].
 
-[??? Very briefly introduce each technique, refer to Methods for details]
+[??? Very briefly introduce each technique, refer to Methods for details; !!!added]
 

### 2019-08-27 Manuscript/manuscript.Rmd
results edits

@@
 
-1. **Overlap Counts (OC)**: For each genomic bin, the total number of instances where a bin overlapped with regions assigned to genomic annotations (features).
+1. **Overlap Count (OC)**: For each genomic bin, the total number of instances where a bin overlapped with regions assigned to genomic annotations (features).
 
@@
 Once the model inputs were established, a random forest classifier was trained on chromosome-specific datasets using 10-fold cross validation.
-The model was then validated on the same separate chromosome specific test set for unbiased comparisons [???
-Ugly sentence, rewrite] and evaluated using Matthews Correlation Coefficient (MCC).
+The different combinations of inputs were evaluated by assessing the Matthews Correlation Coefficient (MCC) of each model [???
+Ugly sentence, rewrite; !!!fixed].
 Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2 \times 5 \times 3 \times 4 \times 21 = 2520$) models.
@@
 
-![**A diagram of the ensemble framework detailing the combination of inputs used in the model building pipeline.** [???
-Describe abbreviations on the figure, the figure itself is already described in text] ](Figures/figure3_ensemble_framework_V3.png)
+![**A diagram of the ensemble framework detailing the combination of inputs used in the model building pipeline.** Each cell line (GM12878, K562) specific model was composed of a combination of different data level characteristics including resolution (5 kb, 10 kb, 25 kb, 50 kb, 100 kb), predictor type (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)), and re-sampling technique (no re-sampling (None), random over-sampling (ROS), random under-sampling (RUS), synthetic minority over-sampling technique (SMOTE)).
+The following sets of genomic annotations were used to create each predictor type including histone modification (HM), chromating state segmentations (ChromHMM), transcription factor binding sites (TFBS).
+[???
+Describe abbreviations on the figure, the figure itself is already described in text;!!!fixed] ](Figures/figure3_ensemble_framework_V3.png)
 

### 2019-08-27 Manuscript/manuscript.Rmd
results edits

@@
 ## SMOTE RESAMPLING, DISTANCE-BASED ASSOCIATIONS OF TAD BOUNDARIES AND GENOMIC ANNOTATIONS, AND 10KB RESOLUTION OF HI-C DATA PROVIDED OPTIMAL MODEL PERFORMANCE [???
-This paragraph was completely rewritten, check for logic flow]
+This paragraph was completely rewritten, check for logic flow; !!!fixed]
 
@@
 These results suggest that finer resolution of Hi-C data is not always optimal for accurate TAD calling and prediction, and sparsity of the data needs to be considered.
+Additionally, performances tended to be much more variable between chromosomes at lower resolutions, evidenced by the wider error bars for the 50 kb and 100 kb resolutions.
+[???
+Where are the results?; !!!added]
 
-Additionally, performances tended to be much more variable between chromosomes at lower resolutions.
-[???
-Where are the results?] Moreover, this decreasing trend in performance was much more evident under the optimal combination of data level characteristics (SMOTE resampling with distance type predictors).
-[???
-Where are the results?]
-
-In summary, our results imply that using random under- and oversampling, distance-type predictors, and the data at 10kb resolution results in an optimally performing cell line-specific random forest-based TAD boundary prediction model.
+In summary, our results imply that using random under- and over-sampling, distance-type predictors, and the data at 10kb resolution results in an optimally performing cell line-specific random forest-based TAD boundary prediction model.
 

### 2019-08-27 Manuscript/manuscript.Rmd
results edits

@@
 ## SMOTE RESAMPLING, DISTANCE-BASED ASSOCIATIONS OF TAD BOUNDARIES AND GENOMIC ANNOTATIONS, AND 10KB RESOLUTION OF HI-C DATA PROVIDED OPTIMAL MODEL PERFORMANCE [???
-This paragraph was completely rewritten, check for logic flow; !!!fixed]
+This paragraph was completely rewritten, check for logic flow; !!!checked]
 
@@
 [???
-Quantify sparsity, need to substantiate this statement] This sparsity may lead to inaccurate TAD calling and, subsequently, to worse model performance.
+Quantify sparsity, need to substantiate this statement; !!!divide nonzero elements by total?] This sparsity may lead to inaccurate TAD calling and, subsequently, to worse model performance.
 These results suggest that finer resolution of Hi-C data is not always optimal for accurate TAD calling and prediction, and sparsity of the data needs to be considered.
@@
 ![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) Barplots comparing performances of models using specific groups of functional genomic annotation as the feature space including histone modifications (HM; red), chromatin states (ChromHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all three groups (Combined; purple).
-(B) Recursive feature elimimation analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
-(C) Clustered heatmap of variable importances for the union of the top 8 most predictive TFBS across chromosomes.
+(B) Recursive feature elimination analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
+(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes.
 Error bars represent standard deviation from the mean MCC across each chromosome.](Figures/annot_specific_rfe_varimps_heatmap.png)
@@
 Where is this figure?
-It seemed important] By clustering the regions (see Methods), we were able to predict a comparable number of TAD boundary regions as called by the ARROWHEAD TAD caller.
+It seemed important !!!how best to include?
+as an example for specific section of genome?] By clustering the regions (see Methods), we were able to predict a comparable number of TAD boundary regions as called by the ARROWHEAD TAD caller.
 However, only 24% and 29% of predicted and called (and 10 kb flanked) TAD boundaries overlapped for the GM12878 and K562 cell line, respectively, suggesting differing locations in TAD boundaries throughout the linear genome (Supplementary Figure 9).
 [???
-Need further drill down, as we discussed]
+Need further drill down, as we discussed; !!!discuss in meeting]
 
@@
 We found that the signal strength for the CTCF, RAD21, SMC3, and ZNF143 [???
-Make all in this order!] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5; Supplementary Figure 10[???; !!!fixed]).
+Make all in this order!; !!!reasoning of order is to match heatmap; discuss in meeting] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5; Supplementary Figure 10[???; !!!fixed]).
 Thus, our model is able to alleviate resolution limitations and precisely locate TAD boundaries that correspond to the highest signal strength of known TAD boundary-forming TFBSs.
@@
 Error bars represent ± 1 standard deviation from the mean MCC across each chromosomal section of the linear genome.
-(B) Recursive feature elimimation analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
+(B) Recursive feature elimination analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
 Error bars represent 1 standard deviation away from the mean cross-validated MCC.
-(C) Clustered heatmap of variable importances for the union of the top 8 most predictive TFBS across chromosomes.
+(C) Clustered heatmap of predictive importance for the union of the top 8 most predictive TFBS across chromosomes.
 

### 2019-08-27 Manuscript/manuscript.Rmd
Clean up ??? in Results

@@
 Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [@dixon2012topological; @sofueva2013cohesin] [???
-Add ref, see one in SpectralTAD; !!!added]), we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, and 9314, 10881, 6923, 3197, and 831 unique TAD boundaries for the K562 cell line across each of the five resolutions respectively (Supplementary Figure 1).
+After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [@dixon2012topological; @sofueva2013cohesin]), we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, and 9314, 10881, 6923, 3197, and 831 unique TAD boundaries for the K562 cell line across each of the five resolutions respectively (Supplementary Figure 1).
 To account for the variability in boundary location due to varying resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1A).
 TAD boundary regions were defined as regions on the linear genome where a genomic bin overlapped with a flanked TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as the regions that did not overlap with a flanked TAD boundary ($Y = 0$).
-On average, we found that only 18.0% (SD=4.6%) [???
-Need to put exactly, e.g., $18.34 \pm 5.06 \%$; !!!added] of TAD boundary regions overlapped between both cell lines (Supplementary Figure 2).
+On average, we found that only $18.0 \pm 4.6 \%$ of TAD boundary regions overlapped between both cell lines (Supplementary Figure 2).
 Given the cell type specificity of TAD boundaries, we opted to build cell line specific models for predicting TAD boundary regions.
@@
 
-Given that the number of bins annotated as TAD boundaries (TAD boundary regions) is much smaller than the number of non-TAD boundary bins, we investigated the class imbalance (CI) [???
-I changed PI to CI - change in supplementary accordingly; !!!fixed] featured at each resolution.
+Given that the number of bins annotated as TAD boundaries (TAD boundary regions) is much smaller than the number of non-TAD boundary bins, we investigated the class imbalance (CI) featured at each resolution.
 The CI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions and ranging from 0 to 0.50.
-The CI was found to be invariant to resolution, remaining consistently low across chromosomes, with an average of 0.196 (SD=0.025) and 0.166 (SD=0.026) for the GM12878 and K562 cell lines, respectively [???
-Add exact numbers, like $18.34 \pm 5.06 \%$ !!!added] (Supplementary Figure 3).
-To account for such imbalance we evaluated 4 re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries.
+The CI was found to be invariant to resolution, remaining consistently low across chromosomes, with an average of $0.196 \pm 0.025$ and $0.166 \pm 0.026$ for the GM12878 and K562 cell lines, respectively (Supplementary Figure 3).
+To account for such imbalance, we evaluated three re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries.
 **Random over-sampling** (ROS) was defined as sampling with replacement from TAD boundary regions.
@@
 Lastly, we considered **Synthetic minority over-sampling technique** (SMOTE), which is a combination of both random over- and under-sampling [@chawla2002smote].
-
-[??? Very briefly introduce each technique, refer to Methods for details; !!!added]
 
@@
 Once the model inputs were established, a random forest classifier was trained on chromosome-specific datasets using 10-fold cross validation.
-The different combinations of inputs were evaluated by assessing the Matthews Correlation Coefficient (MCC) of each model [???
-Ugly sentence, rewrite; !!!fixed].
+The different combinations of inputs were evaluated by assessing the Matthews Correlation Coefficient (MCC) of each model.
 Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2 \times 5 \times 3 \times 4 \times 21 = 2520$) models.
@@
 ![**A diagram of the ensemble framework detailing the combination of inputs used in the model building pipeline.** Each cell line (GM12878, K562) specific model was composed of a combination of different data level characteristics including resolution (5 kb, 10 kb, 25 kb, 50 kb, 100 kb), predictor type (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)), and re-sampling technique (no re-sampling (None), random over-sampling (ROS), random under-sampling (RUS), synthetic minority over-sampling technique (SMOTE)).
-The following sets of genomic annotations were used to create each predictor type including histone modification (HM), chromating state segmentations (ChromHMM), transcription factor binding sites (TFBS).
-[???
-Describe abbreviations on the figure, the figure itself is already described in text;!!!fixed] ](Figures/figure3_ensemble_framework_V3.png)
+The three types of genomic annotations, histone modification (HM), chromating state segmentations (ChromHMM), transcription factor binding sites (TFBS), were used as predictors.](Figures/figure3_ensemble_framework_V3.png)
 
-## SMOTE RESAMPLING, DISTANCE-BASED ASSOCIATIONS OF TAD BOUNDARIES AND GENOMIC ANNOTATIONS, AND 10KB RESOLUTION OF HI-C DATA PROVIDED OPTIMAL MODEL PERFORMANCE [???
-This paragraph was completely rewritten, check for logic flow; !!!checked]
+## SMOTE RESAMPLING, DISTANCE-BASED ASSOCIATIONS OF TAD BOUNDARIES AND GENOMIC ANNOTATIONS, AND 10KB RESOLUTION OF HI-C DATA PROVIDED OPTIMAL MODEL PERFORMANCE
 
@@
 Additionally, performances tended to be much more variable between chromosomes at lower resolutions, evidenced by the wider error bars for the 50 kb and 100 kb resolutions.
-[???
-Where are the results?; !!!added]
-
 In summary, our results imply that using random under- and over-sampling, distance-type predictors, and the data at 10kb resolution results in an optimally performing cell line-specific random forest-based TAD boundary prediction model.
@@
 We found that the signal strength for the CTCF, RAD21, SMC3, and ZNF143 [???
-Make all in this order!; !!!reasoning of order is to match heatmap; discuss in meeting] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5; Supplementary Figure 10[???; !!!fixed]).
+Make all in this order!; !!!reasoning of order is to match heatmap; discuss in meeting] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5; Supplementary Figure 10).
 Thus, our model is able to alleviate resolution limitations and precisely locate TAD boundaries that correspond to the highest signal strength of known TAD boundary-forming TFBSs.

### 2019-08-27 Manuscript/manuscript.Rmd
wip through methods

@@
 
-## DOMAIN DATA
+## TAD boundary data
 
@@
 TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all resolutions and cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
+[???
+TBD, did you process the data yourself?
+Or, just downloaded coordinates.
+If the latter, why the whole mishmash of data processing description?]
 
@@
 Genomic annotation data in the form of cell type specific chromatin states (ChromHMM), histone modifications (HM), and transcription factor binding sites (TFBS) were obtained from the UCSC Genome Browser Database (GRCh37/hg19 human genome assembly) [@Tyner:2017aa] (Supplementary Table 2).
-Each functional annotation was represented by chromosome-specific coordinates on the linear genome obtained by ChIP-seq peak calling algorithms.
+[???
+The former two may be combined, TBD]
 
-## DEVELOPING FRAMEWORK TO DETERMINE OPTIMAL DATA LEVEL CHARACTERISTICS FOR TAD BOUNDARY PREDICTION
+## Machine learning FRAMEWORK FOR TAD BOUNDARY PREDICTION
 
-### CLASSIFICATION
+To make the data amenable for model training, the genome was binned into equally sized intervals defined by the data resolution of the corresponding contact matrix.
+As an example, for domain data obtained from a 100 kb resolution contact matrix, the genome was binned into 100 kb intervals.
+To accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
+A genomic bin was defined as a TAD boundary region ($Y = 1$) if it overlapped with at least one flanked TAD boundary, and a non-TAD boundary region ($Y = 0$) otherwise.
+Random forest models were used to train on Arrowhead-predicted TAD boundary regions.
+Training was performed separately for each cell line, data resolution, and chromosome.
 
-To establish the data for classification, the genome was binned into equally sized intervals defined by the data resolution of the corresponding contact matrix.
-As an example, for domain data obtained from a 100 kb resolution contact matrix, the genome was binned into 100 kb intervals.
-In order to accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
-That is, for 100 kb resolution data, each uniquely identified TAD boundary was flanked on either side by 100 kb for a total width around each boundary point of 200,000 base pairs.
-A genomic bin was defined as a TAD boundary region ($Y = 1$) if it overlapped with at least one flanked TAD boundary.
-Otherwise, the bin was considered a non-TAD boundary region ($Y = 0$).
-Random forest classifiers were used to discriminate between TAD and non-TAD boundary regions on chromosome-specific sections of the linear genome.
+Cell line-specific genomic annotations were used to built the predictors for of our random forest models.
+We created three types of predictors (Figure 1): **Overlap Count (OC)** - the total number of overlaps between a bin and genomic annotation regions;  **Overlap Percent (OP)** - the percent of overlap between the bin and the total width of genomic annotation regions overlapping it; **Log2 Distance** - the $log_{2}$ of the distance in bases (refered to hereafter as *Distance*), from the center of the bin to the center of the nearest genomic annotation region.
 
-### FEATURE ENGINEERING
-
-Cell line specific genomic annotations were used to built the feature space of our random forest models.
-Here, we created three types of predictors that were used to describe the relationship between functional annotations and genomic bins.
-They are described in detail below:
-
-1. **Overlap Count (OC)**: For each genomic bin, the total number of instances where a bin overlapped with regions assigned to genomic annotations (features).
-
-2.
-**Overlap Percent (OP)**: For each genomic bin, the percent of overlap between the bin and the region assigned to a genomic annotation, defined as the *feature width*.
-If multiple overlaps existed, the *feature width* was defined as the sum of the total number of bases that overlapped with a particular bin.
-
-3.
-**Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter as *Distance*), from the center of the bin to the center of the nearest region defined by a specific genomic annotation.
-
-### TRAINING AND TESTING
-
-The data set used for modeling was composed of two components: the response vector **Y**, an indicator variable separating between TAD and non-TAD boundary regions, and the predictor-type specific data matrix, **X** = {$X_1$, $X_2$, ..., $X_p$}, where $p$ was the complete set of functional annotations.
-Each composed data set was specific to cell line, resolution, and chromosome.
-We then split the data into a 7:3 ratio of training to testing sets.
-<!--For the task of performance evaluation and prediction, the test set remained untouched to account for an unbiased comparison between data level characteristics.-->
+The complete dataset used for modeling was composed of two components: the response vector **Y**, an indicator variable separating between TAD and non-TAD boundary regions, and the predictor-type specific data matrix, **X** = {$X_1$, $X_2$, ..., $X_p$}, where $p$ was the complete set of predictors.
+The data was split into a 7:3 ratio of training and testing sets.
 

### 2019-08-28 Scripts/comparing_predicted_boundaries_vs_called_boundaries.Rmd
editted barplots

@@
 
-pred_v_called_10_df <- data.frame(LogDist = c(#Predicted
-    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1),
-    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[2]]))$distance+1),
-    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[3]]))$distance+1),
-    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[4]]))$distance+1),
-
-    #Called
-    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1),
-    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[2]]))$distance+1),
-    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[3]]))$distance+1),
-    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[4]]))$distance+1)
+#predicted but not called
+pbnc <- all_pred_bounds[-unique(subjectHits(findOverlaps(all_true_bounds,all_pred_bounds_r)))]
+
+#called and predicted
+cap1 <- all_pred_bounds[unique(subjectHits(findOverlaps(all_true_bounds,all_pred_bounds_r)))]
+cap2 <- all_true_bounds_r[unique(queryHits(findOverlaps(all_true_bounds,all_pred_bounds_r)))]
+cap <- GRangesList(cap1,cap2)
+cap <- do.call("c", cap)
+
+#called by not predicted
+all_true_bounds2 <- all_true_bounds[-unique(queryHits(findOverlaps(all_true_bounds,all_pred_bounds_r)))]
+cbnp <- resize(all_true_bounds2, width=1,fix = "center")
+
+pred_v_called_10_df <- data.frame(LogDist = c(#PBNC
+    log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1),
+    log2(mcols(distanceToNearest(pbnc, annots.GR.f[[2]]))$distance+1),
+    log2(mcols(distanceToNearest(pbnc, annots.GR.f[[3]]))$distance+1),
+    log2(mcols(distanceToNearest(pbnc, annots.GR.f[[4]]))$distance+1),
+
+    #CAP
+    log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1),
+    log2(mcols(distanceToNearest(cap, annots.GR.f[[2]]))$distance+1),
+    log2(mcols(distanceToNearest(cap, annots.GR.f[[3]]))$distance+1),
+    log2(mcols(distanceToNearest(cap, annots.GR.f[[4]]))$distance+1),
+
+    #CBNP
+    log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1),
+    log2(mcols(distanceToNearest(cbnp, annots.GR.f[[2]]))$distance+1),
+    log2(mcols(distanceToNearest(cbnp, annots.GR.f[[3]]))$distance+1),
+    log2(mcols(distanceToNearest(cbnp, annots.GR.f[[4]]))$distance+1)
 ),
-Annotation = c(#Predicted
-    rep("CTCF",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
-    rep("RAD21",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
-    rep("SMC3",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
-    rep("ZNF143",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
-
-    #Called
-    rep("CTCF",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
-    rep("RAD21",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
-    rep("SMC3",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
-    rep("ZNF143",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1)))),
-BoundReg = c(#Predicted
-    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
-    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
-    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
-    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
-
-    #Called
-    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
-    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
-    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
-    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1)))))
-
-pred_v_called_10_df$BoundReg <- factor(pred_v_called_10_df$BoundReg, levels=c("Predicted", "Called"))
+Annotation = c(#pbnc
+    rep("CTCF",length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
+    rep("RAD21",length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
+    rep("SMC3",length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
+    rep("ZNF143",length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
+
+    #cap
+    rep("CTCF",length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
+    rep("RAD21",length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
+    rep("SMC3",length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
+    rep("ZNF143",length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
+
+    #cbnp
+    rep("CTCF",length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1))),
+    rep("RAD21",length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1))),
+    rep("SMC3",length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1))),
+    rep("ZNF143",length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1)))),
+BoundReg = c(#pbnc
+    rep("PBNC", length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
+    rep("PBNC", length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
+    rep("PBNC", length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
+    rep("PBNC", length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
+
+    #cap
+    rep("CAP", length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
+    rep("CAP", length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
+    rep("CAP", length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
+    rep("CAP", length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
+
+    #cbnp
+    rep("CBNP", length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1))),
+    rep("CBNP", length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1))),
+    rep("CBNP", length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1))),
+    rep("CBNP", length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1)))))
+
+pred_v_called_10_df$BoundReg <- factor(pred_v_called_10_df$BoundReg, levels=c("PBNC", "CAP", "CBNP"))
 
@@
     geom_signif(test = "wilcox.test", 
-                comparisons = list( c("Predicted", "Called")),
+                comparisons = list(c("PBNC", "CAP"),
+                                   c("PBNC", "CBNP"),
+                                   c("CBNP", "CAP")),
                 vjust = 0,
@@
     scale_fill_manual(name="Boundary Region",
-                      values=c("red",
+                      values=c("green",
+                               "red",
                                "blue"))+
-    scale_color_manual(values=c("red",
+    scale_color_manual(values=c("green",
+                               "red",
                                "blue")) +
@@
 
+## Distance Plots
+
 ### Plots v2

### 2019-08-28 Manuscript/manuscript.Rmd
wip on methods, unfinished

@@
 
-The complete dataset used for modeling was composed of two components: the response vector **Y**, an indicator variable separating between TAD and non-TAD boundary regions, and the predictor-type specific data matrix, **X** = {$X_1$, $X_2$, ..., $X_p$}, where $p$ was the complete set of predictors.
+The complete dataset used for modeling was composed of two components: the response vector **Y**, an indicator variable separating between TAD and non-TAD boundary regions, and the predictor-type specific data matrix, **X** = {$X_1$, $X_2$, ..., $X_p$}, where $p$ was the set of predictors.
+One, or all types of predictors were used as described.
 The data was split into a 7:3 ratio of training and testing sets.
 
-### DATA RE-SAMPLING
+### Addressing class imbalance
 
-Class imbalance was (CI) defined as the ratio of minority class observations to the sum of minority and majority class observations:
+Class imbalance (CI) was defined as the proportion of minority class out of the total number of observations:
 
@@
 
-where $C_{min}$ denotes the set of TAD boundary regions and $C_{maj}$ denotes the complementary set non-TAD boundary regions.
-Here, CI is bounded by 0 and 0.50.
-Heavily imbalanced classes tend to approach 0, while balanced classes approach 0.50.
-
-In order to assess the influence of imbalanced classes, we evaluated four re-sampling techniques (including to no re-sampling). They are described in detail below.
-
-1. **No Sampling**: All of the data points from the majority and minority classes of the training set were used.
-
-2.
-**Random Under-Sampling (RUS)**: All of the data points from the minority class of the training set were used.
+where $C_{min}$ denotes the set of TAD boundary regions and $C_{maj}$ denotes the set non-TAD boundary regions.
+CI of heavily imbalanced classes approaches 0, while CI for balanced classes approaches 0.50.
+To assess the effect of CI on predictive performance, we first used the data with **o Sampling**, that is, the majority and minority classes were used as is.
+We evaluated three re-sampling techniques: **Random Under-Sampling (RUS)** - ll of the data points from the minority class of the training set were used.
 Sampling without replacement was used to obtain the same number of data points from the majority class.
@@
 Sampling with replacement was used to obtain the same number of data points from the minority class.
+[???
+I leave this unfinished because the definitions seem plain wrong]
 
@@
 
-### FINAL MODEL ASSESSMENT AND PERFORMANCE
+[??? Stopped here]
+
+### Assessmend of model performance
 

### 2019-08-28 Manuscript/manuscript.Rmd
changed methods/results headers to sentence case

--- 2019-08-27 Manuscript/manuscript.Rmd
@@
 
-# METHODS
+# Methods
 
@@
 
-## GENOMIC ANNOTATION DATA
+## Genomic annotation data
 
@@
 
-## Machine learning FRAMEWORK FOR TAD BOUNDARY PREDICTION
+## Machine learning framework for TAD boundary prediction
 
@@
 
-### DATA RE-SAMPLING
+### Data re-sampling
 
@@
 
-### FINAL MODEL ASSESSMENT AND PERFORMANCE
+### Final model assessment and performance
 
@@
 
-### FEATURE REDUCTION
+### Feature reduction
 
@@
 
-## USING OPTIMALLY BUILT RANDOM FOREST CLASSIFIERS FOR MORE PRECISE TAD BOUNDARY PREDICTION
+## Using optimally built random forest classifiers for more precise TAD boundary prediction
 
@@
 
-# RESULTS
+# Results
 
-## A RESOLUTION-SPECIFIC APPROACH FOR PREDICTING TAD BOUNDARIES
+## A resolution-specific approach for predicting TAD boundaries
 
@@
 
-## THREE TYPES OF PREDICTORS DEFINE THE ASSOCIATIONS BETWEEN TAD BOUNDARY REGIONS AND GENOMIC ANNOTATIONS
+## Three types of predictors define the associations between TAD boundary regions and genomic annotations
 
@@
 
-## TAD VS. NON-TAD BOUNDARY CLASS IMBALANCE IS SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION
+## TAD vs. non-TAD boundary class imbalance is severe irrespectively of Hi-C data resolution
 
@@
 
-## ENSEMBLE FRAMEWORK FOR TAD BOUNDARY PREDICTION
+## Ensemble framework for TAD boundary prediction
 
@@
 
-## SMOTE RESAMPLING, DISTANCE-BASED ASSOCIATIONS OF TAD BOUNDARIES AND GENOMIC ANNOTATIONS, AND 10KB RESOLUTION OF HI-C DATA PROVIDED OPTIMAL MODEL PERFORMANCE
+## SMOTE re-sampling, distance-based associations of TAD boundaries and genomic annotations, and 10 kb resolutions of Hi-C data provided optimal model performance
 
@@
 
-## TRANSCRIPTION FACTOR BINDING SITES OUTPERFORM OTHER ANNOTATION-SPECIFIC MODELS
+## Transcription factor binding sites outperform other annotation-specific models
 
@@
 
-## PREDICTIVE IMPORTANCES CONFIRMED BIOLOGICAL FUNCTIONALITY OF CTCF, RAD21, SMC3, and ZNF143 AT TAD BOUNDARIES
+## Predictive importances confirmed biological functionality of CTCF, RAD21, SMC3, and ZNF143 at TAD boundaries
 
@@
 
-## PREDICTIVE MODELING DEFINES PRECISE AND BIOLOGICALLY RELEVANT LOCATION OF TAD BOUNDARIES
+## Predictive modeling defines precise and biologically relevant location of TAD boundaries
 

### 2019-08-28 Manuscript/manuscript.Rmd

--- 2019-08-28 Manuscript/manuscript.Rmd
@@
 
-### Assessmend of model performance
+### Assessment of model performance
 

### 2019-08-28 Manuscript/manuscript.Rmd
edits

@@
 [???
-Need further drill down, as we discussed; !!!discuss in meeting]
+Need further drill down, as we discussed; !!!added distance to annotations figure in next paragraph]
 
@@
 Thus, our model is able to alleviate resolution limitations and precisely locate TAD boundaries that correspond to the highest signal strength of known TAD boundary-forming TFBSs.
+Furthermore, when compared to called TAD boundaries, the boundaries that we predicted with our model were found to be statistically significantly closer to the top ranked TFBS, suggesting stronger enrichment profiles near predicted TAD boundaries (Supplementary Figure 11).
 
@@
 
+**Supplementary Figure 11.
+Known architectural transcription factors were statistically significantly closer to predicted TAD boundaries then called TAD boundaries.** Barplots illustrate the log2 distance in basepairs from classes of TAD boundaries to transcription factors including CTCF, RAD21, SMC3, and ZNF143 for the GM12878 (A) and K562 (B) cell lines.
+TAD boundaries were classified into the 3 classes.
+Predicted but not called (PBNC) were the set of 10 kb flanked predicted TAD boundaries the did not overlap with 10 kb flanked called TAD boundaries.
+Called and predicted (CAP) were the set of 10 kb flanked called and predicted TAD boundaries that overlapped with each other.
+Called but not predicted (CBNP) were the set of 10 kb flanked called TAD boundaries that did not overlap with 10 kb flanked predicted TAD boundaries.
+
 # Abbreviations

### 2019-08-28 Scripts/comparing_predicted_boundaries_vs_called_boundaries.Rmd
changed formatting of heatmaps; increase fonts

@@
 EnrichedHeatmap(mat_pred_ctcf, 
-                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                 #heatmap_legend_param = list(show_heatmap_legend = FALSE),
@@
                 axis_name = axis_names,
-                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col ="red", 
-                                                                                   lwd = 2), 
-                                                                         yaxis_side = "right", 
-                                                                         yaxis_facing = "left")))
+				column_title_gp = gpar(fontsize = 20),
+				row_title_gp = gpar(fontsize = 20),
+				axis_name_gp = gpar(fontsize = 20),
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col ="darkgreen", fontsize = 10,
+                                                                                   lwd = 2), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+
 ```
@@
 EnrichedHeatmap(mat_called_ctcf, 
-                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                 #heatmap_legend_param = list(show_heatmap_legend = FALSE),
@@
                 axis_name = axis_names,
-                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red", 
-                                                                                   lwd = 2,
-                                                                                   lty=3), 
+				column_title_gp = gpar(fontsize = 20),
+				row_title_gp = gpar(fontsize = 20),
+				axis_name_gp = gpar(fontsize = 20),
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
+                                                                                   lwd = 2), 
                                                                          yaxis_side = "right", 
@@
 EnrichedHeatmap(mat_pred_rad21, 
-                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                 #heatmap_legend_param = list(show_heatmap_legend = FALSE),
@@
                 axis_name = axis_names,
-                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red", 
-                                                                                   lwd = 2), 
-                                                                         yaxis_side = "right", 
-                                                                         yaxis_facing = "left")))
+				column_title_gp = gpar(fontsize = 20),
+				row_title_gp = gpar(fontsize = 20),
+				axis_name_gp = gpar(fontsize = 20),
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "darkgreen", 
+                                                                                   lwd = 2), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+
 ```
@@
 EnrichedHeatmap(mat_called_rad21, 
-                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                 #heatmap_legend_param = list(show_heatmap_legend = FALSE),
@@
                 axis_name = axis_names,
-                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red", 
-                                                                                   lwd = 2,
-                                                                                   lty = 3), 
-                                                                         yaxis_side = "right", 
-                                                                         yaxis_facing = "left")))
+				column_title_gp = gpar(fontsize = 20),
+				row_title_gp = gpar(fontsize = 20),
+				axis_name_gp = gpar(fontsize = 20),
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
+                                                                                   lwd = 2), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+
 ```
@@
 EnrichedHeatmap(mat_pred_smc3, 
-                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                 #heatmap_legend_param = list(show_heatmap_legend = FALSE),
@@
 EnrichedHeatmap(mat_called_smc3, 
-                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                 #heatmap_legend_param = list(show_heatmap_legend = FALSE),
@@
 EnrichedHeatmap(mat_pred_znf143, 
-                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                 #heatmap_legend_param = list(show_heatmap_legend = FALSE),
@@
 EnrichedHeatmap(mat_called_znf143, 
-                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
+                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                 #heatmap_legend_param = list(show_heatmap_legend = FALSE),
@@
 EnrichedHeatmap(mat_pred_ctcf, 
-                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
+                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                 #heatmap_legend_param = list(show_heatmap_legend = FALSE),
@@
                 axis_name = axis_names,
-                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col ="blue", 
-                                                                                   lwd = 2), 
-                                                                         yaxis_side = "right", 
-                                                                         yaxis_facing = "left")))
+				column_title_gp = gpar(fontsize = 20),
+				row_title_gp = gpar(fontsize = 20),
+				axis_name_gp = gpar(fontsize = 20),
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col ="darkgreen", fontsize = 10,
+                                                                                   lwd = 2), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+
 ```
@@
                 axis_name = axis_names,
+				column_title_gp = gpar(fontsize = 20),
+				row_title_gp = gpar(fontsize = 20),
+				axis_name_gp = gpar(fontsize = 20),
                 top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
-                                                                                   lwd = 2,
-                                                                                   lty=3), 
-                                                                         yaxis_side = "right", 
-                                                                         yaxis_facing = "left")))
+                                                                                   lwd = 2), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+
 ```
@@
 EnrichedHeatmap(mat_pred_rad21, 
-                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
+                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                 #heatmap_legend_param = list(show_heatmap_legend = FALSE),
@@
                 axis_name = axis_names,
-                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
-                                                                                   lwd = 2), 
-                                                                         yaxis_side = "right", 
-                                                                         yaxis_facing = "left")))
+				column_title_gp = gpar(fontsize = 20),
+				row_title_gp = gpar(fontsize = 20),
+				axis_name_gp = gpar(fontsize = 20),
+                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "darkgreen", 
+                                                                                   lwd = 2), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+
 ```
@@
                 axis_name = axis_names,
+				column_title_gp = gpar(fontsize = 20),
+				row_title_gp = gpar(fontsize = 20),
+				axis_name_gp = gpar(fontsize = 20),
                 top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
-                                                                                   lwd = 2,
-                                                                                   lty = 3), 
-                                                                         yaxis_side = "right", 
-                                                                         yaxis_facing = "left")))
+                                                                                   lwd = 2), 
+                                                                         yaxis_side = "right", 
+                                                                         yaxis_facing = "left")))
+
 ```
@@
 EnrichedHeatmap(mat_pred_smc3, 
-                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
+                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                 #heatmap_legend_param = list(show_heatmap_legend = FALSE),
@@
 EnrichedHeatmap(mat_pred_znf143, 
-                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
+                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                 #heatmap_legend_param = list(show_heatmap_legend = FALSE),

### 2019-08-28 Manuscript/manuscript.Rmd
edits

@@
 We found that the signal strength for the CTCF, RAD21, SMC3, and ZNF143 [???
-Make all in this order!; !!!reasoning of order is to match heatmap; discuss in meeting] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5; Supplementary Figure 10).
+Make all in this order!; !!!fixed] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5; Supplementary Figure 10).
 Thus, our model is able to alleviate resolution limitations and precisely locate TAD boundaries that correspond to the highest signal strength of known TAD boundary-forming TFBSs.
@@
 
-![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by (A) SMC3, (B) ZNF143, (C) CTCF, and (D) RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.](Figures/enrichment_heatmaps_gm12878.png) [???
-Order]
+![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by (A) CTCF, (B) RAD21, (C) SMC3, and (D) ZNF143 around the centers of 10 kb flanked predicted and called TAD boundaries.](Figures/enrichment_heatmaps_gm12878.png)
 

### 2019-08-28 Scripts/evaluating_jaccard_indices.Rmd
initial commit

---
title: "Jaccard Index Heatmaps for TFBS"
author: "Spiro Stilianoudakis"
date: "August 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(scales)
library(GGally)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggpubr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)
```

# GM12878

```{r}
jaccard.mat.gm12878_tfbs <-  readRDS("Z:/TAD_data_analysis/jaccard/jaccard.mat.gm12878_tfbs.rds")

diag(jaccard.mat.gm12878_tfbs) <- NA

distance.col = as.dist(jaccard.mat.gm12878_tfbs)
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(jaccard.mat.gm12878_tfbs))
heatmap.2(t(jaccard.mat.gm12878_tfbs),
          #labRow=rownames(rfegm12878.mat),
          #labCol=colnames(rfegm12878.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="none",     # only draw a row dendrogram,
          #Rowv = FALSE,
          #Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=1,
          cexCol=1)
```

# K562

```{r}
jaccard.mat.k562_tfbs <-  readRDS("Z:/TAD_data_analysis/jaccard/jaccard.mat.k562_tfbs.rds")

diag(jaccard.mat.k562_tfbs) <- NA

distance.col = as.dist(jaccard.mat.k562_tfbs)
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(jaccard.mat.k562_tfbs))
heatmap.2(t(jaccard.mat.k562_tfbs),
          #labRow=rownames(rfegm12878.mat),
          #labCol=colnames(rfegm12878.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="none",     # only draw a row dendrogram,
          #Rowv = FALSE,
          #Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=1,
          cexCol=1)
```

### 2019-08-28 Scripts/visualizing_example_predicted_tad_bounds.Rmd
editted plotting parameters

@@
   xlab("Base Pair") +
-  ylab("Predicted Probability") +
+  ylab("Probability") +
   scale_color_manual(name = '', 

### 2019-08-28 Manuscript/manuscript.Rmd
edits

@@
 After obtaining our optimally built random forest classifier, we investigated whether our predictive models can alleviate resolution limitations of Hi-C data by predicting TAD boundaries at base pair resolution.
-We were able to identify regions where the model predicted the base pair to be a TAD boundary with probability equal to 1.
+We were able to identify regions where the model predicted the base pair to be a TAD boundary with probability equal to 1 (Figure 5).
 [???
 Where is this figure?
-It seemed important !!!how best to include?
-as an example for specific section of genome?] By clustering the regions (see Methods), we were able to predict a comparable number of TAD boundary regions as called by the ARROWHEAD TAD caller.
+It seemed important; !!!added] By clustering the regions (see Methods), we were able to predict a comparable number of TAD boundary regions as called by the ARROWHEAD TAD caller.
 However, only 24% and 29% of predicted and called (and 10 kb flanked) TAD boundaries overlapped for the GM12878 and K562 cell line, respectively, suggesting differing locations in TAD boundaries throughout the linear genome (Supplementary Figure 9).
@@
 We found that the signal strength for the CTCF, RAD21, SMC3, and ZNF143 [???
-Make all in this order!; !!!fixed] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5; Supplementary Figure 10).
+Make all in this order!; !!!fixed] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 6; Supplementary Figure 10).
 Thus, our model is able to alleviate resolution limitations and precisely locate TAD boundaries that correspond to the highest signal strength of known TAD boundary-forming TFBSs.
@@
 
-![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by (A) CTCF, (B) RAD21, (C) SMC3, and (D) ZNF143 around the centers of 10 kb flanked predicted and called TAD boundaries.](Figures/enrichment_heatmaps_gm12878.png)
+![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17390000-18640000; GM12878).
+The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.
+Called TADs are outlined in blue.
+The blue vertical lines represent a called TAD boundary identified by the ARROWHEAD algorithm.
+The black line represents the predicted probability of each base pair being a TAD boundary.
+Regions of adjacent base pairs with probability of 1 are represented by the green regions along the x-axis.
+The green vertical lines represent the subsequent base pair predicted to be a TAD boundary using medoid partitioning.
+(B) Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by SMC3, ZNF143, CTCF, and RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.](Figures/visualizing_boundaries_example_with_enriched_heatmaps.png)
 

### 2019-08-28 Manuscript/manuscript.Rmd
fixed figure numbers

@@
 After obtaining our optimally built random forest classifier, we investigated whether our predictive models can alleviate resolution limitations of Hi-C data by predicting TAD boundaries at base pair resolution.
-We were able to identify regions where the model predicted the base pair to be a TAD boundary with probability equal to 1 (Figure 5).
+We were able to identify regions where the model predicted the base pair to be a TAD boundary with probability equal to 1 (Figure 5A).
 [???
@@
 We found that the signal strength for the CTCF, RAD21, SMC3, and ZNF143 [???
-Make all in this order!; !!!fixed] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 6; Supplementary Figure 10).
+Make all in this order!; !!!fixed] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5B; Supplementary Figure 10).
 Thus, our model is able to alleviate resolution limitations and precisely locate TAD boundaries that correspond to the highest signal strength of known TAD boundary-forming TFBSs.

### 2019-08-28 Manuscript/manuscript.Rmd
edits

@@
 CI of heavily imbalanced classes approaches 0, while CI for balanced classes approaches 0.50.
-To assess the effect of CI on predictive performance, we first used the data with **o Sampling**, that is, the majority and minority classes were used as is.
-We evaluated three re-sampling techniques: **Random Under-Sampling (RUS)** - ll of the data points from the minority class of the training set were used.
+To assess the effect of CI on predictive performance, we first used the data with **No Sampling**, that is, the majority and minority classes were used as is.
+We evaluated three re-sampling techniques: **Random Under-Sampling (RUS)** - all of the data points from the minority class of the training set were used.
 Sampling without replacement was used to obtain the same number of data points from the majority class.
@@
 Many genomic annotations, notably architectural proteins, tend to exhibit an extensive pattern of colocalization (correlation) [@van2014insulator].
-This can contribute to high collinearity which can result in overfitting a predictive model.
-To measure the pairwise correlation of each cell line specific annotation, we used the Jaccard Index.
+<!--This can contribute to high collinearity which can result in overfitting a predictive model.--> To measure the pairwise correlation of each cell line specific annotation, we used the Jaccard Index.
 The Jaccard Index measures the ratio of the number of intersecting base pairs between two sets to the number of base pairs in the union, subtracted by the intersection [@favorov2012exploring].
-The quantity ranges from 0.0 to 1.0, where 0.0 represents no overlap (no correlation) and 1.0 represent complete overlap (complete correlation).
+The quantity ranges from 0 to 1, where 0 represents no overlap (no correlation) and 1 represent complete overlap (complete correlation).
 
@@
 The best performing subset was identified, ranging from 2 to the maximum number of features by powers of 2.
-Given that our approach is chromosome specific, we aggregated the predictive importance of the union of the optimal set of features across chromosome using the mean decrease in node impurity.
-We then performed hierarchical clustering to obtained the most common and top ranked annotations responsible for TAD boundary prediction.
+We then aggregated the predictive importance of the union of the optimal set of features across chromosome using the mean decrease in node impurity.
+Hierarchical clustering was performed to obtained the most common and top ranked annotations responsible for TAD boundary prediction.
 
@@
 
-Once we established our optimally built and feature reduced random forest classifier, we aimed to leverage the enrichment of known annotations to predict TAD boundaries at base pair resolution.
-We established a *predicted TAD boundary region* as a collection of adjacent base pairs that were given a probability of 1 by our model in being a predicted TAD boundary.
-To guard against inflating the number of predicted TAD boundaries, we clustered the distances between the midpoints of the *predicted TAD boundary region*.
+By leveraging the enrichment of known annotations in our model, we established a *predicted TAD boundary region* as a collection of adjacent base pairs that were given a probability of 1 for being a potentially predicted TAD boundary.
+To guard against inflating the number of predicted TAD boundaries, we clustered the distances between the midpoints of the *predicted TAD boundary regions*.
 We then performed partitioning around mediods (PAM) to determine the *predicted TAD boundary region* that was most representative of the cluster.
-Lastly, the midpoint, in this case a particular basepair, of the *predicted TAD boundary region* identified as the medoid was defined as a *predicted TAD boundary*.
+The midpoint, in this case a particular basepair, of the *predicted TAD boundary region* identified as the medoid was defined as a final *predicted TAD boundary*.
+This process was repeated throughout the chromosome-specific sections of the linear genome.
 

### 2019-08-28 Scripts/comparing_predicted_boundaries_vs_called_boundaries.Rmd
changed color to forest green

@@
     scale_fill_manual(name="Boundary Region",
-                      values=c("green",
+                      values=c("forestgreen",
                                "red",
                                "blue"))+
-    scale_color_manual(values=c("green",
+    scale_color_manual(values=c("forestgreen",
                                "red",

### 2019-08-28 Manuscript/manuscript.Rmd
edits

@@
 TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all resolutions and cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
-[???
-TBD, did you process the data yourself?
-Or, just downloaded coordinates.
-If the latter, why the whole mishmash of data processing description?]
 
@@
 **Random Over-Sampling (ROS)**: All of the data points from the majority class of the training set were used.
-Sampling with replacement was used to obtain the same number of data points from the minority class.
-[???
-I leave this unfinished because the definitions seem plain wrong]
+Sampling with replacement from minority class was used to obtain the same number of data points as in the majority class.
 

### 2019-08-29 Manuscript/manuscript.Rmd
reordered figures

@@
 
-## TAD boundary data
+## Genomic annotation and TAD boundary data
 
@@
 
-## Genomic annotation data
-
-Genomic annotation data in the form of cell type specific chromatin states (ChromHMM), histone modifications (HM), and transcription factor binding sites (TFBS) were obtained from the UCSC Genome Browser Database (GRCh37/hg19 human genome assembly) [@Tyner:2017aa] (Supplementary Table 2).
-[???
-The former two may be combined, TBD]
+Genomic annotation data in the form of cell type specific chromatin states (ChromHMM), histone modifications (HM), and transcription factor binding sites (TFBS) were obtained from the UCSC Genome Browser Database (GRCh37/hg19 human genome assembly) [@Tyner:2017aa] (Supplementary Table 1).
 
@@
 Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [@dixon2012topological; @sofueva2013cohesin]), we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, and 9314, 10881, 6923, 3197, and 831 unique TAD boundaries for the K562 cell line across each of the five resolutions respectively (Supplementary Figure 1).
+After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [@dixon2012topological; @sofueva2013cohesin]), we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, across each of the five resolutions respectively (Table 1).
+Similar numbers of TAD boundaries were found for the K562 cell line (not reported).
 To account for the variability in boundary location due to varying resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1A).
 TAD boundary regions were defined as regions on the linear genome where a genomic bin overlapped with a flanked TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as the regions that did not overlap with a flanked TAD boundary ($Y = 0$).
-On average, we found that only $18.0 \pm 4.6 \%$ of TAD boundary regions overlapped between both cell lines (Supplementary Figure 2).
+On average, we found that only $18.0 \pm 4.6 \%$ of TAD boundary regions overlapped between both cell lines.
 Given the cell type specificity of TAD boundaries, we opted to build cell line specific models for predicting TAD boundary regions.
@@
 In summary, we developed a framework enabling resolution-specific prediction of TAD boundaries, with resolution-specific bins defining the response variable.
+
+| Resolution | Total number of called TADs | Total number of unique TAD boundaries | Average Class Imbalance (SD) |
+|:----------:|:---------------------------:|:-------------------------------------:|:----------------------------:|
+|5 kb        |8043	                       | 16133                                 | 0.06 (0.02)                  |
+|10 kb	     |7650	                       | 14824                                 | 0.10 (0.01)                  |
+|25 kb	     |4208	                       | 8081                                  | 0.14 (0.01)                  |   
+|50 kb	     |1772	                       | 3560	                                 | 0.12 (0.01)                  |
+|100 kb	     |444	                         | 919	                                 | 0.06 (0.01)                  |    
+Table: Domain data and class imbalance summaries across resolutions for GM12878.
+
+## Three types of predictors define the associations between TAD boundary regions and genomic annotations
+
+A total of 78 cell type specific functional genomic annotations for the GM12878 and K562 cell line were used to build the feature space of downstream predictive models (Supplementary Table 1).
+The annotations could be broken down into three sets including histone modifications (HM), chromatin state segmentations (ChromHMM), and transcription factor binding sites (TFBS).
+We constructed three different predictor types for each functional genomic annotation (Figure 1B).
+Counts of overlaps (**overlap count**, OC) were defined as the total number of genomic annotation regions that overlapped within a given genomic bin.
+Percents of overlaps (**overlap percent**, OP) were defined as the proportion of a bin overlapped by an annotation region.
+**Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations.
+A log2-transformation of distance was used to account for the skewness present in the distributions of distances (Supplementary Figure 1).
+These feature engineering steps were performed to improve TAD boundary predictions by accounting for direct (OC), proportional (OP), and indirect (distance) relationships between TAD boundaries and genomic annotations.
 
@@
 
-## Three types of predictors define the associations between TAD boundary regions and genomic annotations
-
-A total of 78 cell type specific functional genomic annotations for the GM12878 and K562 cell line were used to build the feature space of downstream predictive models (Supplementary Table 2).
-The annotations could be broken down into three sets including histone modifications (HM), chromatin state segmentations (ChromHMM), and transcription factor binding sites (TFBS).
-We constructed three different predictor types for each functional genomic annotation (Figure 1B).
-Counts of overlaps (**overlap count**, OC) were defined as the total number of genomic annotation regions that overlapped within a given genomic bin.
-Percents of overlaps (**overlap percent**, OP) were defined as the proportion of a bin overlapped by an annotation region.
-**Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations.
-A log2-transformation of distance was used to account for the skewness present in the distributions of distances (Supplementary Figure 4).
-These feature engineering steps were performed to improve TAD boundary predictions by accounting for direct (OC), proportional (OP), and indirect (distance) relationships between TAD boundaries and genomic annotations.
-
 ## TAD vs. non-TAD boundary class imbalance is severe irrespectively of Hi-C data resolution
@@
 The CI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions and ranging from 0 to 0.50.
-The CI was found to be invariant to resolution, remaining consistently low across chromosomes, with an average of $0.196 \pm 0.025$ and $0.166 \pm 0.026$ for the GM12878 and K562 cell lines, respectively (Supplementary Figure 3).
+The CI was found to be invariant to resolution, remaining consistently low across chromosomes, with an averages of 0.06, 0.10, 0.14, 0.12, and 0.06 across each resolutions for GM12878 (Table 1).
+Similar class imbalances were found for the K562 cell line (not reported).
 To account for such imbalance, we evaluated three re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries.
@@
 Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2 \times 5 \times 3 \times 4 \times 21 = 2520$) models.
-Additional performance metrics are reported in the Supplementary materials.
+<!--Additional performance metrics are reported in the Supplementary materials.-->
 
@@
 Expectedly, when using data as-is, that is, with class imbalance present, the models performed poorly.
-Using any of the resampling techniques improved the performance, with SMOTE-resampled data being the most optimal (Figure 3, Supplementary Figure 3).
+Using any of the resampling techniques improved the performance, with SMOTE-resampled data being the most optimal (Figure 3, Supplementary Figure 2).
 These results suggest that a combination of both random over- and under-sampling (SMOTE) can improve TAD boundary prediction.
 
-We found that, regardless of resampling technique, random forest classifiers built using a distance-type feature space yielded consistently higher MCCs when compared to the overlap count and overlap percent predictor types (Figure 3), and these results were consistent across resolutions and cell types (Supplementary Figure 5).
+We found that, regardless of resampling technique, random forest classifiers built using a distance-type feature space yielded consistently higher MCCs when compared to the overlap count and overlap percent predictor types (Figure 3), and these results were consistent across resolutions and cell types (Supplementary Figure 2).
 This indicated that models are better able to discriminate between TAD and non-TAD boundary regions when provided with spatially related associations.
@@
 [???
-Quantify sparsity, need to substantiate this statement; !!!divide nonzero elements by total?] This sparsity may lead to inaccurate TAD calling and, subsequently, to worse model performance.
+Quantify sparsity] This sparsity may lead to inaccurate TAD calling and, subsequently, to worse model performance.
 These results suggest that finer resolution of Hi-C data is not always optimal for accurate TAD calling and prediction, and sparsity of the data needs to be considered.
@@
 In doing so, we inspected the proportion of predictive importance that was explained by each of the three groups of genomic annotations (histone modifications (HM), chromatin states (ChromHMM), and transcription factor binding sites (TFBS)).
-For optimal random forest classifiers, we found that the majority of the proportional predictive importance was obtained by transcription factor binding sites (Supplementary Figure 6).
-Furthermore, models build solely on TFBSs outperformed other annotation-specific models at all resolutions (Figure 4A; Supplementary Figure 7A).
+For optimal random forest classifiers, we found that the majority of the proportional predictive importance was obtained by transcription factor binding sites (Supplementary Figure 3).
+Furthermore, models build solely on TFBSs outperformed other annotation-specific models at all resolutions (Figure 4A; Supplementary Figure 4A).
 Notably, the TFBS-specific models outperformed models built on the combined sets of annotations, and this effect was most pronounced at lower resolutions.
@@
 
-Given that many TFBS are known to colocalize together on the linear genome and are therefore highly correlated (Supplementary Figure 8), we sought to avoid overfitting by performing recursive feature elimination.
-We found that our models were able to obtain near-optimal performance using approximately eight TFBSs (Figure 4B; Supplementary Figure 7B).
+Given that many TFBS are known to colocalize together on the linear genome and are therefore highly correlated, we sought to avoid overfitting by performing recursive feature elimination.
+We found that our models were able to obtain near-optimal performance using approximately eight TFBSs (Figure 4B; Supplementary Figure 4B).
 However, given that we train our models on chromosome-specific data, the most significant annotations vary for each chromosome.
-To determine the most common TFBSs, we clustered the predictive importance values across chromosomes (Figure 4C; Supplementary Figure 7C).
+To determine the most common TFBSs, we clustered the predictive importance values across chromosomes (Figure 4C; Supplementary Figure 4C).
 We found that, similar to other studies [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD boundary regions.
@@
 It seemed important; !!!added] By clustering the regions (see Methods), we were able to predict a comparable number of TAD boundary regions as called by the ARROWHEAD TAD caller.
-However, only 24% and 29% of predicted and called (and 10 kb flanked) TAD boundaries overlapped for the GM12878 and K562 cell line, respectively, suggesting differing locations in TAD boundaries throughout the linear genome (Supplementary Figure 9).
+However, only 24% and 29% of predicted and called (and 10 kb flanked) TAD boundaries overlapped for the GM12878 and K562 cell line, respectively, suggesting differing locations in TAD boundaries throughout the linear genome (Supplementary Figure 5).
 [???
@@
 We found that the signal strength for the CTCF, RAD21, SMC3, and ZNF143 [???
-Make all in this order!; !!!fixed] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5B; Supplementary Figure 10).
+Make all in this order!; !!!fixed] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5B; Supplementary Figure 6).
 Thus, our model is able to alleviate resolution limitations and precisely locate TAD boundaries that correspond to the highest signal strength of known TAD boundary-forming TFBSs.
-Furthermore, when compared to called TAD boundaries, the boundaries that we predicted with our model were found to be statistically significantly closer to the top ranked TFBS, suggesting stronger enrichment profiles near predicted TAD boundaries (Supplementary Figure 11).
+Furthermore, when compared to called TAD boundaries, the boundaries that we predicted with our model were found to be statistically significantly closer to the top ranked TFBS, suggesting stronger enrichment profiles near predicted TAD boundaries (Supplementary Figure 7).
 
@@
 
-**Supplementary Table 1. Hi-C data.** A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains.
-
-**Supplementary Table 2.
-Genomic annotations.** A complete list of the cell line specific genomic annotations used to build the feature space for all downstream models.
+**Supplementary Table 1.
+Hi-C and genomic annotation data.** (A) A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains.
+(B) A complete list of the cell line specific genomic annotations used to build the feature space for all downstream models.
 The GRCh37/hg19 human genome assembly was used.
@@
 **Supplementary Figure 1.
-Diagram of the number of called TADs and TAD boundaries.** TADs were called using the ARROWHEAD pipeline [@durand2016juicebox] at 5 resolutions: 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb, for both the GM12878 and K562 cell line, across each autosomal chromosome (excluding chromosome 9).
-A preprocessing step was included to filter the TADs that exceeded 2 mb in width.
-The coordinates of unique TAD boundaries were then extracted and enumerated at each resolution.
-
-**Supplementary Figure 2. Venn diagrams showing that TAD boundary regions exhibit cell-line specificity across resolution.**
-
-**Supplementary Figure 3.
-Boxplots illustrating that the cell line specific class imbalance remained severe irrespective of resolution.** Class imbalance (CI) was defined as the ratio of TAD boundary regions to the sum of both TAD and non-TAD boundary regions.
-The boxplots provide summaries of CI across chromosomes across resolution, for the GM12878 (A) and K562 (B) cell lines.
-
-**Supplementary Figure 4.
 Performing $log_{2}$ transformations normalizes skewed distance densities across resolution.** When measured in basepairs, distances were highly right skewed (red lines) across all resolutions for both the GM12878 (A) and K562 (B) cell lines.
@@
 
-**Supplementary Figure 5.
+**Supplementary Figure 2.
 Models built using distance-type predictors combined with SMOTE re-sampling yielded optimal MCCs across resolution on K562.** Barplots comparing the performances of random forest classifiers built using different combinations of data level characteristics for K562.
@@
 
-**Supplementary Figure 6.
+**Supplementary Figure 3.
 The proportional importance of optimally built cell line specific models was outweighed by transcription factor binding sites across resolutions.** Stacked barplots illustrate the proportion of total predictive importance in cell line specific random forest classifiers for (A) GM12878 and (B) K562 respectively.
@@
 
-**Supplementary Figure 7.
+**Supplementary Figure 4.
 Assessing top ranked transcription factors in TAD boundary prediction for K562.** (A) Barplots comparing performances of models using K562-specific groups of functional genomic annotation as the feature space including histone modifications (HM; red), chromatin states (ChromHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all 3 groups (Combined; purple).
@@
 
-**Supplementary Figure 8. Pairwise Jaccard Indices illustrate correlations between cell line specific transcription factor binding sites for GM12878 (A) and K562 (B).**
-
-**Supplementary Figure 9.
+**Supplementary Figure 5.
 Venn diagrams illustrating the amount of overlap between predicted and called TAD boundary regions.** For each of the GM12878 (A) and K562 (B), both predicted and called TAD boundaries were flanked other either side by 10 kb and the amount of overlap was enumerated.
 
-**Supplementary Figure 10.
+**Supplementary Figure 6.
 Predicted TAD boundaries were centered closer to peak signal regions defined by known architectural transcription factors when compared to called TAD boundaries for K562.** Enrichment
@@
 
-**Supplementary Figure 11.
+**Supplementary Figure 7.
 Known architectural transcription factors were statistically significantly closer to predicted TAD boundaries then called TAD boundaries.** Barplots illustrate the log2 distance in basepairs from classes of TAD boundaries to transcription factors including CTCF, RAD21, SMC3, and ZNF143 for the GM12878 (A) and K562 (B) cell lines.

### 2019-08-29 Manuscript/manuscript.Rmd
edits

@@
 <!--[still revising]-->
-Recently, an L1-regularized multiple logistic regression model, called *HiCfeat*, was developed to predict TAD boundary regions using a collection of 69 transcription factor binding sites on the GM12878 cell line [@mourad2016computational].
+Recently, an L1-regularized multiple logistic regression model, called *HiCfeat*, 
+was developed to predict TAD boundaries using transcription factor binding sites 
+on GM12878 [@mourad2016computational]. Based on a 1 kb binned genomic data matrix 
+and 20 kb flanked TAD boundaries, the model was trained using proportions of 
+overlaps between ChiP-seq peak defined functional element coordinates and genomic 
+bins. However, several problems exist with this study. First, many transcription 
+factors are known to colocalize, and therefore exhibit high correlations. Given 
+a group of features that are highly correlated, L1-regularization tends to pick 
+only one of them, while shrinking the others to zero [@zou2005regularization]. 
+Here, ensemble learning techniques could offer a more robust method toward 
+identifying  annotations associated with TAD boudaries. Likewise, it is unclear 
+how other sets of epigenomic features affect prediction, including chromatin state 
+segmentations and histone modifications. Secondly, the class imbalance issue was 
+not addressed prior to modelling. Instead, model performance was evaluated using 
+ROC (receiver operating characteristic) curves and subsequent AUC (area under the 
+curve). It has been shown that AUC is insensitive to class imbalance, creating 
+artificially inflated values inlfuenced by the majority class [@prati2011survey; 
+@wei2013role]. It is unclear how simple data level solutions to class imbalance, 
+such random under-sampling and random over-sampling affect TAD boundary prediction. 
+Likewise, a more composite metric such as Matthews Correlation Coefficient (MCC), 
+might provide more sensitive assessment of model performance. Thirdly, the relationship 
+between annotations and boundaries was quantified using proportions of overlaps. This 
+type of predictor ignores distances, which offers a much more spatially descriptive 
+feature space and could improve predictive performance. Lastly, it is unclear how *HiCfeat* 
+would perform on other cell lines and Hi-C data resolutions, giving *HiCfeat* a limited 
+application in TAD boundary prediction.
 
@@
 To assess the effect of CI on predictive performance, we first used the data with **No Sampling**, that is, the majority and minority classes were used as is.
-We evaluated three re-sampling techniques: **Random Under-Sampling (RUS)** - all of the data points from the minority class of the training set were used.
-Sampling without replacement was used to obtain the same number of data points from the majority class.
-
-3.
-**Random Over-Sampling (ROS)**: All of the data points from the majority class of the training set were used.
-Sampling with replacement from minority class was used to obtain the same number of data points as in the majority class.
-
-4.
-**SMOTE** (Synthetic Minority Over-Sampling Technique): This method incorporates both random under- and over-sampling [@chawla2002smote].
-Under-sampling is performed without replacement from the majority class.
-Over-sampling is performed by creating new synthetic observations using the minority class.
-The minority class is over-sampled by taking each minority class sample and introducing synthetic examples along the feature vectors joining any/all of the k=5 (default) minority class nearest neighbors.
-The SMOTE algorithm can have many variations in the weightinh of over- and under-sampling.
+We evaluated three re-sampling techniques.
+For **Random Under-Sampling (RUS)**, all of the data points from the minority class of the training set were used.
+Then sampling without replacement was used to obtain the same number of data points from the majority class.
+For **Random Over-Sampling (ROS)**, all of the data points from the majority class of the training set were used.
+Then, sampling with replacement from minority class was used to obtain the same number of data points as in the majority class.
+Lastly, for **SMOTE** (Synthetic Minority Over-Sampling Technique), both random under- and over-sampling was incorporated [@chawla2002smote].
+Under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the minority class.
+The minority class was over-sampled by taking each minority class sample and introducing synthetic examples along the feature vectors joining any/all of the k=5 (default) minority class nearest neighbors.
+The SMOTE algorithm can have many variations in the weighting of over- and under-sampling.
 In this study we restricted the algorithm to 100% over-sampling and 200% under-sampling.
@@
 Many genomic annotations, notably architectural proteins, tend to exhibit an extensive pattern of colocalization (correlation) [@van2014insulator].
-<!--This can contribute to high collinearity which can result in overfitting a predictive model.--> To measure the pairwise correlation of each cell line specific annotation, we used the Jaccard Index.
-The Jaccard Index measures the ratio of the number of intersecting base pairs between two sets to the number of base pairs in the union, subtracted by the intersection [@favorov2012exploring].
-The quantity ranges from 0 to 1, where 0 represents no overlap (no correlation) and 1 represent complete overlap (complete correlation).
-
-In order to suitably reduce the feature space and prevent overfitting, we implemented recursive feature elimination to estimate the optimal number of necessary features to include in the model.
+To suitably reduce the feature space and prevent overfitting, we implemented recursive feature elimination to estimate the optimal number of necessary features to include in the model.
 The best performing subset was identified, ranging from 2 to the maximum number of features by powers of 2.
-We then aggregated the predictive importance of the union of the optimal set of features across chromosome using the mean decrease in node impurity.
-Hierarchical clustering was performed to obtained the most common and top ranked annotations responsible for TAD boundary prediction.
+We then aggregated the predictive importance of the union of the optimal set of features across chromosomes using the mean decrease in node impurity to determine the most common and top ranked annotations for predicting TAD boundaries.
 
@@
 
-By leveraging the enrichment of known annotations in our model, we established a *predicted TAD boundary region* as a collection of adjacent base pairs that were given a probability of 1 for being a potentially predicted TAD boundary.
+By leveraging the enrichment of top ranked annotations in our model, we established *predicted TAD boundary regions* as a collection of adjacent base pairs that were given a probability of 1 for being a potentially predicted TAD boundary.
 To guard against inflating the number of predicted TAD boundaries, we clustered the distances between the midpoints of the *predicted TAD boundary regions*.

### 2019-08-29 Manuscript/manuscript.Rmd
added k562 results to table 1

@@
 After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [@dixon2012topological; @sofueva2013cohesin]), we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, across each of the five resolutions respectively (Table 1).
-Similar numbers of TAD boundaries were found for the K562 cell line (not reported).
+Similar numbers of TAD boundaries were found for the K562 cell line.
 To account for the variability in boundary location due to varying resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1A).
@@
 
-| Resolution | Total number of called TADs | Total number of unique TAD boundaries | Average Class Imbalance (SD) |
-|:----------:|:---------------------------:|:-------------------------------------:|:----------------------------:|
-|5 kb        |8043	                       | 16133                                 | 0.06 (0.02)                  |
-|10 kb	     |7650	                       | 14824                                 | 0.10 (0.01)                  |
-|25 kb	     |4208	                       | 8081                                  | 0.14 (0.01)                  |   
-|50 kb	     |1772	                       | 3560	                                 | 0.12 (0.01)                  |
-|100 kb	     |444	                         | 919	                                 | 0.06 (0.01)                  |    
-Table: Domain data and class imbalance summaries across resolutions for GM12878.
+| Resolution | Total number of called TADs | Total number of unique TAD boundaries | Average Class Imbalance ($\pm$ SD) |
+|:----------:|:---------------------------:|:-------------------------------------:|:----------------------------------:|
+|5 kb        |8043 (4750)                  | 16133 (9314)                          | 0.06 $\pm$ 0.02 (0.04 $\pm$ 0.02)  |
+|10 kb	     |7650 (5796) 	               | 14824 (10881)                         | 0.10 $\pm$ 0.01 (0.08 $\pm$ 0.02)  |
+|25 kb	     |4208 (3675)                  | 8081 (6923)                           | 0.14 $\pm$ 0.01 (0.12 $\pm$ 0.01)  |   
+|50 kb	     |1772 (1617)	                 | 3560	(3197)                           | 0.12 $\pm$ 0.01 (0.11 $\pm$ 0.01)  |
+|100 kb	     |444	(399)                    | 919	(831)                            | 0.06 $\pm$ 0.01 (0.06 $\pm$ 0.01)  |    
+Table: Domain data and class imbalance summaries across resolutions for GM12878 (K562).
 
@@
 The CI was found to be invariant to resolution, remaining consistently low across chromosomes, with an averages of 0.06, 0.10, 0.14, 0.12, and 0.06 across each resolutions for GM12878 (Table 1).
-Similar class imbalances were found for the K562 cell line (not reported).
+Similar class imbalances were found for the K562 cell line.
 To account for such imbalance, we evaluated three re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries.

### 2019-08-29 Scripts/evaluating_model_performances_rf.Rmd
changed formatting of error bars

@@
 ggplot(all_rfperfs_mcc[all_rfperfs_mcc$CL=="GM12878",], aes(x=Resolution, y=MCC, color=Predictor, fill=Predictor, group=Predictor)) +
-     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
-                 position=position_dodge(.9), alpha=0.75) +
      geom_bar(stat="identity", position = position_dodge()) +
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.75,
+                 position=position_dodge(.9), alpha=0.75, color="black", size=1) +
      facet_grid(. ~ Resampling)+
@@
 ggplot(all_rfperfs_mcc[all_rfperfs_mcc$CL=="K562",], aes(x=Resolution, y=MCC, color=Predictor, fill=Predictor, group=Predictor)) +
-     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.5,
-                 position=position_dodge(.9), alpha=0.75) +
      geom_bar(stat="identity", position = position_dodge()) +
+     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=.75,
+                 position=position_dodge(.9), alpha=0.75, color="black", size=1) +
      facet_grid(. ~ Resampling)+

### 2019-08-29 Manuscript/manuscript.Rmd
Fix sampling methods

@@
 We evaluated three re-sampling techniques.
-For **Random Under-Sampling (RUS)**, all of the data points from the minority class of the training set were used.
-Then sampling without replacement was used to obtain the same number of data points from the majority class.
-For **Random Over-Sampling (ROS)**, all of the data points from the majority class of the training set were used.
-Then, sampling with replacement from minority class was used to obtain the same number of data points as in the majority class.
-Lastly, for **SMOTE** (Synthetic Minority Over-Sampling Technique), both random under- and over-sampling was incorporated [@chawla2002smote].
-Under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the minority class.
-The minority class was over-sampled by taking each minority class sample and introducing synthetic examples along the feature vectors joining any/all of the k=5 (default) minority class nearest neighbors.
-The SMOTE algorithm can have many variations in the weighting of over- and under-sampling.
-In this study we restricted the algorithm to 100% over-sampling and 200% under-sampling.
-That is, 1 new synthetic observation was to be created for each existing minority class data point, while 2 data points were simultaneously randomly selected from the majority class.
-This combination results in perfectly balanced classes.
-The *DMwR* R package was used to perform SMOTE (version 0.4.1).
-
-[??? Stopped here]
+For **Random Under-Sampling (RUS)**, the majority class was sampled without replacement to obtain the same number of data points in the minority class.
+For **Random Over-Sampling (ROS)**, the minority class was sampled with replacement to obtain the same number of data points in the majority class.
+For **SMOTE** (Synthetic Minority Over-Sampling Technique), under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the $k=5$ minority class nearest neighbors [@chawla2002smote] (implemented in the `DMwR` v.0.4.1 R package).
+We restricted the algorithm to 100% over-sampling and 200% under-sampling, which creates perfectly balanced classes.
 

### 2019-08-29 Manuscript/manuscript.Rmd
finish methods

@@
 
-Random forest classification models were built to compare model performances between combinations of data resolutions, predictor types, and re-sampling techniques.
-To reduce bias due to random dataset generation, 10-fold cross validation was used to tune the number of annotations, *p*, to consider at each node.
-The number of trees that were aggregated for each random forest model was set to the default, n=500.
-All random forest algorithms were implemented in R using the *caret* package version 6.0 [@kuhn2012caret].
+Random forest classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, predictor types, and re-sampling techniques.
+Ten-fold cross validation was used to tune the number of annotations, *p*, to consider at each node.
+[???
+Isn't it used for preventing overfitting?
+TBD] The number of trees that were aggregated for each random forest model was set to $n=500$.
+
 The performance of each model was compared using Matthews Correlation Coefficient (MCC), defined as <!--The MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
@@
 <!--Additional performance metrics including AUROC, accuracy, sensitivity, and specificity were [???
-are?] reported in the supplementary materials.
-[???
-Where is it?]-->
+are?] reported in the supplementary materials.-->
 
@@
 We then aggregated the predictive importance of the union of the optimal set of features across chromosomes using the mean decrease in node impurity to determine the most common and top ranked annotations for predicting TAD boundaries.
+[???
+TBD, at which stage it was done]
 
@@
 
-By leveraging the enrichment of top ranked annotations in our model, we established *predicted TAD boundary regions* as a collection of adjacent base pairs that were given a probability of 1 for being a potentially predicted TAD boundary.
-To guard against inflating the number of predicted TAD boundaries, we clustered the distances between the midpoints of the *predicted TAD boundary regions*.
+Using optimally trained models, we established *predicted TAD boundary regions* as a collection of adjacent bases predicted as TAD boundary with the probability of 1.
+[???
+Do not understand from here:] To guard against inflating the number of predicted TAD boundaries, we clustered the distances between the midpoints of the *predicted TAD boundary regions*.
 We then performed partitioning around mediods (PAM) to determine the *predicted TAD boundary region* that was most representative of the cluster.
 The midpoint, in this case a particular basepair, of the *predicted TAD boundary region* identified as the medoid was defined as a final *predicted TAD boundary*.
-This process was repeated throughout the chromosome-specific sections of the linear genome.
+[???
+To here.
+REWRITE!]
 

### 2019-08-30 Manuscript/manuscript.Rmd
intro edits

@@
 
-# INTRODUCTION
+# Introduction
 
-The advent of various genome-wide sequencing technologies, such as high-throughput conformation capture (notably Hi-C), have revealed the spatial organization of the human genome  [@lieberman2009comprehensive].
-Analyses have shown that the genome is folded into distinct compartments termed topologically associating domains (TADs) [@dixon2012topological].
-Given their high degree of conservation between cell types and species, it has been proposed that TADs represent the fundamental building blocks of organization, giving the genome its 3D structure [@rocha2015breaking].
-Studies have shown that changing the 3D structure of the DNA, causing disruptions in these domains, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @Flavahan2016; @song2017ctcf].
-Therefore, it has become increasingly important to be able to identify the key molecular drivers of the formation of TAD boundaries in order to further our understanding of the human genome.
+The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed the spatial organization of the human genome  [@lieberman2009comprehensive].
+The genome has been shown to form tight, compact folds in order to fit inside the nucleus.
+This folding does not occur randomly; in fact, the genome exhibits a hierarchical 3D structure [@dixon2012topological].
+Among this hierarchy are distict compartments where the genome folds and interacts with itself more frequently termed topologically associating domains (TADs).
+TADs have garnered much interest in recent years given that they are heavily linked to gene expression [@dixon2015chromatin].
+Moreover, changing the 3D structure of the DNA, causing disruptions in the boundaries that demarcate TADs, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @Flavahan2016; @song2017ctcf].
 It has been thought that the collection of particular functional genomic elements may contribute to the formation of TADs.
@@
 Likewise, chromatin has been shown to exhibit certain modifications at TAD boundaries, evidenced by the frequent observation of the H3K36me3 histone mark [@dixon2012topological].
-However, the growing number of publically available annotated genomic elements and there collinearity pose a significant problem for establishing methods robust enough to determine the most important epigenomic factors that contribute to TAD boudandary formation.
-Moreover, the plasticity of functional annotations make TAD boundary prediction a cell line specific problem [@wang2012widespread]
+
+## Exhisting problems and limitations
+
+A growing number of studies have proposed computational tools used to identify additional key molecular drivers of the formation of TAD boundaries.
+The classical approach is to build classification models that leverage the relationship between ChIP-seq genomic annotations and TAD boundary regions.
+However, the growing number of publically available annotated genomic elements, and there collinearity, pose a significant problem for establishing methods robust enough to determine the most important genomic factors that contribute to TAD boudandary formation.
+Likewise, it is unclear what the best method is for quantifying this relationship.
+Incorporating a distance measure has largely been ignored, but could offer a much more spatially descriptive feature space thereby improving predictive performance.
+
+Another key factor in these approaches becomes resolution.
+Resolution determines the bin sizes of the linear genome used to enumerate contacts caused by chromatin folding.
+Due to high sequencing cost, most available Hi-C datasets have relatively low resolution, in the kilobase range.
+This is in stark contrast to ChIP-seq experiments which annotate regions of the genome at hundreds of base pairs in resolution.
+However, simply increasing sequencing depth to obtain higher resolution could have unintended consequences since this could introduce sparsity in the number of contacts which TAD callers are often ill-equiped to handle [@cresswell2019spectraltad, @sexton2012three].
+It is unclear how varying levels of resolution affect the association between functional genomic annotations and TAD boundary regions.
+Increased resolution could also further exacerbate the class imbalance created from the proportionally much smaller number of TAD boundary regions compared to non-TAD boundary regions throughout the linear genome.
+Classifiers implemented on heavily imbalanced datasets are known to exhibit poor performances as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
+
+## Previous methods
+
+Recently, an L1-regularized multiple logistic regression model, called *HiCfeat*, 
+was developed to predict TAD boundaries using transcription factor binding sites 
+on GM12878 [@mourad2016computational].
 

### 2019-08-30 Manuscript/manuscript.Rmd
intro edits

@@
 Namely, the CCCTC-binding factor (CTCF) has been shown to be enriched at TAD boundaries [@ghirlando2016ctcf].
-Additional transcription factors including SMC1, SMC3, and RAD21 have also been shown to colocalize near TAD boundaries [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+Additional transcription factors including SMC1, SMC3, and RAD21 have also been shown to colocalize near TAD boundaries forming a cohesin ring under the proposed loop extrusion model [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
 Likewise, chromatin has been shown to exhibit certain modifications at TAD boundaries, evidenced by the frequent observation of the H3K36me3 histone mark [@dixon2012topological].
 
-## Exhisting problems and limitations
-
-A growing number of studies have proposed computational tools used to identify additional key molecular drivers of the formation of TAD boundaries.
+A growing number of studies have proposed computational tools used to identify the complete set of key molecular drivers of the formation of TAD boundaries.
 The classical approach is to build classification models that leverage the relationship between ChIP-seq genomic annotations and TAD boundary regions.
-However, the growing number of publically available annotated genomic elements, and there collinearity, pose a significant problem for establishing methods robust enough to determine the most important genomic factors that contribute to TAD boudandary formation.
-Likewise, it is unclear what the best method is for quantifying this relationship.
+A key factor in these approaches becomes resolution.
+Resolution determines the bin sizes of the linear genome used to enumerate contacts caused by chromatin folding.
+Due to high sequencing cost, most available Hi-C datasets have relatively low resolution, in the kilobase range.
+This is in stark contrast to ChIP-seq experiments which annotate regions of the genome at hundreds of base pairs in resolution [???
+REF, Bonev 2017?].
+This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited our understanding of epigenomic regulation its potential link to chromatin architecture.
+However, simply increasing sequencing depth to obtain higher resolution could have unintended consequences since this could introduce sparsity in the number of contacts which TAD callers are often ill-equiped to handle [@cresswell2019spectraltad, @sexton2012three].
+Increased resolution could also further exacerbate the class imbalance created from the proportionally much smaller number of TAD boundary regions compared to non-TAD boundary regions throughout the linear genome.
+Classifiers implemented on heavily imbalanced datasets are known to exhibit poor performances as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
+It is unclear how simple data level solutions to class imbalance, such random under-sampling and random over-sampling affect TAD boundary prediction.
+Additionally, how relationships between genomic anntotations and bins of varying resolutions are quantified remains an open question.
 Incorporating a distance measure has largely been ignored, but could offer a much more spatially descriptive feature space thereby improving predictive performance.
 
-Another key factor in these approaches becomes resolution.
-Resolution determines the bin sizes of the linear genome used to enumerate contacts caused by chromatin folding.
-Due to high sequencing cost, most available Hi-C datasets have relatively low resolution, in the kilobase range.
-This is in stark contrast to ChIP-seq experiments which annotate regions of the genome at hundreds of base pairs in resolution.
-However, simply increasing sequencing depth to obtain higher resolution could have unintended consequences since this could introduce sparsity in the number of contacts which TAD callers are often ill-equiped to handle [@cresswell2019spectraltad, @sexton2012three].
-It is unclear how varying levels of resolution affect the association between functional genomic annotations and TAD boundary regions.
-Increased resolution could also further exacerbate the class imbalance created from the proportionally much smaller number of TAD boundary regions compared to non-TAD boundary regions throughout the linear genome.
-Classifiers implemented on heavily imbalanced datasets are known to exhibit poor performances as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
-
-## Previous methods
-
 Recently, an L1-regularized multiple logistic regression model, called *HiCfeat*, 
-was developed to predict TAD boundaries using transcription factor binding sites 
+was developed to predict TAD boundaries using transcription factor binding sites (TFBS) 
 on GM12878 [@mourad2016computational].
-
-## PROBLEMS AND LIMITATIONS
-
-The distinct patterns in epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches toward TAD boundary prediction  <!--[@dixon2015chromatin; @di2017novo]-->.
-Currently, classification models have been used to draw associations between these functional annotations and genomic regions that include TAD boundaries.
-However, many key characteristics of 3D genomic data remain unexplored, potentially limiting the performance of predictive modeling.
-
-First, the use of different levels of association between TAD boundary regions and genomic features as predictors remain underexplored.
-These associations are termed predictor-types and make up the feature space of classifiers.
-Counts of overlaps (**overlap count**, OC) is the most commonly used type of association as it simply counts the total number of peaks defining a genomic annotation that are inside a given TAD boundary region.
-Percents of overlaps (**overlap percent**, OP) represents a more precise measure of association as it considers the proportion of overlap between a genomic annotation and a boundary region.
-However, the distance between boundary regions and genomic annotations are currently unexplored.
-This association allows for quantifying the spatial relationship between genomic elements and boundary regions.
-We hypothesize that the inclusion of this type of association will correspond with more accurate identification of functional genomic elements association with TAD boundary formation.
-
-Secondly, the minority of TAD boundaries as compared with the rest of the genome creates proportionally small TAD boundary regions versus non-TAD boundary regions.
-These boundary regions make up the minority class, while the non-boundary regions make up the remaining majority class.
-The large disparity is sizes between minority and majority classes creates imbalanced data, as can be characterized by the *class imbalance* (CI).
-Here, CI is defined as the ratio of the set minority class observations to the sum of both sets of minority and majority class observations.
-That is, CI is bounded by 0 and 0.50.
-A dataset is considered balanced if CI $\approx$ 0.50, and imbalanced as CI approaches 0.
-Classifiers implemented on heavily imbalanced datasets are known to exhibit poor performances as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
-We hypothesize that the implementation of novel data resampling techniques will significantly improve model performance.
-Futhermore, the choice of performance metric can mask the poor performance of models implemented on imbalanced data.
-It has been shown that conventional metrics such as AUC and accuracy are insensitive to class imbalance, creating artificially inflated values influenced by the majority class [@prati2011survey; @wei2013role].
-Therefore, we hypothesize that a more composite metric such as Matthews Correlation Coefficient (MCC), might provide more sensitive assessment of model performance, given that it penalizes for both false positives and false negatives.
-
-Thirdly, TAD boundary location is known to be heavily influenced by the resolution of the subsequent Hi-C interaction matrix [@sexton2012three].
-Higher resolutions require a larger number of mapped reads, thereby creating larger data matrices, increasing computation time.
-However, the increased resolution available in newer datasets has highlighted the existence of a hierarchical structure of TADs inside other TADs [@pal2019hi].
-It is unclear how varying levels of resolution affect the association between functional genomic annotations and TAD boundary regions.
-<!--[link these two paragraphs]-->
-<!--[Paragraph about disconnect between Hi-C and epigenomic data] 
-Despite the success of Hi-C technologies in revealing the high-order levels of genome organization (chromosome territories, A/B compartments, TADs, sub-TADs, chromatin loops), resolution of Hi-C data (~750kb [???
-REF, Bonev 2017?]) remains well below resolution of epigenomic assays (hundredths of bases for ChIP-seq).
-One of the key missing pieces to connect 3D genome architecture to transcription has been the inability of Hi-C to attain the resolution necessary to discern gene-level features of chromatin.
-This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited our understanding of epigenomic regulation of gene expression and its potential link to chromatin architecture.
-Although computational [???
-REFS?](Zhang et al., “HiCPlus.”, Carron et al., “Boost-HiC.”) and technological [@Hsieh:2019aa][@Ma:1998aa][@Belaghzal2017] methods for enhancing resolution of Hi-C data started to appear, they [???
-remains to write about their pitfalls].
-One aim of this study is to predict the location of TAD boundaries on a scale comparable to epigenomic assays.
-For this, we developed a model trained on a relatively coarse Hi-C data for predicting 3D features (TAD boundaries) from 1D data (epigenomic datasets).-->
-
-## PREVIOUS METHODS
-
-<!--[still revising]-->
-Recently, an L1-regularized multiple logistic regression model, called *HiCfeat*, 
-was developed to predict TAD boundaries using transcription factor binding sites 
-on GM12878 [@mourad2016computational]. Based on a 1 kb binned genomic data matrix 
-and 20 kb flanked TAD boundaries, the model was trained using proportions of 
-overlaps between ChiP-seq peak defined functional element coordinates and genomic 
-bins. However, several problems exist with this study. First, many transcription 
-factors are known to colocalize, and therefore exhibit high correlations. Given 
-a group of features that are highly correlated, L1-regularization tends to pick 
-only one of them, while shrinking the others to zero [@zou2005regularization]. 
-Here, ensemble learning techniques could offer a more robust method toward 
-identifying  annotations associated with TAD boudaries. Likewise, it is unclear 
-how other sets of epigenomic features affect prediction, including chromatin state 
-segmentations and histone modifications. Secondly, the class imbalance issue was 
-not addressed prior to modelling. Instead, model performance was evaluated using 
-ROC (receiver operating characteristic) curves and subsequent AUC (area under the 
-curve). It has been shown that AUC is insensitive to class imbalance, creating 
-artificially inflated values inlfuenced by the majority class [@prati2011survey; 
-@wei2013role]. It is unclear how simple data level solutions to class imbalance, 
-such random under-sampling and random over-sampling affect TAD boundary prediction. 
-Likewise, a more composite metric such as Matthews Correlation Coefficient (MCC), 
-might provide more sensitive assessment of model performance. Thirdly, the relationship 
-between annotations and boundaries was quantified using proportions of overlaps. This 
-type of predictor ignores distances, which offers a much more spatially descriptive 
-feature space and could improve predictive performance. Lastly, it is unclear how *HiCfeat* 
-would perform on other cell lines and Hi-C data resolutions, giving *HiCfeat* a limited 
-application in TAD boundary prediction.
-
-Another method used an L2-based regularized linear model to discriminate between what was termed as "boundary-" and "TAD-segments" of the hESC cell line [@hong2017computational].
-
-A method devolped in 2015 used a tree based model to predict TAD boundary regions using 9 different cell line specific histone modifications, as well as consensus CTCF peaks, across 8 cell lines [@huang2015predicting].
+High resolution Hi-C data at 1 kb was used and percentage of overlap between regions defining TFBS and 1 kb bins was used for feature engineering.
+However, class imbalance was not adressed and, instead area under the receiver operating curve (AUROC) was used to evaluate model performance.
+This is problematic since it has been shown that AUC is insensitive to class imbalance, creating artificially inflated values inlfuenced by the majority class [@prati2011survey; @wei2013role].
+Two additional studies were proposed in 2015 and 2017 respectively, one using histone modifications in a Bayesian Additive Regression Trees (BART) model [@huang2015predicting] and the other using combined sets of TFBS, DNase hypersensitive sites, and histone modifications in an L2-based regularized linear model [@hong2017computational].
+Both used re-sampling techniques prior to modeling, with both implementing random under-sampling to balance TAD and non-TAD boundary regions.
+However, given the large disparity between the number of genomic regions labeled as containing a TAD boundary or not, performing random under-sampling alone is likely to be unstable and introduce bias.
+Also, it is unclear how other data level solutions compare to simple random under-sampling such as random over-sampling or a weighted combination of both random under- and over-sampling together.
+Furthermore, there was not a consensus in either resolution or feature engineering.
+The BART model was implemented on 5 kb Hi-C data using sequence read count between ChIP-seq data and 5 kb bins, while the L2-based regularized linear model was implemented on filtered TADs greater than 200 kb in length using the elemental count that appeared in each 150 kb bin.
 

### 2019-08-30 Manuscript/manuscript.Rmd
intro edits

@@
 A growing number of studies have proposed computational tools used to identify the complete set of key molecular drivers of the formation of TAD boundaries.
-The classical approach is to build classification models that leverage the relationship between ChIP-seq genomic annotations and TAD boundary regions.
+The classical approach is to build classification models that leverage the relationship between ChIP-seq genomic annotations and TAD boundary regions [@mourad2016computational; @huang2015predicting; @hong2017computational].
 A key factor in these approaches becomes resolution.
@@
 It is unclear how simple data level solutions to class imbalance, such random under-sampling and random over-sampling affect TAD boundary prediction.
-Additionally, how relationships between genomic anntotations and bins of varying resolutions are quantified remains an open question.
+Additionally, identifying the most informative feature engineering steps used to quantify the relationships between genomic anntotations and bins of varying resolutions remains an open question.
 Incorporating a distance measure has largely been ignored, but could offer a much more spatially descriptive feature space thereby improving predictive performance.
 
+<!--
 Recently, an L1-regularized multiple logistic regression model, called *HiCfeat*, 
@@
 The BART model was implemented on 5 kb Hi-C data using sequence read count between ChIP-seq data and 5 kb bins, while the L2-based regularized linear model was implemented on filtered TADs greater than 200 kb in length using the elemental count that appeared in each 150 kb bin.
+-->
 
-## OUR APPROACH
-
-In this study, we have developed a computational framework aimed at determining the optimal set of data level characteristics necessary for optimal prediction of TAD boundaries and identification of influential genomic annotations.
-These include the best combination of predictor type, resampling technique, and data resolution.
-We utilize random forest classification models built on Hi-C data from two cell lines, including GM12878 and K562, obtained at four different resolutions, including 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-For each cell line and resolution, we compared three predictor types, including counts, percents, and distances.
-Additionally, we compared three re-sampling techniques, including random under-sampling, random over-sampling, and a weighted combination of both referred to as Synthetic Minority Over-sampling Technique (SMOTE).
-Model performances were evaluated and compared using Matthews Correlation Coefficient (MCC).
-We performed 10-fold cross-validation for parameter tuning and to guard against over-fitting.
-We found that the optimally built cell line specific model is one implemented using distance type predictors, with SMOTE resampling, at the 10-kb data resolution.
-We also determined that simply including transcription factor binding sites was necessary for optimal performance.
-The inclusion of chromatin states and histone modifications was found to induce noise into the model.
-Specifically, we found that the transcription factors CTCF, ZNF143, RAD21, and SMC3 exhibited high predictive importances, confirming there involvement in TAD boundary formation.
-We then aimed to evaluate the cell line specificity of TAD boundaries by validating our optimally built models across cell lines.
-We found that models built and validated on the same cell line outperformed models that were validated across cell lines, confirming the cell line specific nature and plasticity of TAD boundaries and functional genomic annotations respectively.
-<!--[add conclusion from results of predicting finer bins]-->
+To date, there has yet to be established a unified approach toward TAD boundary prediction.
+Therefore, in this study we first developed a computational framework aimed at determining the set of data level characteristics necessary for optimal TAD boundary prediction.
+We assessed the Matthews Correlation Coefficient (MCC) of 10-fold cross-validated random forest classifiers with different combinations of model inputs consisting of vary data resolutions, re-sampling techniques, and feature engineering steps.
+We showed that 10 kb resolution data, combined with both random over- and under-sampling, and a feature space composed of distances between ChIP-seq annotations and genomic bins yielded the best model performances.
+We showed that our optimally built model was able to identify known architectural proteins CTCF, RAD21, SMC3, and ZNF143 as exhibiting high predictive importance, confirming their biological functionality near TAD boundaries.
+We then aimed to use our optimally built model to more precisely predict the location of TAD boundaries at base pair resolution.
+We showed that, compared to TAD boundaries identified by a TAD caller, these top ranked transcription factors were much more enriched near the predicted TAD boundaries identified by our model indicating much more precise locations throughout the linear genome.
+This improved precision in TAD boundary location can provide insight into the role that epigenomics has on the spatial architecture of the human genome
 

### 2019-08-30 Manuscript/manuscript.Rmd
grammar edit

@@
 It is unclear how simple data level solutions to class imbalance, such random under-sampling and random over-sampling affect TAD boundary prediction.
-Additionally, identifying the most informative feature engineering steps used to quantify the relationships between genomic anntotations and bins of varying resolutions remains an open question.
+Additionally, identifying the most informative feature engineering steps used to quantify the relationships between genomic annotations and bins of varying resolutions remains an open question.
 Incorporating a distance measure has largely been ignored, but could offer a much more spatially descriptive feature space thereby improving predictive performance.

### 2019-08-31 Manuscript/manuscript.Rmd
edits

@@
 Namely, the CCCTC-binding factor (CTCF) has been shown to be enriched at TAD boundaries [@ghirlando2016ctcf].
-Additional transcription factors including SMC1, SMC3, and RAD21 have also been shown to colocalize near TAD boundaries forming a cohesin ring under the proposed loop extrusion model [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+Additional transcription factors including SMC1, SMC3, and RAD21 have also been shown to colocalize near TAD boundaries forming a cohesin ring under the proposed loop extrusion model, whereby loops are formed during interphase [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
 Likewise, chromatin has been shown to exhibit certain modifications at TAD boundaries, evidenced by the frequent observation of the H3K36me3 histone mark [@dixon2012topological].
+The growing number of publically available genomic annotation data and their distinct patterns prompt the use of computational approaches toward TAD boundary prediction.
 
-A growing number of studies have proposed computational tools used to identify the complete set of key molecular drivers of the formation of TAD boundaries.
-The classical approach is to build classification models that leverage the relationship between ChIP-seq genomic annotations and TAD boundary regions [@mourad2016computational; @huang2015predicting; @hong2017computational].
+The classical approach is to build classification models that leverage the relationship between ChIP-seq genomic annotations and TAD boundary regions <!--[@mourad2016computational; @huang2015predicting; @hong2017computational]-->.
 A key factor in these approaches becomes resolution.
 Resolution determines the bin sizes of the linear genome used to enumerate contacts caused by chromatin folding.
-Due to high sequencing cost, most available Hi-C datasets have relatively low resolution, in the kilobase range.
+Due to high sequencing cost, most available Hi-C datasets have relatively low resolution, in the hundreds of kilobase range.
 This is in stark contrast to ChIP-seq experiments which annotate regions of the genome at hundreds of base pairs in resolution [???
 REF, Bonev 2017?].
-This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited our understanding of epigenomic regulation its potential link to chromatin architecture.
+This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited our understanding of epigenomic regulation and its potential link to chromatin architecture.
 However, simply increasing sequencing depth to obtain higher resolution could have unintended consequences since this could introduce sparsity in the number of contacts which TAD callers are often ill-equiped to handle [@cresswell2019spectraltad, @sexton2012three].
@@
 Classifiers implemented on heavily imbalanced datasets are known to exhibit poor performances as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
-It is unclear how simple data level solutions to class imbalance, such random under-sampling and random over-sampling affect TAD boundary prediction.
 Additionally, identifying the most informative feature engineering steps used to quantify the relationships between genomic annotations and bins of varying resolutions remains an open question.
 Incorporating a distance measure has largely been ignored, but could offer a much more spatially descriptive feature space thereby improving predictive performance.
+
+A method developed by Mourad et al [@mourad2016computational], called *HiCFeat*, used the percentage of overlap between several ChIP-seq defined transcription factor binding site (TFBS) regions and 1 kb genomic bins to build an L1-regularized multiple logistic regression model to predict TAD boundary regions.
+However, class imbalance was not addressed and instead, model performance was evaluated using area under the receiver operating characteristic curve (AUROC) which is known to be insensitive to class imbalance, creating artificially inflated values influenced by the majority class [@prati2011survey; @wei2013role].
+<!--A more appropriate evaluation tool to consider would be a composite metric such as Matthews Correlation Coefficient (MCC), which penalizes for both false positives and false negatives.--> Furthermore, by only considering percentage of overlap in defining the feature space, *HiCFeat* is limited in its granularity given that many regions on the linear genome will not be overlapped with any transcription factors, resulting in a zero inflated model.
+This, likely being further exacerbated by the class imbalance.
+Two additional studies were proposed in 2015 and 2017 respectively, one using histone modifications in a Bayesian Additive Regression Trees (BART) model [@huang2015predicting] and the other using combined sets of TFBS, DNase hypersensitive sites, and histone modifications together in an L2-based regularized linear model [@hong2017computational].
+The BART model was built on relatively high resolution Hi-C data at 5 kb, while the L2-regularized model used 200 kb resolution Hi-C data.
+Both methods addressed class imbalance by performing random under-sampling (RUS).
+However, given the large disparity between the number of TAD vs non-TAD boundary regions, performing random under-sampling alone is likely to be unstable and introduce bias.
+Also, it is unclear how other data level solutions compare to simple random under-sampling such as random over-sampling or a weighted combination of both random under- and over-sampling together.
+There was also a consensus on feature engineering where both methods used the elemental read count that appeared in each bin to describe the relationship between ChIP-seq annotations and genomic regions.
 

### 2019-08-31 Manuscript/manuscript.Rmd
intro edits

@@
 However, class imbalance was not addressed and instead, model performance was evaluated using area under the receiver operating characteristic curve (AUROC) which is known to be insensitive to class imbalance, creating artificially inflated values influenced by the majority class [@prati2011survey; @wei2013role].
-<!--A more appropriate evaluation tool to consider would be a composite metric such as Matthews Correlation Coefficient (MCC), which penalizes for both false positives and false negatives.--> Furthermore, by only considering percentage of overlap in defining the feature space, *HiCFeat* is limited in its granularity given that many regions on the linear genome will not be overlapped with any transcription factors, resulting in a zero inflated model.
+<!--A more appropriate evaluation tool to consider would be a composite metric such as Matthews Correlation Coefficient (MCC), which penalizes for both false positives and false negatives.--> Furthermore, by only considering the percentage of overlap in defining the feature space, *HiCFeat* is limited in its granularity given that many regions on the linear genome will not be overlapped with any genomic annotations, resulting in a zero inflated model.
 This, likely being further exacerbated by the class imbalance.
-Two additional studies were proposed in 2015 and 2017 respectively, one using histone modifications in a Bayesian Additive Regression Trees (BART) model [@huang2015predicting] and the other using combined sets of TFBS, DNase hypersensitive sites, and histone modifications together in an L2-based regularized linear model [@hong2017computational].
+Two additional studies were proposed in 2015 and 2017 respectively, one using histone modifications in a Bayesian Additive Regression Trees (BART) model [@huang2015predicting] and the other using combined sets of TFBS, DNase I hypersensitive sites, and histone modifications together in an L2-based regularized linear model [@hong2017computational].
 The BART model was built on relatively high resolution Hi-C data at 5 kb, while the L2-regularized model used 200 kb resolution Hi-C data.
-Both methods addressed class imbalance by performing random under-sampling (RUS).
-However, given the large disparity between the number of TAD vs non-TAD boundary regions, performing random under-sampling alone is likely to be unstable and introduce bias.
+Both methods addressed class imbalance by performing random under-sampling (RUS), and used the elemental read count that appeared in each bin to describe the relationship between ChIP-seq annotations and genomic regions.
+Firstly, given the large disparity between the number of TAD vs non-TAD boundary regions, performing random under-sampling alone is likely to be unstable and introduce bias.
 Also, it is unclear how other data level solutions compare to simple random under-sampling such as random over-sampling or a weighted combination of both random under- and over-sampling together.
-There was also a consensus on feature engineering where both methods used the elemental read count that appeared in each bin to describe the relationship between ChIP-seq annotations and genomic regions.
+Secondly, using read count overlap as the feature space suffers from similar limitations as the percentage of overlap.
+Moreover, it is unclear how either of these feature engineering steps compare to enumerating the distance in basepairs between ChIP-seq annotations and genomic bins in TAD boundary prediction.
 
-<!--
-Recently, an L1-regularized multiple logistic regression model, called *HiCfeat*, 
-was developed to predict TAD boundaries using transcription factor binding sites (TFBS) 
-on GM12878 [@mourad2016computational].
-High resolution Hi-C data at 1 kb was used and percentage of overlap between regions defining TFBS and 1 kb bins was used for feature engineering.
-However, class imbalance was not adressed and, instead area under the receiver operating curve (AUROC) was used to evaluate model performance.
-This is problematic since it has been shown that AUC is insensitive to class imbalance, creating artificially inflated values inlfuenced by the majority class [@prati2011survey; @wei2013role].
-Two additional studies were proposed in 2015 and 2017 respectively, one using histone modifications in a Bayesian Additive Regression Trees (BART) model [@huang2015predicting] and the other using combined sets of TFBS, DNase hypersensitive sites, and histone modifications in an L2-based regularized linear model [@hong2017computational].
-Both used re-sampling techniques prior to modeling, with both implementing random under-sampling to balance TAD and non-TAD boundary regions.
-However, given the large disparity between the number of genomic regions labeled as containing a TAD boundary or not, performing random under-sampling alone is likely to be unstable and introduce bias.
-Also, it is unclear how other data level solutions compare to simple random under-sampling such as random over-sampling or a weighted combination of both random under- and over-sampling together.
-Furthermore, there was not a consensus in either resolution or feature engineering.
-The BART model was implemented on 5 kb Hi-C data using sequence read count between ChIP-seq data and 5 kb bins, while the L2-based regularized linear model was implemented on filtered TADs greater than 200 kb in length using the elemental count that appeared in each 150 kb bin.
--->
-
-To date, there has yet to be established a unified approach toward TAD boundary prediction.
-Therefore, in this study we first developed a computational framework aimed at determining the set of data level characteristics necessary for optimal TAD boundary prediction.
+Therefore, given the many pitfalls encountered by previous methods we set out to establish a unified approach toward TAD boundary prediction.
+In this study we first developed a computational framework aimed at determining the set of data level characteristics necessary for optimal TAD boundary prediction.
 We assessed the Matthews Correlation Coefficient (MCC) of 10-fold cross-validated random forest classifiers with different combinations of model inputs consisting of vary data resolutions, re-sampling techniques, and feature engineering steps.
-We showed that 10 kb resolution data, combined with both random over- and under-sampling, and a feature space composed of distances between ChIP-seq annotations and genomic bins yielded the best model performances.
+We showed that 10 kb resolution data, combined with both random over- and under-sampling, and a feature space composed of distances between ChIP-seq annotations and genomic bins yielded the best model performances for TAD boundary prediction.
 We showed that our optimally built model was able to identify known architectural proteins CTCF, RAD21, SMC3, and ZNF143 as exhibiting high predictive importance, confirming their biological functionality near TAD boundaries.
@@
 We showed that, compared to TAD boundaries identified by a TAD caller, these top ranked transcription factors were much more enriched near the predicted TAD boundaries identified by our model indicating much more precise locations throughout the linear genome.
-This improved precision in TAD boundary location can provide insight into the role that epigenomics has on the spatial architecture of the human genome
+This improved precision in TAD boundary location can provide insight into the role that epigenomics has on the spatial architecture of the human genome.
 

### 2019-08-31 Manuscript/manuscript.Rmd
First paragraph edits

@@
 
-The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed the spatial organization of the human genome  [@lieberman2009comprehensive].
+The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed the spatial organization of the human genome [???
+So what?] [@lieberman2009comprehensive].
 The genome has been shown to form tight, compact folds in order to fit inside the nucleus.
-This folding does not occur randomly; in fact, the genome exhibits a hierarchical 3D structure [@dixon2012topological].
-Among this hierarchy are distict compartments where the genome folds and interacts with itself more frequently termed topologically associating domains (TADs).
-TADs have garnered much interest in recent years given that they are heavily linked to gene expression [@dixon2015chromatin].
-Moreover, changing the 3D structure of the DNA, causing disruptions in the boundaries that demarcate TADs, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @Flavahan2016; @song2017ctcf].
+[???
+So what?] This folding does not occur randomly; in fact, the genome exhibits a hierarchical 3D structure [@dixon2012topological].
+[???
+So what?] [???
+All the above is pointless babbling, rewrite]
+
+[??? This is very vague:  gene expression regulation [@dixon2015chromatin]
+
+Among them, Topologically Associated Domains [???
+THIS IS THE RIGHT SPELLING!] (TADs) have attracted most attention given their prominent role in constraining enhancer-promoter communication [@Lupianez:2015aa; @Franke:2016aa] and might be related to genome stability [@Canela:2017aa].
+Disruption of TAD boundaries can lead to developmental disorders [@lupianez2016breaking], cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@Sun:2018aa; @Meaburn:2007aa].
+[???
+This level of clarity is required]
+
 It has been thought that the collection of particular functional genomic elements may contribute to the formation of TADs.

### 2019-09-02 Manuscript/manuscript.Rmd
intro edits

--- 2019-08-31 Manuscript/manuscript.Rmd
@@
 
-The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed the spatial organization of the human genome  [@lieberman2009comprehensive].
-The genome has been shown to form tight, compact folds in order to fit inside the nucleus.
-This folding does not occur randomly; in fact, the genome exhibits a hierarchical 3D structure [@dixon2012topological].
-Among this hierarchy are distict compartments where the genome folds and interacts with itself more frequently termed topologically associating domains (TADs).
-TADs have garnered much interest in recent years given that they are heavily linked to gene expression [@dixon2015chromatin].
-Moreover, changing the 3D structure of the DNA, causing disruptions in the boundaries that demarcate TADs, can lead to adverse outcomes and diseases like cancer [@hnisz2016activation; @Flavahan2016; @song2017ctcf].
-It has been thought that the collection of particular functional genomic elements may contribute to the formation of TADs.
-Namely, the CCCTC-binding factor (CTCF) has been shown to be enriched at TAD boundaries [@ghirlando2016ctcf].
-Additional transcription factors including SMC1, SMC3, and RAD21 have also been shown to colocalize near TAD boundaries forming a cohesin ring under the proposed loop extrusion model, whereby loops are formed during interphase [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
-Likewise, chromatin has been shown to exhibit certain modifications at TAD boundaries, evidenced by the frequent observation of the H3K36me3 histone mark [@dixon2012topological].
-The growing number of publically available genomic annotation data and their distinct patterns prompt the use of computational approaches toward TAD boundary prediction.
+The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed important 3-dimensional (3D) spatial constructs within the human genome such as loops [@rao20143d], Topologically Associated Domains (TADs) [@nora2012spatial;@dixon2012topological], and A/B compartments [@lieberman2009comprehensive].
+Among these, TADs represent regions on the linear genome, at megabase scale, that are highly self-interacting.
+Emerging evidence has linked TADs to critical roles in cell dynamics like gene regulation and cell differentiation, an example being the mechanism by which enhancers loop to come into contact with distal promoters to initiate transcription within these domains [@Lupianez:2015aa; @Franke:2016aa].
+Likewise, disruption of TAD boundaries has been shown to lead to developmental disorders [@lupianez2016breaking], such as cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@Sun:2018aa; @Meaburn:2007aa].
+Therefore, identifying the location of TAD boundaries remains a top priority in our goal to understand the functionality of the human genome.
 
-The classical approach is to build classification models that leverage the relationship between ChIP-seq genomic annotations and TAD boundary regions <!--[@mourad2016computational; @huang2015predicting; @hong2017computational]-->.
-A key factor in these approaches becomes resolution.
+A key factor in locating TAD boundaries is Hi-C data "resolution".
 Resolution determines the bin sizes of the linear genome used to enumerate contacts caused by chromatin folding.
-Due to high sequencing cost, most available Hi-C datasets have relatively low resolution, in the hundreds of kilobase range.
-This is in stark contrast to ChIP-seq experiments which annotate regions of the genome at hundreds of base pairs in resolution [???
-REF, Bonev 2017?].
-This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited our understanding of epigenomic regulation and its potential link to chromatin architecture.
-However, simply increasing sequencing depth to obtain higher resolution could have unintended consequences since this could introduce sparsity in the number of contacts which TAD callers are often ill-equiped to handle [@cresswell2019spectraltad, @sexton2012three].
-Increased resolution could also further exacerbate the class imbalance created from the proportionally much smaller number of TAD boundary regions compared to non-TAD boundary regions throughout the linear genome.
-Classifiers implemented on heavily imbalanced datasets are known to exhibit poor performances as the learned model is biased towards the majority class [@lusa2010class; @chen2013influence; @jeni2013facing].
-Additionally, identifying the most informative feature engineering steps used to quantify the relationships between genomic annotations and bins of varying resolutions remains an open question.
-Incorporating a distance measure has largely been ignored, but could offer a much more spatially descriptive feature space thereby improving predictive performance.
+Lower resolutions contribute to larger bin sizes, which lead to variability in the location of TAD boundaries.
+Due to high sequencing costs, most available Hi-C datasets have relatively low resolution, ranging from 25 kb to 100 kb.
+To increase the resolution of Hi-C data requires a quadratic increase in the total sequencing depth [@schmitt2016genome].
+While these low resolution Hi-C datasets can be used to probe higher order genomic patterns such as A/B compartments, more refined resolutions are necessary to define sub-domains and the boundaries that demarcate them.
+Furthermore, even at its highest (750 bp [@bonev2017multiscale]), Hi-C sequencing resolution still remains well below the resolution of ChIP-Sequencing experiments used to annotate the genome, which ranges in the tens of base pairs.
+This resolution gap between 1D and 3D genomic maps can make it difficult to disentangle the role of additional factors related to TAD boundaries, thereby limiting our understanding of epigenomic regulation and its potential link to chromatin architecture.
+We hypothesize that, by leveraging genomic annotations--defined by high resolution ChIP-Seq data--known to be enriched at TAD boundaries, we may be able more precisely predict the locations of TAD boundaries on the linear genome.
 
+Several methods have been developed to predict TAD boundary location using genomic annotations.
+However, most ignore key characteristics of 3D genomic data that are detrimental to model performance.
 A method developed by Mourad et al [@mourad2016computational], called *HiCFeat*, used the percentage of overlap between several ChIP-seq defined transcription factor binding site (TFBS) regions and 1 kb genomic bins to build an L1-regularized multiple logistic regression model to predict TAD boundary regions.
-However, class imbalance was not addressed and instead, model performance was evaluated using area under the receiver operating characteristic curve (AUROC) which is known to be insensitive to class imbalance, creating artificially inflated values influenced by the majority class [@prati2011survey; @wei2013role].
+However, the high level of resolution is likely to introduce heavily imbalanced classes created from the proportionally much smaller number of TAD boundary regions compared to non-TAD boundary regions throughout the linear genome.
+*HiCFeat* did not the address class imbalance.
+Instead, model performance was evaluated using area under the receiver operating characteristic curve (AUROC) which is known to be insensitive to class imbalance, creating artificially inflated values influenced by the majority class [@prati2011survey; @wei2013role].
 <!--A more appropriate evaluation tool to consider would be a composite metric such as Matthews Correlation Coefficient (MCC), which penalizes for both false positives and false negatives.--> Furthermore, by only considering the percentage of overlap in defining the feature space, *HiCFeat* is limited in its granularity given that many regions on the linear genome will not be overlapped with any genomic annotations, resulting in a zero inflated model.
-This, likely being further exacerbated by the class imbalance.
-Two additional studies were proposed in 2015 and 2017 respectively, one using histone modifications in a Bayesian Additive Regression Trees (BART) model [@huang2015predicting] and the other using combined sets of TFBS, DNase I hypersensitive sites, and histone modifications together in an L2-based regularized linear model [@hong2017computational].
+<!--This, likely being further exacerbated by the class imbalance.--> Two additional studies were proposed in 2015 and 2017 respectively, one using histone modifications in a Bayesian Additive Regression Trees (BART) model [@huang2015predicting] and the other using combined sets of TFBS, DNase I hypersensitive sites, and histone modifications together in an L2-based regularized linear model [@hong2017computational].
 The BART model was built on relatively high resolution Hi-C data at 5 kb, while the L2-regularized model used 200 kb resolution Hi-C data.
@@
 This improved precision in TAD boundary location can provide insight into the role that epigenomics has on the spatial architecture of the human genome.
+
+<!--
+Extensive research using high resolution maps (ranging from 750 bp to 1 mb) have probed much of the aspects of 3D chromatin architecture identifying several epigenomic modifications associated with TAD boundaries [@rao20143d; @bonev2017multiscale].
+For instance, it is known that the CCCTC-binding factor (CTCF) is enriched at TAD boundaries acting as an insulator interfering with enhancer-promotor interactions [@ghirlando2016ctcf; @song2017ctcf; @ong2014ctcf].
+Additional transcription factors including SMC1, SMC3, and RAD21 have also been shown to colocalize near TAD boundaries forming a cohesin ring under the proposed loop extrusion model, whereby loops are formed during interphase [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+-->
 

### 2019-09-02 Manuscript/manuscript.Rmd
intro edits

@@
 Due to high sequencing costs, most available Hi-C datasets have relatively low resolution, ranging from 25 kb to 100 kb.
-To increase the resolution of Hi-C data requires a quadratic increase in the total sequencing depth [@schmitt2016genome].
+Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth, obtaining high resolution remains difficult [@schmitt2016genome].
 While these low resolution Hi-C datasets can be used to probe higher order genomic patterns such as A/B compartments, more refined resolutions are necessary to define sub-domains and the boundaries that demarcate them.
 Furthermore, even at its highest (750 bp [@bonev2017multiscale]), Hi-C sequencing resolution still remains well below the resolution of ChIP-Sequencing experiments used to annotate the genome, which ranges in the tens of base pairs.
-This resolution gap between 1D and 3D genomic maps can make it difficult to disentangle the role of additional factors related to TAD boundaries, thereby limiting our understanding of epigenomic regulation and its potential link to chromatin architecture.
-We hypothesize that, by leveraging genomic annotations--defined by high resolution ChIP-Seq data--known to be enriched at TAD boundaries, we may be able more precisely predict the locations of TAD boundaries on the linear genome.
+This resolution gap between 1D and 3D genomic maps can make it difficult to disentangle the role of genomic factors related to TAD boundaries, thereby limiting our understanding of epigenomic regulation and its potential link to chromatin architecture.
+We hypothesize that, by leveraging genomic annotations--defined by high resolution ChIP-Seq data--known to be enriched at TAD boundaries, we may be able more precisely predict the locations of TAD boundaries at higher resolutions.
 
@@
 A method developed by Mourad et al [@mourad2016computational], called *HiCFeat*, used the percentage of overlap between several ChIP-seq defined transcription factor binding site (TFBS) regions and 1 kb genomic bins to build an L1-regularized multiple logistic regression model to predict TAD boundary regions.
-However, the high level of resolution is likely to introduce heavily imbalanced classes created from the proportionally much smaller number of TAD boundary regions compared to non-TAD boundary regions throughout the linear genome.
+However, such high level of resolution is likely to introduce heavily imbalanced classes created from the proportionally much smaller number of TAD boundary regions compared to non-TAD boundary regions throughout the linear genome.
 *HiCFeat* did not the address class imbalance.
@@
 Firstly, given the large disparity between the number of TAD vs non-TAD boundary regions, performing random under-sampling alone is likely to be unstable and introduce bias.
-Also, it is unclear how other data level solutions compare to simple random under-sampling such as random over-sampling or a weighted combination of both random under- and over-sampling together.
+Also, it is unclear how other re-sampling solutions compare to simple random under-sampling such as random over-sampling or a weighted combination of both random under- and over-sampling together.
 Secondly, using read count overlap as the feature space suffers from similar limitations as the percentage of overlap.
-Moreover, it is unclear how either of these feature engineering steps compare to enumerating the distance in basepairs between ChIP-seq annotations and genomic bins in TAD boundary prediction.
+Moreover, it is unclear how either of these feature engineering steps compare to enumerating the distance in base pairs between ChIP-seq annotations and genomic bins in TAD boundary prediction, which offer a more spatial measure of association.
 
-Therefore, given the many pitfalls encountered by previous methods we set out to establish a unified approach toward TAD boundary prediction.
+Given the many pitfalls encountered by previous methods we set out to establish a unified approach toward TAD boundary prediction.
 In this study we first developed a computational framework aimed at determining the set of data level characteristics necessary for optimal TAD boundary prediction.
@@
 We then aimed to use our optimally built model to more precisely predict the location of TAD boundaries at base pair resolution.
-We showed that, compared to TAD boundaries identified by a TAD caller, these top ranked transcription factors were much more enriched near the predicted TAD boundaries identified by our model indicating much more precise locations throughout the linear genome.
+We showed that, compared to TAD boundaries identified by a TAD caller [@durand2016juicebox], these top ranked transcription factors were much more enriched near the predicted TAD boundaries identified by our model indicating much more precise locations throughout the linear genome.
 This improved precision in TAD boundary location can provide insight into the role that epigenomics has on the spatial architecture of the human genome.

### 2019-09-03 Manuscript/manuscript.Rmd
discussion edits

@@
 Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth, obtaining high resolution remains difficult [@schmitt2016genome].
-While these low resolution Hi-C datasets can be used to probe higher order genomic patterns such as A/B compartments, more refined resolutions are necessary to define sub-domains and the boundaries that demarcate them.
+While these low resolution Hi-C datasets can be used to probe higher order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define sub-domains and the boundaries that demarcate them.
 Furthermore, even at its highest (750 bp [@bonev2017multiscale]), Hi-C sequencing resolution still remains well below the resolution of ChIP-Sequencing experiments used to annotate the genome, which ranges in the tens of base pairs.
 This resolution gap between 1D and 3D genomic maps can make it difficult to disentangle the role of genomic factors related to TAD boundaries, thereby limiting our understanding of epigenomic regulation and its potential link to chromatin architecture.
-We hypothesize that, by leveraging genomic annotations--defined by high resolution ChIP-Seq data--known to be enriched at TAD boundaries, we may be able more precisely predict the locations of TAD boundaries at higher resolutions.
+We hypothesize that, by leveraging genomic annotations--defined by high resolution ChIP-Seq data--known to be enriched at TAD boundaries, we may be able more to precisely predict the locations of TAD boundaries at higher resolutions.
 
@@
 
-ChIP-seq assays offer much higher resolutions (often in the tens of bases) compared to Hi-C sequenced data, which can be in the hundreds of kilobases.
-This disparity in resolution can affect a TAD caller's ability to precisely locate TADs.[???
-This is for the introduction, justifying motives for your work]
-
 ![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17390000-18640000; GM12878).
@@
 
-# DISCUSSION
+# Discussion
 
-In this study we developed an ensemble framework to systematically compare model performances for different combinations of re-sampling and feature engineering techniques aimed at determining a consensus approach to predicting TAD boundary formation using genomic annotations.
-We provide direct comparisons of cell line specific random forest models built on a variety of different data dependent characteristics, including 4 contact matrix resolutions ($\{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$), 3 predictor-types ($\{\textit{OC}, \textit{OP}, \textit{Distance}\}$), and 4 re-sampling techniques ($\{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$), for both the GM12878 and K562 cell lines.
-[???
-Learn Markdown] [???
-What's the summary of your work?]
+In this study we developed an ensemble framework to systematically compare model performances for different combinations of Hi-C resolution, data re-sampling, and feature engineering techniques.
+By implementing our framework across multiple cell lines, we showed that there exists a consensus approach toward precise TAD boundary prediction.
+We showed that random forest classification models trained on domain data extracted from 10 kb resolution maps, using random over- and under-sampling to account for class imbalance, with a distance-type predictor space yield optimal model performances for both the GM12878 and K562 cell lines.
 
-The experiments derived from our ensemble framework provide a useful guide toward the exploration of chromatin organization, while highlighting the impact of both class imbalance and feature engineering in TAD boundary prediction.
-Using the framework we demonstrated that random forest models built on imbalanced data exhibited poor performance, regardless of cell line, resolution, or predictor type.
-In our framework, [???
-Too much "framework" mentioning] we opted to leave the test set as a completely untouched holdout set, only performing the re-sampling, and subsequent learning, on the training set.
-This was done so as to incur the least amount of bias and so that all conclusions could be made soley between model characteristics.
-As a result, we showed that Matthews Correlation Coefficient was much more sensitive to the imbalance present in the test set, compared to more popular metrics like AUROC, which attain artificially high values by correctly predicting majority class samples [???
-I don't see results for it].
-When comparing re-sampling techniques, we found that SMOTE re-sampling outperformed models built on both simple ROS or RUS, implying that, in fact, a combination of both random under-sampling and random over-sampling is preferred in TAD boundary prediction.
-Furthermore, the most improvement [???
-In what?] was seen when combining SMOTE resampling on distance-type features when building random forest classifiers.
-These two characteristics exhibited consistently better performance results across both the GM12878 and K562 cell lines.
-This confirmed our hypothesis that the most granular and spatially informative representation of the relationship between TAD boundaries and annotations resulted in the best performing model.
-
-When applying SMOTE re-sampling, with distance-type predictors, on transcription factor binding sites alone, we found that random forest classifiers performed better when compared to other annotation-specific models, including histone modifications and chromatin state segmentations.
-Likewise the performance of TFBS specific models was comparable to models with all annotations combined, across both cell line and resolution.
-This suggests that the majority of the key molecular drivers aiding in the formation of TAD boundaryies are transctiption factors, and that modifications at histone tails such as acetylation or methylation play less of a role.
-
-We also observed that, while the best set of data characteristics were consistent across resolutions, performances of classifiers built on said characteristics tended to decline as resolution decreased.
-For both cell lines, top performance was achieved at the 10 kb data resolution, while the worst performance was obtained at the 50 kb and 100 kb resolution for the GM12878 and K562 cell line respectively.
-This suggests that TAD boundary prediction is intimately related to the resolution that boundaries are called on.
-This result can be attributed to one of two factors in the scheme of our framework.
-First, at higher resolutions, by model construction genomic bins were smaller, thereby resulting in more accurate profiles for the genomic annotations [??
-Don't understand this sentence ??].
-Secondly, because we are mainly concerned with TAD boundaries, and not the hierarchical structure of domains as a whole, the sparsity of contact matrices at higher resolutions does not impair boundary prediction [??
-Doesn't this contradict your results about low resolution causing worse boundary prediction ??].
-Conversely, lower resolutions imply larger bin windows and lead to less specificity in boundary location on the linear genome, resulting in worse performances.
-Given the trend in performances across resolution, future research is necessary in determining the optimal resolution to use when predicting TAD boundaries [??
-Might want to qualify the statement in results about 10kb data being best by saying that it only applies to your data ??].
-[???
-This paragraph is a mess]
-
-Given the formulation of our framework, we were not able to make direct comparisons between cell lines.
-This was due to the fact that we opted to use cell line specific annotations, and there existed some annotations that were available on the K562 cell line that were not available to GM12878, and vice versa.
-[???
-Did they provide additional advantage?] However, we were able to confirm that final models built on the optimal set of data characteristics identified consistent and well known proteins related to the 3D structure of chromatin, for both cell lines.
-Our results indicated that the zinc finger protein CTCF, as well components of the cohesin complex, SMC3 and RAD21, were found to be the key molecular drivers most predictive of TAD boundary formation, consistent across cell line and resolution.
-In addition, models derived from our framework recognized known mediaters of long range enhancer-promoter interactions, the ZNF143 and YY1 transcription factors, as being highly predictive of TAD boundaries.
-
-In summary, we have shown that TAD boundary prediction is a multi-faceted problem composed of many data irregularities and characteristics that previous model have failed to address.
-We have shown that our proposed framework suitably addresses each of these components, while also providing the optimal considerations to make in an effort to build consensus classifiers used to predict TAD boundary formation [??
-formation or location.
-Formation implies some temporal element ??] from functional genomic annotations.
-Given the stability of our results, this opens up the possibility of widening our framework to include a broader set of classifiers, cell lines, and Hi-C contact matix resolutions that will inevitably assist us in gaining a better understanding of the mechanisms associated with the architecture of the human genome.
+Previous studies tended to focus only on specific sets of genomic annotations including chromatin states, histone modifications, or transcription factor binding sites alone.
+Using our framework, we were able to conclude that simply building random forest classifiers on cell line specific transcription factor binding sites alone can yield near optimal model performance, thereby significantly reducing the feature space and computational complexity of the model.
+Specifically, we found that the CCCTC-binding factor (CTCF) and cohesin complexes (RAD21 and SMC3) were the most important features of TAD boundary prediction, confirming their enrichment at TAD boundaries as part of the loop extrusion model [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+Likewise, we found the the zinc-finger protein ZNF143 was also given high predictive importance.
+This confirmed the known role of ZNF143 as a chromatin-looping factor that contributes to the architectural foundation of the genome by providing sequence specificity at promoters connected with distal regulatory elements [@bailey2015znf143;@gonzalez2017znf143].
 

### 2019-09-03 Manuscript/manuscript.Rmd
discussion edits

@@
 
-In this study we developed an ensemble framework to systematically compare model performances for different combinations of Hi-C resolution, data re-sampling, and feature engineering techniques.
+In this study we developed an ensemble framework to systematically compare the effects of different combinations of Hi-C resolution, data re-sampling, and feature engineering techniques on the performance of models aimed at TAD boundary prediction.
 By implementing our framework across multiple cell lines, we showed that there exists a consensus approach toward precise TAD boundary prediction.
-We showed that random forest classification models trained on domain data extracted from 10 kb resolution maps, using random over- and under-sampling to account for class imbalance, with a distance-type predictor space yield optimal model performances for both the GM12878 and K562 cell lines.
+We showed that random forest classification models trained on domain data extracted from 10 kb resolution maps, using random over- and under-sampling to account for class imbalance, with a distance-type predictor space yielded optimal model performances for both the GM12878 and K562 cell lines.
 
-Previous studies tended to focus only on specific sets of genomic annotations including chromatin states, histone modifications, or transcription factor binding sites alone.
-Using our framework, we were able to conclude that simply building random forest classifiers on cell line specific transcription factor binding sites alone can yield near optimal model performance, thereby significantly reducing the feature space and computational complexity of the model.
+Previous studies tended to focus only on specific sets of genomic annotations including chromatin states, histone modifications, or transcription factor binding sites (TFBS) alone.
+Using our framework, we were able to conclude that simply building random forest classifiers only on cell line specific TFBS can yield near optimal model performance, thereby significantly reducing the feature space and computational complexity of the model.
 Specifically, we found that the CCCTC-binding factor (CTCF) and cohesin complexes (RAD21 and SMC3) were the most important features of TAD boundary prediction, confirming their enrichment at TAD boundaries as part of the loop extrusion model [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
 Likewise, we found the the zinc-finger protein ZNF143 was also given high predictive importance.
-This confirmed the known role of ZNF143 as a chromatin-looping factor that contributes to the architectural foundation of the genome by providing sequence specificity at promoters connected with distal regulatory elements [@bailey2015znf143;@gonzalez2017znf143].
+This confirmed the known role of ZNF143 as a chromatin-looping factor that contributes to the structural foundation of the genome by providing sequence specificity at promoters connected with distal regulatory elements [@bailey2015znf143;@gonzalez2017znf143].
+
+By leveraging the enrichment of these architectural proteins we were able to more precisely identify TAD boundaries at a much more refined resolution.
+To do so, we evaluated the ChIP-Seq signal strength between the CTCF, RAD21, SMC3, and ZNF143 transcription factors and a 10 kb flanked window of predicted TAD boundaries identified by our optimally built random forest model.
+We showed that the genomic signals for each TFBS was much more consolidated near the center of our flanked predicted TAD boundary then the flanked boundary identified by the ARROWHEAD TAD caller.
+We also evaluated the distal relationships between the same architectural proteins and found that they were statistically significantly closer in base pair distance to our predicted TAD boundaries, than to ones identified by ARROWHEAD.
+
+In summary, we have shown that TAD boundary prediction is a multi-faceted problem composed of many data irregularities and characteristics that previous methods have failed to address.
+Through our ensemble framework, we provide a useful guide toward the exploration of chromatin organization, while highlighting the impact of data resolution, class imbalance, and feature engineering in TAD boundary prediction.
+Lastly, by building models using known enriched transcription factors, we were able to bridge the resolution gap between ChIP-Seq and Hi-C sequencing for more precise TAD boundary prediction.
+
+<!--
+The two proteins differ in that YY1 preferentially
+occupies interacting enhancers and promoters, whereas CTCF
+preferentially occupies sites distal from these regulatory elements that tend to form larger loops and participate in insulation.
+Deletion of YY1 binding sites or depletion of YY1 can disrupt
+enhancer-promoter contacts and normal gene expression.
+Thus, YY1-mediated structuring of enhancer-promoter loops is
+analogous to CTCF-mediated structuring of TADs, CTCF contact domains, and insulated neighborhoods. This model of
+YY1-mediated structuring of enhancer-promoter loops accounts
+for diverse functions reported previously for YY1, including contributions to both gene activation and repression and to gene
+dysregulation in cancer. ["YY1 Is a Structural Regulator
+of Enhancer-Promoter Loops"]
+-->
 

### 2019-09-03 Manuscript/manuscript.Rmd
discussion edits

@@
 We showed that the genomic signals for each TFBS was much more consolidated near the center of our flanked predicted TAD boundary then the flanked boundary identified by the ARROWHEAD TAD caller.
-We also evaluated the distal relationships between the same architectural proteins and found that they were statistically significantly closer in base pair distance to our predicted TAD boundaries, than to ones identified by ARROWHEAD.
+We also evaluated the distal relationships between the same architectural proteins and found that they were statistically significantly closer in base pair distance to our predicted TAD boundaries, than to those identified by ARROWHEAD.
+
+# Conclusion
 
@@
 Through our ensemble framework, we provide a useful guide toward the exploration of chromatin organization, while highlighting the impact of data resolution, class imbalance, and feature engineering in TAD boundary prediction.
-Lastly, by building models using known enriched transcription factors, we were able to bridge the resolution gap between ChIP-Seq and Hi-C sequencing for more precise TAD boundary prediction.
+Lastly, by building models using known enriched transcription factors, we were able to bridge the resolution gap between 1D ChIP-Seq annotations and 3D Hi-C sequencing for more precise TAD boundary prediction.
+This improved precision in TAD boundary location offers the potential for further exploration into the 3D organization of the human genome.
 

### 2019-09-03 Manuscript/manuscript.Rmd
added refs in intro

@@
 
-A key factor in locating TAD boundaries is Hi-C data "resolution".
-Resolution determines the bin sizes of the linear genome used to enumerate contacts caused by chromatin folding.
+A key factor in locating TAD boundaries is "resolution".
+Due to the high-dimensional nature of Hi-C data, genome binning has been a common strategy for dealing with a low signal-to-noise ratio problem [@li2019comparison].
+Resolution, therefore, determines the bin sizes of the linear genome used to enumerate contacts caused by chromatin folding.
 Lower resolutions contribute to larger bin sizes, which lead to variability in the location of TAD boundaries.
@@
 Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth, obtaining high resolution remains difficult [@schmitt2016genome].
-While these low resolution Hi-C datasets can be used to probe higher order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define sub-domains and the boundaries that demarcate them.
-Furthermore, even at its highest (750 bp [@bonev2017multiscale]), Hi-C sequencing resolution still remains well below the resolution of ChIP-Sequencing experiments used to annotate the genome, which ranges in the tens of base pairs.
+While these low resolution Hi-C datasets can be used to probe higher order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define sub-domains and the boundaries that demarcate them [@fudenberg2016formation].
+Furthermore, even at its highest (750 bp [@bonev2017multiscale]), Hi-C sequencing resolution still remains well below the resolution of ChIP-Sequencing experiments used to annotate the genome, which ranges in the tens of base pairs [@mendoza2009genome].
 This resolution gap between 1D and 3D genomic maps can make it difficult to disentangle the role of genomic factors related to TAD boundaries, thereby limiting our understanding of epigenomic regulation and its potential link to chromatin architecture.

### 2019-09-03 Manuscript/manuscript.Rmd
grammar

@@
 Emerging evidence has linked TADs to critical roles in cell dynamics like gene regulation and cell differentiation, an example being the mechanism by which enhancers loop to come into contact with distal promoters to initiate transcription within these domains [@Lupianez:2015aa; @Franke:2016aa].
-Likewise, disruption of TAD boundaries has been shown to lead to developmental disorders [@lupianez2016breaking], such as cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@Sun:2018aa; @Meaburn:2007aa].
+Likewise, disruption of TAD boundaries has been shown to lead to developmental disorders [@lupianez2016breaking], cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@Sun:2018aa; @Meaburn:2007aa].
 Therefore, identifying the location of TAD boundaries remains a top priority in our goal to understand the functionality of the human genome.
@@
 Several methods have been developed to predict TAD boundary location using genomic annotations.
-However, most ignore key characteristics of 3D genomic data that are detrimental to model performance.
+However, most ignore key characteristics of 3D genomic data that are detrimental to both model performance and accurate boundary identification.
 A method developed by Mourad et al [@mourad2016computational], called *HiCFeat*, used the percentage of overlap between several ChIP-seq defined transcription factor binding site (TFBS) regions and 1 kb genomic bins to build an L1-regularized multiple logistic regression model to predict TAD boundary regions.
@@
 Instead, model performance was evaluated using area under the receiver operating characteristic curve (AUROC) which is known to be insensitive to class imbalance, creating artificially inflated values influenced by the majority class [@prati2011survey; @wei2013role].
-<!--A more appropriate evaluation tool to consider would be a composite metric such as Matthews Correlation Coefficient (MCC), which penalizes for both false positives and false negatives.--> Furthermore, by only considering the percentage of overlap in defining the feature space, *HiCFeat* is limited in its granularity given that many regions on the linear genome will not be overlapped with any genomic annotations, resulting in a zero inflated model.
+<!--A more appropriate evaluation tool to consider would be a composite metric such as Matthews Correlation Coefficient (MCC), which penalizes for both false positives and false negatives.--> Furthermore, by only considering the percentage of overlap in defining the feature space, *HiCFeat* is limited in its granularity given that many regions on the linear genome will not be overlapped with any genomic annotations.
 <!--This, likely being further exacerbated by the class imbalance.--> Two additional studies were proposed in 2015 and 2017 respectively, one using histone modifications in a Bayesian Additive Regression Trees (BART) model [@huang2015predicting] and the other using combined sets of TFBS, DNase I hypersensitive sites, and histone modifications together in an L2-based regularized linear model [@hong2017computational].

### 2019-10-16 kellen/Legends.Rmd
add manuscript section

---
title: "Legends"
author: "Kellen Cresswell"
date: "October 16, 2019"
output: pdf_document
---

**Figure 1. Oversampling is needed to account for class imbalance**. A feed-forward neural network with a single hidden layer and 16 nodes was used to predict TAD boundaries. Adjusted PPV was calculated to determine the of accuracy predictions. Results are seperated by oversampling approach (None, RUS, ROS, SMOTE) and feature type (TFBS, BroadHMM, Histones). All results were generated using distance. GM12878 cell line, various resolutions.

**Figure 2. Results are generally consistent with node selection**. A feed-forward neural network with a single hidden layer and varying numbers of nodes (4,8,12,16,24,32,64) was used to predict TAD boundaries. Adjusted PPV was calculated to determine the accuracy of predictions. Results are presented for TFBS (a), histones (b) and broadHMM (c) and feature type (Combined, Distance, Overlap and Percent Overlap). GM12878 cell line, various resolutions.

**Figure 3. Neural networks and logistic regressions peform similarly**. A feed-forward neural network with a single hidden layer with 16 nodes and an elastic-net logistic regression model was used to predict TAD boundaries. Adjusted PPV was calculated to determine the accuracy of predictions. Results are presented for TFBS across all feature types (Combined, Distance, Overlap and Percent Overlap). GM12878 cell line, various resolutions.

**Figure 4. Neural network results are robust to feature selection**. A feed-forward neural network with a single hidden layer and 16 nodes was used to predict TAD boundaries. Adjusted PPV was calculated to determine the of accuracy predictions. Results are seperated by data source (TFBS, BroadHMM, Histones) and feature type (Combined, Distance, Overlap and Percent Overlap). All results were generated using distance. GM12878 cell line, various resolutions.

**Figure 5. Certain features consistently appear near predicted TAD boundaries.**. TAD boundaries were predicted using a feed-forward neural network. The mean distance from predicted TAD boundaries was calculated for all features and are shown in a Heatmap. Results are presented for combined, TFBS (a), histones (b) and broadHMM (c). Rows represent resolution and columns individual features. Clustering was performing using Ward's clustering.

### 2019-10-16 kellen/manuscript.Rmd
add manuscript section

---
title: "Methods"
author: "Kellen Cresswell"
date: "October 14, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Methods

## The data structure

For each resolution and genomic feature (histones, broadHMM and transcription factor binding sites) were arranged

## Choosing the neural network hyperparameters

A deep feed forward neural network was fit to predict the location of TAD boundaries. The ideal number of hidden layers (1,2) and nodes (4,8,12,16,32,64), and the resampling scheme ("none", "SMOTE", "RUS", "ROS") was tested based on cross-validation using adjusted precision as our measure of accuracy. To prevent overfitting, a dropout layer was added between every layer. In general, we find that networks with more than 1 layer tend to either overfit the data, resulting in a decrease in prediction quality. As a result, we present results for single layer models exclusively. In addition, we find the choice of activation function to be largely inconsequential to our predictive ability as a result a simple ReLU activation function is used for all layers.

# Results

## SMOTE sampling increases predictive ability compared to other methods

We find that SMOTE oversampling outperforms other oversampling methods in terms of TAD boundary detection (Figure 1). In general, we find that the all over sampling methods produce comparable results. However, we find that any oversampling method results in better precision than no oversampling at all. Without oversampling or undersampling, the vast majority of models (74%) fail to predict a single TAD boundary across all data types and resolutions. SMOTE has the smallest proportion of failures (0.5%) followed by RUS (0.9%) and ROS (2%). This demonstrates the need to balance the data before predicting TAD boundaries.

## TAD prediction is largely invariant to the number of layers

We find that regardless of the number of hidden layers (4,8,12,16,32,64), the neural network is able to predict TAD boundaries near those annotated by TAD callers. The number of layers with the best performance is 16 (Median $PPV_a$ = .941) and the worst is 4 (Median $PPV_a$ = .932). In rare circumstances (Figure 2a,2b,2c), we find that networks with too few layers will have poor predictive ability. As a result, we use a single layer network with 16 layers as our default architecture for comparison of features.

## Neural network approaches outperform logistic regression for complex datasets

To test, whether the neural network approaches can outperform simple models, we fit a logistic regression with variable selection using an elastic net algorithm and compare results. We find the for overlap, distance and percent overlap, both approaches perform similarly well (Figure 3). For the more complex combined dataset, the neural network approach produces slightly better results than the logistic regression approach. These results suggest a neural network may be optimal for more complex datasets and better at integrating future data.

## Histone modifications, broadHMM and transcription factor binding sites have similar predictive abilities

We fnd that the three tested categories produce similar results in terms of predictive ability. Transcription factor binding sites (Median $PPV_a$ = .941) produced the best results, followed by BroadHMM (Median $PPV_a$ = .940) and histone modifications (Median $PPV_a$ = .925). Figure 4 summarises these results, demonstrating the similarity. These results suggest that boundary prediction is robust to the type of data source used for prediction.

## Distance provides the best prediction results

To determine the best feature for prediction, we compared distance, overlap, percent overlap and combination of all features. We find that simply using distance (Median $PPV_a$ = .950) outperforms overlap (Median $PPV_a$ = .930) and percent overlap (Median $PPV_a$ = .915). Additionally, we find that the combined (Median $PPV_a$ = .940) approach outperforms overlap and percent overlap but not distance.

## Predicted TADs tend to be near true TADs

To determine the accuracy of predicted TADs in terms of raw distance, we calculate the mean distance of predicted TADs and non-predicted TADs from annotated ones. We find a large difference in mean distance (64.2 vs. 5.87) between predicted TADs and non-predicted TADs. These results suggest that our method is able to succesfully differentiate random regions and TAD regions.

## The profile of TAD predictors is unique to the data type

Distance from predicted TAD boundaries was calculated for a range of features, seperated by resolution. Features were clustered using Ward.D2 clustering and visualized using a heatmap (Figure 5). TFBS and BroadHMM can be seperated into three distinct groups (Enriched, Depleted and unrelated). The core enriched TFBS group includes CTCF, RAD21, Pu1 and Smc3ab9263. For BroadHMM, the core group is heterochromatin, insulators and weak enhancers. In TFBS, there is heavy depletion in Nfe2 and Tr4. In BroadHMM, repetive CNVs, poised promoters and Txn transitions are all depleted. In the case of histones, a different pattern emerges with two distinct groups (a large enriched group and a smaller depleted group). The large group consists of H3k27me3, H3k9me3, H2az, H3k4me1, H3k4me2, H327ac and H3k4me3. The depleted group consists of H3k36me3, H3k79me2, H3k9ac, H4k20me1.

Summarized across all resolutions and features, we find that H3K9me3 co-locates the closest with predicted TAD boundaries followed by heterochromatin. Of the top 10 features, 6 are histones, 2 are from BroadHMM (heterochromatin, insulators) and 2 are TFBS (CTCF, Pu1).

Boxplot with distance from predicted and TAD caller predicted
Plot from Spiros paper with predicted and sites around boundaries

### 2019-10-16 kellen/manuscript.Rmd
Proofread all, add ???

@@
 
-A deep feed forward neural network was fit to predict the location of TAD boundaries.
+A deep feed forward [???
+terminology: I remember "fully connected" - shall we use it?] neural network was fit to predict the location of TAD boundaries.
 The ideal number of hidden layers (1,2) and nodes (4,8,12,16,32,64), and the resampling scheme ("none", "SMOTE", "RUS", "ROS") was tested based on cross-validation using adjusted precision as our measure of accuracy.
@@
 As a result, we present results for single layer models exclusively.
-In addition, we find the choice of activation function to be largely inconsequential to our predictive ability as a result a simple ReLU activation function is used for all layers.
+[???
+So, no dropout?] In addition, we find the choice of activation function to be largely inconsequential to our predictive ability as a result a simple ReLU activation function is used for all layers.
+
+[??? How standard errors on all plots were generated?]
 
 # Results
+
+[??? Need justification for usind "Adjusted PPV" - what is it, why used?]
 
@@
 However, we find that any oversampling method results in better precision than no oversampling at all.
-Without oversampling or undersampling, the vast majority of models (74%) fail to predict a single TAD boundary across all data types and resolutions.
+Without oversampling or undersampling, the vast majority of models (74%) [???
+TBD, I do not understand this number] fail to predict a single TAD boundary across all data types and resolutions [???
+making calculation of adj PPV impossible?].
 SMOTE has the smallest proportion of failures (0.5%) followed by RUS (0.9%) and ROS (2%).
 This demonstrates the need to balance the data before predicting TAD boundaries.
+
+[??? figure 1 has results for "none" only for 5Kb resolution - why?]
+[???
+Adjusted PPV are too similar.
+See above, we need a strong justification why not AUC, MCC, F1.
+Can you try if any of those can be used?
+I am quite uneassy that we'll be asked to use something else than PPV.
+So, justify]
+[??? Figure 1 - can we quantify that on average SMOTE is better? It doesn't look so]
+[??? Figure 1 - can we quantify TFBSs are better than others?]
 
@@
 
+[??? This section may be titled something like "Network architecture engineeting" describing all steps in more details, e.g., playing with dropouts. Need results.]
+[??? A figure illustrating the final architecture.]
+[??? How "Combined" are handled? Visualize. "Combined" - You merge them. Can you try to feed them in in parallel? "Combined in parallel"]
+[??? Another story - performance drops with lower resolution. To be described]
+
 ## Neural network approaches outperform logistic regression for complex datasets
@@
 We find the for overlap, distance and percent overlap, both approaches perform similarly well (Figure 3).
-For the more complex combined dataset, the neural network approach produces slightly better results than the logistic regression approach.
+[???
+That's why I don't like PPV.
+Previously, the story was that distance performs best.
+How can we show it?] For the more complex combined dataset, the neural network approach produces slightly better results than the logistic regression approach.
 These results suggest a neural network may be optimal for more complex datasets and better at integrating future data.
+
+[??? How to show distance performs better? Metric other than PPV?]
+[??? Add Random Forest for comparison]
+[??? "Combined in parallel" performance?]
 
@@
 
-We fnd that the three tested categories produce similar results in terms of predictive ability.
+We find that the three tested categories produce similar results in terms of predictive ability.
 Transcription factor binding sites (Median $PPV_a$ = .941) produced the best results, followed by BroadHMM (Median $PPV_a$ = .940) and histone modifications (Median $PPV_a$ = .925).
@@
 These results suggest that boundary prediction is robust to the type of data source used for prediction.
+
+[??? Can we use something other than PPV? Previously, TFBS performed better, and that makes sense]
 
@@
 
+[??? Which figure demonstrates it? Again, PPV seem to give minuscule differences]
+
+## CTCF, RAD21 etc. are the most predictive
+
+[??? Need feature selection results - random forest?]
+
 ## Predicted TADs tend to be near true TADs
@@
 We find a large difference in mean distance (64.2 vs.
-5.87) between predicted TADs and non-predicted TADs.
+5.87) [???
+Where those numbers come from?
+What do they mean, units?
+Figure?] between predicted TADs and non-predicted TADs.
 These results suggest that our method is able to succesfully differentiate random regions and TAD regions.
+
+[??? Need figure: Boxplots of distances between CTCF and detected from Hi-C, predicted from genomic annotations, not predicted. For CTCF, RAD21 and other selected features]
 
@@
 
+[??? Figure 5: Instead of clustering, sort columns by average smallest to largest distance. This way, one can see what is the closest and fartherst]
+
 Boxplot with distance from predicted and TAD caller predicted

### 2019-10-16 kellen/manuscript.Rmd
adjusted precision

--- 2019-10-16 kellen/manuscript.Rmd
@@
 
-## The data structure
+## Adjusted Precision
 
-For each resolution and genomic feature (histones, broadHMM and transcription factor binding sites) were arranged
+In the contact matrix domains, TAD boundaries are often noisy with imprecise locations.
+This noise can cause boundaries to shift by multiple bins depending on the TAD caller used.
+Additionally, we find that genomic features such as CTCF and RAD21 exist at elevated levels in bins around called TAD boundaries and not just in the bin containing the boundary itself.
+To account for this imprecision we use a flanked form of the precision metric called adjusted precision ($P_a$).
+In the framework of boundary prediction, traditional precision takes two inputs: true positives ($TP$) whch are correctly identified TAD boundaries and false positives ($FP$) which are regions incorrectly identified as TAD boundaries.
+Adjusted precision introduces a flanking region ($f$) such that true positives become all predicted TAD boundaries within $f$ of a true TAD boundary and false positives become those that are not within $f$ of a true TAD boundary.
+We calculate adjusted precision using the following formula:
+
+$$
+P_{a} = \frac{TP_{a}}{FP_{a}+TP_{a}}
+$$
+
+where $TP_{a}$ is the flanked true positive value and $FP_{a}$ is the flanked false positive value.
+
+Conveniently we can convert the adjusted precision score to another measure "adjusted false discovery rate ($FDR_a$)" by simply taking 1-$P_{a}$.
+$FDR_a$ can be interpreted as the probability that a TAD boundary identified by a given approach is within $f$ of a true TAD boundary.
 

### 2019-10-19 kellen/Legends.Rmd
updated

@@
 **Figure 1.
-Oversampling is needed to account for class imbalance**.
+Performance is mildly dependent on layers**.
+A feed-forward neural network with either one or two hidden layer(s) and 16 nodes was used to predict TAD boundaries.
+Adjusted PPV (200kb flank) was calculated to determine the accuracy of predictions.
+Results are seperated by number of layers (1 or 2) and predictor type (Combined, Distance, Overlap, Percent Overlap).
+GM12878 cell line, various resolutions.
+
+**Figure 2.
+Performance is mildly dependent on dropout**.
+A feed-forward neural network with one layer and 16 nodes was used to predict TAD boundaries.
+Adjusted PPV (200kb flank) was calculated to determine the accuracy of predictions.
+Varying levels of dropout were used (0,0.1,0.2,0.3,0.4,0.5) Results are seperated by dropout level and predictor type (Combined, Distance, Overlap, Percent Overlap).
+GM12878 cell line, various resolutions.
+
+**Figure 3.
+Over or under sampling is needed to account for class imbalance**.
 A feed-forward neural network with a single hidden layer and 16 nodes was used to predict TAD boundaries.
@@
 
-**Figure 2.
+**Figure 4.
 Results are generally consistent with node selection**.
@@
 
-**Figure 3.
+**Figure 5.
 Neural networks and logistic regressions peform similarly**.
-A feed-forward neural network with a single hidden layer with 16 nodes and an elastic-net logistic regression model was used to predict TAD boundaries.
-Adjusted PPV was calculated to determine the accuracy of predictions.
+A feed-forward neural network with a single hidden layer with 16 nodes, an elastic-net logistic regression model and a random forest was used to predict TAD boundaries.
+Adjusted PPV (200kb flank) was calculated to determine the accuracy of predictions.
 Results are presented for TFBS across all feature types (Combined, Distance, Overlap and Percent Overlap).
@@
 
-**Figure 4.
+**Figure 6.
 Neural network results are robust to feature selection**.
@@
 
-**Figure 5.
+**Figure 7.
+A small number of features can be used to predict TAD boundaries.** TADs were predicted using a random forest model (500 trees) and variable importance was extracted for TFBS (a), histones(b) and broadHMM (c).
+Rows correspond to resolution and columns to features.
+Mean importance is shown.
+GM12878 cell line, various resolutions.
+
+**Figure 8.
+Predicted boundary types that are also called by a TAD caller perform best.** TADs were predicted using single layer neural networks with 16 nodes.
+Predictions were classified into four categories Not Predicted and Called, Not Predicted and Not Called, Predicted and Called, Predicted and Not Called) where called refers to TADs identified using the SpectralTAD TAD caller and predicted refers to boundaries predicted by the neural network.
+Distance from these boundary types was calculated for a range of genomic annotations.
+We present the top 5 closest TFBS features.
+x-axis- Feature, y-axis - Distance from boundary.
+GM12878 cell line, 50kb resolution.
+
+**Figure 9.
 Certain features consistently appear near predicted TAD boundaries.**.
@@
 Rows represent resolution and columns individual features.
-Clustering was performing using Ward's clustering.
+
+**Supplementary Table 1.
+Comparison of over/under sampling methods.** Neural network models were fit with 16 nodes and a single layer using no resampling, random undersampling (rus), random oversampling (ros) and SMOTE.
+Adjusted precision was calculated for each model and summarized across resolutions (5kb, 10kb, 25kb, 50kb, 100kb) and annotation types (TFBS, histones, broadHMM).
+Results are seperated by predictor type.
+GM12878 cell line, various resolutions.
+
+**Supplementary Table 2.
+The effect of nodes on model performance.** Single layer neural networks were fit using varying numbers of nodes (4,8,12,16,24,32,64) and adjusted precision was calculated.
+Results are seperated by resolution and annotation type.
+GM12878 cell line, various resolutions.
+
+**Supplementary Table 3.
+The effect of nodes on model performance.** Single layer neural networks with 16 nodes, penalized logistic regression, random forest and support vector machine models were used to predict TAD boundaries.
+Adjusted precision was calculated based on these predictions and presented for each method.
+Results are summarized across resolutions (5kb, 10kb, 25kb, 50kb, 100kb) and annotation type (TFBS, histones, broadHMM).
+Results are seperated by predictor type.
+GM12878 cell line, various resolutions.
+
+**Supplementary Table 4.
+The effect of predictor type on model performance.** Single layer neural networks with 16 nodes were used to predict TAD boundaries using different types of predictors.
+Adjusted precision (200kb flank) was used to assess prediction accuracy.
+Results are summarized across resolutions (5kb, 10kb, 25kb, 50kb, 100kb) and seperated by annotation type.
+GM12878 cell line, various resolutions.
+
+**Supplementary Table 5.
+A small set of predictors show high importance for each method.** A random forest model (500 trees) was used to predict TAD boundaries.
+Variable importance was extracted and summarized.
+Results are summarized across resolutions (5kb, 10kb, 25kb, 50kb, 100kb) and seperated by annotation type.
+GM12878 cell line, various resolutions.
+
+**Supplementary Table 6.
+Summary of distances from TAD boundaries.** TADs were predicted using single layer neural networks with 16 nodes.
+Predictions were classified into four categories Not Predicted and Called, Not Predicted and Not Called, Predicted and Called, Predicted and Not Called) where called refers to TADs identified using the SpectralTAD TAD caller and predicted refers to boundaries predicted by the neural network.
+Distance from these boundary types was calculated for a range of genomic annotations.
+GM12878 cell line, 50kb resolution.
+
+**Supplementary Table x. Summary of resolutions.**

### 2019-10-19 kellen/manuscript.Rmd
Add Peakachu

--- 2019-10-16 kellen/manuscript.Rmd
@@
 # Methods
+
+## Data sources
+
+All GM12878 Hi-C data were downloaded from GSE63525 [@rao20143d] (Supplementary Table1).
+TAD boundaries were identified using SpectralTAD [@cresswelkg:2019aa].
+Three categories of genomic annotations (BroadHMM, histone modifications and transcription factor binding sites (TFBS)) were downloaded from the UCSC genome browser [@Tyner:2017aa] (Supplementary Table 1).
+All data corresponds to GRCh37/hg19.
+
+## Feature Engineering
+
+We create four types of feature (distance, overlap, percent overlap and combined).
+Each method starts with binning the matrix based on resolution.
+For instance, the start of the bins for a 5kb matrix would be located at 0,5kb,10kb,15kb, etc.
+Distance is calculated by finding the distance between the start of each bin and the closest location of each genomic feature.
+Overlap is calculated by taking the start point of each bin, flanking it on both sides by half the resolution and calculating the number of times a given genomic feature appears within the flanking region.
+Percent overlap calculates the percentage of the flanking region that is covered by a given genomic feature.
+Combined is simply a combination of them all, combined in side-by-side manner.
+Prediction is performed using matrices of these features with the response being the location of predicted TAD boundaries.
 
@@
 
-A deep feed forward neural network was fit to predict the location of TAD boundaries.
+A feed forward neural network was fit to predict the location of TAD boundaries.
 The ideal number of hidden layers (1,2) and nodes (4,8,12,16,32,64), and the resampling scheme ("none", "SMOTE", "RUS", "ROS") was tested based on cross-validation using adjusted precision as our measure of accuracy.
+Results were summarized across all chromosomes.
 To prevent overfitting, a dropout layer was added between every layer.
-In general, we find that networks with more than 1 layer tend to either overfit the data, resulting in a decrease in prediction quality.
+In general, we find that networks with more than 1 layer tend to either overfit the data (Figure 1), resulting in a decrease in prediction quality.
 As a result, we present results for single layer models exclusively.
+Additionally, we find that a dropout of 50% on the final layer provides consistently better results (Figure 2).
 In addition, we find the choice of activation function to be largely inconsequential to our predictive ability as a result a simple ReLU activation function is used for all layers.
@@
 
-## SMOTE sampling increases predictive ability compared to other methods
+## Why use adjusted precision?
 
-We find that SMOTE oversampling outperforms other oversampling methods in terms of TAD boundary detection (Figure 1).
-In general, we find that the all over sampling methods produce comparable results.
+TAD boundary data has two unique features, it is heavily imbalanced (there are much less TAD boundaries than non-TAD boundaries) and it is imprecise due to limitations with resolution.
+An additional complication arises due to the fact that TAD callers are only capable of identifying single points as their best guess for a TAD boundary.
+As a result, the response vector of any predictive algorithm will be comparitively sparse compared to the features.
+
+The implicit impreciseness of TAD calling leads to inflated false positive values as algorithms will detect TADs not only at the detected TAD boundary but also in regions around it.
+As a result, traditional measures of prediction quality will return poor results for any algorithm.
+For this reason, we introduce the flanking region around the boundary allowing us to account for boundaries predicted near TAD boundaries but not exactly on the boundary.
+Precision is used because it monotonically increases with flank size due to the absence of false negative and true negatives in its formula.
+This is not the case for measurements such as accuracy, F1 and matthews correlation coefficient which can decrease with increasing flank size due to the removal of negative cases as the flank becomes larger.
+
+## Oversampling greatly increases predictive ability
+
+We find that SMOTE oversampling slightly outperforms other oversampling methods in terms of TAD boundary detection (Figure 3, Supplementary Table 1).
+Summarized across all resolutions, feature types and data sources, SMOTE performed best (Mean $PPV_a$ = 0.837, Median $PPV_a$ = 0.933) with a slight advantage over RUS (Mean $PPV_a$ = 0.837, Median $PPV_a$ = 0.930).
+In general, we find that the all oversampling and undersampling methods produce comparable results.
 However, we find that any oversampling method results in better precision than no oversampling at all.
+
+Another side-effect of imbalance is algorithms failing to learn the data and simply predicting no positive outcomes (TAD boundaries).
+To test, how well oversampling approaches deal with this issue we fit models across all resolutions (5kb,10kb,25kb,50kb,100kb), feature types (distance, overlap, percent overlap, combined) and data sources (TFBS, histones, broadHMM) and calculated the percentage of models with zero boundary predictions.
+In total, there were 1320 models tested for each sampling type.
 Without oversampling or undersampling, the vast majority of models (74%) fail to predict a single TAD boundary across all data types and resolutions.
@@
 
-## TAD prediction is largely invariant to the number of layers
+[??? figure 1 has results for "none" only for 5Kb resolution - why?? The rest are zero or below the threshold]
+[???
+Adjusted PPV are too similar.
+See above, we need a strong justification why not AUC, MCC, F1.
+Can you try if any of those can be used?
+I am quite uneassy that we'll be asked to use something else than PPV.
+So, justify]
+[??? Figure 1 - can we quantify that on average SMOTE is better? It doesn't look so?? Added but very slight]
+[??? Figure 1 - can we quantify TFBSs are better than others?? Added later but very slight]
+
+## Network architecture engineering
 
@@
 The number of layers with the best performance is 16 (Median $PPV_a$ = .941) and the worst is 4 (Median $PPV_a$ = .932).
-In rare circumstances (Figure 2a,2b,2c), we find that networks with too few layers will have poor predictive ability.
+In rare circumstances (Figure 4a,4b,4c, Supplementary Table 2), we find that networks with too few nodes will have poor predictive ability.
 As a result, we use a single layer network with 16 layers as our default architecture for comparison of features.
+Using results from testing layers (Figure 1) and dropout (Figure 2), we define a baseline model for testing with a single hidden layer containg 16 nodes and a final dropout of 0.5.
+This is used for all analysis unless otherwise stated.
 
-## Neural network approaches outperform logistic regression for complex datasets
+## Performance drops with lower resolution
 
-To test, whether the neural network approaches can outperform simple models, we fit a logistic regression with variable selection using an elastic net algorithm and compare results.
-We find the for overlap, distance and percent overlap, both approaches perform similarly well (Figure 3).
-For the more complex combined dataset, the neural network approach produces slightly better results than the logistic regression approach.
+TBD, Supplementary Table x
+
+## Neural network approaches outperform other machine learning algorithms on complex datasets
+
+To test, whether the neural network approaches can outperform simple models, we fit a logistic regression with variable selection using an elastic net algorithm, a random forest model and an linear discriminant analysis model (LDA) (Will add) and compared results.
+We find the for overlap, distance and percent overlap, both approaches perform similarly well (Figure 5, Supplementary Table 3).
+[???
+That's why I don't like PPV.
+Previously, the story was that distance performs best.
+How can we show it?] For the more complex combined dataset, the neural network approach produces slightly better results than the logistic regression approach.
+Both methods outperform the random forest and LDA models on all datasets.
 These results suggest a neural network may be optimal for more complex datasets and better at integrating future data.
+
+[??? How to show distance performs better? Metric other than PPV?]
+[??? Add Random Forest for comparison]
+[??? "Combined in parallel" performance?]
 
@@
 
-We fnd that the three tested categories produce similar results in terms of predictive ability.
+We find that the three tested categories produce similar results in terms of predictive ability.
 Transcription factor binding sites (Median $PPV_a$ = .941) produced the best results, followed by BroadHMM (Median $PPV_a$ = .940) and histone modifications (Median $PPV_a$ = .925).
-Figure 4 summarises these results, demonstrating the similarity.
+Figure 6 summarises these results, demonstrating the similarity.
 These results suggest that boundary prediction is robust to the type of data source used for prediction.
+
+[??? Can we use something other than PPV? Previously, TFBS performed better, and that makes sense.]
 
@@
 We find that simply using distance (Median $PPV_a$ = .950) outperforms overlap (Median $PPV_a$ = .930) and percent overlap (Median $PPV_a$ = .915).
-Additionally, we find that the combined (Median $PPV_a$ = .940) approach outperforms overlap and percent overlap but not distance.
+Additionally, we find that the combined (Median $PPV_a$ = .940) approach outperforms overlap and percent overlap but not distance (Figure 6, Supplementary Table 4).
+
+[??? Which figure demonstrates it? Again, PPV seem to give minuscule differences]
+
+## TADs can be predicted by multiple genomic annotations
+
+Variable importance was calculated by creating random forest models across all resolutions and feature types and extracting importance.
+Among transcription factor binding sites, we find that CTCF, Smc3ab92, Znf143, Rad21 and Pu1 have the highest levels of importance.
+For histones, the most important features are H3k9me3, H2az, H4k20me1, H3k4me1 and H3k27me3.
+BroadHMM is mainly explained by insulators, heterochromatin and weak enhancers with repressed and repetive CNV playing a role.
+Results are summarized in Figure 7 and Supplementary Table 5.
 
@@
 
-To determine the accuracy of predicted TADs in terms of raw distance, we calculate the mean distance of predicted TADs and non-predicted TADs from annotated ones.
-We find a large difference in mean distance (64.2 vs.
-5.87) between predicted TADs and non-predicted TADs.
-These results suggest that our method is able to succesfully differentiate random regions and TAD regions.
+TAD prediction involves two parts: the prediction of TADs by our algorithm and prediction by the TAD caller.
+For each bin, there are four unique situations (TAD predicted and TAD called, TAD predicted and TAD not called, TAD not predicted and TAD called, TAD not predicted and TAD not called).
+As expected TADs predicted by our method hare nearer CTCF, Pu1, RAD21, Smc3ab9263 and Znf143 than those not predicted (Figure 8, Supplementary Table 6).
+Additionally, we find annotations are also closer in those TAD boundaries that are also called by the TAD caller.
+
+[??? Need figure: Boxplots of distances between CTCF and detected from Hi-C, predicted from genomic annotations, not predicted. For CTCF, RAD21 and other selected features]
 
@@
 Distance from predicted TAD boundaries was calculated for a range of features, seperated by resolution.
-Features were clustered using Ward.D2 clustering and visualized using a heatmap (Figure 5).
+Features were clustered using Ward.D2 clustering and visualized using a heatmap (Figure 9).
 TFBS and BroadHMM can be seperated into three distinct groups (Enriched, Depleted and unrelated).

### 2019-10-20 kellen/manuscript.Rmd
Read through methods, waiting for figure access

@@
 
-All GM12878 Hi-C data were downloaded from GSE63525 [@rao20143d] (Supplementary Table1).
+All GM12878 Hi-C data were downloaded from GSE63525 [@rao20143d] (Supplementary Table 1 [???
+Currently, missing]).
 TAD boundaries were identified using SpectralTAD [@cresswelkg:2019aa].
 Three categories of genomic annotations (BroadHMM, histone modifications and transcription factor binding sites (TFBS)) were downloaded from the UCSC genome browser [@Tyner:2017aa] (Supplementary Table 1).
-All data corresponds to GRCh37/hg19.
+All data corresponds to the GRCh37/hg19 genome assembly.
 
@@
 
-We create four types of feature (distance, overlap, percent overlap and combined).
+We create four types of predictors (distance, overlap, percent overlap and combined).
 Each method starts with binning the matrix based on resolution.
-For instance, the start of the bins for a 5kb matrix would be located at 0,5kb,10kb,15kb, etc.
-Distance is calculated by finding the distance between the start of each bin and the closest location of each genomic feature.
-Overlap is calculated by taking the start point of each bin, flanking it on both sides by half the resolution and calculating the number of times a given genomic feature appears within the flanking region.
-Percent overlap calculates the percentage of the flanking region that is covered by a given genomic feature.
-Combined is simply a combination of them all, combined in side-by-side manner.
+For instance, the start of the bins for a 5kb matrix would be located at 0, 5kb, 10kb, 15kb, etc.
+_Distance_ is calculated by finding the distance between the start of each bin and the closest location [???
+TBD, center, or just closest border?] of each genomic feature.
+_Overlap_ is calculated by taking the start point of each bin, flanking it on both sides by half the resolution and calculating the number of times a given genomic feature appears within the flanking region.
+_Percent overlap_ calculates the percentage of the flanking region that is covered by a given genomic feature.
+_Combined_ is simply a combination of them all, combined in side-by-side manner.
 Prediction is performed using matrices of these features with the response being the location of predicted TAD boundaries.
@@
 
-In the contact matrix domains, TAD boundaries are often noisy with imprecise locations.
-This noise can cause boundaries to shift by multiple bins depending on the TAD caller used.
+Given noise and frequent dropouts in Hi-C matrices, especially at high resolution, the location of TAD boundaries detected by a TAD caller is frequently imprecise.
+The noise can cause boundaries to shift from their true locations by multiple bins depending on the TAD caller used.
 Additionally, we find that genomic features such as CTCF and RAD21 exist at elevated levels in bins around called TAD boundaries and not just in the bin containing the boundary itself.
-To account for this imprecision we use a flanked form of the precision metric called adjusted precision ($P_a$).
+To account for this imprecision we use a flanked form of the precision metric [???
+Need to describe why Precision is used in the first place.
+Important] called adjusted precision ($P_a$).
 In the framework of boundary prediction, traditional precision takes two inputs: true positives ($TP$) whch are correctly identified TAD boundaries and false positives ($FP$) which are regions incorrectly identified as TAD boundaries.
@@
 
-Conveniently we can convert the adjusted precision score to another measure "adjusted false discovery rate ($FDR_a$)" by simply taking 1-$P_{a}$.
+Conveniently we can convert the adjusted precision score to another measure "adjusted false discovery rate ($FDR_a$)" [???
+Why we need to?
+Describe, important] by simply taking $1-P_{a}$.
 $FDR_a$ can be interpreted as the probability that a TAD boundary identified by a given approach is within $f$ of a true TAD boundary.
+[???
+What is f was set to?]
 
@@
 A feed forward neural network was fit to predict the location of TAD boundaries.
-The ideal number of hidden layers (1,2) and nodes (4,8,12,16,32,64), and the resampling scheme ("none", "SMOTE", "RUS", "ROS") was tested based on cross-validation using adjusted precision as our measure of accuracy.
+The ideal number of hidden layers (1, 2) and nodes (4, 8, 12, 16, 32, 64), and the resampling scheme ("none", "SMOTE", "RUS", "ROS") was tested based on cross-validation [???
+Need details, how cross-validation was set up] using adjusted precision as our measure of accuracy.
 Results were summarized across all chromosomes.

### 2019-10-21 kellen/Legends.Rmd
current edits

@@
 GM12878 cell line, various resolutions.
+[???
+No dropout layers?]
 
@@
 Adjusted PPV (200kb flank) was calculated to determine the accuracy of predictions.
-Varying levels of dropout were used (0,0.1,0.2,0.3,0.4,0.5) Results are seperated by dropout level and predictor type (Combined, Distance, Overlap, Percent Overlap).
+Varying levels of dropout were used (0, 0.1, 0.2, 0.3, 0.4, 0.5) Results are separated by dropout level and predictor type (Combined, Distance, Overlap, Percent Overlap).
 GM12878 cell line, various resolutions.
@@
 Over or under sampling is needed to account for class imbalance**.
-A feed-forward neural network with a single hidden layer and 16 nodes was used to predict TAD boundaries.
-Adjusted PPV was calculated to determine the of accuracy predictions.
-Results are seperated by oversampling approach (None, RUS, ROS, SMOTE) and feature type (TFBS, BroadHMM, Histones).
+A feed-forward neural network with a single hidden layer and 16 nodes [???
+Dropout?] was used to predict TAD boundaries.
+Adjusted PPV was calculated to determine the accuracy of predictions.
+Results are separated by oversampling approach (None, RUS, ROS, SMOTE) and feature type (TFBS, BroadHMM, Histones).
 All results were generated using distance.
@@
 Results are generally consistent with node selection**.
-A feed-forward neural network with a single hidden layer and varying numbers of nodes (4,8,12,16,24,32,64) was used to predict TAD boundaries.
+A feed-forward neural network with a single hidden layer and varying numbers of nodes (4, 8, 12, 16, 24, 32, 64) was used to predict TAD boundaries.
 Adjusted PPV was calculated to determine the accuracy of predictions.

### 2019-10-21 kellen/manuscript.Rmd
current edits

@@
 
-## Choosing the neural network hyperparameters
+## Choosing the neural network hyperparameters [??? This should be a part of network architecture engineering]
 
@@
 To prevent overfitting, a dropout layer was added between every layer.
-In general, we find that networks with more than 1 layer tend to either overfit the data (Figure 1), resulting in a decrease in prediction quality.
+In general, we find that networks with more than 1 layer tend to either overfit the data (Figure 1) [???
+As judged by the slight decrease of PPV?], resulting in a decrease in prediction quality.
 As a result, we present results for single layer models exclusively.
 Additionally, we find that a dropout of 50% on the final layer provides consistently better results (Figure 2).
-In addition, we find the choice of activation function to be largely inconsequential to our predictive ability as a result a simple ReLU activation function is used for all layers.
+[???
+Extremely hard to see.
+Can it be quantified?] In addition, we find the choice of activation function [???
+Opens Pandora's box - need to show the proof.
+What other hunctions did you compare] to be largely inconsequential to our predictive ability as a result a simple ReLU activation function is used for all layers.
 
@@
 
-TAD boundary data has two unique features, it is heavily imbalanced (there are much less TAD boundaries than non-TAD boundaries) and it is imprecise due to limitations with resolution.
-An additional complication arises due to the fact that TAD callers are only capable of identifying single points as their best guess for a TAD boundary.
-As a result, the response vector of any predictive algorithm will be comparitively sparse compared to the features.
+TAD boundary data has two [???
+Unclear, what are the two features?] unique properties affecting prediction performance.
+The first property is that the data is heavily imbalanced (there are much less TAD boundaries than non-TAD boundaries).
+and it is imprecise due to limitations with resolution.
+An additional complication arises due to the fact that TAD callers are only capable of identifying single points as their best guess for a TAD boundary [???
+I don't understand].
+As a result, the response vector of any predictive algorithm will be comparitively sparse compared to the features [???
+Unclear, which features].
 
 The implicit impreciseness of TAD calling leads to inflated false positive values as algorithms will detect TADs not only at the detected TAD boundary but also in regions around it.
-As a result, traditional measures of prediction quality will return poor results for any algorithm.
-For this reason, we introduce the flanking region around the boundary allowing us to account for boundaries predicted near TAD boundaries but not exactly on the boundary.
+As a result, traditional measures of prediction quality [???
+like what?] will return poor results for any algorithm.
+For this reason, we introduce the flanking region around the boundary [???
+It is best to be illustrated.
+I don't get this idea how it will affect performance] allowing us to account for boundaries predicted near TAD boundaries but not exactly on the boundary.
 Precision is used because it monotonically increases with flank size due to the absence of false negative and true negatives in its formula.
-This is not the case for measurements such as accuracy, F1 and matthews correlation coefficient which can decrease with increasing flank size due to the removal of negative cases as the flank becomes larger.
+[???
+I do not understand, too many different statements] This is not the case for measurements such as accuracy, F1 and matthews correlation coefficient which can decrease with increasing flank size due to the removal of negative cases as the flank becomes larger.
 
@@
 Summarized across all resolutions, feature types and data sources, SMOTE performed best (Mean $PPV_a$ = 0.837, Median $PPV_a$ = 0.933) with a slight advantage over RUS (Mean $PPV_a$ = 0.837, Median $PPV_a$ = 0.930).
-In general, we find that the all oversampling and undersampling methods produce comparable results.
-However, we find that any oversampling method results in better precision than no oversampling at all.
+In general, we find that the all oversampling and undersampling methods produce comparable results and increase prediction performance as compared with no oversampling.
 
 Another side-effect of imbalance is algorithms failing to learn the data and simply predicting no positive outcomes (TAD boundaries).
-To test, how well oversampling approaches deal with this issue we fit models across all resolutions (5kb,10kb,25kb,50kb,100kb), feature types (distance, overlap, percent overlap, combined) and data sources (TFBS, histones, broadHMM) and calculated the percentage of models with zero boundary predictions.
-In total, there were 1320 models tested for each sampling type.
+To test, how well oversampling approaches deal with this issue we fit models across all resolutions (5kb, 10kb, 25kb, 50kb, 100kb), feature types (distance, overlap, percent overlap, combined) and data sources (TFBS, histones, broadHMM [???
+We don't combine them?
+TBD, but we should]) and calculated the percentage of models with zero boundary predictions.
+In total, there were 1,320 [???
+Need details how this number was obtained.
+It does not account] models tested for each sampling type.
 Without oversampling or undersampling, the vast majority of models (74%) fail to predict a single TAD boundary across all data types and resolutions.
@@
 
-[??? figure 1 has results for "none" only for 5Kb resolution - why?? The rest are zero or below the threshold]
-[???
-Adjusted PPV are too similar.
-See above, we need a strong justification why not AUC, MCC, F1.
-Can you try if any of those can be used?
-I am quite uneassy that we'll be asked to use something else than PPV.
-So, justify]
-[??? Figure 1 - can we quantify that on average SMOTE is better? It doesn't look so?? Added but very slight]
-[??? Figure 1 - can we quantify TFBSs are better than others?? Added later but very slight]
+## Network architecture engineering [??? Combine it with the last Methods section]
 
-## Network architecture engineering
-
-We find that regardless of the number of hidden layers (4,8,12,16,32,64), the neural network is able to predict TAD boundaries near those annotated by TAD callers.
+We find that regardless of the number of hidden layers (4, 8, 12, 16, 32, 64), the neural network is able to predict TAD boundaries near those annotated by TAD callers.
 The number of layers with the best performance is 16 (Median $PPV_a$ = .941) and the worst is 4 (Median $PPV_a$ = .932).
-In rare circumstances (Figure 4a,4b,4c, Supplementary Table 2), we find that networks with too few nodes will have poor predictive ability.
+In rare circumstances (Figure 4a, 4b, 4c, Supplementary Table 2), we find that networks with too few nodes will have poor predictive ability.
 As a result, we use a single layer network with 16 layers as our default architecture for comparison of features.

### 2019-10-22 Papers.Rmd
Add Peakachu
Add Ramirez 2018, TFBSs at TAD boundaries

@@
 Model trained using data from Hi-C performs well in other technologies, Micro-C, DNA SPRITE.
-Code athttps://github.com/tariks/peakachu, Predicted loops for 56 cell/tissue types are available athttp://promoter.bx.psu.edu/hi-c/publications.html
+Code athttps://github.com/tariks/peakachu, Predicted loops for 56 cell/tissue types are available at http://promoter.bx.psu.edu/hi-c/publications.html
+
+- Ramírez, Fidel, Vivek Bhardwaj, Laura Arrigoni, Kin Chung Lam, Björn A.
+Grüning, José Villaveces, Bianca Habermann, Asifa Akhtar, and Thomas Manke.
+“High-Resolution TADs Reveal DNA Sequences Underlying Genome Organization in Flies.” Nature Communications 9, no.
+1 (December 2018).
+https://doi.org/10.1038/s41467-017-02525-w.
+- TFBSs enriched at and can predict TAD boundaries in Drosophila.
+Eight motifs are enriched, CTCF to a lesser extent.
+Classification of TAD boundaries into active/inactive, promoters/non-promoters, correlation with gene expression.
+Most promoter-boundaries are marked by divergent promoters, genes at them have higher expression and lower variability.
+Motif combination is predictive of boundary strength.
+TAD boundary prediction (Linear, Logistic, GBM, RF) identifies open chromatin as an important feature.
 

### 2019-10-31 Papers.Rmd
Add Neural Network paper example

@@
 Similar enrich- ments at TAD boundaries are observed for RAD21, SMC3 (Cohesin complex), and ZNF143, consistent with previous reports [@Dixon:2012aa][@Zuin:2014aa][@Bailey2015].
+
+- Neural network results reporting, figures: - `Deepimpute` - scRNA-seq imputation using deep neural networks.
+Sub-networks, each processes up to 512 genes needed to be imputed.
+Four layers: Input - dense (ReLU activation) - 20% dropout - output.
+MSE as loss function.
+Outperforms MAGIC, DrImpute, ScImpute, SAVER, VIPER, and DCA on multiple metrics (PCC, several clustering metrics).
+Using 9 datasets.
+https://github.com/lanagarmire/DeepImpute - Arisdakessian, Cédric, Olivier Poirion, Breck Yunits, Xun Zhu, and Lana X.
+Garmire.
+“DeepImpute: An Accurate, Fast, and Scalable Deep Neural Network Method to Impute Single-Cell RNA-Seq Data.” Genome Biology 20, no.
+1 (December 2019): 211.
+https://doi.org/10.1186/s13059-019-1837-6.

### 2019-11-02 Papers.Rmd
Add note that Conservation, GC content, distanceB  to TSS did NOT improve predictions

@@
 Optimization framework, Louvain algorithm to optimize Q.
-Confirmed Dixon's observations of H3K4me3, H3K27ac enrichment at TAD boundaries, depletion of H3K9me3, H3K27me3 enriched across resolutions.
+Confirmed Dixons observations of H3K4me3, H3K27ac enrichment at TAD boundaries, depletion of H3K9me3, H3K27me3 enriched across resolutions.
 Genes, especially, housekeeping, are enriched near TAD boundaries.
@@
 Many other in my `Zotero/Genome/Sequencing/Epigenomics/machine learning` collection
+
+- Conservation, GC content, distance  to TSS did NOT improve predictions.
+Jialiang Huang et al., “Predicting Chromatin Organization Using Histone Marks,” Genome Biology 16, no.
+1 (December 2015), https://doi.org/10.1186/s13059-015-0740-z.
 
@@
 - SPEID - predict enhancer-promoter interactions from sequence only using deep learning.
-Extends author's PEP work, compared with TargetFinder, not RIPPLE.
+Extends authors PEP work, compared with TargetFinder, not RIPPLE.
 Three layers, convolutional, recurrent, dense.

### 2019-11-07 Papers.Rmd
Add themis
Add Prati 2009 review

@@
 ## TAD predictions
+
+- Schreiber, Jacob, Maxwell Libbrecht, Jeffrey Bilmes, and William Stafford Noble.
+“Nucleotide Sequence and DNaseI Sensitivity Are Predictive of 3D Chromatin Architecture.” Preprint.
+Bioinformatics, January 27, 2017.
+https://doi.org/10.1101/103614.
+- Rambutan - a deep convolutional network predicting Hi-C contacts from DNA sequence (one-hot encoded) and DHSs (signal, logFC over control).
+Fit-Hi-C defines significant (q-value <= 1e-6) contacts used for training.
+Genomic distance (binarized) is also included.
+1kb-5kb data.
+AUROC, AUPR for performance evaluation.Description of network topology, training.
+Balanced batches for training.
+Predictions correlated with Insulation Score, replication timing.
+Predict Hi-C contacts for 53 human cell types, clustered by cell types.
+https://github.com/jmschrei/rambutan
 
@@
 
+- Prati, Ronaldo C, Gustavo EAPA Batista, and Maria Carolina Monard. “Data Mining with Imbalanced Class Distributions: Concepts and Methods.” In IICAI, 359–376, 2009.
+. Class imbalance problem, methods to address it. From ROS/RUS to heuristic ROS/RUS, cost-sensitive learning. Metrics for evaluation.
+
 - Twitter tread on class imbalance, https://twitter.com/goodfellow_ian/status/1127994332416364549
@@
 
+- Extra recipes steps for dealing with unbalanced data. https://github.com/EmilHvitfeldt/themis
+
 - Check your (Mixed) Model for Multicollinearity with ‘performance’, https://www.r-bloggers.com/check-your-mixed-model-for-multicollinearity-with-performance/

### 2020-01-08 Scripts/functions_for_R_package/annots_to_datamatrix_func.r
cleaning up figures and tables

@@ -1,49 +1,0 @@
-#function to create data matrix for training predictive model
-annots_to_datamatrix_func <- function(seqData, resolution, predictortype="distance", annotationListGR, chromosome){
-  resolution=as.integer(resolution)
-  
-  seqData <- c(seqData[1]-1, seqData)
-  
-  start=seqData[1] 
-  start=0
-  end=seqData[length(seqData)] - (seqData[length(seqData)] %% resolution)
-  rows = seqData[seqData %in% seq(start, end, resolution)]
-  
-  data_mat <- matrix(nrow=length(rows),
-                     ncol=length(annotationListGR))
-  rownames(data_mat) <- rows
-  
-  dat_mat_gr <- flank(GRanges(seqnames = tolower(chromosome),
-                              IRanges(start = as.numeric(rownames(data_mat)),
-                                      #end = as.numeric(rownames(data_mat)),
-                                      width=1)), (resolution/2), both=TRUE)
-  
-  if(predictortype=="distance"){
-    for(i in 1:length(annotationListGR)){
-      d <- distance_func(dat_mat_gr, annotationListGR[[i]])
-      data_mat[,i] <- d
-    }
-    data_mat <- apply(data_mat,2,function(x){log(x + 1, base=2)})
-    colnames(data_mat) <- names(annotationListGR)
-  }else if(predictortype=="binary"){
-    for(i in 1:length(annotationListGR)){
-      cb <- binary_func(dat_mat_gr, annotationListGR[[i]])
-      data_mat[,i] <- cb
-    }
-    colnames(data_mat) <- names(annotationListGR)
-  }else if(predictortype=="count"){
-    for(i in 1:length(annotationListGR)){
-      co <- count_func(dat_mat_gr, annotationListGR[[i]])
-      data_mat[,i] <- co
-    }
-    colnames(data_mat) <- names(annotationListGR)
-  }else{
-    for(i in 1:length(annotationListGR)){
-      cp <- percent_func(dat_mat_gr, annotationListGR[[i]])
-      data_mat[,i] <- cp
-    }
-    colnames(data_mat) <- names(annotationListGR)
-  }
-  
-  return(data_mat)
-}

### 2020-01-08 Scripts/functions_for_R_package/binary_predictor_types_func.r

@@ -1,10 +1,0 @@
-####calculating binary overlaps
-binary_func <- function(binned_data_gr, annot_data_gr){
-  #Finding the total number of overlaps between genomic bins and the specific genomic annotation
-  count_binary <- countOverlaps(binned_data_gr, annot_data_gr)
-  
-  #Binarizing the overlap (1 or 0)
-  count_binary <- ifelse(count_binary>0,1,0)
-  
-  return(count_binary)
-}

### 2020-01-08 Scripts/functions_for_R_package/extract_boundaries_func.r

@@ -1,30 +1,0 @@
-#function to extract unique chromosome specific TAD boundaries
-extract_boundaries_func <- function(domains.mat, preprocess, chromosome, resolution){
-  resolution=as.integer(resolution)
-  domains.mat <- domains.mat[,1:3]
-  domains.mat[,1] <- paste0("chr",domains.mat[,1])
-  colnames(domains.mat) <- c("Chromosome", "Start", "End")
-  if(preprocess==TRUE){
-    ##restricting domain data to TADs > 2*resolution and < 2,000,000
-    domains.mat <- domains.mat[which((domains.mat$End - domains.mat$Start)>(2*resolution) & (domains.mat$End - domains.mat$Start)<2000000),]
-    }
-  
-  ##concatenating boundary coordinates into one long vector
-  coords <- domains.mat
-  colnames(coords)[2:3] <- c("coordinate", "coordinate")
-  coords <- rbind.data.frame(coords[,c(1,2)],coords[,c(1,3)])
-  coords$Chromosome <- as.character(coords$Chromosome)
-  
-  ##sorting by chromosome and coordinate
-  coords <- coords[order(as.numeric(substr(coords$Chromosome,4,5)), coords$coordinate, decreasing = FALSE),]
-  
-  ##remove duplicates for coordinates that are conjoined
-  coords <- coords[!duplicated(coords),]
-  
-  bounds <- GRanges(seqnames=coords$Chromosome, ranges=IRanges(start=coords$coordinate, width=1))
-  
-  #chromsome specific boundary data
-  bounds_chr_specific <- bounds[which(as.character(seqnames(bounds))==tolower(chromosome))]
-  
-  return(bounds_chr_specific)
-}

### 2020-01-08 Scripts/functions_for_R_package/percent_predictor_types_func.r

@@ -1,33 +1,0 @@
-####calculating percent overlaps
-percent_func <- function(binned_data_gr, annot_data_gr){
-  count_percent <- numeric(length(binned_data_gr))
-  
-  #Finding the total number of overlaps between genomic bins and the specific genomic annotation
-  c <- countOverlaps(binned_data_gr, annot_data_gr)
-  
-  #places where c=0 denotes no overlap 
-  #places where c>0 denotes some type of overlap, could be partial or within
-  
-  #for c=0 assign percent overlap as 0
-  count_percent[which(c==0)] <- 0
-  
-  #for c=1:
-  count_percent[which(c==1)] <- width(pintersect(findOverlapPairs(annot_data_gr,binned_data_gr[which(c==1)])))/(width(binned_data_gr[1]))
-  
-  #for c>1:
-  #iterate through all bins with multiple overlaps with the annotation of interest
-  #find how many and which annotations overlap within each iterate
-  #calculate the width of each overlap
-  #sum the total widths and divide by bin width
-  #bins with some type of overlap
-  mo <- which(c>1)
-  count_percent[mo] <- unlist(
-    lapply(
-      lapply(
-        lapply(
-          mo, function(x){width(pintersect(findOverlapPairs(annot_data_gr,binned_data_gr[x])))}),
-        sum),
-      function(x){x/width(binned_data_gr[1])}))
-  
-  return(count_percent)
-}

### 2020-01-08 Scripts/functions_for_R_package/predict_at_bp_resolution_func.r

@@ -1,64 +1,0 @@
-#function to predict TAD boundaries at bp resolution
-predict_at_bp_resolution_func <- function(bounds.GR, resolution, chromosome, seqData, annotationListGR, tadModel){
-  resolution=as.integer(resolution)
-  
-  test_data <- matrix(nrow=length(seqData),
-                      ncol=length(annotationListGR))
-  
-  seqData <- c(seqData[1]-1, seqData)
-  
-  d <- lapply(annotationListGR, function(x){distance_func(GRanges(seqnames=tolower(chromosome),
-                                                                  IRanges(start=seqData,
-                                                                          end=seqData)), 
-                                                          x)})
-  for(i in 1:length(annotationListGR)){
-    test_data[,i] <- d[[i]]
-  }
-  
-  colnames(test_data) <- names(annotationListGR)
-  test_data <- apply(test_data,2,function(x){log(x + 1, base=2)})
-  
-  pred.tadModel <- predict(tadModel,newdata=test_data,type="prob")[,"Yes"]
-  
-  prob1basenumdiff <- diff(seqData[which(pred.tadModel==1)])
-  retain <- numeric()
-  x <- 1
-  for(i in 1:length(prob1basenumdiff)){
-    if(prob1basenumdiff[i]<=1){retain[i] = x}else{x = x+1; retain[i] = x}
-  }
-  retain = c(1,retain)
-  
-  mid <- numeric()
-  for(i in unique(retain)){
-    #print(i)
-    bpdat <- seqData[which(pred.tadModel==1)][which(retain==i)]
-    n=length(bpdat)
-    mid[i] <- ceiling((bpdat[1]+bpdat[n])/2)
-  }
-  
-  x <- dist(mid, method = "euclidean")
-  hc1 <- hclust(x, method = "complete")
-  z <- sapply(2:(length(mid)-1), function(i) { 
-    mean(silhouette(cutree(hc1, i), dist=x)[,"sil_width"]) })
-  k=which.max(z)+1
-  c <- clara(mid, 
-             k=k, 
-             samples=100,
-             metric = "euclidean",
-             stand = FALSE, 
-             trace = 2, 
-             medoids.x = TRUE)
-  
-  predBound_gr <- GRanges(seqnames=tolower(chromosome),
-                          IRanges(start=seqData[which(seqData %in% c$medoids)],
-                                  end=seqData[which(seqData %in% c$medoids)]))
[…]

### 2020-01-08 Scripts/functions_for_R_package/predict_tad_bounds_func.r

@@ -1,163 +1,0 @@
-#function to predict cl, resolution, and chromosome specific tad boundaries using optimal parameters
-predict_tad_bounds_func <- function(resolution, bounds.GR, datamatrix, chromosome, sampling="smote", metric="MCC", seed=123, crossvalidation=TRUE, number=10, featureSelection=FALSE){
-  resolution=as.integer(resolution)
-  
-  y <- ifelse(as.numeric(rownames(data_mat)) %in% start(bounds.GR), 1, 0)
-  
-  full_data <- cbind.data.frame(y, data_mat)
-  ##Changing levels of response (y) to yes no
-  full_data$y <- factor(full_data$y)
-  levels(full_data$y) <- c("No", "Yes")
-  
-  #splitting into training and testing
-  set.seed(seed)
-  inTrainingSet <- sample(length(full_data$y),floor(length(full_data$y)*.7))
-  train <- full_data[inTrainingSet,]
-  test <- full_data[-inTrainingSet,]
-  
-  if(sampling=="ros"){
-    #assign sample indeces
-    set.seed(seed)
-    sampids.train <- sample(x = which(train$y=="Yes"),
-                            size = length(which(train$y=="No")),
-                            replace = TRUE)
-    
-    train <- rbind.data.frame(train[which(train$y=="No"),],
-                              train[sampids.train,])
-    
-    #Randomly shuffle the data
-    set.seed(seed)
-    train <- train[sample(nrow(train)),]
-    
-  }else if(sampling=="rus"){
-    set.seed(123)
-    sampids.train <- sample(x = which(train$y=="No"),
-                            size = length(which(train$y=="Yes")),
-                            replace = FALSE)
-    
-    train <- rbind.data.frame(train[which(train$y=="Yes"),],
-                              train[sampids.train,])
-    
-    #Randomly shuffle the data
-    set.seed(321)
-    train <- train[sample(nrow(train)),]
-    
-  }else if(sampling=="smote"){
-    set.seed(seed)
-    train <- SMOTE(y ~ ., 
-                   data=train, 
-                   perc.over = 100, 
-                   perc.under = 200)
-    
-    #Randomly shuffle the data
-    set.seed(seed)
-    train <- train[sample(nrow(train)),]
-  }else{train=train}
-  
-  
-  ##defining one summary function for roc,auprc,f1,and mcc
[…]

### 2020-01-08 Scripts/functions_for_R_package/predict_tad_bounds_func_new.R

@@ -1,210 +1,0 @@
-#function to predict cl, resolution, and chromosome specific tad boundaries using optimal parameters
-predict_tad_bounds_func_new <- function(resolution, bounds.GR, annotationListGR, chromosome, predictortype=predictor, sampling="smote", metric="MCC", seed=123, crossvalidation=TRUE, number=10){
-  resolution=as.integer(resolution)
-  
-  seqData <- c(seqData[1]-1, seqData)
-  
-  start=0
-  end=seqData[length(seqData)] - (seqData[length(seqData)] %% resolution)
-  rows = seqData[seqData %in% seq(start, end, resolution)]
-  
-  data_mat <- matrix(nrow=length(rows),
-                     ncol=length(annotationListGR))
-  rownames(data_mat) <- rows
-  
-  dat_mat_gr <- flank(GRanges(seqnames = tolower(chromosome),
-                              IRanges(start = as.numeric(rownames(data_mat)),
-                                      #end = as.numeric(rownames(data_mat)),
-                                      width=1)), (resolution/2), both=TRUE)
-  
-  dat_mat_gr_dist <- GRanges(seqnames = tolower(chromosome),
-                             IRanges(start = as.numeric(rownames(data_mat)),
-                                     #end = as.numeric(rownames(data_mat)),
-                                     width=1))
-  
-  if(predictortype=="distance"){
-    for(i in 1:length(annotationListGR)){
-      d <- distance_func(dat_mat_gr_dist, annotationListGR[[i]])
-      data_mat[,i] <- d
-    }
-    data_mat <- apply(data_mat,2,function(x){log(x + 1, base=2)})
-    colnames(data_mat) <- names(annotationListGR)
-  }else if(predictortype=="binary"){
-    for(i in 1:length(annotationListGR)){
-      cb <- binary_func(dat_mat_gr, annotationListGR[[i]])
-      data_mat[,i] <- cb
-    }
-    colnames(data_mat) <- names(annotationListGR)
-  }else if(predictortype=="oc"){
-    for(i in 1:length(annotationListGR)){
-      co <- count_func(dat_mat_gr, annotationListGR[[i]])
-      data_mat[,i] <- co
-    }
-    colnames(data_mat) <- names(annotationListGR)
-  }else{
-    for(i in 1:length(annotationListGR)){
-      cp <- percent_func(dat_mat_gr, annotationListGR[[i]])
-      data_mat[,i] <- cp
-    }
[…]

### 2020-01-08 Scripts/functions_for_R_package/predict_tad_bounds_func_new_V2.R

@@ -1,216 +1,0 @@
-#function to predict cl, resolution, and chromosome specific tad boundaries using optimal parameters
-predict_tad_bounds_func_new_V2 <- function(resolution, bounds.GR, annotationListGR, chromosome, predictortype=predictor, sampling="smote", metric="MCC", seed=123, crossvalidation=TRUE, number=10){
-  resolution=as.integer(resolution)
-  
-  seqData <- c(seqData[1]-1, seqData)
-  
-  start=0
-  end=seqData[length(seqData)] - (seqData[length(seqData)] %% resolution)
-  rows = seqData[seqData %in% seq(start, end, resolution)]
-  
-  data_mat <- matrix(nrow=length(rows),
-                     ncol=length(annotationListGR))
-  rownames(data_mat) <- rows
-  
-  dat_mat_gr <- flank(GRanges(seqnames = tolower(chromosome),
-                              IRanges(start = as.numeric(rownames(data_mat)),
-                                      #end = as.numeric(rownames(data_mat)),
-                                      width=1)), (resolution/2), both=TRUE)
-  
-  dat_mat_gr_dist <- GRanges(seqnames = tolower(chromosome),
-                             IRanges(start = as.numeric(rownames(data_mat)),
-                                     #end = as.numeric(rownames(data_mat)),
-                                     width=1))
-  
-  if(predictortype=="distance"){
-    for(i in 1:length(annotationListGR)){
-      d <- distance_func(dat_mat_gr_dist, annotationListGR[[i]])
-      data_mat[,i] <- d
-    }
-    data_mat <- apply(data_mat,2,function(x){log(x + 1, base=2)})
-    colnames(data_mat) <- names(annotationListGR)
-  }else if(predictortype=="binary"){
-    for(i in 1:length(annotationListGR)){
-      cb <- binary_func(dat_mat_gr, annotationListGR[[i]])
-      data_mat[,i] <- cb
-    }
-    colnames(data_mat) <- names(annotationListGR)
-  }else if(predictortype=="oc"){
-    for(i in 1:length(annotationListGR)){
-      co <- count_func(dat_mat_gr, annotationListGR[[i]])
-      data_mat[,i] <- co
-    }
-    colnames(data_mat) <- names(annotationListGR)
-  }else{
-    for(i in 1:length(annotationListGR)){
-      cp <- percent_func(dat_mat_gr, annotationListGR[[i]])
-      data_mat[,i] <- cp
-    }
[…]

### 2020-01-08 Manuscript/Supplementary/supplementary_legends.Rmd
editted legends

@@
 
-**Supplementary Table 1. Hi-C data.** A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains.
+**Supplementary Table 1. Hi-C data.** A complete list of the Hi-C data libraries obtained from GEO GSE63525 [@rao20143d] used to obtain the locations of topologically associating domains.
 
@@
 The GRCh37/hg19 human genome assembly was used.
-"Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Available Cell Type" - the name of the cell type in which the annotation was available, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
+"Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
 

### 2020-01-08 Manuscript/manuscript.Rmd
edits

@@
 Biological replicate Hi-C data were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1) for the GM12878 and K562 cell lines.
-The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the Arrowhead algorithm [@durand2016juicebox].
+The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from Hi-C data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the ARROWHEAD algorithm [@durand2016juicebox].
 TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all resolutions and cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
 
-Genomic annotation data in the form of cell type specific chromatin states (ChromHMM), histone modifications (HM), and transcription factor binding sites (TFBS) were obtained from the UCSC Genome Browser Database (GRCh37/hg19 human genome assembly) [@Tyner:2017aa] (Supplementary Table 1).
+Genomic annotation data in the form of cell type-specific cis-regulatory elements (CSS), histone modifications (HM), and transcription factor binding sites (TFBS) were obtained from the UCSC Genome Browser Database (GRCh37/hg19 human genome assembly) [@Tyner:2017aa] (Supplementary Table 2).
 
@@
 
-To make the data amenable for model training, the genome was binned into equally sized intervals defined by the data resolution of the corresponding contact matrix.
-As an example, for domain data obtained from a 100 kb resolution contact matrix, the genome was binned into 100 kb intervals.
-To accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix.
-A genomic bin was defined as a TAD boundary region ($Y = 1$) if it overlapped with at least one flanked TAD boundary, and a non-TAD boundary region ($Y = 0$) otherwise.
-Random forest models were used to train on Arrowhead-predicted TAD boundary regions.
-Training was performed separately for each cell line, data resolution, and chromosome.
+To make the data amenable for model training, the genome was first binned into equally sized intervals defined by the data resolution (*r*) of the corresponding contact matrix.
+The binning was initiated at the chromosome-specific genomic coordinate marking half of the resolution, and continued in congruent intervals until the end of the chromosome (*mod r* + *r/2*).
+This was to ensure that called (ground truth) TAD boundaries would be positioned in the center of genomic bins.
+Genomic bins were then defined as TAD boundary regions (*Y = 1*) if they contained a TAD boundary, and non-TAD boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for random forest classification.
 
-Cell line-specific genomic annotations were used to built the predictors for of our random forest models.
-We created three types of predictors (Figure 1): **Overlap Count (OC)** - the total number of overlaps between a bin and genomic annotation regions;  **Overlap Percent (OP)** - the percent of overlap between the bin and the total width of genomic annotation regions overlapping it; **Log2 Distance** - the $log_{2}$ of the distance in bases (refered to hereafter as *Distance*), from the center of the bin to the center of the nearest genomic annotation region.
+Cell type-specific genomic annotations were used to build the predictor space for of our random forest models.
+We created three types of predictors: *Overlap Count (OC)* - the total number of overlaps between a bin and genomic annotation regions;  *Overlap Percent (OP)* - the percent of overlap between the bin and the total width of genomic annotation regions overlapping it; *Log2 Distance* - the $log_{2}$ of the distance in bases (refered to hereafter as *Distance*), from the center of the bin to the center of the nearest genomic annotation region.
 
-The complete dataset used for modeling was composed of two components: the response vector **Y**, an indicator variable separating between TAD and non-TAD boundary regions, and the predictor-type specific data matrix, **X** = {$X_1$, $X_2$, ..., $X_p$}, where $p$ was the set of predictors.
-One, or all types of predictors were used as described.
-The data was split into a 7:3 ratio of training and testing sets.
+The chromosome-specific dataset used for modeling was composed of two components: the response vector **Y**, an indicator variable separating between TAD and non-TAD boundary regions, and the predictor-type specific data matrix, **X** = {$X_1$, $X_2$, ..., $X_p$}, where $p$ was the set of genomic annotations.
+<!--One, or all types of predictors were used as described.
+The data was split into a 7:3 ratio of training and testing sets.-->
 
-### Addressing class imbalance
+## Addressing class imbalance
 
@@
 CI of heavily imbalanced classes approaches 0, while CI for balanced classes approaches 0.50.
-To assess the effect of CI on predictive performance, we first used the data with **No Sampling**, that is, the majority and minority classes were used as is.
+To assess the effect of CI on predictive performance, we first used the data with *No Sampling*, that is, the majority and minority classes were used as is.
 We evaluated three re-sampling techniques.
-For **Random Under-Sampling (RUS)**, the majority class was sampled without replacement to obtain the same number of data points in the minority class.
-For **Random Over-Sampling (ROS)**, the minority class was sampled with replacement to obtain the same number of data points in the majority class.
-For **SMOTE** (Synthetic Minority Over-Sampling Technique), under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the $k=5$ minority class nearest neighbors [@chawla2002smote] (implemented in the `DMwR` v.0.4.1 R package).
+For *Random Under-Sampling (RUS)*, the majority class was sampled without replacement to obtain the same number of data points in the minority class.
+For *Random Over-Sampling (ROS)*, the minority class was sampled with replacement to obtain the same number of data points in the majority class.
+For *SMOTE* (Synthetic Minority Over-Sampling Technique), under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the $k=5$ minority class nearest neighbors [@chawla2002smote] (implemented in the `DMwR` v.0.4.1 R package).
 We restricted the algorithm to 100% over-sampling and 200% under-sampling, which creates perfectly balanced classes.
 
-### Assessment of model performance
+## Assessment of model performance
 
 Random forest classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, predictor types, and re-sampling techniques.
-Ten-fold cross validation was used to tune the number of annotations, *p*, to consider at each node.
-[???
-Isn't it used for preventing overfitting?
-TBD] The number of trees that were aggregated for each random forest model was set to $n=500$.
-
+Five-fold cross validation was used to tune the number of annotations, *p*, to consider at each node.
+The number of trees that were aggregated for each random forest model was set to the default, $n=500$.
 The performance of each model was compared using Matthews Correlation Coefficient (MCC), defined as <!--The MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
@@
 
-### Feature reduction
+## Feature reduction
 
@@
 
-## Using optimally built random forest classifiers for more precise TAD boundary prediction
+## Precise TAD boundary prediction at bp resolution
 
+Next, we aimed to investigate whether we could alleviate resolution limitations that plague conventional TAD calling algorithms.
+To do so, we extended our optimally built TAD prediction models to obtain predictions at base pair (bp) resolution.
+Naturally, when dealing with such fine resolution, there will exist collections of spatially close base pairs with similar predictor profiles (i.e.
+similar distances), and will thus yield similar predictions.
+To guard against inflating the number of predicted TAD boundaries we developed a technique that combines both hierarchical clustering and partitioning techniques to identify more precise TAD boundaries throughout the linear genome.
+
+We first established a *predicted TAD boundary area* (PTBA) as a collection of adjacent base pairs that have been identified as being a predicted TAD boundary (using the optimal probability threshold identified by the combination of TPR and FPR closest to the point (0,1) on the ROC curve).
+We then performed hierarchical clustering on the pairwise distances (in base pairs) between the midpoints of each PTBA using complete linkage clustering.
+To identify the optimal number of clusters, *k*, we calculated the mean silhouette score over all possible sizes of clusters *m*:
+
+$$\bar{s}_{m} = \dfrac{\sum^{m}_{i} s_{i}}{m},$$
+
+where $s_{i}$ is the cluster-specific silhouette score defined as,
+
+$$s_{i} = \dfrac{b_{i} - a_{i}}{max[a_{i},b_{i}]}.$$
+
+Here, $a_{i}$ is the mean distance between each cluster entry and all other observations in the same cluster, and $b_{i}$ is the mean distance between entries within the same cluster.
+Therefore number of clusters, *k*, that maximized the mean silhouette score, $\bar{s}_{m}$ were used to identify groupings of PTBA, which we defined as *predicted TAD boundary regions* (PTBR).
+
+To precisely identify the PTBA most representative of each PTBR we performed an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
+The midpoint of the corresponding cluster medoid, in this case a particular PTBA, will be defined as a *predicted TAD boundary point* (PTBP).
+In the event that a particular PTBA has an even number of base pairs, then ceiling function was applied to extract the right most base pair.
+Thus, the hierarchical structure of our defined predicted TAD boundary objects were as follows: PTBR > PTBA > PTBP.
+That is, each PTBR is a collection of PTBAs, which are themselves a collection of adjacent base pairs.
+The uniquely identified PTBP was then the midpoint of the most representative PTBA within a PTBR.
+
+<!--
 Using optimally trained models, we established *predicted TAD boundary regions* as a collection of adjacent bases predicted as TAD boundary with the probability of 1.
@@
 REWRITE!]
+-->
+
+## Comparing Called vs Predicted TAD boundaries
+
+To evaluate if our predicted TAD boundaries are biologically significant we will asssess the signal strength obtained from key ChIP-Seq peak elements known to be enriched at TAD boundaries including CTCF, RAD21, SMC3, and ZNF143.
+To do so we will used enrich heatmaps and Student’s t-tests to compare distances from selected ChiP-seq data to our predicted TAD boundaries compared to called TAD boundaries (ARROWHEAD).
+
+Furthermore, we will assess the conservation of our predicted TAD boundaries within cell types and between resolutions, as well as between cell types and within resolutions and compare with ARROWHEAD called TAD boundaries.
+To do so we will evaluate Jaccard Indices.
+Jaccard is a metric used to measure overlap between sets (genomic regions).
+Thus we can use it as measure of overlap between TAD boundaries.
+Given two sets of TAD boundaries (either between resolution or cell type) A and B, we define the Jaccard Index as,
+
+$$J_{(A,B)} = \dfrac{A \cap B}{A \cup B}.$$
+To give the sets of boundaries A and B dimensionality to enable us to calculate overlap, we flank each boundary point by a flanking factor, *f*=5000.
 
@@
 
+<!--
 ![**Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** (A) Unique boundaries are denoted by the blue dots.
@@
 ](Figures/model_construction_and_predictor_types.png)
+-->
 
@@
 
+<!--
 ![**A diagram of the ensemble framework detailing the combination of inputs used in the model building pipeline.** Each cell line (GM12878, K562) specific model was composed of a combination of different data level characteristics including resolution (5 kb, 10 kb, 25 kb, 50 kb, 100 kb), predictor type (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)), and re-sampling technique (no re-sampling (None), random over-sampling (ROS), random under-sampling (RUS), synthetic minority over-sampling technique (SMOTE)).
 The three types of genomic annotations, histone modification (HM), chromating state segmentations (ChromHMM), transcription factor binding sites (TFBS), were used as predictors.](Figures/figure3_ensemble_framework_V3.png)
+-->
 
@@
 
+<!--
 ![**Models built using distance-type predictors combined with SMOTE re-sampling yielded optimal MCCs across resolution.** Barplots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
@@
 Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/model_performances_v3_bars.png)
+-->
 
@@
 
+<!--
 ![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) Barplots comparing performances of models using specific groups of functional genomic annotation as the feature space including histone modifications (HM; red), chromatin states (ChromHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all three groups (Combined; purple).
@@
 Error bars represent standard deviation from the mean MCC across each chromosome.](Figures/annot_specific_rfe_varimps_heatmap.png)
+-->
 
@@
 
+<!--
 ![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17390000-18640000; GM12878).
@@
 (B) Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by SMC3, ZNF143, CTCF, and RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.](Figures/visualizing_boundaries_example_with_enriched_heatmaps.png)
+-->
 

### 2020-01-08 Manuscript/manuscript.Rmd
edits

@@
 
-<!--
 ![**Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** (A) Unique boundaries are denoted by the blue dots.
-The yellow regions denote the flanked boundary regions according to the Hi-C data resolution (i.e., 100 kb resolution corresponded to a 100 kb flank for a total boundary region of 200 kb).
 The linear genome was subsequently binned into resolution-specific intervals.
-The response vector **Y** was defined as a genomic bin that either overlapped with a flanked TAD boundary ($Y = 1$) or did not ($Y = 0$).
-(B) Three types of associations between bins and genomic annotations (green shapes) used to build the feature space include _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
+The response vector **Y** was defined as a genomic bin that either overlapped with a TAD boundary ($Y = 1$) or did not ($Y = 0$).
+(B) Three types of associations between bins and genomic annotations (green shapes) used to build the feature space of random forest classification models include _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
 ](Figures/model_construction_and_predictor_types.png)
--->
 

### 2020-01-09 Scripts/data_summaries.R
initial commit

@@ -1,0 +1,113 @@
+
+CHR = paste0("CHR", c(1:8,10:22))
+numtads <- numeric()
+numbounds <- numeric()
+numbins <- numeric()
+imbalance <- numeric()
+r = c("5000","10000","25000","50000","100000")
+
+getChrLength <- function(genome = "BSgenome.Hsapiens.UCSC.hg19"){
+  g <- getBSgenome(genome, masked=FALSE)
+  data.frame(chrom=1:24, length=seqlengths(g)[1:24])
+}
+.chrAsNum <- function(tbl){
+  tbl$chrom <- gsub("chr", "", tbl$chrom)
+  tbl$chrom[tbl$chrom=="X"] <- 23
+  tbl$chrom[tbl$chrom=="Y"] <- 24
+  tbl$chrom <- as.numeric(tbl$chrom)
+  tbl[order(tbl$chrom),]
+}
+getCentromeres <- function( genome="hg19" ){
+  mySession <- try(browserSession("UCSC"), silent=TRUE)
+  # In case of failure, try another mirror
+  if(inherits(mySession, "try-error"))
+    mySession <- browserSession("UCSC",
+                                url="http://genome-euro.ucsc.edu/cgi-bin/")
+  genome(mySession) <- genome
+  obj <- ucscTableQuery(mySession, table="gap")
+  tbl <- getTable(obj)
+  tbl <- tbl[tbl$type=="centromere", c("chrom", "chromStart", "chromEnd")]
+  colnames(tbl)[2:3] <- c("centromerStart", "centromerEnd")
+  .chrAsNum(tbl)
+}
+makeHg19 <- function(){
+  tbl <- merge(getChrLength(), getCentromeres(), by="chrom")
+  cumlen <- c(0, cumsum(as.numeric(tbl$length))[-nrow(tbl)])
+  cbind.data.frame(tbl, cumlen=cumlen)    
+}
+hg19 <- makeHg19()
+hg19$chrom <- paste0("CHR",hg19$chrom)
+
+seqLength <- hg19$length[hg19$chrom %in% CHR]
+seqDataList <- list()
+for(k in 1:length(seqLength)){
+  seqData <- c(0:seqLength[k])
+  centromereStart <- hg19$centromerStart[hg19$chrom==CHR[k]]
+  centromereEnd <- hg19$centromerEnd[hg19$chrom==CHR[k]]
[…]

### 2020-01-09 Manuscript/manuscript.Rmd
edits

@@
 Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [@dixon2012topological; @sofueva2013cohesin]), we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, across each of the five resolutions respectively (Table 1).
+<!--After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [@dixon2012topological; @sofueva2013cohesin]),--> We obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, across each of the five resolutions respectively (Table 1).
 Similar numbers of TAD boundaries were found for the K562 cell line.
@@
 
-| Resolution | Total number of called TADs | Total number of unique TAD boundaries | Average Class Imbalance ($\pm$ SD) |
-|:----------:|:---------------------------:|:-------------------------------------:|:----------------------------------:|
-|5 kb        |8043 (4750)                  | 16133 (9314)                          | 0.06 $\pm$ 0.02 (0.04 $\pm$ 0.02)  |
-|10 kb	     |7650 (5796) 	               | 14824 (10881)                         | 0.10 $\pm$ 0.01 (0.08 $\pm$ 0.02)  |
-|25 kb	     |4208 (3675)                  | 8081 (6923)                           | 0.14 $\pm$ 0.01 (0.12 $\pm$ 0.01)  |   
-|50 kb	     |1772 (1617)	                 | 3560	(3197)                           | 0.12 $\pm$ 0.01 (0.11 $\pm$ 0.01)  |
-|100 kb	     |444	(399)                    | 919	(831)                            | 0.06 $\pm$ 0.01 (0.06 $\pm$ 0.01)  |    
-Table: Domain data and class imbalance summaries across resolutions for GM12878 (K562).
+| Resolution | Total number of called TADs | Total number of unique TAD boundaries | Total number of Genomic Bins | Class Imbalance |
+|:----------:|:---------------------------:|:-------------------------------------:|:----------------------------:|:---------------:|
+|5 kb        |8052                         | 15468                                 | 535363                       | 0.03            |
+|10 kb	     |7676 	                       | 14253                                 | 267682                       | 0.05            |
+|25 kb	     |4670                         | 8363                                  | 107073                       | 0.08            |
+|50 kb	     |2349	                       | 4224                                  | 53537                        | 0.08            |
+|100 kb	     |1031                         | 1883                                  | 26768                        | 0.07            |
+Table: Domain data and class imbalance summaries across resolutions for GM12878.
 

### 2020-01-09 Manuscript/Figures/figure_legends.Rmd
edits

--- 2019-05-29 Manuscript/Figures/figure_legends.Rmd
@@
 **Figure 1.
-Ensemble Framework.** A diagram of the cell line specific ensemble framework detailing the various combination of inputs used in the model building pipeline.
-The minoirty and majority classes were represented by the genomic bins that overlapped with flanked TAD boundaries or did not, respectively.
-Functional genomic annotations obtained from the UCSC Genome Browser Database composed the feature space.
-The data was split into a 7:3 training to testing set ratio.
-A feature engineering step was included to isolate the spatial relationship, of increasing granularity, between annotations and genomic bins.
-Data re-sampling and regularization was applied to the training data.
-Lastly, a random forest classification algorithm was implemeted and validated on the testing data.
-
-<!--
-A given system within the ensemble framework included the total number of genomic bins, labeled as having been overlapped with a flanked TAD boundary ($Y=1$) or not ($Y=0$).
-The data matrix that composed the feature space was composed of predictor-type specific annotations represented by $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
-The data was then split into a 7:3 training to testing set ratio.
-A re-sampling technique was applied to the training set, followed by an elastic-net regularization to reduce the feature space.
-Lastly, a random forest classification model was performed on the re-sampled and reduced training set and validated on the held out testing set common to all ensemble systems in the framework.
--->
+Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** (A) Unique boundaries are denoted by the blue dots.
+The linear genome was subsequently binned into resolution-specific intervals.
+The response vector **Y** was defined as a genomic bin that either overlapped with a TAD boundary ($Y = 1$) or did not ($Y = 0$).
+(B) Three types of associations between bins and genomic annotations (green shapes) used to build the feature space of random forest classification models include _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
 
 **Figure 2.
-Model Construction.** An illustration of the proposed model construction given cell line specific Hi-C data.
-Above is an example of a subsection of the contact matrix for chromosome 14 (at megabase scale) on GM12878 [@durand2016juicer].
-The contact matrix is a visualization of the interconnectivity of the linear genome at 100 kb resolution.
-The boundary coordinates of TADs were identified using the Arrowhead algorithm.
-To account for the uncertainty in TAD boundary detection, each boundary point was flanked on both sides by resolution-specific genomic regions (bins).
-The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region ($Y=1$) or not ($Y=0$).
-The spatial relationship between positional coordinates of various functional genomic annotations, obtained from the UCSC Genome Browser Database, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.
-
-**Figure 3.
-Predictor types.** Three separate types of predictors were considered when quantifying the association between TAD boundaries and genomic annotations.
-Each predictor type was used to build the feature space of specific models in the ensemble framework.
-(A) _Overlap Counts_ (OC) consider the total number of genomic features that overlapped with each genomic bin.
-(B) _Overlap Percent_ (OP) was calculated by dividing the sum of all feature widths within each specific bin by the total bin width.
-(C) _Distance_ ($log_{2}$ transformed) was calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest region defining a genomic annotation.
-
-**Figure 4.
-SMOTE re-sampled models built on distance-type predictors yielded optimal MCCs across resolutions for GM12878.** Performances of random forest classification models built on each of the 3 predictor types: (A) OC, (B) OP, and (C) Distance.
-Within each predictor type, and across resolution, training data was re-sampled using different techniques including: None (red), ROS (green), RUS (blue), and SMOTE (purple).
-Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.
-
-**Figure 5.
-The proportional importance of optimally built predictive models was outweighed by transcription factor binding sites across resolutions for GM12878.** Stacked barplots illustrate the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework (SMOTE re-sampling; with distance-type predictors), for each resolution on GM12878.
-Proportions are grouped by the class of cell line specific annotations in the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).
-
-**Figure 6.
-Optimally built TFBS-specific models outperformed other annotation-specific models across resolution for GM12878** Performances were compared for random forest models built using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
-Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types.
-The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.
-
-**Figure 7.
-Top 20 most predictive transcription factor binding sites sorted by 10 kb for GM12878.** A heatmap illustrating the importance of the key cell line specific transcription factors for optimally built random forest models across resolution.
-Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100.
-Transcription factors with higher values of predictive importance are denoted in dark red.
-
-**Figure 8.
-Top predictive transcription factor binding sites were significantly closer to bins that overlapped with 10 kb flanked TAD boundaries on GM12878** Boxplots illustrating the distribution of distances (on $log_{2}$ scale) around 10 kb regions on the linear genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential cell line specific TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
-P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].
+A diagram of the ensemble framework detailing the steps for combining different inputs used in the random forest model building pipeline.** Step 1 is to establish the rowise (genomic bins) and colwise (genomic annotations) dimensions of the data matrix, **A**, by combining a resolution (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)).
+Step 2 is to split **A** into a training and testing set according to a 7:3 ratio.
+Step 3 is to apply a re-sampling technique to the training set (no re-sampling, random over-sampling, random under-sampling, or SMOTE re-sampling).
+Step 4 is to implement the random forest algorithm and perform 5-fold cross-validation to tune for the *mtry* parameter.
+Finally, step 5 is to validate the model on the separate test data for unbiased model evaluation.

### 2020-01-09 Manuscript/Supplementary/supplementary_legends.Rmd
edits

@@
 
+**Supplementary Table 3.** Domain data and class imbalance summaries across resolutions for GM12878.
+
 **Supplementary Figure 1.
-Performing $log_{2}$ transformations normalized skewed distance densities across resolution for GM12878.** When measured in basepairs, distances were highly right skewed for all resolutions: (A) 10 kb, (B) 25 kb, (C) 50 kb, and (D) 100 kb.
-After $log_{2}$ transforming the distances, densities became much more gaussian distributed for all resolutions: (E) 10 kb, (F) 25 kb, (G) 50 kb, and (H) 100 kb.
-Each density curve represents a cell line specific annotation, and its relationship with all resolution specific genomic bins.
-
-**Supplementary Figure 2.
-Performing $log_{2}$ transformations normalized skewed distance densities across resolution for K562.** When measured in basepairs, distances were highly right skewed for all resolutions: (A) 10 kb, (B) 25 kb, (C) 50 kb, and (D) 100 kb.
-After $log_{2}$ transforming the distances, densities became much more gaussian distributed for all resolutions: (E) 10 kb, (F) 25 kb, (G) 50 kb, and (H) 100 kb.
-Each density curve represents a cell line specific annotation, and its relationship with all resolution specific genomic bins.
-
-**Supplementary Table 3.
-Data Summaries and Imbalance Ratios.** For K562, average number of genomic bins, TADs called, and the corresponding boundaries and imbalance ratios, across each of the autosomal chromosomes (omitting chromosome 9), stratified by resolution.
-The resolution of the Hi-C contact matrix dictated the width of each genomic bin, with lower resolutions corresponding to wider genomic bins.
-
-**Supplementary Table 4.
-Inter-Resolution ICCs.** For K562, two-way intraclass correlation coefficients between resolutions for the following quantities: Number of genomic bins, number of TADs called, number of unique TAD boundaries, and imbalance ratio.
-The ICC was computed across 21 of the autosomal chromosomes.
-All quatities, except for imbalance ratio, was correlated with data resolution.
-Instead, imbalance ratios remained consistent and low across resolutions.
-
-**Table 5.
-Jaccard Indices.** For K562, the median (range) Jaccard index illustrating the pairwise similarity between annotations within specific groups, including chromatin segmentation states, histone modifications, and transcription factor binding sites.
-The Jaccard Index measures the ratio of the number of intersecting base pairs between any two sets, to the number of base pairs in the union of the two sets.
-The number of cell line specific annotations included within each group is also provided.
-
-**Supplementary Table 6. Full list of aggregated performances for GM12878.** Performances were stratified by resolution, resampling technique, and predictor type, and then averaged across chromosomes.
-
-**Supplementary Table 7. Full list of aggregated performances for K562.** Performances were stratified by resolution, resampling technique, and predictor type, and then averaged across chromosomes.
-
-**Supplementary Figure 3.
-SMOTE re-sampled models built on distance-type predictors yielded optimal MCCs across resolutions for K562.** Performances of random forest classification models built on each of the 3 predictor types: (A) OC, (B) OP, and (C) Distance.
-Within each predictor type, and across resolution, training data was re-sampled using different techniques including: None (red), ROS (green), RUS (blue), and SMOTE (purple).
-Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.
-
-**Supplementary Figure 4.
-The proportional importance of optimally built predictive models was outweighed by transcription factor binding sites across resolutions for K562.** Stacked barplots illustrate the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework (SMOTE re-sampling; with distance-type predictors), for each resolution on GM12878.
-Proportions are grouped by the class of cell line specific annotations in the feature space including chromatin state segmentations (CSS), histone modifications (HM), and transcription factor binding sites (TFBS).
-
-**Supplementary Figure 5.
-Optimally built TFBS-specific models outperformed other annotation-specific models across resolution for K562** Performances were compared for random forest models built using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple).
-Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types.
-The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.
-
-**Supplementary Figure 6.
-Top 20 most predictive transcription factor binding sites sorted by 10 kb for K562.** A heatmap illustrating the importance of the key cell line specific transcription factors for optimally built random forest models across resolution.
-Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100.
-Transcription factors with higher values of predictive importance are denoted in dark red.
-
-**Supplementary Figure 9.
-Top predictive transcription factor binding sites were significantly closer to bins that overlapped with varying units of flanked TAD boundaries on GM12878** Boxplots illustrating the distribution of distances (on $log_{2}$ scale) around (A) 25 kb, (B) 50 kb, and (C) 100 kb regions on the linear genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential cell line specific TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281.
-P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].
-
-**Supplementary Figure 10.
-Top predictive transcription factor binding sites were significantly closer to bins that overlapped with varying units of flanked TAD boundaries on K562** Boxplots illustrating the distribution of distances (on $log_{2}$ scale) around (A) 10 kb, (B) 25 kb, (C) 50 kb, and (D) 100 kb regions on the linear genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential cell line specific TFBS including SMC3, CTCF, RAD21, and ZNF143.
-P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [$NS$ = p > 0.05; $*$ = 0.01 < p $\le$ 0.05; $**$ = 0.001 < p $\le$ 0.01; $***$ = 0.0001 < p $\le$ 0.001; $****$ = p $\le$ 0.00001].
-
-<!--
-**Supplementary Figure 12.
-Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 25 kb resolution, on GM12878.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D).
-For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary.
-That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
--->
+Performing $log_{2}$ transformations normalized skewed genomic distance densities across all resolutions.** When measured in basepairs, distances were highly right skewed for all resolutions for both the (A) GM12878 and (B) K562 cell lines.
+After $log_{2}$ transforming the distances, densities became much more gaussian distributed for all resolutions.

### 2020-01-09 Manuscript/manuscript.Rmd
edits

@@
 
-Genomic annotation data in the form of cell type-specific cis-regulatory elements (CSS), histone modifications (HM), and transcription factor binding sites (TFBS) were obtained from the UCSC Genome Browser Database (GRCh37/hg19 human genome assembly) [@Tyner:2017aa] (Supplementary Table 2).
+Genomic annotation data in the form of cell type-specific cis-regulatory elements (CRE), histone modifications (HM), and transcription factor binding sites (TFBS) were obtained from the UCSC Genome Browser Database (GRCh37/hg19 human genome assembly) [@Tyner:2017aa] (Supplementary Table 2).
 
@@
 Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-<!--After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [@dixon2012topological; @sofueva2013cohesin]),--> We obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, across each of the five resolutions respectively (Table 1).
-Similar numbers of TAD boundaries were found for the K562 cell line.
-To account for the variability in boundary location due to varying resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1A).
-TAD boundary regions were defined as regions on the linear genome where a genomic bin overlapped with a flanked TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as the regions that did not overlap with a flanked TAD boundary ($Y = 0$).
-On average, we found that only $18.0 \pm 4.6 \%$ of TAD boundary regions overlapped between both cell lines.
-Given the cell type specificity of TAD boundaries, we opted to build cell line specific models for predicting TAD boundary regions.
-The results presented are for the GM12878 cell line, with K562 results presented in the Supplementary material.
-In summary, we developed a framework enabling resolution-specific prediction of TAD boundaries, with resolution-specific bins defining the response variable.
+<!--After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [@dixon2012topological; @sofueva2013cohesin]),--> The results presented are for the GM12878 cell line, with K562 results presented in the Supplementary material.
+We obtained a total of 8052, 7676, 4670, 2349, and 1031 called TADs across each resolution respectively (Table 1).
+From the called TADs we obtained a total of 15468, 14253, 8363, 4224, and 1883 unique TAD boundaries (Table 2).
+The resolution-specific approach we developed to create TAD vs non-TAD boundary regions amenable for binary classification (See Methods) resulted in a total of 535363, 267682, 107073, 53537, and 26768 genomic bins.
+TAD boundary regions were defined as regions on the linear genome where a genomic bin contained a called TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as genomic bins that did not contain a TAD boundary ($Y = 0$) (Figure 1A).
 
-| Resolution | Total number of called TADs | Total number of unique TAD boundaries | Total number of Genomic Bins | Class Imbalance |
+## TAD vs. non-TAD boundary class imbalance is severe irrespectively of Hi-C data resolution
+
+Under this construction, the class imbalance among the genomic bins was found to be both severe and invariant toward resolution.
+Specifically, we found the imbalance between TAD boundary and non-TAD boundary regions to be 0.03, 0.05, 0.08, 0.08, and 0.07 for each resolution respectively (Table 2).
+Furthermore, the data summaries presented in Table 1 were found to be similar to those exibited by the K562 cell line (Supplementary Table 3).
+
+| Resolution | Total number of called TADs | Total number of unique TAD boundaries | Total number of genomic bins | Class imbalance |
 |:----------:|:---------------------------:|:-------------------------------------:|:----------------------------:|:---------------:|
@@
 
-A total of 78 cell type specific functional genomic annotations for the GM12878 and K562 cell line were used to build the feature space of downstream predictive models (Supplementary Table 1).
-The annotations could be broken down into three sets including histone modifications (HM), chromatin state segmentations (ChromHMM), and transcription factor binding sites (TFBS).
+A total of 78 cell type specific functional genomic annotations were used to build the feature space of downstream random forest models (Supplementary Table 1).
+The annotations could be broken down into three sets including histone modifications (HM), cis-regulatory elements (CRE), and transcription factor binding sites (TFBS).
 We constructed three different predictor types for each functional genomic annotation (Figure 1B).
-Counts of overlaps (**overlap count**, OC) were defined as the total number of genomic annotation regions that overlapped within a given genomic bin.
-Percents of overlaps (**overlap percent**, OP) were defined as the proportion of a bin overlapped by an annotation region.
+Counts of overlaps (**Overlap Counts**, OC) were defined as the total number of genomic annotation regions that overlapped within a given genomic bin.
+Percents of overlaps (**Overlap Percent**, OP) were defined as the proportion of a bin overlapped by an annotation region.
 **Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations.
-A log2-transformation of distance was used to account for the skewness present in the distributions of distances (Supplementary Figure 1).
+A log2-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
 These feature engineering steps were performed to improve TAD boundary predictions by accounting for direct (OC), proportional (OP), and indirect (distance) relationships between TAD boundaries and genomic annotations.
@@
 
-## TAD vs. non-TAD boundary class imbalance is severe irrespectively of Hi-C data resolution
+## Building an ensemble framework for TAD boundary prediction
 
-Given that the number of bins annotated as TAD boundaries (TAD boundary regions) is much smaller than the number of non-TAD boundary bins, we investigated the class imbalance (CI) featured at each resolution.
-The CI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions and ranging from 0 to 0.50.
-The CI was found to be invariant to resolution, remaining consistently low across chromosomes, with an averages of 0.06, 0.10, 0.14, 0.12, and 0.06 across each resolutions for GM12878 (Table 1).
-Similar class imbalances were found for the K562 cell line.
-To account for such imbalance, we evaluated three re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries.
+To account for the heavily imbalanced classes reported above, we evaluated three re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries.
 **Random over-sampling** (ROS) was defined as sampling with replacement from TAD boundary regions.
@@
 
-## Ensemble framework for TAD boundary prediction
-
 To identify the combination of data resolution, predictor type, and re-sampling technique necessary for optimal cell line specific TAD boundary prediction, we created an ensemble framework to systematically compare performances of different model inputs (Figure 2).
-The framework uses data for a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, using one of the predictor type *P = {OC, OP, Distance}*, and the re-sampling technique *B = {None, RUS, ROS, SMOTE}*.
-Once the model inputs were established, a random forest classifier was trained on chromosome-specific datasets using 10-fold cross validation.
+The framework uses data for a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, using a particular predictor type *P = {OC, OP, Distance}*, and re-sampling technique *B = {None, RUS, ROS, SMOTE}*.
+Once the model inputs were established, a random forest classifier was trained on chromosome-specific datasets using 5-fold cross validation.
 The different combinations of inputs were evaluated by assessing the Matthews Correlation Coefficient (MCC) of each model.
@@
 
-<!--
-![**A diagram of the ensemble framework detailing the combination of inputs used in the model building pipeline.** Each cell line (GM12878, K562) specific model was composed of a combination of different data level characteristics including resolution (5 kb, 10 kb, 25 kb, 50 kb, 100 kb), predictor type (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)), and re-sampling technique (no re-sampling (None), random over-sampling (ROS), random under-sampling (RUS), synthetic minority over-sampling technique (SMOTE)).
-The three types of genomic annotations, histone modification (HM), chromating state segmentations (ChromHMM), transcription factor binding sites (TFBS), were used as predictors.](Figures/figure3_ensemble_framework_V3.png)
--->
+![**A diagram of the ensemble framework detailing the steps for combining different inputs used in the random forest model building pipeline.** Step 1 is to establish the rowise (genomic bins) and columnwise (genomic annotations) dimensions of the data matrix, **A**, by combining a resolution (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)).
+Step 2 is to split **A** into a training and testing set according to a 7:3 ratio.
+Step 3 is to apply a re-sampling technique to the training set (no re-sampling, random over-sampling, random under-sampling, or SMOTE re-sampling).
+Step 4 is to implement the random forest algorithm and perform 5-fold cross-validation to tune for the *mtry* parameter.
+Finally, step 5 is to validate the model on the separate test data for unbiased model evaluation.](Figures/ensemble_framework.png)
 

### 2020-01-09 Scripts/data_summaries.R
added k562 results

@@ -1,4 +1,6 @@
 
+# GM12878
+
 CHR = paste0("CHR", c(1:8,10:22))
 numtads <- numeric()
 numbounds <- numeric()
@@ -111,3 +113,119 @@ data.frame(resolution = c("5 kb",
            numbins=numbins,
            imbalance=imbalance)
 
+
+#########################################################################################
+
+# K562 
+
+CHR = paste0("CHR", c(1:8,10:22))
+numtads <- numeric()
+numbounds <- numeric()
+numbins <- numeric()
+imbalance <- numeric()
+r = c("5000","10000","25000","50000","100000")
+
+getChrLength <- function(genome = "BSgenome.Hsapiens.UCSC.hg19"){
+  g <- getBSgenome(genome, masked=FALSE)
+  data.frame(chrom=1:24, length=seqlengths(g)[1:24])
+}
+.chrAsNum <- function(tbl){
+  tbl$chrom <- gsub("chr", "", tbl$chrom)
+  tbl$chrom[tbl$chrom=="X"] <- 23
+  tbl$chrom[tbl$chrom=="Y"] <- 24
+  tbl$chrom <- as.numeric(tbl$chrom)
+  tbl[order(tbl$chrom),]
+}
+getCentromeres <- function( genome="hg19" ){
+  mySession <- try(browserSession("UCSC"), silent=TRUE)
+  # In case of failure, try another mirror
+  if(inherits(mySession, "try-error"))
+    mySession <- browserSession("UCSC",
+                                url="http://genome-euro.ucsc.edu/cgi-bin/")
+  genome(mySession) <- genome
+  obj <- ucscTableQuery(mySession, table="gap")
+  tbl <- getTable(obj)
+  tbl <- tbl[tbl$type=="centromere", c("chrom", "chromStart", "chromEnd")]
+  colnames(tbl)[2:3] <- c("centromerStart", "centromerEnd")
+  .chrAsNum(tbl)
+}
+makeHg19 <- function(){
+  tbl <- merge(getChrLength(), getCentromeres(), by="chrom")
+  cumlen <- c(0, cumsum(as.numeric(tbl$length))[-nrow(tbl)])
+  cbind.data.frame(tbl, cumlen=cumlen)    
+}
+hg19 <- makeHg19()
+hg19$chrom <- paste0("CHR",hg19$chrom)
+
+seqLength <- hg19$length[hg19$chrom %in% CHR]
[…]

### 2020-01-09 Manuscript/Figures/figure_legends.Rmd
edits

@@
 Finally, step 5 is to validate the model on the separate test data for unbiased model evaluation.
+
+**Figure 3.
+Models built using distance-type predictors combined with random under-sampling yielded optimal predictive performance.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
+Performances are compared across resolution, within each predictor-type: (A) OC, (B) OP, and (C) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.

### 2020-01-09 Manuscript/manuscript.Rmd
edits

@@
 
-## SMOTE re-sampling, distance-based associations of TAD boundaries and genomic annotations, and 10 kb resolutions of Hi-C data provided optimal model performance
+## Random under-sampling, distance-based predictors, and 10 kb resolutions of Hi-C data provided the optimal data level characteristics for TAD boundary prediction
 
@@
 The reason for the improved performance between 5 kb and 10 kb data resolutions can be due to the sparsity in the interaction frequency matrices at finer resolutions.
-[???
-Quantify sparsity] This sparsity may lead to inaccurate TAD calling and, subsequently, to worse model performance.
+This sparsity may lead to inaccurate TAD calling and, subsequently, to worse model performance.
 These results suggest that finer resolution of Hi-C data is not always optimal for accurate TAD calling and prediction, and sparsity of the data needs to be considered.
@@
 
-<!--
-![**Models built using distance-type predictors combined with SMOTE re-sampling yielded optimal MCCs across resolution.** Barplots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
-Within each re-sampling technique (A-D), performances are compared for each type of feature space: OC (red), OP (green), and Distance (blue), across resolutions.
-Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/model_performances_v3_bars.png)
--->
+![**Models built using distance-type predictors combined with random under-sampling yielded optimal predictive performance.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
+Performances are compared across resolution, within each predictor-type: (A) OC, (B) OP, and (C) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/performances.png)
 

### 2020-01-10 Manuscript/manuscript.Rmd
edits

@@
 The resolution-specific approach we developed to create TAD vs non-TAD boundary regions amenable for binary classification (See Methods) resulted in a total of 535363, 267682, 107073, 53537, and 26768 genomic bins.
-TAD boundary regions were defined as regions on the linear genome where a genomic bin contained a called TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as genomic bins that did not contain a TAD boundary ($Y = 0$) (Figure 1A).
+TAD boundary regions were defined as regions on the linear genome where a genomic bin contained a called TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as genomic bins that did not contain a TAD boundary ($Y = 0$) (Figure 1).
 
@@
 The annotations could be broken down into three sets including histone modifications (HM), cis-regulatory elements (CRE), and transcription factor binding sites (TFBS).
-We constructed three different predictor types for each functional genomic annotation (Figure 1B).
+We constructed three different predictor types for each functional genomic annotation (Figure 1).
 Counts of overlaps (**Overlap Counts**, OC) were defined as the total number of genomic annotation regions that overlapped within a given genomic bin.
@@
 A log2-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
-These feature engineering steps were performed to improve TAD boundary predictions by accounting for direct (OC), proportional (OP), and indirect (distance) relationships between TAD boundaries and genomic annotations.
+These feature engineering procedures were performed to improve TAD boundary predictions by accounting for direct (OC), proportional (OP), and indirect (distance) relationships between TAD boundaries and genomic annotations.
 
-![**Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** (A) Unique boundaries are denoted by the blue dots.
+![**Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** Unique boundaries are denoted by the blue dots.
 The linear genome was subsequently binned into resolution-specific intervals.
 The response vector **Y** was defined as a genomic bin that either overlapped with a TAD boundary ($Y = 1$) or did not ($Y = 0$).
-(B) Three types of associations between bins and genomic annotations (green shapes) used to build the feature space of random forest classification models include _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
+Three types of associations between bins and genomic annotations (green shapes) were then used to build the feature space of random forest classification models include _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
 ](Figures/model_construction_and_predictor_types.png)
@@
 The different combinations of inputs were evaluated by assessing the Matthews Correlation Coefficient (MCC) of each model.
-Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2 \times 5 \times 3 \times 4 \times 21 = 2520$) models.
+Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2 \times 5 \times 3 \times 4 \times 21 (= 2520)$ models.
 <!--Additional performance metrics are reported in the Supplementary materials.-->
@@
 
-We investigated the effect of class imbalance on model performance using three re-sampling techniques.
 Expectedly, when using data as-is, that is, with class imbalance present, the models performed poorly.
-Using any of the resampling techniques improved the performance, with SMOTE-resampled data being the most optimal (Figure 3, Supplementary Figure 2).
-These results suggest that a combination of both random over- and under-sampling (SMOTE) can improve TAD boundary prediction.
+Using any of the resampling techniques was found to improve model performance, with RUS narrowly out performing SMOTE re-sampling as the most optimal class balancing technique for all resolutions (Figure 3).
+These results suggest that simple randomly under-sampling alone can drastically improve TAD boundary prediction.
+<!--These results suggest that a combination of both random over- and under-sampling (SMOTE) can improve TAD boundary prediction.-->
 
-We found that, regardless of resampling technique, random forest classifiers built using a distance-type feature space yielded consistently higher MCCs when compared to the overlap count and overlap percent predictor types (Figure 3), and these results were consistent across resolutions and cell types (Supplementary Figure 2).
+Additionally, we found that regardless of resampling technique, random forest classifiers built using a distance-type feature space yielded consistently higher MCCs when compared to the overlap count and overlap percent predictor types (Figure 3), and these results were consistent across resolutions and cell types (Supplementary Figure 2).
 This indicated that models are better able to discriminate between TAD and non-TAD boundary regions when provided with spatially related associations.

### 2020-01-16 Manuscript/Figures/figure_legends.Rmd

@@
 **Figure 1.
-Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** (A) Unique boundaries are denoted by the blue dots.
+Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** Unique boundaries are denoted by the blue dots.
 The linear genome was subsequently binned into resolution-specific intervals.
 The response vector **Y** was defined as a genomic bin that either overlapped with a TAD boundary ($Y = 1$) or did not ($Y = 0$).
-(B) Three types of associations between bins and genomic annotations (green shapes) used to build the feature space of random forest classification models include _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
+Three types of associations between bins and genomic annotations (green shapes) were then used to build the feature space of random forest classification models include _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
 

### 2020-01-16 Manuscript/manuscript.Rmd

@@
 $$J_{(A,B)} = \dfrac{A \cap B}{A \cup B}.$$
-To give the sets of boundaries A and B dimensionality to enable us to calculate overlap, we flank each boundary point by a flanking factor, *f*=5000.
+To give the sets of boundaries A and B dimensionality to enable us to calculate overlap, we flank each boundary point by a flanking factor, $f=max\{r_{A},r_{B}\}$, where $r_{A(B)}$ is the Hi-C data resolution used to call TADs for A (B).
 

### 2020-01-20 Manuscript/Figures/figure_legends.Rmd
edited fig 3 legend

@@
 Models built using distance-type predictors combined with random under-sampling yielded optimal predictive performance.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
-Performances are compared across resolution, within each predictor-type: (A) OC, (B) OP, and (C) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Performances are compared across resolution, within each predictor-type: (A) Signal (B) OC, (C) OP, and (D) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.

### 2020-01-22 Manuscript/manuscript.Rmd
results edits

@@
 
-## A resolution-specific approach for predicting TAD boundaries
+## Developing a computational framework for optimal TAD boundary prediction
 
-We analyzed publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1).
+We developed a computational framework, refered to as **TADRF**, aimed at determining the optimal set of data level characteristics necessary for TAD boundary prediction using Random Forest classification models.
+Our framework is resolution-specific and uses called TAD boundaries as ground truth to establish TAD-boundary and non-TAD boundary regions.
+Under our framework, we binned the linear genome at intervals specific to the Hi-C data resolution used to call TADs.
+TAD boundary regions were defined as regions on the linear genome where a genomic bin contained a called TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as genomic bins that did not contain a TAD boundary ($Y = 0$) (Figure 1 A).
+Under this construction, the number of non-TAD boundary regions are exceed the number of TAD boundary regions.
+To cope with the imbalance among the class of genomic bins, we evaluated three re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries.
+**Random over-sampling** (ROS) was defined as sampling with replacement from TAD boundary regions.
+**Random under-sampling** (RUS) was defined as sampling with replacement from non-TAD boundary regions.
+Lastly, we considered **Synthetic minority over-sampling technique** (SMOTE), which is a combination of both random over- and under-sampling [@chawla2002smote].
+
+Various one-dimensional cell line-specific ChIP-seq tracks (genomic elements) were used to construct the feature space for the random forests including cis-regulatory elements, histone modifications, and transcription factor binding sites.
+Four different feature engineering procedures were developed for each genomic element (Figure 1 B).
+**Peak Signal** was defined as the [???include definition].
+Counts of overlaps (**Overlap Counts**, OC) were defined as the total number of genomic annotation regions that overlapped within a given genomic bin.
+Percents of overlaps (**Overlap Percent**, OP) were defined as the proportion of a bin overlapped by an annotation region.
+**Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations.
+A log2-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
+These feature engineering procedures were performed to improve TAD boundary predictions by accounting for direct (OC), proportional (Signal/OP), and spatial (distance) relationships between TAD boundaries and genomic annotations.
+
+![**Illustrating the resolution-specific data construction and feature engineering used for downstream random forest modeling.** (A) The linear genome was subsequently binned into resolution-specific intervals.
+The response vector **Y** was defined as a genomic bin that either overlapped with a TAD boundary ($Y = 1$) or did not ($Y = 0$).
+(B) Four types of associations between bins and genomic annotations (green shapes) were then used to build the feature space including _Peak Signal_ (Signal), _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
+](Figures/model_construction_and_predictor_types.png)
+
+We applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1).
 Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-<!--After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [@dixon2012topological; @sofueva2013cohesin]),--> The results presented are for the GM12878 cell line, with K562 results presented in the Supplementary material.
+The results presented are for the GM12878 cell line, with K562 results presented in the Supplementary material.
 We obtained a total of 8052, 7676, 4670, 2349, and 1031 called TADs across each resolution respectively (Table 1).
@@
 The resolution-specific approach we developed to create TAD vs non-TAD boundary regions amenable for binary classification (See Methods) resulted in a total of 535363, 267682, 107073, 53537, and 26768 genomic bins.
-TAD boundary regions were defined as regions on the linear genome where a genomic bin contained a called TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as genomic bins that did not contain a TAD boundary ($Y = 0$) (Figure 1).
-
-## TAD vs. non-TAD boundary class imbalance is severe irrespectively of Hi-C data resolution
-
-Under this construction, the class imbalance among the genomic bins was found to be both severe and invariant toward resolution.
+The class imbalance among the genomic bins was found to be both severe and invariant toward resolution.
 Specifically, we found the imbalance between TAD boundary and non-TAD boundary regions to be 0.03, 0.05, 0.08, 0.08, and 0.07 for each resolution respectively (Table 2).
@@
 These feature engineering procedures were performed to improve TAD boundary predictions by accounting for direct (OC), proportional (OP), and indirect (distance) relationships between TAD boundaries and genomic annotations.
-
-![**Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** Unique boundaries are denoted by the blue dots.
-The linear genome was subsequently binned into resolution-specific intervals.
-The response vector **Y** was defined as a genomic bin that either overlapped with a TAD boundary ($Y = 1$) or did not ($Y = 0$).
-Three types of associations between bins and genomic annotations (green shapes) were then used to build the feature space of random forest classification models include _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
-](Figures/model_construction_and_predictor_types.png)
 

### 2020-01-22 Manuscript/Figures/figure_legends.Rmd
edits

@@
 **Figure 1.
-Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** Unique boundaries are denoted by the blue dots.
-The linear genome was subsequently binned into resolution-specific intervals.
+Illustrating the resolution-specific data construction and feature engineering used for downstream random forest modeling.** (A) The linear genome was subsequently binned into resolution-specific intervals.
 The response vector **Y** was defined as a genomic bin that either overlapped with a TAD boundary ($Y = 1$) or did not ($Y = 0$).
-Three types of associations between bins and genomic annotations (green shapes) were then used to build the feature space of random forest classification models include _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
+(B) Four types of associations between bins and genomic annotations (green shapes) were then used to build the feature space including _Peak Signal_ (Signal), _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
 

### 2020-01-22 Manuscript/manuscript.Rmd
edits

@@
 
+We applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1).
+Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
+A total of 78 cell type specific functional genomic annotations were used to build the feature space of downstream random forest models (Supplementary Table 2).
+The annotations could be broken down into three sets including histone modifications (HM), cis-regulatory elements (CRE), and transcription factor binding sites (TFBS).
+The results presented are for the GM12878 cell line, with K562 results presented in the Supplementary material.
+
 ![**Illustrating the resolution-specific data construction and feature engineering used for downstream random forest modeling.** (A) The linear genome was subsequently binned into resolution-specific intervals.
 The response vector **Y** was defined as a genomic bin that either overlapped with a TAD boundary ($Y = 1$) or did not ($Y = 0$).
-(B) Four types of associations between bins and genomic annotations (green shapes) were then used to build the feature space including _Peak Signal_ (Signal), _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.
-](Figures/model_construction_and_predictor_types.png)
+(B) Four types of associations between bins and genomic annotations (green shapes) were then used to build the feature space including _Peak Signal_ (Signal), _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.](Figures/model_construction_and_predictor_types.png)
 
-We applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1).
-Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-The results presented are for the GM12878 cell line, with K562 results presented in the Supplementary material.
 We obtained a total of 8052, 7676, 4670, 2349, and 1031 called TADs across each resolution respectively (Table 1).
-From the called TADs we obtained a total of 15468, 14253, 8363, 4224, and 1883 unique TAD boundaries (Table 2).
+From the called TADs, a total of 15468, 14253, 8363, 4224, and 1883 unique TAD boundaries were obtained (Table 2).
 The resolution-specific approach we developed to create TAD vs non-TAD boundary regions amenable for binary classification (See Methods) resulted in a total of 535363, 267682, 107073, 53537, and 26768 genomic bins.
 The class imbalance among the genomic bins was found to be both severe and invariant toward resolution.
-Specifically, we found the imbalance between TAD boundary and non-TAD boundary regions to be 0.03, 0.05, 0.08, 0.08, and 0.07 for each resolution respectively (Table 2).
+Specifically, we found the imbalance between TAD boundary and non-TAD boundary regions to be 0.03, 0.05, 0.08, 0.08, and 0.07 for each resolution respectively (Table 1).
 Furthermore, the data summaries presented in Table 1 were found to be similar to those exibited by the K562 cell line (Supplementary Table 3).
@@
 
-## Three types of predictors define the associations between TAD boundary regions and genomic annotations
-
-A total of 78 cell type specific functional genomic annotations were used to build the feature space of downstream random forest models (Supplementary Table 1).
-The annotations could be broken down into three sets including histone modifications (HM), cis-regulatory elements (CRE), and transcription factor binding sites (TFBS).
-We constructed three different predictor types for each functional genomic annotation (Figure 1).
-Counts of overlaps (**Overlap Counts**, OC) were defined as the total number of genomic annotation regions that overlapped within a given genomic bin.
-Percents of overlaps (**Overlap Percent**, OP) were defined as the proportion of a bin overlapped by an annotation region.
-**Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations.
-A log2-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
-These feature engineering procedures were performed to improve TAD boundary predictions by accounting for direct (OC), proportional (OP), and indirect (distance) relationships between TAD boundaries and genomic annotations.
-
-## Building an ensemble framework for TAD boundary prediction
-
-To account for the heavily imbalanced classes reported above, we evaluated three re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries.
-**Random over-sampling** (ROS) was defined as sampling with replacement from TAD boundary regions.
-**Random under-sampling** (RUS) was defined as sampling with replacement from non-TAD boundary regions.
-Lastly, we considered **Synthetic minority over-sampling technique** (SMOTE), which is a combination of both random over- and under-sampling [@chawla2002smote].
-
-To identify the combination of data resolution, predictor type, and re-sampling technique necessary for optimal cell line specific TAD boundary prediction, we created an ensemble framework to systematically compare performances of different model inputs (Figure 2).
-The framework uses data for a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, using a particular predictor type *P = {OC, OP, Distance}*, and re-sampling technique *B = {None, RUS, ROS, SMOTE}*.
-Once the model inputs were established, a random forest classifier was trained on chromosome-specific datasets using 5-fold cross validation.
+Our computational framework was used to identify the combination of data resolution, predictor type, and re-sampling technique necessary for optimal cell line specific TAD boundary prediction (Figure 2).
+The framework uses data for a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, using a particular predictor type *P = {Signal, OC, OP, Distance}*, and re-sampling technique *B = {None, RUS, ROS, SMOTE}*.
+Once the model inputs were established, we trained a random forest classifier on chromosome-specific sections of the genome using 5-fold cross validation.
 The different combinations of inputs were evaluated by assessing the Matthews Correlation Coefficient (MCC) of each model.
-Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2 \times 5 \times 3 \times 4 \times 21 (= 2520)$ models.
-<!--Additional performance metrics are reported in the Supplementary materials.-->
+Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2 \times 5 \times 4 \times 4 \times 21 (= 3360)$ models.
 

### 2020-01-23 Manuscript/Figures/figure_legends.Rmd
edits

@@
 **Figure 3.
-Models built using distance-type predictors combined with random under-sampling yielded optimal predictive performance.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
+Models built using distance-type predictors combined with random under-sampling yielded optimal predictive performance for GM12878.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
 Performances are compared across resolution, within each predictor-type: (A) Signal (B) OC, (C) OP, and (D) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.
+
+**Figure 4: Assessing top ranked transcription factors in TAD boundary prediction.** (A) Barplots comparing performances of models using specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (CRE; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all three classes (Combined; purple).
+(B) Recursive feature elimination analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
+Error bars represent standard deviation from the mean MCC across each chromosome.
+(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes.

### 2020-01-23 Manuscript/Supplementary/supplementary_legends.Rmd
edits

@@
 
-**Supplementary Table 3.** Domain data and class imbalance summaries across resolutions for GM12878.
+**Supplementary Table 3.** Domain data and class imbalance summaries across resolutions for K562.
 
@@
 After $log_{2}$ transforming the distances, densities became much more gaussian distributed for all resolutions.
+
+**Supplementary Figure 2.
+Models built using distance-type predictors combined with random under-sampling yielded optimal predictive performance for K562.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
+Performances are compared across resolution, within each predictor-type: (A) Signal (B) OC, (C) OP, and (D) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.
+
+**Supplementary Figure 3.
+The proportional importance of optimally built random forest models was outweighed by transcription factor binding sites across resolutions.** Stacked barplots illustrate the proportion of total predictive importance in models using optimal data level characteristics determined by the computational framework (SMOTE re-sampling; with distance-type predictors), for each resolution on (A) GM12878 and (B) K562.
+Proportions are grouped by the class of cell line specific genomic elements in the feature space including histone modifications (HM), cis-regulatory elements (CRE), and transcription factor binding sites (TFBS).

### 2020-01-23 Scripts/comparing_annotation_specific_models.R
edits

@@ -223,6 +223,7 @@ ggplot(all_rfperfs_mcc, aes(x=Resolution, y=MCC, group=Annotation, fill=Annotati
   axis.title.y = element_text(size = 20),
   legend.text=element_text(size=15),
   legend.title=element_text(size=20),
+  legend.position = "bottom",
   plot.title = element_text(size=20))
 
 ####################################################################################################

### 2020-01-24 Manuscript/manuscript.Rmd

@@
 
-Cell type-specific genomic annotations were used to build the predictor space for of our random forest models.
-We created three types of predictors: *Overlap Count (OC)* - the total number of overlaps between a bin and genomic annotation regions;  *Overlap Percent (OP)* - the percent of overlap between the bin and the total width of genomic annotation regions overlapping it; *Log2 Distance* - the $log_{2}$ of the distance in bases (refered to hereafter as *Distance*), from the center of the bin to the center of the nearest genomic annotation region.
+Cell type-specific genomic annotations [???"annotations" or "elements"] were used to build the predictor space for of our random forest models.
+We created four types of predictors: *Peak Signal Strength* - [???include definition] (refered to hereafter as *Signal*), *Overlap Count (OC)* - the total number of overlaps between a bin and genomic annotation regions;  *Overlap Percent (OP)* - the percent of overlap between the bin and the total width of genomic annotation regions overlapping it; *Log2 Distance* - the $log_{2}$ of the distance in bases (refered to hereafter as *Distance*), from the center of the bin to the center of the nearest genomic annotation region.
 
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-<!--Additional performance metrics including AUROC, accuracy, sensitivity, and specificity were [???
-are?] reported in the supplementary materials.-->
+[???include reason for using mcc, why not others?] <!--Additional performance metrics including AUROC, accuracy, sensitivity, and specificity were reported in the supplementary materials.-->
 
@@
 
+\newpage
+
 | Resolution | Total number of called TADs | Total number of unique TAD boundaries | Total number of genomic bins | Class imbalance |
@@
 
-Expectedly, when using data as-is, that is, with class imbalance present, the models performed poorly.
-Using any of the resampling techniques was found to improve model performance, with RUS narrowly out performing SMOTE re-sampling as the most optimal class balancing technique for all resolutions (Figure 3).
+Expectedly, when using data as-is, that is, with class imbalance present, the models exhibited low MCCs.
+Similarly poor performances were found when using ROS as well.
+However, RUS and SMOTE re-sampling led to drastic improvement in performance, especially at higher resolutions.
+We found that RUS narrowly out performed SMOTE as the most optimal class balancing technique for all resolutions and predictor types (Figure 3).
 These results suggest that simple randomly under-sampling alone can drastically improve TAD boundary prediction.
-<!--These results suggest that a combination of both random over- and under-sampling (SMOTE) can improve TAD boundary prediction.-->
+<!--These results suggest that a combination of both random over- and under-sampling (SMOTE) can improve TAD boundary prediction.-->Additionally, we found that at higher resolutions, random forest classifiers built using a distance-type feature space yielded substantially higher MCCs when compared to the peak signal stength, overlap count, and overlap percent predictor types (Figure 3).
+As with comparing class balancing techniques, this improvement was less evident at lower resolutions.
+<!--This indicated that models are better able to discriminate between TAD and non-TAD boundary regions when provided with spatially related associations.-->
 
-Additionally, we found that regardless of resampling technique, random forest classifiers built using a distance-type feature space yielded consistently higher MCCs when compared to the overlap count and overlap percent predictor types (Figure 3), and these results were consistent across resolutions and cell types (Supplementary Figure 2).
-This indicated that models are better able to discriminate between TAD and non-TAD boundary regions when provided with spatially related associations.
-
-Interestingly, we found that performances peaked at 10 kb resolution and then degraded as data resolution decreased.
-The reason for the improved performance between 5 kb and 10 kb data resolutions can be due to the sparsity in the interaction frequency matrices at finer resolutions.
+Interestingly, for the optimal re-sampling and predictor type, we found that performances peaked at 10 kb resolution and then degraded as data resolution decreased.
+The reason for the improved performance between 5 kb and 10 kb data resolutions can be attributed to the sparsity in the interaction frequency matrices at finer resolutions.
 This sparsity may lead to inaccurate TAD calling and, subsequently, to worse model performance.
 These results suggest that finer resolution of Hi-C data is not always optimal for accurate TAD calling and prediction, and sparsity of the data needs to be considered.
-Additionally, performances tended to be much more variable between chromosomes at lower resolutions, evidenced by the wider error bars for the 50 kb and 100 kb resolutions.
-In summary, our results imply that using random under- and over-sampling, distance-type predictors, and the data at 10kb resolution results in an optimally performing cell line-specific random forest-based TAD boundary prediction model.
+Furthermore, performances tended to be much more variable between chromosomes at lower resolutions, evidenced by the wider error bars for the 50 kb and 100 kb resolutions.
+These results were found to be consistent for the K562 cell line (Supplementary Figure 2).
+In summary, our computational framework showed that using random under-sampling, distance-type predictors, and Hi-C data at 10kb resolution yields an optimally performing cell line-specific random forest classification model for TAD boundary prediction.
 
@@
 
-## Transcription factor binding sites outperform other annotation-specific models
+## Transcription factor binding sites outperform HM- and CRE-specific models
 
-We then aimed to compare the performances of annotation-specifc models.
-In doing so, we inspected the proportion of predictive importance that was explained by each of the three groups of genomic annotations (histone modifications (HM), chromatin states (ChromHMM), and transcription factor binding sites (TFBS)).
-For optimal random forest classifiers, we found that the majority of the proportional predictive importance was obtained by transcription factor binding sites (Supplementary Figure 3).
-Furthermore, models build solely on TFBSs outperformed other annotation-specific models at all resolutions (Figure 4A; Supplementary Figure 4A).
-Notably, the TFBS-specific models outperformed models built on the combined sets of annotations, and this effect was most pronounced at lower resolutions.
-This indicated that the inclusion of other types of annotations contributed to additional noise rather than signal in TAD boundary prediction.
+We then aimed to compare the performances of genomic class-specifc models.
+In doing so, we inspected the proportion of predictive importance that was explained by each of the three classes of genomic elements including histone modifications (HM), cis-regulatory elements (CRE), and transcription factor binding sites (TFBS).
+For an optimally built random forest classifier at each data resolution--smote re-sampling, and distance-type predictors--we found that the majority of the proportional predictive importance was obtained by transcription factor binding sites for both cell lines (Supplementary Figure 3 A-B).
+Furthermore, models built solely on TFBS outperformed other class-specific models (Figure 4A; Supplementary Figure 4A).
+Notably, the TFBS-specific models outperformed models built on the combination of all genomic elements at lower resolutions, indicating that the inclusion of other types of annotations contributed to additional noise rather than signal in TAD boundary prediction.
 In summary, these results suggest that TFBS are the primary drivers of TAD boundary formation in both the GM12878 and K562 cell lines.
@@
 
-<!--
-![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) Barplots comparing performances of models using specific groups of functional genomic annotation as the feature space including histone modifications (HM; red), chromatin states (ChromHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all three groups (Combined; purple).
+![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) Barplots comparing performances of models using specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (CRE; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all three classes (Combined; purple).
 (B) Recursive feature elimination analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
-(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes.
-Error bars represent standard deviation from the mean MCC across each chromosome.](Figures/annot_specific_rfe_varimps_heatmap.png)
--->
+Error bars represent standard deviation from the mean MCC across each chromosome.
+(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes.](Figures/annots_specifc_rfe_importances.png)
 
@@
 # Discussion
+
+<!--Additional performance metrics were reported for both cell lines including positive predictive value (PPV; precision), F1-Score (F1), Accuracy, Area Under the Receiver Operating Characteristic Curve (AUC), Area Under the Precision-Recall Curve.-->
 

### 2020-01-24 Manuscript/Figures/figure_legends.Rmd
edits

@@
 
-**Figure 4: Assessing top ranked transcription factors in TAD boundary prediction.** (A) Barplots comparing performances of models using specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (CRE; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all three classes (Combined; purple).
+**Figure 4.
+Assessing top ranked transcription factors in TAD boundary prediction for GM12878.** (A) Barplots comparing performances of models using specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (CRE; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all three classes (Combined; purple).
 (B) Recursive feature elimination analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
@@
 (C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes.
+
+**Figure 5.
+Predicted TAD boundaries are enriched with known molecular drivers of the 3D chromatin architecture.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17390000-18640000; GM12878).
+The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.
+Called TADs are outlined in blue.
+The blue vertical lines represent a called TAD boundary identified by the ARROWHEAD algorithm.
+The black line represents the predicted probability of each base pair being a TAD boundary.
+Regions of adjacent base pairs with probability of 1 are represented by the green regions along the x-axis.
+The green vertical lines represent the subsequent base pair predicted to be a TAD boundary using medoid partitioning.
+<!--(B) Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by SMC3, ZNF143, CTCF, and RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.-->

### 2020-01-24 Manuscript/Supplementary/supplementary_legends.Rmd
edits

@@
 Proportions are grouped by the class of cell line specific genomic elements in the feature space including histone modifications (HM), cis-regulatory elements (CRE), and transcription factor binding sites (TFBS).
+
+**Supplementary Figure 4.
+Assessing top ranked transcription factors in TAD boundary prediction for K562.** (A) Barplots comparing performances of models using specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (CRE; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all three classes (Combined; purple).
+(B) Recursive feature elimination analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
+Error bars represent standard deviation from the mean MCC across each chromosome.
+(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes.

### 2020-01-24 Manuscript/manuscript.Rmd
edits

@@
 TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all resolutions and cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
-
 Genomic annotation data in the form of cell type-specific cis-regulatory elements (CRE), histone modifications (HM), and transcription factor binding sites (TFBS) were obtained from the UCSC Genome Browser Database (GRCh37/hg19 human genome assembly) [@Tyner:2017aa] (Supplementary Table 2).
 
-## Machine learning framework for TAD boundary prediction
+## Computational framework for TAD boundary prediction using random forests
 
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-[???include reason for using mcc, why not others?] <!--Additional performance metrics including AUROC, accuracy, sensitivity, and specificity were reported in the supplementary materials.-->
+[???include reason for using mcc, why not others?].
+We refer to the complete computational framework used to compare random forest model inputs as *TADRF*.
+<!--Additional performance metrics including AUROC, accuracy, sensitivity, and specificity were reported in the supplementary materials.-->
 
@@
 Many genomic annotations, notably architectural proteins, tend to exhibit an extensive pattern of colocalization (correlation) [@van2014insulator].
-To suitably reduce the feature space and prevent overfitting, we implemented recursive feature elimination to estimate the optimal number of necessary features to include in the model.
+To suitably reduce the feature space and prevent overfitting, we implemented recursive feature elimination to estimate the optimal number of necessary features to include in the best fitting *TADRF* model.
 The best performing subset was identified, ranging from 2 to the maximum number of features by powers of 2.
@@
 To guard against inflating the number of predicted TAD boundaries we developed a technique that combines both hierarchical clustering and partitioning techniques to identify more precise TAD boundaries throughout the linear genome.
+We refer to our method as *preciseTAD*.
 
@@
 
-We developed a computational framework, refered to as **TADRF**, aimed at determining the optimal set of data level characteristics necessary for TAD boundary prediction using Random Forest classification models.
+We developed a computational framework, refered to as *TADRF*, aimed at determining the optimal set of data level characteristics necessary for TAD boundary prediction using Random Forest classification models.
 Our framework is resolution-specific and uses called TAD boundaries as ground truth to establish TAD-boundary and non-TAD boundary regions.
@@
 To cope with the imbalance among the class of genomic bins, we evaluated three re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries.
-**Random over-sampling** (ROS) was defined as sampling with replacement from TAD boundary regions.
-**Random under-sampling** (RUS) was defined as sampling with replacement from non-TAD boundary regions.
-Lastly, we considered **Synthetic minority over-sampling technique** (SMOTE), which is a combination of both random over- and under-sampling [@chawla2002smote].
+*Random over-sampling* (ROS) was defined as sampling with replacement from TAD boundary regions.
+*Random under-sampling* (RUS) was defined as sampling with replacement from non-TAD boundary regions.
+Lastly, we considered *Synthetic minority over-sampling technique* (SMOTE), which is a combination of both random over- and under-sampling [@chawla2002smote].
 
@@
 Four different feature engineering procedures were developed for each genomic element (Figure 1 B).
-**Peak Signal** was defined as the [???include definition].
-Counts of overlaps (**Overlap Counts**, OC) were defined as the total number of genomic annotation regions that overlapped within a given genomic bin.
-Percents of overlaps (**Overlap Percent**, OP) were defined as the proportion of a bin overlapped by an annotation region.
-**Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations.
+*Peak Signal* was defined as the [???include definition].
+Counts of overlaps (*Overlap Counts*, OC) were defined as the total number of genomic annotation regions that overlapped within a given genomic bin.
+Percents of overlaps (*Overlap Percent*, OP) were defined as the proportion of a bin overlapped by an annotation region.
+*Distance* was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations.
 A log2-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
@@
 
-Expectedly, when using data as-is, that is, with class imbalance present, the models exhibited low MCCs.
+Expectedly, when using data with class imbalance present, that is no re-sampling, the models exhibited low MCCs, with very little variability among different resolutions (Figure 3).
 Similarly poor performances were found when using ROS as well.
 However, RUS and SMOTE re-sampling led to drastic improvement in performance, especially at higher resolutions.
-We found that RUS narrowly out performed SMOTE as the most optimal class balancing technique for all resolutions and predictor types (Figure 3).
+We found that RUS narrowly out performed SMOTE as the most optimal class balancing technique for all resolutions and predictor types.
 These results suggest that simple randomly under-sampling alone can drastically improve TAD boundary prediction.
-<!--These results suggest that a combination of both random over- and under-sampling (SMOTE) can improve TAD boundary prediction.-->Additionally, we found that at higher resolutions, random forest classifiers built using a distance-type feature space yielded substantially higher MCCs when compared to the peak signal stength, overlap count, and overlap percent predictor types (Figure 3).
+<!--These results suggest that a combination of both random over- and under-sampling (SMOTE) can improve TAD boundary prediction.-->Additionally, we found that at higher resolutions, random forest classifiers built using a distance-type feature space yielded substantially higher MCCs when compared to the peak signal stength, overlap count, and overlap percent predictor types.
 As with comparing class balancing techniques, this improvement was less evident at lower resolutions.
@@
 
-![**Models built using distance-type predictors combined with random under-sampling yielded optimal predictive performance.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
+![**Models built using distance-type predictors combined with random under-sampling at 10 kb yielded optimal predictive performance for GM12878.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
 Performances are compared across resolution, within each predictor-type: (A) OC, (B) OP, and (C) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
@@
 Notably, the TFBS-specific models outperformed models built on the combination of all genomic elements at lower resolutions, indicating that the inclusion of other types of annotations contributed to additional noise rather than signal in TAD boundary prediction.
-In summary, these results suggest that TFBS are the primary drivers of TAD boundary formation in both the GM12878 and K562 cell lines.
+Our results suggest that TFBS are the primary drivers of TAD boundary formation in both the GM12878 and K562 cell lines.
 
@@
 
-Given that many TFBS are known to colocalize together on the linear genome and are therefore highly correlated, we sought to avoid overfitting by performing recursive feature elimination.
-We found that our models were able to obtain near-optimal performance using approximately eight TFBSs (Figure 4B; Supplementary Figure 4B).
-However, given that we train our models on chromosome-specific data, the most significant annotations vary for each chromosome.
-To determine the most common TFBSs, we clustered the predictive importance values across chromosomes (Figure 4C; Supplementary Figure 4C).
-We found that, similar to other studies [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD boundary regions.
+Given that many TFBS are known to colocalize together on the linear genome and are therefore highly correlated, we sought to further optimize our TAD prediction model to avoid overfitting by performing recursive feature elimination.
+We found that, under our framework, we were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figure 4B).
+However, given that we trained our model on chromosome-specific data, the most significant annotations were found to vary for each chromosome.
+To determine the most common TFBS, we clustered the predictive importances across chromosomes.
+We found that, similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD boundary regions for all chromosomes (Figure 4C; Supplementary Figure 4C).
+Therefore, using our framework *TADRF* was able to identify the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@fudenberg2016formation; @alipour2012self].
 
-![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) Barplots comparing performances of models using specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (CRE; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all three classes (Combined; purple).
-(B) Recursive feature elimination analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
+![**Assessing top ranked transcription factors in TAD boundary prediction for GM12878.** (A) Barplots comparing performances of models using specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (CRE; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all three classes (Combined; purple).
+(B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.
 Error bars represent standard deviation from the mean MCC across each chromosome.
-(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes.](Figures/annots_specifc_rfe_importances.png)
+(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.
+Importances were calculated as the mean decrease in accuracy among permuted features in out-of-bag samples.](Figures/annots_specifc_rfe_importances.png)
 
-## Predictive modeling defines precise and biologically relevant location of TAD boundaries
+## *preciseTAD* defines precise and biologically relevant locations of TAD boundaries
 
-After obtaining our optimally built random forest classifier, we investigated whether our predictive models can alleviate resolution limitations of Hi-C data by predicting TAD boundaries at base pair resolution.
-We were able to identify regions where the model predicted the base pair to be a TAD boundary with probability equal to 1 (Figure 5A).
+After obtaining our optimally built *TADRF* model, we investigated whether we could leverage our model to alleviate resolution limitations of Hi-C data by predicting TAD boundaries at base pair resolution.
+Our method, referred to as *preciseTAD*, uses a combination of complete linkage hierarchical clustering with a scalable version of partitioning around mediods (PAM), known as clustering large applications (CLARA) to reduce many adjacent base pairs with similarly high predictive probabilities down to a set of the most representative and biologically meaningful predicted TAD boundaries (see Methods).
+*preciseTAD* was applied to chromosome-specific sections of the linear genome.
+For each chromosome, we defined our new validation data using distance-type predictors among only the transcription factor binding sites for each base pair.
+That is, each base pair had a corresponding row vector, **X**=$\{X_{1}, ..., X_{p}\}$, representing the $log_{2}$ genomic distances to the nearest respective transcription factor binding sites (Supplementary Table 2).
+
+We first used ROC analysis to obtain an optimal probability threshold for defining potential predicted TAD boundaries.
+We reported an average threshold of ???
+(SD=???) among the 21 autosomal chromosomes that were analyzed (mean=???, SD=???
+for K562).
+We referred to collections of chromosome-specific base pairs that exceeded this threshold when used to validate our *TADRF* model as *predicted TAD boundary areas* (PTBA), given that collections of adjacent base pairs tended to exhibit similar prediction profiles.
+We found that there were a total of ???
+PTBA, containing an average of ???
+base pairs each (???
+PTBA for K562; mean base pairs=???, SD=???).
+*preciseTAD* then implements complete linkage hierarchical clustering on the dissimilarity matrix constructed from the pairwise distances (in base pairs) among the midpoints of each chromsome-specific PTBA.
+Using the silhouette score (see methods), we reported a total of k=???
+chromosome-specific clusters (k=???
+for K562).
+We referred to these *k* clusters as *predicted TAD boundary regions* (PTBR).
+That is, each PTBR contained the midpoints of multiple PTBA.
+Lastly, given each PTBR, *preciseTAD* uses CLARA partitioning to obtain the most representative midpoint.
+We referred to this as the *predicted TAD boundary point* (PTBP).
+These PTBP were identified as the most representative base pair among each PTBR.
+*preciseTAD* was able to identify a total of ???
+PTBP across each chromosome.
+We reported less predicted TAD boundaries than ARROWHEAD at 10 kb (Table 1).
+This is attributed to ARROWHEAD's inherent inflation of called TAD boundaries, especially near fuzzy areas along the diagonal of Hi-C contact matrices (Figure 5A).
+Likewise, under the framework of *preciseTAD*, any two TADs are inherently demarcated by only one predicted TAD boundary, leading to comparatively less TAD boundaries.
+We also find that predicted TAD boundaries identified by *preciseTAD* were much more likely to demarcate high concentrations of inter-chromosomal contacts among Hi-C contact matrices (Figure 5A).
+[???include a result that demonstrates this; discuss in meeting]
+
+???stopped here; waiting to predicted tad boundaries results
+
+<!--We were able to identify regions where the model predicted the base pair to be a TAD boundary with probability equal to 1 (Figure 5A).
 [???
@@
 Furthermore, when compared to called TAD boundaries, the boundaries that we predicted with our model were found to be statistically significantly closer to the top ranked TFBS, suggesting stronger enrichment profiles near predicted TAD boundaries (Supplementary Figure 7).
+-->
 

### 2020-01-24 Scripts/visualizing_example_predicted_tad_bounds.R
initial commit

@@ -1,0 +1,288 @@
+library(BSgenome)
+library(randomForest)
+library(DMwR)
+library(cluster)
+library(pROC)
+library(PRROC)
+library(caret)
+library(GenomicRanges)
+
+# Loading necessary functions
+
+source("C:/Users/stili/Documents/preciseTAD_functions/functions/annots_to_granges_func.r")
+source("C:/Users/stili/Documents/preciseTAD_functions/functions/binary_func.r")
+source("C:/Users/stili/Documents/preciseTAD_functions/functions/count_func.r")
+source("C:/Users/stili/Documents/preciseTAD_functions/functions/distance_func.r")
+source("C:/Users/stili/Documents/preciseTAD_functions/functions/signal_func.r")
+source("C:/Users/stili/Documents/preciseTAD_functions/functions/extract_boundaries_func.r")
+source("C:/Users/stili/Documents/preciseTAD_functions/functions/percent_func.r")
+source("C:/Users/stili/Documents/preciseTAD_functions/functions/TADRF.r")
+source("C:/Users/stili/Documents/preciseTAD_functions/functions/preciseTAD.r")
+
+# Extracting TAD boundaries using the extract_boundaries_func function for ARROWHEAD defined TADs at 10kb resolution
+
+domains <- read.table("Z:/TAD_data_analysis/GM12878/10kb/GM12878_domain_data_10000.b.txt")
+bounds.GR <- extract_boundaries_func(domains.mat=domains, 
+                                     preprocess=FALSE, 
+                                     CHR="CHR22", 
+                                     resolution=10000)
+
+# Obtaining list of GRanges objects of ChIP-seq data used for modelling
+
+genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
+                                             pattern="*.bed",
+                                             signal=4)
+
+tadModel <- TADRF(bounds.GR=bounds.GR,
+                  resolution=10000,
+                  genomicElements.GR=genomicElements.GR,
+                  featureType="distance",
+                  resampling="smote",
+                  trainCHR="CHR22",
+                  predictCHR="CHR22",
+                  number=5,
+                  ntrees=500,
+                  metric="MCC",
+                  verbose=TRUE,
+                  seed=123,
[…]

### 2020-01-24 Manuscript/Figures/figure_legends.Rmd
edits

@@
 **Figure 5.
-Predicted TAD boundaries are enriched with known molecular drivers of the 3D chromatin architecture.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17390000-18640000; GM12878).
+Predicted TAD boundaries are enriched with known molecular drivers of the 3D chromatin architecture.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17389000-18011000; GM12878).
 The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.

### 2020-01-24 Manuscript/manuscript.Rmd
edits

@@
 Therefore, using our framework *TADRF* was able to identify the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@fudenberg2016formation; @alipour2012self].
+Therefore, we could further optimize our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
+To summarize, the optimally built cell line-specific random forest model under our *TADRF* framework was found to be one built using 10 kb resolution data, leveraging distance-type predictors for the CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites, while implementing random under-sampling to balance TAD and non-TAD boundary defined genomic bins.
 
@@
 *preciseTAD* was applied to chromosome-specific sections of the linear genome.
-For each chromosome, we defined our new validation data using distance-type predictors among only the transcription factor binding sites for each base pair.
-That is, each base pair had a corresponding row vector, **X**=$\{X_{1}, ..., X_{p}\}$, representing the $log_{2}$ genomic distances to the nearest respective transcription factor binding sites (Supplementary Table 2).
+For each chromosome, we defined our new validation data using distance-type predictors among only the most informative TFBS for each base pair, namely the CTCF, RAD21, SMC3, and ZNF143 transcription factors.
+That is, each base pair had a corresponding row vector, **X**=$\{X_{1}, ..., X_{4}\}$, representing the $log_{2}$ genomic distances to the nearest respective transcription factor binding site.
 
@@
 
-<!--
-![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17390000-18640000; GM12878).
+![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17389000-18011000; GM12878).
 The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.
@@
 Regions of adjacent base pairs with probability of 1 are represented by the green regions along the x-axis.
-The green vertical lines represent the subsequent base pair predicted to be a TAD boundary using medoid partitioning.
-(B) Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by SMC3, ZNF143, CTCF, and RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.](Figures/visualizing_boundaries_example_with_enriched_heatmaps.png)
--->
+The green vertical lines represent the subsequent base pair predicted to be a TAD boundary using medoid partitioning.](Figures/visualizing_ptbp_and_ctbp.png)
 

### 2020-03-31 Manuscript/Figures/figure_legends.Rmd

@@
 **Figure 5.
-Predicted TAD boundaries are enriched with known molecular drivers of the 3D chromatin architecture.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17389000-18011000; GM12878).
-The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.
-Called TADs are outlined in blue.
-The blue vertical lines represent a called TAD boundary identified by the ARROWHEAD algorithm.
-The black line represents the predicted probability of each base pair being a TAD boundary.
-Regions of adjacent base pairs with probability of 1 are represented by the green regions along the x-axis.
-The green vertical lines represent the subsequent base pair predicted to be a TAD boundary using medoid partitioning.
+Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17389000-18011000; GM12878).
+The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.The blue vertical lines represent called boundaries identified by ARROWHEAD, with the corresponding called TADs outlined in blue on the upper diagonal contact matrix above.
+The black line represents the predicted probability of each base pair being a TAD boundary when validated by *TADRF*.
+Collections of red vertical lines represent base pairs whose predictive probability exceed the ROC threshold, labeled as *predicted TAD boundary areas* (PTBA).
+The midpoints of spatially similar PTBA were clustered together into *predicted TAD boundary regions* (PTBR), denoted by the yellow regions along the x-axis.
+The green vertical lines represent the *predicted TAD boundary points* (PTBA) identified by *preciseTAD*, with the corresponding predicted TADs outlined above in green.
 <!--(B) Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by SMC3, ZNF143, CTCF, and RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.-->

### 2020-03-31 Manuscript/manuscript.Rmd

@@
 ![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17389000-18011000; GM12878).
-The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.
-Called TADs are outlined in blue.
-The blue vertical lines represent a called TAD boundary identified by the ARROWHEAD algorithm.
-The black line represents the predicted probability of each base pair being a TAD boundary.
-Regions of adjacent base pairs with probability of 1 are represented by the green regions along the x-axis.
-The green vertical lines represent the subsequent base pair predicted to be a TAD boundary using medoid partitioning.](Figures/visualizing_ptbp_and_ctbp.png)
+The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.The blue vertical lines represent called boundaries identified by ARROWHEAD, with the corresponding called TADs outlined in blue on the upper diagonal contact matrix above.
+The black line represents the predicted probability of each base pair being a TAD boundary when validated by *TADRF*.
+Collections of red vertical lines represent base pairs whose predictive probability exceed the ROC threshold, labeled as *predicted TAD boundary areas* (PTBA).
+The midpoints of spatially similar PTBA were clustered together into *predicted TAD boundary regions* (PTBR), denoted by the yellow regions along the x-axis.
+The green vertical lines represent the *predicted TAD boundary points* (PTBA) identified by *preciseTAD*, with the corresponding predicted TADs outlined above in green.](Figures/visualizing_ptbp_and_ctbp.png)
 

### 2020-04-03 Manuscript/manuscript.Rmd
methods edits

@@
 
+## TAD boundary data
+
+Biological replicate Hi-C data were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1) for the GM12878 and K562 cell lines.
+The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from Hi-C data at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolution using the ARROWHEAD algorithm [@durand2016juicebox].
+TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all resolutions and cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
+
 ## Genomic annotation and TAD boundary data
 
-Biological replicate Hi-C data were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1) for the GM12878 and K562 cell lines.
-The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from Hi-C data at 10 kb, 25 kb, 50 kb, and 100 kb resolution using the ARROWHEAD algorithm [@durand2016juicebox].
-TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all resolutions and cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
-Genomic annotation data in the form of cell type-specific cis-regulatory elements (CRE), histone modifications (HM), and transcription factor binding sites (TFBS) were obtained from the UCSC Genome Browser Database (GRCh37/hg19 human genome assembly) [@Tyner:2017aa] (Supplementary Table 2).
+A total of 78 cell type-specific ChIP-Seq annotations in the form of cell cis-regulatory elements (CRE), histone modifications (HM), and transcription factor binding sites (TFBS) were obtained from the UCSC Genome Browser Database for both GM12878 and K562 (GRCh37/hg19 human genome assembly) [@Tyner:2017aa] (Supplementary Table 2).
 
@@
 The binning was initiated at the chromosome-specific genomic coordinate marking half of the resolution, and continued in congruent intervals until the end of the chromosome (*mod r* + *r/2*).
-This was to ensure that called (ground truth) TAD boundaries would be positioned in the center of genomic bins.
+This was to ensure that called (ground truth) TAD boundaries would be positioned in the center of respective genomic bins.
 Genomic bins were then defined as TAD boundary regions (*Y = 1*) if they contained a TAD boundary, and non-TAD boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for random forest classification.
 
-Cell type-specific genomic annotations [???"annotations" or "elements"] were used to build the predictor space for of our random forest models.
+Cell type-specific genomic annotations were used to build the predictor space for of our random forest models.
 We created four types of predictors: *Peak Signal Strength* - [???include definition] (refered to hereafter as *Signal*), *Overlap Count (OC)* - the total number of overlaps between a bin and genomic annotation regions;  *Overlap Percent (OP)* - the percent of overlap between the bin and the total width of genomic annotation regions overlapping it; *Log2 Distance* - the $log_{2}$ of the distance in bases (refered to hereafter as *Distance*), from the center of the bin to the center of the nearest genomic annotation region.
 
-The chromosome-specific dataset used for modeling was composed of two components: the response vector **Y**, an indicator variable separating between TAD and non-TAD boundary regions, and the predictor-type specific data matrix, **X** = {$X_1$, $X_2$, ..., $X_p$}, where $p$ was the set of genomic annotations.
-<!--One, or all types of predictors were used as described.
-The data was split into a 7:3 ratio of training and testing sets.-->
+Chromosome-specific datasets used for modeling were composed of two components: the response vector **Y**, an indicator variable separating between TAD and non-TAD boundary regions, and the predictor-type specific data matrix, **X** = {$X_1$, $X_2$, ..., $X_p$}, where $p$ was the set of genomic annotations.
+Each dataset was concatenated to form a whole genome dataset.
+The dataset was then split into a 7:3 ratio for training and testing respectively.
 
-## Addressing class imbalance
-
-Class imbalance (CI) was defined as the proportion of minority class out of the total number of observations:
-
-$$CI = \dfrac{C_{min}}{C_{min} + C_{maj}}$$
-
-where $C_{min}$ denotes the set of TAD boundary regions and $C_{maj}$ denotes the set non-TAD boundary regions.
-CI of heavily imbalanced classes approaches 0, while CI for balanced classes approaches 0.50.
-To assess the effect of CI on predictive performance, we first used the data with *No Sampling*, that is, the majority and minority classes were used as is.
-We evaluated three re-sampling techniques.
-For *Random Under-Sampling (RUS)*, the majority class was sampled without replacement to obtain the same number of data points in the minority class.
-For *Random Over-Sampling (ROS)*, the minority class was sampled with replacement to obtain the same number of data points in the majority class.
-For *SMOTE* (Synthetic Minority Over-Sampling Technique), under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the $k=5$ minority class nearest neighbors [@chawla2002smote] (implemented in the `DMwR` v.0.4.1 R package).
+To assess the impact of class imbalance (CI), defined as the proportion of TAD boundary regions to non-TAD boundary regions, we evaluated three re-sampling techniques including *Random Over-Sampling (ROS)*, *Random Under-Sampling (RUS)*, and *Synthetic Minority Over-Sampling Technique (SMOTE)*.
+For ROS, the minority class was sampled with replacement to obtain the same number of data points in the majority class.
+For RUS, the majority class was sampled without replacement to obtain the same number of data points in the minority class.
+For SMOTE, under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the $k=5$ minority class nearest neighbors [@chawla2002smote] (implemented in the `DMwR` v.0.4.1 R package).
 We restricted the algorithm to 100% over-sampling and 200% under-sampling, which creates perfectly balanced classes.
@@
 Random forest classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, predictor types, and re-sampling techniques.
-Five-fold cross validation was used to tune the number of annotations, *p*, to consider at each node.
+Three-fold cross validation was used to tune the number of annotations, *p*, to consider at each node.
 The number of trees that were aggregated for each random forest model was set to the default, $n=500$.
-The performance of each model was compared using Matthews Correlation Coefficient (MCC), defined as <!--The MCC is, in essence, the correlation coefficient between the observed and predicted binary classifications [@brodersen2010balanced].
-A value of 1 represents a perfect prediction, while a value of -1 represents total disagreement between prediction and observation.
-A value of 0 indicates no better than random prediction.
-The MCC is defined as-->
+The performance of each model was compared using Balanced Accuracy (BA), defined as
 
@@
 
+<!--
 $$
@@
 $$
-<!--
-$$Balanced \quad Accuracy = \dfrac{1}{2}\left( \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} \right)$$
 -->
+
+$$BA = \dfrac{1}{2}\left( \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} \right)$$
 
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-[???include reason for using mcc, why not others?].
-We refer to the complete computational framework used to compare random forest model inputs as *TADRF*.
-<!--Additional performance metrics including AUROC, accuracy, sensitivity, and specificity were reported in the supplementary materials.-->
+<!--We refer to the complete computational framework used to compare random forest model inputs as *TADRF*.-->
 
-## Feature reduction
+## Feature reduction and predictive importance
 
 Many genomic annotations, notably architectural proteins, tend to exhibit an extensive pattern of colocalization (correlation) [@van2014insulator].
-To suitably reduce the feature space and prevent overfitting, we implemented recursive feature elimination to estimate the optimal number of necessary features to include in the best fitting *TADRF* model.
+To suitably reduce the feature space and prevent overfitting, we implemented recursive feature elimination to estimate the optimal number of necessary features to include in the best fitting random forest model.
 The best performing subset was identified, ranging from 2 to the maximum number of features by powers of 2.
-We then aggregated the predictive importance of the union of the optimal set of features across chromosomes using the mean decrease in node impurity to determine the most common and top ranked annotations for predicting TAD boundaries.
-[???
-TBD, at which stage it was done]
+We then aggregated the predictive importance of the union of the optimal set of features across chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top ranked annotations for predicting TAD boundary regions.
 
@@
 similar distances), and will thus yield similar predictions.
-To guard against inflating the number of predicted TAD boundaries we developed a technique that combines both hierarchical clustering and partitioning techniques to identify more precise TAD boundaries throughout the linear genome.
-We refer to our method as *preciseTAD*.
+To guard against inflating the number of predicted TAD boundaries we developed a technique that combines both density-based spatial clustering (DBSCAN) and partitioning techniques to identify more precise TAD boundaries throughout the linear genome.
 
-We first established a *predicted TAD boundary area* (PTBA) as a collection of adjacent base pairs that have been identified as being a predicted TAD boundary (using the optimal probability threshold identified by the combination of TPR and FPR closest to the point (0,1) on the ROC curve).
-We then performed hierarchical clustering on the pairwise distances (in base pairs) between the midpoints of each PTBA using complete linkage clustering.
+We first established a *predicted TAD boundary area* (PTBA) as a collection of adjacent base pairs that have been identified as being a predicted TAD boundary with probability 1 according to the random forest model.
+We then implemented DBSCAN on the distance matrix (in base pairs) constructed from the midpoints of each PTBA using the R packacge *dbscan* (version 1.1-5) [@hahsler2019dbscan].
+To identify the optimal number of clusters, *k*, the eps parameter ($\epsilon$) was assigned as the respective data resolution.
+The heuristic being that PTBA midpoints with genomic distances less than resolution should occupy the same designated cluster.
+The corresponding MinPts parameter was set to 3.
+We defined these *k* clusters of PTBAs as *predicted TAD boundary regions* (PTBR).
+
+<!--
+We then performed hierarchical clustering on the distance matrix (in base pairs) constructed from the midpoints of each PTBA using complete linkage clustering.
 To identify the optimal number of clusters, *k*, we calculated the mean silhouette score over all possible sizes of clusters *m*:
@@
 Therefore number of clusters, *k*, that maximized the mean silhouette score, $\bar{s}_{m}$ were used to identify groupings of PTBA, which we defined as *predicted TAD boundary regions* (PTBR).
+-->
 
 To precisely identify the PTBA most representative of each PTBR we performed an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
-The midpoint of the corresponding cluster medoid, in this case a particular PTBA, will be defined as a *predicted TAD boundary point* (PTBP).
-In the event that a particular PTBA has an even number of base pairs, then ceiling function was applied to extract the right most base pair.
+The midpoint of the corresponding cluster medoid, in this case a particular PTBA, was defined as a *predicted TAD boundary point* (PTBP).
 Thus, the hierarchical structure of our defined predicted TAD boundary objects were as follows: PTBR > PTBA > PTBP.
-That is, each PTBR is a collection of PTBAs, which are themselves a collection of adjacent base pairs.
-The uniquely identified PTBP was then the midpoint of the most representative PTBA within a PTBR.
+That is, each PTBR is a collection of PTBA midpoints, with the uniquely identified PTBP being the most representative midpoint within a clustered PTBR.
 
@@
 Error bars represent standard deviation from the mean MCC across each chromosome.
-(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.
-Importances were calculated as the mean decrease in accuracy among permuted features in out-of-bag samples.](Figures/annots_specifc_rfe_importances.png)
+(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.](Figures/annots_specifc_rfe_importances.png)
 

### 2020-04-03 Manuscript/manuscript.Rmd
methods edits

@@
 
-To evaluate if our predicted TAD boundaries are biologically significant we will asssess the signal strength obtained from key ChIP-Seq peak elements known to be enriched at TAD boundaries including CTCF, RAD21, SMC3, and ZNF143.
-To do so we will used enrich heatmaps and Student’s t-tests to compare distances from selected ChiP-seq data to our predicted TAD boundaries compared to called TAD boundaries (ARROWHEAD).
+To evaluate if our predicted TAD boundaries are biologically significant we asssessed the signal strength obtained from key ChIP-Seq peak elements known to be enriched at TAD boundaries including CTCF, RAD21, SMC3, and ZNF143.
+To do so we used enriched heatmaps and Wilcoxon Rank-Sum tests to compare distances from selected ChiP-seq data to our predicted TAD boundaries compared to ARROWHEAD boundaries.
 
-Furthermore, we will assess the conservation of our predicted TAD boundaries within cell types and between resolutions, as well as between cell types and within resolutions and compare with ARROWHEAD called TAD boundaries.
-To do so we will evaluate Jaccard Indices.
-Jaccard is a metric used to measure overlap between sets (genomic regions).
-Thus we can use it as measure of overlap between TAD boundaries.
-Given two sets of TAD boundaries (either between resolution or cell type) A and B, we define the Jaccard Index as,
+Furthermore, we assessed the conservation of our predicted TAD boundaries across cell types and compared with ARROWHEAD.
+Boundaries were flanked by resolution and overlaps were evaluated visually using venn diagrams and Jaccard Indices.
+Jaccard is a metric used to measure overlap between sets defined as
 
-$$J_{(A,B)} = \dfrac{A \cap B}{A \cup B}.$$
-To give the sets of boundaries A and B dimensionality to enable us to calculate overlap, we flank each boundary point by a flanking factor, $f=max\{r_{A},r_{B}\}$, where $r_{A(B)}$ is the Hi-C data resolution used to call TADs for A (B).
+$$J_{(A,B)} = \dfrac{A \cap B}{A \cup B}$$
+
+where A and B are genomic regions.
 

### 2020-04-03 Manuscript/manuscript.Rmd
results edits

@@
 
-We developed a computational framework, refered to as *TADRF*, aimed at determining the optimal set of data level characteristics necessary for TAD boundary prediction using Random Forest classification models.
-Our framework is resolution-specific and uses called TAD boundaries as ground truth to establish TAD-boundary and non-TAD boundary regions.
-Under our framework, we binned the linear genome at intervals specific to the Hi-C data resolution used to call TADs.
-TAD boundary regions were defined as regions on the linear genome where a genomic bin contained a called TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as genomic bins that did not contain a TAD boundary ($Y = 0$) (Figure 1 A).
-Under this construction, the number of non-TAD boundary regions are exceed the number of TAD boundary regions.
-To cope with the imbalance among the class of genomic bins, we evaluated three re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries.
+We developed a computational framework<!--, refered to as *TADRF*,--> aimed at determining the optimal set of data level characteristics necessary for TAD boundary prediction using random forest classification models.
+We then leveraged our optimally built random forest to precisely predict the genomic coordinates of TAD boundaries at base pair resolution.
+
+Our framework is resolution-specific and uses arbitrary called TAD boundaries as ground truth to establish TAD-boundary and non-TAD boundary regions.
+To demonstrate, we applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1).
+Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
+TAD boundary regions were defined as regions on the linear genome where a genomic bin contained a called TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as genomic bins that did not contain a TAD boundary ($Y = 0$) (Figure 1A).
+Under this construction, the number of non-TAD boundary regions far exceed the number of TAD boundary regions.
+To cope with the imbalance among the classes of genomic bins, we evaluated three re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries.
 *Random over-sampling* (ROS) was defined as sampling with replacement from TAD boundary regions.
@@
 
-Various one-dimensional cell line-specific ChIP-seq tracks (genomic elements) were used to construct the feature space for the random forests including cis-regulatory elements, histone modifications, and transcription factor binding sites.
+A total of 78 cell type specific functional genomic annotations were used to build the feature space of downstream random forest models (Supplementary Table 2).
+The annotations could be broken down into three sets including histone modifications (HM), cis-regulatory elements (CRE), and transcription factor binding sites (TFBS).
 Four different feature engineering procedures were developed for each genomic element (Figure 1 B).
@@
 
-We applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1).
-Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-A total of 78 cell type specific functional genomic annotations were used to build the feature space of downstream random forest models (Supplementary Table 2).
-The annotations could be broken down into three sets including histone modifications (HM), cis-regulatory elements (CRE), and transcription factor binding sites (TFBS).
-The results presented are for the GM12878 cell line, with K562 results presented in the Supplementary material.
-
 ![**Illustrating the resolution-specific data construction and feature engineering used for downstream random forest modeling.** (A) The linear genome was subsequently binned into resolution-specific intervals.
@@
 (B) Four types of associations between bins and genomic annotations (green shapes) were then used to build the feature space including _Peak Signal_ (Signal), _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.](Figures/model_construction_and_predictor_types.png)
+
+Thus, under our framework, we considered combinations of data for a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, with a specific engineered feature space *P = {Signal, OC, OP, Distance}*, and re-sampling technique *B = {None, RUS, ROS, SMOTE}* (Figure 2).
+Model inputs were evaluated by assessing the balanced accuracy (BA) of each combination.
+Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2 \times 5 \times 4 \times 4 (= 160)$ models.
+The results presented are for the GM12878 cell line, with K562 results presented in the Supplementary material.
+
+![**A diagram of the ensemble framework detailing the steps for combining different inputs used in the random forest model building pipeline.** Step 1 is to establish the rowise (genomic bins) and columnwise (genomic annotations) dimensions of the data matrix, **A**, by combining a resolution (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)).
+Step 2 is to split **A** into a training and testing set according to a 7:3 ratio.
+Step 3 is to apply a re-sampling technique to the training set (no re-sampling, random over-sampling, random under-sampling, or SMOTE re-sampling).
+Step 4 is to implement the random forest algorithm and perform 3-fold cross-validation to tune for the *mtry* parameter.
+Finally, step 5 is to validate the model on the separate test data and evaluate model performance using balanced accuracy (BA).](Figures/ensemble_framework.png)
 
@@
 Furthermore, the data summaries presented in Table 1 were found to be similar to those exibited by the K562 cell line (Supplementary Table 3).
-
-\newpage
 
@@
 Table: Domain data and class imbalance summaries across resolutions for GM12878.
-
-Our computational framework was used to identify the combination of data resolution, predictor type, and re-sampling technique necessary for optimal cell line specific TAD boundary prediction (Figure 2).
-The framework uses data for a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, using a particular predictor type *P = {Signal, OC, OP, Distance}*, and re-sampling technique *B = {None, RUS, ROS, SMOTE}*.
-Once the model inputs were established, we trained a random forest classifier on chromosome-specific sections of the genome using 5-fold cross validation.
-The different combinations of inputs were evaluated by assessing the Matthews Correlation Coefficient (MCC) of each model.
-Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2 \times 5 \times 4 \times 4 \times 21 (= 3360)$ models.
-
-![**A diagram of the ensemble framework detailing the steps for combining different inputs used in the random forest model building pipeline.** Step 1 is to establish the rowise (genomic bins) and columnwise (genomic annotations) dimensions of the data matrix, **A**, by combining a resolution (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)).
-Step 2 is to split **A** into a training and testing set according to a 7:3 ratio.
-Step 3 is to apply a re-sampling technique to the training set (no re-sampling, random over-sampling, random under-sampling, or SMOTE re-sampling).
-Step 4 is to implement the random forest algorithm and perform 5-fold cross-validation to tune for the *mtry* parameter.
-Finally, step 5 is to validate the model on the separate test data for unbiased model evaluation.](Figures/ensemble_framework.png)
 

### 2020-04-03 Manuscript/manuscript.Rmd
results edits

@@
 
-## Random under-sampling, distance-based predictors, and 10 kb resolutions of Hi-C data provided the optimal data level characteristics for TAD boundary prediction
+## 5 kb resolution, random under-sampling, and distance-based predictors provided optimal performance for TAD boundary prediction
 
-Expectedly, when using data with class imbalance present, that is no re-sampling, the models exhibited low MCCs, with very little variability among different resolutions (Figure 3).
+<!--
+Expectedly, when using data with class imbalance present, that is no re-sampling, the models exhibited low balanced accuracies, with very little variability among different resolutions (Figure 3).
 Similarly poor performances were found when using ROS as well.
@@
 These results suggest that simple randomly under-sampling alone can drastically improve TAD boundary prediction.
-<!--These results suggest that a combination of both random over- and under-sampling (SMOTE) can improve TAD boundary prediction.-->Additionally, we found that at higher resolutions, random forest classifiers built using a distance-type feature space yielded substantially higher MCCs when compared to the peak signal stength, overlap count, and overlap percent predictor types.
+Additionally, we found that at higher resolutions, random forest classifiers built using a distance-type feature space yielded substantially higher MCCs when compared to the peak signal stength, overlap count, and overlap percent predictor types.
 As with comparing class balancing techniques, this improvement was less evident at lower resolutions.
-<!--This indicated that models are better able to discriminate between TAD and non-TAD boundary regions when provided with spatially related associations.-->
 
@@
 In summary, our computational framework showed that using random under-sampling, distance-type predictors, and Hi-C data at 10kb resolution yields an optimally performing cell line-specific random forest classification model for TAD boundary prediction.
+-->
 
-![**Models built using distance-type predictors combined with random under-sampling at 10 kb yielded optimal predictive performance for GM12878.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
+![**Models built using distance-type predictors combined with random under-sampling at 5 kb yielded optimal predictive performance for GM12878.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
 Performances are compared across resolution, within each predictor-type: (A) OC, (B) OP, and (C) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/performances.png)
+Performances were evaluated using balanced accuracy.](Figures/performances.png)
 

### 2020-04-29 Scripts_for_results/01_creating_table_of_data_summaries.r
removed file

@@ -1,251 +1,0 @@
-#01 Creating Table of of Data Summeries
-
-## Loading packages and functions
-
-library(S4Vectors)
-library(GenomicRanges)
-library(ggplot2)
-library(caret)
-library(randomForest)
-library(glmnet)
-library(gbm)
-library(DMwR)
-library(rtracklayer)
-library(Biostrings)
-library(BSgenome)
-library(cluster)
-library(pROC)
-library(SuperLearner)
-library(data.table)
-library(PRROC)
-library(bigmemory)
-library(ranger)
-library(dplyr)
-library(parallel)
-library(doSNOW)
-library(foreach)
-library(pbapply)
-library(ggpubr)
-library(scales)
-library(GGally)
-library(VennDiagram)
-library(network)
-library(sna)
-library(gtable)
-library(grid)
-library(magrittr) 
-library(DT)
-library(tidyverse)
-library(reshape)
-library(ROSE)
-library(lattice)
-library(corrplot)
-library(cluster)
-library(RColorBrewer)
-library(GenometriCorr)
-library(ggsignif)
-library(Vennerable)
-library(VennDiagram)
-library(ChIPpeakAnno)
-library(EnrichedHeatmap)
-
-source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
-
-
-### GM12878
-
-CHR = paste0("CHR", c(1:8,10:22))
-numtads <- numeric()
-numbounds <- numeric()
-numbins <- numeric()
-imbalance <- numeric()
-r = c("5000","10000","25000","50000","100000")
-
-getChrLength <- function(genome = "BSgenome.Hsapiens.UCSC.hg19"){
-  g <- getBSgenome(genome, masked=FALSE)
[…]

### 2020-04-29 Scripts_for_results/02_creating_lineplot_of_balanced_accuracies.r

@@ -1,654 +1,0 @@
-#02 Creating line plot of balanced accuracies
-
-## Loading packages and functions
-
-library(S4Vectors)
-library(GenomicRanges)
-library(ggplot2)
-library(caret)
-library(randomForest)
-library(glmnet)
-library(gbm)
-library(DMwR)
-library(rtracklayer)
-library(Biostrings)
-library(BSgenome)
-library(cluster)
-library(pROC)
-library(SuperLearner)
-library(data.table)
-library(PRROC)
-library(bigmemory)
-library(ranger)
-library(dplyr)
-library(parallel)
-library(doSNOW)
-library(foreach)
-library(pbapply)
-library(ggpubr)
-library(scales)
-library(GGally)
-library(VennDiagram)
-library(network)
-library(sna)
-library(gtable)
-library(grid)
-library(magrittr) 
-library(DT)
-library(tidyverse)
-library(reshape)
-library(ROSE)
-library(lattice)
-library(corrplot)
-library(cluster)
-library(RColorBrewer)
-library(GenometriCorr)
-library(ggsignif)
-library(Vennerable)
-library(VennDiagram)
-library(ChIPpeakAnno)
-library(EnrichedHeatmap)
-
-source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
-
-### GM12878
-
-####5kb
-
-badata_gm12878_5kb <- numeric()
-for(j in c("none","ros","rus","smote")){
-    for(k in c("distance", "oc", "op", "signal")){
-      print(c(j,k))
-      files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
-                                 "WHOLE", 
-                                 "/",
[…]

### 2020-04-29 Scripts_for_results/03_creating_annotation_specifc_barplots.r

@@ -1,339 +1,0 @@
-#03 Creating annotation specific barplots
-
-## Loading packages and functions
-
-library(S4Vectors)
-library(GenomicRanges)
-library(ggplot2)
-library(caret)
-library(randomForest)
-library(glmnet)
-library(gbm)
-library(DMwR)
-library(rtracklayer)
-library(Biostrings)
-library(BSgenome)
-library(cluster)
-library(pROC)
-library(SuperLearner)
-library(data.table)
-library(PRROC)
-library(bigmemory)
-library(ranger)
-library(dplyr)
-library(parallel)
-library(doSNOW)
-library(foreach)
-library(pbapply)
-library(ggpubr)
-library(scales)
-library(GGally)
-library(VennDiagram)
-library(network)
-library(sna)
-library(gtable)
-library(grid)
-library(magrittr) 
-library(DT)
-library(tidyverse)
-library(reshape)
-library(ROSE)
-library(lattice)
-library(corrplot)
-library(cluster)
-library(RColorBrewer)
-library(GenometriCorr)
-library(ggsignif)
-library(Vennerable)
-library(VennDiagram)
-library(ChIPpeakAnno)
-library(EnrichedHeatmap)
-
-source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
-
-### GM12878 (rus; distance types)
-
-#### 5kb
-
-badata_gm12878_5kb <- numeric()
-
-for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
-  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
[…]

### 2020-04-29 Scripts_for_results/04_creating_rfe_lineplot.r

@@ -1,136 +1,0 @@
-#04 Creating RFE line plot
-
-## Loading packages and functions
-
-library(S4Vectors)
-library(GenomicRanges)
-library(ggplot2)
-library(caret)
-library(randomForest)
-library(glmnet)
-library(gbm)
-library(DMwR)
-library(rtracklayer)
-library(Biostrings)
-library(BSgenome)
-library(cluster)
-library(pROC)
-library(SuperLearner)
-library(data.table)
-library(PRROC)
-library(bigmemory)
-library(ranger)
-library(dplyr)
-library(parallel)
-library(doSNOW)
-library(foreach)
-library(pbapply)
-library(ggpubr)
-library(scales)
-library(GGally)
-library(VennDiagram)
-library(network)
-library(sna)
-library(gtable)
-library(grid)
-library(magrittr) 
-library(DT)
-library(tidyverse)
-library(reshape)
-library(ROSE)
-library(lattice)
-library(corrplot)
-library(cluster)
-library(RColorBrewer)
-library(GenometriCorr)
-library(ggsignif)
-library(Vennerable)
-library(VennDiagram)
-library(ChIPpeakAnno)
-library(EnrichedHeatmap)
-
-source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
-
-### GM12878
-
-#### Optimal parameters: 5 kb, TFBS, distance type predictors, RUS
-
-rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/WHOLE/rus/distance/TADrfe_3.rds"))
[…]

### 2020-04-29 Scripts_for_results/05_creating_importance_plot.r

@@ -1,241 +1,0 @@
-#05 Creating importance plot
-
-## Loading packages and functions
-
-library(S4Vectors)
-library(GenomicRanges)
-library(ggplot2)
-library(caret)
-library(randomForest)
-library(glmnet)
-library(gbm)
-library(DMwR)
-library(rtracklayer)
-library(Biostrings)
-library(BSgenome)
-library(cluster)
-library(pROC)
-library(SuperLearner)
-library(data.table)
-library(PRROC)
-library(bigmemory)
-library(ranger)
-library(dplyr)
-library(parallel)
-library(doSNOW)
-library(foreach)
-library(pbapply)
-library(ggpubr)
-library(scales)
-library(GGally)
-library(VennDiagram)
-library(network)
-library(sna)
-library(gtable)
-library(grid)
-library(magrittr) 
-library(DT)
-library(tidyverse)
-library(reshape)
-library(ROSE)
-library(lattice)
-library(corrplot)
-library(cluster)
-library(RColorBrewer)
-library(GenometriCorr)
-library(ggsignif)
-library(Vennerable)
-library(VennDiagram)
-library(ChIPpeakAnno)
-library(EnrichedHeatmap)
-
-source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
-
-### GM12878
-
-#### Importance barchart/heatmap
-
-rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/WHOLE/rus/distance/TADrfe_3.rds"))
-
-set.size = 8
[…]

### 2020-04-29 Scripts_for_results/06_creating_enriched_heatmaps.r

@@ -1,197 +1,0 @@
-#06 Creating enriched heatmaps
-
-## Loading packages and functions
-
-library(S4Vectors)
-library(GenomicRanges)
-library(ggplot2)
-library(caret)
-library(randomForest)
-library(glmnet)
-library(gbm)
-library(DMwR)
-library(rtracklayer)
-library(Biostrings)
-library(BSgenome)
-library(cluster)
-library(pROC)
-library(SuperLearner)
-library(data.table)
-library(PRROC)
-library(bigmemory)
-library(ranger)
-library(dplyr)
-library(parallel)
-library(doSNOW)
-library(foreach)
-library(pbapply)
-library(ggpubr)
-library(scales)
-library(GGally)
-library(VennDiagram)
-library(network)
-library(sna)
-library(gtable)
-library(grid)
-library(magrittr) 
-library(DT)
-library(tidyverse)
-library(reshape)
-library(ROSE)
-library(lattice)
-library(corrplot)
-library(cluster)
-library(RColorBrewer)
-library(GenometriCorr)
-library(ggsignif)
-library(Vennerable)
-library(VennDiagram)
-library(ChIPpeakAnno)
-library(EnrichedHeatmap)
-
-source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
-
-### GM12878
-
-#### Create granges from top tfbs
-
-genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
-                                             pattern="*.bed",
-											 signal=4)
-
[…]

### 2020-04-29 Scripts_for_results/07_creating_distance_to_chipseq.r

@@ -1,270 +1,0 @@
-#07 Creating distance to chip-seq plots
-
-## Loading packages and functions
-
-library(S4Vectors)
-library(GenomicRanges)
-library(ggplot2)
-library(caret)
-library(randomForest)
-library(glmnet)
-library(gbm)
-library(DMwR)
-library(rtracklayer)
-library(Biostrings)
-library(BSgenome)
-library(cluster)
-library(pROC)
-library(SuperLearner)
-library(data.table)
-library(PRROC)
-library(bigmemory)
-library(ranger)
-library(dplyr)
-library(parallel)
-library(doSNOW)
-library(foreach)
-library(pbapply)
-library(ggpubr)
-library(scales)
-library(GGally)
-library(VennDiagram)
-library(network)
-library(sna)
-library(gtable)
-library(grid)
-library(magrittr) 
-library(DT)
-library(tidyverse)
-library(reshape)
-library(ROSE)
-library(lattice)
-library(corrplot)
-library(cluster)
-library(RColorBrewer)
-library(GenometriCorr)
-library(ggsignif)
-library(Vennerable)
-library(VennDiagram)
-library(ChIPpeakAnno)
-library(EnrichedHeatmap)
-
-source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
-
-### GM12878
-
-#### Create granges from top tfbs
-
-genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
-                                             pattern="*.bed",
-											 signal=4)
-
[…]

### 2020-04-29 Scripts_for_results/08_creating_venn_diagrams.r

@@ -1,199 +1,0 @@
-#08 Creating venn diagrams
-
-## Loading packages and functions
-
-library(S4Vectors)
-library(GenomicRanges)
-library(ggplot2)
-library(caret)
-library(randomForest)
-library(glmnet)
-library(gbm)
-library(DMwR)
-library(rtracklayer)
-library(Biostrings)
-library(BSgenome)
-library(cluster)
-library(pROC)
-library(SuperLearner)
-library(data.table)
-library(PRROC)
-library(bigmemory)
-library(ranger)
-library(dplyr)
-library(parallel)
-library(doSNOW)
-library(foreach)
-library(pbapply)
-library(ggpubr)
-library(scales)
-library(GGally)
-library(VennDiagram)
-library(network)
-library(sna)
-library(gtable)
-library(grid)
-library(magrittr) 
-library(DT)
-library(tidyverse)
-library(reshape)
-library(ROSE)
-library(lattice)
-library(corrplot)
-library(cluster)
-library(RColorBrewer)
-library(GenometriCorr)
-library(ggsignif)
-library(Vennerable)
-library(VennDiagram)
-library(ChIPpeakAnno)
-library(EnrichedHeatmap)
-
-source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
-
-### Extracting called and predicted boundaries
-
-#### GM12878
[…]

### 2020-04-29 Scripts_for_results/09_visualizing_example_of_preciseTAD_predictions.r

@@ -1,229 +1,0 @@
-#09 visualizing example of predicted TAD boundaries
-
-## Loading packages and functions
-
-library(S4Vectors)
-library(GenomicRanges)
-library(ggplot2)
-library(caret)
-library(randomForest)
-library(glmnet)
-library(gbm)
-library(DMwR)
-library(rtracklayer)
-library(Biostrings)
-library(BSgenome)
-library(cluster)
-library(pROC)
-library(SuperLearner)
-library(data.table)
-library(PRROC)
-library(bigmemory)
-library(ranger)
-library(dplyr)
-library(parallel)
-library(doSNOW)
-library(foreach)
-library(pbapply)
-library(ggpubr)
-library(scales)
-library(GGally)
-library(VennDiagram)
-library(network)
-library(sna)
-library(gtable)
-library(grid)
-library(magrittr) 
-library(DT)
-library(tidyverse)
-library(reshape)
-library(ROSE)
-library(lattice)
-library(corrplot)
-library(cluster)
-library(RColorBrewer)
-library(GenometriCorr)
-library(ggsignif)
-library(Vennerable)
-library(VennDiagram)
-library(ChIPpeakAnno)
-library(EnrichedHeatmap)
-
-source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADrf.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
-
-## Extracting TAD boundaries using the extract_boundaries_func function for ARROWHEAD defined TADs at 10kb resolution
-
-domains <- read.table("Z:/TAD_data_analysis/GM12878/5kb/GM12878_domain_data_5000.b.txt")
-bounds.GR <- extract_boundaries_func(domains.mat=domains, 
-                                     preprocess=FALSE, 
[…]

### 2020-04-29 Scripts_for_results/01_creating_table_of_data_summaries.Rmd
initial commit

---
title: "Creating Table of Data Summaries"
author: "Spiro Stilianoudakis"
date: "4/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages and functions

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

## Creating seqdata

```{r}

getChrLength <- function(genome = "BSgenome.Hsapiens.UCSC.hg19"){
  g <- getBSgenome(genome, masked=FALSE)
  data.frame(chrom=1:24, length=seqlengths(g)[1:24])
}
.chrAsNum <- function(tbl){
  tbl$chrom <- gsub("chr", "", tbl$chrom)
  tbl$chrom[tbl$chrom=="X"] <- 23
  tbl$chrom[tbl$chrom=="Y"] <- 24
  tbl$chrom <- as.numeric(tbl$chrom)
  tbl[order(tbl$chrom),]
}
getCentromeres <- function( genome="hg19" ){
  mySession <- try(browserSession("UCSC"), silent=TRUE)
  # In case of failure, try another mirror
  if(inherits(mySession, "try-error"))
    mySession <- browserSession("UCSC",
                                url="http://genome-euro.ucsc.edu/cgi-bin/")
  genome(mySession) <- genome
  obj <- ucscTableQuery(mySession, table="gap")
  tbl <- getTable(obj)
  tbl <- tbl[tbl$type=="centromere", c("chrom", "chromStart", "chromEnd")]
  colnames(tbl)[2:3] <- c("centromerStart", "centromerEnd")
  .chrAsNum(tbl)
}
makeHg19 <- function(){
  tbl <- merge(getChrLength(), getCentromeres(), by="chrom")
  cumlen <- c(0, cumsum(as.numeric(tbl$length))[-nrow(tbl)])
  cbind.data.frame(tbl, cumlen=cumlen)    
}
hg19 <- makeHg19()
hg19$chrom <- paste0("CHR",hg19$chrom)

seqLength <- hg19$length[hg19$chrom %in% CHR]
seqDataList <- list()
for(k in 1:length(seqLength)){
  seqData <- c(0:seqLength[k])
  centromereStart <- hg19$centromerStart[hg19$chrom==CHR[k]]
  centromereEnd <- hg19$centromerEnd[hg19$chrom==CHR[k]]
  seqDataList[[k]] <- seqData[-which(seqData %in% c(centromereStart:centromereEnd))]
}
names(seqDataList) <- CHR

```

## ARROWHEAD

### GM12878

```{r}
CHR = paste0("CHR", c(1:8,10:22))
numtads <- numeric()
numbounds <- numeric()
numbins <- numeric()
imbalance <- numeric()
r = c("5000","10000","25000","50000","100000")

for(i in 1:length(r)){
  resolution = as.integer(r[i])

  domains <- read.table(paste0("Z:/TAD_data_analysis/GSE63525_data/arrowhead_output/GM12878/GM12878_domain_data_",
                               r[i],
                               ".b.txt"))

  domains <- domains[which(domains$V1 %in% as.numeric(gsub("CHR","",CHR))),]

  numtads[i] <- nrow(domains)

  bounds <- extract_boundaries_func(domains.mat=domains, 
                                    preprocess=FALSE, 
                                    CHR=CHR, 
                                    resolution=resolution)

  numbounds[i] <- length(bounds)

  bounds.GR.flank <- flank(bounds, width=(resolution/2), both=TRUE)

  data_mat_list <- list()
  outcome_list <- list()
  #full_list <- list()
  #train_list <- list()
  #test_list <- list()

  for(j in 1:length(CHR)){
    #start = 0
    start = (resolution/2)
    end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% resolution) + (resolution/2)
    #end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% (resolution/2))
    rows = seqDataList[[j]][seqDataList[[j]] %in% seq(start, end, resolution)]

    #data_mat_list[[j]] <- matrix(nrow=length(rows),
    #                             ncol=length(genomicElements.GR))
    #rownames(data_mat_list[[j]]) <- rows

    outcome_list[[j]] <- countOverlaps(GRanges(seqnames = tolower(CHR[j]),
                                               IRanges(#start = as.numeric(rownames(data_mat_list[[j]])),
                                                       start = rows,
                                                       width = resolution)), bounds.GR.flank)
    outcome_list[[j]] <- ifelse(outcome_list[[j]],1,0)
    outcome_list[[j]] <- factor(outcome_list[[j]])
    levels(outcome_list[[j]]) <- c("No", "Yes")

    #full_list[[j]] <- cbind.data.frame(outcome_list[[j]], data_mat_list[[j]])
    #names(full_list[[j]])[1] <- "y"
  }
  ci <- unlist(outcome_list)
  numbins[i] <- length(ci)
  imbalance[i] <- as.numeric(round(table(ci)[2]/sum(table(ci)),2))
}

data.frame(resolution = c("5 kb",
                          "10 kb",
                          "25 kb",
                          "50 kb",
                          "100 kb"),
           numtads=numtads,
           numbounds=numbounds,
           numbins=numbins,
           imbalance=imbalance)

```

### K562

```{r}
CHR = paste0("CHR", c(1:8,10:22))
numtads <- numeric()
numbounds <- numeric()
numbins <- numeric()
imbalance <- numeric()
r = c("5000","10000","25000","50000","100000")

for(i in 1:length(r)){
  resolution = as.integer(r[i])

  domains <- read.table(paste0("Z:/TAD_data_analysis/GSE63525_data/arrowhead_output/K562/K562_domain_data_",
                               r[i],
                               ".b.txt"))

  domains <- domains[which(domains$V1 %in% as.numeric(gsub("CHR","",CHR))),]

  numtads[i] <- nrow(domains)

  bounds <- extract_boundaries_func(domains.mat=domains, 
                                    preprocess=FALSE, 
                                    CHR=CHR, 
                                    resolution=resolution)

  numbounds[i] <- length(bounds)

  bounds.GR.flank <- flank(bounds, width=(resolution/2), both=TRUE)

  data_mat_list <- list()
  outcome_list <- list()
  #full_list <- list()
  #train_list <- list()
  #test_list <- list()

  for(j in 1:length(CHR)){
    print(c(r[i],CHR[j]))
    #start = 0
    start = (resolution/2)
    end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% resolution) + (resolution/2)
    #end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% (resolution/2))
    rows = seqDataList[[j]][seqDataList[[j]] %in% seq(start, end, resolution)]

    #data_mat_list[[j]] <- matrix(nrow=length(rows),
    #                             ncol=length(genomicElements.GR))
    #rownames(data_mat_list[[j]]) <- rows

    outcome_list[[j]] <- countOverlaps(GRanges(seqnames = tolower(CHR[j]),
                                               IRanges(#start = as.numeric(rownames(data_mat_list[[j]])),
                                                 start = rows,
                                                 width = resolution)), bounds.GR.flank)
    outcome_list[[j]] <- ifelse(outcome_list[[j]],1,0)
    outcome_list[[j]] <- factor(outcome_list[[j]])
    levels(outcome_list[[j]]) <- c("No", "Yes")

    #full_list[[j]] <- cbind.data.frame(outcome_list[[j]], data_mat_list[[j]])
    #names(full_list[[j]])[1] <- "y"
  }
  ci <- unlist(outcome_list)
  numbins[i] <- length(ci)
  imbalance[i] <- as.numeric(round(table(ci)[2]/sum(table(ci)),2))
}

data.frame(resolution = c("5 kb",
                          "10 kb",
                          "25 kb",
                          "50 kb",
                          "100 kb"),
           numtads=numtads,
           numbounds=numbounds,
           numbins=numbins,
           imbalance=imbalance)

```

## SpectralTAD

### GM12878

```{r}
CHR = paste0("CHR", c(1:8,10:22))
numtads <- numeric()
numbounds <- numeric()
numbins <- numeric()
imbalance <- numeric()
r = c("5","10","25","50","100")

for(i in 1:length(r)){
  resolution = as.integer(r[i])*1000

  domains <- as.data.frame(readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/spectralTAD/GM12878/domain_data_gm12878_",
                                          r[i],
                                          "kb.rds")))

  domains <- domains[which(domains$chr %in% as.numeric(gsub("CHR","",CHR))),]

  numtads[i] <- nrow(domains)

  bounds <- extract_boundaries_func(domains.mat=domains, 
                                    preprocess=FALSE, 
                                    CHR=CHR, 
                                    resolution=resolution)

  numbounds[i] <- length(bounds)

  bounds.GR.flank <- flank(bounds, width=(resolution/2), both=TRUE)

  data_mat_list <- list()
  outcome_list <- list()
  #full_list <- list()
  #train_list <- list()
  #test_list <- list()

  for(j in 1:length(CHR)){
    print(c(r[i],CHR[j]))
    #start = 0
    start = (resolution/2)
    end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% resolution) + (resolution/2)
    #end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% (resolution/2))
    rows = seqDataList[[j]][seqDataList[[j]] %in% seq(start, end, resolution)]

    #data_mat_list[[j]] <- matrix(nrow=length(rows),
    #                             ncol=length(genomicElements.GR))
    #rownames(data_mat_list[[j]]) <- rows

    outcome_list[[j]] <- countOverlaps(GRanges(seqnames = tolower(CHR[j]),
                                               IRanges(#start = as.numeric(rownames(data_mat_list[[j]])),
                                                 start = rows,
                                                 width = resolution)), bounds.GR.flank)
    outcome_list[[j]] <- ifelse(outcome_list[[j]],1,0)
    outcome_list[[j]] <- factor(outcome_list[[j]])
    levels(outcome_list[[j]]) <- c("No", "Yes")

    #full_list[[j]] <- cbind.data.frame(outcome_list[[j]], data_mat_list[[j]])
    #names(full_list[[j]])[1] <- "y"
  }
  ci <- unlist(outcome_list)
  numbins[i] <- length(ci)
  imbalance[i] <- as.numeric(round(table(ci)[2]/sum(table(ci)),2))
}

data.frame(resolution = c("5 kb",
                          "10 kb",
                          "25 kb",
                          "50 kb",
                          "100 kb"),
           numtads=numtads,
           numbounds=numbounds,
           numbins=numbins,
           imbalance=imbalance)

```

### K562

```{r}
CHR = paste0("CHR", c(1:8,10:22))
numtads <- numeric()
numbounds <- numeric()
numbins <- numeric()
imbalance <- numeric()
r = c("5","10","25","50","100")

for(i in 1:length(r)){
  resolution = as.integer(r[i])*1000

  domains <- as.data.frame(readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/spectralTAD/K562/domain_data_k562_",
                                          r[i],
                                          "kb.rds")))

  domains <- domains[which(domains$chr %in% as.numeric(gsub("CHR","",CHR))),]

  numtads[i] <- nrow(domains)

  bounds <- extract_boundaries_func(domains.mat=domains, 
                                    preprocess=FALSE, 
                                    CHR=CHR, 
                                    resolution=resolution)

  numbounds[i] <- length(bounds)

  bounds.GR.flank <- flank(bounds, width=(resolution/2), both=TRUE)

  data_mat_list <- list()
  outcome_list <- list()
  #full_list <- list()
  #train_list <- list()
  #test_list <- list()

  for(j in 1:length(CHR)){
    print(c(r[i],CHR[j]))
    #start = 0
    start = (resolution/2)
    end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% resolution) + (resolution/2)
    #end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% (resolution/2))
    rows = seqDataList[[j]][seqDataList[[j]] %in% seq(start, end, resolution)]

    #data_mat_list[[j]] <- matrix(nrow=length(rows),
    #                             ncol=length(genomicElements.GR))
    #rownames(data_mat_list[[j]]) <- rows

    outcome_list[[j]] <- countOverlaps(GRanges(seqnames = tolower(CHR[j]),
                                               IRanges(#start = as.numeric(rownames(data_mat_list[[j]])),
                                                 start = rows,
                                                 width = resolution)), bounds.GR.flank)
    outcome_list[[j]] <- ifelse(outcome_list[[j]],1,0)
    outcome_list[[j]] <- factor(outcome_list[[j]])
    levels(outcome_list[[j]]) <- c("No", "Yes")

    #full_list[[j]] <- cbind.data.frame(outcome_list[[j]], data_mat_list[[j]])
    #names(full_list[[j]])[1] <- "y"
  }
  ci <- unlist(outcome_list)
  numbins[i] <- length(ci)
  imbalance[i] <- as.numeric(round(table(ci)[2]/sum(table(ci)),2))
}

data.frame(resolution = c("5 kb",
                          "10 kb",
                          "25 kb",
                          "50 kb",
                          "100 kb"),
           numtads=numtads,
           numbounds=numbounds,
           numbins=numbins,
           imbalance=imbalance)

```

## PEAKACHU

### GM12878

```{r}
CHR = paste0("CHR", c(1:8,10:22))
numtads <- numeric()
numbounds <- numeric()
numbins <- numeric()
imbalance <- numeric()
r = "10000"

#for(i in 1:length(r)){
resolution = as.integer(r)

domains <- readRDS("/home/stilianoudakisc/TAD_data_analysis/peakachu/peakachu_GM12878.rds")

domains <- domains[which(domains$chr %in% as.numeric(gsub("CHR","",CHR))),]

numtads <- nrow(domains)

bounds <- extract_boundaries_func(domains.mat=domains, 
                                  preprocess=FALSE, 
                                  CHR=CHR, 
                                  resolution=resolution)

numbounds <- length(bounds)

bounds.GR.flank <- flank(bounds, width=(resolution/2), both=TRUE)

data_mat_list <- list()
outcome_list <- list()
#full_list <- list()
#train_list <- list()
#test_list <- list()

for(j in 1:length(CHR)){
  print(c(r,CHR[j]))
  #start = 0
  start = (resolution/2)
  end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% resolution) + (resolution/2)
  #end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% (resolution/2))
  rows = seqDataList[[j]][seqDataList[[j]] %in% seq(start, end, resolution)]

  #data_mat_list[[j]] <- matrix(nrow=length(rows),
  #                             ncol=length(genomicElements.GR))
  #rownames(data_mat_list[[j]]) <- rows

  outcome_list[[j]] <- countOverlaps(GRanges(seqnames = tolower(CHR[j]),
                                             IRanges(#start = as.numeric(rownames(data_mat_list[[j]])),
                                               start = rows,
                                               width = resolution)), bounds.GR.flank)
  outcome_list[[j]] <- ifelse(outcome_list[[j]],1,0)
  outcome_list[[j]] <- factor(outcome_list[[j]])
  levels(outcome_list[[j]]) <- c("No", "Yes")

  #full_list[[j]] <- cbind.data.frame(outcome_list[[j]], data_mat_list[[j]])
  #names(full_list[[j]])[1] <- "y"
}
ci <- unlist(outcome_list)
numbins <- length(ci)
imbalance <- as.numeric(round(table(ci)[2]/sum(table(ci)),2))
#}

data.frame(resolution = c("10 kb"),
           numtads=numtads,
           numbounds=numbounds,
           numbins=numbins,
           imbalance=imbalance)

```

### K562

```{r}
CHR = paste0("CHR", c(1:8,10:22))
numtads <- numeric()
numbounds <- numeric()
numbins <- numeric()
imbalance <- numeric()
r = "10000"

#for(i in 1:length(r)){
resolution = as.integer(r)

domains <- readRDS("/home/stilianoudakisc/TAD_data_analysis/peakachu/peakachu_K562.rds")

domains <- domains[which(domains$chr %in% as.numeric(gsub("CHR","",CHR))),]

numtads <- nrow(domains)

bounds <- extract_boundaries_func(domains.mat=domains, 
                                  preprocess=FALSE, 
                                  CHR=CHR, 
                                  resolution=resolution)

numbounds <- length(bounds)

bounds.GR.flank <- flank(bounds, width=(resolution/2), both=TRUE)

data_mat_list <- list()
outcome_list <- list()
#full_list <- list()
#train_list <- list()
#test_list <- list()

for(j in 1:length(CHR)){
  print(c(r,CHR[j]))
  #start = 0
  start = (resolution/2)
  end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% resolution) + (resolution/2)
  #end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% (resolution/2))
  rows = seqDataList[[j]][seqDataList[[j]] %in% seq(start, end, resolution)]

  #data_mat_list[[j]] <- matrix(nrow=length(rows),
  #                             ncol=length(genomicElements.GR))
  #rownames(data_mat_list[[j]]) <- rows

  outcome_list[[j]] <- countOverlaps(GRanges(seqnames = tolower(CHR[j]),
                                             IRanges(#start = as.numeric(rownames(data_mat_list[[j]])),
                                               start = rows,
                                               width = resolution)), bounds.GR.flank)
  outcome_list[[j]] <- ifelse(outcome_list[[j]],1,0)
  outcome_list[[j]] <- factor(outcome_list[[j]])
  levels(outcome_list[[j]]) <- c("No", "Yes")

  #full_list[[j]] <- cbind.data.frame(outcome_list[[j]], data_mat_list[[j]])
  #names(full_list[[j]])[1] <- "y"
}
ci <- unlist(outcome_list)
numbins <- length(ci)
imbalance <- as.numeric(round(table(ci)[2]/sum(table(ci)),2))
#}

data.frame(resolution = c("10 kb"),
           numtads=numtads,
           numbounds=numbounds,
           numbins=numbins,
           imbalance=imbalance)

```

## LOLLIPOP

### GM12878

```{r}
CHR = paste0("CHR", c(1:8,10:22))
numtads <- numeric()
numbounds <- numeric()
numbins <- numeric()
imbalance <- numeric()
r = "10000"

#for(i in 1:length(r)){
resolution = as.integer(r)

domains <- readRDS("/home/stilianoudakisc/TAD_data_analysis/lollipop/lollipop_GM12878.rds")

domains <- domains[which(domains$chr %in% as.numeric(gsub("CHR","",CHR))),]

numtads <- nrow(domains)

bounds <- extract_boundaries_func(domains.mat=domains, 
                                  preprocess=FALSE, 
                                  CHR=CHR, 
                                  resolution=resolution)

numbounds <- length(bounds)

bounds.GR.flank <- flank(bounds, width=(resolution/2), both=TRUE)

data_mat_list <- list()
outcome_list <- list()
#full_list <- list()
#train_list <- list()
#test_list <- list()

for(j in 1:length(CHR)){
  print(c(r,CHR[j]))
  #start = 0
  start = (resolution/2)
  end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% resolution) + (resolution/2)
  #end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% (resolution/2))
  rows = seqDataList[[j]][seqDataList[[j]] %in% seq(start, end, resolution)]

  #data_mat_list[[j]] <- matrix(nrow=length(rows),
  #                             ncol=length(genomicElements.GR))
  #rownames(data_mat_list[[j]]) <- rows

  outcome_list[[j]] <- countOverlaps(GRanges(seqnames = tolower(CHR[j]),
                                             IRanges(#start = as.numeric(rownames(data_mat_list[[j]])),
                                               start = rows,
                                               width = resolution)), bounds.GR.flank)
  outcome_list[[j]] <- ifelse(outcome_list[[j]],1,0)
  outcome_list[[j]] <- factor(outcome_list[[j]])
  levels(outcome_list[[j]]) <- c("No", "Yes")

  #full_list[[j]] <- cbind.data.frame(outcome_list[[j]], data_mat_list[[j]])
  #names(full_list[[j]])[1] <- "y"
}
ci <- unlist(outcome_list)
numbins <- length(ci)
imbalance <- as.numeric(round(table(ci)[2]/sum(table(ci)),2))
#}

data.frame(resolution = c("10 kb"),
           numtads=numtads,
           numbounds=numbounds,
           numbins=numbins,
           imbalance=imbalance)

```

### K562

```{r}
CHR = paste0("CHR", c(1:8,10:22))
numtads <- numeric()
numbounds <- numeric()
numbins <- numeric()
imbalance <- numeric()
r = "10000"

#for(i in 1:length(r)){
resolution = as.integer(r)

domains <- readRDS("/home/stilianoudakisc/TAD_data_analysis/lollipop/lollipop_K562.rds")

domains <- domains[which(domains$chr %in% as.numeric(gsub("CHR","",CHR))),]

numtads <- nrow(domains)

bounds <- extract_boundaries_func(domains.mat=domains, 
                                  preprocess=FALSE, 
                                  CHR=CHR, 
                                  resolution=resolution)

numbounds <- length(bounds)

bounds.GR.flank <- flank(bounds, width=(resolution/2), both=TRUE)

data_mat_list <- list()
outcome_list <- list()
#full_list <- list()
#train_list <- list()
#test_list <- list()

for(j in 1:length(CHR)){
  print(c(r,CHR[j]))
  #start = 0
  start = (resolution/2)
  end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% resolution) + (resolution/2)
  #end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% (resolution/2))
  rows = seqDataList[[j]][seqDataList[[j]] %in% seq(start, end, resolution)]

  #data_mat_list[[j]] <- matrix(nrow=length(rows),
  #                             ncol=length(genomicElements.GR))
  #rownames(data_mat_list[[j]]) <- rows

  outcome_list[[j]] <- countOverlaps(GRanges(seqnames = tolower(CHR[j]),
                                             IRanges(#start = as.numeric(rownames(data_mat_list[[j]])),
                                               start = rows,
                                               width = resolution)), bounds.GR.flank)
  outcome_list[[j]] <- ifelse(outcome_list[[j]],1,0)
  outcome_list[[j]] <- factor(outcome_list[[j]])
  levels(outcome_list[[j]]) <- c("No", "Yes")

  #full_list[[j]] <- cbind.data.frame(outcome_list[[j]], data_mat_list[[j]])
  #names(full_list[[j]])[1] <- "y"
}
ci <- unlist(outcome_list)
numbins <- length(ci)
imbalance <- as.numeric(round(table(ci)[2]/sum(table(ci)),2))
#}

data.frame(resolution = c("10 kb"),
           numtads=numtads,
           numbounds=numbounds,
           numbins=numbins,
           imbalance=imbalance)

```

### 2020-04-29 Scripts_for_results/02_creating_lineplot_of_balanced_accuracies.Rmd
initial commit

---
title: "Creating line plot of balanced accuracies"
author: "Spiro Stilianoudakis"
date: "4/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages and functions

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

## ARROWHEAD

### GM12878

####5kb

```{r}
badata_gm12878_5kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF.rds"))
      perfdata <- perfdata[[3]]

      badata_gm12878_5kb <- rbind(badata_gm12878_5kb,
                                   perfdata[10,2])
    }
  }
}
```

####10kb

```{r}
badata_gm12878_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF.rds"))
      perfdata <- perfdata[[3]]

      badata_gm12878_10kb <- rbind(badata_gm12878_10kb,
                                   perfdata[10,2])
    }
  }
}

```

####25kb

```{r}
badata_gm12878_25kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF.rds"))
      perfdata <- perfdata[[3]]

      badata_gm12878_25kb <- rbind(badata_gm12878_25kb,
                                   perfdata[10,2])
    }
  }
}

```

####50kb

```{r}
badata_gm12878_50kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF.rds"))
      perfdata <- perfdata[[3]]

      badata_gm12878_50kb <- rbind(badata_gm12878_50kb,
                                   perfdata[10,2])
    }
  }
}

```

####100kb

```{r}
badata_gm12878_100kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF.rds"))
      perfdata <- perfdata[[3]]

      badata_gm12878_100kb <- rbind(badata_gm12878_100kb,
                                    perfdata[10,2])
    }
  }
}

```

#### Plotting

```{r}
all_rfperfs <- rbind.data.frame(badata_gm12878_5kb,
                                badata_gm12878_10kb,
                                badata_gm12878_25kb,
                                badata_gm12878_50kb,
                                badata_gm12878_100kb)
all_rfperfs$CL <- c(rep("GM12878", length(badata_gm12878_5kb)*5))
all_rfperfs$Resolution <- c(rep("5 kb", length(badata_gm12878_5kb)),
                            rep("10 kb", length(badata_gm12878_10kb)),
                            rep("25 kb", length(badata_gm12878_25kb)),
                            rep("50 kb", length(badata_gm12878_50kb)),
                            rep("100 kb", length(badata_gm12878_100kb)))
all_rfperfs$Resampling <- c(rep("None", 4),
                            rep("ROS", 4),
                            rep("RUS", 4),
                            rep("SMOTE", 4))
all_rfperfs$Predictor <- c("Distance", "OC", "OP", "Signal")
all_rfperfs$Chromosome <- c(rep("CHR1", 16),
                            rep("CHR2", 16),
                            rep("CHR3", 16),
                            rep("CHR4", 16),
                            rep("CHR5", 16),
                            rep("CHR6", 16),
                            rep("CHR7", 16),
                            rep("CHR8", 16),
                            rep("CHR10", 16),
                            rep("CHR11", 16),
                            rep("CHR12", 16),
                            rep("CHR13", 16),
                            rep("CHR14", 16),
                            rep("CHR15", 16),
                            rep("CHR16", 16),
                            rep("CHR17", 16),
                            rep("CHR18", 16),
                            rep("CHR19", 16),
                            rep("CHR20", 16),
                            rep("CHR21", 16),
                            rep("CHR22", 16))

all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("Signal", "OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_ba <- all_rfperfs %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(Performance = mean(V1, na.rm = TRUE),
                   PerformanceSD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_ba, aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
  geom_line(size=2, position=position_dodge(0.5))+
  geom_point(size=5, position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=1,
                position=position_dodge(0.5)) +
  facet_grid(. ~ Predictor)+
  theme_minimal() +
  theme_bw()+
  xlab("Resolution") + 
  ylab("Balanced Accuracy") + #ylim(-.1,.5) +
  scale_color_discrete(name="Resampling Technique")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  strip.text.x = element_text(size = 15),
  strip.text.y = element_text(size = 15),
  #panel.spacing = unit(2, "lines"),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20),
  legend.position="bottom")

```

### K562

####5kb

```{r}
badata_k562_5kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF.rds"))
      perfdata <- perfdata[[3]]

      badata_k562_5kb <- rbind(badata_k562_5kb,
                               perfdata[10,2])
    }
  }
}

```

####10kb

```{r}
badata_k562_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF.rds"))
      perfdata <- perfdata[[3]]

      badata_k562_10kb <- rbind(badata_k562_10kb,
                                perfdata[10,2])
    }
  }
}

```

####25kb

```{r}
badata_k562_25kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF.rds"))
      perfdata <- perfdata[[3]]

      badata_k562_25kb <- rbind(badata_k562_25kb,
                                perfdata[10,2])
    }
  }
}

```

####50kb

```{r}
badata_k562_50kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF.rds"))
      perfdata <- perfdata[[3]]

      badata_k562_50kb <- rbind(badata_k562_50kb,
                                perfdata[10,2])
    }
  }
}

```

####100kb

```{r}
badata_k562_100kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF.rds"))
      perfdata <- perfdata[[3]]

      badata_k562_100kb <- rbind(badata_k562_100kb,
                                 perfdata[10,2])
    }
  }
}

```

#### Plotting

```{r}
all_rfperfs <- rbind.data.frame(badata_k562_5kb,
                                badata_k562_10kb,
                                badata_k562_25kb,
                                badata_k562_50kb,
                                badata_k562_100kb)
all_rfperfs$CL <- c(rep("K562", length(badata_k562_5kb)*5))
all_rfperfs$Resolution <- c(rep("5 kb", length(badata_k562_5kb)),
                            rep("10 kb", length(badata_k562_10kb)),
                            rep("25 kb", length(badata_k562_25kb)),
                            rep("50 kb", length(badata_k562_50kb)),
                            rep("100 kb", length(badata_k562_100kb)))
all_rfperfs$Resampling <- c(rep("None", 4),
                            rep("ROS", 4),
                            rep("RUS", 4),
                            rep("SMOTE", 4))
all_rfperfs$Predictor <- c("Distance", "OC", "OP", "Signal")
all_rfperfs$Chromosome <- c(rep("CHR1", 16),
                            rep("CHR2", 16),
                            rep("CHR3", 16),
                            rep("CHR4", 16),
                            rep("CHR5", 16),
                            rep("CHR6", 16),
                            rep("CHR7", 16),
                            rep("CHR8", 16),
                            rep("CHR10", 16),
                            rep("CHR11", 16),
                            rep("CHR12", 16),
                            rep("CHR13", 16),
                            rep("CHR14", 16),
                            rep("CHR15", 16),
                            rep("CHR16", 16),
                            rep("CHR17", 16),
                            rep("CHR18", 16),
                            rep("CHR19", 16),
                            rep("CHR20", 16),
                            rep("CHR21", 16),
                            rep("CHR22", 16))

all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("Signal", "OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_ba <- all_rfperfs %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(Performance = mean(V1, na.rm = TRUE),
                   PerformanceSD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_ba, aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
  geom_line(size=2, position=position_dodge(0.5))+
  geom_point(size=5, position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=1,
                position=position_dodge(0.5)) +
  facet_grid(. ~ Predictor)+
  theme_minimal() +
  theme_bw()+
  xlab("Resolution") + 
  ylab("Balanced Accuracy") + #ylim(-.1,.5) +
  scale_color_discrete(name="Resampling Technique")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  strip.text.x = element_text(size = 15),
  strip.text.y = element_text(size = 15),
  #panel.spacing = unit(2, "lines"),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20),
  legend.position="bottom")

```

## SpectralTAD

### GM12878

####5kb

```{r}
badata_gm12878_5kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_spectralTAD.rds"))
      perfdata <- perfdata[[3]]

      badata_gm12878_5kb <- rbind(badata_gm12878_5kb,
                                   perfdata[10,2])
    }
  }
}
```

####10kb

```{r}
badata_gm12878_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_spectralTAD.rds"))
      perfdata <- perfdata[[3]]

      badata_gm12878_10kb <- rbind(badata_gm12878_10kb,
                                   perfdata[10,2])
    }
  }
}

```

####25kb

```{r}
badata_gm12878_25kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_spectralTAD.rds"))
      perfdata <- perfdata[[3]]

      badata_gm12878_25kb <- rbind(badata_gm12878_25kb,
                                   perfdata[10,2])
    }
  }
}

```

####50kb

```{r}
badata_gm12878_50kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_spectralTAD.rds"))
      perfdata <- perfdata[[3]]

      badata_gm12878_50kb <- rbind(badata_gm12878_50kb,
                                   perfdata[10,2])
    }
  }
}

```

####100kb

```{r}
badata_gm12878_100kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_spectralTAD.rds"))
      perfdata <- perfdata[[3]]

      badata_gm12878_100kb <- rbind(badata_gm12878_100kb,
                                    perfdata[10,2])
    }
  }
}

```

#### Plotting

```{r}
all_rfperfs <- rbind.data.frame(badata_gm12878_5kb,
                                badata_gm12878_10kb,
                                badata_gm12878_25kb,
                                badata_gm12878_50kb,
                                badata_gm12878_100kb)
all_rfperfs$CL <- c(rep("GM12878", length(badata_gm12878_5kb)*5))
all_rfperfs$Resolution <- c(rep("5 kb", length(badata_gm12878_5kb)),
                            rep("10 kb", length(badata_gm12878_10kb)),
                            rep("25 kb", length(badata_gm12878_25kb)),
                            rep("50 kb", length(badata_gm12878_50kb)),
                            rep("100 kb", length(badata_gm12878_100kb)))
all_rfperfs$Resampling <- c(rep("None", 4),
                            rep("ROS", 4),
                            rep("RUS", 4),
                            rep("SMOTE", 4))
all_rfperfs$Predictor <- c("Distance", "OC", "OP", "Signal")
all_rfperfs$Chromosome <- c(rep("CHR1", 16),
                            rep("CHR2", 16),
                            rep("CHR3", 16),
                            rep("CHR4", 16),
                            rep("CHR5", 16),
                            rep("CHR6", 16),
                            rep("CHR7", 16),
                            rep("CHR8", 16),
                            rep("CHR10", 16),
                            rep("CHR11", 16),
                            rep("CHR12", 16),
                            rep("CHR13", 16),
                            rep("CHR14", 16),
                            rep("CHR15", 16),
                            rep("CHR16", 16),
                            rep("CHR17", 16),
                            rep("CHR18", 16),
                            rep("CHR19", 16),
                            rep("CHR20", 16),
                            rep("CHR21", 16),
                            rep("CHR22", 16))

all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("Signal", "OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_ba <- all_rfperfs %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(Performance = mean(V1, na.rm = TRUE),
                   PerformanceSD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_ba, aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
  geom_line(size=2, position=position_dodge(0.5))+
  geom_point(size=5, position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=1,
                position=position_dodge(0.5)) +
  facet_grid(. ~ Predictor)+
  theme_minimal() +
  theme_bw()+
  xlab("Resolution") + 
  ylab("Balanced Accuracy") + #ylim(-.1,.5) +
  scale_color_discrete(name="Resampling Technique")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  strip.text.x = element_text(size = 15),
  strip.text.y = element_text(size = 15),
  #panel.spacing = unit(2, "lines"),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20),
  legend.position="bottom")

```

### K562

####5kb

```{r}
badata_k562_5kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_spectralTAD.rds"))
      perfdata <- perfdata[[3]]

      badata_k562_5kb <- rbind(badata_k562_5kb,
                               perfdata[10,2])
    }
  }
}

```

####10kb

```{r}
badata_k562_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_spectralTAD.rds"))
      perfdata <- perfdata[[3]]

      badata_k562_10kb <- rbind(badata_k562_10kb,
                                perfdata[10,2])
    }
  }
}

```

####25kb

```{r}
badata_k562_25kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_spectralTAD.rds"))
      perfdata <- perfdata[[3]]

      badata_k562_25kb <- rbind(badata_k562_25kb,
                                perfdata[10,2])
    }
  }
}

```

####50kb

```{r}
badata_k562_50kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_spectralTAD.rds"))
      perfdata <- perfdata[[3]]

      badata_k562_50kb <- rbind(badata_k562_50kb,
                                perfdata[10,2])
    }
  }
}

```

####100kb

```{r}
badata_k562_100kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_spectralTAD.rds"))
      perfdata <- perfdata[[3]]

      badata_k562_100kb <- rbind(badata_k562_100kb,
                                 perfdata[10,2])
    }
  }
}

```

#### Plotting

```{r}
all_rfperfs <- rbind.data.frame(badata_k562_5kb,
                                badata_k562_10kb,
                                badata_k562_25kb,
                                badata_k562_50kb,
                                badata_k562_100kb)
all_rfperfs$CL <- c(rep("K562", length(badata_k562_5kb)*5))
all_rfperfs$Resolution <- c(rep("5 kb", length(badata_k562_5kb)),
                            rep("10 kb", length(badata_k562_10kb)),
                            rep("25 kb", length(badata_k562_25kb)),
                            rep("50 kb", length(badata_k562_50kb)),
                            rep("100 kb", length(badata_k562_100kb)))
all_rfperfs$Resampling <- c(rep("None", 4),
                            rep("ROS", 4),
                            rep("RUS", 4),
                            rep("SMOTE", 4))
all_rfperfs$Predictor <- c("Distance", "OC", "OP", "Signal")
all_rfperfs$Chromosome <- c(rep("CHR1", 16),
                            rep("CHR2", 16),
                            rep("CHR3", 16),
                            rep("CHR4", 16),
                            rep("CHR5", 16),
                            rep("CHR6", 16),
                            rep("CHR7", 16),
                            rep("CHR8", 16),
                            rep("CHR10", 16),
                            rep("CHR11", 16),
                            rep("CHR12", 16),
                            rep("CHR13", 16),
                            rep("CHR14", 16),
                            rep("CHR15", 16),
                            rep("CHR16", 16),
                            rep("CHR17", 16),
                            rep("CHR18", 16),
                            rep("CHR19", 16),
                            rep("CHR20", 16),
                            rep("CHR21", 16),
                            rep("CHR22", 16))

all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("Signal", "OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_ba <- all_rfperfs %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(Performance = mean(V1, na.rm = TRUE),
                   PerformanceSD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_ba, aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
  geom_line(size=2, position=position_dodge(0.5))+
  geom_point(size=5, position=position_dodge(0.5))+
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=1,
                position=position_dodge(0.5)) +
  facet_grid(. ~ Predictor)+
  theme_minimal() +
  theme_bw()+
  xlab("Resolution") + 
  ylab("Balanced Accuracy") + #ylim(-.1,.5) +
  scale_color_discrete(name="Resampling Technique")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  strip.text.x = element_text(size = 15),
  strip.text.y = element_text(size = 15),
  #panel.spacing = unit(2, "lines"),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20),
  legend.position="bottom")

```

## PEAKACHU

### GM12878

#### 10kb

```{r}
badata_gm12878_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_peakachu.rds"))
      perfdata <- perfdata[[3]]

      badata_gm12878_10kb <- rbind(badata_gm12878_10kb,
                                   perfdata[10,2])
    }
  }
}

```

#### Plotting

```{r}
all_rfperfs <- rbind.data.frame(badata_gm12878_10kb)
all_rfperfs$CL <- rep("GM12878", length(badata_gm12878_5kb))
all_rfperfs$Resolution <- rep("10 kb", length(badata_gm12878_10kb))
all_rfperfs$Resampling <- c(rep("None", 4),
                            rep("ROS", 4),
                            rep("RUS", 4),
                            rep("SMOTE", 4))
all_rfperfs$Predictor <- c("Distance", "OC", "OP", "Signal")
all_rfperfs$Chromosome <- c(rep("CHR1", 16),
                            rep("CHR2", 16),
                            rep("CHR3", 16),
                            rep("CHR4", 16),
                            rep("CHR5", 16),
                            rep("CHR6", 16),
                            rep("CHR7", 16),
                            rep("CHR8", 16),
                            rep("CHR10", 16),
                            rep("CHR11", 16),
                            rep("CHR12", 16),
                            rep("CHR13", 16),
                            rep("CHR14", 16),
                            rep("CHR15", 16),
                            rep("CHR16", 16),
                            rep("CHR17", 16),
                            rep("CHR18", 16),
                            rep("CHR19", 16),
                            rep("CHR20", 16),
                            rep("CHR21", 16),
                            rep("CHR22", 16))

all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("Signal", "OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_ba <- all_rfperfs %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(Performance = mean(V1, na.rm = TRUE),
                   PerformanceSD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_ba, aes(x=Predictor, y=Performance, fill=Resampling)) +
  geom_bar(stat = "identity", position_dodge(0.9))+
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=1,
                position=position_dodge(0.9)) +
  facet_grid(. ~ Predictor)+
  theme_minimal() +
  theme_bw()+
  xlab("Predictor Type") + 
  ylab("Balanced Accuracy") + #ylim(-.1,.5) +
  scale_color_discrete(name="Resampling Technique")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  strip.text.x = element_text(size = 15),
  strip.text.y = element_text(size = 15),
  #panel.spacing = unit(2, "lines"),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20),
  legend.position="bottom")
```

### K562

#### 10kb

```{r}
badata_k562_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_peakachu.rds"))
      perfdata <- perfdata[[3]]

      badata_k562_10kb <- rbind(badata_k562_10kb,
                                   perfdata[10,2])
    }
  }
}

```

#### Plotting

```{r}
all_rfperfs <- rbind.data.frame(badata_k562_10kb)
all_rfperfs$CL <- rep("K562", length(badata_k562_5kb))
all_rfperfs$Resolution <- rep("10 kb", length(badata_k562_10kb))
all_rfperfs$Resampling <- c(rep("None", 4),
                            rep("ROS", 4),
                            rep("RUS", 4),
                            rep("SMOTE", 4))
all_rfperfs$Predictor <- c("Distance", "OC", "OP", "Signal")
all_rfperfs$Chromosome <- c(rep("CHR1", 16),
                            rep("CHR2", 16),
                            rep("CHR3", 16),
                            rep("CHR4", 16),
                            rep("CHR5", 16),
                            rep("CHR6", 16),
                            rep("CHR7", 16),
                            rep("CHR8", 16),
                            rep("CHR10", 16),
                            rep("CHR11", 16),
                            rep("CHR12", 16),
                            rep("CHR13", 16),
                            rep("CHR14", 16),
                            rep("CHR15", 16),
                            rep("CHR16", 16),
                            rep("CHR17", 16),
                            rep("CHR18", 16),
                            rep("CHR19", 16),
                            rep("CHR20", 16),
                            rep("CHR21", 16),
                            rep("CHR22", 16))

all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("Signal", "OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_ba <- all_rfperfs %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(Performance = mean(V1, na.rm = TRUE),
                   PerformanceSD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_ba, aes(x=Predictor, y=Performance, fill=Resampling)) +
  geom_bar(stat = "identity", position_dodge(0.9))+
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=1,
                position=position_dodge(0.9)) +
  facet_grid(. ~ Predictor)+
  theme_minimal() +
  theme_bw()+
  xlab("Predictor Type") + 
  ylab("Balanced Accuracy") + #ylim(-.1,.5) +
  scale_color_discrete(name="Resampling Technique")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  strip.text.x = element_text(size = 15),
  strip.text.y = element_text(size = 15),
  #panel.spacing = unit(2, "lines"),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20),
  legend.position="bottom")
```

## LOLLIPOP

### GM12878

#### 10kb

```{r}
badata_gm12878_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_lollipop.rds"))
      perfdata <- perfdata[[3]]

      badata_gm12878_10kb <- rbind(badata_gm12878_10kb,
                                   perfdata[10,2])
    }
  }
}

```

#### Plotting

```{r}
all_rfperfs <- rbind.data.frame(badata_gm12878_10kb)
all_rfperfs$CL <- rep("GM12878", length(badata_gm12878_5kb))
all_rfperfs$Resolution <- rep("10 kb", length(badata_gm12878_10kb))
all_rfperfs$Resampling <- c(rep("None", 4),
                            rep("ROS", 4),
                            rep("RUS", 4),
                            rep("SMOTE", 4))
all_rfperfs$Predictor <- c("Distance", "OC", "OP", "Signal")
all_rfperfs$Chromosome <- c(rep("CHR1", 16),
                            rep("CHR2", 16),
                            rep("CHR3", 16),
                            rep("CHR4", 16),
                            rep("CHR5", 16),
                            rep("CHR6", 16),
                            rep("CHR7", 16),
                            rep("CHR8", 16),
                            rep("CHR10", 16),
                            rep("CHR11", 16),
                            rep("CHR12", 16),
                            rep("CHR13", 16),
                            rep("CHR14", 16),
                            rep("CHR15", 16),
                            rep("CHR16", 16),
                            rep("CHR17", 16),
                            rep("CHR18", 16),
                            rep("CHR19", 16),
                            rep("CHR20", 16),
                            rep("CHR21", 16),
                            rep("CHR22", 16))

all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("Signal", "OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_ba <- all_rfperfs %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(Performance = mean(V1, na.rm = TRUE),
                   PerformanceSD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_ba, aes(x=Predictor, y=Performance, fill=Resampling)) +
  geom_bar(stat = "identity", position_dodge(0.9))+
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=1,
                position=position_dodge(0.9)) +
  facet_grid(. ~ Predictor)+
  theme_minimal() +
  theme_bw()+
  xlab("Predictor Type") + 
  ylab("Balanced Accuracy") + #ylim(-.1,.5) +
  scale_color_discrete(name="Resampling Technique")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  strip.text.x = element_text(size = 15),
  strip.text.y = element_text(size = 15),
  #panel.spacing = unit(2, "lines"),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20),
  legend.position="bottom")
```

### K562

#### 10kb

```{r}
badata_k562_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
  for(j in c("none","ros","rus","smote")){
    for(k in c("distance", "oc", "op", "signal")){
      print(c(i,j,k))
      files <- list.files(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/"))

      perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                 i, 
                                 "/",
                                 j, 
                                 "/", 
                                 k, 
                                 "/TADRF_lollipop.rds"))
      perfdata <- perfdata[[3]]

      badata_k562_10kb <- rbind(badata_k562_10kb,
                                   perfdata[10,2])
    }
  }
}

```

#### Plotting

```{r}
all_rfperfs <- rbind.data.frame(badata_k562_10kb)
all_rfperfs$CL <- rep("K562", length(badata_k562_5kb))
all_rfperfs$Resolution <- rep("10 kb", length(badata_k562_10kb))
all_rfperfs$Resampling <- c(rep("None", 4),
                            rep("ROS", 4),
                            rep("RUS", 4),
                            rep("SMOTE", 4))
all_rfperfs$Predictor <- c("Distance", "OC", "OP", "Signal")
all_rfperfs$Chromosome <- c(rep("CHR1", 16),
                            rep("CHR2", 16),
                            rep("CHR3", 16),
                            rep("CHR4", 16),
                            rep("CHR5", 16),
                            rep("CHR6", 16),
                            rep("CHR7", 16),
                            rep("CHR8", 16),
                            rep("CHR10", 16),
                            rep("CHR11", 16),
                            rep("CHR12", 16),
                            rep("CHR13", 16),
                            rep("CHR14", 16),
                            rep("CHR15", 16),
                            rep("CHR16", 16),
                            rep("CHR17", 16),
                            rep("CHR18", 16),
                            rep("CHR19", 16),
                            rep("CHR20", 16),
                            rep("CHR21", 16),
                            rep("CHR22", 16))

all_rfperfs$Resolution <- factor(all_rfperfs$Resolution, levels = c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
all_rfperfs$Resampling <- factor(all_rfperfs$Resampling, levels = c("None", "ROS", "RUS", "SMOTE"))
all_rfperfs$Predictor <- factor(all_rfperfs$Predictor, levels = c("Signal", "OC", "OP", "Distance"))
all_rfperfs$Chromosome <- factor(all_rfperfs$Chromosome, levels = paste0("CHR", c(1:8,10:22)))

all_rfperfs_ba <- all_rfperfs %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(Performance = mean(V1, na.rm = TRUE),
                   PerformanceSD = sd(V1, na.rm = TRUE))

ggplot(all_rfperfs_ba, aes(x=Predictor, y=Performance, fill=Resampling)) +
  geom_bar(stat = "identity", position_dodge(0.9))+
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=1,
                position=position_dodge(0.9)) +
  facet_grid(. ~ Predictor)+
  theme_minimal() +
  theme_bw()+
  xlab("Predictor Type") + 
  ylab("Balanced Accuracy") + #ylim(-.1,.5) +
  scale_color_discrete(name="Resampling Technique")+
  guides(shape=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  strip.text.x = element_text(size = 15),
  strip.text.y = element_text(size = 15),
  #panel.spacing = unit(2, "lines"),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20),
  legend.position="bottom")
```

### 2020-04-29 Scripts_for_results/03_creating_annotation_specifc_barplots.Rmd
initial commit

---
title: "Creating annotation specific barplots"
author: "Spiro Stilianoudakis"
date: "4/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages and functions

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

## ARROWHEAD

### GM12878 (rus; distance types)

#### 5kb

```{r}
badata_gm12878_5kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF.rds"))
    perfdata <- perfdata[[3]]
  }

  badata_gm12878_5kb <- rbind(badata_gm12878_5kb,
                               perfdata[10,2])

 }
}

```

#### Plotting

```{r}
all_rfperfs <- data.frame(Perf=badata_gm12878_5kb)
all_rfperfs$Resolution <- rep("5 kb", length(badata_gm12878_5kb))
all_rfperfs$Annotation <- c("BroadHMM","HM","TFBS","ALL")
all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "BroadHMM", "TFBS", "ALL"))
all_rfperfs$Chromosome <- c(rep("CHR1", 4),
                            rep("CHR2", 4),
                            rep("CHR3", 4),
                            rep("CHR4", 4),
                            rep("CHR5", 4),
                            rep("CHR6", 4),
                            rep("CHR7", 4),
                            rep("CHR8", 4),
                            rep("CHR10", 4),
                            rep("CHR11", 4),
                            rep("CHR12", 4),
                            rep("CHR13", 4),
                            rep("CHR14", 4),
                            rep("CHR15", 4),
                            rep("CHR16", 4),
                            rep("CHR17", 4),
                            rep("CHR18", 4),
                            rep("CHR19", 4),
                            rep("CHR20", 4),
                            rep("CHR21", 4),
                            rep("CHR22", 4))

all_rfperfs <- all_rfperfs %>% 
  group_by(Resolution, Annotation) %>% 
  dplyr::summarise(Performance = mean(Perf, na.rm = TRUE),
                   PerformanceSD = sd(Perf, na.rm = TRUE))

ggplot(all_rfperfs, aes(x=Annotation, y=Performance, fill=Annotation)) +
    geom_bar(stat="identity") +
    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=.75) +
    theme_minimal() +
    theme_bw()+
    xlab("Resolution") + 
    ylab("Balanced Accuracy") + 
    scale_fill_discrete(name="Genomic Class")+
    theme(axis.text.x = element_text(size=15,
                                     angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    legend.position = "bottom",
    plot.title = element_text(size=20))
```

### K562 (rus; distance types)

#### 5kb

```{r}
badata_k562_5kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF.rds"))
    perfdata <- perfdata[[3]]
  }

  badata_k562_5kb <- rbind(badata_k562_5kb,
                               perfdata[10,2])

 }
}

```

#### Plotting

```{r}
all_rfperfs <- data.frame(Perf=badata_k562_5kb)
all_rfperfs$Resolution <- rep("5 kb", length(badata_k562_5kb))
all_rfperfs$Annotation <- c("BroadHMM","HM","TFBS","ALL")
all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "BroadHMM", "TFBS", "ALL"))
all_rfperfs$Chromosome <- c(rep("CHR1", 4),
                            rep("CHR2", 4),
                            rep("CHR3", 4),
                            rep("CHR4", 4),
                            rep("CHR5", 4),
                            rep("CHR6", 4),
                            rep("CHR7", 4),
                            rep("CHR8", 4),
                            rep("CHR10", 4),
                            rep("CHR11", 4),
                            rep("CHR12", 4),
                            rep("CHR13", 4),
                            rep("CHR14", 4),
                            rep("CHR15", 4),
                            rep("CHR16", 4),
                            rep("CHR17", 4),
                            rep("CHR18", 4),
                            rep("CHR19", 4),
                            rep("CHR20", 4),
                            rep("CHR21", 4),
                            rep("CHR22", 4))

all_rfperfs <- all_rfperfs %>% 
  group_by(Resolution, Annotation) %>% 
  dplyr::summarise(Performance = mean(Perf, na.rm = TRUE),
                   PerformanceSD = sd(Perf, na.rm = TRUE))

ggplot(all_rfperfs, aes(x=Annotation, y=Performance, fill=Annotation)) +
    geom_bar(stat="identity") +
    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=.75) +
    theme_minimal() +
    theme_bw()+
    xlab("Resolution") + 
    ylab("Balanced Accuracy") + 
    scale_fill_discrete(name="Genomic Class")+
    theme(axis.text.x = element_text(size=15,
                                     angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    legend.position = "bottom",
    plot.title = element_text(size=20))
```

## PEAKACHU

### GM12878 (rus; distance types)

#### 10kb

```{r}
badata_gm12878_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_peakachu_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_peakachu.rds"))
    perfdata <- perfdata[[3]]
  }

  badata_gm12878_10kb <- rbind(badata_gm12878_10kb,
                               perfdata[10,2])

 }
}

```

#### Plotting

```{r}
all_rfperfs <- data.frame(Perf=badata_gm12878_10kb)
all_rfperfs$Resolution <- rep("10 kb", length(badata_gm12878_10kb))
all_rfperfs$Annotation <- c("BroadHMM","HM","TFBS","ALL")
all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "BroadHMM", "TFBS", "ALL"))
all_rfperfs$Chromosome <- c(rep("CHR1", 4),
                            rep("CHR2", 4),
                            rep("CHR3", 4),
                            rep("CHR4", 4),
                            rep("CHR5", 4),
                            rep("CHR6", 4),
                            rep("CHR7", 4),
                            rep("CHR8", 4),
                            rep("CHR10", 4),
                            rep("CHR11", 4),
                            rep("CHR12", 4),
                            rep("CHR13", 4),
                            rep("CHR14", 4),
                            rep("CHR15", 4),
                            rep("CHR16", 4),
                            rep("CHR17", 4),
                            rep("CHR18", 4),
                            rep("CHR19", 4),
                            rep("CHR20", 4),
                            rep("CHR21", 4),
                            rep("CHR22", 4))

all_rfperfs <- all_rfperfs %>% 
  group_by(Resolution, Annotation) %>% 
  dplyr::summarise(Performance = mean(Perf, na.rm = TRUE),
                   PerformanceSD = sd(Perf, na.rm = TRUE))

ggplot(all_rfperfs, aes(x=Annotation, y=Performance, fill=Annotation)) +
    geom_bar(stat="identity") +
    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=.75) +
    theme_minimal() +
    theme_bw()+
    xlab("Resolution") + 
    ylab("Balanced Accuracy") + 
    scale_fill_discrete(name="Genomic Class")+
    theme(axis.text.x = element_text(size=15,
                                     angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    legend.position = "bottom",
    plot.title = element_text(size=20))
```

### K562 (rus; distance types)

#### 10kb

```{r}
badata_k562_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_peakachu_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_peakachu.rds"))
    perfdata <- perfdata[[3]]
  }

  badata_k562_10kb <- rbind(badata_k562_10kb,
                               perfdata[10,2])

 }
}

```

#### Plotting

```{r}
all_rfperfs <- data.frame(Perf=badata_k562_10kb)
all_rfperfs$Resolution <- rep("10 kb", length(badata_k562_10kb))
all_rfperfs$Annotation <- c("BroadHMM","HM","TFBS","ALL")
all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "BroadHMM", "TFBS", "ALL"))
all_rfperfs$Chromosome <- c(rep("CHR1", 4),
                            rep("CHR2", 4),
                            rep("CHR3", 4),
                            rep("CHR4", 4),
                            rep("CHR5", 4),
                            rep("CHR6", 4),
                            rep("CHR7", 4),
                            rep("CHR8", 4),
                            rep("CHR10", 4),
                            rep("CHR11", 4),
                            rep("CHR12", 4),
                            rep("CHR13", 4),
                            rep("CHR14", 4),
                            rep("CHR15", 4),
                            rep("CHR16", 4),
                            rep("CHR17", 4),
                            rep("CHR18", 4),
                            rep("CHR19", 4),
                            rep("CHR20", 4),
                            rep("CHR21", 4),
                            rep("CHR22", 4))

all_rfperfs <- all_rfperfs %>% 
  group_by(Resolution, Annotation) %>% 
  dplyr::summarise(Performance = mean(Perf, na.rm = TRUE),
                   PerformanceSD = sd(Perf, na.rm = TRUE))

ggplot(all_rfperfs, aes(x=Annotation, y=Performance, fill=Annotation)) +
    geom_bar(stat="identity") +
    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=.75) +
    theme_minimal() +
    theme_bw()+
    xlab("Resolution") + 
    ylab("Balanced Accuracy") + 
    scale_fill_discrete(name="Genomic Class")+
    theme(axis.text.x = element_text(size=15,
                                     angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    legend.position = "bottom",
    plot.title = element_text(size=20))
```

## LOLLIPOP

### GM12878 (rus; distance types)

#### 10kb

```{r}
badata_gm12878_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_lollipop_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_lollipop.rds"))
    perfdata <- perfdata[[3]]
  }

  badata_gm12878_10kb <- rbind(badata_gm12878_10kb,
                               perfdata[10,2])

 }
}

```

#### Plotting

```{r}
all_rfperfs <- data.frame(Perf=badata_gm12878_10kb)
all_rfperfs$Resolution <- rep("10 kb", length(badata_gm12878_10kb))
all_rfperfs$Annotation <- c("BroadHMM","HM","TFBS","ALL")
all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "BroadHMM", "TFBS", "ALL"))
all_rfperfs$Chromosome <- c(rep("CHR1", 4),
                            rep("CHR2", 4),
                            rep("CHR3", 4),
                            rep("CHR4", 4),
                            rep("CHR5", 4),
                            rep("CHR6", 4),
                            rep("CHR7", 4),
                            rep("CHR8", 4),
                            rep("CHR10", 4),
                            rep("CHR11", 4),
                            rep("CHR12", 4),
                            rep("CHR13", 4),
                            rep("CHR14", 4),
                            rep("CHR15", 4),
                            rep("CHR16", 4),
                            rep("CHR17", 4),
                            rep("CHR18", 4),
                            rep("CHR19", 4),
                            rep("CHR20", 4),
                            rep("CHR21", 4),
                            rep("CHR22", 4))

all_rfperfs <- all_rfperfs %>% 
  group_by(Resolution, Annotation) %>% 
  dplyr::summarise(Performance = mean(Perf, na.rm = TRUE),
                   PerformanceSD = sd(Perf, na.rm = TRUE))

ggplot(all_rfperfs, aes(x=Annotation, y=Performance, fill=Annotation)) +
    geom_bar(stat="identity") +
    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=.75) +
    theme_minimal() +
    theme_bw()+
    xlab("Resolution") + 
    ylab("Balanced Accuracy") + 
    scale_fill_discrete(name="Genomic Class")+
    theme(axis.text.x = element_text(size=15,
                                     angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    legend.position = "bottom",
    plot.title = element_text(size=20))
```

### K562 (rus; distance types)

#### 10kb

```{r}
badata_k562_10kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_lollipop_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_lollipop.rds"))
    perfdata <- perfdata[[3]]
  }

  badata_k562_10kb <- rbind(badata_k562_10kb,
                               perfdata[10,2])

 }
}

```

#### Plotting

```{r}
all_rfperfs <- data.frame(Perf=badata_k562_10kb)
all_rfperfs$Resolution <- rep("10 kb", length(badata_k562_10kb))
all_rfperfs$Annotation <- c("BroadHMM","HM","TFBS","ALL")
all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "BroadHMM", "TFBS", "ALL"))
all_rfperfs$Chromosome <- c(rep("CHR1", 4),
                            rep("CHR2", 4),
                            rep("CHR3", 4),
                            rep("CHR4", 4),
                            rep("CHR5", 4),
                            rep("CHR6", 4),
                            rep("CHR7", 4),
                            rep("CHR8", 4),
                            rep("CHR10", 4),
                            rep("CHR11", 4),
                            rep("CHR12", 4),
                            rep("CHR13", 4),
                            rep("CHR14", 4),
                            rep("CHR15", 4),
                            rep("CHR16", 4),
                            rep("CHR17", 4),
                            rep("CHR18", 4),
                            rep("CHR19", 4),
                            rep("CHR20", 4),
                            rep("CHR21", 4),
                            rep("CHR22", 4))

all_rfperfs <- all_rfperfs %>% 
  group_by(Resolution, Annotation) %>% 
  dplyr::summarise(Performance = mean(Perf, na.rm = TRUE),
                   PerformanceSD = sd(Perf, na.rm = TRUE))

ggplot(all_rfperfs, aes(x=Annotation, y=Performance, fill=Annotation)) +
    geom_bar(stat="identity") +
    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=.75) +
    theme_minimal() +
    theme_bw()+
    xlab("Resolution") + 
    ylab("Balanced Accuracy") + 
    scale_fill_discrete(name="Genomic Class")+
    theme(axis.text.x = element_text(size=15,
                                     angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    legend.position = "bottom",
    plot.title = element_text(size=20))
```

### 2020-04-29 Scripts_for_results/04_creating_rfe_lineplot.Rmd
initial commit

---
title: "Creating RFE line plot"
author: "Spiro Stilianoudakis"
date: "4/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages and functions

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

## ARROWHEAD

### GM12878

#### Optimal parameters: 5 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

rfeperchr_summ <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
                   PerformanceSD = sd(Accuracy, na.rm = TRUE))

ggplot(rfeperchr_summ, aes(x=Variables, y=Performance)) + 
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), 
                width=2, 
                size=1, 
                color="red") +
  geom_line(size=2, color="red") +
  geom_point(size=4, color="red") +
  xlab("Number of top ranked annotations") +
  ylab("Cross-Validated Accuracy") +
  scale_color_discrete(name="Cell line")+
  scale_x_continuous(breaks = c(2,4,8,16,32,52),
                     labels = c(2,4,8,16,32,52))+
  theme_minimal() +
  theme_bw()+
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")
```

### K562

#### Optimal parameters: 5 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("K562")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

rfeperchr_summ <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
                   PerformanceSD = sd(Accuracy, na.rm = TRUE))

ggplot(rfeperchr_summ, aes(x=Variables, y=Performance)) + 
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), 
                width=2, 
                size=1, 
                color="red") +
  geom_line(size=2, color="red") +
  geom_point(size=4, color="red") +
  xlab("Number of top ranked annotations") +
  ylab("Cross-Validated Accuracy") +
  scale_color_discrete(name="Cell line")+
  scale_x_continuous(breaks = c(2,4,8,16,32,52),
                     labels = c(2,4,8,16,32,52))+
  theme_minimal() +
  theme_bw()+
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")
```

## PEAKACHU

### GM12878

#### Optimal parameters: 10 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_peakachu.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

rfeperchr_summ <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
                   PerformanceSD = sd(Accuracy, na.rm = TRUE))

ggplot(rfeperchr_summ, aes(x=Variables, y=Performance)) + 
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), 
                width=2, 
                size=1, 
                color="red") +
  geom_line(size=2, color="red") +
  geom_point(size=4, color="red") +
  xlab("Number of top ranked annotations") +
  ylab("Cross-Validated Accuracy") +
  scale_color_discrete(name="Cell line")+
  scale_x_continuous(breaks = c(2,4,8,16,32,52),
                     labels = c(2,4,8,16,32,52))+
  theme_minimal() +
  theme_bw()+
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")
```

### K562

#### Optimal parameters: 10 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("K562")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_peakachu.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

rfeperchr_summ <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
                   PerformanceSD = sd(Accuracy, na.rm = TRUE))

ggplot(rfeperchr_summ, aes(x=Variables, y=Performance)) + 
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), 
                width=2, 
                size=1, 
                color="red") +
  geom_line(size=2, color="red") +
  geom_point(size=4, color="red") +
  xlab("Number of top ranked annotations") +
  ylab("Cross-Validated Accuracy") +
  scale_color_discrete(name="Cell line")+
  scale_x_continuous(breaks = c(2,4,8,16,32,52),
                     labels = c(2,4,8,16,32,52))+
  theme_minimal() +
  theme_bw()+
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")
```

## LOLLIPOP

### GM12878

#### Optimal parameters: 10 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_lollipop.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

rfeperchr_summ <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
                   PerformanceSD = sd(Accuracy, na.rm = TRUE))

ggplot(rfeperchr_summ, aes(x=Variables, y=Performance)) + 
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), 
                width=2, 
                size=1, 
                color="red") +
  geom_line(size=2, color="red") +
  geom_point(size=4, color="red") +
  xlab("Number of top ranked annotations") +
  ylab("Cross-Validated Accuracy") +
  scale_color_discrete(name="Cell line")+
  scale_x_continuous(breaks = c(2,4,8,16,32,52),
                     labels = c(2,4,8,16,32,52))+
  theme_minimal() +
  theme_bw()+
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")
```

### K562

#### Optimal parameters: 10 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("K562")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_lollipop.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

rfeperchr_summ <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
                   PerformanceSD = sd(Accuracy, na.rm = TRUE))

ggplot(rfeperchr_summ, aes(x=Variables, y=Performance)) + 
  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), 
                width=2, 
                size=1, 
                color="red") +
  geom_line(size=2, color="red") +
  geom_point(size=4, color="red") +
  xlab("Number of top ranked annotations") +
  ylab("Cross-Validated Accuracy") +
  scale_color_discrete(name="Cell line")+
  scale_x_continuous(breaks = c(2,4,8,16,32,52),
                     labels = c(2,4,8,16,32,52))+
  theme_minimal() +
  theme_bw()+
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")
```

### 2020-04-29 Scripts_for_results/05_creating_importance_plot.Rmd
initial commit

---
title: "Creating importance plot"
author: "Spiro Stilianoudakis"
date: "4/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages and functions

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)
library(gplots)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

## ARROWHEAD

### GM12878

#### Optimal parameters: 5 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe.rds"))

    set.size = 8
    rfeModelResults <- rfeModelResultsList[[2]]
    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
    rfe.set <- rfe.set[rfe.order, ]
    rfe.set$CHR <- chrs[k]
    rfeperchr[[k]] <- rfe.set
  }
}

rfeperchr <- do.call(rbind.data.frame, rfeperchr)
rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
names(rfeperchr) <- c("TFBS", chrs)
rfeperchr[is.na(rfeperchr)] <- 0
rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]

rfe.set.mat <- as.matrix(rfeperchr[,-1])
rownames(rfe.set.mat) <- rfeperchr$TFBS

distance.col = dist(rfe.set.mat, method = "euclidean")
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfe.set.mat))

heatmap.2(t(rfe.set.mat),
          #labRow=rownames(rfe.set.mat),
          #labCol=colnames(rfe.set.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="column",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=.5,
          cexCol=1,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          rowsep=0:nrow(t(rfe.set.mat)),
          colsep=0:ncol(t(rfe.set.mat)),
          sepwidth=c(0.00001,0.00001),
          sepcolor="black"
)

```

### K562

#### Optimal parameters: 5 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("K562")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe.rds"))

    set.size = 8
    rfeModelResults <- rfeModelResultsList[[2]]
    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
    rfe.set <- rfe.set[rfe.order, ]
    rfe.set$CHR <- chrs[k]
    rfeperchr[[k]] <- rfe.set
  }
}

rfeperchr <- do.call(rbind.data.frame, rfeperchr)
rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
names(rfeperchr) <- c("TFBS", chrs)
rfeperchr[is.na(rfeperchr)] <- 0
rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]

rfe.set.mat <- as.matrix(rfeperchr[,-1])
rownames(rfe.set.mat) <- rfeperchr$TFBS

distance.col = dist(rfe.set.mat, method = "euclidean")
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfe.set.mat))

heatmap.2(t(rfe.set.mat),
          #labRow=rownames(rfe.set.mat),
          #labCol=colnames(rfe.set.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="column",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=.5,
          cexCol=1,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          rowsep=0:nrow(t(rfe.set.mat)),
          colsep=0:ncol(t(rfe.set.mat)),
          sepwidth=c(0.00001,0.00001),
          sepcolor="black"
)

```

## PEAKACHU

### GM12878

#### Optimal parameters: 5 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_peakachu.rds"))

    set.size = 8
    rfeModelResults <- rfeModelResultsList[[2]]
    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
    rfe.set <- rfe.set[rfe.order, ]
    rfe.set$CHR <- chrs[k]
    rfeperchr[[k]] <- rfe.set
  }
}

rfeperchr <- do.call(rbind.data.frame, rfeperchr)
rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
names(rfeperchr) <- c("TFBS", chrs)
rfeperchr[is.na(rfeperchr)] <- 0
rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]

rfe.set.mat <- as.matrix(rfeperchr[,-1])
rownames(rfe.set.mat) <- rfeperchr$TFBS

distance.col = dist(rfe.set.mat, method = "euclidean")
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfe.set.mat))

heatmap.2(t(rfe.set.mat),
          #labRow=rownames(rfe.set.mat),
          #labCol=colnames(rfe.set.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="column",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=.5,
          cexCol=1,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          rowsep=0:nrow(t(rfe.set.mat)),
          colsep=0:ncol(t(rfe.set.mat)),
          sepwidth=c(0.00001,0.00001),
          sepcolor="black"
)

```

### K562

#### Optimal parameters: 5 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("K562")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_peakachu.rds"))

    set.size = 8
    rfeModelResults <- rfeModelResultsList[[2]]
    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
    rfe.set <- rfe.set[rfe.order, ]
    rfe.set$CHR <- chrs[k]
    rfeperchr[[k]] <- rfe.set
  }
}

rfeperchr <- do.call(rbind.data.frame, rfeperchr)
rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
names(rfeperchr) <- c("TFBS", chrs)
rfeperchr[is.na(rfeperchr)] <- 0
rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]

rfe.set.mat <- as.matrix(rfeperchr[,-1])
rownames(rfe.set.mat) <- rfeperchr$TFBS

distance.col = dist(rfe.set.mat, method = "euclidean")
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfe.set.mat))

heatmap.2(t(rfe.set.mat),
          #labRow=rownames(rfe.set.mat),
          #labCol=colnames(rfe.set.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="column",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=.5,
          cexCol=1,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          rowsep=0:nrow(t(rfe.set.mat)),
          colsep=0:ncol(t(rfe.set.mat)),
          sepwidth=c(0.00001,0.00001),
          sepcolor="black"
)

```

## LOLLIPOP

### GM12878

#### Optimal parameters: 5 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_lollipop.rds"))

    set.size = 8
    rfeModelResults <- rfeModelResultsList[[2]]
    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
    rfe.set <- rfe.set[rfe.order, ]
    rfe.set$CHR <- chrs[k]
    rfeperchr[[k]] <- rfe.set
  }
}

rfeperchr <- do.call(rbind.data.frame, rfeperchr)
rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
names(rfeperchr) <- c("TFBS", chrs)
rfeperchr[is.na(rfeperchr)] <- 0
rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]

rfe.set.mat <- as.matrix(rfeperchr[,-1])
rownames(rfe.set.mat) <- rfeperchr$TFBS

distance.col = dist(rfe.set.mat, method = "euclidean")
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfe.set.mat))

heatmap.2(t(rfe.set.mat),
          #labRow=rownames(rfe.set.mat),
          #labCol=colnames(rfe.set.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="column",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=.5,
          cexCol=1,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          rowsep=0:nrow(t(rfe.set.mat)),
          colsep=0:ncol(t(rfe.set.mat)),
          sepwidth=c(0.00001,0.00001),
          sepcolor="black"
)

```

### K562

#### Optimal parameters: 5 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("K562")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "5kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_lollipop.rds"))

    set.size = 8
    rfeModelResults <- rfeModelResultsList[[2]]
    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
    rfe.set <- rfe.set[rfe.order, ]
    rfe.set$CHR <- chrs[k]
    rfeperchr[[k]] <- rfe.set
  }
}

rfeperchr <- do.call(rbind.data.frame, rfeperchr)
rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
names(rfeperchr) <- c("TFBS", chrs)
rfeperchr[is.na(rfeperchr)] <- 0
rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]

rfe.set.mat <- as.matrix(rfeperchr[,-1])
rownames(rfe.set.mat) <- rfeperchr$TFBS

distance.col = dist(rfe.set.mat, method = "euclidean")
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfe.set.mat))

heatmap.2(t(rfe.set.mat),
          #labRow=rownames(rfe.set.mat),
          #labCol=colnames(rfe.set.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="column",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=.5,
          cexCol=1,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          rowsep=0:nrow(t(rfe.set.mat)),
          colsep=0:ncol(t(rfe.set.mat)),
          sepwidth=c(0.00001,0.00001),
          sepcolor="black"
)

```

### 2020-04-29 Scripts_for_results/06_creating_enriched_heatmaps.Rmd
initial commit

---
title: "Creating enriched heatmaps"
author: "Spiro Stilianoudakis"
date: "4/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages and functions

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

## Enriched heatmap function

```{r}
enriched_func <- function(boundaries, annotations, e=5, w=50, ct){
  axis_names <- c(paste0("-",e,"kb"), "Center", paste0(e,"kb"))

  norm_mat <- normalizeToMatrix(annotations, 
                                boundaries, 
                                value_column = "coverage", 
                                extend = e*1000, 
                                w = 50,
                                mean_mode = "w0",
                                keep = c(0,.999))
  EH <- EnrichedHeatmap(norm_mat, 
                        col = ifelse(ct=="ARROWHEAD" | ct=="PEAKACHU" | ct=="LOLLIPOP", c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)),
                                     c("black",colorRampPalette(c("white", "pink", "red"))(99))), 
                        #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                        row_title="Boundaries",
                        show_heatmap_legend = FALSE,
                        row_title_side="left", 
                        column_title=ct, 
                        axis_name = axis_names,
                        column_title_gp = gpar(fontsize = 10),
                        row_title_gp = gpar(fontsize = 10),
                        axis_name_gp = gpar(fontsize = 10),
                        top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = ifelse(ct=="ARROWHEAD", "blue", "red"), 
                                                                                           fontsize = 10,
                                                                                           lwd = 2), 
                                                                                 axis_param = list(side = "right",
                                                                                                   facing = "inside"))))
  return(EH)
}

```

## ARROWHEAD

### GM12878

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

```

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```

###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```

###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```

###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

### K562

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

```

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```

###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```

###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```

###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

## PEAKACHU

### GM12878

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

```

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```

###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```

###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```

###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

### K562

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

```

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```

###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```

###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```

###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

## LOLLIPOP

### GM12878

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_lollipop.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

```

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```

###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```

###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```

###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

### K562

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_lollipop.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

```

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```

###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```

###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```

###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

### 2020-04-29 Scripts_for_results/07_creating_distance_to_chipseq.Rmd
initial commit

---
title: "Creating distance to chip-seq plots"
author: "Spiro Stilianoudakis"
date: "4/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages and functions

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

## ARROWHEAD

### GM12878

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

```

#### Plotting

```{r}
pred_v_called_df <- data.frame(LogDist = c(#preciseTAD
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1),

  #ARROWHEAD
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)
),
Annotation = c(#preciseTAD
  rep("CTCF",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("RAD21",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("SMC3",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ZNF143",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1))),

  #ARROWHEAD
  rep("CTCF",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("RAD21",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("SMC3",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ZNF143",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)))),
BoundReg = c(#preciseTAD
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1))),

  #ARROWHEAD
  rep("ARROWHEAD", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("ARROWHEAD", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("ARROWHEAD", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ARROWHEAD", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)))))

pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("preciseTAD", "ARROWHEAD"))

ggplot(pred_v_called_df, aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  + 
  facet_grid(~ Annotation) +    
  stat_boxplot(geom ='errorbar', width = 0.2) + 
  geom_boxplot(outlier.shape = NA) +
  geom_signif(test = "wilcox.test", 
              comparisons = list(c("preciseTAD","ARROWHEAD")),
              vjust = 0,
              textsize = 4,
              size = .5,
              step_increase = .08,
              color="black") +
  theme_minimal()+
  theme_bw()+
  ylab("Log2 Distance to Annotation")+
  xlab("") +
  scale_fill_manual(name="Boundary",
                    values=c("forestgreen",
                             "blue"))+
  scale_color_manual(values=c("black",
                              "black")) +
  guides(color=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

```

### K562

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

```

#### Plotting

```{r}
pred_v_called_df <- data.frame(LogDist = c(#preciseTAD
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1),

  #ARROWHEAD
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)
),
Annotation = c(#preciseTAD
  rep("CTCF",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("RAD21",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("SMC3",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ZNF143",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1))),

  #ARROWHEAD
  rep("CTCF",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("RAD21",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("SMC3",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ZNF143",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)))),
BoundReg = c(#preciseTAD
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1))),

  #ARROWHEAD
  rep("ARROWHEAD", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("ARROWHEAD", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("ARROWHEAD", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ARROWHEAD", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)))))

pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("preciseTAD", "ARROWHEAD"))

ggplot(pred_v_called_df, aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  + 
  facet_grid(~ Annotation) +    
  stat_boxplot(geom ='errorbar', width = 0.2) + 
  geom_boxplot(outlier.shape = NA) +
  geom_signif(test = "wilcox.test", 
              comparisons = list(c("preciseTAD","ARROWHEAD")),
              vjust = 0,
              textsize = 4,
              size = .5,
              step_increase = .08,
              color="black") +
  theme_minimal()+
  theme_bw()+
  ylab("Log2 Distance to Annotation")+
  xlab("") +
  scale_fill_manual(name="Boundary",
                    values=c("forestgreen",
                             "blue"))+
  scale_color_manual(values=c("black",
                              "black")) +
  guides(color=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

```

## PEAKACHU

### GM12878

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

```

#### Plotting

```{r}
pred_v_called_df <- data.frame(LogDist = c(#preciseTAD
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1),

  #PEAKACHU
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)
),
Annotation = c(#preciseTAD
  rep("CTCF",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("RAD21",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("SMC3",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ZNF143",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1))),

  #PEAKACHU
  rep("CTCF",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("RAD21",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("SMC3",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ZNF143",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)))),
BoundReg = c(#preciseTAD
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1))),

  #PEAKACHU
  rep("PEAKACHU", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("PEAKACHU", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("PEAKACHU", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("PEAKACHU", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)))))

pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("preciseTAD", "PEAKACHU"))

ggplot(pred_v_called_df, aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  + 
  facet_grid(~ Annotation) +    
  stat_boxplot(geom ='errorbar', width = 0.2) + 
  geom_boxplot(outlier.shape = NA) +
  geom_signif(test = "wilcox.test", 
              comparisons = list(c("preciseTAD","PEAKACHU")),
              vjust = 0,
              textsize = 4,
              size = .5,
              step_increase = .08,
              color="black") +
  theme_minimal()+
  theme_bw()+
  ylab("Log2 Distance to Annotation")+
  xlab("") +
  scale_fill_manual(name="Boundary",
                    values=c("forestgreen",
                             "blue"))+
  scale_color_manual(values=c("black",
                              "black")) +
  guides(color=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

```

### K562

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

```

#### Plotting

```{r}
pred_v_called_df <- data.frame(LogDist = c(#preciseTAD
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1),

  #PEAKACHU
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)
),
Annotation = c(#preciseTAD
  rep("CTCF",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("RAD21",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("SMC3",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ZNF143",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1))),

  #PEAKACHU
  rep("CTCF",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("RAD21",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("SMC3",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ZNF143",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)))),
BoundReg = c(#preciseTAD
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1))),

  #PEAKACHU
  rep("PEAKACHU", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("PEAKACHU", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("PEAKACHU", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("PEAKACHU", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)))))

pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("preciseTAD", "PEAKACHU"))

ggplot(pred_v_called_df, aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  + 
  facet_grid(~ Annotation) +    
  stat_boxplot(geom ='errorbar', width = 0.2) + 
  geom_boxplot(outlier.shape = NA) +
  geom_signif(test = "wilcox.test", 
              comparisons = list(c("preciseTAD","PEAKACHU")),
              vjust = 0,
              textsize = 4,
              size = .5,
              step_increase = .08,
              color="black") +
  theme_minimal()+
  theme_bw()+
  ylab("Log2 Distance to Annotation")+
  xlab("") +
  scale_fill_manual(name="Boundary",
                    values=c("forestgreen",
                             "blue"))+
  scale_color_manual(values=c("black",
                              "black")) +
  guides(color=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

```

## LOLLIPOP

### GM12878

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_lollipop.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

```

#### Plotting

```{r}
pred_v_called_df <- data.frame(LogDist = c(#preciseTAD
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1),

  #LOLLIPOP
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)
),
Annotation = c(#preciseTAD
  rep("CTCF",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("RAD21",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("SMC3",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ZNF143",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1))),

  #LOLLIPOP
  rep("CTCF",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("RAD21",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("SMC3",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ZNF143",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)))),
BoundReg = c(#preciseTAD
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1))),

  #LOLLIPOP
  rep("LOLLIPOP", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("LOLLIPOP", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("LOLLIPOP", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("LOLLIPOP", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)))))

pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("preciseTAD", "LOLLIPOP"))

ggplot(pred_v_called_df, aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  + 
  facet_grid(~ Annotation) +    
  stat_boxplot(geom ='errorbar', width = 0.2) + 
  geom_boxplot(outlier.shape = NA) +
  geom_signif(test = "wilcox.test", 
              comparisons = list(c("preciseTAD","LOLLIPOP")),
              vjust = 0,
              textsize = 4,
              size = .5,
              step_increase = .08,
              color="black") +
  theme_minimal()+
  theme_bw()+
  ylab("Log2 Distance to Annotation")+
  xlab("") +
  scale_fill_manual(name="Boundary",
                    values=c("forestgreen",
                             "blue"))+
  scale_color_manual(values=c("black",
                              "black")) +
  guides(color=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

```

### K562

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_lollipop.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

```

#### Plotting

```{r}
pred_v_called_df <- data.frame(LogDist = c(#preciseTAD
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1),
  log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1),

  #LOLLIPOP
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1),
  log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)
),
Annotation = c(#preciseTAD
  rep("CTCF",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("RAD21",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("SMC3",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ZNF143",length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1))),

  #LOLLIPOP
  rep("CTCF",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("RAD21",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("SMC3",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("ZNF143",length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)))),
BoundReg = c(#preciseTAD
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("preciseTAD", length(log2(mcols(distanceToNearest(all_pred_bounds, genomicElements.GR[[4]]))$distance+1))),

  #LOLLIPOP
  rep("LOLLIPOP", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[1]]))$distance+1))),
  rep("LOLLIPOP", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[2]]))$distance+1))),
  rep("LOLLIPOP", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[3]]))$distance+1))),
  rep("LOLLIPOP", length(log2(mcols(distanceToNearest(all_true_bounds, genomicElements.GR[[4]]))$distance+1)))))

pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("preciseTAD", "LOLLIPOP"))

ggplot(pred_v_called_df, aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  + 
  facet_grid(~ Annotation) +    
  stat_boxplot(geom ='errorbar', width = 0.2) + 
  geom_boxplot(outlier.shape = NA) +
  geom_signif(test = "wilcox.test", 
              comparisons = list(c("preciseTAD","LOLLIPOP")),
              vjust = 0,
              textsize = 4,
              size = .5,
              step_increase = .08,
              color="black") +
  theme_minimal()+
  theme_bw()+
  ylab("Log2 Distance to Annotation")+
  xlab("") +
  scale_fill_manual(name="Boundary",
                    values=c("forestgreen",
                             "blue"))+
  scale_color_manual(values=c("black",
                              "black")) +
  guides(color=FALSE, linetype=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

```

### 2020-04-29 Scripts_for_results/08_creating_venn_diagrams.Rmd
initial commit

--- 2020-04-29 Scripts_for_results/06_creating_enriched_heatmaps.Rmd
@@
 ---
-title: "Creating enriched heatmaps"
+title: "Creating Venn diagrams"
 author: "Spiro Stilianoudakis"
@@
 
-## Enriched heatmap function
-
-```{r}
-enriched_func <- function(boundaries, annotations, e=5, w=50, ct){
-  axis_names <- c(paste0("-",e,"kb"), "Center", paste0(e,"kb"))
-
-  norm_mat <- normalizeToMatrix(annotations, 
-                                boundaries, 
-                                value_column = "coverage", 
-                                extend = e*1000, 
-                                w = 50,
-                                mean_mode = "w0",
-                                keep = c(0,.999))
-  EH <- EnrichedHeatmap(norm_mat, 
-                        col = ifelse(ct=="ARROWHEAD" | ct=="PEAKACHU" | ct=="LOLLIPOP", c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)),
-                                     c("black",colorRampPalette(c("white", "pink", "red"))(99))), 
-                        #heatmap_legend_param = list(show_heatmap_legend = FALSE),
-                        row_title="Boundaries",
-                        show_heatmap_legend = FALSE,
-                        row_title_side="left", 
-                        column_title=ct, 
-                        axis_name = axis_names,
-                        column_title_gp = gpar(fontsize = 10),
-                        row_title_gp = gpar(fontsize = 10),
-                        axis_name_gp = gpar(fontsize = 10),
-                        top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = ifelse(ct=="ARROWHEAD", "blue", "red"), 
-                                                                                           fontsize = 10,
-                                                                                           lwd = 2), 
-                                                                                 axis_param = list(side = "right",
-                                                                                                   facing = "inside"))))
-  return(EH)
-}
-
-```
-
 ## ARROWHEAD
@@
 ### GM12878
-
-#### Create granges from top tfbs
-
-```{r}
-genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
-                                             pattern="*.bed",
-											 signal=4)
-```
 
@@
 
-all_true_bounds <- do.call("c", true_bound_list)
-all_pred_bounds <- do.call("c", pred_bound_list)
+all_true_bounds_gm12878 <- do.call("c", true_bound_list)
+all_pred_bounds_gm12878 <- do.call("c", pred_bound_list)
 
-length(all_true_bounds) #
-length(all_pred_bounds) #
+all_true_bounds_gm12878 <- flank(all_true_bounds_gm12878, 5000, both=TRUE)
+all_pred_bounds_gm12878 <- flank(all_pred_bounds_gm12878, 5000, both=TRUE)
 
@@
 
-###### CTCF
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="ARROWHEAD")
-enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
-```
-
-###### RAD21
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="ARROWHEAD")
-enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
-```
-
-###### SMC3
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="ARROWHEAD")
-enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
-```
-
-###### ZNF143
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="ARROWHEAD")
-enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
-```
-
 ### K562
-
-#### Create granges from top tfbs
-
-```{r}
-genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS",
-                                             pattern="*.bed",
-											 signal=4)
-```
 
@@
 
-all_true_bounds <- do.call("c", true_bound_list)
-all_pred_bounds <- do.call("c", pred_bound_list)
+all_true_bounds_k562 <- do.call("c", true_bound_list)
+all_pred_bounds_k562 <- do.call("c", pred_bound_list)
 
-length(all_true_bounds) #
-length(all_pred_bounds) #
+all_true_bounds_k562 <- flank(all_true_bounds_k562, 5000, both=TRUE)
+all_pred_bounds_k562 <- flank(all_pred_bounds_k562, 5000, both=TRUE)
 
@@
 
-###### CTCF
+### Within cell line (preciseTAD vs ARROWHEAD)
 
 ```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="ARROWHEAD")
-enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
+venn_cnt2venn <- function(venn_cnt){
+  n <- which(colnames(venn_cnt)=="Counts") - 1
+  SetNames=colnames(venn_cnt)[1:n]
+  Weight=venn_cnt[,"Counts"]
+  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
+  Venn(SetNames=SetNames, Weight=Weight)
+}
+
+###### GM12878
+
+res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
+                                  all_true_bounds_gm12878),
+                       NameOfPeaks=c("preciseTAD", "ARROWHEAD"))
+
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+
+###### K562
+
+res <- makeVennDiagram(Peaks=list(all_pred_bounds_k562,
+                                  all_true_bounds_k562),
+                       NameOfPeaks=c("preciseTAD", "ARROWHEAD"))
+
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+
 ```
 
-###### RAD21
+#### Across cell line
 
 ```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="ARROWHEAD")
-enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
-```
+###### preciseTAD
 
-###### SMC3
+res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
+                                  all_pred_bounds_k562),
+                       NameOfPeaks=c("GM12878", "K562"))
 
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="ARROWHEAD")
-enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
-```
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
 
-###### ZNF143
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
 
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="ARROWHEAD")
-enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
+###### ARROWHEAD
+
+res <- makeVennDiagram(Peaks=list(all_true_bounds_gm12878,
+                                  all_true_bounds_k562),
+                       NameOfPeaks=c("GM12878", "K562"))
+
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+
 ```
@@
 
-###### CTCF
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="PEAKACHU")
-enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
-```
-
-###### RAD21
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="PEAKACHU")
-enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
-```
-
-###### SMC3
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="PEAKACHU")
-enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
-```
-
-###### ZNF143
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="PEAKACHU")
-enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
-```
-
 ### K562
-
-#### Create granges from top tfbs
-
-```{r}
-genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS",
-                                             pattern="*.bed",
-											 signal=4)
-```
 
@@
 
-###### CTCF
+### Within cell line (preciseTAD vs PEAKACHU)
 
 ```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="PEAKACHU")
-enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
+venn_cnt2venn <- function(venn_cnt){
+  n <- which(colnames(venn_cnt)=="Counts") - 1
+  SetNames=colnames(venn_cnt)[1:n]
+  Weight=venn_cnt[,"Counts"]
+  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
+  Venn(SetNames=SetNames, Weight=Weight)
+}
+
+###### GM12878
+
+res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
+                                  all_true_bounds_gm12878),
+                       NameOfPeaks=c("preciseTAD", "PEAKACHU"))
+
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+
+###### K562
+
+res <- makeVennDiagram(Peaks=list(all_pred_bounds_k562,
+                                  all_true_bounds_k562),
+                       NameOfPeaks=c("preciseTAD", "PEAKACHU"))
+
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+
 ```
 
-###### RAD21
+#### Across cell line
 
 ```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="PEAKACHU")
-enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
-```
+###### preciseTAD
 
-###### SMC3
+res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
+                                  all_pred_bounds_k562),
+                       NameOfPeaks=c("GM12878", "K562"))
 
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="PEAKACHU")
-enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
-```
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
 
-###### ZNF143
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
 
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="PEAKACHU")
-enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
+###### PEAKACHU
+
+res <- makeVennDiagram(Peaks=list(all_true_bounds_gm12878,
+                                  all_true_bounds_k562),
+                       NameOfPeaks=c("GM12878", "K562"))
+
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+
 ```
@@
 
-###### CTCF
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="LOLLIPOP")
-enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
-```
-
-###### RAD21
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="LOLLIPOP")
-enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
-```
-
-###### SMC3
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="LOLLIPOP")
-enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
-```
-
-###### ZNF143
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="LOLLIPOP")
-enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
-```
-
 ### K562
-
-#### Create granges from top tfbs
-
-```{r}
-genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS",
-                                             pattern="*.bed",
-											 signal=4)
-```
 
@@
 
-###### CTCF
+### Within cell line (preciseTAD vs LOLLIPOP)
 
 ```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="LOLLIPOP")
-enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
+venn_cnt2venn <- function(venn_cnt){
+  n <- which(colnames(venn_cnt)=="Counts") - 1
+  SetNames=colnames(venn_cnt)[1:n]
+  Weight=venn_cnt[,"Counts"]
+  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
+  Venn(SetNames=SetNames, Weight=Weight)
+}
+
+###### GM12878
+
+res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
+                                  all_true_bounds_gm12878),
+                       NameOfPeaks=c("preciseTAD", "LOLLIPOP"))
+
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+
+###### K562
+
+res <- makeVennDiagram(Peaks=list(all_pred_bounds_k562,
+                                  all_true_bounds_k562),
+                       NameOfPeaks=c("preciseTAD", "LOLLIPOP"))
+
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+
 ```
 
-###### RAD21
+#### Across cell line
 
 ```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="LOLLIPOP")
-enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
+###### preciseTAD
+
+res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
+                                  all_pred_bounds_k562),
+                       NameOfPeaks=c("GM12878", "K562"))
+
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+
+###### LOLLIPOP
+
+res <- makeVennDiagram(Peaks=list(all_true_bounds_gm12878,
+                                  all_true_bounds_k562),
+                       NameOfPeaks=c("GM12878", "K562"))
+
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "lightblue"
+gp[["Face"]][["10"]]$fill <-  "red"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+
 ```
-
-###### SMC3
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="LOLLIPOP")
-enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
-```
-
-###### ZNF143
-
-```{r}
-enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="LOLLIPOP")
-enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
-```

### 2020-04-29 Scripts_for_results/09_visualizing_example_of_preciseTAD_predictions.Rmd
initial commit

---
title: "Visualizing example of predicted TAD boundaries"
author: "Spiro Stilianoudakis"
date: "4/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages and functions

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrf.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

# ARROWHEAD

## Extracting TAD boundaries using the extract_boundaries_func function for ARROWHEAD defined TADs at 10kb resolution

```{r}
domains <- read.table("Z:/TAD_data_analysis/GM12878/5kb/GM12878_domain_data_5000.b.txt")
bounds.GR <- extract_boundaries_func(domains.mat=domains, 
                                     preprocess=FALSE, 
                                     CHR=paste0("CHR", c(1:8,10:22)), 
                                     resolution=5000)
```

## Obtaining list of GRanges objects of ChIP-seq data used for modelling

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
                                             pattern="*.bed",
                                             signal=4)
```

## Running TADrf and preciseTAD

```{r}
tadModel <- TADrf(bounds.GR=bounds.GR,
                  resolution=5000,
                  genomicElements.GR=genomicElements.GR,
                  featureType="distance",
                  resampling="rus",
                  trainCHR=paste0("CHR", c(1:8,10:22)),
                  predictCHR=NULL,
                  cvFolds=3,
                  ntrees=100,
                  cvMetric="Accuracy",
                  verbose=TRUE,
                  seed=123,
                  model=TRUE,
                  importances=TRUE,
                  performances=FALSE)

bounds.GR <- extract_boundaries_func(domains.mat=domains, 
                                     preprocess=FALSE, 
                                     CHR="CHR22", 
                                     resolution=5000)

pt <- preciseTAD(bounds.GR=bounds.GR,
                      genomicElements.GR=genomicElements.GR,
                      featureType="distance",
                      CHR="CHR22",
                      chromCoords=list(17389000,18011000),
                      tadModel=tadModel[[1]],
                      threshold=1.0,
                      flank=NULL,
                      verbose=TRUE,
                      seed=123,
                      parallel=FALSE,
                      cores=NULL,
                      splits=NULL,
                      method.Dist="euclidean",
                      DBSCAN=TRUE,
                      DBSCAN_params=list(5000,3), #or list(10000,3)
                      method.Clust=NULL,
                      PTBR=TRUE,
                      CLARA=TRUE,
                      samples=100)

```

##OR (pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD.rds"))

## Plotting

```{r}
getChrLength <- function(genome = "BSgenome.Hsapiens.UCSC.hg19"){
  g <- getBSgenome(genome, masked=FALSE)
  data.frame(chrom=1:24, length=seqlengths(g)[1:24])
}
.chrAsNum <- function(tbl){
  tbl$chrom <- gsub("chr", "", tbl$chrom)
  tbl$chrom[tbl$chrom=="X"] <- 23
  tbl$chrom[tbl$chrom=="Y"] <- 24
  tbl$chrom <- as.numeric(tbl$chrom)
  tbl[order(tbl$chrom),]
}
getCentromeres <- function( genome="hg19" ){
  mySession <- try(browserSession("UCSC"), silent=TRUE)
  # In case of failure, try another mirror
  if(inherits(mySession, "try-error"))
    mySession <- browserSession("UCSC",
                                url="http://genome-euro.ucsc.edu/cgi-bin/")
  genome(mySession) <- genome
  obj <- ucscTableQuery(mySession, table="gap")
  tbl <- getTable(obj)
  tbl <- tbl[tbl$type=="centromere", c("chrom", "chromStart", "chromEnd")]
  colnames(tbl)[2:3] <- c("centromerStart", "centromerEnd")
  .chrAsNum(tbl)
}
makeHg19 <- function(){
  tbl <- merge(getChrLength(), getCentromeres(), by="chrom")
  cumlen <- c(0, cumsum(as.numeric(tbl$length))[-nrow(tbl)])
  cbind.data.frame(tbl, cumlen=cumlen)    
}
hg19 <- makeHg19()
hg19$chrom <- paste0("CHR",hg19$chrom)

seqDataTest <- c(17389000:18011000)

CHR="CHR22"

  if("TRUE" %in% table(seqDataTest %in% c(hg19$centromerStart[hg19$chrom==CHR]:hg19$centromerEnd[hg19$chrom==CHR]))){
    centromereTestStart <- hg19$centromerStart[hg19$chrom==CHR]
    centromereTestEnd <- hg19$centromerEnd[hg19$chrom==CHR]
    seqDataTest <- seqDataTest[-which(seqDataTest %in% c(centromereTestStart:centromereTestEnd))]
  }

test_data <- matrix(nrow=length(seqDataTest),
                    ncol=length(genomicElements.GR))
p <- lapply(genomicElements.GR, function(x){distance_func(GRanges(seqnames=tolower(CHR),
                                                                    IRanges(start=seqDataTest,
                                                                            end=seqDataTest)), 
                                                            x)})
for(i in 1:length(genomicElements.GR)){
  test_data[,i] <- p[[i]]
}
colnames(test_data) <- gsub(paste0(c("K562", "Gm12878", "-", "Broad", "Haib", "Sydh", "Uta", "Uw", "Uchicago"), collapse = "|"),"",names(genomicElements.GR))
test_data <- apply(test_data,2,function(x){log(x + 1, base=2)})
predictions <- predict(tadModel[[1]],newdata=test_data,type="prob")[,"Yes"]

predprobdata <- data.frame(basenum=c(17389000:18011000),
                           prob=predictions)
predprobdata$predicted <- ifelse(predprobdata$basenum %in% start(pt[[2]]), "Yes", "No")
predprobdata$called <- ifelse(predprobdata$basenum %in% start(pt[[3]]), "Yes", "No")

calleddata <- predprobdata[which(predprobdata$called=="Yes"),]

predicteddata <- predprobdata[which(predprobdata$prob>=1.0),]

predicteddata2 <- predprobdata[which(predprobdata$predicted=="Yes"),]
#predicteddata2 <- predicteddata2[-c(3),]

ggplot() + 
  geom_line(data=predprobdata, aes(x=basenum, y=prob), 
            color='black',
            size=1)+
  #geom_vline(data=predicteddata, aes(xintercept=basenum, 
  #                                   color="red"),
  #           size=.5,
  #           show.legend = TRUE)+
  geom_vline(data=calleddata, aes(xintercept=basenum, 
                                  color="blue"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata2, aes(xintercept=basenum, 
                                      color="green"),
             size=.75,
             show.legend = TRUE)+
  xlab("Base Pair Coordinate") +
  ylab("Probability") +
  scale_color_manual(name = '', 
                     values =c("blue", "green"),
                     labels = c("ARROWHEAD",
                                "preciseTAD"))+
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

```

### 2020-05-01 Scripts_for_results/04_creating_rfe_lineplot.Rmd
edits to results scripts

@@
                 size=1, 
-                color="red") +
-  geom_line(size=2, color="red") +
-  geom_point(size=4, color="red") +
+                color="blue") +
+  geom_line(size=2, color="blue") +
+  geom_point(size=4, color="blue") +
   xlab("Number of top ranked annotations") +

### 2020-05-01 Scripts_for_results/05_creating_importance_plot.Rmd
edits to results scripts

@@
 
+rfe.set.mat <- t(apply(rfe.set.mat,1,rev))
+
 distance.col = dist(rfe.set.mat, method = "euclidean")
@@
           trace="none",         # turns off trace lines inside the heat map
-          margins=c(12,8),     # widens margins around plot
+          margins=c(10,4),     # widens margins around plot
           col=my_palette,       # use on color palette defined earlier
@@
 
+rfe.set.mat <- t(apply(rfe.set.mat,1,rev))
+
 distance.col = dist(rfe.set.mat, method = "euclidean")
 cluster.col = hclust(distance.col, method = "average")
-my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfe.set.mat))
+my_palette <- colorRampPalette(c("white", "lightblue", "blue"))(ncol(rfe.set.mat))
 
@@
                                           "/",
-                                          "5kb/results_by_chr/",
+                                          "10kb/results_by_chr/",
                                           chrs[k],

### 2020-05-01 Scripts_for_results/09_visualizing_example_of_preciseTAD_predictions.Rmd
edits to results scripts

@@
                                      preprocess=FALSE, 
-                                     CHR="CHR22", 
+                                     #CHR="CHR22", 
+                                     CHR="CHR21", 
                                      resolution=5000)
@@
                       CHR="CHR22",
-                      chromCoords=list(17389000,18011000),
+                      CHR="CHR21",
+                      #chromCoords=list(17389000,18011000),
+                      chromCoords=list(15150000,17270000),
                       tadModel=tadModel[[1]],
@@
                       PTBR=TRUE,
-                      CLARA=TRUE,
+                      CLARA=FALSE,
                       samples=100)
@@
 
-##OR (pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD.rds"))
+##OR 
+##(pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD.rds"))
+##(pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR21/rus/distance/preciseTAD.rds"))
 
@@
 
-seqDataTest <- c(17389000:18011000)
+#seqDataTest <- c(17389000:18011000)
+#seqDataTest <- c(25745000:26176000)
+seqDataTest <- c(15150000:17270000)
 
-CHR="CHR22"
+#CHR="CHR22"
+CHR="CHR21"
 
@@
 
-predprobdata <- data.frame(basenum=c(17389000:18011000),
+predprobdata <- data.frame(#basenum=c(17389000:18011000),
+                           basenum=c(15150000:17270000),
                            prob=predictions)

### 2020-05-01 Manuscript/manuscript.Rmd
edits to results section

@@
 
-We developed a computational framework<!--, refered to as *TADRF*,--> aimed at determining the optimal set of data level characteristics necessary for TAD boundary prediction using random forest classification models.
-We then leveraged our optimally built random forest to precisely predict the genomic coordinates of TAD boundaries at base pair resolution.
+We developed a computational framework<!--, refered to as *TADRF*,--> aimed at determining the optimal set of data level characteristics necessary for topologically associated domain (TAD) boundary prediction using random forest classification models.
+We then leveraged our optimally built random forest to precisely predict the genomic coordinates of both TAD and loop boundaries at base pair resolution.
 
-Our framework is resolution-specific and uses arbitrary called TAD boundaries as ground truth to establish TAD-boundary and non-TAD boundary regions.
+Our framework is resolution-specific and uses arbitrary called TAD and loop boundaries as ground truth to establish TAD(loop)-boundary and non-TAD(loop) boundary regions.
 To demonstrate, we applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1).
-Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-TAD boundary regions were defined as regions on the linear genome where a genomic bin contained a called TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as genomic bins that did not contain a TAD boundary ($Y = 0$) (Figure 1A).
-Under this construction, the number of non-TAD boundary regions far exceed the number of TAD boundary regions.
-To cope with the imbalance among the classes of genomic bins, we evaluated three re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries.
-*Random over-sampling* (ROS) was defined as sampling with replacement from TAD boundary regions.
-*Random under-sampling* (RUS) was defined as sampling with replacement from non-TAD boundary regions.
+TADs were subsequently called using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
+For loop boundaries we opted to use boundaries obtained by the PEAKACHU tool for the GM12878 and K562 cell lines at 10 kb resolution [@salameh2019supervised].
+
+Boundary regions were defined as regions on the linear genome where a genomic bin contained a called boundary ($Y = 1$), while non-boundary regions were defined as genomic bins that did not contain a boundary ($Y = 0$) (Figure 1A).
+Under this construction, the number of non-boundary regions far exceeded the number of boundary regions.
+To cope with the imbalance among the classes of genomic bins, we evaluated three re-sampling techniques (in addition to no re-sampling) before predicting boundary regions.
+*Random over-sampling* (ROS) was defined as sampling with replacement from boundary regions.
+*Random under-sampling* (RUS) was defined as sampling with replacement from non-boundary regions.
 Lastly, we considered *Synthetic minority over-sampling technique* (SMOTE), which is a combination of both random over- and under-sampling [@chawla2002smote].
 
-A total of 78 cell type specific functional genomic annotations were used to build the feature space of downstream random forest models (Supplementary Table 2).
-The annotations could be broken down into three sets including histone modifications (HM), cis-regulatory elements (CRE), and transcription factor binding sites (TFBS).
+A total of 78 cell line specific functional genomic annotations were used to build the feature space of downstream random forest models (Supplementary Table 2).
+The annotations could be broken down into three sets including histone modifications (HM), cis-regulatory elements (BroadHMM), and transcription factor binding sites (TFBS).
 Four different feature engineering procedures were developed for each genomic element (Figure 1 B).
@@
 A log2-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
-These feature engineering procedures were performed to improve TAD boundary predictions by accounting for direct (OC), proportional (Signal/OP), and spatial (distance) relationships between TAD boundaries and genomic annotations.
+These feature engineering procedures were performed to improve boundary predictions by accounting for direct (OC), proportional (Signal/OP), and spatial (distance) relationships between TAD boundaries and genomic annotations.
 
@@
 The response vector **Y** was defined as a genomic bin that either overlapped with a TAD boundary ($Y = 1$) or did not ($Y = 0$).
-(B) Four types of associations between bins and genomic annotations (green shapes) were then used to build the feature space including _Peak Signal_ (Signal), _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.](Figures/model_construction_and_predictor_types.png)
+(B) Four types of associations between bins and genomic annotations (green shapes) were then used to build the feature space including _Peak Signal_ (Signal), _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.](Figures/figure1_model_construction_and_predictor_types.png)
 
-Thus, under our framework, we considered combinations of data for a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, with a specific engineered feature space *P = {Signal, OC, OP, Distance}*, and re-sampling technique *B = {None, RUS, ROS, SMOTE}* (Figure 2).
+Thus, under our framework, we considered combinations of data for a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, with a specific engineered feature space *P = {Signal, OC, OP, Distance}*, and re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
+Once the model inputs were established, a random forest classifier was trained on chromosome-specific genomic bins (excluding chromosome 9), *C = {CHR1, ..., CHR22}*, using 5-fold cross-validation.
 Model inputs were evaluated by assessing the balanced accuracy (BA) of each combination.
-Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2 \times 5 \times 4 \times 4 (= 160)$ models.
-The results presented are for the GM12878 cell line, with K562 results presented in the Supplementary material.
+<!--The results presented are for the ARROWHEAD boundaries, with PEAKACHU boundaries presented in the Supplementary material.
+Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |S| \times |C|$ different ensemble systems, totaling $2 \times 5 \times 4 \times 4 \times 21 (= 3360)$ models.-->
 
-![**A diagram of the ensemble framework detailing the steps for combining different inputs used in the random forest model building pipeline.** Step 1 is to establish the rowise (genomic bins) and columnwise (genomic annotations) dimensions of the data matrix, **A**, by combining a resolution (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)).
+![**A diagram of the ensemble framework detailing the steps for combining different inputs used in the random forest model building pipeline.** Step 1 is to establish the chromosome-specific rowise (genomic bins) and columnwise (genomic annotations) dimensions of the data matrix, **A**, by combining a resolution (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)).
 Step 2 is to split **A** into a training and testing set according to a 7:3 ratio.
 Step 3 is to apply a re-sampling technique to the training set (no re-sampling, random over-sampling, random under-sampling, or SMOTE re-sampling).
-Step 4 is to implement the random forest algorithm and perform 3-fold cross-validation to tune for the *mtry* parameter.
-Finally, step 5 is to validate the model on the separate test data and evaluate model performance using balanced accuracy (BA).](Figures/ensemble_framework.png)
+Step 4 is to implement the random forest algorithm and perform 5-fold cross-validation to tune for the *mtry* parameter.
+Finally, step 5 is to validate the model on the separate test data and evaluate model performance using balanced accuracy (BA).](Figures/figure2_ensemble_framework.png)
 
-We obtained a total of 8052, 7676, 4670, 2349, and 1031 called TADs across each resolution respectively (Table 1).
-From the called TADs, a total of 15468, 14253, 8363, 4224, and 1883 unique TAD boundaries were obtained (Table 2).
-The resolution-specific approach we developed to create TAD vs non-TAD boundary regions amenable for binary classification (See Methods) resulted in a total of 535363, 267682, 107073, 53537, and 26768 genomic bins.
-The class imbalance among the genomic bins was found to be both severe and invariant toward resolution.
-Specifically, we found the imbalance between TAD boundary and non-TAD boundary regions to be 0.03, 0.05, 0.08, 0.08, and 0.07 for each resolution respectively (Table 1).
-Furthermore, the data summaries presented in Table 1 were found to be similar to those exibited by the K562 cell line (Supplementary Table 3).
+Using ARROWHEAD, we obtained a total of 8052, 7676, 4670, 2349, and 1031 called TADs  across each resolution respectively (Table 1).
+From the called TADs, a total of 15468, 14253, 8363, 4224, and 1883 unique TAD boundaries were obtained (Table 1).
+The resolution-specific approach we developed to create boundary vs non-boundary regions resulted in a total of 535363, 267682, 107073, 53537, and 26768 genomic bins.
+The class imbalance among the genomic bins was both severe and invariant toward resolution, resulting in 0.03, 0.05, 0.08, 0.08, and 0.07 for each resolution respectively (Table 1).
+Boundary data summaries were similar for K562 cell line, as well as for PEAKACHU defined boundaries (Supplementary Tables 3-4).
 
@@
 
-<!--
 Expectedly, when using data with class imbalance present, that is no re-sampling, the models exhibited low balanced accuracies, with very little variability among different resolutions (Figure 3).
@@
 As with comparing class balancing techniques, this improvement was less evident at lower resolutions.
+These results were found to be consistent for the K562 cell line (Supplementary Figure 2).
+Contrary to ARROWHEAD defined boundaries, random forest models built on PEAKACHU loop boundaries exhibited optimal performance when implemented on SMOTE re-sampled data for both GM12878 and K562 cell lines (Supplementary Figure 3).
+In summary, our computational framework showed that using random under-sampling, distance-type predictors, and Hi-C data at 5kb resolution yields an optimally performing cell line-specific random forest classification model for TAD boundary region prediction.
 
+<!--
 Interestingly, for the optimal re-sampling and predictor type, we found that performances peaked at 10 kb resolution and then degraded as data resolution decreased.
@@
 ![**Models built using distance-type predictors combined with random under-sampling at 5 kb yielded optimal predictive performance for GM12878.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
-Performances are compared across resolution, within each predictor-type: (A) OC, (B) OP, and (C) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Performances were evaluated using balanced accuracy.](Figures/performances.png)
+Performances are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Performances were evaluated using balanced accuracy.](Figures/figure3_performances.png)
 
-## Transcription factor binding sites outperform HM- and CRE-specific models
+## Transcription factor binding sites outperform HM- and BroadHMM-specific models
 
 We then aimed to compare the performances of genomic class-specifc models.
-In doing so, we inspected the proportion of predictive importance that was explained by each of the three classes of genomic elements including histone modifications (HM), cis-regulatory elements (CRE), and transcription factor binding sites (TFBS).
-For an optimally built random forest classifier at each data resolution--smote re-sampling, and distance-type predictors--we found that the majority of the proportional predictive importance was obtained by transcription factor binding sites for both cell lines (Supplementary Figure 3 A-B).
-Furthermore, models built solely on TFBS outperformed other class-specific models (Figure 4A; Supplementary Figure 4A).
-Notably, the TFBS-specific models outperformed models built on the combination of all genomic elements at lower resolutions, indicating that the inclusion of other types of annotations contributed to additional noise rather than signal in TAD boundary prediction.
-Our results suggest that TFBS are the primary drivers of TAD boundary formation in both the GM12878 and K562 cell lines.
+In doing so, we evaluated performances for an optimally built random forest model using only histone modifications (HM), cis-regulatory elements (BroadHMM), and transcription factor binding sites (TFBS) separately.
+We found that models built solely on TFBS outperformed other class-specific models suggesting that TFBS are the primary drivers of TAD and loop boundary formation in both the GM12878 and K562 cell lines (Figure 4A; Supplementary Figures 4A,5A,6A).
 
@@
 
-Given that many TFBS are known to colocalize together on the linear genome and are therefore highly correlated, we sought to further optimize our TAD prediction model to avoid overfitting by performing recursive feature elimination.
-We found that, under our framework, we were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figure 4B).
+We sought to further optimize our TAD prediction model by performing recursive feature elimination to avoid overfitting and select only the most influential TFBS across all chromosomes.
+Under our framework, we were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figures 4B,5B,6B).
 However, given that we trained our model on chromosome-specific data, the most significant annotations were found to vary for each chromosome.
 To determine the most common TFBS, we clustered the predictive importances across chromosomes.
-We found that, similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD boundary regions for all chromosomes (Figure 4C; Supplementary Figure 4C).
-Therefore, using our framework *TADRF* was able to identify the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@fudenberg2016formation; @alipour2012self].
-Therefore, we could further optimize our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
-To summarize, the optimally built cell line-specific random forest model under our *TADRF* framework was found to be one built using 10 kb resolution data, leveraging distance-type predictors for the CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites, while implementing random under-sampling to balance TAD and non-TAD boundary defined genomic bins.
+We found that, similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD boundary regions for all chromosomes (Figure 4C; Supplementary Figures 4C,5C,6C).
+Therefore, our framework was able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@fudenberg2016formation; @alipour2012self].
+We further optimized our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
 
-![**Assessing top ranked transcription factors in TAD boundary prediction for GM12878.** (A) Barplots comparing performances of models using specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (CRE; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all three classes (Combined; purple).
+<!--
+To summarize, the optimally built cell line-specific random forest model under our computational framework was found to be one built using 10 kb resolution data, leveraging distance-type predictors for the CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites, while implementing random under-sampling to balance TAD and non-TAD boundary defined genomic bins.
+-->
+
+![**Assessing top ranked transcription factors in TAD boundary prediction for GM12878.** (A) Barplots comparing performances of models using specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (BroadHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model containing all three classes (ALL; purple).
 (B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.
-Error bars represent standard deviation from the mean MCC across each chromosome.
-(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.](Figures/annots_specifc_rfe_importances.png)
+Error bars represent standard deviation from the cross-validated accuracy across each chromosome.
+(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.](Figures/figure4_annots_specifc_rfe_importances.png)
 
-## *preciseTAD* defines precise and biologically relevant locations of TAD boundaries
+## *preciseTAD* identifies precise and biologically relevant locations of TAD boundaries
 
-After obtaining our optimally built *TADRF* model, we investigated whether we could leverage our model to alleviate resolution limitations of Hi-C data by predicting TAD boundaries at base pair resolution.
-Our method, referred to as *preciseTAD*, uses a combination of complete linkage hierarchical clustering with a scalable version of partitioning around mediods (PAM), known as clustering large applications (CLARA) to reduce many adjacent base pairs with similarly high predictive probabilities down to a set of the most representative and biologically meaningful predicted TAD boundaries (see Methods).
-*preciseTAD* was applied to chromosome-specific sections of the linear genome.
-For each chromosome, we defined our new validation data using distance-type predictors among only the most informative TFBS for each base pair, namely the CTCF, RAD21, SMC3, and ZNF143 transcription factors.
-That is, each base pair had a corresponding row vector, **X**=$\{X_{1}, ..., X_{4}\}$, representing the $log_{2}$ genomic distances to the nearest respective transcription factor binding site.
+After obtaining our optimally built random forest model, we investigated whether we could leverage our model to alleviate resolution limitations of Hi-C data by predicting TAD boundaries at base pair resolution.
+Our method, referred to as *preciseTAD*, leverages a user specified binary classifier with a combination of density-based hierarchical clustering and a scalable version of partitioning around mediods (PAM), known as clustering large applications (CLARA) to precisely identify the most representative and biologically meaningful predicted chromosome-specific domain boundaries (see Methods).
 
+Here, we opted to implement preciseTAD using an optimally built whole genome random forest model.
+That is, a random forest model built on 5 kb defined genomic bins, with random under-sampling, and distance-type predictors for the top informative TFBS (CTCF, RAD21, SMC3, and ZNF143).
+The reason for this was because of the improved performance that was exhibited for a whole genome random forest compared to aggregated chromosome-specific models (Supplementary Figure 7).
+
+???stopped here; waiting to predicted tad boundaries results
+
+<!--
 We first used ROC analysis to obtain an optimal probability threshold for defining potential predicted TAD boundaries.
@@
 [???include a result that demonstrates this; discuss in meeting]
-
-???stopped here; waiting to predicted tad boundaries results
+-->
 
@@
 Furthermore, when compared to called TAD boundaries, the boundaries that we predicted with our model were found to be statistically significantly closer to the top ranked TFBS, suggesting stronger enrichment profiles near predicted TAD boundaries (Supplementary Figure 7).
--->
 
@@
 The green vertical lines represent the *predicted TAD boundary points* (PTBA) identified by *preciseTAD*, with the corresponding predicted TADs outlined above in green.](Figures/visualizing_ptbp_and_ctbp.png)
+-->
 
@@
 
-**Supplementary Table 1.
-Hi-C and genomic annotation data.** (A) A complete list of the Hi-C data libraries used to obtain the locations of topologically associating domains.
-(B) A complete list of the cell line specific genomic annotations used to build the feature space for all downstream models.
+**Supplementary Table 1.** A complete list of the Hi-C data libraries obtained from GEO GSE63525 [@rao20143d] used to obtain the locations of topologically associating domains for ARROWHEAD, as well as the locations for the cell line specific .txt files of loop boundaries obtained by PEAKACHU [@salameh2019supervised].
+
+**Supplementary Table 2.** A complete list of the genomic annotations used to build the feature space for all downstream models.
 The GRCh37/hg19 human genome assembly was used.
-"Genomic Class" - broad category of genomic features, "Element" - names of genomic annotations, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
+"Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
 
-**Supplementary Figure 1.
-Performing $log_{2}$ transformations normalizes skewed distance densities across resolution.** When measured in basepairs, distances were highly right skewed (red lines) across all resolutions for both the GM12878 (A) and K562 (B) cell lines.
-After $log_{2}$ transforming the distances (blue lines), densities became much more gaussian distributed for all resolutions.
+**Supplementary Figure 1.** Density curves illustrate the normalization of distances before (red) and after (blue) performing a $log_{2}$ transformation across differing bin sizes including 10 kb, 25 kb, 50 kb, and 100 kb for both the (A) GM12878 and (B) K562 cell lines respectively.
+Distances are measured as the number of base pairs from the center of a genomic bin to the center of the nearest genomic annotation.
+Each density curve represents a particular genomic annotation.
+
+**Supplementary Table 3.** Domain boundary and class imbalance summaries from SpectralTAD across resolution for both the
+GM12878 and K562 cell lines respectively.
+
+**Supplementary Table 4.** Loop boundary and class imbalance summaries from PEAKACHU 10 kb resolution for both the GM12878 and K562 cell lines respectively.
 
 **Supplementary Figure 2.
-Models built using distance-type predictors combined with SMOTE re-sampling yielded optimal MCCs across resolution on K562.** Barplots comparing the performances of random forest classifiers built using different combinations of data level characteristics for K562.
-Within each re-sampling technique (A-D), performances are compared for each type of feature space: OC (red), OP (green), and Distance (blue), across resolutions.
-Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.
+Models built using distance-type predictors combined with random under-sampling at 5 kb yielded optimal predictive performance for K562.** Line plots comparing the performances of random forest classifiers built using ARROWHEAD boundaries at different combinations of data level characteristics.
+Performances are compared across resolution, within each predictor-type: (A) Signal (B) OC, (C) OP, and (D) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Performances were evaluated using balanced accuracy.
 
+**Supplementary Figure 3.
+Models built using distance-type predictors combined with SMOTE re-sampling yielded optimal predictive performance for GM12878 K562.** Line plots comparing the performances of random forest classifiers built using using PEAKACHU boundaries at different combinations of data level characteristics for (A) GM12878 and (B) K562.
+Performances are compared across resampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple), and within each predictor-type: Signal, OC, OP, and Distance.
+
+**Supplementary Figure 4.
+Assessing top ranked transcription factors in TAD boundary prediction for K562.** (A) Barplots comparing performances of models built using ARROWHEAD boundaries on specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (BroadHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model containing all three classes (ALL; purple).
+(B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.
+Error bars represent standard deviation from the cross-validated accuracy across each chromosome.
+(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.
+
+**Supplementary Figure 5.
+Assessing top ranked transcription factors in loop boundary prediction for GM12878.** (A) Barplots comparing performances of models built using PEAKACHU boundaries on specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (BroadHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model containing all three classes (ALL; purple).
+(B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.
+Error bars represent standard deviation from the cross-validated accuracy across each chromosome.
+(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.
+
+**Supplementary Figure 6.
+Assessing top ranked transcription factors in loop boundary prediction for K562.** (A) Barplots comparing performances of models built using PEAKACHU boundaries on specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (BroadHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model containing all three classes (ALL; purple).
+(B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.
+Error bars represent standard deviation from the cross-validated accuracy across each chromosome.
+(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.
+
+**Supplementary Figure 7.
+Whole genome random forest model outperform chromosome-specific random forest models across resolutions.** Random forest models built on ARROWHEAD boundaries using 5 kb defined genomic bins, with random under-sampling, and distance-type predictors for the top informative TFBS (CTCF, RAD21, SMC3, and ZNF143) applied to the entire genome (A) exhibit higher balanced accuracies than their chromosome specific counterparts (B) across each resolution respectively.
+
+<!--
 **Supplementary Figure 3.
@@
 Proportional importance was then calculated according to the annotation group of the feature space including histone modifications (HM), chromatin state segmentations (ChromHMM), and transcription factor binding sites (TFBS).
-
-**Supplementary Figure 4.
-Assessing top ranked transcription factors in TAD boundary prediction for K562.** (A) Barplots comparing performances of models using K562-specific groups of functional genomic annotation as the feature space including histone modifications (HM; red), chromatin states (ChromHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all 3 groups (Combined; purple).
-Error bars represent ± 1 standard deviation from the mean MCC across each chromosomal section of the linear genome.
-(B) Recursive feature elimination analysis used to reduce the number of TFBS to include in the optimally build random forest classifier.
-Error bars represent 1 standard deviation away from the mean cross-validated MCC.
-(C) Clustered heatmap of predictive importance for the union of the top 8 most predictive TFBS across chromosomes.
 
@@
 Called but not predicted (CBNP) were the set of 10 kb flanked called TAD boundaries that did not overlap with 10 kb flanked predicted TAD boundaries.
+-->
 

### 2020-05-02 Manuscript/manuscript.Rmd
Data questions

@@
 
-Biological replicate Hi-C data were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1) for the GM12878 and K562 cell lines.
+Biological replicate [???
+Didn't you use combined Arrowhead calls?
+Replicates seem irrelevant] Hi-C data were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1) for the GM12878 and K562 cell lines.
 The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from Hi-C data at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolution using the ARROWHEAD algorithm [@durand2016juicebox].
 TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all resolutions and cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
+[???
+Can you look up closer?
+If Arrowhead could call boundaries at 5kb, but not 10kb, it is strange]
 

### 2020-05-02 Manuscript/manuscript.Rmd
Consolidate data sources section

@@
 
-## TAD boundary data
+## Data sources
 
@@
 Can you look up closer?
-If Arrowhead could call boundaries at 5kb, but not 10kb, it is strange]
-
-## Genomic annotation and TAD boundary data
-
-A total of 78 cell type-specific ChIP-Seq annotations in the form of cell cis-regulatory elements (CRE), histone modifications (HM), and transcription factor binding sites (TFBS) were obtained from the UCSC Genome Browser Database for both GM12878 and K562 (GRCh37/hg19 human genome assembly) [@Tyner:2017aa] (Supplementary Table 2).
+If Arrowhead could call boundaries at 5kb, but not 10kb, it is strange] Cell type-specific genomic annotations (BroadHMM chromatin segmentations, histone modifications, and transcription factor binding sites) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (GRCh37/hg19 human genome assembly, Supplementary Table 2).
+[???
+Change "cis-regulatory elements (CRE)" to "C]
 

### 2020-05-02 Manuscript/manuscript.Rmd
Finish methods

@@
 
-## Computational framework for TAD boundary prediction using random forests
+## Computational framework for TAD boundary prediction
 
-To make the data amenable for model training, the genome was first binned into equally sized intervals defined by the data resolution (*r*) of the corresponding contact matrix.
-The binning was initiated at the chromosome-specific genomic coordinate marking half of the resolution, and continued in congruent intervals until the end of the chromosome (*mod r* + *r/2*).
-This was to ensure that called (ground truth) TAD boundaries would be positioned in the center of respective genomic bins.
-Genomic bins were then defined as TAD boundary regions (*Y = 1*) if they contained a TAD boundary, and non-TAD boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for random forest classification.
+In Hi-C, each chromosome is binned into non-overlapping regions of the same length *r*, typically, 5kb and above.
+The *r* parameter defines the resolution of Hi-C data.
+Consequently, the location of TAD boundaries is limited by the resolution *r*.
+We designed a strategy called _shifted binning_ that partitions the genome into regions of the same length *r*, but with middle points corresponding to boundaries defined by the original binning.
 
-Cell type-specific genomic annotations were used to build the predictor space for of our random forest models.
-We created four types of predictors: *Peak Signal Strength* - [???include definition] (refered to hereafter as *Signal*), *Overlap Count (OC)* - the total number of overlaps between a bin and genomic annotation regions;  *Overlap Percent (OP)* - the percent of overlap between the bin and the total width of genomic annotation regions overlapping it; *Log2 Distance* - the $log_{2}$ of the distance in bases (refered to hereafter as *Distance*), from the center of the bin to the center of the nearest genomic annotation region.
+To create shifted binning, the first chromosome-specific bin was set at half of the resolution *r*, and continued in congruent intervals of length *r* until the end of the chromosome (*mod r* + *r/2*).
+The shifted genomic bins, referred hereafted as bins for simplicity, were then defined as TAD boundary regions (*Y = 1*) if they contained a TAD boundary, and non-TAD boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification (Figure 1).
 
-Chromosome-specific datasets used for modeling were composed of two components: the response vector **Y**, an indicator variable separating between TAD and non-TAD boundary regions, and the predictor-type specific data matrix, **X** = {$X_1$, $X_2$, ..., $X_p$}, where $p$ was the set of genomic annotations.
-Each dataset was concatenated to form a whole genome dataset.
-The dataset was then split into a 7:3 ratio for training and testing respectively.
+Cell type-specific genomic annotations were used to build the predictor space for our TAD boundary prediction framework.
+Bins were annotated by the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average [???
+Is that correct?
+Or, max?] signal strength of the corresponding annotation (*Peak Signal Strength*), and the $log_{2}$ of the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
+
+Chromosome-specific datasets used for modeling were composed of two components: the response vector $Y_N$, an indicator variable separating between TAD and non-TAD boundary regions, and the predictor-type specific data matrix, $X = X_1, X_2, ..., X_p$ [???
+Need to incorporate N, use proper math notation, maybe $\in$], where $n \in N$ is the number of bins (different for each chromosome) and $p$ is the number of genomic annotations (depends on the type of annotartions).
+Chromosome-specific dataseta were concatenated to form a whole genome dataset.
+The dataset was then split into a 7:3 ratio for training and testing, respectively.
+
+## Class imbalance assessment
 
@@
 We restricted the algorithm to 100% over-sampling and 200% under-sampling, which creates perfectly balanced classes.
+[???
+Of what size?]
 
@@
 The number of trees that were aggregated for each random forest model was set to the default, $n=500$.
-The performance of each model was compared using Balanced Accuracy (BA), defined as
+The performance of each model was compared using Balanced Accuracy (BA), defined as the average of sensitivity and specificity: [???
+Correct?]
 
@@
 
-## Feature reduction and predictive importance
+## Feature selection and predictive importance
 
@@
 To suitably reduce the feature space and prevent overfitting, we implemented recursive feature elimination to estimate the optimal number of necessary features to include in the best fitting random forest model.
-The best performing subset was identified, ranging from 2 to the maximum number of features by powers of 2.
+The best performing subset was identified, ranging from 2 to the maximum number of features by power of 2.
 We then aggregated the predictive importance of the union of the optimal set of features across chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top ranked annotations for predicting TAD boundary regions.
 
-## Precise TAD boundary prediction at bp resolution
+## TAD boundary prediction at bp resolution
 
-Next, we aimed to investigate whether we could alleviate resolution limitations that plague conventional TAD calling algorithms.
-To do so, we extended our optimally built TAD prediction models to obtain predictions at base pair (bp) resolution.
-Naturally, when dealing with such fine resolution, there will exist collections of spatially close base pairs with similar predictor profiles (i.e.
-similar distances), and will thus yield similar predictions.
+To investigate whether we could alleviate limitations of resolution *r* of Hi-C data that limits the precision of conventional TAD calling algorithms, we applied our optimally built TAD prediction models for predicting TAD boundaries at base pair (bp) resolution.
+[???
+Write how your vector Y and annotation matrices change].
+Naturally, when dealing with such fine resolution, there will be spatially close base pairs with similar predictor profiles (i.e.
+similar overlap counts, distances).
 To guard against inflating the number of predicted TAD boundaries we developed a technique that combines both density-based spatial clustering (DBSCAN) and partitioning techniques to identify more precise TAD boundaries throughout the linear genome.
@@
 We defined these *k* clusters of PTBAs as *predicted TAD boundary regions* (PTBR).
+[???
+This deserves a schematic figure, before Figure 5.
+And part of it may be in Results] [???
+I would switch the notation.
+First, you detect REGIONS.
+They can be adjacent, clustered together, forming AREA.
+Within this area, you can do pam clustering, and identify POINT]
 
@@
 
-To evaluate if our predicted TAD boundaries are biologically significant we asssessed the signal strength obtained from key ChIP-Seq peak elements known to be enriched at TAD boundaries including CTCF, RAD21, SMC3, and ZNF143.
-To do so we used enriched heatmaps and Wilcoxon Rank-Sum tests to compare distances from selected ChiP-seq data to our predicted TAD boundaries compared to ARROWHEAD boundaries.
+To evaluate biological significance of our predictions, we evaluated the average signal profile of CTCF, RAD21, SMC3, and ZNF143 centered on the predicted TAD boundaries.
+The signal proviles were plotted using the `EnrichedHeatmap` R package [???
+Add version and citation].
+Furthermore, we compared the [???
+log2?] distance between TAD boundaries and CTCF, RAD21, SMC3, and ZNF143 binding sites using Wilcoxon Rank-Sum test.
 
-Furthermore, we assessed the conservation of our predicted TAD boundaries across cell types and compared with ARROWHEAD.
-Boundaries were flanked by resolution and overlaps were evaluated visually using venn diagrams and Jaccard Indices.
-Jaccard is a metric used to measure overlap between sets defined as
+Under the hypothesis that TAD boundaries are highly concerved across cell types [@dixon2012topological; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa], we assessed the conservation of our predicted TAD boundaries across cell types and prediction algorithms.
+Boundaries were flanked by resolution and overlaps were evaluated using Venn diagrams [???
+Package?] and Jaccard index defined as
 
@@
 
-where A and B are genomic regions.
+where A and B are sets of genomic regions.
 

### 2020-05-02 Manuscript/manuscript.Rmd
Results run-through

@@
 Is that correct?
-Or, max?] signal strength of the corresponding annotation (*Peak Signal Strength*), and the $log_{2}$ of the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
+Or, max?] signal strength of the corresponding annotation (*Peak Signal Strength*), and the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
+A log2-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
 
@@
 
-We developed a computational framework<!--, refered to as *TADRF*,--> aimed at determining the optimal set of data level characteristics necessary for topologically associated domain (TAD) boundary prediction using random forest classification models.
-We then leveraged our optimally built random forest to precisely predict the genomic coordinates of both TAD and loop boundaries at base pair resolution.
+We developed a computational framework<!--, refered to as *TADRF*,--> aimed at determining the optimal set of data level characteristics necessary for topologically associated domain (TAD) boundary prediction.
+Random forest machine learning algorithm was selected as the most robust to overfitting [???
+Read 10.1002/widm.1072 and 10.1002/widm.1301, elaborate, cite] We then leveraged our optimally built random forest to precisely predict the genomic coordinates of both TAD and loop boundaries at base pair resolution.
 
@@
 To demonstrate, we applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1).
-TADs were subsequently called using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
+TADs were subsequently called [???
+Did you call them?] using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
 For loop boundaries we opted to use boundaries obtained by the PEAKACHU tool for the GM12878 and K562 cell lines at 10 kb resolution [@salameh2019supervised].
+[???
+TAD and loop boundaries should be distinguished, to describe when we have all results]
 
-Boundary regions were defined as regions on the linear genome where a genomic bin contained a called boundary ($Y = 1$), while non-boundary regions were defined as genomic bins that did not contain a boundary ($Y = 0$) (Figure 1A).
-Under this construction, the number of non-boundary regions far exceeded the number of boundary regions.
-To cope with the imbalance among the classes of genomic bins, we evaluated three re-sampling techniques (in addition to no re-sampling) before predicting boundary regions.
+Boundary regions were defined as regions containing a called boundary ($Y = 1$), while non-boundary regions were defined as genomic bins that did not contain a boundary ($Y = 0$) (Figure 1A, see Methods).
+The total number of TADs, TAD boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 3).
+The number of non-boundary regions highly outnumbered boundary regions, and these results were consistent for loop boundaries (Supplementary Table 4).
+Such disproportional presence of examples in one class is known as "class imbalance" problem that negatively affects model performance [???
+Add refs].
+To address class imbalance, we evaluated the effect of three re-sampling techniques on prediction performance.
 *Random over-sampling* (ROS) was defined as sampling with replacement from boundary regions.
 *Random under-sampling* (RUS) was defined as sampling with replacement from non-boundary regions.
-Lastly, we considered *Synthetic minority over-sampling technique* (SMOTE), which is a combination of both random over- and under-sampling [@chawla2002smote].
+Lastly, we considered *Synthetic minority over-sampling technique* (SMOTE), which is a combination of both random over- and under-sampling [@chawla2002smote] (see Methods).
+These strategies allowed us to select the best performing model.
 
-A total of 78 cell line specific functional genomic annotations were used to build the feature space of downstream random forest models (Supplementary Table 2).
-The annotations could be broken down into three sets including histone modifications (HM), cis-regulatory elements (BroadHMM), and transcription factor binding sites (TFBS).
-Four different feature engineering procedures were developed for each genomic element (Figure 1 B).
-*Peak Signal* was defined as the [???include definition].
-Counts of overlaps (*Overlap Counts*, OC) were defined as the total number of genomic annotation regions that overlapped within a given genomic bin.
-Percents of overlaps (*Overlap Percent*, OP) were defined as the proportion of a bin overlapped by an annotation region.
-*Distance* was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations.
-A log2-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
-These feature engineering procedures were performed to improve boundary predictions by accounting for direct (OC), proportional (Signal/OP), and spatial (distance) relationships between TAD boundaries and genomic annotations.
+A total of 78 cell line specific functional genomic annotations were used to build the feature space of downstream random forest models.
+These annotations included BroadHMM shromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS, Supplementary Table 2).
+Four feature engineering procedures were developed for each genomic annotation (Figure 1B, see Methods) with the goal to improve boundary predictions by accounting for signal strength association (Signal), direct (OC), proportional (OP), and spatial (Distance) relationships between TAD boundaries and genomic annotations.
 
@@
 
-Thus, under our framework, we considered combinations of data for a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, with a specific engineered feature space *P = {Signal, OC, OP, Distance}*, and re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
+In summary, we considered combinations of data for a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, with a specific engineered feature space *P = {Signal, OC, OP, Distance}*, and re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
 Once the model inputs were established, a random forest classifier was trained on chromosome-specific genomic bins (excluding chromosome 9), *C = {CHR1, ..., CHR22}*, using 5-fold cross-validation.
@@
 <!--The results presented are for the ARROWHEAD boundaries, with PEAKACHU boundaries presented in the Supplementary material.
-Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |S| \times |C|$ different ensemble systems, totaling $2 \times 5 \times 4 \times 4 \times 21 (= 3360)$ models.-->
+Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |S| \times |C|$ different ensemble systems, totaling $2 \times 5 \times 4 \times 4 \times 21 (= 3360)$ models.--> [???
+When we have all results, Peakachu results will likely need to be described in parallel.
+They are about loops, theoretically different from TAD boundaries.
+For discussion]
 
@@
 
-Using ARROWHEAD, we obtained a total of 8052, 7676, 4670, 2349, and 1031 called TADs  across each resolution respectively (Table 1).
+<!-- Using ARROWHEAD, we obtained a total of 8052, 7676, 4670, 2349, and 1031 called TADs  across each resolution respectively (Table 1).
 From the called TADs, a total of 15468, 14253, 8363, 4224, and 1883 unique TAD boundaries were obtained (Table 1).
@@
 Boundary data summaries were similar for K562 cell line, as well as for PEAKACHU defined boundaries (Supplementary Tables 3-4).
+-->
 
@@
 
-Expectedly, when using data with class imbalance present, that is no re-sampling, the models exhibited low balanced accuracies, with very little variability among different resolutions (Figure 3).
-Similarly poor performances were found when using ROS as well.
+Expectedly, when using data with class imbalance present, that is, the data were used as-is, the models exhibited low balanced accuracies, with very little variability among different resolutions (Figure 3).
+Similarly, poor performances were found when using ROS as well.
 However, RUS and SMOTE re-sampling led to drastic improvement in performance, especially at higher resolutions.
-We found that RUS narrowly out performed SMOTE as the most optimal class balancing technique for all resolutions and predictor types.
+We found that RUS marginally outperformed SMOTE as the most optimal class balancing technique for all resolutions and predictor types.
 These results suggest that simple randomly under-sampling alone can drastically improve TAD boundary prediction.
-Additionally, we found that at higher resolutions, random forest classifiers built using a distance-type feature space yielded substantially higher MCCs when compared to the peak signal stength, overlap count, and overlap percent predictor types.
+
+Additionally, we found that at higher resolutions, random forest classifiers built using a distance-type feature space yielded substantially higher balanced accuracies when compared to the peak signal stength, overlap count, and overlap percent predictor types.
 As with comparing class balancing techniques, this improvement was less evident at lower resolutions.
 These results were found to be consistent for the K562 cell line (Supplementary Figure 2).
-Contrary to ARROWHEAD defined boundaries, random forest models built on PEAKACHU loop boundaries exhibited optimal performance when implemented on SMOTE re-sampled data for both GM12878 and K562 cell lines (Supplementary Figure 3).
-In summary, our computational framework showed that using random under-sampling, distance-type predictors, and Hi-C data at 5kb resolution yields an optimally performing cell line-specific random forest classification model for TAD boundary region prediction.
+Random forest models built on PEAKACHU loop boundaries with SMOTE resampling marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3).
+In summary, random under-sampling and SMOTE, distance-type predictors, and Hi-C data at 5kb resolution yields an optimally performing cell line-specific random forest classification model for TAD and loop boundary predictions.
 
@@
 
-We then aimed to compare the performances of genomic class-specifc models.
-In doing so, we evaluated performances for an optimally built random forest model using only histone modifications (HM), cis-regulatory elements (BroadHMM), and transcription factor binding sites (TFBS) separately.
-We found that models built solely on TFBS outperformed other class-specific models suggesting that TFBS are the primary drivers of TAD and loop boundary formation in both the GM12878 and K562 cell lines (Figure 4A; Supplementary Figures 4A,5A,6A).
+We hypothesized that the type of genomic annotations may affect the predictive performance.
+Using the aforementioned optimal settings, we built separate random forest models using BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS).
+We found that models built on TFBSs outperformed other annotation-specific models, and these results were consistent for loop boundaries (Figure 4A; Supplementary Figures 4A,5A,6A).
+These results suggest that TFBS are the primary drivers of TAD and loop boundary formation in both the GM12878 and K562 cell lines.
 
@@
 We sought to further optimize our TAD prediction model by performing recursive feature elimination to avoid overfitting and select only the most influential TFBS across all chromosomes.
-Under our framework, we were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figures 4B,5B,6B).
+We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figures 4B,5B,6B).
 However, given that we trained our model on chromosome-specific data, the most significant annotations were found to vary for each chromosome.
-To determine the most common TFBS, we clustered the predictive importances across chromosomes.
-We found that, similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD boundary regions for all chromosomes (Figure 4C; Supplementary Figures 4C,5C,6C).
-Therefore, our framework was able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@fudenberg2016formation; @alipour2012self].
+To determine transcription factors most important for boundary predigtion, we clustered the predictive importances of top eight significant TFs across chromosomes.
+We found that, similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD and loop boundaries for all chromosomes (Figure 4C; Supplementary Figures 4C,5C,6C).
 We further optimized our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
+In summary, our framework was able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@fudenberg2016formation; @alipour2012self].
 

### 2020-05-06 Manuscript/manuscript.Rmd
Add discussion point
methods edits (data sources section)

@@
 
-Biological replicate [???
-Didn't you use combined Arrowhead calls?
-Replicates seem irrelevant] Hi-C data were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1) for the GM12878 and K562 cell lines.
-The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from Hi-C data at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolution using the ARROWHEAD algorithm [@durand2016juicebox].
-TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all resolutions and cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line.
+Within this study we used both TAD boundary and loop boundary data derived from the publically available tools ARROWHEAD [@durand2016juicebox] and PEAKACHU [@salameh2019supervised] respectively.
+ARROWHEAD is part of the Juicer suite of tools for Hi-C data analysis and visualization.
+To obtain TAD boundaries we applied ARROWHEAD from downloaded primary Hi-C data for the GM12878 and K562 cell lines from Geo GSE63525 [@rao20143d] (libraries HIC001-HIC018 and HIC069-HIC074 for GM12878 and K562 respectively) produced with the MboI restriction enzyme (Supplementary Table 1).
+The contact matrices were constructed from all read pairs that uniquely align to the genome (MAPQ>0).
+The default tools for ARROWHEAD were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1).
+For chromatin loop boundaries, we used loops identified by PEAKACHU at 10 kb for the GM12878 and K562 cell line [@salameh2019supervised].
+Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop.
+Chromosome 9 was excluded from all downstream analyses due to the sparsity of the contact matrix at the 5 kb and 10 kb resolutions for the K562 cell line.
 [???
 Can you look up closer?
-If Arrowhead could call boundaries at 5kb, but not 10kb, it is strange] Cell type-specific genomic annotations (BroadHMM chromatin segmentations, histone modifications, and transcription factor binding sites) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (GRCh37/hg19 human genome assembly, Supplementary Table 2).
+If Arrowhead could call boundaries at 5kb, but not 10kb, it is strange; !!!https://groups.google.com/forum/#!searchin/3d-genomics/chr9$20from$20k562%7Csort:date].
+Cell type-specific genomic annotations (BroadHMM chromatin segmentations, histone modifications, and transcription factor binding sites) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (GRCh37/hg19 human genome assembly, Supplementary Table 2).
 [???
-Change "cis-regulatory elements (CRE)" to "C]
+Change "cis-regulatory elements (CRE)" to "C; !!!fixed]
 
@@
 
+<!-- Discuss advantages and disadvantages of Balanced Accuracy.
+The disadvantage is that we restrict TP to the originally detected TAD boundaries.
+While there are likely many more that couldn't be detected but are TP.
+We currently count them as FP -->
+
 # Conclusion
@@
 
-**Supplementary Table 1.** A complete list of the Hi-C data libraries obtained from GEO GSE63525 [@rao20143d] used to obtain the locations of topologically associating domains for ARROWHEAD, as well as the locations for the cell line specific .txt files of loop boundaries obtained by PEAKACHU [@salameh2019supervised].
+**Additional File 1**.
+An example script for applying the ARROWHEAD tool to in situ Hi-C data (HIC001-HIC018) for resolutions 5kb, 10kb, 25kb, 50kb, 100kb to obtain chromosome-specific TAD boundaries on the GM12878 cell line.
+
+**Supplementary Table 1.** A complete list of the Hi-C data libraries obtained from GEO GSE63525 [@rao20143d] used to obtain the locations of topologically associating domains for ARROWHEAD, as well as the locations for the cell line specific .txt files of loop boundaries obtained by PEAKACHU.
+[@salameh2019supervised].
 

### 2020-05-06 Manuscript/manuscript.Rmd
methods edits (computational framework for boundary prediction section)

@@
 
-## Computational framework for TAD boundary prediction
+## Computational framework for boundary prediction
 
@@
 To create shifted binning, the first chromosome-specific bin was set at half of the resolution *r*, and continued in congruent intervals of length *r* until the end of the chromosome (*mod r* + *r/2*).
-The shifted genomic bins, referred hereafted as bins for simplicity, were then defined as TAD boundary regions (*Y = 1*) if they contained a TAD boundary, and non-TAD boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification (Figure 1).
+The shifted genomic bins, referred hereafted as bins for simplicity, were then defined as boundary regions (*Y = 1*) if they contained a TAD (or loop) boundary, and non-boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification (Figure 1).
 
@@
 Is that correct?
-Or, max?] signal strength of the corresponding annotation (*Peak Signal Strength*), and the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
+Or, max?; !!!yes average] signal strength of the corresponding annotation (*Peak Signal Strength*), and the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
 A log2-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
+Note that model built using a *Peak Signal Strength* feature space where only composed of histone modifications and transcription factor binding sites.
+That is, they did not include BroadHMM chromatin segmentations.
 
-Chromosome-specific datasets used for modeling were composed of two components: the response vector $Y_N$, an indicator variable separating between TAD and non-TAD boundary regions, and the predictor-type specific data matrix, $X = X_1, X_2, ..., X_p$ [???
-Need to incorporate N, use proper math notation, maybe $\in$], where $n \in N$ is the number of bins (different for each chromosome) and $p$ is the number of genomic annotations (depends on the type of annotartions).
-Chromosome-specific dataseta were concatenated to form a whole genome dataset.
-The dataset was then split into a 7:3 ratio for training and testing, respectively.
+Chromosome-specific datasets used for modeling were composed of two components: the response vector $Y_{i}$, an indicator variable separating between boundary and non-boundary regions, and the predictor-type specific data matrix, $\textbf{X}_{ij}$, where $i \in \{ 1,2, \cdots,N \}$ ($N$ being the number of chromosome-specific bins) and $j \in \{ 1,2,\cdots,p \}$ ($p$ being the number of genomic annotations).
+<!--Chromosome-specific datasets were concatenated to form a whole genome dataset.
+The dataset was then split into a 7:3 ratio for training and testing, respectively.[!!!only comes into play with preciseTAD]-->
 

### 2020-05-06 Manuscript/manuscript.Rmd
methods edits (boundary prediction at bp resolution section)

@@
 
-Chromosome-specific datasets used for modeling were composed of two components: the response vector $Y_{i}$, an indicator variable separating between boundary and non-boundary regions, and the predictor-type specific data matrix, $\textbf{X}_{ij}$, where $i \in \{ 1,2, \cdots,N \}$ ($N$ being the number of chromosome-specific bins) and $j \in \{ 1,2,\cdots,p \}$ ($p$ being the number of genomic annotations).
+Chromosome-specific datasets used for modeling were composed of two components: the response vector $Y_{i}$, an indicator variable separating between boundary and non-boundary regions, and the predictor-type specific data matrix, $\textbf{X}_{ij}$, where $i \in \{ 1,2, \cdots,N \}$ ($N$ being the number of chromosome-specific bins) and $j \in \{ 1,2,\cdots,P \}$ ($P$ being the number of genomic annotations).
 <!--Chromosome-specific datasets were concatenated to form a whole genome dataset.
@@
 
-To assess the impact of class imbalance (CI), defined as the proportion of TAD boundary regions to non-TAD boundary regions, we evaluated three re-sampling techniques including *Random Over-Sampling (ROS)*, *Random Under-Sampling (RUS)*, and *Synthetic Minority Over-Sampling Technique (SMOTE)*.
+To assess the impact of class imbalance (CI), defined as the proportion of boundary regions to non-boundary regions, we evaluated three re-sampling techniques including *Random Over-Sampling (ROS)*, *Random Under-Sampling (RUS)*, and *Synthetic Minority Over-Sampling Technique (SMOTE)*.
 For ROS, the minority class was sampled with replacement to obtain the same number of data points in the majority class.
@@
 [???
-Of what size?]
+Of what size?; !!!not sure what question means]
 
@@
 Random forest classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, predictor types, and re-sampling techniques.
-Three-fold cross validation was used to tune the number of annotations, *p*, to consider at each node.
+Five-fold cross validation was used to tune the number of annotations, *p*, to consider at each node.
 The number of trees that were aggregated for each random forest model was set to the default, $n=500$.
 The performance of each model was compared using Balanced Accuracy (BA), defined as the average of sensitivity and specificity: [???
-Correct?]
+Correct?;!!!yep]
 
@@
 
-## TAD boundary prediction at bp resolution
+## Boundary prediction at bp resolution
 
@@
 [???
-Write how your vector Y and annotation matrices change].
+Write how your vector Y and annotation matrices change;!!!added].
+At this point, we opted to implement an optimally built whole genome random forest model.
+That is, a random forest model built on the optimal combination of data resolution (binning), predictor type (feature space), re-sampling technique (class balancing correction), and annotations (most informative genomic elements).
+That is, $Y$ has length $N$ where $N=n_1+n_2+\cdots+n_{22}$, the total number of bins across each chromosome.
+The data matrix $\textbf{X}$ has dimensions $N \times p_s$, where $p_s \subset P$, a subset of the most predictive genomic elements.
+
 Naturally, when dealing with such fine resolution, there will be spatially close base pairs with similar predictor profiles (i.e.
 similar overlap counts, distances).
-To guard against inflating the number of predicted TAD boundaries we developed a technique that combines both density-based spatial clustering (DBSCAN) and partitioning techniques to identify more precise TAD boundaries throughout the linear genome.
+To guard against inflating the number of predicted TAD boundaries we developed a technique that combines both density-based spatial clustering (DBSCAN) and partitioning techniques to identify precise TAD boundaries throughout the linear genome.
 

### 2020-05-06 Manuscript/manuscript.Rmd
methods edits (boundary prediction section)

@@
 
-We first established a *predicted TAD boundary area* (PTBA) as a collection of adjacent base pairs that have been identified as being a predicted TAD boundary with probability 1 according to the random forest model.
-We then implemented DBSCAN on the distance matrix (in base pairs) constructed from the midpoints of each PTBA using the R packacge *dbscan* (version 1.1-5) [@hahsler2019dbscan].
-To identify the optimal number of clusters, *k*, the eps parameter ($\epsilon$) was assigned as the respective data resolution.
-The heuristic being that PTBA midpoints with genomic distances less than resolution should occupy the same designated cluster.
+We first established a *predicted TAD boundary regions* (PTBR) as clusters of densitity-reachable base pairs which have been identified as being a predicted TAD boundary with probability 1 according to the random forest model using *DBSCAN* (version 1.1-5) [@hahsler2019dbscan].
+The DBSCAN algorithm takes two parameters, *eps* ($\epsilon$) and *MinPts*.
+The eps parameter ($\epsilon$) was assigned as the respective data resolution.
+The heuristic being that base pairs with genomic distances less than resolution should occupy the same designated cluster.
 The corresponding MinPts parameter was set to 3.
-We defined these *k* clusters of PTBAs as *predicted TAD boundary regions* (PTBR).
 [???
 This deserves a schematic figure, before Figure 5.
-And part of it may be in Results] [???
+And part of it may be in Results;!!!added PTBR to example of Figure 5 A] [???
 I would switch the notation.
@@
 They can be adjacent, clustered together, forming AREA.
-Within this area, you can do pam clustering, and identify POINT]
+Within this area, you can do pam clustering, and identify POINT;!!!editted, used term "region" instead of "area"]
+
+To precisely identify the PTBA most representative base pair of each PTBR we performed an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
+The midpoint of the corresponding cluster medoid, in this case a particular PTBR, was defined as a *preciseTAD boundary point* (PTBP).
+<!--Thus, the hierarchical structure of our defined predicted TAD boundary objects were as follows: PTBR > PTBA > PTBP.--> That is, each PTBR is a collection of base pairs, with the uniquely identified PTBP being the most representative base pair.
 
@@
 -->
-
-To precisely identify the PTBA most representative of each PTBR we performed an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
-The midpoint of the corresponding cluster medoid, in this case a particular PTBA, was defined as a *predicted TAD boundary point* (PTBP).
-Thus, the hierarchical structure of our defined predicted TAD boundary objects were as follows: PTBR > PTBA > PTBP.
-That is, each PTBR is a collection of PTBA midpoints, with the uniquely identified PTBP being the most representative midpoint within a clustered PTBR.
 

### 2020-05-06 Manuscript/manuscript.Rmd
methods edits (comparing called v predicted boundaries section)

@@
 
-## Comparing Called vs Predicted TAD boundaries
+## Comparing called vs predicted boundaries
 
-To evaluate biological significance of our predictions, we evaluated the average signal profile of CTCF, RAD21, SMC3, and ZNF143 centered on the predicted TAD boundaries.
-The signal proviles were plotted using the `EnrichedHeatmap` R package [???
-Add version and citation].
-Furthermore, we compared the [???
-log2?] distance between TAD boundaries and CTCF, RAD21, SMC3, and ZNF143 binding sites using Wilcoxon Rank-Sum test.
+Next, we evaluated the biological significance of our predicted boundaries with respect to the enrichment of several known molecular drivers of 3D chromatin architecture including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
+Enrichmed heatmaps were used to compare preciseTAD boundaries to both ARROWHEAD and PEAKACHU called boundaries using the `EnrichedHeatmap` R package (version 1.14.0) [@gu2018enrichedheatmap].
+Furthermore, we compared the $log_2$ [???
+log2?] distance between TAD boundaries and the same top predictive transcription factor binding sites using Wilcoxon Rank-Sum test.
 
 Under the hypothesis that TAD boundaries are highly concerved across cell types [@dixon2012topological; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa], we assessed the conservation of our predicted TAD boundaries across cell types and prediction algorithms.
-Boundaries were flanked by resolution and overlaps were evaluated using Venn diagrams [???
-Package?] and Jaccard index defined as
+Boundaries were flanked by resolution and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0) [???
+Package?;!!!added] and evaluated using the Jaccard index defined as
 
@@
 
-where A and B are sets of genomic regions.
+where A and B represent genomic regions created by flanking called and predicted boundaries.
 

### 2020-05-06 Scripts_for_results/02_creating_lineplot_of_balanced_accuracies.Rmd
edits to results scripts
edits

@@
 all_rfperfs <- rbind.data.frame(badata_gm12878_10kb)
-all_rfperfs$CL <- rep("GM12878", length(badata_gm12878_5kb))
+all_rfperfs$CL <- rep("GM12878", length(badata_gm12878_10kb))
 all_rfperfs$Resolution <- rep("10 kb", length(badata_gm12878_10kb))
@@
 
-ggplot(all_rfperfs_ba, aes(x=Predictor, y=Performance, fill=Resampling)) +
-  geom_bar(stat = "identity", position_dodge(0.9))+
+ggplot(d, aes(x=Predictor, y=Performance,fill=Resampling)) +
+    geom_bar(position=position_dodge(), stat="identity")+
     geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=1,
                   position=position_dodge(0.9)) +
-  facet_grid(. ~ Predictor)+
+    #facet_grid(. ~ Predictor)+
     theme_minimal() +
@@
 ```
+
+## ARROWHEAD WHOLE GENOME

### 2020-05-06 Scripts_for_results/09_visualizing_example_of_preciseTAD_predictions.Rmd
edits

@@
                       featureType="distance",
-                      CHR="CHR22",
+                      #CHR="CHR22",
                       CHR="CHR21",
@@
   geom_vline(data=predicteddata2, aes(xintercept=basenum, 
-                                      color="green"),
-             size=.75,
+                                      color="forestgreen"),
+             size=1,
              show.legend = TRUE)+
+  annotate(geom = "segment",x = 15492234, xend = 15519798,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
+  annotate(geom = "segment",x = 15635994, xend = 15792137,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
+  annotate(geom = "segment",x = 16147181, xend = 16244962,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
+  annotate(geom = "segment",x = 16845543, xend = 16958034,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
   xlab("Base Pair Coordinate") +
@@
   scale_color_manual(name = '', 
-                     values =c("blue", "green"),
+                     values =c("blue", "forestgreen"),
                      labels = c("ARROWHEAD",
                                 "preciseTAD"))+
+  scale_y_continuous(breaks=c(0,.5,1), limits=c(0,1))+
   theme_minimal() +

### 2020-05-08 Manuscript/manuscript.Rmd
edits to methods (enriched heatmap details) and results (paragraph 1)

@@
 
-We first established a *predicted TAD boundary regions* (PTBR) as clusters of densitity-reachable base pairs which have been identified as being a predicted TAD boundary with probability 1 according to the random forest model using *DBSCAN* (version 1.1-5) [@hahsler2019dbscan].
+We first established *predicted TAD boundary regions* (PTBR) as clusters of density-reachable base pairs which have been identified as being a predicted TAD boundary with probability 1 according to the random forest model using *DBSCAN* (version 1.1-5) [@hahsler2019dbscan].
 The DBSCAN algorithm takes two parameters, *eps* ($\epsilon$) and *MinPts*.
@@
 They can be adjacent, clustered together, forming AREA.
-Within this area, you can do pam clustering, and identify POINT;!!!editted, used term "region" instead of "area"]
-
-To precisely identify the PTBA most representative base pair of each PTBR we performed an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
+Within this area, you can do pam clustering, and identify POINT;!!!editted, used term "region" instead of "area"] To precisely identify the most representative base pair among each PTBR we performed an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
 The midpoint of the corresponding cluster medoid, in this case a particular PTBR, was defined as a *preciseTAD boundary point* (PTBP).
-<!--Thus, the hierarchical structure of our defined predicted TAD boundary objects were as follows: PTBR > PTBA > PTBP.--> That is, each PTBR is a collection of base pairs, with the uniquely identified PTBP being the most representative base pair.
+<!--Thus, the hierarchical structure of our defined predicted TAD boundary objects were as follows: PTBR > PTBA > PTBP.--> That is, each PTBR is a cluster of base pairs highly probable of being a boundary, with the uniquely identified PTBP being the most representative base pair.
 
@@
 Enrichmed heatmaps were used to compare preciseTAD boundaries to both ARROWHEAD and PEAKACHU called boundaries using the `EnrichedHeatmap` R package (version 1.14.0) [@gu2018enrichedheatmap].
-Furthermore, we compared the $log_2$ [???
-log2?] distance between TAD boundaries and the same top predictive transcription factor binding sites using Wilcoxon Rank-Sum test.
+For each boundary (both called and predicted), a 5000 bp flank was created on either side.
+The flanking was broken up into 50 bp segments, for a total of 100 windows on both sides of a given boundary.
+A coverage value was generated for each window with respect to a given ChIP-seq annotation, as the mean signal averaged by the width of the window, denoted by,
 
-Under the hypothesis that TAD boundaries are highly concerved across cell types [@dixon2012topological; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa], we assessed the conservation of our predicted TAD boundaries across cell types and prediction algorithms.
+$$v_{c} = \dfrac{\Sigma_{j}^{m} \Sigma_{i}^{n}x_{ij}w_{ij}}{L}$$
+where $x_{ij}$ is the total number of base pairs of annotation $i$ in window $j$ and $w_{ij}$ is the number of base pairs that overlap between annotation $i$ and window $j$.
+The denominator, $L$, is the width of the windows (here, $L=50$).
+The rows of the heatmaps are ordered by enriched scores.
+The enriched scores are calculated as the sum of coverage values weighted by the distance to the flanked boundary, denoted by
+
+$$s_{e} = \Sigma_{d=1}^{n_{1}}\left(\dfrac{x_{1d}* d}{n_{1}} \right) + \Sigma_{u=1}^{n_{2}}\left(\dfrac{x_{2u}* (n_{2} - u + 1)}{n_{2}} \right)$$
+where $n_{1}$ and $n_{2}$ represent the number of downstream and upstream coverage values to sum over. Here, $n_{1}=n_{2}=100$.
+
+Additionally, we compared the $log_2$ [???
+log2?;!!!added] distance between TAD boundaries and the same top predictive transcription factor binding sites using Wilcoxon Rank-Sum test.
+The alpha level of significance was set to 0.05.
+
+Furthermore, under the hypothesis that TAD boundaries are highly concerved across cell types [@dixon2012topological; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa], we assessed the conservation of our predicted TAD boundaries across cell types and prediction algorithms.
 Boundaries were flanked by resolution and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0) [???
@@
 We developed a computational framework<!--, refered to as *TADRF*,--> aimed at determining the optimal set of data level characteristics necessary for topologically associated domain (TAD) boundary prediction.
-Random forest machine learning algorithm was selected as the most robust to overfitting [???
-Read 10.1002/widm.1072 and 10.1002/widm.1301, elaborate, cite] We then leveraged our optimally built random forest to precisely predict the genomic coordinates of both TAD and loop boundaries at base pair resolution.
+We chose the random forest (RF) machine learning algorithm as our binary classification tool.
+The reason for choosing RF was two-fold: (1) In order to devise a tunable prediction rule in a supervised learning framework that was both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors with respect to their ability to predict boundary regions [@boulesteix2012overview] [???
+Read 10.1002/widm.1072 and 10.1002/widm.1301, elaborate, cite;!!!added first source].
+We then leveraged our optimally built RF to precisely predict the genomic coordinates of both TAD and loop boundaries at base pair resolution.
 
@@
 TADs were subsequently called [???
-Did you call them?] using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
+Did you call them?; !!!yes] using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
 For loop boundaries we opted to use boundaries obtained by the PEAKACHU tool for the GM12878 and K562 cell lines at 10 kb resolution [@salameh2019supervised].

### 2020-05-08 Scripts_for_results/09_visualizing_example_of_preciseTAD_predictions.Rmd
edits

@@
              show.legend = TRUE)+
-  annotate(geom = "segment",x = 15492234, xend = 15519798,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
-  annotate(geom = "segment",x = 15635994, xend = 15792137,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
-  annotate(geom = "segment",x = 16147181, xend = 16244962,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
-  annotate(geom = "segment",x = 16845543, xend = 16958034,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
+  #annotate(geom = "segment",x = 15492234, xend = 15519798,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
+  #annotate(geom = "segment",x = 15635994, xend = 15792137,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
+  #annotate(geom = "segment",x = 16147181, xend = 16244962,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
+  #annotate(geom = "segment",x = 16845543, xend = 16958034,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
   xlab("Base Pair Coordinate") +
@@
 
+ptbrdata <- data.frame(basenum=c(15770000:15780000))
+
+ggplot(predprobdata, aes(x=basenum, y=prob)) + 
+    geom_line(data=predprobdata, aes(x=basenum, y=prob), 
+              color='black',
+              size=.5)+
+    #geom_smooth(method = "loess",span = 0.0001, color="red")+
+    #geom_vline(data=predicteddata, aes(xintercept=basenum, 
+    #                                   color="red"),
+    #           size=.5,
+    #           show.legend = TRUE)+
+    geom_vline(data=calleddata, aes(xintercept=basenum, 
+                                    color="blue"),
+               size=2.5,
+               show.legend = FALSE)+
+    geom_vline(data=predicteddata2, aes(xintercept=basenum, 
+                                        color="forestgreen"),
+               size=2.5,
+               show.legend = FALSE)+
+    geom_vline(data=ptbrdata, aes(xintercept=basenum, 
+                                        color="yellow"),
+               size=1,
+               show.legend = TRUE,
+               alpha=.5)+
+    #annotate(geom = "segment",x = 15492234, xend = 15519798,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
+    #annotate(geom = "segment",x = 15635994, xend = 15792137,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
+    #annotate(geom = "segment",x = 16147181, xend = 16244962,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
+    #annotate(geom = "segment",x = 16845543, xend = 16958034,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
+    xlab("Base Pair Coordinate") +
+    ylab("Probability") + 
+    xlim(15776433-50000,15776433+50000)+
+    scale_color_manual(name = '', 
+                       values =c("blue", "forestgreen","yellow"),
+                       labels = c("ARROWHEAD",
+                                  "preciseTAD",
+                                  "PTBR"))+
+    #scale_y_continuous(breaks=c(0,.5,1), limits=c(0,1))+
+    #theme_minimal() +
+    theme_bw() +
+    theme(axis.text.x = element_text(size=15),
+          axis.text.y = element_blank(),
+          axis.title.x = element_blank(),
+          axis.title.y = element_blank(),
+          #strip.text.x = element_text(size = 15),
+          #panel.spacing = unit(2, "lines"),
+          panel.background = element_blank(),
+          panel.grid.minor = element_blank(),
+          panel.grid.major = element_blank(),
+          legend.text=element_blank(),
+          legend.title=element_blank(),
+          #plot.title = element_text(size=20),
+          legend.position = "bottom")
+
 ```

### 2020-05-08 Manuscript/manuscript.Rmd
added class imbalance references in results

@@
 We chose the random forest (RF) machine learning algorithm as our binary classification tool.
-The reason for choosing RF was two-fold: (1) In order to devise a tunable prediction rule in a supervised learning framework that was both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors with respect to their ability to predict boundary regions [@boulesteix2012overview] [???
+The reason for choosing RF was two-fold: (1) In order to devise a tunable prediction rule in a supervised learning framework that is both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors with respect to their ability to predict boundary regions [@boulesteix2012overview] [???
 Read 10.1002/widm.1072 and 10.1002/widm.1301, elaborate, cite;!!!added first source].
@@
 The number of non-boundary regions highly outnumbered boundary regions, and these results were consistent for loop boundaries (Supplementary Table 4).
-Such disproportional presence of examples in one class is known as "class imbalance" problem that negatively affects model performance [???
-Add refs].
+Such disproportional presence of examples in one class is known as a "class imbalance" problem that negatively affects model performance [@prati2011survey; @wei2013role] [???
+Add refs; !!!added].
 To address class imbalance, we evaluated the effect of three re-sampling techniques on prediction performance.

### 2020-05-08 Manuscript/manuscript.Rmd
added more detail in preciseTAD section of methods

@@
 ARROWHEAD is part of the Juicer suite of tools for Hi-C data analysis and visualization.
-To obtain TAD boundaries we applied ARROWHEAD from downloaded primary Hi-C data for the GM12878 and K562 cell lines from Geo GSE63525 [@rao20143d] (libraries HIC001-HIC018 and HIC069-HIC074 for GM12878 and K562 respectively) produced with the MboI restriction enzyme (Supplementary Table 1).
-The contact matrices were constructed from all read pairs that uniquely align to the genome (MAPQ>0).
+To obtain TAD boundaries we applied ARROWHEAD using downloaded primary Hi-C data from Geo GSE63525 [@rao20143d] for the GM12878 and K562 cell lines (libraries HIC001-HIC018 and HIC069-HIC074 for GM12878 and K562 respectively) produced with the MboI restriction enzyme (Supplementary Table 1).
+The contact matrices were constructed from all read pairs that uniquely aligned to the genome (MAPQ>0).
 The default tools for ARROWHEAD were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1).
-For chromatin loop boundaries, we used loops identified by PEAKACHU at 10 kb for the GM12878 and K562 cell line [@salameh2019supervised].
+For chromatin loop boundaries, we used loops identified by PEAKACHU at 10 kb for the GM12878 and K562 cell lines [@salameh2019supervised].
 Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop.
@@
 If Arrowhead could call boundaries at 5kb, but not 10kb, it is strange; !!!https://groups.google.com/forum/#!searchin/3d-genomics/chr9$20from$20k562%7Csort:date].
-Cell type-specific genomic annotations (BroadHMM chromatin segmentations, histone modifications, and transcription factor binding sites) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (GRCh37/hg19 human genome assembly, Supplementary Table 2).
+Cell line-specific genomic annotations were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] in the form of BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) (GRCh37/hg19 human genome assembly, Supplementary Table 2).
 [???
@@
 
-In Hi-C, each chromosome is binned into non-overlapping regions of the same length *r*, typically, 5kb and above.
+In Hi-C, each chromosome is binned into non-overlapping regions of the same length *r*, typically 5kb and above.
 The *r* parameter defines the resolution of Hi-C data.
@@
 
-Cell type-specific genomic annotations were used to build the predictor space for our TAD boundary prediction framework.
-Bins were annotated by the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average [???
+Cell type-specific genomic annotations were used to build the feature space for our boundary prediction framework.
+Bins were annotated by one of either the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average [???
 Is that correct?
-Or, max?; !!!yes average] signal strength of the corresponding annotation (*Peak Signal Strength*), and the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
-A log2-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
-Note that model built using a *Peak Signal Strength* feature space where only composed of histone modifications and transcription factor binding sites.
+Or, max?; !!!yes average] signal strength of the corresponding annotation (*Peak Signal Strength*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
+A $log_2$-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
+It should be noted that models built using a *Peak Signal Strength* feature space were only composed of histone modifications and transcription factor binding sites.
 That is, they did not include BroadHMM chromatin segmentations.
 
-Chromosome-specific datasets used for modeling were composed of two components: the response vector $Y_{i}$, an indicator variable separating between boundary and non-boundary regions, and the predictor-type specific data matrix, $\textbf{X}_{ij}$, where $i \in \{ 1,2, \cdots,N \}$ ($N$ being the number of chromosome-specific bins) and $j \in \{ 1,2,\cdots,P \}$ ($P$ being the number of genomic annotations).
+Chromosome-specific datasets used for modeling were composed of two components: the response vector $Y_{i}$, an indicator variable distinguishing boundary and non-boundary regions, and the predictor-type specific data matrix, $\textbf{X}_{ij}$, where $i \in \{ 1,2, \cdots,N \}$ ($N$ being the number of chromosome-specific bins) and $j \in \{ 1,2,\cdots,P \}$ ($P$ being the number of genomic annotations).
 <!--Chromosome-specific datasets were concatenated to form a whole genome dataset.
@@
 
-Random forest classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, predictor types, and re-sampling techniques.
-Five-fold cross validation was used to tune the number of annotations, *p*, to consider at each node.
-The number of trees that were aggregated for each random forest model was set to the default, $n=500$.
+Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, predictor types, and re-sampling techniques.
+Five-fold cross validation was used to tune the number of annotations, *P*, to consider at each node.
+The number of trees that were aggregated for each RF model was set to the default, $n=500$.
 The performance of each model was compared using Balanced Accuracy (BA), defined as the average of sensitivity and specificity: [???
@@
 
-where TP refers to the number of bins correctly identified as containing a TAD boundary (true positives), FP refers to the number of bins incorrectly identified as containing a TAD boundary (false positives), TN refers to the number of bins correctly identified as not containing a TAD boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a TAD boundary (false negatives).
+where TP refers to the number of bins correctly identified as containing a boundary (true positives), FP refers to the number of bins incorrectly identified as containing a boundary (false positives), TN refers to the number of bins correctly identified as not containing a boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a boundary (false negatives).
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
@@
 Many genomic annotations, notably architectural proteins, tend to exhibit an extensive pattern of colocalization (correlation) [@van2014insulator].
-To suitably reduce the feature space and prevent overfitting, we implemented recursive feature elimination to estimate the optimal number of necessary features to include in the best fitting random forest model.
+To suitably reduce the feature space and improve computational efficiency, while maintaining optimal performance, we implemented recursive feature elimination.
+In doing so, we estimated the near optimal number of necessary features to include in the best fitting RF model.
 The best performing subset was identified, ranging from 2 to the maximum number of features by power of 2.
-We then aggregated the predictive importance of the union of the optimal set of features across chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top ranked annotations for predicting TAD boundary regions.
+We then aggregated the predictive importance of the union of the optimal set of features across chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top ranked annotations for predicting boundary regions.
 
@@
 
-To investigate whether we could alleviate limitations of resolution *r* of Hi-C data that limits the precision of conventional TAD calling algorithms, we applied our optimally built TAD prediction models for predicting TAD boundaries at base pair (bp) resolution.
+To investigate whether we could alleviate resolution limitations of conventional TAD and loop boundary calling algorithms, we applied our RF model to predict boundaries from base pair (bp) resolution data.
 [???
 Write how your vector Y and annotation matrices change;!!!added].
-At this point, we opted to implement an optimally built whole genome random forest model.
+At this point, we opted to implement an optimally built whole genome RF model.
 That is, a random forest model built on the optimal combination of data resolution (binning), predictor type (feature space), re-sampling technique (class balancing correction), and annotations (most informative genomic elements).
-That is, $Y$ has length $N$ where $N=n_1+n_2+\cdots+n_{22}$, the total number of bins across each chromosome.
-The data matrix $\textbf{X}$ has dimensions $N \times p_s$, where $p_s \subset P$, a subset of the most predictive genomic elements.
+Here, $Y$ was of length $N$ where $N=n_1+n_2+\cdots+n_{22}$, the total number of bins across each chromosome.
+The data matrix $\textbf{X}$ had dimensions $N \times p_s$, where $p_s \subset P$, a subset of the most predictive genomic elements.
+Given that each chromosome is composed of tens, in some cases hundreds, of millions of base pairs, we used the same whole genome RF model to predict boundaries from chromosome-specific bp resolution data.
 
@@
 
-We first established *predicted TAD boundary regions* (PTBR) as clusters of density-reachable base pairs which have been identified as being a predicted TAD boundary with probability 1 according to the random forest model using *DBSCAN* (version 1.1-5) [@hahsler2019dbscan].
-The DBSCAN algorithm takes two parameters, *eps* ($\epsilon$) and *MinPts*.
-The eps parameter ($\epsilon$) was assigned as the respective data resolution.
+First, we extracted the vector $p_{n_{i}}$ that denoted the probability of being a boundary point for each chromosome-specific base pair from our RF model, where $n_{i}$ was the length of chromosome $i$.
+We then applied *DBSCAN* (version 1.1-5) to the matrix of pairwise distances between base pairs with $p_{n_{i}}=1$.
+The DBSCAN algorithm takes two parameters, *eps* ($\epsilon$) and *MinPts* [@hahsler2019dbscan].
+The eps parameter was assigned as the respective data resolution.
 The heuristic being that base pairs with genomic distances less than resolution should occupy the same designated cluster.
 The corresponding MinPts parameter was set to 3.
-[???
+The resulting clusters of density-reachable base pairs identified by DBSCAN were termed *predicted TAD boundary regions* (PTBR) [???
 This deserves a schematic figure, before Figure 5.
@@
 They can be adjacent, clustered together, forming AREA.
-Within this area, you can do pam clustering, and identify POINT;!!!editted, used term "region" instead of "area"] To precisely identify the most representative base pair among each PTBR we performed an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
-The midpoint of the corresponding cluster medoid, in this case a particular PTBR, was defined as a *preciseTAD boundary point* (PTBP).
-<!--Thus, the hierarchical structure of our defined predicted TAD boundary objects were as follows: PTBR > PTBA > PTBP.--> That is, each PTBR is a cluster of base pairs highly probable of being a boundary, with the uniquely identified PTBP being the most representative base pair.
+Within this area, you can do pam clustering, and identify POINT;!!!editted, used term "region" instead of "area"].
+To precisely identify the most representative base pair among each PTBR we performed an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
+Thusly, the corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative base pair within each clustered PTBR.
 

### 2020-05-08 Scripts_for_results/02_creating_lineplot_of_balanced_accuracies.Rmd
edits

@@
   ylab("Balanced Accuracy") + #ylim(-.1,.5) +
-  scale_color_discrete(name="Resampling Technique")+
+  scale_color_discrete(name="Resampling\nTechnique")+
   guides(shape=FALSE, linetype=FALSE)+
@@
   strip.text.y = element_text(size = 15),
-  #panel.spacing = unit(2, "lines"),
+  panel.spacing = unit(2, "lines"),
   legend.text=element_text(size=15),
@@
     ylab("Balanced Accuracy") + #ylim(-.1,.5) +
-  scale_color_discrete(name="Resampling Technique")+
+    scale_color_discrete(name="Resampling\nTechnique")+
     guides(shape=FALSE, linetype=FALSE)+
@@
     strip.text.y = element_text(size = 15),
-  #panel.spacing = unit(2, "lines"),
+    panel.spacing = unit(2, "lines"),
     legend.text=element_text(size=15),
@@
     legend.position="bottom")
-
 ```

### 2020-05-08 Manuscript/manuscript.Rmd
address ???

@@
 Chromosome 9 was excluded from all downstream analyses due to the sparsity of the contact matrix at the 5 kb and 10 kb resolutions for the K562 cell line.
-[???
-Can you look up closer?
-If Arrowhead could call boundaries at 5kb, but not 10kb, it is strange; !!!https://groups.google.com/forum/#!searchin/3d-genomics/chr9$20from$20k562%7Csort:date].
 Cell line-specific genomic annotations were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] in the form of BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) (GRCh37/hg19 human genome assembly, Supplementary Table 2).
-[???
-Change "cis-regulatory elements (CRE)" to "C; !!!fixed]
 
@@
 Cell type-specific genomic annotations were used to build the feature space for our boundary prediction framework.
-Bins were annotated by one of either the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average [???
-Is that correct?
-Or, max?; !!!yes average] signal strength of the corresponding annotation (*Peak Signal Strength*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
+Bins were annotated by one of either the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average signal strength of the corresponding annotation (*Peak Signal Strength*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
 A $log_2$-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
@@
 We restricted the algorithm to 100% over-sampling and 200% under-sampling, which creates perfectly balanced classes.
-[???
-Of what size?; !!!not sure what question means]
 
@@
 The number of trees that were aggregated for each RF model was set to the default, $n=500$.
-The performance of each model was compared using Balanced Accuracy (BA), defined as the average of sensitivity and specificity: [???
-Correct?;!!!yep]
+The performance of each model was compared using Balanced Accuracy (BA), defined as the average of sensitivity and specificity:
 
@@
 
-Additionally, we compared the $log_2$ [???
-log2?;!!!added] distance between TAD boundaries and the same top predictive transcription factor binding sites using Wilcoxon Rank-Sum test.
+Additionally, we compared the $log_2$ distance between TAD boundaries and the same top predictive transcription factor binding sites using Wilcoxon Rank-Sum test.
 The alpha level of significance was set to 0.05.
@@
 Furthermore, under the hypothesis that TAD boundaries are highly concerved across cell types [@dixon2012topological; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa], we assessed the conservation of our predicted TAD boundaries across cell types and prediction algorithms.
-Boundaries were flanked by resolution and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0) [???
-Package?;!!!added] and evaluated using the Jaccard index defined as
+Boundaries were flanked by resolution and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0) and evaluated using the Jaccard index defined as
 
@@
 We chose the random forest (RF) machine learning algorithm as our binary classification tool.
-The reason for choosing RF was two-fold: (1) In order to devise a tunable prediction rule in a supervised learning framework that is both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors with respect to their ability to predict boundary regions [@boulesteix2012overview] [???
-Read 10.1002/widm.1072 and 10.1002/widm.1301, elaborate, cite;!!!added first source].
+The reason for choosing RF was two-fold: (1) In order to devise a tunable prediction rule in a supervised learning framework that is both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors with respect to their ability to predict boundary regions [@boulesteix2012overview].
 We then leveraged our optimally built RF to precisely predict the genomic coordinates of both TAD and loop boundaries at base pair resolution.
@@
 To demonstrate, we applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1).
-TADs were subsequently called [???
-Did you call them?; !!!yes] using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
+TADs were subsequently called using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
 For loop boundaries we opted to use boundaries obtained by the PEAKACHU tool for the GM12878 and K562 cell lines at 10 kb resolution [@salameh2019supervised].
@@
 The number of non-boundary regions highly outnumbered boundary regions, and these results were consistent for loop boundaries (Supplementary Table 4).
-Such disproportional presence of examples in one class is known as a "class imbalance" problem that negatively affects model performance [@prati2011survey; @wei2013role] [???
-Add refs; !!!added].
+Such disproportional presence of examples in one class is known as a "class imbalance" problem that negatively affects model performance [@prati2011survey; @wei2013role].
 To address class imbalance, we evaluated the effect of three re-sampling techniques on prediction performance.

### 2020-05-08 Manuscript/manuscript.Rmd
Review ???

@@
 [???
-Write how your vector Y and annotation matrices change;!!!added].
+Write how your vector Y and annotation matrices change;!!!added ???You describe whole-genome model.
+It should have been described early on.
+Here, describe chromosome-specific bp-resolution model].
 At this point, we opted to implement an optimally built whole genome RF model.
@@
 First, we extracted the vector $p_{n_{i}}$ that denoted the probability of being a boundary point for each chromosome-specific base pair from our RF model, where $n_{i}$ was the length of chromosome $i$.
-We then applied *DBSCAN* (version 1.1-5) to the matrix of pairwise distances between base pairs with $p_{n_{i}}=1$.
+We then applied *DBSCAN* (version 1.1-5) to the matrix of pairwise distances [???
+Is that true?
+Matrix is 2-dimensional] between base pairs with $p_{n_{i}}=1$.
 The DBSCAN algorithm takes two parameters, *eps* ($\epsilon$) and *MinPts* [@hahsler2019dbscan].
-The eps parameter was assigned as the respective data resolution.
+The eps parameter was assigned as the respective data resolution [???
+Meaning?].
 The heuristic being that base pairs with genomic distances less than resolution should occupy the same designated cluster.
-The corresponding MinPts parameter was set to 3.
+The corresponding MinPts parameter was set to 3 [???
+Meaning?].
 The resulting clusters of density-reachable base pairs identified by DBSCAN were termed *predicted TAD boundary regions* (PTBR) [???
-This deserves a schematic figure, before Figure 5.
-And part of it may be in Results;!!!added PTBR to example of Figure 5 A] [???
-I would switch the notation.
-First, you detect REGIONS.
-They can be adjacent, clustered together, forming AREA.
-Within this area, you can do pam clustering, and identify POINT;!!!editted, used term "region" instead of "area"].
+Use simple words: "boundary region" (many bases clustered by DBSCAN), then "boundary base" (selected by PAM)].
 To precisely identify the most representative base pair among each PTBR we performed an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].

### 2020-05-13 Scripts_for_results/05_creating_importance_plot.Rmd
swapped Heatmap for heatmap.2

@@
 
+Heatmap(t(rfe.set.mat),
+        col=my_palette,
+        border=TRUE,
+        cluster_rows=FALSE,
+        clustering_distance_columns = "euclidean",
+        clustering_method_columns = "complete",
+        show_row_names = FALSE,
+        column_names_rot = 90,
+        column_names_centered = FALSE,
+        show_heatmap_legend = FALSE,
+        heatmap_legend_param = list(title = "Predictive\nImportance"),
+        rect_gp = gpar(col = "black", lwd = 1),
+        column_dend_side = "bottom",column_names_side = "bottom")
 ```
@@
 
+Heatmap(t(rfe.set.mat),
+        col=my_palette,
+        border=TRUE,
+        cluster_rows=FALSE,
+        clustering_distance_columns = "euclidean",
+        clustering_method_columns = "complete",
+        show_row_names = FALSE,
+        column_names_rot = 90,
+        column_names_centered = FALSE,
+        show_heatmap_legend = FALSE,
+        heatmap_legend_param = list(title = "Predictive\nImportance"),
+        rect_gp = gpar(col = "black", lwd = 1),
+        column_dend_side = "top",column_names_side = "top")
 ```

### 2020-05-13 Manuscript/manuscript.Rmd
combining arrowhead and peakachu; methods edits

@@
 Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, predictor types, and re-sampling techniques.
-Five-fold cross validation was used to tune the number of annotations, *P*, to consider at each node.
-The number of trees that were aggregated for each RF model was set to the default, $n=500$.
+Five-fold cross validation was used to tune the number of annotations, *P*, to consider at each node (*mtry*).
+The number of trees (*ntree*) that were aggregated for each RF model was set to 500.
+The minimum number of observations per root node (*nodesize*) was set to 1.
 The performance of each model was compared using Balanced Accuracy (BA), defined as the average of sensitivity and specificity:
@@
 
-To investigate whether we could alleviate resolution limitations of conventional TAD and loop boundary calling algorithms, we applied our RF model to predict boundaries from base pair (bp) resolution data.
-[???
+To investigate whether we could alleviate resolution limitations of conventional TAD and chromatin  loop calling tools, we developed *preciseTAD*, an algorithm that leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base pair (bp) resolution.
+To demonstrate, we opted to implement an optimally built whole genome RF model.
+That is, a random forest model built on the optimal combination of data resolution (binning), predictor type (feature space), re-sampling technique (class balancing correction), and annotations (most informative genomic elements) [???
 Write how your vector Y and annotation matrices change;!!!added ???You describe whole-genome model.
@@
 Here, describe chromosome-specific bp-resolution model].
-At this point, we opted to implement an optimally built whole genome RF model.
-That is, a random forest model built on the optimal combination of data resolution (binning), predictor type (feature space), re-sampling technique (class balancing correction), and annotations (most informative genomic elements).
 Here, $Y$ was of length $N$ where $N=n_1+n_2+\cdots+n_{22}$, the total number of bins across each chromosome.
 The data matrix $\textbf{X}$ had dimensions $N \times p_s$, where $p_s \subset P$, a subset of the most predictive genomic elements.
-Given that each chromosome is composed of tens, in some cases hundreds, of millions of base pairs, we used the same whole genome RF model to predict boundaries from chromosome-specific bp resolution data.
+The whole genome RF was tuned sequentially.
+First, *mtry*=$\sqrt{p}$ and *nodesize*=1, then we allowed *ntree* to range from 10 to 1000 by values of 10, and determined where the balanced accuracies converged, say at $t$.
+Next, we set *mtry*=$\sqrt{p}$ and *ntree*=$t$ and allowed *nodesize* to range from 1 to 21 by values of 2, again evaluating where performances converged.
+<!--Given that each chromosome is composed of tens, in some cases hundreds, of millions of base pairs,--> We then used the same whole genome RF model to predict boundaries from chromosome-specific bp resolution data.
 
 Naturally, when dealing with such fine resolution, there will be spatially close base pairs with similar predictor profiles (i.e.
-similar overlap counts, distances).
-To guard against inflating the number of predicted TAD boundaries we developed a technique that combines both density-based spatial clustering (DBSCAN) and partitioning techniques to identify precise TAD boundaries throughout the linear genome.
-
-First, we extracted the vector $p_{n_{i}}$ that denoted the probability of being a boundary point for each chromosome-specific base pair from our RF model, where $n_{i}$ was the length of chromosome $i$.
-We then applied *DBSCAN* (version 1.1-5) to the matrix of pairwise distances [???
+similar overlap counts, distances, etc.).
+*preciseTAD* guards against inflating the number of predicted boundaries by combining both density-based spatial clustering (DBSCAN) and partitioning techniques to identify precise TAD (or loop) boundaries throughout the linear genome.
+First the vector, $p_{n_{i}}$, denoting each base pair's probability of being a boundary point from the RF model, was extracted, where $n_{i}$ represents the length of chromosome $i$.
+Next, *DBSCAN* (version 1.1-5) was applied to the matrix of pairwise genomic distances [???
 Is that true?
@@
 Meaning?].
-The resulting clusters of density-reachable base pairs identified by DBSCAN were termed *predicted TAD boundary regions* (PTBR) [???
+The resulting clusters of density-reachable base pairs identified by DBSCAN were termed *preciseTAD boundary regions* (PTBR) [???
 Use simple words: "boundary region" (many bases clustered by DBSCAN), then "boundary base" (selected by PAM)].
-To precisely identify the most representative base pair among each PTBR we performed an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
+To precisely identify a single base pair among each PTBR, *preciseTAD* then implements an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
 Thusly, the corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative base pair within each clustered PTBR.
@@
 
-where A and B represent genomic regions created by flanking called and predicted boundaries.
+where A and B represent genomic regions created by flanking called and predicted boundaries. That is, the set of shared boundaries divided by the total number of unique boundaries.
 
@@
 Using the aforementioned optimal settings, we built separate random forest models using BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS).
-We found that models built on TFBSs outperformed other annotation-specific models, and these results were consistent for loop boundaries (Figure 4A; Supplementary Figures 4A,5A,6A).
+We found that models built on TFBSs outperformed other annotation-specific models, and these results were consistent for loop boundaries, for both cell lines (Figure 4A; Supplementary Figures 4A).
 These results suggest that TFBS are the primary drivers of TAD and loop boundary formation in both the GM12878 and K562 cell lines.
@@
 We sought to further optimize our TAD prediction model by performing recursive feature elimination to avoid overfitting and select only the most influential TFBS across all chromosomes.
-We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figures 4B,5B,6B).
+We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figures 4B).
 However, given that we trained our model on chromosome-specific data, the most significant annotations were found to vary for each chromosome.
-To determine transcription factors most important for boundary predigtion, we clustered the predictive importances of top eight significant TFs across chromosomes.
-We found that, similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD and loop boundaries for all chromosomes (Figure 4C; Supplementary Figures 4C,5C,6C).
+To determine transcription factors most important for boundary prediction, we clustered the predictive importances of the top eight significant TFs across chromosomes.
+We found that, similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD and loop boundaries for all chromosomes (Figure 4C; Supplementary Figures 4C).
 We further optimized our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
@@
 
-![**Assessing top ranked transcription factors in TAD boundary prediction for GM12878.** (A) Barplots comparing performances of models using specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (BroadHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model containing all three classes (ALL; purple).
+![**Assessing top ranked transcription factors in TAD and loop boundary prediction for GM12878.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using specific classes of functional genomic elements as the feature space including histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.
 Error bars represent standard deviation from the cross-validated accuracy across each chromosome.
-(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.](Figures/figure4_annots_specifc_rfe_importances.png)
+(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.](Figures/figure4_annots_specifc_rfe_importances_arrowhead_peakachu.png)
 
@@
 The reason for this was because of the improved performance that was exhibited for a whole genome random forest compared to aggregated chromosome-specific models (Supplementary Figure 7).
+When tuning the full genome RF we found that performances converged when *mtry*=2, *ntree*=100, and *nodesize*=???.
 
@@
 **Supplementary Figure 4.
-Assessing top ranked transcription factors in TAD boundary prediction for K562.** (A) Barplots comparing performances of models built using ARROWHEAD boundaries on specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (BroadHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model containing all three classes (ALL; purple).
-(B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.
-Error bars represent standard deviation from the cross-validated accuracy across each chromosome.
-(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.
-
-**Supplementary Figure 5.
-Assessing top ranked transcription factors in loop boundary prediction for GM12878.** (A) Barplots comparing performances of models built using PEAKACHU boundaries on specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (BroadHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model containing all three classes (ALL; purple).
-(B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.
-Error bars represent standard deviation from the cross-validated accuracy across each chromosome.
-(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.
-
-**Supplementary Figure 6.
-Assessing top ranked transcription factors in loop boundary prediction for K562.** (A) Barplots comparing performances of models built using PEAKACHU boundaries on specific classes of functional genomic elements as the feature space including histone modifications (HM; red), cis-regulated elements (BroadHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model containing all three classes (ALL; purple).
+Assessing top ranked transcription factors in TAD and loop boundary prediction for K562.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using specific classes of functional genomic elements as the feature space including histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.

### 2020-05-15 Scripts_for_results/10_evaluating_jaccard_indices.Rmd
initial commit

---
title: "Evaluating Jaccard Indices"
author: "Spiro Stilianoudakis"
date: "5/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages and functions

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

# ARROWHEAD

## GM12878

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds_gm12878 <- do.call("c", true_bound_list)
all_pred_bounds_gm12878 <- do.call("c", pred_bound_list)

all_true_bounds_gm12878_arrowhead <- flank(all_true_bounds_gm12878, 5000, both=TRUE)
all_pred_bounds_gm12878_arrowhead <- flank(all_pred_bounds_gm12878, 5000, both=TRUE)

```

## K562

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds_k562 <- do.call("c", true_bound_list)
all_pred_bounds_k562 <- do.call("c", pred_bound_list)

all_true_bounds_k562_arrowhead <- flank(all_true_bounds_k562, 5000, both=TRUE)
all_pred_bounds_k562_arrowhead <- flank(all_pred_bounds_k562, 5000, both=TRUE)

```

## Jaccard Indices

```{r}
#original
jaccard_o <- numeric()
for(i in 1:length(chrs)){
  g1 <- all_true_bounds_gm12878_arrowhead[which(as.character(seqnames(all_true_bounds_gm12878_arrowhead))==tolower(chrs[i]))]
  g2 <- all_true_bounds_k562_arrowhead[which(as.character(seqnames(all_true_bounds_k562_arrowhead))==tolower(chrs[i]))]

  co <- countOverlaps(g1,g2)

  int <- length(co[which(co>0)])

  uni <- length(g1) + length(g2) - int

  jaccard_o[i] <- int/uni
}
summary(jaccard_o)

#preciseTAD
jaccard_p <- numeric()
for(i in 1:length(chrs)){
  g1 <- all_pred_bounds_gm12878_arrowhead[which(as.character(seqnames(all_pred_bounds_gm12878_arrowhead))==tolower(chrs[i]))]
  g2 <- all_pred_bounds_k562_arrowhead[which(as.character(seqnames(all_pred_bounds_k562_arrowhead))==tolower(chrs[i]))]

  co <- countOverlaps(g1,g2)

  int <- length(co[which(co>0)])

  uni <- length(g1) + length(g2) - int

  jaccard_p[i] <- int/uni
}
summary(jaccard_p)

wilcox.test(jaccard_o,jaccard_p)
```

# PEAKACHU

## GM12878

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds_gm12878 <- do.call("c", true_bound_list)
all_pred_bounds_gm12878 <- do.call("c", pred_bound_list)

all_true_bounds_gm12878_peakachu <- flank(all_true_bounds_gm12878, 10000, both=TRUE)
all_pred_bounds_gm12878_peakachu <- flank(all_pred_bounds_gm12878, 10000, both=TRUE)

```

## K562

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]

}

all_true_bounds_k562 <- do.call("c", true_bound_list)
all_pred_bounds_k562 <- do.call("c", pred_bound_list)

all_true_bounds_k562_peakachu <- flank(all_true_bounds_k562, 10000, both=TRUE)
all_pred_bounds_k562_peakachu <- flank(all_pred_bounds_k562, 10000, both=TRUE)

```

## Jaccard Indices

```{r}
#original
jaccard_o <- numeric()
for(i in 1:length(chrs)){
  g1 <- all_true_bounds_gm12878_peakachu[which(as.character(seqnames(all_true_bounds_gm12878_peakachu))==tolower(chrs[i]))]
  g2 <- all_true_bounds_k562_peakachu[which(as.character(seqnames(all_true_bounds_k562_peakachu))==tolower(chrs[i]))]

  co <- countOverlaps(g1,g2)

  int <- length(co[which(co>0)])

  uni <- length(g1) + length(g2) - int

  jaccard_o[i] <- int/uni
}
summary(jaccard_o)

#preciseTAD
jaccard_p <- numeric()
for(i in 1:length(chrs)){
  g1 <- all_pred_bounds_gm12878_peakachu[which(as.character(seqnames(all_pred_bounds_gm12878_peakachu))==tolower(chrs[i]))]
  g2 <- all_pred_bounds_k562_peakachu[which(as.character(seqnames(all_pred_bounds_k562_peakachu))==tolower(chrs[i]))]

  co <- countOverlaps(g1,g2)

  int <- length(co[which(co>0)])

  uni <- length(g1) + length(g2) - int

  jaccard_p[i] <- int/uni
}
summary(jaccard_p)

wilcox.test(jaccard_o,jaccard_p)
```

### 2020-05-15 Scripts_for_results/02_creating_lineplot_of_balanced_accuracies.Rmd
added panel spacing
edits

@@
 all_rfperfs <- rbind.data.frame(badata_k562_10kb)
-all_rfperfs$CL <- rep("K562", length(badata_k562_5kb))
+all_rfperfs$CL <- rep("K562", length(badata_k562_10kb))
 all_rfperfs$Resolution <- rep("10 kb", length(badata_k562_10kb))
@@
 ## ARROWHEAD WHOLE GENOME
+
+```{r}
+t_whole_arrowhead_gm12878 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb/results_by_chr/WHOLE/rus/distance/TADRF_3.rds")
+t_whole_arrowhead_gm12878 <- t_whole_arrowhead_gm12878[[3]][10,2]
+t_whole_arrowhead_k562 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/K562/5kb/results_by_chr/WHOLE/rus/distance/TADRF_3.rds")
+t_whole_arrowhead_k562 <- t_whole_arrowhead_k562[[3]][10,2]
+
+t_whole_peakachu_gm12878 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/GM12878/10kb/results_by_chr/WHOLE/rus/distance/TADRF_3_peakachu.rds")
+t_whole_peakachu_gm12878 <- t_whole_peakachu_gm12878[[3]][10,2]
+t_whole_peakachu_k562 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/K562/10kb/results_by_chr/WHOLE/rus/distance/TADRF_3_peakachu.rds")
+t_whole_peakachu_k562 <- t_whole_peakachu_k562[[3]][10,2]
+
+t_chr_arrowhead_gm12878 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/miscellaneous/saved_rds_files/all_rfperfs_ba_arrowhead_gm12878.rds")
+t_chr_arrowhead_k562 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/miscellaneous/saved_rds_files/all_rfperfs_ba_arrowhead_k562.rds")
+t_chr_peakachu_gm12878 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/miscellaneous/saved_rds_files/all_rfperfs_ba_peakachu_gm12878.rds")
+t_chr_peakachu_k562 <- readRDS("/home/stilianoudakisc/TAD_data_analysis/miscellaneous/saved_rds_files/all_rfperfs_ba_peakachu_k562.rds")
+
+all_rfperfs_chr_vs_whole_arrowhead_peakachu <- data.frame(BA=c(t_whole_arrowhead_gm12878,
+                      t_whole_arrowhead_k562,
+					  t_whole_peakachu_gm12878,
+					  t_whole_peakachu_k562,
+					  as.numeric(t_chr_arrowhead_gm12878[12,4]),
+					  as.numeric(t_chr_arrowhead_k562[12,4]),
+					  as.numeric(t_chr_peakachu_gm12878[12,4]),
+					  as.numeric(t_chr_peakachu_k562[12,4])),
+				CL=rep(c("GM12878","K562"),4),
+				Tool=rep(c("ARROWHEAD","ARROWHEAD","PEAKACHU","PEAKACHU"),2),
+				Method=c(rep("Whole",4),rep("Per CHR",4)))
+
+#all_rfperfs_chr_vs_whole_arrowhead_peakachu <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/all_rfperfs_chr_vs_whole_arrowhead_peakachu.rds")
+
+ggplot(all_rfperfs_chr_vs_whole_arrowhead_peakachu, 
+       aes(x=Method, y=BA, fill=Method)) +
+  geom_bar(stat = "identity")+
+  facet_grid(CL ~ Tool)+
+  theme_minimal() +
+  theme_bw()+
+  xlab("Method") + 
+  ylab("Balanced Accuracy") + 
+  guides(fill=FALSE)+
+  theme(axis.text.x = element_text(size=15,
+                                   angle = 45, 
+                                   #margin = ggplot2::margin(t = 35),
+                                   hjust = 1
+  ),
+  axis.text.y = element_text(size = 15),
+  axis.title.x = element_text(size = 20),
+  axis.title.y = element_text(size = 20),
+  strip.text.x = element_text(size = 15),
+  strip.text.y = element_text(size = 15),
+  #panel.spacing = unit(2, "lines"),
+  legend.text=element_text(size=15),
+  legend.title=element_text(size=20),
+  plot.title = element_text(size=20),
+  legend.position="bottom")
+```

### 2020-05-15 Scripts_for_results/04_creating_rfe_lineplot.Rmd
edits

@@
     rfeModelResults <- rfeModelResultsList[[1]]
-    rfeModelResults <- rfeModelResults[,c(1,11)]
+    rfeModelResults <- rfeModelResults[,c(1,4:5)]
     rfeModelResults$CL <- i
@@
 }
-
+rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
 rfeperchr_summ <- rfeperchr %>%
   dplyr::group_by(Variables) %>%
-  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
-                   PerformanceSD = sd(Accuracy, na.rm = TRUE))
+  dplyr::summarise(Performance = mean(BA, na.rm = TRUE),
+                   PerformanceSD = sd(BA, na.rm = TRUE))
 

### 2020-05-15 Scripts_for_results/06_creating_enriched_heatmaps.Rmd
edits

@@
 chrs <- paste0("CHR", c(1:8,10:22))
-chrs <- paste0("CHR", c(2:8,10:15,17:22))
+chrs <- paste0("CHR", c(21:22))
 for(i in 1:length(chrs)){

### 2020-05-15 Scripts_for_results/07_creating_distance_to_chipseq.Rmd
edits

@@
 chrs <- paste0("CHR", c(1:8,10:22))
+chrs <- paste0("CHR", c(21:22))
 for(i in 1:length(chrs)){

### 2020-05-15 Scripts_for_results/08_creating_venn_diagrams.Rmd
edits

@@
 
-all_true_bounds_gm12878 <- flank(all_true_bounds_gm12878, 5000, both=TRUE)
-all_pred_bounds_gm12878 <- flank(all_pred_bounds_gm12878, 5000, both=TRUE)
+all_true_bounds_gm12878 <- flank(all_true_bounds_gm12878, 10000, both=TRUE)
+all_pred_bounds_gm12878 <- flank(all_pred_bounds_gm12878, 10000, both=TRUE)
 
@@
 
-all_true_bounds_k562 <- flank(all_true_bounds_k562, 5000, both=TRUE)
-all_pred_bounds_k562 <- flank(all_pred_bounds_k562, 5000, both=TRUE)
+all_true_bounds_k562 <- flank(all_true_bounds_k562, 10000, both=TRUE)
+all_pred_bounds_k562 <- flank(all_pred_bounds_k562, 10000, both=TRUE)
 

### 2020-05-15 Manuscript/manuscript.Rmd
edits to results section; added full results including tables and figures; some place holders for figures

@@
 The data matrix $\textbf{X}$ had dimensions $N \times p_s$, where $p_s \subset P$, a subset of the most predictive genomic elements.
-The whole genome RF was tuned sequentially.
-First, *mtry*=$\sqrt{p}$ and *nodesize*=1, then we allowed *ntree* to range from 10 to 1000 by values of 10, and determined where the balanced accuracies converged, say at $t$.
-Next, we set *mtry*=$\sqrt{p}$ and *ntree*=$t$ and allowed *nodesize* to range from 1 to 21 by values of 2, again evaluating where performances converged.
-<!--Given that each chromosome is composed of tens, in some cases hundreds, of millions of base pairs,--> We then used the same whole genome RF model to predict boundaries from chromosome-specific bp resolution data.
+The *nodesize* and *ntree* parameters were tuned sequentially using a grid search across values from ???-???
+by ???
+and from ???-???
+by ???
+for each, respectively.
+We then used the same optimized whole genome RF model to predict boundaries from chromosome-specific bp resolution data.
 
@@
 
-Additionally, we compared the $log_2$ distance between TAD boundaries and the same top predictive transcription factor binding sites using Wilcoxon Rank-Sum test.
-The alpha level of significance was set to 0.05.
+Additionally, we compared the median $log_2$ distances between TAD boundaries and the same top predictive transcription factor binding sites using Wilcoxon Rank-Sum test.
 
@@
 
-where A and B represent genomic regions created by flanking called and predicted boundaries. That is, the set of shared boundaries divided by the total number of unique boundaries.
+where A and B represent genomic regions created by flanking called and predicted boundaries.
+That is, the set of shared boundaries divided by the total number of unique boundaries.
+Wilcoxon rank sum tests were used to compare chromosome-specific jaccard indices across cell lines, between *preciseTAD* boundaries and both ARROWHEAD and PEAKACHU boundaries respectively.
+The alpha level of significance was set to 0.05 for all statistical tests.
 
@@
 
-Here, we opted to implement preciseTAD using an optimally built whole genome random forest model.
+At this point, we opted to implement preciseTAD using an optimally built whole genome random forest model.
 That is, a random forest model built on 5 kb defined genomic bins, with random under-sampling, and distance-type predictors for the top informative TFBS (CTCF, RAD21, SMC3, and ZNF143).
-The reason for this was because of the improved performance that was exhibited for a whole genome random forest compared to aggregated chromosome-specific models (Supplementary Figure 7).
-When tuning the full genome RF we found that performances converged when *mtry*=2, *ntree*=100, and *nodesize*=???.
+The reason for this was because of the improved performance that was exhibited for a whole genome random forest compared to aggregated chromosome-specific models (Supplementary Figure 5).
+When tuning the full genome RF we found that performances converged when *mtry*=2, *ntree*=250, and *nodesize*=???
+(Supplementary Figures 6-7).
 
-???stopped here; waiting to predicted tad boundaries results
-
-<!--
-We first used ROC analysis to obtain an optimal probability threshold for defining potential predicted TAD boundaries.
-We reported an average threshold of ???
-(SD=???) among the 21 autosomal chromosomes that were analyzed (mean=???, SD=???
-for K562).
-We referred to collections of chromosome-specific base pairs that exceeded this threshold when used to validate our *TADRF* model as *predicted TAD boundary areas* (PTBA), given that collections of adjacent base pairs tended to exhibit similar prediction profiles.
-We found that there were a total of ???
-PTBA, containing an average of ???
-base pairs each (???
-PTBA for K562; mean base pairs=???, SD=???).
-*preciseTAD* then implements complete linkage hierarchical clustering on the dissimilarity matrix constructed from the pairwise distances (in base pairs) among the midpoints of each chromsome-specific PTBA.
-Using the silhouette score (see methods), we reported a total of k=???
-chromosome-specific clusters (k=???
-for K562).
-We referred to these *k* clusters as *predicted TAD boundary regions* (PTBR).
-That is, each PTBR contained the midpoints of multiple PTBA.
-Lastly, given each PTBR, *preciseTAD* uses CLARA partitioning to obtain the most representative midpoint.
-We referred to this as the *predicted TAD boundary point* (PTBP).
-These PTBP were identified as the most representative base pair among each PTBR.
-*preciseTAD* was able to identify a total of ???
-PTBP across each chromosome.
-We reported less predicted TAD boundaries than ARROWHEAD at 10 kb (Table 1).
+When built using ARROWHEAD, at 5 kb, *preciseTAD* was able to predict a total of ???
+and ???
+boundaries for GM12878 and K562 cell lines respectively.
+We reported less predicted TAD boundaries than ARROWHEAD (Table 1, Supplementary Table 3).
 This is attributed to ARROWHEAD's inherent inflation of called TAD boundaries, especially near fuzzy areas along the diagonal of Hi-C contact matrices (Figure 5A).
 Likewise, under the framework of *preciseTAD*, any two TADs are inherently demarcated by only one predicted TAD boundary, leading to comparatively less TAD boundaries.
-We also find that predicted TAD boundaries identified by *preciseTAD* were much more likely to demarcate high concentrations of inter-chromosomal contacts among Hi-C contact matrices (Figure 5A).
-[???include a result that demonstrates this; discuss in meeting]
--->
+Visually speaking, we also found that predicted TAD boundaries identified by *preciseTAD* were much more likely to demarcate high concentrations of inter-chromosomal contacts among Hi-C contact matrices (Figure 5A).
+When built using PEAKACHU loop boundaries, *preciseTAD* was able to predict a total ???
+and ???
+boundaries for GM12878 and K562 cell lines respectively.
+This can be attributed to the fact that PEAKACHU's is built using soley CTCF sites, while *preciseTAD* also incorporates information from other architectural proteins including RAD21, SMC3, and ZNF143.
 
-<!--We were able to identify regions where the model predicted the base pair to be a TAD boundary with probability equal to 1 (Figure 5A).
-[???
-Where is this figure?
-It seemed important; !!!added] By clustering the regions (see Methods), we were able to predict a comparable number of TAD boundary regions as called by the ARROWHEAD TAD caller.
-However, only 24% and 29% of predicted and called (and 10 kb flanked) TAD boundaries overlapped for the GM12878 and K562 cell line, respectively, suggesting differing locations in TAD boundaries throughout the linear genome (Supplementary Figure 5).
-[???
-Need further drill down, as we discussed; !!!added distance to annotations figure in next paragraph]
+Next, we evaluated the biological significance of *preciseTAD* boundaries.
+Enriched heatmaps indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or PEAKACHU boundaries alone (Figure 5 B-C.
+Likewise, *preciseTAD* boundaries were also more enriched for other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 8-9).
+Furthermore, when compared to called TAD or loop boundaries, *preciseTAD* were found to be statistically significantly closer to the same cell line-specific top ranked TFBS (Figure 5D, Supplementary Figure 10-11).
 
-For each predicted TAD boundary region, we were able to identify the summit locations of TAD boundary location by performing partitioning around medoids (see Methods).
-To compare the summit locations of predicted and called TAD boundaries, we evaluated the signal strength of ChIP-seq peak regions around a 10 kb flanking region.
-We found that the signal strength for the CTCF, RAD21, SMC3, and ZNF143 [???
-Make all in this order!; !!!fixed] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5B; Supplementary Figure 6).
-Thus, our model is able to alleviate resolution limitations and precisely locate TAD boundaries that correspond to the highest signal strength of known TAD boundary-forming TFBSs.
-Furthermore, when compared to called TAD boundaries, the boundaries that we predicted with our model were found to be statistically significantly closer to the top ranked TFBS, suggesting stronger enrichment profiles near predicted TAD boundaries (Supplementary Figure 7).
+![**preciseTAD boundaries are enriched in CTCF sites.** (A) Visualizing locations of predicted vs called ARROWHEAD TAD boundaries on GM12878 (chr 21: 15150000-17270000).
+The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.
+The blue vertical lines represent boundaries identified by ARROWHEAD, with the corresponding called TADs outlined in blue on the upper diagonal contact matrix above.
+The black line represents the predicted probability of each base pair being a TAD boundary when validated by our random forest.
+The green vertical lines represent the *preciseTAD boundary points* (PTBP) predicted by *preciseTAD*, with the corresponding demarcated TADs outlined above in green.
+Below is a zoomed in portion of the genome showing a cluster of base pairs with high probability representing a single *preciseTAD boundary region (PTBR) colored in yellow.
+(B) Enriched heatmaps comparing the enrichment of CTCF sites around 5 kb flanked preciseTAD and ARROWHEAD TAD boundaries respectively.
+(C) Enriched heatmaps comparing the enrichment of CTCF sites around 10 kb flanked preciseTAD and PEAKACHU loop boundaries respectively.
+(D) $Log_{2}$ genomic distances from boundaries to nearest CTCF site between preciseTAD boundaries and both ARROWHEAD and PEAKACHU boundaries, respectively.](Figures/figure5_enrichment_and_log2dist_ctcf.png)
 
-![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17389000-18011000; GM12878).
-The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.The blue vertical lines represent called boundaries identified by ARROWHEAD, with the corresponding called TADs outlined in blue on the upper diagonal contact matrix above.
-The black line represents the predicted probability of each base pair being a TAD boundary when validated by *TADRF*.
-Collections of red vertical lines represent base pairs whose predictive probability exceed the ROC threshold, labeled as *predicted TAD boundary areas* (PTBA).
-The midpoints of spatially similar PTBA were clustered together into *predicted TAD boundary regions* (PTBR), denoted by the yellow regions along the x-axis.
-The green vertical lines represent the *predicted TAD boundary points* (PTBA) identified by *preciseTAD*, with the corresponding predicted TADs outlined above in green.](Figures/visualizing_ptbp_and_ctbp.png)
--->
+## *preciseTAD* boundaries are conserved across cell lines
+
+Subsequent comparisons of *preciseTAD* with both ARROWHEAD and PEAKACHU revealed that our predicted boundaries were more conserved between the GM12878 and K562 cell lines.
+To assess conservation, we evaluated the overlap between cell line specific boundaries after flanking by the resolution use to make predictions.
+Boundaries involving ARROWHEAD were flanked by 5 kb, while boundaries involving PEAKACHU were flanked by 10 kb.
+We found that a significant proportion of flanked boundaries predicted by *preciseTAD* overlapped between GM12878 and K562.
+Specifically, 45%???
+and 61%???
+of *preciseTAD* boundaries were conserved across cell lines when built on ARROWHEAD and PEAKACHU boundaries respectively (Figure 6A).
+Additionally, median jaccard index (MJI) was found to be 0.472 (IQR=0.441-0.503; p=???) and 0.647 (IQR=0.646-0.647; p=???) for *preciseTAD* predicted TAD and loop boundaries (Supplementary Table 5).
+Comparatively, only 25% (MJI=0.284; IQR=0.268-0.301) and 49% (MJI=0.509; IQR=0.503-0.515) of called/predicted ARROWHEAD and PEAKACHU boundaries were conserved (Figure 6A, Supplementary Table 5).
+
+Expectedly, the majority of flanked TAD boundaries predicted by *preciseTAD* represented a subset of the larger group of predicted loop boundaries.
+This makes sense as the boundaries that demarcate chromatin loops make up a broader class of boundaries, with TAD boundaries representing the next level in 3D chromatin hierarchy, followed by A/B compartments.
+For GM12878, 83% of predicted TAD and loop boundaries overlapped with eachother, while only 3% of predicted TAD boundaries were not contained in the set of flank-predicted loop boundaries (Figure 6B).
+Similarly, for K562, 75% overlap occured between predicted TAD and loop boundaries, with only 4% of predicted TAD boundaries remaining outside of the set of flank-predicted loop boundaries (Figure 6B).
+
+![**preciseTAD boundaries are conserved between the GM12878 and K562 cell lines.** (A) Venn diagrams illustrating the percentage of overlap between GM12878- and K562-specific predicted and called boundaries.
+(B) Venn diagrams illustrating the nested structure of predicted TAD and loop boundaries identified by *preciseTAD* for the GM12878 and K562 cell lines.
+Note, predicted and called TAD boundaries were flanked by 5 kb, while predicted and called loop boundaries were flanked by 10 kb prior to calculating overlaps to reflect the resolution that was used to predict each respectively.](Figures/figure6_venn_diagrams.png)
 
@@
 
+**Supplementary Figure 5.
+Whole genome random forest model outperform chromosome-specific random forest models across resolutions.** Random forest models built on ARROWHEAD boundaries using 5 kb defined genomic bins, with random under-sampling, and distance-type predictors for the top informative TFBS (CTCF, RAD21, SMC3, and ZNF143) applied to the entire genome (A) exhibit higher balanced accuracies than their chromosome specific counterparts (B) across each resolution respectively.
+
+**Supplementary Figure 6.
+Whole genome RF performances converge when ntree=250.** Scatter plot of cross-validated balanced accuracies (BA) for random forests built using both ARROWHEAD (circles) and PEAKACHU (triangles) boundaries, with random under-sampling, distance-type predictors (CTCF, RAD21, SMC3, and ZNF143), over the entire binned genome, for GM12878 (red) and K562 (blue) respectively.
+For the ARROWHEAD model, 5kb bins were used, while 10kb bins were used for the PEAKACHU model.
+Performances converged after trees of size 250, marked by the dashed line.
+
 **Supplementary Figure 7.
-Whole genome random forest model outperform chromosome-specific random forest models across resolutions.** Random forest models built on ARROWHEAD boundaries using 5 kb defined genomic bins, with random under-sampling, and distance-type predictors for the top informative TFBS (CTCF, RAD21, SMC3, and ZNF143) applied to the entire genome (A) exhibit higher balanced accuracies than their chromosome specific counterparts (B) across each resolution respectively.
+Whole genome RF performances converge when nodesize=???.** Scatter plot of cross-validated balanced accuracies (BA) for random forests built using both ARROWHEAD (circles) and PEAKACHU (triangles) boundaries, with random under-sampling, distance-type predictors (CTCF, RAD21, SMC3, and ZNF143), over the entire binned genome, for GM12878 (red) and K562 (blue) respectively.
+For the ARROWHEAD model, 5kb bins were used, while 10kb bins were used for the PEAKACHU model.
+Performances converged after nodesize values of ???, marked by the dashed line.
+
+**Supplementary Figure 8.
+preciseTAD boundaries are more enriched for GM12878-specific SMC3, RAD21, and ZNF143 sites.** Enriched heatmaps comparing preciseTAD boundaries with both (A) ARROWHEAD and (B) PEAKACHU boundaries for the GM12878 cell line.
+
+**Supplementary Figure 9.preciseTAD boundaries are more enriched for K562-specific CTCF, SMC3, RAD21, and ZNF143 sites.** Enriched heatmaps comparing preciseTAD boundaries with both (A) ARROWHEAD and (B) PEAKACHU boundaries for the K562 cell line.
+
+**Supplementary Figure 10.
+preciseTAD boundaries are spatially closer to GM12878-specific SMC3, RAD21, and ZNF143 sites.** Boxplots comparing the $log_{2}$ genomic distances from each preciseTAD boundary (green) and called boundary (either ARROWHEAD or PEAKACHU; blue) to the nearest SMC3, RAD21, and ZNF143 sites on the linear genome for GM12878.
+
+**Supplementary Figure 11.
+preciseTAD boundaries are spatially closer to K572-specific CTCF, SMC3, RAD21, and ZNF143 sites.** Boxplots comparing the $log_{2}$ genomic distances from each preciseTAD boundary (green) and called boundary (either ARROWHEAD or PEAKACHU; blue) to the nearest CTCF, SMC3, RAD21, and ZNF143 sites on the linear genome for K562.
+
+**Supplementary Table 5.** Median chromosome-specific Jaccard indices (IQR) for called and *preciseTAD* predicted TAD (ARROWHEAD) and loop (PEAKACHU) boundaries between the GM12878 and K562 cell lines.
+The p-value is from a nonparametric Wilcoxon-rank sum test.
+Note, predicted and called *TAD* boundaries were flanked by 5 kb, while predicted and called *loop* boundaries were flanked by 10 kb prior to calculating Jaccard indices to reflect the resolution that was used to predict each respectively.
 

### 2020-05-15 Manuscript/manuscript.Rmd
editted discussion, first 2 paragraphs

@@
 
-In this study we developed an ensemble framework to systematically compare the effects of different combinations of Hi-C resolution, data re-sampling, and feature engineering techniques on the performance of models aimed at TAD boundary prediction.
-By implementing our framework across multiple cell lines, we showed that there exists a consensus approach toward precise TAD boundary prediction.
-We showed that random forest classification models trained on domain data extracted from 10 kb resolution maps, using random over- and under-sampling to account for class imbalance, with a distance-type predictor space yielded optimal model performances for both the GM12878 and K562 cell lines.
+Here we present *preciseTAD*, a random forest-based approach coupled with density-based spatial clustering (DBSCAN) and scalable partition around medoids (PAM/CLARA) to more precisely predict TAD or loop boundaries on the linear genome.
+*preciseTAD* leverages a random forest (RF) classification algorithm built on ground truth TAD(loop) boundaries obtained from a user defined TAD(loop) calling tool and ChIP-seq defined genomic annotations as the feature space.
+We optimized our RF model by creating a computational framework that systematically compared the performances of different combinations of genome binning (resolution), feature engineering procedure, and re-sampling technique.
+In doing so, we first introduced a new strategy for establishing boundary prediction data referred to as *shifted binning*, in which the rows of the data matrix were controlled by the data resolution (either 5kb, 10kb, 25kb, 50kb, and 100kb) used to obtain ground truth boundaries, while assuring ground truth bounderies were located central to any given genomic bin.
+Furthermore, we introduced a new procedure for drawing spatial associations between boundary regions and genomic annotations, referred to as *distance*-type predictors.
+The method was benchmarked against two boundary calling tools, ARROWHEAD [@durand2016juicebox], an established TAD-caller, and PEAKACHU [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
+For a more in depth study, we applied *preciseTAD* on cell line-specific boundaries and ChIP-seq data from the GM12878 and K562 cell lines.
 
-Previous studies tended to focus only on specific sets of genomic annotations including chromatin states, histone modifications, or transcription factor binding sites (TFBS) alone.
-Using our framework, we were able to conclude that simply building random forest classifiers only on cell line specific TFBS can yield near optimal model performance, thereby significantly reducing the feature space and computational complexity of the model.
-Specifically, we found that the CCCTC-binding factor (CTCF) and cohesin complexes (RAD21 and SMC3) were the most important features of TAD boundary prediction, confirming their enrichment at TAD boundaries as part of the loop extrusion model [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
-Likewise, we found the the zinc-finger protein ZNF143 was also given high predictive importance.
-This confirmed the known role of ZNF143 as a chromatin-looping factor that contributes to the structural foundation of the genome by providing sequence specificity at promoters connected with distal regulatory elements [@bailey2015znf143;@gonzalez2017znf143].
+Our computational framework alone yielded many interesting results.
+First, we showed that RF models built using *distance*-type predictors out performed models built on previously published feature engineering techniques including overlap counts and overlap percents.
+Moreover, we were further able to optimize our RF model by introducing random under-sampling, a technique to correct for the severe class imbalance between TAD(loop) and non-TAD(loop) boundary regions.
+We showed that in our optimized RF, transcription factor binding sites provided an overwhelming amount of signal in the model, indeed out-performing histone modification- and BroadHMM-specific models, contradicting a previous study that found histone marks alone were effective in predicting TAD boundaries [@huang2015predicting].
+Likewise, our RF model built using *distance*-type predictors was consistently able to identify the group of the top known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143 as being highly predictive of TAD(loop) boundary regions across both cell lines.
+These are known components of the loop extrusion model, an established theory for how loops are made by a ring-shaped adenosine triphosphatase complex called cohesin [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+This suggested that random forests, when tuned and feature engineered correctly, are highly effective in accurately predicting boundary regions, contradicting a previous study that found simple multiple linear regression out performed random forests in a TAD boundary prediction setting using both human and drosophila Hi-C data [@mourad2016computational].
+Plausible reasons for their findings include lack of class balancing prior to modeling and usage of rudimentary feature engineering procedures including overlap counts and overlap percents.
 
-By leveraging the enrichment of these architectural proteins we were able to more precisely identify TAD boundaries at a much more refined resolution.
-To do so, we evaluated the ChIP-Seq signal strength between the CTCF, RAD21, SMC3, and ZNF143 transcription factors and a 10 kb flanked window of predicted TAD boundaries identified by our optimally built random forest model.
-We showed that the genomic signals for each TFBS was much more consolidated near the center of our flanked predicted TAD boundary then the flanked boundary identified by the ARROWHEAD TAD caller.
-We also evaluated the distal relationships between the same architectural proteins and found that they were statistically significantly closer in base pair distance to our predicted TAD boundaries, than to those identified by ARROWHEAD.
+???stopped here
 

### 2020-05-22 Scripts_for_results/03_creating_annotation_specifc_barplots.Rmd
fixed colors

@@
 ```
+
+## SpectralTAD
+
+### GM12878 (rus; distance types)
+
+#### 25kb
+
+```{r}
+badata_gm12878_25kb <- numeric()
+for(i in paste0("CHR", c(1:8,10:22))){
+ for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
+   print(c(i,j))
+  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
+    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
+                               i,
+                               "/rus/distance/TADRF_spectralTAD_",
+                               j, 
+                               ".rds"))
+    perfdata <- perfdata[[3]]
+  }else{
+    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
+                               i,
+                               "/rus/distance/TADRF_spectralTAD.rds"))
+    perfdata <- perfdata[[3]]
+  }
+
+  badata_gm12878_25kb <- rbind(badata_gm12878_25kb,
+                               perfdata[10,2])
+
+ }
+}
+
+```
+
+#### Plotting
+
+```{r}
+all_rfperfs <- data.frame(Perf=badata_gm12878_25kb)
+all_rfperfs$Resolution <- rep("25 kb", length(badata_gm12878_25kb))
+all_rfperfs$Annotation <- c("BroadHMM","HM","TFBS","ALL")
+all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "BroadHMM", "TFBS", "ALL"))
+all_rfperfs$Chromosome <- c(rep("CHR1", 4),
+                            rep("CHR2", 4),
+                            rep("CHR3", 4),
+                            rep("CHR4", 4),
+                            rep("CHR5", 4),
+                            rep("CHR6", 4),
+                            rep("CHR7", 4),
+                            rep("CHR8", 4),
+                            rep("CHR10", 4),
+                            rep("CHR11", 4),
+                            rep("CHR12", 4),
+                            rep("CHR13", 4),
+                            rep("CHR14", 4),
+                            rep("CHR15", 4),
+                            rep("CHR16", 4),
+                            rep("CHR17", 4),
+                            rep("CHR18", 4),
+                            rep("CHR19", 4),
+                            rep("CHR20", 4),
+                            rep("CHR21", 4),
+                            rep("CHR22", 4))
+
+all_rfperfs <- all_rfperfs %>% 
+  group_by(Resolution, Annotation) %>% 
+  dplyr::summarise(Performance = mean(Perf, na.rm = TRUE),
+                   PerformanceSD = sd(Perf, na.rm = TRUE))
+
+ggplot(all_rfperfs, aes(x=Annotation, y=Performance, fill=Annotation)) +
+    geom_bar(stat="identity") +
+    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=.75) +
+    theme_minimal() +
+    theme_bw()+
+    xlab("Resolution") + 
+    ylab("Balanced Accuracy") + 
+    scale_fill_discrete(name="Genomic Class")+
+    theme(axis.text.x = element_text(size=15,
+                                     angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    legend.position = "bottom",
+    plot.title = element_text(size=20))
+```
+
+### K562 (rus; distance types)
+
+#### 25kb
+
+```{r}
+badata_k562_25kb <- numeric()
+for(i in paste0("CHR", c(1:8,10:22))){
+ for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
+   print(c(i,j))
+  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
+    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
+                               i,
+                               "/rus/distance/TADRF_spectralTAD_",
+                               j, 
+                               ".rds"))
+    perfdata <- perfdata[[3]]
+  }else{
+    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
+                               i,
+                               "/rus/distance/TADRF_spectralTAD.rds"))
+    perfdata <- perfdata[[3]]
+  }
+
+  badata_k562_25kb <- rbind(badata_k562_25kb,
+                               perfdata[10,2])
+
+ }
+}
+
+```
+
+#### Plotting
+
+```{r}
+all_rfperfs <- data.frame(Perf=badata_k562_25kb)
+all_rfperfs$Resolution <- rep("10 kb", length(badata_k562_25kb))
+all_rfperfs$Annotation <- c("BroadHMM","HM","TFBS","ALL")
+all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "BroadHMM", "TFBS", "ALL"))
+all_rfperfs$Chromosome <- c(rep("CHR1", 4),
+                            rep("CHR2", 4),
+                            rep("CHR3", 4),
+                            rep("CHR4", 4),
+                            rep("CHR5", 4),
+                            rep("CHR6", 4),
+                            rep("CHR7", 4),
+                            rep("CHR8", 4),
+                            rep("CHR10", 4),
+                            rep("CHR11", 4),
+                            rep("CHR12", 4),
+                            rep("CHR13", 4),
+                            rep("CHR14", 4),
+                            rep("CHR15", 4),
+                            rep("CHR16", 4),
+                            rep("CHR17", 4),
+                            rep("CHR18", 4),
+                            rep("CHR19", 4),
+                            rep("CHR20", 4),
+                            rep("CHR21", 4),
+                            rep("CHR22", 4))
+
+all_rfperfs <- all_rfperfs %>% 
+  group_by(Resolution, Annotation) %>% 
+  dplyr::summarise(Performance = mean(Perf, na.rm = TRUE),
+                   PerformanceSD = sd(Perf, na.rm = TRUE))
+
+ggplot(all_rfperfs, aes(x=Annotation, y=Performance, fill=Annotation)) +
+    geom_bar(stat="identity") +
+    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=.75) +
+    theme_minimal() +
+    theme_bw()+
+    xlab("Resolution") + 
+    ylab("Balanced Accuracy") + 
+    scale_fill_discrete(name="Genomic Class")+
+    theme(axis.text.x = element_text(size=15,
+                                     angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    legend.position = "bottom",
+    plot.title = element_text(size=20))
+```

### 2020-05-22 Scripts_for_results/04_creating_rfe_lineplot.Rmd
fixed colors

@@
 ```
+
+## SpectralTAD
+
+### GM12878
+
+#### Optimal parameters: 25 kb, TFBS, distance type predictors, RUS
+
+```{r}
+chrs <- paste0("CHR",c(1:8,10:22))
+rfeperchr <- data.frame()
+for(i in c("GM12878")){
+  for(k in 1:length(chrs)){print(c(i,k));
+    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
+                                          i,
+                                          "/",
+                                          "25kb/results_by_chr/",
+                                          chrs[k],
+                                          "/rus/distance/TADrfe_spectralTAD.rds"))
+    rfeModelResults <- rfeModelResultsList[[1]]
+    rfeModelResults <- rfeModelResults[,c(1,4:5)]
+    rfeModelResults$CL <- i
+    rfeModelResults$Chromosome <- chrs[k]
+    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
+  }
+}
+rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
+rfeperchr_summ <- rfeperchr %>%
+  dplyr::group_by(Variables) %>%
+  dplyr::summarise(Performance = mean(BA, na.rm = TRUE),
+                   PerformanceSD = sd(BA, na.rm = TRUE))
+
+ggplot(rfeperchr_summ, aes(x=Variables, y=Performance)) + 
+  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), 
+                width=2, 
+                size=1, 
+                color="red") +
+  geom_line(size=2, color="red") +
+  geom_point(size=4, color="red") +
+  xlab("Number of top ranked annotations") +
+  ylab("Cross-Validated Accuracy") +
+  scale_color_discrete(name="Cell line")+
+  scale_x_continuous(breaks = c(2,4,8,16,32,52),
+                     labels = c(2,4,8,16,32,52))+
+  theme_minimal() +
+  theme_bw()+
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        #strip.text.x = element_text(size = 15),
+        #panel.spacing = unit(2, "lines"),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        plot.title = element_text(size=20),
+        legend.position = "bottom")
+```
+
+### K562
+
+#### Optimal parameters: 25 kb, TFBS, distance type predictors, RUS
+
+```{r}
+chrs <- paste0("CHR",c(1:8,10:22))
+rfeperchr <- data.frame()
+for(i in c("K562")){
+  for(k in 1:length(chrs)){print(c(i,k));
+    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
+                                          i,
+                                          "/",
+                                          "25kb/results_by_chr/",
+                                          chrs[k],
+                                          "/rus/distance/TADrfe_spectralTAD.rds"))
+    rfeModelResults <- rfeModelResultsList[[1]]
+    rfeModelResults <- rfeModelResults[,c(1,11)]
+    rfeModelResults$CL <- i
+    rfeModelResults$Chromosome <- chrs[k]
+    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
+  }
+}
+
+rfeperchr_summ <- rfeperchr %>%
+  dplyr::group_by(Variables) %>%
+  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
+                   PerformanceSD = sd(Accuracy, na.rm = TRUE))
+
+ggplot(rfeperchr_summ, aes(x=Variables, y=Performance)) + 
+  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), 
+                width=2, 
+                size=1, 
+                color="blue") +
+  geom_line(size=2, color="blue") +
+  geom_point(size=4, color="blue") +
+  xlab("Number of top ranked annotations") +
+  ylab("Cross-Validated Accuracy") +
+  scale_color_discrete(name="Cell line")+
+  scale_x_continuous(breaks = c(2,4,8,16,32,52),
+                     labels = c(2,4,8,16,32,52))+
+  theme_minimal() +
+  theme_bw()+
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        #strip.text.x = element_text(size = 15),
+        #panel.spacing = unit(2, "lines"),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        plot.title = element_text(size=20),
+        legend.position = "bottom")
+```

### 2020-05-22 Scripts_for_results/05_creating_importance_plot.Rmd
fixed colors

@@
 cluster.col = hclust(distance.col, method = "average")
-my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfe.set.mat))
+my_palette <- colorRampPalette(c("white", "lightblue", "blue"))(ncol(rfe.set.mat))
 
@@
 
-#### Optimal parameters: 5 kb, TFBS, distance type predictors, RUS
+#### Optimal parameters: 10 kb, TFBS, distance type predictors, RUS
 
@@
 ```
+
+## SpectralTAD
+
+### GM12878
+
+#### Optimal parameters: 25 kb, TFBS, distance type predictors, RUS
+
+```{r}
+chrs <- paste0("CHR",c(1:8,10:22))
+rfeperchr <- list()
+for(i in c("GM12878")){
+  for(k in 1:length(chrs)){
+    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
+                                          i,
+                                          "/",
+                                          "25kb/results_by_chr/",
+                                          chrs[k],
+                                          "/rus/distance/TADrfe_spectralTAD.rds"))
+
+    set.size = 8
+    rfeModelResults <- rfeModelResultsList[[2]]
+    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
+    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
+    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
+    rfe.set <- rfe.set[rfe.order, ]
+    rfe.set$CHR <- chrs[k]
+    rfeperchr[[k]] <- rfe.set
+  }
+}
+
+rfeperchr <- do.call(rbind.data.frame, rfeperchr)
+rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
+names(rfeperchr) <- c("TFBS", chrs)
+rfeperchr[is.na(rfeperchr)] <- 0
+rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]
+
+rfe.set.mat <- as.matrix(rfeperchr[,-1])
+rownames(rfe.set.mat) <- rfeperchr$TFBS
+
+rfe.set.mat <- t(apply(rfe.set.mat,1,rev))
+
+distance.col = dist(rfe.set.mat, method = "euclidean")
+cluster.col = hclust(distance.col, method = "average")
+my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfe.set.mat))
+
+heatmap.2(t(rfe.set.mat),
+          #labRow=rownames(rfe.set.mat),
+          #labCol=colnames(rfe.set.mat),
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins=c(10,4),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #keysize = 1.5,
+          #key.title = "Elastic-Net Coefficient",
+          dendrogram="column",     # only draw a row dendrogram,
+          Rowv = FALSE,
+          Colv = reorder(as.dendrogram(cluster.col), 37:1),
+          cexRow=.5,
+          cexCol=1,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          rowsep=0:nrow(t(rfe.set.mat)),
+          colsep=0:ncol(t(rfe.set.mat)),
+          sepwidth=c(0.00001,0.00001),
+          sepcolor="black"
+)
+
+Heatmap(t(rfe.set.mat),
+        col=my_palette,
+        border=TRUE,
+        cluster_rows=FALSE,
+        clustering_distance_columns = "euclidean",
+        clustering_method_columns = "complete",
+        show_row_names = FALSE,
+        column_names_rot = 90,
+        column_names_centered = FALSE,
+        show_heatmap_legend = FALSE,
+        heatmap_legend_param = list(title = "Predictive\nImportance"),
+        rect_gp = gpar(col = "black", lwd = 1),
+        column_dend_side = "top",column_names_side = "top")
+```
+
+### K562
+
+#### Optimal parameters: 25 kb, TFBS, distance type predictors, RUS
+
+```{r}
+chrs <- paste0("CHR",c(1:8,10:22))
+rfeperchr <- list()
+for(i in c("K562")){
+  for(k in 1:length(chrs)){
+    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
+                                          i,
+                                          "/",
+                                          "25kb/results_by_chr/",
+                                          chrs[k],
+                                          "/rus/distance/TADrfe_spectralTAD.rds"))
+
+    set.size = 8
+    rfeModelResults <- rfeModelResultsList[[2]]
+    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
+    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
+    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
+    rfe.set <- rfe.set[rfe.order, ]
+    rfe.set$CHR <- chrs[k]
+    rfeperchr[[k]] <- rfe.set
+  }
+}
+
+rfeperchr <- do.call(rbind.data.frame, rfeperchr)
+rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
+names(rfeperchr) <- c("TFBS", chrs)
+rfeperchr[is.na(rfeperchr)] <- 0
+rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]
+
+rfe.set.mat <- as.matrix(rfeperchr[,-1])
+rownames(rfe.set.mat) <- rfeperchr$TFBS
+
+rfe.set.mat <- t(apply(rfe.set.mat,1,rev))
+
+distance.col = dist(rfe.set.mat, method = "euclidean")
+cluster.col = hclust(distance.col, method = "average")
+my_palette <- colorRampPalette(c("white", "lightblue", "blue"))(ncol(rfe.set.mat))
+
+heatmap.2(t(rfe.set.mat),
+          #labRow=rownames(rfe.set.mat),
+          #labCol=colnames(rfe.set.mat),
+          #cellnote = ,  # same data set for cell labels
+          #main = "", # heat map title
+          notecol="black",      # change font color of cell labels to black
+          density.info="none",  # turns off density plot inside color legend
+          trace="none",         # turns off trace lines inside the heat map
+          margins=c(10,4),     # widens margins around plot
+          col=my_palette,       # use on color palette defined earlier
+          na.color = "gray",
+          #breaks=col_breaks,    # enable color transition at specified limits
+          key=FALSE,
+          #keysize = 1.5,
+          #key.title = "Elastic-Net Coefficient",
+          dendrogram="column",     # only draw a row dendrogram,
+          Rowv = FALSE,
+          Colv = reorder(as.dendrogram(cluster.col), 37:1),
+          cexRow=.5,
+          cexCol=1,
+          #labRow = FALSE,
+          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
+          #lhei=c(.5,6,0),
+          rowsep=0:nrow(t(rfe.set.mat)),
+          colsep=0:ncol(t(rfe.set.mat)),
+          sepwidth=c(0.00001,0.00001),
+          sepcolor="black"
+)
+
+```

### 2020-05-22 Scripts_for_results/08_creating_venn_diagrams.Rmd
added nested venn diagram section

@@
 
+### Nesting between pt(arrowhead) and pt(peakachu)
+
+```{r}
+venn_cnt2venn <- function(venn_cnt){
+  n <- which(colnames(venn_cnt)=="Counts") - 1
+  SetNames=colnames(venn_cnt)[1:n]
+  Weight=venn_cnt[,"Counts"]
+  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
+  Venn(SetNames=SetNames, Weight=Weight)
+}
+
+###### GM12878
+
+res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878_a,
+                                  all_pred_bounds_gm12878_p),
+                       NameOfPeaks=c("preciseTAD", "PEAKACHU"))
+
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "red"
+gp[["Face"]][["10"]]$fill <-  "lightblue"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+
+###### K562
+
+res <- makeVennDiagram(Peaks=list(all_pred_bounds_k562_a,
+                                  all_pred_bounds_k562_p),
+                       NameOfPeaks=c("preciseTAD", "PEAKACHU"))
+
+venn.pt <- venn_cnt2venn(res$vennCounts)
+venn.pt <- compute.Venn(venn.pt)
+gp <- VennThemes(venn.pt)
+gp[["Face"]][["11"]]$fill <-  "purple"
+gp[["Face"]][["01"]]$fill <-  "red"
+gp[["Face"]][["10"]]$fill <-  "lightblue"
+gp[["FaceText"]][["10"]]$cex <- 2
+gp[["FaceText"]][["11"]]$cex <- 2
+gp[["FaceText"]][["01"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- 2
+gp[["SetText"]][["Set2"]]$cex <- 2
+
+gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+
+```
+
 ## LOLLIPOP

### 2020-05-26 Manuscript/manuscript.Rmd
edits to methods

@@
 
-## Computational framework for boundary prediction
+## Shifted-binning for binary classification
 
@@
 
-Cell type-specific genomic annotations were used to build the feature space for our boundary prediction framework.
+## Feature engineering
+
+Cell line-specific genomic annotations were used to build the feature space for our boundary prediction framework.
 Bins were annotated by one of either the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average signal strength of the corresponding annotation (*Peak Signal Strength*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
@@
 
-Chromosome-specific datasets used for modeling were composed of two components: the response vector $Y_{i}$, an indicator variable distinguishing boundary and non-boundary regions, and the predictor-type specific data matrix, $\textbf{X}_{ij}$, where $i \in \{ 1,2, \cdots,N \}$ ($N$ being the number of chromosome-specific bins) and $j \in \{ 1,2,\cdots,P \}$ ($P$ being the number of genomic annotations).
-<!--Chromosome-specific datasets were concatenated to form a whole genome dataset.
-The dataset was then split into a 7:3 ratio for training and testing, respectively.[!!!only comes into play with preciseTAD]-->
-
-## Class imbalance assessment
+## Addressing class imbalance
 
@@
 
-## Assessment of model performance
+## Establishing computational framework for assessing model performance
 
-Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, predictor types, and re-sampling techniques.
-Five-fold cross validation was used to tune the number of annotations, *P*, to consider at each node (*mtry*).
+Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, feature engineering procedures, and re-sampling techniques.
+First, the data matrix $A_{N \times (p+1)}$ was constructed by combining the binned genome from each of the $n-1$ autosomal chromosomes ($1,2,\cdots, i-1,i+1,\cdots,22$) as well as a particular feature engineering procedure.
+Re-sampling was then performed on $A$.
+An RF classifier was then trained on $A$ using 5-fold cross-validation to tune for the number of annotations, *p*, to consider at each node (*mtry*).
 The number of trees (*ntree*) that were aggregated for each RF model was set to 500.
 The minimum number of observations per root node (*nodesize*) was set to 1.
-The performance of each model was compared using Balanced Accuracy (BA), defined as the average of sensitivity and specificity:
+To evaluate model performance, the $i^{th}$ chromosome was used for testing.
+The performance of each combination of model inputs was compared using Balanced Accuracy (BA), defined as the average of sensitivity and specificity:
 
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-<!--We refer to the complete computational framework used to compare random forest model inputs as *TADRF*.-->
+<!--We refer to the complete computational framework used to compare random forest model inputs as *TADRF*.--> Performances were aggregated across each $i^{th}$ holdout chromosome using means and standard deviations.
 
@@
 
-## Boundary prediction at bp resolution
+## Boundary prediction at bp resolution using *preciseTAD*
 
 To investigate whether we could alleviate resolution limitations of conventional TAD and chromatin loop calling tools, we developed *preciseTAD*, an algorithm that leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base pair (bp) resolution.
-To demonstrate, we opted to implement an optimally built whole genome RF model.
-That is, a random forest model built on the optimal combination of data resolution (binning), predictor type (feature space), re-sampling technique (class balancing correction), and annotations (most informative genomic elements) [???
-Write how your vector Y and annotation matrices change;!!!added ???You describe whole-genome model.
-It should have been described early on.
-Here, describe chromosome-specific bp-resolution model].
-Here, $Y$ was of length $N$ where $N=n_1+n_2+\cdots+n_{22}$, the total number of bins across each chromosome.
-The data matrix $\textbf{X}$ had dimensions $N \times p_s$, where $p_s \subset P$, a subset of the most predictive genomic elements.
-The *nodesize* and *ntree* parameters were tuned sequentially using a grid search across values from ???-???
-by ???
-and from ???-???
-by ???
-for each, respectively.
-We then used the same optimized whole genome RF model to predict boundaries from chromosome-specific bp resolution data.
+To demonstrate, we implemented an optimally built RF model using the framework described above.
+That is, a random forest model built on the optimal combination of data resolution (binning), predictor type (feature space), re-sampling technique (class balancing correction), and annotations (most informative genomic elements).
 
-Naturally, when dealing with such fine resolution, there will be spatially close base pairs with similar predictor profiles (i.e.
+First the vector, $p_{n_{i}}$, denoting each base pair's probability of being a boundary point from the RF model, was extracted, where $n_{i}$ represents the length of chromosome $i$.
+Next, *DBSCAN* (version 1.1-5) was applied to the matrix of pairwise genomic distances between base pairs with $p_{n_{i}}=1$.
+This was to avoid the inflation of predicted boundaries that can occur naturally when dealing with such fine resolution, namely, due to spatially close base pairs with similar predictor profiles (i.e.
 similar overlap counts, distances, etc.).
-*preciseTAD* guards against inflating the number of predicted boundaries by combining both density-based spatial clustering (DBSCAN) and partitioning techniques to identify precise TAD (or loop) boundaries throughout the linear genome.
-First the vector, $p_{n_{i}}$, denoting each base pair's probability of being a boundary point from the RF model, was extracted, where $n_{i}$ represents the length of chromosome $i$.
-Next, *DBSCAN* (version 1.1-5) was applied to the matrix of pairwise genomic distances [???
-Is that true?
-Matrix is 2-dimensional] between base pairs with $p_{n_{i}}=1$.
-The DBSCAN algorithm takes two parameters, *eps* ($\epsilon$) and *MinPts* [@hahsler2019dbscan].
-The eps parameter was assigned as the respective data resolution [???
-Meaning?].
-The heuristic being that base pairs with genomic distances less than resolution should occupy the same designated cluster.
-The corresponding MinPts parameter was set to 3 [???
-Meaning?].
-The resulting clusters of density-reachable base pairs identified by DBSCAN were termed *preciseTAD boundary regions* (PTBR) [???
-Use simple words: "boundary region" (many bases clustered by DBSCAN), then "boundary base" (selected by PAM)].
+The DBSCAN algorithm takes two parameters, *eps* ($\epsilon$) and *MinPts*.
+The eps parameter was assigned as the respective data resolution.
+The heuristic being that density-reachable base pairs with genomic distances less than resolution should occupy the same designated cluster.
+The corresponding MinPts parameter was set to recommended value of 3, representing $1+dim(data)$ [@hahsler2019dbscan].
+The resulting clusters of highly predictive base pairs identified by DBSCAN were termed *preciseTAD boundary regions* (PTBR).
 To precisely identify a single base pair among each PTBR, *preciseTAD* then implements an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
-Thusly, the corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative base pair within each clustered PTBR.
-
-<!--
-We then performed hierarchical clustering on the distance matrix (in base pairs) constructed from the midpoints of each PTBA using complete linkage clustering.
-To identify the optimal number of clusters, *k*, we calculated the mean silhouette score over all possible sizes of clusters *m*:
-
-$$\bar{s}_{m} = \dfrac{\sum^{m}_{i} s_{i}}{m},$$
-
-where $s_{i}$ is the cluster-specific silhouette score defined as,
-
-$$s_{i} = \dfrac{b_{i} - a_{i}}{max[a_{i},b_{i}]}.$$
-
-Here, $a_{i}$ is the mean distance between each cluster entry and all other observations in the same cluster, and $b_{i}$ is the mean distance between entries within the same cluster.
-Therefore number of clusters, *k*, that maximized the mean silhouette score, $\bar{s}_{m}$ were used to identify groupings of PTBA, which we defined as *predicted TAD boundary regions* (PTBR).
--->
-
-<!--
-Using optimally trained models, we established *predicted TAD boundary regions* as a collection of adjacent bases predicted as TAD boundary with the probability of 1.
-[???
-Do not understand from here:] To guard against inflating the number of predicted TAD boundaries, we clustered the distances between the midpoints of the *predicted TAD boundary regions*.
-We then performed partitioning around mediods (PAM) to determine the *predicted TAD boundary region* that was most representative of the cluster.
-The midpoint, in this case a particular basepair, of the *predicted TAD boundary region* identified as the medoid was defined as a final *predicted TAD boundary*.
-[???
-To here.
-REWRITE!]
--->
+Thusly, the corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative and biologically meaningful base pair within each clustered PTBR.
 
@@
 
-Furthermore, under the hypothesis that TAD boundaries are highly concerved across cell types [@dixon2012topological; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa], we assessed the conservation of our predicted TAD boundaries across cell types and prediction algorithms.
+Furthermore, under the hypothesis that TAD boundaries are highly concerved across cell types [@dixon2012topological; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa], we assessed the conservation of our predicted TAD boundaries across cell lines and prediction algorithms.
 Boundaries were flanked by resolution and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0) and evaluated using the Jaccard index defined as
@@
 where A and B represent genomic regions created by flanking called and predicted boundaries.
-That is, the set of shared boundaries divided by the total number of unique boundaries.
+That is, between cell lines, the number of overlapping flanked boundaries divided by the total number of flanked boundaries.
 Wilcoxon rank sum tests were used to compare chromosome-specific jaccard indices across cell lines, between *preciseTAD* boundaries and both ARROWHEAD and PEAKACHU boundaries respectively.

### 2020-05-26 Manuscript/manuscript.Rmd
added to discussion

@@
 
-Our framework is resolution-specific and uses arbitrary called TAD and loop boundaries as ground truth to establish TAD(loop)-boundary and non-TAD(loop) boundary regions.
+Our framework is resolution-specific and uses called TAD and loop boundaries as ground truth to establish TAD(loop)-boundary and non-TAD(loop) boundary regions.
 To demonstrate, we applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1).
@@
 
-In summary, we considered combinations of data for a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, with a specific engineered feature space *P = {Signal, OC, OP, Distance}*, and re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
-Once the model inputs were established, a random forest classifier was trained on chromosome-specific genomic bins (excluding chromosome 9), *C = {CHR1, ..., CHR22}*, using 5-fold cross-validation.
-Model inputs were evaluated by assessing the balanced accuracy (BA) of each combination.
+In summary, we considered combinations of data from a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, with a specific engineered feature space *P = {Signal, OC, OP, Distance}*, and re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
+Once the model inputs were established, a random forest classifier was trained on $n-1$ chromosomes, while reserving the $i^{th}$ chromosome for testing.
+Five-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed to default values of 500 and 1 respectively.
+Model inputs were evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (See Methods).
 <!--The results presented are for the ARROWHEAD boundaries, with PEAKACHU boundaries presented in the Supplementary material.
@@
 
-![**A diagram of the ensemble framework detailing the steps for combining different inputs used in the random forest model building pipeline.** Step 1 is to establish the chromosome-specific rowise (genomic bins) and columnwise (genomic annotations) dimensions of the data matrix, **A**, by combining a resolution (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)).
-Step 2 is to split **A** into a training and testing set according to a 7:3 ratio.
+![**A diagram of the ensemble framework detailing the steps for combining different inputs used in the random forest model building pipeline.** Step 1 is to establish the chromosome-specific rowise (genomic bins) and columnwise (genomic annotations) dimensions of the data matrix, **A**, by combining a resolution (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)) for the $n-1$ chromosomes.
+Step 2 is to use the binned data matrix for the holdout chromosome $i$ as the test data.
 Step 3 is to apply a re-sampling technique to the training set (no re-sampling, random over-sampling, random under-sampling, or SMOTE re-sampling).
-Step 4 is to implement the random forest algorithm and perform 5-fold cross-validation to tune for the *mtry* parameter.
+Step 4 is to train the random forest model and perform 5-fold cross-validation to tune for the *mtry* parameter.
 Finally, step 5 is to validate the model on the separate test data and evaluate model performance using balanced accuracy (BA).](Figures/figure2_ensemble_framework.png)
@@
 
-![**Models built using distance-type predictors combined with random under-sampling at 5 kb yielded optimal predictive performance for GM12878.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
+![**???[needs updating with new framework, takes longest, do last]Models built using distance-type predictors combined with random under-sampling at 5 kb yielded optimal predictive performance for GM12878.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
 Performances are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
@@
 
-<!--Additional performance metrics were reported for both cell lines including positive predictive value (PPV; precision), F1-Score (F1), Accuracy, Area Under the Receiver Operating Characteristic Curve (AUC), Area Under the Precision-Recall Curve.-->
-
-Here we present *preciseTAD*, a random forest-based approach coupled with density-based spatial clustering (DBSCAN) and scalable partition around medoids (PAM/CLARA) to more precisely predict TAD or loop boundaries on the linear genome.
+Here we present *preciseTAD*, a random forest-based approach coupled with spatial clustering (DBSCAN) and scalable partition around medoids (CLARA) that allows for more precise prediction of TAD or loop boundaries.
 *preciseTAD* leverages a random forest (RF) classification algorithm built on ground truth TAD(loop) boundaries obtained from a user defined TAD(loop) calling tool and ChIP-seq defined genomic annotations as the feature space.
@@
 Furthermore, we introduced a new procedure for drawing spatial associations between boundary regions and genomic annotations, referred to as *distance*-type predictors.
-The method was benchmarked against two boundary calling tools, ARROWHEAD [@durand2016juicebox], an established TAD-caller, and PEAKACHU [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
-For a more in depth study, we applied *preciseTAD* on cell line-specific boundaries and ChIP-seq data from the GM12878 and K562 cell lines.
+We benchmarked *preciseTAD* against two boundary calling tools, ARROWHEAD [@durand2016juicebox], an established TAD-caller, and PEAKACHU [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
+For a more in depth study, we also applied *preciseTAD* on cell line-specific boundaries and ChIP-seq data from the GM12878 and K562 cell lines.
 
@@
 
+Besides balanced accuracy (BA), we investigated five other performance metrics to evaluate the optimal combination of data level characteristics for boundary region prediction including accuracy, area under the receiver operating characteristic curve (AUC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Supplementary Tables 6-7).
+The accuracy metric can be artificially inflated by true negatives (TN), the set of genomic bins correctly predicted as not containing a ground truth boundary.
+AUC captures how a model generally performs accross different thresholds.
+However, it doesn't place more emphasis on one class over the other, so it does not reflect the minority class well.
+Precision indicates the rate at which positive predictions are correct and can be artificially deflated by low proportions of true positives (TP), the set of genomic bins correctly predicted as containing a ground truth boundary.
+While F1-score is a composite metric, it can be very sensitive towards disparate values for precision and recall.
+Lastly, AUPRC is insensitive toward class imbalance and also omits from its calculation TN.
+All of these are important considerations to make when choosing a performance metric.
+For these reasons we opted to report the balanced accuracy (BA).
+The BA benifits from incorporating all components of the confusion matrix, while also being sensitive to class imbalance, a necessary characteristic when comparing performances to models built using no data re-sampling.
+
 ???stopped here
-
-<!-- Discuss advantages and disadvantages of Balanced Accuracy.
-The disadvantage is that we restrict TP to the originally detected TAD boundaries.
-While there are likely many more that couldn't be detected but are TP.
-We currently count them as FP -->
 
@@
 
+**Supplementary Table 6.**
+
+**Supplementary Table 7.**
+
 <!--

### 2020-05-27 Manuscript/manuscript.Rmd
added to discussion

@@
 
+The performance of *preciseTAD* was found to be empirically better than both ARROWHEAD and PEAKACHU ground truth boundaries.
+*preciseTAD* provides bp resolution predicted boundaries, thereby alleviating resolution limitations of conventional TAD-callers.
+We show that, unlike ARROWHEAD, *preciseTAD* does not inflate the number of predicted boundaries, instead, providing only the most biologically meaningful boundaries.
+*preciseTAD* boundaries we found to be more enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143.
+Likewise *preciseTAD* boundaries were found to be more conserved between GM12878 and K562 cell lines, further highlighting their biological significance.
+
 ???stopped here

### 2020-05-27 Manuscript/manuscript.Rmd
added to discussion

@@
 
+A limitation of *preciseTAD* is that it is dependent on "ground truth" boundaries provided by a user-defined TAD(loop)-caller.
+Ideally we would perform simulation studies to benchmark *preciseTAD* against simulated boundaries.
+While there are existing methods for simulating Hi-C data sets [@forcato2017comparison; @zheng2020freehi], of which boundaries can be extracted from, to date, there are no such methods for simulating ChIP-seq data.
+However, given *preciseTAD* is applied on chromosome-specific sections of the linear genome, we feel that aggregating results across chromosomes provides strong empirical evidence of the superiority of *preciseTAD*.
+Another limitation is that *preciseTAD* does not provide hierarchical boundaries, but instead simply provides the bp coordinate that demarcates TADs(loops).
+Studies have shown evidence of the hierarchical nature to the 3D architecture of the human genome [@hansen2018recent; @weinreb2016identification; @fraser2015hierarchical].
+In such a hierarchy, the boundaries provided by *preciseTAD* can be interpreted as the lowest level of boundaries.
+
 ???stopped here

### 2020-05-27 Manuscript/manuscript.Rmd
added to discussion

@@
 
-???stopped here
-
-# Conclusion
-
-In summary, we have shown that TAD boundary prediction is a multi-faceted problem composed of many data irregularities and characteristics that previous methods have failed to address.
-Through our ensemble framework, we provide a useful guide toward the exploration of chromatin organization, while highlighting the impact of data resolution, class imbalance, and feature engineering in TAD boundary prediction.
-Lastly, by building models using known enriched transcription factors, we were able to bridge the resolution gap between 1D ChIP-Seq annotations and 3D Hi-C sequencing for more precise TAD boundary prediction.
-This improved precision in TAD boundary location offers the potential for further exploration into the 3D organization of the human genome.
+In summary, we have shown that TAD boundary prediction is a multi-faceted problem composed of many data irregularities and characteristics.
+Simply quering a contact matrix ignores the fundamental roles of known molecular drivers of 3D chromatin.
+Instead, we propose a method for turning TAD-calling into a supervised learning framework built using ChIP-seq annotations.
+Specifically, we introduce two novel concepts known as *shifted binning* and *distance*-type predictors which we use to build random forest classification models for predicting boundary regions.
+We then introduce *preciseTAD*, a method for leveraging random forests to predict TAD(loop) boundaries at base pair resolution.
+Our method is able to bridge the resolution gap between 1D ChIP-seq annotations and 3D Hi-C sequencing data for more precise and biologically meaningful boundary prediction.
+By releasing our method as an open source R package, we hope to provide an efficient and easy-to-use tool to further explore the 3D organization of the human genome.
 

### 2020-05-28 Manuscript/manuscript.Rmd
edits to discuss and legend of figure 5

@@
 (C) Enriched heatmaps comparing the enrichment of CTCF sites around 10 kb flanked preciseTAD and PEAKACHU loop boundaries respectively.
-(D) $Log_{2}$ genomic distances from boundaries to nearest CTCF site between preciseTAD boundaries and both ARROWHEAD and PEAKACHU boundaries, respectively.](Figures/figure5_enrichment_and_log2dist_ctcf.png)
+(D) $Log_{2}$ genomic distances from boundaries to nearest CTCF site between preciseTAD boundaries and both ARROWHEAD and PEAKACHU boundaries, respectively.
+(E) Matrix of pairwise Jaccard indices across resolutions shows more invariance toward resolution for *preciseTAD* (upper triangular) compared to ARROWHEAD (lower triangular).](Figures/figure5_enrichment_and_log2dist_ctcf.png)
 
@@
 Here we present *preciseTAD*, a random forest-based approach coupled with spatial clustering (DBSCAN) and scalable partition around medoids (CLARA) that allows for more precise prediction of TAD or loop boundaries.
-*preciseTAD* leverages a random forest (RF) classification algorithm built on ground truth TAD(loop) boundaries obtained from a user defined TAD(loop) calling tool and ChIP-seq defined genomic annotations as the feature space.
-We optimized our RF model by creating a computational framework that systematically compared the performances of different combinations of genome binning (resolution), feature engineering procedure, and re-sampling technique.
+*preciseTAD* leverages a random forest (RF) classification algorithm built on ground truth TAD(loop) boundaries obtained from a TAD(loop) calling tool and ChIP-seq defined genomic annotations as the feature space.
+We first optimized our RF model by creating a computational framework that systematically compared the performances of different combinations of genome binning (resolution), feature engineering procedure, and re-sampling technique.
 In doing so, we first introduced a new strategy for establishing boundary prediction data referred to as *shifted binning*, in which the rows of the data matrix were controlled by the data resolution (either 5kb, 10kb, 25kb, 50kb, and 100kb) used to obtain ground truth boundaries, while assuring ground truth bounderies were located central to any given genomic bin.
-Furthermore, we introduced a new procedure for drawing spatial associations between boundary regions and genomic annotations, referred to as *distance*-type predictors.
+Furthermore, we introduced a new procedure for drawing spatial associations between boundary regions and genomic annotations, referred to as *distance*-type predictors, defined as as the $log_{2}$ distance in base pairs from each genomic bin the nearest ChIP-seq peak region.
 We benchmarked *preciseTAD* against two boundary calling tools, ARROWHEAD [@durand2016juicebox], an established TAD-caller, and PEAKACHU [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
@@
 
-Besides balanced accuracy (BA), we investigated five other performance metrics to evaluate the optimal combination of data level characteristics for boundary region prediction including accuracy, area under the receiver operating characteristic curve (AUC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Supplementary Tables 6-7).
+Besides balanced accuracy (BA), we investigated five other performance metrics to evaluate the optimal combination of data level characteristics for RF prediction including accuracy, area under the receiver operating characteristic curve (AUC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Supplementary Tables 6-7).
 The accuracy metric can be artificially inflated by true negatives (TN), the set of genomic bins correctly predicted as not containing a ground truth boundary.
@@
 While F1-score is a composite metric, it can be very sensitive towards disparate values for precision and recall.
-Lastly, AUPRC is insensitive toward class imbalance and also omits from its calculation TN.
+Lastly, AUPRC is insensitive toward class imbalance and also omits from its calculation TN values.
 All of these are important considerations to make when choosing a performance metric.
@@
 We show that, unlike ARROWHEAD, *preciseTAD* does not inflate the number of predicted boundaries, instead, providing only the most biologically meaningful boundaries.
-*preciseTAD* boundaries we found to be more enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143.
+*preciseTAD* boundaries were found to be more enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143.
 Likewise *preciseTAD* boundaries were found to be more conserved between GM12878 and K562 cell lines, further highlighting their biological significance.
@@
 While there are existing methods for simulating Hi-C data sets [@forcato2017comparison; @zheng2020freehi], of which boundaries can be extracted from, to date, there are no such methods for simulating ChIP-seq data.
-However, given *preciseTAD* is applied on chromosome-specific sections of the linear genome, we feel that aggregating results across chromosomes provides strong empirical evidence of the superiority of *preciseTAD*.
+However, given *preciseTAD* is applied on chromosome-specific sections of the linear genome, and on multiple cell lines, we feel that aggregating results across chromosomes provides strong empirical evidence of the superiority of *preciseTAD*.
 Another limitation is that *preciseTAD* does not provide hierarchical boundaries, but instead simply provides the bp coordinate that demarcates TADs(loops).
@@
 We then introduce *preciseTAD*, a method for leveraging random forests to predict TAD(loop) boundaries at base pair resolution.
-Our method is able to bridge the resolution gap between 1D ChIP-seq annotations and 3D Hi-C sequencing data for more precise and biologically meaningful boundary prediction.
+Our method is able to bridge the resolution gap between 1D ChIP-seq annotations and 3D Hi-C sequencing data for more precise and biologically meaningful boundary identification.
 By releasing our method as an open source R package, we hope to provide an efficient and easy-to-use tool to further explore the 3D organization of the human genome.

### 2020-05-28 Manuscript/manuscript.Rmd
added figure 5E description to results

@@
 Likewise, *preciseTAD* boundaries were also more enriched for other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 8-9).
-Furthermore, when compared to called TAD or loop boundaries, *preciseTAD* were found to be statistically significantly closer to the same cell line-specific top ranked TFBS (Figure 5D, Supplementary Figure 10-11).
+When compared to called TAD or loop boundaries, *preciseTAD* boundaries were found to be statistically significantly closer to the same cell line-specific top ranked TFBS (p=???
+and p=???
+vs ARROWHEAD and PEAKACHU respectively) (Figure 5D, Supplementary Figure 10-11).
+We also inspected the affect of resolution on locations of TAD boundaries specifically.
+We found that *preciseTAD* boundaries exhibited higher pairwise Jaccard indices between adjacent resolutions than ARROWHEAD boundaries, thus implying stronger invariance toward resolution (Figure 5E).
 

### 2020-05-28 Scripts_for_results/11_correlations_across_resolutions.Rmd
initial commit

---
title: "Correlations between PTBP at different resolutions"
author: "Spiro Stilianoudakis"
date: "5/28/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages and functions

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)
library(ComplexHeatmap)
library(circlize)
library(cotools)
library(ggcorrplot)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

# Jaccard Function

```{r}
jaccard_mod <- function (query, reference, restrict = NULL, modified=TRUE) {
  if(isTRUE(modified)){
    int = sum(width(intersect(query, reference)))
    minunion = min(sum(as.numeric(width(intersect(query, reference)))),sum(as.numeric(width(union(query, reference)))))
    res = int/minunion
  }else{
    res = sum(width(intersect(query, reference)))/sum(as.numeric(width(union(query, reference)))) 
  }
  return(res)
}
```

## GM12878

```{r}
gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")

pt_gm12878_5kb <- flank(gm12878_5kb[[2]], 5000, both=TRUE)
pt_gm12878_10kb <- flank(gm12878_10kb[[2]], 10000, both=TRUE)
pt_gm12878_25kb <- flank(gm12878_25kb[[2]], 25000, both=TRUE)
pt_gm12878_50kb <- flank(gm12878_50kb[[2]], 50000, both=TRUE)
pt_gm12878_100kb <- flank(gm12878_100kb[[2]], 100000, both=TRUE)

arrow_gm12878_5kb <- flank(gm12878_5kb[[3]], 5000, both=TRUE)
arrow_gm12878_10kb <- flank(gm12878_10kb[[3]], 10000, both=TRUE)
arrow_gm12878_25kb <- flank(gm12878_25kb[[3]], 25000, both=TRUE)
arrow_gm12878_50kb <- flank(gm12878_50kb[[3]], 50000, both=TRUE)
arrow_gm12878_100kb <- flank(gm12878_100kb[[3]], 100000, both=TRUE)

jaccard_matrix <- matrix(nrow=5,ncol=5)
jaccard_matrix[1,2] <- round(genomicCorr.jaccard(pt_gm12878_5kb,pt_gm12878_10kb),2)
jaccard_matrix[1,3] <- round(genomicCorr.jaccard(pt_gm12878_5kb,pt_gm12878_25kb),2)
jaccard_matrix[1,4] <- round(genomicCorr.jaccard(pt_gm12878_5kb,pt_gm12878_50kb),2)
jaccard_matrix[1,5] <- round(genomicCorr.jaccard(pt_gm12878_5kb,pt_gm12878_100kb),2)
jaccard_matrix[2,3] <- round(genomicCorr.jaccard(pt_gm12878_10kb,pt_gm12878_25kb),2)
jaccard_matrix[2,4] <- round(genomicCorr.jaccard(pt_gm12878_10kb,pt_gm12878_50kb),2)
jaccard_matrix[2,5] <- round(genomicCorr.jaccard(pt_gm12878_10kb,pt_gm12878_100kb),2)
jaccard_matrix[3,4] <- round(genomicCorr.jaccard(pt_gm12878_25kb,pt_gm12878_50kb),2)
jaccard_matrix[3,5] <- round(genomicCorr.jaccard(pt_gm12878_25kb,pt_gm12878_100kb),2)
jaccard_matrix[4,5] <- round(genomicCorr.jaccard(pt_gm12878_50kb,pt_gm12878_100kb),2)

jaccard_matrix[2,1] <- round(genomicCorr.jaccard(arrow_gm12878_5kb,arrow_gm12878_10kb),2)
jaccard_matrix[3,1] <- round(genomicCorr.jaccard(arrow_gm12878_5kb,arrow_gm12878_25kb),2)
jaccard_matrix[4,1] <- round(genomicCorr.jaccard(arrow_gm12878_5kb,arrow_gm12878_50kb),2)
jaccard_matrix[5,1] <- round(genomicCorr.jaccard(arrow_gm12878_5kb,arrow_gm12878_100kb),2)
jaccard_matrix[3,2] <- round(genomicCorr.jaccard(arrow_gm12878_10kb,arrow_gm12878_25kb),2)
jaccard_matrix[4,2] <- round(genomicCorr.jaccard(arrow_gm12878_10kb,arrow_gm12878_50kb),2)
jaccard_matrix[5,2] <- round(genomicCorr.jaccard(arrow_gm12878_10kb,arrow_gm12878_100kb),2)
jaccard_matrix[4,3] <- round(genomicCorr.jaccard(arrow_gm12878_25kb,arrow_gm12878_50kb),2)
jaccard_matrix[5,3] <- round(genomicCorr.jaccard(arrow_gm12878_25kb,arrow_gm12878_100kb),2)
jaccard_matrix[5,4] <- round(genomicCorr.jaccard(arrow_gm12878_50kb,arrow_gm12878_100kb),2)

rownames(jaccard_matrix) <- colnames(jaccard_matrix) <- c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb")

col_fun = colorRamp2(c(0,.3,.6), c("blue","white","red"))
col_fun = colorRamp2(c(0,.6), c("white","red"))
Heatmap(jaccard_matrix,  
        col = col_fun,
        cell_fun = function(j, i, x, y, width, height, fill) {
            if(i==j){
              grid.text(sprintf("%.2f", jaccard_matrix[i, j]), x, y, gp = gpar(fontsize = 0))
            }else{grid.text(sprintf("%.2f", jaccard_matrix[i, j]), x, y, gp = gpar(fontsize = 15))}
          },
        cluster_rows = FALSE,
        cluster_columns = FALSE, 
        na_col = "gray",
        show_heatmap_legend = FALSE,
        rect_gp = gpar(col = "black", lwd = 1),
        show_row_names = TRUE,
        row_names_side = c("left"),
        row_names_gp = gpar(fontsize = 15),
        show_column_names = TRUE,
        column_names_side = c("bottom"),
        column_names_gp = gpar(fontsize = 15),
        column_names_rot = 45,
        column_names_centered = FALSE)

col <- colorRampPalette(c("blue","white","red"))
corrplot(jaccard_matrix, 
         method="color", 
         col=col(100),  
         type="full", 
         order="original", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", 
         tl.srt=45, #Text label color and rotation
         # Combine with significance
         #p.mat = p.mat, 
         #sig.level = 0.01, 
         #insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE 
         )
```

## K562

### 2020-05-29 Manuscript/manuscript.Rmd
editted intro

@@
 
-The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed important 3-dimensional (3D) spatial constructs within the human genome such as loops [@rao20143d], Topologically Associated Domains (TADs) [@nora2012spatial;@dixon2012topological], and A/B compartments [@lieberman2009comprehensive].
-Among these, TADs represent regions on the linear genome, at megabase scale, that are highly self-interacting.
-Emerging evidence has linked TADs to critical roles in cell dynamics like gene regulation and cell differentiation, an example being the mechanism by which enhancers loop to come into contact with distal promoters to initiate transcription within these domains [@Lupianez:2015aa; @Franke:2016aa].
-Likewise, disruption of TAD boundaries has been shown to lead to developmental disorders [@lupianez2016breaking], cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@Sun:2018aa; @Meaburn:2007aa].
-Therefore, identifying the location of TAD boundaries remains a top priority in our goal to understand the functionality of the human genome.
+The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of important 3-dimensional (3D) spatial constructs within the human genome such as chromatin loops [@rao20143d], Topologically Associated Domains (TADs) [@nora2012spatial;@dixon2012topological], and A/B compartments [@lieberman2009comprehensive].
+At kilobase scale, gene promotors are often connected via distal regulatory elements, such as enhancers, through chromatin loops, thereby regulating gene expression [@Lupianez:2015aa; @Franke:2016aa].
+Further out, at the megabase scale, TADs represent regions on the linear genome, that are highly self-interacting.
+Emerging evidence has linked TADs to critical roles in cell dynamics and cell differentiation.
+It has been shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological;@krefting2018evolutionary].
+Likewise, disruption of the boundaries that demarcate TADs and loops have been shown to lead to cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@lupianez2016breaking;@Sun:2018aa;@Meaburn:2007aa].
+Therefore, precisely identifying the location of TAD and loop boundaries remains a top priority in our goal to fully understand the functionality of the human genome.
 
-A key factor in locating TAD boundaries is "resolution".
-Due to the high-dimensional nature of Hi-C data, genome binning has been a common strategy for dealing with a low signal-to-noise ratio problem [@li2019comparison].
-Resolution, therefore, determines the bin sizes of the linear genome used to enumerate contacts caused by chromatin folding.
+Several methods have been proposed to identify the genomic coordinates of TAD boundaries throughout the linear genome [@dixon2012topological;@rao20143d;@sexton2012three;@chen2016novo;@filippova2014identification;@shin2016topdom;@weinreb2016identification], less so for chromatin loops [@salameh2019supervised;@kai2018predicting].
+However, a key limitation among most of these "TAD(loop)-callers" is that they are heavily reliant on Hi-C data *resolution*.
+Resolution refers to the sizes of bins used to segment the linear genome as a way to deal with low signal-to-noise incurred by the high dimensional nature of Hi-C data [@li2019comparison].
 Lower resolutions contribute to larger bin sizes, which lead to variability in the location of TAD boundaries.
@@
 Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth, obtaining high resolution remains difficult [@schmitt2016genome].
-While these low resolution Hi-C datasets can be used to probe higher order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define sub-domains and the boundaries that demarcate them [@fudenberg2016formation].
-Furthermore, even at its highest (750 bp [@bonev2017multiscale]), Hi-C sequencing resolution still remains well below the resolution of ChIP-Sequencing experiments used to annotate the genome, which ranges in the tens of base pairs [@mendoza2009genome].
-This resolution gap between 1D and 3D genomic maps can make it difficult to disentangle the role of genomic factors related to TAD boundaries, thereby limiting our understanding of epigenomic regulation and its potential link to chromatin architecture.
-We hypothesize that, by leveraging genomic annotations--defined by high resolution ChIP-Seq data--known to be enriched at TAD boundaries, we may be able more to precisely predict the locations of TAD boundaries at higher resolutions.
+While these low resolution Hi-C datasets can be used to probe higher order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define chromatin loops and TADs [@fudenberg2016formation].
 
-Several methods have been developed to predict TAD boundary location using genomic annotations.
-However, most ignore key characteristics of 3D genomic data that are detrimental to both model performance and accurate boundary identification.
-A method developed by Mourad et al [@mourad2016computational], called *HiCFeat*, used the percentage of overlap between several ChIP-seq defined transcription factor binding site (TFBS) regions and 1 kb genomic bins to build an L1-regularized multiple logistic regression model to predict TAD boundary regions.
-However, such high level of resolution is likely to introduce heavily imbalanced classes created from the proportionally much smaller number of TAD boundary regions compared to non-TAD boundary regions throughout the linear genome.
-*HiCFeat* did not the address class imbalance.
-Instead, model performance was evaluated using area under the receiver operating characteristic curve (AUROC) which is known to be insensitive to class imbalance, creating artificially inflated values influenced by the majority class [@prati2011survey; @wei2013role].
-<!--A more appropriate evaluation tool to consider would be a composite metric such as Matthews Correlation Coefficient (MCC), which penalizes for both false positives and false negatives.--> Furthermore, by only considering the percentage of overlap in defining the feature space, *HiCFeat* is limited in its granularity given that many regions on the linear genome will not be overlapped with any genomic annotations.
-<!--This, likely being further exacerbated by the class imbalance.--> Two additional studies were proposed in 2015 and 2017 respectively, one using histone modifications in a Bayesian Additive Regression Trees (BART) model [@huang2015predicting] and the other using combined sets of TFBS, DNase I hypersensitive sites, and histone modifications together in an L2-based regularized linear model [@hong2017computational].
-The BART model was built on relatively high resolution Hi-C data at 5 kb, while the L2-regularized model used 200 kb resolution Hi-C data.
-Both methods addressed class imbalance by performing random under-sampling (RUS), and used the elemental read count that appeared in each bin to describe the relationship between ChIP-seq annotations and genomic regions.
-Firstly, given the large disparity between the number of TAD vs non-TAD boundary regions, performing random under-sampling alone is likely to be unstable and introduce bias.
-Also, it is unclear how other re-sampling solutions compare to simple random under-sampling such as random over-sampling or a weighted combination of both random under- and over-sampling together.
-Secondly, using read count overlap as the feature space suffers from similar limitations as the percentage of overlap.
-Moreover, it is unclear how either of these feature engineering steps compare to enumerating the distance in base pairs between ChIP-seq annotations and genomic bins in TAD boundary prediction, which offer a more spatial measure of association.
+Another limitation among TAD(loop)-callers is their disregard for the fundamental roles of functional genomic elements on chromatin folding.
+It has been shown that particular genomic elements are enriched at TAD(loop) boundaries.
+Namely, the insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been hypothesized to comprise components of the loop extrusion model, whereby DNA is extruded through cohesin rings forming loops [@hansen2018recent;@fudenberg2016formation;@alipour2012self;@sanborn2015chromatin].
+Additionally, distinct patterns of histone modifications have also been shown to be featured at boundaries, including H3K36 timethylation (H3K36me3) [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
+These elements are annotated on the genome using chromatin immunoprecipitation followed by high-throughput DNA sequencing (ChIP-seq).
+Even at its highest (750 bp [@bonev2017multiscale]), Hi-C sequencing resolution still remains well below the resolution of ChIP-seq experiments, which ranges in the tens of base pairs [@mendoza2009genome].
+Therefore, leveraging such elements in a supervised learning framework lends itself to the possibility of more precisely predicting the locations of TAD (or loop) boundaries at higher resolutions.
 
-Given the many pitfalls encountered by previous methods we set out to establish a unified approach toward TAD boundary prediction.
-In this study we first developed a computational framework aimed at determining the set of data level characteristics necessary for optimal TAD boundary prediction.
-We assessed the Matthews Correlation Coefficient (MCC) of 10-fold cross-validated random forest classifiers with different combinations of model inputs consisting of vary data resolutions, re-sampling techniques, and feature engineering steps.
-We showed that 10 kb resolution data, combined with both random over- and under-sampling, and a feature space composed of distances between ChIP-seq annotations and genomic bins yielded the best model performances for TAD boundary prediction.
-We showed that our optimally built model was able to identify known architectural proteins CTCF, RAD21, SMC3, and ZNF143 as exhibiting high predictive importance, confirming their biological functionality near TAD boundaries.
-We then aimed to use our optimally built model to more precisely predict the location of TAD boundaries at base pair resolution.
-We showed that, compared to TAD boundaries identified by a TAD caller [@durand2016juicebox], these top ranked transcription factors were much more enriched near the predicted TAD boundaries identified by our model indicating much more precise locations throughout the linear genome.
-This improved precision in TAD boundary location can provide insight into the role that epigenomics has on the spatial architecture of the human genome.
-
-<!--
-Extensive research using high resolution maps (ranging from 750 bp to 1 mb) have probed much of the aspects of 3D chromatin architecture identifying several epigenomic modifications associated with TAD boundaries [@rao20143d; @bonev2017multiscale].
-For instance, it is known that the CCCTC-binding factor (CTCF) is enriched at TAD boundaries acting as an insulator interfering with enhancer-promotor interactions [@ghirlando2016ctcf; @song2017ctcf; @ong2014ctcf].
-Additional transcription factors including SMC1, SMC3, and RAD21 have also been shown to colocalize near TAD boundaries forming a cohesin ring under the proposed loop extrusion model, whereby loops are formed during interphase [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
--->
+???stopped here
 
@@
 We further optimized our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
-In summary, our framework was able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@fudenberg2016formation; @alipour2012self].
+In summary, our framework was able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@hansen2018recent;@fudenberg2016formation;@alipour2012self;@sanborn2015chromatin].
 
@@
 Likewise, our RF model built using *distance*-type predictors was consistently able to identify the group of the top known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143 as being highly predictive of TAD(loop) boundary regions across both cell lines.
-These are known components of the loop extrusion model, an established theory for how loops are made by a ring-shaped adenosine triphosphatase complex called cohesin [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+These are known components of the loop extrusion model, an established theory for how loops are made by a ring-shaped adenosine triphosphatase complex called cohesin [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
 This suggested that random forests, when tuned and feature engineered correctly, are highly effective in accurately predicting boundary regions, contradicting a previous study that found simple multiple linear regression out performed random forests in a TAD boundary prediction setting using both human and drosophila Hi-C data [@mourad2016computational].

### 2020-05-30 Manuscript/manuscript.Rmd
added concluding paragraph to intro

@@
 Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth, obtaining high resolution remains difficult [@schmitt2016genome].
-While these low resolution Hi-C datasets can be used to probe higher order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define chromatin loops and TADs [@fudenberg2016formation].
+While these low resolution Hi-C datasets can be used to probe higher order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define TADs and chromatin loops [@fudenberg2016formation].
 
@@
 
-???stopped here
+Here we present *preciseTAD*, an R package for precise identification of TAD(or loop) under a supervised machine learning framework.
+Our method builds upon an optimized random forest classification model (RF) that leverages high resolution ChIP-seq data in the form of regulatory elements (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS).
+We introduce a novel technique for building RF classifiers in a boundary prediction setting composed of a resolution-specific binning process and feature engineering procedure.
+*preciseTAD* then employs density-based clustering (DBSCAN) and scalable partitioning around medoids (CLARA) on prediction probabilities to select the most biologically meaningful boundary coordinates as base pairs on the linear genome, thereby circumventing resolution restrictions of conventional TAD- and loop-callers.
+We demonstrate that predictions made by *preciseTAD* are more enriched for known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143.
+Further, we show that *preciseTAD* boundaries are more conserved across cell lines, highlighting their biological significance.
+This improved precision in TAD and loop boundary location can provide insight into the role that epigenomics has on the spatial architecture of the human genome.
 

### 2020-06-30 Manuscript/manuscript.Rmd
Edits through Introduction

@@
 Several methods have been proposed to identify the genomic coordinates of TAD boundaries throughout the linear genome [@dixon2012topological;@rao20143d;@sexton2012three;@chen2016novo;@filippova2014identification;@shin2016topdom;@weinreb2016identification], less so for chromatin loops [@salameh2019supervised;@kai2018predicting].
-However, a key limitation among most of these "TAD(loop)-callers" is that they are heavily reliant on Hi-C data *resolution*.
+[???
+Check refs, the current ones are suboptimal.
+Check SpectralTAD paper for refs about TAD callers, use https://github.com/mdozmorov/HiC_tools#loop-callers for loop callers] However, a key limitation among most of these TAD- and loop callers, referred hereafter as TAD callers for brevity, is that they are heavily reliant on Hi-C data *resolution*.
 Resolution refers to the sizes of bins used to segment the linear genome as a way to deal with low signal-to-noise incurred by the high dimensional nature of Hi-C data [@li2019comparison].
-Lower resolutions contribute to larger bin sizes, which lead to variability in the location of TAD boundaries.
+Lower resolutions contribute to larger bin sizes, which lead to uncertainty in the location of TAD boundaries.
 Due to high sequencing costs, most available Hi-C datasets have relatively low resolution, ranging from 25 kb to 100 kb.
@@
 
-Another limitation among TAD(loop)-callers is their disregard for the fundamental roles of functional genomic elements on chromatin folding.
-It has been shown that particular genomic elements are enriched at TAD(loop) boundaries.
-Namely, the insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been hypothesized to comprise components of the loop extrusion model, whereby DNA is extruded through cohesin rings forming loops [@hansen2018recent;@fudenberg2016formation;@alipour2012self;@sanborn2015chromatin].
-Additionally, distinct patterns of histone modifications have also been shown to be featured at boundaries, including H3K36 timethylation (H3K36me3) [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
+Another limitation among TAD callers is that they disregard prior knowledge about functional genomic elements associated with TAD and loop boundaries.
+The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been hypothesized to comprise components of the loop extrusion model, whereby DNA is extruded through cohesin rings forming loops [@hansen2018recent;@fudenberg2016formation;@alipour2012self;@sanborn2015chromatin].
+[???
+Rewrite, simplify, describe enrichment first, loop extrusion second] Additionally, distinct patterns of histone modifications have also been shown to be featured at boundaries, including H3K36 timethylation (H3K36me3) [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
 These elements are annotated on the genome using chromatin immunoprecipitation followed by high-throughput DNA sequencing (ChIP-seq).
@@
 This improved precision in TAD and loop boundary location can provide insight into the role that epigenomics has on the spatial architecture of the human genome.
+[???
+Rewrite.
+Say the main methodology first - model on 4 TFBSs, uses distance, RUS, technique for bp-level prediction, one sentence per point.
+Detail next - BroadHMM and histone were tested, OC, OP were tested, various sampling techniques.
+Conclude with findings and package availability]
 
@@
 
-A limitation of *preciseTAD* is that it is dependent on "ground truth" boundaries provided by a user-defined TAD(loop)-caller.
+A limitation of *preciseTAD* is that it is dependent on "ground truth" boundaries provided by a user-defined TAD caller.
 Ideally we would perform simulation studies to benchmark *preciseTAD* against simulated boundaries.

### 2020-07-01 Manuscript/manuscript.Rmd
changed title

--- 2020-05-30 Manuscript/manuscript.Rmd
@@
 ---
-title: Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings
+title: preciseTAD: A machine learning framework for precise TAD boundary prediction at base pair resolution
 csl: styles.ref/genomebiology.csl
 output:
-  pdf_document: default
   word_document:
     reference_docx: styles.doc/NIH_grant_style.docx
+  pdf_document: default
 bibliography: References/references.bib

### 2020-07-01 Manuscript/manuscript.Rmd
cleaned up manuscript by adding revisions; changed title and abstract; changed "Comparing called vs predicted boundaries" section to deeptools; added refs

--- 2020-06-30 Manuscript/manuscript.Rmd
@@
 ---
-title: Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings
+title: "preciseTAD: A machine learning framework for precise TAD boundary prediction at base pair resolution"
 csl: styles.ref/genomebiology.csl
 output:
-  pdf_document: default
   word_document:
     reference_docx: styles.doc/NIH_grant_style.docx
+  pdf_document: default
 bibliography: References/references.bib
@@
 
-**Background.** Topologically Associated Domains (TADs) represent fundamental building blocks that lead to the organization and regulation of the three-dimensional (3D) genome.
-The enrichment of several epigenetic marks at TAD boundaries suggests a strong epigenetic component of TAD boundary formation.
-Several methods have been developed to leverage the growing amount of (epi)genomic annotation data for predicting TAD boundaries; however, they overlooked key characteristics of the data including spatial associations between genomic annotations and boundaries, as well as the severe imbalance in TAD-boundary vs non-TAD boundary defined genomic regions.
-Furthermore, resolution of Hi-C data remains well below the resolution of epigenomic assays (hundredths of bases for ChIP-seq) affecting the ability of Hi-C sequencing in discerning gene-level features of chromatin.
-This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited our understanding of epigenomic regulation of gene expression and its potential link to chromatin architecture.
-
-**Methods.** We first developed an ensemble framework for optimizing data level characteristics necessary for TAD boundary prediction including combinations of 5 Hi-C data resolutions (5 kb to 100 kb), 3 spatially defined predictor types, and 4 re-sampling techniques, across the GM12878 and K562 cell lines.
-We then aimed to predict TAD boundary location on a 1D genomic map by validating optimally built cell line specific models at basepair resolution.
-
-**Results.** We demonstrate with our ensemble framework that cell line specific random forest classifiers built on 10 kb resolution Hi-C data, with distance-type predictors, using SMOTE (*Synthetic Minority Oversampling Technique*) re-sampling yield optimal predictive performances, and outperform existing methods.
-Cell specific transcription factor binding sites (TFBS) were the best type of genomic annotations for predicting TAD boundaries when directly compared with histone modifications and chromatin states; we identified the well-known CTCF, SMC3, RAD21, and ZNF143 TFBS known to be enriched at TAD boundaries.
-Additionally, TAD boundary regions predicted at basepair resolution using our optimally built cell line specific models were found to be significantly closer to known enriched epigenomic marks indicating more accurate identification of TAD boundaries than existing Hi-C sequencing technologies.
-
-**Conclusions.** Our results outline strategies for predictive modeling of 3D genomic domains using 1D genome annotation data.
-The accurate modeling of TAD boundaries will improve our understanding of how epigenetics shapes the 3D structure of the genome.
+Chromosome conformation capture combined with high-throughput sequencing experiments (Hi-C) have revealed that chromatin undergoes layers of compaction through DNA looping and folding, forming dynamic 3D structures.
+Among these are Topologically Associating Domains (TADs), which are known to play critical roles in cell dynamics like gene regulation and cell differentiation.
+Precise TAD mapping remains difficult, as it is strongly reliant on Hi-C data resolution.
+Obtaining genome-wide chromatin interactions at high-resolution is costly resulting in variability in true TAD boundary location by TAD calling algorithms.
+To aid in the precise identification of TAD boundaries we developed preciseTAD, a machine learning framework that leverages the spatial relationship of many high resolution ChIP-seq defined genomic elements, coupled with density-based clustering  and scalable partitioning techniques.
+Our framework precisely predicts chromosome-specific TAD boundaries on multiple cell types.
+We show that known molecular drivers of 3D chromatin including CTCF, RAD21, and SMC3 are more enriched at our predicted TAD boundaries compared to the boundaries identified by the popular ARROWHEAD TAD caller.
+Our results provide useful insights into the 3D organization of the human genome.
 
@@
 Emerging evidence has linked TADs to critical roles in cell dynamics and cell differentiation.
-It has been shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological;@krefting2018evolutionary].
+Studies have shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological;@krefting2018evolutionary].
 Likewise, disruption of the boundaries that demarcate TADs and loops have been shown to lead to cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@lupianez2016breaking;@Sun:2018aa;@Meaburn:2007aa].
-Therefore, precisely identifying the location of TAD and loop boundaries remains a top priority in our goal to fully understand the functionality of the human genome.
+Therefore, precisely identifying the location of TAD and chromatin loop boundaries remains a top priority in our goal to fully understand the functionality of the human genome.
 
@@
 Check SpectralTAD paper for refs about TAD callers, use https://github.com/mdozmorov/HiC_tools#loop-callers for loop callers] However, a key limitation among most of these TAD- and loop callers, referred hereafter as TAD callers for brevity, is that they are heavily reliant on Hi-C data *resolution*.
-Resolution refers to the sizes of bins used to segment the linear genome as a way to deal with low signal-to-noise incurred by the high dimensional nature of Hi-C data [@li2019comparison].
+Resolution refers to the sizes of genomic bins used to segment the linear genome as a way to deal with low signal-to-noise incurred by the high dimensional nature of Hi-C data [@li2019comparison].
 Lower resolutions contribute to larger bin sizes, which lead to uncertainty in the location of TAD boundaries.
@@
 Another limitation among TAD callers is that they disregard prior knowledge about functional genomic elements associated with TAD and loop boundaries.
-The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been hypothesized to comprise components of the loop extrusion model, whereby DNA is extruded through cohesin rings forming loops [@hansen2018recent;@fudenberg2016formation;@alipour2012self;@sanborn2015chromatin].
+The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been hypothesized to comprise components of the loop extrusion model, whereby DNA is extruded through cohesin rings forming chromatin loops [@hansen2018recent;@fudenberg2016formation;@alipour2012self;@sanborn2015chromatin].
 [???
@@
 Even at its highest (750 bp [@bonev2017multiscale]), Hi-C sequencing resolution still remains well below the resolution of ChIP-seq experiments, which ranges in the tens of base pairs [@mendoza2009genome].
-Therefore, leveraging such elements in a supervised learning framework lends itself to the possibility of more precisely predicting the locations of TAD (or loop) boundaries at higher resolutions.
+Therefore, leveraging such elements in a supervised machine learning framework lends itself to the possibility of more precisely predicting the locations of TAD (or loop) boundaries at much higher resolutions.
 
-Here we present *preciseTAD*, an R package for precise identification of TAD(or loop) under a supervised machine learning framework.
-Our method builds upon an optimized random forest classification model (RF) that leverages high resolution ChIP-seq data in the form of regulatory elements (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS).
+Here we present *preciseTAD*, an R package for precise identification of TAD(or loop) boundaries under a supervised machine learning framework.
+Our method builds upon an optimized random forest (RF) classification model that leverages high resolution ChIP-seq data in the form of regulatory elements (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS).
 We introduce a novel technique for building RF classifiers in a boundary prediction setting composed of a resolution-specific binning process and feature engineering procedure.
-*preciseTAD* then employs density-based clustering (DBSCAN) and scalable partitioning around medoids (CLARA) on prediction probabilities to select the most biologically meaningful boundary coordinates as base pairs on the linear genome, thereby circumventing resolution restrictions of conventional TAD- and loop-callers.
+*preciseTAD* then employs density-based clustering (DBSCAN) and scalable partitioning around medoids (CLARA) on prediction probabilities to select the most biologically meaningful boundary coordinates on the linear genome, thereby circumventing resolution restrictions of conventional TAD- and chromatin loop-callers.
 We demonstrate that predictions made by *preciseTAD* are more enriched for known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143.
@@
 
-In Hi-C, each chromosome is binned into non-overlapping regions of the same length *r*, typically 5kb and above.
+In Hi-C, each chromosome is binned into non-overlapping regions of the same length *r*, typically 5 kb and above.
 The *r* parameter defines the resolution of Hi-C data.
 Consequently, the location of TAD boundaries is limited by the resolution *r*.
-We designed a strategy called _shifted binning_ that partitions the genome into regions of the same length *r*, but with middle points corresponding to boundaries defined by the original binning.
+Here, we designed a strategy called _shifted binning_ that partitions the genome into regions of the same length *r*, but with middle points corresponding to boundaries defined by the original binning.
 
@@
 It should be noted that models built using a *Peak Signal Strength* feature space were only composed of histone modifications and transcription factor binding sites.
-That is, they did not include BroadHMM chromatin segmentations.
+That is, they did not include any BroadHMM chromatin segmentations.
 
@@
 Re-sampling was then performed on $A$.
-An RF classifier was then trained on $A$ using 5-fold cross-validation to tune for the number of annotations, *p*, to consider at each node (*mtry*).
+An RF classifier was then trained on $A$ using 3-fold cross-validation to tune for the number of annotations, *p*, to consider at each node (*mtry*).
 The number of trees (*ntree*) that were aggregated for each RF model was set to 500.
@@
 
-<!--
-$$F1 - Score = \frac{2TP}{2TP + FP + FN}$$
--->
-
-<!--
-$$
-MCC = \frac{TP \times TN - FP \times FN}{\sqrt{ (TP + FP)(TP+FN)(TN+FP)(TN+FN) }}
-$$
--->
-
 $$BA = \dfrac{1}{2}\left( \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} \right)$$
 
-<!--
-$$Informedness = \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} - 1$$
--->
-
 where TP refers to the number of bins correctly identified as containing a boundary (true positives), FP refers to the number of bins incorrectly identified as containing a boundary (false positives), TN refers to the number of bins correctly identified as not containing a boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a boundary (false negatives).
-Each of these quantities are obtained from the confusion matrix created by validating the model on the testing set.
-<!--We refer to the complete computational framework used to compare random forest model inputs as *TADRF*.--> Performances were aggregated across each $i^{th}$ holdout chromosome using means and standard deviations.
+Each of these quantities are obtained from the confusion matrix created by validating the model on the test data.
+Performances were aggregated across each $i^{th}$ holdout chromosome using means and standard deviations.
 
@@
 Many genomic annotations, notably architectural proteins, tend to exhibit an extensive pattern of colocalization (correlation) [@van2014insulator].
-To suitably reduce the feature space and improve computational efficiency, while maintaining optimal performance, we implemented recursive feature elimination.
+To suitably reduce the feature space and improve computational efficiency, while maintaining optimal performance, we implemented recursive feature elimination (RFE).
 In doing so, we estimated the near optimal number of necessary features to include in the best fitting RF model.
-The best performing subset was identified, ranging from 2 to the maximum number of features by power of 2.
+The best performing subset was identified, ranging from 2 to the maximum number of features by powers of 2.
 We then aggregated the predictive importance of the union of the optimal set of features across chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top ranked annotations for predicting boundary regions.
@@
 To demonstrate, we implemented an optimally built RF model using the framework described above.
-That is, a random forest model built on the optimal combination of data resolution (binning), predictor type (feature space), re-sampling technique (class balancing correction), and annotations (most informative genomic elements).
+That is, a random forest model built on the optimal combination of data resolution (binning), predictor type (feature space), re-sampling technique (class balancing correction), and top ranked annotations (most informative genomic elements).
 
@@
 To precisely identify a single base pair among each PTBR, *preciseTAD* then implements an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
-Thusly, the corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative and biologically meaningful base pair within each clustered PTBR.
+Thusly, the corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative and biologically meaningful base pair coordinate within each clustered PTBR.
 
@@
 
-Next, we evaluated the biological significance of our predicted boundaries with respect to the enrichment of several known molecular drivers of 3D chromatin architecture including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
-Enrichmed heatmaps were used to compare preciseTAD boundaries to both ARROWHEAD and PEAKACHU called boundaries using the `EnrichedHeatmap` R package (version 1.14.0) [@gu2018enrichedheatmap].
+afgan2018galaxy, ramirez2016deeptools2
+
+Next, we assessed the biological significance of our predicted boundaries with respect to the enrichment profiles of several known molecular drivers of 3D chromatin architecture including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
+To do so, we used the computeMatrix and plotHeatmap tools offered by DeepTools [@ramirez2016deeptools2] via integration with the Galaxy project [@afgan2018galaxy].
+Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum test.
+
+Furthermore, we assessed the hypothesis that TADs and chromatin loops are conserved  [@dixon2012topological; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa] by comparing predicted and called boundaries between the GM12878 and K562 cell lines.
+Boundaries were first flanked by resolution, *r*, and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0) and evaluated using the Jaccard index defined as
+
+$$J_{(A,B)} = \dfrac{A \cap B}{A \cup B}$$
+
+where A and B represent genomic regions created by flanking called and predicted boundaries.
+That is, between cell lines, the number of overlapping flanked boundaries divided by the total number of flanked boundaries.
+Wilcoxon rank sum tests were used to compare chromosome-specific jaccard indices across cell lines, between *preciseTAD* boundaries and both ARROWHEAD and PEAKACHU boundaries respectively.
+All statistical analyses were performed in R version 4.0.1.
+The alpha level of significance was set to 0.05 for all statistical tests.
+
+<!--using the `EnrichedHeatmap` R package (version 1.14.0) [@gu2018enrichedheatmap].
 For each boundary (both called and predicted), a 5000 bp flank was created on either side.
@@
 $$v_{c} = \dfrac{\Sigma_{j}^{m} \Sigma_{i}^{n}x_{ij}w_{ij}}{L}$$
+
 where $x_{ij}$ is the total number of base pairs of annotation $i$ in window $j$ and $w_{ij}$ is the number of base pairs that overlap between annotation $i$ and window $j$.
@@
 $$s_{e} = \Sigma_{d=1}^{n_{1}}\left(\dfrac{x_{1d}* d}{n_{1}} \right) + \Sigma_{u=1}^{n_{2}}\left(\dfrac{x_{2u}* (n_{2} - u + 1)}{n_{2}} \right)$$
-where $n_{1}$ and $n_{2}$ represent the number of downstream and upstream coverage values to sum over. Here, $n_{1}=n_{2}=100$.
-
-Additionally, we compared the median $log_2$ distances between TAD boundaries and the same top predictive transcription factor binding sites using Wilcoxon Rank-Sum test.
-
-Furthermore, under the hypothesis that TAD boundaries are highly concerved across cell types [@dixon2012topological; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa], we assessed the conservation of our predicted TAD boundaries across cell lines and prediction algorithms.
-Boundaries were flanked by resolution and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0) and evaluated using the Jaccard index defined as
-
-$$J_{(A,B)} = \dfrac{A \cap B}{A \cup B}$$
-
-where A and B represent genomic regions created by flanking called and predicted boundaries.
-That is, between cell lines, the number of overlapping flanked boundaries divided by the total number of flanked boundaries.
-Wilcoxon rank sum tests were used to compare chromosome-specific jaccard indices across cell lines, between *preciseTAD* boundaries and both ARROWHEAD and PEAKACHU boundaries respectively.
-The alpha level of significance was set to 0.05 for all statistical tests.
+where $n_{1}$ and $n_{2}$ represent the number of downstream and upstream coverage values to sum over. Here, $n_{1}=n_{2}=100$.-->
 
@@
 
-## Developing a computational framework for optimal TAD boundary prediction
+## Developing a machine learning framework for optimal TAD boundary prediction
 
-We developed a computational framework<!--, refered to as *TADRF*,--> aimed at determining the optimal set of data level characteristics necessary for topologically associated domain (TAD) boundary prediction.
+We developed a machine learning framework<!--, refered to as *TADRF*,--> aimed at determining the optimal set of data level characteristics necessary for topologically associated domain (TAD) boundary prediction.
 We chose the random forest (RF) machine learning algorithm as our binary classification tool.
 The reason for choosing RF was two-fold: (1) In order to devise a tunable prediction rule in a supervised learning framework that is both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors with respect to their ability to predict boundary regions [@boulesteix2012overview].
-We then leveraged our optimally built RF to precisely predict the genomic coordinates of both TAD and loop boundaries at base pair resolution.
+We then developed *preciseTAD*, an algorithm which leverages an optimally built RF to precisely predict the genomic coordinates of both TAD and chromatin loop boundaries at base pair resolution.
 
-Our framework is resolution-specific and uses called TAD and loop boundaries as ground truth to establish TAD(loop)-boundary and non-TAD(loop) boundary regions.
-To demonstrate, we applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1).
+Our framework is resolution-specific and uses called TAD or loop boundaries as ground truth to establish TAD(loop)-boundary and non-TAD(loop) boundary regions.
+To demonstrate, we applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines obtained from GEO GSE63525 (Supplementary Table 1).
 TADs were subsequently called using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-For loop boundaries we opted to use boundaries obtained by the PEAKACHU tool for the GM12878 and K562 cell lines at 10 kb resolution [@salameh2019supervised].
+For loop boundaries, we opted to use boundaries obtained by the PEAKACHU prediction tool for the GM12878 and K562 cell lines at 10 kb resolution [@salameh2019supervised].
 [???
@@
 
-Boundary regions were defined as regions containing a called boundary ($Y = 1$), while non-boundary regions were defined as genomic bins that did not contain a boundary ($Y = 0$) (Figure 1A, see Methods).
+Boundary regions were defined as regions containing a called boundary ($Y = 1$), while non-boundary regions were defined as genomic bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
 The total number of TADs, TAD boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 3).
-The number of non-boundary regions highly outnumbered boundary regions, and these results were consistent for loop boundaries (Supplementary Table 4).
+The number of non-boundary regions highly outnumbered boundary regions, with results consistent for loop boundaries as well (Supplementary Table 4).
 Such disproportional presence of examples in one class is known as a "class imbalance" problem that negatively affects model performance [@prati2011survey; @wei2013role].
@@
 A total of 78 cell line specific functional genomic annotations were used to build the feature space of downstream random forest models.
-These annotations included BroadHMM shromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS, Supplementary Table 2).
+These annotations included BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS, Supplementary Table 2).
 Four feature engineering procedures were developed for each genomic annotation (Figure 1B, see Methods) with the goal to improve boundary predictions by accounting for signal strength association (Signal), direct (OC), proportional (OP), and spatial (Distance) relationships between TAD boundaries and genomic annotations.
@@
 In summary, we considered combinations of data from a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, with a specific engineered feature space *P = {Signal, OC, OP, Distance}*, and re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
-Once the model inputs were established, a random forest classifier was trained on $n-1$ chromosomes, while reserving the $i^{th}$ chromosome for testing.
-Five-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed to default values of 500 and 1 respectively.
+Once the model inputs were established, a random forest classifier was trained on $n-1$ autosomal chromosomes, while reserving the $i^{th}$ chromosome for testing.
+Three-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed to default values of 500 and 1 respectively.
 Model inputs were evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (See Methods).
-<!--The results presented are for the ARROWHEAD boundaries, with PEAKACHU boundaries presented in the Supplementary material.
-Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |S| \times |C|$ different ensemble systems, totaling $2 \times 5 \times 4 \times 4 \times 21 (= 3360)$ models.--> [???
-When we have all results, Peakachu results will likely need to be described in parallel.
-They are about loops, theoretically different from TAD boundaries.
-For discussion]
 
-![**A diagram of the ensemble framework detailing the steps for combining different inputs used in the random forest model building pipeline.** Step 1 is to establish the chromosome-specific rowise (genomic bins) and columnwise (genomic annotations) dimensions of the data matrix, **A**, by combining a resolution (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)) for the $n-1$ chromosomes.
-Step 2 is to use the binned data matrix for the holdout chromosome $i$ as the test data.
+![**A diagram of the machine learning framework detailing the steps for combining different inputs used in the random forest model building pipeline.** Step 1 is to establish the chromosome-specific rowise (genomic bins) and columnwise (genomic annotations) dimensions of the data matrix, **A**, by combining a resolution (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)) for the $n-1$ autosomal chromosomes.
+Step 2 is to reserve the binned data matrix for the holdout chromosome $i$ as the test data.
 Step 3 is to apply a re-sampling technique to the training set (no re-sampling, random over-sampling, random under-sampling, or SMOTE re-sampling).
-Step 4 is to train the random forest model and perform 5-fold cross-validation to tune for the *mtry* parameter.
+Step 4 is to train the random forest model and perform 3-fold cross-validation to tune for the *mtry* parameter.
 Finally, step 5 is to validate the model on the separate test data and evaluate model performance using balanced accuracy (BA).](Figures/figure2_ensemble_framework.png)
@@
 |100 kb	     |1031                         | 1883                                  | 26768                        | 0.07            |
-Table: Domain data and class imbalance summaries across resolutions for GM12878.
+Table: Domain data and class imbalance summaries across resolutions for ARROWHEAD on the GM12878 cell line.
 
@@
 
-Expectedly, when using data with class imbalance present, that is, the data were used as-is, the models exhibited low balanced accuracies, with very little variability among different resolutions (Figure 3).
+Expectedly, when using data with class imbalance present, that is, no re-sampling, the models exhibited low balanced accuracies, with very little variability among different resolutions (Figure 3).
 Similarly, poor performances were found when using ROS as well.
@@
 We found that RUS marginally outperformed SMOTE as the most optimal class balancing technique for all resolutions and predictor types.
-These results suggest that simple randomly under-sampling alone can drastically improve TAD boundary prediction.
+These results suggest that simple random under-sampling alone can drastically improve TAD boundary region prediction.
 
@@
 These results were found to be consistent for the K562 cell line (Supplementary Figure 2).
-Random forest models built on PEAKACHU loop boundaries with SMOTE resampling marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3).
-In summary, random under-sampling and SMOTE, distance-type predictors, and Hi-C data at 5kb resolution yields an optimally performing cell line-specific random forest classification model for TAD and loop boundary predictions.
+Random forest models built on PEAKACHU loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3).
+Five kilobase resolution genomic bins was found to result in optimal prediction for both TAD and loop boundaries, on both cell lines.
+Our results indicate that random under-sampling, distance-type predictors, and Hi-C data at 5kb resolution are the optimal set of data level characteristics for both TAD and chromatin loop boundary region prediction.
 
@@
 
-![**???[needs updating with new framework, takes longest, do last]Models built using distance-type predictors combined with random under-sampling at 5 kb yielded optimal predictive performance for GM12878.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
+![**???[needs updating with new framework, takes longest, do last]Models built using distance-type predictors combined with random under-sampling at 5 kb yielded optimal TAD boundary region predictive performance for GM12878.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
 Performances are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
@@
 
-We sought to further optimize our TAD prediction model by performing recursive feature elimination to avoid overfitting and select only the most influential TFBS across all chromosomes.
+We sought to further optimize our TAD boundary region prediction model by performing recursive feature elimination to avoid overfitting and select only the most influential TFBS across all autosomal chromosomes.
 We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figures 4B).
@@
 
-![**Assessing top ranked transcription factors in TAD and loop boundary prediction for GM12878.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using specific classes of functional genomic elements as the feature space including histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+![**Assessing top ranked transcription factors in TAD and loop boundary region prediction for GM12878.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary region prediction models using distance-type specific classes of functional genomic elements as the feature space including histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.
-Error bars represent standard deviation from the cross-validated accuracy across each chromosome.
+Error bars represent standard deviation from the cross-validated balance accuracy across each autosomal chromosome.
 (C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.](Figures/figure4_annots_specifc_rfe_importances_arrowhead_peakachu.png)
@@
 
+<!--
 At this point, we opted to implement preciseTAD using an optimally built whole genome random forest model.
@@
 (Supplementary Figures 6-7).
+-->
 
-When built using ARROWHEAD, at 5 kb, *preciseTAD* was able to predict a total of ???
+When built using ARROWHEAD ground truth boundaries at 5 kb, *preciseTAD* was able to predict a total of ???
 and ???
@@
 This is attributed to ARROWHEAD's inherent inflation of called TAD boundaries, especially near fuzzy areas along the diagonal of Hi-C contact matrices (Figure 5A).
-Likewise, under the framework of *preciseTAD*, any two TADs are inherently demarcated by only one predicted TAD boundary, leading to comparatively less TAD boundaries.
-Visually speaking, we also found that predicted TAD boundaries identified by *preciseTAD* were much more likely to demarcate high concentrations of inter-chromosomal contacts among Hi-C contact matrices (Figure 5A).
-When built using PEAKACHU loop boundaries, *preciseTAD* was able to predict a total ???
-and ???
-boundaries for GM12878 and K562 cell lines respectively.
-This can be attributed to the fact that PEAKACHU's is built using soley CTCF sites, while *preciseTAD* also incorporates information from other architectural proteins including RAD21, SMC3, and ZNF143.
+However, under the framework of *preciseTAD*, any two TADs are inherently conjoined by only one predicted TAD boundary, leading to comparatively less TAD boundaries.
+Visually speaking, we also found that predicted TAD boundaries identified by *preciseTAD* were much more likely to demarcate high concentrations of inter-chromosomal contacts as seen on a Hi-C contact matrix (Figure 5A).
+[???add peakachu totals when ready]
 
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
-Enriched heatmaps indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or PEAKACHU boundaries alone (Figure 5 B-C.
+Enriched heatmaps indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or PEAKACHU boundaries alone (Figure 5 B-C).
 Likewise, *preciseTAD* boundaries were also more enriched for other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 8-9).
@@
 vs ARROWHEAD and PEAKACHU respectively) (Figure 5D, Supplementary Figure 10-11).
-We also inspected the affect of resolution on locations of TAD boundaries specifically.
+We also inspected the affect of resolution on locations of our predicted TAD boundaries.
 We found that *preciseTAD* boundaries exhibited higher pairwise Jaccard indices between adjacent resolutions than ARROWHEAD boundaries, thus implying stronger invariance toward resolution (Figure 5E).
 
-![**preciseTAD boundaries are enriched in CTCF sites.** (A) Visualizing locations of predicted vs called ARROWHEAD TAD boundaries on GM12878 (chr 21: 15150000-17270000).
+![**preciseTAD boundaries are enriched in CTCF sites.** (A) Visualizing locations of predicted vs called ARROWHEAD TAD boundaries on GM12878 (chr 11: 33000000-34600000).
 The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.
@@
 (D) $Log_{2}$ genomic distances from boundaries to nearest CTCF site between preciseTAD boundaries and both ARROWHEAD and PEAKACHU boundaries, respectively.
-(E) Matrix of pairwise Jaccard indices across resolutions shows more invariance toward resolution for *preciseTAD* (upper triangular) compared to ARROWHEAD (lower triangular).](Figures/figure5_enrichment_and_log2dist_ctcf.png)
+(E) A atrix of pairwise Jaccard indices across resolutions shows more invariance toward resolution for *preciseTAD* (upper triangular) compared to ARROWHEAD (lower triangular).???update when ready](Figures/figure5_enrichment_and_log2dist_ctcf.png)
 
@@
 Subsequent comparisons of *preciseTAD* with both ARROWHEAD and PEAKACHU revealed that our predicted boundaries were more conserved between the GM12878 and K562 cell lines.
-To assess conservation, we evaluated the overlap between cell line specific boundaries after flanking by the resolution use to make predictions.
+To assess conservation, we evaluated the overlap between cell line specific boundaries after flanking by the resolution used to make predictions.
 Boundaries involving ARROWHEAD were flanked by 5 kb, while boundaries involving PEAKACHU were flanked by 10 kb.
@@
 of *preciseTAD* boundaries were conserved across cell lines when built on ARROWHEAD and PEAKACHU boundaries respectively (Figure 6A).
-Additionally, median jaccard index (MJI) was found to be 0.472 (IQR=0.441-0.503; p=???) and 0.647 (IQR=0.646-0.647; p=???) for *preciseTAD* predicted TAD and loop boundaries (Supplementary Table 5).
+Additionally, the median jaccard index (MJI) was found to be 0.472 (IQR=0.441-0.503; p=???) and 0.647 (IQR=0.646-0.647; p=???) for *preciseTAD* predicted TAD and loop boundaries (Supplementary Table 5).
 Comparatively, only 25% (MJI=0.284; IQR=0.268-0.301) and 49% (MJI=0.509; IQR=0.503-0.515) of called/predicted ARROWHEAD and PEAKACHU boundaries were conserved (Figure 6A, Supplementary Table 5).
@@
 *preciseTAD* leverages a random forest (RF) classification algorithm built on ground truth TAD(loop) boundaries obtained from a TAD(loop) calling tool and ChIP-seq defined genomic annotations as the feature space.
-We first optimized our RF model by creating a computational framework that systematically compared the performances of different combinations of genome binning (resolution), feature engineering procedure, and re-sampling technique.
-In doing so, we first introduced a new strategy for establishing boundary prediction data referred to as *shifted binning*, in which the rows of the data matrix were controlled by the data resolution (either 5kb, 10kb, 25kb, 50kb, and 100kb) used to obtain ground truth boundaries, while assuring ground truth bounderies were located central to any given genomic bin.
-Furthermore, we introduced a new procedure for drawing spatial associations between boundary regions and genomic annotations, referred to as *distance*-type predictors, defined as as the $log_{2}$ distance in base pairs from each genomic bin the nearest ChIP-seq peak region.
+We first optimized our RF model by creating a machine learning framework that systematically compared the performances of different combinations of genome binning (resolution), feature engineering procedures, and re-sampling technique.
+In doing so, we first introduced a new strategy for establishing boundary region prediction data referred to as *shifted binning*, in which the rows of the data matrix were controlled by the data resolution (either 5kb, 10kb, 25kb, 50kb, and 100kb) used to obtain ground truth boundaries, while assuring ground truth bounderies were located central to any given genomic bin.
+Furthermore, we introduced a new procedure for drawing spatial associations between boundary regions and genomic annotations, referred to as *distance*-type predictors, defined as as the $log_{2}$ genomic distance in base pairs from each genomic bin the nearest ChIP-seq peak region.
 We benchmarked *preciseTAD* against two boundary calling tools, ARROWHEAD [@durand2016juicebox], an established TAD-caller, and PEAKACHU [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
-For a more in depth study, we also applied *preciseTAD* on cell line-specific boundaries and ChIP-seq data from the GM12878 and K562 cell lines.
+For a more in depth study, we also applied *preciseTAD* on cell line-specific boundaries and ChIP-seq data from both the GM12878 and K562 cell lines.
 
-Our computational framework alone yielded many interesting results.
+Our machine learning framework alone yielded many interesting results.
 First, we showed that RF models built using *distance*-type predictors out performed models built on previously published feature engineering techniques including overlap counts and overlap percents.
@@
 This suggested that random forests, when tuned and feature engineered correctly, are highly effective in accurately predicting boundary regions, contradicting a previous study that found simple multiple linear regression out performed random forests in a TAD boundary prediction setting using both human and drosophila Hi-C data [@mourad2016computational].
-Plausible reasons for their findings include lack of class balancing prior to modeling and usage of rudimentary feature engineering procedures including overlap counts and overlap percents.
+Plausible reasons for their findings include lack of class balancing prior to modeling and usage of rudimentary feature engineering procedures such as overlap counts and overlap percents.
 
@@
 *preciseTAD* provides bp resolution predicted boundaries, thereby alleviating resolution limitations of conventional TAD-callers.
-We show that, unlike ARROWHEAD, *preciseTAD* does not inflate the number of predicted boundaries, instead, providing only the most biologically meaningful boundaries.
+We show that, unlike ARROWHEAD, *preciseTAD* does not inflate the number of predicted boundaries, instead, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
 *preciseTAD* boundaries were found to be more enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143.
@@
 Simply quering a contact matrix ignores the fundamental roles of known molecular drivers of 3D chromatin.
-Instead, we propose a method for turning TAD-calling into a supervised learning framework built using ChIP-seq annotations.
+Instead, we propose a method for turning TAD-calling into a supervised machine learning framework built using ChIP-seq annotations.
 Specifically, we introduce two novel concepts known as *shifted binning* and *distance*-type predictors which we use to build random forest classification models for predicting boundary regions.

### 2020-07-03 Scripts_for_results/07_creating_distance_to_chipseq.Rmd
updated results

--- 2020-04-29 Scripts_for_results/07_creating_distance_to_chipseq.Rmd
@@
                                     chrs[i],
-                                    "/rus/distance/preciseTAD.rds"))
+                                    "/rus/distance/preciseTAD_holdout.rds"))
 
@@
 true_bound_list <- GRangesList()
-chrs <- paste0("CHR", c(1:8,10:22))
+chrs <- paste0("CHR", c(2:8,10:22))
 for(i in 1:length(chrs)){
@@
                                     chrs[i],
-                                    "/rus/distance/preciseTAD_peakachu.rds"))
+                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))
 
@@
 ```
+
+# Combining ARROWHEAD & PEAKACHU for Figure 5D
+
+```{r}
+pred_v_called_df_a$BoundReg <- factor(pred_v_called_df_a$BoundReg, levels=c("ARROWHEAD","preciseTAD"))
+pred_v_called_df_p$BoundReg <- factor(pred_v_called_df_p$BoundReg, levels=c("PEAKACHU","preciseTAD"))
+
+a <- ggplot(pred_v_called_df_a[which(pred_v_called_df_a$Annotation=="CTCF"),], aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  +   
+    stat_boxplot(geom ='errorbar', width = 0.2) + 
+    geom_boxplot(outlier.shape = NA) +
+    geom_signif(test = "wilcox.test", 
+                comparisons = list(c("preciseTAD","ARROWHEAD")),
+                vjust = 0,
+                textsize = 4,
+                size = .5,
+                #step_increase = .5,
+                color="black") +
+    theme_minimal()+
+    theme_bw()+
+    ylab("Log2 Distance to CTCF")+
+    xlab("") +
+    scale_fill_manual(values=c("blue",
+                               "forestgreen"))+
+    scale_color_manual(values=c("blue",
+                                "forestgreen")) +
+    guides(color=FALSE, fill=FALSE)+
+    theme(axis.text.x = element_text(size=10,
+                                     angle = 45,
+                                     hjust = 1),
+          axis.text.y = element_text(size = 10),
+          axis.title.x = element_text(size = 15),
+          axis.title.y = element_text(size = 15),
+          strip.text.x = element_text(size = 10),
+          #panel.spacing = unit(2, "lines"),
+          legend.text=element_text(size=10),
+          legend.title=element_text(size=15),
+          plot.title = element_text(size=15),
+          legend.position = "bottom")
+
+b <- ggplot(pred_v_called_df_p[which(pred_v_called_df_p$Annotation=="CTCF"),], aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  +   
+    stat_boxplot(geom ='errorbar', width = 0.2) + 
+    geom_boxplot(outlier.shape = NA) +
+    geom_signif(test = "wilcox.test", 
+                comparisons = list(c("preciseTAD","PEAKACHU")),
+                vjust = 0,
+                textsize = 4,
+                size = .5,
+                #step_increase = .5,
+                color="black") +
+    theme_minimal()+
+    theme_bw()+
+    ylab("")+
+    xlab("") +
+    scale_fill_manual(values=c("red",
+                               "forestgreen"))+
+    scale_color_manual(values=c("red",
+                                "forestgreen")) +
+    guides(color=FALSE, fill=FALSE)+
+    theme(axis.text.x = element_text(size=10,
+                                     angle = 45,
+                                     hjust = 1),
+          axis.text.y = element_text(size = 10),
+          axis.title.x = element_text(size = 15),
+          axis.title.y = element_text(size = 15),
+          strip.text.x = element_text(size = 10),
+          #panel.spacing = unit(2, "lines"),
+          legend.text=element_text(size=10),
+          legend.title=element_text(size=15),
+          plot.title = element_text(size=15),
+          legend.position = "bottom")
+
+ggarrange(a,b,ncol = 2)
+```

### 2020-07-03 Scripts_for_results/09_visualizing_example_of_preciseTAD_predictions.Rmd
edits
updated results

@@
 
+source("Z:/TAD_data_analysis/functions_for_R_package/createTADdata.R")
 source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADrf.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrandomForest.R")
 source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
@@
 
-## Running TADrf and preciseTAD
+## Creating data matrix
 
 ```{r}
-tadModel <- TADrf(bounds.GR=bounds.GR,
+tadData <- createTADdata(bounds.GR=bounds.GR,
                          resolution=5000,
@@
                          resampling="rus",
-                  trainCHR=paste0("CHR", c(1:8,10:22)),
+                         trainCHR=paste0("CHR",c(1:8,10:22))[-which(paste0("CHR",c(1:8,10:22))=="CHR22")],
                          predictCHR=NULL,
+                         seed=123)
+```
+
+## Running TADrandomForest
+
+```{r}
+tadModel <- TADrandomForest(trainData=tadData[[1]],
+                            testData=NULL,
+                            tuneParams=list(mtry=2,
+                                            ntree=500,
+                                            nodesize=1),
                             cvFolds=3,
-                  ntrees=100,
                             cvMetric="Accuracy",
@@
                             importances=TRUE,
+                            impMeasure="MDA",
                             performances=FALSE)
+```
 
+## Running preciseTAD
+
+```{r}
 bounds.GR <- extract_boundaries_func(domains.mat=domains, 
                                      preprocess=FALSE, 
-                                     #CHR="CHR22", 
-                                     CHR="CHR21", 
+                                     CHR="CHR22", 
                                      resolution=5000)
@@
                       featureType="distance",
-                      #CHR="CHR22",
-                      CHR="CHR21",
-                      #chromCoords=list(17389000,18011000),
-                      chromCoords=list(15150000,17270000),
+                      CHR="CHR22",
+                      chromCoords=list(17000000,19000000),
                       tadModel=tadModel[[1]],
@@
                       DBSCAN=TRUE,
-                      DBSCAN_params=list(5000,3), #or list(10000,3)
+                      DBSCAN_params=list(5000,3), 
                       method.Clust=NULL,
@@
 
+saveRDS(pt, "C:/Users/stili/Downloads/pt_chr21_15150000_17270000")
 ```
@@
 ```{r}
+tadModel <- readRDS("Z:/TAD_data_analysis/miscellaneous/tadModel.rds")
+pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")
+
 getChrLength <- function(genome = "BSgenome.Hsapiens.UCSC.hg19"){
@@
 #seqDataTest <- c(25745000:26176000)
-seqDataTest <- c(15150000:17270000)
+#seqDataTest <- c(15150000:17270000)
+seqDataTest <- c(70595000:71525000)
 
 #CHR="CHR22"
-CHR="CHR21"
+#CHR="CHR21"
+CHR="CHR1"
 
@@
 predprobdata <- data.frame(#basenum=c(17389000:18011000),
-                           basenum=c(15150000:17270000),
+                           #basenum=c(15150000:17270000),
+                           basenum=c(70595000:71525000),
                            prob=predictions)
@@
                                   color="blue"),
-             size=.75,
+             size=1.5,
              show.legend = TRUE)+
@@
                                       color="forestgreen"),
-             size=1,
+             size=1.5,
              show.legend = TRUE)+
@@
 
-ptbrdata <- data.frame(basenum=c(15770000:15780000))
+#ptbrdata <- data.frame(basenum=c(15770000:15780000))
+ptbrdata <- data.frame(basenum=c(70900000:70950000))
 

### 2020-07-03 Scripts_for_results/11_correlations_across_resolutions.Rmd
updated results

@@
 ```{r}
-jaccard_mod <- function (query, reference, restrict = NULL, modified=TRUE) {
+jaccard_mod <- function (query, reference, restrict = NULL, modified=FALSE) {
   if(isTRUE(modified)){
-    int = sum(width(intersect(query, reference)))
-    minunion = min(sum(as.numeric(width(intersect(query, reference)))),sum(as.numeric(width(union(query, reference)))))
+    int = sum(width(GenomicRanges::intersect(query, reference)))
+    minunion = min(sum(as.numeric(width(GenomicRanges::intersect(query, reference)))),sum(as.numeric(width(GenomicRanges::union(query, reference)))))
     res = int/minunion
   }else{
-    res = sum(width(intersect(query, reference)))/sum(as.numeric(width(union(query, reference)))) 
+    res = sum(width(GenomicRanges::intersect(query, reference)))/sum(as.numeric(width(GenomicRanges::union(query, reference)))) 
+  }
+  return(res)
+}
+
+genomicCorr.jaccard = function(query, reference, restrict = NULL) {
+	if(is.null(restrict)) {
+		res = sum(width(GenomicRanges::intersect(query, reference))) / sum(as.numeric(width(GenomicRanges::union(query, reference))))
+	} else {
+		gr1 = GenomicRanges::intersect(query, reference)
+		gr1 = GenomicRanges::intersect(gr1, restrict)
+
+		gr2 = GenomicRanges::union(query, reference)
+		gr2 = GenomicRanges::intersect(gr2, restrict)
+		res = sum(width(gr1)) / sum(width(gr2))
 	}

### 2020-07-03 Manuscript/manuscript.Rmd
minor edit: combined two paragraphs
removed reference names
updated with full results for fig5

@@
 
-afgan2018galaxy, ramirez2016deeptools2
-
 Next, we assessed the biological significance of our predicted boundaries with respect to the enrichment profiles of several known molecular drivers of 3D chromatin architecture including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
-To do so, we used the computeMatrix and plotHeatmap tools offered by DeepTools [@ramirez2016deeptools2] via integration with the Galaxy project [@afgan2018galaxy].
+To do so, we used the computeMatrix and plotHeatmap tools offered by deepTools version 2.0 [@ramirez2016deeptools2] via integration with Galaxy version 3.3.2.0.0 [@afgan2018galaxy].
 Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum test.
-
 Furthermore, we assessed the hypothesis that TADs and chromatin loops are conserved  [@dixon2012topological; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa] by comparing predicted and called boundaries between the GM12878 and K562 cell lines.
@@
 
-<!--
-At this point, we opted to implement preciseTAD using an optimally built whole genome random forest model.
-That is, a random forest model built on 5 kb defined genomic bins, with random under-sampling, and distance-type predictors for the top informative TFBS (CTCF, RAD21, SMC3, and ZNF143).
-The reason for this was because of the improved performance that was exhibited for a whole genome random forest compared to aggregated chromosome-specific models (Supplementary Figure 5).
-When tuning the full genome RF we found that performances converged when *mtry*=2, *ntree*=250, and *nodesize*=???
-(Supplementary Figures 6-7).
--->
-
 When built using ARROWHEAD ground truth boundaries at 5 kb, *preciseTAD* was able to predict a total of ???
@@
 
-![**preciseTAD boundaries are enriched in CTCF sites.** (A) Visualizing locations of predicted vs called ARROWHEAD TAD boundaries on GM12878 (chr 11: 33000000-34600000).
+![**preciseTAD boundaries are enriched in CTCF sites.** (A) Visualizing locations of predicted vs called ARROWHEAD TAD boundaries on GM12878 (chr 1: 70600000-71530000).
 The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.
@@
 
-**Supplementary Figure 5.
-Whole genome random forest model outperform chromosome-specific random forest models across resolutions.** Random forest models built on ARROWHEAD boundaries using 5 kb defined genomic bins, with random under-sampling, and distance-type predictors for the top informative TFBS (CTCF, RAD21, SMC3, and ZNF143) applied to the entire genome (A) exhibit higher balanced accuracies than their chromosome specific counterparts (B) across each resolution respectively.
-
-**Supplementary Figure 6.
-Whole genome RF performances converge when ntree=250.** Scatter plot of cross-validated balanced accuracies (BA) for random forests built using both ARROWHEAD (circles) and PEAKACHU (triangles) boundaries, with random under-sampling, distance-type predictors (CTCF, RAD21, SMC3, and ZNF143), over the entire binned genome, for GM12878 (red) and K562 (blue) respectively.
-For the ARROWHEAD model, 5kb bins were used, while 10kb bins were used for the PEAKACHU model.
-Performances converged after trees of size 250, marked by the dashed line.
-
-**Supplementary Figure 7.
-Whole genome RF performances converge when nodesize=???.** Scatter plot of cross-validated balanced accuracies (BA) for random forests built using both ARROWHEAD (circles) and PEAKACHU (triangles) boundaries, with random under-sampling, distance-type predictors (CTCF, RAD21, SMC3, and ZNF143), over the entire binned genome, for GM12878 (red) and K562 (blue) respectively.
-For the ARROWHEAD model, 5kb bins were used, while 10kb bins were used for the PEAKACHU model.
-Performances converged after nodesize values of ???, marked by the dashed line.
-
 **Supplementary Figure 8.
@@
 
-**Supplementary Table 6.**
+**Supplementary Table 6.** Additional performance metrics when implementing a random forest using ARROWHEAD ground truth TAD boundaries.
 
-**Supplementary Table 7.**
-
-<!--
-**Supplementary Figure 3.
-The proportional importance of optimally built cell line specific models was outweighed by transcription factor binding sites across resolutions.** Stacked barplots illustrate the proportion of total predictive importance in cell line specific random forest classifiers for (A) GM12878 and (B) K562 respectively.
-Model inputs included the optimal data level characteristics determined by the ensemble framework (SMOTE re-sampling; with distance-type predictors).
-Predictive importance was averaged for models built on chromosome specific regions of the linear genome.
-Proportional importance was then calculated according to the annotation group of the feature space including histone modifications (HM), chromatin state segmentations (ChromHMM), and transcription factor binding sites (TFBS).
-
-**Supplementary Figure 5.
-Venn diagrams illustrating the amount of overlap between predicted and called TAD boundary regions.** For each of the GM12878 (A) and K562 (B), both predicted and called TAD boundaries were flanked other either side by 10 kb and the amount of overlap was enumerated.
-
-**Supplementary Figure 6.
-Predicted TAD boundaries were centered closer to peak signal regions defined by known architectural transcription factors when compared to called TAD boundaries for K562.** Enrichment
-heatmaps illustrate the average signal strength of K562-specific ChIP-seq peak regions defined by (A) SMC3, (B) ZNF143, (C) CTCF, and (D) RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.
-
-**Supplementary Figure 7.
-Known architectural transcription factors were statistically significantly closer to predicted TAD boundaries then called TAD boundaries.** Barplots illustrate the log2 distance in basepairs from classes of TAD boundaries to transcription factors including CTCF, RAD21, SMC3, and ZNF143 for the GM12878 (A) and K562 (B) cell lines.
-TAD boundaries were classified into the 3 classes.
-Predicted but not called (PBNC) were the set of 10 kb flanked predicted TAD boundaries the did not overlap with 10 kb flanked called TAD boundaries.
-Called and predicted (CAP) were the set of 10 kb flanked called and predicted TAD boundaries that overlapped with each other.
-Called but not predicted (CBNP) were the set of 10 kb flanked called TAD boundaries that did not overlap with 10 kb flanked predicted TAD boundaries.
--->
+**Supplementary Table 7.** Additional performance metrics when implementing a random forest using PEAKACHU ground truth chromatin loop boundaries.
 

### 2020-07-03 Manuscript/manuscript.Rmd
Some more read-through

@@
 The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been hypothesized to comprise components of the loop extrusion model, whereby DNA is extruded through cohesin rings forming chromatin loops [@hansen2018recent;@fudenberg2016formation;@alipour2012self;@sanborn2015chromatin].
-[???
-Rewrite, simplify, describe enrichment first, loop extrusion second] Additionally, distinct patterns of histone modifications have also been shown to be featured at boundaries, including H3K36 timethylation (H3K36me3) [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
+Additionally, distinct patterns of histone modifications have also been shown to be featured at boundaries, including H3K36 timethylation (H3K36me3) [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
 These elements are annotated on the genome using chromatin immunoprecipitation followed by high-throughput DNA sequencing (ChIP-seq).
@@
 ARROWHEAD is part of the Juicer suite of tools for Hi-C data analysis and visualization.
-To obtain TAD boundaries we applied ARROWHEAD using downloaded primary Hi-C data from Geo GSE63525 [@rao20143d] for the GM12878 and K562 cell lines (libraries HIC001-HIC018 and HIC069-HIC074 for GM12878 and K562 respectively) produced with the MboI restriction enzyme (Supplementary Table 1).
+To obtain TAD boundaries we applied ARROWHEAD using downloaded primary Hi-C data from Geo GSE63525 [@rao20143d] for the GM12878 and K562 cell lines (libraries HIC001-HIC018 and HIC069-HIC074 for GM12878 and K562 respectively) [???
+Were they threated separately?] produced with the MboI restriction enzyme (Supplementary Table 1).
 The contact matrices were constructed from all read pairs that uniquely aligned to the genome (MAPQ>0).
@@
 
-In Hi-C, each chromosome is binned into non-overlapping regions of the same length *r*, typically 5 kb and above.
+In Hi-C, each chromosome is binned into non-overlapping regions of length *r*, typically 5 kb and above.
 The *r* parameter defines the resolution of Hi-C data.
-Consequently, the location of TAD boundaries is limited by the resolution *r*.
 Here, we designed a strategy called _shifted binning_ that partitions the genome into regions of the same length *r*, but with middle points corresponding to boundaries defined by the original binning.
 
-To create shifted binning, the first chromosome-specific bin was set at half of the resolution *r*, and continued in congruent intervals of length *r* until the end of the chromosome (*mod r* + *r/2*).
-The shifted genomic bins, referred hereafted as bins for simplicity, were then defined as boundary regions (*Y = 1*) if they contained a TAD (or loop) boundary, and non-boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification (Figure 1).
+To create shifted binning, the first shifted bin was set to start at half of the resolution *r*, and continued in intervals of length *r* until the end of the chromosome (*mod r* + *r/2*).
+The shifted bins, referred hereafted as bins for simplicity, were then defined as boundary-containing regions (*Y = 1*) if they contained a TAD (or loop) boundary, and non-boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification (Figure 1).
 
@@
 Bins were annotated by one of either the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average signal strength of the corresponding annotation (*Peak Signal Strength*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
-A $log_2$-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
+A $log_2$-transformation [???
+Shouldn't it be log2 + 1?] of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
 It should be noted that models built using a *Peak Signal Strength* feature space were only composed of histone modifications and transcription factor binding sites.

### 2020-07-03 Manuscript/manuscript.Rmd
More edits

@@
 Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, feature engineering procedures, and re-sampling techniques.
-First, the data matrix $A_{N \times (p+1)}$ was constructed by combining the binned genome from each of the $n-1$ autosomal chromosomes ($1,2,\cdots, i-1,i+1,\cdots,22$) as well as a particular feature engineering procedure.
+First, the data matrix $A_{N \times (p+1)}$ was constructed by combining the binned genome from each of the $n-1$ autosomal chromosomes ($1,2,\cdots, i-1,i+1,\cdots,22$) [???
+Define N and p asap introducing.
+What is i?
+also define immediately.
+Adjust this whole paragraph accordingly.
+There's a term "hold-out" - isn't it how you should define it?] as well as a particular feature engineering procedure.
 Re-sampling was then performed on $A$.
@@
 
-$$BA = \dfrac{1}{2}\left( \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} \right)$$
+$$BA = \dfrac{1}{2}\left( sensitivity + specificity \right) = \dfrac{1}{2}\left( \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} \right)$$
 
@@
 To demonstrate, we implemented an optimally built RF model using the framework described above.
-That is, a random forest model built on the optimal combination of data resolution (binning), predictor type (feature space), re-sampling technique (class balancing correction), and top ranked annotations (most informative genomic elements).
+That is, a random forest model was built on the optimal combination of data resolution (binning), predictor type (feature space), re-sampling technique (class balancing correction), and top ranked annotations (most informative genomic elements).
+
+[??? There is a big gap there. Describe the construction of dependent vector Y and predictor matrix _for each base_]
 
 First the vector, $p_{n_{i}}$, denoting each base pair's probability of being a boundary point from the RF model, was extracted, where $n_{i}$ represents the length of chromosome $i$.
-Next, *DBSCAN* (version 1.1-5) was applied to the matrix of pairwise genomic distances between base pairs with $p_{n_{i}}=1$.
+Next, *DBSCAN* [???
+We need to define what to italicize.
+Check below, make consistent throughout the manuscript] (version 1.1-5) was applied to the matrix of pairwise genomic distances between base pairs with $p_{n_{i}}=1$.
 This was to avoid the inflation of predicted boundaries that can occur naturally when dealing with such fine resolution, namely, due to spatially close base pairs with similar predictor profiles (i.e.
@@
 The DBSCAN algorithm takes two parameters, *eps* ($\epsilon$) and *MinPts*.
-The eps parameter was assigned as the respective data resolution.
+The *eps* parameter was assigned as the respective data resolution.
 The heuristic being that density-reachable base pairs with genomic distances less than resolution should occupy the same designated cluster.
-The corresponding MinPts parameter was set to recommended value of 3, representing $1+dim(data)$ [@hahsler2019dbscan].
+The corresponding *MinPts* parameter was set to recommended value of 3, representing $1+dim(data)$ [@hahsler2019dbscan].
 The resulting clusters of highly predictive base pairs identified by DBSCAN were termed *preciseTAD boundary regions* (PTBR).
 To precisely identify a single base pair among each PTBR, *preciseTAD* then implements an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
-Thusly, the corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative and biologically meaningful base pair coordinate within each clustered PTBR.
+The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative and biologically meaningful base pair coordinate within each clustered PTBR.
 
@@
 Next, we assessed the biological significance of our predicted boundaries with respect to the enrichment profiles of several known molecular drivers of 3D chromatin architecture including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
-To do so, we used the computeMatrix and plotHeatmap tools offered by deepTools version 2.0 [@ramirez2016deeptools2] via integration with Galaxy version 3.3.2.0.0 [@afgan2018galaxy].
+To do so, we used the computeMatrix [???
+Again, I expected italics, but decide and correct] and plotHeatmap tools offered by deepTools version 2.0 [@ramirez2016deeptools2] via integration with Galaxy version 3.3.2.0.0 [@afgan2018galaxy].
 Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum test.

### 2020-07-06 Manuscript/manuscript.Rmd
WIP on results

@@
 
-Cell line-specific genomic annotations were used to build the feature space for our boundary prediction framework.
+Cell line-specific genomic annotations were used to build the predictor space for our boundary prediction framework.
 Bins were annotated by one of either the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average signal strength of the corresponding annotation (*Peak Signal Strength*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
@@
 Shouldn't it be log2 + 1?] of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
-It should be noted that models built using a *Peak Signal Strength* feature space were only composed of histone modifications and transcription factor binding sites.
-That is, they did not include any BroadHMM chromatin segmentations.
+Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin segmentations lack signal values.
 
@@
 Many genomic annotations, notably architectural proteins, tend to exhibit an extensive pattern of colocalization (correlation) [@van2014insulator].
-To suitably reduce the feature space and improve computational efficiency, while maintaining optimal performance, we implemented recursive feature elimination (RFE).
+To suitably reduce the predictor space and improve computational efficiency, while maintaining optimal performance, we implemented recursive feature elimination (RFE).
 In doing so, we estimated the near optimal number of necessary features to include in the best fitting RF model.
@@
 To demonstrate, we implemented an optimally built RF model using the framework described above.
-That is, a random forest model was built on the optimal combination of data resolution (binning), predictor type (feature space), re-sampling technique (class balancing correction), and top ranked annotations (most informative genomic elements).
+That is, a random forest model was built on the optimal combination of data resolution (binning), predictor type (predictor space), re-sampling technique (class balancing correction), and top ranked annotations (most informative genomic elements).
 
@@
 Our framework is resolution-specific and uses called TAD or loop boundaries as ground truth to establish TAD(loop)-boundary and non-TAD(loop) boundary regions.
-To demonstrate, we applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines obtained from GEO GSE63525 (Supplementary Table 1).
+To demonstrate, we applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines obtained from GEO GSE63525 (Supplementary Table 1) [???
+Update table and methods with relevant data only, not individual samples].
 TADs were subsequently called using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
@@
 [???
-TAD and loop boundaries should be distinguished, to describe when we have all results]
+Is there other resolution?
+???
+TAD and loop boundaries should be distinguished, to describe when we have all results] [???
+Define that ARROWHEAD data constitute the main results]
 
 Boundary regions were defined as regions containing a called boundary ($Y = 1$), while non-boundary regions were defined as genomic bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
-The total number of TADs, TAD boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 3).
+The total number of TADs, TAD boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 3 [???
+I can see numbers for K562 (?) only?
+There's a discrepancy with legend.]).
 The number of non-boundary regions highly outnumbered boundary regions, with results consistent for loop boundaries as well (Supplementary Table 4).
-Such disproportional presence of examples in one class is known as a "class imbalance" problem that negatively affects model performance [@prati2011survey; @wei2013role].
-To address class imbalance, we evaluated the effect of three re-sampling techniques on prediction performance.
-*Random over-sampling* (ROS) was defined as sampling with replacement from boundary regions.
-*Random under-sampling* (RUS) was defined as sampling with replacement from non-boundary regions.
-Lastly, we considered *Synthetic minority over-sampling technique* (SMOTE), which is a combination of both random over- and under-sampling [@chawla2002smote] (see Methods).
+Such disproportional presence of examples in one class is known as a "class imbalance" problem that negatively affects predictive modeling [@prati2011survey; @wei2013role].
+To address class imbalance, we evaluated the effect of three re-sampling techniques.
+*Random over-sampling* (ROS) was defined as sampling with replacement from the minority class (boundary regions).
+*Random under-sampling* (RUS) was defined as sampling with replacement from the majority cluss (non-boundary regions).
+Lastly, we tested *Synthetic minority over-sampling technique* (SMOTE), which is a combination of both random over- and under-sampling to create balanced classes [@chawla2002smote] (see Methods).
+
+A total of 78 [???
+77 in the table?] cell-line-specific functional genomic annotations were used to build the predictor space.
+These included BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS, Supplementary Table 2).
+Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
+These include signal strength association (Signal), direct (OC), proportional (OP), and spatial (Distance) relationships (see Methods).
+
+![**Resolution-specific data construction and feature engineering used for downstream random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals (see Methods).
+The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD boundary, respectively.
+(B) Four types of associations between bins and genomic annotations (green shapes) were considered to build the predictor space including _Average Peak Signal_ (Signal), _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.](Figures/figure1_model_construction_and_predictor_types.png)
+
+In summary, we considered combinations of data from two cell line *L = {GM12878, K562}*, five resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor space *P = {Signal, OC, OP, Distance}*, and three re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
+Once the model inputs were established, a random forest classifier was trained on $n-1$ autosomal chromosomes, while reserving the $i^{th}$ chromosome for testing.
+Three-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed to default values of 500 and 1 respectively.
+Model performance was evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (see Methods).
 These strategies allowed us to select the best performing model.
 
-A total of 78 cell line specific functional genomic annotations were used to build the feature space of downstream random forest models.
-These annotations included BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS, Supplementary Table 2).
-Four feature engineering procedures were developed for each genomic annotation (Figure 1B, see Methods) with the goal to improve boundary predictions by accounting for signal strength association (Signal), direct (OC), proportional (OP), and spatial (Distance) relationships between TAD boundaries and genomic annotations.
-
-![**Illustrating the resolution-specific data construction and feature engineering used for downstream random forest modeling.** (A) The linear genome was subsequently binned into resolution-specific intervals.
-The response vector **Y** was defined as a genomic bin that either overlapped with a TAD boundary ($Y = 1$) or did not ($Y = 0$).
-(B) Four types of associations between bins and genomic annotations (green shapes) were then used to build the feature space including _Peak Signal_ (Signal), _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.](Figures/figure1_model_construction_and_predictor_types.png)
-
-In summary, we considered combinations of data from a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, with a specific engineered feature space *P = {Signal, OC, OP, Distance}*, and re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
-Once the model inputs were established, a random forest classifier was trained on $n-1$ autosomal chromosomes, while reserving the $i^{th}$ chromosome for testing.
-Three-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed to default values of 500 and 1 respectively.
-Model inputs were evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (See Methods).
-
-![**A diagram of the machine learning framework detailing the steps for combining different inputs used in the random forest model building pipeline.** Step 1 is to establish the chromosome-specific rowise (genomic bins) and columnwise (genomic annotations) dimensions of the data matrix, **A**, by combining a resolution (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)) for the $n-1$ autosomal chromosomes.
-Step 2 is to reserve the binned data matrix for the holdout chromosome $i$ as the test data.
+![**A diagram of the machine learning framework.** Step 1 defines the chromosome-specific predictor-response matrix **A** of $N$ genomic bins (rows), $p$ genomic annotations, and one response vector $Y$ ($p+1$ columns).
+Resolution-specific data (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)) for the $n-1$ autosomal chromosomes.
+Step 2 is to reserve the predictor-response matrix for the holdout chromosome $i$ as the test data.
 Step 3 is to apply a re-sampling technique to the training set (no re-sampling, random over-sampling, random under-sampling, or SMOTE re-sampling).
 Step 4 is to train the random forest model and perform 3-fold cross-validation to tune for the *mtry* parameter.
-Finally, step 5 is to validate the model on the separate test data and evaluate model performance using balanced accuracy (BA).](Figures/figure2_ensemble_framework.png)
+Finally, step 5 is to validate the model on the separate test data and evaluate model performance using balanced accuracy (BA).](Figures/figure2_ensemble_framework.png) [???
+DEfine all indexes, what is N, p+1, i?]
 
@@
 
-Additionally, we found that at higher resolutions, random forest classifiers built using a distance-type feature space yielded substantially higher balanced accuracies when compared to the peak signal stength, overlap count, and overlap percent predictor types.
+Additionally, we found that at higher resolutions, random forest classifiers built using a distance-type predictor space yielded substantially higher balanced accuracies when compared to the peak signal stength, overlap count, and overlap percent predictor types.
 As with comparing class balancing techniques, this improvement was less evident at lower resolutions.
@@
 
-![**Assessing top ranked transcription factors in TAD and loop boundary region prediction for GM12878.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary region prediction models using distance-type specific classes of functional genomic elements as the feature space including histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+![**Assessing top ranked transcription factors in TAD and loop boundary region prediction for GM12878.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary region prediction models using distance-type specific classes of functional genomic elements as the predictor space including histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.
@@
 Here we present *preciseTAD*, a random forest-based approach coupled with spatial clustering (DBSCAN) and scalable partition around medoids (CLARA) that allows for more precise prediction of TAD or loop boundaries.
-*preciseTAD* leverages a random forest (RF) classification algorithm built on ground truth TAD(loop) boundaries obtained from a TAD(loop) calling tool and ChIP-seq defined genomic annotations as the feature space.
+*preciseTAD* leverages a random forest (RF) classification algorithm built on ground truth TAD(loop) boundaries obtained from a TAD(loop) calling tool and ChIP-seq defined genomic annotations as the predictor space.
 We first optimized our RF model by creating a machine learning framework that systematically compared the performances of different combinations of genome binning (resolution), feature engineering procedures, and re-sampling technique.
@@
 
-**Supplementary Table 2.** A complete list of the genomic annotations used to build the feature space for all downstream models.
+**Supplementary Table 2.** A complete list of the genomic annotations used to build the predictor space for all downstream models.
 The GRCh37/hg19 human genome assembly was used.
@@
 **Supplementary Figure 4.
-Assessing top ranked transcription factors in TAD and loop boundary prediction for K562.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using specific classes of functional genomic elements as the feature space including histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+Assessing top ranked transcription factors in TAD and loop boundary prediction for K562.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using specific classes of functional genomic elements as the predictor space including histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.

### 2020-07-06 Manuscript/manuscript.Rmd
Edits through Figure 5

@@
 
-## 5 kb resolution, random under-sampling, and distance-based predictors provided optimal performance for TAD boundary prediction
+## Random under-sampling, distance-based predictors, and high-resolution Hi-C data provide optimal performance for boundary prediction
 
@@
 We found that RUS marginally outperformed SMOTE as the most optimal class balancing technique for all resolutions and predictor types.
-These results suggest that simple random under-sampling alone can drastically improve TAD boundary region prediction.
+These results suggest that simple random under-sampling can significantly improve TAD boundary region prediction.
 
-Additionally, we found that at higher resolutions, random forest classifiers built using a distance-type predictor space yielded substantially higher balanced accuracies when compared to the peak signal stength, overlap count, and overlap percent predictor types.
-As with comparing class balancing techniques, this improvement was less evident at lower resolutions.
-These results were found to be consistent for the K562 cell line (Supplementary Figure 2).
+Additionally, we found that using a distance-type predictor space yielded substantially higher balanced accuracies when compared to the peak signal stength, overlap count, and overlap percent predictor types.
+As with class balancing techniques, this improvement was less evident at lower resolutions.
+These results were consistent for the K562 cell line (Supplementary Figure 2).
 Random forest models built on PEAKACHU loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3).
 Five kilobase resolution genomic bins was found to result in optimal prediction for both TAD and loop boundaries, on both cell lines.
-Our results indicate that random under-sampling, distance-type predictors, and Hi-C data at 5kb resolution are the optimal set of data level characteristics for both TAD and chromatin loop boundary region prediction.
+Our results indicate that random under-sampling, distance-type predictors, and high-resolution Hi-C data provide the optimal set of data level characteristics for both TAD and loop boundary prediction.
 
@@
 
-![**???[needs updating with new framework, takes longest, do last]Models built using distance-type predictors combined with random under-sampling at 5 kb yielded optimal TAD boundary region predictive performance for GM12878.** Line plots comparing the performances of random forest classifiers built using different combinations of data level characteristics.
-Performances are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Performances were evaluated using balanced accuracy.](Figures/figure3_performances.png)
+![**???[needs updating with new framework, takes longest, do last] Distance-type predictors combined with random under-sampling yielded optimal TAD boundary region predictive performance for GM12879 ARROWHEAD TAD boundaries.** Balanced accuracy is compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).](Figures/figure3_performances.png)
 
-## Transcription factor binding sites outperform HM- and BroadHMM-specific models
+## Transcription factor binding sites outperform histone- and chromatin segmentation-specific models
 
-We hypothesized that the type of genomic annotations may affect the predictive performance.
-Using the aforementioned optimal settings, we built separate random forest models using BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS).
+We hypothesized that the type of genomic annotations may also affect the predictive performance.
+Using the established optimal settings (RUS, Distance), we built separate random forest models using BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS).
 We found that models built on TFBSs outperformed other annotation-specific models, and these results were consistent for loop boundaries, for both cell lines (Figure 4A; Supplementary Figures 4A).
@@
 
-![**Assessing top ranked transcription factors in TAD and loop boundary region prediction for GM12878.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary region prediction models using distance-type specific classes of functional genomic elements as the predictor space including histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
-(B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.
-Error bars represent standard deviation from the cross-validated balance accuracy across each autosomal chromosome.
-(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.](Figures/figure4_annots_specifc_rfe_importances_arrowhead_peakachu.png)
+![**Binding of SMC3, Rad21, CTCF, and Znf143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+(B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
+Error bars represent standard deviation from the cross-validated accuracy across each chromosome.
+(C) Clustered heatmap of the predictive importance for the union of the top 8 chromosome-specific most predictive TFBSs.](Figures/figure4_annots_specifc_rfe_importances_arrowhead_peakachu.png)
 
@@
 
-After obtaining our optimally built random forest model, we investigated whether we could leverage our model to alleviate resolution limitations of Hi-C data by predicting TAD boundaries at base pair resolution.
-Our method, referred to as *preciseTAD*, leverages a user specified binary classifier with a combination of density-based hierarchical clustering and a scalable version of partitioning around mediods (PAM), known as clustering large applications (CLARA) to precisely identify the most representative and biologically meaningful predicted chromosome-specific domain boundaries (see Methods).
+Using our optimally built random forest model, we attempted to overcome resolution limitations of Hi-C data by predicting TAD [???
+Check throughout the manuscript - we may need to define "interacting domains" referring to TADs and loops] boundaries at base resolution.
+Intuitively, the predictor-response space is built on a base-resolution level, and the model trained on a bin-level space predicts the probability of each base being a boundary.
+Our method, referred to as *preciseTAD*, leverages a user-specified [???
+We need pre-trained models and understanding how they perform on different cell lines] model with density-based hierarchical clustering (DBSCAN) and a scalable partitioning around mediods clustering (CLARA) to predict the boundary location ad base resolution (see Methods).
 
@@
 boundaries for GM12878 and K562 cell lines respectively.
-We reported less predicted TAD boundaries than ARROWHEAD (Table 1, Supplementary Table 3).
-This is attributed to ARROWHEAD's inherent inflation of called TAD boundaries, especially near fuzzy areas along the diagonal of Hi-C contact matrices (Figure 5A).
+We reported less predicted TAD boundaries than ARROWHEAD (Table 1, Supplementary Table 3) [???
+Where is this info?].
+This may be attributed to ARROWHEAD's boundaries frequently being separated by gaps, the effect especially pronounced near sparse areas of Hi-C contact matrices (Figure 5A) [???
+I don't see it, data not shown?].
 However, under the framework of *preciseTAD*, any two TADs are inherently conjoined by only one predicted TAD boundary, leading to comparatively less TAD boundaries.
-Visually speaking, we also found that predicted TAD boundaries identified by *preciseTAD* were much more likely to demarcate high concentrations of inter-chromosomal contacts as seen on a Hi-C contact matrix (Figure 5A).
+[???
+Unclear explanation, so what?
+preciseTAD is driven by genomic annotations.
+May it be too stringent thresholds?
+This all may be for the discussion, if we have a good understanding why] We also found that predicted TAD boundaries identified by *preciseTAD* were visually more likely to demarcate high concentrations of inter-chromosomal contacts as seen on a Hi-C contact matrix (Figure 5A).
 [???add peakachu totals when ready]
@@
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
-Enriched heatmaps indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or PEAKACHU boundaries alone (Figure 5 B-C).
+Signal heatmaps [???
+Make sure to mention DeepTools in Methods] indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or PEAKACHU boundaries alone (Figure 5 B-C).
 Likewise, *preciseTAD* boundaries were also more enriched for other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 8-9).
@@
 vs ARROWHEAD and PEAKACHU respectively) (Figure 5D, Supplementary Figure 10-11).
-We also inspected the affect of resolution on locations of our predicted TAD boundaries.
+We also inspected the effect of resolution on locations of our predicted TAD boundaries.
 We found that *preciseTAD* boundaries exhibited higher pairwise Jaccard indices between adjacent resolutions than ARROWHEAD boundaries, thus implying stronger invariance toward resolution (Figure 5E).
 
-![**preciseTAD boundaries are enriched in CTCF sites.** (A) Visualizing locations of predicted vs called ARROWHEAD TAD boundaries on GM12878 (chr 1: 70600000-71530000).
-The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.
-The blue vertical lines represent boundaries identified by ARROWHEAD, with the corresponding called TADs outlined in blue on the upper diagonal contact matrix above.
-The black line represents the predicted probability of each base pair being a TAD boundary when validated by our random forest.
-The green vertical lines represent the *preciseTAD boundary points* (PTBP) predicted by *preciseTAD*, with the corresponding demarcated TADs outlined above in green.
-Below is a zoomed in portion of the genome showing a cluster of base pairs with high probability representing a single *preciseTAD boundary region (PTBR) colored in yellow.
-(B) Enriched heatmaps comparing the enrichment of CTCF sites around 5 kb flanked preciseTAD and ARROWHEAD TAD boundaries respectively.
-(C) Enriched heatmaps comparing the enrichment of CTCF sites around 10 kb flanked preciseTAD and PEAKACHU loop boundaries respectively.
-(D) $Log_{2}$ genomic distances from boundaries to nearest CTCF site between preciseTAD boundaries and both ARROWHEAD and PEAKACHU boundaries, respectively.
-(E) A atrix of pairwise Jaccard indices across resolutions shows more invariance toward resolution for *preciseTAD* (upper triangular) compared to ARROWHEAD (lower triangular).???update when ready](Figures/figure5_enrichment_and_log2dist_ctcf.png)
+![**preciseTAD boundaries are enriched in CTCF sites.** (A) The location of preciseTAD (green) vs.
+ARROWHEAD (blue) boundaries on GM12878 (chr 1: 70600000-71530000).
+The black line represents the probability of each base being a TAD boundary.
+The green vertical lines represent the *preciseTAD boundary points* (PTBP).
+A zoomed-in portion of the genome shows a yellow-highlighted cluster of bases with high probability of being a boundary, the *preciseTAD boundary region (PTBR).
+(B) Heatmaps comparing the enrichment of CTCF signal around preciseTAD and ARROWHEAD TAD boundaries, and (C) around preciseTAD and PEAKACHU loop boundaries.
+(D) $Log_{2}$ genomic distances from boundaries to nearest CTCF sites.
+(E) Pairwise Jaccard indices shows better overlap among *preciseTAD*-detected boundaries across resolutions (upper triangular) as compared to ARROWHEAD (lower triangular).](Figures/figure5_enrichment_and_log2dist_ctcf.png) [???
+Panel E - do we have it for Peakachu?
+- stretched, can be put in figure.
+Can you color triangulars blue/red for Arrowhead/Peakachu, green for preciseTAD?]
 
@@
 Distances are measured as the number of base pairs from the center of a genomic bin to the center of the nearest genomic annotation.
-Each density curve represents a particular genomic annotation.
+Each density curve represents individual genomic annotation.
 
@@
 **Supplementary Figure 2.
-Models built using distance-type predictors combined with random under-sampling at 5 kb yielded optimal predictive performance for K562.** Line plots comparing the performances of random forest classifiers built using ARROWHEAD boundaries at different combinations of data level characteristics.
-Performances are compared across resolution, within each predictor-type: (A) Signal (B) OC, (C) OP, and (D) Distance, and between each re-sampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Performances were evaluated using balanced accuracy.
+Distance-type predictors combined with random under-sampling yielded optimal TAD boundary region predictive performance for K562 ARROWHEAD TAD boundaries.** Balanced accuracy is compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 
 **Supplementary Figure 3.
-Models built using distance-type predictors combined with SMOTE re-sampling yielded optimal predictive performance for GM12878 K562.** Line plots comparing the performances of random forest classifiers built using using PEAKACHU boundaries at different combinations of data level characteristics for (A) GM12878 and (B) K562.
-Performances are compared across resampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple), and within each predictor-type: Signal, OC, OP, and Distance.
+Distance-type predictors combined with random under-sampling or SMOTE re-sampling yielded optimal predictive performance for A) GM12878 and B) K562 Peakachu loop boundaries.** Balanced accuracy is compared within each predictor-type: Signal, OC, OP, and Distance, and across across resampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 
 **Supplementary Figure 4.
-Assessing top ranked transcription factors in TAD and loop boundary prediction for K562.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using specific classes of functional genomic elements as the predictor space including histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
-(B) Recursive feature elimination (RFE) analysis used to reduce the number of TFBS to include in the optimally built random forest model.
+Binding of SMC3, Rad21, CTCF, and Znf143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+(B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
 Error bars represent standard deviation from the cross-validated accuracy across each chromosome.
-(C) Clustered heatmap of predictive importances for the union of the top 8 most predictive TFBS across chromosomes as determined from performing RFE.
+(C) Clustered heatmap of the predictive importance for the union of the top 8 chromosome-specific most predictive TFBSs.
 

### 2020-07-07 Manuscript/manuscript.Rmd
Last part of results edits

@@
 Emerging evidence has linked TADs to critical roles in cell dynamics and cell differentiation.
-Studies have shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological;@krefting2018evolutionary].
+Studies have shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
 Likewise, disruption of the boundaries that demarcate TADs and loops have been shown to lead to cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@lupianez2016breaking;@Sun:2018aa;@Meaburn:2007aa].
@@
 
-Within this study we used both TAD boundary and loop boundary data derived from the publically available tools ARROWHEAD [@durand2016juicebox] and PEAKACHU [@salameh2019supervised] respectively.
+Within this study we used both TAD boundary and loop boundary data derived from the publically available tools ARROWHEAD [@durand2016juicebox] and Peakachu [@salameh2019supervised] respectively.
 ARROWHEAD is part of the Juicer suite of tools for Hi-C data analysis and visualization.
@@
 The default tools for ARROWHEAD were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1).
-For chromatin loop boundaries, we used loops identified by PEAKACHU at 10 kb for the GM12878 and K562 cell lines [@salameh2019supervised].
+For chromatin loop boundaries, we used loops identified by Peakachu at 10 kb for the GM12878 and K562 cell lines [@salameh2019supervised].
 Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop.
@@
 
-## Comparing called vs predicted boundaries
+## Comparing called vs. predicted boundaries
 
@@
 Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum test.
-Furthermore, we assessed the hypothesis that TADs and chromatin loops are conserved  [@dixon2012topological; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa] by comparing predicted and called boundaries between the GM12878 and K562 cell lines.
-Boundaries were first flanked by resolution, *r*, and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0) and evaluated using the Jaccard index defined as
+Furthermore, we compared the overlap between predicted and called boundaries in GM12878 and K562 cell lines.
+Boundaries were first flanked by resolution, *r*, and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0).
+Overlaps were further quantified using Jaccard index defined as
 
@@
 That is, between cell lines, the number of overlapping flanked boundaries divided by the total number of flanked boundaries.
-Wilcoxon rank sum tests were used to compare chromosome-specific jaccard indices across cell lines, between *preciseTAD* boundaries and both ARROWHEAD and PEAKACHU boundaries respectively.
+Wilcoxon rank sum tests were used to compare chromosome-specific Jaccard indices across cell lines, between *preciseTAD* boundaries and both ARROWHEAD and Peakachu boundaries, respectively.
 All statistical analyses were performed in R version 4.0.1.
@@
 TADs were subsequently called using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-For loop boundaries, we opted to use boundaries obtained by the PEAKACHU prediction tool for the GM12878 and K562 cell lines at 10 kb resolution [@salameh2019supervised].
+For loop boundaries, we opted to use boundaries obtained by the Peakachu prediction tool for the GM12878 and K562 cell lines at 10 kb resolution [@salameh2019supervised].
 [???
@@
 Finally, step 5 is to validate the model on the separate test data and evaluate model performance using balanced accuracy (BA).](Figures/figure2_ensemble_framework.png) [???
-DEfine all indexes, what is N, p+1, i?]
+DEfine all indices, what is N, p+1, i?]
 
@@
 The class imbalance among the genomic bins was both severe and invariant toward resolution, resulting in 0.03, 0.05, 0.08, 0.08, and 0.07 for each resolution respectively (Table 1).
-Boundary data summaries were similar for K562 cell line, as well as for PEAKACHU defined boundaries (Supplementary Tables 3-4).
+Boundary data summaries were similar for K562 cell line, as well as for Peakachu defined boundaries (Supplementary Tables 3-4).
 -->
@@
 These results were consistent for the K562 cell line (Supplementary Figure 2).
-Random forest models built on PEAKACHU loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3).
+Random forest models built on Peakachu loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3).
 Five kilobase resolution genomic bins was found to result in optimal prediction for both TAD and loop boundaries, on both cell lines.
@@
 
-![**Binding of SMC3, Rad21, CTCF, and Znf143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+![**Binding of SMC3, Rad21, CTCF, and Znf143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (Peakachu) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
@@
 Signal heatmaps [???
-Make sure to mention DeepTools in Methods] indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or PEAKACHU boundaries alone (Figure 5 B-C).
+Make sure to mention DeepTools in Methods] indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or Peakachu boundaries alone (Figure 5 B-C).
 Likewise, *preciseTAD* boundaries were also more enriched for other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 8-9).
@@
 and p=???
-vs ARROWHEAD and PEAKACHU respectively) (Figure 5D, Supplementary Figure 10-11).
+vs ARROWHEAD and Peakachu respectively) (Figure 5D, Supplementary Figure 10-11).
 We also inspected the effect of resolution on locations of our predicted TAD boundaries.
@@
 A zoomed-in portion of the genome shows a yellow-highlighted cluster of bases with high probability of being a boundary, the *preciseTAD boundary region (PTBR).
-(B) Heatmaps comparing the enrichment of CTCF signal around preciseTAD and ARROWHEAD TAD boundaries, and (C) around preciseTAD and PEAKACHU loop boundaries.
+(B) Heatmaps comparing the enrichment of CTCF signal around preciseTAD and ARROWHEAD TAD boundaries, and (C) around preciseTAD and Peakachu loop boundaries.
 (D) $Log_{2}$ genomic distances from boundaries to nearest CTCF sites.
@@
 
-Subsequent comparisons of *preciseTAD* with both ARROWHEAD and PEAKACHU revealed that our predicted boundaries were more conserved between the GM12878 and K562 cell lines.
-To assess conservation, we evaluated the overlap between cell line specific boundaries after flanking by the resolution used to make predictions.
-Boundaries involving ARROWHEAD were flanked by 5 kb, while boundaries involving PEAKACHU were flanked by 10 kb.
+TAD boundaries are known to be relatively conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
+To assess conservation, we evaluated the overlap between cell-line-specific boundaries detected by *preciseTAD*, ARROWHEAD, and Peakachu after flanking them by the resolution of the Hi-C data.
+Boundaries involving ARROWHEAD were flanked by 5 kb, while boundaries involving Peakachu were flanked by 10 kb.
 We found that a significant proportion of flanked boundaries predicted by *preciseTAD* overlapped between GM12878 and K562.
@@
 and 61%???
-of *preciseTAD* boundaries were conserved across cell lines when built on ARROWHEAD and PEAKACHU boundaries respectively (Figure 6A).
-Additionally, the median jaccard index (MJI) was found to be 0.472 (IQR=0.441-0.503; p=???) and 0.647 (IQR=0.646-0.647; p=???) for *preciseTAD* predicted TAD and loop boundaries (Supplementary Table 5).
-Comparatively, only 25% (MJI=0.284; IQR=0.268-0.301) and 49% (MJI=0.509; IQR=0.503-0.515) of called/predicted ARROWHEAD and PEAKACHU boundaries were conserved (Figure 6A, Supplementary Table 5).
+of *preciseTAD* boundaries were conserved across cell lines when built on ARROWHEAD and Peakachu boundaries respectively (Figure 6A).
+Additionally, the median Jaccard index (MJI) was found to be 0.472 (IQR=0.441-0.503; p=???) and 0.647 (IQR=0.646-0.647; p=???) for *preciseTAD* predicted TAD and loop boundaries (Supplementary Table 5).
+Comparatively, only 25% (MJI=0.284; IQR=0.268-0.301) and 49% (MJI=0.509; IQR=0.503-0.515) of called/predicted ARROWHEAD and Peakachu boundaries were conserved (Figure 6A, Supplementary Table 5).
+These results demonstrate that boundaries predicted using genomic annotations (*preciseTAD*) are better conserved across cell lines.
 
-Expectedly, the majority of flanked TAD boundaries predicted by *preciseTAD* represented a subset of the larger group of predicted loop boundaries.
-This makes sense as the boundaries that demarcate chromatin loops make up a broader class of boundaries, with TAD boundaries representing the next level in 3D chromatin hierarchy, followed by A/B compartments.
-For GM12878, 83% of predicted TAD and loop boundaries overlapped with eachother, while only 3% of predicted TAD boundaries were not contained in the set of flank-predicted loop boundaries (Figure 6B).
-Similarly, for K562, 75% overlap occured between predicted TAD and loop boundaries, with only 4% of predicted TAD boundaries remaining outside of the set of flank-predicted loop boundaries (Figure 6B).
+The majority of boundaries predicted by the ARROWHEAD-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model (Figure 6B).
+This is expected as loop boundaries (Peackachu) are more abundant, while TAD boundaries (ARROWHEAD) represent the narrower level of the 3D chromatin organization.
+83% and 75% of predicted TAD and loop boundaries overlapped with each other for GM12878 and K562 cell lines, respectively (Figure 6B).
+Together with the results shown on Figure 4, the high overlap between boundaries predicted by ARROWHEAD- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar protein complexes.
 
-![**preciseTAD boundaries are conserved between the GM12878 and K562 cell lines.** (A) Venn diagrams illustrating the percentage of overlap between GM12878- and K562-specific predicted and called boundaries.
-(B) Venn diagrams illustrating the nested structure of predicted TAD and loop boundaries identified by *preciseTAD* for the GM12878 and K562 cell lines.
-Note, predicted and called TAD boundaries were flanked by 5 kb, while predicted and called loop boundaries were flanked by 10 kb prior to calculating overlaps to reflect the resolution that was used to predict each respectively.](Figures/figure6_venn_diagrams.png)
+![**preciseTAD boundaries are more conserved between the GM12878 and K562 cell lines.** (A) Venn diagrams illustrating the overlap between GM12878- and K562-specific predicted and called boundaries.
+(B) Venn diagrams illustrating the agreement between boundaries predicted using ARROWHEAD- and Peakachu-trained models.](Figures/figure6_venn_diagrams.png)
+[??? What is the difference between leftmost Venn diagrams on panel A?] [??? What are the numbers?]
 
@@
 Furthermore, we introduced a new procedure for drawing spatial associations between boundary regions and genomic annotations, referred to as *distance*-type predictors, defined as as the $log_{2}$ genomic distance in base pairs from each genomic bin the nearest ChIP-seq peak region.
-We benchmarked *preciseTAD* against two boundary calling tools, ARROWHEAD [@durand2016juicebox], an established TAD-caller, and PEAKACHU [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
+We benchmarked *preciseTAD* against two boundary calling tools, ARROWHEAD [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
 For a more in depth study, we also applied *preciseTAD* on cell line-specific boundaries and ChIP-seq data from both the GM12878 and K562 cell lines.
@@
 
-The performance of *preciseTAD* was found to be empirically better than both ARROWHEAD and PEAKACHU ground truth boundaries.
+The performance of *preciseTAD* was found to be empirically better than both ARROWHEAD and Peakachu ground truth boundaries.
 *preciseTAD* provides bp resolution predicted boundaries, thereby alleviating resolution limitations of conventional TAD-callers.
@@
 
-**Supplementary Table 1.** A complete list of the Hi-C data libraries obtained from GEO GSE63525 [@rao20143d] used to obtain the locations of topologically associating domains for ARROWHEAD, as well as the locations for the cell line specific .txt files of loop boundaries obtained by PEAKACHU.
+**Supplementary Table 1.** A complete list of the Hi-C data libraries obtained from GEO GSE63525 [@rao20143d] used to obtain the locations of topologically associating domains for ARROWHEAD, as well as the locations for the cell line specific .txt files of loop boundaries obtained by Peakachu.
 [@salameh2019supervised].
@@
 
-**Supplementary Table 4.** Loop boundary and class imbalance summaries from PEAKACHU 10 kb resolution for both the GM12878 and K562 cell lines respectively.
+**Supplementary Table 4.** Loop boundary and class imbalance summaries from Peakachu 10 kb resolution for both the GM12878 and K562 cell lines respectively.
 
@@
 **Supplementary Figure 4.
-Binding of SMC3, Rad21, CTCF, and Znf143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+Binding of SMC3, Rad21, CTCF, and Znf143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (Peakachu) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
@@
 **Supplementary Figure 8.
-preciseTAD boundaries are more enriched for GM12878-specific SMC3, RAD21, and ZNF143 sites.** Enriched heatmaps comparing preciseTAD boundaries with both (A) ARROWHEAD and (B) PEAKACHU boundaries for the GM12878 cell line.
+preciseTAD boundaries are more enriched for GM12878-specific SMC3, RAD21, and ZNF143 sites.** Enriched heatmaps comparing preciseTAD boundaries with both (A) ARROWHEAD and (B) Peakachu boundaries for the GM12878 cell line.
 
-**Supplementary Figure 9.preciseTAD boundaries are more enriched for K562-specific CTCF, SMC3, RAD21, and ZNF143 sites.** Enriched heatmaps comparing preciseTAD boundaries with both (A) ARROWHEAD and (B) PEAKACHU boundaries for the K562 cell line.
+**Supplementary Figure 9.preciseTAD boundaries are more enriched for K562-specific CTCF, SMC3, RAD21, and ZNF143 sites.** Enriched heatmaps comparing preciseTAD boundaries with both (A) ARROWHEAD and (B) Peakachu boundaries for the K562 cell line.
 
 **Supplementary Figure 10.
-preciseTAD boundaries are spatially closer to GM12878-specific SMC3, RAD21, and ZNF143 sites.** Boxplots comparing the $log_{2}$ genomic distances from each preciseTAD boundary (green) and called boundary (either ARROWHEAD or PEAKACHU; blue) to the nearest SMC3, RAD21, and ZNF143 sites on the linear genome for GM12878.
+preciseTAD boundaries are spatially closer to GM12878-specific SMC3, RAD21, and ZNF143 sites.** Boxplots comparing the $log_{2}$ genomic distances from each preciseTAD boundary (green) and called boundary (either ARROWHEAD or Peakachu; blue) to the nearest SMC3, RAD21, and ZNF143 sites on the linear genome for GM12878.
 
 **Supplementary Figure 11.
-preciseTAD boundaries are spatially closer to K572-specific CTCF, SMC3, RAD21, and ZNF143 sites.** Boxplots comparing the $log_{2}$ genomic distances from each preciseTAD boundary (green) and called boundary (either ARROWHEAD or PEAKACHU; blue) to the nearest CTCF, SMC3, RAD21, and ZNF143 sites on the linear genome for K562.
+preciseTAD boundaries are spatially closer to K572-specific CTCF, SMC3, RAD21, and ZNF143 sites.** Boxplots comparing the $log_{2}$ genomic distances from each preciseTAD boundary (green) and called boundary (either ARROWHEAD or Peakachu; blue) to the nearest CTCF, SMC3, RAD21, and ZNF143 sites on the linear genome for K562.
+[??? Combine Supplementary Figure 10 and 11. Make panel A and, underneath, panel B. Remove CTCF from Y-axis and put overhead labels above each plot pair]
 
-**Supplementary Table 5.** Median chromosome-specific Jaccard indices (IQR) for called and *preciseTAD* predicted TAD (ARROWHEAD) and loop (PEAKACHU) boundaries between the GM12878 and K562 cell lines.
-The p-value is from a nonparametric Wilcoxon-rank sum test.
-Note, predicted and called *TAD* boundaries were flanked by 5 kb, while predicted and called *loop* boundaries were flanked by 10 kb prior to calculating Jaccard indices to reflect the resolution that was used to predict each respectively.
+**Supplementary Table 5.** Median chromosome-specific Jaccard indices (IQR) for ARROWHEAD- and Peakachu-called and *preciseTAD* predicted boundaries between the GM12878 and K562 cell lines [???
+Where is cell line information?] [???
+What is in parentheses?].
+The p-value is from a nonparametric Wilcoxon-rank sum test [???
+Absent].
+Note, ARROWHEAD-called and predicted boundaries were flanked by 5 kb, while Peakachu-called and predicted boundaries were flanked by 10 kb prior to calculating Jaccard indices.
 
@@
 
-**Supplementary Table 7.** Additional performance metrics when implementing a random forest using PEAKACHU ground truth chromatin loop boundaries.
+**Supplementary Table 7.** Additional performance metrics when implementing a random forest using Peakachu ground truth chromatin loop boundaries.
 

### 2020-07-08 Manuscript/manuscript.Rmd
Polishing discussion

@@
 The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of important 3-dimensional (3D) spatial constructs within the human genome such as chromatin loops [@rao20143d], Topologically Associated Domains (TADs) [@nora2012spatial;@dixon2012topological], and A/B compartments [@lieberman2009comprehensive].
-At kilobase scale, gene promotors are often connected via distal regulatory elements, such as enhancers, through chromatin loops, thereby regulating gene expression [@Lupianez:2015aa; @Franke:2016aa].
+At kilobase scale, gene promoters are often connected via distal regulatory elements, such as enhancers, through chromatin loops, thereby regulating gene expression [@Lupianez:2015aa; @Franke:2016aa].
 Further out, at the megabase scale, TADs represent regions on the linear genome, that are highly self-interacting.
@@
 
-Here we present *preciseTAD*, a random forest-based approach coupled with spatial clustering (DBSCAN) and scalable partition around medoids (CLARA) that allows for more precise prediction of TAD or loop boundaries.
-*preciseTAD* leverages a random forest (RF) classification algorithm built on ground truth TAD(loop) boundaries obtained from a TAD(loop) calling tool and ChIP-seq defined genomic annotations as the predictor space.
-We first optimized our RF model by creating a machine learning framework that systematically compared the performances of different combinations of genome binning (resolution), feature engineering procedures, and re-sampling technique.
-In doing so, we first introduced a new strategy for establishing boundary region prediction data referred to as *shifted binning*, in which the rows of the data matrix were controlled by the data resolution (either 5kb, 10kb, 25kb, 50kb, and 100kb) used to obtain ground truth boundaries, while assuring ground truth bounderies were located central to any given genomic bin.
-Furthermore, we introduced a new procedure for drawing spatial associations between boundary regions and genomic annotations, referred to as *distance*-type predictors, defined as as the $log_{2}$ genomic distance in base pairs from each genomic bin the nearest ChIP-seq peak region.
+We present *preciseTAD*, a machine learning approach for precise prediction of TAD or loop boundaries from functional genomic annotations.
+*preciseTAD* leverages a random forest (RF) classification model built on ground truth TAD/loop boundaries obtained from a TAD/loop calling tools and ChIP-seq defined genomic annotations as the predictor space.
 We benchmarked *preciseTAD* against two boundary calling tools, ARROWHEAD [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
-For a more in depth study, we also applied *preciseTAD* on cell line-specific boundaries and ChIP-seq data from both the GM12878 and K562 cell lines.
+We applied *preciseTAD* on cell line-specific boundaries and ChIP-seq data from both the GM12878 and K562 cell lines.
+We first optimized our RF model by systematically comparing different combinations of genome binning (resolution), feature engineering procedures, and re-sampling technique addressing class imbalance.
+We show that distance between boundary regions and genomic annotations coupled with random undersampling technique help to form the predictor space resulting in optimal model performance.
+We demonstrate that binding of four transcription factors (SMC3, Rad21, CTCF, Znf143) are sufficient for accurate TAD and loop boundary predictions.
+The model predicts probability for each base to be a baoundary, and, coupled with spatial clustering (DBSCAN) and scalable partition around medoids clustering (CLARA), allows for the detection of boundaries at the base-level resolution.
 
-Our machine learning framework alone yielded many interesting results.
-First, we showed that RF models built using *distance*-type predictors out performed models built on previously published feature engineering techniques including overlap counts and overlap percents.
-Moreover, we were further able to optimize our RF model by introducing random under-sampling, a technique to correct for the severe class imbalance between TAD(loop) and non-TAD(loop) boundary regions.
-We showed that in our optimized RF, transcription factor binding sites provided an overwhelming amount of signal in the model, indeed out-performing histone modification- and BroadHMM-specific models, contradicting a previous study that found histone marks alone were effective in predicting TAD boundaries [@huang2015predicting].
-Likewise, our RF model built using *distance*-type predictors was consistently able to identify the group of the top known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143 as being highly predictive of TAD(loop) boundary regions across both cell lines.
+Our random forest framework yielded several interesting observations.
+First, we showed that RF models built using *distance*-type predictors out performed models built on previously published feature engineering techniques including signal strength, overlap counts and overlap percents [@mourad2016computational].
+[???
+Add more REFs] We further demonstrated that class imbalance hinders boundary prediction, but can be effectively addressed by a simple random under-sampling technique.
+The unaddressed class imbalance problem in previous studies [???
+Add REFs] We showed that information about only four transcription factors (SMC3, Rad21, CTCF, Znf143) is necessary and sufficient transcription for accurate boundary prediction, out-performing histone modification- and BroadHMM-built models.
 These are known components of the loop extrusion model, an established theory for how loops are made by a ring-shaped adenosine triphosphatase complex called cohesin [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
-This suggested that random forests, when tuned and feature engineered correctly, are highly effective in accurately predicting boundary regions, contradicting a previous study that found simple multiple linear regression out performed random forests in a TAD boundary prediction setting using both human and drosophila Hi-C data [@mourad2016computational].
-Plausible reasons for their findings include lack of class balancing prior to modeling and usage of rudimentary feature engineering procedures such as overlap counts and overlap percents.
+Interestingly, the same transcription factors accurately predicted both TAD and loop boundaries, suggesting similarity of the mechanisms of TAD and loop formation.
+Although our observations contradict a previous study showing histone marks alone were effective in predicting TAD boundaries [@huang2015predicting], our findings are backed by a large body of literature [???
+Add REFs].
+This suggested that the random forest model, when tuned and feature engineered correctly, is highly effective in predicting boundary regions.
 
-Besides balanced accuracy (BA), we investigated five other performance metrics to evaluate the optimal combination of data level characteristics for RF prediction including accuracy, area under the receiver operating characteristic curve (AUC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Supplementary Tables 6-7).
-The accuracy metric can be artificially inflated by true negatives (TN), the set of genomic bins correctly predicted as not containing a ground truth boundary.
-AUC captures how a model generally performs accross different thresholds.
-However, it doesn't place more emphasis on one class over the other, so it does not reflect the minority class well.
+Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Supplementary Tables 6-7 [???
+Merge them into one Excel with two sheets - same message]).
+The accuracy metric can be artificially inflated by true negatives (TN), the set of genomic bins correctly predicted as not containing a ground truth boundary [???
+Is it because of class imbalance?].
+AUROC captures how a model generally performs accross different thresholds.
+However, it doesn't place more emphasis on one class over the other, so it does not reflect the minority class well [???
+So, another class imbalance problem?
+Define class imbalance message early, why you investigated 5 other metrics].
 Precision indicates the rate at which positive predictions are correct and can be artificially deflated by low proportions of true positives (TP), the set of genomic bins correctly predicted as containing a ground truth boundary.
 While F1-score is a composite metric, it can be very sensitive towards disparate values for precision and recall.
-Lastly, AUPRC is insensitive toward class imbalance and also omits from its calculation TN values.
+Lastly, AUPRC is insensitive toward class imbalance and also omits from its calculation TN values [???
+So why didn't you use it?].
 All of these are important considerations to make when choosing a performance metric.
 For these reasons we opted to report the balanced accuracy (BA).
-The BA benifits from incorporating all components of the confusion matrix, while also being sensitive to class imbalance, a necessary characteristic when comparing performances to models built using no data re-sampling.
+The BA benefits from incorporating all components of the confusion matrix, while also being sensitive to class imbalance, a necessary characteristic when comparing performances to models built using no data re-sampling.
+[???
+The logic is messed when reading this paragraph.]
 
-The performance of *preciseTAD* was found to be empirically better than both ARROWHEAD and Peakachu ground truth boundaries.
-*preciseTAD* provides bp resolution predicted boundaries, thereby alleviating resolution limitations of conventional TAD-callers.
-We show that, unlike ARROWHEAD, *preciseTAD* does not inflate the number of predicted boundaries, instead, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
-*preciseTAD* boundaries were found to be more enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143.
+The performance of *preciseTAD* was found to be empirically better [???
+As judged by what?] than both ARROWHEAD and Peakachu ground truth boundaries.
+Guided by both low-resolution Hi-C data and high-resolution genome annotation data, *preciseTAD* predicts base-level resolution boundaries, alleviating resolution limitations of Hi-C data.
+We show that, unlike ARROWHEAD, *preciseTAD* does not inflate the number of predicted boundaries [???
+Where did you show this?
+TBD], instead, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
+*preciseTAD* boundaries were found to be more enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143 [???
+So what?].
 Likewise *preciseTAD* boundaries were found to be more conserved between GM12878 and K562 cell lines, further highlighting their biological significance.
+[???
+So what?]
 
 A limitation of *preciseTAD* is that it is dependent on "ground truth" boundaries provided by a user-defined TAD caller.
-Ideally we would perform simulation studies to benchmark *preciseTAD* against simulated boundaries.
-While there are existing methods for simulating Hi-C data sets [@forcato2017comparison; @zheng2020freehi], of which boundaries can be extracted from, to date, there are no such methods for simulating ChIP-seq data.
-However, given *preciseTAD* is applied on chromosome-specific sections of the linear genome, and on multiple cell lines, we feel that aggregating results across chromosomes provides strong empirical evidence of the superiority of *preciseTAD*.
-Another limitation is that *preciseTAD* does not provide hierarchical boundaries, but instead simply provides the bp coordinate that demarcates TADs(loops).
+Given the wide variery of TAD callers and their variable performance [@Zufferey:2018aa; @forcato2017comparison], it is hard to define "ground truth" TAD boundaries.
+Ideally we would benchmark *preciseTAD* against simulated boundaries.
+While methods for simulating Hi-C data sets wish boundary annotations exist [@forcato2017comparison; @zheng2020freehi], methods for simulating the associated genomic annotations (the main component guiding *preciseTAD* predictions) are lacking.
+Given *preciseTAD* can be trained on the whole-genome data, we feel that the total number of TAD/loop boundaries is sufficient to guide learning of the association between genomic annotations and boundaries for precise boundary predictions.
+
+Another limitation of *preciseTAD* is that it does not provide hierarchical boundaries, but instead provides the coordinates of boundary points and regions.
 Studies have shown evidence of the hierarchical nature to the 3D architecture of the human genome [@hansen2018recent; @weinreb2016identification; @fraser2015hierarchical].
-In such a hierarchy, the boundaries provided by *preciseTAD* can be interpreted as the lowest level of boundaries.
+In such a hierarchy, the boundaries provided by *preciseTAD* can be interpreted as the lowest level of boundaries [???
+This can be debated.
+We are training on and predicting certain level of boundaries.
+Suggesting discussing that false positives detected by preciseTAD may represent boundaries at finer resolution].
 
-In summary, we have shown that TAD boundary prediction is a multi-faceted problem composed of many data irregularities and characteristics.
-Simply quering a contact matrix ignores the fundamental roles of known molecular drivers of 3D chromatin.
-Instead, we propose a method for turning TAD-calling into a supervised machine learning framework built using ChIP-seq annotations.
-Specifically, we introduce two novel concepts known as *shifted binning* and *distance*-type predictors which we use to build random forest classification models for predicting boundary regions.
-We then introduce *preciseTAD*, a method for leveraging random forests to predict TAD(loop) boundaries at base pair resolution.
+In summary, we demonstrate that TAD/loop boundary prediction is a multi-faceted problem requiring consideration of multiple statistical and biological properties of genomic data.
+Simply considering the properties of Hi-C contact matrices ignores the fundamental roles of known molecular drivers of the 3D chromatin structures.
+Instead, we propose a supervised machine learning framework that leverages both Hi-C contact matrix information and genomic annotations.
+Our method introduces three concepts - *shifted binning*, *distance*-type predictors, and *random undersampling* - which we use to build random forest classification models for predicting boundary regions.
 Our method is able to bridge the resolution gap between 1D ChIP-seq annotations and 3D Hi-C sequencing data for more precise and biologically meaningful boundary identification.
-By releasing our method as an open source R package, we hope to provide an efficient and easy-to-use tool to further explore the 3D organization of the human genome.
+We introduce *preciseTAD*, an open source R package for leveraging random forests to predict TAD/loop boundaries at base resolution.
+We hope that *preciseTAD* will serve as an efficient and easy-to-use tool to further explore the 3D organization of the genome.
 

### 2020-07-08 Manuscript/manuscript.Rmd
Fixes for all ??? that MD could fix

@@
 
-Several methods have been proposed to identify the genomic coordinates of TAD boundaries throughout the linear genome [@dixon2012topological;@rao20143d;@sexton2012three;@chen2016novo;@filippova2014identification;@shin2016topdom;@weinreb2016identification], less so for chromatin loops [@salameh2019supervised;@kai2018predicting].
-[???
-Check refs, the current ones are suboptimal.
-Check SpectralTAD paper for refs about TAD callers, use https://github.com/mdozmorov/HiC_tools#loop-callers for loop callers] However, a key limitation among most of these TAD- and loop callers, referred hereafter as TAD callers for brevity, is that they are heavily reliant on Hi-C data *resolution*.
+Several methods have been proposed to identify the genomic coordinates of TAD boundaries throughout the linear genome (reviewed in [@Zufferey:2018aa; @forcato2017comparison]), less so for chromatin loops [@rao20143d; @Ay:2014aa; @Heinz:2010aa].
+However, a key limitation among most of these TAD- and loop callers, referred hereafter as TAD callers for brevity, is that they are heavily reliant on Hi-C data *resolution*.
 Resolution refers to the sizes of genomic bins used to segment the linear genome as a way to deal with low signal-to-noise incurred by the high dimensional nature of Hi-C data [@li2019comparison].
@@
 Another limitation among TAD callers is that they disregard prior knowledge about functional genomic elements associated with TAD and loop boundaries.
-The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been hypothesized to comprise components of the loop extrusion model, whereby DNA is extruded through cohesin rings forming chromatin loops [@hansen2018recent;@fudenberg2016formation;@alipour2012self;@sanborn2015chromatin].
+The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been hypothesized to comprise components of the loop extrusion model, whereby DNA is extruded through cohesin rings forming chromatin loops [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
 Additionally, distinct patterns of histone modifications have also been shown to be featured at boundaries, including H3K36 timethylation (H3K36me3) [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
@@
 Detail next - BroadHMM and histone were tested, OC, OP were tested, various sampling techniques.
-Conclude with findings and package availability]
+Conclude with findings and package availability.
+For MD, last part when ready to write an abstract]
 
@@
 [???
-Is there other resolution?
-???
-TAD and loop boundaries should be distinguished, to describe when we have all results] [???
-Define that ARROWHEAD data constitute the main results]
+TAD and loop boundaries should be distinguished, to describe when we have all results.
+For MD] [???
+Define that ARROWHEAD data constitute the main results.
+For MD]
 
@@
 Finally, step 5 is to validate the model on the separate test data and evaluate model performance using balanced accuracy (BA).](Figures/figure2_ensemble_framework.png) [???
-DEfine all indices, what is N, p+1, i?]
+Define all indices, what is N, p+1, i?]
 
@@
 
-![**???[needs updating with new framework, takes longest, do last] Distance-type predictors combined with random under-sampling yielded optimal TAD boundary region predictive performance for GM12879 ARROWHEAD TAD boundaries.** Balanced accuracy is compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).](Figures/figure3_performances.png)
+![**???[needs updating with new framework, takes longest, do last - ???
+Is this current?] Distance-type predictors combined with random under-sampling yielded optimal TAD boundary region predictive performance for GM12879 ARROWHEAD TAD boundaries.** Balanced accuracy is compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).](Figures/figure3_performances.png)
 
@@
 We further optimized our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
-In summary, our framework was able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@hansen2018recent;@fudenberg2016formation;@alipour2012self;@sanborn2015chromatin].
+In summary, our framework was able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
 
@@
 
-Using our optimally built random forest model, we attempted to overcome resolution limitations of Hi-C data by predicting TAD [???
-Check throughout the manuscript - we may need to define "interacting domains" referring to TADs and loops] boundaries at base resolution.
+Using our optimally built random forest model trained on ARROWHEAD/Peakachu boundaries, we attempted to predict TAD/loop boundaries at base resolution.
 Intuitively, the predictor-response space is built on a base-resolution level, and the model trained on a bin-level space predicts the probability of each base being a boundary.
@@
 Our random forest framework yielded several interesting observations.
-First, we showed that RF models built using *distance*-type predictors out performed models built on previously published feature engineering techniques including signal strength, overlap counts and overlap percents [@mourad2016computational].
-[???
-Add more REFs] We further demonstrated that class imbalance hinders boundary prediction, but can be effectively addressed by a simple random under-sampling technique.
-The unaddressed class imbalance problem in previous studies [???
-Add REFs] We showed that information about only four transcription factors (SMC3, Rad21, CTCF, Znf143) is necessary and sufficient transcription for accurate boundary prediction, out-performing histone modification- and BroadHMM-built models.
-These are known components of the loop extrusion model, an established theory for how loops are made by a ring-shaped adenosine triphosphatase complex called cohesin [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self].
+First, we showed that RF models built using *distance*-type predictors outperformed models built on previously published feature engineering techniques including signal strength, overlap counts and overlap percents [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa; @kai2018predicting].
+We further demonstrated that class imbalance hinders boundary prediction, but can be effectively addressed by a simple random under-sampling technique.
+The unaddressed class imbalance problem in previous studies [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa] We showed that information about only four transcription factors (SMC3, Rad21, CTCF, Znf143) is necessary and sufficient transcription for accurate boundary prediction, outperforming histone modification- and BroadHMM-built models [@Moore:2015aa; @Al-Bkhetan:2018aa].
+These are known components of the loop extrusion model, an established theory for how loops are made by a ring-shaped adenosine triphosphatase complex called cohesin [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
 Interestingly, the same transcription factors accurately predicted both TAD and loop boundaries, suggesting similarity of the mechanisms of TAD and loop formation.

### 2020-07-10 Manuscript/manuscript.Rmd
addressed some ???, need to discuss others

@@
 To obtain TAD boundaries we applied ARROWHEAD using downloaded primary Hi-C data from Geo GSE63525 [@rao20143d] for the GM12878 and K562 cell lines (libraries HIC001-HIC018 and HIC069-HIC074 for GM12878 and K562 respectively) [???
-Were they threated separately?] produced with the MboI restriction enzyme (Supplementary Table 1).
+Were they threated separately?;!!!fixed] produced with the MboI restriction enzyme (Supplementary Table 1).
 The contact matrices were constructed from all read pairs that uniquely aligned to the genome (MAPQ>0).
@@
 Cell line-specific genomic annotations were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] in the form of BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) (GRCh37/hg19 human genome assembly, Supplementary Table 2).
+
+[???added spectralTAD]
 
@@
 Bins were annotated by one of either the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average signal strength of the corresponding annotation (*Peak Signal Strength*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
-A $log_2$-transformation [???
-Shouldn't it be log2 + 1?] of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
+A ($log_2$+1)-transformation [???
+Shouldn't it be log2 + 1?; yes, fixed] of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
 Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin segmentations lack signal values.
@@
 
-## Establishing computational framework for assessing model performance
+## Establishing optimal data level characteristics for TAD boundary region prediction
 
 Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, feature engineering procedures, and re-sampling techniques.
-First, the data matrix $A_{N \times (p+1)}$ was constructed by combining the binned genome from each of the $n-1$ autosomal chromosomes ($1,2,\cdots, i-1,i+1,\cdots,22$) [???
-Define N and p asap introducing.
-What is i?
-also define immediately.
-Adjust this whole paragraph accordingly.
-There's a term "hold-out" - isn't it how you should define it?] as well as a particular feature engineering procedure.
-Re-sampling was then performed on $A$.
-An RF classifier was then trained on $A$ using 3-fold cross-validation to tune for the number of annotations, *p*, to consider at each node (*mtry*).
+A *holdout chromosome* technique was devised as a way for unbiased model evaluation on each autosomal chromosome.
+The $i^{th}$ holdout chromosome was identified and a data matrix, $A_{N \times (p+1)}$, was constructed by combining the binned genome from the remaining chromosomes ($1,2,\cdots, i-1,i+1,\cdots,21,22$), where $N=[n_{1} n_{2} \cdots n_{21} n_{22}]'$ and $n_{k}$ is the length of chromosome *k* after being binned into non-overlapping regions of resolution *r*, such that $k \ne i$.
+Re-sampling was then performed on $A$ and an RF classifier was trained on $A$ using 3-fold cross-validation to tune for the number of annotations, *p*, to consider at each node (*mtry*).
 The number of trees (*ntree*) that were aggregated for each RF model was set to 500.
 The minimum number of observations per root node (*nodesize*) was set to 1.
-To evaluate model performance, the $i^{th}$ chromosome was used for testing.
-The performance of each combination of model inputs was compared using Balanced Accuracy (BA), defined as the average of sensitivity and specificity:
+The binned data for the holdout chromosome $i$ was reserved for testing.
+Models were evaluated using Balanced Accuracy (BA), defined as the average of sensitivity and specificity:
 
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the test data.
-Performances were aggregated across each $i^{th}$ holdout chromosome using means and standard deviations.
+The process was repeated for each $i^{th}$ holdout chromosome and performances were aggregated using means and standard deviations.
+[??? Define N and p asap introducing. What is i? also define immediately. Adjust this whole paragraph accordingly. There's a term "hold-out" - isn't it how you should define it?; !!!rewrote]
 
@@
 
-[??? There is a big gap there. Describe the construction of dependent vector Y and predictor matrix _for each base_]
+[??? There is a big gap there. Describe the construction of dependent vector Y and predictor matrix _for each base_;!!!talk about in meeting]
 
@@
 We need to define what to italicize.
-Check below, make consistent throughout the manuscript] (version 1.1-5) was applied to the matrix of pairwise genomic distances between base pairs with $p_{n_{i}}=1$.
+Check below, make consistent throughout the manuscript;!!!talk about in meeting] (version 1.1-5) was applied to the matrix of pairwise genomic distances between base pairs with $p_{n_{i}}=1$.
 This was to avoid the inflation of predicted boundaries that can occur naturally when dealing with such fine resolution, namely, due to spatially close base pairs with similar predictor profiles (i.e.
@@
 Next, we assessed the biological significance of our predicted boundaries with respect to the enrichment profiles of several known molecular drivers of 3D chromatin architecture including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
-To do so, we used the computeMatrix [???
-Again, I expected italics, but decide and correct] and plotHeatmap tools offered by deepTools version 2.0 [@ramirez2016deeptools2] via integration with Galaxy version 3.3.2.0.0 [@afgan2018galaxy].
+To do so, we used the *computeMatrix* [???
+Again, I expected italics, but decide and correct;!!!talk about in meeting] and *plotHeatmap* tools offered by *deepTools* version 2.0 [@ramirez2016deeptools2] via integration with Galaxy version 3.3.2.0.0 [@afgan2018galaxy].
 Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum test.
@@
 To demonstrate, we applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines obtained from GEO GSE63525 (Supplementary Table 1) [???
-Update table and methods with relevant data only, not individual samples].
+Update table and methods with relevant data only, not individual samples;!!!fixed].
 TADs were subsequently called using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
@@
 Boundary regions were defined as regions containing a called boundary ($Y = 1$), while non-boundary regions were defined as genomic bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
-The total number of TADs, TAD boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 3 [???
+The total number of TADs, TAD boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 2 [???
 I can see numbers for K562 (?) only?
-There's a discrepancy with legend.]).
-The number of non-boundary regions highly outnumbered boundary regions, with results consistent for loop boundaries as well (Supplementary Table 4).
+There's a discrepancy with legend.!!!fixed, need to added spectralTAD]).
+The number of non-boundary regions highly outnumbered boundary regions, with results consistent for loop boundaries as well (Supplementary Table 3).
 Such disproportional presence of examples in one class is known as a "class imbalance" problem that negatively affects predictive modeling [@prati2011survey; @wei2013role].
@@
 
-A total of 78 [???
-77 in the table?] cell-line-specific functional genomic annotations were used to build the predictor space.
-These included BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS, Supplementary Table 2).
+A total of 77 [???
+77 in the table?;!!!fixed] cell-line-specific functional genomic annotations were used to build the predictor space.
+These included BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 4).
 Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
@@
 Finally, step 5 is to validate the model on the separate test data and evaluate model performance using balanced accuracy (BA).](Figures/figure2_ensemble_framework.png) [???
-Define all indices, what is N, p+1, i?]
+Define all indices, what is N, p+1, i?;!!!defined in methods, define here again?]
 
@@
 ![**???[needs updating with new framework, takes longest, do last - ???
-Is this current?] Distance-type predictors combined with random under-sampling yielded optimal TAD boundary region predictive performance for GM12879 ARROWHEAD TAD boundaries.** Balanced accuracy is compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).](Figures/figure3_performances.png)
+Is this current?;talk about in meeting] Distance-type predictors combined with random under-sampling yielded optimal TAD boundary region predictive performance for GM12879 ARROWHEAD TAD boundaries.** Balanced accuracy is compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).](Figures/figure3_performances.png)
 
@@
 Our method, referred to as *preciseTAD*, leverages a user-specified [???
-We need pre-trained models and understanding how they perform on different cell lines] model with density-based hierarchical clustering (DBSCAN) and a scalable partitioning around mediods clustering (CLARA) to predict the boundary location ad base resolution (see Methods).
+We need pre-trained models and understanding how they perform on different cell lines;!!!working on it] model with density-based hierarchical clustering (DBSCAN) and a scalable partitioning around mediods clustering (CLARA) to predict the boundary location ad base resolution (see Methods).
 
@@
 boundaries for GM12878 and K562 cell lines respectively.
-We reported less predicted TAD boundaries than ARROWHEAD (Table 1, Supplementary Table 3) [???
-Where is this info?].
-This may be attributed to ARROWHEAD's boundaries frequently being separated by gaps, the effect especially pronounced near sparse areas of Hi-C contact matrices (Figure 5A) [???
+We reported less predicted TAD boundaries than ARROWHEAD (Table 1, Supplementary Table 2) [???
+Where is this info?;!!!talk about in meeting].
+This can be attributed to ARROWHEAD's boundaries frequently being separated by gaps, the effect especially pronounced near sparse areas of Hi-C contact matrices (Figure 5A) [???
 I don't see it, data not shown?].
@@
 Signal heatmaps [???
-Make sure to mention DeepTools in Methods] indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or Peakachu boundaries alone (Figure 5 B-C).
+Make sure to mention DeepTools in Methods;!!!added] indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or Peakachu boundaries alone (Figure 5 B-C).
 Likewise, *preciseTAD* boundaries were also more enriched for other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 8-9).
@@
 - stretched, can be put in figure.
-Can you color triangulars blue/red for Arrowhead/Peakachu, green for preciseTAD?]
+Can you color triangulars blue/red for Arrowhead/Peakachu, green for preciseTAD?;!!!can't be done for peakachu because we only have 1 resolution (10kb)]
 
@@
 (B) Venn diagrams illustrating the agreement between boundaries predicted using ARROWHEAD- and Peakachu-trained models.](Figures/figure6_venn_diagrams.png)
-[??? What is the difference between leftmost Venn diagrams on panel A?] [??? What are the numbers?]
+[??? What is the difference between leftmost Venn diagrams on panel A?] [??? What are the numbers?;!!!talk in meeting]
 
@@
 An example script for applying the ARROWHEAD tool to in situ Hi-C data (HIC001-HIC018) for resolutions 5kb, 10kb, 25kb, 50kb, 100kb to obtain chromosome-specific TAD boundaries on the GM12878 cell line.
+Prior to implementing SpectralTAD, the dump command offered by juicer [@durand2016juicer] was used to extract the contacts in sparse data matrix format.
 
@@
 
-**Supplementary Table 2.** A complete list of the genomic annotations used to build the predictor space for all downstream models.
+**Supplementary Table 2.** Domain boundary and class imbalance summaries from ARROWHEAD for the K562 cell line. [???add spectralTAD]
+
+**Supplementary Table 3.** Loop boundary and class imbalance summaries from Peakachu 10 kb resolution for both the GM12878 and K562 cell lines respectively.
+
+**Supplementary Table 4.** A complete list of the genomic annotations used to build the predictor space for all downstream models.
 The GRCh37/hg19 human genome assembly was used.
@@
 Each density curve represents individual genomic annotation.
-
-**Supplementary Table 3.** Domain boundary and class imbalance summaries from SpectralTAD across resolution for both the
-GM12878 and K562 cell lines respectively.
-
-**Supplementary Table 4.** Loop boundary and class imbalance summaries from Peakachu 10 kb resolution for both the GM12878 and K562 cell lines respectively.
 

### 2020-07-11 Manuscript/manuscript.Rmd
addressed some ???

@@
 
-[??? There is a big gap there. Describe the construction of dependent vector Y and predictor matrix _for each base_;!!!talk about in meeting]
+[???
+There is a big gap there.
+Describe the construction of dependent vector Y and predictor matrix _for each base_;!!!talk about in meeting; specify that each base pair has own prob; don't use "base pair" only "base" or "base level"]
 
 First the vector, $p_{n_{i}}$, denoting each base pair's probability of being a boundary point from the RF model, was extracted, where $n_{i}$ represents the length of chromosome $i$.
-Next, *DBSCAN* [???
+Next, DBSCAN [???
 We need to define what to italicize.
@@
 The resulting clusters of highly predictive base pairs identified by DBSCAN were termed *preciseTAD boundary regions* (PTBR).
-To precisely identify a single base pair among each PTBR, *preciseTAD* then implements an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
+To precisely identify a single base pair among each PTBR, preciseTAD then implements an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
 The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative and biologically meaningful base pair coordinate within each clustered PTBR.
@@
 Next, we assessed the biological significance of our predicted boundaries with respect to the enrichment profiles of several known molecular drivers of 3D chromatin architecture including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
-To do so, we used the *computeMatrix* [???
-Again, I expected italics, but decide and correct;!!!talk about in meeting] and *plotHeatmap* tools offered by *deepTools* version 2.0 [@ramirez2016deeptools2] via integration with Galaxy version 3.3.2.0.0 [@afgan2018galaxy].
+To do so, we used the computeMatrix [???
+Again, I expected italics, but decide and correct;!!!talk about in meeting] and plotHeatmap tools offered by deepTools version 2.0 [@ramirez2016deeptools2] via integration with Galaxy version 3.3.2.0.0 [@afgan2018galaxy].
 Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum test.
@@
 - stretched, can be put in figure.
-Can you color triangulars blue/red for Arrowhead/Peakachu, green for preciseTAD?;!!!can't be done for peakachu because we only have 1 resolution (10kb)]
+Can you color triangulars blue/green for Arrowhead/preciseTAD, green for preciseTAD?;!!!can't be done for peakachu because we only have 1 resolution (10kb)]
 
@@
 (B) Venn diagrams illustrating the agreement between boundaries predicted using ARROWHEAD- and Peakachu-trained models.](Figures/figure6_venn_diagrams.png)
-[??? What is the difference between leftmost Venn diagrams on panel A?] [??? What are the numbers?;!!!talk in meeting]
+[??? What is the difference between leftmost Venn diagrams on panel A?] [??? What are the numbers?;!!!talk in meeting; add indication of what ground truth is for preciseTAD]
 
@@
 The accuracy metric can be artificially inflated by true negatives (TN), the set of genomic bins correctly predicted as not containing a ground truth boundary [???
-Is it because of class imbalance?].
+Is it because of class imbalance?; add detail].
 AUROC captures how a model generally performs accross different thresholds.
@@
 Lastly, AUPRC is insensitive toward class imbalance and also omits from its calculation TN values [???
-So why didn't you use it?].
+So why didn't you use it?
+for MD].
 All of these are important considerations to make when choosing a performance metric.

### 2020-07-11 Manuscript/manuscript.Rmd
A couple of thoughts

@@
 
-Several methods have been proposed to identify the genomic coordinates of TAD boundaries throughout the linear genome (reviewed in [@Zufferey:2018aa; @forcato2017comparison]), less so for chromatin loops [@rao20143d; @Ay:2014aa; @Heinz:2010aa].
+Several methods have been proposed to identify the genomic coordinates of TAD boundaries throughout the linear genome (reviewed in [@Zufferey:2018aa; @forcato2017comparison]), less so for chromatin loops [@rao20143d; @Ay:2014aa; @Heinz:2010aa; @salameh2019supervised].
 However, a key limitation among most of these TAD- and loop callers, referred hereafter as TAD callers for brevity, is that they are heavily reliant on Hi-C data *resolution*.
@@
 TBD], instead, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
-*preciseTAD* boundaries were found to be more enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143 [???
+*preciseTAD* TAD and loop boundaries were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops are dynamic structures generated by similar mechanisms [@hansen2018recent].
+[???
 So what?].

### 2020-07-12 Manuscript/manuscript.Rmd
Fix data, abbreviations ???

@@
 
-Within this study we used both TAD boundary and loop boundary data derived from the publically available tools ARROWHEAD [@durand2016juicebox] and Peakachu [@salameh2019supervised] respectively.
-ARROWHEAD is part of the Juicer suite of tools for Hi-C data analysis and visualization.
-To obtain TAD boundaries we applied ARROWHEAD using downloaded primary Hi-C data from Geo GSE63525 [@rao20143d] for the GM12878 and K562 cell lines (libraries HIC001-HIC018 and HIC069-HIC074 for GM12878 and K562 respectively) [???
-Were they threated separately?;!!!fixed] produced with the MboI restriction enzyme (Supplementary Table 1).
+Within this study we used both TAD boundary and loop boundary data derived from the publicly available tools ARROWHEAD [@durand2016juicebox] and Peakachu [@salameh2019supervised] respectively.
+ARROWHEAD TAD boundaries were called from primary Hi-C data from Geo GSE63525 [@rao20143d] for the GM12878 and K562 cell lines (Supplementary Table 1).
 The contact matrices were constructed from all read pairs that uniquely aligned to the genome (MAPQ>0).
 The default tools for ARROWHEAD were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1).
-For chromatin loop boundaries, we used loops identified by Peakachu at 10 kb for the GM12878 and K562 cell lines [@salameh2019supervised].
+Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab web site (Supplementary Table 1).
 Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop.
-Chromosome 9 was excluded from all downstream analyses due to the sparsity of the contact matrix at the 5 kb and 10 kb resolutions for the K562 cell line.
-Cell line-specific genomic annotations were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] in the form of BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) (GRCh37/hg19 human genome assembly, Supplementary Table 2).
+Chromosome 9 was excluded from all downstream analyses due to sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
+Cell-line-specific genomic annotations (BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa]  (GRCh37/hg19 human genome assembly, Supplementary Table 2).
 
@@
 Bins were annotated by one of either the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average signal strength of the corresponding annotation (*Peak Signal Strength*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
-A ($log_2$+1)-transformation [???
-Shouldn't it be log2 + 1?; yes, fixed] of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
+A ($log_2 + 1$)-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
 Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin segmentations lack signal values.
@@
 The $i^{th}$ holdout chromosome was identified and a data matrix, $A_{N \times (p+1)}$, was constructed by combining the binned genome from the remaining chromosomes ($1,2,\cdots, i-1,i+1,\cdots,21,22$), where $N=[n_{1} n_{2} \cdots n_{21} n_{22}]'$ and $n_{k}$ is the length of chromosome *k* after being binned into non-overlapping regions of resolution *r*, such that $k \ne i$.
-Re-sampling was then performed on $A$ and an RF classifier was trained on $A$ using 3-fold cross-validation to tune for the number of annotations, *p*, to consider at each node (*mtry*).
+$p$, the number of annotations, together with one response vector, define column-wise dimension of the matrix $A$.
+Re-sampling was then performed on $A$ and an RF classifier was trained using 3-fold cross-validation to tune for the number of annotations to consider at each node (*mtry*).
 The number of trees (*ntree*) that were aggregated for each RF model was set to 500.
@@
 The process was repeated for each $i^{th}$ holdout chromosome and performances were aggregated using means and standard deviations.
-[??? Define N and p asap introducing. What is i? also define immediately. Adjust this whole paragraph accordingly. There's a term "hold-out" - isn't it how you should define it?; !!!rewrote]
 
@@
 
-**Supplementary Table 1.** A complete list of the Hi-C data libraries obtained from GEO GSE63525 [@rao20143d] used to obtain the locations of topologically associating domains for ARROWHEAD, as well as the locations for the cell line specific .txt files of loop boundaries obtained by Peakachu.
-[@salameh2019supervised].
+**Supplementary Table 1.** Data source for Hi-C matrices used to call topologically associated domains with ARROWHEAD, as well as loop boundaries obtained by Peakachu.
 

### 2020-07-23 Manuscript/manuscript.Rmd
Add micro-C discussion

@@
 Given the wide variery of TAD callers and their variable performance [@Zufferey:2018aa; @forcato2017comparison], it is hard to define "ground truth" TAD boundaries.
-Ideally we would benchmark *preciseTAD* against simulated boundaries.
-While methods for simulating Hi-C data sets wish boundary annotations exist [@forcato2017comparison; @zheng2020freehi], methods for simulating the associated genomic annotations (the main component guiding *preciseTAD* predictions) are lacking.
-Given *preciseTAD* can be trained on the whole-genome data, we feel that the total number of TAD/loop boundaries is sufficient to guide learning of the association between genomic annotations and boundaries for precise boundary predictions.
+<!--Ideally we would benchmark *preciseTAD* against simulated boundaries.
+While methods for simulating Hi-C data sets with boundary annotations exist [@forcato2017comparison; @zheng2020freehi], methods for simulating the associated genomic annotations (the main component guiding *preciseTAD* predictions) are lacking.-->Ultra-deep Hi-C sequencing [@bonev2017multiscale] and newer technologies for precise mapping of chromatin interactions (e.g., Micro-C [@Krietenstein:2020aa]), coupled with more precise technologies for genomic annotation profiling (e.g., CUT&RUN for precise mapping of transcription factor binding sites) will help to refine the location and the genomic signatures of "ground truth" TAD boundaries.
+In the current work, given *preciseTAD* can be trained on the whole-genome data, we feel that the total number of TAD/loop boundaries is sufficient to guide learning of the association between genomic annotations and boundaries for precise boundary predictions.
 
-Another limitation of *preciseTAD* is that it does not provide hierarchical boundaries, but instead provides the coordinates of boundary points and regions.
+Another limitation of *preciseTAD* is that it does not provide information about hierarchy of TAD boundaries, but instead provides the coordinates of boundary points and regions.
 Studies have shown evidence of the hierarchical nature to the 3D architecture of the human genome [@hansen2018recent; @weinreb2016identification; @fraser2015hierarchical].

### 2020-07-23 Manuscript/manuscript.Rmd
Discuss different TAD boundary types

@@
 
-Another limitation of *preciseTAD* is that it does not provide information about hierarchy of TAD boundaries, but instead provides the coordinates of boundary points and regions.
-Studies have shown evidence of the hierarchical nature to the 3D architecture of the human genome [@hansen2018recent; @weinreb2016identification; @fraser2015hierarchical].
-In such a hierarchy, the boundaries provided by *preciseTAD* can be interpreted as the lowest level of boundaries [???
-This can be debated.
-We are training on and predicting certain level of boundaries.
-Suggesting discussing that false positives detected by preciseTAD may represent boundaries at finer resolution].
+Another limitation of *preciseTAD* is that it does not distinguish boundary types.
+The hierarchical nature of TAD boundaries [@weinreb2016identification; @fraser2015hierarchical; @Cresswell:2020ab] is not considered by *preciseTAD* due to the lack of gold standard of TAD hierarchy.
+Recent research distinguishes CTCF-associated boundaries, CTCF-negative YY1-enriched boundaries, CTCF- and YY1- depleted promoter boundaries, and a fourth class of weak boundaries largely depleted of all three features [@Krietenstein:2020aa].
+Furthermore, actively transcribed regions can serve as TAD boundaries themselves, independently of CTCF binding [@Harrold:2020aa].
+This may lead to high proportion of TAD boundaries being undetected by *preciseTAD* despite being detected by TAD callers [???
+What is the false positive rate?
+We may be missing TADs that are distinct from the canonical CTCF boundaries.
+TBD].
+Our future work will include defining separate models trained on different TAD boundary types, and predicting precise locations for each of them.
 

### 2020-07-31 Manuscript/manuscript.Rmd
updated results

@@
 output:
+  pdf_document: 
   word_document:
     reference_docx: styles.doc/NIH_grant_style.docx
-  pdf_document: default
 bibliography: References/references.bib
@@
 The contact matrices were constructed from all read pairs that uniquely aligned to the genome (MAPQ>0).
-The default tools for ARROWHEAD were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1).
-Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab web site (Supplementary Table 1).
+The default parameters for ARROWHEAD were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1).
+Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab web site <!--(Supplementary Table 1)-->.
 Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop.
 Chromosome 9 was excluded from all downstream analyses due to sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-Cell-line-specific genomic annotations (BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa]  (GRCh37/hg19 human genome assembly, Supplementary Table 2).
+Cell-line-specific genomic annotations (BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa]  (GRCh37/hg19 human genome assembly<!--, Supplementary Table 2-->).
 
@@
 To do so, we used the computeMatrix [???
-Again, I expected italics, but decide and correct;!!!talk about in meeting] and plotHeatmap tools offered by deepTools version 2.0 [@ramirez2016deeptools2] via integration with Galaxy version 3.3.2.0.0 [@afgan2018galaxy].
+Again, I expected italics, but decide and correct;!!!talk about in meeting] and plotHeatmap tools offered by deepTools version 2.0 [@ramirez2016deeptools] via integration with Galaxy version 3.3.2.0.0 [@afgan2018galaxy].
 Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum test.
@@
 
-We developed a machine learning framework<!--, refered to as *TADRF*,--> aimed at determining the optimal set of data level characteristics necessary for topologically associated domain (TAD) boundary prediction.
+We developed a machine learning framework aimed at determining the optimal set of data level characteristics necessary for topologically associated domain (TAD) boundary prediction.
 We chose the random forest (RF) machine learning algorithm as our binary classification tool.
@@
 There's a discrepancy with legend.!!!fixed, need to added spectralTAD]).
-The number of non-boundary regions highly outnumbered boundary regions, with results consistent for loop boundaries as well (Supplementary Table 3).
+The number of non-boundary regions highly outnumbered boundary regions, with results consistent for loop boundaries as well.
 Such disproportional presence of examples in one class is known as a "class imbalance" problem that negatively affects predictive modeling [@prati2011survey; @wei2013role].
@@
 77 in the table?;!!!fixed] cell-line-specific functional genomic annotations were used to build the predictor space.
-These included BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 4).
+These included BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 3).
 Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
@@
 The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD boundary, respectively.
-(B) Four types of associations between bins and genomic annotations (green shapes) were considered to build the predictor space including _Average Peak Signal_ (Signal), _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.](Figures/figure1_model_construction_and_predictor_types.png)
+(B) Four types of associations between bins and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and ($log_{2}$) Distance.](Figures/figure1.png)
 
@@
 
-![**A diagram of the machine learning framework.** Step 1 defines the chromosome-specific predictor-response matrix **A** of $N$ genomic bins (rows), $p$ genomic annotations, and one response vector $Y$ ($p+1$ columns).
-Resolution-specific data (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)) for the $n-1$ autosomal chromosomes.
-Step 2 is to reserve the predictor-response matrix for the holdout chromosome $i$ as the test data.
+![**A diagram of the machine learning framework used to build TAD/loop boundary region prediction models.** Step 1 defines the data matrix A, composed of N genomic bins for each chromosome, except a holdout chromosome *i*, *p* genomic annotations, and the response vector **Y** (for *p*+1 columns).
+Resolution-specific data (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)) for the n-1 autosomal chromosomes.
+Step 2 is to reserve the predictor-response matrix for the holdout chromosome *i* as the test data.
 Step 3 is to apply a re-sampling technique to the training set (no re-sampling, random over-sampling, random under-sampling, or SMOTE re-sampling).
-Step 4 is to train the random forest model and perform 3-fold cross-validation to tune for the *mtry* parameter.
-Finally, step 5 is to validate the model on the separate test data and evaluate model performance using balanced accuracy (BA).](Figures/figure2_ensemble_framework.png) [???
-Define all indices, what is N, p+1, i?;!!!defined in methods, define here again?]
+Step 4 is to train the random forest model and perform 3-fold cross-validation to tune for the mtry parameter.
+Finally, step 5 is to validate the model on the separate test data composed of the binned data from the holdout chromosome *i* and to evaluate model performance using balanced accuracy (BA).](Figures/figure2.png)
 
@@
 
-| Resolution | Total number of called TADs | Total number of unique TAD boundaries | Total number of genomic bins | Class imbalance |
-|:----------:|:---------------------------:|:-------------------------------------:|:----------------------------:|:---------------:|
-|5 kb        |8052                         | 15468                                 | 535363                       | 0.03            |
-|10 kb	     |7676 	                       | 14253                                 | 267682                       | 0.05            |
-|25 kb	     |4670                         | 8363                                  | 107073                       | 0.08            |
-|50 kb	     |2349	                       | 4224                                  | 53537                        | 0.08            |
-|100 kb	     |1031                         | 1883                                  | 26768                        | 0.07            |
-Table: Domain data and class imbalance summaries across resolutions for ARROWHEAD on the GM12878 cell line.
+|          Tool         |     Resolution    |     Total number of called TADs/chromatin loops    |     Total number of unique TAD/chromatin loop boundaries    |     Total number of genomic bins    |     Class imbalance    |
+|:---------------------:|:-----------------:|:--------------------------------------------------:|:-----------------------------------------------------------:|:-----------------------------------:|:----------------------:|
+|        ARROWHEAD      |       5   kb      |                         8052                       |                             15468                           |                535363               |           0.03         |
+|     ARROWHEAD         |       10   kb     |                         7676                       |                             14253                           |                267682               |           0.05         |
+|     ARROWHEAD         |       25   kb     |                         4670                       |                             8363                            |                107073               |           0.08         |
+|     ARROWHEAD         |       50   kb     |                         2349                       |                             4224                            |                 53537               |           0.08         |
+|     ARROWHEAD         |      100   kb     |                         1031                       |                             1883                            |                 26768               |           0.07         |
+|        PEAKACHU       |       10   kb     |                        16185                       |                          21421                              |                267682               |        0.14            |
+Table: TAD/loop boundary data and class imbalance summaries across resolutions for ARROWHEAD and PEAKACHU on the GM12878 cell line.
+Class imbalance is calculated as the ratio of total number of unique boundaries to the total number of genomic bins.
 
@@
 
-![**???[needs updating with new framework, takes longest, do last - ???
-Is this current?;talk about in meeting] Distance-type predictors combined with random under-sampling yielded optimal TAD boundary region predictive performance for GM12879 ARROWHEAD TAD boundaries.** Balanced accuracy is compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).](Figures/figure3_performances.png)
+![*Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for GM12878 ARROWHEAD TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
 
@@
 
-![**Binding of SMC3, Rad21, CTCF, and Znf143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (Peakachu) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+![**Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
-Error bars represent standard deviation from the cross-validated accuracy across each chromosome.
-(C) Clustered heatmap of the predictive importance for the union of the top 8 chromosome-specific most predictive TFBSs.](Figures/figure4_annots_specifc_rfe_importances_arrowhead_peakachu.png)
+Error bars represent 1 standard deviation from the cross-validated accuracy across each holdout chromosome.
+(C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs.
+The columns represent the holdout chromosome excluded from the training data.
+(D) Receiver operating characteristic (ROC) curves and subsequent area under the curves (AUCs) when training and testing on the same cell line versus across cell lines.
+The curves represent the average sensitivities and specificities across each holdout chromosome.](Figures/figure4.png)
 
@@
 
-![**preciseTAD boundaries are enriched in CTCF sites.** (A) The location of preciseTAD (green) vs.
+![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.**(A) The location of preciseTAD (green) vs.
 ARROWHEAD (blue) boundaries on GM12878 (chr 1: 70600000-71530000).
-The black line represents the probability of each base being a TAD boundary.
-The green vertical lines represent the *preciseTAD boundary points* (PTBP).
-A zoomed-in portion of the genome shows a yellow-highlighted cluster of bases with high probability of being a boundary, the *preciseTAD boundary region (PTBR).
-(B) Heatmaps comparing the enrichment of CTCF signal around preciseTAD and ARROWHEAD TAD boundaries, and (C) around preciseTAD and Peakachu loop boundaries.
-(D) $Log_{2}$ genomic distances from boundaries to nearest CTCF sites.
-(E) Pairwise Jaccard indices shows better overlap among *preciseTAD*-detected boundaries across resolutions (upper triangular) as compared to ARROWHEAD (lower triangular).](Figures/figure5_enrichment_and_log2dist_ctcf.png) [???
-Panel E - do we have it for Peakachu?
-- stretched, can be put in figure.
-Can you color triangulars blue/green for Arrowhead/preciseTAD, green for preciseTAD?;!!!can't be done for peakachu because we only have 1 resolution (10kb)]
+The black line represents the predicted probability of each base being a TAD boundary.
+A zoomed-in portion of the genome shows a yellow-highlighted cluster of bases with high probability of being a boundary, the preciseTAD boundary region (PTBR).
+(B) Enriched heatmaps comparing the enrichment of CTCF signal around ARROWHEAD TAD boundaries and preciseTAD boundaries, and (C) around Peakachu loop boundaries and preciseTAD for the entire genome.
+(D) Log 2 genomic distances from boundaries to nearest CTCF sites.
+(E) Venn diagrams illustrating the levels of conservation between TAD/loop boundaries for GM12878 (red) and K562 (blue) identified by preciseTAD (using ARROWHEAD; top left), ARROWHEAD (top right), preciseTAD (using PEAKACHU; bottom left), and PEAKACHU (bottom right).
+The median Jaccard Index (IQR) across each chromosome is provided below each venn diagram.](Figures/figure5.png)
 
@@
 Together with the results shown on Figure 4, the high overlap between boundaries predicted by ARROWHEAD- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar protein complexes.
-
-![**preciseTAD boundaries are more conserved between the GM12878 and K562 cell lines.** (A) Venn diagrams illustrating the overlap between GM12878- and K562-specific predicted and called boundaries.
-(B) Venn diagrams illustrating the agreement between boundaries predicted using ARROWHEAD- and Peakachu-trained models.](Figures/figure6_venn_diagrams.png)
-[??? What is the difference between leftmost Venn diagrams on panel A?] [??? What are the numbers?;!!!talk in meeting; add indication of what ground truth is for preciseTAD]
 
@@
 
-**Supplementary Table 2.** Domain boundary and class imbalance summaries from ARROWHEAD for the K562 cell line. [???add spectralTAD]
+**Supplementary Table 2.** TAD/loop boundary data and class imbalance summaries across resolutions for ARROWHEAD and PEAKACHU on the k562 cell line.
+Class imbalance is calculated as the ratio of total number of unique boundaries to the total number of genomic bins.
 
-**Supplementary Table 3.** Loop boundary and class imbalance summaries from Peakachu 10 kb resolution for both the GM12878 and K562 cell lines respectively.
+**Supplementary Table 3.** A complete list of the genomic annotations used to build the predictor space for all downstream models.
+The GRCh37/hg19 human genome assembly was used.
+“Genomic Class” - broad category of genomic features, “Element” - names of genomic features, “Cell Type-Specific Source” - download URL specific to the cell line (not all annotations were provided by the same institutions).
 
-**Supplementary Table 4.** A complete list of the genomic annotations used to build the predictor space for all downstream models.
-The GRCh37/hg19 human genome assembly was used.
-"Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
+**Supplementary Table 4.** Additional performance metrics when implementing a random forest using
+ARROWHEAD ground truth TAD boundaries. Performances are averaged across each holdout chromosome that was reserved for testing.
+
+**Supplementary Table 5.** Additional performance metrics when implementing a random forest using
+PEAKACHU ground truth chromatin loop boundaries. Performances are averaged across each holdout chromosome that was reserved for testing.
 
@@
 **Supplementary Figure 2.
-Distance-type predictors combined with random under-sampling yielded optimal TAD boundary region predictive performance for K562 ARROWHEAD TAD boundaries.** Balanced accuracy is compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for K562 ARROWHEAD TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.
 
 **Supplementary Figure 3.
-Distance-type predictors combined with random under-sampling or SMOTE re-sampling yielded optimal predictive performance for A) GM12878 and B) K562 Peakachu loop boundaries.** Balanced accuracy is compared within each predictor-type: Signal, OC, OP, and Distance, and across across resampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Distance-type predictors combined with random under-sampling or SMOTE re-sampling yielded optimal predictive performance PEAKACHU loop boundaries at 10 kb resolution.** Averaged balanced accuracies are compared for A) GM12878 and B) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.
 
 **Supplementary Figure 4.
-Binding of SMC3, Rad21, CTCF, and Znf143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (Peakachu) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
-Error bars represent standard deviation from the cross-validated accuracy across each chromosome.
-(C) Clustered heatmap of the predictive importance for the union of the top 8 chromosome-specific most predictive TFBSs.
+Error bars represent 1 standard deviation from the cross-validated accuracy across each holdout chromosome.
+(C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs.
+The columns represent the holdout chromosome excluded from the training data.
+(D) Receiver operating characteristic (ROC) curves and subsequent area under the curves (AUCs) when training and testing on the same cell line versus across cell lines.
+The curves represent the average sensitivities and specificities across each holdout chromosome.
+
+**Supplementary Figure 5.
+preciseTAD boundaries are more enriched for known molecular drivers of 3D chromatin.** Enriched heatmaps comparing the enrichment of preciseTAD (green) boundaries with ARROWHEAD called TAD boundaries (blue) around key (A) GM12878-specific and (B) K562-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
+
+**Supplementary Figure 6.
+preciseTAD boundaries are more enriched for known molecular drivers of 3D chromatin.** Enriched heatmaps comparing the enrichment of preciseTAD (green) boundaries with PEAKACHU predicted chromatin loop boundaries (blue) around key (A) GM12878-specific and (B) K562-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
+
+**Supplementary Figure 7.
+preciseTAD boundaries are spatially closer to known molecular drivers of 3D chromatin.** Boxplots comparing the $log_{2}$ genomic distances from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
 
 **Supplementary Figure 8.
-preciseTAD boundaries are more enriched for GM12878-specific SMC3, RAD21, and ZNF143 sites.** Enriched heatmaps comparing preciseTAD boundaries with both (A) ARROWHEAD and (B) Peakachu boundaries for the GM12878 cell line.
-
-**Supplementary Figure 9.preciseTAD boundaries are more enriched for K562-specific CTCF, SMC3, RAD21, and ZNF143 sites.** Enriched heatmaps comparing preciseTAD boundaries with both (A) ARROWHEAD and (B) Peakachu boundaries for the K562 cell line.
-
-**Supplementary Figure 10.
-preciseTAD boundaries are spatially closer to GM12878-specific SMC3, RAD21, and ZNF143 sites.** Boxplots comparing the $log_{2}$ genomic distances from each preciseTAD boundary (green) and called boundary (either ARROWHEAD or Peakachu; blue) to the nearest SMC3, RAD21, and ZNF143 sites on the linear genome for GM12878.
-
-**Supplementary Figure 11.
-preciseTAD boundaries are spatially closer to K572-specific CTCF, SMC3, RAD21, and ZNF143 sites.** Boxplots comparing the $log_{2}$ genomic distances from each preciseTAD boundary (green) and called boundary (either ARROWHEAD or Peakachu; blue) to the nearest CTCF, SMC3, RAD21, and ZNF143 sites on the linear genome for K562.
-[??? Combine Supplementary Figure 10 and 11. Make panel A and, underneath, panel B. Remove CTCF from Y-axis and put overhead labels above each plot pair]
-
-**Supplementary Table 5.** Median chromosome-specific Jaccard indices (IQR) for ARROWHEAD- and Peakachu-called and *preciseTAD* predicted boundaries between the GM12878 and K562 cell lines [???
-Where is cell line information?] [???
-What is in parentheses?].
-The p-value is from a nonparametric Wilcoxon-rank sum test [???
-Absent].
-Note, ARROWHEAD-called and predicted boundaries were flanked by 5 kb, while Peakachu-called and predicted boundaries were flanked by 10 kb prior to calculating Jaccard indices.
-
-**Supplementary Table 6.** Additional performance metrics when implementing a random forest using ARROWHEAD ground truth TAD boundaries.
-
-**Supplementary Table 7.** Additional performance metrics when implementing a random forest using Peakachu ground truth chromatin loop boundaries.
+preciseTAD predicted TAD boundaries using ARROWHEAD are nested within preciseTAD predicted chromatin loop boundaries using PEAKACHU.** Venn diagrams illustrating the agreement between boundaries predicted using ARROWHEAD- and Peakachu-trained models.
+TAD/loop boundaries were flanked by resolution (5 kb for models using ARROWHEAD and 10 kb for PEAKACHU).
 

### 2020-07-31 Scripts_for_results/01_creating_table_of_data_summaries.Rmd
updated results

@@
 
-domains <- readRDS("/home/stilianoudakisc/TAD_data_analysis/peakachu/peakachu_GM12878.rds")
+domains <- readRDS("Z:/TAD_data_analysis/peakachu/peakachu_GM12878.rds")
 
@@
 
-domains <- readRDS("/home/stilianoudakisc/TAD_data_analysis/peakachu/peakachu_K562.rds")
+domains <- readRDS("Z:/TAD_data_analysis/peakachu/peakachu_K562.rds")
 
@@
 ```
-
-## LOLLIPOP
-
-### GM12878
-
-```{r}
-CHR = paste0("CHR", c(1:8,10:22))
-numtads <- numeric()
-numbounds <- numeric()
-numbins <- numeric()
-imbalance <- numeric()
-r = "10000"
-
-#for(i in 1:length(r)){
-resolution = as.integer(r)
-
-domains <- readRDS("/home/stilianoudakisc/TAD_data_analysis/lollipop/lollipop_GM12878.rds")
-
-domains <- domains[which(domains$chr %in% as.numeric(gsub("CHR","",CHR))),]
-
-numtads <- nrow(domains)
-
-bounds <- extract_boundaries_func(domains.mat=domains, 
-                                  preprocess=FALSE, 
-                                  CHR=CHR, 
-                                  resolution=resolution)
-
-numbounds <- length(bounds)
-
-bounds.GR.flank <- flank(bounds, width=(resolution/2), both=TRUE)
-
-data_mat_list <- list()
-outcome_list <- list()
-#full_list <- list()
-#train_list <- list()
-#test_list <- list()
-
-for(j in 1:length(CHR)){
-  print(c(r,CHR[j]))
-  #start = 0
-  start = (resolution/2)
-  end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% resolution) + (resolution/2)
-  #end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% (resolution/2))
-  rows = seqDataList[[j]][seqDataList[[j]] %in% seq(start, end, resolution)]
-
-  #data_mat_list[[j]] <- matrix(nrow=length(rows),
-  #                             ncol=length(genomicElements.GR))
-  #rownames(data_mat_list[[j]]) <- rows
-
-  outcome_list[[j]] <- countOverlaps(GRanges(seqnames = tolower(CHR[j]),
-                                             IRanges(#start = as.numeric(rownames(data_mat_list[[j]])),
-                                               start = rows,
-                                               width = resolution)), bounds.GR.flank)
-  outcome_list[[j]] <- ifelse(outcome_list[[j]],1,0)
-  outcome_list[[j]] <- factor(outcome_list[[j]])
-  levels(outcome_list[[j]]) <- c("No", "Yes")
-
-  #full_list[[j]] <- cbind.data.frame(outcome_list[[j]], data_mat_list[[j]])
-  #names(full_list[[j]])[1] <- "y"
-}
-ci <- unlist(outcome_list)
-numbins <- length(ci)
-imbalance <- as.numeric(round(table(ci)[2]/sum(table(ci)),2))
-#}
-
-data.frame(resolution = c("10 kb"),
-           numtads=numtads,
-           numbounds=numbounds,
-           numbins=numbins,
-           imbalance=imbalance)
-
-```
-
-### K562
-
-```{r}
-CHR = paste0("CHR", c(1:8,10:22))
-numtads <- numeric()
-numbounds <- numeric()
-numbins <- numeric()
-imbalance <- numeric()
-r = "10000"
-
-#for(i in 1:length(r)){
-resolution = as.integer(r)
-
-domains <- readRDS("/home/stilianoudakisc/TAD_data_analysis/lollipop/lollipop_K562.rds")
-
-domains <- domains[which(domains$chr %in% as.numeric(gsub("CHR","",CHR))),]
-
-numtads <- nrow(domains)
-
-bounds <- extract_boundaries_func(domains.mat=domains, 
-                                  preprocess=FALSE, 
-                                  CHR=CHR, 
-                                  resolution=resolution)
-
-numbounds <- length(bounds)
-
-bounds.GR.flank <- flank(bounds, width=(resolution/2), both=TRUE)
-
-data_mat_list <- list()
-outcome_list <- list()
-#full_list <- list()
-#train_list <- list()
-#test_list <- list()
-
-for(j in 1:length(CHR)){
-  print(c(r,CHR[j]))
-  #start = 0
-  start = (resolution/2)
-  end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% resolution) + (resolution/2)
-  #end = seqDataList[[j]][length(seqDataList[[j]])] - (seqDataList[[j]][length(seqDataList[[j]])] %% (resolution/2))
-  rows = seqDataList[[j]][seqDataList[[j]] %in% seq(start, end, resolution)]
-
-  #data_mat_list[[j]] <- matrix(nrow=length(rows),
-  #                             ncol=length(genomicElements.GR))
-  #rownames(data_mat_list[[j]]) <- rows
-
-  outcome_list[[j]] <- countOverlaps(GRanges(seqnames = tolower(CHR[j]),
-                                             IRanges(#start = as.numeric(rownames(data_mat_list[[j]])),
-                                               start = rows,
-                                               width = resolution)), bounds.GR.flank)
-  outcome_list[[j]] <- ifelse(outcome_list[[j]],1,0)
-  outcome_list[[j]] <- factor(outcome_list[[j]])
-  levels(outcome_list[[j]]) <- c("No", "Yes")
-
-  #full_list[[j]] <- cbind.data.frame(outcome_list[[j]], data_mat_list[[j]])
-  #names(full_list[[j]])[1] <- "y"
-}
-ci <- unlist(outcome_list)
-numbins <- length(ci)
-imbalance <- as.numeric(round(table(ci)[2]/sum(table(ci)),2))
-#}
-
-data.frame(resolution = c("10 kb"),
-           numtads=numtads,
-           numbounds=numbounds,
-           numbins=numbins,
-           imbalance=imbalance)
-
-```

### 2020-07-31 Scripts_for_results/03_creating_annotation_specifc_barplots.Rmd
updated results

@@
 
-## LOLLIPOP
-
-### GM12878 (rus; distance types)
-
-#### 10kb
-
-```{r}
-badata_gm12878_10kb <- numeric()
-for(i in paste0("CHR", c(1:8,10:22))){
- for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
-   print(c(i,j))
-  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
-    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
-                               i,
-                               "/rus/distance/TADRF_lollipop_",
-                               j, 
-                               ".rds"))
-    perfdata <- perfdata[[3]]
-  }else{
-    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
-                               i,
-                               "/rus/distance/TADRF_lollipop.rds"))
-    perfdata <- perfdata[[3]]
-  }
-
-  badata_gm12878_10kb <- rbind(badata_gm12878_10kb,
-                               perfdata[10,2])
-
- }
-}
-
-```
-
-#### Plotting
-
-```{r}
-all_rfperfs <- data.frame(Perf=badata_gm12878_10kb)
-all_rfperfs$Resolution <- rep("10 kb", length(badata_gm12878_10kb))
-all_rfperfs$Annotation <- c("BroadHMM","HM","TFBS","ALL")
-all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "BroadHMM", "TFBS", "ALL"))
-all_rfperfs$Chromosome <- c(rep("CHR1", 4),
-                            rep("CHR2", 4),
-                            rep("CHR3", 4),
-                            rep("CHR4", 4),
-                            rep("CHR5", 4),
-                            rep("CHR6", 4),
-                            rep("CHR7", 4),
-                            rep("CHR8", 4),
-                            rep("CHR10", 4),
-                            rep("CHR11", 4),
-                            rep("CHR12", 4),
-                            rep("CHR13", 4),
-                            rep("CHR14", 4),
-                            rep("CHR15", 4),
-                            rep("CHR16", 4),
-                            rep("CHR17", 4),
-                            rep("CHR18", 4),
-                            rep("CHR19", 4),
-                            rep("CHR20", 4),
-                            rep("CHR21", 4),
-                            rep("CHR22", 4))
-
-all_rfperfs <- all_rfperfs %>% 
-  group_by(Resolution, Annotation) %>% 
-  dplyr::summarise(Performance = mean(Perf, na.rm = TRUE),
-                   PerformanceSD = sd(Perf, na.rm = TRUE))
-
-ggplot(all_rfperfs, aes(x=Annotation, y=Performance, fill=Annotation)) +
-    geom_bar(stat="identity") +
-    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=.75) +
-    theme_minimal() +
-    theme_bw()+
-    xlab("Resolution") + 
-    ylab("Balanced Accuracy") + 
-    scale_fill_discrete(name="Genomic Class")+
-    theme(axis.text.x = element_text(size=15,
-                                     angle = 45, 
-                                     #margin = ggplot2::margin(t = 35),
-                                     hjust = 1
-    ),
-    axis.text.y = element_text(size = 15),
-    axis.title.x = element_text(size = 20),
-    axis.title.y = element_text(size = 20),
-    legend.text=element_text(size=15),
-    legend.title=element_text(size=20),
-    legend.position = "bottom",
-    plot.title = element_text(size=20))
-```
-
-### K562 (rus; distance types)
-
-#### 10kb
-
-```{r}
-badata_k562_10kb <- numeric()
-for(i in paste0("CHR", c(1:8,10:22))){
- for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
-   print(c(i,j))
-  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
-    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
-                               i,
-                               "/rus/distance/TADRF_lollipop_",
-                               j, 
-                               ".rds"))
-    perfdata <- perfdata[[3]]
-  }else{
-    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
-                               i,
-                               "/rus/distance/TADRF_lollipop.rds"))
-    perfdata <- perfdata[[3]]
-  }
-
-  badata_k562_10kb <- rbind(badata_k562_10kb,
-                               perfdata[10,2])
-
- }
-}
-
-```
-
-#### Plotting
-
-```{r}
-all_rfperfs <- data.frame(Perf=badata_k562_10kb)
-all_rfperfs$Resolution <- rep("10 kb", length(badata_k562_10kb))
-all_rfperfs$Annotation <- c("BroadHMM","HM","TFBS","ALL")
-all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "BroadHMM", "TFBS", "ALL"))
-all_rfperfs$Chromosome <- c(rep("CHR1", 4),
-                            rep("CHR2", 4),
-                            rep("CHR3", 4),
-                            rep("CHR4", 4),
-                            rep("CHR5", 4),
-                            rep("CHR6", 4),
-                            rep("CHR7", 4),
-                            rep("CHR8", 4),
-                            rep("CHR10", 4),
-                            rep("CHR11", 4),
-                            rep("CHR12", 4),
-                            rep("CHR13", 4),
-                            rep("CHR14", 4),
-                            rep("CHR15", 4),
-                            rep("CHR16", 4),
-                            rep("CHR17", 4),
-                            rep("CHR18", 4),
-                            rep("CHR19", 4),
-                            rep("CHR20", 4),
-                            rep("CHR21", 4),
-                            rep("CHR22", 4))
-
-all_rfperfs <- all_rfperfs %>% 
-  group_by(Resolution, Annotation) %>% 
-  dplyr::summarise(Performance = mean(Perf, na.rm = TRUE),
-                   PerformanceSD = sd(Perf, na.rm = TRUE))
-
-ggplot(all_rfperfs, aes(x=Annotation, y=Performance, fill=Annotation)) +
-    geom_bar(stat="identity") +
-    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=.75) +
-    theme_minimal() +
-    theme_bw()+
-    xlab("Resolution") + 
-    ylab("Balanced Accuracy") + 
-    scale_fill_discrete(name="Genomic Class")+
-    theme(axis.text.x = element_text(size=15,
-                                     angle = 45, 
-                                     #margin = ggplot2::margin(t = 35),
-                                     hjust = 1
-    ),
-    axis.text.y = element_text(size = 15),
-    axis.title.x = element_text(size = 20),
-    axis.title.y = element_text(size = 20),
-    legend.text=element_text(size=15),
-    legend.title=element_text(size=20),
-    legend.position = "bottom",
-    plot.title = element_text(size=20))
-```
-
 ## SpectralTAD

### 2020-07-31 Scripts_for_results/04_creating_rfe_lineplot.Rmd
updated results

@@
 
-## LOLLIPOP
-
-### GM12878
-
-#### Optimal parameters: 10 kb, TFBS, distance type predictors, RUS
-
-```{r}
-chrs <- paste0("CHR",c(1:8,10:22))
-rfeperchr <- data.frame()
-for(i in c("GM12878")){
-  for(k in 1:length(chrs)){print(c(i,k));
-    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
-                                          i,
-                                          "/",
-                                          "10kb/results_by_chr/",
-                                          chrs[k],
-                                          "/rus/distance/TADrfe_lollipop.rds"))
-    rfeModelResults <- rfeModelResultsList[[1]]
-    rfeModelResults <- rfeModelResults[,c(1,11)]
-    rfeModelResults$CL <- i
-    rfeModelResults$Chromosome <- chrs[k]
-    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
-  }
-}
-
-rfeperchr_summ <- rfeperchr %>%
-  dplyr::group_by(Variables) %>%
-  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
-                   PerformanceSD = sd(Accuracy, na.rm = TRUE))
-
-ggplot(rfeperchr_summ, aes(x=Variables, y=Performance)) + 
-  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), 
-                width=2, 
-                size=1, 
-                color="red") +
-  geom_line(size=2, color="red") +
-  geom_point(size=4, color="red") +
-  xlab("Number of top ranked annotations") +
-  ylab("Cross-Validated Accuracy") +
-  scale_color_discrete(name="Cell line")+
-  scale_x_continuous(breaks = c(2,4,8,16,32,52),
-                     labels = c(2,4,8,16,32,52))+
-  theme_minimal() +
-  theme_bw()+
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        #strip.text.x = element_text(size = 15),
-        #panel.spacing = unit(2, "lines"),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20),
-        plot.title = element_text(size=20),
-        legend.position = "bottom")
-```
-
-### K562
-
-#### Optimal parameters: 10 kb, TFBS, distance type predictors, RUS
-
-```{r}
-chrs <- paste0("CHR",c(1:8,10:22))
-rfeperchr <- data.frame()
-for(i in c("K562")){
-  for(k in 1:length(chrs)){print(c(i,k));
-    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
-                                          i,
-                                          "/",
-                                          "10kb/results_by_chr/",
-                                          chrs[k],
-                                          "/rus/distance/TADrfe_lollipop.rds"))
-    rfeModelResults <- rfeModelResultsList[[1]]
-    rfeModelResults <- rfeModelResults[,c(1,11)]
-    rfeModelResults$CL <- i
-    rfeModelResults$Chromosome <- chrs[k]
-    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
-  }
-}
-
-rfeperchr_summ <- rfeperchr %>%
-  dplyr::group_by(Variables) %>%
-  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
-                   PerformanceSD = sd(Accuracy, na.rm = TRUE))
-
-ggplot(rfeperchr_summ, aes(x=Variables, y=Performance)) + 
-  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), 
-                width=2, 
-                size=1, 
-                color="blue") +
-  geom_line(size=2, color="blue") +
-  geom_point(size=4, color="blue") +
-  xlab("Number of top ranked annotations") +
-  ylab("Cross-Validated Accuracy") +
-  scale_color_discrete(name="Cell line")+
-  scale_x_continuous(breaks = c(2,4,8,16,32,52),
-                     labels = c(2,4,8,16,32,52))+
-  theme_minimal() +
-  theme_bw()+
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        #strip.text.x = element_text(size = 15),
-        #panel.spacing = unit(2, "lines"),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20),
-        plot.title = element_text(size=20),
-        legend.position = "bottom")
-```
-
 ## SpectralTAD
@@
 ```
+
+# Plotting
+
+```{r}
+rfeperchr_summ_arrowhead <- rfeperchr_summ
+rfeperchr_summ_peakachu <- rfeperchr_summ
+
+rfeperchr_summ_gm12878 <- rbind.data.frame(rfeperchr_summ_arrowhead,rfeperchr_summ_peakachu)
+rfeperchr_summ_gm12878$Tool <- c(rep("ARROWHEAD", nrow(rfeperchr_summ_arrowhead)),
+                                 rep("PEAKACHU", nrow(rfeperchr_summ_peakachu)))
+
+ggplot(rfeperchr_summ_gm12878, aes(x=Variables, y=Performance, color=Tool)) + 
+  geom_line(size=2,) +
+  geom_point(size=4, position = position_dodge(.9)) +
+  geom_errorbar(aes(ymin=Performance-(PerformanceSD+.01), ymax=Performance+(PerformanceSD+.01)), 
+                width=4, 
+                size=1,
+                position = position_dodge(.9)) +
+  xlab("Number of top ranked annotations") +
+  ylab("Cross-Validated BA") +
+  scale_color_manual(name="Boundary Type", 
+                       values=c("blue", "red"))+
+  scale_x_continuous(breaks = c(2,4,8,16,32,52),
+                     labels = c(2,4,8,16,32,52))+
+  theme_minimal() +
+  theme_bw()+
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        #strip.text.x = element_text(size = 15),
+        #panel.spacing = unit(2, "lines"),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        plot.title = element_text(size=20),
+        legend.position = "right")
+```

### 2020-07-31 Scripts_for_results/06_creating_enriched_heatmaps.Rmd
updated results

@@
                         row_title_gp = gpar(fontsize = 10),
-                        axis_name_gp = gpar(fontsize = 10),
-                        top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = ifelse(ct=="ARROWHEAD", "blue", "red"), 
+                        axis_name_gp = gpar(fontsize = 10),height=unit(2, "in"),
+                        width=unit(2, "in")
+                        top_annotation = HeatmapAnnotation(height=unit(2, "in"),
+                                                           width=unit(2, "in"),
+                                                           lines = anno_enriched(gp = gpar(col = ifelse(ct=="ARROWHEAD", "blue", "red"), 
                                                                                            fontsize = 10,
@@
 chrs <- paste0("CHR", c(1:8,10:22))
-chrs <- paste0("CHR", c(21:22))
 for(i in 1:length(chrs)){

### 2020-07-31 Scripts_for_results/07_creating_distance_to_chipseq.Rmd
updated results

@@
 
-pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("preciseTAD", "ARROWHEAD"))
+pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("ARROWHEAD", "preciseTAD"))
 
@@
 true_bound_list <- GRangesList()
-chrs <- paste0("CHR", c(2:8,10:22))
+chrs <- paste0("CHR", c(1:8,10:22))
 for(i in 1:length(chrs)){
@@
 
-pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("preciseTAD", "PEAKACHU"))
+pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("PEAKACHU", "preciseTAD"))
 
@@
 true_bound_list <- GRangesList()
-chrs <- paste0("CHR", c(1:8,10:22))
+chrs <- paste0("CHR", c(2:8,10,11,13:22))
 for(i in 1:length(chrs)){

### 2020-07-31 Scripts_for_results/08_creating_venn_diagrams.Rmd
updated results

--- 2020-05-15 Scripts_for_results/08_creating_venn_diagrams.Rmd
@@
 
-#### Across cell line
+### Across cell line
 
@@
 gp[["FaceText"]][["01"]]$cex <- 2
-gp[["SetText"]][["Set1"]]$cex <- 2
-gp[["SetText"]][["Set2"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- .1
+gp[["SetText"]][["Set2"]]$cex <- .1
 
 gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+
+genomicCorr.jaccard(all_pred_bounds_gm12878,all_pred_bounds_k562)
 
@@
 gp[["FaceText"]][["01"]]$cex <- 2
-gp[["SetText"]][["Set1"]]$cex <- 2
-gp[["SetText"]][["Set2"]]$cex <- 2
+gp[["SetText"]][["Set1"]]$cex <- .1
+gp[["SetText"]][["Set2"]]$cex <- .1
 
@@
 
+genomicCorr.jaccard(all_true_bounds_gm12878,all_true_bounds_k562)
 ```
@@
 
-## LOLLIPOP
-
-### GM12878
-
-#### Extracting called and predicted boundaries
-
-```{r}
-pred_bound_list <- GRangesList()
-true_bound_list <- GRangesList()
-chrs <- paste0("CHR", c(1:8,10:22))
-chrs <- paste0("CHR", c(2:8,10:15,17:22))
-for(i in 1:length(chrs)){
-  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
-                                    chrs[i],
-                                    "/rus/distance/preciseTAD_lollipop.rds"))
-
-  true_bound_list[[i]] <- called_and_pred[[3]]
-  pred_bound_list[[i]] <- called_and_pred[[2]]
-
-}
-
-all_true_bounds_gm12878 <- do.call("c", true_bound_list)
-all_pred_bounds_gm12878 <- do.call("c", pred_bound_list)
-
-all_true_bounds_gm12878 <- flank(all_true_bounds_gm12878, 5000, both=TRUE)
-all_pred_bounds_gm12878 <- flank(all_pred_bounds_gm12878, 5000, both=TRUE)
-
-```
-
-### K562
-
-#### Extracting called and predicted boundaries
-
-```{r}
-pred_bound_list <- GRangesList()
-true_bound_list <- GRangesList()
-chrs <- paste0("CHR", c(1:8,10:22))
-chrs <- paste0("CHR", c(2:8,10:15,17:22))
-for(i in 1:length(chrs)){
-  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
-                                    chrs[i],
-                                    "/rus/distance/preciseTAD_lollipop.rds"))
-
-  true_bound_list[[i]] <- called_and_pred[[3]]
-  pred_bound_list[[i]] <- called_and_pred[[2]]
-
-}
-
-all_true_bounds_k562 <- do.call("c", true_bound_list)
-all_pred_bounds_k562 <- do.call("c", pred_bound_list)
-
-all_true_bounds_k562 <- flank(all_true_bounds_k562, 5000, both=TRUE)
-all_pred_bounds_k562 <- flank(all_pred_bounds_k562, 5000, both=TRUE)
-
-```
-
-### Within cell line (preciseTAD vs LOLLIPOP)
+### Nesting between pt(arrowhead) and pt(peakachu)
 
@@
 
-res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
-                                  all_true_bounds_gm12878),
-                       NameOfPeaks=c("preciseTAD", "LOLLIPOP"))
+res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878_a,
+                                  all_pred_bounds_gm12878_p),
+                       NameOfPeaks=c("preciseTAD", "PEAKACHU"))
 
@@
 gp[["Face"]][["11"]]$fill <-  "purple"
-gp[["Face"]][["01"]]$fill <-  "lightblue"
-gp[["Face"]][["10"]]$fill <-  "red"
+gp[["Face"]][["01"]]$fill <-  "red"
+gp[["Face"]][["10"]]$fill <-  "lightblue"
 gp[["FaceText"]][["10"]]$cex <- 2
@@
 
-res <- makeVennDiagram(Peaks=list(all_pred_bounds_k562,
-                                  all_true_bounds_k562),
-                       NameOfPeaks=c("preciseTAD", "LOLLIPOP"))
+res <- makeVennDiagram(Peaks=list(all_pred_bounds_k562_a,
+                                  all_pred_bounds_k562_p),
+                       NameOfPeaks=c("preciseTAD", "PEAKACHU"))
 
@@
 
-#### Across cell line
+# Jaccard Indices
 
 ```{r}
-###### preciseTAD
+genomicCorr.jaccard = function(query, reference, restrict = NULL) {
+  if(is.null(restrict)) {
+    res = sum(width(GenomicRanges::intersect(query, reference))) / sum(as.numeric(width(GenomicRanges::union(query, reference))))
+  } else {
+    gr1 = GenomicRanges::intersect(query, reference)
+    gr1 = GenomicRanges::intersect(gr1, restrict)
 
-res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
-                                  all_pred_bounds_k562),
-                       NameOfPeaks=c("GM12878", "K562"))
+    gr2 = GenomicRanges::union(query, reference)
+    gr2 = GenomicRanges::intersect(gr2, restrict)
+    res = sum(width(gr1)) / sum(width(gr2))
+  }
+  return(res)
+}
 
-venn.pt <- venn_cnt2venn(res$vennCounts)
-venn.pt <- compute.Venn(venn.pt)
-gp <- VennThemes(venn.pt)
-gp[["Face"]][["11"]]$fill <-  "purple"
-gp[["Face"]][["01"]]$fill <-  "lightblue"
-gp[["Face"]][["10"]]$fill <-  "red"
-gp[["FaceText"]][["10"]]$cex <- 2
-gp[["FaceText"]][["11"]]$cex <- 2
-gp[["FaceText"]][["01"]]$cex <- 2
-gp[["SetText"]][["Set1"]]$cex <- 2
-gp[["SetText"]][["Set2"]]$cex <- 2
+chrs <- paste0("CHR", c(1:8,10:22))
+ji_pred <- numeric()
+ji_true <- numeric()
+for(i in 1:length(chrs)){
+  called_and_pred_gm12878 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+                                    chrs[i],
+                                    "/rus/distance/preciseTAD_holdout.rds"))
 
-gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+  called_and_pred_k562 <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+                                            chrs[i],
+                                            "/rus/distance/preciseTAD_holdout.rds"))
 
-###### LOLLIPOP
+  called_and_pred_gm12878[[2]] <- flank(called_and_pred_gm12878[[2]], 5000, both=TRUE)
+  called_and_pred_gm12878[[3]] <- flank(called_and_pred_gm12878[[3]], 5000, both=TRUE)
+  called_and_pred_k562[[2]] <- flank(called_and_pred_k562[[2]], 5000, both=TRUE)
+  called_and_pred_k562[[3]] <- flank(called_and_pred_k562[[3]], 5000, both=TRUE)
 
-res <- makeVennDiagram(Peaks=list(all_true_bounds_gm12878,
-                                  all_true_bounds_k562),
-                       NameOfPeaks=c("GM12878", "K562"))
+  ji_pred[i] <- genomicCorr.jaccard(called_and_pred_gm12878[[2]],called_and_pred_k562[[2]])
+  ji_true[i] <- genomicCorr.jaccard(called_and_pred_gm12878[[3]],called_and_pred_k562[[3]])
+}
 
-venn.pt <- venn_cnt2venn(res$vennCounts)
-venn.pt <- compute.Venn(venn.pt)
-gp <- VennThemes(venn.pt)
-gp[["Face"]][["11"]]$fill <-  "purple"
-gp[["Face"]][["01"]]$fill <-  "lightblue"
-gp[["Face"]][["10"]]$fill <-  "red"
-gp[["FaceText"]][["10"]]$cex <- 2
-gp[["FaceText"]][["11"]]$cex <- 2
-gp[["FaceText"]][["01"]]$cex <- 2
-gp[["SetText"]][["Set1"]]$cex <- 2
-gp[["SetText"]][["Set2"]]$cex <- 2
+summary(ji_pred)
+summary(ji_true)
+wilcox.test(ji_pred,ji_true)
 
-gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
+##############################################################################################
+
+chrs <- paste0("CHR", c(1:8,10:22))
+ji_pred <- numeric()
+ji_true <- numeric()
+for(i in 1:length(chrs)){
+  called_and_pred_gm12878 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+                                            chrs[i],
+                                            "/rus/distance/preciseTAD_holdout_peakachu.rds"))
+
+  called_and_pred_k562 <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+                                         chrs[i],
+                                         "/rus/distance/preciseTAD_holdout_peakachu.rds"))
+
+  called_and_pred_gm12878[[2]] <- flank(called_and_pred_gm12878[[2]], 10000, both=TRUE)
+  called_and_pred_gm12878[[3]] <- flank(called_and_pred_gm12878[[3]], 10000, both=TRUE)
+  called_and_pred_k562[[2]] <- flank(called_and_pred_k562[[2]], 10000, both=TRUE)
+  called_and_pred_k562[[3]] <- flank(called_and_pred_k562[[3]], 10000, both=TRUE)
+
+  ji_pred[i] <- genomicCorr.jaccard(called_and_pred_gm12878[[2]],called_and_pred_k562[[2]])
+  ji_true[i] <- genomicCorr.jaccard(called_and_pred_gm12878[[3]],called_and_pred_k562[[3]])
+}
+
+summary(ji_pred)
+summary(ji_true)
+wilcox.test(ji_pred,ji_true)
 

### 2020-07-31 Scripts_for_results/11_correlations_across_resolutions.Rmd
updated results

@@
 library(ggcorrplot)
+library(circlize)
 
@@
 ```{r}
-gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
-gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
-gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
-gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
-gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
+gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")
+gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")
+gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")
+gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")
+gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")
 

### 2020-07-31 Scripts_for_results/12_cross_cell_line_performances.Rmd
initial commit

---
title: "Cross cell line performance"
author: "Spiro Stilianoudakis"
date: "7/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading packages and functions

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)
library(ComplexHeatmap)
library(circlize)
library(cotools)
library(ggcorrplot)
library(circlize)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/createTADdata.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

# ARROWHEAD

```{r}
arrowhead_g_on_g <- list()
arrowhead_g_on_g_auc <- numeric()
arrowhead_g_on_k <- list()
arrowhead_g_on_k_auc <- numeric()
arrowhead_k_on_k <- list()
arrowhead_k_on_k_auc <- numeric()
arrowhead_k_on_g <- list()
arrowhead_k_on_g_auc <- numeric()

peakachu_g_on_g <- list()
peakachu_g_on_g_auc <- numeric()
peakachu_g_on_k <- list()
peakachu_g_on_k_auc <- numeric()
peakachu_k_on_k <- list()
peakachu_k_on_k_auc <- numeric()
peakachu_k_on_g <- list()
peakachu_k_on_g_auc <- numeric()

genomicElements.GR_gm12878 <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS_nonames",
                                             pattern="*.bed",
                                             signal=4)
genomicElements.GR_k562 <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS_nonames",
                                             pattern="*.bed",
                                             signal=4)

domains_arrowhead_gm12878 <- read.table("Z:/TAD_data_analysis/GSE63525_data/arrowhead_output/GM12878/GM12878_domain_data_5000.b.txt", header=F)
bounds.GR_arrowhead_gm12878 <- extract_boundaries_func(domains.mat=domains_arrowhead_gm12878, 
                                     preprocess=FALSE, 
                                     CHR=paste0("CHR", c(1:8,10:22)), 
                                     resolution=5000)
domains_arrowhead_k562 <- read.table("Z:/TAD_data_analysis/GSE63525_data/arrowhead_output/K562/K562_domain_data_5000.b.txt", header=F)
bounds.GR_arrowhead_k562 <- extract_boundaries_func(domains.mat=domains_arrowhead_k562, 
                                     preprocess=FALSE, 
                                     CHR=paste0("CHR", c(1:8,10:22)), 
                                     resolution=5000)

domains_peakachu_gm12878 <- readRDS("Z:/TAD_data_analysis/peakachu/peakachu_GM12878.rds")
bounds.GR_peakachu_gm12878 <- extract_boundaries_func(domains.mat=domains_peakachu_gm12878, 
                                     preprocess=FALSE, 
                                     CHR=paste0("CHR", c(1:8,10:22)), 
                                     resolution=5000)
domains_peakachu_k562 <- readRDS("Z:/TAD_data_analysis/peakachu/peakachu_K562.rds")
bounds.GR_peakachu_k562 <- extract_boundaries_func(domains.mat=domains_peakachu_k562, 
                                     preprocess=FALSE, 
                                     CHR=paste0("CHR", c(1:8,10:22)), 
                                     resolution=5000)

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  print(chrs[i])

  #ARROWHEAD

  TADRF_arrowhead_g_on_g <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                           chrs[i],
                                           "/rus/distance/TADRF_holdout_gm12878_on_gm12878.rds"))

  arrowhead_g_on_g_auc[i] <- TADRF_arrowhead_g_on_g[[3]][18,2]

  TADRF_arrowhead_g_on_k <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                           chrs[i],
                                           "/rus/distance/TADRF_holdout_gm12878_on_k562.rds"))

  arrowhead_g_on_k_auc[i] <- TADRF_arrowhead_g_on_k[[3]][18,2]

  TADRF_arrowhead_k_on_k <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/5kb/results_by_chr/",
                                           chrs[i],
                                           "/rus/distance/TADRF_holdout_k562_on_k562.rds"))

  arrowhead_k_on_k_auc[i] <- TADRF_arrowhead_k_on_k[[3]][18,2]

  TADRF_arrowhead_k_on_g <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/5kb/results_by_chr/",
                                           chrs[i],
                                           "/rus/distance/TADRF_holdout_k562_on_gm12878.rds"))

  arrowhead_k_on_g_auc[i] <- TADRF_arrowhead_k_on_g[[3]][18,2]

  tadData_arrowhead_gm12878 <- createTADdata(bounds.GR=bounds.GR_arrowhead_gm12878,
                         resolution=5000,
                         genomicElements.GR=genomicElements.GR_gm12878,
                         featureType="distance",
                         resampling="rus",
                         trainCHR=paste0("CHR",c(1:8,10:22))[-which(paste0("CHR",c(1:8,10:22))==chrs[i])],
                         predictCHR=chrs[i],
                         seed=123)
  tadData_arrowhead_k562 <- createTADdata(bounds.GR=bounds.GR_arrowhead_k562,
                         resolution=5000,
                         genomicElements.GR=genomicElements.GR_k562,
                         featureType="distance",
                         resampling="rus",
                         trainCHR=paste0("CHR",c(1:8,10:22))[-which(paste0("CHR",c(1:8,10:22))==chrs[i])],
                         predictCHR=chrs[i],
                         seed=123)

  pred <- as.vector(predict(TADRF_arrowhead_g_on_g[[1]], 
                                       newdata=tadData_arrowhead_gm12878[[2]][,-1], 
                                       type="prob")[,"Yes"])
  ROC <- pROC::roc(tadData_arrowhead_gm12878[[2]]$y, pred, quiet = TRUE)
  arrowhead_g_on_g[[i]] <- data.frame(specificity=ROC$specificities,sensitivity=ROC$sensitivities,chr=chrs[i])

  pred <- as.vector(predict(TADRF_arrowhead_g_on_k[[1]], 
                                       newdata=tadData_arrowhead_k562[[2]][,-1], 
                                       type="prob")[,"Yes"])
  ROC <- pROC::roc(tadData_arrowhead_k562[[2]]$y, pred, quiet = TRUE)
  arrowhead_g_on_k[[i]] <- data.frame(specificity=ROC$specificities,sensitivity=ROC$sensitivities,chr=chrs[i])

  pred <- as.vector(predict(TADRF_arrowhead_k_on_k[[1]], 
                                       newdata=tadData_arrowhead_k562[[2]][,-1], 
                                       type="prob")[,"Yes"])
  ROC <- pROC::roc(tadData_arrowhead_k562[[2]]$y, pred, quiet = TRUE)
  arrowhead_k_on_k[[i]] <- data.frame(specificity=ROC$specificities,sensitivity=ROC$sensitivities,chr=chrs[i])

  pred <- as.vector(predict(TADRF_arrowhead_k_on_g[[1]], 
                                       newdata=tadData_arrowhead_gm12878[[2]][,-1], 
                                       type="prob")[,"Yes"])
  ROC <- pROC::roc(tadData_arrowhead_gm12878[[2]]$y, pred, quiet = TRUE)
  arrowhead_k_on_g[[i]] <- data.frame(specificity=ROC$specificities,sensitivity=ROC$sensitivities,chr=chrs[i])

  #########################################################################################################

  #PEAKACHU

  TADRF_peakachu_g_on_g <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                           chrs[i],
                                           "/rus/distance/TADRF_holdout_gm12878_on_gm12878_peakachu.rds"))

  peakachu_g_on_g_auc[i] <- TADRF_peakachu_g_on_g[[3]][18,2]

  TADRF_peakachu_g_on_k <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                           chrs[i],
                                           "/rus/distance/TADRF_holdout_gm12878_on_k562_peakachu.rds"))

  peakachu_g_on_k_auc[i] <- TADRF_peakachu_g_on_k[[3]][18,2]

  TADRF_peakachu_k_on_k <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/10kb/results_by_chr/",
                                           chrs[i],
                                           "/rus/distance/TADRF_holdout_k562_on_k562_peakachu.rds"))

  peakachu_k_on_k_auc[i] <- TADRF_peakachu_k_on_k[[3]][18,2]

  TADRF_peakachu_k_on_g <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/10kb/results_by_chr/",
                                           chrs[i],
                                           "/rus/distance/TADRF_holdout_k562_on_gm12878_peakachu.rds"))

  peakachu_k_on_g_auc[i] <- TADRF_peakachu_k_on_g[[3]][18,2]

  tadData_peakachu_gm12878 <- createTADdata(bounds.GR=bounds.GR_peakachu_gm12878,
                         resolution=5000,
                         genomicElements.GR=genomicElements.GR_gm12878,
                         featureType="distance",
                         resampling="rus",
                         trainCHR=paste0("CHR",c(1:8,10:22))[-which(paste0("CHR",c(1:8,10:22))==chrs[i])],
                         predictCHR=chrs[i],
                         seed=123)
  tadData_peakachu_k562 <- createTADdata(bounds.GR=bounds.GR_peakachu_k562,
                         resolution=5000,
                         genomicElements.GR=genomicElements.GR_k562,
                         featureType="distance",
                         resampling="rus",
                         trainCHR=paste0("CHR",c(1:8,10:22))[-which(paste0("CHR",c(1:8,10:22))==chrs[i])],
                         predictCHR=chrs[i],
                         seed=123)

  pred <- as.vector(predict(TADRF_peakachu_g_on_g[[1]], 
                                       newdata=tadData_peakachu_gm12878[[2]][,-1], 
                                       type="prob")[,"Yes"])
  ROC <- pROC::roc(tadData_peakachu_gm12878[[2]]$y, pred, quiet = TRUE)
  peakachu_g_on_g[[i]] <- data.frame(specificity=ROC$specificities,sensitivity=ROC$sensitivities,chr=chrs[i])

  pred <- as.vector(predict(TADRF_peakachu_g_on_k[[1]], 
                                       newdata=tadData_peakachu_k562[[2]][,-1], 
                                       type="prob")[,"Yes"])
  ROC <- pROC::roc(tadData_peakachu_k562[[2]]$y, pred, quiet = TRUE)
  peakachu_g_on_k[[i]] <- data.frame(specificity=ROC$specificities,sensitivity=ROC$sensitivities,chr=chrs[i])

  pred <- as.vector(predict(TADRF_peakachu_k_on_k[[1]], 
                                       newdata=tadData_peakachu_k562[[2]][,-1], 
                                       type="prob")[,"Yes"])
  ROC <- pROC::roc(tadData_peakachu_k562[[2]]$y, pred, quiet = TRUE)
  peakachu_k_on_k[[i]] <- data.frame(specificity=ROC$specificities,sensitivity=ROC$sensitivities,chr=chrs[i])

  pred <- as.vector(predict(TADRF_peakachu_k_on_g[[1]], 
                                       newdata=tadData_peakachu_gm12878[[2]][,-1], 
                                       type="prob")[,"Yes"])
  ROC <- pROC::roc(tadData_peakachu_gm12878[[2]]$y, pred, quiet = TRUE)
  peakachu_k_on_g[[i]] <- data.frame(specificity=ROC$specificities,sensitivity=ROC$sensitivities,chr=chrs[i])

}

saveRDS(arrowhead_g_on_g, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/arrowhead_g_on_g.rds")
saveRDS(arrowhead_g_on_g_auc, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/arrowhead_g_on_g_auc.rds") 
saveRDS(arrowhead_g_on_k, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/arrowhead_g_on_k.rds")
saveRDS(arrowhead_g_on_k_auc, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/arrowhead_g_on_k_auc.rds")
saveRDS(arrowhead_k_on_k, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/arrowhead_k_on_k.rds")
saveRDS(arrowhead_k_on_k_auc, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/arrowhead_k_on_k_auc.rds")
saveRDS(arrowhead_k_on_g, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/arrowhead_k_on_g.rds")
saveRDS(arrowhead_k_on_g_auc, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/arrowhead_k_on_g_auc.rds")

saveRDS(peakachu_g_on_g, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/peakachu_g_on_g.rds")
saveRDS(peakachu_g_on_g_auc, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/peakachu_g_on_g_auc.rds") 
saveRDS(peakachu_g_on_k, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/peakachu_g_on_k.rds")
saveRDS(peakachu_g_on_k_auc, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/peakachu_g_on_k_auc.rds") 
saveRDS(peakachu_k_on_k, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/peakachu_k_on_k.rds")
saveRDS(peakachu_k_on_k_auc, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/peakachu_k_on_k_auc.rds") 
saveRDS(peakachu_k_on_g, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/peakachu_k_on_g.rds")
saveRDS(peakachu_k_on_g_auc, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/peakachu_k_on_g_auc.rds")

```

# Plotting

```{r}
arrowhead_g_on_g <- readRDS("Z:/TAD_data_analysis/miscellaneous/arrowhead_g_on_k.rds")
arrowhead_g_on_g_auc <- readRDS("Z:/TAD_data_analysis/miscellaneous/arrowhead_g_on_k_auc.rds") 
arrowhead_g_on_k <- readRDS("Z:/TAD_data_analysis/miscellaneous/arrowhead_g_on_g.rds")
arrowhead_g_on_k_auc <- readRDS("Z:/TAD_data_analysis/miscellaneous/arrowhead_g_on_g_auc.rds") 
arrowhead_k_on_g <- readRDS("Z:/TAD_data_analysis/miscellaneous/arrowhead_k_on_k.rds")
arrowhead_k_on_g_auc <- readRDS("Z:/TAD_data_analysis/miscellaneous/arrowhead_k_on_k_auc.rds") 
arrowhead_k_on_k <- readRDS("Z:/TAD_data_analysis/miscellaneous/arrowhead_k_on_g.rds")
arrowhead_k_on_k_auc <- readRDS("Z:/TAD_data_analysis/miscellaneous/arrowhead_k_on_g_auc.rds")

peakachu_g_on_g <- readRDS("Z:/TAD_data_analysis/miscellaneous/peakachu_g_on_g.rds")
peakachu_g_on_g_auc <- readRDS("Z:/TAD_data_analysis/miscellaneous/peakachu_g_on_g_auc.rds") 
peakachu_g_on_k <- readRDS("Z:/TAD_data_analysis/miscellaneous/peakachu_g_on_k.rds")
peakachu_g_on_k_auc <- readRDS("Z:/TAD_data_analysis/miscellaneous/peakachu_g_on_k_auc.rds") 
peakachu_k_on_k <- readRDS("Z:/TAD_data_analysis/miscellaneous/peakachu_k_on_k.rds")
peakachu_k_on_k_auc <- readRDS("Z:/TAD_data_analysis/miscellaneous/peakachu_k_on_k_auc.rds") 
peakachu_k_on_g <- readRDS("Z:/TAD_data_analysis/miscellaneous/peakachu_k_on_g.rds")
peakachu_k_on_g_auc <- readRDS("Z:/TAD_data_analysis/miscellaneous/peakachu_k_on_g_auc.rds")

arrowhead_g_on_k <- do.call("rbind.data.frame", arrowhead_g_on_k)

arrowhead_g_on_g[[12]] <- rbind.data.frame(arrowhead_g_on_g[[12]],
                                           data.frame(specificity=1,sensitivity=0,chr="CHR13"),
                                           data.frame(specificity=1,sensitivity=0,chr="CHR13"),
                                           data.frame(specificity=1,sensitivity=0,chr="CHR13"))
arrowhead_g_on_g[[13]] <- rbind.data.frame(arrowhead_g_on_g[[13]],
                                           data.frame(specificity=1,sensitivity=0,chr="CHR14"))
arrowhead_g_on_g[[20]] <- rbind.data.frame(arrowhead_g_on_g[[20]],
                                           data.frame(specificity=1,sensitivity=0,chr="CHR21"),
                                           data.frame(specificity=1,sensitivity=0,chr="CHR21"),
                                           data.frame(specificity=1,sensitivity=0,chr="CHR21"),
                                           data.frame(specificity=1,sensitivity=0,chr="CHR21"))
arrowhead_g_on_g <- do.call("rbind.data.frame", arrowhead_g_on_g)

arrowhead_k_on_k[[15]] <- rbind.data.frame(arrowhead_k_on_k[[15]],
                                           data.frame(specificity=1,sensitivity=0,chr="CHR16"))
arrowhead_k_on_k[[17]] <- rbind.data.frame(arrowhead_k_on_k[[17]],
                                           data.frame(specificity=1,sensitivity=0,chr="CHR18"),
                                           data.frame(specificity=1,sensitivity=0,chr="CHR18"))
arrowhead_k_on_k[[20]] <- rbind.data.frame(arrowhead_k_on_k[[20]],
                                           data.frame(specificity=1,sensitivity=0,chr="CHR21"),
                                           data.frame(specificity=1,sensitivity=0,chr="CHR21"))
arrowhead_k_on_k <- do.call("rbind.data.frame", arrowhead_k_on_k)

arrowhead_k_on_g[[12]] <- rbind.data.frame(arrowhead_k_on_g[[12]],
                                           data.frame(specificity=1,sensitivity=0,chr="CHR13"))
arrowhead_k_on_g <- do.call("rbind.data.frame", arrowhead_k_on_g)

peakachu_g_on_g[[20]] <- rbind.data.frame(peakachu_g_on_g[[20]],
                                           data.frame(specificity=1,sensitivity=0,chr="CHR21"))
peakachu_g_on_g <- do.call("rbind.data.frame", peakachu_g_on_g)

peakachu_g_on_k[[20]] <- rbind.data.frame(peakachu_g_on_k[[20]],
                                           data.frame(specificity=1,sensitivity=0,chr="CHR21"))
peakachu_g_on_k <- do.call("rbind.data.frame", peakachu_g_on_k)

peakachu_k_on_g[[20]] <- rbind.data.frame(peakachu_k_on_g[[20]],
                                          data.frame(specificity=1,sensitivity=0,chr="CHR21"),
                                          data.frame(specificity=1,sensitivity=0,chr="CHR21"))
peakachu_k_on_g <- do.call("rbind.data.frame", peakachu_k_on_g)

peakachu_k_on_k <- do.call("rbind.data.frame", peakachu_k_on_k)

# GM12878 
##arrowhead
data <- rbind.data.frame(arrowhead_g_on_g, arrowhead_g_on_k)
data$id <- rep(factor(rep(c(1:502),21)),2)
data$CL <- c(rep("GM12878 on GM12878", nrow(arrowhead_g_on_g)),
                 rep("GM12878 on K562", nrow(arrowhead_g_on_k)))

a1 <- reshape(data[which(data$CL=="GM12878 on GM12878"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "specificity")
a1 <- rowMeans(a1[,-c(1:3)])
b1 <- reshape(data[which(data$CL=="GM12878 on GM12878"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "sensitivity")
b1 <- rowMeans(b1[,-c(1:3)])
ave_sens_spec_gm12878_on_gm12878 <- data.frame(specificity=a1, sensitivity=b1)

a2 <- reshape(data[which(data$CL=="GM12878 on K562"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "specificity")
a2 <- rowMeans(a2[,-c(1:3)])
b2 <- reshape(data[which(data$CL=="GM12878 on K562"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "sensitivity")
b2 <- rowMeans(b2[,-c(1:3)])
ave_sens_spec_gm12878_on_k562 <- data.frame(specificity=a2, sensitivity=b2)

ave_sens_spec_arrow <- rbind.data.frame(ave_sens_spec_gm12878_on_gm12878,ave_sens_spec_gm12878_on_k562)
ave_sens_spec_arrow$Training_Testing <- c(rep("GM12878 on GM12878", nrow(ave_sens_spec_gm12878_on_gm12878)),
                                       rep("GM12878 on K562", nrow(ave_sens_spec_gm12878_on_k562)))
ave_sens_spec_arrow$Tool <- "ARROWHEAD"

##peakachu
data <- rbind.data.frame(peakachu_g_on_g, peakachu_g_on_k)
data$id <- rep(factor(rep(c(1:502),21)),2)
data$CL <- c(rep("GM12878 on GM12878", nrow(peakachu_g_on_g)),
                 rep("GM12878 on K562", nrow(peakachu_g_on_k)))

a1 <- reshape(data[which(data$CL=="GM12878 on GM12878"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "specificity")
a1 <- rowMeans(a1[,-c(1:3)])
b1 <- reshape(data[which(data$CL=="GM12878 on GM12878"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "sensitivity")
b1 <- rowMeans(b1[,-c(1:3)])
ave_sens_spec_gm12878_on_gm12878 <- data.frame(specificity=a1, sensitivity=b1)

a2 <- reshape(data[which(data$CL=="GM12878 on K562"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "specificity")
a2 <- rowMeans(a2[,-c(1:3)])
b2 <- reshape(data[which(data$CL=="GM12878 on K562"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "sensitivity")
b2 <- rowMeans(b2[,-c(1:3)])
ave_sens_spec_gm12878_on_k562 <- data.frame(specificity=a2, sensitivity=b2)

ave_sens_spec_peak <- rbind.data.frame(ave_sens_spec_gm12878_on_gm12878,ave_sens_spec_gm12878_on_k562)
ave_sens_spec_peak$Training_Testing <- c(rep("GM12878 on GM12878", nrow(ave_sens_spec_gm12878_on_gm12878)),
                                       rep("GM12878 on K562", nrow(ave_sens_spec_gm12878_on_k562)))
ave_sens_spec_peak$Tool <- "PEAKACHU"

all_ave_sens_spec_df <- rbind.data.frame(ave_sens_spec_arrow,ave_sens_spec_peak)

ggplot(all_ave_sens_spec_df, aes(x=1-specificity, y=sensitivity, linetype=Training_Testing, color=Tool)) +
  facet_grid(. ~ Tool) +
  geom_line(size=1) +
  geom_abline(slope = 1, intercept = 0) +
  xlab("1-Specificity") + 
  ylab("Sensitivity") + 
  scale_linetype_discrete(name="Training/Testing") +
  scale_color_manual(values = c("blue","red")) +
  guides(color=FALSE, linetype=guide_legend(nrow=2,byrow=TRUE)) +
  theme_minimal() +
  theme_bw()+
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

##################################################################################################################

# K562
##arrowhead
data <- rbind.data.frame(arrowhead_k_on_k, arrowhead_k_on_g)
data$id <- rep(factor(rep(c(1:502),21)),2)
data$CL <- c(rep("K562 on K562", nrow(arrowhead_k_on_k)),
                 rep("K562 on GM12878", nrow(arrowhead_k_on_g)))

a1 <- reshape(data[which(data$CL=="K562 on K562"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "specificity")
a1 <- rowMeans(a1[,-c(1:3)])
b1 <- reshape(data[which(data$CL=="K562 on K562"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "sensitivity")
b1 <- rowMeans(b1[,-c(1:3)])
ave_sens_spec_k562_on_k562 <- data.frame(specificity=a1, sensitivity=b1)

a2 <- reshape(data[which(data$CL=="K562 on GM12878"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "specificity")
a2 <- rowMeans(a2[,-c(1:3)])
b2 <- reshape(data[which(data$CL=="K562 on GM12878"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "sensitivity")
b2 <- rowMeans(b2[,-c(1:3)])
ave_sens_spec_k562_on_gm12878 <- data.frame(specificity=a2, sensitivity=b2)

ave_sens_spec_arrow <- rbind.data.frame(ave_sens_spec_k562_on_k562,ave_sens_spec_k562_on_gm12878)
ave_sens_spec_arrow$Training_Testing <- c(rep("K562 on K562", nrow(ave_sens_spec_k562_on_k562)),
                                       rep("K562 on GM12878", nrow(ave_sens_spec_k562_on_gm12878)))
ave_sens_spec_arrow$Tool <- "ARROWHEAD"

##peakachu
data <- rbind.data.frame(peakachu_k_on_k, peakachu_k_on_g)
data$id <- rep(factor(rep(c(1:502),21)),2)
data$CL <- c(rep("K562 on K562", nrow(peakachu_k_on_k)),
                 rep("K562 on GM12878", nrow(peakachu_k_on_g)))

a1 <- reshape(data[which(data$CL=="K562 on K562"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "specificity")
a1 <- rowMeans(a1[,-c(1:3)])
b1 <- reshape(data[which(data$CL=="K562 on K562"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "sensitivity")
b1 <- rowMeans(b1[,-c(1:3)])
ave_sens_spec_k562_on_k562 <- data.frame(specificity=a1, sensitivity=b1)

a2 <- reshape(data[which(data$CL=="K562 on GM12878"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "specificity")
a2 <- rowMeans(a2[,-c(1:3)])
b2 <- reshape(data[which(data$CL=="K562 on GM12878"),], 
             idvar = "id",
             timevar="chr",
             direction="wide",
             v.names = "sensitivity")
b2 <- rowMeans(b2[,-c(1:3)])
ave_sens_spec_k562_on_gm12878 <- data.frame(specificity=a2, sensitivity=b2)

ave_sens_spec_peak <- rbind.data.frame(ave_sens_spec_k562_on_k562,ave_sens_spec_k562_on_gm12878)
ave_sens_spec_peak$Training_Testing <- c(rep("K562 on K562", nrow(ave_sens_spec_k562_on_k562)),
                                       rep("K562 on GM12878", nrow(ave_sens_spec_k562_on_gm12878)))
ave_sens_spec_peak$Tool <- "PEAKACHU"

all_ave_sens_spec_df <- rbind.data.frame(ave_sens_spec_arrow,ave_sens_spec_peak)

ggplot(all_ave_sens_spec_df, aes(x=1-specificity, y=sensitivity, linetype=Training_Testing, color=Tool)) +
  facet_grid(. ~ Tool) +
  geom_line(size=1) +
  geom_abline(slope = 1, intercept = 0) +
  xlab("1-Specificity") + 
  ylab("Sensitivity") + 
  scale_linetype_discrete(name="Training/Testing") +
  scale_color_manual(values = c("blue","red")) +
  guides(color=FALSE, linetype=guide_legend(nrow=2,byrow=TRUE)) +
  theme_minimal() +
  theme_bw()+
  theme(axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 10),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=10),
        legend.title=element_text(size=15),
        plot.title = element_text(size=15),
        legend.position = "bottom")

```

### 2020-07-31 Manuscript/manuscript.Rmd
editted results

@@
 
+## Evaluating performance across cell lines
+
+When evaluating performance across cell lines, a random forest model was built using ground truth boundaries and genomic annotations from one cell line such that the data matrix was constructed using genomic bins from $n-1$ chromosomes.
+The test data used to evaluate performance was constructed from the binned data of the $i^{th}$ holdout chromosome with genomic annotations from the other cell line.
+Thus, the models were trained on cell line specific data and tested on the other cell line.
+This process was repeated for each holdout chromosome.
+To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivies and specificities when tested on the cell line specific holdout chromosome test data, and reported the area under the curve (AUC).
+
 ## Boundary prediction at bp resolution using *preciseTAD*
@@
 We chose the random forest (RF) machine learning algorithm as our binary classification tool.
-The reason for choosing RF was two-fold: (1) In order to devise a tunable prediction rule in a supervised learning framework that is both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors with respect to their ability to predict boundary regions [@boulesteix2012overview].
-We then developed *preciseTAD*, an algorithm which leverages an optimally built RF to precisely predict the genomic coordinates of both TAD and chromatin loop boundaries at base pair resolution.
+The reason being two-fold: (1) In order to devise a tunable prediction rule in a supervised learning framework that is both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors [@boulesteix2012overview].
+We extended our method and developed *preciseTAD*, an algorithm which leverages an optimally built RF to precisely predict the genomic coordinates of both TAD and chromatin loop boundaries at base pair resolution.
 
 Our framework is resolution-specific and uses called TAD or loop boundaries as ground truth to establish TAD(loop)-boundary and non-TAD(loop) boundary regions.
-To demonstrate, we applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines obtained from GEO GSE63525 (Supplementary Table 1) [???
-Update table and methods with relevant data only, not individual samples;!!!fixed].
+To demonstrate, we applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines obtained from GEO GSE63525 (Supplementary Table 1).
 TADs were subsequently called using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-For loop boundaries, we opted to use boundaries obtained by the Peakachu prediction tool for the GM12878 and K562 cell lines at 10 kb resolution [@salameh2019supervised].
+For loops, we opted to use boundaries obtained by the PEAKACHU prediction tool for the GM12878 and K562 cell lines at 10 kb resolution [@salameh2019supervised].
 [???
@@
 Boundary regions were defined as regions containing a called boundary ($Y = 1$), while non-boundary regions were defined as genomic bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
-The total number of TADs, TAD boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 2 [???
-I can see numbers for K562 (?) only?
-There's a discrepancy with legend.!!!fixed, need to added spectralTAD]).
+The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 2).
 The number of non-boundary regions highly outnumbered boundary regions, with results consistent for loop boundaries as well.
@@
 
-A total of 77 [???
-77 in the table?;!!!fixed] cell-line-specific functional genomic annotations were used to build the predictor space.
+A total of 77 cell-line-specific functional genomic annotations were used to build the predictor space.
 These included BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 3).
@@
 
-In summary, we considered combinations of data from two cell line *L = {GM12878, K562}*, five resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor space *P = {Signal, OC, OP, Distance}*, and three re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
+We considered combinations of data from two cell line *L = {GM12878, K562}*, five resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor space *P = {Signal, OC, OP, Distance}*, and three re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
 Once the model inputs were established, a random forest classifier was trained on $n-1$ autosomal chromosomes, while reserving the $i^{th}$ chromosome for testing.
@@
 Finally, step 5 is to validate the model on the separate test data composed of the binned data from the holdout chromosome *i* and to evaluate model performance using balanced accuracy (BA).](Figures/figure2.png)
-
-<!-- Using ARROWHEAD, we obtained a total of 8052, 7676, 4670, 2349, and 1031 called TADs  across each resolution respectively (Table 1).
-From the called TADs, a total of 15468, 14253, 8363, 4224, and 1883 unique TAD boundaries were obtained (Table 1).
-The resolution-specific approach we developed to create boundary vs non-boundary regions resulted in a total of 535363, 267682, 107073, 53537, and 26768 genomic bins.
-The class imbalance among the genomic bins was both severe and invariant toward resolution, resulting in 0.03, 0.05, 0.08, 0.08, and 0.07 for each resolution respectively (Table 1).
-Boundary data summaries were similar for K562 cell line, as well as for Peakachu defined boundaries (Supplementary Tables 3-4).
--->
 
@@
 However, RUS and SMOTE re-sampling led to drastic improvement in performance, especially at higher resolutions.
-We found that RUS marginally outperformed SMOTE as the most optimal class balancing technique for all resolutions and predictor types.
-These results suggest that simple random under-sampling can significantly improve TAD boundary region prediction.
+We found that RUS marginally outperformed SMOTE as the most optimal class balancing technique for all resolutions and predictor types when predicting TAD boundary regions.
 
 Additionally, we found that using a distance-type predictor space yielded substantially higher balanced accuracies when compared to the peak signal stength, overlap count, and overlap percent predictor types.
-As with class balancing techniques, this improvement was less evident at lower resolutions.
-These results were consistent for the K562 cell line (Supplementary Figure 2).
-Random forest models built on Peakachu loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3).
-Five kilobase resolution genomic bins was found to result in optimal prediction for both TAD and loop boundaries, on both cell lines.
-Our results indicate that random under-sampling, distance-type predictors, and high-resolution Hi-C data provide the optimal set of data level characteristics for both TAD and loop boundary prediction.
-
-<!--
-Interestingly, for the optimal re-sampling and predictor type, we found that performances peaked at 10 kb resolution and then degraded as data resolution decreased.
-The reason for the improved performance between 5 kb and 10 kb data resolutions can be attributed to the sparsity in the interaction frequency matrices at finer resolutions.
-This sparsity may lead to inaccurate TAD calling and, subsequently, to worse model performance.
-These results suggest that finer resolution of Hi-C data is not always optimal for accurate TAD calling and prediction, and sparsity of the data needs to be considered.
-Furthermore, performances tended to be much more variable between chromosomes at lower resolutions, evidenced by the wider error bars for the 50 kb and 100 kb resolutions.
-These results were found to be consistent for the K562 cell line (Supplementary Figure 2).
-In summary, our computational framework showed that using random under-sampling, distance-type predictors, and Hi-C data at 10kb resolution yields an optimally performing cell line-specific random forest classification model for TAD boundary prediction.
--->
+As with class balancing techniques, this improvement was less evident at lower resolutions with results consistent for K562 (Supplementary Figure 2).
+Random forest models built on PEAKACHU-defined loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3).
+Furthermore, 5 kb resolution genomic bins led to optimal prediction for both TAD and loop boundaries, on both cell lines.
+Our results indicate that random under-sampling, distance-type predictors, and high-resolution Hi-C data provide the optimal set of data level characteristics for both TAD and chromatin loop boundary prediction.
 
@@
 We hypothesized that the type of genomic annotations may also affect the predictive performance.
-Using the established optimal settings (RUS, Distance), we built separate random forest models using BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS).
-We found that models built on TFBSs outperformed other annotation-specific models, and these results were consistent for loop boundaries, for both cell lines (Figure 4A; Supplementary Figures 4A).
-These results suggest that TFBS are the primary drivers of TAD and loop boundary formation in both the GM12878 and K562 cell lines.
+Using the established optimal settings (RUS, Distance, 5 kb bins), we built separate random forest models using BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS).
+We found that models built on TFBSs outperformed other annotation-specific models, with results consistent for loop boundaries, on both cell lines (Figure 4A; Supplementary Figures 4A).
+These results suggest that TFBS are the primary drivers of TAD and loop boundary formation in both the GM12878 and K562.
 
@@
 
-We sought to further optimize our TAD boundary region prediction model by performing recursive feature elimination to avoid overfitting and select only the most influential TFBS across all autosomal chromosomes.
+We sought to further optimize our boundary region prediction models by performing recursive feature elimination to avoid overfitting and select only the most influential TFBS across all autosomal chromosomes.
 We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figures 4B).
-However, given that we trained our model on chromosome-specific data, the most significant annotations were found to vary for each chromosome.
-To determine transcription factors most important for boundary prediction, we clustered the predictive importances of the top eight significant TFs across chromosomes.
+However, given that we trained our model on chromosome-specific data, the most significant annotations were found to vary for each chromosome that was left out of training and reserved for testing.
+To determine transcription factors most important for boundary prediction, we clustered the predictive importances (mean decrease in accuracy) of the top eight significant TFs across chromosomes.
 We found that, similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD and loop boundaries for all chromosomes (Figure 4C; Supplementary Figures 4C).
 We further optimized our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
-In summary, our framework was able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
+In summary, under our machine learning framework we were able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
 
-<!--
-To summarize, the optimally built cell line-specific random forest model under our computational framework was found to be one built using 10 kb resolution data, leveraging distance-type predictors for the CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites, while implementing random under-sampling to balance TAD and non-TAD boundary defined genomic bins.
--->
+## Training in one cell line accurately predicts boundary regions in other cell lines
+
+Having demonstrated the optimal performance in our framework's ability to predict boundary regions, we next attempted to predict boundary regions in one cell line when trained on another (See Methods).
+We found that training and testing using ARROWHEAD ground truth TAD boundaries and genomic elements from GM12878 resulted in an average AUC=0.845 (Figure 4D).
+However when training on GM12878 and testing on K562, our model's average AUC only marginally decreased to 0.803.
+Likewise, training and testing on PEAKACHU resulted in an average AUC=0.885 and decreased only slightly to 0.868 when trained on GM12878 and K562.
+Results were consistent when training on K562 and testing on GM12878 (Supplementary Figure 4D).
 

### 2020-07-31 Manuscript/manuscript.Rmd
editted results

@@
 Using our optimally built random forest model trained on ARROWHEAD/Peakachu boundaries, we attempted to predict TAD/loop boundaries at base resolution.
-Intuitively, the predictor-response space is built on a base-resolution level, and the model trained on a bin-level space predicts the probability of each base being a boundary.
-Our method, referred to as *preciseTAD*, leverages a user-specified [???
-We need pre-trained models and understanding how they perform on different cell lines;!!!working on it] model with density-based hierarchical clustering (DBSCAN) and a scalable partitioning around mediods clustering (CLARA) to predict the boundary location ad base resolution (see Methods).
+Intuitively, the predictor-response space is built on a base-resolution level, and the model trained (using the optimal characteristics outlined above) on a bin-level space predicts the probability of each base being a boundary.
+Our method, referred to as *preciseTAD*, leverages a user-specified model with density-based hierarchical clustering (DBSCAN) and a scalable partitioning around mediods clustering (CLARA) to predict the boundary location at base resolution (see Methods).
 
-When built using ARROWHEAD ground truth boundaries at 5 kb, *preciseTAD* was able to predict a total of ???
-and ???
-boundaries for GM12878 and K562 cell lines respectively.
-We reported less predicted TAD boundaries than ARROWHEAD (Table 1, Supplementary Table 2) [???
-Where is this info?;!!!talk about in meeting].
-This can be attributed to ARROWHEAD's boundaries frequently being separated by gaps, the effect especially pronounced near sparse areas of Hi-C contact matrices (Figure 5A) [???
-I don't see it, data not shown?].
+When built using ARROWHEAD and PEAKACHU ground truth boundaries at 5 kb and 10 kb respectively, *preciseTAD* was able to predict a total of 7846 TAD and 15838 chromatin loop boundaries on GM12878, as well as 8883 TAD and 11016 chromatin loop boundaries on K562.
+Noticeably, we reported less predicted TAD boundaries at 5 kb than ARROWHEAD on both cell lines (Table 1, Supplementary Table 2).
+This can be attributed to ARROWHEAD's inflation of called TADs, especially at higher resolutions, that do not correspond to intra-chromosomal contacts featured on a contact matrix (Figure 1A).
+Likewise, ARROWHEAD often produces nested and overlapped TADs that do not have demarcated boundaries, further exacerbating this inflation.
 However, under the framework of *preciseTAD*, any two TADs are inherently conjoined by only one predicted TAD boundary, leading to comparatively less TAD boundaries.
@@
 May it be too stringent thresholds?
-This all may be for the discussion, if we have a good understanding why] We also found that predicted TAD boundaries identified by *preciseTAD* were visually more likely to demarcate high concentrations of inter-chromosomal contacts as seen on a Hi-C contact matrix (Figure 5A).
-[???add peakachu totals when ready]
+This all may be for the discussion, if we have a good understanding why] Additionally, *preciseTAD* boundaries were visually more likely to demarcate high concentrations of intra-chromosomal contacts as seen on a Hi-C contact matrix (Figure 5A).
+*preciseTAD* also predicted fewer chromatin loop boundaries than PEAKACHU (Table 1, Supplementary Table 2).
+This can be contributed to the fact that *preciseTAD* leverages 4 known drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143, contrasting PEAKACHU which considers only CTCF sites.
+This methodology likely leads to many more false positives, resulting in inflated number of chromatin loops.
 
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
-Signal heatmaps [???
-Make sure to mention DeepTools in Methods;!!!added] indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or Peakachu boundaries alone (Figure 5 B-C).
-Likewise, *preciseTAD* boundaries were also more enriched for other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 8-9).
-When compared to called TAD or loop boundaries, *preciseTAD* boundaries were found to be statistically significantly closer to the same cell line-specific top ranked TFBS (p=???
-and p=???
-vs ARROWHEAD and Peakachu respectively) (Figure 5D, Supplementary Figure 10-11).
-We also inspected the effect of resolution on locations of our predicted TAD boundaries.
-We found that *preciseTAD* boundaries exhibited higher pairwise Jaccard indices between adjacent resolutions than ARROWHEAD boundaries, thus implying stronger invariance toward resolution (Figure 5E).
+Signal heatmaps indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or PEAKACHU boundaries alone (Figure 5 B-C).
+Likewise, *preciseTAD* boundaries were also more enriched for other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 5-6).
+When compared to called TAD or loop boundaries, *preciseTAD* boundaries were found to be statistically significantly closer to the same cell line-specific top ranked TFBS (p<0.001 and p<0.001 versus ARROWHEAD and PEAKACHU respectively) (Figure 5D, Supplementary Figure 7).
+
+## *preciseTAD* boundaries are more conserved across cell lines
+
+TAD boundaries are known to be relatively conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
+To assess conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, ARROWHEAD, and Peakachu after flanking them by the resolution of the Hi-C data.
+Boundaries involving ARROWHEAD were flanked by 5 kb, while boundaries involving PEAKACHU were flanked by 10 kb.
+We found that 35% of *preciseTAD* predicted TAD boundaries and 55% of *preciseTAD* predicted loop boundaries were were conserved between cell lines, compared to only 26% and 55% for ARROWHEAD and PEAKACHU alone (Figure 5E) [???should I mention jaccard or scrap it?
+significantly different for arrowhead but not peakachu].
+
+<!--Additionally, the median Jaccard index (MJI) was found to be 0.472 (IQR=0.441-0.503; p=???) and 0.647 (IQR=0.646-0.647; p=???) for *preciseTAD* predicted TAD and loop boundaries (Supplementary Table 5).
+Comparatively, only 25% (MJI=0.284; IQR=0.268-0.301) and 49% (MJI=0.509; IQR=0.503-0.515) of called/predicted ARROWHEAD and Peakachu boundaries were conserved (Figure 6A, Supplementary Table 5).
+These results demonstrate that boundaries predicted using genomic annotations (*preciseTAD*) are better conserved across cell lines.-->
+
+<!--We also inspected the effect of resolution on locations of our predicted TAD boundaries.
+We found that *preciseTAD* boundaries exhibited higher pairwise Jaccard indices between adjacent resolutions than ARROWHEAD boundaries, thus implying stronger invariance toward resolution (Figure 5E).-->
 
@@
 
-## *preciseTAD* boundaries are conserved across cell lines
+## *preciseTAD* predicted TAD boundaries are nested within predicted loop boundaries
 
-TAD boundaries are known to be relatively conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
-To assess conservation, we evaluated the overlap between cell-line-specific boundaries detected by *preciseTAD*, ARROWHEAD, and Peakachu after flanking them by the resolution of the Hi-C data.
-Boundaries involving ARROWHEAD were flanked by 5 kb, while boundaries involving Peakachu were flanked by 10 kb.
-We found that a significant proportion of flanked boundaries predicted by *preciseTAD* overlapped between GM12878 and K562.
-Specifically, 45%???
-and 61%???
-of *preciseTAD* boundaries were conserved across cell lines when built on ARROWHEAD and Peakachu boundaries respectively (Figure 6A).
-Additionally, the median Jaccard index (MJI) was found to be 0.472 (IQR=0.441-0.503; p=???) and 0.647 (IQR=0.646-0.647; p=???) for *preciseTAD* predicted TAD and loop boundaries (Supplementary Table 5).
-Comparatively, only 25% (MJI=0.284; IQR=0.268-0.301) and 49% (MJI=0.509; IQR=0.503-0.515) of called/predicted ARROWHEAD and Peakachu boundaries were conserved (Figure 6A, Supplementary Table 5).
-These results demonstrate that boundaries predicted using genomic annotations (*preciseTAD*) are better conserved across cell lines.
-
-The majority of boundaries predicted by the ARROWHEAD-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model (Figure 6B).
+The majority of boundaries predicted by the ARROWHEAD-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model.
+We found that 95.6% and 95.7% of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 8).
 This is expected as loop boundaries (Peackachu) are more abundant, while TAD boundaries (ARROWHEAD) represent the narrower level of the 3D chromatin organization.
-83% and 75% of predicted TAD and loop boundaries overlapped with each other for GM12878 and K562 cell lines, respectively (Figure 6B).
 Together with the results shown on Figure 4, the high overlap between boundaries predicted by ARROWHEAD- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar protein complexes.

### 2020-08-02 Manuscript/manuscript.Rmd
edits to methods, results, and discussion

@@
 ---
-title: "preciseTAD: A machine learning framework for precise TAD boundary prediction at base pair resolution"
+title: "preciseTAD: A machine learning framework for precise TAD boundary prediction at base level resolution"
 csl: styles.ref/genomebiology.csl
@@
 Chromosome conformation capture combined with high-throughput sequencing experiments (Hi-C) have revealed that chromatin undergoes layers of compaction through DNA looping and folding, forming dynamic 3D structures.
-Among these are Topologically Associating Domains (TADs), which are known to play critical roles in cell dynamics like gene regulation and cell differentiation.
+Among these are Topologically Associated Domains (TADs), which are known to play critical roles in cell dynamics like gene regulation and cell differentiation.
 Precise TAD mapping remains difficult, as it is strongly reliant on Hi-C data resolution.
@@
 
-Several methods have been proposed to identify the genomic coordinates of TAD boundaries throughout the linear genome (reviewed in [@Zufferey:2018aa; @forcato2017comparison]), less so for chromatin loops [@rao20143d; @Ay:2014aa; @Heinz:2010aa; @salameh2019supervised].
+Several methods have been proposed to identify the genomic coordinates of TAD boundaries (reviewed in [@Zufferey:2018aa; @forcato2017comparison]), less so for chromatin loops [@rao20143d; @Ay:2014aa; @Heinz:2010aa; @salameh2019supervised].
 However, a key limitation among most of these TAD- and loop callers, referred hereafter as TAD callers for brevity, is that they are heavily reliant on Hi-C data *resolution*.
@@
 These elements are annotated on the genome using chromatin immunoprecipitation followed by high-throughput DNA sequencing (ChIP-seq).
-Even at its highest (750 bp [@bonev2017multiscale]), Hi-C sequencing resolution still remains well below the resolution of ChIP-seq experiments, which ranges in the tens of base pairs [@mendoza2009genome].
+Even at its highest (750 bp [@bonev2017multiscale]), Hi-C sequencing resolution still remains well below the resolution of ChIP-seq experiments, which ranges in the tens of bases [@mendoza2009genome].
 Therefore, leveraging such elements in a supervised machine learning framework lends itself to the possibility of more precisely predicting the locations of TAD (or loop) boundaries at much higher resolutions.
 
-Here we present *preciseTAD*, an R package for precise identification of TAD(or loop) boundaries under a supervised machine learning framework.
+Here we present *preciseTAD*, an R package for precise identification of TAD(or loop) boundaries under a supervised machine learning (ML) framework.
 Our method builds upon an optimized random forest (RF) classification model that leverages high resolution ChIP-seq data in the form of regulatory elements (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS).
@@
 
-Within this study we used both TAD boundary and loop boundary data derived from the publicly available tools ARROWHEAD [@durand2016juicebox] and Peakachu [@salameh2019supervised] respectively.
-ARROWHEAD TAD boundaries were called from primary Hi-C data from Geo GSE63525 [@rao20143d] for the GM12878 and K562 cell lines (Supplementary Table 1).
+Within this study we used both TAD boundary and loop boundary data derived from the publicly available tools ARROWHEAD [@durand2016juicebox] and PEAKACHU [@salameh2019supervised] respectively.
+ARROWHEAD TAD boundaries were called from primary Hi-C data from Geo GSE63525 [@rao20143d] for the GM12878 and K562 cell lines.
 The contact matrices were constructed from all read pairs that uniquely aligned to the genome (MAPQ>0).
 The default parameters for ARROWHEAD were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1).
-Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab web site <!--(Supplementary Table 1)-->.
+PEAKACHU chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab web site.
 Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop.
 Chromosome 9 was excluded from all downstream analyses due to sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-Cell-line-specific genomic annotations (BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa]  (GRCh37/hg19 human genome assembly<!--, Supplementary Table 2-->).
-
-[???added spectralTAD]
+Cell-line-specific genomic annotations (BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa]  (GRCh37/hg19 human genome assembly).
 
@@
 To create shifted binning, the first shifted bin was set to start at half of the resolution *r*, and continued in intervals of length *r* until the end of the chromosome (*mod r* + *r/2*).
-The shifted bins, referred hereafted as bins for simplicity, were then defined as boundary-containing regions (*Y = 1*) if they contained a TAD (or loop) boundary, and non-boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification (Figure 1).
+The shifted bins, referred hereafted as bins for simplicity, were then defined as boundary-containing regions (*Y = 1*) if they contained a TAD (or loop) boundary, and non-boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification.
 
@@
 Bins were annotated by one of either the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average signal strength of the corresponding annotation (*Peak Signal Strength*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
-A ($log_2 + 1$)-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
+A ($log_2 + 1$)-transformation of distance was used to account for the skewness present in the distributions of genomic distances.
 Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin segmentations lack signal values.
@@
 For SMOTE, under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the $k=5$ minority class nearest neighbors [@chawla2002smote] (implemented in the `DMwR` v.0.4.1 R package).
-We restricted the algorithm to 100% over-sampling and 200% under-sampling, which creates perfectly balanced classes.
+We restricted the SMOTE algorithm to 100% over-sampling and 200% under-sampling, which creates perfectly balanced classes.
 
@@
 The $i^{th}$ holdout chromosome was identified and a data matrix, $A_{N \times (p+1)}$, was constructed by combining the binned genome from the remaining chromosomes ($1,2,\cdots, i-1,i+1,\cdots,21,22$), where $N=[n_{1} n_{2} \cdots n_{21} n_{22}]'$ and $n_{k}$ is the length of chromosome *k* after being binned into non-overlapping regions of resolution *r*, such that $k \ne i$.
-$p$, the number of annotations, together with one response vector, define column-wise dimension of the matrix $A$.
+$p$, the number of annotations, together with the response vector **Y**, defined column-wise dimension of the matrix $A$.
 Re-sampling was then performed on $A$ and an RF classifier was trained using 3-fold cross-validation to tune for the number of annotations to consider at each node (*mtry*).
@@
 This process was repeated for each holdout chromosome.
-To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivies and specificities when tested on the cell line specific holdout chromosome test data, and reported the area under the curve (AUC).
+To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivies and specificities, and reported the area under the curve (AUC).
 
@@
 
-To investigate whether we could alleviate resolution limitations of conventional TAD and chromatin loop calling tools, we developed *preciseTAD*, an algorithm that leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base pair (bp) resolution.
+To investigate whether we could alleviate resolution limitations of conventional TAD and chromatin loop calling tools, we developed *preciseTAD*, an algorithm that leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution.
 To demonstrate, we implemented an optimally built RF model using the framework described above.
@@
 
-[???
-There is a big gap there.
-Describe the construction of dependent vector Y and predictor matrix _for each base_;!!!talk about in meeting; specify that each base pair has own prob; don't use "base pair" only "base" or "base level"]
-
-First the vector, $p_{n_{i}}$, denoting each base pair's probability of being a boundary point from the RF model, was extracted, where $n_{i}$ represents the length of chromosome $i$.
-Next, DBSCAN [???
-We need to define what to italicize.
-Check below, make consistent throughout the manuscript;!!!talk about in meeting] (version 1.1-5) was applied to the matrix of pairwise genomic distances between base pairs with $p_{n_{i}}=1$.
-This was to avoid the inflation of predicted boundaries that can occur naturally when dealing with such fine resolution, namely, due to spatially close base pairs with similar predictor profiles (i.e.
+We first construct a base level resolution predictor space for a particular chromosome **i**, using one of the above feature engineering procedures described above.
+We then validate our RF model on the base level predictor space to extract the probability vector, $p_{n_{i}}$, denoting each base's probability of being a boundary point from the RF model, where $n_{i}$ represents the length of chromosome **i**.
+Next, DBSCAN (version 1.1-5) was applied to the matrix of pairwise genomic distances between bases with $p_{n_{i}}=1$.
+This was to avoid the inflation of predicted boundaries that can occur naturally when dealing with such fine resolution, namely, due to spatially close bases with similar predictor profiles (i.e.
 similar overlap counts, distances, etc.).
@@
 The *eps* parameter was assigned as the respective data resolution.
-The heuristic being that density-reachable base pairs with genomic distances less than resolution should occupy the same designated cluster.
+The heuristic being that density-reachable bases with genomic distances less than resolution should occupy the same designated cluster.
 The corresponding *MinPts* parameter was set to recommended value of 3, representing $1+dim(data)$ [@hahsler2019dbscan].
-The resulting clusters of highly predictive base pairs identified by DBSCAN were termed *preciseTAD boundary regions* (PTBR).
-To precisely identify a single base pair among each PTBR, preciseTAD then implements an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
-The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative and biologically meaningful base pair coordinate within each clustered PTBR.
+The resulting clusters of highly predictive bases identified by DBSCAN were termed *preciseTAD boundary regions* (PTBR).
+To precisely identify a single base among each PTBR, preciseTAD then implements an extension of partitioning around medoids (PAM), known as CLARA (**Clustering Large Applications**) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
+The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative and biologically meaningful base coordinate within each clustered PTBR.
 
@@
 Next, we assessed the biological significance of our predicted boundaries with respect to the enrichment profiles of several known molecular drivers of 3D chromatin architecture including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
-To do so, we used the computeMatrix [???
-Again, I expected italics, but decide and correct;!!!talk about in meeting] and plotHeatmap tools offered by deepTools version 2.0 [@ramirez2016deeptools] via integration with Galaxy version 3.3.2.0.0 [@afgan2018galaxy].
-Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum test.
+To do so, we used the **computeMatrix** and **plotHeatmap** tools offered by deepTools (version 2.0) [@ramirez2016deeptools] via integration with Galaxy (version 3.3.2.0.0) [@afgan2018galaxy].
+Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum tests.
 Furthermore, we compared the overlap between predicted and called boundaries in GM12878 and K562 cell lines.
 Boundaries were first flanked by resolution, *r*, and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0).
-Overlaps were further quantified using Jaccard index defined as
+Overlaps were further quantified using the Jaccard index defined as
 
@@
 That is, between cell lines, the number of overlapping flanked boundaries divided by the total number of flanked boundaries.
-Wilcoxon rank sum tests were used to compare chromosome-specific Jaccard indices across cell lines, between *preciseTAD* boundaries and both ARROWHEAD and Peakachu boundaries, respectively.
+Wilcoxon Rank-Sum tests were used to compare chromosome-specific Jaccard indices across cell lines, between *preciseTAD* boundaries and both ARROWHEAD and PEAKACHU boundaries, respectively.
 All statistical analyses were performed in R version 4.0.1.
@@
 
-where $x_{ij}$ is the total number of base pairs of annotation $i$ in window $j$ and $w_{ij}$ is the number of base pairs that overlap between annotation $i$ and window $j$.
+where $x_{ij}$ is the total number of bases of annotation $i$ in window $j$ and $w_{ij}$ is the number of bases that overlap between annotation $i$ and window $j$.
 The denominator, $L$, is the width of the windows (here, $L=50$).
@@
 
-## Developing a machine learning framework for optimal TAD boundary prediction
+## Developing a ML framework for optimal TAD boundary prediction
 
-We developed a machine learning framework aimed at determining the optimal set of data level characteristics necessary for topologically associated domain (TAD) boundary prediction.
-We chose the random forest (RF) machine learning algorithm as our binary classification tool.
+We developed a machine learning (ML) framework aimed at determining the optimal set of data level characteristics necessary for topologically associated domain (TAD) boundary prediction.
+We chose the random forest (RF) algorithm as our binary classification tool.
 The reason being two-fold: (1) In order to devise a tunable prediction rule in a supervised learning framework that is both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors [@boulesteix2012overview].
-We extended our method and developed *preciseTAD*, an algorithm which leverages an optimally built RF to precisely predict the genomic coordinates of both TAD and chromatin loop boundaries at base pair resolution.
+We extended our method and developed *preciseTAD*, an algorithm which leverages an optimally built RF to precisely predict the genomic coordinates of both TAD and chromatin loop boundaries at base resolution.
 
-Our framework is resolution-specific and uses called TAD or loop boundaries as ground truth to establish TAD(loop)-boundary and non-TAD(loop) boundary regions.
-To demonstrate, we applied our framework to publically available replicate Hi-C data sets from the GM12878 and K562 cell lines obtained from GEO GSE63525 (Supplementary Table 1).
+We use called TAD or loop boundaries as ground truth to establish TAD(loop)-boundary and non-TAD(loop) boundary regions.
+To demonstrate, we applied our framework to publicly available replicate Hi-C data sets from the GM12878 and K562 cell lines obtained from GEO GSE63525 (Supplementary Table 1).
 TADs were subsequently called using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
@@
 
-Boundary regions were defined as regions containing a called boundary ($Y = 1$), while non-boundary regions were defined as genomic bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
+In our ML framework boundary regions were defined as regions containing a called boundary ($Y = 1$), while non-boundary regions were defined as genomic bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
 The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 2).
@@
 
-A total of 77 cell-line-specific functional genomic annotations were used to build the predictor space.
+A total of 77 cell line-specific functional genomic annotations were used to build the predictor space.
 These included BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 3).
@@
 These include signal strength association (Signal), direct (OC), proportional (OP), and spatial (Distance) relationships (see Methods).
+A ($log_2 + 1$)-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
 
@@
 The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD boundary, respectively.
-(B) Four types of associations between bins and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and ($log_{2}$) Distance.](Figures/figure1.png)
+(B) Four types of associations between bins and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png)
 
-We considered combinations of data from two cell line *L = {GM12878, K562}*, five resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor space *P = {Signal, OC, OP, Distance}*, and three re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
+In total, we considered combinations of data from two cell lines *L = {GM12878, K562}*, five resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor space *P = {Signal, OC, OP, Distance}*, and three re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
 Once the model inputs were established, a random forest classifier was trained on $n-1$ autosomal chromosomes, while reserving the $i^{th}$ chromosome for testing.
@@
 Model performance was evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (see Methods).
-These strategies allowed us to select the best performing model.
+These strategies allowed us to select the best performing model in an unbiased manner.
 
@@
 
-![*Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for GM12878 ARROWHEAD TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+![**Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for GM12878 ARROWHEAD TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
@@
 However when training on GM12878 and testing on K562, our model's average AUC only marginally decreased to 0.803.
-Likewise, training and testing on PEAKACHU resulted in an average AUC=0.885 and decreased only slightly to 0.868 when trained on GM12878 and K562.
+Likewise, training and testing on PEAKACHU resulted in an average AUC=0.885 and decreased only slightly to 0.868 when trained on GM12878 and tested on K562.
 Results were consistent when training on K562 and testing on GM12878 (Supplementary Figure 4D).
+[???need concluding sentence]
 
@@
 
-Using our optimally built random forest model trained on ARROWHEAD/Peakachu boundaries, we attempted to predict TAD/loop boundaries at base resolution.
+Using our optimally built random forest model trained on ARROWHEAD/PEAKACHU boundaries, we attempted to predict TAD/loop boundaries at base resolution.
 Intuitively, the predictor-response space is built on a base-resolution level, and the model trained (using the optimal characteristics outlined above) on a bin-level space predicts the probability of each base being a boundary.
@@
 Noticeably, we reported less predicted TAD boundaries at 5 kb than ARROWHEAD on both cell lines (Table 1, Supplementary Table 2).
-This can be attributed to ARROWHEAD's inflation of called TADs, especially at higher resolutions, that do not correspond to intra-chromosomal contacts featured on a contact matrix (Figure 1A).
+This can be attributed to ARROWHEAD's inflation of called TADs, especially at higher resolutions, that often do not correspond to intra-chromosomal contacts featured on a contact matrix (Figure 1A).
 Likewise, ARROWHEAD often produces nested and overlapped TADs that do not have demarcated boundaries, further exacerbating this inflation.
@@
 May it be too stringent thresholds?
-This all may be for the discussion, if we have a good understanding why] Additionally, *preciseTAD* boundaries were visually more likely to demarcate high concentrations of intra-chromosomal contacts as seen on a Hi-C contact matrix (Figure 5A).
+This all may be for the discussion, if we have a good understanding why] Additionally, *preciseTAD* boundaries were visually more likely to demarcate high concentrations of intra-chromosomal contacts as can be seen on a Hi-C contact matrix (Figure 5A).
 *preciseTAD* also predicted fewer chromatin loop boundaries than PEAKACHU (Table 1, Supplementary Table 2).
@@
 TAD boundaries are known to be relatively conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
-To assess conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, ARROWHEAD, and Peakachu after flanking them by the resolution of the Hi-C data.
+To assess conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, ARROWHEAD, and PEAKACHU after flanking them by the resolution of the Hi-C data.
 Boundaries involving ARROWHEAD were flanked by 5 kb, while boundaries involving PEAKACHU were flanked by 10 kb.
@@
 We found that 95.6% and 95.7% of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 8).
-This is expected as loop boundaries (Peackachu) are more abundant, while TAD boundaries (ARROWHEAD) represent the narrower level of the 3D chromatin organization.
+This is expected as loop boundaries (PEAKACHU) are more abundant, while TAD boundaries (ARROWHEAD) represent the narrower level of the 3D chromatin organization.
 Together with the results shown on Figure 4, the high overlap between boundaries predicted by ARROWHEAD- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar protein complexes.
@@
 *preciseTAD* leverages a random forest (RF) classification model built on ground truth TAD/loop boundaries obtained from a TAD/loop calling tools and ChIP-seq defined genomic annotations as the predictor space.
-We benchmarked *preciseTAD* against two boundary calling tools, ARROWHEAD [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
-We applied *preciseTAD* on cell line-specific boundaries and ChIP-seq data from both the GM12878 and K562 cell lines.
-We first optimized our RF model by systematically comparing different combinations of genome binning (resolution), feature engineering procedures, and re-sampling technique addressing class imbalance.
-We show that distance between boundary regions and genomic annotations coupled with random undersampling technique help to form the predictor space resulting in optimal model performance.
-We demonstrate that binding of four transcription factors (SMC3, Rad21, CTCF, Znf143) are sufficient for accurate TAD and loop boundary predictions.
-The model predicts probability for each base to be a baoundary, and, coupled with spatial clustering (DBSCAN) and scalable partition around medoids clustering (CLARA), allows for the detection of boundaries at the base-level resolution.
+We benchmarked *preciseTAD* against two boundary calling tools, ARROWHEAD [@durand2016juicebox], an established TAD-caller, and PEAKACHU [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
+We applied *preciseTAD* on cell line-specific boundaries and ChIP-seq data from both GM12878 and K562.
+We first optimized our RF model by systematically comparing different combinations of genome binning (resolution), feature engineering procedures, and re-sampling techniques.
+We show that genomic distance between boundary regions and annotations, coupled with random under-sampling help to form the predictor space resulting in optimal model performance.
+<!--We demonstrate that binding of four transcription factors (SMC3, Rad21, CTCF, Znf143) are sufficient for accurate TAD and loop boundary predictions.
+The model predicts probability for each base to be a baoundary, and, coupled with spatial clustering (DBSCAN) and scalable partition around medoids clustering (CLARA), allows for the detection of boundaries at the base-level resolution.-->
 
-Our random forest framework yielded several interesting observations.
-First, we showed that RF models built using *distance*-type predictors outperformed models built on previously published feature engineering techniques including signal strength, overlap counts and overlap percents [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa; @kai2018predicting].
-We further demonstrated that class imbalance hinders boundary prediction, but can be effectively addressed by a simple random under-sampling technique.
-The unaddressed class imbalance problem in previous studies [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa] We showed that information about only four transcription factors (SMC3, Rad21, CTCF, Znf143) is necessary and sufficient transcription for accurate boundary prediction, outperforming histone modification- and BroadHMM-built models [@Moore:2015aa; @Al-Bkhetan:2018aa].
+Our machine learning framework yielded several interesting observations.
+First, we demonstrated that RF models built using *distance*-type predictors outperformed models built on previously published feature engineering techniques including signal strength, overlap counts and overlap percents [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa; @kai2018predicting].
+We further demonstrated that class imbalance hinders boundary prediction, but can be effectively addressed by a simple random under-sampling technique, an aspect of boundary prediction that was unaddressed in previous studies [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa].
+We showed that information about only four transcription factors (SMC3, Rad21, CTCF, Znf143) is necessary and sufficient for accurate boundary prediction, outperforming histone modification- and BroadHMM-built models [@Moore:2015aa; @Al-Bkhetan:2018aa].
 These are known components of the loop extrusion model, an established theory for how loops are made by a ring-shaped adenosine triphosphatase complex called cohesin [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
@@
 
-Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Supplementary Tables 6-7 [???
+Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Supplementary Tables 4-5 [???
 Merge them into one Excel with two sheets - same message]).
-The accuracy metric can be artificially inflated by true negatives (TN), the set of genomic bins correctly predicted as not containing a ground truth boundary [???
-Is it because of class imbalance?; add detail].
+Our aim was to have a balanced metric that was sensitive to class imbalance such that it would not favor one component of the confusion matrix.
+The accuracy metric can be artificially inflated by true negatives (TN), the set of genomic bins correctly predicted as not containing a ground truth boundary.
 AUROC captures how a model generally performs accross different thresholds.
-However, it doesn't place more emphasis on one class over the other, so it does not reflect the minority class well [???
-So, another class imbalance problem?
-Define class imbalance message early, why you investigated 5 other metrics].
+However, it doesn't place more emphasis on one class over the other, so it does not reflect the minority class well.
 Precision indicates the rate at which positive predictions are correct and can be artificially deflated by low proportions of true positives (TP), the set of genomic bins correctly predicted as containing a ground truth boundary.
@@
 The BA benefits from incorporating all components of the confusion matrix, while also being sensitive to class imbalance, a necessary characteristic when comparing performances to models built using no data re-sampling.
-[???
-The logic is messed when reading this paragraph.]
 
-The performance of *preciseTAD* was found to be empirically better [???
-As judged by what?] than both ARROWHEAD and Peakachu ground truth boundaries.
 Guided by both low-resolution Hi-C data and high-resolution genome annotation data, *preciseTAD* predicts base-level resolution boundaries, alleviating resolution limitations of Hi-C data.
-We show that, unlike ARROWHEAD, *preciseTAD* does not inflate the number of predicted boundaries [???
-Where did you show this?
-TBD], instead, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
+We show that, unlike ARROWHEAD, *preciseTAD* does not inflate the number of predicted boundaries, instead, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
 *preciseTAD* TAD and loop boundaries were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops are dynamic structures generated by similar mechanisms [@hansen2018recent].
@@
 So what?].
-Likewise *preciseTAD* boundaries were found to be more conserved between GM12878 and K562 cell lines, further highlighting their biological significance.
+Likewise *preciseTAD* boundaries were found to be more conserved between GM12878 and K562 cell lines, a known feature among the 3D architecture of the human genome, further highlighting their biological significance [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
 [???
@@
 
+*preciseTAD* offers flexibility in controlling both the number of TAD(loop) boundaries as well as the distance between them.
+The two primary parameters are the probability threshold (*t*) and $\epsilon$ (refered to as eps; parameter of DBSCAN).
+The combination of these two quantities change the resulting number of predicted boundaries from *preciseTAD*.
+A lower threshold and $\epsilon$ will result in more clusters of bases, and therefore, more boundaries.
+As a heuristic, we evaluated the pairwise combination of 4 different thresholds ($t=(0.95,0.975,0.99,1.0)$) and 4 different $\epsilon$ values ($\epsilon=(0.2 r, 0.5r, r, 2r)$)), where $r=5000$, the optimal resolution.
+We found that $t=1.0$ and $\epsilon=r$ ensured that boundaries were at least 5kb bases away from each other, while also suitably enriched for architectural proteins (Supplementary Figures 9-10).
+
 A limitation of *preciseTAD* is that it is dependent on "ground truth" boundaries provided by a user-defined TAD caller.
-Given the wide variery of TAD callers and their variable performance [@Zufferey:2018aa; @forcato2017comparison], it is hard to define "ground truth" TAD boundaries.
+Given the wide variety of TAD callers and their variable performance [@Zufferey:2018aa; @forcato2017comparison], it is hard to define "ground truth" TAD boundaries.
 <!--Ideally we would benchmark *preciseTAD* against simulated boundaries.
@@
 We may be missing TADs that are distinct from the canonical CTCF boundaries.
-TBD].
+TBD; !!!discuss in meeting].
 Our future work will include defining separate models trained on different TAD boundary types, and predicting precise locations for each of them.
@@
 Simply considering the properties of Hi-C contact matrices ignores the fundamental roles of known molecular drivers of the 3D chromatin structures.
-Instead, we propose a supervised machine learning framework that leverages both Hi-C contact matrix information and genomic annotations.
+Instead, we propose *preciseTAD*, a supervised machine learning framework that leverages both Hi-C contact matrix information and genomic annotations.
 Our method introduces three concepts - *shifted binning*, *distance*-type predictors, and *random undersampling* - which we use to build random forest classification models for predicting boundary regions.
@@
 **Supplementary Figure 1.** Density curves illustrate the normalization of distances before (red) and after (blue) performing a $log_{2}$ transformation across differing bin sizes including 10 kb, 25 kb, 50 kb, and 100 kb for both the (A) GM12878 and (B) K562 cell lines respectively.
-Distances are measured as the number of base pairs from the center of a genomic bin to the center of the nearest genomic annotation.
+Distances are measured as the number of bases from the center of a genomic bin to the center of the nearest genomic annotation.
 Each density curve represents individual genomic annotation.
@@
 
+**Supplementary Figure 9**.
+Density plots illustrating the genomic distance (in bases) between predicted TAD boundaries identified by preciseTAD for different combinations of thresholds (t) and eps values ($\epsilon$) on GM12878.
+The median genomic distance (range) is provided for each combination.
+
+**Supplementary Figure 10**.
+The formation of TADs (CHR22: 25mb-27mb) demarcated by boundaries predicted by preciseTAD for different combinations of thresholds (t) and eps values ($\epsilon$) on GM12878.
+The visualization was created by the juicebox toolbox [@durand2016juicebox] using the GM12878 insitu primary HIC file provided by Rao et al.
+2014 [@rao20143d].
+
 # Abbreviations

### 2020-08-02 Scripts_for_results/13_saving_boundary_data_for_deeptools.Rmd
initial commit

---
title: "Saving boundary datasets for DeepTools"
author: "Spiro Stilianoudakis"
date: "7/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading packages and functions

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

# ARROWHEAD

## GM12878

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout.rds"))

  pred_bound_list[[i]] <- called_and_pred[[2]]
  true_bound_list[[i]] <- called_and_pred[[3]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #15468
length(all_pred_bounds) #7846

all_true_bounds_df <- data.frame(chr=as.character(seqnames(all_true_bounds)),
                                 start=start(all_true_bounds),
                                 end=start(all_true_bounds)+1)

all_pred_bounds_df <- data.frame(chr=as.character(seqnames(all_pred_bounds)),
                                 start=start(all_pred_bounds),
                                 end=start(all_pred_bounds)+1)

write.table(all_true_bounds_df, "C:/Users/stili/Documents/TAD_miscellaneous/data/bedfiles_for_deeptools/arrowhead_gm12878_5kb.bed",
            col.names = FALSE,
            row.names = FALSE,
            quote = FALSE,
            sep = "\t")

write.table(all_pred_bounds_df, "C:/Users/stili/Documents/TAD_miscellaneous/data/bedfiles_for_deeptools/preciseTAD_arrowhead_gm12878_5kb.bed",
            col.names = FALSE,
            row.names = FALSE,
            quote = FALSE,
            sep = "\t")
```

## K562

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout.rds"))

  pred_bound_list[[i]] <- called_and_pred[[2]]
  true_bound_list[[i]] <- called_and_pred[[3]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #9316
length(all_pred_bounds) #8883

all_true_bounds_df <- data.frame(chr=as.character(seqnames(all_true_bounds)),
                                 start=start(all_true_bounds),
                                 end=start(all_true_bounds)+1)

all_pred_bounds_df <- data.frame(chr=as.character(seqnames(all_pred_bounds)),
                                 start=start(all_pred_bounds),
                                 end=start(all_pred_bounds)+1)

write.table(all_true_bounds_df, "C:/Users/stili/Documents/TAD_miscellaneous/data/bedfiles_for_deeptools/arrowhead_k562_5kb.bed",
            col.names = FALSE,
            row.names = FALSE,
            quote = FALSE,
            sep = "\t")

write.table(all_pred_bounds_df, "C:/Users/stili/Documents/TAD_miscellaneous/data/bedfiles_for_deeptools/preciseTAD_arrowhead_k562_5kb.bed",
            col.names = FALSE,
            row.names = FALSE,
            quote = FALSE,
            sep = "\t")
```

# PEAKACHU

## GM12878

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))

  pred_bound_list[[i]] <- called_and_pred[[2]]
  true_bound_list[[i]] <- called_and_pred[[3]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #21421
length(all_pred_bounds) #15838

all_true_bounds_df <- data.frame(chr=as.character(seqnames(all_true_bounds)),
                                 start=start(all_true_bounds),
                                 end=start(all_true_bounds)+1)

all_pred_bounds_df <- data.frame(chr=as.character(seqnames(all_pred_bounds)),
                                 start=start(all_pred_bounds),
                                 end=start(all_pred_bounds)+1)

write.table(all_true_bounds_df, "C:/Users/stili/Documents/TAD_miscellaneous/data/bedfiles_for_deeptools/peakachu_gm12878_10kb.bed",
            col.names = FALSE,
            row.names = FALSE,
            quote = FALSE,
            sep = "\t")

write.table(all_pred_bounds_df, "C:/Users/stili/Documents/TAD_miscellaneous/data/bedfiles_for_deeptools/preciseTAD_peakachu_gm12878_10kb.bed",
            col.names = FALSE,
            row.names = FALSE,
            quote = FALSE,
            sep = "\t")
```

## K562

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10,11,13:22))
for(i in 1:length(chrs)){
  print(i)
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))

  pred_bound_list[[i]] <- called_and_pred[[2]]
  true_bound_list[[i]] <- called_and_pred[[3]]

}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #20773
length(all_pred_bounds) #10379

all_true_bounds_df <- data.frame(chr=as.character(seqnames(all_true_bounds)),
                                 start=start(all_true_bounds),
                                 end=start(all_true_bounds)+1)

all_pred_bounds_df <- data.frame(chr=as.character(seqnames(all_pred_bounds)),
                                 start=start(all_pred_bounds),
                                 end=start(all_pred_bounds)+1)

write.table(all_true_bounds_df, "C:/Users/stili/Documents/TAD_miscellaneous/data/bedfiles_for_deeptools/peakachu_k562_10kb.bed",
            col.names = FALSE,
            row.names = FALSE,
            quote = FALSE,
            sep = "\t")

write.table(all_pred_bounds_df, "C:/Users/stili/Documents/TAD_miscellaneous/data/bedfiles_for_deeptools/preciseTAD_peakachu_k562_10kb.bed",
            col.names = FALSE,
            row.names = FALSE,
            quote = FALSE,
            sep = "\t")
```

### 2020-08-06 Manuscript/manuscript.Rmd
edits

@@
 
-Chromosome conformation capture combined with high-throughput sequencing experiments (Hi-C) have revealed that chromatin undergoes layers of compaction through DNA looping and folding, forming dynamic 3D structures.
+**Background** Chromosome conformation capture combined with high-throughput sequencing experiments (Hi-C) have revealed that chromatin undergoes layers of compaction through DNA looping and folding, forming dynamic 3D structures.
 Among these are Topologically Associated Domains (TADs), which are known to play critical roles in cell dynamics like gene regulation and cell differentiation.
 Precise TAD mapping remains difficult, as it is strongly reliant on Hi-C data resolution.
-Obtaining genome-wide chromatin interactions at high-resolution is costly resulting in variability in true TAD boundary location by TAD calling algorithms.
-To aid in the precise identification of TAD boundaries we developed preciseTAD, a machine learning framework that leverages the spatial relationship of many high resolution ChIP-seq defined genomic elements, coupled with density-based clustering  and scalable partitioning techniques.
-Our framework precisely predicts chromosome-specific TAD boundaries on multiple cell types.
-We show that known molecular drivers of 3D chromatin including CTCF, RAD21, and SMC3 are more enriched at our predicted TAD boundaries compared to the boundaries identified by the popular ARROWHEAD TAD caller.
-Our results provide useful insights into the 3D organization of the human genome.
+Obtaining genome-wide chromatin interactions at high-resolution is costly resulting in variability in true TAD boundary location by conventional TAD calling algorithms.
 
-# ABSTRACT (MD version)
+**Methods** To aid in the precise identification of TAD boundaries we developed preciseTAD, a random forest based framework that leverages the spatial relationship of high resolution ChIP-seq defined genomic elements, coupled with density-based clustering and scalable partitioning techniques.
+We benchmarked our method against a popular TAD-caller and a novel chromatin loop prediction algorithm on multiple cell lines.
 
-**Background.** Topologically Associated Domains (TADs) represent fundamental building blocks of the three-dimensional (3D) genome organization and regulation.
-Several epigenetic marks, such as CTCF, are highly enriched at TAD boundaries, suggesting a strong epigenetic component of TAD boundary formation.
-Several methods have been developed to leverage the growing amount of (epi)genomic annotation data for predicting TAD boundaries; however, they overlooked key characteristics of the data, such as spatial associations between a genomic annotation and a boundary.
-Furthermore, the number of regions containing TAD boundaries is much smaller than the rest of the genome, creating a class imbalance problem.
+**Results** We show that our framework performs well when predicting both TAD and chromatin loop boundaries.
+Compared to established techniques, boundaries predicted by preciseTAD are more enriched for CTCF, RAD21, SMC3, and ZNF143 sites.
+Likewise, preciseTAD boundaries were more conserved across cell lines, highlighting their biological significance.
 
-**Methods.** To investigate the problem of spatial genomic relationships and class imbalance, we developed an ensemble framework for optimizing prediction of TAD boundaries.
-We utilized several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) coupled with various metrics for classifier performance evaluation (Area Under Receiver Operating Characteristics (AUROC) curve, Precision-Recall curve (AUPRC), F1, Matthews Correlation Coefficient (MCC), among others) to select the best predictive model in class imbalance settings.
-
-**Results.** Using different feature engineering and resampling strategies, coupled with elastic net-based feature selection, we systematically compared the performance of models predicting the location of TAD boundaries (Gm12878 and K562 Hi-C data at 10kb to 100kb resolutions).
-Precision-Recall curves were found to be best suited for evaluating model performance in class imbalance settings.
-Random undersampling and SMOTE-resampled data performed best for optimal parameter selection.
-Transcription Factor Binding Sites (TFBSs) were the best type of genomic annotations for predicting TAD boundaries when directly compared with histone modifications and chromatin states; we identified well-known CTCF, SMC3, RAD21, and several novel TFBSs as best predictors of TAD boundaries.
-Importantly, spatial relationships (distance between TAD boundaries and genomic annotations) were best predictors of TAD boundaries as compared with commonly used overlap counts or percent overlap measures.
-
-**Conclusions.** Our results outline strategies for predictive modeling of 3D genomic domains using 1D genome annotation data.
-The accurate modeling of TAD boundaries will improve our understanding of how epigenetics shapes the 3D structure of the genome.
+**Conclusion** Our results outline strategies for predictive modeling of 3D genomic domains using 1D genome annotation data.
+The precise identification of TAD boundaries will improve our understanding of how epigenetics shapes the 3D structure of the genome.
 
@@
 
-Within this study we used both TAD boundary and loop boundary data derived from the publicly available tools ARROWHEAD [@durand2016juicebox] and PEAKACHU [@salameh2019supervised] respectively.
-ARROWHEAD TAD boundaries were called from primary Hi-C data from Geo GSE63525 [@rao20143d] for the GM12878 and K562 cell lines.
+Within this study we used both TAD boundary and loop boundary data derived from the publicly available tools Arrowhead [@durand2016juicebox] and Peakachu [???change to lowercase] [@salameh2019supervised] respectively.
+Arrowhead [???change to lowercase] TAD boundaries were called from primary Hi-C data from Geo GSE63525 [@rao20143d] for the GM12878 and K562 cell lines.
 The contact matrices were constructed from all read pairs that uniquely aligned to the genome (MAPQ>0).
-The default parameters for ARROWHEAD were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1).
-PEAKACHU chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab web site.
+The default parameters for Arrowhead were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1).
+Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab web site.
 Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop.
@@
 That is, between cell lines, the number of overlapping flanked boundaries divided by the total number of flanked boundaries.
-Wilcoxon Rank-Sum tests were used to compare chromosome-specific Jaccard indices across cell lines, between *preciseTAD* boundaries and both ARROWHEAD and PEAKACHU boundaries, respectively.
+Wilcoxon Rank-Sum tests were used to compare chromosome-specific Jaccard indices across cell lines, between *preciseTAD* boundaries and both Arrowhead and Peakachu boundaries, respectively.
 All statistical analyses were performed in R version 4.0.1.
@@
 To demonstrate, we applied our framework to publicly available replicate Hi-C data sets from the GM12878 and K562 cell lines obtained from GEO GSE63525 (Supplementary Table 1).
-TADs were subsequently called using the ARROWHEAD pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-For loops, we opted to use boundaries obtained by the PEAKACHU prediction tool for the GM12878 and K562 cell lines at 10 kb resolution [@salameh2019supervised].
+TADs were subsequently called using the Arrowhead pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
+For loops, we opted to use boundaries obtained by the Peakachu prediction tool for the GM12878 and K562 cell lines at 10 kb resolution [@salameh2019supervised].
 [???
@@
 For MD] [???
-Define that ARROWHEAD data constitute the main results.
+Define that Arrowhead data constitute the main results.
 For MD]
@@
 |:---------------------:|:-----------------:|:--------------------------------------------------:|:-----------------------------------------------------------:|:-----------------------------------:|:----------------------:|
-|        ARROWHEAD      |       5   kb      |                         8052                       |                             15468                           |                535363               |           0.03         |
-|     ARROWHEAD         |       10   kb     |                         7676                       |                             14253                           |                267682               |           0.05         |
-|     ARROWHEAD         |       25   kb     |                         4670                       |                             8363                            |                107073               |           0.08         |
-|     ARROWHEAD         |       50   kb     |                         2349                       |                             4224                            |                 53537               |           0.08         |
-|     ARROWHEAD         |      100   kb     |                         1031                       |                             1883                            |                 26768               |           0.07         |
-|        PEAKACHU       |       10   kb     |                        16185                       |                          21421                              |                267682               |        0.14            |
-Table: TAD/loop boundary data and class imbalance summaries across resolutions for ARROWHEAD and PEAKACHU on the GM12878 cell line.
+|        Arrowhead      |       5   kb      |                         8052                       |                             15468                           |                535363               |           0.03         |
+|     Arrowhead         |       10   kb     |                         7676                       |                             14253                           |                267682               |           0.05         |
+|     Arrowhead         |       25   kb     |                         4670                       |                             8363                            |                107073               |           0.08         |
+|     Arrowhead         |       50   kb     |                         2349                       |                             4224                            |                 53537               |           0.08         |
+|     Arrowhead         |      100   kb     |                         1031                       |                             1883                            |                 26768               |           0.07         |
+|        Peakachu       |       10   kb     |                        16185                       |                          21421                              |                267682               |        0.14            |
+Table: TAD/loop boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the GM12878 cell line.
 Class imbalance is calculated as the ratio of total number of unique boundaries to the total number of genomic bins.
@@
 As with class balancing techniques, this improvement was less evident at lower resolutions with results consistent for K562 (Supplementary Figure 2).
-Random forest models built on PEAKACHU-defined loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3).
+Random forest models built on Peakachu-defined loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3).
 Furthermore, 5 kb resolution genomic bins led to optimal prediction for both TAD and loop boundaries, on both cell lines.
@@
 
-![**Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for GM12878 ARROWHEAD TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+![**Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for GM12878 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
@@
 Having demonstrated the optimal performance in our framework's ability to predict boundary regions, we next attempted to predict boundary regions in one cell line when trained on another (See Methods).
-We found that training and testing using ARROWHEAD ground truth TAD boundaries and genomic elements from GM12878 resulted in an average AUC=0.845 (Figure 4D).
+We found that training and testing using Arrowhead ground truth TAD boundaries and genomic elements from GM12878 resulted in an average AUC=0.845 (Figure 4D).
 However when training on GM12878 and testing on K562, our model's average AUC only marginally decreased to 0.803.
-Likewise, training and testing on PEAKACHU resulted in an average AUC=0.885 and decreased only slightly to 0.868 when trained on GM12878 and tested on K562.
+Likewise, training and testing on Peakachu resulted in an average AUC=0.885 and decreased only slightly to 0.868 when trained on GM12878 and tested on K562.
 Results were consistent when training on K562 and testing on GM12878 (Supplementary Figure 4D).
@@
 
-![**Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+![**Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
@@
 
-Using our optimally built random forest model trained on ARROWHEAD/PEAKACHU boundaries, we attempted to predict TAD/loop boundaries at base resolution.
+Using our optimally built random forest model trained on Arrowhead/Peakachu boundaries, we attempted to predict TAD/loop boundaries at base resolution.
 Intuitively, the predictor-response space is built on a base-resolution level, and the model trained (using the optimal characteristics outlined above) on a bin-level space predicts the probability of each base being a boundary.
@@
 
-When built using ARROWHEAD and PEAKACHU ground truth boundaries at 5 kb and 10 kb respectively, *preciseTAD* was able to predict a total of 7846 TAD and 15838 chromatin loop boundaries on GM12878, as well as 8883 TAD and 11016 chromatin loop boundaries on K562.
-Noticeably, we reported less predicted TAD boundaries at 5 kb than ARROWHEAD on both cell lines (Table 1, Supplementary Table 2).
-This can be attributed to ARROWHEAD's inflation of called TADs, especially at higher resolutions, that often do not correspond to intra-chromosomal contacts featured on a contact matrix (Figure 1A).
-Likewise, ARROWHEAD often produces nested and overlapped TADs that do not have demarcated boundaries, further exacerbating this inflation.
+When built using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb respectively, *preciseTAD* was able to predict a total of 7846 TAD and 15838 chromatin loop boundaries on GM12878, as well as 8883 TAD and 11016 chromatin loop boundaries on K562.
+Noticeably, we reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Supplementary Table 2).
+This can be attributed to Arrowhead's inflation of called TADs, especially at higher resolutions, that often do not correspond to intra-chromosomal contacts featured on a contact matrix (Figure 1A).
+Likewise, Arrowhead often produces nested and overlapped TADs that do not have demarcated boundaries, further exacerbating this inflation.
 However, under the framework of *preciseTAD*, any two TADs are inherently conjoined by only one predicted TAD boundary, leading to comparatively less TAD boundaries.
@@
 This all may be for the discussion, if we have a good understanding why] Additionally, *preciseTAD* boundaries were visually more likely to demarcate high concentrations of intra-chromosomal contacts as can be seen on a Hi-C contact matrix (Figure 5A).
-*preciseTAD* also predicted fewer chromatin loop boundaries than PEAKACHU (Table 1, Supplementary Table 2).
-This can be contributed to the fact that *preciseTAD* leverages 4 known drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143, contrasting PEAKACHU which considers only CTCF sites.
+*preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Supplementary Table 2).
+This can be contributed to the fact that *preciseTAD* leverages 4 known drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143, contrasting Peakachu which considers only CTCF sites.
 This methodology likely leads to many more false positives, resulting in inflated number of chromatin loops.
@@
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
-Signal heatmaps indicated that our predicted boundaries were more enriched for CTCF sites than either ARROWHEAD or PEAKACHU boundaries alone (Figure 5 B-C).
+Signal heatmaps indicated that our predicted boundaries were more enriched for CTCF sites than either Arrowhead or Peakachu boundaries alone (Figure 5 B-C).
 Likewise, *preciseTAD* boundaries were also more enriched for other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 5-6).
-When compared to called TAD or loop boundaries, *preciseTAD* boundaries were found to be statistically significantly closer to the same cell line-specific top ranked TFBS (p<0.001 and p<0.001 versus ARROWHEAD and PEAKACHU respectively) (Figure 5D, Supplementary Figure 7).
+When compared to called TAD or loop boundaries, *preciseTAD* boundaries were found to be statistically significantly closer to the same cell line-specific top ranked TFBS (p<0.001 and p<0.001 versus Arrowhead and Peakachu respectively) (Figure 5D, Supplementary Figure 7).
 
@@
 TAD boundaries are known to be relatively conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
-To assess conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, ARROWHEAD, and PEAKACHU after flanking them by the resolution of the Hi-C data.
-Boundaries involving ARROWHEAD were flanked by 5 kb, while boundaries involving PEAKACHU were flanked by 10 kb.
-We found that 35% of *preciseTAD* predicted TAD boundaries and 55% of *preciseTAD* predicted loop boundaries were were conserved between cell lines, compared to only 26% and 55% for ARROWHEAD and PEAKACHU alone (Figure 5E) [???should I mention jaccard or scrap it?
+To assess conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, Arrowhead, and Peakachu after flanking them by the resolution of the Hi-C data.
+Boundaries involving Arrowhead were flanked by 5 kb, while boundaries involving Peakachu were flanked by 10 kb.
+We found that 35% of *preciseTAD* predicted TAD boundaries and 55% of *preciseTAD* predicted loop boundaries were were conserved between cell lines, compared to only 26% and 55% for Arrowhead and Peakachu alone (Figure 5E) [???should I mention jaccard or scrap it?
 significantly different for arrowhead but not peakachu].
@@
 <!--Additionally, the median Jaccard index (MJI) was found to be 0.472 (IQR=0.441-0.503; p=???) and 0.647 (IQR=0.646-0.647; p=???) for *preciseTAD* predicted TAD and loop boundaries (Supplementary Table 5).
-Comparatively, only 25% (MJI=0.284; IQR=0.268-0.301) and 49% (MJI=0.509; IQR=0.503-0.515) of called/predicted ARROWHEAD and Peakachu boundaries were conserved (Figure 6A, Supplementary Table 5).
+Comparatively, only 25% (MJI=0.284; IQR=0.268-0.301) and 49% (MJI=0.509; IQR=0.503-0.515) of called/predicted Arrowhead and Peakachu boundaries were conserved (Figure 6A, Supplementary Table 5).
 These results demonstrate that boundaries predicted using genomic annotations (*preciseTAD*) are better conserved across cell lines.-->
@@
 <!--We also inspected the effect of resolution on locations of our predicted TAD boundaries.
-We found that *preciseTAD* boundaries exhibited higher pairwise Jaccard indices between adjacent resolutions than ARROWHEAD boundaries, thus implying stronger invariance toward resolution (Figure 5E).-->
+We found that *preciseTAD* boundaries exhibited higher pairwise Jaccard indices between adjacent resolutions than Arrowhead boundaries, thus implying stronger invariance toward resolution (Figure 5E).-->
 
 ![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.**(A) The location of preciseTAD (green) vs.
-ARROWHEAD (blue) boundaries on GM12878 (chr 1: 70600000-71530000).
+Arrowhead (blue) boundaries on GM12878 (chr 1: 70600000-71530000).
 The black line represents the predicted probability of each base being a TAD boundary.
 A zoomed-in portion of the genome shows a yellow-highlighted cluster of bases with high probability of being a boundary, the preciseTAD boundary region (PTBR).
-(B) Enriched heatmaps comparing the enrichment of CTCF signal around ARROWHEAD TAD boundaries and preciseTAD boundaries, and (C) around Peakachu loop boundaries and preciseTAD for the entire genome.
+(B) Enriched heatmaps comparing the enrichment of CTCF signal around Arrowhead TAD boundaries and preciseTAD boundaries, and (C) around Peakachu loop boundaries and preciseTAD for the entire genome.
 (D) Log 2 genomic distances from boundaries to nearest CTCF sites.
-(E) Venn diagrams illustrating the levels of conservation between TAD/loop boundaries for GM12878 (red) and K562 (blue) identified by preciseTAD (using ARROWHEAD; top left), ARROWHEAD (top right), preciseTAD (using PEAKACHU; bottom left), and PEAKACHU (bottom right).
+(E) Venn diagrams illustrating the levels of conservation between TAD/loop boundaries for GM12878 (red) and K562 (blue) identified by preciseTAD (using Arrowhead; top left), Arrowhead (top right), preciseTAD (using Peakachu; bottom left), and Peakachu (bottom right).
 The median Jaccard Index (IQR) across each chromosome is provided below each venn diagram.](Figures/figure5.png)
@@
 
-The majority of boundaries predicted by the ARROWHEAD-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model.
+The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model.
 We found that 95.6% and 95.7% of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 8).
-This is expected as loop boundaries (PEAKACHU) are more abundant, while TAD boundaries (ARROWHEAD) represent the narrower level of the 3D chromatin organization.
-Together with the results shown on Figure 4, the high overlap between boundaries predicted by ARROWHEAD- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar protein complexes.
+This is expected as loop boundaries (Peakachu) are more abundant, while TAD boundaries (Arrowhead) represent the narrower level of the 3D chromatin organization.
+Together with the results shown on Figure 4, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar protein complexes.
 
@@
 *preciseTAD* leverages a random forest (RF) classification model built on ground truth TAD/loop boundaries obtained from a TAD/loop calling tools and ChIP-seq defined genomic annotations as the predictor space.
-We benchmarked *preciseTAD* against two boundary calling tools, ARROWHEAD [@durand2016juicebox], an established TAD-caller, and PEAKACHU [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
+We benchmarked *preciseTAD* against two boundary calling tools, Arrowhead [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
 We applied *preciseTAD* on cell line-specific boundaries and ChIP-seq data from both GM12878 and K562.
@@
 Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Supplementary Tables 4-5 [???
-Merge them into one Excel with two sheets - same message]).
+Merge them into one Excel with two sheets - same message]!!!will do when ready).
 Our aim was to have a balanced metric that was sensitive to class imbalance such that it would not favor one component of the confusion matrix.
@@
 Guided by both low-resolution Hi-C data and high-resolution genome annotation data, *preciseTAD* predicts base-level resolution boundaries, alleviating resolution limitations of Hi-C data.
-We show that, unlike ARROWHEAD, *preciseTAD* does not inflate the number of predicted boundaries, instead, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
+We show that, unlike Arrowhead, *preciseTAD* does not inflate the number of predicted boundaries, instead, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
 *preciseTAD* TAD and loop boundaries were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops are dynamic structures generated by similar mechanisms [@hansen2018recent].
@@
 As a heuristic, we evaluated the pairwise combination of 4 different thresholds ($t=(0.95,0.975,0.99,1.0)$) and 4 different $\epsilon$ values ($\epsilon=(0.2 r, 0.5r, r, 2r)$)), where $r=5000$, the optimal resolution.
-We found that $t=1.0$ and $\epsilon=r$ ensured that boundaries were at least 5kb bases away from each other, while also suitably enriched for architectural proteins (Supplementary Figures 9-10).
+We found that the normalized overlaps--calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries --between top TFBS sites and flanked preciseTAD boundaries were maximized for combinations of t=1.0 and eps=r (Supplementary Figure 9).
+The same heuristic ($t=1.0$ and $\epsilon=r$) ensured that boundaries were at least 5kb bases away from each other, while also suitably enriched for architectural proteins (Supplementary Figures 10-11).
 
@@
 **Additional File 1**.
-An example script for applying the ARROWHEAD tool to in situ Hi-C data (HIC001-HIC018) for resolutions 5kb, 10kb, 25kb, 50kb, 100kb to obtain chromosome-specific TAD boundaries on the GM12878 cell line.
+An example script for applying the Arrowhead tool to in situ Hi-C data (HIC001-HIC018) for resolutions 5kb, 10kb, 25kb, 50kb, 100kb to obtain chromosome-specific TAD boundaries on the GM12878 cell line.
 Prior to implementing SpectralTAD, the dump command offered by juicer [@durand2016juicer] was used to extract the contacts in sparse data matrix format.
 
-**Supplementary Table 1.** Data source for Hi-C matrices used to call topologically associated domains with ARROWHEAD, as well as loop boundaries obtained by Peakachu.
+**Supplementary Table 1.** Data source for Hi-C matrices used to call topologically associated domains with Arrowhead, as well as loop boundaries obtained by Peakachu.
 
-**Supplementary Table 2.** TAD/loop boundary data and class imbalance summaries across resolutions for ARROWHEAD and PEAKACHU on the k562 cell line.
+**Supplementary Table 2.** TAD/loop boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the k562 cell line.
 Class imbalance is calculated as the ratio of total number of unique boundaries to the total number of genomic bins.
@@
 **Supplementary Table 4.** Additional performance metrics when implementing a random forest using
-ARROWHEAD ground truth TAD boundaries. Performances are averaged across each holdout chromosome that was reserved for testing.
+Arrowhead ground truth TAD boundaries. Performances are averaged across each holdout chromosome that was reserved for testing.
 
 **Supplementary Table 5.** Additional performance metrics when implementing a random forest using
-PEAKACHU ground truth chromatin loop boundaries. Performances are averaged across each holdout chromosome that was reserved for testing.
+Peakachu ground truth chromatin loop boundaries. Performances are averaged across each holdout chromosome that was reserved for testing.
 
@@
 **Supplementary Figure 2.
-Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for K562 ARROWHEAD TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for K562 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.
@@
 **Supplementary Figure 3.
-Distance-type predictors combined with random under-sampling or SMOTE re-sampling yielded optimal predictive performance PEAKACHU loop boundaries at 10 kb resolution.** Averaged balanced accuracies are compared for A) GM12878 and B) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Distance-type predictors combined with random under-sampling or SMOTE re-sampling yielded optimal predictive performance Peakachu loop boundaries at 10 kb resolution.** Averaged balanced accuracies are compared for A) GM12878 and B) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.
@@
 **Supplementary Figure 4.
-Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (ARROWHEAD) and loop (PEAKACHU) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
@@
 **Supplementary Figure 5.
-preciseTAD boundaries are more enriched for known molecular drivers of 3D chromatin.** Enriched heatmaps comparing the enrichment of preciseTAD (green) boundaries with ARROWHEAD called TAD boundaries (blue) around key (A) GM12878-specific and (B) K562-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
+preciseTAD boundaries are more enriched for known molecular drivers of 3D chromatin.** Enriched heatmaps comparing the enrichment of preciseTAD (green) boundaries with Arrowhead called TAD boundaries (blue) around key (A) GM12878-specific and (B) K562-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
 
 **Supplementary Figure 6.
-preciseTAD boundaries are more enriched for known molecular drivers of 3D chromatin.** Enriched heatmaps comparing the enrichment of preciseTAD (green) boundaries with PEAKACHU predicted chromatin loop boundaries (blue) around key (A) GM12878-specific and (B) K562-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
+preciseTAD boundaries are more enriched for known molecular drivers of 3D chromatin.** Enriched heatmaps comparing the enrichment of preciseTAD (green) boundaries with Peakachu predicted chromatin loop boundaries (blue) around key (A) GM12878-specific and (B) K562-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
 
@@
 **Supplementary Figure 8.
-preciseTAD predicted TAD boundaries using ARROWHEAD are nested within preciseTAD predicted chromatin loop boundaries using PEAKACHU.** Venn diagrams illustrating the agreement between boundaries predicted using ARROWHEAD- and Peakachu-trained models.
-TAD/loop boundaries were flanked by resolution (5 kb for models using ARROWHEAD and 10 kb for PEAKACHU).
+preciseTAD predicted TAD boundaries using Arrowhead are nested within preciseTAD predicted chromatin loop boundaries using Peakachu.** Venn diagrams illustrating the agreement between boundaries predicted using Arrowhead- and Peakachu-trained models.
+TAD/loop boundaries were flanked by resolution (5 kb for models using Arrowhead and 10 kb for Peakachu).
 
-**Supplementary Figure 9**.
-Density plots illustrating the genomic distance (in bases) between predicted TAD boundaries identified by preciseTAD for different combinations of thresholds (t) and eps values ($\epsilon$) on GM12878.
+**Supplementary Figure 9.** Barplots illustrating the normalized overlap between known molecular drivers of 3D chromatin and flanked predicted TAD boundaries identified by preciseTAD (using Arrowhead ground truth boundaries) on GM12878 and for chromosome 22.
+Normalized overlap was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted (on chr22).
+Boundaries were flanked by 5 kb resolution.
+
+**Supplementary Figure 10.** Density plots illustrating the genomic distance (in bases) between predicted TAD boundaries identified by preciseTAD (using Arrowhead ground truth boundaries) for different combinations of thresholds (t) and epsilon parameter values (eps) on GM12878 and for chromosome 22.
 The median genomic distance (range) is provided for each combination.
 
-**Supplementary Figure 10**.
+**Supplementary Figure 11**.
 The formation of TADs (CHR22: 25mb-27mb) demarcated by boundaries predicted by preciseTAD for different combinations of thresholds (t) and eps values ($\epsilon$) on GM12878.

### 2020-08-06 Scripts_for_results/14_evaluating_preciseTAD_parameters.Rmd
initial commit

---
title: "Evaluating preciseTAD parameters"
author: "Spiro Stilianoudakis"
date: "8/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(GenomicRanges)
library(ggplot2)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

# Extracting boundaries for juicer

```{r}
juicer_func <- function(grdat){
  #n <- length(unique(as.character(seqnames(grdat))))

  chrs <- unique(as.character(seqnames(grdat)))

  mat_list <- list()

  for(i in 1:length(chrs)){
    grdat_chr <- grdat[which(as.character(seqnames(grdat))==chrs[i])]

    if(length(grdat_chr)>1){
      mymat <- matrix(nrow=(length(grdat_chr)-1),
                      ncol=6)
      mymat[,1] <- mymat[,4] <- chrs[i]
      for(j in 1:(length(grdat_chr)-1)){
        mymat[j,2] <- mymat[j,5] <- start(grdat_chr)[j]
        mymat[j,3] <- mymat[j,6] <- start(grdat_chr)[j+1]
      }

      mat_list[[i]] <- mymat

    }

  }

  mat_list <- do.call("rbind",mat_list)
  return(mat_list)

}

```

## Chromosome 22

### t=1

#### e=1000

```{r}
pt_1_1000_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_1_1000_22.rds")

length(pt_1_1000_22[[2]]) #447
length(pt_1_1000_22[[3]]) #306

pt_1_1000_22_juicer <- juicer_func(pt_1_1000_22[[2]])
write.table(pt_1_1000_22_juicer, 
            "C:/Users/stili/Downloads/pt_1_1000_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")

arrowhead_22_juicer <- juicer_func(pt_1_1000_22[[3]])
write.table(arrowhead_22_juicer, 
            "C:/Users/stili/Downloads/arrowhead_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

#### e=2500

```{r}
pt_1_2500_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_1_2500_22.rds")

length(pt_1_2500_22[[2]]) #351
length(pt_1_2500_22[[3]]) #306

pt_1_2500_22_juicer <- juicer_func(pt_1_2500_22[[2]])
write.table(pt_1_2500_22_juicer, 
            "C:/Users/stili/Downloads/pt_1_2500_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

#### e=5000

```{r}
pt_1_5000_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_1_5000_22.rds")
#pt_1_5000_22_o <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")

length(pt_1_5000_22[[2]]) #247
#length(pt_1_5000_22_o[[2]]) #119
length(pt_1_5000_22[[3]]) #306

pt_1_5000_22_juicer <- juicer_func(pt_1_5000_22[[2]])
write.table(pt_1_5000_22_juicer, 
            "C:/Users/stili/Downloads/pt_1_5000_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")

#pt_1_5000_22_juicer_o <- juicer_func(pt_1_5000_22_o[[2]])
#write.table(pt_1_5000_22_juicer_o, 
#            "C:/Users/stili/Downloads/pt_1_5000_22_juicer_o.bed",
#            quote = FALSE,
#            col.names = FALSE,
#            row.names = FALSE,
#            sep = "\t")
```

#### e=10000

```{r}
pt_1_10000_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_1_10000_22.rds")

length(pt_1_10000_22[[2]]) #226
length(pt_1_10000_22[[3]]) #306

pt_1_10000_22_juicer <- juicer_func(pt_1_10000_22[[2]])
write.table(pt_1_10000_22_juicer, 
            "C:/Users/stili/Downloads/pt_1_10000_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

### t=.99

#### e=1000

```{r}
pt_99_1000_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_99_1000_22.rds")

length(pt_99_1000_22[[2]]) #
length(pt_99_1000_22[[3]]) #306

pt_99_1000_22_juicer <- juicer_func(pt_99_1000_22[[2]])
write.table(pt_99_1000_22_juicer, 
            "C:/Users/stili/Downloads/pt_99_1000_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

#### e=2500

```{r}
pt_99_2500_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_99_2500_22.rds")

length(pt_99_2500_22[[2]]) #486
length(pt_99_2500_22[[3]]) #306

pt_99_2500_22_juicer <- juicer_func(pt_99_2500_22[[2]])
write.table(pt_99_2500_22_juicer, 
            "C:/Users/stili/Downloads/pt_99_2500_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

#### e=5000

```{r}
pt_99_5000_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_99_5000_22.rds")

length(pt_99_5000_22[[2]]) #368
length(pt_99_5000_22[[3]]) #306

pt_99_5000_22_juicer <- juicer_func(pt_99_5000_22[[2]])
write.table(pt_99_5000_22_juicer, 
            "C:/Users/stili/Downloads/pt_99_5000_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

#### e=10000

```{r}
pt_99_10000_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_99_10000_22.rds")

length(pt_99_10000_22[[2]]) #299
length(pt_99_10000_22[[3]]) #306

pt_99_10000_22_juicer <- juicer_func(pt_99_10000_22[[2]])
write.table(pt_99_10000_22_juicer, 
            "C:/Users/stili/Downloads/pt_99_10000_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

### t=.975

#### e=1000

```{r}
pt_975_1000_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_975_1000_22.rds")

length(pt_975_1000_22[[2]]) #
length(pt_975_1000_22[[3]]) #306

pt_975_1000_22_juicer <- juicer_func(pt_975_1000_22[[2]])
write.table(pt_975_1000_22_juicer, 
            "C:/Users/stili/Downloads/pt_975_1000_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

#### e=2500

```{r}
pt_975_2500_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_975_2500_22.rds")

length(pt_975_2500_22[[2]]) #599
length(pt_975_2500_22[[3]]) #306

pt_975_2500_22_juicer <- juicer_func(pt_975_2500_22[[2]])
write.table(pt_975_2500_22_juicer, 
            "C:/Users/stili/Downloads/pt_975_2500_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

#### e=5000

```{r}
pt_975_5000_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_975_5000_22.rds")

length(pt_975_5000_22[[2]]) #418
length(pt_975_5000_22[[3]]) #306

pt_975_5000_22_juicer <- juicer_func(pt_975_5000_22[[2]])
write.table(pt_975_5000_22_juicer, 
            "C:/Users/stili/Downloads/pt_975_5000_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

#### e=10000

```{r}
pt_975_10000_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_975_10000_22.rds")

length(pt_975_10000_22[[2]]) #312
length(pt_975_10000_22[[3]]) #306

pt_975_10000_22_juicer <- juicer_func(pt_975_10000_22[[2]])
write.table(pt_975_10000_22_juicer, 
            "C:/Users/stili/Downloads/pt_975_10000_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

### t=.95

#### e=1000

```{r}
#pt_95_1000_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/t_95_1000_22.rds")

#length(pt_95_1000_22[[2]]) #
#length(pt_95_1000_22[[3]]) #306

#pt_95_1000_22_juicer <- juicer_func(pt_95_1000_22[[2]])
#write.table(pt_95_1000_22_juicer, 
#            "C:/Users/stili/Downloads/pt_95_1000_22_juicer.bed",
#            quote = FALSE,
#            col.names = FALSE,
#            row.names = FALSE,
#            sep = "\t")
```

#### e=2500

```{r}
pt_95_2500_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_95_2500_22.rds")

length(pt_95_2500_22[[2]]) #636
length(pt_95_2500_22[[3]]) #306

pt_95_2500_22_juicer <- juicer_func(pt_95_2500_22[[2]])
write.table(pt_95_2500_22_juicer, 
            "C:/Users/stili/Downloads/pt_95_2500_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

#### e=5000

```{r}
pt_95_5000_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_95_5000_22.rds")

length(pt_95_5000_22[[2]]) #396
length(pt_95_5000_22[[3]]) #306

pt_95_5000_22_juicer <- juicer_func(pt_95_5000_22[[2]])
write.table(pt_95_5000_22_juicer, 
            "C:/Users/stili/Downloads/pt_95_5000_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

#### e=10000

```{r}
pt_95_10000_22 <- readRDS("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/pt_95_10000_22.rds")

length(pt_95_10000_22[[2]]) #298
length(pt_95_10000_22[[3]]) #306

pt_95_10000_22_juicer <- juicer_func(pt_95_10000_22[[2]])
write.table(pt_95_10000_22_juicer, 
            "C:/Users/stili/Downloads/pt_95_10000_22_juicer.bed",
            quote = FALSE,
            col.names = FALSE,
            row.names = FALSE,
            sep = "\t")
```

# Plotting density of distances between boundaries

```{r}
dist_dens <- data.frame(Distance = c(diff(start(pt_1_1000_22[[2]]))[-which(diff(start(pt_1_1000_22[[2]]))>2000000)],
                                     diff(start(pt_1_2500_22[[2]]))[-which(diff(start(pt_1_2500_22[[2]]))>2000000)],
                                     diff(start(pt_1_5000_22[[2]]))[-which(diff(start(pt_1_5000_22[[2]]))>2000000)],
                                     diff(start(pt_1_10000_22[[2]]))[-which(diff(start(pt_1_10000_22[[2]]))>2000000)],
                                     diff(start(pt_99_1000_22[[2]])),
                                     diff(start(pt_99_2500_22[[2]])),
                                     diff(start(pt_99_5000_22[[2]])),
                                     diff(start(pt_99_10000_22[[2]])),
                                     diff(start(pt_975_1000_22[[2]])),
                                     diff(start(pt_975_2500_22[[2]])),
                                     diff(start(pt_975_5000_22[[2]]))[-which(diff(start(pt_975_5000_22[[2]]))>2000000)],
                                     diff(start(pt_975_10000_22[[2]]))[-which(diff(start(pt_975_10000_22[[2]]))>2000000)],
                                     #diff(start(pt_95_1000_22[[2]]))[-which(diff(start(pt_95_1000_22[[2]]))>2000000)],
                                     diff(start(pt_95_2500_22[[2]])),
                                     diff(start(pt_95_5000_22[[2]])),
                                     diff(start(pt_95_10000_22[[2]]))),
                        Threshold = c(rep("t=1.0", length(diff(start(pt_1_1000_22[[2]]))[-which(diff(start(pt_1_1000_22[[2]]))>2000000)])+
                                        length(diff(start(pt_1_2500_22[[2]]))[-which(diff(start(pt_1_2500_22[[2]]))>2000000)])+
                                        length(diff(start(pt_1_5000_22[[2]]))[-which(diff(start(pt_1_5000_22[[2]]))>2000000)])+
                                        length(diff(start(pt_1_10000_22[[2]]))[-which(diff(start(pt_1_10000_22[[2]]))>2000000)])),
                                      rep("t=0.99", length(diff(start(pt_99_1000_22[[2]])))+
                                        length(diff(start(pt_99_2500_22[[2]])))+
                                        length(diff(start(pt_99_5000_22[[2]])))+
                                        length(diff(start(pt_99_10000_22[[2]])))),
                                      rep("t=0.975", length(diff(start(pt_975_1000_22[[2]])))+
                                        length(diff(start(pt_975_2500_22[[2]])))+
                                        length(diff(start(pt_975_5000_22[[2]]))[-which(diff(start(pt_975_5000_22[[2]]))>2000000)])+
                                        length(diff(start(pt_975_10000_22[[2]]))[-which(diff(start(pt_975_10000_22[[2]]))>2000000)])),
                                      rep("t=0.95", #length(diff(start(pt_95_1000_22[[2]]))[-which(diff(start(pt_95_1000_22[[2]]))>2000000)])+
                                        length(diff(start(pt_95_2500_22[[2]])))+
                                        length(diff(start(pt_95_5000_22[[2]])))+
                                        length(diff(start(pt_95_10000_22[[2]]))))),
                        Epsilon = c(rep("eps=0.2r", length(diff(start(pt_1_1000_22[[2]]))[-which(diff(start(pt_1_1000_22[[2]]))>2000000)])),
                                    rep("eps=0.5r", length(diff(start(pt_1_2500_22[[2]]))[-which(diff(start(pt_1_2500_22[[2]]))>2000000)])),
                                    rep("eps=r", length(diff(start(pt_1_5000_22[[2]]))[-which(diff(start(pt_1_5000_22[[2]]))>2000000)])),
                                    rep("eps=2r", length(diff(start(pt_1_10000_22[[2]]))[-which(diff(start(pt_1_10000_22[[2]]))>2000000)])),
                                    rep("eps=0.2r", length(diff(start(pt_99_1000_22[[2]])))),
                                    rep("eps=0.5r", length(diff(start(pt_99_2500_22[[2]])))),
                                    rep("eps=r", length(diff(start(pt_99_5000_22[[2]])))),
                                    rep("eps=2r", length(diff(start(pt_99_10000_22[[2]])))),
                                    rep("eps=0.2r", length(diff(start(pt_975_1000_22[[2]])))),
                                    rep("eps=0.5r", length(diff(start(pt_975_2500_22[[2]])))),
                                    rep("eps=r", length(diff(start(pt_975_5000_22[[2]]))[-which(diff(start(pt_975_5000_22[[2]]))>2000000)])),
                                    rep("eps=2r", length(diff(start(pt_975_10000_22[[2]]))[-which(diff(start(pt_975_10000_22[[2]]))>2000000)])),
                                    #rep("eps=0.2r", length(diff(start(pt_95_1000_22[[2]]))[-which(diff(start(pt_95_1000_22[[2]]))>2000000)])),
                                    rep("eps=0.5r", length(diff(start(pt_95_2500_22[[2]])))),
                                    rep("eps=r", length(diff(start(pt_95_5000_22[[2]])))),
                                    rep("eps=2r", length(diff(start(pt_95_10000_22[[2]]))))))

dist_dens$Epsilon <- factor(dist_dens$Epsilon, levels=c("eps=0.2r",
                                                        "eps=0.5r",
                                                        "eps=r",
                                                        "eps=2r"))

ggplot(data=dist_dens, aes(x=Distance)) +
  facet_grid(Epsilon ~ Threshold) +
  geom_density(fill="gray", color="black", alpha=0.8) +
  ylab("Density") +
  xlab("Distance between predicted TAD boundaries") +
  theme_minimal() +
  theme_bw()+
  theme(axis.text.x = element_text(size=10,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background.x = element_blank(),
        #strip.background.y = element_blank(),
        legend.text=element_text(size=10),
        legend.title=element_text(size=15),
        plot.title = element_text(size=15))
```

# Overlaps per boundaries

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
                                             pattern="*.bed",
											 signal=4)

df <- data.frame(Overlap = c(length(unique(subjectHits(findOverlaps(flank(pt_1_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_1_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_1_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_1_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_1_10000_22[[2]])-.1,

length(unique(subjectHits(findOverlaps(flank(pt_99_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_99_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_99_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_99_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_99_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_975_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_975_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_975_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_975_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_975_10000_22[[2]]),

NA,
length(unique(subjectHits(findOverlaps(flank(pt_95_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_95_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_95_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_95_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_1_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_1_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_1_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_1_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_1_10000_22[[2]])-.1,

length(unique(subjectHits(findOverlaps(flank(pt_99_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_99_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_99_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_99_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_99_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_975_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_975_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_975_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_975_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_975_10000_22[[2]]),

NA,
length(unique(subjectHits(findOverlaps(flank(pt_95_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_95_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_95_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_95_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_1_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_1_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_1_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_1_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_1_10000_22[[2]])-.1,

length(unique(subjectHits(findOverlaps(flank(pt_99_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_99_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_99_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_99_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_99_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_975_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_975_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_975_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_975_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_975_10000_22[[2]]),

NA,
length(unique(subjectHits(findOverlaps(flank(pt_95_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_95_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_95_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_95_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_1_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_1_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_1_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_1_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_1_10000_22[[2]])-.1,

length(unique(subjectHits(findOverlaps(flank(pt_99_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_99_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_99_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_99_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_99_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_975_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_975_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_975_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_975_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_975_10000_22[[2]]),

NA,
length(unique(subjectHits(findOverlaps(flank(pt_95_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_95_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_95_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_95_10000_22[[2]])),

Threshold = c(rep(c(rep("t=1.0",4),
              rep("t=0.99",4),
              rep("t=0.975",4),
              rep("t=0.95",4)),4)),

Epsilon = rep(c("eps=1000",
              "eps=2500",
			  "eps=5000",
			  "eps=10000"),16),

Annotation = c(rep("CTCF", 16),
               rep("RAD21", 16),
			   rep("SMC3", 16),
			   rep("ZNF143", 16))
)

df$Epsilon <- factor(df$Epsilon, levels=c("eps=1000", "eps=2500", "eps=5000", "eps=10000"))

ggplot(data=df, aes(x=Annotation, y=Overlap, fill=Annotation)) +
  facet_grid(Epsilon ~ Threshold) +
  geom_bar(stat='identity') +
  ylim(0,1.5)+
  ylab("Normalized Overlap") +
  xlab("Annotation") +
  guides(fill=FALSE) +
  theme_minimal() +
  theme_bw()+
  theme(axis.text.x = element_text(size=10,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background.x = element_blank(),
        #strip.background.y = element_blank(),
        legend.text=element_text(size=10),
        legend.title=element_text(size=15),
        plot.title = element_text(size=15))
```

### 2020-08-07 Manuscript/manuscript.Rmd
First shot on Abstract

@@
 
-# ABSTRACT (Spiro version)
+# ABSTRACT
 
-**Background** Chromosome conformation capture combined with high-throughput sequencing experiments (Hi-C) have revealed that chromatin undergoes layers of compaction through DNA looping and folding, forming dynamic 3D structures.
-Among these are Topologically Associated Domains (TADs), which are known to play critical roles in cell dynamics like gene regulation and cell differentiation.
-Precise TAD mapping remains difficult, as it is strongly reliant on Hi-C data resolution.
-Obtaining genome-wide chromatin interactions at high-resolution is costly resulting in variability in true TAD boundary location by conventional TAD calling algorithms.
+**Background** High-throughput chromosome conformation capture technology (Hi-C) has revealed extensive DNA looping and folding into discrete 3D domains.
+Among these are Topologically Associated Domains (TADs) and chromatin loops, which are known to play critical roles in cell dynamics like gene regulation and cell differentiation.
+The relatively low resolution of Hi-C data (regions of several kilobases in size) prevents precise mapping of domain boundaries.
+TAD and loop boundaries have been characterized by the presence of CTCF and members of cohesin complex binding sites, typically mapped at higher precision.
+Several methods have been developed to leverage genome annotation  data for predicting TAD/loop boundaries; however, they overlooked key characteristics of the data, such as spatial associations between an annotation and a boundary.
+Furthermore, the number of regions containing boundaries is much smaller than the rest of the genome, creating a class imbalance problem.
 
-**Methods** To aid in the precise identification of TAD boundaries we developed preciseTAD, a random forest based framework that leverages the spatial relationship of high resolution ChIP-seq defined genomic elements, coupled with density-based clustering and scalable partitioning techniques.
-We benchmarked our method against a popular TAD-caller and a novel chromatin loop prediction algorithm on multiple cell lines.
+**Methods** To improve the detection of domain boundaries, we developed preciseTAD, a random forest-based framework that leverages high-resolution genome annotation data coupled with density-based clustering and scalable partitioning techniques.
+We utilized several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) to investigate class imbalance.
+We benchmarked our method against Arrowhead TAD caller and a novel chromatin loop prediction algorithm, Peakachu, on multiple cell lines.
 
-**Results** We show that our framework performs well when predicting both TAD and chromatin loop boundaries.
-Compared to established techniques, boundaries predicted by preciseTAD are more enriched for CTCF, RAD21, SMC3, and ZNF143 sites.
-Likewise, preciseTAD boundaries were more conserved across cell lines, highlighting their biological significance.
+**Results** Using different feature engineering and resampling strategies, we found spatial relationships between boundaries and annotations have the most predictive power.
+Transcription factor binding sites outperformed other genome annotation types.
+Random under-sampling significantly improved model performance.
+Boundaries predicted by preciseTAD were more enriched for nearby CTCF, RAD21, SMC3, and ZNF143 sites and more conserved across cell lines, highlighting their higher biological significance.
 
-**Conclusion** Our results outline strategies for predictive modeling of 3D genomic domains using 1D genome annotation data.
-The precise identification of TAD boundaries will improve our understanding of how epigenetics shapes the 3D structure of the genome.
+**Conclusion** Our results outline strategies for predictive modeling of 3D genomic domains using genome annotation data.
+Our method is implemented as a preciseTAD R package (Bioconductor URL).
+The precise identification of TAD boundaries will improve our understanding of how epigenomics shapes the 3D structure of the genome.
 

### 2020-08-07 Manuscript/manuscript.Rmd
Concluding paragraph polishing

@@
 Here we present *preciseTAD*, an R package for precise identification of TAD(or loop) boundaries under a supervised machine learning (ML) framework.
-Our method builds upon an optimized random forest (RF) classification model that leverages high resolution ChIP-seq data in the form of regulatory elements (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS).
-We introduce a novel technique for building RF classifiers in a boundary prediction setting composed of a resolution-specific binning process and feature engineering procedure.
-*preciseTAD* then employs density-based clustering (DBSCAN) and scalable partitioning around medoids (CLARA) on prediction probabilities to select the most biologically meaningful boundary coordinates on the linear genome, thereby circumventing resolution restrictions of conventional TAD- and chromatin loop-callers.
+Our method builds upon an optimized random forest (RF) classification model that leverages high resolution genome annotation data in the form of chromatin segmentation (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS).
+We introduce a novel pipeline for building optimal boundary prediction classifier composed of a resolution-specific binning process and feature engineering procedure.
+We found that spatial associations between boundaries and annotations perform best, transcription factor binding sites further improve prediction accuracy, and a simple random undersampling technique effectively addresses the negative effect of class imbalance.
+Translated from Hi-C data resolution level to base level, *preciseTAD* employs density-based clustering (DBSCAN) and scalable partitioning around medoids (CLARA) on prediction probabilities to select the most biologically meaningful boundary coordinates, thereby circumventing resolution restrictions of conventional TAD- and chromatin loop-callers.
 We demonstrate that predictions made by *preciseTAD* are more enriched for known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143.
 Further, we show that *preciseTAD* boundaries are more conserved across cell lines, highlighting their biological significance.
-This improved precision in TAD and loop boundary location can provide insight into the role that epigenomics has on the spatial architecture of the human genome.
-[???
-Rewrite.
-Say the main methodology first - model on 4 TFBSs, uses distance, RUS, technique for bp-level prediction, one sentence per point.
-Detail next - BroadHMM and histone were tested, OC, OP were tested, various sampling techniques.
-Conclude with findings and package availability.
-For MD, last part when ready to write an abstract]
+This improved precision in TAD and loop boundary location can provide insight into the role that epigenomics has on the 3D architecture of the human genome.
 

### 2020-08-07 Manuscript/manuscript.Rmd
Removing most ???

@@
 
-Within this study we used both TAD boundary and loop boundary data derived from the publicly available tools Arrowhead [@durand2016juicebox] and Peakachu [???change to lowercase] [@salameh2019supervised] respectively.
-Arrowhead [???change to lowercase] TAD boundaries were called from primary Hi-C data from Geo GSE63525 [@rao20143d] for the GM12878 and K562 cell lines.
+Within this study we used both TAD boundary and loop boundary data derived from the publicly available tools Arrowhead [@durand2016juicebox] and Peakachu [@salameh2019supervised] respectively.
+Arrowhead TAD boundaries were called from primary Hi-C data from Geo GSE63525 [@rao20143d] for the GM12878 and K562 cell lines.
 The contact matrices were constructed from all read pairs that uniquely aligned to the genome (MAPQ>0).
@@
 
-We developed a machine learning (ML) framework aimed at determining the optimal set of data level characteristics necessary for topologically associated domain (TAD) boundary prediction.
+We developed a machine learning (ML) framework aimed at determining the optimal set of data level characteristics necessary for precise prediction of boundaries of Topologically Associated Domains (TADs) and chromatin loops, collectively referred to as domain boundaries.
 We chose the random forest (RF) algorithm as our binary classification tool.
 The reason being two-fold: (1) In order to devise a tunable prediction rule in a supervised learning framework that is both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors [@boulesteix2012overview].
-We extended our method and developed *preciseTAD*, an algorithm which leverages an optimally built RF to precisely predict the genomic coordinates of both TAD and chromatin loop boundaries at base resolution.
+We extended our method and developed *preciseTAD*, an R package which leverages an optimally built RF to precisely predict the genomic coordinates of TAD and loop boundaries at base resolution.
 
-We use called TAD or loop boundaries as ground truth to establish TAD(loop)-boundary and non-TAD(loop) boundary regions.
-To demonstrate, we applied our framework to publicly available replicate Hi-C data sets from the GM12878 and K562 cell lines obtained from GEO GSE63525 (Supplementary Table 1).
-TADs were subsequently called using the Arrowhead pipeline from the juicer toolbox [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb.
-For loops, we opted to use boundaries obtained by the Peakachu prediction tool for the GM12878 and K562 cell lines at 10 kb resolution [@salameh2019supervised].
-[???
-TAD and loop boundaries should be distinguished, to describe when we have all results.
-For MD] [???
-Define that Arrowhead data constitute the main results.
-For MD]
+We use published Arrowhead-called TAD boundaries [@durand2016juicer] and Peakachu-predicted loop boundaries [@salameh2019supervised] as ground truth.
+Data from GM12878 and K565 cell lines at 5-100kb resolution (Arrowhead) and 10kb resolution (Peakachu) were used (Supplementary Table 1).
 
@@
 Results were consistent when training on K562 and testing on GM12878 (Supplementary Figure 4D).
-[???need concluding sentence]
+These results suggest that a classifier trained on the data from one cell line performs well when using data from another cell line.
 
@@
 This can be attributed to Arrowhead's inflation of called TADs, especially at higher resolutions, that often do not correspond to intra-chromosomal contacts featured on a contact matrix (Figure 1A).
-Likewise, Arrowhead often produces nested and overlapped TADs that do not have demarcated boundaries, further exacerbating this inflation.
-However, under the framework of *preciseTAD*, any two TADs are inherently conjoined by only one predicted TAD boundary, leading to comparatively less TAD boundaries.
+<!--Likewise, Arrowhead often produces nested and overlapped TADs that do not have demarcated boundaries, further exacerbating this inflation.
+However, under the framework of *preciseTAD*, any two domains are inherently conjoined by only one predicted boundary, leading to comparatively less TAD boundaries.
 [???
@@
 May it be too stringent thresholds?
-This all may be for the discussion, if we have a good understanding why] Additionally, *preciseTAD* boundaries were visually more likely to demarcate high concentrations of intra-chromosomal contacts as can be seen on a Hi-C contact matrix (Figure 5A).
+This all may be for the discussion, if we have a good understanding why] -->Additionally, *preciseTAD* boundaries were visually more likely to demarcate high concentrations of intra-chromosomal contacts as can be seen on a Hi-C contact matrix (Figure 5A).
 *preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Supplementary Table 2).
@@
 Boundaries involving Arrowhead were flanked by 5 kb, while boundaries involving Peakachu were flanked by 10 kb.
-We found that 35% of *preciseTAD* predicted TAD boundaries and 55% of *preciseTAD* predicted loop boundaries were were conserved between cell lines, compared to only 26% and 55% for Arrowhead and Peakachu alone (Figure 5E) [???should I mention jaccard or scrap it?
-significantly different for arrowhead but not peakachu].
+We found that 35% of *preciseTAD* predicted TAD boundaries and 55% of *preciseTAD* predicted loop boundaries were were conserved between cell lines, compared to only 26% and 55% for Arrowhead and Peakachu alone (Figure 5E).
 
@@
 We showed that information about only four transcription factors (SMC3, Rad21, CTCF, Znf143) is necessary and sufficient for accurate boundary prediction, outperforming histone modification- and BroadHMM-built models [@Moore:2015aa; @Al-Bkhetan:2018aa].
-These are known components of the loop extrusion model, an established theory for how loops are made by a ring-shaped adenosine triphosphatase complex called cohesin [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
+These are known components of the loop extrusion model, an established theory for how loops are made by a ring-shaped adenosine triphosphatase complex called cohesin [@hansen2018recent; @sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
 Interestingly, the same transcription factors accurately predicted both TAD and loop boundaries, suggesting similarity of the mechanisms of TAD and loop formation.
-Although our observations contradict a previous study showing histone marks alone were effective in predicting TAD boundaries [@huang2015predicting], our findings are backed by a large body of literature [???
+<!--Although our observations contradict a previous study showing histone marks alone were effective in predicting TAD boundaries [@huang2015predicting], our findings are backed by a large body of literature [???
 Add REFs].
-This suggested that the random forest model, when tuned and feature engineered correctly, is highly effective in predicting boundary regions.
+-->This suggested that the random forest model, when tuned and feature engineered correctly, is highly effective in predicting domain boundaries.
 
-Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Supplementary Tables 4-5 [???
-Merge them into one Excel with two sheets - same message]!!!will do when ready).
+Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC).
 Our aim was to have a balanced metric that was sensitive to class imbalance such that it would not favor one component of the confusion matrix.
@@
 Lastly, AUPRC is insensitive toward class imbalance and also omits from its calculation TN values [???
-So why didn't you use it?
-for MD].
+So why didn't you use it?].
 All of these are important considerations to make when choosing a performance metric.
@@
 *preciseTAD* TAD and loop boundaries were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops are dynamic structures generated by similar mechanisms [@hansen2018recent].
-[???
-So what?].
 Likewise *preciseTAD* boundaries were found to be more conserved between GM12878 and K562 cell lines, a known feature among the 3D architecture of the human genome, further highlighting their biological significance [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
-[???
-So what?]
 
@@
 Furthermore, actively transcribed regions can serve as TAD boundaries themselves, independently of CTCF binding [@Harrold:2020aa].
-This may lead to high proportion of TAD boundaries being undetected by *preciseTAD* despite being detected by TAD callers [???
-What is the false positive rate?
-We may be missing TADs that are distinct from the canonical CTCF boundaries.
-TBD; !!!discuss in meeting].
+This may lead to some TAD boundaries being undetected by *preciseTAD* despite being detected by TAD callers.
 Our future work will include defining separate models trained on different TAD boundary types, and predicting precise locations for each of them.

### 2020-08-08 Manuscript/manuscript.Rmd
Abstract and Intro polishing

@@
 **Background** High-throughput chromosome conformation capture technology (Hi-C) has revealed extensive DNA looping and folding into discrete 3D domains.
-Among these are Topologically Associated Domains (TADs) and chromatin loops, which are known to play critical roles in cell dynamics like gene regulation and cell differentiation.
+Among these are Topologically Associated Domains (TADs) and chromatin loops, known to play critical roles in cellular processes like gene regulation and cell differentiation.
 The relatively low resolution of Hi-C data (regions of several kilobases in size) prevents precise mapping of domain boundaries.
@@
 **Methods** To improve the detection of domain boundaries, we developed preciseTAD, a random forest-based framework that leverages high-resolution genome annotation data coupled with density-based clustering and scalable partitioning techniques.
-We utilized several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) to investigate class imbalance.
-We benchmarked our method against Arrowhead TAD caller and a novel chromatin loop prediction algorithm, Peakachu, on multiple cell lines.
+We investigated several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) to address class imbalance.
+We benchmarked our method against Arrowhead domain caller and a novel chromatin loop prediction algorithm, Peakachu, on multiple cell lines.
 
-**Results** Using different feature engineering and resampling strategies, we found spatial relationships between boundaries and annotations have the most predictive power.
+**Results** Using different feature engineering and resampling strategies, we found spatial relationships (distance) between boundaries and annotations have the most predictive power.
 Transcription factor binding sites outperformed other genome annotation types.
 Random under-sampling significantly improved model performance.
-Boundaries predicted by preciseTAD were more enriched for nearby CTCF, RAD21, SMC3, and ZNF143 sites and more conserved across cell lines, highlighting their higher biological significance.
+Boundaries predicted by preciseTAD were more enriched for CTCF, RAD21, SMC3, and ZNF143 sites and more conserved across cell lines, highlighting their higher biological significance.
 
 **Conclusion** Our results outline strategies for predictive modeling of 3D genomic domains using genome annotation data.
-Our method is implemented as a preciseTAD R package (Bioconductor URL).
-The precise identification of TAD boundaries will improve our understanding of how epigenomics shapes the 3D structure of the genome.
+The precise identification of TAD boundaries will improve our understanding of how genomic regulators shapes the 3D structure of the genome.
+
+**Availability.** Our method is implemented as an R package, *preciseTAD*, available on https://github.com/dozmorovlab/preciseTAD and Bioconductor (submitted).
 
@@
 At kilobase scale, gene promoters are often connected via distal regulatory elements, such as enhancers, through chromatin loops, thereby regulating gene expression [@Lupianez:2015aa; @Franke:2016aa].
-Further out, at the megabase scale, TADs represent regions on the linear genome, that are highly self-interacting.
+Further, at the megabase scale, TADs represent regions on the linear genome, that are highly self-interacting.
 Emerging evidence has linked TADs to critical roles in cell dynamics and cell differentiation.
 Studies have shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
-Likewise, disruption of the boundaries that demarcate TADs and loops have been shown to lead to cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@lupianez2016breaking;@Sun:2018aa;@Meaburn:2007aa].
+Likewise, disruption of boundaries demarcating TADs and loops promotes cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@lupianez2016breaking;@Sun:2018aa;@Meaburn:2007aa].
 Therefore, precisely identifying the location of TAD and chromatin loop boundaries remains a top priority in our goal to fully understand the functionality of the human genome.
 
-Several methods have been proposed to identify the genomic coordinates of TAD boundaries (reviewed in [@Zufferey:2018aa; @forcato2017comparison]), less so for chromatin loops [@rao20143d; @Ay:2014aa; @Heinz:2010aa; @salameh2019supervised].
-However, a key limitation among most of these TAD- and loop callers, referred hereafter as TAD callers for brevity, is that they are heavily reliant on Hi-C data *resolution*.
-Resolution refers to the sizes of genomic bins used to segment the linear genome as a way to deal with low signal-to-noise incurred by the high dimensional nature of Hi-C data [@li2019comparison].
+Several methods have been proposed to identify the genomic coordinates of TAD boundaries (reviewed in [@Zufferey:2018aa; @forcato2017comparison]), and chromatin loops [@rao20143d; @Ay:2014aa; @Heinz:2010aa; @salameh2019supervised].
+However, a key limitation among most of these TAD- and loop callers, referred hereafter as domain callers, is that they are heavily reliant on Hi-C data *resolution*.
+Resolution refers to the sizes of genomic regions (bins) used to segment the linear genome [???
+Is this the right statement and reference?
+as a way to deal with low signal-to-noise incurred by the high dimensional nature of Hi-C data [@li2019comparison] ???].
 Lower resolutions contribute to larger bin sizes, which lead to uncertainty in the location of TAD boundaries.
@@
 
-Another limitation among TAD callers is that they disregard prior knowledge about functional genomic elements associated with TAD and loop boundaries.
-The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been hypothesized to comprise components of the loop extrusion model, whereby DNA is extruded through cohesin rings forming chromatin loops [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
-Additionally, distinct patterns of histone modifications have also been shown to be featured at boundaries, including H3K36 timethylation (H3K36me3) [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
-These elements are annotated on the genome using chromatin immunoprecipitation followed by high-throughput DNA sequencing (ChIP-seq).
-Even at its highest (750 bp [@bonev2017multiscale]), Hi-C sequencing resolution still remains well below the resolution of ChIP-seq experiments, which ranges in the tens of bases [@mendoza2009genome].
-Therefore, leveraging such elements in a supervised machine learning framework lends itself to the possibility of more precisely predicting the locations of TAD (or loop) boundaries at much higher resolutions.
+Another limitation among domain callers is that they disregard prior knowledge about functional genomic annotations associated with TAD and loop boundaries.
+The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been identified as components of the loop extrusion model, whereby DNA is extruded through cohesin rings forming chromatin loops [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
+Additionally, distinct patterns of histone modifications have also been shown to be present at boundaries, including H3K36 timethylation (H3K36me3) [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
+These genomic annotations are obtained using chromatin immunoprecipitation followed by high-throughput DNA sequencing (ChIP-seq).
+The resolution of ChIP-seq experiments is typically on the order of tens to hundreths bases [@mendoza2009genome], well below tens of kilobases resolution of Hi-C data (750 bp is the highest resolution of Hi-C data to date [@bonev2017multiscale]).
+Therefore, leveraging precisely mapped genomic annotations in a supervised machine learning framework provides the possibility of more precisely predicting the locations of TAD (or loop) boundaries.
 
-Here we present *preciseTAD*, an R package for precise identification of TAD(or loop) boundaries under a supervised machine learning (ML) framework.
-Our method builds upon an optimized random forest (RF) classification model that leverages high resolution genome annotation data in the form of chromatin segmentation (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS).
-We introduce a novel pipeline for building optimal boundary prediction classifier composed of a resolution-specific binning process and feature engineering procedure.
-We found that spatial associations between boundaries and annotations perform best, transcription factor binding sites further improve prediction accuracy, and a simple random undersampling technique effectively addresses the negative effect of class imbalance.
-Translated from Hi-C data resolution level to base level, *preciseTAD* employs density-based clustering (DBSCAN) and scalable partitioning around medoids (CLARA) on prediction probabilities to select the most biologically meaningful boundary coordinates, thereby circumventing resolution restrictions of conventional TAD- and chromatin loop-callers.
+Here we present *preciseTAD*, an R package implementing optimally tuned machine learning framework for precise identification of domain boundaries using genome annotation data.
+Our method utilizes random forest (RF) algorithm trained on chromatin segmentation (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) data.
+We introduce a systematic pipeline for building optimal boundary prediction classifier.
+We found that spatial associations (distance) between boundaries and annotations perform best, transcription factor binding sites further improve prediction accuracy, and a simple random undersampling technique effectively addresses the negative effect of class imbalance.
+Translated from Hi-C data resolution level to base level (annotating each base and predicting its boundary probability), *preciseTAD* employs density-based clustering (DBSCAN) and scalable partitioning around medoids (CLARA) on prediction probabilities to select genome annotation-guided boundary coordinates.
+This approach circumvents resolution restrictions of Hi-C data, allowing for the precise detection of biologically meaningful boundaries.
 We demonstrate that predictions made by *preciseTAD* are more enriched for known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143.
-Further, we show that *preciseTAD* boundaries are more conserved across cell lines, highlighting their biological significance.
-This improved precision in TAD and loop boundary location can provide insight into the role that epigenomics has on the 3D architecture of the human genome.
+Further, we show that *preciseTAD* boundaries are more conserved across cell lines.
+This improved precision in TAD and loop boundary location can provide insight into the role of genomic regulators on the 3D genome organization.
+The *preciseTAD* R package is freely available on GitHub (https://github.com/dozmorovlab/preciseTAD) and on Bioconductor (submitted).
 
@@
 
-A limitation of *preciseTAD* is that it is dependent on "ground truth" boundaries provided by a user-defined TAD caller.
-Given the wide variety of TAD callers and their variable performance [@Zufferey:2018aa; @forcato2017comparison], it is hard to define "ground truth" TAD boundaries.
+A limitation of *preciseTAD* is that it is dependent on "ground truth" boundaries provided by a user-defined domain caller.
+Given the wide variety of domain callers and their variable performance [@Zufferey:2018aa; @forcato2017comparison], it is hard to define "ground truth" TAD boundaries.
 <!--Ideally we would benchmark *preciseTAD* against simulated boundaries.
@@
 Furthermore, actively transcribed regions can serve as TAD boundaries themselves, independently of CTCF binding [@Harrold:2020aa].
-This may lead to some TAD boundaries being undetected by *preciseTAD* despite being detected by TAD callers.
+This may lead to some TAD boundaries being undetected by *preciseTAD* despite being detected by domain callers.
 Our future work will include defining separate models trained on different TAD boundary types, and predicting precise locations for each of them.

### 2020-08-08 Manuscript/manuscript.Rmd
Methods polishing

@@
 
-Within this study we used both TAD boundary and loop boundary data derived from the publicly available tools Arrowhead [@durand2016juicebox] and Peakachu [@salameh2019supervised] respectively.
-Arrowhead TAD boundaries were called from primary Hi-C data from Geo GSE63525 [@rao20143d] for the GM12878 and K562 cell lines.
+Publicly available TAD and loop boundaries called by Arrowhead [@durand2016juicebox] and Peakachu [@salameh2019supervised] tools, respectively, were used for training.
+Arrowhead TAD boundaries were called from primary Hi-C data for the GM12878 and K562 cell lines [@rao20143d].
 The contact matrices were constructed from all read pairs that uniquely aligned to the genome (MAPQ>0).
 The default parameters for Arrowhead were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1).
-Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab web site.
-Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop.
+Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab web site (Supplementary Table S1).
+Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop anchor.
 Chromosome 9 was excluded from all downstream analyses due to sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-Cell-line-specific genomic annotations (BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa]  (GRCh37/hg19 human genome assembly).
+Cell-line-specific genomic annotations (BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table S3).
 
@@
 To create shifted binning, the first shifted bin was set to start at half of the resolution *r*, and continued in intervals of length *r* until the end of the chromosome (*mod r* + *r/2*).
-The shifted bins, referred hereafted as bins for simplicity, were then defined as boundary-containing regions (*Y = 1*) if they contained a TAD (or loop) boundary, and non-boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification.
+The shifted bins, referred hereafted as bins for simplicity, were then defined as boundary-containing regions (*Y = 1*) if they contained a TAD (or loop) boundary, and non-boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification (Figure 1A).
 
@@
 Cell line-specific genomic annotations were used to build the predictor space for our boundary prediction framework.
-Bins were annotated by one of either the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average signal strength of the corresponding annotation (*Peak Signal Strength*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*).
+Bins were annotated by one of either the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average signal strength of the corresponding annotation (*Peak Signal Strength*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*) (Figure 1B).
 A ($log_2 + 1$)-transformation of distance was used to account for the skewness present in the distributions of genomic distances.
@@
 Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, feature engineering procedures, and re-sampling techniques.
-A *holdout chromosome* technique was devised as a way for unbiased model evaluation on each autosomal chromosome.
+A *holdout chromosome* technique was used for model evaluation on each autosomal chromosome.
 The $i^{th}$ holdout chromosome was identified and a data matrix, $A_{N \times (p+1)}$, was constructed by combining the binned genome from the remaining chromosomes ($1,2,\cdots, i-1,i+1,\cdots,21,22$), where $N=[n_{1} n_{2} \cdots n_{21} n_{22}]'$ and $n_{k}$ is the length of chromosome *k* after being binned into non-overlapping regions of resolution *r*, such that $k \ne i$.
@@
 Each of these quantities are obtained from the confusion matrix created by validating the model on the test data.
-The process was repeated for each $i^{th}$ holdout chromosome and performances were aggregated using means and standard deviations.
+The process was repeated for each $i^{th}$ holdout chromosome and performances were aggregated using mean and standard deviation.
 
@@
 
-To investigate whether we could alleviate resolution limitations of conventional TAD and chromatin loop calling tools, we developed *preciseTAD*, an algorithm that leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution.
-To demonstrate, we implemented an optimally built RF model using the framework described above.
-That is, a random forest model was built on the optimal combination of data resolution (binning), predictor type (predictor space), re-sampling technique (class balancing correction), and top ranked annotations (most informative genomic elements).
+To investigate whether we could alleviate resolution limitations of conventional domain calling tools, we developed *preciseTAD*, an algorithm that leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution.
+To demonstrate, we implemented an optimally trained RF model using the framework described above.
+That is, a random forest model was built on the optimal combination of predictor type (predictor space), re-sampling technique (class balancing correction), and top ranked annotations (most informative genomic elements) to maximaly accurately predict boundaries at _Hi-C resolution level_.
 
-We first construct a base level resolution predictor space for a particular chromosome **i**, using one of the above feature engineering procedures described above.
-We then validate our RF model on the base level predictor space to extract the probability vector, $p_{n_{i}}$, denoting each base's probability of being a boundary point from the RF model, where $n_{i}$ represents the length of chromosome **i**.
-Next, DBSCAN (version 1.1-5) was applied to the matrix of pairwise genomic distances between bases with $p_{n_{i}}=1$.
-This was to avoid the inflation of predicted boundaries that can occur naturally when dealing with such fine resolution, namely, due to spatially close bases with similar predictor profiles (i.e.
-similar overlap counts, distances, etc.).
+To precisely idenify boundary locations, we first construct a _base-level resolution_ predictor space for a particular chromosome **i**.
+We then apply our optimally trained RF model on the base-level predictor space to extract the probability vector, $p_{n_{i}}$, denoting each base's probability of being a boundary point.
+Here, $n_{i}$ represents the length of chromosome **i**.
+Next, DBSCAN (version 1.1-5) was applied to the matrix [???
+vector?] of pairwise genomic distances between bases with $p_{n_{i}}=1$.
+This was to avoid the inflation of predicted boundaries that can occur naturally when dealing with such fine resolution, namely, due to spatially close bases with similar predictor profiles (i.e., similar overlap counts, distances, etc.).
 The DBSCAN algorithm takes two parameters, *eps* ($\epsilon$) and *MinPts*.
@@
 The resulting clusters of highly predictive bases identified by DBSCAN were termed *preciseTAD boundary regions* (PTBR).
-To precisely identify a single base among each PTBR, preciseTAD then implements an extension of partitioning around medoids (PAM), known as CLARA (**Clustering Large Applications**) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
+To precisely identify a single base among each PTBR, *preciseTAD* then implements an extension of partitioning around medoids (PAM), known as CLARA (**Clustering Large Applications**) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
 The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative and biologically meaningful base coordinate within each clustered PTBR.
@@
 
-Next, we assessed the biological significance of our predicted boundaries with respect to the enrichment profiles of several known molecular drivers of 3D chromatin architecture including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
+Next, we assessed the biological significance of our predicted boundaries by their association with several known molecular drivers of 3D chromatin architecture including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
 To do so, we used the **computeMatrix** and **plotHeatmap** tools offered by deepTools (version 2.0) [@ramirez2016deeptools] via integration with Galaxy (version 3.3.2.0.0) [@afgan2018galaxy].
@@
 An example script for applying the Arrowhead tool to in situ Hi-C data (HIC001-HIC018) for resolutions 5kb, 10kb, 25kb, 50kb, 100kb to obtain chromosome-specific TAD boundaries on the GM12878 cell line.
-Prior to implementing SpectralTAD, the dump command offered by juicer [@durand2016juicer] was used to extract the contacts in sparse data matrix format.
+<!--Prior to implementing SpectralTAD, the dump command offered by juicer [@durand2016juicer] was used to extract the contacts in sparse data matrix format.-->
 

### 2020-08-08 Manuscript/manuscript.Rmd
Polish results

@@
 The default parameters for Arrowhead were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1).
-Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab web site (Supplementary Table S1).
+Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab web site (Supplementary Table 1).
 Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop anchor.
 Chromosome 9 was excluded from all downstream analyses due to sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-Cell-line-specific genomic annotations (BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table S3).
+Cell-line-specific genomic annotations (BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 3).
 
@@
 We chose the random forest (RF) algorithm as our binary classification tool.
-The reason being two-fold: (1) In order to devise a tunable prediction rule in a supervised learning framework that is both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors [@boulesteix2012overview].
-We extended our method and developed *preciseTAD*, an R package which leverages an optimally built RF to precisely predict the genomic coordinates of TAD and loop boundaries at base resolution.
-
+The reason for it is two-fold: (1) to devise a tunable prediction rule in a supervised learning framework that is both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors [@boulesteix2012overview].
 We use published Arrowhead-called TAD boundaries [@durand2016juicer] and Peakachu-predicted loop boundaries [@salameh2019supervised] as ground truth.
 Data from GM12878 and K565 cell lines at 5-100kb resolution (Arrowhead) and 10kb resolution (Peakachu) were used (Supplementary Table 1).
+We developed *preciseTAD*, an R package which leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base resolution from cell type-specific genome annotation data.
 
@@
 The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 2).
-The number of non-boundary regions highly outnumbered boundary regions, with results consistent for loop boundaries as well.
+The number of non-boundary regions highly outnumbered boundary regions.
 Such disproportional presence of examples in one class is known as a "class imbalance" problem that negatively affects predictive modeling [@prati2011survey; @wei2013role].
@@
 |:---------------------:|:-----------------:|:--------------------------------------------------:|:-----------------------------------------------------------:|:-----------------------------------:|:----------------------:|
-|        Arrowhead      |       5   kb      |                         8052                       |                             15468                           |                535363               |           0.03         |
-|     Arrowhead         |       10   kb     |                         7676                       |                             14253                           |                267682               |           0.05         |
-|     Arrowhead         |       25   kb     |                         4670                       |                             8363                            |                107073               |           0.08         |
-|     Arrowhead         |       50   kb     |                         2349                       |                             4224                            |                 53537               |           0.08         |
-|     Arrowhead         |      100   kb     |                         1031                       |                             1883                            |                 26768               |           0.07         |
-|        Peakachu       |       10   kb     |                        16185                       |                          21421                              |                267682               |        0.14            |
+|        Arrowhead      |       5   kb      |                         8,052                       |                             15,468                           |                535,363               |           0.03         |
+|     Arrowhead         |       10   kb     |                         7,676                       |                             14,253                           |                267,682               |           0.05         |
+|     Arrowhead         |       25   kb     |                         4,670                       |                             8,363                            |                107,073               |           0.08         |
+|     Arrowhead         |       50   kb     |                         2,349                       |                             4,224                            |                 53,537               |           0.08         |
+|     Arrowhead         |      100   kb     |                         1,031                       |                             1,883                            |                 26,768               |           0.07         |
+|        Peakachu       |       10   kb     |                        16,185                       |                          21,421                              |                267,682               |        0.14            |
 Table: TAD/loop boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the GM12878 cell line.
@@
 Expectedly, when using data with class imbalance present, that is, no re-sampling, the models exhibited low balanced accuracies, with very little variability among different resolutions (Figure 3).
-Similarly, poor performances were found when using ROS as well.
+Similarly, poor performances were found when using ROS.
 However, RUS and SMOTE re-sampling led to drastic improvement in performance, especially at higher resolutions.
@@
 We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figures 4B).
-However, given that we trained our model on chromosome-specific data, the most significant annotations were found to vary for each chromosome that was left out of training and reserved for testing.
+However, given that we trained our model on chromosome-specific data, the most significant annotations vary for each chromosome.
 To determine transcription factors most important for boundary prediction, we clustered the predictive importances (mean decrease in accuracy) of the top eight significant TFs across chromosomes.
-We found that, similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD and loop boundaries for all chromosomes (Figure 4C; Supplementary Figures 4C).
+We found that, similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were consistently predictive of TAD and loop boundaries for all chromosomes (Figure 4C; Supplementary Figures 4C).
 We further optimized our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
-In summary, under our machine learning framework we were able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
+In summary, our model was able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
 
@@
 Using our optimally built random forest model trained on Arrowhead/Peakachu boundaries, we attempted to predict TAD/loop boundaries at base resolution.
-Intuitively, the predictor-response space is built on a base-resolution level, and the model trained (using the optimal characteristics outlined above) on a bin-level space predicts the probability of each base being a boundary.
-Our method, referred to as *preciseTAD*, leverages a user-specified model with density-based hierarchical clustering (DBSCAN) and a scalable partitioning around mediods clustering (CLARA) to predict the boundary location at base resolution (see Methods).
+Intuitively, the predictor-response space is built on a base-resolution level, and the model trained on a bin-level space is used to predict the probability of each base being a boundary.
+Our method, referred to as *preciseTAD*, uses density-based hierarchical clustering (DBSCAN) and a scalable partitioning around mediods clustering (CLARA) to predict the boundary location at base resolution (see Methods).
 
-When built using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb respectively, *preciseTAD* was able to predict a total of 7846 TAD and 15838 chromatin loop boundaries on GM12878, as well as 8883 TAD and 11016 chromatin loop boundaries on K562.
+When built using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb respectively, *preciseTAD* was able to predict a total of 7,846 TAD and 15,838 chromatin loop boundaries on GM12878, as well as 8,883 TAD and 11,016 chromatin loop boundaries on K562.
 Noticeably, we reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Supplementary Table 2).
-This can be attributed to Arrowhead's inflation of called TADs, especially at higher resolutions, that often do not correspond to intra-chromosomal contacts featured on a contact matrix (Figure 1A).
+This can be attributed to Arrowhead's inflation of called TADs, especially at higher resolutions, that often do not correspond to intra-chromosomal contacts featured on a contact matrix.
 <!--Likewise, Arrowhead often produces nested and overlapped TADs that do not have demarcated boundaries, further exacerbating this inflation.
@@
 *preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Supplementary Table 2).
-This can be contributed to the fact that *preciseTAD* leverages 4 known drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143, contrasting Peakachu which considers only CTCF sites.
-This methodology likely leads to many more false positives, resulting in inflated number of chromatin loops.
+This can be contributed to the fact that *preciseTAD* leverages four known drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143, contrasting Peakachu which considers only CTCF sites as true positives.
+These results suggest that genome annotation-driven predicted boundaries may be more biologically relevant, in contrast to boundaries detected from Hi-C data alone.
 
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
-Signal heatmaps indicated that our predicted boundaries were more enriched for CTCF sites than either Arrowhead or Peakachu boundaries alone (Figure 5 B-C).
-Likewise, *preciseTAD* boundaries were also more enriched for other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 5-6).
-When compared to called TAD or loop boundaries, *preciseTAD* boundaries were found to be statistically significantly closer to the same cell line-specific top ranked TFBS (p<0.001 and p<0.001 versus Arrowhead and Peakachu respectively) (Figure 5D, Supplementary Figure 7).
+Signal heatmaps indicated that our predicted boundaries were more frequently co-localized with CTCF sites than either Arrowhead or Peakachu boundaries alone (Figure 5 B-C).
+Likewise, *preciseTAD* boundaries were also more co-localized with other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 5-6).
+When compared to called TAD or loop boundaries, *preciseTAD* boundaries were statistically significantly closer to the same cell line-specific top ranked TFBS (p<0.001 and p<0.001 versus Arrowhead and Peakachu respectively) (Figure 5D, Supplementary Figure 7).
+These results indicate that *preciseTAD*-predicted boundaries better reflect the known bioloby of boundary formation.
 
@@
 We found that 35% of *preciseTAD* predicted TAD boundaries and 55% of *preciseTAD* predicted loop boundaries were were conserved between cell lines, compared to only 26% and 55% for Arrowhead and Peakachu alone (Figure 5E).
+The better conservation of *preciseTAD*-predicted boundaries further support the notion of their higher biological relevance.
 
@@
 This is expected as loop boundaries (Peakachu) are more abundant, while TAD boundaries (Arrowhead) represent the narrower level of the 3D chromatin organization.
-Together with the results shown on Figure 4, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar protein complexes.
+Together with the results on Figure 4, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar protein complexes.
 
@@
 
-**Supplementary Table 2.** TAD/loop boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the k562 cell line.
+**Supplementary Table 2.** TAD/loop boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the K562 cell line.
 Class imbalance is calculated as the ratio of total number of unique boundaries to the total number of genomic bins.
@@
 
-**Supplementary Figure 1.** Density curves illustrate the normalization of distances before (red) and after (blue) performing a $log_{2}$ transformation across differing bin sizes including 10 kb, 25 kb, 50 kb, and 100 kb for both the (A) GM12878 and (B) K562 cell lines respectively.
+**Supplementary Figure 1.** Density curves illustrate the normalization of distances before (red) and after (blue) performing a $log_{2}$ transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines, respectively.
 Distances are measured as the number of bases from the center of a genomic bin to the center of the nearest genomic annotation.
 Each density curve represents individual genomic annotation.
+[???
+All of them?
+Or, TFBSs only?]
 
@@
 Boundaries were flanked by 5 kb resolution.
+[???
+Where is the threshold description?]
 

### 2020-08-08 Manuscript/manuscript.Rmd
Discussion edits

@@
 We present *preciseTAD*, a machine learning approach for precise prediction of TAD or loop boundaries from functional genomic annotations.
-*preciseTAD* leverages a random forest (RF) classification model built on ground truth TAD/loop boundaries obtained from a TAD/loop calling tools and ChIP-seq defined genomic annotations as the predictor space.
+*preciseTAD* leverages a random forest (RF) classification model built on ground truth TAD/loop boundaries obtained from a TAD/loop calling tools and genomic annotations as the predictor space.
 We benchmarked *preciseTAD* against two boundary calling tools, Arrowhead [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
-We applied *preciseTAD* on cell line-specific boundaries and ChIP-seq data from both GM12878 and K562.
+We applied *preciseTAD* on cell line-specific boundaries and annotation data from both GM12878 and K562.
 We first optimized our RF model by systematically comparing different combinations of genome binning (resolution), feature engineering procedures, and re-sampling techniques.
-We show that genomic distance between boundary regions and annotations, coupled with random under-sampling help to form the predictor space resulting in optimal model performance.
-<!--We demonstrate that binding of four transcription factors (SMC3, Rad21, CTCF, Znf143) are sufficient for accurate TAD and loop boundary predictions.
-The model predicts probability for each base to be a baoundary, and, coupled with spatial clustering (DBSCAN) and scalable partition around medoids clustering (CLARA), allows for the detection of boundaries at the base-level resolution.-->
+We show that genomic distance between high-resolution boundary regions and transcription factor binding sites, coupled with random under-sampling results in best model performance.
+We demonstrate that binding of four transcription factors (SMC3, Rad21, CTCF, Znf143) are sufficient for accurate TAD and loop boundary predictions.
+Applied to each annotated base, the model predicts probability for each base to be a boundary, and, coupled with spatial clustering (DBSCAN) and scalable partition around medoids clustering (CLARA), allows for the detection of boundaries at the base-level resolution.
+*preciseTAD* is implemented as an R package, and allows for precise prediction of boundaries for any cell type for which the corresponding genomic annotations are available.
 
@@
 Add REFs].
--->This suggested that the random forest model, when tuned and feature engineered correctly, is highly effective in predicting domain boundaries.
+-->This suggested that the random forest model, when tuned and feature engineered correctly, is highly effective in predicting biologically relevant domain boundaries.
 
 Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC).
-Our aim was to have a balanced metric that was sensitive to class imbalance such that it would not favor one component of the confusion matrix.
+Our aim was to have a balanced metric sensitive to class imbalance such that it would not favor one component of the confusion matrix.
 The accuracy metric can be artificially inflated by true negatives (TN), the set of genomic bins correctly predicted as not containing a ground truth boundary.
@@
 *preciseTAD* TAD and loop boundaries were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops are dynamic structures generated by similar mechanisms [@hansen2018recent].
-Likewise *preciseTAD* boundaries were found to be more conserved between GM12878 and K562 cell lines, a known feature among the 3D architecture of the human genome, further highlighting their biological significance [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
+Likewise, *preciseTAD* boundaries were found to be more conserved between GM12878 and K562 cell lines, a known feature among the 3D architecture of the human genome, further highlighting their biological significance [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
 
@@
 The same heuristic ($t=1.0$ and $\epsilon=r$) ensured that boundaries were at least 5kb bases away from each other, while also suitably enriched for architectural proteins (Supplementary Figures 10-11).
+These most optimal heuristics are set as default, but can be further tuned, if necessary.
 

### 2020-08-09 Manuscript/manuscript.Rmd
Adjust TAD conservation refs

@@
 
-TAD boundaries are known to be relatively conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
+TAD boundaries are known to be relatively conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @sexton2012three].
 To assess conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, Arrowhead, and Peakachu after flanking them by the resolution of the Hi-C data.
@@
 *preciseTAD* TAD and loop boundaries were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops are dynamic structures generated by similar mechanisms [@hansen2018recent].
-Likewise, *preciseTAD* boundaries were found to be more conserved between GM12878 and K562 cell lines, a known feature among the 3D architecture of the human genome, further highlighting their biological significance [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
+Likewise, *preciseTAD* boundaries were found to be more conserved between GM12878 and K562 cell lines, a known feature among the 3D architecture of the human genome, further highlighting their biological significance.
 

### 2020-08-11 Manuscript/manuscript.Rmd
Fix ???, one left

@@
 
-# ABSTRACT
+# Abstract
 
@@
 However, a key limitation among most of these TAD- and loop callers, referred hereafter as domain callers, is that they are heavily reliant on Hi-C data *resolution*.
-Resolution refers to the sizes of genomic regions (bins) used to segment the linear genome [???
-Is this the right statement and reference?
-as a way to deal with low signal-to-noise incurred by the high dimensional nature of Hi-C data [@li2019comparison] ???].
+Resolution refers to the sizes of genomic regions (bins) used to segment the linear genome [@li2019comparison].
 Lower resolutions contribute to larger bin sizes, which lead to uncertainty in the location of TAD boundaries.
@@
 Here, $n_{i}$ represents the length of chromosome **i**.
-Next, DBSCAN (version 1.1-5) was applied to the matrix [???
-vector?] of pairwise genomic distances between bases with $p_{n_{i}}=1$.
+Next, DBSCAN (version 1.1-5) was applied to the matrix of pairwise genomic distances between bases with $p_{n_{i}}=1$.
 This was to avoid the inflation of predicted boundaries that can occur naturally when dealing with such fine resolution, namely, due to spatially close bases with similar predictor profiles (i.e., similar overlap counts, distances, etc.).
@@
 The accuracy metric can be artificially inflated by true negatives (TN), the set of genomic bins correctly predicted as not containing a ground truth boundary.
-AUROC captures how a model generally performs accross different thresholds.
+AUROC captures how a model generally performs across different thresholds.
 However, it doesn't place more emphasis on one class over the other, so it does not reflect the minority class well.
@@
 While F1-score is a composite metric, it can be very sensitive towards disparate values for precision and recall.
-Lastly, AUPRC is insensitive toward class imbalance and also omits from its calculation TN values [???
-So why didn't you use it?].
+Lastly, AUPRC is insensitive toward class imbalance, preventing us to investigate its effect, and also omits from its calculation TN values.
 All of these are important considerations to make when choosing a performance metric.
@@
 Distances are measured as the number of bases from the center of a genomic bin to the center of the nearest genomic annotation.
+All genomic annotations were used.
 Each density curve represents individual genomic annotation.
-[???
-All of them?
-Or, TFBSs only?]
 

### 2020-08-14 Manuscript/manuscript.Rmd
updated

--- 2020-08-09 Manuscript/manuscript.Rmd
@@
 
-**Methods** To improve the detection of domain boundaries, we developed preciseTAD, a random forest-based framework that leverages high-resolution genome annotation data coupled with density-based clustering and scalable partitioning techniques.
+**Methods** To improve the detection of domain boundaries, we developed *preciseTAD*, a random forest-based framework that leverages high-resolution genome annotation data coupled with density-based clustering and scalable partitioning techniques.
 We investigated several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) to address class imbalance.
-We benchmarked our method against Arrowhead domain caller and a novel chromatin loop prediction algorithm, Peakachu, on multiple cell lines.
+We benchmarked our method against the Arrowhead domain caller and a novel chromatin loop prediction algorithm, Peakachu, on multiple cell lines.
 
@@
 However, a key limitation among most of these TAD- and loop callers, referred hereafter as domain callers, is that they are heavily reliant on Hi-C data *resolution*.
-Resolution refers to the sizes of genomic regions (bins) used to segment the linear genome [???
-Is this the right statement and reference?
-as a way to deal with low signal-to-noise incurred by the high dimensional nature of Hi-C data [@li2019comparison] ???].
+Resolution refers to the sizes of genomic regions (bins) used to segment the linear genome.
 Lower resolutions contribute to larger bin sizes, which lead to uncertainty in the location of TAD boundaries.
@@
 These genomic annotations are obtained using chromatin immunoprecipitation followed by high-throughput DNA sequencing (ChIP-seq).
-The resolution of ChIP-seq experiments is typically on the order of tens to hundreths bases [@mendoza2009genome], well below tens of kilobases resolution of Hi-C data (750 bp is the highest resolution of Hi-C data to date [@bonev2017multiscale]).
+The resolution of ChIP-seq experiments is typically on the order of tens to hundreds of bases [@mendoza2009genome], well below the resolution of Hi-C data (tens of kilobases; 750 bp is the highest resolution of Hi-C data to date [@bonev2017multiscale]).
 Therefore, leveraging precisely mapped genomic annotations in a supervised machine learning framework provides the possibility of more precisely predicting the locations of TAD (or loop) boundaries.
 
-Here we present *preciseTAD*, an R package implementing optimally tuned machine learning framework for precise identification of domain boundaries using genome annotation data.
-Our method utilizes random forest (RF) algorithm trained on chromatin segmentation (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) data.
+Here we present *preciseTAD*, an R package for implementing an optimally tuned machine learning framework for precise identification of domain boundaries using genome annotation data.
+Our method utilizes the random forest (RF) algorithm trained on chromatin segmentation (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) data.
 We introduce a systematic pipeline for building optimal boundary prediction classifier.
@@
 Chromosome 9 was excluded from all downstream analyses due to sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-Cell-line-specific genomic annotations (BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 3).
+Cell-line-specific genomic annotations (BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 2).
 
@@
 The $i^{th}$ holdout chromosome was identified and a data matrix, $A_{N \times (p+1)}$, was constructed by combining the binned genome from the remaining chromosomes ($1,2,\cdots, i-1,i+1,\cdots,21,22$), where $N=[n_{1} n_{2} \cdots n_{21} n_{22}]'$ and $n_{k}$ is the length of chromosome *k* after being binned into non-overlapping regions of resolution *r*, such that $k \ne i$.
-$p$, the number of annotations, together with the response vector **Y**, defined column-wise dimension of the matrix $A$.
+$p$, the number of annotations, together with the response vector **Y**, defined the column-wise dimension of the matrix $A$.
 Re-sampling was then performed on $A$ and an RF classifier was trained using 3-fold cross-validation to tune for the number of annotations to consider at each node (*mtry*).
@@
 To demonstrate, we implemented an optimally trained RF model using the framework described above.
-That is, a random forest model was built on the optimal combination of predictor type (predictor space), re-sampling technique (class balancing correction), and top ranked annotations (most informative genomic elements) to maximaly accurately predict boundaries at _Hi-C resolution level_.
+That is, a random forest model was built on the optimal combination of predictor type (predictor space), re-sampling technique (class balancing correction), and top ranked annotations (most informative genomic elements) to maximally accurately predict boundaries at base _Hi-C resolution level_.
 
-To precisely idenify boundary locations, we first construct a _base-level resolution_ predictor space for a particular chromosome **i**.
+To precisely identify boundary locations, we first construct a _base-level resolution_ predictor space for a particular chromosome *i*.
 We then apply our optimally trained RF model on the base-level predictor space to extract the probability vector, $p_{n_{i}}$, denoting each base's probability of being a boundary point.
-Here, $n_{i}$ represents the length of chromosome **i**.
-Next, DBSCAN (version 1.1-5) was applied to the matrix [???
-vector?] of pairwise genomic distances between bases with $p_{n_{i}}=1$.
-This was to avoid the inflation of predicted boundaries that can occur naturally when dealing with such fine resolution, namely, due to spatially close bases with similar predictor profiles (i.e., similar overlap counts, distances, etc.).
-The DBSCAN algorithm takes two parameters, *eps* ($\epsilon$) and *MinPts*.
-The *eps* parameter was assigned as the respective data resolution.
-The heuristic being that density-reachable bases with genomic distances less than resolution should occupy the same designated cluster.
-The corresponding *MinPts* parameter was set to recommended value of 3, representing $1+dim(data)$ [@hahsler2019dbscan].
+Here, $n_{i}$ represents the length of chromosome *i*.
+A threshold (*t*) is specified on $p_{n_{i}}$, such that base coordinates with $p_{n_{i}} \ge t$ are extracted.
+Next, density-based spatial clustering of applications with noise (DBSCAN; version 1.1-5) is applied to the matrix of pairwise genomic distances between bases with $p_{n_{i}} \ge t$.
 The resulting clusters of highly predictive bases identified by DBSCAN were termed *preciseTAD boundary regions* (PTBR).
@@
 The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative and biologically meaningful base coordinate within each clustered PTBR.
+
+The DBSCAN algorithm takes two parameters, *MinPts* and *eps* ($\epsilon$).
+The *MinPts* parameter was set to the recommended value of 3, representing $1+dim(data)$ [@hahsler2019dbscan].
+To decide on the optimal value of *t* and $\epsilon$ in *preciseTAD*, we considered the normalized enrichment of flanked predicted boundaries, defined as
+
+$$N_{e} = \dfrac{1}{b} \Sigma_{i=1}^{n}e_{i}$$
+where $e_{i}$ is the number ChIP-seq peak regions that overlap with the $i^{th}$ predicted boundary, $b$, flanked by resolution $r$.
+We evaluated $N_{e}$ for combinations of $t=\{0.95, 0.975, 0.99, 1.0 \}$ and $\epsilon = \{5000, 10000, 15000, 20000, 25000 \}$.
+The heuristic of $\epsilon$ is that density-reachable bases with genomic distances less than $\epsilon$ should occupy the same designated cluster.
 
@@
 Data from GM12878 and K565 cell lines at 5-100kb resolution (Arrowhead) and 10kb resolution (Peakachu) were used (Supplementary Table 1).
-We developed *preciseTAD*, an R package which leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base resolution from cell type-specific genome annotation data.
+We next developed *preciseTAD*, an R package which leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base resolution from cell type-specific genome annotation data.
 
-In our ML framework boundary regions were defined as regions containing a called boundary ($Y = 1$), while non-boundary regions were defined as genomic bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
-The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 2).
+In our ML framework boundary regions were defined as genomic bins containing a called boundary ($Y = 1$), while non-boundary regions were defined as bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
+The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 3).
 The number of non-boundary regions highly outnumbered boundary regions.
@@
 A total of 77 cell line-specific functional genomic annotations were used to build the predictor space.
-These included BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 3).
+These included BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 2).
 Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
-These include signal strength association (Signal), direct (OC), proportional (OP), and spatial (Distance) relationships (see Methods).
+These included signal strength association (Signal), direct (OC), proportional (OP), and spatial (Distance) relationships (see Methods).
 A ($log_2 + 1$)-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
@@
 
-![**A diagram of the machine learning framework used to build TAD/loop boundary region prediction models.** Step 1 defines the data matrix A, composed of N genomic bins for each chromosome, except a holdout chromosome *i*, *p* genomic annotations, and the response vector **Y** (for *p*+1 columns).
-Resolution-specific data (5 kb, 10 kb, 25 kb, 50 kb, or 100 kb) and feature engineering procedure (overlap count (OC), overlap percent (OP), $log_{2}$ distance (Distance)) for the n-1 autosomal chromosomes.
+![**A diagram of the machine learning framework used to build TAD/loop boundary region prediction models.** Step 1 defines the dimensions of the data matrix $A_{N \times (p+1)}$ used for training and testing by establishing a resolution, $r$, at which to bin the linear genome into $N$ genomic bins for each chromosome, except a holdout chromosome *i*.
+The response vector **Y** is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$) A feature engineering procedure is selected to define the feature space of $A$ composed of $p$ genomic annotations.
 Step 2 is to reserve the predictor-response matrix for the holdout chromosome *i* as the test data.
-Step 3 is to apply a re-sampling technique to the training set (no re-sampling, random over-sampling, random under-sampling, or SMOTE re-sampling).
+Step 3 is to apply a re-sampling technique to the training data to address class imbalance.
 Step 4 is to train the random forest model and perform 3-fold cross-validation to tune for the mtry parameter.
@@
 
-We hypothesized that the type of genomic annotations may also affect the predictive performance.
+We hypothesized that the type of genomic annotations may also affect predictive performance.
 Using the established optimal settings (RUS, Distance, 5 kb bins), we built separate random forest models using BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS).
 We found that models built on TFBSs outperformed other annotation-specific models, with results consistent for loop boundaries, on both cell lines (Figure 4A; Supplementary Figures 4A).
-These results suggest that TFBS are the primary drivers of TAD and loop boundary formation in both the GM12878 and K562.
+These results suggest that TFBS are the primary drivers of TAD and loop boundary formation in both GM12878 and K562.
 
@@
 We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figures 4B).
-However, given that we trained our model on chromosome-specific data, the most significant annotations vary for each chromosome.
+However, given that we trained our model on chromosome-specific data, the most significant annotations varied for each set of chromosomes.
 To determine transcription factors most important for boundary prediction, we clustered the predictive importances (mean decrease in accuracy) of the top eight significant TFs across chromosomes.
-We found that, similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were consistently predictive of TAD and loop boundaries for all chromosomes (Figure 4C; Supplementary Figures 4C).
+We found that, similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were consistently predictive of TAD and loop boundaries (Figure 4C; Supplementary Figures 4C).
 We further optimized our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
 In summary, our model was able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
+[???update]
 
@@
 Using our optimally built random forest model trained on Arrowhead/Peakachu boundaries, we attempted to predict TAD/loop boundaries at base resolution.
-Intuitively, the predictor-response space is built on a base-resolution level, and the model trained on a bin-level space is used to predict the probability of each base being a boundary.
+Intuitively, the predictor-response space was built on a base-resolution level, and the model trained on a bin-level space was used to predict the probability of each base being a boundary.
 Our method, referred to as *preciseTAD*, uses density-based hierarchical clustering (DBSCAN) and a scalable partitioning around mediods clustering (CLARA) to predict the boundary location at base resolution (see Methods).
@@
 When built using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb respectively, *preciseTAD* was able to predict a total of 7,846 TAD and 15,838 chromatin loop boundaries on GM12878, as well as 8,883 TAD and 11,016 chromatin loop boundaries on K562.
-Noticeably, we reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Supplementary Table 2).
+Noticeably, we reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Supplementary Table 3).
 This can be attributed to Arrowhead's inflation of called TADs, especially at higher resolutions, that often do not correspond to intra-chromosomal contacts featured on a contact matrix.
-<!--Likewise, Arrowhead often produces nested and overlapped TADs that do not have demarcated boundaries, further exacerbating this inflation.
-However, under the framework of *preciseTAD*, any two domains are inherently conjoined by only one predicted boundary, leading to comparatively less TAD boundaries.
-[???
-Unclear explanation, so what?
-preciseTAD is driven by genomic annotations.
-May it be too stringent thresholds?
-This all may be for the discussion, if we have a good understanding why] -->Additionally, *preciseTAD* boundaries were visually more likely to demarcate high concentrations of intra-chromosomal contacts as can be seen on a Hi-C contact matrix (Figure 5A).
-*preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Supplementary Table 2).
+Additionally, *preciseTAD* boundaries were visually more likely to demarcate high concentrations of intra-chromosomal contacts as can be seen on a Hi-C contact matrix (Figure 5A).
+*preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Supplementary Table 3).
 This can be contributed to the fact that *preciseTAD* leverages four known drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143, contrasting Peakachu which considers only CTCF sites as true positives.
@@
 When compared to called TAD or loop boundaries, *preciseTAD* boundaries were statistically significantly closer to the same cell line-specific top ranked TFBS (p<0.001 and p<0.001 versus Arrowhead and Peakachu respectively) (Figure 5D, Supplementary Figure 7).
-These results indicate that *preciseTAD*-predicted boundaries better reflect the known bioloby of boundary formation.
+These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
 
@@
 The better conservation of *preciseTAD*-predicted boundaries further support the notion of their higher biological relevance.
-
-<!--Additionally, the median Jaccard index (MJI) was found to be 0.472 (IQR=0.441-0.503; p=???) and 0.647 (IQR=0.646-0.647; p=???) for *preciseTAD* predicted TAD and loop boundaries (Supplementary Table 5).
-Comparatively, only 25% (MJI=0.284; IQR=0.268-0.301) and 49% (MJI=0.509; IQR=0.503-0.515) of called/predicted Arrowhead and Peakachu boundaries were conserved (Figure 6A, Supplementary Table 5).
-These results demonstrate that boundaries predicted using genomic annotations (*preciseTAD*) are better conserved across cell lines.-->
-
-<!--We also inspected the effect of resolution on locations of our predicted TAD boundaries.
-We found that *preciseTAD* boundaries exhibited higher pairwise Jaccard indices between adjacent resolutions than Arrowhead boundaries, thus implying stronger invariance toward resolution (Figure 5E).-->
 
@@
 We present *preciseTAD*, a machine learning approach for precise prediction of TAD or loop boundaries from functional genomic annotations.
-*preciseTAD* leverages a random forest (RF) classification model built on ground truth TAD/loop boundaries obtained from a TAD/loop calling tools and genomic annotations as the predictor space.
+*preciseTAD* leverages a random forest (RF) classification model built on ground truth TAD/loop boundaries obtained from TAD/loop calling tools and genomic annotations as the predictor space.
 We benchmarked *preciseTAD* against two boundary calling tools, Arrowhead [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
@@
 We show that genomic distance between high-resolution boundary regions and transcription factor binding sites, coupled with random under-sampling results in best model performance.
-We demonstrate that binding of four transcription factors (SMC3, Rad21, CTCF, Znf143) are sufficient for accurate TAD and loop boundary predictions.
+We demonstrate that binding of four transcription factors (SMC3, RAD21, CTCF, ZNF143) are sufficient for accurate TAD and loop boundary predictions.
 Applied to each annotated base, the model predicts probability for each base to be a boundary, and, coupled with spatial clustering (DBSCAN) and scalable partition around medoids clustering (CLARA), allows for the detection of boundaries at the base-level resolution.
@@
 We further demonstrated that class imbalance hinders boundary prediction, but can be effectively addressed by a simple random under-sampling technique, an aspect of boundary prediction that was unaddressed in previous studies [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa].
-We showed that information about only four transcription factors (SMC3, Rad21, CTCF, Znf143) is necessary and sufficient for accurate boundary prediction, outperforming histone modification- and BroadHMM-built models [@Moore:2015aa; @Al-Bkhetan:2018aa].
+We showed that information about only four transcription factors (SMC3, RAD21, CTCF, ZNF143) is necessary and sufficient for accurate boundary prediction, outperforming histone modification- and BroadHMM-built models [@Moore:2015aa; @Al-Bkhetan:2018aa].
 These are known components of the loop extrusion model, an established theory for how loops are made by a ring-shaped adenosine triphosphatase complex called cohesin [@hansen2018recent; @sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
 Interestingly, the same transcription factors accurately predicted both TAD and loop boundaries, suggesting similarity of the mechanisms of TAD and loop formation.
-<!--Although our observations contradict a previous study showing histone marks alone were effective in predicting TAD boundaries [@huang2015predicting], our findings are backed by a large body of literature [???
-Add REFs].
--->This suggested that the random forest model, when tuned and feature engineered correctly, is highly effective in predicting biologically relevant domain boundaries.
+This suggested that the random forest model, when tuned and feature engineered correctly, is highly effective in predicting biologically relevant domain boundaries.
 
@@
 While F1-score is a composite metric, it can be very sensitive towards disparate values for precision and recall.
-Lastly, AUPRC is insensitive toward class imbalance and also omits from its calculation TN values [???
-So why didn't you use it?].
+Lastly, AUPRC is insensitive toward class imbalance and also omits from its calculation TN values.
 All of these are important considerations to make when choosing a performance metric.
@@
 The BA benefits from incorporating all components of the confusion matrix, while also being sensitive to class imbalance, a necessary characteristic when comparing performances to models built using no data re-sampling.
+[???refer to supp tables 4 and 5 here]
 
@@
 The same heuristic ($t=1.0$ and $\epsilon=r$) ensured that boundaries were at least 5kb bases away from each other, while also suitably enriched for architectural proteins (Supplementary Figures 10-11).
-These most optimal heuristics are set as default, but can be further tuned, if necessary.
+These most optimal heuristics are set as default, but can be further tuned, if necessary.[???update]
 
@@
 
-**Supplementary Table 2.** TAD/loop boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the K562 cell line.
-Class imbalance is calculated as the ratio of total number of unique boundaries to the total number of genomic bins.
-
-**Supplementary Table 3.** A complete list of the genomic annotations used to build the predictor space for all downstream models.
+**Supplementary Table 2.** A complete list of the genomic annotations used to build the predictor space for all downstream models.
 The GRCh37/hg19 human genome assembly was used.
 “Genomic Class” - broad category of genomic features, “Element” - names of genomic features, “Cell Type-Specific Source” - download URL specific to the cell line (not all annotations were provided by the same institutions).
+
+**Supplementary Table 3.** TAD/loop boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the K562 cell line.
+Class imbalance is calculated as the ratio of total number of unique boundaries to the total number of genomic bins.
 
@@
 Each density curve represents individual genomic annotation.
-[???
-All of them?
-Or, TFBSs only?]
 
@@
 
-**Supplementary Figure 9.** Barplots illustrating the normalized overlap between known molecular drivers of 3D chromatin and flanked predicted TAD boundaries identified by preciseTAD (using Arrowhead ground truth boundaries) on GM12878 and for chromosome 22.
+**Supplementary Figure 9.** Barplots illustrating the normalized overlap between known molecular drivers of 3D chromatin and flanked predicted TAD boundaries identified by preciseTAD (using Arrowhead ground truth boundaries) for different combinations of thresholds (t) and epsilon parameter values (eps) on GM12878 and for chromosome 22.
 Normalized overlap was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted (on chr22).
 Boundaries were flanked by 5 kb resolution.
-[???
-Where is the threshold description?]
 

### 2020-08-14 Manuscript/manuscript.Rmd

@@
 However, a key limitation among most of these TAD- and loop callers, referred hereafter as domain callers, is that they are heavily reliant on Hi-C data *resolution*.
-Resolution refers to the sizes of genomic regions (bins) used to segment the linear genome.
+Resolution refers to the sizes of genomic regions (bins) used to segment the linear genome [@li2019comparison].
 Lower resolutions contribute to larger bin sizes, which lead to uncertainty in the location of TAD boundaries.
@@
 $$N_{e} = \dfrac{1}{b} \Sigma_{i=1}^{n}e_{i}$$
+
 where $e_{i}$ is the number ChIP-seq peak regions that overlap with the $i^{th}$ predicted boundary, $b$, flanked by resolution $r$.
@@
 While F1-score is a composite metric, it can be very sensitive towards disparate values for precision and recall.
-Lastly, AUPRC is insensitive toward class imbalance and also omits from its calculation TN values.
+Lastly, AUPRC is insensitive toward class imbalance, preventing us to investigate its effect, and also omits from its calculation TN values.
 All of these are important considerations to make when choosing a performance metric.
@@
 The BA benefits from incorporating all components of the confusion matrix, while also being sensitive to class imbalance, a necessary characteristic when comparing performances to models built using no data re-sampling.
-[???refer to supp tables 4 and 5 here]
+[???refer to supp tables 4 and 5 here when ready]
 
@@
 Distances are measured as the number of bases from the center of a genomic bin to the center of the nearest genomic annotation.
-Each density curve represents individual genomic annotation.
+All genomic annotations were used.
+Each density curve represents an individual genomic annotation.
 

### 2020-08-14 Manuscript/manuscript.Rmd
updated figures

@@
 output:
-  pdf_document: 
   word_document:
     reference_docx: styles.doc/NIH_grant_style.docx
+  pdf_document: 
 bibliography: References/references.bib
@@
 In summary, our model was able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
-[???update]
 
@@
 
-![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.**(A) The location of preciseTAD (green) vs.
-Arrowhead (blue) boundaries on GM12878 (chr 1: 70600000-71530000).
+![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of preciseTAD (green) vs.
+ARROWHEAD (blue) boundaries on GM12878 (chr 14: 50085000-50800000).
 The black line represents the predicted probability of each base being a TAD boundary.
-A zoomed-in portion of the genome shows a yellow-highlighted cluster of bases with high probability of being a boundary, the preciseTAD boundary region (PTBR).
-(B) Enriched heatmaps comparing the enrichment of CTCF signal around Arrowhead TAD boundaries and preciseTAD boundaries, and (C) around Peakachu loop boundaries and preciseTAD for the entire genome.
-(D) Log 2 genomic distances from boundaries to nearest CTCF sites.
-(E) Venn diagrams illustrating the levels of conservation between TAD/loop boundaries for GM12878 (red) and K562 (blue) identified by preciseTAD (using Arrowhead; top left), Arrowhead (top right), preciseTAD (using Peakachu; bottom left), and Peakachu (bottom right).
-The median Jaccard Index (IQR) across each chromosome is provided below each venn diagram.](Figures/figure5.png)
+(B)Bigwig visualization of known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143.
+(C) Enriched heatmaps comparing the enrichment of CTCF signal around ARROWHEAD TAD boundaries and preciseTAD boundaries, and (D) around Peakachu loop boundaries and preciseTAD for the entire genome.
+(E) Log 2 genomic distances from boundaries to nearest CTCF sites.
+(F) Venn diagrams illustrating the levels of conservation between TAD/loop boundaries for GM12878 (red) and K562 (blue) identified by preciseTAD (using ARROWHEAD; top left), ARROWHEAD (top right), preciseTAD (using PEAKACHU; bottom left), and PEAKACHU (bottom right).
+The median Jaccard Index (IQR) across each chromosome is provided below each venn diagram](Figures/figure5.png)
 
@@
 A lower threshold and $\epsilon$ will result in more clusters of bases, and therefore, more boundaries.
-As a heuristic, we evaluated the pairwise combination of 4 different thresholds ($t=(0.95,0.975,0.99,1.0)$) and 4 different $\epsilon$ values ($\epsilon=(0.2 r, 0.5r, r, 2r)$)), where $r=5000$, the optimal resolution.
-We found that the normalized overlaps--calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries --between top TFBS sites and flanked preciseTAD boundaries were maximized for combinations of t=1.0 and eps=r (Supplementary Figure 9).
-The same heuristic ($t=1.0$ and $\epsilon=r$) ensured that boundaries were at least 5kb bases away from each other, while also suitably enriched for architectural proteins (Supplementary Figures 10-11).
-These most optimal heuristics are set as default, but can be further tuned, if necessary.[???update]
+As a heuristic, we evaluated the pairwise combination of 4 different thresholds ($t=(0.95,0.975,0.99,1.0)$) and 4 different $eps$ values ($\epsilon=(r, 2r, 3r, 4r, 5r)$)), where $r=5000$, the optimal resolution.
+We found that the normalized overlaps--calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries --between top TFBS sites and flanked preciseTAD boundaries were maximized for combinations of t=1.0 and $eps=r$ (Supplementary Figure 9).
 
@@
 
-**Supplementary Figure 9.** Barplots illustrating the normalized overlap between known molecular drivers of 3D chromatin and flanked predicted TAD boundaries identified by preciseTAD (using Arrowhead ground truth boundaries) for different combinations of thresholds (t) and epsilon parameter values (eps) on GM12878 and for chromosome 22.
+**Supplementary Figure 9.** Linecharts illustrating the normalized overlap between known molecular drivers of 3D chromatin and flanked predicted TAD boundaries identified by preciseTAD (using Arrowhead ground truth boundaries) for different combinations of thresholds (t) and epsilon parameter values (eps) on GM12878 and for chromosome 22.
 Normalized overlap was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted (on chr22).
 Boundaries were flanked by 5 kb resolution.
-
-**Supplementary Figure 10.** Density plots illustrating the genomic distance (in bases) between predicted TAD boundaries identified by preciseTAD (using Arrowhead ground truth boundaries) for different combinations of thresholds (t) and epsilon parameter values (eps) on GM12878 and for chromosome 22.
-The median genomic distance (range) is provided for each combination.
-
-**Supplementary Figure 11**.
-The formation of TADs (CHR22: 25mb-27mb) demarcated by boundaries predicted by preciseTAD for different combinations of thresholds (t) and eps values ($\epsilon$) on GM12878.
-The visualization was created by the juicebox toolbox [@durand2016juicebox] using the GM12878 insitu primary HIC file provided by Rao et al.
-2014 [@rao20143d].
 

### 2020-08-14 Scripts_for_results/03_creating_annotation_specifc_barplots.Rmd
updated figures/tables

@@
   if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
-    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                i,
@@
   }else{
-    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                i,
@@
   if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
-    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/5kb/results_by_chr/",
                                i,
@@
   }else{
-    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
+    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/5kb/results_by_chr/",
                                i,
@@
   if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
-    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                i,
@@
   }else{
-    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                i,
@@
   if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
-    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/10kb/results_by_chr/",
                                i,
@@
   }else{
-    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
+    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/K562/10kb/results_by_chr/",
                                i,
@@
 ```
+
+#############################################
+
+#Plotting
+
+```{r}
+ggplot(all_rfperfs_a_p, aes(x=Annotation, y=Performance, fill=Tool)) +
+    facet_grid(. ~ Tool) +
+    geom_bar(stat="identity") +
+    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=.75, size=1) +
+    guides(fill=FALSE) +
+    scale_fill_manual(values = c("blue", "red"))+
+    theme_minimal() +
+    theme_bw()+
+    xlab("Genomic Class") + 
+    ylab("Balanced Accuracy") + 
+    theme(axis.text.x = element_text(size=15,
+                                     angle = 45, 
+                                     #margin = ggplot2::margin(t = 35),
+                                     hjust = 1
+    ),
+    axis.text.y = element_text(size = 15),
+    axis.title.x = element_text(size = 20),
+    axis.title.y = element_text(size = 20),
+    strip.text.x = element_text(size = 20),
+    legend.text=element_text(size=15),
+    legend.title=element_text(size=20),
+    legend.position = "bottom",
+    plot.title = element_text(size=20))
+```

### 2020-08-14 Scripts_for_results/04_creating_rfe_lineplot.Rmd
updated figures/tables

--- 2020-05-22 Scripts_for_results/04_creating_rfe_lineplot.Rmd
@@
   for(k in 1:length(chrs)){print(c(i,k));
-    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
+    rfeModelResultsList <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/",
                                           i,
@@
                                           chrs[k],
-                                          "/rus/distance/TADrfe.rds"))
+                                          "/rus/distance/TADrfe_holdout.rds"))
     rfeModelResults <- rfeModelResultsList[[1]]
@@
 rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
-rfeperchr_summ <- rfeperchr %>%
+rfeperchr_summ_mean <- rfeperchr %>%
   dplyr::group_by(Variables) %>%
@@
                    PerformanceSD = sd(BA, na.rm = TRUE))
+rfeperchr_summ_med <- rfeperchr %>%
+  dplyr::group_by(Variables) %>%
+  dplyr::summarise(Performance = median(BA, na.rm = TRUE),
+                   PerformanceIQR = IQR(BA, na.rm = TRUE))
 
@@
                                           chrs[k],
-                                          "/rus/distance/TADrfe.rds"))
+                                          "/rus/distance/TADrfe_holdout.rds"))
     rfeModelResults <- rfeModelResultsList[[1]]
-    rfeModelResults <- rfeModelResults[,c(1,11)]
+    rfeModelResults <- rfeModelResults[,c(1,4:5)]
     rfeModelResults$CL <- i
@@
 }
-
-rfeperchr_summ <- rfeperchr %>%
+rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
+rfeperchr_summ_mean <- rfeperchr %>%
   dplyr::group_by(Variables) %>%
-  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
-                   PerformanceSD = sd(Accuracy, na.rm = TRUE))
+  dplyr::summarise(Performance = mean(BA, na.rm = TRUE),
+                   PerformanceSD = sd(BA, na.rm = TRUE))
+rfeperchr_summ_med <- rfeperchr %>%
+  dplyr::group_by(Variables) %>%
+  dplyr::summarise(Performance = median(BA, na.rm = TRUE),
+                   PerformanceIQR = IQR(BA, na.rm = TRUE))
 
@@
                                           chrs[k],
-                                          "/rus/distance/TADrfe_peakachu.rds"))
+                                          "/rus/distance/TADrfe_holdout_peakachu.rds"))
     rfeModelResults <- rfeModelResultsList[[1]]
@@
                                           chrs[k],
-                                          "/rus/distance/TADrfe_peakachu.rds"))
+                                          "/rus/distance/TADrfe_holdout_peakachu.rds"))
     rfeModelResults <- rfeModelResultsList[[1]]
-    rfeModelResults <- rfeModelResults[,c(1,11)]
+    rfeModelResults <- rfeModelResults[,c(1,4:5)]
     rfeModelResults$CL <- i
@@
 }
-
-rfeperchr_summ <- rfeperchr %>%
+rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
+rfeperchr_summ_mean <- rfeperchr %>%
   dplyr::group_by(Variables) %>%
-  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
-                   PerformanceSD = sd(Accuracy, na.rm = TRUE))
-
-ggplot(rfeperchr_summ, aes(x=Variables, y=Performance)) + 
-  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), 
-                width=2, 
-                size=1, 
-                color="blue") +
-  geom_line(size=2, color="blue") +
-  geom_point(size=4, color="blue") +
-  xlab("Number of top ranked annotations") +
-  ylab("Cross-Validated Accuracy") +
-  scale_color_discrete(name="Cell line")+
-  scale_x_continuous(breaks = c(2,4,8,16,32,52),
-                     labels = c(2,4,8,16,32,52))+
-  theme_minimal() +
-  theme_bw()+
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        #strip.text.x = element_text(size = 15),
-        #panel.spacing = unit(2, "lines"),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20),
-        plot.title = element_text(size=20),
-        legend.position = "bottom")
-```
-
-## LOLLIPOP
-
-### GM12878
-
-#### Optimal parameters: 10 kb, TFBS, distance type predictors, RUS
-
-```{r}
-chrs <- paste0("CHR",c(1:8,10:22))
-rfeperchr <- data.frame()
-for(i in c("GM12878")){
-  for(k in 1:length(chrs)){print(c(i,k));
-    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
-                                          i,
-                                          "/",
-                                          "10kb/results_by_chr/",
-                                          chrs[k],
-                                          "/rus/distance/TADrfe_lollipop.rds"))
-    rfeModelResults <- rfeModelResultsList[[1]]
-    rfeModelResults <- rfeModelResults[,c(1,11)]
-    rfeModelResults$CL <- i
-    rfeModelResults$Chromosome <- chrs[k]
-    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
-  }
-}
-
-rfeperchr_summ <- rfeperchr %>%
+  dplyr::summarise(Performance = mean(BA, na.rm = TRUE),
+                   PerformanceSD = sd(BA, na.rm = TRUE))
+rfeperchr_summ_med <- rfeperchr %>%
   dplyr::group_by(Variables) %>%
-  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
-                   PerformanceSD = sd(Accuracy, na.rm = TRUE))
-
-ggplot(rfeperchr_summ, aes(x=Variables, y=Performance)) + 
-  geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), 
-                width=2, 
-                size=1, 
-                color="red") +
-  geom_line(size=2, color="red") +
-  geom_point(size=4, color="red") +
-  xlab("Number of top ranked annotations") +
-  ylab("Cross-Validated Accuracy") +
-  scale_color_discrete(name="Cell line")+
-  scale_x_continuous(breaks = c(2,4,8,16,32,52),
-                     labels = c(2,4,8,16,32,52))+
-  theme_minimal() +
-  theme_bw()+
-  theme(axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 20),
-        axis.title.y = element_text(size = 20),
-        panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        #strip.text.x = element_text(size = 15),
-        #panel.spacing = unit(2, "lines"),
-        legend.text=element_text(size=15),
-        legend.title=element_text(size=20),
-        plot.title = element_text(size=20),
-        legend.position = "bottom")
-```
-
-### K562
-
-#### Optimal parameters: 10 kb, TFBS, distance type predictors, RUS
-
-```{r}
-chrs <- paste0("CHR",c(1:8,10:22))
-rfeperchr <- data.frame()
-for(i in c("K562")){
-  for(k in 1:length(chrs)){print(c(i,k));
-    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
-                                          i,
-                                          "/",
-                                          "10kb/results_by_chr/",
-                                          chrs[k],
-                                          "/rus/distance/TADrfe_lollipop.rds"))
-    rfeModelResults <- rfeModelResultsList[[1]]
-    rfeModelResults <- rfeModelResults[,c(1,11)]
-    rfeModelResults$CL <- i
-    rfeModelResults$Chromosome <- chrs[k]
-    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
-  }
-}
-
-rfeperchr_summ <- rfeperchr %>%
-  dplyr::group_by(Variables) %>%
-  dplyr::summarise(Performance = mean(Accuracy, na.rm = TRUE),
-                   PerformanceSD = sd(Accuracy, na.rm = TRUE))
+  dplyr::summarise(Performance = median(BA, na.rm = TRUE),
+                   PerformanceIQR = IQR(BA, na.rm = TRUE))
 
@@
 ```
+
+###########################
+
+# Plotting
+
+```{r}
+rfeperchr_gm12878_5kb_arrowhead_med <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/rfeperchr_gm12878_5kb_arrowhead_med.rds")
+rfeperchr_gm12878_10kb_peakachu_med <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/rfeperchr_gm12878_10kb_peakachu_med.rds")
+
+rfeperchr_summ_gm12878 <- rbind.data.frame(rfeperchr_gm12878_5kb_arrowhead_med,rfeperchr_gm12878_10kb_peakachu_med)
+rfeperchr_summ_gm12878$Tool <- c(rep("Arrowhead", nrow(rfeperchr_gm12878_5kb_arrowhead_med)),
+                                 rep("Peakachu", nrow(rfeperchr_gm12878_10kb_peakachu_med)))
+
+rfeperchr_k562_5kb_arrowhead_med <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/rfeperchr_k562_5kb_arrowhead_med.rds")
+rfeperchr_k562_10kb_peakachu_med <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/rfeperchr_k562_10kb_peakachu_med.rds")
+
+rfeperchr_summ_k562 <- rbind.data.frame(rfeperchr_k562_5kb_arrowhead_med,rfeperchr_k562_10kb_peakachu_med)
+rfeperchr_summ_k562$Tool <- c(rep("Arrowhead", nrow(rfeperchr_k562_5kb_arrowhead_med)),
+                                 rep("Peakachu", nrow(rfeperchr_k562_10kb_peakachu_med)))
+
+ggplot(rfeperchr_summ_gm12878, aes(x=Variables, y=Performance, color=Tool)) + 
+    geom_line(size=2,) +
+    geom_point(size=4, position = position_dodge(.9)) +
+    geom_errorbar(aes(ymin=Performance-(PerformanceIQR+.01), ymax=Performance+(PerformanceIQR+.01)), 
+                  width=4, 
+                  size=1,
+                  position = position_dodge(.9)) +
+    xlab("Number of top ranked annotations") +
+    ylab("Cross-Validated BA") + guides(color=guide_legend(nrow=2))+
+    scale_color_manual(name="Boundary Type", 
+                       values=c("blue", "red"))+
+    scale_x_continuous(breaks = c(2,4,8,16,32,52),
+                       labels = c(2,4,8,16,32,52))+
+    theme_minimal() +
+    theme_bw()+
+    theme(axis.text.x = element_text(size = 15),
+          axis.text.y = element_text(size = 15),
+          axis.title.x = element_text(size = 20),
+          axis.title.y = element_text(size = 20),
+          panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+          #strip.text.x = element_text(size = 15),
+          #panel.spacing = unit(2, "lines"),
+          legend.text=element_text(size=15),
+          legend.title=element_text(size=20),
+          plot.title = element_text(size=20),
+          legend.position = c(.75,.1))
+```

### 2020-08-14 Scripts_for_results/05_creating_importance_plot.Rmd
updated figures/tables

@@
   for(k in 1:length(chrs)){
-    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
+    rfeModelResultsList <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/",
                                           i,
@@
                                           chrs[k],
-                                          "/rus/distance/TADrfe.rds"))
+                                          "/rus/distance/TADrfe_holdout.rds"))
 
@@
 }
-
 rfeperchr <- do.call(rbind.data.frame, rfeperchr)
@@
 rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]
-
 rfe.set.mat <- as.matrix(rfeperchr[,-1])
 rownames(rfe.set.mat) <- rfeperchr$TFBS
-
 rfe.set.mat <- t(apply(rfe.set.mat,1,rev))
@@
                                           chrs[k],
-                                          "/rus/distance/TADrfe_peakachu.rds"))
+                                          "/rus/distance/TADrfe_holdout_peakachu.rds"))
 
@@
 rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]
-
 rfe.set.mat <- as.matrix(rfeperchr[,-1])
 rownames(rfe.set.mat) <- rfeperchr$TFBS
-
-rfe.set.mat <- t(apply(rfe.set.mat,1,rev))
-
-distance.col = dist(rfe.set.mat, method = "euclidean")
-cluster.col = hclust(distance.col, method = "average")
-my_palette <- colorRampPalette(c("white", "lightblue", "blue"))(ncol(rfe.set.mat))
-
-heatmap.2(t(rfe.set.mat),
-          #labRow=rownames(rfe.set.mat),
-          #labCol=colnames(rfe.set.mat),
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins=c(10,4),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          #keysize = 1.5,
-          #key.title = "Elastic-Net Coefficient",
-          dendrogram="column",     # only draw a row dendrogram,
-          Rowv = FALSE,
-          Colv = reorder(as.dendrogram(cluster.col), 37:1),
-          cexRow=.5,
-          cexCol=1,
-          #labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          rowsep=0:nrow(t(rfe.set.mat)),
-          colsep=0:ncol(t(rfe.set.mat)),
-          sepwidth=c(0.00001,0.00001),
-          sepcolor="black"
-)
-
-```
-
-## LOLLIPOP
-
-### GM12878
-
-#### Optimal parameters: 10 kb, TFBS, distance type predictors, RUS
-
-```{r}
-chrs <- paste0("CHR",c(1:8,10:22))
-rfeperchr <- list()
-for(i in c("GM12878")){
-  for(k in 1:length(chrs)){
-    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
-                                          i,
-                                          "/",
-                                          "10kb/results_by_chr/",
-                                          chrs[k],
-                                          "/rus/distance/TADrfe_lollipop.rds"))
-
-    set.size = 8
-    rfeModelResults <- rfeModelResultsList[[2]]
-    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
-    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
-    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
-    rfe.set <- rfe.set[rfe.order, ]
-    rfe.set$CHR <- chrs[k]
-    rfeperchr[[k]] <- rfe.set
-  }
-}
-
-rfeperchr <- do.call(rbind.data.frame, rfeperchr)
-rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
-names(rfeperchr) <- c("TFBS", chrs)
-rfeperchr[is.na(rfeperchr)] <- 0
-rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]
-
-rfe.set.mat <- as.matrix(rfeperchr[,-1])
-rownames(rfe.set.mat) <- rfeperchr$TFBS
-
-rfe.set.mat <- t(apply(rfe.set.mat,1,rev))
-
-distance.col = dist(rfe.set.mat, method = "euclidean")
-cluster.col = hclust(distance.col, method = "average")
-my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfe.set.mat))
-
-heatmap.2(t(rfe.set.mat),
-          #labRow=rownames(rfe.set.mat),
-          #labCol=colnames(rfe.set.mat),
-          #cellnote = ,  # same data set for cell labels
-          #main = "", # heat map title
-          notecol="black",      # change font color of cell labels to black
-          density.info="none",  # turns off density plot inside color legend
-          trace="none",         # turns off trace lines inside the heat map
-          margins=c(10,4),     # widens margins around plot
-          col=my_palette,       # use on color palette defined earlier
-          na.color = "gray",
-          #breaks=col_breaks,    # enable color transition at specified limits
-          key=FALSE,
-          #keysize = 1.5,
-          #key.title = "Elastic-Net Coefficient",
-          dendrogram="column",     # only draw a row dendrogram,
-          Rowv = FALSE,
-          Colv = reorder(as.dendrogram(cluster.col), 37:1),
-          cexRow=.5,
-          cexCol=1,
-          #labRow = FALSE,
-          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
-          #lhei=c(.5,6,0),
-          rowsep=0:nrow(t(rfe.set.mat)),
-          colsep=0:ncol(t(rfe.set.mat)),
-          sepwidth=c(0.00001,0.00001),
-          sepcolor="black"
-)
-
-```
-
-### K562
-
-#### Optimal parameters: 10 kb, TFBS, distance type predictors, RUS
-
-```{r}
-chrs <- paste0("CHR",c(1:8,10:22))
-rfeperchr <- list()
-for(i in c("K562")){
-  for(k in 1:length(chrs)){
-    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
-                                          i,
-                                          "/",
-                                          "10kb/results_by_chr/",
-                                          chrs[k],
-                                          "/rus/distance/TADrfe_lollipop.rds"))
-
-    set.size = 8
-    rfeModelResults <- rfeModelResultsList[[2]]
-    rfe.set <- rfeModelResults[rfeModelResults$Variables==set.size & rfeModelResults$Resample=="Fold1",]
-    rfe.set <- aggregate(rfe.set[, c("Overall")], list(rfe.set$var), mean)
-    rfe.order <- order(rfe.set[, c("x")], decreasing = TRUE)
-    rfe.set <- rfe.set[rfe.order, ]
-    rfe.set$CHR <- chrs[k]
-    rfeperchr[[k]] <- rfe.set
-  }
-}
-
-rfeperchr <- do.call(rbind.data.frame, rfeperchr)
-rfeperchr <- reshape(rfeperchr, idvar = "Group.1", timevar = "CHR", direction = "wide")
-names(rfeperchr) <- c("TFBS", chrs)
-rfeperchr[is.na(rfeperchr)] <- 0
-rfeperchr <- rfeperchr[order(rowMeans(rfeperchr[,-1], na.rm = TRUE),decreasing = TRUE),]
-
-rfe.set.mat <- as.matrix(rfeperchr[,-1])
-rownames(rfe.set.mat) <- rfeperchr$TFBS
-
 rfe.set.mat <- t(apply(rfe.set.mat,1,rev))
@@
 ```
+
+####################################
+
+#Plotting
+
+```{r}
+rfe.set.mat <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/impmat_gm12878_5kb_arrowhead.rds")
+rfe.set.mat <- rfe.set.mat[-13,]
+rfe.set.mat <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/impmat_gm12878_10kb_peakachu.rds")
+
+distance.col = dist(rfe.set.mat, method = "euclidean")
+#cluster.col = hclust(distance.col, method = "average")
+my_palette <- colorRampPalette(c("white", "lightblue", "blue"))(ncol(rfe.set.mat))
+#my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfe.set.mat))
+
+Heatmap(t(rfe.set.mat),
+        col=my_palette,
+        border=TRUE,
+        cluster_rows=FALSE,
+        clustering_distance_columns = "euclidean",
+        clustering_method_columns = "complete", #"ward.D",
+        show_row_names = FALSE,
+        show_column_names = FALSE,
+        show_column_dend = FALSE,
+        column_names_gp=gpar(fontsize = 20),
+        column_names_rot = 90,
+        column_names_centered = FALSE,
+        show_heatmap_legend = FALSE,
+        heatmap_legend_param = list(title = "Predictive\nImportance"),
+        rect_gp = gpar(col = "black", lwd = 1),
+        column_dend_side = "bottom",column_names_side = "bottom")
+
+```

### 2020-08-14 Scripts_for_results/09_visualizing_example_of_preciseTAD_predictions.Rmd
updated figures/tables

@@
 source("Z:/TAD_data_analysis/functions_for_R_package/TADrandomForest.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe2.R")
 source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
@@
                          resampling="rus",
-                         trainCHR=paste0("CHR",c(1:8,10:22))[-which(paste0("CHR",c(1:8,10:22))=="CHR22")],
-                         predictCHR=NULL,
+                         trainCHR=paste0("CHR",c(1:8,10:22))[-which(paste0("CHR",c(1:8,10:22))=="CHR14")],
+                         predictCHR="CHR14",
                          seed=123)
@@
                                      preprocess=FALSE, 
-                                     CHR="CHR22", 
+                                     CHR="CHR14", 
                                      resolution=5000)
@@
                       featureType="distance",
-                      CHR="CHR22",
-                      chromCoords=list(17000000,19000000),
+                      CHR="CHR14",
+                      chromCoords=list(50085000,50800000),
                       tadModel=tadModel[[1]],
-                      threshold=1.0,
+                      threshold=1,
                       flank=NULL,
@@
                       PTBR=TRUE,
-                      CLARA=FALSE,
+                      CLARA=TRUE,
                       samples=100)
 
-saveRDS(pt, "C:/Users/stili/Downloads/pt_chr21_15150000_17270000")
+#saveRDS(pt, "C:/Users/stili/Downloads/pt_chr21_15150000_17270000")
 ```
@@
 ```{r}
-tadModel <- readRDS("Z:/TAD_data_analysis/miscellaneous/tadModel.rds")
-pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")
+#tadModel <- readRDS("Z:/TAD_data_analysis/miscellaneous/tadModel.rds")
+#pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")
 
@@
 #seqDataTest <- c(15150000:17270000)
-seqDataTest <- c(70595000:71525000)
+seqDataTest <- c(50085000:50800000)
 
@@
 #CHR="CHR21"
-CHR="CHR1"
+CHR="CHR14"
 
@@
                            #basenum=c(15150000:17270000),
-                           basenum=c(70595000:71525000),
+                           basenum=c(50085000:50800000),
                            prob=predictions)

### 2020-08-14 Scripts_for_results/12_cross_cell_line_performances.Rmd
updated figures and tables

@@
   theme_bw()+
-  theme(axis.text.x = element_text(size = 10),
-        axis.text.y = element_text(size = 10),
-        axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15),
+  theme(axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 20),
+        axis.title.y = element_text(size = 20),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
-        strip.text.x = element_text(size = 10),
+        strip.text.x = element_text(size = 15),
         #panel.spacing = unit(2, "lines"),
-        legend.text=element_text(size=10),
-        legend.title=element_text(size=15),
-        plot.title = element_text(size=15),
+        legend.text=element_text(size=15),
+        legend.title=element_text(size=20),
+        plot.title = element_text(size=20),
         legend.position = "bottom")

### 2020-08-14 Scripts_for_results/14_evaluating_preciseTAD_parameters.Rmd
updated figures and tables

@@
 
-df <- data.frame(Overlap = c(length(unique(subjectHits(findOverlaps(flank(pt_1_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_1_1000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_1_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_1_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_1_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_1_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_1_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_1_10000_22[[2]])-.1,
+t = c(".95",".975",".99","1.0")
+eps = c(5000,10000,15000,20000,25000)
 
-length(unique(subjectHits(findOverlaps(flank(pt_99_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_99_1000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_99_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_99_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_99_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_99_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_99_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_99_10000_22[[2]]),
+NO1_ctcf = numeric()
+NO2_ctcf = numeric()
+NO3_ctcf = numeric()
+for(i in 1:length(t)){
+  for(j in 1:length(eps)){
+    print(c(t[i], eps[j]))
 
-length(unique(subjectHits(findOverlaps(flank(pt_975_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_975_1000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_975_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_975_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_975_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_975_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_975_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_975_10000_22[[2]]),
+    if(t[i]=="1.0" & eps[j]==5000){
+      pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
+    }else{
+      pt <- readRDS(paste0("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/chr22/pt",
+                           t[i],
+                           ".",
+                           eps[j],
+                           ".rds"))
+    }
 
-NA,
-length(unique(subjectHits(findOverlaps(flank(pt_95_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_95_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_95_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_95_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_95_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_95_10000_22[[2]]),
+    NO1_ctcf = rbind(NO1_ctcf,
+                length(unique(subjectHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt[[2]]))
 
-length(unique(subjectHits(findOverlaps(flank(pt_1_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_1_1000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_1_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_1_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_1_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_1_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_1_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_1_10000_22[[2]])-.1,
+    NO2_ctcf = rbind(NO2_ctcf,
+                length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt[[2]]))
 
-length(unique(subjectHits(findOverlaps(flank(pt_99_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_99_1000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_99_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_99_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_99_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_99_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_99_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_99_10000_22[[2]]),
+    NO3_ctcf = rbind(NO3_ctcf,
+                length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))*(1/(mean(mcols(distanceToNearest(pt[[2]],genomicElements.GR[[1]]))$distance)+1))/length(pt[[2]]))
 
-length(unique(subjectHits(findOverlaps(flank(pt_975_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_975_1000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_975_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_975_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_975_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_975_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_975_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_975_10000_22[[2]]),
+  }
+}
 
-NA,
-length(unique(subjectHits(findOverlaps(flank(pt_95_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_95_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_95_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_95_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_95_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_95_10000_22[[2]]),
+NO1_rad21 = numeric()
+NO2_rad21 = numeric()
+NO3_rad21 = numeric()
+for(i in 1:length(t)){
+  for(j in 1:length(eps)){
+    print(c(t[i], eps[j]))
 
-length(unique(subjectHits(findOverlaps(flank(pt_1_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_1_1000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_1_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_1_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_1_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_1_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_1_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_1_10000_22[[2]])-.1,
+    if(t[i]=="1.0" & eps[j]==5000){
+      pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
+    }else{
+      pt <- readRDS(paste0("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/chr22/pt",
+                           t[i],
+                           ".",
+                           eps[j],
+                           ".rds"))
+    }
 
-length(unique(subjectHits(findOverlaps(flank(pt_99_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_99_1000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_99_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_99_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_99_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_99_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_99_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_99_10000_22[[2]]),
+    NO1_rad21 = rbind(NO1_rad21,
+                     length(unique(subjectHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt[[2]]))
 
-length(unique(subjectHits(findOverlaps(flank(pt_975_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_975_1000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_975_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_975_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_975_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_975_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_975_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_975_10000_22[[2]]),
+    NO2_rad21 = rbind(NO2_rad21,
+                     length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt[[2]]))
 
-NA,
-length(unique(subjectHits(findOverlaps(flank(pt_95_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_95_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_95_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_95_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_95_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_95_10000_22[[2]]),
+    NO3_rad21 = rbind(NO3_rad21,
+                     length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))*(1/(mean(mcols(distanceToNearest(pt[[2]],genomicElements.GR[[2]]))$distance)+1))/length(pt[[2]]))
 
-length(unique(subjectHits(findOverlaps(flank(pt_1_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_1_1000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_1_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_1_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_1_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_1_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_1_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_1_10000_22[[2]])-.1,
+  }
+}
 
-length(unique(subjectHits(findOverlaps(flank(pt_99_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_99_1000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_99_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_99_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_99_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_99_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_99_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_99_10000_22[[2]]),
+NO1_smc3 = numeric()
+NO2_smc3 = numeric()
+NO3_smc3 = numeric()
+for(i in 1:length(t)){
+  for(j in 1:length(eps)){
+    print(c(t[i], eps[j]))
 
-length(unique(subjectHits(findOverlaps(flank(pt_975_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_975_1000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_975_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_975_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_975_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_975_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_975_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_975_10000_22[[2]]),
+    if(t[i]=="1.0" & eps[j]==5000){
+      pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
+    }else{
+      pt <- readRDS(paste0("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/chr22/pt",
+                           t[i],
+                           ".",
+                           eps[j],
+                           ".rds"))
+    }
 
-NA,
-length(unique(subjectHits(findOverlaps(flank(pt_95_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_95_2500_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_95_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_95_5000_22[[2]]),
-length(unique(subjectHits(findOverlaps(flank(pt_95_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_95_10000_22[[2]])),
+    NO1_smc3 = rbind(NO1_smc3,
+                      length(unique(subjectHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt[[2]]))
 
-Threshold = c(rep(c(rep("t=1.0",4),
-              rep("t=0.99",4),
-              rep("t=0.975",4),
-              rep("t=0.95",4)),4)),
+    NO2_smc3 = rbind(NO2_smc3,
+                      length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt[[2]]))
 
-Epsilon = rep(c("eps=1000",
-              "eps=2500",
-			  "eps=5000",
-			  "eps=10000"),16),
+    NO3_smc3 = rbind(NO3_smc3,
+                      length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))*(1/(mean(mcols(distanceToNearest(pt[[2]],genomicElements.GR[[3]]))$distance)+1))/length(pt[[2]]))
 
-Annotation = c(rep("CTCF", 16),
-               rep("RAD21", 16),
-			   rep("SMC3", 16),
-			   rep("ZNF143", 16))
-)
+  }
+}
 
-df$Epsilon <- factor(df$Epsilon, levels=c("eps=1000", "eps=2500", "eps=5000", "eps=10000"))
+NO1_znf143 = numeric()
+NO2_znf143 = numeric()
+NO3_znf143 = numeric()
+for(i in 1:length(t)){
+  for(j in 1:length(eps)){
+    print(c(t[i], eps[j]))
 
-ggplot(data=df, aes(x=Annotation, y=Overlap, fill=Annotation)) +
-  facet_grid(Epsilon ~ Threshold) +
-  geom_bar(stat='identity') +
-  ylim(0,1.5)+
-  ylab("Normalized Overlap") +
-  xlab("Annotation") +
-  guides(fill=FALSE) +
+    if(t[i]=="1.0" & eps[j]==5000){
+      pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
+    }else{
+      pt <- readRDS(paste0("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/chr22/pt",
+                           t[i],
+                           ".",
+                           eps[j],
+                           ".rds"))
+    }
+
+    NO1_znf143 = rbind(NO1_znf143,
+                     length(unique(subjectHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt[[2]]))
+
+    NO2_znf143 = rbind(NO2_znf143,
+                     length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt[[2]]))
+
+    NO3_znf143 = rbind(NO3_znf143,
+                     length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))*(1/(mean(mcols(distanceToNearest(pt[[2]],genomicElements.GR[[4]]))$distance)+1))/length(pt[[2]]))
+
+  }
+}
+
+params_df <- rbind.data.frame(cbind(NO1_ctcf,NO2_ctcf,NO3_ctcf),
+      cbind(NO1_rad21,NO2_rad21,NO3_rad21),
+      cbind(NO1_smc3,NO2_smc3,NO3_smc3),
+      cbind(NO1_znf143,NO2_znf143,NO3_znf143))
+params_df$Threshold <- rep(c(rep("0.95", 5),
+                         rep("0.975", 5),
+                         rep("0.99", 5),
+                         rep("1.0", 5)),4)
+params_df$eps <- rep(c("5000","10000","15000","20000","25000"), 4*4)
+params_df$eps <- factor(params_df$eps, levels=c("5000","10000","15000","20000","25000"))
+params_df$Annotation <- c(rep("CTCF", 20),
+                          rep("RAD21", 20),
+                          rep("SMC3", 20),
+                          rep("ZNF143", 20))
+
+ggplot(params_df, aes(x=eps, y=V1, color=Annotation, group=Annotation)) +
+  facet_grid(. ~ Threshold)+
+  geom_line(size=2, position=position_dodge(0.5))+
+  geom_point(size=5, position=position_dodge(0.5))+
   theme_minimal() +
   theme_bw()+
-  theme(axis.text.x = element_text(size=10,
+  xlab("eps") + 
+  ylab("Normalized Overlap") + 
+  theme(axis.text.x = element_text(size=15,
                                    angle = 45, 
                                    #margin = ggplot2::margin(t = 35),
-                                   hjust = 1),
-        axis.text.y = element_text(size = 10),
-        axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15),
-        panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        #strip.background.x = element_blank(),
-        #strip.background.y = element_blank(),
-        legend.text=element_text(size=10),
-        legend.title=element_text(size=15),
-        plot.title = element_text(size=15))
+                                   hjust = 1
+  ),
+  axis.text.y = element_text(size = 15),
+  axis.title.x = element_text(size = 20),
+  axis.title.y = element_text(size = 20),
+  strip.text.x = element_text(size = 15),
+  strip.text.y = element_text(size = 15),
+  legend.text=element_text(size=15),
+  legend.title=element_text(size=20),
+  plot.title = element_text(size=20),
+  legend.position="bottom")
 ```

### 2020-08-14 Manuscript/manuscript.Rmd
updated nodesize
updated text to match fig 5

@@
 The number of trees (*ntree*) that were aggregated for each RF model was set to 500.
-The minimum number of observations per root node (*nodesize*) was set to 1.
+The minimum number of observations per root node (*nodesize*) was set to .01% of the rows in the data.
 The binned data for the holdout chromosome $i$ was reserved for testing.
@@
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
-Signal heatmaps indicated that our predicted boundaries were more frequently co-localized with CTCF sites than either Arrowhead or Peakachu boundaries alone (Figure 5 B-C).
-Likewise, *preciseTAD* boundaries were also more co-localized with other molecular drivers of 3D chromatin including RAD21, SMC3, and ZNF143 for both GM12878 and K562 cell lines (Supplementary Figures 5-6).
-When compared to called TAD or loop boundaries, *preciseTAD* boundaries were statistically significantly closer to the same cell line-specific top ranked TFBS (p<0.001 and p<0.001 versus Arrowhead and Peakachu respectively) (Figure 5D, Supplementary Figure 7).
+Peak regions associated with known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143 were found to co-localize more frequently around *preciseTAD* predicted boundaries (Figure 5B).
+Furthermore, signal heatmaps indicated that our predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Figure 5 C-D; Supplementary Figures 5-6).
+When compared to called TAD or loop boundaries, *preciseTAD* boundaries were statistically significantly closer to the same cell line-specific top ranked TFBS (p<0.001 and p<0.001 versus Arrowhead and Peakachu respectively) (Figure 5E, Supplementary Figure 7).
 These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
@@
 Boundaries involving Arrowhead were flanked by 5 kb, while boundaries involving Peakachu were flanked by 10 kb.
-We found that 35% of *preciseTAD* predicted TAD boundaries and 55% of *preciseTAD* predicted loop boundaries were were conserved between cell lines, compared to only 26% and 55% for Arrowhead and Peakachu alone (Figure 5E).
+We found that 35% of *preciseTAD* predicted TAD boundaries and 55% of *preciseTAD* predicted loop boundaries were were conserved between cell lines, compared to only 26% and 55% for Arrowhead and Peakachu alone (Figure 5F).
 The better conservation of *preciseTAD*-predicted boundaries further support the notion of their higher biological relevance.
@@
 The black line represents the predicted probability of each base being a TAD boundary.
-(B)Bigwig visualization of known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143.
+(B) Genome browse visualization of bigwig files for known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143.
 (C) Enriched heatmaps comparing the enrichment of CTCF signal around ARROWHEAD TAD boundaries and preciseTAD boundaries, and (D) around Peakachu loop boundaries and preciseTAD for the entire genome.

### 2020-08-15 Manuscript/manuscript.Rmd
Abstract and intro polishing

@@
 The relatively low resolution of Hi-C data (regions of several kilobases in size) prevents precise mapping of domain boundaries.
-TAD and loop boundaries have been characterized by the presence of CTCF and members of cohesin complex binding sites, typically mapped at higher precision.
+TAD and loop boundaries have been characterized by the presence of CTCF and members of cohesin complex binding sites, and other genomic annotations.
+They are typically defined at high resolution (~100bp), suggesting they can inform the precise location of domain boundaries.
 Several methods have been developed to leverage genome annotation  data for predicting TAD/loop boundaries; however, they overlooked key characteristics of the data, such as spatial associations between an annotation and a boundary.
@@
 Boundaries predicted by preciseTAD were more enriched for CTCF, RAD21, SMC3, and ZNF143 sites and more conserved across cell lines, highlighting their higher biological significance.
+The model trained in one cell line perform well in predicting boundaries in another cell line.
 
 **Conclusion** Our results outline strategies for predictive modeling of 3D genomic domains using genome annotation data.
-The precise identification of TAD boundaries will improve our understanding of how genomic regulators shapes the 3D structure of the genome.
+The precise identification of domain boundaries will improve our understanding of how genomic regulators are associated with the 3D structure of the genome.
 
@@
 
-The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of important 3-dimensional (3D) spatial constructs within the human genome such as chromatin loops [@rao20143d], Topologically Associated Domains (TADs) [@nora2012spatial;@dixon2012topological], and A/B compartments [@lieberman2009comprehensive].
+The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of 3-dimensional (3D) spatial constructs within the human genome such as chromatin loops [@rao20143d], Topologically Associated Domains (TADs) [@nora2012spatial;@dixon2012topological], and A/B compartments [@lieberman2009comprehensive].
 At kilobase scale, gene promoters are often connected via distal regulatory elements, such as enhancers, through chromatin loops, thereby regulating gene expression [@Lupianez:2015aa; @Franke:2016aa].
@@
 
-Several methods have been proposed to identify the genomic coordinates of TAD boundaries (reviewed in [@Zufferey:2018aa; @forcato2017comparison]), and chromatin loops [@rao20143d; @Ay:2014aa; @Heinz:2010aa; @salameh2019supervised].
-However, a key limitation among most of these TAD- and loop callers, referred hereafter as domain callers, is that they are heavily reliant on Hi-C data *resolution*.
+Several methods have been proposed to identify genomic coordinates of TADs (reviewed in [@Zufferey:2018aa; @forcato2017comparison]), and chromatin loops [@rao20143d; @Ay:2014aa; @Heinz:2010aa; @salameh2019supervised].
+However, a key limitation among most of these TAD- and loop callers is that they are heavily reliant on Hi-C data *resolution*.
 Resolution refers to the sizes of genomic regions (bins) used to segment the linear genome [@li2019comparison].
-Lower resolutions contribute to larger bin sizes, which lead to uncertainty in the location of TAD boundaries.
+Lower resolutions contribute to larger bin sizes, which lead to uncertainty in the location of boundaries.
 Due to high sequencing costs, most available Hi-C datasets have relatively low resolution, ranging from 25 kb to 100 kb.
 Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth, obtaining high resolution remains difficult [@schmitt2016genome].
-While these low resolution Hi-C datasets can be used to probe higher order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define TADs and chromatin loops [@fudenberg2016formation].
+While these low resolution Hi-C datasets can be used to probe higher order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define TAD and loop boundaries [@fudenberg2016formation].
 
-Another limitation among domain callers is that they disregard prior knowledge about functional genomic annotations associated with TAD and loop boundaries.
+Another limitation among domain callers is that they disregard prior knowledge about functional genomic annotations associated with TAD and loop boundaries, referred hereafter as domain boundaries.
 The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been identified as components of the loop extrusion model, whereby DNA is extruded through cohesin rings forming chromatin loops [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
-Additionally, distinct patterns of histone modifications have also been shown to be present at boundaries, including H3K36 timethylation (H3K36me3) [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
+Additionally, distinct patterns of histone modifications have also been shown to be present at boundaries, including H3K36me3 [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
 These genomic annotations are obtained using chromatin immunoprecipitation followed by high-throughput DNA sequencing (ChIP-seq).
 The resolution of ChIP-seq experiments is typically on the order of tens to hundreds of bases [@mendoza2009genome], well below the resolution of Hi-C data (tens of kilobases; 750 bp is the highest resolution of Hi-C data to date [@bonev2017multiscale]).
-Therefore, leveraging precisely mapped genomic annotations in a supervised machine learning framework provides the possibility of more precisely predicting the locations of TAD (or loop) boundaries.
+Therefore, leveraging precisely mapped genomic annotations in a supervised machine learning framework provides the possibility of more precisely predicting the locations of domain boundaries.
 
-Here we present *preciseTAD*, an R package for implementing an optimally tuned machine learning framework for precise identification of domain boundaries using genome annotation data.
+We present *preciseTAD*, an R package implementing an optimally tuned machine learning framework for precise identification of domain boundaries using genome annotation data.
 Our method utilizes the random forest (RF) algorithm trained on chromatin segmentation (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) data.
@@
 We demonstrate that predictions made by *preciseTAD* are more enriched for known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143.
-Further, we show that *preciseTAD* boundaries are more conserved across cell lines.
-This improved precision in TAD and loop boundary location can provide insight into the role of genomic regulators on the 3D genome organization.
+Further, we show that *preciseTAD* boundaries are more conserved across cell lines, and the model trained in one cell line can predict boundaries in another cell line.
+This improved precision in domain boundary location can provide insight into the association between genomic regulators and the 3D genome organization.
 The *preciseTAD* R package is freely available on GitHub (https://github.com/dozmorovlab/preciseTAD) and on Bioconductor (submitted).

### 2020-08-15 Manuscript/manuscript.Rmd
Methods polishing

@@
 Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop anchor.
-Chromosome 9 was excluded from all downstream analyses due to sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
+Chromosome 9 was excluded from all downstream analyses due to the sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
 Cell-line-specific genomic annotations (BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 2).
@@
 
-In Hi-C, each chromosome is binned into non-overlapping regions of length *r*, typically 5 kb and above.
+In Hi-C, each chromosome is binned into non-overlapping regions of length *r*, typically, 5 kb and above.
 The *r* parameter defines the resolution of Hi-C data.
@@
 
-Cell line-specific genomic annotations were used to build the predictor space for our boundary prediction framework.
+Cell-line-specific genomic annotations were used to build the predictor space.
 Bins were annotated by one of either the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average signal strength of the corresponding annotation (*Peak Signal Strength*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*) (Figure 1B).
-A ($log_2 + 1$)-transformation of distance was used to account for the skewness present in the distributions of genomic distances.
+A ($log_2 + 1$)-transformation of distance was used to account for the skewness of the distance distributions.
 Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin segmentations lack signal values.
@@
 
-To assess the impact of class imbalance (CI), defined as the proportion of boundary regions to non-boundary regions, we evaluated three re-sampling techniques including *Random Over-Sampling (ROS)*, *Random Under-Sampling (RUS)*, and *Synthetic Minority Over-Sampling Technique (SMOTE)*.
+To assess the impact of class imbalance (CI), defined as the proportion of boundary regions to non-boundary regions, we evaluated three re-sampling techniques.
+These include *Random Over-Sampling (ROS)*, *Random Under-Sampling (RUS)*, and *Synthetic Minority Over-Sampling Technique (SMOTE)*.
 For ROS, the minority class was sampled with replacement to obtain the same number of data points in the majority class.
@@
 In doing so, we estimated the near optimal number of necessary features to include in the best fitting RF model.
-The best performing subset was identified, ranging from 2 to the maximum number of features by powers of 2.
+The best performing subset was identified, ranging from 2 to the maximum number of features incremented by the power of 2.
 We then aggregated the predictive importance of the union of the optimal set of features across chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top ranked annotations for predicting boundary regions.
@@
 To investigate whether we could alleviate resolution limitations of conventional domain calling tools, we developed *preciseTAD*, an algorithm that leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution.
-To demonstrate, we implemented an optimally trained RF model using the framework described above.
-That is, a random forest model was built on the optimal combination of predictor type (predictor space), re-sampling technique (class balancing correction), and top ranked annotations (most informative genomic elements) to maximally accurately predict boundaries at base _Hi-C resolution level_.
+A random forest model was built on the optimal combination of predictor type (predictor space), re-sampling technique (class balancing correction), and top ranked annotations (most informative genomic elements) to maximally accurately predict boundaries at the _Hi-C resolution level_.
 
-To precisely identify boundary locations, we first construct a _base-level resolution_ predictor space for a particular chromosome *i*.
-We then apply our optimally trained RF model on the base-level predictor space to extract the probability vector, $p_{n_{i}}$, denoting each base's probability of being a boundary point.
+To precisely identify boundary locations, we first constructed a _base-level resolution_ predictor space for a particular chromosome *i*.
+We then apply our optimally trained RF model on the base-level predictor space to extract the probability vector, $p_{n_{i}}$, denoting each base's probability of being a boundary.
 Here, $n_{i}$ represents the length of chromosome *i*.
@@
 The resulting clusters of highly predictive bases identified by DBSCAN were termed *preciseTAD boundary regions* (PTBR).
-To precisely identify a single base among each PTBR, *preciseTAD* then implements an extension of partitioning around medoids (PAM), known as CLARA (**Clustering Large Applications**) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
-The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative and biologically meaningful base coordinate within each clustered PTBR.
+To precisely identify a single base among each PTBR, *preciseTAD* then implements an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
+The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative base coordinate within each clustered PTBR.
 
-The DBSCAN algorithm takes two parameters, *MinPts* and *eps* ($\epsilon$).
+The DBSCAN algorithm has two parameters, *MinPts* and *eps* ($\epsilon$).
 The *MinPts* parameter was set to the recommended value of 3, representing $1+dim(data)$ [@hahsler2019dbscan].
-To decide on the optimal value of *t* and $\epsilon$ in *preciseTAD*, we considered the normalized enrichment of flanked predicted boundaries, defined as
+To decide on the optimal value of *t* and $\epsilon$ in *preciseTAD*, we considered the normalized enrichment $N_{e}$ of flanked predicted boundaries, defined as
 
@@
 Next, we assessed the biological significance of our predicted boundaries by their association with several known molecular drivers of 3D chromatin architecture including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
-To do so, we used the **computeMatrix** and **plotHeatmap** tools offered by deepTools (version 2.0) [@ramirez2016deeptools] via integration with Galaxy (version 3.3.2.0.0) [@afgan2018galaxy].
+To do so, we used the *computeMatrix* and *plotHeatmap* tools offered by deepTools (version 2.0) [@ramirez2016deeptools] via integration with Galaxy (version 3.3.2.0.0) [@afgan2018galaxy].
 Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum tests.
@@
 All statistical analyses were performed in R version 4.0.1.
-The alpha level of significance was set to 0.05 for all statistical tests.
+The significance level was set to 0.05 for all statistical tests.
 

### 2020-08-15 Manuscript/manuscript.Rmd
Results polishing

@@
 
-In our ML framework boundary regions were defined as genomic bins containing a called boundary ($Y = 1$), while non-boundary regions were defined as bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
+Boundary regions were defined as genomic bins containing a called boundary ($Y = 1$), while non-boundary regions were defined as bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
 The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 3).
@@
 
-A total of 77 cell line-specific functional genomic annotations were used to build the predictor space.
+A total of 77 cell-line-specific genomic annotations were used to build the predictor space.
 These included BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 2).
 Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
-These included signal strength association (Signal), direct (OC), proportional (OP), and spatial (Distance) relationships (see Methods).
-A ($log_2 + 1$)-transformation of distance was used to account for the skewness present in the distributions of genomic distances (Supplementary Figure 1).
+These included signal strength association (Signal), direct (OC), proportional (OP), and spatial ($log_2 + 1$ Distance) relationships (see Methods, Supplementary Figure 1).
 
@@
 ![**Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for GM12878 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
+Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
 
@@
 
-## Predictive importances confirmed biological functionality of CTCF, RAD21, SMC3, and ZNF143 at TAD boundaries
+## Predictive importances confirmed biological role of CTCF, RAD21, SMC3, and ZNF143 for boundary formation
 
@@
 We further optimized our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
-In summary, our model was able to yield the top molecular drivers of the 3D architecture of the human genome, components of the popular loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
+In summary, our model was able to yield the known molecular drivers of the loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
 
@@
 We found that training and testing using Arrowhead ground truth TAD boundaries and genomic elements from GM12878 resulted in an average AUC=0.845 (Figure 4D).
-However when training on GM12878 and testing on K562, our model's average AUC only marginally decreased to 0.803.
+When training on GM12878 and testing on K562, our model's average AUC only marginally decreased to 0.803.
 Likewise, training and testing on Peakachu resulted in an average AUC=0.885 and decreased only slightly to 0.868 when trained on GM12878 and tested on K562.
@@
 
-Using our optimally built random forest model trained on Arrowhead/Peakachu boundaries, we attempted to predict TAD/loop boundaries at base resolution.
-Intuitively, the predictor-response space was built on a base-resolution level, and the model trained on a bin-level space was used to predict the probability of each base being a boundary.
+Using our optimally built random forest model trained on Arrowhead/Peakachu boundaries, we attempted to predict boundaries at base resolution.
+Intuitively, instead of bin-level annotations, the predictor-response space was built on a base-level, that is, each base was associated with the corresponding genomic annotation.
+The model trained on a bin-level space was then applied on a base-level space to predict the probability of each base being a boundary.
 Our method, referred to as *preciseTAD*, uses density-based hierarchical clustering (DBSCAN) and a scalable partitioning around mediods clustering (CLARA) to predict the boundary location at base resolution (see Methods).
 
-When built using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb respectively, *preciseTAD* was able to predict a total of 7,846 TAD and 15,838 chromatin loop boundaries on GM12878, as well as 8,883 TAD and 11,016 chromatin loop boundaries on K562.
-Noticeably, we reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Supplementary Table 3).
-This can be attributed to Arrowhead's inflation of called TADs, especially at higher resolutions, that often do not correspond to intra-chromosomal contacts featured on a contact matrix.
+When built using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb respectively, *preciseTAD* was able to predict a total of 7,846 TAD and 15,838 chromatin loop boundaries on GM12878, as well as 8,883 TAD and 11,016 chromatin loop boundaries on K562 [???
+Need them in Supplementary Table 4, Excel, BED format, sheet 1 - GM12878 PTBR, sheet 2 - GM12878 PTBP, sheet 3,4 - K562.
+Supp tables 1, 2, 3 are OK, renumber subsequent.
+Write legend].
+We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Supplementary Table 3).
+This can be attributed to Arrowhead's inflation of called TADs, especially at higher resolutions, that, when visualized, often do not correspond to intra-chromosomal contacts featured on a contact matrix.
 Additionally, *preciseTAD* boundaries were visually more likely to demarcate high concentrations of intra-chromosomal contacts as can be seen on a Hi-C contact matrix (Figure 5A).
 *preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Supplementary Table 3).
-This can be contributed to the fact that *preciseTAD* leverages four known drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143, contrasting Peakachu which considers only CTCF sites as true positives.
+This can be attributed to the fact that *preciseTAD* leverages four known drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143, contrasting Peakachu which considers only CTCF sites to mark the predicted boundaries as true positives.
 These results suggest that genome annotation-driven predicted boundaries may be more biologically relevant, in contrast to boundaries detected from Hi-C data alone.
@@
 This is expected as loop boundaries (Peakachu) are more abundant, while TAD boundaries (Arrowhead) represent the narrower level of the 3D chromatin organization.
-Together with the results on Figure 4, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar protein complexes.
+Together with the results on Figure 4, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop domain boundaries may be driven by similar molecular mechanisms.
 

### 2020-08-15 Manuscript/manuscript.Rmd
Discussion polishing

@@
 Here, $n_{i}$ represents the length of chromosome *i*.
-A threshold (*t*) is specified on $p_{n_{i}}$, such that base coordinates with $p_{n_{i}} \ge t$ are extracted.
+A threshold ($t$) is specified on $p_{n_{i}}$, such that base coordinates with $p_{n_{i}} \ge t$ are extracted.
 Next, density-based spatial clustering of applications with noise (DBSCAN; version 1.1-5) is applied to the matrix of pairwise genomic distances between bases with $p_{n_{i}} \ge t$.
@@
 The *MinPts* parameter was set to the recommended value of 3, representing $1+dim(data)$ [@hahsler2019dbscan].
-To decide on the optimal value of *t* and $\epsilon$ in *preciseTAD*, we considered the normalized enrichment $N_{e}$ of flanked predicted boundaries, defined as
+To decide on the optimal value of $t$ and $\epsilon$ in *preciseTAD*, we considered the normalized enrichment $N_{e}$ of flanked predicted boundaries, defined as
 
@@
 We present *preciseTAD*, a machine learning approach for precise prediction of TAD or loop boundaries from functional genomic annotations.
-*preciseTAD* leverages a random forest (RF) classification model built on ground truth TAD/loop boundaries obtained from TAD/loop calling tools and genomic annotations as the predictor space.
-We benchmarked *preciseTAD* against two boundary calling tools, Arrowhead [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
-We applied *preciseTAD* on cell line-specific boundaries and annotation data from both GM12878 and K562.
+*preciseTAD* leverages a random forest (RF) classification model built on ground truth TAD/loop boundaries obtained from domain calling tools, and genomic annotations as the predictor space.
+*preciseTAD* was benchmarked against two boundary calling tools, Arrowhead [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
 We first optimized our RF model by systematically comparing different combinations of genome binning (resolution), feature engineering procedures, and re-sampling techniques.
-We show that genomic distance between high-resolution boundary regions and transcription factor binding sites, coupled with random under-sampling results in best model performance.
-We demonstrate that binding of four transcription factors (SMC3, RAD21, CTCF, ZNF143) are sufficient for accurate TAD and loop boundary predictions.
-Applied to each annotated base, the model predicts probability for each base to be a boundary, and, coupled with spatial clustering (DBSCAN) and scalable partition around medoids clustering (CLARA), allows for the detection of boundaries at the base-level resolution.
+Our results demonstrate that genomic distance between high-resolution boundary regions and transcription factor binding sites, coupled with random under-sampling results in best model performance.
+We demonstrate that binding of four transcription factors (SMC3, RAD21, CTCF, ZNF143) are sufficient for accurate boundary predictions.
+Applied to each annotated base, the model predicts probability for each base to be a boundary.
+Further, coupled with spatial clustering (DBSCAN) and scalable partition around medoids clustering (CLARA), it allows for the detection of boundaries at the base-level resolution.
 *preciseTAD* is implemented as an R package, and allows for precise prediction of boundaries for any cell type for which the corresponding genomic annotations are available.
@@
 We showed that information about only four transcription factors (SMC3, RAD21, CTCF, ZNF143) is necessary and sufficient for accurate boundary prediction, outperforming histone modification- and BroadHMM-built models [@Moore:2015aa; @Al-Bkhetan:2018aa].
-These are known components of the loop extrusion model, an established theory for how loops are made by a ring-shaped adenosine triphosphatase complex called cohesin [@hansen2018recent; @sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
+These are known components of the loop extrusion model, an established theory of how loops are made by a ring-shaped adenosine triphosphatase-driven complex called cohesin [@hansen2018recent; @sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
 Interestingly, the same transcription factors accurately predicted both TAD and loop boundaries, suggesting similarity of the mechanisms of TAD and loop formation.
@@
 
-Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC).
+<!-- Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC).
 Our aim was to have a balanced metric sensitive to class imbalance such that it would not favor one component of the confusion matrix.
@@
 The BA benefits from incorporating all components of the confusion matrix, while also being sensitive to class imbalance, a necessary characteristic when comparing performances to models built using no data re-sampling.
-[???refer to supp tables 4 and 5 here when ready]
+[???refer to supp tables 4 and 5 here when ready] -->
 
@@
 We show that, unlike Arrowhead, *preciseTAD* does not inflate the number of predicted boundaries, instead, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
-*preciseTAD* TAD and loop boundaries were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops are dynamic structures generated by similar mechanisms [@hansen2018recent].
-Likewise, *preciseTAD* boundaries were found to be more conserved between GM12878 and K562 cell lines, a known feature among the 3D architecture of the human genome, further highlighting their biological significance.
+*preciseTAD* boundaries were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops may be generated by similar mechanisms [@hansen2018recent].
+Likewise, *preciseTAD* boundaries were more conserved between GM12878 and K562 cell lines, a known feature among the 3D architecture of the human genome, further highlighting their biological significance.
 
-*preciseTAD* offers flexibility in controlling both the number of TAD(loop) boundaries as well as the distance between them.
-The two primary parameters are the probability threshold (*t*) and $\epsilon$ (refered to as eps; parameter of DBSCAN).
+*preciseTAD* offers flexibility in controlling both the number of predicted boundaries as well as the distance between them.
+The two primary parameters are the probability threshold $t$ and $\epsilon$ (referred to as eps; parameter of DBSCAN).
 The combination of these two quantities change the resulting number of predicted boundaries from *preciseTAD*.
-A lower threshold and $\epsilon$ will result in more clusters of bases, and therefore, more boundaries.
-As a heuristic, we evaluated the pairwise combination of 4 different thresholds ($t=(0.95,0.975,0.99,1.0)$) and 4 different $eps$ values ($\epsilon=(r, 2r, 3r, 4r, 5r)$)), where $r=5000$, the optimal resolution.
-We found that the normalized overlaps--calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries --between top TFBS sites and flanked preciseTAD boundaries were maximized for combinations of t=1.0 and $eps=r$ (Supplementary Figure 9).
+Lower values of $t$ and $\epsilon$ will result in more clusters of bases, and therefore, more boundaries.
+As a heuristic, we evaluated the pairwise combination of four different thresholds ($t=(0.95,0.975,0.99,1.0)$) and four different $eps$ values ($\epsilon=(r, 2r, 3r, 4r, 5r)$)), where $r=5000$, the optimal resolution.
+We found that the normalized overlaps--calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries --between top TFBS sites and flanked preciseTAD boundaries were maximized for combinations of $t=1.0$ and $eps=r$ (Supplementary Figure 9).
 
 A limitation of *preciseTAD* is that it is dependent on "ground truth" boundaries provided by a user-defined domain caller.
-Given the wide variety of domain callers and their variable performance [@Zufferey:2018aa; @forcato2017comparison], it is hard to define "ground truth" TAD boundaries.
+Given the wide variety of domain callers and their variable performance [@Zufferey:2018aa; @forcato2017comparison], it is hard to define "ground truth" boundaries.
 <!--Ideally we would benchmark *preciseTAD* against simulated boundaries.
@@
 We introduce *preciseTAD*, an open source R package for leveraging random forests to predict TAD/loop boundaries at base resolution.
-We hope that *preciseTAD* will serve as an efficient and easy-to-use tool to further explore the 3D organization of the genome.
+We hope that *preciseTAD* will serve as an efficient and easy-to-use tool to further exploration of the 3D organization of the genome.
 

### 2020-08-15 Manuscript/manuscript.Rmd
Update supplementary legends

@@
 **Additional File 1**.
-An example script for applying the Arrowhead tool to in situ Hi-C data (HIC001-HIC018) for resolutions 5kb, 10kb, 25kb, 50kb, 100kb to obtain chromosome-specific TAD boundaries on the GM12878 cell line.
+An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions.
 <!--Prior to implementing SpectralTAD, the dump command offered by juicer [@durand2016juicer] was used to extract the contacts in sparse data matrix format.-->
@@
 
-**Supplementary Table 2.** A complete list of the genomic annotations used to build the predictor space for all downstream models.
+**Supplementary Table 2.** A complete list of genomic annotations used to build the predictor space for all downstream models.
 The GRCh37/hg19 human genome assembly was used.
-“Genomic Class” - broad category of genomic features, “Element” - names of genomic features, “Cell Type-Specific Source” - download URL specific to the cell line (not all annotations were provided by the same institutions).
+"Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
 
@@
 
-**Supplementary Figure 1.** Density curves illustrate the normalization of distances before (red) and after (blue) performing a $log_{2}$ transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines, respectively.
+**Supplementary Figure 1.** Density curves of distances before (red) and after (blue) performing a $log_{2}$ transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines, respectively.
 Distances are measured as the number of bases from the center of a genomic bin to the center of the nearest genomic annotation.
-All genomic annotations were used.
-Each density curve represents an individual genomic annotation.
+Each density curve represents an individual genomic annotation (77 total).
 
@@
 Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for K562 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.
+Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.
 
@@
 Distance-type predictors combined with random under-sampling or SMOTE re-sampling yielded optimal predictive performance Peakachu loop boundaries at 10 kb resolution.** Averaged balanced accuracies are compared for A) GM12878 and B) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.
+Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.
 

### 2020-08-15 Manuscript/manuscript.Rmd
Grammarly fixes

@@
 Boundaries predicted by preciseTAD were more enriched for CTCF, RAD21, SMC3, and ZNF143 sites and more conserved across cell lines, highlighting their higher biological significance.
-The model trained in one cell line perform well in predicting boundaries in another cell line.
+The model trained in one cell line performs well in predicting boundaries in another cell line.
 
@@
 The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of 3-dimensional (3D) spatial constructs within the human genome such as chromatin loops [@rao20143d], Topologically Associated Domains (TADs) [@nora2012spatial;@dixon2012topological], and A/B compartments [@lieberman2009comprehensive].
-At kilobase scale, gene promoters are often connected via distal regulatory elements, such as enhancers, through chromatin loops, thereby regulating gene expression [@Lupianez:2015aa; @Franke:2016aa].
+At the kilobase scale, gene promoters are often connected via distal regulatory elements, such as enhancers, through chromatin loops, thereby regulating gene expression [@Lupianez:2015aa; @Franke:2016aa].
 Further, at the megabase scale, TADs represent regions on the linear genome, that are highly self-interacting.
@@
 Several methods have been proposed to identify genomic coordinates of TADs (reviewed in [@Zufferey:2018aa; @forcato2017comparison]), and chromatin loops [@rao20143d; @Ay:2014aa; @Heinz:2010aa; @salameh2019supervised].
-However, a key limitation among most of these TAD- and loop callers is that they are heavily reliant on Hi-C data *resolution*.
+However, a key limitation among most of these TAD- and loop callers is that they rely heavily on Hi-C data *resolution*.
 Resolution refers to the sizes of genomic regions (bins) used to segment the linear genome [@li2019comparison].
@@
 Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth, obtaining high resolution remains difficult [@schmitt2016genome].
-While these low resolution Hi-C datasets can be used to probe higher order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define TAD and loop boundaries [@fudenberg2016formation].
+While these low-resolution Hi-C datasets can be used to probe higher-order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define TAD and loop boundaries [@fudenberg2016formation].
 
@@
 This approach circumvents resolution restrictions of Hi-C data, allowing for the precise detection of biologically meaningful boundaries.
-We demonstrate that predictions made by *preciseTAD* are more enriched for known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143.
+We demonstrate that *preciseTAD* predictions are more enriched for known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143.
 Further, we show that *preciseTAD* boundaries are more conserved across cell lines, and the model trained in one cell line can predict boundaries in another cell line.
-This improved precision in domain boundary location can provide insight into the association between genomic regulators and the 3D genome organization.
+This improved precision in the domain boundary location can provide insight into the association between genomic regulators and the 3D genome organization.
 The *preciseTAD* R package is freely available on GitHub (https://github.com/dozmorovlab/preciseTAD) and on Bioconductor (submitted).
@@
 The default parameters for Arrowhead were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1).
-Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab web site (Supplementary Table 1).
+Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab website (Supplementary Table 1).
 Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop anchor.
@@
 
-To create shifted binning, the first shifted bin was set to start at half of the resolution *r*, and continued in intervals of length *r* until the end of the chromosome (*mod r* + *r/2*).
-The shifted bins, referred hereafted as bins for simplicity, were then defined as boundary-containing regions (*Y = 1*) if they contained a TAD (or loop) boundary, and non-boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification (Figure 1A).
+To create shifted binning, the first shifted bin was set to start at half of the resolution *r* and continued in intervals of length *r* until the end of the chromosome (*mod r* + *r/2*).
+The shifted bins, referred hereafter as bins for simplicity, were then defined as boundary-containing regions (*Y = 1*) if they contained a TAD (or loop) boundary, and non-boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification (Figure 1A).
 
@@
 
-To assess the impact of class imbalance (CI), defined as the proportion of boundary regions to non-boundary regions, we evaluated three re-sampling techniques.
+To assess the impact of class imbalance (CI), defined as the proportion of boundary regions to non-boundary regions, we evaluated three resampling techniques.
 These include *Random Over-Sampling (ROS)*, *Random Under-Sampling (RUS)*, and *Synthetic Minority Over-Sampling Technique (SMOTE)*.
@@
 
-Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, feature engineering procedures, and re-sampling techniques.
+Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, feature engineering procedures, and resampling techniques.
 A *holdout chromosome* technique was used for model evaluation on each autosomal chromosome.
@@
 $p$, the number of annotations, together with the response vector **Y**, defined the column-wise dimension of the matrix $A$.
-Re-sampling was then performed on $A$ and an RF classifier was trained using 3-fold cross-validation to tune for the number of annotations to consider at each node (*mtry*).
+Re-sampling was then performed on $A$, and an RF classifier was trained using 3-fold cross-validation to tune for the number of annotations to consider at each node (*mtry*).
 The number of trees (*ntree*) that were aggregated for each RF model was set to 500.
@@
 where TP refers to the number of bins correctly identified as containing a boundary (true positives), FP refers to the number of bins incorrectly identified as containing a boundary (false positives), TN refers to the number of bins correctly identified as not containing a boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a boundary (false negatives).
-Each of these quantities are obtained from the confusion matrix created by validating the model on the test data.
-The process was repeated for each $i^{th}$ holdout chromosome and performances were aggregated using mean and standard deviation.
+Each of these quantities is obtained from the confusion matrix created by validating the model on the test data.
+The process was repeated for each $i^{th}$ holdout chromosome, and performances were aggregated using mean and standard deviation.
 
@@
 To suitably reduce the predictor space and improve computational efficiency, while maintaining optimal performance, we implemented recursive feature elimination (RFE).
-In doing so, we estimated the near optimal number of necessary features to include in the best fitting RF model.
+In doing so, we estimated the near-optimal number of necessary features to include in the best fitting RF model.
 The best performing subset was identified, ranging from 2 to the maximum number of features incremented by the power of 2.
-We then aggregated the predictive importance of the union of the optimal set of features across chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top ranked annotations for predicting boundary regions.
+We then aggregated the predictive importance of the union of the optimal set of features across chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top-ranked annotations for predicting boundary regions.
 
@@
 The test data used to evaluate performance was constructed from the binned data of the $i^{th}$ holdout chromosome with genomic annotations from the other cell line.
-Thus, the models were trained on cell line specific data and tested on the other cell line.
+Thus, the models were trained on cell-line-specific data and tested on the other cell line.
 This process was repeated for each holdout chromosome.
-To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivies and specificities, and reported the area under the curve (AUC).
+To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivities and specificities and reported the area under the curve (AUC).
 
@@
 
-To investigate whether we could alleviate resolution limitations of conventional domain calling tools, we developed *preciseTAD*, an algorithm that leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution.
-A random forest model was built on the optimal combination of predictor type (predictor space), re-sampling technique (class balancing correction), and top ranked annotations (most informative genomic elements) to maximally accurately predict boundaries at the _Hi-C resolution level_.
+To investigate whether we could alleviate the resolution limitations of conventional domain calling tools, we developed *preciseTAD*.
+This algorithm leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution.
+A random forest model was built on the optimal combination of predictor type (predictor space), resampling technique (class balancing correction), and top-ranked annotations (most informative genomic elements) to maximally accurately predict boundaries at the _Hi-C resolution level_.
 
@@
 
-Next, we assessed the biological significance of our predicted boundaries by their association with several known molecular drivers of 3D chromatin architecture including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
+We assessed the biological significance of our predicted boundaries by their association with several known molecular drivers of 3D chromatin architecture, including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
 To do so, we used the *computeMatrix* and *plotHeatmap* tools offered by deepTools (version 2.0) [@ramirez2016deeptools] via integration with Galaxy (version 3.3.2.0.0) [@afgan2018galaxy].
@@
 
-## Developing a ML framework for optimal TAD boundary prediction
+## Developing an ML framework for optimal TAD boundary prediction
 
@@
 Data from GM12878 and K565 cell lines at 5-100kb resolution (Arrowhead) and 10kb resolution (Peakachu) were used (Supplementary Table 1).
-We next developed *preciseTAD*, an R package which leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base resolution from cell type-specific genome annotation data.
+We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base resolution from cell-type-specific genome annotation data.
 
@@
 The number of non-boundary regions highly outnumbered boundary regions.
-Such disproportional presence of examples in one class is known as a "class imbalance" problem that negatively affects predictive modeling [@prati2011survey; @wei2013role].
-To address class imbalance, we evaluated the effect of three re-sampling techniques.
+Such a disproportional presence of examples in one class is known as a "class imbalance" problem that negatively affects predictive modeling [@prati2011survey; @wei2013role].
+To address the class imbalance, we evaluated the effect of three resampling techniques.
 *Random over-sampling* (ROS) was defined as sampling with replacement from the minority class (boundary regions).
-*Random under-sampling* (RUS) was defined as sampling with replacement from the majority cluss (non-boundary regions).
+*Random under-sampling* (RUS) was defined as sampling with replacement from the majority class (non-boundary regions).
 Lastly, we tested *Synthetic minority over-sampling technique* (SMOTE), which is a combination of both random over- and under-sampling to create balanced classes [@chawla2002smote] (see Methods).
@@
 A total of 77 cell-line-specific genomic annotations were used to build the predictor space.
-These included BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 2).
+These included BroadHMM chromatin segmentation, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 2).
 Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
@@
 ![**Resolution-specific data construction and feature engineering used for downstream random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals (see Methods).
-The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD boundary, respectively.
+The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD boundary.
 (B) Four types of associations between bins and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png)
@@
 Once the model inputs were established, a random forest classifier was trained on $n-1$ autosomal chromosomes, while reserving the $i^{th}$ chromosome for testing.
-Three-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed to default values of 500 and 1 respectively.
+Three-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed to default values of 500 and 1, respectively.
 Model performance was evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (see Methods).
@@
 ![**A diagram of the machine learning framework used to build TAD/loop boundary region prediction models.** Step 1 defines the dimensions of the data matrix $A_{N \times (p+1)}$ used for training and testing by establishing a resolution, $r$, at which to bin the linear genome into $N$ genomic bins for each chromosome, except a holdout chromosome *i*.
-The response vector **Y** is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$) A feature engineering procedure is selected to define the feature space of $A$ composed of $p$ genomic annotations.
+The response vector **Y** is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$).
+A feature engineering procedure is selected to define the feature space of $A$ composed of $p$ genomic annotations.
 Step 2 is to reserve the predictor-response matrix for the holdout chromosome *i* as the test data.
-Step 3 is to apply a re-sampling technique to the training data to address class imbalance.
+Step 3 is to apply a resampling technique to the training data to address the class imbalance.
 Step 4 is to train the random forest model and perform 3-fold cross-validation to tune for the mtry parameter.
@@
 
-Expectedly, when using data with class imbalance present, that is, no re-sampling, the models exhibited low balanced accuracies, with very little variability among different resolutions (Figure 3).
+Expectedly, when using data with class imbalance present, that is, no resampling, the models exhibited low balanced accuracies, with minimal variability among different resolutions (Figure 3).
 Similarly, poor performances were found when using ROS.
-However, RUS and SMOTE re-sampling led to drastic improvement in performance, especially at higher resolutions.
-We found that RUS marginally outperformed SMOTE as the most optimal class balancing technique for all resolutions and predictor types when predicting TAD boundary regions.
+However, RUS and SMOTE re-sampling led to a drastic improvement in performance, especially at higher resolutions.
+We found that RUS marginally outperformed SMOTE as the optimal class balancing technique for all resolutions and predictor types when predicting TAD boundary regions.
 
-Additionally, we found that using a distance-type predictor space yielded substantially higher balanced accuracies when compared to the peak signal stength, overlap count, and overlap percent predictor types.
-As with class balancing techniques, this improvement was less evident at lower resolutions with results consistent for K562 (Supplementary Figure 2).
+Additionally, we found that using a distance-type predictor space yielded substantially higher balanced accuracy compared to the peak signal strength, overlap count, and overlap percent predictor types.
+As with class balancing techniques, this improvement was less evident at lower resolutions, with results consistent for K562 (Supplementary Figure 2).
 Random forest models built on Peakachu-defined loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3).
-Furthermore, 5 kb resolution genomic bins led to optimal prediction for both TAD and loop boundaries, on both cell lines.
+Furthermore, 5 kb resolution genomic bins led to the optimal prediction for both TAD and loop boundaries, on both cell lines.
 Our results indicate that random under-sampling, distance-type predictors, and high-resolution Hi-C data provide the optimal set of data level characteristics for both TAD and chromatin loop boundary prediction.
 
-![**Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for GM12878 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+![**Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for GM12878 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
@@
 We hypothesized that the type of genomic annotations may also affect predictive performance.
-Using the established optimal settings (RUS, Distance, 5 kb bins), we built separate random forest models using BroadHMM chromatin segmentations, histone modifications (HM), and transcription factor binding sites (TFBS).
+Using the established optimal settings (RUS, Distance, 5 kb bins), we built separate random forest models using BroadHMM chromatin segmentation, histone modifications (HM), and transcription factor binding sites (TFBS).
 We found that models built on TFBSs outperformed other annotation-specific models, with results consistent for loop boundaries, on both cell lines (Figure 4A; Supplementary Figures 4A).
@@
 
-## Predictive importances confirmed biological role of CTCF, RAD21, SMC3, and ZNF143 for boundary formation
+## Predictive importances confirmed the biological role of CTCF, RAD21, SMC3, and ZNF143 for boundary formation
 
-We sought to further optimize our boundary region prediction models by performing recursive feature elimination to avoid overfitting and select only the most influential TFBS across all autosomal chromosomes.
+We sought to further optimize our boundary region prediction models by recursive feature elimination to avoid overfitting and selecting only the most influential TFBS across all autosomal chromosomes.
 We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figures 4B).
-However, given that we trained our model on chromosome-specific data, the most significant annotations varied for each set of chromosomes.
-To determine transcription factors most important for boundary prediction, we clustered the predictive importances (mean decrease in accuracy) of the top eight significant TFs across chromosomes.
-We found that, similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were consistently predictive of TAD and loop boundaries (Figure 4C; Supplementary Figures 4C).
-We further optimized our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
+However, given that we trained our model on chromosome-specific data, the most significant annotations varied for each chromosome set.
+To determine transcription factors most important for boundary prediction, we clustered the predictive importance (mean decrease in accuracy) of the top eight significant TFs across chromosomes.
+We found that similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were consistently predictive of TAD and loop boundaries (Figure 4C; Supplementary Figures 4C).
+We optimized our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
 In summary, our model was able to yield the known molecular drivers of the loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
@@
 When training on GM12878 and testing on K562, our model's average AUC only marginally decreased to 0.803.
-Likewise, training and testing on Peakachu resulted in an average AUC=0.885 and decreased only slightly to 0.868 when trained on GM12878 and tested on K562.
+Likewise, training and testing on Peakachu resulted in an average AUC=0.885 and slightly reduced to 0.868 when trained on GM12878 and tested on K562.
 Results were consistent when training on K562 and testing on GM12878 (Supplementary Figure 4D).
@@
 Intuitively, instead of bin-level annotations, the predictor-response space was built on a base-level, that is, each base was associated with the corresponding genomic annotation.
-The model trained on a bin-level space was then applied on a base-level space to predict the probability of each base being a boundary.
-Our method, referred to as *preciseTAD*, uses density-based hierarchical clustering (DBSCAN) and a scalable partitioning around mediods clustering (CLARA) to predict the boundary location at base resolution (see Methods).
+The model trained on a bin-level space was then applied on a base-level space to predict each base's probability of being a boundary.
+Our method, referred to as *preciseTAD*, uses density-based hierarchical clustering (DBSCAN) and a scalable partitioning around medoids clustering (CLARA) to predict the boundary location at base resolution (see Methods).
 
-When built using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb respectively, *preciseTAD* was able to predict a total of 7,846 TAD and 15,838 chromatin loop boundaries on GM12878, as well as 8,883 TAD and 11,016 chromatin loop boundaries on K562 [???
+When built using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, *preciseTAD* was able to predict a total of 7,846 TAD and 15,838 chromatin loop boundaries on GM12878, as well as 8,883 TAD and 11,016 chromatin loop boundaries on K562 [???
 Need them in Supplementary Table 4, Excel, BED format, sheet 1 - GM12878 PTBR, sheet 2 - GM12878 PTBP, sheet 3,4 - K562.
@@
 This can be attributed to Arrowhead's inflation of called TADs, especially at higher resolutions, that, when visualized, often do not correspond to intra-chromosomal contacts featured on a contact matrix.
-Additionally, *preciseTAD* boundaries were visually more likely to demarcate high concentrations of intra-chromosomal contacts as can be seen on a Hi-C contact matrix (Figure 5A).
+Additionally, *preciseTAD* boundaries were visually more likely to demarcate high concentrations of intra-chromosomal contacts [???
+Do not understand], as can be seen on a Hi-C contact matrix (Figure 5A).
 *preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Supplementary Table 3).
-This can be attributed to the fact that *preciseTAD* leverages four known drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143, contrasting Peakachu which considers only CTCF sites to mark the predicted boundaries as true positives.
-These results suggest that genome annotation-driven predicted boundaries may be more biologically relevant, in contrast to boundaries detected from Hi-C data alone.
+This can be attributed to the fact that *preciseTAD* leverages four known drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143.
+This is in contrast to Peakachu, which considers only CTCF sites to mark the predicted boundaries as true positives.
+These results suggest that genome annotation-driven predicted boundaries may be more biologically relevant than those detected from Hi-C data alone.
 
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
-Peak regions associated with known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143 were found to co-localize more frequently around *preciseTAD* predicted boundaries (Figure 5B).
+Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, were found to co-localize more frequently around *preciseTAD* predicted boundaries (Figure 5B).
 Furthermore, signal heatmaps indicated that our predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Figure 5 C-D; Supplementary Figures 5-6).
-When compared to called TAD or loop boundaries, *preciseTAD* boundaries were statistically significantly closer to the same cell line-specific top ranked TFBS (p<0.001 and p<0.001 versus Arrowhead and Peakachu respectively) (Figure 5E, Supplementary Figure 7).
+When compared to called TAD or loop boundaries, *preciseTAD* boundaries were statistically significantly closer to the same cell line-specific top-ranked TFBS (p<0.001 and p<0.001 versus Arrowhead and Peakachu respectively) (Figure 5E, Supplementary Figure 7).
 These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
@@
 
-TAD boundaries are known to be relatively conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @sexton2012three].
+TAD boundaries are relatively conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @sexton2012three].
 To assess conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, Arrowhead, and Peakachu after flanking them by the resolution of the Hi-C data.
 Boundaries involving Arrowhead were flanked by 5 kb, while boundaries involving Peakachu were flanked by 10 kb.
-We found that 35% of *preciseTAD* predicted TAD boundaries and 55% of *preciseTAD* predicted loop boundaries were were conserved between cell lines, compared to only 26% and 55% for Arrowhead and Peakachu alone (Figure 5F).
-The better conservation of *preciseTAD*-predicted boundaries further support the notion of their higher biological relevance.
+We found that 35% of *preciseTAD* predicted TAD boundaries and 55% of *preciseTAD* predicted loop boundaries were conserved between cell lines, compared to only 26% and 55% for Arrowhead and Peakachu alone (Figure 5F).
+The better conservation of *preciseTAD*-predicted boundaries further supports the notion of their higher biological relevance.
 
@@
 (C) Enriched heatmaps comparing the enrichment of CTCF signal around ARROWHEAD TAD boundaries and preciseTAD boundaries, and (D) around Peakachu loop boundaries and preciseTAD for the entire genome.
-(E) Log 2 genomic distances from boundaries to nearest CTCF sites.
+(E) Log 2 genomic distances from boundaries to the nearest CTCF sites.
 (F) Venn diagrams illustrating the levels of conservation between TAD/loop boundaries for GM12878 (red) and K562 (blue) identified by preciseTAD (using ARROWHEAD; top left), ARROWHEAD (top right), preciseTAD (using PEAKACHU; bottom left), and PEAKACHU (bottom right).
-The median Jaccard Index (IQR) across each chromosome is provided below each venn diagram](Figures/figure5.png)
+The median Jaccard Index (IQR) across each chromosome is provided below each Venn diagram](Figures/figure5.png)
 
@@
 This is expected as loop boundaries (Peakachu) are more abundant, while TAD boundaries (Arrowhead) represent the narrower level of the 3D chromatin organization.
-Together with the results on Figure 4, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop domain boundaries may be driven by similar molecular mechanisms.
+Together with the results in Figure 4, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop domain boundaries may be driven by similar molecular mechanisms.
 
@@
 *preciseTAD* was benchmarked against two boundary calling tools, Arrowhead [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
-We first optimized our RF model by systematically comparing different combinations of genome binning (resolution), feature engineering procedures, and re-sampling techniques.
+We first optimized our RF model by systematically comparing different combinations of genome binning (resolution), feature engineering procedures, and resampling techniques.
 Our results demonstrate that genomic distance between high-resolution boundary regions and transcription factor binding sites, coupled with random under-sampling results in best model performance.
-We demonstrate that binding of four transcription factors (SMC3, RAD21, CTCF, ZNF143) are sufficient for accurate boundary predictions.
-Applied to each annotated base, the model predicts probability for each base to be a boundary.
+We show that binding of four transcription factors (SMC3, RAD21, CTCF, ZNF143) is sufficient for accurate boundary predictions.
+Applied to each annotated base, the model predicts the probability for each base to be a boundary.
 Further, coupled with spatial clustering (DBSCAN) and scalable partition around medoids clustering (CLARA), it allows for the detection of boundaries at the base-level resolution.
@@
 Our machine learning framework yielded several interesting observations.
-First, we demonstrated that RF models built using *distance*-type predictors outperformed models built on previously published feature engineering techniques including signal strength, overlap counts and overlap percents [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa; @kai2018predicting].
-We further demonstrated that class imbalance hinders boundary prediction, but can be effectively addressed by a simple random under-sampling technique, an aspect of boundary prediction that was unaddressed in previous studies [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa].
+We first demonstrated that RF models built using *distance*-type predictors outperformed models built on previously published feature engineering techniques, including signal strength, overlap counts, and overlap percents [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa; @kai2018predicting].
+We further demonstrated that class imbalance hinders boundary prediction, but can be effectively addressed by a simple random under-sampling technique, an aspect of boundary prediction unaddressed in previous studies [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa].
 We showed that information about only four transcription factors (SMC3, RAD21, CTCF, ZNF143) is necessary and sufficient for accurate boundary prediction, outperforming histone modification- and BroadHMM-built models [@Moore:2015aa; @Al-Bkhetan:2018aa].
 These are known components of the loop extrusion model, an established theory of how loops are made by a ring-shaped adenosine triphosphatase-driven complex called cohesin [@hansen2018recent; @sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
-Interestingly, the same transcription factors accurately predicted both TAD and loop boundaries, suggesting similarity of the mechanisms of TAD and loop formation.
+Interestingly, the same transcription factors accurately predicted both TAD and loop boundaries, suggesting a similarity of the mechanisms of TAD and loop formation.
 This suggested that the random forest model, when tuned and feature engineered correctly, is highly effective in predicting biologically relevant domain boundaries.
@@
 Precision indicates the rate at which positive predictions are correct and can be artificially deflated by low proportions of true positives (TP), the set of genomic bins correctly predicted as containing a ground truth boundary.
-While F1-score is a composite metric, it can be very sensitive towards disparate values for precision and recall.
-Lastly, AUPRC is insensitive toward class imbalance, preventing us to investigate its effect, and also omits from its calculation TN values.
+While F1-score is a composite metric, it can be susceptible to different values for precision and recall.
+Lastly, AUPRC is insensitive toward class imbalance, preventing us from investigating its effect, and also omits from its calculation TN values.
 All of these are important considerations to make when choosing a performance metric.
-For these reasons we opted to report the balanced accuracy (BA).
-The BA benefits from incorporating all components of the confusion matrix, while also being sensitive to class imbalance, a necessary characteristic when comparing performances to models built using no data re-sampling.
+For these reasons, we opted to report balanced accuracy (BA).
+The BA benefits from incorporating all components of the confusion matrix, while also being sensitive to class imbalance, a necessary characteristic when comparing performances to models built using no data resampling.
 [???refer to supp tables 4 and 5 here when ready] -->
@@
 Guided by both low-resolution Hi-C data and high-resolution genome annotation data, *preciseTAD* predicts base-level resolution boundaries, alleviating resolution limitations of Hi-C data.
-We show that, unlike Arrowhead, *preciseTAD* does not inflate the number of predicted boundaries, instead, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
+We show that, unlike Arrowhead, *preciseTAD* does not inflate the number of predicted boundaries, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
 *preciseTAD* boundaries were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops may be generated by similar mechanisms [@hansen2018recent].
@@
 
-*preciseTAD* offers flexibility in controlling both the number of predicted boundaries as well as the distance between them.
+*preciseTAD* offers flexibility in controlling both the number of predicted boundaries and the distance between them.
 The two primary parameters are the probability threshold $t$ and $\epsilon$ (referred to as eps; parameter of DBSCAN).
-The combination of these two quantities change the resulting number of predicted boundaries from *preciseTAD*.
+The combination of these two quantities changes the resulting number of predicted boundaries from *preciseTAD*.
 Lower values of $t$ and $\epsilon$ will result in more clusters of bases, and therefore, more boundaries.
@@
 Given the wide variety of domain callers and their variable performance [@Zufferey:2018aa; @forcato2017comparison], it is hard to define "ground truth" boundaries.
-<!--Ideally we would benchmark *preciseTAD* against simulated boundaries.
+<!--Ideally, we would benchmark *preciseTAD* against simulated boundaries.
 While methods for simulating Hi-C data sets with boundary annotations exist [@forcato2017comparison; @zheng2020freehi], methods for simulating the associated genomic annotations (the main component guiding *preciseTAD* predictions) are lacking.-->Ultra-deep Hi-C sequencing [@bonev2017multiscale] and newer technologies for precise mapping of chromatin interactions (e.g., Micro-C [@Krietenstein:2020aa]), coupled with more precise technologies for genomic annotation profiling (e.g., CUT&RUN for precise mapping of transcription factor binding sites) will help to refine the location and the genomic signatures of "ground truth" TAD boundaries.
@@
 The hierarchical nature of TAD boundaries [@weinreb2016identification; @fraser2015hierarchical; @Cresswell:2020ab] is not considered by *preciseTAD* due to the lack of gold standard of TAD hierarchy.
-Recent research distinguishes CTCF-associated boundaries, CTCF-negative YY1-enriched boundaries, CTCF- and YY1- depleted promoter boundaries, and a fourth class of weak boundaries largely depleted of all three features [@Krietenstein:2020aa].
+Recent research distinguishes CTCF-associated boundaries, CTCF-negative YY1-enriched boundaries, CTCF- and YY1- depleted promoter boundaries, and the fourth class of weak boundaries largely depleted of all three features [@Krietenstein:2020aa].
 Furthermore, actively transcribed regions can serve as TAD boundaries themselves, independently of CTCF binding [@Harrold:2020aa].
 This may lead to some TAD boundaries being undetected by *preciseTAD* despite being detected by domain callers.
-Our future work will include defining separate models trained on different TAD boundary types, and predicting precise locations for each of them.
+Our future work will include defining separate models trained on different TAD boundary types and predicting precise locations for each of them.
 
@@
 Our method introduces three concepts - *shifted binning*, *distance*-type predictors, and *random undersampling* - which we use to build random forest classification models for predicting boundary regions.
-Our method is able to bridge the resolution gap between 1D ChIP-seq annotations and 3D Hi-C sequencing data for more precise and biologically meaningful boundary identification.
+Our method can bridge the resolution gap between 1D ChIP-seq annotations and 3D Hi-C sequencing data for more precise and biologically meaningful boundary identification.
 We introduce *preciseTAD*, an open source R package for leveraging random forests to predict TAD/loop boundaries at base resolution.
-We hope that *preciseTAD* will serve as an efficient and easy-to-use tool to further exploration of the 3D organization of the genome.
+We hope that *preciseTAD* will serve as an efficient and easy-to-use tool to further explore the genome's 3D organization.
 
@@
 **Supplementary Table 3.** TAD/loop boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the K562 cell line.
-Class imbalance is calculated as the ratio of total number of unique boundaries to the total number of genomic bins.
+Class imbalance is calculated as the ratio of the total number of unique boundaries to the total number of genomic bins.
 
@@
 **Supplementary Figure 1.** Density curves of distances before (red) and after (blue) performing a $log_{2}$ transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines, respectively.
-Distances are measured as the number of bases from the center of a genomic bin to the center of the nearest genomic annotation.
+Distances are measured as the number of bases from the center of a genomic bin to the nearest genomic annotation center.
 Each density curve represents an individual genomic annotation (77 total).
@@
 **Supplementary Figure 2.
-Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for K562 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across re-sampling techniques: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for K562 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.
@@
 **Supplementary Figure 3.
-Distance-type predictors combined with random under-sampling or SMOTE re-sampling yielded optimal predictive performance Peakachu loop boundaries at 10 kb resolution.** Averaged balanced accuracies are compared for A) GM12878 and B) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Distance-type predictors combined with random under-sampling or SMOTE re-sampling yielded optimal predictive performance Peakachu loop boundaries at 10 kb resolution.** Averaged balanced accuracies are compared for A) GM12878 and B) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.

### 2020-08-15 Manuscript/manuscript.Rmd
address todo preprint items

@@
 output:
+  pdf_document: 
   word_document:
     reference_docx: styles.doc/NIH_grant_style.docx
-  pdf_document: 
 bibliography: References/references.bib
@@
 
-When built using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, *preciseTAD* was able to predict a total of 7,846 TAD and 15,838 chromatin loop boundaries on GM12878, as well as 8,883 TAD and 11,016 chromatin loop boundaries on K562 [???
-Need them in Supplementary Table 4, Excel, BED format, sheet 1 - GM12878 PTBR, sheet 2 - GM12878 PTBP, sheet 3,4 - K562.
-Supp tables 1, 2, 3 are OK, renumber subsequent.
-Write legend].
+When built using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, *preciseTAD* was able to predict a total of 7,846 TAD and 15,838 chromatin loop boundaries on GM12878, as well as 8,883 TAD and 11,016 chromatin loop boundaries on K562 (Supplementary Table 4).
 We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Supplementary Table 3).
-This can be attributed to Arrowhead's inflation of called TADs, especially at higher resolutions, that, when visualized, often do not correspond to intra-chromosomal contacts featured on a contact matrix.
-Additionally, *preciseTAD* boundaries were visually more likely to demarcate high concentrations of intra-chromosomal contacts [???
-Do not understand], as can be seen on a Hi-C contact matrix (Figure 5A).
+This can be attributed to Arrowhead's inflation of called TADs, especially at higher resolutions, that, when visualized, often do not correspond to intra-chromosomal contacts featured on a contact matrix (Figure 5A).
 *preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Supplementary Table 3).
@@
 ![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of preciseTAD (green) vs.
-ARROWHEAD (blue) boundaries on GM12878 (chr 14: 50085000-50800000).
+Arrowhead (blue) boundaries on GM12878 (chr 14: 50085000-50800000).
 The black line represents the predicted probability of each base being a TAD boundary.
 (B) Genome browse visualization of bigwig files for known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143.
-(C) Enriched heatmaps comparing the enrichment of CTCF signal around ARROWHEAD TAD boundaries and preciseTAD boundaries, and (D) around Peakachu loop boundaries and preciseTAD for the entire genome.
+(C) Enriched heatmaps comparing the enrichment of CTCF signal around Arrowhead TAD boundaries and preciseTAD boundaries, and (D) around Peakachu loop boundaries and preciseTAD for the entire genome.
 (E) Log 2 genomic distances from boundaries to the nearest CTCF sites.
-(F) Venn diagrams illustrating the levels of conservation between TAD/loop boundaries for GM12878 (red) and K562 (blue) identified by preciseTAD (using ARROWHEAD; top left), ARROWHEAD (top right), preciseTAD (using PEAKACHU; bottom left), and PEAKACHU (bottom right).
+(F) Venn diagrams illustrating the levels of conservation between TAD/loop boundaries for GM12878 (red) and K562 (blue) identified by preciseTAD (using Arrowhead; top left), Arrowhead (top right), preciseTAD (using Peakachu; bottom left), and Peakachu (bottom right).
 The median Jaccard Index (IQR) across each chromosome is provided below each Venn diagram](Figures/figure5.png)
@@
 
-**Supplementary Table 4.** Additional performance metrics when implementing a random forest using
-Arrowhead ground truth TAD boundaries. Performances are averaged across each holdout chromosome that was reserved for testing.
+**Supplementary Table 4.** GM12878(K562)_PTBR - The start and end coordinates defining the clusters of *preciseTAD* predicted TAD boundary regions (PTBRs) for each chromosome on GM12878 (K562).
+GM12878(k562)_TAD - The start and end coordinates defining TADs demarcated by a unique *preciseTAD* predicted TAD boundary point (PTBP) for each chromosome on GM12878 (K562).
 
-**Supplementary Table 5.** Additional performance metrics when implementing a random forest using
-Peakachu ground truth chromatin loop boundaries. Performances are averaged across each holdout chromosome that was reserved for testing.
+*preciseTAD* predicted boundary regions (PTBR) and points (PTBP) for GM12878 and k562, using Arrowhead TAD boundary coordinates as ground truth. For PTBP,
+
+<!--
+**Supplementary Table 5.** Additional performance metrics when implementing a random forest using Arrowhead ground truth TAD boundaries.
+Performances are averaged across each holdout chromosome that was reserved for testing.
+
+**Supplementary Table 6.** Additional performance metrics when implementing a random forest using Peakachu ground truth chromatin loop boundaries.
+Performances are averaged across each holdout chromosome that was reserved for testing.
+-->
 
@@
 
+AUC-Area Under the Curve; BA-Balance Accuracyl; bp-base pair; BroadHMM-BroadHMM cis-regulated elements; ChIP-seq-Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI-Class Imbalance; CLARA-Clustering Large Applications ;DBSCAN-Density-Based Spatial Clustering of Applications with Noise; FN-False Negatives; FP-False Positives; Hi-C-High-througput chromosome conformation capture; HM-Histone Modifications; kb-kilobase; ML-Machine Learning; OC-Overlap Counts; OP-Overlap Percents; PAM-Partitioning Around Medoids; PTBP-preciseTAD Boundary Point; PTBR-preciseTAD Boundary Region; RF-Random Forest; RFE-Recursive Feature Elimination; ROC-Receiver Operating Characteristic; ROS-Random Over-Sampling
+RUS	Random Under-Sampling; SMOTE-Synthetic Minority Over-sampling Technique; TAD-Topologically Associated Domains; TFBS-Transcription Factor Binding Sites; TN-True Negatives; TP-True Positives
+
 # Acknowledgements

### 2020-08-16 Manuscript/manuscript.Rmd
Fix very sloppy abbreviations

@@
 
-AUC-Area Under the Curve; BA-Balance Accuracyl; bp-base pair; BroadHMM-BroadHMM cis-regulated elements; ChIP-seq-Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI-Class Imbalance; CLARA-Clustering Large Applications ;DBSCAN-Density-Based Spatial Clustering of Applications with Noise; FN-False Negatives; FP-False Positives; Hi-C-High-througput chromosome conformation capture; HM-Histone Modifications; kb-kilobase; ML-Machine Learning; OC-Overlap Counts; OP-Overlap Percents; PAM-Partitioning Around Medoids; PTBP-preciseTAD Boundary Point; PTBR-preciseTAD Boundary Region; RF-Random Forest; RFE-Recursive Feature Elimination; ROC-Receiver Operating Characteristic; ROS-Random Over-Sampling
-RUS	Random Under-Sampling; SMOTE-Synthetic Minority Over-sampling Technique; TAD-Topologically Associated Domains; TFBS-Transcription Factor Binding Sites; TN-True Negatives; TP-True Positives
+AUC - Area Under the Curve; BA - Balance Accuracy; bp - base pair; BroadHMM - BroadHMM chromatin segmentation states; ChIP-seq - Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI - Class Imbalance; CLARA - Clustering Large Applications; DBSCAN - Density-Based Spatial Clustering of Applications with Noise; FN - False Negatives; FP - False Positives; Hi-C - High-throughput chromosome conformation capture technology; HM - Histone Modifications; kb - kilobase; ML - Machine Learning; OC - Overlap Counts; OP - Overlap Percents; PAM - Partitioning Around Medoids; PTBP - preciseTAD Boundary Point; PTBR - preciseTAD Boundary Region; RF - Random Forest; RFE - Recursive Feature Elimination; ROC - Receiver Operating Characteristic; ROS - Random Over-Sampling
+RUS	Random Under-Sampling; SMOTE - Synthetic Minority Over-sampling Technique; TAD - Topologically Associated Domains; TFBS - Transcription Factor Binding Sites; TN - True Negatives; TP - True Positives
 

### 2020-08-16 Manuscript/manuscript.Rmd
editted supp table 4 and legend; added boundaries from peakachu to table and as bed files

--- 2020-08-15 Manuscript/manuscript.Rmd
@@
 
-**Supplementary Table 4.** GM12878(K562)_PTBR - The start and end coordinates defining the clusters of *preciseTAD* predicted TAD boundary regions (PTBRs) for each chromosome on GM12878 (K562).
-GM12878(k562)_TAD - The start and end coordinates defining TADs demarcated by a unique *preciseTAD* predicted TAD boundary point (PTBP) for each chromosome on GM12878 (K562).
-
-*preciseTAD* predicted boundary regions (PTBR) and points (PTBP) for GM12878 and k562, using Arrowhead TAD boundary coordinates as ground truth. For PTBP,
+**Supplementary Table 4.** *preciseTAD* predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562, using Arrowhead TAD and Peakachu chromatin loop boundary coordinates as ground truth.
+For PTBRs, the start and end coordinates define the clusters of spatially proximate bases with probabilities equal to 1.
+For PTBPs, the start and end (start+1) coordinates define the uniquely identified boundary coordinate predicted by *preciseTAD* within each PTBR.
 
@@
 
-AUC-Area Under the Curve; BA-Balance Accuracyl; bp-base pair; BroadHMM-BroadHMM cis-regulated elements; ChIP-seq-Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI-Class Imbalance; CLARA-Clustering Large Applications ;DBSCAN-Density-Based Spatial Clustering of Applications with Noise; FN-False Negatives; FP-False Positives; Hi-C-High-througput chromosome conformation capture; HM-Histone Modifications; kb-kilobase; ML-Machine Learning; OC-Overlap Counts; OP-Overlap Percents; PAM-Partitioning Around Medoids; PTBP-preciseTAD Boundary Point; PTBR-preciseTAD Boundary Region; RF-Random Forest; RFE-Recursive Feature Elimination; ROC-Receiver Operating Characteristic; ROS-Random Over-Sampling
-RUS	Random Under-Sampling; SMOTE-Synthetic Minority Over-sampling Technique; TAD-Topologically Associated Domains; TFBS-Transcription Factor Binding Sites; TN-True Negatives; TP-True Positives
+AUC - Area Under the Curve; BA - Balance Accuracy; bp - base pair; BroadHMM - BroadHMM chromatin segmentation states; ChIP-seq - Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI - Class Imbalance; CLARA - Clustering Large Applications; DBSCAN - Density-Based Spatial Clustering of Applications with Noise; FN - False Negatives; FP - False Positives; Hi-C - High-throughput chromosome conformation capture technology; HM - Histone Modifications; kb - kilobase; ML - Machine Learning; OC - Overlap Counts; OP - Overlap Percents; PAM - Partitioning Around Medoids; PTBP - preciseTAD Boundary Point; PTBR - preciseTAD Boundary Region; RF - Random Forest; RFE - Recursive Feature Elimination; ROC - Receiver Operating Characteristic; ROS - Random Over-Sampling; RUS	Random Under-Sampling; SMOTE - Synthetic Minority Over-sampling Technique; TAD - Topologically Associated Domains; TFBS - Transcription Factor Binding Sites; TN - True Negatives; TP - True Positives
 

### 2020-08-17 Manuscript/manuscript.Rmd
Polish legend for Supplementary Table 4

@@
 **Supplementary Table 4.** *preciseTAD* predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562, using Arrowhead TAD and Peakachu chromatin loop boundary coordinates as ground truth.
-For PTBRs, the start and end coordinates define the clusters of spatially proximate bases with probabilities equal to 1.
-For PTBPs, the start and end (start+1) coordinates define the uniquely identified boundary coordinate predicted by *preciseTAD* within each PTBR.
+For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability of being a boundary equal to 1.
+For PTBPs, the start and end (start+1) coordinates define the uniquely identified boundary coordinate within each PTBR.
+All coordinates are in hg18/GRCh37 reference genome.
 

### 2020-08-17 Manuscript/manuscript.Rmd
Working on abstract clarity

@@
 
-**Background** High-throughput chromosome conformation capture technology (Hi-C) has revealed extensive DNA looping and folding into discrete 3D domains.
-Among these are Topologically Associated Domains (TADs) and chromatin loops, known to play critical roles in cellular processes like gene regulation and cell differentiation.
+**Background.** High-throughput chromosome conformation capture technology (Hi-C) revealed extensive DNA looping and folding into discrete 3D domains.
+Among these are Topologically Associated Domains (TADs) and chromatin loops, critical for cellular processes like gene regulation and cell differentiation.
 The relatively low resolution of Hi-C data (regions of several kilobases in size) prevents precise mapping of domain boundaries.
-TAD and loop boundaries have been characterized by the presence of CTCF and members of cohesin complex binding sites, and other genomic annotations.
-They are typically defined at high resolution (~100bp), suggesting they can inform the precise location of domain boundaries.
-Several methods have been developed to leverage genome annotation data for predicting TAD/loop boundaries; however, they overlooked key characteristics of the data, such as spatial associations between an annotation and a boundary.
-Furthermore, the number of regions containing boundaries is much smaller than the rest of the genome, creating a class imbalance problem.
+However, the high resolution of genomic annotations associated with boundaries, such as CTCF, members of cohesin complex, suggest they can inform the precise location of domain boundaries.
+Several methods attempted to leverage genome annotation data for predicting TAD/loop boundaries; however, they overlooked key characteristics of the data, such as spatial associations between an annotation and a boundary, and a much smaller number of boundaries than the rest of the genome (class imbalance).
 
-**Methods** To improve the detection of domain boundaries, we developed *preciseTAD*, a random forest-based framework that leverages high-resolution genome annotation data coupled with density-based clustering and scalable partitioning techniques.
-We investigated several resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) to address class imbalance.
-We benchmarked our method against the Arrowhead domain caller and a novel chromatin loop prediction algorithm, Peakachu, on multiple cell lines.
+**Methods.** We developed *preciseTAD*, an optimized random forest model to improve the location of domain boundaries.
+Trained on high-resolution genome annotation data and boundaries from low-resolution Hi-C data, the model predicts the location of boundaries at base-level resolution.
+We investigated several feature engineering and resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) to select the most optimal data characteristics and address class imbalance.
+Density-based clustering and scalable partitioning techniques were used to identify the precise location of boundary regions.
+We benchmarked our method against the Arrowhead domain caller and a novel chromatin loop prediction algorithm, Peakachu, on two most annotated cell lines.
 
-**Results** Using different feature engineering and resampling strategies, we found spatial relationships (distance) between boundaries and annotations have the most predictive power.
+**Results.** Spatial relationships (distance) between boundaries and annotations have the most predictive power.
 Transcription factor binding sites outperformed other genome annotation types.
 Random under-sampling significantly improved model performance.
-Boundaries predicted by preciseTAD were more enriched for CTCF, RAD21, SMC3, and ZNF143 sites and more conserved across cell lines, highlighting their higher biological significance.
+Boundaries predicted by *preciseTAD* were more enriched for CTCF, RAD21, SMC3, and ZNF143 signal and more conserved across cell lines, highlighting their higher biological significance.
 The model trained in one cell line performs well in predicting boundaries in another cell line.
 
-**Conclusion** Our results outline strategies for predictive modeling of 3D genomic domains using genome annotation data.
+**Conclusion.** Our study implements the method and outlines strategies for TAD/loop boundary prediction using genome annotation data.
 The precise identification of domain boundaries will improve our understanding of how genomic regulators are associated with the 3D structure of the genome.
 
-**Availability.** Our method is implemented as an R package, *preciseTAD*, available on https://github.com/dozmorovlab/preciseTAD and Bioconductor (submitted).
+**Availability.** *preciseTAD* R package is available on https://github.com/dozmorovlab/preciseTAD and Bioconductor (submitted).
 

### 2020-08-18 Manuscript/manuscript.Rmd
More polishing

@@
 
-**Results.** Spatial relationships (distance) between boundaries and annotations have the most predictive power.
+**Results.** Spatial relationship (distance in the linear genome) between boundaries and annotations has the most predictive power.
 Transcription factor binding sites outperformed other genome annotation types.
@@
 
-The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of 3-dimensional (3D) spatial constructs within the human genome such as chromatin loops [@rao20143d], Topologically Associated Domains (TADs) [@nora2012spatial;@dixon2012topological], and A/B compartments [@lieberman2009comprehensive].
-At the kilobase scale, gene promoters are often connected via distal regulatory elements, such as enhancers, through chromatin loops, thereby regulating gene expression [@Lupianez:2015aa; @Franke:2016aa].
-Further, at the megabase scale, TADs represent regions on the linear genome, that are highly self-interacting.
-Emerging evidence has linked TADs to critical roles in cell dynamics and cell differentiation.
-Studies have shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
-Likewise, disruption of boundaries demarcating TADs and loops promotes cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@lupianez2016breaking;@Sun:2018aa;@Meaburn:2007aa].
-Therefore, precisely identifying the location of TAD and chromatin loop boundaries remains a top priority in our goal to fully understand the functionality of the human genome.
+The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of the 3-dimensional (3D) structure of the human genome such as chromatin loops [@rao20143d], Topologically Associated Domains (TADs) [@nora2012spatial;@dixon2012topological], and A/B compartments [@lieberman2009comprehensive].
+At the kilobase scale, chromatin loops connect gene promoters with distal enhancers, thereby regulating gene expression [@Lupianez:2015aa; @Franke:2016aa].
+At the megabase scale, TADs represent regions on the linear genome, that are highly self-interacting.
+<!--Emerging evidence has linked TADs to critical roles in cell dynamics and cell differentiation.
+Studies have shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].--> Disruption of boundaries demarcating TADs and loops promotes cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@lupianez2016breaking;@Sun:2018aa;@Meaburn:2007aa].
+Identifying the precise location of TAD and chromatin loop boundaries remains a top priority in our goal to fully understand the functionality of the human genome.
 
 Several methods have been proposed to identify genomic coordinates of TADs (reviewed in [@Zufferey:2018aa; @forcato2017comparison]), and chromatin loops [@rao20143d; @Ay:2014aa; @Heinz:2010aa; @salameh2019supervised].
-However, a key limitation among most of these TAD- and loop callers is that they rely heavily on Hi-C data *resolution*.
-Resolution refers to the sizes of genomic regions (bins) used to segment the linear genome [@li2019comparison].
-Lower resolutions contribute to larger bin sizes, which lead to uncertainty in the location of boundaries.
+However, a key limitation among most of these TAD- and loop callers is that they depend on Hi-C data *resolution*.
+Resolution refers to the size of genomic regions (bins) used to segment the linear genome [@li2019comparison].
+Lower resolution contribute to larger bin size, which leads to increased uncertainty in the location of boundaries.
 Due to high sequencing costs, most available Hi-C datasets have relatively low resolution, ranging from 25 kb to 100 kb.
-Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth, obtaining high resolution remains difficult [@schmitt2016genome].
 While these low-resolution Hi-C datasets can be used to probe higher-order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define TAD and loop boundaries [@fudenberg2016formation].
+Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth [@schmitt2016genome], obtaining high resolution remains difficult.
 
 Another limitation among domain callers is that they disregard prior knowledge about functional genomic annotations associated with TAD and loop boundaries, referred hereafter as domain boundaries.
-The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been identified as components of the loop extrusion model, whereby DNA is extruded through cohesin rings forming chromatin loops [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
-Additionally, distinct patterns of histone modifications have also been shown to be present at boundaries, including H3K36me3 [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
+The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been identified as components of the loop extrusion model<!--, whereby DNA is extruded through cohesin rings forming chromatin loops--> [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
+Furthermore, distinct patterns of histone modifications have also been shown to be present at boundaries<!--including H3K36me3--> [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
 These genomic annotations are obtained using chromatin immunoprecipitation followed by high-throughput DNA sequencing (ChIP-seq).
@@
 
-We present *preciseTAD*, an R package implementing an optimally tuned machine learning framework for precise identification of domain boundaries using genome annotation data.
-Our method utilizes the random forest (RF) algorithm trained on chromatin segmentation (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) data.
-We introduce a systematic pipeline for building optimal boundary prediction classifier.
-We found that spatial associations (distance) between boundaries and annotations perform best, transcription factor binding sites further improve prediction accuracy, and a simple random undersampling technique effectively addresses the negative effect of class imbalance.
-Translated from Hi-C data resolution level to base level (annotating each base and predicting its boundary probability), *preciseTAD* employs density-based clustering (DBSCAN) and scalable partitioning around medoids (CLARA) on prediction probabilities to select genome annotation-guided boundary coordinates.
+We present *preciseTAD*, an optimally tuned machine learning framework for precise identification of domain boundaries using genome annotation data.
+Our method utilizes the random forest (RF) algorithm trained on high-resolution chromatin segmentation (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) data to predict low-resolution boundaries.
+We introduce a systematic pipeline for building the optimal boundary prediction classifier.
+We found that spatial associations (linear distance) between boundaries and annotations perform best, transcription factor binding sites further improve prediction accuracy, and a simple random undersampling technique effectively addresses the negative effect of class imbalance.
+Translated from Hi-C data resolution level to base level (annotating each base and predicting its boundary probability), *preciseTAD* employs density-based clustering (DBSCAN) and scalable partitioning around medoids (CLARA) to select genome annotation-guided boundary coordinates.
 This approach circumvents resolution restrictions of Hi-C data, allowing for the precise detection of biologically meaningful boundaries.
@@
 We present *preciseTAD*, a machine learning approach for precise prediction of TAD or loop boundaries from functional genomic annotations.
-*preciseTAD* leverages a random forest (RF) classification model built on ground truth TAD/loop boundaries obtained from domain calling tools, and genomic annotations as the predictor space.
+*preciseTAD* leverages a random forest (RF) classification model built on low-resolution TAD/loop boundaries obtained from domain calling tools, and high-resolution genomic annotations as the predictor space.
+*preciseTAD* predicts the probability of each base being a boundary, and identifies the precise location of boundary regions and the most likely boundary points.
 *preciseTAD* was benchmarked against two boundary calling tools, Arrowhead [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
@@
 We show that binding of four transcription factors (SMC3, RAD21, CTCF, ZNF143) is sufficient for accurate boundary predictions.
-Applied to each annotated base, the model predicts the probability for each base to be a boundary.
-Further, coupled with spatial clustering (DBSCAN) and scalable partition around medoids clustering (CLARA), it allows for the detection of boundaries at the base-level resolution.
 *preciseTAD* is implemented as an R package, and allows for precise prediction of boundaries for any cell type for which the corresponding genomic annotations are available.
@@
 <!--Ideally, we would benchmark *preciseTAD* against simulated boundaries.
-While methods for simulating Hi-C data sets with boundary annotations exist [@forcato2017comparison; @zheng2020freehi], methods for simulating the associated genomic annotations (the main component guiding *preciseTAD* predictions) are lacking.-->Ultra-deep Hi-C sequencing [@bonev2017multiscale] and newer technologies for precise mapping of chromatin interactions (e.g., Micro-C [@Krietenstein:2020aa]), coupled with more precise technologies for genomic annotation profiling (e.g., CUT&RUN for precise mapping of transcription factor binding sites) will help to refine the location and the genomic signatures of "ground truth" TAD boundaries.
+While methods for simulating Hi-C data sets with boundary annotations exist [@forcato2017comparison; @zheng2020freehi], methods for simulating the associated genomic annotations (the main component guiding *preciseTAD* predictions) are lacking.-->Ultra-deep Hi-C sequencing [@bonev2017multiscale] and newer technologies for precise mapping of chromatin interactions (e.g., Micro-C [@Krietenstein:2020aa]), coupled with more precise technologies for genomic annotation profiling (e.g., CUT&RUN for precise mapping of transcription factor binding sites) will help to refine the location and the genomic signatures of "ground truth" boundaries.
 In the current work, given *preciseTAD* can be trained on the whole-genome data, we feel that the total number of TAD/loop boundaries is sufficient to guide learning of the association between genomic annotations and boundaries for precise boundary predictions.
@@
 The hierarchical nature of TAD boundaries [@weinreb2016identification; @fraser2015hierarchical; @Cresswell:2020ab] is not considered by *preciseTAD* due to the lack of gold standard of TAD hierarchy.
+*preciseTAD* also does not consider the directionality of CTCF binding [@Harrold:2020aa] as it predicts individual boundaries in contrast to pairs of convergent CTCF motifs marking individual domains.
 Recent research distinguishes CTCF-associated boundaries, CTCF-negative YY1-enriched boundaries, CTCF- and YY1- depleted promoter boundaries, and the fourth class of weak boundaries largely depleted of all three features [@Krietenstein:2020aa].
@@
 This may lead to some TAD boundaries being undetected by *preciseTAD* despite being detected by domain callers.
-Our future work will include defining separate models trained on different TAD boundary types and predicting precise locations for each of them.
+Our future work will involve incorporating the directionality of CTCF binding in predictive modeling, including additional predictor types, and defining separate models trained on different boundary types.
 

### 2020-08-19 Manuscript/manuscript.Rmd
Add discussion paragraph with new refs

@@
 **Background.** High-throughput chromosome conformation capture technology (Hi-C) revealed extensive DNA looping and folding into discrete 3D domains.
-Among these are Topologically Associated Domains (TADs) and chromatin loops, critical for cellular processes like gene regulation and cell differentiation.
+Among these are Topologically Associated Domains (TADs) and chromatin loops, 3D domains critical for cellular processes like gene regulation and cell differentiation.
 The relatively low resolution of Hi-C data (regions of several kilobases in size) prevents precise mapping of domain boundaries.
@@
 
+*preciseTAD* requires both cell-type-specific chromatin conformation capture data (Hi-C in the current study) and genome annotation data.
+Hi-C data provides information about the approximate location of domain boundaries, while genome annotation data is used to train a model that can predict boundaries at the base-level resolution.
+The diversity of chromatin conformation capture technologies [@Kempfer:2019aa] and analysis methods [@Hansen:2019aa] limits the availability of harmonized cell-type-specific domain boundary information.
+Although the ENCODE, NIH Roadmap Epigenomics, FANTOM5, BLUEPRINT, and other members of the International Human Epigenome Consortium (IHEC) [@Stunnenberg:2016aa] have been actively cataloging cell-type-specific genome annotation datasets, these data remain very sparse.
+Efforts to systematically catalog chromatin conformation capture data [@Wang:2018ab] and impute missing cell-type-specific genome annotation information [@Schreiber:2020aa] started to appear.
+We envision the broader availability of matched cell-type-specific omics data will enable a more systematic analysis of domain boundaries using *preciseTAD*.
+Importantly, the *preciseTAD* model trained in one cell type can be used to predict domain boundaries in another cell line using only genome annotation information (CTCF, SMC3, RAD21, ZNF143) from that cell line, thus lowering the data availability requirements.
+
 In summary, we demonstrate that TAD/loop boundary prediction is a multi-faceted problem requiring consideration of multiple statistical and biological properties of genomic data.

### 2020-08-23 Scripts_for_results/06_creating_enriched_heatmaps.Rmd
updated results scripts

@@
 ```
+
+########################################3
+
+# Plotting
+
+```{r}
+
+pred_bound_list <- GRangesList()
+true_bound_list <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+                                    chrs[i],
+                                    "/rus/distance/preciseTAD_holdout.rds"))
+
+  true_bound_list[[i]] <- called_and_pred[[3]]
+  pred_bound_list[[i]] <- called_and_pred[[2]]
+
+}
+
+all_true_bounds <- do.call("c", true_bound_list)
+all_pred_bounds <- do.call("c", pred_bound_list)
+
+length(all_true_bounds) #
+length(all_pred_bounds) #
+
+e=5
+norm_mat_pt_ctcf <- normalizeToMatrix(genomicElements.GR[[1]], 
+                              all_pred_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_pt_ctcf <- colSums(norm_mat_pt_ctcf[])
+norm_mat_pt_rad21 <- normalizeToMatrix(genomicElements.GR[[2]], 
+                              all_pred_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_pt_rad21 <- colSums(norm_mat_pt_rad21[])
+norm_mat_pt_smc3 <- normalizeToMatrix(genomicElements.GR[[3]], 
+                              all_pred_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_pt_smc3 <- colSums(norm_mat_pt_smc3[])
+norm_mat_pt_znf143 <- normalizeToMatrix(genomicElements.GR[[4]], 
+                              all_pred_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_pt_znf143 <- colSums(norm_mat_pt_znf143[])
+
+norm_mat_a_ctcf <- normalizeToMatrix(genomicElements.GR[[1]], 
+                              all_true_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_a_ctcf <- colSums(norm_mat_a_ctcf[])
+norm_mat_a_rad21 <- normalizeToMatrix(genomicElements.GR[[2]], 
+                              all_true_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_a_rad21 <- colSums(norm_mat_a_rad21[])
+norm_mat_a_smc3 <- normalizeToMatrix(genomicElements.GR[[3]], 
+                              all_true_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_a_smc3 <- colSums(norm_mat_a_smc3[])
+norm_mat_a_znf143 <- normalizeToMatrix(genomicElements.GR[[4]], 
+                              all_true_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_a_znf143 <- colSums(norm_mat_a_znf143[])
+
+df <- data.frame(X = rep(c(1:200),8),
+                 E = c(norm_mat_pt_ctcf,
+                       norm_mat_pt_rad21,
+                       norm_mat_pt_smc3,
+                       norm_mat_pt_znf143,
+                       norm_mat_a_ctcf,
+                       norm_mat_a_rad21,
+                       norm_mat_a_smc3,
+                       norm_mat_a_znf143),
+                 Tool = c(rep("preciseTAD", 200*4),
+                          rep("Arrowhead", 200*4)),
+                 A = rep(c(rep("CTCF", 200),
+                       rep("RAD21", 200),
+                       rep("SMC3", 200),
+                       rep("ZNF143", 200)),2))
+
+ggplot(data=df, aes(x=X, y=E/5000, group=Tool, color=Tool)) +
+  facet_grid(. ~ A) +
+  geom_line(alpha=.75, size=1.5) +
+  xlab("Distance from boundary (kb)") +
+  ylab("") +
+  scale_color_manual(name="Tool", 
+                       values=c("blue", "forestgreen"))+
+  scale_x_continuous(breaks=c(0,100,200),
+                     label=c("-5", "Center", "5")) +
+  theme_minimal() +
+    theme_bw()+
+    theme(axis.text.x = element_text(size = 15),
+          axis.text.y = element_text(size = 20),
+          axis.title.x = element_text(size = 20),
+          axis.title.y = element_text(size = 20),
+          panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+          strip.text.x = element_text(size = 20),
+          #panel.spacing = unit(2, "lines"),
+          legend.text=element_text(size=20),
+          legend.title=element_text(size=20),
+          plot.title = element_text(size=20),
+          legend.position = "bottom")
+
+################################################################################
+
+pred_bound_list <- GRangesList()
+true_bound_list <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
+                                    chrs[i],
+                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))
+
+  true_bound_list[[i]] <- called_and_pred[[3]]
+  pred_bound_list[[i]] <- called_and_pred[[2]]
+
+}
+
+all_true_bounds <- do.call("c", true_bound_list)
+all_pred_bounds <- do.call("c", pred_bound_list)
+
+length(all_true_bounds) #
+length(all_pred_bounds) #
+
+e=10
+norm_mat_pt_ctcf <- normalizeToMatrix(genomicElements.GR[[1]], 
+                              all_pred_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_pt_ctcf <- colSums(norm_mat_pt_ctcf[])
+norm_mat_pt_rad21 <- normalizeToMatrix(genomicElements.GR[[2]], 
+                              all_pred_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_pt_rad21 <- colSums(norm_mat_pt_rad21[])
+norm_mat_pt_smc3 <- normalizeToMatrix(genomicElements.GR[[3]], 
+                              all_pred_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_pt_smc3 <- colSums(norm_mat_pt_smc3[])
+norm_mat_pt_znf143 <- normalizeToMatrix(genomicElements.GR[[4]], 
+                              all_pred_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_pt_znf143 <- colSums(norm_mat_pt_znf143[])
+
+norm_mat_p_ctcf <- normalizeToMatrix(genomicElements.GR[[1]], 
+                              all_true_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_p_ctcf <- colSums(norm_mat_p_ctcf[])
+norm_mat_p_rad21 <- normalizeToMatrix(genomicElements.GR[[2]], 
+                              all_true_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_p_rad21 <- colSums(norm_mat_p_rad21[])
+norm_mat_p_smc3 <- normalizeToMatrix(genomicElements.GR[[3]], 
+                              all_true_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_p_smc3 <- colSums(norm_mat_p_smc3[])
+norm_mat_p_znf143 <- normalizeToMatrix(genomicElements.GR[[4]], 
+                              all_true_bounds, 
+                              value_column = "coverage", 
+                              extend = e*1000, 
+                              w = 50,
+                              mean_mode = "coverage")
+norm_mat_p_znf143 <- colSums(norm_mat_p_znf143[])
+
+df <- data.frame(X = rep(c(1:400),8),
+                 E = c(norm_mat_pt_ctcf,
+                       norm_mat_pt_rad21,
+                       norm_mat_pt_smc3,
+                       norm_mat_pt_znf143,
+                       norm_mat_p_ctcf,
+                       norm_mat_p_rad21,
+                       norm_mat_p_smc3,
+                       norm_mat_p_znf143),
+                 Tool = c(rep("preciseTAD", 400*4),
+                          rep("Peakachu", 400*4)),
+                 A = rep(c(rep("CTCF", 400),
+                       rep("RAD21", 400),
+                       rep("SMC3", 400),
+                       rep("ZNF143", 400)),2))
+
+ggplot(data=df, aes(x=X, y=E/10000, group=Tool, color=Tool)) +
+    facet_grid(. ~ A) +
+    geom_line(alpha=.75, size=1.5) +
+    xlab("Distance from boundary (kb)") +
+    ylab("") +
+    scale_color_manual(name="Tool", 
+                       values=c("red", "forestgreen"))+
+    scale_x_continuous(breaks=c(0,200,400),
+                       label=c("-10", "Center", "10")) +
+    theme_minimal() +
+    theme_bw()+
+    theme(axis.text.x = element_text(size = 15),
+          axis.text.y = element_text(size = 20),
+          axis.title.x = element_text(size = 20),
+          axis.title.y = element_text(size = 20),
+          panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+          strip.text.x = element_text(size = 20),
+          #panel.spacing = unit(2, "lines"),
+          legend.text=element_text(size=20),
+          legend.title=element_text(size=20),
+          plot.title = element_text(size=20),
+          legend.position = "bottom")
+```

### 2020-08-23 Scripts_for_results/03_creating_annotation_specific_barplots.R

@@ -1,0 +1,158 @@
+#03_creating_annotation_specific_barplots
+
+library(S4Vectors)
+library(GenomicRanges)
+library(ggplot2)
+library(caret)
+library(randomForest)
+library(glmnet)
+library(gbm)
+library(DMwR)
+library(rtracklayer)
+library(Biostrings)
+library(BSgenome)
+library(cluster)
+library(pROC)
+library(SuperLearner)
+library(data.table)
+library(PRROC)
+library(bigmemory)
+library(ranger)
+library(dplyr)
+library(parallel)
+library(doSNOW)
+library(foreach)
+library(pbapply)
+library(ggpubr)
+library(scales)
+library(GGally)
+library(VennDiagram)
+library(network)
+library(sna)
+library(gtable)
+library(grid)
+library(magrittr) 
+library(DT)
+library(tidyverse)
+library(reshape)
+library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
+library(GenometriCorr)
+library(ggsignif)
+library(Vennerable)
+library(VennDiagram)
+library(ChIPpeakAnno)
+library(EnrichedHeatmap)
+
+source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
+badata_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/badata_gm12878_5kb_arrowhead_annotations.rds")
+
+all_rfperfs <- data.frame(Perf=badata_gm12878_5kb)
[…]

### 2020-08-23 Scripts_for_results/04_creating_rfe_lineplot.R

@@ -1,0 +1,98 @@
+#04_creating_rfe_lineplot
+
+library(S4Vectors)
+library(GenomicRanges)
+library(ggplot2)
+library(caret)
+library(randomForest)
+library(glmnet)
+library(gbm)
+library(DMwR)
+library(rtracklayer)
+library(Biostrings)
+library(BSgenome)
+library(cluster)
+library(pROC)
+library(SuperLearner)
+library(data.table)
+library(PRROC)
+library(bigmemory)
+library(ranger)
+library(dplyr)
+library(parallel)
+library(doSNOW)
+library(foreach)
+library(pbapply)
+library(ggpubr)
+library(scales)
+library(GGally)
+library(VennDiagram)
+library(network)
+library(sna)
+library(gtable)
+library(grid)
+library(magrittr) 
+library(DT)
+library(tidyverse)
+library(reshape)
+library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
+library(GenometriCorr)
+library(ggsignif)
+library(Vennerable)
+library(VennDiagram)
+library(ChIPpeakAnno)
+library(EnrichedHeatmap)
+
+source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
+rfeperchr_gm12878_5kb_arrowhead_mean <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/rfeperchr_gm12878_5kb_arrowhead_mean.rds")
+rfeperchr_gm12878_10kb_peakachu_mean <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/rfeperchr_gm12878_10kb_peakachu_mean.rds")
+
[…]

### 2020-08-23 Scripts_for_results/05_creating_importance_plot.R

@@ -1,0 +1,174 @@
+#05_creating_importance_plot
+
+library(S4Vectors)
+library(GenomicRanges)
+library(ggplot2)
+library(caret)
+library(randomForest)
+library(glmnet)
+library(gbm)
+library(DMwR)
+library(rtracklayer)
+library(Biostrings)
+library(BSgenome)
+library(cluster)
+library(pROC)
+library(SuperLearner)
+library(data.table)
+library(PRROC)
+library(bigmemory)
+library(ranger)
+library(dplyr)
+library(parallel)
+library(doSNOW)
+library(foreach)
+library(pbapply)
+library(ggpubr)
+library(scales)
+library(GGally)
+library(VennDiagram)
+library(network)
+library(sna)
+library(gtable)
+library(grid)
+library(magrittr) 
+library(DT)
+library(tidyverse)
+library(reshape)
+library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
+library(GenometriCorr)
+library(ggsignif)
+library(Vennerable)
+library(VennDiagram)
+library(ChIPpeakAnno)
+library(EnrichedHeatmap)
+
+source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
+chrs <- paste0("CHR",c(1:8,10:22))
+rfeperchr <- list()
+for(i in c("GM12878")){
+  for(k in 1:length(chrs)){
+    #rfeModelResultsList <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/",
+    #                                      i,
+    #                                      "/",
[…]

### 2020-08-23 Scripts_for_results/09_visualizing_example_of_preciseTAD.R

@@ -1,17 +1,5 @@
----
-title: "Visualizing example of predicted TAD boundaries"
-author: "Spiro Stilianoudakis"
-date: "4/29/2020"
-output: html_document
----
+#09_visualizing_example_of_preciseTAD
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-## Loading packages and functions
-
-```{r}
 library(S4Vectors)
 library(GenomicRanges)
 library(ggplot2)
@@ -52,7 +40,7 @@ library(lattice)
 library(corrplot)
 library(cluster)
 library(RColorBrewer)
-library(GenometriCorr)
+#library(GenometriCorr)
 library(ggsignif)
 library(Vennerable)
 library(VennDiagram)
@@ -71,32 +59,16 @@ source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
 source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
 source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
 
-```
-
-# ARROWHEAD
-
-## Extracting TAD boundaries using the extract_boundaries_func function for ARROWHEAD defined TADs at 10kb resolution
-
-```{r}
 domains <- read.table("Z:/TAD_data_analysis/GM12878/5kb/GM12878_domain_data_5000.b.txt")
 bounds.GR <- extract_boundaries_func(domains.mat=domains, 
                                      preprocess=FALSE, 
                                      CHR=paste0("CHR", c(1:8,10:22)), 
                                      resolution=5000)
-```
 
-
-## Obtaining list of GRanges objects of ChIP-seq data used for modelling
-
-```{r}
 genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
                                              pattern="*.bed",
                                              signal=4)
-```
 
-## Creating data matrix
-
-```{r}
 tadData <- createTADdata(bounds.GR=bounds.GR,
                          resolution=5000,
                          genomicElements.GR=genomicElements.GR,
@@ -105,11 +77,7 @@ tadData <- createTADdata(bounds.GR=bounds.GR,
                          trainCHR=paste0("CHR",c(1:8,10:22))[-which(paste0("CHR",c(1:8,10:22))=="CHR14")],
                          predictCHR="CHR14",
                          seed=123)
-```
 
-## Running TADrandomForest
-
-```{r}
[…]

### 2020-08-23 Scripts_for_results/12_cross_cell_line_performances.R

@@ -1,0 +1,416 @@
+#12_cross_cell_line_performances
+
+library(S4Vectors)
+library(GenomicRanges)
+library(ggplot2)
+library(caret)
+library(randomForest)
+library(glmnet)
+library(gbm)
+library(DMwR)
+library(rtracklayer)
+library(Biostrings)
+library(BSgenome)
+library(cluster)
+library(pROC)
+library(SuperLearner)
+library(data.table)
+library(PRROC)
+library(bigmemory)
+library(ranger)
+library(dplyr)
+library(parallel)
+library(doSNOW)
+library(foreach)
+library(pbapply)
+library(ggpubr)
+library(scales)
+library(GGally)
+library(VennDiagram)
+library(network)
+library(sna)
+library(gtable)
+library(grid)
+library(magrittr) 
+library(DT)
+library(tidyverse)
+library(reshape)
+library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
+library(GenometriCorr)
+library(ggsignif)
+library(Vennerable)
+library(VennDiagram)
+library(ChIPpeakAnno)
+library(EnrichedHeatmap)
+library(ComplexHeatmap)
+library(circlize)
+library(cotools)
+library(ggcorrplot)
+library(circlize)
+library(egg)
+
+source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/createTADdata.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
+
[…]

### 2020-08-23 Manuscript/manuscript.Rmd
edited figure legends and numbering

@@
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
-Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, were found to co-localize more frequently around *preciseTAD* predicted boundaries (Figure 5B).
-Furthermore, signal heatmaps indicated that our predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Figure 5 C-D; Supplementary Figures 5-6).
-When compared to called TAD or loop boundaries, *preciseTAD* boundaries were statistically significantly closer to the same cell line-specific top-ranked TFBS (p<0.001 and p<0.001 versus Arrowhead and Peakachu respectively) (Figure 5E, Supplementary Figure 7).
+
+Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, were found to co-localize more frequently around *preciseTAD* predicted TAD and loop boundaries compared to Arrowhead called TAD and Peakached loop boundaries respectively (Figure 5B-5C; Supplementary Figure 5).
+Furthermore, signal heatmaps indicated that our predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Supplementary Figures 6-7).
+When compared to called TAD or loop boundaries, *preciseTAD* boundaries were statistically significantly closer to the same cell line-specific top-ranked TFBS (p<0.001 and p<0.001 versus Arrowhead and Peakachu respectively) (Figure 6A, Supplementary Figure 8).
 These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
+
+![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of ARROWHEAD called TAD boundaries (blue) vs *preciseTAD* predicted TAD boundaries (green) on GM12878 (chr 14: 50085000-50800000).
+The black line represents the predicted probability of each base being a TAD boundary.
+Genome browser visualization of bigwig files for known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143 is presented underneath.
+Profile plots comparing the signal strength of top TFBS around flanked (B) ARROWHEAD called TAD boundaries (blue) and *preciseTAD* predicted TAD boundaries (green), and (C) around Peakachu loop boundaries (red) and *preciseTAD* predicted loop boundaries (green).](Figures/figure5.png)
 
@@
 Boundaries involving Arrowhead were flanked by 5 kb, while boundaries involving Peakachu were flanked by 10 kb.
-We found that 35% of *preciseTAD* predicted TAD boundaries and 55% of *preciseTAD* predicted loop boundaries were conserved between cell lines, compared to only 26% and 55% for Arrowhead and Peakachu alone (Figure 5F).
+We found that 35% of *preciseTAD* predicted TAD boundaries and 55% of *preciseTAD* predicted loop boundaries were conserved between cell lines, compared to only 26% and 55% for Arrowhead and Peakachu alone (Figure 6B).
 The better conservation of *preciseTAD*-predicted boundaries further supports the notion of their higher biological relevance.
 
-![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of preciseTAD (green) vs.
-Arrowhead (blue) boundaries on GM12878 (chr 14: 50085000-50800000).
-The black line represents the predicted probability of each base being a TAD boundary.
-(B) Genome browse visualization of bigwig files for known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143.
-(C) Enriched heatmaps comparing the enrichment of CTCF signal around Arrowhead TAD boundaries and preciseTAD boundaries, and (D) around Peakachu loop boundaries and preciseTAD for the entire genome.
-(E) Log 2 genomic distances from boundaries to the nearest CTCF sites.
-(F) Venn diagrams illustrating the levels of conservation between TAD/loop boundaries for GM12878 (red) and K562 (blue) identified by preciseTAD (using Arrowhead; top left), Arrowhead (top right), preciseTAD (using Peakachu; bottom left), and Peakachu (bottom right).
-The median Jaccard Index (IQR) across each chromosome is provided below each Venn diagram](Figures/figure5.png)
+![**preciseTAD predicted boundaries are both statistically significantly closer to CTCF sites and more conserved across cell lines**.
+(A) Log2 genomic distances from called and predicted boundaries to nearest CTCF sites.
+The p-value is derived from the Wilcoxon Rank Sum test.
+(B) Venn diagrams illustrating the levels of conservation between TAD/loop boundaries for GM12878 (red) and K562 (blue) identified by *preciseTAD* (using ARROWHEAD; top left), ARROWHEAD (top right), *preciseTAD* (using PEAKACHU; bottom left), and PEAKACHU (bottom right).
+The median Jaccard Index (IQR) across each chromosome is provided below each venn diagram.](Figures/figure6.png)
 
@@
 The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model.
-We found that 95.6% and 95.7% of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 8).
+We found that 95.6% and 95.7% of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 9).
 This is expected as loop boundaries (Peakachu) are more abundant, while TAD boundaries (Arrowhead) represent the narrower level of the 3D chromatin organization.
@@
 As a heuristic, we evaluated the pairwise combination of four different thresholds ($t=(0.95,0.975,0.99,1.0)$) and four different $eps$ values ($\epsilon=(r, 2r, 3r, 4r, 5r)$)), where $r=5000$, the optimal resolution.
-We found that the normalized overlaps--calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries --between top TFBS sites and flanked preciseTAD boundaries were maximized for combinations of $t=1.0$ and $eps=r$ (Supplementary Figure 9).
+We found that the normalized overlaps--calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries --between top TFBS sites and flanked *preciseTAD* boundaries were maximized for combinations of $t=1.0$ and $eps=r$ (Supplementary Figure 10).
 
@@
 
-**Supplementary Figure 5.
-preciseTAD boundaries are more enriched for known molecular drivers of 3D chromatin.** Enriched heatmaps comparing the enrichment of preciseTAD (green) boundaries with Arrowhead called TAD boundaries (blue) around key (A) GM12878-specific and (B) K562-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
+**Supplementary Figure 5.** Profile plots comparing the signal strength of top TFBS around flanked (B) ARROWHEAD called TAD boundaries (blue) and *preciseTAD* predicted TAD boundaries (green), and (C) around Peakachu loop boundaries (red) and preciseTAD predicted loop boundaries (green) on K562.
 
-**Supplementary Figure 6.
-preciseTAD boundaries are more enriched for known molecular drivers of 3D chromatin.** Enriched heatmaps comparing the enrichment of preciseTAD (green) boundaries with Peakachu predicted chromatin loop boundaries (blue) around key (A) GM12878-specific and (B) K562-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
+**Supplementary Figure 6.** *preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.
+Enriched heatmaps comparing the enrichment of (A) ARROWHEAD called TAD boundaries vs *preciseTAD* predicted TAD boundaries, and (B) Peakachu loop boundaries vs *preciseTAD* predicted loop boundaries around key GM12878-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
 
-**Supplementary Figure 7.
-preciseTAD boundaries are spatially closer to known molecular drivers of 3D chromatin.** Boxplots comparing the $log_{2}$ genomic distances from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
+**Supplementary Figure 7.** *preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.
+Enriched heatmaps comparing the enrichment of (A) ARROWHEAD called TAD boundaries vs *preciseTAD* predicted TAD boundaries, and (B) Peakachu loop boundaries vs preciseTAD predicted loop boundaries around key K562-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
 
-**Supplementary Figure 8.
-preciseTAD predicted TAD boundaries using Arrowhead are nested within preciseTAD predicted chromatin loop boundaries using Peakachu.** Venn diagrams illustrating the agreement between boundaries predicted using Arrowhead- and Peakachu-trained models.
-TAD/loop boundaries were flanked by resolution (5 kb for models using Arrowhead and 10 kb for Peakachu).
+**Supplementary Figure 8.** *preciseTAD* boundaries are spatially closer to known molecular drivers of 3D chromatin.
+Boxplots comparing the log2 genomic distances from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
+The p-value is derived from the Wilcoxon Rank Sum test.
 
-**Supplementary Figure 9.** Linecharts illustrating the normalized overlap between known molecular drivers of 3D chromatin and flanked predicted TAD boundaries identified by preciseTAD (using Arrowhead ground truth boundaries) for different combinations of thresholds (t) and epsilon parameter values (eps) on GM12878 and for chromosome 22.
+**Supplementary Figure 9.** *preciseTAD* predicted TAD boundaries using ARROWHEAD are nested within *preciseTAD* predicted chromatin loop boundaries using PEAKACHU.
+Venn diagrams illustrating the agreement between boundaries predicted using ARROWHEAD- and Peakachu-trained models.
+TAD/loop boundaries were flanked by resolution (5 kb for models using ARROWHEAD and 10 kb for PEAKACHU).
+
+**Supplementary Figure 10.** Linecharts illustrating the normalized overlap between known molecular drivers of 3D chromatin and flanked predicted TAD boundaries identified by *preciseTAD* (using Arrowhead ground truth boundaries) for different combinations of thresholds (t) and epsilon parameter values (eps) on GM12878 and for chromosome 22.
 Normalized overlap was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted (on chr22).

### 2020-08-25 Manuscript/manuscript.Rmd
fixed spacing issue
Add my tweaks back

@@
 ---
-title: "preciseTAD: A machine learning framework for precise TAD boundary prediction at base level resolution"
+title: "preciseTAD: A machine learning framework for precise TAD boundary prediction at base-level resolution"
 csl: styles.ref/genomebiology.csl
@@
 **Background.** High-throughput chromosome conformation capture technology (Hi-C) revealed extensive DNA looping and folding into discrete 3D domains.
-Among these are Topologically Associated Domains (TADs) and chromatin loops, 3D domains critical for cellular processes like gene regulation and cell differentiation.
+These include Topologically Associated Domains (TADs) and chromatin loops, 3D domains critical for cellular processes like gene regulation and cell differentiation.
 The relatively low resolution of Hi-C data (regions of several kilobases in size) prevents precise mapping of domain boundaries.
-However, the high resolution of genomic annotations associated with boundaries, such as CTCF, members of cohesin complex, suggest they can inform the precise location of domain boundaries.
+However, the high resolution of genomic annotations associated with boundaries, such as CTCF, members of cohesin complex, suggests they can inform the precise location of domain boundaries.
 Several methods attempted to leverage genome annotation data for predicting TAD/loop boundaries; however, they overlooked key characteristics of the data, such as spatial associations between an annotation and a boundary, and a much smaller number of boundaries than the rest of the genome (class imbalance).
@@
 We investigated several feature engineering and resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) to select the most optimal data characteristics and address class imbalance.
-Density-based clustering and scalable partitioning techniques were used to identify the precise location of boundary regions.
+Density-based clustering and scalable partitioning techniques were used to identify the precise location of boundary regions and summit points.
 We benchmarked our method against the Arrowhead domain caller and a novel chromatin loop prediction algorithm, Peakachu, on two most annotated cell lines.
@@
 
-**Conclusion.** Our study implements the method and outlines strategies for TAD/loop boundary prediction using genome annotation data.
-The precise identification of domain boundaries will improve our understanding of how genomic regulators are associated with the 3D structure of the genome.
+**Conclusion.** Our study implements the method and outlines strategies for precise domain boundary prediction using genome annotation data.
+The precise identification of domain boundaries will improve our understanding of how genomic regulators are shaping the 3D structure of the genome.
 
@@
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
-
 Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, were found to co-localize more frequently around *preciseTAD* predicted TAD and loop boundaries compared to Arrowhead called TAD and Peakached loop boundaries respectively (Figure 5B-5C; Supplementary Figure 5).

### 2020-08-25 Manuscript/manuscript.Rmd
Major edits

@@
 **Background.** High-throughput chromosome conformation capture technology (Hi-C) revealed extensive DNA looping and folding into discrete 3D domains.
-These include Topologically Associated Domains (TADs) and chromatin loops, 3D domains critical for cellular processes like gene regulation and cell differentiation.
+These include Topologically Associating Domains (TADs) and chromatin loops, 3D domains critical for cellular processes like gene regulation and cell differentiation.
 The relatively low resolution of Hi-C data (regions of several kilobases in size) prevents precise mapping of domain boundaries.
 However, the high resolution of genomic annotations associated with boundaries, such as CTCF, members of cohesin complex, suggests they can inform the precise location of domain boundaries.
-Several methods attempted to leverage genome annotation data for predicting TAD/loop boundaries; however, they overlooked key characteristics of the data, such as spatial associations between an annotation and a boundary, and a much smaller number of boundaries than the rest of the genome (class imbalance).
+Several methods attempted to leverage genome annotation data for predicting domain boundaries; however, they overlooked key characteristics of the data, such as spatial associations between an annotation and a boundary, and a much smaller number of boundaries than the rest of the genome (class imbalance).
 
@@
 
-The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of the 3-dimensional (3D) structure of the human genome such as chromatin loops [@rao20143d], Topologically Associated Domains (TADs) [@nora2012spatial;@dixon2012topological], and A/B compartments [@lieberman2009comprehensive].
+The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of the 3-dimensional (3D) structure of the human genome such as chromatin loops [@rao20143d], Topologically Associating Domains (TADs) [@nora2012spatial;@dixon2012topological], and A/B compartments [@lieberman2009comprehensive].
 At the kilobase scale, chromatin loops connect gene promoters with distal enhancers, thereby regulating gene expression [@Lupianez:2015aa; @Franke:2016aa].
@@
 We present *preciseTAD*, an optimally tuned machine learning framework for precise identification of domain boundaries using genome annotation data.
-Our method utilizes the random forest (RF) algorithm trained on high-resolution chromatin segmentation (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) data to predict low-resolution boundaries.
+Our method utilizes the random forest (RF) algorithm trained on high-resolution chromatin state data (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) data to predict low-resolution boundaries.
 We introduce a systematic pipeline for building the optimal boundary prediction classifier.
@@
 Chromosome 9 was excluded from all downstream analyses due to the sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-Cell-line-specific genomic annotations (BroadHMM chromatin segmentations (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 2).
+Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 2).
 
@@
 A ($log_2 + 1$)-transformation of distance was used to account for the skewness of the distance distributions.
-Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin segmentations lack signal values.
+Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin states lack signal values.
 
@@
 We assessed the biological significance of our predicted boundaries by their association with several known molecular drivers of 3D chromatin architecture, including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
-To do so, we used the *computeMatrix* and *plotHeatmap* tools offered by deepTools (version 2.0) [@ramirez2016deeptools] via integration with Galaxy (version 3.3.2.0.0) [@afgan2018galaxy].
+To do so, we used the *computeMatrix* and *plotHeatmap* tools offered by deepTools (version 2.0) [@ramirez2016deeptools] via integration with Galaxy (version 3.3.2.0.0) [@afgan2018galaxy] [???
+Correct, change to new pipeline].
 Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum tests.
@@
 
-We developed a machine learning (ML) framework aimed at determining the optimal set of data level characteristics necessary for precise prediction of boundaries of Topologically Associated Domains (TADs) and chromatin loops, collectively referred to as domain boundaries.
+We developed a machine learning (ML) framework aimed at determining the optimal set of data level characteristics necessary for precise prediction of boundaries of Topologically Associating Domains (TADs) and chromatin loops, collectively referred to as domain boundaries.
 We chose the random forest (RF) algorithm as our binary classification tool.
@@
 A total of 77 cell-line-specific genomic annotations were used to build the predictor space.
-These included BroadHMM chromatin segmentation, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 2).
+These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 2).
 Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
@@
 
-![**A diagram of the machine learning framework used to build TAD/loop boundary region prediction models.** Step 1 defines the dimensions of the data matrix $A_{N \times (p+1)}$ used for training and testing by establishing a resolution, $r$, at which to bin the linear genome into $N$ genomic bins for each chromosome, except a holdout chromosome *i*.
+![**A diagram of the machine learning framework used to build domain boundary region prediction models.** Step 1 defines the dimensions of the data matrix $A_{N \times (p+1)}$ used for training and testing by establishing a resolution, $r$, at which to bin the linear genome into $N$ genomic bins for each chromosome, except a holdout chromosome *i*.
 The response vector **Y** is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$).
@@
 |        Peakachu       |       10   kb     |                        16,185                       |                          21,421                              |                267,682               |        0.14            |
-Table: TAD/loop boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the GM12878 cell line.
+Table: Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the GM12878 cell line.
 Class imbalance is calculated as the ratio of total number of unique boundaries to the total number of genomic bins.
@@
 
-## Transcription factor binding sites outperform histone- and chromatin segmentation-specific models
+## Transcription factor binding sites outperform histone- and chromatin state-specific models
 
 We hypothesized that the type of genomic annotations may also affect predictive performance.
-Using the established optimal settings (RUS, Distance, 5 kb bins), we built separate random forest models using BroadHMM chromatin segmentation, histone modifications (HM), and transcription factor binding sites (TFBS).
+Using the established optimal settings (RUS, Distance, 5 kb bins), we built separate random forest models using BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS).
 We found that models built on TFBSs outperformed other annotation-specific models, with results consistent for loop boundaries, on both cell lines (Figure 4A; Supplementary Figures 4A).
@@
 However, given that we trained our model on chromosome-specific data, the most significant annotations varied for each chromosome set.
-To determine transcription factors most important for boundary prediction, we clustered the predictive importance (mean decrease in accuracy) of the top eight significant TFs across chromosomes.
-We found that similar to other studies [@sanborn2015chromatin; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were consistently predictive of TAD and loop boundaries (Figure 4C; Supplementary Figures 4C).
-We optimized our model by only considering these top informative TFBS when building the random forest, thereby decreasing computational burden while maintaining high predictive performance.
+To determine transcription factors most important for boundary prediction across all chromosomes, we clustered the predictive importance (mean decrease in accuracy) of the top eight significant TFs across chromosomes.
+We found four transcription factors, CTCF, RAD21, SMC3, and ZNF143, being consistently predictive of TAD and loop boundaries (Figure 4C; Supplementary Figures 4C).
+We optimized our model by only considering these top four TFBS when building the random forest model, thereby decreasing computational burden while maintaining high predictive performance.
 In summary, our model was able to yield the known molecular drivers of the loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
@@
 Having demonstrated the optimal performance in our framework's ability to predict boundary regions, we next attempted to predict boundary regions in one cell line when trained on another (See Methods).
-We found that training and testing using Arrowhead ground truth TAD boundaries and genomic elements from GM12878 resulted in an average AUC=0.845 (Figure 4D).
-When training on GM12878 and testing on K562, our model's average AUC only marginally decreased to 0.803.
-Likewise, training and testing on Peakachu resulted in an average AUC=0.885 and slightly reduced to 0.868 when trained on GM12878 and tested on K562.
-Results were consistent when training on K562 and testing on GM12878 (Supplementary Figure 4D).
-These results suggest that a classifier trained on the data from one cell line performs well when using data from another cell line.
+We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from GM12878 cell line resulted in an average AUC=0.845 (Figure 4D).
+The performance of this model only slightly decreased when evaluated using K562-specific Arrowhead boundaries and genomic annotation data (AUC = 0.803).
+Likewise, the performance of the model trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable when evaluated using K562-specific Peakachu boundaries and genomic annotations (AUC=0.885 and 0.868, respectively).
+These results were consistent when training on K562 and testing on GM12878 (Supplementary Figure 4D).
+In summary, our observations suggest that a classifier trained on the data from one cell line performs well when using data from another cell line.
 
-![**Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+![**Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
@@
 The model trained on a bin-level space was then applied on a base-level space to predict each base's probability of being a boundary.
-Our method, referred to as *preciseTAD*, uses density-based hierarchical clustering (DBSCAN) and a scalable partitioning around medoids clustering (CLARA) to predict the boundary location at base resolution (see Methods).
+Our method, referred to as *preciseTAD*, uses density-based hierarchical clustering (DBSCAN) and a scalable partitioning around medoids clustering (CLARA) to predict the location of boundary regions and summit points (highest boundary probability) at base resolution (see Methods).
 
@@
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
-Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, were found to co-localize more frequently around *preciseTAD* predicted TAD and loop boundaries compared to Arrowhead called TAD and Peakached loop boundaries respectively (Figure 5B-5C; Supplementary Figure 5).
+Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, co-localized more frequently around *preciseTAD*-predicted TAD and loop boundaries compared to Arrowhead called TAD and Peakached loop boundaries respectively (Figure 5B-5C; Supplementary Figure 5).
 Furthermore, signal heatmaps indicated that our predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Supplementary Figures 6-7).
-When compared to called TAD or loop boundaries, *preciseTAD* boundaries were statistically significantly closer to the same cell line-specific top-ranked TFBS (p<0.001 and p<0.001 versus Arrowhead and Peakachu respectively) (Figure 6A, Supplementary Figure 8).
+*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Supplementary Figure 8).
 These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
 
-![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of ARROWHEAD called TAD boundaries (blue) vs *preciseTAD* predicted TAD boundaries (green) on GM12878 (chr 14: 50085000-50800000).
+![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of Arrowhead-called TAD boundaries (blue) vs.
+*preciseTAD*-predicted TAD boundaries (green) on GM12878 data (chr14:50085000-50800000).
 The black line represents the predicted probability of each base being a TAD boundary.
-Genome browser visualization of bigwig files for known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143 is presented underneath.
-Profile plots comparing the signal strength of top TFBS around flanked (B) ARROWHEAD called TAD boundaries (blue) and *preciseTAD* predicted TAD boundaries (green), and (C) around Peakachu loop boundaries (red) and *preciseTAD* predicted loop boundaries (green).](Figures/figure5.png)
+(B, C) Profile plots comparing the signal strength of CTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called boundaries (blue, B), Peakachu loop boundaries (red, C) vs.
+*preciseTAD*-predicted boundaries (green).](Figures/figure5.png)
 
@@
 TAD boundaries are relatively conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @sexton2012three].
-To assess conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, Arrowhead, and Peakachu after flanking them by the resolution of the Hi-C data.
+To assess the level of cross-cell-line conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, Arrowhead, and Peakachu.
 Boundaries involving Arrowhead were flanked by 5 kb, while boundaries involving Peakachu were flanked by 10 kb.
-We found that 35% of *preciseTAD* predicted TAD boundaries and 55% of *preciseTAD* predicted loop boundaries were conserved between cell lines, compared to only 26% and 55% for Arrowhead and Peakachu alone (Figure 6B).
+We found that 35%/55% of *preciseTAD*-predicted domain boundaries using models trained on Arrowhead/Peakachu data, respectively, were conserved between GM12878 and K562 cell lines.
+This is in contrast to only 26% and 55% for Arrowhead and Peakachu boundaries themselves (Figure 6B).
 The better conservation of *preciseTAD*-predicted boundaries further supports the notion of their higher biological relevance.
 
-![**preciseTAD predicted boundaries are both statistically significantly closer to CTCF sites and more conserved across cell lines**.
+![**preciseTAD-predicted boundaries are both statistically significantly closer to CTCF sites and more conserved across cell lines**.
 (A) Log2 genomic distances from called and predicted boundaries to nearest CTCF sites.
-The p-value is derived from the Wilcoxon Rank Sum test.
-(B) Venn diagrams illustrating the levels of conservation between TAD/loop boundaries for GM12878 (red) and K562 (blue) identified by *preciseTAD* (using ARROWHEAD; top left), ARROWHEAD (top right), *preciseTAD* (using PEAKACHU; bottom left), and PEAKACHU (bottom right).
-The median Jaccard Index (IQR) across each chromosome is provided below each venn diagram.](Figures/figure6.png)
+P-value are from the Wilcoxon Rank Sum test.
+(B) Venn diagrams illustrating the levels of conservation between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead-trained *preciseTAD* model (top left), Arrowhead boundaries themselves (top right), Peakachu-trained *preciseTAD* model (bottom left), and Peakachu boundaries themselves (bottom right).
+J - the median Jaccard Index (IQR in parentheses) across all chromosomes.](Figures/figure6.png)
 
-## *preciseTAD* predicted TAD boundaries are nested within predicted loop boundaries
+## *preciseTAD*-predicted TAD boundaries are nested within predicted loop boundaries
 
@@
 This is expected as loop boundaries (Peakachu) are more abundant, while TAD boundaries (Arrowhead) represent the narrower level of the 3D chromatin organization.
-Together with the results in Figure 4, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop domain boundaries may be driven by similar molecular mechanisms.
+Together with the results in Figure 4, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar molecular mechanisms.
 
@@
 We present *preciseTAD*, a machine learning approach for precise prediction of TAD or loop boundaries from functional genomic annotations.
-*preciseTAD* leverages a random forest (RF) classification model built on low-resolution TAD/loop boundaries obtained from domain calling tools, and high-resolution genomic annotations as the predictor space.
+*preciseTAD* leverages a random forest (RF) classification model built on low-resolution domain boundaries obtained from domain calling tools, and high-resolution genomic annotations as the predictor space.
 *preciseTAD* predicts the probability of each base being a boundary, and identifies the precise location of boundary regions and the most likely boundary points.
@@
 As a heuristic, we evaluated the pairwise combination of four different thresholds ($t=(0.95,0.975,0.99,1.0)$) and four different $eps$ values ($\epsilon=(r, 2r, 3r, 4r, 5r)$)), where $r=5000$, the optimal resolution.
-We found that the normalized overlaps--calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries --between top TFBS sites and flanked *preciseTAD* boundaries were maximized for combinations of $t=1.0$ and $eps=r$ (Supplementary Figure 10).
+We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries were maximized for combinations of $t=1.0$ and $eps=r$ (Supplementary Figure 10).
+[???
+We talked about relaxing t threshold, but it requires extensive reruns.
+Where are we on that?]
 
@@
 While methods for simulating Hi-C data sets with boundary annotations exist [@forcato2017comparison; @zheng2020freehi], methods for simulating the associated genomic annotations (the main component guiding *preciseTAD* predictions) are lacking.-->Ultra-deep Hi-C sequencing [@bonev2017multiscale] and newer technologies for precise mapping of chromatin interactions (e.g., Micro-C [@Krietenstein:2020aa]), coupled with more precise technologies for genomic annotation profiling (e.g., CUT&RUN for precise mapping of transcription factor binding sites) will help to refine the location and the genomic signatures of "ground truth" boundaries.
-In the current work, given *preciseTAD* can be trained on the whole-genome data, we feel that the total number of TAD/loop boundaries is sufficient to guide learning of the association between genomic annotations and boundaries for precise boundary predictions.
+In the current work, given *preciseTAD* can be trained on the whole-genome data, we feel that the total number of domain boundaries is sufficient to guide learning of the association between genomic annotations and boundaries for precise boundary predictions.
 
@@
 
-In summary, we demonstrate that TAD/loop boundary prediction is a multi-faceted problem requiring consideration of multiple statistical and biological properties of genomic data.
+In summary, we demonstrate that domain boundary prediction is a multi-faceted problem requiring consideration of multiple statistical and biological properties of genomic data.
 Simply considering the properties of Hi-C contact matrices ignores the fundamental roles of known molecular drivers of the 3D chromatin structures.
@@
 Our method can bridge the resolution gap between 1D ChIP-seq annotations and 3D Hi-C sequencing data for more precise and biologically meaningful boundary identification.
-We introduce *preciseTAD*, an open source R package for leveraging random forests to predict TAD/loop boundaries at base resolution.
+We introduce *preciseTAD*, an open source R package for leveraging random forests to predict domain boundaries at base resolution.
 We hope that *preciseTAD* will serve as an efficient and easy-to-use tool to further explore the genome's 3D organization.
@@
 
-**Supplementary Table 1.** Data source for Hi-C matrices used to call topologically associated domains with Arrowhead, as well as loop boundaries obtained by Peakachu.
+**Supplementary Table 1.** Data source for Hi-C matrices used to call topologically associating domains with Arrowhead, as well as loop boundaries obtained by Peakachu.
 
@@
 
-**Supplementary Table 3.** TAD/loop boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the K562 cell line.
+**Supplementary Table 3.** Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the K562 cell line.
 Class imbalance is calculated as the ratio of the total number of unique boundaries to the total number of genomic bins.
 
-**Supplementary Table 4.** *preciseTAD* predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562, using Arrowhead TAD and Peakachu chromatin loop boundary coordinates as ground truth.
+**Supplementary Table 4.** Genomic coordinates of *preciseTAD*-predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562, using Arrowhead TAD and Peakachu chromatin loop boundary coordinates as ground truth.
 For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability of being a boundary equal to 1.
 For PTBPs, the start and end (start+1) coordinates define the uniquely identified boundary coordinate within each PTBR.
-All coordinates are in hg18/GRCh37 reference genome.
+All coordinates are in hg19/GRCh37 reference genome.
 
@@
 **Supplementary Figure 4.
-Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), cis-regulated elements (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
@@
 
-**Supplementary Figure 5.** Profile plots comparing the signal strength of top TFBS around flanked (B) ARROWHEAD called TAD boundaries (blue) and *preciseTAD* predicted TAD boundaries (green), and (C) around Peakachu loop boundaries (red) and preciseTAD predicted loop boundaries (green) on K562.
+**Supplementary Figure 5.** Profile plots comparing the signal strength of top TFBS around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green), and (B) around Peakachu loop boundaries (red) and preciseTAD predicted loop boundaries (green) on K562.
+
+**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** Profile plots comparing the signal strength of CTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called boundaries (blue, A), Peakachu loop boundaries (red, B) vs.
+*preciseTAD*-predicted boundaries (green) on K562 data (chr14:50085000-50800000).
 
 **Supplementary Figure 6.** *preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.
-Enriched heatmaps comparing the enrichment of (A) ARROWHEAD called TAD boundaries vs *preciseTAD* predicted TAD boundaries, and (B) Peakachu loop boundaries vs *preciseTAD* predicted loop boundaries around key GM12878-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
+Enriched heatmaps comparing the enrichment of (A) Arrowhead called TAD boundaries vs *preciseTAD*-predicted TAD boundaries, and (B) Peakachu loop boundaries vs *preciseTAD*-predicted loop boundaries around key GM12878-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
 
 **Supplementary Figure 7.** *preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.
-Enriched heatmaps comparing the enrichment of (A) ARROWHEAD called TAD boundaries vs *preciseTAD* predicted TAD boundaries, and (B) Peakachu loop boundaries vs preciseTAD predicted loop boundaries around key K562-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
+Enriched heatmaps comparing the enrichment of (A) Arrowhead called TAD boundaries vs *preciseTAD*-predicted TAD boundaries, and (B) Peakachu loop boundaries vs preciseTAD predicted loop boundaries around key K562-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
 
@@
 
-**Supplementary Figure 9.** *preciseTAD* predicted TAD boundaries using ARROWHEAD are nested within *preciseTAD* predicted chromatin loop boundaries using PEAKACHU.
-Venn diagrams illustrating the agreement between boundaries predicted using ARROWHEAD- and Peakachu-trained models.
-TAD/loop boundaries were flanked by resolution (5 kb for models using ARROWHEAD and 10 kb for PEAKACHU).
+**Supplementary Figure 9.** *preciseTAD*-predicted TAD boundaries using Arrowhead are nested within *preciseTAD*-predicted chromatin loop boundaries using Peakachu.
+Venn diagrams illustrating the agreement between boundaries predicted using Arrowhead- and Peakachu-trained models.
+Domain boundaries were flanked by resolution (5 kb for models using Arrowhead and 10 kb for Peakachu).
 
-**Supplementary Figure 10.** Linecharts illustrating the normalized overlap between known molecular drivers of 3D chromatin and flanked predicted TAD boundaries identified by *preciseTAD* (using Arrowhead ground truth boundaries) for different combinations of thresholds (t) and epsilon parameter values (eps) on GM12878 and for chromosome 22.
-Normalized overlap was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted (on chr22).
-Boundaries were flanked by 5 kb resolution.
+**Supplementary Figure 10.** Linecharts illustrating the normalized overlap between known molecular drivers of 3D chromatin and resolution-flanked *preciseTAD*-predicted boundaries (trained on Arrowhead boundaries) for different combinations of thresholds (t) and epsilon parameter values (eps).
+Data from GM12878 cell line, chromosome 22, at 5kb resolution was used.
+Normalized overlap was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted.
 
@@
 
-AUC - Area Under the Curve; BA - Balance Accuracy; bp - base pair; BroadHMM - BroadHMM chromatin segmentation states; ChIP-seq - Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI - Class Imbalance; CLARA - Clustering Large Applications; DBSCAN - Density-Based Spatial Clustering of Applications with Noise; FN - False Negatives; FP - False Positives; Hi-C - High-throughput chromosome conformation capture technology; HM - Histone Modifications; kb - kilobase; ML - Machine Learning; OC - Overlap Counts; OP - Overlap Percents; PAM - Partitioning Around Medoids; PTBP - preciseTAD Boundary Point; PTBR - preciseTAD Boundary Region; RF - Random Forest; RFE - Recursive Feature Elimination; ROC - Receiver Operating Characteristic; ROS - Random Over-Sampling; RUS	Random Under-Sampling; SMOTE - Synthetic Minority Over-sampling Technique; TAD - Topologically Associated Domains; TFBS - Transcription Factor Binding Sites; TN - True Negatives; TP - True Positives
+AUC - Area Under the Curve; BA - Balance Accuracy; bp - base pair; BroadHMM - BroadHMM chromatin state data; ChIP-seq - Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI - Class Imbalance; CLARA - Clustering Large Applications; DBSCAN - Density-Based Spatial Clustering of Applications with Noise; FN - False Negatives; FP - False Positives; Hi-C - High-throughput chromosome conformation capture technology; HM - Histone Modifications; kb - kilobase; ML - Machine Learning; OC - Overlap Counts; OP - Overlap Percents; PAM - Partitioning Around Medoids; PTBP - preciseTAD Boundary Point; PTBR - preciseTAD Boundary Region; RF - Random Forest; RFE - Recursive Feature Elimination; ROC - Receiver Operating Characteristic; ROS - Random Over-Sampling; RUS	Random Under-Sampling; SMOTE - Synthetic Minority Over-sampling Technique; TAD - Topologically Associating Domains; TFBS - Transcription Factor Binding Sites; TN - True Negatives; TP - True Positives
 

### 2020-08-26 Manuscript/manuscript.Rmd
completed todo items

@@
 We assessed the biological significance of our predicted boundaries by their association with several known molecular drivers of 3D chromatin architecture, including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
-To do so, we used the *computeMatrix* and *plotHeatmap* tools offered by deepTools (version 2.0) [@ramirez2016deeptools] via integration with Galaxy (version 3.3.2.0.0) [@afgan2018galaxy] [???
-Correct, change to new pipeline].
+To do so, we used the *computeMatrix*, *plotProfile*, and *plotHeatmap* tools offered by deepTools (version 2.0) [@ramirez2016deeptools] <!--via integration with Galaxy (version 3.3.2.0.0) [@afgan2018galaxy]--> [???
+Correct, change to new pipeline; !!!removed galaxy usage].
 Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum tests.
@@
 Boundaries involving Arrowhead were flanked by 5 kb, while boundaries involving Peakachu were flanked by 10 kb.
-We found that 35%/55% of *preciseTAD*-predicted domain boundaries using models trained on Arrowhead/Peakachu data, respectively, were conserved between GM12878 and K562 cell lines.
-This is in contrast to only 26% and 55% for Arrowhead and Peakachu boundaries themselves (Figure 6B).
+We found that 46%/63% of *preciseTAD*-predicted domain boundaries using models trained on Arrowhead/Peakachu data, respectively, were conserved between GM12878 and K562 cell lines.
+This is in contrast to only 26% and 63% for Arrowhead and Peakachu boundaries themselves (Figure 6B).
 The better conservation of *preciseTAD*-predicted boundaries further supports the notion of their higher biological relevance.
@@
 The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model.
-We found that 95.6% and 95.7% of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 9).
+We found that 86.8% and 92.6% of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 9).
 This is expected as loop boundaries (Peakachu) are more abundant, while TAD boundaries (Arrowhead) represent the narrower level of the 3D chromatin organization.
@@
 **Supplementary Figure 9.** *preciseTAD*-predicted TAD boundaries using Arrowhead are nested within *preciseTAD*-predicted chromatin loop boundaries using Peakachu.
-Venn diagrams illustrating the agreement between boundaries predicted using Arrowhead- and Peakachu-trained models.
+Venn diagrams illustrating the agreement between boundaries predicted using Arrowhead- and Peakachu-trained models for (A) GM12878 and (B) K562.
 Domain boundaries were flanked by resolution (5 kb for models using Arrowhead and 10 kb for Peakachu).

### 2020-08-26 Scripts_for_results/05_creating_importance_plot.R

@@ -93,7 +93,7 @@ rfe.set.mat <- as.matrix(rfeperchr[,-1])
 rownames(rfe.set.mat) <- rfeperchr$TFBS
 rfe.set.mat <- t(apply(rfe.set.mat,1,rev))
 
-#rfe.set.mat <- rfe.set.mat[-12,]
+rfe.set.mat <- rfe.set.mat[-12,]
 rownames(rfe.set.mat)[2] <- "Znf143"
 
 distance.col = dist(rfe.set.mat, method = "euclidean")

### 2020-08-26 Scripts_for_results/12_cross_cell_line_performances.R

@@ -1,416 +1,0 @@
-#12_cross_cell_line_performances
-
-library(S4Vectors)
-library(GenomicRanges)
-library(ggplot2)
-library(caret)
-library(randomForest)
-library(glmnet)
-library(gbm)
-library(DMwR)
-library(rtracklayer)
-library(Biostrings)
-library(BSgenome)
-library(cluster)
-library(pROC)
-library(SuperLearner)
-library(data.table)
-library(PRROC)
-library(bigmemory)
-library(ranger)
-library(dplyr)
-library(parallel)
-library(doSNOW)
-library(foreach)
-library(pbapply)
-library(ggpubr)
-library(scales)
-library(GGally)
-library(VennDiagram)
-library(network)
-library(sna)
-library(gtable)
-library(grid)
-library(magrittr) 
-library(DT)
-library(tidyverse)
-library(reshape)
-library(ROSE)
-library(lattice)
-library(corrplot)
-library(cluster)
-library(RColorBrewer)
-library(GenometriCorr)
-library(ggsignif)
-library(Vennerable)
-library(VennDiagram)
-library(ChIPpeakAnno)
-library(EnrichedHeatmap)
-library(ComplexHeatmap)
-library(circlize)
-library(cotools)
-library(ggcorrplot)
-library(circlize)
-library(egg)
-
-source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/createTADdata.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
-source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
-
-
[…]

### 2020-08-26 Scripts_for_results/07_creating_distance_to_chipseq.R
initial commit

@@ -1,0 +1,364 @@
+#07_creating_distance_to_chipseq
+
+library(S4Vectors)
+library(GenomicRanges)
+library(ggplot2)
+library(caret)
+library(randomForest)
+library(glmnet)
+library(gbm)
+library(DMwR)
+library(rtracklayer)
+library(Biostrings)
+library(BSgenome)
+library(cluster)
+library(pROC)
+library(SuperLearner)
+library(data.table)
+library(PRROC)
+library(bigmemory)
+library(ranger)
+library(dplyr)
+library(parallel)
+library(doSNOW)
+library(foreach)
+library(pbapply)
+library(ggpubr)
+library(scales)
+library(GGally)
+library(VennDiagram)
+library(network)
+library(sna)
+library(gtable)
+library(grid)
+library(magrittr) 
+library(DT)
+library(tidyverse)
+library(reshape)
+library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
+library(GenometriCorr)
+library(ggsignif)
+library(Vennerable)
+library(VennDiagram)
+library(ChIPpeakAnno)
+library(EnrichedHeatmap)
+
+source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
+#gm12878 
+
+genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
+                                             pattern="*.bed",
+                                             signal=4)
+
+pred_bound_list <- GRangesList()
+true_bound_list <- GRangesList()
[…]

### 2020-08-26 Scripts_for_results/08_creating_venn_diagrams.R

@@ -1,0 +1,346 @@
+#08_creating_venn_diagrams
+
+library(S4Vectors)
+library(GenomicRanges)
+library(ggplot2)
+library(caret)
+library(randomForest)
+library(glmnet)
+library(gbm)
+library(DMwR)
+library(rtracklayer)
+library(Biostrings)
+library(BSgenome)
+library(cluster)
+library(pROC)
+library(SuperLearner)
+library(data.table)
+library(PRROC)
+library(bigmemory)
+library(ranger)
+library(dplyr)
+library(parallel)
+library(doSNOW)
+library(foreach)
+library(pbapply)
+library(ggpubr)
+library(scales)
+library(GGally)
+library(VennDiagram)
+library(network)
+library(sna)
+library(gtable)
+library(grid)
+library(magrittr) 
+library(DT)
+library(tidyverse)
+library(reshape)
+library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
+library(GenometriCorr)
+library(ggsignif)
+library(Vennerable)
+library(VennDiagram)
+library(ChIPpeakAnno)
+library(EnrichedHeatmap)
+
+source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
+venn_cnt2venn <- function(venn_cnt){
+  n <- which(colnames(venn_cnt)=="Counts") - 1
+  SetNames=colnames(venn_cnt)[1:n]
+  Weight=venn_cnt[,"Counts"]
[…]

### 2020-08-26 Scripts_for_results/15_cross_cell_line_auprc.R

@@ -1,0 +1,489 @@
+source("/home/stilianoudakisc/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("/home/stilianoudakisc/TAD_data_analysis/functions_for_R_package/createTADdata.R")
+source("/home/stilianoudakisc/TAD_data_analysis/functions_for_R_package/TADrandomForest.R")
+source("/home/stilianoudakisc/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("/home/stilianoudakisc/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("/home/stilianoudakisc/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("/home/stilianoudakisc/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("/home/stilianoudakisc/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("/home/stilianoudakisc/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("/home/stilianoudakisc/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("/home/stilianoudakisc/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
+#arrowhead
+
+domains <- read.table("/home/stilianoudakisc/TAD_data_analysis/GSE63525_data/arrowhead_output/GM12878/GM12878_domain_data_5000.b.txt", header=F)
+bounds.GR_gm12878 <- extract_boundaries_func(domains.mat=domains, 
+                                     preprocess=FALSE, 
+                                     CHR=paste0("CHR", c(1:8,10:22)), 
+                                     resolution=5000)
+genomicElements.GR_gm12878 <- annots_to_granges_func(filepath = "/home/stilianoudakisc/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS_nonames",
+                                             pattern="*.bed",
+                                             signal=4)
+
+domains <- read.table("/home/stilianoudakisc/TAD_data_analysis/GSE63525_data/arrowhead_output/K562/K562_domain_data_5000.b.txt", header=F)
+bounds.GR_k562 <- extract_boundaries_func(domains.mat=domains, 
+                                             preprocess=FALSE, 
+                                             CHR=paste0("CHR", c(1:8,10:22)), 
[…]

### 2020-08-26 Manuscript/manuscript.Rmd
Adjust figure location

@@
 
+![**Resolution-specific data construction and feature engineering used for downstream random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals (see Methods).
+The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD boundary.
+(B) Four types of associations between bins and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png)
+
 Boundary regions were defined as genomic bins containing a called boundary ($Y = 1$), while non-boundary regions were defined as bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
@@
 Lastly, we tested *Synthetic minority over-sampling technique* (SMOTE), which is a combination of both random over- and under-sampling to create balanced classes [@chawla2002smote] (see Methods).
-
-A total of 77 cell-line-specific genomic annotations were used to build the predictor space.
-These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 2).
-Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
-These included signal strength association (Signal), direct (OC), proportional (OP), and spatial ($log_2 + 1$ Distance) relationships (see Methods, Supplementary Figure 1).
-
-![**Resolution-specific data construction and feature engineering used for downstream random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals (see Methods).
-The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD boundary.
-(B) Four types of associations between bins and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png)
-
-In total, we considered combinations of data from two cell lines *L = {GM12878, K562}*, five resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor space *P = {Signal, OC, OP, Distance}*, and three re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
-Once the model inputs were established, a random forest classifier was trained on $n-1$ autosomal chromosomes, while reserving the $i^{th}$ chromosome for testing.
-Three-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed to default values of 500 and 1, respectively.
-Model performance was evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (see Methods).
-These strategies allowed us to select the best performing model in an unbiased manner.
-
-![**A diagram of the machine learning framework used to build domain boundary region prediction models.** Step 1 defines the dimensions of the data matrix $A_{N \times (p+1)}$ used for training and testing by establishing a resolution, $r$, at which to bin the linear genome into $N$ genomic bins for each chromosome, except a holdout chromosome *i*.
-The response vector **Y** is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$).
-A feature engineering procedure is selected to define the feature space of $A$ composed of $p$ genomic annotations.
-Step 2 is to reserve the predictor-response matrix for the holdout chromosome *i* as the test data.
-Step 3 is to apply a resampling technique to the training data to address the class imbalance.
-Step 4 is to train the random forest model and perform 3-fold cross-validation to tune for the mtry parameter.
-Finally, step 5 is to validate the model on the separate test data composed of the binned data from the holdout chromosome *i* and to evaluate model performance using balanced accuracy (BA).](Figures/figure2.png)
 
@@
 Class imbalance is calculated as the ratio of total number of unique boundaries to the total number of genomic bins.
+
+![**A machine learning framework for building domain boundary region prediction models.** Step 1 employs a range of feature engineering techniques to define defines the predictor matrix $A_{N \times (p)}$, where $N$ is the number of genomic bins, $p$ is the number of genomic annotations, $i$ is a holdout chromosome.
+The response vector $Y_N$ is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$).
+Step 2 is reserves the predictor-response matrix for the holdout chromosome $i$ as the test data.
+Step 3 applies a resampling technique to the training data to address the class imbalance.
+Step 4 trains the random forest model and performs 3-fold cross-validation to tune the mtry parameter.
+Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and to evaluate model performance using balanced accuracy (BA).](Figures/figure2.png)
+
+A total of 77 cell-line-specific genomic annotations were used to build the predictor space.
+These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 2).
+Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
+These included signal strength association (Signal), direct (OC), proportional (OP), and spatial ($log_2 + 1$ Distance) relationships (see Methods, Supplementary Figure 1).
+
+In total, we considered combinations of data from two cell lines *L = {GM12878, K562}*, five resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor space *P = {Signal, OC, OP, Distance}*, and three re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
+Once the model inputs were established, a random forest classifier was trained on $n-1$ autosomal chromosomes, while reserving the $i^{th}$ chromosome for testing.
+Three-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed to default values of 500 and 1, respectively.
+Model performance was evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (see Methods).
+These strategies allowed us to select the best performing model in an unbiased manner.
 
@@
 
+![**Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+(B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
+Error bars represent 1 standard deviation from the cross-validated accuracy across each holdout chromosome.
+(C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs.
+The columns represent the holdout chromosome excluded from the training data.
+(D) Receiver operating characteristic (ROC) curves and subsequent area under the curves (AUCs) when training and testing on the same cell line versus across cell lines.
+The curves represent the average sensitivities and specificities across each holdout chromosome.](Figures/figure4.png)
+
 ## Predictive importances confirmed the biological role of CTCF, RAD21, SMC3, and ZNF143 for boundary formation
@@
 
-![**Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
-(B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
-Error bars represent 1 standard deviation from the cross-validated accuracy across each holdout chromosome.
-(C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs.
-The columns represent the holdout chromosome excluded from the training data.
-(D) Receiver operating characteristic (ROC) curves and subsequent area under the curves (AUCs) when training and testing on the same cell line versus across cell lines.
-The curves represent the average sensitivities and specificities across each holdout chromosome.](Figures/figure4.png)
-
 ## *preciseTAD* identifies precise and biologically relevant locations of TAD boundaries
@@
 
+![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of Arrowhead-called TAD boundaries (blue) vs.
+*preciseTAD*-predicted TAD boundaries (green) on GM12878 data (chr14:50085000-50800000).
+The black line represents the predicted probability of each base being a TAD boundary.
+(B, C) Profile plots comparing the signal strength of CTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called boundaries (blue, B), Peakachu loop boundaries (red, C) vs.
+*preciseTAD*-predicted boundaries (green).](Figures/figure5.png)
+
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
@@
 These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
-
-![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of Arrowhead-called TAD boundaries (blue) vs.
-*preciseTAD*-predicted TAD boundaries (green) on GM12878 data (chr14:50085000-50800000).
-The black line represents the predicted probability of each base being a TAD boundary.
-(B, C) Profile plots comparing the signal strength of CTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called boundaries (blue, B), Peakachu loop boundaries (red, C) vs.
-*preciseTAD*-predicted boundaries (green).](Figures/figure5.png)
 

### 2020-08-26 Manuscript/manuscript.Rmd
cleanup ???

@@
 We assessed the biological significance of our predicted boundaries by their association with several known molecular drivers of 3D chromatin architecture, including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
-To do so, we used the *computeMatrix*, *plotProfile*, and *plotHeatmap* tools offered by deepTools (version 2.0) [@ramirez2016deeptools] <!--via integration with Galaxy (version 3.3.2.0.0) [@afgan2018galaxy]--> [???
-Correct, change to new pipeline; !!!removed galaxy usage].
+To do so, we used the *computeMatrix*, *plotProfile*, and *plotHeatmap* tools offered by deepTools (version 2.0) [@ramirez2016deeptools].
 Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum tests.
@@
 We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries were maximized for combinations of $t=1.0$ and $eps=r$ (Supplementary Figure 10).
-[???
-We talked about relaxing t threshold, but it requires extensive reruns.
-Where are we on that?]
 

### 2020-08-27 Manuscript/manuscript.Rmd

@@
 (A) Log2 genomic distances from called and predicted boundaries to nearest CTCF sites.
-P-value are from the Wilcoxon Rank Sum test.
-(B) Venn diagrams illustrating the levels of conservation between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead-trained *preciseTAD* model (top left), Arrowhead boundaries themselves (top right), Peakachu-trained *preciseTAD* model (bottom left), and Peakachu boundaries themselves (bottom right).
-J - the median Jaccard Index (IQR in parentheses) across all chromosomes.](Figures/figure6.png)
+The p-value is derived from the Wilcoxon Rank Sum test.
+(B) Venn diagrams illustrating the levels of conservation between TAD/loop boundaries for GM12878 (red) and K562 (blue) identified by preciseTAD (using ARROWHEAD; top left), ARROWHEAD (top right), preciseTAD (using PEAKACHU; bottom left), and PEAKACHU (bottom right).
+The Jaccard Index, evaluating the similarity between each set of boundaries flanked by resolution, is provided below each venn diagram.](Figures/figure6.png)
 

### 2020-08-27 Manuscript/manuscript.Rmd
Revert Figure 6 legend
Fog 6: Jaccard reflects whole genome overlap

--- 2020-08-26 Manuscript/manuscript.Rmd
@@
 (A) Log2 genomic distances from called and predicted boundaries to nearest CTCF sites.
-P-value are from the Wilcoxon Rank Sum test.
+The p-values are from the Wilcoxon Rank Sum test.
 (B) Venn diagrams illustrating the levels of conservation between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead-trained *preciseTAD* model (top left), Arrowhead boundaries themselves (top right), Peakachu-trained *preciseTAD* model (bottom left), and Peakachu boundaries themselves (bottom right).
-J - the median Jaccard Index (IQR in parentheses) across all chromosomes.](Figures/figure6.png)
+J - the Jaccard Index evaluating the similarity between each set of boundaries flanked by resolution.](Figures/figure6.png)
 

### 2020-08-30 Manuscript/manuscript.Rmd
added to supp fig5; editted legend

@@
 
-**Supplementary Figure 5.** Profile plots comparing the signal strength of top TFBS around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green), and (B) around Peakachu loop boundaries (red) and preciseTAD predicted loop boundaries (green) on K562.
+**Supplementary Figure 5.** Profile plots comparing the signal strength of top TFBS around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green), (B) Peakachu chromatin loop boundaries (red) and preciseTAD predicted loop boundaries (green) on K562, (C) Arrowhead called TAD boundaries (blue), Peakachu chromatin loop boundaries (red), and SpectralTAD called TAD boundaries (green) on GM12878 and (D) on K562.
 

### 2020-08-30 Manuscript/manuscript.Rmd
Add new writeup about Supp Fig 5CD

@@
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
-Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, co-localized more frequently around *preciseTAD*-predicted TAD and loop boundaries compared to Arrowhead called TAD and Peakached loop boundaries respectively (Figure 5B-5C; Supplementary Figure 5).
-Furthermore, signal heatmaps indicated that our predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Supplementary Figures 6-7).
+Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, co-localized more frequently around *preciseTAD*-predicted TAD and loop boundaries compared to Arrowhead called TAD and Peakachu loop boundaries respectively (Figure 5B, C; Supplementary Figure 5A, B).
+Surprised by the poor signal distribution at the Arrowhead boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, and our SpectralTAD [@Cresswell:2020ab] TAD caller.
+We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the well-performing Peakachu- and SpectralTAD-called boundaries (Supplementary Figure 5C, D).
+Furthermore, signal heatmaps indicated that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Supplementary Figures 6-7).
 *preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Supplementary Figure 8).

### 2020-08-30 Manuscript/manuscript.Rmd
Polish title and abstract

@@
 ---
-title: "preciseTAD: A machine learning framework for precise TAD boundary prediction at base-level resolution"
+title: "preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution"
 csl: styles.ref/genomebiology.csl
@@
 **Background.** High-throughput chromosome conformation capture technology (Hi-C) revealed extensive DNA looping and folding into discrete 3D domains.
-These include Topologically Associating Domains (TADs) and chromatin loops, 3D domains critical for cellular processes like gene regulation and cell differentiation.
+These include Topologically Associating Domains (TADs) and chromatin loops, the 3D domains critical for cellular processes like gene regulation and cell differentiation.
 The relatively low resolution of Hi-C data (regions of several kilobases in size) prevents precise mapping of domain boundaries.
-However, the high resolution of genomic annotations associated with boundaries, such as CTCF, members of cohesin complex, suggests they can inform the precise location of domain boundaries.
+However, the high resolution of genomic annotations associated with boundaries, such as CTCF and members of cohesin complex, suggests they can inform the precise location of domain boundaries.
 Several methods attempted to leverage genome annotation data for predicting domain boundaries; however, they overlooked key characteristics of the data, such as spatial associations between an annotation and a boundary, and a much smaller number of boundaries than the rest of the genome (class imbalance).
@@
 Boundaries predicted by *preciseTAD* were more enriched for CTCF, RAD21, SMC3, and ZNF143 signal and more conserved across cell lines, highlighting their higher biological significance.
-The model trained in one cell line performs well in predicting boundaries in another cell line.
+The model pre-trained in one cell line performs well in predicting boundaries in another cell line using only genomic annotations, enabling the detection of domain boundaries in cells without Hi-C data.
 
-**Conclusion.** Our study implements the method and outlines strategies for precise domain boundary prediction using genome annotation data.
+**Conclusion.** Our study implements the method and the pre-trained models for precise domain boundary prediction using genome annotation data.
 The precise identification of domain boundaries will improve our understanding of how genomic regulators are shaping the 3D structure of the genome.
 
-**Availability.** *preciseTAD* R package is available on https://github.com/dozmorovlab/preciseTAD and Bioconductor (submitted).
+**Availability.** *preciseTAD* R package is available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor (submitted).
 
@@
 This improved precision in the domain boundary location can provide insight into the association between genomic regulators and the 3D genome organization.
-The *preciseTAD* R package is freely available on GitHub (https://github.com/dozmorovlab/preciseTAD) and on Bioconductor (submitted).
+The *preciseTAD* R package is freely available on GitHub (https://dozmorovlab.github.io/preciseTAD/) and on Bioconductor (submitted).
 

### 2020-08-30 Manuscript/manuscript.Rmd
Final touches before preprint

@@
 We found that spatial associations (linear distance) between boundaries and annotations perform best, transcription factor binding sites further improve prediction accuracy, and a simple random undersampling technique effectively addresses the negative effect of class imbalance.
-Translated from Hi-C data resolution level to base level (annotating each base and predicting its boundary probability), *preciseTAD* employs density-based clustering (DBSCAN) and scalable partitioning around medoids (CLARA) to select genome annotation-guided boundary coordinates.
+Translated from Hi-C data resolution level to base level (annotating each base and predicting its boundary probability), *preciseTAD* employs density-based clustering (DBSCAN) and scalable partitioning around medoids (CLARA) to detect genome annotation-guided boundary regions and points at a base-level resolution.
 This approach circumvents resolution restrictions of Hi-C data, allowing for the precise detection of biologically meaningful boundaries.
@@
 This improved precision in the domain boundary location can provide insight into the association between genomic regulators and the 3D genome organization.
-The *preciseTAD* R package is freely available on GitHub (https://dozmorovlab.github.io/preciseTAD/) and on Bioconductor (submitted).
+The *preciseTAD* R package is freely available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor (submitted).
 
@@
 
-When evaluating performance across cell lines, a random forest model was built using ground truth boundaries and genomic annotations from one cell line such that the data matrix was constructed using genomic bins from $n-1$ chromosomes.
-The test data used to evaluate performance was constructed from the binned data of the $i^{th}$ holdout chromosome with genomic annotations from the other cell line.
-Thus, the models were trained on cell-line-specific data and tested on the other cell line.
+When evaluating performance across cell lines, a random forest model was built using Arrowhead/Peakachu-detected boundaries ("ground truth") and genomic annotations from one cell line such that the data matrix was constructed using genomic bins from $n-1$ chromosomes.
+The test data was constructed from the binned data of the holdout chromosome with genomic annotations from the other cell line.
+The predicted boundaries were evaluated for overlap with the "ground truth" boundaries from the that other cell line.
 This process was repeated for each holdout chromosome.
@@
 
-## Boundary prediction at bp resolution using *preciseTAD*
+## Boundary prediction at the base-level resolution using *preciseTAD*
 
@@
 Here, $n_{i}$ represents the length of chromosome *i*.
-A threshold ($t$) is specified on $p_{n_{i}}$, such that base coordinates with $p_{n_{i}} \ge t$ are extracted.
-Next, density-based spatial clustering of applications with noise (DBSCAN; version 1.1-5) is applied to the matrix of pairwise genomic distances between bases with $p_{n_{i}} \ge t$.
-The resulting clusters of highly predictive bases identified by DBSCAN were termed *preciseTAD boundary regions* (PTBR).
+A threshold $t$ specifies the probability at which a base with $p_{n_{i}} \ge t$ is designated as boundary (the default $t=1$).
+Next, density-based spatial clustering of applications with noise (DBSCAN; version 1.1-5) is applied to the matrix of pairwise genomic distances between boundary-annotated bases.
+The resulting clusters of spatially colocalized bases predicted as being boundaries were termed *preciseTAD boundary regions* (PTBR).
 To precisely identify a single base among each PTBR, *preciseTAD* then implements an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
@@
 
-where A and B represent genomic regions created by flanking called and predicted boundaries.
+where A and B represent genomic regions created by flanked called and predicted boundaries.
 That is, between cell lines, the number of overlapping flanked boundaries divided by the total number of flanked boundaries.
@@
 
-Having demonstrated the optimal performance in our framework's ability to predict boundary regions, we next attempted to predict boundary regions in one cell line when trained on another (See Methods).
+Having demonstrated the optimal performance in our framework's ability to predict boundary regions, we next attempted to predict boundary regions in one cell line using the model pre-trained on data from another another cell line (See Methods).
 We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from GM12878 cell line resulted in an average AUC=0.845 (Figure 4D).
@@
 Likewise, the performance of the model trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable when evaluated using K562-specific Peakachu boundaries and genomic annotations (AUC=0.885 and 0.868, respectively).
-These results were consistent when training on K562 and testing on GM12878 (Supplementary Figure 4D).
-In summary, our observations suggest that a classifier trained on the data from one cell line performs well when using data from another cell line.
+These results were consistent when training on K562 and testing on GM12878 data (Supplementary Figure 4D).
+In summary, our observations suggest that a model trained on data from one cell line performs well when using the data from another cell line.
 
-## *preciseTAD* identifies precise and biologically relevant locations of TAD boundaries
+## *preciseTAD* identifies precise and biologically relevant domain boundaries
 
-Using our optimally built random forest model trained on Arrowhead/Peakachu boundaries, we attempted to predict boundaries at base resolution.
-Intuitively, instead of bin-level annotations, the predictor-response space was built on a base-level, that is, each base was associated with the corresponding genomic annotation.
+Using our optimally built random forest model trained on Arrowhead/Peakachu boundaries, we attempted to predict boundaries at base-level resolution.
+Intuitively, instead of bin-level annotations, the predictor-response space was built on a base-level, that is, each base was associated with a genomic annotation.
 The model trained on a bin-level space was then applied on a base-level space to predict each base's probability of being a boundary.
-Our method, referred to as *preciseTAD*, uses density-based hierarchical clustering (DBSCAN) and a scalable partitioning around medoids clustering (CLARA) to predict the location of boundary regions and summit points (highest boundary probability) at base resolution (see Methods).
+Our method, referred to as *preciseTAD*, uses density-based hierarchical clustering (DBSCAN) and a scalable partitioning around medoids clustering (CLARA) to predict the location of boundary regions and summit points (highest boundary probability) at base-level resolution (see Methods).
 
-When built using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, *preciseTAD* was able to predict a total of 7,846 TAD and 15,838 chromatin loop boundaries on GM12878, as well as 8,883 TAD and 11,016 chromatin loop boundaries on K562 (Supplementary Table 4).
+When trained using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, the *preciseTAD* model predicted a total of 7,846 TAD and 15,838 chromatin loop boundaries in GM12878, as well as 8,883 TAD and 11,016 chromatin loop boundaries in K562 cell line (Supplementary Table 4).
 We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Supplementary Table 3).
-This can be attributed to Arrowhead's inflation of called TADs, especially at higher resolutions, that, when visualized, often do not correspond to intra-chromosomal contacts featured on a contact matrix (Figure 5A).
+This can be attributed to Arrowhead's inflation of called TADs, that, when visualized, often do not correspond to domains enriched in internal interactions (Figure 5A) and signal of known drivers of domain boundaries (Supplementary Figure 5).
 *preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Supplementary Table 3).
@@
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
-Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, co-localized more frequently around *preciseTAD*-predicted TAD and loop boundaries compared to Arrowhead called TAD and Peakachu loop boundaries respectively (Figure 5B, C; Supplementary Figure 5A, B).
+Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, colocalized more frequently around *preciseTAD*-predicted TAD and loop boundaries compared to Arrowhead-called TAD and Peakachu loop boundaries respectively (Figure 5B, C; Supplementary Figure 5A, B).
 Surprised by the poor signal distribution at the Arrowhead boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, and our SpectralTAD [@Cresswell:2020ab] TAD caller.
 We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the well-performing Peakachu- and SpectralTAD-called boundaries (Supplementary Figure 5C, D).
-Furthermore, signal heatmaps indicated that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Supplementary Figures 6-7).
-*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Supplementary Figure 8).
+Signal heatmaps indicated that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Supplementary Figures 6-7).
+*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBSs (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Supplementary Figure 8).
 These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
@@
 
-TAD boundaries are relatively conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @sexton2012three].
+Previous studies suggest that TAD boundaries are conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @sexton2012three].
 To assess the level of cross-cell-line conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, Arrowhead, and Peakachu.
@@
 
-## *preciseTAD*-predicted TAD boundaries are nested within predicted loop boundaries
+## Boundaries predicted by *preciseTAD* models trained on TAD and loop boundaries are highly overlapping
 
@@
 We first optimized our RF model by systematically comparing different combinations of genome binning (resolution), feature engineering procedures, and resampling techniques.
-Our results demonstrate that genomic distance between high-resolution boundary regions and transcription factor binding sites, coupled with random under-sampling results in best model performance.
+Our results demonstrate that genomic distance between boundary regions and genomic annotations coupled with random under-sampling results in best model performance.
 We show that binding of four transcription factors (SMC3, RAD21, CTCF, ZNF143) is sufficient for accurate boundary predictions.
-*preciseTAD* is implemented as an R package, and allows for precise prediction of boundaries for any cell type for which the corresponding genomic annotations are available.
+*preciseTAD* is implemented as an R package, provides the pre-trained models, and allows for precise prediction of boundaries for any cell type for which the genomic annotations are available.
 
@@
 We further demonstrated that class imbalance hinders boundary prediction, but can be effectively addressed by a simple random under-sampling technique, an aspect of boundary prediction unaddressed in previous studies [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa].
-We showed that information about only four transcription factors (SMC3, RAD21, CTCF, ZNF143) is necessary and sufficient for accurate boundary prediction, outperforming histone modification- and BroadHMM-built models [@Moore:2015aa; @Al-Bkhetan:2018aa].
+We showed that information about only four transcription factors (CTCF, SMC3, RAD21, ZNF143) is necessary and sufficient for accurate boundary prediction, outperforming histone modification- and BroadHMM-built models [@Moore:2015aa; @Al-Bkhetan:2018aa].
 These are known components of the loop extrusion model, an established theory of how loops are made by a ring-shaped adenosine triphosphatase-driven complex called cohesin [@hansen2018recent; @sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
@@
 
-A limitation of *preciseTAD* is that it is dependent on "ground truth" boundaries provided by a user-defined domain caller.
-Given the wide variety of domain callers and their variable performance [@Zufferey:2018aa; @forcato2017comparison], it is hard to define "ground truth" boundaries.
+A limitation of *preciseTAD* is that it is dependent on the "ground truth" boundaries provided by a domain caller.
+Given the wide variety of domain callers and their variable performance [@Zufferey:2018aa; @forcato2017comparison], defining "ground truth" boundaries is challenging.
 <!--Ideally, we would benchmark *preciseTAD* against simulated boundaries.
-While methods for simulating Hi-C data sets with boundary annotations exist [@forcato2017comparison; @zheng2020freehi], methods for simulating the associated genomic annotations (the main component guiding *preciseTAD* predictions) are lacking.-->Ultra-deep Hi-C sequencing [@bonev2017multiscale] and newer technologies for precise mapping of chromatin interactions (e.g., Micro-C [@Krietenstein:2020aa]), coupled with more precise technologies for genomic annotation profiling (e.g., CUT&RUN for precise mapping of transcription factor binding sites) will help to refine the location and the genomic signatures of "ground truth" boundaries.
-In the current work, given *preciseTAD* can be trained on the whole-genome data, we feel that the total number of domain boundaries is sufficient to guide learning of the association between genomic annotations and boundaries for precise boundary predictions.
+While methods for simulating Hi-C data sets with boundary annotations exist [@forcato2017comparison; @zheng2020freehi], methods for simulating the associated genomic annotations (the main component guiding *preciseTAD* predictions) are lacking.-->Ultra-deep Hi-C sequencing [@bonev2017multiscale] and newer technologies for precise mapping of chromatin interactions (e.g., Micro-C [@Krietenstein:2020aa]), coupled with more precise technologies for genomic annotation profiling (e.g., CUT&RUN for precise mapping of transcription factor binding sites) will help to refine the location and the genomic signatures of the "ground truth" boundaries.
+In the current work, we feel that the total number of domain boundaries is sufficient to guide learning of the association between genomic annotations and boundaries for precise boundary predictions.
+Indeed, models trained on the larger number of Peakachu-predicted boundaries performed better than those trained on Arrowhead boundaries.
+Although we provide models trained on both boundary types, we recommend Peakachu-trained models for the base-level prediction of domain boundaries.
 
@@
 
-*preciseTAD* requires both cell-type-specific chromatin conformation capture data (Hi-C in the current study) and genome annotation data.
+Using the provided pre-trained models, *preciseTAD* is able to identify precise domain boundaries using cell-type-specific genome annotation information of only four transcription factors, CTCF, SMC3, RAD21, ZNF143.
+Although the ENCODE, NIH Roadmap Epigenomics, FANTOM5, BLUEPRINT, and other members of the International Human Epigenome Consortium (IHEC) [@Stunnenberg:2016aa] have been actively cataloging cell-type-specific genome annotation datasets, these data remain very sparse.
+To date (September 2020), the ENCODE project has only five cell lines (GM12878, K562, H1-hESC, HeLa-S3, HepG2) with all four transcription factor genomic annotations.
+Efforts to <!--systematically catalog chromatin conformation capture data [@Wang:2018ab] and -->impute missing cell-type-specific genome annotation information [@Schreiber:2020aa] started to appear.
+We envision the broader availability of cell-type-specific genomic annotations will enable a more systematic analysis of domain boundaries using *preciseTAD*.
+<!--*preciseTAD* requires both cell-type-specific chromatin conformation capture data (Hi-C in the current study) and genome annotation data.
 Hi-C data provides information about the approximate location of domain boundaries, while genome annotation data is used to train a model that can predict boundaries at the base-level resolution.
-The diversity of chromatin conformation capture technologies [@Kempfer:2019aa] and analysis methods [@Hansen:2019aa] limits the availability of harmonized cell-type-specific domain boundary information.
-Although the ENCODE, NIH Roadmap Epigenomics, FANTOM5, BLUEPRINT, and other members of the International Human Epigenome Consortium (IHEC) [@Stunnenberg:2016aa] have been actively cataloging cell-type-specific genome annotation datasets, these data remain very sparse.
-Efforts to systematically catalog chromatin conformation capture data [@Wang:2018ab] and impute missing cell-type-specific genome annotation information [@Schreiber:2020aa] started to appear.
-We envision the broader availability of matched cell-type-specific omics data will enable a more systematic analysis of domain boundaries using *preciseTAD*.
-Importantly, the *preciseTAD* model trained in one cell type can be used to predict domain boundaries in another cell line using only genome annotation information (CTCF, SMC3, RAD21, ZNF143) from that cell line, thus lowering the data availability requirements.
+The diversity of chromatin conformation capture technologies [@Kempfer:2019aa] and analysis methods [@Hansen:2019aa] limits the availability of harmonized cell-type-specific domain boundary information.-->
 
@@
 Our method can bridge the resolution gap between 1D ChIP-seq annotations and 3D Hi-C sequencing data for more precise and biologically meaningful boundary identification.
-We introduce *preciseTAD*, an open source R package for leveraging random forests to predict domain boundaries at base resolution.
+We introduce *preciseTAD*, an open source R package for leveraging random forests to predict domain boundaries at base-думуд resolution.
 We hope that *preciseTAD* will serve as an efficient and easy-to-use tool to further explore the genome's 3D organization.

### 2020-09-03 Manuscript/manuscript.Rmd
Minor edits
completed todo items

@@
 We found that spatial associations (linear distance) between boundaries and annotations perform best, transcription factor binding sites further improve prediction accuracy, and a simple random undersampling technique effectively addresses the negative effect of class imbalance.
-Translated from Hi-C data resolution level to base level (annotating each base and predicting its boundary probability), *preciseTAD* employs density-based clustering (DBSCAN) and scalable partitioning around medoids (CLARA) to detect genome annotation-guided boundary regions and points at a base-level resolution.
+Translated from Hi-C data resolution level to base level (annotating each base and predicting its boundary probability), *preciseTAD* employs density-based clustering (DBSCAN) and partitioning around medoids (PAM) to detect genome annotation-guided boundary regions and points at a base-level resolution.
 This approach circumvents resolution restrictions of Hi-C data, allowing for the precise detection of biologically meaningful boundaries.
@@
 The resulting clusters of spatially colocalized bases predicted as being boundaries were termed *preciseTAD boundary regions* (PTBR).
-To precisely identify a single base among each PTBR, *preciseTAD* then implements an extension of partitioning around medoids (PAM), known as CLARA (Clustering Large Applications) for better scaling and more computational efficiency [@reynolds2006clustering; @wei2000empirical].
+To precisely identify a single base among each PTBR, *preciseTAD* then implements partitioning around medoids (PAM) on the sub distance matrix derived from each cluster.
 The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative base coordinate within each clustered PTBR.
@@
 The model trained on a bin-level space was then applied on a base-level space to predict each base's probability of being a boundary.
-Our method, referred to as *preciseTAD*, uses density-based hierarchical clustering (DBSCAN) and a scalable partitioning around medoids clustering (CLARA) to predict the location of boundary regions and summit points (highest boundary probability) at base-level resolution (see Methods).
+Our method, referred to as *preciseTAD*, uses density-based spatial clustering (DBSCAN) and partitioning around medoids (PAM) to predict the location of boundary regions and summit points (highest boundary probability) at base-level resolution (see Methods).
 
@@
 Our method can bridge the resolution gap between 1D ChIP-seq annotations and 3D Hi-C sequencing data for more precise and biologically meaningful boundary identification.
-We introduce *preciseTAD*, an open source R package for leveraging random forests to predict domain boundaries at base-думуд resolution.
+We introduce *preciseTAD*, an open source R package for leveraging random forests to predict domain boundaries at base-level resolution.
 We hope that *preciseTAD* will serve as an efficient and easy-to-use tool to further explore the genome's 3D organization.
@@
 
-AUC - Area Under the Curve; BA - Balance Accuracy; bp - base pair; BroadHMM - BroadHMM chromatin state data; ChIP-seq - Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI - Class Imbalance; CLARA - Clustering Large Applications; DBSCAN - Density-Based Spatial Clustering of Applications with Noise; FN - False Negatives; FP - False Positives; Hi-C - High-throughput chromosome conformation capture technology; HM - Histone Modifications; kb - kilobase; ML - Machine Learning; OC - Overlap Counts; OP - Overlap Percents; PAM - Partitioning Around Medoids; PTBP - preciseTAD Boundary Point; PTBR - preciseTAD Boundary Region; RF - Random Forest; RFE - Recursive Feature Elimination; ROC - Receiver Operating Characteristic; ROS - Random Over-Sampling; RUS	Random Under-Sampling; SMOTE - Synthetic Minority Over-sampling Technique; TAD - Topologically Associating Domains; TFBS - Transcription Factor Binding Sites; TN - True Negatives; TP - True Positives
+AUC - Area Under the Curve; BA - Balance Accuracy; bp - base pair; BroadHMM - BroadHMM chromatin state data; ChIP-seq - Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI - Class Imbalance; DBSCAN - Density-Based Spatial Clustering of Applications with Noise; FN - False Negatives; FP - False Positives; Hi-C - High-throughput chromosome conformation capture technology; HM - Histone Modifications; kb - kilobase; ML - Machine Learning; OC - Overlap Counts; OP - Overlap Percents; PAM - Partitioning Around Medoids; PTBP - preciseTAD Boundary Point; PTBR - preciseTAD Boundary Region; RF - Random Forest; RFE - Recursive Feature Elimination; ROC - Receiver Operating Characteristic; ROS - Random Over-Sampling; RUS	Random Under-Sampling; SMOTE - Synthetic Minority Over-sampling Technique; TAD - Topologically Associating Domains; TFBS - Transcription Factor Binding Sites; TN - True Negatives; TP - True Positives
 

### 2020-09-04 Manuscript/manuscript.Rmd
Comment out funding
Suppl table 4 Work in progress
Remove abstract sections

@@
 
-**Background.** High-throughput chromosome conformation capture technology (Hi-C) revealed extensive DNA looping and folding into discrete 3D domains.
+High-throughput chromosome conformation capture technology (Hi-C) revealed extensive DNA looping and folding into discrete 3D domains.
 These include Topologically Associating Domains (TADs) and chromatin loops, the 3D domains critical for cellular processes like gene regulation and cell differentiation.
@@
 
-**Methods.** We developed *preciseTAD*, an optimized random forest model to improve the location of domain boundaries.
+We developed *preciseTAD*, an optimized random forest model to improve the location of domain boundaries.
 Trained on high-resolution genome annotation data and boundaries from low-resolution Hi-C data, the model predicts the location of boundaries at base-level resolution.
@@
 
-**Results.** Spatial relationship (distance in the linear genome) between boundaries and annotations has the most predictive power.
+Spatial relationship (distance in the linear genome) between boundaries and annotations has the most predictive power.
 Transcription factor binding sites outperformed other genome annotation types.
@@
 
-**Conclusion.** Our study implements the method and the pre-trained models for precise domain boundary prediction using genome annotation data.
+Our study implements the method and the pre-trained models for precise domain boundary prediction using genome annotation data.
 The precise identification of domain boundaries will improve our understanding of how genomic regulators are shaping the 3D structure of the genome.
-
-**Availability.** *preciseTAD* R package is available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor (submitted).
+*preciseTAD* R package is available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor (submitted).
 
@@
 All coordinates are in hg19/GRCh37 reference genome.
+(Work in progress)
 
@@
 
-# Funding
+<!-- # Funding -->
 

### 2020-09-04 Manuscript/manuscript.Rmd
More tweaks

@@
 Density-based clustering and scalable partitioning techniques were used to identify the precise location of boundary regions and summit points.
-We benchmarked our method against the Arrowhead domain caller and a novel chromatin loop prediction algorithm, Peakachu, on two most annotated cell lines.
+We benchmarked our method against the Arrowhead domain caller and a novel chromatin loop prediction algorithm, Peakachu, on the two most annotated cell lines.
 
-Spatial relationship (distance in the linear genome) between boundaries and annotations has the most predictive power.
+We found that spatial relationship (distance in the linear genome) between boundaries and annotations has the most predictive power.
 Transcription factor binding sites outperformed other genome annotation types.

### 2020-09-09 Manuscript/manuscript.Rmd
Add [@schreiber2019pitfall] ref

@@
 Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, feature engineering procedures, and resampling techniques.
-A *holdout chromosome* technique was used for model evaluation on each autosomal chromosome.
+Following recommendations to evaluate the model on unseen data [@schreiber2019pitfall], a *holdout chromosome* technique was used for estimating model's performance.
 The $i^{th}$ holdout chromosome was identified and a data matrix, $A_{N \times (p+1)}$, was constructed by combining the binned genome from the remaining chromosomes ($1,2,\cdots, i-1,i+1,\cdots,21,22$), where $N=[n_{1} n_{2} \cdots n_{21} n_{22}]'$ and $n_{k}$ is the length of chromosome *k* after being binned into non-overlapping regions of resolution *r*, such that $k \ne i$.
@@
 
-When evaluating performance across cell lines, a random forest model was built using Arrowhead/Peakachu-detected boundaries ("ground truth") and genomic annotations from one cell line such that the data matrix was constructed using genomic bins from $n-1$ chromosomes.
+When evaluating performance across cell lines, we followed the same strategy of evaluating a model trained in one cell line on unseen data from another cell line [@schreiber2019pitfall].
+A random forest model was built using Arrowhead/Peakachu-detected boundaries ("ground truth") and genomic annotations from one cell line such that the data matrix was constructed using genomic bins from $n-1$ chromosomes.
 The test data was constructed from the binned data of the holdout chromosome with genomic annotations from the other cell line.

### 2020-09-09 Manuscript/manuscript.Rmd
Discuss PTBR width, add refs

@@
 Guided by both low-resolution Hi-C data and high-resolution genome annotation data, *preciseTAD* predicts base-level resolution boundaries, alleviating resolution limitations of Hi-C data.
+However, a natural question is how resolution (width) of boundary regions identified by *preciseTAD* (PTBRs) compares with that of Hi-C data.
+Our preliminary observations indicate that, under most optimal settings, the width of PTBRs parallels the resolution of Hi-C data.
+Furthermore, each PTBR is formed by several sub-regions with the probability of being a boundary defined by the threshold $t$ ($t=1$ in the current study).
+Our results are in line with the emergent view that domain boundaries are dynamic [@chang2020tads] and arise as a consequence of the population average in bulk Hi-C data [@fudenberg2016formation; @Flyamer:2017aa].
+
 We show that, unlike Arrowhead, *preciseTAD* does not inflate the number of predicted boundaries, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
-*preciseTAD* boundaries were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops may be generated by similar mechanisms [@hansen2018recent].
+*preciseTAD* boundaries predicted using models trained on either TAD or loop boundaries (Arrowhead and Peakachu data) were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops may be generated by similar mechanisms [@hansen2018recent].
 Likewise, *preciseTAD* boundaries were more conserved between GM12878 and K562 cell lines, a known feature among the 3D architecture of the human genome, further highlighting their biological significance.

### 2020-09-11 Scripts_for_results/13_saving_boundary_data_for_deeptools.Rmd
addressed todo items

@@
 
-  pred_bound_list[[i]] <- called_and_pred[[2]]
-  true_bound_list[[i]] <- called_and_pred[[3]]
+  pred_bound_list[[i]] <- called_and_pred$PTBP
+  true_bound_list[[i]] <- called_and_pred$CTBP
 
@@
 length(all_true_bounds) #15468
-length(all_pred_bounds) #7846
+length(all_pred_bounds) #12258
 
@@
 length(all_true_bounds) #9316
-length(all_pred_bounds) #8883
+length(all_pred_bounds) #9603
 
@@
 length(all_true_bounds) #21421
-length(all_pred_bounds) #15838
+length(all_pred_bounds) #15707
 
@@
 for(i in 1:length(chrs)){
-  print(i)
   called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
@@
 length(all_true_bounds) #20773
-length(all_pred_bounds) #10379
+length(all_pred_bounds) #10516
 

### 2020-09-11 Scripts_for_results/05_creating_importance_plot.R

@@ -106,8 +106,8 @@ Heatmap(t(rfe.set.mat),
         clustering_distance_columns = "euclidean",
         clustering_method_columns = "ward.D",
         show_row_names = FALSE,
-        heatmap_width = unit(6, "in"),
-        heatmap_height = unit(2.5, "in"),
+        #heatmap_width = unit(6, "in"),
+        #heatmap_height = unit(2.5, "in"),
         #show_column_names = FALSE,
         #show_column_dend = FALSE,
         #column_names_gp=gpar(fontsize = 20),
@@ -160,8 +160,8 @@ Heatmap(t(rfe.set.mat),
         clustering_distance_columns = "euclidean",
         clustering_method_columns = "ward.D",
         show_row_names = FALSE,
-        heatmap_width = unit(6, "in"),
-        heatmap_height = unit(2.5, "in"),
+        #heatmap_width = unit(6, "in"),
+        #heatmap_height = unit(2.5, "in"),
         #show_column_names = FALSE,
         #show_column_dend = FALSE,
         #column_names_gp=gpar(fontsize = 20),

### 2020-09-11 Scripts_for_results/07_creating_distance_to_chipseq.R

@@ -72,8 +72,8 @@ for(i in 1:length(chrs)){
                                     chrs[i],
                                     "/rus/distance/preciseTAD_holdout.rds"))
   
-  true_bound_list[[i]] <- called_and_pred[[3]]
-  pred_bound_list[[i]] <- called_and_pred[[2]]
+  true_bound_list[[i]] <- called_and_pred$CTBP
+  pred_bound_list[[i]] <- called_and_pred$PTBP
   
 }
 
@@ -127,8 +127,8 @@ for(i in 1:length(chrs)){
                                     chrs[i],
                                     "/rus/distance/preciseTAD_holdout_peakachu.rds"))
   
-  true_bound_list[[i]] <- called_and_pred[[3]]
-  pred_bound_list[[i]] <- called_and_pred[[2]]
+  true_bound_list[[i]] <- called_and_pred$CTBP
+  pred_bound_list[[i]] <- called_and_pred$PTBP
   
 }
 
@@ -262,8 +262,8 @@ for(i in 1:length(chrs)){
                                     chrs[i],
                                     "/rus/distance/preciseTAD_holdout.rds"))
   
-  true_bound_list[[i]] <- called_and_pred[[3]]
-  pred_bound_list[[i]] <- called_and_pred[[2]]
+  true_bound_list[[i]] <- called_and_pred$CTBP
+  pred_bound_list[[i]] <- called_and_pred$PTBP
   
 }
 
@@ -317,8 +317,8 @@ for(i in 1:length(chrs)){
                                     chrs[i],
                                     "/rus/distance/preciseTAD_holdout_peakachu.rds"))
   
-  true_bound_list[[i]] <- called_and_pred[[3]]
-  pred_bound_list[[i]] <- called_and_pred[[2]]
+  true_bound_list[[i]] <- called_and_pred$CTBP
+  pred_bound_list[[i]] <- called_and_pred$PTBP
   
 }
 
@@ -362,3 +362,76 @@ BoundReg = c(#preciseTAD
 
 pred_v_called_df_p$BoundReg <- factor(pred_v_called_df_p$BoundReg, levels=c("Peakachu", "preciseTAD"))
 
+######################
+
+#plotting
+
+a <- ggplot(pred_v_called_df_a[which(pred_v_called_df_a$Annotation=="CTCF"),], aes(x=BoundReg, y = LogDist, fill=BoundReg))  +   
[…]

### 2020-09-11 Scripts_for_results/08_creating_venn_diagrams.R

@@ -92,8 +92,8 @@ for(i in 1:length(chrs)){
                                     chrs[i],
                                     "/rus/distance/preciseTAD_holdout.rds"))
   
-  true_bound_list[[i]] <- called_and_pred[[3]]
-  pred_bound_list[[i]] <- called_and_pred[[2]]
+  true_bound_list[[i]] <- called_and_pred$CTBP
+  pred_bound_list[[i]] <- called_and_pred$PTBP
   
 }
 
@@ -110,8 +110,8 @@ for(i in 1:length(chrs)){
                                     chrs[i],
                                     "/rus/distance/preciseTAD_holdout.rds"))
   
-  true_bound_list[[i]] <- called_and_pred[[3]]
-  pred_bound_list[[i]] <- called_and_pred[[2]]
+  true_bound_list[[i]] <- called_and_pred$CTBP
+  pred_bound_list[[i]] <- called_and_pred$PTBP
 }
 
 all_true_bounds_k562 <- do.call("c", true_bound_list)
@@ -132,8 +132,8 @@ gp[["Face"]][["10"]]$fill <-  "red"
 gp[["FaceText"]][["10"]]$cex <- 2
 gp[["FaceText"]][["11"]]$cex <- 2
 gp[["FaceText"]][["01"]]$cex <- 2
-gp[["SetText"]][["Set1"]]$cex <- .1
-gp[["SetText"]][["Set2"]]$cex <- .1
+gp[["SetText"]][["Set1"]]$cex <- .01
+gp[["SetText"]][["Set2"]]$cex <- .01
 
 gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
 
@@ -152,8 +152,8 @@ gp[["Face"]][["10"]]$fill <-  "red"
 gp[["FaceText"]][["10"]]$cex <- 2
 gp[["FaceText"]][["11"]]$cex <- 2
 gp[["FaceText"]][["01"]]$cex <- 2
-gp[["SetText"]][["Set1"]]$cex <- .1
-gp[["SetText"]][["Set2"]]$cex <- .1
+gp[["SetText"]][["Set1"]]$cex <- .01
+gp[["SetText"]][["Set2"]]$cex <- .01
 
[…]

### 2020-09-11 Scripts_for_results/09_visualizing_example_of_preciseTAD.R

@@ -112,7 +112,7 @@ pt <- preciseTAD(bounds.GR=bounds.GR,
                  splits=NULL,
                  method.Dist="euclidean",
                  DBSCAN=TRUE,
-                 DBSCAN_params=list(5000,3),
+                 DBSCAN_params=list(10000,3),
                  method.Clust=NULL,
                  PTBR=TRUE,
                  CLARA=TRUE,
@@ -183,9 +183,9 @@ predprobdata <- data.frame(#basenum=c(17389000:18011000),
   basenum=c(50085000:50800000),
   prob=predictions)
 
-predprobdata$predicted <- ifelse(predprobdata$basenum %in% c(50101115,50343720,50571497,50787832), "Yes", "No")
+predprobdata$predicted <- ifelse(predprobdata$basenum %in% start(pt$PTBP), "Yes", "No")
 
-predprobdata$called <- ifelse(predprobdata$basenum %in% start(pt[[3]]), "Yes", "No")
+predprobdata$called <- ifelse(predprobdata$basenum %in% start(pt$CTBP), "Yes", "No")
 
 calleddata <- predprobdata[which(predprobdata$called=="Yes"),]
 
@@ -193,28 +193,39 @@ predicteddata <- predprobdata[which(predprobdata$prob>=1.0),]
 
 predicteddata2 <- predprobdata[which(predprobdata$predicted=="Yes"),]
 
+ptbrdf <- data.frame(x=c(1,2),y=c(50315887,50334548))
+
 ggplot() + 
+  #probabilities
   geom_line(data=predprobdata, aes(x=basenum, y=prob), 
             color='black',
             size=1)+
+  #ctbp
   geom_vline(data=calleddata, aes(xintercept=basenum, 
                                   color="blue"),
              size=1.5,
              show.legend = TRUE)+
+  #ptbp
   geom_vline(data=predicteddata2, aes(xintercept=basenum, 
                                       color="forestgreen"),
              size=1.5,
              show.legend = TRUE)+
+  #ptbr
+  geom_vline(data=ptbrdf, aes(xintercept=y, 
+                                      color="yellow"),
+             size=1,
+             show.legend = TRUE)+
   xlab("Base Coordinate (mb)") +
   ylab("") +
   scale_color_manual(name = '', 
-                     values =c("blue", "forestgreen"),
+                     values =c("blue", "forestgreen", "yellow"),
                      labels = c("ARROWHEAD",
-                                "preciseTAD"))+
[…]

### 2020-09-11 Manuscript/manuscript.Rmd

@@
 Furthermore, each PTBR is formed by several sub-regions with the probability of being a boundary defined by the threshold $t$ ($t=1$ in the current study).
-Our results are in line with the emergent view that domain boundaries are dynamic [@chang2020tads] and arise as a consequence of the population average in bulk Hi-C data [@fudenberg2016formation; @Flyamer:2017aa].
+Yet, the preciseTAD boundary points (PTBSs, medoids identified within each PTBR) had the highest density of CTCF and other transcription factor binding signal (Figure 5).
+Our results are in line with the emergent view that domain boundaries are dynamic [@chang2020tads] and their well-defined location arise as a consequence of the population average in bulk Hi-C data [@fudenberg2016formation; @Flyamer:2017aa].
 

### 2020-09-11 Scripts_for_results/16_psuedocode.Rmd
initial commit

---
title: "psuedocode"
author: "Spiro Stilianoudakis"
date: "9/6/2020"
output: pdf_document
header-includes:
- \usepackage{stackengine}
- \usepackage{amsmath}
- \usepackage{algorithm2e}
- \usepackage[noend]{algpseudocode}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# preciseTAD (CV)

\begin{algorithm}[H]
\DontPrintSemicolon
\SetAlgoLined
1. Consider an optimized RF model (M) built on the set of autosomal chromosomes $\{ k |i \notin k \}$ binned at some resolution $r$
\BlankLine
2. \For{each chr $i$ do}{
\BlankLine
3.    Construct the base-level resolution predictor space $A_{n \times p}$ where $n$ is the length of chr $i$ and $p$ is the number of predictors\;
\BlankLine
4.    Assign threshold $\{t | 0 \le t \le 1 \}$ and $\{\epsilon | \epsilon > 0 \}$\;
\BlankLine
5.    \eIf{$|t| > 1$ or $|\epsilon| > 1$}{
\BlankLine
6.          Assign grid $(g)$ of combinations of $t$ and $\epsilon$ \;
\BlankLine
7.               \For{each combination $l$ in g}{
\BlankLine
8.                  Evaluate M on $A_{n \times p}$ to get the probability of each genomic coordinate as being a domain boundary $\pi_{n}$\;
\BlankLine
9.                  Subset $\{\pi_{n} | \pi_{n} \ge t_{l} \}$\;
\BlankLine
10.                 Construct the pairwise distance matrix $D$ between genomic coordinates where $\pi_{n} \ge t_{l}$\;
\BlankLine
11.                 Apply DBSCAN on $D$ with $MinPts=3$ and $\epsilon=\epsilon_{l}$\;
\BlankLine
12.                 \For{each cluster $k$ identified by DBSCAN}{
\BlankLine
13.                     Assign $w_{k}$ as the number of coordinates that span each cluster of bases in $k$ (PTBR)\;
\BlankLine
14.                     Perform PAM on the sub-distance matrix $D_{k}$ to extract the cluster medoid $b_{k}$ (PTBP)\;
\BlankLine
15.                     \For{each predictor p}{
\BlankLine
16.                         Calculate the normalized enrichment (NE) over all predictors
                            $$NE = \dfrac{1}{p} \left[ \Sigma_{s=1}^{p} \left[ \dfrac{1}{b} \Sigma_{k=1}^{b} e_{ks} \times c_{k} \right] \right]$$
                            where $e_{ks} = \textbf{I}\{ r_{s} \in (b_{k}-f, b_{k}+f)\}$ is the number of elemental regions $r$ of predictor $p$ that overlap with each flanked boundary and $c_{k} = \dfrac{ \textbf{I}\{ \pi_{n} \ge t_{l} \in w_{k} \} }{w_{k}}$ is the coverage probability of each PTBR\;
\BlankLine
17.                         Determine where $NE$ converges as optimal $\{t,\epsilon\}$ combination\;
\BlankLine
18.                         Repeat steps 12-18 on $A_{nxp}$ with optimal $\{t,\epsilon\}$\;
\BlankLine
                     }
\BlankLine
                 }
\BlankLine
              }
\BlankLine
   }{
\BlankLine
19.  Perform steps 12-18 on $A_{nxp}$ such that $t=t_{0}$ and $\epsilon=\epsilon_{0}$\;
\BlankLine
   }
\BlankLine
}
\caption{Psuedocode for $preciseTAD$ implementation.}
\end{algorithm}

### 2020-09-11 Scripts_for_results/02_creating_lineplot_of_balanced_accuracy.R

@@ -1,0 +1,660 @@
+#02_creating_lineplot_of_balanced_accuracy
+
+library(S4Vectors)
+library(GenomicRanges)
+library(ggplot2)
+library(caret)
+library(randomForest)
+library(glmnet)
+library(gbm)
+library(DMwR)
+library(rtracklayer)
+library(Biostrings)
+library(BSgenome)
+library(cluster)
+library(pROC)
+library(SuperLearner)
+library(data.table)
+library(PRROC)
+library(bigmemory)
+library(ranger)
+library(dplyr)
+library(parallel)
+library(doSNOW)
+library(foreach)
+library(pbapply)
+library(ggpubr)
+library(scales)
+library(GGally)
+library(VennDiagram)
+library(network)
+library(sna)
+library(gtable)
+library(grid)
+library(magrittr) 
+library(DT)
+library(tidyverse)
+library(reshape)
+library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
+library(GenometriCorr)
+library(ggsignif)
+library(Vennerable)
+library(VennDiagram)
+library(ChIPpeakAnno)
+library(EnrichedHeatmap)
+
+source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
+## GM12878
+
+### ARROWHEAD
+
+####5kb
+
+badata_gm12878_5kb <- numeric()
+for(i in paste0("CHR", c(1:2))){
+  for(j in c("none","ros","rus","smote")){
+    for(k in c("distance", "oc", "op", "signal")){
+      print(c(i,j,k))
[…]

### 2020-09-11 Scripts_for_results/12_cross_cell_line_performances.R

@@ -1,0 +1,1175 @@
+#12_cross_cell_line_performances
+
+library(S4Vectors)
+library(GenomicRanges)
+library(ggplot2)
+library(caret)
+library(randomForest)
+library(glmnet)
+library(gbm)
+library(DMwR)
+library(rtracklayer)
+library(Biostrings)
+library(BSgenome)
+library(cluster)
+library(pROC)
+library(SuperLearner)
+library(data.table)
+library(PRROC)
+library(bigmemory)
+library(ranger)
+library(dplyr)
+library(parallel)
+library(doSNOW)
+library(foreach)
+library(pbapply)
+library(ggpubr)
+library(scales)
+library(GGally)
+library(VennDiagram)
+library(network)
+library(sna)
+library(gtable)
+library(grid)
+library(magrittr) 
+library(DT)
+library(tidyverse)
+library(reshape)
+library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
+library(GenometriCorr)
+library(ggsignif)
+library(Vennerable)
+library(VennDiagram)
+library(ChIPpeakAnno)
+library(EnrichedHeatmap)
+library(ComplexHeatmap)
+library(circlize)
+library(cotools)
+library(ggcorrplot)
+library(circlize)
+library(egg)
+
+source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/createTADdata.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
[…]

### 2020-09-11 Scripts_for_results/17_location_of_ptbp_in_ptbr.R

@@ -1,0 +1,171 @@
+#17_location_of_ptbp_in_ptbr
+
+library(S4Vectors)
+library(GenomicRanges)
+library(ggplot2)
+library(caret)
+library(randomForest)
+library(glmnet)
+library(gbm)
+library(DMwR)
+library(rtracklayer)
+library(Biostrings)
+library(BSgenome)
+library(cluster)
+library(pROC)
+library(SuperLearner)
+library(data.table)
+library(PRROC)
+library(bigmemory)
+library(ranger)
+library(dplyr)
+library(parallel)
+library(doSNOW)
+library(foreach)
+library(pbapply)
+library(ggpubr)
+library(scales)
+library(GGally)
+library(VennDiagram)
+library(network)
+library(sna)
+library(gtable)
+library(grid)
+library(magrittr) 
+library(DT)
+library(tidyverse)
+library(reshape)
+library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
+library(GenometriCorr)
+library(ggsignif)
+library(Vennerable)
+library(VennDiagram)
+library(ChIPpeakAnno)
+library(EnrichedHeatmap)
+
+source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
+#arrowhead
+
+##gm12878
+
+ptbp_location <- list()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  print(chrs[i])
[…]

### 2020-09-11 Scripts_for_results/18_saving_ptbrs_ptbps.R

@@ -1,0 +1,221 @@
+#18_saving_ptbrs_ptbps
+
+library(S4Vectors)
+library(GenomicRanges)
+library(ggplot2)
+library(caret)
+library(randomForest)
+library(glmnet)
+library(gbm)
+library(DMwR)
+library(rtracklayer)
+library(Biostrings)
+library(BSgenome)
+library(cluster)
+library(pROC)
+library(SuperLearner)
+library(data.table)
+library(PRROC)
+library(bigmemory)
+library(ranger)
+library(dplyr)
+library(parallel)
+library(doSNOW)
+library(foreach)
+library(pbapply)
+library(ggpubr)
+library(scales)
+library(GGally)
+library(VennDiagram)
+library(network)
+library(sna)
+library(gtable)
+library(grid)
+library(magrittr) 
+library(DT)
+library(tidyverse)
+library(reshape)
+library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
+library(GenometriCorr)
+library(ggsignif)
+library(Vennerable)
+library(VennDiagram)
+library(ChIPpeakAnno)
+library(EnrichedHeatmap)
+
+source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
+OUT <- createWorkbook()
+
+#arrowhead
+
+##gm12878
+
+###ptbr
+
+ptbr <- GRangesList()
+chrs <- paste0("CHR", c(1:8,10:22))
+for(i in 1:length(chrs)){
+  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
[…]

### 2020-09-11 Scripts_for_results/19_creating_table_of_model_performances.R

@@ -1,0 +1,267 @@
+#19_creating_table_of_model_performances
+
+library(S4Vectors)
+library(GenomicRanges)
+library(ggplot2)
+library(caret)
+library(randomForest)
+library(glmnet)
+library(gbm)
+library(DMwR)
+library(rtracklayer)
+library(Biostrings)
+library(BSgenome)
+library(cluster)
+library(pROC)
+library(SuperLearner)
+library(data.table)
+library(PRROC)
+library(bigmemory)
+library(ranger)
+library(dplyr)
+library(parallel)
+library(doSNOW)
+library(foreach)
+library(pbapply)
+library(ggpubr)
+library(scales)
+library(GGally)
+library(VennDiagram)
+library(network)
+library(sna)
+library(gtable)
+library(grid)
+library(magrittr) 
+library(DT)
+library(tidyverse)
+library(reshape)
+library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
+library(GenometriCorr)
+library(ggsignif)
+library(Vennerable)
+library(VennDiagram)
+library(ChIPpeakAnno)
+library(EnrichedHeatmap)
+
+source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
+#Metric  Performance
+#1                TN 3.291200e+04
+#2                FN 2.260000e+02
+#3                FP 1.474300e+04
+#4                TP 1.369000e+03
+#5             Total 4.925000e+04
+#6       Sensitivity 8.583072e-01
+#7       Specificity 6.906306e-01
+#8             Kappa 1.016840e-01
+#9          Accuracy 6.960609e-01
[…]

### 2020-09-16 Manuscript/manuscript.Rmd
edits to manuscript; updated figures and  legends

@@
 We found that spatial relationship (distance in the linear genome) between boundaries and annotations has the most predictive power.
+Random under-sampling significantly improved model performance.
 Transcription factor binding sites outperformed other genome annotation types.
-Random under-sampling significantly improved model performance.
 Boundaries predicted by *preciseTAD* were more enriched for CTCF, RAD21, SMC3, and ZNF143 signal and more conserved across cell lines, highlighting their higher biological significance.
@@
 Resolution refers to the size of genomic regions (bins) used to segment the linear genome [@li2019comparison].
-Lower resolution contribute to larger bin size, which leads to increased uncertainty in the location of boundaries.
+Lower resolutions contribute to larger bin sizes, which leads to increased uncertainty in the location of boundaries.
 Due to high sequencing costs, most available Hi-C datasets have relatively low resolution, ranging from 25 kb to 100 kb.
@@
 We present *preciseTAD*, an optimally tuned machine learning framework for precise identification of domain boundaries using genome annotation data.
-Our method utilizes the random forest (RF) algorithm trained on high-resolution chromatin state data (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) data to predict low-resolution boundaries.
+Our method utilizes the random forest (RF) algorithm trained on high-resolution chromatin state (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) data to predict low-resolution boundaries.
 We introduce a systematic pipeline for building the optimal boundary prediction classifier.
@@
 Publicly available TAD and loop boundaries called by Arrowhead [@durand2016juicebox] and Peakachu [@salameh2019supervised] tools, respectively, were used for training.
-Arrowhead TAD boundaries were called from primary Hi-C data for the GM12878 and K562 cell lines [@rao20143d].
-The contact matrices were constructed from all read pairs that uniquely aligned to the genome (MAPQ>0).
-The default parameters for Arrowhead were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1).
+TAD boundaries were called from primary Hi-C data for the GM12878 and K562 cell lines using Arrowhead, a TAD-caller a part of the juicer suite of tools (version 7.5) [@durand2016juicer; @rao20143d].
+The contact matrices were constructed from all read pairs that uniquely aligned to the genome (MAPQ>0) (Additional File 1).
+The default parameters for Arrowhead were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions.
 Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab website (Supplementary Table 1).
@@
 
-Cell-line-specific genomic annotations were used to build the predictor space.
-Bins were annotated by one of either the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), the average signal strength of the corresponding annotation (*Peak Signal Strength*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*) (Figure 1B).
+Cell line-specific genomic annotations were used to build the predictor space.
+Bins were annotated by one of either the average signal strength of the corresponding annotation (*Peak Signal Strength*), the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*) (Figure 1B).
 A ($log_2 + 1$)-transformation of distance was used to account for the skewness of the distance distributions.
-Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin states lack signal values.
+Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin states lack signal values (Supplementary Figure 1).
 
@@
 The $i^{th}$ holdout chromosome was identified and a data matrix, $A_{N \times (p+1)}$, was constructed by combining the binned genome from the remaining chromosomes ($1,2,\cdots, i-1,i+1,\cdots,21,22$), where $N=[n_{1} n_{2} \cdots n_{21} n_{22}]'$ and $n_{k}$ is the length of chromosome *k* after being binned into non-overlapping regions of resolution *r*, such that $k \ne i$.
-$p$, the number of annotations, together with the response vector **Y**, defined the column-wise dimension of the matrix $A$.
+$p$, the number of annotations, together with the response vector, **Y**, defined the column-wise dimension of the matrix $A$.
 Re-sampling was then performed on $A$, and an RF classifier was trained using 3-fold cross-validation to tune for the number of annotations to consider at each node (*mtry*).
 The number of trees (*ntree*) that were aggregated for each RF model was set to 500.
-The minimum number of observations per root node (*nodesize*) was set to .01% of the rows in the data.
+The minimum number of observations per root node (*nodesize*) was set to .1% of the rows in the data.
 The binned data for the holdout chromosome $i$ was reserved for testing.
@@
 The best performing subset was identified, ranging from 2 to the maximum number of features incremented by the power of 2.
-We then aggregated the predictive importance of the union of the optimal set of features across chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top-ranked annotations for predicting boundary regions.
+We then aggregated the predictive importance of the union of the optimal set of features across holdout chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top-ranked annotations for predicting boundary regions.
 
@@
 The test data was constructed from the binned data of the holdout chromosome with genomic annotations from the other cell line.
-The predicted boundaries were evaluated for overlap with the "ground truth" boundaries from the that other cell line.
+The predicted boundaries were evaluated for overlap with the "ground truth" boundaries from the other cell line.
 This process was repeated for each holdout chromosome.
-To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivities and specificities and reported the area under the curve (AUC).
+To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivities and specificities at different cutoffs, across each holdout chromosome, and reported the corresponding average area under the curve (AUC).
 
@@
 To investigate whether we could alleviate the resolution limitations of conventional domain calling tools, we developed *preciseTAD*.
-This algorithm leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution.
-A random forest model was built on the optimal combination of predictor type (predictor space), resampling technique (class balancing correction), and top-ranked annotations (most informative genomic elements) to maximally accurately predict boundaries at the _Hi-C resolution level_.
+This algorithm leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution (Supplementary Figure 2).
 
-To precisely identify boundary locations, we first constructed a _base-level resolution_ predictor space for a particular chromosome *i*.
-We then apply our optimally trained RF model on the base-level predictor space to extract the probability vector, $p_{n_{i}}$, denoting each base's probability of being a boundary.
+A random forest model $(M)$ was built on the optimal combination of predictor type (predictor space), resampling technique (class balancing correction), and top-ranked annotations (most informative genomic elements) for a set of binned chromosomes $\{k | k \ne i \}$ <!--, to maximally accurately predict boundaries at the _Hi-C resolution level_-->.
+To precisely identify boundary locations, we first constructed a _base-level resolution_ predictor space for the chromosome *i*, $A_{n \times p}$, where $n$ is the length of chromosome $i$ and $p$ is the optimal number of annotations.
+We then evaluate $M$ on the base-level predictor space to extract the probability vector, $\pi_{n_{i}}$, denoting each base's probability of being a boundary.
 Here, $n_{i}$ represents the length of chromosome *i*.
-A threshold $t$ specifies the probability at which a base with $p_{n_{i}} \ge t$ is designated as boundary (the default $t=1$).
-Next, density-based spatial clustering of applications with noise (DBSCAN; version 1.1-5) is applied to the matrix of pairwise genomic distances between boundary-annotated bases.
-The resulting clusters of spatially colocalized bases predicted as being boundaries were termed *preciseTAD boundary regions* (PTBR).
-To precisely identify a single base among each PTBR, *preciseTAD* then implements partitioning around medoids (PAM) on the sub distance matrix derived from each cluster.
+A threshold $t$ specifies the probability at which a base with $\pi_{n_{i}} \ge t$ is designated as a potential boundary (the default $t=1$).
+Next, density-based spatial clustering of applications with noise (DBSCAN; version 1.1-5) is applied to the matrix of pairwise genomic distances between boundary-annotated bases, $D$.
+The minimum and maximum coordinates of each cluster, $k$, of spatially colocalized bases were termed *preciseTAD boundary regions* (PTBR).
+To precisely identify a single base among each PTBR, *preciseTAD* then implements partitioning around medoids (PAM) on the sub distance matrix,$D_{k}$, derived from each cluster.
 The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative base coordinate within each clustered PTBR.
@@
 The *MinPts* parameter was set to the recommended value of 3, representing $1+dim(data)$ [@hahsler2019dbscan].
-To decide on the optimal value of $t$ and $\epsilon$ in *preciseTAD*, we considered the normalized enrichment $N_{e}$ of flanked predicted boundaries, defined as
+To decide on the optimal value of $t$ and $\epsilon$ in *preciseTAD*, we considered the normalized enrichment $NE$ of flanked predicted boundaries, defined as
 
-$$N_{e} = \dfrac{1}{b} \Sigma_{i=1}^{n}e_{i}$$
+$$NE = \dfrac{1}{p} \left[ \Sigma_{s=1}^{p} \left[ \dfrac{1}{b} \Sigma_{k=1}^{b} e_{ks} \times c_{k} \right] \right]$$
 
-where $e_{i}$ is the number ChIP-seq peak regions that overlap with the $i^{th}$ predicted boundary, $b$, flanked by resolution $r$.
-We evaluated $N_{e}$ for combinations of $t=\{0.95, 0.975, 0.99, 1.0 \}$ and $\epsilon = \{5000, 10000, 15000, 20000, 25000 \}$.
+where $e_{ks} = \textbf{I}\{ r_{s} \in (b_{k}-f, b_{k}+f)\}$ is the number of elemental regions $r$ of predictor $p$ that overlap with each flanked boundary.
+We evaluated $NE$ for combinations of $t=\{0.975, 0.99, 1.0 \}$ and $\epsilon = \{1000, 5000, 10000, 15000, 20000, 25000 \}$.
 The heuristic of $\epsilon$ is that density-reachable bases with genomic distances less than $\epsilon$ should occupy the same designated cluster.
@@
 The reason for it is two-fold: (1) to devise a tunable prediction rule in a supervised learning framework that is both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors [@boulesteix2012overview].
-We use published Arrowhead-called TAD boundaries [@durand2016juicer] and Peakachu-predicted loop boundaries [@salameh2019supervised] as ground truth.
+We used Arrowhead-called TAD boundaries [@durand2016juicer] and published Peakachu-predicted loop boundaries [@salameh2019supervised] as ground truth.
 Data from GM12878 and K565 cell lines at 5-100kb resolution (Arrowhead) and 10kb resolution (Peakachu) were used (Supplementary Table 1).
-We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base resolution from cell-type-specific genome annotation data.
+We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base resolution from cell line-specific genome annotation data.
 
-![**Resolution-specific data construction and feature engineering used for downstream random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals (see Methods).
-The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD boundary.
-(B) Four types of associations between bins and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png)
+![**Resolution-specific data construction and feature engineering used for downstream random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals using *shifted binning* (see Methods).
+The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD(or loop) boundary.
+(B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png)
 
@@
 
-A total of 77 cell-line-specific genomic annotations were used to build the predictor space.
+A total of 77 cell line-specific genomic annotations were used to build the predictor space.
 These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 2).
@@
 Once the model inputs were established, a random forest classifier was trained on $n-1$ autosomal chromosomes, while reserving the $i^{th}$ chromosome for testing.
-Three-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed to default values of 500 and 1, respectively.
+Three-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed at 500 and at 0.1% of the rows in the training data, respectively.
 Model performance was evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (see Methods).
@@
 Additionally, we found that using a distance-type predictor space yielded substantially higher balanced accuracy compared to the peak signal strength, overlap count, and overlap percent predictor types.
-As with class balancing techniques, this improvement was less evident at lower resolutions, with results consistent for K562 (Supplementary Figure 2).
-Random forest models built on Peakachu-defined loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3).
+As with class balancing techniques, this improvement was less evident at lower resolutions, with results consistent for K562 (Supplementary Figure 3A).
+Random forest models built on Peakachu-defined loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3B,3C).
 Furthermore, 5 kb resolution genomic bins led to the optimal prediction for both TAD and loop boundaries, on both cell lines.
@@
 
-![**Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for GM12878 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+![**Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for GM12878 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
@@
 The columns represent the holdout chromosome excluded from the training data.
-(D) Receiver operating characteristic (ROC) curves and subsequent area under the curves (AUCs) when training and testing on the same cell line versus across cell lines.
-The curves represent the average sensitivities and specificities across each holdout chromosome.](Figures/figure4.png)
+(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on the same cell line (blue.
+Arrowhead ground truth; red, Peakachu ground truth) versus across cell lines (black, dashed).
+The curves represent the average sensitivities and specificities across each holdout chromosome.
+The shaded areas around each curve represent $\pm$ 1 standard deviation aways from the average.](Figures/figure4.png)
 
@@
 Having demonstrated the optimal performance in our framework's ability to predict boundary regions, we next attempted to predict boundary regions in one cell line using the model pre-trained on data from another another cell line (See Methods).
-We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from GM12878 cell line resulted in an average AUC=0.845 (Figure 4D).
-The performance of this model only slightly decreased when evaluated using K562-specific Arrowhead boundaries and genomic annotation data (AUC = 0.803).
-Likewise, the performance of the model trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable when evaluated using K562-specific Peakachu boundaries and genomic annotations (AUC=0.885 and 0.868, respectively).
+We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from GM12878 cell line resulted in an average AUC=0.792 (Figure 4D).
+Suprisingly, when testing on the K562 cell line, the average AUC increased to 0.837.
+Likewise, the performance of the model trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable when evaluated using K562-specific Peakachu boundaries and genomic annotations (AUC=0.881 and 0.868, respectively).
 These results were consistent when training on K562 and testing on GM12878 data (Supplementary Figure 4D).
-In summary, our observations suggest that a model trained on data from one cell line performs well when using the data from another cell line.
+The average ROC curves were found to be well within $\pm$ 1 standard deviation of eachother, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.
 
@@
 The model trained on a bin-level space was then applied on a base-level space to predict each base's probability of being a boundary.
-Our method, referred to as *preciseTAD*, uses density-based spatial clustering (DBSCAN) and partitioning around medoids (PAM) to predict the location of boundary regions and summit points (highest boundary probability) at base-level resolution (see Methods).
+Our method, referred to as *preciseTAD*, uses density-based spatial clustering (DBSCAN) and partitioning around medoids (PAM) to predict the location of boundary regions and summit points (highest boundary probability) at base-level resolution (see Methods; Supplementary Figure 2).
 
-When trained using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, the *preciseTAD* model predicted a total of 7,846 TAD and 15,838 chromatin loop boundaries in GM12878, as well as 8,883 TAD and 11,016 chromatin loop boundaries in K562 cell line (Supplementary Table 4).
+When trained using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, the *preciseTAD* model predicted a total of 12,258 TAD and 15,707 chromatin loop boundaries in GM12878, as well as 9,603 TAD and 11,154 chromatin loop boundaries in K562 cell line (Supplementary Table 4).
 We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Supplementary Table 3).
-This can be attributed to Arrowhead's inflation of called TADs, that, when visualized, often do not correspond to domains enriched in internal interactions (Figure 5A) and signal of known drivers of domain boundaries (Supplementary Figure 5).
+This can be attributed to Arrowhead's inflation of called TADs, that, when visualized, often do not correspond to domains enriched in internal interactions (Figure 5A) and signal of known drivers of domain boundaries (Figure 5B).
 *preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Supplementary Table 3).
@@
 The black line represents the predicted probability of each base being a TAD boundary.
-(B, C) Profile plots comparing the signal strength of CTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called boundaries (blue, B), Peakachu loop boundaries (red, C) vs.
+(B) A zoomed-in portion of the genome shows the preciseTAD boundary region (PTBR), a yellow-highlighted cluster of bases with high probability of being a boundary.
+Underneath is the genome browser visualization of bigwig files for known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143 associated with the PTBR.
+(C, D) Profile plots comparing the signal strength of CTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called boundaries (blue, C), Peakachu loop boundaries (red, D) vs.
 *preciseTAD*-predicted boundaries (green).](Figures/figure5.png)
@@
 Next, we evaluated the biological significance of *preciseTAD* boundaries.
-Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, colocalized more frequently around *preciseTAD*-predicted TAD and loop boundaries compared to Arrowhead-called TAD and Peakachu loop boundaries respectively (Figure 5B, C; Supplementary Figure 5A, B).
-Surprised by the poor signal distribution at the Arrowhead boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, and our SpectralTAD [@Cresswell:2020ab] TAD caller.
+Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, colocalized more frequently around *preciseTAD*-predicted TAD and loop boundaries compared to Arrowhead-called TAD and Peakachu loop boundaries respectively (Figure 5C, 5D; Supplementary Figure 5A, 5B).
+Surprised by the poor signal distribution around Arrowhead boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, and our SpectralTAD [@Cresswell:2020ab] TAD caller.
 We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the well-performing Peakachu- and SpectralTAD-called boundaries (Supplementary Figure 5C, D).
@@
 Boundaries involving Arrowhead were flanked by 5 kb, while boundaries involving Peakachu were flanked by 10 kb.
-We found that 46%/63% of *preciseTAD*-predicted domain boundaries using models trained on Arrowhead/Peakachu data, respectively, were conserved between GM12878 and K562 cell lines.
-This is in contrast to only 26% and 63% for Arrowhead and Peakachu boundaries themselves (Figure 6B).
+Only 26% and 49% of boundaries were conserved between cell lines for Arrowhead and Peakachu boundaries (J=0.186 and J=0.388), respectively (Figure 6D, 6D.
+However, we found 45%/56% of *preciseTAD*-predicted domain boundaries using models trained on Arrowhead/Peakachu data (J=0.383 and J=0.444), respectively, were conserved between GM12878 and K562 cell lines (Figure 6C, 6E).
 The better conservation of *preciseTAD*-predicted boundaries further supports the notion of their higher biological relevance.
@@
 The p-values are from the Wilcoxon Rank Sum test.
-(B) Venn diagrams illustrating the levels of conservation between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead-trained *preciseTAD* model (top left), Arrowhead boundaries themselves (top right), Peakachu-trained *preciseTAD* model (bottom left), and Peakachu boundaries themselves (bottom right).
+(B) Venn diagrams illustrating the levels of conservation between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead boundaries themselves, Arrowhead-trained *preciseTAD* models (C), Peakachu boundaries themselves (C), and Peakachu-trained *preciseTAD* model (D).
 J - the Jaccard Index evaluating the similarity between each set of boundaries flanked by resolution.](Figures/figure6.png)
@@
 The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model.
-We found that 86.8% and 92.6% of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 9).
+We found that 88.8% and 95.8% of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 9).
 This is expected as loop boundaries (Peakachu) are more abundant, while TAD boundaries (Arrowhead) represent the narrower level of the 3D chromatin organization.
 Together with the results in Figure 4, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar molecular mechanisms.
+
+???include paragraph for figure7
 
@@
 We show that binding of four transcription factors (SMC3, RAD21, CTCF, ZNF143) is sufficient for accurate boundary predictions.
-*preciseTAD* is implemented as an R package, provides the pre-trained models, and allows for precise prediction of boundaries for any cell type for which the genomic annotations are available.
+*preciseTAD* is implemented as an R package, provides the pre-trained models, and allows for precise prediction of boundaries for any cell line for which the genomic annotations are available.
 
@@
 
-<!-- Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC).
+Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Supplementary Table 5).
 Our aim was to have a balanced metric sensitive to class imbalance such that it would not favor one component of the confusion matrix.
@@
 The BA benefits from incorporating all components of the confusion matrix, while also being sensitive to class imbalance, a necessary characteristic when comparing performances to models built using no data resampling.
-[???refer to supp tables 4 and 5 here when ready] -->
 
@@
 Furthermore, each PTBR is formed by several sub-regions with the probability of being a boundary defined by the threshold $t$ ($t=1$ in the current study).
-Yet, the preciseTAD boundary points (PTBSs, medoids identified within each PTBR) had the highest density of CTCF and other transcription factor binding signal (Figure 5).
+Yet, the preciseTAD boundary points (PTBPs, medoids identified within each PTBR) had the highest density of CTCF and other transcription factor binding signal (Figure 5).
 Our results are in line with the emergent view that domain boundaries are dynamic [@chang2020tads] and their well-defined location arise as a consequence of the population average in bulk Hi-C data [@fudenberg2016formation; @Flyamer:2017aa].
@@
 Lower values of $t$ and $\epsilon$ will result in more clusters of bases, and therefore, more boundaries.
-As a heuristic, we evaluated the pairwise combination of four different thresholds ($t=(0.95,0.975,0.99,1.0)$) and four different $eps$ values ($\epsilon=(r, 2r, 3r, 4r, 5r)$)), where $r=5000$, the optimal resolution.
-We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries were maximized for combinations of $t=1.0$ and $eps=r$ (Supplementary Figure 10).
+As a heuristic, we evaluated the pairwise combination of 3 different thresholds ($t=(0.975,0.99,1.0)$) and 6 different $\epsilon$ values ($\epsilon=(1000,5000,10000,15000,20000,25000)$)).
+We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (Supplementary Figure 10).
 
@@
 
-Using the provided pre-trained models, *preciseTAD* is able to identify precise domain boundaries using cell-type-specific genome annotation information of only four transcription factors, CTCF, SMC3, RAD21, ZNF143.
-Although the ENCODE, NIH Roadmap Epigenomics, FANTOM5, BLUEPRINT, and other members of the International Human Epigenome Consortium (IHEC) [@Stunnenberg:2016aa] have been actively cataloging cell-type-specific genome annotation datasets, these data remain very sparse.
+Using the provided pre-trained models, *preciseTAD* is able to identify precise domain boundaries using cell line-specific genome annotation information of only four transcription factors, CTCF, SMC3, RAD21, ZNF143.
+Although the ENCODE, NIH Roadmap Epigenomics, FANTOM5, BLUEPRINT, and other members of the International Human Epigenome Consortium (IHEC) [@Stunnenberg:2016aa] have been actively cataloging cell line-specific genome annotation datasets, these data remain very sparse.
 To date (September 2020), the ENCODE project has only five cell lines (GM12878, K562, H1-hESC, HeLa-S3, HepG2) with all four transcription factor genomic annotations.
-Efforts to <!--systematically catalog chromatin conformation capture data [@Wang:2018ab] and -->impute missing cell-type-specific genome annotation information [@Schreiber:2020aa] started to appear.
-We envision the broader availability of cell-type-specific genomic annotations will enable a more systematic analysis of domain boundaries using *preciseTAD*.
-<!--*preciseTAD* requires both cell-type-specific chromatin conformation capture data (Hi-C in the current study) and genome annotation data.
+Efforts to <!--systematically catalog chromatin conformation capture data [@Wang:2018ab] and -->impute missing cell line-specific genome annotation information [@Schreiber:2020aa] started to appear.
+We envision the broader availability of cell line-specific genomic annotations will enable a more systematic analysis of domain boundaries using *preciseTAD*.
+<!--*preciseTAD* requires both cell line-specific chromatin conformation capture data (Hi-C in the current study) and genome annotation data.
 Hi-C data provides information about the approximate location of domain boundaries, while genome annotation data is used to train a model that can predict boundaries at the base-level resolution.
-The diversity of chromatin conformation capture technologies [@Kempfer:2019aa] and analysis methods [@Hansen:2019aa] limits the availability of harmonized cell-type-specific domain boundary information.-->
+The diversity of chromatin conformation capture technologies [@Kempfer:2019aa] and analysis methods [@Hansen:2019aa] limits the availability of harmonized cell line-specific domain boundary information.-->
 
@@
 **Additional File 1**.
-An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions.
-<!--Prior to implementing SpectralTAD, the dump command offered by juicer [@durand2016juicer] was used to extract the contacts in sparse data matrix format.-->
+An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions as well implemeting various deepTools commands to generate plotProfiels and plotHeatmaps.
 
@@
 The GRCh37/hg19 human genome assembly was used.
-"Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Cell Type-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
-
-**Supplementary Table 3.** Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the K562 cell line.
-Class imbalance is calculated as the ratio of the total number of unique boundaries to the total number of genomic bins.
-
-**Supplementary Table 4.** Genomic coordinates of *preciseTAD*-predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562, using Arrowhead TAD and Peakachu chromatin loop boundary coordinates as ground truth.
-For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability of being a boundary equal to 1.
-For PTBPs, the start and end (start+1) coordinates define the uniquely identified boundary coordinate within each PTBR.
-All coordinates are in hg19/GRCh37 reference genome.
-(Work in progress)
-
-<!--
-**Supplementary Table 5.** Additional performance metrics when implementing a random forest using Arrowhead ground truth TAD boundaries.
-Performances are averaged across each holdout chromosome that was reserved for testing.
-
-**Supplementary Table 6.** Additional performance metrics when implementing a random forest using Peakachu ground truth chromatin loop boundaries.
-Performances are averaged across each holdout chromosome that was reserved for testing.
--->
+"Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Cell line-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
 
@@
 
-**Supplementary Figure 2.
-Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for K562 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: (A) Signal, (B) OC, (C) OP, and (D) Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+**Supplementary Figure 2** Psuedocode of the *preciseTAD* algorithm.
+
+**Supplementary Table 3.** Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the K562 cell line.
+Class imbalance is calculated as the ratio of the total number of unique boundaries to the total number of genomic bins.
+
+**Supplementary Figure 3** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562.
+(B) Averaged balanced accuracies are compared for GM12878 and (C) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.
 
-**Supplementary Figure 3.
-Distance-type predictors combined with random under-sampling or SMOTE re-sampling yielded optimal predictive performance Peakachu loop boundaries at 10 kb resolution.** Averaged balanced accuracies are compared for A) GM12878 and B) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.
-
-**Supplementary Figure 4.
-Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+**Supplementary Figure 4.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using K562-specific histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
@@
 The columns represent the holdout chromosome excluded from the training data.
-(D) Receiver operating characteristic (ROC) curves and subsequent area under the curves (AUCs) when training and testing on the same cell line versus across cell lines.
+(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on the same cell line (blue.
+Arrowhead ground truth; red, Peakachu ground truth) versus across cell lines (black, dashed).
 The curves represent the average sensitivities and specificities across each holdout chromosome.
+The shaded areas around each curve represent $\pm$ 1 standard deviation aways from the average.
+
+**Supplementary Table 4.** Genomic coordinates of *preciseTAD*-predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562, using Arrowhead TAD and Peakachu chromatin loop boundary coordinates as ground truth.
+For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability of being a boundary equal to 1 and $\epsilon=10000$.
+For PTBPs, the start and end (start+1) coordinates define the uniquely identified boundary coordinate within each PTBR.
+All coordinates are in hg19/GRCh37 reference genome.
+(Work in progress)
 
@@
 
-**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** Profile plots comparing the signal strength of CTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called boundaries (blue, A), Peakachu loop boundaries (red, B) vs.
-*preciseTAD*-predicted boundaries (green) on K562 data (chr14:50085000-50800000).
-
 **Supplementary Figure 6.** *preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.
-Enriched heatmaps comparing the enrichment of (A) Arrowhead called TAD boundaries vs *preciseTAD*-predicted TAD boundaries, and (B) Peakachu loop boundaries vs *preciseTAD*-predicted loop boundaries around key GM12878-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
+Enriched heatmaps comparing the enrichment of Arrowhead called TAD boundaries vs *preciseTAD*-predicted TAD boundaries around key transcription factor binding sites known to contribute to the 3D chromatin architecture for (A) GM12878 and (B) K562.
 
 **Supplementary Figure 7.** *preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.
-Enriched heatmaps comparing the enrichment of (A) Arrowhead called TAD boundaries vs *preciseTAD*-predicted TAD boundaries, and (B) Peakachu loop boundaries vs preciseTAD predicted loop boundaries around key K562-specific transcription factor binding sites known to contribute to the 3D chromatin architecture.
+Enriched heatmaps comparing the enrichment of Peakachu chromatin loop boundaries vs *preciseTAD*-predicted chromatin boundaries around key transcription factor binding sites known to contribute to the 3D chromatin architecture for (A) GM12878 and (B) K562.
 
@@
 
-**Supplementary Figure 10.** Linecharts illustrating the normalized overlap between known molecular drivers of 3D chromatin and resolution-flanked *preciseTAD*-predicted boundaries (trained on Arrowhead boundaries) for different combinations of thresholds (t) and epsilon parameter values (eps).
-Data from GM12878 cell line, chromosome 22, at 5kb resolution was used.
-Normalized overlap was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted.
+**Supplementary Figure 10.** Linecharts illustrating the normalized enrichment (NE) between known molecular drivers of 3D chromatin and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps).
+Data from GM12878 and K562 cell lines, chromosome 22, at 5kb resolution was used.
+NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model.
+Error bars indicate standard deviation away from the mean.
+
+**Supplementary Table 5.** Additional performance metrics when implementing a random forest using Arrowhead/Peakachu ground truth TAD/loop boundaries.
+Performances are averaged across each holdout chromosome that was reserved for testing.
 

### 2020-09-16 Scripts_for_results/16_psuedocode.Rmd
edits to manuscript; updated figures and  legends

@@
 \BlankLine
-2. \For{each chr $i$ do}{
+2. \For{each chr $i$}{
 \BlankLine
@@
 16.                         Calculate the normalized enrichment (NE) over all predictors
-                            $$NE = \dfrac{1}{p} \left[ \Sigma_{s=1}^{p} \left[ \dfrac{1}{b} \Sigma_{k=1}^{b} e_{ks} \times c_{k} \right] \right]$$
-                            where $e_{ks} = \textbf{I}\{ r_{s} \in (b_{k}-f, b_{k}+f)\}$ is the number of elemental regions $r$ of predictor $p$ that overlap with each flanked boundary and $c_{k} = \dfrac{ \textbf{I}\{ \pi_{n} \ge t_{l} \in w_{k} \} }{w_{k}}$ is the coverage probability of each PTBR\;
+                            $$NE = \dfrac{1}{p} \left[ \Sigma_{s=1}^{p} \left[ \dfrac{1}{b} \Sigma_{k=1}^{b} e_{ks} \right] \right]$$
+                            where $e_{ks} = \textbf{I}\{ r_{s} \in (b_{k}-f, b_{k}+f)\}$ is the number of elemental regions $r$ of predictor $p$ that overlap with each flanked boundary\;
 \BlankLine

### 2020-09-16 Manuscript/manuscript.Rmd
fixed figure positions

@@
   pdf_document: 
+    extra_dependencies: ["float"]
   word_document:
@@
 ---
+
+```{r}
+knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
+```
 

### 2020-09-16 Manuscript/manuscript.Rmd
editted suppfig10 and legend

@@
 
-**Supplementary Figure 10.** Linecharts illustrating the normalized enrichment (NE) between known molecular drivers of 3D chromatin and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps).
-Data from GM12878 and K562 cell lines, chromosome 22, at 5kb resolution was used.
+**Supplementary Figure 10.** Linecharts illustrating the normalized enrichment (NE) between known molecular drivers of 3D chromatin and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps) using data from GM12878 (A) and K562 (B) cell lines, chromosome 22, at 5kb resolution was used.
 NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model.

### 2020-09-17 Manuscript/manuscript.Rmd
added cross cell line prediction last paragraph manuscript; editted figures

--- 2020-09-16 Manuscript/manuscript.Rmd
@@
 Together with the results in Figure 4, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar molecular mechanisms.
+Guided by the high predictive performance when training and testing on different cell lines (Figure 4D), we opted to evaluate whether *preciseTAD* could be leveraged to predict boundaries using unseen base level cell line-specific annotation data.
+To do so, we evaluated two separate scenarios for each type of ground truth boundary: 1) training on GM12878 and predicting boundaries on GM12878 (GM on GM) vs training on K562 and predicting on GM12878 (K on GM), and 2) training on K562 and predicting boundaries on K562 (K on K) vs training on GM12878 and predicting boundaries on K562 (GM on K).
+Using Arrowhead ground truth, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries were overlapped in each scenario, respectively (Supplementary Figure 10A, 10B).
+Likewise, when using Peakachu ground truth, there was 85% (J=0.705) and 88% (J=0.759) of overlap between predicted boundaries, respectively (Supplementary 10C, 10D).
+Furthermore, boundaries predicted on unseen annotation data exhibited similar levels of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line.
+These results open up the possibility of using preciseTAD to predict TAD or loop boundaries for cell lines that do not currently have Hi-C data.
 
@@
 As a heuristic, we evaluated the pairwise combination of 3 different thresholds ($t=(0.975,0.99,1.0)$) and 6 different $\epsilon$ values ($\epsilon=(1000,5000,10000,15000,20000,25000)$)).
-We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (Supplementary Figure 10).
+We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (Supplementary Figure 11).
 
@@
 
-**Supplementary Figure 1.** Density curves of distances before (red) and after (blue) performing a $log_{2}$ transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines, respectively.
+**Supplementary Figure 1.
+$log_{2}$ transformation normalizes genomic distance.** Density curves of distances before (red) and after (blue) performing a $log_{2}$ transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines, respectively.
 Distances are measured as the number of bases from the center of a genomic bin to the nearest genomic annotation center.
@@
 
-**Supplementary Figure 2** Psuedocode of the *preciseTAD* algorithm.
+**Supplementary Figure 2.** Psuedocode of the *preciseTAD* algorithm.
 
@@
 
-**Supplementary Figure 3** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562.
+**Supplementary Figure 3.
+Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal boundary region predictive performance.** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562.
 (B) Averaged balanced accuracies are compared for GM12878 and (C) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
@@
 
-**Supplementary Figure 4.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using K562-specific histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+**Supplementary Figure 4.
+Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using K562-specific histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
@@
 
-**Supplementary Figure 6.** *preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.
-Enriched heatmaps comparing the enrichment of Arrowhead called TAD boundaries vs *preciseTAD*-predicted TAD boundaries around key transcription factor binding sites known to contribute to the 3D chromatin architecture for (A) GM12878 and (B) K562.
+**Supplementary Figure 6.
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.** Enriched heatmaps comparing the enrichment of Arrowhead called TAD boundaries vs *preciseTAD*-predicted TAD boundaries around key transcription factor binding sites known to contribute to the 3D chromatin architecture for (A) GM12878 and (B) K562.
 
-**Supplementary Figure 7.** *preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.
-Enriched heatmaps comparing the enrichment of Peakachu chromatin loop boundaries vs *preciseTAD*-predicted chromatin boundaries around key transcription factor binding sites known to contribute to the 3D chromatin architecture for (A) GM12878 and (B) K562.
+**Supplementary Figure 7.
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.** Enriched heatmaps comparing the enrichment of Peakachu chromatin loop boundaries vs *preciseTAD*-predicted chromatin boundaries around key transcription factor binding sites known to contribute to the 3D chromatin architecture for (A) GM12878 and (B) K562.
 
-**Supplementary Figure 8.** *preciseTAD* boundaries are spatially closer to known molecular drivers of 3D chromatin.
-Boxplots comparing the log2 genomic distances from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
+**Supplementary Figure 8.
+*preciseTAD* boundaries are spatially closer to known molecular drivers of 3D chromatin.** Boxplots comparing the log2 genomic distances from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
 The p-value is derived from the Wilcoxon Rank Sum test.
 
-**Supplementary Figure 9.** *preciseTAD*-predicted TAD boundaries using Arrowhead are nested within *preciseTAD*-predicted chromatin loop boundaries using Peakachu.
-Venn diagrams illustrating the agreement between boundaries predicted using Arrowhead- and Peakachu-trained models for (A) GM12878 and (B) K562.
+**Supplementary Figure 9.*preciseTAD*-predicted TAD boundaries are nested within *preciseTAD*-predicted chromatin loop boundaries.** Venn diagrams illustrating the agreement between boundaries predicted using Arrowhead- and Peakachu-trained models for (A) GM12878 and (B) K562.
 Domain boundaries were flanked by resolution (5 kb for models using Arrowhead and 10 kb for Peakachu).
 
-**Supplementary Figure 10.** Linecharts illustrating the normalized enrichment (NE) between known molecular drivers of 3D chromatin and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps).
-Data from GM12878 and K562 cell lines, chromosome 22, at 5kb resolution was used.
+**Supplementary Figure 10.
+*preciseTAD* accurately predicts boundaries on cell lines using unseen annotation data.** Venn diagrams comparing flanked predicted boundaries using Arrowhead ground truth to: (A) train on GM12878 and predict on GM12878 (GM on GM) vs train on K562 and predict on GM12878 (K on GM), (B) train on K562 predict on K562 (K on K) vs train on GM12878 predict on K562 (GM on K).
+(C-D) Using Peakachu ground truth.
+The corresponding profilePlots (deepTools version 2.0) are provided to the right.
+Predicted boundaries using Arrowhead ground truth were flanked by 5 kb, while boundaries predicted using Peakachu ground truth were flanked by 10 kb.
+
+**Supplementary Figure 11.
+Normalized Enrichment levels converge for combinations on t=1.0 and $\epsilon=10000$.** Linecharts illustrating the normalized enrichment (NE) between known molecular drivers of 3D chromatin and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps) using data from GM12878 (A) and K562 (B) cell lines, chromosome 22, at 5kb resolution was used.
 NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model.

### 2020-09-17 Manuscript/manuscript.Rmd
removed my ??? for fig7
echo=FALSE to code chunk
Abstract polishing

@@
 
-```{r}
+```{r echo=FALSE}
 knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
@@
 We investigated several feature engineering and resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) to select the most optimal data characteristics and address class imbalance.
-Density-based clustering and scalable partitioning techniques were used to identify the precise location of boundary regions and summit points.
+Density-based clustering (DBSCAN) and partitioning around medoids (PAM) techniques were used to identify the precise location of boundary regions and summit points.
 We benchmarked our method against the Arrowhead domain caller and a novel chromatin loop prediction algorithm, Peakachu, on the two most annotated cell lines.
@@
 Boundaries predicted by *preciseTAD* were more enriched for CTCF, RAD21, SMC3, and ZNF143 signal and more conserved across cell lines, highlighting their higher biological significance.
-The model pre-trained in one cell line performs well in predicting boundaries in another cell line using only genomic annotations, enabling the detection of domain boundaries in cells without Hi-C data.
+The model pre-trained in one cell line performs well in another cell line.
+Using cell line-specific genomic annotations, the pre-trained models enable the detection of domain boundaries in cells without Hi-C data.
 
@@
 
-???include paragraph for figure7
-
 # Discussion

### 2020-09-17 Manuscript/manuscript.Rmd
Polishing introduction

@@
 The precise identification of domain boundaries will improve our understanding of how genomic regulators are shaping the 3D structure of the genome.
-*preciseTAD* R package is available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor (submitted).
+<!-- *preciseTAD* R package is available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor (submitted).
+-->
 
@@
 Several methods have been proposed to identify genomic coordinates of TADs (reviewed in [@Zufferey:2018aa; @forcato2017comparison]), and chromatin loops [@rao20143d; @Ay:2014aa; @Heinz:2010aa; @salameh2019supervised].
-However, a key limitation among most of these TAD- and loop callers is that they depend on Hi-C data *resolution*.
+However, a key limitation of them is that they depend on Hi-C data *resolution*.
 Resolution refers to the size of genomic regions (bins) used to segment the linear genome [@li2019comparison].
@@
 The resolution of ChIP-seq experiments is typically on the order of tens to hundreds of bases [@mendoza2009genome], well below the resolution of Hi-C data (tens of kilobases; 750 bp is the highest resolution of Hi-C data to date [@bonev2017multiscale]).
-Therefore, leveraging precisely mapped genomic annotations in a supervised machine learning framework provides the possibility of more precisely predicting the locations of domain boundaries.
+Therefore, leveraging precisely mapped genomic annotations in a supervised machine learning framework enables more precise prediction of the locations of domain boundaries.
 
@@
 We introduce a systematic pipeline for building the optimal boundary prediction classifier.
-We found that spatial associations (linear distance) between boundaries and annotations perform best, transcription factor binding sites further improve prediction accuracy, and a simple random undersampling technique effectively addresses the negative effect of class imbalance.
+We found that spatial associations (linear distance) between boundaries and annotations perform best, transcription factor binding sites improve prediction accuracy, and a simple random undersampling technique effectively addresses the negative effect of class imbalance.
 Translated from Hi-C data resolution level to base level (annotating each base and predicting its boundary probability), *preciseTAD* employs density-based clustering (DBSCAN) and partitioning around medoids (PAM) to detect genome annotation-guided boundary regions and points at a base-level resolution.
@@
 We demonstrate that *preciseTAD* predictions are more enriched for known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143.
-Further, we show that *preciseTAD* boundaries are more conserved across cell lines, and the model trained in one cell line can predict boundaries in another cell line.
+Further, we show that *preciseTAD*-detected boundaries are more conserved across cell lines, and the model trained in one cell line can predict boundaries in another cell line.
 This improved precision in the domain boundary location can provide insight into the association between genomic regulators and the 3D genome organization.

### 2020-09-17 Manuscript/manuscript.Rmd
Polishing Methods

@@
 
-Publicly available TAD and loop boundaries called by Arrowhead [@durand2016juicebox] and Peakachu [@salameh2019supervised] tools, respectively, were used for training.
-TAD boundaries were called from primary Hi-C data for the GM12878 and K562 cell lines using Arrowhead, a TAD-caller a part of the juicer suite of tools (version 7.5) [@durand2016juicer; @rao20143d].
-The contact matrices were constructed from all read pairs that uniquely aligned to the genome (MAPQ>0) (Additional File 1).
-The default parameters for Arrowhead were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions.
+TAD and loop boundaries called by Arrowhead [@durand2016juicebox] and Peakachu [@salameh2019supervised] tools were used for training.
+The autosomal genomic coordinates in the GRCh37/hg19 human genome assembly were considered.
+Arrowhead-defined TAD boundaries were called from the GM12878 and K562 cell line Hi-C data (MAPQ>0, 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions) using the default parameters (Additional File 1).
 Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab website (Supplementary Table 1).
@@
 
-To assess the impact of class imbalance (CI), defined as the proportion of boundary regions to non-boundary regions, we evaluated three resampling techniques.
-These include *Random Over-Sampling (ROS)*, *Random Under-Sampling (RUS)*, and *Synthetic Minority Over-Sampling Technique (SMOTE)*.
+To assess the impact of class imbalance (CI), defined as the proportion of boundary regions to non-boundary regions, we evaluated three resampling techniques: *Random Over-Sampling (ROS)*, *Random Under-Sampling (RUS)*, and *Synthetic Minority Over-Sampling Technique (SMOTE)*.
 For ROS, the minority class was sampled with replacement to obtain the same number of data points in the majority class.
@@
 For SMOTE, under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the $k=5$ minority class nearest neighbors [@chawla2002smote] (implemented in the `DMwR` v.0.4.1 R package).
-We restricted the SMOTE algorithm to 100% over-sampling and 200% under-sampling, which creates perfectly balanced classes.
+We restricted the SMOTE algorithm to 100% over-sampling and 200% under-sampling, to create perfectly balanced classes.
 
@@
 The number of trees (*ntree*) that were aggregated for each RF model was set to 500.
-The minimum number of observations per root node (*nodesize*) was set to .1% of the rows in the data.
+The minimum number of observations per root node (*nodesize*) was set to 0.1% of the rows in the data.
 The binned data for the holdout chromosome $i$ was reserved for testing.
@@
 To suitably reduce the predictor space and improve computational efficiency, while maintaining optimal performance, we implemented recursive feature elimination (RFE).
-In doing so, we estimated the near-optimal number of necessary features to include in the best fitting RF model.
-The best performing subset was identified, ranging from 2 to the maximum number of features incremented by the power of 2.
+We estimated the near-optimal number of necessary features, ranging from 2 to the maximum number of features incremented by the power of 2.
 We then aggregated the predictive importance of the union of the optimal set of features across holdout chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top-ranked annotations for predicting boundary regions.
@@
 The minimum and maximum coordinates of each cluster, $k$, of spatially colocalized bases were termed *preciseTAD boundary regions* (PTBR).
-To precisely identify a single base among each PTBR, *preciseTAD* then implements partitioning around medoids (PAM) on the sub distance matrix,$D_{k}$, derived from each cluster.
+To precisely identify a single base among each PTBR, *preciseTAD* implements partitioning around medoids (PAM) on the distance matrix, $D_{k}$, derived from each cluster.
 The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative base coordinate within each clustered PTBR.
@@
 The heuristic of $\epsilon$ is that density-reachable bases with genomic distances less than $\epsilon$ should occupy the same designated cluster.
+[???
+Add what was used as the default, refer to suppl figure]
 
@@
 
-We assessed the biological significance of our predicted boundaries by their association with several known molecular drivers of 3D chromatin architecture, including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks.
-To do so, we used the *computeMatrix*, *plotProfile*, and *plotHeatmap* tools offered by deepTools (version 2.0) [@ramirez2016deeptools].
+We assessed the biological significance of our predicted boundaries by their association with the signal of CTCF, RAD21, SMC3, and ZNF143 using *deepTools* (version 2.0) [@ramirez2016deeptools] (*computeMatrix*, *plotProfile*, and *plotHeatmap* tools).
 Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum tests.
@@
 
-![**Resolution-specific data construction and feature engineering used for downstream random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals using *shifted binning* (see Methods).
-The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD(or loop) boundary.
+![**Resolution-specific data construction and feature engineering for random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals using *shifted binning* (see Methods).
+The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD (or loop) boundary.
 (B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png)
@@
 **Additional File 1**.
-An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions as well implemeting various deepTools commands to generate plotProfiels and plotHeatmaps.
+An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions.
+An example of deepTools commands to generate plotProfiels and plotHeatmaps is also provided.
 
-**Supplementary Table 1.** Data source for Hi-C matrices used to call topologically associating domains with Arrowhead, as well as loop boundaries obtained by Peakachu.
+**Supplementary Table 1.** Data sources for Hi-C matrices used to call topologically associating domains with Arrowhead, as well as loop boundaries obtained by Peakachu.
 
@@
 **Supplementary Figure 1.
-$log_{2}$ transformation normalizes genomic distance.** Density curves of distances before (red) and after (blue) performing a $log_{2}$ transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines, respectively.
-Distances are measured as the number of bases from the center of a genomic bin to the nearest genomic annotation center.
+The $log_{2}$ transformation of genomic distances normalizes their distributions.** Distances are measured as the number of bases from the center of a genomic bin to the nearest genomic annotation center.
+Density curves of distances before (red) and after (blue) performing a $log_{2}$ transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines.
 Each density curve represents an individual genomic annotation (77 total).
 
-**Supplementary Figure 2.** Psuedocode of the *preciseTAD* algorithm.
+**Supplementary Figure 2.** Pseudocode of the *preciseTAD* algorithm.
 

### 2020-09-17 Manuscript/manuscript.Rmd
Half-way through results

@@
 
-We developed a machine learning (ML) framework aimed at determining the optimal set of data level characteristics necessary for precise prediction of boundaries of Topologically Associating Domains (TADs) and chromatin loops, collectively referred to as domain boundaries.
+We developed a machine learning (ML) framework for determining the optimal set of data level characteristics to predict boundaries of Topologically Associating Domains (TADs) and chromatin loops, collectively referred to as domain boundaries.
 We chose the random forest (RF) algorithm as our binary classification tool.
@@
 
-![**A machine learning framework for building domain boundary region prediction models.** Step 1 employs a range of feature engineering techniques to define defines the predictor matrix $A_{N \times (p)}$, where $N$ is the number of genomic bins, $p$ is the number of genomic annotations, $i$ is a holdout chromosome.
+![**A machine learning framework for building domain boundary region prediction models.** Step 1 employs a range of feature engineering techniques to define the predictor matrix $A_{N \times (p)}$, where $N$ is the number of genomic bins, $p$ is the number of genomic annotations, $i$ is a holdout chromosome.
 The response vector $Y_N$ is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$).
-Step 2 is reserves the predictor-response matrix for the holdout chromosome $i$ as the test data.
+Step 2 reserves the predictor-response matrix for the holdout chromosome $i$ as the test data.
 Step 3 applies a resampling technique to the training data to address the class imbalance.
@@
 
-![**Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal TAD boundary region predictive performance for GM12878 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
+![**Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yield optimal TAD boundary region predictive performance for GM12878 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Error bars indicate standard deviation from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
 
@@
 
-![**Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+![**SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
-Error bars represent 1 standard deviation from the cross-validated accuracy across each holdout chromosome.
+Error bars represent 1 standard deviation from the mean cross-validated accuracy across each holdout chromosome.
 (C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs.
 The columns represent the holdout chromosome excluded from the training data.
-(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on the same cell line (blue.
+[???
+What is color gradient?
+Also, add to supp fig 4] (D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on the same cell line (blue.
 Arrowhead ground truth; red, Peakachu ground truth) versus across cell lines (black, dashed).
@@
 **Supplementary Figure 3.
-Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yielded optimal boundary region predictive performance.** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562.
+Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yield optimal boundary region predictive performance.** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562.
 (B) Averaged balanced accuracies are compared for GM12878 and (C) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
@@
 **Supplementary Figure 4.
-Binding of SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using K562-specific histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using K562-specific histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
-Error bars represent 1 standard deviation from the cross-validated accuracy across each holdout chromosome.
+Error bars represent 1 standard deviation from the mean cross-validated accuracy across each holdout chromosome.
 (C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs.

### 2020-09-17 Manuscript/manuscript.Rmd
Results finished

@@
 *preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Supplementary Table 3).
-This can be attributed to the fact that *preciseTAD* leverages four known drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143.
-This is in contrast to Peakachu, which considers only CTCF sites to mark the predicted boundaries as true positives.
+This can be attributed to Peakachu's use of only CTCF sites to call boundaries, while *preciseTAD* leverages four known drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143.
 These results suggest that genome annotation-driven predicted boundaries may be more biologically relevant than those detected from Hi-C data alone.
@@
 The black line represents the predicted probability of each base being a TAD boundary.
-(B) A zoomed-in portion of the genome shows the preciseTAD boundary region (PTBR), a yellow-highlighted cluster of bases with high probability of being a boundary.
-Underneath is the genome browser visualization of bigwig files for known molecular drivers of 3D chromatin including CTCF, RAD21, SMC3, and ZNF143 associated with the PTBR.
-(C, D) Profile plots comparing the signal strength of CTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called boundaries (blue, C), Peakachu loop boundaries (red, D) vs.
+(B) A zoomed-in portion of the genome shows the preciseTAD boundary region (PTBR, highlighted yellow), a cluster of bases with high probability of being a boundary, and the corresponding signal profiles of CTCF, RAD21, SMC3, and ZNF143.
+(C, D) Signal profile plots comparing the strength of CTCF, RAD21, SMC3, and ZNF143 binding around Arrowhead-called boundaries (blue, C), Peakachu loop boundaries (red, D) vs.
 *preciseTAD*-predicted boundaries (green).](Figures/figure5.png)
 
-Next, we evaluated the biological significance of *preciseTAD* boundaries.
-Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, colocalized more frequently around *preciseTAD*-predicted TAD and loop boundaries compared to Arrowhead-called TAD and Peakachu loop boundaries respectively (Figure 5C, 5D; Supplementary Figure 5A, 5B).
+Next, we evaluated the biological significance of *preciseTAD* boundary points.
+Signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (Figure 5C, 5D; Supplementary Figure 5A, 5B).
 Surprised by the poor signal distribution around Arrowhead boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, and our SpectralTAD [@Cresswell:2020ab] TAD caller.
-We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the well-performing Peakachu- and SpectralTAD-called boundaries (Supplementary Figure 5C, D).
-Signal heatmaps indicated that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Supplementary Figures 6-7).
+We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the relatively well-performing Peakachu- and SpectralTAD-called boundaries (Supplementary Figure 5C, D).
+Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Supplementary Figures 6-7).
 *preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBSs (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Supplementary Figure 8).
@@
 To assess the level of cross-cell-line conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, Arrowhead, and Peakachu.
-Boundaries involving Arrowhead were flanked by 5 kb, while boundaries involving Peakachu were flanked by 10 kb.
 Only 26% and 49% of boundaries were conserved between cell lines for Arrowhead and Peakachu boundaries (J=0.186 and J=0.388), respectively (Figure 6D, 6D.
-However, we found 45%/56% of *preciseTAD*-predicted domain boundaries using models trained on Arrowhead/Peakachu data (J=0.383 and J=0.444), respectively, were conserved between GM12878 and K562 cell lines (Figure 6C, 6E).
+However, 45%/56% of *preciseTAD*-predicted domain boundaries were conserved between GM12878 and K562 cell lines when using models trained on Arrowhead/Peakachu data (J=0.383 and J=0.444, respectively, Figure 6C, 6E).
 The better conservation of *preciseTAD*-predicted boundaries further supports the notion of their higher biological relevance.
 
-![**preciseTAD-predicted boundaries are both statistically significantly closer to CTCF sites and more conserved across cell lines**.
-(A) Log2 genomic distances from called and predicted boundaries to nearest CTCF sites.
+![**preciseTAD-predicted boundaries are closer to CTCF sites and more conserved across cell lines**.
+(A) Log2 genomic distance distribution from called and predicted boundaries to nearest CTCF sites.
 The p-values are from the Wilcoxon Rank Sum test.
-(B) Venn diagrams illustrating the levels of conservation between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead boundaries themselves, Arrowhead-trained *preciseTAD* models (C), Peakachu boundaries themselves (C), and Peakachu-trained *preciseTAD* model (D).
-J - the Jaccard Index evaluating the similarity between each set of boundaries flanked by resolution.](Figures/figure6.png)
+(B-E) Venn diagrams illustrating the levels of conservation (overlap) between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead (B), Peakachu (D), *preciseTAD*-predicted boundaries using Arrowhead- and Peakachu-trained models () Arrowhead-trained *preciseTAD* models (C), Peakachu boundaries themselves (C, E, respectively).
+Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.](Figures/figure6.png)
 
@@
 The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model.
-We found that 88.8% and 95.8% of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 9).
-This is expected as loop boundaries (Peakachu) are more abundant, while TAD boundaries (Arrowhead) represent the narrower level of the 3D chromatin organization.
-Together with the results in Figure 4, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar molecular mechanisms.
-Guided by the high predictive performance when training and testing on different cell lines (Figure 4D), we opted to evaluate whether *preciseTAD* could be leveraged to predict boundaries using unseen base level cell line-specific annotation data.
-To do so, we evaluated two separate scenarios for each type of ground truth boundary: 1) training on GM12878 and predicting boundaries on GM12878 (GM on GM) vs training on K562 and predicting on GM12878 (K on GM), and 2) training on K562 and predicting boundaries on K562 (K on K) vs training on GM12878 and predicting boundaries on K562 (GM on K).
-Using Arrowhead ground truth, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries were overlapped in each scenario, respectively (Supplementary Figure 10A, 10B).
-Likewise, when using Peakachu ground truth, there was 85% (J=0.705) and 88% (J=0.759) of overlap between predicted boundaries, respectively (Supplementary 10C, 10D).
+We found that 88.8% and 95.8% [???
+These numbers are different from what is shown on Supp Fig 9] of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 9).
+[???
+After clarification, MD to rewrite the first two sentences, unclear] This is expected as loop boundaries (Peakachu) are more abundant, while TAD boundaries (Arrowhead) represent the higher level of the 3D chromatin organization.
+Together with the results in Figure 4C, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar molecular mechanisms.
+
+Guided by the high predictive performance when training and testing on different cell lines (Figure 4D), we opted to evaluate whether models trained using Arrowhead/Peakachu ground truth data in one cell line could be leveraged to predict boundaries using annotation data from another cell line.
+We evaluated two scenarios: 1) training on GM12878 and predicting boundaries on GM12878 (GM on GM) vs.
+training on K562 and predicting on GM12878 (K on GM), and 2) training on K562 and predicting boundaries on K562 (K on K) vs.
+training on GM12878 and predicting boundaries on K562 (GM on K).
+Using Arrowhead-trained models, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries overlapped in both cross-cell-line prediction scenarios (Supplementary Figure 10A, 10B).
+Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlaps (Supplementary 10C, 10D).
 Furthermore, boundaries predicted on unseen annotation data exhibited similar levels of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line.
-These results open up the possibility of using preciseTAD to predict TAD or loop boundaries for cell lines that do not currently have Hi-C data.
+[???
+Where is it shown?] These results indicate that *preciseTAD* pre-trained models can be successfully used to predict domain boundaries for cell lines lacking Hi-C data but for which genome annotation data is available.
 
@@
 
-**Supplementary Table 4.** Genomic coordinates of *preciseTAD*-predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562, using Arrowhead TAD and Peakachu chromatin loop boundary coordinates as ground truth.
-For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability of being a boundary equal to 1 and $\epsilon=10000$.
-For PTBPs, the start and end (start+1) coordinates define the uniquely identified boundary coordinate within each PTBR.
-All coordinates are in hg19/GRCh37 reference genome.
-(Work in progress)
+**Supplementary Table 4.** hg19/GRCh37 genomic coordinates of *preciseTAD*-predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562 cell lines, using models trained on Arrowhead TAD and Peakachu chromatin loop boundaries as ground truth.
+For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability of being a boundary equal to 1.
+For PTBPs, the start and end (start+1) coordinates define the most likely boundary point within each PTBR.
 
-**Supplementary Figure 5.** Profile plots comparing the signal strength of top TFBS around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green), (B) Peakachu chromatin loop boundaries (red) and preciseTAD predicted loop boundaries (green) on K562, (C) Arrowhead called TAD boundaries (blue), Peakachu chromatin loop boundaries (red), and SpectralTAD called TAD boundaries (green) on GM12878 and (D) on K562.
+**Supplementary Figure 5.** Signal profile plots comparing the binding strength of top TFBSs around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green) on K562, (B) Peakachu chromatin loop boundaries (red) and preciseTAD predicted loop boundaries (green) on K562, (C) Arrowhead called TAD boundaries (blue), Peakachu chromatin loop boundaries (red), and SpectralTAD called TAD boundaries (green) on GM12878 and (D) on K562.
 
 **Supplementary Figure 6.
-*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.** Enriched heatmaps comparing the enrichment of Arrowhead called TAD boundaries vs *preciseTAD*-predicted TAD boundaries around key transcription factor binding sites known to contribute to the 3D chromatin architecture for (A) GM12878 and (B) K562.
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Arrowhead boundaries.** Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called TAD boundaries vs.
+*preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
 
 **Supplementary Figure 7.
-*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.** Enriched heatmaps comparing the enrichment of Peakachu chromatin loop boundaries vs *preciseTAD*-predicted chromatin boundaries around key transcription factor binding sites known to contribute to the 3D chromatin architecture for (A) GM12878 and (B) K562.
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Peakachu boundaries.** Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Peakachu chromatin loop boundaries vs.
+*preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
 
 **Supplementary Figure 8.
-*preciseTAD* boundaries are spatially closer to known molecular drivers of 3D chromatin.** Boxplots comparing the log2 genomic distances from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
-The p-value is derived from the Wilcoxon Rank Sum test.
+*preciseTAD* boundaries are spatially closer to known molecular drivers of 3D chromatin.** Boxplots comparing the log2 genomic distance distributions from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
+p-values are derived from the Wilcoxon Rank Sum test.
 
-**Supplementary Figure 9.*preciseTAD*-predicted TAD boundaries are nested within *preciseTAD*-predicted chromatin loop boundaries.** Venn diagrams illustrating the agreement between boundaries predicted using Arrowhead- and Peakachu-trained models for (A) GM12878 and (B) K562.
-Domain boundaries were flanked by resolution (5 kb for models using Arrowhead and 10 kb for Peakachu).
+**Supplementary Figure 9.
+The agreement between *preciseTAD*-predicted boundaries using Arrowhead- and Peakachu-trained models**.
+Venn diagrams of boundary overlaps using (A) GM12878 and (B) K562 data.
+Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
 
 **Supplementary Figure 10.
-*preciseTAD* accurately predicts boundaries on cell lines using unseen annotation data.** Venn diagrams comparing flanked predicted boundaries using Arrowhead ground truth to: (A) train on GM12878 and predict on GM12878 (GM on GM) vs train on K562 and predict on GM12878 (K on GM), (B) train on K562 predict on K562 (K on K) vs train on GM12878 predict on K562 (GM on K).
-(C-D) Using Peakachu ground truth.
-The corresponding profilePlots (deepTools version 2.0) are provided to the right.
-Predicted boundaries using Arrowhead ground truth were flanked by 5 kb, while boundaries predicted using Peakachu ground truth were flanked by 10 kb.
+Pre-trained *preciseTAD* models accurately predict boundaries on cell lines using annotation data only.** Venn diagrams and signal profile plots comparing flanked predicted boundaries using Arrowhead (A, B) and Peakachu (C, D) trained models.
+(A, C) train on GM12878 and predict on GM12878 (red, GM on GM) vs.
+train on K562 and predict on GM12878 (blue, K on GM), (B, D) train on K562 predict on K562 (red, K on K) vs.
+train on GM12878 predict on K562 (blue, GM on K).
+Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
 

### 2020-09-17 Manuscript/manuscript.Rmd
addressed ???

@@
 The heuristic of $\epsilon$ is that density-reachable bases with genomic distances less than $\epsilon$ should occupy the same designated cluster.
+The default combination was set to $t=1.0$ and $\epsilon=10000$ (Supplementary Figure 11).
 [???
-Add what was used as the default, refer to suppl figure]
+Add what was used as the default, refer to suppl figure; !!!added]
 
@@
 The columns represent the holdout chromosome excluded from the training data.
-[???
+(???
 What is color gradient?
-Also, add to supp fig 4] (D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on the same cell line (blue.
+Also, add to supp fig 4; !!!added) (D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on the same cell line (blue.
 Arrowhead ground truth; red, Peakachu ground truth) versus across cell lines (black, dashed).
@@
 We found that 88.8% and 95.8% [???
-These numbers are different from what is shown on Supp Fig 9] of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 9).
+These numbers are different from what is shown on Supp Fig 9; !!!the %'s shown are (left region)/(left + middle); should I take out the percentages in the figure?] of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 9).
 [???
@@
 Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlaps (Supplementary 10C, 10D).
-Furthermore, boundaries predicted on unseen annotation data exhibited similar levels of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line.
+Furthermore, boundaries predicted on unseen annotation data exhibited similar levels of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Supplementary Figure 10).
 [???
-Where is it shown?] These results indicate that *preciseTAD* pre-trained models can be successfully used to predict domain boundaries for cell lines lacking Hi-C data but for which genome annotation data is available.
+Where is it shown?; !!!left portion of figure; should I add letters?] These results indicate that *preciseTAD* pre-trained models can be successfully used to predict domain boundaries for cell lines lacking Hi-C data but for which genome annotation data is available.
 

### 2020-09-18 Manuscript/manuscript.Rmd
latest updates

--- 2020-09-17 Manuscript/manuscript.Rmd
@@
 The heuristic of $\epsilon$ is that density-reachable bases with genomic distances less than $\epsilon$ should occupy the same designated cluster.
-[???
-Add what was used as the default, refer to suppl figure]
+The default combination was set to $t=1.0$ and $\epsilon=10000$ based on our tests (Supplementary Figure 11).
 
@@
 The columns represent the holdout chromosome excluded from the training data.
-[???
-What is color gradient?
-Also, add to supp fig 4] (D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on the same cell line (blue.
+(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on the same cell line (blue.
 Arrowhead ground truth; red, Peakachu ground truth) versus across cell lines (black, dashed).
@@
 We found that 88.8% and 95.8% [???
-These numbers are different from what is shown on Supp Fig 9] of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 9).
+These numbers are different from what is shown on Supp Fig 9; !!!the %'s shown are (left region)/(left + middle); should I take out the percentages in the figure?
+???
+Still unclear, calculations don't make sense.
+TBD] of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 9).
 [???
@@
 Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlaps (Supplementary 10C, 10D).
-Furthermore, boundaries predicted on unseen annotation data exhibited similar levels of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line.
-[???
-Where is it shown?] These results indicate that *preciseTAD* pre-trained models can be successfully used to predict domain boundaries for cell lines lacking Hi-C data but for which genome annotation data is available.
+Furthermore, boundaries predicted on unseen annotation data exhibited similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Supplementary Figure 10).
+These results indicate that *preciseTAD* pre-trained models can be successfully used to predict domain boundaries for cell lines lacking Hi-C data but for which genome annotation data is available.
 
@@
 **Supplementary Figure 11.
-Normalized Enrichment levels converge for combinations on t=1.0 and $\epsilon=10000$.** Linecharts illustrating the normalized enrichment (NE) between known molecular drivers of 3D chromatin and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps) using data from GM12878 (A) and K562 (B) cell lines, chromosome 22, at 5kb resolution was used.
+Normalized Enrichment levels suggest t=1.0 and $\epsilon=10000$ as the most optimal parameters for biologically relevant *preciseTAD*-predicted boundaries.** Linecharts illustrating the normalized enrichment (NE) between CTCF, RAD21, SMC3, ZNF143 and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps).
 NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model.
-Error bars indicate standard deviation away from the mean.
+Data from GM12878 (A) and K562 (B) cell lines, chromosome 22, at 5kb resolution was used.
+Error bars indicate standard deviation from the mean.
 
@@
 
-AUC - Area Under the Curve; BA - Balance Accuracy; bp - base pair; BroadHMM - BroadHMM chromatin state data; ChIP-seq - Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI - Class Imbalance; DBSCAN - Density-Based Spatial Clustering of Applications with Noise; FN - False Negatives; FP - False Positives; Hi-C - High-throughput chromosome conformation capture technology; HM - Histone Modifications; kb - kilobase; ML - Machine Learning; OC - Overlap Counts; OP - Overlap Percents; PAM - Partitioning Around Medoids; PTBP - preciseTAD Boundary Point; PTBR - preciseTAD Boundary Region; RF - Random Forest; RFE - Recursive Feature Elimination; ROC - Receiver Operating Characteristic; ROS - Random Over-Sampling; RUS	Random Under-Sampling; SMOTE - Synthetic Minority Over-sampling Technique; TAD - Topologically Associating Domains; TFBS - Transcription Factor Binding Sites; TN - True Negatives; TP - True Positives
+AUC - Area Under the Curve; BA - Balanced Accuracy; bp - base pair; BroadHMM - BroadHMM chromatin state data; ChIP-seq - Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI - Class Imbalance; DBSCAN - Density-Based Spatial Clustering of Applications with Noise; FN - False Negatives; FP - False Positives; Hi-C - High-throughput chromosome conformation capture technology; HM - Histone Modifications; kb - kilobase; ML - Machine Learning; OC - Overlap Counts; OP - Overlap Percents; PAM - Partitioning Around Medoids; PTBP - preciseTAD Boundary Point; PTBR - preciseTAD Boundary Region; RF - Random Forest; RFE - Recursive Feature Elimination; ROC - Receiver Operating Characteristic; ROS - Random Over-Sampling; RUS	Random Under-Sampling; SMOTE - Synthetic Minority Over-sampling Technique; TAD - Topologically Associating Domains; TFBS - Transcription Factor Binding Sites; TN - True Negatives; TP - True Positives
 

### 2020-09-18 Manuscript/manuscript.Rmd
Clean percentage ???

@@
 
-The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model.
-We found that 88.8% and 95.8% [???
+The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model (Supplementary Figure 9).
+<!--We found that 88.8% and 95.8% [???
 These numbers are different from what is shown on Supp Fig 9; !!!the %'s shown are (left region)/(left + middle); should I take out the percentages in the figure?
@@
 [???
-After clarification, MD to rewrite the first two sentences, unclear] This is expected as loop boundaries (Peakachu) are more abundant, while TAD boundaries (Arrowhead) represent the higher level of the 3D chromatin organization.
+After clarification, MD to rewrite the first two sentences, unclear] -->This is expected as loop boundaries detected by Peakachu are more abundant, while comparatively wide TAD boundaries detected by Arrowhead likely represent the higher level of the 3D chromatin organization.
 Together with the results in Figure 4C, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar molecular mechanisms.

### 2020-09-18 Manuscript/manuscript.Rmd
current todo

@@
 The columns represent the holdout chromosome excluded from the training data.
-(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on the same cell line (blue.
-Arrowhead ground truth; red, Peakachu ground truth) versus across cell lines (black, dashed).
+(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on the same cell line (blue, Arrowhead ground truth; red, Peakachu ground truth) versus across cell lines (black, dashed).
 The curves represent the average sensitivities and specificities across each holdout chromosome.
-The shaded areas around each curve represent $\pm$ 1 standard deviation aways from the average.](Figures/figure4.png)
+The shaded areas around each curve represent 1 standard deviation from the average.](Figures/figure4.png)
 
@@
 We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from GM12878 cell line resulted in an average AUC=0.792 (Figure 4D).
-Suprisingly, when testing on the K562 cell line, the average AUC increased to 0.837.
-Likewise, the performance of the model trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable when evaluated using K562-specific Peakachu boundaries and genomic annotations (AUC=0.881 and 0.868, respectively).
+Surprisingly, when testing on the K562 cell line, the average AUC increased to 0.837 [???
+Wrong number?].
+Likewise, the performance of the model trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable when evaluated using K562-specific Peakachu boundaries and genomic annotations (AUC=0.881 and 0.868 [???
+Wrong number?], respectively).
 These results were consistent when training on K562 and testing on GM12878 data (Supplementary Figure 4D).
-The average ROC curves were found to be well within $\pm$ 1 standard deviation of eachother, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.
+The average ROC curves were found to be well within 1 standard deviation of each other, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.
 

### 2020-09-19 Manuscript/manuscript.Rmd
addressed ???

@@
 We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from GM12878 cell line resulted in an average AUC=0.792 (Figure 4D).
-Surprisingly, when testing on the K562 cell line, the average AUC increased to 0.837 [???
-Wrong number?].
-Likewise, the performance of the model trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable when evaluated using K562-specific Peakachu boundaries and genomic annotations (AUC=0.881 and 0.868 [???
-Wrong number?], respectively).
+Surprisingly, when testing on the K562 cell line, the average AUC increased slightly to 0.795.
+Likewise, the performance of the model trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable when evaluated using K562-specific Peakachu boundaries and genomic annotations (AUC=0.881 and 0.874, respectively).
 These results were consistent when training on K562 and testing on GM12878 data (Supplementary Figure 4D).

### 2020-09-22 Scripts_for_results/16_psuedocode.Rmd
updated main figures; changed suppfig2 to pdf

@@
 ---
-title: "psuedocode"
-author: "Spiro Stilianoudakis"
-date: "9/6/2020"
+#title: "psuedocode"
+#author: "Spiro Stilianoudakis"
+#date: "9/6/2020"
 output: pdf_document
@@
 ```
-
-# preciseTAD (CV)
 

### 2020-09-22 Manuscript/manuscript.Rmd
add detail to fig4 legend; added detail to cross cell line performance section; added new cross cell line prediction section

@@
 
-When evaluating performance across cell lines, we followed the same strategy of evaluating a model trained in one cell line on unseen data from another cell line [@schreiber2019pitfall].
-A random forest model was built using Arrowhead/Peakachu-detected boundaries ("ground truth") and genomic annotations from one cell line such that the data matrix was constructed using genomic bins from $n-1$ chromosomes.
-The test data was constructed from the binned data of the holdout chromosome with genomic annotations from the other cell line.
-The predicted boundaries were evaluated for overlap with the "ground truth" boundaries from the other cell line.
-This process was repeated for each holdout chromosome.
+When evaluating performance across cell lines, we compared the strategy of training and testing binned and annotation data from the same cell line with training and testing across cell lines.
+To do so, we built a model using binned and annotation data from $n-1$ chromosomes of the other cell line, while maintaining same testing data from the same cell line strategy (i.e.
+data from the $i^{th}$ holdout chromosome).
+As before, this process was repeated for each holdout chromosome.
 To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivities and specificities at different cutoffs, across each holdout chromosome, and reported the corresponding average area under the curve (AUC).
@@
 
-## Comparing called vs. predicted boundaries
+## Predicting boundaries across cell lines
+
+We aimed to extend the strategy of building and comparing boundary region prediction models using same cell line versus across cell line data to predict boundaries at base level resolution across cell lines.
+To do so, we applied *preciseTAD* on models built using cell line specific annotation data to predict boundaries on base level annotation data from another cell line.
+As before, this strategy was compared to applying *preciseTAD* on models and base level annotation data from the same cell line.
+
+## Evaluating called and predicted boundary precision
 
@@
 The columns represent the holdout chromosome excluded from the training data.
-(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on the same cell line (blue, Arrowhead ground truth; red, Peakachu ground truth) versus across cell lines (black, dashed).
+(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on GM12878 data (blue, Arrowhead ground truth; red, Peakachu ground truth) versus training on K562 and testing on GM12878 data (black, dashed).
 The curves represent the average sensitivities and specificities across each holdout chromosome.
@@
 We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from GM12878 cell line resulted in an average AUC=0.792 (Figure 4D).
-Surprisingly, when testing on the K562 cell line, the average AUC increased slightly to 0.795.
-Likewise, the performance of the model trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable when evaluated using K562-specific Peakachu boundaries and genomic annotations (AUC=0.881 and 0.874, respectively).
-These results were consistent when training on K562 and testing on GM12878 data (Supplementary Figure 4D).
+Surprisingly, when training on the K562 cell line and testing on GM12878, the average AUC increased slightly to 0.795.
+Likewise, the average performance of models trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable to models trained on K562-specific Peakachu boundaries and genomic annotations (Avg.
+AUC=0.881 and 0.874, respectively).
+These results were consistent when comparing training/testing strategies on K562 with training on GM12878 and testing on K562 data (Supplementary Figure 4D).
 The average ROC curves were found to be well within 1 standard deviation of each other, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.
@@
 **Supplementary Figure 4.
-SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using K562-specific histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
@@
 The columns represent the holdout chromosome excluded from the training data.
-(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on the same cell line (blue.
-Arrowhead ground truth; red, Peakachu ground truth) versus across cell lines (black, dashed).
+(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on K562 data (blue, Arrowhead ground truth; red, Peakachu ground truth) versus training on GM12878 and testing on K5628 data (black, dashed).
 The curves represent the average sensitivities and specificities across each holdout chromosome.
-The shaded areas around each curve represent $\pm$ 1 standard deviation aways from the average.
+The shaded areas around each curve represent 1 standard deviation from the average.
 

### 2020-09-22 Manuscript/manuscript.Rmd
shortened fig3 title per journal requirements

@@
 
-![**Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yield optimal TAD boundary region predictive performance for GM12878 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+![**Determining optimal data level characteristics for building TAD boundary region prediction models on GM12878.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Error bars indicate standard deviation from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
@@
 **Supplementary Figure 3.
-Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yield optimal boundary region predictive performance.** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562.
+Determining optimal data level characteristics for building TAD boundary region prediction models on K562.** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562.
 (B) Averaged balanced accuracies are compared for GM12878 and (C) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).

### 2020-09-22 Manuscript/manuscript.Rmd
shortened fig4 title

@@
 
-![**SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in GM12878 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+![**SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in GM12878.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
@@
 **Supplementary Figure 4.
-SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predicts TAD and loop boundaries in K562 cell line.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in K562.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.

### 2020-09-22 Manuscript/manuscript.Rmd
shortened table title

@@
 |        Peakachu       |       10   kb     |                        16,185                       |                          21,421                              |                267,682               |        0.14            |
-Table: Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the GM12878 cell line.
-Class imbalance is calculated as the ratio of total number of unique boundaries to the total number of genomic bins.
+Table: Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on GM12878.
 
@@
 
-**Supplementary Table 3.** Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on the K562 cell line.
-Class imbalance is calculated as the ratio of the total number of unique boundaries to the total number of genomic bins.
+**Supplementary Table 3.** Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on K562.
 

### 2020-09-22 Manuscript/manuscript.Rmd
fixed grammar
moved fig2 position
added a keywords section that needs to be filled in
Changed "intro" to "background"; moved methdos section to last; added Declaration section filled in some subsections, others still need filled in

@@
 
-# Introduction
+# Keywords
+
+# Background
 
@@
 The *preciseTAD* R package is freely available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor (submitted).
-
-# Methods
-
-## Data sources
-
-TAD and loop boundaries called by Arrowhead [@durand2016juicebox] and Peakachu [@salameh2019supervised] tools were used for training.
-The autosomal genomic coordinates in the GRCh37/hg19 human genome assembly were considered.
-Arrowhead-defined TAD boundaries were called from the GM12878 and K562 cell line Hi-C data (MAPQ>0, 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions) using the default parameters (Additional File 1).
-Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab website (Supplementary Table 1).
-Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop anchor.
-Chromosome 9 was excluded from all downstream analyses due to the sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 2).
-
-## Shifted-binning for binary classification
-
-In Hi-C, each chromosome is binned into non-overlapping regions of length *r*, typically, 5 kb and above.
-The *r* parameter defines the resolution of Hi-C data.
-Here, we designed a strategy called _shifted binning_ that partitions the genome into regions of the same length *r*, but with middle points corresponding to boundaries defined by the original binning.
-
-To create shifted binning, the first shifted bin was set to start at half of the resolution *r* and continued in intervals of length *r* until the end of the chromosome (*mod r* + *r/2*).
-The shifted bins, referred hereafter as bins for simplicity, were then defined as boundary-containing regions (*Y = 1*) if they contained a TAD (or loop) boundary, and non-boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification (Figure 1A).
-
-## Feature engineering
-
-Cell line-specific genomic annotations were used to build the predictor space.
-Bins were annotated by one of either the average signal strength of the corresponding annotation (*Peak Signal Strength*), the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*) (Figure 1B).
-A ($log_2 + 1$)-transformation of distance was used to account for the skewness of the distance distributions.
-Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin states lack signal values (Supplementary Figure 1).
-
-## Addressing class imbalance
-
-To assess the impact of class imbalance (CI), defined as the proportion of boundary regions to non-boundary regions, we evaluated three resampling techniques: *Random Over-Sampling (ROS)*, *Random Under-Sampling (RUS)*, and *Synthetic Minority Over-Sampling Technique (SMOTE)*.
-For ROS, the minority class was sampled with replacement to obtain the same number of data points in the majority class.
-For RUS, the majority class was sampled without replacement to obtain the same number of data points in the minority class.
-For SMOTE, under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the $k=5$ minority class nearest neighbors [@chawla2002smote] (implemented in the `DMwR` v.0.4.1 R package).
-We restricted the SMOTE algorithm to 100% over-sampling and 200% under-sampling, to create perfectly balanced classes.
-
-## Establishing optimal data level characteristics for TAD boundary region prediction
-
-Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, feature engineering procedures, and resampling techniques.
-Following recommendations to evaluate the model on unseen data [@schreiber2019pitfall], a *holdout chromosome* technique was used for estimating model's performance.
-The $i^{th}$ holdout chromosome was identified and a data matrix, $A_{N \times (p+1)}$, was constructed by combining the binned genome from the remaining chromosomes ($1,2,\cdots, i-1,i+1,\cdots,21,22$), where $N=[n_{1} n_{2} \cdots n_{21} n_{22}]'$ and $n_{k}$ is the length of chromosome *k* after being binned into non-overlapping regions of resolution *r*, such that $k \ne i$.
-$p$, the number of annotations, together with the response vector, **Y**, defined the column-wise dimension of the matrix $A$.
-Re-sampling was then performed on $A$, and an RF classifier was trained using 3-fold cross-validation to tune for the number of annotations to consider at each node (*mtry*).
-The number of trees (*ntree*) that were aggregated for each RF model was set to 500.
-The minimum number of observations per root node (*nodesize*) was set to 0.1% of the rows in the data.
-The binned data for the holdout chromosome $i$ was reserved for testing.
-Models were evaluated using Balanced Accuracy (BA), defined as the average of sensitivity and specificity:
-
-$$BA = \dfrac{1}{2}\left( sensitivity + specificity \right) = \dfrac{1}{2}\left( \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} \right)$$
-
-where TP refers to the number of bins correctly identified as containing a boundary (true positives), FP refers to the number of bins incorrectly identified as containing a boundary (false positives), TN refers to the number of bins correctly identified as not containing a boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a boundary (false negatives).
-Each of these quantities is obtained from the confusion matrix created by validating the model on the test data.
-The process was repeated for each $i^{th}$ holdout chromosome, and performances were aggregated using mean and standard deviation.
-
-## Feature selection and predictive importance
-
-Many genomic annotations, notably architectural proteins, tend to exhibit an extensive pattern of colocalization (correlation) [@van2014insulator].
-To suitably reduce the predictor space and improve computational efficiency, while maintaining optimal performance, we implemented recursive feature elimination (RFE).
-We estimated the near-optimal number of necessary features, ranging from 2 to the maximum number of features incremented by the power of 2.
-We then aggregated the predictive importance of the union of the optimal set of features across holdout chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top-ranked annotations for predicting boundary regions.
-
-## Evaluating performance across cell lines
-
-When evaluating performance across cell lines, we compared the strategy of training and testing binned and annotation data from the same cell line with training and testing across cell lines.
-To do so, we built a model using binned and annotation data from $n-1$ chromosomes of the other cell line, while maintaining same testing data from the same cell line strategy (i.e.
-data from the $i^{th}$ holdout chromosome).
-As before, this process was repeated for each holdout chromosome.
-To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivities and specificities at different cutoffs, across each holdout chromosome, and reported the corresponding average area under the curve (AUC).
-
-## Boundary prediction at the base-level resolution using *preciseTAD*
-
-To investigate whether we could alleviate the resolution limitations of conventional domain calling tools, we developed *preciseTAD*.
-This algorithm leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution (Supplementary Figure 2).
-
-A random forest model $(M)$ was built on the optimal combination of predictor type (predictor space), resampling technique (class balancing correction), and top-ranked annotations (most informative genomic elements) for a set of binned chromosomes $\{k | k \ne i \}$ <!--, to maximally accurately predict boundaries at the _Hi-C resolution level_-->.
-To precisely identify boundary locations, we first constructed a _base-level resolution_ predictor space for the chromosome *i*, $A_{n \times p}$, where $n$ is the length of chromosome $i$ and $p$ is the optimal number of annotations.
-We then evaluate $M$ on the base-level predictor space to extract the probability vector, $\pi_{n_{i}}$, denoting each base's probability of being a boundary.
-Here, $n_{i}$ represents the length of chromosome *i*.
-A threshold $t$ specifies the probability at which a base with $\pi_{n_{i}} \ge t$ is designated as a potential boundary (the default $t=1$).
-Next, density-based spatial clustering of applications with noise (DBSCAN; version 1.1-5) is applied to the matrix of pairwise genomic distances between boundary-annotated bases, $D$.
-The minimum and maximum coordinates of each cluster, $k$, of spatially colocalized bases were termed *preciseTAD boundary regions* (PTBR).
-To precisely identify a single base among each PTBR, *preciseTAD* implements partitioning around medoids (PAM) on the distance matrix, $D_{k}$, derived from each cluster.
-The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative base coordinate within each clustered PTBR.
-
-The DBSCAN algorithm has two parameters, *MinPts* and *eps* ($\epsilon$).
-The *MinPts* parameter was set to the recommended value of 3, representing $1+dim(data)$ [@hahsler2019dbscan].
-To decide on the optimal value of $t$ and $\epsilon$ in *preciseTAD*, we considered the normalized enrichment $NE$ of flanked predicted boundaries, defined as
-
-$$NE = \dfrac{1}{p} \left[ \Sigma_{s=1}^{p} \left[ \dfrac{1}{b} \Sigma_{k=1}^{b} e_{ks} \times c_{k} \right] \right]$$
-
-where $e_{ks} = \textbf{I}\{ r_{s} \in (b_{k}-f, b_{k}+f)\}$ is the number of elemental regions $r$ of predictor $p$ that overlap with each flanked boundary.
-We evaluated $NE$ for combinations of $t=\{0.975, 0.99, 1.0 \}$ and $\epsilon = \{1000, 5000, 10000, 15000, 20000, 25000 \}$.
-The heuristic of $\epsilon$ is that density-reachable bases with genomic distances less than $\epsilon$ should occupy the same designated cluster.
-The default combination was set to $t=1.0$ and $\epsilon=10000$ based on our tests (Supplementary Figure 11).
-
-## Predicting boundaries across cell lines
-
-We aimed to extend the strategy of building and comparing boundary region prediction models using same cell line versus across cell line data to predict boundaries at base level resolution across cell lines.
-To do so, we applied *preciseTAD* on models built using cell line specific annotation data to predict boundaries on base level annotation data from another cell line.
-As before, this strategy was compared to applying *preciseTAD* on models and base level annotation data from the same cell line.
-
-## Evaluating called and predicted boundary precision
-
-We assessed the biological significance of our predicted boundaries by their association with the signal of CTCF, RAD21, SMC3, and ZNF143 using *deepTools* (version 2.0) [@ramirez2016deeptools] (*computeMatrix*, *plotProfile*, and *plotHeatmap* tools).
-Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum tests.
-Furthermore, we compared the overlap between predicted and called boundaries in GM12878 and K562 cell lines.
-Boundaries were first flanked by resolution, *r*, and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0).
-Overlaps were further quantified using the Jaccard index defined as
-
-$$J_{(A,B)} = \dfrac{A \cap B}{A \cup B}$$
-
-where A and B represent genomic regions created by flanked called and predicted boundaries.
-That is, between cell lines, the number of overlapping flanked boundaries divided by the total number of flanked boundaries.
-Wilcoxon Rank-Sum tests were used to compare chromosome-specific Jaccard indices across cell lines, between *preciseTAD* boundaries and both Arrowhead and Peakachu boundaries, respectively.
-All statistical analyses were performed in R version 4.0.1.
-The significance level was set to 0.05 for all statistical tests.
-
-<!--using the `EnrichedHeatmap` R package (version 1.14.0) [@gu2018enrichedheatmap].
-For each boundary (both called and predicted), a 5000 bp flank was created on either side.
-The flanking was broken up into 50 bp segments, for a total of 100 windows on both sides of a given boundary.
-A coverage value was generated for each window with respect to a given ChIP-seq annotation, as the mean signal averaged by the width of the window, denoted by,
-
-$$v_{c} = \dfrac{\Sigma_{j}^{m} \Sigma_{i}^{n}x_{ij}w_{ij}}{L}$$
-
-where $x_{ij}$ is the total number of bases of annotation $i$ in window $j$ and $w_{ij}$ is the number of bases that overlap between annotation $i$ and window $j$.
-The denominator, $L$, is the width of the windows (here, $L=50$).
-The rows of the heatmaps are ordered by enriched scores.
-The enriched scores are calculated as the sum of coverage values weighted by the distance to the flanked boundary, denoted by
-
-$$s_{e} = \Sigma_{d=1}^{n_{1}}\left(\dfrac{x_{1d}* d}{n_{1}} \right) + \Sigma_{u=1}^{n_{2}}\left(\dfrac{x_{2u}* (n_{2} - u + 1)}{n_{2}} \right)$$
-where $n_{1}$ and $n_{2}$ represent the number of downstream and upstream coverage values to sum over. Here, $n_{1}=n_{2}=100$.-->
 
@@
 
-![**A machine learning framework for building domain boundary region prediction models.** Step 1 employs a range of feature engineering techniques to define the predictor matrix $A_{N \times (p)}$, where $N$ is the number of genomic bins, $p$ is the number of genomic annotations, $i$ is a holdout chromosome.
-The response vector $Y_N$ is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$).
-Step 2 reserves the predictor-response matrix for the holdout chromosome $i$ as the test data.
-Step 3 applies a resampling technique to the training data to address the class imbalance.
-Step 4 trains the random forest model and performs 3-fold cross-validation to tune the mtry parameter.
-Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and to evaluate model performance using balanced accuracy (BA).](Figures/figure2.png)
-
 A total of 77 cell line-specific genomic annotations were used to build the predictor space.
@@
 These strategies allowed us to select the best performing model in an unbiased manner.
+
+![**A machine learning framework for building domain boundary region prediction models.** Step 1 employs a range of feature engineering techniques to define the predictor matrix $A_{N \times (p)}$, where $N$ is the number of genomic bins, $p$ is the number of genomic annotations, $i$ is a holdout chromosome.
+The response vector $Y_N$ is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$).
+Step 2 reserves the predictor-response matrix for the holdout chromosome $i$ as the test data.
+Step 3 applies a resampling technique to the training data to address the class imbalance.
+Step 4 trains the random forest model and performs 3-fold cross-validation to tune the mtry parameter.
+Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and to evaluate model performance using balanced accuracy (BA).](Figures/figure2.png)
 
@@
 
+# Conclusion
+
 In summary, we demonstrate that domain boundary prediction is a multi-faceted problem requiring consideration of multiple statistical and biological properties of genomic data.
@@
 We hope that *preciseTAD* will serve as an efficient and easy-to-use tool to further explore the genome's 3D organization.
+
+# Methods
+
+## Data sources
+
+TAD and loop boundaries called by Arrowhead [@durand2016juicebox] and Peakachu [@salameh2019supervised] tools were used for training.
+The autosomal genomic coordinates in the GRCh37/hg19 human genome assembly were considered.
+Arrowhead-defined TAD boundaries were called from the GM12878 and K562 cell line Hi-C data (MAPQ>0, 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions) using the default parameters (Additional File 1).
+Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab website (Supplementary Table 1).
+Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop anchor.
+Chromosome 9 was excluded from all downstream analyses due to the sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
+Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 2).
+
+## Shifted-binning for binary classification
+
+In Hi-C, each chromosome is binned into non-overlapping regions of length *r*, typically, 5 kb and above.
+The *r* parameter defines the resolution of Hi-C data.
+Here, we designed a strategy called _shifted binning_ that partitions the genome into regions of the same length *r*, but with middle points corresponding to boundaries defined by the original binning.
+
+To create shifted binning, the first shifted bin was set to start at half of the resolution *r* and continued in intervals of length *r* until the end of the chromosome (*mod r* + *r/2*).
+The shifted bins, referred hereafter as bins for simplicity, were then defined as boundary-containing regions (*Y = 1*) if they contained a TAD (or loop) boundary, and non-boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification (Figure 1A).
+
+## Feature engineering
+
+Cell line-specific genomic annotations were used to build the predictor space.
+Bins were annotated by one of either the average signal strength of the corresponding annotation (*Peak Signal Strength*), the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*) (Figure 1B).
+A ($log_2 + 1$)-transformation of distance was used to account for the skewness of the distance distributions.
+Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin states lack signal values (Supplementary Figure 1).
+
+## Addressing class imbalance
+
+To assess the impact of class imbalance (CI), defined as the proportion of boundary regions to non-boundary regions, we evaluated three resampling techniques: *Random Over-Sampling (ROS)*, *Random Under-Sampling (RUS)*, and *Synthetic Minority Over-Sampling Technique (SMOTE)*.
+For ROS, the minority class was sampled with replacement to obtain the same number of data points in the majority class.
+For RUS, the majority class was sampled without replacement to obtain the same number of data points in the minority class.
+For SMOTE, under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the $k=5$ minority class nearest neighbors [@chawla2002smote] (implemented in the `DMwR` v.0.4.1 R package).
+We restricted the SMOTE algorithm to 100% over-sampling and 200% under-sampling, to create perfectly balanced classes.
+
+## Establishing optimal data level characteristics for TAD boundary region prediction
+
+Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, feature engineering procedures, and resampling techniques.
+Following recommendations to evaluate the model on unseen data [@schreiber2019pitfall], a *holdout chromosome* technique was used for estimating model's performance.
+The $i^{th}$ holdout chromosome was identified and a data matrix, $A_{N \times (p+1)}$, was constructed by combining the binned genome from the remaining chromosomes ($1,2,\cdots, i-1,i+1,\cdots,21,22$), where $N=[n_{1} n_{2} \cdots n_{21} n_{22}]'$ and $n_{k}$ is the length of chromosome *k* after being binned into non-overlapping regions of resolution *r*, such that $k \ne i$.
+$p$, the number of annotations, together with the response vector, **Y**, defined the column-wise dimension of the matrix $A$.
+Re-sampling was then performed on $A$, and an RF classifier was trained using 3-fold cross-validation to tune for the number of annotations to consider at each node (*mtry*).
+The number of trees (*ntree*) that were aggregated for each RF model was set to 500.
+The minimum number of observations per root node (*nodesize*) was set to 0.1% of the rows in the data.
+The binned data for the holdout chromosome $i$ was reserved for testing.
+Models were evaluated using Balanced Accuracy (BA), defined as the average of sensitivity and specificity:
+
+$$BA = \dfrac{1}{2}\left( sensitivity + specificity \right) = \dfrac{1}{2}\left( \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} \right)$$
+
+where TP refers to the number of bins correctly identified as containing a boundary (true positives), FP refers to the number of bins incorrectly identified as containing a boundary (false positives), TN refers to the number of bins correctly identified as not containing a boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a boundary (false negatives).
+Each of these quantities is obtained from the confusion matrix created by validating the model on the test data.
+The process was repeated for each $i^{th}$ holdout chromosome, and performances were aggregated using mean and standard deviation.
+
+## Feature selection and predictive importance
+
+Many genomic annotations, notably architectural proteins, tend to exhibit an extensive pattern of colocalization (correlation) [@van2014insulator].
+To suitably reduce the predictor space and improve computational efficiency, while maintaining optimal performance, we implemented recursive feature elimination (RFE).
+We estimated the near-optimal number of necessary features, ranging from 2 to the maximum number of features incremented by the power of 2.
+We then aggregated the predictive importance of the union of the optimal set of features across holdout chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top-ranked annotations for predicting boundary regions.
+
+## Evaluating performance across cell lines
+
+When evaluating performance across cell lines, we compared the strategy of training and testing binned and annotation data from the same cell line with training and testing across cell lines.
+To do so, we built a model using binned and annotation data from $n-1$ chromosomes of the other cell line, while maintaining same testing data from the same cell line strategy (i.e.
+data from the $i^{th}$ holdout chromosome).
+As before, this process was repeated for each holdout chromosome.
+To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivities and specificities at different cutoffs, across each holdout chromosome, and reported the corresponding average area under the curve (AUC).
+
+## Boundary prediction at the base-level resolution using *preciseTAD*
+
+To investigate whether we could alleviate the resolution limitations of conventional domain calling tools, we developed *preciseTAD*.
+This algorithm leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution (Supplementary Figure 2).
+
+A random forest model $(M)$ was built on the optimal combination of predictor type (predictor space), resampling technique (class balancing correction), and top-ranked annotations (most informative genomic elements) for a set of binned chromosomes $\{k | k \ne i \}$ <!--, to maximally accurately predict boundaries at the _Hi-C resolution level_-->.
+To precisely identify boundary locations, we first constructed a _base-level resolution_ predictor space for the chromosome *i*, $A_{n \times p}$, where $n$ is the length of chromosome $i$ and $p$ is the optimal number of annotations.
+We then evaluate $M$ on the base-level predictor space to extract the probability vector, $\pi_{n_{i}}$, denoting each base's probability of being a boundary.
+Here, $n_{i}$ represents the length of chromosome *i*.
+A threshold $t$ specifies the probability at which a base with $\pi_{n_{i}} \ge t$ is designated as a potential boundary (the default $t=1$).
+Next, density-based spatial clustering of applications with noise (DBSCAN; version 1.1-5) is applied to the matrix of pairwise genomic distances between boundary-annotated bases, $D$.
+The minimum and maximum coordinates of each cluster, $k$, of spatially colocalized bases were termed *preciseTAD boundary regions* (PTBR).
+To precisely identify a single base among each PTBR, *preciseTAD* implements partitioning around medoids (PAM) on the distance matrix, $D_{k}$, derived from each cluster.
+The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative base coordinate within each clustered PTBR.
+
+The DBSCAN algorithm has two parameters, *MinPts* and *eps* ($\epsilon$).
+The *MinPts* parameter was set to the recommended value of 3, representing $1+dim(data)$ [@hahsler2019dbscan].
+To decide on the optimal value of $t$ and $\epsilon$ in *preciseTAD*, we considered the normalized enrichment $NE$ of flanked predicted boundaries, defined as
+
+$$NE = \dfrac{1}{p} \left[ \Sigma_{s=1}^{p} \left[ \dfrac{1}{b} \Sigma_{k=1}^{b} e_{ks} \times c_{k} \right] \right]$$
+
+where $e_{ks} = \textbf{I}\{ r_{s} \in (b_{k}-f, b_{k}+f)\}$ is the number of elemental regions $r$ of predictor $p$ that overlap with each flanked boundary.
+We evaluated $NE$ for combinations of $t=\{0.975, 0.99, 1.0 \}$ and $\epsilon = \{1000, 5000, 10000, 15000, 20000, 25000 \}$.
+The heuristic of $\epsilon$ is that density-reachable bases with genomic distances less than $\epsilon$ should occupy the same designated cluster.
+The default combination was set to $t=1.0$ and $\epsilon=10000$ based on our tests (Supplementary Figure 11).
+
+## Predicting boundaries across cell lines
+
+We aimed to extend the strategy of building and comparing boundary region prediction models using same cell line versus across cell line data to predict boundaries at base level resolution across cell lines.
+To do so, we applied *preciseTAD* on models built using cell line specific annotation data to predict boundaries on base level annotation data from another cell line.
+As before, this strategy was compared to applying *preciseTAD* on models and base level annotation data from the same cell line.
+
+## Evaluating called and predicted boundary precision
+
+We assessed the biological significance of our predicted boundaries by their association with the signal of CTCF, RAD21, SMC3, and ZNF143 using *deepTools* (version 2.0) [@ramirez2016deeptools] (*computeMatrix*, *plotProfile*, and *plotHeatmap* tools).
+Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum tests.
+Furthermore, we compared the overlap between predicted and called boundaries in GM12878 and K562 cell lines.
+Boundaries were first flanked by resolution, *r*, and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0).
+Overlaps were further quantified using the Jaccard index defined as
+
+$$J_{(A,B)} = \dfrac{A \cap B}{A \cup B}$$
+
+where A and B represent genomic regions created by flanked called and predicted boundaries.
+That is, between cell lines, the number of overlapping flanked boundaries divided by the total number of flanked boundaries.
+Wilcoxon Rank-Sum tests were used to compare chromosome-specific Jaccard indices across cell lines, between *preciseTAD* boundaries and both Arrowhead and Peakachu boundaries, respectively.
+All statistical analyses were performed in R version 4.0.1.
+The significance level was set to 0.05 for all statistical tests.
+
+<!--using the `EnrichedHeatmap` R package (version 1.14.0) [@gu2018enrichedheatmap].
+For each boundary (both called and predicted), a 5000 bp flank was created on either side.
+The flanking was broken up into 50 bp segments, for a total of 100 windows on both sides of a given boundary.
+A coverage value was generated for each window with respect to a given ChIP-seq annotation, as the mean signal averaged by the width of the window, denoted by,
+
+$$v_{c} = \dfrac{\Sigma_{j}^{m} \Sigma_{i}^{n}x_{ij}w_{ij}}{L}$$
+
+where $x_{ij}$ is the total number of bases of annotation $i$ in window $j$ and $w_{ij}$ is the number of bases that overlap between annotation $i$ and window $j$.
+The denominator, $L$, is the width of the windows (here, $L=50$).
+The rows of the heatmaps are ordered by enriched scores.
+The enriched scores are calculated as the sum of coverage values weighted by the distance to the flanked boundary, denoted by
+
+$$s_{e} = \Sigma_{d=1}^{n_{1}}\left(\dfrac{x_{1d}* d}{n_{1}} \right) + \Sigma_{u=1}^{n_{2}}\left(\dfrac{x_{2u}* (n_{2} - u + 1)}{n_{2}} \right)$$
+where $n_{1}$ and $n_{2}$ represent the number of downstream and upstream coverage values to sum over. Here, $n_{1}=n_{2}=100$.-->
 
@@
 # Supplementary Legends
-
-**Additional File 1**.
-An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions.
-An example of deepTools commands to generate plotProfiels and plotHeatmaps is also provided.
 
@@
 
+# Additional File Legends
+
+**Additional File 1**.
+An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions.
+An example of deepTools commands to generate plotProfiles and plotHeatmaps is also provided.
+
 # Abbreviations
@@
 
-# Acknowledgements
+# Declarations
 
-_Conflict of Interest._ None.
+## Ethics approval and consent to participate
 
-<!-- # Funding -->
+Not applicable
+
+## Consent for publication
+
+Not applicable
+
+## Availability of data and materials
+
+All data generated or analysed during this study are included in this published article [and its supplementary information files].
+
+## Competing interests
+
+Not applicable
+
+## Funding
+
+## Authors' contributions
+
+## Acknowledgements
+
+## Authors' information (optional)
 

### 2020-09-23 Manuscript/manuscript.Rmd
Polish Evaluating performance across cell lines

@@
 
-When evaluating performance across cell lines, we compared the strategy of training and testing binned and annotation data from the same cell line with training and testing across cell lines.
-To do so, we built a model using binned and annotation data from $n-1$ chromosomes of the other cell line, while maintaining same testing data from the same cell line strategy (i.e.
-data from the $i^{th}$ holdout chromosome).
-As before, this process was repeated for each holdout chromosome.
+We used the same holdout chromosome strategy to evaluate a model trained in one cell line on unseen data from another cell line [@schreiber2019pitfall].
+Given two cell lines, GM12878 and K562, we first evaluated the performance of cell line-specific models.
+That is, models trained on cell line-specific data from $n-1$ chromosomes were evaluated on the $i^{th}$ holdout chromosome data from the same cell line.
+Second, we evaluated models trained on cell line-specific data from $n-1$ chromosomes using the $i^{th}$ holdout chromosome data from a different cell line.
+That is, models trained using K562 cell line-specific data were evaluated on unseen chromosome data from GM12878 cell line.
+This process was repeated for each holdout chromosome.
 To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivities and specificities at different cutoffs, across each holdout chromosome, and reported the corresponding average area under the curve (AUC).

### 2020-09-23 Manuscript/manuscript.Rmd
Removing Predicting boundaries across cell lines
Polish Training in one cell line accurately predicts boundary regions in other cell lines

@@
 We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from GM12878 cell line resulted in an average AUC=0.792 (Figure 4D).
-Surprisingly, when training on the K562 cell line and testing on GM12878, the average AUC increased slightly to 0.795.
+Interestingly, when training on the K562 cell line and testing on GM12878, the average AUC increased slightly to 0.795.
 Likewise, the average performance of models trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable to models trained on K562-specific Peakachu boundaries and genomic annotations (Avg.
@@
 These results were consistent when comparing training/testing strategies on K562 with training on GM12878 and testing on K562 data (Supplementary Figure 4D).
-The average ROC curves were found to be well within 1 standard deviation of each other, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.
+The average ROC curves were found to be within 1 standard deviation of each other, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.
 
@@
 
+<!--
 ## Predicting boundaries across cell lines
@@
 As before, this strategy was compared to applying *preciseTAD* on models and base level annotation data from the same cell line.
+-->
 

### 2020-09-25 Manuscript/manuscript.Rmd
Add 100-words abstract

@@
 
+<!-- 100 words abstract start -->
+The low resolution of high-throughput chromosome conformation capture data limits the precise mapping of boundaries of topologically associating domains and chromatin loops.
+We developed preciseTAD, an optimized random forest model trained on high-resolution genome annotation data (e.g., CTCF ChIP-seq) to predicts the location of domain boundaries at base-level resolution.
+Distance between boundaries and annotations, random under-sampling, and transcription factor binding sites resulted in best model performance.
+preciseTAD boundaries were more enriched for CTCF, RAD21, SMC3, and ZNF143, conserved across cell lines.
+Using genome annotations, the pre-trained models can detect boundaries in cells without Hi-C data.
+preciseTAD is available at https://bioconductor.org/packages/preciseTAD
+<!-- 100 words abstract end -->
+
+<!--
 High-throughput chromosome conformation capture technology (Hi-C) revealed extensive DNA looping and folding into discrete 3D domains.
@@
 The precise identification of domain boundaries will improve our understanding of how genomic regulators are shaping the 3D structure of the genome.
-<!-- *preciseTAD* R package is available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor (submitted).
+*preciseTAD* R package is available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor (submitted).
 -->

### 2020-09-26 BMC_Genome_Biology_submission/additional_files/additional_file_legends.Rmd
submission folder initial commit

--- 2020-09-23 Manuscript/manuscript.Rmd
@@
 title: "preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution"
-csl: styles.ref/genomebiology.csl
+subtitle: "Additional File Legends"
 output:
-  pdf_document: 
-    extra_dependencies: ["float"]
   word_document:
-    reference_docx: styles.doc/NIH_grant_style.docx
-bibliography: References/references.bib
+    toc: yes
 ---
 
-```{r echo=FALSE}
-knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
 ```
 
-Spiro C. Stilianoudakis^1^ (stilianoudasc@mymail.vcu.edu), Mikhail G. Dozmorov^1\*^ (mikhail.dozmorov@vcuhealth.org)
+# Additional File 1
 
-^1^ Dept. of Biostatistics, Virginia Commonwealth University, Richmond, VA, 23298, USA  
-^\*^ To whom correspondence should be addressed: Virginia Commonwealth University, Richmond, VA, 23298, 804-827-2055, mikhail.dozmorov@vcuhealth.org
-
-# Abstract
-
-High-throughput chromosome conformation capture technology (Hi-C) revealed extensive DNA looping and folding into discrete 3D domains.
-These include Topologically Associating Domains (TADs) and chromatin loops, the 3D domains critical for cellular processes like gene regulation and cell differentiation.
-The relatively low resolution of Hi-C data (regions of several kilobases in size) prevents precise mapping of domain boundaries.
-However, the high resolution of genomic annotations associated with boundaries, such as CTCF and members of cohesin complex, suggests they can inform the precise location of domain boundaries.
-Several methods attempted to leverage genome annotation data for predicting domain boundaries; however, they overlooked key characteristics of the data, such as spatial associations between an annotation and a boundary, and a much smaller number of boundaries than the rest of the genome (class imbalance).
-
-We developed *preciseTAD*, an optimized random forest model to improve the location of domain boundaries.
-Trained on high-resolution genome annotation data and boundaries from low-resolution Hi-C data, the model predicts the location of boundaries at base-level resolution.
-We investigated several feature engineering and resampling techniques (random over- and undersampling, Synthetic Minority Over-sampling TEchnique (SMOTE)) to select the most optimal data characteristics and address class imbalance.
-Density-based clustering (DBSCAN) and partitioning around medoids (PAM) techniques were used to identify the precise location of boundary regions and summit points.
-We benchmarked our method against the Arrowhead domain caller and a novel chromatin loop prediction algorithm, Peakachu, on the two most annotated cell lines.
-
-We found that spatial relationship (distance in the linear genome) between boundaries and annotations has the most predictive power.
-Random under-sampling significantly improved model performance.
-Transcription factor binding sites outperformed other genome annotation types.
-Boundaries predicted by *preciseTAD* were more enriched for CTCF, RAD21, SMC3, and ZNF143 signal and more conserved across cell lines, highlighting their higher biological significance.
-The model pre-trained in one cell line performs well in another cell line.
-Using cell line-specific genomic annotations, the pre-trained models enable the detection of domain boundaries in cells without Hi-C data.
-
-Our study implements the method and the pre-trained models for precise domain boundary prediction using genome annotation data.
-The precise identification of domain boundaries will improve our understanding of how genomic regulators are shaping the 3D structure of the genome.
-<!-- *preciseTAD* R package is available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor (submitted).
--->
-
-# Keywords
-
-# Background
-
-The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of the 3-dimensional (3D) structure of the human genome such as chromatin loops [@rao20143d], Topologically Associating Domains (TADs) [@nora2012spatial;@dixon2012topological], and A/B compartments [@lieberman2009comprehensive].
-At the kilobase scale, chromatin loops connect gene promoters with distal enhancers, thereby regulating gene expression [@Lupianez:2015aa; @Franke:2016aa].
-At the megabase scale, TADs represent regions on the linear genome, that are highly self-interacting.
-<!--Emerging evidence has linked TADs to critical roles in cell dynamics and cell differentiation.
-Studies have shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].--> Disruption of boundaries demarcating TADs and loops promotes cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@lupianez2016breaking;@Sun:2018aa;@Meaburn:2007aa].
-Identifying the precise location of TAD and chromatin loop boundaries remains a top priority in our goal to fully understand the functionality of the human genome.
-
-Several methods have been proposed to identify genomic coordinates of TADs (reviewed in [@Zufferey:2018aa; @forcato2017comparison]), and chromatin loops [@rao20143d; @Ay:2014aa; @Heinz:2010aa; @salameh2019supervised].
-However, a key limitation of them is that they depend on Hi-C data *resolution*.
-Resolution refers to the size of genomic regions (bins) used to segment the linear genome [@li2019comparison].
-Lower resolutions contribute to larger bin sizes, which leads to increased uncertainty in the location of boundaries.
-Due to high sequencing costs, most available Hi-C datasets have relatively low resolution, ranging from 25 kb to 100 kb.
-While these low-resolution Hi-C datasets can be used to probe higher-order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define TAD and loop boundaries [@fudenberg2016formation].
-Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth [@schmitt2016genome], obtaining high resolution remains difficult.
-
-Another limitation among domain callers is that they disregard prior knowledge about functional genomic annotations associated with TAD and loop boundaries, referred hereafter as domain boundaries.
-The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been identified as components of the loop extrusion model<!--, whereby DNA is extruded through cohesin rings forming chromatin loops--> [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
-Furthermore, distinct patterns of histone modifications have also been shown to be present at boundaries<!--including H3K36me3--> [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
-These genomic annotations are obtained using chromatin immunoprecipitation followed by high-throughput DNA sequencing (ChIP-seq).
-The resolution of ChIP-seq experiments is typically on the order of tens to hundreds of bases [@mendoza2009genome], well below the resolution of Hi-C data (tens of kilobases; 750 bp is the highest resolution of Hi-C data to date [@bonev2017multiscale]).
-Therefore, leveraging precisely mapped genomic annotations in a supervised machine learning framework enables more precise prediction of the locations of domain boundaries.
-
-We present *preciseTAD*, an optimally tuned machine learning framework for precise identification of domain boundaries using genome annotation data.
-Our method utilizes the random forest (RF) algorithm trained on high-resolution chromatin state (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) data to predict low-resolution boundaries.
-We introduce a systematic pipeline for building the optimal boundary prediction classifier.
-We found that spatial associations (linear distance) between boundaries and annotations perform best, transcription factor binding sites improve prediction accuracy, and a simple random undersampling technique effectively addresses the negative effect of class imbalance.
-Translated from Hi-C data resolution level to base level (annotating each base and predicting its boundary probability), *preciseTAD* employs density-based clustering (DBSCAN) and partitioning around medoids (PAM) to detect genome annotation-guided boundary regions and points at a base-level resolution.
-This approach circumvents resolution restrictions of Hi-C data, allowing for the precise detection of biologically meaningful boundaries.
-We demonstrate that *preciseTAD* predictions are more enriched for known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143.
-Further, we show that *preciseTAD*-detected boundaries are more conserved across cell lines, and the model trained in one cell line can predict boundaries in another cell line.
-This improved precision in the domain boundary location can provide insight into the association between genomic regulators and the 3D genome organization.
-The *preciseTAD* R package is freely available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor (submitted).
-
-# Results
-
-## Developing an ML framework for optimal TAD boundary prediction
-
-We developed a machine learning (ML) framework for determining the optimal set of data level characteristics to predict boundaries of Topologically Associating Domains (TADs) and chromatin loops, collectively referred to as domain boundaries.
-We chose the random forest (RF) algorithm as our binary classification tool.
-The reason for it is two-fold: (1) to devise a tunable prediction rule in a supervised learning framework that is both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors [@boulesteix2012overview].
-We used Arrowhead-called TAD boundaries [@durand2016juicer] and published Peakachu-predicted loop boundaries [@salameh2019supervised] as ground truth.
-Data from GM12878 and K565 cell lines at 5-100kb resolution (Arrowhead) and 10kb resolution (Peakachu) were used (Supplementary Table 1).
-We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base resolution from cell line-specific genome annotation data.
-
-![**Resolution-specific data construction and feature engineering for random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals using *shifted binning* (see Methods).
-The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD (or loop) boundary.
-(B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png)
-
-Boundary regions were defined as genomic bins containing a called boundary ($Y = 1$), while non-boundary regions were defined as bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
-The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 3).
-The number of non-boundary regions highly outnumbered boundary regions.
-Such a disproportional presence of examples in one class is known as a "class imbalance" problem that negatively affects predictive modeling [@prati2011survey; @wei2013role].
-To address the class imbalance, we evaluated the effect of three resampling techniques.
-*Random over-sampling* (ROS) was defined as sampling with replacement from the minority class (boundary regions).
-*Random under-sampling* (RUS) was defined as sampling with replacement from the majority class (non-boundary regions).
-Lastly, we tested *Synthetic minority over-sampling technique* (SMOTE), which is a combination of both random over- and under-sampling to create balanced classes [@chawla2002smote] (see Methods).
-
-|          Tool         |     Resolution    |     Total number of called TADs/chromatin loops    |     Total number of unique TAD/chromatin loop boundaries    |     Total number of genomic bins    |     Class imbalance    |
-|:---------------------:|:-----------------:|:--------------------------------------------------:|:-----------------------------------------------------------:|:-----------------------------------:|:----------------------:|
-|        Arrowhead      |       5   kb      |                         8,052                       |                             15,468                           |                535,363               |           0.03         |
-|     Arrowhead         |       10   kb     |                         7,676                       |                             14,253                           |                267,682               |           0.05         |
-|     Arrowhead         |       25   kb     |                         4,670                       |                             8,363                            |                107,073               |           0.08         |
-|     Arrowhead         |       50   kb     |                         2,349                       |                             4,224                            |                 53,537               |           0.08         |
-|     Arrowhead         |      100   kb     |                         1,031                       |                             1,883                            |                 26,768               |           0.07         |
-|        Peakachu       |       10   kb     |                        16,185                       |                          21,421                              |                267,682               |        0.14            |
-Table: Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on GM12878.
-
-A total of 77 cell line-specific genomic annotations were used to build the predictor space.
-These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 2).
-Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
-These included signal strength association (Signal), direct (OC), proportional (OP), and spatial ($log_2 + 1$ Distance) relationships (see Methods, Supplementary Figure 1).
-
-In total, we considered combinations of data from two cell lines *L = {GM12878, K562}*, five resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor space *P = {Signal, OC, OP, Distance}*, and three re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
-Once the model inputs were established, a random forest classifier was trained on $n-1$ autosomal chromosomes, while reserving the $i^{th}$ chromosome for testing.
-Three-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed at 500 and at 0.1% of the rows in the training data, respectively.
-Model performance was evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (see Methods).
-These strategies allowed us to select the best performing model in an unbiased manner.
-
-![**A machine learning framework for building domain boundary region prediction models.** Step 1 employs a range of feature engineering techniques to define the predictor matrix $A_{N \times (p)}$, where $N$ is the number of genomic bins, $p$ is the number of genomic annotations, $i$ is a holdout chromosome.
-The response vector $Y_N$ is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$).
-Step 2 reserves the predictor-response matrix for the holdout chromosome $i$ as the test data.
-Step 3 applies a resampling technique to the training data to address the class imbalance.
-Step 4 trains the random forest model and performs 3-fold cross-validation to tune the mtry parameter.
-Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and to evaluate model performance using balanced accuracy (BA).](Figures/figure2.png)
-
-## Random under-sampling, distance-based predictors, and high-resolution Hi-C data provide optimal performance for boundary prediction
-
-Expectedly, when using data with class imbalance present, that is, no resampling, the models exhibited low balanced accuracies, with minimal variability among different resolutions (Figure 3).
-Similarly, poor performances were found when using ROS.
-However, RUS and SMOTE re-sampling led to a drastic improvement in performance, especially at higher resolutions.
-We found that RUS marginally outperformed SMOTE as the optimal class balancing technique for all resolutions and predictor types when predicting TAD boundary regions.
-
-Additionally, we found that using a distance-type predictor space yielded substantially higher balanced accuracy compared to the peak signal strength, overlap count, and overlap percent predictor types.
-As with class balancing techniques, this improvement was less evident at lower resolutions, with results consistent for K562 (Supplementary Figure 3A).
-Random forest models built on Peakachu-defined loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3B,3C).
-Furthermore, 5 kb resolution genomic bins led to the optimal prediction for both TAD and loop boundaries, on both cell lines.
-Our results indicate that random under-sampling, distance-type predictors, and high-resolution Hi-C data provide the optimal set of data level characteristics for both TAD and chromatin loop boundary prediction.
-
-![**Determining optimal data level characteristics for building TAD boundary region prediction models on GM12878.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Error bars indicate standard deviation from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
-
-## Transcription factor binding sites outperform histone- and chromatin state-specific models
-
-We hypothesized that the type of genomic annotations may also affect predictive performance.
-Using the established optimal settings (RUS, Distance, 5 kb bins), we built separate random forest models using BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS).
-We found that models built on TFBSs outperformed other annotation-specific models, with results consistent for loop boundaries, on both cell lines (Figure 4A; Supplementary Figures 4A).
-These results suggest that TFBS are the primary drivers of TAD and loop boundary formation in both GM12878 and K562.
-
-![**SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in GM12878.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
-(B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
-Error bars represent 1 standard deviation from the mean cross-validated accuracy across each holdout chromosome.
-(C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs.
-The columns represent the holdout chromosome excluded from the training data.
-(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on GM12878 data (blue, Arrowhead ground truth; red, Peakachu ground truth) versus training on K562 and testing on GM12878 data (black, dashed).
-The curves represent the average sensitivities and specificities across each holdout chromosome.
-The shaded areas around each curve represent 1 standard deviation from the average.](Figures/figure4.png)
-
-## Predictive importances confirmed the biological role of CTCF, RAD21, SMC3, and ZNF143 for boundary formation
-
-We sought to further optimize our boundary region prediction models by recursive feature elimination to avoid overfitting and selecting only the most influential TFBS across all autosomal chromosomes.
-We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figures 4B).
-However, given that we trained our model on chromosome-specific data, the most significant annotations varied for each chromosome set.
-To determine transcription factors most important for boundary prediction across all chromosomes, we clustered the predictive importance (mean decrease in accuracy) of the top eight significant TFs across chromosomes.
-We found four transcription factors, CTCF, RAD21, SMC3, and ZNF143, being consistently predictive of TAD and loop boundaries (Figure 4C; Supplementary Figures 4C).
-We optimized our model by only considering these top four TFBS when building the random forest model, thereby decreasing computational burden while maintaining high predictive performance.
-In summary, our model was able to yield the known molecular drivers of the loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
-
-## Training in one cell line accurately predicts boundary regions in other cell lines
-
-Having demonstrated the optimal performance in our framework's ability to predict boundary regions, we next attempted to predict boundary regions in one cell line using the model pre-trained on data from another another cell line (See Methods).
-We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from GM12878 cell line resulted in an average AUC=0.792 (Figure 4D).
-Surprisingly, when training on the K562 cell line and testing on GM12878, the average AUC increased slightly to 0.795.
-Likewise, the average performance of models trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable to models trained on K562-specific Peakachu boundaries and genomic annotations (Avg.
-AUC=0.881 and 0.874, respectively).
-These results were consistent when comparing training/testing strategies on K562 with training on GM12878 and testing on K562 data (Supplementary Figure 4D).
-The average ROC curves were found to be well within 1 standard deviation of each other, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.
-
-## *preciseTAD* identifies precise and biologically relevant domain boundaries
-
-Using our optimally built random forest model trained on Arrowhead/Peakachu boundaries, we attempted to predict boundaries at base-level resolution.
-Intuitively, instead of bin-level annotations, the predictor-response space was built on a base-level, that is, each base was associated with a genomic annotation.
-The model trained on a bin-level space was then applied on a base-level space to predict each base's probability of being a boundary.
-Our method, referred to as *preciseTAD*, uses density-based spatial clustering (DBSCAN) and partitioning around medoids (PAM) to predict the location of boundary regions and summit points (highest boundary probability) at base-level resolution (see Methods; Supplementary Figure 2).
-
-When trained using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, the *preciseTAD* model predicted a total of 12,258 TAD and 15,707 chromatin loop boundaries in GM12878, as well as 9,603 TAD and 11,154 chromatin loop boundaries in K562 cell line (Supplementary Table 4).
-We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Supplementary Table 3).
-This can be attributed to Arrowhead's inflation of called TADs, that, when visualized, often do not correspond to domains enriched in internal interactions (Figure 5A) and signal of known drivers of domain boundaries (Figure 5B).
-*preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Supplementary Table 3).
-This can be attributed to Peakachu's use of only CTCF sites to call boundaries, while *preciseTAD* leverages four known drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143.
-These results suggest that genome annotation-driven predicted boundaries may be more biologically relevant than those detected from Hi-C data alone.
-
-![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of Arrowhead-called TAD boundaries (blue) vs.
-*preciseTAD*-predicted TAD boundaries (green) on GM12878 data (chr14:50085000-50800000).
-The black line represents the predicted probability of each base being a TAD boundary.
-(B) A zoomed-in portion of the genome shows the preciseTAD boundary region (PTBR, highlighted yellow), a cluster of bases with high probability of being a boundary, and the corresponding signal profiles of CTCF, RAD21, SMC3, and ZNF143.
-(C, D) Signal profile plots comparing the strength of CTCF, RAD21, SMC3, and ZNF143 binding around Arrowhead-called boundaries (blue, C), Peakachu loop boundaries (red, D) vs.
-*preciseTAD*-predicted boundaries (green).](Figures/figure5.png)
-
-Next, we evaluated the biological significance of *preciseTAD* boundary points.
-Signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (Figure 5C, 5D; Supplementary Figure 5A, 5B).
-Surprised by the poor signal distribution around Arrowhead boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, and our SpectralTAD [@Cresswell:2020ab] TAD caller.
-We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the relatively well-performing Peakachu- and SpectralTAD-called boundaries (Supplementary Figure 5C, D).
-Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Supplementary Figures 6-7).
-*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBSs (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Supplementary Figure 8).
-These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
-
-## *preciseTAD* boundaries are more conserved across cell lines
-
-Previous studies suggest that TAD boundaries are conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @sexton2012three].
-To assess the level of cross-cell-line conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, Arrowhead, and Peakachu.
-Only 26% and 49% of boundaries were conserved between cell lines for Arrowhead and Peakachu boundaries (J=0.186 and J=0.388), respectively (Figure 6D, 6D.
-However, 45%/56% of *preciseTAD*-predicted domain boundaries were conserved between GM12878 and K562 cell lines when using models trained on Arrowhead/Peakachu data (J=0.383 and J=0.444, respectively, Figure 6C, 6E).
-The better conservation of *preciseTAD*-predicted boundaries further supports the notion of their higher biological relevance.
-
-![**preciseTAD-predicted boundaries are closer to CTCF sites and more conserved across cell lines**.
-(A) Log2 genomic distance distribution from called and predicted boundaries to nearest CTCF sites.
-The p-values are from the Wilcoxon Rank Sum test.
-(B-E) Venn diagrams illustrating the levels of conservation (overlap) between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead (B), Peakachu (D), *preciseTAD*-predicted boundaries using Arrowhead- and Peakachu-trained models () Arrowhead-trained *preciseTAD* models (C), Peakachu boundaries themselves (C, E, respectively).
-Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.](Figures/figure6.png)
-
-## Boundaries predicted by *preciseTAD* models trained on TAD and loop boundaries are highly overlapping
-
-The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model (Supplementary Figure 9).
-<!--We found that 88.8% and 95.8% [???
-These numbers are different from what is shown on Supp Fig 9; !!!the %'s shown are (left region)/(left + middle); should I take out the percentages in the figure?
-???
-Still unclear, calculations don't make sense.
-TBD] of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 9).
-[???
-After clarification, MD to rewrite the first two sentences, unclear] -->This is expected as loop boundaries detected by Peakachu are more abundant, while comparatively wide TAD boundaries detected by Arrowhead likely represent the higher level of the 3D chromatin organization.
-Together with the results in Figure 4C, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar molecular mechanisms.
-
-Guided by the high predictive performance when training and testing on different cell lines (Figure 4D), we opted to evaluate whether models trained using Arrowhead/Peakachu ground truth data in one cell line could be leveraged to predict boundaries using annotation data from another cell line.
-We evaluated two scenarios: 1) training on GM12878 and predicting boundaries on GM12878 (GM on GM) vs.
-training on K562 and predicting on GM12878 (K on GM), and 2) training on K562 and predicting boundaries on K562 (K on K) vs.
-training on GM12878 and predicting boundaries on K562 (GM on K).
-Using Arrowhead-trained models, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries overlapped in both cross-cell-line prediction scenarios (Supplementary Figure 10A, 10B).
-Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlaps (Supplementary 10C, 10D).
-Furthermore, boundaries predicted on unseen annotation data exhibited similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Supplementary Figure 10).
-These results indicate that *preciseTAD* pre-trained models can be successfully used to predict domain boundaries for cell lines lacking Hi-C data but for which genome annotation data is available.
-
-# Discussion
-
-We present *preciseTAD*, a machine learning approach for precise prediction of TAD or loop boundaries from functional genomic annotations.
-*preciseTAD* leverages a random forest (RF) classification model built on low-resolution domain boundaries obtained from domain calling tools, and high-resolution genomic annotations as the predictor space.
-*preciseTAD* predicts the probability of each base being a boundary, and identifies the precise location of boundary regions and the most likely boundary points.
-*preciseTAD* was benchmarked against two boundary calling tools, Arrowhead [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
-We first optimized our RF model by systematically comparing different combinations of genome binning (resolution), feature engineering procedures, and resampling techniques.
-Our results demonstrate that genomic distance between boundary regions and genomic annotations coupled with random under-sampling results in best model performance.
-We show that binding of four transcription factors (SMC3, RAD21, CTCF, ZNF143) is sufficient for accurate boundary predictions.
-*preciseTAD* is implemented as an R package, provides the pre-trained models, and allows for precise prediction of boundaries for any cell line for which the genomic annotations are available.
-
-Our machine learning framework yielded several interesting observations.
-We first demonstrated that RF models built using *distance*-type predictors outperformed models built on previously published feature engineering techniques, including signal strength, overlap counts, and overlap percents [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa; @kai2018predicting].
-We further demonstrated that class imbalance hinders boundary prediction, but can be effectively addressed by a simple random under-sampling technique, an aspect of boundary prediction unaddressed in previous studies [@mourad2016computational; @Moore:2015aa; @Al-Bkhetan:2018aa].
-We showed that information about only four transcription factors (CTCF, SMC3, RAD21, ZNF143) is necessary and sufficient for accurate boundary prediction, outperforming histone modification- and BroadHMM-built models [@Moore:2015aa; @Al-Bkhetan:2018aa].
-These are known components of the loop extrusion model, an established theory of how loops are made by a ring-shaped adenosine triphosphatase-driven complex called cohesin [@hansen2018recent; @sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
-Interestingly, the same transcription factors accurately predicted both TAD and loop boundaries, suggesting a similarity of the mechanisms of TAD and loop formation.
-This suggested that the random forest model, when tuned and feature engineered correctly, is highly effective in predicting biologically relevant domain boundaries.
-
-Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Supplementary Table 5).
-Our aim was to have a balanced metric sensitive to class imbalance such that it would not favor one component of the confusion matrix.
-The accuracy metric can be artificially inflated by true negatives (TN), the set of genomic bins correctly predicted as not containing a ground truth boundary.
-AUROC captures how a model generally performs across different thresholds.
-However, it doesn't place more emphasis on one class over the other, so it does not reflect the minority class well.
-Precision indicates the rate at which positive predictions are correct and can be artificially deflated by low proportions of true positives (TP), the set of genomic bins correctly predicted as containing a ground truth boundary.
-While F1-score is a composite metric, it can be susceptible to different values for precision and recall.
-Lastly, AUPRC is insensitive toward class imbalance, preventing us from investigating its effect, and also omits from its calculation TN values.
-All of these are important considerations to make when choosing a performance metric.
-For these reasons, we opted to report balanced accuracy (BA).
-The BA benefits from incorporating all components of the confusion matrix, while also being sensitive to class imbalance, a necessary characteristic when comparing performances to models built using no data resampling.
-
-Guided by both low-resolution Hi-C data and high-resolution genome annotation data, *preciseTAD* predicts base-level resolution boundaries, alleviating resolution limitations of Hi-C data.
-However, a natural question is how resolution (width) of boundary regions identified by *preciseTAD* (PTBRs) compares with that of Hi-C data.
-Our preliminary observations indicate that, under most optimal settings, the width of PTBRs parallels the resolution of Hi-C data.
-Furthermore, each PTBR is formed by several sub-regions with the probability of being a boundary defined by the threshold $t$ ($t=1$ in the current study).
-Yet, the preciseTAD boundary points (PTBPs, medoids identified within each PTBR) had the highest density of CTCF and other transcription factor binding signal (Figure 5).
-Our results are in line with the emergent view that domain boundaries are dynamic [@chang2020tads] and their well-defined location arise as a consequence of the population average in bulk Hi-C data [@fudenberg2016formation; @Flyamer:2017aa].
-
-We show that, unlike Arrowhead, *preciseTAD* does not inflate the number of predicted boundaries, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
-*preciseTAD* boundaries predicted using models trained on either TAD or loop boundaries (Arrowhead and Peakachu data) were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops may be generated by similar mechanisms [@hansen2018recent].
-Likewise, *preciseTAD* boundaries were more conserved between GM12878 and K562 cell lines, a known feature among the 3D architecture of the human genome, further highlighting their biological significance.
-
-*preciseTAD* offers flexibility in controlling both the number of predicted boundaries and the distance between them.
-The two primary parameters are the probability threshold $t$ and $\epsilon$ (referred to as eps; parameter of DBSCAN).
-The combination of these two quantities changes the resulting number of predicted boundaries from *preciseTAD*.
-Lower values of $t$ and $\epsilon$ will result in more clusters of bases, and therefore, more boundaries.
-As a heuristic, we evaluated the pairwise combination of 3 different thresholds ($t=(0.975,0.99,1.0)$) and 6 different $\epsilon$ values ($\epsilon=(1000,5000,10000,15000,20000,25000)$)).
-We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (Supplementary Figure 11).
-
-A limitation of *preciseTAD* is that it is dependent on the "ground truth" boundaries provided by a domain caller.
-Given the wide variety of domain callers and their variable performance [@Zufferey:2018aa; @forcato2017comparison], defining "ground truth" boundaries is challenging.
-<!--Ideally, we would benchmark *preciseTAD* against simulated boundaries.
-While methods for simulating Hi-C data sets with boundary annotations exist [@forcato2017comparison; @zheng2020freehi], methods for simulating the associated genomic annotations (the main component guiding *preciseTAD* predictions) are lacking.-->Ultra-deep Hi-C sequencing [@bonev2017multiscale] and newer technologies for precise mapping of chromatin interactions (e.g., Micro-C [@Krietenstein:2020aa]), coupled with more precise technologies for genomic annotation profiling (e.g., CUT&RUN for precise mapping of transcription factor binding sites) will help to refine the location and the genomic signatures of the "ground truth" boundaries.
-In the current work, we feel that the total number of domain boundaries is sufficient to guide learning of the association between genomic annotations and boundaries for precise boundary predictions.
-Indeed, models trained on the larger number of Peakachu-predicted boundaries performed better than those trained on Arrowhead boundaries.
-Although we provide models trained on both boundary types, we recommend Peakachu-trained models for the base-level prediction of domain boundaries.
-
-Another limitation of *preciseTAD* is that it does not distinguish boundary types.
-The hierarchical nature of TAD boundaries [@weinreb2016identification; @fraser2015hierarchical; @Cresswell:2020ab] is not considered by *preciseTAD* due to the lack of gold standard of TAD hierarchy.
-*preciseTAD* also does not consider the directionality of CTCF binding [@Harrold:2020aa] as it predicts individual boundaries in contrast to pairs of convergent CTCF motifs marking individual domains.
-Recent research distinguishes CTCF-associated boundaries, CTCF-negative YY1-enriched boundaries, CTCF- and YY1- depleted promoter boundaries, and the fourth class of weak boundaries largely depleted of all three features [@Krietenstein:2020aa].
-Furthermore, actively transcribed regions can serve as TAD boundaries themselves, independently of CTCF binding [@Harrold:2020aa].
-This may lead to some TAD boundaries being undetected by *preciseTAD* despite being detected by domain callers.
-Our future work will involve incorporating the directionality of CTCF binding in predictive modeling, including additional predictor types, and defining separate models trained on different boundary types.
-
-Using the provided pre-trained models, *preciseTAD* is able to identify precise domain boundaries using cell line-specific genome annotation information of only four transcription factors, CTCF, SMC3, RAD21, ZNF143.
-Although the ENCODE, NIH Roadmap Epigenomics, FANTOM5, BLUEPRINT, and other members of the International Human Epigenome Consortium (IHEC) [@Stunnenberg:2016aa] have been actively cataloging cell line-specific genome annotation datasets, these data remain very sparse.
-To date (September 2020), the ENCODE project has only five cell lines (GM12878, K562, H1-hESC, HeLa-S3, HepG2) with all four transcription factor genomic annotations.
-Efforts to <!--systematically catalog chromatin conformation capture data [@Wang:2018ab] and -->impute missing cell line-specific genome annotation information [@Schreiber:2020aa] started to appear.
-We envision the broader availability of cell line-specific genomic annotations will enable a more systematic analysis of domain boundaries using *preciseTAD*.
-<!--*preciseTAD* requires both cell line-specific chromatin conformation capture data (Hi-C in the current study) and genome annotation data.
-Hi-C data provides information about the approximate location of domain boundaries, while genome annotation data is used to train a model that can predict boundaries at the base-level resolution.
-The diversity of chromatin conformation capture technologies [@Kempfer:2019aa] and analysis methods [@Hansen:2019aa] limits the availability of harmonized cell line-specific domain boundary information.-->
-
-# Conclusion
-
-In summary, we demonstrate that domain boundary prediction is a multi-faceted problem requiring consideration of multiple statistical and biological properties of genomic data.
-Simply considering the properties of Hi-C contact matrices ignores the fundamental roles of known molecular drivers of the 3D chromatin structures.
-Instead, we propose *preciseTAD*, a supervised machine learning framework that leverages both Hi-C contact matrix information and genomic annotations.
-Our method introduces three concepts - *shifted binning*, *distance*-type predictors, and *random undersampling* - which we use to build random forest classification models for predicting boundary regions.
-Our method can bridge the resolution gap between 1D ChIP-seq annotations and 3D Hi-C sequencing data for more precise and biologically meaningful boundary identification.
-We introduce *preciseTAD*, an open source R package for leveraging random forests to predict domain boundaries at base-level resolution.
-We hope that *preciseTAD* will serve as an efficient and easy-to-use tool to further explore the genome's 3D organization.
-
-# Methods
-
-## Data sources
-
-TAD and loop boundaries called by Arrowhead [@durand2016juicebox] and Peakachu [@salameh2019supervised] tools were used for training.
-The autosomal genomic coordinates in the GRCh37/hg19 human genome assembly were considered.
-Arrowhead-defined TAD boundaries were called from the GM12878 and K562 cell line Hi-C data (MAPQ>0, 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions) using the default parameters (Additional File 1).
-Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab website (Supplementary Table 1).
-Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop anchor.
-Chromosome 9 was excluded from all downstream analyses due to the sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 2).
-
-## Shifted-binning for binary classification
-
-In Hi-C, each chromosome is binned into non-overlapping regions of length *r*, typically, 5 kb and above.
-The *r* parameter defines the resolution of Hi-C data.
-Here, we designed a strategy called _shifted binning_ that partitions the genome into regions of the same length *r*, but with middle points corresponding to boundaries defined by the original binning.
-
-To create shifted binning, the first shifted bin was set to start at half of the resolution *r* and continued in intervals of length *r* until the end of the chromosome (*mod r* + *r/2*).
-The shifted bins, referred hereafter as bins for simplicity, were then defined as boundary-containing regions (*Y = 1*) if they contained a TAD (or loop) boundary, and non-boundary regions (*Y = 0*) otherwise, thus establishing the binary response vector (**Y**) used for classification (Figure 1A).
-
-## Feature engineering
-
-Cell line-specific genomic annotations were used to build the predictor space.
-Bins were annotated by one of either the average signal strength of the corresponding annotation (*Peak Signal Strength*), the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*) (Figure 1B).
-A ($log_2 + 1$)-transformation of distance was used to account for the skewness of the distance distributions.
-Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin states lack signal values (Supplementary Figure 1).
-
-## Addressing class imbalance
-
-To assess the impact of class imbalance (CI), defined as the proportion of boundary regions to non-boundary regions, we evaluated three resampling techniques: *Random Over-Sampling (ROS)*, *Random Under-Sampling (RUS)*, and *Synthetic Minority Over-Sampling Technique (SMOTE)*.
-For ROS, the minority class was sampled with replacement to obtain the same number of data points in the majority class.
-For RUS, the majority class was sampled without replacement to obtain the same number of data points in the minority class.
-For SMOTE, under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the $k=5$ minority class nearest neighbors [@chawla2002smote] (implemented in the `DMwR` v.0.4.1 R package).
-We restricted the SMOTE algorithm to 100% over-sampling and 200% under-sampling, to create perfectly balanced classes.
-
-## Establishing optimal data level characteristics for TAD boundary region prediction
-
-Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, feature engineering procedures, and resampling techniques.
-Following recommendations to evaluate the model on unseen data [@schreiber2019pitfall], a *holdout chromosome* technique was used for estimating model's performance.
-The $i^{th}$ holdout chromosome was identified and a data matrix, $A_{N \times (p+1)}$, was constructed by combining the binned genome from the remaining chromosomes ($1,2,\cdots, i-1,i+1,\cdots,21,22$), where $N=[n_{1} n_{2} \cdots n_{21} n_{22}]'$ and $n_{k}$ is the length of chromosome *k* after being binned into non-overlapping regions of resolution *r*, such that $k \ne i$.
-$p$, the number of annotations, together with the response vector, **Y**, defined the column-wise dimension of the matrix $A$.
-Re-sampling was then performed on $A$, and an RF classifier was trained using 3-fold cross-validation to tune for the number of annotations to consider at each node (*mtry*).
-The number of trees (*ntree*) that were aggregated for each RF model was set to 500.
-The minimum number of observations per root node (*nodesize*) was set to 0.1% of the rows in the data.
-The binned data for the holdout chromosome $i$ was reserved for testing.
-Models were evaluated using Balanced Accuracy (BA), defined as the average of sensitivity and specificity:
-
-$$BA = \dfrac{1}{2}\left( sensitivity + specificity \right) = \dfrac{1}{2}\left( \dfrac{TP}{TP+FN} + \dfrac{TN}{TN+FP} \right)$$
-
-where TP refers to the number of bins correctly identified as containing a boundary (true positives), FP refers to the number of bins incorrectly identified as containing a boundary (false positives), TN refers to the number of bins correctly identified as not containing a boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a boundary (false negatives).
-Each of these quantities is obtained from the confusion matrix created by validating the model on the test data.
-The process was repeated for each $i^{th}$ holdout chromosome, and performances were aggregated using mean and standard deviation.
-
-## Feature selection and predictive importance
-
-Many genomic annotations, notably architectural proteins, tend to exhibit an extensive pattern of colocalization (correlation) [@van2014insulator].
-To suitably reduce the predictor space and improve computational efficiency, while maintaining optimal performance, we implemented recursive feature elimination (RFE).
-We estimated the near-optimal number of necessary features, ranging from 2 to the maximum number of features incremented by the power of 2.
-We then aggregated the predictive importance of the union of the optimal set of features across holdout chromosomes using the mean decrease in node impurity among permuted features in out-of-bag samples to determine the most common and top-ranked annotations for predicting boundary regions.
-
-## Evaluating performance across cell lines
-
-We used the same holdout chromosome strategy to evaluate a model trained in one cell line on unseen data from another cell line [@schreiber2019pitfall].
-Given two cell lines, GM12878 and K562, we first evaluated the performance of cell line-specific models.
-That is, models trained on cell line-specific data from $n-1$ chromosomes were evaluated on the $i^{th}$ holdout chromosome data from the same cell line.
-Second, we evaluated models trained on cell line-specific data from $n-1$ chromosomes using the $i^{th}$ holdout chromosome data from a different cell line.
-That is, models trained using K562 cell line-specific data were evaluated on unseen chromosome data from GM12878 cell line.
-This process was repeated for each holdout chromosome.
-To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivities and specificities at different cutoffs, across each holdout chromosome, and reported the corresponding average area under the curve (AUC).
-
-## Boundary prediction at the base-level resolution using *preciseTAD*
-
-To investigate whether we could alleviate the resolution limitations of conventional domain calling tools, we developed *preciseTAD*.
-This algorithm leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution (Supplementary Figure 2).
-
-A random forest model $(M)$ was built on the optimal combination of predictor type (predictor space), resampling technique (class balancing correction), and top-ranked annotations (most informative genomic elements) for a set of binned chromosomes $\{k | k \ne i \}$ <!--, to maximally accurately predict boundaries at the _Hi-C resolution level_-->.
-To precisely identify boundary locations, we first constructed a _base-level resolution_ predictor space for the chromosome *i*, $A_{n \times p}$, where $n$ is the length of chromosome $i$ and $p$ is the optimal number of annotations.
-We then evaluate $M$ on the base-level predictor space to extract the probability vector, $\pi_{n_{i}}$, denoting each base's probability of being a boundary.
-Here, $n_{i}$ represents the length of chromosome *i*.
-A threshold $t$ specifies the probability at which a base with $\pi_{n_{i}} \ge t$ is designated as a potential boundary (the default $t=1$).
-Next, density-based spatial clustering of applications with noise (DBSCAN; version 1.1-5) is applied to the matrix of pairwise genomic distances between boundary-annotated bases, $D$.
-The minimum and maximum coordinates of each cluster, $k$, of spatially colocalized bases were termed *preciseTAD boundary regions* (PTBR).
-To precisely identify a single base among each PTBR, *preciseTAD* implements partitioning around medoids (PAM) on the distance matrix, $D_{k}$, derived from each cluster.
-The corresponding cluster medoid was defined as a *preciseTAD boundary point* (PTBP), making it the most representative base coordinate within each clustered PTBR.
-
-The DBSCAN algorithm has two parameters, *MinPts* and *eps* ($\epsilon$).
-The *MinPts* parameter was set to the recommended value of 3, representing $1+dim(data)$ [@hahsler2019dbscan].
-To decide on the optimal value of $t$ and $\epsilon$ in *preciseTAD*, we considered the normalized enrichment $NE$ of flanked predicted boundaries, defined as
-
-$$NE = \dfrac{1}{p} \left[ \Sigma_{s=1}^{p} \left[ \dfrac{1}{b} \Sigma_{k=1}^{b} e_{ks} \times c_{k} \right] \right]$$
-
-where $e_{ks} = \textbf{I}\{ r_{s} \in (b_{k}-f, b_{k}+f)\}$ is the number of elemental regions $r$ of predictor $p$ that overlap with each flanked boundary.
-We evaluated $NE$ for combinations of $t=\{0.975, 0.99, 1.0 \}$ and $\epsilon = \{1000, 5000, 10000, 15000, 20000, 25000 \}$.
-The heuristic of $\epsilon$ is that density-reachable bases with genomic distances less than $\epsilon$ should occupy the same designated cluster.
-The default combination was set to $t=1.0$ and $\epsilon=10000$ based on our tests (Supplementary Figure 11).
-
-## Predicting boundaries across cell lines
-
-We aimed to extend the strategy of building and comparing boundary region prediction models using same cell line versus across cell line data to predict boundaries at base level resolution across cell lines.
-To do so, we applied *preciseTAD* on models built using cell line specific annotation data to predict boundaries on base level annotation data from another cell line.
-As before, this strategy was compared to applying *preciseTAD* on models and base level annotation data from the same cell line.
-
-## Evaluating called and predicted boundary precision
-
-We assessed the biological significance of our predicted boundaries by their association with the signal of CTCF, RAD21, SMC3, and ZNF143 using *deepTools* (version 2.0) [@ramirez2016deeptools] (*computeMatrix*, *plotProfile*, and *plotHeatmap* tools).
-Additionally, we compared the median $log_2$ genomic distances between TAD boundaries and the same top predictive ChIP-seq annotations using Wilcoxon Rank-Sum tests.
-Furthermore, we compared the overlap between predicted and called boundaries in GM12878 and K562 cell lines.
-Boundaries were first flanked by resolution, *r*, and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0).
-Overlaps were further quantified using the Jaccard index defined as
-
-$$J_{(A,B)} = \dfrac{A \cap B}{A \cup B}$$
-
-where A and B represent genomic regions created by flanked called and predicted boundaries.
-That is, between cell lines, the number of overlapping flanked boundaries divided by the total number of flanked boundaries.
-Wilcoxon Rank-Sum tests were used to compare chromosome-specific Jaccard indices across cell lines, between *preciseTAD* boundaries and both Arrowhead and Peakachu boundaries, respectively.
-All statistical analyses were performed in R version 4.0.1.
-The significance level was set to 0.05 for all statistical tests.
-
-<!--using the `EnrichedHeatmap` R package (version 1.14.0) [@gu2018enrichedheatmap].
-For each boundary (both called and predicted), a 5000 bp flank was created on either side.
-The flanking was broken up into 50 bp segments, for a total of 100 windows on both sides of a given boundary.
-A coverage value was generated for each window with respect to a given ChIP-seq annotation, as the mean signal averaged by the width of the window, denoted by,
-
-$$v_{c} = \dfrac{\Sigma_{j}^{m} \Sigma_{i}^{n}x_{ij}w_{ij}}{L}$$
-
-where $x_{ij}$ is the total number of bases of annotation $i$ in window $j$ and $w_{ij}$ is the number of bases that overlap between annotation $i$ and window $j$.
-The denominator, $L$, is the width of the windows (here, $L=50$).
-The rows of the heatmaps are ordered by enriched scores.
-The enriched scores are calculated as the sum of coverage values weighted by the distance to the flanked boundary, denoted by
-
-$$s_{e} = \Sigma_{d=1}^{n_{1}}\left(\dfrac{x_{1d}* d}{n_{1}} \right) + \Sigma_{u=1}^{n_{2}}\left(\dfrac{x_{2u}* (n_{2} - u + 1)}{n_{2}} \right)$$
-where $n_{1}$ and $n_{2}$ represent the number of downstream and upstream coverage values to sum over. Here, $n_{1}=n_{2}=100$.-->
-
-<!--
-The two proteins differ in that YY1 preferentially
-occupies interacting enhancers and promoters, whereas CTCF
-preferentially occupies sites distal from these regulatory elements that tend to form larger loops and participate in insulation.
-Deletion of YY1 binding sites or depletion of YY1 can disrupt
-enhancer-promoter contacts and normal gene expression.
-Thus, YY1-mediated structuring of enhancer-promoter loops is
-analogous to CTCF-mediated structuring of TADs, CTCF contact domains, and insulated neighborhoods. This model of
-YY1-mediated structuring of enhancer-promoter loops accounts
-for diverse functions reported previously for YY1, including contributions to both gene activation and repression and to gene
-dysregulation in cancer. ["YY1 Is a Structural Regulator
-of Enhancer-Promoter Loops"]
--->
-
-# Supplementary Legends
-
-**Supplementary Table 1.** Data sources for Hi-C matrices used to call topologically associating domains with Arrowhead, as well as loop boundaries obtained by Peakachu.
-
-**Supplementary Table 2.** A complete list of genomic annotations used to build the predictor space for all downstream models.
-The GRCh37/hg19 human genome assembly was used.
-"Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Cell line-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
-
-**Supplementary Figure 1.
-The $log_{2}$ transformation of genomic distances normalizes their distributions.** Distances are measured as the number of bases from the center of a genomic bin to the nearest genomic annotation center.
-Density curves of distances before (red) and after (blue) performing a $log_{2}$ transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines.
-Each density curve represents an individual genomic annotation (77 total).
-
-**Supplementary Figure 2.** Pseudocode of the *preciseTAD* algorithm.
-
-**Supplementary Table 3.** Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on K562.
-
-**Supplementary Figure 3.
-Determining optimal data level characteristics for building TAD boundary region prediction models on K562.** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562.
-(B) Averaged balanced accuracies are compared for GM12878 and (C) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.
-
-**Supplementary Figure 4.
-SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in K562.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
-(B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
-Error bars represent 1 standard deviation from the mean cross-validated accuracy across each holdout chromosome.
-(C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs.
-The columns represent the holdout chromosome excluded from the training data.
-(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on K562 data (blue, Arrowhead ground truth; red, Peakachu ground truth) versus training on GM12878 and testing on K5628 data (black, dashed).
-The curves represent the average sensitivities and specificities across each holdout chromosome.
-The shaded areas around each curve represent 1 standard deviation from the average.
-
-**Supplementary Table 4.** hg19/GRCh37 genomic coordinates of *preciseTAD*-predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562 cell lines, using models trained on Arrowhead TAD and Peakachu chromatin loop boundaries as ground truth.
-For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability of being a boundary equal to 1.
-For PTBPs, the start and end (start+1) coordinates define the most likely boundary point within each PTBR.
-
-**Supplementary Figure 5.** Signal profile plots comparing the binding strength of top TFBSs around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green) on K562, (B) Peakachu chromatin loop boundaries (red) and preciseTAD predicted loop boundaries (green) on K562, (C) Arrowhead called TAD boundaries (blue), Peakachu chromatin loop boundaries (red), and SpectralTAD called TAD boundaries (green) on GM12878 and (D) on K562.
-
-**Supplementary Figure 6.
-*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Arrowhead boundaries.** Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called TAD boundaries vs.
-*preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
-
-**Supplementary Figure 7.
-*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Peakachu boundaries.** Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Peakachu chromatin loop boundaries vs.
-*preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
-
-**Supplementary Figure 8.
-*preciseTAD* boundaries are spatially closer to known molecular drivers of 3D chromatin.** Boxplots comparing the log2 genomic distance distributions from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
-p-values are derived from the Wilcoxon Rank Sum test.
-
-**Supplementary Figure 9.
-The agreement between *preciseTAD*-predicted boundaries using Arrowhead- and Peakachu-trained models**.
-Venn diagrams of boundary overlaps using (A) GM12878 and (B) K562 data.
-Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
-
-**Supplementary Figure 10.
-Pre-trained *preciseTAD* models accurately predict boundaries on cell lines using annotation data only.** Venn diagrams and signal profile plots comparing flanked predicted boundaries using Arrowhead (A, B) and Peakachu (C, D) trained models.
-(A, C) train on GM12878 and predict on GM12878 (red, GM on GM) vs.
-train on K562 and predict on GM12878 (blue, K on GM), (B, D) train on K562 predict on K562 (red, K on K) vs.
-train on GM12878 predict on K562 (blue, GM on K).
-Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
-
-**Supplementary Figure 11.
-Normalized Enrichment levels suggest t=1.0 and $\epsilon=10000$ as the most optimal parameters for biologically relevant *preciseTAD*-predicted boundaries.** Linecharts illustrating the normalized enrichment (NE) between CTCF, RAD21, SMC3, ZNF143 and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps).
-NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model.
-Data from GM12878 (A) and K562 (B) cell lines, chromosome 22, at 5kb resolution was used.
-Error bars indicate standard deviation from the mean.
-
-**Supplementary Table 5.** Additional performance metrics when implementing a random forest using Arrowhead/Peakachu ground truth TAD/loop boundaries.
-Performances are averaged across each holdout chromosome that was reserved for testing.
-
-# Additional File Legends
-
-**Additional File 1**.
 An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions.
 An example of deepTools commands to generate plotProfiles and plotHeatmaps is also provided.
-
-# Abbreviations
-
-AUC - Area Under the Curve; BA - Balanced Accuracy; bp - base pair; BroadHMM - BroadHMM chromatin state data; ChIP-seq - Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI - Class Imbalance; DBSCAN - Density-Based Spatial Clustering of Applications with Noise; FN - False Negatives; FP - False Positives; Hi-C - High-throughput chromosome conformation capture technology; HM - Histone Modifications; kb - kilobase; ML - Machine Learning; OC - Overlap Counts; OP - Overlap Percents; PAM - Partitioning Around Medoids; PTBP - preciseTAD Boundary Point; PTBR - preciseTAD Boundary Region; RF - Random Forest; RFE - Recursive Feature Elimination; ROC - Receiver Operating Characteristic; ROS - Random Over-Sampling; RUS	Random Under-Sampling; SMOTE - Synthetic Minority Over-sampling Technique; TAD - Topologically Associating Domains; TFBS - Transcription Factor Binding Sites; TN - True Negatives; TP - True Positives
-
-# Declarations
-
-## Ethics approval and consent to participate
-
-Not applicable
-
-## Consent for publication
-
-Not applicable
-
-## Availability of data and materials
-
-All data generated or analysed during this study are included in this published article [and its supplementary information files].
-
-## Competing interests
-
-Not applicable
-
-## Funding
-
-## Authors' contributions
-
-## Acknowledgements
-
-## Authors' information (optional)
-
-# References

### 2020-09-26 BMC_Genome_Biology_submission/supplementary_figures/supplementary_figure_legends.Rmd
submission folder initial commit

---
title: "preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution"
subtitle: "Supplementary Figure Legends"
output:
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Supplementary Figure 1. The $log_{2}$ transformation of genomic distances normalizes their distributions.

Distances are measured as the number of bases from the center of a genomic bin to the nearest genomic annotation center. Density curves of distances before (red) and after (blue) performing a $log_{2}$ transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines. Each density curve represents an individual genomic annotation (77 total).

# Supplementary Figure 2. Psuedocode.

Pseudocode of the *preciseTAD* algorithm.

# Supplementary Figure 3. Determining optimal data level characteristics for building TAD boundary region prediction models on K562.

(A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562. (B) Averaged balanced accuracies are compared for GM12878 and (C) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple). Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.

# Supplementary Figure 4. SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in K562.

(A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL). (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors. Error bars represent 1 standard deviation from the mean cross-validated accuracy across each holdout chromosome. (C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs. The columns represent the holdout chromosome excluded from the training data. (D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on K562 data (blue, Arrowhead ground truth; red, Peakachu ground truth) versus training on GM12878 and testing on K5628 data (black, dashed). The curves represent the average sensitivities and specificities across each holdout chromosome. The shaded areas around each curve represent 1 standard deviation from the average.

# Supplementary Figure 5. preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.

Signal profile plots comparing the binding strength of top TFBSs around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green) on K562, (B) Peakachu chromatin loop boundaries (red) and preciseTAD predicted loop boundaries (green) on K562, (C) Arrowhead called TAD boundaries (blue), Peakachu chromatin loop boundaries (red), and SpectralTAD called TAD boundaries (green) on GM12878 and (D) on K562.

# Supplementary Figure 6. *preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Arrowhead boundaries.

Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called TAD boundaries vs. *preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.

# Supplementary Figure 7. *preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Peakachu boundaries.

Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Peakachu chromatin loop boundaries vs. *preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.

# Supplementary Figure 8. *preciseTAD* boundaries are spatially closer to known molecular drivers of 3D chromatin.

Boxplots comparing the log2 genomic distance distributions from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites. p-values are derived from the Wilcoxon Rank Sum test.

# Supplementary Figure 9. The agreement between *preciseTAD*-predicted boundaries using Arrowhead- and Peakachu-trained models.

Venn diagrams of boundary overlaps using (A) GM12878 and (B) K562 data. Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.

# Supplementary Figure 10. Pre-trained *preciseTAD* models accurately predict boundaries on cell lines using annotation data only.

Venn diagrams and signal profile plots comparing flanked predicted boundaries using Arrowhead (A, B) and Peakachu (C, D) trained models. (A, C) train on GM12878 and predict on GM12878 (red, GM on GM) vs. train on K562 and predict on GM12878 (blue, K on GM), (B, D) train on K562 predict on K562 (red, K on K) vs. train on GM12878 predict on K562 (blue, GM on K). Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.

# Supplementary Figure 11. Normalized Enrichment levels suggest t=1.0 and $\epsilon=10000$ as the most optimal parameters for biologically relevant *preciseTAD*-predicted boundaries.

Linecharts illustrating the normalized enrichment (NE) between CTCF, RAD21, SMC3, ZNF143 and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps). NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model. Data from GM12878 (A) and K562 (B) cell lines, chromosome 22, at 5kb resolution was used. Error bars indicate standard deviation from the mean.

### 2020-09-26 BMC_Genome_Biology_submission/supplementary_tables/supplementary_table_legends.Rmd
submission folder initial commit

---
title: "preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution"
subtitle: "Supplementary Table Legends"
output:
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Supplementary Table 1.

Data sources for Hi-C matrices used to call topologically associating domains with Arrowhead, as well as loop boundaries obtained by Peakachu.

# Supplementary Table 2.

A complete list of genomic annotations used to build the predictor space for all downstream models. The GRCh37/hg19 human genome assembly was used. "Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Cell line-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).

# Supplementary Table 3.

Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on K562.

# Supplementary Table 4.

hg19/GRCh37 genomic coordinates of *preciseTAD*-predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562 cell lines, using models trained on Arrowhead TAD and Peakachu chromatin loop boundaries as ground truth. For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability of being a boundary equal to 1. For PTBPs, the start and end (start+1) coordinates define the most likely boundary point within each PTBR.

# Supplementary Table 5.

Additional performance metrics when implementing a random forest using Arrowhead/Peakachu ground truth TAD/loop boundaries. Performances are averaged across each holdout chromosome that was reserved for testing.

### 2020-09-27 Manuscript/manuscript.Rmd
added keywords and filled out some declarations subheaders

@@
 # Keywords
+
+Hi-C sequencing, TADs, high resolution, machine learning, random forest, spatial clustering
 
@@
 
-# Supplementary Legends
-
-**Supplementary Table 1.** Data sources for Hi-C matrices used to call topologically associating domains with Arrowhead, as well as loop boundaries obtained by Peakachu.
-
-**Supplementary Table 2.** A complete list of genomic annotations used to build the predictor space for all downstream models.
-The GRCh37/hg19 human genome assembly was used.
-"Genomic Class" - broad category of genomic features, "Element" - names of genomic features, "Cell line-Specific Source" - download URL specific to the cell line (not all annotations were provided by the same institutions).
-
-**Supplementary Figure 1.
-The $log_{2}$ transformation of genomic distances normalizes their distributions.** Distances are measured as the number of bases from the center of a genomic bin to the nearest genomic annotation center.
-Density curves of distances before (red) and after (blue) performing a $log_{2}$ transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines.
-Each density curve represents an individual genomic annotation (77 total).
-
-**Supplementary Figure 2.** Pseudocode of the *preciseTAD* algorithm.
-
-**Supplementary Table 3.** Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on K562.
-
-**Supplementary Figure 3.
-Determining optimal data level characteristics for building TAD boundary region prediction models on K562.** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562.
-(B) Averaged balanced accuracies are compared for GM12878 and (C) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.
-
-**Supplementary Figure 4.
-SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in K562.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
-(B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
-Error bars represent 1 standard deviation from the mean cross-validated accuracy across each holdout chromosome.
-(C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs.
-The columns represent the holdout chromosome excluded from the training data.
-(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on K562 data (blue, Arrowhead ground truth; red, Peakachu ground truth) versus training on GM12878 and testing on K5628 data (black, dashed).
-The curves represent the average sensitivities and specificities across each holdout chromosome.
-The shaded areas around each curve represent 1 standard deviation from the average.
-
-**Supplementary Table 4.** hg19/GRCh37 genomic coordinates of *preciseTAD*-predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562 cell lines, using models trained on Arrowhead TAD and Peakachu chromatin loop boundaries as ground truth.
-For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability of being a boundary equal to 1.
-For PTBPs, the start and end (start+1) coordinates define the most likely boundary point within each PTBR.
-
-**Supplementary Figure 5.** Signal profile plots comparing the binding strength of top TFBSs around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green) on K562, (B) Peakachu chromatin loop boundaries (red) and preciseTAD predicted loop boundaries (green) on K562, (C) Arrowhead called TAD boundaries (blue), Peakachu chromatin loop boundaries (red), and SpectralTAD called TAD boundaries (green) on GM12878 and (D) on K562.
-
-**Supplementary Figure 6.
-*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Arrowhead boundaries.** Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called TAD boundaries vs.
-*preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
-
-**Supplementary Figure 7.
-*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Peakachu boundaries.** Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Peakachu chromatin loop boundaries vs.
-*preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
-
-**Supplementary Figure 8.
-*preciseTAD* boundaries are spatially closer to known molecular drivers of 3D chromatin.** Boxplots comparing the log2 genomic distance distributions from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
-p-values are derived from the Wilcoxon Rank Sum test.
-
-**Supplementary Figure 9.
-The agreement between *preciseTAD*-predicted boundaries using Arrowhead- and Peakachu-trained models**.
-Venn diagrams of boundary overlaps using (A) GM12878 and (B) K562 data.
-Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
-
-**Supplementary Figure 10.
-Pre-trained *preciseTAD* models accurately predict boundaries on cell lines using annotation data only.** Venn diagrams and signal profile plots comparing flanked predicted boundaries using Arrowhead (A, B) and Peakachu (C, D) trained models.
-(A, C) train on GM12878 and predict on GM12878 (red, GM on GM) vs.
-train on K562 and predict on GM12878 (blue, K on GM), (B, D) train on K562 predict on K562 (red, K on K) vs.
-train on GM12878 predict on K562 (blue, GM on K).
-Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
-
-**Supplementary Figure 11.
-Normalized Enrichment levels suggest t=1.0 and $\epsilon=10000$ as the most optimal parameters for biologically relevant *preciseTAD*-predicted boundaries.** Linecharts illustrating the normalized enrichment (NE) between CTCF, RAD21, SMC3, ZNF143 and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps).
-NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model.
-Data from GM12878 (A) and K562 (B) cell lines, chromosome 22, at 5kb resolution was used.
-Error bars indicate standard deviation from the mean.
-
-**Supplementary Table 5.** Additional performance metrics when implementing a random forest using Arrowhead/Peakachu ground truth TAD/loop boundaries.
-Performances are averaged across each holdout chromosome that was reserved for testing.
-
-# Additional File Legends
-
-**Additional File 1**.
-An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions.
-An example of deepTools commands to generate plotProfiles and plotHeatmaps is also provided.
-
 # Abbreviations
@@
 All data generated or analysed during this study are included in this published article [and its supplementary information files].
+The source code of *preciseTAD* version 0.99.6 used in the experiments is available on github at https://github.com/dozmorovlab/preciseTAD.
 
@@
 
-Not applicable
+The authors declare that they have no competing interests.
 
@@
 
+^1^ Dept. of Biostatistics, Virginia Commonwealth University, Richmond, VA, 23298, USA  
+^\*^ To whom correspondence should be addressed: Virginia Commonwealth University, Richmond, VA, 23298, 804-827-2055, mikhail.dozmorov@vcuhealth.org
+
 # References

### 2020-09-27 Manuscript/manuscript.Rmd
added author's contributions
Fixes

@@
 <!-- 100 words abstract start -->
-The low resolution of high-throughput chromosome conformation capture data limits the precise mapping of boundaries of topologically associating domains and chromatin loops.
+The low resolution of high-throughput chromatin conformation capture data limits the precise mapping of boundaries of topologically associating domains and chromatin loops.
 We developed preciseTAD, an optimized random forest model trained on high-resolution genome annotation data (e.g., CTCF ChIP-seq) to predicts the location of domain boundaries at base-level resolution.
@@
 
-Hi-C sequencing, TADs, high resolution, machine learning, random forest, spatial clustering
+Hi-C, TAD, chromatin, machine learning, random forest, spatial clustering
 
@@
 
+<!--
 # Abbreviations
@@
 AUC - Area Under the Curve; BA - Balanced Accuracy; bp - base pair; BroadHMM - BroadHMM chromatin state data; ChIP-seq - Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI - Class Imbalance; DBSCAN - Density-Based Spatial Clustering of Applications with Noise; FN - False Negatives; FP - False Positives; Hi-C - High-throughput chromosome conformation capture technology; HM - Histone Modifications; kb - kilobase; ML - Machine Learning; OC - Overlap Counts; OP - Overlap Percents; PAM - Partitioning Around Medoids; PTBP - preciseTAD Boundary Point; PTBR - preciseTAD Boundary Region; RF - Random Forest; RFE - Recursive Feature Elimination; ROC - Receiver Operating Characteristic; ROS - Random Over-Sampling; RUS	Random Under-Sampling; SMOTE - Synthetic Minority Over-sampling Technique; TAD - Topologically Associating Domains; TFBS - Transcription Factor Binding Sites; TN - True Negatives; TP - True Positives
+-->
 
@@
 
-All data generated or analysed during this study are included in this published article [and its supplementary information files].
+All data generated or analyzed during this study are included in this published article [and its supplementary information files].
 The source code of *preciseTAD* version 0.99.6 used in the experiments is available on github at https://github.com/dozmorovlab/preciseTAD.
@@
 
+MD conceptualized and supervised the study.
+MD and SS wrote the manuscript.
+SS and MD wrote the software associated with the R package.
+SS performed the analysis for the final results.
+The authors read and approved the final manuscript.
+
 ## Acknowledgements
 
+<!--
 ## Authors' information (optional)
@@
 ^\*^ To whom correspondence should be addressed: Virginia Commonwealth University, Richmond, VA, 23298, 804-827-2055, mikhail.dozmorov@vcuhealth.org
+-->
 

### 2020-09-27 Manuscript/manuscript.Rmd
added figure keys; renumbered supp figs/tables; added additional file legends

@@
   word_document:
-    reference_docx: styles.doc/NIH_grant_style.docx
+    reference_docx: styles.doc/Arial_11_double_space_normal_margins.docx
 bibliography: References/references.bib
@@
 We used Arrowhead-called TAD boundaries [@durand2016juicer] and published Peakachu-predicted loop boundaries [@salameh2019supervised] as ground truth.
-Data from GM12878 and K565 cell lines at 5-100kb resolution (Arrowhead) and 10kb resolution (Peakachu) were used (Supplementary Table 1).
+Data from GM12878 and K565 cell lines at 5-100kb resolution (Arrowhead) and 10kb resolution (Peakachu) were used (Additional file: Arrowhead Script, Additional file: Table S1<!--Supplementary Table 1-->).
 We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base resolution from cell line-specific genome annotation data.
 
+<!--
 ![**Resolution-specific data construction and feature engineering for random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals using *shifted binning* (see Methods).
@@
 (B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png)
+-->
 
 Boundary regions were defined as genomic bins containing a called boundary ($Y = 1$), while non-boundary regions were defined as bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
-The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Supplementary Table 3).
+The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Additional file: Table S2<!--Supplementary Table 3-->).
 The number of non-boundary regions highly outnumbered boundary regions.
@@
 A total of 77 cell line-specific genomic annotations were used to build the predictor space.
-These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Supplementary Table 2).
+These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Additional file: Table S3<!--Supplementary Table 2-->).
 Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
-These included signal strength association (Signal), direct (OC), proportional (OP), and spatial ($log_2 + 1$ Distance) relationships (see Methods, Supplementary Figure 1).
+These included signal strength association (Signal), direct (OC), proportional (OP), and spatial ($log_2 + 1$ Distance) relationships (see Methods, Additional file: Figure S1<!--Supplementary Figure 1-->).
 
@@
 
+<!--
 ![**A machine learning framework for building domain boundary region prediction models.** Step 1 employs a range of feature engineering techniques to define the predictor matrix $A_{N \times (p)}$, where $N$ is the number of genomic bins, $p$ is the number of genomic annotations, $i$ is a holdout chromosome.
@@
 Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and to evaluate model performance using balanced accuracy (BA).](Figures/figure2.png)
+-->
 
@@
 Additionally, we found that using a distance-type predictor space yielded substantially higher balanced accuracy compared to the peak signal strength, overlap count, and overlap percent predictor types.
-As with class balancing techniques, this improvement was less evident at lower resolutions, with results consistent for K562 (Supplementary Figure 3A).
-Random forest models built on Peakachu-defined loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Supplementary Figure 3B,3C).
+As with class balancing techniques, this improvement was less evident at lower resolutions, with results consistent for K562 (Additional file: Figure S2A<!--Supplementary Figure 3A-->).
+Random forest models built on Peakachu-defined loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Additional file: Figure S2B, S2C<!--Supplementary Figure 3B,3C-->).
 Furthermore, 5 kb resolution genomic bins led to the optimal prediction for both TAD and loop boundaries, on both cell lines.
@@
 
+<!--
 ![**Determining optimal data level characteristics for building TAD boundary region prediction models on GM12878.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Error bars indicate standard deviation from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
+-->
 
@@
 Using the established optimal settings (RUS, Distance, 5 kb bins), we built separate random forest models using BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS).
-We found that models built on TFBSs outperformed other annotation-specific models, with results consistent for loop boundaries, on both cell lines (Figure 4A; Supplementary Figures 4A).
+We found that models built on TFBSs outperformed other annotation-specific models, with results consistent for loop boundaries, on both cell lines (Figure 4A; Additional file: Figure S3A<!--Supplementary Figures 4A-->).
 These results suggest that TFBS are the primary drivers of TAD and loop boundary formation in both GM12878 and K562.
 
+<!--
 ![**SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in GM12878.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
@@
 The shaded areas around each curve represent 1 standard deviation from the average.](Figures/figure4.png)
+-->
 
@@
 We sought to further optimize our boundary region prediction models by recursive feature elimination to avoid overfitting and selecting only the most influential TFBS across all autosomal chromosomes.
-We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Supplementary Figures 4B).
+We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Additional file: Figure S3B<!--Supplementary Figures 4B-->).
 However, given that we trained our model on chromosome-specific data, the most significant annotations varied for each chromosome set.
 To determine transcription factors most important for boundary prediction across all chromosomes, we clustered the predictive importance (mean decrease in accuracy) of the top eight significant TFs across chromosomes.
-We found four transcription factors, CTCF, RAD21, SMC3, and ZNF143, being consistently predictive of TAD and loop boundaries (Figure 4C; Supplementary Figures 4C).
+We found four transcription factors, CTCF, RAD21, SMC3, and ZNF143, being consistently predictive of TAD and loop boundaries (Figure 4C; Additional file: Figure S3C<!--Supplementary Figures 4C-->).
 We optimized our model by only considering these top four TFBS when building the random forest model, thereby decreasing computational burden while maintaining high predictive performance.
@@
 AUC=0.881 and 0.874, respectively).
-These results were consistent when comparing training/testing strategies on K562 with training on GM12878 and testing on K562 data (Supplementary Figure 4D).
+These results were consistent when comparing training/testing strategies on K562 with training on GM12878 and testing on K562 data (Additional file: Figure S3D<!--Supplementary Figure 4D-->).
 The average ROC curves were found to be within 1 standard deviation of each other, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.
@@
 The model trained on a bin-level space was then applied on a base-level space to predict each base's probability of being a boundary.
-Our method, referred to as *preciseTAD*, uses density-based spatial clustering (DBSCAN) and partitioning around medoids (PAM) to predict the location of boundary regions and summit points (highest boundary probability) at base-level resolution (see Methods; Supplementary Figure 2).
+Our method, referred to as *preciseTAD*, uses density-based spatial clustering (DBSCAN) and partitioning around medoids (PAM) to predict the location of boundary regions and summit points (highest boundary probability) at base-level resolution (see Methods; Additional file: Figure S4<!--Supplementary Figure 2-->).
 
-When trained using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, the *preciseTAD* model predicted a total of 12,258 TAD and 15,707 chromatin loop boundaries in GM12878, as well as 9,603 TAD and 11,154 chromatin loop boundaries in K562 cell line (Supplementary Table 4).
-We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Supplementary Table 3).
+When trained using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, the *preciseTAD* model predicted a total of 12,258 TAD and 15,707 chromatin loop boundaries in GM12878, as well as 9,603 TAD and 11,154 chromatin loop boundaries in K562 cell line (Additional file: Table S4<!--Supplementary Table 4-->).
+We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Additional file: Table S2<!--Supplementary Table 3-->).
 This can be attributed to Arrowhead's inflation of called TADs, that, when visualized, often do not correspond to domains enriched in internal interactions (Figure 5A) and signal of known drivers of domain boundaries (Figure 5B).
-*preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Supplementary Table 3).
+*preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Additional file: Table S2<!--Supplementary Table 3-->).
 This can be attributed to Peakachu's use of only CTCF sites to call boundaries, while *preciseTAD* leverages four known drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143.
@@
 
+<!--
 ![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of Arrowhead-called TAD boundaries (blue) vs.
@@
 *preciseTAD*-predicted boundaries (green).](Figures/figure5.png)
+-->
 
 Next, we evaluated the biological significance of *preciseTAD* boundary points.
-Signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (Figure 5C, 5D; Supplementary Figure 5A, 5B).
+Signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (Figure 5C, 5D; Additional file: Figure S5A, S5B<!--Supplementary Figure 5A, 5B-->).
 Surprised by the poor signal distribution around Arrowhead boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, and our SpectralTAD [@Cresswell:2020ab] TAD caller.
-We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the relatively well-performing Peakachu- and SpectralTAD-called boundaries (Supplementary Figure 5C, D).
-Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Supplementary Figures 6-7).
-*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBSs (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Supplementary Figure 8).
+We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the relatively well-performing Peakachu- and SpectralTAD-called boundaries (Additional file: Figure S5C, S5D<!--Supplementary Figure 5C, D-->).
+Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Additional file: Figure S6-S7<!--Supplementary Figures 6-7-->).
+*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBSs (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Additional file: Figure S8<!--Supplementary Figure 8-->).
 These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
@@
 
+<!--
 ![**preciseTAD-predicted boundaries are closer to CTCF sites and more conserved across cell lines**.
@@
 Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.](Figures/figure6.png)
+-->
 
@@
 
-The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model (Supplementary Figure 9).
+The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model (Additional file: Figure S9<!--Supplementary Figure 9-->).
 <!--We found that 88.8% and 95.8% [???
@@
 training on GM12878 and predicting boundaries on K562 (GM on K).
-Using Arrowhead-trained models, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries overlapped in both cross-cell-line prediction scenarios (Supplementary Figure 10A, 10B).
-Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlaps (Supplementary 10C, 10D).
-Furthermore, boundaries predicted on unseen annotation data exhibited similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Supplementary Figure 10).
+Using Arrowhead-trained models, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries overlapped in both cross-cell-line prediction scenarios (Additional file: Figure S10A, S10B<!--Supplementary Figure 10A, 10B-->).
+Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlaps (Additional file: Figure S10C, S10D<!--Supplementary 10C, 10D-->).
+Furthermore, boundaries predicted on unseen annotation data exhibited similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Additional file: Figure S10<!--Supplementary Figure 10-->).
 These results indicate that *preciseTAD* pre-trained models can be successfully used to predict domain boundaries for cell lines lacking Hi-C data but for which genome annotation data is available.
@@
 
-Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Supplementary Table 5).
+Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Additional file: Table S5<!--Supplementary Table 5-->).
 Our aim was to have a balanced metric sensitive to class imbalance such that it would not favor one component of the confusion matrix.
@@
 As a heuristic, we evaluated the pairwise combination of 3 different thresholds ($t=(0.975,0.99,1.0)$) and 6 different $\epsilon$ values ($\epsilon=(1000,5000,10000,15000,20000,25000)$)).
-We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (Supplementary Figure 11).
+We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (Additional file: Figure S11<!--Supplementary Figure 11-->).
 
@@
 The autosomal genomic coordinates in the GRCh37/hg19 human genome assembly were considered.
-Arrowhead-defined TAD boundaries were called from the GM12878 and K562 cell line Hi-C data (MAPQ>0, 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions) using the default parameters (Additional File 1).
-Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab website (Supplementary Table 1).
+Arrowhead-defined TAD boundaries were called from the GM12878 and K562 cell line Hi-C data (MAPQ>0, 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions) using the default parameters (Additional file: Arrowhead Script).
+Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab website (Additional file: Table S1<!--Supplementary Table 1-->).
 Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop anchor.
 Chromosome 9 was excluded from all downstream analyses due to the sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Supplementary Table 2).
+Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Additional file: Table 3<!--Supplementary Table 2-->).
 
@@
 A ($log_2 + 1$)-transformation of distance was used to account for the skewness of the distance distributions.
-Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin states lack signal values (Supplementary Figure 1).
+Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin states lack signal values (Additional file: Figure S1<!--Supplementary Figure 1-->).
 
@@
 To investigate whether we could alleviate the resolution limitations of conventional domain calling tools, we developed *preciseTAD*.
-This algorithm leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution (Supplementary Figure 2).
+This algorithm leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution (Additional file: Figure S4<!--Supplementary Figure 2-->).
 
@@
 The heuristic of $\epsilon$ is that density-reachable bases with genomic distances less than $\epsilon$ should occupy the same designated cluster.
-The default combination was set to $t=1.0$ and $\epsilon=10000$ based on our tests (Supplementary Figure 11).
+The default combination was set to $t=1.0$ and $\epsilon=10000$ based on our tests (Additional file: Figure S11<!--Supplementary Figure 11-->).
 
@@
 
+# Figure legends
+
+**Figure 1.
+Resolution-specific data construction and feature engineering for random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals using *shifted binning* (see Methods).
+The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD (or loop) boundary.
+(B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).
+
+**Figure 2.
+A machine learning framework for building domain boundary region prediction models.** Step 1 employs a range of feature engineering techniques to define the predictor matrix $A_{N \times (p)}$, where $N$ is the number of genomic bins, $p$ is the number of genomic annotations, $i$ is a holdout chromosome.
+The response vector $Y_N$ is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$).
+Step 2 reserves the predictor-response matrix for the holdout chromosome $i$ as the test data.
+Step 3 applies a resampling technique to the training data to address the class imbalance.
+Step 4 trains the random forest model and performs 3-fold cross-validation to tune the mtry parameter.
+Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and to evaluate model performance using balanced accuracy (BA).
+
+**Figure 3.
+Determining optimal data level characteristics for building TAD boundary region prediction models on GM12878.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Error bars indicate standard deviation from the mean performance across each holdout chromosome used for testing.
+
+**Figure 4.
+SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in GM12878.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+(B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
+Error bars represent 1 standard deviation from the mean cross-validated accuracy across each holdout chromosome.
+(C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs.
+The columns represent the holdout chromosome excluded from the training data.
+(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on GM12878 data (blue, Arrowhead ground truth; red, Peakachu ground truth) versus training on K562 and testing on GM12878 data (black, dashed).
+The curves represent the average sensitivities and specificities across each holdout chromosome.
+The shaded areas around each curve represent 1 standard deviation from the average.
+
+**Figure 5.
+preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of Arrowhead-called TAD boundaries (blue) vs.
+*preciseTAD*-predicted TAD boundaries (green) on GM12878 data (chr14:50085000-50800000).
+The black line represents the predicted probability of each base being a TAD boundary.
+(B) A zoomed-in portion of the genome shows the preciseTAD boundary region (PTBR, highlighted yellow), a cluster of bases with high probability of being a boundary, and the corresponding signal profiles of CTCF, RAD21, SMC3, and ZNF143.
+(C, D) Signal profile plots comparing the strength of CTCF, RAD21, SMC3, and ZNF143 binding around Arrowhead-called boundaries (blue, C), Peakachu loop boundaries (red, D) vs.
+*preciseTAD*-predicted boundaries (green).
+
+**Figure 6.
+preciseTAD-predicted boundaries are closer to CTCF sites and more conserved across cell lines**.
+(A) Log2 genomic distance distribution from called and predicted boundaries to nearest CTCF sites.
+The p-values are from the Wilcoxon Rank Sum test.
+(B-E) Venn diagrams illustrating the levels of conservation (overlap) between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead (B), Peakachu (D), *preciseTAD*-predicted boundaries using Arrowhead- and Peakachu-trained models () Arrowhead-trained *preciseTAD* models (C), Peakachu boundaries themselves (C, E, respectively).
+Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
+
+# Additional file legends
+
+**Arrowhead Script.** An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions.
+
+**Table S1.** Data sources for Hi-C matrices used to call topologically associating domains with Arrowhead, as well as loop boundaries obtained by Peakachu.
+
+**Table S2.** Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on K562.
+
+**Table S3.** A complete list of genomic annotations used to build the predictor space for all downstream models.
+The GRCh37/hg19 human genome assembly was used.
+“Genomic Class” - broad category of genomic features, “Element” - names of genomic features, “Cell line-Specific Source” - download URL specific to the cell line (not all annotations were provided by the same institutions).
+
+**Figure S1.
+The log_2 transformation of genomic distances normalizes their distributions.** Distances are measured as the number of bases from the center of a genomic bin to the nearest genomic annotation center.
+Density curves of distances before (red) and after (blue) performing a log_2 transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines.
+Each density curve represents an individual genomic annotation (77 total).
+
+**Figure S2.
+Determining optimal data level characteristics for building TAD boundary region prediction models on K562.** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562.
+(B) Averaged balanced accuracies are compared for GM12878 and (C) K562 within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.
+
+**Figure S3.
+SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in K562.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+(B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
+Error bars represent 1 standard deviation from the mean cross-validated accuracy across each holdout chromosome.
+(C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs.
+The columns represent the holdout chromosome excluded from the training data.
+(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on K562 data (blue, Arrowhead ground truth; red, Peakachu ground truth) versus training on GM12878 and testing on K5628 data (black, dashed).
+The curves represent the average sensitivities and specificities across each holdout chromosome.
+The shaded areas around each curve represent 1 standard deviation from the average.
+
+**Figure S4. Pseudocode of the *preciseTAD* algorithm.**
+
+**Table S4.** hg19/GRCh37 genomic coordinates of *preciseTAD*-predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562 cell lines, using models trained on Arrowhead TAD and Peakachu chromatin loop boundaries as ground truth.
+For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability of being a boundary equal to 1.
+For PTBPs, the start and end (start+1) coordinates define the most likely boundary point within each PTBR.
+
+**Figure S5.
+*preciseTAD* boundaries are enriched for known molecular drivers of 3D chromatin.** Signal profile plots comparing the binding strength of top TFBSs around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green) on K562, (B) Peakachu chromatin loop boundaries (red) and *preciseTAD* predicted loop boundaries (green) on K562, (C) Arrowhead called TAD boundaries (blue), Peakachu chromatin loop boundaries (red), and SpectralTAD called TAD boundaries (green) on GM12878 and (D) on K562.
+
+**Figure S6.
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Arrowhead boundaries.** Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called TAD boundaries vs.
+*preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
+
+**Figure S7.
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Peakachu boundaries.** Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Peakachu chromatin loop boundaries vs.
+*preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
+
+**Figure S8.
+*preciseTAD* boundaries are spatially closer to known molecular drivers of 3D chromatin.** Boxplots comparing the log2 genomic distance distributions from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
+p-values are derived from the Wilcoxon Rank Sum test.
+
+**Figure S9.
+The agreement between *preciseTAD*-predicted boundaries using Arrowhead- and Peakachu-trained models.** Venn diagrams of boundary overlaps using (A) GM12878 and (B) K562 data.
+Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
+
+**Figure S10.
+Pre-trained *preciseTAD* models accurately predict boundaries on cell lines using annotation data only.** Venn diagrams and signal profile plots comparing flanked predicted boundaries using Arrowhead (A, B) and Peakachu (C, D) trained models.
+(A, C) train on GM12878 and predict on GM12878 (red, GM on GM) vs.
+train on K562 and predict on GM12878 (blue, K on GM), (B, D) train on K562 predict on K562 (red, K on K) vs.
+train on GM12878 predict on K562 (blue, GM on K).
+Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
+
+**Table S5.** Additional performance metrics when implementing a random forest using Arrowhead/Peakachu ground truth TAD/loop boundaries.
+Performances are averaged across each holdout chromosome that was reserved for testing.
+
+**Figure S11.
+Normalized Enrichment levels suggest t=1.0 and $\epsilon$=10000 as the most optimal parameters for biologically relevant *preciseTAD*-predicted boundaries.** Linecharts illustrating the normalized enrichment (NE) between CTCF, RAD21, SMC3, ZNF143 and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps).
+NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model.
+Data from GM12878 (A) and K562 (B) cell lines, chromosome 22, at 5kb resolution was used.
+Error bars indicate standard deviation from the mean.
+
 # Declarations

### 2020-09-27 BMC_Genome_Biology_submission/cover_letter_Genome_Biology.Rmd
First cover letter draft

---
output:
  word_document:
    reference_docx: /Users/mdozmorov/Documents/Work/presentations/Templates/grant_template/styles.doc/NSF_grant_style.docx
  html_document: default
---

Dear Editor,

We are submitting our manuscript "preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution" to be considered for publication in _Genome Biology_. This manuscript will be of interest to the community studying the three-dimensional (3D) structure of the genome.

The main highlights of the software are:

- An R package implementing a comprehensive machine learning framework for predicting boundaries of 3D domains (topologically associating domains, chromatin loops) using one-dimensional (1D) genomic annotation data (e.g., ChIP-seq from ENCODE).

- Models pre-trained on Arrowhead-called TAD boundaries and Peakachu-called loop boundaries can predict domain boundaries in cells without Hi-C data using only genomic annotation data.

The main findings of our work are:

- Transcription factors, spatial relationships (distance within the linear genome) between them and boundaries, random undersampling are the necessary features for accurate boundary predictions.

- Only four transcription factors, CTCF, RAD21, SMC3, ZNF143, are necessary and sufficient for domain boundary predictions.

- Boundaries of TADs and loops are associated with the same genome annotation signatures.

- Biological properties of predicted domain boundaries include the highest genomic signal of CTCF and other transcription factors, more conservation across cell lines, closer proximity to other genomic signatures.

In summary, our systematic machine learning framework evaluates previously overlooked properties of 3D and 1D data, linking them into the most optimal model for domain boundary predictions. Our framework, implemented in the *preciseTAD* R package, and the pre-trained models enable leveraging widely available 1D genomic annotation data to predict the location of domain boundaries in cells without relatively rare 3D data. This improved precision in the domain boundary location can provide deeper insight into the association between genomic regulators and the 3D genome organization across cell lines.

The *preciseTAD* R package has been accepted to Bioconductor, https://bioconductor.org/packages/preciseTAD. Its source code is available on GitHub https://dozmorovlab.github.io/preciseTAD/. All data needed to reproduce our results are available from public repositories and publications. We also want to assure that this manuscript is not being considered for publication elsewhere.

With our best regards,  
On behalf of all authors,

Mikhail Dozmorov, Ph.D., Blick scholar  
Assistant Professor,  Department of Biostatistics 
Affiliate, Department of Pathology  
Virginia Commonwealth University  
One Capitol Square, room 738  
830 East Main Street  
Richmond,  Virginia  23298  
e-mail:  mikhail.dozmorov@vcuhealth.org  
Phone: 804-827-2055

### 2020-09-27 Manuscript/manuscript.Rmd

@@
 
-**Arrowhead Script.** An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions.
+**Additional File 1: Arrowhead Script.** An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions.
 
-**Table S1.** Data sources for Hi-C matrices used to call topologically associating domains with Arrowhead, as well as loop boundaries obtained by Peakachu.
+**Additional File 2: Table S1.** Data sources for Hi-C matrices used to call topologically associating domains with Arrowhead, as well as loop boundaries obtained by Peakachu.
 
-**Table S2.** Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on K562.
+**Additional File 3: Table S2.** Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on K562.
 
-**Table S3.** A complete list of genomic annotations used to build the predictor space for all downstream models.
+**Additional File 4: Table S3.** A complete list of genomic annotations used to build the predictor space for all downstream models.
 The GRCh37/hg19 human genome assembly was used.
@@
 
-**Figure S1.
+**Additional File 5: Figure S1.
 The log_2 transformation of genomic distances normalizes their distributions.** Distances are measured as the number of bases from the center of a genomic bin to the nearest genomic annotation center.
@@
 
-**Figure S2.
+**Additional File 6: Figure S2.
 Determining optimal data level characteristics for building TAD boundary region prediction models on K562.** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562.
@@
 
-**Figure S3.
+**Additional File 7: Figure S3.
 SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in K562.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
@@
 
-**Figure S4. Pseudocode of the *preciseTAD* algorithm.**
+**Additional File 8: Figure S4. Pseudocode of the *preciseTAD* algorithm.**
 
-**Table S4.** hg19/GRCh37 genomic coordinates of *preciseTAD*-predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562 cell lines, using models trained on Arrowhead TAD and Peakachu chromatin loop boundaries as ground truth.
+**Additional File 9: Table S4.** hg19/GRCh37 genomic coordinates of *preciseTAD*-predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562 cell lines, using models trained on Arrowhead TAD and Peakachu chromatin loop boundaries as ground truth.
 For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability of being a boundary equal to 1.
@@
 
-**Figure S5.
+**Additional File 10: Figure S5.
 *preciseTAD* boundaries are enriched for known molecular drivers of 3D chromatin.** Signal profile plots comparing the binding strength of top TFBSs around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green) on K562, (B) Peakachu chromatin loop boundaries (red) and *preciseTAD* predicted loop boundaries (green) on K562, (C) Arrowhead called TAD boundaries (blue), Peakachu chromatin loop boundaries (red), and SpectralTAD called TAD boundaries (green) on GM12878 and (D) on K562.
 
-**Figure S6.
+**Additional File 11: Figure S6.
 *preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Arrowhead boundaries.** Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called TAD boundaries vs.
@@
 
-**Figure S7.
+**Additional File 12: Figure S7.
 *preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Peakachu boundaries.** Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Peakachu chromatin loop boundaries vs.
@@
 
-**Figure S8.
+**Additional File 13: Figure S8.
 *preciseTAD* boundaries are spatially closer to known molecular drivers of 3D chromatin.** Boxplots comparing the log2 genomic distance distributions from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
@@
 
-**Figure S9.
+**Additional File 14: Figure S9.
 The agreement between *preciseTAD*-predicted boundaries using Arrowhead- and Peakachu-trained models.** Venn diagrams of boundary overlaps using (A) GM12878 and (B) K562 data.
@@
 
-**Figure S10.
+**Additional File 15: Figure S10.
 Pre-trained *preciseTAD* models accurately predict boundaries on cell lines using annotation data only.** Venn diagrams and signal profile plots comparing flanked predicted boundaries using Arrowhead (A, B) and Peakachu (C, D) trained models.
@@
 
-**Table S5.** Additional performance metrics when implementing a random forest using Arrowhead/Peakachu ground truth TAD/loop boundaries.
+**Additional File 16: Table S5.** Additional performance metrics when implementing a random forest using Arrowhead/Peakachu ground truth TAD/loop boundaries.
 Performances are averaged across each holdout chromosome that was reserved for testing.
 
-**Figure S11.
+**Additional File 17: Figure S11.
 Normalized Enrichment levels suggest t=1.0 and $\epsilon$=10000 as the most optimal parameters for biologically relevant *preciseTAD*-predicted boundaries.** Linecharts illustrating the normalized enrichment (NE) between CTCF, RAD21, SMC3, ZNF143 and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps).

### 2020-09-28 BMC_Genome_Biology_submission/cover_letter_Genome_Biology.Rmd
Small edits

@@
 
+- We provide genomic coordinates of the predicted TAD/loop boundaries for GM12878 and K562 cell lines.
+
 In summary, our systematic machine learning framework evaluates previously overlooked properties of 3D and 1D data, linking them into the most optimal model for domain boundary predictions.
@@
 Mikhail Dozmorov, Ph.D., Blick scholar  
-Assistant Professor,  Department of Biostatistics 
+Associate Professor,  Department of Biostatistics 
 Affiliate, Department of Pathology  

### 2020-09-28 Manuscript/manuscript.Rmd
Small edits
added numbers to additional files in body of manuscript

@@
 
-Hi-C, TAD, chromatin, machine learning, random forest, spatial clustering
+Hi-C, TAD, machine learning, random forest, DBSCAN
 
@@
 We used Arrowhead-called TAD boundaries [@durand2016juicer] and published Peakachu-predicted loop boundaries [@salameh2019supervised] as ground truth.
-Data from GM12878 and K565 cell lines at 5-100kb resolution (Arrowhead) and 10kb resolution (Peakachu) were used (Additional file: Arrowhead Script, Additional file: Table S1<!--Supplementary Table 1-->).
+Data from GM12878 and K565 cell lines at 5-100kb resolution (Arrowhead) and 10kb resolution (Peakachu) were used (Additional file 1: Arrowhead Script, Additional file 2: Table S1<!--Supplementary Table 1-->).
 We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base resolution from cell line-specific genome annotation data.
@@
 Boundary regions were defined as genomic bins containing a called boundary ($Y = 1$), while non-boundary regions were defined as bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
-The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Additional file: Table S2<!--Supplementary Table 3-->).
+The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Additional file 3: Table S2<!--Supplementary Table 3-->).
 The number of non-boundary regions highly outnumbered boundary regions.
@@
 A total of 77 cell line-specific genomic annotations were used to build the predictor space.
-These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Additional file: Table S3<!--Supplementary Table 2-->).
+These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Additional file 4: Table S3<!--Supplementary Table 2-->).
 Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
-These included signal strength association (Signal), direct (OC), proportional (OP), and spatial ($log_2 + 1$ Distance) relationships (see Methods, Additional file: Figure S1<!--Supplementary Figure 1-->).
+These included signal strength association (Signal), direct (OC), proportional (OP), and spatial ($log_2 + 1$ Distance) relationships (see Methods, Additional file 5: Figure S1<!--Supplementary Figure 1-->).
 
@@
 Additionally, we found that using a distance-type predictor space yielded substantially higher balanced accuracy compared to the peak signal strength, overlap count, and overlap percent predictor types.
-As with class balancing techniques, this improvement was less evident at lower resolutions, with results consistent for K562 (Additional file: Figure S2A<!--Supplementary Figure 3A-->).
-Random forest models built on Peakachu-defined loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Additional file: Figure S2B, S2C<!--Supplementary Figure 3B,3C-->).
+As with class balancing techniques, this improvement was less evident at lower resolutions, with results consistent for K562 (Additional file 6: Figure S2A<!--Supplementary Figure 3A-->).
+Random forest models built on Peakachu-defined loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Additional file 6: Figure S2B, S2C<!--Supplementary Figure 3B,3C-->).
 Furthermore, 5 kb resolution genomic bins led to the optimal prediction for both TAD and loop boundaries, on both cell lines.
@@
 Using the established optimal settings (RUS, Distance, 5 kb bins), we built separate random forest models using BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS).
-We found that models built on TFBSs outperformed other annotation-specific models, with results consistent for loop boundaries, on both cell lines (Figure 4A; Additional file: Figure S3A<!--Supplementary Figures 4A-->).
+We found that models built on TFBSs outperformed other annotation-specific models, with results consistent for loop boundaries, on both cell lines (Figure 4A; Additional file 7: Figure S3A<!--Supplementary Figures 4A-->).
 These results suggest that TFBS are the primary drivers of TAD and loop boundary formation in both GM12878 and K562.
@@
 We sought to further optimize our boundary region prediction models by recursive feature elimination to avoid overfitting and selecting only the most influential TFBS across all autosomal chromosomes.
-We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Additional file: Figure S3B<!--Supplementary Figures 4B-->).
+We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Additional file 7: Figure S3B<!--Supplementary Figures 4B-->).
 However, given that we trained our model on chromosome-specific data, the most significant annotations varied for each chromosome set.
 To determine transcription factors most important for boundary prediction across all chromosomes, we clustered the predictive importance (mean decrease in accuracy) of the top eight significant TFs across chromosomes.
-We found four transcription factors, CTCF, RAD21, SMC3, and ZNF143, being consistently predictive of TAD and loop boundaries (Figure 4C; Additional file: Figure S3C<!--Supplementary Figures 4C-->).
+We found four transcription factors, CTCF, RAD21, SMC3, and ZNF143, being consistently predictive of TAD and loop boundaries (Figure 4C; Additional file 7: Figure S3C<!--Supplementary Figures 4C-->).
 We optimized our model by only considering these top four TFBS when building the random forest model, thereby decreasing computational burden while maintaining high predictive performance.
@@
 AUC=0.881 and 0.874, respectively).
-These results were consistent when comparing training/testing strategies on K562 with training on GM12878 and testing on K562 data (Additional file: Figure S3D<!--Supplementary Figure 4D-->).
+These results were consistent when comparing training/testing strategies on K562 with training on GM12878 and testing on K562 data (Additional file 7: Figure S3D<!--Supplementary Figure 4D-->).
 The average ROC curves were found to be within 1 standard deviation of each other, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.
@@
 The model trained on a bin-level space was then applied on a base-level space to predict each base's probability of being a boundary.
-Our method, referred to as *preciseTAD*, uses density-based spatial clustering (DBSCAN) and partitioning around medoids (PAM) to predict the location of boundary regions and summit points (highest boundary probability) at base-level resolution (see Methods; Additional file: Figure S4<!--Supplementary Figure 2-->).
+Our method, referred to as *preciseTAD*, uses density-based spatial clustering (DBSCAN) and partitioning around medoids (PAM) to predict the location of boundary regions and summit points (highest boundary probability) at base-level resolution (see Methods; Additional file 8: Figure S4<!--Supplementary Figure 2-->).
 
-When trained using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, the *preciseTAD* model predicted a total of 12,258 TAD and 15,707 chromatin loop boundaries in GM12878, as well as 9,603 TAD and 11,154 chromatin loop boundaries in K562 cell line (Additional file: Table S4<!--Supplementary Table 4-->).
-We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Additional file: Table S2<!--Supplementary Table 3-->).
+When trained using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, the *preciseTAD* model predicted a total of 12,258 TAD and 15,707 chromatin loop boundaries in GM12878, as well as 9,603 TAD and 11,154 chromatin loop boundaries in K562 cell line (Additional file 9: Table S4<!--Supplementary Table 4-->).
+We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Additional file 3: Table S2<!--Supplementary Table 3-->).
 This can be attributed to Arrowhead's inflation of called TADs, that, when visualized, often do not correspond to domains enriched in internal interactions (Figure 5A) and signal of known drivers of domain boundaries (Figure 5B).
-*preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Additional file: Table S2<!--Supplementary Table 3-->).
+*preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Additional file 3: Table S2<!--Supplementary Table 3-->).
 This can be attributed to Peakachu's use of only CTCF sites to call boundaries, while *preciseTAD* leverages four known drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143.
@@
 Next, we evaluated the biological significance of *preciseTAD* boundary points.
-Signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (Figure 5C, 5D; Additional file: Figure S5A, S5B<!--Supplementary Figure 5A, 5B-->).
+Signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (Figure 5C, 5D; Additional file 10: Figure S5A, S5B<!--Supplementary Figure 5A, 5B-->).
 Surprised by the poor signal distribution around Arrowhead boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, and our SpectralTAD [@Cresswell:2020ab] TAD caller.
-We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the relatively well-performing Peakachu- and SpectralTAD-called boundaries (Additional file: Figure S5C, S5D<!--Supplementary Figure 5C, D-->).
-Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Additional file: Figure S6-S7<!--Supplementary Figures 6-7-->).
-*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBSs (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Additional file: Figure S8<!--Supplementary Figure 8-->).
+We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the relatively well-performing Peakachu- and SpectralTAD-called boundaries (Additional file 10: Figure S5C, S5D<!--Supplementary Figure 5C, D-->).
+Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Additional file 11-12: Figure S6-S7<!--Supplementary Figures 6-7-->).
+*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBSs (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Additional file 13: Figure S8<!--Supplementary Figure 8-->).
 These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
@@
 
-The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model (Additional file: Figure S9<!--Supplementary Figure 9-->).
+The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model (Additional file 14: Figure S9<!--Supplementary Figure 9-->).
 <!--We found that 88.8% and 95.8% [???
@@
 training on GM12878 and predicting boundaries on K562 (GM on K).
-Using Arrowhead-trained models, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries overlapped in both cross-cell-line prediction scenarios (Additional file: Figure S10A, S10B<!--Supplementary Figure 10A, 10B-->).
-Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlaps (Additional file: Figure S10C, S10D<!--Supplementary 10C, 10D-->).
-Furthermore, boundaries predicted on unseen annotation data exhibited similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Additional file: Figure S10<!--Supplementary Figure 10-->).
+Using Arrowhead-trained models, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries overlapped in both cross-cell-line prediction scenarios (Additional file 15: Figure S10A, S10B<!--Supplementary Figure 10A, 10B-->).
+Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlaps (Additional file 15: Figure S10C, S10D<!--Supplementary 10C, 10D-->).
+Furthermore, boundaries predicted on unseen annotation data exhibited similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Additional file 15: Figure S10<!--Supplementary Figure 10-->).
 These results indicate that *preciseTAD* pre-trained models can be successfully used to predict domain boundaries for cell lines lacking Hi-C data but for which genome annotation data is available.
@@
 
-Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Additional file: Table S5<!--Supplementary Table 5-->).
+Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Additional file 16: Table S5<!--Supplementary Table 5-->).
 Our aim was to have a balanced metric sensitive to class imbalance such that it would not favor one component of the confusion matrix.
@@
 As a heuristic, we evaluated the pairwise combination of 3 different thresholds ($t=(0.975,0.99,1.0)$) and 6 different $\epsilon$ values ($\epsilon=(1000,5000,10000,15000,20000,25000)$)).
-We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (Additional file: Figure S11<!--Supplementary Figure 11-->).
+We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (Additional file 17: Figure S11<!--Supplementary Figure 11-->).
 
@@
 The autosomal genomic coordinates in the GRCh37/hg19 human genome assembly were considered.
-Arrowhead-defined TAD boundaries were called from the GM12878 and K562 cell line Hi-C data (MAPQ>0, 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions) using the default parameters (Additional file: Arrowhead Script).
-Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab website (Additional file: Table S1<!--Supplementary Table 1-->).
+Arrowhead-defined TAD boundaries were called from the GM12878 and K562 cell line Hi-C data (MAPQ>0, 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions) using the default parameters (Additional file 1: Arrowhead Script).
+Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab website (Additional file 2: Table S1<!--Supplementary Table 1-->).
 Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop anchor.
 Chromosome 9 was excluded from all downstream analyses due to the sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Additional file: Table 3<!--Supplementary Table 2-->).
+Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Additional file 4: Table S3<!--Supplementary Table 2-->).
 
@@
 A ($log_2 + 1$)-transformation of distance was used to account for the skewness of the distance distributions.
-Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin states lack signal values (Additional file: Figure S1<!--Supplementary Figure 1-->).
+Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin states lack signal values (Additional file 5: Figure S1<!--Supplementary Figure 1-->).
 
@@
 To investigate whether we could alleviate the resolution limitations of conventional domain calling tools, we developed *preciseTAD*.
-This algorithm leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution (Additional file: Figure S4<!--Supplementary Figure 2-->).
+This algorithm leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution (Additional file 8: Figure S4<!--Supplementary Figure 2-->).
 
@@
 The heuristic of $\epsilon$ is that density-reachable bases with genomic distances less than $\epsilon$ should occupy the same designated cluster.
-The default combination was set to $t=1.0$ and $\epsilon=10000$ based on our tests (Additional file: Figure S11<!--Supplementary Figure 11-->).
+The default combination was set to $t=1.0$ and $\epsilon=10000$ based on our tests (Additional file 17: Figure S11<!--Supplementary Figure 11-->).
 

### 2020-09-28 BMC_Genome_Biology_submission/cover_letter_Genome_Biology.Rmd
added additonal bullet pt under main finding to echo main highlight

@@
 output:
+  pdf_document: default
+  html_document: default
   word_document:
-    reference_docx: /Users/mdozmorov/Documents/Work/presentations/Templates/grant_template/styles.doc/NSF_grant_style.docx
-  html_document: default
+    reference_docx: styles.doc/NSF_grant_style.docx
 ---
@@
 
-- Transcription factors, spatial relationships (distance within the linear genome) between them and boundaries, random undersampling are the necessary features for accurate boundary predictions.
+- Transcription factors, spatial relationships (distance within the linear genome) between them and boundaries, random under-sampling are the necessary features for accurate boundary predictions.
 
@@
 
-- Biological properties of predicted domain boundaries include the highest genomic signal of CTCF and other transcription factors, more conservation across cell lines, closer proximity to other genomic signatures.
+- Biological properties of domain boundaries predicted using *preciseTAD* include the highest genomic signal of CTCF and other transcription factors, closer proximity to other genomic signatures, and more conservation across cell lines.
 
 - We provide genomic coordinates of the predicted TAD/loop boundaries for GM12878 and K562 cell lines.
+
+- Across cell-line prediction results in similar boundary location as same cell-line prediction, giving rise to the possibility of predicting boundaries for cell-lines of which Hi-C data is currently unavailable.
 

### 2020-09-28 Manuscript/manuscript.Rmd
minor grammar corrections for background, results, discussion

@@
 The low resolution of high-throughput chromatin conformation capture data limits the precise mapping of boundaries of topologically associating domains and chromatin loops.
-We developed preciseTAD, an optimized random forest model trained on high-resolution genome annotation data (e.g., CTCF ChIP-seq) to predicts the location of domain boundaries at base-level resolution.
+We developed preciseTAD, an optimized random forest model trained on high-resolution genome annotation data (e.g., CTCF ChIP-seq) to predict the location of domain boundaries at base-level resolution.
 Distance between boundaries and annotations, random under-sampling, and transcription factor binding sites resulted in best model performance.
-preciseTAD boundaries were more enriched for CTCF, RAD21, SMC3, and ZNF143, conserved across cell lines.
-Using genome annotations, the pre-trained models can detect boundaries in cells without Hi-C data.
+preciseTAD boundaries were more enriched for CTCF, RAD21, SMC3, and ZNF143, and conserved across cell lines.
+Using genome annotations, pre-trained models can detect boundaries in cells without Hi-C data.
 preciseTAD is available at https://bioconductor.org/packages/preciseTAD
@@
 We present *preciseTAD*, an optimally tuned machine learning framework for precise identification of domain boundaries using genome annotation data.
-Our method utilizes the random forest (RF) algorithm trained on high-resolution chromatin state (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS) data to predict low-resolution boundaries.
-We introduce a systematic pipeline for building the optimal boundary prediction classifier.
-We found that spatial associations (linear distance) between boundaries and annotations perform best, transcription factor binding sites improve prediction accuracy, and a simple random undersampling technique effectively addresses the negative effect of class imbalance.
+Our method utilizes the random forest (RF) algorithm trained on high-resolution chromatin state (BroadHMM), histone modification (HM), and transcription factor binding site (TFBS) data to predict low-resolution boundaries.
+We introduce a systematic pipeline for building the optimal boundary region prediction classifier.
+We found that spatial associations (linear distance) between boundaries and annotations perform best, transcription factor binding sites improve prediction performance, and a simple random undersampling technique effectively addresses the negative effect of class imbalance.
 Translated from Hi-C data resolution level to base level (annotating each base and predicting its boundary probability), *preciseTAD* employs density-based clustering (DBSCAN) and partitioning around medoids (PAM) to detect genome annotation-guided boundary regions and points at a base-level resolution.
@@
 We demonstrate that *preciseTAD* predictions are more enriched for known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143.
-Further, we show that *preciseTAD*-detected boundaries are more conserved across cell lines, and the model trained in one cell line can predict boundaries in another cell line.
+Further, we show that *preciseTAD*-predicted boundaries are more conserved across cell lines, and the model trained in one cell line can predict boundaries in another cell line.
 This improved precision in the domain boundary location can provide insight into the association between genomic regulators and the 3D genome organization.
@@
 
-We developed a machine learning (ML) framework for determining the optimal set of data level characteristics to predict boundaries of Topologically Associating Domains (TADs) and chromatin loops, collectively referred to as domain boundaries.
+We developed a machine learning (ML) framework for determining the optimal set of data level characteristics to predict boundary regions of Topologically Associating Domains (TADs) and chromatin loops, collectively referred to as domain boundaries.
 We chose the random forest (RF) algorithm as our binary classification tool.
@@
 We used Arrowhead-called TAD boundaries [@durand2016juicer] and published Peakachu-predicted loop boundaries [@salameh2019supervised] as ground truth.
-Data from GM12878 and K565 cell lines at 5-100kb resolution (Arrowhead) and 10kb resolution (Peakachu) were used (Additional file 1: Arrowhead Script, Additional file 2: Table S1<!--Supplementary Table 1-->).
-We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base resolution from cell line-specific genome annotation data.
+Data from GM12878 and K562 cell lines at 5-100kb resolution (Arrowhead) and 10kb resolution (Peakachu) were used (Additional file 1: Arrowhead Script, Additional file 2: Table S1<!--Supplementary Table 1-->).
+We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base-level resolution from cell line-specific genome annotation data.
 
@@
 
-In total, we considered combinations of data from two cell lines *L = {GM12878, K562}*, five resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor space *P = {Signal, OC, OP, Distance}*, and three re-sampling technique *S = {None, RUS, ROS, SMOTE}* (Figure 2).
+In total, we considered combinations of data from two cell lines *L = {GM12878, K562}*, five resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor spaces *P = {Signal, OC, OP, Distance}*, and three re-sampling techniques *S = {None, RUS, ROS, SMOTE}* (Figure 2).
 Once the model inputs were established, a random forest classifier was trained on $n-1$ autosomal chromosomes, while reserving the $i^{th}$ chromosome for testing.
@@
 
-Additionally, we found that using a distance-type predictor space yielded substantially higher balanced accuracy compared to the peak signal strength, overlap count, and overlap percent predictor types.
+Additionally, we found that using a distance-type predictor space yielded substantially higher balanced accuracies compared to the peak signal strength, overlap count, and overlap percent predictor types.
 As with class balancing techniques, this improvement was less evident at lower resolutions, with results consistent for K562 (Additional file 6: Figure S2A<!--Supplementary Figure 3A-->).
-Random forest models built on Peakachu-defined loop boundaries with SMOTE resampling only marginally outperformed RUS for both GM12878 and K562 cell lines (Additional file 6: Figure S2B, S2C<!--Supplementary Figure 3B,3C-->).
-Furthermore, 5 kb resolution genomic bins led to the optimal prediction for both TAD and loop boundaries, on both cell lines.
+Furthermore, 5 kb resolution genomic bins led to the optimal prediction for TAD boundary regions, on both cell lines.
+Random forest models built on Peakachu-defined loop boundary regions yielded optimal prediction performance when using a distance-type predictor space, with SMOTE resampling only marginally outperforming RUS, for both cell lines (Additional file 6: Figure S2B, S2C<!--Supplementary Figure 3B,3C-->).
 Our results indicate that random under-sampling, distance-type predictors, and high-resolution Hi-C data provide the optimal set of data level characteristics for both TAD and chromatin loop boundary prediction.
@@
 We hypothesized that the type of genomic annotations may also affect predictive performance.
-Using the established optimal settings (RUS, Distance, 5 kb bins), we built separate random forest models using BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS).
+Using the established optimal settings (RUS, Distance, 5 kb/10 kb (Arrowhead/Peakachu ground truth) genomic bins), we built separate random forest models using histone modifications (HM), BroadHMM chromatin states (BroadHMM), and transcription factor binding sites (TFBS).
 We found that models built on TFBSs outperformed other annotation-specific models, with results consistent for loop boundaries, on both cell lines (Figure 4A; Additional file 7: Figure S3A<!--Supplementary Figures 4A-->).
@@
 
-We sought to further optimize our boundary region prediction models by recursive feature elimination to avoid overfitting and selecting only the most influential TFBS across all autosomal chromosomes.
+We sought to further optimize our boundary region prediction models by implementing recursive feature elimination to avoid overfitting and selecting only the most influential TFBS across all autosomal chromosomes.
 We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Additional file 7: Figure S3B<!--Supplementary Figures 4B-->).
-However, given that we trained our model on chromosome-specific data, the most significant annotations varied for each chromosome set.
+However, given that we trained our models on chromosome-specific data, the most significant annotations varied for each holdout chromosome.
 To determine transcription factors most important for boundary prediction across all chromosomes, we clustered the predictive importance (mean decrease in accuracy) of the top eight significant TFs across chromosomes.
@@
 We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Additional file 3: Table S2<!--Supplementary Table 3-->).
-This can be attributed to Arrowhead's inflation of called TADs, that, when visualized, often do not correspond to domains enriched in internal interactions (Figure 5A) and signal of known drivers of domain boundaries (Figure 5B).
+This can be attributed to Arrowhead's inflation of called TADs at 5 kb, that, when visualized, often do not correspond to domains enriched in internal interactions (Figure 5A) and signal of known drivers of domain boundaries (Figure 5B).
 *preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Additional file 3: Table S2<!--Supplementary Table 3-->).
@@
 Next, we evaluated the biological significance of *preciseTAD* boundary points.
-Signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (Figure 5C, 5D; Additional file 10: Figure S5A, S5B<!--Supplementary Figure 5A, 5B-->).
+The signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (Figure 5C, 5D; Additional file 10: Figure S5A, S5B<!--Supplementary Figure 5A, 5B-->).
 Surprised by the poor signal distribution around Arrowhead boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, and our SpectralTAD [@Cresswell:2020ab] TAD caller.
@@
 Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Additional file 11-12: Figure S6-S7<!--Supplementary Figures 6-7-->).
-*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBSs (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Additional file 13: Figure S8<!--Supplementary Figure 8-->).
+*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Additional file 13: Figure S8<!--Supplementary Figure 8-->).
 These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
@@
 To assess the level of cross-cell-line conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, Arrowhead, and Peakachu.
-Only 26% and 49% of boundaries were conserved between cell lines for Arrowhead and Peakachu boundaries (J=0.186 and J=0.388), respectively (Figure 6D, 6D.
+Only 26% and 49% of boundaries were conserved between cell lines for Arrowhead and Peakachu boundaries (J=0.186 and J=0.388), respectively (Figure 6B, 6D).
 However, 45%/56% of *preciseTAD*-predicted domain boundaries were conserved between GM12878 and K562 cell lines when using models trained on Arrowhead/Peakachu data (J=0.383 and J=0.444, respectively, Figure 6C, 6E).
@@
 Using Arrowhead-trained models, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries overlapped in both cross-cell-line prediction scenarios (Additional file 15: Figure S10A, S10B<!--Supplementary Figure 10A, 10B-->).
-Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlaps (Additional file 15: Figure S10C, S10D<!--Supplementary 10C, 10D-->).
+Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlap (Additional file 15: Figure S10C, S10D<!--Supplementary 10C, 10D-->).
 Furthermore, boundaries predicted on unseen annotation data exhibited similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Additional file 15: Figure S10<!--Supplementary Figure 10-->).
@@
 
-Using the provided pre-trained models, *preciseTAD* is able to identify precise domain boundaries using cell line-specific genome annotation information of only four transcription factors, CTCF, SMC3, RAD21, ZNF143.
+Using the provided pre-trained models, *preciseTAD* is able to identify precise domain boundaries using cell line-specific genome annotation information of only four transcription factors including CTCF, SMC3, RAD21, and ZNF143.
 Although the ENCODE, NIH Roadmap Epigenomics, FANTOM5, BLUEPRINT, and other members of the International Human Epigenome Consortium (IHEC) [@Stunnenberg:2016aa] have been actively cataloging cell line-specific genome annotation datasets, these data remain very sparse.
@@
 In summary, we demonstrate that domain boundary prediction is a multi-faceted problem requiring consideration of multiple statistical and biological properties of genomic data.
-Simply considering the properties of Hi-C contact matrices ignores the fundamental roles of known molecular drivers of the 3D chromatin structures.
+Simply considering the properties of Hi-C contact matrices ignores the fundamental roles of known molecular drivers of 3D chromatin structures.
 Instead, we propose *preciseTAD*, a supervised machine learning framework that leverages both Hi-C contact matrix information and genomic annotations.

### 2020-09-28 Manuscript/manuscript.Rmd
grammar edits to methods

@@
 This improved precision in the domain boundary location can provide insight into the association between genomic regulators and the 3D genome organization.
-The *preciseTAD* R package is freely available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor (submitted).
+The *preciseTAD* R package is freely available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor.
 
@@
 
-TAD and loop boundaries called by Arrowhead [@durand2016juicebox] and Peakachu [@salameh2019supervised] tools were used for training.
+TAD and loop boundaries called by Arrowhead [@durand2016juicebox] and Peakachu [@salameh2019supervised] tools were used for training and testing.
 The autosomal genomic coordinates in the GRCh37/hg19 human genome assembly were considered.
-Arrowhead-defined TAD boundaries were called from the GM12878 and K562 cell line Hi-C data (MAPQ>0, 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions) using the default parameters (Additional file 1: Arrowhead Script).
+Arrowhead-defined TAD boundaries were called from Hi-C data for the GM12878 and K562 cell lines (MAPQ>0, 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions) using the default parameters (Additional file 1: Arrowhead Script).
 Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab website (Additional file 2: Table S1<!--Supplementary Table 1-->).
@@
 Bins were annotated by one of either the average signal strength of the corresponding annotation (*Peak Signal Strength*), the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*) (Figure 1B).
-A ($log_2 + 1$)-transformation of distance was used to account for the skewness of the distance distributions.
-Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin states lack signal values (Additional file 5: Figure S1<!--Supplementary Figure 1-->).
+A ($log_2 + 1$)-transformation of distance was used to account for the skewness of the distance distributions  (Additional file 5: Figure S1<!--Supplementary Figure 1-->).
+Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin states lack signal values.
 
@@
 Random forest (RF) classification models (the `caret` v.6.0 R package [@kuhn2012caret]) were built to compare model performances between combinations of data resolutions, feature engineering procedures, and resampling techniques.
-Following recommendations to evaluate the model on unseen data [@schreiber2019pitfall], a *holdout chromosome* technique was used for estimating model's performance.
+Following recommendations to evaluate the model on unseen data [@schreiber2019pitfall], a *holdout chromosome* technique was used for estimating model performance.
 The $i^{th}$ holdout chromosome was identified and a data matrix, $A_{N \times (p+1)}$, was constructed by combining the binned genome from the remaining chromosomes ($1,2,\cdots, i-1,i+1,\cdots,21,22$), where $N=[n_{1} n_{2} \cdots n_{21} n_{22}]'$ and $n_{k}$ is the length of chromosome *k* after being binned into non-overlapping regions of resolution *r*, such that $k \ne i$.
-$p$, the number of annotations, together with the response vector, **Y**, defined the column-wise dimension of the matrix $A$.
+The number of annotations, $p$, together with the response vector, **Y**, defined the column-wise dimension of the matrix $A$.
 Re-sampling was then performed on $A$, and an RF classifier was trained using 3-fold cross-validation to tune for the number of annotations to consider at each node (*mtry*).
@@
 Each of these quantities is obtained from the confusion matrix created by validating the model on the test data.
-The process was repeated for each $i^{th}$ holdout chromosome, and performances were aggregated using mean and standard deviation.
+The process was repeated for each $i^{th}$ holdout chromosome, and performances were aggregated using the mean and standard deviation.
 
@@
 Second, we evaluated models trained on cell line-specific data from $n-1$ chromosomes using the $i^{th}$ holdout chromosome data from a different cell line.
-That is, models trained using K562 cell line-specific data were evaluated on unseen chromosome data from GM12878 cell line.
+That is, models trained using K562 cell line-specific data were evaluated on unseen chromosome data from the GM12878 cell line.
 This process was repeated for each holdout chromosome.
@@
 To investigate whether we could alleviate the resolution limitations of conventional domain calling tools, we developed *preciseTAD*.
-This algorithm leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base resolution (Additional file 8: Figure S4<!--Supplementary Figure 2-->).
+This algorithm leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base-level resolution (Additional file 8: Figure S4<!--Supplementary Figure 2-->).
 
@@
 To precisely identify boundary locations, we first constructed a _base-level resolution_ predictor space for the chromosome *i*, $A_{n \times p}$, where $n$ is the length of chromosome $i$ and $p$ is the optimal number of annotations.
-We then evaluate $M$ on the base-level predictor space to extract the probability vector, $\pi_{n_{i}}$, denoting each base's probability of being a boundary.
-Here, $n_{i}$ represents the length of chromosome *i*.
-A threshold $t$ specifies the probability at which a base with $\pi_{n_{i}} \ge t$ is designated as a potential boundary (the default $t=1$).
-Next, density-based spatial clustering of applications with noise (DBSCAN; version 1.1-5) is applied to the matrix of pairwise genomic distances between boundary-annotated bases, $D$.
+We then evaluate $M$ on the base-level predictor space to extract the probability vector, $\pi_{n}$, denoting each base's probability of being a boundary.
+A threshold $t$ specifies the probability at which a base with $\pi_{n} \ge t$ is designated as a potential boundary (the default $t=1$).
+Next, density-based spatial clustering of applications with noise (DBSCAN; version 1.1-5) is applied to the matrix of pairwise genomic distances between boundary-annotated bases, $D$, such that $\pi_{n} \ge t$.
 The minimum and maximum coordinates of each cluster, $k$, of spatially colocalized bases were termed *preciseTAD boundary regions* (PTBR).
@@
 
-$$NE = \dfrac{1}{p} \left[ \Sigma_{s=1}^{p} \left[ \dfrac{1}{b} \Sigma_{k=1}^{b} e_{ks} \times c_{k} \right] \right]$$
+$$NE = \dfrac{1}{p} \left[ \Sigma_{s=1}^{p} \left[ \dfrac{1}{b} \Sigma_{k=1}^{b} e_{ks} \right] \right]$$
 
@@
 Wilcoxon Rank-Sum tests were used to compare chromosome-specific Jaccard indices across cell lines, between *preciseTAD* boundaries and both Arrowhead and Peakachu boundaries, respectively.
-All statistical analyses were performed in R version 4.0.1.
+All statistical analyses were performed in R (version 4.0.1).
 The significance level was set to 0.05 for all statistical tests.

### 2020-09-28 BMC_Genome_Biology_submission/cover_letter_Genome_Biology.Rmd
changed path
Polishing cover letter

@@
   word_document:
-    reference_docx: styles.doc/NSF_grant_style.docx
+    reference_docx: ../Manuscript/styles.doc/NSF_grant_style.docx
 ---
 
-Dear Editor,
+To the Editor of the "Regulatory Elements" special issue
 
-We are submitting our manuscript "preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution" to be considered for publication in _Genome Biology_.
-This manuscript will be of interest to the community studying the three-dimensional (3D) structure of the genome.
+Dear Dr. Sands,
 
-The main highlights of the software are:
+We are submitting our manuscript "preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution" to be considered for the special issue "Regulatory Elements" in _Genome Biology_.
+This manuscript will be of interest to the community studying the regulatory associations within the three-dimensional (3D) genome structure.
 
-- An R package implementing a comprehensive machine learning framework for predicting boundaries of 3D domains (topologically associating domains, chromatin loops) using one-dimensional (1D) genomic annotation data (e.g., ChIP-seq from ENCODE).
+Our manuscript is submitted for the "Software" section. The main highlights of the software are:
 
-- Models pre-trained on Arrowhead-called TAD boundaries and Peakachu-called loop boundaries can predict domain boundaries in cells without Hi-C data using only genomic annotation data.
+- A Bioconductor R package *preciseTAD* implementing a comprehensive machine learning framework for predicting boundaries of 3D domains (topologically associating domains (TADs), chromatin loops) using one-dimensional (1D) regulatory genomic annotation data (e.g., ChIP-seq from ENCODE).
+
+- *preciseTAD* can be used to refine the location of domain boundaries and identify de novo boundaries missed by conventional TAD/loop callers.
+
+- *preciseTAD* prioritizes genomic signatures associated with domain boundaries.
+Trained on any 3D genomic features (e.g., besides TAD/loop boundaries, regions of A/B compartment switching, frequently interacting regions (FIREs), differentially interacting chromatin regions, etc.), *preciseTAD* defines (epi)genomic signatures most predictive of those features.
+
+- The provided models pre-trained on Arrowhead-called TAD boundaries and Peakachu-called loop boundaries can predict domain boundaries in cells without Hi-C data using only genomic annotation data.
 
@@
 
-- Transcription factors, spatial relationships (distance within the linear genome) between them and boundaries, random under-sampling are the necessary features for accurate boundary predictions.
+- Transcription factors, spatial relationships (distance within the linear genome) between them and boundaries, random under-sampling are the critical features needed for accurate boundary predictions.
 
-- Only four transcription factors, CTCF, RAD21, SMC3, ZNF143, are necessary and sufficient for domain boundary predictions.
+- Only four transcription factors, CTCF, RAD21, SMC3, ZNF143, are sufficient for domain boundary predictions.
 
-- Boundaries of TADs and loops are associated with the same genome annotation signatures.
+- Boundaries of TADs and loops are associated with the same genome annotation signatures, suggesting similar mechanisms of their formation.
 
@@
 
-- Across cell-line prediction results in similar boundary location as same cell-line prediction, giving rise to the possibility of predicting boundaries for cell-lines of which Hi-C data is currently unavailable.
+In summary, our systematic machine learning framework evaluates previously overlooked properties of 3D interactions and 1D regulatory data, linking them into the most optimal model for domain boundary predictions.
+This improved precision in the domain boundary location can provide deeper insight into the association between genomic regulators and the 3D genome organization.
 
-In summary, our systematic machine learning framework evaluates previously overlooked properties of 3D and 1D data, linking them into the most optimal model for domain boundary predictions.
-Our framework, implemented in the *preciseTAD* R package, and the pre-trained models enable leveraging widely available 1D genomic annotation data to predict the location of domain boundaries in cells without relatively rare 3D data.
-This improved precision in the domain boundary location can provide deeper insight into the association between genomic regulators and the 3D genome organization across cell lines.
-
-The *preciseTAD* R package has been accepted to Bioconductor, https://bioconductor.org/packages/preciseTAD.
-Its source code is available on GitHub https://dozmorovlab.github.io/preciseTAD/.
+The *preciseTAD* R package is available on Bioconductor, https://bioconductor.org/packages/preciseTAD.
+Its source code is freely available on GitHub https://dozmorovlab.github.io/preciseTAD/.
 All data needed to reproduce our results are available from public repositories and publications.

### 2020-09-28 Manuscript/manuscript.Rmd

@@
 We used Arrowhead-called TAD boundaries [@durand2016juicer] and published Peakachu-predicted loop boundaries [@salameh2019supervised] as ground truth.
-Data from GM12878 and K562 cell lines at 5-100kb resolution (Arrowhead) and 10kb resolution (Peakachu) were used (Additional file 1: Arrowhead Script, Additional file 2: Table S1<!--Supplementary Table 1-->).
+Data from GM12878 and K562 cell lines at 5-100 kb resolution (Arrowhead) and 10 kb resolution (Peakachu) were used (Additional file 1: Arrowhead Script, Additional file 2: Table S1<!--Supplementary Table 1-->).
 We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base-level resolution from cell line-specific genome annotation data.
@@
 The columns represent the holdout chromosome excluded from the training data.
+Rows are sorted in decreasing order according to the columnwise average importance.
 (D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on GM12878 data (blue, Arrowhead ground truth; red, Peakachu ground truth) versus training on K562 and testing on GM12878 data (black, dashed).
@@
 preciseTAD-predicted boundaries are closer to CTCF sites and more conserved across cell lines**.
-(A) Log2 genomic distance distribution from called and predicted boundaries to nearest CTCF sites.
+(A) $log_{2}$ genomic distance distribution from called and predicted boundaries to nearest CTCF sites.
 The p-values are from the Wilcoxon Rank Sum test.
-(B-E) Venn diagrams illustrating the levels of conservation (overlap) between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead (B), Peakachu (D), *preciseTAD*-predicted boundaries using Arrowhead- and Peakachu-trained models () Arrowhead-trained *preciseTAD* models (C), Peakachu boundaries themselves (C, E, respectively).
+(B-E) Venn diagrams illustrating the levels of conservation (overlap) between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead (B), Peakachu (D), and *preciseTAD*-predicted boundaries using (C) Arrowhead- and (E) Peakachu-trained models.
 Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
@@
 
-**Additional File 1: Arrowhead Script.** An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5kb, 10kb, 25kb, 50kb, 100kb resolutions.
+**Additional File 1: Arrowhead Script.** An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5 kb, 10 kb, 25 kb, 50 kb, 100 kb resolutions.
 
@@
 **Additional File 5: Figure S1.
-The log_2 transformation of genomic distances normalizes their distributions.** Distances are measured as the number of bases from the center of a genomic bin to the nearest genomic annotation center.
-Density curves of distances before (red) and after (blue) performing a log_2 transformation across 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines.
+The $log_2$ transformation of genomic distances normalizes their distributions.** Distances are measured as the number of bases from the center of a genomic bin to the nearest genomic annotation center.
+Density curves of distances before (red) and after (blue) performing a $log_2$ transformation across 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines.
 Each density curve represents an individual genomic annotation (77 total).
@@
 Determining optimal data level characteristics for building TAD boundary region prediction models on K562.** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562.
-(B) Averaged balanced accuracies are compared for GM12878 and (C) K562 within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.
+Averaged balanced accuracies are compared for Peakachu-trained models built on (B) GM12878 and (C) K562 within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.
 
@@
 The columns represent the holdout chromosome excluded from the training data.
+Rows are sorted in decreasing order according to the columnwise average importance.
 (D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on K562 data (blue, Arrowhead ground truth; red, Peakachu ground truth) versus training on GM12878 and testing on K5628 data (black, dashed).
@@
 **Additional File 10: Figure S5.
-*preciseTAD* boundaries are enriched for known molecular drivers of 3D chromatin.** Signal profile plots comparing the binding strength of top TFBSs around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green) on K562, (B) Peakachu chromatin loop boundaries (red) and *preciseTAD* predicted loop boundaries (green) on K562, (C) Arrowhead called TAD boundaries (blue), Peakachu chromatin loop boundaries (red), and SpectralTAD called TAD boundaries (green) on GM12878 and (D) on K562.
+*preciseTAD* boundaries are enriched for known molecular drivers of 3D chromatin.** Signal profile plots comparing the binding strength of top TFBS around flanked (A) Arrowhead called TAD boundaries (blue) and *preciseTAD*-predicted TAD boundaries (green) on K562, (B) Peakachu chromatin loop boundaries (red) and *preciseTAD* predicted loop boundaries (green) on K562, (C) Arrowhead called TAD boundaries (blue), Peakachu chromatin loop boundaries (red), and SpectralTAD called TAD boundaries (green) on GM12878 and (D) on K562.
 
 **Additional File 11: Figure S6.
-*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Arrowhead boundaries.** Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called TAD boundaries vs.
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Arrowhead boundaries.** Enrichment heatmaps comparing the signal distribution of CTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called TAD boundaries vs.
 *preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
@@
 **Additional File 12: Figure S7.
-*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Peakachu boundaries.** Enrichment heatmaps comparing the signal distribution ofCTCF, RAD21, SMC3, and ZNF143 around Peakachu chromatin loop boundaries vs.
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Peakachu boundaries.** Enrichment heatmaps comparing the signal distribution of CTCF, RAD21, SMC3, and ZNF143 around Peakachu-predicted chromatin loop boundaries vs.
 *preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
@@
 Pre-trained *preciseTAD* models accurately predict boundaries on cell lines using annotation data only.** Venn diagrams and signal profile plots comparing flanked predicted boundaries using Arrowhead (A, B) and Peakachu (C, D) trained models.
-(A, C) train on GM12878 and predict on GM12878 (red, GM on GM) vs.
-train on K562 and predict on GM12878 (blue, K on GM), (B, D) train on K562 predict on K562 (red, K on K) vs.
-train on GM12878 predict on K562 (blue, GM on K).
+(A, C) Models trained on GM12878 and predicted on GM12878 (red, GM on GM) vs.
+models trained on K562 and predicted on GM12878 (blue, K on GM), (B, D) models trained on K562 and predicted on K562 (red, K on K) vs.
+models trained on GM12878 and predicted on K562 (blue, GM on K).
 Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
@@
 NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model.
-Data from GM12878 (A) and K562 (B) cell lines, chromosome 22, at 5kb resolution was used.
-Error bars indicate standard deviation from the mean.
+Data from GM12878 (A) and K562 (B) cell lines, chromosome 22, at 5 kb resolution was used.
+Error bars indicate 1 standard deviation from the mean.
 

### 2020-09-28 Manuscript/manuscript.Rmd
simplify BioC availability
knit to word

@@
 output:
+  word_document:
+    reference_docx: styles.doc/Arial_11_double_space_normal_margins.docx
   pdf_document: 
     extra_dependencies: ["float"]
-  word_document:
-    reference_docx: styles.doc/Arial_11_double_space_normal_margins.docx
 bibliography: References/references.bib

### 2020-09-29 Manuscript/manuscript.Rmd
uncommented figures for bioarxiv submission

--- 2020-09-28 Manuscript/manuscript.Rmd
@@
 This improved precision in the domain boundary location can provide insight into the association between genomic regulators and the 3D genome organization.
-The *preciseTAD* R package is freely available on https://dozmorovlab.github.io/preciseTAD/ and Bioconductor.
+The *preciseTAD* R package is freely available on https://bioconductor.org/packages/preciseTAD.
 
@@
 
-<!--
 ![**Resolution-specific data construction and feature engineering for random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals using *shifted binning* (see Methods).
@@
 (B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png)
--->
 
@@
 |:---------------------:|:-----------------:|:--------------------------------------------------:|:-----------------------------------------------------------:|:-----------------------------------:|:----------------------:|
-|        Arrowhead      |       5   kb      |                         8,052                       |                             15,468                           |                535,363               |           0.03         |
-|     Arrowhead         |       10   kb     |                         7,676                       |                             14,253                           |                267,682               |           0.05         |
-|     Arrowhead         |       25   kb     |                         4,670                       |                             8,363                            |                107,073               |           0.08         |
-|     Arrowhead         |       50   kb     |                         2,349                       |                             4,224                            |                 53,537               |           0.08         |
-|     Arrowhead         |      100   kb     |                         1,031                       |                             1,883                            |                 26,768               |           0.07         |
-|        Peakachu       |       10   kb     |                        16,185                       |                          21,421                              |                267,682               |        0.14            |
+|        Arrowhead      |       5   kb      |                         8052                       |                             15468                           |                535363               |           0.03         |
+|     Arrowhead         |       10   kb     |                         7676                       |                             14253                           |                267682               |           0.05         |
+|     Arrowhead         |       25   kb     |                         4670                       |                             8363                            |                107073               |           0.08         |
+|     Arrowhead         |       50   kb     |                         2349                       |                             4224                            |                 53537               |           0.08         |
+|     Arrowhead         |      100   kb     |                         1031                       |                             1883                            |                 26768               |           0.07         |
+|        Peakachu       |       10   kb     |                        16185                       |                          21421                              |                267682               |        0.14            |
 Table: Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on GM12878.
@@
 
-<!--
 ![**A machine learning framework for building domain boundary region prediction models.** Step 1 employs a range of feature engineering techniques to define the predictor matrix $A_{N \times (p)}$, where $N$ is the number of genomic bins, $p$ is the number of genomic annotations, $i$ is a holdout chromosome.
@@
 Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and to evaluate model performance using balanced accuracy (BA).](Figures/figure2.png)
--->
 
@@
 
-<!--
 ![**Determining optimal data level characteristics for building TAD boundary region prediction models on GM12878.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
 Error bars indicate standard deviation from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
--->
 
@@
 
-<!--
 ![**SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in GM12878.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
@@
 The shaded areas around each curve represent 1 standard deviation from the average.](Figures/figure4.png)
--->
 
@@
 
-<!--
 ![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of Arrowhead-called TAD boundaries (blue) vs.
@@
 *preciseTAD*-predicted boundaries (green).](Figures/figure5.png)
--->
 
@@
 
-<!--
 ![**preciseTAD-predicted boundaries are closer to CTCF sites and more conserved across cell lines**.
@@
 Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.](Figures/figure6.png)
--->
 
@@
 
+<!--
 # Figure legends
@@
 Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
+-->
 

### 2020-09-29 Manuscript/manuscript.Rmd
More touches

@@
 ^1^ Dept. of Biostatistics, Virginia Commonwealth University, Richmond, VA, 23298, USA  
-^\*^ To whom correspondence should be addressed: Virginia Commonwealth University, Richmond, VA, 23298, 804-827-2055, mikhail.dozmorov@vcuhealth.org
+^\*^ To whom correspondence should be addressed<!--: Virginia Commonwealth University, Richmond, VA, 23298, 804-827-2055, mikhail.dozmorov@vcuhealth.org-->
 
@@
 The model pre-trained in one cell line performs well in another cell line.
-Using cell line-specific genomic annotations, the pre-trained models enable the detection of domain boundaries in cells without Hi-C data.
+Using cell line-specific genomic annotations, the pre-trained models enable detecting domain boundaries in cells without Hi-C data.
 
@@
 At the kilobase scale, chromatin loops connect gene promoters with distal enhancers, thereby regulating gene expression [@Lupianez:2015aa; @Franke:2016aa].
-At the megabase scale, TADs represent regions on the linear genome, that are highly self-interacting.
+At the megabase scale, TADs represent regions on the linear genome that are highly self-interacting.
 <!--Emerging evidence has linked TADs to critical roles in cell dynamics and cell differentiation.
@@
 While these low-resolution Hi-C datasets can be used to probe higher-order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define TAD and loop boundaries [@fudenberg2016formation].
-Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth [@schmitt2016genome], obtaining high resolution remains difficult.
+Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth [@schmitt2016genome], obtaining high-resolution HI-C data and boundaries remains difficult.
 
@@
 The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD (or loop) boundary.
-(B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png)
+(B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space, including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png)
 
 Boundary regions were defined as genomic bins containing a called boundary ($Y = 1$), while non-boundary regions were defined as bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
-The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Additional file 3: Table S2<!--Supplementary Table 3-->).
+The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Additional file 3: Table S2[???
+Wrong]<!--Supplementary Table 3-->).
 The number of non-boundary regions highly outnumbered boundary regions.
@@
 A total of 77 cell line-specific genomic annotations were used to build the predictor space.
-These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Additional file 4: Table S3<!--Supplementary Table 2-->).
+These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Additional file 4: Table S3[???
+Wrong]<!--Supplementary Table 2-->).
 Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
@@
 Step 4 trains the random forest model and performs 3-fold cross-validation to tune the mtry parameter.
-Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and to evaluate model performance using balanced accuracy (BA).](Figures/figure2.png)
+Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and evaluates model performance using balanced accuracy (BA).](Figures/figure2.png)
 
@@
 
-Additionally, we found that using a distance-type predictor space yielded substantially higher balanced accuracies compared to the peak signal strength, overlap count, and overlap percent predictor types.
+Additionally, we found that using a distance-type predictor space yielded substantially higher balanced accuracy than the peak signal strength, overlap count, and overlap percent predictor types.
 As with class balancing techniques, this improvement was less evident at lower resolutions, with results consistent for K562 (Additional file 6: Figure S2A<!--Supplementary Figure 3A-->).
-Furthermore, 5 kb resolution genomic bins led to the optimal prediction for TAD boundary regions, on both cell lines.
+Furthermore, 5 kb resolution genomic bins led to the optimal prediction for TAD boundary regions on both cell lines.
 Random forest models built on Peakachu-defined loop boundary regions yielded optimal prediction performance when using a distance-type predictor space, with SMOTE resampling only marginally outperforming RUS, for both cell lines (Additional file 6: Figure S2B, S2C<!--Supplementary Figure 3B,3C-->).
@@
 
-Having demonstrated the optimal performance in our framework's ability to predict boundary regions, we next attempted to predict boundary regions in one cell line using the model pre-trained on data from another another cell line (See Methods).
-We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from GM12878 cell line resulted in an average AUC=0.792 (Figure 4D).
+Having demonstrated the optimal performance in our framework's ability to predict boundary regions, we next attempted to predict boundary regions in one cell line using the model pre-trained on data from another cell line (See Methods).
+We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from the GM12878 cell line resulted in an average AUC=0.792 (Figure 4D).
 Interestingly, when training on the K562 cell line and testing on GM12878, the average AUC increased slightly to 0.795.
-Likewise, the average performance of models trained using Peakachu boundaries and genomic annotation data from GM12878 cell line was comparable to models trained on K562-specific Peakachu boundaries and genomic annotations (Avg.
+Likewise, the average performance of models trained using Peakachu boundaries and genomic annotation data from the GM12878 cell line was comparable to models trained on K562-specific Peakachu boundaries and genomic annotations (Avg.
 AUC=0.881 and 0.874, respectively).
@@
 ![**preciseTAD-predicted boundaries are closer to CTCF sites and more conserved across cell lines**.
-(A) Log2 genomic distance distribution from called and predicted boundaries to nearest CTCF sites.
+(A) Log2 genomic distance distribution from called and predicted boundaries to the nearest CTCF sites.
 The p-values are from the Wilcoxon Rank Sum test.
@@
 <!--We found that 88.8% and 95.8% [???
-These numbers are different from what is shown on Supp Fig 9; !!!the %'s shown are (left region)/(left + middle); should I take out the percentages in the figure?
+These numbers are different from what is shown in Supp Fig 9; !!!the %'s shown are (left region)/(left + middle); should I take out the percentages in the figure?
 ???
@@
 Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlap (Additional file 15: Figure S10C, S10D<!--Supplementary 10C, 10D-->).
-Furthermore, boundaries predicted on unseen annotation data exhibited similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Additional file 15: Figure S10<!--Supplementary Figure 10-->).
+Furthermore, boundaries predicted on unseen annotation data exhibited a similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Additional file 15: Figure S10<!--Supplementary Figure 10-->).
 These results indicate that *preciseTAD* pre-trained models can be successfully used to predict domain boundaries for cell lines lacking Hi-C data but for which genome annotation data is available.
@@
 We first optimized our RF model by systematically comparing different combinations of genome binning (resolution), feature engineering procedures, and resampling techniques.
-Our results demonstrate that genomic distance between boundary regions and genomic annotations coupled with random under-sampling results in best model performance.
+Our results demonstrate that genomic distance between boundary regions and genomic annotations coupled with random under-sampling results in the best model performance.
 We show that binding of four transcription factors (SMC3, RAD21, CTCF, ZNF143) is sufficient for accurate boundary predictions.
@@
 AUROC captures how a model generally performs across different thresholds.
-However, it doesn't place more emphasis on one class over the other, so it does not reflect the minority class well.
+However, it doesn't emphasize one class over the other, so it does not reflect the minority class well.
 Precision indicates the rate at which positive predictions are correct and can be artificially deflated by low proportions of true positives (TP), the set of genomic bins correctly predicted as containing a ground truth boundary.
@@
 Yet, the preciseTAD boundary points (PTBPs, medoids identified within each PTBR) had the highest density of CTCF and other transcription factor binding signal (Figure 5).
-Our results are in line with the emergent view that domain boundaries are dynamic [@chang2020tads] and their well-defined location arise as a consequence of the population average in bulk Hi-C data [@fudenberg2016formation; @Flyamer:2017aa].
+Our results are in line with the emergent view that domain boundaries are dynamic [@chang2020tads], and their well-defined location arises as a consequence of the population average in bulk Hi-C data [@fudenberg2016formation; @Flyamer:2017aa].
 
@@
 
-Using the provided pre-trained models, *preciseTAD* is able to identify precise domain boundaries using cell line-specific genome annotation information of only four transcription factors including CTCF, SMC3, RAD21, and ZNF143.
+Using the provided pre-trained models, *preciseTAD* can identify precise domain boundaries using cell line-specific genome annotation information of only four transcription factors, including CTCF, SMC3, RAD21, and ZNF143.
 Although the ENCODE, NIH Roadmap Epigenomics, FANTOM5, BLUEPRINT, and other members of the International Human Epigenome Consortium (IHEC) [@Stunnenberg:2016aa] have been actively cataloging cell line-specific genome annotation datasets, these data remain very sparse.
@@
 Arrowhead-defined TAD boundaries were called from Hi-C data for the GM12878 and K562 cell lines (MAPQ>0, 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions) using the default parameters (Additional file 1: Arrowhead Script).
-Peakachu chromatin loop boundaries called at 10 kb for the GM12878 and K562 cell lines were downloaded from the Yue lab website (Additional file 2: Table S1<!--Supplementary Table 1-->).
+Peakachu chromatin loop boundaries called at 10 kb for the GM12878, and K562 cell lines were downloaded from the Yue lab website (Additional file 2: Table S1<!--Supplementary Table 1-->).
 Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop anchor.
@@
 For SMOTE, under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the $k=5$ minority class nearest neighbors [@chawla2002smote] (implemented in the `DMwR` v.0.4.1 R package).
-We restricted the SMOTE algorithm to 100% over-sampling and 200% under-sampling, to create perfectly balanced classes.
+We restricted the SMOTE algorithm to 100% over-sampling and 200% under-sampling to create perfectly balanced classes.
 
@@
 The $i^{th}$ holdout chromosome was identified and a data matrix, $A_{N \times (p+1)}$, was constructed by combining the binned genome from the remaining chromosomes ($1,2,\cdots, i-1,i+1,\cdots,21,22$), where $N=[n_{1} n_{2} \cdots n_{21} n_{22}]'$ and $n_{k}$ is the length of chromosome *k* after being binned into non-overlapping regions of resolution *r*, such that $k \ne i$.
-The number of annotations, $p$, together with the response vector, **Y**, defined the column-wise dimension of the matrix $A$.
+The number of annotations, $p$, and the response vector, **Y**, defined the column-wise dimension of the matrix $A$.
 Re-sampling was then performed on $A$, and an RF classifier was trained using 3-fold cross-validation to tune for the number of annotations to consider at each node (*mtry*).
@@
 
-We aimed to extend the strategy of building and comparing boundary region prediction models using same cell line versus across cell line data to predict boundaries at base level resolution across cell lines.
-To do so, we applied *preciseTAD* on models built using cell line specific annotation data to predict boundaries on base level annotation data from another cell line.
+We aimed to extend the strategy of building and comparing boundary region prediction models using the same cell line versus across cell line data to predict boundaries at base level resolution across cell lines.
+To do so, we applied *preciseTAD* on models built using cell line-specific annotation data to predict boundaries on base-level annotation data from another cell line.
 As before, this strategy was compared to applying *preciseTAD* on models and base level annotation data from the same cell line.
@@
 The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD (or loop) boundary.
-(B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).
+(B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space, including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).
 
@@
 preciseTAD-predicted boundaries are closer to CTCF sites and more conserved across cell lines**.
-(A) $log_{2}$ genomic distance distribution from called and predicted boundaries to nearest CTCF sites.
+(A) $log_{2}$ genomic distance distribution from called and predicted boundaries to the nearest CTCF sites.
 The p-values are from the Wilcoxon Rank Sum test.
@@
 Averaged balanced accuracies are compared for Peakachu-trained models built on (B) GM12878 and (C) K562 within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Error bars indicate 1 standard deviation away from the mean performance across each holdout chromosome used for testing.
+Error bars indicate 1 standard deviation from the mean performance across each holdout chromosome used for testing.
 
@@
 **Additional File 14: Figure S9.
-The agreement between *preciseTAD*-predicted boundaries using Arrowhead- and Peakachu-trained models.** Venn diagrams of boundary overlaps using (A) GM12878 and (B) K562 data.
+The agreement between *preciseTAD*-predicted boundaries using Arrowhead- and Peakachu-trained models.** Venn diagrams of boundary overlap using (A) GM12878 and (B) K562 data.
 Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
@@
 NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model.
-Data from GM12878 (A) and K562 (B) cell lines, chromosome 22, at 5 kb resolution was used.
+Data from GM12878 (A) and K562 (B) cell lines, chromosome 22, at 5 kb resolution were used.
 Error bars indicate 1 standard deviation from the mean.
-
+<!--
 # Declarations
@@
 
-## Availability of data and materials
-
-All data generated or analyzed during this study are included in this published article [and its supplementary information files].
-The source code of *preciseTAD* version 0.99.6 used in the experiments is available on github at https://github.com/dozmorovlab/preciseTAD.
-
 ## Competing interests
@@
 ## Funding
+
+## Acknowledgements
+-->
+
+## Availability of data and materials
+
+All data generated or analyzed during this study are publicly available and provided in the supplementary files.
+The source code of *preciseTAD* version 0.99.6 used for all analyses is available at https://github.com/dozmorovlab/preciseTAD.
 
@@
 
-## Acknowledgements
-
 <!--
@@
 -->
-
 # References

### 2020-09-29 Manuscript/manuscript.Rmd
addressed ???

@@
 Boundary regions were defined as genomic bins containing a called boundary ($Y = 1$), while non-boundary regions were defined as bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
-The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Additional file 3: Table S2[???
-Wrong]<!--Supplementary Table 3-->).
+The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Additional file 3: Table S2<!--Supplementary Table 3-->).
 The number of non-boundary regions highly outnumbered boundary regions.
@@
 A total of 77 cell line-specific genomic annotations were used to build the predictor space.
-These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Additional file 4: Table S3[???
-Wrong]<!--Supplementary Table 2-->).
+These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Additional file 4: Table S3<!--Supplementary Table 2-->).
 Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
@@
 Chromosome 9 was excluded from all downstream analyses due to the sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Additional file 4: Table S3<!--Supplementary Table 2-->).
+Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Additional file 3: Table S2<!--Supplementary Table 2-->).
 

### 2020-09-29 Manuscript/manuscript.Rmd

@@
 ![**preciseTAD-predicted boundaries are closer to CTCF sites and more conserved across cell lines**.
-(A) Log2 genomic distance distribution from called and predicted boundaries to the nearest CTCF sites.
+(A) $log_{2}$ genomic distance distribution from called and predicted boundaries to the nearest CTCF sites.
 The p-values are from the Wilcoxon Rank Sum test.
-(B-E) Venn diagrams illustrating the levels of conservation (overlap) between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead (B), Peakachu (D), *preciseTAD*-predicted boundaries using Arrowhead- and Peakachu-trained models () Arrowhead-trained *preciseTAD* models (C), Peakachu boundaries themselves (C, E, respectively).
+(B-E) Venn diagrams illustrating the levels of conservation (overlap) between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead (B), Peakachu (D), and *preciseTAD*-predicted boundaries using (C) Arrowhead- and (E) Peakachu-trained models.
 Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.](Figures/figure6.png)

### 2020-09-30 BMC_Genome_Biology_submission/cover_letter_Genome_Biology.Rmd
final touches

@@
 
-Our manuscript is submitted for the "Software" section. The main highlights of the software are:
+Our manuscript is submitted under the "Software" category. The main highlights of our software are:
 
@@
 
-- *preciseTAD* prioritizes genomic signatures associated with domain boundaries.
-Trained on any 3D genomic features (e.g., besides TAD/loop boundaries, regions of A/B compartment switching, frequently interacting regions (FIREs), differentially interacting chromatin regions, etc.), *preciseTAD* defines (epi)genomic signatures most predictive of those features.
+- *preciseTAD* prioritizes regulatory elements associated with domain boundaries.
+Trained on any 3D features (e.g., besides TAD/loop boundaries, regions of A/B compartment switching, frequently interacting regions (FIREs), differentially interacting chromatin regions, etc.), *preciseTAD* defines (epi)genomic signatures most predictive of those features.
 
@@
 
-- Boundaries of TADs and loops are associated with the same genome annotation signatures, suggesting similar mechanisms of their formation.
+- Boundaries of TADs and loops are associated with the same regulatory signatures, suggesting similar mechanisms of their formation.
 
-- Biological properties of domain boundaries predicted using *preciseTAD* include the highest genomic signal of CTCF and other transcription factors, closer proximity to other genomic signatures, and more conservation across cell lines.
+- Biological properties of domain boundaries predicted using *preciseTAD* include the highest genomic signal of CTCF and other transcription factors, closer proximity to other genomic signatures, and higher` conservation across cell lines.
 
@@
 In summary, our systematic machine learning framework evaluates previously overlooked properties of 3D interactions and 1D regulatory data, linking them into the most optimal model for domain boundary predictions.
-This improved precision in the domain boundary location can provide deeper insight into the association between genomic regulators and the 3D genome organization.
+This improved precision in the domain boundary location will provide deeper insight into the association between genomic regulators and the 3D genome organization.
 

### 2020-09-30 Manuscript/manuscript.Rmd
final touches

@@
 Yet, the preciseTAD boundary points (PTBPs, medoids identified within each PTBR) had the highest density of CTCF and other transcription factor binding signal (Figure 5).
-Our results are in line with the emergent view that domain boundaries are dynamic [@chang2020tads], and their well-defined location arises as a consequence of the population average in bulk Hi-C data [@fudenberg2016formation; @Flyamer:2017aa].
+Our results are in line with the emergent view that domain boundaries are flexible [@chang2020tads; @Maeshima:2020aa], and their well-defined location arises as a consequence of the population average in bulk Hi-C data [@fudenberg2016formation; @Flyamer:2017aa].
 

### 2020-09-30 BMC_Genome_Biology_submission/cover_letter_Genome_Biology.Rmd
Final notes

@@
 We are submitting our manuscript "preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution" to be considered for the special issue "Regulatory Elements" in _Genome Biology_.
-This manuscript will be of interest to the community studying the regulatory associations within the three-dimensional (3D) genome structure.
+This manuscript will be of interest to the community studying the regulatory associations with the three-dimensional (3D) genome structure.
 
@@
 
-- The provided models pre-trained on Arrowhead-called TAD boundaries and Peakachu-called loop boundaries can predict domain boundaries in cells without Hi-C data using only genomic annotation data.
+- The pre-trained models provided with the package can predict domain boundaries in cells without Hi-C data using only genomic annotation data.
 
@@
 
-- Transcription factors, spatial relationships (distance within the linear genome) between them and boundaries, random under-sampling are the critical features needed for accurate boundary predictions.
+- Transcription factors, spatial relationships (distance within the linear genome) between them and boundaries, random under-sampling are the critical considerations needed for accurate boundary predictions.
 
@@
 
-- Biological properties of domain boundaries predicted using *preciseTAD* include the highest genomic signal of CTCF and other transcription factors, closer proximity to other genomic signatures, and higher` conservation across cell lines.
+- Biological properties of boundaries predicted using *preciseTAD* include the highest genomic signal of CTCF and other transcription factors, closer proximity to other genomic signatures, and higher` conservation across cell lines.
 
@@
 
-In summary, our systematic machine learning framework evaluates previously overlooked properties of 3D interactions and 1D regulatory data, linking them into the most optimal model for domain boundary predictions.
+In summary, our systematic machine learning framework evaluates previously overlooked properties of 3D and 1D data associations, linking them into the most optimal model for domain boundary predictions.
 This improved precision in the domain boundary location will provide deeper insight into the association between genomic regulators and the 3D genome organization.
@@
 With our best regards,
-On behalf of all authors,
 
@@
 Phone: 804-827-2055
+
+09/30/2020

### 2020-09-30 BMC_Genome_Biology_submission/cover_letter_Genome_Biology.Rmd
Formatted for GB
Submitted

@@
 output:
-  pdf_document: default
-  html_document: default
   word_document:
     reference_docx: ../Manuscript/styles.doc/NSF_grant_style.docx
+  html_document: default
+  pdf_document: default
 ---
+
+September 30, 2020
 
@@
 09/30/2020
+
+From: "BioMed Central Editorial Office" <em@editorialmanager.com>
+Subject: [EXTERNAL] Confirmation of your submission to Genome Biology GBIO-D-20-01545
+Date: September 30, 2020 at 9:04:06 AM EDT
+To: "Mikhail G Dozmorov" <mikhail.dozmorov@vcuhealth.org>
+Reply-To: "BioMed Central Editorial Office" <editorial@genomebiology.com>
+
+GBIO-D-20-01545 
+preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution
+Spiro Stilianoudakis; Mikhail G Dozmorov, Ph.D.
+Genome Biology
+
+Dear Dr. Dozmorov,
+
+Thank you for submitting your manuscript 'preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution' to Genome Biology.
+
+The submission id is: GBIO-D-20-01545
+Please refer to this number in any future correspondence.
+
+During the review process, you can keep track of the status of your manuscript by accessing the following website:
+
+https://urldefense.com/v3/__https://www.editorialmanager.com/gbio/__;!!JqxBPMk!xwmo-1zdQADscZxt7BYRNTr10BgiwyWHUtyM5IrjPB7IhwenePPD6G33cjdQIs2vUCjOuw$
+
+If you have forgotten your username or password please use the "Send Login Details" link to get your login information. For security reasons, your password will be reset.
+
+Best wishes,
+
+Editorial Office
+BioMed Central

### 2021-01-14 Scripts_for_results/24_preciseTAD_summaries.R
added scripts for results

@@ -1,0 +1,312 @@
+#24_preciseTAD_summaries
+
+library(S4Vectors)
+library(GenomicRanges)
+library(ggplot2)
+library(caret)
+library(randomForest)
+library(glmnet)
+library(gbm)
+library(DMwR)
+library(rtracklayer)
+library(Biostrings)
+library(BSgenome)
+library(cluster)
+library(pROC)
+library(SuperLearner)
+library(data.table)
+library(PRROC)
+library(bigmemory)
+library(ranger)
+library(dplyr)
+library(parallel)
+library(doSNOW)
+library(foreach)
+library(pbapply)
+library(ggpubr)
+library(scales)
+library(GGally)
+library(VennDiagram)
+library(network)
+library(sna)
+library(gtable)
+library(grid)
+library(magrittr) 
+library(DT)
+library(tidyverse)
+library(reshape)
+library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
+library(GenometriCorr)
+library(ggsignif)
+library(Vennerable)
+library(VennDiagram)
+library(ChIPpeakAnno)
+library(EnrichedHeatmap)
+
+source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
+
+#gm12878
+
+##arrowhead
+
[…]

### 2021-01-14 Scripts_for_results/25_comparing_preciseTAD_quality_cross_cell_lines.R

@@ -1,0 +1,126 @@
+#25_comparing_preciseTAD_quality_cross_cell_lines
+
+library(S4Vectors)
+library(GenomicRanges)
+library(ggplot2)
+library(caret)
+library(randomForest)
+library(glmnet)
+library(gbm)
+library(DMwR)
+library(rtracklayer)
+library(Biostrings)
+library(BSgenome)
+library(cluster)
+library(pROC)
+library(SuperLearner)
+library(data.table)
+library(PRROC)
+library(bigmemory)
+library(ranger)
+library(dplyr)
+library(parallel)
+library(doSNOW)
+library(foreach)
+library(pbapply)
+library(ggpubr)
+library(scales)
+library(GGally)
+library(VennDiagram)
+library(network)
+library(sna)
+library(gtable)
+library(grid)
+library(magrittr) 
+library(DT)
+library(tidyverse)
+library(reshape)
+library(ROSE)
+library(lattice)
+library(corrplot)
+library(cluster)
+library(RColorBrewer)
+#library(GenometriCorr)
+library(ggsignif)
+library(Vennerable)
+library(VennDiagram)
+library(ChIPpeakAnno)
+library(EnrichedHeatmap)
+
+source("Z:/TAD_data_analysis/functions_for_R_package/createTADdata.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrandomForest.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe2.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
+source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")
+
[…]

### 2021-01-14 Scripts_for_results/26_dnase_vs_topTFBS.R

@@ -1,0 +1,964 @@
+#26_dnase_vs_topTFBS
+
+library(dplyr)
+library(ggplot2)
+
+#arrowhead
+
+##gm12878
+
+#badata_gm12878_5kb <- numeric()
+#for(i in paste0("CHR", c(1:8,10:22))){
+#  for(j in c("ctcf",
+#             "rad21",
+#             "smc3",
+#             "znf143",
+#             "ctcf_rad21",
+#             "ctcf_smc3",
+#             "ctcf_znf143",
+#             "rad21_smc3",
+#             "rad21_znf143",
+#             "smc3_znf143",
+#             "ctcf_rad21_smc3",
+#             "ctcf_rad21_znf143",
+#             "rad21_smc3_znf143",
+#             "smc3_znf143_ctcf",
+#             "topTFBS")){
+#    print(c(i,j))
+#    
+#    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+#                               i, 
+#                               "/",
+#                               "rus", 
+#                               "/", 
+#                               "distance", 
+#                               "/TADRF_holdout_",
+#                               j,
+#                               ".rds"))
+#    perfdata <- perfdata[[3]]						   
+#    
+#    badata_gm12878_5kb <- rbind(badata_gm12878_5kb,
+#                                perfdata[10,2])
+#  }
+#}
+
+
+#saveRDS(badata_gm12878_5kb, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/saved_rds_files/TADRF_holdout_gm12878_topTFBS_combinations.rds")
+
+badata_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/TADRF_holdout_gm12878_topTFBS_combinations.rds")
+
+all_rfperfs <- cbind.data.frame(V1=badata_gm12878_5kb,
+                                Combination=rep(c("ctcf",
+                                                  "rad21",
+                                                  "smc3",
+                                                  "znf143",
+                                                  "ctcf_rad21",
+                                                  "ctcf_smc3",
+                                                  "ctcf_znf143",
+                                                  "rad21_smc3",
+                                                  "rad21_znf143",
+                                                  "smc3_znf143",
+                                                  "ctcf_rad21_smc3",
+                                                  "ctcf_rad21_znf143",
+                                                  "rad21_smc3_znf143",
[…]

### 2021-01-14 Scripts_for_results/27_cage_vs_topTFBS.R

@@ -1,0 +1,963 @@
+#27_cage_vs_topTFBS
+
+library(dplyr)
+library(ggplot2)
+
+#arrowhead
+
+##gm12878
+
+#badata_gm12878_5kb <- numeric()
+#for(i in paste0("CHR", c(1:8,10:22))){
+# for(j in c("ctcf",
+#             "rad21",
+#             "smc3",
+#             "znf143",
+#             "ctcf_rad21",
+#             "ctcf_smc3",
+#             "ctcf_znf143",
+#             "rad21_smc3",
+#             "rad21_znf143",
+#             "smc3_znf143",
+#             "ctcf_rad21_smc3",
+#             "ctcf_rad21_znf143",
+#             "rad21_smc3_znf143",
+#             "smc3_znf143_ctcf",
+#             "topTFBS")){
+#    print(c(i,j))
+#    
+#    perfdata <- readRDS(paste0("/home/stilianoudakisc/TAD_data_analysis/GM12878/5kb/results_by_chr/",
+#                               i, 
+#                               "/",
+#                               "rus", 
+#                               "/", 
+#                               "distance", 
+#                               "/TADRF_holdout_",
+#                               j,
+#                              ".rds"))
+#    perfdata <- perfdata[[3]]						   
+#    
+#    badata_gm12878_5kb <- rbind(badata_gm12878_5kb,
+#                                perfdata[10,2])
+#  }
+#}
+
+
+#saveRDS(badata_gm12878_5kb, "/home/stilianoudakisc/TAD_data_analysis/miscellaneous/saved_rds_files/TADRF_holdout_gm12878_topTFBS_combinations.rds")
+
+badata_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/miscellaneous/saved_rds_files/TADRF_holdout_gm12878_topTFBS_combinations.rds")
+
+all_rfperfs <- cbind.data.frame(V1=badata_gm12878_5kb,
+                                Combination=rep(c("ctcf",
+                                                  "rad21",
+                                                  "smc3",
+                                                  "znf143",
+                                                  "ctcf_rad21",
+                                                  "ctcf_smc3",
+                                                  "ctcf_znf143",
+                                                  "rad21_smc3",
+                                                  "rad21_znf143",
+                                                  "smc3_znf143",
+                                                  "ctcf_rad21_smc3",
+                                                  "ctcf_rad21_znf143",
+                                                  "rad21_smc3_znf143",
[…]

### 2021-01-14 BMC_Genome_Biology_submission/grubert_manuscript_figures_tables/manuscript/manuscript.Rmd
added folder for grubert-specific figures/table/manuscript

--- 2020-09-30 Manuscript/manuscript.Rmd
@@
 
-![**Resolution-specific data construction and feature engineering for random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals using *shifted binning* (see Methods).
+<!-- ![**Resolution-specific data construction and feature engineering for random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals using *shifted binning* (see Methods).
 The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD (or loop) boundary.
-(B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space, including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png)
+(B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space, including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png) -->
 
@@
 
-![**A machine learning framework for building domain boundary region prediction models.** Step 1 employs a range of feature engineering techniques to define the predictor matrix $A_{N \times (p)}$, where $N$ is the number of genomic bins, $p$ is the number of genomic annotations, $i$ is a holdout chromosome.
+<!-- ![**A machine learning framework for building domain boundary region prediction models.** Step 1 employs a range of feature engineering techniques to define the predictor matrix $A_{N \times (p)}$, where $N$ is the number of genomic bins, $p$ is the number of genomic annotations, $i$ is a holdout chromosome.
 The response vector $Y_N$ is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$).
@@
 Step 4 trains the random forest model and performs 3-fold cross-validation to tune the mtry parameter.
-Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and evaluates model performance using balanced accuracy (BA).](Figures/figure2.png)
+Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and evaluates model performance using balanced accuracy (BA).](Figures/figure2.png) -->
 
@@
 
-![**Determining optimal data level characteristics for building TAD boundary region prediction models on GM12878.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Error bars indicate standard deviation from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)
+<!-- ![**Determining optimal data level characteristics for building TAD boundary region prediction models on GM12878.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Error bars indicate standard deviation from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png) -->
 
@@
 
-![**SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in GM12878.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+<!-- ![**SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in GM12878.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
 (B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
@@
 The curves represent the average sensitivities and specificities across each holdout chromosome.
-The shaded areas around each curve represent 1 standard deviation from the average.](Figures/figure4.png)
+The shaded areas around each curve represent 1 standard deviation from the average.](Figures/figure4.png) -->
 
@@
 
-![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of Arrowhead-called TAD boundaries (blue) vs.
+<!-- ![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of Arrowhead-called TAD boundaries (blue) vs.
 *preciseTAD*-predicted TAD boundaries (green) on GM12878 data (chr14:50085000-50800000).
@@
 (C, D) Signal profile plots comparing the strength of CTCF, RAD21, SMC3, and ZNF143 binding around Arrowhead-called boundaries (blue, C), Peakachu loop boundaries (red, D) vs.
-*preciseTAD*-predicted boundaries (green).](Figures/figure5.png)
+*preciseTAD*-predicted boundaries (green).](Figures/figure5.png) -->
 
@@
 
-![**preciseTAD-predicted boundaries are closer to CTCF sites and more conserved across cell lines**.
+<!-- ![**preciseTAD-predicted boundaries are closer to CTCF sites and more conserved across cell lines**.
 (A) $log_{2}$ genomic distance distribution from called and predicted boundaries to the nearest CTCF sites.
@@
 (B-E) Venn diagrams illustrating the levels of conservation (overlap) between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead (B), Peakachu (D), and *preciseTAD*-predicted boundaries using (C) Arrowhead- and (E) Peakachu-trained models.
-Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.](Figures/figure6.png)
+Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.](Figures/figure6.png) -->
 
@@
 
-<!--
 # Figure legends
@@
 Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
--->
 
@@
 Error bars indicate 1 standard deviation from the mean.
-<!--
+
 # Declarations
@@
 
+This work was supported in part by <!--the PhRMA Foundation Research Informatics Award and -->the George and Lavinia Blick Research Fund scholarship to MD.
+
+<!--
 ## Acknowledgements
 -->
-
 ## Availability of data and materials

### 2021-01-21 BMC_Genome_Biology_submission/grubert_manuscript_figures_tables/manuscript/manuscript.Rmd
made edits to grubert version of manuscript

@@
 title: "preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution"
-csl: styles.ref/genomebiology.csl
+csl: ../styles.ref/genomebiology.csl
 output:
-  word_document:
-    reference_docx: styles.doc/Arial_11_double_space_normal_margins.docx
   pdf_document: 
     extra_dependencies: ["float"]
-bibliography: References/references.bib
+  word_document:
+    reference_docx: ../styles.doc/Arial_11_double_space_normal_margins.docx
+bibliography: ../References/references.bib
 ---
@@
 ^\*^ To whom correspondence should be addressed<!--: Virginia Commonwealth University, Richmond, VA, 23298, 804-827-2055, mikhail.dozmorov@vcuhealth.org-->
+
+<!--revision symbol: %%%-->
 
@@
 At the megabase scale, TADs represent regions on the linear genome that are highly self-interacting.
-<!--Emerging evidence has linked TADs to critical roles in cell dynamics and cell differentiation.
-Studies have shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].--> Disruption of boundaries demarcating TADs and loops promotes cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@lupianez2016breaking;@Sun:2018aa;@Meaburn:2007aa].
+Emerging evidence has linked TADs to critical roles in cell dynamics and cell differentiation.
+Studies have shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
+Disruption of boundaries demarcating TADs and loops promotes cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@lupianez2016breaking;@Sun:2018aa;@Meaburn:2007aa].
 Identifying the precise location of TAD and chromatin loop boundaries remains a top priority in our goal to fully understand the functionality of the human genome.
@@
 Another limitation among domain callers is that they disregard prior knowledge about functional genomic annotations associated with TAD and loop boundaries, referred hereafter as domain boundaries.
-The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been identified as components of the loop extrusion model<!--, whereby DNA is extruded through cohesin rings forming chromatin loops--> [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
-Furthermore, distinct patterns of histone modifications have also been shown to be present at boundaries<!--including H3K36me3--> [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
+The insulator binding protein, CTCF, and additional cofactors such as SMC3 and RAD21 have been identified as components of the loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
+Furthermore, distinct patterns of histone modifications have also been shown to be present at boundaries [@lieberman2009comprehensive;@dixon2012topological;@libbrecht2015joint].
 These genomic annotations are obtained using chromatin immunoprecipitation followed by high-throughput DNA sequencing (ChIP-seq).
@@
 We present *preciseTAD*, an optimally tuned machine learning framework for precise identification of domain boundaries using genome annotation data.
-Our method utilizes the random forest (RF) algorithm trained on high-resolution chromatin state (BroadHMM), histone modification (HM), and transcription factor binding site (TFBS) data to predict low-resolution boundaries.
+Our method utilizes the random forest (RF) algorithm trained on high-resolution chromatin state (BroadHMM), histone modification (HM), and transcription factor binding site (TFBS) data to predict both low-resolution TAD and chromatin-loop boundaries.
 We introduce a systematic pipeline for building the optimal boundary region prediction classifier.
@@
 We used Arrowhead-called TAD boundaries [@durand2016juicer] and published Peakachu-predicted loop boundaries [@salameh2019supervised] as ground truth.
-Data from GM12878 and K562 cell lines at 5-100 kb resolution (Arrowhead) and 10 kb resolution (Peakachu) were used (Additional file 1: Arrowhead Script, Additional file 2: Table S1<!--Supplementary Table 1-->).
+Data from GM12878 and K562 cell lines at 5-100 kb resolution (Arrowhead) and 10 kb resolution (Peakachu) were used (Additional file 1: Arrowhead Script, Additional file 2: Table S1).
 We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base-level resolution from cell line-specific genome annotation data.
 
-<!-- ![**Resolution-specific data construction and feature engineering for random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals using *shifted binning* (see Methods).
+<!--![**Resolution-specific data construction and feature engineering for random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals using *shifted binning* (see Methods).
 The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD (or loop) boundary.
-(B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space, including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](Figures/figure1.png) -->
+(B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space, including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).](../main_figures/figure1.png)-->
 
 Boundary regions were defined as genomic bins containing a called boundary ($Y = 1$), while non-boundary regions were defined as bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
-The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Additional file 3: Table S2<!--Supplementary Table 3-->).
+The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Additional file 3: Table S2).
 The number of non-boundary regions highly outnumbered boundary regions.
@@
 
-|          Tool         |     Resolution    |     Total number of called TADs/chromatin loops    |     Total number of unique TAD/chromatin loop boundaries    |     Total number of genomic bins    |     Class imbalance    |
-|:---------------------:|:-----------------:|:--------------------------------------------------:|:-----------------------------------------------------------:|:-----------------------------------:|:----------------------:|
+|          Tool         |     Resolution/Bin Size    |     Total number of called TADs/chromatin loops    |     Total number of unique TAD/chromatin loop boundaries    |     Total number of genomic bins    |     Class imbalance    |
+|:---------------------:|:--------------------------:|:--------------------------------------------------:|:-----------------------------------------------------------:|:-----------------------------------:|:----------------------:|
 |        Arrowhead      |       5   kb               |                         8052                       |                             15468                           |                535363               |           0.03         |
@@
 |        Peakachu       |       10   kb              |                        16185                       |                          21421                              |                267682               |        0.14            |
-Table: Domain boundary data and class imbalance summaries across resolutions for Arrowhead and Peakachu on GM12878.
+|        Grubert        |       5    kb              |                        16232                       |                          18455                              |                535363               |        0.07            |
+Table: Domain boundary data and class imbalance summaries across resolutions for Arrowhead, Peakachu<!--%%%, and Grubert--> on GM12878.
 
 A total of 77 cell line-specific genomic annotations were used to build the predictor space.
-These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Additional file 4: Table S3<!--Supplementary Table 2-->).
+These included BroadHMM chromatin state data, histone modifications (HM), and transcription factor binding sites (TFBS) (Additional file 4: Table S3).
 Four feature engineering procedures were developed to quantify the association between genomic annotations and bins (Figure 1B).
-These included signal strength association (Signal), direct (OC), proportional (OP), and spatial ($log_2 + 1$ Distance) relationships (see Methods, Additional file 5: Figure S1<!--Supplementary Figure 1-->).
+These included signal strength association (Signal), direct (OC), proportional (OP), and spatial ($log_2 + 1$ Distance) relationships (see Methods, Additional file 5: Figure S1).
 
@@
 Step 4 trains the random forest model and performs 3-fold cross-validation to tune the mtry parameter.
-Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and evaluates model performance using balanced accuracy (BA).](Figures/figure2.png) -->
+Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and evaluates model performance using balanced accuracy (BA).](../main_figures/figure2.png) -->
+
+<!--%%%
+![**A machine learning framework for building domain boundary region prediction models.** Step 1 combines the response vector ($\textbf{Y}_N$) from *shifted binning* and a feature engineering procedure to form the data matrix $A_{N \times (p+1)}$ for chromosomes $\{1, 2, ..., i-1, i+1, ..., 22 \}$.
+Step 2 reserves the predictor-response matrix for the holdout chromosome $i$ as the test data using Grubert-defined boundaries as $\textbf{Y}_{test}$.
+Step 3 applies a resampling technique to the training data to address the class imbalance.
+Step 4 trains the random forest model and performs 3-fold cross-validation to tune the mtry parameter.
+Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and evaluates the model performance using balanced accuracy (BA)](../main_figures/figure2.png)
+-->
 
@@
 Additionally, we found that using a distance-type predictor space yielded substantially higher balanced accuracy than the peak signal strength, overlap count, and overlap percent predictor types.
-As with class balancing techniques, this improvement was less evident at lower resolutions, with results consistent for K562 (Additional file 6: Figure S2A<!--Supplementary Figure 3A-->).
+As with class balancing techniques, this improvement was less evident at lower resolutions, with results consistent for K562 (Additional file 6: Figure S2A).
 Furthermore, 5 kb resolution genomic bins led to the optimal prediction for TAD boundary regions on both cell lines.
-Random forest models built on Peakachu-defined loop boundary regions yielded optimal prediction performance when using a distance-type predictor space, with SMOTE resampling only marginally outperforming RUS, for both cell lines (Additional file 6: Figure S2B, S2C<!--Supplementary Figure 3B,3C-->).
+Random forest models built on Peakachu-defined loop boundary regions yielded optimal prediction performance when using a distance-type predictor space, with SMOTE resampling only marginally outperforming RUS, for both cell lines (Additional file 6: Figure S2B, S2C).
 Our results indicate that random under-sampling, distance-type predictors, and high-resolution Hi-C data provide the optimal set of data level characteristics for both TAD and chromatin loop boundary prediction.
@@
 <!-- ![**Determining optimal data level characteristics for building TAD boundary region prediction models on GM12878.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Error bars indicate standard deviation from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png) -->
+Error bars indicate 1 standard deviation from the mean performance across each holdout chromosome used for testing.](../main_figures/figure3.png) -->
 
@@
 Using the established optimal settings (RUS, Distance, 5 kb/10 kb (Arrowhead/Peakachu ground truth) genomic bins), we built separate random forest models using histone modifications (HM), BroadHMM chromatin states (BroadHMM), and transcription factor binding sites (TFBS).
-We found that models built on TFBSs outperformed other annotation-specific models, with results consistent for loop boundaries, on both cell lines (Figure 4A; Additional file 7: Figure S3A<!--Supplementary Figures 4A-->).
+We found that models built on TFBSs outperformed other annotation-specific models, with results consistent for loop boundaries, on both cell lines (Figure 4A; Additional file 7: Figure S3A).
 These results suggest that TFBS are the primary drivers of TAD and loop boundary formation in both GM12878 and K562.
@@
 The curves represent the average sensitivities and specificities across each holdout chromosome.
-The shaded areas around each curve represent 1 standard deviation from the average.](Figures/figure4.png) -->
+The shaded areas around each curve represent 1 standard deviation from the average.](../main_figures/figure4.png) -->
 
@@
 We sought to further optimize our boundary region prediction models by implementing recursive feature elimination to avoid overfitting and selecting only the most influential TFBS across all autosomal chromosomes.
-We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Additional file 7: Figure S3B<!--Supplementary Figures 4B-->).
+We were able to obtain near-optimal performance using approximately eight TFBS (Figure 4B; Additional file 7: Figure S3B).
 However, given that we trained our models on chromosome-specific data, the most significant annotations varied for each holdout chromosome.
 To determine transcription factors most important for boundary prediction across all chromosomes, we clustered the predictive importance (mean decrease in accuracy) of the top eight significant TFs across chromosomes.
-We found four transcription factors, CTCF, RAD21, SMC3, and ZNF143, being consistently predictive of TAD and loop boundaries (Figure 4C; Additional file 7: Figure S3C<!--Supplementary Figures 4C-->).
+We found four transcription factors, CTCF, RAD21, SMC3, and ZNF143, being consistently predictive of TAD and loop boundaries (Figure 4C; Additional file 7: Figure S3C).
 We optimized our model by only considering these top four TFBS when building the random forest model, thereby decreasing computational burden while maintaining high predictive performance.
@@
 AUC=0.881 and 0.874, respectively).
-These results were consistent when comparing training/testing strategies on K562 with training on GM12878 and testing on K562 data (Additional file 7: Figure S3D<!--Supplementary Figure 4D-->).
+These results were consistent when comparing training/testing strategies on K562 with training on GM12878 and testing on K562 data (Additional file 7: Figure S3D).
 The average ROC curves were found to be within 1 standard deviation of each other, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.
@@
 The model trained on a bin-level space was then applied on a base-level space to predict each base's probability of being a boundary.
-Our method, referred to as *preciseTAD*, uses density-based spatial clustering (DBSCAN) and partitioning around medoids (PAM) to predict the location of boundary regions and summit points (highest boundary probability) at base-level resolution (see Methods; Additional file 8: Figure S4<!--Supplementary Figure 2-->).
+Our method, referred to as *preciseTAD*, uses density-based spatial clustering (DBSCAN) and partitioning around medoids (PAM) to predict the location of boundary regions and summit points (highest boundary probability) at base-level resolution (see Methods; Additional file 8: Figure S4).
 
-When trained using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, the *preciseTAD* model predicted a total of 12,258 TAD and 15,707 chromatin loop boundaries in GM12878, as well as 9,603 TAD and 11,154 chromatin loop boundaries in K562 cell line (Additional file 9: Table S4<!--Supplementary Table 4-->).
-We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Additional file 3: Table S2<!--Supplementary Table 3-->).
+When trained using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, the *preciseTAD* model predicted a total of 12,258 TAD and 15,707 chromatin loop boundaries in GM12878, as well as 9,603 TAD and 11,154 chromatin loop boundaries in K562 cell line (Additional file 9: Table S4).
+We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Additional file 3: Table S2).
 This can be attributed to Arrowhead's inflation of called TADs at 5 kb, that, when visualized, often do not correspond to domains enriched in internal interactions (Figure 5A) and signal of known drivers of domain boundaries (Figure 5B).
-*preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Additional file 3: Table S2<!--Supplementary Table 3-->).
+*preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Additional file 3: Table S2).
 This can be attributed to Peakachu's use of only CTCF sites to call boundaries, while *preciseTAD* leverages four known drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143.
@@
 (C, D) Signal profile plots comparing the strength of CTCF, RAD21, SMC3, and ZNF143 binding around Arrowhead-called boundaries (blue, C), Peakachu loop boundaries (red, D) vs.
-*preciseTAD*-predicted boundaries (green).](Figures/figure5.png) -->
+*preciseTAD*-predicted boundaries (green).](../main_figures/figure5.png) -->
+
+<!--%%%
+![**preciseTAD boundaries are enriched for known molecular drivers of 3D chromatin.** (A) The location of Arrowhead-called TAD boundaries (blue) vs.
+*preciseTAD*-predicted TAD boundaries (green) on GM12878 data (chr14:50085000-50800000).
+The black line represents the predicted probability of each base being a TAD boundary.
+(B) A zoomed-in portion of the genome shows the preciseTAD boundary region (PTBR, highlighted yellow), a cluster of bases with high probability of being a boundary, and the corresponding signal profiles of CTCF, RAD21, SMC3, and ZNF143.](../main_figures/figure5.png)
+-->
 
 Next, we evaluated the biological significance of *preciseTAD* boundary points.
-The signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (Figure 5C, 5D; Additional file 10: Figure S5A, S5B<!--Supplementary Figure 5A, 5B-->).
+The signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (Figure 5C, 5D; Additional file 10: Figure S5A, S5B).
 Surprised by the poor signal distribution around Arrowhead boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, and our SpectralTAD [@Cresswell:2020ab] TAD caller.
-We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the relatively well-performing Peakachu- and SpectralTAD-called boundaries (Additional file 10: Figure S5C, S5D<!--Supplementary Figure 5C, D-->).
-Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Additional file 11-12: Figure S6-S7<!--Supplementary Figures 6-7-->).
-*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Additional file 13: Figure S8<!--Supplementary Figure 8-->).
+We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the relatively well-performing Peakachu- and SpectralTAD-called boundaries (Additional file 10: Figure S5C, S5D).
+Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Additional file 11-12: Figure S6-S7).
+*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Additional file 13: Figure S8).
 These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
@@
 
-<!-- ![**preciseTAD-predicted boundaries are closer to CTCF sites and more conserved across cell lines**.
+<!-- ![**preciseTAD boundaries are closer to CTCF sites and more conserved across cell lines**.
 (A) $log_{2}$ genomic distance distribution from called and predicted boundaries to the nearest CTCF sites.
@@
 (B-E) Venn diagrams illustrating the levels of conservation (overlap) between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead (B), Peakachu (D), and *preciseTAD*-predicted boundaries using (C) Arrowhead- and (E) Peakachu-trained models.
-Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.](Figures/figure6.png) -->
+Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.](../main_figures/figure6.png) -->
+
+<!--%%%
+![**preciseTAD boundaries are more enriched for known molecular drivers of 3D chromatin.** (C, D) Signal profile plots illustrating enrichment strength of CTCF, RAD21, SMC3, and ZNF143 sites around *preciseTAD*-predicted boundaries (green) compared to (A) Arrowhead-called boundaries (blue), (B) Peakachu loop boundaries (red), and (C) Grubert loop boundaries (purple).
+Boundaries involving Arrowhead and Grubert were flanked by 5 kb, while Peakachu-related boundaries were flanked by 10 kb.](../main_figures/figure6.png)
+-->
+
+<!--%%%
+![**preciseTAD boundaries are closer to CTCF sites and more conserved across cell lines**.
+(A) Violin plots illustrating the $log_{2}$ genomic distance distribution from ground-truth vs.
+*preciseTAD*-predicted boundaries to the nearest CTCF sites.
+The p-values are from the Wilcoxon Rank Sum test.
+(B-G) Venn diagrams illustrating the levels of conservation (overlap) between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by (B) Arrowhead, (C) Peakachu, and (D) Grubert, compared to *preciseTAD*-predicted boundaries using (E) Arrowhead-, (F) Peakachu-, and (G) Grubert-trained models, respectively.
+Boundaries involving Arrowhead and Grubert were flanked by 5 kb, while Peakachu-related boundaries were flanked by 10 kb.](../main_figures/figure7.png)
+-->
 
@@
 
-The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model (Additional file 14: Figure S9<!--Supplementary Figure 9-->).
-<!--We found that 88.8% and 95.8% [???
-These numbers are different from what is shown in Supp Fig 9; !!!the %'s shown are (left region)/(left + middle); should I take out the percentages in the figure?
-???
-Still unclear, calculations don't make sense.
-TBD] of our predicted TAD boundaries were overlapped by predicted loop boundaries for GM12878 and K562, respectively (Supplementary Figure 9).
-[???
-After clarification, MD to rewrite the first two sentences, unclear] -->This is expected as loop boundaries detected by Peakachu are more abundant, while comparatively wide TAD boundaries detected by Arrowhead likely represent the higher level of the 3D chromatin organization.
+The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model (Additional file 14: Figure S9).
+This is expected as loop boundaries detected by Peakachu are more abundant, while comparatively wide TAD boundaries detected by Arrowhead likely represent the higher level of the 3D chromatin organization.
 Together with the results in Figure 4C, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar molecular mechanisms.
@@
 training on GM12878 and predicting boundaries on K562 (GM on K).
-Using Arrowhead-trained models, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries overlapped in both cross-cell-line prediction scenarios (Additional file 15: Figure S10A, S10B<!--Supplementary Figure 10A, 10B-->).
-Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlap (Additional file 15: Figure S10C, S10D<!--Supplementary 10C, 10D-->).
-Furthermore, boundaries predicted on unseen annotation data exhibited a similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Additional file 15: Figure S10<!--Supplementary Figure 10-->).
+Using Arrowhead-trained models, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries overlapped in both cross-cell-line prediction scenarios (Additional file 15: Figure S10A, S10B).
+Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlap (Additional file 15: Figure S10C, S10D).
+Furthermore, boundaries predicted on unseen annotation data exhibited a similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Additional file 15: Figure S10).
 These results indicate that *preciseTAD* pre-trained models can be successfully used to predict domain boundaries for cell lines lacking Hi-C data but for which genome annotation data is available.
@@
 
-Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Additional file 16: Table S5<!--Supplementary Table 5-->).
+Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Additional file 16: Table S5).
 Our aim was to have a balanced metric sensitive to class imbalance such that it would not favor one component of the confusion matrix.
@@
 As a heuristic, we evaluated the pairwise combination of 3 different thresholds ($t=(0.975,0.99,1.0)$) and 6 different $\epsilon$ values ($\epsilon=(1000,5000,10000,15000,20000,25000)$)).
-We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (Additional file 17: Figure S11<!--Supplementary Figure 11-->).
+We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (Additional file 17: Figure S11).
 
@@
 
-TAD and loop boundaries called by Arrowhead [@durand2016juicebox] and Peakachu [@salameh2019supervised] tools were used for training and testing.
+TAD and loop boundaries called by *Arrowhead* [@durand2016juicebox] and *Peakachu* [@salameh2019supervised] tools were used for training and testing.
 The autosomal genomic coordinates in the GRCh37/hg19 human genome assembly were considered.
 Arrowhead-defined TAD boundaries were called from Hi-C data for the GM12878 and K562 cell lines (MAPQ>0, 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions) using the default parameters (Additional file 1: Arrowhead Script).
-Peakachu chromatin loop boundaries called at 10 kb for the GM12878, and K562 cell lines were downloaded from the Yue lab website (Additional file 2: Table S1<!--Supplementary Table 1-->).
+Peakachu chromatin loop boundaries called at 10 kb for the GM12878, and K562 cell lines were downloaded from the Yue lab website (Additional file 2: Table S1).
 Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop anchor.
 Chromosome 9 was excluded from all downstream analyses due to the sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Additional file 3: Table S2<!--Supplementary Table 2-->).
+<!--%%% Additionally cohesin-mediated chromatin loops mapped via chromatin interaction analysis by paired-end tag sequencing (ChIA-PET) were downloaded for GM12878 and K562 [@grubert2020landscape] (Additional file 2: Table S1), which we refer to as *Grubert*.--> Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Additional file 3: Table S2).
 
@@
 Bins were annotated by one of either the average signal strength of the corresponding annotation (*Peak Signal Strength*), the number of overlaps with an annotation (*Overlap Count (OC)*), the percent of overlap between the bin and the total width of genomic annotation regions overlapping it (*Overlap Percent (OP)*), or the distance in bases from the center of the bin to the center of the nearest genomic annotation region (*Distance*) (Figure 1B).
-A ($log_2 + 1$)-transformation of distance was used to account for the skewness of the distance distributions  (Additional file 5: Figure S1<!--Supplementary Figure 1-->).
+A ($log_2 + 1$)-transformation of distance was used to account for the skewness of the distance distributions  (Additional file 5: Figure S1).
 Models built using a *Peak Signal Strength* predictor space were only composed of histone modifications and transcription factor binding sites because BroadHMM chromatin states lack signal values.
@@
 The binned data for the holdout chromosome $i$ was reserved for testing.
-Models were evaluated using Balanced Accuracy (BA), defined as the average of sensitivity and specificity:
+<!--%%%The response vector associated with the testing data ($\textbf{Y}_{test}$) was built using Grubert-defined chromatin loops as a gold standard when validating the models.--> Models were then evaluated using Balanced Accuracy (BA), defined as the average of sensitivity and specificity:
 
@@
 
-where TP refers to the number of bins correctly identified as containing a boundary (true positives), FP refers to the number of bins incorrectly identified as containing a boundary (false positives), TN refers to the number of bins correctly identified as not containing a boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a boundary (false negatives).
+<!--%%%where values of the confusion matrix, true negatives (TP), false positives (FP), true negatives (TN), and false negatives (FN) were related to genomic bins that contained a Grubert-defined boundary in the test data.
+That is, TP refers to the number of bins correctly identified as containing a boundary (true positives), FP refers to the number of bins incorrectly identified as containing a boundary (false positives), TN refers to the number of bins correctly identified as not containing a boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a boundary (false negatives).
 Each of these quantities is obtained from the confusion matrix created by validating the model on the test data.
-The process was repeated for each $i^{th}$ holdout chromosome, and performances were aggregated using the mean and standard deviation.
+The process was repeated for each $i^{th}$ holdout chromosome, and performances were aggregated using the mean and standard deviation.-->
+
+<!--where TP refers to the number of bins correctly identified as containing a boundary (true positives), FP refers to the number of bins incorrectly identified as containing a boundary (false positives), TN refers to the number of bins correctly identified as not containing a boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a boundary (false negatives).
+Each of these quantities is obtained from the confusion matrix created by validating the model on the test data.
+The process was repeated for each $i^{th}$ holdout chromosome, and performances were aggregated using the mean and standard deviation.-->
 
@@
 To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivities and specificities at different cutoffs, across each holdout chromosome, and reported the corresponding average area under the curve (AUC).
+<!--%%%As before, the response vector for the test data was derived from cell line-specific Grubert boundaries.-->
 
@@
 To investigate whether we could alleviate the resolution limitations of conventional domain calling tools, we developed *preciseTAD*.
-This algorithm leverages a random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base-level resolution (Additional file 8: Figure S4<!--Supplementary Figure 2-->).
+This algorithm leverages an optimized random forest model in conjunction with density-based and partitioning techniques to predict boundaries at base-level resolution (Additional file 8: Figure S4).
 
-A random forest model $(M)$ was built on the optimal combination of predictor type (predictor space), resampling technique (class balancing correction), and top-ranked annotations (most informative genomic elements) for a set of binned chromosomes $\{k | k \ne i \}$ <!--, to maximally accurately predict boundaries at the _Hi-C resolution level_-->.
+A random forest model $(M)$ was built on the optimal combination of predictor type (predictor space), resampling technique (class balancing correction), and top-ranked annotations (most informative genomic elements) for a set of binned chromosomes $\{k | k \ne i \}$.
 To precisely identify boundary locations, we first constructed a _base-level resolution_ predictor space for the chromosome *i*, $A_{n \times p}$, where $n$ is the length of chromosome $i$ and $p$ is the optimal number of annotations.
@@
 The heuristic of $\epsilon$ is that density-reachable bases with genomic distances less than $\epsilon$ should occupy the same designated cluster.
-The default combination was set to $t=1.0$ and $\epsilon=10000$ based on our tests (Additional file 17: Figure S11<!--Supplementary Figure 11-->).
-
-<!--
-## Predicting boundaries across cell lines
-
-We aimed to extend the strategy of building and comparing boundary region prediction models using the same cell line versus across cell line data to predict boundaries at base level resolution across cell lines.
-To do so, we applied *preciseTAD* on models built using cell line-specific annotation data to predict boundaries on base-level annotation data from another cell line.
-As before, this strategy was compared to applying *preciseTAD* on models and base level annotation data from the same cell line.
--->
+The default combination was set to $t=1.0$ and $\epsilon=10000$ based on our tests (Additional file 17: Figure S11).
 
@@
 
-<!--
-The two proteins differ in that YY1 preferentially
-occupies interacting enhancers and promoters, whereas CTCF
-preferentially occupies sites distal from these regulatory elements that tend to form larger loops and participate in insulation.
-Deletion of YY1 binding sites or depletion of YY1 can disrupt
-enhancer-promoter contacts and normal gene expression.
-Thus, YY1-mediated structuring of enhancer-promoter loops is
-analogous to CTCF-mediated structuring of TADs, CTCF contact domains, and insulated neighborhoods. This model of
-YY1-mediated structuring of enhancer-promoter loops accounts
-for diverse functions reported previously for YY1, including contributions to both gene activation and repression and to gene
-dysregulation in cancer. ["YY1 Is a Structural Regulator
-of Enhancer-Promoter Loops"]
+<!--%%%
+## Predicting boundaries across cell lines
+
+We extended the *preciseTAD* algorithm by implementing a strategy to predict domain boundaries across cell lines.
+To do so, we applied *preciseTAD* on models built using cell line-specific annotation data to predict boundaries on base-level annotation data from another cell line.
+We compared this strategy to applying *preciseTAD* on models and base level annotation data from the same cell line.
+Results were compared by assessing the overlap between flanked same-cell-line and cross-cell-line predicted boundaries using venn diagrams and Jaccard indices.
 -->
@@
 Determining optimal data level characteristics for building TAD boundary region prediction models on GM12878.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
-Error bars indicate standard deviation from the mean performance across each holdout chromosome used for testing.
+Error bars indicate 1 standard deviation from the mean performance across each holdout chromosome used for testing.
 
@@
 
+<!--%%%
+**Figure 1.
+Resolution-specific data construction and feature engineering for random forest modeling.** (A) The linear genome was binned into non-overlapping resolution-specific intervals using *shifted binning* (see Methods).
+The response vector **Y** was defined as 1/0 if a genomic bin overlapped/did not overlap with a TAD (or loop) boundary.
+(B) Four types of associations between bins (blue dashed lines) and genomic annotations (green shapes) were considered to build the predictor space, including Average Peak Signal (Signal), Overlap Counts (OC), Overlap Percent (OP), and $log_{2}$ distance (Distance).
+
+**Figure 2.
+A machine learning framework for building domain boundary region prediction models.** Step 1 combines the response vector ($\textbf{Y}_N$) from *shifted binning* and a feature engineering procedure to form the data matrix $A_{N \times (p+1)}$ for chromosomes $\{1, 2, ..., i-1, i+1, ..., 22 \}$.
+Step 2 reserves the predictor-response matrix for the holdout chromosome $i$ as the test data using Grubert-defined boundaries as $\textbf{Y}_{test}$.
+Step 3 applies a resampling technique to the training data to address the class imbalance.
+Step 4 trains the random forest model and performs 3-fold cross-validation to tune the mtry parameter.
+Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and evaluates the model performance using balanced accuracy (BA).
+
+**Figure 3.
+Determining optimal data level characteristics for building TAD boundary region prediction models on GM12878.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Error bars indicate 1 standard deviation from the mean performance across each holdout chromosome used for testing.
+
+**Figure 4.
+SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in GM12878.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+(B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
+Error bars represent 1 standard deviation from the mean cross-validated accuracy across each holdout chromosome.
+(C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs.
+The columns represent the holdout chromosome excluded from the training data.
+Rows are sorted in decreasing order according to the columnwise average importance.
+(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on GM12878 data (blue, Arrowhead ground truth; red, Peakachu ground truth) versus training on K562 and testing on GM12878 data (black, dashed).
+The curves represent the average sensitivities and specificities across each holdout chromosome.
+The shaded areas around each curve represent 1 standard deviation from the average.
+
+**Figure 5.
+*preciseTAD* predicts more biologically meaningful TAD boundaries** (A) The location of Arrowhead-called TAD boundaries (blue) vs.
+*preciseTAD*-predicted TAD boundaries (green) on GM12878 data (chr14:50085000-50800000).
+The black line represents the predicted probability of each base being a TAD boundary.
+(B) A zoomed-in portion of the genome shows the preciseTAD boundary region (PTBR, highlighted yellow), a cluster of bases with high probability of being a boundary, and the corresponding signal profiles of CTCF, RAD21, SMC3, and ZNF143.
+
+**Figure 6.
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.** (C, D) Signal profile plots illustrating enrichment strength of CTCF, RAD21, SMC3, and ZNF143 sites around *preciseTAD*-predicted boundaries (green) compared to (A) Arrowhead-called boundaries (blue), (B) Peakachu loop boundaries (red), and (C) Grubert loop boundaries (purple).
+Boundaries involving Arrowhead and Grubert were flanked by 5 kb, while Peakachu-related boundaries were flanked by 10 kb.
+
+**Figure 7.
+*preciseTAD* boundaries are closer to CTCF sites and more conserved across cell lines**.
+(A) Violin plots illustrating the $log_{2}$ genomic distance distribution from ground-truth vs.
+*preciseTAD*-predicted boundaries to the nearest CTCF sites.
+The p-values are from the Wilcoxon Rank Sum test.
+(B-G) Venn diagrams illustrating the levels of conservation (overlap) between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by (B) Arrowhead, (C) Peakachu, and (D) Grubert, compared to *preciseTAD*-predicted boundaries using (E) Arrowhead-, (F) Peakachu-, and (G) Grubert-trained models, respectively.
+Boundaries involving Arrowhead and Grubert were flanked by 5 kb, while Peakachu-related boundaries were flanked by 10 kb.
+-->
+
 # Additional file legends
@@
 
-**Additional File 2: Table S1.** Data sources for Hi-C matrices used to call topologically associating domains with Arrowhead, as well as loop boundaries obtained by Peakachu.
+**Additional File 2: Table S1.** Data sources for Hi-C matrices used to call topologically associating domains with Arrowhead, as well as chromatin loop boundaries obtained by Peakachu.
 
@@
 
+<!--%%%
+**Additional File 1: Arrowhead Script.** An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5 kb, 10 kb, 25 kb, 50 kb, 100 kb resolutions.
+
+**Additional File 2: Table S1.** Data sources for Hi-C matrices used to call topologically associating domains with Arrowhead, as well as chromatin loop boundaries obtained by Peakachu and Grubert.
+
+**Additional File 3: Table S2.** Domain boundary data and class imbalance summaries across resolutions for Arrowhead, Peakachu, and Grubert on K562.
+
+**Additional File 4: Table S3.** A complete list of genomic annotations used to build the predictor space for all downstream models.
+The GRCh37/hg19 human genome assembly was used.
+“Genomic Class” - broad category of genomic features, “Element” - names of genomic features, “Cell line-Specific Source” - download URL specific to the cell line (not all annotations were provided by the same institutions).
+
+**Additional File 5: Figure S1.
+The $log_2$ transformation of genomic distances normalizes their distributions.** Distances are measured as the number of bases from the center of a genomic bin to the nearest genomic annotation center.
+Density curves of distances before (red) and after (blue) performing a $log_2$ transformation across 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb data resolutions for both the (A) GM12878 and (B) K562 cell lines.
+Each density curve represents an individual genomic annotation (77 total).
+
+**Additional File 6: Figure S2.
+Determining optimal data level characteristics for building TAD boundary region prediction models on K562.** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562.
+Averaged balanced accuracies are compared for Peakachu-trained models built on (B) GM12878 and (C) K562 within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple).
+Error bars indicate 1 standard deviation from the mean performance across each holdout chromosome used for testing.
+
+**Additional File 7: Figure S3.
+SMC3, RAD21, CTCF, and ZNF143 transcription factors accurately predict TAD and loop boundaries in K562.** (A) Barplots comparing performances of TAD (Arrowhead) and loop (Peakachu) boundary prediction models using histone modifications (HM), chromatin states (BroadHMM), transcription factor binding sites (TFBS), in addition to a model containing all three classes (ALL).
+(B) Recursive feature elimination (RFE) analysis used to select the optimal number of predictors.
+Error bars represent 1 standard deviation from the mean cross-validated accuracy across each holdout chromosome.
+(C) Clustered heatmap of the predictive importance for the union of the top 8 most predictive chromosome-specific TFBSs.
+The columns represent the holdout chromosome excluded from the training data.
+Rows are sorted in decreasing order according to the columnwise average importance.
+(D) Receiver operating characteristic (ROC) curves and the corresponding average area under the curves (AUCs) when training and testing on K562 data (blue, Arrowhead ground truth; red, Peakachu ground truth) versus training on GM12878 and testing on K5628 data (black, dashed).
+The curves represent the average sensitivities and specificities across each holdout chromosome.
+The shaded areas around each curve represent 1 standard deviation from the average.
+
+**Additional File 8: Figure S4. Pseudocode of the *preciseTAD* algorithm.**
+
+**Additional File 9: Table S4.** hg19/GRCh37 genomic coordinates of *preciseTAD*-predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562 cell lines, using models trained on Arrowhead, Peakachu, and Grubert TAD/chromatin loop boundaries as ground truth.
+For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability threshold (*t*) equal to 1 and epsilon-neighborhood ($\epsilon$) equal to 10000.
+For PTBPs, the start and end (start+1) coordinates define the most likely boundary point within each PTBR.
+
+**Additional File 10: Figure S5.
+*preciseTAD* boundaries are enriched for known molecular drivers of 3D chromatin.** Signal profile plots comparing the binding strength of top TFBS around flanked (A) Arrowhead called TAD boundaries (blue) vs.
+*preciseTAD*-predicted TAD boundaries (green) on K562, and (B) Peakachu chromatin loop boundaries (red) vs.
+*preciseTAD* predicted loop boundaries (green) on K562.
+
+**Additional File 11: Figure S6.
+Comparing enrichment levels between TAD/chromatin loop calling tools.** Signal profile plots comparing the binding strength of top TFBS around flanked Arrowhead called TAD boundaries (blue), Peakachu chromatin loop boundaries, Grubert chromatin loop boundaries (purple), and SpectralTAD called TAD boundaries (green) on (A) GM12878 and (B) on K562.
+
+**Additional File 12: Figure S7.
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Arrowhead boundaries.** Enrichment heatmaps comparing the signal distribution of CTCF, RAD21, SMC3, and ZNF143 around Arrowhead-called TAD boundaries vs.
+*preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
+
+**Additional File 13: Figure S8.
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Peakachu boundaries.** Enrichment heatmaps comparing the signal distribution of CTCF, RAD21, SMC3, and ZNF143 around Peakachu-predicted chromatin loop boundaries vs.
+*preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
+
+**Additional File 14: Figure S9.
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Grubert boundaries.** Enrichment heatmaps comparing the signal distribution of CTCF, RAD21, SMC3, and ZNF143 around Grubert-predicted chromatin loop boundaries vs.
+*preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
+
+**Additional File 15: Figure S10.
+*preciseTAD* boundaries are spatially closer to known molecular drivers of 3D chromatin.** Boxplots comparing the log2 genomic distance distributions from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
+p-values are derived from the Wilcoxon Rank Sum test.
+
+**Additional File 16: Figure S11.
+*preciseTAD* using Arrowhead ground truth boundaries are nested within *preciseTAD*-predicted boundaries using chromatin loop boundaries.** Venn diagrams of boundary overlap when implementing *preciseTAD* using Arrowhead boundaries vs.
+chromatin loop boundaries defined either by (A-B) Peakachu or (C-D) Grubert.
+Boundaries involving Arrowhead and Grubert were flanked by 5 kb, while Peakachu-related boundaries were flanked by 10 kb.
+
+**Additional File 17: Figure S12.
+*preciseTAD* trained on Arrowhead accurately predicts boundaries on cell lines using annotation data only.** Venn diagrams and signal profile plots comparing flanked predicted boundaries using Arrowhead trained models.
+(A) Models trained on GM12878 and predicted on GM12878 (red, GM on GM) vs.
+models trained on K562 and predicted on GM12878 (blue, K on GM).
+(B) Models trained on K562 and predicted on K562 (red, K on K) vs.
+models trained on GM12878 and predicted on K562 (blue, GM on K).
+Boundaries were flanked by 5 kb.
+
+**Additional File 18: Figure S13.
+*preciseTAD* trained on Peakachu accurately predicts boundaries on cell lines using annotation data only.** Venn diagrams and signal profile plots comparing flanked predicted boundaries using Arrowhead trained models.
+(A) Models trained on GM12878 and predicted on GM12878 (red, GM on GM) vs.
+models trained on K562 and predicted on GM12878 (blue, K on GM).
+(B) Models trained on K562 and predicted on K562 (red, K on K) vs.
+models trained on GM12878 and predicted on K562 (blue, GM on K).
+Boundaries were flanked by 10 kb.
+
+**Additional File 19: Figure S14.
+*preciseTAD* trained on Grubert accurately predicts boundaries on cell lines using annotation data only.** Venn diagrams and signal profile plots comparing flanked predicted boundaries using Arrowhead trained models.
+(A) Models trained on GM12878 and predicted on GM12878 (red, GM on GM) vs.
+models trained on K562 and predicted on GM12878 (blue, K on GM).
+(B) Models trained on K562 and predicted on K562 (red, K on K) vs.
+models trained on GM12878 and predicted on K562 (blue, GM on K).
+Boundaries were flanked by 5 kb.
+
+**Additional File 20: Table S5.** Additional performance metrics when implementing a random forest using Arrowhead/Peakachu ground truth TAD/loop boundaries.
+Performances are averaged across each holdout chromosome that was reserved for testing.
+
+**Additional File 21: Figure S15.
+Normalized Enrichment levels suggest t=1.0 and $\epsilon$=10000 as the most optimal parameters for biologically relevant *preciseTAD*-predicted boundaries.** Linecharts illustrating the normalized enrichment (NE) between CTCF, RAD21, SMC3, ZNF143 and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (*t*) and epsilon-neighborhood parameter values ($\epsilon$).
+NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model.
+Error bars indicate 1 standard deviation from the mean.
+
+**Additional File 99: Figure S99.
+*preciseTAD*-predicted TAD boundaries are resolution invariant.** Heatmaps illustrate the Jaccard indices between pairwise preciseTAD-predicted boundaries (green) and Arrowhead called TAD boundaries (blue) across resolution for (A) GM12878 and (B) K562.
+Boundaries were flanked by 50 kb.
+-->
+
 # Declarations

### 2021-01-21 BMC_Genome_Biology_submission/grubert_manuscript_figures_tables/manuscript/manuscript.Rmd
edits to grubert version of manuscript + additional refs

@@
 We used Arrowhead-called TAD boundaries [@durand2016juicer] and published Peakachu-predicted loop boundaries [@salameh2019supervised] as ground truth.
-Data from GM12878 and K562 cell lines at 5-100 kb resolution (Arrowhead) and 10 kb resolution (Peakachu) were used (Additional file 1: Arrowhead Script, Additional file 2: Table S1).
+Data from GM12878 and K562 cell lines at 5-100 kb resolution (Arrowhead) and 10 kb resolution (Peakachu) were used (Additional file 1: Arrowhead Script, Additional file 2: Table S1<!--Supplementary Table 1-->).
 We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base-level resolution from cell line-specific genome annotation data.
+
+<!--%%%%
+We developed a machine learning (ML) framework for determining the optimal set of data level characteristics to predict boundary regions of Topologically Associating Domains (TADs) and chromatin loops, collectively referred to as domain boundaries.
+We chose the random forest (RF) algorithm as our binary classification tool.
+The reason for it is two-fold: (1) to devise a tunable prediction rule in a supervised learning framework that is both robust to overfitting and able to handle multiple correlated predictors, and (2) to allow for an interpretable ranking of predictors [@boulesteix2012overview].
+For TAD prediction, we derived cell line specific boundaries at 5-100 kb resolutions using *Arrowhead* [@durand2016juicer] (Additional file 1: Arrowhead Script, Additional file 2: Table S1).
+For chromatin loop prediction, we downloaded loops derived by *Peakachu* [@salameh2019supervised] at 10 kb (Additional file 2: Table S1).
+Our models were trained on cell line-specific functional genomic annotation data (ChIP-seq peak regions) publicly available through ENCODE [@encode2004encode; @davis2018encyclopedia] (Additional file 4: Table S3).
+We used ChIA-PET derived loop boundaries [@grubert2020landscape] (Additional file 2: Table S1), referred hereafter as *Grubert* boundaries, as the gold standard when validating our models and extracting performance metrics (See Methods).
+We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base-level resolution from cell line-specific genome annotation data.-->
 
@@
 
-In total, we considered combinations of data from two cell lines *L = {GM12878, K562}*, five resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor spaces *P = {Signal, OC, OP, Distance}*, and three re-sampling techniques *S = {None, RUS, ROS, SMOTE}* (Figure 2).
+<!--%%%Our training/testing framework was used to determine the optimal set of data-level characteristics for TAD/loop boundary region prediction including resolution (bin size), feature engineering, and resampling (Figure 2).--> In total, we considered combinations of data from two cell lines *L = {GM12878, K562}*, five resolutions *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor spaces *P = {Signal, OC, OP, Distance}*, and three re-sampling techniques *S = {None, RUS, ROS, SMOTE}*.
 Once the model inputs were established, a random forest classifier was trained on $n-1$ autosomal chromosomes, while reserving the $i^{th}$ chromosome for testing.
 Three-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed at 500 and at 0.1% of the rows in the training data, respectively.
-Model performance was evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (see Methods).
+<!--%%%Models were validated on the testing data using cell line-specific Grubert-defined boundaries as $\textbf{Y}_{test}$ for gold standard comparison.--> Model performance was evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (see Methods).
 These strategies allowed us to select the best performing model in an unbiased manner.
@@
 
-We hypothesized that the type of genomic annotations may also affect predictive performance.
+We hypothesized that the class of genomic annotation may also affect predictive performance.
 Using the established optimal settings (RUS, Distance, 5 kb/10 kb (Arrowhead/Peakachu ground truth) genomic bins), we built separate random forest models using histone modifications (HM), BroadHMM chromatin states (BroadHMM), and transcription factor binding sites (TFBS).
@@
 Having demonstrated the optimal performance in our framework's ability to predict boundary regions, we next attempted to predict boundary regions in one cell line using the model pre-trained on data from another cell line (See Methods).
-We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from the GM12878 cell line resulted in an average AUC=0.792 (Figure 4D).
-Interestingly, when training on the K562 cell line and testing on GM12878, the average AUC increased slightly to 0.795.
+We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from the GM12878 cell line resulted in an average AUC=0.792 <!--%%% 0.840--> (Figure 4D).
+Interestingly, when training on the K562 cell line and testing on GM12878, the average AUC increased slightly to 0.795 <!--%%% 0.899-->.
 Likewise, the average performance of models trained using Peakachu boundaries and genomic annotation data from the GM12878 cell line was comparable to models trained on K562-specific Peakachu boundaries and genomic annotations (Avg.
-AUC=0.881 and 0.874, respectively).
+AUC=0.881 <!--%%% 0.923--> and 0.874 <!--%%% 0.876-->, respectively).
 These results were consistent when comparing training/testing strategies on K562 with training on GM12878 and testing on K562 data (Additional file 7: Figure S3D).
@@
 Next, we evaluated the biological significance of *preciseTAD* boundary points.
-The signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (Figure 5C, 5D; Additional file 10: Figure S5A, S5B).
-Surprised by the poor signal distribution around Arrowhead boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, and our SpectralTAD [@Cresswell:2020ab] TAD caller.
-We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the relatively well-performing Peakachu- and SpectralTAD-called boundaries (Additional file 10: Figure S5C, S5D).
-Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Additional file 11-12: Figure S6-S7).
+The signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (Figure 5C, 5D; Additional file 10: Figure S5A, S5B <!--%%%Figure 6A, 6B; Additional file 10: Figure S5A, S5B -->).
+<!--%%%Additionally, we found that when trained on cohesin-mediated chromatin loops, *preciseTAD*-predicted boundaries showed similar levels of enrichment to the set of ChIA-PET derived loop boundaries (Figure 6C; Additional file 10: Figure S5C).--> Surprised by the poor signal distribution around Arrowhead and Peakachu boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, <!--%%%Grubert,--> and our SpectralTAD [@Cresswell:2020ab] TAD caller.
+We confirmed the poor signal distribution around Arrowhead-, Peakachu-, and SpectralTAD-called boundaries,in contrast to the well-performing Grubert-defined boundaries (Additional file 10: Figure S5C, S5D <!--%%%Additional File 11: Figure S6-->).
+Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone<!--%%%, while showing similar levels of enrichment when compared to Grubert--> (Additional file 11-12: Figure S6-S7 <!--%%%Additional File 12-14: Figure S7-S8-->).
 *preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Additional file 13: Figure S8).
-These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
+These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.<!--%%%While *preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS compared to either Arrowhead and Peakachu boundaries alone, Grubert boundaries were found to be the most spatially proximal (Wilcoxon p-value < 0.001; Figure 7A; Additional file 15: Figure S10).
+These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation when compared to a novel TAD-caller or loop prediction algorithm.-->
+
+<!--%%%
+![**preciseTAD boundaries are more enriched for known molecular drivers of 3D chromatin.** (C, D) Signal profile plots illustrating enrichment strength of CTCF, RAD21, SMC3, and ZNF143 sites around *preciseTAD*-predicted boundaries (green) compared to (A) Arrowhead-called boundaries (blue), (B) Peakachu loop boundaries (red), and (C) Grubert loop boundaries (purple).
+Boundaries involving Arrowhead and Grubert were flanked by 5 kb, while Peakachu-related boundaries were flanked by 10 kb.](../main_figures/figure6.png)
+-->
 
@@
 
+<!--%%%Previous studies suggest that TAD boundaries are conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @sexton2012three].
+To assess the level of cross-cell-line conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, Arrowhead, Peakachu, and Grubert.
+Only 26% and 49% of boundaries were conserved between cell lines for Arrowhead and Peakachu boundaries (J=0.186 and J=0.388),respectively, while Grubert boundaries exhibited the largest level of conservation among TAD/loop calling tools at 52% (J=0.464) (Figure 7C-7D).
+Comparatively, *preciseTAD*-predicted boundaries were more conserved between GM12878 and K562 cell lines regardless of which ground truth boundary was used (45%; J=0.383, 56%; J=0.444, and 59%; J=0.495 respectively) (Figure 7E-7F).
+The better conservation of *preciseTAD*-predicted boundaries further supports the notion of their higher biological relevance.-->
+
 <!-- ![**preciseTAD boundaries are closer to CTCF sites and more conserved across cell lines**.
@@
 Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.](../main_figures/figure6.png) -->
-
-<!--%%%
-![**preciseTAD boundaries are more enriched for known molecular drivers of 3D chromatin.** (C, D) Signal profile plots illustrating enrichment strength of CTCF, RAD21, SMC3, and ZNF143 sites around *preciseTAD*-predicted boundaries (green) compared to (A) Arrowhead-called boundaries (blue), (B) Peakachu loop boundaries (red), and (C) Grubert loop boundaries (purple).
-Boundaries involving Arrowhead and Grubert were flanked by 5 kb, while Peakachu-related boundaries were flanked by 10 kb.](../main_figures/figure6.png)
--->
 
@@
 
-Guided by the high predictive performance when training and testing on different cell lines (Figure 4D), we opted to evaluate whether models trained using Arrowhead/Peakachu ground truth data in one cell line could be leveraged to predict boundaries using annotation data from another cell line.
+<!--%%%
+The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by either the Peakachu- or Grubert-trained model (Additional file 16: Figure S11).
+This is expected as loop boundaries detected by Peakachu and Grubert are more abundant, while comparatively wide TAD boundaries detected by Arrowhead likely represent the higher level of the 3D chromatin organization.
+Together with the results in Figure 4C, the high overlap between TAD and loop boundaries predicted by Arrowhead- and Peakachu-/Grubert-trained models suggests that TAD and loop boundaries may be driven by similar molecular mechanisms.-->
+
+Guided by the high predictive performance when training and testing on different cell lines (Figure 4D), we opted to evaluate whether models trained using Arrowhead/Peakachu<!--%%%/Grubert--> ground truth data in one cell line could be leveraged to predict boundaries using annotation data from another cell line.
 We evaluated two scenarios: 1) training on GM12878 and predicting boundaries on GM12878 (GM on GM) vs.
@@
 training on GM12878 and predicting boundaries on K562 (GM on K).
-Using Arrowhead-trained models, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries overlapped in both cross-cell-line prediction scenarios (Additional file 15: Figure S10A, S10B).
-Likewise, when using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlap (Additional file 15: Figure S10C, S10D).
-Furthermore, boundaries predicted on unseen annotation data exhibited a similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Additional file 15: Figure S10).
-These results indicate that *preciseTAD* pre-trained models can be successfully used to predict domain boundaries for cell lines lacking Hi-C data but for which genome annotation data is available.
+Using Arrowhead-trained models, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries overlapped in both cross-cell-line prediction scenarios (Additional file 15: Figure S10A, S10B <!--Additional file 17: Figure S12-->).
+When using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlap (Additional file 15: Figure S10C, S10D <!--Additional file 18: Figure S13-->).
+<!--%%%Lastly, when using Grubert-trained models, we observed 86% (J=0.698) and 80% (J=0.0.660) overlap (Additional file 19: Figure S14).--> Furthermore, boundaries predicted on unseen annotation data exhibited a similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Additional files 17-19: Figure S12-S14).
+These results indicate that *preciseTAD* pre-trained models can be successfully used to accurately predict both TAD and loop boundaries for cell lines lacking Hi-C data but for which genome annotation data is available.
 
@@
 
-We present *preciseTAD*, a machine learning approach for precise prediction of TAD or loop boundaries from functional genomic annotations.
+We present *preciseTAD*, a machine learning approach for precise prediction of TAD and chromatin loop boundaries from functional genomic annotations.
 *preciseTAD* leverages a random forest (RF) classification model built on low-resolution domain boundaries obtained from domain calling tools, and high-resolution genomic annotations as the predictor space.
 *preciseTAD* predicts the probability of each base being a boundary, and identifies the precise location of boundary regions and the most likely boundary points.
-*preciseTAD* was benchmarked against two boundary calling tools, Arrowhead [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
+*preciseTAD* was benchmarked against two boundary calling tools <!--%%%multiple boundary calling tools including Arrowhead [@durand2016juicebox], an established TAD-caller, Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops, and Grubert a method for mapping cohesin-mediated loops via chromatin interaction analysis by paired-end tag sequencing (ChIA-PET) [@grubert2020landscape].-->, Arrowhead [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
 We first optimized our RF model by systematically comparing different combinations of genome binning (resolution), feature engineering procedures, and resampling techniques.
@@
 *preciseTAD* is implemented as an R package, provides the pre-trained models, and allows for precise prediction of boundaries for any cell line for which the genomic annotations are available.
+
+<!--%%%%
+We present *preciseTAD*, a machine learning approach for precise prediction of TAD and chromatin loop boundaries from functional genomic annotations.
+*preciseTAD* leverages a random forest (RF) classification model built on low-resolution domain boundaries obtained from domain calling tools, and high-resolution genomic annotations as the predictor space.
+*preciseTAD* predicts the probability of each base being a boundary, and identifies the precise location of boundary regions and the most likely boundary points.
+*preciseTAD* was benchmarked against multiple boundary calling tools including Arrowhead [@durand2016juicebox], an established TAD-caller, Peakachu [@salameh2019supervised], a recently published algorithm for predicting chromatin loops, and Grubert [@grubert2020landscape], a method for mapping cohesin-mediated loops via chromatin interaction analysis by paired-end tag sequencing (ChIA-PET).
+We first optimized our RF model by systematically comparing different combinations of genome binning (resolution), feature engineering procedures, and resampling techniques.
+Our results demonstrate that genomic distance between boundary regions and genomic annotations coupled with random under-sampling results in the best model performance.
+We show that binding of four transcription factors (SMC3, RAD21, CTCF, ZNF143) is sufficient for accurate boundary predictions.
+*preciseTAD* is implemented as an R package (version 1.1.1; Bioconductor version 3.12) and provides the pre-trained models, via an ExperimentHub R package *preciseTADhub* (version 0.99.8; Bioconductor version 3.13), which allows for precise prediction of boundaries for any cell line for which the genomic annotations are available.
+-->
 
@@
 
-Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Additional file 16: Table S5).
+Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Additional file 16: Table S5 <!--%%%Additional file 20: Table S5-->).
 Our aim was to have a balanced metric sensitive to class imbalance such that it would not favor one component of the confusion matrix.
@@
 
-We show that, unlike Arrowhead, *preciseTAD* does not inflate the number of predicted boundaries, providing only the most biologically meaningful boundaries that demarcate regions of high inter-chromosomal interactions.
-*preciseTAD* boundaries predicted using models trained on either TAD or loop boundaries (Arrowhead and Peakachu data) were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops may be generated by similar mechanisms [@hansen2018recent].
+We show that, unlike Arrowhead, *preciseTAD* does not inflate the number of predicted boundaries, providing only the most biologically meaningful TAD boundaries that demarcate regions of high inter-chromosomal interactions.
+*preciseTAD* boundaries predicted using models trained on either TAD or loop boundaries were enriched for known architectural transcription factors including CTCF, RAD21, SMC3, and ZNF143, supporting recent observations that TADs and loops may be generated by similar mechanisms [@hansen2018recent].
 Likewise, *preciseTAD* boundaries were more conserved between GM12878 and K562 cell lines, a known feature among the 3D architecture of the human genome, further highlighting their biological significance.
@@
 As a heuristic, we evaluated the pairwise combination of 3 different thresholds ($t=(0.975,0.99,1.0)$) and 6 different $\epsilon$ values ($\epsilon=(1000,5000,10000,15000,20000,25000)$)).
-We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (Additional file 17: Figure S11).
+We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (Additional file 17: Figure S11 <!--%%%Additional file 21: Figure S15-->).
 
@@
 Given the wide variety of domain callers and their variable performance [@Zufferey:2018aa; @forcato2017comparison], defining "ground truth" boundaries is challenging.
-<!--Ideally, we would benchmark *preciseTAD* against simulated boundaries.
-While methods for simulating Hi-C data sets with boundary annotations exist [@forcato2017comparison; @zheng2020freehi], methods for simulating the associated genomic annotations (the main component guiding *preciseTAD* predictions) are lacking.-->Ultra-deep Hi-C sequencing [@bonev2017multiscale] and newer technologies for precise mapping of chromatin interactions (e.g., Micro-C [@Krietenstein:2020aa]), coupled with more precise technologies for genomic annotation profiling (e.g., CUT&RUN for precise mapping of transcription factor binding sites) will help to refine the location and the genomic signatures of the "ground truth" boundaries.
+Ultra-deep Hi-C sequencing [@bonev2017multiscale] and newer technologies for precise mapping of chromatin interactions (e.g., Micro-C [@Krietenstein:2020aa]), coupled with more precise technologies for genomic annotation profiling (e.g., CUT&RUN for precise mapping of transcription factor binding sites) will help to refine the location and the genomic signatures of the "ground truth" boundaries.
 In the current work, we feel that the total number of domain boundaries is sufficient to guide learning of the association between genomic annotations and boundaries for precise boundary predictions.
-Indeed, models trained on the larger number of Peakachu-predicted boundaries performed better than those trained on Arrowhead boundaries.
-Although we provide models trained on both boundary types, we recommend Peakachu-trained models for the base-level prediction of domain boundaries.
+Indeed, models trained on the larger number of Peakachu-defined boundaries performed better than those trained on Arrowhead boundaries.
+Although we provide models trained on both boundary types in *preciesTADhub*, we recommend Peakachu-trained models for the base-level prediction of domain boundaries.
 
@@
 To date (September 2020), the ENCODE project has only five cell lines (GM12878, K562, H1-hESC, HeLa-S3, HepG2) with all four transcription factor genomic annotations.
-Efforts to <!--systematically catalog chromatin conformation capture data [@Wang:2018ab] and -->impute missing cell line-specific genome annotation information [@Schreiber:2020aa] started to appear.
+Efforts to impute missing cell line-specific genome annotation information [@Schreiber:2020aa] started to appear.
 We envision the broader availability of cell line-specific genomic annotations will enable a more systematic analysis of domain boundaries using *preciseTAD*.
-<!--*preciseTAD* requires both cell line-specific chromatin conformation capture data (Hi-C in the current study) and genome annotation data.
-Hi-C data provides information about the approximate location of domain boundaries, while genome annotation data is used to train a model that can predict boundaries at the base-level resolution.
-The diversity of chromatin conformation capture technologies [@Kempfer:2019aa] and analysis methods [@Hansen:2019aa] limits the availability of harmonized cell line-specific domain boundary information.-->
 

### 2021-01-21 BMC_Genome_Biology_submission/grubert_manuscript_figures_tables/manuscript/manuscript.Rmd
revised commenting scheme for new sentences/paragraphs

@@
 
+<!--
 We developed a machine learning (ML) framework for determining the optimal set of data level characteristics to predict boundary regions of Topologically Associating Domains (TADs) and chromatin loops, collectively referred to as domain boundaries.
@@
 We used Arrowhead-called TAD boundaries [@durand2016juicer] and published Peakachu-predicted loop boundaries [@salameh2019supervised] as ground truth.
-Data from GM12878 and K562 cell lines at 5-100 kb resolution (Arrowhead) and 10 kb resolution (Peakachu) were used (Additional file 1: Arrowhead Script, Additional file 2: Table S1<!--Supplementary Table 1-->).
+Data from GM12878 and K562 cell lines at 5-100 kb resolution (Arrowhead) and 10 kb resolution (Peakachu) were used (Additional file 1: Arrowhead Script, Additional file 2: Table S1).
 We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base-level resolution from cell line-specific genome annotation data.
+-->
 
-<!--%%%%
+<!--%%%% revised paragraph-->
 We developed a machine learning (ML) framework for determining the optimal set of data level characteristics to predict boundary regions of Topologically Associating Domains (TADs) and chromatin loops, collectively referred to as domain boundaries.
@@
 We used ChIA-PET derived loop boundaries [@grubert2020landscape] (Additional file 2: Table S1), referred hereafter as *Grubert* boundaries, as the gold standard when validating our models and extracting performance metrics (See Methods).
-We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base-level resolution from cell line-specific genome annotation data.-->
+We next developed *preciseTAD*, an R package that leverages an optimally built RF to precisely predict genomic coordinates of TAD and loop boundaries at base-level resolution from cell line-specific genome annotation data.
+<!--%%%-->
 
@@
 |        Grubert        |       5    kb              |                        16232                       |                          18455                              |                535363               |        0.07            |
-Table: Domain boundary data and class imbalance summaries across resolutions for Arrowhead, Peakachu<!--%%%, and Grubert--> on GM12878.
+Table: Domain boundary data and class imbalance summaries across resolutions for Arrowhead, Peakachu<!--%%%-->, and Grubert<!--%%%--> on GM12878.
 
@@
 
-<!--%%%Our training/testing framework was used to determine the optimal set of data-level characteristics for TAD/loop boundary region prediction including resolution (bin size), feature engineering, and resampling (Figure 2).--> In total, we considered combinations of data from two cell lines *L = {GM12878, K562}*, five resolutions *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor spaces *P = {Signal, OC, OP, Distance}*, and three re-sampling techniques *S = {None, RUS, ROS, SMOTE}*.
+<!--%%%-->Our training/testing framework was used to determine the optimal set of data-level characteristics for TAD/loop boundary region prediction including resolution (bin size), feature engineering, and resampling (Figure 2).<!--%%%--> In total, we considered combinations of data from two cell lines *L = {GM12878, K562}*, five resolutions *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, four types of predictor spaces *P = {Signal, OC, OP, Distance}*, and three re-sampling techniques *S = {None, RUS, ROS, SMOTE}*.
 Once the model inputs were established, a random forest classifier was trained on $n-1$ autosomal chromosomes, while reserving the $i^{th}$ chromosome for testing.
 Three-fold cross-validation was used to tune the *mtry* hyperparameter, while *ntree* and *nodesize* were fixed at 500 and at 0.1% of the rows in the training data, respectively.
-<!--%%%Models were validated on the testing data using cell line-specific Grubert-defined boundaries as $\textbf{Y}_{test}$ for gold standard comparison.--> Model performance was evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (see Methods).
+<!--%%%-->Models were validated on the testing data using cell line-specific Grubert-defined boundaries as $\textbf{Y}_{test}$ for gold standard comparison.<!--%%%--> Model performance was evaluated by aggregating the mean balanced accuracy (BA) across each holdout chromosome (see Methods).
 These strategies allowed us to select the best performing model in an unbiased manner.
@@
 Having demonstrated the optimal performance in our framework's ability to predict boundary regions, we next attempted to predict boundary regions in one cell line using the model pre-trained on data from another cell line (See Methods).
-We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from the GM12878 cell line resulted in an average AUC=0.792 <!--%%% 0.840--> (Figure 4D).
-Interestingly, when training on the K562 cell line and testing on GM12878, the average AUC increased slightly to 0.795 <!--%%% 0.899-->.
+We found that training and testing using Arrowhead ground truth TAD boundaries and genomic annotation data from the GM12878 cell line resulted in an average AUC=<!--0.792--> <!--%%%--> 0.840<!--%%%--> (Figure 4D).
+Interestingly, when training on the K562 cell line and testing on GM12878, the average AUC increased slightly to <!--0.795--> <!--%%%--> 0.899<!--%%%-->.
 Likewise, the average performance of models trained using Peakachu boundaries and genomic annotation data from the GM12878 cell line was comparable to models trained on K562-specific Peakachu boundaries and genomic annotations (Avg.
-AUC=0.881 <!--%%% 0.923--> and 0.874 <!--%%% 0.876-->, respectively).
+AUC=<!--0.881--> <!--%%%--> 0.923<!--%%%--> and <!--0.874--> <!--%%%--> 0.876<!--%%%-->, respectively).
 These results were consistent when comparing training/testing strategies on K562 with training on GM12878 and testing on K562 data (Additional file 7: Figure S3D).
@@
 Next, we evaluated the biological significance of *preciseTAD* boundary points.
-The signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (Figure 5C, 5D; Additional file 10: Figure S5A, S5B <!--%%%Figure 6A, 6B; Additional file 10: Figure S5A, S5B -->).
-<!--%%%Additionally, we found that when trained on cohesin-mediated chromatin loops, *preciseTAD*-predicted boundaries showed similar levels of enrichment to the set of ChIA-PET derived loop boundaries (Figure 6C; Additional file 10: Figure S5C).--> Surprised by the poor signal distribution around Arrowhead and Peakachu boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, <!--%%%Grubert,--> and our SpectralTAD [@Cresswell:2020ab] TAD caller.
-We confirmed the poor signal distribution around Arrowhead-, Peakachu-, and SpectralTAD-called boundaries,in contrast to the well-performing Grubert-defined boundaries (Additional file 10: Figure S5C, S5D <!--%%%Additional File 11: Figure S6-->).
-Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone<!--%%%, while showing similar levels of enrichment when compared to Grubert--> (Additional file 11-12: Figure S6-S7 <!--%%%Additional File 12-14: Figure S7-S8-->).
-*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Additional file 13: Figure S8).
-These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.<!--%%%While *preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS compared to either Arrowhead and Peakachu boundaries alone, Grubert boundaries were found to be the most spatially proximal (Wilcoxon p-value < 0.001; Figure 7A; Additional file 15: Figure S10).
-These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation when compared to a novel TAD-caller or loop prediction algorithm.-->
+The signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (<!--Figure 5C, 5D; Additional file 10: Figure S5A, S5B--> <!--%%%-->Figure 6A, 6B; Additional file 10: Figure S5A, S5B <!--%%%-->).
+<!--%%%-->Additionally, we found that when trained on cohesin-mediated chromatin loops, *preciseTAD*-predicted boundaries showed similar levels of enrichment to the set of ChIA-PET derived loop boundaries (Figure 6C; Additional file 10: Figure S5C).<!--%%%--> Surprised by the poor signal distribution around Arrowhead and Peakachu boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, <!--%%%-->Grubert,<!--%%%--> and our SpectralTAD [@Cresswell:2020ab] TAD caller.
+We confirmed the poor signal distribution around Arrowhead-, Peakachu-, and SpectralTAD-called boundaries,in contrast to the well-performing Grubert-defined boundaries (<!--Additional file 10: Figure S5C, S5D--> <!--%%%-->Additional File 11: Figure S6<!--%%%-->).
+Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone<!--%%%-->, while showing similar levels of enrichment when compared to Grubert<!--%%%--> (<!--Additional file 11-12: Figure S6-S7--> <!--%%%-->Additional File 12-14: Figure S7-S9<!--%%%-->).
+*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, <!--Figure 6A, Additional file 13: Figure S8-->  <!--%%%-->Figure 7A; Additional file 15: Figure S10<!--%%%-->).
+These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.<!--%%%-->While *preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS compared to either Arrowhead and Peakachu boundaries alone, Grubert boundaries were found to be the most spatially proximal (Wilcoxon p-value < 0.001; Figure 7A; Additional file 15: Figure S10).
+These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation when compared to a novel TAD-caller or loop prediction algorithm.<!--%%%-->
 
@@
 
+<!--
 Previous studies suggest that TAD boundaries are conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @sexton2012three].
@@
 The better conservation of *preciseTAD*-predicted boundaries further supports the notion of their higher biological relevance.
+-->
 
-<!--%%%Previous studies suggest that TAD boundaries are conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @sexton2012three].
+<!--%%%revised paragraph-->
+Previous studies suggest that TAD boundaries are conserved across cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @sexton2012three].
 To assess the level of cross-cell-line conservation, we evaluated the overlap between cell line-specific boundaries detected by *preciseTAD*, Arrowhead, Peakachu, and Grubert.
@@
 Comparatively, *preciseTAD*-predicted boundaries were more conserved between GM12878 and K562 cell lines regardless of which ground truth boundary was used (45%; J=0.383, 56%; J=0.444, and 59%; J=0.495 respectively) (Figure 7E-7F).
-The better conservation of *preciseTAD*-predicted boundaries further supports the notion of their higher biological relevance.-->
+The better conservation of *preciseTAD*-predicted boundaries further supports the notion of their higher biological relevance.
+<!--%%%-->
 
@@
 
+<!--
 The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by the Peakachu-trained model (Additional file 14: Figure S9).
@@
 Together with the results in Figure 4C, the high overlap between boundaries predicted by Arrowhead- and Peakachu-trained models suggests that TAD and loop boundaries may be driven by similar molecular mechanisms.
+-->
 
-<!--%%%
+<!--%%%revised paragraph-->
 The majority of boundaries predicted by the Arrowhead-trained *preciseTAD* model represented a subset of the larger group of boundaries predicted by either the Peakachu- or Grubert-trained model (Additional file 16: Figure S11).
 This is expected as loop boundaries detected by Peakachu and Grubert are more abundant, while comparatively wide TAD boundaries detected by Arrowhead likely represent the higher level of the 3D chromatin organization.
-Together with the results in Figure 4C, the high overlap between TAD and loop boundaries predicted by Arrowhead- and Peakachu-/Grubert-trained models suggests that TAD and loop boundaries may be driven by similar molecular mechanisms.-->
+Together with the results in Figure 4C, the high overlap between TAD and loop boundaries predicted by Arrowhead- and Peakachu-/Grubert-trained models suggests that TAD and loop boundaries may be driven by similar molecular mechanisms.
+<!--%%%-->
 
-Guided by the high predictive performance when training and testing on different cell lines (Figure 4D), we opted to evaluate whether models trained using Arrowhead/Peakachu<!--%%%/Grubert--> ground truth data in one cell line could be leveraged to predict boundaries using annotation data from another cell line.
+Guided by the high predictive performance when training and testing on different cell lines (Figure 4D), we opted to evaluate whether models trained using Arrowhead/Peakachu<!--%%%-->/Grubert<!--%%%--> ground truth data in one cell line could be leveraged to predict boundaries using annotation data from another cell line.
 We evaluated two scenarios: 1) training on GM12878 and predicting boundaries on GM12878 (GM on GM) vs.
@@
 training on GM12878 and predicting boundaries on K562 (GM on K).
-Using Arrowhead-trained models, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries overlapped in both cross-cell-line prediction scenarios (Additional file 15: Figure S10A, S10B <!--Additional file 17: Figure S12-->).
-When using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlap (Additional file 15: Figure S10C, S10D <!--Additional file 18: Figure S13-->).
-<!--%%%Lastly, when using Grubert-trained models, we observed 86% (J=0.698) and 80% (J=0.0.660) overlap (Additional file 19: Figure S14).--> Furthermore, boundaries predicted on unseen annotation data exhibited a similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Additional files 17-19: Figure S12-S14).
+Using Arrowhead-trained models, 76% (J=0.701) and 81% (J=0.751) of predicted boundaries overlapped in both cross-cell-line prediction scenarios (<!--Additional file 15: Figure S10A, S10B--> <!--%%%-->Additional file 17: Figure S12<!--%%%-->).
+When using Peakachu-trained models, we observed 85% (J=0.705) and 88% (J=0.759) overlap (<!--Additional file 15: Figure S10C, S10D--> <!--%%%-->Additional file 18: Figure S13<!--%%%-->).
+<!--%%%-->Lastly, when using Grubert-trained models, we observed 86% (J=0.698) and 80% (J=0.0.660) overlap (Additional file 19: Figure S14).<!--%%%--> Furthermore, boundaries predicted on unseen annotation data exhibited a similar level of enrichment for CTCF, RAD21, SMC3, and ZNF143 as did those trained and predicted on the same cell line (Additional files 17-19: Figure S12-S14).
 These results indicate that *preciseTAD* pre-trained models can be successfully used to accurately predict both TAD and loop boundaries for cell lines lacking Hi-C data but for which genome annotation data is available.
@@
 
+<!--
 We present *preciseTAD*, a machine learning approach for precise prediction of TAD and chromatin loop boundaries from functional genomic annotations.
@@
 *preciseTAD* predicts the probability of each base being a boundary, and identifies the precise location of boundary regions and the most likely boundary points.
-*preciseTAD* was benchmarked against two boundary calling tools <!--%%%multiple boundary calling tools including Arrowhead [@durand2016juicebox], an established TAD-caller, Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops, and Grubert a method for mapping cohesin-mediated loops via chromatin interaction analysis by paired-end tag sequencing (ChIA-PET) [@grubert2020landscape].-->, Arrowhead [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
+*preciseTAD* was benchmarked against two boundary calling tools, Arrowhead [@durand2016juicebox], an established TAD-caller, and Peakachu [@salameh2019supervised] a recently published algorithm for predicting chromatin loops.
 We first optimized our RF model by systematically comparing different combinations of genome binning (resolution), feature engineering procedures, and resampling techniques.
@@
 *preciseTAD* is implemented as an R package, provides the pre-trained models, and allows for precise prediction of boundaries for any cell line for which the genomic annotations are available.
+-->
 
-<!--%%%%
+<!--%%%%revised paragraph-->
 We present *preciseTAD*, a machine learning approach for precise prediction of TAD and chromatin loop boundaries from functional genomic annotations.
@@
 *preciseTAD* is implemented as an R package (version 1.1.1; Bioconductor version 3.12) and provides the pre-trained models, via an ExperimentHub R package *preciseTADhub* (version 0.99.8; Bioconductor version 3.13), which allows for precise prediction of boundaries for any cell line for which the genomic annotations are available.
--->
+<!--%%%%-->
 
@@
 
-Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (Additional file 16: Table S5 <!--%%%Additional file 20: Table S5-->).
+Besides balanced accuracy (BA), we investigated five other performance metrics, including accuracy, area under the receiver operating characteristic curve (AUROC), precision, F1-score, and area under the precision-recall curve (AUPRC) (<!--Additional file 16: Table S5--> <!--%%%-->Additional file 20: Table S5<!--%%%-->).
 Our aim was to have a balanced metric sensitive to class imbalance such that it would not favor one component of the confusion matrix.
@@
 As a heuristic, we evaluated the pairwise combination of 3 different thresholds ($t=(0.975,0.99,1.0)$) and 6 different $\epsilon$ values ($\epsilon=(1000,5000,10000,15000,20000,25000)$)).
-We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (Additional file 17: Figure S11 <!--%%%Additional file 21: Figure S15-->).
+We found that the normalized overlaps - calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries - between top TFBS sites and flanked *preciseTAD* boundaries converged for combinations of $t=1.0$ and $\epsilon=10000$ (<!--Additional file 17: Figure S11--> <!--%%%-->Additional file 21: Figure S15<!--%%%-->).
 
@@
 Chromosome 9 was excluded from all downstream analyses due to the sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-<!--%%% Additionally cohesin-mediated chromatin loops mapped via chromatin interaction analysis by paired-end tag sequencing (ChIA-PET) were downloaded for GM12878 and K562 [@grubert2020landscape] (Additional file 2: Table S1), which we refer to as *Grubert*.--> Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Additional file 3: Table S2).
+<!--%%%-->Additionally cohesin-mediated chromatin loops mapped via chromatin interaction analysis by paired-end tag sequencing (ChIA-PET) were downloaded for GM12878 and K562 [@grubert2020landscape] (Additional file 2: Table S1), which we refer to as *Grubert*.<!--%%%--> Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Additional file 3: Table S2).
 
@@
 The binned data for the holdout chromosome $i$ was reserved for testing.
-<!--%%%The response vector associated with the testing data ($\textbf{Y}_{test}$) was built using Grubert-defined chromatin loops as a gold standard when validating the models.--> Models were then evaluated using Balanced Accuracy (BA), defined as the average of sensitivity and specificity:
+<!--%%%-->The response vector associated with the testing data ($\textbf{Y}_{test}$) was built using Grubert-defined chromatin loops as a gold standard when validating the models.<!--%%%--> Models were then evaluated using Balanced Accuracy (BA), defined as the average of sensitivity and specificity:
 
@@
 
-<!--%%%where values of the confusion matrix, true negatives (TP), false positives (FP), true negatives (TN), and false negatives (FN) were related to genomic bins that contained a Grubert-defined boundary in the test data.
+<!--
+where TP refers to the number of bins correctly identified as containing a boundary (true positives), FP refers to the number of bins incorrectly identified as containing a boundary (false positives), TN refers to the number of bins correctly identified as not containing a boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a boundary (false negatives).
+Each of these quantities is obtained from the confusion matrix created by validating the model on the test data.
+The process was repeated for each $i^{th}$ holdout chromosome, and performances were aggregated using the mean and standard deviation.
+-->
+
+<!--%%%revised paragraph-->
+where values of the confusion matrix, true negatives (TP), false positives (FP), true negatives (TN), and false negatives (FN) were related to genomic bins that contained a Grubert-defined boundary in the test data.
 That is, TP refers to the number of bins correctly identified as containing a boundary (true positives), FP refers to the number of bins incorrectly identified as containing a boundary (false positives), TN refers to the number of bins correctly identified as not containing a boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a boundary (false negatives).
 Each of these quantities is obtained from the confusion matrix created by validating the model on the test data.
-The process was repeated for each $i^{th}$ holdout chromosome, and performances were aggregated using the mean and standard deviation.-->
-
-<!--where TP refers to the number of bins correctly identified as containing a boundary (true positives), FP refers to the number of bins incorrectly identified as containing a boundary (false positives), TN refers to the number of bins correctly identified as not containing a boundary (true negatives), and FN refers to the number of bins incorrectly identified as not containing a boundary (false negatives).
-Each of these quantities is obtained from the confusion matrix created by validating the model on the test data.
-The process was repeated for each $i^{th}$ holdout chromosome, and performances were aggregated using the mean and standard deviation.-->
+The process was repeated for each $i^{th}$ holdout chromosome, and performances were aggregated using the mean and standard deviation.
+<!--%%%-->
 
@@
 To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivities and specificities at different cutoffs, across each holdout chromosome, and reported the corresponding average area under the curve (AUC).
-<!--%%%As before, the response vector for the test data was derived from cell line-specific Grubert boundaries.-->
+<!--%%%-->As before, the response vector for the test data was derived from cell line-specific Grubert boundaries.<!--%%%-->
 
@@
 
-<!--%%%
+<!--%%%new paragraph-->
 ## Predicting boundaries across cell lines
@@
 Results were compared by assessing the overlap between flanked same-cell-line and cross-cell-line predicted boundaries using venn diagrams and Jaccard indices.
--->
+<!--%%%-->
 
@@
 
+<!--
 **Figure 1.
@@
 Boundaries involving Arrowhead/Peakachu were flanked by 5 kb/10 kb, respectively.
+-->
 
-<!--%%%
+<!--%%%-->
 **Figure 1.
@@
 Boundaries involving Arrowhead and Grubert were flanked by 5 kb, while Peakachu-related boundaries were flanked by 10 kb.
--->
+<!--%%%-->
 
@@
 
+<!--
 **Additional File 1: Arrowhead Script.** An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5 kb, 10 kb, 25 kb, 50 kb, 100 kb resolutions.
@@
 Error bars indicate 1 standard deviation from the mean.
+-->
 
-<!--%%%
+<!--%%%-->
 **Additional File 1: Arrowhead Script.** An example script for applying Arrowhead to in situ Hi-C data (HIC001-HIC018) to obtain chromosome-specific TAD boundaries on the GM12878 cell line at 5 kb, 10 kb, 25 kb, 50 kb, 100 kb resolutions.
@@
 Boundaries were flanked by 50 kb.
--->
+<!--%%%-->
 

### 2021-01-22 BMC_Genome_Biology_submission/grubert_manuscript_figures_tables/manuscript/manuscript.Rmd
minor edits for grammar and structure including new reference

@@
 At the megabase scale, TADs represent regions on the linear genome that are highly self-interacting.
-Emerging evidence has linked TADs to critical roles in cell dynamics and cell differentiation.
+Emerging evidence has linked TADs to critical roles in cell dynamics and cell differentiation [@phillips2013architectural].
 Studies have shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
 Disruption of boundaries demarcating TADs and loops promotes cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@lupianez2016breaking;@Sun:2018aa;@Meaburn:2007aa].
-Identifying the precise location of TAD and chromatin loop boundaries remains a top priority in our goal to fully understand the functionality of the human genome.
+Thus, identifying the precise location of TAD and chromatin loop boundaries remains a top priority in our goal to fully understand the functionality of the human genome.
 
@@
 While these low-resolution Hi-C datasets can be used to probe higher-order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define TAD and loop boundaries [@fudenberg2016formation].
-Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth [@schmitt2016genome], obtaining high-resolution HI-C data and boundaries remains difficult.
+Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth [@schmitt2016genome], obtaining high-resolution Hi-C data and boundaries remains difficult.
 
@@
 We demonstrate that *preciseTAD* predictions are more enriched for known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143.
-Further, we show that *preciseTAD*-predicted boundaries are more conserved across cell lines, and the model trained in one cell line can predict boundaries in another cell line.
+Further, we show that *preciseTAD*-predicted boundaries are more conserved across cell lines, and the model trained in one cell line can accurately predict boundaries in another cell line.
 This improved precision in the domain boundary location can provide insight into the association between genomic regulators and the 3D genome organization.
-The *preciseTAD* R package is freely available on https://bioconductor.org/packages/preciseTAD.
+The *preciseTAD* R package and supplementary *preciseTADhub* ExperimentHub package are freely available on Bioconductor.
 
@@
 For chromatin loop prediction, we downloaded loops derived by *Peakachu* [@salameh2019supervised] at 10 kb (Additional file 2: Table S1).
-Our models were trained on cell line-specific functional genomic annotation data (ChIP-seq peak regions) publicly available through ENCODE [@encode2004encode; @davis2018encyclopedia] (Additional file 4: Table S3).
+Our models were trained on cell line-specific functional genomic annotation data (ChIP-seq peak regions) publicly available through ENCODE [@encode2004encode; @davis2018encyclopedia] (Additional file 3: Table S2).
 We used ChIA-PET derived loop boundaries [@grubert2020landscape] (Additional file 2: Table S1), referred hereafter as *Grubert* boundaries, as the gold standard when validating our models and extracting performance metrics (See Methods).
@@
 Boundary regions were defined as genomic bins containing a called boundary ($Y = 1$), while non-boundary regions were defined as bins that did not contain a called boundary ($Y = 0$) (Figure 1A, see Methods).
-The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Additional file 3: Table S2).
+The total number of called TADs, their unique boundaries, and the number of genomic bins expectedly decreased with the decreased resolution of Hi-C data (Table 1, Additional file 4: Table S3).
 The number of non-boundary regions highly outnumbered boundary regions.
@@
 Furthermore, 5 kb resolution genomic bins led to the optimal prediction for TAD boundary regions on both cell lines.
-Random forest models built on Peakachu-defined loop boundary regions yielded optimal prediction performance when using a distance-type predictor space, with SMOTE resampling only marginally outperforming RUS, for both cell lines (Additional file 6: Figure S2B, S2C).
+Random forest models built on Peakachu-defined loop boundary regions yielded optimal prediction performance when using a distance-type predictor space, with RUS marginally outperforming SMOTE, for both cell lines (Additional file 6: Figure S2B, S2C).
 Our results indicate that random under-sampling, distance-type predictors, and high-resolution Hi-C data provide the optimal set of data level characteristics for both TAD and chromatin loop boundary prediction.
@@
 We optimized our model by only considering these top four TFBS when building the random forest model, thereby decreasing computational burden while maintaining high predictive performance.
-In summary, our model was able to yield the known molecular drivers of the loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa].
+In summary, our model was able to yield the known molecular drivers of the loop extrusion model [@hansen2018recent;@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @Mirny:2019aa; @Davidson:2019aa], suggesting that TAD and loop formation are carried out by similar mechanisms.
 
@@
 Likewise, the average performance of models trained using Peakachu boundaries and genomic annotation data from the GM12878 cell line was comparable to models trained on K562-specific Peakachu boundaries and genomic annotations (Avg.
-AUC=<!--0.881--> <!--%%%--> 0.923<!--%%%--> and <!--0.874--> <!--%%%--> 0.876<!--%%%-->, respectively).
+AUC=<!--0.881--> <!--%%%--> 0.923<!--%%%--> and <!--0.874--> <!--%%%--> 0.876<!--%%%-->, respectively (Figure 4D)).
 These results were consistent when comparing training/testing strategies on K562 with training on GM12878 and testing on K562 data (Additional file 7: Figure S3D).
-The average ROC curves were found to be within 1 standard deviation of each other, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.
+In both instances the average ROC curves were found to be within 1 standard deviation of each other, suggesting that a model trained on data from one cell line performs well when using the data from another cell line, allowing for the opportunity to predict boundaries for cell lines that do not currently have Hi-C data available.
 
@@
 When trained using Arrowhead and Peakachu ground truth boundaries at 5 kb and 10 kb, respectively, the *preciseTAD* model predicted a total of 12,258 TAD and 15,707 chromatin loop boundaries in GM12878, as well as 9,603 TAD and 11,154 chromatin loop boundaries in K562 cell line (Additional file 9: Table S4).
-We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Additional file 3: Table S2).
+We reported less predicted TAD boundaries at 5 kb than Arrowhead on both cell lines (Table 1, Additional file 4: Table S3).
 This can be attributed to Arrowhead's inflation of called TADs at 5 kb, that, when visualized, often do not correspond to domains enriched in internal interactions (Figure 5A) and signal of known drivers of domain boundaries (Figure 5B).
-*preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Additional file 3: Table S2).
+*preciseTAD* also predicted fewer chromatin loop boundaries than Peakachu (Table 1, Additional file 4: Table S3).
 This can be attributed to Peakachu's use of only CTCF sites to call boundaries, while *preciseTAD* leverages four known drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143.
@@
 The signal of four known molecular drivers of 3D chromatin (CTCF, RAD21, SMC3, and ZNF143) colocalized more frequently around *preciseTAD*-predicted boundary points, as compared to Arrowhead-called TAD and Peakachu loop boundaries, respectively (<!--Figure 5C, 5D; Additional file 10: Figure S5A, S5B--> <!--%%%-->Figure 6A, 6B; Additional file 10: Figure S5A, S5B <!--%%%-->).
-<!--%%%-->Additionally, we found that when trained on cohesin-mediated chromatin loops, *preciseTAD*-predicted boundaries showed similar levels of enrichment to the set of ChIA-PET derived loop boundaries (Figure 6C; Additional file 10: Figure S5C).<!--%%%--> Surprised by the poor signal distribution around Arrowhead and Peakachu boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, <!--%%%-->Grubert,<!--%%%--> and our SpectralTAD [@Cresswell:2020ab] TAD caller.
+<!--%%%-->Additionally, we found that when trained on cohesin-mediated chromatin loops, *preciseTAD*-predicted boundaries showed similar levels of colocalization to the set of ChIA-PET derived loop boundaries (Figure 6C; Additional file 10: Figure S5C).<!--%%%--> Surprised by the poor signal distribution around Arrowhead and Peakachu boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, <!--%%%-->Grubert,<!--%%%--> and our SpectralTAD [@Cresswell:2020ab] TAD caller.
 We confirmed the poor signal distribution around Arrowhead-, Peakachu-, and SpectralTAD-called boundaries,in contrast to the well-performing Grubert-defined boundaries (<!--Additional file 10: Figure S5C, S5D--> <!--%%%-->Additional File 11: Figure S6<!--%%%-->).
 Signal enrichment heatmaps confirmed that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone<!--%%%-->, while showing similar levels of enrichment when compared to Grubert<!--%%%--> (<!--Additional file 11-12: Figure S6-S7--> <!--%%%-->Additional File 12-14: Figure S7-S9<!--%%%-->).
-*preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, <!--Figure 6A, Additional file 13: Figure S8-->  <!--%%%-->Figure 7A; Additional file 15: Figure S10<!--%%%-->).
-These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.<!--%%%-->While *preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS compared to either Arrowhead and Peakachu boundaries alone, Grubert boundaries were found to be the most spatially proximal (Wilcoxon p-value < 0.001; Figure 7A; Additional file 15: Figure S10).
+<!--%%%-->While *preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS compared to either Arrowhead and Peakachu boundaries alone, Grubert boundaries were found to be the most spatially proximal (Wilcoxon p-value < 0.001; Figure 7A; Additional file 15: Figure S10).
 These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation when compared to a novel TAD-caller or loop prediction algorithm.<!--%%%-->
@@
 
-Guided by the high predictive performance when training and testing on different cell lines (Figure 4D), we opted to evaluate whether models trained using Arrowhead/Peakachu<!--%%%-->/Grubert<!--%%%--> ground truth data in one cell line could be leveraged to predict boundaries using annotation data from another cell line.
+Guided by the high predictive performance when training and testing on different cell lines (Figure 4D), we opted to evaluate whether models trained using Arrowhead/Peakachu<!--%%%-->/Grubert<!--%%%--> ground truth data using *preciseTAD* in one cell line could be leveraged to predict boundaries using annotation data from another cell line.
 We evaluated two scenarios: 1) training on GM12878 and predicting boundaries on GM12878 (GM on GM) vs.
@@
 We show that binding of four transcription factors (SMC3, RAD21, CTCF, ZNF143) is sufficient for accurate boundary predictions.
-*preciseTAD* is implemented as an R package (version 1.1.1; Bioconductor version 3.12) and provides the pre-trained models, via an ExperimentHub R package *preciseTADhub* (version 0.99.8; Bioconductor version 3.13), which allows for precise prediction of boundaries for any cell line for which the genomic annotations are available.
+*preciseTAD* is implemented as an R package (version 1.1.1; Bioconductor version 3.12), while pre-trained boundary region prediction models are provided via an ExperimentHub R package *preciseTADhub* (version 0.99.8; Bioconductor version 3.13).
+These open source tools allow for precise prediction of boundaries for any cell line for which the genomic annotations are available.
 <!--%%%%-->
@@
 While F1-score is a composite metric, it can be susceptible to different values for precision and recall.
-Lastly, AUPRC is insensitive toward class imbalance, preventing us from investigating its effect, and also omits from its calculation TN values.
+Lastly, AUPRC is insensitive toward class imbalance, preventing us from investigating its effect, and also omits TN values from its calculation.
 All of these are important considerations to make when choosing a performance metric.
@@
 Peakachu chromatin loop boundaries called at 10 kb for the GM12878, and K562 cell lines were downloaded from the Yue lab website (Additional file 2: Table S1).
-Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop anchor.
+<!--%%%-->Additionally cohesin-mediated chromatin loops mapped via chromatin interaction analysis by paired-end tag sequencing (ChIA-PET) were downloaded for GM12878 and K562 [@grubert2020landscape] (Additional file 2: Table S1), which we refer to as *Grubert*.<!--%%%--> For loops, unique boundaries were considered as the midpoints within the coordinate of each chromatin loop anchor.
 Chromosome 9 was excluded from all downstream analyses due to the sparsity of contact matrices at 5 kb and 10 kb resolutions for the K562 cell line.
-<!--%%%-->Additionally cohesin-mediated chromatin loops mapped via chromatin interaction analysis by paired-end tag sequencing (ChIA-PET) were downloaded for GM12878 and K562 [@grubert2020landscape] (Additional file 2: Table S1), which we refer to as *Grubert*.<!--%%%--> Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Additional file 3: Table S2).
+Cell-line-specific genomic annotations (BroadHMM chromatin states (BroadHMM), histone modifications (HM), and transcription factor binding sites (TFBS)) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (Additional file 3: Table S2).
 
@@
 The *MinPts* parameter was set to the recommended value of 3, representing $1+dim(data)$ [@hahsler2019dbscan].
-To decide on the optimal value of $t$ and $\epsilon$ in *preciseTAD*, we considered the normalized enrichment $NE$ of flanked predicted boundaries, defined as
+To decide on the optimal value of $t$ and $\epsilon$ in *preciseTAD*, we considered the normalized enrichment ($NE$) of flanked predicted boundaries, defined as
 
@@
 The black line represents the predicted probability of each base being a TAD boundary.
-(B) A zoomed-in portion of the genome shows the preciseTAD boundary region (PTBR, highlighted yellow), a cluster of bases with high probability of being a boundary, and the corresponding signal profiles of CTCF, RAD21, SMC3, and ZNF143.
+(B) A zoomed-in portion of the genome shows the preciseTAD boundary region (PTBR, highlighted yellow), a cluster of bases with high probability of being a boundary, and the corresponding binding signal of CTCF, RAD21, SMC3, and ZNF143.
 
 **Figure 6.
-*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.** (C, D) Signal profile plots illustrating enrichment strength of CTCF, RAD21, SMC3, and ZNF143 sites around *preciseTAD*-predicted boundaries (green) compared to (A) Arrowhead-called boundaries (blue), (B) Peakachu loop boundaries (red), and (C) Grubert loop boundaries (purple).
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin.** Signal profile plots illustrating enrichment strength of CTCF, RAD21, SMC3, and ZNF143 sites around *preciseTAD*-predicted boundaries (green) compared to (A) Arrowhead-called boundaries (blue), (B) Peakachu loop boundaries (red), and (C) Grubert loop boundaries (purple).
 Boundaries involving Arrowhead and Grubert were flanked by 5 kb, while Peakachu-related boundaries were flanked by 10 kb.
@@
 
-**Additional File 3: Table S2.** Domain boundary data and class imbalance summaries across resolutions for Arrowhead, Peakachu, and Grubert on K562.
-
-**Additional File 4: Table S3.** A complete list of genomic annotations used to build the predictor space for all downstream models.
+**Additional File 3: Table S2.** A complete list of genomic annotations used to build the predictor space for all downstream models.
 The GRCh37/hg19 human genome assembly was used.
 “Genomic Class” - broad category of genomic features, “Element” - names of genomic features, “Cell line-Specific Source” - download URL specific to the cell line (not all annotations were provided by the same institutions).
+
+**Additional File 4: Table S3.** Domain boundary data and class imbalance summaries across resolutions for Arrowhead, Peakachu, and Grubert on K562.
 
@@
 For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability threshold (*t*) equal to 1 and epsilon-neighborhood ($\epsilon$) equal to 10000.
-For PTBPs, the start and end (start+1) coordinates define the most likely boundary point within each PTBR.
+For PTBPs, the start and end (start+1) coordinates define the most biologically meaningful boundary point within each PTBR.
 
@@
 **Additional File 14: Figure S9.
-*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Grubert boundaries.** Enrichment heatmaps comparing the signal distribution of CTCF, RAD21, SMC3, and ZNF143 around Grubert-predicted chromatin loop boundaries vs.
+*preciseTAD* boundaries are more enriched for known molecular drivers of 3D chromatin, as compared with Grubert boundaries.** Enrichment heatmaps comparing the signal distribution of CTCF, RAD21, SMC3, and ZNF143 around Grubert(ChIA-PET)-defined chromatin loop boundaries vs.
 *preciseTAD*-predicted TAD boundaries for (A) GM12878 and (B) K562 cell lines.
@@
 **Additional File 15: Figure S10.
-*preciseTAD* boundaries are spatially closer to known molecular drivers of 3D chromatin.** Boxplots comparing the log2 genomic distance distributions from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
+*preciseTAD* boundaries are spatially closer to known molecular drivers of 3D chromatin.** Boxplots comparing the $log_{2}$ genomic distance distributions from predicted and called boundaries to the nearest (A) GM12878-specific and (B) K562-specific CTCF, RAD21, SMC3, and ZNF143 transcription factor binding sites.
 p-values are derived from the Wilcoxon Rank Sum test.
@@
 Performances are averaged across each holdout chromosome that was reserved for testing.
+In conjuction with the devised machine learning framework, $\textbf{Y}_{test}$ was constructed using Grubert-defined boundaries.
 
 **Additional File 21: Figure S15.
-Normalized Enrichment levels suggest t=1.0 and $\epsilon$=10000 as the most optimal parameters for biologically relevant *preciseTAD*-predicted boundaries.** Linecharts illustrating the normalized enrichment (NE) between CTCF, RAD21, SMC3, ZNF143 and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (*t*) and epsilon-neighborhood parameter values ($\epsilon$).
-NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model.
+Normalized Enrichment levels suggest t=1.0 and $\epsilon$=10000 as the most optimal parameters for biologically relevant *preciseTAD*-predicted boundaries.** Linecharts illustrating the normalized enrichment (NE) among resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (*t*) and epsilon-neighborhood parameter values ($\epsilon$).
+NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the top 4 most predictive genomic elements (CTCF, RAD21, SMC3, and ZNF143).
 Error bars indicate 1 standard deviation from the mean.

### 2021-05-29 BMC_Genome_Biology_submission/grubert_manuscript_figures_tables/manuscript/manuscript_v1.Rmd
Start the new version

--- 2021-01-22 BMC_Genome_Biology_submission/grubert_manuscript_figures_tables/manuscript/manuscript.Rmd
@@
 
-The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of the 3-dimensional (3D) structure of the human genome such as chromatin loops [@rao20143d], Topologically Associating Domains (TADs) [@nora2012spatial;@dixon2012topological], and A/B compartments [@lieberman2009comprehensive].
-At the kilobase scale, chromatin loops connect gene promoters with distal enhancers, thereby regulating gene expression [@Lupianez:2015aa; @Franke:2016aa].
+The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of the 3-dimensional (3D) structure of the human genome such as chromatin loops [@Lupianez:2015aa; @Franke:2016aa; @rao20143d; @Phanstiel:2017uq], Topologically Associating Domains (TADs) [@nora2012spatial; @dixon2012topological; @Hou:2012aa; @sexton2012three], and A/B compartments [@lieberman2009comprehensive; @rao20143d], reviewed in [@Beagan:2020wz].
+At the kilobase scale, chromatin loops (corner-dot structures on Hi-C chromatin interaction maps) connect gene promoters with distal enhancers, promoting regulation of gene expression.
 At the megabase scale, TADs represent regions on the linear genome that are highly self-interacting.
-Emerging evidence has linked TADs to critical roles in cell dynamics and cell differentiation [@phillips2013architectural].
-Studies have shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].
-Disruption of boundaries demarcating TADs and loops promotes cancer [@hnisz2016activation; @taberlay2016three] and other disorders [@lupianez2016breaking;@Sun:2018aa;@Meaburn:2007aa].
-Thus, identifying the precise location of TAD and chromatin loop boundaries remains a top priority in our goal to fully understand the functionality of the human genome.
+Perhaps the most prominent feature of TADs is that they are demarcated by boundaries, suggesting that most of the mammalian genome is folded into non-overlapping chromatin interaction domains [@nora2012spatial; @dixon2012topological; @Hou:2012aa; @sexton2012three].
+Boundaries were found to be enriched in architectural factors such as CTCF (in convergent orientation [@rao20143d; @Tang:2015aa]), RAD21, SMC3 (members of the cohesin complex), YY1, and ZNF143 [@Dixon:2012aa; @Rao:2014aa; @Phillips-Cremins2013:aa; @Corces:2016aa; @Heidari:2014wr].
+<!--Emerging evidence has linked TADs and loops to regulation of gene expression, cellular dynamics, differentiation [@phillips2013architectural; @Beagan:2020wz].
+Studies have shown that TADs themselves are highly conserved across species and cell lines [@dixon2012topological; @krefting2018evolutionary; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa].--> Disruption of boundaries have been reported to promote human cancers [@hnisz2016activation; @taberlay2016three; @Flavahan2016], neurological disorders [@Sun:2018aa], and pathologies of limb development [@Franke:2016aa; @lupianez2016breaking].
+Thus, identifying the precise location of boundaries remains a top priority to fully understand the functionality of the human genome.
+
+TAD and loop boundaries are not mutually exclusive.
+Rao et al.
+demonstrated that boundaries of TADs, referred to as "contact domains", are enriched in chromatin loops [@rao20143d].
+Numerous observations demonstrated the presence of hierarchically nested smaller chromatin domains within TADs [@phillips2013architectural; @rao20143d], also demarcated by shared boundaries [@Norton:2018aa; @Cresswell:2020ab].
+Boundaries were shown to form by the seminal 'loop extrusion' mechanism of the molecular motors (condensin and cohesin) tracking along the DNA sequence, ‘extruding’ the intervening DNA, and pausing at the convergent CTCF motifs [@Alipour:2012aa; @Fudenberg:2016aa; @Goloborodko:2016vz].
+The loop extrusion mechanism is now a leading hypothesis for the formation of distinct classes of chromatin loops and contact domains [@Beagan:2020wz].
+In our work, we are focusing on TAD and loop boundaries created by the loop extrusion mechanism, and refer to the associated chromatin structures as "contact domains".
+
+The low-resolution of Hi-C data is a primary limitation for precise boundary detection.
+Resolution refers to the size of genomic regions (bins) used to segment the linear genome [@li2019comparison].
+Because increasing resolution of Hi-C data requires a quadratic increase in the total sequencing depth [@schmitt2016genome] and the associated costs, most available Hi-C datasets have relatively low resolution, ranging from 5 kb to 100 kb.<!--While these low-resolution Hi-C datasets can be used to probe higher-order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define TAD and loop boundaries [@fudenberg2016formation].--> Lower resolution corresponding to larger bin sizes leads to increased uncertainty in boundary location.
+
+In contrast to low-resolution Hi-C data, functional/regulatory genome annotations (histone modifications, DNAse I hypersensitive sites, DNA methylation, and transcription factor binding sites (TFBSs)) assembled by the ENCODE and other consortia have been profiled at relatively high resolution (10-300bp).
+The association of domain boundaries with CTCF and other architectural proteins [@rao20143d; @Tang:2015aa; @Phillips:2009aa] holds promise that these high-resolution marks may inform the more precise location of domain boundaries.
+Indeed, methods like Lollipop
+
+The ENCODE, NIH Roadmap Epigenomics, FANTOM5, BLUEPRINT, and other members of the International Human Epigenome Consortium (IHEC) [@Stunnenberg:2016aa] have been actively cataloging functional/regulatory genome annotation datasets, such as cell type- and tissue-specific histone modifications, DNAse I hypersensitive sites, DNA methylation, and transcription factor binding sites (TFBSs).
+
+Numerous studies demonstrated the association of domain boundaries with genomic annotations [@Dixon:2015aa; @Whalen:2016aa; @Dekker:2016aa; @Bonev:2016aa; @Wang:2016ab].
 
@@
 However, a key limitation of them is that they depend on Hi-C data *resolution*.
-Resolution refers to the size of genomic regions (bins) used to segment the linear genome [@li2019comparison].
-Lower resolutions contribute to larger bin sizes, which leads to increased uncertainty in the location of boundaries.
-Due to high sequencing costs, most available Hi-C datasets have relatively low resolution, ranging from 25 kb to 100 kb.
-While these low-resolution Hi-C datasets can be used to probe higher-order genomic patterns such as A/B compartments, more refined resolutions are necessary to accurately define TAD and loop boundaries [@fudenberg2016formation].
-Because increasing the resolution of Hi-C data requires a quadratic increase in the total sequencing depth [@schmitt2016genome], obtaining high-resolution Hi-C data and boundaries remains difficult.
 

### 2021-05-30 BMC_Genome_Biology_submission/grubert_manuscript_figures_tables/manuscript/manuscript_v1.Rmd
More WIP

@@
 
-In contrast to low-resolution Hi-C data, functional/regulatory genome annotations (histone modifications, DNAse I hypersensitive sites, DNA methylation, and transcription factor binding sites (TFBSs)) assembled by the ENCODE and other consortia have been profiled at relatively high resolution (10-300bp).
+In contrast to low-resolution Hi-C data, functional/regulatory genome annotations (histone modifications, DNAse I hypersensitive sites, DNA methylation, and transcription factor binding sites (TFBSs)) assembled by the ENCODE [@ENCODE-Project-Consortium:2012aa] and other consortia have been profiled at relatively high resolution (10-300bp).
 The association of domain boundaries with CTCF and other architectural proteins [@rao20143d; @Tang:2015aa; @Phillips:2009aa] holds promise that these high-resolution marks may inform the more precise location of domain boundaries.
-Indeed, methods like Lollipop
+Methods like Lollipop used
+
+GM12878 (lympho-blastoid), K562 (chronic myelogenous leukemia)
+
+Random forest has been used in multiple methods (Lollipop, 3dEpiLoop, Peakachu)
+
+RAD21 signal was the most predictive feature, followed by CTCF (Lollipop)
+
+Lollipop used motif strength, orientation, loop size, average sequence conservation, in-between features, gene expression.
 

### 2021-05-31 BMC_Genome_Biology_submission/grubert_manuscript_figures_tables/manuscript/manuscript_v1.Rmd
More WIP

@@
 
-The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of the 3-dimensional (3D) structure of the human genome such as chromatin loops [@Lupianez:2015aa; @Franke:2016aa; @rao20143d; @Phanstiel:2017uq], Topologically Associating Domains (TADs) [@nora2012spatial; @dixon2012topological; @Hou:2012aa; @sexton2012three], and A/B compartments [@lieberman2009comprehensive; @rao20143d], reviewed in [@Beagan:2020wz].
+The advent of chromosome conformation capture (3C) sequencing technologies, and its successor Hi-C, have revealed a hierarchy of the 3-dimensional (3D) structure of the human genome such as chromatin loops [@Lupianez:2015aa; @Franke:2016aa; @rao20143d; @Phanstiel:2017uq], Topologically Associating Domains (TADs) [@nora2012spatial; @dixon2012topological; @Hou:2012aa; @sexton2012three], and A/B compartments [@lieberman2009comprehensive; @rao20143d], reviewed in [@Beagan:2020wz; @Chang:2020vw].
 At the kilobase scale, chromatin loops (corner-dot structures on Hi-C chromatin interaction maps) connect gene promoters with distal enhancers, promoting regulation of gene expression.
@@
 Perhaps the most prominent feature of TADs is that they are demarcated by boundaries, suggesting that most of the mammalian genome is folded into non-overlapping chromatin interaction domains [@nora2012spatial; @dixon2012topological; @Hou:2012aa; @sexton2012three].
-Boundaries were found to be enriched in architectural factors such as CTCF (in convergent orientation [@rao20143d; @Tang:2015aa]), RAD21, SMC3 (members of the cohesin complex), YY1, and ZNF143 [@Dixon:2012aa; @Rao:2014aa; @Phillips-Cremins2013:aa; @Corces:2016aa; @Heidari:2014wr].
+Boundaries were found to be enriched in architectural factors such as CTCF (in convergent orientation [@rao20143d; @Tang:2015aa]), RAD21, SMC3 (members of the cohesin complex), YY1, and ZNF143 [@Dixon:2012aa; @rao20143d; @Phillips-Cremins2013:aa; @Corces:2016aa; @Heidari:2014wr].
 <!--Emerging evidence has linked TADs and loops to regulation of gene expression, cellular dynamics, differentiation [@phillips2013architectural; @Beagan:2020wz].
@@
 
-In contrast to low-resolution Hi-C data, functional/regulatory genome annotations (histone modifications, DNAse I hypersensitive sites, DNA methylation, and transcription factor binding sites (TFBSs)) assembled by the ENCODE [@ENCODE-Project-Consortium:2012aa] and other consortia have been profiled at relatively high resolution (10-300bp).
-The association of domain boundaries with CTCF and other architectural proteins [@rao20143d; @Tang:2015aa; @Phillips:2009aa] holds promise that these high-resolution marks may inform the more precise location of domain boundaries.
-Methods like Lollipop used
+In contrast to low-resolution Hi-C data, functional/regulatory genome annotations (histone modifications, DNAse I hypersensitive sites, DNA methylation, and transcription factor binding sites (TFBSs)) assembled by the ENCODE [@ENCODE-Project-Consortium:2012aa] and other consortia have been profiled at relatively high resolution (10-300bp) [@Dozmorov:2017aa].
+The one-dimensional genome annotation data has been used to predict functional chromatin contacts (e.g., HiC-Reg [@Zhang:2019aa]), boundaries of chromatin domains (e.g., Lollipop [@Kai:2018aa], 3DEpiLoop [@Al-Bkhetan:2018aa]), with 48 methods recently reviewed by Tao et al.
+[@Tao:2021uc].
+The association of domain boundaries with CTCF and other genomic annotations [@dixon2012topological; @rao20143d; @Tang:2015aa; @Phillips:2009aa; @phillips2013architectural] holds promise that these high-resolution marks may inform the more precise location of domain boundaries.
+
+3DEpiLoop predicts two types of chromatin loops, CTCF-mediated and RNAPII-mediated.
+They showed differences in genome annotation signatures with TFBSs best predicting CTCF-mediated loops and histone marks best predicting RNAPII-mediated loops, indicating differences in annotation signatures for different loop types.
+In their tests, random forest outperformed AdaBoost classification trees, neural networks, SVM, Stochastic Gradient Boosting.
 
@@
 
-Random forest has been used in multiple methods (Lollipop, 3dEpiLoop, Peakachu)
+Random forest has been used in multiple methods (Lollipop, 3dEpiLoop, Peakachu, HiC-Reg)
 
@@
 Lollipop used motif strength, orientation, loop size, average sequence conservation, in-between features, gene expression.
-
-The ENCODE, NIH Roadmap Epigenomics, FANTOM5, BLUEPRINT, and other members of the International Human Epigenome Consortium (IHEC) [@Stunnenberg:2016aa] have been actively cataloging functional/regulatory genome annotation datasets, such as cell type- and tissue-specific histone modifications, DNAse I hypersensitive sites, DNA methylation, and transcription factor binding sites (TFBSs).
-
-Numerous studies demonstrated the association of domain boundaries with genomic annotations [@Dixon:2015aa; @Whalen:2016aa; @Dekker:2016aa; @Bonev:2016aa; @Wang:2016ab].
+HiC-Reg uses histone marks, TFBSs, variants of genomic distance (loop size), multi-cell line features.
 
@@
 # Discussion
+
+Boundaries predicted by preciseTAD are dependent on the training data.
+Numerous methods for boundary detection have been proposed [@Zufferey:2018aa], with a relatively poor replicability among them [@forcato2017comparison].
+It is possible that different methods detect functionally distinct boundaries of different chromatin structures [@Beagan:2020wz; @Chang:2020vw].
+Although CTCF and architectural proteins are now considered the "canonical" marks of domain boundaries [@rao20143d; @Phillips-Cremins2013:aa; @Corces:2016aa; @Heidari:2014wr], boundaries of TADs discovered by Dixon et al.
+were also enriched in housekeeping and tRNA genes and active promoters [@Dixon:2012aa].
+, 3DEpiLoop predicts two types of chromatin loops when trained on CTCF- and RNAPII ChIA-PET data.
+These loops showed differences in genome annotation signatures with TFBSs best predicting CTCF-mediated loops and histone marks best predicting RNAPII-mediated loops.
+Our future goal include predicting boundary types other than those mediated by CTCF and cohesin.
+
+Boundaries have also been defined by different patterns of CTCF orientation [@Nanni:2020aa].
 

### 2021-06-04 BMC_Genome_Biology_submission/grubert_manuscript_figures_tables/manuscript/manuscript_v1.Rmd
WIP

@@
 In contrast to low-resolution Hi-C data, functional/regulatory genome annotations (histone modifications, DNAse I hypersensitive sites, DNA methylation, and transcription factor binding sites (TFBSs)) assembled by the ENCODE [@ENCODE-Project-Consortium:2012aa] and other consortia have been profiled at relatively high resolution (10-300bp) [@Dozmorov:2017aa].
-The one-dimensional genome annotation data has been used to predict functional chromatin contacts (e.g., HiC-Reg [@Zhang:2019aa]), boundaries of chromatin domains (e.g., Lollipop [@Kai:2018aa], 3DEpiLoop [@Al-Bkhetan:2018aa]), with 48 methods recently reviewed by Tao et al.
+The one-dimensional sequence- and genome annotation data has been used to predict functional chromatin contacts (e.g., HubPredictor [@huang2015predicting], HiC-Reg [@Zhang:2019aa]), boundaries of chromatin domains (e.g., Lollipop [@Kai:2018aa], 3DEpiLoop [@Al-Bkhetan:2018aa]), with 48 methods recently reviewed by Tao et al.
 [@Tao:2021uc].
@@
 HiC-Reg uses histone marks, TFBSs, variants of genomic distance (loop size), multi-cell line features.
+
+HubPredictor used histone marks and transcription factors [@huang2015predicting].
+
+pTADs uses chromatin states, histones, TFBSs.
+Sequence properties - DNA shape (minor groove width, propeller twist, Roll, helix twist, calculated by DNAshape program, further transformed into seven statistical values like mean, RMSE, median, min/max, SD, population deviation), DNA properties (di-/trinucleotides etc.
+139 properties total), TFBS motif occurrences (1442 PWMs), conservation score (PhastCons 46-way).
 
